### 2016-10-11 ordinal_games/ordinal_games.tex
Started Research repository

\documentclass[11pt]{article} % use larger type; default would be 10pt

\input{../common/preamble}

\title{Games with ordinal sequences of moves}
\author{John Gowers}
\date{}

\begin{document}

\begin{titlepage} % Shamelessly stolen from the online LaTeX book.
	\centering
	{\scshape\LARGE University of Bath \par}
	\vspace{1cm}
	{\scshape\Large PhD Confirmation Report \par}
	\vspace{1.5cm}
	{\huge\bfseries Games with ordinal sequences of moves \par}
	\vspace{2cm}
	{\Large\itshape John Gowers \par}
	\vfill
	supervised by\par
	Dr.~James \textsc{Laird}

	\vfill

% Bottom of the page
	{\large \today\par}
\end{titlepage}

\addtocontents{toc}{\protect\enlargethispage{35mm}}
\tableofcontents
\thispagestyle{empty}

\setcounter{tocdepth}{2}

\section{Introduction}

\lettrine[image=true, lines=6, findent=3pt, nindent=0pt]{cleos-g.png}{ame Semantics}, or the use of games and strategies to model logical systems and programming languages, has its origins in a model of intuitionistic logic by Lorenzen \cite{lorenzengames} using games.  Towards the end of the twentieth century, several authors, starting with Blass \cite{blassgames}, realized that certain natural operations on games could be used to model the connectives in Girard's linear logic.  Major results from this enterprise include:
\begin{itemize}
  \item A fully complete categorical semantics for the multiplicative fragment of linear logic, together with the MIX rule, by Abramsky and Jagadeesan \cite{abramskyjagadeesangames}
  \item A fully complete categorical semantics for the multiplicative fragment of linear logic without the MIX rule, by Hyland and Ong \cite{HylandOngGames}
  \item A modification of Abramsky and Jagadeesan's construction, giving a fully complete model of the multiplicative-exponential fragment of linear logic, by Baillot, Danos, Ehrhard and Regnier \cite{bion}
  \item Fully complete models of the negative fragment of linear logic by others, starting with independent work by Curien \cite{curiengames} and Lamarche \cite{lamarchegames}.  
\end{itemize}

Another major early result was the use of game semantics to give a fully abstract model of the programming language PCF (This result was obtained independently, using different techniques, by Abramsky, Jagadeesan and Malacaria \cite{ajmPcf}, by Hyland and Ong \cite{hoPcf}, and by Nickau \cite{nickauPcf}).

Central to much of the current work on game semantics for linear logic is the treatment of the exponential connective $\oc$.  Several approaches have been made to model this connective in a game-theoretic way (see Section 3 of \cite{martinsthesis} for a brief survey).  We shall use the construction from \cite{ajmPcf} and \cite{hyland1997games}: if $A$ is a game, then $\oc A$ is the game formed by playing a countably infinite number of copies of $A$ --- $A_0,A_1,A_2,\dots$ --- in parallel, where only the opponent $O$ may switch games and where neither player may play in game $A_{n+1}$ until a move has been made in game $A_n$.

This definition, and in particular the restriction on the order in which games may be started, allows us to give the game $\oc A$ the structure of the \emph{cofree commutative comonoid} over $A$ \cite{LairdCofCommCom} and gives rise to a \emph{linear exponential comonad} on our category of games.  The linear exponential comonad \cite{SchalkWhatIs} and the cofree commutative comonoid functor \cite{LafontCofCommCom,MelliesCofCommCom} are both sufficient to model the exponential connective from linear logic.

The restriction that says that the copies of $A$ in $\oc A$ must be opened in order, motivates the following definition \cite{laird02}: if $A,B$ are games, then the \emph{sequoid} $A\sequoid B$ of $A$ and $B$ is the game in which $A$ and $B$ are played in parallel, only the opponent $O$ may switch games, and play must start in $A$.  It turns out that if $A$ is a game, then the operation $A\sequoid\blank$ gives rise to an endofunctor on the category $\G$ of games, and that the exponential $\oc A$ is the final coalgebra for this endofunctor.  That is to say, we have a morphism $\cmap{\alpha}{\oc A}{A\sequoid\oc A}$ such that whenever $\cmap{\sigma}{B}{A\sequoid B}$ is a morphism, there is a unique morphism $\cmap{\fcoal{\sigma}}{B}{\oc A}$ such that the following diagram commutes:
\[
  \begin{tikzcd}
    B \arrow[r, "\sigma"] \arrow[d, "\fcoal\sigma"']
      & A\sequoid B \arrow[d, "A\sequoid\fcoal\sigma"] \\
    \oc A \arrow[r, "\alpha"']
      & A\sequoid\oc A
  \end{tikzcd}
  \]
Existing proofs of this fact in a finitary games setting (e.g., in \cite{martinsthesis}) make implicit use of the fact that $\oc A$ is the limit of the sequence
\[
  I \leftarrow A \leftarrow A\sequoid A \leftarrow A\sequoid(A\sequoid A) \leftarrow \dots
  \]
Indeed, any finite-length play in $\oc A$ must involve only finitely many copies of $A$, so exists as a play in $(A\sequoid\blank)^n I$ for some $n$.

On the other hand, when we start imposing winning conditions upon infinite plays, $\oc A$ is no longer the limit of the sequence above.  Indeed, define a game $\co A$ which is exactly like $\oc A$ except that all infinite plays that contain moves from infinitely many copies of $A$ are wins for the player $P$, regardless of who has won the individual games.  This game still admits a cone over the sequence above, since any play occurring in $(A\sequoid\blank)^nI$ for some $n$ must involve only finitely many copies of $A$.  Moreover, it does not admit a morphism of cones to $\oc A$.  In fact, in the infinitary setting, $\co A$, and not $\oc A$, is the limit of the above sequence.

\[
  \begin{tikzcd}
    \co A \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr] \arrow[drrrr, phantom, yshift=0.5em, "\cdots"]
      &
        &
          &
            & \\
    I
      & A \arrow[l]
        & A\sequoid A \arrow[l]
          & A\sequoid(A\sequoid A) \arrow[l]
            & \cdots \arrow[l]
  \end{tikzcd}
  \]
Applying the functor $A\sequoid\blank$ to the cone from $\co A$ gives rise to another cone over the sequence:
\[
  \begin{tikzcd}
    %
    & A\sequoid\co A \arrow[dl] \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr, phantom, yshift=0.5em, "\cdots"]
        &
          &
            & \\
    I
      & A \arrow[l]
        & A\sequoid A \arrow[l]
          & A\sequoid(A\sequoid A) \arrow[l]
            & \cdots \arrow[l]
  \end{tikzcd}
  \]
and therefore a morphism $A\sequoid\co A\to \co A$.  We can then continue to apply the functor $A\sequoid\blank$ to build up a second layer of the sequence:
\[
  \begin{tikzcd}
    \co A \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr] \arrow[drrrr, phantom, xshift=1em, "\cdots"]
      & A\sequoid\co A \arrow[l]
        & A\sequoid(A\sequoid \co A) \arrow[l]
          & A \sequoid(A\sequoid(A\sequoid\co A)) \arrow[l]
            & \cdots \arrow[l] \\
    I
      & A \arrow[l]
        & A\sequoid A \arrow[l]
          & A\sequoid(A\sequoid A) \arrow[l]
            & \cdots \arrow[l]
  \end{tikzcd}
  \]
What is the limit of this entire diagram?  An $O$-winning infinite play $s$ in $(A\sequoid\blank)^n \co A$ may be identified with an $O$-winning play in $\oc A$ such that either the opponent $O$ wins in one of the games $A_1,\dots,A_n$ or that only finitely many copies of $A$ are opened.  It follows that the limit of the diagram \emph{is} the final coalgebra $\oc A$.

The diagrams we have drawn above are special cases of the \emph{final sequence} \cite{finalseq}: given a category $\C$ with a terminal object $1$ and enough limits (in a sense which will become clear) and an endofunctor $\cmap{\F}{\C}{\C}$, we may construct an ordinal-indexed sequence
\[
  1, \F(1), \F^2(1),\dots \F^\omega(1), \F^{\omega+1}(1),\dots,\F^\delta(1),\dots
  \]
together with commuting morphisms $\F^\gamma(1)\to\F^\delta(1)$ for $\delta\le\gamma$, by setting $\F^{\delta+1}(1) = \F(\F^\delta(1))$ and letting $\F^\mu(1)$ be the limit of the diagram formed by the $\F^\gamma(1)$ for $\gamma<\mu$ if $\mu$ is a limit-ordinal.  It is well known that if $\delta$ is an ordinal and the map
\[
  \F^{\delta+1}(1)\to\F^{\delta}(1)
  \]
is an isomorphism, then the inverse of this isomorphism exhibits $\F^{\delta}(1)$ as the final coalgebra of $\F$.  In this case, we say that the final sequence \emph{stabilizes at $\delta$}.

In the case of finitary games, then, we have
\[
  \oc A\cong(A\sequoid\blank)^\omega(I)
  \]
and in the infinitary case, we have
\[
  \oc A\cong(A\sequoid\blank)^{\omega2}(I)
  \]
The eventual goal of this research is to study the behaviour of the final sequence of the functor $A\sequoid\blank$ in categories of games.  Since the sequence stabilizes so early on for existing categories of games, this question is not very interesting in that setting.  We want to modify our definitions of games in such a way that this final sequence will take much longer to stabilize, and it turns out that one way to do that is to allow plays of transfinite length.

Games with ordinal sequences of moves are not a new idea.  They have, for example, been studied in \cite{longgamesbook} from the point of view of determinacy.  Even in game semantics, as we shall see, we may identify games in which we impose a winning condition on the infinite plays with games in which the players are allowed to make plays of length $\omega$ -- we shall call these $(\omega+1)$-games, in contrast to the finitary games, which we shall call $\omega$-games.  Allowing plays whose lengths are longer transfinite ordinals will give rise to a richer variety of plays, which will be reflected in the final sequence.

One important aspect of the shift from finite to transfinite plays is that the idea of a \emph{play} or \emph{position} takes on a new importance, in contrast to the finitary case, where we can define everything in terms of \emph{moves}.  Normally, a move is designated as either a $P$-move or an $O$-move; we will extend this so that every position is either a $P$-position or an $O$-position.  A position $s$ will be an ordinal-indexed sequence of moves; if there is a last move $a$, then $s$ is a $P$-position or an $O$-position according as $a$ is a $P$-move or an $O$-move.  If the length of $s$ is a limit ordinal, however, then its sign cannot be determined from the signs of its constituent moves.  This is useful if we want to model games with a winning condition as $(\omega+1)$-games: a play of length $\omega$ in a game corresponds to an infinite play in that game, and its designation as a $P$-position or $O$-position is essentially the same thing as saying whether it is a $P$-winning or $O$-winning play.

This approach is similar to that of Blass \cite{blassgames}, and indeed our treatment of $P$-positions and $O$-positions under the connectives will follow his approach.  For example, a position $s$ in a tensor product $A\tensor B$ is a $P$-position if and only if its restrictions to $A$ and $B$ are both $P$-positions.

To avoid certain mathematical difficulties, we shall follow Curien, Lamarche and others by requiring that our games be \emph{negative} -- that is, they must always begin with an $O$-move.  In fact, we shall go further than that: under the usual alternating condition, saying that $O$ always starts is the same thing as requiring that the empty position $\emptyplay$ is a $P$-position.  In order to avoid problems constructing our category, we shall need to require that \emph{all} positions whose lengths are limit ordinals be $P$-positions.  We shall call games satisfying this property \emph{completely negative}.

This condition on the sign of games allows us to construct a well-behaved category of games, but it has one serious problem that occurs as soon as we consider games with transfinite-length plays: if $A,B$ are completely negative games, then the linear implication $A\implies B$ is not necessarily completely negative.

We want $A\implies B$ to be the internal hom in our closed monoidal category, so we need to find a way around this.  Our solution is to construct, for every game $A$, a `minimal extension' $A^{\cn}$ of $A$ that is completely negative.  We prove various results about the relationship $A^{\cn}$ and $A$ that make this precise and then use them to show that the game $A\impliescn B\coloneqq (A\implies B)^{\cn}$ does give rise to a closed monoidal structure in our category.  We also give a tentative way of constructing a category whose objects are \emph{all} games, not just the completely negative ones, and use our results to show that this category is in fact equivalent to our existing category of completely negative games.

Having constructed a symmetric monoidal closed category of games, we introduce the sequoid operator and the exponential, and study the final sequence.  We shall characterize the exponential $\oc A$ as a final coalgebra for the functor $A\sequoid\blank$ and use this characterization to prove that $\oc A$ admits the structure of a cofree commutative comonoid on $A$.  Then we turn to the final sequence.  This section will involve some material that is more ordinal-theoretic than game-theoretic; we assign an ordinal \emph{rank} to a (transfinite) sequence of natural numbers and then show that this idea of rank can be used to characterize each term of the final sequence for a functor of the form $A\sequoid\blank$.  We will show that the reason that the final sequences converge so quickly for finitary games and win-games is that a sequence of length $\omega$ necessarily has low rank: once we allow longer plays, we can get sequences with higher ranks and the final sequence will carry on for longer.

\subsection{Original contribution}

Games with ordinal sequences of enablings have been studied by Laird from a Game Semantics point of view \cite{LairdOrdinalGames}, but to my knowledge this is the first transfinite games category built in the tradition of Abramsky and Jagadeesan.  Passing to transfinite games causes problems when we try to show that our category is monoidal closed, and we have to come up with new techniques in order to get a monoidal closed category (see Sections \ref{TransSMCCSex} to \ref{ImpliesCnSex}).

The characterization of the final coalgebra for the functor $A\sequoid\blank$ in a transfinite games category is new, though the behaviour in finitary game categories and win-game categories is well known.  Our definition of the rank of a sequence of natural numbers is heavily motivated by the game semantics, so it is likely that this is new too (though similar constructions of ordinal ranks of objects are common in mathematics).

Otherwise, most of the material in this report is a straightforward translation of the existing game semantics of Abramsky, Jagadeesan, Hyland, Ong, Curien, Lamarche and so on into the transfinite setting.

\subsection{Conventions}

I shall denote the composition of morphisms $A\xrightarrow{\sigma}B\xrightarrow{\tau}C$ by $\comp\tau\sigma$, the disjoint union of two sets $X,Y$ by $X\cprd Y$ and the corresponding copairing of two functions $\map{f}{X}{Z},\map{g}{Y}{Z}$ by $\cmap{f\cprd g}{X\cprd Y}{Z}$.

Following the $\forall$belard/$\exists$loise convention that is sometimes used for Opponent/Player, I shall refer to the opponent $O$ as `he' and the player $P$ as `she' throughout.

\subsection{Acknowledgements}

It goes without saying that I owe my biggest debt of gratitude for the material in this report to my supervisor, Jim Laird.  Dr Laird introduced me to Game Semantics a year ago and suggested my initial direction of research in the subject, and his insights and instinct for the subject have been invaluable in the development of the material contained in this report, and in the preparation of the report itself -- particularly when things were going wrong.  Dr Laird gave me some extremely useful feedback on an earlier draft of this report and supplied some of the details for the material in section \ref{SeqExpIsCofCommCom}.

I am indebted to all the authors listed in the Bibliography, but I single out the seminal papers of Blass \cite{blassgames} and Abramsky-Jagadeesan \cite{abramskyjagadeesangames} for their development of the subject and their clear presentation of their full completeness results, the set of notes on Game Semantics by Martin Hyland \cite{hyland1997games} and the excellent online notes by Andrea Schalk \cite{Schalk2001GsNotes,SchalkWhatIs}.  I also single out the PhD thesis of Martin Churchill \cite{martinsthesis}, prepared under Dr Laird's supervision.  The work in this report can be seen as a partial sequel to some of Dr Churchill's work, and the clear presentation in his thesis has greatly helped in this task.

I would also like to extend my thanks to Paul Blain Levy for his work organizing the GaLoP 2016 conference and the Midlands Graduate School 2016, both of which I attended this year.  I presented some of this material at GaLoP and the questions and comment I received there have shaped the course of this work.  Thanks also to Alexander Kurz for his lectures on coalgebra at the Midlands Graduate School.

Thanks go to all my friends and family members who have patiently supported me while I embarked on this research.  Thank you to CN for designing the splendid letter `G' (complete with $\sequoid$ symbols!) that features at the beginning of this introduction.

\section{Our starting category of games}

Before studying games with transfinite sequences of moves, we shall illustrate some of the choices we have made by defining a category of games with finite sequences of moves.  We have chosen these definitions because they extend particularly well to the transfinite case.

\subsection{Games and strategies}

We shall use the notation introduced in \cite{abramskyjagadeesangames} to describe games.  All our games $A$ will have, at their heart, the following three pieces of information:
\begin{itemize}
  \item A set $M_A$ of possible moves
  \item A function $\cmap{\lambda_A}{M_A}{\OP}$ assigning to each move the player who is allowed to make that move
  \item A prefix-closed set $P_A\subset M_A^*$ of finite sequences of moves.
\end{itemize}
We shall normally insist on an \emph{alternating condition} on $P_A$:
\begin{description}
  \item[Alternating condition] If $a,b\in M_A$ are moves and $s\in M_A^*$ is a sequence of moves such that $sa, sab\in P_A$, then $\lambda_A(a)=\neg\lambda_A(b)$.
\end{description}

As in \cite{abramskyjagadeesangames}, we identify a \emph{strategy} for a game $A$ with the set of sequences of moves that can occur when player $P$ is playing according to that strategy so that a typical definition of a (partial) strategy might be a set $\sigma\subset P_A$ such that (for all $s\in M_A^*, a,b\in M_A$):
\begin{itemize}
  \item $\emptyplay\in\sigma$ (ensures that $\sigma$ is non-empty)
  \item If $sa\in\sigma$, $\lambda_A(a)=P$ and $sab\in P_A$ then $sab\in\sigma$ ($\sigma$ contains all legal replies by player $O$)
  \item If $s,sa,sb\in\sigma$ and $\lambda_A(a)=P$ then $a=b$ ($\sigma$ contains at most one legal reply by player $P$)
\end{itemize}

We can impose additional constraints on $\sigma$ that will ensure that $\sigma$ is total, strict, history free and so on.  The definition given immediately above is not the only definition of a strategy found in the literature, however.  For example, the games described in \cite{abramskyjagadeesangames} have the curious property that the set $P_A$ may contain plays that cannot actually occur when $A$ is being played; in particular, all plays must start with a move by player $O$, but the set $P_A$ may contain positions that start with a $P$-move.  These plays do not affect the strategies for $A$, but they might come into play if we perform operations on $A$ such as forming the negation $\neg A$ or the implication $A\implies B$.

This behaviour is made implicit in Abramsky and Jagadeesan's definitions, which do not impose any conditions upon the set $P_A$ beyond the basic alternation condition given above, but which mandate that any play occurring \emph{in a strategy} must begin with an $O$-move.  For the sake of clarity, we adopt a different, but completely equivalent, approach.  For a game $A$, we define a set $L_A$, regarded as the set of \emph{legal plays} occurring in $P_A$.  In some games models, such as that found in \cite{blassgames}, $L_A$ may be defined to be the whole of $P_A$, while in \cite{abramskyjagadeesangames} it is defined to be that subset of $P_A$ consisting of plays that begin with an $O$-move.

The point of specifying $L_A$ separately is that it allows us to unify the definition of a \emph{strategy}, while making clearer the behaviour observed above, whereby certain plays in $P_A$ may not occur `in normal play'; this behaviour was previously only implicit in the definition of a strategy.  Our unified definition then becomes:

\begin{definition}
  If $A=(M_A,\lambda_A,P_A)$ is a game and $L_A$ is its associated set of legal plays (in a particular games model) then a (partial) \emph{strategy} for $A$ is a subset $\sigma\subset L_A$ such that for all $s\in L_A$ and all $a, b\in M_A$:
  \begin{itemize}
    \item $\emptyplay\in\sigma$
    \item If $s\in\sigma$ and $a$ is an $O$-move, and if $sa\in L_A$, then $sa\in\sigma$
    \item If $s\in\sigma$ and $a,b$ are $P$-moves, and if $sa,sb\in\sigma$, then $a=b$
  \end{itemize}
\end{definition}

\subsection{Positive and negative games, ownership of plays and connectives}

Abramsky-Jagadeesan games, as described in \cite{abramskyjagadeesangames}, may admit both plays that start with a $P$-move and plays that start with an $O$-move.  Other games models, such as those found in \cite{blassgames} and \cite{curiengames}, are more restrictive.  The games in \cite{curiengames} only contain plays starting with an $O$-move.  The plays in \cite{blassgames} may start with either a $P$-move or an $O$-move, but a play starting with a $P$-move and a play starting with an $O$-move may not occur in the same game.

\begin{definition}
  We say that a game $A=(M_A,\lambda_A,P_A)$ is \emph{positive} if every play in $P_A$ begins with a $P$-move.
  We say that $A$ is \emph{negative} if every play in $P_A$ begins with an $O$-move.
\end{definition}

So the Curien model found in \cite{curiengames} admits only negative games, the Blass model in \cite{blassgames} admits positive and negative games, while the Abramsky-Jagadeesan model found in \cite{abramskyjagadeesangames} admits not only positive and negative games, but also games that are neither negative nor positive.  We shall now examine the reasons for and drawbacks of each of these choices.

The earliest games model, found in \cite{conwaygames}, did not include a definition of which player is to move at a given position; rather, games are defined recursively as pairs of games $\{L|R\}$, where $L$ represents the positions that the left player may move into, while $R$ represents the positions that the right player may move into.  Blass's definition departs completely from this tradition; now, at every position $s$ only one of the two players is allowed to move; extending this logic on to the empty position $\emptyplay$, it follows that all games are either positive or negative.  This property means that we may freely define $L_A=P_A$, since there is never any question about whose turn it is to play.  By contrast, if we were to define $L_A=P_A$ for Abramsky-Jagadeesan games, then a strategy might end up containing two branches, one of plays beginning with an $O$-move and one of plays beginning with a $P$-move, which is undesirable.  The alternative definition of $L_A$ avoids this problem.

In the case of a Blass game $A$, we may define a function $\zeta_A\colon P_A\to\OP$ that says which player owns each play; the idea is that if we are in position $s$, then the next player to move is given by $\neg\zeta_A(s)$; i.e., the opposing player to the player who has just made the move.  One might want to define $\zeta_A$ by setting $\zeta_A(sa)=\lambda_A(a)$, so that ownership of a play is decided by who has made the last move in the play, but this definition does not extend in an obvious way to the empty position $\emptyplay$ (and, as we shall see in the next chapter, it does not extend to plays over limit ordinals).  In this case, $\zeta_A(\emptyplay)$ is part of the game's data, and it determines whether the game is positive or negative: if $\zeta_A(\emptyplay) = P$ then all plays must start with an $O$-move, and the game is negative -- and vice versa.

An important question then arises: how should we extend the function $\zeta_A$ to games formed from connectives?  The solution adopted by Blass is to use binary conjunctions to deduce the ownership of a play from the ownership of the restrictions of that play to the two component games.  In the case of the tensor product $A\tensor B$ of two games $A$ and $B$, we define $\cmap{\zeta_{A\tensor B}}{P_{A\tensor B}}{\OP}$ by setting
\[
  \zeta_{A\tensor B}(s) = (\zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B))
  \]
where $\cmap{\wedge}{\OP\times \OP}{\OP}$ is as in Figure \ref{truthtables}.

\begin{figure}[h]
  \begin{center}
    $\begin{array}{cc|c}
      a & b & a \wedge b \\
      \hline
      O & O & O \\
      O & P & O \\
      P & O & O \\
      P & P & P
    \end{array}$
    \quad
    $\begin{array}{cc|c}
      a & b & a \vee b \\
      \hline
      O & O & O \\
      O & P & P \\
      P & O & P \\
      P & P & P
    \end{array}$
    \quad
    $\begin{array}{cc|c}
      a & b & a \Rightarrow b \\
      \hline
      O & O & P \\
      O & P & P \\
      P & O & O \\
      P & P & P
    \end{array}$
    \caption{Truth tables for binary conjunctions on $\OP$}
    \label{truthtables}
  \end{center}
\end{figure}

Similarly, we may extend $\zeta$ to the implication $A\implies B$ and the par $A\parr B$ by setting
\begin{align*}
  \zeta_{A\implies B}(s)=(\zeta_A(s\vert_A)\Rightarrow \zeta_B(s\vert_B))\\
  \zeta_{A\parr B}(s) = (\zeta_A(s\vert_A) \vee \zeta_B(s\vert_B))
\end{align*}

Note that if we use these definitions then the owner $\zeta_C(sa)$ of a play $sa$ might not correspond to the player $\lambda_C(a)$ who played the last move $a$.  For example, let $A,B$ be two positive games and form their tensor product $A\tensor B$.  Then we have
\[
  \zeta_{A\tensor B}(\emptyplay) = (\zeta_A(\emptyplay) \wedge \zeta_B(\emptyplay)) = O \wedge O = O
  \]
and so $A\tensor B$ is a positive game.  Player $P$ plays an opening move in one of the two games - let us say she plays the move $a$ in the game $A$.  But then we have
\[
  \zeta_{A\tensor B}(a) = (\zeta_A(a) \wedge \zeta_B(\emptyplay)) = P \wedge O = O
  \]
In other words, it is still player $P$'s turn to play!  Blass embrace this possibility and allows player $P$ to make these two moves.  In his paper, he introduces the notions of \emph{strict} and \emph{relaxed} games, where the strict games are the objects of study but the relaxed games are often used since they allow more manipulations.  In this case, the game $A\tensor B$ is defined as a relaxed game that might not satisfy the alternating condition; in the process of converting it into a strict game, these two opening moves by player $P$ are combined into a single move.

This `double move' can only occur at the start of the game, and Blass treats it as a special case in his proofs.  Perhaps unsurprisingly, this inconsistency causes major problems if we try to compose strategies.  We do not get an associative composition of strategies for $A\implies B$ with strategies for $B\implies C$ and so we do not get a categorical semantics.  An example of the failure of associativity in Blass's games model is given towards the end of \cite{abramskyjagadeesangames}.

By contrast, Abramsky-Jagadeesan games may admit moves by both players at the same position (specifically, at the beginning of the game, before any moves have been played), but this does not cause problems since we insist that our legal plays start with an $O$-move and be strictly alternating.  The authors of \cite{abramskyjagadeesangames} note that their model can be considered as an intermediate between Conway's games, where the position tells you nothing about which player is to move, and Blass games, where the position completely determines which player is to move.  In Abramsky-Jagadeesan games, one can deduce which player is to move (by looking at which player made the last move) in every position except the empty starting position.

In the Abramsky-Jagadeesan model, a positive game is an immediate win to player $P$, since player $O$ has no legal move to start the game off.  As we noted before, this does not mean that the content of a positive game is meaningless, since we can use connectives to `unlock' these illegal plays.  For example, if $Q$ is a positive game and $N$ is a negative game then $Q\parr N$ is a negative game, and the possible positions in $Q$ are now all achievable.

Curien's game model (\cite{curiengames}) is similar to Abramsky's and Jagadeesan's, but involves only negative games.  The only slight problem is that negative Abramsky-Jagadeesan games are not closed under implication: if $N,L$ are negative games then $N\implies L$ may be neither negative nor positive.  We may fix this by modifying the definition of $N\implies L$ so that we delete from $P_{N\implies L}$ all plays that start with a $P$-move - or, equivalently, by requiring that all plays start in $L$.  This is the approach taken in \cite{martinsthesis}, where it fits well with the paper's treatment of the \emph{sequoid} operator $\sequoid$, which is a version of the tensor product that has been modified so that play is required to start in the left-hand game.

Our approach will be similar to that of Curien's in that we will admit only negative games as objects of our category, but we will also incorporate elements of Blass's model: each position $s$ in our game will be designated either an $O$-position or a $P$-position via a function $\zeta$ and we will extend $\zeta$ to the connectives using the truth tables in Figure \ref{truthtables}.  We shall start by developing the theory of finitary games in order to illustrate our approach, but it will not be until we start considering transfinite games that we see the value of this aspect of Blass's semantics: transfinite games may contain many non-empty plays that have no last move and we will want to designate them as $P$-positions or $O$-positions so that we know which player moves next.

\subsection{Our definition of games and strategies}

\begin{definition}
  A \emph{game} is a triple $(M_A,\lambda_A,\zeta_A,P_A)$ where
  \begin{itemize}
    \item $M_A$ is a set of moves,
    \item $\cmap{\lambda_A}{M_A}{\OP}$ is a function that assigns a player to each move,
    \item $P_A\subset M_A^*$ is a non-empty prefix-closed set of plays that can occur in the game and
    \item $\cmap{\zeta_A}{P_A}{\OP}$ is a function that assigns a player to each position
  \end{itemize}
  such that
  \begin{itemize}
    \item If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.
    \item If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s)=\neg\zeta_A(sa)$.
  \end{itemize}
\end{definition}

\begin{remark}[Notes on the definition]
  Given a game $A=(M_A,\lambda_A,\zeta_A,P_A)$, define $b_A=\neg\zeta_A(\emptyplay)$.  Then every play in $P_A$ must start with a $b_A$-move, so $A$ is either positive or negative.

  Note that $\zeta_A$ is now completely specified by $\lambda_A$ and $b_A$, so we could have specified our games more efficiently by replacing $\zeta_A$ with $b_A$ in our definition, as done in \cite{martinsthesis}.  The slightly more unwieldy $\zeta_A$ will be useful when we come to extend our games over the ordinals, though, so we retain it.

  If $a\in M_A$ then we may recover $\lambda_A(a)$ from $\zeta_A$ so long as $a$ occurs in some play in $P_A$.  Since moves that can never be played do not affect the game at all, we do not really need $\lambda_A$ in our definition, but we keep it to make the connection to earlier work clearer.

  If $a\in M_A$ and $\lambda_A(a)=O$, we call $a$ an \emph{$O$-move}.  If $\lambda_A(a)=P$, we call $a$ a \emph{$P$-move}.  If $s\in P_A$ and $\zeta_A(s)=O$, we call $s$ an \emph{$O$-play} or \emph{$O$-position}.  If $\zeta_A(s)=P$, we call $s$ a \emph{$P$-play} or \emph{$P$-position}.
\end{remark}

We give the usual definition of a strategy as an appropriate subset of $P_A$, where we have identified the strategy with the set of all plays that can arise when player $P$ plays according to that strategy:

\begin{definition}
  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  A \emph{strategy} for $A$ is a non-empty prefix-closed subset $\sigma\subset P_A$ such that:
  \begin{itemize}
    \item If $a\in P_A$ is an $O$-move and $s\in\sigma$ is a $P$-position such that $sa\in P_A$, then $sa\in\sigma$.
    \item If $s\in\sigma$ is an $O$-position and $a,b\in M_A$ are $P$-moves such that $sa,sb\in\sigma$, then $a=b$.
  \end{itemize}
\end{definition}

The definition above will be the most technically useful, but it is also convenient to give a strategy by a partial function that tells player $P$ which move to make in each $O$-position.  If we write $P_A^-=\zeta_A\inv(\{O\})$ for the set of all $O$-positions and $M_A^+=\lambda_A\inv(\{P\})$ for the set of all $P$-moves, then the strategy $\sigma$ above gives rise to a partial function $\hat\sigma\from P_A^-\pfun M_A^+$ given by:
\[
  \hat\sigma(s)=
  \begin{cases}
    a & \textrm{if $a\in M_A^+$ and $sa\in P_A$}\\
    \textrm{undefined} & \textrm{if $sb\not\in P_A$ for all $b\in M_A^+$}
  \end{cases}
  \]
The second condition on strategies tells us that this is well defined.  Going in the other direction, if we are given a partial function $f\from P_A^-\pfun M_A^+$  then we can define a strategy $\overline{f}$ by
\[
  \overline f = \{s\in M_A^*\suchthat \textrm{for all $ta\prefix s$ with $\zeta_A(t)=O$, $f(t)$ is defined and equal to $a$}\}
  \]

\subsection{Connectives}

Our definitions of connectives on games are as in \cite{blassgames}.

\begin{definition}
  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  The negation of $A$, $\neggame{A}$, is the game formed by interchanging the roles of the two players.
  \begin{itemize}
    \item $M_{\bneggame A}=M_A$
    \item $\lambda_{\bneggame A} = \comp\neg{\lambda_A}$
    \item $\zeta_{\bneggame A} = \comp\neg{\zeta_A}$
    \item $P_{\bneggame A} = P_A$
  \end{itemize}
\end{definition}

It follows immediately from the definitions that $\neggame A$ is a well formed game.

We now define the tensor product $A\tensor B$, the par $A\parr B$ and the linear implication $A\implies B$ of two games.  All these games are obtained by playing $A$ and $B$ in parallel, so they all have the same set of moves:
\[
  M_{A\tensor B} = M_{A\parr B} = M_{A\implies B} = M_A \cprd M_B
  \]

Ownership of moves is decided via the obvious co-pairing functions:
\begin{IEEEeqnarray*}{c}
  \lambda_{A\tensor B} = \lambda_{A\parr B} = \lambda_A \cprd \lambda_B\\
  \lambda_{A\implies B} = (\neg\circ\lambda_A) \cprd \lambda_B
\end{IEEEeqnarray*}

We define the set $P_A\|P_B$ to be the set of all plays in $(M_A \cprd M_B)^*$ whose $M_A$-component is a play from $P_A$ and whose $M_B$-component is a play from $P_B$:
\[
  P_A\|P_B = \{s\in (M_A\cprd M_B)^*\suchthat s\vert_A\in P_A,\; s\vert_B\in P_B\}
  \]

We are now in a position to define $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$ as functions $P_A\|P_B\to\OP$:
\begin{IEEEeqnarray*}{rCl}
  \zeta_{A\tensor B}(s) & = & \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \\
  \zeta_{A\parr B}(s) & = & \zeta_A(s\vert_A) \vee \zeta_B(s\vert_B) \\
  \zeta_{A\implies B}(s) & = & \zeta_A(s\vert_A) \Rightarrow \zeta_B(s\vert_B)
\end{IEEEeqnarray*}

(Here, $\wedge$, $\vee$ and $\Rightarrow$ are as in Figure \ref{truthtables}.)

As things stand, $P_A\|P_B$ is not a valid set of plays for our $\lambda$ and $\zeta$ functions.  The first problem is that $P_A\|P_B$ contains plays which are not alternating with respect to $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$.  The second problem is that the $\zeta$ and $\lambda$ functions do not always agree with one another.  For example, suppose that $Q,R$ are two positive games.  So we have $\zeta_Q(\emptyplay) = \zeta_R(\emptyplay) = O$.  Then $\zeta_{Q\tensor R}(\emptyplay) = O\wedge O = O$.  But now suppose that player $P$ can make an opening move $q$ in $Q$.  Then we have
\[
  \zeta_{Q\tensor R}(q) = \zeta_Q(q) \wedge \zeta_R(\emptyplay) = P \wedge O = O
  \]
but $\lambda_{Q\tensor R}(q) = P$.

Our solution is to throw away some plays from $P_A\| P_B$ so that what remains satisfies the alternating condition and the condition on the $\lambda$ and $\zeta$ functions.

\begin{definition}
  Let $M$ be a set, let $P\subset M^*$ be prefix closed and let $\cmap{\lambda}{M}{\OP},\cmap{\zeta}{P}{\OP}$ be functions.  If $s\in P$, we say that $s$ is \emph{alternating with respect to $\zeta$} if the set of prefixes of $s$ satisfies the alternating condition: if $t,ta\prefix s$, then $\zeta(t) = \neg\zeta(ta)$.

  We say that $s$ is \emph{well formed with respect to $\lambda,\zeta$} if whenever $ta\prefix s$, for some $a\in M$, we have $\zeta(ta)=\lambda(a)$.

  Now let $A,B$ be games.  We define:
  \begin{IEEEeqnarray*}{rCl}
    P_{A\tensor B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\tensor B}$ \\ $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$}}\right\} \\
    P_{A\parr B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\parr B}$ \\ $s$ is well formed with respect to $\zeta_{A\parr B},\lambda_{A\parr B}$}}\right\} \\
    P_{A\implies B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\implies B}$ \\ $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$}}\right\}
  \end{IEEEeqnarray*}
\end{definition}

\begin{definition}
  We define:
  \begin{IEEEeqnarray*}{cCc}
    A\tensor B & = & (M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B}) \\
    A\parr B & = & (M_{A\parr B}, \lambda_{A\parr B}, \zeta_{A\parr B}, P_{A\parr B}) \\
    A\implies B & = & (M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})
  \end{IEEEeqnarray*}
\end{definition}

\begin{proposition}
  $A\tensor B$,$A\parr B$,$A\implies B$ are well formed games.  Moreover, $P_{A\tensor B}$ is the largest subset $X\subset P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, X)$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.  
  \begin{proof}
    We will prove the proposition for $A\tensor B$; the other two cases are entirely similar.  Alternatively, observe that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$ and $A\implies B = \neggame A \parr B$.

    For $A\tensor B$, it suffices to show that $P_{A\tensor B}$ is alternating with respect to $\zeta_{A\tensor B}$, since every $s\in P_{A\tensor B}$ is well-formed by definition.  Suppose $s,sa\in P_{A\tensor B}$; then $s,sa\prefix sa$; since $sa$ is alternating with respect to $\zeta_{A\tensor B}$, it follows that $\zeta_{A\tensor B}(s) = \neg\zeta_{A\tensor B}(sa)$.

    For the second part of the proposition, suppose that $V\subset P_A\|P_B$ is prefix-closed and satisfies the alternating condition with respect to $\zeta_{A\tensor B}$ and that every $s\in V$ is well-formed with respect to $\lambda_{A\tensor B},\zeta_{A\tensor B}$.  We need to show that $V\subset P_{A\tensor B}$, for which it will suffice to show that every $s\in V$ is alternating.  This is easy to see: since $V$ is prefix closed, the set of all prefixes of $s$ is a subset of $V$, and so it satisfies the alternating condition with respect to $\zeta_{A\tensor B}$.  
  \end{proof}
\end{proposition}

A design feature of the connectives $\tensor,\parr,\implies$ is that only player $O$ may switch games in $A\tensor B$, while only player $P$ may switch games in $A\parr B$ and $A\implies B$.  The $\implies$ case follows immediately from the $\parr$ case by noting that $A\implies B = \neggame A\parr B$, and the $\parr$ case then follows from the $\tensor$ case by observing that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$.  Thus, it will suffice to prove the following proposition for the tensor product:

\begin{proposition}
  \label{WhoSwitchesGames}
  Let $A,B$ be games.  Suppose $s\in P_{A\implies B}$, $a\in M_A$ and $b\in M_B$.  Then:

  i) If $sab\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(b)=O$

  ii) If $sba\in P_{A\tensor B}$ then $\lambda_{\tensor B}(a)=O$.

  \begin{proof}

    (i): $\begin{aligned}[t]
      \lambda_{A\tensor B}(b) & = \zeta_{A\tensor B}(sab) \\
       & = \zeta_{A\tensor B}(s\vert_A a) \wedge \zeta_{A\tensor B}(s\vert_B b) \\
       & = \lambda_{A\tensor B}(a) \wedge \lambda_{A\tensor B}(b)
    \end{aligned}$

    By alternation, either $\lambda_{A\tensor B}(a)=O$ or $\lambda_{A\tensor B}(b)=O$, so this last expression must be equal to $O$.

    (ii): \noindent$\begin{aligned}[t]
      \lambda_{A\tensor B}(a) & = \zeta_{A\tensor B}(sba) \\
       & = \zeta_{A\tensor B}(s\vert_A a) \wedge \zeta_{A\tensor B}(s\vert_B b) \\
       & = \lambda_{A\tensor B}(a) \wedge \lambda_{A\tensor B}(b) = O\textrm{ (by the same argument)} && \quad\;\qedhere
    \end{aligned}$
  \end{proof}
\end{proposition}

\subsection{A category of games and partial strategies}
\label{CategoricalSemantics}

Following \cite{joyalgames} and \cite{abramskyjagadeesangames}, we define a category $\G$ whose objects are games where the morphisms from a game $A$ to a game $B$ are strategies for $A\implies B$.  For the sake of simplicity, and to avoid various technical issues, we shall require that the games in our category be \emph{negative} - namely, they should start with an opponent move.  In our language, we call a game $A$ \emph{negative} if $\zeta_A(\emptyplay)=P$ (and we call it positive if $\zeta_A(\emptyplay)=O$).  The equations
\begin{gather*}
  P \wedge P = P \\
  P \Rightarrow P = P
\end{gather*}
tell us that the class of negative games is closed under $\tensor$ and $\implies$ (since $P\vee P=P$, it is also closed under $\parr$, but the par of two negative games has no legal moves in our presentation, so it does not give a good model of the $\parr$ connective in linear logic and we will not consider it).

In order to get a category, we need a way to compose a strategy for $A\implies B$ with a strategy for $B\implies C$.  Our treatment of composition is heavily influenced by work done by Hyland and Schalk (see \cite{hyland1997games}, \cite{hylandschalkgames} and the excellent set of notes \cite{Schalk2001GsNotes}).

We shall use the usual definition of composition.  If $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, we define a set
\[
  \sigma\|\tau = \{\s\in (M_A \cprd M_B \cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
  \]
Then we define the composite strategy on $A\implies C$ to be
\[
  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
  \]
The process of showing that this is indeed a strategy for $A\implies C$, and that composition is associative, will be quite involved.  We shall start by recording some nice properties of negative games that will tell us that $\comp\tau\sigma$ is alternating:

\begin{proposition}
  Let $A,B$ be negative games and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\tensor B}$.  Then:
  \begin{enumerate}[i)]
    \item Either $\zeta_{A}(s\vert_A)=P$ or $\zeta_{B}(s\vert_B)=P$.  
    \item $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$.  
  \end{enumerate}
  Furthermore, (i) and (ii) hold if we replace $\tensor$ with $\implies$ throughout and if we replace (i) by the statement that either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=O$.
  \begin{proof}
    See Appendix \ref{nice-negative-games-proof}.
  \end{proof}
  \label{nice-negative-games}
\end{proposition}

We gave an example earlier in which a play $sa$ in $P_A\|P_B$ was not well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$.  The crucial thing that made that example work was that we had $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=O$.  This then meant that $\zeta_{A\tensor B}(sa)=O$ even when $\lambda_{A\tensor B}=P$.  Part (i) of the proposition above tells us that this situation never occurs, and part (ii) tells us that this is enough to ensure that we never get any alternating sequences that are not well formed.

A corollary of our result is that we have:
\begin{align*}
  P_{A\tensor B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\tensor B}$}\} \\
  P_{A\implies B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\implies B}$}\}
\end{align*}
if $A,B$ are negative games.  In other words, we can ignore the well-formedness condition on plays if we are dealing with only negative games.

This proposition allows us to prove the following useful fact:

\begin{lemma}
  \label{alternatingsequenceslemma}
  Let $A,B,C$ be negative games, and let $\s\in (M_A\cprd M_B\cprd M_C)^*$.  If any two of the following statements are true, then so is the third:
  \begin{gather*}
    \s\vert_{A,B}\in P_{A\implies B}\\
    \s\vert_{A,C}\in P_{A\implies C}\\
    \s\vert_{B,C}\in P_{B\implies C}
  \end{gather*}
  \begin{proof}
    See Appendix \ref{alternatingsequenceslemmaproof}.
  \end{proof}
\end{lemma}

Now we can move on to the main work.  We start with a surprising lemma about strategies on the implication $A\implies B$.

\begin{lemma}
  \label{PlayInStrategyDeterminedByComponents}
  Let $A,B$ be games and let $\sigma$ be a strategy for $A\implies B$.  Suppose that $s,t\in\sigma$ are such that $s\vert_A=t\vert_A$ and $s\vert_B=t\vert_B$.  Then $s=t$.
  \begin{proof}
    Suppose that $s\ne t$.  Let $r\prefix s,t$ be the longest common subsequence of $s$ and $t$ - so we have $rx\prefix s, ry\prefix t$ for some moves $x,y\in M_{A\implies B}$ with $x\ne y$.  Since $rx,ry$ are both substrings of the strategy $\sigma$, $r$ must be a $P$-position and therefore the moves $x,y$ must take place in the same game.  Without loss of generality, suppose that $x,y\in M_A$.  Then we have $r\vert_A x\prefix s\vert_A,r\vert_Ay\prefix t\vert_A$ and so $s\vert_A\ne t\vert_A$.
  \end{proof}
\end{lemma}

Thus we see that the plays according to some given strategy $\sigma$ for $A\implies B$ are characterized by their $A$- and $B$-components.  More is true, however: given games $A$ and $B$, the strategies on $A\implies B$ are characterized by the $A$- and $B$-components of their constituent plays:
\begin{lemma}
  \label{HylandSchalkFaithful}
  Let $A,B$ be games and let $\sigma,\sigma'$ be strategies for $A\implies B$ such that
  \[
    \{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}=\{(s'\vert_A,s'\vert_B)\suchthat\textrm{$s'\in\sigma'$ is a $P$-position}\}
    \]
  Then $\sigma=\sigma'$.
  \begin{proof}
    See Appendix \ref{HylandSchalkFaithfulProof}.
  \end{proof}
\end{lemma}

Given games $A,B$ and a strategy $\sigma$ for $A\implies B$, the set
\[
  \{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}\subset P_A\times P_B
  \]
is a \emph{relation} between $P_A$ and $P_B$.  Writing $\grel\sigma\subset P_A\times P_B$, we will show that if $A,B,C$ are games and $A\xrightarrow{\sigma}\map{\tau}{B}{C}$ are morphisms, then:
\[
  \grel{\comp\tau\sigma}=\comp{\grel\tau}{\grel\sigma}
  \]
under the usual composition of relations:
\[
  \comp{\grel\tau}{\grel\sigma} = \{(s,t)\in P_A\times P_C\suchthat \exists u\in P_B\esuchthat (s,u)\in\grel\sigma,\;(u,t)\in\grel\tau\}
  \]
Thus we will get a functor $\cmap{\F}{\G}{\Rel}$, where $\G$ is our category of negative games and $\Rel$ is the category of sets and relations.  Proposition \ref{HylandSchalkFaithful} then tells us that this functor is faithful.

It is clear from the definition of $\comp\tau\sigma$ that $\grel{\comp\tau\sigma}\subset\comp{\grel\tau}{\grel\sigma}$; indeed if $\s\in\sigma\|\tau$, then $(\s\vert_A,\s\vert_B)\in\grel\sigma$ and $(\s\vert_B,\s\vert_C)\in\grel\tau$, so $(\s\vert_A,\s\vert_C)\in\comp{\grel\tau}{\grel\sigma}$.  To show the reverse inclusion, we need to show the following: if $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$, then there is some $\s\in (M_A\cprd M_B\cprd M_C)^*$ such that $\s\vert_{A,B}=s$ and $\s\vert_{B,C}=t$.

This can be shown in an easy way.  Roughly speaking, we write out the sequence $s$, and then insert immediately after each $B$-move the $C$-moves from $t$ that occur after that $B$-move.  This technique works for arbitrary sequences and is sufficient to prove that $\grel{\comp\tau\sigma}=\comp{\grel\tau}{\grel\sigma}$.  However, it turns out that if $s$ and $t$ are alternating plays in $A\implies B$ and $B\implies C$ then this interleaving is unique - and even more is true:

\begin{lemma}
  \label{LiftingLemma}
  Let $A,B,C$ be negative games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose that $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$.  Let $n=\length(s)+\length(t\vert_C)$; i.e., the total number of unique terms of $s$ and $t$ after we have identified their common $B$-component.  Then for all $k$ with $0\le k\le n$, there is a unique sequence $\s^k\in\sigma\|\tau$ of length $k$ such that $\s^k\vert_A\prefix s\vert_A$ and $\s^k\vert_C\prefix t\vert_C$.  Moreover, for this $\s^k$ we have $\s^k\vert_{A,B}\prefix s$ and $\s^k\vert_{B,C}\prefix t$, and if $j\le k$ then $\s^j\prefix \s^k$.  
  \begin{proof}
    See Appendix \ref{LiftingLemmaProof}.
  \end{proof}
\end{lemma}

Note that Lemma \ref{LiftingLemma} is stronger than saying that there is a unique sequence $\s^k$ of length $k$ such that $\s^k\vert_{A,B}\prefix s$ and $\s^k\vert_{B,C}\prefix t$.  Instead, we are saying that there exists a sequence $\s^k$ with those properties, but that it is uniquely determined even when we make no requirement on its $B$-component other than that the whole sequence is contained in $\sigma\|\tau$.

As a corollary, we see that the sequences $s$ and $t$ may be interleaved: set $\s=\s^n$; then we have $\s\vert_{A,B}\prefix s$ and $\s\vert_{B,C}\prefix t$.  In fact, we have $\s\vert_{A,B}=s$ and $\s\vert_{B,C}=t$ by a length argument:
\[
  \length(\s\vert_{A,B})\le\length(s)=n-\length(t\vert_C)\le n-\length(\s\vert_C)=\length(\s\vert_{A,B})
  \]
so we must have equality everywhere, and similarly for $\s\vert_{B,C}$ and $t$.

We now have all the ingredients ready to prove that $\comp\tau\sigma$ is a well-defined strategy.

\begin{proposition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $\comp\tau\sigma$ (as defined above) is a strategy for $A\implies C$.

  \begin{proof}
    By Lemma \ref{alternatingsequenceslemma}, $\comp\tau\sigma\in P_{A\implies C}$.  Moreover, it is non-empty, since it contains $\emptyplay$.  We need to show that the two strategy conditions hold for $\comp\tau\sigma$.

    Firstly, suppose that $\s\in\sigma\|\tau$ and $\s\vert_{A,C}$ is a $P$-play in $A\implies C$.  Suppose that $\s\vert_{A,C} a\in P_{A\implies C}$ for some $a\in M_A$.  We claim that $\s a\in\sigma\|\tau$.

    Indeed, certainly $\s a\vert_{B,C}=\s\vert_{B,C}\in\tau$.  Moreover, we have $\s a\vert_{A,C}\in P_{A\implies C}$, so Lemma \ref{alternatingsequenceslemma} tells us that $\s a\vert_{A,B}\in P_{A\implies B}$.

    Since $a$ is an $O$-move in $A\implies B$, it is an $O$-move in $A\implies C$.  Since $\s\vert_{A,B}\in\sigma$, we must have $\s a\vert_{A,B}\in\sigma$, by the definition of a strategy.  So $\s a\in\sigma\|\tau$.

    By a symmetrical argument, if $\s\vert_{A,C} c\in P_{A\implies C}$ for some $c\in M_C$, then $\s c\in\sigma\|\tau$.

    For the second strategy property, suppose that $s\in\comp\tau\sigma$ is n $O$-play and that $sx, sy\in\comp\tau\sigma$.  We claim that $x=y$.  By the definition of $\comp\tau\sigma$, there must be sequences $\s,\t\in\sigma\|\tau$ with $\s\vert_{A,C}=sx$ and $\t\vert_{A,C}=sy$.  Moreover, by removing any $B$-moves form the end of $\s,\t$, we may assume that the last move in $\s$ is $x$ and the last move in $\t$ is $y$.  We may write $\s=\s'\b x$ and $\t=\t'\bbeta y$, where $\b$ and $\bbeta$ are sequences composed entirely out of $B$-moves and neither $\s'$ nor $\t'$ ends with a $B$-move.  In particular, $\s'\vert_{A,C}=\t'\vert_{A,C}=s$.

    Without loss of generality, $\length(\s')\le\length(\t')$.  Let $\t''$ be the prefix of $\t'$ that has the same length as $\s'$, writing $\t'=\t''\r$.

    Now $\s'$ and $\t''$ have the same length, and we have
    \[
      \begin{matrix}
        \s'\vert_A\prefix\s\vert_A & \t''\vert_A\prefix\s\vert_A \\
        \s'\vert_C\prefix\s\vert_C & \t''\vert_C\prefix\s\vert_C
      \end{matrix}
      \]
    so we must have $\s'=\t''$, by uniqueness in Lemma \ref{LiftingLemma}.  Now observe that we have
    \[
      \s'\vert_{A,C}=\t'\vert_{A,C}=\t''\vert_{A,C}\r\vert_{A,C}=\s'\vert_{A,C}\r\vert_{A,C}
      \]
    Since $\t'=\t''\r$ does not end with a $B$-move, $\r\vert_{A,C}$ must be non-empty if $\r$ is non-empty.  Therefore $\r=\emptyplay$, and so $\t'=\t''=\s'$.

    We now claim that $\length(\b)=\length(\bbeta)$.  Indeed, suppose instead that $\length(\b)<\length(\bbeta)$.  Then there would be a prefix $\bbeta'\prefix\bbeta$ of length $\length(\b)+1$.  Then we would have
    \[
      \begin{matrix}
        \s'\b x\vert_A=\s\vert_A & \s'\bbeta'\vert_A=\s'\vert_A\prefix\s\vert_A \\
        \s'\b x\vert_C=\s\vert_C & \s'\bbeta'\vert_C=\s'\vert_C\prefix\s\vert_C
      \end{matrix}
      \]
    and so $\s'\b x=\s'\bbeta'$ by Lemma \ref{LiftingLemma}, which is clearly impossible.  Therefore, $\length(\b)=\length(\bbeta)$.  Now we can apply Lemma \ref{LiftingLemma} in the same way to tell us that $\b=\bbeta$.

    Suppose that $\zeta_B(\s'\b\vert_B)=P$.  Since $\s'\b\in\sigma\|\tau$, this means that $\zeta_A(\s'\b\vert_A)=P$, by Proposition \ref{nice-negative-games}(i).  Therefore, $\zeta_{A\implies B}(\s'\b)=P$, so $x$ and $y$ must both be moves in $C$.  Then we have $\s'\b\vert_{B,C}x,\s'\b\vert_{B,C}y\in\tau$, and so $x=y$ by the definition of a strategy.

    By a symmetrical argument, if $\zeta_B(\s'\b\vert_B)=O$, then $x$ and $y$ must both be moves in $A$.  We then have $\s'\b\vert_{A,B}x,\s'\b\vert_{A,B}y\in\sigma$, so $x=y$.
  \end{proof}
\end{proposition}

Now we are ready to define our category $\G$ of games.  We have defined composition of strategies, so we need to define identity morphisms.  Identity morphisms are given by the copycat strategy, as usual:
\[
  \id_A=\left\{s\in P_{A\implies A}\suchthat\textrm{for all even length $t\prefix s$, $t\vert_\bneggame{A}=t\vert_A$}\right\}
  \]
We can now state our first main result.

\begin{theorem}
  \label{IsCategory}
  The collection of negative games, with morphisms from $A$ to $B$ given by strategies on $A\implies B$ with the notions of composition and identity given above, forms a category $\G$.  Moreover, there is a faithful functor $\F\from\G\to\Rel$, where $\Rel$ is the category of sets and relations, given by sending a game $A$ to the set of plays $P_A$ and sending a strategy $\sigma\from A\implies B$ to the set
  \[
    \grel{\sigma}=\{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}\subset P_A\times P_B
    \]
  \begin{proof}
    We shall make much use of the relational content of a strategy.  We first need to show that the identity is indeed an identity and that composition is associative.  For the identity, note that $\grel{\id_A}=\Delta_{P_A}\subset P_A\times P_A$, the identity relation in $\Rel$.  If $B,C$ are negative games and $\sigma\colon B\implies A,\tau\colon A\implies C$ are strategies, then from our earlier discussion we have
    \[
      \grel{\comp{\id_A}{\sigma}}=\comp{\grel{\id_A}}{\grel\sigma}=\comp{\Delta_{P_A}}{\grel\sigma}=\grel\sigma
      \]
    and therefore $\comp{\id_A}{\sigma}=\sigma$, by Lemma \ref{HylandSchalkFaithful}.  Similarly, $\comp{\tau}{\id_A}=\tau$.

    For associativity of composition, we hijack the associativity in $\Rel$: if $A,B,C,D$ are negative games, and $\map{\sigma}AB\xrightarrow{\tau}\map{\upsilon}CD$ are morphisms, then we have:
    \begin{align*}
      \grel{\comp{(\comp\upsilon\tau)}{\sigma}} & = \comp{\grel{\comp\upsilon\tau}}{\sigma} \\
        & = \comp{(\comp{\grel\upsilon}{\grel\tau})}{\grel\sigma} \\
        & = \comp{\grel\upsilon}{(\comp{\grel\tau}{\grel\sigma})} \quad\textrm{by associativity in $\Rel$} \\
        & = \comp{\grel\upsilon}{\grel{\comp\tau\sigma}} \\
        & = \grel{\comp{\upsilon}{(\comp\tau\sigma)}}
    \end{align*}
    and so $\comp{(\comp\upsilon\tau)}{\sigma}=\comp{\upsilon}{(\comp\tau\sigma)}$, by Lemma \ref{HylandSchalkFaithful}.

    We have already shown that the map $\F$ respects composition, so it is a functor.  It is faithful by Lemma \ref{HylandSchalkFaithful}.
  \end{proof}
\end{theorem}

\subsection{Total strategies and winning conditions}

Let $A$ be a game.  We call a strategy $\sigma$ for $A$ \emph{total} if it satisfies the additional requirement that whenever $s\in\sigma$ is an $O$-play, there exists some $a\in M_A$ such that $sa\in\sigma$ (before we only required that such a play be unique if it existed).

We might want to talk about a category of negative games and total strategies.  However, we cannot do this immediately, since the composition of two total strategies need not be total.

\begin{example}
  \label{TotalCompositionExample}
  Let $\st$ be the negative game where each player has a unique move at every position:
  \begin{gather*}
    M_{\st} = \{q,a\} \\
    \lambda_{\st}(q) = O,\;\lambda_{\st}(a)=P \\
    P_{\st} = \{\emptyplay, q, qa, qaq, qaqa, \dots\}
  \end{gather*}

  Let $I$ be the negative game with no moves and let $\bot$ be the negative game with a single opponent move and no further play:
  \[
    \begin{matrix}
      M_I=\emptyset & M_\bot = \{*\} \\
      \lambda_I=\emptyset  & \lambda_\bot(*)=O \\
      P_I=\{\emptyplay\} & P_\bot = \{\emptyplay, *\}
    \end{matrix}
    \]

  It is easy to see that if $A$ is a negative game then strategies for $I\implies A$ are the same thing as strategies for $A$ and that strategies for $A\implies\bot$ are the same thing as opponent strategies for $A$.  So we get morphisms $\cmap{\sigma}{I}{\st},\cmap{\tau}{\st}{\bot}$ given by the unique player and opponent strategies for $\st$:
  \[
    \sigma = P_\st\quad\tau = \{*s\suchthat s\in P_\st\}
    \]
  Moreover, both these strategies are total.

  The plays in $\sigma\|\tau$ are now those sequences $\s\in(M_I\cprd M_\st\cprd M_\bot)^*$ such that:
  \begin{gather*}
    \s\vert_A=\emptyplay \\
    \s\vert_B\in P_\st \\
    \textrm{If $\s\ne\emptyplay$ then $\s\vert_C=*$}
  \end{gather*}

  Upon restricting these sequences to $A$ and $C$, we see that $\comp\tau\sigma$ contains only two plays - $\emptyplay$ and $*$.  $*$ is an $O$-play with no $P$-reply in $\comp\tau\sigma$, so $\comp\tau\sigma$ is not a total strategy.
\end{example}

Clearly it is the infinite play in the game $\st$ that is causing the problem.  We can get around this by insisting that our games contain no infinite plays: if $A$ is a game, we say $A$ has an infinite play if $(P_A,\prefix)$ has an infinite chain.

\begin{proposition}
  \label{BoundedTotalComposition}
  Let $A,B,C$ be negative games and assume that $B$ has no infinite play.  Let $\sigma$ be a total strategy for $A\implies B$ and let $\tau$ be a total strategy for $B\implies C$.  Then $\comp\tau\sigma$ is a total strategy for $A\implies C$.
  \begin{proof}
    We have already shown that $\comp\tau\sigma$ is a strategy for $A\implies C$, so we need to show that it is total.  Let $s\in\comp\tau\sigma$ be an $O$-play.  We seek a $P$-move $x$ such that $sx\in\comp\tau\sigma$.

    By the definition of $\comp\tau\sigma$, there is some $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.  Since $P_B$ contains no infinite chain, we may take $\s$ to be maximal such that $\s\vert_{A,B}=s$.

    Since $s$ is an $O$-play, $\s\vert_A$ must be a $P$-play in $A$ and $\s\vert_C$ must be an $O$-play in $C$.  Consider the $B$-component $\s\vert_B$ of $\s$.  If this is an $O$-play, then $\s\vert_{A,B}$ is an $O$-play in $\sigma$, so, by totality of $\sigma$, there exists $x$ such that $\s\vert_{A,B}x\in\sigma$ and therefore $\s x\in\sigma\|\tau$.  Similarly, if $\s\vert_B$ is a $P$-play, then $\s\vert_{B,C}$ is an $O$-play in $\tau$, so there exists $x$ such that $\s\vert_{B,C}x\in\tau$ and so $\s x\in\sigma\|\tau$.

    If $x$ is a $B$-move, we have $\s x\vert_{A,C}=s$, contradicting maximality of $s$.  Therefore, $x$ is an $A$- or $C$-move, and we have $sx\in\comp\tau\sigma$.
  \end{proof}
\end{proposition}

The result of this proposition means that we could create a category of games and total strategies by requiring that all our games have no infinite plays.  However, this approach will not work for us, since our particular version of the exponential connective $\oc$ introduces infinite plays into all non-empty games.  Moreover, it seems a bit wasteful to require that none of the games $A,B,C$ have infinite plays when it is only infinite plays in game $B$ that are causing problems.

Fortunately, there is a cleverer way of getting around the problem.  Recall that we defined a game to be given by a tuple $(M_A,\lambda_A,\zeta_A,P_A)$.  Given such a game, and given some subset $X\subset P_A$, define $X^\omega$ to be the set of all infinite plays in the game -- i.e., the set of all infinite sequences $s\in M_A^\omega$ all of whose prefixes lie in $X$.

\begin{definition}
  A \emph{win-game} is a tuple $A=(M_A,\lambda_A,\zeta_A,P_A,W_A)$ where $(M_A,\lambda_A,\zeta_A,P_A)$ is a game as defined before and $\cmap{W_A}{P_A^\omega}{\OP}$ is a function telling us whether each infinite play is a win for player $P$ or for player $O$.  
\end{definition}

To distinguish our original games from these win-games, we shall refer to the earlier games as \emph{finitary games}.

We can define an appropriate notion of strategies for these games.  If $A$ is a win-game, then a \emph{winning strategy} for $A$ is a total strategy for $(M_A,\lambda_A,\zeta_A,P_A)$ such that $W_A(s)=P$ for all $s\in\sigma^\omega$.

We can also extend our connectives to our new win games.  At the level of finitary games, our definitions of the connectives are unchanged, and it remains to define the $W$-functions.  If $A$ is a win game, then $W_{\neggame A}=\neg\circ W_A$.

If $A$ and $B$ are win games, we would like to define $W_{A\tensor B}$ by
\[
  W_{A\tensor B}(s) = W_A(s\vert_A) \wedge W_B(s\vert_B)
  \]
However, this is not well defined at present because one out of $s\vert_A$ and $s\vert_B$ might be a finite sequence even if $s$ is infinite.  For this purpose, it will be convenient to extend our function $W_A$ to include finite plays as well using $\zeta_A$:
\[
  W_A^* = \zeta_A\cprd W_A\from P_A\cprd P_A^\omega \to\OP
  \]
We can then define
\[
  W_{A\tensor B}(s) = W_A^*(s\vert_A)\wedge W_B^*(s\vert_B)
  \]
Indeed, we could do away with $\zeta_A$ and $W_A$ altogether, replacing them with $W_A^*$.  Since the rule for $\zeta_{A\tensor B}$ is also given by a conjunction, our rule for the tensor product becomes:
\[
  W_{A\tensor B}^*(s) = W_A^*(s\vert_A)\wedge W_B^*(s\vert_B)
  \]
This will be the starting point for our development of transfinite games in the next section.  In our formulation, finitary games are games played over the ordinal $\omega$, while win-games will be games played over the ordinal $\omega+1$.  We make no special distinction between finite and infinite plays, so the function $\zeta_A$ for our transfinite games incorporates both the function $\zeta_A$ and the function $W_A$ from our win-games, in the same manner as the function $W_A^*$ defined above.  One advantage of this point of view is that we no longer have to treat the finite- and infinite-play cases separately, but can give a uniform presentation.

For now, let us concentrate on developing the theory of win-games in the traditional way.  Having defined the tensor product, we may recover the definitions of the par $\parr$ and linear implication $\implies$ of two games as usual.  In particular, this means that we have
\[
  W_{A\implies B}^*(s) = (W_A(s\vert_A) \Rightarrow W_B(s\vert_B))
  \]

It is worth examining the definitions of the $W$-functions for tensor and implication.  Recall that in the tensor product, it is always player $O$ who switches games.  Therefore, if $s$ is an infinite play in $A\tensor B$ and $s\vert_A$ is finite and non-empty, it must be the case that player $P$ made the last move in $s$, and so $W_A^*(s\vert_A)=P$.  If we assume our games are negative, then this extends to the case that $s\vert_A$ is empty.  This tells us that player $P$ wins an infinite play $s$ in $A\tensor B$ if and only if each component is either $P$-winning or is finite.

Similarly, player $P$ wins an infinite play $s$ in $A\implies B$ if and only if $s\vert_A$ is infinite and $O$-winning or if $\s\vert_B$ is either finite or is infinite and $P$-winning.  Since it is player $P$ who switches games in $A\implies B$, if $s\vert_A$ is finite then it will end with an $O$-move, so will count as an $O$-winning play.

The point now is that if $A,B,C$ are negative win-games and $\sigma$ and $\tau$ are strategies for $A\implies B$ and $B\implies C$, we will never end up in the situation we were in in Example \ref{TotalCompositionExample} where we have an infinite play in $B$ that stops us from replying in the composition $\comp\tau\sigma$.  In that example, the unique infinite play in $\st$ would have to be either $O$-winning or $P$-winning, so either $\sigma$ or $\tau$ would not be a valid winning strategy.

\begin{proposition}
  \label{CompWinningIsWinning}
  Let $A,B,C$ be negative win-games, let $\sigma$ be a winning strategy for $A\implies B$ and let $\tau$ be a winning strategy for $B\implies C$.  Then $\comp\tau\sigma$ is a winning strategy for $A\implies C$.  
  \begin{proof}
    See Appendix \ref{CompWinningIsWinningProof}.
  \end{proof}
\end{proposition}

We get another result:

\begin{theorem}
  The collection of all negative win-games, with morphisms from $A$ to $B$ given by winning strategies on $A\implies B$ and composition defined as above, is a category.
  \begin{proof}
    We have shown already that the composition of two winning strategies is a winning strategy.  Associativity of composition is inherited from finitary games and the identity strategy is winning for $A\implies A$.  
  \end{proof}
\end{theorem}

\section{Transfinite games}

\begin{note}
  In this section, we assume familiarity with ordinals, ordinal arithmetic and transfinite induction/recursion.  We shall frequently identify an ordinal $\alpha$ with the set $\{\beta\suchthat\beta<\alpha\}$ of all ordinals less than $\alpha$ without comment.
\end{note}

In the last section, we came across win-games, where in addition to the usual function $\cmap{\zeta_A}{P_A}{\OP}$ we have a function $\cmap{W_A}{P_A^\omega}{\OP}$, where $P_A^\omega$ is the set of infinite limits of plays in $P_A$.  We saw that it is useful to combine these two functions into one:
\[
  W_A^* = \zeta_A\cprd W_A\from P_A\cprd P_A^*\to\OP
  \]
This suggests that it might make sense to combine $P_A$ and $P_A^\omega$ into one a single set $\overline{P_A}$ and use the function $W_A^*$ instead of $\zeta_A$ and $W_A$.  This new set will contain both finite and infinite plays, and the infinite plays will be precisely the limits of the finite plays.  In this way, the set of possible lengths of plays in $\overline{P_A}$ is the set $\{0,1,2,3,\dots,\omega\}$, or the ordinal $\omega+1$.

Contrast this with the finitary case, in which the set of possible lengths of plays is the set $\{0,1,2,3,\dots\}$, or the ordinal $\omega$.  In the coming sections, we will generalize these results so that we end up with games where the plays can have much larger ordinal lengths.  Win-games will be taken to be the motivating example throughout.

\subsection{Transfinite Games and Strategies}

We fix some ordinal $\alpha$ throughout.  Given a set $M$, we write $M^{*<\alpha}$ for the set of all ordinal-length sequences of elements of $M$ whose length is less than $\alpha$.

\begin{definition}
  A \emph{game over $\alpha$}, or an \emph{$\alpha$-game}, is given by a tuple
  \[
    A = (M_A, \lambda_A, \zeta_A, P_A)
    \]
  where
  \begin{itemize}
    \item $M_A$ is a set of moves.
    \item $\cmap{\lambda_A}{M_A}{\OP}$ is a function telling us which player may make each move.
    \item $P_A$ is a set of pairs $(\beta, s)$, where $\beta<\alpha$ is some ordinal and $\cmap{s}{\beta}{M_A}$ is a sequence of moves of length $\beta$.  
    \item $\cmap{\zeta_A}{P_A}{\OP}$ tells us which player owns each position.
  \end{itemize}

  We will normally abuse notation and write $s$ instead of $(\beta, s)$ and $\length(s)$ instead of $\beta$.  If $a\in M_A$, we will write $a$ for the $1$-move play $(1, a)$, and $st$ for the concatenation of two sequences $s$ and $t$ (where $\length(st)=\length(s)+\length(t)$).  We will write $t\prefix s$ if $\length(t)\le\length(s)$ and $s\vert_{\length(t)}=t$.

  To be called a game, $(M_A, \lambda_A, \zeta_A, P_A)$ has to satisfy four rules.
  \begin{description}
    \item[Prefix closure] $P_A$ must be closed under the relation $\prefix$.  
    \item[Well-formedness] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.  
    \item[Alternating condition] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s)=\neg\zeta_A(sa)$.
    \item[Limit condition] If $\mu<\alpha$ is a limit ordinal and $s\in(M_A)^\mu$ is a sequence of length $\mu$ such that every proper prefix $t\pprefix s$ is in $P_A$, then $s$ is in $P_A$.  
  \end{description}
\end{definition}

\begin{remark}
  In the $\omega+1$ case, the limit condition tells us that the plays of length $\omega$ in $P_A$ are precisely those infinite plays all of whose finite prefixes lie in $P_A$.  It also guarantees that $P_A$ is non-empty, since the empty play $\emptyplay$ will always satisfy the conditions.

  In the $\omega+1$ case, $\zeta_A$ will take the role of what we previously called $W_A^*$, while $P_A$ takes the role of what we called $P_A\cprd P_A^\infty$.  
\end{remark}

We define strategies for these games in much the same way that we defined them before:

\begin{definition}
  Let $A$ be an $\alpha$-game.  A (partial) \emph{strategy} for $A$ is a subset $\sigma\subset P_A$ satisfying three conditions:
  \begin{description}
    \item[$\sigma$ contains all $O$-replies] If $s\in\sigma$ is a $P$-play and $sa\in P_A$ is an $O$-response, then $sa\in\sigma$.
    \item[$P$-replies are unique] If $s\in\sigma$ is an $O$-play and $sa,sb\in\sigma$ are $P$-responses, then $a=b$.
    \item[Limit condition] If $\mu<\alpha$ is a limit ordinal and $s\in P_A$ is a sequence of length $\mu$ such that every proper prefix $t\pprefix s$ lies in $\sigma$, then $s\in\sigma$.
  \end{description}

  We call $\sigma$ \emph{total} if it satisfies the extra requirement:

  \begin{description}
    \item[$P$ always has a reply] If $s\in\sigma$ is an $O$-play, then there is some $P$-move $a\in M_A$ with $sa\in\sigma$.
  \end{description}
\end{definition}

The only new part of this is the limit condition.  Let us examine what it means in the $\omega+1$ case.  Play according to a total strategy $\sigma$ gives rise to a sequence of plays $\emptyplay \prefix s_1\prefix s_2\prefix\dots$ (were $s_i$ has length $i$).  The limit condition then tells us that the limit $s_\omega$ of these plays must be contained in $\sigma$.  If $\zeta_A(s_\omega)=O$ then $P$ has no response to $s_\omega$ (since there are no plays of length $\omega+2$), contradicting totality of $\sigma$.  So for $\sigma$ to be a total strategy, we must have $\zeta_A(s_\omega)=P$ for every $s_\omega$ arising as the limit of finite plays according to $\sigma$.  So total strategies for $\omega+1$-games are exactly the same thing as the winning strategies for win-games that we defined earlier.

If $s\in P_A$ and $\length(s)$ is a successor ordinal, we will call $s$ a \emph{successor play} or \emph{successor position}.  If $\length(s)$ is a limit ordinal, we will call $s$ a \emph{limiting play} or \emph{limiting position}.

\subsection{Connectives}

We may define connectives for $\alpha$-games in much the same way that we defined them for finitary games and win-games.

\begin{definition}
  Let $A$ be an $\alpha$-game.  The negation $\neggame A$ of $A$ is given by
  \begin{itemize}
    \item $M_\bneggame A=M_A$
    \item $\lambda_\bneggame A = \neg\circ\lambda_A$
    \item $\zeta_\bneggame A = \neg\circ\zeta_A$
    \item $P_\bneggame A = P_A$
  \end{itemize}
\end{definition}

For the other connectives -- $\tensor$, $\parr$ and $\implies$ -- we will use interleaved plays.  If $A$ and $B$ are $\alpha$ games, then our interleaved plays will be sequences taking values in $M_A\cprd M_B$.  If $\beta<\alpha$ and $s\in(M_A\cprd M_B)^\beta$, we may write $\beta_A$ for $s\inv(M_A)$ and $\beta_B$ for $s\inv(M_B)$.

\begin{lemma}
  \label{TechnicalOrdinalLemma}
  Let $\beta$ be an ordinal, and let $\gamma$ be any subset of $\beta$.  Then $\gamma$ inherits a well-ordering from $\beta$ and, as ordinals, we have $\gamma\le\beta$.  
  \begin{proof}
    Any subset of $\gamma$ is a subset of $\beta$, so it has a least element.  Therefore, the inherited order on $\gamma$ is a well-order.

    Suppose for a contradiction that $\beta<\gamma$.  Then we have order preserving injections
    \[
      i\from \gamma\hookrightarrow\beta\quad j\from\beta\hookrightarrow\gamma
      \]
    where $i$ is inclusion of $\gamma$ as a subset of $\beta$ and $j$ is inclusion of $\beta$ as a proper initial prefix of $\gamma$.  Let $f\from\gamma\hookrightarrow\gamma$ be the composition $\gamma\xhookrightarrow{i}\beta\xhookrightarrow{j}\gamma$.  Then $f$ is order preserving.

    Let $S=\{\delta\in\gamma\suchthat f(\delta)<\delta\}$.  $S$ is non-empty, since $\beta\in S$ (considering $\beta$ as an element of $\gamma$), so $S$ has a least element $\xi$.  Now $f(\xi)<\xi$, so $f(f(\xi))<f(\xi)$, since $f$ is order-preserving and injective.  Therefore, $\xi\le f(\xi)$ by minimality of $\xi$, which is a contradiction.
  \end{proof}
\end{lemma}

Using Lemma \ref{TechnicalOrdinalLemma}, we see that $\beta_A,\beta_B\le\beta$; in particular, they are both less than $\alpha$, so we get induced sequences $s\vert_A$ of length $\beta_A$ and $s\vert_B$ of length $\beta_B$.  We define
\[
  P_A\|P_B = \left\{s\in (M_A\cprd M_B)^{*<\alpha}\suchthat s\vert_A\in P_A,\;s\vert_B\in P_B\right\}
  \]

We may now define functions $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}\from P_A\|P_B\to\OP$ as before:
\begin{IEEEeqnarray*}{rCc}
  \zeta_{A\tensor B}(s) & = & \zeta_A(s\vert_A)\wedge\zeta_B(s\vert_B)\\
  \zeta_{A\parr B}(s) & = & \zeta_A(s\vert_A)\vee\zeta_B(s\vert_B)\\
  \zeta_{A\implies B}(s) & = & (\zeta_A(s\vert_A)\Rightarrow \zeta_B(s\vert_B))
\end{IEEEeqnarray*}

Our definitions of the functions $\lambda_{A\tensor B},\lambda_{A\parr B},\lambda_{A\implies B}\from M_A\cprd M_B\to \OP$ are the same as before:
\begin{gather*}
  \lambda_{A\tensor B}=\lambda_{A\parr B}=\lambda_A\cprd \lambda_B \\
  \lambda_{A\implies B} = (\neg\circ\lambda_A)\cprd \lambda_B
\end{gather*}

Given a set $M$, a prefix-closed set $P\subset M^{*<\alpha}$ and functions $\cmap{\lambda}{M}{\OP},\cmap{\zeta}{P}{\OP}$, we say that a play $s\in P$ is \emph{well-formed with respect to $\lambda,\zeta$} if whenever $ta\prefix s$ (with $a\in M$) we have $\zeta(ta)=\lambda(a)$.  We say that $s$ is \emph{alternating with respect to $\zeta$} if whenever $t,ta$ are prefixes of $s$ (where $a\in M$), we have $\zeta(t)=\neg\zeta(ta)$.

As before, we now define:

\begin{IEEEeqnarray*}{rCl}
  P_{A\tensor B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\tensor B}$ \\ $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$}}\right\} \\
  P_{A\parr B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\parr B}$ \\ $s$ is well formed with respect to $\zeta_{A\parr B},\lambda_{A\parr B}$}}\right\} \\
  P_{A\implies B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\implies B}$ \\ $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$}}\right\}
\end{IEEEeqnarray*}

Setting $M_{A\tensor B}=M_{A\parr B}=M_{A\implies B} = M_A\cprd M_B$, and restricting $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$ to $P_{A\tensor B},P_{A\parr B},P_{A\implies B}$ respectively, we arrive at our definitions of the connectives:
\begin{IEEEeqnarray*}{cCc}
  A\tensor B & = & (M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B})\\
  A\parr B & = & (M_{A\parr B}, \lambda_{A\parr B}, \zeta_{A\parr B}, P_{A\parr B})\\
  A\implies B & = & (M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})
\end{IEEEeqnarray*}

\begin{proposition}
  \label{TransTensorWellFormed}
  $A\tensor B$, $A\parr B$ and $A\implies B$ are well formed games.  Moreover, $P_{A\tensor B}$ is the largest subset $X\subset P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, X)$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.
  \begin{proof}
    As before, we prove this proposition for $A\tensor B$ and the other two cases are entirely similar.  Alternatively, observe that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$ and that $A\implies B = \neggame A \parr B$.

    Examining the definitions of well formed and alternating sequences, it is immediate that $P_{A\tensor B}$ is prefix-closed.  Moreover, every sequence contained in $P_{A\tensor B}$ is well formed, so the well-formedness condition holds.  If $s,sa\in P_{A\tensor B}$ then $s,sa$ are both prefixes of $sa$ and so we must have $\zeta_{A\tensor B}(s)=\neg\zeta_{A\tensor B}(sa)$, since $sa$ is alternating.

    To show that the limit condition holds, suppose that $\mu<\alpha$ is a limit ordinal and that $s\in(M_A)^\mu$ is a sequence of length $\mu$ such that $t\in P_{A\tensor B}$ for every proper prefix $t\pprefix s$.  For each $t\pprefix s$, then, we must have $t\vert_A\in P_A$ and $t\vert_B\in P_B$.

    We claim that $s\vert_A\in P_A$.  Indeed, if $\length(s\vert_A)$ is a successor ordinal, then $s\vert_A$ has a last move $a$.  Let $t$ be the prefix of $s$ consisting of all moves up to and including that last move.  Then $\length(t)$ is a successor ordinal, so $t$ must be a \emph{proper} prefix of $s$, and therefore $s\vert_A=t\vert_A\in P_A$.  If instead $\length(s\vert_A)$ is a limit ordinal, then for every proper prefix $u\pprefix s\vert_A$, we have some $t\prefix s$ with $t\vert_A=u$ (take $t$ to be the prefix consisting of all moves in $s$ that occur in $u$ or that occur before some move in $u$).  Since $s\vert_A\ne u$, $t$ must be a \emph{proper} prefix of $s$, and so $t\vert_A\in P_A$.  Since $u$ is arbitrary, the limit condition for $A$ tells us that $s\vert_A\in P_A$.

    By an identical argument, $s\vert_B\in P_B$, and so $s\in P_A\|P_B$.  We claim that $s$ is alternating with respect to $\zeta_{A\tensor B}$.  Indeed, if $t,ta\prefix s$, then $t,ta$ must both be \emph{proper} prefixes of $s$, since $\length(s)$ is a limit ordinal and $\length(ta)$ is a successor ordinal.  So $ta$ is alternating and therefore $\zeta_{A\tensor B}(t)=\neg\zeta_{A\tensor B}(ta)$.

    Lastly, we show that $s$ is well formed with respect to $\lambda_{A\tensor B},\zeta_{A\tensor B}$.  Suppose $ta\prefix s$.  Once again, $ta$ must be a \emph{proper} prefix of $s$, since it clearly has a different length.  Therefore, $ta$ is well formed and we have $\zeta_{A\tensor B}(ta)=\lambda_{A\tensor B}(a)$.  Therefore, $s\in P_{A\tensor B}$.

    For the second part of the proposition, suppose that $V\subset P_A\|P_B$ is prefix closed and satisfies the alternating condition with respect to $\zeta_{A\tensor B}$ and that if $sa\in V$ then $\zeta_{A\tensor B}(sa)=\lambda_{A\tensor B}(a)$.  We want to show that $V\subset P_{A\tensor B}$.  Indeed, if $s\in V$ and $ta\prefix s$, then $ta\in V$ (since $V$ is prefix closed) and therefore $\zeta_{A\tensor B}(ta)=\lambda_{A\tensor B}(a)=\neg\zeta_{A\tensor B}(s)$.  
  \end{proof}
\end{proposition}

As before, we want to show that if player $O$ switches games in the tensor product and that player $P$ switches games in the par and linear implication.  Recalling that if $A,B$ are $\alpha$-games then $A\parr B = \neggame{(\neggame A\tensor \neggame B)}$ and that $A\implies B = \neggame A\parr B$, we only need to prove this for the tensor product:

\begin{proposition}
  \label{TransWhoSwitchesGames}
  Let $A,B$ be $\alpha$-games.  Suppose that $s\in P_{A\implies B}$, $a\in M_A$ and $b\in M_B$.  Then:

  i) If $sab\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(b) = O$

  ii) If $sba\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(a) = O$.

  \begin{proof}
    Unchanged from the finitary case - see Proposition \ref{WhoSwitchesGames}
  \end{proof}
\end{proposition}

\subsection{Categories of transfinite games and strategies}

We want to build a category $\G(\alpha)$ whose objects are games and whose morphisms are strategies on the linear implication of two games.  Given $\alpha$-games $A$, $B$ and $C$ and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we define
\begin{gather*}
  \sigma\|\tau = \left\{\s\in (M_A\cprd M_B\cprd M_C)^{*<\alpha\#\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\right\}\\
  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}
\end{gather*}

Here, $\alpha\#\alpha$ is intended to be an upper bound and indeed any sufficiently large ordinal will do without changing the elements of $\sigma\|\tau$.  The symbol $\#$ denotes the so-called \emph{natural addition} on ordinals: if $\beta,\gamma$ are ordinals then the order type of $\beta\#\gamma$ is the largest well-ordering on the disjoint union $\beta\sqcup\gamma$ such that the restrictions to $\beta$ and $\gamma$ give the original orderings\footnote{Alternatively, $\#$ represents the coproduct in the category of well-ordered sets and order-preserving maps.}.  For example, we have $\omega\#1=\omega+1$, but $1\#\omega=\omega+1$ as well (and \emph{not} $1+\omega$, which equals $\omega$).  In any case, this is not an important point - we want to allow the sequences $\s$ to be as long as we need to be, but we need to introduce some bound to make it clear that the resulting collection of plays is a small set.  $\alpha\#\alpha$ turns out to be a suitable upper bound.

For the functor $\cmap{\F}{\G(\alpha)}{\Rel}$, we shall want to show that
\[
  \comp\tau\sigma = \left\{s\in P_{A\implies C}\suchthat\exists t\in\sigma,u\in\tau\esuchthat s\vert_A=t\vert_A,\;t\vert_B=u\vert_B,\;s\vert_C=u\vert_C\right\}
  \]
To show this, we will want to show that for any such $s,t,u$ there is some interleaving $\s$ such that $\s\vert_{A,C}=s$, $\s\vert_{A,B}=t$ and $\s\vert_{B,C}=u$.  Even though $s$, $t$ and $u$ all have length less than $\alpha$, $\s$ might have longer length; it will, however, have length less than $\alpha\#\alpha$.

It is not immediately clear from the definition that the elements of $\comp\tau\sigma$ have length less than $\alpha$, and in fact it turns out that this is not true.  For this reason, we will eventually need to place restrictions on the ordinal $\alpha$ to make sure that $\comp\tau\sigma$ is indeed a valid strategy for $A\implies C$.

\subsubsection{Completely negative and almost completely negative $\alpha$-games}

Recall that when defining a finitary game $A=(M_A,\lambda_A,\zeta_A,P_A)$, the function $\zeta_A$ was entirely determined by two pieces of information: the function $\lambda_A$ (to determine $\zeta_A(sa)$ for any non-empty play $sa$) and the designation of the game as either \emph{positive} or \emph{negative} (to determine $\zeta_A(\emptyplay)$).  In the $\omega+1$ case, we also needed to specify a function $\cmap{W_A}{P_A^\infty}{\OP}$ to get the sign of each $\omega$-play.  The general case is similar - once we have specified $\zeta_A(s)$ for any play $s$ whose length is a limit ordinal, the values of $\zeta_A(t)$ for $t$ a play over a successor ordinal are determined by the alternating condition (alternatively, they are determined automatically by well-formedness).

When building a category of games, we restricted our attention to the negative games.  This is necessary in order to avoid technical complications\footnote{The category in \cite{abramskyjagadeesangames} has both positive and negative games as objects, together with games where either player may start, but it does not admit a faithful functor into $\Rel$ in the way that we want.}.  Of course, these technical complications carry over to the transfinite case, so we need a new negativity condition for our $\alpha$-games.

\begin{definition}
  Let $A$ be an $\alpha$-game.  We say that $A$ is \emph{completely negative} if $\zeta_A(s)=P$ whenever $s\in P_A$ and $\length(s)$ is a limit ordinal.
\end{definition}

Since the only limiting play in the finitary case is the empty play, we see that the completely negative $\omega$-games are precisely the negative games.  But now consider the $\omega+1$ case.  If $A$ is a win-game, then $A$ is completely negative only if it is negative and all infinite plays are $P$-winning.  Recall that we \emph{were} able to build a category of negative win-games without making the requirement that player $P$ wins all infinite plays, so if we insist on complete negativity then we lose much of the richness of our category for no technical benefit.  We would be better off with some weaker condition.

\begin{definition}
  Let $\alpha$ be an ordinal.  If $\alpha=\alpha'+1$ and $A$ is an $\alpha$-game, we say that $s\in P_A$ is \emph{length maximal} if it has the largest possible length - i.e., if $\length(s)=\alpha'$.

  If $\alpha$ is a limit ordinal then there are no length maximal plays in $\alpha$-games.

  Let $A$ be an $\alpha$-game.  We say that $A$ is \emph{almost completely negative} (\emph{acn}) if $\zeta_A(s)=P$ whenever $\length(s)$ is a limit ordinal \emph{and $s$ is not length-maximal}.
\end{definition}

Note that for most ordinals $\alpha$ there is no difference between being completely negative and being acn.  The only ordinals for which there is  a difference are those of the form $\mu+1$, where $\mu$ is a limit ordinal.

Our category will have acn $\alpha$-games as objects and the morphisms from $A$ to $B$ will be partial strategies for $A\implies B$.  Later we will consider the total strategy case.

\begin{proposition}
  \label{TensorIsAcn}
  Let $A,B$ be acn $\alpha$-games.  Then $A\tensor B$ is acn
  \begin{proof}
    Let $s\in P_{A\tensor B}$ be a limiting play that is not length maximal.  Then at least one of $s\vert_A$ and $s\vert_B$ must be a limiting play (otherwise they both have last moves and the later of the two will be the last move in $s$).  Suppose that $s\vert_A$ and $s\vert_B$ are both limiting plays.  By Lemma \ref{TechnicalOrdinalLemma}, $\length(s\vert_A),\length(s\vert_B)\le\length(s)$, so neither $s\vert_A$ nor $s\vert_B$ is length maximal, since $s$ is not.  Therefore, $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=P$, since $A$ and $B$ are acn.  Therefore, $\zeta_{A\tensor B}(s)=P$, since $P\wedge P=P$.

    Suppose instead that $s\vert_A$ is a successor play.  Then $s\vert_B$ is a limiting play.  Since $s$ is a limiting play, there must be moves from $B$ in $s$ that occur after the last move in $s\vert_A$.  Therefore, $\zeta_A(s\vert_A)=P$ by Proposition \ref{TransWhoSwitchesGames}.  Now $s\vert_B$ is a limiting play and not length maximal, so $\zeta_B(s\vert_B)=P$ and therefore $\zeta_{A\tensor B}(s)=P$.  The case where $s\vert_B$ is a successor play and $s\vert_A$ is a limiting play is similar.
  \end{proof}
\end{proposition}

Note, however, that $A\implies B$ is not necessarily acn, even if $A,B$ are completely negative.  This is a direct consequence of the extension of the definitions to ordinals greater than $\omega$.  For negative $\omega$-games $A,B$, the only limiting play is the empty play and its components are both necessarily empty, so they are also limiting plays.  Therefore, $A\implies B$ is a negative game, by the equation $(P\Rightarrow P) = P$.

However, when we move beyond $\omega$, it is no longer true that the components of a limiting play are always limiting plays, so we cannot be sure that they are $P$-positions, and this means that $A\implies B$ is not necessarily completely negative, even if $A,B$ are.  As an example, we take the completely negative game
\[
  \bot=\{\{*\},\{*\mapsto O\},\{\emptyplay\mapsto P,\;*\mapsto O\}, \{\emptyplay, *\}\}
  \]
which has a single $O$-move with no $P$-replies.  If $A$ is an acn $\alpha$-game, then $A\implies\bot$ is the same as the game $\neggame A$, but with the extra $O$-move $*$ attached to the start.  For $\omega$-games, this extra $O$-move means that $A\implies\bot$ is negative if $A$ is negative, but if $A$ contains plays of length greater than $\omega$ then $A\implies\bot$ is not completely negative if $A$ is completely negative: indeed, if $s\in P_A$ is a non-empty limiting play, then we have
\[
  \zeta_{A\implies\bot}(*s)=(\zeta_A(s)\Rightarrow\zeta_\bot(*))=(P\Rightarrow O) = O
  \]
But $*s$ is a limiting play, so $A\implies\bot$ is not completely negative.

This will pose a problem for our categorical semantics.  We want to build a category where the objects are acn $\alpha$-games and where the morphisms from a game $A$ to a game $B$ are strategies for $A\implies B$.  We also want the category to be monoidal closed, which means that we would really like $A\implies B$ to be an object of the category.  As we have just seen, this is not the case in general.

We take the following approach: we define a morphism in our category between objects $A$ and $B$ to be a strategy for $A\implies B$, ignoring the fact that this is not an object of our category.  We will get a working definition of the composition of strategies.  Then, when we come to define the monoidal closed structure on the category, we will use a slightly modified form of $A\implies B$ for our linear implication.  This modified form will be, in a sense we shall make precise, the smallest modification of $A\implies B$ that is completely negative, and this will be enough to show that it does indeed give us a monoidal closed structure.

Before moving on to the discussion of composition of strategies, we shall want a version of Proposition \ref{nice-negative-games} to record the properties of negative games that make them so useful for our definition of composition.

\begin{proposition}
  \label{NiceAcnGames}
  a) Let $A,B$ be acn $\alpha$-games and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\tensor B}$.  Then:
  \begin{enumerate}[i)]
    \item If $s$ is not a length maximal limiting play, then either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=P$.  
    \item $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$ (so $s\in P_{A\tensor B}$).
  \end{enumerate}

  b) Let $A$ be an acn $\alpha$-game, {\bf let $B$ be an arbitrary $\alpha$-game} and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\implies B}$.  Then:
  \begin{enumerate}[i)]
    \item If $s$ is not a length maximal limiting play, then either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=O$.
    \item $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$ (so $s\in P_{A\implies B}$).
  \end{enumerate}
\end{proposition}

Note that the extra hypothesis on (i) is necessary: suppose $\alpha=\omega+1$ and let $\st$ be as defined above where the unique infinite play is $O$-winning.  Then $\st\tensor\st$ contains an infinite play $s$ both of whose components are infinite and we have $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=O$.

\begin{proof}[Proof of Proposition \ref{NiceAcnGames}]
  (a): By Proposition \ref{TransTensorWellFormed}, for part (ii) it suffices to show that the set of alternating plays in $P_A\|P_B$ is well-formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$ - i.e., that if $s,sx\in P_A\|P_B$ are alternating then $\zeta_{A\tensor B}(sx)=\lambda_{A\tensor B}(x)$.

  If $s$ is a limiting play, then one of $s\vert_A,s\vert_B$ must be a limiting play.  By Lemma \ref{TechnicalOrdinalLemma}, $\length(s\vert_A),\length(s\vert_B)\le\length(s)$, so $s\vert_A$ and $s\vert_B$ are not length maximal if $s$ is not.  Therefore, either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=P$, since $A$ and $B$ are both acn.

  We may now prove (i) and (ii) for all successor plays by induction on their length, exactly as we did in Proposition \ref{nice-negative-games}.

  (b): Again, by Proposition \ref{TransTensorWellFormed}, for part (ii) it suffices to show that the set of alternating plays in $P_A\|P_B$ is well-formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$ - i.e., that if $s,sx\in P_A\|P_B$ are alternating then $\zeta_{A\implies B}(sx)=\lambda_{A\tensor B}(x)$.

  We prove this by induction on the length of the play $s$; the successor case is exactly as in Proposition \ref{nice-negative-games}.  Suppose that $s$ is a non-length maximal limiting play.  If $s\vert_A$ is a limiting play, then we are done, since $A$ is acn and $s\vert_A$ is not length maximal by Lemma \ref{TechnicalOrdinalLemma}.  Otherwise, if $s\vert_A$ is a successor play, then it has a last move $a$.  Since $s$ is a limiting play, there must be moves from $B$ occurring later in $s$ than $a$, so $a$ is an $O$-move in $A\implies B$ by Proposition \ref{TransWhoSwitchesGames}, so it is a $P$-move in $A$.
\end{proof}

\subsubsection{Interleavings and the functor into $\Rel$}

We now set out to extend to the transfinite case some of the results that we proved in the previous section about plays and strategies for the game $A\implies B$.

\begin{lemma}
  \label{TransPlayInStrategyDeterminedByComponents}
  Let $A,B$ be $\alpha$-games and let $\sigma$ be a strategy for $A\implies B$.  Suppose that $s,t\in\sigma$ are such that $s\vert_A=t\vert_A$ and $s\vert_B=t\vert_B$.  Then $s=t$.
  \begin{proof}
    Exactly as in Lemma \ref{PlayInStrategyDeterminedByComponents}: suppose $s\ne t$.  By well-ordering, there is an earliest index $\beta$ such that $s(\beta)\ne t(\beta)$.  So we have a sequence $r$ and moves $x\ne y$ such that $rx\prefix s$ and $ry\prefix t$.  Since $x\ne y$, $r$ must be a $P$-position by the definition of strategy, and so $x,y$ must take place in the same game.  Therefore, either $s\vert_A\ne t\vert_A$ or $s\vert_B\ne t\vert_B$.
  \end{proof}
\end{lemma}

Given acn $\alpha$-games $A$ and $B$ and a strategy $\sigma$ for $A\implies B$, we may define a relation $\grel\sigma\subset P_A\times P_B$ by
\[
  \grel\sigma = \{(s\vert_A,s\vert_B)\suchthat\textrm{$s\in\sigma$ is a $P$-position}\}
  \]
Once we have our category $\G(\alpha)$ set up, this will allow us to define a functor $\cmap{\F(\alpha)}{\G(\alpha)}{\Rel}$.  Then the following lemma, which is a version of Lemma \ref{HylandSchalkFaithful}, will tell us that this functor is faithful.

\begin{lemma}
  \label{TransHylandSchalkFaithful}
  Let $A,B$ be $\alpha$-games and let $\sigma,\sigma'$ be strategies for $A\implies B$.  Suppose that $\grel\sigma=\grel{\sigma'}$ as subsets of $P_A\times P_B$.  Then $\sigma=\sigma'$.
  \begin{proof}
    See Appendix \ref{HylandSchalkFaithfulProof}.
  \end{proof}
\end{lemma}

We will postpone discussion of the functor $\cmap{\F(\alpha)}{\G(\alpha)}{\Rel}$ until we have proved the main technical result, which will be the transfinite version of Lemma \ref{LiftingLemma}.

\begin{lemma}
  \label{TransLiftingLemma}
  Let $A,B$ be acn $\alpha$-games, let $C$ be an arbitrary $\alpha$-game, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose that $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$.  Then there exists some ordinal $\beta<\alpha\#\alpha$ such that for all $\gamma$ with $0\le\gamma\le\beta$ there is a unique sequence $\s^\gamma\in\sigma\|\tau$ of length $\gamma$ such that $\s^\gamma\vert_A\prefix s\vert_A$ and $\s\gamma\vert_C\prefix t\vert_C$.  Moreover, for this $\s^\gamma$ we have $\s^\gamma\vert_{A,B}\prefix s$ and $\s^\gamma\prefix t$ and if $\delta\le\gamma$ then $\s^\delta\prefix\s^\gamma$.  Lastly, we have $\s^\beta\vert_{A,B}=s$ and $\s^\beta\vert_{B,C}=t$.
\end{lemma}

Note that we have no explicit formula for the ordinal $\beta$ as we did for the the numeral $n$ in Lemma \ref{LiftingLemma}, owing to the fact that addition of ordinals is less well-behaved than addition of numerals.  Nevertheless, this lemma shall be sufficient for our purposes.

\begin{proof}[Proof of Lemma \ref{TransLiftingLemma}]
  We proceed by induction on $\gamma$.  At some point we will be unable to proceed further with the induction, so we terminate and the final $\gamma$ we reach will be our $\beta$.

  There is a unique sequence of length $0$, namely the empty sequence and its $A$- and $C$-components are both empty, so are prefixes of $s$ and $t$.

  Now suppose that $\mu$ is a limit ordinal and that we have a chain of sequences $\s^\gamma$ for all $\gamma<\mu$ such that $\s^\gamma\vert_{A,B}\prefix s$ and $\s^\gamma\vert_{B,C}\prefix t$.  Then we may take the limit $\s^\mu$ of these sequences and we have $\s^\mu\vert_{A,B}\prefix s$ and $\s^\mu\vert_{B,C}\prefix t$.  For uniqueness, suppose that $\t^\mu$ has length $\mu$ and that $\t^\mu\vert_A\prefix s\vert_A$ and $\t^\mu\vert_C\prefix t\vert_C$.  Let $\gamma<\mu$, and let $\t^\gamma$ be the initial prefix of $\t^\mu$ of length $\gamma$.  Then $\t^\gamma\vert_A\prefix s\vert_A$ and $\t^\gamma\vert_C\prefix t\vert_C$, so $\t^\gamma=\s^\gamma$, by uniqueness.  Since $\gamma<\mu$ was arbitrary, it follows that $\t^\mu=\s^\mu$.

  Lastly, suppose that $\gamma=\delta+1$ for some ordinal $\delta$ and suppose that we have already constructed the sequence $\s^\delta$.  If $X$ is an acn $\alpha$-games, $y$ is an arbitrary $\alpha$-game and $r\in P_{X\implies Y}$ is not length maximal, then Proposition \ref{NiceAcnGames}(i) tells us that either $\zeta_X(r\vert_X)=P$ or $\zeta_Y(r\vert_Y)=O$.  We have $\s^\delta\vert_{A,B}\in P_{A\implies B}$ and $\s^\delta\vert_{B,C}\in P_{B\implies C}$, so if we assume that $\s^\delta\vert_{A,B}$ and $\s^\delta\vert_{B,C}$ are not length maximal plays, this gives us four possible `sign profiles' for the components of the sequence $\s^\delta$:

  \[
    \begin{array}{c|ccc}
      \textbf{Case} & \zeta_A(\s^\delta\vert_A) & \zeta_B(\s^\delta\vert_B) & \zeta_C(\s^\delta\vert_C) \\
      \hline
      \textbf{A} & P & P & P \\
      \textbf{B} & P & P & O \\
      \textbf{C} & P & O & O \\
      \textbf{D} & O & O & O
    \end{array}
    \]

  We now split the argument up according to cases:

  \begin{description}
    \item[Cases A and B: ] We have $\s^\delta\vert_{B,C}\prefix t$.  If in fact $\s^\delta\vert_{B,C}=t$, then we terminate and set $\beta=\delta$.  We claim that in this case we must have $\s^\beta\vert_{A,B}=s$.  Certainly, $\s^\beta\vert_{A,B}\prefix s$; if this prefix relation is proper then we must have $\s^\beta\vert_{A,B}x\prefix s$ for some move $x$.  Since $\zeta_A(\s^\beta\vert_A)=\zeta_B(\s^\beta\vert_B)=P$, $x$ must be an $O$-move and it must therefore take place in $B$, which is a contradiction, since $s\vert_B=t\vert_B$:
      \[
        \s^\beta\vert_Bx\prefix s\vert_B = t\vert_B=\s^\beta\vert_{B,C}\vert_B=\s^\beta\vert_B\quad\textbf{(contradictory)}
        \]
      Therefore, $\s^\beta\vert_{A,B}=s$.  We must have $\beta<\alpha\#\alpha$, since we may decompose the set of (distinct) moves in $\s^k$ as the disjoint union of the set of moves that occur in $A$ and the set of moves that occur in $B$ or $C$.  The induced ordering on each of these sets corresponds with the natural ordering of the moves as a play in $P_A$ or in $P_{B\implies C}$, and since $A$ and $B\implies C$ are both $\alpha$-games, this implies that these two orders are both less than $\alpha$.

      Now suppose instead that $\s^\delta\vert_{B,C}$ is a \emph{proper} prefix of $t$.  So $\s^\delta\vert_{B,C}x\prefix t$ for some move $x$.  We set $\s^{\delta+1}=\s^\delta x$.  Now certainly $\s^{\delta+1}\vert_{B,C}\prefix t$; we claim that $\s^{\delta+1}\vert_{A,B}\prefix s$.

      If $x$ is a move from $C$ then $\s^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}\prefix s$.  So suppose that $x$ is a move from $B$ - so $\s^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}x$.  Since $s\vert_B=t\vert_B$, this must be a prefix of $s$ unless there is some move from $A$ that occurs immediately after $\s^\delta\vert_{A,B}$.  But this is impossible in \textbf{Cases A and B}, since $\s^\delta\vert_{A,B}$ is a $P$-position in $A\implies B$ while $\s^\delta\vert_A$ is an $O$-position in $\neggame A$, so any move following $\s^\delta\vert_{A,B}$ must be a move in $B$.

      Lastly, we show uniqueness.  Suppose that $\t^{\delta+1}\in \sigma\|\tau$ has length $\delta+1$ and that $\t\vert_A\prefix s\vert_C$ and $\t\vert_C\prefix t\vert_C$.  Let $y$ be the last move of $\t^{\delta+1}$ and write $\t^{\delta+1}=\t^\delta y$.  Then we have
      \[
        \t^\delta\vert_A\prefix \t^{\delta+1}\vert_A\prefix s\vert_A\quad\t^\delta\vert_C\prefix\t^{\delta+1}\vert_C\prefix t\vert_C
        \]
      and so $\t^\delta=\s^\delta$ by uniqueness for sequences of length $\delta$.  We claim that $y=x$.  By our argument above, $y$ cannot be a move from $A$, so it is a move from $B$ or $C$.  Then we have:
      \begin{gather*}
        \s^\delta y\vert_{B,C} = \t^{\delta+1}\vert_{B,C}\in\tau \\
        \s^\delta x\vert_{B,C} \prefix t\in\tau
      \end{gather*}
      In \textbf{Case B}, $\s^\delta\vert_{B,C}x,\s^\delta\vert_{B,C}y$ are both $P$-plays in $B\implies C$, so they must be equal, since $\tau$ is a strategy.  In \textbf{Case A}, $x$ and $y$ must both be $O$-moves in $C$.  So the fact that $\t^{\delta+1}\vert_C=\s^{\delta+1}\vert_C$ means that $x=y$.

      Therefore, $\t^{\delta+1}=\s^{\delta+1}$.

    \item[Cases C and D: ] Entirely symmetrical.  This time, we get the next move from $s$ instead of $t$, and uniqueness follows from the fact that $\sigma$ is a strategy. 
  \end{description}

  We still need to deal with the case that one of $\s^\delta\vert_{A,B},\s^\delta\vert_{B,C}$ is length maximal.  In that case, the `sign profile' for the components of $\s^\delta$ might not fit one of the cases in the table above, since Proposition \ref{NiceAcnGames}(i) only holds for non-length maximal pays.  If the components of $\s^\delta$ do fit \textbf{Case A, B, C or D} above, then our existing argument is valid.  Otherwise, there are four new cases to consider:
  \[
    \begin{array}{c|cccl}
      \textbf{Case} & \zeta_A(\s^\delta\vert_A) & \zeta_B(\s^\delta\vert_B) & \zeta_C(\s^\delta\vert_C) & \\
      \cline{1-4}
      \textbf{E} & O & P & P & \rdelim\}{2}{60mm}[\parbox{60mm}{\hangindent=1em where $\s^\delta\vert_{A,B}$ is a length maximal \\ limiting play}] \\
      \textbf{F} & O & P & O & \\
      \textbf{G} & P & O & P & \rdelim\}{2}{60mm}[\parbox{60mm}{\hangindent=1em where $\s^\delta\vert_{B,C}$ is a length maximal \\ limiting play}] \\
      \textbf{H} & O & O & P &
    \end{array}
    \]

  In \textbf{Cases E and F}, we must have $\s^\delta\vert_{A,B}=s$, since it is already length maximal.  If we also have $\s^\delta\vert_{B,C}=t$ then we set $\beta=\delta$ and terminate.  Otherwise, we have $\s^\delta\vert_{B,C}x\prefix t$ for some move $x$, and we set $\s^{\delta+1}=\s^\delta x$.  Then we certainly have $\s^{\delta+1}\vert_{A,B}\prefix s$ and $\s^{\delta+1}\vert_{B,C}\prefix t$.

  For uniqueness, suppose that $\t^{\delta+1}\in\sigma\|\tau$ has length $\delta+1$ and that $\t^{\delta+1}\vert_A\prefix s\vert_A$ and $\t^{\delta+1}\vert_C\prefix t\vert_C$.  As before, the induction hypothesis tells us that $\t^{\delta+1}$ must be of the form $\s^\delta y$ for some move $y$.  We claim that $x$ and $y$ must both be moves in $C$: if $x$ is a move in $A$ or $B$ then we have $\s^\delta\vert_{A,B}x\prefix s$, contradicting length maximality of $\s^\delta\vert_{A,B}$.  If $y$ is a move in $A$ or $B$ then we have $\t^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}y\in\sigma$, and this also contradicts length maximality of $\s^\delta\vert_{A,B}$.  It follows that $x$ and $y$ are both moves in $C$, so they are identical, since $\s^{\delta+1}\vert_C=\t^{\delta+1}\vert_C$.

  We deal with \textbf{Cases G and H} using a symmetrical argument.
\end{proof}

We shall use (the proof of) this lemma to show that composition is well defined for acn $\alpha$-games.  First, though, we shall need to impose some conditions on the ordinal $\alpha$.  To start with, we shall assume that $\alpha=\omega^\beta$ for some $\beta$.  It is well known that these are precisely the \emph{additively closed} ordinals -- so if $\gamma,\delta<\omega^\beta$ then $\gamma+\delta<\omega^\beta$.  We shall want a stronger property though -- the ordinals of the form $\omega^\beta$ are closed under the natural addition $\#$ that we introduced earlier.

To see this, suppose that $\gamma,\delta<\omega^\beta$.  We may write $\gamma$ and $\delta$ in their \emph{Cantor normal forms}:
\begin{gather*}
  \gamma = \omega^{\beta_1}.j_1 + \omega^{\beta_2}.j_2 + \cdots + \omega^{\beta_n}.j_n \\
  \delta = \omega^{\beta_1}.k_1 + \omega^{\beta_2}.k_2 + \cdots + \omega^{\beta_n}.k_n
\end{gather*}
Here, $\beta_1>\beta_2>\cdots>\beta_n$, and $n,j_1,\dots,j_n,k_1,\dots,k_n<\omega$ (We allow $j_i,k_i$ to be zero so that we can use the same sequence $\beta_i$ in both cases.)  Then we may write
\[
  \gamma\#\delta = \omega^{\beta_1}.(j_1+k_1) + \omega^{\beta_2}.(j_2+k_2) + \cdots + \omega^{\beta_n}.(j_n+k_n)
  \]
using the fact that $\omega^\xi+\omega^\eta=\omega^\xi\#\omega^\eta$ if $\xi\ge\eta$ and the fact that the natural addition $\#$ is commutative.  Since $\gamma,\delta<\omega^\beta$, we must have $\beta_i<\beta$ for each $i$ and therefore $\gamma\#\delta<\omega^\beta$, since $\omega^\beta$ is additively closed.

The reason that this is good for us is that it means that if $A,B,C$ are completely negative $\omega^\beta$-games, and if $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$ then any sequence $\s\in\sigma\|\tau$ must have length less than $\omega^\beta$.  Indeed, we may split $\s$ into its $A,B$-component and its $C$-component -- if these have lengths $\gamma,\delta<\omega^\beta$ then the full sequence has length at most $\gamma\#\delta<\omega^\beta$.  This allows us to ensure that $\s\vert_{A,C}$ has length at most $\omega^\beta$ -- so that it is a valid play in $A\implies C$.

To get an idea of why we need to make some restriction on the ordinal $\alpha$, consider the situation when $\alpha=\omega^2+1$.  We define a game $\st$ as before:
\begin{gather*}
  M_{\st} = \{q,a\} \\
  \lambda_{\st}(q) = O,\;\lambda_{\st}(a)=P \\
\end{gather*}
$P_\st$ will be the set of all plays $s\in M_\st^{*<\omega^2+1}$ such that $q$ is always followed by $a$, $a$ is always followed by $q$ and a limiting play is always followed by $q$.  We define $\zeta_\st$ to make $\st$ into a completely negative game.

Let $A=B=C=\st$.  Consider the sequence of plays $s_0,s_1,\dots,s_{\omega^2}$ in $A\implies B$ shown in Figure \ref{TooLongAB} and the sequence $t_0,t_1,\dots,t_{\omega+1}$ in $B\implies C$ shown in Figure \ref{TooLongBC}.  These sequences have matching $B$-components, so Lemma \ref{TransLiftingLemma} tells us that we can interleave them to give a sequence $\s$.  But now $\s\vert_{A,C}$ consists in a single move in $C$ followed by a play of length $\omega^2$ in $A$, followed by a single move in $C$ - in other words, it has length $\omega^2+1$, which is too long.  
\begin{figure}[!ht]
  \[
    \begin{array}{ccccc}
      \delta & A & B & \zeta_A(s_\delta\vert_A) & \zeta_B(s_\delta\vert_B) \\
      \hline
      0 & & & P & P \\
      \hline
      1 & & q & P & O \\
      2 & q & & O & O \\
      3 & a & & P & O \\
      4 & q & & O & O \\
      5 & a & & P & O \\
      \vdots & \vdots & & \vdots & \vdots \\
      \hline
      \omega & & & P & O \\
      \hline
      \omega+1 & & a & P & P \\
      \omega+2 & & q & P & O \\
      \omega+3 & q & & O & O \\
      \omega+4 & a & & P & O \\
      \vdots & \vdots & & \vdots & \vdots \\
      \hline
      \omega2 & & & P & O \\
      \hline
      \omega2+1 & & a & P & P \\
      \omega2+2 & & q & P & O \\
      \omega2+3 & q & & O & O \\
      \omega2+4 & a & & P & O \\
      \vdots & \vdots & & \vdots & \vdots \\
      \hline
      \omega3 & & & P & O \\
      \hline
      \multicolumn{5}{c}{\vdots}\\
      \multicolumn{5}{c}{\vdots}\\
      \hline
      \omega^2 & & & P & P \\
      \hline
    \end{array}
    \]
  \caption{Diagrammatic representation of a play $s$ of length $\omega^2$ in $A\implies B=\st\implies \st$.  Here $\s_\delta$ is the initial segment of $s$ of length $\delta$.  Note that $s\vert_A$ has length $\omega^2$, while $s\vert_B$ has length $\omega$, since only finitely many moves from $B$ are played in each $\omega$-segment.}
  \label{TooLongAB}
\end{figure}

\begin{figure}[!ht]
  \[
    \begin{array}{ccccc}
      \delta & B & C & \zeta_B(t_\delta\vert_B) & \zeta_C(t_\delta\vert_C) \\
      \hline
      0 & & & P & P \\
      \hline
      1 & & q & P & O \\
      2 & q & & O & O \\
      3 & a & & P & O \\
      4 & q & & O & O \\
      5 & a & & P & O \\
      \vdots & \vdots & & \vdots & \vdots \\
      \hline
      \omega & & & P & O \\
      \hline
      \omega+1 & & a & P & P \\
    \end{array}
    \]
  \caption{Diagrammatic representation of a play $t$ of length $\omega+1$ in $B\implies C=\st\implies \st$.  Compare with Figure \ref{TooLongAB} and notice that the $B$-component of this sequence is exactly the same as the $B$-component in that sequence.}
  \label{TooLongBC}
\end{figure}

Therefore we shall restrict for now to ordinals $\alpha$ of the form $\omega^\beta$.  This means in particular that there is no distinction between completely negative $\alpha$-games and acn $\alpha$-games, so we shall deal with completely negative games for simplicity.  Later on, we shall mimic the construction of win-games to construct categories of games over ordinals of the form $\omega^\beta+1$, but for the reasons outlined above this will not be as simple as changing the ordinal from $\omega^\beta$ to $\omega^\beta+1$ in our definitions.

Now we have made this restriction on $\alpha$, the fact that composition is well-defined follows as a corollary of Lemma \ref{TransLiftingLemma}.

\begin{corollary}
  Let $\alpha$ be an ordinal of the form $\omega^{\beta}$.  Let $A,B$ be completely negative $\alpha$-games, let $C$ be an arbitrary $\alpha$-game, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Set
  \[
    \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
    \]
  as before.  Then $\comp\tau\sigma$ is a strategy for $A\implies C$.

  \begin{proof}
    We first claim that if $\s\in\sigma\|\tau$ then $\length(\s)<\alpha$.  Indeed, suppose that $\length(\s\vert_{A,B})=\gamma$ and $\length(\s\vert_C)=\delta$.  Then $\gamma,\delta<\alpha$, since $\s\vert_{A,B}\in P_{A\implies C}$ and $\s\vert_C\in P_C$.  We have order-preserving inclusions
    \begin{gather*}
      \gamma\hookrightarrow\length(\s)\\
      \delta\hookrightarrow\length(\s)
    \end{gather*}
    that make the underlying set of $\length(\s)$ into the disjoint union $\gamma\sqcup\delta$.  Then the induced orderings on $\gamma,\delta$ are the same as their original orderings, so we must have $\length(\s)\le\gamma\#\delta$.  Since $\alpha$ is closed under natural addition $\#$, this means that $\length(\s)<\alpha$.

    Now we see that $\comp\tau\sigma\subset P_A\|P_C$: if $\s\in\sigma\|\tau$, then $\s\vert_{A,C}\vert_A=\s\vert_{A,B}\vert_A\in P_A$ and similarly $\s\vert_{A,C}\vert_C=\s\vert_{B,C}\vert_C\in P_C$.  To show that $\comp\tau\sigma\subset P_{A\implies C}$, it suffices by Proposition \ref{NiceAcnGames}(ii) to show that $\comp\tau\sigma$ is alternating with respect to $\zeta_{A\implies C}$.

    Suppose $\s a\in\sigma\|\tau$ for some move $a\in M_A$.  By the proof of Lemma \ref{TransLiftingLemma}, we must be in \textbf{Case C or D} (there are no length maximal plays, so \textbf{Cases G and H} never occur).  The following table shows that we must have $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{A\implies C}(\s\vert_{A,C})$:
    \[
      \begin{array}{c|ccc|cc}
        \textbf{Case} & \zeta_A(\s\vert_A) & \zeta_B(\s\vert_B) & \zeta_C(\s\vert_C) & \zeta_{A\implies B}(\s\vert_{A,B}) & \zeta_{A\implies C}(\s\vert_{A,C}) \\
        \hline
        \textbf{C} & P & O & O & O & O \\
        \textbf{D} & O & O & O & P & P \\
      \end{array}
      \]
    Then we get:
    \[
      \lambda_{A\implies C}(a) = \lambda_{A\implies B}(a) = \neg\zeta_{A\implies B}(\s) = \neg\zeta_{A\implies C}(\s)
      \]
    as desired.  The case when we have $\s c\in\tau\|\sigma$ for some $c\in M_C$ is entirely symmetrical, working in \textbf{Cases A and B} this time.  Therefore, $\comp\tau\sigma\subset P_{A\implies C}$.

    We now need to show that the two strategy conditions are satisfied.  Let $\s\in\sigma\|\tau$ and suppose that $\s\vert_{A,C}$ is a $P$-position and that $a\in M_A$ is an $O$-move in $A$ such that $\s\vert_{A,C}a \in P_{A\implies C}$.  We want to show that $\s\vert_{A,C}a\in \comp\tau\sigma$.  Since $\s\vert_{A,C}$ is a $P$-position, we must be in \textbf{Case A or Case D}.  In that case, $\s\vert_{A,B}$ is a $P$-position and we know that $\s\vert_Aa\in P_A$, so $\s\vert_{A,B}a\in P_{A\implies B}$.  Since $\sigma$ is a strategy, that implies that $\s\vert_{A,B}a\in\sigma$ and therefore $\s a\in\sigma\|\tau$.  So we have $\s\vert_{A,C}a=\s a\vert_{A,C}\in\comp\tau\sigma$.

    A symmetrical argument shows that if $c\in M_C$ is an $O$-move in $C$ and $\s\vert_{A,C}c\in P_{A\implies C}$ then $\s\vert_{A,C}c\in\comp\tau\sigma$.

    Lastly, suppose that we have $s\in P_{A\implies C}$ is an $O$-position and that $x,y\in M_{A\implies C}$ are $P$-moves such that $sx,sy\in\comp\tau\sigma$.  We need to show that $x=y$.  By the definition of $\comp\tau\sigma$, there are sequences $\s,\t\in\sigma\|\tau$ with $\s\vert_{A,C}=sx$ and $\t\vert_{A,C}=sy$.  We may write:
    \begin{gather*}
      \s = \s'x \\
      \t = \t'y
    \end{gather*}

    Without loss of generality, assume that $\length(\s')\le\length(\t')$ and write $\t'=\t''\r$, where $\t''$ has the same length as $\s'$.  Then $\t''\vert_A\prefix\s'\vert_A$ and $\t''\vert_C\prefix\s'\vert_C$, so $\t''=\s'$ by Lemma \ref{TransLiftingLemma}.

    We claim that $\r=\emptyplay$.  Indeed, suppose $\r$ is non-empty.  We have
    \[
      \t''\r\vert_{A,C}=\t'\vert_{A,C}=s=\s'\vert_{A,C}=\t''\vert_{A,C}
      \]
    and so $\r$ must be entirely composed of moves from $B$.  Let $b$ be the first move in $\r$.  Then $\s'x$ and $\s'b$ have the same length and we have $\s'b\vert_A\prefix\s'x\vert_A$ and $\s'b\vert_C\prefix\s'x\vert_C$, so $b=a$, which is impossible.

    Therefore, we must have $\s'x, \s'y\in\sigma\|\tau$.  Since $x,y$ are $P$-moves in $A\implies C$, each must be either an $O$-move in $A$ or a $P$-move in $C$.  It follows that either $\s'$ is in \textbf{Case B} and $x$ and $y$ are both moves in $C$ or that $\s'$ is in \textbf{Case C} and $x$ and $y$ are both moves in $A$.  Suppose $\s'$ is in \textbf{Case B} and $x$ and $y$ are moves in $C$.  Then $\s'\vert_{B,C}x,\s'\vert_{B,C}\in\tau$ and so $x=y$, since they are $P$-moves and $\tau$ is a strategy.  Similarly, if $\s'$ is in \textbf{Case C} and $x$ and $y$ are moves in $A$, we have $\s'\vert_{A,B}x,\s'\vert_{A,B}y\in\sigma$ and so $x=y$ since $\sigma$ is a strategy.
  \end{proof}
\end{corollary}

As a second corollary of Lemma \ref{TransLiftingLemma}, we show that the relational presentation of games and strategies respects composition:

\begin{corollary}
  \label{TransHylandSchalkIsFunctor}
  Let $\alpha=\omega^\beta$ for some $\beta$ and let $A,B,C$ be completely negative $\alpha$-games.  Let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then we have:
  \[
    \grel{\comp\tau\sigma} = \comp{\grel\tau}{\grel\sigma}
    \]
  \begin{proof}
    We have 
    \begin{gather*}
      \grel{\comp\tau\sigma} = \left\{(s\vert_A,s\vert_C)\suchthat\textrm{$s\in\comp\tau\sigma$ is a $P$-play}\right\} \\
      \comp{\grel\tau}{\grel\sigma}=\{(s,t)\in P_A\times P_C\suchthat\exists u\in P_B\esuchthat (s,u)\in\grel\tau,\;(u,t)\in\grel\sigma\}
    \end{gather*}
    Suppose $s\in\comp\tau\sigma$ is a $P$-play and write $s=\s\vert_{A,C}$, where $\s\in\sigma\|\tau$.  Then we have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$.  Since $s=\s\vert_{A,C}$ is a $P$-play, $\s$ must be in \textbf{Case A or Case D}, so $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both $P$-plays.  Therefore, we have
    \begin{gather*}
      (s\vert_A,\s\vert_B)\in\grel\sigma\\
      (\s\vert_B,s\vert_C)\in\grel\tau
    \end{gather*}
    and therefore $(s\vert_A,s\vert_C)\in\comp{\grel\tau}{\grel\sigma}$.  Conversely, suppose $(s, t)\in\comp{\grel\tau}{\grel\sigma}$.  Then there exist $S\in\sigma,T\in\tau$ such that $S\vert_A=s$, $S\vert_B=T\vert_B$ and $T\vert_C=t$.  By Lemma \ref{TransLiftingLemma}, there is some $\s\in\sigma\|\tau$ such that $\s\vert_A=s$ and $\s\vert_C=t$.  So $(s,t)\in\grel{\comp\tau\sigma}$.
  \end{proof}
\end{corollary}

\begin{corollary}
  \label{TransIsCategory}
  Let $\alpha=\omega^\beta$ for some $\beta$.  Then we can define a category $\G(\alpha)$ as follows - the objects are completely negative $\alpha$-games, and if $A,B$ are two objects then a morphism from $A$ to $B$ is given by a strategy for $A\implies B$.  We compose strategies as above.  If $A$ is an object, then the identity morphism on $A$ is given by
  \[
    \id_A = \left\{s\in P_{A\implies A}\suchthat\textrm{for all $P$-positions $t\prefix s$, $t\vert_A=t\vert_\bneggame{A}$}\right\}
    \]
  \begin{proof}
    We need to check that this is indeed an identity and that composition is associative.  We do this using the relational presentation exactly as in Theorem \ref{IsCategory}.  
  \end{proof}
\end{corollary}

\subsubsection{Symmetric monoidal structure}

In this section, we shall fix an ordinal $\alpha=\omega^\beta$.  The tensor product $\tensor$ on $\alpha$-games makes the category $\G(\alpha)$ into a monoidal category.  If $A,B$ are objects of $\G(\alpha)$, then Proposition \ref{TensorIsAcn} tells us that $A\tensor B$ is an object of $\G(\alpha)$.  In fact, $\tensor$ gives us a functor $\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ as follows: let $A,A',B,B'$ be completely negative $\alpha$-games, let $\sigma$ be a strategy for $A'\implies A$ and let $\tau$ be a strategy for $B'\implies B$.  Then we define a strategy $\sigma\tensor\tau$ for $(A'\tensor B')\implies (A\tensor B)$ as follows:
\[
  \sigma\tensor\tau = \{s\in P_{(A'\tensor B')\implies(A\tensor B)}\suchthat s\vert_{A',A}\in\sigma,\;s\vert_{B',B}\in\tau\}
  \]
To show that this is indeed a strategy for $(A'\tensor B')\implies (A\tensor B)$, suppose that $s\in\sigma\tensor\tau$ is a $P$-position and that $sx\in P_{(A'\tensor B')\implies (A\tensor B)}$.  We need to show that $sx\vert_{A',A}\in\sigma$ and that $sx\vert_{B', B}\in\tau$.

We claim that $s\vert_{A',A}$ and $s\vert_{B',B}$ are $P$-positions in $A'\implies A$ and $B'\implies B$.  Indeed, suppose without loss of generality that $s\vert_{A',A}$ is an $O$-position in $A'\implies A$.  We will show that $s$ is an $O$-position in $(A'\tensor B')\implies (A\tensor B)$, contradicting our assumptions.

If $s\vert_{A',A}$ is an $O$-position, then $s\vert_{A'}$ is a $P$-position in $A'$ and $s\vert_A$ is an $O$-position in $A$.  Now, $s\vert_{A,B}$ is a play in $A\tensor B$, so Proposition \ref{NiceAcnGames}(i) tells us that $s\vert_B$ must be a $P$-position in $B$.

Now $s\vert_{B',B}$ is a play in $\tau\subset P_{B'\implies B}$, so Proposition \ref{NiceAcnGames}(i) now tells us that $s\vert_{B'}$ is a $P$-position in $B'$.  It follows that $s\vert_{A',B'}$ is a $P$-position in $A'\tensor B'$ and that $s\vert_{A,B}$ is an $O$-position in $A\tensor B$, so $s$ is an $O$-position in $(A'\tensor B')\implies (A\tensor B)$, which is the desired contradiction.

Without loss of generality, suppose that the move $x$ occurs in $A'$ or $A$.  Since $s\vert_{A', A}$ is a $P$-position, we must have $sx\vert_{A',A}\in\sigma$, by the definition of a strategy, and then $s x\vert_{B',B}=s\vert_{B',B}\in\tau$.  So $sx\in\sigma\tensor\tau$.

For the second strategy condition, suppose that $sx, sy\in\sigma\tensor \tau$, where $s$ is an $O$-position in $(A'\tensor B')\implies(A\tensor B)$ and $x,y$ are $P$-moves.  Then $s\vert_{A',B'}$ is a $P$-position in $A'\tensor B'$ and $s\vert_{A,B}$ is an $O$-position in $A\tensor B$.

This immediately tells us that $s\vert_{A'}$ is a $P$-position in $A'$ and that $s\vert_{B'}$ is a $P$-position in $B'$.  Moreover, by Proposition \ref{NiceAcnGames}(i), we know that either $s\vert_{A}$ is a $P$-position in $A$ and $s\vert_{B}$ is an $O$-position in $B$ or that $s\vert_A$ is an $O$-position in $A$ and $s\vert_B$ is a $P$-position in $B$.

That is, we find ourselves in one of the following cases:
\[
  \begin{array}{c|cccc}
    \textbf{Case} & \zeta_{A'}(s\vert_{A'}) & \zeta_{B'}(s\vert_{B'}) & \zeta_A(s\vert_A) & \zeta_B(s\vert_B) \\
    \hline
    \textbf{1} & P & P & P & O\\
    \textbf{2} & P & P & O & P
  \end{array}
  \]

Suppose we are in \textbf{Case 1}.  Then $x$ cannot be a move in $A$ or $A'$: indeed, it is a $P$-move in $(A'\tensor B')\implies (A\tensor B)$, so it would be a $P$-move in $A'\implies A$.  But $s\vert_{A',A}$ is a $P$-position in $A'\implies A$.  Similarly, $y$ cannot be a move in $A$ or $A'$.  Therefore, $x$ and $y$ are both $P$-moves in $B\implies B'$, and then the fact that $\tau$ is a strategy implies that $x=x'$.

In \textbf{Case 2}, we can use a symmetrical argument, this time using the fact that $\sigma$ is a strategy.

It is easy to show that this tensor action on strategies respects composition: indeed, if we have morphisms
\begin{gather*}
  A''\xrightarrow{\sigma'}A'\xrightarrow{\sigma}A\\
  B''\xrightarrow{\tau'}B'\xrightarrow{\tau}B
\end{gather*}
then we have
\begin{gather*}
  (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'}) = \left\{s\in P_{(A''\tensor B'')\implies(A\tensor B)}\suchthat s\vert_{A'', A}\in\comp\sigma{\sigma'},\;s\vert_{B'', B}\in\comp\tau{\tau'}\right\}
\end{gather*}
Meanwhile:
\begin{align*}
  (\sigma'\tensor\tau')\|(\sigma\tensor\tau) &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{120pt}{
    \setlength{\abovedisplayskip}{-5pt}
    \setlength{\belowdisplayskip}{-10pt}
    \begin{IEEEeqnarray*}{cCc}
      \s\vert_{A''\tensor B'',A'\tensor B'} & \in & \sigma'\tensor\tau' \\
      \s\vert_{A'\tensor B',A\tensor B} & \in & \sigma\tensor\tau
    \end{IEEEeqnarray*}}
    \normalsize
  \end{minipage}}}\right\} \\[1em]
  &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
    \setlength{\abovedisplayskip}{-5pt}
    \setlength{\belowdisplayskip}{-10pt}
    \begin{IEEEeqnarray*}{cCc}
      \s\vert_{A'', A'} & \in & \sigma' \\
      \s\vert_{A', A} & \in & \sigma \\
      \s\vert_{B'', B'} & \in & \tau' \\
      \s\vert_{B', B} & \in & \tau
    \end{IEEEeqnarray*}}
    \normalsize
  \end{minipage}}}\right\} \\[1em]
  &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
    \setlength{\abovedisplayskip}{-5pt}
    \setlength{\belowdisplayskip}{-10pt}
    \begin{IEEEeqnarray*}{cCc}
      \s\vert_{A'', A', A} & \in & \sigma'\|\sigma \\
      \s\vert_{B'', B', B} & \in & \tau'\|\tau
    \end{IEEEeqnarray*}}
    \normalsize
  \end{minipage}}}\right\}
\end{align*}

It follows that
\[
  \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}
  = \left\{\s\vert_{A''\tensor B'', A\tensor B}\suchthat\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)\right\}
  = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
  \]
To define the associators and unitors (which are the obvious choices) for our tensor product, we introduce a bit more technology.  Let $A',A$ be $\alpha$-games.  We call a bijective function $\cmap{f}{P_{A'}}{P_A}$ a \emph{tree isomorphism} if $f$ preserves length and the prefix ordering and commutes with $\zeta_A,\zeta_{A'}$.  If $A,A'$ are completely negative, then we have a strategy $\sigma_f$ for $A'\implies A$ given by
\[
  \sigma_f = \left\{s\in P_{A'\implies A}\suchthat \textrm{for all $P$-positions $t\prefix s$, we have $t\vert_A = f\left(t\vert_{A'}\right)$}\right\}
  \]
We check that $\sigma_f$ is indeed a strategy.  It is clearly prefix-closed and satisfies the limit condition by the definition.  If $s\in\sigma_f$ is a $P$-position, then we must have $sx\in\sigma_f$ for all $sx\in P_{A'\implies A}$.  Now suppose that $sx,sy\in \sigma_f$.  We first claim that $x$ and $y$ take place in the same game.  Indeed, suppose instead that $x$ is a move in $A'$ and $y$ is a move in $A$.  Then we have
\begin{gather*}
  s\vert_A = f\bracketed{s\vert_{A'}x} \\
  s\vert_Ay = f\bracketed{s\vert_{A'}}
\end{gather*}
But this is impossible, since $f$ preserves lengths.  Therefore, $x$ and $y$ take place in the same game.  If they are moves in $A$, we have
\[
  s\vert_A x = f\bracketed{s\vert_{A'}} = s\vert_Ay
  \]
and so $x=y$, and if they are moves in $A'$, we have
\[
  s\vert_{A'}x = f\inv\bracketed{s\vert_A} = s\vert_{A'}y
  \]
and so $x=y$ again.

We call a strategy $\sigma_f$ arising from a tree isomorphism $f$ a \emph{copycat strategy}.  The relational presentation $\grel{\sigma_f}$ of such a strategy $\sigma_f$ is the graph of the function $\cmap{f}{P_{A'}}{P_A}$, and therefore the function $f$ is determined uniquely by the strategy $f$.  Moreover, if we have completely negative $\alpha$-games $A'', A', A$ and tree isomorphisms $A''\xrightarrow{f'}A'\xrightarrow{f}A$, then we must have
\[
  \comp{\sigma_f}{\sigma_{f'}} = \sigma_{\comp{f}{f'}}
  \]
We therefore have a full-on-objects subcategory $\G_{\cc}(\alpha)$ of $\G(\alpha)$ of games and copycat strategies that comes equipped with a natural functor $\cmap{\H}{\G_{\cc}(\alpha)}{\Set}$ that sends a game $A$ to $P_A$ and a copycat strategy $\sigma_f$ to the function $f$.  We get a commutative square in $\CAT$:
\[
  \begin{tikzcd}
    \G_{\cc}(\alpha) \arrow[r, hook] \arrow[d, "\H"']
      & \G(\alpha) \arrow[d, "\F"] \\
    \Set \arrow[r, hook]
      & \Rel
  \end{tikzcd}
  \]
where all the functors in the diagram are faithful.

Given sets $X,Y$ and a function $\cmap{\phi}{X}{Y}$, we write $\overline\phi\from X^{*<\alpha}\to Y^{*<\alpha}$ for the induced map that acts pointwise via $\phi$.  Observe that disjoint union induces the structure of a symmetric monoidal category on $\Set$ with associators, unitors and braiding:
\begin{gather*}
  \assoc_{X,Y,Z}\from (X\cprd Y)\cprd Z\to X\cprd(Y\cprd Z)\\
  \lunit_X\from \emptyset\cprd X\to X\\
  \runit_X\from X\cprd\emptyset\to X\\
  \braid_{X,Y}\from X\cprd Y\to Y\cprd X
\end{gather*}

Suppose $A,B,C$ are completely negative $\alpha$-games.  We have a function
\[
  \assoc_{M_A,M_B,M_C}\from M_{(A\tensor B)\tensor C}\to M_{A\tensor(B\tensor C)}
  \]
and it is clear from the definition that this gives rise to a function
\[
  \overline{\assoc_{M_A,M_B,M_C}}\from P_{(A\tensor B)\tensor C}\to P_{A\tensor(B\tensor C)}
  \]
The tensor unit in our category will be the empty game $I=(\emptyset, \emptyset, \emptyset, \{\emptyplay\})$.  If $A$ is a completely negative $\alpha$-game, we get natural maps
\begin{gather*}
  \lunit_{M_A}\from M_{I\tensor A}\to M_A \\
  \runit_{M_A}\from M_{A\tensor I}\to M_A
\end{gather*}
and these give rise to maps
\begin{gather*}
  \overline{\lunit_{M_A}}\from P_{I\tensor A}\to P_A\\
  \overline{\runit_{M_A}}\from P_{A\tensor I}\to P_A
\end{gather*}
Lastly, we have a map
\[
  \braid_{M_A,M_B}\from M_{A\tensor B}\to M_{B\tensor A}
  \]
inducing a map
\[
  \overline{\braid_{M_A,M_B}}\from P_{A\tensor B}\to P_{B\tensor A}
  \]
It is clear that these maps on sets of plays are all tree isomorphisms, so they give rise to isomorphisms in $\G(\alpha)$:
\begin{gather*}
  \assoc_{A,B,C}\from (A\tensor B)\tensor C\to A\tensor (B\tensor B)\\
  \lunit_A\from I\tensor A\to A\\
  \runit_A\from A\tensor I\to A\\
  \braid_{A,B}\from A\tensor B\to B\tensor A
\end{gather*}
Since the original isomorphisms in $\Set$ satisfy the pentagon, triangle and hexagon identities, and since all the functors we are considering are faithful, our isomorphisms in $\G(\alpha)$ must satisfy the pentagon, triangle and hexagon identities as well.  We give the argument in the case of the pentagon identity.

Given completely negative $\alpha$-games $A,B,C,D$, we have the following commutative diagram in $\Set$:
\[
  \begin{tikzpicture}[commutative diagrams/every diagram]
    \node (P0) at (90:2.3cm) {$M_{(A\tensor B)\tensor(C\tensor D)}$};
    \node (P1) at (90+72:2cm) {$M_{((A\tensor B)\tensor C)\tensor D}$} ;
    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{$M_{(A\tensor(B\tensor C))\tensor D}$}};
    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{$ M_{A\tensor((B\tensor C)\tensor D)} $}};
    \node (P4) at (90+4*72:2cm) {$ M_{A\tensor(B\tensor(C\tensor D))} $};
  \path[commutative diagrams/.cd, every arrow, every label]
    (P1) edge node {$\assoc_{M_{A\tensor B},M_C,M_D}$} (P0)
    (P1) edge node[swap] {$\assoc_{M_A,M_B,M_C}\tensor\id_D$} (P2)
    (P2) edge node[swap, yshift=-1em] {$\assoc_{M_A,M_{B\tensor C},M_D}$} (P3)
    (P3) edge node[swap] {$\id_A\tensor\assoc_{M_B,M_C,M_D}$} (P4)
    (P0) edge node {$\assoc_{M_A,M_B,M_{C\tensor D}}$} (P4);
  \end{tikzpicture}
  \]
which immediately gives rise to a second commutative diagram in $\Set$:
\[
  \begin{tikzpicture}[commutative diagrams/every diagram]
    \node (P0) at (90:2.3cm) {$P_{(A\tensor B)\tensor(C\tensor D)}$};
    \node (P1) at (90+72:2cm) {$P_{((A\tensor B)\tensor C)\tensor D}$} ;
    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{$P_{(A\tensor(B\tensor C))\tensor D}$}};
    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{$ P_{A\tensor((B\tensor C)\tensor D)} $}};
    \node (P4) at (90+4*72:2cm) {$ P_{A\tensor(B\tensor(C\tensor D))} $};
  \path[commutative diagrams/.cd, every arrow, every label]
    (P1) edge node {$\overline{\assoc_{M_{A\tensor B},M_C,M_D}}$} (P0)
    (P1) edge node[swap] {$\overline{\assoc_{M_A,M_B,M_C}\tensor\id_D}$} (P2)
    (P2) edge node[swap, yshift=-1em] {$\overline{\assoc_{M_A,M_{B\tensor C},M_D}}$} (P3)
    (P3) edge node[swap] {$\overline{\id_A\tensor\assoc_{M_B,M_C,M_D}}$} (P4)
    (P0) edge node {$\overline{\assoc_{M_A,M_B,M_{C\tensor D}}}$} (P4);
  \end{tikzpicture}
  \]
But this is the image under the functor $\H$ of the following diagram in $\G_{\cc}(\alpha)$:
\[
  \begin{tikzpicture}[commutative diagrams/every diagram]
    \node (P0) at (90:2.3cm) {${(A\tensor B)\tensor(C\tensor D)}$};
    \node (P1) at (90+72:2cm) {${((A\tensor B)\tensor C)\tensor D}$} ;
    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{${(A\tensor(B\tensor C))\tensor D}$}};
    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{${A\tensor((B\tensor C)\tensor D)} $}};
    \node (P4) at (90+4*72:2cm) {${A\tensor(B\tensor(C\tensor D))} $};
  \path[commutative diagrams/.cd, every arrow, every label]
    (P1) edge node {$\assoc_{{A\tensor B},C,D}$} (P0)
    (P1) edge node[swap] {$\assoc_{A,B,C}\tensor\id_D$} (P2)
    (P2) edge node[swap, yshift=-1em] {$\assoc_{A,{B\tensor C},D}$} (P3)
    (P3) edge node[swap] {$\id_A\tensor\assoc_{B,C,D}$} (P4)
    (P0) edge node {$\assoc_{A,B,{C\tensor D}}$} (P4);
  \end{tikzpicture}
  \]
Since $\H$ is a faithful functor and the second diagram commutes, this last diagram must commute as well.

It remains to show that $\assoc_{A,B,C},\lunit_A,\runit_A,\braid_{A,B}$ are natural transformations.  We show this for $\assoc_{A,B,C}$ and the other cases are entirely similar.

Showing that $\assoc_{A,B,C}$ is a natural transformation from $((\blank\tensor \blank)\tensor \blank)$ to $(\blank\tensor(\blank\tensor \blank)\from \G(\alpha)\times\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ means showing that the following diagram commutes for all completely negative $\alpha$-games $A',B',C',A,B,C$ and all morphisms $\sigma\from A'\to A,\tau\from B'\to B,\upsilon\from C'\to C$:
\[
  \begin{tikzcd}
    (A'\tensor B')\tensor C' \arrow[r, "(\sigma\tensor\tau)\tensor\upsilon"'] \arrow[d, "\assoc_{A', B', C'}"']
      & (A\tensor B)\tensor C \arrow[d, "\assoc_{A,B,C}"] \\
    A'\tensor(B'\tensor C') \arrow[r, "\sigma\tensor(\tau\tensor\upsilon)"']
      & A\tensor(B\tensor C)
  \end{tikzcd}
  \]
It is easy to check that this diagram commutes by applying the functor $\F\colon\G(\alpha)\to\Rel$.  The relational content $\grel{\assoc_{A,B,C}}$ of the strategy $\assoc_{A,B,C}$ is the graph of the function 
\[
  \overline{\assoc_{M_A,M_B,M_C}}\from P_{(A\tensor B)\tensor C}\to P_{A\tensor(B\tensor C)}
  \]
and its action by left composition on $\grel{(\sigma\tensor\tau)\tensor\upsilon}\subset P_{(A'\tensor B')\tensor C'}\times P_{(A\tensor B)\tensor C}$ is pointwise application of this function.  We find that
\begin{align*}
  \grel{\comp{\assoc_{A,B,C}}{(\sigma\tensor\tau)\tensor\upsilon}}
  &=\comp{\grel{\assoc_{A,B,C}}}{\grel{(\sigma\tensor\tau)\tensor\upsilon}}\\
  &=\left\{(s,t)\in P_{(A'\tensor B')\tensor C'}\times P_{A\tensor(B\tensor C)}\;\middle|\;\mbox{\pbox{\textwidth}{$(s\vert_{A'},t\vert_A)\in\grel{\sigma}$\\$(s\vert_{B'},t\vert_B)\in\grel\tau$\\$(s\vert_{C'},t\vert_C)\in\grel\upsilon$}}\right\}
\end{align*}
A similar argument now shows that $\grel{\comp{\sigma\tensor(\tau\tensor\upsilon)}{\assoc_{A', B', C'}}}$ is equal to the same set, and so we have a commutative diagram in $\Rel$:
\[
  \begin{tikzcd}
    P_{(A'\tensor B')\tensor C'} \arrow[r, "\grel{(\sigma\tensor\tau)\tensor\upsilon}"'] \arrow[d, "\grel{\assoc_{A', B', C'}}"']
      & P_{(A\tensor B)\tensor C} \arrow[d, "\grel{\assoc_{A,B,C}}"] \\
    P_{A'\tensor(B'\tensor C')} \arrow[r, "\grel{\sigma\tensor(\tau\tensor\upsilon)}"']
      & P_{A\tensor(B\tensor C)}
  \end{tikzcd}
  \]
Therefore, our original diagram in $\G(\alpha)$ is commutative, since the functor $\F$ is faithful.

We therefore have the structure of a symmetric monoidal category on $\G(\alpha)$.

\subsubsection{Symmetric monoidal closed structure}
\label{TransSMCCSex}

In existing finitary models of game semantics, the category of games is made into a symmetric monoidal closed category where the linear implication of two objects is given by the connective $\implies$.  As we remarked earlier, this approach will not work immediately for us, since $A\implies B$ need not be completely negative even if $A$ and $B$ are.  Our solution will be to modify $A\implies B$ so that it becomes completely negative.

Remember that when we proved that the composition of strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ is well defined, we were careful not to require that $C$ be acn (or completely negative).  From the point of view of constructing a category whose objects are $\alpha$-games, this is not useful, but it does allow us to construct certain alternative categories.

\begin{definition}
  Recall that if $\C$ is a category and $A$ is an object of $\C$, then the \emph{slice category} $\C/A$ is the category where the objects are morphisms
  \[
    \map{f}{B}{A}
    \]
  where $B$ is an object of $\C$ and where the morphisms between an object $\map{f}{B}{A}$ and an object $\map{g}{C}{A}$ are commutative triangles:
  \[
    \begin{tikzcd}
      B \arrow[r, "f"] \arrow[d, "h"']
       & A \\
      C \arrow[ur, "g"]
        &
    \end{tikzcd}
    \]
  Let $A$ be a (not necessarily completely negative) $\alpha$-game.  Abusing notation slightly, we write $\G(\alpha)/A$ for the category whose objects are strategies
  \[
    \sigma\from B\implies A
    \]
  for $B$ a \emph{completely negative} $\alpha$-game and where the morphisms from an object $\map{\sigma}{B}{A}$ to an object $\map{\tau}{C}{A}$ are commutative triangles of the form
  \[
    \begin{tikzcd}
      B \arrow[r, "\sigma"] \arrow[d, "\upsilon"']
       & A \\
      C \arrow[ur, "\tau"]
        &
    \end{tikzcd}
    \]
\end{definition}

The main technical result we shall use to construct our closed monoidal structure is the following theorem:
\begin{theorem}
  \label{SliceTerminalObject}
  Let $A$ be an $\alpha$-game.  Then the category $\G(\alpha)/A$ has a terminal object.
\end{theorem}

Note that if $A$ is completely negative, then the terminal object of $\G(\alpha)/A$ is the identity strategy $\map{\id_A}{A}{A}$, as is standard for slice categories.  If $A$ is not completely negative, then we will need to use a different construction.

We will write this terminal object as $A^{\cn}\xrightarrow{\cn}A$.  $A^{\cn}$ should be thought of as the `smallest completely negative extension of $A$', and the fact that it gives rise to a terminal object in $\G(\alpha)/A$ makes this vague notion precise.  If $A$ and $B$ are completely negative $\alpha$-games, we shall define a game $A\impliescn B$ to be given by $(A\implies B)^{\cn}$.  We will then be able to use the fact that $(A\implies B)^{\cn}$ gives rise to a terminal object in the category $\G(\alpha)/(A\implies B)$ to show that the connective $\impliescn$ in fact gives rise to a monoidal closed structure on $\G(\alpha)$.

\begin{definition}
  Let $A$ be an $\alpha$-game.  We form a completely negative $\alpha$-game $A^{\cn}$ as follows:
  \begin{itemize}
    \item $M_{A^{\cn}}=M_A\cprd \{*_t\suchthat \textrm{$t\in P_A$ is a limiting $O$-play}\}$
    \item $\lambda_{A^{\cn}}(x)=\lambda_A(x)$ for all $x\in M_A$.  $\lambda_{A^{\cn}}(*_s)=O$
    \item $\zeta_{A^{\cn}}(sx)=\lambda_{A^{\cn}}(x)$ for $sx\in P_{A^{\cn}}$ a successor play.
    \item $\zeta_{A^{\cn}}(s)=P$ for $s\in P_{A^{\cn}}$ a limiting play.
  \end{itemize}
  \[
    P_{A^{\cn}} = \left\{s\in \left(M_{A^{\cn}}\right)^{*<\alpha}\;\middle|\;\mbox{\pbox{200px}{
      $t\vert_{M_A}\in P_A$\\
      If $u*_t\prefix s$ then $u=t$. \\
      If $vx\prefix s$ and $v\vert_{M_A}$ is a limiting $O$-play in $P_A$ then $x=*_v$
    }}\right\}
    \]

  In other words, we force $A$ to be completely negative by making all limiting plays be $P$-plays.  If $u$ was a limiting $O$-play in $A$, then it becomes a $P$-play in $A^{\cn}$.  Since the moves that follow $u$ in $A$ are $P$-moves, we add in an extra $O$-move $*_u$ in order to preserve the alternating condition.
\end{definition}

\begin{example}
  If $\alpha=\omega$ and $A$ is a negative game then we have $\bneggame A^{\cn}\cong A\implies\bot$: the single move in $\bot$ takes the role of $*_{\emptyplay}$.  However, if $\alpha$ is a higher ordinal, then this does not hold, since $A\implies\bot$ is no longer a completely negative game.

  If $A,B$ are completely negative $\alpha$-games, we define $A\impliescn B$ to stand for $(A\implies B)^{\cn}$.  Then we do have $\bneggame{A}^{\cn}\cong A\impliescn \bot$.  The object $A\impliescn B$ will be the linear implication in our category.
\end{example}

\begin{notation}
  Given a sequence $s\in P_{A^{\cn}}$, we may restrict $s$ to a play $s\vert_A\in P_A$ by removing all the $*$-moves.  
\end{notation}

Given an $\alpha$-game $A$, there is a natural strategy $\cn_A$ for $A^{\cn}\implies A$ given by
\[
  \cn_A = \left\{s\in P_{A^{\cn}\implies A}\suchthat\textrm{for all $P$-positions $t\prefix s$, $t\vert_{A^{\cn}}\vert_A=t\vert_A$}\right\}
  \]
Concretely, this strategy is the copycat strategy for $A$, with the difference that whenever we reach a limiting $O$-play $u$ in $A$, player $P$ plays the extra move $*_u$ in $A^{\cn}$ before continuing.

We claim that $\map{\cn_A}{A^{\cn}}{A}$ is the terminal object in the category $\G(\alpha)/A$.  To do that, it will suffice to prove the following proposition:

\begin{proposition}
  \label{CnUniversalProperty}
  $\cn_A$ is a total strategy for $A^{\cn}\implies A$.  Moreover, $\cn_A$ satisfies the following universal property: given a completely negative $\alpha$-game $B$ and a strategy $\sigma$ for $B\implies A$, there is a unique strategy $\sigma^{\cn}$ for $B\implies A^{\cn}$ such that the following diagram commutes:
  \[
    \begin{tikzcd}
      B \arrow[r, "\sigma^{\cn}"] \arrow[dr, "\sigma"']
        & A^{\cn} \arrow[d, "\cn_A"] \\
      %
        & A
    \end{tikzcd}
    \]
\end{proposition}

\begin{proof}
  We first show that $\cn_A$ is a valid strategy for $A^{\cn}\implies A$.  It is certainly prefix closed and satisfies the limiting condition by its definition.  Moreover, if $s\in\cn_A$ is a $P$-position and $sx\in P_{A^{\cn}\implies A}$ then $sx$ satisfies the conditions to be an element of $\cn_A$.

  Suppose that $sx, sy\in \cn_A$ are $P$-positions.  Suppose first that neither $x$ nor $y$ is a move of the form $*_t$.  We claim that $sx,sy$ take place in the same game.  Indeed, suppose instead that $x$ is a move in $A^{\cn}$ and $y$ is a move in $A$.  Then we have:
  \begin{gather*}
    s\vert_{A^{\cn}}\vert_A x = sx\vert_{A^{\cn}}\vert_A = sx\vert_A = s\vert_A\\
    s\vert_{A^{\cn}}\vert_A = sy\vert_{A^{\cn}}\vert_A = sy\vert_A = s\vert_Ay
  \end{gather*}
  which is a contradiction since it implies that $s\vert_{A^{\cn}}\vert_A$ is simultaneously a shorter sequence than $s\vert_A$ and a longer sequence than $s\vert_A$.

  If $x,y$ are both moves in $A^{\cn}$ then we have
  \begin{align*}
    s\vert_{A^{\cn}}\vert_A x &= sx\vert_{A^{\cn}}\vert_A \\
    & = sx\vert_A\\
    & = s\vert_A
  \end{align*}
  and $s\vert_{A^{\cn}}\vert_Ay=s\vert_A$ by an identical argument, and so $x=y$.  Similarly, if $x,y$ are both moves in $A$, then we have:
  \begin{align*}
    s\vert_A x &= sx\vert_A \\
    &= sx\vert_{A^{\cn}}\vert_A\\
    &= s\vert_{A^{\cn}}\vert_A
  \end{align*}
  and similarly for $y$, so $x=y$.

  Now, without loss of generality assume that $x=*_t$ for some $t$.  Then $s\vert_{A^{\cn}}\vert_A$ is a limiting play.  Suppose for a contradiction that $y$ is a move in $A$.  Then we have:
  \[
    s\vert_{A^{\cn}}\vert_A = sy\vert_{A^{\cn}}\vert_A=sy\vert_A = s\vert_Ay
    \]
  which is a contradiction, since $s\vert_Ay$ is a successor play.  Therefore, $y$ is a move in $A^{\cn}$.  We have:
  \begin{align*}
    t &= s\vert_{A^{\cn}}\vert_A\\
    &= s*_t\vert_{A^{\cn}}\vert_A\\
    &= s*_t\vert_{A^{\cn}}\vert_A\\
    &= s\vert_{A^{\cn}}\vert_A
  \end{align*}
  Therefore, $s\vert_{A^{\cn}}\vert_A$ is a limiting $O$-play in $A$ and therefore we have $x=y=*_t$ by the definition of $A^{\cn}$.

  Now we show that $\cn_A$ is total.  Suppose that $s\in\cn_A$ is an $O$-position.  Then $s\vert_{A^{\cn}}$ is a $P$-position and $s\vert_A$ is an $O$-position.  Suppose that $s=ty$ is a successor play.  Note that $y$ cannot be a $*$-move, since these are all $O$-moves occurring in $A^{\cn}$.  If $y$ takes place in $A^{\cn}$ then we have $t\vert_{A^{\cn}}\vert_A=t\vert_A$ and therefore player $P$ can play $y$ in $A$ and still be playing according to $\cn$.  Similarly, if $y$ takes place in $A$, then player $P$ can play $y$ in $A^{\cn}$ and be in accordance with $\cn_A$.

  Suppose instead that $s$ is a limiting play.  It is clear from the definition that $s\vert_{A^{\cn}}\vert_A$ and $s\vert_A$ are both cofinal in $s$, so they are both limiting plays.  Therefore, $s\vert_A$ is a limiting $O$-play in $A$ and $s\vert_{A^{\cn}}\vert_A$ must be the corresponding $P$-play in $A^{\cn}$.  Therefore, player $P$ may play $*_t$ (where $t=s\vert_A$) in $A^{\cn}$ and still be in accordance with $A^{\cn}$.  So $\cn_A$ is total.

  Let $q\in P_A$.  We claim that there is some $s\in\cn_A$ such that $s\vert_A=q$.  Indeed, since Player $P$ makes all $*$-moves in $A^{\cn}\implies A$, player $O$ has a strategy for $A^{\cn}\implies A$ in which he plays the moves of the sequence $q$ in order.  Since the strategy $\cn_A$ is total, player $P$ always has a reply to Player $O$'s moves and the resulting sequence $s$ satisfies $s\vert_A=q$.

  Therefore, the relational presentation of $\cn_A$ has the following property: for all sequences $q\in P_A$, there exists some $r\in P_{A^{\cn}}$ such that $(r,q)\in\grel{\cn_A}$.  Moreover, it is not difficult to see that this $r$ is unique, since play passes from $A$ to $A^{\cn}$ without fail at each turn, so a $P$-position in $\cn_A$ is uniquely determined by its sequence of $O$-moves, which must agree with its $A$-component.

  In other words, the relational presentation $\grel{\cn_A}$ is the graph of an injective function $h\colon P_A\to P_{A^{\cn}}$.

  Let $B$ be a completely negative $\alpha$-game and let $\sigma$ be a strategy for $B\implies A$.  We define the strategy $\sigma^{\cn}$ for $B\implies A^{\cn}$ as follows:
  \[
    \sigma^{\cn} = \{s\in P_{B\implies A^{\cn}}\suchthat s\vert_{B,M_A}\in\sigma\}
    \]
  where we write $s\vert_{B,M_A}$ for the sequence obtained by deleting all $*$-moves from $s$.

  $\sigma^{\cn}$ is prefix closed, since $\sigma$ is, and satisfies the limit condition, since $\sigma$ does.  Suppose that $s\in\sigma^{\cn}$ is a $P$-position and that $sx\in P_{B\implies A^{\cn}}$.  If $x$ is a $*$-move, then we have $sx\vert_{B,M_A}=s\vert_{B,M_A}\in\sigma$, so $sx\in\sigma^{\cn}$.  Otherwise, we have $sx\vert_{B,M_A}=s\vert_{B,M_A}x$.

  If $s\vert_{B,M_A}$ is a $P$-position in $B\implies A$ then $s\vert_{B,M_A}x\in\sigma$ and therefore $sx\in\sigma^{\cn}$.  So suppose instead that $s\vert_{B,M_A}$ is an $O$-position.  If $s=ty$ is a successor position then $y$ is a $P$-move in $B\implies A^{\cn}$, so in particular $y$ is not a $*$-move and therefore $s\vert_{B,M_A}=t\vert_{B,M_A}y$ is a $P$-position.  Therefore, $s$ must be a limiting play.

  Since $s$ is a $P$-position, $s\vert_B$ must be a $P$-position, $s\vert_{A^{\cn}}\vert_A$ must be an $O$-position in $A$ and $s\vert_{A^{\cn}}$ must be a $P$-position in $A^{\cn}$.  It follows that $u\coloneqq s\vert_{A^{\cn}}\vert_A$ is a limiting $O$-play.  It follows that $x$ is a move in $A^{\cn}$, and therefore that $x=*_u$, which is a case we have already dealt with.

  Next, suppose that $sx, sy\in\sigma^{\cn}$ are $P$-positions.  In particular, $x,y$ are not $*$-moves and we have $s\vert_{B,M_A}x,s\vert_{B,M_A}y\in\sigma$.  Therefore, $x=y$.  So $\sigma^{\cn}$ is a strategy.

  Lastly, suppose that $\sigma$ is a total strategy.  Let $s\in\sigma^{\cn}$ be an $O$-position in $B\implies A^{\cn}$.  Then $s\vert_B$ is a $P$-position in $B$ and $s\vert_{A^{\cn}}$ is an $O$-position in $A^{\cn}$.  So $s\vert_{A^{\cn}}$ is a successor play in $A^{\cn}$, since $A^{\cn}$ is completely negative.  If the last move of $s\vert_{A^{\cn}}$ is not a $*$-move then $s\vert_{A^{\cn}}\vert_A$ has the same last move as $s\vert_{A^{\cn}}$ and is therefore an $O$-position as well.  Then $s\vert_{B,M_A}$ is an $O$-position and so there is some $x\in P_{B\implies A}$ such that $s\vert_{B,M_A}x\in\sigma$. Then $sx\in P_{B\implies A^{\cn}}$ and so $sx\in\sigma^{\cn}$.

  Suppose instead that $s\vert_{A^{\cn}}=t*_u$, where $u=t\vert_A$.  Then $u$ is an $O$-position in $A$, so $s\vert_{B,M_A}$ is an $O$-position in $B\implies A$ and therefore there is some $x\in P_{B\implies A}$ such that $s\vert_{B,M_A}x\in\sigma$.  Then $sx\in\sigma^{\cn}$.  So $\sigma^{\cn}$ is a total strategy.

  We claim that $\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}=\grel\sigma$.  Then we will have $\comp{\cn_A}{\sigma^{\cn}}=\sigma$ by Lemma \ref{TransHylandSchalkFaithful} and Corollary \ref{TransHylandSchalkIsFunctor}.  Suppose $(s,t)\in\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}$.  Then there is some $u\in P_{A^{\cn}}$ such that $(s,u)\in\grel{\sigma^{\cn}}$ and $(u,t)\in\grel{\cn_A}$.  Therefore, $(s,u\vert_A)\in\grel\sigma$ and $t=u\vert_A$.  It follows that $(s,t)\in\grel{\sigma}$, so $\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}\subset\grel\sigma$.

  To show the reverse inclusion, we shall use the following lemma, which we shall prove later.

  \begin{lemma}
    \label{CnLiftingLemma}
    Let $B$ be a completely negative $\alpha$-game, let $A$ be an arbitrary $\alpha$-game and let $\sigma$ be a strategy for $B\implies A$.  Let $s\in\sigma$ be a $P$-position.  Then there is a unique $P$-position $t\in B\implies A^{\cn}$ such that $t\vert_{B,M_A}=s$.
  \end{lemma}

  We use Lemma \ref{CnLiftingLemma} to show the reverse inclusion as follows: let $s\in\sigma$ be a $P$-position -- so $(s\vert_B,s\vert_A)$ is an arbitrary element of $\grel\sigma$.  By Lemma \ref{CnLiftingLemma} there exists $t\in B\implies A^{\cn}$ such that $t\vert_{B,M_A}=s$.  In particular, $t\vert_{A^{\cn}}\vert_A=s\vert_A$ and $t\vert_B=s\vert_B$.  So we have $(s\vert_B,t\vert_{A^{\cn}})\in\grel{\sigma^{\cn}}$ and $(t\vert_{A^{\cn}},s\vert_A)\in\grel{\cn_A}$.  It follows that $(s\vert_B,s\vert_A)\in\grel{\sigma}$.  So $\grel\sigma\subset\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}$.

  Lastly, we need to show that the strategy $\sigma^{\cn}$ is unique.  Suppose that there were some other strategy $\tau$ for $B\implies A^{\cn}$ making the diagram commute:
  \[
    \begin{tikzcd}
      B \arrow[r, "\tau"] \arrow[dr, "\sigma"']
        & A^{\cn} \arrow[d, "\cn_A"] \\
      %
        & A
    \end{tikzcd}
    \]
  We shall show that $\grel\tau=\grel{\sigma^{\cn}}$ -- so $\tau=\sigma^{\cn}$.  First suppose that $s\in\sigma^{\cn}$ is a $P$-position.  Since $\sigma = \comp{\cn_A}{\tau}$, there is some sequence $\s\in\tau\|\cn_A$ such that $\s\vert_{B,A}=s\vert_{B,M_A}$.  We have $\s\vert_{A^{\cn}}\vert_A=\s\vert_A$ and therefore $s\vert_{B,M_A}=\s\vert_{B,A^{\cn}}\vert_{B,M_A}$.  Therefore, $s=\s\vert_{B,A^{\cn}}\in\tau$, by uniqueness in Lemma \ref{CnLiftingLemma}.  So $\grel{\sigma^{\cn}}\subset\grel{\tau}$.

  Conversely, suppose that $s\in\tau$ is a $P$-position.  Then our argument above tells us that we have $(s\vert_{A^{\cn}},s\vert_{A^{\cn}}\vert_A)\in\grel{\cn_A}$.  So $(s\vert_B,s\vert_{A^{\cn}}\vert_A)\in\grel\sigma$.  Therefore there is some $P$-position $u\in\sigma$ such that $u\vert_B=s\vert_B$ and $u\vert_A=s\vert_{A^{\cn}}\vert_A$.  By Lemma \ref{CnLiftingLemma}, there is a sequence $t\in\sigma^{\cn}$ with $t\vert_{B,M_A}=s$.  Then we have
  \[
    (s\vert_B,s\vert_{A^{\cn}})=(t\vert_B,t\vert_{A^{\cn}})\in\grel{\sigma^{\cn}}
    \]
  and therefore $\grel\tau\subset\grel{\sigma^{\cn}}$.  
\end{proof}

It remains to prove Lemma \ref{CnLiftingLemma}.

\begin{proof}[Proof of Lemma \ref{CnLiftingLemma}]
  This proof is similar to the proof of \ref{TransLiftingLemma}.  We inductively construct a sequence $t^0\prefix t^1\prefix\dots\prefix t^\gamma\prefix\dots\prefix t^\beta$, where $t^\gamma$ has length $\gamma$ and $t^\beta$ is our desired sequence $t$.  We shall prove inductively that $t^\gamma$ is the unique element $u\in\sigma^{\cn}$ of length $\gamma$ such that $u\vert_{B,M_A}=t$.

  If $\gamma$ is a limit ordinal, then set $t^\gamma$ to be the limit of all the sequences $t^\delta$ for $\delta<\gamma$.  We have $r\vert_{B,M_A}\prefix s$ for all proper prefixes $r\pprefix t^{\gamma}$ and therefore $t^\gamma\vert_{B,M_A}\prefix s$.  For uniqueness, suppose that $u^\gamma$ has length $\gamma$ and $u^\gamma\vert_{B,M_A}\prefix s$.  If $\delta<\gamma$ and we write $u^\delta$ for the prefix of $u^\gamma$ of length $\delta$ then we have $u^\delta=t^\delta$ by uniqueness and it follows that $u^\gamma=t^\gamma$.

  Suppose instead that $\gamma=\delta+1$ is a successor ordinal.  We have a sequence $t^\delta$ of length $\delta$.

  Suppose first that $t^\delta$ is an $O$-position.  Then, as usual, $t^\delta\vert_{B,M_A}$ is an $O$-position.  We have $t^\delta\vert_{B,M_A}\prefix s$; since $s$ is a $P$-position, this must be a proper prefix, so there is some move $x$ such that $t^\delta\vert_{B,M_A}x\prefix s$.  By the argument above (showing that $\sigma^{\cn}$ is total if $\sigma$ is total), we must have $t^\delta x\in\sigma$.  We set $t^{\delta+1}=t^\delta x$.  Then $t^{\delta+1}\vert_{B,M_A}\prefix s$.

  For uniqueness, suppose that $u^{\delta+1}$ is some other sequence of length $\delta+1$ with $u^{\delta+1}\vert_{B,M_A}\prefix s$.  Writing $u^{\delta+1}=u^\delta y$, we have $u^{\delta}=t^\delta$ by uniqueness for sequences of length $\delta$.  Then $t^\delta x,t^\delta y\in\sigma$ and so $x=y$.  So $u^{\delta+1}=t^{\delta+1}$.

  Now suppose that $t^\delta$ is a $P$-position.  We have $t^\delta\vert_{B,M_A}\prefix s$.  If $t^\delta\vert_{B,M_A}=s$ then we terminate, setting $\beta=\delta$.  Otherwise, there is some move $x$ such that $t^\delta\vert_{B,M_A}x\prefix s$.

  Suppose that $t^\delta\vert_{B,M_A}$ is a $P$-position.  Then $x$ is an $O$-move, so $t^\delta x$ is alternating.  \textbf{Since $B$ is completely negative}, Proposition \ref{NiceAcnGames} tells us that $t^\delta x\in P_{B\implies A^{\cn}}$.  Therefore, $t^\delta x\in\sigma^{\cn}$, since $\sigma^{\cn}$ is a strategy.  We set $t^{\delta+1}=t^\delta x$.  Then we certainly have $t^{\delta+1}\vert_{B,M_A}\prefix s$.  For uniqueness, suppose that $u^{\delta+1}$ has length $\delta+1$ and that $u^{\delta+1}\vert_{B,M_A}\prefix s$.  Then $u^{\delta+1}=t^\delta y$ for some $y$ by uniqueness for sequences of length $\delta$.  Since $t^\delta\vert_{B,M_A}$ is a $P$-position, it is in particular not a limiting $O$-play, so $y$ cannot be a $*$-move.  Therefore, we have $u^{\delta}\vert_{B,M_A}y\prefix s$ and so $x=y$.

  Suppose instead that $t^\delta\vert_{B,M_A}$ is an $O$-position.  Then $v\coloneqq t^\delta\vert_{A^{\cn}}\vert_A$ must be a limiting $O$-play.  We set $t^{\delta+1}=t^\delta *_v$.  Since $*_v$ is the only move possible in position $t^\delta$, this must certainly be unique, and we have $t^\delta *_v\vert_{B,M_A}=t^\delta\vert_{B,M_A}\prefix s$.

  This completes the proof by induction.
\end{proof}

\subsubsection{A digression}
\label{DigressionSex}

Earlier on, we defined a category $\G(\alpha)/A$ for $A$ an arbitrary $\alpha$-game.  At this point, it is tempting to define a category as follows:

\begin{definition}
  The objects of the category $\tilde{\G}(\alpha)$ are (not necessarily completely negative) $\alpha$-games.  If $A,B$ are $\alpha$-games, a morphism in $\tilde{\G}(\alpha)$ from $A$ to $B$ is a functor
  \[
    \F\from\G(\alpha)/A\to\G(\alpha)/B
    \]
  that commutes with the natural projection functors $p_A\from\G(\alpha)/A\to\G(\alpha)$ and $p_B\from\G(\alpha)/B\to\G(\alpha)$.  
\end{definition}

This definition is useful because we have a natural embedding (the $2$-Yoneda embedding) of $\G(\alpha)$ into the category $\tilde{\G}(\alpha)$ that sends a completely negative game $N$ to the category $\G/N$ and sends a morphism $\sigma\from M\implies N$ to the `post-composition with $\sigma$' functor between the slice categories $\G(\alpha)//M$ and $\G(\alpha)/N$.

It is well known that this is a fully faithful embedding.  I claim that it is also essentially surjective, so it is in fact an equivalence of categories.  Indeed, this follows from what we have just shown:

\begin{proposition}
  Let $A$ be an arbitrary $\alpha$ game.  Then the categories $\G(\alpha)/A$ and $\G(\alpha)/A^{\cn}$ are isomorphic as categories, via an isomorphism that commutes with the projection functors.

  \begin{proof}
    We have a natural functor from $\G(\alpha)/A^{\cn}$ to $\G(\alpha)/A$ given by post-composition with $\cn_A$, where functoriality follows from associativity of composition.  This functor certainly commutes with the projection functors.  Then Proposition \ref{CnUniversalProperty} tells us that it is fully faithful and a bijection on objects, so it is a categorical isomorphism.
  \end{proof}
\end{proposition}

Therefore, the categories $\G(\alpha)$ and $\tilde{\G}(\alpha)$ are equivalent.  This suggests one strategy for defining a symmetric monoidal closed structure on $\G(\alpha)$: since the objects of $\tilde{\G}(\alpha)$ are not required to be completely negative, we may freely define a closed monoidal structure on $\tilde{\G}(\alpha)$ by setting the linear implication between games $A$ and $B$ to be the game $A\implies B$ and the tensor product to be the game $A\tensor B$.  This symmetric monoidal closed structure will give rise to a symmetric monoidal closed structure on $\G(\alpha)$ via the equivalence of categories.

However, there is still quite a lot of work to show that this does indeed give a symmetric monoidal closed structure on $\tilde{\G}(\alpha)$, and it will be easier to construct the closed structure on $\G(\alpha)$ directly.

\subsubsection{The completely negative linear implication $A\impliescn B$}
\label{ImpliesCnSex}

Let $A,B$ be completely negative $\alpha$-games.  We have a completely negative $\alpha$-game $A\impliescn B\coloneqq (A\implies B)^{\cn}$.  We shall construct a monoidal closed structure on $\G(\alpha)$ where the linear implication between $A$ and $B$ is $A\impliescn B$.

We shall start off with the relevant result about the (usual) implication $A\implies B$:

\begin{proposition}
  \label{impliesTreeIsom}
  Let $A,B,C$ be completely negative $\alpha$ games.  Then the games $(A\tensor B)\implies C$ and $A\implies(B\implies C)$ are tree isomorphic.
\end{proposition}

\begin{note}
  Since $(A\tensor B)\implies C$ is not a completely negative game in general, we cannot say that these games are isomorphic as objects of $\G(\alpha)$, but it will help us to know that they are tree-isomorphic as games.
\end{note}

\begin{proof}[Proof of Proposition \ref{impliesTreeIsom}]
  The sets of plays $P_{(A\tensor B)\implies C}$ and $P_{A\implies(B\implies C)}$ are both appropriate subsets of $P_A\|P_B\|P_C$.  We just need to check that $\lambda_{(A\tensor B)\implies C}=\lambda_{A\implies(B\implies C)}$ and that $\zeta_{(A\tensor B)\implies C}=\zeta_{A\implies(B\implies C)}$.

  We have
  \begin{align*}
    \lambda_{(A\tensor B)\implies C} &= \neg\circ\lambda_{A\tensor B}\cprd\lambda_C\\
    &= \neg\circ\lambda_A\cprd\neg\circ\lambda_B\cprd\lambda_C\\
    &= \neg\circ\lambda_A\cprd\lambda_{B\implies C}\\
    &= \lambda_{A\implies(B\implies C)}
  \end{align*}
  and
  \begin{align*}
    \zeta_{(A\tensor B)\implies C}(s) & = ((\zeta_A(s\vert_A)\wedge\zeta_B(s\vert_B))\Rightarrow\zeta_C(s\vert_C))\\
    &=(\zeta_A(s\vert_A)\Rightarrow(\zeta_B(s\vert_B)\Rightarrow\zeta_C(s\vert_C))) \\
    &=\zeta_{A\implies(B\implies C)}(s)
  \end{align*}
  where we can prove the second equality as follows: if $p,q,r\in\OP$, then $((p\wedge q)\Rightarrow r) = O$ if and only if $p=q=P$ and $r=O$.  Meanwhile, $(p\Rightarrow (q\Rightarrow r))=O$ if and only if $p=q=P$ and $r=O$.  So $((p\wedge q)\Rightarrow r) = (p\Rightarrow(q\Rightarrow r))$.
\end{proof}

To construct the monoidal closed structure, it suffices to give a morphism
\[
  \ev_{A,B}\from (A\impliescn B)\tensor A\to B
  \]
for all pairs $(A,B)$ of completely negative $\alpha$-games, such that for all completely negative $\alpha$-games $X$ and all morphisms $\sigma\from X\tensor A\to B$ there is a unique morphism $\upsilon\from X\to A\impliescn B$ making the following diagram commute:
\[
  \begin{tikzcd}
    X\tensor A_3 \arrow[r, "\sigma"] \arrow[d, "\upsilon\tensor\id_A"']
      & B_2 \\
    (A_1\impliescn B_1)\tensor A_2 \arrow[ur, "\ev_{A,B}"']
      &
  \end{tikzcd}
  \]
(Here we have numbered the copies of $A$ and $B$ so we can refer to them individually).

The strategy $\ev_{A,B}$ for $((A\impliescn B)\tensor A)\implies B$ is constructed as follows: we have our strategy $\cn_{A\implies B}$ for $(A\impliescn B)\implies(A\implies B)$.  By Proposition \ref{impliesTreeIsom}, this game is tree isomorphic to the game $((A\impliescn B)\tensor A)\implies B$, so we get the strategy $\ev_{A,B}$ by applying this tree isomorphism to the strategy $\cn_{A\implies B}$.

We need to show that the strategy $\ev_{A,B}$ satisfies the property given above.  Let $X$ be a completely negative $\alpha$-game and let $\sigma$ be a strategy for $(X\tensor A)\implies B$.  Then $\sigma$ gives rise, via the tree isomorphism above, to a strategy $\tilde{\sigma}$ for $X\implies(A\implies B)$.  Since the tree isomorphism does nothing more than identify $P_{(X\tensor A)\implies B}$ with $P_{X\implies(A\implies B)}$ as subsets of $(M_X\cprd M_B\cprd M_C)^{*<\alpha}$, we may identify $\sigma$ and $\tilde{\sigma}$ as subsets of $(M_X\cprd M_A\cprd M_B)$.

Similarly, we may identify $\ev_{A,B}$ with $\cn_{A\implies B}$ as subsets of 
\[
  \left(M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}
  \]
where we have again labelled the different copies of $A$ and $B$ to avoid confusion.

The strategy $\tilde{\sigma}$ gives rise to a strategy ${\tilde{\sigma}}^{\cn}$ for $X\implies(A\impliescn B)$.  We claim that this ${\tilde{\sigma}}^{\cn}$ satisfies the property above.

First, we show that $\comp{\ev_{A,B}}{({\tilde{\sigma}}^{\cn}\tensor\id_A)}=\sigma$.  By the definition of ${\tilde{\sigma}}^{\cn}$, we know that it makes the following diagram commute:
\[
  \begin{tikzcd}
    X \arrow[r, "{\tilde{\sigma}}^{\cn}"] \arrow[dr, "\tilde\sigma"']
      & A_1\impliescn B_1 \arrow[d, "\cn_{A\implies B}"] \\
    %
      & A_2\implies B_2
  \end{tikzcd}
  \]
where we have labelled the copies of $A$ and $B$ so we can tell them apart.  Therefore, we have
\[
  \tilde\sigma = \{\s\vert_{X,A_2,B_2}\suchthat \s\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}\}
  \]
where
\[
  {\tilde\sigma}^{\cn}\|\cn_{A\implies B} = \left\{\s\in \left(M_X\cprd M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}\;\middle|\;\mbox{\pbox{\textwidth}{
    $\s\vert_{X,A_1,B_1}\in{\tilde\sigma}^{\cn}$\\
    $\s\vert_{A_1,B_1,A_2,B_2}\in\cn_{A\implies B}$
  }}\right\}
  \]
Now we have
\[
  \comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}=
  \left\{\t\vert_{X,A_2,B_2}\suchthat\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}\right\}
  \]
where
\[
  \left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}
  =\left\{\t\in\left(M_X\cprd M_{A_3}\cprd M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}\;\middle|\;
  \mbox{\pbox{\textwidth}{
    $\t\vert_{X,A_1,B_1}\in{\tilde\sigma}^{\cn}$\\
    $\t\vert_{A_3,A_2}\in\id_A$\\
    $\t\vert_{A_2,B_2}\in\ev_{A,B}$
  }}\right\}
  \]
Remembering that we may identify $\ev_{A,B}$ with $\cn_{A\implies B}$ as sets of plays, we see that
\[
  \comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}\subset\tilde\sigma=\sigma
  \]
since if $\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}$ then we have $\t\vert_{X,A_1,B_1,A_2,B_2}\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}$ and so $\t\vert_{X,A_2,B_2}\in\tilde\sigma$.

Conversely, let $s\in\tilde\sigma$ and write $s=\s\vert_{X,A_2,B_2}$, where $\s\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}$.  We may construct a sequence $\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}$ with $\t\vert_{X,A_1,B_1,A_2,B_2}=\s$ by inserting before each $P$-move in $A_2$ the corresponding move in $A_3$ and inserting \emph{after} each $O$-move in $A_2$ the corresponding move in $A_3$.  Therefore:
\[
  \sigma\subset\comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}
  \]
For uniqueness, suppose that we have a strategy $\upsilon$ for $X\implies(A\impliescn B)$ making the following diagram commute:
\[
  \begin{tikzcd}
    X\tensor A_3 \arrow[r, "\sigma"] \arrow[d, "\upsilon\tensor\id_A"']
      & B_2 \\
    (A_1\impliescn B_1)\tensor A_2 \arrow[ur, "\ev_{A,B}"']
      &
  \end{tikzcd}
  \]
Exactly the same argument then tells us that
\[
  \comp{\cn_{A\implies B}}{\upsilon}=\comp{\ev_{A,B}}{\upsilon\tensor\id_A}=\sigma=\tilde\sigma
  \]
(as sets of plays) and so $\upsilon={\tilde\sigma}^{\cn}$ by the uniqueness part of Proposition \ref{CnUniversalProperty}.

Therefore $\G(\alpha)$ has the structure of a symmetric monoidal category with tensor product given by $\tensor$ and linear implication given by $\impliescn$.

\subsubsection{Win-games and winning strategies}

We shall not develop the theory of transfinite win-games in this report, leaving this work for future research.  The basic idea is as follows.  Let $\alpha$ be an ordinal of the form $\omega^\beta$.  We form a category $\G(\alpha+1)$ of games where the objects are acn $\alpha+1$-games.

Given an acn $\alpha+1$-game $A$, we have an associated $\alpha$-game $A^\circ$ given by forgetting about the plays of length $\alpha$.  We call a total strategy $\sigma$ for $A^\circ$ \emph{winning} if every play of length $\alpha$ that is the limit of plays from $\sigma$ is a $P$-play in $A$.

We can then show that winning strategies compose to give winning strategies, just as in the $\omega+1$-case.  The morphisms between objects $A$ and $B$ in our category will be winning strategies for $A^\circ\implies B^\circ$.  We can then show that this category inherits a closed monoidal structure from $\G(\alpha)$.

This construction agrees with the previous one in the sense that $\G(\omega+1)$ and our original category $\mathcal W$ of win-games are isomorphic as categories.

\section{Exponentials}

We want to model the exponential connective $\oc$ from linear logic in our game semantics.  We adapt the approach taken in \cite{laird02} and \cite{martinsthesis} to our transfinite games.

\begin{definition}
  Let $\G(\alpha)$ be a category of transfinite games and let $A$ be an object of $\G(\alpha)$.  Then the \emph{exponential} $\oc A$ is given as follows:
  \begin{itemize}
    \item $M_{\oc A} = A\times\omega$
    \item $\lambda_{\oc A} = \lambda_A\circ\pr_1$
  \end{itemize}

  Given an ordinal-indexed sequence $s$ taking values in $M_{\oc A}$ and some $n\in\omega$, we write $s\vert_n$ for the subsequence of $s$ consisting of terms of the form $(a,n)$.  Then define
  \[
    \oc P_A = \{s\in M_{\oc A}^{*<\alpha}\suchthat s\vert_n\in P_A\textrm{ for all }n\in \omega\}
    \]
  We define $\zeta_{\oc A}\from \oc P_A\to \OP$ by
  \[
    \zeta_{\oc A}(s) = \bigwedge_{n\in \omega} \zeta_A(s\vert_n)
    \]
  (Here, if $(b_n)\in\OP^\omega$ then we have $\bigwedge_{n\in\omega} b_n = P$ if $b_n=P$ for all $n$ and $\bigwedge_{n\in\omega}=O$ otherwise.)

  We define $P_{\oc A}$ to be the set of all sequences $s\in\oc P_A$ that are well formed with respect to $\zeta_{\oc A},\lambda_{\oc A}$ and are alternating with respect to $\zeta_{\oc A}$ and that satisfy the following property:

  \begin{itemize}
    \item If the term $(a,n)$ occurs in $s$, and if $m<n$, then there is some term $(b,m)$ that occurs earlier in the sequence $s$ than $(a,n)$.  
  \end{itemize}

  Then $\oc A=(M_{\oc A},\lambda_{\oc A},\zeta_{\oc A},P_{\oc A})$.  
\end{definition}

So $\oc A$ is like an infinite tensor product of copies of $A$ with the restriction that the first move must take place in the first copy and that moves may not take place in a subsequent copy of $A$ until moves have been made in all earlier copies.

\begin{proposition}
  $\oc A$ is a well formed game.
  \begin{proof}
    Exactly the same argument from Proposition \ref{TransTensorWellFormed}.
  \end{proof}
\end{proposition}

Just like the tensor product, the exponential $\oc A$ has the property that only player $O$ may switch games:

\begin{proposition}
  \label{ExponentialWhoSwitchesGames}
  Suppose that $s(a,m)(b,n)\in P_{\oc A}$, where $m\ne n$.  Then $\lambda_{\oc A}(b,n)=O$.  
  \begin{proof}
    $\begin{aligned}[t]
      \lambda_{\oc A}(b,n) &= \zeta_{\oc A}(s(a,m)(b,n))\\
      &= \bigwedge_{k\in\omega}\zeta_A(s(a,m)(b,n)\vert_k)
    \end{aligned}$

    Now by alternation we must have either $\zeta_A(s\vert_m(a,m))=O$ or $\zeta_A(s\vert_n(b,n))=O$.  So this last expression must be equal to $O$.
  \end{proof}
\end{proposition}

We can also prove a version of Proposition \ref{NiceAcnGames} for the exponential connective using the same argument.

To demonstrate why it is important to restrict the order in which the opponent $O$ may open games, we define a commutative comonoid structure on $\oc A$.  The comultiplication $\mu\from \oc A\to \oc A\tensor \oc A$ is the copycat strategy that opens a new copy of $A$ on the left hand side whenever a new copy of $A$ is opened on the right hand side.  (Here we see why the condition on the order in which games may be opened is important -- if we had no such restriction then there would be no canonical way to choose which copy of $A$ to open on the left hand side and the comultiplication would not be associative.)

The counit $\eta\from \oc A\to I$ is the unique empty strategy on $\oc A\implies I$.

For associativity of comultiplication, we want to check that the following diagram commutes:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\mu"] \arrow[dd, "\mu"']
      & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \mu"] \\
    %
      & \oc A \tensor (\oc A \tensor \oc A) \arrow[d, "\assoc_{A,A,A}\inv"] \\
    \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}"']
      & (\oc A \tensor \oc A) \tensor \oc A
  \end{tikzcd}
  \]
For this, note that each path round the diagram is a copycat strategy $\oc A \to (\oc A\tensor \oc A)\tensor \oc A$.  Since we are forced to open copies of $\oc A$ in order, there is only one such copycat strategy, and so the two paths must be equal.

Exactly the same argument tells us that comultiplication is commutative and that the counit is indeed a counit for this comultiplication.

We have a natural forgetful functor from the category of comonoids over $\G(\alpha)$ to $\G(\alpha)$ itself.  We first want to show that we have a functor in the opposite direction that sends a game $A$ to this comonoid over $\oc A$.

Let $A,B$ be completely negative $\alpha$-games and let $\sigma$ be a strategy for $A\implies B$.  Then we have a natural strategy $\oc \sigma$ for $\oc A\implies\oc B$ given by
\[
  \oc\sigma = \{s\in P_{\oc A}\suchthat s\vert_n\in\sigma\textrm{ for all $n\in\omega$}\}
  \]
where we have written $s\vert_n$ for the subsequence of $s$ consisting of all terms that occur in the $n$-th copy of $A$ or the $n$-th copy of $B$.

The proof that this is a strategy may be adapted from the discussion of the strategy $\sigma\tensor\tau$ above.  Similarly, we may show that if $A,B,C$ are completely negative $\alpha$-games and we have strategies $A\xrightarrow{\sigma}B\xrightarrow{\tau}C$ then
\[
  \comp{\oc\tau}{\oc\sigma} = \oc(\comp\tau\sigma)
  \]
using the same argument we used to show that taking the tensor product of two strategies preserves composition.

This gives us a functor $\cmap{\oc}{\G(\alpha)}{\G(\alpha)}$.  We want to show that it gives rise to a functor from $\G(\alpha)$ into the category of comonoids over $\G(\alpha)$ sending a game $A$ to the comonoid $\oc A\to \oc A\tensor \oc A$.  For this, we need to show that if $A,B$ are completely negative $\alpha$-games and $\sigma$ is a strategy for $A\implies B$ then the following diagram commutes:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\mu"] \arrow[d, "\oc \sigma"']
      & \oc A \tensor \oc A \arrow[d, "\oc \sigma \tensor \oc \sigma"] \\
    \oc B \arrow[r, "\mu"']
      & \oc B \tensor \oc B
  \end{tikzcd}
  \]
Each branch of this diagram is a strategy for $\oc A\implies(\oc B\tensor\oc B)$ in which player $P$ plays according to $\sigma$, opening a new copy of $A$ on the left each time player $O$ opens a copy of $B$ on the right.  Since the order in which player $P$ may open copies of $A$ is pre-determined, there is a unique such strategy, and so this diagram must commute.

We shall eventually show that in fact $\oc A\to\oc A\tensor\oc A$ is the \emph{cofree commutative comonoid} on $A$.  To show that, we will need \cite{martinsthesis} to give a map $\der\from\oc A\to A$, and we will need to show that for each commutative comonoid $B\to B\tensor B$ and each morphism $\sigma\from B\to A$ there exists a unique morphism $\sigma^\dagger\from B\to \oc A$ such that the following diagram commutes:
\[
  \begin{tikzcd}
    A
      & \oc A \arrow[l, "\der"'] \arrow[r, "\mu"]
        & \oc A \tensor \oc A \\
    %
      & B \arrow[r] \arrow[u, dotted, "\sigma^\dagger"'] \arrow[ul, "\sigma"]
        & B\tensor B \arrow[u, dotted, "\sigma^\dagger \tensor \sigma^\dagger"']
  \end{tikzcd}
  \]
We are not yet in a position to define the morphism $\sigma^\dagger$, but it is easy to see what $\der$ is: it is the copycat strategy on $\oc A\implies\oc A$ that copies the moves from $A$ on the right into the first copy of $A$ on the left.

\subsection{Products in $\G(\alpha)$}

Let $(A_i\suchthat i\in I)$ be a collection of objects of $\G(\alpha)$.  We define the product
\[
  \prod_i A_i
  \]
to be the game given by
\begin{itemize}
  \item $M_{\prod_i A_i}=\bigcprd_i M_{A_i}$
  \item $\lambda_{\prod_i A_i}=\bigcprd_i \lambda_{A_i}$
  \item $P_{\prod_i A_i} = \bigcprd_i P_{A_i}$
  \item $\zeta_{\prod_i A_i} = \bigcprd_i \zeta_{A_i}$
\end{itemize}
This is the game where Player $O$ may decide which of the $A_i$ to play his first move in; play then continues in that game and the other games are never used.

We claim that $\prod_i A_i$ is the categorical product of the $A_i$ in $\G(\alpha)$.  First note that we have natural projection strategies $\pr_j$ for $\prod_i A_i\to A_j$ for each $j\in I$, in which player $P$ plays copycat in game $A_j$ on the left.  Now if $B$ is an object of $\G(\alpha)$ and $\sigma_i$ are strategies for $B\implies A_i$ for each $i\in I$, then we have a strategy $\sigma$ for $B\implies\prod_i A_i$ in which player $P$ uses strategy $j$ when player $O$'s initial move takes place in $A_j$:
\[
  \sigma = \bigcprd_i \sigma_i
  \]

We can see that $\comp{\pr_j}{\sigma}=\sigma_j$ for each $j$: indeed, $\grel{\pr_j}$ is the graph of the inclusion $P_{A_j}\hookrightarrow P_{\prod_i A_i}$, while $\grel\sigma$ is the union of the relations $\grel{\sigma_i}$, so this equation holds in the relational presentation:
\[
  \comp{\grel{\pr_j}}{\grel{\sigma}}=\grel{\sigma_j}
  \]
Moreover, it is easy to see that $\grel\sigma$ is the unique relation between $P_B$ and $P_{\prod_i A_i}$ such that this equation holds for all $j$, and therefore $sigma$ is the unique strategy for $B\implies\prod_i A_i$ such that $\comp{\pr_j}{\sigma}=\sigma_j$ for each $j\in I$.  Therefore, $\G(\alpha)$ has all small products.

Given games $A,B$, we shall write $A\times B$ for the product of $A$ and $B$.

\subsection{The exponential as a final coalgebra}

Our definition of the exponential connective $\oc$ was different from the definitions of the other connectives in that it involved an explicit restriction on the order in which new games could be opened.  We saw that this restriction was necessary in order to guarantee associativity of the comultiplication in our comonoid, but it means that it is hard to study the exponential $\oc A$ using the connectives $\tensor$ and $\implies$.

Let $A,B$ be objects of some category $\G(\alpha)$ of transfinite games.  Following \cite{laird02}, we define the \emph{sequoid} $A\sequoid B$ by:

\begin{itemize}
  \item $M_{A\sequoid B} = M_{A\tensor B}$
  \item $\lambda_{A\sequoid B}=\lambda_{A\tensor B}$
  \item $P_{A\sequoid B} = \{s\in P_{A\tensor B}\suchthat\textrm{$s=\emptyplay$ or the first move of $s$ takes place in $A$}\}$
  \item $\zeta_{A\sequoid B} = \zeta_{A\tensor B}\vert_{P_{A\sequoid B}}$
\end{itemize}

It is clear that $A\sequoid B$ is a well-formed game - namely, it is the weakening of the tensor product $A\tensor A$ such that player $O$ is forced to start play in the game $A$.  We have a natural copycat strategy $\wk\from A\tensor B\to A\sequoid B$ and the morphism
\[
  \dec_{A,B}\from A\tensor B\to (A\sequoid B)\times(B\sequoid A)
  \]
induced by the morphisms
\[
  A\tensor B\xrightarrow{\wk}A\sequoid B\quad A\tensor B\xrightarrow{\braid}B\tensor A\xrightarrow{\wk}B\sequoid A
  \]
is an isomorphism.

Other natural copycat isomorphisms may be verified by inspection:
\begin{gather*}
  \passoc_{A,B,C} \from (A\sequoid B) \sequoid C \toisom A\sequoid (B\tensor C) \\
  \pcomm_{A,B,C} = \comp{\passoc_{A,B,C}\inv}{\comp{(\id_A\tensor\braid)}{\passoc_{A,B,C}}} \from (A\sequoid B)\sequoid C \toisom (A\sequoid C)\sequoid B\\
  \lun_A \from I\sequoid A \toisom I\\
  \run_A \from A\sequoid I \toisom A \\
  \dist_{A,B,C}=\langle \pi_1\sequoid\id_C,\pi_2\sequoid\id_C\rangle\from (A\times B)\sequoid C \toisom (A\sequoid C)\times(B\sequoid C)
\end{gather*}

One important point is that the sequoid does not give rise to a functor $\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ in the way that the tensor product does.  To see why, let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $C\implies D$.  We would like to construct a strategy $\sigma\sequoid\tau$ for
\[
  (A\sequoid C)\implies (B\sequoid D)
  \]
in which player $P$ plays according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $B$ and $D$, exactly as in the strategy $\sigma\tensor\tau$.  The problem is that $\sigma\tensor\tau$ is not necessarily a valid strategy for $(A\sequoid C)\implies (B\sequoid D)$, even if $\sigma$ is a valid strategy for $A\implies B$ and $\tau$ is a valid strategy for $C\implies D$.

Indeed, suppose that player $P$'s reply in $\sigma$ to a particular opening move in $B$ is also a move in $B$, and suppose further that player $P$'s reply in $\tau$ to a particular opening move in $D$ is a move in $C$ (for example, if $\tau$ is a copycat strategy).  Now consider the following narrative for the game $(A\sequoid C)\implies (B\sequoid D)$:
\begin{enumerate}
  \item Player $O$ plays the opening move in $B$, as he must.
  \item Player $P$ replies in $B$, according to $\sigma$.  
  \item Player $O$ decides to switch and start the game $D$.
  \item According to $\tau$, player $P$ should reply with a move in $C$.  But she cannot play in $C$, since no moves have been played in $A$ yet.
\end{enumerate}

In order to fix this situation, we place a restriction on the strategy $\sigma$.

\begin{definition}
  Let $A,B$ be objects of $\G(\alpha)$.  A strategy $\sigma$ for $A\implies B$ is called \emph{strict} if player $P$'s reply to each opening $O$-move in $B$ is a move in $A$ - so if $bx\in\sigma$ then $x\in M_A$.

  It is easy to see that the composition of strict strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ is a strict strategy for $A\implies C$ and that the identity strategy is strict.  Therefore, we have a full-on-objects subcategory $\G_s(\alpha)$ of $\G(\alpha)$ of games and strict strategies.
\end{definition}

\begin{proposition}
  Let $A,B,C,D$ be objects of $\G(\alpha)$, let $\sigma$ be a strict strategy for $A\implies B$ and let $\tau$ be a strict strategy for $C\implies D$.  Then $\sigma\sequoid\tau=\sigma\tensor\tau\cap P_{(A\sequoid C)\implies (B\sequoid D)}$ is a strict strategy for $(A\sequoid C)\implies (B\sequoid D)$ and the following diagram commutes (so $\wk$ is a natural transformation between $\blank\tensor\blank$ and $\blank\sequoid\blank$):
  \[
    \begin{tikzcd}
      A\tensor C \arrow[r, "\sigma\tensor\tau"] \arrow[d, "\wk"']
        & B\tensor D \arrow[d, "\wk"] \\
      A\sequoid C \arrow[r, "\sigma\sequoid\tau"']
        & B\sequoid D
    \end{tikzcd}
    \]

  \begin{proof}
    We know that $\sigma\tensor\tau$ is a valid strategy for $(A\tensor C)\implies (B\tensor D)$, so we just need to check that no moves in $B$ take place before moves in $D$ and that no moves in $A$ take place before moves in $C$.  Indeed, player $O$'s opening move must take place in $B$; then, since $\sigma$ is strict, player $P$'s reply will take place in $A$.  So $\sigma\sequoid\tau$ is a valid strategy for $(A\sequoid C)\implies(B\sequoid D)$; moreover, it is itself a strict strategy.
  \end{proof}
\end{proposition}

What this means is that $\blank\sequoid\blank$ gives us a functor, not from $\G(\alpha)\times\G(\alpha)$ to $\G(\alpha)$, but from $\G_s(\alpha)\times\G(\alpha)$ to $\G_s(\alpha)$.  In fact, the isomorphism $\passoc\from (A\sequoid B)\sequoid C\cong A\sequoid(B\tensor C)$ tells us that $\blank\sequoid\blank$ is a \emph{right action} of the monoidal category $\G(\alpha)$ upon the category $\G_s(\alpha)$.

The closed monoidal category $\G(\alpha)$, the subcategory $\G_s(\alpha)$, the morphisms $\passoc$ and $\run$, and the natural transformation $\wk$ in fact give rise to a structure known as a \emph{sequoidal category} (This definition was first introduced in \cite{laird02}, but with the direction of the sequoid operator reversed; see, for example, \cite{martinsthesis} for the definition where the orientation of the sequoid agrees with ours).

Moreover, the isomorphism $\dec_{A,B,C}\from A\tensor B\cong (A\sequoid B)\times(B\sequoid A)$ means that our sequoidal category is \emph{decomposable} and the isomorphism $\dist_{A,B,C}\from (A\times B)\sequoid C\to (A\sequoid C)\times(B\sequoid C)$ tells us that it is \emph{distributive}.

The last part of the definition of a sequoidal category that we will need is the coherence diagram:
\[
  \begin{tikzcd}
    (A \tensor B) \tensor C \arrow[r, "\wk\tensor\id_C"] \arrow[d, "\assoc_{A,B,C}"']
      & (A \sequoid B) \tensor C \arrow[r, "\wk"]
        & (A \sequoid B) \sequoid C \\
    A \tensor (B \tensor C) \arrow[r, "\wk"]
      & A \sequoid (B \tensor C) \arrow[ur, "\passoc_{A,B,C}"']
        &
  \end{tikzcd}
  \]
Commutativity of this diagram in $\G(\alpha)$ may be verified by inspection.

\cite{laird02} gives examples of what we can prove in general sequoidal categories, particularly in the cpo-enriched setting.  They are used in \cite{martinsthesis} to study the logic modelled by games and history-sensitive strategies.  The most useful property of the sequoid from the point of view of our study of the exponential is that it allows us to express our exponential as a final coalgebra.

Let $\C$ be a category and let $\F\from \C\to\C$ be an endofunctor.  A \emph{coalgebra} for $\F$ is an object $A$ of $\C$ together with a morphism $\map{f}{A}{\F(A)}$.  Given two coalgebras
\begin{gather*}
  \map{f}{A}{\F(A)}\\
  \map{g}{B}{\F(B)}
\end{gather*}
a \emph{coalgebra homomorphism} from $\map{f}{A}{\F(A)}$ to $\map{g}{B}{\F(A)}$ is a morphism $\cmap{h}{A}{B}$ that makes the following square commute:
\[
  \begin{tikzcd}
    A \arrow[r, "f"] \arrow[d, "h"']
      & \F(A) \arrow[d, "\F(h)"] \\
    B \arrow[r, "g"']
      & \F(B)
  \end{tikzcd}
  \]

A \emph{final coalgebra} for $\F$ is a terminal object for the category of coalgebras and coalgebra homomorphisms.  Namely, it is an object $Z$ of $\C$ together with a morphism $\map{\alpha}{Z}{\F(Z)}$ such that for each coalgebra $\map{f}{A}{\F(A)}$ there is a unique morphism
\[
  \fcoal{f}\from A \to Z
  \]
making the following diagram commute:
\[
  \begin{tikzcd}
    A \arrow[r, "f"] \arrow[d, "\fcoal{f}"']
      & \F(A) \arrow[d, "\F\left(\fcoal{f}\right)"] \\
    Z \arrow[r, "\alpha"']
      & \F(Z)
  \end{tikzcd}
  \]

\begin{theorem}
  Let $A$ be an object of a category $\G(\alpha)$ of games.  Then $\oc A$ may be given the structure of a final coalgebra for the functor
  \[
    A\sequoid\blank\from \G(\alpha)\to\G(\alpha)
    \]
  \begin{proof}
    The coalgebra morphism $\alpha\from \oc A\to A\sequoid\oc A$ is given by
    \[
      \alpha \from \oc A \xrightarrow{\mu} \oc A \tensor \oc A \xrightarrow{\der\tensor\id_{\oc A}} A\tensor\oc A\xrightarrow{\wk} A\sequoid\oc A
      \]
    In other words, it is the copycat strategy where moves from the extra copy of $A$ on the right are copied into the first copy of $A$ on the left, moves from the first copy of $A$ in the exponential $\oc A$ on the right are copied into the second copy of $A$ on the left and so on.

    Now let $B$ be a game and let $\sigma$ be a strategy for $B\implies A\sequoid B$.  We define a strategy $\fcoal{\sigma}$ for $B\implies \oc A$ as follows: we first define
    \[
      \|\sigma\| = \{\s\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}\suchthat\forall i\ge 0, \s\vert_{B_i,A_i,B_{i+1}}\in\sigma\}
      \]
    Then we set
    \[
      \fcoal\sigma = P_{B\implies\oc A} \cap \{\s\vert_{B_0,\oc A}\suchthat\s\in\|\sigma\|\}
      \]
    where we write $\s\vert_{B_0, \oc A}$ for $\s\vert_{B_0,A_0,A_1,\dots}$.

    We shall omit the proof that $\fcoal\sigma$ is a strategy.  We claim that the final coalgebra diagram commutes:
    \[
      \begin{tikzcd}
        B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
          & A\sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
        \oc A \arrow[r, "\alpha"']
          & A\sequoid\oc A
      \end{tikzcd}
      \]
    First, we have:
    \[
      \fcoal{\sigma} = P_{B\implies \oc A} \cap \left\{\s\vert_{B_0,A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
        $\s\in(M_B\times\omega\sqcup M_A\times\omega)^{*<\alpha}$\\
        $\forall i\ge0,\;\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
      }}\right\}
      \]
    We claim that:
    \begin{align*}
      \id_A\sequoid\fcoal\sigma &= P_{(A\sequoid B)\implies(A\sequoid\oc A)}\;\cap\\
      &\left\{\s\vert_{A_{-2},B_0,A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
        $\s\in (M_{A_{-2}}\cprd M_{A_{-1}} \cprd M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}$\\
        $\s\vert_{A_{-2},A_{-1}}\in\id_A$\\
        $\forall i\ge 0$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
      }}\right\}
    \end{align*}
    Using the definition:
    \[
      \id\sequoid\fcoal{\sigma} = \{s\in P_{(A_{-2}\sequoid B_0)\implies(A_{-1}\sequoid\oc A)}\suchthat
      s\vert_{A_{-2},A_{-1}}\in\id_A,\;s\vert_{B_0,\oc A}\in\fcoal\sigma\}
      \]
    it is clear that the RHS above is a subset of the LHS.  To show the reverse inclusion, suppose we have some sequence $s\in\id\sequoid\fcoal\sigma$.  Since $s\vert_{B_0,\oc A}\in\fcoal\sigma$, there is some sequence $\s\in\|\sigma\|$ with $\s\vert_{B_0,A_0,A_1,\dots}=s$.  Then it is possible to interleave this sequence with the sequence $s\vert_{A_{-2},A_{-1}}$ exactly as we did towards the end of Section \ref{ImpliesCnSex}: we insert \emph{before} each $P$-move in $A_{-1}$ the corresponding move in $A_{-2}$ and insert \emph{after} each $O$-move in $A_{-1}$ the corresponding move in $A_{-2}$.  This interleaved sequence -- call it $\t$ -- satisfies $\t\vert_{A_{-2},A_{-1}}\in\id_A$ and $\t\vert_{B_i,A_i,B_{i+1}}\in\sigma$ for all $i\ge0$, so it gives rise to an element of the RHS.  Moreover, we have $t\vert_{A_{-2},B_0,A_{-1},A_0,A_1,\dots}=s$, and therefore $s$ is contained in the RHS.

    We now have $\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma} =$
    \[
      P_{B\implies A\sequoid\oc A} \cap \left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
        $\s\in(M_{B_{-1}}\cprd M_{A_{-2}}\cprd M_{A_{-1}}\cprd M_B\times\omega \cprd M_A\times\omega)^{*<\alpha}$\\
        $\s\vert_{B_{-1},A_{-2},B_0}\in\sigma$\\
        $\s\vert_{A_{-2},A_{-1}}\in\id_A$\\
        $\forall i\ge 0$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
      }}\right\}
      \]
    We claim that this is equal to the following strategy:
    \[
      S =
      P_{B\implies A\sequoid\oc A}\cap\left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
        $\s\in (M_{B_{-1}}\cprd M_{A_{-1}} \cprd M_B\times\omega \cprd M_A\times\omega)^{*<\alpha}$\\
        $\forall i\ge -1$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
      }}\right\}
      \]
    $S$ is a strategy since it is nothing more than a relabelling of the indices of $\fcoal\sigma$.  To show that these two strategies are the same, it suffices to show that they contain the same $P$-positions.

    Suppose we have some $P$-position $s\in\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma}$ and write $s=\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}$.  By the argument above, we may assume that all moves from $A_{-2}$ are adjacent to a move from $A_{-1}$; since $s$ is a $P$-position, it cannot end with an $O$-move in $A_{-1}$, and therefore $\s\vert_{A_{-2},A_{-1}}$ must have even length.  Therefore 
    \[
      \s\vert_{A_{-2}}=\s\vert_{A_{-1}}
      \]
    by the definition of $\id_A$.

    It follows (after hiding $M_{A_{-2}}$) that $\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma} \subset S$.  Conversely, given an element $s=\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\in S$, we may interleave in a play in $A_{-2}$ that is identical to the play in $\s\vert_{A_{-1}}$ as above, showing that $s\in\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma}$.

    It remains only to observe that $S$ is precisely the strategy $\comp{\alpha}{\fcoal\sigma}$, and so the square above does indeed commute.

    Now we show uniqueness.  Suppose that $\tau$ is some strategy for $B\implies\oc A$ such that the diagram commutes:
    \[
      \begin{tikzcd}
        B \arrow[r, "\sigma"] \arrow[d, "\tau"']
          & A\sequoid B \arrow[d, "\id_A\sequoid\tau"] \\
        \oc A \arrow[r, "\alpha"']
          & A\sequoid\oc A
      \end{tikzcd}
      \]
    We claim that $\tau=\fcoal\sigma$.  The argument above tells us that
    \[
      \comp{(\id_A\sequoid\tau)}{\sigma} =
      \left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
        $\s\in(M_{B_{-1}}\cprd M_{A_{-1}}\cprd M_{B_0}\cprd M_A\times\omega)^{*<\alpha}$\\
        $\s\vert_{B_{-1},A_{-1},B_0}\in\sigma$\\
        $\s\vert_{B_0,A_0,A_1,\dots}\in\tau$
      }}\right\}
      \]
    Meanwhile, we have
    \[
      \comp{\alpha}{\tau} = \{t^\dagger\suchthat t\in\tau\}
      \]
    where $t^\dagger\in(M_{B_{-1}}\cprd M_{A_{-1}}\cprd M_A\times\omega)^{*<\alpha}$ is formed by reducing the indices on the copies of $A$ and $B$ in $t\in(M_{B_0}\cprd M_A\times\omega)^{*<\alpha}$.

    We have $\comp{(\id\sequoid\tau)}{\sigma}=\comp\alpha\tau$, so, after promoting all indices by $1$, we may write:
    \begin{equation}\label{taufixedpoint}
      \tau = 
      \left\{\s\vert_{B_{0},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
        $\s\in(M_{B_0}\cprd M_{B_1}\cprd M_A\times\omega)^{*<\alpha}$\\
        $\s\vert_{B_0,A_0,B_1}\in\sigma$\\
        ($\s\vert_{B_1,A_1,A_2 \dots})^\dagger\in\tau$
      }}\right\}
      \tag{$*$}
    \end{equation}
    Let $t\in\tau$.  Then we have just shown that we may interleave $t$ with a sequence $r\in M_{B_1}$ such that the interleaved sequence $\t\in(M_{B_0}\cprd M_{B_1}\cprd M_{A}\times\omega)^{*<\alpha}$ satisfies
    \begin{gather*}
      \t\vert_{B_0,\oc A}=t\quad\t\vert_{B_1}=r\\
      \t\vert_{B_0,A_0,B_1}\in\sigma\\
      (\t\vert_{B_1,A_1,A_2,\dots})^\dagger\in\tau
    \end{gather*}
    Let $t_1=(\t\vert_{B_1,A_1,A_2,\dots})^\dagger$.  Applying the result repeatedly allows us to build up a sequence $t=t_0,t_1,t_2,\dots$ where $t_i\in\tau$ for each $i$, together with a sequence $\t=\t_0,\t_1,\t_2,\dots\in (M_{B_0}\cprd M_{B_1}\cprd M_A\times\omega)^{*<\alpha}$ such that for each $i$:
    \begin{gather*}
      \t_i\vert_{B_0,\oc A}=t_i\\
      \t_i\vert_{B_0,A_0,B_1}\in\sigma
    \end{gather*}
    By construction, the $A$-components of the $\t_i$ agree (indeed, the $A_i$-component of $\t_j$ is the same as the $A_{i+j}$-component of $\t_0$), and the $B_1$-component of $\t_i$ is the same as the $B_0$-component of $t_{i+1}$.  Therefore, the $\t_i$ interleave to give a sequence
    \[
      \T\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}
      \]
    such that $\T\vert_{B_0,\oc A}=t$ and for all $i\ge 0$, $\T\vert_{B_i,A_i,B_{i+1}}\in\sigma$.  It follows that $t\in\fcoal\sigma$ and so $\tau\subset\fcoal\sigma$.

    Now suppose that $s\in\fcoal\sigma$.  We show by transfinite induction on the length of $s$ that $s\in\tau$.  Since $\tau$ satisfies the limiting condition, the limiting case of the induction is easy.  So suppose instead that $s=s'a$ is a successor play, and suppose that the last move $a$ takes place in the game $A_n$.  By induction, we assume that $s'\in\tau$.  We now apply the construction above to give us a sequence
    \[
      s'=t_0,t_1,\dots,t_{n+1}
      \]
    of plays in $\tau$ whose $A$-components agree so that the $A_i$-component of $t_j$ is the $A_{i+j}$-component of $s'$.  It follows that the $A$-components of $t_{n+1}$ also agree with the components of $A_{n+1},A_{n+2},\dots$ of $sa$, since the move $a$ takes place in $A_n$.

    We have $t_{n+1}\in\tau$.  We now claim that $t_{n}a$ satisfies the conditions on the right in \eqref{taufixedpoint}, so $t_n a\in\tau$ as well.  Indeed, we have $s'a\in\fcoal\sigma$, so there exists some $\s a\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}$ with $\s\vert_{B_0,\oc A}=s$ and $\s a\vert_{B_i,A_i,B_{i+1}}\in\sigma$ for all $i$.

    Consider the sequence
    \[
      \s a\vert_{B_n,B_{n+1},A_n,A_{n+1},A_{n+2},\dots}
      \]
    We have $\s a\vert_{B_n,A_n,A_{n+1}}\in\sigma$ (since $\s a\in\fcoal\sigma$) and $\s a\vert_{B_{n+1},A_{n+1},A_{n+2},\dots}=s \vert_{B_{n+1},A_{n+1},A_{n+2},\dots}\in\tau$ by \eqref{taufixedpoint}.  Therefore, $\s a\vert_{B_n,B_{n+1},A_n,A_{n+1},A_{n+2},\dots}$ satisfies the conditions for the right hand side of \eqref{taufixedpoint} (after subtracting $n$ from each of the indices) and therefore 
    \[
      t_n a=\s a\vert_{B_n,A_n,A_{n+1},\dots}\in\tau
      \]
    Moreover, this sequence is contained in $\fcoal\sigma$ (by checking the definition).

    By repeatedly applying this argument, we eventually show that 
    \[
      sa=\s a\vert_{B_0,A_0,A_1,\dots}\in\tau
      \]
    This completes the proof.
  \end{proof}
\end{theorem}

\begin{note}
  This is not the same as the proof found in \cite{martinsthesis}, which implicitly uses the fact that in the finitary games setting we may identify $\oc A$ with the limit of the diagram
  \[
    I \leftarrow A \leftarrow A\sequoid A \leftarrow A\sequoid(A\sequoid A) \leftarrow \cdots
    \]
  As we shall see in the next section, we do not have this identification in the transfinite setting.  However, we will give an alternative proof that $\oc A$ is the final coalgebra for $A\sequoid\blank$ in the next section that will be more along the lines of the proof in \cite{martinsthesis}.  
\end{note}

\pagebreak

\subsection{The sequoidal exponential gives a cofree commutative comonoid}
\label{SeqExpIsCofCommCom}

As an application of this result, we shall prove that $\oc A\xrightarrow{\mu}\oc A\tensor \oc A$ is the cofree commutative comonoid on $A$.  We start with a small but useful lemma:

\begin{lemma}
  \[
    \oc A \tensor \oc A \cong \oc(A\times A)
    \]
  \begin{proof}
    We check that the game trees are isomorphic.  The basic idea is that in each $P$-position the player $O$ may either play in one of the games that has already been opened, or he has a choice of two new games to open -- in $\oc A\tensor \oc A$, he may open either the first unopened copy of $A$ on the left or the first unopened copy of $A$ on the right, while in $\oc(A\times A)$ he may open either of the copies of $A$ in the first unopened copy of $A\times A$.  
  \end{proof}
\end{lemma}

This means that $\oc A\tensor\oc A$ is the final coalgebra for the functor 
\[
  (A\times A)\sequoid\blank
  \]
Upon examining the induced morphism $\oc A\tensor \oc A \to (A\times A)\sequoid(\oc A\tensor \oc A)$, we observe that it is equal to the following composite
\[
  \oc A\tensor \oc A \xrightarrow{\xi} (A\sequoid(\oc A\tensor\oc A)) \times (A\sequoid(\oc A\tensor\oc A))\xrightarrow{\dist\inv}(A\times A)\sequoid(\oc A\tensor \oc A)
  \]
where the morphism $\xi$ is induced by the morphisms
\[
  \begin{tikzcd}
    %
      &
        & (A\sequoid\oc A)\tensor \oc A \arrow[r, "\wk"]
          & (A\sequoid\oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
            & A\sequoid (\oc A\tensor \oc A) \\
    \oc A \tensor \oc A \arrow[urr, "\alpha\tensor\id"] \arrow[dr, "\sym"]
      &
        &
          &
            & \\
    %
      & \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"]
        & (A\sequoid\oc A)\tensor \oc A \arrow[r, "\wk"]
          & (A\sequoid\oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
            & A\sequoid (\oc A\tensor \oc A) \\
  \end{tikzcd}
  \]

Now let $\map{\mu}{B}{B\tensor B}$ be a commutative comonoid in $\G(\alpha)$ and let $\sigma\from B\to A$ be a morphism.  We build up a chain as follows:
\[
  B \xrightarrow{\mu} B\tensor B \xrightarrow{\sigma\tensor\id_B} A \tensor B \xrightarrow{\wk} A \sequoid B \xrightarrow{\Delta} (A \sequoid B) \times (A \sequoid B) \rightarrow{\dist_{A,A,B}\inv} (A\times A)\sequoid B
  \]
where $\Delta=\langle\id,\id\rangle$ is the diagonal morphism into the product.  The composite $\comp{\comp{\wk}{\sigma\tensor\id_B}}{\mu}$ gives rise to a unique morphism
\[
  \sigma^\dagger=\fcoal{\comp{\comp{\wk}{\sigma\tensor\id_B}}{\mu}}\from B\to \oc A
  \]
making the following diagram commute:
\[
  \begin{tikzcd}
    B \arrow[r, "\mu"] \arrow[d, "\sigma^\dagger"']
      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
        & A\tensor B \arrow[r, "\wk"]
          & A \sequoid B \arrow[d, "\id_A\sequoid\sigma^\dagger"] \\
    \oc A \arrow[rrr, "\alpha"]
      &
        &
          & A\sequoid\oc A
  \end{tikzcd}
  \]

We claim that $\sigma^\dag$ gives us a homomorphism of comonoids; that is, that the following square commutes:
\[
  \begin{tikzcd}
  B \arrow[r, "\mu"] \arrow[d, "\sigma^\dag"']
    & B\tensor B \arrow[d, "\sigma^\dag\tensor\sigma^\dag"] \\
  \oc A \arrow[r, "\mu"]
    & \oc A \tensor \oc A
  \end{tikzcd}
  \]
We will show this by proving that the two paths round the square are both anamorphisms for the morphism $B\to (A\times A)\sequoid B$ given above.  Since anamorphisms are unique by the definition of a final coalgebra, this will mean that the two branches are equal.

We start with the branch $B\to B\tensor B \to \oc A\tensor \oc A$.  We claim that the following diagram commutes:
\begin{longdiagram}
  \begin{tikzcd}
    B \arrow[r, "\mu"] \arrow[d, "\sigma^\dag"]
      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
        & A \tensor B \arrow[r, "\wk"]
          & A \sequoid B \arrow[r, "\Delta"] \arrow[d, "\id_A\sequoid\sigma^\dagger"]
            & (A\sequoid B) \times (A \sequoid B) \arrow[r, "{\dist_{A,A,B}\inv}"] \arrow[d, "{\langle\id_A\sequoid\sigma^\dagger,\id_A\sequoid\sigma^\dagger\rangle}"]
              & (A \times A) \sequoid B \arrow[d, "\id_{A\times A}\sequoid\sigma^{\dagger}"] \\
    \oc A \arrow[rrr, "\alpha"] \arrow[d, "\mu"]
      &
        &
          & A\sequoid \oc A \arrow[r, "\Delta"]
            & (A \sequoid \oc A)\times (A\sequoid \oc A) \arrow[r, "{\dist_{A,A,\oc A}\inv}"']
              & (A\times A)\sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
    \oc A \tensor \oc A \arrow[rrrrr]
      &
        &
          &
            &
              & (A\times A)\sequoid(\oc A\tensor \oc A)
  \end{tikzcd}
\end{longdiagram}

The rectangle at the top left is one we have drawn before.  The square in the middle at the top commutes because $\Delta$ gives rise to a natural transformation between $\id_{\G(\alpha)}$ and $\blank\times\blank$.  The square at the top right commutes because $\dist$ is a natural transformation.

The rectangle at the bottom commutes because both branches are copycat strategies for $\oc A\implies (A\times A)\sequoid(\oc A\tensor\oc A)$, and there is a unique such strategy.

It follows that $\comp\mu{\sigma^\dagger}$ is an anamorphism for the morphism along the top and the functor $(A\times A)\sequoid\blank$.

Now we deal with the other branch.  We claim that we have the following commutative diagram:
\begin{longdiagram}
  \begin{tikzcd}
    B \arrow[r, "\mu"] \arrow[dd, "\mu"'] \arrow[ddr, phantom, "\textbf{1}"]
      & B\tensor B \arrow[r, "\sigma\tensor \id_B"] \arrow[d, "\id_B\tensor\mu"] \arrow[dr, phantom, "\textbf{2}"]
        & A \tensor B \arrow[rrr, "\wk"] \arrow[d, "\id_A\tensor\mu"] \arrow[drrr, phantom, "\textbf{3}"]
          &
            &
              & A\sequoid B \arrow[d, "\id_A\sequoid\mu"] \\
    %
      & B \tensor(B\tensor B) \arrow[r, "\sigma\tensor\id_{B\tensor B}"] \arrow[d, "{\assoc_{B,B,B}\inv}"]
        & A \tensor (B \tensor B) \arrow[rrr, "\wk"] \arrow[drr, phantom, "\textbf{4}"]
          &
            &
              & A \sequoid (B\tensor B) \arrow[dd, "\id_A\sequoid(\sigma^\dagger \tensor \sigma^\dagger)"] \arrow[dl, "{\passoc_{A,B,B}}"] \arrow[ddl, phantom, "\textbf{7}"] \\
    B \tensor B \arrow[r, "\mu\tensor \id_B"] \arrow[d, "\sigma^\dagger \tensor \sigma^\dagger"'] \arrow[drrr, phantom, "\textbf{5}" yshift=-0.3em]
      & (B \tensor B) \tensor B \arrow[r, "(\sigma\tensor\id_B)\tensor\id_B"' yshift=-0.3em]
        & (A \tensor B) \tensor B \arrow[r, "\wk\tensor\id_B"]
          & (A \sequoid B) \tensor B \arrow[r, "\wk"] \arrow[d, "(\id\sequoid\sigma^\dagger)\tensor\sigma^\dagger"'] \arrow[dr, phantom, "\textbf{6}"]
            & (A\sequoid B)\sequoid B \arrow[d, "(\id\sequoid\sigma^\dagger)\sequoid\sigma^\dagger"]
              & \\
    \oc A \tensor \oc A \arrow[rrr, "\alpha\sequoid\id_{\oc A}"']
      &
        &
          & (A \sequoid \oc A)\tensor \oc A \arrow[r, "\wk"]
            & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
              & A \sequoid (\oc A \tensor \oc A)
  \end{tikzcd}
\end{longdiagram}

We check that each cell commutes in turn.
\begin{enumerate}[{\bf 1}]
  \item is the diagram showing that the comultiplication for $B$ is associative.
  \item commutes since $\blank\tensor\blank$ is a functor.
  \item commutes since $\wk$ is a natural transformation.
  \item is the coherence diagram for sequoidal categories that we gave earlier.
  \item is obtained from an earlier diagram by taking the tensor product with $B$ on the top, taking the tensor product with $\oc A$ on the bottom, and passing between the two with the morphism $\sigma^\dag$.  
  \item commutes because $\wk$ is a natural transformation.
  \item commutes because $\passoc$ is a natural transformation.  
\end{enumerate}

\pagebreak

Furthermore, note that the morphism along the bottom is one of the two morphisms $\oc A\tensor\oc A \to A\sequoid(\oc A \tensor \oc A)$ that we gave before.  To get the other one, note that since the comultiplication in $B$ is commutative, we have a commutative diagram:
\[
  \begin{tikzcd}
    %
      & B \arrow[ddl, "\mu"'] \arrow[dd, "\mu"] \\
    %
      & \\
    B\tensor B \arrow[r, "\sym"] \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"']
      & B\tensor B \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"] \\
    \oc A \tensor \oc A \arrow[r, "\sym"]
      & \oc A \tensor \oc A
  \end{tikzcd}
  \]
which we may glue on to the left hand side of the diagram above, giving a commutative diagram with the second morphism $\oc A\tensor \oc A\to A\sequoid(\oc A\tensor \oc A)$ along the bottom.

These two diagrams between them induce a commutative diagram
\begin{longdiagram}
  \begin{tikzcd}
    B \arrow[r, "\mu"] \arrow[d, "\mu"']
      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
        & A \tensor B \arrow[r, "\wk"]
          & A \sequoid B \arrow[r, "\Delta"]
            & (A \sequoid B) \times (A \sequoid B) \arrow[r, "{\dist_{A,A,B}\inv}" yshift=0.6em] \arrow[d, "{\langle \id_A\sequoid\mu, \id_A\sequoid\mu\rangle}"']
              & (A\times A)\sequoid B \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
    B\tensor B \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"']
      &
        &
          &
            & (A \sequoid (B \tensor B)) \times (A \sequoid (B\tensor B)) \arrow[d, "{\langle \id_A\sequoid(\sigma^\dagger\tensor\sigma^\dagger), \id_A\sequoid(\sigma^\dagger\tensor\sigma^\dagger)\rangle}"'] \arrow[r, "{\dist_{A,A,B\tensor B}\inv}"]
              & (A \times A) \sequoid (B\tensor B) \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
    \oc A \times \oc A \arrow[rrrr, "\xi"]
      &
        &
          &
            & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "{\dist_{A,A,\oc A\tensor\oc A}\inv}" yshift=0.3em]
              & (A\times A) \sequoid(\oc A \tensor \oc A)
  \end{tikzcd}
\end{longdiagram}

that proves that $\comp{\sigma^\dagger\tensor\sigma^\dagger}{\mu}$ is an anamorphism for the morphism along the top as well.  Therefore, $\sigma^\dagger$ does give us a homomorphism of comonoids.

We claim that $\sigma^\dagger$ makes the following diagram commute:
\[
  \begin{tikzcd}
    B \arrow[d, "\sigma^\dagger"'] \arrow[dr, "\sigma"]
      & \\
    \oc A \arrow[r, "\der"']
      & A
  \end{tikzcd}
  \]
Indeed, we have a commutative diagram
\[
  \begin{tikzcd}
    B \arrow[r, "\comp{\wk}{\comp{(\sigma\tensor\id_B)}{\mu}}" yshift=0.3em] \arrow[d, "\sigma^\dagger"']
      & A \sequoid B \arrow[dr, "\id_A\sequoid 1"] \arrow[d, "\id_A\sequoid\sigma^\dagger"']
        & 
          & \\
    \oc A \arrow[r, "\alpha"']
      & A \sequoid \oc A \arrow[r, "\id_A\sequoid 1"']
        & A \sequoid I \arrow[r, "\run_A"]
          & A
  \end{tikzcd}
  \]
and we observe that the morphism along the bottom is precisely $\der$, while the morphism along the top is precisely $\sigma$.

Now we show uniqueness.  Suppose that $\tau\from B\to\oc A$ is a morphism making the following diagram commute:
\[
  \begin{tikzcd}
    %
      & B \arrow[d, "\tau"] \arrow[r, "\mu"] \arrow[dl, "\sigma"']
        & B \tensor B \arrow[d, "\tau\tensor\tau"] \\
    A
      & \oc A \arrow[l, "\der"] \arrow[r, "\mu"]
        & \oc A \tensor \oc A
  \end{tikzcd}
  \]
Then we get the following commutative diagram:
\[
  \begin{tikzcd}
    B \arrow[r, "\mu"] \arrow[d, "\tau"]
      & B \tensor B \arrow[r, "\sigma\tensor\id_A"] \arrow[d, "\tau\tensor\tau"]
        & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id_A\tensor\tau"]
          & A \sequoid B \arrow[d, "\id_A\sequoid\tau"] \\
    \oc A \arrow[r, "\mu"]
      & \oc A \tensor \oc A \arrow[r, "\der\tensor\id_A"]
        & A \tensor \oc A \arrow[r, "\wk"]
          & A \sequoid \oc A
  \end{tikzcd}
  \]
where commutativity of the middle square is derived from the commutative triangle on the left of the diagram immediately above.  Now observe that the morphism $A\to A\sequoid\oc A$ along the bottom is precisely the morphism $\alpha$.  Therefore, $\tau$ is an anamorphism for the morphism
\[
  B \xrightarrow{\mu} B\tensor B \xrightarrow{\sigma\tensor\id_A} A\tensor B \xrightarrow{\wk} A \sequoid B
  \]
and so $\tau=\sigma$.

We have shown that $\oc A \xrightarrow{\mu}\oc A \tensor \oc A$ is indeed the cofree commutative comonoid on $A$.

\section{The final sequence}

Familiarity with the final sequence is assumed; see \cite{finalseq} for a less terse presentation of the following material.

Let $\C$ be a category and let $\F\from \C\to \C$ be an endofunctor.  Suppose that $\C$ has a terminal object $1$.  We shall further assume that we are able to construct all the limits we want in $\C$.  Let $\Ord$ denote the ordered class of ordinals, considered as a category.  We shall inductively construct a functor $\FS_\F\from\oppcat\Ord\to\C$ (known as the \emph{final sequence of $\F$}) as follows:

\begin{itemize}
  \item $\FS_\F(0)=1$
  \item $\FS_\F(\beta+1) =\F\left(\FS_F(\beta)\right)$
  \item On the level of morphisms, $\FS_\F(0\le\beta)$ is the unique morphism $\FS_\F(\beta)\to 1$
  \item $\FS_\F(\beta+1\le\beta+2)=\F(\FS_\F(\beta\le\beta+1))$
  \item If $\mu$ is a limit ordinal, then $\FS_\F(\mu)$ is the limit of the diagram
    \[
      \mu\hookrightarrow\Ord\xrightarrow{\FS_\F}\C
      \]
    and $\FS_\F(\beta\le\mu)$ is the arrow in the limiting cone
  \item Applying the functor $\F$ to the cone $\FS_\F(\mu)$ gives rise to a new cone over the above diagram, inducing a unique arrow $\FS_\F(\mu+1)\to\FS_\F(\mu)$.  We set $\FS_\F(\mu\le\mu+1)$ to be equal to this arrow.
\end{itemize}

A standard fact about the final sequence (see \cite{finalseq}) is that if $\delta$ is an ordinal and the morphism
\[
  \FS_\F(\delta\le\delta+1)\from \F(\FS_\F(\delta))\to \FS_\F(\delta)
  \]
is an isomorphism, then the inverse of this morphism exhibits $\FS_\F(\delta)$ as the final coalgebra for the endofunctor $\F$.  In this case, we say that the final sequence $\FS_\F$ has \emph{stabilized by $\delta$}.

Our goal is to characterize the final sequence for functors of the form $A\sequoid\blank$ in categories $\G(\alpha)$ of games, in the hope that this will allow us to study the exponential $\oc A$ in more depth.

\subsection{The rank of a transfinite sequence of natural numbers}

We fix a (large) ordinal $\alpha$.  The goal of this section is to assign an ordinal \emph{rank} to a sequence $\beta\to\omega$ of natural numbers (for $\beta<\alpha$).  This rank will turn out to be the key to characterizing the final sequence of the $A\sequoid\blank$ functor.  This rank will not depend on $\alpha$, and we could do without mentioning $\alpha$ at all (although mentioning $\alpha$ allows us to avoid size issues).

To define our rank, we will give a chain of subsets 
\[
  R_0\subset R_1\subset R_2\subset\dots \subset R_\delta \subset\dots \subset \omega^{*\alpha}
  \]
where $\delta$ will run over all the ordinals.  We think of $R_\delta$ as being the set of all sequences \emph{with rank at most $\delta$}; accordingly, we shall define the \emph{rank} of a sequence $s$ to be the smallest ordinal $\delta$ such that $s\in R_\delta$.

\begin{definition}
  Let $(s\from\beta\to\omega)\in\omega^{*<\alpha}$.  We define the \emph{derivative} of $s$ to be the sequence $\Delta s$ given by:
  \[
    s\inv\left(\omega\setminus\{0\}\right) \xrightarrow{s} \omega\setminus\{0\} \xrightarrow{n\mapsto n-1} \omega
    \]
  In other words, we remove all occurrences of $0$ from the sequence $s$ and then subtract $1$ from each term.  
\end{definition}

We shall now define the sets $R_\delta$:
\begin{definition}
  \begin{itemize}
    \item $R_0=\{\emptyplay\}$
    \item $R_{\delta+1}=\left\{s\in\omega^{*<\alpha}\suchthat \Delta s\in R_\delta\right\}$
    \item If $\mu$ is a limit ordinal then $R_\mu$ is the limit closure of the union of the $R_\delta$ for $\delta<\mu$.  In other words, a sequence $s$ is contained in $R_\mu$ if \textbf{either}
      \begin{itemize}
        \item $\length(s)$ is a successor ordinal and $s\in R_\delta$ for some $\delta<\mu$ \textbf{or}
        \item $\length(s)$ is a limit ordinal and for all proper prefixes $t\pprefix s$, $t\in R_\delta$ for some $\delta<\mu$
      \end{itemize}
  \end{itemize}

  If $s\in\omega^{*<\alpha}$, we define $\rank(s) = \min\{\delta\suchthat s\in R_\delta\}$.
\end{definition}

One consequence of the above definition is that if $\mu$ is a limit ordinal then all the sequences of rank $\mu$ have limiting length.

We need to prove some results so we can be sure that the rank of a sequence is well defined.

\begin{proposition}
  \label{RankProposition}
  \begin{enumerate}[i)]
    \item If $s\in R_\delta$ and $t$ is any subsequence of $s$ (not necessarily an initial prefix), then $t\in R_\delta$
    \item If $s\in R_\delta$, then $\Delta s\in R_\delta$.
    \item If $\gamma\le\delta$, then $R_\gamma\subset R_\delta$
    \item If $s\in\omega^{*<\alpha}$, then $s\in R_\delta$ for some $\delta$.
  \end{enumerate}

  \begin{proof}
    \begin{enumerate}[(i): ]
      \item We prove this by induction on $\delta$.  Suppose $s\in R_{\delta+1}$ and $t$ is a subsequence of $s$.  Then $\Delta s\in R_\delta$.  Now $\Delta t$ is a subsequence of $\Delta s$, so $\Delta t\in R_\delta$ by the induction hypothesis and therefore $\Delta t\in R_{\delta +1}$.

        Let $\mu$ be a limit ordinal and suppose that $s\in R_\mu$.  If $s$ has successor length, then $s\in R_\delta$ for some $\delta<\mu$.  Then $t\in R_\delta$ by the induction hypothesis.  If $t$ has successor length, this automatically means that $t\in R_\mu$, while if $t$ has limiting length, then every subsequence of $t$ is contained in $R_\delta$ by induction, so $t\in R_\mu$.

        Suppose instead that $s$ has limiting length.  Then for all proper prefixes $u\pprefix s$, we have $u\in R_\delta$ for some $\delta<\mu$.  If $t$ has successor length, then $t$ cannot be cofinal in $s$, so it is a subsequence of some proper prefix $u$ of $s$.  Therefore, $t\in R_\delta$ by the induction hypothesis, and so $t\in R_\mu$ as before.

        If instead $t$ has limiting length, then every proper prefix $v\pprefix t$ is a subsequence of some proper prefix $u\pprefix s$.  Therefore, by induction, for every proper prefix $v\pprefix t$, we have $v\in R_\delta$ for some $\delta<\mu$ and therefore $t\in\mu$.

      \item Induction on $\delta$.  If $s\in R_{\delta+1}$ then $\Delta s\in R_\delta$; by the induction hypothesis, this means that $\Delta\Delta s\in R_\delta$ and therefore that $\Delta s\in R_{\delta+1}$.

        Now let $\mu$ be a limit ordinal.  Suppose $s\in R_\mu$.  If $s$ has successor length, it means that $s\in R_\delta$ for some $\delta<\mu$, so $\Delta s\in R_\delta$ by induction.  By (i), all the prefixes of $\Delta s$ are in $R_\delta$ as well, so $\Delta s\in R_\mu$.

        Suppose instead that $s$ has limiting length.  Then for all proper prefixes $t\pprefix s$, we have $t\in R_\delta$ for some $\delta<\mu$.  If $\Delta s$ has successor length, then we may choose some proper prefix $t\pprefix s$ such that $\Delta s = \Delta t$ and therefore $\Delta s\in R_\delta$, so it is in $R_\mu$.  If instead $\Delta s$ has limiting length, then for all proper prefixes $v\pprefix\Delta s$, we may choose some $u\pprefix s$ with $v=\Delta u$.  Then we have $u\in R_\delta$ for some $\delta<\mu$, so $v\in R_\delta$ by the induction hypothesis.  Therefore, $t\in R_\mu$.

      \item It is clear that $R_\delta\subset R_\mu$ if $\delta<\mu$ and $\mu$ is a limit ordinal.  Therefore, by induction it will suffice to show that $R_\delta\subset R_{\delta+1}$ for all $\delta$.

        Suppose $s\in R_\delta$.  Then $\Delta s\in R_\delta$ by (ii) and therefore $s\in R_{\delta+1}$.

      \item We show this by induction on the length $\beta$ of $s$.  If $\beta=0$ then $s\in R_0$.  Suppose that $s=s'n$.  If we apply $\Delta$ $n$ times to $s$ then we end up with the sequence $\Delta^ns .0$.  Applying $\Delta$ never lengthens the sequence, by Lemma \ref{TechnicalOrdinalLemma}.  Now if we apply $\Delta$ one more time, we end up with a strictly shorter sequence, so by induction it is contained in some $R_\delta$.  Then $s$ is contained in $R_{\delta+n+1}$.

        Now suppose that $s$ has limiting length.  Then, by induction, for all proper prefixes $t\pprefix s$ there exists $\delta_t$ such that $t\in R_{\delta_t}$.  If we let $\mu$ be some limit ordinal that is greater than all the $\delta_t$, then $s\in R_\mu$.  \qedhere
    \end{enumerate}
  \end{proof}
\end{proposition}

\begin{example}
  Any sequence with only finitely many distinct terms has finite rank: indeed, suppose $s\from\beta\to n$ is such a sequence.  Then, after applying the derivative $n$ times, we end up with the empty sequence.

  The `identity' sequence $\omega\to\omega$ has rank $\omega$: indeed, every proper prefix has finite rank, but applying the derivative operator has no effect.

  More generally, the division algorithm for ordinal arithmetic tells us that if $\gamma$ is an ordinal, then there is a unique ordinal $\gamma'$ and a unique natural number $n$ such that $\gamma=\omega\gamma' + n$.  If $\beta$ is an ordinal, we may define a sequence $c_\beta\from \beta\to\omega$ by setting:
  \[
    c_\beta(\omega\gamma'+n) = n
    \]
  We show by induction on $\beta$ that the sequence $c_\beta$ has rank $\beta$.  First, we claim that
  \[
    c_\beta = \Delta c_{\beta+1}
    \]
  The first thing to show is that the order type of $c_{\beta+1}\inv(\omega\setminus\{0\})$ is $\beta$.  Indeed, $c_{\beta+1}\inv(\omega\setminus\{0\})$ is precisely the set of successor ordinals that are less than $\beta+1$.  We therefore have an order preserving bijection
  \begin{IEEEeqnarray*}{rCl}
    \beta & \to & c_{\beta+1}\inv(\omega\setminus\{0\}) \\
    \gamma & \mapsto & \gamma+1
  \end{IEEEeqnarray*}

  This map sends $\omega\gamma'+n$ to $\omega\gamma'+(n+1)$.  The map $\Delta c_{\beta+1}$ is therefore given by:
  \begin{IEEEeqnarray*}{CCCCCCC}
    \beta & \xrightarrow{\sim} & c_{\beta+1}\inv(\omega\setminus\{0\}) & \rightarrow & \omega \setminus \{0\} & \rightarrow & \omega \\
    \omega\gamma' + n & \mapsto & \omega\gamma' + (n+1) & \mapsto & n+1 & \mapsto & n
  \end{IEEEeqnarray*}
  In other words, it is the same as $c_\beta$.  This deals with the successor step of the induction.

  Now let $\mu$ be a limit ordinal.  A proper prefix of $c_\mu$ is a sequence of the form $c_\delta$ for $\delta<\mu$.  By the induction hypothesis, $c_\delta\in R_\delta$ for all $\delta<\mu$ and therefore $c_\mu\in R_\mu$.

  Now suppose for a contradiction that $c_\mu\in R_\delta$ for some $\delta<\mu$.  Then $c_{\delta+1}\prefix c_\mu$ so, by Proposition \ref{RankProposition}(i), $c_{\delta+1}\in R_\delta$, which contradicts our induction hypothesis.

  Therefore, $\rank(c_\mu)=\mu$.  
\end{example}

We call $c_\delta$ the \emph{canonical sequence of length $\delta$}.  We want to use it to obtain a neater characterization of the sets $R_\delta$.  What we would like to say is that $\rank(s)\ge\delta$ if and only if $c_\delta$ is a subsequence of $s$.  However, this is not quite true.  For example, the sequence
\[
  23456\dots
  \]
over $\omega$ has rank $\omega$, but does not contain the sequence $c_\omega=01234\dots$ as a subsequence.  We will have to modify the condition a little bit; the cost will be that our characterization only works for limit ordinals, but this is not a big problem.

\begin{definition}
  Let $s\from\beta\to\omega$ be a sequence.  We say that $s$ is \emph{weakly increasing} if $s(\delta)<s(\delta+1)$ for all $\delta<\beta$.
\end{definition}

\begin{example}
  $c_\beta$ is weakly increasing for any $\beta$.  If we take, for example, the sequence $c_{\omega+\omega}$:
  \[
    01234\dots\;01234\dots
    \]
  then we see where the `weakly' comes from: we have $c_{\omega+\omega}(2)>c_{\omega+\omega}(\omega)$, even though $2<\omega$.  \emph{Weakly increasing} means `increasing on every $\omega$-segment, but unconstrained at limits'.

  There are plenty of other weakly increasing sequences.  For example:
  \begin{gather*}
    2468\dots \\
    12358\dots\;2357\dots \\
    01234\dots\;12345\dots\;23456\dots\;34567\dots\;45678\dots\;\dots\dots
  \end{gather*}
\end{example}

\pagebreak

\begin{lemma}
  \label{WeaklyIncreasingLemma}
  \begin{enumerate}[i)]
    \item Let $s\in\omega^{*<\alpha}$ be weakly increasing.  Then $\Delta s$ is weakly increasing.
    \item Suppose $\mu$ is a limit ordinal and that $s\in \omega^{*<\alpha}$ is such that $\rank(s)=\mu$.  Then $\rank(\Delta s)=\mu$.
    \item Let $\mu$ be a limit ordinal and let $s\from\mu\to\omega$ be a weakly increasing sequence of length $\mu$.  Then $\rank(s)=\mu$.  
  \end{enumerate}

  \begin{proof}
    \begin{enumerate}[(i): ]
      \item Let $m,n$ be adjacent terms in $\Delta s$.  That means that $(m+1).p$ occurs somewhere in the sequence $s$, so $p>m+1$, since $s$ is weakly increasing.  In particular, $p\ne 0$, so it is not removed from the sequence.  It follows that $n=p-1$ and therefore that $m<n$.

      \item We have $s\in R_\mu$, so $\Delta s\in R_\mu$; i.e., $\rank(\Delta s)\le\mu$.  Suppose that $\Delta s\in R_\delta$ for $\delta<\mu$.  Then $s\in R_{\delta+1}$, which is a contradiction.

      \item We prove the following statement by induction on $\beta$: if $s\from\beta\to\omega$ is a weakly increasing sequence of length $\beta$, then
        \begin{itemize}
          \item If $\beta=\omega\beta'+m$ is a successor ordinal, and $s=s'n_0\dots n_{m-1}$, then $\rank(s) = \omega\beta'+n_{m-1}+1$
          \item If $\beta=\omega\beta'$ is a limit ordinal then $\rank(s)=\beta$
        \end{itemize}
        Suppose that $s$ has length $\omega\beta'+m$ and write $s$ as $s'n_0\dots n_{m-1}$, where $s'$ is a limiting play.  Write $n=n_{m-1}$ -- so $n_i<n$ for $i<m-1$.  By the induction hypothesis, $s'$ has rank $\omega\beta'$.

        If we apply the derivative $n$ times to $s$ then we end up with the sequence $\Delta^n s'.0$.  By part (ii), $\Delta^n s'$ has rank $\omega\beta'$, and so $\Delta^n s'.0$ has rank at least $\omega\beta'$.  Moreover, since it is a successor play, it cannot have limiting rank, and therefore its rank is at least $\omega\beta+1'$.  If we take the derivative one more time, then we end up with the sequence $\Delta^{n+1}s'$, which has rank $\omega\beta'$, and it follows that $\Delta^n s'.0$ has rank $\omega\beta'+1$.  Therefore, $s$ has rank $\omega\beta'+n+1$.

        Now suppose that $\mu$ is a limit ordinal and that $s$ has length $\mu$.  If we take some proper prefix $t\pprefix s$ of length $\delta<\mu$, then $t$ is weakly increasing, so by the induction hypothesis it has rank at most $\delta+m$ for some $m$.  $\delta+m<\mu$ and $t$ was arbitrary, so it follows that $s\in R_\mu$; i.e., that $\rank(s)\le\mu$.

        We claim that $\rank(s)=\mu$.  Indeed, suppose that $s\in R_\delta$ for some $\delta<\mu$.  Let $u$ be the prefix of $s$ of length $\delta+1$.  By the induction hypothesis, $\rank(u)\ge\delta+1>\rank(s)$, which is a contradiction, since $u\prefix s$.  \qedhere
    \end{enumerate}
  \end{proof}
\end{lemma}

We can now give our classification result:

\begin{theorem}
  Let $s\in\omega^{*<\alpha}$ and let $\mu<\alpha$ be a limit ordinal.  Then $\rank(s)\ge\mu$ if and only if $s$ has a weakly increasing subsequence of length $\mu$.

  For $n\ge 1$, $\rank(s)\ge\mu+n$ if and only if $s$ has a subsequence of the form $tm$, where $t$ is weakly increasing of length $\mu$ and $m\ge n-1$ is a single term.

  \begin{proof}
    \emph{If: } Suppose $t$ is a weakly increasing subsequence of length $\mu$.  By Lemma \ref{WeaklyIncreasingLemma}, $t$ has rank $\mu$, so by Proposition \ref{RankProposition}, $s$ has rank at least $\mu$.

    Write $s=s'u$, where $t$ is a subsequence of $s'$ and $u$ contains some term $m\ge n-1$.  Then $s'$ has rank at least $\mu$.  Then $\Delta^{n-1} s'$ has rank at least $\mu$ and $\Delta^{n-1}u\ne\emptyplay$, since $u$ contains the term $m$.  Let $x$ be the first term of $\Delta^{n-1}u$.  Then $\Delta^{n-1}s'.x$ is a subsequence of $\Delta^{n-1}s$, and it must have rank at least $\mu+1$ (since it is a successor play and contains $\Delta^{n-1}s'$ as a subsequence.  Therefore, $\Delta^{n-1}s$ has rank at least $\mu+1$ and so $s$ has rank at least $\mu+1+(n-1)=\mu+n$.

    \emph{Only if: } We prove by induction on $\delta$ that if $s\in\omega^{*<\alpha}$ has rank $\delta$ then $s$ satisfies the appropriate condition above.  First, let $\mu$ be a limit ordinal and suppose that $s$ has rank $\mu+1$.  We want to show that $s$ has a weakly increasing subsequence of length $\mu$ that is not cofinal in $s$.

    Since $s$ has rank $\mu+1$, $\Delta s$ has rank $\mu$, so contains a weakly increasing subsequence of length $\mu$, by the induction hypothesis.  This sequence lifts to a weakly increasing subsequence $u$ of $s$.  If $s$ has successor length, then $u$ is not cofinal in $s$, so we win.

    Otherwise, suppose that $s$ has limiting length.  Then there must be some proper prefix $t\pprefix s$ of rank $\mu$; otherwise, $s\in R_\mu$, which is a contradiction.  Then by the induction hypothesis we can find a weakly increasing subsequence of $t$ of length $\mu$, and this subsequence is not cofinal in $s$.

    Now let $n\ge1\in\omega$ and suppose that $s$ has rank $\mu+n$.  If we apply the derivative $n-1$ times to $s$ then we end up with a sequence of rank $\mu+1$.  By the previous part, this sequence must have a subsequence of the form $u.m$, where $u$ is weakly increasing of length $\mu$ and $m$ is a single term.  This sequence lifts to a subsequence $\hat u.(m+n-1)$ of $s$, where $\hat u$ is still weakly increasing.

    Lastly, suppose that $s$ has rank $\mu$, for $\mu$ a limit ordinal.  It follows that $s$ has limiting length.

    For each limit ordinal $\lambda<\mu$, let $t_\lambda$ be the shortest prefix of $s$ of rank at least $\lambda$.  Since $s$ has rank $\mu$, $t_\lambda$ exists for each $\lambda$.  By the induction hypothesis, each $t_\lambda$ has some weakly increasing subsequence of length $\lambda$.  We will prove something stronger: we will inductively construct for each $\lambda$ a weakly increasing subsequence $u_\lambda$ of $t_\lambda$ such that $u_\lambda$ has length $\lambda$ and such that if $\lambda'\le\lambda$ then $u_{\lambda'}\prefix u_\lambda$.

    Suppose we have constructed $u_\lambda$.  Note that the rank of $t_\lambda$ must be less than $\lambda+\omega$; otherwise, $t_\lambda$ would have to have some prefix of length $\lambda+m$ for some $m$, contradicting minimality of $t_\lambda$.  Therefore, $t_\lambda$ is a proper prefix of $t_{\lambda+\omega}$, so we write $t_{\lambda+\omega}=t_\lambda.v$ for some sequence $v$.

    We claim that for all $N\in\omega$ there is some $n\ge N$ occurring in the sequence $v$.  Indeed, if $N$ is such that there is no $n\ge N$ occurring in $v$, then we may take the derivative of $u_{\lambda+\omega}$ finitely many times and end up with a sequence of rank $\lambda$, which is a contradiction.  We construct $u_{\lambda+\omega}$ as follows: let $n_0$ be the least value occurring in the sequence $v$ and let $a_0$ be the earliest occurrence of $n_0$ in the sequence $v$.  Now let $N$ be the largest value that occurs (not necessarily strictly) earlier than $a_0$ in the sequence $v$.  We know that there is some $n\ge N$ occurring in $v$; let $n_1$ be the least such $n$.  Certainly, $n_1$ may only occur later in the sequence $v$ than $a_0$, so let $a_1$ be the first occurrence of $n_1$ in the sequence $v$.  Continuing in this way, we build up an increasing subsequence $a_0 a_1 a_2 \dots$ of $v$.  We set
    \[
      u_{\lambda+\omega} = u_\lambda a_0 a_1 a_2 \dots
      \]
    Then certainly $u_\lambda$ is a prefix of $u_{\lambda+\omega}$.

    Now suppose that $\mu$ is a multiple of $\omega^2$ and we have constructed the sequences $u_\lambda$ for all limit ordinals $\lambda<\mu$.  Then the sequences $u_\lambda$ glue to give a sequence $u_\mu$.  We need to check that $u_\mu$ is a subsequence of $t_\mu$.  Indeed, if $u_\mu$ is not a subsequence of $t_\mu$ then there is some earliest term $b$ in the sequence $u_\mu$ such that $b$ is not a term of $t_\mu$.  But then there is some $\lambda'<\mu$ such that $u_{\lambda'}$ is not a subsequence of $t_\mu$, which is a contradiction.

    This completes the induction.

    To complete the argument, suppose that $\mu$ is a limit ordinal and that $\rank(s)\ge\mu$.  Write $\gamma=\rank(s)$.  We may write $\gamma=\lambda+m$ for some $m$, where $\lambda\ge\mu$ is a limit ordinal.  Then $s$ has a weakly increasing subsequence of length $\lambda$, and we may take a prefix of this subsequence to obtain a weakly increasing subsequence of $s$ of length $\mu$.

    Now suppose that $\rank(s)\ge\mu+n$.  We may write $\rank(s) = \lambda+m$, where $\lambda$ is a limit ordinal and either $\lambda>\mu$ or $\lambda=\mu$ and $m\ge n$.  In the first case, $s$ has a weakly increasing sequence of length $\lambda$; we may then take a prefix of length $\mu+\omega$ of this sequence and note that this sequence must have a subsequence of the form $up$, for some $p\ge (n-1)$.

    In the second case, $s$ has a subsequence of the form $uq$, where $u$ is weakly increasing of length $\mu$ and $q\ge m-1\ge n-1$.  
  \end{proof}
\end{theorem}

A consequence of this classification is that if $s\in\omega^{*<\alpha}$, then $\rank(s)<\length(s)+\omega$.  Furthermore, if $\mu$ is a limit ordinal and $\length(s)<\mu$, then $\rank(s)<\mu$.  We will see that this is the reason why the final sequence for $A\sequoid\blank$ converges so quickly for $\omega$- and $(\omega+1)$-games: there are no sequences of finite length with infinite rank, and every sequence of length $\le \omega+1$ has rank less than $\omega+\omega$.

\subsection{Classification of the final sequence for $A\sequoid\protect\blank$}

Let $\G(\alpha)$ be a category of games, and let $A$ be an object of $\G(\alpha)$.  We have $M_{\oc A}=M_A\times\omega$, so there is a natural map $\pr_2\from M_{\oc A}\to \omega$.  If $s$ is a play in $\oc A$, then we get an associated sequence of natural numbers $\hat s\from\length(s)\to\omega$ given by\[
  \hat s = \pr_2 \circ s
  \]

Given an ordinal $\delta$, we define a game $(\oc A)_\delta=(M_{\oc A},\lambda_{\oc A}, \zeta_{\oc A}, P_{\oc A,\delta})$, where $P_{\oc A,\delta}$ is the subset of $P_{\oc A}$ given by:
\[
  P_{\oc A,\delta} = \{s\in P_{\oc A}\suchthat \rank(\hat s)\le\delta\}
  \]
As we have seen, this set is prefix-closed, so $(\oc A)_\delta$ is a well formed game.

For an ordinal $\delta$, let $A^{\sequoid\delta}$ denote term $\delta$ in the final sequence for $A\sequoid\blank$ (i.e., $A^{\sequoid\delta}=\FS_{A\sequoid\blank}(\delta)$).

Our main result is as follows:

\begin{theorem}
  \label{MainFinalSequenceResult}
  \[
    A^{\sequoid\delta}\cong (\oc A)_\delta
    \]
  Given ordinals $\gamma\le\delta$, the arrow $A^{\sequoid\delta}\to A^{\sequoid\gamma}$ in the final sequence is given by the copycat morphism $(\oc A)_\delta\to(\oc A)_\gamma$ induced by the inclusion $P_{\oc A, \gamma}\hookrightarrow P_{\oc A, \delta}$.  
\end{theorem}

As a sanity check, we observe that if $n<\omega$ then the sequences of rank $n$ are precisely the sequences that only involve the terms $0,\dots,n-1$.  Therefore, it is easy to see that $A^{\sequoid n}\cong(\oc A)_n$ for all $n<\omega$.

\begin{proof}[Proof of Theorem \ref{MainFinalSequenceResult}]
  If $s\in P_{\oc A}$ then $\hat s$ has rank $0$ if and only if $s=\emptyplay$.  Therefore, it is easy to see that $A^{\sequoid 0}=I\cong(\oc A)_0$.

  Consider the game $A\sequoid (\oc A)_\delta$.  If $s$ is a play in this game, then we may identify $s$ with a subsequence of $\oc A$ by labelling the copy of $s$ on the left as $A_0$ and increasing the index by one for each copy of $A$ on the right.  In other words:
  \[
    \Delta\hat s = ({s\vert_{(\oc_A)_\delta}})\hat{}
    \]
  By the induction hypothesis, $({s\vert_{(\oc_A)_\delta}})\hat{}$ has rank at most $\delta$ and therefore $\hat s$ has rank at most $\delta+1$.

  Conversely, if $s$ is a sequence in $P_{\oc A}$ and $\Delta\hat s$ has rank at most $\delta$, it means that $s\vert_{A_2,A_3,\dots}\in P_{(\oc_A)_\delta}$ and so $s$ is a play in $A\sequoid(\oc A)_\delta$.

  We check the assertion about the morphisms in the category.  There is a unique morphism $(\oc A)_\delta\to I$ for each $\delta$, so there is nothing to check there.  Suppose $\mu<\alpha$ is a limit ordinal.  By induction, $A^{\sequoid\mu}\cong (\oc_A)_\mu$ and the morphisms $A^{\sequoid\mu}\to A^{\sequoid\delta}$ for $\delta<\mu$ are copycat morphisms induced by the inclusion $P_{\oc A, \delta}\hookrightarrow P_{\oc A,\mu}$.  If we apply the functor $A\sequoid\blank$ to this cone, then we get a cone from $A\sequoid A^{\sequoid \mu}$ over the diagram formed by $A^{\sequoid\delta}$ for $\delta<\mu$.  Our argument above also tells us that all the arrows in this new diagram are induced by inclusion functions, and therefore the morphism
  \[
    A^{\sequoid\mu}\to A\sequoid A^{\sequoid\mu}
    \]
  induced by the inclusion $P_{\oc A,\mu}\hookrightarrow P_{\oc A, \mu+1}$ commutes with both cones, so it is the morphism $A^{\sequoid\mu+1}\to A^{\sequoid\mu}$ in our diagram.  Under the isomorphism $A^{\sequoid\delta}\cong (\oc A)_\delta$ that we have constructed already, the functor $A\sequoid\blank$ sends inclusion morphisms to inclusion morphisms, so by induction the morphism $A^{\sequoid\mu+n+1}\to A^{\sequoid\mu+n}$ is also induced by an inclusion map.

  It remains to deal with the limiting case.  Let $\mu$ be a limit ordinal.  Then $(\oc A)_\mu$ admits a cone over the diagram given by the $A^{\sequoid \delta}$ for $\delta<\mu$, again given by copycat morphisms induced by inclusion maps.  Let $B$ be an object of $\G(\alpha)$ and suppose that we have a cone
  \[
    \left(\map{\sigma_\delta}{B}{A^{\sequoid\delta}}\right)_{\delta<\mu}
    \]
  over the diagram given by the $A^{\sequoid\delta}$ and the inclusion morphisms between them.  This means that if we identify $A^{\sequoid\delta}$ with $(\oc A)_\delta$ then the strategies $\sigma_\delta$ form a chain.  Then (under this identification) we set
  \[
    \sigma = \textrm{limit closure of }\bigcup_{\delta<\mu}\sigma_\delta
    \]
  Since $B$ satisfies the limit condition, we do not introduce any extra plays when we take the limit closure and so $\sigma$ is a subset of $P_{B\implies (\oc A)_\mu}$, by the definition of a sequence of rank $\mu$.  $\sigma$ is limit-closed, so it is a strategy, since the $\sigma_\delta$ are.  It is clear that composing $\sigma$ with the inclusion morphism $(\oc A)_\mu\to(\oc A)_\delta$ gives $\sigma_\delta$, so this is a morphism of cones.

  Now suppose that $\tau\from B\to(\oc A)_\mu$ also gives rise to a morphism of cones.  By applying the functor into $\Rel$, we can check that if we compose $\tau$ with the inclusion morphism $(\oc A)_\mu\to(\oc A)_\delta$ then we get the strategy $\tau\cap P_{B\implies(\oc A)_\delta}$.  Therefore, for all $\delta<\mu$:
  \[
    \tau \cap P_{B\implies(\oc A)_\delta}=\sigma_\delta
    \]
  Since $\tau$ satisfies the limit condition, it is clear that $\sigma\subset\tau$.  Conversely, suppose that $s\in\tau$.  Since $\tau\subset P_{B\implies(\oc A)_\mu}$, $s\vert_{(\oc A)_\mu}$ must have rank at most $\mu$.  If $s\vert_{(\oc A)_\mu}$ has rank $\delta<\mu$, it follows that $s\in\sigma_\delta\subset\sigma$.  If instead $s\vert_{(\oc A)_\mu}$ has rank $\mu$ then it must be a limiting play, so by the limit condition on $\sigma$ it suffices to show that all the proper prefixes of $s$ are contained in $\sigma$.  Since $s\vert_{(\oc A)_\mu}$ has rank $\mu$, all its proper prefixes have rank less than $\mu$ and are therefore contained in $\sigma$ by the argument we have just used.

  It follows that $\sigma=\tau$, and therefore that the limiting cone $A^{\sequoid\mu}$ is indeed given by the game $(\oc A)_\mu$, together with the morphisms induced by inclusion functions.  This completes the induction.  
\end{proof}

As a consequence of this classification, we have:

\begin{corollary}
  Let $\alpha=\omega^\beta$ for some $\beta$.  If $A$ is an object of $\G(\alpha)$, then the final sequence for the functor $A\sequoid\blank\from\G(\alpha)\to\G(\alpha)$ stabilizes by $\alpha$.

  Moreover, this bound is tight: there exists some completely negative $\alpha$-game $A$ such that the final sequence for $A\sequoid\blank$ does not stabilize before $\alpha$.  
  \begin{proof}
    We want to show that the morphism
    \[
      A^{\sequoid\alpha+1}\to A^{\sequoid\alpha}
      \]
    in the final sequence for $A\sequoid\blank$ is an isomorphism.  If we make the identification given by our classification result, then we may identify this morphism with the copycat morphism $(\oc A)_{\alpha+1}\to(\oc A)_\alpha$ induced by the inclusion function
    \[
      P_{\oc A,\alpha}\hookrightarrow P_{\oc A,\alpha+1}
      \]
    But we have already shown that any sequence of length less than $\alpha$ must have rank less than $\alpha$ and therefore this inclusion map is the identity.  It follows that the morphism $(\oc A)_{\alpha+1}\to(\oc A)_\alpha$ is the identity and so the morphism above is indeed an isomorphism.

    To show tightness of the bound, it suffices to exhibit a game $A$ such that there sequences $s\in\oc A$ of length less than $\alpha$ and arbitrarily high rank.  We take $A$ to be the $\alpha$-game $\st$ where there is a unique legal play $qaqa\dots$ of any length $\delta<\alpha$.  Then for any $\delta<\alpha$ we may construct a play $s\in\oc A$ of the form
    \[
      q_1a_1q_2a_2\dots\;q_1a_1q_2a_2\dots\;\dots\dots
      \]
    such that $\hat{s}$ has the canonical sequence $c_{\delta}$ as a subsequence.  Therefore, $\hat{s}$ has rank at least $\delta$.  
  \end{proof}
\end{corollary}

\begin{note}
  This result gives an alternative proof that $\oc A$ is the final coalgebra for the functor $A\sequoid\blank$.

  Although we have not developed the theory of win-games of length $\omega^\beta+1$, this result also sheds some light on why the final sequence for $\omega+1$-games stabilizes at $\omega+\omega$: this time, we use the fact that any sequence of length at most $\omega+1$ must have rank at most $\omega+\omega$.  
\end{note}

\section{Further Directions}

There are still a few areas in the current direction that need working out, such as the construction of transfinite win-games with winning strategies.  I also plan to examine the internal logic of these categories of transfinite games to characterize them logically, and to investigate the logical meaning of convergence of the final sequence.  Another direction is to see what our classification of the final sequence tells us about the exponential $\oc A$, and whether it tells us anything about the $\omega$-games case.

The paper \cite{MelliesCofCommCom} gives category-theoretic conditions under which the final sequence for $A\sequoid\blank$ always terminates at $\omega$ (though it is not stated in quite that language).  I plan to examine this work to see which of these conditions fail for categories of transfinite games.  There are other category-theoretic questions to ask about the behaviour of the final sequence.  It is known, for example, that the final sequence for a finitary endofunctor on $\Set$ must always terminate by $\omega+\omega$ \cite{finalseq} and there are other results generalizing this.  Although our endofunctor is not a functor on $\Set$, it can be turned into a functor on $\Set$ if we restrict to copycat strategies.  It would be worthwhile to view the results of this research under that lens.

As a longer-term piece of research: we had a number of mathematical problems caused by the sequential nature of the games we studied, and we were forced to restrict our attention to negative games (though we found a possible way of getting around that).  An alternative approach, studied by Abramsky and Melli\`{e}s \cite{AMConcurrent}, is to study \emph{concurrent games}.  These games, where the players $O$ and $P$ move concurrently, rather than sequentially, avoid many of the problems present with sequential games; indeed, the authors of \cite{AMConcurrent} obtain a full completeness result for MALL using these concurrent games.  It is not immediately obvious how to apply the research in this report to concurrent games, nor how to develop the sequoid operator in a concurrent setting.  One possible approach to the latter problem is to observe that in our category of games we have a natural isomorphism
\[
  \G_s(A\sequoid B,C)\cong\G_s(A,B\implies C)
  \]
(where $\G_s$ is a category of games and strict strategies) so that $\blank\sequoid B$ is something like a left adjoint to the functor $B\implies\blank$ in the strict subcategory.  In a general cpo-enriched monoidal category $\C$, we can say that a morphism $f\from X\to Y$ is \emph{strict} if the composition
\[
  I\xrightarrow{\emptyplay_X}X\xrightarrow{f}Y = \emptyplay_Y
  \]
where $\emptyplay_X$ and $\emptyplay_Y$ are the bottom elements of $\C(I,X)$ and $\C(I,Y)$ respectively.

The eventual goal here will be to develop a sequoidal category of concurrent games and to characterize its internal logic.  A further direction in this area is to mimic the results in this report in a concurrent setting.

A surprising direction of research is given by the material in Sections \ref{TransSMCCSex} through \ref{ImpliesCnSex}, in particular trying to generalize the construction in Section \ref{DigressionSex} to other categories.  The situation here is fairly non-standard: we a category (of completely negative games), but we also have all the non-completely negative games that are not objects of the category but still admit morphisms into them.  We dealt with these objects by using a construction that mimics the traditional slice categories from category theory, but I would be interested to pursue this further and try to develop it in a more general category-theoretic framework.  It might be worthwhile to study these questions in the context of finitary games, particularly as $A^{\cn}$ has a presentation there in terms of the linear connectives (specifically, $N^{\cn}=N$ if $N$ is negative and $P^{\cn}=\bneggame{P}\implies\bot$ if $P$ is positive).

In Section \ref{DigressionSex} we constructed a category $\tilde{\G}$ whose objects are arbitrary (not necessarily completely negative) games.  Even in the finitary setting, this poses an obvious question: is this category  $*$-autonomous and can we use it to model fragments of linear logic that we could not model in the completely negative case?  Of course, there are other obstacles to doing this besides the sign of the games in our category, and the fact that $\tilde{\G}$ is equivalent as a category to $\G$ casts some doubt on whether this is possible, but I would like to explore this direction further.

Another thing that is worth looking into is the effect that removing the limiting condition might have on these games.  The limiting condition played no great role in our construction of $\G(\alpha)$, though it was crucial in our work on the final sequence.  Removing the limiting condition might allow certain forms of unbounded non-determinism to be modelled.  The work done in \cite{LairdOrdinalGames} is connected to this, and it will be instructive to compare the research in this report with Laird's earlier work on transfinite game semantics.

Lastly, there is further technical research to be done into sequoidal categories, such as finding appropriate conditions under which the sequoidal exponential gives rise to a linear exponential comonad or cofree commutative comonoid.

\appendix
\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}

\section{Proofs}

This Appendix contains proofs from the early sections that were omitted from the main body of the text to avoid breaking up the flow.

\subsection{Proof of Proposition \ref{nice-negative-games}}
\label{nice-negative-games-proof}

We proceed by induction on the length $n$ of $s$.  If $n=0$ then $s=\emptyplay$ and so $\zeta_A(s\vert_A)=\zeta_A(\emptyplay)=P$ and similarly for $B$, since $A,B$ are negative games.  Now suppose that $n>0$ - so $s=tm$ for some $t\in P_{A\tensor B},m\in M_{A\tensor B}$.  By induction, either $t\vert_A=P$ or $t\vert_B=P$, so there are three cases:
\begin{description}
  \item[Case 1:] $\zeta_A(t\vert_A)=P$ and $\zeta_B(t\vert_B)=P$. Then either $tm\vert_A=t\vert_A$ (if $m$ is a $B$-move) or $tm\vert_B=t\vert_B$ (if $m$ is an $A$-move).  This proves part (i).  For part (ii), note that in this case we have $\zeta_{A\tensor B}(t)=P$, so $\zeta_{A\tensor B}(tm)=O$, since $tm$ is alternating.  If $m$ is an $A$-move, it means that $\zeta_B(tm\vert_B)=\zeta_B(t\vert_B)=P$, so we must have $\zeta_A(tm\vert_A)=O$ by the definition of $\zeta_{A\tensor B}$.  Then
    \[
      \lambda_{A\tensor B}(m)=\lambda_A(m)=\zeta_A(t\vert_Am)=O=\zeta_{A\tensor B}(tm)
      \]
    If $m$ is a $B$-move, the argument is similar.
  \item[Case 2:] $\zeta_A(t\vert_A)=P$ and $\zeta_B(t\vert_B)=O$.  For part (i), it will suffice to show that $m$ is a $B$-move - so $tm\vert_A=t\vert_A$.  Indeed, we have $\zeta_{A\tensor B}(t)=O$, so $\zeta_{A\tensor B}(tm)=P$, since $tm$ is alternating with respect to $\zeta_{A\tensor B}$.  In particular, $\zeta_B(tm\vert_B)=P$, so we must have $tm\vert_B\ne t\vert_B$ and therefore $m$ is a $B$-move.  For part (ii), we have:
    \begin{gather*}
      \lambda_{A\tensor B}(m)=\lambda_B(m)=\zeta_B(t\vert_Bm)=\neg\zeta_B(t\vert_B)=\neg O = P \\
      \zeta_{A\tensor B}(tm)=\neg\zeta_{A\tensor B}(t)=t = \neg O = P = \lambda_{A\tensor B}
    \end{gather*}
  \item[Case 3:] $\zeta_A(t\vert_A)=O$ and $\zeta_B(t\vert_B)=P$.  Similar to Case 2.
\end{description}

Finally, note that the $\tensor$ result implies the $\implies$ result after writing $A\implies B=\neggame{A}\parr B = \neggame{(A\tensor \neggame{B})}$.

\subsection{Proof of Proposition \ref{alternatingsequenceslemma}}
\label{alternatingsequenceslemmaproof}

By symmetry, it will suffice to prove that if $\s\vert_{A,B}\in P_{A\implies B}$ and $\s\vert_{B,C}\in P_{B\implies C}$ then $\s\vert_{A,C}\in P_{A\implies C}$.  If $X,Y$ are negative games, then sequences $t\in P_{X\implies Y}$ are specified by the following properties - $t\vert_X\in P_X$, $t\vert_Y\in P_Y$, if $t$ has even length, then $\zeta_{X\implies Y}(t)=P$ and if $t$ has odd length then $\zeta_{X\implies Y}(t)=O$.  We need to show that these properties holds if $X=A$, $Y=C$ and $t=\s\vert_{A,C}$.

Certainly, $\s\vert_{A,C}\vert_A=\s\vert_A=\s\vert_{A,B}\vert_A\in P_A$ and similarly $\s\vert_{A,C}\vert_C\in P_C$.

If $\s\vert_{A,C}$ has even length, it means that the lengths of $\s\vert_A$ and $\s\vert_C$ have the same parity, and therefore that the lengths of $\s\vert_{A,B}$ and $\s\vert_{B,C}$ have the same parity.  Since $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, it follows that $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{B\implies C}(\s\vert_{B,C})$.  If $\zeta_B(\s\vert_B)=P$ then $\zeta_{A\implies B}(\s\vert_{A,B})=P$ and if $\zeta_B(\s\vert_B)=O$ then $\zeta_{B\implies C}(\s\vert_{B,C})=P$, so we must have $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{B\implies C}(\s\vert_{B,C})=P$.  By transitivity of $\Rightarrow$, it follows that $\zeta_{A\implies C}(\s\vert_{A,C})=P$.

If $\s\vert_{A,C}$ has odd length, it means that the lengths of $\s\vert_A$ and $\s\vert_C$ has opposite parities and therefore that the lengths of $\s\vert_{A,B}$ and $\s\vert_{B,C}$ have opposite parities.  So it follows that $\zeta_{A\implies B}(\s\vert_{A,B})=\neg\zeta_{B\implies C}(\s\vert_{B,C})$.  Suppose that $\zeta_{A\implies B}(\s\vert_{A,B})=O$.  Then $\zeta_A(\s\vert_A)=P$ and $\zeta_B(\s\vert_B)=O$.  By Proposition \ref{nice-negative-games} above applied to $\s\vert_{B,C}$, we must have $\zeta_C(\s\vert_C)=O$ and therefore $\zeta_{A\implies C}(\s\vert_{A,C})=(P\Rightarrow O)=O$.

If instead we have $\zeta_{B\implies C}(\s\vert_{B,C})=O$, then $\zeta_B(\s\vert_B)=P$ and $\zeta_C(\s\vert_C)=O$.  By Proposition \ref{nice-negative-games} applied to $\s\vert_{A,B}$, we must have $\zeta_A(\s\vert_A)=P$ and so $\zeta_{A\implies C}(\s\vert_{A,C})=(P\Rightarrow O) = O$.

\subsection{Proof of Proposition \ref{HylandSchalkFaithful}, Proposition \ref{TransHylandSchalkFaithful}}
\label{HylandSchalkFaithfulProof}

Our proof is essentially that given in \cite{CalderonMcCusker}.  Suppose for a contradiction that $\sigma\ne\sigma'$, so without loss of generality there is some $P$-position $s\in\sigma\setminus\sigma'$ (using the definition of a strategy).  By hypothesis, there is some $s'\in\sigma'$ such that $s'\vert_A=s\vert_A$ and $s'\vert_B=s\vert_B$.  Clearly, $s\ne s'$, since $s\not\in\sigma'$, so let $r\prefix s$ be the largest common prefix of $s$ and $s'$.  We therefore have $rx\prefix s,ry\prefix s'$, where $x,y\in M_{A\implies B}$ and $x\ne y$.

Since $s\vert_A=s'\vert_A$ and $s\vert_B=s'\vert_B$, the moves $x$ and $y$ must take place in different games (otherwise we would be forced to have $x=y$).  They are therefore both $P$-moves.  Suppose without loss of generality that $x$ is an $A$-move and that $y$ is a $B$-move.  By hypothesis, there is some $P$-position $t\in\sigma$ such that $t\vert_A=ry\vert_A=r\vert_A$ and $t\vert_B=ry\vert_B=r\vert_By$.

Now clearly $rx\ne t$ (since their restrictions to $A$ and $B$ are different).  Let $q\prefix rx, t$ be their largest common prefix; then we have $qu\prefix rx, qv\prefix t$ for some $u\ne v$.  But now since $qu, qv\in\sigma$, $u$ and $v$ must both be $O$-moves, so they must be contained in the same component.  But this is impossible: if they are both $A$-moves then we have $q\vert_Au\prefix r\vert_A x$ and $q\vert_Av\prefix r\vert_A$, so $u=v$ and if they are both $B$-moves then we have $q\vert_Bu\prefix r\vert_B$ and $q\vert_Bv\prefix r\vert_By$, so $u=v$ again.  This is a contradiction.

\subsection{Proof of Lemma \ref{LiftingLemma}}
\label{LiftingLemmaProof}

We prove this by induction on $k$.  There is a unique sequence of length $0$, namely the empty sequence, and its $A$- and $C$-components are both empty, so are prefixes of $s$ and $t$.

Suppose now that $k=1$.  We make the observation that if $a$ is an $O$-move in $A$ and if $b$ is an $O$-move in $B$ then $a$ is a $P$-move in $A\implies B$ and $b$ is a $P$-move in $B\implies C$.  Since the starting move in $A\implies B$ or $B\implies C$ must be an $O$-move in both its component game and in the game as a whole, we see that any sequence in $\sigma\|\tau$ must begin with a move in $C$.  So we have $\s^1=c$, for some $C$-move $c$, and the condition that $\s^1\vert_C\prefix t$ means that $c$ must be the first move in $t$, which is always a move from $C$.  We have $\s^1\vert_A=\emptyplay\prefix s\vert_A$ and $\s^1\vert_B=\emptyplay\prefix s\vert_B$, as desired.

Now suppose that we have constructed the sequence $\s^k$ for some $k$ such that $1\le k<n$.  We seek a sequence $\s^{k+1}\in \sigma\|\tau$ of length $k+1$ such that $\s^{k+1}\vert_A\prefix s$ and $\s^{k+1}\vert_C\prefix t$.  If we write $\s'$ for the sequence obtained by removing the last move in $\s^{k+1}$, it is clear that $\s'\vert_A\prefix s$ and $\s'\vert_C\prefix t$, so $\s'=\s^k$ by uniqueness.  Therefore, $\s^{k+1}$ is of the form $\s^kx$, for some move $x\in M_A\cprd M_B\cprd M_C$.

Write $\s^k=\s''y$, where $y$ is the last move in $\s^k$.  Our move $x$ will depend on which game $y$ is played on as follows:

\begin{itemize}
  \item Suppose $y$ is a move in $A$ or an $O$-move in $B$.  By induction, $\s''y\vert_{A,B}$ is a prefix of $s$ ending in $y$.  We claim that it is a proper prefix.

    Indeed, let $b$ be the last $B$-move occurring in $\s''y$ (since play in $A\implies B$ starts with a $B$-move, there must be such a move).  If $b=y$, then $b$ is an $O$-move in $A\implies B$.  Otherwise, $y$ must be a move in $A$, and then $b$ is again an $O$-move in $A\implies B$, since player $P$ switches games.  Therefore, $b$ is a $P$-move in $B\implies C$.  Now $\s''y\vert_B$ is a prefix of $t$ ending in $b$.  Since $b$ is a $P$-move in $B\implies C$, it may only be followed in $B\implies C$ by another move from $B$, so there are two possibilities: either $\s''y\vert_{B,C}=t$ or there is some other $B$-move $b'$ that occurs later than $b$ in the sequence $t$.  In the first case, $\s''y\vert_{A,B}$ must be a proper prefix of $s$ by length considerations:
    \begin{align*}
      \length(\s''y\vert_{A,B}) & = \length(\s''y) - \length(\s''y\vert_C) \\
        & = \length(\s''y) - \length(t\vert_C) \\
        & = k - \length(t\vert_C) < n - \length(t\vert_C) = \length(s)
    \end{align*}
    while in the second case $\s''y\vert_B$ must be a proper prefix of $t\vert_B=s\vert_B$, and so $\s''y\vert_{A,B}$ must be a proper prefix of $s$.

    Therefore, we have $\s''y\vert_{A,B}x\prefix s$ for some move $x\in M_A\cprd M_B$.  If $x$ is an $A$-move then $\s''yx\vert_{B,C}=\s''y\vert_{B,C}\prefix t$, as desired.  If $x$ is a move in $B$, then it must be a $P$-move in $A\implies B$ (since $y$ is either a move in $A$ or an $O$-move in $B$), so it is an $O$-move in $B\implies C$.  Since $s\vert_B=t\vert_B$, we must have $\s''yx\vert_B\prefix t\vert_B$, and so $y$ must be a $P$-move in $B\implies C$, and should therefore be followed by another move in $B$, which must be $x$.  Therefore, $\s''yx\vert_{B,C}\prefix t$.

    For uniqueness, suppose that $\s''yz\in\sigma\|\tau$ is such that $\s''yz\vert_A\prefix s\vert_A$ and $\s''yz\vert_C\prefix t\vert_C$.  As before, let $b$ be the last $B$-move occurring in $\s''y$; we have already shown that $b$ must be a $P$-move in $B\implies C$, and it follows that it must be the last move occurring in $\s''y\vert_{B,C}$ (since it can only be followed by another $B$-move).  Suppose that $z\in M_B\cprd M_C$.  Then $\s''yz\vert_{B,C}=\s''y\vert_{B,C}z$; since the last move in $\s''y\vert_{B,C}$ is $b$, this means that $z$ must be an $O$-move in $B$.  So $z$ is either an $O$-move in $B$ or a move in $A$.

    If $y$ was an $O$-move in $A$, then $y$ is a $P$-move in $A\implies B$, so it must be followed in $A\implies B$ by another move from $A$.  Then the condition that $\s''yz\vert_A\prefix s\vert_A$ tells us that $z=x$.  If instead $y$ was a $P$-move in $A$ or a move in $B$ then $y$ is an $O$-move in $A\implies B$; now, since we have $\s''y\vert_{A,B}z,\s''y\vert_{A,B}x\in\sigma$, it must be the case that $x=z$ by the definition of a strategy.

  \item If instead $y$ is a move in $C$ or a $P$-move in $B$, we use a symmetrical argument, choosing $x$ to be the next move along in $t$.  We need to take a little extra care here when we talk about the last $B$-move in $\s''y$; there may in fact be no $B$-moves in $\s''y$.  Since any play in $A\implies B$ must begin with a $B$-move, this only happens when $\s''y$ is entirely made up of $C$-moves.  In this case, it is not difficult to show that $\s''y\vert_{B,C}$ is a proper prefix of $t$ by length considerations.  \qedhere
\end{itemize}

\subsection{Proof of Proposition \ref{CompWinningIsWinning}}
\label{CompWinningIsWinningProof}

First, we want to show that $\comp\tau\sigma$ is a total strategy.  Let $s\in\comp\tau\sigma$ be an $O$-position; then we have some $\s\in\sigma\|\tau$ with $\s\vert_{A,C}=s$.

We claim that there is a maximal such $\s$.  By Lemma \ref{LiftingLemma}, $\s$ is determined by its length, and so the only way that there could not be a maximal such $\s$ is if there is some infinite sequence $\S\in(M_A\cprd M_B\cprd M_C)^\omega$ with $\S\vert_{A,B}\in\sigma\cup\sigma^\omega$, $\S\vert_{B,C}\in\tau\cup\tau^\omega$ and $\S\vert_{A,C}=s$.  Since $\S$ has some finite prefix $\s$ with $\s\vert_{A,C}=s$, $\S\vert_A$ and $\S\vert_C$ must both be finite, so they are $O$-plays in the games $A\implies B$ and $B\implies C$ respectively.

Now $\S\vert_B$ is infinite.  If $W_B(\S\vert_B)=O$, then $W_{A\implies B}(\S\vert_{A,B})=O$, contradicting the fact that $\sigma$ is a winning strategy.  Symmetrically, if $W_B(\S\vert_B)=P$, then $W_{B\implies C}(\S\vert_{B,C})=O$, contradicting the fact that $\tau$ is a winning strategy.  We have a contradiction in either case, so if $\sigma$ and $\tau$ are indeed winning strategies, there must be a maximal (finite) $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.

The argument from Proposition \ref{BoundedTotalComposition} now applies, showing that $sx\in\comp\tau\sigma$ for some $P$-move $x$.

Lastly, we want to show that any infinite play in $\comp\tau\sigma$ is $P$-winning.  Suppose $s$ is some infinite play in $\comp\tau\sigma$.  For each finite prefix $t\prefix s$ there is some $\t\in\sigma\|\tau$ with $\t\vert_{A,C}=t$, and by Lemma \ref{LiftingLemma}, we have $\t'\prefix\t$ if $t'\prefix t$.  Therefore, these $\t$ glue to give an infinite sequence $\s\in(M_A\cprd M_B\cprd M_C)^\omega$ such that $\s\vert_{A,B}\in\sigma^\omega$ and $\s\vert_{B,C}\in\tau^\omega$.  We claim that $W_{A\implies B}^*(\s\vert_{A,B})=W_{B\implies C}^*(\s\vert_{B,C})=P$ - then it follows that $W_{A\implies C}^*(\s\vert_{A,C})=P$ by transitivity of $\Rightarrow$.  If $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both infinite, then this is automatically true, since $\sigma$ and $\tau$ are winning strategies.  Otherwise, one of them must be infinite and the other finite.

Suppose that $\s\vert_{A,B}$ is finite.  Let $\t$ be the shortest finite prefix of $\s$ with $\t\vert_{A,B}=\s\vert_{A,B}$; then we have $\t c\prefix \s$ for some move $c\in M_C$.  If $\t\vert_{A,B}=\emptyplay$, then $W_A^*(\t\vert_{A,B})=P$ since $A$ and $B$ are negative.  Otherwise, there is at least one $B$-move in $\t\vert_{A,B}$.  Let $b$ be the last $B$-move occurring in $\t\vert_{A,B}$ - then it is the last $B$-move occurring in $\t\vert_{B,C}$; since it is followed by the move $c$, it must be an $O$-move in $B\implies C$ and therefore a $P$-move in $B$.  Therefore, $W_{A\implies B}^*(\s\vert_{A,B})=P$.

If instead $\s\vert_{B,C}$ is finite, once again we have some $\t\prefix\s$ with $\t\vert_{A,B}=\s\vert_{A,B}$ and $\t a\prefix\s$ for some move $a\in M_A$.  Since $\s\vert_{A,B}$ is infinite, it must be non-empty, so it must contain some $B$-move.  Let $b$ be the last $B$-move occurring in $\s\vert_{A,B}$; since $b$ is followed by an $A$-move, it must be an $O$-move in $B$.  Now $b$ is also the last $B$-move occurring in $\s\vert_{B,C}$ and so $W_{B\implies C}^*(\s\vert_{B,C})=P$.

\section{Weakenings}

This appendix contains material that I developed earlier in the year.  The material was originally intended to be applied to the study of the final sequence (the idea is that if $\gamma<\delta$ then $A^{\sequoid\gamma}$ is a (lax) weakening of $A^{\sequoid\delta}$ and to use these results to prove that the sequence stabilizes.  Since we have obtained this result by another method, this material is not directly applicable to the final sequence any more, but it is of interest in its own right and links in with work by Juliusz Chroboczek on subtyping \cite{juliuszthesis}.

\subsection{Weakenings}

Let $A=(M_A,\lambda_A,P_A)$ be a game.  Then we have two notions of a \emph{weakening} of $A$ - informally, a game that is \emph{easier} than $A$, from the player $P$'s point of view.

\begin{enumerate}
  \item An \emph{antecedent weakening} of $A$ is a game $A'=(M_A,\lambda_A,P_{A'})$, where $P_{A'}\subset P_{A}$ such that for every $O$-play $s$ occurring in both $P_A$ and $P_{A'}$, the set of $P$-responses to $s$ in $A'$ is precisely the set of $P$-responses to $s$ in $A$ and for every $P$-play $t$ occurring in both $P_A$ and $P_{A'}$, the set of $O$-responses to $t$ in $A'$ is a subset of the set of $O$-responses to $t$ in $A$.  
  \item A \emph{precedent strengthening} of $A$ is a game $A''=(M_A,\lambda_A,P_{A''})$ where $P_A\subset P_{A''}$ such that for every $O$-play $s$ occurring in both $P_A$ and $P_{A''}$, the set of player responses to $s$ in $A$ is a subset of the set of $P$-responses to $s$ in $A''$, and such that for every $P$-play $t$ occurring in both $P_A$ and $P_{A''}$ the set of $O$-responses to $t$ in $A$ is precisely the set of $O$-responses to $t$ in $A''$.  
\end{enumerate}

In other words, a precedent strengthening of $A$ is a game in which the player has more choices at each move, but the opponent has the same choices, while an antecedent weakening of $A$ is a game in which the player has the same choices at each move, but the opponent has fewer choices.

We can express the definition of an antecedent weakening more compactly as follows: $(M_A, \lambda_A, P_{A'})$ is an antecedent weakening of $(M_A, \lambda_A, P_A)$ if $P_{A'}\subset P_A$ and the following condition holds: whenever $s\in P_{A'}$ is an $O$-play and $a\in M_A$ is a $P$-move such that $sa\in P_A$, then $sa\in P_{A'}$.  This condition says that player $P$ has all the moves available to her in $A'$ that she had in $P_A$ - the other conditions mentioned above follow automatically from the fact that $P_{A'}\subset P_A$.

The important fact about both types of weakening is that we have copycat morphisms $A\to A',A\to A''$.

From here on, we will use the term \emph{weakening} to refer to an antecedent weakening.  If $A'$ is a weakening of $A$, we will write $\cmap{\wk}{A}{A'}$ for the copycat morphism.

\begin{proposition}
  Let $A'$ be a weakening of $A$.  Then $\cmap{\wk}{A}{A'}$ has a right inverse.

  \begin{proof}
    The inverse for $\wk$ is the partial strategy $\cmap{\str}{A'}{A}$.  This is also constructed as a copycat strategy; the only difference is that if $O$ makes a move in $A$ that does not occur in $P_{A'}$ then the player $P$ has no reply.  We now claim that $\comp\wk\str=\id_{A'}$.

    Formally:
    \begin{IEEEeqnarray*}{rCl}
      \wk & = & \left\{s\in P_{A\implies A'}\suchthat\textrm{if $|s|$ is even, then $s\vert_A=s\vert_{A'}$}\right\} \\
      \str & = & \left\{s\in P_{A'\implies A}\suchthat\textrm{if $|s|$ is even, then $s\vert_A'=s\vert_{A}$}\right\}
    \end{IEEEeqnarray*}

    We wish to show that $\comp\wk\str=\id_{A'}$.  We shall show that $\comp{\grel\wk}{\grel\str}=\Delta_{P_{A'}}$ in $\Rel$.

    It is easy to see that
    \begin{IEEEeqnarray*}{rCl}
      \grel\wk & = & \{(s, s)\suchthat s\in P_{A'}\}\subset P_A\times P_{A'} \\
      \grel\str & = & \{(s, s)\suchthat s\in P_{A'}\}\subset P_{A'}\times P_A
    \end{IEEEeqnarray*}

    It is then easy to see that $\comp\wk\str=\Delta_{A'}\subset P_{A'}\times P_{A'}$, as we wanted.  As a sanity check, if we try to take the composition the other way round then we get $\Delta_{A'}\subset P_A\times P_A$, which is not the identity unless $P_{A'}=P_A$.
  \end{proof}
\end{proposition}

\subsection{The weakening monad of a game}

\subsubsection{Weakening pullback of a game}

Let $A$ be a game.  Suppose $B$ is a game and $\cmap{\sigma}{B}{A}$ is a morphism.  Define
\[
  P_{B'}=\{\s\vert_B\suchthat \s\in\sigma\}
  \]
$P_{B'}$ is prefix closed, since $\sigma$ is, so $B'=(M_B, \lambda_B, P_{B'})$ is a well-formed game.  We claim that $B'$ is a weakening of $B$.  Indeed, suppose $s\in P_{B'}$ is an $O$-play and $sa\in P_B$.  By the definition of $P_{B'}$, there must be some $\s\in\sigma$ such that $\s\vert_B=s$; choosing $\s$ minimal, we may assume that the last move in $\s$ coincides with the last move of $s$.  Since $s$ is an $O$-play, this last move is an $O$-move in $B$ and therefore a $P$-move in $B\implies A$.  Therefore, $\s a\in \sigma$ since $\sigma$ is a strategy and so $sa=\s a\vert_B\in P_{B'}$.  We call $B'$ the \emph{weakening pullback} of $A$ along the morphism $\sigma$.

Next, we define a morphism $\cmap{\sigma'}{B'}{A}$.  As sets, $\sigma'=\sigma$ (noting that, by definition, $\sigma\subset P_{B'\implies A}$).  We claim that
\[
  \begin{tikzcd}
    B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
      & B' \arrow[d, "\sigma'"] \\
    %
      & A
  \end{tikzcd}
  \]
commutes.

Once again, we check this in $\Rel$.  If we note that $\grel\wk=\Delta_{P_{B'}}\subset P_B\times P_{B'}$ and that $\grel\sigma=\grel{\sigma'}$ as sets, then it is clear that $\comp{\grel{\sigma'}}{\grel\wk}=\grel\sigma$ in $\Rel$, and so $\comp{\sigma'}{\wk}=\sigma$ in $\G$.

The weakening $B'$ and the morphism $\sigma'$ satisfy a universal property - namely, if $B''$ is a weakening of $B$ and $\cmap{\sigma''}{B''}{A}$ is a morphism such that
\begin{equation}
  \label{pullback.b.double.prime}
  \begin{tikzcd}
    B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
      & B'' \arrow[d, "\sigma''"] \\
    %
      & A
  \end{tikzcd}
\end{equation}
commutes, then $B'$ is a weakening of $B''$ and 
\begin{equation}
  \label{pullback.b.prime}
  \begin{tikzcd}
    B'' \arrow[r, "\wk"] \arrow[dr, "\sigma''"']
      & B' \arrow[d, "\sigma'"] \\
    %
      & A
  \end{tikzcd}
\end{equation}
commutes.  Indeed, working in $\Rel$ again, diagram \eqref{pullback.b.double.prime} tells us that $\grel\sigma=\grel{\sigma''}$ as sets, which implies that $\sigma\subset P_{B''}\times P_A$.  Noting the definition of $P_{B'}$, it follows that $\map{\sigma'}{B'}{A}$ is the weakening pullback of $A$ along $\sigma''$, and so diagram \eqref{pullback.b.prime} commutes.

\subsection{The weakening monad}

We shall want to prove various useful properties of these weakening pullbacks, notably a functoriality condition: if $C\xrightarrow{\tau}\map{\sigma}{B}{A}$ are morphisms, then we get a morphism $\cmap{\tau'}{C'}{B'}$ such that $(\comp\sigma\tau)'=\comp{\sigma'}{\tau'}$.  This and other useful facts are brought together in the following theorem:

\begin{theorem}
  Let $A$ be a game.  Then we have a functor $\cmap{\weak_A}{\G/A}{\G/A}$ that sends a morphism $\map{\sigma}{B}{A}$ to the pullback weakening $\map{\sigma'}{B'}{A}$ and that gives rise to an idempotent monad on $\G/A$.

  \begin{proof}
    In order to complete the definition of the functor $\weak_A$, we need to define its action on morphisms.  Let $C\xrightarrow{\tau}\map{\sigma}{B}{A}$ be morphisms in $\G$ (so $\tau$ gives us a morphism from $\map{\comp\sigma\tau}{C}{A}$ to $\map{\sigma}{B}{A}$ in $\G/A$).  We define a morphism $\cmap{\tau'}{C'}{B'}$ by $\tau'=\tau\cap P_{C'\implies B'}$.

    It is easy to see that $\tau'$ is a strategy, so we need to check that $\comp{\sigma'}{\tau'}=(\comp\sigma\tau)'$.  As usual, we perform this check in $\Rel$.

    Since $(\comp\sigma\tau)'$ is created according to the pullback recipe given above, we have $\grel{(\comp\sigma\tau)'}=\grel{\comp\sigma\tau}$ as sets.  So, as subsets of $P_{C'}\times P_A$, we have:
    \begin{align*}
      \grel{(\comp\sigma\tau)'} & = \grel{\comp\sigma\tau} \\
                                & = \comp{\grel\sigma}{\grel\tau} \\
                                & = \{(s, t)\in P_{C'}\times P_{A}\suchthat \exists u\in P_B \esuchthat (s,u)\in\grel\tau, (u,t)\in\grel\sigma\}
    \end{align*}

    Meanwhile, as sets we have $\grel{\sigma'}=\grel\sigma$ and $\grel{\tau'}=\grel\tau\cap (P_{C'}\times P_{B'})$.  So, as subsets of $P_{C'}\times P_A$, we have:
    \begin{align*}
      \comp{\grel{\sigma'}}{\grel{\tau'}} & = \{(s, t)\in P_{C'}\times P_A\suchthat \exists u\in P_{B'} \esuchthat (s,u)\in\grel\tau, (u,t)\in\grel\sigma\}
    \end{align*}

     - in other words, the same thing, but with $P_{B'}$ instead of $P_B$.  It is clear then that $\comp{\grel{\sigma'}}{\grel{\tau'}}\subset\grel{(\comp\sigma\tau)'}$.  In the other direction, suppose $(s,t)\in P_{C'}\times P_A$ and that there exists $u\in P_B$ such that $(s,u)\in\grel\tau$ and $(u,t)\in\grel\sigma$.  But now, since $(u,t)\in\grel\sigma$, we must have $u\in P_{B'}$ by the definition of $P_{B'}$ and therefore $(u,t)\in \comp{\grel{\sigma'}}{\grel{\tau'}}$.

     So far what we have done is show that the morphism $\tau'$ does indeed give us a morphism in $\G/A$ from $\map{(\comp\sigma\tau)'}{C'}{A}$ to $\map{\sigma'}{B'}{A}$.  We still need to prove that what we have defined respects composition and so gives us a functor $\G/A\to \G/A$.

     This means proving the following statement: suppose $\map{\upsilon}{D}{C}\xrightarrow{\tau}\map{\sigma}{B}{A}$ are morphisms in $\G$.  This gives us morphisms $\upsilon,\tau$ in $\G/A$ as pictured in the diagram below:
    \[
      \begin{tikzcd}
        D \arrow[r, "\upsilon"] \arrow[drr, "\comp{\sigma}{\comp{\tau}{\upsilon}}"']
          & C \arrow[r, "\tau"] \arrow[dr, "\comp\sigma\tau"]
            & B \arrow[d, "\sigma"] \\
        %
          &
            & A
      \end{tikzcd}
      \]
    We have $\cmap{\upsilon'}{D'}{C'}$ given by $\upsilon'=\upsilon\cap P_{D'\implies C'}$ and $\cmap{\tau'}{C'}{B'}$ given by $\tau'=\tau\cap P_{C'\implies B'}$, as before.  We also have a morphism $\cmap{(\comp\tau\upsilon)'}{D'}{B'}$ given by $(\comp\tau\upsilon)'=(\comp\tau\upsilon)\cap P_{D'\implies B'}$.  We need to show that $(\comp\tau\upsilon)'=\comp{\tau'}{\upsilon'}$.

    We have $(\comp\tau\upsilon)'=(\comp\tau\upsilon)\cap P_{D'\implies B'}$, so:
    \begin{align*}
      \grel{(\comp\tau\upsilon)'} & = \grel{(\comp\tau\upsilon)}\cap(P_{D'}\times P_{B'}) \\
       & = (\comp{\grel\tau}{\grel\upsilon}) \cap (P_{D'}\times P_{B'}) \\
       & = \{(s,t)\in P_{D'}\times P_{B'} \suchthat \exists u\in P_C \esuchthat (s,u) \in \grel\upsilon\;, (u,t) \in \grel\tau \}
    \end{align*}

    Meanwhile, $\grel{\tau '} = \grel\tau \cap P_{D'}$ and $\grel{\upsilon '} = \grel\upsilon \cap P_{B'}$, so
    \[
      \comp{\grel{\tau '}}{\grel{\upsilon '}} = \{(s,t) \in P_{D'}\times P_{B'} \suchthat \exists u\in P_{C'} \esuchthat (s,u) \in \grel\upsilon\; (u,t)\in \grel\tau \}
      \]
    which is the same thing, but with $P_{C'}$ rather than $P_C$.

    Clearly, $\comp{\grel{\tau '}}{\grel{\upsilon '}} \subseteq \grel{(\comp\tau\upsilon)'}$.  In the other direction, suppose that $s\in P_{D'}, t\in P_{B'}$ and that $u\in P_C$ such that $(s,u)\in \grel\upsilon,(u,t)\in\grel\tau$.  It will suffice to show that $u\in P_{C'}$.  Now note that $C'$ is pullback of $A$ along $\comp\sigma\tau$ and that $B'$ is pullback of $A$ along $\sigma$.  Therefore:
    \begin{align*}
      P_{C'} & = \{\s\vert_C\suchthat \s\in\comp\sigma\tau\} \\
      P_{B'} & = \{\t\vert_B\suchthat \t\in\sigma\}
    \end{align*}
    Since $t\in P_{B'}$, there must be some $\t\in \sigma$ such that $\t\vert_B=t$.  Put another way, there must be some $v\in P_A$ such that $(t,v)\in\grel\sigma$.  We have $(u,t)\in\grel\tau$, so therefore $(u,v)\in\grel{\comp\sigma\tau}$, and it follows that $u\in P_{C'}$.

    Therefore, we have that $\grel{\comp{\tau'}{\upsilon'}}=\comp{\grel{\tau '}}{\grel{\upsilon '}} = \grel{(\comp\tau\upsilon)'}$.  Since the Hyland-Schalk functor is faithful, this means that $\comp{\tau '}{\upsilon '}=(\comp\tau\upsilon)'$.

    This all means that we can define a functor $\cmap{\weak_A}{\G/A}{\G/A}$ by
    \begin{IEEEeqnarray*}{CCCCC}
      \map{\sigma}{B}{A} & \quad & \mapsto & \quad & \map{\sigma'}{B'}{A} \\
      \begin{tikzcd}
        C \arrow[r, "\tau"] \arrow[dr, "\comp\sigma\tau"']
         & B \arrow[d, "\sigma"] \\
        %
         & A
      \end{tikzcd}
      & \quad & \mapsto & \quad &
      \begin{tikzcd}
        C' \arrow[r, "\tau'"] \arrow[dr, "\comp{\sigma'}{\tau'}"']
         & B' \arrow[d, "\sigma'"] \\
        %
         & A
      \end{tikzcd}
    \end{IEEEeqnarray*}

    We now define the monad structure on $\G/A$.  The unit transformation $\cmap{\eta_A}{\id_{\G/A}}{\weak_A}$ is given by the weakening morphisms $\cmap{\wk}{B}{B'}$ for each object $\map{\sigma}{B}{A}$; we have already shown that the diagrams
    \[
      \begin{tikzcd}
        B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
         & B' \arrow[d, "\sigma'"] \\
        %
         & A
      \end{tikzcd}
      \]
    commute.  To show that this is indeed a natural transformation, we need to show that if we are given some morphism in $\G/A$
    \[
      \begin{tikzcd}
        C \arrow[r, "\tau"] \arrow[dr, "\comp\sigma\tau"']
          & B \arrow[d, "\sigma"] \\
        %
          & A
      \end{tikzcd}
      \]
    then the following square commutes:
    \[
      \begin{tikzcd}
        C \arrow[r, "\wk"] \arrow[d, "\tau"']
          & C' \arrow[d, "\tau'"] \\
        B \arrow[r, "\wk"']
          & B'
      \end{tikzcd}
      \]
    To show this, we work in $\Rel$ again.  On the one hand, we have:
    \begin{align*}
      \comp{\grel{\tau'}}{\grel{\wk}} & = \{(s,t)\in P_C\times P_{B'}\suchthat\exists u\in P_{C'}\esuchthat (s,u)\in\grel\wk\;,(u,t)\in\grel{\tau'}\} \\
       & = \{(s, t)\in P_{C'}\times P_{B'}\suchthat (s,t)\in\grel{\tau'}\} \\
       & = \grel{\tau'} = \grel{\tau}\cap(P_{C'}\times P_{B'})
    \end{align*}
    On the other hand:
    \begin{align*}
      \comp{\grel\wk}{\grel\tau} & = \{(s, t)\in P_C\times P_{B'}\suchthat \exists u\in P_B\esuchthat (s,u)\in \grel\tau, (u, t)\in \grel\wk\} \\
       & = \grel\tau \cap (P_C\times P_{B'})
    \end{align*}

    We certainly have $\comp{\grel{\tau'}}{\grel\wk}\subseteq\comp{\grel\wk}{\grel\tau}$.  In the other direction, suppose that $s\in P_C$ and $t\in P_{B'}$ such that $(s,t)\in\grel\tau$.  It will suffice to show that $s\in P_{C'}$.  Indeed, by the definition of $P_{B'}$, there is some $v\in P_A$ such that $(t, v)\in\grel\sigma$.  Therefore, $(s, v)\in\grel{\comp{\sigma}{\tau}}$, and so $s\in P_{C'}$, as required.

   Before defining the multiplication $\cmap{\mu_A}{\comp{\weak_A}{\weak_A}}{\weak_A}$ in the monad, we look at the identities that this unit transformation $\eta_A$ will have to satisfy.  If $\map{\sigma}{B}{A}$ is an object of $\G/A$ then we want the diagrams
   \[
     \begin{tikzcd}
       B' \arrow[r, "\wk"] \arrow[dr, equals]
         & B'' \arrow[d, "\mu_A(B)"] \\
       %
         & B'
     \end{tikzcd}
     \textrm{ and }
     \begin{tikzcd}
       B' \arrow[r, "\wk'"] \arrow[dr, equals]
         & B'' \arrow[d, "\mu_A(B)"] \\
       %
         & B'
     \end{tikzcd}
     \]
   to commute.  The arrow $\cmap{\wk}{B'}{B''}$ in the first diagram is the weakening arrow obtained from the object $\map{\sigma'}{B'}{A}$ of $\G/A$ using the natural transformation $\eta_A$, while the arrow $\cmap{\wk'}{B'}{B''}$ in the second diagram is obtained by applying the functor $\weak_A$ to the morphism $\cmap{\wk}{B}{B'}$.

   In practice, however, there is no need for this distinction: $B''$ is the same game as $B'$ and the arrows $\wk$ and $\wk'$ are the identity.  To see this, recall the definitions of $B'$ and $\sigma'$:
   \begin{align*}
     P_{B'} & = \{\s\vert_B\suchthat \s\in\sigma\} \\
     \sigma' & = \sigma\textrm{ (as sets of plays)}
   \end{align*}
   Then we should have $P_{B''} = \{\s\vert_{B'}\suchthat \s\in\sigma'\}$, but since $\sigma'$ is the same set as $\sigma$, this is exactly the same as the definition of $P_{B'}$.

   Since $\wk,\wk'$ are identity maps, we observe that we have the strict equality $\comp{\weak_A}{\weak_A}=\weak_A$ and we had better define $\mu_A$ to be the identity transformation.  This $\mu_A$ is automatically associative and the unit diagrams above hold (since all maps involved are identity maps).  We end up with an idempotent monad on $\G/A$.
  \end{proof}
\end{theorem}

\subsection{Lax weakening morphisms}

We now introduce a lax version of our notion of weakening morphism that is stable under composition with isomorphisms:

\begin{definition}
  Let $A,B$ be games.  We say that a morphism $\cmap{\sigma}{B}{A}$ is a \emph{lax weakening} if it is the composition of a weakening morphism and an isomorphism; in other words, if there exists a weakening $B'$ of $B$ and an isomorphism $\cmap{\hat{\sigma}}{B'}{A}$ such that the diagram
  \[
    \begin{tikzcd}
      B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
        & B' \arrow[d, "\hat\sigma", Sim'] \\
      %
        & A
    \end{tikzcd}
    \]
  commutes.
\end{definition}

\begin{proposition}

  i) If $B'$ is a weakening of $B$, then $\cmap{\wk}{B}{B'}$ is a lax weakening.

  ii) If $\cmap{\sigma}{B}{A}$ is an isomorphism, then $\sigma$ is a lax weakening.

  iii) If $C\xrightarrow{\tau}\map{\sigma}{B}{A}$ are morphisms such that $\sigma$ and $\tau$ are lax weakenings, then $\cmap{\comp\sigma\tau}{C}{A}$ is a lax weakening.

  \begin{proof}
    (i) and (ii) are both obvious.  For part (iii), note that we have the diagram
    \[
      \begin{tikzcd}
        C \arrow[r, "\wk"] \arrow[dr, "\tau"']
          & C' \arrow[d, "\hat\tau", Sim']
            & \\
        %
          & B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
            & B' \arrow[d, "\hat\sigma", Sim'] \\
        %
          &
            & A
      \end{tikzcd}
      \]
    It will suffice to find a weakening $C''$ of $C'$ and an isomorphism $\cmap{\hat{\hat\tau}}{C''}{B'}$ making the following diagram commute:
    \[
      \begin{tikzcd}
        C \arrow[r, "\wk"] \arrow[dr, "\tau"']
          & C' \arrow[d, "\hat\tau", Sim'] \arrow[r, "\wk"]
            & C'' \arrow[d, "\hat{\hat\tau}", Sim'] \\
        %
          & B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
            & B' \arrow[d, "\hat\sigma", Sim'] \\
        %
          &
            & A
      \end{tikzcd}
      \]
    Therefore, it will suffice to prove the lemma which follows.
  \end{proof}
\end{proposition}

\begin{lemma}[Lifting of weakenings along isomorphisms]
  Let $B,C$ be games and let $\cmap{\tau}{C}{B}$ be an isomorphism.  Let $B'$ be a weakening of $B$.  Then there is a weakening $C'$ of $C$ and an isomorphism $\cmap{\tau'}{C'}{B'}$ such that the following diagram commutes:
  \[
    \begin{tikzcd}
      C \arrow[r, "\wk"] \arrow[d, "\tau"', Sim]
        & C' \arrow[d, "\tau'"', Sim] \\
      B \arrow[r, "\wk"'] 
        & B'
    \end{tikzcd}
    \]
\end{lemma}

We shall give two proofs of this lemma - one direct proof using the Hyland-Schalk functor and one proof using the idempotent monad structure described in the previous section.

\begin{proof}[First proof]
  We know that $\cmap{\tau}{C}{B}$ is an isomorphism; therefore, its image $\grel\tau\subset P_C\times P_B$ under the Hyland-Schalk functor is an isomorphism in $\Rel$.  It is well-known (and easy to show) that the isomorphisms in $\Rel$ are precisely those relations that are the graphs of bijective functions.  Therefore, we have a bijection $\cmap{\grel\tau}{P_C}{P_B}$ with the property that

  i) For all $s\in P_C$ there exists a $P$-play $\s\in\tau$ such that $\s\vert_C=s$ and $\s\vert_B=\grel\tau(s)$

  ii) For all $P$-plays $\s\in\tau$, $\s\vert_B=\grel\tau\left(\s\vert_C\right)$.

  Let $P_{C'}=\grel\tau\inv(P_{B'})\subseteq P_C$.  We claim that $P_{C'}$ is prefix-closed.  Let $s\in P_{C'}$ and let $t\prefix s$.  By the definition of $P_{C'}$, $\tau(s)\in P_{B'}$.  Since $P_{B'}$ is prefix-closed, it will suffice to show that $\grel\tau(t)\prefix\grel\tau(s)$.

  By (i), we know that there exists a $P$-play $\s\in\tau$ such that $\s\vert_C = s$ and $\s\vert_B = \grel\tau(s)$.  Since $t\prefix s$, there is some prefix $\t\prefix\s$ such that $\t\vert_C = t$.  Then, by (ii), we must have $\grel\tau(t)=\t\vert_B\prefix\s\vert_B$.

  Therefore, $C'=(M_C,\lambda_C, P_{C'})$ is a well-formed game.  We claim that it is a weakening of $C$.

  Indeed, suppose $s\in P_{C'}$ is an $O$-play and that $sc$ is a $P$-reply in $P_C$.  We need to show that $sc\in P_{C'}$.

  By the definition of $P_{C'}$, we know that $\grel\tau(s)\in P_{B'}$.  By (i) we know that there exists some $P$-play $\s\in\tau$ such that $\s\vert_C=s$ and $\s\vert_B=\grel\tau(s)$; since $\s$ is a $P$-play, we can deduce that $s$ and $\grel\tau(s)$ have the same sign, and so $\grel\tau(s)$ is an $O$-play in $P_{B'}$.  Examining (i) and (ii) above, we can see that $\grel\tau(sc)=\grel\tau(s)b$ for some $b\in P_B$.  Therefore, since $B'$ is a weakening of $B$, we have $\grel\tau(sc)\in P_{B'}$ and so $sc\in P_{C'}$ as desired.

  Lastly, we define $\tau'$ to be given by the set $\tau \cap P_{C\implies B}$, and we claim that the diagram
  \[
    \begin{tikzcd}
      C \arrow[r, "\wk"] \arrow[d, "\tau"', Sim]
        & C' \arrow[d, "\tau'"'] \\
      B \arrow[r, "\wk"'] 
        & B'
    \end{tikzcd}
    \]
  commutes.  This is most easily checked by applying the faithful functor
  \[
    \G \xrightarrow{\F} \Rel \xrightarrow{\dagger} \oppcat{\Rel}
    \]
  where $\cmap{\dagger}{\Rel}{\oppcat{\Rel}}$ is the identity on objects and flips a relation $R\subset A\times B$ to give a relation $R^\dagger\subset B\times A$.  If $\cmap{\wk}{A}{A'}$ is a weakening morphism in $\G$ then its image $\grel\wk$ under this functor is the graph of the inclusion $P_{A'}\hookrightarrow P_A$.  Meanwhile, the image of $\tau$ under this functor is the graph of the function $\cmap{\grel\tau\inv}{P_B}{P_C}$.  By the definition of $P_{C'}$, the image of $\tau'$ under this functor is the graph of the function $\cmap{\grel\tau\inv\vert_{P_{B'}}}{P_{B'}}{P_{C'}}$.  It is then easy to check that the resulting diagram commutes in $\Rel$:
  \[
    \begin{tikzcd}
      P_C
        & P_{C'} \arrow[l, hook', "\grel\wk"'] \\
      P_B \arrow[u, "\grel\tau\inv"]
        & P_{B'} \arrow[u, "\grel\tau\inv\vert_{P_{B'}}"'] \arrow[l, hook', "\grel\wk"]
    \end{tikzcd}
    \]

  The last thing that we need to do is to check that $\tau'$ is an isomorphism.  If we apply exactly the same argument to $\map{\wk}{C}{C'}$ and the isomorphism $\cmap{\tau\inv}{B}{C}$ then we get a weakening $B''$ of $B$ and an isomorphism $\cmap{(\tau\inv)'}{B''}{C'}$ making the following diagram commute:
  \[
    \begin{tikzcd}
      B \arrow[r, "\wk"] \arrow[d, "\tau\inv"', Sim]
        & B'' \arrow[d, "(\tau\inv)'"] \\
      C \arrow[r, "\wk"']
        & C'
    \end{tikzcd}
    \]
  Now note that $P_{B''}$ is defined to be $\grel\tau(P_{C'})$.  Since $\grel\tau$ is a bijection and $P_C$ was defined to be $\grel\tau\inv(P_{B'})$, we get that $B''=B'$.  We now get:
  \begin{align*}
    B \xrightarrow{\wk} B' \xrightarrow{(\tau\inv)'} C' \xrightarrow{\tau'} B'
    & = B \xrightarrow{\tau\inv} C \xrightarrow{\wk} C' \xrightarrow{\tau'} B' \\
    & = B \xrightarrow{\tau\inv} C \xrightarrow{\tau} B \xrightarrow{\wk} B' \\
    & = B \xrightarrow{\wk} B'
  \end{align*}
  Since $\wk$ is an epimorphism, it follows that $\comp{\tau'}{(\tau\inv)'}=\id_{B'}$.  An identical argument shows that $\comp{(\tau\inv)'}{\tau'}=\id_{C'}$.  So $\tau'$ is an isomorphism.
\end{proof}

\begin{proof}[Second proof]
  We start off with the diagram
  \[
    \begin{tikzcd}
      C \arrow[d, "\tau"', Sim]
        & \\
      B \arrow[r, "\wk"]
        & B'
    \end{tikzcd}
    \]

  We use the monad on the category $\G/B'$.  Let $C'$ be the pullback of $B'$ along the morphism $\cmap{\comp\wk\tau}{C}{B'}$.  This gives us the diagram
  \[
    \begin{tikzcd}
      C \arrow[d, "\tau"', Sim] \arrow[r, "\wk"]
        & C' \arrow[d, "(\comp\wk\tau)'"] \\
      B \arrow[r, "\wk"]
        & B'
    \end{tikzcd}
    \]
  It remains to show that $(\comp\wk\tau)'$ is an isomorphism.

  To show this, let us rearrange the original diagram a bit to make the monadic structure explicit:
  \[
    \begin{tikzcd}
      C \arrow[r, "\tau", Sim'] \arrow[dr, "\comp\wk\tau"']
        & B \arrow[d, "\wk"] \\
      %
        & B'
    \end{tikzcd}
    \]
  When we apply the functor $\weak_{B'}$ to this diagram, we get
  \[
    \begin{tikzcd}
      C' \arrow[r, "\tau'"] \arrow[dr, "(\comp\wk\tau)'"']
        & B' \arrow[d, "\wk'"] \\
      %
        & B'
    \end{tikzcd}
    \]
  By definition, $\cmap{\wk=\eta_B}{B}{B'}$, and so $\wk'=(\eta_B)'$.  Since our monad is idempotent, $(\eta_B)'$ is an isomorphism.  $\tau'$ is an isomorphism by functoriality and therefore $(\comp\wk\tau)'$ is an isomorphism, as desired.
\end{proof}

\bibliographystyle{alpha}
\bibliography{ordinal_games}

\end{document}

### 2016-10-11 ordinal_games/presentation/presentation.tex
Started Research repository

\documentclass{beamer}

\usepackage[utf8]{inputenc}

\usepackage{graphicx} % support the \includegraphics command and options

\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{mathtools} % for the all important \coloneqq symbol
\usepackage{url} % for \url
\usepackage{IEEEtrantools} % for \IEEEeqnarray

%% Font things %%
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{cmll} % Linear logic symbols!

%% Lists %%
\usepackage{enumerate}

%% Graphics %%
\usepackage{tikz}
\usetikzlibrary{cd}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}

%% Changes to enumerate things so they look better %%

\makeatletter
\def\enumfix{%
\if@inlabel
 \noindent \par\nobreak\vskip-\topsep\hrule\@height\z@
\fi}

\let\olditemize\itemize
\def\itemize{\enumfix\olditemize}
\let\oldenumerate\enumerate
\def\enumerate{\enumfix\oldenumerate}

%% Random crap %%
\usepackage{xifthen}

\makeatletter
\def\thm@space@setup{%
  \thm@preskip=\parskip \thm@postskip=0pt
}
\makeatother

\makeatletter
\newcommand*{\relrelbarsep}{.386ex}
\newcommand*{\relrelbar}{%
  \mathrel{%
    \mathpalette\@relrelbar\relrelbarsep
  }%
}
\newcommand*{\@relrelbar}[2]{%
  \raise#2\hbox to 0pt{$\m@th#1\relbar$\hss}%
  \lower#2\hbox{$\m@th#1\relbar$}%
}
\providecommand*{\rightrightarrowsfill@}{%
  \arrowfill@\relrelbar\relrelbar\rightrightarrows
}
\providecommand*{\leftleftarrowsfill@}{%
  \arrowfill@\leftleftarrows\relrelbar\relrelbar
}
\providecommand*{\xrightrightarrows}[2][]{%
  \ext@arrow 0359\rightrightarrowsfill@{#1}{#2}%
}
\providecommand*{\xleftleftarrows}[2][]{%
  \ext@arrow 3095\leftleftarrowsfill@{#1}{#2}%
}
\makeatother

\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\Rings}{\catname{CRing}}
\newcommand{\CAT}{\catname{CAT}}
\newcommand{\Top}{\catname{Top}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Cont}{\catname{Cont}}
\newcommand{\Sch}{\catname{Sch}}
\newcommand{\Mod}[1][]{\ifthenelse{\isempty{#1}}{\catname{Mod}}{#1\catname{mod}}}
\DeclareMathOperator{\sh}{Sh}
\newcommand{\Sh}[1][]{\ifthenelse{\isempty{#1}}{\sh}{\sh(#1)}}
\newcommand{\map}[3]{#2\xrightarrow{#1} #3}
\newcommand*\from{\colon}
\newcommand{\cmap}[3]{#1\from{}#2\to{}#3}
\newcommand\oppcat[1]{#1^{\mathrm{op}}}
\DeclareRobustCommand{\vmap}[3] {\begin{tikzcd} #2 \arrow[d, "#1"] \\ #3 \end{tikzcd}}
\newcommand{\partref}[1]{(\ref{#1})}
\newcommand{\intgrpd}[4] {#1 \xrightrightarrows[#3]{#4} #2}
\DeclareRobustCommand{\bigintgrpd}[4] {\begin{tikzcd}[ampersand replacement=\&] #1 \arrow[r, shift left=0.5ex, "#3"] \arrow[r, shift right=0.5ex, "#4"'] \& #2 \end{tikzcd}}

\usepackage{xspace}

\newcommand{\etale}{\'{e}tale\xspace}
\newcommand{\Etale}{\'{E}tale\xspace}

\def \inv {^{-1}}

\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\op}{op}
\DeclareMathOperator{\pr}{pr}
\DeclareMathOperator{\pre}{{pre}}
\DeclareMathOperator{\et}{{\acute{e}t}}

\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Spec}{Spec}

\DeclareMathOperator{\ol}{ol}

\def\presuper#1#2%
  {\mathop{}%
   \mathopen{\vphantom{#2}}^{#1}%
   \kern-\scriptspace%
   #2}
\def\presub#1#2%
  {\mathop{}%
   \mathopen{\vphantom{#2}}_{#1}%
   \kern-\scriptspace%
   #2}

%% Our things %%

\newcommand{\neggame}[1]{\presuper{\perp}{#1}}
\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\newcommand{\varsequoid}{\vartriangleleft}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#1 \circ #2}
\newcommand{\cprd}{\sqcup}
\newcommand{\G}{\mathcal G}
\newcommand{\C}{\mathcal C}
\newcommand{\F}{\mathcal F}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\renewcommand{\L}{\mathcal L}

\newcommand{\nsb}{N\sequoid\underline{\hspace{1.5ex}}\;}

%%% END Article customizations

\title{Games with ordinal sequence of moves}

\author{John Gowers and James Laird}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\section*{Outline}
\begin{frame}
  \tableofcontents
\end{frame}

\section{Preliminaries}

\subsection{Our starting point - the Abramsky-Jagadeesan Games Model}

\begin{frame}
  \frametitle{Our starting point - the Abramsky-Jagadeesan Games Model}

  We start off with a few simple categories of games:

  \begin{itemize}
    \item Games with a winning condition:
      \[
        A=(M_A,\lambda_A,b_A,P_A,W_A)
        \]
      The winning condition prevents infinite internal chattering.
    \item Games without a winning condition:
      \[
        A=(M_A,\lambda_A,b_A,P_A)
        \]
      We have no winning condition, so we have to use \\
      partial strategies or require that our games be bounded.
    \item We have the tensor product ($\tensor$) and implication ($\implies$) \\
      given by interleaving games and a categorical semantics $\G$\\
      where a morphism from $A$ to $B$ is a strategy for $A\implies B$.
  \end{itemize}

\end{frame}

\subsection{Exponentials and the sequoid operator}

\begin{frame}
  \frametitle{Construction of an exponential for our game model}

  $N$ is a negative game ($b_N=O$).

  \[
    !N=(M_N\times\mathbb N,\lambda_N\circ\pr_1,O,P_{!N})
    \]

  $!N$ is made up of countably many copies of the game $N$,\\
  indexed by $\mathbb N$ and played in parallel, with the opponent\\
  switching games.

  $!N$ has the structure of the cofree commutative comonoid\\
  generated by $N$:
  \[
    !N\implies !N\tensor !N
    \]

\end{frame}

\begin{frame}
  \frametitle{The sequoid operator on games}

  \begin{itemize}
    \item $N\sequoid L$ is a weakening of $N\tensor L$ in which the opponent must make the first move in the game $N$.
    \item It induces a monoidal category action of $\G$ on \\
      (a modified version of) itself:
      \[
        L \sequoid (M \tensor N) \cong (L \sequoid M) \sequoid N
        \]
      This is the basis of the definition of a \emph{sequoidal category}.
    \item Then the exponential $!N$ arises as the final coalgebra \\
      for the `sequoid on the left by $N$' functor $\nsb$
      \[
        !N\implies N\sequoid !N
        \]
  \end{itemize}

\end{frame}

\subsection{Coalgebras and the final sequence}

\begin{frame}[fragile]
  \frametitle{The final sequence}
  Let $\C$ be a category and $\cmap{\F}{\C}{\C}$ be an endofunctor.
  \[
    \begin{tikzcd}
      1
        & \F(1) \arrow[l]
          & \F^2(1) \arrow[l]
            & \F^3(1) \arrow[l]
              & \cdots \arrow[l] \\
      \F^\omega(1) \arrow[u] \arrow[ur] \arrow[urr] \arrow [urrr] \arrow[urrrr, phantom, xshift=5.0ex, yshift=-0.5ex, "\cdots"]
        & \F^{\omega+1}(1) \arrow[l]
          & \F^{\omega+2}(1) \arrow[l]
            & \F^{\omega+3}(1) \arrow[l]
              & \cdots \arrow[l] \\
      \F^{\omega2}(1) \arrow[u] \arrow[ur] \arrow[urr] \arrow [urrr] \arrow[urrrr, phantom, xshift=5.0ex, yshift=-0.5ex, "\cdots"]
        & \cdots \arrow[l]
          &
            & \\
      \arrow[u, phantom, "\vdots"]
    \end{tikzcd}
    \]

  If a final coalgebra for $\F$ exists, then it occurs as $\F^\alpha(1)$ \\
  for some $\alpha$ and the sequence stabilizes thereafter.
\end{frame}

\section{Stabilization ordinals for categories of games}

\begin{frame}
  \frametitle{Stabilization ordinals for sequoidal categories of games}

  \begin{itemize}
    \item If $N$ is an object in the category $\G$ of games without \\
      a winning condition, then the final sequence for $\nsb$ \\
      stabilizes by $\omega$.
      \pause
    \item If $N$ is an object in the category $\mathcal W$ of games with \\
      a winning condition, then the final sequence for $\nsb$ \\
      stabilizes by $\omega2$.
      \pause
    \item If $\C$ is a sequoidal category, do the final sequences \\
      corresponding to `sequoid on the left' functors \\
      always stabilize by $\omega2$?  (No.)
      \pause
    \item Can we replace $\omega2$ by some other ordinal to give us a recipe \\
      for constructing the exponential in any sequoidal category?
  \end{itemize}
\end{frame}

\section{Games with ordinal sequences of moves}

\subsection{What we end up with}

\begin{frame}
  \frametitle{Idea of transfinite games}

  \begin{itemize}
    \item For games without a winning condition, we may have a move \\
      at time $n$ for every $n\in\omega$.  
    \item For games with a winning condition, we have things happening \\
      at time $\omega$ as well.  
    \item We now take things further, and construct a category $\G(\alpha)$ \\
      for every ordinal $\alpha$.  
    \item We will get $\G\cong\G(\omega)$ and $\mathcal W\cong\G(\omega+1)$.
    \item There is a connection between the ordinal $\alpha$ and the \\
      stabilization ordinals for functors of the form
      \[
        \cmap{\nsb}{\G(\alpha)}{\G(\alpha)}
        \]
  \end{itemize}
\end{frame}

\subsection{Brief outline of the construction}

\begin{frame}
  \frametitle{A brief outline of the construction of the category of games played over the ordinal $\alpha$}

  Fix an ordinal $\alpha$.  We construct a sequoidal category of \\
  games of length $\alpha$ by mimicking the Abramsky-Jagadeesan \\
  construction:
  \[
    N=(M_N, \lambda_N, \zeta_N, P_N)
    \]

  \begin{itemize}
    \item $M_N$ is a set of moves.
    \item $\cmap{\lambda_N}{M_N}{\OP}$ is a function saying which player each \\
      move belongs to.
    \item $P_N$ is a prefix closed set of ordinal length sequences (plays) \\
      that take values in $M_N$ and are indexed by ordinals $<\alpha$
    \item $\cmap{\zeta_N}{P_N}{\OP}$ assigns a player to each play.
  \end{itemize}

\end{frame}

\subsection{Stabilization ordinals}

\begin{frame}
  \frametitle{The stabilization ordinal of the category $\G(\alpha)$}

  \begin{itemize}
    \item The behaviour of the stabilization ordinal for functors \\
      of the form $\nsb$ in the category $\G(\alpha)$ is complicated \\
      in general.
    \item However, the final sequence for such functors never stabilizes \\
      before $\alpha$.
    \item Therefore, we have constructed sequoidal categories of games \\
      with arbitrarily high stabilization ordinals: there is no \\
      general recipe for constructing this exponential using only \\
      the application of the functor and passing to small limits.
  \end{itemize}
\end{frame}

\end{document}

### 2016-10-11 ordinal_games/split-epimorphisms/split-epimorphisms.tex
Started Research repository

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc}

\usepackage{graphicx} % support the \includegraphics command and options

\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{mathtools} % for the all important \coloneqq symbol
\usepackage{url} % for \url
\usepackage{IEEEtrantools} % for \IEEEeqnarray

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%% Font things %%
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{cmll} % Linear logic symbols!

%% Lists %%
\usepackage{enumerate}

%% Graphics %%
\usepackage{tikz}
\usetikzlibrary{cd}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}

%% Theorems! %%
\usepackage{amsthm}
\theoremstyle{plain} % Theorems, lemmas, propositions etc.
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{construction}[theorem]{Construction}
\theoremstyle{definition} % Definitions etc.  Remarks too, because I don't like the way the 'remark' style looks.
\newtheorem{definition}[theorem]{Definition}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

%% Exercises and answers %%
\usepackage{answers}

\newtheoremstyle{exercisestyle}% name
  {6pt}   % ABOVESPACE
  {6pt}   % BELOWSPACE
  {\itshape}  % BODYFONT
  {0pt}       % INDENT (empty value is the same as 0pt)
  {\bfseries} % HEADFONT
  {.}         % HEADPUNCT
  {3pt} % HEADSPACE
  {}          % CUSTOM-HEAD-SPEC

\theoremstyle{exercisestyle}
\newtheorem{exercise}{Exercise}
\newtheorem{answerthm}{Exercise}

\Newassociation{answer}{answerthm}{answers}
\newcommand{\answerthmparams}{}

%% Changes to enumerate things so they look better %%

\makeatletter
\def\enumfix{%
\if@inlabel
 \noindent \par\nobreak\vskip-\topsep\hrule\@height\z@
\fi}

\let\olditemize\itemize
\def\itemize{\enumfix\olditemize}
\let\oldenumerate\enumerate
\def\enumerate{\enumfix\oldenumerate}

%% Random crap %%
\usepackage{xifthen}

\makeatletter
\def\thm@space@setup{%
  \thm@preskip=\parskip \thm@postskip=0pt
}
\makeatother

\makeatletter
\newcommand*{\relrelbarsep}{.386ex}
\newcommand*{\relrelbar}{%
  \mathrel{%
    \mathpalette\@relrelbar\relrelbarsep
  }%
}
\newcommand*{\@relrelbar}[2]{%
  \raise#2\hbox to 0pt{$\m@th#1\relbar$\hss}%
  \lower#2\hbox{$\m@th#1\relbar$}%
}
\providecommand*{\rightrightarrowsfill@}{%
  \arrowfill@\relrelbar\relrelbar\rightrightarrows
}
\providecommand*{\leftleftarrowsfill@}{%
  \arrowfill@\leftleftarrows\relrelbar\relrelbar
}
\providecommand*{\xrightrightarrows}[2][]{%
  \ext@arrow 0359\rightrightarrowsfill@{#1}{#2}%
}
\providecommand*{\xleftleftarrows}[2][]{%
  \ext@arrow 3095\leftleftarrowsfill@{#1}{#2}%
}
\makeatother

\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\Rings}{\catname{CRing}}
\newcommand{\CAT}{\catname{CAT}}
\newcommand{\Top}{\catname{Top}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Cont}{\catname{Cont}}
\newcommand{\Sch}{\catname{Sch}}
\newcommand{\Rel}{\catname{Rel}}
\newcommand{\Mod}[1][]{\ifthenelse{\isempty{#1}}{\catname{Mod}}{#1\catname{mod}}}
\DeclareMathOperator{\sh}{Sh}
\newcommand{\Sh}[1][]{\ifthenelse{\isempty{#1}}{\sh}{\sh(#1)}}
\newcommand{\map}[3]{#2\xrightarrow{#1} #3}
\newcommand*\from{\colon}
\newcommand{\cmap}[3]{#1\from{}#2\to{}#3}
\newcommand\oppcat[1]{#1^{\mathrm{op}}}
\DeclareRobustCommand{\vmap}[3] {\begin{tikzcd} #2 \arrow[d, "#1"] \\ #3 \end{tikzcd}}
\newcommand{\partref}[1]{(\ref{#1})}
\newcommand{\intgrpd}[4] {#1 \xrightrightarrows[#3]{#4} #2}
\DeclareRobustCommand{\bigintgrpd}[4] {\begin{tikzcd}[ampersand replacement=\&] #1 \arrow[r, shift left=0.5ex, "#3"] \arrow[r, shift right=0.5ex, "#4"'] \& #2 \end{tikzcd}}

\usepackage{xspace}

\newcommand{\etale}{\'{e}tale\xspace}
\newcommand{\Etale}{\'{E}tale\xspace}

\def \inv {^{-1}}

\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\op}{op}
\DeclareMathOperator{\pr}{pr}
\DeclareMathOperator{\pre}{{pre}}
\DeclareMathOperator{\et}{{\acute{e}t}}

\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Spec}{Spec}

\DeclareMathOperator{\ol}{ol}

\def\presuper#1#2%
  {\mathop{}%
   \mathopen{\vphantom{#2}}^{#1}%
   \kern-\scriptspace%
   #2}
\def\presub#1#2%
  {\mathop{}%
   \mathopen{\vphantom{#2}}_{#1}%
   \kern-\scriptspace%
   #2}

%% Our things %%

\newcommand{\neggame}[1]{\presuper{\perp}{#1}}
\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\newcommand{\varsequoid}{\vartriangleleft}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#1 \circ #2}
\newcommand{\cprd}{\sqcup}
\newcommand{\G}{\mathcal G}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\newcommand{\F}{\mathcal F}
\renewcommand{\L}{\mathcal L}
\DeclareMathOperator{\wk}{wk}
\DeclareMathOperator{\str}{str}
\newcommand{\s}{\mathfrak{s}}
\renewcommand{\t}{\mathfrak{t}}

%%% END Article customizations

\begin{document}

\section{Weakenings}

Let $A=(M_A,\lambda_A,P_A)$ be a game.  Then we have two notions of a \emph{weakening} of $A$ - informally, a game that is \emph{easier} than $A$, from the player $P$'s point of view.

\begin{enumerate}
  \item An \emph{antecedent weakening} of $A$ is a game $A'=(M_A,\lambda_A,P_{A'})$, where $P_{A'}\subset P_{A}$ such that for every $O$-play $s$ occuring in both $P_A$ and $P_{A'}$, the set of $P$-responses to $s$ in $A'$ is precisely the set of $P$-responses to $s$ in $A$ and for every $P$-play $t$ occurring in both $P_A$ and $P_{A'}$, the set of $O$-responses to $t$ in $A'$ is a subset of the set of $O$-responses to $t$ in $A$.  
  \item A \emph{precedent strengthening} of $A$ is a game $A''=(M_A,\lambda_A,P_{A''})$ where $P_A\subset P_{A''}$ such that for every $O$-play $s$ occuring in both $P_A$ and $P_{A''}$, the set of player responses to $s$ in $A$ is a subset of the set of $P$-responses to $s$ in $A''$, and such that for every $P$-play $t$ occuring in both $P_A$ and $P_{A''}$ the set of $O$-responses to $t$ in $A$ is precisely the set of $O$-responses to $t$ in $A''$.  
\end{enumerate}

In other words, a precedent strengthening of $A$ is a game in which the player has more choices at each move, but the opponent has the same choices, while an antecedent weakening of $A$ is a game in which the player has the same choices at each move, but the opponent has fewer choices.

The important fact about both these types of weakening is that we have copycat morphisms $A\to A',A\to A''$.

From here on, we will use the term \emph{weakening} to refer to an antecedent weakening.  If $A'$ is a weakening of $A$, we will write $\cmap{\wk}{A}{A'}$ for the copycat morphism.

\begin{proposition}
  Let $A'$ be a weakening of $A$.  Then $\cmap{\wk}{A}{A'}$ has a right inverse.

  \begin{proof}
    The inverse for $\wk$ is the partial strategy $\cmap{\str}{A'}{A}$.  This is also constructed as a copycat strategy; the only difference is that if $O$ makes a move in $A$ that does not occur in $P_{A'}$ then the player $P$ has no reply.  We now claim that $\comp\wk\str=\id_{A'}$.

    Formally:
    \begin{IEEEeqnarray*}{rCl}
      \wk & = & \left\{s\in P_{A\implies A'}\suchthat\textrm{if $|s|$ is even, then $s\vert_A=s\vert_{A'}$}\right\} \\
      \str & = & \left\{s\in P_{A'\implies A}\suchthat\textrm{if $|s|$ is even, then $s\vert_A'=s\vert_{A}$}\right\}
    \end{IEEEeqnarray*}

    To show that $\comp\wk\str=\id_{A'}$, it suffices to show that player $P$'s response, under $\comp\wk\str$, to an $O$-move in the left-hand copy of $A'$ is to copy that move into the right-hand copy of $A'$ and that her response to an $O$-move in the right hand copy is to copy that move into the left hand copy.  This is fairly straightforward to show inductively, using the narrative definition of composition: if $O$ makes a move in the left-hand copy of $A'$, then Player $P$'s response under $\str$ is to copy that move across into $A$.  Then, by $\wk$, Player $P$ copies the move over into the right-hand copy of $A'$, completing her move.

    To go in the other direction, if Player $O$ plays in the right hand copy of $A'$, then Player $P$'s response under $\wk$ is to copy that move into $A$.  Now, since that move came from $A'$ originally, she is able to copy it over into the left-hand copy of $A'$.  Therefore, Player $P$'s overall strategy is the copycat strategy on $A'$.
  \end{proof}

\end{proposition}

We now show that is in fact a characterization of weakenings, in the sense that every strategy with a right inverse is \emph{equivalent} to some weakening strategy.

Explicitly:

\begin{proposition}
  If a morphism $\cmap{\sigma}{A}{B}$ has a right inverse, then there is a weakening $A'$ of $A$ and an isomorphism $\cmap{\hat{\sigma}}{A'}{B}$ such that
    \[
    \begin{tikzcd}
      A \arrow[r, "\sigma"] \arrow[dr, "\wk"']
        & B \arrow[d, leftarrow, "\rotatebox{90}{\(\sim\)}"', "\hat{\sigma}"] \\
      %
        & A'
    \end{tikzcd}
    \]
    commutes.

    \begin{proof}
      Let $\cmap{\sigma}{A}{B}$ be a morphism of games and suppose that $\sigma$ has a right inverse $\tau$ - so $\comp\sigma\tau=\id_B$.  Define
      \[
        P_{A'}=\{\s\vert_A\suchthat \s\in\sigma\}
        \]
      $P_{A'}$ is clearly prefix-closed, so $A'=(M_A,\lambda_A,P_{A'})$ is a well-defined game.

      We claim that $A'$ is a weakening of $A$.  It will suffice to show that if $s\in P_{A'}$ is an $O$-play and $sa\in P_A$ is a $P$-reply, then $sa\in P_{A'}$ (the other conditions follow automatically from the fact that $P_{A'}\subset P_A$).

      Let $s\in P_{A'}$ be an $O$-play.  By the definition of $P_{A'}$, there exists $\s\in \sigma$ such that $\s\vert_A=s$.  We may choose $\s$ minimal, so that the last move made in $\s$ corresponds to the last move played in $s$.  This last move was an $O$-move in $A$, so it is a $P$-move in $A\implies B$.  This means that $\s$ is a $P$-play, and so $\s a\in \sigma$, since $\tau$ is a strategy.  Therefore, $\s a\vert_A=sa$, and so $sa\in P_{A'}$.

      We now define strategies $\cmap{\hat\sigma}{A'}{B}, \cmap{\hat\tau}{B}{A'}$, given as sets of plays by:
      \begin{align*}
        \hat\sigma & = \sigma \\
        \hat\tau & = \tau \cap P_{B\implies A'}
      \end{align*}
      $\hat\tau$ is clearly a valid strategy for $B\implies A'$, and $\hat\sigma$ is a valid strategy for $A'\implies B$ by the definition of $P_{A'}$.

      We claim that $\sigma$ and $\tau$ are inverses and that the diagram given above commutes.

      Since $\comp\sigma\tau=\id_B$, to show that $\comp{\hat\sigma}{\hat\tau}=\id_B$, it suffices to show that $\comp\sigma\tau=\id_B=\comp{\hat\sigma}{\hat\tau}$.  We have
      \begin{align*}
        \comp\sigma\tau & = \{\s\vert_{B,B}\suchthat \s\in \L(B,A,B), \s\vert_{B,A}\in\tau,\s\vert_{A,B}\in\sigma\} \\
        \comp{\hat\sigma}{\hat\tau} & = \{\s\vert_{B,B}\suchthat \s\in \L(B,A',B), \s\vert_{B,A'}\in\hat\tau,\s\vert_{A',B}\in\hat\sigma\}
      \end{align*}

      Since $\hat\tau\subset\tau$ and $\hat\sigma=\sigma$ as sets of plays, it is clear that $\comp{\hat\sigma}{\hat\tau}\subset\comp\sigma\tau$.  Going in the other direction, suppose $\s\in\L(B,A',B)$ is such that $\s\vert_{B,A}\in\tau$ and $\s\vert_{A,B}\in\sigma$.  Then, by definition,
      \[
        \s\vert_A=\s\vert_{A,B}\vert_A\in P_{A'}
        \]
      and so $\s\in\L(B,A',B)$ and $\s\vert_{B,A}\in P_{B\implies A'}$, which implies that $\s\vert_{B,A}\in\hat\tau$.  So $\comp\sigma\tau\subset\comp{\hat\sigma}{\hat\tau}$, and therefore $\comp{\hat\sigma}{\hat\tau}=\comp\sigma\tau=\id_B$.  
    \end{proof}
\end{proposition}

\end{document}

### 2016-10-11 ordinal_games/split-epimorphisms/weakenings.tex
Started Research repository

--- 2016-10-11 ordinal_games/ordinal_games.tex
@@
 
-\input{../common/preamble}
-
-\title{Games with ordinal sequences of moves}
-\author{John Gowers}
-\date{}
+\usepackage[utf8]{inputenc}
+
+\usepackage{graphicx} % support the \includegraphics command and options
+
+\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
+
+%%% PACKAGES
+\usepackage{booktabs} % for much better looking tables
+\usepackage{array} % for better arrays (eg matrices) in maths
+\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
+\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
+\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
+\usepackage{mathtools} % for the all important \coloneqq symbol
+\usepackage{url} % for \url
+\usepackage{IEEEtrantools} % for \IEEEeqnarray
+
+%%% ToC (table of contents) APPEARANCE
+\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
+\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
+\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
+\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!
+
+%% Font things %%
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{stmaryrd}
+\usepackage{mathtools}
+\usepackage{cmll} % Linear logic symbols!
+
+%% Lists %%
+\usepackage{enumerate}
+
+%% Graphics %%
+\usepackage{tikz}
+\usetikzlibrary{cd}
+\usetikzlibrary{patterns}
+\usetikzlibrary{calc}
+
+%% Theorems! %%
+\usepackage{amsthm}
+\theoremstyle{plain} % Theorems, lemmas, propositions etc.
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{fact}[theorem]{Fact}
+\newtheorem{construction}[theorem]{Construction}
+\theoremstyle{definition} % Definitions etc.  Remarks too, because I don't like the way the 'remark' style looks.
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{notation}[theorem]{Notation}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{question}[theorem]{Question}
+
+%% Exercises and answers %%
+\usepackage{answers}
+
+\newtheoremstyle{exercisestyle}% name
+  {6pt}   % ABOVESPACE
+  {6pt}   % BELOWSPACE
+  {\itshape}  % BODYFONT
+  {0pt}       % INDENT (empty value is the same as 0pt)
+  {\bfseries} % HEADFONT
+  {.}         % HEADPUNCT
+  {3pt} % HEADSPACE
+  {}          % CUSTOM-HEAD-SPEC
+
+\theoremstyle{exercisestyle}
+\newtheorem{exercise}{Exercise}
+\newtheorem{answerthm}{Exercise}
+
+\Newassociation{answer}{answerthm}{answers}
+\newcommand{\answerthmparams}{}
+
+%% Changes to enumerate things so they look better %%
+
+\makeatletter
+\def\enumfix{%
+\if@inlabel
+ \noindent \par\nobreak\vskip-\topsep\hrule\@height\z@
+\fi}
+
+\let\olditemize\itemize
+\def\itemize{\enumfix\olditemize}
+\let\oldenumerate\enumerate
+\def\enumerate{\enumfix\oldenumerate}
+
+%% Random crap %%
+\usepackage{xifthen}
+
+\makeatletter
+\def\thm@space@setup{%
+  \thm@preskip=\parskip \thm@postskip=0pt
+}
+\makeatother
+
+\makeatletter
+\newcommand*{\relrelbarsep}{.386ex}
+\newcommand*{\relrelbar}{%
+  \mathrel{%
+    \mathpalette\@relrelbar\relrelbarsep
+  }%
+}
+\newcommand*{\@relrelbar}[2]{%
+  \raise#2\hbox to 0pt{$\m@th#1\relbar$\hss}%
+  \lower#2\hbox{$\m@th#1\relbar$}%
+}
+\providecommand*{\rightrightarrowsfill@}{%
+  \arrowfill@\relrelbar\relrelbar\rightrightarrows
+}
+\providecommand*{\leftleftarrowsfill@}{%
+  \arrowfill@\leftleftarrows\relrelbar\relrelbar
+}
+\providecommand*{\xrightrightarrows}[2][]{%
+  \ext@arrow 0359\rightrightarrowsfill@{#1}{#2}%
+}
+\providecommand*{\xleftleftarrows}[2][]{%
+  \ext@arrow 3095\leftleftarrowsfill@{#1}{#2}%
+}
+\makeatother
+
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
+\newcommand{\Rings}{\catname{CRing}}
+\newcommand{\CAT}{\catname{CAT}}
+\newcommand{\Top}{\catname{Top}}
+\newcommand{\Set}{\catname{Set}}
+\newcommand{\Cont}{\catname{Cont}}
+\newcommand{\Sch}{\catname{Sch}}
+\newcommand{\Rel}{\catname{Rel}}
+\newcommand{\Mod}[1][]{\ifthenelse{\isempty{#1}}{\catname{Mod}}{#1\catname{mod}}}
+\DeclareMathOperator{\sh}{Sh}
+\newcommand{\Sh}[1][]{\ifthenelse{\isempty{#1}}{\sh}{\sh(#1)}}
+\newcommand{\map}[3]{#2\xrightarrow{#1} #3}
+\newcommand*\from{\colon}
+\newcommand{\cmap}[3]{#1\from{}#2\to{}#3}
+\newcommand\oppcat[1]{#1^{\mathrm{op}}}
+\DeclareRobustCommand{\vmap}[3] {\begin{tikzcd} #2 \arrow[d, "#1"] \\ #3 \end{tikzcd}}
+\newcommand{\partref}[1]{(\ref{#1})}
+\newcommand{\intgrpd}[4] {#1 \xrightrightarrows[#3]{#4} #2}
+\DeclareRobustCommand{\bigintgrpd}[4] {\begin{tikzcd}[ampersand replacement=\&] #1 \arrow[r, shift left=0.5ex, "#3"] \arrow[r, shift right=0.5ex, "#4"'] \& #2 \end{tikzcd}}
+
+\usepackage{xspace}
+
+\newcommand{\etale}{\'{e}tale\xspace}
+\newcommand{\Etale}{\'{E}tale\xspace}
+
+\def \inv {^{-1}}
+
+\DeclareMathOperator{\id}{id}
+\DeclareMathOperator{\op}{op}
+\DeclareMathOperator{\pr}{pr}
+\DeclareMathOperator{\pre}{{pre}}
+\DeclareMathOperator{\et}{{\acute{e}t}}
+
+\DeclareMathOperator{\Hom}{Hom}
+\DeclareMathOperator{\Spec}{Spec}
+
+\DeclareMathOperator{\ol}{ol}
+
+\def\presuper#1#2%
+  {\mathop{}%
+   \mathopen{\vphantom{#2}}^{#1}%
+   \kern-\scriptspace%
+   #2} \def\presub#1#2%
+  {\mathop{}%
+   \mathopen{\vphantom{#2}}_{#1}%
+   \kern-\scriptspace%
+   #2}
+
+%% Our things %%
+
+\newcommand{\neggame}[1]{\presuper{\perp}{#1}}
+\newcommand{\tensor}{\otimes}
+\newcommand{\sequoid}{\oslash}
+\newcommand{\varsequoid}{\vartriangleleft}
+\renewcommand{\implies}{\multimap}
+\newcommand{\comp}[2]{#1 \circ #2}
+\newcommand{\cprd}{\sqcup}
+\newcommand{\G}{\mathcal G}
+\newcommand{\suchthat}{\;\colon\;}
+\newcommand{\varsuchthat}{\;\mid\;}
+\newcommand{\esuchthat}{\;.\;}
+\newcommand{\OP}{\{O,P\}}
+\newcommand{\F}{\mathcal F}
+\renewcommand{\L}{\mathcal L}
+\DeclareMathOperator{\wk}{wk}
+\DeclareMathOperator{\weak}{weak}
+\DeclareMathOperator{\str}{str}
+\newcommand{\s}{\mathfrak{s}}
+\renewcommand{\t}{\mathfrak{t}}
+\newcommand{\grel}[1]{\underline{#1}}
+\newcommand{\prefix}{\sqsubseteq}
+
+%% Isomorphism arrows on commutative diagrams %%
+\tikzset{Isom/.style={every to/.append style={edge node={node [sloped, above, allow upside down, auto=false]{$\cong$}}}},
+         Isom'/.style={every to/.append style={edge node={node [sloped, above, allow upside down, auto=false, rotate=180]{$\cong$}}}},
+         Sim/.style={every to/.append style={edge node={node [sloped, above, allow upside down, auto=false]{$\sim$}}}},
+         Sim'/.style={every to/.append style={edge node={node [sloped, above, allow upside down, auto=false, rotate=180]{$\sim$}}}}}
+
+%%% END Article customizations
 
@@
 
-\begin{titlepage} % Shamelessly stolen from the online LaTeX book.
-	\centering
-	{\scshape\LARGE University of Bath \par}
-	\vspace{1cm}
-	{\scshape\Large PhD Confirmation Report \par}
-	\vspace{1.5cm}
-	{\huge\bfseries Games with ordinal sequences of moves \par}
-	\vspace{2cm}
-	{\Large\itshape John Gowers \par}
-	\vfill
-	supervised by\par
-	Dr.~James \textsc{Laird}
-
-	\vfill
-
-% Bottom of the page
-	{\large \today\par}
-\end{titlepage}
-
-\addtocontents{toc}{\protect\enlargethispage{35mm}}
-\tableofcontents
-\thispagestyle{empty}
-
-\setcounter{tocdepth}{2}
-
-\section{Introduction}
-
-\lettrine[image=true, lines=6, findent=3pt, nindent=0pt]{cleos-g.png}{ame Semantics}, or the use of games and strategies to model logical systems and programming languages, has its origins in a model of intuitionistic logic by Lorenzen \cite{lorenzengames} using games.
-Towards the end of the twentieth century, several authors, starting with Blass \cite{blassgames}, realized that certain natural operations on games could be used to model the connectives in Girard's linear logic.
-Major results from this enterprise include:
-\begin{itemize}
-  \item A fully complete categorical semantics for the multiplicative fragment of linear logic, together with the MIX rule, by Abramsky and Jagadeesan \cite{abramskyjagadeesangames}
-  \item A fully complete categorical semantics for the multiplicative fragment of linear logic without the MIX rule, by Hyland and Ong \cite{HylandOngGames}
-  \item A modification of Abramsky and Jagadeesan's construction, giving a fully complete model of the multiplicative-exponential fragment of linear logic, by Baillot, Danos, Ehrhard and Regnier \cite{bion}
-  \item Fully complete models of the negative fragment of linear logic by others, starting with independent work by Curien \cite{curiengames} and Lamarche \cite{lamarchegames}.  
-\end{itemize}
-
-Another major early result was the use of game semantics to give a fully abstract model of the programming language PCF (This result was obtained independently, using different techniques, by Abramsky, Jagadeesan and Malacaria \cite{ajmPcf}, by Hyland and Ong \cite{hoPcf}, and by Nickau \cite{nickauPcf}).
-
-Central to much of the current work on game semantics for linear logic is the treatment of the exponential connective $\oc$.
-Several approaches have been made to model this connective in a game-theoretic way (see Section 3 of \cite{martinsthesis} for a brief survey).
-We shall use the construction from \cite{ajmPcf} and \cite{hyland1997games}: if $A$ is a game, then $\oc A$ is the game formed by playing a countably infinite number of copies of $A$ --- $A_0,A_1,A_2,\dots$ --- in parallel, where only the opponent $O$ may switch games and where neither player may play in game $A_{n+1}$ until a move has been made in game $A_n$.
-
-This definition, and in particular the restriction on the order in which games may be started, allows us to give the game $\oc A$ the structure of the \emph{cofree commutative comonoid} over $A$ \cite{LairdCofCommCom} and gives rise to a \emph{linear exponential comonad} on our category of games.
-The linear exponential comonad \cite{SchalkWhatIs} and the cofree commutative comonoid functor \cite{LafontCofCommCom,MelliesCofCommCom} are both sufficient to model the exponential connective from linear logic.
-
-The restriction that says that the copies of $A$ in $\oc A$ must be opened in order, motivates the following definition \cite{laird02}: if $A,B$ are games, then the \emph{sequoid} $A\sequoid B$ of $A$ and $B$ is the game in which $A$ and $B$ are played in parallel, only the opponent $O$ may switch games, and play must start in $A$.
-It turns out that if $A$ is a game, then the operation $A\sequoid\blank$ gives rise to an endofunctor on the category $\G$ of games, and that the exponential $\oc A$ is the final coalgebra for this endofunctor.
-That is to say, we have a morphism $\cmap{\alpha}{\oc A}{A\sequoid\oc A}$ such that whenever $\cmap{\sigma}{B}{A\sequoid B}$ is a morphism, there is a unique morphism $\cmap{\fcoal{\sigma}}{B}{\oc A}$ such that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\sigma"] \arrow[d, "\fcoal\sigma"']
-      & A\sequoid B \arrow[d, "A\sequoid\fcoal\sigma"] \\
-    \oc A \arrow[r, "\alpha"']
-      & A\sequoid\oc A
-  \end{tikzcd}
-  \]
-Existing proofs of this fact in a finitary games setting (e.g., in \cite{martinsthesis}) make implicit use of the fact that $\oc A$ is the limit of the sequence
-\[
-  I \leftarrow A \leftarrow A\sequoid A \leftarrow A\sequoid(A\sequoid A) \leftarrow \dots
-  \]
-Indeed, any finite-length play in $\oc A$ must involve only finitely many copies of $A$, so exists as a play in $(A\sequoid\blank)^n I$ for some $n$.
-
-On the other hand, when we start imposing winning conditions upon infinite plays, $\oc A$ is no longer the limit of the sequence above.
-Indeed, define a game $\co A$ which is exactly like $\oc A$ except that all infinite plays that contain moves from infinitely many copies of $A$ are wins for the player $P$, regardless of who has won the individual games.
-This game still admits a cone over the sequence above, since any play occurring in $(A\sequoid\blank)^nI$ for some $n$ must involve only finitely many copies of $A$.
-Moreover, it does not admit a morphism of cones to $\oc A$.
-In fact, in the infinitary setting, $\co A$, and not $\oc A$, is the limit of the above sequence.
-
-\[
-  \begin{tikzcd}
-    \co A \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr] \arrow[drrrr, phantom, yshift=0.5em, "\cdots"]
-      &
-        &
-          &
-            & \\
-    I
-      & A \arrow[l]
-        & A\sequoid A \arrow[l]
-          & A\sequoid(A\sequoid A) \arrow[l]
-            & \cdots \arrow[l]
-  \end{tikzcd}
-  \]
-Applying the functor $A\sequoid\blank$ to the cone from $\co A$ gives rise to another cone over the sequence:
-\[
-  \begin{tikzcd}
-    %
-    & A\sequoid\co A \arrow[dl] \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr, phantom, yshift=0.5em, "\cdots"]
-        &
-          &
-            & \\
-    I
-      & A \arrow[l]
-        & A\sequoid A \arrow[l]
-          & A\sequoid(A\sequoid A) \arrow[l]
-            & \cdots \arrow[l]
-  \end{tikzcd}
-  \]
-and therefore a morphism $A\sequoid\co A\to \co A$.  We can then continue to apply the functor $A\sequoid\blank$ to build up a second layer of the sequence:
-\[
-  \begin{tikzcd}
-    \co A \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr] \arrow[drrrr, phantom, xshift=1em, "\cdots"]
-      & A\sequoid\co A \arrow[l]
-        & A\sequoid(A\sequoid \co A) \arrow[l]
-          & A \sequoid(A\sequoid(A\sequoid\co A)) \arrow[l]
-            & \cdots \arrow[l] \\
-    I
-      & A \arrow[l]
-        & A\sequoid A \arrow[l]
-          & A\sequoid(A\sequoid A) \arrow[l]
-            & \cdots \arrow[l]
-  \end{tikzcd}
-  \]
-What is the limit of this entire diagram?
-An $O$-winning infinite play $s$ in $(A\sequoid\blank)^n \co A$ may be identified with an $O$-winning play in $\oc A$ such that either the opponent $O$ wins in one of the games $A_1,\dots,A_n$ or that only finitely many copies of $A$ are opened.
-It follows that the limit of the diagram \emph{is} the final coalgebra $\oc A$.
-
-The diagrams we have drawn above are special cases of the \emph{final sequence} \cite{finalseq}: given a category $\C$ with a terminal object $1$ and enough limits (in a sense which will become clear) and an endofunctor $\cmap{\F}{\C}{\C}$, we may construct an ordinal-indexed sequence
-\[
-  1, \F(1), \F^2(1),\dots \F^\omega(1), \F^{\omega+1}(1),\dots,\F^\delta(1),\dots
-  \]
-together with commuting morphisms $\F^\gamma(1)\to\F^\delta(1)$ for $\delta\le\gamma$, by setting $\F^{\delta+1}(1) = \F(\F^\delta(1))$ and letting $\F^\mu(1)$ be the limit of the diagram formed by the $\F^\gamma(1)$ for $\gamma<\mu$ if $\mu$ is a limit-ordinal.
-It is well known that if $\delta$ is an ordinal and the map
-\[
-  \F^{\delta+1}(1)\to\F^{\delta}(1)
-  \]
-is an isomorphism, then the inverse of this isomorphism exhibits $\F^{\delta}(1)$ as the final coalgebra of $\F$.  In this case, we say that the final sequence \emph{stabilizes at $\delta$}.
-
-In the case of finitary games, then, we have
-\[
-  \oc A\cong(A\sequoid\blank)^\omega(I)
-  \]
-and in the infinitary case, we have
-\[
-  \oc A\cong(A\sequoid\blank)^{\omega2}(I)
-  \]
-The eventual goal of this research is to study the behaviour of the final sequence of the functor $A\sequoid\blank$ in categories of games.
-Since the sequence stabilizes so early on for existing categories of games, this question is not very interesting in that setting.
-We want to modify our definitions of games in such a way that this final sequence will take much longer to stabilize, and it turns out that one way to do that is to allow plays of transfinite length.
-
-Games with ordinal sequences of moves are not a new idea.
-They have, for example, been studied in \cite{longgamesbook} from the point of view of determinacy.
-Even in game semantics, as we shall see, we may identify games in which we impose a winning condition on the infinite plays with games in which the players are allowed to make plays of length $\omega$ -- we shall call these $(\omega+1)$-games, in contrast to the finitary games, which we shall call $\omega$-games.
-Allowing plays whose lengths are longer transfinite ordinals will give rise to a richer variety of plays, which will be reflected in the final sequence.
-
-One important aspect of the shift from finite to transfinite plays is that the idea of a \emph{play} or \emph{position} takes on a new importance, in contrast to the finitary case, where we can define everything in terms of \emph{moves}.
-Normally, a move is designated as either a $P$-move or an $O$-move; we will extend this so that every position is either a $P$-position or an $O$-position.
-A position $s$ will be an ordinal-indexed sequence of moves; if there is a last move $a$, then $s$ is a $P$-position or an $O$-position according as $a$ is a $P$-move or an $O$-move.
-If the length of $s$ is a limit ordinal, however, then its sign cannot be determined from the signs of its constituent moves.
-This is useful if we want to model games with a winning condition as $(\omega+1)$-games: a play of length $\omega$ in a game corresponds to an infinite play in that game, and its designation as a $P$-position or $O$-position is essentially the same thing as saying whether it is a $P$-winning or $O$-winning play.
-
-This approach is similar to that of Blass \cite{blassgames}, and indeed our treatment of $P$-positions and $O$-positions under the connectives will follow his approach.
-For example, a position $s$ in a tensor product $A\tensor B$ is a $P$-position if and only if its restrictions to $A$ and $B$ are both $P$-positions.
-
-To avoid certain mathematical difficulties, we shall follow Curien, Lamarche and others by requiring that our games be \emph{negative} -- that is, they must always begin with an $O$-move.
-In fact, we shall go further than that: under the usual alternating condition, saying that $O$ always starts is the same thing as requiring that the empty position $\emptyplay$ is a $P$-position.
-In order to avoid problems constructing our category, we shall need to require that \emph{all} positions whose lengths are limit ordinals be $P$-positions.
-We shall call games satisfying this property \emph{completely negative}.
-
-This condition on the sign of games allows us to construct a well-behaved category of games, but it has one serious problem that occurs as soon as we consider games with transfinite-length plays: if $A,B$ are completely negative games, then the linear implication $A\implies B$ is not necessarily completely negative.
-
-We want $A\implies B$ to be the internal hom in our closed monoidal category, so we need to find a way around this.
-Our solution is to construct, for every game $A$, a `minimal extension' $A^{\cn}$ of $A$ that is completely negative.
-We prove various results about the relationship $A^{\cn}$ and $A$ that make this precise and then use them to show that the game $A\impliescn B\coloneqq (A\implies B)^{\cn}$ does give rise to a closed monoidal structure in our category.
-We also give a tentative way of constructing a category whose objects are \emph{all} games, not just the completely negative ones, and use our results to show that this category is in fact equivalent to our existing category of completely negative games.
-
-Having constructed a symmetric monoidal closed category of games, we introduce the sequoid operator and the exponential, and study the final sequence.
-We shall characterize the exponential $\oc A$ as a final coalgebra for the functor $A\sequoid\blank$ and use this characterization to prove that $\oc A$ admits the structure of a cofree commutative comonoid on $A$.
-Then we turn to the final sequence.
-This section will involve some material that is more ordinal-theoretic than game-theoretic; we assign an ordinal \emph{rank} to a (transfinite) sequence of natural numbers and then show that this idea of rank can be used to characterize each term of the final sequence for a functor of the form $A\sequoid\blank$.
-We will show that the reason that the final sequences converge so quickly for finitary games and win-games is that a sequence of length $\omega$ necessarily has low rank: once we allow longer plays, we can get sequences with higher ranks and the final sequence will carry on for longer.
-
-\subsection{Original contribution}
-
-Games with ordinal sequences of enablings have been studied by Laird from a Game Semantics point of view \cite{LairdOrdinalGames}, but to my knowledge this is the first transfinite games category built in the tradition of Abramsky and Jagadeesan.
-Passing to transfinite games causes problems when we try to show that our category is monoidal closed, and we have to come up with new techniques in order to get a monoidal closed category (see Sections \ref{TransSMCCSex} to \ref{ImpliesCnSex}).
-
-The characterization of the final coalgebra for the functor $A\sequoid\blank$ in a transfinite games category is new, though the behaviour in finitary game categories and win-game categories is well known.
-Our definition of the rank of a sequence of natural numbers is heavily motivated by the game semantics, so it is likely that this is new too (though similar constructions of ordinal ranks of objects are common in mathematics).
-
-Otherwise, most of the material in this report is a straightforward translation of the existing game semantics of Abramsky, Jagadeesan, Hyland, Ong, Curien, Lamarche and so on into the transfinite setting.
-
-\subsection{Conventions}
-
-I shall denote the composition of morphisms $A\xrightarrow{\sigma}B\xrightarrow{\tau}C$ by $\comp\tau\sigma$, the disjoint union of two sets $X,Y$ by $X\cprd Y$ and the corresponding copairing of two functions $\map{f}{X}{Z},\map{g}{Y}{Z}$ by $\cmap{f\cprd g}{X\cprd Y}{Z}$.
-
-Following the $\forall$belard/$\exists$loise convention that is sometimes used for Opponent/Player, I shall refer to the opponent $O$ as `he' and the player $P$ as `she' throughout.
-
-\subsection{Acknowledgements}
-
-It goes without saying that I owe my biggest debt of gratitude for the material in this report to my supervisor, Jim Laird.
-Dr Laird introduced me to Game Semantics a year ago and suggested my initial direction of research in the subject, and his insights and instinct for the subject have been invaluable in the development of the material contained in this report, and in the preparation of the report itself -- particularly when things were going wrong.
-Dr Laird gave me some extremely useful feedback on an earlier draft of this report and supplied some of the details for the material in section \ref{SeqExpIsCofCommCom}.
-
-I am indebted to all the authors listed in the Bibliography, but I single out the seminal papers of Blass \cite{blassgames} and Abramsky-Jagadeesan \cite{abramskyjagadeesangames} for their development of the subject and their clear presentation of their full completeness results, the set of notes on Game Semantics by Martin Hyland \cite{hyland1997games} and the excellent online notes by Andrea Schalk \cite{Schalk2001GsNotes,SchalkWhatIs}.
-I also single out the PhD thesis of Martin Churchill \cite{martinsthesis}, prepared under Dr Laird's supervision.
-The work in this report can be seen as a partial sequel to some of Dr Churchill's work, and the clear presentation in his thesis has greatly helped in this task.
-
-I would also like to extend my thanks to Paul Blain Levy for his work organizing the GaLoP 2016 conference and the Midlands Graduate School 2016, both of which I attended this year.
-I presented some of this material at GaLoP and the questions and comment I received there have shaped the course of this work.
-Thanks also to Alexander Kurz for his lectures on coalgebra at the Midlands Graduate School.
-
-Thanks go to all my friends and family members who have patiently supported me while I embarked on this research.
-Thank you to CN for designing the splendid letter `G' (complete with $\sequoid$ symbols!) that features at the beginning of this introduction.
-
-\section{Our starting category of games}
-
-Before studying games with transfinite sequences of moves, we shall illustrate some of the choices we have made by defining a category of games with finite sequences of moves.
-We have chosen these definitions because they extend particularly well to the transfinite case.
-
-\subsection{Games and strategies}
-
-We shall use the notation introduced in \cite{abramskyjagadeesangames} to describe games.  All our games $A$ will have, at their heart, the following three pieces of information:
-\begin{itemize}
-  \item A set $M_A$ of possible moves
-  \item A function $\cmap{\lambda_A}{M_A}{\OP}$ assigning to each move the player who is allowed to make that move
-  \item A prefix-closed set $P_A\subset M_A^*$ of finite sequences of moves.
-\end{itemize}
-We shall normally insist on an \emph{alternating condition} on $P_A$:
-\begin{description}
-  \item[Alternating condition] If $a,b\in M_A$ are moves and $s\in M_A^*$ is a sequence of moves such that $sa, sab\in P_A$, then $\lambda_A(a)=\neg\lambda_A(b)$.
-\end{description}
-
-As in \cite{abramskyjagadeesangames}, we identify a \emph{strategy} for a game $A$ with the set of sequences of moves that can occur when player $P$ is playing according to that strategy so that a typical definition of a (partial) strategy might be a set $\sigma\subset P_A$ such that (for all $s\in M_A^*, a,b\in M_A$):
-\begin{itemize}
-  \item $\emptyplay\in\sigma$ (ensures that $\sigma$ is non-empty)
-  \item If $sa\in\sigma$, $\lambda_A(a)=P$ and $sab\in P_A$ then $sab\in\sigma$ ($\sigma$ contains all legal replies by player $O$)
-  \item If $s,sa,sb\in\sigma$ and $\lambda_A(a)=P$ then $a=b$ ($\sigma$ contains at most one legal reply by player $P$)
-\end{itemize}
-
-We can impose additional constraints on $\sigma$ that will ensure that $\sigma$ is total, strict, history free and so on.
-The definition given immediately above is not the only definition of a strategy found in the literature, however.
-For example, the games described in \cite{abramskyjagadeesangames} have the curious property that the set $P_A$ may contain plays that cannot actually occur when $A$ is being played; in particular, all plays must start with a move by player $O$, but the set $P_A$ may contain positions that start with a $P$-move.
-These plays do not affect the strategies for $A$, but they might come into play if we perform operations on $A$ such as forming the negation $\neg A$ or the implication $A\implies B$.
-
-This behaviour is made implicit in Abramsky and Jagadeesan's definitions, which do not impose any conditions upon the set $P_A$ beyond the basic alternation condition given above, but which mandate that any play occurring \emph{in a strategy} must begin with an $O$-move.
-For the sake of clarity, we adopt a different, but completely equivalent, approach.
-For a game $A$, we define a set $L_A$, regarded as the set of \emph{legal plays} occurring in $P_A$.
-In some games models, such as that found in \cite{blassgames}, $L_A$ may be defined to be the whole of $P_A$, while in \cite{abramskyjagadeesangames} it is defined to be that subset of $P_A$ consisting of plays that begin with an $O$-move.
-
-The point of specifying $L_A$ separately is that it allows us to unify the definition of a \emph{strategy}, while making clearer the behaviour observed above, whereby certain plays in $P_A$ may not occur `in normal play'; this behaviour was previously only implicit in the definition of a strategy.
-Our unified definition then becomes:
-
-\begin{definition}
-  If $A=(M_A,\lambda_A,P_A)$ is a game and $L_A$ is its associated set of legal plays (in a particular games model) then a (partial) \emph{strategy} for $A$ is a subset $\sigma\subset L_A$ such that for all $s\in L_A$ and all $a, b\in M_A$:
-  \begin{itemize}
-    \item $\emptyplay\in\sigma$
-    \item If $s\in\sigma$ and $a$ is an $O$-move, and if $sa\in L_A$, then $sa\in\sigma$
-    \item If $s\in\sigma$ and $a,b$ are $P$-moves, and if $sa,sb\in\sigma$, then $a=b$
-  \end{itemize}
-\end{definition}
-
-\subsection{Positive and negative games, ownership of plays and connectives}
-
-Abramsky-Jagadeesan games, as described in \cite{abramskyjagadeesangames}, may admit both plays that start with a $P$-move and plays that start with an $O$-move.
-Other games models, such as those found in \cite{blassgames} and \cite{curiengames}, are more restrictive.
-The games in \cite{curiengames} only contain plays starting with an $O$-move.
-The plays in \cite{blassgames} may start with either a $P$-move or an $O$-move, but a play starting with a $P$-move and a play starting with an $O$-move may not occur in the same game.
-
-\begin{definition}
-  We say that a game $A=(M_A,\lambda_A,P_A)$ is \emph{positive} if every play in $P_A$ begins with a $P$-move.
-  We say that $A$ is \emph{negative} if every play in $P_A$ begins with an $O$-move.
-\end{definition}
-
-So the Curien model found in \cite{curiengames} admits only negative games, the Blass model in \cite{blassgames} admits positive and negative games, while the Abramsky-Jagadeesan model found in \cite{abramskyjagadeesangames} admits not only positive and negative games, but also games that are neither negative nor positive.
-We shall now examine the reasons for and drawbacks of each of these choices.
-
-The earliest games model, found in \cite{conwaygames}, did not include a definition of which player is to move at a given position; rather, games are defined recursively as pairs of games $\{L|R\}$, where $L$ represents the positions that the left player may move into, while $R$ represents the positions that the right player may move into.
-Blass's definition departs completely from this tradition; now, at every position $s$ only one of the two players is allowed to move; extending this logic on to the empty position $\emptyplay$, it follows that all games are either positive or negative.
-This property means that we may freely define $L_A=P_A$, since there is never any question about whose turn it is to play.
-By contrast, if we were to define $L_A=P_A$ for Abramsky-Jagadeesan games, then a strategy might end up containing two branches, one of plays beginning with an $O$-move and one of plays beginning with a $P$-move, which is undesirable.
-The alternative definition of $L_A$ avoids this problem.
-
-In the case of a Blass game $A$, we may define a function $\zeta_A\colon P_A\to\OP$ that says which player owns each play; the idea is that if we are in position $s$, then the next player to move is given by $\neg\zeta_A(s)$; i.e., the opposing player to the player who has just made the move.
-One might want to define $\zeta_A$ by setting $\zeta_A(sa)=\lambda_A(a)$, so that ownership of a play is decided by who has made the last move in the play, but this definition does not extend in an obvious way to the empty position $\emptyplay$ (and, as we shall see in the next chapter, it does not extend to plays over limit ordinals).
-In this case, $\zeta_A(\emptyplay)$ is part of the game's data, and it determines whether the game is positive or negative: if $\zeta_A(\emptyplay) = P$ then all plays must start with an $O$-move, and the game is negative -- and vice versa.
-
-An important question then arises: how should we extend the function $\zeta_A$ to games formed from connectives?
-The solution adopted by Blass is to use binary conjunctions to deduce the ownership of a play from the ownership of the restrictions of that play to the two component games.
-In the case of the tensor product $A\tensor B$ of two games $A$ and $B$, we define $\cmap{\zeta_{A\tensor B}}{P_{A\tensor B}}{\OP}$ by setting
-\[
-  \zeta_{A\tensor B}(s) = (\zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B))
-  \]
-where $\cmap{\wedge}{\OP\times \OP}{\OP}$ is as in Figure \ref{truthtables}.
-
-\begin{figure}[h]
-  \begin{center}
-    $\begin{array}{cc|c}
-      a & b & a \wedge b \\
-      \hline
-      O & O & O \\
-      O & P & O \\
-      P & O & O \\
-      P & P & P
-    \end{array}$
-    \quad
-    $\begin{array}{cc|c}
-      a & b & a \vee b \\
-      \hline
-      O & O & O \\
-      O & P & P \\
-      P & O & P \\
-      P & P & P
-    \end{array}$
-    \quad
-    $\begin{array}{cc|c}
-      a & b & a \Rightarrow b \\
-      \hline
-      O & O & P \\
-      O & P & P \\
-      P & O & O \\
-      P & P & P
-    \end{array}$
-    \caption{Truth tables for binary conjunctions on $\OP$}
-    \label{truthtables}
-  \end{center}
-\end{figure}
-
-Similarly, we may extend $\zeta$ to the implication $A\implies B$ and the par $A\parr B$ by setting
-\begin{align*}
-  \zeta_{A\implies B}(s)=(\zeta_A(s\vert_A)\Rightarrow \zeta_B(s\vert_B))\\
-  \zeta_{A\parr B}(s) = (\zeta_A(s\vert_A) \vee \zeta_B(s\vert_B))
-\end{align*}
-
-Note that if we use these definitions then the owner $\zeta_C(sa)$ of a play $sa$ might not correspond to the player $\lambda_C(a)$ who played the last move $a$.
-For example, let $A,B$ be two positive games and form their tensor product $A\tensor B$.
-Then we have
-\[
-  \zeta_{A\tensor B}(\emptyplay) = (\zeta_A(\emptyplay) \wedge \zeta_B(\emptyplay)) = O \wedge O = O
-  \]
-and so $A\tensor B$ is a positive game.  Player $P$ plays an opening move in one of the two games - let us say she plays the move $a$ in the game $A$.  But then we have
-\[
-  \zeta_{A\tensor B}(a) = (\zeta_A(a) \wedge \zeta_B(\emptyplay)) = P \wedge O = O
-  \]
-In other words, it is still player $P$'s turn to play!
-Blass embrace this possibility and allows player $P$ to make these two moves.
-In his paper, he introduces the notions of \emph{strict} and \emph{relaxed} games, where the strict games are the objects of study but the relaxed games are often used since they allow more manipulations.
-In this case, the game $A\tensor B$ is defined as a relaxed game that might not satisfy the alternating condition; in the process of converting it into a strict game, these two opening moves by player $P$ are combined into a single move.
-
-This `double move' can only occur at the start of the game, and Blass treats it as a special case in his proofs.
-Perhaps unsurprisingly, this inconsistency causes major problems if we try to compose strategies.
-We do not get an associative composition of strategies for $A\implies B$ with strategies for $B\implies C$ and so we do not get a categorical semantics.
-An example of the failure of associativity in Blass's games model is given towards the end of \cite{abramskyjagadeesangames}.
-
-By contrast, Abramsky-Jagadeesan games may admit moves by both players at the same position (specifically, at the beginning of the game, before any moves have been played), but this does not cause problems since we insist that our legal plays start with an $O$-move and be strictly alternating.
-The authors of \cite{abramskyjagadeesangames} note that their model can be considered as an intermediate between Conway's games, where the position tells you nothing about which player is to move, and Blass games, where the position completely determines which player is to move.
-In Abramsky-Jagadeesan games, one can deduce which player is to move (by looking at which player made the last move) in every position except the empty starting position.
-
-In the Abramsky-Jagadeesan model, a positive game is an immediate win to player $P$, since player $O$ has no legal move to start the game off.
-As we noted before, this does not mean that the content of a positive game is meaningless, since we can use connectives to `unlock' these illegal plays.
-For example, if $Q$ is a positive game and $N$ is a negative game then $Q\parr N$ is a negative game, and the possible positions in $Q$ are now all achievable.
-
-Curien's game model (\cite{curiengames}) is similar to Abramsky's and Jagadeesan's, but involves only negative games.
-The only slight problem is that negative Abramsky-Jagadeesan games are not closed under implication: if $N,L$ are negative games then $N\implies L$ may be neither negative nor positive.
-We may fix this by modifying the definition of $N\implies L$ so that we delete from $P_{N\implies L}$ all plays that start with a $P$-move - or, equivalently, by requiring that all plays start in $L$.
-This is the approach taken in \cite{martinsthesis}, where it fits well with the paper's treatment of the \emph{sequoid} operator $\sequoid$, which is a version of the tensor product that has been modified so that play is required to start in the left-hand game.
-
-Our approach will be similar to that of Curien's in that we will admit only negative games as objects of our category, but we will also incorporate elements of Blass's model: each position $s$ in our game will be designated either an $O$-position or a $P$-position via a function $\zeta$ and we will extend $\zeta$ to the connectives using the truth tables in Figure \ref{truthtables}.
-We shall start by developing the theory of finitary games in order to illustrate our approach, but it will not be until we start considering transfinite games that we see the value of this aspect of Blass's semantics: transfinite games may contain many non-empty plays that have no last move and we will want to designate them as $P$-positions or $O$-positions so that we know which player moves next.
-
-\subsection{Our definition of games and strategies}
-
-\begin{definition}
-  A \emph{game} is a triple $(M_A,\lambda_A,\zeta_A,P_A)$ where
-  \begin{itemize}
-    \item $M_A$ is a set of moves,
-    \item $\cmap{\lambda_A}{M_A}{\OP}$ is a function that assigns a player to each move,
-    \item $P_A\subset M_A^*$ is a non-empty prefix-closed set of plays that can occur in the game and
-    \item $\cmap{\zeta_A}{P_A}{\OP}$ is a function that assigns a player to each position
-  \end{itemize}
-  such that
-  \begin{itemize}
-    \item If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.
-    \item If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s)=\neg\zeta_A(sa)$.
-  \end{itemize}
-\end{definition}
-
-\begin{remark}[Notes on the definition]
-  Given a game $A=(M_A,\lambda_A,\zeta_A,P_A)$, define $b_A=\neg\zeta_A(\emptyplay)$.  Then every play in $P_A$ must start with a $b_A$-move, so $A$ is either positive or negative.
-
-  Note that $\zeta_A$ is now completely specified by $\lambda_A$ and $b_A$, so we could have specified our games more efficiently by replacing $\zeta_A$ with $b_A$ in our definition, as done in \cite{martinsthesis}.
-The slightly more unwieldy $\zeta_A$ will be useful when we come to extend our games over the ordinals, though, so we retain it.
-
-  If $a\in M_A$ then we may recover $\lambda_A(a)$ from $\zeta_A$ so long as $a$ occurs in some play in $P_A$.
-Since moves that can never be played do not affect the game at all, we do not really need $\lambda_A$ in our definition, but we keep it to make the connection to earlier work clearer.
-
-  If $a\in M_A$ and $\lambda_A(a)=O$, we call $a$ an \emph{$O$-move}.
-If $\lambda_A(a)=P$, we call $a$ a \emph{$P$-move}.
-If $s\in P_A$ and $\zeta_A(s)=O$, we call $s$ an \emph{$O$-play} or \emph{$O$-position}.
-If $\zeta_A(s)=P$, we call $s$ a \emph{$P$-play} or \emph{$P$-position}.
-\end{remark}
-
-We give the usual definition of a strategy as an appropriate subset of $P_A$, where we have identified the strategy with the set of all plays that can arise when player $P$ plays according to that strategy:
-
-\begin{definition}
-  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  A \emph{strategy} for $A$ is a non-empty prefix-closed subset $\sigma\subset P_A$ such that:
-  \begin{itemize}
-    \item If $a\in P_A$ is an $O$-move and $s\in\sigma$ is a $P$-position such that $sa\in P_A$, then $sa\in\sigma$.
-    \item If $s\in\sigma$ is an $O$-position and $a,b\in M_A$ are $P$-moves such that $sa,sb\in\sigma$, then $a=b$.
-  \end{itemize}
-\end{definition}
-
-The definition above will be the most technically useful, but it is also convenient to give a strategy by a partial function that tells player $P$ which move to make in each $O$-position.
-If we write $P_A^-=\zeta_A\inv(\{O\})$ for the set of all $O$-positions and $M_A^+=\lambda_A\inv(\{P\})$ for the set of all $P$-moves, then the strategy $\sigma$ above gives rise to a partial function $\hat\sigma\from P_A^-\pfun M_A^+$ given by:
-\[
-  \hat\sigma(s)=
-  \begin{cases}
-    a & \textrm{if $a\in M_A^+$ and $sa\in P_A$}\\
-    \textrm{undefined} & \textrm{if $sb\not\in P_A$ for all $b\in M_A^+$}
-  \end{cases}
-  \]
-The second condition on strategies tells us that this is well defined.
-Going in the other direction, if we are given a partial function $f\from P_A^-\pfun M_A^+$  then we can define a strategy $\overline{f}$ by
-\[
-  \overline f = \{s\in M_A^*\suchthat \textrm{for all $ta\prefix s$ with $\zeta_A(t)=O$, $f(t)$ is defined and equal to $a$}\}
-  \]
-
-\subsection{Connectives}
-
-Our definitions of connectives on games are as in \cite{blassgames}.
-
-\begin{definition}
-  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  The negation of $A$, $\neggame{A}$, is the game formed by interchanging the roles of the two players.
-  \begin{itemize}
-    \item $M_{\bneggame A}=M_A$
-    \item $\lambda_{\bneggame A} = \comp\neg{\lambda_A}$
-    \item $\zeta_{\bneggame A} = \comp\neg{\zeta_A}$
-    \item $P_{\bneggame A} = P_A$
-  \end{itemize}
-\end{definition}
-
-It follows immediately from the definitions that $\neggame A$ is a well formed game.
-
-We now define the tensor product $A\tensor B$, the par $A\parr B$ and the linear implication $A\implies B$ of two games.
-All these games are obtained by playing $A$ and $B$ in parallel, so they all have the same set of moves:
-\[
-  M_{A\tensor B} = M_{A\parr B} = M_{A\implies B} = M_A \cprd M_B
-  \]
-
-Ownership of moves is decided via the obvious co-pairing functions:
-\begin{IEEEeqnarray*}{c}
-  \lambda_{A\tensor B} = \lambda_{A\parr B} = \lambda_A \cprd \lambda_B\\
-  \lambda_{A\implies B} = (\neg\circ\lambda_A) \cprd \lambda_B
+\section{The Hyland-Schalk functor $\G\to\Rel$}
+\label{hylandschalke}
+
+Let $\G$ denote an appropriate category of games and strategies, and let $\Rel$ denote the category of sets and relations.
+It is known (Hyland, Schalk, 1996) that the following define a functor $\cmap{\F}{\G}{\Rel}$:
+
+\begin{IEEEeqnarray*}{CCC}
+  \F(A) & = & P_A \\
+  \F\left(\map{\sigma}{A}{B}\right) & = & \{(\s\vert_A, \s\vert_B)\suchthat \s\in\sigma\textrm{ is a $P$-play}\}
 \end{IEEEeqnarray*}
 
-We define the set $P_A\|P_B$ to be the set of all plays in $(M_A \cprd M_B)^*$ whose $M_A$-component is a play from $P_A$ and whose $M_B$-component is a play from $P_B$:
-\[
-  P_A\|P_B = \{s\in (M_A\cprd M_B)^*\suchthat s\vert_A\in P_A,\; s\vert_B\in P_B\}
-  \]
-
-We are now in a position to define $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$ as functions $P_A\|P_B\to\OP$:
-\begin{IEEEeqnarray*}{rCl}
-  \zeta_{A\tensor B}(s) & = & \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \\
-  \zeta_{A\parr B}(s) & = & \zeta_A(s\vert_A) \vee \zeta_B(s\vert_B) \\
-  \zeta_{A\implies B}(s) & = & \zeta_A(s\vert_A) \Rightarrow \zeta_B(s\vert_B)
-\end{IEEEeqnarray*}
-
-(Here, $\wedge$, $\vee$ and $\Rightarrow$ are as in Figure \ref{truthtables}.)
-
-As things stand, $P_A\|P_B$ is not a valid set of plays for our $\lambda$ and $\zeta$ functions.
-The first problem is that $P_A\|P_B$ contains plays which are not alternating with respect to $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$.
-The second problem is that the $\zeta$ and $\lambda$ functions do not always agree with one another.
-For example, suppose that $Q,R$ are two positive games.
-So we have $\zeta_Q(\emptyplay) = \zeta_R(\emptyplay) = O$.
-Then $\zeta_{Q\tensor R}(\emptyplay) = O\wedge O = O$.
-But now suppose that player $P$ can make an opening move $q$ in $Q$.
-Then we have
-\[
-  \zeta_{Q\tensor R}(q) = \zeta_Q(q) \wedge \zeta_R(\emptyplay) = P \wedge O = O
-  \]
-but $\lambda_{Q\tensor R}(q) = P$.
-
-Our solution is to throw away some plays from $P_A\| P_B$ so that what remains satisfies the alternating condition and the condition on the $\lambda$ and $\zeta$ functions.
-
-\begin{definition}
-  Let $M$ be a set, let $P\subset M^*$ be prefix closed and let $\cmap{\lambda}{M}{\OP},\cmap{\zeta}{P}{\OP}$ be functions.
-If $s\in P$, we say that $s$ is \emph{alternating with respect to $\zeta$} if the set of prefixes of $s$ satisfies the alternating condition: if $t,ta\prefix s$, then $\zeta(t) = \neg\zeta(ta)$.
-
-  We say that $s$ is \emph{well formed with respect to $\lambda,\zeta$} if whenever $ta\prefix s$, for some $a\in M$, we have $\zeta(ta)=\lambda(a)$.
-
-  Now let $A,B$ be games.  We define:
-  \begin{IEEEeqnarray*}{rCl}
-    P_{A\tensor B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\tensor B}$ \\ $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$}}\right\} \\
-    P_{A\parr B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\parr B}$ \\ $s$ is well formed with respect to $\zeta_{A\parr B},\lambda_{A\parr B}$}}\right\} \\
-    P_{A\implies B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\implies B}$ \\ $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$}}\right\}
-  \end{IEEEeqnarray*}
-\end{definition}
-
-\begin{definition}
-  We define:
-  \begin{IEEEeqnarray*}{cCc}
-    A\tensor B & = & (M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B}) \\
-    A\parr B & = & (M_{A\parr B}, \lambda_{A\parr B}, \zeta_{A\parr B}, P_{A\parr B}) \\
-    A\implies B & = & (M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})
-  \end{IEEEeqnarray*}
-\end{definition}
-
-\begin{proposition}
-  $A\tensor B$,$A\parr B$,$A\implies B$ are well formed games.
-Moreover, $P_{A\tensor B}$ is the largest subset $X\subset P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, X)$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.
-  \begin{proof}
-    We will prove the proposition for $A\tensor B$; the other two cases are entirely similar.
-Alternatively, observe that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$ and $A\implies B = \neggame A \parr B$.
-
-    For $A\tensor B$, it suffices to show that $P_{A\tensor B}$ is alternating with respect to $\zeta_{A\tensor B}$, since every $s\in P_{A\tensor B}$ is well-formed by definition.
-Suppose $s,sa\in P_{A\tensor B}$; then $s,sa\prefix sa$; since $sa$ is alternating with respect to $\zeta_{A\tensor B}$, it follows that $\zeta_{A\tensor B}(s) = \neg\zeta_{A\tensor B}(sa)$.
-
-    For the second part of the proposition, suppose that $V\subset P_A\|P_B$ is prefix-closed and satisfies the alternating condition with respect to $\zeta_{A\tensor B}$ and that every $s\in V$ is well-formed with respect to $\lambda_{A\tensor B},\zeta_{A\tensor B}$.
-We need to show that $V\subset P_{A\tensor B}$, for which it will suffice to show that every $s\in V$ is alternating.
-This is easy to see: since $V$ is prefix closed, the set of all prefixes of $s$ is a subset of $V$, and so it satisfies the alternating condition with respect to $\zeta_{A\tensor B}$.
-  \end{proof}
-\end{proposition}
-
-A design feature of the connectives $\tensor,\parr,\implies$ is that only player $O$ may switch games in $A\tensor B$, while only player $P$ may switch games in $A\parr B$ and $A\implies B$.
-The $\implies$ case follows immediately from the $\parr$ case by noting that $A\implies B = \neggame A\parr B$, and the $\parr$ case then follows from the $\tensor$ case by observing that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$.
-Thus, it will suffice to prove the following proposition for the tensor product:
-
-\begin{proposition}
-  \label{WhoSwitchesGames}
-  Let $A,B$ be games.  Suppose $s\in P_{A\implies B}$, $a\in M_A$ and $b\in M_B$.  Then:
-
-  i) If $sab\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(b)=O$
-
-  ii) If $sba\in P_{A\tensor B}$ then $\lambda_{\tensor B}(a)=O$.
-
-  \begin{proof}
-
-    (i): $\begin{aligned}[t]
-      \lambda_{A\tensor B}(b) & = \zeta_{A\tensor B}(sab) \\
-       & = \zeta_{A\tensor B}(s\vert_A a) \wedge \zeta_{A\tensor B}(s\vert_B b) \\
-       & = \lambda_{A\tensor B}(a) \wedge \lambda_{A\tensor B}(b)
-    \end{aligned}$
-
-    By alternation, either $\lambda_{A\tensor B}(a)=O$ or $\lambda_{A\tensor B}(b)=O$, so this last expression must be equal to $O$.
-
-    (ii): \noindent$\begin{aligned}[t]
-      \lambda_{A\tensor B}(a) & = \zeta_{A\tensor B}(sba) \\
-       & = \zeta_{A\tensor B}(s\vert_A a) \wedge \zeta_{A\tensor B}(s\vert_B b) \\
-       & = \lambda_{A\tensor B}(a) \wedge \lambda_{A\tensor B}(b) = O\textrm{ (by the same argument)} && \quad\;\qedhere
-    \end{aligned}$
-  \end{proof}
-\end{proposition}
-
-\subsection{A category of games and partial strategies}
-\label{CategoricalSemantics}
-
-Following \cite{joyalgames} and \cite{abramskyjagadeesangames}, we define a category $\G$ whose objects are games where the morphisms from a game $A$ to a game $B$ are strategies for $A\implies B$.
-For the sake of simplicity, and to avoid various technical issues, we shall require that the games in our category be \emph{negative} - namely, they should start with an opponent move.
-In our language, we call a game $A$ \emph{negative} if $\zeta_A(\emptyplay)=P$ (and we call it positive if $\zeta_A(\emptyplay)=O$).
-The equations
-\begin{gather*}
-  P \wedge P = P \\
-  P \Rightarrow P = P
-\end{gather*}
-tell us that the class of negative games is closed under $\tensor$ and $\implies$ (since $P\vee P=P$, it is also closed under $\parr$, but the par of two negative games has no legal moves in our presentation, so it does not give a good model of the $\parr$ connective in linear logic and we will not consider it).
-
-In order to get a category, we need a way to compose a strategy for $A\implies B$ with a strategy for $B\implies C$.
-Our treatment of composition is heavily influenced by work done by Hyland and Schalk (see \cite{hyland1997games}, \cite{hylandschalkgames} and the excellent set of notes \cite{Schalk2001GsNotes}).
-
-We shall use the usual definition of composition.  If $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, we define a set
-\[
-  \sigma\|\tau = \{\s\in (M_A \cprd M_B \cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
-  \]
-Then we define the composite strategy on $A\implies C$ to be
-\[
-  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
-  \]
-The process of showing that this is indeed a strategy for $A\implies C$, and that composition is associative, will be quite involved.
-We shall start by recording some nice properties of negative games that will tell us that $\comp\tau\sigma$ is alternating:
-
-\begin{proposition}
-  Let $A,B$ be negative games and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\tensor B}$.  Then:
-  \begin{enumerate}[i)]
-    \item Either $\zeta_{A}(s\vert_A)=P$ or $\zeta_{B}(s\vert_B)=P$.  
-    \item $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$.  
-  \end{enumerate}
-  Furthermore, (i) and (ii) hold if we replace $\tensor$ with $\implies$ throughout and if we replace (i) by the statement that either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=O$.
-  \begin{proof}
-    See Appendix \ref{nice-negative-games-proof}.
-  \end{proof}
-  \label{nice-negative-games}
-\end{proposition}
-
-We gave an example earlier in which a play $sa$ in $P_A\|P_B$ was not well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$.
-The crucial thing that made that example work was that we had $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=O$.
-This then meant that $\zeta_{A\tensor B}(sa)=O$ even when $\lambda_{A\tensor B}=P$.
-Part (i) of the proposition above tells us that this situation never occurs, and part (ii) tells us that this is enough to ensure that we never get any alternating sequences that are not well formed.
-
-A corollary of our result is that we have:
-\begin{align*}
-  P_{A\tensor B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\tensor B}$}\} \\
-  P_{A\implies B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\implies B}$}\}
-\end{align*}
-if $A,B$ are negative games.  In other words, we can ignore the well-formedness condition on plays if we are dealing with only negative games.
-
-This proposition allows us to prove the following useful fact:
-
-\begin{lemma}
-  \label{alternatingsequenceslemma}
-  Let $A,B,C$ be negative games, and let $\s\in (M_A\cprd M_B\cprd M_C)^*$.  If any two of the following statements are true, then so is the third:
-  \begin{gather*}
-    \s\vert_{A,B}\in P_{A\implies B}\\
-    \s\vert_{A,C}\in P_{A\implies C}\\
-    \s\vert_{B,C}\in P_{B\implies C}
-  \end{gather*}
-  \begin{proof}
-    See Appendix \ref{alternatingsequenceslemmaproof}.
-  \end{proof}
-\end{lemma}
-
-Now we can move on to the main work.  We start with a surprising lemma about strategies on the implication $A\implies B$.
-
-\begin{lemma}
-  \label{PlayInStrategyDeterminedByComponents}
-  Let $A,B$ be games and let $\sigma$ be a strategy for $A\implies B$.  Suppose that $s,t\in\sigma$ are such that $s\vert_A=t\vert_A$ and $s\vert_B=t\vert_B$.  Then $s=t$.
-  \begin{proof}
-    Suppose that $s\ne t$.
-Let $r\prefix s,t$ be the longest common subsequence of $s$ and $t$ - so we have $rx\prefix s, ry\prefix t$ for some moves $x,y\in M_{A\implies B}$ with $x\ne y$.
-Since $rx,ry$ are both substrings of the strategy $\sigma$, $r$ must be a $P$-position and therefore the moves $x,y$ must take place in the same game.
-Without loss of generality, suppose that $x,y\in M_A$.
-Then we have $r\vert_A x\prefix s\vert_A,r\vert_Ay\prefix t\vert_A$ and so $s\vert_A\ne t\vert_A$.
-  \end{proof}
-\end{lemma}
-
-Thus we see that the plays according to some given strategy $\sigma$ for $A\implies B$ are characterized by their $A$- and $B$-components.
-More is true, however: given games $A$ and $B$, the strategies on $A\implies B$ are characterized by the $A$- and $B$-components of their constituent plays:
-\begin{lemma}
-  \label{HylandSchalkFaithful}
-  Let $A,B$ be games and let $\sigma,\sigma'$ be strategies for $A\implies B$ such that
-  \[
-    \{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}=\{(s'\vert_A,s'\vert_B)\suchthat\textrm{$s'\in\sigma'$ is a $P$-position}\}
-    \]
-  Then $\sigma=\sigma'$.
-  \begin{proof}
-    See Appendix \ref{HylandSchalkFaithfulProof}.
-  \end{proof}
-\end{lemma}
-
-Given games $A,B$ and a strategy $\sigma$ for $A\implies B$, the set
-\[
-  \{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}\subset P_A\times P_B
-  \]
-is a \emph{relation} between $P_A$ and $P_B$.  Writing $\grel\sigma\subset P_A\times P_B$, we will show that if $A,B,C$ are games and $A\xrightarrow{\sigma}\map{\tau}{B}{C}$ are morphisms, then:
-\[
-  \grel{\comp\tau\sigma}=\comp{\grel\tau}{\grel\sigma}
-  \]
-under the usual composition of relations:
-\[
-  \comp{\grel\tau}{\grel\sigma} = \{(s,t)\in P_A\times P_C\suchthat \exists u\in P_B\esuchthat (s,u)\in\grel\sigma,\;(u,t)\in\grel\tau\}
-  \]
-Thus we will get a functor $\cmap{\F}{\G}{\Rel}$, where $\G$ is our category of negative games and $\Rel$ is the category of sets and relations.
-Proposition \ref{HylandSchalkFaithful} then tells us that this functor is faithful.
-
-It is clear from the definition of $\comp\tau\sigma$ that $\grel{\comp\tau\sigma}\subset\comp{\grel\tau}{\grel\sigma}$; indeed if $\s\in\sigma\|\tau$, then $(\s\vert_A,\s\vert_B)\in\grel\sigma$ and $(\s\vert_B,\s\vert_C)\in\grel\tau$, so $(\s\vert_A,\s\vert_C)\in\comp{\grel\tau}{\grel\sigma}$.
-To show the reverse inclusion, we need to show the following: if $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$, then there is some $\s\in (M_A\cprd M_B\cprd M_C)^*$ such that $\s\vert_{A,B}=s$ and $\s\vert_{B,C}=t$.
-
-This can be shown in an easy way.
-Roughly speaking, we write out the sequence $s$, and then insert immediately after each $B$-move the $C$-moves from $t$ that occur after that $B$-move.
-This technique works for arbitrary sequences and is sufficient to prove that $\grel{\comp\tau\sigma}=\comp{\grel\tau}{\grel\sigma}$.
-However, it turns out that if $s$ and $t$ are alternating plays in $A\implies B$ and $B\implies C$ then this interleaving is unique - and even more is true:
-
-\begin{lemma}
-  \label{LiftingLemma}
-  Let $A,B,C$ be negative games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Suppose that $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$.
-Let $n=\length(s)+\length(t\vert_C)$; i.e., the total number of unique terms of $s$ and $t$ after we have identified their common $B$-component.
-Then for all $k$ with $0\le k\le n$, there is a unique sequence $\s^k\in\sigma\|\tau$ of length $k$ such that $\s^k\vert_A\prefix s\vert_A$ and $\s^k\vert_C\prefix t\vert_C$.
-Moreover, for this $\s^k$ we have $\s^k\vert_{A,B}\prefix s$ and $\s^k\vert_{B,C}\prefix t$, and if $j\le k$ then $\s^j\prefix \s^k$.
-  \begin{proof}
-    See Appendix \ref{LiftingLemmaProof}.
-  \end{proof}
-\end{lemma}
-
-Note that Lemma \ref{LiftingLemma} is stronger than saying that there is a unique sequence $\s^k$ of length $k$ such that $\s^k\vert_{A,B}\prefix s$ and $\s^k\vert_{B,C}\prefix t$.
-Instead, we are saying that there exists a sequence $\s^k$ with those properties, but that it is uniquely determined even when we make no requirement on its $B$-component other than that the whole sequence is contained in $\sigma\|\tau$.
-
-As a corollary, we see that the sequences $s$ and $t$ may be interleaved: set $\s=\s^n$; then we have $\s\vert_{A,B}\prefix s$ and $\s\vert_{B,C}\prefix t$.
-In fact, we have $\s\vert_{A,B}=s$ and $\s\vert_{B,C}=t$ by a length argument:
-\[
-  \length(\s\vert_{A,B})\le\length(s)=n-\length(t\vert_C)\le n-\length(\s\vert_C)=\length(\s\vert_{A,B})
-  \]
-so we must have equality everywhere, and similarly for $\s\vert_{B,C}$ and $t$.
-
-We now have all the ingredients ready to prove that $\comp\tau\sigma$ is a well-defined strategy.
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $\comp\tau\sigma$ (as defined above) is a strategy for $A\implies C$.
-
-  \begin{proof}
-    By Lemma \ref{alternatingsequenceslemma}, $\comp\tau\sigma\in P_{A\implies C}$.
-Moreover, it is non-empty, since it contains $\emptyplay$.
-We need to show that the two strategy conditions hold for $\comp\tau\sigma$.
-
-    Firstly, suppose that $\s\in\sigma\|\tau$ and $\s\vert_{A,C}$ is a $P$-play in $A\implies C$.
-Suppose that $\s\vert_{A,C} a\in P_{A\implies C}$ for some $a\in M_A$.
-We claim that $\s a\in\sigma\|\tau$.
-
-    Indeed, certainly $\s a\vert_{B,C}=\s\vert_{B,C}\in\tau$.
-Moreover, we have $\s a\vert_{A,C}\in P_{A\implies C}$, so Lemma \ref{alternatingsequenceslemma} tells us that $\s a\vert_{A,B}\in P_{A\implies B}$.
-
-    Since $a$ is an $O$-move in $A\implies B$, it is an $O$-move in $A\implies C$.
-Since $\s\vert_{A,B}\in\sigma$, we must have $\s a\vert_{A,B}\in\sigma$, by the definition of a strategy.
-So $\s a\in\sigma\|\tau$.
-
-    By a symmetrical argument, if $\s\vert_{A,C} c\in P_{A\implies C}$ for some $c\in M_C$, then $\s c\in\sigma\|\tau$.
-
-    For the second strategy property, suppose that $s\in\comp\tau\sigma$ is n $O$-play and that $sx, sy\in\comp\tau\sigma$.
-We claim that $x=y$.
-By the definition of $\comp\tau\sigma$, there must be sequences $\s,\t\in\sigma\|\tau$ with $\s\vert_{A,C}=sx$ and $\t\vert_{A,C}=sy$.
-Moreover, by removing any $B$-moves form the end of $\s,\t$, we may assume that the last move in $\s$ is $x$ and the last move in $\t$ is $y$.
-We may write $\s=\s'\b x$ and $\t=\t'\bbeta y$, where $\b$ and $\bbeta$ are sequences composed entirely out of $B$-moves and neither $\s'$ nor $\t'$ ends with a $B$-move.
-In particular, $\s'\vert_{A,C}=\t'\vert_{A,C}=s$.
-
-    Without loss of generality, $\length(\s')\le\length(\t')$.  Let $\t''$ be the prefix of $\t'$ that has the same length as $\s'$, writing $\t'=\t''\r$.
-
-    Now $\s'$ and $\t''$ have the same length, and we have
-    \[
-      \begin{matrix}
-        \s'\vert_A\prefix\s\vert_A & \t''\vert_A\prefix\s\vert_A \\
-        \s'\vert_C\prefix\s\vert_C & \t''\vert_C\prefix\s\vert_C
-      \end{matrix}
-      \]
-    so we must have $\s'=\t''$, by uniqueness in Lemma \ref{LiftingLemma}.  Now observe that we have
-    \[
-      \s'\vert_{A,C}=\t'\vert_{A,C}=\t''\vert_{A,C}\r\vert_{A,C}=\s'\vert_{A,C}\r\vert_{A,C}
-      \]
-    Since $\t'=\t''\r$ does not end with a $B$-move, $\r\vert_{A,C}$ must be non-empty if $\r$ is non-empty.  Therefore $\r=\emptyplay$, and so $\t'=\t''=\s'$.
-
-    We now claim that $\length(\b)=\length(\bbeta)$.
-Indeed, suppose instead that $\length(\b)<\length(\bbeta)$.
-Then there would be a prefix $\bbeta'\prefix\bbeta$ of length $\length(\b)+1$.
-Then we would have
-    \[
-      \begin{matrix}
-        \s'\b x\vert_A=\s\vert_A & \s'\bbeta'\vert_A=\s'\vert_A\prefix\s\vert_A \\
-        \s'\b x\vert_C=\s\vert_C & \s'\bbeta'\vert_C=\s'\vert_C\prefix\s\vert_C
-      \end{matrix}
-      \]
-    and so $\s'\b x=\s'\bbeta'$ by Lemma \ref{LiftingLemma}, which is clearly impossible.
-Therefore, $\length(\b)=\length(\bbeta)$.
-Now we can apply Lemma \ref{LiftingLemma} in the same way to tell us that $\b=\bbeta$.
-
-    Suppose that $\zeta_B(\s'\b\vert_B)=P$.
-Since $\s'\b\in\sigma\|\tau$, this means that $\zeta_A(\s'\b\vert_A)=P$, by Proposition \ref{nice-negative-games}(i).
-Therefore, $\zeta_{A\implies B}(\s'\b)=P$, so $x$ and $y$ must both be moves in $C$.
-Then we have $\s'\b\vert_{B,C}x,\s'\b\vert_{B,C}y\in\tau$, and so $x=y$ by the definition of a strategy.
-
-    By a symmetrical argument, if $\zeta_B(\s'\b\vert_B)=O$, then $x$ and $y$ must both be moves in $A$.  We then have $\s'\b\vert_{A,B}x,\s'\b\vert_{A,B}y\in\sigma$, so $x=y$.
-  \end{proof}
-\end{proposition}
-
-Now we are ready to define our category $\G$ of games.
-We have defined composition of strategies, so we need to define identity morphisms.
-Identity morphisms are given by the copycat strategy, as usual:
-\[
-  \id_A=\left\{s\in P_{A\implies A}\suchthat\textrm{for all even length $t\prefix s$, $t\vert_\bneggame{A}=t\vert_A$}\right\}
-  \]
-We can now state our first main result.
-
-\begin{theorem}
-  \label{IsCategory}
-  The collection of negative games, with morphisms from $A$ to $B$ given by strategies on $A\implies B$ with the notions of composition and identity given above, forms a category $\G$.
-Moreover, there is a faithful functor $\F\from\G\to\Rel$, where $\Rel$ is the category of sets and relations, given by sending a game $A$ to the set of plays $P_A$ and sending a strategy $\sigma\from A\implies B$ to the set
-  \[
-    \grel{\sigma}=\{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}\subset P_A\times P_B
-    \]
-  \begin{proof}
-    We shall make much use of the relational content of a strategy.
-We first need to show that the identity is indeed an identity and that composition is associative.
-For the identity, note that $\grel{\id_A}=\Delta_{P_A}\subset P_A\times P_A$, the identity relation in $\Rel$.
-If $B,C$ are negative games and $\sigma\colon B\implies A,\tau\colon A\implies C$ are strategies, then from our earlier discussion we have
-    \[
-      \grel{\comp{\id_A}{\sigma}}=\comp{\grel{\id_A}}{\grel\sigma}=\comp{\Delta_{P_A}}{\grel\sigma}=\grel\sigma
-      \]
-    and therefore $\comp{\id_A}{\sigma}=\sigma$, by Lemma \ref{HylandSchalkFaithful}.  Similarly, $\comp{\tau}{\id_A}=\tau$.
-
-    For associativity of composition, we hijack the associativity in $\Rel$: if $A,B,C,D$ are negative games, and $\map{\sigma}AB\xrightarrow{\tau}\map{\upsilon}CD$ are morphisms, then we have:
-    \begin{align*}
-      \grel{\comp{(\comp\upsilon\tau)}{\sigma}} & = \comp{\grel{\comp\upsilon\tau}}{\sigma} \\
-        & = \comp{(\comp{\grel\upsilon}{\grel\tau})}{\grel\sigma} \\
-        & = \comp{\grel\upsilon}{(\comp{\grel\tau}{\grel\sigma})} \quad\textrm{by associativity in $\Rel$} \\
-        & = \comp{\grel\upsilon}{\grel{\comp\tau\sigma}} \\
-        & = \grel{\comp{\upsilon}{(\comp\tau\sigma)}}
-    \end{align*}
-    and so $\comp{(\comp\upsilon\tau)}{\sigma}=\comp{\upsilon}{(\comp\tau\sigma)}$, by Lemma \ref{HylandSchalkFaithful}.
-
-    We have already shown that the map $\F$ respects composition, so it is a functor.  It is faithful by Lemma \ref{HylandSchalkFaithful}.
-  \end{proof}
-\end{theorem}
-
-\subsection{Total strategies and winning conditions}
-
-Let $A$ be a game.
-We call a strategy $\sigma$ for $A$ \emph{total} if it satisfies the additional requirement that whenever $s\in\sigma$ is an $O$-play, there exists some $a\in M_A$ such that $sa\in\sigma$ (before we only required that such a play be unique if it existed).
-
-We might want to talk about a category of negative games and total strategies.  However, we cannot do this immediately, since the composition of two total strategies need not be total.
-
-\begin{example}
-  \label{TotalCompositionExample}
-  Let $\st$ be the negative game where each player has a unique move at every position:
-  \begin{gather*}
-    M_{\st} = \{q,a\} \\
-    \lambda_{\st}(q) = O,\;\lambda_{\st}(a)=P \\
-    P_{\st} = \{\emptyplay, q, qa, qaq, qaqa, \dots\}
-  \end{gather*}
-
-  Let $I$ be the negative game with no moves and let $\bot$ be the negative game with a single opponent move and no further play:
-  \[
-    \begin{matrix}
-      M_I=\emptyset & M_\bot = \{*\} \\
-      \lambda_I=\emptyset  & \lambda_\bot(*)=O \\
-      P_I=\{\emptyplay\} & P_\bot = \{\emptyplay, *\}
-    \end{matrix}
-    \]
-
-  It is easy to see that if $A$ is a negative game then strategies for $I\implies A$ are the same thing as strategies for $A$ and that strategies for $A\implies\bot$ are the same thing as opponent strategies for $A$.
-So we get morphisms $\cmap{\sigma}{I}{\st},\cmap{\tau}{\st}{\bot}$ given by the unique player and opponent strategies for $\st$:
-  \[
-    \sigma = P_\st\quad\tau = \{*s\suchthat s\in P_\st\}
-    \]
-  Moreover, both these strategies are total.
-
-  The plays in $\sigma\|\tau$ are now those sequences $\s\in(M_I\cprd M_\st\cprd M_\bot)^*$ such that:
-  \begin{gather*}
-    \s\vert_A=\emptyplay \\
-    \s\vert_B\in P_\st \\
-    \textrm{If $\s\ne\emptyplay$ then $\s\vert_C=*$}
-  \end{gather*}
-
-  Upon restricting these sequences to $A$ and $C$, we see that $\comp\tau\sigma$ contains only two plays - $\emptyplay$ and $*$.
-$*$ is an $O$-play with no $P$-reply in $\comp\tau\sigma$, so $\comp\tau\sigma$ is not a total strategy.
-\end{example}
-
-Clearly it is the infinite play in the game $\st$ that is causing the problem.
-We can get around this by insisting that our games contain no infinite plays: if $A$ is a game, we say $A$ has an infinite play if $(P_A,\prefix)$ has an infinite chain.
-
-\begin{proposition}
-  \label{BoundedTotalComposition}
-  Let $A,B,C$ be negative games and assume that $B$ has no infinite play.
-Let $\sigma$ be a total strategy for $A\implies B$ and let $\tau$ be a total strategy for $B\implies C$.
-Then $\comp\tau\sigma$ is a total strategy for $A\implies C$.
-  \begin{proof}
-    We have already shown that $\comp\tau\sigma$ is a strategy for $A\implies C$, so we need to show that it is total.
-Let $s\in\comp\tau\sigma$ be an $O$-play.
-We seek a $P$-move $x$ such that $sx\in\comp\tau\sigma$.
-
-    By the definition of $\comp\tau\sigma$, there is some $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-Since $P_B$ contains no infinite chain, we may take $\s$ to be maximal such that $\s\vert_{A,B}=s$.
-
-    Since $s$ is an $O$-play, $\s\vert_A$ must be a $P$-play in $A$ and $\s\vert_C$ must be an $O$-play in $C$.
-Consider the $B$-component $\s\vert_B$ of $\s$.
-If this is an $O$-play, then $\s\vert_{A,B}$ is an $O$-play in $\sigma$, so, by totality of $\sigma$, there exists $x$ such that $\s\vert_{A,B}x\in\sigma$ and therefore $\s x\in\sigma\|\tau$.
-Similarly, if $\s\vert_B$ is a $P$-play, then $\s\vert_{B,C}$ is an $O$-play in $\tau$, so there exists $x$ such that $\s\vert_{B,C}x\in\tau$ and so $\s x\in\sigma\|\tau$.
-
-    If $x$ is a $B$-move, we have $\s x\vert_{A,C}=s$, contradicting maximality of $s$.  Therefore, $x$ is an $A$- or $C$-move, and we have $sx\in\comp\tau\sigma$.
-  \end{proof}
-\end{proposition}
-
-The result of this proposition means that we could create a category of games and total strategies by requiring that all our games have no infinite plays.
-However, this approach will not work for us, since our particular version of the exponential connective $\oc$ introduces infinite plays into all non-empty games.
-Moreover, it seems a bit wasteful to require that none of the games $A,B,C$ have infinite plays when it is only infinite plays in game $B$ that are causing problems.
-
-Fortunately, there is a cleverer way of getting around the problem.
-Recall that we defined a game to be given by a tuple $(M_A,\lambda_A,\zeta_A,P_A)$.
-Given such a game, and given some subset $X\subset P_A$, define $X^\omega$ to be the set of all infinite plays in the game -- i.e., the set of all infinite sequences $s\in M_A^\omega$ all of whose prefixes lie in $X$.
-
-\begin{definition}
-  A \emph{win-game} is a tuple $A=(M_A,\lambda_A,\zeta_A,P_A,W_A)$ where $(M_A,\lambda_A,\zeta_A,P_A)$ is a game as defined before and $\cmap{W_A}{P_A^\omega}{\OP}$ is a function telling us whether each infinite play is a win for player $P$ or for player $O$.
-\end{definition}
-
-To distinguish our original games from these win-games, we shall refer to the earlier games as \emph{finitary games}.
-
-We can define an appropriate notion of strategies for these games.
-If $A$ is a win-game, then a \emph{winning strategy} for $A$ is a total strategy for $(M_A,\lambda_A,\zeta_A,P_A)$ such that $W_A(s)=P$ for all $s\in\sigma^\omega$.
-
-We can also extend our connectives to our new win games.
-At the level of finitary games, our definitions of the connectives are unchanged, and it remains to define the $W$-functions.
-If $A$ is a win game, then $W_{\neggame A}=\neg\circ W_A$.
-
-If $A$ and $B$ are win games, we would like to define $W_{A\tensor B}$ by
-\[
-  W_{A\tensor B}(s) = W_A(s\vert_A) \wedge W_B(s\vert_B)
-  \]
-However, this is not well defined at present because one out of $s\vert_A$ and $s\vert_B$ might be a finite sequence even if $s$ is infinite.
-For this purpose, it will be convenient to extend our function $W_A$ to include finite plays as well using $\zeta_A$:
-\[
-  W_A^* = \zeta_A\cprd W_A\from P_A\cprd P_A^\omega \to\OP
-  \]
-We can then define
-\[
-  W_{A\tensor B}(s) = W_A^*(s\vert_A)\wedge W_B^*(s\vert_B)
-  \]
-Indeed, we could do away with $\zeta_A$ and $W_A$ altogether, replacing them with $W_A^*$.
-Since the rule for $\zeta_{A\tensor B}$ is also given by a conjunction, our rule for the tensor product becomes:
-\[
-  W_{A\tensor B}^*(s) = W_A^*(s\vert_A)\wedge W_B^*(s\vert_B)
-  \]
-This will be the starting point for our development of transfinite games in the next section.
-In our formulation, finitary games are games played over the ordinal $\omega$, while win-games will be games played over the ordinal $\omega+1$.
-We make no special distinction between finite and infinite plays, so the function $\zeta_A$ for our transfinite games incorporates both the function $\zeta_A$ and the function $W_A$ from our win-games, in the same manner as the function $W_A^*$ defined above.
-One advantage of this point of view is that we no longer have to treat the finite- and infinite-play cases separately, but can give a uniform presentation.
-
-For now, let us concentrate on developing the theory of win-games in the traditional way.
-Having defined the tensor product, we may recover the definitions of the par $\parr$ and linear implication $\implies$ of two games as usual.
-In particular, this means that we have
-\[
-  W_{A\implies B}^*(s) = (W_A(s\vert_A) \Rightarrow W_B(s\vert_B))
-  \]
-
-It is worth examining the definitions of the $W$-functions for tensor and implication.
-Recall that in the tensor product, it is always player $O$ who switches games.
-Therefore, if $s$ is an infinite play in $A\tensor B$ and $s\vert_A$ is finite and non-empty, it must be the case that player $P$ made the last move in $s$, and so $W_A^*(s\vert_A)=P$.
-If we assume our games are negative, then this extends to the case that $s\vert_A$ is empty.
-This tells us that player $P$ wins an infinite play $s$ in $A\tensor B$ if and only if each component is either $P$-winning or is finite.
-
-Similarly, player $P$ wins an infinite play $s$ in $A\implies B$ if and only if $s\vert_A$ is infinite and $O$-winning or if $\s\vert_B$ is either finite or is infinite and $P$-winning.
-Since it is player $P$ who switches games in $A\implies B$, if $s\vert_A$ is finite then it will end with an $O$-move, so will count as an $O$-winning play.
-
-The point now is that if $A,B,C$ are negative win-games and $\sigma$ and $\tau$ are strategies for $A\implies B$ and $B\implies C$, we will never end up in the situation we were in in Example \ref{TotalCompositionExample} where we have an infinite play in $B$ that stops us from replying in the composition $\comp\tau\sigma$.
-In that example, the unique infinite play in $\st$ would have to be either $O$-winning or $P$-winning, so either $\sigma$ or $\tau$ would not be a valid winning strategy.
-
-\begin{proposition}
-  \label{CompWinningIsWinning}
-  Let $A,B,C$ be negative win-games, let $\sigma$ be a winning strategy for $A\implies B$ and let $\tau$ be a winning strategy for $B\implies C$.
-Then $\comp\tau\sigma$ is a winning strategy for $A\implies C$.
-  \begin{proof}
-    See Appendix \ref{CompWinningIsWinningProof}.
-  \end{proof}
-\end{proposition}
-
-We get another result:
-
-\begin{theorem}
-  The collection of all negative win-games, with morphisms from $A$ to $B$ given by winning strategies on $A\implies B$ and composition defined as above, is a category.
-  \begin{proof}
-    We have shown already that the composition of two winning strategies is a winning strategy.
-Associativity of composition is inherited from finitary games and the identity strategy is winning for $A\implies A$.
-  \end{proof}
-\end{theorem}
-
-\section{Transfinite games}
-
-\begin{note}
-  In this section, we assume familiarity with ordinals, ordinal arithmetic and transfinite induction/recursion.
-We shall frequently identify an ordinal $\alpha$ with the set $\{\beta\suchthat\beta<\alpha\}$ of all ordinals less than $\alpha$ without comment.
-\end{note}
-
-In the last section, we came across win-games, where in addition to the usual function $\cmap{\zeta_A}{P_A}{\OP}$ we have a function $\cmap{W_A}{P_A^\omega}{\OP}$, where $P_A^\omega$ is the set of infinite limits of plays in $P_A$.
-We saw that it is useful to combine these two functions into one:
-\[
-  W_A^* = \zeta_A\cprd W_A\from P_A\cprd P_A^*\to\OP
-  \]
-This suggests that it might make sense to combine $P_A$ and $P_A^\omega$ into one a single set $\overline{P_A}$ and use the function $W_A^*$ instead of $\zeta_A$ and $W_A$.
-This new set will contain both finite and infinite plays, and the infinite plays will be precisely the limits of the finite plays.
-In this way, the set of possible lengths of plays in $\overline{P_A}$ is the set $\{0,1,2,3,\dots,\omega\}$, or the ordinal $\omega+1$.
-
-Contrast this with the finitary case, in which the set of possible lengths of plays is the set $\{0,1,2,3,\dots\}$, or the ordinal $\omega$.
-In the coming sections, we will generalize these results so that we end up with games where the plays can have much larger ordinal lengths.
-Win-games will be taken to be the motivating example throughout.
-
-\subsection{Transfinite Games and Strategies}
-
-We fix some ordinal $\alpha$ throughout.  Given a set $M$, we write $M^{*<\alpha}$ for the set of all ordinal-length sequences of elements of $M$ whose length is less than $\alpha$.
-
-\begin{definition}
-  A \emph{game over $\alpha$}, or an \emph{$\alpha$-game}, is given by a tuple
-  \[
-    A = (M_A, \lambda_A, \zeta_A, P_A)
-    \]
-  where
-  \begin{itemize}
-    \item $M_A$ is a set of moves.
-    \item $\cmap{\lambda_A}{M_A}{\OP}$ is a function telling us which player may make each move.
-    \item $P_A$ is a set of pairs $(\beta, s)$, where $\beta<\alpha$ is some ordinal and $\cmap{s}{\beta}{M_A}$ is a sequence of moves of length $\beta$.  
-    \item $\cmap{\zeta_A}{P_A}{\OP}$ tells us which player owns each position.
-  \end{itemize}
-
-  We will normally abuse notation and write $s$ instead of $(\beta, s)$ and $\length(s)$ instead of $\beta$.
-If $a\in M_A$, we will write $a$ for the $1$-move play $(1, a)$, and $st$ for the concatenation of two sequences $s$ and $t$ (where $\length(st)=\length(s)+\length(t)$).
-We will write $t\prefix s$ if $\length(t)\le\length(s)$ and $s\vert_{\length(t)}=t$.
-
-  To be called a game, $(M_A, \lambda_A, \zeta_A, P_A)$ has to satisfy four rules.
-  \begin{description}
-    \item[Prefix closure] $P_A$ must be closed under the relation $\prefix$.  
-    \item[Well-formedness] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.  
-    \item[Alternating condition] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s)=\neg\zeta_A(sa)$.
-    \item[Limit condition] If $\mu<\alpha$ is a limit ordinal and $s\in(M_A)^\mu$ is a sequence of length $\mu$ such that every proper prefix $t\pprefix s$ is in $P_A$, then $s$ is in $P_A$.  
-  \end{description}
-\end{definition}
-
-\begin{remark}
-  In the $\omega+1$ case, the limit condition tells us that the plays of length $\omega$ in $P_A$ are precisely those infinite plays all of whose finite prefixes lie in $P_A$.
-It also guarantees that $P_A$ is non-empty, since the empty play $\emptyplay$ will always satisfy the conditions.
-
-  In the $\omega+1$ case, $\zeta_A$ will take the role of what we previously called $W_A^*$, while $P_A$ takes the role of what we called $P_A\cprd P_A^\infty$.  
-\end{remark}
-
-We define strategies for these games in much the same way that we defined them before:
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  A (partial) \emph{strategy} for $A$ is a subset $\sigma\subset P_A$ satisfying three conditions:
-  \begin{description}
-    \item[$\sigma$ contains all $O$-replies] If $s\in\sigma$ is a $P$-play and $sa\in P_A$ is an $O$-response, then $sa\in\sigma$.
-    \item[$P$-replies are unique] If $s\in\sigma$ is an $O$-play and $sa,sb\in\sigma$ are $P$-responses, then $a=b$.
-    \item[Limit condition] If $\mu<\alpha$ is a limit ordinal and $s\in P_A$ is a sequence of length $\mu$ such that every proper prefix $t\pprefix s$ lies in $\sigma$, then $s\in\sigma$.
-  \end{description}
-
-  We call $\sigma$ \emph{total} if it satisfies the extra requirement:
-
-  \begin{description}
-    \item[$P$ always has a reply] If $s\in\sigma$ is an $O$-play, then there is some $P$-move $a\in M_A$ with $sa\in\sigma$.
-  \end{description}
-\end{definition}
-
-The only new part of this is the limit condition.
-Let us examine what it means in the $\omega+1$ case.
-Play according to a total strategy $\sigma$ gives rise to a sequence of plays $\emptyplay \prefix s_1\prefix s_2\prefix\dots$ (were $s_i$ has length $i$).
-The limit condition then tells us that the limit $s_\omega$ of these plays must be contained in $\sigma$.
-If $\zeta_A(s_\omega)=O$ then $P$ has no response to $s_\omega$ (since there are no plays of length $\omega+2$), contradicting totality of $\sigma$.
-So for $\sigma$ to be a total strategy, we must have $\zeta_A(s_\omega)=P$ for every $s_\omega$ arising as the limit of finite plays according to $\sigma$.
-So total strategies for $\omega+1$-games are exactly the same thing as the winning strategies for win-games that we defined earlier.
-
-If $s\in P_A$ and $\length(s)$ is a successor ordinal, we will call $s$ a \emph{successor play} or \emph{successor position}.
-If $\length(s)$ is a limit ordinal, we will call $s$ a \emph{limiting play} or \emph{limiting position}.
-
-\subsection{Connectives}
-
-We may define connectives for $\alpha$-games in much the same way that we defined them for finitary games and win-games.
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  The negation $\neggame A$ of $A$ is given by
-  \begin{itemize}
-    \item $M_\bneggame A=M_A$
-    \item $\lambda_\bneggame A = \neg\circ\lambda_A$
-    \item $\zeta_\bneggame A = \neg\circ\zeta_A$
-    \item $P_\bneggame A = P_A$
-  \end{itemize}
-\end{definition}
-
-For the other connectives -- $\tensor$, $\parr$ and $\implies$ -- we will use interleaved plays.
-If $A$ and $B$ are $\alpha$ games, then our interleaved plays will be sequences taking values in $M_A\cprd M_B$.
-If $\beta<\alpha$ and $s\in(M_A\cprd M_B)^\beta$, we may write $\beta_A$ for $s\inv(M_A)$ and $\beta_B$ for $s\inv(M_B)$.
-
-\begin{lemma}
-  \label{TechnicalOrdinalLemma}
-  Let $\beta$ be an ordinal, and let $\gamma$ be any subset of $\beta$.  Then $\gamma$ inherits a well-ordering from $\beta$ and, as ordinals, we have $\gamma\le\beta$.  
-  \begin{proof}
-    Any subset of $\gamma$ is a subset of $\beta$, so it has a least element.  Therefore, the inherited order on $\gamma$ is a well-order.
-
-    Suppose for a contradiction that $\beta<\gamma$.  Then we have order preserving injections
-    \[
-      i\from \gamma\hookrightarrow\beta\quad j\from\beta\hookrightarrow\gamma
-      \]
-    where $i$ is inclusion of $\gamma$ as a subset of $\beta$ and $j$ is inclusion of $\beta$ as a proper initial prefix of $\gamma$.
-Let $f\from\gamma\hookrightarrow\gamma$ be the composition $\gamma\xhookrightarrow{i}\beta\xhookrightarrow{j}\gamma$.
-Then $f$ is order preserving.
-
-    Let $S=\{\delta\in\gamma\suchthat f(\delta)<\delta\}$.
-$S$ is non-empty, since $\beta\in S$ (considering $\beta$ as an element of $\gamma$), so $S$ has a least element $\xi$.
-Now $f(\xi)<\xi$, so $f(f(\xi))<f(\xi)$, since $f$ is order-preserving and injective.
-Therefore, $\xi\le f(\xi)$ by minimality of $\xi$, which is a contradiction.
-  \end{proof}
-\end{lemma}
-
-Using Lemma \ref{TechnicalOrdinalLemma}, we see that $\beta_A,\beta_B\le\beta$; in particular, they are both less than $\alpha$, so we get induced sequences $s\vert_A$ of length $\beta_A$ and $s\vert_B$ of length $\beta_B$.
-We define
-\[
-  P_A\|P_B = \left\{s\in (M_A\cprd M_B)^{*<\alpha}\suchthat s\vert_A\in P_A,\;s\vert_B\in P_B\right\}
-  \]
-
-We may now define functions $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}\from P_A\|P_B\to\OP$ as before:
-\begin{IEEEeqnarray*}{rCc}
-  \zeta_{A\tensor B}(s) & = & \zeta_A(s\vert_A)\wedge\zeta_B(s\vert_B)\\
-  \zeta_{A\parr B}(s) & = & \zeta_A(s\vert_A)\vee\zeta_B(s\vert_B)\\
-  \zeta_{A\implies B}(s) & = & (\zeta_A(s\vert_A)\Rightarrow \zeta_B(s\vert_B))
-\end{IEEEeqnarray*}
-
-Our definitions of the functions $\lambda_{A\tensor B},\lambda_{A\parr B},\lambda_{A\implies B}\from M_A\cprd M_B\to \OP$ are the same as before:
-\begin{gather*}
-  \lambda_{A\tensor B}=\lambda_{A\parr B}=\lambda_A\cprd \lambda_B \\
-  \lambda_{A\implies B} = (\neg\circ\lambda_A)\cprd \lambda_B
-\end{gather*}
-
-Given a set $M$, a prefix-closed set $P\subset M^{*<\alpha}$ and functions $\cmap{\lambda}{M}{\OP},\cmap{\zeta}{P}{\OP}$, we say that a play $s\in P$ is \emph{well-formed with respect to $\lambda,\zeta$} if whenever $ta\prefix s$ (with $a\in M$) we have $\zeta(ta)=\lambda(a)$.
-We say that $s$ is \emph{alternating with respect to $\zeta$} if whenever $t,ta$ are prefixes of $s$ (where $a\in M$), we have $\zeta(t)=\neg\zeta(ta)$.
-
-As before, we now define:
-
-\begin{IEEEeqnarray*}{rCl}
-  P_{A\tensor B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\tensor B}$ \\ $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$}}\right\} \\
-  P_{A\parr B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\parr B}$ \\ $s$ is well formed with respect to $\zeta_{A\parr B},\lambda_{A\parr B}$}}\right\} \\
-  P_{A\implies B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\implies B}$ \\ $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$}}\right\}
-\end{IEEEeqnarray*}
-
-Setting $M_{A\tensor B}=M_{A\parr B}=M_{A\implies B} = M_A\cprd M_B$, and restricting $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$ to $P_{A\tensor B},P_{A\parr B},P_{A\implies B}$ respectively, we arrive at our definitions of the connectives:
-\begin{IEEEeqnarray*}{cCc}
-  A\tensor B & = & (M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B})\\
-  A\parr B & = & (M_{A\parr B}, \lambda_{A\parr B}, \zeta_{A\parr B}, P_{A\parr B})\\
-  A\implies B & = & (M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})
-\end{IEEEeqnarray*}
-
-\begin{proposition}
-  \label{TransTensorWellFormed}
-  $A\tensor B$, $A\parr B$ and $A\implies B$ are well formed games.
-Moreover, $P_{A\tensor B}$ is the largest subset $X\subset P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, X)$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.
-  \begin{proof}
-    As before, we prove this proposition for $A\tensor B$ and the other two cases are entirely similar.
-Alternatively, observe that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$ and that $A\implies B = \neggame A \parr B$.
-
-    Examining the definitions of well formed and alternating sequences, it is immediate that $P_{A\tensor B}$ is prefix-closed.
-Moreover, every sequence contained in $P_{A\tensor B}$ is well formed, so the well-formedness condition holds.
-If $s,sa\in P_{A\tensor B}$ then $s,sa$ are both prefixes of $sa$ and so we must have $\zeta_{A\tensor B}(s)=\neg\zeta_{A\tensor B}(sa)$, since $sa$ is alternating.
-
-    To show that the limit condition holds, suppose that $\mu<\alpha$ is a limit ordinal and that $s\in(M_A)^\mu$ is a sequence of length $\mu$ such that $t\in P_{A\tensor B}$ for every proper prefix $t\pprefix s$.
-For each $t\pprefix s$, then, we must have $t\vert_A\in P_A$ and $t\vert_B\in P_B$.
-
-    We claim that $s\vert_A\in P_A$.
-Indeed, if $\length(s\vert_A)$ is a successor ordinal, then $s\vert_A$ has a last move $a$.
-Let $t$ be the prefix of $s$ consisting of all moves up to and including that last move.
-Then $\length(t)$ is a successor ordinal, so $t$ must be a \emph{proper} prefix of $s$, and therefore $s\vert_A=t\vert_A\in P_A$.
-If instead $\length(s\vert_A)$ is a limit ordinal, then for every proper prefix $u\pprefix s\vert_A$, we have some $t\prefix s$ with $t\vert_A=u$ (take $t$ to be the prefix consisting of all moves in $s$ that occur in $u$ or that occur before some move in $u$).
-Since $s\vert_A\ne u$, $t$ must be a \emph{proper} prefix of $s$, and so $t\vert_A\in P_A$.
-Since $u$ is arbitrary, the limit condition for $A$ tells us that $s\vert_A\in P_A$.
-
-    By an identical argument, $s\vert_B\in P_B$, and so $s\in P_A\|P_B$.
-We claim that $s$ is alternating with respect to $\zeta_{A\tensor B}$.
-Indeed, if $t,ta\prefix s$, then $t,ta$ must both be \emph{proper} prefixes of $s$, since $\length(s)$ is a limit ordinal and $\length(ta)$ is a successor ordinal.
-So $ta$ is alternating and therefore $\zeta_{A\tensor B}(t)=\neg\zeta_{A\tensor B}(ta)$.
-
-    Lastly, we show that $s$ is well formed with respect to $\lambda_{A\tensor B},\zeta_{A\tensor B}$.
-Suppose $ta\prefix s$.
-Once again, $ta$ must be a \emph{proper} prefix of $s$, since it clearly has a different length.
-Therefore, $ta$ is well formed and we have $\zeta_{A\tensor B}(ta)=\lambda_{A\tensor B}(a)$.
-Therefore, $s\in P_{A\tensor B}$.
-
-    For the second part of the proposition, suppose that $V\subset P_A\|P_B$ is prefix closed and satisfies the alternating condition with respect to $\zeta_{A\tensor B}$ and that if $sa\in V$ then $\zeta_{A\tensor B}(sa)=\lambda_{A\tensor B}(a)$.
-We want to show that $V\subset P_{A\tensor B}$.
-Indeed, if $s\in V$ and $ta\prefix s$, then $ta\in V$ (since $V$ is prefix closed) and therefore $\zeta_{A\tensor B}(ta)=\lambda_{A\tensor B}(a)=\neg\zeta_{A\tensor B}(s)$.
-  \end{proof}
-\end{proposition}
-
-As before, we want to show that if player $O$ switches games in the tensor product and that player $P$ switches games in the par and linear implication.
-Recalling that if $A,B$ are $\alpha$-games then $A\parr B = \neggame{(\neggame A\tensor \neggame B)}$ and that $A\implies B = \neggame A\parr B$, we only need to prove this for the tensor product:
-
-\begin{proposition}
-  \label{TransWhoSwitchesGames}
-  Let $A,B$ be $\alpha$-games.  Suppose that $s\in P_{A\implies B}$, $a\in M_A$ and $b\in M_B$.  Then:
-
-  i) If $sab\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(b) = O$
-
-  ii) If $sba\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(a) = O$.
-
-  \begin{proof}
-    Unchanged from the finitary case - see Proposition \ref{WhoSwitchesGames}
-  \end{proof}
-\end{proposition}
-
-\subsection{Categories of transfinite games and strategies}
-
-We want to build a category $\G(\alpha)$ whose objects are games and whose morphisms are strategies on the linear implication of two games.
-Given $\alpha$-games $A$, $B$ and $C$ and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we define
-\begin{gather*}
-  \sigma\|\tau = \left\{\s\in (M_A\cprd M_B\cprd M_C)^{*<\alpha\#\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\right\}\\
-  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}
-\end{gather*}
-
-Here, $\alpha\#\alpha$ is intended to be an upper bound and indeed any sufficiently large ordinal will do without changing the elements of $\sigma\|\tau$.
-The symbol $\#$ denotes the so-called \emph{natural addition} on ordinals: if $\beta,\gamma$ are ordinals then the order type of $\beta\#\gamma$ is the largest well-ordering on the disjoint union $\beta\sqcup\gamma$ such that the restrictions to $\beta$ and $\gamma$ give the original orderings\footnote{Alternatively, $\#$ represents the coproduct in the category of well-ordered sets and order-preserving maps.}.
-For example, we have $\omega\#1=\omega+1$, but $1\#\omega=\omega+1$ as well (and \emph{not} $1+\omega$, which equals $\omega$).
-In any case, this is not an important point - we want to allow the sequences $\s$ to be as long as we need to be, but we need to introduce some bound to make it clear that the resulting collection of plays is a small set.
-$\alpha\#\alpha$ turns out to be a suitable upper bound.
-
-For the functor $\cmap{\F}{\G(\alpha)}{\Rel}$, we shall want to show that
-\[
-  \comp\tau\sigma = \left\{s\in P_{A\implies C}\suchthat\exists t\in\sigma,u\in\tau\esuchthat s\vert_A=t\vert_A,\;t\vert_B=u\vert_B,\;s\vert_C=u\vert_C\right\}
-  \]
-To show this, we will want to show that for any such $s,t,u$ there is some interleaving $\s$ such that $\s\vert_{A,C}=s$, $\s\vert_{A,B}=t$ and $\s\vert_{B,C}=u$.
-Even though $s$, $t$ and $u$ all have length less than $\alpha$, $\s$ might have longer length; it will, however, have length less than $\alpha\#\alpha$.
-
-It is not immediately clear from the definition that the elements of $\comp\tau\sigma$ have length less than $\alpha$, and in fact it turns out that this is not true.
-For this reason, we will eventually need to place restrictions on the ordinal $\alpha$ to make sure that $\comp\tau\sigma$ is indeed a valid strategy for $A\implies C$.
-
-\subsubsection{Completely negative and almost completely negative $\alpha$-games}
-
-Recall that when defining a finitary game $A=(M_A,\lambda_A,\zeta_A,P_A)$, the function $\zeta_A$ was entirely determined by two pieces of information: the function $\lambda_A$ (to determine $\zeta_A(sa)$ for any non-empty play $sa$) and the designation of the game as either \emph{positive} or \emph{negative} (to determine $\zeta_A(\emptyplay)$).
-In the $\omega+1$ case, we also needed to specify a function $\cmap{W_A}{P_A^\infty}{\OP}$ to get the sign of each $\omega$-play.
-The general case is similar - once we have specified $\zeta_A(s)$ for any play $s$ whose length is a limit ordinal, the values of $\zeta_A(t)$ for $t$ a play over a successor ordinal are determined by the alternating condition (alternatively, they are determined automatically by well-formedness).
-
-When building a category of games, we restricted our attention to the negative games.
-This is necessary in order to avoid technical complications\footnote{The category in \cite{abramskyjagadeesangames} has both positive and negative games as objects, together with games where either player may start, but it does not admit a faithful functor into $\Rel$ in the way that we want.}.
-Of course, these technical complications carry over to the transfinite case, so we need a new negativity condition for our $\alpha$-games.
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  We say that $A$ is \emph{completely negative} if $\zeta_A(s)=P$ whenever $s\in P_A$ and $\length(s)$ is a limit ordinal.
-\end{definition}
-
-Since the only limiting play in the finitary case is the empty play, we see that the completely negative $\omega$-games are precisely the negative games.
-But now consider the $\omega+1$ case.
-If $A$ is a win-game, then $A$ is completely negative only if it is negative and all infinite plays are $P$-winning.
-Recall that we \emph{were} able to build a category of negative win-games without making the requirement that player $P$ wins all infinite plays, so if we insist on complete negativity then we lose much of the richness of our category for no technical benefit.
-We would be better off with some weaker condition.
-
-\begin{definition}
-  Let $\alpha$ be an ordinal.  If $\alpha=\alpha'+1$ and $A$ is an $\alpha$-game, we say that $s\in P_A$ is \emph{length maximal} if it has the largest possible length - i.e., if $\length(s)=\alpha'$.
-
-  If $\alpha$ is a limit ordinal then there are no length maximal plays in $\alpha$-games.
-
-  Let $A$ be an $\alpha$-game.  We say that $A$ is \emph{almost completely negative} (\emph{acn}) if $\zeta_A(s)=P$ whenever $\length(s)$ is a limit ordinal \emph{and $s$ is not length-maximal}.
-\end{definition}
-
-Note that for most ordinals $\alpha$ there is no difference between being completely negative and being acn.
-The only ordinals for which there is  a difference are those of the form $\mu+1$, where $\mu$ is a limit ordinal.
-
-Our category will have acn $\alpha$-games as objects and the morphisms from $A$ to $B$ will be partial strategies for $A\implies B$.  Later we will consider the total strategy case.
-
-\begin{proposition}
-  \label{TensorIsAcn}
-  Let $A,B$ be acn $\alpha$-games.  Then $A\tensor B$ is acn
-  \begin{proof}
-    Let $s\in P_{A\tensor B}$ be a limiting play that is not length maximal.
-Then at least one of $s\vert_A$ and $s\vert_B$ must be a limiting play (otherwise they both have last moves and the later of the two will be the last move in $s$).
-Suppose that $s\vert_A$ and $s\vert_B$ are both limiting plays.
-By Lemma \ref{TechnicalOrdinalLemma}, $\length(s\vert_A),\length(s\vert_B)\le\length(s)$, so neither $s\vert_A$ nor $s\vert_B$ is length maximal, since $s$ is not.
-Therefore, $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=P$, since $A$ and $B$ are acn.
-Therefore, $\zeta_{A\tensor B}(s)=P$, since $P\wedge P=P$.
-
-    Suppose instead that $s\vert_A$ is a successor play.
-Then $s\vert_B$ is a limiting play.
-Since $s$ is a limiting play, there must be moves from $B$ in $s$ that occur after the last move in $s\vert_A$.
-Therefore, $\zeta_A(s\vert_A)=P$ by Proposition \ref{TransWhoSwitchesGames}.
-Now $s\vert_B$ is a limiting play and not length maximal, so $\zeta_B(s\vert_B)=P$ and therefore $\zeta_{A\tensor B}(s)=P$.
-The case where $s\vert_B$ is a successor play and $s\vert_A$ is a limiting play is similar.
-  \end{proof}
-\end{proposition}
-
-Note, however, that $A\implies B$ is not necessarily acn, even if $A,B$ are completely negative.
-This is a direct consequence of the extension of the definitions to ordinals greater than $\omega$.
-For negative $\omega$-games $A,B$, the only limiting play is the empty play and its components are both necessarily empty, so they are also limiting plays.
-Therefore, $A\implies B$ is a negative game, by the equation $(P\Rightarrow P) = P$.
-
-However, when we move beyond $\omega$, it is no longer true that the components of a limiting play are always limiting plays, so we cannot be sure that they are $P$-positions, and this means that $A\implies B$ is not necessarily completely negative, even if $A,B$ are.
-As an example, we take the completely negative game
-\[
-  \bot=\{\{*\},\{*\mapsto O\},\{\emptyplay\mapsto P,\;*\mapsto O\}, \{\emptyplay, *\}\}
-  \]
-which has a single $O$-move with no $P$-replies.
-If $A$ is an acn $\alpha$-game, then $A\implies\bot$ is the same as the game $\neggame A$, but with the extra $O$-move $*$ attached to the start.
-For $\omega$-games, this extra $O$-move means that $A\implies\bot$ is negative if $A$ is negative, but if $A$ contains plays of length greater than $\omega$ then $A\implies\bot$ is not completely negative if $A$ is completely negative: indeed, if $s\in P_A$ is a non-empty limiting play, then we have
-\[
-  \zeta_{A\implies\bot}(*s)=(\zeta_A(s)\Rightarrow\zeta_\bot(*))=(P\Rightarrow O) = O
-  \]
-But $*s$ is a limiting play, so $A\implies\bot$ is not completely negative.
-
-This will pose a problem for our categorical semantics.
-We want to build a category where the objects are acn $\alpha$-games and where the morphisms from a game $A$ to a game $B$ are strategies for $A\implies B$.
-We also want the category to be monoidal closed, which means that we would really like $A\implies B$ to be an object of the category.
-As we have just seen, this is not the case in general.
-
-We take the following approach: we define a morphism in our category between objects $A$ and $B$ to be a strategy for $A\implies B$, ignoring the fact that this is not an object of our category.
-We will get a working definition of the composition of strategies.
-Then, when we come to define the monoidal closed structure on the category, we will use a slightly modified form of $A\implies B$ for our linear implication.
-This modified form will be, in a sense we shall make precise, the smallest modification of $A\implies B$ that is completely negative, and this will be enough to show that it does indeed give us a monoidal closed structure.
-
-Before moving on to the discussion of composition of strategies, we shall want a version of Proposition \ref{nice-negative-games} to record the properties of negative games that make them so useful for our definition of composition.
-
-\begin{proposition}
-  \label{NiceAcnGames}
-  a) Let $A,B$ be acn $\alpha$-games and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\tensor B}$.  Then:
-  \begin{enumerate}[i)]
-    \item If $s$ is not a length maximal limiting play, then either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=P$.  
-    \item $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$ (so $s\in P_{A\tensor B}$).
-  \end{enumerate}
-
-  b) Let $A$ be an acn $\alpha$-game, {\bf let $B$ be an arbitrary $\alpha$-game} and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\implies B}$.  Then:
-  \begin{enumerate}[i)]
-    \item If $s$ is not a length maximal limiting play, then either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=O$.
-    \item $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$ (so $s\in P_{A\implies B}$).
-  \end{enumerate}
-\end{proposition}
-
-Note that the extra hypothesis on (i) is necessary: suppose $\alpha=\omega+1$ and let $\st$ be as defined above where the unique infinite play is $O$-winning.
-Then $\st\tensor\st$ contains an infinite play $s$ both of whose components are infinite and we have $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=O$.
-
-\begin{proof}[Proof of Proposition \ref{NiceAcnGames}]
-  (a): By Proposition \ref{TransTensorWellFormed}, for part (ii) it suffices to show that the set of alternating plays in $P_A\|P_B$ is well-formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$ - i.e., that if $s,sx\in P_A\|P_B$ are alternating then $\zeta_{A\tensor B}(sx)=\lambda_{A\tensor B}(x)$.
-
-  If $s$ is a limiting play, then one of $s\vert_A,s\vert_B$ must be a limiting play.
-By Lemma \ref{TechnicalOrdinalLemma}, $\length(s\vert_A),\length(s\vert_B)\le\length(s)$, so $s\vert_A$ and $s\vert_B$ are not length maximal if $s$ is not.
-Therefore, either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=P$, since $A$ and $B$ are both acn.
-
-  We may now prove (i) and (ii) for all successor plays by induction on their length, exactly as we did in Proposition \ref{nice-negative-games}.
-
-  (b): Again, by Proposition \ref{TransTensorWellFormed}, for part (ii) it suffices to show that the set of alternating plays in $P_A\|P_B$ is well-formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$ - i.e., that if $s,sx\in P_A\|P_B$ are alternating then $\zeta_{A\implies B}(sx)=\lambda_{A\tensor B}(x)$.
-
-  We prove this by induction on the length of the play $s$; the successor case is exactly as in Proposition \ref{nice-negative-games}.
-Suppose that $s$ is a non-length maximal limiting play.
-If $s\vert_A$ is a limiting play, then we are done, since $A$ is acn and $s\vert_A$ is not length maximal by Lemma \ref{TechnicalOrdinalLemma}.
-Otherwise, if $s\vert_A$ is a successor play, then it has a last move $a$.
-Since $s$ is a limiting play, there must be moves from $B$ occurring later in $s$ than $a$, so $a$ is an $O$-move in $A\implies B$ by Proposition \ref{TransWhoSwitchesGames}, so it is a $P$-move in $A$.
-\end{proof}
-
-\subsubsection{Interleavings and the functor into $\Rel$}
-
-We now set out to extend to the transfinite case some of the results that we proved in the previous section about plays and strategies for the game $A\implies B$.
-
-\begin{lemma}
-  \label{TransPlayInStrategyDeterminedByComponents}
-  Let $A,B$ be $\alpha$-games and let $\sigma$ be a strategy for $A\implies B$.  Suppose that $s,t\in\sigma$ are such that $s\vert_A=t\vert_A$ and $s\vert_B=t\vert_B$.  Then $s=t$.
-  \begin{proof}
-    Exactly as in Lemma \ref{PlayInStrategyDeterminedByComponents}: suppose $s\ne t$.
-By well-ordering, there is an earliest index $\beta$ such that $s(\beta)\ne t(\beta)$.
-So we have a sequence $r$ and moves $x\ne y$ such that $rx\prefix s$ and $ry\prefix t$.
-Since $x\ne y$, $r$ must be a $P$-position by the definition of strategy, and so $x,y$ must take place in the same game.
-Therefore, either $s\vert_A\ne t\vert_A$ or $s\vert_B\ne t\vert_B$.
-  \end{proof}
-\end{lemma}
-
-Given acn $\alpha$-games $A$ and $B$ and a strategy $\sigma$ for $A\implies B$, we may define a relation $\grel\sigma\subset P_A\times P_B$ by
-\[
-  \grel\sigma = \{(s\vert_A,s\vert_B)\suchthat\textrm{$s\in\sigma$ is a $P$-position}\}
-  \]
-Once we have our category $\G(\alpha)$ set up, this will allow us to define a functor $\cmap{\F(\alpha)}{\G(\alpha)}{\Rel}$.
-Then the following lemma, which is a version of Lemma \ref{HylandSchalkFaithful}, will tell us that this functor is faithful.
-
-\begin{lemma}
-  \label{TransHylandSchalkFaithful}
-  Let $A,B$ be $\alpha$-games and let $\sigma,\sigma'$ be strategies for $A\implies B$.  Suppose that $\grel\sigma=\grel{\sigma'}$ as subsets of $P_A\times P_B$.  Then $\sigma=\sigma'$.
-  \begin{proof}
-    See Appendix \ref{HylandSchalkFaithfulProof}.
-  \end{proof}
-\end{lemma}
-
-We will postpone discussion of the functor $\cmap{\F(\alpha)}{\G(\alpha)}{\Rel}$ until we have proved the main technical result, which will be the transfinite version of Lemma \ref{LiftingLemma}.
-
-\begin{lemma}
-  \label{TransLiftingLemma}
-  Let $A,B$ be acn $\alpha$-games, let $C$ be an arbitrary $\alpha$-game, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Suppose that $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$.
-Then there exists some ordinal $\beta<\alpha\#\alpha$ such that for all $\gamma$ with $0\le\gamma\le\beta$ there is a unique sequence $\s^\gamma\in\sigma\|\tau$ of length $\gamma$ such that $\s^\gamma\vert_A\prefix s\vert_A$ and $\s\gamma\vert_C\prefix t\vert_C$.
-Moreover, for this $\s^\gamma$ we have $\s^\gamma\vert_{A,B}\prefix s$ and $\s^\gamma\prefix t$ and if $\delta\le\gamma$ then $\s^\delta\prefix\s^\gamma$.
-Lastly, we have $\s^\beta\vert_{A,B}=s$ and $\s^\beta\vert_{B,C}=t$.
-\end{lemma}
-
-Note that we have no explicit formula for the ordinal $\beta$ as we did for the the numeral $n$ in Lemma \ref{LiftingLemma}, owing to the fact that addition of ordinals is less well-behaved than addition of numerals.
-Nevertheless, this lemma shall be sufficient for our purposes.
-
-\begin{proof}[Proof of Lemma \ref{TransLiftingLemma}]
-  We proceed by induction on $\gamma$.  At some point we will be unable to proceed further with the induction, so we terminate and the final $\gamma$ we reach will be our $\beta$.
-
-  There is a unique sequence of length $0$, namely the empty sequence and its $A$- and $C$-components are both empty, so are prefixes of $s$ and $t$.
-
-  Now suppose that $\mu$ is a limit ordinal and that we have a chain of sequences $\s^\gamma$ for all $\gamma<\mu$ such that $\s^\gamma\vert_{A,B}\prefix s$ and $\s^\gamma\vert_{B,C}\prefix t$.
-Then we may take the limit $\s^\mu$ of these sequences and we have $\s^\mu\vert_{A,B}\prefix s$ and $\s^\mu\vert_{B,C}\prefix t$.
-For uniqueness, suppose that $\t^\mu$ has length $\mu$ and that $\t^\mu\vert_A\prefix s\vert_A$ and $\t^\mu\vert_C\prefix t\vert_C$.
-Let $\gamma<\mu$, and let $\t^\gamma$ be the initial prefix of $\t^\mu$ of length $\gamma$.
-Then $\t^\gamma\vert_A\prefix s\vert_A$ and $\t^\gamma\vert_C\prefix t\vert_C$, so $\t^\gamma=\s^\gamma$, by uniqueness.
-Since $\gamma<\mu$ was arbitrary, it follows that $\t^\mu=\s^\mu$.
-
-  Lastly, suppose that $\gamma=\delta+1$ for some ordinal $\delta$ and suppose that we have already constructed the sequence $\s^\delta$.
-If $X$ is an acn $\alpha$-games, $y$ is an arbitrary $\alpha$-game and $r\in P_{X\implies Y}$ is not length maximal, then Proposition \ref{NiceAcnGames}(i) tells us that either $\zeta_X(r\vert_X)=P$ or $\zeta_Y(r\vert_Y)=O$.
-We have $\s^\delta\vert_{A,B}\in P_{A\implies B}$ and $\s^\delta\vert_{B,C}\in P_{B\implies C}$, so if we assume that $\s^\delta\vert_{A,B}$ and $\s^\delta\vert_{B,C}$ are not length maximal plays, this gives us four possible `sign profiles' for the components of the sequence $\s^\delta$:
-
-  \[
-    \begin{array}{c|ccc}
-      \textbf{Case} & \zeta_A(\s^\delta\vert_A) & \zeta_B(\s^\delta\vert_B) & \zeta_C(\s^\delta\vert_C) \\
-      \hline
-      \textbf{A} & P & P & P \\
-      \textbf{B} & P & P & O \\
-      \textbf{C} & P & O & O \\
-      \textbf{D} & O & O & O
-    \end{array}
-    \]
-
-  We now split the argument up according to cases:
-
-  \begin{description}
-    \item[Cases A and B: ] We have $\s^\delta\vert_{B,C}\prefix t$.
-If in fact $\s^\delta\vert_{B,C}=t$, then we terminate and set $\beta=\delta$.
-We claim that in this case we must have $\s^\beta\vert_{A,B}=s$.
-Certainly, $\s^\beta\vert_{A,B}\prefix s$; if this prefix relation is proper then we must have $\s^\beta\vert_{A,B}x\prefix s$ for some move $x$.
-Since $\zeta_A(\s^\beta\vert_A)=\zeta_B(\s^\beta\vert_B)=P$, $x$ must be an $O$-move and it must therefore take place in $B$, which is a contradiction, since $s\vert_B=t\vert_B$:
-      \[
-        \s^\beta\vert_Bx\prefix s\vert_B = t\vert_B=\s^\beta\vert_{B,C}\vert_B=\s^\beta\vert_B\quad\textbf{(contradictory)}
-        \]
-      Therefore, $\s^\beta\vert_{A,B}=s$.
-We must have $\beta<\alpha\#\alpha$, since we may decompose the set of (distinct) moves in $\s^k$ as the disjoint union of the set of moves that occur in $A$ and the set of moves that occur in $B$ or $C$.
-The induced ordering on each of these sets corresponds with the natural ordering of the moves as a play in $P_A$ or in $P_{B\implies C}$, and since $A$ and $B\implies C$ are both $\alpha$-games, this implies that these two orders are both less than $\alpha$.
-
-      Now suppose instead that $\s^\delta\vert_{B,C}$ is a \emph{proper} prefix of $t$.
-So $\s^\delta\vert_{B,C}x\prefix t$ for some move $x$.
-We set $\s^{\delta+1}=\s^\delta x$.
-Now certainly $\s^{\delta+1}\vert_{B,C}\prefix t$; we claim that $\s^{\delta+1}\vert_{A,B}\prefix s$.
-
-      If $x$ is a move from $C$ then $\s^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}\prefix s$.
-So suppose that $x$ is a move from $B$ - so $\s^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}x$.
-Since $s\vert_B=t\vert_B$, this must be a prefix of $s$ unless there is some move from $A$ that occurs immediately after $\s^\delta\vert_{A,B}$.
-But this is impossible in \textbf{Cases A and B}, since $\s^\delta\vert_{A,B}$ is a $P$-position in $A\implies B$ while $\s^\delta\vert_A$ is an $O$-position in $\neggame A$, so any move following $\s^\delta\vert_{A,B}$ must be a move in $B$.
-
-      Lastly, we show uniqueness.
-Suppose that $\t^{\delta+1}\in \sigma\|\tau$ has length $\delta+1$ and that $\t\vert_A\prefix s\vert_C$ and $\t\vert_C\prefix t\vert_C$.
-Let $y$ be the last move of $\t^{\delta+1}$ and write $\t^{\delta+1}=\t^\delta y$.
-Then we have
-      \[
-        \t^\delta\vert_A\prefix \t^{\delta+1}\vert_A\prefix s\vert_A\quad\t^\delta\vert_C\prefix\t^{\delta+1}\vert_C\prefix t\vert_C
-        \]
-      and so $\t^\delta=\s^\delta$ by uniqueness for sequences of length $\delta$.
-We claim that $y=x$.
-By our argument above, $y$ cannot be a move from $A$, so it is a move from $B$ or $C$.
-Then we have:
-      \begin{gather*}
-        \s^\delta y\vert_{B,C} = \t^{\delta+1}\vert_{B,C}\in\tau \\
-        \s^\delta x\vert_{B,C} \prefix t\in\tau
-      \end{gather*}
-      In \textbf{Case B}, $\s^\delta\vert_{B,C}x,\s^\delta\vert_{B,C}y$ are both $P$-plays in $B\implies C$, so they must be equal, since $\tau$ is a strategy.
-In \textbf{Case A}, $x$ and $y$ must both be $O$-moves in $C$.
-So the fact that $\t^{\delta+1}\vert_C=\s^{\delta+1}\vert_C$ means that $x=y$.
-
-      Therefore, $\t^{\delta+1}=\s^{\delta+1}$.
-
-    \item[Cases C and D: ] Entirely symmetrical.  This time, we get the next move from $s$ instead of $t$, and uniqueness follows from the fact that $\sigma$ is a strategy. 
-  \end{description}
-
-  We still need to deal with the case that one of $\s^\delta\vert_{A,B},\s^\delta\vert_{B,C}$ is length maximal.
-In that case, the `sign profile' for the components of $\s^\delta$ might not fit one of the cases in the table above, since Proposition \ref{NiceAcnGames}(i) only holds for non-length maximal pays.
-If the components of $\s^\delta$ do fit \textbf{Case A, B, C or D} above, then our existing argument is valid.
-Otherwise, there are four new cases to consider:
-  \[
-    \begin{array}{c|cccl}
-      \textbf{Case} & \zeta_A(\s^\delta\vert_A) & \zeta_B(\s^\delta\vert_B) & \zeta_C(\s^\delta\vert_C) & \\
-      \cline{1-4}
-      \textbf{E} & O & P & P & \rdelim\}{2}{60mm}[\parbox{60mm}{\hangindent=1em where $\s^\delta\vert_{A,B}$ is a length maximal \\ limiting play}] \\
-      \textbf{F} & O & P & O & \\
-      \textbf{G} & P & O & P & \rdelim\}{2}{60mm}[\parbox{60mm}{\hangindent=1em where $\s^\delta\vert_{B,C}$ is a length maximal \\ limiting play}] \\
-      \textbf{H} & O & O & P &
-    \end{array}
-    \]
-
-  In \textbf{Cases E and F}, we must have $\s^\delta\vert_{A,B}=s$, since it is already length maximal.
-If we also have $\s^\delta\vert_{B,C}=t$ then we set $\beta=\delta$ and terminate.
-Otherwise, we have $\s^\delta\vert_{B,C}x\prefix t$ for some move $x$, and we set $\s^{\delta+1}=\s^\delta x$.
-Then we certainly have $\s^{\delta+1}\vert_{A,B}\prefix s$ and $\s^{\delta+1}\vert_{B,C}\prefix t$.
-
-  For uniqueness, suppose that $\t^{\delta+1}\in\sigma\|\tau$ has length $\delta+1$ and that $\t^{\delta+1}\vert_A\prefix s\vert_A$ and $\t^{\delta+1}\vert_C\prefix t\vert_C$.
-As before, the induction hypothesis tells us that $\t^{\delta+1}$ must be of the form $\s^\delta y$ for some move $y$.
-We claim that $x$ and $y$ must both be moves in $C$: if $x$ is a move in $A$ or $B$ then we have $\s^\delta\vert_{A,B}x\prefix s$, contradicting length maximality of $\s^\delta\vert_{A,B}$.
-If $y$ is a move in $A$ or $B$ then we have $\t^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}y\in\sigma$, and this also contradicts length maximality of $\s^\delta\vert_{A,B}$.
-It follows that $x$ and $y$ are both moves in $C$, so they are identical, since $\s^{\delta+1}\vert_C=\t^{\delta+1}\vert_C$.
-
-  We deal with \textbf{Cases G and H} using a symmetrical argument.
-\end{proof}
-
-We shall use (the proof of) this lemma to show that composition is well defined for acn $\alpha$-games.
-First, though, we shall need to impose some conditions on the ordinal $\alpha$.
-To start with, we shall assume that $\alpha=\omega^\beta$ for some $\beta$.
-It is well known that these are precisely the \emph{additively closed} ordinals -- so if $\gamma,\delta<\omega^\beta$ then $\gamma+\delta<\omega^\beta$.
-We shall want a stronger property though -- the ordinals of the form $\omega^\beta$ are closed under the natural addition $\#$ that we introduced earlier.
-
-To see this, suppose that $\gamma,\delta<\omega^\beta$.  We may write $\gamma$ and $\delta$ in their \emph{Cantor normal forms}:
-\begin{gather*}
-  \gamma = \omega^{\beta_1}.j_1 + \omega^{\beta_2}.j_2 + \cdots + \omega^{\beta_n}.j_n \\
-  \delta = \omega^{\beta_1}.k_1 + \omega^{\beta_2}.k_2 + \cdots + \omega^{\beta_n}.k_n
-\end{gather*}
-Here, $\beta_1>\beta_2>\cdots>\beta_n$, and $n,j_1,\dots,j_n,k_1,\dots,k_n<\omega$ (We allow $j_i,k_i$ to be zero so that we can use the same sequence $\beta_i$ in both cases.)  Then we may write
-\[
-  \gamma\#\delta = \omega^{\beta_1}.(j_1+k_1) + \omega^{\beta_2}.(j_2+k_2) + \cdots + \omega^{\beta_n}.(j_n+k_n)
-  \]
-using the fact that $\omega^\xi+\omega^\eta=\omega^\xi\#\omega^\eta$ if $\xi\ge\eta$ and the fact that the natural addition $\#$ is commutative.
-Since $\gamma,\delta<\omega^\beta$, we must have $\beta_i<\beta$ for each $i$ and therefore $\gamma\#\delta<\omega^\beta$, since $\omega^\beta$ is additively closed.
-
-The reason that this is good for us is that it means that if $A,B,C$ are completely negative $\omega^\beta$-games, and if $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$ then any sequence $\s\in\sigma\|\tau$ must have length less than $\omega^\beta$.
-Indeed, we may split $\s$ into its $A,B$-component and its $C$-component -- if these have lengths $\gamma,\delta<\omega^\beta$ then the full sequence has length at most $\gamma\#\delta<\omega^\beta$.
-This allows us to ensure that $\s\vert_{A,C}$ has length at most $\omega^\beta$ -- so that it is a valid play in $A\implies C$.
-
-To get an idea of why we need to make some restriction on the ordinal $\alpha$, consider the situation when $\alpha=\omega^2+1$.  We define a game $\st$ as before:
-\begin{gather*}
-  M_{\st} = \{q,a\} \\
-  \lambda_{\st}(q) = O,\;\lambda_{\st}(a)=P \\
-\end{gather*}
-$P_\st$ will be the set of all plays $s\in M_\st^{*<\omega^2+1}$ such that $q$ is always followed by $a$, $a$ is always followed by $q$ and a limiting play is always followed by $q$.
-We define $\zeta_\st$ to make $\st$ into a completely negative game.
-
-Let $A=B=C=\st$.
-Consider the sequence of plays $s_0,s_1,\dots,s_{\omega^2}$ in $A\implies B$ shown in Figure \ref{TooLongAB} and the sequence $t_0,t_1,\dots,t_{\omega+1}$ in $B\implies C$ shown in Figure \ref{TooLongBC}.
-These sequences have matching $B$-components, so Lemma \ref{TransLiftingLemma} tells us that we can interleave them to give a sequence $\s$.
-But now $\s\vert_{A,C}$ consists in a single move in $C$ followed by a play of length $\omega^2$ in $A$, followed by a single move in $C$ - in other words, it has length $\omega^2+1$, which is too long.
-\begin{figure}[!ht]
-  \[
-    \begin{array}{ccccc}
-      \delta & A & B & \zeta_A(s_\delta\vert_A) & \zeta_B(s_\delta\vert_B) \\
-      \hline
-      0 & & & P & P \\
-      \hline
-      1 & & q & P & O \\
-      2 & q & & O & O \\
-      3 & a & & P & O \\
-      4 & q & & O & O \\
-      5 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega & & & P & O \\
-      \hline
-      \omega+1 & & a & P & P \\
-      \omega+2 & & q & P & O \\
-      \omega+3 & q & & O & O \\
-      \omega+4 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega2 & & & P & O \\
-      \hline
-      \omega2+1 & & a & P & P \\
-      \omega2+2 & & q & P & O \\
-      \omega2+3 & q & & O & O \\
-      \omega2+4 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega3 & & & P & O \\
-      \hline
-      \multicolumn{5}{c}{\vdots}\\
-      \multicolumn{5}{c}{\vdots}\\
-      \hline
-      \omega^2 & & & P & P \\
-      \hline
-    \end{array}
-    \]
-  \caption{Diagrammatic representation of a play $s$ of length $\omega^2$ in $A\implies B=\st\implies \st$.
-Here $\s_\delta$ is the initial segment of $s$ of length $\delta$.
-Note that $s\vert_A$ has length $\omega^2$, while $s\vert_B$ has length $\omega$, since only finitely many moves from $B$ are played in each $\omega$-segment.}
-  \label{TooLongAB}
-\end{figure}
-
-\begin{figure}[!ht]
-  \[
-    \begin{array}{ccccc}
-      \delta & B & C & \zeta_B(t_\delta\vert_B) & \zeta_C(t_\delta\vert_C) \\
-      \hline
-      0 & & & P & P \\
-      \hline
-      1 & & q & P & O \\
-      2 & q & & O & O \\
-      3 & a & & P & O \\
-      4 & q & & O & O \\
-      5 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega & & & P & O \\
-      \hline
-      \omega+1 & & a & P & P \\
-    \end{array}
-    \]
-  \caption{Diagrammatic representation of a play $t$ of length $\omega+1$ in $B\implies C=\st\implies \st$.
-Compare with Figure \ref{TooLongAB} and notice that the $B$-component of this sequence is exactly the same as the $B$-component in that sequence.}
-  \label{TooLongBC}
-\end{figure}
-
-Therefore we shall restrict for now to ordinals $\alpha$ of the form $\omega^\beta$.
-This means in particular that there is no distinction between completely negative $\alpha$-games and acn $\alpha$-games, so we shall deal with completely negative games for simplicity.
-Later on, we shall mimic the construction of win-games to construct categories of games over ordinals of the form $\omega^\beta+1$, but for the reasons outlined above this will not be as simple as changing the ordinal from $\omega^\beta$ to $\omega^\beta+1$ in our definitions.
-
-Now we have made this restriction on $\alpha$, the fact that composition is well-defined follows as a corollary of Lemma \ref{TransLiftingLemma}.
-
-\begin{corollary}
-  Let $\alpha$ be an ordinal of the form $\omega^{\beta}$.
-Let $A,B$ be completely negative $\alpha$-games, let $C$ be an arbitrary $\alpha$-game, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Set
-  \[
-    \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
-    \]
-  as before.  Then $\comp\tau\sigma$ is a strategy for $A\implies C$.
-
-  \begin{proof}
-    We first claim that if $\s\in\sigma\|\tau$ then $\length(\s)<\alpha$.
-Indeed, suppose that $\length(\s\vert_{A,B})=\gamma$ and $\length(\s\vert_C)=\delta$.
-Then $\gamma,\delta<\alpha$, since $\s\vert_{A,B}\in P_{A\implies C}$ and $\s\vert_C\in P_C$.
-We have order-preserving inclusions
-    \begin{gather*}
-      \gamma\hookrightarrow\length(\s)\\
-      \delta\hookrightarrow\length(\s)
-    \end{gather*}
-    that make the underlying set of $\length(\s)$ into the disjoint union $\gamma\sqcup\delta$.
-Then the induced orderings on $\gamma,\delta$ are the same as their original orderings, so we must have $\length(\s)\le\gamma\#\delta$.
-Since $\alpha$ is closed under natural addition $\#$, this means that $\length(\s)<\alpha$.
-
-    Now we see that $\comp\tau\sigma\subset P_A\|P_C$: if $\s\in\sigma\|\tau$, then $\s\vert_{A,C}\vert_A=\s\vert_{A,B}\vert_A\in P_A$ and similarly $\s\vert_{A,C}\vert_C=\s\vert_{B,C}\vert_C\in P_C$.
-To show that $\comp\tau\sigma\subset P_{A\implies C}$, it suffices by Proposition \ref{NiceAcnGames}(ii) to show that $\comp\tau\sigma$ is alternating with respect to $\zeta_{A\implies C}$.
-
-    Suppose $\s a\in\sigma\|\tau$ for some move $a\in M_A$.
-By the proof of Lemma \ref{TransLiftingLemma}, we must be in \textbf{Case C or D} (there are no length maximal plays, so \textbf{Cases G and H} never occur).
-The following table shows that we must have $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{A\implies C}(\s\vert_{A,C})$:
-    \[
-      \begin{array}{c|ccc|cc}
-        \textbf{Case} & \zeta_A(\s\vert_A) & \zeta_B(\s\vert_B) & \zeta_C(\s\vert_C) & \zeta_{A\implies B}(\s\vert_{A,B}) & \zeta_{A\implies C}(\s\vert_{A,C}) \\
-        \hline
-        \textbf{C} & P & O & O & O & O \\
-        \textbf{D} & O & O & O & P & P \\
-      \end{array}
-      \]
-    Then we get:
-    \[
-      \lambda_{A\implies C}(a) = \lambda_{A\implies B}(a) = \neg\zeta_{A\implies B}(\s) = \neg\zeta_{A\implies C}(\s)
-      \]
-    as desired.
-The case when we have $\s c\in\tau\|\sigma$ for some $c\in M_C$ is entirely symmetrical, working in \textbf{Cases A and B} this time.
-Therefore, $\comp\tau\sigma\subset P_{A\implies C}$.
-
-    We now need to show that the two strategy conditions are satisfied.
-Let $\s\in\sigma\|\tau$ and suppose that $\s\vert_{A,C}$ is a $P$-position and that $a\in M_A$ is an $O$-move in $A$ such that $\s\vert_{A,C}a \in P_{A\implies C}$.
-We want to show that $\s\vert_{A,C}a\in \comp\tau\sigma$.
-Since $\s\vert_{A,C}$ is a $P$-position, we must be in \textbf{Case A or Case D}.
-In that case, $\s\vert_{A,B}$ is a $P$-position and we know that $\s\vert_Aa\in P_A$, so $\s\vert_{A,B}a\in P_{A\implies B}$.
-Since $\sigma$ is a strategy, that implies that $\s\vert_{A,B}a\in\sigma$ and therefore $\s a\in\sigma\|\tau$.
-So we have $\s\vert_{A,C}a=\s a\vert_{A,C}\in\comp\tau\sigma$.
-
-    A symmetrical argument shows that if $c\in M_C$ is an $O$-move in $C$ and $\s\vert_{A,C}c\in P_{A\implies C}$ then $\s\vert_{A,C}c\in\comp\tau\sigma$.
-
-    Lastly, suppose that we have $s\in P_{A\implies C}$ is an $O$-position and that $x,y\in M_{A\implies C}$ are $P$-moves such that $sx,sy\in\comp\tau\sigma$.
-We need to show that $x=y$.
-By the definition of $\comp\tau\sigma$, there are sequences $\s,\t\in\sigma\|\tau$ with $\s\vert_{A,C}=sx$ and $\t\vert_{A,C}=sy$.
-We may write:
-    \begin{gather*}
-      \s = \s'x \\
-      \t = \t'y
-    \end{gather*}
-
-    Without loss of generality, assume that $\length(\s')\le\length(\t')$ and write $\t'=\t''\r$, where $\t''$ has the same length as $\s'$.
-Then $\t''\vert_A\prefix\s'\vert_A$ and $\t''\vert_C\prefix\s'\vert_C$, so $\t''=\s'$ by Lemma \ref{TransLiftingLemma}.
-
-    We claim that $\r=\emptyplay$.  Indeed, suppose $\r$ is non-empty.  We have
-    \[
-      \t''\r\vert_{A,C}=\t'\vert_{A,C}=s=\s'\vert_{A,C}=\t''\vert_{A,C}
-      \]
-    and so $\r$ must be entirely composed of moves from $B$.
-Let $b$ be the first move in $\r$.
-Then $\s'x$ and $\s'b$ have the same length and we have $\s'b\vert_A\prefix\s'x\vert_A$ and $\s'b\vert_C\prefix\s'x\vert_C$, so $b=a$, which is impossible.
-
-    Therefore, we must have $\s'x, \s'y\in\sigma\|\tau$.
-Since $x,y$ are $P$-moves in $A\implies C$, each must be either an $O$-move in $A$ or a $P$-move in $C$.
-It follows that either $\s'$ is in \textbf{Case B} and $x$ and $y$ are both moves in $C$ or that $\s'$ is in \textbf{Case C} and $x$ and $y$ are both moves in $A$.
-Suppose $\s'$ is in \textbf{Case B} and $x$ and $y$ are moves in $C$.
-Then $\s'\vert_{B,C}x,\s'\vert_{B,C}\in\tau$ and so $x=y$, since they are $P$-moves and $\tau$ is a strategy.
-Similarly, if $\s'$ is in \textbf{Case C} and $x$ and $y$ are moves in $A$, we have $\s'\vert_{A,B}x,\s'\vert_{A,B}y\in\sigma$ and so $x=y$ since $\sigma$ is a strategy.
-  \end{proof}
-\end{corollary}
-
-As a second corollary of Lemma \ref{TransLiftingLemma}, we show that the relational presentation of games and strategies respects composition:
-
-\begin{corollary}
-  \label{TransHylandSchalkIsFunctor}
-  Let $\alpha=\omega^\beta$ for some $\beta$ and let $A,B,C$ be completely negative $\alpha$-games.
-Let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Then we have:
-  \[
-    \grel{\comp\tau\sigma} = \comp{\grel\tau}{\grel\sigma}
-    \]
-  \begin{proof}
-    We have 
-    \begin{gather*}
-      \grel{\comp\tau\sigma} = \left\{(s\vert_A,s\vert_C)\suchthat\textrm{$s\in\comp\tau\sigma$ is a $P$-play}\right\} \\
-      \comp{\grel\tau}{\grel\sigma}=\{(s,t)\in P_A\times P_C\suchthat\exists u\in P_B\esuchthat (s,u)\in\grel\tau,\;(u,t)\in\grel\sigma\}
-    \end{gather*}
-    Suppose $s\in\comp\tau\sigma$ is a $P$-play and write $s=\s\vert_{A,C}$, where $\s\in\sigma\|\tau$.
-Then we have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$.
-Since $s=\s\vert_{A,C}$ is a $P$-play, $\s$ must be in \textbf{Case A or Case D}, so $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both $P$-plays.
-Therefore, we have
-    \begin{gather*}
-      (s\vert_A,\s\vert_B)\in\grel\sigma\\
-      (\s\vert_B,s\vert_C)\in\grel\tau
-    \end{gather*}
-    and therefore $(s\vert_A,s\vert_C)\in\comp{\grel\tau}{\grel\sigma}$.
-Conversely, suppose $(s, t)\in\comp{\grel\tau}{\grel\sigma}$.
-Then there exist $S\in\sigma,T\in\tau$ such that $S\vert_A=s$, $S\vert_B=T\vert_B$ and $T\vert_C=t$.
-By Lemma \ref{TransLiftingLemma}, there is some $\s\in\sigma\|\tau$ such that $\s\vert_A=s$ and $\s\vert_C=t$.
-So $(s,t)\in\grel{\comp\tau\sigma}$.
-  \end{proof}
-\end{corollary}
-
-\begin{corollary}
-  \label{TransIsCategory}
-  Let $\alpha=\omega^\beta$ for some $\beta$.
-Then we can define a category $\G(\alpha)$ as follows - the objects are completely negative $\alpha$-games, and if $A,B$ are two objects then a morphism from $A$ to $B$ is given by a strategy for $A\implies B$.
-We compose strategies as above.
-If $A$ is an object, then the identity morphism on $A$ is given by
-  \[
-    \id_A = \left\{s\in P_{A\implies A}\suchthat\textrm{for all $P$-positions $t\prefix s$, $t\vert_A=t\vert_\bneggame{A}$}\right\}
-    \]
-  \begin{proof}
-    We need to check that this is indeed an identity and that composition is associative.  We do this using the relational presentation exactly as in Theorem \ref{IsCategory}.  
-  \end{proof}
-\end{corollary}
-
-\subsubsection{Symmetric monoidal structure}
-
-In this section, we shall fix an ordinal $\alpha=\omega^\beta$.
-The tensor product $\tensor$ on $\alpha$-games makes the category $\G(\alpha)$ into a monoidal category.
-If $A,B$ are objects of $\G(\alpha)$, then Proposition \ref{TensorIsAcn} tells us that $A\tensor B$ is an object of $\G(\alpha)$.
-In fact, $\tensor$ gives us a functor $\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ as follows: let $A,A',B,B'$ be completely negative $\alpha$-games, let $\sigma$ be a strategy for $A'\implies A$ and let $\tau$ be a strategy for $B'\implies B$.
-Then we define a strategy $\sigma\tensor\tau$ for $(A'\tensor B')\implies (A\tensor B)$ as follows:
-\[
-  \sigma\tensor\tau = \{s\in P_{(A'\tensor B')\implies(A\tensor B)}\suchthat s\vert_{A',A}\in\sigma,\;s\vert_{B',B}\in\tau\}
-  \]
-To show that this is indeed a strategy for $(A'\tensor B')\implies (A\tensor B)$, suppose that $s\in\sigma\tensor\tau$ is a $P$-position and that $sx\in P_{(A'\tensor B')\implies (A\tensor B)}$.
-We need to show that $sx\vert_{A',A}\in\sigma$ and that $sx\vert_{B', B}\in\tau$.
-
-We claim that $s\vert_{A',A}$ and $s\vert_{B',B}$ are $P$-positions in $A'\implies A$ and $B'\implies B$.
-Indeed, suppose without loss of generality that $s\vert_{A',A}$ is an $O$-position in $A'\implies A$.
-We will show that $s$ is an $O$-position in $(A'\tensor B')\implies (A\tensor B)$, contradicting our assumptions.
-
-If $s\vert_{A',A}$ is an $O$-position, then $s\vert_{A'}$ is a $P$-position in $A'$ and $s\vert_A$ is an $O$-position in $A$.
-Now, $s\vert_{A,B}$ is a play in $A\tensor B$, so Proposition \ref{NiceAcnGames}(i) tells us that $s\vert_B$ must be a $P$-position in $B$.
-
-Now $s\vert_{B',B}$ is a play in $\tau\subset P_{B'\implies B}$, so Proposition \ref{NiceAcnGames}(i) now tells us that $s\vert_{B'}$ is a $P$-position in $B'$.
-It follows that $s\vert_{A',B'}$ is a $P$-position in $A'\tensor B'$ and that $s\vert_{A,B}$ is an $O$-position in $A\tensor B$, so $s$ is an $O$-position in $(A'\tensor B')\implies (A\tensor B)$, which is the desired contradiction.
-
-Without loss of generality, suppose that the move $x$ occurs in $A'$ or $A$.
-Since $s\vert_{A', A}$ is a $P$-position, we must have $sx\vert_{A',A}\in\sigma$, by the definition of a strategy, and then $s x\vert_{B',B}=s\vert_{B',B}\in\tau$.
-So $sx\in\sigma\tensor\tau$.
-
-For the second strategy condition, suppose that $sx, sy\in\sigma\tensor \tau$, where $s$ is an $O$-position in $(A'\tensor B')\implies(A\tensor B)$ and $x,y$ are $P$-moves.
-Then $s\vert_{A',B'}$ is a $P$-position in $A'\tensor B'$ and $s\vert_{A,B}$ is an $O$-position in $A\tensor B$.
-
-This immediately tells us that $s\vert_{A'}$ is a $P$-position in $A'$ and that $s\vert_{B'}$ is a $P$-position in $B'$.
-Moreover, by Proposition \ref{NiceAcnGames}(i), we know that either $s\vert_{A}$ is a $P$-position in $A$ and $s\vert_{B}$ is an $O$-position in $B$ or that $s\vert_A$ is an $O$-position in $A$ and $s\vert_B$ is a $P$-position in $B$.
-
-That is, we find ourselves in one of the following cases:
-\[
-  \begin{array}{c|cccc}
-    \textbf{Case} & \zeta_{A'}(s\vert_{A'}) & \zeta_{B'}(s\vert_{B'}) & \zeta_A(s\vert_A) & \zeta_B(s\vert_B) \\
-    \hline
-    \textbf{1} & P & P & P & O\\
-    \textbf{2} & P & P & O & P
-  \end{array}
-  \]
-
-Suppose we are in \textbf{Case 1}.
-Then $x$ cannot be a move in $A$ or $A'$: indeed, it is a $P$-move in $(A'\tensor B')\implies (A\tensor B)$, so it would be a $P$-move in $A'\implies A$.
-But $s\vert_{A',A}$ is a $P$-position in $A'\implies A$.
-Similarly, $y$ cannot be a move in $A$ or $A'$.
-Therefore, $x$ and $y$ are both $P$-moves in $B\implies B'$, and then the fact that $\tau$ is a strategy implies that $x=x'$.
-
-In \textbf{Case 2}, we can use a symmetrical argument, this time using the fact that $\sigma$ is a strategy.
-
-It is easy to show that this tensor action on strategies respects composition: indeed, if we have morphisms
-\begin{gather*}
-  A''\xrightarrow{\sigma'}A'\xrightarrow{\sigma}A\\
-  B''\xrightarrow{\tau'}B'\xrightarrow{\tau}B
-\end{gather*}
-then we have
-\begin{gather*}
-  (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'}) = \left\{s\in P_{(A''\tensor B'')\implies(A\tensor B)}\suchthat s\vert_{A'', A}\in\comp\sigma{\sigma'},\;s\vert_{B'', B}\in\comp\tau{\tau'}\right\}
-\end{gather*}
-Meanwhile:
-\begin{align*}
-  (\sigma'\tensor\tau')\|(\sigma\tensor\tau) &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{120pt}{
-    \setlength{\abovedisplayskip}{-5pt}
-    \setlength{\belowdisplayskip}{-10pt}
-    \begin{IEEEeqnarray*}{cCc}
-      \s\vert_{A''\tensor B'',A'\tensor B'} & \in & \sigma'\tensor\tau' \\
-      \s\vert_{A'\tensor B',A\tensor B} & \in & \sigma\tensor\tau
-    \end{IEEEeqnarray*}}
-    \normalsize
-  \end{minipage}}}\right\} \\[1em]
-  &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
-    \setlength{\abovedisplayskip}{-5pt}
-    \setlength{\belowdisplayskip}{-10pt}
-    \begin{IEEEeqnarray*}{cCc}
-      \s\vert_{A'', A'} & \in & \sigma' \\
-      \s\vert_{A', A} & \in & \sigma \\
-      \s\vert_{B'', B'} & \in & \tau' \\
-      \s\vert_{B', B} & \in & \tau
-    \end{IEEEeqnarray*}}
-    \normalsize
-  \end{minipage}}}\right\} \\[1em]
-  &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
-    \setlength{\abovedisplayskip}{-5pt}
-    \setlength{\belowdisplayskip}{-10pt}
-    \begin{IEEEeqnarray*}{cCc}
-      \s\vert_{A'', A', A} & \in & \sigma'\|\sigma \\
-      \s\vert_{B'', B', B} & \in & \tau'\|\tau
-    \end{IEEEeqnarray*}}
-    \normalsize
-  \end{minipage}}}\right\}
-\end{align*}
-
-It follows that
-\[
-  \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}
-  = \left\{\s\vert_{A''\tensor B'', A\tensor B}\suchthat\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)\right\}
-  = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
-  \]
-To define the associators and unitors (which are the obvious choices) for our tensor product, we introduce a bit more technology.
-Let $A',A$ be $\alpha$-games.
-We call a bijective function $\cmap{f}{P_{A'}}{P_A}$ a \emph{tree isomorphism} if $f$ preserves length and the prefix ordering and commutes with $\zeta_A,\zeta_{A'}$.
-If $A,A'$ are completely negative, then we have a strategy $\sigma_f$ for $A'\implies A$ given by
-\[
-  \sigma_f = \left\{s\in P_{A'\implies A}\suchthat \textrm{for all $P$-positions $t\prefix s$, we have $t\vert_A = f\left(t\vert_{A'}\right)$}\right\}
-  \]
-We check that $\sigma_f$ is indeed a strategy.
-It is clearly prefix-closed and satisfies the limit condition by the definition.
-If $s\in\sigma_f$ is a $P$-position, then we must have $sx\in\sigma_f$ for all $sx\in P_{A'\implies A}$.
-Now suppose that $sx,sy\in \sigma_f$.
-We first claim that $x$ and $y$ take place in the same game.
-Indeed, suppose instead that $x$ is a move in $A'$ and $y$ is a move in $A$.
-Then we have
-\begin{gather*}
-  s\vert_A = f\bracketed{s\vert_{A'}x} \\
-  s\vert_Ay = f\bracketed{s\vert_{A'}}
-\end{gather*}
-But this is impossible, since $f$ preserves lengths.  Therefore, $x$ and $y$ take place in the same game.  If they are moves in $A$, we have
-\[
-  s\vert_A x = f\bracketed{s\vert_{A'}} = s\vert_Ay
-  \]
-and so $x=y$, and if they are moves in $A'$, we have
-\[
-  s\vert_{A'}x = f\inv\bracketed{s\vert_A} = s\vert_{A'}y
-  \]
-and so $x=y$ again.
-
-We call a strategy $\sigma_f$ arising from a tree isomorphism $f$ a \emph{copycat strategy}.
-The relational presentation $\grel{\sigma_f}$ of such a strategy $\sigma_f$ is the graph of the function $\cmap{f}{P_{A'}}{P_A}$, and therefore the function $f$ is determined uniquely by the strategy $f$.
-Moreover, if we have completely negative $\alpha$-games $A'', A', A$ and tree isomorphisms $A''\xrightarrow{f'}A'\xrightarrow{f}A$, then we must have
-\[
-  \comp{\sigma_f}{\sigma_{f'}} = \sigma_{\comp{f}{f'}}
-  \]
-We therefore have a full-on-objects subcategory $\G_{\cc}(\alpha)$ of $\G(\alpha)$ of games and copycat strategies that comes equipped with a natural functor $\cmap{\H}{\G_{\cc}(\alpha)}{\Set}$ that sends a game $A$ to $P_A$ and a copycat strategy $\sigma_f$ to the function $f$.
-We get a commutative square in $\CAT$:
-\[
-  \begin{tikzcd}
-    \G_{\cc}(\alpha) \arrow[r, hook] \arrow[d, "\H"']
-      & \G(\alpha) \arrow[d, "\F"] \\
-    \Set \arrow[r, hook]
-      & \Rel
-  \end{tikzcd}
-  \]
-where all the functors in the diagram are faithful.
-
-Given sets $X,Y$ and a function $\cmap{\phi}{X}{Y}$, we write $\overline\phi\from X^{*<\alpha}\to Y^{*<\alpha}$ for the induced map that acts pointwise via $\phi$.
-Observe that disjoint union induces the structure of a symmetric monoidal category on $\Set$ with associators, unitors and braiding:
-\begin{gather*}
-  \assoc_{X,Y,Z}\from (X\cprd Y)\cprd Z\to X\cprd(Y\cprd Z)\\
-  \lunit_X\from \emptyset\cprd X\to X\\
-  \runit_X\from X\cprd\emptyset\to X\\
-  \braid_{X,Y}\from X\cprd Y\to Y\cprd X
-\end{gather*}
-
-Suppose $A,B,C$ are completely negative $\alpha$-games.  We have a function
-\[
-  \assoc_{M_A,M_B,M_C}\from M_{(A\tensor B)\tensor C}\to M_{A\tensor(B\tensor C)}
-  \]
-and it is clear from the definition that this gives rise to a function
-\[
-  \overline{\assoc_{M_A,M_B,M_C}}\from P_{(A\tensor B)\tensor C}\to P_{A\tensor(B\tensor C)}
-  \]
-The tensor unit in our category will be the empty game $I=(\emptyset, \emptyset, \emptyset, \{\emptyplay\})$.  If $A$ is a completely negative $\alpha$-game, we get natural maps
-\begin{gather*}
-  \lunit_{M_A}\from M_{I\tensor A}\to M_A \\
-  \runit_{M_A}\from M_{A\tensor I}\to M_A
-\end{gather*}
-and these give rise to maps
-\begin{gather*}
-  \overline{\lunit_{M_A}}\from P_{I\tensor A}\to P_A\\
-  \overline{\runit_{M_A}}\from P_{A\tensor I}\to P_A
-\end{gather*}
-Lastly, we have a map
-\[
-  \braid_{M_A,M_B}\from M_{A\tensor B}\to M_{B\tensor A}
-  \]
-inducing a map
-\[
-  \overline{\braid_{M_A,M_B}}\from P_{A\tensor B}\to P_{B\tensor A}
-  \]
-It is clear that these maps on sets of plays are all tree isomorphisms, so they give rise to isomorphisms in $\G(\alpha)$:
-\begin{gather*}
-  \assoc_{A,B,C}\from (A\tensor B)\tensor C\to A\tensor (B\tensor B)\\
-  \lunit_A\from I\tensor A\to A\\
-  \runit_A\from A\tensor I\to A\\
-  \braid_{A,B}\from A\tensor B\to B\tensor A
-\end{gather*}
-Since the original isomorphisms in $\Set$ satisfy the pentagon, triangle and hexagon identities, and since all the functors we are considering are faithful, our isomorphisms in $\G(\alpha)$ must satisfy the pentagon, triangle and hexagon identities as well.
-We give the argument in the case of the pentagon identity.
-
-Given completely negative $\alpha$-games $A,B,C,D$, we have the following commutative diagram in $\Set$:
-\[
-  \begin{tikzpicture}[commutative diagrams/every diagram]
-    \node (P0) at (90:2.3cm) {$M_{(A\tensor B)\tensor(C\tensor D)}$};
-    \node (P1) at (90+72:2cm) {$M_{((A\tensor B)\tensor C)\tensor D}$} ;
-    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{$M_{(A\tensor(B\tensor C))\tensor D}$}};
-    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{$ M_{A\tensor((B\tensor C)\tensor D)} $}};
-    \node (P4) at (90+4*72:2cm) {$ M_{A\tensor(B\tensor(C\tensor D))} $};
-  \path[commutative diagrams/.cd, every arrow, every label]
-    (P1) edge node {$\assoc_{M_{A\tensor B},M_C,M_D}$} (P0)
-    (P1) edge node[swap] {$\assoc_{M_A,M_B,M_C}\tensor\id_D$} (P2)
-    (P2) edge node[swap, yshift=-1em] {$\assoc_{M_A,M_{B\tensor C},M_D}$} (P3)
-    (P3) edge node[swap] {$\id_A\tensor\assoc_{M_B,M_C,M_D}$} (P4)
-    (P0) edge node {$\assoc_{M_A,M_B,M_{C\tensor D}}$} (P4);
-  \end{tikzpicture}
-  \]
-which immediately gives rise to a second commutative diagram in $\Set$:
-\[
-  \begin{tikzpicture}[commutative diagrams/every diagram]
-    \node (P0) at (90:2.3cm) {$P_{(A\tensor B)\tensor(C\tensor D)}$};
-    \node (P1) at (90+72:2cm) {$P_{((A\tensor B)\tensor C)\tensor D}$} ;
-    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{$P_{(A\tensor(B\tensor C))\tensor D}$}};
-    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{$ P_{A\tensor((B\tensor C)\tensor D)} $}};
-    \node (P4) at (90+4*72:2cm) {$ P_{A\tensor(B\tensor(C\tensor D))} $};
-  \path[commutative diagrams/.cd, every arrow, every label]
-    (P1) edge node {$\overline{\assoc_{M_{A\tensor B},M_C,M_D}}$} (P0)
-    (P1) edge node[swap] {$\overline{\assoc_{M_A,M_B,M_C}\tensor\id_D}$} (P2)
-    (P2) edge node[swap, yshift=-1em] {$\overline{\assoc_{M_A,M_{B\tensor C},M_D}}$} (P3)
-    (P3) edge node[swap] {$\overline{\id_A\tensor\assoc_{M_B,M_C,M_D}}$} (P4)
-    (P0) edge node {$\overline{\assoc_{M_A,M_B,M_{C\tensor D}}}$} (P4);
-  \end{tikzpicture}
-  \]
-But this is the image under the functor $\H$ of the following diagram in $\G_{\cc}(\alpha)$:
-\[
-  \begin{tikzpicture}[commutative diagrams/every diagram]
-    \node (P0) at (90:2.3cm) {${(A\tensor B)\tensor(C\tensor D)}$};
-    \node (P1) at (90+72:2cm) {${((A\tensor B)\tensor C)\tensor D}$} ;
-    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{${(A\tensor(B\tensor C))\tensor D}$}};
-    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{${A\tensor((B\tensor C)\tensor D)} $}};
-    \node (P4) at (90+4*72:2cm) {${A\tensor(B\tensor(C\tensor D))} $};
-  \path[commutative diagrams/.cd, every arrow, every label]
-    (P1) edge node {$\assoc_{{A\tensor B},C,D}$} (P0)
-    (P1) edge node[swap] {$\assoc_{A,B,C}\tensor\id_D$} (P2)
-    (P2) edge node[swap, yshift=-1em] {$\assoc_{A,{B\tensor C},D}$} (P3)
-    (P3) edge node[swap] {$\id_A\tensor\assoc_{B,C,D}$} (P4)
-    (P0) edge node {$\assoc_{A,B,{C\tensor D}}$} (P4);
-  \end{tikzpicture}
-  \]
-Since $\H$ is a faithful functor and the second diagram commutes, this last diagram must commute as well.
-
-It remains to show that $\assoc_{A,B,C},\lunit_A,\runit_A,\braid_{A,B}$ are natural transformations.  We show this for $\assoc_{A,B,C}$ and the other cases are entirely similar.
-
-Showing that $\assoc_{A,B,C}$ is a natural transformation from $((\blank\tensor \blank)\tensor \blank)$ to $(\blank\tensor(\blank\tensor \blank)\from \G(\alpha)\times\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ means showing that the following diagram commutes for all completely negative $\alpha$-games $A',B',C',A,B,C$ and all morphisms $\sigma\from A'\to A,\tau\from B'\to B,\upsilon\from C'\to C$:
-\[
-  \begin{tikzcd}
-    (A'\tensor B')\tensor C' \arrow[r, "(\sigma\tensor\tau)\tensor\upsilon"'] \arrow[d, "\assoc_{A', B', C'}"']
-      & (A\tensor B)\tensor C \arrow[d, "\assoc_{A,B,C}"] \\
-    A'\tensor(B'\tensor C') \arrow[r, "\sigma\tensor(\tau\tensor\upsilon)"']
-      & A\tensor(B\tensor C)
-  \end{tikzcd}
-  \]
-It is easy to check that this diagram commutes by applying the functor $\F\colon\G(\alpha)\to\Rel$.
-The relational content $\grel{\assoc_{A,B,C}}$ of the strategy $\assoc_{A,B,C}$ is the graph of the function
-\[
-  \overline{\assoc_{M_A,M_B,M_C}}\from P_{(A\tensor B)\tensor C}\to P_{A\tensor(B\tensor C)}
-  \]
-and its action by left composition on $\grel{(\sigma\tensor\tau)\tensor\upsilon}\subset P_{(A'\tensor B')\tensor C'}\times P_{(A\tensor B)\tensor C}$ is pointwise application of this function.
-We find that
-\begin{align*}
-  \grel{\comp{\assoc_{A,B,C}}{(\sigma\tensor\tau)\tensor\upsilon}}
-  &=\comp{\grel{\assoc_{A,B,C}}}{\grel{(\sigma\tensor\tau)\tensor\upsilon}}\\
-  &=\left\{(s,t)\in P_{(A'\tensor B')\tensor C'}\times P_{A\tensor(B\tensor C)}\;\middle|\;\mbox{\pbox{\textwidth}{$(s\vert_{A'},t\vert_A)\in\grel{\sigma}$\\$(s\vert_{B'},t\vert_B)\in\grel\tau$\\$(s\vert_{C'},t\vert_C)\in\grel\upsilon$}}\right\}
-\end{align*}
-A similar argument now shows that $\grel{\comp{\sigma\tensor(\tau\tensor\upsilon)}{\assoc_{A', B', C'}}}$ is equal to the same set, and so we have a commutative diagram in $\Rel$:
-\[
-  \begin{tikzcd}
-    P_{(A'\tensor B')\tensor C'} \arrow[r, "\grel{(\sigma\tensor\tau)\tensor\upsilon}"'] \arrow[d, "\grel{\assoc_{A', B', C'}}"']
-      & P_{(A\tensor B)\tensor C} \arrow[d, "\grel{\assoc_{A,B,C}}"] \\
-    P_{A'\tensor(B'\tensor C')} \arrow[r, "\grel{\sigma\tensor(\tau\tensor\upsilon)}"']
-      & P_{A\tensor(B\tensor C)}
-  \end{tikzcd}
-  \]
-Therefore, our original diagram in $\G(\alpha)$ is commutative, since the functor $\F$ is faithful.
-
-We therefore have the structure of a symmetric monoidal category on $\G(\alpha)$.
-
-\subsubsection{Symmetric monoidal closed structure}
-\label{TransSMCCSex}
-
-In existing finitary models of game semantics, the category of games is made into a symmetric monoidal closed category where the linear implication of two objects is given by the connective $\implies$.
-As we remarked earlier, this approach will not work immediately for us, since $A\implies B$ need not be completely negative even if $A$ and $B$ are.
-Our solution will be to modify $A\implies B$ so that it becomes completely negative.
-
-Remember that when we proved that the composition of strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ is well defined, we were careful not to require that $C$ be acn (or completely negative).
-From the point of view of constructing a category whose objects are $\alpha$-games, this is not useful, but it does allow us to construct certain alternative categories.
-
-\begin{definition}
-  Recall that if $\C$ is a category and $A$ is an object of $\C$, then the \emph{slice category} $\C/A$ is the category where the objects are morphisms
-  \[
-    \map{f}{B}{A}
-    \]
-  where $B$ is an object of $\C$ and where the morphisms between an object $\map{f}{B}{A}$ and an object $\map{g}{C}{A}$ are commutative triangles:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "f"] \arrow[d, "h"']
-       & A \\
-      C \arrow[ur, "g"]
-        &
-    \end{tikzcd}
-    \]
-  Let $A$ be a (not necessarily completely negative) $\alpha$-game.  Abusing notation slightly, we write $\G(\alpha)/A$ for the category whose objects are strategies
-  \[
-    \sigma\from B\implies A
-    \]
-  for $B$ a \emph{completely negative} $\alpha$-game and where the morphisms from an object $\map{\sigma}{B}{A}$ to an object $\map{\tau}{C}{A}$ are commutative triangles of the form
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\sigma"] \arrow[d, "\upsilon"']
-       & A \\
-      C \arrow[ur, "\tau"]
-        &
-    \end{tikzcd}
-    \]
-\end{definition}
-
-The main technical result we shall use to construct our closed monoidal structure is the following theorem:
-\begin{theorem}
-  \label{SliceTerminalObject}
-  Let $A$ be an $\alpha$-game.  Then the category $\G(\alpha)/A$ has a terminal object.
-\end{theorem}
-
-Note that if $A$ is completely negative, then the terminal object of $\G(\alpha)/A$ is the identity strategy $\map{\id_A}{A}{A}$, as is standard for slice categories.
-If $A$ is not completely negative, then we will need to use a different construction.
-
-We will write this terminal object as $A^{\cn}\xrightarrow{\cn}A$.
-$A^{\cn}$ should be thought of as the `smallest completely negative extension of $A$', and the fact that it gives rise to a terminal object in $\G(\alpha)/A$ makes this vague notion precise.
-If $A$ and $B$ are completely negative $\alpha$-games, we shall define a game $A\impliescn B$ to be given by $(A\implies B)^{\cn}$.
-We will then be able to use the fact that $(A\implies B)^{\cn}$ gives rise to a terminal object in the category $\G(\alpha)/(A\implies B)$ to show that the connective $\impliescn$ in fact gives rise to a monoidal closed structure on $\G(\alpha)$.
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  We form a completely negative $\alpha$-game $A^{\cn}$ as follows:
-  \begin{itemize}
-    \item $M_{A^{\cn}}=M_A\cprd \{*_t\suchthat \textrm{$t\in P_A$ is a limiting $O$-play}\}$
-    \item $\lambda_{A^{\cn}}(x)=\lambda_A(x)$ for all $x\in M_A$.  $\lambda_{A^{\cn}}(*_s)=O$
-    \item $\zeta_{A^{\cn}}(sx)=\lambda_{A^{\cn}}(x)$ for $sx\in P_{A^{\cn}}$ a successor play.
-    \item $\zeta_{A^{\cn}}(s)=P$ for $s\in P_{A^{\cn}}$ a limiting play.
-  \end{itemize}
-  \[
-    P_{A^{\cn}} = \left\{s\in \left(M_{A^{\cn}}\right)^{*<\alpha}\;\middle|\;\mbox{\pbox{200px}{
-      $t\vert_{M_A}\in P_A$\\
-      If $u*_t\prefix s$ then $u=t$. \\
-      If $vx\prefix s$ and $v\vert_{M_A}$ is a limiting $O$-play in $P_A$ then $x=*_v$
-    }}\right\}
-    \]
-
-  In other words, we force $A$ to be completely negative by making all limiting plays be $P$-plays.
-If $u$ was a limiting $O$-play in $A$, then it becomes a $P$-play in $A^{\cn}$.
-Since the moves that follow $u$ in $A$ are $P$-moves, we add in an extra $O$-move $*_u$ in order to preserve the alternating condition.
-\end{definition}
-
-\begin{example}
-  If $\alpha=\omega$ and $A$ is a negative game then we have $\bneggame A^{\cn}\cong A\implies\bot$: the single move in $\bot$ takes the role of $*_{\emptyplay}$.
-However, if $\alpha$ is a higher ordinal, then this does not hold, since $A\implies\bot$ is no longer a completely negative game.
-
-  If $A,B$ are completely negative $\alpha$-games, we define $A\impliescn B$ to stand for $(A\implies B)^{\cn}$.
-Then we do have $\bneggame{A}^{\cn}\cong A\impliescn \bot$.
-The object $A\impliescn B$ will be the linear implication in our category.
-\end{example}
+It can be shown that this functor $\F$ is faithful (see Calderon and McCusker, 2010 for a proof).
+This surprising fact will be very useful for us: if we want to show that a particular diagram commutes in $\G$, we can normally do so more easily by applying the functor $\F$ to the diagram and showing that the resulting diagram commutes in $\Rel$.
 
 \begin{notation}
-  Given a sequence $s\in P_{A^{\cn}}$, we may restrict $s$ to a play $s\vert_A\in P_A$ by removing all the $*$-moves.  
+  We shall simplify our notation by writing $P_A$ rather than $\F(A)$ and writing $\grel{\sigma}$ rather than $\F(\sigma)$.
 \end{notation}
 
-Given an $\alpha$-game $A$, there is a natural strategy $\cn_A$ for $A^{\cn}\implies A$ given by
-\[
-  \cn_A = \left\{s\in P_{A^{\cn}\implies A}\suchthat\textrm{for all $P$-positions $t\prefix s$, $t\vert_{A^{\cn}}\vert_A=t\vert_A$}\right\}
-  \]
-Concretely, this strategy is the copycat strategy for $A$, with the difference that whenever we reach a limiting $O$-play $u$ in $A$, player $P$ plays the extra move $*_u$ in $A^{\cn}$ before continuing.
-
-We claim that $\map{\cn_A}{A^{\cn}}{A}$ is the terminal object in the category $\G(\alpha)/A$.  To do that, it will suffice to prove the following proposition:
-
-\begin{proposition}
-  \label{CnUniversalProperty}
-  $\cn_A$ is a total strategy for $A^{\cn}\implies A$.
-Moreover, $\cn_A$ satisfies the following universal property: given a completely negative $\alpha$-game $B$ and a strategy $\sigma$ for $B\implies A$, there is a unique strategy $\sigma^{\cn}$ for $B\implies A^{\cn}$ such that the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\sigma^{\cn}"] \arrow[dr, "\sigma"']
-        & A^{\cn} \arrow[d, "\cn_A"] \\
-      %
-        & A
-    \end{tikzcd}
-    \]
-\end{proposition}
-
-\begin{proof}
-  We first show that $\cn_A$ is a valid strategy for $A^{\cn}\implies A$.
-It is certainly prefix closed and satisfies the limiting condition by its definition.
-Moreover, if $s\in\cn_A$ is a $P$-position and $sx\in P_{A^{\cn}\implies A}$ then $sx$ satisfies the conditions to be an element of $\cn_A$.
-
-  Suppose that $sx, sy\in \cn_A$ are $P$-positions.
-Suppose first that neither $x$ nor $y$ is a move of the form $*_t$.
-We claim that $sx,sy$ take place in the same game.
-Indeed, suppose instead that $x$ is a move in $A^{\cn}$ and $y$ is a move in $A$.
-Then we have:
-  \begin{gather*}
-    s\vert_{A^{\cn}}\vert_A x = sx\vert_{A^{\cn}}\vert_A = sx\vert_A = s\vert_A\\
-    s\vert_{A^{\cn}}\vert_A = sy\vert_{A^{\cn}}\vert_A = sy\vert_A = s\vert_Ay
-  \end{gather*}
-  which is a contradiction since it implies that $s\vert_{A^{\cn}}\vert_A$ is simultaneously a shorter sequence than $s\vert_A$ and a longer sequence than $s\vert_A$.
-
-  If $x,y$ are both moves in $A^{\cn}$ then we have
-  \begin{align*}
-    s\vert_{A^{\cn}}\vert_A x &= sx\vert_{A^{\cn}}\vert_A \\
-    & = sx\vert_A\\
-    & = s\vert_A
-  \end{align*}
-  and $s\vert_{A^{\cn}}\vert_Ay=s\vert_A$ by an identical argument, and so $x=y$.  Similarly, if $x,y$ are both moves in $A$, then we have:
-  \begin{align*}
-    s\vert_A x &= sx\vert_A \\
-    &= sx\vert_{A^{\cn}}\vert_A\\
-    &= s\vert_{A^{\cn}}\vert_A
-  \end{align*}
-  and similarly for $y$, so $x=y$.
-
-  Now, without loss of generality assume that $x=*_t$ for some $t$.  Then $s\vert_{A^{\cn}}\vert_A$ is a limiting play.  Suppose for a contradiction that $y$ is a move in $A$.  Then we have:
-  \[
-    s\vert_{A^{\cn}}\vert_A = sy\vert_{A^{\cn}}\vert_A=sy\vert_A = s\vert_Ay
-    \]
-  which is a contradiction, since $s\vert_Ay$ is a successor play.  Therefore, $y$ is a move in $A^{\cn}$.  We have:
-  \begin{align*}
-    t &= s\vert_{A^{\cn}}\vert_A\\
-    &= s*_t\vert_{A^{\cn}}\vert_A\\
-    &= s*_t\vert_{A^{\cn}}\vert_A\\
-    &= s\vert_{A^{\cn}}\vert_A
-  \end{align*}
-  Therefore, $s\vert_{A^{\cn}}\vert_A$ is a limiting $O$-play in $A$ and therefore we have $x=y=*_t$ by the definition of $A^{\cn}$.
-
-  Now we show that $\cn_A$ is total.
-Suppose that $s\in\cn_A$ is an $O$-position.
-Then $s\vert_{A^{\cn}}$ is a $P$-position and $s\vert_A$ is an $O$-position.
-Suppose that $s=ty$ is a successor play.
-Note that $y$ cannot be a $*$-move, since these are all $O$-moves occurring in $A^{\cn}$.
-If $y$ takes place in $A^{\cn}$ then we have $t\vert_{A^{\cn}}\vert_A=t\vert_A$ and therefore player $P$ can play $y$ in $A$ and still be playing according to $\cn$.
-Similarly, if $y$ takes place in $A$, then player $P$ can play $y$ in $A^{\cn}$ and be in accordance with $\cn_A$.
-
-  Suppose instead that $s$ is a limiting play.
-It is clear from the definition that $s\vert_{A^{\cn}}\vert_A$ and $s\vert_A$ are both cofinal in $s$, so they are both limiting plays.
-Therefore, $s\vert_A$ is a limiting $O$-play in $A$ and $s\vert_{A^{\cn}}\vert_A$ must be the corresponding $P$-play in $A^{\cn}$.
-Therefore, player $P$ may play $*_t$ (where $t=s\vert_A$) in $A^{\cn}$ and still be in accordance with $A^{\cn}$.
-So $\cn_A$ is total.
-
-  Let $q\in P_A$.
-We claim that there is some $s\in\cn_A$ such that $s\vert_A=q$.
-Indeed, since Player $P$ makes all $*$-moves in $A^{\cn}\implies A$, player $O$ has a strategy for $A^{\cn}\implies A$ in which he plays the moves of the sequence $q$ in order.
-Since the strategy $\cn_A$ is total, player $P$ always has a reply to Player $O$'s moves and the resulting sequence $s$ satisfies $s\vert_A=q$.
-
-  Therefore, the relational presentation of $\cn_A$ has the following property: for all sequences $q\in P_A$, there exists some $r\in P_{A^{\cn}}$ such that $(r,q)\in\grel{\cn_A}$.
-Moreover, it is not difficult to see that this $r$ is unique, since play passes from $A$ to $A^{\cn}$ without fail at each turn, so a $P$-position in $\cn_A$ is uniquely determined by its sequence of $O$-moves, which must agree with its $A$-component.
-
-  In other words, the relational presentation $\grel{\cn_A}$ is the graph of an injective function $h\colon P_A\to P_{A^{\cn}}$.
-
-  Let $B$ be a completely negative $\alpha$-game and let $\sigma$ be a strategy for $B\implies A$.  We define the strategy $\sigma^{\cn}$ for $B\implies A^{\cn}$ as follows:
-  \[
-    \sigma^{\cn} = \{s\in P_{B\implies A^{\cn}}\suchthat s\vert_{B,M_A}\in\sigma\}
-    \]
-  where we write $s\vert_{B,M_A}$ for the sequence obtained by deleting all $*$-moves from $s$.
-
-  $\sigma^{\cn}$ is prefix closed, since $\sigma$ is, and satisfies the limit condition, since $\sigma$ does.
-Suppose that $s\in\sigma^{\cn}$ is a $P$-position and that $sx\in P_{B\implies A^{\cn}}$.
-If $x$ is a $*$-move, then we have $sx\vert_{B,M_A}=s\vert_{B,M_A}\in\sigma$, so $sx\in\sigma^{\cn}$.
-Otherwise, we have $sx\vert_{B,M_A}=s\vert_{B,M_A}x$.
-
-  If $s\vert_{B,M_A}$ is a $P$-position in $B\implies A$ then $s\vert_{B,M_A}x\in\sigma$ and therefore $sx\in\sigma^{\cn}$.
-So suppose instead that $s\vert_{B,M_A}$ is an $O$-position.
-If $s=ty$ is a successor position then $y$ is a $P$-move in $B\implies A^{\cn}$, so in particular $y$ is not a $*$-move and therefore $s\vert_{B,M_A}=t\vert_{B,M_A}y$ is a $P$-position.
-Therefore, $s$ must be a limiting play.
-
-  Since $s$ is a $P$-position, $s\vert_B$ must be a $P$-position, $s\vert_{A^{\cn}}\vert_A$ must be an $O$-position in $A$ and $s\vert_{A^{\cn}}$ must be a $P$-position in $A^{\cn}$.
-It follows that $u\coloneqq s\vert_{A^{\cn}}\vert_A$ is a limiting $O$-play.
-It follows that $x$ is a move in $A^{\cn}$, and therefore that $x=*_u$, which is a case we have already dealt with.
-
-  Next, suppose that $sx, sy\in\sigma^{\cn}$ are $P$-positions.
-In particular, $x,y$ are not $*$-moves and we have $s\vert_{B,M_A}x,s\vert_{B,M_A}y\in\sigma$.
-Therefore, $x=y$.
-So $\sigma^{\cn}$ is a strategy.
-
-  Lastly, suppose that $\sigma$ is a total strategy.
-Let $s\in\sigma^{\cn}$ be an $O$-position in $B\implies A^{\cn}$.
-Then $s\vert_B$ is a $P$-position in $B$ and $s\vert_{A^{\cn}}$ is an $O$-position in $A^{\cn}$.
-So $s\vert_{A^{\cn}}$ is a successor play in $A^{\cn}$, since $A^{\cn}$ is completely negative.
-If the last move of $s\vert_{A^{\cn}}$ is not a $*$-move then $s\vert_{A^{\cn}}\vert_A$ has the same last move as $s\vert_{A^{\cn}}$ and is therefore an $O$-position as well.
-Then $s\vert_{B,M_A}$ is an $O$-position and so there is some $x\in P_{B\implies A}$ such that $s\vert_{B,M_A}x\in\sigma$.
-Then $sx\in P_{B\implies A^{\cn}}$ and so $sx\in\sigma^{\cn}$.
-
-  Suppose instead that $s\vert_{A^{\cn}}=t*_u$, where $u=t\vert_A$.
-Then $u$ is an $O$-position in $A$, so $s\vert_{B,M_A}$ is an $O$-position in $B\implies A$ and therefore there is some $x\in P_{B\implies A}$ such that $s\vert_{B,M_A}x\in\sigma$.
-Then $sx\in\sigma^{\cn}$.
-So $\sigma^{\cn}$ is a total strategy.
-
-  We claim that $\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}=\grel\sigma$.
-Then we will have $\comp{\cn_A}{\sigma^{\cn}}=\sigma$ by Lemma \ref{TransHylandSchalkFaithful} and Corollary \ref{TransHylandSchalkIsFunctor}.
-Suppose $(s,t)\in\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}$.
-Then there is some $u\in P_{A^{\cn}}$ such that $(s,u)\in\grel{\sigma^{\cn}}$ and $(u,t)\in\grel{\cn_A}$.
-Therefore, $(s,u\vert_A)\in\grel\sigma$ and $t=u\vert_A$.
-It follows that $(s,t)\in\grel{\sigma}$, so $\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}\subset\grel\sigma$.
-
-  To show the reverse inclusion, we shall use the following lemma, which we shall prove later.
-
-  \begin{lemma}
-    \label{CnLiftingLemma}
-    Let $B$ be a completely negative $\alpha$-game, let $A$ be an arbitrary $\alpha$-game and let $\sigma$ be a strategy for $B\implies A$.
-Let $s\in\sigma$ be a $P$-position.
-Then there is a unique $P$-position $t\in B\implies A^{\cn}$ such that $t\vert_{B,M_A}=s$.
-  \end{lemma}
-
-  We use Lemma \ref{CnLiftingLemma} to show the reverse inclusion as follows: let $s\in\sigma$ be a $P$-position -- so $(s\vert_B,s\vert_A)$ is an arbitrary element of $\grel\sigma$.
-By Lemma \ref{CnLiftingLemma} there exists $t\in B\implies A^{\cn}$ such that $t\vert_{B,M_A}=s$.
-In particular, $t\vert_{A^{\cn}}\vert_A=s\vert_A$ and $t\vert_B=s\vert_B$.
-So we have $(s\vert_B,t\vert_{A^{\cn}})\in\grel{\sigma^{\cn}}$ and $(t\vert_{A^{\cn}},s\vert_A)\in\grel{\cn_A}$.
-It follows that $(s\vert_B,s\vert_A)\in\grel{\sigma}$.
-So $\grel\sigma\subset\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}$.
-
-  Lastly, we need to show that the strategy $\sigma^{\cn}$ is unique.  Suppose that there were some other strategy $\tau$ for $B\implies A^{\cn}$ making the diagram commute:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\tau"] \arrow[dr, "\sigma"']
-        & A^{\cn} \arrow[d, "\cn_A"] \\
-      %
-        & A
-    \end{tikzcd}
-    \]
-  We shall show that $\grel\tau=\grel{\sigma^{\cn}}$ -- so $\tau=\sigma^{\cn}$.
-First suppose that $s\in\sigma^{\cn}$ is a $P$-position.
-Since $\sigma = \comp{\cn_A}{\tau}$, there is some sequence $\s\in\tau\|\cn_A$ such that $\s\vert_{B,A}=s\vert_{B,M_A}$.
-We have $\s\vert_{A^{\cn}}\vert_A=\s\vert_A$ and therefore $s\vert_{B,M_A}=\s\vert_{B,A^{\cn}}\vert_{B,M_A}$.
-Therefore, $s=\s\vert_{B,A^{\cn}}\in\tau$, by uniqueness in Lemma \ref{CnLiftingLemma}.
-So $\grel{\sigma^{\cn}}\subset\grel{\tau}$.
-
-  Conversely, suppose that $s\in\tau$ is a $P$-position.
-Then our argument above tells us that we have $(s\vert_{A^{\cn}},s\vert_{A^{\cn}}\vert_A)\in\grel{\cn_A}$.
-So $(s\vert_B,s\vert_{A^{\cn}}\vert_A)\in\grel\sigma$.
-Therefore there is some $P$-position $u\in\sigma$ such that $u\vert_B=s\vert_B$ and $u\vert_A=s\vert_{A^{\cn}}\vert_A$.
-By Lemma \ref{CnLiftingLemma}, there is a sequence $t\in\sigma^{\cn}$ with $t\vert_{B,M_A}=s$.
-Then we have
-  \[
-    (s\vert_B,s\vert_{A^{\cn}})=(t\vert_B,t\vert_{A^{\cn}})\in\grel{\sigma^{\cn}}
-    \]
-  and therefore $\grel\tau\subset\grel{\sigma^{\cn}}$.  
-\end{proof}
-
-It remains to prove Lemma \ref{CnLiftingLemma}.
-
-\begin{proof}[Proof of Lemma \ref{CnLiftingLemma}]
-  This proof is similar to the proof of \ref{TransLiftingLemma}.
-We inductively construct a sequence $t^0\prefix t^1\prefix\dots\prefix t^\gamma\prefix\dots\prefix t^\beta$, where $t^\gamma$ has length $\gamma$ and $t^\beta$ is our desired sequence $t$.
-We shall prove inductively that $t^\gamma$ is the unique element $u\in\sigma^{\cn}$ of length $\gamma$ such that $u\vert_{B,M_A}=t$.
-
-  If $\gamma$ is a limit ordinal, then set $t^\gamma$ to be the limit of all the sequences $t^\delta$ for $\delta<\gamma$.
-We have $r\vert_{B,M_A}\prefix s$ for all proper prefixes $r\pprefix t^{\gamma}$ and therefore $t^\gamma\vert_{B,M_A}\prefix s$.
-For uniqueness, suppose that $u^\gamma$ has length $\gamma$ and $u^\gamma\vert_{B,M_A}\prefix s$.
-If $\delta<\gamma$ and we write $u^\delta$ for the prefix of $u^\gamma$ of length $\delta$ then we have $u^\delta=t^\delta$ by uniqueness and it follows that $u^\gamma=t^\gamma$.
-
-  Suppose instead that $\gamma=\delta+1$ is a successor ordinal.  We have a sequence $t^\delta$ of length $\delta$.
-
-  Suppose first that $t^\delta$ is an $O$-position.
-Then, as usual, $t^\delta\vert_{B,M_A}$ is an $O$-position.
-We have $t^\delta\vert_{B,M_A}\prefix s$; since $s$ is a $P$-position, this must be a proper prefix, so there is some move $x$ such that $t^\delta\vert_{B,M_A}x\prefix s$.
-By the argument above (showing that $\sigma^{\cn}$ is total if $\sigma$ is total), we must have $t^\delta x\in\sigma$.
-We set $t^{\delta+1}=t^\delta x$.
-Then $t^{\delta+1}\vert_{B,M_A}\prefix s$.
-
-  For uniqueness, suppose that $u^{\delta+1}$ is some other sequence of length $\delta+1$ with $u^{\delta+1}\vert_{B,M_A}\prefix s$.
-Writing $u^{\delta+1}=u^\delta y$, we have $u^{\delta}=t^\delta$ by uniqueness for sequences of length $\delta$.
-Then $t^\delta x,t^\delta y\in\sigma$ and so $x=y$.
-So $u^{\delta+1}=t^{\delta+1}$.
-
-  Now suppose that $t^\delta$ is a $P$-position.
-We have $t^\delta\vert_{B,M_A}\prefix s$.
-If $t^\delta\vert_{B,M_A}=s$ then we terminate, setting $\beta=\delta$.
-Otherwise, there is some move $x$ such that $t^\delta\vert_{B,M_A}x\prefix s$.
-
-  Suppose that $t^\delta\vert_{B,M_A}$ is a $P$-position.
-Then $x$ is an $O$-move, so $t^\delta x$ is alternating.
-\textbf{Since $B$ is completely negative}, Proposition \ref{NiceAcnGames} tells us that $t^\delta x\in P_{B\implies A^{\cn}}$.
-Therefore, $t^\delta x\in\sigma^{\cn}$, since $\sigma^{\cn}$ is a strategy.
-We set $t^{\delta+1}=t^\delta x$.
-Then we certainly have $t^{\delta+1}\vert_{B,M_A}\prefix s$.
-For uniqueness, suppose that $u^{\delta+1}$ has length $\delta+1$ and that $u^{\delta+1}\vert_{B,M_A}\prefix s$.
-Then $u^{\delta+1}=t^\delta y$ for some $y$ by uniqueness for sequences of length $\delta$.
-Since $t^\delta\vert_{B,M_A}$ is a $P$-position, it is in particular not a limiting $O$-play, so $y$ cannot be a $*$-move.
-Therefore, we have $u^{\delta}\vert_{B,M_A}y\prefix s$ and so $x=y$.
-
-  Suppose instead that $t^\delta\vert_{B,M_A}$ is an $O$-position.
-Then $v\coloneqq t^\delta\vert_{A^{\cn}}\vert_A$ must be a limiting $O$-play.
-We set $t^{\delta+1}=t^\delta *_v$.
-Since $*_v$ is the only move possible in position $t^\delta$, this must certainly be unique, and we have $t^\delta *_v\vert_{B,M_A}=t^\delta\vert_{B,M_A}\prefix s$.
-
-  This completes the proof by induction.
-\end{proof}
-
-\subsubsection{A digression}
-\label{DigressionSex}
-
-Earlier on, we defined a category $\G(\alpha)/A$ for $A$ an arbitrary $\alpha$-game.  At this point, it is tempting to define a category as follows:
-
-\begin{definition}
-  The objects of the category $\tilde{\G}(\alpha)$ are (not necessarily completely negative) $\alpha$-games.
-If $A,B$ are $\alpha$-games, a morphism in $\tilde{\G}(\alpha)$ from $A$ to $B$ is a functor
-  \[
-    \F\from\G(\alpha)/A\to\G(\alpha)/B
-    \]
-  that commutes with the natural projection functors $p_A\from\G(\alpha)/A\to\G(\alpha)$ and $p_B\from\G(\alpha)/B\to\G(\alpha)$.  
-\end{definition}
-
-This definition is useful because we have a natural embedding (the $2$-Yoneda embedding) of $\G(\alpha)$ into the category $\tilde{\G}(\alpha)$ that sends a completely negative game $N$ to the category $\G/N$ and sends a morphism $\sigma\from M\implies N$ to the `post-composition with $\sigma$' functor between the slice categories $\G(\alpha)//M$ and $\G(\alpha)/N$.
-
-It is well known that this is a fully faithful embedding.
-I claim that it is also essentially surjective, so it is in fact an equivalence of categories.
-Indeed, this follows from what we have just shown:
-
-\begin{proposition}
-  Let $A$ be an arbitrary $\alpha$ game.  Then the categories $\G(\alpha)/A$ and $\G(\alpha)/A^{\cn}$ are isomorphic as categories, via an isomorphism that commutes with the projection functors.
-
-  \begin{proof}
-    We have a natural functor from $\G(\alpha)/A^{\cn}$ to $\G(\alpha)/A$ given by post-composition with $\cn_A$, where functoriality follows from associativity of composition.
-This functor certainly commutes with the projection functors.
-Then Proposition \ref{CnUniversalProperty} tells us that it is fully faithful and a bijection on objects, so it is a categorical isomorphism.
-  \end{proof}
-\end{proposition}
-
-Therefore, the categories $\G(\alpha)$ and $\tilde{\G}(\alpha)$ are equivalent.
-This suggests one strategy for defining a symmetric monoidal closed structure on $\G(\alpha)$: since the objects of $\tilde{\G}(\alpha)$ are not required to be completely negative, we may freely define a closed monoidal structure on $\tilde{\G}(\alpha)$ by setting the linear implication between games $A$ and $B$ to be the game $A\implies B$ and the tensor product to be the game $A\tensor B$.
-This symmetric monoidal closed structure will give rise to a symmetric monoidal closed structure on $\G(\alpha)$ via the equivalence of categories.
-
-However, there is still quite a lot of work to show that this does indeed give a symmetric monoidal closed structure on $\tilde{\G}(\alpha)$, and it will be easier to construct the closed structure on $\G(\alpha)$ directly.
-
-\subsubsection{The completely negative linear implication $A\impliescn B$}
-\label{ImpliesCnSex}
-
-Let $A,B$ be completely negative $\alpha$-games.
-We have a completely negative $\alpha$-game $A\impliescn B\coloneqq (A\implies B)^{\cn}$.
-We shall construct a monoidal closed structure on $\G(\alpha)$ where the linear implication between $A$ and $B$ is $A\impliescn B$.
-
-We shall start off with the relevant result about the (usual) implication $A\implies B$:
-
-\begin{proposition}
-  \label{impliesTreeIsom}
-  Let $A,B,C$ be completely negative $\alpha$ games.  Then the games $(A\tensor B)\implies C$ and $A\implies(B\implies C)$ are tree isomorphic.
-\end{proposition}
-
-\begin{note}
-  Since $(A\tensor B)\implies C$ is not a completely negative game in general, we cannot say that these games are isomorphic as objects of $\G(\alpha)$, but it will help us to know that they are tree-isomorphic as games.
-\end{note}
-
-\begin{proof}[Proof of Proposition \ref{impliesTreeIsom}]
-  The sets of plays $P_{(A\tensor B)\implies C}$ and $P_{A\implies(B\implies C)}$ are both appropriate subsets of $P_A\|P_B\|P_C$.
-We just need to check that $\lambda_{(A\tensor B)\implies C}=\lambda_{A\implies(B\implies C)}$ and that $\zeta_{(A\tensor B)\implies C}=\zeta_{A\implies(B\implies C)}$.
-
-  We have
-  \begin{align*}
-    \lambda_{(A\tensor B)\implies C} &= \neg\circ\lambda_{A\tensor B}\cprd\lambda_C\\
-    &= \neg\circ\lambda_A\cprd\neg\circ\lambda_B\cprd\lambda_C\\
-    &= \neg\circ\lambda_A\cprd\lambda_{B\implies C}\\
-    &= \lambda_{A\implies(B\implies C)}
-  \end{align*}
-  and
-  \begin{align*}
-    \zeta_{(A\tensor B)\implies C}(s) & = ((\zeta_A(s\vert_A)\wedge\zeta_B(s\vert_B))\Rightarrow\zeta_C(s\vert_C))\\
-    &=(\zeta_A(s\vert_A)\Rightarrow(\zeta_B(s\vert_B)\Rightarrow\zeta_C(s\vert_C))) \\
-    &=\zeta_{A\implies(B\implies C)}(s)
-  \end{align*}
-  where we can prove the second equality as follows: if $p,q,r\in\OP$, then $((p\wedge q)\Rightarrow r) = O$ if and only if $p=q=P$ and $r=O$.
-Meanwhile, $(p\Rightarrow (q\Rightarrow r))=O$ if and only if $p=q=P$ and $r=O$.
-So $((p\wedge q)\Rightarrow r) = (p\Rightarrow(q\Rightarrow r))$.
-\end{proof}
-
-To construct the monoidal closed structure, it suffices to give a morphism
-\[
-  \ev_{A,B}\from (A\impliescn B)\tensor A\to B
-  \]
-for all pairs $(A,B)$ of completely negative $\alpha$-games, such that for all completely negative $\alpha$-games $X$ and all morphisms $\sigma\from X\tensor A\to B$ there is a unique morphism $\upsilon\from X\to A\impliescn B$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    X\tensor A_3 \arrow[r, "\sigma"] \arrow[d, "\upsilon\tensor\id_A"']
-      & B_2 \\
-    (A_1\impliescn B_1)\tensor A_2 \arrow[ur, "\ev_{A,B}"']
-      &
-  \end{tikzcd}
-  \]
-(Here we have numbered the copies of $A$ and $B$ so we can refer to them individually).
-
-The strategy $\ev_{A,B}$ for $((A\impliescn B)\tensor A)\implies B$ is constructed as follows: we have our strategy $\cn_{A\implies B}$ for $(A\impliescn B)\implies(A\implies B)$.
-By Proposition \ref{impliesTreeIsom}, this game is tree isomorphic to the game $((A\impliescn B)\tensor A)\implies B$, so we get the strategy $\ev_{A,B}$ by applying this tree isomorphism to the strategy $\cn_{A\implies B}$.
-
-We need to show that the strategy $\ev_{A,B}$ satisfies the property given above.
-Let $X$ be a completely negative $\alpha$-game and let $\sigma$ be a strategy for $(X\tensor A)\implies B$.
-Then $\sigma$ gives rise, via the tree isomorphism above, to a strategy $\tilde{\sigma}$ for $X\implies(A\implies B)$.
-Since the tree isomorphism does nothing more than identify $P_{(X\tensor A)\implies B}$ with $P_{X\implies(A\implies B)}$ as subsets of $(M_X\cprd M_B\cprd M_C)^{*<\alpha}$, we may identify $\sigma$ and $\tilde{\sigma}$ as subsets of $(M_X\cprd M_A\cprd M_B)$.
-
-Similarly, we may identify $\ev_{A,B}$ with $\cn_{A\implies B}$ as subsets of 
-\[
-  \left(M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}
-  \]
-where we have again labelled the different copies of $A$ and $B$ to avoid confusion.
-
-The strategy $\tilde{\sigma}$ gives rise to a strategy ${\tilde{\sigma}}^{\cn}$ for $X\implies(A\impliescn B)$.  We claim that this ${\tilde{\sigma}}^{\cn}$ satisfies the property above.
-
-First, we show that $\comp{\ev_{A,B}}{({\tilde{\sigma}}^{\cn}\tensor\id_A)}=\sigma$.  By the definition of ${\tilde{\sigma}}^{\cn}$, we know that it makes the following diagram commute:
-\[
-  \begin{tikzcd}
-    X \arrow[r, "{\tilde{\sigma}}^{\cn}"] \arrow[dr, "\tilde\sigma"']
-      & A_1\impliescn B_1 \arrow[d, "\cn_{A\implies B}"] \\
-    %
-      & A_2\implies B_2
-  \end{tikzcd}
-  \]
-where we have labelled the copies of $A$ and $B$ so we can tell them apart.  Therefore, we have
-\[
-  \tilde\sigma = \{\s\vert_{X,A_2,B_2}\suchthat \s\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}\}
-  \]
-where
-\[
-  {\tilde\sigma}^{\cn}\|\cn_{A\implies B} = \left\{\s\in \left(M_X\cprd M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}\;\middle|\;\mbox{\pbox{\textwidth}{
-    $\s\vert_{X,A_1,B_1}\in{\tilde\sigma}^{\cn}$\\
-    $\s\vert_{A_1,B_1,A_2,B_2}\in\cn_{A\implies B}$
-  }}\right\}
-  \]
-Now we have
-\[
-  \comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}=
-  \left\{\t\vert_{X,A_2,B_2}\suchthat\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}\right\}
-  \]
-where
-\[
-  \left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}
-  =\left\{\t\in\left(M_X\cprd M_{A_3}\cprd M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}\;\middle|\;
-  \mbox{\pbox{\textwidth}{
-    $\t\vert_{X,A_1,B_1}\in{\tilde\sigma}^{\cn}$\\
-    $\t\vert_{A_3,A_2}\in\id_A$\\
-    $\t\vert_{A_2,B_2}\in\ev_{A,B}$
-  }}\right\}
-  \]
-Remembering that we may identify $\ev_{A,B}$ with $\cn_{A\implies B}$ as sets of plays, we see that
-\[
-  \comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}\subset\tilde\sigma=\sigma
-  \]
-since if $\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}$ then we have $\t\vert_{X,A_1,B_1,A_2,B_2}\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}$ and so $\t\vert_{X,A_2,B_2}\in\tilde\sigma$.
-
-Conversely, let $s\in\tilde\sigma$ and write $s=\s\vert_{X,A_2,B_2}$, where $\s\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}$.
-We may construct a sequence $\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}$ with $\t\vert_{X,A_1,B_1,A_2,B_2}=\s$ by inserting before each $P$-move in $A_2$ the corresponding move in $A_3$ and inserting \emph{after} each $O$-move in $A_2$ the corresponding move in $A_3$.
-Therefore:
-\[
-  \sigma\subset\comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}
-  \]
-For uniqueness, suppose that we have a strategy $\upsilon$ for $X\implies(A\impliescn B)$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    X\tensor A_3 \arrow[r, "\sigma"] \arrow[d, "\upsilon\tensor\id_A"']
-      & B_2 \\
-    (A_1\impliescn B_1)\tensor A_2 \arrow[ur, "\ev_{A,B}"']
-      &
-  \end{tikzcd}
-  \]
-Exactly the same argument then tells us that
-\[
-  \comp{\cn_{A\implies B}}{\upsilon}=\comp{\ev_{A,B}}{\upsilon\tensor\id_A}=\sigma=\tilde\sigma
-  \]
-(as sets of plays) and so $\upsilon={\tilde\sigma}^{\cn}$ by the uniqueness part of Proposition \ref{CnUniversalProperty}.
-
-Therefore $\G(\alpha)$ has the structure of a symmetric monoidal category with tensor product given by $\tensor$ and linear implication given by $\impliescn$.
-
-\subsubsection{Win-games and winning strategies}
-
-We shall not develop the theory of transfinite win-games in this report, leaving this work for future research.
-The basic idea is as follows.
-Let $\alpha$ be an ordinal of the form $\omega^\beta$.
-We form a category $\G(\alpha+1)$ of games where the objects are acn $\alpha+1$-games.
-
-Given an acn $\alpha+1$-game $A$, we have an associated $\alpha$-game $A^\circ$ given by forgetting about the plays of length $\alpha$.
-We call a total strategy $\sigma$ for $A^\circ$ \emph{winning} if every play of length $\alpha$ that is the limit of plays from $\sigma$ is a $P$-play in $A$.
-
-We can then show that winning strategies compose to give winning strategies, just as in the $\omega+1$-case.
-The morphisms between objects $A$ and $B$ in our category will be winning strategies for $A^\circ\implies B^\circ$.
-We can then show that this category inherits a closed monoidal structure from $\G(\alpha)$.
-
-This construction agrees with the previous one in the sense that $\G(\omega+1)$ and our original category $\mathcal W$ of win-games are isomorphic as categories.
-
-\section{Exponentials}
-
-We want to model the exponential connective $\oc$ from linear logic in our game semantics.  We adapt the approach taken in \cite{laird02} and \cite{martinsthesis} to our transfinite games.
-
-\begin{definition}
-  Let $\G(\alpha)$ be a category of transfinite games and let $A$ be an object of $\G(\alpha)$.  Then the \emph{exponential} $\oc A$ is given as follows:
-  \begin{itemize}
-    \item $M_{\oc A} = A\times\omega$
-    \item $\lambda_{\oc A} = \lambda_A\circ\pr_1$
-  \end{itemize}
-
-  Given an ordinal-indexed sequence $s$ taking values in $M_{\oc A}$ and some $n\in\omega$, we write $s\vert_n$ for the subsequence of $s$ consisting of terms of the form $(a,n)$.  Then define
-  \[
-    \oc P_A = \{s\in M_{\oc A}^{*<\alpha}\suchthat s\vert_n\in P_A\textrm{ for all }n\in \omega\}
-    \]
-  We define $\zeta_{\oc A}\from \oc P_A\to \OP$ by
-  \[
-    \zeta_{\oc A}(s) = \bigwedge_{n\in \omega} \zeta_A(s\vert_n)
-    \]
-  (Here, if $(b_n)\in\OP^\omega$ then we have $\bigwedge_{n\in\omega} b_n = P$ if $b_n=P$ for all $n$ and $\bigwedge_{n\in\omega}=O$ otherwise.)
-
-  We define $P_{\oc A}$ to be the set of all sequences $s\in\oc P_A$ that are well formed with respect to $\zeta_{\oc A},\lambda_{\oc A}$ and are alternating with respect to $\zeta_{\oc A}$ and that satisfy the following property:
-
-  \begin{itemize}
-    \item If the term $(a,n)$ occurs in $s$, and if $m<n$, then there is some term $(b,m)$ that occurs earlier in the sequence $s$ than $(a,n)$.  
-  \end{itemize}
-
-  Then $\oc A=(M_{\oc A},\lambda_{\oc A},\zeta_{\oc A},P_{\oc A})$.  
-\end{definition}
-
-So $\oc A$ is like an infinite tensor product of copies of $A$ with the restriction that the first move must take place in the first copy and that moves may not take place in a subsequent copy of $A$ until moves have been made in all earlier copies.
-
-\begin{proposition}
-  $\oc A$ is a well formed game.
-  \begin{proof}
-    Exactly the same argument from Proposition \ref{TransTensorWellFormed}.
-  \end{proof}
-\end{proposition}
-
-Just like the tensor product, the exponential $\oc A$ has the property that only player $O$ may switch games:
-
-\begin{proposition}
-  \label{ExponentialWhoSwitchesGames}
-  Suppose that $s(a,m)(b,n)\in P_{\oc A}$, where $m\ne n$.  Then $\lambda_{\oc A}(b,n)=O$.  
-  \begin{proof}
-    $\begin{aligned}[t]
-      \lambda_{\oc A}(b,n) &= \zeta_{\oc A}(s(a,m)(b,n))\\
-      &= \bigwedge_{k\in\omega}\zeta_A(s(a,m)(b,n)\vert_k)
-    \end{aligned}$
-
-    Now by alternation we must have either $\zeta_A(s\vert_m(a,m))=O$ or $\zeta_A(s\vert_n(b,n))=O$.  So this last expression must be equal to $O$.
-  \end{proof}
-\end{proposition}
-
-We can also prove a version of Proposition \ref{NiceAcnGames} for the exponential connective using the same argument.
-
-To demonstrate why it is important to restrict the order in which the opponent $O$ may open games, we define a commutative comonoid structure on $\oc A$.
-The comultiplication $\mu\from \oc A\to \oc A\tensor \oc A$ is the copycat strategy that opens a new copy of $A$ on the left hand side whenever a new copy of $A$ is opened on the right hand side.
-(Here we see why the condition on the order in which games may be opened is important -- if we had no such restriction then there would be no canonical way to choose which copy of $A$ to open on the left hand side and the comultiplication would not be associative.)
-
-The counit $\eta\from \oc A\to I$ is the unique empty strategy on $\oc A\implies I$.
-
-For associativity of comultiplication, we want to check that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[dd, "\mu"']
-      & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \mu"] \\
-    %
-      & \oc A \tensor (\oc A \tensor \oc A) \arrow[d, "\assoc_{A,A,A}\inv"] \\
-    \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}"']
-      & (\oc A \tensor \oc A) \tensor \oc A
-  \end{tikzcd}
-  \]
-For this, note that each path round the diagram is a copycat strategy $\oc A \to (\oc A\tensor \oc A)\tensor \oc A$.
-Since we are forced to open copies of $\oc A$ in order, there is only one such copycat strategy, and so the two paths must be equal.
-
-Exactly the same argument tells us that comultiplication is commutative and that the counit is indeed a counit for this comultiplication.
-
-We have a natural forgetful functor from the category of comonoids over $\G(\alpha)$ to $\G(\alpha)$ itself.
-We first want to show that we have a functor in the opposite direction that sends a game $A$ to this comonoid over $\oc A$.
-
-Let $A,B$ be completely negative $\alpha$-games and let $\sigma$ be a strategy for $A\implies B$.  Then we have a natural strategy $\oc \sigma$ for $\oc A\implies\oc B$ given by
-\[
-  \oc\sigma = \{s\in P_{\oc A}\suchthat s\vert_n\in\sigma\textrm{ for all $n\in\omega$}\}
-  \]
-where we have written $s\vert_n$ for the subsequence of $s$ consisting of all terms that occur in the $n$-th copy of $A$ or the $n$-th copy of $B$.
-
-The proof that this is a strategy may be adapted from the discussion of the strategy $\sigma\tensor\tau$ above.
-Similarly, we may show that if $A,B,C$ are completely negative $\alpha$-games and we have strategies $A\xrightarrow{\sigma}B\xrightarrow{\tau}C$ then
-\[
-  \comp{\oc\tau}{\oc\sigma} = \oc(\comp\tau\sigma)
-  \]
-using the same argument we used to show that taking the tensor product of two strategies preserves composition.
-
-This gives us a functor $\cmap{\oc}{\G(\alpha)}{\G(\alpha)}$.
-We want to show that it gives rise to a functor from $\G(\alpha)$ into the category of comonoids over $\G(\alpha)$ sending a game $A$ to the comonoid $\oc A\to \oc A\tensor \oc A$.
-For this, we need to show that if $A,B$ are completely negative $\alpha$-games and $\sigma$ is a strategy for $A\implies B$ then the following diagram commutes:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[d, "\oc \sigma"']
-      & \oc A \tensor \oc A \arrow[d, "\oc \sigma \tensor \oc \sigma"] \\
-    \oc B \arrow[r, "\mu"']
-      & \oc B \tensor \oc B
-  \end{tikzcd}
-  \]
-Each branch of this diagram is a strategy for $\oc A\implies(\oc B\tensor\oc B)$ in which player $P$ plays according to $\sigma$, opening a new copy of $A$ on the left each time player $O$ opens a copy of $B$ on the right.
-Since the order in which player $P$ may open copies of $A$ is pre-determined, there is a unique such strategy, and so this diagram must commute.
-
-We shall eventually show that in fact $\oc A\to\oc A\tensor\oc A$ is the \emph{cofree commutative comonoid} on $A$.
-To show that, we will need \cite{martinsthesis} to give a map $\der\from\oc A\to A$, and we will need to show that for each commutative comonoid $B\to B\tensor B$ and each morphism $\sigma\from B\to A$ there exists a unique morphism $\sigma^\dagger\from B\to \oc A$ such that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    A
-      & \oc A \arrow[l, "\der"'] \arrow[r, "\mu"]
-        & \oc A \tensor \oc A \\
-    %
-      & B \arrow[r] \arrow[u, dotted, "\sigma^\dagger"'] \arrow[ul, "\sigma"]
-        & B\tensor B \arrow[u, dotted, "\sigma^\dagger \tensor \sigma^\dagger"']
-  \end{tikzcd}
-  \]
-We are not yet in a position to define the morphism $\sigma^\dagger$, but it is easy to see what $\der$ is: it is the copycat strategy on $\oc A\implies\oc A$ that copies the moves from $A$ on the right into the first copy of $A$ on the left.
-
-\subsection{Products in $\G(\alpha)$}
-
-Let $(A_i\suchthat i\in I)$ be a collection of objects of $\G(\alpha)$.  We define the product
-\[
-  \prod_i A_i
-  \]
-to be the game given by
-\begin{itemize}
-  \item $M_{\prod_i A_i}=\bigcprd_i M_{A_i}$
-  \item $\lambda_{\prod_i A_i}=\bigcprd_i \lambda_{A_i}$
-  \item $P_{\prod_i A_i} = \bigcprd_i P_{A_i}$
-  \item $\zeta_{\prod_i A_i} = \bigcprd_i \zeta_{A_i}$
-\end{itemize}
-This is the game where Player $O$ may decide which of the $A_i$ to play his first move in; play then continues in that game and the other games are never used.
-
-We claim that $\prod_i A_i$ is the categorical product of the $A_i$ in $\G(\alpha)$.
-First note that we have natural projection strategies $\pr_j$ for $\prod_i A_i\to A_j$ for each $j\in I$, in which player $P$ plays copycat in game $A_j$ on the left.
-Now if $B$ is an object of $\G(\alpha)$ and $\sigma_i$ are strategies for $B\implies A_i$ for each $i\in I$, then we have a strategy $\sigma$ for $B\implies\prod_i A_i$ in which player $P$ uses strategy $j$ when player $O$'s initial move takes place in $A_j$:
-\[
-  \sigma = \bigcprd_i \sigma_i
-  \]
-
-We can see that $\comp{\pr_j}{\sigma}=\sigma_j$ for each $j$: indeed, $\grel{\pr_j}$ is the graph of the inclusion $P_{A_j}\hookrightarrow P_{\prod_i A_i}$, while $\grel\sigma$ is the union of the relations $\grel{\sigma_i}$, so this equation holds in the relational presentation:
-\[
-  \comp{\grel{\pr_j}}{\grel{\sigma}}=\grel{\sigma_j}
-  \]
-Moreover, it is easy to see that $\grel\sigma$ is the unique relation between $P_B$ and $P_{\prod_i A_i}$ such that this equation holds for all $j$, and therefore $sigma$ is the unique strategy for $B\implies\prod_i A_i$ such that $\comp{\pr_j}{\sigma}=\sigma_j$ for each $j\in I$.
-Therefore, $\G(\alpha)$ has all small products.
-
-Given games $A,B$, we shall write $A\times B$ for the product of $A$ and $B$.
-
-\subsection{The exponential as a final coalgebra}
-
-Our definition of the exponential connective $\oc$ was different from the definitions of the other connectives in that it involved an explicit restriction on the order in which new games could be opened.
-We saw that this restriction was necessary in order to guarantee associativity of the comultiplication in our comonoid, but it means that it is hard to study the exponential $\oc A$ using the connectives $\tensor$ and $\implies$.
-
-Let $A,B$ be objects of some category $\G(\alpha)$ of transfinite games.  Following \cite{laird02}, we define the \emph{sequoid} $A\sequoid B$ by:
-
-\begin{itemize}
-  \item $M_{A\sequoid B} = M_{A\tensor B}$
-  \item $\lambda_{A\sequoid B}=\lambda_{A\tensor B}$
-  \item $P_{A\sequoid B} = \{s\in P_{A\tensor B}\suchthat\textrm{$s=\emptyplay$ or the first move of $s$ takes place in $A$}\}$
-  \item $\zeta_{A\sequoid B} = \zeta_{A\tensor B}\vert_{P_{A\sequoid B}}$
-\end{itemize}
-
-It is clear that $A\sequoid B$ is a well-formed game - namely, it is the weakening of the tensor product $A\tensor A$ such that player $O$ is forced to start play in the game $A$.
-We have a natural copycat strategy $\wk\from A\tensor B\to A\sequoid B$ and the morphism
-\[
-  \dec_{A,B}\from A\tensor B\to (A\sequoid B)\times(B\sequoid A)
-  \]
-induced by the morphisms
-\[
-  A\tensor B\xrightarrow{\wk}A\sequoid B\quad A\tensor B\xrightarrow{\braid}B\tensor A\xrightarrow{\wk}B\sequoid A
-  \]
-is an isomorphism.
-
-Other natural copycat isomorphisms may be verified by inspection:
-\begin{gather*}
-  \passoc_{A,B,C} \from (A\sequoid B) \sequoid C \toisom A\sequoid (B\tensor C) \\
-  \pcomm_{A,B,C} = \comp{\passoc_{A,B,C}\inv}{\comp{(\id_A\tensor\braid)}{\passoc_{A,B,C}}} \from (A\sequoid B)\sequoid C \toisom (A\sequoid C)\sequoid B\\
-  \lun_A \from I\sequoid A \toisom I\\
-  \run_A \from A\sequoid I \toisom A \\
-  \dist_{A,B,C}=\langle \pi_1\sequoid\id_C,\pi_2\sequoid\id_C\rangle\from (A\times B)\sequoid C \toisom (A\sequoid C)\times(B\sequoid C)
-\end{gather*}
-
-One important point is that the sequoid does not give rise to a functor $\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ in the way that the tensor product does.
-To see why, let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $C\implies D$.
-We would like to construct a strategy $\sigma\sequoid\tau$ for
-\[
-  (A\sequoid C)\implies (B\sequoid D)
-  \]
-in which player $P$ plays according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $B$ and $D$, exactly as in the strategy $\sigma\tensor\tau$.
-The problem is that $\sigma\tensor\tau$ is not necessarily a valid strategy for $(A\sequoid C)\implies (B\sequoid D)$, even if $\sigma$ is a valid strategy for $A\implies B$ and $\tau$ is a valid strategy for $C\implies D$.
-
-Indeed, suppose that player $P$'s reply in $\sigma$ to a particular opening move in $B$ is also a move in $B$, and suppose further that player $P$'s reply in $\tau$ to a particular opening move in $D$ is a move in $C$ (for example, if $\tau$ is a copycat strategy).
-Now consider the following narrative for the game $(A\sequoid C)\implies (B\sequoid D)$:
-\begin{enumerate}
-  \item Player $O$ plays the opening move in $B$, as he must.
-  \item Player $P$ replies in $B$, according to $\sigma$.  
-  \item Player $O$ decides to switch and start the game $D$.
-  \item According to $\tau$, player $P$ should reply with a move in $C$.  But she cannot play in $C$, since no moves have been played in $A$ yet.
-\end{enumerate}
-
-In order to fix this situation, we place a restriction on the strategy $\sigma$.
-
-\begin{definition}
-  Let $A,B$ be objects of $\G(\alpha)$.
-A strategy $\sigma$ for $A\implies B$ is called \emph{strict} if player $P$'s reply to each opening $O$-move in $B$ is a move in $A$ - so if $bx\in\sigma$ then $x\in M_A$.
-
-  It is easy to see that the composition of strict strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ is a strict strategy for $A\implies C$ and that the identity strategy is strict.
-Therefore, we have a full-on-objects subcategory $\G_s(\alpha)$ of $\G(\alpha)$ of games and strict strategies.
-\end{definition}
-
-\begin{proposition}
-  Let $A,B,C,D$ be objects of $\G(\alpha)$, let $\sigma$ be a strict strategy for $A\implies B$ and let $\tau$ be a strict strategy for $C\implies D$.
-Then $\sigma\sequoid\tau=\sigma\tensor\tau\cap P_{(A\sequoid C)\implies (B\sequoid D)}$ is a strict strategy for $(A\sequoid C)\implies (B\sequoid D)$ and the following diagram commutes (so $\wk$ is a natural transformation between $\blank\tensor\blank$ and $\blank\sequoid\blank$):
-  \[
-    \begin{tikzcd}
-      A\tensor C \arrow[r, "\sigma\tensor\tau"] \arrow[d, "\wk"']
-        & B\tensor D \arrow[d, "\wk"] \\
-      A\sequoid C \arrow[r, "\sigma\sequoid\tau"']
-        & B\sequoid D
-    \end{tikzcd}
-    \]
-
-  \begin{proof}
-    We know that $\sigma\tensor\tau$ is a valid strategy for $(A\tensor C)\implies (B\tensor D)$, so we just need to check that no moves in $B$ take place before moves in $D$ and that no moves in $A$ take place before moves in $C$.
-Indeed, player $O$'s opening move must take place in $B$; then, since $\sigma$ is strict, player $P$'s reply will take place in $A$.
-So $\sigma\sequoid\tau$ is a valid strategy for $(A\sequoid C)\implies(B\sequoid D)$; moreover, it is itself a strict strategy.
-  \end{proof}
-\end{proposition}
-
-What this means is that $\blank\sequoid\blank$ gives us a functor, not from $\G(\alpha)\times\G(\alpha)$ to $\G(\alpha)$, but from $\G_s(\alpha)\times\G(\alpha)$ to $\G_s(\alpha)$.
-In fact, the isomorphism $\passoc\from (A\sequoid B)\sequoid C\cong A\sequoid(B\tensor C)$ tells us that $\blank\sequoid\blank$ is a \emph{right action} of the monoidal category $\G(\alpha)$ upon the category $\G_s(\alpha)$.
-
-The closed monoidal category $\G(\alpha)$, the subcategory $\G_s(\alpha)$, the morphisms $\passoc$ and $\run$, and the natural transformation $\wk$ in fact give rise to a structure known as a \emph{sequoidal category} (This definition was first introduced in \cite{laird02}, but with the direction of the sequoid operator reversed; see, for example, \cite{martinsthesis} for the definition where the orientation of the sequoid agrees with ours).
-
-Moreover, the isomorphism $\dec_{A,B,C}\from A\tensor B\cong (A\sequoid B)\times(B\sequoid A)$ means that our sequoidal category is \emph{decomposable} and the isomorphism $\dist_{A,B,C}\from (A\times B)\sequoid C\to (A\sequoid C)\times(B\sequoid C)$ tells us that it is \emph{distributive}.
-
-The last part of the definition of a sequoidal category that we will need is the coherence diagram:
-\[
-  \begin{tikzcd}
-    (A \tensor B) \tensor C \arrow[r, "\wk\tensor\id_C"] \arrow[d, "\assoc_{A,B,C}"']
-      & (A \sequoid B) \tensor C \arrow[r, "\wk"]
-        & (A \sequoid B) \sequoid C \\
-    A \tensor (B \tensor C) \arrow[r, "\wk"]
-      & A \sequoid (B \tensor C) \arrow[ur, "\passoc_{A,B,C}"']
-        &
-  \end{tikzcd}
-  \]
-Commutativity of this diagram in $\G(\alpha)$ may be verified by inspection.
-
-\cite{laird02} gives examples of what we can prove in general sequoidal categories, particularly in the cpo-enriched setting.
-They are used in \cite{martinsthesis} to study the logic modelled by games and history-sensitive strategies.
-The most useful property of the sequoid from the point of view of our study of the exponential is that it allows us to express our exponential as a final coalgebra.
-
-Let $\C$ be a category and let $\F\from \C\to\C$ be an endofunctor.  A \emph{coalgebra} for $\F$ is an object $A$ of $\C$ together with a morphism $\map{f}{A}{\F(A)}$.  Given two coalgebras
-\begin{gather*}
-  \map{f}{A}{\F(A)}\\
-  \map{g}{B}{\F(B)}
-\end{gather*}
-a \emph{coalgebra homomorphism} from $\map{f}{A}{\F(A)}$ to $\map{g}{B}{\F(A)}$ is a morphism $\cmap{h}{A}{B}$ that makes the following square commute:
-\[
-  \begin{tikzcd}
-    A \arrow[r, "f"] \arrow[d, "h"']
-      & \F(A) \arrow[d, "\F(h)"] \\
-    B \arrow[r, "g"']
-      & \F(B)
-  \end{tikzcd}
-  \]
-
-A \emph{final coalgebra} for $\F$ is a terminal object for the category of coalgebras and coalgebra homomorphisms.
-Namely, it is an object $Z$ of $\C$ together with a morphism $\map{\alpha}{Z}{\F(Z)}$ such that for each coalgebra $\map{f}{A}{\F(A)}$ there is a unique morphism
-\[
-  \fcoal{f}\from A \to Z
-  \]
-making the following diagram commute:
-\[
-  \begin{tikzcd}
-    A \arrow[r, "f"] \arrow[d, "\fcoal{f}"']
-      & \F(A) \arrow[d, "\F\left(\fcoal{f}\right)"] \\
-    Z \arrow[r, "\alpha"']
-      & \F(Z)
-  \end{tikzcd}
-  \]
-
-\begin{theorem}
-  Let $A$ be an object of a category $\G(\alpha)$ of games.  Then $\oc A$ may be given the structure of a final coalgebra for the functor
-  \[
-    A\sequoid\blank\from \G(\alpha)\to\G(\alpha)
-    \]
-  \begin{proof}
-    The coalgebra morphism $\alpha\from \oc A\to A\sequoid\oc A$ is given by
-    \[
-      \alpha \from \oc A \xrightarrow{\mu} \oc A \tensor \oc A \xrightarrow{\der\tensor\id_{\oc A}} A\tensor\oc A\xrightarrow{\wk} A\sequoid\oc A
-      \]
-    In other words, it is the copycat strategy where moves from the extra copy of $A$ on the right are copied into the first copy of $A$ on the left, moves from the first copy of $A$ in the exponential $\oc A$ on the right are copied into the second copy of $A$ on the left and so on.
-
-    Now let $B$ be a game and let $\sigma$ be a strategy for $B\implies A\sequoid B$.  We define a strategy $\fcoal{\sigma}$ for $B\implies \oc A$ as follows: we first define
-    \[
-      \|\sigma\| = \{\s\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}\suchthat\forall i\ge 0, \s\vert_{B_i,A_i,B_{i+1}}\in\sigma\}
-      \]
-    Then we set
-    \[
-      \fcoal\sigma = P_{B\implies\oc A} \cap \{\s\vert_{B_0,\oc A}\suchthat\s\in\|\sigma\|\}
-      \]
-    where we write $\s\vert_{B_0, \oc A}$ for $\s\vert_{B_0,A_0,A_1,\dots}$.
-
-    We shall omit the proof that $\fcoal\sigma$ is a strategy.  We claim that the final coalgebra diagram commutes:
-    \[
-      \begin{tikzcd}
-        B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
-          & A\sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
-        \oc A \arrow[r, "\alpha"']
-          & A\sequoid\oc A
-      \end{tikzcd}
-      \]
-    First, we have:
-    \[
-      \fcoal{\sigma} = P_{B\implies \oc A} \cap \left\{\s\vert_{B_0,A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_B\times\omega\sqcup M_A\times\omega)^{*<\alpha}$\\
-        $\forall i\ge0,\;\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-      \]
-    We claim that:
-    \begin{align*}
-      \id_A\sequoid\fcoal\sigma &= P_{(A\sequoid B)\implies(A\sequoid\oc A)}\;\cap\\
-      &\left\{\s\vert_{A_{-2},B_0,A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in (M_{A_{-2}}\cprd M_{A_{-1}} \cprd M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{A_{-2},A_{-1}}\in\id_A$\\
-        $\forall i\ge 0$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-    \end{align*}
-    Using the definition:
-    \[
-      \id\sequoid\fcoal{\sigma} = \{s\in P_{(A_{-2}\sequoid B_0)\implies(A_{-1}\sequoid\oc A)}\suchthat
-      s\vert_{A_{-2},A_{-1}}\in\id_A,\;s\vert_{B_0,\oc A}\in\fcoal\sigma\}
-      \]
-    it is clear that the RHS above is a subset of the LHS.
-To show the reverse inclusion, suppose we have some sequence $s\in\id\sequoid\fcoal\sigma$.
-Since $s\vert_{B_0,\oc A}\in\fcoal\sigma$, there is some sequence $\s\in\|\sigma\|$ with $\s\vert_{B_0,A_0,A_1,\dots}=s$.
-Then it is possible to interleave this sequence with the sequence $s\vert_{A_{-2},A_{-1}}$ exactly as we did towards the end of Section \ref{ImpliesCnSex}: we insert \emph{before} each $P$-move in $A_{-1}$ the corresponding move in $A_{-2}$ and insert \emph{after} each $O$-move in $A_{-1}$ the corresponding move in $A_{-2}$.
-This interleaved sequence -- call it $\t$ -- satisfies $\t\vert_{A_{-2},A_{-1}}\in\id_A$ and $\t\vert_{B_i,A_i,B_{i+1}}\in\sigma$ for all $i\ge0$, so it gives rise to an element of the RHS.
-Moreover, we have $t\vert_{A_{-2},B_0,A_{-1},A_0,A_1,\dots}=s$, and therefore $s$ is contained in the RHS.
-
-    We now have $\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma} =$
-    \[
-      P_{B\implies A\sequoid\oc A} \cap \left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_{B_{-1}}\cprd M_{A_{-2}}\cprd M_{A_{-1}}\cprd M_B\times\omega \cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{B_{-1},A_{-2},B_0}\in\sigma$\\
-        $\s\vert_{A_{-2},A_{-1}}\in\id_A$\\
-        $\forall i\ge 0$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-      \]
-    We claim that this is equal to the following strategy:
-    \[
-      S =
-      P_{B\implies A\sequoid\oc A}\cap\left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in (M_{B_{-1}}\cprd M_{A_{-1}} \cprd M_B\times\omega \cprd M_A\times\omega)^{*<\alpha}$\\
-        $\forall i\ge -1$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-      \]
-    $S$ is a strategy since it is nothing more than a relabelling of the indices of $\fcoal\sigma$.
-To show that these two strategies are the same, it suffices to show that they contain the same $P$-positions.
-
-    Suppose we have some $P$-position $s\in\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma}$ and write $s=\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}$.
-By the argument above, we may assume that all moves from $A_{-2}$ are adjacent to a move from $A_{-1}$; since $s$ is a $P$-position, it cannot end with an $O$-move in $A_{-1}$, and therefore $\s\vert_{A_{-2},A_{-1}}$ must have even length.
-Therefore
-    \[
-      \s\vert_{A_{-2}}=\s\vert_{A_{-1}}
-      \]
-    by the definition of $\id_A$.
-
-    It follows (after hiding $M_{A_{-2}}$) that $\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma} \subset S$.
-Conversely, given an element $s=\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\in S$, we may interleave in a play in $A_{-2}$ that is identical to the play in $\s\vert_{A_{-1}}$ as above, showing that $s\in\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma}$.
-
-    It remains only to observe that $S$ is precisely the strategy $\comp{\alpha}{\fcoal\sigma}$, and so the square above does indeed commute.
-
-    Now we show uniqueness.  Suppose that $\tau$ is some strategy for $B\implies\oc A$ such that the diagram commutes:
-    \[
-      \begin{tikzcd}
-        B \arrow[r, "\sigma"] \arrow[d, "\tau"']
-          & A\sequoid B \arrow[d, "\id_A\sequoid\tau"] \\
-        \oc A \arrow[r, "\alpha"']
-          & A\sequoid\oc A
-      \end{tikzcd}
-      \]
-    We claim that $\tau=\fcoal\sigma$.  The argument above tells us that
-    \[
-      \comp{(\id_A\sequoid\tau)}{\sigma} =
-      \left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_{B_{-1}}\cprd M_{A_{-1}}\cprd M_{B_0}\cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{B_{-1},A_{-1},B_0}\in\sigma$\\
-        $\s\vert_{B_0,A_0,A_1,\dots}\in\tau$
-      }}\right\}
-      \]
-    Meanwhile, we have
-    \[
-      \comp{\alpha}{\tau} = \{t^\dagger\suchthat t\in\tau\}
-      \]
-    where $t^\dagger\in(M_{B_{-1}}\cprd M_{A_{-1}}\cprd M_A\times\omega)^{*<\alpha}$ is formed by reducing the indices on the copies of $A$ and $B$ in $t\in(M_{B_0}\cprd M_A\times\omega)^{*<\alpha}$.
-
-    We have $\comp{(\id\sequoid\tau)}{\sigma}=\comp\alpha\tau$, so, after promoting all indices by $1$, we may write:
-    \begin{equation}\label{taufixedpoint}
-      \tau = 
-      \left\{\s\vert_{B_{0},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_{B_0}\cprd M_{B_1}\cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{B_0,A_0,B_1}\in\sigma$\\
-        ($\s\vert_{B_1,A_1,A_2 \dots})^\dagger\in\tau$
-      }}\right\}
-      \tag{$*$}
-    \end{equation}
-    Let $t\in\tau$.
-Then we have just shown that we may interleave $t$ with a sequence $r\in M_{B_1}$ such that the interleaved sequence $\t\in(M_{B_0}\cprd M_{B_1}\cprd M_{A}\times\omega)^{*<\alpha}$ satisfies
-    \begin{gather*}
-      \t\vert_{B_0,\oc A}=t\quad\t\vert_{B_1}=r\\
-      \t\vert_{B_0,A_0,B_1}\in\sigma\\
-      (\t\vert_{B_1,A_1,A_2,\dots})^\dagger\in\tau
-    \end{gather*}
-    Let $t_1=(\t\vert_{B_1,A_1,A_2,\dots})^\dagger$.
-Applying the result repeatedly allows us to build up a sequence $t=t_0,t_1,t_2,\dots$ where $t_i\in\tau$ for each $i$, together with a sequence $\t=\t_0,\t_1,\t_2,\dots\in (M_{B_0}\cprd M_{B_1}\cprd M_A\times\omega)^{*<\alpha}$ such that for each $i$:
-    \begin{gather*}
-      \t_i\vert_{B_0,\oc A}=t_i\\
-      \t_i\vert_{B_0,A_0,B_1}\in\sigma
-    \end{gather*}
-    By construction, the $A$-components of the $\t_i$ agree (indeed, the $A_i$-component of $\t_j$ is the same as the $A_{i+j}$-component of $\t_0$), and the $B_1$-component of $\t_i$ is the same as the $B_0$-component of $t_{i+1}$.
-Therefore, the $\t_i$ interleave to give a sequence
-    \[
-      \T\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}
-      \]
-    such that $\T\vert_{B_0,\oc A}=t$ and for all $i\ge 0$, $\T\vert_{B_i,A_i,B_{i+1}}\in\sigma$.  It follows that $t\in\fcoal\sigma$ and so $\tau\subset\fcoal\sigma$.
-
-    Now suppose that $s\in\fcoal\sigma$.
-We show by transfinite induction on the length of $s$ that $s\in\tau$.
-Since $\tau$ satisfies the limiting condition, the limiting case of the induction is easy.
-So suppose instead that $s=s'a$ is a successor play, and suppose that the last move $a$ takes place in the game $A_n$.
-By induction, we assume that $s'\in\tau$.
-We now apply the construction above to give us a sequence
-    \[
-      s'=t_0,t_1,\dots,t_{n+1}
-      \]
-    of plays in $\tau$ whose $A$-components agree so that the $A_i$-component of $t_j$ is the $A_{i+j}$-component of $s'$.
-It follows that the $A$-components of $t_{n+1}$ also agree with the components of $A_{n+1},A_{n+2},\dots$ of $sa$, since the move $a$ takes place in $A_n$.
-
-    We have $t_{n+1}\in\tau$.
-We now claim that $t_{n}a$ satisfies the conditions on the right in \eqref{taufixedpoint}, so $t_n a\in\tau$ as well.
-Indeed, we have $s'a\in\fcoal\sigma$, so there exists some $\s a\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}$ with $\s\vert_{B_0,\oc A}=s$ and $\s a\vert_{B_i,A_i,B_{i+1}}\in\sigma$ for all $i$.
-
-    Consider the sequence
-    \[
-      \s a\vert_{B_n,B_{n+1},A_n,A_{n+1},A_{n+2},\dots}
-      \]
-    We have $\s a\vert_{B_n,A_n,A_{n+1}}\in\sigma$ (since $\s a\in\fcoal\sigma$) and $\s a\vert_{B_{n+1},A_{n+1},A_{n+2},\dots}=s \vert_{B_{n+1},A_{n+1},A_{n+2},\dots}\in\tau$ by \eqref{taufixedpoint}.
-Therefore, $\s a\vert_{B_n,B_{n+1},A_n,A_{n+1},A_{n+2},\dots}$ satisfies the conditions for the right hand side of \eqref{taufixedpoint} (after subtracting $n$ from each of the indices) and therefore
-    \[
-      t_n a=\s a\vert_{B_n,A_n,A_{n+1},\dots}\in\tau
-      \]
-    Moreover, this sequence is contained in $\fcoal\sigma$ (by checking the definition).
-
-    By repeatedly applying this argument, we eventually show that 
-    \[
-      sa=\s a\vert_{B_0,A_0,A_1,\dots}\in\tau
-      \]
-    This completes the proof.
-  \end{proof}
-\end{theorem}
-
-\begin{note}
-  This is not the same as the proof found in \cite{martinsthesis}, which implicitly uses the fact that in the finitary games setting we may identify $\oc A$ with the limit of the diagram
-  \[
-    I \leftarrow A \leftarrow A\sequoid A \leftarrow A\sequoid(A\sequoid A) \leftarrow \cdots
-    \]
-  As we shall see in the next section, we do not have this identification in the transfinite setting.
-However, we will give an alternative proof that $\oc A$ is the final coalgebra for $A\sequoid\blank$ in the next section that will be more along the lines of the proof in \cite{martinsthesis}.
-\end{note}
-
-\pagebreak
-
-\subsection{The sequoidal exponential gives a cofree commutative comonoid}
-\label{SeqExpIsCofCommCom}
-
-As an application of this result, we shall prove that $\oc A\xrightarrow{\mu}\oc A\tensor \oc A$ is the cofree commutative comonoid on $A$.  We start with a small but useful lemma:
-
-\begin{lemma}
-  \[
-    \oc A \tensor \oc A \cong \oc(A\times A)
-    \]
-  \begin{proof}
-    We check that the game trees are isomorphic.
-The basic idea is that in each $P$-position the player $O$ may either play in one of the games that has already been opened, or he has a choice of two new games to open -- in $\oc A\tensor \oc A$, he may open either the first unopened copy of $A$ on the left or the first unopened copy of $A$ on the right, while in $\oc(A\times A)$ he may open either of the copies of $A$ in the first unopened copy of $A\times A$.
-  \end{proof}
-\end{lemma}
-
-This means that $\oc A\tensor\oc A$ is the final coalgebra for the functor 
-\[
-  (A\times A)\sequoid\blank
-  \]
-Upon examining the induced morphism $\oc A\tensor \oc A \to (A\times A)\sequoid(\oc A\tensor \oc A)$, we observe that it is equal to the following composite
-\[
-  \oc A\tensor \oc A \xrightarrow{\xi} (A\sequoid(\oc A\tensor\oc A)) \times (A\sequoid(\oc A\tensor\oc A))\xrightarrow{\dist\inv}(A\times A)\sequoid(\oc A\tensor \oc A)
-  \]
-where the morphism $\xi$ is induced by the morphisms
-\[
-  \begin{tikzcd}
-    %
-      &
-        & (A\sequoid\oc A)\tensor \oc A \arrow[r, "\wk"]
-          & (A\sequoid\oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            & A\sequoid (\oc A\tensor \oc A) \\
-    \oc A \tensor \oc A \arrow[urr, "\alpha\tensor\id"] \arrow[dr, "\sym"]
-      &
-        &
-          &
-            & \\
-    %
-      & \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"]
-        & (A\sequoid\oc A)\tensor \oc A \arrow[r, "\wk"]
-          & (A\sequoid\oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            & A\sequoid (\oc A\tensor \oc A) \\
-  \end{tikzcd}
-  \]
-
-Now let $\map{\mu}{B}{B\tensor B}$ be a commutative comonoid in $\G(\alpha)$ and let $\sigma\from B\to A$ be a morphism.  We build up a chain as follows:
-\[
-  B \xrightarrow{\mu} B\tensor B \xrightarrow{\sigma\tensor\id_B} A \tensor B \xrightarrow{\wk} A \sequoid B \xrightarrow{\Delta} (A \sequoid B) \times (A \sequoid B) \rightarrow{\dist_{A,A,B}\inv} (A\times A)\sequoid B
-  \]
-where $\Delta=\langle\id,\id\rangle$ is the diagonal morphism into the product.  The composite $\comp{\comp{\wk}{\sigma\tensor\id_B}}{\mu}$ gives rise to a unique morphism
-\[
-  \sigma^\dagger=\fcoal{\comp{\comp{\wk}{\sigma\tensor\id_B}}{\mu}}\from B\to \oc A
-  \]
-making the following diagram commute:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\sigma^\dagger"']
-      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
-        & A\tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[d, "\id_A\sequoid\sigma^\dagger"] \\
-    \oc A \arrow[rrr, "\alpha"]
-      &
-        &
-          & A\sequoid\oc A
-  \end{tikzcd}
-  \]
-
-We claim that $\sigma^\dag$ gives us a homomorphism of comonoids; that is, that the following square commutes:
-\[
-  \begin{tikzcd}
-  B \arrow[r, "\mu"] \arrow[d, "\sigma^\dag"']
-    & B\tensor B \arrow[d, "\sigma^\dag\tensor\sigma^\dag"] \\
-  \oc A \arrow[r, "\mu"]
-    & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-We will show this by proving that the two paths round the square are both anamorphisms for the morphism $B\to (A\times A)\sequoid B$ given above.
-Since anamorphisms are unique by the definition of a final coalgebra, this will mean that the two branches are equal.
-
-We start with the branch $B\to B\tensor B \to \oc A\tensor \oc A$.  We claim that the following diagram commutes:
-\begin{longdiagram}
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\sigma^\dag"]
-      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
-        & A \tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[r, "\Delta"] \arrow[d, "\id_A\sequoid\sigma^\dagger"]
-            & (A\sequoid B) \times (A \sequoid B) \arrow[r, "{\dist_{A,A,B}\inv}"] \arrow[d, "{\langle\id_A\sequoid\sigma^\dagger,\id_A\sequoid\sigma^\dagger\rangle}"]
-              & (A \times A) \sequoid B \arrow[d, "\id_{A\times A}\sequoid\sigma^{\dagger}"] \\
-    \oc A \arrow[rrr, "\alpha"] \arrow[d, "\mu"]
-      &
-        &
-          & A\sequoid \oc A \arrow[r, "\Delta"]
-            & (A \sequoid \oc A)\times (A\sequoid \oc A) \arrow[r, "{\dist_{A,A,\oc A}\inv}"']
-              & (A\times A)\sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
-    \oc A \tensor \oc A \arrow[rrrrr]
-      &
-        &
-          &
-            &
-              & (A\times A)\sequoid(\oc A\tensor \oc A)
-  \end{tikzcd}
-\end{longdiagram}
-
-The rectangle at the top left is one we have drawn before.
-The square in the middle at the top commutes because $\Delta$ gives rise to a natural transformation between $\id_{\G(\alpha)}$ and $\blank\times\blank$.
-The square at the top right commutes because $\dist$ is a natural transformation.
-
-The rectangle at the bottom commutes because both branches are copycat strategies for $\oc A\implies (A\times A)\sequoid(\oc A\tensor\oc A)$, and there is a unique such strategy.
-
-It follows that $\comp\mu{\sigma^\dagger}$ is an anamorphism for the morphism along the top and the functor $(A\times A)\sequoid\blank$.
-
-Now we deal with the other branch.  We claim that we have the following commutative diagram:
-\begin{longdiagram}
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[dd, "\mu"'] \arrow[ddr, phantom, "\textbf{1}"]
-      & B\tensor B \arrow[r, "\sigma\tensor \id_B"] \arrow[d, "\id_B\tensor\mu"] \arrow[dr, phantom, "\textbf{2}"]
-        & A \tensor B \arrow[rrr, "\wk"] \arrow[d, "\id_A\tensor\mu"] \arrow[drrr, phantom, "\textbf{3}"]
-          &
-            &
-              & A\sequoid B \arrow[d, "\id_A\sequoid\mu"] \\
-    %
-      & B \tensor(B\tensor B) \arrow[r, "\sigma\tensor\id_{B\tensor B}"] \arrow[d, "{\assoc_{B,B,B}\inv}"]
-        & A \tensor (B \tensor B) \arrow[rrr, "\wk"] \arrow[drr, phantom, "\textbf{4}"]
-          &
-            &
-              & A \sequoid (B\tensor B) \arrow[dd, "\id_A\sequoid(\sigma^\dagger \tensor \sigma^\dagger)"] \arrow[dl, "{\passoc_{A,B,B}}"] \arrow[ddl, phantom, "\textbf{7}"] \\
-    B \tensor B \arrow[r, "\mu\tensor \id_B"] \arrow[d, "\sigma^\dagger \tensor \sigma^\dagger"'] \arrow[drrr, phantom, "\textbf{5}" yshift=-0.3em]
-      & (B \tensor B) \tensor B \arrow[r, "(\sigma\tensor\id_B)\tensor\id_B"' yshift=-0.3em]
-        & (A \tensor B) \tensor B \arrow[r, "\wk\tensor\id_B"]
-          & (A \sequoid B) \tensor B \arrow[r, "\wk"] \arrow[d, "(\id\sequoid\sigma^\dagger)\tensor\sigma^\dagger"'] \arrow[dr, phantom, "\textbf{6}"]
-            & (A\sequoid B)\sequoid B \arrow[d, "(\id\sequoid\sigma^\dagger)\sequoid\sigma^\dagger"]
-              & \\
-    \oc A \tensor \oc A \arrow[rrr, "\alpha\sequoid\id_{\oc A}"']
-      &
-        &
-          & (A \sequoid \oc A)\tensor \oc A \arrow[r, "\wk"]
-            & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-              & A \sequoid (\oc A \tensor \oc A)
-  \end{tikzcd}
-\end{longdiagram}
-
-We check that each cell commutes in turn.
-\begin{enumerate}[{\bf 1}]
-  \item is the diagram showing that the comultiplication for $B$ is associative.
-  \item commutes since $\blank\tensor\blank$ is a functor.
-  \item commutes since $\wk$ is a natural transformation.
-  \item is the coherence diagram for sequoidal categories that we gave earlier.
-  \item is obtained from an earlier diagram by taking the tensor product with $B$ on the top, taking the tensor product with $\oc A$ on the bottom, and passing between the two with the morphism $\sigma^\dag$.
-  \item commutes because $\wk$ is a natural transformation.
-  \item commutes because $\passoc$ is a natural transformation.  
-\end{enumerate}
-
-\pagebreak
-
-Furthermore, note that the morphism along the bottom is one of the two morphisms $\oc A\tensor\oc A \to A\sequoid(\oc A \tensor \oc A)$ that we gave before.
-To get the other one, note that since the comultiplication in $B$ is commutative, we have a commutative diagram:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[ddl, "\mu"'] \arrow[dd, "\mu"] \\
-    %
-      & \\
-    B\tensor B \arrow[r, "\sym"] \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"']
-      & B\tensor B \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"] \\
-    \oc A \tensor \oc A \arrow[r, "\sym"]
-      & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-which we may glue on to the left hand side of the diagram above, giving a commutative diagram with the second morphism $\oc A\tensor \oc A\to A\sequoid(\oc A\tensor \oc A)$ along the bottom.
-
-These two diagrams between them induce a commutative diagram
-\begin{longdiagram}
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\mu"']
-      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
-        & A \tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[r, "\Delta"]
-            & (A \sequoid B) \times (A \sequoid B) \arrow[r, "{\dist_{A,A,B}\inv}" yshift=0.6em] \arrow[d, "{\langle \id_A\sequoid\mu, \id_A\sequoid\mu\rangle}"']
-              & (A\times A)\sequoid B \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
-    B\tensor B \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"']
-      &
-        &
-          &
-            & (A \sequoid (B \tensor B)) \times (A \sequoid (B\tensor B)) \arrow[d, "{\langle \id_A\sequoid(\sigma^\dagger\tensor\sigma^\dagger), \id_A\sequoid(\sigma^\dagger\tensor\sigma^\dagger)\rangle}"'] \arrow[r, "{\dist_{A,A,B\tensor B}\inv}"]
-              & (A \times A) \sequoid (B\tensor B) \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
-    \oc A \times \oc A \arrow[rrrr, "\xi"]
-      &
-        &
-          &
-            & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "{\dist_{A,A,\oc A\tensor\oc A}\inv}" yshift=0.3em]
-              & (A\times A) \sequoid(\oc A \tensor \oc A)
-  \end{tikzcd}
-\end{longdiagram}
-
-that proves that $\comp{\sigma^\dagger\tensor\sigma^\dagger}{\mu}$ is an anamorphism for the morphism along the top as well.  Therefore, $\sigma^\dagger$ does give us a homomorphism of comonoids.
-
-We claim that $\sigma^\dagger$ makes the following diagram commute:
-\[
-  \begin{tikzcd}
-    B \arrow[d, "\sigma^\dagger"'] \arrow[dr, "\sigma"]
-      & \\
-    \oc A \arrow[r, "\der"']
-      & A
-  \end{tikzcd}
-  \]
-Indeed, we have a commutative diagram
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\comp{\wk}{\comp{(\sigma\tensor\id_B)}{\mu}}" yshift=0.3em] \arrow[d, "\sigma^\dagger"']
-      & A \sequoid B \arrow[dr, "\id_A\sequoid 1"] \arrow[d, "\id_A\sequoid\sigma^\dagger"']
-        & 
-          & \\
-    \oc A \arrow[r, "\alpha"']
-      & A \sequoid \oc A \arrow[r, "\id_A\sequoid 1"']
-        & A \sequoid I \arrow[r, "\run_A"]
-          & A
-  \end{tikzcd}
-  \]
-and we observe that the morphism along the bottom is precisely $\der$, while the morphism along the top is precisely $\sigma$.
-
-Now we show uniqueness.  Suppose that $\tau\from B\to\oc A$ is a morphism making the following diagram commute:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[d, "\tau"] \arrow[r, "\mu"] \arrow[dl, "\sigma"']
-        & B \tensor B \arrow[d, "\tau\tensor\tau"] \\
-    A
-      & \oc A \arrow[l, "\der"] \arrow[r, "\mu"]
-        & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-Then we get the following commutative diagram:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\tau"]
-      & B \tensor B \arrow[r, "\sigma\tensor\id_A"] \arrow[d, "\tau\tensor\tau"]
-        & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id_A\tensor\tau"]
-          & A \sequoid B \arrow[d, "\id_A\sequoid\tau"] \\
-    \oc A \arrow[r, "\mu"]
-      & \oc A \tensor \oc A \arrow[r, "\der\tensor\id_A"]
-        & A \tensor \oc A \arrow[r, "\wk"]
-          & A \sequoid \oc A
-  \end{tikzcd}
-  \]
-where commutativity of the middle square is derived from the commutative triangle on the left of the diagram immediately above.
-Now observe that the morphism $A\to A\sequoid\oc A$ along the bottom is precisely the morphism $\alpha$.
-Therefore, $\tau$ is an anamorphism for the morphism
-\[
-  B \xrightarrow{\mu} B\tensor B \xrightarrow{\sigma\tensor\id_A} A\tensor B \xrightarrow{\wk} A \sequoid B
-  \]
-and so $\tau=\sigma$.
-
-We have shown that $\oc A \xrightarrow{\mu}\oc A \tensor \oc A$ is indeed the cofree commutative comonoid on $A$.
-
-\section{The final sequence}
-
-Familiarity with the final sequence is assumed; see \cite{finalseq} for a less terse presentation of the following material.
-
-Let $\C$ be a category and let $\F\from \C\to \C$ be an endofunctor.
-Suppose that $\C$ has a terminal object $1$.
-We shall further assume that we are able to construct all the limits we want in $\C$.
-Let $\Ord$ denote the ordered class of ordinals, considered as a category.
-We shall inductively construct a functor $\FS_\F\from\oppcat\Ord\to\C$ (known as the \emph{final sequence of $\F$}) as follows:
-
-\begin{itemize}
-  \item $\FS_\F(0)=1$
-  \item $\FS_\F(\beta+1) =\F\left(\FS_F(\beta)\right)$
-  \item On the level of morphisms, $\FS_\F(0\le\beta)$ is the unique morphism $\FS_\F(\beta)\to 1$
-  \item $\FS_\F(\beta+1\le\beta+2)=\F(\FS_\F(\beta\le\beta+1))$
-  \item If $\mu$ is a limit ordinal, then $\FS_\F(\mu)$ is the limit of the diagram
-    \[
-      \mu\hookrightarrow\Ord\xrightarrow{\FS_\F}\C
-      \]
-    and $\FS_\F(\beta\le\mu)$ is the arrow in the limiting cone
-  \item Applying the functor $\F$ to the cone $\FS_\F(\mu)$ gives rise to a new cone over the above diagram, inducing a unique arrow $\FS_\F(\mu+1)\to\FS_\F(\mu)$.
-We set $\FS_\F(\mu\le\mu+1)$ to be equal to this arrow.
-\end{itemize}
-
-A standard fact about the final sequence (see \cite{finalseq}) is that if $\delta$ is an ordinal and the morphism
-\[
-  \FS_\F(\delta\le\delta+1)\from \F(\FS_\F(\delta))\to \FS_\F(\delta)
-  \]
-is an isomorphism, then the inverse of this morphism exhibits $\FS_\F(\delta)$ as the final coalgebra for the endofunctor $\F$.
-In this case, we say that the final sequence $\FS_\F$ has \emph{stabilized by $\delta$}.
-
-Our goal is to characterize the final sequence for functors of the form $A\sequoid\blank$ in categories $\G(\alpha)$ of games, in the hope that this will allow us to study the exponential $\oc A$ in more depth.
-
-\subsection{The rank of a transfinite sequence of natural numbers}
-
-We fix a (large) ordinal $\alpha$.
-The goal of this section is to assign an ordinal \emph{rank} to a sequence $\beta\to\omega$ of natural numbers (for $\beta<\alpha$).
-This rank will turn out to be the key to characterizing the final sequence of the $A\sequoid\blank$ functor.
-This rank will not depend on $\alpha$, and we could do without mentioning $\alpha$ at all (although mentioning $\alpha$ allows us to avoid size issues).
-
-To define our rank, we will give a chain of subsets 
-\[
-  R_0\subset R_1\subset R_2\subset\dots \subset R_\delta \subset\dots \subset \omega^{*\alpha}
-  \]
-where $\delta$ will run over all the ordinals.
-We think of $R_\delta$ as being the set of all sequences \emph{with rank at most $\delta$}; accordingly, we shall define the \emph{rank} of a sequence $s$ to be the smallest ordinal $\delta$ such that $s\in R_\delta$.
-
-\begin{definition}
-  Let $(s\from\beta\to\omega)\in\omega^{*<\alpha}$.  We define the \emph{derivative} of $s$ to be the sequence $\Delta s$ given by:
-  \[
-    s\inv\left(\omega\setminus\{0\}\right) \xrightarrow{s} \omega\setminus\{0\} \xrightarrow{n\mapsto n-1} \omega
-    \]
-  In other words, we remove all occurrences of $0$ from the sequence $s$ and then subtract $1$ from each term.  
-\end{definition}
-
-We shall now define the sets $R_\delta$:
-\begin{definition}
-  \begin{itemize}
-    \item $R_0=\{\emptyplay\}$
-    \item $R_{\delta+1}=\left\{s\in\omega^{*<\alpha}\suchthat \Delta s\in R_\delta\right\}$
-    \item If $\mu$ is a limit ordinal then $R_\mu$ is the limit closure of the union of the $R_\delta$ for $\delta<\mu$.  In other words, a sequence $s$ is contained in $R_\mu$ if \textbf{either}
-      \begin{itemize}
-        \item $\length(s)$ is a successor ordinal and $s\in R_\delta$ for some $\delta<\mu$ \textbf{or}
-        \item $\length(s)$ is a limit ordinal and for all proper prefixes $t\pprefix s$, $t\in R_\delta$ for some $\delta<\mu$
-      \end{itemize}
-  \end{itemize}
-
-  If $s\in\omega^{*<\alpha}$, we define $\rank(s) = \min\{\delta\suchthat s\in R_\delta\}$.
-\end{definition}
-
-One consequence of the above definition is that if $\mu$ is a limit ordinal then all the sequences of rank $\mu$ have limiting length.
-
-We need to prove some results so we can be sure that the rank of a sequence is well defined.
-
-\begin{proposition}
-  \label{RankProposition}
-  \begin{enumerate}[i)]
-    \item If $s\in R_\delta$ and $t$ is any subsequence of $s$ (not necessarily an initial prefix), then $t\in R_\delta$
-    \item If $s\in R_\delta$, then $\Delta s\in R_\delta$.
-    \item If $\gamma\le\delta$, then $R_\gamma\subset R_\delta$
-    \item If $s\in\omega^{*<\alpha}$, then $s\in R_\delta$ for some $\delta$.
-  \end{enumerate}
-
-  \begin{proof}
-    \begin{enumerate}[(i): ]
-      \item We prove this by induction on $\delta$.
-Suppose $s\in R_{\delta+1}$ and $t$ is a subsequence of $s$.
-Then $\Delta s\in R_\delta$.
-Now $\Delta t$ is a subsequence of $\Delta s$, so $\Delta t\in R_\delta$ by the induction hypothesis and therefore $\Delta t\in R_{\delta +1}$.
-
-        Let $\mu$ be a limit ordinal and suppose that $s\in R_\mu$.
-If $s$ has successor length, then $s\in R_\delta$ for some $\delta<\mu$.
-Then $t\in R_\delta$ by the induction hypothesis.
-If $t$ has successor length, this automatically means that $t\in R_\mu$, while if $t$ has limiting length, then every subsequence of $t$ is contained in $R_\delta$ by induction, so $t\in R_\mu$.
-
-        Suppose instead that $s$ has limiting length.
-Then for all proper prefixes $u\pprefix s$, we have $u\in R_\delta$ for some $\delta<\mu$.
-If $t$ has successor length, then $t$ cannot be cofinal in $s$, so it is a subsequence of some proper prefix $u$ of $s$.
-Therefore, $t\in R_\delta$ by the induction hypothesis, and so $t\in R_\mu$ as before.
-
-        If instead $t$ has limiting length, then every proper prefix $v\pprefix t$ is a subsequence of some proper prefix $u\pprefix s$.
-Therefore, by induction, for every proper prefix $v\pprefix t$, we have $v\in R_\delta$ for some $\delta<\mu$ and therefore $t\in\mu$.
-
-      \item Induction on $\delta$.
-If $s\in R_{\delta+1}$ then $\Delta s\in R_\delta$; by the induction hypothesis, this means that $\Delta\Delta s\in R_\delta$ and therefore that $\Delta s\in R_{\delta+1}$.
-
-        Now let $\mu$ be a limit ordinal.
-Suppose $s\in R_\mu$.
-If $s$ has successor length, it means that $s\in R_\delta$ for some $\delta<\mu$, so $\Delta s\in R_\delta$ by induction.
-By (i), all the prefixes of $\Delta s$ are in $R_\delta$ as well, so $\Delta s\in R_\mu$.
-
-        Suppose instead that $s$ has limiting length.
-Then for all proper prefixes $t\pprefix s$, we have $t\in R_\delta$ for some $\delta<\mu$.
-If $\Delta s$ has successor length, then we may choose some proper prefix $t\pprefix s$ such that $\Delta s = \Delta t$ and therefore $\Delta s\in R_\delta$, so it is in $R_\mu$.
-If instead $\Delta s$ has limiting length, then for all proper prefixes $v\pprefix\Delta s$, we may choose some $u\pprefix s$ with $v=\Delta u$.
-Then we have $u\in R_\delta$ for some $\delta<\mu$, so $v\in R_\delta$ by the induction hypothesis.
-Therefore, $t\in R_\mu$.
-
-      \item It is clear that $R_\delta\subset R_\mu$ if $\delta<\mu$ and $\mu$ is a limit ordinal.
-Therefore, by induction it will suffice to show that $R_\delta\subset R_{\delta+1}$ for all $\delta$.
-
-        Suppose $s\in R_\delta$.  Then $\Delta s\in R_\delta$ by (ii) and therefore $s\in R_{\delta+1}$.
-
-      \item We show this by induction on the length $\beta$ of $s$.
-If $\beta=0$ then $s\in R_0$.
-Suppose that $s=s'n$.
-If we apply $\Delta$ $n$ times to $s$ then we end up with the sequence $\Delta^ns .0$.
-Applying $\Delta$ never lengthens the sequence, by Lemma \ref{TechnicalOrdinalLemma}.
-Now if we apply $\Delta$ one more time, we end up with a strictly shorter sequence, so by induction it is contained in some $R_\delta$.
-Then $s$ is contained in $R_{\delta+n+1}$.
-
-        Now suppose that $s$ has limiting length.
-Then, by induction, for all proper prefixes $t\pprefix s$ there exists $\delta_t$ such that $t\in R_{\delta_t}$.
-If we let $\mu$ be some limit ordinal that is greater than all the $\delta_t$, then $s\in R_\mu$.
-\qedhere
-    \end{enumerate}
-  \end{proof}
-\end{proposition}
-
-\begin{example}
-  Any sequence with only finitely many distinct terms has finite rank: indeed, suppose $s\from\beta\to n$ is such a sequence.
-Then, after applying the derivative $n$ times, we end up with the empty sequence.
-
-  The `identity' sequence $\omega\to\omega$ has rank $\omega$: indeed, every proper prefix has finite rank, but applying the derivative operator has no effect.
-
-  More generally, the division algorithm for ordinal arithmetic tells us that if $\gamma$ is an ordinal, then there is a unique ordinal $\gamma'$ and a unique natural number $n$ such that $\gamma=\omega\gamma' + n$.
-If $\beta$ is an ordinal, we may define a sequence $c_\beta\from \beta\to\omega$ by setting:
-  \[
-    c_\beta(\omega\gamma'+n) = n
-    \]
-  We show by induction on $\beta$ that the sequence $c_\beta$ has rank $\beta$.  First, we claim that
-  \[
-    c_\beta = \Delta c_{\beta+1}
-    \]
-  The first thing to show is that the order type of $c_{\beta+1}\inv(\omega\setminus\{0\})$ is $\beta$.
-Indeed, $c_{\beta+1}\inv(\omega\setminus\{0\})$ is precisely the set of successor ordinals that are less than $\beta+1$.
-We therefore have an order preserving bijection
-  \begin{IEEEeqnarray*}{rCl}
-    \beta & \to & c_{\beta+1}\inv(\omega\setminus\{0\}) \\
-    \gamma & \mapsto & \gamma+1
-  \end{IEEEeqnarray*}
-
-  This map sends $\omega\gamma'+n$ to $\omega\gamma'+(n+1)$.  The map $\Delta c_{\beta+1}$ is therefore given by:
-  \begin{IEEEeqnarray*}{CCCCCCC}
-    \beta & \xrightarrow{\sim} & c_{\beta+1}\inv(\omega\setminus\{0\}) & \rightarrow & \omega \setminus \{0\} & \rightarrow & \omega \\
-    \omega\gamma' + n & \mapsto & \omega\gamma' + (n+1) & \mapsto & n+1 & \mapsto & n
-  \end{IEEEeqnarray*}
-  In other words, it is the same as $c_\beta$.  This deals with the successor step of the induction.
-
-  Now let $\mu$ be a limit ordinal.
-A proper prefix of $c_\mu$ is a sequence of the form $c_\delta$ for $\delta<\mu$.
-By the induction hypothesis, $c_\delta\in R_\delta$ for all $\delta<\mu$ and therefore $c_\mu\in R_\mu$.
-
-  Now suppose for a contradiction that $c_\mu\in R_\delta$ for some $\delta<\mu$.
-Then $c_{\delta+1}\prefix c_\mu$ so, by Proposition \ref{RankProposition}(i), $c_{\delta+1}\in R_\delta$, which contradicts our induction hypothesis.
-
-  Therefore, $\rank(c_\mu)=\mu$.  
-\end{example}
-
-We call $c_\delta$ the \emph{canonical sequence of length $\delta$}.
-We want to use it to obtain a neater characterization of the sets $R_\delta$.
-What we would like to say is that $\rank(s)\ge\delta$ if and only if $c_\delta$ is a subsequence of $s$.
-However, this is not quite true.
-For example, the sequence
-\[
-  23456\dots
-  \]
-over $\omega$ has rank $\omega$, but does not contain the sequence $c_\omega=01234\dots$ as a subsequence.
-We will have to modify the condition a little bit; the cost will be that our characterization only works for limit ordinals, but this is not a big problem.
-
-\begin{definition}
-  Let $s\from\beta\to\omega$ be a sequence.  We say that $s$ is \emph{weakly increasing} if $s(\delta)<s(\delta+1)$ for all $\delta<\beta$.
-\end{definition}
-
-\begin{example}
-  $c_\beta$ is weakly increasing for any $\beta$.  If we take, for example, the sequence $c_{\omega+\omega}$:
-  \[
-    01234\dots\;01234\dots
-    \]
-  then we see where the `weakly' comes from: we have $c_{\omega+\omega}(2)>c_{\omega+\omega}(\omega)$, even though $2<\omega$.
-\emph{Weakly increasing} means `increasing on every $\omega$-segment, but unconstrained at limits'.
-
-  There are plenty of other weakly increasing sequences.  For example:
-  \begin{gather*}
-    2468\dots \\
-    12358\dots\;2357\dots \\
-    01234\dots\;12345\dots\;23456\dots\;34567\dots\;45678\dots\;\dots\dots
-  \end{gather*}
-\end{example}
-
-\pagebreak
-
-\begin{lemma}
-  \label{WeaklyIncreasingLemma}
-  \begin{enumerate}[i)]
-    \item Let $s\in\omega^{*<\alpha}$ be weakly increasing.  Then $\Delta s$ is weakly increasing.
-    \item Suppose $\mu$ is a limit ordinal and that $s\in \omega^{*<\alpha}$ is such that $\rank(s)=\mu$.  Then $\rank(\Delta s)=\mu$.
-    \item Let $\mu$ be a limit ordinal and let $s\from\mu\to\omega$ be a weakly increasing sequence of length $\mu$.  Then $\rank(s)=\mu$.  
-  \end{enumerate}
-
-  \begin{proof}
-    \begin{enumerate}[(i): ]
-      \item Let $m,n$ be adjacent terms in $\Delta s$.
-That means that $(m+1).p$ occurs somewhere in the sequence $s$, so $p>m+1$, since $s$ is weakly increasing.
-In particular, $p\ne 0$, so it is not removed from the sequence.
-It follows that $n=p-1$ and therefore that $m<n$.
-
-      \item We have $s\in R_\mu$, so $\Delta s\in R_\mu$; i.e., $\rank(\Delta s)\le\mu$.  Suppose that $\Delta s\in R_\delta$ for $\delta<\mu$.  Then $s\in R_{\delta+1}$, which is a contradiction.
-
-      \item We prove the following statement by induction on $\beta$: if $s\from\beta\to\omega$ is a weakly increasing sequence of length $\beta$, then
-        \begin{itemize}
-          \item If $\beta=\omega\beta'+m$ is a successor ordinal, and $s=s'n_0\dots n_{m-1}$, then $\rank(s) = \omega\beta'+n_{m-1}+1$
-          \item If $\beta=\omega\beta'$ is a limit ordinal then $\rank(s)=\beta$
-        \end{itemize}
-        Suppose that $s$ has length $\omega\beta'+m$ and write $s$ as $s'n_0\dots n_{m-1}$, where $s'$ is a limiting play.
-Write $n=n_{m-1}$ -- so $n_i<n$ for $i<m-1$.
-By the induction hypothesis, $s'$ has rank $\omega\beta'$.
-
-        If we apply the derivative $n$ times to $s$ then we end up with the sequence $\Delta^n s'.0$.
-By part (ii), $\Delta^n s'$ has rank $\omega\beta'$, and so $\Delta^n s'.0$ has rank at least $\omega\beta'$.
-Moreover, since it is a successor play, it cannot have limiting rank, and therefore its rank is at least $\omega\beta+1'$.
-If we take the derivative one more time, then we end up with the sequence $\Delta^{n+1}s'$, which has rank $\omega\beta'$, and it follows that $\Delta^n s'.0$ has rank $\omega\beta'+1$.
-Therefore, $s$ has rank $\omega\beta'+n+1$.
-
-        Now suppose that $\mu$ is a limit ordinal and that $s$ has length $\mu$.
-If we take some proper prefix $t\pprefix s$ of length $\delta<\mu$, then $t$ is weakly increasing, so by the induction hypothesis it has rank at most $\delta+m$ for some $m$.
-$\delta+m<\mu$ and $t$ was arbitrary, so it follows that $s\in R_\mu$; i.e., that $\rank(s)\le\mu$.
-
-        We claim that $\rank(s)=\mu$.
-Indeed, suppose that $s\in R_\delta$ for some $\delta<\mu$.
-Let $u$ be the prefix of $s$ of length $\delta+1$.
-By the induction hypothesis, $\rank(u)\ge\delta+1>\rank(s)$, which is a contradiction, since $u\prefix s$.
-\qedhere
-    \end{enumerate}
-  \end{proof}
-\end{lemma}
-
-We can now give our classification result:
-
-\begin{theorem}
-  Let $s\in\omega^{*<\alpha}$ and let $\mu<\alpha$ be a limit ordinal.  Then $\rank(s)\ge\mu$ if and only if $s$ has a weakly increasing subsequence of length $\mu$.
-
-  For $n\ge 1$, $\rank(s)\ge\mu+n$ if and only if $s$ has a subsequence of the form $tm$, where $t$ is weakly increasing of length $\mu$ and $m\ge n-1$ is a single term.
-
-  \begin{proof}
-    \emph{If: } Suppose $t$ is a weakly increasing subsequence of length $\mu$.
-By Lemma \ref{WeaklyIncreasingLemma}, $t$ has rank $\mu$, so by Proposition \ref{RankProposition}, $s$ has rank at least $\mu$.
-
-    Write $s=s'u$, where $t$ is a subsequence of $s'$ and $u$ contains some term $m\ge n-1$.
-Then $s'$ has rank at least $\mu$.
-Then $\Delta^{n-1} s'$ has rank at least $\mu$ and $\Delta^{n-1}u\ne\emptyplay$, since $u$ contains the term $m$.
-Let $x$ be the first term of $\Delta^{n-1}u$.
-Then $\Delta^{n-1}s'.x$ is a subsequence of $\Delta^{n-1}s$, and it must have rank at least $\mu+1$ (since it is a successor play and contains $\Delta^{n-1}s'$ as a subsequence.
-Therefore, $\Delta^{n-1}s$ has rank at least $\mu+1$ and so $s$ has rank at least $\mu+1+(n-1)=\mu+n$.
-
-    \emph{Only if: } We prove by induction on $\delta$ that if $s\in\omega^{*<\alpha}$ has rank $\delta$ then $s$ satisfies the appropriate condition above.
-First, let $\mu$ be a limit ordinal and suppose that $s$ has rank $\mu+1$.
-We want to show that $s$ has a weakly increasing subsequence of length $\mu$ that is not cofinal in $s$.
-
-    Since $s$ has rank $\mu+1$, $\Delta s$ has rank $\mu$, so contains a weakly increasing subsequence of length $\mu$, by the induction hypothesis.
-This sequence lifts to a weakly increasing subsequence $u$ of $s$.
-If $s$ has successor length, then $u$ is not cofinal in $s$, so we win.
-
-    Otherwise, suppose that $s$ has limiting length.
-Then there must be some proper prefix $t\pprefix s$ of rank $\mu$; otherwise, $s\in R_\mu$, which is a contradiction.
-Then by the induction hypothesis we can find a weakly increasing subsequence of $t$ of length $\mu$, and this subsequence is not cofinal in $s$.
-
-    Now let $n\ge1\in\omega$ and suppose that $s$ has rank $\mu+n$.
-If we apply the derivative $n-1$ times to $s$ then we end up with a sequence of rank $\mu+1$.
-By the previous part, this sequence must have a subsequence of the form $u.m$, where $u$ is weakly increasing of length $\mu$ and $m$ is a single term.
-This sequence lifts to a subsequence $\hat u.(m+n-1)$ of $s$, where $\hat u$ is still weakly increasing.
-
-    Lastly, suppose that $s$ has rank $\mu$, for $\mu$ a limit ordinal.  It follows that $s$ has limiting length.
-
-    For each limit ordinal $\lambda<\mu$, let $t_\lambda$ be the shortest prefix of $s$ of rank at least $\lambda$.
-Since $s$ has rank $\mu$, $t_\lambda$ exists for each $\lambda$.
-By the induction hypothesis, each $t_\lambda$ has some weakly increasing subsequence of length $\lambda$.
-We will prove something stronger: we will inductively construct for each $\lambda$ a weakly increasing subsequence $u_\lambda$ of $t_\lambda$ such that $u_\lambda$ has length $\lambda$ and such that if $\lambda'\le\lambda$ then $u_{\lambda'}\prefix u_\lambda$.
-
-    Suppose we have constructed $u_\lambda$.
-Note that the rank of $t_\lambda$ must be less than $\lambda+\omega$; otherwise, $t_\lambda$ would have to have some prefix of length $\lambda+m$ for some $m$, contradicting minimality of $t_\lambda$.
-Therefore, $t_\lambda$ is a proper prefix of $t_{\lambda+\omega}$, so we write $t_{\lambda+\omega}=t_\lambda.v$ for some sequence $v$.
-
-    We claim that for all $N\in\omega$ there is some $n\ge N$ occurring in the sequence $v$.
-Indeed, if $N$ is such that there is no $n\ge N$ occurring in $v$, then we may take the derivative of $u_{\lambda+\omega}$ finitely many times and end up with a sequence of rank $\lambda$, which is a contradiction.
-We construct $u_{\lambda+\omega}$ as follows: let $n_0$ be the least value occurring in the sequence $v$ and let $a_0$ be the earliest occurrence of $n_0$ in the sequence $v$.
-Now let $N$ be the largest value that occurs (not necessarily strictly) earlier than $a_0$ in the sequence $v$.
-We know that there is some $n\ge N$ occurring in $v$; let $n_1$ be the least such $n$.
-Certainly, $n_1$ may only occur later in the sequence $v$ than $a_0$, so let $a_1$ be the first occurrence of $n_1$ in the sequence $v$.
-Continuing in this way, we build up an increasing subsequence $a_0 a_1 a_2 \dots$ of $v$.
-We set
-    \[
-      u_{\lambda+\omega} = u_\lambda a_0 a_1 a_2 \dots
-      \]
-    Then certainly $u_\lambda$ is a prefix of $u_{\lambda+\omega}$.
-
-    Now suppose that $\mu$ is a multiple of $\omega^2$ and we have constructed the sequences $u_\lambda$ for all limit ordinals $\lambda<\mu$.
-Then the sequences $u_\lambda$ glue to give a sequence $u_\mu$.
-We need to check that $u_\mu$ is a subsequence of $t_\mu$.
-Indeed, if $u_\mu$ is not a subsequence of $t_\mu$ then there is some earliest term $b$ in the sequence $u_\mu$ such that $b$ is not a term of $t_\mu$.
-But then there is some $\lambda'<\mu$ such that $u_{\lambda'}$ is not a subsequence of $t_\mu$, which is a contradiction.
-
-    This completes the induction.
-
-    To complete the argument, suppose that $\mu$ is a limit ordinal and that $\rank(s)\ge\mu$.
-Write $\gamma=\rank(s)$.
-We may write $\gamma=\lambda+m$ for some $m$, where $\lambda\ge\mu$ is a limit ordinal.
-Then $s$ has a weakly increasing subsequence of length $\lambda$, and we may take a prefix of this subsequence to obtain a weakly increasing subsequence of $s$ of length $\mu$.
-
-    Now suppose that $\rank(s)\ge\mu+n$.
-We may write $\rank(s) = \lambda+m$, where $\lambda$ is a limit ordinal and either $\lambda>\mu$ or $\lambda=\mu$ and $m\ge n$.
-In the first case, $s$ has a weakly increasing sequence of length $\lambda$; we may then take a prefix of length $\mu+\omega$ of this sequence and note that this sequence must have a subsequence of the form $up$, for some $p\ge (n-1)$.
-
-    In the second case, $s$ has a subsequence of the form $uq$, where $u$ is weakly increasing of length $\mu$ and $q\ge m-1\ge n-1$.  
-  \end{proof}
-\end{theorem}
-
-A consequence of this classification is that if $s\in\omega^{*<\alpha}$, then $\rank(s)<\length(s)+\omega$.
-Furthermore, if $\mu$ is a limit ordinal and $\length(s)<\mu$, then $\rank(s)<\mu$.
-We will see that this is the reason why the final sequence for $A\sequoid\blank$ converges so quickly for $\omega$- and $(\omega+1)$-games: there are no sequences of finite length with infinite rank, and every sequence of length $\le \omega+1$ has rank less than $\omega+\omega$.
-
-\subsection{Classification of the final sequence for $A\sequoid\protect\blank$}
-
-Let $\G(\alpha)$ be a category of games, and let $A$ be an object of $\G(\alpha)$.
-We have $M_{\oc A}=M_A\times\omega$, so there is a natural map $\pr_2\from M_{\oc A}\to \omega$.
-If $s$ is a play in $\oc A$, then we get an associated sequence of natural numbers $\hat s\from\length(s)\to\omega$ given by\[
-  \hat s = \pr_2 \circ s
-  \]
-
-Given an ordinal $\delta$, we define a game $(\oc A)_\delta=(M_{\oc A},\lambda_{\oc A}, \zeta_{\oc A}, P_{\oc A,\delta})$, where $P_{\oc A,\delta}$ is the subset of $P_{\oc A}$ given by:
-\[
-  P_{\oc A,\delta} = \{s\in P_{\oc A}\suchthat \rank(\hat s)\le\delta\}
-  \]
-As we have seen, this set is prefix-closed, so $(\oc A)_\delta$ is a well formed game.
-
-For an ordinal $\delta$, let $A^{\sequoid\delta}$ denote term $\delta$ in the final sequence for $A\sequoid\blank$ (i.e., $A^{\sequoid\delta}=\FS_{A\sequoid\blank}(\delta)$).
-
-Our main result is as follows:
-
-\begin{theorem}
-  \label{MainFinalSequenceResult}
-  \[
-    A^{\sequoid\delta}\cong (\oc A)_\delta
-    \]
-  Given ordinals $\gamma\le\delta$, the arrow $A^{\sequoid\delta}\to A^{\sequoid\gamma}$ in the final sequence is given by the copycat morphism $(\oc A)_\delta\to(\oc A)_\gamma$ induced by the inclusion $P_{\oc A, \gamma}\hookrightarrow P_{\oc A, \delta}$.
-\end{theorem}
-
-As a sanity check, we observe that if $n<\omega$ then the sequences of rank $n$ are precisely the sequences that only involve the terms $0,\dots,n-1$.
-Therefore, it is easy to see that $A^{\sequoid n}\cong(\oc A)_n$ for all $n<\omega$.
-
-\begin{proof}[Proof of Theorem \ref{MainFinalSequenceResult}]
-  If $s\in P_{\oc A}$ then $\hat s$ has rank $0$ if and only if $s=\emptyplay$.  Therefore, it is easy to see that $A^{\sequoid 0}=I\cong(\oc A)_0$.
-
-  Consider the game $A\sequoid (\oc A)_\delta$.
-If $s$ is a play in this game, then we may identify $s$ with a subsequence of $\oc A$ by labelling the copy of $s$ on the left as $A_0$ and increasing the index by one for each copy of $A$ on the right.
-In other words:
-  \[
-    \Delta\hat s = ({s\vert_{(\oc_A)_\delta}})\hat{}
-    \]
-  By the induction hypothesis, $({s\vert_{(\oc_A)_\delta}})\hat{}$ has rank at most $\delta$ and therefore $\hat s$ has rank at most $\delta+1$.
-
-  Conversely, if $s$ is a sequence in $P_{\oc A}$ and $\Delta\hat s$ has rank at most $\delta$, it means that $s\vert_{A_2,A_3,\dots}\in P_{(\oc_A)_\delta}$ and so $s$ is a play in $A\sequoid(\oc A)_\delta$.
-
-  We check the assertion about the morphisms in the category.
-There is a unique morphism $(\oc A)_\delta\to I$ for each $\delta$, so there is nothing to check there.
-Suppose $\mu<\alpha$ is a limit ordinal.
-By induction, $A^{\sequoid\mu}\cong (\oc_A)_\mu$ and the morphisms $A^{\sequoid\mu}\to A^{\sequoid\delta}$ for $\delta<\mu$ are copycat morphisms induced by the inclusion $P_{\oc A, \delta}\hookrightarrow P_{\oc A,\mu}$.
-If we apply the functor $A\sequoid\blank$ to this cone, then we get a cone from $A\sequoid A^{\sequoid \mu}$ over the diagram formed by $A^{\sequoid\delta}$ for $\delta<\mu$.
-Our argument above also tells us that all the arrows in this new diagram are induced by inclusion functions, and therefore the morphism
-  \[
-    A^{\sequoid\mu}\to A\sequoid A^{\sequoid\mu}
-    \]
-  induced by the inclusion $P_{\oc A,\mu}\hookrightarrow P_{\oc A, \mu+1}$ commutes with both cones, so it is the morphism $A^{\sequoid\mu+1}\to A^{\sequoid\mu}$ in our diagram.
-Under the isomorphism $A^{\sequoid\delta}\cong (\oc A)_\delta$ that we have constructed already, the functor $A\sequoid\blank$ sends inclusion morphisms to inclusion morphisms, so by induction the morphism $A^{\sequoid\mu+n+1}\to A^{\sequoid\mu+n}$ is also induced by an inclusion map.
-
-  It remains to deal with the limiting case.
-Let $\mu$ be a limit ordinal.
-Then $(\oc A)_\mu$ admits a cone over the diagram given by the $A^{\sequoid \delta}$ for $\delta<\mu$, again given by copycat morphisms induced by inclusion maps.
-Let $B$ be an object of $\G(\alpha)$ and suppose that we have a cone
-  \[
-    \left(\map{\sigma_\delta}{B}{A^{\sequoid\delta}}\right)_{\delta<\mu}
-    \]
-  over the diagram given by the $A^{\sequoid\delta}$ and the inclusion morphisms between them.
-This means that if we identify $A^{\sequoid\delta}$ with $(\oc A)_\delta$ then the strategies $\sigma_\delta$ form a chain.
-Then (under this identification) we set
-  \[
-    \sigma = \textrm{limit closure of }\bigcup_{\delta<\mu}\sigma_\delta
-    \]
-  Since $B$ satisfies the limit condition, we do not introduce any extra plays when we take the limit closure and so $\sigma$ is a subset of $P_{B\implies (\oc A)_\mu}$, by the definition of a sequence of rank $\mu$.
-$\sigma$ is limit-closed, so it is a strategy, since the $\sigma_\delta$ are.
-It is clear that composing $\sigma$ with the inclusion morphism $(\oc A)_\mu\to(\oc A)_\delta$ gives $\sigma_\delta$, so this is a morphism of cones.
-
-  Now suppose that $\tau\from B\to(\oc A)_\mu$ also gives rise to a morphism of cones.
-By applying the functor into $\Rel$, we can check that if we compose $\tau$ with the inclusion morphism $(\oc A)_\mu\to(\oc A)_\delta$ then we get the strategy $\tau\cap P_{B\implies(\oc A)_\delta}$.
-Therefore, for all $\delta<\mu$:
-  \[
-    \tau \cap P_{B\implies(\oc A)_\delta}=\sigma_\delta
-    \]
-  Since $\tau$ satisfies the limit condition, it is clear that $\sigma\subset\tau$.
-Conversely, suppose that $s\in\tau$.
-Since $\tau\subset P_{B\implies(\oc A)_\mu}$, $s\vert_{(\oc A)_\mu}$ must have rank at most $\mu$.
-If $s\vert_{(\oc A)_\mu}$ has rank $\delta<\mu$, it follows that $s\in\sigma_\delta\subset\sigma$.
-If instead $s\vert_{(\oc A)_\mu}$ has rank $\mu$ then it must be a limiting play, so by the limit condition on $\sigma$ it suffices to show that all the proper prefixes of $s$ are contained in $\sigma$.
-Since $s\vert_{(\oc A)_\mu}$ has rank $\mu$, all its proper prefixes have rank less than $\mu$ and are therefore contained in $\sigma$ by the argument we have just used.
-
-  It follows that $\sigma=\tau$, and therefore that the limiting cone $A^{\sequoid\mu}$ is indeed given by the game $(\oc A)_\mu$, together with the morphisms induced by inclusion functions.
-This completes the induction.
-\end{proof}
-
-As a consequence of this classification, we have:
-
-\begin{corollary}
-  Let $\alpha=\omega^\beta$ for some $\beta$.  If $A$ is an object of $\G(\alpha)$, then the final sequence for the functor $A\sequoid\blank\from\G(\alpha)\to\G(\alpha)$ stabilizes by $\alpha$.
-
-  Moreover, this bound is tight: there exists some completely negative $\alpha$-game $A$ such that the final sequence for $A\sequoid\blank$ does not stabilize before $\alpha$.  
-  \begin{proof}
-    We want to show that the morphism
-    \[
-      A^{\sequoid\alpha+1}\to A^{\sequoid\alpha}
-      \]
-    in the final sequence for $A\sequoid\blank$ is an isomorphism.
-If we make the identification given by our classification result, then we may identify this morphism with the copycat morphism $(\oc A)_{\alpha+1}\to(\oc A)_\alpha$ induced by the inclusion function
-    \[
-      P_{\oc A,\alpha}\hookrightarrow P_{\oc A,\alpha+1}
-      \]
-    But we have already shown that any sequence of length less than $\alpha$ must have rank less than $\alpha$ and therefore this inclusion map is the identity.
-It follows that the morphism $(\oc A)_{\alpha+1}\to(\oc A)_\alpha$ is the identity and so the morphism above is indeed an isomorphism.
-
-    To show tightness of the bound, it suffices to exhibit a game $A$ such that there sequences $s\in\oc A$ of length less than $\alpha$ and arbitrarily high rank.
-We take $A$ to be the $\alpha$-game $\st$ where there is a unique legal play $qaqa\dots$ of any length $\delta<\alpha$.
-Then for any $\delta<\alpha$ we may construct a play $s\in\oc A$ of the form
-    \[
-      q_1a_1q_2a_2\dots\;q_1a_1q_2a_2\dots\;\dots\dots
-      \]
-    such that $\hat{s}$ has the canonical sequence $c_{\delta}$ as a subsequence.  Therefore, $\hat{s}$ has rank at least $\delta$.  
-  \end{proof}
-\end{corollary}
-
-\begin{note}
-  This result gives an alternative proof that $\oc A$ is the final coalgebra for the functor $A\sequoid\blank$.
-
-  Although we have not developed the theory of win-games of length $\omega^\beta+1$, this result also sheds some light on why the final sequence for $\omega+1$-games stabilizes at $\omega+\omega$: this time, we use the fact that any sequence of length at most $\omega+1$ must have rank at most $\omega+\omega$.
-\end{note}
-
-\section{Further Directions}
-
-There are still a few areas in the current direction that need working out, such as the construction of transfinite win-games with winning strategies.
-I also plan to examine the internal logic of these categories of transfinite games to characterize them logically, and to investigate the logical meaning of convergence of the final sequence.
-Another direction is to see what our classification of the final sequence tells us about the exponential $\oc A$, and whether it tells us anything about the $\omega$-games case.
-
-The paper \cite{MelliesCofCommCom} gives category-theoretic conditions under which the final sequence for $A\sequoid\blank$ always terminates at $\omega$ (though it is not stated in quite that language).
-I plan to examine this work to see which of these conditions fail for categories of transfinite games.
-There are other category-theoretic questions to ask about the behaviour of the final sequence.
-It is known, for example, that the final sequence for a finitary endofunctor on $\Set$ must always terminate by $\omega+\omega$ \cite{finalseq} and there are other results generalizing this.
-Although our endofunctor is not a functor on $\Set$, it can be turned into a functor on $\Set$ if we restrict to copycat strategies.
-It would be worthwhile to view the results of this research under that lens.
-
-As a longer-term piece of research: we had a number of mathematical problems caused by the sequential nature of the games we studied, and we were forced to restrict our attention to negative games (though we found a possible way of getting around that).
-An alternative approach, studied by Abramsky and Melli\`{e}s \cite{AMConcurrent}, is to study \emph{concurrent games}.
-These games, where the players $O$ and $P$ move concurrently, rather than sequentially, avoid many of the problems present with sequential games; indeed, the authors of \cite{AMConcurrent} obtain a full completeness result for MALL using these concurrent games.
-It is not immediately obvious how to apply the research in this report to concurrent games, nor how to develop the sequoid operator in a concurrent setting.
-One possible approach to the latter problem is to observe that in our category of games we have a natural isomorphism
-\[
-  \G_s(A\sequoid B,C)\cong\G_s(A,B\implies C)
-  \]
-(where $\G_s$ is a category of games and strict strategies) so that $\blank\sequoid B$ is something like a left adjoint to the functor $B\implies\blank$ in the strict subcategory.
-In a general cpo-enriched monoidal category $\C$, we can say that a morphism $f\from X\to Y$ is \emph{strict} if the composition
-\[
-  I\xrightarrow{\emptyplay_X}X\xrightarrow{f}Y = \emptyplay_Y
-  \]
-where $\emptyplay_X$ and $\emptyplay_Y$ are the bottom elements of $\C(I,X)$ and $\C(I,Y)$ respectively.
-
-The eventual goal here will be to develop a sequoidal category of concurrent games and to characterize its internal logic.
-A further direction in this area is to mimic the results in this report in a concurrent setting.
-
-A surprising direction of research is given by the material in Sections \ref{TransSMCCSex} through \ref{ImpliesCnSex}, in particular trying to generalize the construction in Section \ref{DigressionSex} to other categories.
-The situation here is fairly non-standard: we a category (of completely negative games), but we also have all the non-completely negative games that are not objects of the category but still admit morphisms into them.
-We dealt with these objects by using a construction that mimics the traditional slice categories from category theory, but I would be interested to pursue this further and try to develop it in a more general category-theoretic framework.
-It might be worthwhile to study these questions in the context of finitary games, particularly as $A^{\cn}$ has a presentation there in terms of the linear connectives (specifically, $N^{\cn}=N$ if $N$ is negative and $P^{\cn}=\bneggame{P}\implies\bot$ if $P$ is positive).
-
-In Section \ref{DigressionSex} we constructed a category $\tilde{\G}$ whose objects are arbitrary (not necessarily completely negative) games.
-Even in the finitary setting, this poses an obvious question: is this category  $*$-autonomous and can we use it to model fragments of linear logic that we could not model in the completely negative case?
-Of course, there are other obstacles to doing this besides the sign of the games in our category, and the fact that $\tilde{\G}$ is equivalent as a category to $\G$ casts some doubt on whether this is possible, but I would like to explore this direction further.
-
-Another thing that is worth looking into is the effect that removing the limiting condition might have on these games.
-The limiting condition played no great role in our construction of $\G(\alpha)$, though it was crucial in our work on the final sequence.
-Removing the limiting condition might allow certain forms of unbounded non-determinism to be modelled.
-The work done in \cite{LairdOrdinalGames} is connected to this, and it will be instructive to compare the research in this report with Laird's earlier work on transfinite game semantics.
-
-Lastly, there is further technical research to be done into sequoidal categories, such as finding appropriate conditions under which the sequoidal exponential gives rise to a linear exponential comonad or cofree commutative comonoid.
-
-\appendix
-\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
-
-\section{Proofs}
-
-This Appendix contains proofs from the early sections that were omitted from the main body of the text to avoid breaking up the flow.
-
-\subsection{Proof of Proposition \ref{nice-negative-games}}
-\label{nice-negative-games-proof}
-
-We proceed by induction on the length $n$ of $s$.
-If $n=0$ then $s=\emptyplay$ and so $\zeta_A(s\vert_A)=\zeta_A(\emptyplay)=P$ and similarly for $B$, since $A,B$ are negative games.
-Now suppose that $n>0$ - so $s=tm$ for some $t\in P_{A\tensor B},m\in M_{A\tensor B}$.
-By induction, either $t\vert_A=P$ or $t\vert_B=P$, so there are three cases:
-\begin{description}
-  \item[Case 1:] $\zeta_A(t\vert_A)=P$ and $\zeta_B(t\vert_B)=P$.
-Then either $tm\vert_A=t\vert_A$ (if $m$ is a $B$-move) or $tm\vert_B=t\vert_B$ (if $m$ is an $A$-move).
-This proves part (i).
-For part (ii), note that in this case we have $\zeta_{A\tensor B}(t)=P$, so $\zeta_{A\tensor B}(tm)=O$, since $tm$ is alternating.
-If $m$ is an $A$-move, it means that $\zeta_B(tm\vert_B)=\zeta_B(t\vert_B)=P$, so we must have $\zeta_A(tm\vert_A)=O$ by the definition of $\zeta_{A\tensor B}$.
-Then
-    \[
-      \lambda_{A\tensor B}(m)=\lambda_A(m)=\zeta_A(t\vert_Am)=O=\zeta_{A\tensor B}(tm)
-      \]
-    If $m$ is a $B$-move, the argument is similar.
-  \item[Case 2:] $\zeta_A(t\vert_A)=P$ and $\zeta_B(t\vert_B)=O$.
-For part (i), it will suffice to show that $m$ is a $B$-move - so $tm\vert_A=t\vert_A$.
-Indeed, we have $\zeta_{A\tensor B}(t)=O$, so $\zeta_{A\tensor B}(tm)=P$, since $tm$ is alternating with respect to $\zeta_{A\tensor B}$.
-In particular, $\zeta_B(tm\vert_B)=P$, so we must have $tm\vert_B\ne t\vert_B$ and therefore $m$ is a $B$-move.
-For part (ii), we have:
-    \begin{gather*}
-      \lambda_{A\tensor B}(m)=\lambda_B(m)=\zeta_B(t\vert_Bm)=\neg\zeta_B(t\vert_B)=\neg O = P \\
-      \zeta_{A\tensor B}(tm)=\neg\zeta_{A\tensor B}(t)=t = \neg O = P = \lambda_{A\tensor B}
-    \end{gather*}
-  \item[Case 3:] $\zeta_A(t\vert_A)=O$ and $\zeta_B(t\vert_B)=P$.  Similar to Case 2.
-\end{description}
-
-Finally, note that the $\tensor$ result implies the $\implies$ result after writing $A\implies B=\neggame{A}\parr B = \neggame{(A\tensor \neggame{B})}$.
-
-\subsection{Proof of Proposition \ref{alternatingsequenceslemma}}
-\label{alternatingsequenceslemmaproof}
-
-By symmetry, it will suffice to prove that if $\s\vert_{A,B}\in P_{A\implies B}$ and $\s\vert_{B,C}\in P_{B\implies C}$ then $\s\vert_{A,C}\in P_{A\implies C}$.
-If $X,Y$ are negative games, then sequences $t\in P_{X\implies Y}$ are specified by the following properties - $t\vert_X\in P_X$, $t\vert_Y\in P_Y$, if $t$ has even length, then $\zeta_{X\implies Y}(t)=P$ and if $t$ has odd length then $\zeta_{X\implies Y}(t)=O$.
-We need to show that these properties holds if $X=A$, $Y=C$ and $t=\s\vert_{A,C}$.
-
-Certainly, $\s\vert_{A,C}\vert_A=\s\vert_A=\s\vert_{A,B}\vert_A\in P_A$ and similarly $\s\vert_{A,C}\vert_C\in P_C$.
-
-If $\s\vert_{A,C}$ has even length, it means that the lengths of $\s\vert_A$ and $\s\vert_C$ have the same parity, and therefore that the lengths of $\s\vert_{A,B}$ and $\s\vert_{B,C}$ have the same parity.
-Since $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, it follows that $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{B\implies C}(\s\vert_{B,C})$.
-If $\zeta_B(\s\vert_B)=P$ then $\zeta_{A\implies B}(\s\vert_{A,B})=P$ and if $\zeta_B(\s\vert_B)=O$ then $\zeta_{B\implies C}(\s\vert_{B,C})=P$, so we must have $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{B\implies C}(\s\vert_{B,C})=P$.
-By transitivity of $\Rightarrow$, it follows that $\zeta_{A\implies C}(\s\vert_{A,C})=P$.
-
-If $\s\vert_{A,C}$ has odd length, it means that the lengths of $\s\vert_A$ and $\s\vert_C$ has opposite parities and therefore that the lengths of $\s\vert_{A,B}$ and $\s\vert_{B,C}$ have opposite parities.
-So it follows that $\zeta_{A\implies B}(\s\vert_{A,B})=\neg\zeta_{B\implies C}(\s\vert_{B,C})$.
-Suppose that $\zeta_{A\implies B}(\s\vert_{A,B})=O$.
-Then $\zeta_A(\s\vert_A)=P$ and $\zeta_B(\s\vert_B)=O$.
-By Proposition \ref{nice-negative-games} above applied to $\s\vert_{B,C}$, we must have $\zeta_C(\s\vert_C)=O$ and therefore $\zeta_{A\implies C}(\s\vert_{A,C})=(P\Rightarrow O)=O$.
-
-If instead we have $\zeta_{B\implies C}(\s\vert_{B,C})=O$, then $\zeta_B(\s\vert_B)=P$ and $\zeta_C(\s\vert_C)=O$.
-By Proposition \ref{nice-negative-games} applied to $\s\vert_{A,B}$, we must have $\zeta_A(\s\vert_A)=P$ and so $\zeta_{A\implies C}(\s\vert_{A,C})=(P\Rightarrow O) = O$.
-
-\subsection{Proof of Proposition \ref{HylandSchalkFaithful}, Proposition \ref{TransHylandSchalkFaithful}}
-\label{HylandSchalkFaithfulProof}
-
-Our proof is essentially that given in \cite{CalderonMcCusker}.
-Suppose for a contradiction that $\sigma\ne\sigma'$, so without loss of generality there is some $P$-position $s\in\sigma\setminus\sigma'$ (using the definition of a strategy).
-By hypothesis, there is some $s'\in\sigma'$ such that $s'\vert_A=s\vert_A$ and $s'\vert_B=s\vert_B$.
-Clearly, $s\ne s'$, since $s\not\in\sigma'$, so let $r\prefix s$ be the largest common prefix of $s$ and $s'$.
-We therefore have $rx\prefix s,ry\prefix s'$, where $x,y\in M_{A\implies B}$ and $x\ne y$.
-
-Since $s\vert_A=s'\vert_A$ and $s\vert_B=s'\vert_B$, the moves $x$ and $y$ must take place in different games (otherwise we would be forced to have $x=y$).
-They are therefore both $P$-moves.
-Suppose without loss of generality that $x$ is an $A$-move and that $y$ is a $B$-move.
-By hypothesis, there is some $P$-position $t\in\sigma$ such that $t\vert_A=ry\vert_A=r\vert_A$ and $t\vert_B=ry\vert_B=r\vert_By$.
-
-Now clearly $rx\ne t$ (since their restrictions to $A$ and $B$ are different).
-Let $q\prefix rx, t$ be their largest common prefix; then we have $qu\prefix rx, qv\prefix t$ for some $u\ne v$.
-But now since $qu, qv\in\sigma$, $u$ and $v$ must both be $O$-moves, so they must be contained in the same component.
-But this is impossible: if they are both $A$-moves then we have $q\vert_Au\prefix r\vert_A x$ and $q\vert_Av\prefix r\vert_A$, so $u=v$ and if they are both $B$-moves then we have $q\vert_Bu\prefix r\vert_B$ and $q\vert_Bv\prefix r\vert_By$, so $u=v$ again.
-This is a contradiction.
-
-\subsection{Proof of Lemma \ref{LiftingLemma}}
-\label{LiftingLemmaProof}
-
-We prove this by induction on $k$.  There is a unique sequence of length $0$, namely the empty sequence, and its $A$- and $C$-components are both empty, so are prefixes of $s$ and $t$.
-
-Suppose now that $k=1$.
-We make the observation that if $a$ is an $O$-move in $A$ and if $b$ is an $O$-move in $B$ then $a$ is a $P$-move in $A\implies B$ and $b$ is a $P$-move in $B\implies C$.
-Since the starting move in $A\implies B$ or $B\implies C$ must be an $O$-move in both its component game and in the game as a whole, we see that any sequence in $\sigma\|\tau$ must begin with a move in $C$.
-So we have $\s^1=c$, for some $C$-move $c$, and the condition that $\s^1\vert_C\prefix t$ means that $c$ must be the first move in $t$, which is always a move from $C$.
-We have $\s^1\vert_A=\emptyplay\prefix s\vert_A$ and $\s^1\vert_B=\emptyplay\prefix s\vert_B$, as desired.
-
-Now suppose that we have constructed the sequence $\s^k$ for some $k$ such that $1\le k<n$.
-We seek a sequence $\s^{k+1}\in \sigma\|\tau$ of length $k+1$ such that $\s^{k+1}\vert_A\prefix s$ and $\s^{k+1}\vert_C\prefix t$.
-If we write $\s'$ for the sequence obtained by removing the last move in $\s^{k+1}$, it is clear that $\s'\vert_A\prefix s$ and $\s'\vert_C\prefix t$, so $\s'=\s^k$ by uniqueness.
-Therefore, $\s^{k+1}$ is of the form $\s^kx$, for some move $x\in M_A\cprd M_B\cprd M_C$.
-
-Write $\s^k=\s''y$, where $y$ is the last move in $\s^k$.  Our move $x$ will depend on which game $y$ is played on as follows:
-
-\begin{itemize}
-  \item Suppose $y$ is a move in $A$ or an $O$-move in $B$.  By induction, $\s''y\vert_{A,B}$ is a prefix of $s$ ending in $y$.  We claim that it is a proper prefix.
-
-    Indeed, let $b$ be the last $B$-move occurring in $\s''y$ (since play in $A\implies B$ starts with a $B$-move, there must be such a move).
-If $b=y$, then $b$ is an $O$-move in $A\implies B$.
-Otherwise, $y$ must be a move in $A$, and then $b$ is again an $O$-move in $A\implies B$, since player $P$ switches games.
-Therefore, $b$ is a $P$-move in $B\implies C$.
-Now $\s''y\vert_B$ is a prefix of $t$ ending in $b$.
-Since $b$ is a $P$-move in $B\implies C$, it may only be followed in $B\implies C$ by another move from $B$, so there are two possibilities: either $\s''y\vert_{B,C}=t$ or there is some other $B$-move $b'$ that occurs later than $b$ in the sequence $t$.
-In the first case, $\s''y\vert_{A,B}$ must be a proper prefix of $s$ by length considerations:
-    \begin{align*}
-      \length(\s''y\vert_{A,B}) & = \length(\s''y) - \length(\s''y\vert_C) \\
-        & = \length(\s''y) - \length(t\vert_C) \\
-        & = k - \length(t\vert_C) < n - \length(t\vert_C) = \length(s)
-    \end{align*}
-    while in the second case $\s''y\vert_B$ must be a proper prefix of $t\vert_B=s\vert_B$, and so $\s''y\vert_{A,B}$ must be a proper prefix of $s$.
-
-    Therefore, we have $\s''y\vert_{A,B}x\prefix s$ for some move $x\in M_A\cprd M_B$.
-If $x$ is an $A$-move then $\s''yx\vert_{B,C}=\s''y\vert_{B,C}\prefix t$, as desired.
-If $x$ is a move in $B$, then it must be a $P$-move in $A\implies B$ (since $y$ is either a move in $A$ or an $O$-move in $B$), so it is an $O$-move in $B\implies C$.
-Since $s\vert_B=t\vert_B$, we must have $\s''yx\vert_B\prefix t\vert_B$, and so $y$ must be a $P$-move in $B\implies C$, and should therefore be followed by another move in $B$, which must be $x$.
-Therefore, $\s''yx\vert_{B,C}\prefix t$.
-
-    For uniqueness, suppose that $\s''yz\in\sigma\|\tau$ is such that $\s''yz\vert_A\prefix s\vert_A$ and $\s''yz\vert_C\prefix t\vert_C$.
-As before, let $b$ be the last $B$-move occurring in $\s''y$; we have already shown that $b$ must be a $P$-move in $B\implies C$, and it follows that it must be the last move occurring in $\s''y\vert_{B,C}$ (since it can only be followed by another $B$-move).
-Suppose that $z\in M_B\cprd M_C$.
-Then $\s''yz\vert_{B,C}=\s''y\vert_{B,C}z$; since the last move in $\s''y\vert_{B,C}$ is $b$, this means that $z$ must be an $O$-move in $B$.
-So $z$ is either an $O$-move in $B$ or a move in $A$.
-
-    If $y$ was an $O$-move in $A$, then $y$ is a $P$-move in $A\implies B$, so it must be followed in $A\implies B$ by another move from $A$.
-Then the condition that $\s''yz\vert_A\prefix s\vert_A$ tells us that $z=x$.
-If instead $y$ was a $P$-move in $A$ or a move in $B$ then $y$ is an $O$-move in $A\implies B$; now, since we have $\s''y\vert_{A,B}z,\s''y\vert_{A,B}x\in\sigma$, it must be the case that $x=z$ by the definition of a strategy.
-
-  \item If instead $y$ is a move in $C$ or a $P$-move in $B$, we use a symmetrical argument, choosing $x$ to be the next move along in $t$.
-We need to take a little extra care here when we talk about the last $B$-move in $\s''y$; there may in fact be no $B$-moves in $\s''y$.
-Since any play in $A\implies B$ must begin with a $B$-move, this only happens when $\s''y$ is entirely made up of $C$-moves.
-In this case, it is not difficult to show that $\s''y\vert_{B,C}$ is a proper prefix of $t$ by length considerations.
-\qedhere
-\end{itemize}
-
-\subsection{Proof of Proposition \ref{CompWinningIsWinning}}
-\label{CompWinningIsWinningProof}
-
-First, we want to show that $\comp\tau\sigma$ is a total strategy.  Let $s\in\comp\tau\sigma$ be an $O$-position; then we have some $\s\in\sigma\|\tau$ with $\s\vert_{A,C}=s$.
-
-We claim that there is a maximal such $\s$.
-By Lemma \ref{LiftingLemma}, $\s$ is determined by its length, and so the only way that there could not be a maximal such $\s$ is if there is some infinite sequence $\S\in(M_A\cprd M_B\cprd M_C)^\omega$ with $\S\vert_{A,B}\in\sigma\cup\sigma^\omega$, $\S\vert_{B,C}\in\tau\cup\tau^\omega$ and $\S\vert_{A,C}=s$.
-Since $\S$ has some finite prefix $\s$ with $\s\vert_{A,C}=s$, $\S\vert_A$ and $\S\vert_C$ must both be finite, so they are $O$-plays in the games $A\implies B$ and $B\implies C$ respectively.
-
-Now $\S\vert_B$ is infinite.
-If $W_B(\S\vert_B)=O$, then $W_{A\implies B}(\S\vert_{A,B})=O$, contradicting the fact that $\sigma$ is a winning strategy.
-Symmetrically, if $W_B(\S\vert_B)=P$, then $W_{B\implies C}(\S\vert_{B,C})=O$, contradicting the fact that $\tau$ is a winning strategy.
-We have a contradiction in either case, so if $\sigma$ and $\tau$ are indeed winning strategies, there must be a maximal (finite) $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-
-The argument from Proposition \ref{BoundedTotalComposition} now applies, showing that $sx\in\comp\tau\sigma$ for some $P$-move $x$.
-
-Lastly, we want to show that any infinite play in $\comp\tau\sigma$ is $P$-winning.
-Suppose $s$ is some infinite play in $\comp\tau\sigma$.
-For each finite prefix $t\prefix s$ there is some $\t\in\sigma\|\tau$ with $\t\vert_{A,C}=t$, and by Lemma \ref{LiftingLemma}, we have $\t'\prefix\t$ if $t'\prefix t$.
-Therefore, these $\t$ glue to give an infinite sequence $\s\in(M_A\cprd M_B\cprd M_C)^\omega$ such that $\s\vert_{A,B}\in\sigma^\omega$ and $\s\vert_{B,C}\in\tau^\omega$.
-We claim that $W_{A\implies B}^*(\s\vert_{A,B})=W_{B\implies C}^*(\s\vert_{B,C})=P$ - then it follows that $W_{A\implies C}^*(\s\vert_{A,C})=P$ by transitivity of $\Rightarrow$.
-If $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both infinite, then this is automatically true, since $\sigma$ and $\tau$ are winning strategies.
-Otherwise, one of them must be infinite and the other finite.
-
-Suppose that $\s\vert_{A,B}$ is finite.
-Let $\t$ be the shortest finite prefix of $\s$ with $\t\vert_{A,B}=\s\vert_{A,B}$; then we have $\t c\prefix \s$ for some move $c\in M_C$.
-If $\t\vert_{A,B}=\emptyplay$, then $W_A^*(\t\vert_{A,B})=P$ since $A$ and $B$ are negative.
-Otherwise, there is at least one $B$-move in $\t\vert_{A,B}$.
-Let $b$ be the last $B$-move occurring in $\t\vert_{A,B}$ - then it is the last $B$-move occurring in $\t\vert_{B,C}$; since it is followed by the move $c$, it must be an $O$-move in $B\implies C$ and therefore a $P$-move in $B$.
-Therefore, $W_{A\implies B}^*(\s\vert_{A,B})=P$.
-
-If instead $\s\vert_{B,C}$ is finite, once again we have some $\t\prefix\s$ with $\t\vert_{A,B}=\s\vert_{A,B}$ and $\t a\prefix\s$ for some move $a\in M_A$.
-Since $\s\vert_{A,B}$ is infinite, it must be non-empty, so it must contain some $B$-move.
-Let $b$ be the last $B$-move occurring in $\s\vert_{A,B}$; since $b$ is followed by an $A$-move, it must be an $O$-move in $B$.
-Now $b$ is also the last $B$-move occurring in $\s\vert_{B,C}$ and so $W_{B\implies C}^*(\s\vert_{B,C})=P$.
-
 \section{Weakenings}
-
-This appendix contains material that I developed earlier in the year.
-The material was originally intended to be applied to the study of the final sequence (the idea is that if $\gamma<\delta$ then $A^{\sequoid\gamma}$ is a (lax) weakening of $A^{\sequoid\delta}$ and to use these results to prove that the sequence stabilizes.
-Since we have obtained this result by another method, this material is not directly applicable to the final sequence any more, but it is of interest in its own right and links in with work by Juliusz Chroboczek on subtyping \cite{juliuszthesis}.
-
-\subsection{Weakenings}
 
@@
 
-    We wish to show that $\comp\wk\str=\id_{A'}$.  We shall show that $\comp{\grel\wk}{\grel\str}=\Delta_{P_{A'}}$ in $\Rel$.
+    We wish to show that $\comp\wk\str=\id_{A'}$.  In the style of section \ref{hylandschalke}, we shall show that $\comp{\grel\wk}{\grel\str}=\Delta_{P_{A'}}$ in $\Rel$.
 
@@
 
-\subsection{The weakening monad of a game}
-
-\subsubsection{Weakening pullback of a game}
+\section{The weakening monad of a game}
+
+\subsection{Weakening pullback of a game}
 
@@
 
-\subsection{Lax weakening morphisms}
+\section{Lax weakening morphisms}
 
@@
 
-\bibliographystyle{alpha}
-\bibliography{ordinal_games}
-
 \end{document}

### 2016-10-11 ordinal_games/weakenings/weakenings.tex
Started Research repository

--- 2016-10-11 ordinal_games/split-epimorphisms/split-epimorphisms.tex
@@
 \newcommand{\Sch}{\catname{Sch}}
-\newcommand{\Rel}{\catname{Rel}}
 \newcommand{\Mod}[1][]{\ifthenelse{\isempty{#1}}{\catname{Mod}}{#1\catname{mod}}}
@@
 \newcommand{\OP}{\{O,P\}}
-\newcommand{\F}{\mathcal F}
 \renewcommand{\L}{\mathcal L}
-\DeclareMathOperator{\wk}{wk}
-\DeclareMathOperator{\str}{str}
-\newcommand{\s}{\mathfrak{s}}
-\renewcommand{\t}{\mathfrak{t}}
 
@@
 
-Let $A=(M_A,\lambda_A,P_A)$ be a game.  Then we have two notions of a \emph{weakening} of $A$ - informally, a game that is \emph{easier} than $A$, from the player $P$'s point of view.
+Let $A=(M_A,\lambda_A,P_A)$ be an Abramsky-Jagadeesan game.
+We give two different notions of a \emph{weakening} of $A$ (informally, a game that is `easier' than $A$ from the point of view of Player $P$):
 
 \begin{enumerate}
-  \item An \emph{antecedent weakening} of $A$ is a game $A'=(M_A,\lambda_A,P_{A'})$, where $P_{A'}\subset P_{A}$ such that for every $O$-play $s$ occuring in both $P_A$ and $P_{A'}$, the set of $P$-responses to $s$ in $A'$ is precisely the set of $P$-responses to $s$ in $A$ and for every $P$-play $t$ occurring in both $P_A$ and $P_{A'}$, the set of $O$-responses to $t$ in $A'$ is a subset of the set of $O$-responses to $t$ in $A$.
-  \item A \emph{precedent strengthening} of $A$ is a game $A''=(M_A,\lambda_A,P_{A''})$ where $P_A\subset P_{A''}$ such that for every $O$-play $s$ occuring in both $P_A$ and $P_{A''}$, the set of player responses to $s$ in $A$ is a subset of the set of $P$-responses to $s$ in $A''$, and such that for every $P$-play $t$ occuring in both $P_A$ and $P_{A''}$ the set of $O$-responses to $t$ in $A$ is precisely the set of $O$-responses to $t$ in $A''$.
+  \item We call a game $B=(M_B,\lambda_B,P_B)$ an \emph{antecedent weakening} if $M_B=M_A$, $\lambda_B=\lambda_A$ and $P_B\subset P_A$ such that whenever is is Player $P$'s turn to move in $B$, she has all the options available that she had in $A$:
+
+    For all $s\in P_B$ ending in an $O$-move, and for all $a\in M_A$ such that $sa\in P_A$, we have $sa\in P_B$.
+
+  \item We call a game $C=(M_C,\lambda_C,P_C)$ a \emph{precedent strengthening} if $M_C=M_A$, $\lambda_C=\lambda_A$ and $P_A\subset P_C$ such that for any $P$-play in $C$ that also occurred in $A$,
+
 \end{enumerate}
 
-In other words, a precedent strengthening of $A$ is a game in which the player has more choices at each move, but the opponent has the same choices, while an antecedent weakening of $A$ is a game in which the player has the same choices at each move, but the opponent has fewer choices.
-
-The important fact about both these types of weakening is that we have copycat morphisms $A\to A',A\to A''$.
-
-From here on, we will use the term \emph{weakening} to refer to an antecedent weakening.  If $A'$ is a weakening of $A$, we will write $\cmap{\wk}{A}{A'}$ for the copycat morphism.
-
-\begin{proposition}
-  Let $A'$ be a weakening of $A$.  Then $\cmap{\wk}{A}{A'}$ has a right inverse.
-
-  \begin{proof}
-    The inverse for $\wk$ is the partial strategy $\cmap{\str}{A'}{A}$.
-This is also constructed as a copycat strategy; the only difference is that if $O$ makes a move in $A$ that does not occur in $P_{A'}$ then the player $P$ has no reply.
-We now claim that $\comp\wk\str=\id_{A'}$.
-
-    Formally:
-    \begin{IEEEeqnarray*}{rCl}
-      \wk & = & \left\{s\in P_{A\implies A'}\suchthat\textrm{if $|s|$ is even, then $s\vert_A=s\vert_{A'}$}\right\} \\
-      \str & = & \left\{s\in P_{A'\implies A}\suchthat\textrm{if $|s|$ is even, then $s\vert_A'=s\vert_{A}$}\right\}
-    \end{IEEEeqnarray*}
-
-    To show that $\comp\wk\str=\id_{A'}$, it suffices to show that player $P$'s response, under $\comp\wk\str$, to an $O$-move in the left-hand copy of $A'$ is to copy that move into the right-hand copy of $A'$ and that her response to an $O$-move in the right hand copy is to copy that move into the left hand copy.
-This is fairly straightforward to show inductively, using the narrative definition of composition: if $O$ makes a move in the left-hand copy of $A'$, then Player $P$'s response under $\str$ is to copy that move across into $A$.
-Then, by $\wk$, Player $P$ copies the move over into the right-hand copy of $A'$, completing her move.
-
-    To go in the other direction, if Player $O$ plays in the right hand copy of $A'$, then Player $P$'s response under $\wk$ is to copy that move into $A$.
-Now, since that move came from $A'$ originally, she is able to copy it over into the left-hand copy of $A'$.
-Therefore, Player $P$'s overall strategy is the copycat strategy on $A'$.
-  \end{proof}
-
-\end{proposition}
-
-We now show that is in fact a characterization of weakenings, in the sense that every strategy with a right inverse is \emph{equivalent} to some weakening strategy.
-
-Explicitly:
-
-\begin{proposition}
-  If a morphism $\cmap{\sigma}{A}{B}$ has a right inverse, then there is a weakening $A'$ of $A$ and an isomorphism $\cmap{\hat{\sigma}}{A'}{B}$ such that
-    \[
-    \begin{tikzcd}
-      A \arrow[r, "\sigma"] \arrow[dr, "\wk"']
-        & B \arrow[d, leftarrow, "\rotatebox{90}{\(\sim\)}"', "\hat{\sigma}"] \\
-      %
-        & A'
-    \end{tikzcd}
-    \]
-    commutes.
-
-    \begin{proof}
-      Let $\cmap{\sigma}{A}{B}$ be a morphism of games and suppose that $\sigma$ has a right inverse $\tau$ - so $\comp\sigma\tau=\id_B$.  Define
-      \[
-        P_{A'}=\{\s\vert_A\suchthat \s\in\sigma\}
-        \]
-      $P_{A'}$ is clearly prefix-closed, so $A'=(M_A,\lambda_A,P_{A'})$ is a well-defined game.
-
-      We claim that $A'$ is a weakening of $A$.
-It will suffice to show that if $s\in P_{A'}$ is an $O$-play and $sa\in P_A$ is a $P$-reply, then $sa\in P_{A'}$ (the other conditions follow automatically from the fact that $P_{A'}\subset P_A$).
-
-      Let $s\in P_{A'}$ be an $O$-play.
-By the definition of $P_{A'}$, there exists $\s\in \sigma$ such that $\s\vert_A=s$.
-We may choose $\s$ minimal, so that the last move made in $\s$ corresponds to the last move played in $s$.
-This last move was an $O$-move in $A$, so it is a $P$-move in $A\implies B$.
-This means that $\s$ is a $P$-play, and so $\s a\in \sigma$, since $\tau$ is a strategy.
-Therefore, $\s a\vert_A=sa$, and so $sa\in P_{A'}$.
-
-      We now define strategies $\cmap{\hat\sigma}{A'}{B}, \cmap{\hat\tau}{B}{A'}$, given as sets of plays by:
-      \begin{align*}
-        \hat\sigma & = \sigma \\
-        \hat\tau & = \tau \cap P_{B\implies A'}
-      \end{align*}
-      $\hat\tau$ is clearly a valid strategy for $B\implies A'$, and $\hat\sigma$ is a valid strategy for $A'\implies B$ by the definition of $P_{A'}$.
-
-      We claim that $\sigma$ and $\tau$ are inverses and that the diagram given above commutes.
-
-      Since $\comp\sigma\tau=\id_B$, to show that $\comp{\hat\sigma}{\hat\tau}=\id_B$, it suffices to show that $\comp\sigma\tau=\id_B=\comp{\hat\sigma}{\hat\tau}$.  We have
-      \begin{align*}
-        \comp\sigma\tau & = \{\s\vert_{B,B}\suchthat \s\in \L(B,A,B), \s\vert_{B,A}\in\tau,\s\vert_{A,B}\in\sigma\} \\
-        \comp{\hat\sigma}{\hat\tau} & = \{\s\vert_{B,B}\suchthat \s\in \L(B,A',B), \s\vert_{B,A'}\in\hat\tau,\s\vert_{A',B}\in\hat\sigma\}
-      \end{align*}
-
-      Since $\hat\tau\subset\tau$ and $\hat\sigma=\sigma$ as sets of plays, it is clear that $\comp{\hat\sigma}{\hat\tau}\subset\comp\sigma\tau$.
-Going in the other direction, suppose $\s\in\L(B,A',B)$ is such that $\s\vert_{B,A}\in\tau$ and $\s\vert_{A,B}\in\sigma$.
-Then, by definition,
-      \[
-        \s\vert_A=\s\vert_{A,B}\vert_A\in P_{A'}
-        \]
-      and so $\s\in\L(B,A',B)$ and $\s\vert_{B,A}\in P_{B\implies A'}$, which implies that $\s\vert_{B,A}\in\hat\tau$.
-So $\comp\sigma\tau\subset\comp{\hat\sigma}{\hat\tau}$, and therefore $\comp{\hat\sigma}{\hat\tau}=\comp\sigma\tau=\id_B$.
-    \end{proof}
-\end{proposition}
-
 \end{document}

### 2016-10-11 CN/alterimage.m

@@ -1,0 +1,36 @@
+[DC, map] = imread("dc.png");
+DC = double(ind2rgb(DC,map));
+DC = 1 .- DC;
+DC_size = size(DC);
+
+DC_row = reshape(DC, [], 3).';
+
+colours = [0, 0, 0;
+           111, 156, 101;
+           0, 0, 510];
+
+colours = colours';
+colours = (255 .- colours) ./ 255;
+
+colours2 = [0, 0, 0;
+           199, 199, 160;
+           0, 510, 0];
+
+colours2 = colours2';
+colours2 = (255 .- colours2) ./ 255;
+
+PROJ13 = [1, 0, 0;
+          0, 0, 0;
+          0, 0, 1];
+
+combined_matrix1 = colours * PROJ13 * inv(colours);
+combined_matrix2 = colours2 * PROJ13 * inv(colours2);
+
+combined_matrix = combined_matrix2 * combined_matrix1;
+
+new_row = combined_matrix * DC_row;
+
+new_image = reshape(new_row.', DC_size);
+new_image = 1 .- new_image;
+
+imwrite(new_image, "altered_dc.png");

### 2016-10-11 old/1/ordinal_games.tex
Started writing paper.

\documentclass[11pt]{article} % use larger type; default would be 10pt

\usepackage[utf8]{inputenc}

\usepackage{graphicx} % support the \includegraphics command and options

\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{mathtools} % for the all important \coloneqq symbol
\usepackage{url} % for \url
\usepackage{IEEEtrantools} % for \IEEEeqnarray

%%% ToC (table of contents) APPEARANCE
\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%% Font things %%
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{mathtools}
\usepackage{cmll} % Linear logic symbols!

%% Lists %%
\usepackage{enumerate}

%% Graphics %%
\usepackage{tikz}
\usetikzlibrary{cd}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}

%% Theorems! %%
\usepackage{amsthm}
\theoremstyle{plain} % Theorems, lemmas, propositions etc.
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{construction}[theorem]{Construction}
\theoremstyle{definition} % Definitions etc.  Remarks too, because I don't like the way the 'remark' style looks.
\newtheorem{definition}[theorem]{Definition}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

%% Exercises and answers %%
\usepackage{answers}

\newtheoremstyle{exercisestyle}% name
  {6pt}   % ABOVESPACE
  {6pt}   % BELOWSPACE
  {\itshape}  % BODYFONT
  {0pt}       % INDENT (empty value is the same as 0pt)
  {\bfseries} % HEADFONT
  {.}         % HEADPUNCT
  {3pt} % HEADSPACE
  {}          % CUSTOM-HEAD-SPEC

\theoremstyle{exercisestyle}
\newtheorem{exercise}{Exercise}
\newtheorem{answerthm}{Exercise}

\Newassociation{answer}{answerthm}{answers}
\newcommand{\answerthmparams}{}

%% Changes to enumerate things so they look better %%

\makeatletter
\def\enumfix{%
\if@inlabel
 \noindent \par\nobreak\vskip-\topsep\hrule\@height\z@
\fi}

\let\olditemize\itemize
\def\itemize{\enumfix\olditemize}
\let\oldenumerate\enumerate
\def\enumerate{\enumfix\oldenumerate}

%% Random crap %%
\usepackage{xifthen}

\makeatletter
\def\thm@space@setup{%
  \thm@preskip=\parskip \thm@postskip=0pt
}
\makeatother

\makeatletter
\newcommand*{\relrelbarsep}{.386ex}
\newcommand*{\relrelbar}{%
  \mathrel{%
    \mathpalette\@relrelbar\relrelbarsep
  }%
}
\newcommand*{\@relrelbar}[2]{%
  \raise#2\hbox to 0pt{$\m@th#1\relbar$\hss}%
  \lower#2\hbox{$\m@th#1\relbar$}%
}
\providecommand*{\rightrightarrowsfill@}{%
  \arrowfill@\relrelbar\relrelbar\rightrightarrows
}
\providecommand*{\leftleftarrowsfill@}{%
  \arrowfill@\leftleftarrows\relrelbar\relrelbar
}
\providecommand*{\xrightrightarrows}[2][]{%
  \ext@arrow 0359\rightrightarrowsfill@{#1}{#2}%
}
\providecommand*{\xleftleftarrows}[2][]{%
  \ext@arrow 3095\leftleftarrowsfill@{#1}{#2}%
}
\makeatother

\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\Rings}{\catname{CRing}}
\newcommand{\CAT}{\catname{CAT}}
\newcommand{\Top}{\catname{Top}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Cont}{\catname{Cont}}
\newcommand{\Sch}{\catname{Sch}}
\newcommand{\Mod}[1][]{\ifthenelse{\isempty{#1}}{\catname{Mod}}{#1\catname{mod}}}
\DeclareMathOperator{\sh}{Sh}
\newcommand{\Sh}[1][]{\ifthenelse{\isempty{#1}}{\sh}{\sh(#1)}}
\newcommand{\map}[3]{#2\xrightarrow{#1} #3}
\newcommand*\from{\colon}
\newcommand{\cmap}[3]{#1\from{}#2\to{}#3}
\newcommand\oppcat[1]{#1^{\mathrm{op}}}
\DeclareRobustCommand{\vmap}[3] {\begin{tikzcd} #2 \arrow[d, "#1"] \\ #3 \end{tikzcd}}
\newcommand{\partref}[1]{(\ref{#1})}
\newcommand{\intgrpd}[4] {#1 \xrightrightarrows[#3]{#4} #2}
\DeclareRobustCommand{\bigintgrpd}[4] {\begin{tikzcd}[ampersand replacement=\&] #1 \arrow[r, shift left=0.5ex, "#3"] \arrow[r, shift right=0.5ex, "#4"'] \& #2 \end{tikzcd}}

\usepackage{xspace}

\newcommand{\etale}{\'{e}tale\xspace}
\newcommand{\Etale}{\'{E}tale\xspace}

\def \inv {^{-1}}

\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\op}{op}
\DeclareMathOperator{\pr}{pr}
\DeclareMathOperator{\pre}{{pre}}
\DeclareMathOperator{\et}{{\acute{e}t}}

\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Spec}{Spec}

\DeclareMathOperator{\ol}{ol}

\def\presuper#1#2%
  {\mathop{}%
   \mathopen{\vphantom{#2}}^{#1}%
   \kern-\scriptspace%
   #2}
\def\presub#1#2%
  {\mathop{}%
   \mathopen{\vphantom{#2}}_{#1}%
   \kern-\scriptspace%
   #2}

%% Our things %%

\newcommand{\neggame}[1]{\presuper{\perp}{#1}}
\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\newcommand{\varsequoid}{\vartriangleleft}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#1 \circ #2}
\newcommand{\cprd}{\sqcup}
\newcommand{\G}{\mathcal G}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\renewcommand{\L}{\mathcal L}
\newcommand{\s}{\mathfrak s}
\renewcommand{\t}{\mathfrak t}

%%% END Article customizations

\begin{document}

\section{Abramsky-Jagadeesan games: a review}
\label{abjagreview}

\subsection{Games and strategies}

We use the definition of games found $\otimes$ in \cite{martinsthesis}, which is essentially that of \cite{blassgames} and \cite{abramskyjagadeesangames}.

\begin{definition}
  A \emph{game} $A$ is a tuple
  \[
    (M_A, \lambda_A, b_A, P_A)
  \]
  where
  \begin{itemize}
    \item $M_A$ is a set of moves.
    \item $\cmap{\lambda_A}{M_A}{\{O,P\}}$ is a function designating each move as a $P$-move or an $O$-move.
    \item $b_A\in\{O,P\}$ specifies a starting player.
    \item $P_A\subset M_A^*$ is a prefix-closed set of legal plays in the game such that $P$-moves and $O$-moves alternate.
  \end{itemize}
\end{definition}

\begin{notation}
  If $b_A=P$, we say that $A$ is a \emph{positive game}, and if $b_A=O$, we say that $A$ is a \emph{negative game}.

  Given $n\in\mathbb N$, write $P_A(n)$ for the set of plays in $P_A$ of length $n$.

  We shall define a function $\cmap{\zeta_A}{P_A}{\{O,P\}}$ by setting $\zeta_A(s)=O$ if $s$ ends in an $O$-move and $\zeta_A(s)=P$ if $s$ ends in a $P$-move.   $\zeta_A$ then tells us which player played last, or who is responsible for the current state of the game.  If $\zeta_A(s)=O$, we say that $s$ is an \emph{$O$-play}; if $\zeta_A(s)=P$, we say that $s$ is a \emph{$P$-play}.

  We write $\epsilon$ for the empty sequence in $M_A^*$.
\end{notation}

We now give a definition of a (player) strategy for a game.  A strategy can be thought of as a partial function from $O$-plays to $P$-moves, telling the player which move to play in a particular position.  We follow \cite{abramskyjagadeesangames} and others in presenting a strategy as the game-tree of the positions that can be obtained by following the strategy; our presentation, which is that of \cite{abramskyjagadeesangames},  differs slightly from that in \cite{martinsthesis} in that our strategies contain all $O$-plays and $P$-plays that arise, rather than the $P$-plays on their own.  The two definitions are clearly equivalent, but ours will generalize more readily later on.

\begin{definition}
  Let $A$ be a game.  A \emph{strategy} for $A$ is a prefix-closed subset $\sigma\subset P_A$ such that:
  \begin{itemize}
    \item $\sigma$ contains at most one $P$-reply to any $O$-play.  I.e., if $s\in\sigma$ is an $O$-play and $a,b$ are $P$-moves such that $sa,sb\in\sigma$, then $a=b$.
    \item $\sigma$ contains all $O$-replies to $P$-plays.  I.e., if $s\in\sigma$ is a $P$-play and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.  
    \item $\epsilon\in\sigma$.
  \end{itemize}

  We say the strategy $\sigma$ is \emph{total} if it is non-empty and contains $P$-replies to all its $O$-plays; i.e., if $s\in\sigma$ is an $O$-play then there is some (necessarily unique) $P$-move $a$ such that $sa\in\sigma$.
\end{definition}

\subsection{Connectives on games}

\subsubsection{Negation}

If $A$ is any game, we write $\neggame{A}$ for the game obtained by switching the roles of $O$ and $P$.  In particular, if $P$ is a positive game then $\neggame P$ will be a negative game, and if $N$ is a negative game then $\neggame N$ will be a positive game.

Officially:
\[
  \neggame A = (M_A, \neg\circ\lambda_A, \neg b_A, P_A)
\]
where $\cmap{\neg}{\{O,P\}}{\{O,P\}}$ switches $O$ and $P$.

\subsubsection{Tensor and implies}
Our main recipe for combining two games into one will be playing games in parallel.  This means that we set up copies of each game side by side and a starting player, and on each go the player whose turn it is may choose to play in either game, so long as their move makes a valid play in that game.

Let us see what this means in practice:

\begin{itemize}
  \item If $M,N$ are negative games, then the negative game obtained by playing $M,N$ in parallel is called the \emph{tensor product} $M\tensor N$.  Observe that player $P$ is forced to play in whichever game player $O$ has just played in (since the only moves available in the other game are $O$-moves), but that player $O$ may play in either game when it is his turn.
  \item There is a dual to the tensor product.  If $P,Q$ are positive games, then the positive game obtained by playing $P,Q$ in parallel is called the \emph{par} $P\parr Q$.  In this game, it is player $P$ who may play in either of the two games when it is her turn, while player $O$ is restricted to playing in whichever game player $P$ has just played in.
  \item Now suppose that $P$ is a positive game and that $N$ is a negative game.  In order to play these two games in parallel, we must be careful to choose a starting player.  Let us suppose for now that $O$ starts.  Then $O$ must make the first move in the game $N$.  Thereafter, it is $P$ who may choose which game to make her next move in, while $O$ must play in whichever game $P$ has just played in.

  The case we are most interested in is when the game $P$ is the negation $\neggame M$ of some negative game $M$.  Then the negative game obtained by playing $\neggame M$ and $N$ in parallel is called the \emph{implication} of $N$ from $M$, and is written $M\implies N$.  
\end{itemize}

\begin{exercise}
  Suppose $M,N$ are negative games and suppose that player $P$ has strategies for the games $M$ and $M\implies N$.  Show how she may combine these strategies to obtain a strategy for the game $N$.
\end{exercise}

We shall now give a formal definition of playing two games in parallel.

\begin{notation}
  Let $X,Y$ be sets.  If $s\in(X\cprd Y)^*$ is any sequence made up of terms from both $X$ and $Y$ then we write $s\vert_X$ for the subsequence of $s$ made up of all those terms that came from $X$ and $s\vert_Y$ for the subsequence of $s$ made up of all those terms that came from $Y$.

  Now suppose $S\subset X^*$ is a set of sequences of elements of $X$ and that $T\subset Y^*$ is a set of sequences of elements of $Y$.  We write $S\|T$ for the subset of $(X\cprd Y)^*$ made up of those sequences $s$ such that $s\vert_X\in S$ and $s\vert_Y\in T$.  
\end{notation}

\begin{definition}
  Let $A,B$ be games, and let $b\in\{O,P\}$ be a choice of starting player.

  The \emph{game with starting player $b$ obtained by playing $A$,$B$ in parallel} is given by
  \[
    A\|_bB=(M_A\cprd M_B,\lambda_A\cprd\lambda_B,b,(P_A\|P_B)\cap M_{A\|_bB}^\circledast)
  \]

  Here, $M_{A\|_bB}^\circledast$ is the set of all sequences $s\in(M_A\cprd M_B)^*$ that start with a $b$-move and thereafter alternate $O$-moves and $P$-moves.

  If $M,N$ are negative games, we write $M\tensor N$ for $M\|_ON$.

  If $P,Q$ are positive games, we write $P\parr Q$ for $P\|_PQ$.

  If $M,N$ are negative games, we write $M\implies N$ for $N\|_O\neggame M$.
\end{definition}

\subsubsection{Sequoid}

If $A,B$ are games, then the we can weaken the game $A\|_bB$ by requiring that the starting player $b$ play the first move in game $A$.  In this case, we must have $b=b_A$, or the resulting game has no legal plays at all.  For this reason, we may suppress mention of the starting player $b$ in our notation.

\begin{definition}
  We use the notation from \cite{martinsthesis}.  If $X,Y$ are sets and $S\subset X^*, T\subset Y^*$ then we write $S\|_LT\subset S\|T$ for the set of all sequences $s\in S\|T$ that are either empty or have their first term in $S$.  Then we define
  \[
    A\llfloor B = (M_A\cprd M_B,\lambda_A\cprd\lambda_B,b_A,P_A\|_LP_B)
  \]

  The starting player $b_B$ for the game $B$ is then the player who has the ability to switch games, while the other player must play in whichever game their opponent has just played in.  If $b_B=O$ then we write $A\sequoid B$ for $A\llfloor B$ and if $b_B=P$ then we write $A\varsequoid B$ for $A\llfloor B$.

  In particular, if $M,N$ are negative games, then $M\sequoid N$ is the weakening of the tensor $M\tensor N$ in which player $O$ is forced to make his first move in the game $M$.  
\end{definition}

\subsection{Categorical Semantics}
\label{abjag-categorical-semantics}

We build a category $\mathcal G$ whose objects are negative games.  If $M,N$ are negative games, then the morphisms $M\to N$ will be strategies for $M\implies N$.

\subsubsection{Identity morphisms}

Let $N$ be a negative game.  Then $N\implies N$ is given by the games $N$ and $\neggame N$ played in parallel, with player $P$ switching games.  The identity morphism $N\to N$ is the \emph{copycat strategy}:
\begin{itemize}
  \item $O$ makes a move in $N$.
  \item $P$ plays that move in $\neggame N$.
  \item $O$ replies to the move in $\neggame N$.
  \item $P$ plays $O$'s reply in $N$.
  \item ... and so on.
\end{itemize}

This strategy is total, since $P$ always has a reply to $O$'s move (play that move in the other game).

\subsection{Composition of morphisms}

Suppose $L,M,N$ are negative games and we have strategies $\sigma$ for $L\implies M$ and $\tau$ for $M\implies N$.  We want to be able to compose these strategies to give us a strategy $\comp\tau\sigma$ for $L\implies N$.

Let us put ourselves in the position of player $P$.  We need to know which move she makes in response to each opponent move.  Player $P$ first of all sets up the games $L\implies M$ and $M\implies N$ side by side.  The rough idea is that she can use the strategy $\sigma$ on the left hand side and the strategy $\tau$ on the right hand side, while playing the copies of $M$ and $\neggame M$ against each other in order to obtain plays in $L\implies N$.  Let us look at this a bit more closely.

We are playing in the game $L\implies N$.
\begin{itemize}
  \item $O$ must make his first move in the game $N$.
  \item $P$ copies this move as the first move in her copy of $M\implies N$.
  \item $P$ now uses the strategy $\tau$ for $M\implies N$ to reply to $O$'s move, within the game $M\implies N$.  If her reply is in the game $N$, then she copies her reply over to $L\implies N$, and play continues.
  \item Otherwise, her reply is in the game $\neggame M$.  In that case, she copies that move over as the first move in her copy of $L\implies M$.  
  \item She then uses her strategy $\sigma$ to reply to that move in $L\implies M$.  If her reply is in the game $\neggame L$, then she makes that play in the game $L\implies N$, and play continues with the next opponent move.
  \item Otherwise, her reply is in the game $M$.  She copies that move over to $M\implies N$ and replies to it using $\tau$.  
  \item She continues in this way until she makes a play either in $\neggame L$ or in $N$.  The then waits for $O$'s response, and replies to that in the same way.
\end{itemize}

There is a chance that $P$ ends up switching back and forth between the copies of $M$ and $\neggame M$ forever, and never makes her reply to $O$, even if the strategies $\sigma$ and $\tau$ were total.  For this reason, the composition of total strategies need not be total, and so we must deal with general strategies in this games model.  We shall shortly consider ways to get around this.

\begin{definition}
  Let $L,M,N$ be games.  Let
  \[
    \L(L,M,N)\subset (L\cprd M\cprd N)^*
  \]
  denote the set of all sequences $s\in(L\cprd M\cprd N)^*$ such that $L$-moves and $N$-moves never occur at adjacent positions of $s$.

  Now let $\cmap{\sigma}{L}{M},\cmap{\tau}{M}{N}$ be strategies.  Define
  \[
    \tau\|\sigma=\{s\in\L(L,M,N)\colon s\vert_{L,M}\in\sigma, s\vert_{M,N}\in \tau\}
  \]

  $\tau\|\sigma$ is the set of all plays that occur when $P$ plays in $L\implies M$ according to $\sigma$ and in $M\implies N$ according to $\tau$, identifying the moves in $M$ in the two games.  The condition that $L$-moves and $N$-moves are never adjacent reflects this: player $P$ never moves directly from an $L$-move to an $N$-move or vice versa without putting a move in $M$ in between.

  We can recover the composed strategy $\comp\tau\sigma$ for $L\implies N$ by forgetting the moves in $M$:
  \[
    \tau\sigma=\{s\vert_{L,N}\colon s\in\tau\|\sigma\}
  \]
  If $\map{\rho}{K}{L}\xrightarrow{\sigma}\map{\tau}{M}{N}$ are morphisms, then we have
  \begin{align*}
    \comp\tau{(\comp\sigma\rho)}&=\{s\vert_{K,N}\colon s\in(K\cprd L\cprd M\cprd N)^*, s\vert_{K,L}\in\rho,\;s\vert_{L,M}\in\sigma,\;s\vert_{M,N}\in\tau\}\\
                                &= \comp{(\comp\tau\sigma)}\rho
  \end{align*}
  so this composition is associative, and it is easy to check that the copycat strategy is the identity.
\end{definition}

\subsection{Sequoidal category structure}

We can endow $\mathcal G$ with a richer categorical structure, using the tensor and sequoid connectives.  In investigating this, we arrive at the definition of a \emph{sequoidal category}, introduced in \cite{laird02}.

\subsubsection{Symmetric monoidal closed category structure}

The operation $\tensor$ makes $\mathcal G$ into a symmetric monoidal closed category:

First, we need to show that $\cmap{\tensor}{\G\times\G}{\G}$ is a functor.  This comes down to finding, for each pair $\map{\sigma}{K}{L},\map{\tau}{M}{N}$ of strategies, a strategy 
\[
  \map{\sigma\tensor\tau}{K\tensor M}{L\tensor N}
\]

The strategy $\sigma\tensor\tau$ is the obvious one: reply to opponent moves in $M$ or $N$ according to $\tau$ and reply to opponent moves in $K$ or $L$ according to $\sigma$.  It is easy to see that this is indeed a functor.

The tensor unit is the empty game $I=\{\emptyset,\emptyset,O,\{\epsilon\}\}$ with no moves.  The unitors and associators are given by copycat strategies in the natural way.

This monoidal category is then closed with respect to $\implies$: we have a natural bijection
\[
  \G(L\tensor M,N)\cong\G(L,M\implies N)
\]

\subsubsection{Strict morphisms}

We might try and do something similar with the sequoid.  However, in this case we do not get a functor $\cmap{\sequoid}{\G\times\G}{\G}$.  Indeed, suppose $\map{\sigma}{K}{L},\map{\tau}{M}{N}$ are strategies as before.  We can try and combine them as before to get a strategy for
\[
  (K\sequoid M) \implies (L\sequoid N)
\]
where $P$ replies to $O$-moves in $M$ or $N$ using $\tau$ and replies to $O$-moves in $K$ or $L$ using $\sigma$.  But consider this sequence of events:
\begin{itemize}
  \item $O$ makes his first move in $L$, as required by the definitions of $\sequoid$ and $\implies$.
  \item The strategy $\tau$ tells $P$ to reply to $O$ in the game $L$, rather than in $K$.
  \item After $P$ has played in $L$, $O$ switches games and plays a move in $N$.  
  \item Now the strategy $\sigma$ tells $P$ to reply to this move in $M$.
\end{itemize}

Unfortunately for $P$, she cannot make a move in $M$, since no move has been made in $K$ yet.

We can fix this problem by requiring that the morphism $\tau$ be \emph{strict}.  Given games $K,L$, a \emph{strict morphism} is a strategy for $K\implies L$ such that player $P$'s first move is in the game $K$.  In our case above, if $\tau$ is a strict strategy then $P$ will make her first move in $K$ and there will be no subsequent problems.  The copycat morphism is certainly strict, as is the composition of two strict morphisms, so we get a full-on-objects subcategory $\G_s$ of $\G$, where the objects are the negative games and the morphisms are the strict morphisms.  The sequoid then gives us a functor
\[
  \cmap{\sequoid}{\G_s\times \G}{\G_s}
\]

In the world of programming languages, strict morphisms correspond to functions that always evaluate their argument.  Suppose we define a game $\mathbf N$ by
\[
  \mathbf N=(\mathbb N \sqcup \{q\}, (n\mapsto P,\;q\mapsto O), O, \{\epsilon, q\} \cup \{qn\colon n\in\mathbb N\})
\]
then a strategy for this game corresponds to a program that returns a natural number.  A strict morphism $\mathbf N\to\mathbf N$, then, corresponds to a program that takes in one natural number and returns another one: 
\begin{itemize}
  \item $O$ plays the move $q$ in the game $\mathbf N$ on the right.
  \item $P$ plays the move $q$ in the game $\neggame{\mathbf N}$ on the left.
  \item $O$ responds to $P$ by playing a natural number $m$ in $\neggame{\mathbf N}$.
  \item $P$ then plays a natural number $n$ in $\mathbf N$.  
\end{itemize}

Since the number $n$ is allowed to depend on $m$, the strict morphisms $\mathbf N\to\mathbf N$ correspond to functions $\mathbb N\to\mathbb N$.

There are non-strict strategies for $\mathbf N\implies\mathbf N$, where $P$ responds immediately to $O$ by playing a natural number in $\mathbf N$ on the right, ending the game immediately.  These correspond to non-strict functions, which always return the same value without evaluating their argument.

\begin{remark}
  In the programming language point of view, there is a difference between a function that returns a constant value without evaluating the argument and a function that evaluates the argument but nevertheless returns the same value every time.  In the latter case, the program will fail to terminate if the program for evaluating the argument does not terminate, whereas the non-strict version may terminate anyway, since the non-terminating bit of code is never run.
\end{remark}

\subsubsection{Sequoidal categories}

The definition of a sequoidal category is a generalization of the category of games we are constructing.

The functor $\cmap{\sequoid}{\G_s\times\G}\G$ actually gives us a monoidal-category action of $\G$ on $\G_s$.  That is, the functor $\_\sequoid (M\tensor N)$ is (naturally isomorphic to) the composition of the functors $\_\sequoid M$ and $\_\sequoid N$.  In other words, for each $L,M,N$ we have isomorphisms
\[
  L\sequoid(M\tensor N)\cong (L\sequoid M)\sequoid N
\]
satisfying certain coherence conditions.  Once again, the isomorphism is the obvious copycat one - in both games, $O$ must start in the game $L$ but thereafter may switch to any game.

TODO: Finish off this section, introduce exponentials, introduce win-games.

\section{Games with ordinal sequences of moves}

We now moify the definitions from the last section so that our games admit sequences of moves of ordinal length.  This will involve making two main changes.

\begin{itemize}
  \item Our set $P_A$ of legal plays, rather than containing only finite sequences of moves, will be allowed to contain sequences of moves of ordinal length (given as functions from some ordinal into the set of moves $M_A$.
  \item Plays (sequences of moves) rather than moves will be taken as primitive.  In particular, we shall replace the sign function for moves $\cmap{\lambda_A}{P_A}{\{O,P\}}$ with the sign function for plays $\cmap{\zeta_A}{P_A}{\{O,P\}}$ that assigns a player to each play.
\end{itemize}

\subsection{Preliminary definitions}

\begin{definition}
  Let $\beta$ be an ordinal, and let $M$ be a set of moves.  An \emph{$\beta$-play} or \emph{play of length $\beta$} on \emph{move-set $M$} is a function $\cmap{s}{\beta}{M}$.  We shall use the same notation as we did for finite sequences; for example, if $s$ is a $\beta$-play on $M$, and $a\in M$, we write $sa$ for the $(\beta+1)$-play that agrees with $s$ on the initial segment $\beta$ and takes the value $a$ on the final element.

  If $s$ is a $\beta$-play on $M$, and $\gamma<\beta$, we have a $\gamma$-play $s\vert_\gamma$, given by restricting $s$ to the initial segment $\gamma$.

  If $\alpha$ is an ordinal and $M$ is a set of moves, we write $M^{*<\alpha}$ for the set of all $\beta$-plays on $M$, where $\beta$ ranges over all ordinals less than $\alpha$.  
\end{definition}

\begin{definition}
  Let $\alpha$ be an ordinal.  A \emph{game $A$ over $\alpha$} is given by a tuple
  \[
    (M_A, \lambda_A, \zeta_A, P_A)
  \]
  where
  \begin{itemize}
    \item $M_A$ is a set of moves,
    \item $\cmap{\lambda_A}{M_A}{\OP}$ is a function saying which player each move belongs to,
    \item $P_A$ is a prefix closed subset of $M_A^{*<\alpha}$ satisfying two conditions given below and
    \item $\cmap{\zeta_A}{P_A}{\OP}$ is a function, saying which player each play belongs, to that obeys the rule
      \[
        \zeta_A(sa)=\lambda_A(a)
      \]
      for all plays $sa$ over successor ordinals.
  \end{itemize}

  If $\beta<\alpha$ is some ordinal, we write $P_A(\beta)$ for the set of all $\beta$-plays in $P_A$.

  The two conditions we impose on the set $P_A$ are:
  \begin{description}
    \item[Alternating condition] If $s,sa\in P_A$ then $\lambda_A(a)=\neg\zeta_A(s)$.
    \item[Sheaf condition] If $\mu<\alpha$ is a limit ordinal, then $P_A(\lambda)$ is the set of all limits of plays of length less than $\lambda$.  In other words:
      \[
        P_A(\mu) = \{\cmap{s}{\mu}{M_A}\varsuchthat \mu\vert_\beta\in P_A(\beta)\textrm{ for all }\beta<\mu\}
      \]
  \end{description}
\end{definition}

\begin{remark}
  \begin{enumerate}
    \item For plays whose length is a successor ordinal, the function $\zeta_A$ is entirely determined by the function $\lambda_A$.  So we could think of $\zeta_A$ as a function that determines the owner of each play whose length is a limit ordinal.

      In particular, the sheaf condition tells us that $P_A(0)=\{\epsilon\}$, where $\epsilon$ is the empty play of length $0$.  The value $\zeta_A(\epsilon)$ then tells us who the starting player is, since, by the alternating condition, all plays of length $1$ must consist of a $b_A$ move, where
      \[
        b_A=\neg\zeta_A(\epsilon)
      \]

    \item We don't really need the set $M_A$ and the function $\lambda_A$, but they will help us to avoid confusion, while maintaining a link with the games of section \ref{abjagreview}.  
  \end{enumerate}
\end{remark}

\begin{notation}
  Let $A$ be a game over an ordinal $\alpha$, and let $s\in P_A$.  As before, we call $s$ an \emph{$O$-play} if $\zeta_A(s)=O$ and a \emph{$P$-play} if $\zeta_A(s)=P$.

  If $a\in M_A$, we call $a$ an \emph{$O$-move} if $\lambda_A(a)=O$ and a \emph{$P$-move} if $\lambda_A(a)=P$.
\end{notation}

\begin{example}
  Here are some examples to bear in mind when formulating our definitions:
  \begin{enumerate}
    \item It is easy to see that the games over $\omega$ correspond to the games from section \ref{abjagreview}.  
    \item Games over the ordinal $\omega+1$ correspond to the win games from section \ref{win-games}.  If $A$ is a game over $\omega+1$, then the sheaf condition tells us that $P_A(\alpha+1)$ is the set of all limits of finite plays in $P_A$; i.e., the set of all infinite plays that occur in the game $A$.  Then the action of the function $\zeta_A$ on $P_A(\omega)$ corresponds exactly to the set $W_A$ by
      \[
        W_A=\{s\in P_A(\omega)\suchthat \zeta_A(s)=P\}
      \]
    \item Games over the ordinal $\omega2$ correspond to a sort of `double game': we start by playing a game over $\omega$, then build up an infinite play $s$.  $s$ then determines a second game over $\omega$ whose starting player is determined by $\zeta_A(s)$.  
  \end{enumerate}
\end{example}

We need a definition of strategy for our games.  Compare this definition with that from section \ref{abjagreview}.

\begin{definition}
  Let $\alpha$ be a game, and let $A$ be a game over $\alpha$.  A \emph{strategy} for $A$ is given by a prefix-closed subset $\sigma\subset P_A$ such that:
  \begin{itemize}
    \item If $s\in\sigma$ is an $O$-play, and $a,b$ are $P$-moves such that $sa,sb\in\sigma$, then $a=b$.
    \item If $s\in\sigma$ is a $P$-play, and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.  
    \item $\sigma$ satisfies the sheaf condition: if $\mu<\alpha$ is a limit ordinal then
      \[
        \sigma\cap P_A(\mu)=\{\cmap{s}{\mu}{M_A}\varsuchthat s\vert_\beta\in\sigma\textrm{ for all }\beta<\mu\}
      \]
  \end{itemize}
\end{definition}

This definition is exactly the same as that from section \ref{abjagreview}, except we have replaced the requirement that $\varepsilon\in\sigma$ with the stronger sheaf condition.

\begin{definition}
  Let $\alpha$ be an ordinal, and let $A$ be a game over $\alpha$.  We say a strategy $\sigma$ for $\alpha$ is \emph{total} if it contains exactly one $P$-response to every $O$-play.  I.e., if $s\in\sigma$ is an $O$-play, then there exists a (necessarily unique) $P$-play $a$ such that $sa\in\sigma$.
\end{definition}

\subsection{Monoidal category structure}

\subsubsection{Some connectives}

For the rest of the section, fix an ordinal $\alpha$.  We want to build a monoidal category of $\alpha$-games and strategies, as in section \ref{abjagreview}.  First, we need to define the connectives $\tensor$ and $\implies$ for $\alpha$-games.

We start with some auxiliary definitions.
\begin{definition}
  Let $X,Y$ be sets of moves, let $\beta<\alpha$ and let $\cmap{s}{\beta}{X\cprd Y}$ be a sequence taking values in both $X$ and $Y$.  Then we get a partition of the ordinal $\beta$ into two subsets:
  \begin{IEEEeqnarray*}{cCc}
    \beta_X&=&s\inv(X)\\
    \beta_Y&=&s\inv(Y)
  \end{IEEEeqnarray*}
  Under the ordering induced from $\beta$, $\beta_X$ and $\beta_Y$ become ordinals in their own right.  It can be shown that $\beta_X,\beta_Y\le\beta$, so in particular $\beta_X,\beta_Y<\alpha$.  We now have two new plays given by restricting $s$ to each of these two ordinals:
  \begin{align*}
    &\cmap{s\vert_X}{\beta_X}{X}\\
    &\cmap{s\vert_Y}{\beta_Y}{Y}
  \end{align*}
  Now suppose that $S\subset X^{*<\alpha}$ is a set of sequences of elements of $X$ and that $T\subset Y^{*<\alpha}$ is a set of sequences of elements of $Y$.  We write $S\|T$ for the subset of $(X\cprd Y)^{*<\alpha}$ made up of those sequences $s$ such that $s\vert_X\in S$ and $s\vert_Y\in T$.
\end{definition}

We are now in a position to define the tensor product.

\begin{definition}
  Let $N,L$ be negative games over $\alpha$.  We get the natural map $\lambda_{N\tensor L}=\cmap{(\lambda_N\cprd \lambda_L)}{M_N\cprd M_L}{\OP}$ given by the copairing.  We can then define a map $\cmap{\zeta_{N\tensor L}}{P_N\| P_L}{\OP}$ given as follows:
  \[
    \zeta_{N\tensor L}(s)=\zeta_N(s\vert_N)\wedge\zeta_L(s\vert_L)
  \]
  In other words, player $O$ owns a play if he owns either one of the plays obtained by restricting the play to the individual games $N,L$.

  A consequence of building games over ordinals greater than $\omega+1$ is that there might be plays $sa\in P_N\|P_L$ such that $\lambda_{N\tensor L}(a)\ne\zeta_{N\tensor L}(sa)$.  This might occur if $s$ is a play over a limit ordinal and $\zeta_N(s\vert_N)=\zeta_L(s\vert_L)=O$.  In that case, regardless of whether player $P$ plays the next move $a$ in $N$ or in $L$, player $O$ will still be winning in the other game, so we will have $\zeta_{N\tensor L}(sa)=O$.  To avoid this situation, we make the play $sa$ illegal; in other words, we remove from the set $P_N\|P_L$ all plays $sa$ such that $\zeta_{N\tensor L}(sa)\ne\lambda_{N\tensor L}(a)$.  The effect of this on the games is that if player $O$ ever manages to obtain a winning position in both games simultaneously, he wins immediately, since there are no plays available to player $P$.

  Even after throwing away these invalid plays, we still need to make our set of valid plays satisfy the alternating condition with respect to $\zeta_{N\tensor L}$.  If $\cmap{\zeta}{P_N\|P_L}{\OP}$ is any function, then we say a sequence $s\in P_N\|P_L$ is \emph{alternating with respect to $\zeta$} if the set of (initial) subsequences of $s$ satisfies the alternating condition with respect to $\zeta$; i.e., if whenever $t,ta$ are initial subsequences of $s$, we have $\zeta(ta)=\neg\zeta(t)$.

  Let $P_{N\tensor L}$ be the set of all sequences $s\in P_N\|P_L$ that satisfy the following two conditions:
  \begin{itemize}
    \item If $s=s'a$ is a play over a successor ordinal then $\zeta_{N\tensor L}(s)=\lambda_{N\tensor L}(a)$.
    \item $s$ is alternating with respect to $\zeta_{N\tensor L}$.
  \end{itemize}
  Then the \emph{tensor product} $N\tensor L$ of $N$ and $L$ is given by the tuple
  \[
    N\tensor L=(M_N\cprd M_L,\lambda_{N\tensor L},\zeta_{N\tensor L},P_{N\tensor L})
  \]
\end{definition}

The definition of implication is similar.

\begin{definition}
  Let $N,L$ be negative games over $\alpha$.  Define $\lambda_{N\implies L}$ to be the copairing $\cmap{((\neg\circ\lambda_N)\cprd\lambda_L)}{M_N\cprd M_L}{\OP}$.

  We can then define $\cmap{\zeta_{N\implies L}}{P_N\|P_L}{\OP}$ as follows:
  \[
    \zeta_{N\implies L}(s)=\left(\zeta_N(s\vert_N)\Rightarrow\zeta_L(s\vert_L)\right)
  \]
  In other words, player $O$ owns the play if either its restriction to $N$ is an $O$-play or its restriction to $L$ is a $P$-play.

  We now define $P_{N\implies L}$ to be the set of all sequences $s\in P_N\|P_L$ that satisfy the following two conditions:
  \begin{itemize}
    \item If $s=s'a$ is a play over a successor ordinal then $\zeta_{N\implies L}(s)=\lambda_{N\implies L}(a)$.
    \item $s$ is alternating with respect to $\zeta_{N\implies L}$.
  \end{itemize}
  We define the game $N\implies L$ by
  \[
    N\implies L=(M_N\cprd M_L,\lambda_{N\implies L},\zeta_{N\implies L},P_{N\implies L})
  \]
\end{definition}

\begin{proposition}
$N\tensor L$ and $N\implies L$ are well-formed games.

\begin{proof}
  We prove this for $N\tensor L$; the proof for $N\implies L$ is similar.

  Since $P_N\|P_L$ is prefix closed, so is $P_{N\tensor L}$, since if a sequence is alternating then so are its subsequences.  We need to prove that $P_{N\tensor L}$ satisfies the alternating condition with respect to $\zeta_{N\tensor L}$ and the sheaf condition.  Suppose $s,sa\in P_{N\tensor L}$.  Then $s,sa$ are both subsequences of $sa$, which is alternating by the definition of $P_{N\tensor L}$.  Therefore, $s,sa$ have opposite signs under $\zeta_{N\tensor L}$.

  For the sheaf condition, let $\mu<\alpha$ be a limit ordinal and suppose $\cmap{s}{\mu}{M_N\cprd M_L}$ be such that $s\vert_\beta\in P_{N\tensor L}$ for all $\beta<\mu$.  We need to show that $s\in P_{N\tensor L}$.

  To show this, we need to show that $s\in P_N\|P_L$ and that $s$ is alternating with respect to $\zeta_{N\implies L}$.  First we show that $s\in P_N\|P_L$; i.e., $s\vert_N\in P_N$ and $s\vert_L\in P_L$.

  Write $\mu_N$ for $s\inv(N)$ and $\mu_L$ for $s\inv(L)$.  If the image of $\mu_N$ in $\mu$ is contained inside some ordinal $\beta<\mu$, then we have
  \[
    s\vert_\beta\in P_{N\tensor L}
  \]
  and therefore $s\vert_N=s\vert_\beta\vert_{\mu_N}\in P_N$.  Otherwise, the image of $\mu_N$ is cofinal in $\mu$.

  In that case, $\mu_N$ is a limit ordinal.  Let $\beta_N$ be any ordinal less than $\mu_N$.  Then the image of $\beta_N$ in $\mu$ is contained in some ordinal $\beta<\mu$.  By the same argument as before, we have $s\vert_N\vert_{\beta_N}\in P_N$.  Since $\beta_N<\mu_N$ is arbitrary, we now have $s\vert_N\in P_N$ by the sheaf condition on $P_N$.

  Lastly, $s$ is certainly alternating with respect to $\zeta_{N\tensor L}$.  Indeed, if $t,ta$ are subsequences of $s$, then $ta$ must be a \emph{proper} subsequence (since it is a sequence over a successor ordinal).  Then we know that $ta$ is alternating, and therefore $t$ and $ta$ have opposite signs.
\end{proof}
\end{proposition}

A phenomenon occurs for implication similar to that observed for the tensor product.  Though the sign $\zeta_{N\implies L}(s)$ of a play $s$ in $N\implies L$ is given by the formula
\[
  \zeta_{N\implies L}(s)=(\zeta_N(s\vert_N)\Rightarrow\zeta_L(s\vert_L))
\]
there are only three values of the pair $(\zeta_N(s\vert_N),\zeta_L(s\vert_L))$ that occur in normal play: $(O,O)$, $(P,P)$ (in which case $\zeta_{N\implies L}(s)=P$) and $(P,O)$ (in which case $\zeta_{N\implies L}(s)=O$).  The fourth case $(O,P)$ - giving $\zeta_{N\implies L}(s)=P$ - can still occur, but only for a limiting play, and if it does occur then there are no legal opponent replies.  In this case, player $P$ wins immediately.  This is the content of the following lemma:

\begin{lemma}
  Let $N,L$ be negative $\alpha$-games, and suppose $s,sa$ are plays in $N\implies L$.  Then:
  \begin{enumerate}[i)]
    \item Either $\zeta_N(s\vert_N)=P$ or $\zeta_L(s\vert_L)=O$.
    \item Either $\zeta_N(sa\vert_N)=P$ or $\zeta_L(sa\vert_L)=O$.
  \end{enumerate}
  \begin{proof}
    \begin{enumerate}[(i):]
      \item Suppose $s\in P_{N\implies L}$ such that $\zeta_N(s\vert_N)=O$ and $\zeta_L(s\vert_L)=P$.  Then $\zeta_{N\implies L}(s)=P$.  Suppose that $a\in M_N\cprd M_L$ with $\lambda_{N\implies L}(a)=O$.  We shall show that $sa\not \in P_{N\implies L}$.

        If $a\in M_N$ then $\zeta_L(sa\vert_L)=\zeta_L(s\vert_L)=P$, and if $a\in M_L$ then $\zeta_N(sa\vert_N)=\zeta_N(s\vert_N)=O$.  In either case, 
        \[
          \zeta_{N\implies L}(sa)=(\zeta_N(sa\vert_N)\Rightarrow\zeta_L(sa\vert_L))=P
        \]
        But $\lambda_{N\implies L}=O$, and therefore $sa\not\in P_{N\implies L}$.

      \item Now suppose that $s,sa\in P_{N\implies L}$.

        Suppose first that $\zeta_{N\implies L}(sa)=O$.  In that case, we must have $\zeta_N(sa\vert_N)=P$ \emph{and} $\zeta_L(sa\vert_L)=O$, and we are done.  So suppose instead that $\zeta_{N\implies L}(sa)=P$.  In that case, $\zeta_{N\implies L}(s)=O$, by alternation.  In that case, we must have $\zeta_N(s\vert_N)=P$ and $\zeta_L(s\vert_L)=O$.

        If $a\in M_N$ then $\zeta_L(sa\vert_L)=\zeta_L(s\vert_L)=O$, and if $a\in M_L$ then $\zeta_N(sa\vert_N)=\zeta_N(s\vert_N)=P$.
    \end{enumerate}
  \end{proof}
\end{lemma}

\subsubsection{Morphisms, composition of morphisms and identity morphisms}

We now define a category $\G(\alpha)$.  The objects of $\G(\alpha)$ are negative games over $\alpha$, and if $N,L$ are such games, then a morphism $N\to L$ is a strategy for $N\implies L$.  We define the composition of two morphisms as in section \ref{abjagreview}.

\begin{definition}
  Let $N,M,L$ be negative games over $\alpha$.  Define
  \[
    \L^\alpha(N,M,L)\subset(M_N\cprd M_M\cprd M_L)^{*<\alpha}
  \]
  to be the set of all sequences $s\in(M_N\cprd M_M\cprd M_L)^{*<\alpha}$ such that if $t,ta$ are subsequences of $s$, then $t$ and $ta$ are not an $L$-move and an $N$-move, or vice versa: in other words, either $t,ta$ come from the same game, or one of them is an $M$-move - we are not allowed to jump straight from $L$ to $N$ or back again.

  Now let $\cmap{\sigma}{N}{M}$,$\cmap{\tau}{M}{L}$ be strategies.  Define
  \[
    \tau\|\sigma = \{s\in\L^\alpha(N,M,L)\suchthat s\vert_{N,M}\in \sigma,\; s\vert_{M,L}\in\tau\}
  \]
  Then the composition of $\sigma$ and $\tau$ is given by
  \[
    \comp\tau\sigma=\{s\vert_{N,L}\suchthat s\in\tau\|\sigma\}
  \]
\end{definition}

\begin{proposition}
  $\comp\tau\sigma$ is a well-formed strategy on $N\implies L$.
  \begin{proof}
    There are several things we need to check:
    \begin{enumerate}[1)]
      \item $\comp\tau\sigma$ is prefix closed.
      \item $\comp\tau\sigma\subset P_{N\implies L}$.  In other words:
        \begin{enumerate}[a)]
          \item For every $s\in\comp\tau\sigma$, $s\vert_N\in P_N$ and $s\vert_L\in P_L$
          \item If $ta\in\comp\tau\sigma$ is a play over a successor ordinal, then $\zeta_{N\implies L}(ta)=\lambda_{N\implies L}(a)$.
          \item $\comp\tau\sigma$ is alternating with respect to $\zeta_{N\implies L}$.
        \end{enumerate}
      \item If $s\in\sigma$ is an $O$-play and $sa,sb\in\sigma$, then $a=b$.
      \item If $s\in\sigma$ is a $P$-play and $sa\in P_{N\implies L}$ then $sa\in\sigma$.
      \item $\sigma$ satifies the sheaf condition.
    \end{enumerate}

    \begin{enumerate}[(1): ]
      \item $L^\alpha(N,M,L)$ is certainly prefix closed, and it follows that $\tau\|\sigma$ is too.  If $s\in\tau\|\sigma$, and $t$ is a prefix of $s\vert_{N,L}$, let $\tilde{t}$ be the prefix of $s$ made up of the terms of $t$ together with any term from $M$ that comes earlier in the sequence.  Then $\tilde{t}\in\tau\|\sigma$, and $t=\tilde{t}\vert_{N,L}$, so $t\in\comp\tau\sigma$.

      \item $\comp\tau\sigma\subset P_{N\implies L}$:
        \begin{enumerate}[(a): ]
          \item Let $s\in\tau\|\sigma$.  We need to show that $(s\vert_{N,L})\vert_N\in P_N$ and that $(s\vert_{N,L})\vert_L\in P_L$.  But
            \[
              (s\vert_{N,L})\vert_N=(s\vert_{N,M})\vert_N
            \]
            and $s\vert_{N,M}\in\sigma\subset P_{N\implies M}$, so $(s\vert_{N,L})\vert_N\in P_N$, and similarly, $(s\vert_{N,L})\vert_L\in P_L$.
          \item We want to show that $\comp\tau\sigma$ is alternating with respect to $\zeta_{N\implies L}$.  Suppose $s,sa\in\comp\tau\sigma$, and suppose that $s=s'\vert_{N,L}$, where $s'\in\tau\|\sigma$ and $sa=s'a\vert_{N,L}$.  We have:
            \begin{IEEEeqnarray*}{rCl}
              \zeta_{N\implies L}(s)&=&(\zeta_N(s\vert_N)\Rightarrow\zeta_L(s\vert_L))\\
              \zeta_{N\implies M}(s'\vert_{N,M})&=&(\zeta_N(s\vert_N)\Rightarrow\zeta_M(s'\vert_M))\\
              \zeta_{M\implies L}(s'\vert_{M,L})&=&(\zeta_M(s'\vert_M)\Rightarrow\zeta_L(s\vert_L))
            \end{IEEEeqnarray*}
            Therefore, if $\zeta_{N\implies L}=O$, then either $\zeta_{N\implies M}(s'\vert_{N,M})=O$ or $\zeta_{M\implies L}(s'\vert_{M,L})=O$ (by transitivity of $\Rightarrow$).  In the first case, we must have 
        \end{enumerate}
    \end{enumerate}
  \end{proof}
\end{proposition}

TODO: incorporate into proof.

So, I think that to show alternation, we need to show two things:

1) If $s, sa\in\comp\tau\sigma$, then $\zeta_{A\implies C}(s)=\neg\zeta_{A\implies C}(sa)$.

2) If $s\in\comp\tau\sigma$ is a play over a limit ordinal, then $\zeta_{A\implies C}(s)=P$.

Let's look at (2).

Suppose $\s\in\tau\|\sigma$ and that $\zeta_{A\implies C}(s\vert_{A,C})=O$.  We shall show that $\s$ must be a play over a successor ordinal.

By definition, we must have $\zeta_A(\s\vert_A)=P$ and $\zeta_C(\s\vert_C)=O$.  So that gives us two cases:

Case 1: $\zeta_B(\s\vert_B)=P$.  In this case, $\zeta_{B\implies C}(\s\vert_{B,C})=O$, so $\s\vert_{B,C}$ is a play over a successor ordinal.  Then the last move in $\s\vert_{B,C}$ must have been played in $C$ (player switches), and then the definition of $\L(A,B,C)$ tells us that this is in fact the last move in $\s$.

Case 2: $\zeta_B(\s\vert_B)=O$.  Similar.

OK, so far so good.  What about (1)?

Suppose that $s,sa\in\comp\tau\sigma$.  Let us write $s=\s\vert_{A,C}$, where $\s\in\tau\|\sigma$ is chosen minimal so it has no trailing $B$-moves.  So $sa=\s \mathfrak b a\vert_{A,C}$, where $\mathfrak b$ is a sequence of $B$-moves.

PPP P P P
PPO P O O
PPP P P P
PPO P O O
POO O P O

\end{document}

### 2016-10-11 old/2/ordinal_games.tex
Started writing paper.

--- 2016-10-11 ordinal_games/ordinal_games.tex
@@
 
-\input{../common/preamble}
-
-\title{Games with ordinal sequences of moves}
-\author{John Gowers}
-\date{}
+\usepackage[utf8]{inputenc}
+
+\usepackage{graphicx} % support the \includegraphics command and options
+
+\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
+
+%%% PACKAGES
+\usepackage{booktabs} % for much better looking tables
+\usepackage{array} % for better arrays (eg matrices) in maths
+\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)\prefix\t$.
+\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
+\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
+\usepackage{mathtools} % for the all important \coloneqq symbol
+\usepackage{url} % for \url
+\usepackage{IEEEtrantools} % for \IEEEeqnarray
+\usepackage{pbox} % for \pbox
+
+%%% ToC (table of contents) APPEARANCE
+\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
+\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
+\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
+\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!
+
+%% Font things %%
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{stmaryrd}
+\usepackage{mathtools}
+\usepackage{cmll} % Linear logic symbols!
+
+%% Lists %%
+\usepackage{enumerate}
+
+%% Graphics %%
+\usepackage{tikz}
+\usetikzlibrary{cd}
+\usetikzlibrary{patterns}
+\usetikzlibrary{calc}
+
+%% Theorems! %%
+\usepackage{amsthm}
+\theoremstyle{plain} % Theorems, lemmas, propositions etc.
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{fact}[theorem]{Fact}
+\newtheorem{construction}[theorem]{Construction}
+\theoremstyle{definition} % Definitions etc.  Remarks too, because I don't like the way the 'remark' style looks.
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{notation}[theorem]{Notation}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example}
+\newtheorem{question}[theorem]{Question}
+
+%% Exercises and answers %%
+\usepackage{answers}
+
+\newtheoremstyle{exercisestyle}% name
+  {6pt}   % ABOVESPACE
+  {6pt}   % BELOWSPACE
+  {\itshape}  % BODYFONT
+  {0pt}       % INDENT (empty value is the same as 0pt)
+  {\bfseries} % HEADFONT
+  {.}         % HEADPUNCT
+  {3pt} % HEADSPACE
+  {}          % CUSTOM-HEAD-SPEC
+
+\theoremstyle{exercisestyle}
+\newtheorem{exercise}{Exercise}
+\newtheorem{answerthm}{Exercise}
+
+\Newassociation{answer}{answerthm}{answers}
+\newcommand{\answerthmparams}{}
+
+%% Changes to enumerate things so they look better %%
+
+\makeatletter
+\def\enumfix{%
+\if@inlabel
+ \noindent \par\nobreak\vskip-\topsep\hrule\@height\z@
+\fi}
+
+\let\olditemize\itemize
+\def\itemize{\enumfix\olditemize}
+\let\oldenumerate\enumerate
+\def\enumerate{\enumfix\oldenumerate}
+
+%% Random crap %%
+\usepackage{xifthen}
+
+\makeatletter
+\def\thm@space@setup{%
+  \thm@preskip=\parskip \thm@postskip=0pt
+}
+\makeatother
+
+\makeatletter
+\newcommand*{\relrelbarsep}{.386ex}
+\newcommand*{\relrelbar}{%
+  \mathrel{%
+    \mathpalette\@relrelbar\relrelbarsep
+  }%
+}
+\newcommand*{\@relrelbar}[2]{%
+  \raise#2\hbox to 0pt{$\m@th#1\relbar$\hss}%
+  \lower#2\hbox{$\m@th#1\relbar$}%
+}
+\providecommand*{\rightrightarrowsfill@}{%
+  \arrowfill@\relrelbar\relrelbar\rightrightarrows
+}
+\providecommand*{\leftleftarrowsfill@}{%
+  \arrowfill@\leftleftarrows\relrelbar\relrelbar
+}
+\providecommand*{\xrightrightarrows}[2][]{%
+  \ext@arrow 0359\rightrightarrowsfill@{#1}{#2}%
+}
+\providecommand*{\xleftleftarrows}[2][]{%
+  \ext@arrow 3095\leftleftarrowsfill@{#1}{#2}%
+}
+\makeatother
+
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
+\newcommand{\Rings}{\catname{CRing}}
+\newcommand{\CAT}{\catname{CAT}}
+\newcommand{\Top}{\catname{Top}}
+\newcommand{\Set}{\catname{Set}}
+\newcommand{\Cont}{\catname{Cont}}
+\newcommand{\Sch}{\catname{Sch}}
+\newcommand{\Mod}[1][]{\ifthenelse{\isempty{#1}}{\catname{Mod}}{#1\catname{mod}}}
+\DeclareMathOperator{\sh}{Sh}
+\newcommand{\Sh}[1][]{\ifthenelse{\isempty{#1}}{\sh}{\sh(#1)}}
+\newcommand{\map}[3]{#2\xrightarrow{#1} #3}
+\newcommand*\from{\colon}
+\newcommand{\cmap}[3]{#1\from{}#2\to{}#3}
+\newcommand\oppcat[1]{#1^{\mathrm{op}}}
+\DeclareRobustCommand{\vmap}[3] {\begin{tikzcd} #2 \arrow[d, "#1"] \\ #3 \end{tikzcd}}
+\newcommand{\partref}[1]{(\ref{#1})}
+\newcommand{\intgrpd}[4] {#1 \xrightrightarrows[#3]{#4} #2}
+\DeclareRobustCommand{\bigintgrpd}[4] {\begin{tikzcd}[ampersand replacement=\&] #1 \arrow[r, shift left=0.5ex, "#3"] \arrow[r, shift right=0.5ex, "#4"'] \& #2 \end{tikzcd}}
+
+\usepackage{xspace}
+
+\newcommand{\etale}{\'{e}tale\xspace}
+\newcommand{\Etale}{\'{E}tale\xspace}
+
+\def \inv {^{-1}}
+
+\DeclareMathOperator{\id}{id}
+\DeclareMathOperator{\op}{op}
+\DeclareMathOperator{\pr}{pr}
+\DeclareMathOperator{\pre}{{pre}}
+\DeclareMathOperator{\et}{{\acute{e}t}}
+
+\DeclareMathOperator{\Hom}{Hom}
+\DeclareMathOperator{\Spec}{Spec}
+
+\DeclareMathOperator{\ol}{ol}
+
+\def\presuper#1#2%
+  {\mathop{}%
+   \mathopen{\vphantom{#2}}^{#1}%
+   \kern-\scriptspace%
+   #2}
+\def\presub#1#2%
+  {\mathop{}%
+   \mathopen{\vphantom{#2}}_{#1}%
+   \kern-\scriptspace%
+   #2}
+
+%% Our things %%
+
+\newcommand{\neggame}[1]{\presuper{\perp}{#1}}
+\newcommand{\tensor}{\otimes}
+\newcommand{\sequoid}{\oslash}
+\newcommand{\varsequoid}{\vartriangleleft}
+\renewcommand{\implies}{\multimap}
+\newcommand{\comp}[2]{#1 \circ #2}
+\newcommand{\cprd}{\sqcup}
+\newcommand{\G}{\mathcal G}
+\newcommand{\suchthat}{\;\colon\;}
+\newcommand{\varsuchthat}{\;\mid\;}
+\newcommand{\OP}{\{O,P\}}
+\renewcommand{\L}{\mathcal L}
+\newcommand{\s}{\mathfrak s}
+\renewcommand{\t}{\mathfrak t}
+\newcommand{\emptyplay}{\epsilon}
+\newcommand{\bracketed}[1]{\left({#1}\right)}
+\newcommand{\bneggame}[1]{\bracketed{\neggame{#1}}}
+\newcommand{\prefix}{\sqsubseteq}
+\renewcommand{\ss}{\mathbf{s}}
+\newcommand{\pfun}{\rightharpoonup}
+
+%%% END Article customizations
 
@@
 
-\begin{titlepage} % Shamelessly stolen from the online LaTeX book.
-	\centering
-	{\scshape\LARGE University of Bath \par}
-	\vspace{1cm}
-	{\scshape\Large PhD Confirmation Report \par}
-	\vspace{1.5cm}
-	{\huge\bfseries Games with ordinal sequences of moves \par}
-	\vspace{2cm}
-	{\Large\itshape John Gowers \par}
-	\vfill
-	supervised by\par
-	Dr.~James \textsc{Laird}
-
-	\vfill
-
-% Bottom of the page
-	{\large \today\par}
-\end{titlepage}
-
-\addtocontents{toc}{\protect\enlargethispage{35mm}}
-\tableofcontents
-\thispagestyle{empty}
-
-\setcounter{tocdepth}{2}
-
 \section{Introduction}
 
-\lettrine[image=true, lines=6, findent=3pt, nindent=0pt]{cleos-g.png}{ame Semantics}, or the use of games and strategies to model logical systems and programming languages, has its origins in a model of intuitionistic logic by Lorenzen \cite{lorenzengames} using games.
-Towards the end of the twentieth century, several authors, starting with Blass \cite{blassgames}, realized that certain natural operations on games could be used to model the connectives in Girard's linear logic.
-Major results from this enterprise include:
-\begin{itemize}
-  \item A fully complete categorical semantics for the multiplicative fragment of linear logic, together with the MIX rule, by Abramsky and Jagadeesan \cite{abramskyjagadeesangames}
-  \item A fully complete categorical semantics for the multiplicative fragment of linear logic without the MIX rule, by Hyland and Ong \cite{HylandOngGames}
-  \item A modification of Abramsky and Jagadeesan's construction, giving a fully complete model of the multiplicative-exponential fragment of linear logic, by Baillot, Danos, Ehrhard and Regnier \cite{bion}
-  \item Fully complete models of the negative fragment of linear logic by others, starting with independent work by Curien \cite{curiengames} and Lamarche \cite{lamarchegames}.  
-\end{itemize}
-
-Another major early result was the use of game semantics to give a fully abstract model of the programming language PCF (This result was obtained independently, using different techniques, by Abramsky, Jagadeesan and Malacaria \cite{ajmPcf}, by Hyland and Ong \cite{hoPcf}, and by Nickau \cite{nickauPcf}).
-
-Central to much of the current work on game semantics for linear logic is the treatment of the exponential connective $\oc$.
-Several approaches have been made to model this connective in a game-theoretic way (see Section 3 of \cite{martinsthesis} for a brief survey).
-We shall use the construction from \cite{ajmPcf} and \cite{hyland1997games}: if $A$ is a game, then $\oc A$ is the game formed by playing a countably infinite number of copies of $A$ --- $A_0,A_1,A_2,\dots$ --- in parallel, where only the opponent $O$ may switch games and where neither player may play in game $A_{n+1}$ until a move has been made in game $A_n$.
-
-This definition, and in particular the restriction on the order in which games may be started, allows us to give the game $\oc A$ the structure of the \emph{cofree commutative comonoid} over $A$ \cite{LairdCofCommCom} and gives rise to a \emph{linear exponential comonad} on our category of games.
-The linear exponential comonad \cite{SchalkWhatIs} and the cofree commutative comonoid functor \cite{LafontCofCommCom,MelliesCofCommCom} are both sufficient to model the exponential connective from linear logic.
-
-The restriction that says that the copies of $A$ in $\oc A$ must be opened in order, motivates the following definition \cite{laird02}: if $A,B$ are games, then the \emph{sequoid} $A\sequoid B$ of $A$ and $B$ is the game in which $A$ and $B$ are played in parallel, only the opponent $O$ may switch games, and play must start in $A$.
-It turns out that if $A$ is a game, then the operation $A\sequoid\blank$ gives rise to an endofunctor on the category $\G$ of games, and that the exponential $\oc A$ is the final coalgebra for this endofunctor.
-That is to say, we have a morphism $\cmap{\alpha}{\oc A}{A\sequoid\oc A}$ such that whenever $\cmap{\sigma}{B}{A\sequoid B}$ is a morphism, there is a unique morphism $\cmap{\fcoal{\sigma}}{B}{\oc A}$ such that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\sigma"] \arrow[d, "\fcoal\sigma"']
-      & A\sequoid B \arrow[d, "A\sequoid\fcoal\sigma"] \\
-    \oc A \arrow[r, "\alpha"']
-      & A\sequoid\oc A
-  \end{tikzcd}
-  \]
-Existing proofs of this fact in a finitary games setting (e.g., in \cite{martinsthesis}) make implicit use of the fact that $\oc A$ is the limit of the sequence
-\[
-  I \leftarrow A \leftarrow A\sequoid A \leftarrow A\sequoid(A\sequoid A) \leftarrow \dots
-  \]
-Indeed, any finite-length play in $\oc A$ must involve only finitely many copies of $A$, so exists as a play in $(A\sequoid\blank)^n I$ for some $n$.
-
-On the other hand, when we start imposing winning conditions upon infinite plays, $\oc A$ is no longer the limit of the sequence above.
-Indeed, define a game $\co A$ which is exactly like $\oc A$ except that all infinite plays that contain moves from infinitely many copies of $A$ are wins for the player $P$, regardless of who has won the individual games.
-This game still admits a cone over the sequence above, since any play occurring in $(A\sequoid\blank)^nI$ for some $n$ must involve only finitely many copies of $A$.
-Moreover, it does not admit a morphism of cones to $\oc A$.
-In fact, in the infinitary setting, $\co A$, and not $\oc A$, is the limit of the above sequence.
-
-\[
-  \begin{tikzcd}
-    \co A \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr] \arrow[drrrr, phantom, yshift=0.5em, "\cdots"]
-      &
-        &
-          &
-            & \\
-    I
-      & A \arrow[l]
-        & A\sequoid A \arrow[l]
-          & A\sequoid(A\sequoid A) \arrow[l]
-            & \cdots \arrow[l]
-  \end{tikzcd}
-  \]
-Applying the functor $A\sequoid\blank$ to the cone from $\co A$ gives rise to another cone over the sequence:
-\[
-  \begin{tikzcd}
-    %
-    & A\sequoid\co A \arrow[dl] \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr, phantom, yshift=0.5em, "\cdots"]
-        &
-          &
-            & \\
-    I
-      & A \arrow[l]
-        & A\sequoid A \arrow[l]
-          & A\sequoid(A\sequoid A) \arrow[l]
-            & \cdots \arrow[l]
-  \end{tikzcd}
-  \]
-and therefore a morphism $A\sequoid\co A\to \co A$.  We can then continue to apply the functor $A\sequoid\blank$ to build up a second layer of the sequence:
-\[
-  \begin{tikzcd}
-    \co A \arrow[d] \arrow[dr] \arrow[drr] \arrow[drrr] \arrow[drrrr, phantom, xshift=1em, "\cdots"]
-      & A\sequoid\co A \arrow[l]
-        & A\sequoid(A\sequoid \co A) \arrow[l]
-          & A \sequoid(A\sequoid(A\sequoid\co A)) \arrow[l]
-            & \cdots \arrow[l] \\
-    I
-      & A \arrow[l]
-        & A\sequoid A \arrow[l]
-          & A\sequoid(A\sequoid A) \arrow[l]
-            & \cdots \arrow[l]
-  \end{tikzcd}
-  \]
-What is the limit of this entire diagram?
-An $O$-winning infinite play $s$ in $(A\sequoid\blank)^n \co A$ may be identified with an $O$-winning play in $\oc A$ such that either the opponent $O$ wins in one of the games $A_1,\dots,A_n$ or that only finitely many copies of $A$ are opened.
-It follows that the limit of the diagram \emph{is} the final coalgebra $\oc A$.
-
-The diagrams we have drawn above are special cases of the \emph{final sequence} \cite{finalseq}: given a category $\C$ with a terminal object $1$ and enough limits (in a sense which will become clear) and an endofunctor $\cmap{\F}{\C}{\C}$, we may construct an ordinal-indexed sequence
-\[
-  1, \F(1), \F^2(1),\dots \F^\omega(1), \F^{\omega+1}(1),\dots,\F^\delta(1),\dots
-  \]
-together with commuting morphisms $\F^\gamma(1)\to\F^\delta(1)$ for $\delta\le\gamma$, by setting $\F^{\delta+1}(1) = \F(\F^\delta(1))$ and letting $\F^\mu(1)$ be the limit of the diagram formed by the $\F^\gamma(1)$ for $\gamma<\mu$ if $\mu$ is a limit-ordinal.
-It is well known that if $\delta$ is an ordinal and the map
-\[
-  \F^{\delta+1}(1)\to\F^{\delta}(1)
-  \]
-is an isomorphism, then the inverse of this isomorphism exhibits $\F^{\delta}(1)$ as the final coalgebra of $\F$.  In this case, we say that the final sequence \emph{stabilizes at $\delta$}.
-
-In the case of finitary games, then, we have
-\[
-  \oc A\cong(A\sequoid\blank)^\omega(I)
-  \]
-and in the infinitary case, we have
-\[
-  \oc A\cong(A\sequoid\blank)^{\omega2}(I)
-  \]
-The eventual goal of this research is to study the behaviour of the final sequence of the functor $A\sequoid\blank$ in categories of games.
-Since the sequence stabilizes so early on for existing categories of games, this question is not very interesting in that setting.
-We want to modify our definitions of games in such a way that this final sequence will take much longer to stabilize, and it turns out that one way to do that is to allow plays of transfinite length.
-
-Games with ordinal sequences of moves are not a new idea.
-They have, for example, been studied in \cite{longgamesbook} from the point of view of determinacy.
-Even in game semantics, as we shall see, we may identify games in which we impose a winning condition on the infinite plays with games in which the players are allowed to make plays of length $\omega$ -- we shall call these $(\omega+1)$-games, in contrast to the finitary games, which we shall call $\omega$-games.
-Allowing plays whose lengths are longer transfinite ordinals will give rise to a richer variety of plays, which will be reflected in the final sequence.
-
-One important aspect of the shift from finite to transfinite plays is that the idea of a \emph{play} or \emph{position} takes on a new importance, in contrast to the finitary case, where we can define everything in terms of \emph{moves}.
-Normally, a move is designated as either a $P$-move or an $O$-move; we will extend this so that every position is either a $P$-position or an $O$-position.
-A position $s$ will be an ordinal-indexed sequence of moves; if there is a last move $a$, then $s$ is a $P$-position or an $O$-position according as $a$ is a $P$-move or an $O$-move.
-If the length of $s$ is a limit ordinal, however, then its sign cannot be determined from the signs of its constituent moves.
-This is useful if we want to model games with a winning condition as $(\omega+1)$-games: a play of length $\omega$ in a game corresponds to an infinite play in that game, and its designation as a $P$-position or $O$-position is essentially the same thing as saying whether it is a $P$-winning or $O$-winning play.
-
-This approach is similar to that of Blass \cite{blassgames}, and indeed our treatment of $P$-positions and $O$-positions under the connectives will follow his approach.
-For example, a position $s$ in a tensor product $A\tensor B$ is a $P$-position if and only if its restrictions to $A$ and $B$ are both $P$-positions.
-
-To avoid certain mathematical difficulties, we shall follow Curien, Lamarche and others by requiring that our games be \emph{negative} -- that is, they must always begin with an $O$-move.
-In fact, we shall go further than that: under the usual alternating condition, saying that $O$ always starts is the same thing as requiring that the empty position $\emptyplay$ is a $P$-position.
-In order to avoid problems constructing our category, we shall need to require that \emph{all} positions whose lengths are limit ordinals be $P$-positions.
-We shall call games satisfying this property \emph{completely negative}.
-
-This condition on the sign of games allows us to construct a well-behaved category of games, but it has one serious problem that occurs as soon as we consider games with transfinite-length plays: if $A,B$ are completely negative games, then the linear implication $A\implies B$ is not necessarily completely negative.
-
-We want $A\implies B$ to be the internal hom in our closed monoidal category, so we need to find a way around this.
-Our solution is to construct, for every game $A$, a `minimal extension' $A^{\cn}$ of $A$ that is completely negative.
-We prove various results about the relationship $A^{\cn}$ and $A$ that make this precise and then use them to show that the game $A\impliescn B\coloneqq (A\implies B)^{\cn}$ does give rise to a closed monoidal structure in our category.
-We also give a tentative way of constructing a category whose objects are \emph{all} games, not just the completely negative ones, and use our results to show that this category is in fact equivalent to our existing category of completely negative games.
-
-Having constructed a symmetric monoidal closed category of games, we introduce the sequoid operator and the exponential, and study the final sequence.
-We shall characterize the exponential $\oc A$ as a final coalgebra for the functor $A\sequoid\blank$ and use this characterization to prove that $\oc A$ admits the structure of a cofree commutative comonoid on $A$.
-Then we turn to the final sequence.
-This section will involve some material that is more ordinal-theoretic than game-theoretic; we assign an ordinal \emph{rank} to a (transfinite) sequence of natural numbers and then show that this idea of rank can be used to characterize each term of the final sequence for a functor of the form $A\sequoid\blank$.
-We will show that the reason that the final sequences converge so quickly for finitary games and win-games is that a sequence of length $\omega$ necessarily has low rank: once we allow longer plays, we can get sequences with higher ranks and the final sequence will carry on for longer.
-
-\subsection{Original contribution}
-
-Games with ordinal sequences of enablings have been studied by Laird from a Game Semantics point of view \cite{LairdOrdinalGames}, but to my knowledge this is the first transfinite games category built in the tradition of Abramsky and Jagadeesan.
-Passing to transfinite games causes problems when we try to show that our category is monoidal closed, and we have to come up with new techniques in order to get a monoidal closed category (see Sections \ref{TransSMCCSex} to \ref{ImpliesCnSex}).
-
-The characterization of the final coalgebra for the functor $A\sequoid\blank$ in a transfinite games category is new, though the behaviour in finitary game categories and win-game categories is well known.
-Our definition of the rank of a sequence of natural numbers is heavily motivated by the game semantics, so it is likely that this is new too (though similar constructions of ordinal ranks of objects are common in mathematics).
-
-Otherwise, most of the material in this report is a straightforward translation of the existing game semantics of Abramsky, Jagadeesan, Hyland, Ong, Curien, Lamarche and so on into the transfinite setting.
-
-\subsection{Conventions}
-
-I shall denote the composition of morphisms $A\xrightarrow{\sigma}B\xrightarrow{\tau}C$ by $\comp\tau\sigma$, the disjoint union of two sets $X,Y$ by $X\cprd Y$ and the corresponding copairing of two functions $\map{f}{X}{Z},\map{g}{Y}{Z}$ by $\cmap{f\cprd g}{X\cprd Y}{Z}$.
-
-Following the $\forall$belard/$\exists$loise convention that is sometimes used for Opponent/Player, I shall refer to the opponent $O$ as `he' and the player $P$ as `she' throughout.
-
-\subsection{Acknowledgements}
-
-It goes without saying that I owe my biggest debt of gratitude for the material in this report to my supervisor, Jim Laird.
-Dr Laird introduced me to Game Semantics a year ago and suggested my initial direction of research in the subject, and his insights and instinct for the subject have been invaluable in the development of the material contained in this report, and in the preparation of the report itself -- particularly when things were going wrong.
-Dr Laird gave me some extremely useful feedback on an earlier draft of this report and supplied some of the details for the material in section \ref{SeqExpIsCofCommCom}.
-
-I am indebted to all the authors listed in the Bibliography, but I single out the seminal papers of Blass \cite{blassgames} and Abramsky-Jagadeesan \cite{abramskyjagadeesangames} for their development of the subject and their clear presentation of their full completeness results, the set of notes on Game Semantics by Martin Hyland \cite{hyland1997games} and the excellent online notes by Andrea Schalk \cite{Schalk2001GsNotes,SchalkWhatIs}.
-I also single out the PhD thesis of Martin Churchill \cite{martinsthesis}, prepared under Dr Laird's supervision.
-The work in this report can be seen as a partial sequel to some of Dr Churchill's work, and the clear presentation in his thesis has greatly helped in this task.
-
-I would also like to extend my thanks to Paul Blain Levy for his work organizing the GaLoP 2016 conference and the Midlands Graduate School 2016, both of which I attended this year.
-I presented some of this material at GaLoP and the questions and comment I received there have shaped the course of this work.
-Thanks also to Alexander Kurz for his lectures on coalgebra at the Midlands Graduate School.
-
-Thanks go to all my friends and family members who have patiently supported me while I embarked on this research.
-Thank you to CN for designing the splendid letter `G' (complete with $\sequoid$ symbols!) that features at the beginning of this introduction.
+These are games with ordinal sequences of moves.
+
+TODO: Talk about what they are and why we are interested, being careful to point out that our $\omega+1$ games correspond to games with winning conditions.
 
@@
 
-The point of specifying $L_A$ separately is that it allows us to unify the definition of a \emph{strategy}, while making clearer the behaviour observed above, whereby certain plays in $P_A$ may not occur `in normal play'; this behaviour was previously only implicit in the definition of a strategy.
+The point of specifying $L_A$ separately is that it allows us to unify the definitionn of a \emph{strategy}, while making clearer the behaviour observed above, whereby certain plays in $P_A$ may not occur `in normal play'; this behaviour was previously only implicit in the definition of a strategy.
 Our unified definition then becomes:
@@
 
-The earliest games model, found in \cite{conwaygames}, did not include a definition of which player is to move at a given position; rather, games are defined recursively as pairs of games $\{L|R\}$, where $L$ represents the positions that the left player may move into, while $R$ represents the positions that the right player may move into.
+The earliest games model, found in \cite{conwaygames}, did not include a definition of which player is to move at a given position; rather, games are defined recursively as pairs of games $\{L|R\}$, where $L$ represents the positions that the left player may move into, while $R$ represents the positions that the rigth player may move into.
 Blass's definition departs completely from this tradition; now, at every position $s$ only one of the two players is allowed to move; extending this logic on to the empty position $\emptyplay$, it follows that all games are either positive or negative.
@@
 \begin{align*}
-  \zeta_{A\implies B}(s)=(\zeta_A(s\vert_A)\Rightarrow \zeta_B(s\vert_B))\\
-  \zeta_{A\parr B}(s) = (\zeta_A(s\vert_A) \vee \zeta_B(s\vert_B))
+  \zeta_{A\implies B}(s)=(s\vert_A\Rightarrow s\vert_B)\\
+  \zeta_{A\parr B}(s) = (s\vert_A \vee s\vert_B)
 \end{align*}
@@
 
-Our approach will be similar to that of Curien's in that we will admit only negative games as objects of our category, but we will also incorporate elements of Blass's model: each position $s$ in our game will be designated either an $O$-position or a $P$-position via a function $\zeta$ and we will extend $\zeta$ to the connectives using the truth tables in Figure \ref{truthtables}.
-We shall start by developing the theory of finitary games in order to illustrate our approach, but it will not be until we start considering transfinite games that we see the value of this aspect of Blass's semantics: transfinite games may contain many non-empty plays that have no last move and we will want to designate them as $P$-positions or $O$-positions so that we know which player moves next.
+We shall adopt elements of both the Blass and the Abramsky-Jagadeesan games models; specifically, we shall use Blass's games and Abramsky-Jagadeesan's strategies.
+This means that our games model will be more restrictive than either the Blass or the Abramsky-Jagadeesan models, but this lack of flexibility will be just what we need in order to extend these games over the transfinite ordinals.
+We will later consider ways we can relax our model to recover Abramsky and Jagadeesan's games model.
 
@@
 
-  Note that $\zeta_A$ is now completely specified by $\lambda_A$ and $b_A$, so we could have specified our games more efficiently by replacing $\zeta_A$ with $b_A$ in our definition, as done in \cite{martinsthesis}.
+  Note that $\zeta_A$ is now completely specified by $\lambda_A$ and $b_A$, so we could have specified our games mor efficiently by replacing $\zeta_A$ with $b_A$ in our definition, as done in \cite{martinsthesis}.
 The slightly more unwieldy $\zeta_A$ will be useful when we come to extend our games over the ordinals, though, so we retain it.
@@
 If $\zeta_A(s)=P$, we call $s$ a \emph{$P$-play} or \emph{$P$-position}.
+
 \end{remark}
@@
 
-Ownership of moves is decided via the obvious co-pairing functions:
+Ownership of moves is decided via the obvious copairing functions:
 \begin{IEEEeqnarray*}{c}
@@
 
-  We say that $s$ is \emph{well formed with respect to $\lambda,\zeta$} if whenever $ta\prefix s$, for some $a\in M$, we have $\zeta(ta)=\lambda(a)$.
+  We say that $s$ is \emph{well formed with respect to $\lambda,\zeta$} if $s = \emptyplay$ or if $s=s'a$ and $\zeta(s)=\lambda(a)$.
 
@@
   $A\tensor B$,$A\parr B$,$A\implies B$ are well formed games.
-Moreover, $P_{A\tensor B}$ is the largest subset $X\subset P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, X)$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.
+Moreover, $P_{A\tensor B}$ is the largest subset of $P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B})$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.
   \begin{proof}
@@
 \subsection{A category of games and partial strategies}
-\label{CategoricalSemantics}
 
 Following \cite{joyalgames} and \cite{abramskyjagadeesangames}, we define a category $\G$ whose objects are games where the morphisms from a game $A$ to a game $B$ are strategies for $A\implies B$.
-For the sake of simplicity, and to avoid various technical issues, we shall require that the games in our category be \emph{negative} - namely, they should start with an opponent move.
+For the sake of simplicity, and to avoid varioius technical issues, we shall require that the games in our category be \emph{negative} - namely, they should start with an opponent move.
 In our language, we call a game $A$ \emph{negative} if $\zeta_A(\emptyplay)=P$ (and we call it positive if $\zeta_A(\emptyplay)=O$).
@@
 In order to get a category, we need a way to compose a strategy for $A\implies B$ with a strategy for $B\implies C$.
-Our treatment of composition is heavily influenced by work done by Hyland and Schalk (see \cite{hyland1997games}, \cite{hylandschalkgames} and the excellent set of notes \cite{Schalk2001GsNotes}).
-
-We shall use the usual definition of composition.  If $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, we define a set
-\[
-  \sigma\|\tau = \{\s\in (M_A \cprd M_B \cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
-  \]
-Then we define the composite strategy on $A\implies C$ to be
+We do this in the standard way (see \cite{joyalgames} or \cite{martinsthesis}, for example).
+
+Given negative games $A,B,C$ and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, define
+\[
+  \sigma\|\tau = \{\s\in(M_A\cprd M_B\cprd M_C)^*\suchthat \s\vert_{A,B}\in \sigma,\;\s\vert_{B,C}\in\tau\}
+  \]
+We then define
 \[
@@
   \]
-The process of showing that this is indeed a strategy for $A\implies C$, and that composition is associative, will be quite involved.
-We shall start by recording some nice properties of negative games that will tell us that $\comp\tau\sigma$ is alternating:
+Before proving that this is indeed a strategy for $A\implies C$, we first record a nice property of negative games that will make things particularly easy for us:
 
@@
   Furthermore, (i) and (ii) hold if we replace $\tensor$ with $\implies$ throughout and if we replace (i) by the statement that either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=O$.
-  \begin{proof}
-    See Appendix \ref{nice-negative-games-proof}.
-  \end{proof}
   \label{nice-negative-games}
@@
 
-A corollary of our result is that we have:
-\begin{align*}
-  P_{A\tensor B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\tensor B}$}\} \\
-  P_{A\implies B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\implies B}$}\}
-\end{align*}
-if $A,B$ are negative games.  In other words, we can ignore the well-formedness condition on plays if we are dealing with only negative games.
-
-This proposition allows us to prove the following useful fact:
-
-\begin{lemma}
-  \label{alternatingsequenceslemma}
-  Let $A,B,C$ be negative games, and let $\s\in (M_A\cprd M_B\cprd M_C)^*$.  If any two of the following statements are true, then so is the third:
-  \begin{gather*}
-    \s\vert_{A,B}\in P_{A\implies B}\\
-    \s\vert_{A,C}\in P_{A\implies C}\\
-    \s\vert_{B,C}\in P_{B\implies C}
-  \end{gather*}
-  \begin{proof}
-    See Appendix \ref{alternatingsequenceslemmaproof}.
-  \end{proof}
-\end{lemma}
-
-Now we can move on to the main work.  We start with a surprising lemma about strategies on the implication $A\implies B$.
-
-\begin{lemma}
-  \label{PlayInStrategyDeterminedByComponents}
-  Let $A,B$ be games and let $\sigma$ be a strategy for $A\implies B$.  Suppose that $s,t\in\sigma$ are such that $s\vert_A=t\vert_A$ and $s\vert_B=t\vert_B$.  Then $s=t$.
-  \begin{proof}
-    Suppose that $s\ne t$.
-Let $r\prefix s,t$ be the longest common subsequence of $s$ and $t$ - so we have $rx\prefix s, ry\prefix t$ for some moves $x,y\in M_{A\implies B}$ with $x\ne y$.
-Since $rx,ry$ are both substrings of the strategy $\sigma$, $r$ must be a $P$-position and therefore the moves $x,y$ must take place in the same game.
-Without loss of generality, suppose that $x,y\in M_A$.
-Then we have $r\vert_A x\prefix s\vert_A,r\vert_Ay\prefix t\vert_A$ and so $s\vert_A\ne t\vert_A$.
-  \end{proof}
-\end{lemma}
-
-Thus we see that the plays according to some given strategy $\sigma$ for $A\implies B$ are characterized by their $A$- and $B$-components.
-More is true, however: given games $A$ and $B$, the strategies on $A\implies B$ are characterized by the $A$- and $B$-components of their constituent plays:
-\begin{lemma}
-  \label{HylandSchalkFaithful}
-  Let $A,B$ be games and let $\sigma,\sigma'$ be strategies for $A\implies B$ such that
-  \[
-    \{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}=\{(s'\vert_A,s'\vert_B)\suchthat\textrm{$s'\in\sigma'$ is a $P$-position}\}
-    \]
-  Then $\sigma=\sigma'$.
-  \begin{proof}
-    See Appendix \ref{HylandSchalkFaithfulProof}.
-  \end{proof}
-\end{lemma}
-
-Given games $A,B$ and a strategy $\sigma$ for $A\implies B$, the set
-\[
-  \{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}\subset P_A\times P_B
-  \]
-is a \emph{relation} between $P_A$ and $P_B$.  Writing $\grel\sigma\subset P_A\times P_B$, we will show that if $A,B,C$ are games and $A\xrightarrow{\sigma}\map{\tau}{B}{C}$ are morphisms, then:
-\[
-  \grel{\comp\tau\sigma}=\comp{\grel\tau}{\grel\sigma}
-  \]
-under the usual composition of relations:
-\[
-  \comp{\grel\tau}{\grel\sigma} = \{(s,t)\in P_A\times P_C\suchthat \exists u\in P_B\esuchthat (s,u)\in\grel\sigma,\;(u,t)\in\grel\tau\}
-  \]
-Thus we will get a functor $\cmap{\F}{\G}{\Rel}$, where $\G$ is our category of negative games and $\Rel$ is the category of sets and relations.
-Proposition \ref{HylandSchalkFaithful} then tells us that this functor is faithful.
-
-It is clear from the definition of $\comp\tau\sigma$ that $\grel{\comp\tau\sigma}\subset\comp{\grel\tau}{\grel\sigma}$; indeed if $\s\in\sigma\|\tau$, then $(\s\vert_A,\s\vert_B)\in\grel\sigma$ and $(\s\vert_B,\s\vert_C)\in\grel\tau$, so $(\s\vert_A,\s\vert_C)\in\comp{\grel\tau}{\grel\sigma}$.
-To show the reverse inclusion, we need to show the following: if $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$, then there is some $\s\in (M_A\cprd M_B\cprd M_C)^*$ such that $\s\vert_{A,B}=s$ and $\s\vert_{B,C}=t$.
-
-This can be shown in an easy way.
-Roughly speaking, we write out the sequence $s$, and then insert immediately after each $B$-move the $C$-moves from $t$ that occur after that $B$-move.
-This technique works for arbitrary sequences and is sufficient to prove that $\grel{\comp\tau\sigma}=\comp{\grel\tau}{\grel\sigma}$.
-However, it turns out that if $s$ and $t$ are alternating plays in $A\implies B$ and $B\implies C$ then this interleaving is unique - and even more is true:
-
-\begin{lemma}
-  \label{LiftingLemma}
-  Let $A,B,C$ be negative games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Suppose that $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$.
-Let $n=\length(s)+\length(t\vert_C)$; i.e., the total number of unique terms of $s$ and $t$ after we have identified their common $B$-component.
-Then for all $k$ with $0\le k\le n$, there is a unique sequence $\s^k\in\sigma\|\tau$ of length $k$ such that $\s^k\vert_A\prefix s\vert_A$ and $\s^k\vert_C\prefix t\vert_C$.
-Moreover, for this $\s^k$ we have $\s^k\vert_{A,B}\prefix s$ and $\s^k\vert_{B,C}\prefix t$, and if $j\le k$ then $\s^j\prefix \s^k$.
-  \begin{proof}
-    See Appendix \ref{LiftingLemmaProof}.
-  \end{proof}
-\end{lemma}
-
-Note that Lemma \ref{LiftingLemma} is stronger than saying that there is a unique sequence $\s^k$ of length $k$ such that $\s^k\vert_{A,B}\prefix s$ and $\s^k\vert_{B,C}\prefix t$.
-Instead, we are saying that there exists a sequence $\s^k$ with those properties, but that it is uniquely determined even when we make no requirement on its $B$-component other than that the whole sequence is contained in $\sigma\|\tau$.
-
-As a corollary, we see that the sequences $s$ and $t$ may be interleaved: set $\s=\s^n$; then we have $\s\vert_{A,B}\prefix s$ and $\s\vert_{B,C}\prefix t$.
-In fact, we have $\s\vert_{A,B}=s$ and $\s\vert_{B,C}=t$ by a length argument:
-\[
-  \length(\s\vert_{A,B})\le\length(s)=n-\length(t\vert_C)\le n-\length(\s\vert_C)=\length(\s\vert_{A,B})
-  \]
-so we must have equality everywhere, and similarly for $\s\vert_{B,C}$ and $t$.
-
-We now have all the ingredients ready to prove that $\comp\tau\sigma$ is a well-defined strategy.
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $\comp\tau\sigma$ (as defined above) is a strategy for $A\implies C$.
-
-  \begin{proof}
-    By Lemma \ref{alternatingsequenceslemma}, $\comp\tau\sigma\in P_{A\implies C}$.
-Moreover, it is non-empty, since it contains $\emptyplay$.
-We need to show that the two strategy conditions hold for $\comp\tau\sigma$.
-
-    Firstly, suppose that $\s\in\sigma\|\tau$ and $\s\vert_{A,C}$ is a $P$-play in $A\implies C$.
-Suppose that $\s\vert_{A,C} a\in P_{A\implies C}$ for some $a\in M_A$.
-We claim that $\s a\in\sigma\|\tau$.
-
-    Indeed, certainly $\s a\vert_{B,C}=\s\vert_{B,C}\in\tau$.
-Moreover, we have $\s a\vert_{A,C}\in P_{A\implies C}$, so Lemma \ref{alternatingsequenceslemma} tells us that $\s a\vert_{A,B}\in P_{A\implies B}$.
-
-    Since $a$ is an $O$-move in $A\implies B$, it is an $O$-move in $A\implies C$.
-Since $\s\vert_{A,B}\in\sigma$, we must have $\s a\vert_{A,B}\in\sigma$, by the definition of a strategy.
-So $\s a\in\sigma\|\tau$.
-
-    By a symmetrical argument, if $\s\vert_{A,C} c\in P_{A\implies C}$ for some $c\in M_C$, then $\s c\in\sigma\|\tau$.
-
-    For the second strategy property, suppose that $s\in\comp\tau\sigma$ is n $O$-play and that $sx, sy\in\comp\tau\sigma$.
-We claim that $x=y$.
-By the definition of $\comp\tau\sigma$, there must be sequences $\s,\t\in\sigma\|\tau$ with $\s\vert_{A,C}=sx$ and $\t\vert_{A,C}=sy$.
-Moreover, by removing any $B$-moves form the end of $\s,\t$, we may assume that the last move in $\s$ is $x$ and the last move in $\t$ is $y$.
-We may write $\s=\s'\b x$ and $\t=\t'\bbeta y$, where $\b$ and $\bbeta$ are sequences composed entirely out of $B$-moves and neither $\s'$ nor $\t'$ ends with a $B$-move.
-In particular, $\s'\vert_{A,C}=\t'\vert_{A,C}=s$.
-
-    Without loss of generality, $\length(\s')\le\length(\t')$.  Let $\t''$ be the prefix of $\t'$ that has the same length as $\s'$, writing $\t'=\t''\r$.
-
-    Now $\s'$ and $\t''$ have the same length, and we have
-    \[
-      \begin{matrix}
-        \s'\vert_A\prefix\s\vert_A & \t''\vert_A\prefix\s\vert_A \\
-        \s'\vert_C\prefix\s\vert_C & \t''\vert_C\prefix\s\vert_C
-      \end{matrix}
-      \]
-    so we must have $\s'=\t''$, by uniqueness in Lemma \ref{LiftingLemma}.  Now observe that we have
-    \[
-      \s'\vert_{A,C}=\t'\vert_{A,C}=\t''\vert_{A,C}\r\vert_{A,C}=\s'\vert_{A,C}\r\vert_{A,C}
-      \]
-    Since $\t'=\t''\r$ does not end with a $B$-move, $\r\vert_{A,C}$ must be non-empty if $\r$ is non-empty.  Therefore $\r=\emptyplay$, and so $\t'=\t''=\s'$.
-
-    We now claim that $\length(\b)=\length(\bbeta)$.
-Indeed, suppose instead that $\length(\b)<\length(\bbeta)$.
-Then there would be a prefix $\bbeta'\prefix\bbeta$ of length $\length(\b)+1$.
-Then we would have
-    \[
-      \begin{matrix}
-        \s'\b x\vert_A=\s\vert_A & \s'\bbeta'\vert_A=\s'\vert_A\prefix\s\vert_A \\
-        \s'\b x\vert_C=\s\vert_C & \s'\bbeta'\vert_C=\s'\vert_C\prefix\s\vert_C
-      \end{matrix}
-      \]
-    and so $\s'\b x=\s'\bbeta'$ by Lemma \ref{LiftingLemma}, which is clearly impossible.
-Therefore, $\length(\b)=\length(\bbeta)$.
-Now we can apply Lemma \ref{LiftingLemma} in the same way to tell us that $\b=\bbeta$.
-
-    Suppose that $\zeta_B(\s'\b\vert_B)=P$.
-Since $\s'\b\in\sigma\|\tau$, this means that $\zeta_A(\s'\b\vert_A)=P$, by Proposition \ref{nice-negative-games}(i).
-Therefore, $\zeta_{A\implies B}(\s'\b)=P$, so $x$ and $y$ must both be moves in $C$.
-Then we have $\s'\b\vert_{B,C}x,\s'\b\vert_{B,C}y\in\tau$, and so $x=y$ by the definition of a strategy.
-
-    By a symmetrical argument, if $\zeta_B(\s'\b\vert_B)=O$, then $x$ and $y$ must both be moves in $A$.  We then have $\s'\b\vert_{A,B}x,\s'\b\vert_{A,B}y\in\sigma$, so $x=y$.
-  \end{proof}
-\end{proposition}
-
-Now we are ready to define our category $\G$ of games.
-We have defined composition of strategies, so we need to define identity morphisms.
-Identity morphisms are given by the copycat strategy, as usual:
-\[
-  \id_A=\left\{s\in P_{A\implies A}\suchthat\textrm{for all even length $t\prefix s$, $t\vert_\bneggame{A}=t\vert_A$}\right\}
-  \]
-We can now state our first main result.
-
-\begin{theorem}
-  \label{IsCategory}
-  The collection of negative games, with morphisms from $A$ to $B$ given by strategies on $A\implies B$ with the notions of composition and identity given above, forms a category $\G$.
-Moreover, there is a faithful functor $\F\from\G\to\Rel$, where $\Rel$ is the category of sets and relations, given by sending a game $A$ to the set of plays $P_A$ and sending a strategy $\sigma\from A\implies B$ to the set
-  \[
-    \grel{\sigma}=\{(s\vert_A,s\vert_B)\suchthat \textrm{$s\in\sigma$ is a $P$-position}\}\subset P_A\times P_B
-    \]
-  \begin{proof}
-    We shall make much use of the relational content of a strategy.
-We first need to show that the identity is indeed an identity and that composition is associative.
-For the identity, note that $\grel{\id_A}=\Delta_{P_A}\subset P_A\times P_A$, the identity relation in $\Rel$.
-If $B,C$ are negative games and $\sigma\colon B\implies A,\tau\colon A\implies C$ are strategies, then from our earlier discussion we have
-    \[
-      \grel{\comp{\id_A}{\sigma}}=\comp{\grel{\id_A}}{\grel\sigma}=\comp{\Delta_{P_A}}{\grel\sigma}=\grel\sigma
-      \]
-    and therefore $\comp{\id_A}{\sigma}=\sigma$, by Lemma \ref{HylandSchalkFaithful}.  Similarly, $\comp{\tau}{\id_A}=\tau$.
-
-    For associativity of composition, we hijack the associativity in $\Rel$: if $A,B,C,D$ are negative games, and $\map{\sigma}AB\xrightarrow{\tau}\map{\upsilon}CD$ are morphisms, then we have:
-    \begin{align*}
-      \grel{\comp{(\comp\upsilon\tau)}{\sigma}} & = \comp{\grel{\comp\upsilon\tau}}{\sigma} \\
-        & = \comp{(\comp{\grel\upsilon}{\grel\tau})}{\grel\sigma} \\
-        & = \comp{\grel\upsilon}{(\comp{\grel\tau}{\grel\sigma})} \quad\textrm{by associativity in $\Rel$} \\
-        & = \comp{\grel\upsilon}{\grel{\comp\tau\sigma}} \\
-        & = \grel{\comp{\upsilon}{(\comp\tau\sigma)}}
-    \end{align*}
-    and so $\comp{(\comp\upsilon\tau)}{\sigma}=\comp{\upsilon}{(\comp\tau\sigma)}$, by Lemma \ref{HylandSchalkFaithful}.
-
-    We have already shown that the map $\F$ respects composition, so it is a functor.  It is faithful by Lemma \ref{HylandSchalkFaithful}.
-  \end{proof}
-\end{theorem}
-
-\subsection{Total strategies and winning conditions}
-
-Let $A$ be a game.
-We call a strategy $\sigma$ for $A$ \emph{total} if it satisfies the additional requirement that whenever $s\in\sigma$ is an $O$-play, there exists some $a\in M_A$ such that $sa\in\sigma$ (before we only required that such a play be unique if it existed).
-
-We might want to talk about a category of negative games and total strategies.  However, we cannot do this immediately, since the composition of two total strategies need not be total.
-
-\begin{example}
-  \label{TotalCompositionExample}
-  Let $\st$ be the negative game where each player has a unique move at every position:
-  \begin{gather*}
-    M_{\st} = \{q,a\} \\
-    \lambda_{\st}(q) = O,\;\lambda_{\st}(a)=P \\
-    P_{\st} = \{\emptyplay, q, qa, qaq, qaqa, \dots\}
-  \end{gather*}
-
-  Let $I$ be the negative game with no moves and let $\bot$ be the negative game with a single opponent move and no further play:
-  \[
-    \begin{matrix}
-      M_I=\emptyset & M_\bot = \{*\} \\
-      \lambda_I=\emptyset  & \lambda_\bot(*)=O \\
-      P_I=\{\emptyplay\} & P_\bot = \{\emptyplay, *\}
-    \end{matrix}
-    \]
-
-  It is easy to see that if $A$ is a negative game then strategies for $I\implies A$ are the same thing as strategies for $A$ and that strategies for $A\implies\bot$ are the same thing as opponent strategies for $A$.
-So we get morphisms $\cmap{\sigma}{I}{\st},\cmap{\tau}{\st}{\bot}$ given by the unique player and opponent strategies for $\st$:
-  \[
-    \sigma = P_\st\quad\tau = \{*s\suchthat s\in P_\st\}
-    \]
-  Moreover, both these strategies are total.
-
-  The plays in $\sigma\|\tau$ are now those sequences $\s\in(M_I\cprd M_\st\cprd M_\bot)^*$ such that:
-  \begin{gather*}
-    \s\vert_A=\emptyplay \\
-    \s\vert_B\in P_\st \\
-    \textrm{If $\s\ne\emptyplay$ then $\s\vert_C=*$}
-  \end{gather*}
-
-  Upon restricting these sequences to $A$ and $C$, we see that $\comp\tau\sigma$ contains only two plays - $\emptyplay$ and $*$.
-$*$ is an $O$-play with no $P$-reply in $\comp\tau\sigma$, so $\comp\tau\sigma$ is not a total strategy.
-\end{example}
-
-Clearly it is the infinite play in the game $\st$ that is causing the problem.
-We can get around this by insisting that our games contain no infinite plays: if $A$ is a game, we say $A$ has an infinite play if $(P_A,\prefix)$ has an infinite chain.
-
-\begin{proposition}
-  \label{BoundedTotalComposition}
-  Let $A,B,C$ be negative games and assume that $B$ has no infinite play.
-Let $\sigma$ be a total strategy for $A\implies B$ and let $\tau$ be a total strategy for $B\implies C$.
-Then $\comp\tau\sigma$ is a total strategy for $A\implies C$.
-  \begin{proof}
-    We have already shown that $\comp\tau\sigma$ is a strategy for $A\implies C$, so we need to show that it is total.
-Let $s\in\comp\tau\sigma$ be an $O$-play.
-We seek a $P$-move $x$ such that $sx\in\comp\tau\sigma$.
-
-    By the definition of $\comp\tau\sigma$, there is some $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-Since $P_B$ contains no infinite chain, we may take $\s$ to be maximal such that $\s\vert_{A,B}=s$.
-
-    Since $s$ is an $O$-play, $\s\vert_A$ must be a $P$-play in $A$ and $\s\vert_C$ must be an $O$-play in $C$.
-Consider the $B$-component $\s\vert_B$ of $\s$.
-If this is an $O$-play, then $\s\vert_{A,B}$ is an $O$-play in $\sigma$, so, by totality of $\sigma$, there exists $x$ such that $\s\vert_{A,B}x\in\sigma$ and therefore $\s x\in\sigma\|\tau$.
-Similarly, if $\s\vert_B$ is a $P$-play, then $\s\vert_{B,C}$ is an $O$-play in $\tau$, so there exists $x$ such that $\s\vert_{B,C}x\in\tau$ and so $\s x\in\sigma\|\tau$.
-
-    If $x$ is a $B$-move, we have $\s x\vert_{A,C}=s$, contradicting maximality of $s$.  Therefore, $x$ is an $A$- or $C$-move, and we have $sx\in\comp\tau\sigma$.
-  \end{proof}
-\end{proposition}
-
-The result of this proposition means that we could create a category of games and total strategies by requiring that all our games have no infinite plays.
-However, this approach will not work for us, since our particular version of the exponential connective $\oc$ introduces infinite plays into all non-empty games.
-Moreover, it seems a bit wasteful to require that none of the games $A,B,C$ have infinite plays when it is only infinite plays in game $B$ that are causing problems.
-
-Fortunately, there is a cleverer way of getting around the problem.
-Recall that we defined a game to be given by a tuple $(M_A,\lambda_A,\zeta_A,P_A)$.
-Given such a game, and given some subset $X\subset P_A$, define $X^\omega$ to be the set of all infinite plays in the game -- i.e., the set of all infinite sequences $s\in M_A^\omega$ all of whose prefixes lie in $X$.
-
-\begin{definition}
-  A \emph{win-game} is a tuple $A=(M_A,\lambda_A,\zeta_A,P_A,W_A)$ where $(M_A,\lambda_A,\zeta_A,P_A)$ is a game as defined before and $\cmap{W_A}{P_A^\omega}{\OP}$ is a function telling us whether each infinite play is a win for player $P$ or for player $O$.
-\end{definition}
-
-To distinguish our original games from these win-games, we shall refer to the earlier games as \emph{finitary games}.
-
-We can define an appropriate notion of strategies for these games.
-If $A$ is a win-game, then a \emph{winning strategy} for $A$ is a total strategy for $(M_A,\lambda_A,\zeta_A,P_A)$ such that $W_A(s)=P$ for all $s\in\sigma^\omega$.
-
-We can also extend our connectives to our new win games.
-At the level of finitary games, our definitions of the connectives are unchanged, and it remains to define the $W$-functions.
-If $A$ is a win game, then $W_{\neggame A}=\neg\circ W_A$.
-
-If $A$ and $B$ are win games, we would like to define $W_{A\tensor B}$ by
-\[
-  W_{A\tensor B}(s) = W_A(s\vert_A) \wedge W_B(s\vert_B)
-  \]
-However, this is not well defined at present because one out of $s\vert_A$ and $s\vert_B$ might be a finite sequence even if $s$ is infinite.
-For this purpose, it will be convenient to extend our function $W_A$ to include finite plays as well using $\zeta_A$:
-\[
-  W_A^* = \zeta_A\cprd W_A\from P_A\cprd P_A^\omega \to\OP
-  \]
-We can then define
-\[
-  W_{A\tensor B}(s) = W_A^*(s\vert_A)\wedge W_B^*(s\vert_B)
-  \]
-Indeed, we could do away with $\zeta_A$ and $W_A$ altogether, replacing them with $W_A^*$.
-Since the rule for $\zeta_{A\tensor B}$ is also given by a conjunction, our rule for the tensor product becomes:
-\[
-  W_{A\tensor B}^*(s) = W_A^*(s\vert_A)\wedge W_B^*(s\vert_B)
-  \]
-This will be the starting point for our development of transfinite games in the next section.
-In our formulation, finitary games are games played over the ordinal $\omega$, while win-games will be games played over the ordinal $\omega+1$.
-We make no special distinction between finite and infinite plays, so the function $\zeta_A$ for our transfinite games incorporates both the function $\zeta_A$ and the function $W_A$ from our win-games, in the same manner as the function $W_A^*$ defined above.
-One advantage of this point of view is that we no longer have to treat the finite- and infinite-play cases separately, but can give a uniform presentation.
-
-For now, let us concentrate on developing the theory of win-games in the traditional way.
-Having defined the tensor product, we may recover the definitions of the par $\parr$ and linear implication $\implies$ of two games as usual.
-In particular, this means that we have
-\[
-  W_{A\implies B}^*(s) = (W_A(s\vert_A) \Rightarrow W_B(s\vert_B))
-  \]
-
-It is worth examining the definitions of the $W$-functions for tensor and implication.
-Recall that in the tensor product, it is always player $O$ who switches games.
-Therefore, if $s$ is an infinite play in $A\tensor B$ and $s\vert_A$ is finite and non-empty, it must be the case that player $P$ made the last move in $s$, and so $W_A^*(s\vert_A)=P$.
-If we assume our games are negative, then this extends to the case that $s\vert_A$ is empty.
-This tells us that player $P$ wins an infinite play $s$ in $A\tensor B$ if and only if each component is either $P$-winning or is finite.
-
-Similarly, player $P$ wins an infinite play $s$ in $A\implies B$ if and only if $s\vert_A$ is infinite and $O$-winning or if $\s\vert_B$ is either finite or is infinite and $P$-winning.
-Since it is player $P$ who switches games in $A\implies B$, if $s\vert_A$ is finite then it will end with an $O$-move, so will count as an $O$-winning play.
-
-The point now is that if $A,B,C$ are negative win-games and $\sigma$ and $\tau$ are strategies for $A\implies B$ and $B\implies C$, we will never end up in the situation we were in in Example \ref{TotalCompositionExample} where we have an infinite play in $B$ that stops us from replying in the composition $\comp\tau\sigma$.
-In that example, the unique infinite play in $\st$ would have to be either $O$-winning or $P$-winning, so either $\sigma$ or $\tau$ would not be a valid winning strategy.
-
-\begin{proposition}
-  \label{CompWinningIsWinning}
-  Let $A,B,C$ be negative win-games, let $\sigma$ be a winning strategy for $A\implies B$ and let $\tau$ be a winning strategy for $B\implies C$.
-Then $\comp\tau\sigma$ is a winning strategy for $A\implies C$.
-  \begin{proof}
-    See Appendix \ref{CompWinningIsWinningProof}.
-  \end{proof}
-\end{proposition}
-
-We get another result:
-
-\begin{theorem}
-  The collection of all negative win-games, with morphisms from $A$ to $B$ given by winning strategies on $A\implies B$ and composition defined as above, is a category.
-  \begin{proof}
-    We have shown already that the composition of two winning strategies is a winning strategy.
-Associativity of composition is inherited from finitary games and the identity strategy is winning for $A\implies A$.
-  \end{proof}
-\end{theorem}
-
-\section{Transfinite games}
-
-\begin{note}
-  In this section, we assume familiarity with ordinals, ordinal arithmetic and transfinite induction/recursion.
-We shall frequently identify an ordinal $\alpha$ with the set $\{\beta\suchthat\beta<\alpha\}$ of all ordinals less than $\alpha$ without comment.
-\end{note}
-
-In the last section, we came across win-games, where in addition to the usual function $\cmap{\zeta_A}{P_A}{\OP}$ we have a function $\cmap{W_A}{P_A^\omega}{\OP}$, where $P_A^\omega$ is the set of infinite limits of plays in $P_A$.
-We saw that it is useful to combine these two functions into one:
-\[
-  W_A^* = \zeta_A\cprd W_A\from P_A\cprd P_A^*\to\OP
-  \]
-This suggests that it might make sense to combine $P_A$ and $P_A^\omega$ into one a single set $\overline{P_A}$ and use the function $W_A^*$ instead of $\zeta_A$ and $W_A$.
-This new set will contain both finite and infinite plays, and the infinite plays will be precisely the limits of the finite plays.
-In this way, the set of possible lengths of plays in $\overline{P_A}$ is the set $\{0,1,2,3,\dots,\omega\}$, or the ordinal $\omega+1$.
-
-Contrast this with the finitary case, in which the set of possible lengths of plays is the set $\{0,1,2,3,\dots\}$, or the ordinal $\omega$.
-In the coming sections, we will generalize these results so that we end up with games where the plays can have much larger ordinal lengths.
-Win-games will be taken to be the motivating example throughout.
-
-\subsection{Transfinite Games and Strategies}
-
-We fix some ordinal $\alpha$ throughout.  Given a set $M$, we write $M^{*<\alpha}$ for the set of all ordinal-length sequences of elements of $M$ whose length is less than $\alpha$.
-
-\begin{definition}
-  A \emph{game over $\alpha$}, or an \emph{$\alpha$-game}, is given by a tuple
-  \[
-    A = (M_A, \lambda_A, \zeta_A, P_A)
-    \]
-  where
-  \begin{itemize}
-    \item $M_A$ is a set of moves.
-    \item $\cmap{\lambda_A}{M_A}{\OP}$ is a function telling us which player may make each move.
-    \item $P_A$ is a set of pairs $(\beta, s)$, where $\beta<\alpha$ is some ordinal and $\cmap{s}{\beta}{M_A}$ is a sequence of moves of length $\beta$.  
-    \item $\cmap{\zeta_A}{P_A}{\OP}$ tells us which player owns each position.
-  \end{itemize}
-
-  We will normally abuse notation and write $s$ instead of $(\beta, s)$ and $\length(s)$ instead of $\beta$.
-If $a\in M_A$, we will write $a$ for the $1$-move play $(1, a)$, and $st$ for the concatenation of two sequences $s$ and $t$ (where $\length(st)=\length(s)+\length(t)$).
-We will write $t\prefix s$ if $\length(t)\le\length(s)$ and $s\vert_{\length(t)}=t$.
-
-  To be called a game, $(M_A, \lambda_A, \zeta_A, P_A)$ has to satisfy four rules.
-  \begin{description}
-    \item[Prefix closure] $P_A$ must be closed under the relation $\prefix$.  
-    \item[Well-formedness] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.  
-    \item[Alternating condition] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s)=\neg\zeta_A(sa)$.
-    \item[Limit condition] If $\mu<\alpha$ is a limit ordinal and $s\in(M_A)^\mu$ is a sequence of length $\mu$ such that every proper prefix $t\pprefix s$ is in $P_A$, then $s$ is in $P_A$.  
-  \end{description}
-\end{definition}
-
-\begin{remark}
-  In the $\omega+1$ case, the limit condition tells us that the plays of length $\omega$ in $P_A$ are precisely those infinite plays all of whose finite prefixes lie in $P_A$.
-It also guarantees that $P_A$ is non-empty, since the empty play $\emptyplay$ will always satisfy the conditions.
-
-  In the $\omega+1$ case, $\zeta_A$ will take the role of what we previously called $W_A^*$, while $P_A$ takes the role of what we called $P_A\cprd P_A^\infty$.  
-\end{remark}
-
-We define strategies for these games in much the same way that we defined them before:
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  A (partial) \emph{strategy} for $A$ is a subset $\sigma\subset P_A$ satisfying three conditions:
-  \begin{description}
-    \item[$\sigma$ contains all $O$-replies] If $s\in\sigma$ is a $P$-play and $sa\in P_A$ is an $O$-response, then $sa\in\sigma$.
-    \item[$P$-replies are unique] If $s\in\sigma$ is an $O$-play and $sa,sb\in\sigma$ are $P$-responses, then $a=b$.
-    \item[Limit condition] If $\mu<\alpha$ is a limit ordinal and $s\in P_A$ is a sequence of length $\mu$ such that every proper prefix $t\pprefix s$ lies in $\sigma$, then $s\in\sigma$.
-  \end{description}
-
-  We call $\sigma$ \emph{total} if it satisfies the extra requirement:
-
-  \begin{description}
-    \item[$P$ always has a reply] If $s\in\sigma$ is an $O$-play, then there is some $P$-move $a\in M_A$ with $sa\in\sigma$.
-  \end{description}
-\end{definition}
-
-The only new part of this is the limit condition.
-Let us examine what it means in the $\omega+1$ case.
-Play according to a total strategy $\sigma$ gives rise to a sequence of plays $\emptyplay \prefix s_1\prefix s_2\prefix\dots$ (were $s_i$ has length $i$).
-The limit condition then tells us that the limit $s_\omega$ of these plays must be contained in $\sigma$.
-If $\zeta_A(s_\omega)=O$ then $P$ has no response to $s_\omega$ (since there are no plays of length $\omega+2$), contradicting totality of $\sigma$.
-So for $\sigma$ to be a total strategy, we must have $\zeta_A(s_\omega)=P$ for every $s_\omega$ arising as the limit of finite plays according to $\sigma$.
-So total strategies for $\omega+1$-games are exactly the same thing as the winning strategies for win-games that we defined earlier.
-
-If $s\in P_A$ and $\length(s)$ is a successor ordinal, we will call $s$ a \emph{successor play} or \emph{successor position}.
-If $\length(s)$ is a limit ordinal, we will call $s$ a \emph{limiting play} or \emph{limiting position}.
-
-\subsection{Connectives}
-
-We may define connectives for $\alpha$-games in much the same way that we defined them for finitary games and win-games.
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  The negation $\neggame A$ of $A$ is given by
-  \begin{itemize}
-    \item $M_\bneggame A=M_A$
-    \item $\lambda_\bneggame A = \neg\circ\lambda_A$
-    \item $\zeta_\bneggame A = \neg\circ\zeta_A$
-    \item $P_\bneggame A = P_A$
-  \end{itemize}
-\end{definition}
-
-For the other connectives -- $\tensor$, $\parr$ and $\implies$ -- we will use interleaved plays.
-If $A$ and $B$ are $\alpha$ games, then our interleaved plays will be sequences taking values in $M_A\cprd M_B$.
-If $\beta<\alpha$ and $s\in(M_A\cprd M_B)^\beta$, we may write $\beta_A$ for $s\inv(M_A)$ and $\beta_B$ for $s\inv(M_B)$.
-
-\begin{lemma}
-  \label{TechnicalOrdinalLemma}
-  Let $\beta$ be an ordinal, and let $\gamma$ be any subset of $\beta$.  Then $\gamma$ inherits a well-ordering from $\beta$ and, as ordinals, we have $\gamma\le\beta$.  
-  \begin{proof}
-    Any subset of $\gamma$ is a subset of $\beta$, so it has a least element.  Therefore, the inherited order on $\gamma$ is a well-order.
-
-    Suppose for a contradiction that $\beta<\gamma$.  Then we have order preserving injections
-    \[
-      i\from \gamma\hookrightarrow\beta\quad j\from\beta\hookrightarrow\gamma
-      \]
-    where $i$ is inclusion of $\gamma$ as a subset of $\beta$ and $j$ is inclusion of $\beta$ as a proper initial prefix of $\gamma$.
-Let $f\from\gamma\hookrightarrow\gamma$ be the composition $\gamma\xhookrightarrow{i}\beta\xhookrightarrow{j}\gamma$.
-Then $f$ is order preserving.
-
-    Let $S=\{\delta\in\gamma\suchthat f(\delta)<\delta\}$.
-$S$ is non-empty, since $\beta\in S$ (considering $\beta$ as an element of $\gamma$), so $S$ has a least element $\xi$.
-Now $f(\xi)<\xi$, so $f(f(\xi))<f(\xi)$, since $f$ is order-preserving and injective.
-Therefore, $\xi\le f(\xi)$ by minimality of $\xi$, which is a contradiction.
-  \end{proof}
-\end{lemma}
-
-Using Lemma \ref{TechnicalOrdinalLemma}, we see that $\beta_A,\beta_B\le\beta$; in particular, they are both less than $\alpha$, so we get induced sequences $s\vert_A$ of length $\beta_A$ and $s\vert_B$ of length $\beta_B$.
-We define
-\[
-  P_A\|P_B = \left\{s\in (M_A\cprd M_B)^{*<\alpha}\suchthat s\vert_A\in P_A,\;s\vert_B\in P_B\right\}
-  \]
-
-We may now define functions $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}\from P_A\|P_B\to\OP$ as before:
-\begin{IEEEeqnarray*}{rCc}
-  \zeta_{A\tensor B}(s) & = & \zeta_A(s\vert_A)\wedge\zeta_B(s\vert_B)\\
-  \zeta_{A\parr B}(s) & = & \zeta_A(s\vert_A)\vee\zeta_B(s\vert_B)\\
-  \zeta_{A\implies B}(s) & = & (\zeta_A(s\vert_A)\Rightarrow \zeta_B(s\vert_B))
-\end{IEEEeqnarray*}
-
-Our definitions of the functions $\lambda_{A\tensor B},\lambda_{A\parr B},\lambda_{A\implies B}\from M_A\cprd M_B\to \OP$ are the same as before:
-\begin{gather*}
-  \lambda_{A\tensor B}=\lambda_{A\parr B}=\lambda_A\cprd \lambda_B \\
-  \lambda_{A\implies B} = (\neg\circ\lambda_A)\cprd \lambda_B
-\end{gather*}
-
-Given a set $M$, a prefix-closed set $P\subset M^{*<\alpha}$ and functions $\cmap{\lambda}{M}{\OP},\cmap{\zeta}{P}{\OP}$, we say that a play $s\in P$ is \emph{well-formed with respect to $\lambda,\zeta$} if whenever $ta\prefix s$ (with $a\in M$) we have $\zeta(ta)=\lambda(a)$.
-We say that $s$ is \emph{alternating with respect to $\zeta$} if whenever $t,ta$ are prefixes of $s$ (where $a\in M$), we have $\zeta(t)=\neg\zeta(ta)$.
-
-As before, we now define:
-
-\begin{IEEEeqnarray*}{rCl}
-  P_{A\tensor B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\tensor B}$ \\ $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$}}\right\} \\
-  P_{A\parr B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\parr B}$ \\ $s$ is well formed with respect to $\zeta_{A\parr B},\lambda_{A\parr B}$}}\right\} \\
-  P_{A\implies B} & = & \left\{s\in P_A\|P_B \;\middle|\; \mbox{\pbox{\textwidth}{$s$ is alternating with respect to $\zeta_{A\implies B}$ \\ $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$}}\right\}
-\end{IEEEeqnarray*}
-
-Setting $M_{A\tensor B}=M_{A\parr B}=M_{A\implies B} = M_A\cprd M_B$, and restricting $\zeta_{A\tensor B},\zeta_{A\parr B},\zeta_{A\implies B}$ to $P_{A\tensor B},P_{A\parr B},P_{A\implies B}$ respectively, we arrive at our definitions of the connectives:
-\begin{IEEEeqnarray*}{cCc}
-  A\tensor B & = & (M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B})\\
-  A\parr B & = & (M_{A\parr B}, \lambda_{A\parr B}, \zeta_{A\parr B}, P_{A\parr B})\\
-  A\implies B & = & (M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})
-\end{IEEEeqnarray*}
-
-\begin{proposition}
-  \label{TransTensorWellFormed}
-  $A\tensor B$, $A\parr B$ and $A\implies B$ are well formed games.
-Moreover, $P_{A\tensor B}$ is the largest subset $X\subset P_A\|P_B$ such that $(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, X)$ is a well formed game and similarly for the connectives $\parr$ and $\implies$.
-  \begin{proof}
-    As before, we prove this proposition for $A\tensor B$ and the other two cases are entirely similar.
-Alternatively, observe that $A\parr B=\neggame{(\neggame A \tensor \neggame B)}$ and that $A\implies B = \neggame A \parr B$.
-
-    Examining the definitions of well formed and alternating sequences, it is immediate that $P_{A\tensor B}$ is prefix-closed.
-Moreover, every sequence contained in $P_{A\tensor B}$ is well formed, so the well-formedness condition holds.
-If $s,sa\in P_{A\tensor B}$ then $s,sa$ are both prefixes of $sa$ and so we must have $\zeta_{A\tensor B}(s)=\neg\zeta_{A\tensor B}(sa)$, since $sa$ is alternating.
-
-    To show that the limit condition holds, suppose that $\mu<\alpha$ is a limit ordinal and that $s\in(M_A)^\mu$ is a sequence of length $\mu$ such that $t\in P_{A\tensor B}$ for every proper prefix $t\pprefix s$.
-For each $t\pprefix s$, then, we must have $t\vert_A\in P_A$ and $t\vert_B\in P_B$.
-
-    We claim that $s\vert_A\in P_A$.
-Indeed, if $\length(s\vert_A)$ is a successor ordinal, then $s\vert_A$ has a last move $a$.
-Let $t$ be the prefix of $s$ consisting of all moves up to and including that last move.
-Then $\length(t)$ is a successor ordinal, so $t$ must be a \emph{proper} prefix of $s$, and therefore $s\vert_A=t\vert_A\in P_A$.
-If instead $\length(s\vert_A)$ is a limit ordinal, then for every proper prefix $u\pprefix s\vert_A$, we have some $t\prefix s$ with $t\vert_A=u$ (take $t$ to be the prefix consisting of all moves in $s$ that occur in $u$ or that occur before some move in $u$).
-Since $s\vert_A\ne u$, $t$ must be a \emph{proper} prefix of $s$, and so $t\vert_A\in P_A$.
-Since $u$ is arbitrary, the limit condition for $A$ tells us that $s\vert_A\in P_A$.
-
-    By an identical argument, $s\vert_B\in P_B$, and so $s\in P_A\|P_B$.
-We claim that $s$ is alternating with respect to $\zeta_{A\tensor B}$.
-Indeed, if $t,ta\prefix s$, then $t,ta$ must both be \emph{proper} prefixes of $s$, since $\length(s)$ is a limit ordinal and $\length(ta)$ is a successor ordinal.
-So $ta$ is alternating and therefore $\zeta_{A\tensor B}(t)=\neg\zeta_{A\tensor B}(ta)$.
-
-    Lastly, we show that $s$ is well formed with respect to $\lambda_{A\tensor B},\zeta_{A\tensor B}$.
-Suppose $ta\prefix s$.
-Once again, $ta$ must be a \emph{proper} prefix of $s$, since it clearly has a different length.
-Therefore, $ta$ is well formed and we have $\zeta_{A\tensor B}(ta)=\lambda_{A\tensor B}(a)$.
-Therefore, $s\in P_{A\tensor B}$.
-
-    For the second part of the proposition, suppose that $V\subset P_A\|P_B$ is prefix closed and satisfies the alternating condition with respect to $\zeta_{A\tensor B}$ and that if $sa\in V$ then $\zeta_{A\tensor B}(sa)=\lambda_{A\tensor B}(a)$.
-We want to show that $V\subset P_{A\tensor B}$.
-Indeed, if $s\in V$ and $ta\prefix s$, then $ta\in V$ (since $V$ is prefix closed) and therefore $\zeta_{A\tensor B}(ta)=\lambda_{A\tensor B}(a)=\neg\zeta_{A\tensor B}(s)$.
-  \end{proof}
-\end{proposition}
-
-As before, we want to show that if player $O$ switches games in the tensor product and that player $P$ switches games in the par and linear implication.
-Recalling that if $A,B$ are $\alpha$-games then $A\parr B = \neggame{(\neggame A\tensor \neggame B)}$ and that $A\implies B = \neggame A\parr B$, we only need to prove this for the tensor product:
-
-\begin{proposition}
-  \label{TransWhoSwitchesGames}
-  Let $A,B$ be $\alpha$-games.  Suppose that $s\in P_{A\implies B}$, $a\in M_A$ and $b\in M_B$.  Then:
-
-  i) If $sab\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(b) = O$
-
-  ii) If $sba\in P_{A\tensor B}$ then $\lambda_{A\tensor B}(a) = O$.
-
-  \begin{proof}
-    Unchanged from the finitary case - see Proposition \ref{WhoSwitchesGames}
-  \end{proof}
-\end{proposition}
-
-\subsection{Categories of transfinite games and strategies}
-
-We want to build a category $\G(\alpha)$ whose objects are games and whose morphisms are strategies on the linear implication of two games.
-Given $\alpha$-games $A$, $B$ and $C$ and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we define
-\begin{gather*}
-  \sigma\|\tau = \left\{\s\in (M_A\cprd M_B\cprd M_C)^{*<\alpha\#\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\right\}\\
-  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}
-\end{gather*}
-
-Here, $\alpha\#\alpha$ is intended to be an upper bound and indeed any sufficiently large ordinal will do without changing the elements of $\sigma\|\tau$.
-The symbol $\#$ denotes the so-called \emph{natural addition} on ordinals: if $\beta,\gamma$ are ordinals then the order type of $\beta\#\gamma$ is the largest well-ordering on the disjoint union $\beta\sqcup\gamma$ such that the restrictions to $\beta$ and $\gamma$ give the original orderings\footnote{Alternatively, $\#$ represents the coproduct in the category of well-ordered sets and order-preserving maps.}.
-For example, we have $\omega\#1=\omega+1$, but $1\#\omega=\omega+1$ as well (and \emph{not} $1+\omega$, which equals $\omega$).
-In any case, this is not an important point - we want to allow the sequences $\s$ to be as long as we need to be, but we need to introduce some bound to make it clear that the resulting collection of plays is a small set.
-$\alpha\#\alpha$ turns out to be a suitable upper bound.
-
-For the functor $\cmap{\F}{\G(\alpha)}{\Rel}$, we shall want to show that
-\[
-  \comp\tau\sigma = \left\{s\in P_{A\implies C}\suchthat\exists t\in\sigma,u\in\tau\esuchthat s\vert_A=t\vert_A,\;t\vert_B=u\vert_B,\;s\vert_C=u\vert_C\right\}
-  \]
-To show this, we will want to show that for any such $s,t,u$ there is some interleaving $\s$ such that $\s\vert_{A,C}=s$, $\s\vert_{A,B}=t$ and $\s\vert_{B,C}=u$.
-Even though $s$, $t$ and $u$ all have length less than $\alpha$, $\s$ might have longer length; it will, however, have length less than $\alpha\#\alpha$.
-
-It is not immediately clear from the definition that the elements of $\comp\tau\sigma$ have length less than $\alpha$, and in fact it turns out that this is not true.
-For this reason, we will eventually need to place restrictions on the ordinal $\alpha$ to make sure that $\comp\tau\sigma$ is indeed a valid strategy for $A\implies C$.
-
-\subsubsection{Completely negative and almost completely negative $\alpha$-games}
-
-Recall that when defining a finitary game $A=(M_A,\lambda_A,\zeta_A,P_A)$, the function $\zeta_A$ was entirely determined by two pieces of information: the function $\lambda_A$ (to determine $\zeta_A(sa)$ for any non-empty play $sa$) and the designation of the game as either \emph{positive} or \emph{negative} (to determine $\zeta_A(\emptyplay)$).
-In the $\omega+1$ case, we also needed to specify a function $\cmap{W_A}{P_A^\infty}{\OP}$ to get the sign of each $\omega$-play.
-The general case is similar - once we have specified $\zeta_A(s)$ for any play $s$ whose length is a limit ordinal, the values of $\zeta_A(t)$ for $t$ a play over a successor ordinal are determined by the alternating condition (alternatively, they are determined automatically by well-formedness).
-
-When building a category of games, we restricted our attention to the negative games.
-This is necessary in order to avoid technical complications\footnote{The category in \cite{abramskyjagadeesangames} has both positive and negative games as objects, together with games where either player may start, but it does not admit a faithful functor into $\Rel$ in the way that we want.}.
-Of course, these technical complications carry over to the transfinite case, so we need a new negativity condition for our $\alpha$-games.
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  We say that $A$ is \emph{completely negative} if $\zeta_A(s)=P$ whenever $s\in P_A$ and $\length(s)$ is a limit ordinal.
-\end{definition}
-
-Since the only limiting play in the finitary case is the empty play, we see that the completely negative $\omega$-games are precisely the negative games.
-But now consider the $\omega+1$ case.
-If $A$ is a win-game, then $A$ is completely negative only if it is negative and all infinite plays are $P$-winning.
-Recall that we \emph{were} able to build a category of negative win-games without making the requirement that player $P$ wins all infinite plays, so if we insist on complete negativity then we lose much of the richness of our category for no technical benefit.
-We would be better off with some weaker condition.
-
-\begin{definition}
-  Let $\alpha$ be an ordinal.  If $\alpha=\alpha'+1$ and $A$ is an $\alpha$-game, we say that $s\in P_A$ is \emph{length maximal} if it has the largest possible length - i.e., if $\length(s)=\alpha'$.
-
-  If $\alpha$ is a limit ordinal then there are no length maximal plays in $\alpha$-games.
-
-  Let $A$ be an $\alpha$-game.  We say that $A$ is \emph{almost completely negative} (\emph{acn}) if $\zeta_A(s)=P$ whenever $\length(s)$ is a limit ordinal \emph{and $s$ is not length-maximal}.
-\end{definition}
-
-Note that for most ordinals $\alpha$ there is no difference between being completely negative and being acn.
-The only ordinals for which there is  a difference are those of the form $\mu+1$, where $\mu$ is a limit ordinal.
-
-Our category will have acn $\alpha$-games as objects and the morphisms from $A$ to $B$ will be partial strategies for $A\implies B$.  Later we will consider the total strategy case.
-
-\begin{proposition}
-  \label{TensorIsAcn}
-  Let $A,B$ be acn $\alpha$-games.  Then $A\tensor B$ is acn
-  \begin{proof}
-    Let $s\in P_{A\tensor B}$ be a limiting play that is not length maximal.
-Then at least one of $s\vert_A$ and $s\vert_B$ must be a limiting play (otherwise they both have last moves and the later of the two will be the last move in $s$).
-Suppose that $s\vert_A$ and $s\vert_B$ are both limiting plays.
-By Lemma \ref{TechnicalOrdinalLemma}, $\length(s\vert_A),\length(s\vert_B)\le\length(s)$, so neither $s\vert_A$ nor $s\vert_B$ is length maximal, since $s$ is not.
-Therefore, $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=P$, since $A$ and $B$ are acn.
-Therefore, $\zeta_{A\tensor B}(s)=P$, since $P\wedge P=P$.
-
-    Suppose instead that $s\vert_A$ is a successor play.
-Then $s\vert_B$ is a limiting play.
-Since $s$ is a limiting play, there must be moves from $B$ in $s$ that occur after the last move in $s\vert_A$.
-Therefore, $\zeta_A(s\vert_A)=P$ by Proposition \ref{TransWhoSwitchesGames}.
-Now $s\vert_B$ is a limiting play and not length maximal, so $\zeta_B(s\vert_B)=P$ and therefore $\zeta_{A\tensor B}(s)=P$.
-The case where $s\vert_B$ is a successor play and $s\vert_A$ is a limiting play is similar.
-  \end{proof}
-\end{proposition}
-
-Note, however, that $A\implies B$ is not necessarily acn, even if $A,B$ are completely negative.
-This is a direct consequence of the extension of the definitions to ordinals greater than $\omega$.
-For negative $\omega$-games $A,B$, the only limiting play is the empty play and its components are both necessarily empty, so they are also limiting plays.
-Therefore, $A\implies B$ is a negative game, by the equation $(P\Rightarrow P) = P$.
-
-However, when we move beyond $\omega$, it is no longer true that the components of a limiting play are always limiting plays, so we cannot be sure that they are $P$-positions, and this means that $A\implies B$ is not necessarily completely negative, even if $A,B$ are.
-As an example, we take the completely negative game
-\[
-  \bot=\{\{*\},\{*\mapsto O\},\{\emptyplay\mapsto P,\;*\mapsto O\}, \{\emptyplay, *\}\}
-  \]
-which has a single $O$-move with no $P$-replies.
-If $A$ is an acn $\alpha$-game, then $A\implies\bot$ is the same as the game $\neggame A$, but with the extra $O$-move $*$ attached to the start.
-For $\omega$-games, this extra $O$-move means that $A\implies\bot$ is negative if $A$ is negative, but if $A$ contains plays of length greater than $\omega$ then $A\implies\bot$ is not completely negative if $A$ is completely negative: indeed, if $s\in P_A$ is a non-empty limiting play, then we have
-\[
-  \zeta_{A\implies\bot}(*s)=(\zeta_A(s)\Rightarrow\zeta_\bot(*))=(P\Rightarrow O) = O
-  \]
-But $*s$ is a limiting play, so $A\implies\bot$ is not completely negative.
-
-This will pose a problem for our categorical semantics.
-We want to build a category where the objects are acn $\alpha$-games and where the morphisms from a game $A$ to a game $B$ are strategies for $A\implies B$.
-We also want the category to be monoidal closed, which means that we would really like $A\implies B$ to be an object of the category.
-As we have just seen, this is not the case in general.
-
-We take the following approach: we define a morphism in our category between objects $A$ and $B$ to be a strategy for $A\implies B$, ignoring the fact that this is not an object of our category.
-We will get a working definition of the composition of strategies.
-Then, when we come to define the monoidal closed structure on the category, we will use a slightly modified form of $A\implies B$ for our linear implication.
-This modified form will be, in a sense we shall make precise, the smallest modification of $A\implies B$ that is completely negative, and this will be enough to show that it does indeed give us a monoidal closed structure.
-
-Before moving on to the discussion of composition of strategies, we shall want a version of Proposition \ref{nice-negative-games} to record the properties of negative games that make them so useful for our definition of composition.
-
-\begin{proposition}
-  \label{NiceAcnGames}
-  a) Let $A,B$ be acn $\alpha$-games and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\tensor B}$.  Then:
-  \begin{enumerate}[i)]
-    \item If $s$ is not a length maximal limiting play, then either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=P$.  
-    \item $s$ is well formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$ (so $s\in P_{A\tensor B}$).
-  \end{enumerate}
-
-  b) Let $A$ be an acn $\alpha$-game, {\bf let $B$ be an arbitrary $\alpha$-game} and suppose that $s\in P_A\|P_B$ is alternating with respect to $\zeta_{A\implies B}$.  Then:
-  \begin{enumerate}[i)]
-    \item If $s$ is not a length maximal limiting play, then either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=O$.
-    \item $s$ is well formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$ (so $s\in P_{A\implies B}$).
-  \end{enumerate}
-\end{proposition}
-
-Note that the extra hypothesis on (i) is necessary: suppose $\alpha=\omega+1$ and let $\st$ be as defined above where the unique infinite play is $O$-winning.
-Then $\st\tensor\st$ contains an infinite play $s$ both of whose components are infinite and we have $\zeta_A(s\vert_A)=\zeta_B(s\vert_B)=O$.
-
-\begin{proof}[Proof of Proposition \ref{NiceAcnGames}]
-  (a): By Proposition \ref{TransTensorWellFormed}, for part (ii) it suffices to show that the set of alternating plays in $P_A\|P_B$ is well-formed with respect to $\zeta_{A\tensor B},\lambda_{A\tensor B}$ - i.e., that if $s,sx\in P_A\|P_B$ are alternating then $\zeta_{A\tensor B}(sx)=\lambda_{A\tensor B}(x)$.
-
-  If $s$ is a limiting play, then one of $s\vert_A,s\vert_B$ must be a limiting play.
-By Lemma \ref{TechnicalOrdinalLemma}, $\length(s\vert_A),\length(s\vert_B)\le\length(s)$, so $s\vert_A$ and $s\vert_B$ are not length maximal if $s$ is not.
-Therefore, either $\zeta_A(s\vert_A)=P$ or $\zeta_B(s\vert_B)=P$, since $A$ and $B$ are both acn.
-
-  We may now prove (i) and (ii) for all successor plays by induction on their length, exactly as we did in Proposition \ref{nice-negative-games}.
-
-  (b): Again, by Proposition \ref{TransTensorWellFormed}, for part (ii) it suffices to show that the set of alternating plays in $P_A\|P_B$ is well-formed with respect to $\zeta_{A\implies B},\lambda_{A\implies B}$ - i.e., that if $s,sx\in P_A\|P_B$ are alternating then $\zeta_{A\implies B}(sx)=\lambda_{A\tensor B}(x)$.
-
-  We prove this by induction on the length of the play $s$; the successor case is exactly as in Proposition \ref{nice-negative-games}.
-Suppose that $s$ is a non-length maximal limiting play.
-If $s\vert_A$ is a limiting play, then we are done, since $A$ is acn and $s\vert_A$ is not length maximal by Lemma \ref{TechnicalOrdinalLemma}.
-Otherwise, if $s\vert_A$ is a successor play, then it has a last move $a$.
-Since $s$ is a limiting play, there must be moves from $B$ occurring later in $s$ than $a$, so $a$ is an $O$-move in $A\implies B$ by Proposition \ref{TransWhoSwitchesGames}, so it is a $P$-move in $A$.
-\end{proof}
-
-\subsubsection{Interleavings and the functor into $\Rel$}
-
-We now set out to extend to the transfinite case some of the results that we proved in the previous section about plays and strategies for the game $A\implies B$.
-
-\begin{lemma}
-  \label{TransPlayInStrategyDeterminedByComponents}
-  Let $A,B$ be $\alpha$-games and let $\sigma$ be a strategy for $A\implies B$.  Suppose that $s,t\in\sigma$ are such that $s\vert_A=t\vert_A$ and $s\vert_B=t\vert_B$.  Then $s=t$.
-  \begin{proof}
-    Exactly as in Lemma \ref{PlayInStrategyDeterminedByComponents}: suppose $s\ne t$.
-By well-ordering, there is an earliest index $\beta$ such that $s(\beta)\ne t(\beta)$.
-So we have a sequence $r$ and moves $x\ne y$ such that $rx\prefix s$ and $ry\prefix t$.
-Since $x\ne y$, $r$ must be a $P$-position by the definition of strategy, and so $x,y$ must take place in the same game.
-Therefore, either $s\vert_A\ne t\vert_A$ or $s\vert_B\ne t\vert_B$.
-  \end{proof}
-\end{lemma}
-
-Given acn $\alpha$-games $A$ and $B$ and a strategy $\sigma$ for $A\implies B$, we may define a relation $\grel\sigma\subset P_A\times P_B$ by
-\[
-  \grel\sigma = \{(s\vert_A,s\vert_B)\suchthat\textrm{$s\in\sigma$ is a $P$-position}\}
-  \]
-Once we have our category $\G(\alpha)$ set up, this will allow us to define a functor $\cmap{\F(\alpha)}{\G(\alpha)}{\Rel}$.
-Then the following lemma, which is a version of Lemma \ref{HylandSchalkFaithful}, will tell us that this functor is faithful.
-
-\begin{lemma}
-  \label{TransHylandSchalkFaithful}
-  Let $A,B$ be $\alpha$-games and let $\sigma,\sigma'$ be strategies for $A\implies B$.  Suppose that $\grel\sigma=\grel{\sigma'}$ as subsets of $P_A\times P_B$.  Then $\sigma=\sigma'$.
-  \begin{proof}
-    See Appendix \ref{HylandSchalkFaithfulProof}.
-  \end{proof}
-\end{lemma}
-
-We will postpone discussion of the functor $\cmap{\F(\alpha)}{\G(\alpha)}{\Rel}$ until we have proved the main technical result, which will be the transfinite version of Lemma \ref{LiftingLemma}.
-
-\begin{lemma}
-  \label{TransLiftingLemma}
-  Let $A,B$ be acn $\alpha$-games, let $C$ be an arbitrary $\alpha$-game, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Suppose that $s\in\sigma$ and $t\in\tau$ are such that $s\vert_B=t\vert_B$.
-Then there exists some ordinal $\beta<\alpha\#\alpha$ such that for all $\gamma$ with $0\le\gamma\le\beta$ there is a unique sequence $\s^\gamma\in\sigma\|\tau$ of length $\gamma$ such that $\s^\gamma\vert_A\prefix s\vert_A$ and $\s\gamma\vert_C\prefix t\vert_C$.
-Moreover, for this $\s^\gamma$ we have $\s^\gamma\vert_{A,B}\prefix s$ and $\s^\gamma\prefix t$ and if $\delta\le\gamma$ then $\s^\delta\prefix\s^\gamma$.
-Lastly, we have $\s^\beta\vert_{A,B}=s$ and $\s^\beta\vert_{B,C}=t$.
-\end{lemma}
-
-Note that we have no explicit formula for the ordinal $\beta$ as we did for the the numeral $n$ in Lemma \ref{LiftingLemma}, owing to the fact that addition of ordinals is less well-behaved than addition of numerals.
-Nevertheless, this lemma shall be sufficient for our purposes.
-
-\begin{proof}[Proof of Lemma \ref{TransLiftingLemma}]
-  We proceed by induction on $\gamma$.  At some point we will be unable to proceed further with the induction, so we terminate and the final $\gamma$ we reach will be our $\beta$.
-
-  There is a unique sequence of length $0$, namely the empty sequence and its $A$- and $C$-components are both empty, so are prefixes of $s$ and $t$.
-
-  Now suppose that $\mu$ is a limit ordinal and that we have a chain of sequences $\s^\gamma$ for all $\gamma<\mu$ such that $\s^\gamma\vert_{A,B}\prefix s$ and $\s^\gamma\vert_{B,C}\prefix t$.
-Then we may take the limit $\s^\mu$ of these sequences and we have $\s^\mu\vert_{A,B}\prefix s$ and $\s^\mu\vert_{B,C}\prefix t$.
-For uniqueness, suppose that $\t^\mu$ has length $\mu$ and that $\t^\mu\vert_A\prefix s\vert_A$ and $\t^\mu\vert_C\prefix t\vert_C$.
-Let $\gamma<\mu$, and let $\t^\gamma$ be the initial prefix of $\t^\mu$ of length $\gamma$.
-Then $\t^\gamma\vert_A\prefix s\vert_A$ and $\t^\gamma\vert_C\prefix t\vert_C$, so $\t^\gamma=\s^\gamma$, by uniqueness.
-Since $\gamma<\mu$ was arbitrary, it follows that $\t^\mu=\s^\mu$.
-
-  Lastly, suppose that $\gamma=\delta+1$ for some ordinal $\delta$ and suppose that we have already constructed the sequence $\s^\delta$.
-If $X$ is an acn $\alpha$-games, $y$ is an arbitrary $\alpha$-game and $r\in P_{X\implies Y}$ is not length maximal, then Proposition \ref{NiceAcnGames}(i) tells us that either $\zeta_X(r\vert_X)=P$ or $\zeta_Y(r\vert_Y)=O$.
-We have $\s^\delta\vert_{A,B}\in P_{A\implies B}$ and $\s^\delta\vert_{B,C}\in P_{B\implies C}$, so if we assume that $\s^\delta\vert_{A,B}$ and $\s^\delta\vert_{B,C}$ are not length maximal plays, this gives us four possible `sign profiles' for the components of the sequence $\s^\delta$:
-
-  \[
-    \begin{array}{c|ccc}
-      \textbf{Case} & \zeta_A(\s^\delta\vert_A) & \zeta_B(\s^\delta\vert_B) & \zeta_C(\s^\delta\vert_C) \\
-      \hline
-      \textbf{A} & P & P & P \\
-      \textbf{B} & P & P & O \\
-      \textbf{C} & P & O & O \\
-      \textbf{D} & O & O & O
-    \end{array}
-    \]
-
-  We now split the argument up according to cases:
-
-  \begin{description}
-    \item[Cases A and B: ] We have $\s^\delta\vert_{B,C}\prefix t$.
-If in fact $\s^\delta\vert_{B,C}=t$, then we terminate and set $\beta=\delta$.
-We claim that in this case we must have $\s^\beta\vert_{A,B}=s$.
-Certainly, $\s^\beta\vert_{A,B}\prefix s$; if this prefix relation is proper then we must have $\s^\beta\vert_{A,B}x\prefix s$ for some move $x$.
-Since $\zeta_A(\s^\beta\vert_A)=\zeta_B(\s^\beta\vert_B)=P$, $x$ must be an $O$-move and it must therefore take place in $B$, which is a contradiction, since $s\vert_B=t\vert_B$:
-      \[
-        \s^\beta\vert_Bx\prefix s\vert_B = t\vert_B=\s^\beta\vert_{B,C}\vert_B=\s^\beta\vert_B\quad\textbf{(contradictory)}
-        \]
-      Therefore, $\s^\beta\vert_{A,B}=s$.
-We must have $\beta<\alpha\#\alpha$, since we may decompose the set of (distinct) moves in $\s^k$ as the disjoint union of the set of moves that occur in $A$ and the set of moves that occur in $B$ or $C$.
-The induced ordering on each of these sets corresponds with the natural ordering of the moves as a play in $P_A$ or in $P_{B\implies C}$, and since $A$ and $B\implies C$ are both $\alpha$-games, this implies that these two orders are both less than $\alpha$.
-
-      Now suppose instead that $\s^\delta\vert_{B,C}$ is a \emph{proper} prefix of $t$.
-So $\s^\delta\vert_{B,C}x\prefix t$ for some move $x$.
-We set $\s^{\delta+1}=\s^\delta x$.
-Now certainly $\s^{\delta+1}\vert_{B,C}\prefix t$; we claim that $\s^{\delta+1}\vert_{A,B}\prefix s$.
-
-      If $x$ is a move from $C$ then $\s^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}\prefix s$.
-So suppose that $x$ is a move from $B$ - so $\s^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}x$.
-Since $s\vert_B=t\vert_B$, this must be a prefix of $s$ unless there is some move from $A$ that occurs immediately after $\s^\delta\vert_{A,B}$.
-But this is impossible in \textbf{Cases A and B}, since $\s^\delta\vert_{A,B}$ is a $P$-position in $A\implies B$ while $\s^\delta\vert_A$ is an $O$-position in $\neggame A$, so any move following $\s^\delta\vert_{A,B}$ must be a move in $B$.
-
-      Lastly, we show uniqueness.
-Suppose that $\t^{\delta+1}\in \sigma\|\tau$ has length $\delta+1$ and that $\t\vert_A\prefix s\vert_C$ and $\t\vert_C\prefix t\vert_C$.
-Let $y$ be the last move of $\t^{\delta+1}$ and write $\t^{\delta+1}=\t^\delta y$.
-Then we have
-      \[
-        \t^\delta\vert_A\prefix \t^{\delta+1}\vert_A\prefix s\vert_A\quad\t^\delta\vert_C\prefix\t^{\delta+1}\vert_C\prefix t\vert_C
-        \]
-      and so $\t^\delta=\s^\delta$ by uniqueness for sequences of length $\delta$.
-We claim that $y=x$.
-By our argument above, $y$ cannot be a move from $A$, so it is a move from $B$ or $C$.
-Then we have:
-      \begin{gather*}
-        \s^\delta y\vert_{B,C} = \t^{\delta+1}\vert_{B,C}\in\tau \\
-        \s^\delta x\vert_{B,C} \prefix t\in\tau
-      \end{gather*}
-      In \textbf{Case B}, $\s^\delta\vert_{B,C}x,\s^\delta\vert_{B,C}y$ are both $P$-plays in $B\implies C$, so they must be equal, since $\tau$ is a strategy.
-In \textbf{Case A}, $x$ and $y$ must both be $O$-moves in $C$.
-So the fact that $\t^{\delta+1}\vert_C=\s^{\delta+1}\vert_C$ means that $x=y$.
-
-      Therefore, $\t^{\delta+1}=\s^{\delta+1}$.
-
-    \item[Cases C and D: ] Entirely symmetrical.  This time, we get the next move from $s$ instead of $t$, and uniqueness follows from the fact that $\sigma$ is a strategy. 
-  \end{description}
-
-  We still need to deal with the case that one of $\s^\delta\vert_{A,B},\s^\delta\vert_{B,C}$ is length maximal.
-In that case, the `sign profile' for the components of $\s^\delta$ might not fit one of the cases in the table above, since Proposition \ref{NiceAcnGames}(i) only holds for non-length maximal pays.
-If the components of $\s^\delta$ do fit \textbf{Case A, B, C or D} above, then our existing argument is valid.
-Otherwise, there are four new cases to consider:
-  \[
-    \begin{array}{c|cccl}
-      \textbf{Case} & \zeta_A(\s^\delta\vert_A) & \zeta_B(\s^\delta\vert_B) & \zeta_C(\s^\delta\vert_C) & \\
-      \cline{1-4}
-      \textbf{E} & O & P & P & \rdelim\}{2}{60mm}[\parbox{60mm}{\hangindent=1em where $\s^\delta\vert_{A,B}$ is a length maximal \\ limiting play}] \\
-      \textbf{F} & O & P & O & \\
-      \textbf{G} & P & O & P & \rdelim\}{2}{60mm}[\parbox{60mm}{\hangindent=1em where $\s^\delta\vert_{B,C}$ is a length maximal \\ limiting play}] \\
-      \textbf{H} & O & O & P &
-    \end{array}
-    \]
-
-  In \textbf{Cases E and F}, we must have $\s^\delta\vert_{A,B}=s$, since it is already length maximal.
-If we also have $\s^\delta\vert_{B,C}=t$ then we set $\beta=\delta$ and terminate.
-Otherwise, we have $\s^\delta\vert_{B,C}x\prefix t$ for some move $x$, and we set $\s^{\delta+1}=\s^\delta x$.
-Then we certainly have $\s^{\delta+1}\vert_{A,B}\prefix s$ and $\s^{\delta+1}\vert_{B,C}\prefix t$.
-
-  For uniqueness, suppose that $\t^{\delta+1}\in\sigma\|\tau$ has length $\delta+1$ and that $\t^{\delta+1}\vert_A\prefix s\vert_A$ and $\t^{\delta+1}\vert_C\prefix t\vert_C$.
-As before, the induction hypothesis tells us that $\t^{\delta+1}$ must be of the form $\s^\delta y$ for some move $y$.
-We claim that $x$ and $y$ must both be moves in $C$: if $x$ is a move in $A$ or $B$ then we have $\s^\delta\vert_{A,B}x\prefix s$, contradicting length maximality of $\s^\delta\vert_{A,B}$.
-If $y$ is a move in $A$ or $B$ then we have $\t^{\delta+1}\vert_{A,B}=\s^\delta\vert_{A,B}y\in\sigma$, and this also contradicts length maximality of $\s^\delta\vert_{A,B}$.
-It follows that $x$ and $y$ are both moves in $C$, so they are identical, since $\s^{\delta+1}\vert_C=\t^{\delta+1}\vert_C$.
-
-  We deal with \textbf{Cases G and H} using a symmetrical argument.
-\end{proof}
-
-We shall use (the proof of) this lemma to show that composition is well defined for acn $\alpha$-games.
-First, though, we shall need to impose some conditions on the ordinal $\alpha$.
-To start with, we shall assume that $\alpha=\omega^\beta$ for some $\beta$.
-It is well known that these are precisely the \emph{additively closed} ordinals -- so if $\gamma,\delta<\omega^\beta$ then $\gamma+\delta<\omega^\beta$.
-We shall want a stronger property though -- the ordinals of the form $\omega^\beta$ are closed under the natural addition $\#$ that we introduced earlier.
-
-To see this, suppose that $\gamma,\delta<\omega^\beta$.  We may write $\gamma$ and $\delta$ in their \emph{Cantor normal forms}:
-\begin{gather*}
-  \gamma = \omega^{\beta_1}.j_1 + \omega^{\beta_2}.j_2 + \cdots + \omega^{\beta_n}.j_n \\
-  \delta = \omega^{\beta_1}.k_1 + \omega^{\beta_2}.k_2 + \cdots + \omega^{\beta_n}.k_n
-\end{gather*}
-Here, $\beta_1>\beta_2>\cdots>\beta_n$, and $n,j_1,\dots,j_n,k_1,\dots,k_n<\omega$ (We allow $j_i,k_i$ to be zero so that we can use the same sequence $\beta_i$ in both cases.)  Then we may write
-\[
-  \gamma\#\delta = \omega^{\beta_1}.(j_1+k_1) + \omega^{\beta_2}.(j_2+k_2) + \cdots + \omega^{\beta_n}.(j_n+k_n)
-  \]
-using the fact that $\omega^\xi+\omega^\eta=\omega^\xi\#\omega^\eta$ if $\xi\ge\eta$ and the fact that the natural addition $\#$ is commutative.
-Since $\gamma,\delta<\omega^\beta$, we must have $\beta_i<\beta$ for each $i$ and therefore $\gamma\#\delta<\omega^\beta$, since $\omega^\beta$ is additively closed.
-
-The reason that this is good for us is that it means that if $A,B,C$ are completely negative $\omega^\beta$-games, and if $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$ then any sequence $\s\in\sigma\|\tau$ must have length less than $\omega^\beta$.
-Indeed, we may split $\s$ into its $A,B$-component and its $C$-component -- if these have lengths $\gamma,\delta<\omega^\beta$ then the full sequence has length at most $\gamma\#\delta<\omega^\beta$.
-This allows us to ensure that $\s\vert_{A,C}$ has length at most $\omega^\beta$ -- so that it is a valid play in $A\implies C$.
-
-To get an idea of why we need to make some restriction on the ordinal $\alpha$, consider the situation when $\alpha=\omega^2+1$.  We define a game $\st$ as before:
-\begin{gather*}
-  M_{\st} = \{q,a\} \\
-  \lambda_{\st}(q) = O,\;\lambda_{\st}(a)=P \\
-\end{gather*}
-$P_\st$ will be the set of all plays $s\in M_\st^{*<\omega^2+1}$ such that $q$ is always followed by $a$, $a$ is always followed by $q$ and a limiting play is always followed by $q$.
-We define $\zeta_\st$ to make $\st$ into a completely negative game.
-
-Let $A=B=C=\st$.
-Consider the sequence of plays $s_0,s_1,\dots,s_{\omega^2}$ in $A\implies B$ shown in Figure \ref{TooLongAB} and the sequence $t_0,t_1,\dots,t_{\omega+1}$ in $B\implies C$ shown in Figure \ref{TooLongBC}.
-These sequences have matching $B$-components, so Lemma \ref{TransLiftingLemma} tells us that we can interleave them to give a sequence $\s$.
-But now $\s\vert_{A,C}$ consists in a single move in $C$ followed by a play of length $\omega^2$ in $A$, followed by a single move in $C$ - in other words, it has length $\omega^2+1$, which is too long.
-\begin{figure}[!ht]
-  \[
-    \begin{array}{ccccc}
-      \delta & A & B & \zeta_A(s_\delta\vert_A) & \zeta_B(s_\delta\vert_B) \\
-      \hline
-      0 & & & P & P \\
-      \hline
-      1 & & q & P & O \\
-      2 & q & & O & O \\
-      3 & a & & P & O \\
-      4 & q & & O & O \\
-      5 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega & & & P & O \\
-      \hline
-      \omega+1 & & a & P & P \\
-      \omega+2 & & q & P & O \\
-      \omega+3 & q & & O & O \\
-      \omega+4 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega2 & & & P & O \\
-      \hline
-      \omega2+1 & & a & P & P \\
-      \omega2+2 & & q & P & O \\
-      \omega2+3 & q & & O & O \\
-      \omega2+4 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega3 & & & P & O \\
-      \hline
-      \multicolumn{5}{c}{\vdots}\\
-      \multicolumn{5}{c}{\vdots}\\
-      \hline
-      \omega^2 & & & P & P \\
-      \hline
-    \end{array}
-    \]
-  \caption{Diagrammatic representation of a play $s$ of length $\omega^2$ in $A\implies B=\st\implies \st$.
-Here $\s_\delta$ is the initial segment of $s$ of length $\delta$.
-Note that $s\vert_A$ has length $\omega^2$, while $s\vert_B$ has length $\omega$, since only finitely many moves from $B$ are played in each $\omega$-segment.}
-  \label{TooLongAB}
-\end{figure}
-
-\begin{figure}[!ht]
-  \[
-    \begin{array}{ccccc}
-      \delta & B & C & \zeta_B(t_\delta\vert_B) & \zeta_C(t_\delta\vert_C) \\
-      \hline
-      0 & & & P & P \\
-      \hline
-      1 & & q & P & O \\
-      2 & q & & O & O \\
-      3 & a & & P & O \\
-      4 & q & & O & O \\
-      5 & a & & P & O \\
-      \vdots & \vdots & & \vdots & \vdots \\
-      \hline
-      \omega & & & P & O \\
-      \hline
-      \omega+1 & & a & P & P \\
-    \end{array}
-    \]
-  \caption{Diagrammatic representation of a play $t$ of length $\omega+1$ in $B\implies C=\st\implies \st$.
-Compare with Figure \ref{TooLongAB} and notice that the $B$-component of this sequence is exactly the same as the $B$-component in that sequence.}
-  \label{TooLongBC}
-\end{figure}
-
-Therefore we shall restrict for now to ordinals $\alpha$ of the form $\omega^\beta$.
-This means in particular that there is no distinction between completely negative $\alpha$-games and acn $\alpha$-games, so we shall deal with completely negative games for simplicity.
-Later on, we shall mimic the construction of win-games to construct categories of games over ordinals of the form $\omega^\beta+1$, but for the reasons outlined above this will not be as simple as changing the ordinal from $\omega^\beta$ to $\omega^\beta+1$ in our definitions.
-
-Now we have made this restriction on $\alpha$, the fact that composition is well-defined follows as a corollary of Lemma \ref{TransLiftingLemma}.
-
-\begin{corollary}
-  Let $\alpha$ be an ordinal of the form $\omega^{\beta}$.
-Let $A,B$ be completely negative $\alpha$-games, let $C$ be an arbitrary $\alpha$-game, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Set
-  \[
-    \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
-    \]
-  as before.  Then $\comp\tau\sigma$ is a strategy for $A\implies C$.
-
-  \begin{proof}
-    We first claim that if $\s\in\sigma\|\tau$ then $\length(\s)<\alpha$.
-Indeed, suppose that $\length(\s\vert_{A,B})=\gamma$ and $\length(\s\vert_C)=\delta$.
-Then $\gamma,\delta<\alpha$, since $\s\vert_{A,B}\in P_{A\implies C}$ and $\s\vert_C\in P_C$.
-We have order-preserving inclusions
-    \begin{gather*}
-      \gamma\hookrightarrow\length(\s)\\
-      \delta\hookrightarrow\length(\s)
-    \end{gather*}
-    that make the underlying set of $\length(\s)$ into the disjoint union $\gamma\sqcup\delta$.
-Then the induced orderings on $\gamma,\delta$ are the same as their original orderings, so we must have $\length(\s)\le\gamma\#\delta$.
-Since $\alpha$ is closed under natural addition $\#$, this means that $\length(\s)<\alpha$.
-
-    Now we see that $\comp\tau\sigma\subset P_A\|P_C$: if $\s\in\sigma\|\tau$, then $\s\vert_{A,C}\vert_A=\s\vert_{A,B}\vert_A\in P_A$ and similarly $\s\vert_{A,C}\vert_C=\s\vert_{B,C}\vert_C\in P_C$.
-To show that $\comp\tau\sigma\subset P_{A\implies C}$, it suffices by Proposition \ref{NiceAcnGames}(ii) to show that $\comp\tau\sigma$ is alternating with respect to $\zeta_{A\implies C}$.
-
-    Suppose $\s a\in\sigma\|\tau$ for some move $a\in M_A$.
-By the proof of Lemma \ref{TransLiftingLemma}, we must be in \textbf{Case C or D} (there are no length maximal plays, so \textbf{Cases G and H} never occur).
-The following table shows that we must have $\zeta_{A\implies B}(\s\vert_{A,B})=\zeta_{A\implies C}(\s\vert_{A,C})$:
-    \[
-      \begin{array}{c|ccc|cc}
-        \textbf{Case} & \zeta_A(\s\vert_A) & \zeta_B(\s\vert_B) & \zeta_C(\s\vert_C) & \zeta_{A\implies B}(\s\vert_{A,B}) & \zeta_{A\implies C}(\s\vert_{A,C}) \\
-        \hline
-        \textbf{C} & P & O & O & O & O \\
-        \textbf{D} & O & O & O & P & P \\
-      \end{array}
-      \]
-    Then we get:
-    \[
-      \lambda_{A\implies C}(a) = \lambda_{A\implies B}(a) = \neg\zeta_{A\implies B}(\s) = \neg\zeta_{A\implies C}(\s)
-      \]
-    as desired.
-The case when we have $\s c\in\tau\|\sigma$ for some $c\in M_C$ is entirely symmetrical, working in \textbf{Cases A and B} this time.
-Therefore, $\comp\tau\sigma\subset P_{A\implies C}$.
-
-    We now need to show that the two strategy conditions are satisfied.
-Let $\s\in\sigma\|\tau$ and suppose that $\s\vert_{A,C}$ is a $P$-position and that $a\in M_A$ is an $O$-move in $A$ such that $\s\vert_{A,C}a \in P_{A\implies C}$.
-We want to show that $\s\vert_{A,C}a\in \comp\tau\sigma$.
-Since $\s\vert_{A,C}$ is a $P$-position, we must be in \textbf{Case A or Case D}.
-In that case, $\s\vert_{A,B}$ is a $P$-position and we know that $\s\vert_Aa\in P_A$, so $\s\vert_{A,B}a\in P_{A\implies B}$.
-Since $\sigma$ is a strategy, that implies that $\s\vert_{A,B}a\in\sigma$ and therefore $\s a\in\sigma\|\tau$.
-So we have $\s\vert_{A,C}a=\s a\vert_{A,C}\in\comp\tau\sigma$.
-
-    A symmetrical argument shows that if $c\in M_C$ is an $O$-move in $C$ and $\s\vert_{A,C}c\in P_{A\implies C}$ then $\s\vert_{A,C}c\in\comp\tau\sigma$.
-
-    Lastly, suppose that we have $s\in P_{A\implies C}$ is an $O$-position and that $x,y\in M_{A\implies C}$ are $P$-moves such that $sx,sy\in\comp\tau\sigma$.
-We need to show that $x=y$.
-By the definition of $\comp\tau\sigma$, there are sequences $\s,\t\in\sigma\|\tau$ with $\s\vert_{A,C}=sx$ and $\t\vert_{A,C}=sy$.
-We may write:
-    \begin{gather*}
-      \s = \s'x \\
-      \t = \t'y
-    \end{gather*}
-
-    Without loss of generality, assume that $\length(\s')\le\length(\t')$ and write $\t'=\t''\r$, where $\t''$ has the same length as $\s'$.
-Then $\t''\vert_A\prefix\s'\vert_A$ and $\t''\vert_C\prefix\s'\vert_C$, so $\t''=\s'$ by Lemma \ref{TransLiftingLemma}.
-
-    We claim that $\r=\emptyplay$.  Indeed, suppose $\r$ is non-empty.  We have
-    \[
-      \t''\r\vert_{A,C}=\t'\vert_{A,C}=s=\s'\vert_{A,C}=\t''\vert_{A,C}
-      \]
-    and so $\r$ must be entirely composed of moves from $B$.
-Let $b$ be the first move in $\r$.
-Then $\s'x$ and $\s'b$ have the same length and we have $\s'b\vert_A\prefix\s'x\vert_A$ and $\s'b\vert_C\prefix\s'x\vert_C$, so $b=a$, which is impossible.
-
-    Therefore, we must have $\s'x, \s'y\in\sigma\|\tau$.
-Since $x,y$ are $P$-moves in $A\implies C$, each must be either an $O$-move in $A$ or a $P$-move in $C$.
-It follows that either $\s'$ is in \textbf{Case B} and $x$ and $y$ are both moves in $C$ or that $\s'$ is in \textbf{Case C} and $x$ and $y$ are both moves in $A$.
-Suppose $\s'$ is in \textbf{Case B} and $x$ and $y$ are moves in $C$.
-Then $\s'\vert_{B,C}x,\s'\vert_{B,C}\in\tau$ and so $x=y$, since they are $P$-moves and $\tau$ is a strategy.
-Similarly, if $\s'$ is in \textbf{Case C} and $x$ and $y$ are moves in $A$, we have $\s'\vert_{A,B}x,\s'\vert_{A,B}y\in\sigma$ and so $x=y$ since $\sigma$ is a strategy.
-  \end{proof}
-\end{corollary}
-
-As a second corollary of Lemma \ref{TransLiftingLemma}, we show that the relational presentation of games and strategies respects composition:
-
-\begin{corollary}
-  \label{TransHylandSchalkIsFunctor}
-  Let $\alpha=\omega^\beta$ for some $\beta$ and let $A,B,C$ be completely negative $\alpha$-games.
-Let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Then we have:
-  \[
-    \grel{\comp\tau\sigma} = \comp{\grel\tau}{\grel\sigma}
-    \]
-  \begin{proof}
-    We have 
-    \begin{gather*}
-      \grel{\comp\tau\sigma} = \left\{(s\vert_A,s\vert_C)\suchthat\textrm{$s\in\comp\tau\sigma$ is a $P$-play}\right\} \\
-      \comp{\grel\tau}{\grel\sigma}=\{(s,t)\in P_A\times P_C\suchthat\exists u\in P_B\esuchthat (s,u)\in\grel\tau,\;(u,t)\in\grel\sigma\}
-    \end{gather*}
-    Suppose $s\in\comp\tau\sigma$ is a $P$-play and write $s=\s\vert_{A,C}$, where $\s\in\sigma\|\tau$.
-Then we have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$.
-Since $s=\s\vert_{A,C}$ is a $P$-play, $\s$ must be in \textbf{Case A or Case D}, so $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both $P$-plays.
-Therefore, we have
-    \begin{gather*}
-      (s\vert_A,\s\vert_B)\in\grel\sigma\\
-      (\s\vert_B,s\vert_C)\in\grel\tau
-    \end{gather*}
-    and therefore $(s\vert_A,s\vert_C)\in\comp{\grel\tau}{\grel\sigma}$.
-Conversely, suppose $(s, t)\in\comp{\grel\tau}{\grel\sigma}$.
-Then there exist $S\in\sigma,T\in\tau$ such that $S\vert_A=s$, $S\vert_B=T\vert_B$ and $T\vert_C=t$.
-By Lemma \ref{TransLiftingLemma}, there is some $\s\in\sigma\|\tau$ such that $\s\vert_A=s$ and $\s\vert_C=t$.
-So $(s,t)\in\grel{\comp\tau\sigma}$.
-  \end{proof}
-\end{corollary}
-
-\begin{corollary}
-  \label{TransIsCategory}
-  Let $\alpha=\omega^\beta$ for some $\beta$.
-Then we can define a category $\G(\alpha)$ as follows - the objects are completely negative $\alpha$-games, and if $A,B$ are two objects then a morphism from $A$ to $B$ is given by a strategy for $A\implies B$.
-We compose strategies as above.
-If $A$ is an object, then the identity morphism on $A$ is given by
-  \[
-    \id_A = \left\{s\in P_{A\implies A}\suchthat\textrm{for all $P$-positions $t\prefix s$, $t\vert_A=t\vert_\bneggame{A}$}\right\}
-    \]
-  \begin{proof}
-    We need to check that this is indeed an identity and that composition is associative.  We do this using the relational presentation exactly as in Theorem \ref{IsCategory}.  
-  \end{proof}
-\end{corollary}
-
-\subsubsection{Symmetric monoidal structure}
-
-In this section, we shall fix an ordinal $\alpha=\omega^\beta$.
-The tensor product $\tensor$ on $\alpha$-games makes the category $\G(\alpha)$ into a monoidal category.
-If $A,B$ are objects of $\G(\alpha)$, then Proposition \ref{TensorIsAcn} tells us that $A\tensor B$ is an object of $\G(\alpha)$.
-In fact, $\tensor$ gives us a functor $\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ as follows: let $A,A',B,B'$ be completely negative $\alpha$-games, let $\sigma$ be a strategy for $A'\implies A$ and let $\tau$ be a strategy for $B'\implies B$.
-Then we define a strategy $\sigma\tensor\tau$ for $(A'\tensor B')\implies (A\tensor B)$ as follows:
-\[
-  \sigma\tensor\tau = \{s\in P_{(A'\tensor B')\implies(A\tensor B)}\suchthat s\vert_{A',A}\in\sigma,\;s\vert_{B',B}\in\tau\}
-  \]
-To show that this is indeed a strategy for $(A'\tensor B')\implies (A\tensor B)$, suppose that $s\in\sigma\tensor\tau$ is a $P$-position and that $sx\in P_{(A'\tensor B')\implies (A\tensor B)}$.
-We need to show that $sx\vert_{A',A}\in\sigma$ and that $sx\vert_{B', B}\in\tau$.
-
-We claim that $s\vert_{A',A}$ and $s\vert_{B',B}$ are $P$-positions in $A'\implies A$ and $B'\implies B$.
-Indeed, suppose without loss of generality that $s\vert_{A',A}$ is an $O$-position in $A'\implies A$.
-We will show that $s$ is an $O$-position in $(A'\tensor B')\implies (A\tensor B)$, contradicting our assumptions.
-
-If $s\vert_{A',A}$ is an $O$-position, then $s\vert_{A'}$ is a $P$-position in $A'$ and $s\vert_A$ is an $O$-position in $A$.
-Now, $s\vert_{A,B}$ is a play in $A\tensor B$, so Proposition \ref{NiceAcnGames}(i) tells us that $s\vert_B$ must be a $P$-position in $B$.
-
-Now $s\vert_{B',B}$ is a play in $\tau\subset P_{B'\implies B}$, so Proposition \ref{NiceAcnGames}(i) now tells us that $s\vert_{B'}$ is a $P$-position in $B'$.
-It follows that $s\vert_{A',B'}$ is a $P$-position in $A'\tensor B'$ and that $s\vert_{A,B}$ is an $O$-position in $A\tensor B$, so $s$ is an $O$-position in $(A'\tensor B')\implies (A\tensor B)$, which is the desired contradiction.
-
-Without loss of generality, suppose that the move $x$ occurs in $A'$ or $A$.
-Since $s\vert_{A', A}$ is a $P$-position, we must have $sx\vert_{A',A}\in\sigma$, by the definition of a strategy, and then $s x\vert_{B',B}=s\vert_{B',B}\in\tau$.
-So $sx\in\sigma\tensor\tau$.
-
-For the second strategy condition, suppose that $sx, sy\in\sigma\tensor \tau$, where $s$ is an $O$-position in $(A'\tensor B')\implies(A\tensor B)$ and $x,y$ are $P$-moves.
-Then $s\vert_{A',B'}$ is a $P$-position in $A'\tensor B'$ and $s\vert_{A,B}$ is an $O$-position in $A\tensor B$.
-
-This immediately tells us that $s\vert_{A'}$ is a $P$-position in $A'$ and that $s\vert_{B'}$ is a $P$-position in $B'$.
-Moreover, by Proposition \ref{NiceAcnGames}(i), we know that either $s\vert_{A}$ is a $P$-position in $A$ and $s\vert_{B}$ is an $O$-position in $B$ or that $s\vert_A$ is an $O$-position in $A$ and $s\vert_B$ is a $P$-position in $B$.
-
-That is, we find ourselves in one of the following cases:
-\[
-  \begin{array}{c|cccc}
-    \textbf{Case} & \zeta_{A'}(s\vert_{A'}) & \zeta_{B'}(s\vert_{B'}) & \zeta_A(s\vert_A) & \zeta_B(s\vert_B) \\
-    \hline
-    \textbf{1} & P & P & P & O\\
-    \textbf{2} & P & P & O & P
-  \end{array}
-  \]
-
-Suppose we are in \textbf{Case 1}.
-Then $x$ cannot be a move in $A$ or $A'$: indeed, it is a $P$-move in $(A'\tensor B')\implies (A\tensor B)$, so it would be a $P$-move in $A'\implies A$.
-But $s\vert_{A',A}$ is a $P$-position in $A'\implies A$.
-Similarly, $y$ cannot be a move in $A$ or $A'$.
-Therefore, $x$ and $y$ are both $P$-moves in $B\implies B'$, and then the fact that $\tau$ is a strategy implies that $x=x'$.
-
-In \textbf{Case 2}, we can use a symmetrical argument, this time using the fact that $\sigma$ is a strategy.
-
-It is easy to show that this tensor action on strategies respects composition: indeed, if we have morphisms
-\begin{gather*}
-  A''\xrightarrow{\sigma'}A'\xrightarrow{\sigma}A\\
-  B''\xrightarrow{\tau'}B'\xrightarrow{\tau}B
-\end{gather*}
-then we have
-\begin{gather*}
-  (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'}) = \left\{s\in P_{(A''\tensor B'')\implies(A\tensor B)}\suchthat s\vert_{A'', A}\in\comp\sigma{\sigma'},\;s\vert_{B'', B}\in\comp\tau{\tau'}\right\}
-\end{gather*}
-Meanwhile:
-\begin{align*}
-  (\sigma'\tensor\tau')\|(\sigma\tensor\tau) &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{120pt}{
-    \setlength{\abovedisplayskip}{-5pt}
-    \setlength{\belowdisplayskip}{-10pt}
-    \begin{IEEEeqnarray*}{cCc}
-      \s\vert_{A''\tensor B'',A'\tensor B'} & \in & \sigma'\tensor\tau' \\
-      \s\vert_{A'\tensor B',A\tensor B} & \in & \sigma\tensor\tau
-    \end{IEEEeqnarray*}}
-    \normalsize
-  \end{minipage}}}\right\} \\[1em]
-  &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
-    \setlength{\abovedisplayskip}{-5pt}
-    \setlength{\belowdisplayskip}{-10pt}
-    \begin{IEEEeqnarray*}{cCc}
-      \s\vert_{A'', A'} & \in & \sigma' \\
-      \s\vert_{A', A} & \in & \sigma \\
-      \s\vert_{B'', B'} & \in & \tau' \\
-      \s\vert_{B', B} & \in & \tau
-    \end{IEEEeqnarray*}}
-    \normalsize
-  \end{minipage}}}\right\} \\[1em]
-  &= \left\{\s\in (M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})^{*<\alpha}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
-    \setlength{\abovedisplayskip}{-5pt}
-    \setlength{\belowdisplayskip}{-10pt}
-    \begin{IEEEeqnarray*}{cCc}
-      \s\vert_{A'', A', A} & \in & \sigma'\|\sigma \\
-      \s\vert_{B'', B', B} & \in & \tau'\|\tau
-    \end{IEEEeqnarray*}}
-    \normalsize
-  \end{minipage}}}\right\}
-\end{align*}
-
-It follows that
-\[
-  \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}
-  = \left\{\s\vert_{A''\tensor B'', A\tensor B}\suchthat\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)\right\}
-  = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
-  \]
-To define the associators and unitors (which are the obvious choices) for our tensor product, we introduce a bit more technology.
-Let $A',A$ be $\alpha$-games.
-We call a bijective function $\cmap{f}{P_{A'}}{P_A}$ a \emph{tree isomorphism} if $f$ preserves length and the prefix ordering and commutes with $\zeta_A,\zeta_{A'}$.
-If $A,A'$ are completely negative, then we have a strategy $\sigma_f$ for $A'\implies A$ given by
-\[
-  \sigma_f = \left\{s\in P_{A'\implies A}\suchthat \textrm{for all $P$-positions $t\prefix s$, we have $t\vert_A = f\left(t\vert_{A'}\right)$}\right\}
-  \]
-We check that $\sigma_f$ is indeed a strategy.
-It is clearly prefix-closed and satisfies the limit condition by the definition.
-If $s\in\sigma_f$ is a $P$-position, then we must have $sx\in\sigma_f$ for all $sx\in P_{A'\implies A}$.
-Now suppose that $sx,sy\in \sigma_f$.
-We first claim that $x$ and $y$ take place in the same game.
-Indeed, suppose instead that $x$ is a move in $A'$ and $y$ is a move in $A$.
-Then we have
-\begin{gather*}
-  s\vert_A = f\bracketed{s\vert_{A'}x} \\
-  s\vert_Ay = f\bracketed{s\vert_{A'}}
-\end{gather*}
-But this is impossible, since $f$ preserves lengths.  Therefore, $x$ and $y$ take place in the same game.  If they are moves in $A$, we have
-\[
-  s\vert_A x = f\bracketed{s\vert_{A'}} = s\vert_Ay
-  \]
-and so $x=y$, and if they are moves in $A'$, we have
-\[
-  s\vert_{A'}x = f\inv\bracketed{s\vert_A} = s\vert_{A'}y
-  \]
-and so $x=y$ again.
-
-We call a strategy $\sigma_f$ arising from a tree isomorphism $f$ a \emph{copycat strategy}.
-The relational presentation $\grel{\sigma_f}$ of such a strategy $\sigma_f$ is the graph of the function $\cmap{f}{P_{A'}}{P_A}$, and therefore the function $f$ is determined uniquely by the strategy $f$.
-Moreover, if we have completely negative $\alpha$-games $A'', A', A$ and tree isomorphisms $A''\xrightarrow{f'}A'\xrightarrow{f}A$, then we must have
-\[
-  \comp{\sigma_f}{\sigma_{f'}} = \sigma_{\comp{f}{f'}}
-  \]
-We therefore have a full-on-objects subcategory $\G_{\cc}(\alpha)$ of $\G(\alpha)$ of games and copycat strategies that comes equipped with a natural functor $\cmap{\H}{\G_{\cc}(\alpha)}{\Set}$ that sends a game $A$ to $P_A$ and a copycat strategy $\sigma_f$ to the function $f$.
-We get a commutative square in $\CAT$:
-\[
-  \begin{tikzcd}
-    \G_{\cc}(\alpha) \arrow[r, hook] \arrow[d, "\H"']
-      & \G(\alpha) \arrow[d, "\F"] \\
-    \Set \arrow[r, hook]
-      & \Rel
-  \end{tikzcd}
-  \]
-where all the functors in the diagram are faithful.
-
-Given sets $X,Y$ and a function $\cmap{\phi}{X}{Y}$, we write $\overline\phi\from X^{*<\alpha}\to Y^{*<\alpha}$ for the induced map that acts pointwise via $\phi$.
-Observe that disjoint union induces the structure of a symmetric monoidal category on $\Set$ with associators, unitors and braiding:
-\begin{gather*}
-  \assoc_{X,Y,Z}\from (X\cprd Y)\cprd Z\to X\cprd(Y\cprd Z)\\
-  \lunit_X\from \emptyset\cprd X\to X\\
-  \runit_X\from X\cprd\emptyset\to X\\
-  \braid_{X,Y}\from X\cprd Y\to Y\cprd X
-\end{gather*}
-
-Suppose $A,B,C$ are completely negative $\alpha$-games.  We have a function
-\[
-  \assoc_{M_A,M_B,M_C}\from M_{(A\tensor B)\tensor C}\to M_{A\tensor(B\tensor C)}
-  \]
-and it is clear from the definition that this gives rise to a function
-\[
-  \overline{\assoc_{M_A,M_B,M_C}}\from P_{(A\tensor B)\tensor C}\to P_{A\tensor(B\tensor C)}
-  \]
-The tensor unit in our category will be the empty game $I=(\emptyset, \emptyset, \emptyset, \{\emptyplay\})$.  If $A$ is a completely negative $\alpha$-game, we get natural maps
-\begin{gather*}
-  \lunit_{M_A}\from M_{I\tensor A}\to M_A \\
-  \runit_{M_A}\from M_{A\tensor I}\to M_A
-\end{gather*}
-and these give rise to maps
-\begin{gather*}
-  \overline{\lunit_{M_A}}\from P_{I\tensor A}\to P_A\\
-  \overline{\runit_{M_A}}\from P_{A\tensor I}\to P_A
-\end{gather*}
-Lastly, we have a map
-\[
-  \braid_{M_A,M_B}\from M_{A\tensor B}\to M_{B\tensor A}
-  \]
-inducing a map
-\[
-  \overline{\braid_{M_A,M_B}}\from P_{A\tensor B}\to P_{B\tensor A}
-  \]
-It is clear that these maps on sets of plays are all tree isomorphisms, so they give rise to isomorphisms in $\G(\alpha)$:
-\begin{gather*}
-  \assoc_{A,B,C}\from (A\tensor B)\tensor C\to A\tensor (B\tensor B)\\
-  \lunit_A\from I\tensor A\to A\\
-  \runit_A\from A\tensor I\to A\\
-  \braid_{A,B}\from A\tensor B\to B\tensor A
-\end{gather*}
-Since the original isomorphisms in $\Set$ satisfy the pentagon, triangle and hexagon identities, and since all the functors we are considering are faithful, our isomorphisms in $\G(\alpha)$ must satisfy the pentagon, triangle and hexagon identities as well.
-We give the argument in the case of the pentagon identity.
-
-Given completely negative $\alpha$-games $A,B,C,D$, we have the following commutative diagram in $\Set$:
-\[
-  \begin{tikzpicture}[commutative diagrams/every diagram]
-    \node (P0) at (90:2.3cm) {$M_{(A\tensor B)\tensor(C\tensor D)}$};
-    \node (P1) at (90+72:2cm) {$M_{((A\tensor B)\tensor C)\tensor D}$} ;
-    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{$M_{(A\tensor(B\tensor C))\tensor D}$}};
-    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{$ M_{A\tensor((B\tensor C)\tensor D)} $}};
-    \node (P4) at (90+4*72:2cm) {$ M_{A\tensor(B\tensor(C\tensor D))} $};
-  \path[commutative diagrams/.cd, every arrow, every label]
-    (P1) edge node {$\assoc_{M_{A\tensor B},M_C,M_D}$} (P0)
-    (P1) edge node[swap] {$\assoc_{M_A,M_B,M_C}\tensor\id_D$} (P2)
-    (P2) edge node[swap, yshift=-1em] {$\assoc_{M_A,M_{B\tensor C},M_D}$} (P3)
-    (P3) edge node[swap] {$\id_A\tensor\assoc_{M_B,M_C,M_D}$} (P4)
-    (P0) edge node {$\assoc_{M_A,M_B,M_{C\tensor D}}$} (P4);
-  \end{tikzpicture}
-  \]
-which immediately gives rise to a second commutative diagram in $\Set$:
-\[
-  \begin{tikzpicture}[commutative diagrams/every diagram]
-    \node (P0) at (90:2.3cm) {$P_{(A\tensor B)\tensor(C\tensor D)}$};
-    \node (P1) at (90+72:2cm) {$P_{((A\tensor B)\tensor C)\tensor D}$} ;
-    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{$P_{(A\tensor(B\tensor C))\tensor D}$}};
-    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{$ P_{A\tensor((B\tensor C)\tensor D)} $}};
-    \node (P4) at (90+4*72:2cm) {$ P_{A\tensor(B\tensor(C\tensor D))} $};
-  \path[commutative diagrams/.cd, every arrow, every label]
-    (P1) edge node {$\overline{\assoc_{M_{A\tensor B},M_C,M_D}}$} (P0)
-    (P1) edge node[swap] {$\overline{\assoc_{M_A,M_B,M_C}\tensor\id_D}$} (P2)
-    (P2) edge node[swap, yshift=-1em] {$\overline{\assoc_{M_A,M_{B\tensor C},M_D}}$} (P3)
-    (P3) edge node[swap] {$\overline{\id_A\tensor\assoc_{M_B,M_C,M_D}}$} (P4)
-    (P0) edge node {$\overline{\assoc_{M_A,M_B,M_{C\tensor D}}}$} (P4);
-  \end{tikzpicture}
-  \]
-But this is the image under the functor $\H$ of the following diagram in $\G_{\cc}(\alpha)$:
-\[
-  \begin{tikzpicture}[commutative diagrams/every diagram]
-    \node (P0) at (90:2.3cm) {${(A\tensor B)\tensor(C\tensor D)}$};
-    \node (P1) at (90+72:2cm) {${((A\tensor B)\tensor C)\tensor D}$} ;
-    \node (P2) at (90+2*72:2cm) {\makebox[5ex][r]{${(A\tensor(B\tensor C))\tensor D}$}};
-    \node (P3) at (90+3*72:2cm) {\makebox[5ex][l]{${A\tensor((B\tensor C)\tensor D)} $}};
-    \node (P4) at (90+4*72:2cm) {${A\tensor(B\tensor(C\tensor D))} $};
-  \path[commutative diagrams/.cd, every arrow, every label]
-    (P1) edge node {$\assoc_{{A\tensor B},C,D}$} (P0)
-    (P1) edge node[swap] {$\assoc_{A,B,C}\tensor\id_D$} (P2)
-    (P2) edge node[swap, yshift=-1em] {$\assoc_{A,{B\tensor C},D}$} (P3)
-    (P3) edge node[swap] {$\id_A\tensor\assoc_{B,C,D}$} (P4)
-    (P0) edge node {$\assoc_{A,B,{C\tensor D}}$} (P4);
-  \end{tikzpicture}
-  \]
-Since $\H$ is a faithful functor and the second diagram commutes, this last diagram must commute as well.
-
-It remains to show that $\assoc_{A,B,C},\lunit_A,\runit_A,\braid_{A,B}$ are natural transformations.  We show this for $\assoc_{A,B,C}$ and the other cases are entirely similar.
-
-Showing that $\assoc_{A,B,C}$ is a natural transformation from $((\blank\tensor \blank)\tensor \blank)$ to $(\blank\tensor(\blank\tensor \blank)\from \G(\alpha)\times\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ means showing that the following diagram commutes for all completely negative $\alpha$-games $A',B',C',A,B,C$ and all morphisms $\sigma\from A'\to A,\tau\from B'\to B,\upsilon\from C'\to C$:
-\[
-  \begin{tikzcd}
-    (A'\tensor B')\tensor C' \arrow[r, "(\sigma\tensor\tau)\tensor\upsilon"'] \arrow[d, "\assoc_{A', B', C'}"']
-      & (A\tensor B)\tensor C \arrow[d, "\assoc_{A,B,C}"] \\
-    A'\tensor(B'\tensor C') \arrow[r, "\sigma\tensor(\tau\tensor\upsilon)"']
-      & A\tensor(B\tensor C)
-  \end{tikzcd}
-  \]
-It is easy to check that this diagram commutes by applying the functor $\F\colon\G(\alpha)\to\Rel$.
-The relational content $\grel{\assoc_{A,B,C}}$ of the strategy $\assoc_{A,B,C}$ is the graph of the function
-\[
-  \overline{\assoc_{M_A,M_B,M_C}}\from P_{(A\tensor B)\tensor C}\to P_{A\tensor(B\tensor C)}
-  \]
-and its action by left composition on $\grel{(\sigma\tensor\tau)\tensor\upsilon}\subset P_{(A'\tensor B')\tensor C'}\times P_{(A\tensor B)\tensor C}$ is pointwise application of this function.
-We find that
-\begin{align*}
-  \grel{\comp{\assoc_{A,B,C}}{(\sigma\tensor\tau)\tensor\upsilon}}
-  &=\comp{\grel{\assoc_{A,B,C}}}{\grel{(\sigma\tensor\tau)\tensor\upsilon}}\\
-  &=\left\{(s,t)\in P_{(A'\tensor B')\tensor C'}\times P_{A\tensor(B\tensor C)}\;\middle|\;\mbox{\pbox{\textwidth}{$(s\vert_{A'},t\vert_A)\in\grel{\sigma}$\\$(s\vert_{B'},t\vert_B)\in\grel\tau$\\$(s\vert_{C'},t\vert_C)\in\grel\upsilon$}}\right\}
-\end{align*}
-A similar argument now shows that $\grel{\comp{\sigma\tensor(\tau\tensor\upsilon)}{\assoc_{A', B', C'}}}$ is equal to the same set, and so we have a commutative diagram in $\Rel$:
-\[
-  \begin{tikzcd}
-    P_{(A'\tensor B')\tensor C'} \arrow[r, "\grel{(\sigma\tensor\tau)\tensor\upsilon}"'] \arrow[d, "\grel{\assoc_{A', B', C'}}"']
-      & P_{(A\tensor B)\tensor C} \arrow[d, "\grel{\assoc_{A,B,C}}"] \\
-    P_{A'\tensor(B'\tensor C')} \arrow[r, "\grel{\sigma\tensor(\tau\tensor\upsilon)}"']
-      & P_{A\tensor(B\tensor C)}
-  \end{tikzcd}
-  \]
-Therefore, our original diagram in $\G(\alpha)$ is commutative, since the functor $\F$ is faithful.
-
-We therefore have the structure of a symmetric monoidal category on $\G(\alpha)$.
-
-\subsubsection{Symmetric monoidal closed structure}
-\label{TransSMCCSex}
-
-In existing finitary models of game semantics, the category of games is made into a symmetric monoidal closed category where the linear implication of two objects is given by the connective $\implies$.
-As we remarked earlier, this approach will not work immediately for us, since $A\implies B$ need not be completely negative even if $A$ and $B$ are.
-Our solution will be to modify $A\implies B$ so that it becomes completely negative.
-
-Remember that when we proved that the composition of strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ is well defined, we were careful not to require that $C$ be acn (or completely negative).
-From the point of view of constructing a category whose objects are $\alpha$-games, this is not useful, but it does allow us to construct certain alternative categories.
-
-\begin{definition}
-  Recall that if $\C$ is a category and $A$ is an object of $\C$, then the \emph{slice category} $\C/A$ is the category where the objects are morphisms
-  \[
-    \map{f}{B}{A}
-    \]
-  where $B$ is an object of $\C$ and where the morphisms between an object $\map{f}{B}{A}$ and an object $\map{g}{C}{A}$ are commutative triangles:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "f"] \arrow[d, "h"']
-       & A \\
-      C \arrow[ur, "g"]
-        &
-    \end{tikzcd}
-    \]
-  Let $A$ be a (not necessarily completely negative) $\alpha$-game.  Abusing notation slightly, we write $\G(\alpha)/A$ for the category whose objects are strategies
-  \[
-    \sigma\from B\implies A
-    \]
-  for $B$ a \emph{completely negative} $\alpha$-game and where the morphisms from an object $\map{\sigma}{B}{A}$ to an object $\map{\tau}{C}{A}$ are commutative triangles of the form
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\sigma"] \arrow[d, "\upsilon"']
-       & A \\
-      C \arrow[ur, "\tau"]
-        &
-    \end{tikzcd}
-    \]
-\end{definition}
-
-The main technical result we shall use to construct our closed monoidal structure is the following theorem:
-\begin{theorem}
-  \label{SliceTerminalObject}
-  Let $A$ be an $\alpha$-game.  Then the category $\G(\alpha)/A$ has a terminal object.
-\end{theorem}
-
-Note that if $A$ is completely negative, then the terminal object of $\G(\alpha)/A$ is the identity strategy $\map{\id_A}{A}{A}$, as is standard for slice categories.
-If $A$ is not completely negative, then we will need to use a different construction.
-
-We will write this terminal object as $A^{\cn}\xrightarrow{\cn}A$.
-$A^{\cn}$ should be thought of as the `smallest completely negative extension of $A$', and the fact that it gives rise to a terminal object in $\G(\alpha)/A$ makes this vague notion precise.
-If $A$ and $B$ are completely negative $\alpha$-games, we shall define a game $A\impliescn B$ to be given by $(A\implies B)^{\cn}$.
-We will then be able to use the fact that $(A\implies B)^{\cn}$ gives rise to a terminal object in the category $\G(\alpha)/(A\implies B)$ to show that the connective $\impliescn$ in fact gives rise to a monoidal closed structure on $\G(\alpha)$.
-
-\begin{definition}
-  Let $A$ be an $\alpha$-game.  We form a completely negative $\alpha$-game $A^{\cn}$ as follows:
-  \begin{itemize}
-    \item $M_{A^{\cn}}=M_A\cprd \{*_t\suchthat \textrm{$t\in P_A$ is a limiting $O$-play}\}$
-    \item $\lambda_{A^{\cn}}(x)=\lambda_A(x)$ for all $x\in M_A$.  $\lambda_{A^{\cn}}(*_s)=O$
-    \item $\zeta_{A^{\cn}}(sx)=\lambda_{A^{\cn}}(x)$ for $sx\in P_{A^{\cn}}$ a successor play.
-    \item $\zeta_{A^{\cn}}(s)=P$ for $s\in P_{A^{\cn}}$ a limiting play.
-  \end{itemize}
-  \[
-    P_{A^{\cn}} = \left\{s\in \left(M_{A^{\cn}}\right)^{*<\alpha}\;\middle|\;\mbox{\pbox{200px}{
-      $t\vert_{M_A}\in P_A$\\
-      If $u*_t\prefix s$ then $u=t$. \\
-      If $vx\prefix s$ and $v\vert_{M_A}$ is a limiting $O$-play in $P_A$ then $x=*_v$
-    }}\right\}
-    \]
-
-  In other words, we force $A$ to be completely negative by making all limiting plays be $P$-plays.
-If $u$ was a limiting $O$-play in $A$, then it becomes a $P$-play in $A^{\cn}$.
-Since the moves that follow $u$ in $A$ are $P$-moves, we add in an extra $O$-move $*_u$ in order to preserve the alternating condition.
-\end{definition}
-
-\begin{example}
-  If $\alpha=\omega$ and $A$ is a negative game then we have $\bneggame A^{\cn}\cong A\implies\bot$: the single move in $\bot$ takes the role of $*_{\emptyplay}$.
-However, if $\alpha$ is a higher ordinal, then this does not hold, since $A\implies\bot$ is no longer a completely negative game.
-
-  If $A,B$ are completely negative $\alpha$-games, we define $A\impliescn B$ to stand for $(A\implies B)^{\cn}$.
-Then we do have $\bneggame{A}^{\cn}\cong A\impliescn \bot$.
-The object $A\impliescn B$ will be the linear implication in our category.
-\end{example}
-
-\begin{notation}
-  Given a sequence $s\in P_{A^{\cn}}$, we may restrict $s$ to a play $s\vert_A\in P_A$ by removing all the $*$-moves.  
-\end{notation}
-
-Given an $\alpha$-game $A$, there is a natural strategy $\cn_A$ for $A^{\cn}\implies A$ given by
-\[
-  \cn_A = \left\{s\in P_{A^{\cn}\implies A}\suchthat\textrm{for all $P$-positions $t\prefix s$, $t\vert_{A^{\cn}}\vert_A=t\vert_A$}\right\}
-  \]
-Concretely, this strategy is the copycat strategy for $A$, with the difference that whenever we reach a limiting $O$-play $u$ in $A$, player $P$ plays the extra move $*_u$ in $A^{\cn}$ before continuing.
-
-We claim that $\map{\cn_A}{A^{\cn}}{A}$ is the terminal object in the category $\G(\alpha)/A$.  To do that, it will suffice to prove the following proposition:
-
-\begin{proposition}
-  \label{CnUniversalProperty}
-  $\cn_A$ is a total strategy for $A^{\cn}\implies A$.
-Moreover, $\cn_A$ satisfies the following universal property: given a completely negative $\alpha$-game $B$ and a strategy $\sigma$ for $B\implies A$, there is a unique strategy $\sigma^{\cn}$ for $B\implies A^{\cn}$ such that the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\sigma^{\cn}"] \arrow[dr, "\sigma"']
-        & A^{\cn} \arrow[d, "\cn_A"] \\
-      %
-        & A
-    \end{tikzcd}
-    \]
-\end{proposition}
-
-\begin{proof}
-  We first show that $\cn_A$ is a valid strategy for $A^{\cn}\implies A$.
-It is certainly prefix closed and satisfies the limiting condition by its definition.
-Moreover, if $s\in\cn_A$ is a $P$-position and $sx\in P_{A^{\cn}\implies A}$ then $sx$ satisfies the conditions to be an element of $\cn_A$.
-
-  Suppose that $sx, sy\in \cn_A$ are $P$-positions.
-Suppose first that neither $x$ nor $y$ is a move of the form $*_t$.
-We claim that $sx,sy$ take place in the same game.
-Indeed, suppose instead that $x$ is a move in $A^{\cn}$ and $y$ is a move in $A$.
-Then we have:
-  \begin{gather*}
-    s\vert_{A^{\cn}}\vert_A x = sx\vert_{A^{\cn}}\vert_A = sx\vert_A = s\vert_A\\
-    s\vert_{A^{\cn}}\vert_A = sy\vert_{A^{\cn}}\vert_A = sy\vert_A = s\vert_Ay
-  \end{gather*}
-  which is a contradiction since it implies that $s\vert_{A^{\cn}}\vert_A$ is simultaneously a shorter sequence than $s\vert_A$ and a longer sequence than $s\vert_A$.
-
-  If $x,y$ are both moves in $A^{\cn}$ then we have
-  \begin{align*}
-    s\vert_{A^{\cn}}\vert_A x &= sx\vert_{A^{\cn}}\vert_A \\
-    & = sx\vert_A\\
-    & = s\vert_A
-  \end{align*}
-  and $s\vert_{A^{\cn}}\vert_Ay=s\vert_A$ by an identical argument, and so $x=y$.  Similarly, if $x,y$ are both moves in $A$, then we have:
-  \begin{align*}
-    s\vert_A x &= sx\vert_A \\
-    &= sx\vert_{A^{\cn}}\vert_A\\
-    &= s\vert_{A^{\cn}}\vert_A
-  \end{align*}
-  and similarly for $y$, so $x=y$.
-
-  Now, without loss of generality assume that $x=*_t$ for some $t$.  Then $s\vert_{A^{\cn}}\vert_A$ is a limiting play.  Suppose for a contradiction that $y$ is a move in $A$.  Then we have:
-  \[
-    s\vert_{A^{\cn}}\vert_A = sy\vert_{A^{\cn}}\vert_A=sy\vert_A = s\vert_Ay
-    \]
-  which is a contradiction, since $s\vert_Ay$ is a successor play.  Therefore, $y$ is a move in $A^{\cn}$.  We have:
-  \begin{align*}
-    t &= s\vert_{A^{\cn}}\vert_A\\
-    &= s*_t\vert_{A^{\cn}}\vert_A\\
-    &= s*_t\vert_{A^{\cn}}\vert_A\\
-    &= s\vert_{A^{\cn}}\vert_A
-  \end{align*}
-  Therefore, $s\vert_{A^{\cn}}\vert_A$ is a limiting $O$-play in $A$ and therefore we have $x=y=*_t$ by the definition of $A^{\cn}$.
-
-  Now we show that $\cn_A$ is total.
-Suppose that $s\in\cn_A$ is an $O$-position.
-Then $s\vert_{A^{\cn}}$ is a $P$-position and $s\vert_A$ is an $O$-position.
-Suppose that $s=ty$ is a successor play.
-Note that $y$ cannot be a $*$-move, since these are all $O$-moves occurring in $A^{\cn}$.
-If $y$ takes place in $A^{\cn}$ then we have $t\vert_{A^{\cn}}\vert_A=t\vert_A$ and therefore player $P$ can play $y$ in $A$ and still be playing according to $\cn$.
-Similarly, if $y$ takes place in $A$, then player $P$ can play $y$ in $A^{\cn}$ and be in accordance with $\cn_A$.
-
-  Suppose instead that $s$ is a limiting play.
-It is clear from the definition that $s\vert_{A^{\cn}}\vert_A$ and $s\vert_A$ are both cofinal in $s$, so they are both limiting plays.
-Therefore, $s\vert_A$ is a limiting $O$-play in $A$ and $s\vert_{A^{\cn}}\vert_A$ must be the corresponding $P$-play in $A^{\cn}$.
-Therefore, player $P$ may play $*_t$ (where $t=s\vert_A$) in $A^{\cn}$ and still be in accordance with $A^{\cn}$.
-So $\cn_A$ is total.
-
-  Let $q\in P_A$.
-We claim that there is some $s\in\cn_A$ such that $s\vert_A=q$.
-Indeed, since Player $P$ makes all $*$-moves in $A^{\cn}\implies A$, player $O$ has a strategy for $A^{\cn}\implies A$ in which he plays the moves of the sequence $q$ in order.
-Since the strategy $\cn_A$ is total, player $P$ always has a reply to Player $O$'s moves and the resulting sequence $s$ satisfies $s\vert_A=q$.
-
-  Therefore, the relational presentation of $\cn_A$ has the following property: for all sequences $q\in P_A$, there exists some $r\in P_{A^{\cn}}$ such that $(r,q)\in\grel{\cn_A}$.
-Moreover, it is not difficult to see that this $r$ is unique, since play passes from $A$ to $A^{\cn}$ without fail at each turn, so a $P$-position in $\cn_A$ is uniquely determined by its sequence of $O$-moves, which must agree with its $A$-component.
-
-  In other words, the relational presentation $\grel{\cn_A}$ is the graph of an injective function $h\colon P_A\to P_{A^{\cn}}$.
-
-  Let $B$ be a completely negative $\alpha$-game and let $\sigma$ be a strategy for $B\implies A$.  We define the strategy $\sigma^{\cn}$ for $B\implies A^{\cn}$ as follows:
-  \[
-    \sigma^{\cn} = \{s\in P_{B\implies A^{\cn}}\suchthat s\vert_{B,M_A}\in\sigma\}
-    \]
-  where we write $s\vert_{B,M_A}$ for the sequence obtained by deleting all $*$-moves from $s$.
-
-  $\sigma^{\cn}$ is prefix closed, since $\sigma$ is, and satisfies the limit condition, since $\sigma$ does.
-Suppose that $s\in\sigma^{\cn}$ is a $P$-position and that $sx\in P_{B\implies A^{\cn}}$.
-If $x$ is a $*$-move, then we have $sx\vert_{B,M_A}=s\vert_{B,M_A}\in\sigma$, so $sx\in\sigma^{\cn}$.
-Otherwise, we have $sx\vert_{B,M_A}=s\vert_{B,M_A}x$.
-
-  If $s\vert_{B,M_A}$ is a $P$-position in $B\implies A$ then $s\vert_{B,M_A}x\in\sigma$ and therefore $sx\in\sigma^{\cn}$.
-So suppose instead that $s\vert_{B,M_A}$ is an $O$-position.
-If $s=ty$ is a successor position then $y$ is a $P$-move in $B\implies A^{\cn}$, so in particular $y$ is not a $*$-move and therefore $s\vert_{B,M_A}=t\vert_{B,M_A}y$ is a $P$-position.
-Therefore, $s$ must be a limiting play.
-
-  Since $s$ is a $P$-position, $s\vert_B$ must be a $P$-position, $s\vert_{A^{\cn}}\vert_A$ must be an $O$-position in $A$ and $s\vert_{A^{\cn}}$ must be a $P$-position in $A^{\cn}$.
-It follows that $u\coloneqq s\vert_{A^{\cn}}\vert_A$ is a limiting $O$-play.
-It follows that $x$ is a move in $A^{\cn}$, and therefore that $x=*_u$, which is a case we have already dealt with.
-
-  Next, suppose that $sx, sy\in\sigma^{\cn}$ are $P$-positions.
-In particular, $x,y$ are not $*$-moves and we have $s\vert_{B,M_A}x,s\vert_{B,M_A}y\in\sigma$.
-Therefore, $x=y$.
-So $\sigma^{\cn}$ is a strategy.
-
-  Lastly, suppose that $\sigma$ is a total strategy.
-Let $s\in\sigma^{\cn}$ be an $O$-position in $B\implies A^{\cn}$.
-Then $s\vert_B$ is a $P$-position in $B$ and $s\vert_{A^{\cn}}$ is an $O$-position in $A^{\cn}$.
-So $s\vert_{A^{\cn}}$ is a successor play in $A^{\cn}$, since $A^{\cn}$ is completely negative.
-If the last move of $s\vert_{A^{\cn}}$ is not a $*$-move then $s\vert_{A^{\cn}}\vert_A$ has the same last move as $s\vert_{A^{\cn}}$ and is therefore an $O$-position as well.
-Then $s\vert_{B,M_A}$ is an $O$-position and so there is some $x\in P_{B\implies A}$ such that $s\vert_{B,M_A}x\in\sigma$.
-Then $sx\in P_{B\implies A^{\cn}}$ and so $sx\in\sigma^{\cn}$.
-
-  Suppose instead that $s\vert_{A^{\cn}}=t*_u$, where $u=t\vert_A$.
-Then $u$ is an $O$-position in $A$, so $s\vert_{B,M_A}$ is an $O$-position in $B\implies A$ and therefore there is some $x\in P_{B\implies A}$ such that $s\vert_{B,M_A}x\in\sigma$.
-Then $sx\in\sigma^{\cn}$.
-So $\sigma^{\cn}$ is a total strategy.
-
-  We claim that $\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}=\grel\sigma$.
-Then we will have $\comp{\cn_A}{\sigma^{\cn}}=\sigma$ by Lemma \ref{TransHylandSchalkFaithful} and Corollary \ref{TransHylandSchalkIsFunctor}.
-Suppose $(s,t)\in\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}$.
-Then there is some $u\in P_{A^{\cn}}$ such that $(s,u)\in\grel{\sigma^{\cn}}$ and $(u,t)\in\grel{\cn_A}$.
-Therefore, $(s,u\vert_A)\in\grel\sigma$ and $t=u\vert_A$.
-It follows that $(s,t)\in\grel{\sigma}$, so $\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}\subset\grel\sigma$.
-
-  To show the reverse inclusion, we shall use the following lemma, which we shall prove later.
-
-  \begin{lemma}
-    \label{CnLiftingLemma}
-    Let $B$ be a completely negative $\alpha$-game, let $A$ be an arbitrary $\alpha$-game and let $\sigma$ be a strategy for $B\implies A$.
-Let $s\in\sigma$ be a $P$-position.
-Then there is a unique $P$-position $t\in B\implies A^{\cn}$ such that $t\vert_{B,M_A}=s$.
-  \end{lemma}
-
-  We use Lemma \ref{CnLiftingLemma} to show the reverse inclusion as follows: let $s\in\sigma$ be a $P$-position -- so $(s\vert_B,s\vert_A)$ is an arbitrary element of $\grel\sigma$.
-By Lemma \ref{CnLiftingLemma} there exists $t\in B\implies A^{\cn}$ such that $t\vert_{B,M_A}=s$.
-In particular, $t\vert_{A^{\cn}}\vert_A=s\vert_A$ and $t\vert_B=s\vert_B$.
-So we have $(s\vert_B,t\vert_{A^{\cn}})\in\grel{\sigma^{\cn}}$ and $(t\vert_{A^{\cn}},s\vert_A)\in\grel{\cn_A}$.
-It follows that $(s\vert_B,s\vert_A)\in\grel{\sigma}$.
-So $\grel\sigma\subset\comp{\grel{\cn_A}}{\grel{\sigma^{\cn}}}$.
-
-  Lastly, we need to show that the strategy $\sigma^{\cn}$ is unique.  Suppose that there were some other strategy $\tau$ for $B\implies A^{\cn}$ making the diagram commute:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\tau"] \arrow[dr, "\sigma"']
-        & A^{\cn} \arrow[d, "\cn_A"] \\
-      %
-        & A
-    \end{tikzcd}
-    \]
-  We shall show that $\grel\tau=\grel{\sigma^{\cn}}$ -- so $\tau=\sigma^{\cn}$.
-First suppose that $s\in\sigma^{\cn}$ is a $P$-position.
-Since $\sigma = \comp{\cn_A}{\tau}$, there is some sequence $\s\in\tau\|\cn_A$ such that $\s\vert_{B,A}=s\vert_{B,M_A}$.
-We have $\s\vert_{A^{\cn}}\vert_A=\s\vert_A$ and therefore $s\vert_{B,M_A}=\s\vert_{B,A^{\cn}}\vert_{B,M_A}$.
-Therefore, $s=\s\vert_{B,A^{\cn}}\in\tau$, by uniqueness in Lemma \ref{CnLiftingLemma}.
-So $\grel{\sigma^{\cn}}\subset\grel{\tau}$.
-
-  Conversely, suppose that $s\in\tau$ is a $P$-position.
-Then our argument above tells us that we have $(s\vert_{A^{\cn}},s\vert_{A^{\cn}}\vert_A)\in\grel{\cn_A}$.
-So $(s\vert_B,s\vert_{A^{\cn}}\vert_A)\in\grel\sigma$.
-Therefore there is some $P$-position $u\in\sigma$ such that $u\vert_B=s\vert_B$ and $u\vert_A=s\vert_{A^{\cn}}\vert_A$.
-By Lemma \ref{CnLiftingLemma}, there is a sequence $t\in\sigma^{\cn}$ with $t\vert_{B,M_A}=s$.
-Then we have
-  \[
-    (s\vert_B,s\vert_{A^{\cn}})=(t\vert_B,t\vert_{A^{\cn}})\in\grel{\sigma^{\cn}}
-    \]
-  and therefore $\grel\tau\subset\grel{\sigma^{\cn}}$.  
-\end{proof}
-
-It remains to prove Lemma \ref{CnLiftingLemma}.
-
-\begin{proof}[Proof of Lemma \ref{CnLiftingLemma}]
-  This proof is similar to the proof of \ref{TransLiftingLemma}.
-We inductively construct a sequence $t^0\prefix t^1\prefix\dots\prefix t^\gamma\prefix\dots\prefix t^\beta$, where $t^\gamma$ has length $\gamma$ and $t^\beta$ is our desired sequence $t$.
-We shall prove inductively that $t^\gamma$ is the unique element $u\in\sigma^{\cn}$ of length $\gamma$ such that $u\vert_{B,M_A}=t$.
-
-  If $\gamma$ is a limit ordinal, then set $t^\gamma$ to be the limit of all the sequences $t^\delta$ for $\delta<\gamma$.
-We have $r\vert_{B,M_A}\prefix s$ for all proper prefixes $r\pprefix t^{\gamma}$ and therefore $t^\gamma\vert_{B,M_A}\prefix s$.
-For uniqueness, suppose that $u^\gamma$ has length $\gamma$ and $u^\gamma\vert_{B,M_A}\prefix s$.
-If $\delta<\gamma$ and we write $u^\delta$ for the prefix of $u^\gamma$ of length $\delta$ then we have $u^\delta=t^\delta$ by uniqueness and it follows that $u^\gamma=t^\gamma$.
-
-  Suppose instead that $\gamma=\delta+1$ is a successor ordinal.  We have a sequence $t^\delta$ of length $\delta$.
-
-  Suppose first that $t^\delta$ is an $O$-position.
-Then, as usual, $t^\delta\vert_{B,M_A}$ is an $O$-position.
-We have $t^\delta\vert_{B,M_A}\prefix s$; since $s$ is a $P$-position, this must be a proper prefix, so there is some move $x$ such that $t^\delta\vert_{B,M_A}x\prefix s$.
-By the argument above (showing that $\sigma^{\cn}$ is total if $\sigma$ is total), we must have $t^\delta x\in\sigma$.
-We set $t^{\delta+1}=t^\delta x$.
-Then $t^{\delta+1}\vert_{B,M_A}\prefix s$.
-
-  For uniqueness, suppose that $u^{\delta+1}$ is some other sequence of length $\delta+1$ with $u^{\delta+1}\vert_{B,M_A}\prefix s$.
-Writing $u^{\delta+1}=u^\delta y$, we have $u^{\delta}=t^\delta$ by uniqueness for sequences of length $\delta$.
-Then $t^\delta x,t^\delta y\in\sigma$ and so $x=y$.
-So $u^{\delta+1}=t^{\delta+1}$.
-
-  Now suppose that $t^\delta$ is a $P$-position.
-We have $t^\delta\vert_{B,M_A}\prefix s$.
-If $t^\delta\vert_{B,M_A}=s$ then we terminate, setting $\beta=\delta$.
-Otherwise, there is some move $x$ such that $t^\delta\vert_{B,M_A}x\prefix s$.
-
-  Suppose that $t^\delta\vert_{B,M_A}$ is a $P$-position.
-Then $x$ is an $O$-move, so $t^\delta x$ is alternating.
-\textbf{Since $B$ is completely negative}, Proposition \ref{NiceAcnGames} tells us that $t^\delta x\in P_{B\implies A^{\cn}}$.
-Therefore, $t^\delta x\in\sigma^{\cn}$, since $\sigma^{\cn}$ is a strategy.
-We set $t^{\delta+1}=t^\delta x$.
-Then we certainly have $t^{\delta+1}\vert_{B,M_A}\prefix s$.
-For uniqueness, suppose that $u^{\delta+1}$ has length $\delta+1$ and that $u^{\delta+1}\vert_{B,M_A}\prefix s$.
-Then $u^{\delta+1}=t^\delta y$ for some $y$ by uniqueness for sequences of length $\delta$.
-Since $t^\delta\vert_{B,M_A}$ is a $P$-position, it is in particular not a limiting $O$-play, so $y$ cannot be a $*$-move.
-Therefore, we have $u^{\delta}\vert_{B,M_A}y\prefix s$ and so $x=y$.
-
-  Suppose instead that $t^\delta\vert_{B,M_A}$ is an $O$-position.
-Then $v\coloneqq t^\delta\vert_{A^{\cn}}\vert_A$ must be a limiting $O$-play.
-We set $t^{\delta+1}=t^\delta *_v$.
-Since $*_v$ is the only move possible in position $t^\delta$, this must certainly be unique, and we have $t^\delta *_v\vert_{B,M_A}=t^\delta\vert_{B,M_A}\prefix s$.
-
-  This completes the proof by induction.
-\end{proof}
-
-\subsubsection{A digression}
-\label{DigressionSex}
-
-Earlier on, we defined a category $\G(\alpha)/A$ for $A$ an arbitrary $\alpha$-game.  At this point, it is tempting to define a category as follows:
-
-\begin{definition}
-  The objects of the category $\tilde{\G}(\alpha)$ are (not necessarily completely negative) $\alpha$-games.
-If $A,B$ are $\alpha$-games, a morphism in $\tilde{\G}(\alpha)$ from $A$ to $B$ is a functor
-  \[
-    \F\from\G(\alpha)/A\to\G(\alpha)/B
-    \]
-  that commutes with the natural projection functors $p_A\from\G(\alpha)/A\to\G(\alpha)$ and $p_B\from\G(\alpha)/B\to\G(\alpha)$.  
-\end{definition}
-
-This definition is useful because we have a natural embedding (the $2$-Yoneda embedding) of $\G(\alpha)$ into the category $\tilde{\G}(\alpha)$ that sends a completely negative game $N$ to the category $\G/N$ and sends a morphism $\sigma\from M\implies N$ to the `post-composition with $\sigma$' functor between the slice categories $\G(\alpha)//M$ and $\G(\alpha)/N$.
-
-It is well known that this is a fully faithful embedding.
-I claim that it is also essentially surjective, so it is in fact an equivalence of categories.
-Indeed, this follows from what we have just shown:
-
-\begin{proposition}
-  Let $A$ be an arbitrary $\alpha$ game.  Then the categories $\G(\alpha)/A$ and $\G(\alpha)/A^{\cn}$ are isomorphic as categories, via an isomorphism that commutes with the projection functors.
-
-  \begin{proof}
-    We have a natural functor from $\G(\alpha)/A^{\cn}$ to $\G(\alpha)/A$ given by post-composition with $\cn_A$, where functoriality follows from associativity of composition.
-This functor certainly commutes with the projection functors.
-Then Proposition \ref{CnUniversalProperty} tells us that it is fully faithful and a bijection on objects, so it is a categorical isomorphism.
-  \end{proof}
-\end{proposition}
-
-Therefore, the categories $\G(\alpha)$ and $\tilde{\G}(\alpha)$ are equivalent.
-This suggests one strategy for defining a symmetric monoidal closed structure on $\G(\alpha)$: since the objects of $\tilde{\G}(\alpha)$ are not required to be completely negative, we may freely define a closed monoidal structure on $\tilde{\G}(\alpha)$ by setting the linear implication between games $A$ and $B$ to be the game $A\implies B$ and the tensor product to be the game $A\tensor B$.
-This symmetric monoidal closed structure will give rise to a symmetric monoidal closed structure on $\G(\alpha)$ via the equivalence of categories.
-
-However, there is still quite a lot of work to show that this does indeed give a symmetric monoidal closed structure on $\tilde{\G}(\alpha)$, and it will be easier to construct the closed structure on $\G(\alpha)$ directly.
-
-\subsubsection{The completely negative linear implication $A\impliescn B$}
-\label{ImpliesCnSex}
-
-Let $A,B$ be completely negative $\alpha$-games.
-We have a completely negative $\alpha$-game $A\impliescn B\coloneqq (A\implies B)^{\cn}$.
-We shall construct a monoidal closed structure on $\G(\alpha)$ where the linear implication between $A$ and $B$ is $A\impliescn B$.
-
-We shall start off with the relevant result about the (usual) implication $A\implies B$:
-
-\begin{proposition}
-  \label{impliesTreeIsom}
-  Let $A,B,C$ be completely negative $\alpha$ games.  Then the games $(A\tensor B)\implies C$ and $A\implies(B\implies C)$ are tree isomorphic.
-\end{proposition}
-
-\begin{note}
-  Since $(A\tensor B)\implies C$ is not a completely negative game in general, we cannot say that these games are isomorphic as objects of $\G(\alpha)$, but it will help us to know that they are tree-isomorphic as games.
-\end{note}
-
-\begin{proof}[Proof of Proposition \ref{impliesTreeIsom}]
-  The sets of plays $P_{(A\tensor B)\implies C}$ and $P_{A\implies(B\implies C)}$ are both appropriate subsets of $P_A\|P_B\|P_C$.
-We just need to check that $\lambda_{(A\tensor B)\implies C}=\lambda_{A\implies(B\implies C)}$ and that $\zeta_{(A\tensor B)\implies C}=\zeta_{A\implies(B\implies C)}$.
-
-  We have
-  \begin{align*}
-    \lambda_{(A\tensor B)\implies C} &= \neg\circ\lambda_{A\tensor B}\cprd\lambda_C\\
-    &= \neg\circ\lambda_A\cprd\neg\circ\lambda_B\cprd\lambda_C\\
-    &= \neg\circ\lambda_A\cprd\lambda_{B\implies C}\\
-    &= \lambda_{A\implies(B\implies C)}
-  \end{align*}
-  and
-  \begin{align*}
-    \zeta_{(A\tensor B)\implies C}(s) & = ((\zeta_A(s\vert_A)\wedge\zeta_B(s\vert_B))\Rightarrow\zeta_C(s\vert_C))\\
-    &=(\zeta_A(s\vert_A)\Rightarrow(\zeta_B(s\vert_B)\Rightarrow\zeta_C(s\vert_C))) \\
-    &=\zeta_{A\implies(B\implies C)}(s)
-  \end{align*}
-  where we can prove the second equality as follows: if $p,q,r\in\OP$, then $((p\wedge q)\Rightarrow r) = O$ if and only if $p=q=P$ and $r=O$.
-Meanwhile, $(p\Rightarrow (q\Rightarrow r))=O$ if and only if $p=q=P$ and $r=O$.
-So $((p\wedge q)\Rightarrow r) = (p\Rightarrow(q\Rightarrow r))$.
-\end{proof}
-
-To construct the monoidal closed structure, it suffices to give a morphism
-\[
-  \ev_{A,B}\from (A\impliescn B)\tensor A\to B
-  \]
-for all pairs $(A,B)$ of completely negative $\alpha$-games, such that for all completely negative $\alpha$-games $X$ and all morphisms $\sigma\from X\tensor A\to B$ there is a unique morphism $\upsilon\from X\to A\impliescn B$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    X\tensor A_3 \arrow[r, "\sigma"] \arrow[d, "\upsilon\tensor\id_A"']
-      & B_2 \\
-    (A_1\impliescn B_1)\tensor A_2 \arrow[ur, "\ev_{A,B}"']
-      &
-  \end{tikzcd}
-  \]
-(Here we have numbered the copies of $A$ and $B$ so we can refer to them individually).
-
-The strategy $\ev_{A,B}$ for $((A\impliescn B)\tensor A)\implies B$ is constructed as follows: we have our strategy $\cn_{A\implies B}$ for $(A\impliescn B)\implies(A\implies B)$.
-By Proposition \ref{impliesTreeIsom}, this game is tree isomorphic to the game $((A\impliescn B)\tensor A)\implies B$, so we get the strategy $\ev_{A,B}$ by applying this tree isomorphism to the strategy $\cn_{A\implies B}$.
-
-We need to show that the strategy $\ev_{A,B}$ satisfies the property given above.
-Let $X$ be a completely negative $\alpha$-game and let $\sigma$ be a strategy for $(X\tensor A)\implies B$.
-Then $\sigma$ gives rise, via the tree isomorphism above, to a strategy $\tilde{\sigma}$ for $X\implies(A\implies B)$.
-Since the tree isomorphism does nothing more than identify $P_{(X\tensor A)\implies B}$ with $P_{X\implies(A\implies B)}$ as subsets of $(M_X\cprd M_B\cprd M_C)^{*<\alpha}$, we may identify $\sigma$ and $\tilde{\sigma}$ as subsets of $(M_X\cprd M_A\cprd M_B)$.
-
-Similarly, we may identify $\ev_{A,B}$ with $\cn_{A\implies B}$ as subsets of 
-\[
-  \left(M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}
-  \]
-where we have again labelled the different copies of $A$ and $B$ to avoid confusion.
-
-The strategy $\tilde{\sigma}$ gives rise to a strategy ${\tilde{\sigma}}^{\cn}$ for $X\implies(A\impliescn B)$.  We claim that this ${\tilde{\sigma}}^{\cn}$ satisfies the property above.
-
-First, we show that $\comp{\ev_{A,B}}{({\tilde{\sigma}}^{\cn}\tensor\id_A)}=\sigma$.  By the definition of ${\tilde{\sigma}}^{\cn}$, we know that it makes the following diagram commute:
-\[
-  \begin{tikzcd}
-    X \arrow[r, "{\tilde{\sigma}}^{\cn}"] \arrow[dr, "\tilde\sigma"']
-      & A_1\impliescn B_1 \arrow[d, "\cn_{A\implies B}"] \\
-    %
-      & A_2\implies B_2
-  \end{tikzcd}
-  \]
-where we have labelled the copies of $A$ and $B$ so we can tell them apart.  Therefore, we have
-\[
-  \tilde\sigma = \{\s\vert_{X,A_2,B_2}\suchthat \s\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}\}
-  \]
-where
-\[
-  {\tilde\sigma}^{\cn}\|\cn_{A\implies B} = \left\{\s\in \left(M_X\cprd M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}\;\middle|\;\mbox{\pbox{\textwidth}{
-    $\s\vert_{X,A_1,B_1}\in{\tilde\sigma}^{\cn}$\\
-    $\s\vert_{A_1,B_1,A_2,B_2}\in\cn_{A\implies B}$
-  }}\right\}
-  \]
-Now we have
-\[
-  \comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}=
-  \left\{\t\vert_{X,A_2,B_2}\suchthat\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}\right\}
-  \]
-where
-\[
-  \left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}
-  =\left\{\t\in\left(M_X\cprd M_{A_3}\cprd M_{A_1}\cprd M_{B_1}\cprd M_{A_2}\cprd M_{B_2}\right)^{*<\alpha}\;\middle|\;
-  \mbox{\pbox{\textwidth}{
-    $\t\vert_{X,A_1,B_1}\in{\tilde\sigma}^{\cn}$\\
-    $\t\vert_{A_3,A_2}\in\id_A$\\
-    $\t\vert_{A_2,B_2}\in\ev_{A,B}$
-  }}\right\}
-  \]
-Remembering that we may identify $\ev_{A,B}$ with $\cn_{A\implies B}$ as sets of plays, we see that
-\[
-  \comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}\subset\tilde\sigma=\sigma
-  \]
-since if $\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}$ then we have $\t\vert_{X,A_1,B_1,A_2,B_2}\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}$ and so $\t\vert_{X,A_2,B_2}\in\tilde\sigma$.
-
-Conversely, let $s\in\tilde\sigma$ and write $s=\s\vert_{X,A_2,B_2}$, where $\s\in{\tilde\sigma}^{\cn}\|\cn_{A\implies B}$.
-We may construct a sequence $\t\in\left({\tilde\sigma}^{\cn}\tensor\id_A\right)\|\ev_{A,B}$ with $\t\vert_{X,A_1,B_1,A_2,B_2}=\s$ by inserting before each $P$-move in $A_2$ the corresponding move in $A_3$ and inserting \emph{after} each $O$-move in $A_2$ the corresponding move in $A_3$.
-Therefore:
-\[
-  \sigma\subset\comp{\ev_{A,B}}{({\tilde\sigma}^{\cn}\tensor\id_A)}
-  \]
-For uniqueness, suppose that we have a strategy $\upsilon$ for $X\implies(A\impliescn B)$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    X\tensor A_3 \arrow[r, "\sigma"] \arrow[d, "\upsilon\tensor\id_A"']
-      & B_2 \\
-    (A_1\impliescn B_1)\tensor A_2 \arrow[ur, "\ev_{A,B}"']
-      &
-  \end{tikzcd}
-  \]
-Exactly the same argument then tells us that
-\[
-  \comp{\cn_{A\implies B}}{\upsilon}=\comp{\ev_{A,B}}{\upsilon\tensor\id_A}=\sigma=\tilde\sigma
-  \]
-(as sets of plays) and so $\upsilon={\tilde\sigma}^{\cn}$ by the uniqueness part of Proposition \ref{CnUniversalProperty}.
-
-Therefore $\G(\alpha)$ has the structure of a symmetric monoidal category with tensor product given by $\tensor$ and linear implication given by $\impliescn$.
-
-\subsubsection{Win-games and winning strategies}
-
-We shall not develop the theory of transfinite win-games in this report, leaving this work for future research.
-The basic idea is as follows.
-Let $\alpha$ be an ordinal of the form $\omega^\beta$.
-We form a category $\G(\alpha+1)$ of games where the objects are acn $\alpha+1$-games.
-
-Given an acn $\alpha+1$-game $A$, we have an associated $\alpha$-game $A^\circ$ given by forgetting about the plays of length $\alpha$.
-We call a total strategy $\sigma$ for $A^\circ$ \emph{winning} if every play of length $\alpha$ that is the limit of plays from $\sigma$ is a $P$-play in $A$.
-
-We can then show that winning strategies compose to give winning strategies, just as in the $\omega+1$-case.
-The morphisms between objects $A$ and $B$ in our category will be winning strategies for $A^\circ\implies B^\circ$.
-We can then show that this category inherits a closed monoidal structure from $\G(\alpha)$.
-
-This construction agrees with the previous one in the sense that $\G(\omega+1)$ and our original category $\mathcal W$ of win-games are isomorphic as categories.
-
-\section{Exponentials}
-
-We want to model the exponential connective $\oc$ from linear logic in our game semantics.  We adapt the approach taken in \cite{laird02} and \cite{martinsthesis} to our transfinite games.
-
-\begin{definition}
-  Let $\G(\alpha)$ be a category of transfinite games and let $A$ be an object of $\G(\alpha)$.  Then the \emph{exponential} $\oc A$ is given as follows:
-  \begin{itemize}
-    \item $M_{\oc A} = A\times\omega$
-    \item $\lambda_{\oc A} = \lambda_A\circ\pr_1$
-  \end{itemize}
-
-  Given an ordinal-indexed sequence $s$ taking values in $M_{\oc A}$ and some $n\in\omega$, we write $s\vert_n$ for the subsequence of $s$ consisting of terms of the form $(a,n)$.  Then define
-  \[
-    \oc P_A = \{s\in M_{\oc A}^{*<\alpha}\suchthat s\vert_n\in P_A\textrm{ for all }n\in \omega\}
-    \]
-  We define $\zeta_{\oc A}\from \oc P_A\to \OP$ by
-  \[
-    \zeta_{\oc A}(s) = \bigwedge_{n\in \omega} \zeta_A(s\vert_n)
-    \]
-  (Here, if $(b_n)\in\OP^\omega$ then we have $\bigwedge_{n\in\omega} b_n = P$ if $b_n=P$ for all $n$ and $\bigwedge_{n\in\omega}=O$ otherwise.)
-
-  We define $P_{\oc A}$ to be the set of all sequences $s\in\oc P_A$ that are well formed with respect to $\zeta_{\oc A},\lambda_{\oc A}$ and are alternating with respect to $\zeta_{\oc A}$ and that satisfy the following property:
-
-  \begin{itemize}
-    \item If the term $(a,n)$ occurs in $s$, and if $m<n$, then there is some term $(b,m)$ that occurs earlier in the sequence $s$ than $(a,n)$.  
-  \end{itemize}
-
-  Then $\oc A=(M_{\oc A},\lambda_{\oc A},\zeta_{\oc A},P_{\oc A})$.  
-\end{definition}
-
-So $\oc A$ is like an infinite tensor product of copies of $A$ with the restriction that the first move must take place in the first copy and that moves may not take place in a subsequent copy of $A$ until moves have been made in all earlier copies.
-
-\begin{proposition}
-  $\oc A$ is a well formed game.
-  \begin{proof}
-    Exactly the same argument from Proposition \ref{TransTensorWellFormed}.
-  \end{proof}
-\end{proposition}
-
-Just like the tensor product, the exponential $\oc A$ has the property that only player $O$ may switch games:
-
-\begin{proposition}
-  \label{ExponentialWhoSwitchesGames}
-  Suppose that $s(a,m)(b,n)\in P_{\oc A}$, where $m\ne n$.  Then $\lambda_{\oc A}(b,n)=O$.  
-  \begin{proof}
-    $\begin{aligned}[t]
-      \lambda_{\oc A}(b,n) &= \zeta_{\oc A}(s(a,m)(b,n))\\
-      &= \bigwedge_{k\in\omega}\zeta_A(s(a,m)(b,n)\vert_k)
-    \end{aligned}$
-
-    Now by alternation we must have either $\zeta_A(s\vert_m(a,m))=O$ or $\zeta_A(s\vert_n(b,n))=O$.  So this last expression must be equal to $O$.
-  \end{proof}
-\end{proposition}
-
-We can also prove a version of Proposition \ref{NiceAcnGames} for the exponential connective using the same argument.
-
-To demonstrate why it is important to restrict the order in which the opponent $O$ may open games, we define a commutative comonoid structure on $\oc A$.
-The comultiplication $\mu\from \oc A\to \oc A\tensor \oc A$ is the copycat strategy that opens a new copy of $A$ on the left hand side whenever a new copy of $A$ is opened on the right hand side.
-(Here we see why the condition on the order in which games may be opened is important -- if we had no such restriction then there would be no canonical way to choose which copy of $A$ to open on the left hand side and the comultiplication would not be associative.)
-
-The counit $\eta\from \oc A\to I$ is the unique empty strategy on $\oc A\implies I$.
-
-For associativity of comultiplication, we want to check that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[dd, "\mu"']
-      & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \mu"] \\
-    %
-      & \oc A \tensor (\oc A \tensor \oc A) \arrow[d, "\assoc_{A,A,A}\inv"] \\
-    \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}"']
-      & (\oc A \tensor \oc A) \tensor \oc A
-  \end{tikzcd}
-  \]
-For this, note that each path round the diagram is a copycat strategy $\oc A \to (\oc A\tensor \oc A)\tensor \oc A$.
-Since we are forced to open copies of $\oc A$ in order, there is only one such copycat strategy, and so the two paths must be equal.
-
-Exactly the same argument tells us that comultiplication is commutative and that the counit is indeed a counit for this comultiplication.
-
-We have a natural forgetful functor from the category of comonoids over $\G(\alpha)$ to $\G(\alpha)$ itself.
-We first want to show that we have a functor in the opposite direction that sends a game $A$ to this comonoid over $\oc A$.
-
-Let $A,B$ be completely negative $\alpha$-games and let $\sigma$ be a strategy for $A\implies B$.  Then we have a natural strategy $\oc \sigma$ for $\oc A\implies\oc B$ given by
-\[
-  \oc\sigma = \{s\in P_{\oc A}\suchthat s\vert_n\in\sigma\textrm{ for all $n\in\omega$}\}
-  \]
-where we have written $s\vert_n$ for the subsequence of $s$ consisting of all terms that occur in the $n$-th copy of $A$ or the $n$-th copy of $B$.
-
-The proof that this is a strategy may be adapted from the discussion of the strategy $\sigma\tensor\tau$ above.
-Similarly, we may show that if $A,B,C$ are completely negative $\alpha$-games and we have strategies $A\xrightarrow{\sigma}B\xrightarrow{\tau}C$ then
-\[
-  \comp{\oc\tau}{\oc\sigma} = \oc(\comp\tau\sigma)
-  \]
-using the same argument we used to show that taking the tensor product of two strategies preserves composition.
-
-This gives us a functor $\cmap{\oc}{\G(\alpha)}{\G(\alpha)}$.
-We want to show that it gives rise to a functor from $\G(\alpha)$ into the category of comonoids over $\G(\alpha)$ sending a game $A$ to the comonoid $\oc A\to \oc A\tensor \oc A$.
-For this, we need to show that if $A,B$ are completely negative $\alpha$-games and $\sigma$ is a strategy for $A\implies B$ then the following diagram commutes:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[d, "\oc \sigma"']
-      & \oc A \tensor \oc A \arrow[d, "\oc \sigma \tensor \oc \sigma"] \\
-    \oc B \arrow[r, "\mu"']
-      & \oc B \tensor \oc B
-  \end{tikzcd}
-  \]
-Each branch of this diagram is a strategy for $\oc A\implies(\oc B\tensor\oc B)$ in which player $P$ plays according to $\sigma$, opening a new copy of $A$ on the left each time player $O$ opens a copy of $B$ on the right.
-Since the order in which player $P$ may open copies of $A$ is pre-determined, there is a unique such strategy, and so this diagram must commute.
-
-We shall eventually show that in fact $\oc A\to\oc A\tensor\oc A$ is the \emph{cofree commutative comonoid} on $A$.
-To show that, we will need \cite{martinsthesis} to give a map $\der\from\oc A\to A$, and we will need to show that for each commutative comonoid $B\to B\tensor B$ and each morphism $\sigma\from B\to A$ there exists a unique morphism $\sigma^\dagger\from B\to \oc A$ such that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    A
-      & \oc A \arrow[l, "\der"'] \arrow[r, "\mu"]
-        & \oc A \tensor \oc A \\
-    %
-      & B \arrow[r] \arrow[u, dotted, "\sigma^\dagger"'] \arrow[ul, "\sigma"]
-        & B\tensor B \arrow[u, dotted, "\sigma^\dagger \tensor \sigma^\dagger"']
-  \end{tikzcd}
-  \]
-We are not yet in a position to define the morphism $\sigma^\dagger$, but it is easy to see what $\der$ is: it is the copycat strategy on $\oc A\implies\oc A$ that copies the moves from $A$ on the right into the first copy of $A$ on the left.
-
-\subsection{Products in $\G(\alpha)$}
-
-Let $(A_i\suchthat i\in I)$ be a collection of objects of $\G(\alpha)$.  We define the product
-\[
-  \prod_i A_i
-  \]
-to be the game given by
-\begin{itemize}
-  \item $M_{\prod_i A_i}=\bigcprd_i M_{A_i}$
-  \item $\lambda_{\prod_i A_i}=\bigcprd_i \lambda_{A_i}$
-  \item $P_{\prod_i A_i} = \bigcprd_i P_{A_i}$
-  \item $\zeta_{\prod_i A_i} = \bigcprd_i \zeta_{A_i}$
-\end{itemize}
-This is the game where Player $O$ may decide which of the $A_i$ to play his first move in; play then continues in that game and the other games are never used.
-
-We claim that $\prod_i A_i$ is the categorical product of the $A_i$ in $\G(\alpha)$.
-First note that we have natural projection strategies $\pr_j$ for $\prod_i A_i\to A_j$ for each $j\in I$, in which player $P$ plays copycat in game $A_j$ on the left.
-Now if $B$ is an object of $\G(\alpha)$ and $\sigma_i$ are strategies for $B\implies A_i$ for each $i\in I$, then we have a strategy $\sigma$ for $B\implies\prod_i A_i$ in which player $P$ uses strategy $j$ when player $O$'s initial move takes place in $A_j$:
-\[
-  \sigma = \bigcprd_i \sigma_i
-  \]
-
-We can see that $\comp{\pr_j}{\sigma}=\sigma_j$ for each $j$: indeed, $\grel{\pr_j}$ is the graph of the inclusion $P_{A_j}\hookrightarrow P_{\prod_i A_i}$, while $\grel\sigma$ is the union of the relations $\grel{\sigma_i}$, so this equation holds in the relational presentation:
-\[
-  \comp{\grel{\pr_j}}{\grel{\sigma}}=\grel{\sigma_j}
-  \]
-Moreover, it is easy to see that $\grel\sigma$ is the unique relation between $P_B$ and $P_{\prod_i A_i}$ such that this equation holds for all $j$, and therefore $sigma$ is the unique strategy for $B\implies\prod_i A_i$ such that $\comp{\pr_j}{\sigma}=\sigma_j$ for each $j\in I$.
-Therefore, $\G(\alpha)$ has all small products.
-
-Given games $A,B$, we shall write $A\times B$ for the product of $A$ and $B$.
-
-\subsection{The exponential as a final coalgebra}
-
-Our definition of the exponential connective $\oc$ was different from the definitions of the other connectives in that it involved an explicit restriction on the order in which new games could be opened.
-We saw that this restriction was necessary in order to guarantee associativity of the comultiplication in our comonoid, but it means that it is hard to study the exponential $\oc A$ using the connectives $\tensor$ and $\implies$.
-
-Let $A,B$ be objects of some category $\G(\alpha)$ of transfinite games.  Following \cite{laird02}, we define the \emph{sequoid} $A\sequoid B$ by:
-
-\begin{itemize}
-  \item $M_{A\sequoid B} = M_{A\tensor B}$
-  \item $\lambda_{A\sequoid B}=\lambda_{A\tensor B}$
-  \item $P_{A\sequoid B} = \{s\in P_{A\tensor B}\suchthat\textrm{$s=\emptyplay$ or the first move of $s$ takes place in $A$}\}$
-  \item $\zeta_{A\sequoid B} = \zeta_{A\tensor B}\vert_{P_{A\sequoid B}}$
-\end{itemize}
-
-It is clear that $A\sequoid B$ is a well-formed game - namely, it is the weakening of the tensor product $A\tensor A$ such that player $O$ is forced to start play in the game $A$.
-We have a natural copycat strategy $\wk\from A\tensor B\to A\sequoid B$ and the morphism
-\[
-  \dec_{A,B}\from A\tensor B\to (A\sequoid B)\times(B\sequoid A)
-  \]
-induced by the morphisms
-\[
-  A\tensor B\xrightarrow{\wk}A\sequoid B\quad A\tensor B\xrightarrow{\braid}B\tensor A\xrightarrow{\wk}B\sequoid A
-  \]
-is an isomorphism.
-
-Other natural copycat isomorphisms may be verified by inspection:
-\begin{gather*}
-  \passoc_{A,B,C} \from (A\sequoid B) \sequoid C \toisom A\sequoid (B\tensor C) \\
-  \pcomm_{A,B,C} = \comp{\passoc_{A,B,C}\inv}{\comp{(\id_A\tensor\braid)}{\passoc_{A,B,C}}} \from (A\sequoid B)\sequoid C \toisom (A\sequoid C)\sequoid B\\
-  \lun_A \from I\sequoid A \toisom I\\
-  \run_A \from A\sequoid I \toisom A \\
-  \dist_{A,B,C}=\langle \pi_1\sequoid\id_C,\pi_2\sequoid\id_C\rangle\from (A\times B)\sequoid C \toisom (A\sequoid C)\times(B\sequoid C)
-\end{gather*}
-
-One important point is that the sequoid does not give rise to a functor $\G(\alpha)\times\G(\alpha)\to\G(\alpha)$ in the way that the tensor product does.
-To see why, let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $C\implies D$.
-We would like to construct a strategy $\sigma\sequoid\tau$ for
-\[
-  (A\sequoid C)\implies (B\sequoid D)
-  \]
-in which player $P$ plays according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $B$ and $D$, exactly as in the strategy $\sigma\tensor\tau$.
-The problem is that $\sigma\tensor\tau$ is not necessarily a valid strategy for $(A\sequoid C)\implies (B\sequoid D)$, even if $\sigma$ is a valid strategy for $A\implies B$ and $\tau$ is a valid strategy for $C\implies D$.
-
-Indeed, suppose that player $P$'s reply in $\sigma$ to a particular opening move in $B$ is also a move in $B$, and suppose further that player $P$'s reply in $\tau$ to a particular opening move in $D$ is a move in $C$ (for example, if $\tau$ is a copycat strategy).
-Now consider the following narrative for the game $(A\sequoid C)\implies (B\sequoid D)$:
-\begin{enumerate}
-  \item Player $O$ plays the opening move in $B$, as he must.
-  \item Player $P$ replies in $B$, according to $\sigma$.  
-  \item Player $O$ decides to switch and start the game $D$.
-  \item According to $\tau$, player $P$ should reply with a move in $C$.  But she cannot play in $C$, since no moves have been played in $A$ yet.
-\end{enumerate}
-
-In order to fix this situation, we place a restriction on the strategy $\sigma$.
-
-\begin{definition}
-  Let $A,B$ be objects of $\G(\alpha)$.
-A strategy $\sigma$ for $A\implies B$ is called \emph{strict} if player $P$'s reply to each opening $O$-move in $B$ is a move in $A$ - so if $bx\in\sigma$ then $x\in M_A$.
-
-  It is easy to see that the composition of strict strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ is a strict strategy for $A\implies C$ and that the identity strategy is strict.
-Therefore, we have a full-on-objects subcategory $\G_s(\alpha)$ of $\G(\alpha)$ of games and strict strategies.
-\end{definition}
-
-\begin{proposition}
-  Let $A,B,C,D$ be objects of $\G(\alpha)$, let $\sigma$ be a strict strategy for $A\implies B$ and let $\tau$ be a strict strategy for $C\implies D$.
-Then $\sigma\sequoid\tau=\sigma\tensor\tau\cap P_{(A\sequoid C)\implies (B\sequoid D)}$ is a strict strategy for $(A\sequoid C)\implies (B\sequoid D)$ and the following diagram commutes (so $\wk$ is a natural transformation between $\blank\tensor\blank$ and $\blank\sequoid\blank$):
-  \[
-    \begin{tikzcd}
-      A\tensor C \arrow[r, "\sigma\tensor\tau"] \arrow[d, "\wk"']
-        & B\tensor D \arrow[d, "\wk"] \\
-      A\sequoid C \arrow[r, "\sigma\sequoid\tau"']
-        & B\sequoid D
-    \end{tikzcd}
-    \]
-
-  \begin{proof}
-    We know that $\sigma\tensor\tau$ is a valid strategy for $(A\tensor C)\implies (B\tensor D)$, so we just need to check that no moves in $B$ take place before moves in $D$ and that no moves in $A$ take place before moves in $C$.
-Indeed, player $O$'s opening move must take place in $B$; then, since $\sigma$ is strict, player $P$'s reply will take place in $A$.
-So $\sigma\sequoid\tau$ is a valid strategy for $(A\sequoid C)\implies(B\sequoid D)$; moreover, it is itself a strict strategy.
-  \end{proof}
-\end{proposition}
-
-What this means is that $\blank\sequoid\blank$ gives us a functor, not from $\G(\alpha)\times\G(\alpha)$ to $\G(\alpha)$, but from $\G_s(\alpha)\times\G(\alpha)$ to $\G_s(\alpha)$.
-In fact, the isomorphism $\passoc\from (A\sequoid B)\sequoid C\cong A\sequoid(B\tensor C)$ tells us that $\blank\sequoid\blank$ is a \emph{right action} of the monoidal category $\G(\alpha)$ upon the category $\G_s(\alpha)$.
-
-The closed monoidal category $\G(\alpha)$, the subcategory $\G_s(\alpha)$, the morphisms $\passoc$ and $\run$, and the natural transformation $\wk$ in fact give rise to a structure known as a \emph{sequoidal category} (This definition was first introduced in \cite{laird02}, but with the direction of the sequoid operator reversed; see, for example, \cite{martinsthesis} for the definition where the orientation of the sequoid agrees with ours).
-
-Moreover, the isomorphism $\dec_{A,B,C}\from A\tensor B\cong (A\sequoid B)\times(B\sequoid A)$ means that our sequoidal category is \emph{decomposable} and the isomorphism $\dist_{A,B,C}\from (A\times B)\sequoid C\to (A\sequoid C)\times(B\sequoid C)$ tells us that it is \emph{distributive}.
-
-The last part of the definition of a sequoidal category that we will need is the coherence diagram:
-\[
-  \begin{tikzcd}
-    (A \tensor B) \tensor C \arrow[r, "\wk\tensor\id_C"] \arrow[d, "\assoc_{A,B,C}"']
-      & (A \sequoid B) \tensor C \arrow[r, "\wk"]
-        & (A \sequoid B) \sequoid C \\
-    A \tensor (B \tensor C) \arrow[r, "\wk"]
-      & A \sequoid (B \tensor C) \arrow[ur, "\passoc_{A,B,C}"']
-        &
-  \end{tikzcd}
-  \]
-Commutativity of this diagram in $\G(\alpha)$ may be verified by inspection.
-
-\cite{laird02} gives examples of what we can prove in general sequoidal categories, particularly in the cpo-enriched setting.
-They are used in \cite{martinsthesis} to study the logic modelled by games and history-sensitive strategies.
-The most useful property of the sequoid from the point of view of our study of the exponential is that it allows us to express our exponential as a final coalgebra.
-
-Let $\C$ be a category and let $\F\from \C\to\C$ be an endofunctor.  A \emph{coalgebra} for $\F$ is an object $A$ of $\C$ together with a morphism $\map{f}{A}{\F(A)}$.  Given two coalgebras
-\begin{gather*}
-  \map{f}{A}{\F(A)}\\
-  \map{g}{B}{\F(B)}
-\end{gather*}
-a \emph{coalgebra homomorphism} from $\map{f}{A}{\F(A)}$ to $\map{g}{B}{\F(A)}$ is a morphism $\cmap{h}{A}{B}$ that makes the following square commute:
-\[
-  \begin{tikzcd}
-    A \arrow[r, "f"] \arrow[d, "h"']
-      & \F(A) \arrow[d, "\F(h)"] \\
-    B \arrow[r, "g"']
-      & \F(B)
-  \end{tikzcd}
-  \]
-
-A \emph{final coalgebra} for $\F$ is a terminal object for the category of coalgebras and coalgebra homomorphisms.
-Namely, it is an object $Z$ of $\C$ together with a morphism $\map{\alpha}{Z}{\F(Z)}$ such that for each coalgebra $\map{f}{A}{\F(A)}$ there is a unique morphism
-\[
-  \fcoal{f}\from A \to Z
-  \]
-making the following diagram commute:
-\[
-  \begin{tikzcd}
-    A \arrow[r, "f"] \arrow[d, "\fcoal{f}"']
-      & \F(A) \arrow[d, "\F\left(\fcoal{f}\right)"] \\
-    Z \arrow[r, "\alpha"']
-      & \F(Z)
-  \end{tikzcd}
-  \]
-
-\begin{theorem}
-  Let $A$ be an object of a category $\G(\alpha)$ of games.  Then $\oc A$ may be given the structure of a final coalgebra for the functor
-  \[
-    A\sequoid\blank\from \G(\alpha)\to\G(\alpha)
-    \]
-  \begin{proof}
-    The coalgebra morphism $\alpha\from \oc A\to A\sequoid\oc A$ is given by
-    \[
-      \alpha \from \oc A \xrightarrow{\mu} \oc A \tensor \oc A \xrightarrow{\der\tensor\id_{\oc A}} A\tensor\oc A\xrightarrow{\wk} A\sequoid\oc A
-      \]
-    In other words, it is the copycat strategy where moves from the extra copy of $A$ on the right are copied into the first copy of $A$ on the left, moves from the first copy of $A$ in the exponential $\oc A$ on the right are copied into the second copy of $A$ on the left and so on.
-
-    Now let $B$ be a game and let $\sigma$ be a strategy for $B\implies A\sequoid B$.  We define a strategy $\fcoal{\sigma}$ for $B\implies \oc A$ as follows: we first define
-    \[
-      \|\sigma\| = \{\s\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}\suchthat\forall i\ge 0, \s\vert_{B_i,A_i,B_{i+1}}\in\sigma\}
-      \]
-    Then we set
-    \[
-      \fcoal\sigma = P_{B\implies\oc A} \cap \{\s\vert_{B_0,\oc A}\suchthat\s\in\|\sigma\|\}
-      \]
-    where we write $\s\vert_{B_0, \oc A}$ for $\s\vert_{B_0,A_0,A_1,\dots}$.
-
-    We shall omit the proof that $\fcoal\sigma$ is a strategy.  We claim that the final coalgebra diagram commutes:
-    \[
-      \begin{tikzcd}
-        B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
-          & A\sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
-        \oc A \arrow[r, "\alpha"']
-          & A\sequoid\oc A
-      \end{tikzcd}
-      \]
-    First, we have:
-    \[
-      \fcoal{\sigma} = P_{B\implies \oc A} \cap \left\{\s\vert_{B_0,A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_B\times\omega\sqcup M_A\times\omega)^{*<\alpha}$\\
-        $\forall i\ge0,\;\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-      \]
-    We claim that:
-    \begin{align*}
-      \id_A\sequoid\fcoal\sigma &= P_{(A\sequoid B)\implies(A\sequoid\oc A)}\;\cap\\
-      &\left\{\s\vert_{A_{-2},B_0,A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in (M_{A_{-2}}\cprd M_{A_{-1}} \cprd M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{A_{-2},A_{-1}}\in\id_A$\\
-        $\forall i\ge 0$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-    \end{align*}
-    Using the definition:
-    \[
-      \id\sequoid\fcoal{\sigma} = \{s\in P_{(A_{-2}\sequoid B_0)\implies(A_{-1}\sequoid\oc A)}\suchthat
-      s\vert_{A_{-2},A_{-1}}\in\id_A,\;s\vert_{B_0,\oc A}\in\fcoal\sigma\}
-      \]
-    it is clear that the RHS above is a subset of the LHS.
-To show the reverse inclusion, suppose we have some sequence $s\in\id\sequoid\fcoal\sigma$.
-Since $s\vert_{B_0,\oc A}\in\fcoal\sigma$, there is some sequence $\s\in\|\sigma\|$ with $\s\vert_{B_0,A_0,A_1,\dots}=s$.
-Then it is possible to interleave this sequence with the sequence $s\vert_{A_{-2},A_{-1}}$ exactly as we did towards the end of Section \ref{ImpliesCnSex}: we insert \emph{before} each $P$-move in $A_{-1}$ the corresponding move in $A_{-2}$ and insert \emph{after} each $O$-move in $A_{-1}$ the corresponding move in $A_{-2}$.
-This interleaved sequence -- call it $\t$ -- satisfies $\t\vert_{A_{-2},A_{-1}}\in\id_A$ and $\t\vert_{B_i,A_i,B_{i+1}}\in\sigma$ for all $i\ge0$, so it gives rise to an element of the RHS.
-Moreover, we have $t\vert_{A_{-2},B_0,A_{-1},A_0,A_1,\dots}=s$, and therefore $s$ is contained in the RHS.
-
-    We now have $\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma} =$
-    \[
-      P_{B\implies A\sequoid\oc A} \cap \left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_{B_{-1}}\cprd M_{A_{-2}}\cprd M_{A_{-1}}\cprd M_B\times\omega \cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{B_{-1},A_{-2},B_0}\in\sigma$\\
-        $\s\vert_{A_{-2},A_{-1}}\in\id_A$\\
-        $\forall i\ge 0$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-      \]
-    We claim that this is equal to the following strategy:
-    \[
-      S =
-      P_{B\implies A\sequoid\oc A}\cap\left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in (M_{B_{-1}}\cprd M_{A_{-1}} \cprd M_B\times\omega \cprd M_A\times\omega)^{*<\alpha}$\\
-        $\forall i\ge -1$, $\s\vert_{B_i,A_i,B_{i+1}}\in\sigma$
-      }}\right\}
-      \]
-    $S$ is a strategy since it is nothing more than a relabelling of the indices of $\fcoal\sigma$.
-To show that these two strategies are the same, it suffices to show that they contain the same $P$-positions.
-
-    Suppose we have some $P$-position $s\in\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma}$ and write $s=\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}$.
-By the argument above, we may assume that all moves from $A_{-2}$ are adjacent to a move from $A_{-1}$; since $s$ is a $P$-position, it cannot end with an $O$-move in $A_{-1}$, and therefore $\s\vert_{A_{-2},A_{-1}}$ must have even length.
-Therefore
-    \[
-      \s\vert_{A_{-2}}=\s\vert_{A_{-1}}
-      \]
-    by the definition of $\id_A$.
-
-    It follows (after hiding $M_{A_{-2}}$) that $\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma} \subset S$.
-Conversely, given an element $s=\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\in S$, we may interleave in a play in $A_{-2}$ that is identical to the play in $\s\vert_{A_{-1}}$ as above, showing that $s\in\comp{(\id_A\sequoid\fcoal\sigma)}{\sigma}$.
-
-    It remains only to observe that $S$ is precisely the strategy $\comp{\alpha}{\fcoal\sigma}$, and so the square above does indeed commute.
-
-    Now we show uniqueness.  Suppose that $\tau$ is some strategy for $B\implies\oc A$ such that the diagram commutes:
-    \[
-      \begin{tikzcd}
-        B \arrow[r, "\sigma"] \arrow[d, "\tau"']
-          & A\sequoid B \arrow[d, "\id_A\sequoid\tau"] \\
-        \oc A \arrow[r, "\alpha"']
-          & A\sequoid\oc A
-      \end{tikzcd}
-      \]
-    We claim that $\tau=\fcoal\sigma$.  The argument above tells us that
-    \[
-      \comp{(\id_A\sequoid\tau)}{\sigma} =
-      \left\{\s\vert_{B_{-1},A_{-1},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_{B_{-1}}\cprd M_{A_{-1}}\cprd M_{B_0}\cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{B_{-1},A_{-1},B_0}\in\sigma$\\
-        $\s\vert_{B_0,A_0,A_1,\dots}\in\tau$
-      }}\right\}
-      \]
-    Meanwhile, we have
-    \[
-      \comp{\alpha}{\tau} = \{t^\dagger\suchthat t\in\tau\}
-      \]
-    where $t^\dagger\in(M_{B_{-1}}\cprd M_{A_{-1}}\cprd M_A\times\omega)^{*<\alpha}$ is formed by reducing the indices on the copies of $A$ and $B$ in $t\in(M_{B_0}\cprd M_A\times\omega)^{*<\alpha}$.
-
-    We have $\comp{(\id\sequoid\tau)}{\sigma}=\comp\alpha\tau$, so, after promoting all indices by $1$, we may write:
-    \begin{equation}\label{taufixedpoint}
-      \tau = 
-      \left\{\s\vert_{B_{0},A_0,A_1,\dots}\;\middle|\;\mbox{\pbox{\textwidth}{
-        $\s\in(M_{B_0}\cprd M_{B_1}\cprd M_A\times\omega)^{*<\alpha}$\\
-        $\s\vert_{B_0,A_0,B_1}\in\sigma$\\
-        ($\s\vert_{B_1,A_1,A_2 \dots})^\dagger\in\tau$
-      }}\right\}
-      \tag{$*$}
-    \end{equation}
-    Let $t\in\tau$.
-Then we have just shown that we may interleave $t$ with a sequence $r\in M_{B_1}$ such that the interleaved sequence $\t\in(M_{B_0}\cprd M_{B_1}\cprd M_{A}\times\omega)^{*<\alpha}$ satisfies
-    \begin{gather*}
-      \t\vert_{B_0,\oc A}=t\quad\t\vert_{B_1}=r\\
-      \t\vert_{B_0,A_0,B_1}\in\sigma\\
-      (\t\vert_{B_1,A_1,A_2,\dots})^\dagger\in\tau
-    \end{gather*}
-    Let $t_1=(\t\vert_{B_1,A_1,A_2,\dots})^\dagger$.
-Applying the result repeatedly allows us to build up a sequence $t=t_0,t_1,t_2,\dots$ where $t_i\in\tau$ for each $i$, together with a sequence $\t=\t_0,\t_1,\t_2,\dots\in (M_{B_0}\cprd M_{B_1}\cprd M_A\times\omega)^{*<\alpha}$ such that for each $i$:
-    \begin{gather*}
-      \t_i\vert_{B_0,\oc A}=t_i\\
-      \t_i\vert_{B_0,A_0,B_1}\in\sigma
-    \end{gather*}
-    By construction, the $A$-components of the $\t_i$ agree (indeed, the $A_i$-component of $\t_j$ is the same as the $A_{i+j}$-component of $\t_0$), and the $B_1$-component of $\t_i$ is the same as the $B_0$-component of $t_{i+1}$.
-Therefore, the $\t_i$ interleave to give a sequence
-    \[
-      \T\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}
-      \]
-    such that $\T\vert_{B_0,\oc A}=t$ and for all $i\ge 0$, $\T\vert_{B_i,A_i,B_{i+1}}\in\sigma$.  It follows that $t\in\fcoal\sigma$ and so $\tau\subset\fcoal\sigma$.
-
-    Now suppose that $s\in\fcoal\sigma$.
-We show by transfinite induction on the length of $s$ that $s\in\tau$.
-Since $\tau$ satisfies the limiting condition, the limiting case of the induction is easy.
-So suppose instead that $s=s'a$ is a successor play, and suppose that the last move $a$ takes place in the game $A_n$.
-By induction, we assume that $s'\in\tau$.
-We now apply the construction above to give us a sequence
-    \[
-      s'=t_0,t_1,\dots,t_{n+1}
-      \]
-    of plays in $\tau$ whose $A$-components agree so that the $A_i$-component of $t_j$ is the $A_{i+j}$-component of $s'$.
-It follows that the $A$-components of $t_{n+1}$ also agree with the components of $A_{n+1},A_{n+2},\dots$ of $sa$, since the move $a$ takes place in $A_n$.
-
-    We have $t_{n+1}\in\tau$.
-We now claim that $t_{n}a$ satisfies the conditions on the right in \eqref{taufixedpoint}, so $t_n a\in\tau$ as well.
-Indeed, we have $s'a\in\fcoal\sigma$, so there exists some $\s a\in(M_B\times\omega\cprd M_A\times\omega)^{*<\alpha}$ with $\s\vert_{B_0,\oc A}=s$ and $\s a\vert_{B_i,A_i,B_{i+1}}\in\sigma$ for all $i$.
-
-    Consider the sequence
-    \[
-      \s a\vert_{B_n,B_{n+1},A_n,A_{n+1},A_{n+2},\dots}
-      \]
-    We have $\s a\vert_{B_n,A_n,A_{n+1}}\in\sigma$ (since $\s a\in\fcoal\sigma$) and $\s a\vert_{B_{n+1},A_{n+1},A_{n+2},\dots}=s \vert_{B_{n+1},A_{n+1},A_{n+2},\dots}\in\tau$ by \eqref{taufixedpoint}.
-Therefore, $\s a\vert_{B_n,B_{n+1},A_n,A_{n+1},A_{n+2},\dots}$ satisfies the conditions for the right hand side of \eqref{taufixedpoint} (after subtracting $n$ from each of the indices) and therefore
-    \[
-      t_n a=\s a\vert_{B_n,A_n,A_{n+1},\dots}\in\tau
-      \]
-    Moreover, this sequence is contained in $\fcoal\sigma$ (by checking the definition).
-
-    By repeatedly applying this argument, we eventually show that 
-    \[
-      sa=\s a\vert_{B_0,A_0,A_1,\dots}\in\tau
-      \]
-    This completes the proof.
-  \end{proof}
-\end{theorem}
-
-\begin{note}
-  This is not the same as the proof found in \cite{martinsthesis}, which implicitly uses the fact that in the finitary games setting we may identify $\oc A$ with the limit of the diagram
-  \[
-    I \leftarrow A \leftarrow A\sequoid A \leftarrow A\sequoid(A\sequoid A) \leftarrow \cdots
-    \]
-  As we shall see in the next section, we do not have this identification in the transfinite setting.
-However, we will give an alternative proof that $\oc A$ is the final coalgebra for $A\sequoid\blank$ in the next section that will be more along the lines of the proof in \cite{martinsthesis}.
-\end{note}
-
-\pagebreak
-
-\subsection{The sequoidal exponential gives a cofree commutative comonoid}
-\label{SeqExpIsCofCommCom}
-
-As an application of this result, we shall prove that $\oc A\xrightarrow{\mu}\oc A\tensor \oc A$ is the cofree commutative comonoid on $A$.  We start with a small but useful lemma:
-
-\begin{lemma}
-  \[
-    \oc A \tensor \oc A \cong \oc(A\times A)
-    \]
-  \begin{proof}
-    We check that the game trees are isomorphic.
-The basic idea is that in each $P$-position the player $O$ may either play in one of the games that has already been opened, or he has a choice of two new games to open -- in $\oc A\tensor \oc A$, he may open either the first unopened copy of $A$ on the left or the first unopened copy of $A$ on the right, while in $\oc(A\times A)$ he may open either of the copies of $A$ in the first unopened copy of $A\times A$.
-  \end{proof}
-\end{lemma}
-
-This means that $\oc A\tensor\oc A$ is the final coalgebra for the functor 
-\[
-  (A\times A)\sequoid\blank
-  \]
-Upon examining the induced morphism $\oc A\tensor \oc A \to (A\times A)\sequoid(\oc A\tensor \oc A)$, we observe that it is equal to the following composite
-\[
-  \oc A\tensor \oc A \xrightarrow{\xi} (A\sequoid(\oc A\tensor\oc A)) \times (A\sequoid(\oc A\tensor\oc A))\xrightarrow{\dist\inv}(A\times A)\sequoid(\oc A\tensor \oc A)
-  \]
-where the morphism $\xi$ is induced by the morphisms
-\[
-  \begin{tikzcd}
-    %
-      &
-        & (A\sequoid\oc A)\tensor \oc A \arrow[r, "\wk"]
-          & (A\sequoid\oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            & A\sequoid (\oc A\tensor \oc A) \\
-    \oc A \tensor \oc A \arrow[urr, "\alpha\tensor\id"] \arrow[dr, "\sym"]
-      &
-        &
-          &
-            & \\
-    %
-      & \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"]
-        & (A\sequoid\oc A)\tensor \oc A \arrow[r, "\wk"]
-          & (A\sequoid\oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            & A\sequoid (\oc A\tensor \oc A) \\
-  \end{tikzcd}
-  \]
-
-Now let $\map{\mu}{B}{B\tensor B}$ be a commutative comonoid in $\G(\alpha)$ and let $\sigma\from B\to A$ be a morphism.  We build up a chain as follows:
-\[
-  B \xrightarrow{\mu} B\tensor B \xrightarrow{\sigma\tensor\id_B} A \tensor B \xrightarrow{\wk} A \sequoid B \xrightarrow{\Delta} (A \sequoid B) \times (A \sequoid B) \rightarrow{\dist_{A,A,B}\inv} (A\times A)\sequoid B
-  \]
-where $\Delta=\langle\id,\id\rangle$ is the diagonal morphism into the product.  The composite $\comp{\comp{\wk}{\sigma\tensor\id_B}}{\mu}$ gives rise to a unique morphism
-\[
-  \sigma^\dagger=\fcoal{\comp{\comp{\wk}{\sigma\tensor\id_B}}{\mu}}\from B\to \oc A
-  \]
-making the following diagram commute:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\sigma^\dagger"']
-      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
-        & A\tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[d, "\id_A\sequoid\sigma^\dagger"] \\
-    \oc A \arrow[rrr, "\alpha"]
-      &
-        &
-          & A\sequoid\oc A
-  \end{tikzcd}
-  \]
-
-We claim that $\sigma^\dag$ gives us a homomorphism of comonoids; that is, that the following square commutes:
-\[
-  \begin{tikzcd}
-  B \arrow[r, "\mu"] \arrow[d, "\sigma^\dag"']
-    & B\tensor B \arrow[d, "\sigma^\dag\tensor\sigma^\dag"] \\
-  \oc A \arrow[r, "\mu"]
-    & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-We will show this by proving that the two paths round the square are both anamorphisms for the morphism $B\to (A\times A)\sequoid B$ given above.
-Since anamorphisms are unique by the definition of a final coalgebra, this will mean that the two branches are equal.
-
-We start with the branch $B\to B\tensor B \to \oc A\tensor \oc A$.  We claim that the following diagram commutes:
-\begin{longdiagram}
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\sigma^\dag"]
-      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
-        & A \tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[r, "\Delta"] \arrow[d, "\id_A\sequoid\sigma^\dagger"]
-            & (A\sequoid B) \times (A \sequoid B) \arrow[r, "{\dist_{A,A,B}\inv}"] \arrow[d, "{\langle\id_A\sequoid\sigma^\dagger,\id_A\sequoid\sigma^\dagger\rangle}"]
-              & (A \times A) \sequoid B \arrow[d, "\id_{A\times A}\sequoid\sigma^{\dagger}"] \\
-    \oc A \arrow[rrr, "\alpha"] \arrow[d, "\mu"]
-      &
-        &
-          & A\sequoid \oc A \arrow[r, "\Delta"]
-            & (A \sequoid \oc A)\times (A\sequoid \oc A) \arrow[r, "{\dist_{A,A,\oc A}\inv}"']
-              & (A\times A)\sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
-    \oc A \tensor \oc A \arrow[rrrrr]
-      &
-        &
-          &
-            &
-              & (A\times A)\sequoid(\oc A\tensor \oc A)
-  \end{tikzcd}
-\end{longdiagram}
-
-The rectangle at the top left is one we have drawn before.
-The square in the middle at the top commutes because $\Delta$ gives rise to a natural transformation between $\id_{\G(\alpha)}$ and $\blank\times\blank$.
-The square at the top right commutes because $\dist$ is a natural transformation.
-
-The rectangle at the bottom commutes because both branches are copycat strategies for $\oc A\implies (A\times A)\sequoid(\oc A\tensor\oc A)$, and there is a unique such strategy.
-
-It follows that $\comp\mu{\sigma^\dagger}$ is an anamorphism for the morphism along the top and the functor $(A\times A)\sequoid\blank$.
-
-Now we deal with the other branch.  We claim that we have the following commutative diagram:
-\begin{longdiagram}
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[dd, "\mu"'] \arrow[ddr, phantom, "\textbf{1}"]
-      & B\tensor B \arrow[r, "\sigma\tensor \id_B"] \arrow[d, "\id_B\tensor\mu"] \arrow[dr, phantom, "\textbf{2}"]
-        & A \tensor B \arrow[rrr, "\wk"] \arrow[d, "\id_A\tensor\mu"] \arrow[drrr, phantom, "\textbf{3}"]
-          &
-            &
-              & A\sequoid B \arrow[d, "\id_A\sequoid\mu"] \\
-    %
-      & B \tensor(B\tensor B) \arrow[r, "\sigma\tensor\id_{B\tensor B}"] \arrow[d, "{\assoc_{B,B,B}\inv}"]
-        & A \tensor (B \tensor B) \arrow[rrr, "\wk"] \arrow[drr, phantom, "\textbf{4}"]
-          &
-            &
-              & A \sequoid (B\tensor B) \arrow[dd, "\id_A\sequoid(\sigma^\dagger \tensor \sigma^\dagger)"] \arrow[dl, "{\passoc_{A,B,B}}"] \arrow[ddl, phantom, "\textbf{7}"] \\
-    B \tensor B \arrow[r, "\mu\tensor \id_B"] \arrow[d, "\sigma^\dagger \tensor \sigma^\dagger"'] \arrow[drrr, phantom, "\textbf{5}" yshift=-0.3em]
-      & (B \tensor B) \tensor B \arrow[r, "(\sigma\tensor\id_B)\tensor\id_B"' yshift=-0.3em]
-        & (A \tensor B) \tensor B \arrow[r, "\wk\tensor\id_B"]
-          & (A \sequoid B) \tensor B \arrow[r, "\wk"] \arrow[d, "(\id\sequoid\sigma^\dagger)\tensor\sigma^\dagger"'] \arrow[dr, phantom, "\textbf{6}"]
-            & (A\sequoid B)\sequoid B \arrow[d, "(\id\sequoid\sigma^\dagger)\sequoid\sigma^\dagger"]
-              & \\
-    \oc A \tensor \oc A \arrow[rrr, "\alpha\sequoid\id_{\oc A}"']
-      &
-        &
-          & (A \sequoid \oc A)\tensor \oc A \arrow[r, "\wk"]
-            & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-              & A \sequoid (\oc A \tensor \oc A)
-  \end{tikzcd}
-\end{longdiagram}
-
-We check that each cell commutes in turn.
-\begin{enumerate}[{\bf 1}]
-  \item is the diagram showing that the comultiplication for $B$ is associative.
-  \item commutes since $\blank\tensor\blank$ is a functor.
-  \item commutes since $\wk$ is a natural transformation.
-  \item is the coherence diagram for sequoidal categories that we gave earlier.
-  \item is obtained from an earlier diagram by taking the tensor product with $B$ on the top, taking the tensor product with $\oc A$ on the bottom, and passing between the two with the morphism $\sigma^\dag$.
-  \item commutes because $\wk$ is a natural transformation.
-  \item commutes because $\passoc$ is a natural transformation.  
-\end{enumerate}
-
-\pagebreak
-
-Furthermore, note that the morphism along the bottom is one of the two morphisms $\oc A\tensor\oc A \to A\sequoid(\oc A \tensor \oc A)$ that we gave before.
-To get the other one, note that since the comultiplication in $B$ is commutative, we have a commutative diagram:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[ddl, "\mu"'] \arrow[dd, "\mu"] \\
-    %
-      & \\
-    B\tensor B \arrow[r, "\sym"] \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"']
-      & B\tensor B \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"] \\
-    \oc A \tensor \oc A \arrow[r, "\sym"]
-      & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-which we may glue on to the left hand side of the diagram above, giving a commutative diagram with the second morphism $\oc A\tensor \oc A\to A\sequoid(\oc A\tensor \oc A)$ along the bottom.
-
-These two diagrams between them induce a commutative diagram
-\begin{longdiagram}
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\mu"']
-      & B\tensor B \arrow[r, "\sigma\tensor\id_B"]
-        & A \tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[r, "\Delta"]
-            & (A \sequoid B) \times (A \sequoid B) \arrow[r, "{\dist_{A,A,B}\inv}" yshift=0.6em] \arrow[d, "{\langle \id_A\sequoid\mu, \id_A\sequoid\mu\rangle}"']
-              & (A\times A)\sequoid B \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
-    B\tensor B \arrow[d, "\sigma^\dagger\tensor\sigma^\dagger"']
-      &
-        &
-          &
-            & (A \sequoid (B \tensor B)) \times (A \sequoid (B\tensor B)) \arrow[d, "{\langle \id_A\sequoid(\sigma^\dagger\tensor\sigma^\dagger), \id_A\sequoid(\sigma^\dagger\tensor\sigma^\dagger)\rangle}"'] \arrow[r, "{\dist_{A,A,B\tensor B}\inv}"]
-              & (A \times A) \sequoid (B\tensor B) \arrow[d, "\id_{A\times A}\sequoid\mu"] \\
-    \oc A \times \oc A \arrow[rrrr, "\xi"]
-      &
-        &
-          &
-            & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "{\dist_{A,A,\oc A\tensor\oc A}\inv}" yshift=0.3em]
-              & (A\times A) \sequoid(\oc A \tensor \oc A)
-  \end{tikzcd}
-\end{longdiagram}
-
-that proves that $\comp{\sigma^\dagger\tensor\sigma^\dagger}{\mu}$ is an anamorphism for the morphism along the top as well.  Therefore, $\sigma^\dagger$ does give us a homomorphism of comonoids.
-
-We claim that $\sigma^\dagger$ makes the following diagram commute:
-\[
-  \begin{tikzcd}
-    B \arrow[d, "\sigma^\dagger"'] \arrow[dr, "\sigma"]
-      & \\
-    \oc A \arrow[r, "\der"']
-      & A
-  \end{tikzcd}
-  \]
-Indeed, we have a commutative diagram
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\comp{\wk}{\comp{(\sigma\tensor\id_B)}{\mu}}" yshift=0.3em] \arrow[d, "\sigma^\dagger"']
-      & A \sequoid B \arrow[dr, "\id_A\sequoid 1"] \arrow[d, "\id_A\sequoid\sigma^\dagger"']
-        & 
-          & \\
-    \oc A \arrow[r, "\alpha"']
-      & A \sequoid \oc A \arrow[r, "\id_A\sequoid 1"']
-        & A \sequoid I \arrow[r, "\run_A"]
-          & A
-  \end{tikzcd}
-  \]
-and we observe that the morphism along the bottom is precisely $\der$, while the morphism along the top is precisely $\sigma$.
-
-Now we show uniqueness.  Suppose that $\tau\from B\to\oc A$ is a morphism making the following diagram commute:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[d, "\tau"] \arrow[r, "\mu"] \arrow[dl, "\sigma"']
-        & B \tensor B \arrow[d, "\tau\tensor\tau"] \\
-    A
-      & \oc A \arrow[l, "\der"] \arrow[r, "\mu"]
-        & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-Then we get the following commutative diagram:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\mu"] \arrow[d, "\tau"]
-      & B \tensor B \arrow[r, "\sigma\tensor\id_A"] \arrow[d, "\tau\tensor\tau"]
-        & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id_A\tensor\tau"]
-          & A \sequoid B \arrow[d, "\id_A\sequoid\tau"] \\
-    \oc A \arrow[r, "\mu"]
-      & \oc A \tensor \oc A \arrow[r, "\der\tensor\id_A"]
-        & A \tensor \oc A \arrow[r, "\wk"]
-          & A \sequoid \oc A
-  \end{tikzcd}
-  \]
-where commutativity of the middle square is derived from the commutative triangle on the left of the diagram immediately above.
-Now observe that the morphism $A\to A\sequoid\oc A$ along the bottom is precisely the morphism $\alpha$.
-Therefore, $\tau$ is an anamorphism for the morphism
-\[
-  B \xrightarrow{\mu} B\tensor B \xrightarrow{\sigma\tensor\id_A} A\tensor B \xrightarrow{\wk} A \sequoid B
-  \]
-and so $\tau=\sigma$.
-
-We have shown that $\oc A \xrightarrow{\mu}\oc A \tensor \oc A$ is indeed the cofree commutative comonoid on $A$.
-
-\section{The final sequence}
-
-Familiarity with the final sequence is assumed; see \cite{finalseq} for a less terse presentation of the following material.
-
-Let $\C$ be a category and let $\F\from \C\to \C$ be an endofunctor.
-Suppose that $\C$ has a terminal object $1$.
-We shall further assume that we are able to construct all the limits we want in $\C$.
-Let $\Ord$ denote the ordered class of ordinals, considered as a category.
-We shall inductively construct a functor $\FS_\F\from\oppcat\Ord\to\C$ (known as the \emph{final sequence of $\F$}) as follows:
-
-\begin{itemize}
-  \item $\FS_\F(0)=1$
-  \item $\FS_\F(\beta+1) =\F\left(\FS_F(\beta)\right)$
-  \item On the level of morphisms, $\FS_\F(0\le\beta)$ is the unique morphism $\FS_\F(\beta)\to 1$
-  \item $\FS_\F(\beta+1\le\beta+2)=\F(\FS_\F(\beta\le\beta+1))$
-  \item If $\mu$ is a limit ordinal, then $\FS_\F(\mu)$ is the limit of the diagram
-    \[
-      \mu\hookrightarrow\Ord\xrightarrow{\FS_\F}\C
-      \]
-    and $\FS_\F(\beta\le\mu)$ is the arrow in the limiting cone
-  \item Applying the functor $\F$ to the cone $\FS_\F(\mu)$ gives rise to a new cone over the above diagram, inducing a unique arrow $\FS_\F(\mu+1)\to\FS_\F(\mu)$.
-We set $\FS_\F(\mu\le\mu+1)$ to be equal to this arrow.
-\end{itemize}
-
-A standard fact about the final sequence (see \cite{finalseq}) is that if $\delta$ is an ordinal and the morphism
-\[
-  \FS_\F(\delta\le\delta+1)\from \F(\FS_\F(\delta))\to \FS_\F(\delta)
-  \]
-is an isomorphism, then the inverse of this morphism exhibits $\FS_\F(\delta)$ as the final coalgebra for the endofunctor $\F$.
-In this case, we say that the final sequence $\FS_\F$ has \emph{stabilized by $\delta$}.
-
-Our goal is to characterize the final sequence for functors of the form $A\sequoid\blank$ in categories $\G(\alpha)$ of games, in the hope that this will allow us to study the exponential $\oc A$ in more depth.
-
-\subsection{The rank of a transfinite sequence of natural numbers}
-
-We fix a (large) ordinal $\alpha$.
-The goal of this section is to assign an ordinal \emph{rank} to a sequence $\beta\to\omega$ of natural numbers (for $\beta<\alpha$).
-This rank will turn out to be the key to characterizing the final sequence of the $A\sequoid\blank$ functor.
-This rank will not depend on $\alpha$, and we could do without mentioning $\alpha$ at all (although mentioning $\alpha$ allows us to avoid size issues).
-
-To define our rank, we will give a chain of subsets 
-\[
-  R_0\subset R_1\subset R_2\subset\dots \subset R_\delta \subset\dots \subset \omega^{*\alpha}
-  \]
-where $\delta$ will run over all the ordinals.
-We think of $R_\delta$ as being the set of all sequences \emph{with rank at most $\delta$}; accordingly, we shall define the \emph{rank} of a sequence $s$ to be the smallest ordinal $\delta$ such that $s\in R_\delta$.
-
-\begin{definition}
-  Let $(s\from\beta\to\omega)\in\omega^{*<\alpha}$.  We define the \emph{derivative} of $s$ to be the sequence $\Delta s$ given by:
-  \[
-    s\inv\left(\omega\setminus\{0\}\right) \xrightarrow{s} \omega\setminus\{0\} \xrightarrow{n\mapsto n-1} \omega
-    \]
-  In other words, we remove all occurrences of $0$ from the sequence $s$ and then subtract $1$ from each term.  
-\end{definition}
-
-We shall now define the sets $R_\delta$:
-\begin{definition}
-  \begin{itemize}
-    \item $R_0=\{\emptyplay\}$
-    \item $R_{\delta+1}=\left\{s\in\omega^{*<\alpha}\suchthat \Delta s\in R_\delta\right\}$
-    \item If $\mu$ is a limit ordinal then $R_\mu$ is the limit closure of the union of the $R_\delta$ for $\delta<\mu$.  In other words, a sequence $s$ is contained in $R_\mu$ if \textbf{either}
-      \begin{itemize}
-        \item $\length(s)$ is a successor ordinal and $s\in R_\delta$ for some $\delta<\mu$ \textbf{or}
-        \item $\length(s)$ is a limit ordinal and for all proper prefixes $t\pprefix s$, $t\in R_\delta$ for some $\delta<\mu$
-      \end{itemize}
-  \end{itemize}
-
-  If $s\in\omega^{*<\alpha}$, we define $\rank(s) = \min\{\delta\suchthat s\in R_\delta\}$.
-\end{definition}
-
-One consequence of the above definition is that if $\mu$ is a limit ordinal then all the sequences of rank $\mu$ have limiting length.
-
-We need to prove some results so we can be sure that the rank of a sequence is well defined.
-
-\begin{proposition}
-  \label{RankProposition}
-  \begin{enumerate}[i)]
-    \item If $s\in R_\delta$ and $t$ is any subsequence of $s$ (not necessarily an initial prefix), then $t\in R_\delta$
-    \item If $s\in R_\delta$, then $\Delta s\in R_\delta$.
-    \item If $\gamma\le\delta$, then $R_\gamma\subset R_\delta$
-    \item If $s\in\omega^{*<\alpha}$, then $s\in R_\delta$ for some $\delta$.
-  \end{enumerate}
-
-  \begin{proof}
-    \begin{enumerate}[(i): ]
-      \item We prove this by induction on $\delta$.
-Suppose $s\in R_{\delta+1}$ and $t$ is a subsequence of $s$.
-Then $\Delta s\in R_\delta$.
-Now $\Delta t$ is a subsequence of $\Delta s$, so $\Delta t\in R_\delta$ by the induction hypothesis and therefore $\Delta t\in R_{\delta +1}$.
-
-        Let $\mu$ be a limit ordinal and suppose that $s\in R_\mu$.
-If $s$ has successor length, then $s\in R_\delta$ for some $\delta<\mu$.
-Then $t\in R_\delta$ by the induction hypothesis.
-If $t$ has successor length, this automatically means that $t\in R_\mu$, while if $t$ has limiting length, then every subsequence of $t$ is contained in $R_\delta$ by induction, so $t\in R_\mu$.
-
-        Suppose instead that $s$ has limiting length.
-Then for all proper prefixes $u\pprefix s$, we have $u\in R_\delta$ for some $\delta<\mu$.
-If $t$ has successor length, then $t$ cannot be cofinal in $s$, so it is a subsequence of some proper prefix $u$ of $s$.
-Therefore, $t\in R_\delta$ by the induction hypothesis, and so $t\in R_\mu$ as before.
-
-        If instead $t$ has limiting length, then every proper prefix $v\pprefix t$ is a subsequence of some proper prefix $u\pprefix s$.
-Therefore, by induction, for every proper prefix $v\pprefix t$, we have $v\in R_\delta$ for some $\delta<\mu$ and therefore $t\in\mu$.
-
-      \item Induction on $\delta$.
-If $s\in R_{\delta+1}$ then $\Delta s\in R_\delta$; by the induction hypothesis, this means that $\Delta\Delta s\in R_\delta$ and therefore that $\Delta s\in R_{\delta+1}$.
-
-        Now let $\mu$ be a limit ordinal.
-Suppose $s\in R_\mu$.
-If $s$ has successor length, it means that $s\in R_\delta$ for some $\delta<\mu$, so $\Delta s\in R_\delta$ by induction.
-By (i), all the prefixes of $\Delta s$ are in $R_\delta$ as well, so $\Delta s\in R_\mu$.
-
-        Suppose instead that $s$ has limiting length.
-Then for all proper prefixes $t\pprefix s$, we have $t\in R_\delta$ for some $\delta<\mu$.
-If $\Delta s$ has successor length, then we may choose some proper prefix $t\pprefix s$ such that $\Delta s = \Delta t$ and therefore $\Delta s\in R_\delta$, so it is in $R_\mu$.
-If instead $\Delta s$ has limiting length, then for all proper prefixes $v\pprefix\Delta s$, we may choose some $u\pprefix s$ with $v=\Delta u$.
-Then we have $u\in R_\delta$ for some $\delta<\mu$, so $v\in R_\delta$ by the induction hypothesis.
-Therefore, $t\in R_\mu$.
-
-      \item It is clear that $R_\delta\subset R_\mu$ if $\delta<\mu$ and $\mu$ is a limit ordinal.
-Therefore, by induction it will suffice to show that $R_\delta\subset R_{\delta+1}$ for all $\delta$.
-
-        Suppose $s\in R_\delta$.  Then $\Delta s\in R_\delta$ by (ii) and therefore $s\in R_{\delta+1}$.
-
-      \item We show this by induction on the length $\beta$ of $s$.
-If $\beta=0$ then $s\in R_0$.
-Suppose that $s=s'n$.
-If we apply $\Delta$ $n$ times to $s$ then we end up with the sequence $\Delta^ns .0$.
-Applying $\Delta$ never lengthens the sequence, by Lemma \ref{TechnicalOrdinalLemma}.
-Now if we apply $\Delta$ one more time, we end up with a strictly shorter sequence, so by induction it is contained in some $R_\delta$.
-Then $s$ is contained in $R_{\delta+n+1}$.
-
-        Now suppose that $s$ has limiting length.
-Then, by induction, for all proper prefixes $t\pprefix s$ there exists $\delta_t$ such that $t\in R_{\delta_t}$.
-If we let $\mu$ be some limit ordinal that is greater than all the $\delta_t$, then $s\in R_\mu$.
-\qedhere
-    \end{enumerate}
-  \end{proof}
-\end{proposition}
-
-\begin{example}
-  Any sequence with only finitely many distinct terms has finite rank: indeed, suppose $s\from\beta\to n$ is such a sequence.
-Then, after applying the derivative $n$ times, we end up with the empty sequence.
-
-  The `identity' sequence $\omega\to\omega$ has rank $\omega$: indeed, every proper prefix has finite rank, but applying the derivative operator has no effect.
-
-  More generally, the division algorithm for ordinal arithmetic tells us that if $\gamma$ is an ordinal, then there is a unique ordinal $\gamma'$ and a unique natural number $n$ such that $\gamma=\omega\gamma' + n$.
-If $\beta$ is an ordinal, we may define a sequence $c_\beta\from \beta\to\omega$ by setting:
-  \[
-    c_\beta(\omega\gamma'+n) = n
-    \]
-  We show by induction on $\beta$ that the sequence $c_\beta$ has rank $\beta$.  First, we claim that
-  \[
-    c_\beta = \Delta c_{\beta+1}
-    \]
-  The first thing to show is that the order type of $c_{\beta+1}\inv(\omega\setminus\{0\})$ is $\beta$.
-Indeed, $c_{\beta+1}\inv(\omega\setminus\{0\})$ is precisely the set of successor ordinals that are less than $\beta+1$.
-We therefore have an order preserving bijection
-  \begin{IEEEeqnarray*}{rCl}
-    \beta & \to & c_{\beta+1}\inv(\omega\setminus\{0\}) \\
-    \gamma & \mapsto & \gamma+1
-  \end{IEEEeqnarray*}
-
-  This map sends $\omega\gamma'+n$ to $\omega\gamma'+(n+1)$.  The map $\Delta c_{\beta+1}$ is therefore given by:
-  \begin{IEEEeqnarray*}{CCCCCCC}
-    \beta & \xrightarrow{\sim} & c_{\beta+1}\inv(\omega\setminus\{0\}) & \rightarrow & \omega \setminus \{0\} & \rightarrow & \omega \\
-    \omega\gamma' + n & \mapsto & \omega\gamma' + (n+1) & \mapsto & n+1 & \mapsto & n
-  \end{IEEEeqnarray*}
-  In other words, it is the same as $c_\beta$.  This deals with the successor step of the induction.
-
-  Now let $\mu$ be a limit ordinal.
-A proper prefix of $c_\mu$ is a sequence of the form $c_\delta$ for $\delta<\mu$.
-By the induction hypothesis, $c_\delta\in R_\delta$ for all $\delta<\mu$ and therefore $c_\mu\in R_\mu$.
-
-  Now suppose for a contradiction that $c_\mu\in R_\delta$ for some $\delta<\mu$.
-Then $c_{\delta+1}\prefix c_\mu$ so, by Proposition \ref{RankProposition}(i), $c_{\delta+1}\in R_\delta$, which contradicts our induction hypothesis.
-
-  Therefore, $\rank(c_\mu)=\mu$.  
-\end{example}
-
-We call $c_\delta$ the \emph{canonical sequence of length $\delta$}.
-We want to use it to obtain a neater characterization of the sets $R_\delta$.
-What we would like to say is that $\rank(s)\ge\delta$ if and only if $c_\delta$ is a subsequence of $s$.
-However, this is not quite true.
-For example, the sequence
-\[
-  23456\dots
-  \]
-over $\omega$ has rank $\omega$, but does not contain the sequence $c_\omega=01234\dots$ as a subsequence.
-We will have to modify the condition a little bit; the cost will be that our characterization only works for limit ordinals, but this is not a big problem.
-
-\begin{definition}
-  Let $s\from\beta\to\omega$ be a sequence.  We say that $s$ is \emph{weakly increasing} if $s(\delta)<s(\delta+1)$ for all $\delta<\beta$.
-\end{definition}
-
-\begin{example}
-  $c_\beta$ is weakly increasing for any $\beta$.  If we take, for example, the sequence $c_{\omega+\omega}$:
-  \[
-    01234\dots\;01234\dots
-    \]
-  then we see where the `weakly' comes from: we have $c_{\omega+\omega}(2)>c_{\omega+\omega}(\omega)$, even though $2<\omega$.
-\emph{Weakly increasing} means `increasing on every $\omega$-segment, but unconstrained at limits'.
-
-  There are plenty of other weakly increasing sequences.  For example:
-  \begin{gather*}
-    2468\dots \\
-    12358\dots\;2357\dots \\
-    01234\dots\;12345\dots\;23456\dots\;34567\dots\;45678\dots\;\dots\dots
-  \end{gather*}
-\end{example}
-
-\pagebreak
-
-\begin{lemma}
-  \label{WeaklyIncreasingLemma}
-  \begin{enumerate}[i)]
-    \item Let $s\in\omega^{*<\alpha}$ be weakly increasing.  Then $\Delta s$ is weakly increasing.
-    \item Suppose $\mu$ is a limit ordinal and that $s\in \omega^{*<\alpha}$ is such that $\rank(s)=\mu$.  Then $\rank(\Delta s)=\mu$.
-    \item Let $\mu$ be a limit ordinal and let $s\from\mu\to\omega$ be a weakly increasing sequence of length $\mu$.  Then $\rank(s)=\mu$.  
-  \end{enumerate}
-
-  \begin{proof}
-    \begin{enumerate}[(i): ]
-      \item Let $m,n$ be adjacent terms in $\Delta s$.
-That means that $(m+1).p$ occurs somewhere in the sequence $s$, so $p>m+1$, since $s$ is weakly increasing.
-In particular, $p\ne 0$, so it is not removed from the sequence.
-It follows that $n=p-1$ and therefore that $m<n$.
-
-      \item We have $s\in R_\mu$, so $\Delta s\in R_\mu$; i.e., $\rank(\Delta s)\le\mu$.  Suppose that $\Delta s\in R_\delta$ for $\delta<\mu$.  Then $s\in R_{\delta+1}$, which is a contradiction.
-
-      \item We prove the following statement by induction on $\beta$: if $s\from\beta\to\omega$ is a weakly increasing sequence of length $\beta$, then
-        \begin{itemize}
-          \item If $\beta=\omega\beta'+m$ is a successor ordinal, and $s=s'n_0\dots n_{m-1}$, then $\rank(s) = \omega\beta'+n_{m-1}+1$
-          \item If $\beta=\omega\beta'$ is a limit ordinal then $\rank(s)=\beta$
-        \end{itemize}
-        Suppose that $s$ has length $\omega\beta'+m$ and write $s$ as $s'n_0\dots n_{m-1}$, where $s'$ is a limiting play.
-Write $n=n_{m-1}$ -- so $n_i<n$ for $i<m-1$.
-By the induction hypothesis, $s'$ has rank $\omega\beta'$.
-
-        If we apply the derivative $n$ times to $s$ then we end up with the sequence $\Delta^n s'.0$.
-By part (ii), $\Delta^n s'$ has rank $\omega\beta'$, and so $\Delta^n s'.0$ has rank at least $\omega\beta'$.
-Moreover, since it is a successor play, it cannot have limiting rank, and therefore its rank is at least $\omega\beta+1'$.
-If we take the derivative one more time, then we end up with the sequence $\Delta^{n+1}s'$, which has rank $\omega\beta'$, and it follows that $\Delta^n s'.0$ has rank $\omega\beta'+1$.
-Therefore, $s$ has rank $\omega\beta'+n+1$.
-
-        Now suppose that $\mu$ is a limit ordinal and that $s$ has length $\mu$.
-If we take some proper prefix $t\pprefix s$ of length $\delta<\mu$, then $t$ is weakly increasing, so by the induction hypothesis it has rank at most $\delta+m$ for some $m$.
-$\delta+m<\mu$ and $t$ was arbitrary, so it follows that $s\in R_\mu$; i.e., that $\rank(s)\le\mu$.
-
-        We claim that $\rank(s)=\mu$.
-Indeed, suppose that $s\in R_\delta$ for some $\delta<\mu$.
-Let $u$ be the prefix of $s$ of length $\delta+1$.
-By the induction hypothesis, $\rank(u)\ge\delta+1>\rank(s)$, which is a contradiction, since $u\prefix s$.
-\qedhere
-    \end{enumerate}
-  \end{proof}
-\end{lemma}
-
-We can now give our classification result:
-
-\begin{theorem}
-  Let $s\in\omega^{*<\alpha}$ and let $\mu<\alpha$ be a limit ordinal.  Then $\rank(s)\ge\mu$ if and only if $s$ has a weakly increasing subsequence of length $\mu$.
-
-  For $n\ge 1$, $\rank(s)\ge\mu+n$ if and only if $s$ has a subsequence of the form $tm$, where $t$ is weakly increasing of length $\mu$ and $m\ge n-1$ is a single term.
-
-  \begin{proof}
-    \emph{If: } Suppose $t$ is a weakly increasing subsequence of length $\mu$.
-By Lemma \ref{WeaklyIncreasingLemma}, $t$ has rank $\mu$, so by Proposition \ref{RankProposition}, $s$ has rank at least $\mu$.
-
-    Write $s=s'u$, where $t$ is a subsequence of $s'$ and $u$ contains some term $m\ge n-1$.
-Then $s'$ has rank at least $\mu$.
-Then $\Delta^{n-1} s'$ has rank at least $\mu$ and $\Delta^{n-1}u\ne\emptyplay$, since $u$ contains the term $m$.
-Let $x$ be the first term of $\Delta^{n-1}u$.
-Then $\Delta^{n-1}s'.x$ is a subsequence of $\Delta^{n-1}s$, and it must have rank at least $\mu+1$ (since it is a successor play and contains $\Delta^{n-1}s'$ as a subsequence.
-Therefore, $\Delta^{n-1}s$ has rank at least $\mu+1$ and so $s$ has rank at least $\mu+1+(n-1)=\mu+n$.
-
-    \emph{Only if: } We prove by induction on $\delta$ that if $s\in\omega^{*<\alpha}$ has rank $\delta$ then $s$ satisfies the appropriate condition above.
-First, let $\mu$ be a limit ordinal and suppose that $s$ has rank $\mu+1$.
-We want to show that $s$ has a weakly increasing subsequence of length $\mu$ that is not cofinal in $s$.
-
-    Since $s$ has rank $\mu+1$, $\Delta s$ has rank $\mu$, so contains a weakly increasing subsequence of length $\mu$, by the induction hypothesis.
-This sequence lifts to a weakly increasing subsequence $u$ of $s$.
-If $s$ has successor length, then $u$ is not cofinal in $s$, so we win.
-
-    Otherwise, suppose that $s$ has limiting length.
-Then there must be some proper prefix $t\pprefix s$ of rank $\mu$; otherwise, $s\in R_\mu$, which is a contradiction.
-Then by the induction hypothesis we can find a weakly increasing subsequence of $t$ of length $\mu$, and this subsequence is not cofinal in $s$.
-
-    Now let $n\ge1\in\omega$ and suppose that $s$ has rank $\mu+n$.
-If we apply the derivative $n-1$ times to $s$ then we end up with a sequence of rank $\mu+1$.
-By the previous part, this sequence must have a subsequence of the form $u.m$, where $u$ is weakly increasing of length $\mu$ and $m$ is a single term.
-This sequence lifts to a subsequence $\hat u.(m+n-1)$ of $s$, where $\hat u$ is still weakly increasing.
-
-    Lastly, suppose that $s$ has rank $\mu$, for $\mu$ a limit ordinal.  It follows that $s$ has limiting length.
-
-    For each limit ordinal $\lambda<\mu$, let $t_\lambda$ be the shortest prefix of $s$ of rank at least $\lambda$.
-Since $s$ has rank $\mu$, $t_\lambda$ exists for each $\lambda$.
-By the induction hypothesis, each $t_\lambda$ has some weakly increasing subsequence of length $\lambda$.
-We will prove something stronger: we will inductively construct for each $\lambda$ a weakly increasing subsequence $u_\lambda$ of $t_\lambda$ such that $u_\lambda$ has length $\lambda$ and such that if $\lambda'\le\lambda$ then $u_{\lambda'}\prefix u_\lambda$.
-
-    Suppose we have constructed $u_\lambda$.
-Note that the rank of $t_\lambda$ must be less than $\lambda+\omega$; otherwise, $t_\lambda$ would have to have some prefix of length $\lambda+m$ for some $m$, contradicting minimality of $t_\lambda$.
-Therefore, $t_\lambda$ is a proper prefix of $t_{\lambda+\omega}$, so we write $t_{\lambda+\omega}=t_\lambda.v$ for some sequence $v$.
-
-    We claim that for all $N\in\omega$ there is some $n\ge N$ occurring in the sequence $v$.
-Indeed, if $N$ is such that there is no $n\ge N$ occurring in $v$, then we may take the derivative of $u_{\lambda+\omega}$ finitely many times and end up with a sequence of rank $\lambda$, which is a contradiction.
-We construct $u_{\lambda+\omega}$ as follows: let $n_0$ be the least value occurring in the sequence $v$ and let $a_0$ be the earliest occurrence of $n_0$ in the sequence $v$.
-Now let $N$ be the largest value that occurs (not necessarily strictly) earlier than $a_0$ in the sequence $v$.
-We know that there is some $n\ge N$ occurring in $v$; let $n_1$ be the least such $n$.
-Certainly, $n_1$ may only occur later in the sequence $v$ than $a_0$, so let $a_1$ be the first occurrence of $n_1$ in the sequence $v$.
-Continuing in this way, we build up an increasing subsequence $a_0 a_1 a_2 \dots$ of $v$.
-We set
-    \[
-      u_{\lambda+\omega} = u_\lambda a_0 a_1 a_2 \dots
-      \]
-    Then certainly $u_\lambda$ is a prefix of $u_{\lambda+\omega}$.
-
-    Now suppose that $\mu$ is a multiple of $\omega^2$ and we have constructed the sequences $u_\lambda$ for all limit ordinals $\lambda<\mu$.
-Then the sequences $u_\lambda$ glue to give a sequence $u_\mu$.
-We need to check that $u_\mu$ is a subsequence of $t_\mu$.
-Indeed, if $u_\mu$ is not a subsequence of $t_\mu$ then there is some earliest term $b$ in the sequence $u_\mu$ such that $b$ is not a term of $t_\mu$.
-But then there is some $\lambda'<\mu$ such that $u_{\lambda'}$ is not a subsequence of $t_\mu$, which is a contradiction.
-
-    This completes the induction.
-
-    To complete the argument, suppose that $\mu$ is a limit ordinal and that $\rank(s)\ge\mu$.
-Write $\gamma=\rank(s)$.
-We may write $\gamma=\lambda+m$ for some $m$, where $\lambda\ge\mu$ is a limit ordinal.
-Then $s$ has a weakly increasing subsequence of length $\lambda$, and we may take a prefix of this subsequence to obtain a weakly increasing subsequence of $s$ of length $\mu$.
-
-    Now suppose that $\rank(s)\ge\mu+n$.
-We may write $\rank(s) = \lambda+m$, where $\lambda$ is a limit ordinal and either $\lambda>\mu$ or $\lambda=\mu$ and $m\ge n$.
-In the first case, $s$ has a weakly increasing sequence of length $\lambda$; we may then take a prefix of length $\mu+\omega$ of this sequence and note that this sequence must have a subsequence of the form $up$, for some $p\ge (n-1)$.
-
-    In the second case, $s$ has a subsequence of the form $uq$, where $u$ is weakly increasing of length $\mu$ and $q\ge m-1\ge n-1$.  
-  \end{proof}
-\end{theorem}
-
-A consequence of this classification is that if $s\in\omega^{*<\alpha}$, then $\rank(s)<\length(s)+\omega$.
-Furthermore, if $\mu$ is a limit ordinal and $\length(s)<\mu$, then $\rank(s)<\mu$.
-We will see that this is the reason why the final sequence for $A\sequoid\blank$ converges so quickly for $\omega$- and $(\omega+1)$-games: there are no sequences of finite length with infinite rank, and every sequence of length $\le \omega+1$ has rank less than $\omega+\omega$.
-
-\subsection{Classification of the final sequence for $A\sequoid\protect\blank$}
-
-Let $\G(\alpha)$ be a category of games, and let $A$ be an object of $\G(\alpha)$.
-We have $M_{\oc A}=M_A\times\omega$, so there is a natural map $\pr_2\from M_{\oc A}\to \omega$.
-If $s$ is a play in $\oc A$, then we get an associated sequence of natural numbers $\hat s\from\length(s)\to\omega$ given by\[
-  \hat s = \pr_2 \circ s
-  \]
-
-Given an ordinal $\delta$, we define a game $(\oc A)_\delta=(M_{\oc A},\lambda_{\oc A}, \zeta_{\oc A}, P_{\oc A,\delta})$, where $P_{\oc A,\delta}$ is the subset of $P_{\oc A}$ given by:
-\[
-  P_{\oc A,\delta} = \{s\in P_{\oc A}\suchthat \rank(\hat s)\le\delta\}
-  \]
-As we have seen, this set is prefix-closed, so $(\oc A)_\delta$ is a well formed game.
-
-For an ordinal $\delta$, let $A^{\sequoid\delta}$ denote term $\delta$ in the final sequence for $A\sequoid\blank$ (i.e., $A^{\sequoid\delta}=\FS_{A\sequoid\blank}(\delta)$).
-
-Our main result is as follows:
-
-\begin{theorem}
-  \label{MainFinalSequenceResult}
-  \[
-    A^{\sequoid\delta}\cong (\oc A)_\delta
-    \]
-  Given ordinals $\gamma\le\delta$, the arrow $A^{\sequoid\delta}\to A^{\sequoid\gamma}$ in the final sequence is given by the copycat morphism $(\oc A)_\delta\to(\oc A)_\gamma$ induced by the inclusion $P_{\oc A, \gamma}\hookrightarrow P_{\oc A, \delta}$.
-\end{theorem}
-
-As a sanity check, we observe that if $n<\omega$ then the sequences of rank $n$ are precisely the sequences that only involve the terms $0,\dots,n-1$.
-Therefore, it is easy to see that $A^{\sequoid n}\cong(\oc A)_n$ for all $n<\omega$.
-
-\begin{proof}[Proof of Theorem \ref{MainFinalSequenceResult}]
-  If $s\in P_{\oc A}$ then $\hat s$ has rank $0$ if and only if $s=\emptyplay$.  Therefore, it is easy to see that $A^{\sequoid 0}=I\cong(\oc A)_0$.
-
-  Consider the game $A\sequoid (\oc A)_\delta$.
-If $s$ is a play in this game, then we may identify $s$ with a subsequence of $\oc A$ by labelling the copy of $s$ on the left as $A_0$ and increasing the index by one for each copy of $A$ on the right.
-In other words:
-  \[
-    \Delta\hat s = ({s\vert_{(\oc_A)_\delta}})\hat{}
-    \]
-  By the induction hypothesis, $({s\vert_{(\oc_A)_\delta}})\hat{}$ has rank at most $\delta$ and therefore $\hat s$ has rank at most $\delta+1$.
-
-  Conversely, if $s$ is a sequence in $P_{\oc A}$ and $\Delta\hat s$ has rank at most $\delta$, it means that $s\vert_{A_2,A_3,\dots}\in P_{(\oc_A)_\delta}$ and so $s$ is a play in $A\sequoid(\oc A)_\delta$.
-
-  We check the assertion about the morphisms in the category.
-There is a unique morphism $(\oc A)_\delta\to I$ for each $\delta$, so there is nothing to check there.
-Suppose $\mu<\alpha$ is a limit ordinal.
-By induction, $A^{\sequoid\mu}\cong (\oc_A)_\mu$ and the morphisms $A^{\sequoid\mu}\to A^{\sequoid\delta}$ for $\delta<\mu$ are copycat morphisms induced by the inclusion $P_{\oc A, \delta}\hookrightarrow P_{\oc A,\mu}$.
-If we apply the functor $A\sequoid\blank$ to this cone, then we get a cone from $A\sequoid A^{\sequoid \mu}$ over the diagram formed by $A^{\sequoid\delta}$ for $\delta<\mu$.
-Our argument above also tells us that all the arrows in this new diagram are induced by inclusion functions, and therefore the morphism
-  \[
-    A^{\sequoid\mu}\to A\sequoid A^{\sequoid\mu}
-    \]
-  induced by the inclusion $P_{\oc A,\mu}\hookrightarrow P_{\oc A, \mu+1}$ commutes with both cones, so it is the morphism $A^{\sequoid\mu+1}\to A^{\sequoid\mu}$ in our diagram.
-Under the isomorphism $A^{\sequoid\delta}\cong (\oc A)_\delta$ that we have constructed already, the functor $A\sequoid\blank$ sends inclusion morphisms to inclusion morphisms, so by induction the morphism $A^{\sequoid\mu+n+1}\to A^{\sequoid\mu+n}$ is also induced by an inclusion map.
-
-  It remains to deal with the limiting case.
-Let $\mu$ be a limit ordinal.
-Then $(\oc A)_\mu$ admits a cone over the diagram given by the $A^{\sequoid \delta}$ for $\delta<\mu$, again given by copycat morphisms induced by inclusion maps.
-Let $B$ be an object of $\G(\alpha)$ and suppose that we have a cone
-  \[
-    \left(\map{\sigma_\delta}{B}{A^{\sequoid\delta}}\right)_{\delta<\mu}
-    \]
-  over the diagram given by the $A^{\sequoid\delta}$ and the inclusion morphisms between them.
-This means that if we identify $A^{\sequoid\delta}$ with $(\oc A)_\delta$ then the strategies $\sigma_\delta$ form a chain.
-Then (under this identification) we set
-  \[
-    \sigma = \textrm{limit closure of }\bigcup_{\delta<\mu}\sigma_\delta
-    \]
-  Since $B$ satisfies the limit condition, we do not introduce any extra plays when we take the limit closure and so $\sigma$ is a subset of $P_{B\implies (\oc A)_\mu}$, by the definition of a sequence of rank $\mu$.
-$\sigma$ is limit-closed, so it is a strategy, since the $\sigma_\delta$ are.
-It is clear that composing $\sigma$ with the inclusion morphism $(\oc A)_\mu\to(\oc A)_\delta$ gives $\sigma_\delta$, so this is a morphism of cones.
-
-  Now suppose that $\tau\from B\to(\oc A)_\mu$ also gives rise to a morphism of cones.
-By applying the functor into $\Rel$, we can check that if we compose $\tau$ with the inclusion morphism $(\oc A)_\mu\to(\oc A)_\delta$ then we get the strategy $\tau\cap P_{B\implies(\oc A)_\delta}$.
-Therefore, for all $\delta<\mu$:
-  \[
-    \tau \cap P_{B\implies(\oc A)_\delta}=\sigma_\delta
-    \]
-  Since $\tau$ satisfies the limit condition, it is clear that $\sigma\subset\tau$.
-Conversely, suppose that $s\in\tau$.
-Since $\tau\subset P_{B\implies(\oc A)_\mu}$, $s\vert_{(\oc A)_\mu}$ must have rank at most $\mu$.
-If $s\vert_{(\oc A)_\mu}$ has rank $\delta<\mu$, it follows that $s\in\sigma_\delta\subset\sigma$.
-If instead $s\vert_{(\oc A)_\mu}$ has rank $\mu$ then it must be a limiting play, so by the limit condition on $\sigma$ it suffices to show that all the proper prefixes of $s$ are contained in $\sigma$.
-Since $s\vert_{(\oc A)_\mu}$ has rank $\mu$, all its proper prefixes have rank less than $\mu$ and are therefore contained in $\sigma$ by the argument we have just used.
-
-  It follows that $\sigma=\tau$, and therefore that the limiting cone $A^{\sequoid\mu}$ is indeed given by the game $(\oc A)_\mu$, together with the morphisms induced by inclusion functions.
-This completes the induction.
-\end{proof}
-
-As a consequence of this classification, we have:
-
-\begin{corollary}
-  Let $\alpha=\omega^\beta$ for some $\beta$.  If $A$ is an object of $\G(\alpha)$, then the final sequence for the functor $A\sequoid\blank\from\G(\alpha)\to\G(\alpha)$ stabilizes by $\alpha$.
-
-  Moreover, this bound is tight: there exists some completely negative $\alpha$-game $A$ such that the final sequence for $A\sequoid\blank$ does not stabilize before $\alpha$.  
-  \begin{proof}
-    We want to show that the morphism
-    \[
-      A^{\sequoid\alpha+1}\to A^{\sequoid\alpha}
-      \]
-    in the final sequence for $A\sequoid\blank$ is an isomorphism.
-If we make the identification given by our classification result, then we may identify this morphism with the copycat morphism $(\oc A)_{\alpha+1}\to(\oc A)_\alpha$ induced by the inclusion function
-    \[
-      P_{\oc A,\alpha}\hookrightarrow P_{\oc A,\alpha+1}
-      \]
-    But we have already shown that any sequence of length less than $\alpha$ must have rank less than $\alpha$ and therefore this inclusion map is the identity.
-It follows that the morphism $(\oc A)_{\alpha+1}\to(\oc A)_\alpha$ is the identity and so the morphism above is indeed an isomorphism.
-
-    To show tightness of the bound, it suffices to exhibit a game $A$ such that there sequences $s\in\oc A$ of length less than $\alpha$ and arbitrarily high rank.
-We take $A$ to be the $\alpha$-game $\st$ where there is a unique legal play $qaqa\dots$ of any length $\delta<\alpha$.
-Then for any $\delta<\alpha$ we may construct a play $s\in\oc A$ of the form
-    \[
-      q_1a_1q_2a_2\dots\;q_1a_1q_2a_2\dots\;\dots\dots
-      \]
-    such that $\hat{s}$ has the canonical sequence $c_{\delta}$ as a subsequence.  Therefore, $\hat{s}$ has rank at least $\delta$.  
-  \end{proof}
-\end{corollary}
-
-\begin{note}
-  This result gives an alternative proof that $\oc A$ is the final coalgebra for the functor $A\sequoid\blank$.
-
-  Although we have not developed the theory of win-games of length $\omega^\beta+1$, this result also sheds some light on why the final sequence for $\omega+1$-games stabilizes at $\omega+\omega$: this time, we use the fact that any sequence of length at most $\omega+1$ must have rank at most $\omega+\omega$.
-\end{note}
-
-\section{Further Directions}
-
-There are still a few areas in the current direction that need working out, such as the construction of transfinite win-games with winning strategies.
-I also plan to examine the internal logic of these categories of transfinite games to characterize them logically, and to investigate the logical meaning of convergence of the final sequence.
-Another direction is to see what our classification of the final sequence tells us about the exponential $\oc A$, and whether it tells us anything about the $\omega$-games case.
-
-The paper \cite{MelliesCofCommCom} gives category-theoretic conditions under which the final sequence for $A\sequoid\blank$ always terminates at $\omega$ (though it is not stated in quite that language).
-I plan to examine this work to see which of these conditions fail for categories of transfinite games.
-There are other category-theoretic questions to ask about the behaviour of the final sequence.
-It is known, for example, that the final sequence for a finitary endofunctor on $\Set$ must always terminate by $\omega+\omega$ \cite{finalseq} and there are other results generalizing this.
-Although our endofunctor is not a functor on $\Set$, it can be turned into a functor on $\Set$ if we restrict to copycat strategies.
-It would be worthwhile to view the results of this research under that lens.
-
-As a longer-term piece of research: we had a number of mathematical problems caused by the sequential nature of the games we studied, and we were forced to restrict our attention to negative games (though we found a possible way of getting around that).
-An alternative approach, studied by Abramsky and Melli\`{e}s \cite{AMConcurrent}, is to study \emph{concurrent games}.
-These games, where the players $O$ and $P$ move concurrently, rather than sequentially, avoid many of the problems present with sequential games; indeed, the authors of \cite{AMConcurrent} obtain a full completeness result for MALL using these concurrent games.
-It is not immediately obvious how to apply the research in this report to concurrent games, nor how to develop the sequoid operator in a concurrent setting.
-One possible approach to the latter problem is to observe that in our category of games we have a natural isomorphism
-\[
-  \G_s(A\sequoid B,C)\cong\G_s(A,B\implies C)
-  \]
-(where $\G_s$ is a category of games and strict strategies) so that $\blank\sequoid B$ is something like a left adjoint to the functor $B\implies\blank$ in the strict subcategory.
-In a general cpo-enriched monoidal category $\C$, we can say that a morphism $f\from X\to Y$ is \emph{strict} if the composition
-\[
-  I\xrightarrow{\emptyplay_X}X\xrightarrow{f}Y = \emptyplay_Y
-  \]
-where $\emptyplay_X$ and $\emptyplay_Y$ are the bottom elements of $\C(I,X)$ and $\C(I,Y)$ respectively.
-
-The eventual goal here will be to develop a sequoidal category of concurrent games and to characterize its internal logic.
-A further direction in this area is to mimic the results in this report in a concurrent setting.
-
-A surprising direction of research is given by the material in Sections \ref{TransSMCCSex} through \ref{ImpliesCnSex}, in particular trying to generalize the construction in Section \ref{DigressionSex} to other categories.
-The situation here is fairly non-standard: we a category (of completely negative games), but we also have all the non-completely negative games that are not objects of the category but still admit morphisms into them.
-We dealt with these objects by using a construction that mimics the traditional slice categories from category theory, but I would be interested to pursue this further and try to develop it in a more general category-theoretic framework.
-It might be worthwhile to study these questions in the context of finitary games, particularly as $A^{\cn}$ has a presentation there in terms of the linear connectives (specifically, $N^{\cn}=N$ if $N$ is negative and $P^{\cn}=\bneggame{P}\implies\bot$ if $P$ is positive).
-
-In Section \ref{DigressionSex} we constructed a category $\tilde{\G}$ whose objects are arbitrary (not necessarily completely negative) games.
-Even in the finitary setting, this poses an obvious question: is this category  $*$-autonomous and can we use it to model fragments of linear logic that we could not model in the completely negative case?
-Of course, there are other obstacles to doing this besides the sign of the games in our category, and the fact that $\tilde{\G}$ is equivalent as a category to $\G$ casts some doubt on whether this is possible, but I would like to explore this direction further.
-
-Another thing that is worth looking into is the effect that removing the limiting condition might have on these games.
-The limiting condition played no great role in our construction of $\G(\alpha)$, though it was crucial in our work on the final sequence.
-Removing the limiting condition might allow certain forms of unbounded non-determinism to be modelled.
-The work done in \cite{LairdOrdinalGames} is connected to this, and it will be instructive to compare the research in this report with Laird's earlier work on transfinite game semantics.
-
-Lastly, there is further technical research to be done into sequoidal categories, such as finding appropriate conditions under which the sequoidal exponential gives rise to a linear exponential comonad or cofree commutative comonoid.
-
-\appendix
-\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
-
-\section{Proofs}
-
-This Appendix contains proofs from the early sections that were omitted from the main body of the text to avoid breaking up the flow.
-
-\subsection{Proof of Proposition \ref{nice-negative-games}}
-\label{nice-negative-games-proof}
-
+\begin{proof}[Proof of Proposition \ref{nice-negative-games}]
   We proceed by induction on the length $n$ of $s$.
@@
 For part (ii), note that in this case we have $\zeta_{A\tensor B}(t)=P$, so $\zeta_{A\tensor B}(tm)=O$, since $tm$ is alternating.
-If $m$ is an $A$-move, it means that $\zeta_B(tm\vert_B)=\zeta_B(t\vert_B)=P$, so we must have $\zeta_A(tm\vert_A)=O$ by the definition of $\zeta_{A\tensor B}$.
+If $m$ is an $A$-move, it means that $\zeta_B(tm\vert_B)=\zeta_B(t\vert_B)$, so we must have $\zeta_A(tm\vert_A)=O$.
 Then
@@
   Finally, note that the $\tensor$ result implies the $\implies$ result after writing $A\implies B=\neggame{A}\parr B = \neggame{(A\tensor \neggame{B})}$.
-
-\subsection{Proof of Proposition \ref{alternatingsequenceslemma}}
-\label{alternatingsequenceslemmaproof}
-
+\end{proof}
+
+A corollary of our result is that we have:
+\begin{align*}
+  P_{A\tensor B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\tensor B}$}\} \\
+  P_{A\implies B} & = \{s\in P_A\|P_B\suchthat \textrm{$s$ is alternating with respect to $\zeta_{A\implies B}$}\}
+\end{align*}
+if $A,B$ are negative games.  In other words, we can ignore the well-formedness condition on plays if we are dealing with only negative games.
+
+This proposition allows us to prove the following useful fact:
+
+\begin{lemma}
+  \label{alternatingsequenceslemma}
+  Let $A,B,C$ be negative games, and let $\s\in (M_A\cprd M_B\cprd M_C)^*$.  If any two of the following statements are true, then so is the third:
+  \begin{gather*}
+    \s\vert_{A,B}\in P_{A\implies B}\\
+    \s\vert_{A,C}\in P_{A\implies C}\\
+    \s\vert_{B,C}\in P_{B\implies C}
+  \end{gather*}
+  \begin{proof}
     By symmetry, it will suffice to prove that if $\s\vert_{A,B}\in P_{A\implies B}$ and $\s\vert_{B,C}\in P_{B\implies C}$ then $\s\vert_{A,C}\in P_{A\implies C}$.
@@
 By Proposition \ref{nice-negative-games} applied to $\s\vert_{A,B}$, we must have $\zeta_A(\s\vert_A)=P$ and so $\zeta_{A\implies C}(\s\vert_{A,C})=(P\Rightarrow O) = O$.
-
-\subsection{Proof of Proposition \ref{HylandSchalkFaithful}, Proposition \ref{TransHylandSchalkFaithful}}
-\label{HylandSchalkFaithfulProof}
-
-Our proof is essentially that given in \cite{CalderonMcCusker}.
-Suppose for a contradiction that $\sigma\ne\sigma'$, so without loss of generality there is some $P$-position $s\in\sigma\setminus\sigma'$ (using the definition of a strategy).
-By hypothesis, there is some $s'\in\sigma'$ such that $s'\vert_A=s\vert_A$ and $s'\vert_B=s\vert_B$.
-Clearly, $s\ne s'$, since $s\not\in\sigma'$, so let $r\prefix s$ be the largest common prefix of $s$ and $s'$.
-We therefore have $rx\prefix s,ry\prefix s'$, where $x,y\in M_{A\implies B}$ and $x\ne y$.
-
-Since $s\vert_A=s'\vert_A$ and $s\vert_B=s'\vert_B$, the moves $x$ and $y$ must take place in different games (otherwise we would be forced to have $x=y$).
-They are therefore both $P$-moves.
-Suppose without loss of generality that $x$ is an $A$-move and that $y$ is a $B$-move.
-By hypothesis, there is some $P$-position $t\in\sigma$ such that $t\vert_A=ry\vert_A=r\vert_A$ and $t\vert_B=ry\vert_B=r\vert_By$.
-
-Now clearly $rx\ne t$ (since their restrictions to $A$ and $B$ are different).
-Let $q\prefix rx, t$ be their largest common prefix; then we have $qu\prefix rx, qv\prefix t$ for some $u\ne v$.
-But now since $qu, qv\in\sigma$, $u$ and $v$ must both be $O$-moves, so they must be contained in the same component.
-But this is impossible: if they are both $A$-moves then we have $q\vert_Au\prefix r\vert_A x$ and $q\vert_Av\prefix r\vert_A$, so $u=v$ and if they are both $B$-moves then we have $q\vert_Bu\prefix r\vert_B$ and $q\vert_Bv\prefix r\vert_By$, so $u=v$ again.
-This is a contradiction.
-
-\subsection{Proof of Lemma \ref{LiftingLemma}}
-\label{LiftingLemmaProof}
-
-We prove this by induction on $k$.  There is a unique sequence of length $0$, namely the empty sequence, and its $A$- and $C$-components are both empty, so are prefixes of $s$ and $t$.
-
-Suppose now that $k=1$.
-We make the observation that if $a$ is an $O$-move in $A$ and if $b$ is an $O$-move in $B$ then $a$ is a $P$-move in $A\implies B$ and $b$ is a $P$-move in $B\implies C$.
-Since the starting move in $A\implies B$ or $B\implies C$ must be an $O$-move in both its component game and in the game as a whole, we see that any sequence in $\sigma\|\tau$ must begin with a move in $C$.
-So we have $\s^1=c$, for some $C$-move $c$, and the condition that $\s^1\vert_C\prefix t$ means that $c$ must be the first move in $t$, which is always a move from $C$.
-We have $\s^1\vert_A=\emptyplay\prefix s\vert_A$ and $\s^1\vert_B=\emptyplay\prefix s\vert_B$, as desired.
-
-Now suppose that we have constructed the sequence $\s^k$ for some $k$ such that $1\le k<n$.
-We seek a sequence $\s^{k+1}\in \sigma\|\tau$ of length $k+1$ such that $\s^{k+1}\vert_A\prefix s$ and $\s^{k+1}\vert_C\prefix t$.
-If we write $\s'$ for the sequence obtained by removing the last move in $\s^{k+1}$, it is clear that $\s'\vert_A\prefix s$ and $\s'\vert_C\prefix t$, so $\s'=\s^k$ by uniqueness.
-Therefore, $\s^{k+1}$ is of the form $\s^kx$, for some move $x\in M_A\cprd M_B\cprd M_C$.
-
-Write $\s^k=\s''y$, where $y$ is the last move in $\s^k$.  Our move $x$ will depend on which game $y$ is played on as follows:
-
-\begin{itemize}
-  \item Suppose $y$ is a move in $A$ or an $O$-move in $B$.  By induction, $\s''y\vert_{A,B}$ is a prefix of $s$ ending in $y$.  We claim that it is a proper prefix.
-
-    Indeed, let $b$ be the last $B$-move occurring in $\s''y$ (since play in $A\implies B$ starts with a $B$-move, there must be such a move).
-If $b=y$, then $b$ is an $O$-move in $A\implies B$.
-Otherwise, $y$ must be a move in $A$, and then $b$ is again an $O$-move in $A\implies B$, since player $P$ switches games.
-Therefore, $b$ is a $P$-move in $B\implies C$.
-Now $\s''y\vert_B$ is a prefix of $t$ ending in $b$.
-Since $b$ is a $P$-move in $B\implies C$, it may only be followed in $B\implies C$ by another move from $B$, so there are two possibilities: either $\s''y\vert_{B,C}=t$ or there is some other $B$-move $b'$ that occurs later than $b$ in the sequence $t$.
-In the first case, $\s''y\vert_{A,B}$ must be a proper prefix of $s$ by length considerations:
-    \begin{align*}
-      \length(\s''y\vert_{A,B}) & = \length(\s''y) - \length(\s''y\vert_C) \\
-        & = \length(\s''y) - \length(t\vert_C) \\
-        & = k - \length(t\vert_C) < n - \length(t\vert_C) = \length(s)
-    \end{align*}
-    while in the second case $\s''y\vert_B$ must be a proper prefix of $t\vert_B=s\vert_B$, and so $\s''y\vert_{A,B}$ must be a proper prefix of $s$.
-
-    Therefore, we have $\s''y\vert_{A,B}x\prefix s$ for some move $x\in M_A\cprd M_B$.
-If $x$ is an $A$-move then $\s''yx\vert_{B,C}=\s''y\vert_{B,C}\prefix t$, as desired.
-If $x$ is a move in $B$, then it must be a $P$-move in $A\implies B$ (since $y$ is either a move in $A$ or an $O$-move in $B$), so it is an $O$-move in $B\implies C$.
-Since $s\vert_B=t\vert_B$, we must have $\s''yx\vert_B\prefix t\vert_B$, and so $y$ must be a $P$-move in $B\implies C$, and should therefore be followed by another move in $B$, which must be $x$.
-Therefore, $\s''yx\vert_{B,C}\prefix t$.
-
-    For uniqueness, suppose that $\s''yz\in\sigma\|\tau$ is such that $\s''yz\vert_A\prefix s\vert_A$ and $\s''yz\vert_C\prefix t\vert_C$.
-As before, let $b$ be the last $B$-move occurring in $\s''y$; we have already shown that $b$ must be a $P$-move in $B\implies C$, and it follows that it must be the last move occurring in $\s''y\vert_{B,C}$ (since it can only be followed by another $B$-move).
-Suppose that $z\in M_B\cprd M_C$.
-Then $\s''yz\vert_{B,C}=\s''y\vert_{B,C}z$; since the last move in $\s''y\vert_{B,C}$ is $b$, this means that $z$ must be an $O$-move in $B$.
-So $z$ is either an $O$-move in $B$ or a move in $A$.
-
-    If $y$ was an $O$-move in $A$, then $y$ is a $P$-move in $A\implies B$, so it must be followed in $A\implies B$ by another move from $A$.
-Then the condition that $\s''yz\vert_A\prefix s\vert_A$ tells us that $z=x$.
-If instead $y$ was a $P$-move in $A$ or a move in $B$ then $y$ is an $O$-move in $A\implies B$; now, since we have $\s''y\vert_{A,B}z,\s''y\vert_{A,B}x\in\sigma$, it must be the case that $x=z$ by the definition of a strategy.
-
-  \item If instead $y$ is a move in $C$ or a $P$-move in $B$, we use a symmetrical argument, choosing $x$ to be the next move along in $t$.
-We need to take a little extra care here when we talk about the last $B$-move in $\s''y$; there may in fact be no $B$-moves in $\s''y$.
-Since any play in $A\implies B$ must begin with a $B$-move, this only happens when $\s''y$ is entirely made up of $C$-moves.
-In this case, it is not difficult to show that $\s''y\vert_{B,C}$ is a proper prefix of $t$ by length considerations.
-\qedhere
-\end{itemize}
-
-\subsection{Proof of Proposition \ref{CompWinningIsWinning}}
-\label{CompWinningIsWinningProof}
-
-First, we want to show that $\comp\tau\sigma$ is a total strategy.  Let $s\in\comp\tau\sigma$ be an $O$-position; then we have some $\s\in\sigma\|\tau$ with $\s\vert_{A,C}=s$.
-
-We claim that there is a maximal such $\s$.
-By Lemma \ref{LiftingLemma}, $\s$ is determined by its length, and so the only way that there could not be a maximal such $\s$ is if there is some infinite sequence $\S\in(M_A\cprd M_B\cprd M_C)^\omega$ with $\S\vert_{A,B}\in\sigma\cup\sigma^\omega$, $\S\vert_{B,C}\in\tau\cup\tau^\omega$ and $\S\vert_{A,C}=s$.
-Since $\S$ has some finite prefix $\s$ with $\s\vert_{A,C}=s$, $\S\vert_A$ and $\S\vert_C$ must both be finite, so they are $O$-plays in the games $A\implies B$ and $B\implies C$ respectively.
-
-Now $\S\vert_B$ is infinite.
-If $W_B(\S\vert_B)=O$, then $W_{A\implies B}(\S\vert_{A,B})=O$, contradicting the fact that $\sigma$ is a winning strategy.
-Symmetrically, if $W_B(\S\vert_B)=P$, then $W_{B\implies C}(\S\vert_{B,C})=O$, contradicting the fact that $\tau$ is a winning strategy.
-We have a contradiction in either case, so if $\sigma$ and $\tau$ are indeed winning strategies, there must be a maximal (finite) $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-
-The argument from Proposition \ref{BoundedTotalComposition} now applies, showing that $sx\in\comp\tau\sigma$ for some $P$-move $x$.
-
-Lastly, we want to show that any infinite play in $\comp\tau\sigma$ is $P$-winning.
-Suppose $s$ is some infinite play in $\comp\tau\sigma$.
-For each finite prefix $t\prefix s$ there is some $\t\in\sigma\|\tau$ with $\t\vert_{A,C}=t$, and by Lemma \ref{LiftingLemma}, we have $\t'\prefix\t$ if $t'\prefix t$.
-Therefore, these $\t$ glue to give an infinite sequence $\s\in(M_A\cprd M_B\cprd M_C)^\omega$ such that $\s\vert_{A,B}\in\sigma^\omega$ and $\s\vert_{B,C}\in\tau^\omega$.
-We claim that $W_{A\implies B}^*(\s\vert_{A,B})=W_{B\implies C}^*(\s\vert_{B,C})=P$ - then it follows that $W_{A\implies C}^*(\s\vert_{A,C})=P$ by transitivity of $\Rightarrow$.
-If $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both infinite, then this is automatically true, since $\sigma$ and $\tau$ are winning strategies.
-Otherwise, one of them must be infinite and the other finite.
-
-Suppose that $\s\vert_{A,B}$ is finite.
-Let $\t$ be the shortest finite prefix of $\s$ with $\t\vert_{A,B}=\s\vert_{A,B}$; then we have $\t c\prefix \s$ for some move $c\in M_C$.
-If $\t\vert_{A,B}=\emptyplay$, then $W_A^*(\t\vert_{A,B})=P$ since $A$ and $B$ are negative.
-Otherwise, there is at least one $B$-move in $\t\vert_{A,B}$.
-Let $b$ be the last $B$-move occurring in $\t\vert_{A,B}$ - then it is the last $B$-move occurring in $\t\vert_{B,C}$; since it is followed by the move $c$, it must be an $O$-move in $B\implies C$ and therefore a $P$-move in $B$.
-Therefore, $W_{A\implies B}^*(\s\vert_{A,B})=P$.
-
-If instead $\s\vert_{B,C}$ is finite, once again we have some $\t\prefix\s$ with $\t\vert_{A,B}=\s\vert_{A,B}$ and $\t a\prefix\s$ for some move $a\in M_A$.
-Since $\s\vert_{A,B}$ is infinite, it must be non-empty, so it must contain some $B$-move.
-Let $b$ be the last $B$-move occurring in $\s\vert_{A,B}$; since $b$ is followed by an $A$-move, it must be an $O$-move in $B$.
-Now $b$ is also the last $B$-move occurring in $\s\vert_{B,C}$ and so $W_{B\implies C}^*(\s\vert_{B,C})=P$.
-
-\section{Weakenings}
-
-This appendix contains material that I developed earlier in the year.
-The material was originally intended to be applied to the study of the final sequence (the idea is that if $\gamma<\delta$ then $A^{\sequoid\gamma}$ is a (lax) weakening of $A^{\sequoid\delta}$ and to use these results to prove that the sequence stabilizes.
-Since we have obtained this result by another method, this material is not directly applicable to the final sequence any more, but it is of interest in its own right and links in with work by Juliusz Chroboczek on subtyping \cite{juliuszthesis}.
-
-\subsection{Weakenings}
-
-Let $A=(M_A,\lambda_A,P_A)$ be a game.  Then we have two notions of a \emph{weakening} of $A$ - informally, a game that is \emph{easier} than $A$, from the player $P$'s point of view.
-
-\begin{enumerate}
-  \item An \emph{antecedent weakening} of $A$ is a game $A'=(M_A,\lambda_A,P_{A'})$, where $P_{A'}\subset P_{A}$ such that for every $O$-play $s$ occurring in both $P_A$ and $P_{A'}$, the set of $P$-responses to $s$ in $A'$ is precisely the set of $P$-responses to $s$ in $A$ and for every $P$-play $t$ occurring in both $P_A$ and $P_{A'}$, the set of $O$-responses to $t$ in $A'$ is a subset of the set of $O$-responses to $t$ in $A$.
-  \item A \emph{precedent strengthening} of $A$ is a game $A''=(M_A,\lambda_A,P_{A''})$ where $P_A\subset P_{A''}$ such that for every $O$-play $s$ occurring in both $P_A$ and $P_{A''}$, the set of player responses to $s$ in $A$ is a subset of the set of $P$-responses to $s$ in $A''$, and such that for every $P$-play $t$ occurring in both $P_A$ and $P_{A''}$ the set of $O$-responses to $t$ in $A$ is precisely the set of $O$-responses to $t$ in $A''$.
-\end{enumerate}
-
-In other words, a precedent strengthening of $A$ is a game in which the player has more choices at each move, but the opponent has the same choices, while an antecedent weakening of $A$ is a game in which the player has the same choices at each move, but the opponent has fewer choices.
-
-We can express the definition of an antecedent weakening more compactly as follows: $(M_A, \lambda_A, P_{A'})$ is an antecedent weakening of $(M_A, \lambda_A, P_A)$ if $P_{A'}\subset P_A$ and the following condition holds: whenever $s\in P_{A'}$ is an $O$-play and $a\in M_A$ is a $P$-move such that $sa\in P_A$, then $sa\in P_{A'}$.
-This condition says that player $P$ has all the moves available to her in $A'$ that she had in $P_A$ - the other conditions mentioned above follow automatically from the fact that $P_{A'}\subset P_A$.
-
-The important fact about both types of weakening is that we have copycat morphisms $A\to A',A\to A''$.
-
-From here on, we will use the term \emph{weakening} to refer to an antecedent weakening.  If $A'$ is a weakening of $A$, we will write $\cmap{\wk}{A}{A'}$ for the copycat morphism.
+  \end{proof}
+\end{lemma}
+
+We can use this fact to prove that the composition of two strategies is a well-defined strategy.
 
 \begin{proposition}
-  Let $A'$ be a weakening of $A$.  Then $\cmap{\wk}{A}{A'}$ has a right inverse.
-
+  \label{WellDefinedComposition}
+  Let $A,B,C$ be negative games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $\comp\tau\sigma$ as defined above is a strategy for $A\implies C$.
   \begin{proof}
-    The inverse for $\wk$ is the partial strategy $\cmap{\str}{A'}{A}$.
-This is also constructed as a copycat strategy; the only difference is that if $O$ makes a move in $A$ that does not occur in $P_{A'}$ then the player $P$ has no reply.
-We now claim that $\comp\wk\str=\id_{A'}$.
-
-    Formally:
-    \begin{IEEEeqnarray*}{rCl}
-      \wk & = & \left\{s\in P_{A\implies A'}\suchthat\textrm{if $|s|$ is even, then $s\vert_A=s\vert_{A'}$}\right\} \\
-      \str & = & \left\{s\in P_{A'\implies A}\suchthat\textrm{if $|s|$ is even, then $s\vert_A'=s\vert_{A}$}\right\}
-    \end{IEEEeqnarray*}
-
-    We wish to show that $\comp\wk\str=\id_{A'}$.  We shall show that $\comp{\grel\wk}{\grel\str}=\Delta_{P_{A'}}$ in $\Rel$.
-
-    It is easy to see that
-    \begin{IEEEeqnarray*}{rCl}
-      \grel\wk & = & \{(s, s)\suchthat s\in P_{A'}\}\subset P_A\times P_{A'} \\
-      \grel\str & = & \{(s, s)\suchthat s\in P_{A'}\}\subset P_{A'}\times P_A
-    \end{IEEEeqnarray*}
-
-    It is then easy to see that $\comp\wk\str=\Delta_{A'}\subset P_{A'}\times P_{A'}$, as we wanted.
-As a sanity check, if we try to take the composition the other way round then we get $\Delta_{A'}\subset P_A\times P_A$, which is not the identity unless $P_{A'}=P_A$.
+    We have $\emptyplay\in\comp\tau\sigma$, so $\comp\tau\sigma$ is non-empty.
+Let $\s\in\sigma\|\tau$, and suppose that $t\prefix\s\vert_{A,C}$.
+Let $m$ be the last move of $t$, and let $\t$ be the prefix of $\s$ consisting of all moves up to and including $m$.
+Then $\t\vert_{A,C}=t$.
+Since $\sigma\|\tau$ is clearly prefix closed, it follows that $t\in\comp\tau\sigma$.
+This shows that $\comp\tau\sigma$ is prefix closed.
+
+    Since $\sigma\subset P_{A\implies B}$ and $\tau\subset P_{B\implies C}$, Lemma \ref{alternatingsequenceslemma} tells us that $\s\vert_{A,C}\in P_{A\implies C}$.
+
+    We now show that the two strategy properties hold for $\comp\tau\sigma$.
+Suppose $\s\in\sigma\|\tau$ and that $\zeta_{A\implies C}(\s\vert_{A,C})=P$.
+Suppose also that $a\in M_A$ and that $\s\vert_{A,C}a\in P_{A\implies C}$.
+We claim that $\s a\in\sigma\|\tau$.
+Since $\s a\vert_{B,C}=\s\vert_{B,C}\in \tau$, it will suffice to show that $\s a\vert_{A,B}\in \sigma$.
+
+    We have $\s a\vert_{A,C}=\s\vert_{A,C}a\in P_{A\implies C}$ and $\s a\vert_{B,C}=\s\vert_{B,C}\in P_{B\implies C}$ so, by Lemma \ref{alternatingsequenceslemma}, $\s a\vert_{A,B}=\s\vert_{A,B}a\in P_{A\implies B}$.
+Now $\zeta_{A\implies C}(\s\vert_{A,C})=P$ and so $\lambda_A(a)=P$, since $\s\vert_{A,C}a\in P_{A\implies C}$.
+Since $\s\vert_{A,B}a\in P_{A\implies B}$, it follows that $\zeta_{A\implies B}(\s\vert_{A,B}a)=P$.
+Since $\s\vert_{A,B}\in\sigma$ and $\sigma$ is a strategy, it follows that $\s\vert_{A,B}a\in\sigma$.
+Therefore, $\s a\in\sigma\|\tau$, so $\s\vert_{A,C}a=\s a\vert_{A,C}\in\comp\tau\sigma$.
+
+    An identical argument tells us that if $c\in M_C$ and $\s\vert_{A,C}c\in P_{A\implies C}$ then $\s\vert_{A,C}c\in\comp\tau\sigma$.
+
+    Now suppose that $s\in\comp\tau\sigma$ is such that $\zeta_{A\implies C}(s)=O$ and that $m_1,m_2\in M_{A\implies C}$ are such that $sm_1,sm_2\in\comp\tau\sigma$.  We wish to show that $m_1=m_2$.
+
+    We shall use the argument given in \cite{abramskyjagadeesangames}.
+Given a sequence $s\in\comp\tau\sigma$, we say that $\s\in\sigma\|\tau$ \emph{covers} $s$ if $s\prefix\s\vert_{A,C}$.
+By definition, every sequence in $\comp\tau\sigma$ is covered by some sequence in $\comp\tau\sigma$.
+
+    We claim that if $s\in\comp\tau\sigma$ then there is a sequence $\s$ that is minimal among sequences that cover $s$ (with respect to the prefix ordering).
+In such a case, we must clearly have $\s\vert_{A,C}=s$.
+
+    We shall use the partial-function definition of strategies for the sake of clarity.  Recall that our strategies $\sigma$ and $\tau$ give us partial functions:
+    \begin{gather*}
+      \hat\sigma\from P_{A\implies B}^-\to M_{A\implies B}^+\\
+      \hat\tau\from P_{B\implies C}^-\to M_{B\implies C}^+
+    \end{gather*}
+    It will be helpful to define one more partial function using our sequence $s$.  We define
+    \[
+      \hat s(t) =
+      \begin{cases}
+        a & \textrm{if $ta\prefix s$} \\
+        \textrm{undefined} & \textrm{if $ta\not\prefix s$ for all $a\in M_{A\implies C}$}
+      \end{cases}
+      \]
+    So if we are given some prefix of $s$, $\hat{s}$ tells us what the next move is.
+We shall be interested in $\hat s$ as a partial function $P_{A\implies C}^+\pfun M_{A\implies C}^-$: by Proposition \ref{WhoSwitchesGames}, the $O$-reply to a $P$-play in $A\implies C$ is always in the same game as the last move by player $P$, so $\hat s\from P_{A\implies C}^+\pfun M_{A\implies C}^-$ maps plays ending in an $A$-move to $A$-moves and maps plays ending in a $C$-move to $C$-moves.
+
+    We can now define a map $F\colon \sigma\|\tau\to M_A\cprd M_B\cprd M_C$ by
+    \[
+      F(\s) =
+      \begin{cases}
+        \hat s(\t\vert_{A,C}) & \textrm{if $\t=\emptyplay$ or if $\t$ ends with an $O$-move in $A$ or a $P$-move in $C$} \\
+        \hat \sigma(\t\vert_{A,B}) & \textrm{if $\t$ ends with a $P$-move in $A$ or an $O$-move in $B$} \\
+        \hat \tau(\t\vert_{B,C}) & \textrm{if $\t$ ends with a $P$-move in $B$ or an $O$-move in $C$}
+      \end{cases}
+      \]
+    Note that any of the partial functions $\hat s,\hat\sigma,\hat\tau$ may be undefined at $\t$, so $F$ is only a \emph{partial} function.
+
+    We claim that if $\t\in\sigma\|\tau$ and $F(\t)$ is defined then $\t F(\t)\in\sigma\|\tau$.
+In the first case, if $\t=\emptyplay$ or if $\t$ ends with an $O$-move in $A$ or a $P$-move in $C$, then $\zeta_{A\implies C}(\t\vert_{A,C})=P$.
+If $\t=\emptyplay$ then $F(\t)$ is the first move in $s$, which must be the first move in $\tau$.
+Otherwise, suppose that $\t$ ends with an $O$-move in $A$.
+We have $\t F(\t)\vert_{A,C}\prefix s$, so $\t F(t)\vert_{A,C}\in P_{A\implies C}$, while $\t F(\t)\vert_{B,C}=\t\vert_{B,C}\in P_{B\implies C}$, so $\t F(\t)\vert_{A,B}\in P_{A\implies B}$, by Lemma \ref{alternatingsequenceslemma}.
+Moreover, $\zeta_{A\implies B}(\t)=P$, and therefore $\t F(\t)\vert_{A,B}\in\sigma$.
+Similarly, if $\t$ ends with a $P$-move in $C$, we have $\zeta_{B\implies C}(\t)=P$ which tells us that $\t F(\t)\vert_{B,C}\in\tau$.
+In either case, $\t F(\t)\in\sigma\|\tau$.
+
+    If $\t$ ends with a $P$-move in $A$ or an $O$-move in $B$, then we have $\t\vert_{A,B}\in \sigma\cap P_{A\implies B}^-$.
+Then $\t F(\t)\vert_{A,B}\in\sigma$ by the definition of $\hat\sigma$.
+If $F(\t)$ is an $A$-move, then $\t F(\t)\vert_{B,C}=\t\vert_{B,C}\in\tau$ automatically.
+If instead $F(\t)$ is a $B$-move, we note that $\lambda_{B\implies C}(F(t))=\neg\lambda_{A\implies B}(F(t))=\neg P=O$ and therefore $\t\vert_{B,C} F(\t)\in\tau$ by the definition of a strategy and the argument used in the first case above.
+
+    The third case is similar to the second.
+
+    We construct $\s$ as follows: start with the empty sequence $\emptyplay$ and repeatedly apply the map $\t\mapsto \t F(\t)$ until we reach a point where $F(\t)$ is undefined.
+This will produce either a finite or an infinite sequence.
+If there are trailing $B$-moves then we remove them to produce our sequence $\s$.
+We claim that $\s$ is finite and covers $s$ and moreover that it is minimal among all sequences covering $s$.
+
+    Let $\s'$ be a sequence covering $s$.
+We wish to show that $\s'\prefix\s$, so we show by induction on $n$ that $\s_n'=\s_n$ for all $n$ up to the length of $\s$.
+For the induction step, we need to show that if $\s_i'=\s_i$ for $i=1,\dots,k$ then $\s_{k+1}'=F(\s_1\s_2\dots\s_k)$.
+We shall show simultaneously that $\s\vert_{A,C}=s$.
+
+    Observe that if $b\in M_B$ then either $\lambda_{A\implies B}(b)=O$ or $\lambda_{B\implies C}(b)=O$, so $\s'$ cannot start with a $B$-move.
+Therefore, the first move in $\s'$ must be the first move in $s$, which is $F(\emptyplay)$.
+
+    Now assume that $\s_i'=\s_i$ for $i=1,\dots,k$ and write $\t=\s_1\s_2\dots\s_k$.
+If $\t$ ends with an $O$-move in $A$ or a $P$-move in $C$ then $\zeta_{A\implies C}(\t\vert_{A,C})=P$, so $F(\s)=\hat s(\t\vert_{A,C})$ must be an $O$-reply in the same game as the previous $P$-move, so it is therefore a move in $A$ or $C$.
+Therefore, $\t F(\t)\vert_{A,C}=\t\vert_{A,C} F(\t)\prefix s$.
+Now $\s_{k+1}'$ is an $O$-reply in $A$ or $C$ by the same argument, and $\t\s_{k+1}'\vert_{A,C}$ is also a prefix of $s$, since $\s'$ covers $s$.
+Therefore, we must have $F(\t)=\s_{k+1}'$.
+
   \end{proof}
@@
 
-\subsection{The weakening monad of a game}
-
-\subsubsection{Weakening pullback of a game}
-
-Let $A$ be a game.  Suppose $B$ is a game and $\cmap{\sigma}{B}{A}$ is a morphism.  Define
-\[
-  P_{B'}=\{\s\vert_B\suchthat \s\in\sigma\}
-  \]
-$P_{B'}$ is prefix closed, since $\sigma$ is, so $B'=(M_B, \lambda_B, P_{B'})$ is a well-formed game.
-We claim that $B'$ is a weakening of $B$.
-Indeed, suppose $s\in P_{B'}$ is an $O$-play and $sa\in P_B$.
-By the definition of $P_{B'}$, there must be some $\s\in\sigma$ such that $\s\vert_B=s$; choosing $\s$ minimal, we may assume that the last move in $\s$ coincides with the last move of $s$.
-Since $s$ is an $O$-play, this last move is an $O$-move in $B$ and therefore a $P$-move in $B\implies A$.
-Therefore, $\s a\in \sigma$ since $\sigma$ is a strategy and so $sa=\s a\vert_B\in P_{B'}$.
-We call $B'$ the \emph{weakening pullback} of $A$ along the morphism $\sigma$.
-
-Next, we define a morphism $\cmap{\sigma'}{B'}{A}$.  As sets, $\sigma'=\sigma$ (noting that, by definition, $\sigma\subset P_{B'\implies A}$).  We claim that
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
-      & B' \arrow[d, "\sigma'"] \\
-    %
-      & A
-  \end{tikzcd}
-  \]
-commutes.
-
-Once again, we check this in $\Rel$.
-If we note that $\grel\wk=\Delta_{P_{B'}}\subset P_B\times P_{B'}$ and that $\grel\sigma=\grel{\sigma'}$ as sets, then it is clear that $\comp{\grel{\sigma'}}{\grel\wk}=\grel\sigma$ in $\Rel$, and so $\comp{\sigma'}{\wk}=\sigma$ in $\G$.
-
-The weakening $B'$ and the morphism $\sigma'$ satisfy a universal property - namely, if $B''$ is a weakening of $B$ and $\cmap{\sigma''}{B''}{A}$ is a morphism such that
-\begin{equation}
-  \label{pullback.b.double.prime}
-  \begin{tikzcd}
-    B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
-      & B'' \arrow[d, "\sigma''"] \\
-    %
-      & A
-  \end{tikzcd}
-\end{equation}
-commutes, then $B'$ is a weakening of $B''$ and 
-\begin{equation}
-  \label{pullback.b.prime}
-  \begin{tikzcd}
-    B'' \arrow[r, "\wk"] \arrow[dr, "\sigma''"']
-      & B' \arrow[d, "\sigma'"] \\
-    %
-      & A
-  \end{tikzcd}
-\end{equation}
-commutes.
-Indeed, working in $\Rel$ again, diagram \eqref{pullback.b.double.prime} tells us that $\grel\sigma=\grel{\sigma''}$ as sets, which implies that $\sigma\subset P_{B''}\times P_A$.
-Noting the definition of $P_{B'}$, it follows that $\map{\sigma'}{B'}{A}$ is the weakening pullback of $A$ along $\sigma''$, and so diagram \eqref{pullback.b.prime} commutes.
-
-\subsection{The weakening monad}
-
-We shall want to prove various useful properties of these weakening pullbacks, notably a functoriality condition: if $C\xrightarrow{\tau}\map{\sigma}{B}{A}$ are morphisms, then we get a morphism $\cmap{\tau'}{C'}{B'}$ such that $(\comp\sigma\tau)'=\comp{\sigma'}{\tau'}$.
-This and other useful facts are brought together in the following theorem:
-
-\begin{theorem}
-  Let $A$ be a game.
-Then we have a functor $\cmap{\weak_A}{\G/A}{\G/A}$ that sends a morphism $\map{\sigma}{B}{A}$ to the pullback weakening $\map{\sigma'}{B'}{A}$ and that gives rise to an idempotent monad on $\G/A$.
-
+Now that we have a working composition of strategies, we are ready to make the collection of games into a category.  The identity morphism $A\to A$ is given by the copycat strategy on $A\implies A$:
+\[
+  \id_A = \left\{s\in P_{A\implies A}\suchthat \textrm{for all even-length $t\prefix s$, $t\vert_{\neggame{A}}=t\vert_A$}\right\}
+  \]
+\begin{proposition}
+  Let $\G$ denote the class of games as defined above.
+If we define a morphism from a game $A$ to a game $B$ to be a strategy for $A\implies B$, then the identity morphism and notion of composition given above make $\G$ into a category.
   \begin{proof}
-    In order to complete the definition of the functor $\weak_A$, we need to define its action on morphisms.
-Let $C\xrightarrow{\tau}\map{\sigma}{B}{A}$ be morphisms in $\G$ (so $\tau$ gives us a morphism from $\map{\comp\sigma\tau}{C}{A}$ to $\map{\sigma}{B}{A}$ in $\G/A$).
-We define a morphism $\cmap{\tau'}{C'}{B'}$ by $\tau'=\tau\cap P_{C'\implies B'}$.
-
-    It is easy to see that $\tau'$ is a strategy, so we need to check that $\comp{\sigma'}{\tau'}=(\comp\sigma\tau)'$.  As usual, we perform this check in $\Rel$.
-
-    Since $(\comp\sigma\tau)'$ is created according to the pullback recipe given above, we have $\grel{(\comp\sigma\tau)'}=\grel{\comp\sigma\tau}$ as sets.
-So, as subsets of $P_{C'}\times P_A$, we have:
-    \begin{align*}
-      \grel{(\comp\sigma\tau)'} & = \grel{\comp\sigma\tau} \\
-                                & = \comp{\grel\sigma}{\grel\tau} \\
-                                & = \{(s, t)\in P_{C'}\times P_{A}\suchthat \exists u\in P_B \esuchthat (s,u)\in\grel\tau, (u,t)\in\grel\sigma\}
-    \end{align*}
-
-    Meanwhile, as sets we have $\grel{\sigma'}=\grel\sigma$ and $\grel{\tau'}=\grel\tau\cap (P_{C'}\times P_{B'})$.  So, as subsets of $P_{C'}\times P_A$, we have:
-    \begin{align*}
-      \comp{\grel{\sigma'}}{\grel{\tau'}} & = \{(s, t)\in P_{C'}\times P_A\suchthat \exists u\in P_{B'} \esuchthat (s,u)\in\grel\tau, (u,t)\in\grel\sigma\}
-    \end{align*}
-
-     - in other words, the same thing, but with $P_{B'}$ instead of $P_B$.
-It is clear then that $\comp{\grel{\sigma'}}{\grel{\tau'}}\subset\grel{(\comp\sigma\tau)'}$.
-In the other direction, suppose $(s,t)\in P_{C'}\times P_A$ and that there exists $u\in P_B$ such that $(s,u)\in\grel\tau$ and $(u,t)\in\grel\sigma$.
-But now, since $(u,t)\in\grel\sigma$, we must have $u\in P_{B'}$ by the definition of $P_{B'}$ and therefore $(u,t)\in \comp{\grel{\sigma'}}{\grel{\tau'}}$.
-
-     So far what we have done is show that the morphism $\tau'$ does indeed give us a morphism in $\G/A$ from $\map{(\comp\sigma\tau)'}{C'}{A}$ to $\map{\sigma'}{B'}{A}$.
-We still need to prove that what we have defined respects composition and so gives us a functor $\G/A\to \G/A$.
-
-     This means proving the following statement: suppose $\map{\upsilon}{D}{C}\xrightarrow{\tau}\map{\sigma}{B}{A}$ are morphisms in $\G$.
-This gives us morphisms $\upsilon,\tau$ in $\G/A$ as pictured in the diagram below:
-    \[
-      \begin{tikzcd}
-        D \arrow[r, "\upsilon"] \arrow[drr, "\comp{\sigma}{\comp{\tau}{\upsilon}}"']
-          & C \arrow[r, "\tau"] \arrow[dr, "\comp\sigma\tau"]
-            & B \arrow[d, "\sigma"] \\
-        %
-          &
-            & A
-      \end{tikzcd}
-      \]
-    We have $\cmap{\upsilon'}{D'}{C'}$ given by $\upsilon'=\upsilon\cap P_{D'\implies C'}$ and $\cmap{\tau'}{C'}{B'}$ given by $\tau'=\tau\cap P_{C'\implies B'}$, as before.
-We also have a morphism $\cmap{(\comp\tau\upsilon)'}{D'}{B'}$ given by $(\comp\tau\upsilon)'=(\comp\tau\upsilon)\cap P_{D'\implies B'}$.
-We need to show that $(\comp\tau\upsilon)'=\comp{\tau'}{\upsilon'}$.
-
-    We have $(\comp\tau\upsilon)'=(\comp\tau\upsilon)\cap P_{D'\implies B'}$, so:
-    \begin{align*}
-      \grel{(\comp\tau\upsilon)'} & = \grel{(\comp\tau\upsilon)}\cap(P_{D'}\times P_{B'}) \\
-       & = (\comp{\grel\tau}{\grel\upsilon}) \cap (P_{D'}\times P_{B'}) \\
-       & = \{(s,t)\in P_{D'}\times P_{B'} \suchthat \exists u\in P_C \esuchthat (s,u) \in \grel\upsilon\;, (u,t) \in \grel\tau \}
-    \end{align*}
-
-    Meanwhile, $\grel{\tau '} = \grel\tau \cap P_{D'}$ and $\grel{\upsilon '} = \grel\upsilon \cap P_{B'}$, so
-    \[
-      \comp{\grel{\tau '}}{\grel{\upsilon '}} = \{(s,t) \in P_{D'}\times P_{B'} \suchthat \exists u\in P_{C'} \esuchthat (s,u) \in \grel\upsilon\; (u,t)\in \grel\tau \}
-      \]
-    which is the same thing, but with $P_{C'}$ rather than $P_C$.
-
-    Clearly, $\comp{\grel{\tau '}}{\grel{\upsilon '}} \subseteq \grel{(\comp\tau\upsilon)'}$.
-In the other direction, suppose that $s\in P_{D'}, t\in P_{B'}$ and that $u\in P_C$ such that $(s,u)\in \grel\upsilon,(u,t)\in\grel\tau$.
-It will suffice to show that $u\in P_{C'}$.
-Now note that $C'$ is pullback of $A$ along $\comp\sigma\tau$ and that $B'$ is pullback of $A$ along $\sigma$.
-Therefore:
-    \begin{align*}
-      P_{C'} & = \{\s\vert_C\suchthat \s\in\comp\sigma\tau\} \\
-      P_{B'} & = \{\t\vert_B\suchthat \t\in\sigma\}
-    \end{align*}
-    Since $t\in P_{B'}$, there must be some $\t\in \sigma$ such that $\t\vert_B=t$.
-Put another way, there must be some $v\in P_A$ such that $(t,v)\in\grel\sigma$.
-We have $(u,t)\in\grel\tau$, so therefore $(u,v)\in\grel{\comp\sigma\tau}$, and it follows that $u\in P_{C'}$.
-
-    Therefore, we have that $\grel{\comp{\tau'}{\upsilon'}}=\comp{\grel{\tau '}}{\grel{\upsilon '}} = \grel{(\comp\tau\upsilon)'}$.
-Since the Hyland-Schalk functor is faithful, this means that $\comp{\tau '}{\upsilon '}=(\comp\tau\upsilon)'$.
-
-    This all means that we can define a functor $\cmap{\weak_A}{\G/A}{\G/A}$ by
-    \begin{IEEEeqnarray*}{CCCCC}
-      \map{\sigma}{B}{A} & \quad & \mapsto & \quad & \map{\sigma'}{B'}{A} \\
-      \begin{tikzcd}
-        C \arrow[r, "\tau"] \arrow[dr, "\comp\sigma\tau"']
-         & B \arrow[d, "\sigma"] \\
-        %
-         & A
-      \end{tikzcd}
-      & \quad & \mapsto & \quad &
-      \begin{tikzcd}
-        C' \arrow[r, "\tau'"] \arrow[dr, "\comp{\sigma'}{\tau'}"']
-         & B' \arrow[d, "\sigma'"] \\
-        %
-         & A
-      \end{tikzcd}
-    \end{IEEEeqnarray*}
-
-    We now define the monad structure on $\G/A$.
-The unit transformation $\cmap{\eta_A}{\id_{\G/A}}{\weak_A}$ is given by the weakening morphisms $\cmap{\wk}{B}{B'}$ for each object $\map{\sigma}{B}{A}$; we have already shown that the diagrams
-    \[
-      \begin{tikzcd}
-        B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
-         & B' \arrow[d, "\sigma'"] \\
-        %
-         & A
-      \end{tikzcd}
-      \]
-    commute.  To show that this is indeed a natural transformation, we need to show that if we are given some morphism in $\G/A$
-    \[
-      \begin{tikzcd}
-        C \arrow[r, "\tau"] \arrow[dr, "\comp\sigma\tau"']
-          & B \arrow[d, "\sigma"] \\
-        %
-          & A
-      \end{tikzcd}
-      \]
-    then the following square commutes:
-    \[
-      \begin{tikzcd}
-        C \arrow[r, "\wk"] \arrow[d, "\tau"']
-          & C' \arrow[d, "\tau'"] \\
-        B \arrow[r, "\wk"']
-          & B'
-      \end{tikzcd}
-      \]
-    To show this, we work in $\Rel$ again.  On the one hand, we have:
-    \begin{align*}
-      \comp{\grel{\tau'}}{\grel{\wk}} & = \{(s,t)\in P_C\times P_{B'}\suchthat\exists u\in P_{C'}\esuchthat (s,u)\in\grel\wk\;,(u,t)\in\grel{\tau'}\} \\
-       & = \{(s, t)\in P_{C'}\times P_{B'}\suchthat (s,t)\in\grel{\tau'}\} \\
-       & = \grel{\tau'} = \grel{\tau}\cap(P_{C'}\times P_{B'})
-    \end{align*}
-    On the other hand:
-    \begin{align*}
-      \comp{\grel\wk}{\grel\tau} & = \{(s, t)\in P_C\times P_{B'}\suchthat \exists u\in P_B\esuchthat (s,u)\in \grel\tau, (u, t)\in \grel\wk\} \\
-       & = \grel\tau \cap (P_C\times P_{B'})
-    \end{align*}
-
-    We certainly have $\comp{\grel{\tau'}}{\grel\wk}\subseteq\comp{\grel\wk}{\grel\tau}$.
-In the other direction, suppose that $s\in P_C$ and $t\in P_{B'}$ such that $(s,t)\in\grel\tau$.
-It will suffice to show that $s\in P_{C'}$.
-Indeed, by the definition of $P_{B'}$, there is some $v\in P_A$ such that $(t, v)\in\grel\sigma$.
-Therefore, $(s, v)\in\grel{\comp{\sigma}{\tau}}$, and so $s\in P_{C'}$, as required.
-
-   Before defining the multiplication $\cmap{\mu_A}{\comp{\weak_A}{\weak_A}}{\weak_A}$ in the monad, we look at the identities that this unit transformation $\eta_A$ will have to satisfy.
-If $\map{\sigma}{B}{A}$ is an object of $\G/A$ then we want the diagrams
-   \[
-     \begin{tikzcd}
-       B' \arrow[r, "\wk"] \arrow[dr, equals]
-         & B'' \arrow[d, "\mu_A(B)"] \\
-       %
-         & B'
-     \end{tikzcd}
-     \textrm{ and }
-     \begin{tikzcd}
-       B' \arrow[r, "\wk'"] \arrow[dr, equals]
-         & B'' \arrow[d, "\mu_A(B)"] \\
-       %
-         & B'
-     \end{tikzcd}
-     \]
-   to commute.
-The arrow $\cmap{\wk}{B'}{B''}$ in the first diagram is the weakening arrow obtained from the object $\map{\sigma'}{B'}{A}$ of $\G/A$ using the natural transformation $\eta_A$, while the arrow $\cmap{\wk'}{B'}{B''}$ in the second diagram is obtained by applying the functor $\weak_A$ to the morphism $\cmap{\wk}{B}{B'}$.
-
-   In practice, however, there is no need for this distinction: $B''$ is the same game as $B'$ and the arrows $\wk$ and $\wk'$ are the identity.
-To see this, recall the definitions of $B'$ and $\sigma'$:
-   \begin{align*}
-     P_{B'} & = \{\s\vert_B\suchthat \s\in\sigma\} \\
-     \sigma' & = \sigma\textrm{ (as sets of plays)}
-   \end{align*}
-   Then we should have $P_{B''} = \{\s\vert_{B'}\suchthat \s\in\sigma'\}$, but since $\sigma'$ is the same set as $\sigma$, this is exactly the same as the definition of $P_{B'}$.
-
-   Since $\wk,\wk'$ are identity maps, we observe that we have the strict equality $\comp{\weak_A}{\weak_A}=\weak_A$ and we had better define $\mu_A$ to be the identity transformation.
-This $\mu_A$ is automatically associative and the unit diagrams above hold (since all maps involved are identity maps).
-We end up with an idempotent monad on $\G/A$.
-  \end{proof}
-\end{theorem}
-
-\subsection{Lax weakening morphisms}
-
-We now introduce a lax version of our notion of weakening morphism that is stable under composition with isomorphisms:
-
-\begin{definition}
-  Let $A,B$ be games.
-We say that a morphism $\cmap{\sigma}{B}{A}$ is a \emph{lax weakening} if it is the composition of a weakening morphism and an isomorphism; in other words, if there exists a weakening $B'$ of $B$ and an isomorphism $\cmap{\hat{\sigma}}{B'}{A}$ such that the diagram
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
-        & B' \arrow[d, "\hat\sigma", Sim'] \\
-      %
-        & A
-    \end{tikzcd}
-    \]
-  commutes.
-\end{definition}
-
-\begin{proposition}
-
-  i) If $B'$ is a weakening of $B$, then $\cmap{\wk}{B}{B'}$ is a lax weakening.
-
-  ii) If $\cmap{\sigma}{B}{A}$ is an isomorphism, then $\sigma$ is a lax weakening.
-
-  iii) If $C\xrightarrow{\tau}\map{\sigma}{B}{A}$ are morphisms such that $\sigma$ and $\tau$ are lax weakenings, then $\cmap{\comp\sigma\tau}{C}{A}$ is a lax weakening.
-
-  \begin{proof}
-    (i) and (ii) are both obvious.  For part (iii), note that we have the diagram
-    \[
-      \begin{tikzcd}
-        C \arrow[r, "\wk"] \arrow[dr, "\tau"']
-          & C' \arrow[d, "\hat\tau", Sim']
-            & \\
-        %
-          & B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
-            & B' \arrow[d, "\hat\sigma", Sim'] \\
-        %
-          &
-            & A
-      \end{tikzcd}
-      \]
-    It will suffice to find a weakening $C''$ of $C'$ and an isomorphism $\cmap{\hat{\hat\tau}}{C''}{B'}$ making the following diagram commute:
-    \[
-      \begin{tikzcd}
-        C \arrow[r, "\wk"] \arrow[dr, "\tau"']
-          & C' \arrow[d, "\hat\tau", Sim'] \arrow[r, "\wk"]
-            & C'' \arrow[d, "\hat{\hat\tau}", Sim'] \\
-        %
-          & B \arrow[r, "\wk"] \arrow[dr, "\sigma"']
-            & B' \arrow[d, "\hat\sigma", Sim'] \\
-        %
-          &
-            & A
-      \end{tikzcd}
-      \]
-    Therefore, it will suffice to prove the lemma which follows.
+    We need to show that composition is associative and that $\id_A$ is the identity morphism on $A$.
+For associativity of composition, we claim that if $A\xrightarrow{\sigma}\map{\tau}{B}{C}\xrightarrow{\upsilon}D$ are morphisms then $\comp{(\comp\upsilon\tau)}{\sigma}=S$, where
+    \[
+      S = \{\ss\vert_{A,D}\suchthat \ss\in(M_A\cprd M_B\cprd M_C\cprd M_D)^*,\;\ss\vert_{A,B}\in\sigma,\;\ss\vert_{B,C}\in\tau,\;\ss\vert_{C,D}\in\upsilon\}
+      \]
+
+    Certainly, if $\ss\vert_{A,D}\in S$, then $\ss\vert_{A,D}\in\comp{(\comp\upsilon\tau)}\sigma$: we have $\ss\vert_{B,C,D}\in\tau\|\upsilon$, so $\ss\vert_{B,D}\in\comp\upsilon\tau$.
+Then $\ss\vert_{A,B,D}\in\sigma\|(\comp\upsilon\tau)$, so $\ss\vert_{A,D}\in\comp{(\comp\upsilon\tau)}{\sigma}$.
+
+    Conversely, suppose $s\in\comp{(\comp\upsilon\tau)}{\sigma}$.
+Then there exists $\s\in\sigma\|(\comp\upsilon\tau)$ such that $\s\vert_{A,D}=s$.
+Then the definition of $\comp\upsilon\tau$ tells us that there exists $\t\in\tau\|\upsilon$ such that $\s\vert_{B,D}=\t\vert_{B,D}$.
+We may assume that $\s,\t$ are the minimal covering sequences constructed in Proposition \ref{WellDefinedComposition}.
+
+    Note that we have $\s\in(M_A\cprd M_B\cprd M_D)^*$ and $\t\in(M_B\cprd M_C\cprd M_D)^*$.
+We inductively construct a sequence $\ss\in(M_A\cprd M_B\cprd M_C\cprd M_D)^*$ such that for each inductively-constructed subsequence $\ss'$, we have $\ss'\vert_{A,B,D}\prefix\s$ and $\ss'\vert_{B,C,D}\prefix\t$.
+
+    If $a\in M_A,b\in M_B,c\in M_C$, then we have $\lambda_{A\implies B}(a)=\lambda_{B\implies C}(b)=\lambda_{C\implies D}(c)=P$.
+Therefore, $\s$ and $\t$ must start with a $D$-move, and these $D$-moves must be equal, since $\s\vert_{B,D}=\t\vert_{B,D}$.
+This $D$-move - call it $d$ - is the first move of $\ss$, and it is clear that $d\vert_{A,B,D}\prefix\s$ and $d\vert_{B,C,D}\prefix\t$.
+
+    Now suppose we have constructed a non-empty sequence $\ss'm$ such that $\ss'm\vert_{A,B,D}\prefix\s$ and $\ss'm\vert_{B,C,D}\prefix\t$.
+
+    \begin{description}
+      \item[Case A:] If $m=a\in M_A$, then $\ss'a\vert_{A,B,D}$ is a prefix of $\s$ ending with $a$.
+If $\ss'a\vert_{A,B,D}=\s$, then we set $\ss=\ss'a$ and terminate.
+Otherwise, $\ss'\vert_{A,B,D}ap\prefix\s$ for some move $p$.
+Extend the sequence $\ss'a$ to $\ss'ap$.
+
+      We already have $\ss'ap\vert_{A,B,D}\prefix\s$, so we need to show that $\ss'ap\vert_{B,C,D}=\ss'p\vert_{B,C,D}\prefix\t$.
+If $p\in M_A$, then this is automatic by induction, so suppose that $p\in M_B\cprd M_D$.
+If $\lambda_{A\implies B}(a)=P$, then $p\in M_A$ by the proof of Proposition \ref{WellDefinedComposition}, so we may assume that $\lambda_{A\implies B}(a)=O$.
+    \end{description}
+
   \end{proof}
@@
 
-\begin{lemma}[Lifting of weakenings along isomorphisms]
-  Let $B,C$ be games and let $\cmap{\tau}{C}{B}$ be an isomorphism.
-Let $B'$ be a weakening of $B$.
-Then there is a weakening $C'$ of $C$ and an isomorphism $\cmap{\tau'}{C'}{B'}$ such that the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      C \arrow[r, "\wk"] \arrow[d, "\tau"', Sim]
-        & C' \arrow[d, "\tau'"', Sim] \\
-      B \arrow[r, "\wk"'] 
-        & B'
-    \end{tikzcd}
-    \]
-\end{lemma}
-
-We shall give two proofs of this lemma - one direct proof using the Hyland-Schalk functor and one proof using the idempotent monad structure described in the previous section.
-
-\begin{proof}[First proof]
-  We know that $\cmap{\tau}{C}{B}$ is an isomorphism; therefore, its image $\grel\tau\subset P_C\times P_B$ under the Hyland-Schalk functor is an isomorphism in $\Rel$.
-It is well-known (and easy to show) that the isomorphisms in $\Rel$ are precisely those relations that are the graphs of bijective functions.
-Therefore, we have a bijection $\cmap{\grel\tau}{P_C}{P_B}$ with the property that
-
-  i) For all $s\in P_C$ there exists a $P$-play $\s\in\tau$ such that $\s\vert_C=s$ and $\s\vert_B=\grel\tau(s)$
-
-  ii) For all $P$-plays $\s\in\tau$, $\s\vert_B=\grel\tau\left(\s\vert_C\right)$.
-
-  Let $P_{C'}=\grel\tau\inv(P_{B'})\subseteq P_C$.
-We claim that $P_{C'}$ is prefix-closed.
-Let $s\in P_{C'}$ and let $t\prefix s$.
-By the definition of $P_{C'}$, $\tau(s)\in P_{B'}$.
-Since $P_{B'}$ is prefix-closed, it will suffice to show that $\grel\tau(t)\prefix\grel\tau(s)$.
-
-  By (i), we know that there exists a $P$-play $\s\in\tau$ such that $\s\vert_C = s$ and $\s\vert_B = \grel\tau(s)$.
-Since $t\prefix s$, there is some prefix $\t\prefix\s$ such that $\t\vert_C = t$.
-Then, by (ii), we must have $\grel\tau(t)=\t\vert_B\prefix\s\vert_B$.
-
-  Therefore, $C'=(M_C,\lambda_C, P_{C'})$ is a well-formed game.  We claim that it is a weakening of $C$.
-
-  Indeed, suppose $s\in P_{C'}$ is an $O$-play and that $sc$ is a $P$-reply in $P_C$.  We need to show that $sc\in P_{C'}$.
-
-  By the definition of $P_{C'}$, we know that $\grel\tau(s)\in P_{B'}$.
-By (i) we know that there exists some $P$-play $\s\in\tau$ such that $\s\vert_C=s$ and $\s\vert_B=\grel\tau(s)$; since $\s$ is a $P$-play, we can deduce that $s$ and $\grel\tau(s)$ have the same sign, and so $\grel\tau(s)$ is an $O$-play in $P_{B'}$.
-Examining (i) and (ii) above, we can see that $\grel\tau(sc)=\grel\tau(s)b$ for some $b\in P_B$.
-Therefore, since $B'$ is a weakening of $B$, we have $\grel\tau(sc)\in P_{B'}$ and so $sc\in P_{C'}$ as desired.
-
-  Lastly, we define $\tau'$ to be given by the set $\tau \cap P_{C\implies B}$, and we claim that the diagram
-  \[
-    \begin{tikzcd}
-      C \arrow[r, "\wk"] \arrow[d, "\tau"', Sim]
-        & C' \arrow[d, "\tau'"'] \\
-      B \arrow[r, "\wk"'] 
-        & B'
-    \end{tikzcd}
-    \]
-  commutes.  This is most easily checked by applying the faithful functor
-  \[
-    \G \xrightarrow{\F} \Rel \xrightarrow{\dagger} \oppcat{\Rel}
-    \]
-  where $\cmap{\dagger}{\Rel}{\oppcat{\Rel}}$ is the identity on objects and flips a relation $R\subset A\times B$ to give a relation $R^\dagger\subset B\times A$.
-If $\cmap{\wk}{A}{A'}$ is a weakening morphism in $\G$ then its image $\grel\wk$ under this functor is the graph of the inclusion $P_{A'}\hookrightarrow P_A$.
-Meanwhile, the image of $\tau$ under this functor is the graph of the function $\cmap{\grel\tau\inv}{P_B}{P_C}$.
-By the definition of $P_{C'}$, the image of $\tau'$ under this functor is the graph of the function $\cmap{\grel\tau\inv\vert_{P_{B'}}}{P_{B'}}{P_{C'}}$.
-It is then easy to check that the resulting diagram commutes in $\Rel$:
-  \[
-    \begin{tikzcd}
-      P_C
-        & P_{C'} \arrow[l, hook', "\grel\wk"'] \\
-      P_B \arrow[u, "\grel\tau\inv"]
-        & P_{B'} \arrow[u, "\grel\tau\inv\vert_{P_{B'}}"'] \arrow[l, hook', "\grel\wk"]
-    \end{tikzcd}
-    \]
-
-  The last thing that we need to do is to check that $\tau'$ is an isomorphism.
-If we apply exactly the same argument to $\map{\wk}{C}{C'}$ and the isomorphism $\cmap{\tau\inv}{B}{C}$ then we get a weakening $B''$ of $B$ and an isomorphism $\cmap{(\tau\inv)'}{B''}{C'}$ making the following diagram commute:
-  \[
-    \begin{tikzcd}
-      B \arrow[r, "\wk"] \arrow[d, "\tau\inv"', Sim]
-        & B'' \arrow[d, "(\tau\inv)'"] \\
-      C \arrow[r, "\wk"']
-        & C'
-    \end{tikzcd}
-    \]
-  Now note that $P_{B''}$ is defined to be $\grel\tau(P_{C'})$.  Since $\grel\tau$ is a bijection and $P_C$ was defined to be $\grel\tau\inv(P_{B'})$, we get that $B''=B'$.  We now get:
-  \begin{align*}
-    B \xrightarrow{\wk} B' \xrightarrow{(\tau\inv)'} C' \xrightarrow{\tau'} B'
-    & = B \xrightarrow{\tau\inv} C \xrightarrow{\wk} C' \xrightarrow{\tau'} B' \\
-    & = B \xrightarrow{\tau\inv} C \xrightarrow{\tau} B \xrightarrow{\wk} B' \\
-    & = B \xrightarrow{\wk} B'
-  \end{align*}
-  Since $\wk$ is an epimorphism, it follows that $\comp{\tau'}{(\tau\inv)'}=\id_{B'}$.  An identical argument shows that $\comp{(\tau\inv)'}{\tau'}=\id_{C'}$.  So $\tau'$ is an isomorphism.
-\end{proof}
-
-\begin{proof}[Second proof]
-  We start off with the diagram
-  \[
-    \begin{tikzcd}
-      C \arrow[d, "\tau"', Sim]
-        & \\
-      B \arrow[r, "\wk"]
-        & B'
-    \end{tikzcd}
-    \]
-
-  We use the monad on the category $\G/B'$.  Let $C'$ be the pullback of $B'$ along the morphism $\cmap{\comp\wk\tau}{C}{B'}$.  This gives us the diagram
-  \[
-    \begin{tikzcd}
-      C \arrow[d, "\tau"', Sim] \arrow[r, "\wk"]
-        & C' \arrow[d, "(\comp\wk\tau)'"] \\
-      B \arrow[r, "\wk"]
-        & B'
-    \end{tikzcd}
-    \]
-  It remains to show that $(\comp\wk\tau)'$ is an isomorphism.
-
-  To show this, let us rearrange the original diagram a bit to make the monadic structure explicit:
-  \[
-    \begin{tikzcd}
-      C \arrow[r, "\tau", Sim'] \arrow[dr, "\comp\wk\tau"']
-        & B \arrow[d, "\wk"] \\
-      %
-        & B'
-    \end{tikzcd}
-    \]
-  When we apply the functor $\weak_{B'}$ to this diagram, we get
-  \[
-    \begin{tikzcd}
-      C' \arrow[r, "\tau'"] \arrow[dr, "(\comp\wk\tau)'"']
-        & B' \arrow[d, "\wk'"] \\
-      %
-        & B'
-    \end{tikzcd}
-    \]
-  By definition, $\cmap{\wk=\eta_B}{B}{B'}$, and so $\wk'=(\eta_B)'$.
-Since our monad is idempotent, $(\eta_B)'$ is an isomorphism.
-$\tau'$ is an isomorphism by functoriality and therefore $(\comp\wk\tau)'$ is an isomorphism, as desired.
-\end{proof}
-
 \bibliographystyle{alpha}

### 2016-10-11 round-corner/round-corner.tex
Started writing paper.

\documentclass[11pt]{article}

\input{../common/preamble}

\title{Rounding off a corner}

\author{John Gowers}

\begin{document}

\maketitle

\begin{abstract}
  In \cite{laird02}, Laird introduces the concept of a \emph{sequoidal category}, a certain extension of a monoidal category and gives an example constructed using game semantics.  As noted in \cite{martinsthesis}, cofree commutative comonoids can be constructed coalgebraically in any sequoidal category subject to certain extra hypotheses.  In the first part of this note, we review the coalgebraic construction of cofree commutative comonoids in sequoidal categories.  In the second part, we shall show that the extra hypotheses are necessary as well as sufficient and we shall use transfinite game semantics to construct a sequoidal category in which these hypotheses do not hold.
\end{abstract}

\section{Sequoidal categories}

\subsection{Game semantics and the sequoidal operator}

We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.  A game will be given by a tuple
\[
  A = (M_A, \lambda_A, b_A, P_A)
  \]
where
\begin{itemize}
  \item $M_A$ is a set of moves.
  \item $\lambda_A\from M_A\to\OP$ is a function designating each move as either an \emph{$O$-move} or a \emph{$P$-move}.
  \item $b_A\in\OP$ is a choice of starting player.
  \item $P_A\subset M_A^*$ is a prefix-closed set of alternating plays - so if $sab\in P_A$ then $\lambda_A(a)=\neg\lambda_A(b)$.
\end{itemize}

We call $sa\in P_A$ a \emph{$P$-position} if $a$ is a $P$-move and an \emph{$O$-position} if $a$ is an $O$-move.

Note that plays in $P_A$ do not have to start with a $b_A$-move, so there might be some positions in $P_A$ that can never actually arise when playing the game.

A \emph{strategy} for player $P$ for a game $A$ is identified with the set of positions that may arise when playing according to that strategy.  Namely, it is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the three conditions:
\begin{description}
  \item[(s$\emptyplay$)] If $a\in\sigma$ is a $1$-move play, then $\lambda_A(a)=b_A$.
  \item[(sO)] If $s\in\sigma$ is a $P$-position and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.
  \item[(sP)] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
\end{description}

We shall now concentrate on

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2016-10-27 france-talk/francais.tex
Added abstracts for talks in France.

\documentclass[11pt]{article}

\usepackage[french]{babel}

\input{../common/preamble}

\title{Les jeux transfinis et l'exponentialle sequo\"{i}dale}

\author{John Gowers}

\begin{document}

\maketitle

\begin{abstract}
  Laird \cite{laird02} introduit la notion d'une \emph{cat\'{e}gorie sequo\"{i}dale} -- un augmentation d'une cat\'{e}gorie mono\"{i}dale par un nouveau connecteur $\sequoid$ (le \emph{sequo\"{i}de}) dont il y a un mod\`{e}le naturel construit par utilisation de la s\'{e}mantique des jeux.  On peut utiliser le connecteur sequo\"{i}dale dansce mod\`{e}le pour pr\'{e}senter le connecteur exponentiel $A\mapsto\oc A$ de \cite{hyland1997games} et \cite{ajmPcf} comme coalg\`{e}bre finale.  En supposant des autres hypoth\`{e}ses, on peut d\'{e}montrer que cette coalg\`{e}bre finale $\oc A$
\end{abstract}

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2016-10-27 round-corner/round-corner.tex
Added abstracts for talks in France.

@@
 \begin{abstract}
-  In \cite{laird02}, Laird introduces the concept of a \emph{sequoidal category}, a certain extension of a monoidal category and gives an example constructed using game semantics.
+  In \cite{laird02}, Laird introduces the concept of a \emph{sequoidal category}, a certain extension of a monoidal category, and gives an example constructed using game semantics.
 As noted in \cite{martinsthesis}, cofree commutative comonoids can be constructed coalgebraically in any sequoidal category subject to certain extra hypotheses.

### 2016-10-27 round-corner/round-corner.tex
Made new changes to the new paper.

--- 2016-10-11 round-corner/round-corner.tex
@@
   \item $b_A\in\OP$ is a choice of starting player.
-  \item $P_A\subset M_A^*$ is a prefix-closed set of alternating plays - so if $sab\in P_A$ then $\lambda_A(a)=\neg\lambda_A(b)$.
+  \item $P_A\subset M_A^*$ is a prefix-closed set of alternating plays (so if $sab\in P_A$ then $\lambda_A(a)=\neg\lambda_A(b)$) such that if $as\in P_A$ then $\lambda_A(a)=b_A$.
 \end{itemize}
@@
 
-Note that plays in $P_A$ do not have to start with a $b_A$-move, so there might be some positions in $P_A$ that can never actually arise when playing the game.
-
 A \emph{strategy} for player $P$ for a game $A$ is identified with the set of positions that may arise when playing according to that strategy.
-Namely, it is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the three conditions:
+Namely, it is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the two conditions:
 \begin{description}
-  \item[(s$\emptyplay$)] If $a\in\sigma$ is a $1$-move play, then $\lambda_A(a)=b_A$.
   \item[(sO)] If $s\in\sigma$ is a $P$-position and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.
@@
 
-We shall now concentrate on
+We shall now concentrate on games $A$ for which $b_A=O$, called \emph{negative games}.  We shall informally describe the standard connectives on negative games:
+
+\begin{description}
+  \item[Product] If $A$ and $B$ are negative games then the \emph{product} $A\times B$ is the game given by placing the game trees for $A$ and $B$ side by side: that is, player $O$ may play his first move either in $A$ or in $B$.
+Thereafter, play continues in the game that player $O$ has chosen.
+  \item[Tensor Product] The tensor product $A\tensor B$ is also played by playing the games $A$ and $B$ in parallel, but this time player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
+  \item[Linear implication] The implication $A\implies B$ is played by playing the game $B$ in parallel with the \emph{negation} of $A$ - that is, the game formed by switching the roles of players $P$ and $O$ in $A$.
+Since play in the negation of $A$ starts with a $P$-move, player $O$ is forced to make his first move in the game $B$.
+Thereafter, player $P$ may switch games whenever it is her turn.
+\end{description}
+
+If $A,B,C$ are negative games, $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, then we may form a strategy $\comp\tau\sigma$ for $A\implies C$ by setting
+\[
+  \sigma\|\tau = \{\s\in (M_A\cprd M_B\cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;s\vert_{B,C}\in\tau\}
+  \]
+and then defining
+\[
+  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\comp\tau\sigma\}
+  \]
+It is well known (see, for example, \cite{abramskyjagadeesangames}) that $\comp\tau\sigma$ is indeed a strategy for $A\implies C$ and that this form of composition is associative and has an identity.
+It is also well known that the resulting category $\G$ of games and strategies has products given by the operator $\times$ and a symmetric monoidal closed structure given by the operations $\tensor$ and $\implies$.
+
+We turn now to the non-standard \emph{sequoid} connective $\sequoid$.
+If $A$ and $B$ are negative games, then the sequoid $A\sequoid B$ is similar to the tensor product $A\tensor B$, but with the restriction that player $O$'s first move must take place in the game $A$.
+We observe immediately that we have structural isomorphisms
+\begin{gather*}
+  \dist\from A\tensor B\toisom (A\sequoid B)\times(B\sequoid A)\\
+  \dec\from(A\times B)\sequoid C\toisom (A\sequoid C)\times (B\sequoid C)\\
+  \passoc\from (A\sequoid B)\sequoid C\toisom A\sequoid (B\tensor C)
+\end{gather*}
+
+One further question to ask is: does the sequoid operator give rise to a functor $\blank\sequoid\blank\from\G\times\G\to\G$, as the tensor operator does?
+The answer is no: indeed, let $A,B,C,D$ be negative games, let $\sigma$ be a strategy for $A\implies C$ and let $\tau$ be a strategy for $B\implies D$.
+Our aim is to construct a natural strategy $\sigma\sequoid\tau$ for $(A\sequoid B)\implies (C\sequoid D)$.
+There is an obvious way to try and do this: player $P$ should play according to the strategy $\sigma$ whenever player $O$'s last move was in $A$ or $C$, and according to $\tau$ whenever player $O$'s last move was in $B$ or $D$.
+
+We show that this does not in general give us a strategy for $(A\sequoid B)\implies (C\sequoid D)$.
+Suppose that $\sigma$ is such that player $P$'s response to some opening move in $C$ is another move in $C$ and suppose that $\tau$ is such that player $P$'s response to some opening move in $D$ is a move in $B$ (for example, $\tau$ is a copycat strategy).
+Then we end up with the following sequence of events in the game $(A\sequoid B)\implies(C\sequoid D)$  :
+\begin{enumerate}
+  \item Player $O$ starts with a move in $C$ (as he must).
+  \item Player $P$ responds according to $\sigma$ with another move in $C$.
+  \item Player $O$ decides to switch games and play a move in $D$.
+  \item Player $P$ responds according to $\tau$ with a move in $B$.
+\end{enumerate}
+
+But now player $P$'s last move is not a legal move in $(A\sequoid B)\implies(C\sequoid D)$, since no moves have been played in $A$ yet.
+
+We get round this problem by requiring that the strategy $\sigma$ be \emph{strict} -- that is, whatever player $O$'s opening move in $C$ is, player $P$'s reply must be a move in $A$.
+
+\begin{definition}
+  Let $N,L$ be negative games and let $\sigma$ be a strategy for $N\implies L$.  We say that $\sigma$ is \emph{strict} if player $P$'s reply to an opening move in $L$ is always a move in $N$.  
+\end{definition}
+
+Identity strategies are strict and the composition of two strict strategies is strict, so we get a full-on-objects subcategory $\G_s$ of $\G$ where the morphisms are strict strategies.
+Then the sequoid operator gives rise to a functor:
+\[
+  \blank\sequoid\blank\from \G_s\times\G\to\G_s
+  \]
+
+\subsection{Sequoidal categories}
+
+We now have the motivation required to give the definition of a \emph{sequoidal category} from \cite{laird02}.
+
+\begin{definition}
+  A \emph{sequoidal category} consists of the following data:
+  \begin{itemize}
+    \item A symmetric monoidal category $\C$ with monoidal product $\tensor$ and tensor unit $I$, associators $\assoc_{A,B,C}\from(A\tensor B)\tensor C\toisom A\tensor(B\tensor C)$, unitors $\runit_A\from A\tensor I\toisom A$ and $\lunit_A\from I\tensor A\toisom A$ and braiding $\sym_{A,B}\from A\tensor B\to B\tensor A$.
+    \item A category $\C_s$
+    \item A right monoidal category action of $\C$ on the category $\C_s$.  That is, a functor
+      \[
+        \blank\sequoid\blank\from\C_s\times\C\to\C_s
+        \]
+      together natural isomorphisms
+      \[
+        \passoc_{A,B,C}\from A\sequoid(B\tensor C)\to (A\sequoid B)\sequoid C
+        \]
+      and
+      \[
+        \run_A\from A\sequoid I\toisom A
+        \]
+      subject to the following coherence conditions:
+      \begin{longdiagram}
+        \begin{tikzcd}
+          A\sequoid(B\tensor(C\tensor D)) \arrow[r, "\passoc_{A,B,C\tensor D}" yshift=0.3em] \arrow[d, "\id_A\sequoid \assoc_{B,C,D}"']
+            & (A \sequoid B) \sequoid (C\tensor D) \arrow[r, "\passoc_{A\sequoid B,C,D}" yshift=0.3em]
+              & ((A\sequoid B)\sequoid C) \sequoid D \\
+          A\sequoid((B\tensor C)\tensor D) \arrow[r, "\passoc_{A,B\tensor C,D}"' yshift=-0.3em]
+            & (A\sequoid (B\tensor C)) \sequoid D \arrow[ur, "\passoc_{A,B,C}\sequoid\id_D"']
+              &
+        \end{tikzcd}
+      \end{longdiagram}
+      \begin{longdiagram}
+        \begin{tikzcd}
+          A \sequoid (I\tensor B) \arrow[r, "\passoc_{A,I,B}" yshift=0.3em] \arrow[d, "\id_A\sequoid\lunit_B"']
+            & (A\sequoid I)\sequoid B \arrow[dl, "\run_A"] \\
+          A \sequoid B
+            &
+        \end{tikzcd}
+        \quad
+        \begin{tikzcd}
+          A \sequoid (B\tensor I) \arrow[r, "\passoc_{A,B,I}" yshift=0.3em] \arrow[d, "\id_A\sequoid\runit_B"']
+            & (A\sequoid B) \sequoid I \arrow[dl, "\run_{A\sequoid B}"] \\
+          A\sequoid B
+            &
+        \end{tikzcd}
+      \end{longdiagram}
+
+      \item A functor $J\from \C_s\to\C$ (in the games example, this is the inclusion functor $\G_s\to\G$)
+
+      \item A natural transformation $\wk_{A,B}\from J(A)\tensor B\to J(A\sequoid B)$ satisfying the coherence conditions:
+      \begin{longdiagram}
+        \begin{tikzcd}
+          A \tensor I \arrow[r, "\runit_A" yshift=0.3em] \arrow[d, "\wk_{A,I}"']
+            & A \\
+          A \sequoid I \arrow[ur, "J(\run_A)"']
+            &
+        \end{tikzcd}
+        \quad
+        \begin{tikzcd}
+          (A \tensor B) \tensor C \arrow[r, "\wk_{A,B}\tensor\id_C" yshift=0.3em] \arrow[d, "\assoc_{A,B,C}"']
+            & (A \sequoid B) \tensor C \arrow[r, "\wk_{A\sequoid B, C}" yshift=0.3em]
+              & (A \sequoid B) \sequoid C\\
+          A \tensor (B \tensor C) \arrow[r, "\wk_{A,B\tensor C}"']
+            & A \sequoid (B \tensor C) \arrow[ur, "J(\passoc_{A,B,C})"']
+              &
+        \end{tikzcd}
+      \end{longdiagram}
+  \end{itemize}
+\end{definition}
+
+Our category of games satisfies further conditions:
+
+\begin{definition}
+  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing the monoidal isomorphisms and the morphisms $\wk_{A,B}$, $J$ is the inclusion functor and $J$ reflects isomorphisms.
+
+  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
+In that case, we say that $\C$ is \emph{decomposable} if the natural transformations
+  \begin{gather*}
+    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
+    \dec^0 \from I \to 1
+  \end{gather*}
+  are isomorphisms and we say that $\C$ is \emph{distributive} if the natural transformations
+  \begin{gather*}
+    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
+    \dist_{A,0}\from 1\sequoid A\to 1
+  \end{gather*}
+  are isomorphisms.
+\end{definition}
+
+We have one further piece of structure available to us:
+
+\begin{definition}
+  Let $\C=(\C,\C_s,J,\wk)$ be an inclusive sequoidal category.
+We say that $\C$ is a \emph{sequoidal closed category} if $\C$ is monoidal closed (with internal hom $\implies$ and currying $\Lambda_{A,B,C}\from \C(A\tensor B,C)\toisom \C(A,B\implies C)$) and if the map $f\mapsto\Lambda(\comp{f}{\wk})$ gives rise to a natural transformation
+  \[
+    \Lambda_{A,B,C,s}\from \C_s(A\sequoid B, C) \to \C_s(A,B\implies C)
+    \]
+\end{definition}
+
+It can be shown (see for example \cite{martinsthesis}) that our category $\G$ of games has all this structure.
+
+\begin{theorem}
+  If $A,B$ are games, let $J$ be the inclusion functor $\G_s\to\G$ and let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
+  \[
+    (\G,\G_s,J,\wk)
+    \]
+  is an inclusive, Cartesian, decomposable, distributive sequoidal closed category.
+\end{theorem}
 

### 2016-10-27 france-talk/english.tex

\documentclass[11pt]{article}

\input{../common/preamble}

\title{Transfinite games and the sequoidal exponential}

\author{John Gowers}

\begin{document}

\maketitle

\begin{abstract}
  Laird \cite{laird02} introduces the concept of a \emph{sequoidal category}, an augmentation of a monoidal category by a new operation $\sequoid$ (the sequoid) that has a natural model constructed using game semantics.  The sequoid operator $\sequoid$ in this game-semantic model allows us to present the exponential connective $A\mapsto\oc A$ of \cite{hyland1997games} and \cite{ajmPcf} as a final coalgebra.  Under further assumptions, one can prove coalgebraically that this final coalgebra $\oc A$ is the carrier for a cofree commutative comonoid on $A$, and is therefore a suitable model for the exponential from linear logic.  The authors of \cite{martinsthesis} note that it does not seem to be possible to construct cofree commutative comonoids using the sequoidal category axioms alone.  I shall show that this is indeed impossible by presenting a sequoidal category of transfinite games in which the final coalgebra $\oc A$ admits no comonoid structure.  I shall discuss ways in which this transfinite model can inform our study of the usual finitary model.
\end{abstract}

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2017-02-08 france-talk/francais.tex

@@
 \usepackage[french]{babel}
+\usepackage[T1]{fontenc}
 
 \input{../common/preamble}
+
+\renewcommand{\OP}{\{O, J\}}
+\newcommand{\OJ}{\OP}
 
@@
   Laird \cite{laird02} introduit la notion d'une \emph{cat\'{e}gorie sequo\"{i}dale} -- un augmentation d'une cat\'{e}gorie mono\"{i}dale par un nouveau connecteur $\sequoid$ (le \emph{sequo\"{i}de}) dont il y a un mod\`{e}le naturel construit par utilisation de la s\'{e}mantique des jeux.
-On peut utiliser le connecteur sequo\"{i}dale dansce mod\`{e}le pour pr\'{e}senter le connecteur exponentiel $A\mapsto\oc A$ de \cite{hyland1997games} et \cite{ajmPcf} comme coalg\`{e}bre finale.
-En supposant des autres hypoth\`{e}ses, on peut d\'{e}montrer que cette coalg\`{e}bre finale $\oc A$
+On peut utiliser le connecteur sequo\"{i}dal dans ce mod\`{e}le pour pr\'{e}senter le connecteur exponentiel $A\mapsto\oc A$ de \cite{hyland1997games} et \cite{ajmPcf} comme coalg\`{e}bre finale.
+En supposant des autres hypoth\`{e}ses, on peut d\'{e}montrer que cette coalg\`{e}bre finale $\oc A$ a la structure d'un comono\"{i}de commutatif libre sur $A$, et est donc un mod\`{e}le appropri\'{e} pour le connecteur exponential de la logique lin\'{e}aire.
+Les auteurs de \cite{martinsthesis} r\'{e}marquent que il ne semble pas possible de construire les comono\"{i}des commutatifs libres en n'utilisant que la th\'{e}orie axiomatique des cat\'{e}gories sequo\"{i}dales.
+Je montrerai que ceci est en effet impossible, par pr\'{e}senter une cat\'{e}gorie sequo\"{i}dale dans laquelle la coalg\`{e}bre finale $\oc A$ n'admet pas la structure d'un comono\"{i}de commutatif libre.
+Je parlerai des fa\c{c}ons dont ce mod\`{e}le transfini peut inspirer l'\'{e}tude du mod\`{e}le finitaire habituel.
 \end{abstract}
+
+\section{La s\'{e}mantique des jeux pour la logique lin\'{e}aire}
+
+Je commence par examiner la s\'{e}mantique des jeux.
+Nos jeux seront jou\'{e}s par deux joueurs - la Joueuse ($J$) et l'Opposant ($O$).
+Les jeux qui nous consid\'{e}rons seront tr\`{e}s g\'{e}n\'{e}rals: chaque joueur a un ensemble de coups et les deux joueurs prennent des tours en construisant une partie -- c'est \`{a} dire, une s\'{e}quence des coups -- selon les r\`{e}gles du jeu qui disent quels coups sont authoris\'{e}s dans une position particuli\`{e}re, et quel joueur a gagn\'{e} au fin du jeu.
+Normalement, l'Opposant fait le premier coup.
+
+On peut aussi faire la d\'{e}finition d'une strat\'{e}gie pour un jeu, pour la Joueuse ou pour l'Opposant.
+
+Nous construisons les nouveaux jeux des vieux selons les \emph{connecteurs} de la s\'{e}mantique des jeux: le produit tensoriel $\tensor$ et l'implication lin\'{e}aire $\implies$.
+Le jeu $A\tensor B$ se compose d'une copie du jeu $A$ et une copie du jeu $B$, qui sont jou\'{e}s en parall\`{e}le.
+L'Opposant peut choisir de jouer dans l'un jeu ou dans l'autre, mais il faut que la Joueuse fasse son coup dans le jeu dans lequel l'Opposant vient de jouer.
+
+Le jeu $A\implies B$ se compose aussi d'une copie du jeu $A$ et d'une copie du jeu $B$, qui sont jou\'{e}s en parall\`{e}le, sauf que dans le jeu $A$, les joueurs jouent les r\^{o}les opposites -- c'est \`{a} dire, l'Opposant joue comme joueuse et la joueuse joue comme Opposant.
+Cette fois, c'est la Joueuse qui peut choisir dans quel jeu elle veut jouer, et l'Opposant qui doit suivre dans le m\^{e}me jeu.
+
+On peut maintenant construire une cat\'{e}gorie dont les objets sont les jeux et dont les fl\`{e}ches entre les jeux $A$ et $B$ sont les strat\'{e}gies pour la Joueuse pour le jeu $A\implies B$.
+Il y a un notion naturel de composer une strat\'{e}gie pour $A\implies B$ avec une strat\'{e}gie pour $B\implies C$, et cette composition est associative.
+
+Ensuite, le connecteur tensoriel nous donne la structure d'une categorie monoi\"{i}dale et le connecteur implicative nous donne la structure d'une categorie mono\"{i}dale ferm\'{e}e.
+
+On appel cette cat\'{e}gorie $\G$.
+
+Soit $A,B$ des jeux et soit $\sigma$ une strat\'{e}gie pour $A\implies B$.
+On dit que $\sigma$ est une strat\'{e}gie \emph{stricte} si la Joueuse, apr\`{e}s le premier coup de l'Opposant dans $B$, doit faire son premier coup dans $A$.
+Alors, si on compose deux strat\'{e}gies strictes, la composition est stricte aussi, et \c{c}a nous donne une autre cat\'{e}gorie $\G_s$.
+
+\section{L'exponentielle de Hyland}
+
+Je commence par examiner la s\'{e}mantique des jeux pour le connecteur exponentiel dans la logique lin\'{e}aire.
+Il y a plusieurs versions de l'exponentielle dans la s\'{e}mantique des jeux, mais je vais me concentrer sur l'exponentielle de Hyland et de AJM.
+\`{A} partir d'un jeu $A$, on forme le jeu $\oc A$ qui se compose d'une infinit\'{e} de copies de $A$ - $A_0, A_1, A_2, \dots$, jou\'{e}es en parall\`{e}le, et il est inderdit de jouer dans le jeu $A_{n+1}$ si personne n'a pas encore jou\'{e} dans le jeu $A_n$.
+
+Pour pr\'{e}senter ce jeu comme mod\`{e}le pour l'exponentielle, il suffit de montre qu'il a la structure du comono\"{i}de commutatif libre sur $A$.  Le comultiplication
+\[
+  \oc A \to \oc A \tensor \oc A
+  \]
+est la strat\'{e}gie \flqq{}copycat\frqq{} dans laquelle la Joueuse ouvre une copie de $A$ sur la gauche pour chaque copie de $A$ qui l'Opposant ouvre sur la gauche.
+\`{A} la suite de la restriction sur l'ordre dans lequel on peut ouvrir les copies de $A$, il n'y a qu'une copie de $A$ sur la gauche que la Joueuse peut choisir ; donc, ce comultiplication est associatif.
+
+Certaines recherches par Melli\`{e}s, Tabareau et Tasson \cite{MelliesCofCommCom} font construire cette exponentielle, dans un contexte plus g\'{e}n\'{e}ral th\'{e}oriques de cat\'{e}gorie, comme limite du syst\`{e}me projectif :
+\[
+  1 \leftarrow A \leftarrow \bigotimes_2^{\sim} A \leftarrow \bigotimes_3^{\sim} A \leftarrow \cdots
+  \]
+o\`{u} 
+\[
+  \bigotimes_n^\sim A
+  \]
+est le produit tensoriel symmetris\'{e} -- le co\'{e}galiseur de l'action du groupe $S_n$ sur le produit tensoriel iter\'{e}
+\[
+  \underbrace{A \tensor \cdots \tensor A}_{n}
+  \]
+
+\section{Le connecteur s\'{e}quo\"{i}dal}
+
+Je vais examiner une autre approche, lanc\'{e}e par Jim Laird \cite{laird02}.
+Au lieu de prendre le co\'{e}galiseur du produit tensoriel iter\'{e} sous l'action de $S_n$, on introduit un nouveau connecteur non-standard -- le connecteur \emph{s\'{e}quo\"{i}dal} $\sequoid$.
+Ce connecteur
+\[
+  A \sequoid B \quad \textit{\flqq{}$A$ s\'{e}quo\"{i}de $B$\frqq{}}
+  \]
+fonctionne presque exactement comme le produit tensoriel, sauf que l'Opposant doit jouer le premier coup dans le jeu $A$ sur la gauche.
+Soit $\G$ la cat\'{e}gorie des jeux.
+Le connecteur s\'{e}quo\"{i}dale donne naissance pas \`{a} un foncteur
+\[
+  \G\times\G\to\G
+  \]
+mais \`{a} un foncteur
+\[
+  \G_s\times\G\to\G_s
+  \]
+Ici, $\G_s$ est la cat\'{e}gorie dont les objets sont les jeux et dont les fl\`{e}ches sont les strat\'{e}gies \emph{strictes}
+\[
+  \sigma\from A\implies B
+  \]
+dans lesquelles la Joueuse, apr\`{e}s le premier coup de l'Opposant dans $B$, doit faire son premier coup dans $A$.
+
+Maintenant, soit $A$ un jeu fixe.  On arrive \`{a} un endofoncteur
+\[
+  A\sequoid\blank \from \G \to \G
+  \]
+et on r\'{e}cup\`{e}re l'exponentielle $\oc A$ comme coalg\`{e}bre finale de cet endofoncteur.
+
+\section{Les cat\'{e}gories s\'{e}quo\"{i}dales}
+
+On veut g\'{e}n\'{e}raliser tout \c{c}a, en pr\'{e}sentant la d\'{e}finition d'une cat\'{e}gorie s\'{e}quo\"{i}dale, dont la cat\'{e}gorie des jeux est le prototype.  On commence avec l'identit\'{e}
+\[
+  (A \sequoid B) \sequoid C \cong A \sequoid (B \tensor C)
+  \]
+qui vaut dans la cat\'{e}gorie des jeux.  En fait, c'est un action de la cat\'{e}gorie mono\"{i}dale $\G$ sur la cat\'{e}gorie $\G_s$.
+
+On pr\'{e}sente la d\'{e}finition : une cat\'{e}gorie s\'{e}quo\"{i}dale se compose d'une cat\'{e}gorie mono\"{i}dale $(\C, \tensor, I)$, d'une cat\'{e}gorie $\C_s$ et d'une action \`{a} droite de $\C_s$ sur $\C$:
+\[
+  \passoc \from (A\sequoid B)\sequoid C \to A\sequoid(B\tensor C)
+  \]
+On a besoin aussi d'un foncteur
+\[
+  J \from \C_s \to \C
+  \]
+(dans la cat\'{e}orie de jeux, c'est l'injection canonique.  Enfin, on a besoin d'une transformation naturelle
+\[
+  \wk \from J(A)\tensor B \to J(A\sequoid B)
+  \]
+qui satisfait une condition suppl\'{e}mentaire de compatibilit\'{e}.
+
+\`{A} partir de maintenant, nous consid\'{e}rons que $C_s$ est une sous-cat\'{e}gorie de $\C$, pleine sur les objets, qui contient les isomorphisms mono\"{i}dals, que $J$ est l'injection canonique et que $J$ est un foncteur conservatif.
+
+Soit $\C=(\C,\C_s)$ une cat\'{e}gorie s\'{e}quo\"{i}dale.
+On dit que $\C$ est \emph{Cart\'{e}sienne} si $\C_s$ a tous les produits et qui $J$ pr\'{e}serve ces produits.
+En outre, on dit que $\C$ est \emph{d\'{e}composable} si on peut d\'{e}composer le produit tensoriel comme
+\[
+  A\tensor B \cong A\sequoid B \times B\sequoid A
+  \]
+et que $\C$ est \emph{distributive} si le produit distribue sur le s\'{e}quo\"{i}de:
+\[
+  (A \times B) \sequoid C \cong (A \sequoid C) \times (B \sequoid C)
+  \]
+
+\section{Le comono\"{i}de commutatif libre dans les cat\'{e}gories s\'{e}quo\"{i}dales}
+
+Enfin, on suppose que l'endofoncteur
+\[
+  A\sequoid\blank \from \C \to \C
+  \]
+admet une coalg\`{e}bre finale, qui nous appelerons $\oc A$.
+On veut construire la structure d'un comono\"{i}de commutatif sur $\oc A$, et montrer que ce comono\"{i}de est le comono\"{i}de commutatif libre sur $A$.
+
+Il s'av\`{e}re que si on suppose aussi que la fl\`{e}che naturelle
+\[
+  \oc A \tensor \oc B \to \oc(A\times B)
+  \]
+est une isomorphisme, alors on peut construire la structure d'un comono\"{i}de
+\[
+  \oc A \to \oc A \tensor \oc A
+  \]
+\`{a} partir de la fl\`{e}che diagonale
+\[
+  A \xrightarrow{\Delta} A \times A
+  \]
+et on peut montrer que ce comono\"{i}de est libre sur $A$.
+
+Sans cette hypoth\`{e}se, est-ce qu'on peut construire le comono\"{i}de commutatif libre ?
+
+\section{Les jeux transfinis}
+
+La r\'{e}ponse est non.
+J'ai construit une cat\'{e}gorie s\'{e}quo\"{i}dale dont les objets sont les jeux \emph{transfinis}, dans lesquels les parties peuvent posseder une longueur transfinie.
+Dans ces cat\'{e}gories, on peut construire le foncteur $A\sequoid\blank$, et ce foncteur admet une coalg\`{e}bre finale $\oc A$, qui peut \^{e}tre construit comme dans le cas finitaire: $\oc A$ se compose des jeux $A_0, A_1, \dots$, index\'{e}s par l'ordinal $\omega$.
+
+Pourtant, dans les cat\'{e}gories des jeux transfinis, ce jeu n'a pas la structure naturelle d'un comono\"{i}de.  Examinez la strat\'{e}gie pour le jeu
+\[
+  \oc A \implies \oc A \tensor \oc A
+  \]
+o\`{u} la Joueuse essaie \`{a} copier les coups de l'Opposant sur la droite dans les copies de $A$ sur la gauche.
+Supposons que l'Opposant ouvre tous les copies de $A$ dans la copie de $\oc A$ sur la gauche du produit tensoriel $\oc A \tensor \oc A$.
+Au temps $\omega$, l'Opposant aurait pu ouvert tous ces copies du jeu $A$.
+
+Ensuite, on d\'{e}passe l'ordinal $\omega$, et l'Opposant d\'{e}cide d'ouvrir une copie de $A$ \`{a} l'extr\^{e}me droite.
+Mais maintenant, il n'y a pas de copies de $A$ sur la gauche pour la Joueuse.
+
+On peut aussi v\'{e}rifier que l'identit\'{e}
+\[
+  \oc A \tensor \oc B \cong \oc(A\times B)
+  \]
+est faux pour les jeux transfinis.
+
+\section{Que faire?}
+
+Je veux voir si il y a une autre hypoth\`{e}se sur les cat\'{e}ories s\'{e}quo\"{i}dales, dans laquelle on peut d\'{e}monstrer que la coalg\`{e}bre finale $\oc A$ a la structure d'un comono\"{i}de commutatif libre sur $A$.
+J'esp\`{e}re que cette hypoth\`{e}se puisse se pr\'{e}senter en fonction des connecteurs tensoriel $\tensor$ et s\'{e}quo\"{i}dale $\sequoid$, et pas sous forme de la coalg\`{e}bre finale elle-m\^{e}me.
+
+Bien s\^{u}r, cette hypoth\`{e}se sera n\'{e}cessairement faux dans les cat\'{e}gories des jeux transinis.  J'esp\`{e}re que cela nous aidera \`{a} la chercher.
+
+\section{La s\'{e}quence finale}
+
+J'ai aussi \'{e}tudi\'{e} la s\'{e}quence finale pour l'endofoncteur $A\sequoid\blank$.
+Rappelons que si $\C$ est une cat\'{e}gorie et si $\F\from\C\to\C$ est un endofoncteur, alors on peut counstruire une s\'{e}quence d'objects de $\C$, index\'{e}e par les ordinals, par appliquer cet endofoncteur et prendre les limites.
+
+On construit ainsi un foncteur
+\[
+  \FS_\F\from\oppcat\Ord\to\C
+  \]
+Si
 

### 2017-02-22 nondeterminism/nondeterminism.tex
Modified some files.

\documentclass{article}

\input{../common/preamble}

\title{Transfinite Games for Countable Nondeterminism}

\begin{document}

\section{Introduction}

{\it I would like to expand this section and flesh out the examples a bit more to make them clearer.}

The basic idea underpinning the game semantics for nondeterministic programming languages is to remove the constraint of \emph{determinism} from the usual definition of a strategy (see, for example, \cite{abramskyjagadeesangames}) that says that the player may have at most one reply to each move made by the opponent.  The determinism constraint is of little technical value and its main purpose is to provide a fully abstract denotational semantics for deterministic programming languages; if we remove it in order to study nondeterministic languages, then much of the technical apparatus of game semantics carries over immediately.

One problem that does arise, however, is that the resulting semantics no longer adequately captures the possibility of divergence in the interaction.  In deterministic game semantics, divergence is represented by the absence of a reply to an opponent's move, but this is not adequate in the nondeterministic case because it gives us no way to capture a \emph{possible} divergence.  For example, if we represent divergence by the abence of a reply then Program A, which constantly returns the numeral $1$, and Program B, which makes a nondeterministic choice and then either returns $1$ or diverges, have the same semantics, despite exhibiting different behaviour \cite{mcCHFiniteND}.

We therefore need a new way to keep track of divergence.  This was done by Harmer and McCusker \cite{mcCHFiniteND}, who resolved the problem by adding extra data to the definition of a strategy that records which opponent positions allow the possibility of divergence.  Using this device, Harmer and McCusker were able to provide a fully abstract game semantics for PCF with finite nondeterminism.

There is, however, a technical subtlety that arises when we try to use the same technique to model PCF with \emph{unbounded} nondeterminism; that is, PCF with the addition of a nondeterministic natural number generator that never diverges.  Indeed, if we naively relax the Harmer-McCusker model to allow infinite branching then composition of strategies is no longer associative \cite{RusssThesis}.

Ultimately, the reason why unbounded nondeterminism introduces problems is that it makes the language fine-grained enough to distinguish between computation that is \emph{divergent}; i.e., a computation that carries on for infinitely many steps and does not terminate, and computation that is convergent, but may take an unbounded number of steps to do so.  For example, using recursion, we may define a function that, at each step, makes a nondeterministic choice whether to call its argument or to return.  If we have access to unbounded nondeterminism then we may write a function that nondeterministically chooses a natural number $n$, calls its argument $n$ times and then returns.  Observationally, these programs are different: the first may diverge, while the second always converges.  In the usual model of strategies as sets of positions, the strategies defined by these two programs are the same.

At first glance, it appears that the Harmer-McCusker model is fine-grained enough to distinguish these two strategies, and this is true if we define the strategies directly: the strategy denoting the first program ought to designate the opening move as divergent, whereas the strategy denoting the second program should not designate any positions as divergent.  However, if we want to define these strategies compositionally, it turns out that both strategies are designated divergent, since the model treats an infinite increasing sequence of positions as a divergence occurring from livelock (the `infinite chattering' in the game semantics).  This inconsistency between the direct definition of the strategy and the compositional one is what leads to the failure of composition to be associative.

We need, then, some way to distinguish between computation that takes infinitely many steps and computation that takes a finite, but arbitrarily large, number of steps.  One approach, taken by Tsukada and Ong \cite{TsukadaSheaves} is to represent strategies as trees, rather than sets of positions; here, there is a distinction between a tree of infinite height and an infinite family of trees of finite but arbitrarily large height.  We take a different approach, one suggested by the work of Roscoe and Levy (\cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}, cited in \cite{TsukadaSheaves}), and by Laird's sequential algorithms model for PCF with unbounded nondeterminism \cite{LairdOrdinalGames}, and enlarge our strategies to include information about the infinite positions that may occur in them.

\subsection{Related Work}

A more detailed overview of previous work, particularly \cite{LairdOrdinalGames}.

\section{PCF with Countable Nondeterminism}

As in \cite{LairdOrdinalGames}.

\subsection{Type Theory}

\subsection{Operational Semantics}

\subsection{Must Testing}

We are interested in soundness and adequacy for the `must-converge' relation, since the `may-converge' relation can be adequately modelled using finite nondeterminism.

\section{Game Semantics}

\subsection{Games}

\begin{definition}

  Given a set $X$, we write $\seqs X$ for the set of all (finite and infinite) sequences of elements of $X$ of length $\le \omega$.

  A \emph{game} is given by a tuple
  \[
    A = (M_A, \lambda_A, \zeta_A, P_A)
    \]
  where
  \begin{itemize}
    \item $M_A$ is a set of moves.
    \item $\lambda_A\from M_A\to\OP$ designates each move as an $O$-move (played by Player $O$) or a $P$-move (played by Player $P$).  
    \item $P_A\subset \seqs{M_A}$ is a non-empty prefix-closed set of sequences of moves from $M_A$ of length $\le\omega$, called \emph{positions}.  We call a sequence $s\in P_A$ \emph{infinite} if $\length(s)=\omega$.  Otherwise, we say that $s$ is \emph{finite}.
    \item $\zeta_A\from P_A\to\OP$ designates each position in $P_A$ as a $P$-position or an $O$-position.
  \end{itemize}

  The set $P_A$ and the functions $\lambda_A,\zeta_A$ are required to satisfy certain additional axioms:
  \begin{description}
    \item[Compactness] If $s\in M_A^\omega$ is an infinite sequence of moves such that $t\in P_A$ for all finite prefixes $t\ppprefix s$, then $s\in P_A$.
    \item[Consistency] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.
    \item[Alternation] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s) = \neg \zeta_A(sa)$.
    \item[Negativity] $\zeta_A(\epsilon)=P$, where $\epsilon$ is the empty position.
  \end{description}

  Note that the negativity rule and the alternation rule between them imply that all starting moves are made by player $O$.  
\end{definition}

\subsection{Strategies}

\begin{definition}
  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  A (nondeterministic) \emph{strategy} for $A$ is a pair $\sigma=(T_\sigma, D_\sigma)$, where
  \begin{itemize}
    \item $T_\sigma$ is the set of \emph{traces} of the strategy; i.e., the set of positions that can occur when player $P$ plays according to the strategy.  That is, $T_\sigma$ is a non-empty prefix-closed subset of $P_A$ that is closed under $O$-replies to $P$-positions: whenever $s\in T_\sigma$ is a $P$-position and $a\in M_A$ is an $O$-move such that $sa\in P_A$, then $sa\in T_\sigma$.  We call such a set $T_\sigma$ a \emph{trace set}.

      We will often identify $T_\sigma$ with $\sigma$, and write $s\in\sigma$ instead of $s\in T_\sigma$.

      We say that $T_\sigma$ is \emph{compact} if it satisfies the compactness criterion given above for games: if $s\in M_A^\omega$ is an infinite sequence such that $t\in T_\sigma$ for all finite prefixes $t\ppprefix s$, then $t\in T_\sigma$.

      We require $T_\sigma$ to satisfy the following criterion:
      \begin{description}
        \item[Local compactness] For any $s\in T_\sigma$, there exists some compact trace set $T_s$ such that $s\in T_s\subset T_\sigma$.
      \end{description}

    \item $D_\sigma\subset T_\sigma$ denotes the set of \emph{divergences} in $T_\sigma$; that is, the set of those $O$-positions in $T_\sigma$ for which Player $P$ may elect to diverge rather than respond.  Accordingly, $\zeta_A(s)=O$ for all $s\in D_\sigma$.  
  \end{itemize}

  $T_\sigma$ and $D_\sigma$ are required to satisfy the following divergence axiom:
  \begin{description}
    \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position then either $sa\in T_\sigma$ for some $P$-move $a$ or there exists $t\prefix s$ such that $t\in D_\sigma$.  
  \end{description}

  A consequence of the diverge-or-reply rule is that if $s\in \sigma$ is an infinite $O$-position, then there exists $t\prefix s$ such that $t\in D_\sigma$ (since it is impossible for player $P$ to reply to it, positions of length $\omega+1$ or greater being disallowed).  This works well for our purposes; it captures our intuition that divergence should arise from some infinite behaviour, but it excludes those cases where Player $O$ is `to blame' for the infinite behaviour (passing, for example, a divergent function into the non-divergent strategy $\lambda f.f$).  
\end{definition}

\subsection{Multiplicatives}

Let $A,B$ be games.  If $s\in \seqs{M_A\cprd M_B}$ then we write $s\vert_A$ for the subsequence of $s$ consisting of all moves from $A$ and $s\vert_B$ for the subsequence of $s$ consisting of all moves from $B$.  We write $P_A\|P_B$ for the set of all such sequences $s$ such that $s\vert_A\in P_A$ and $s\vert_B\in P_B$.

\begin{definition}
  Let $A,B$ be games.  Then the \emph{tensor product} of $A$ and $B$ is the game $A\tensor B=(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B})$ where we define $M_{A\tensor B}$, $\lambda_{A\tensor B}$, $\zeta_{A\tensor B}$, $P_{A\tensor B}$ as follows:
  \begin{itemize}
    \item $M_{A\tensor B} = M_A \cprd M_B$
    \item $\lambda_{A\tensor B} = \lambda_A \cprd \lambda_B$
    \item For $s\in P_A\|P_B$, $\zeta_{A\tensor B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B)$.
    \item $P_{A\tensor B}$ is the set of all sequences $s\in P_A\|P_B$ such that $s$ satisfies the alternating condition with respect to $\zeta_{A\tensor B}$: i.e., for all $t,ta\prefix s$, $\zeta_{A\tensor B}(t) = \neg\zeta_{A\tensor B}(ta)$.  
  \end{itemize}
\end{definition}

\begin{definition}
  Let $A,B$ be games.  Then the \emph{linear implication} of $A$ and $B$ is the game $A\implies B=(M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})$ where we define $M_{A\implies B}$, $\lambda_{A\implies B}$, $\zeta_{A\implies B}$, $P_{A\implies B}$ as follows:
  \begin{itemize}
    \item $M_{A\implies B} = M_A \cprd M_B$
    \item $\lambda_{A\implies B} = (\neg\circ\lambda_A) \cprd \lambda_B$
    \item For $s\in P_A\|P_B$, $\zeta_{A\implies B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B)$.
    \item $P_{A\implies B}$ is the set of all sequences $s\in P_A\|P_B$ such that $s$ satisfies the alternating condition with respect to $\zeta_{A\implies B}$.  
  \end{itemize}
\end{definition}

We want to prove that these are well formed games.

\begin{proposition}\label{TensorImpliesWellFormed}
  If $A,B$ are games then $A\tensor B$ and $A\implies B$ are games.
\end{proposition}

First, we will prove a useful lemma.

\begin{lemma}\label{signProfilesLemma}
  Let $A,B$ be games.  Given a position $s\in P_A\|P_B$, we define the \emph{sign profile} of $s$ to be given by the signs of its two components:
  \[
    \begin{array}{cc|c}
      \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \textrm{sign profile} \\
      \hline
      P & P & PP \\
      O & P & OP \\
      P & O & PO \\
      O & O & OO
    \end{array}
    \]
  If $s\in P_{A\tensor B}$ is a finite position, then $s$ cannot have sign profile $OO$.  If $s\in P_{A\implies B}$ is a finite position then $s$ cannot have sign profile $OP$.  
  \begin{proof}
    By negativity, the empty sequence $\epsilon$ always has sign profile $PP$.  Otherwise, $s=s'a$ for some sequence $s'$ and some move $a$.  If $s\in P_{A\tensor B}$ and $s$ has sign profile $OO$, then $s$ is an $O$-position in $A\tensor B$.  Therefore, $s'$ is a $P$-position in $A\tensor B$ and so $s'$ must have sign profile $PP$, by the definition of $\zeta_{A\tensor B}$.  But this is impossible, as the move $a$ can only change the sign profile in one of the two components.

    The proof for the linear implication is entirely similar.
  \end{proof}
\end{lemma}

\begin{proof}[Proof of Proposition \ref{TensorImpliesWellFormed}]
  Alternation is part of the definition and negativity is implied by the equations $P\wedge P = P$ and $P\Rightarrow P = P$.  The only tricky part is proving consistency of the $\lambda$ and $\zeta$ functions.  Since consistency applies only to positions with a last move, we may ignore the infinite plays in $A$ and $B$.

  Suppose $sa\in P_{A\tensor B}$.  We wish to show that $\zeta_{A}(sa)=\lambda_A(a)$.  In the presence of alternation, this is equivalent to showing that $\zeta_A(s) = \neg \lambda_A(a)$.  We show this by cases on the sign profile of $s$.  By Lemma \ref{signProfilesLemma}, $s$ has sign profile $PP$, $OP$ or $PO$.  If $s$ has sign profile $PP$ then $s$ is a $P$-position.  Since $s\vert_A$ and $s\vert_B$ are both $P$-positions, $a$ must be an $O$-move, whether it occurs in $A$ or $B$.

  If instead $s$ has sign profile $OP$ or $PO$, then $s$ is an $O$-position.  By alternation, $sa$ must be a $P$-position, so it must have sign profile $PP$.  By consistency and alternation for the games $A,B$, the move $a$ must be a $P$-move.

  For compactness, suppose that $s\in M_{A\tensor B}^\omega$ is an infinite sequence of moves such that $t\in P_{A\tensor B}$ for all finite prefixes $t\ppprefix s$.  Then $s$ is certainly alternating.  Moreover, for all finite prefixes $t\ppprefix s\vert_A$, we have $t\in P_A$, and so therefore $s\vert_A\in P_A$ by compactness for $A$.  Similarly, $s\vert_B\in P_B$, and therefore, $s\in P_{A\tensor B}$.

  The proof for the linear implication is similar.
\end{proof}

Looking at the proof above, we may deduce the following important fact:

\begin{proposition}
  In the tensor product $A\tensor B$, only player $O$ may switch games.  In the linear implication $A\implies B$, only player $P$ may switch games.
\end{proposition}

\subsection{Composition of Strategies}

Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We shall construct a strategy $\comp\tau\sigma$ for $A\implies C$.

In order to define $T_{\comp\tau\sigma}$, we first define the set $\sigma\|\tau$, given by:
\[
  \sigma\|\tau = \left\{\s\in\seqs{(M_A\cprd M_B\cprd M_C)}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\right\}
  \]
We then define
\[
  T_{\comp\tau\sigma} = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}
  \]
We need to prove that $T_{\comp\tau\sigma}\subset P_{A\implies B}$.  If $\s\in\sigma\|\tau$, then $\s\vert_{A,C}\vert_A=\s\vert_A=\s\vert_{A,B}\vert_A\in P_A$, and similarly $\s\vert_{A,C}\in P_C$, so certainly $\s\vert_{A,C}\in P_A\|P_C$.  It will suffice, then, to show that $\s\vert_{A,C}$ is alternating with respect to $\zeta_{A\implies C}$.

\begin{proposition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose $s,sa\in\comp\tau\sigma$.  Then $\zeta_{A\implies C}(s) = \neg\lambda_{A\implies C}(a)$.  
  \begin{proof}
    Write $sa=\s a\vert_{A,C}$, where $\s a\in\sigma\|\tau$.  Then $\s\vert_{A,C}=s$.  $s,sa$ must be finite, so, by Lemma \ref{signProfilesLemma}, neither $\s\vert_{A,B}$ nor $\s\vert_{B,C}$ may have sign profile $OP$, so we get four possible sign profiles for $\s$ giving us the following values for $\zeta_{A\implies C}(\s\vert_{A,C})$:
    \[
      \begin{array}{ccc|c}
        \zeta_A(\s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_{A\implies C}(s\vert_{A,C}) \\
        \hline
        P & P & P & P \\
        P & P & O & O \\
        P & O & O & O \\
        O & O & O & P
      \end{array}
      \]
    Suppose that $a$ is an $O$-move in $A\implies C$: so $a$ is a $P$-move in $A$ or an $O$-move in $C$.  By alternation in the component games, playing the move $a$ either turns an $O$-position in $A$ into a $P$-position in $A$ or turns a $P$-position in $C$ into an $O$-position in $C$.  That is, we must be switching from sign profile $PPP$ to sign profile $PPO$ or from sign profile $OOO$ to sign profile $POO$.  In either case, $s = \s\vert_{A,C}$ must be a $P$-position.

    Similarly, if $a$ is a $P$-move in $A\implies C$, then switching from $\s$ to $\s a$ must move us from sign profile $PPO$ to sign profile $PPP$ or from sign profile $POO$ to sign profile $OOO$; in either case, $s$ must be an $O$-position.
  \end{proof}
\end{proposition}

To complete the proof that $T_{\comp\tau\sigma}$ is a legal trace set for a strategy, we need to show that $T_{\comp\tau\sigma}$ is closed under opponent replies and that it is locally compact.

\begin{proposition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose $s\in\comp\tau\sigma$ is a $P$-position such that $sa\in P_{A\implies C}$ for some $O$-move $a$.  Then $sa\in\comp\tau\sigma$.

  \begin{proof}
    Write $s=\s\vert_{A,C}$, for $\s\in\sigma\|\tau$.  We show that $\s a\in\sigma\|\tau$: so $sa = \s a\vert_{A,C}\in\comp\tau\sigma$.

    Since $s$ is a $P$-position, the sign profile of $\s$ must be $PPP$ or $OOO$.  It follows that $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$ are both $P$-positions.  Since $a$ is a $P$-move in $A\implies C$, it must be either a $P$-move in $A\implies B$ or a $P$-move in $B\implies C$, by straightforward analysis of the definitions of the $\lambda$ functions.  It follows that either $s\vert_{A,B}a\in\sigma$ (if $a$ is a move in $A$) or that $s\vert_{B,C}a\in\tau$ (if $a$ is a move in $C$).  In either case, we have $\s a\in\sigma\|\tau$, as desired.
  \end{proof}
\end{proposition}

\begin{proposition}\label{locallyCompactComposition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $\comp\tau\sigma$ is locally compact.
\end{proposition}

In order to prove that the composition of locally compact strategies is locally compact, we are going to need some facts about deterministic strategies.

\begin{definition}
  We say a strategy $\sigma$ is \emph{deterministic} if whenever $s\in\sigma$ is an $O$-position and $a,b$ are moves such that $sa,sb\in\sigma$, then $a=b$.
\end{definition}

Deterministic strategies have the following nice technical property:

\begin{proposition}
  Let $A,B,C$ be games, let $\sigma$ be a deterministic strategy for $A\implies B$ and let $\tau$ be a deterministic strategy for $B\implies C$.  Then $\comp\tau\sigma$ is a deterministic strategy.  Moreover, for any $s\in\comp\tau\sigma$, there is a unique minimal $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
  \begin{proof}
    The idea behind the proof is that determinism of $\sigma$ and $\tau$ mean that the play in the intermediate game $B$ is completely determined (since every move played in $B$ is either a $P$-move in $A\implies B$ or a $P$-move in $B\implies C$.  For full details, see \cite{abramskyjagadeesangames}.
  \end{proof}
\end{proposition}

We can use this to prove the following:

\begin{proposition}
  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be compact deterministic strategies.  Then $\comp\tau\sigma$ is compact.
  \begin{proof}
    Let $s\in M_{A\implies C}^\omega$ be an infinite sequence such that $t\in\comp\tau\sigma$ for all finite prefixes $t\ppprefix s$.  For each finite prefix $t$ of $s$, there is a unique minimal sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=t$.  Writing $s$ as the limit of its finite prefixes
    \[
      t_1 \prefix t_2 \prefix t_3 \prefix \dots
      \]
    we build up a sequence
    \[
      \t_1 \prefix \t_2 \prefix \t_3 \prefix \dots
      \]
    where $\t_i$ is the unique minimal sequence in $\sigma\|\tau$ such that $\t_i\vert_{A,C}=t_i$.  We have $\t_i\prefix\t_{i+1}$ because if we remove the last move from $\t_{i+1}$ then the resulting sequence $\u_i$ satisfies $\u_i\vert_{A,C}=t_i$ and therefore $\t_i\prefix\u_i\prefix\t_{i+1}$ by minimality of $\t_i$.

    Then the limit of the sequences $\t_i\vert_{A,B}$ must be contained in $\sigma$, since $\sigma$ is compact, and similarly the limit of the sequences $\t_i\vert_{B,C}$ must be contained in $\tau$, since $\tau$ is compact.  It follows that the limit $\t$ of the sequences $\t_i$ is contained in $\sigma\|\tau$, and therefore that $\t\vert_{A,C}=s\in\comp\tau\sigma$.
  \end{proof}
\end{proposition}

Note that the limit of compact nondeterministic strategies need not be compact.

\begin{example}
  Let the games $I$ and $\st$ be defined as before, and let the game $\Sigma$ be the game with a unique opponent starting move and a unique player reply:
  \[
    \Sigma = (\{q,a\}, \{q\mapsto o, a\mapsto p\}, \{\epsilon\mapsto p,q\mapsto o,qa\mapsto p\}, \{\epsilon, q, qa\}\}
    \]
  Let $\bN$ be the game where the opponent asks the player to choose a natural number:
  \[
    \bN = \left(\{q\} \cup \bN, \{q\mapsto O, n\mapsto P\}, \{\epsilon\mapsto P,q\mapsto O,qn\mapsto P\}, \{\epsilon, q\} \cup \{qn\suchthat n\in\bN\}\right)
    \]
  We have a (deterministic) strategy $\sigma$ for $\bN\implies (\st\implies\Sigma)$ in which the player asks the opponent for a number $n$ and then calls the argument of $\st$ $n$ times before returning.  For example, a play in $\sigma$ might look like this:
  \[
    \begin{array}{ccc}
      \bN & \st & \Sigma \\
      & & q \\
      q & & \\
      2 & & \\
      & q & \\
      & a & \\
      & q & \\
      & a & \\
      & & a
    \end{array}
    \]
  $\sigma$ is compact because there are no infinite chains of positions; indeed, the length of a play in $\sigma$ is already determined by the third move.

  We have a nondeterministic strategy $?$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $? = P_{\bN}$ as sets of positions.  $?$ is compact because all plays in $?$ have length at most $2$.

  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $q,qqa,qqaqa,qqaqaqa,\dots$, but does not contain any limiting plays.  So it is not compact.  It is, however, locally compact, since it is the union of compact strategies $\sigma_n$, where $\sigma_n$ has the unique maximal play
  \[
    q\underbrace{qa\dots qa}_{\textrm{$n$ times}}a
    \]
\end{example}

\begin{proposition}
  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be (nondeterministic, locally compact) strategies.  Then $\comp\tau\sigma$ is locally compact.
  \begin{proof}
    Let $s\in T_{\comp\tau\sigma}$.  Then there is some sequence $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.  We have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, so, by local compactness for $\sigma$ and $\tau$, there are compact strategies $\sigma'\from A\implies B$ and $\tau'\from B\implies C$ such that $\s\vert_{A,B}\in\sigma'$ and $\s\vert_{B,C}\in\tau'$.  After removing positions from $\sigma'$ and $\tau'$, we may assume that they are deterministic (and still compact).  Then $\comp{\tau'}{\sigma'}$ is compact and we have $\s\vert_{A,C}\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$.
  \end{proof}
\end{proposition}

Before we consider the definition of $D_{\comp\tau\sigma}$, we show that composition is associative at the level of trace sets.

\begin{proposition}\label{traceAssociativity}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$, let $\tau$ be a strategy for $B\implies C$ and let $\upsilon$ be a strategy for $C\implies D$.  Then
  \[
    T_{\comp{\upsilon}{(\comp\tau\sigma)}} = T_{\comp{(\comp\upsilon\tau)}{\sigma}}
    \]

  \begin{proof}
    As in \cite{abramskyjagadeesangames}.  Define
    \[
      \sigma\|\tau\|\upsilon = \left\{\s\in\seqs{(M_A \cprd M_B \cprd M_C \cprd M_D)} \suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau,\;\s\vert_{C,D}\in\upsilon\right\}
      \]
    We shall show that 
    \[
      T_{\comp{\upsilon}{(\comp{\tau}{\sigma})}} = \{\s\vert_{A,D}\suchthat\s\in\sigma\|\tau\|\upsilon\}
      \]
    The same claim will follow for $T_{\comp{(\comp{\upsilon}{\tau})}{\sigma}}$ by symmetry, completing the proof.

    Let $\s\in\sigma\|\tau\|\upsilon$.  Then $\s\vert_{A,B,C}\in\sigma\|\tau$ and so $\s\vert_{A,C}\in\comp\tau\sigma$.  Now we see that $\s\vert_{A,C,D}\in (\comp\tau\sigma)\|\upsilon$ and so $\s\vert_{A,D}\in\comp{\upsilon}{(\comp\tau\sigma)}$.  We have shown that
    \[
      \{\s\vert_{A,D}\suchthat\s\in\sigma\|\tau\|\upsilon\} \subset T_{\comp{\upsilon}{(\comp{\tau}{\sigma})}}
      \]
    To show the reverse inclusion, suppose that $s\in\comp{\upsilon}{(\comp\tau\sigma)}$.  Let $\s\in(\comp\tau\sigma)\|\upsilon$ be such that $\s\vert_{A,D}=s$ and let $\t\in\sigma\|\tau$ be such that $\t\vert_{A,C}=\s\vert_{A,C}$.  Our goal is to interleave the sequences $\s$ and $\t$ in order to give rise to a sequence $\u\in\sigma\|\tau\|\upsilon$ such that $\u\vert_{A,D}=s$.

    Note that since $\s\vert_{A,C}=\t\vert_{A,C}$, we may decompose $\s$ and $\t$ into blocks:
    \begin{gather*}
      \s = \s_0D_0\s_1D_1\dots\\
      \t = \s_0B_0\s_1B_1\dots
    \end{gather*}
    where $\s_1,\s_2,\dots$ are sequences of moves from either $A$ or $C$, $B_0,B_1\dots$ are (possibly empty) sequences of moves from $B$ and $D_0,D_1,\dots$ are (possibly empty) sequences of moves from $D$.

    We then form the sequence $\u$ as:
    \[
      \u = \s_0B_0D_0\s_1B_1D_1\dots
      \]
    It might look as if we have made an arbitrary choice in placing the $B_i$ before the $D_i$, but in fact it turns out that there is no choice to make: an examination of sign profiles, for example, will show that $B_i$ is non-empty only if $D_i$ is empty and vice versa: if $\s_i$ can be followed by a move from $B$ then it cannot be followed by a move from $D$.

    In any case, we have
    \begin{gather*}
      \u\vert_{A,C,D} = \s_0D_0\s_1D_1\dots = \s \\
      \u\vert_{A,B,C} = \s_0B_0\s_1B_1\dots = \t
    \end{gather*}
    It follows that $\u\in\sigma\|\tau\|\upsilon$: 
    \begin{gather*}
      \u\vert_{A,B} = \t\vert_{A,B} \in \sigma \\
      \u\vert_{B,C} = \t\vert_{B,C} \in \tau \\
      \u\vert_{C,D} = \s\vert_{C,D} \in \upsilon
    \end{gather*}
    Lastly, we have $\u\vert_{A,D} = \s\vert_{A,D} = s$, completing the proof.
  \end{proof}
\end{proposition}

At the moment, we have an associative composition at the level of trace sets.  We now define composition at the level of divergences.

\begin{definition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We define the divergences of $\comp\tau\sigma$ as follows:
  \[
    D_{\comp\tau\sigma} = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\textrm{ and either $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$}\}
    \]
\end{definition}

\begin{remark}
  Since $D_\sigma$ and $D_\tau$ consist of $O$-positions, any $\s\in\sigma\|\tau$ such that $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$ must have sign profile $POO$ or $PPO$, by Lemma \ref{signProfilesLemma}, and therefore $\s\vert_{A,C}$ must be an $O$-position.  It follows that $D_{\comp\tau\sigma}$ consists of $O$-positions.
\end{remark}

Unlike \cite{mcCHFiniteND}, we do not need to change the definition of $D_{\comp\tau\sigma}$ to reflect divergence arising from infinite chattering.  The following example shows that it arises naturally from existing definition of $D_{\comp\tau\sigma}$.

\begin{example}[Infinite chattering]
  Let $\st$ denote the game where each player has exactly one move available in every position and the resulting infinite position is a $P$-position:
  \[
    \st = (\{q, a\}, \{q\mapsto O, a\mapsto P\}, \{\epsilon\mapsto P,sq\mapsto O,sa\mapsto P,qaqa\dots\mapsto P\}, \{s\prefix qaqa\dots\})
    \]
  Let $I$ denote the empty game with no moves, and let $\bot$ denote the game with a single opponent move and no player reply:
  \begin{gather*}
    I = (\emptyset, \emptyset, \{\epsilon\mapsto P\}, \{\epsilon\}) \\
    \bot = (\{*\}, \{*\mapsto O\}, \{\epsilon\mapsto P, *\mapsto O\}, \{\epsilon, *\})
  \end{gather*}
  There are natural strategies $\sigma$ for $I\implies\st$ and $\tau$ for $\st\implies\bot$ given at the level of traces by:
  \begin{gather*}
    \sigma = \{s \prefix qaqa\dots\} \\
    \tau = \{s \prefix *qaqa\dots\}
  \end{gather*}
  Player $P$ always has a reply to an $O$-position in $\sigma$, and we set $D_\sigma = \emptyset$.  In $\tau$, the infinite sequence $*qaqa\dots$ satisfies $\zeta_{\st}(*qaqa\dots\vert_{\st}) = \zeta_{\st}(qaqa\dots) = P$ and $\zeta_{\bot}(*qaqa\dots\vert_{\bot}) = \zeta_{\bot}(*) = O$ and so it is an $O$-position.  As in the remark at the end of the definition of a strategy, this $O$-position can have no $P$-reply, so it (or some prefix) must be designated divergent.  We set
  \[
    D_\tau = \{*qaqa\dots\}
    \]
  Now, when we compose the strategies $\sigma$ and $\tau$, at the level of traces we have
  \[
    \comp\tau\sigma = \{\epsilon, *\}
    \]
  The sequence $*$ is the restriction to $I,\bot$ of the infinite sequence
  \[
    *qaqa\dots \in \sigma\|\tau
    \]
  We now have that $*qaqa\dots\vert_{\st,\bot}\in D_\tau$ and therefore the sequence $*\in\comp\tau\sigma$ must be designated divergent.  We have
  \[
    D_{\comp\tau\sigma} = \{*\}
    \]
  as desired.

  Note that if we modify the definition of $\st$ so that the infinite position is an $O$-position, then we still get a divergence -- this time, because the sequence $*qaqa\dots\vert_{I,\sigma^*}$ must be contained in $D_\sigma$.  If we leave out the infinite position from $\sigma$ or $\tau$ altogether, then that strategy is no longer locally compact, so it is not a valid strategy according to our definition.
\end{example}

This example is at the heart of the proof that the composition of strategies satisfies the diverge-or-reply rule.  This is the point at which we need local compactness.

\begin{proposition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $D_{\comp\tau\sigma}$ satisfies the diverge-or-reply rule.

  \begin{proof}
    Suppose that $s\in\comp\tau\sigma$ is an $O$-position and that $s\not\in D_{\comp\tau\sigma}$.  Let $\s\in\sigma\|\tau$ be such that $\s\vert_{A,C}=s$.  By local compactness of $\sigma$ and $\tau$, there must be compact strategies $\sigma'\from A\implies B$ and $\tau'\from B\implies C$ such that $\s\vert_{A,C}\in\sigma'$ and $\s\vert_{B,C}\in\tau'$.

    Let $\s'\in\sigma'\|\tau'$ be maximal such that $\s'\vert_{A,C}=s$.  We know that such a maximal sequence must exist: if $\s_i$ are a chain of sequences from $\sigma'\|\tau'$ such that $\s_i\vert_{A,C}=s$ then their limit $\s$ (which is contained in $\sigma'\|\tau'$ by compactness of $\sigma'$ and $\tau'$) must satisfy $\s\vert_{A,C}=\s$.  Since $s\not\in D_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\not\in D_\sigma$ and $\s\vert_{B,C}\not\in D_\tau$.

    Since $s$ is an $O$-position, one of $\s\vert_{A,B}$ and $\s\vert_{B,C}$ must be an $O$-position (by transitivity of $\Rightarrow$).  Suppose without loss of generality that $\s\vert_{A,B}$ is an $O$-position.  Since $\s\vert_{A,B}\not\in D_\sigma$, there must be some move $x$ such that $\s\vert_{A,B}x\in\sigma$, since $\sigma$ satisfies the diverge-or-reply rule.  Then we have $\s x\vert_{A,B}\in\sigma$.  Moreover, Lemma \ref{signProfilesLemma} tells us that $\s\vert_{B,C}$ must be a $P$-position, so $\s x\vert_{B,C}\in\tau$, since $\tau$ is closed under opponent replies.  Therefore, $\s x\in\sigma\|\tau$.  By maximality of $\s$, $x$ must be a move in $A$ and therefore we have $sx\in\comp\sigma\tau$.
  \end{proof}
\end{proposition}

We now have a working definition of composition.  It remains to prove that it is associative at the level of divergences:

\begin{proposition}
  Let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$, let $\tau$ be a strategy for $B\implies C$ and let $\upsilon$ be a strategy for $C\implies D$.  Then 
  \[
    D_{\comp\upsilon{(\comp\tau\sigma)}} = D_{\comp{(\comp\upsilon\tau)}\sigma}
    \]
  \begin{proof}
    We claim that
    \[
      D_{\comp\upsilon{(\comp\tau\sigma)}} = \{\s\vert_{A,D}\suchthat\s\in\sigma\|\tau\|\upsilon\textrm{ and either $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$ or $\s\vert_{C,D}\in D_\upsilon$}\}
      \]
    The same claim will hold for $D_{\comp{(\comp\upsilon\tau)}\sigma}$ by symmetry, completing the proof.

    Let $\s\in\sigma\|\tau\|\upsilon$ be such that either $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$ or $\s\vert_{C,D}\in D_\upsilon$.  Then either $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ or $\s\vert_{B,C}\in D_\upsilon$ and therefore $\s\vert_{A,D}\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.

    Conversely, suppose that $s\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.  By the definition of $D_{\comp\upsilon{(\comp\tau\sigma)}}$, there must be some sequence $\s\in(\comp\tau\sigma)\|\upsilon$ such that $\s\vert_{A,D}=s$ and either $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ or $\s\vert_{C,D}\in D_\upsilon$.

    We now know that there is a sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=\s\vert_{A,C}$.  If $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ then either $\t\vert_{A,B}\in D_\sigma$ or $\t\vert_{B,C}\in D_\tau$.

    We now have the sequences $\s$ and $\t$ and we know that either $\t\vert_{A,B}\in D_\sigma$ or $\t\vert_{B,C}\in D_\tau$ or $\s\vert_{C,D}\in D_\upsilon$.  By the proof of Proposition \ref{traceAssociativity}, we are able to interleave the sequences $\s$ and $\t$ to get a sequence $\u\in\sigma\|\tau\|\upsilon$ such that $\u\vert_{A,C,D}=\s$ and $\u\vert_{A,B,C}=\t$.  Now we have either $\u\vert_{A,B}=\t\vert_{A,B}\in D_\sigma$ or $\u\vert_{B,C}=\t\vert_{B,C}\in D_\tau$ or $\u\vert_{C,D}=\s\vert_{C,D}\in D_\upsilon$.  Moreover, $\u\vert_{A,D}=\s\vert_{A,D}=s$ and therefore $s$ is contained in the set on the right, which completes the proof.
  \end{proof}
\end{proposition}

In order to show that we have a category, it remains to define the identity morphisms.  These are given by the usual copycat strategies:
\[
  \id_A = \{s\in P_{A_1\implies A_2}\suchthat\textrm{for all even length $t\prefix s$, $t\vert_{A_1}=t\vert_{A_2}$}\}
  \]
(Here, we consider infinite plays to have even length).

The divergence set $D_{\id_A}$ is empty: note that infinite positions in $\id_A$ are always $P$-positions.

\begin{theorem}
  There is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
  \begin{proof}
    All that is left to do is to show that $\id_A$ really is an identity morphism.  We shall show that if $A$ and $B$ are games and $\sigma$ is a strategy for $A\implies B$ then $\comp\sigma{\id_A}=\sigma$; it will follow by a symmetrical argument that $\comp{\id_B}\sigma = \sigma$.

    We first show that $T_{\comp\sigma{\id_A}}=T_\sigma$.  Because of closure under opponent replies, it suffices to show that $\sigma$ and $\comp\sigma{\id_A}$ contain the same $P$-positions.  If $s$ is a $P$-position in $\comp\sigma{\id_A}$, then there is some sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=s$.  Since $\s\vert_{A_1,B}$ is a $P$-position, it must have sign profile $PPP$ or $OOO$ by Lemma \ref{signProfilesLemma}, and therefore $\s\vert_{A_1,A_2}$ is a $P$-position, so has even length.  Therefore, $\s\vert_{A_1}=\s\vert_{A_2}$ and so $s=\s\vert_{A_1,B}=\s\vert_{A_2,B}\in\sigma$.

    Conversely, suppose that $s\in\sigma$ is a $P$-position.  There is an obvious sequence $s^2\in\id_A$, given by copying the moves of $s\vert_A$ between copies of $A$, such that $s^2\vert_{A_1}=s^2\vert_{A_2}=s\vert_A$.  Then $s^2\vert_{A_2}=s\vert_{A_2}$, and so the sequences $s^2$ and $s$ may be interleaved as in the proof of Proposition \ref{traceAssociativity} to yield a sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=\s\vert_{A_2,B}=s$.

    Now we show that $D_{\comp\sigma{\id_A}}=D_\sigma$.  Suppose $s\in D_{\comp\sigma{\id_A}}$.  Then there is a sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=s$ and either $\s\vert_{A_1,A_2}\in D_{\id_A}$ or $\s\vert_{A_2,B}\in D_\sigma$.  Since $D_{\id_A}=\emptyset$, we must have $\s\vert_{A_2,B}\in D_\sigma$.  In particular, $\s\vert_{A_2,B}$ is an $O$-position in $A\implies B$ and so $\s\vert_{A_2}$ is a $P$-position in $A$.  It follows by Lemma \ref{signProfilesLemma} that $\s\vert_{A_1,A_2}$ is a $P$-position in $A\implies A$; hence, it is even-length and so $\s\vert_{A_1}=\s\vert_{A_2}$.  It follows that $s=\s\vert_{A_1,B}=\s\vert_{A_2,B}\in D_\sigma$.  So $D_{\comp\sigma{\id_A}}\subset D_\sigma$.

    Conversely, suppose that $s\in D_\sigma$.  We know already that there is some $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,A_2}\in\id_A$ and $\s\vert_{A_2,B}\in\sigma$.  Then $\s\vert_{A,C}\in D_{\comp\sigma{\id_A}}$ by definition.
  \end{proof}
\end{theorem}

\subsection{Symmetric monoidal closed structure}

We make the category $\G$ into a symmetric monoidal closed category with tensor product given by $\tensor$ and linear implication given by $\implies$.  At the level of morphisms, the action of $\blank\tensor\blank$ is defined as follows: if $A,B,C,D$ are games, $\sigma$ is a strategy for $A\implies C$ and $\tau$ is a strategy for $B\implies D$, then $\sigma\tensor\tau$ is the strategy for $(A\tensor B)\implies (C\tensor D)$ given by playing the strategy $\sigma$ in $A$ and $C$ and playing the strategy $\tau$ in $B$ and $D$:
\[
  \sigma\tensor\tau = \left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\suchthat s\vert_{A,C}\in\sigma,\;s\vert_{B,C}\in\tau\right\}
  \]
The divergences for $\sigma\tensor\tau$ are defined using the divergences for $\sigma$ and $\tau$:
\[
  D_{\sigma\tensor\tau} = \left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\suchthat s\vert_{A,C}\in D_\sigma,\;s\vert_{B,D}\in D_\tau\right\}
  \]
\begin{proposition}
  $\sigma\tensor\tau$ is a valid strategy for $(A\tensor B)\implies (C\tensor D)$
  \begin{proof}
    $\sigma\tensor\tau$ is non-empty and prefix-closed, since $\sigma$ and $\tau$ are.  To show that it is a valid trace-set, we need to show that it is closed under opponent replies.

    Let $s\in\sigma\tensor\tau$ be a $P$-position and suppose that $sx\in P_{(A\tensor B)\implies (C\tensor D)}$ for some move $x$.  We start with some brief analysis of sign profiles.

    By Lemma \ref{signProfilesLemma}, $s\vert_{A,B}$ and $s\vert_{C,D}$ must either both be $O$-positions or both be $P$-positions.  If they are $P$-positions, then the only possibility for the sign profile of $s$ is:
    \[
      \begin{array}{cccc}
        \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_D(s\vert_D) \\
        \hline
        P & P & P & P
      \end{array}
      \]
    Otherwise, if they are both $O$-positions, then each of $s\vert_{A,B}$ and $s\vert_{C,D}$ may either have sign profile $OP$ or sign profile $PO$, by Lemma \ref{signProfilesLemma}.  But now, since $s\vert_{A,C}\in\sigma\subset P_{A\implies C}$ and since $s\vert_{B,D}\in\tau\subset P_{B\implies D}$, we also see that neither $s\vert_{A,C}$ nor $s\vert_{B,D}$ may have sign profile $OP$.  We therefore have two more possibilities for the sign profile of $s$:
    \[
      \begin{array}{cccc}
        \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_D(s\vert_D) \\
        \hline
        P & O & P & O \\
        O & P & O & P
      \end{array}
      \]
    In all three cases, $s\vert_{A,C}$ and $s\vert_{B,D}$ are both $P$-positions.  Since $\sigma$ and $\tau$ are both closed under opponent replies, it follows that one of them must contain the move $x$ as a reply to the current position, and therefore that $sx\in\sigma\tensor\tau$, as desired.

    Now we need to show that $\sigma\tensor\tau$ is locally compact.  We first show that if $\sigma$ and $\tau$ are compact strategies then $\sigma\tensor\tau$ is compact.  Indeed, suppose that $s\in\sigma\tensor\tau$ is an infinite sequence such that $t\in\sigma\tensor\tau$ for all finite prefixes $t\ppprefix s$.  Then $\sigma$ must contain all finite prefixes of $s\vert_{A,C}$, so it must contain $s\vert_{A,C}$, since $\sigma$ is compact.  Similarly, $\tau$ must contain $s\vert_{B,D}$.  Therefore, $s\in\sigma\tensor\tau$.  Since $s$ was arbitrary, it follows that $\sigma\tensor\tau$ is compact.

    Now suppose that $\sigma$ and $\tau$ are locally compact.  Let $s\in\sigma\tensor\tau$.  Then there exists compact strategies $\sigma'\from A\implies C$ and $\tau'\from B\implies D$ such that $s\vert_{A,C}\in\sigma'$ and $s\vert_{B,C}\in\tau'$.  Then $s\in\sigma'\tensor\tau'$, which is compact.

    Lastly, we need to show that $D_{\sigma\tensor\tau}$ satisfies diverge-or-reply.  Indeed, suppose that $s\in\sigma\tensor\tau$ is an $O$-position and that $s\not\in D_{\sigma\tensor\tau}$.  Then $s\vert_{A,C}\not\in D_\sigma$ and $s\vert_{B,D}\not\in D_\tau$.  Using Lemma \ref{signProfilesLemma}, we see that $s$ must have one of the following sign profiles:
    \[
      \begin{array}{cccc}
        \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_D(s\vert_D) \\
        \hline
        P & P & P & O \\
        P & P & O & P
      \end{array}
      \]
    It follows that one of $s\vert_{A,C}$ and $s\vert_{B,D}$ must be an $O$-position.  Suppose without loss of generality that $s\vert_{A,C}$ is an $O$-position.  Since $s\vert_{A,C}\not\in D_\sigma$, there must be some move $x$ such that $sx\in\sigma$, since $\sigma$ satisfies diverge-or-reply.  Then we have $sx\in\sigma\tensor\tau$.
  \end{proof}
\end{proposition}

We also need to show that the tensor product respects composition.  This is easy.

\begin{proposition}
  Let $A'',A',A,B'',B',B$ be games and let $\sigma'\from A''\to A'$, $\sigma\from A'\to A$, $\tau'\from B''\to B'$, $\tau\from B'\to B$ be strategies.  Then
  \[
    \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')} = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
    \]
  \begin{proof}
    At the level of trace sets, we have:
    \begin{gather*}
      (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'}) = \left\{s\in P_{(A''\tensor B'')\implies(A\tensor B)}\suchthat s\vert_{A'', A}\in\comp\sigma{\sigma'},\;s\vert_{B'', B}\in\comp\tau{\tau'}\right\}
    \end{gather*}
    Meanwhile:
    \begin{align*}
      (\sigma'\tensor\tau')\|(\sigma\tensor\tau) &= \left\{\s\in \seqs{(M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})}\;\middle|\;{\mbox{\begin{minipage}{120pt}{
        \setlength{\abovedisplayskip}{-5pt}
        \setlength{\belowdisplayskip}{-10pt}
        \begin{IEEEeqnarray*}{cCc}
          \s\vert_{A''\tensor B'',A'\tensor B'} & \in & \sigma'\tensor\tau' \\
          \s\vert_{A'\tensor B',A\tensor B} & \in & \sigma\tensor\tau
        \end{IEEEeqnarray*}}
        \normalsize
      \end{minipage}}}\right\} \\[1em]
      &= \left\{\s\in \seqs{(M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
        \setlength{\abovedisplayskip}{-5pt}
        \setlength{\belowdisplayskip}{-10pt}
        \begin{IEEEeqnarray*}{cCc}
          \s\vert_{A'', A'} & \in & \sigma' \\
          \s\vert_{A', A} & \in & \sigma \\
          \s\vert_{B'', B'} & \in & \tau' \\
          \s\vert_{B', B} & \in & \tau
        \end{IEEEeqnarray*}}
        \normalsize
      \end{minipage}}}\right\} \\[1em]
      &= \left\{\s\in \seqs{(M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
        \setlength{\abovedisplayskip}{-5pt}
        \setlength{\belowdisplayskip}{-10pt}
        \begin{IEEEeqnarray*}{cCc}
          \s\vert_{A'', A', A} & \in & \sigma'\|\sigma \\
          \s\vert_{B'', B', B} & \in & \tau'\|\tau
        \end{IEEEeqnarray*}}
        \normalsize
      \end{minipage}}}\right\}
    \end{align*}

    It follows that
    \[
      \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}
      = \left\{\s\vert_{A''\tensor B'', A\tensor B}\suchthat\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)\right\}
      = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
      \]

    We can show that
    \[
      D_{\comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}} = D_{(\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})}
      \]
    using a similar argument.
  \end{proof}
\end{proposition}

The associators, unitors and braiding for this

\section{Denotational Semantics for Fair PCF}

\subsection{Soundness}

\subsection{Adequacy}

I don't think I'll have a full abstraction result yet, but I could add a section explaining how this model gives us some progress towards full abstraction.

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2017-02-24 nondeterminism/nondeterminism.tex
More modifications, and a new paper added.

@@
 
-The associators, unitors and braiding for this
+The associators, unitors and braiding for this tensor product are the usual (deterministic, compact, non-divergent) copycat strategies.
+It is straightforward to show that they are natural transformations, using the same argument we used to show that $\id_A$ is an identity, and that the appropriate coherence diagrams are satisfied.
+
+Closedness follows immediately from the structural isomorphism
+\[
+  (A \tensor B) \implies C \cong A \implies (B \implies C)
+  \]
+for all games $A,B,C$, together with the definition of morphisms as strategies on the linear implication.
+
+\subsection{Exponentials}
+
+Let $A$ be a game.  We define a game $\oc A$ in which the opponent may at any point open a new copy of the game $A$:
+\[
+  \oc A = (M_{\oc A}, \lambda_{\oc A}, \zeta_{\oc A}, P_{\oc A})
+  \]
+where
+\begin{itemize}
+  \item $M_{\oc A} = \omega \times M_A$
+  \item $\lambda_{\oc A} = \lambda_A \circ \pr_2$
+\end{itemize}
+
+Given some sequence $s\in \seqs{M_{\oc A}}$, we write $s\vert_n$ for the projection on to the second component of the subsequence of $s$ consisting of those moves of the form $(n, a)$.  We define
+\[
+  \oc P_A = \{s\in\seqs{M_{\oc A}} \suchthat s\vert_n\in P_A \textrm{ for all $n\in\omega$}\}
+  \]
+We define $\zeta_{\oc A}\from \oc P_A\to\OP$ by
+\[
+  \zeta_{\oc A}(s) = \bigwedge_{n\in\omega}\zeta_A(s\vert_n)
+  \]
+Lastly, we define $P_{\oc A}$ to be the subset of $\oc P_A$ consisting of all those terms that are alternating with respect to $\zeta_{\oc A}$ and that satisfy the following criterion on the order in which copies of $A$ may be opened:
+\begin{description}
+  \item[Ordering criterion] If the move $(n + 1, a)$ occurs in $s$, for $n\ge 0$, then there must be some move $b$ such that $(n, b)$ occurs earlier in the sequence $s$ than $(n + 1, a)$.  
+\end{description}
+
+This criterion says that player $O$ must open the copies of $A$ in sequence: he is not allowed to play in game $n+1$ till he has made a move in game $n$.
+
+\begin{proposition}
+  $\oc A$ is a well formed game.
+  \begin{proof}
+    Exactly the same argument as in Proposition \ref{TensorImpliesWellFormed}.
+We need to prove a version of Lemma \ref{signProfilesLemma} which will tell us that if $s\in P_{\oc A}$ then either $\zeta_A(s\vert_n)=O$ for at most one value of $n$.
+  \end{proof}
+\end{proposition}
+
+Just like the tensor product, the exponential $\oc A$ has the property that only player $O$ may switch games.
+
+The exponential connective gives rise to a functor $\G\to\G$, where the operation on morphisms $\sigma\from A\implies B$ is given by:
+\[
+  \oc\sigma = \{s\in P_{\oc A\implies \oc B}\suchthat s\vert_{A_n,B_n}\in\sigma\textrm{ for all $n\in\omega$}\}
+  \]
+The proof that $\oc(\cdot)$ preserves composition is the same as for the tensor product.
+
+$\oc(\cdot)$ gives rise to a \emph{linear exponential comonad} on $\G$ (see \cite{hyland1997games}, for example).
+The relevant natural transformations, including the comultiplication $\mult\from\oc A\to \oc\oc A$, which opens a copy of $A$ on the left for every copy of $A$ opened on the right, are all deterministic, compact, non-divergent strategies.
+We only have to show that they are natural transformations.
+For illustration, we shall do this in the case of the comultiplication.
+
+\begin{proposition}
+  Let $A,B$ be games, and let $\sigma$ be a strategy for $A\implies B$.  Then the following diagram commutes:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[r, "\mult"] \arrow[d, "\oc \sigma"']
+        & \oc \oc A \arrow[d, "\oc \oc \sigma"] \\
+      \oc B \arrow[r, "\mult"']
+        & \oc \oc B
+    \end{tikzcd}
+    \]
+  \begin{proof}
+    Both branches of the diagram are strategies that play as $\sigma$ in each copy of $B$ in $\oc \oc B$, opening a copy of $A$ in $\oc A$ as required.
+The ordering condition means that there is only one possible order in which to open the copies of $A$ in $\oc A$, so both strategies must behave the same way.
+
+    A divergence occurs in either branch if an only if a divergence arises in $\sigma$ in one of the $A-B$ pairs.  So both branches have the same divergence sets.
+  \end{proof}
+\end{proposition}
+
+We may now form the co-Kleisli category $\G^{\oc}$.  The objects of $\G^{\oc}$ are games $A$ and a morphism from $A$ to $B$ is given by a strategy for
+\[
+  A \iimpl B \coloneqq \oc A \implies B
+  \]
+We compose two morphisms $\sigma\from A\iimpl B$ and $\tau\from B\iimpl C$ by setting:
+\[
+  \icomp{\tau}{\sigma} = \oc A \xrightarrow{\mult} \oc \oc A \xrightarrow{\oc \sigma} \oc B \xrightarrow{\tau} C
+  \]
+where composition on the right is in the category $\G$.
+
+A standard property of the linear exponential comonad is:
+
+\begin{theorem}
+  The category $\G^{\oc}$ is Cartesian closed with $\tensor$ as the Cartesian product and $\iimpl$ as the internal Hom.
+\end{theorem}
 
 \section{Denotational Semantics for Fair PCF}
+
+Our base PCF type $\bN$ will be denoted by the game $\bN$ defined above, while the product and function types will be interpreted by the connectives $\tensor$ and $\iimpl$.
+It remains to give the denotation of each of the terms of Fair PCF as a strategy for the appropriate game.
+
+The numerals $\underline{n}$ will each be interpreted as the strategy for $\bN$ that always returns the value $n$.
+The nondeterministic oracle $?$ will be interpreted as the strategy $?$ given at the level of trace sets by $?=P_{\bN}$.
+None of these strategies have any divergent positions.
+
+The other PCF terms all have obvious strategies that they correspond to.  The only difficult one is the combinator $\Y_T$.
 

### 2017-03-01 nondeterminism/nondeterminism.tex
Some more modifications.

@@
 \input{../common/preamble}
+
+\newcommand{\stle}{{\;\le_s\;}}
+\newcommand{\exle}{\sqsubseteq}
+\newcommand{\exlub}{\bigsqcup}
+\newcommand{\dv}{{\text{\lightning}}}
 
@@
 
+We shall write $P_A^P=\zeta_A\inv(\{P\})$ for the set of $P$-positions in $A$ and $P_A^O=\zeta\inv(\{O\})$ for the set of $O$-positions in $A$.
+
 \subsection{Strategies}
 
-\begin{definition}
-  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  A (nondeterministic) \emph{strategy} for $A$ is a pair $\sigma=(T_\sigma, D_\sigma)$, where
+A (nondeterministic) \emph{strategy} for a game $A$ will be given by a pair $\sigma=(T_\sigma, D_\sigma)$, where
 \begin{itemize}
@@
 
-      We will often identify $T_\sigma$ with $\sigma$, and write $s\in\sigma$ instead of $s\in T_\sigma$.
+  \item $D_\sigma\subset T_\sigma$ denotes the set of \emph{divergences} in $T_\sigma$; that is, the set of those $O$-positions in $T_\sigma$ for which Player $P$ may elect to diverge rather than respond.
+Accordingly, $\zeta_A(s)=O$ for all $s\in D_\sigma$.
+If a trace has a divergent prefix, then it is divergent, so we shall follow Roscoe and insist that $D_\sigma$ be postfix-closed in $P_A^O$ (\cite{RoscoeCspInfinite}, cited in \cite{mcCHFiniteND}).
+\end{itemize}
 
-      We say that $T_\sigma$ is \emph{compact} if it satisfies the compactness criterion given above for games: if $s\in M_A^\omega$ is an infinite sequence such that $t\in T_\sigma$ for all finite prefixes $t\ppprefix s$, then $t\in T_\sigma$.
+\begin{definition}
+  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  Then a \emph{strategy} for $A$ is a pair $\sigma=(T_\sigma,D_\sigma)$ such that
+  \begin{itemize}
+    \item $T_\sigma\subset P_A$ is a prefix-closed subset such that whenever $s\in T_\sigma$ is a $P$-position and $sa\in P_A$ for some move $a$, then $sa\in P_A$.
+    \item $D_\sigma\subset P_A^O$ is a postfix-closed subset.
+  \end{itemize}
 
-      We require $T_\sigma$ to satisfy the following criterion:
+  $T_\sigma$ and $D_\sigma$ are required to satisfy the following totality axioms:
   \begin{description}
-        \item[Local compactness] For any $s\in T_\sigma$, there exists some compact trace set $T_s$ such that $s\in T_s\subset T_\sigma$.
+    \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position then either $sa\in T_\sigma$ for some $P$-move $a$ or $s\in D_\sigma$.  
   \end{description}
 
-    \item $D_\sigma\subset T_\sigma$ denotes the set of \emph{divergences} in $T_\sigma$; that is, the set of those $O$-positions in $T_\sigma$ for which Player $P$ may elect to diverge rather than respond.
-Accordingly, $\zeta_A(s)=O$ for all $s\in D_\sigma$.
-  \end{itemize}
-
-  $T_\sigma$ and $D_\sigma$ are required to satisfy the following divergence axiom:
-  \begin{description}
-    \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position then either $sa\in T_\sigma$ for some $P$-move $a$ or there exists $t\prefix s$ such that $t\in D_\sigma$.  
-  \end{description}
+  The diverge-or-reply rule tells us that a function must either return a value or go into an infinite loop, and corresponds to the absence of an error constant in our language.
 
@@
 
+We will need one extra condition on the definition of a strategy in order to make sure that the composition of two strategies satisfies the diverge-or-reply rule.
+
+\begin{definition}
+  We say a strategy $\sigma$ is \emph{compact} if it satisfies the compactness criterion given above for games: if $s\in M_A^\omega$ is an infinite sequence such that $t\in T_\sigma$ for all finite prefixes $t\ppprefix s$, then $t\in T_\sigma$.
+\end{definition}
+
+Compactness is too strong a condition for our purposes: we shall later see that it is not preserved by composition.  We shall use the following local version instead:
+
+\begin{definition}
+  We say a strategy $\sigma$ is \emph{locally compact} if whenever $s\in T_\sigma$ there is some compact strategy $\sigma'$ such that $s\in T_{\sigma'}\subset T_\sigma$ and $D_\sigma\subset D_{\sigma'}$.
+\end{definition}
+
+From now on, we shall use the word \emph{strategy} to mean \emph{locally compact strategy}.
+
 \subsection{Multiplicatives}
@@
 Let $A,B$ be games.
-If $s\in \seqs{M_A\cprd M_B}$ then we write $s\vert_A$ for the subsequence of $s$ consisting of all moves from $A$ and $s\vert_B$ for the subsequence of $s$ consisting of all moves from $B$.
+If $s\in \seqs{(M_A\cprd M_B)}$ then we write $s\vert_A$ for the subsequence of $s$ consisting of all moves from $A$ and $s\vert_B$ for the subsequence of $s$ consisting of all moves from $B$.
 We write $P_A\|P_B$ for the set of all such sequences $s$ such that $s\vert_A\in P_A$ and $s\vert_B\in P_B$.
@@
 
-To complete the proof that $T_{\comp\tau\sigma}$ is a legal trace set for a strategy, we need to show that $T_{\comp\tau\sigma}$ is closed under opponent replies and that it is locally compact.
+To complete the proof that $T_{\comp\tau\sigma}$ is a legal trace set for a strategy, we need to show that $T_{\comp\tau\sigma}$ is closed under opponent replies.
 
@@
 In either case, we have $\s a\in\sigma\|\tau$, as desired.
-  \end{proof}
-\end{proposition}
-
-\begin{proposition}\label{locallyCompactComposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $\comp\tau\sigma$ is locally compact.
-\end{proposition}
-
-In order to prove that the composition of locally compact strategies is locally compact, we are going to need some facts about deterministic strategies.
-
-\begin{definition}
-  We say a strategy $\sigma$ is \emph{deterministic} if whenever $s\in\sigma$ is an $O$-position and $a,b$ are moves such that $sa,sb\in\sigma$, then $a=b$.
-\end{definition}
-
-Deterministic strategies have the following nice technical property:
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a deterministic strategy for $A\implies B$ and let $\tau$ be a deterministic strategy for $B\implies C$.
-Then $\comp\tau\sigma$ is a deterministic strategy.
-Moreover, for any $s\in\comp\tau\sigma$, there is a unique minimal $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-  \begin{proof}
-    The idea behind the proof is that determinism of $\sigma$ and $\tau$ mean that the play in the intermediate game $B$ is completely determined (since every move played in $B$ is either a $P$-move in $A\implies B$ or a $P$-move in $B\implies C$.
-For full details, see \cite{abramskyjagadeesangames}.
-  \end{proof}
-\end{proposition}
-
-We can use this to prove the following:
-
-\begin{proposition}
-  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be compact deterministic strategies.  Then $\comp\tau\sigma$ is compact.
-  \begin{proof}
-    Let $s\in M_{A\implies C}^\omega$ be an infinite sequence such that $t\in\comp\tau\sigma$ for all finite prefixes $t\ppprefix s$.
-For each finite prefix $t$ of $s$, there is a unique minimal sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=t$.
-Writing $s$ as the limit of its finite prefixes
-    \[
-      t_1 \prefix t_2 \prefix t_3 \prefix \dots
-      \]
-    we build up a sequence
-    \[
-      \t_1 \prefix \t_2 \prefix \t_3 \prefix \dots
-      \]
-    where $\t_i$ is the unique minimal sequence in $\sigma\|\tau$ such that $\t_i\vert_{A,C}=t_i$.
-We have $\t_i\prefix\t_{i+1}$ because if we remove the last move from $\t_{i+1}$ then the resulting sequence $\u_i$ satisfies $\u_i\vert_{A,C}=t_i$ and therefore $\t_i\prefix\u_i\prefix\t_{i+1}$ by minimality of $\t_i$.
-
-    Then the limit of the sequences $\t_i\vert_{A,B}$ must be contained in $\sigma$, since $\sigma$ is compact, and similarly the limit of the sequences $\t_i\vert_{B,C}$ must be contained in $\tau$, since $\tau$ is compact.
-It follows that the limit $\t$ of the sequences $\t_i$ is contained in $\sigma\|\tau$, and therefore that $\t\vert_{A,C}=s\in\comp\tau\sigma$.
-  \end{proof}
-\end{proposition}
-
-Note that the limit of compact nondeterministic strategies need not be compact.
-
-\begin{example}
-  Let the games $I$ and $\st$ be defined as before, and let the game $\Sigma$ be the game with a unique opponent starting move and a unique player reply:
-  \[
-    \Sigma = (\{q,a\}, \{q\mapsto o, a\mapsto p\}, \{\epsilon\mapsto p,q\mapsto o,qa\mapsto p\}, \{\epsilon, q, qa\}\}
-    \]
-  Let $\bN$ be the game where the opponent asks the player to choose a natural number:
-  \[
-    \bN = \left(\{q\} \cup \bN, \{q\mapsto O, n\mapsto P\}, \{\epsilon\mapsto P,q\mapsto O,qn\mapsto P\}, \{\epsilon, q\} \cup \{qn\suchthat n\in\bN\}\right)
-    \]
-  We have a (deterministic) strategy $\sigma$ for $\bN\implies (\st\implies\Sigma)$ in which the player asks the opponent for a number $n$ and then calls the argument of $\st$ $n$ times before returning.
-For example, a play in $\sigma$ might look like this:
-  \[
-    \begin{array}{ccc}
-      \bN & \st & \Sigma \\
-      & & q \\
-      q & & \\
-      2 & & \\
-      & q & \\
-      & a & \\
-      & q & \\
-      & a & \\
-      & & a
-    \end{array}
-    \]
-  $\sigma$ is compact because there are no infinite chains of positions; indeed, the length of a play in $\sigma$ is already determined by the third move.
-
-  We have a nondeterministic strategy $?$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $?
-= P_{\bN}$ as sets of positions.
-$?$ is compact because all plays in $?$ have length at most $2$.
-
-  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $q,qqa,qqaqa,qqaqaqa,\dots$, but does not contain any limiting plays.
-So it is not compact.
-It is, however, locally compact, since it is the union of compact strategies $\sigma_n$, where $\sigma_n$ has the unique maximal play
-  \[
-    q\underbrace{qa\dots qa}_{\textrm{$n$ times}}a
-    \]
-\end{example}
-
-\begin{proposition}
-  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be (nondeterministic, locally compact) strategies.  Then $\comp\tau\sigma$ is locally compact.
-  \begin{proof}
-    Let $s\in T_{\comp\tau\sigma}$.
-Then there is some sequence $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-We have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, so, by local compactness for $\sigma$ and $\tau$, there are compact strategies $\sigma'\from A\implies B$ and $\tau'\from B\implies C$ such that $\s\vert_{A,B}\in\sigma'$ and $\s\vert_{B,C}\in\tau'$.
-After removing positions from $\sigma'$ and $\tau'$, we may assume that they are deterministic (and still compact).
-Then $\comp{\tau'}{\sigma'}$ is compact and we have $\s\vert_{A,C}\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$.
   \end{proof}
@@
 \begin{definition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We define the divergences of $\comp\tau\sigma$ as follows:
+  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We define the divergences of $\comp\tau\sigma$ as follows: first we define
   \[
-    D_{\comp\tau\sigma} = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\textrm{ and either $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$}\}
+    \sigma\dv\tau = \left\{\s\in\seqs{(M_A\cprd M_B\cprd M_C)}\;\middle|\; \mbox{\pbox{\textwidth}{\flushRight either $\s\vert_{A,B}\in D_\sigma$ and $s\vert_{B,C}\in T_\tau$ \\ or $\s\vert_{A,B}\in T_\sigma$ and $s\vert_{B,C}\in D_\tau$}}\right\}
+    \]
+  \[
+    D_{\comp\tau\sigma} = \{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}
     \]
 \end{definition}
+
+We need to show that this composition satisfies the diverge-or-reply and local compactness rules.
+
+In order to prove that the composition of locally compact strategies is locally compact, we are going to need some facts about deterministic strategies.
+
+\begin{definition}
+  We say a strategy $\sigma$ is \emph{deterministic} if whenever $s\in\sigma$ is an $O$-position and $a,b$ are moves such that $sa,sb\in\sigma$, then $a=b$.
+\end{definition}
+
+Deterministic strategies have the following nice technical property:
+
+\begin{proposition}
+  Let $A,B,C$ be games, let $\sigma$ be a deterministic strategy for $A\implies B$ and let $\tau$ be a deterministic strategy for $B\implies C$.
+Then $\comp\tau\sigma$ is a deterministic strategy.
+Moreover, for any $s\in\comp\tau\sigma$, there is a unique minimal $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
+  \begin{proof}
+    The idea behind the proof is that determinism of $\sigma$ and $\tau$ mean that the play in the intermediate game $B$ is completely determined (since every move played in $B$ is either a $P$-move in $A\implies B$ or a $P$-move in $B\implies C$.
+For full details, see \cite{abramskyjagadeesangames}.
+  \end{proof}
+\end{proposition}
+
+We can use this to prove the following:
+
+\begin{proposition}
+  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be compact deterministic strategies.  Then $\comp\tau\sigma$ is compact.
+  \begin{proof}
+    Let $s\in M_{A\implies C}^\omega$ be an infinite sequence such that $t\in\comp\tau\sigma$ for all finite prefixes $t\ppprefix s$.
+For each finite prefix $t$ of $s$, there is a unique minimal sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=t$.
+Writing $s$ as the limit of its finite prefixes
+    \[
+      t_1 \prefix t_2 \prefix t_3 \prefix \dots
+      \]
+    we build up a sequence
+    \[
+      \t_1 \prefix \t_2 \prefix \t_3 \prefix \dots
+      \]
+    where $\t_i$ is the unique minimal sequence in $\sigma\|\tau$ such that $\t_i\vert_{A,C}=t_i$.
+We have $\t_i\prefix\t_{i+1}$ because if we remove the last move from $\t_{i+1}$ then the resulting sequence $\u_i$ satisfies $\u_i\vert_{A,C}=t_i$ and therefore $\t_i\prefix\u_i\prefix\t_{i+1}$ by minimality of $\t_i$.
+
+    Then the limit of the sequences $\t_i\vert_{A,B}$ must be contained in $\sigma$, since $\sigma$ is compact, and similarly the limit of the sequences $\t_i\vert_{B,C}$ must be contained in $\tau$, since $\tau$ is compact.
+It follows that the limit $\t$ of the sequences $\t_i$ is contained in $\sigma\|\tau$, and therefore that $\t\vert_{A,C}=s\in\comp\tau\sigma$.
+  \end{proof}
+\end{proposition}
+
+Note that the composition of compact nondeterministic strategies need not be compact.
+
+\begin{example}
+  Let the games $I$ and $\st$ be defined as before, and let the game $\Sigma$ be the game with a unique opponent starting move and a unique player reply:
+  \[
+    \Sigma = (\{q,a\}, \{q\mapsto o, a\mapsto p\}, \{\epsilon\mapsto p,q\mapsto o,qa\mapsto p\}, \{\epsilon, q, qa\}\}
+    \]
+  Let $\bN$ be the game where the opponent asks the player to choose a natural number:
+  \[
+    \bN = \left(\{q\} \cup \bN, \{q\mapsto O, n\mapsto P\}, \{\epsilon\mapsto P,q\mapsto O,qn\mapsto P\}, \{\epsilon, q\} \cup \{qn\suchthat n\in\bN\}\right)
+    \]
+  We have a (deterministic) strategy $\sigma$ for $\bN\implies (\st\implies\Sigma)$ in which the player asks the opponent for a number $n$ and then calls the argument of $\st$ $n$ times before returning.
+For example, a play in $\sigma$ might look like this:
+  \[
+    \begin{array}{ccc}
+      \bN & \st & \Sigma \\
+      & & q \\
+      q & & \\
+      2 & & \\
+      & q & \\
+      & a & \\
+      & q & \\
+      & a & \\
+      & & a
+    \end{array}
+    \]
+  $\sigma$ is compact because there are no infinite chains of positions; indeed, the length of a play in $\sigma$ is already determined by the third move.
+
+  We have a nondeterministic strategy $?$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $?
+= P_{\bN}$ as sets of positions.
+$?$ is compact because all plays in $?$ have length at most $2$.
+
+  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $q,qqa,qqaqa,qqaqaqa,\dots$, but does not contain any limiting plays.
+So it is not compact.
+It is, however, locally compact, since it is the union of compact strategies $\sigma_n$, where $\sigma_n$ has the unique maximal play
+  \[
+    q\underbrace{qa\dots qa}_{\textrm{$n$ times}}a
+    \]
+\end{example}
+
+\begin{proposition}
+  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be (nondeterministic, locally compact) strategies.  Then $\comp\tau\sigma$ is locally compact.
+  \begin{proof}
+    Let $s\in T_{\comp\tau\sigma}$.
+Then there is some sequence $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
+We have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, so, by local compactness for $\sigma$ and $\tau$, there are compact strategies $\sigma'\from A\implies B$ and $\tau'\from B\implies C$ such that $\s\vert_{A,B}\in\sigma'$ and $\s\vert_{B,C}\in\tau'$.
+After removing positions from (and possibly adding divergences to) $\sigma'$ and $\tau'$, we may assume that they are deterministic (and still compact).
+Then $\comp{\tau'}{\sigma'}$ is compact and we have $\s\vert_{A,C}\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$ and $D_{\comp\tau\sigma}\subset D_{\comp{\tau'}{\sigma'}}$.
+  \end{proof}
+\end{proposition}
 
@@
 We know that such a maximal sequence must exist: if $\s_i$ are a chain of sequences from $\sigma'\|\tau'$ such that $\s_i\vert_{A,C}=s$ then their limit $\s$ (which is contained in $\sigma'\|\tau'$ by compactness of $\sigma'$ and $\tau'$) must satisfy $\s\vert_{A,C}=\s$.
-Since $s\not\in D_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\not\in D_\sigma$ and $\s\vert_{B,C}\not\in D_\tau$.
+Since $s\not\in D_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\not\in D_\sigma\subset D_{\sigma'}$ and $\s\vert_{B,C}\not\in D_\tau\subset D_{\tau'}$.
 
@@
 Suppose without loss of generality that $\s\vert_{A,B}$ is an $O$-position.
-Since $\s\vert_{A,B}\not\in D_\sigma$, there must be some move $x$ such that $\s\vert_{A,B}x\in\sigma$, since $\sigma$ satisfies the diverge-or-reply rule.
-Then we have $\s x\vert_{A,B}\in\sigma$.
-Moreover, Lemma \ref{signProfilesLemma} tells us that $\s\vert_{B,C}$ must be a $P$-position, so $\s x\vert_{B,C}\in\tau$, since $\tau$ is closed under opponent replies.
-Therefore, $\s x\in\sigma\|\tau$.
-By maximality of $\s$, $x$ must be a move in $A$ and therefore we have $sx\in\comp\sigma\tau$.
+Since $\s\vert_{A,B}\not\in D_{\sigma'}$, there must be some move $x$ such that $\s\vert_{A,B}x\in\sigma'$, since $\sigma'$ satisfies the diverge-or-reply rule.
+Then we have $\s x\vert_{A,B}\in\sigma'$.
+Moreover, Lemma \ref{signProfilesLemma} tells us that $\s\vert_{B,C}$ must be a $P$-position, so $\s x\vert_{B,C}\in\tau'$, since $\tau'$ is closed under opponent replies.
+Therefore, $\s x\in\sigma'\|\tau'$.
+By maximality of $\s$, $x$ must be a move in $A$ and therefore we have $sx\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$.
   \end{proof}
@@
 \[
-  D_{\sigma\tensor\tau} = \left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\suchthat s\vert_{A,C}\in D_\sigma,\;s\vert_{B,D}\in D_\tau\right\}
+  D_{\sigma\tensor\tau} = \left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\suchthat s\vert_{A,C}\in D_\sigma\textrm{ or }s\vert_{B,D}\in D_\tau\right\}
   \]
@@
   \]
+with divergences
+\[
+  D_{\oc\sigma} = \{s \in \oc\sigma\suchthat s\vert_{A_n,B_n}\in D_\sigma\textrm{ for some $n\in\omega$}\}
+  \]
 The proof that $\oc(\cdot)$ preserves composition is the same as for the tensor product.
@@
 
+As usual, we shall use fixed point theorems from domain theory to define the denotation of $\Y$.  The main ideas come from \cite{LairdOrdinalGames}.
+
+\subsection{The stable order on strategies}
+
+We start by defining an order on strategies.  This is the order given in \cite{mcCHFiniteND}.
+
+\begin{definition}
+  Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\stle\tau$ if:
+
+  \begin{enumerate}[1)]
+    \item $T_\sigma\subset T_\tau$
+    \item $D_\tau\subset D_\sigma$
+    \item $T_\tau\subset T_\sigma \cup D_\sigma$
+  \end{enumerate}
+\end{definition}
+
+To show that this is an order, the only non-trivial part is to show that property (3) is transitive.
+Suppose that $\sigma\stle\tau\stle\upsilon$ are strategies and that $s\in T_\upsilon\setminus T_\tau$.
+If $s\in T_\tau$, then there exists $s\in D_\sigma$, since $\sigma\stle\tau$ and if $s\not\in T_\tau$, then $s\in D_\tau\subset D_\sigma$, since $\tau\stle\upsilon$.
+Therefore, $\sigma\stle\upsilon$.
+
+\begin{proposition}
+  Let $A,B,C$ be games, let $\sigma,\sigma'$ be strategies for $A\implies B$ and let $\tau,\tau'$ be strategies for $B\implies C$.  Suppose that $\sigma\stle\sigma'$ and $\tau\stle\tau'$.  Then:
+  \[
+    \comp\tau\sigma\stle\comp{\tau'}{\sigma'}
+    \]
+  \begin{proof}
+    Since $T_\sigma\subset T_{\sigma'}$ and $T_\tau\subset T_{\tau'}$, we have $\sigma\|\tau\subset\sigma'\|\tau'$ and therefore $T_{\comp\tau\sigma}\subset T_{\comp{\tau'}{\sigma'}}$.
+
+    Now suppose that $e\in D_{\comp{\tau'}{\sigma'}}$.  We want to show that there is some $d\in D_{\comp\tau\sigma}$ such that $d\prefix e$.
+
+    We know that there exists some $\e\in\sigma'\|\tau$ such that $\e\vert_{A,C}=e$ and either $\e\vert_{A,B}\in D_{\sigma'}$ or $\e\vert_{B,C}\in D_\tau$.
+Suppose first that $\e\vert_{A,B}\in\sigma$, so $\e\in\sigma\|\tau$.
+Then we have either $\e\vert_{A,B}\in D_{\sigma'}\subset D_\sigma$ or $\e\vert_{A,B}\in D_\tau$, so $\e\vert_{A,C}=e\in D_{\comp\tau\sigma}$.
+
+    Suppose instead that $\e\vert_{A,B}\not\in\sigma$.
+We have $\e\vert_{A,B}\in\sigma'$ and $\sigma\stle\sigma'$, so there exists $d\in D_\sigma$ such that $d\prefix\e\vert_{A,B}$.
+Let $\d$ be a prefix of $\e$ such that $\d\vert_{A,B}=d$.
+Then we have $\d\vert_{A,B}\in D_\sigma$ and $\d\vert_{B,C}\in\tau$, so $\d\vert{A,C}\in\comp\tau\sigma$ and $\d\vert_{A,C}\prefix e$.
+
+    Lastly, suppose that $s\in T_{\comp\tau{\sigma'}}\setminus T_{\comp\tau\sigma}$.
+Write $s=\s\vert_{A,C}$, where $\s\in\comp\tau{\sigma'}$.
+Then $\s\vert_{A,B}\in\sigma'\setminus\sigma$, and therefore there exists $d\in D_\sigma$ such that $d\prefix\s\vert_{A,B}$.
+Let $\d\prefix\s$ be a prefix such that $\d\vert_{A,B}=d$.
+Then $\d\vert_{A,C}\in D_{\comp\tau\sigma}$ and $\d\vert_{A,C}\prefix s$.
+
+    A similar argument works in the case that $\sigma=\sigma'$.  Therefore, the result follows by transitivity of $\stle$.
+  \end{proof}
+\end{proposition}
+
+We want to get a similar result for composition in the category $\G^{\oc}$.  To do that it will suffice to prove the following result:
+
+\begin{proposition}
+  Let $A,B$ be games and let $\sigma,\tau$ be strategies for $A\implies B$ such that $\sigma\stle\tau$.  Then $\oc\sigma\stle\oc\tau$ as strategies for $\oc A\implies \oc B$.
+  \begin{proof}
+    If $s\in\oc\sigma$, then $s\vert_{A_n,B_n}\in\sigma$ for all $n$ and therefore $s\vert_{A_n,B_n}\in\sigma'$ for all $n$.  It follows that $\sigma\subset\tau$.
+
+    If $e\in\oc{\tau}$, then, since $\sigma\stle\tau$, for all $n$ either $e\vert_{A_n,B_n}\in\sigma$ or there exists $d_n\in D_\sigma$ such that $d_n\prefix e\vert_{A_n,B_n}$.
+If $e\in D_{\oc\tau}$, then $e\vert_{A_n,B_n}\in D_\tau$ for some $n$, so there is at least one $d_n$.
+We may choose a prefix $e'$ of $e$ such that $e\vert_{A_n,B_n}\prefix d_n$ whenever $d_n$ is defined and $d_n=e\vert_{A_n,B_n}$ for at least one $n$ (if at least one $d_n$ is finite, then one of the $d_n$ finishes first in $e$, and we let $e'$ be a minimal prefix of $e$ that restricts to $d_n$; if all the $d_n$ are infinite, let $e'=e$).
+Since $D_\sigma\subset\sigma$, we see that $e'\in T_{\oc \sigma}$, and since $e'\vert_{A_n,B_n}=d_n$, we have $e'\in D_{\oc\sigma}$.
+
+    Lastly, If $s\in \oc\tau\setminus\oc\sigma$, then there exists some $n$ such that $s\vert_{A_n,B_n}\in\tau\setminus\sigma$.
+Therefore, $d_n$ is defined for at least one $n$ and it follows that we may construct $e'\in D_{\oc\sigma}$ as before such that $e'\prefix s$.
+  \end{proof}
+\end{proposition}
+
+Let $A$ be a game and let $F$ be a set of strategies for $A$.  We define a strategy $\exlub F$ for $F$ by setting
+\begin{gather*}
+  T_{\exlub F} = \bigcup_{\sigma\in F}T_\sigma \\
+  D_{\exlub F} = \bigcap_{\sigma\in F}D_\sigma
+\end{gather*}
+
 \subsection{Soundness}

### 2017-03-05 nondeterminism/nondeterminism.tex
Go back to here if idea doesn't work.

@@
 \newcommand{\dv}{{\text{\lightning}}}
+\DeclareMathOperator{\pocl}{pocl}
 
@@
 
-A (nondeterministic) \emph{strategy} for a game $A$ will be given by a pair $\sigma=(T_\sigma, D_\sigma)$, where
+A nondeterministic \emph{strategy} for a game $A$ will be given by a pair $\sigma=(T_\sigma, D_\sigma)$, where
 \begin{itemize}
@@
   \item $D_\sigma\subset T_\sigma$ denotes the set of \emph{divergences} in $T_\sigma$; that is, the set of those $O$-positions in $T_\sigma$ for which Player $P$ may elect to diverge rather than respond.
-Accordingly, $\zeta_A(s)=O$ for all $s\in D_\sigma$.
+Accordingly, $\zeta_A(s)=O$ for all minimal $s\in D_\sigma$.
 If a trace has a divergent prefix, then it is divergent, so we shall follow Roscoe and insist that $D_\sigma$ be postfix-closed in $P_A^O$ (\cite{RoscoeCspInfinite}, cited in \cite{mcCHFiniteND}).
@@
 \begin{definition}
-  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  Then a \emph{strategy} for $A$ is a pair $\sigma=(T_\sigma,D_\sigma)$ such that
+  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  Then a (nondeterministic) \emph{strategy} for $A$ is a pair $\sigma=(T_\sigma,D_\sigma)$ such that
   \begin{itemize}
     \item $T_\sigma\subset P_A$ is a prefix-closed subset such that whenever $s\in T_\sigma$ is a $P$-position and $sa\in P_A$ for some move $a$, then $sa\in P_A$.
-    \item $D_\sigma\subset P_A^O$ is a postfix-closed subset.
+    \item $D_\sigma\subset P_A$ is a postfix-closed subset such that all of the minimal positions in $D_\sigma$ are $O$-positions contained in $T_\sigma$.
+In other words, if $s\in D_\sigma$, then there is some $O$-position $t\prefix s$ such that $t\in T_\sigma\cap D_\sigma$.
   \end{itemize}
 
-  $T_\sigma$ and $D_\sigma$ are required to satisfy the following totality axioms:
+  $T_\sigma$ and $D_\sigma$ are required to satisfy the following totality axiom:
   \begin{description}
@@
 
+Given a game $A$ and a subset $S\subset P_A$, we write $\pocl_A(S)$ for the postfix closure of $S$ in $P_A$; i.e.:
+\[
+  \pocl_A(S) = \{s\in P_A\suchthat t\prefix s\textrm{ for some $t\in S$}\}
+  \]
+
 \begin{definition}
@@
   \[
-    D_{\comp\tau\sigma} = \{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}
+    D_{\comp\tau\sigma} = \pocl_{A\implies C}\left(\{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}\right)
     \]
 \end{definition}
+
+\begin{proposition}
+  $D_{\comp\tau\sigma}$ is a well-defined divergence set.
+  \begin{proof}
+    $D_{\comp\tau\sigma}$ alternating by the same argument we used for $T_{\comp\tau\sigma}$, and is postfix-closed by definition.
+Now let $s\in D_{\comp\tau\sigma}$ and suppose that $\s\vert_{A,C}\prefix s$, where $\s\in \sigma\dv\tau$.
+We need to show that there is some $O$-position $t\prefix s$ such that $t\in T_{\comp\tau\sigma}\cap D_{\comp\tau\sigma}$.
+
+    Suppose first that $\s\vert_{A,B}\in D_\sigma$ and $\s\vert_{B,C}\in T_\tau$.
+Then there is some $O$-position $r\prefix \s\vert_{A,B}$ such that $r\in T_\sigma\cap D_\sigma$.
+Let $\t\prefix\s$ be some prefix such that $\t\vert_{A,B}=r$.
+Then $\t\in\sigma\|\tau\cap\sigma\dv\tau$ and so $t\coloneqq\t\vert_{A,C}\in T_{\comp\tau\sigma}\cap D_{\comp\tau\sigma}$.
+Certainly $t\prefix s$, and $t$ is an $O$-position since $r$ is, by examination of sign profiles.
+
+    The case where $\s\vert_{A,B}\in T_\sigma$ and $\s\vert_{B,C}\in D_\tau$ is similar.
+  \end{proof}
+\end{proposition}
 
@@
 
-\begin{remark}
-  Since $D_\sigma$ and $D_\tau$ consist of $O$-positions, any $\s\in\sigma\|\tau$ such that $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$ must have sign profile $POO$ or $PPO$, by Lemma \ref{signProfilesLemma}, and therefore $\s\vert_{A,C}$ must be an $O$-position.
-It follows that $D_{\comp\tau\sigma}$ consists of $O$-positions.
-\end{remark}
-
 Unlike \cite{mcCHFiniteND}, we do not need to change the definition of $D_{\comp\tau\sigma}$ to reflect divergence arising from infinite chattering.
@@
 \begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $D_{\comp\tau\sigma}$ satisfies the diverge-or-reply rule.
+  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $T_{\comp\tau\sigma}, D_{\comp\tau\sigma}$ satisfy the diverge-or-reply rule.
 
@@
   \begin{proof}
-    We claim that
+    Let
     \[
-      D_{\comp\upsilon{(\comp\tau\sigma)}} = \{\s\vert_{A,D}\suchthat\s\in\sigma\|\tau\|\upsilon\textrm{ and either $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$ or $\s\vert_{C,D}\in D_\upsilon$}\}
+      D = \left\{\s\in \seqs{(M_A \cprd M_B \cprd M_C \cprd M_D)} \;\middle|\;\mbox{\pbox{\textwidth}{\flushRight
+        either \textbf{1} $\s\vert_{A,B}\in D_\sigma$, $\s\vert_{B,C}\in T_\tau$ and $\s\vert_{C,D}\in T_\upsilon$ \\
+        or \textbf{2} $\s\vert_{A,B}\in T_\sigma$, $\s\vert_{B,C}\in D_\tau$ and $\s\vert_{C,D}\in T_\upsilon$ \\
+        or \textbf{3} $\s\vert_{A,B}\in T_\sigma$, $\s\vert_{B,C}\in T_\tau$ and $\s\vert_{C,D}\in D_\upsilon$
+      }}\right\}
       \]
+    We claim that $D_{\comp\upsilon{(\comp\tau\sigma)}}=\pocl_{A\implies D}\left(\{\s\vert_{A,D}\suchthat\s\in D\}\right)$.
 The same claim will hold for $D_{\comp{(\comp\upsilon\tau)}\sigma}$ by symmetry, completing the proof.
 
-    Let $\s\in\sigma\|\tau\|\upsilon$ be such that either $\s\vert_{A,B}\in D_\sigma$ or $\s\vert_{B,C}\in D_\tau$ or $\s\vert_{C,D}\in D_\upsilon$.
-Then either $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ or $\s\vert_{B,C}\in D_\upsilon$ and therefore $\s\vert_{A,D}\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.
+    Let $\s\in D$.
+In cases \textbf{1} and \textbf{2}, we must have $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ and $\s\vert_{C,D}\in T_\upsilon$.
+In case \textbf{3}, we have $\s\vert_{C,D}\in D_\upsilon$ and $\s\vert_{A,C}\in T_{\comp\tau\sigma}$.
+In either case, we must have $\s\vert_{A,D}\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.
 
-    Conversely, suppose that $s\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.
-By the definition of $D_{\comp\upsilon{(\comp\tau\sigma)}}$, there must be some sequence $\s\in(\comp\tau\sigma)\|\upsilon$ such that $\s\vert_{A,D}=s$ and either $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ or $\s\vert_{C,D}\in D_\upsilon$.
+    Conversely, suppose that $s\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.  Then there must be some $\t\in \seqs{(M_A\cprd M_C\cprd M_D)}$ such that $\t\vert_{A,D}\prefix s$ and either
+    \[
+      \t\vert_{A,C}\in D_{\comp\tau\sigma}\textrm{ and }\t\vert_{C,D}\in T_\upsilon
+      \]
+    or
+    \[
+      \t\vert_{A,C}\in T_{\comp\tau\sigma}\textrm{ and }\t\vert_{C,D}\in D_\upsilon
+      \]
+    In the first case, we then get a sequence $\u\in \seqs{(M_A\cprd M_B \cprd M_C)}$ such that $\u\vert_{A,C}\prefix\t\vert_{A,C}$ and either
+    \[
+      \u\vert_{A,B}\in D_\sigma\textrm{ and }\u\vert_{B,C}\in T_\tau
+      \]
+    or
+    \[
+      \u\vert_{A,B}\in T_\sigma\textrm{ and }\u\vert_{B,C}\in D_\tau
+      \]
+    By passing to a suitable prefix of $\t$, we may assume that $\u\vert_{A,C}=\t\vert_{A,C}$ (since $T_\upsilon$ is prefix-closed).
 
-    We now know that there is a sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=\s\vert_{A,C}$.
-If $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ then either $\t\vert_{A,B}\in D_\sigma$ or $\t\vert_{B,C}\in D_\tau$.
+    In the second case, we get a sequence $\u\in\sigma\|\tau$ such that $\u\vert_{A,C}=\t\vert_{A,C}$.
 
-    We now have the sequences $\s$ and $\t$ and we know that either $\t\vert_{A,B}\in D_\sigma$ or $\t\vert_{B,C}\in D_\tau$ or $\s\vert_{C,D}\in D_\upsilon$.
-By the proof of Proposition \ref{traceAssociativity}, we are able to interleave the sequences $\s$ and $\t$ to get a sequence $\u\in\sigma\|\tau\|\upsilon$ such that $\u\vert_{A,C,D}=\s$ and $\u\vert_{A,B,C}=\t$.
-Now we have either $\u\vert_{A,B}=\t\vert_{A,B}\in D_\sigma$ or $\u\vert_{B,C}=\t\vert_{B,C}\in D_\tau$ or $\u\vert_{C,D}=\s\vert_{C,D}\in D_\upsilon$.
-Moreover, $\u\vert_{A,D}=\s\vert_{A,D}=s$ and therefore $s$ is contained in the set on the right, which completes the proof.
+    By the argument from Proposition \ref{traceAssociativity}, we may interleave these two sequences $\t$ and $u$ to form a sequence $\s\in\seqs{(M_A\cprd M_B\cprd M_C\cprd M_D)}$ such that $\s\vert_{A,B,C}=\u$ and $\s\vert_{A,C,D}=\t$.
+Then it is clear that $\s\in D$ in all cases and we have $\s\vert_{A,D}=\t\vert_{A,D}\prefix s$.
   \end{proof}
@@
   \]
-(Here, we consider infinite plays to have even length).
+(Here, we consider infinite positions to have even length).
 
@@
 \begin{theorem}
-  There is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
+  Th re is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
   \begin{proof}
@@
 Suppose $s\in D_{\comp\sigma{\id_A}}$.
-Then there is a sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=s$ and either $\s\vert_{A_1,A_2}\in D_{\id_A}$ or $\s\vert_{A_2,B}\in D_\sigma$.
-Since $D_{\id_A}=\emptyset$, we must have $\s\vert_{A_2,B}\in D_\sigma$.
+Since $D_{\id_A}=\emptyset$, there is a sequence $\s\in\seqs{(M_{A_1}\cprd M_{A_2}\cprd M_B)}$ such that $\s\vert_{A_1,B}\prefix s$, $\s\vert_{A_1,B_1}\in\id_A$ and $\s\vert_{A_2,B}\in D_\sigma$.
 In particular, $\s\vert_{A_2,B}$ is an $O$-position in $A\implies B$ and so $\s\vert_{A_2}$ is a $P$-position in $A$.
 It follows by Lemma \ref{signProfilesLemma} that $\s\vert_{A_1,A_2}$ is a $P$-position in $A\implies A$; hence, it is even-length and so $\s\vert_{A_1}=\s\vert_{A_2}$.
-It follows that $s=\s\vert_{A_1,B}=\s\vert_{A_2,B}\in D_\sigma$.
-So $D_{\comp\sigma{\id_A}}\subset D_\sigma$.
+It follows that $\s\vert_{A_1,B}=\s\vert_{A_2,B}\in D_\sigma$, so $s\in D_\sigma$, since $D_\sigma$ is postfix-closed.
+Therefore, $D_{\comp\sigma{\id_A}}\subset D_\sigma$.
 
@@
 \[
-  D_{\sigma\tensor\tau} = \left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\suchthat s\vert_{A,C}\in D_\sigma\textrm{ or }s\vert_{B,D}\in D_\tau\right\}
+  D_{\sigma\tensor\tau} = \pocl\left(\left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\;\middle|\;\mbox{\pbox{\textwidth}{\flushRight
+    either $s\vert_{A,C}\in D_\sigma$ and $s\vert_{B,D}\in T_\tau$ \\
+    or $s\vert_{A,C}\in T_\sigma$ and $s\vert_{B,D}\in D_\tau$
+    }}\right\}\right)
   \]
@@
 
+    $D_{\sigma\tensor\tau}$ is postfix-closed by definition.
+If $s\in D_{\sigma\tensor\tau}$, we need to find some $O$-position $t\in T_{\sigma\tensor\tau}\cap D_{\sigma\tensor\tau}$ such that $t\prefix s$.
+By definition, we know there is some $s'\prefix s$ such that either $s'\vert_{A,C}\in D_\sigma$ and $s'\vert_{B,D}\in T_\tau$ or $s'\vert_{A,C}\in T_\sigma$ and $s'\vert_{B,D}\in D_\tau$.
+In the first case, we know that there is some $r\prefix s'\vert_{A,C}$ such that $r$ is an $O$-move in $T_\sigma\cap D_\sigma$; passing to an appropriate prefix $s''$ of $s'$, we get that $s''\vert_{A,C}=r$ and $s''\vert_{B,D}\in T_\tau$.
+Therefore, $s''\in T_{\sigma\tensor\tau}\cap D_{\sigma\tensor\tau}$.
+Moreover, $s''$ is an $O$-position, since $s''\vert_{A,C}$ is, and the claim follows since $s''\prefix s'\prefix s$.
+The proof in the other case is similar.
+
     Now we need to show that $\sigma\tensor\tau$ is locally compact.
@@
 Let $s\in\sigma\tensor\tau$.
-Then there exists compact strategies $\sigma'\from A\implies C$ and $\tau'\from B\implies D$ such that $s\vert_{A,C}\in\sigma'$ and $s\vert_{B,C}\in\tau'$.
-Then $s\in\sigma'\tensor\tau'$, which is compact.
+Then there exists a compact strategy $\sigma'$ for $A\implies C$ and $\tau'\from B\implies D$ such that $s\vert_{A,C}\in\sigma'\subset\sigma$ and $D_\sigma\subset D_{\sigma'}$ and a compact strategy $\tau'$ for $B\implies C$ such that $s\vert_{B,C}\in\tau'\subset \tau$ and $D_\tau\subset D_{\tau'}$.
+Then $s\in\sigma'\tensor\tau'$, which is compact, and we have $\sigma'\tensor\tau'\subset\sigma\tensor\tau$ and $D_{\sigma\tensor\tau}\subset D_{\sigma'\tensor\tau'}$.
 
-    Lastly, we need to show that $D_{\sigma\tensor\tau}$ satisfies diverge-or-reply.
+    Lastly, we need to show that $\sigma\tensor\tau$ satisfies diverge-or-reply.
 Indeed, suppose that $s\in\sigma\tensor\tau$ is an $O$-position and that $s\not\in D_{\sigma\tensor\tau}$.
@@
 \[
-  \oc P_A = \{s\in\seqs{M_{\oc A}} \suchthat s\vert_n\in P_A \textrm{ for all $n\in\omega$}\}
+  \oc P_A = \left\{s\in\seqs{M_{\oc A}} \suchthat s\vert_n\in P_A \textrm{ for all $n\in\omega$}\right\}
   \]
@@
 \[
-  D_{\oc\sigma} = \{s \in \oc\sigma\suchthat s\vert_{A_n,B_n}\in D_\sigma\textrm{ for some $n\in\omega$}\}
+  D_{\oc\sigma} = \pocl_{\oc A}\left(\left\{s \in \oc\sigma\;\middle|\;\mbox{\pbox{\textwidth}{\Centering
+    there exists $n\in\omega$ such that $s\vert_n\in D_\sigma$ \\
+    and for all $m\ne n$, $s\vert_m\in T_\sigma$
+  }}\right\}\right)
   \]
@@
   \begin{proof}
-    Since $T_\sigma\subset T_{\sigma'}$ and $T_\tau\subset T_{\tau'}$, we have $\sigma\|\tau\subset\sigma'\|\tau'$ and therefore $T_{\comp\tau\sigma}\subset T_{\comp{\tau'}{\sigma'}}$.
+    First suppose that $\tau=\tau'$.
 
-    Now suppose that $e\in D_{\comp{\tau'}{\sigma'}}$.  We want to show that there is some $d\in D_{\comp\tau\sigma}$ such that $d\prefix e$.
+    Since $T_\sigma\subset T_{\sigma'}$, we have $\sigma\|\tau\subset\sigma'\|\tau$ and therefore $T_{\comp\tau\sigma}\subset T_{\comp{\tau}{\sigma'}}$.
 
-    We know that there exists some $\e\in\sigma'\|\tau$ such that $\e\vert_{A,C}=e$ and either $\e\vert_{A,B}\in D_{\sigma'}$ or $\e\vert_{B,C}\in D_\tau$.
-Suppose first that $\e\vert_{A,B}\in\sigma$, so $\e\in\sigma\|\tau$.
-Then we have either $\e\vert_{A,B}\in D_{\sigma'}\subset D_\sigma$ or $\e\vert_{A,B}\in D_\tau$, so $\e\vert_{A,C}=e\in D_{\comp\tau\sigma}$.
+    Now let $e\in D_{\comp{\tau}{\sigma'}}$.
+Suppose $e\prefix\e$, where $\e\in\sigma'\dv\tau$ and suppose first that $\e\vert_{A,B}\in D_{\sigma'}$ and $\e\vert_{B,C}\in T_{\tau}$.
+Since $D_{\sigma'}\subset D_\sigma$, we have $\e\vert_{A,B}\in D_\sigma$, so $\e\in\sigma\dv\tau$ and therefore $e$, which is a postfix of $\e\vert_{A,C}$, is contained in $D_{\comp\tau\sigma}$.
 
-    Suppose instead that $\e\vert_{A,B}\not\in\sigma$.
-We have $\e\vert_{A,B}\in\sigma'$ and $\sigma\stle\sigma'$, so there exists $d\in D_\sigma$ such that $d\prefix\e\vert_{A,B}$.
-Let $\d$ be a prefix of $\e$ such that $\d\vert_{A,B}=d$.
-Then we have $\d\vert_{A,B}\in D_\sigma$ and $\d\vert_{B,C}\in\tau$, so $\d\vert{A,C}\in\comp\tau\sigma$ and $\d\vert_{A,C}\prefix e$.
+    Now suppose that $\e\vert_{A,B}\in T_{\sigma'}$ and $\e\vert_{B,C}\in D_{\tau'}$.
+Since $\sigma\stle\sigma'$, we have $\e\vert_{A,B}\in T_\sigma\cup D_\sigma$.
+If $\e\vert_{B,C}\in T_\sigma$, then we have $\e\in\sigma\dv\tau$ and so $\e\vert_{A,C}\in D_{\comp\tau\sigma}$ and therefore $e\in D_{\comp\tau\sigma}$, since $D_{\comp\tau\sigma}$ is postfix-closed.
 
-    Lastly, suppose that $s\in T_{\comp\tau{\sigma'}}\setminus T_{\comp\tau\sigma}$.
-Write $s=\s\vert_{A,C}$, where $\s\in\comp\tau{\sigma'}$.
-Then $\s\vert_{A,B}\in\sigma'\setminus\sigma$, and therefore there exists $d\in D_\sigma$ such that $d\prefix\s\vert_{A,B}$.
-Let $\d\prefix\s$ be a prefix such that $\d\vert_{A,B}=d$.
-Then $\d\vert_{A,C}\in D_{\comp\tau\sigma}$ and $\d\vert_{A,C}\prefix s$.
+    Otherwise, $\e\vert_{B,C}\in D_\sigma$.
+Then $\e\vert_{A,B}$ and $\e\vert_{B,C}$ have prefixes $q\prefix\e\vert_{A,B}$, $r\prefix\e\vert_{B,C}$ such that $q$ and $r$ are $O$-moves, $q\in T_\sigma\cap D_\sigma$ and $r\in T_\tau\cap D_\tau$.
+Passing to an appropriate prefix $\e'$ of $\e$, we have either $\e'\vert_{A,B}=q$ and $r\prefix\e'\vert_{B,C}$ or $q\prefix\e'\vert_{A,B}$ and $\e\vert_{B,C}=r$.
+In either case, $\e'\in \sigma\dv\tau$ and so $\e'\vert_{A,C}\in D_{\comp\tau\sigma}$.
+Then we have $\e'\vert_{A,C}\prefix\e\vert_{A,C}\prefix e$, and so $e\in D_{\comp\tau\sigma}$.
 
-    A similar argument works in the case that $\sigma=\sigma'$.  Therefore, the result follows by transitivity of $\stle$.
+    Lastly, suppose that $s\in T_{\comp{\tau'}{\sigma'}}\setminus T_{\comp\tau\sigma}$.
+Write $s=\s$, where $\s\in\sigma'\|\tau'$.
+Since $\s\not\in T_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\in\sigma'\setminus\sigma$.
+It follows that $\s\vert_{A,B}\in D_\sigma$ and therefore $\s\in\sigma\dv\tau$.
+Therefore, $s=\s\vert_{A,B}\in D_{\comp\tau\sigma}$.
+
+    The result follows by a similar argument in the case that $\sigma=\sigma'$.  Therefore, the full result follows from transitivity of $\stle$: if $\sigma\stle\sigma'$ and $\tau\stle\tau'$, then
+    \[
+      \comp\tau\sigma \stle \comp\tau{\sigma'} \stle \comp{\tau'}{\sigma'}
+      \]
   \end{proof}
@@
   \begin{proof}
-    If $s\in\oc\sigma$, then $s\vert_{A_n,B_n}\in\sigma$ for all $n$ and therefore $s\vert_{A_n,B_n}\in\sigma'$ for all $n$.  It follows that $\sigma\subset\tau$.
+    If $s\in\oc\sigma$, then $s\vert_{A_n,B_n}\in\sigma$ for all $n$ and therefore $s\vert_{A_n,B_n}\in\sigma'$ for all $n$.  It follows that $\oc\sigma\subset\oc\tau$.
 
-    If $e\in\oc{\tau}$, then, since $\sigma\stle\tau$, for all $n$ either $e\vert_{A_n,B_n}\in\sigma$ or there exists $d_n\in D_\sigma$ such that $d_n\prefix e\vert_{A_n,B_n}$.
-If $e\in D_{\oc\tau}$, then $e\vert_{A_n,B_n}\in D_\tau$ for some $n$, so there is at least one $d_n$.
-We may choose a prefix $e'$ of $e$ such that $e\vert_{A_n,B_n}\prefix d_n$ whenever $d_n$ is defined and $d_n=e\vert_{A_n,B_n}$ for at least one $n$ (if at least one $d_n$ is finite, then one of the $d_n$ finishes first in $e$, and we let $e'$ be a minimal prefix of $e$ that restricts to $d_n$; if all the $d_n$ are infinite, let $e'=e$).
-Since $D_\sigma\subset\sigma$, we see that $e'\in T_{\oc \sigma}$, and since $e'\vert_{A_n,B_n}=d_n$, we have $e'\in D_{\oc\sigma}$.
+    If $e\in D_{\oc\tau}$ then there exists some $e'\prefix e$ and some $n\in\omega$ such that $e'\vert_n\in D_\tau$ and $e'\vert_m\in T_\tau$ for all $m\ne n$.
 
-    Lastly, If $s\in \oc\tau\setminus\oc\sigma$, then there exists some $n$ such that $s\vert_{A_n,B_n}\in\tau\setminus\sigma$.
-Therefore, $d_n$ is defined for at least one $n$ and it follows that we may construct $e'\in D_{\oc\sigma}$ as before such that $e'\prefix s$.
+    Since $\sigma\stle\tau$, we have $D_\tau\subset D_\sigma$ and $T_\tau\subset T_\sigma\cup D_\sigma$.
+For each $m$, define a subsequence $d_n$ of $e'$ as follows: if $e'\vert_m\in T_\sigma$ then $d_m=e'\vert_m$.
+If $e'\vert_m\in D_\sigma$, then there is some prefix of $e'\vert_m$ that is an $O$-position in $T_\sigma\cap D_\sigma$.
+Let $d_m$ be the shortest such prefix of $e'\vert_m$.
+
+    We know that $e'\vert_n\in D_\tau\subset D_\sigma$, so $d_n\in D_\sigma$.
+Let $d$ be the shortest prefix of $e'$ such that there exists some $m$ such that $d_m\in D_\sigma$ and $d_m\prefix d$.
+We claim that $d\vert_k\in T_\sigma$ for all $k\neq m$.
+If $d\vert_k\prefix d_k$, then $d\vert_k\in T_\sigma$, since $d_k\in T_\sigma$.
+Otherwise, $d_k\pprefix d\vert_k$.
+But this contradicts the minimality of $d$.
+
+    Therefore, we have $d\in D_{\oc\sigma}$.  It follows that $e\in D_{\oc\sigma}$, since $D_{\oc\sigma}$ is postfix-closed.
+
+    Lastly, if $s\in \oc\tau\setminus\oc\sigma$, then there exists some $s'\prefix s$ and some $n\in\omega$ such that $s'\vert_{A_n,B_n}\in\tau\setminus\sigma$.
+Therefore, if we construct the $d_n$ as before, we have $d_n\in D_\sigma$ for at least one $n$ and it follows that we may construct $d\in D_{\oc\sigma}$ as before such that $d\prefix s'$.
+It follows that $s\in D_{\oc\sigma}$.
   \end{proof}
@@
 
-Let $A$ be a game and let $F$ be a set of strategies for $A$.  We define a strategy $\exlub F$ for $F$ by setting
+Let $A$ be a game and let $F$ be a non-empty set of strategies for $A$.  We define a strategy $\exlub F$ for $F$ by setting
 \begin{gather*}
@@
 \end{gather*}
+
+\begin{proposition}
+  If $A$ is a game and $F$ is a set of strategies for $A$ then $\exlub F$ is a strategy for $A$.
+  \begin{proof}
+    Certainly $T_{\exlub F}$ is non-empty and prefix-closed and $D_{\exlub F}$ is postfix-closed.
+Suppose $s\in T_{\exlub F}$ is a $P$-position.
+Then $s\in T_\sigma$ for some $\sigma\in F$.
+So if $sa\in P_A$ for some move $a$, then $sa\in T_\sigma$ and therefore $sa\in T_{\exlub F}$.
+
+    Let $s\in D_{\exlub F}$.  Then $s\in D_\sigma$ for all $\sigma\in F$.  It follows that 
+  \end{proof}
+\end{proposition}
 

### 2017-03-06 nondeterminism/nondeterminism.tex
Fix this if you can.

@@
 That is, $T_\sigma$ is a non-empty prefix-closed subset of $P_A$ that is closed under $O$-replies to $P$-positions: whenever $s\in T_\sigma$ is a $P$-position and $a\in M_A$ is an $O$-move such that $sa\in P_A$, then $sa\in T_\sigma$.
-We call such a set $T_\sigma$ a \emph{trace set}.
 
@@
 Accordingly, $\zeta_A(s)=O$ for all minimal $s\in D_\sigma$.
-If a trace has a divergent prefix, then it is divergent, so we shall follow Roscoe and insist that $D_\sigma$ be postfix-closed in $P_A^O$ (\cite{RoscoeCspInfinite}, cited in \cite{mcCHFiniteND}).
+If a trace has a divergent prefix, then it is divergent, so we shall follow Roscoe and insist that $D_\sigma$ be postfix-closed in $P_A$ (\cite{RoscoeCspInfinite}, cited in \cite{mcCHFiniteND}).
 \end{itemize}
@@
 
-  A consequence of the diverge-or-reply rule is that if $s\in \sigma$ is an infinite $O$-position, then there exists $t\prefix s$ such that $t\in D_\sigma$ (since it is impossible for player $P$ to reply to it, positions of length $\omega+1$ or greater being disallowed).
+  A consequence of the diverge-or-reply rule is that if $s\in \sigma$ is an infinite $O$-position, then $s\in D_\sigma$ (since it is impossible for player $P$ to reply to it, positions of length $\omega+1$ or greater being disallowed).
 This works well for our purposes; it captures our intuition that divergence should arise from some infinite behaviour, but it excludes those cases where Player $O$ is `to blame' for the infinite behaviour (passing, for example, a divergent function into the non-divergent strategy $\lambda f.f$).
@@
 
-We start by defining an order on strategies.  This is the order given in \cite{mcCHFiniteND}.
-
-\begin{definition}
+We start by defining some orders on strategies.  Our main ordering, which we shall call the \emph{stable ordering} (following \cite{LairdOrdinalGames}) is the order given in \cite{mcCHFiniteND}.
+
+\begin{definition}[Extensional order]
+  Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\exle\tau$ if:
+
+  \begin{enumerate}[1)]
+    \item $T_\sigma\subset T_\tau$
+    \item $D_\sigma\subset D_\tau$
+  \end{enumerate}
+\end{definition}
+
+The extensional order is simple to define, but it is not preserved by composition (see \cite{mcCHFiniteND} for an example).  Instead, we shall prefer the following order:
+
+\begin{definition}[Stable order]
   Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\stle\tau$ if:
@@
 
-Let $A$ be a game and let $F$ be a non-empty set of strategies for $A$.  We define a strategy $\exlub F$ for $F$ by setting
+If $A$ is a game and $S\subset P_A$ is some set, we say that $s\in S$ is \emph{minimal} if $t\not\in S$ for all proper prefixes $t\pprefix s$.
+Let $A$ be a game and let $F$ be a non-empty set of strategies for $A$ that is directed under the extensional order: so if $\sigma,\tau\in F$ then there is some $\upsilon\in F$ such that $\sigma,\tau\exle\upsilon$.
+Write $D(F) = \bigcap_{\sigma\in F}D_\sigma$.
+We define a strategy $\exlub F$ for $F$ by setting
 \begin{gather*}
-  T_{\exlub F} = \bigcup_{\sigma\in F}T_\sigma \\
-  D_{\exlub F} = \bigcap_{\sigma\in F}D_\sigma
+  T_{\exlub F} = \bigcup_{\sigma\in F}T_\sigma \cup \{s\in D(F)\suchthat\textrm{$s$ is an infinite and minimal $O$-position in $D(F)$}\} \\
+  D_{\exlub F} = D(F) \setminus \{s\in D(F)\suchthat\textrm{$s$ is an infinite and minimal $P$-position in $D(F)$}\}
 \end{gather*}
@@
 \begin{proposition}
-  If $A$ is a game and $F$ is a set of strategies for $A$ then $\exlub F$ is a strategy for $A$.
-  \begin{proof}
-    Certainly $T_{\exlub F}$ is non-empty and prefix-closed and $D_{\exlub F}$ is postfix-closed.
-Suppose $s\in T_{\exlub F}$ is a $P$-position.
-Then $s\in T_\sigma$ for some $\sigma\in F$.
-So if $sa\in P_A$ for some move $a$, then $sa\in T_\sigma$ and therefore $sa\in T_{\exlub F}$.
-
-    Let $s\in D_{\exlub F}$.  Then $s\in D_\sigma$ for all $\sigma\in F$.  It follows that 
+  If $A$ is a game and $F$ is a set of strategies for $A$ that is directed under the extensional order then $\exlub F$ is a strategy for $A$.
+  \begin{proof}
+    Certainly $T_{\exlub F}$ is non-empty.
+To show that $T_{\exlub F}$ is prefix-closed, suppose $s\in T_{\exlub F}$.
+If $s\in T_\sigma$ for some $\sigma\in F$, then $t\in T_{\exlub F}$ for all prefixes $t\prefix s$, since $T_\sigma$ is prefix closed.
+Otherwise, suppose $s\in D(F)$ is infinite and that there is some finite prefix $t\pprefix s$ such that $t\not\in T_{\exlub F}$.
+We shall show that $s$ is not minimal in $D(F)$.
+
+    We have $s\in D_\sigma$ for all $\sigma\in F$.
+So for each $\sigma\in F$, there exists some prefix $t_\sigma\prefix s$ such that $t_\sigma\in T_\sigma\cap D_\sigma$.
+If $t\prefix t_\sigma$, then $t\in T_\sigma$, which contradicts $t$ not being in $T_{\exlub F}$, so we must have $t_\sigma\prefix t$.
+Therfore, the $t_\sigma$ are finite and have length bounded by the length of $t$.
+Let $t_\tau$ be the longest of the $t_\sigma$.
+We have $t_\sigma\prefix t_\tau$ for all $\sigma\in F$, and therefore $t_\tau\in D(F)$.
+So $s$ is not minimal, proving that $T_{\exlub F}$ is prefix-closed.
+
+    Now we show that $D_{\exlub F}$ is postfix-closed.
+Let $s\in D_{\exlub F}$.
+Then $s\in D_\sigma$ for all $\sigma$.
+Suppose that $s\pprefix t$ for some $t$.
+Then $t\in D_\sigma$ for all $\sigma$, so $t\in D(F)$.
+Moreover, $t$ is certainly not minimal in $D(F)$, since it has $s$ as a proper prefix.
+Therefore, $t\in D_{\exlub F}$.
+
+    Suppose $s\in T_{\exlub F}$ is a $P$-position and that $sa\in P_A$.
+Then $s$ is certainly finite, and so $s\in T_\sigma$ for some $\sigma$.
+It follows that $sa\in T_\sigma$, so $sa\in T_{\exlub F}$.
+
+    Now suppose that $d\in D_{\exlub F}$.
+If $d$ is infinite minimal, then $d\in T_{\exlub F}\cap D_{\exlub F}$.
+Moreover, $d$ must be an $O$-position.
+Otherwise, $d$ must have some finite prefix $d'$ such that $d'\in D(F)$ (if $d$ itself is finite, we can take $d'=d$).
+Now $d'\in D_\sigma$ for all $\sigma\in F$, so for each $\sigma\in F$ there is some $O$-position $d_\sigma\prefix d'$ such that $d_\sigma\in T_\sigma\cap D_\sigma$.
+The length of the $d_\sigma$ is bounded by the length of $d'$, so there is some $\tau$ such that $d_\sigma\prefix d_\tau$ for all $\sigma\in F$.
+Then $D_\tau\in D_\sigma$ for all $\sigma\in F$, so $d_\tau\in T_{\exlub F}\cap D_{\exlub F}$.
+
+    Next we show that $\exlub F$ satisfies diverge-or-reply.
+Suppose that $s\in T_{\exlub F}$ is an $O$-position.
+If $s$ is an infinite and minimal $O$-position in $D(F)$, then in particular $s$ is in $D(F)$ and is not a $P$-position, so $s\in D_{\exlub F}$.
+Otherwise, $s\in T_\sigma$ for some $\sigma$.
+Now suppose that $s\not\in D_{\exlub F}$.
+Since $s$ is an $O$-position, this means that $s\not\in D_\tau$ for some $\tau\in F$.
+Since $F$ is directed under the extensional order, it means that there exists some $\upsilon\in F$ such that $\sigma,\tau\exle\upsilon$.
+In particular, $T_\sigma\subset T_\upsilon$ and $D_\upsilon\subset D_\tau$.
+It follows that $s\in T_\upsilon$ but $s\not\in D_\upsilon$; therefore, there exists some $a$ such that $sa\in T_\upsilon$ and so $sa\in T_{\exlub F}$.
+
+    Lastly, we need to show that $\exlub F$ is locally compact.
+Let $s\in T_{\exlub F}$.
+If $s\in T_\sigma$ for some $\sigma$ then there exists $\sigma'$ such that $\sigma'\exle\sigma$ and $s\in T_{\sigma'}$.
+Then certainly we have $\sigma'\exle\exlub F$.
+Otherwise, $s$ is an infinite and minimal $O$-position in $D(F)$.
+We may define a strategy $\sigma_s$ by:
+    \begin{gather*}
+      T_{\sigma_s} = \{t\in P_A\suchthat\textrm{for all $P$-positions $u\prefix t$, $u\prefix s$}\} \\
+      D_{\sigma_s} = P_A \setminus \{\emptyplay\}
+    \end{gather*}
+    This is the strategy where player $P$ always tries to play according to the sequence $s$ and diverges if player $O$ ever deviates from that sequence.
+It is clear that $\sigma_s$ is a valid strategy.
+We just need to show that $\sigma_s\exle \exlub F$.
+Suppose $t\in P_A$ is a $P$-position such that $t\prefix s$ and suppose for a contradiction that $t\not\in T_{\exlub F}$.
+Since $s$ is an $O$-position, $t$ must be finite.
+For each $\sigma\in F$, we know that there is some $O$-position $t_\sigma\prefix s$ such that $t_\sigma\in T_\sigma\cap D_\sigma$.
+Then for each $\sigma$, we cannot have $t\prefix t_\sigma$; otherwise, $t$ would be contained in $T_{\exlub F}$.
+Therefore, $u_\sigma\prefix t$ for all $\sigma$ and so the $u_\sigma$ are finite and have bounded length.
+It follows that there is some $u_\tau$ such that $u_\tau\in T_\sigma$ for all $\sigma\in F$, contradicting minimality of $s$.
+It follows that $t\in T_{\exlub F}$.
+We then see that $T_{\sigma_f}\subset T_{\exlub F}$, by closure under $O$-replies.
+
+    Lastly, we certainly have $D_{\exlub F}\subset D_{\sigma_s}$, since $D_{\exlub F}$ may only contain non-empty positions.
+  \end{proof}
+\end{proposition}
+
+The surprising fact is that $exlub F$ is a least upper bound for directed sets in the \emph{stable} order; i.e., sets $F$ of strategies such that if $\sigma,\tau\in F$ then there exists $\upsilon\in F$ such that
+
+\begin{proposition}
+  Let $A$ be a game and let $F$ be a set of strategies that is directed under the extensional order $\exle$.  Then $\exlub F$ is a least upper bound for $F$.
+  \begin{proof}
+    We certainly have $T_\sigma\subset T_{\exlub F}$ and $D_{\exlub F}\subset D_\sigma$ for all $\sigma\in F$.
+Now suppose that $\alpha$ is some other strategy for $A$ such that $T_\sigma\subset T_\alpha$ and $D_\alpha\subset D_\sigma$ for all $\sigma\in F$.
+Then we have
+    \begin{gather*}
+      \bigcup_{\sigma\in F}T_\sigma\subset T_\alpha \\
+      D_\alpha\subset \bigcap_{\sigma\in F} D_\sigma
+    \end{gather*}
+    Now suppose that $s$ is an infinite $O$-position in $D(F)\setminus T_\alpha$.
+We show that $s$ is not minimal in $D(F)$.
+Indeed, if $s\in D(F)$ then $s\in D_\sigma$ for all $\sigma\in F$.
+Then for each $\sigma\in F$ there exists some $s_\sigma\prefix s$ such that $s\in T_\sigma\cap D_\sigma$.
   \end{proof}

### 2017-03-06 nondeterminism/nondeterminism.tex
Back here if it doesn't work.

@@
 
-The surprising fact is that $exlub F$ is a least upper bound for directed sets in the \emph{stable} order; i.e., sets $F$ of strategies such that if $\sigma,\tau\in F$ then there exists $\upsilon\in F$ such that
-
-\begin{proposition}
-  Let $A$ be a game and let $F$ be a set of strategies that is directed under the extensional order $\exle$.  Then $\exlub F$ is a least upper bound for $F$.
+\begin{proposition}
+  Let $A$ be a game and let $F$ be a set of strategies that is directed under the extensional order $\exle$.  Then $\exlub F$ is an extensional least upper bound for $F$.
   \begin{proof}
@@
     \end{gather*}
-    Now suppose that $s$ is an infinite $O$-position in $D(F)\setminus T_\alpha$.
-We show that $s$ is not minimal in $D(F)$.
+    Now suppose that $s$ is an infinite and minimal $O$-position in $D(F)$.
+We show that $s\in T_\alpha$.
 Indeed, if $s\in D(F)$ then $s\in D_\sigma$ for all $\sigma\in F$.
-Then for each $\sigma\in F$ there exists some $s_\sigma\prefix s$ such that $s\in T_\sigma\cap D_\sigma$.
+Then for each $\sigma\in F$ there exists some $s_\sigma\prefix s$ such that $s_\sigma\in T_\sigma\cap D_\sigma$.
+Since $s$ is minimal in $D(F)$, either one of the $s_\sigma$ is equal to $s$ or the $s_\sigma$ are finite but unbounded in length.
+In the first case, we immediately see that $s\in T_\sigma\susbet T_\alpha$.
+In the second case,
   \end{proof}

### 2017-03-06 nondeterminism/nondeterminism.tex
Line 350 onwards.

--- 2017-03-05 nondeterminism/nondeterminism.tex
@@
 \begin{itemize}
-  \item $T_\sigma$ is the set of \emph{traces} of the strategy; i.e., the set of positions that can occur when player $P$ plays according to the strategy.
-That is, $T_\sigma$ is a non-empty prefix-closed subset of $P_A$ that is closed under $O$-replies to $P$-positions: whenever $s\in T_\sigma$ is a $P$-position and $a\in M_A$ is an $O$-move such that $sa\in P_A$, then $sa\in T_\sigma$.
-We call such a set $T_\sigma$ a \emph{trace set}.
+  \item $T_\sigma$ is the set of \emph{traces} of the strategy; i.e., the set of $P$-positions that can occur when player $P$ plays according to the strategy.
+That is, $T_\sigma$ is a non-empty prefix-closed subset of $P_A^P$.
 
   \item $D_\sigma\subset T_\sigma$ denotes the set of \emph{divergences} in $T_\sigma$; that is, the set of those $O$-positions in $T_\sigma$ for which Player $P$ may elect to diverge rather than respond.
-Accordingly, $\zeta_A(s)=O$ for all minimal $s\in D_\sigma$.
+Accordingly, $\zeta_A(s)=O$ for all $s\in D_\sigma$.
 If a trace has a divergent prefix, then it is divergent, so we shall follow Roscoe and insist that $D_\sigma$ be postfix-closed in $P_A^O$ (\cite{RoscoeCspInfinite}, cited in \cite{mcCHFiniteND}).
@@
   \begin{itemize}
-    \item $T_\sigma\subset P_A$ is a prefix-closed subset such that whenever $s\in T_\sigma$ is a $P$-position and $sa\in P_A$ for some move $a$, then $sa\in P_A$.
-    \item $D_\sigma\subset P_A$ is a postfix-closed subset such that all of the minimal positions in $D_\sigma$ are $O$-positions contained in $T_\sigma$.
-In other words, if $s\in D_\sigma$, then there is some $O$-position $t\prefix s$ such that $t\in T_\sigma\cap D_\sigma$.
+    \item $T_\sigma\subset P_A^P$.
+    \item $D_\sigma\subset P_A$ is a postfix-closed subset such that all of the minimal positions in $D_\sigma$ are replies to moves in $T_\sigma$ or limits of moves in $T_\sigma$.
+In other words, if $s\in D_\sigma$, then there is some $O$-position $t\prefix s$ such that $t\in D_\sigma$ and all $P$-prefixes of $t$ are contained in $T_\sigma$.
   \end{itemize}
@@
   \begin{description}
-    \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position then either $sa\in T_\sigma$ for some $P$-move $a$ or $s\in D_\sigma$.  
+    \item[Diverge-or-reply] If $s\in T_\sigma$ and $sa\in P_A$ then either $sab\in T_\sigma$ for some $P$-move $b$ or $sa\in D_\sigma$.  
   \end{description}
@@
   The diverge-or-reply rule tells us that a function must either return a value or go into an infinite loop, and corresponds to the absence of an error constant in our language.  
-
-  A consequence of the diverge-or-reply rule is that if $s\in \sigma$ is an infinite $O$-position, then there exists $t\prefix s$ such that $t\in D_\sigma$ (since it is impossible for player $P$ to reply to it, positions of length $\omega+1$ or greater being disallowed).
-This works well for our purposes; it captures our intuition that divergence should arise from some infinite behaviour, but it excludes those cases where Player $O$ is `to blame' for the infinite behaviour (passing, for example, a divergent function into the non-divergent strategy $\lambda f.f$).
 \end{definition}
@@
 \begin{definition}
-  We say a strategy $\sigma$ is \emph{compact} if it satisfies the compactness criterion given above for games: if $s\in M_A^\omega$ is an infinite sequence such that $t\in T_\sigma$ for all finite prefixes $t\ppprefix s$, then $t\in T_\sigma$.
+  We say a strategy $\sigma$ is \emph{compact} if $T_\sigma\cup D_\sigma$ satisfies the compactness criterion given above for games: if $s\in M_A^\omega$ is an infinite sequence such that $t\in T_\sigma$ for all finite $P$-prefixes $t\ppprefix s$, then $t\in T_\sigma$ or $t\in D_\sigma$.
 \end{definition}
@@
 We need to prove that $T_{\comp\tau\sigma}\subset P_{A\implies B}$.
-If $\s\in\sigma\|\tau$, then $\s\vert_{A,C}\vert_A=\s\vert_A=\s\vert_{A,B}\vert_A\in P_A$, and similarly $\s\vert_{A,C}\in P_C$, so certainly $\s\vert_{A,C}\in P_A\|P_C$.
-It will suffice, then, to show that $\s\vert_{A,C}$ is alternating with respect to $\zeta_{A\implies C}$.
+$\comp\tau\sigma$ is clearly prefix closed, and transitivity of $\Rightarrow$ proves that all positions in $T_{\comp\tau\sigma}$ are $P$-positions, so we need to show that every finite position in $T_{\comp\tau\sigma}$ has even length.
 
 \begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Suppose $s,sa\in\comp\tau\sigma$.
-Then $\zeta_{A\implies C}(s) = \neg\lambda_{A\implies C}(a)$.
+  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose $s\in\comp\tau\sigma$ is finite.  Then $s$ has even length.
   \begin{proof}
-    Write $sa=\s a\vert_{A,C}$, where $\s a\in\sigma\|\tau$.
-Then $\s\vert_{A,C}=s$.
-$s,sa$ must be finite, so, by Lemma \ref{signProfilesLemma}, neither $\s\vert_{A,B}$ nor $\s\vert_{B,C}$ may have sign profile $OP$, so we get four possible sign profiles for $\s$ giving us the following values for $\zeta_{A\implies C}(\s\vert_{A,C})$:
-    \[
-      \begin{array}{ccc|c}
-        \zeta_A(\s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_{A\implies C}(s\vert_{A,C}) \\
-        \hline
-        P & P & P & P \\
-        P & P & O & O \\
-        P & O & O & O \\
-        O & O & O & P
-      \end{array}
-      \]
-    Suppose that $a$ is an $O$-move in $A\implies C$: so $a$ is a $P$-move in $A$ or an $O$-move in $C$.
-By alternation in the component games, playing the move $a$ either turns an $O$-position in $A$ into a $P$-position in $A$ or turns a $P$-position in $C$ into an $O$-position in $C$.
-That is, we must be switching from sign profile $PPP$ to sign profile $PPO$ or from sign profile $OOO$ to sign profile $POO$.
-In either case, $s = \s\vert_{A,C}$ must be a $P$-position.
-
-    Similarly, if $a$ is a $P$-move in $A\implies C$, then switching from $\s$ to $\s a$ must move us from sign profile $PPO$ to sign profile $PPP$ or from sign profile $POO$ to sign profile $OOO$; in either case, $s$ must be an $O$-position.
-  \end{proof}
-\end{proposition}
-
-To complete the proof that $T_{\comp\tau\sigma}$ is a legal trace set for a strategy, we need to show that $T_{\comp\tau\sigma}$ is closed under opponent replies.
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.
-Suppose $s\in\comp\tau\sigma$ is a $P$-position such that $sa\in P_{A\implies C}$ for some $O$-move $a$.
-Then $sa\in\comp\tau\sigma$.
-
-  \begin{proof}
-    Write $s=\s\vert_{A,C}$, for $\s\in\sigma\|\tau$.  We show that $\s a\in\sigma\|\tau$: so $sa = \s a\vert_{A,C}\in\comp\tau\sigma$.
-
-    Since $s$ is a $P$-position, the sign profile of $\s$ must be $PPP$ or $OOO$.
-It follows that $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$ are both $P$-positions.
-Since $a$ is a $P$-move in $A\implies C$, it must be either a $P$-move in $A\implies B$ or a $P$-move in $B\implies C$, by straightforward analysis of the definitions of the $\lambda$ functions.
-It follows that either $s\vert_{A,B}a\in\sigma$ (if $a$ is a move in $A$) or that $s\vert_{B,C}a\in\tau$ (if $a$ is a move in $C$).
-In either case, we have $\s a\in\sigma\|\tau$, as desired.
+    Write $s=\s\vert_{A,C}$, where $\s\in\sigma\|\tau$.  Then we have
+    \begin{align*}
+      \length(s) & = \length(\s) - \length(\s\vert_B) \\
+       & = \length(\s\vert_{A,B}) + \length(\s\vert_{B,C} - 2\length(\s\vert_B)
+    \end{align*}
+    $\s\vert_{A,B}$ and $\s\vert_{B,C}$ both have even length, since they are $P$-positions, so the result follows.
   \end{proof}
@@
   \]
+We write $\pocl_A^P(S)$ for $\pocl_A(S)\cap P_A^P$ and $\pocl_A^O(S)$ for $\pocl_A(S)\cap P_A^O$.
 
@@
   \[
-    D_{\comp\tau\sigma} = \pocl_{A\implies C}\left(\{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}\right)
+    D_{\comp\tau\sigma} = \pocl_{A\implies C}^O\left(\{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}\right)
     \]
@@
   \begin{proof}
-    $D_{\comp\tau\sigma}$ alternating by the same argument we used for $T_{\comp\tau\sigma}$, and is postfix-closed by definition.
+    $D_{\comp\tau\sigma}$ alternating by the same argument we used for $T_{\comp\tau\sigma}$, and is postfix-closed in $P_{A\implies C}^O$ by definition.
 Now let $s\in D_{\comp\tau\sigma}$ and suppose that $\s\vert_{A,C}\prefix s$, where $\s\in \sigma\dv\tau$.
-We need to show that there is some $O$-position $t\prefix s$ such that $t\in T_{\comp\tau\sigma}\cap D_{\comp\tau\sigma}$.
+We need to show that there is some $O$-position $ta\prefix s$ such that $ta\in D_{\comp\tau\sigma}$ and $t\in T_{\comp\tau\sigma}$.
 
     Suppose first that $\s\vert_{A,B}\in D_\sigma$ and $\s\vert_{B,C}\in T_\tau$.
-Then there is some $O$-position $r\prefix \s\vert_{A,B}$ such that $r\in T_\sigma\cap D_\sigma$.
+Then there is some $O$-position $r\prefix \s\vert_{A,B}$ such that $r\in D_\sigma$ and $q\in T_\sigma$ for all $P$-prefixes $q\prefix r$.
 Let $\t\prefix\s$ be some prefix such that $\t\vert_{A,B}=r$.
-Then $\t\in\sigma\|\tau\cap\sigma\dv\tau$ and so $t\coloneqq\t\vert_{A,C}\in T_{\comp\tau\sigma}\cap D_{\comp\tau\sigma}$.
-Certainly $t\prefix s$, and $t$ is an $O$-position since $r$ is, by examination of sign profiles.
+Then $\t\in\sigma\dv\tau$ and so if we set $t=\t\vert_{A,C}$, we get that $t\in D_{\comp\tau\sigma}$.
+If $u$ is a $P$-prefix of $t$, then there is some prefix $\u$ of $\t$ such that $\u\vert_{A,C}=u$.
+Then $\u\vert_{A,B}$ is a $P$-position by examination of sign profiles and so $\u\vert_{A,B}\in T_\sigma$.
+It follows that $u\in T_{\comp\tau\sigma}$.
 
@@
 For each finite prefix $t$ of $s$, there is a unique minimal sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=t$.
-Writing $s$ as the limit of its finite prefixes
+Writing $s$ as the limit of its finite $P$-prefixes
     \[
@@
 
-    Then the limit of the sequences $\t_i\vert_{A,B}$ must be contained in $\sigma$, since $\sigma$ is compact, and similarly the limit of the sequences $\t_i\vert_{B,C}$ must be contained in $\tau$, since $\tau$ is compact.
-It follows that the limit $\t$ of the sequences $\t_i$ is contained in $\sigma\|\tau$, and therefore that $\t\vert_{A,C}=s\in\comp\tau\sigma$.
+    Then the limit of the sequences $\t_i\vert_{A,B}$ must be contained in $T_\sigma\cup D_\sigma$, since $\sigma$ is compact, and similarly the limit of the sequences $\t_i\vert_{B,C}$ must be contained in $T_\tau\cup D_\tau$, since $\tau$ is compact.
+It follows that the limit $\t$ of the sequences $\t_i$ is contained in $\sigma\|\tau\cup\sigma\dv\tau$, and therefore that $\t\vert_{A,C}=s\in T_{\comp\tau\sigma}\cup D_{\comp\tau\sigma}$.
   \end{proof}
@@
 
-  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $q,qqa,qqaqa,qqaqaqa,\dots$, but does not contain any limiting plays.
+  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $qq,qqaq,qqaqaq,qqaqaqaq,\dots$, but does not contain any limiting plays.
 So it is not compact.
@@
   \begin{gather*}
-    \sigma = \{s \prefix qaqa\dots\} \\
-    \tau = \{s \prefix *qaqa\dots\}
+    \sigma = \{s \prefix^P qaqa\dots\} \\
+    \tau = \{s \prefix^P *qaqa\dots\}
   \end{gather*}
@@
 In $\tau$, the infinite sequence $*qaqa\dots$ satisfies $\zeta_{\st}(*qaqa\dots\vert_{\st}) = \zeta_{\st}(qaqa\dots) = P$ and $\zeta_{\bot}(*qaqa\dots\vert_{\bot}) = \zeta_{\bot}(*) = O$ and so it is an $O$-position.
-As in the remark at the end of the definition of a strategy, this $O$-position can have no $P$-reply, so it (or some prefix) must be designated divergent.
 We set
@@
   \begin{proof}
-    Suppose that $s\in\comp\tau\sigma$ is an $O$-position and that $s\not\in D_{\comp\tau\sigma}$.
+    Suppose that $s\in\comp\tau\sigma$, that $sa\in P_{A\implies C}$ and that $s\not\in D_{\comp\tau\sigma}$.
 Let $\s\in\sigma\|\tau$ be such that $\s\vert_{A,C}=s$.
@@
 
-    Let $\s'\in\sigma'\|\tau'$ be maximal such that $\s'\vert_{A,C}=s$.
-We know that such a maximal sequence must exist: if $\s_i$ are a chain of sequences from $\sigma'\|\tau'$ such that $\s_i\vert_{A,C}=s$ then their limit $\s$ (which is contained in $\sigma'\|\tau'$ by compactness of $\sigma'$ and $\tau'$) must satisfy $\s\vert_{A,C}=\s$.
-Since $s\not\in D_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\not\in D_\sigma\subset D_{\sigma'}$ and $\s\vert_{B,C}\not\in D_\tau\subset D_{\tau'}$.
+    Let $\s'\in\sigma'\|\tau'$ be maximal such that $\s'a\vert_{A,C}=sa$.
+We know that such a maximal sequence must exist: if $\s_i$ are a chain of sequences from $\sigma'\|\tau'$ such that $\s_ia\vert_{A,C}=sa$ then their limit $\s$ (which is contained in $\sigma'\|\tau'$ by compactness of $\sigma'$ and $\tau'$) must satisfy $\s a\vert_{A,C}=s a$.
+Since $sa\not\in D_{\comp\tau\sigma}$, we must have $\s a\vert_{A,B}\not\in D_\sigma\subset D_{\sigma'}$ and $\s a\vert_{B,C}\not\in D_\tau\subset D_{\tau'}$.
 
-    Since $s$ is an $O$-position, one of $\s\vert_{A,B}$ and $\s\vert_{B,C}$ must be an $O$-position (by transitivity of $\Rightarrow$).
-Suppose without loss of generality that $\s\vert_{A,B}$ is an $O$-position.
-Since $\s\vert_{A,B}\not\in D_{\sigma'}$, there must be some move $x$ such that $\s\vert_{A,B}x\in\sigma'$, since $\sigma'$ satisfies the diverge-or-reply rule.
-Then we have $\s x\vert_{A,B}\in\sigma'$.
-Moreover, Lemma \ref{signProfilesLemma} tells us that $\s\vert_{B,C}$ must be a $P$-position, so $\s x\vert_{B,C}\in\tau'$, since $\tau'$ is closed under opponent replies.
-Therefore, $\s x\in\sigma'\|\tau'$.
-By maximality of $\s$, $x$ must be a move in $A$ and therefore we have $sx\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$.
+    Since $sa$ is an $O$-position, one of $\s a\vert_{A,B}$ and $\s a\vert_{B,C}$ must be an $O$-position (by transitivity of $\Rightarrow$).
+Suppose without loss of generality that $\s a\vert_{A,B}$ is an $O$-position.
+Since $\s a\vert_{A,B}\not\in D_{\sigma'}$, there must be some move $b$ such that $\s a\vert_{A,B}b\in\sigma'$, since $\sigma'$ satisfies the diverge-or-reply rule.
+Then we have $\s ab\vert_{A,B}\in\sigma'$.
+Moreover, Lemma \ref{signProfilesLemma} tells us that $\s a\vert_{B,C}$ must be a $P$-position, so $\s ab\vert_{B,C}=\s\vert_{B,C}\in\tau'$.
+Therefore, $\s ab\in\sigma'\|\tau'$.
+By maximality of $\s a$, $b$ must be a move in $A$ and therefore we have $sab\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$.
   \end{proof}
@@
       \]
-    We claim that $D_{\comp\upsilon{(\comp\tau\sigma)}}=\pocl_{A\implies D}\left(\{\s\vert_{A,D}\suchthat\s\in D\}\right)$.
+    We claim that $D_{\comp\upsilon{(\comp\tau\sigma)}}=\pocl_{A\implies D}^O\left(\{\s\vert_{A,D}\suchthat\s\in D\}\right)$.
 The same claim will hold for $D_{\comp{(\comp\upsilon\tau)}\sigma}$ by symmetry, completing the proof.
@@
 \[
-  \id_A = \{s\in P_{A_1\implies A_2}\suchthat\textrm{for all even length $t\prefix s$, $t\vert_{A_1}=t\vert_{A_2}$}\}
+  \id_A = \{s\in P_{A_1\implies A_2}^P\suchthat\textrm{for all even length $t\prefix s$, $t\vert_{A_1}=t\vert_{A_2}$}\}
   \]
@@
 \begin{theorem}
-  Th re is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
+  There is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
   \begin{proof}
@@
     We first show that $T_{\comp\sigma{\id_A}}=T_\sigma$.
-Because of closure under opponent replies, it suffices to show that $\sigma$ and $\comp\sigma{\id_A}$ contain the same $P$-positions.
-If $s$ is a $P$-position in $\comp\sigma{\id_A}$, then there is some sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=s$.
+If $s\in\comp\sigma{\id_A}$, then there is some sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=s$.
 Since $\s\vert_{A_1,B}$ is a $P$-position, it must have sign profile $PPP$ or $OOO$ by Lemma \ref{signProfilesLemma}, and therefore $\s\vert_{A_1,A_2}$ is a $P$-position, so has even length.
@@
 
-    Conversely, suppose that $s\in\sigma$ is a $P$-position.
+    Conversely, suppose that $s\in\sigma$.
 There is an obvious sequence $s^2\in\id_A$, given by copying the moves of $s\vert_A$ between copies of $A$, such that $s^2\vert_{A_1}=s^2\vert_{A_2}=s\vert_A$.
@@
 It follows by Lemma \ref{signProfilesLemma} that $\s\vert_{A_1,A_2}$ is a $P$-position in $A\implies A$; hence, it is even-length and so $\s\vert_{A_1}=\s\vert_{A_2}$.
-It follows that $\s\vert_{A_1,B}=\s\vert_{A_2,B}\in D_\sigma$, so $s\in D_\sigma$, since $D_\sigma$ is postfix-closed.
-Therefore, $D_{\comp\sigma{\id_A}}\subset D_\sigma$.
+Therefore, $\s\vert_{A_1,B}=\s\vert_{A_2,B}\in D_\sigma$, so $s\in D_\sigma$, since $D_\sigma$ is postfix-closed.
+It follows that, $D_{\comp\sigma{\id_A}}\subset D_\sigma$.
 
@@
 \[
-  D_{\sigma\tensor\tau} = \pocl\left(\left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\;\middle|\;\mbox{\pbox{\textwidth}{\flushRight
+  D_{\sigma\tensor\tau} = \pocl^O\left(\left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\;\middle|\;\mbox{\pbox{\textwidth}{\flushRight
     either $s\vert_{A,C}\in D_\sigma$ and $s\vert_{B,D}\in T_\tau$ \\
@@
   \begin{proof}
-    $\sigma\tensor\tau$ is non-empty and prefix-closed, since $\sigma$ and $\tau$ are.  To show that it is a valid trace-set, we need to show that it is closed under opponent replies.
-
-    Let $s\in\sigma\tensor\tau$ be a $P$-position and suppose that $sx\in P_{(A\tensor B)\implies (C\tensor D)}$ for some move $x$.  We start with some brief analysis of sign profiles.
-
-    By Lemma \ref{signProfilesLemma}, $s\vert_{A,B}$ and $s\vert_{C,D}$ must either both be $O$-positions or both be $P$-positions.
-If they are $P$-positions, then the only possibility for the sign profile of $s$ is:
-    \[
-      \begin{array}{cccc}
-        \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_D(s\vert_D) \\
-        \hline
-        P & P & P & P
-      \end{array}
-      \]
-    Otherwise, if they are both $O$-positions, then each of $s\vert_{A,B}$ and $s\vert_{C,D}$ may either have sign profile $OP$ or sign profile $PO$, by Lemma \ref{signProfilesLemma}.
-But now, since $s\vert_{A,C}\in\sigma\subset P_{A\implies C}$ and since $s\vert_{B,D}\in\tau\subset P_{B\implies D}$, we also see that neither $s\vert_{A,C}$ nor $s\vert_{B,D}$ may have sign profile $OP$.
-We therefore have two more possibilities for the sign profile of $s$:
-    \[
-      \begin{array}{cccc}
-        \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_D(s\vert_D) \\
-        \hline
-        P & O & P & O \\
-        O & P & O & P
-      \end{array}
-      \]
-    In all three cases, $s\vert_{A,C}$ and $s\vert_{B,D}$ are both $P$-positions.
-Since $\sigma$ and $\tau$ are both closed under opponent replies, it follows that one of them must contain the move $x$ as a reply to the current position, and therefore that $sx\in\sigma\tensor\tau$, as desired.
+    $\sigma\tensor\tau$ is non-empty and prefix-closed, since $\sigma$ and $\tau$ are.
 
     $D_{\sigma\tensor\tau}$ is postfix-closed by definition.
-If $s\in D_{\sigma\tensor\tau}$, we need to find some $O$-position $t\in T_{\sigma\tensor\tau}\cap D_{\sigma\tensor\tau}$ such that $t\prefix s$.
+If $s\in D_{\sigma\tensor\tau}$, we need to find some prefix $ta\prefix s$ such that $ta\in D_{\sigma\tensor\tau}$ and $t\in T_{\sigma\tensor\tau}$.
 By definition, we know there is some $s'\prefix s$ such that either $s'\vert_{A,C}\in D_\sigma$ and $s'\vert_{B,D}\in T_\tau$ or $s'\vert_{A,C}\in T_\sigma$ and $s'\vert_{B,D}\in D_\tau$.
-In the first case, we know that there is some $r\prefix s'\vert_{A,C}$ such that $r$ is an $O$-move in $T_\sigma\cap D_\sigma$; passing to an appropriate prefix $s''$ of $s'$, we get that $s''\vert_{A,C}=r$ and $s''\vert_{B,D}\in T_\tau$.
-Therefore, $s''\in T_{\sigma\tensor\tau}\cap D_{\sigma\tensor\tau}$.
-Moreover, $s''$ is an $O$-position, since $s''\vert_{A,C}$ is, and the claim follows since $s''\prefix s'\prefix s$.
+In the first case, we know that there is some $ra\prefix s'\vert_{A,C}$ such that $ra\in D_\sigma$ and $r\in T_\sigma$; passing to an appropriate prefix $s''$ of $s'$, we get that $s''a\vert_{A,C}=ra$ and $s''\vert_{B,D}\in T_\tau$.
+Therefore, $s''a\in D_{\sigma\tensor\tau}$ and $s''\in T_{\sigma\tensor\tau}$.
+Moreover, $s''a$ is an $O$-position, since $s''a\vert_{A,C}$ is, and the claim follows since $s''\prefix s'\prefix s$.
 The proof in the other case is similar.
@@
 We first show that if $\sigma$ and $\tau$ are compact strategies then $\sigma\tensor\tau$ is compact.
-Indeed, suppose that $s\in\sigma\tensor\tau$ is an infinite sequence such that $t\in\sigma\tensor\tau$ for all finite prefixes $t\ppprefix s$.
-Then $\sigma$ must contain all finite prefixes of $s\vert_{A,C}$, so it must contain $s\vert_{A,C}$, since $\sigma$ is compact.
-Similarly, $\tau$ must contain $s\vert_{B,D}$.
-Therefore, $s\in\sigma\tensor\tau$.
+Indeed, suppose that $s\in\sigma\tensor\tau$ is an infinite sequence such that $t\in T_{\sigma\tensor\tau}\cup D_{\sigma\tensor\tau}$ for all finite prefixes $t\ppprefix s$.
+Then $\sigma$ must contain all finite prefixes of $s\vert_{A,C}$, so one of $T_\sigma$ and $D_\sigma$ must contain $s\vert_{A,C}$, since $\sigma$ is compact.
+Similarly, one of $T_{\tau}$ and $D_\tau$ must contain $s\vert_{B,D}$.
+Therefore, $s\in T_{\sigma\tensor\tau}\cup D_{\sigma\tensor\tau}$.
 Since $s$ was arbitrary, it follows that $\sigma\tensor\tau$ is compact.
@@
     Lastly, we need to show that $\sigma\tensor\tau$ satisfies diverge-or-reply.
-Indeed, suppose that $s\in\sigma\tensor\tau$ is an $O$-position and that $s\not\in D_{\sigma\tensor\tau}$.
-Then $s\vert_{A,C}\not\in D_\sigma$ and $s\vert_{B,D}\not\in D_\tau$.
-Using Lemma \ref{signProfilesLemma}, we see that $s$ must have one of the following sign profiles:
+Indeed, suppose that $s\in\sigma\tensor\tau$, that $sa\in P_{(A\tensor B)\implies (C\tensor D)}$ and that $sa\not\in D_{\sigma\tensor\tau}$.
+Then $sa\vert_{A,C}\not\in D_\sigma$ and $sa\vert_{B,D}\not\in D_\tau$.
+Using Lemma \ref{signProfilesLemma}, we see that $sa$ must have one of the following sign profiles:
     \[
@@
       \]
-    It follows that one of $s\vert_{A,C}$ and $s\vert_{B,D}$ must be an $O$-position.
-Suppose without loss of generality that $s\vert_{A,C}$ is an $O$-position.
-Since $s\vert_{A,C}\not\in D_\sigma$, there must be some move $x$ such that $sx\in\sigma$, since $\sigma$ satisfies diverge-or-reply.
-Then we have $sx\in\sigma\tensor\tau$.
+    It follows that one of $sa\vert_{A,C}$ and $sa\vert_{B,D}$ must be an $O$-position.
+Suppose without loss of generality that $sa\vert_{A,C}$ is an $O$-position.
+Since $sa\vert_{A,C}\not\in D_\sigma$, there must be some move $b$ such that $sab\in\sigma$, since $\sigma$ satisfies diverge-or-reply.
+Then we have $sab\in\sigma\tensor\tau$.
   \end{proof}
@@
 \[
-  D_{\oc\sigma} = \pocl_{\oc A}\left(\left\{s \in \oc\sigma\;\middle|\;\mbox{\pbox{\textwidth}{\Centering
+  D_{\oc\sigma} = \pocl_{\oc A}^O\left(\left\{s \in \oc\sigma\;\middle|\;\mbox{\pbox{\textwidth}{\Centering
     there exists $n\in\omega$ such that $s\vert_n\in D_\sigma$ \\
@@
 
-We start by defining an order on strategies.  This is the order given in \cite{mcCHFiniteND}.
+We start by defining some orders on strategies.  Our ordering, which we shall call the \emph{stable ordering} (following \cite{LairdOrdinalGames}) is the order given in \cite{mcCHFiniteND}.
 
-\begin{definition}
+\begin{definition}[Stable order]
   Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\stle\tau$ if:
@@
     \item $D_\tau\subset D_\sigma$
-    \item $T_\tau\subset T_\sigma \cup D_\sigma$
+    \item $T_\tau\subset T_\sigma \cup \pocl_A^P(D_\sigma)$
   \end{enumerate}
@@
 Suppose that $\sigma\stle\tau\stle\upsilon$ are strategies and that $s\in T_\upsilon\setminus T_\tau$.
-If $s\in T_\tau$, then there exists $s\in D_\sigma$, since $\sigma\stle\tau$ and if $s\not\in T_\tau$, then $s\in D_\tau\subset D_\sigma$, since $\tau\stle\upsilon$.
+If $s\in T_\tau$, then there exists $d\in D_\sigma$ such that $d\prefix s$, since $\sigma\stle\tau$ and if $s\not\in T_\tau$, then there exists $d\in D_\tau\subset D_\sigma$ such that $d\prefix s$, since $\tau\stle\upsilon$.
 Therefore, $\sigma\stle\upsilon$.
@@
     Now let $e\in D_{\comp{\tau}{\sigma'}}$.
-Suppose $e\prefix\e$, where $\e\in\sigma'\dv\tau$ and suppose first that $\e\vert_{A,B}\in D_{\sigma'}$ and $\e\vert_{B,C}\in T_{\tau}$.
+Suppose $\e\vert_{A,C}\prefix e$, where $\e\in\sigma'\dv\tau$, and suppose first that $\e\vert_{A,B}\in D_{\sigma'}$ and $\e\vert_{B,C}\in T_{\tau}$.
 Since $D_{\sigma'}\subset D_\sigma$, we have $\e\vert_{A,B}\in D_\sigma$, so $\e\in\sigma\dv\tau$ and therefore $e$, which is a postfix of $\e\vert_{A,C}$, is contained in $D_{\comp\tau\sigma}$.
 
-    Now suppose that $\e\vert_{A,B}\in T_{\sigma'}$ and $\e\vert_{B,C}\in D_{\tau'}$.
-Since $\sigma\stle\sigma'$, we have $\e\vert_{A,B}\in T_\sigma\cup D_\sigma$.
+    Now suppose that $\e\vert_{A,B}\in T_{\sigma'}$ and $\e\vert_{B,C}\in D_{\tau}$.
+Since $\sigma\stle\sigma'$, we have $\e\vert_{A,B}\in T_\sigma\cup \pocl_A^O(D_\sigma)$.
 If $\e\vert_{B,C}\in T_\sigma$, then we have $\e\in\sigma\dv\tau$ and so $\e\vert_{A,C}\in D_{\comp\tau\sigma}$ and therefore $e\in D_{\comp\tau\sigma}$, since $D_{\comp\tau\sigma}$ is postfix-closed.
 
-    Otherwise, $\e\vert_{B,C}\in D_\sigma$.
-Then $\e\vert_{A,B}$ and $\e\vert_{B,C}$ have prefixes $q\prefix\e\vert_{A,B}$, $r\prefix\e\vert_{B,C}$ such that $q$ and $r$ are $O$-moves, $q\in T_\sigma\cap D_\sigma$ and $r\in T_\tau\cap D_\tau$.
-Passing to an appropriate prefix $\e'$ of $\e$, we have either $\e'\vert_{A,B}=q$ and $r\prefix\e'\vert_{B,C}$ or $q\prefix\e'\vert_{A,B}$ and $\e\vert_{B,C}=r$.
+    Otherwise, there exists $d\in D_\sigma$ such that $d\prefix\e\vert_{B,C}$.
+Then $\e\vert_{A,B}$ and $\e\vert_{B,C}$ have prefixes $qa\prefix\e\vert_{A,B}$, $rb\prefix\e\vert_{B,C}$ such that $qa\in D_\sigma$, $rb\in D_\tau$, $q\in T_\sigma$ and $r\in T_\tau$.
+Passing to an appropriate prefix $\e'$ of $\e$, we have either $\e'\vert_{A,B}=qa$ and $rb\prefix\e'\vert_{B,C}$ or $qa\prefix\e'\vert_{A,B}$ and $\e\vert_{B,C}=rb$.
 In either case, $\e'\in \sigma\dv\tau$ and so $\e'\vert_{A,C}\in D_{\comp\tau\sigma}$.
@@
 
-    Lastly, suppose that $s\in T_{\comp{\tau'}{\sigma'}}\setminus T_{\comp\tau\sigma}$.
-Write $s=\s$, where $\s\in\sigma'\|\tau'$.
+    Lastly, suppose that $s\in T_{\comp{\tau}{\sigma'}}\setminus T_{\comp\tau\sigma}$.
+Write $s=\s$, where $\s\in\sigma'\|\tau$.
 Since $\s\not\in T_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\in\sigma'\setminus\sigma$.
-It follows that $\s\vert_{A,B}\in D_\sigma$ and therefore $\s\in\sigma\dv\tau$.
-Therefore, $s=\s\vert_{A,B}\in D_{\comp\tau\sigma}$.
+It follows that there exists $d\in D_\sigma$ such that $d\prefix\s\vert_{A,B}$ and therefore $\s\in\sigma\dv\tau$.
+Therefore, $d\prefix\s\vert_{A,B} = s$.
 
@@
 
-    Since $\sigma\stle\tau$, we have $D_\tau\subset D_\sigma$ and $T_\tau\subset T_\sigma\cup D_\sigma$.
+    Since $\sigma\stle\tau$, we have $D_\tau\subset D_\sigma$ and $T_\tau\subset T_\sigma\cup \pocl_A^P(D_\sigma)$.
 For each $m$, define a subsequence $d_n$ of $e'$ as follows: if $e'\vert_m\in T_\sigma$ then $d_m=e'\vert_m$.
-If $e'\vert_m\in D_\sigma$, then there is some prefix of $e'\vert_m$ that is an $O$-position in $T_\sigma\cap D_\sigma$.
+If $e'\vert_m\in \pocl_A^P(D_\sigma)$, then there is some prefix of $e'\vert_m$ that is an $O$-position in $D_\sigma$ and is a reply to a position in $T_\sigma$.
 Let $d_m$ be the shortest such prefix of $e'\vert_m$.
@@
 Let $d$ be the shortest prefix of $e'$ such that there exists some $m$ such that $d_m\in D_\sigma$ and $d_m\prefix d$.
-We claim that $d\vert_k\in T_\sigma$ for all $k\neq m$.
+Write $d=d'a$.
+We claim that $a$ is the last move in $d_m$ and that $d\vert_k\in T_\sigma$ for all $k\neq m$.
+Certainly, $a$ is a move in $d_m$; otherwise, we could remove it and get a shorter sequence that still contains $d_m$ as a subsequence.
 If $d\vert_k\prefix d_k$, then $d\vert_k\in T_\sigma$, since $d_k\in T_\sigma$.
@@
 
-Let $A$ be a game and let $F$ be a non-empty set of strategies for $A$.  We define a strategy $\exlub F$ for $F$ by setting
+If $A$ is a game and $S\subset P_A$ is some set, we say that $s\in S$ is \emph{minimal} if $t\not\in S$ for all proper prefixes $t\pprefix s$.
+Let $A$ be a game and let $F$ be a non-empty set of strategies for $A$ that is directed under the extensional order: so if $\sigma,\tau\in F$ then there is some $\upsilon\in F$ such that $\sigma,\tau\exle\upsilon$.
+We define a strategy $\exlub F$ for $F$ by setting
 \begin{gather*}
@@
 \begin{proposition}
-  If $A$ is a game and $F$ is a set of strategies for $A$ then $\exlub F$ is a strategy for $A$.
+  If $A$ is a game and $F$ is a set of strategies for $A$ that is directed under the extensional order then $\exlub F$ is a strategy for $A$.
   \begin{proof}
-    Certainly $T_{\exlub F}$ is non-empty and prefix-closed and $D_{\exlub F}$ is postfix-closed.
-Suppose $s\in T_{\exlub F}$ is a $P$-position.
-Then $s\in T_\sigma$ for some $\sigma\in F$.
-So if $sa\in P_A$ for some move $a$, then $sa\in T_\sigma$ and therefore $sa\in T_{\exlub F}$.
+    $T_{\exlub F}$ is certainly non-empty and prefix-closed in $T_{\exlub F}$.  Similarly, $D_{\exlub F}$ is certainly postfix-closed.  Suppose that $s\in D_{\exlub F}$.  
+  \end{proof}
+\end{proposition}
 
-    Let $s\in D_{\exlub F}$.  Then $s\in D_\sigma$ for all $\sigma\in F$.  It follows that 
+\begin{proposition}
+  Let $A$ be a game and let $F$ be a set of strategies that is directed under the extensional order $\exle$.  Then $\exlub F$ is an extensional least upper bound for $F$.
+  \begin{proof}
+    We certainly have $T_\sigma\subset T_{\exlub F}$ and $D_{\exlub F}\subset D_\sigma$ for all $\sigma\in F$.
+Now suppose that $\alpha$ is some other strategy for $A$ such that $T_\sigma\subset T_\alpha$ and $D_\alpha\subset D_\sigma$ for all $\sigma\in F$.
+Then we have
+    \begin{gather*}
+      \bigcup_{\sigma\in F}T_\sigma\subset T_\alpha \\
+      D_\alpha\subset \bigcap_{\sigma\in F} D_\sigma
+    \end{gather*}
+    Now suppose that $s$ is an infinite and minimal $O$-position in $D(F)$.
+We show that $s\in T_\alpha$.
+Indeed, if $s\in D(F)$ then $s\in D_\sigma$ for all $\sigma\in F$.
+Then for each $\sigma\in F$ there exists some $s_\sigma\prefix s$ such that $s_\sigma\in T_\sigma\cap D_\sigma$.
+Since $s$ is minimal in $D(F)$, either one of the $s_\sigma$ is equal to $s$ or the $s_\sigma$ are finite but unbounded in length.
+In the first case, we immediately see that $s\in T_\sigma\subset T_\alpha$.
+In the second case,
   \end{proof}

### 2017-03-06 nondeterminism/nondeterminism.tex
Getting there.

@@
 \DeclareMathOperator{\pocl}{pocl}
+\newcommand{\opto}{\longrightarrow}
 
@@
   We have a nondeterministic strategy $?$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $?
-= P_{\bN}$ as sets of positions.
+= P_{\bN}^P$ as sets of positions.
 $?$ is compact because all plays in $?$ have length at most $2$.
@@
     $D_{\sigma\tensor\tau}$ is postfix-closed by definition.
-If $s\in D_{\sigma\tensor\tau}$, we need to find some prefix $ta\prefix s$ such that $ta\in D_{\sigma\tensor\tau}$ and $t\in T_{\sigma\tensor\tau}$.
+If $s\in D_{\sigma\tensor\tau}$, we need to find some prefix $t\prefix s$ such that $t\in D_{\sigma\tensor\tau}$ and $u\in T_{\sigma\tensor\tau}$ for all $P$-prefixes $u\prefix t$.
 By definition, we know there is some $s'\prefix s$ such that either $s'\vert_{A,C}\in D_\sigma$ and $s'\vert_{B,D}\in T_\tau$ or $s'\vert_{A,C}\in T_\sigma$ and $s'\vert_{B,D}\in D_\tau$.
-In the first case, we know that there is some $ra\prefix s'\vert_{A,C}$ such that $ra\in D_\sigma$ and $r\in T_\sigma$; passing to an appropriate prefix $s''$ of $s'$, we get that $s''a\vert_{A,C}=ra$ and $s''\vert_{B,D}\in T_\tau$.
-Therefore, $s''a\in D_{\sigma\tensor\tau}$ and $s''\in T_{\sigma\tensor\tau}$.
-Moreover, $s''a$ is an $O$-position, since $s''a\vert_{A,C}$ is, and the claim follows since $s''\prefix s'\prefix s$.
+In the first case, we know that there is some $r\prefix s'\vert_{A,C}$ such that $r\in D_\sigma$ and $q\in T_\sigma$ for all $P$-prefixes $q\prefix r$; passing to an appropriate prefix $s''$ of $s'$, we get that $s''\vert_{A,C}=r$ and $s''\vert_{B,D}\in T_\tau$.
+Therefore, $s''\in D_{\sigma\tensor\tau}$ and $t''\in T_{\sigma\tensor\tau}$ for all $P$-positions $t''\prefix s''$.
+Moreover, $s''$ is an $O$-position, since $s''\vert_{A,C}$ is, and the claim follows since $s''\prefix s'\prefix s$.
 The proof in the other case is similar.
@@
 
-Our base PCF type $\bN$ will be denoted by the game $\bN$ defined above, while the product and function types will be interpreted by the connectives $\tensor$ and $\iimpl$.
+Our base PCF type $\nat$ will be denoted by the game $\bN$ defined above, while the product and function types will be interpreted by the connectives $\tensor$ and $\iimpl$.
 It remains to give the denotation of each of the terms of Fair PCF as a strategy for the appropriate game.
@@
 The numerals $\underline{n}$ will each be interpreted as the strategy for $\bN$ that always returns the value $n$.
-The nondeterministic oracle $?$ will be interpreted as the strategy $?$ given at the level of trace sets by $?=P_{\bN}$.
+The nondeterministic oracle $?$ will be interpreted as the strategy $?$ given at the level of trace sets by $?=P_{\bN}^P$.
 None of these strategies have any divergent positions.
@@
 
-We start by defining some orders on strategies.  Our ordering, which we shall call the \emph{stable ordering} (following \cite{LairdOrdinalGames}) is the order given in \cite{mcCHFiniteND}.
+We start by defining some orders on strategies.  Our main ordering, which we shall call the \emph{stable ordering} (following \cite{LairdOrdinalGames}) is the order given in \cite{mcCHFiniteND}.
+
+\begin{definition}[Extensional order]
+  Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\exle\tau$ if:
+
+  \begin{enumerate}[1)]
+    \item $T_\sigma\subset T_\tau$
+    \item $D_\tau\subset D_\sigma$
+  \end{enumerate}
+\end{definition}
+
+The extensional order is simple to define, but it is not preserved by composition (see \cite{mcCHFiniteND} for an example).  Instead, we shall use the stable order, which is preserved by composition:
 
@@
     Otherwise, there exists $d\in D_\sigma$ such that $d\prefix\e\vert_{B,C}$.
-Then $\e\vert_{A,B}$ and $\e\vert_{B,C}$ have prefixes $qa\prefix\e\vert_{A,B}$, $rb\prefix\e\vert_{B,C}$ such that $qa\in D_\sigma$, $rb\in D_\tau$, $q\in T_\sigma$ and $r\in T_\tau$.
-Passing to an appropriate prefix $\e'$ of $\e$, we have either $\e'\vert_{A,B}=qa$ and $rb\prefix\e'\vert_{B,C}$ or $qa\prefix\e'\vert_{A,B}$ and $\e\vert_{B,C}=rb$.
+Then $\e\vert_{A,B}$ and $\e\vert_{B,C}$ have prefixes $q\prefix\e\vert_{A,B}$, $r\prefix\e\vert_{B,C}$ such that $q\in D_\sigma$, $r\in D_\tau$ and for all $P$-prefixes $q'\prefix q, r'\prefix r$ we have $q'\in T_\sigma$ and $r'\in T_\tau$.
+Passing to an appropriate prefix $\e'$ of $\e$, we have either $\e'\vert_{A,B}=q$ and $r\prefix\e'\vert_{B,C}$ or $q\prefix\e'\vert_{A,B}$ and $\e\vert_{B,C}=r$.
 In either case, $\e'\in \sigma\dv\tau$ and so $\e'\vert_{A,C}\in D_{\comp\tau\sigma}$.
@@
 For each $m$, define a subsequence $d_n$ of $e'$ as follows: if $e'\vert_m\in T_\sigma$ then $d_m=e'\vert_m$.
-If $e'\vert_m\in \pocl_A^P(D_\sigma)$, then there is some prefix of $e'\vert_m$ that is an $O$-position in $D_\sigma$ and is a reply to a position in $T_\sigma$.
+If $e'\vert_m\in \pocl_A^P(D_\sigma)$, then there is some prefix of $e'\vert_m$ that is an $O$-position in $D_\sigma$, all of whose $P$-prefixes are in $T_\sigma$.
 Let $d_m$ be the shortest such prefix of $e'\vert_m$.
@@
 Certainly, $a$ is a move in $d_m$; otherwise, we could remove it and get a shorter sequence that still contains $d_m$ as a subsequence.
-If $d\vert_k\prefix d_k$, then $d\vert_k\in T_\sigma$, since $d_k\in T_\sigma$.
+If $d\vert_k\prefix d_k$, then $d\vert_k\in T_\sigma$, since it is a $P$-position by examination of sign profiles.
 Otherwise, $d_k\pprefix d\vert_k$.
@@
   \begin{proof}
-    $T_{\exlub F}$ is certainly non-empty and prefix-closed in $T_{\exlub F}$.  Similarly, $D_{\exlub F}$ is certainly postfix-closed.  Suppose that $s\in D_{\exlub F}$.  
+    $T_{\exlub F}$ is certainly non-empty and prefix-closed in $T_{\exlub F}$.
+Similarly, $D_{\exlub F}$ is certainly postfix-closed.
+Suppose that $s\in D_{\exlub F}$.
+For each $\sigma\in F$, there exists some prefix $t_\sigma\prefix s$ such that $t_\sigma\in D_\sigma$ and $u\in T_\sigma$ for all $P$-prefixes $u\prefix t_\sigma$.
+Let $t$ denote the limit of the $t_\sigma$.
+Then $t$ is an $O$-position, since $s$ and the $t_\sigma$ are $O$-positions, so every $P$-prefix of $t$ is a $P$-prefix of one of the $t_\sigma$ and is therefore contained in $T_\sigma\subset T_{\exlub F}$.
+Moreover, $t\in D_\sigma$ for all $\sigma$ by postfix closure of the $D_\sigma$.
+
+    To show that $\exlub F$ satisfies diverge-or-reply, suppose that $s\in T_{\exlub F}$ and that $sa\in P_A$ is such that $sa\not\in D_{\exlub F}$.
+Then there exist $\sigma,\tau\in F$ such that $s\in T_\sigma$ and $sa\not\in D_\tau$.
+Since $F$ is directed under the extensional order, there exists some strategy $\upsilon\in F$ such that $\sigma,\tau\exle\upsilon$.
+In particular, $s\in T_\upsilon$ and $sa\not\in D_\upsilon$.
+It follows that $sab\in T_\upsilon\subset T_{\exlub F}$ for some $b$.
+Therefore, $\exlub F$ satisfies diverge-or-reply.
+
+    Lastly, we show that $\exlub F$ is locally compact.  Let $s\in T_{\exlub F}$.  Then there is some compact strategy $\sigma'$ such that $s\in T_{\sigma'}$ and $\sigma'\exle\sigma\exle\exlub F$.  
   \end{proof}
@@
 
+$\exlub F$ is clearly a least upper bound for directed sets of strategies under the extensional ordering.
+More suprisingly, $\exlub F$ is a least upper bound for directed sets of strategies under the stable ordering.
+
 \begin{proposition}
-  Let $A$ be a game and let $F$ be a set of strategies that is directed under the extensional order $\exle$.  Then $\exlub F$ is an extensional least upper bound for $F$.
+  Let $A$ be a game, and let $F$ be a set of strategies for $A$ that is directed under the stable ordering -- so if $\sigma,\tau\in F$ then there is some strategy $\upsilon\in F$ such that $\sigma,\tau\stle\upsilon$.
+Then $\exlub F$ is a least upper bound for $F$ under the ordering $\stle$.
   \begin{proof}
-    We certainly have $T_\sigma\subset T_{\exlub F}$ and $D_{\exlub F}\subset D_\sigma$ for all $\sigma\in F$.
-Now suppose that $\alpha$ is some other strategy for $A$ such that $T_\sigma\subset T_\alpha$ and $D_\alpha\subset D_\sigma$ for all $\sigma\in F$.
-Then we have
-    \begin{gather*}
-      \bigcup_{\sigma\in F}T_\sigma\subset T_\alpha \\
-      D_\alpha\subset \bigcap_{\sigma\in F} D_\sigma
-    \end{gather*}
-    Now suppose that $s$ is an infinite and minimal $O$-position in $D(F)$.
-We show that $s\in T_\alpha$.
-Indeed, if $s\in D(F)$ then $s\in D_\sigma$ for all $\sigma\in F$.
-Then for each $\sigma\in F$ there exists some $s_\sigma\prefix s$ such that $s_\sigma\in T_\sigma\cap D_\sigma$.
-Since $s$ is minimal in $D(F)$, either one of the $s_\sigma$ is equal to $s$ or the $s_\sigma$ are finite but unbounded in length.
-In the first case, we immediately see that $s\in T_\sigma\subset T_\alpha$.
-In the second case,
+    First we show that $\exlub F$ is a stable upper bound for $F$.
+Let $\sigma\in F$.
+Certainly $T_\sigma\subset T_{\exlub F}$ and $D_{\exlub F}\subset D_\sigma$, so it remains to show that $T_{\exlub F}\subset T_\sigma\cup \pocl_A^P(D_\sigma)$.
+Suppose $s\in T_{\exlub F}$.
+Then $s\in T_\tau$ for some strategy $\tau$.
+Since $F$ is stably directed, there exists some strategy $\upsilon\in F$ such that $\sigma,\tau\stle\upsilon$.
+In particular:
+    \[
+      s\in T_\upsilon \subset T_\sigma \cup \pocl_A^P(D_\sigma)
+      \]
+
+    Now suppose that $\alpha$ is a stable upper bound for $F$; we need to show that $\exlub F\stle\alpha$.
+Since we have $T_\sigma\subset T_\alpha$ and $D_\alpha\subset D_\sigma$ for all $\sigma\in F$, we have $T_{\exlub F}\subset T_\alpha$ and $D_\alpha\subset D_{\exlub F}$.
+Now suppose that $s\in T_\alpha\setminus\pocl_A^P(D_{\exlub F})$.
+Then there exists some $\sigma\in F$ such that $d\not\prefix s$ for all $d\in D_\sigma$.
+It follows that $s\in T_\alpha\setminus\pocl_A^P(D_\sigma)$; since $D_\sigma\stle D_\alpha$, we must have $s\in T_\sigma\subset T_{\exlub F}$.
   \end{proof}
@@
 \subsection{Soundness}
+
+Our proofs for soundness and adequacy follow \cite{LairdOrdinalGames}.
+
+\begin{lemma}
+  \label{jimsLemma}
+  Let $M$ be a reducible program of type $T$.  If $M\opto N$ then $\deno{N}\exle\deno{M}$.
+  \begin{proof}
+    This is easy to show inductively by analysing the reduction rules.
+  \end{proof}
+\end{lemma}
+
+\begin{theorem}[Soundness]
+  Let $M$ be a program of type $\nat$.  If $M\mustconverge$, then $D_{\deno{M}} = \emptyset$.
+  \begin{proof}
+    By Lemma \ref{jimsLemma}, 
+\end{theorem}
 

### 2017-03-08 nondeterminism/nondeterminism.tex
Getting there.
Arrrgh!

@@
 \newcommand{\opto}{\longrightarrow}
+\newcommand{\n}{{\mathtt{n}}}
+\newcommand{\IfO}{{\mathtt{If0}\;}}
+\newcommand{\suc}{{\mathtt{suc\;}}}
+\newcommand{\0}{{\mathtt{0}}}
+\newcommand{\plot}{\triangleleft}
 
@@
 
-  We have a nondeterministic strategy $?$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $?
-= P_{\bN}^P$ as sets of positions.
-$?$ is compact because all plays in $?$ have length at most $2$.
-
-  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $qq,qqaq,qqaqaq,qqaqaqaq,\dots$, but does not contain any limiting plays.
+  We have a nondeterministic strategy $\wn$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $\wn = P_{\bN}^P$ as sets of positions.
+$\wn$ is compact because all plays in $\wn$ have length at most $2$.
+
+  When we compose these strategies, the resulting strategy $\comp\sigma\wn$ contains the infinite chain of positions $qq,qqaq,qqaqaq,qqaqaqaq,\dots$, but does not contain any limiting plays.
 So it is not compact.
@@
 
-The numerals $\underline{n}$ will each be interpreted as the strategy for $\bN$ that always returns the value $n$.
-The nondeterministic oracle $?$ will be interpreted as the strategy $?$ given at the level of trace sets by $?=P_{\bN}^P$.
+The numeral $\0$ will each be interpreted as the strategy for $\bN$ that always returns the value $0$, and the function $\suc$ will be the strategy for $\bN\iimpl\bN$ that interrogates its argument and then returns a value that is one greater.
+The nondeterministic oracle $\wn$ will be interpreted as the strategy $\wn$ given at the level of trace sets by $\wn=P_{\bN}^P$.
 None of these strategies have any divergent positions.
@@
 \begin{proposition}
+  \label{compositionMonotonicSO}
   Let $A,B,C$ be games, let $\sigma,\sigma'$ be strategies for $A\implies B$ and let $\tau,\tau'$ be strategies for $B\implies C$.  Suppose that $\sigma\stle\sigma'$ and $\tau\stle\tau'$.  Then:
@@
 \begin{proposition}
+  \label{exponentiationMonotonicSO}
   Let $A,B$ be games and let $\sigma,\tau$ be strategies for $A\implies B$ such that $\sigma\stle\tau$.  Then $\oc\sigma\stle\oc\tau$ as strategies for $\oc A\implies \oc B$.
@@
 
-\subsection{Soundness}
+Now let $A$ be a game and let $\tau$ be a strategy for $A\iimpl A$.
+The set $\Strat(A)$ of strategies for $A$ is directed-complete under the stable ordering $\stle$ and map $\tau_*\from\Strat(A)\to\Strat(A)$ given by $\sigma\mapsto\icomp\tau\sigma$ is monotone with respect to $\stle$, by Propositions \ref{compositionMonotonicSO} and \ref{exponentiationMonotonicSO}.
+Therefore, by the Bourbaki-Witt theorem, there is a $\stle$-least fix-point of $\tau_*$, which we shall call $\fix_\tau$.
+
+Let $T$ be a PCF term with denotation $A$ and let $\chi_A$ be the strategy for $((A \iimpl A) \iimpl A) \iimpl ((A \iimpl A) \iimpl A)$ corresponding to the $\lambda$-term $\lambda F.\lambda f.
+f(F f)$.
+We define
+\[
+  \deno{\Y_T} = \fix_{\chi_A}
+  \]
+
+\subsection{Soundness and adequacy}
 
@@
   \label{jimsLemma}
-  Let $M$ be a reducible program of type $T$.  If $M\opto N$ then $\deno{N}\exle\deno{M}$.
-  \begin{proof}
-    This is easy to show inductively by analysing the reduction rules.
+  Let $M$ be a reducible program of type $T$.
+Let $F_M = \{N\suchthat M\opto N\}$.
+Then $T_{\deno{M}}\subset\bigcup_{N\in F_M} T_{\deno{N}}$ and $D_{\deno{M}}\subset \bigcup_{N\in F_M} D_{\deno{N}}$.
+  \begin{proof}
+    Structural induction on $M$.
+If $M=\wn$, then $F_M$ is the set of numerals, and we have $T_\wn = \bigcup_{n\in \omega} \{\emptyplay, qn\}$ and $D_\wn=\emptyset$.
+Otherwise, write $M = FN$ for some term $L$ of type $S\to T$ and some term $N$ of type $T$.
+Write $A=\deno{S}$, $B=\deno{T}$, $\sigma=\deno{N}$ and $\tau=\deno{F}$.
+So $\sigma$ is a strategy for $A$ and $\tau$ is a strategy for $A\iimpl B = \oc A \implies B$.
+If $FN$ is reducible via one of the rules
+    \[
+      \begin{tabular}{cc}
+        \inferrule{ }{(\lambda x.M)N\opto M[N/x]}
+          & \inferrule{ }{\Y M \opto M(\Y M)} \\
+        \inferrule{ }{\IfO \0 \opto \lambda x.\lambda y.x}
+          & \inferrule{ }{\IfO (\suc\n) \opto \lambda x.\lambda y.y(\n)}
+      \end{tabular}
+      \]
+    then $FN$ is not reducible via any other rule; moreover, in all of these cases, the terms on either side of the $\opto$ arrow have the same denotations (by structural induction in the case of the $\beta$-reduction).
+Now suppose that $FN$ is reducible by one of the rules
+    \[
+      \begin{tabular}{cc}
+        \inferrule{M\opto M'}{\suc M\opto \suc M'}
+          & \inferrule{M\opto M'}{\IfO M \opto \IfO M'}
+      \end{tabular}
+      \]
+    Let $s\in T_{\comp\tau\sigma}$, and write $s=\s\vert_B$, where $\s\in\sigma\|\tau$.
+By structural induction, there is some term $N'$, having denotation $\sigma'$, such that $N\to N'$ and $\s\vert_A\in T_{\sigma'}$.
+Then we have $s=\s\vert_B\in T_{\comp\tau{\sigma'}}$.
+
+    Now suppose that $d\in D_{\comp\tau\sigma}$.
+Then there is some $\d\in \oc\sigma\dv\tau$ such that $\d\vert_B\prefix d$.
+Since the denotations for $\IfO$ and $\suc$ do not contain any divergences, we must have $\d\in T_\sigma$ and $\d\vert_{\oc A}\in D_{\oc \sigma}$.
+Moreover, the denotations of $\IfO$ and $\suc$ only interrogate their argument once.
+So $\d\vert_{A_0}\in D_\sigma$ and $\d\vert_{A_n}=\emptyplay$ for $n\ne 0$.
+By structural induction there is some $N'$, having denotation $\sigma'$, such that $N\opto N'$ and $\d\vert_{A_0}\in D_{\sigma'}$, and therefore we have $\d\vert_A\in D_{\oc\sigma'}$.
+It follows that $\d\in D_{\icomp{\tau}{\sigma'}}$.
+
+    Lastly, suppose that $F N$ is reducible by the rule
+    \[
+      \begin{tabular}{c}
+        \inferrule{M\opto M'}{M N\opto M' N}
+      \end{tabular}
+      \]
+    Let $s\in T_{\comp\tau\sigma}$ and write $s=\s\vert_B$, where $\s\in\sigma\|\tau$.
+In particular, $\s\in T_\tau$.
+By structural induction, there is some term $F'$, having denotation $\tau'$, such that $F\to F'$ and $\s\in T_{\tau'}$.
+Then $s=\s\vert_B\in T_{\comp{\tau'}{\sigma}}$.
+
+    Now suppose that $d\in D_{\comp\tau\sigma}$.
+Then there is some $\d\in\oc\sigma\dv\tau$ such that $\d\vert_B\prefix d$.
+Suppose first that $\d\vert_A\in D_{\oc\sigma}$ and that $\d\in T_\tau$.
+By structural induction, there is some $F'$, having denotation $\tau'$, such that $F\to F'$ and $\d\in T_{\tau'}$.
+Then $\d\in\oc\sigma\dv\tau'$, so $\d\vert_B\in D_{\comp{\tau'}\sigma}$.
+
+    Suppose instead that $\d\vert_A\in T_{\oc\sigma}$ and that $\d\in D_\tau$.
+By structural induction, there is some $F'$, having denotation $\tau'$, such that $F\to F'$ and $\d\in D_{\tau'}$.
+Then $\d\in\oc\sigma\dv\tau'$, so $\d\vert_B\in D_{\tau'}$.
   \end{proof}
@@
 
-\begin{theorem}[Soundness]
+\begin{theorem}[Consistency]
   Let $M$ be a program of type $\nat$.  If $M\mustconverge$, then $D_{\deno{M}} = \emptyset$.
   \begin{proof}
-    By Lemma \ref{jimsLemma}, 
+    Suppose $d\in D_{\deno M}$.
+The only irreducible programs of type $\nat$ are the numerals, whose denotations do not contain any divergences, so $M$ must be reducible.
+Therefore, by Lemma \ref{jimsLemma}, there exists some $M_1$ such that $M\to M_1$ and $d\in D_{\deno {M_1}}$.
+So $M_1$ is reducible and we may apply Lemma \ref{jimsLemma} again to get a term $M_2$ such that $M_1\to M_2$ and $d\in D_{\deno {M_2}}$.
+We keep on applying Lemma \ref{jimsLemma} and build up a sequence $M\to M_1\to M_2\to M_3\to\cdots$.
+Therefore, $M\not\mustconverge$.
+  \end{proof}
 \end{theorem}
 
-\subsection{Adequacy}
-
-I don't think I'll have a full abstraction result yet, but I could add a section explaining how this model gives us some progress towards full abstraction.
+To prove computational adequacy, we define Plotkin-style approximation relations (\cite{PlotkinApRels}, cited in \cite{LairdOrdinalGames}).
+
+\begin{definition}
+  For each PCF type $T$, we define a relation $\plot_T$ between strategies for $\deno{T}$ and closed terms of type $T$:
+
+  \begin{itemize}
+    \item $\sigma \plot_\nat M$ if $M\not\mustconverge$ implies that $q\in D_\sigma$ and $qn\in T_\sigma$ implies that $M\opto^* \n$.
+    \item $\tau \plot_{S\to T} P$ if $\sigma\plot_S N$ implies that $\comp\tau\sigma \plot_T P N$
+  \end{itemize}
+\end{definition}
+
+\begin{lemma}
+  \begin{enumerate}[i)]
+    \item If $M$ is a term of type $\nat$ such that $M\opto N$ for some unique term $N$, and if $\sigma\plot_\nat N$, then $\sigma\plot_\nat M$
+    \item If $M$ is a term of type $T$ and $\sigma,\tau$ are strategies for $\deno{M}$ such that $\sigma\stle\tau$, and if $\tau\plot_TM$, then $\sigma\plot_TM$.
+    \item If $M$ is a term of type $T$ and $F$ is a stably directed set of strategies for $\deno{M}$ such that $\sigma\plot_TM$ for all $\sigma\in F$, then $\exlub F\plot_TM$.  
+  \end{enumerate}
+  \begin{proof}
+    \begin{enumerate}[(i):]
+      \item Suppose $M\opto N$ for some unique term $N$ and suppose that $\sigma\plot_\nat N$.
+Then, if $M\not\mustconverge$, we must have $N\not\mustconverge$.
+Therefore, $q\in D_\sigma$.
+Suppose $qn\in T_\sigma$.
+Then $N\opto^*\n$, so $N\opto^*\n$.
+      \item Structural induction on $T$.
+let $M$ be a term of type $\nat$.
+Suppose $\sigma,\tau$ are strategies for $\bN$, that $\sigma\stle\tau$ and that $\tau\plot_T M$.
+If $M\not\mustconverge$, then $q\in D_\tau$, so $q\in D_\sigma$.
+If $qn\in T_\sigma$, then $qn\in T_\tau$, so $M\opto^*\n$.
+
+        Now let $P$ be a term of type $S\to T$.
+Write $A=\deno{S}$ and $B=\deno{T}$.
+Suppose that $\tau,\tau'$ are strategies for $A\iimpl B$ such that $\tau\stle\tau'$ and such that $\tau'\plot_{S\to T}P$.
+Suppose that $\sigma\plot_SN$ for some term $N$ of type $S$.
+Then $\icomp{\tau'}{\sigma}\plot_TPN$.
+Since $\tau\stle\tau'$, $\icomp{\tau}{\sigma}\stle\icomp{\tau'}{\sigma}$, by Propositions \ref{compositionMonotonicSO} and \ref{exponentiationMonotonicSO}.
+Therefore, by structural induction, we have $\icomp{\tau}{\sigma}\plot_TPN$.
+Since $\sigma,N$ were abitrary, it follows that $\tau\plot_{S\to T}P$.
+      \item Structural induction on $T$.
+Let $M$ be a term of type $\nat$ and let $F$ be a stably directed set of strategies for $\bN$ such that $\sigma\plot_TM$ for all $\sigma\in F$.
+Suppose $M\not\mustconverge$.
+Then $q\in D_\sigma$ for all $\sigma\in F$, so $q\in D_{\exlub F}$.
+Now suppose that $qn\in T_{\exlub F}$.
+Then $qn\in T_\sigma$ for some $\sigma\in F$, and so $M\opto^*\n$.
+
+        Now let $P$ be a term of type $S\to T$.
+Write $A=\deno{S}$ and $B=\deno{T}$.
+Suppose that $F$ is a stably directed set of strategies for $A\iimpl B$ such that $\tau\plot_{S\to T}P$ for all $\tau\in F$.
+Let $N$ be a term of type $S$ and let $\sigma$ be a strategy for $A$ such that $\sigma\plot_SN$.
+Then $\icomp\tau\sigma\plot_TPN$ for all $\tau\in F$.
+By structural induction, $\exlub_{\tau\in F}(\icomp\tau\sigma)\plot_TPN$.
+Now
+        \qedhere
+    \end{enumerate}
+  \end{proof}
+\end{lemma}
 

### 2017-03-10 nondeterminism/paper/nondeterminism.tex
Major changes.

--- 2017-03-08 nondeterminism/nondeterminism.tex
@@
-\documentclass{article}
-
-\input{../common/preamble}
+\documentclass{entcs} \usepackage{prentcsmacro}
+\sloppy
+% The following is enclosed to allow easy detection of differences in
+% ascii coding.
+% Upper-case    A B C D E F G H I J K L M N O P Q R S T U V W X Y Z
+% Lower-case    a b c d e f g h i j k l m n o p q r s t u v w x y z
+% Digits        0 1 2 3 4 5 6 7 8 9
+% Exclamation   !           Double quote "          Hash (number) #
+% Dollar        $           Percent      %          Ampersand     &
+% Acute accent  '           Left paren   (          Right paren   )
+% Asterisk      *           Plus         +          Comma         ,
+% Minus         -           Point        .          Solidus       /
+% Colon         :           Semicolon    ;          Less than     <
+% Equals        =3D           Greater than >          Question mark ?
+% At            @           Left bracket [          Backslash     \
+% Right bracket ]           Circumflex   ^          Underscore    _
+% Grave accent  `           Left brace   {          Vertical bar  |
+% Right brace   }           Tilde        ~
+
+\input{preamble}
 
 \newcommand{\stle}{{\;\le_s\;}}
+\newcommand{\steq}{{\;=_s\;}}
 \newcommand{\exle}{\sqsubseteq}
 \newcommand{\exlub}{\bigsqcup}
-\newcommand{\dv}{{\text{\lightning}}}
+\newcommand{\dv}{{\lightning}}
 \DeclareMathOperator{\pocl}{pocl}
@@
 \newcommand{\plot}{\triangleleft}
-
-\title{Transfinite Games for Countable Nondeterminism}
-
+\newcommand{\shad}{\mathfrak{S}}
+\newcommand{\tree}{\mathfrak{T}}
+\newcommand{\Tau}{T}
+\newcommand{\Chi}{X}
+
+\def\lastname{Gowers}
 \begin{document}
+\begin{frontmatter}
+  \title{A sound and adequate game semantics for PCF with countable nondeterminism} \author{John
+    Gowers\thanksref{ALL}\thanksref{myemail}}
+  \address{Department of Computer Science \\ University of Bath \\
+    Bath, United Kingdom} \thanks[ALL]{The author is indebted to
+    his supervisor, Jim Laird, without whose research and guidance
+    this paper could not have been written.} \thanks[myemail]{Email:
+    \href{mailto:wjg27@bath.ac.uk} {\texttt{\normalshape
+        W.J.Gowers@bath.ac.uk}}} 
+\begin{abstract} 
+  We give a sound and adequate game semantics for a simple extension of PCF with countable nondeterminism, given in \cite{LairdOrdinalGames}.
+The model is based on the model of idealized Algol with finite nondeterminism given by Harmer and McCusker \cite{mccHFiniteND} with extra information about infinite plays in order to accommodate infinite nondeterminism.
+Our proof of soundness for the model is standard, but the proof of adequacy makes use of a new technique that is linked to the possibly transfinite complexity of evaluation trees in the presence of countable nondeterminism.
+\end{abstract}
+\begin{keyword}
+  Game semantics, countable nondeterminism, ordinal complexity
+\end{keyword}
+\end{frontmatter}
 
@@
   \begin{itemize}
-    \item $T_\sigma\subset P_A^P$.
+    \item $T_\sigma\subset P_A^P$ is prefix-closed.
     \item $D_\sigma\subset P_A$ is a postfix-closed subset such that all of the minimal positions in $D_\sigma$ are replies to moves in $T_\sigma$ or limits of moves in $T_\sigma$.
@@
   If $s\in P_{A\tensor B}$ is a finite position, then $s$ cannot have sign profile $OO$.  If $s\in P_{A\implies B}$ is a finite position then $s$ cannot have sign profile $OP$.  
+\end{lemma}
 \begin{proof}
@@
 \end{proof}
-\end{lemma}
-
-\begin{proof}[Proof of Proposition \ref{TensorImpliesWellFormed}]
+
+\begin{proof*}{Proof of Proposition \ref{TensorImpliesWellFormed}}
   Alternation is part of the definition and negativity is implied by the equations $P\wedge P = P$ and $P\Rightarrow P = P$.
@@
   The proof for the linear implication is similar.
-\end{proof}
+\end{proof*}
 
@@
   Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose $s\in\comp\tau\sigma$ is finite.  Then $s$ has even length.
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-\end{proposition}
 
@@
 
+\end{proposition}
   \begin{proof}
@@
   \end{proof}
-\end{proposition}
 
@@
   $D_{\comp\tau\sigma}$ is a well-defined divergence set.
+\end{proposition}
   \begin{proof}
@@
 Moreover, for any $s\in\comp\tau\sigma$, there is a unique minimal $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
+\end{proposition}
   \begin{proof}
@@
   Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be compact deterministic strategies.  Then $\comp\tau\sigma$ is compact.
+\end{proposition}
   \begin{proof}
@@
   Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be (nondeterministic, locally compact) strategies.  Then $\comp\tau\sigma$ is locally compact.
+\end{proposition}
   \begin{proof}
@@
     \]
+\end{proposition}
   \begin{proof}
@@
   There is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
+\end{theorem}
   \begin{proof}
@@
   \end{proof}
-\end{theorem}
 
@@
   $\sigma\tensor\tau$ is a valid strategy for $(A\tensor B)\implies (C\tensor D)$
+\end{proposition}
   \begin{proof}
@@
   $\oc A$ is a well formed game.
+\end{proposition}
   \begin{proof}
@@
   Let $A,B$ be games and let $\sigma,\tau$ be strategies for $A\implies B$ such that $\sigma\stle\tau$.  Then $\oc\sigma\stle\oc\tau$ as strategies for $\oc A\implies \oc B$.
+\end{proposition}
   \begin{proof}
@@
   If $A$ is a game and $F$ is a set of strategies for $A$ that is directed under the extensional order then $\exlub F$ is a strategy for $A$.
+\end{proposition}
   \begin{proof}
@@
 \begin{proposition}
+  \label{exlubIsStlub}
   Let $A$ be a game, and let $F$ be a set of strategies for $A$ that is directed under the stable ordering -- so if $\sigma,\tau\in F$ then there is some strategy $\upsilon\in F$ such that $\sigma,\tau\stle\upsilon$.
 Then $\exlub F$ is a least upper bound for $F$ under the ordering $\stle$.
+\end{proposition}
   \begin{proof}
@@
 
-\subsection{Soundness and adequacy}
+\subsection{Consistency}
 
 Our proofs for soundness and adequacy follow \cite{LairdOrdinalGames}.
+However, we are forced to use a new technique to prove adequacy, because unlike the model given in \cite{LairdOrdinalGames}, our model does not have the property that function application is continuous with respect to functions in the stable order.
 
@@
 Then $T_{\deno{M}}\subset\bigcup_{N\in F_M} T_{\deno{N}}$ and $D_{\deno{M}}\subset \bigcup_{N\in F_M} D_{\deno{N}}$.
+\end{lemma}
   \begin{proof}
@@
   \end{proof}
-\end{lemma}
 
@@
   Let $M$ be a program of type $\nat$.  If $M\mustconverge$, then $D_{\deno{M}} = \emptyset$.
+\end{theorem}
   \begin{proof}
@@
     \item $\sigma \plot_\nat M$ if $M\not\mustconverge$ implies that $q\in D_\sigma$ and $qn\in T_\sigma$ implies that $M\opto^* \n$.
-    \item $\tau \plot_{S\to T} P$ if $\sigma\plot_S N$ implies that $\comp\tau\sigma \plot_T P N$
+    \item $\tau \plot_{S\to T} P$ if $\sigma\plot_S N$ implies that $\icomp\tau\sigma \plot_T P N$
   \end{itemize}
@@
 \begin{lemma}
-  \begin{enumerate}[i)]
-    \item If $M$ is a term of type $\nat$ such that $M\opto N$ for some unique term $N$, and if $\sigma\plot_\nat N$, then $\sigma\plot_\nat M$
-    \item If $M$ is a term of type $T$ and $\sigma,\tau$ are strategies for $\deno{M}$ such that $\sigma\stle\tau$, and if $\tau\plot_TM$, then $\sigma\plot_TM$.
-    \item If $M$ is a term of type $T$ and $F$ is a stably directed set of strategies for $\deno{M}$ such that $\sigma\plot_TM$ for all $\sigma\in F$, then $\exlub F\plot_TM$.  
-  \end{enumerate}
-  \begin{proof}
-    \begin{enumerate}[(i):]
-      \item Suppose $M\opto N$ for some unique term $N$ and suppose that $\sigma\plot_\nat N$.
+  \label{jims2ndLemma}
+  i) If $M$ is a term of type $\nat$ such that $M\opto N$ for some unique term $N$, and if $\sigma\plot_\nat N$, then $\sigma\plot_\nat M$
+
+  ii) If $M$ is a term of type $T$ and $\sigma,\tau$ are strategies for $\deno{M}$ such that $\sigma\stle\tau$, and if $\tau\plot_TM$, then $\sigma\plot_TM$.
+\end{lemma}
+  \begin{proof}
+    (i): Suppose $M\opto N$ for some unique term $N$ and suppose that $\sigma\plot_\nat N$.
 Then, if $M\not\mustconverge$, we must have $N\not\mustconverge$.
@@
 Then $N\opto^*\n$, so $N\opto^*\n$.
-      \item Structural induction on $T$.
+
+    (ii): Structural induction on $T$.
 let $M$ be a term of type $\nat$.
@@
 Since $\sigma,N$ were abitrary, it follows that $\tau\plot_{S\to T}P$.
-      \item Structural induction on $T$.
-Let $M$ be a term of type $\nat$ and let $F$ be a stably directed set of strategies for $\bN$ such that $\sigma\plot_TM$ for all $\sigma\in F$.
-Suppose $M\not\mustconverge$.
-Then $q\in D_\sigma$ for all $\sigma\in F$, so $q\in D_{\exlub F}$.
-Now suppose that $qn\in T_{\exlub F}$.
-Then $qn\in T_\sigma$ for some $\sigma\in F$, and so $M\opto^*\n$.
-
-        Now let $P$ be a term of type $S\to T$.
-Write $A=\deno{S}$ and $B=\deno{T}$.
-Suppose that $F$ is a stably directed set of strategies for $A\iimpl B$ such that $\tau\plot_{S\to T}P$ for all $\tau\in F$.
-Let $N$ be a term of type $S$ and let $\sigma$ be a strategy for $A$ such that $\sigma\plot_SN$.
-Then $\icomp\tau\sigma\plot_TPN$ for all $\tau\in F$.
-By structural induction, $\exlub_{\tau\in F}(\icomp\tau\sigma)\plot_TPN$.
-Now
-        \qedhere
-    \end{enumerate}
-  \end{proof}
+  \end{proof}
+
+In order to prove adequacy, it will suffice to show that $\deno{M}\plot_TM$ for all terms $M$ of type $T$.
+In most cases, this is a simple induction.
+The only tricky part will be showing that it is true for the recursion combinator.
+
+\begin{lemma}
+  \label{jimY}
+  Let $T$ be a PCF type.  Then $\deno{\Y_T}\plot_{(T\to T)\to T}\Y_T$.
 \end{lemma}
 
-\bibliographystyle{alpha}
-\bibliography{../common/phd_bibliography}
+  In order to show this, we would like to be able to say that if $F$ is a stably directed set of strategies for $\deno{T}$ such that $\sigma\plot_T M$ for all $\sigma\in F$, then $\exlub F\plot_TM$, but it seems difficult to prove this, since function application is not continuous with respect to functions.
+Instead, we shall pass to a slightly finer class of strategies, in which composition is continuous with respect to functions (but not to arguments).
+We shall then be able to pass back to our original model and get our proof of Lemma \ref{jimY}.
+
+\subsection{Multistrategies}
+
+\begin{definition}
+  Let $A$ be a game.  A \emph{multistrategy} for $A$ is a stably directed set $\Sigma$ of strategies for $A$ such that for all $\sigma,\tau\in \Sigma$ we have $T_\sigma=T_\tau$.
+
+  Given a multistrategy $\Sigma$, we write $T_\Sigma$ for the unique value of $T_\sigma$, where $\sigma\in\Sigma$.
+
+  We can extend the stable order to multistrategies.  This time, $\stle$ is a preorder rather than being a full order.
+
+  Let $A$ be a game, and let $\Sigma,\Tau$ be multistrategies for $A$.  We say that $\Sigma\stle\Tau$ if for all $\tau\in\Tau$ there exists $\sigma\in\Sigma$ such that $\sigma\stle\tau$.
+
+  We say that $\Sigma \steq \Tau$ if $\Sigma\stle\Tau$ and $\Tau\stle\Sigma$.
+\end{definition}
+
+\begin{lemma}
+  Let $A$ be a game, let $\sigma$ be a strategy for $A$ and let $\Sigma$ be a multistrategy for $A$ such that $\{\sigma\}\steq\Sigma$.
+Then $\sigma\in\Sigma$ and is a $\stle$-least element of $\Sigma$.
+\end{lemma}
+  \begin{proof}
+    Since $\Sigma\stle\{\sigma\}$, we know that $\tau\stle\sigma$ for all $\tau\in\Sigma$.
+Since $\{\sigma\}\stle\Sigma$, we know that $\sigma\stle\tau$ for some $\tau\in\Tau$ and hence by antisymmetry that $\sigma\in\Sigma$.
+  \end{proof}
+
+Conversely, if $\Sigma$ is a strategy with a $\stle$-greatest element $\sigma$, then $\{\sigma\}\steq\Sigma$.
+
+\begin{definition}
+  Let $A$ be a game and let $F$ be a set of multistrategies for $A$ that is directed with respect to $\stle$.  We define a strategy $\exlub F$ given by
+  \[
+    \exlub F = \left\{\left(\bigcup_{\Sigma\in F} T_\Sigma, D_\sigma\right)\;\middle|\;\textrm{$\sigma\in\Sigma$ for some $\Sigma\in F$}\right\}
+    \]
+\end{definition}
+
+\begin{proposition}
+  $\exlub F$ is a valid multistrategy for $A$.
+\end{proposition}
+  \begin{proof}
+    We need to show that for all $\Sigma\in F$ and for all $\sigma\in\Sigma$, $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)$ satisfies the diverge-or-reply rule.
+Let $\Sigma\in F$ and let $\sigma\in\Sigma$.
+Suppose that $s\in T_\Tau$ for some $\Tau\in F$, that $sa\in P_A$ and that $sa\not\in D_\sigma$.
+Since $F$ is stably directed, there exists some multistrategy $\Upsilon\in F$ such that $\Sigma,\Tau\stle\Upsilon$.
+Let $\tau\in\Tau$.
+Then there are $\upsilon_1,\upsilon_2\in\Upsilon$ such that $\sigma\stle\upsilon_1$ and $\tau\stle\upsilon_2$.
+Then, since $\Upsilon$ is stably directed, there is some $\upsilon\in\Upsilon$ such that $\upsilon_1,\upsilon_2\stle\upsilon$.
+In particular, $s\in T_\upsilon$ and $sa\not\in D_\upsilon$.
+Therefore, $sab\in T_\upsilon$ for some $b$ and so $sab\in\bigcup_{\Sigma\in F}T_\Sigma$.
+  \end{proof}
+
+\begin{proposition}
+  \label{multiExlubIsStlub}
+  $\exlub F$ is a $\stle$-least upper bound for $F$.
+
+\end{proposition}
+  \begin{proof}
+    Let $\Sigma\in F$ and let $\sigma\in\Sigma$.  Then we have $\sigma\stle\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)\in\exlub F$.  So $\exlub F$ is a $\stle$-upper bound for $F$.
+
+    Now suppose that $\Xi$ is some other $\stle$-upper bound for $F$.
+Then for all $\Sigma\in F$ we must have $T_\Sigma\subset T_\Xi$ and so $\bigcup_{\Sigma\in F}T_\Sigma\subset T_\Xi$.
+Now suppose that $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)$ is some element of $\exlub F$, where $\Sigma\in F$ and $\sigma\in\Sigma$.
+We have $\Sigma\stle\Xi$, so there exists some $\xi\in\Xi$ such that $\sigma\stle\xi$.
+We have $\xi = (T_\Xi, D_\xi)$, where $D_\xi\subset D_\sigma$.
+Therefore, $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)\stle\xi$.
+It follows that $\exlub F\stle\Xi$.
+  \end{proof}
+
+\begin{definition}
+  Let $A,B,C$ be games, let $\Sigma$ be a multistrategy for $A\iimpl B$ and let $\Tau$ be a multistrategy for $B\iimpl C$.  Then we define:
+  \[
+    \icomp\Tau\Sigma = \left\{\icomp\tau{\left(\exlub_{\sigma\in\Sigma}\sigma\right)}\;\middle|\;\tau\in\Tau\right\}
+    \]
+  By Lemmas \ref{compositionMonotonicSO} and \ref{exponentiationMonotonicSO} and Proposition \ref{exlubIsStlub}, this is still stably directed.
+\end{definition}
+
+Note that composition of multistrategies is \emph{not} necessarily associative and does not satisfy the rules for the identity, even up to $\steq$.
+The reason for this is the failure of composition of strategies to be continuous.
+It is possible that we could modify the model to make it associative, but we will not need associativity.
+
+What is clear is that composition is monotonic with respect to the stable ordering on multistrategies.  In fact, we it is even continuous with respect to functions (up to $\steq$).
+
+\begin{proposition}
+  \label{RareContinuityResult}
+  i) Let $A,B,C$ be games, let $\Sigma,\Sigma'$ be multistrategies for $A\implies B$ and let $\Tau,\Tau'$ be multistrategies for $B\implies C$ such that $\Sigma\stle\Sigma'$ and $\Tau\stle\Tau'$.
+Then $\icomp\Tau\Sigma\stle\icomp{\Tau'}{\Sigma'}$.
+
+  ii) Let $A,B,C$ be games, let $\Sigma$ be a multistrategy for $A\implies B$ and let $F$ be a stably directed set of multistrategies for $B\implies C$.  Then
+      \[
+        \icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma \steq \exlub_{\Tau\in F}(\icomp\Tau\Sigma)
+        \]
+\end{proposition}
+\begin{proof}
+  (i): We have $\Sigma\stle\Sigma'$ and it follows that $\exlub_{\sigma\in\Sigma}\sigma\stle\exlub_{\sigma\in\Sigma'}\sigma$ by Proposition \ref{exlubIsStlub} and the definition of $\stle$ for multistrategies.
+Then, if $\icomp\tau{\left(\exlub_{\sigma\in\Sigma}\right)}$ is an arbitrary element of $\icomp\Tau\Sigma$, we know that there exists some $\tau'\in \Tau'$ such that $\tau\stle\tau'$.
+Now we have
+  \[
+    \icomp\tau{\left(\exlub_{\sigma\in\Sigma}\sigma\right)}\le\icomp{\tau'}{\left(\exlub_{\sigma\in\Sigma'}\sigma\right)}\in\icomp{\Tau'}{\Sigma'}
+    \]
+  by Proposition \ref{compositionMonotonicSO}.
+
+  (ii): By part (i), $\icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma$ is an upper bound for $\{\icomp\Tau\Sigma\suchthat \Tau\in F\}$ and therefore we have
+  \[
+    \exlub_{\Tau\in F}(\icomp\Tau\Sigma)\stle\icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma
+    \]
+  by Proposition \ref{exlubIsStlub}.  For the other direction, we may write:
+  \begin{align*}
+    \icomp{\left(\exlub_{\Tau\in F}\Tau\right)}{\Sigma} & = \left\{\icomp\tau{\exlub_{\sigma\in\Sigma}\sigma}\;\middle|\;\tau\in\exlub_{\Tau\in F}\Tau\right\} \\
+      & = \left\{\icomp{\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)}{\exlub_{\sigma\in\Sigma}\sigma}\;\middle|\;\textrm{$\tau\in\Tau$ for some $\Tau\in F$}\right\}
+  \end{align*}
+  while we have 
+  \begin{align*}
+    \exlub_{\Tau\in F}(\icomp\Tau\Sigma) & = \exlub_{\Tau\in F}\left\{\icomp\tau{\exlub_{\sigma\in\Sigma}\sigma}\;\middle|\;\tau\in\Tau\right\} \\
+      & = \left\{\left(\bigcup_{\Tau\in F}T_{\icomp{\Tau}{\exlub \Sigma}},D_{\icomp\tau{\exlub\Sigma}}\right)\;\middle|\;\textrm{$\tau\in\Tau$ for some $\Tau\in F$}\right\}
+  \end{align*}
+  Write $\tau_*$ for $\icomp{\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)}{\exlub_{\sigma\in\Sigma}\sigma}$ and $\tau^*$ for $\left(\bigcup_{\Tau\in F}T_{\icomp{\Tau}{\exlub \Sigma}},D_{\icomp\tau{\exlub\Sigma}}\right)$.
+We want to show that $\tau_*\stle\tau^*$ for all $\tau$ such that $\tau\in \Tau$ for some $\Tau\in F$, which will complete the proof.
+
+  We first claim that $T_{\tau_*}=T_{\tau^*}$.
+Indeed, if $s\in T_{\tau_*}$ then $s=\s\vert_{A,C}$, where $\s\vert_{A,B}\in\bigcup_{\Tau\in F}T_\Tau$ and $\s\vert_{B,C}\in T_{\exlub\Sigma}$.
+It follows that $s\in\bigcup_{\Tau\in F}T_{\icomp{\Tau}{\exlub\Sigma}}$.
+Conversely, if $s\in\bigcup_{\Tau\in F} T_{\icomp{\Tau}{\exlub\Sigma}}$, then we have $s\in\icomp{\Tau'}\Sigma$ for some $\Tau'\in F$, so $s\in T_{\tau_*}$.
+
+  Now all we need to show is that $D_{\tau^*}\subset D_{\tau_*}$.
+We have $D_{\tau^*}=D_{\icomp{\tau}{\exlub\Sigma}}$.
+So if $d\in D_{\tau^*}$ then there is some $\d\in\left(\exlub_{\sigma\in\Sigma}\sigma\right)\dv\tau$ such that $\d\vert_{A,C}\prefix d$.
+If $\d\vert_{A,B}\in T_{\exlub \Sigma}$ and $\d\vert_{B,C}\in D_\tau$ then certainly $\d\in \left(\exlub_{\sigma\in\Sigma}\sigma\right)\dv\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)$.
+Otherwise, $\d\vert_{A,B}\in D_{\exlub \Sigma}$ and $\d\vert_{B,C}\in T_\tau$.
+But now, since $T_\tau\subset \bigcup_{\Tau\in F}T_\Tau$, we again have $\d\in \left(\exlub_{\sigma\in\Sigma}\sigma\right)\dv\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)$.
+Therefore, $d\in D_{\tau_*}$.
+\end{proof}
+
+Note that our definition of composition $\icomp\Tau\Sigma$ is not necessarily continuous with respect to $\Sigma$.
+
+\subsection{Adequacy}
+
+We now extend the definition of the predicates $\plot_T$ to multistrategies.
+
+\begin{definition}
+  For each PCF type $T$, we define a relation $\plot_T$ between multistrategies for $\deno{T}$ and closed terms of type $T$: we say that $\Sigma\plot_TM$ if $\sigma\plot_TM$ for all $\sigma\in\Sigma$.
+\end{definition}
+
+We now prove a stronger version of Lemma \ref{jims2ndLemma} that holds for multistrategies.
+
+\begin{lemma}
+  \label{multijims2ndLemma}
+  i) If $M$ is a term of type $\nat$ such that $M\opto N$ for some unique term $N$, and if $\Sigma\plot_\nat N$, then $\Sigma\plot_\nat M$
+
+  ii) If $M$ is a term of type $T$ and $\Sigma,\Tau$ are multistrategies for $\deno{M}$ such that $\Sigma\stle\Tau$, and if $\Tau\plot_TM$, then $\Sigma\plot_TM$.
+
+  iii) If $M$ is a term of type $T$ and $F$ is a stably directed set of multistrategies for $\deno{T}$ such that $\Sigma\plot_TM$ for all $\Sigma\in F$, then $\exlub F\plot_TM$.
+\end{lemma}
+\begin{proof}
+  (i) and (ii) follow immediately from Lemma \ref{jims2ndLemma} and the definition of $\stle$ for multistrategies.
+
+  (iii): Structural induction on $T$.
+If $T=\nat$ and $M\not\mustconverge$, then $q\in D_\sigma$ for all $\sigma$ such that $\sigma\in\Sigma$ for some $\Sigma\in F$.
+Thus, $q\in D_\sigma$ for all $\sigma\in\exlub F$.
+If $qn\in T_{\exlub F}$ then $qn\in T_\Sigma$ for some $\Sigma\in F$.
+Then, since $\Sigma\plot_\nat M$, we have $M\opto^*\n$.
+
+  Now suppose that $T=Q\to R$ and that $M$ is a term of type $Q\to R$ such that $\Tau\plot_{Q\to R}M$ for all $\Tau\in F$.
+Write $A=\deno{Q}$ and $B=\deno{R}$.
+Let $\sigma$ be a strategy for $A$ such that $\sigma\plot_QN$ and write $\Sigma$ for the multistrategy $\{\sigma\}$.
+For each $\Tau\in F$, we have $\icomp\Tau\Sigma = \{\icomp\tau\sigma\suchthat\tau\in\Tau\}$.
+We have $\icomp\tau\sigma\plot_RMN$ for each $\tau$, so $\icomp\Tau\Sigma\plot_RMN$ for each $\Tau\in F$.
+By structural induction, we must have $\exlub_{\Tau\in F}(\icomp\Tau\Sigma)\plot_RMN$.
+Now, by Proposition \ref{RareContinuityResult}, we have $\exlub_{\Tau\in F}(\icomp\Tau\Sigma)=\icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma$ and therefore $\icomp\tau\sigma\plot_RMN$ for each $\tau\in\exlub_{\Tau\in F}\Tau$.
+Since $\sigma, N$ were arbitrary, it follows that $\exlub F\plot_{Q\to R}M$.
+\end{proof}
+
+We now have the technical machinery ready to prove Lemma \ref{jimY}.
+
+\begin{proof*}{Proof of Lemma \ref{jimY}}
+  Recall that we constructed $\deno{\Y_T}$ as the $\stle$-least fixed point of the strategy $\chi_A$ for $((A\iimpl A)\iimpl A)\iimpl((A\iimpl A)\iimpl A)$ corresponding to the lambda term $\lambda F.\lambda f.f(F f)$, where $A=\deno T$.
+This fixed point exists because the set of strategies for $((A\iimpl A)\iimpl A)$ is directed complete.
+
+  Let $S$ denote the set of multistrategies for $(A\iimpl A)\iimpl A$ such that $S\plot_{(T\to T)\to T}\Y_T$.
+By Lemma \ref{multijims2ndLemma}, part (iii), $S$ is directed complete with respect to $\stle$.
+Write $\Chi_A$ for the multistrategy $\chi_A$.
+We first claim that.
+\end{proof*}
+
+\bibliographystyle{entcs}
+\bibliography{phd_bibliography}
 

### 2017-03-10 nondeterminism/paper/nondeterminism.tex
Urgh.

@@
   \address{Department of Computer Science \\ University of Bath \\
-    Bath, United Kingdom} \thanks[ALL]{The author is indebted to
+    Bath, United Kingdom} \thanks[ALL]{Research supported by an
+    EPSRC-SCI-DTA grant.  The author is indebted to
     his supervisor, Jim Laird, without whose research and guidance
@@
   We give a sound and adequate game semantics for a simple extension of PCF with countable nondeterminism, given in \cite{LairdOrdinalGames}.
-The model is based on the model of idealized Algol with finite nondeterminism given by Harmer and McCusker \cite{mccHFiniteND} with extra information about infinite plays in order to accommodate infinite nondeterminism.
+The model is based on the model of idealized Algol with finite nondeterminism given by Harmer and McCusker \cite{mcCHFiniteND} with extra information about infinite plays in order to accommodate infinite nondeterminism.
 Our proof of soundness for the model is standard, but the proof of adequacy makes use of a new technique that is linked to the possibly transfinite complexity of evaluation trees in the presence of countable nondeterminism.
@@
 By Lemma \ref{multijims2ndLemma}, part (iii), $S$ is directed complete with respect to $\stle$.
-Write $\Chi_A$ for the multistrategy $\chi_A$.
-We first claim that.
+Write $\Chi_A$ for the multistrategy $\{\chi_A\}$.
+We first claim that if $\Sigma\in S$ then $\comp{\Chi_A}{\Sigma}\in S$.
+
+  Write $T=T_1\to\dots\to T_k\to\nat$.
+Let $N\from T\to T,N_1\from T_1,\dots,N_k\from T_k$ be terms and let $\tau\from\deno{T\to T},\sigma_1\from\deno{T_1},\dots,\sigma_k\from\deno{T_k}$ be strategies such that $\sigma_i\plot_{T_i}N_i$ for $i=1,\dots,k$.
+
+  We have $\Sigma\in S$, so for all $\sigma\in\Sigma$ we have $\comp{\comp\sigma\tau}{\comp{\sigma_1}{\comp{\cdots}{\sigma_k}}}\plot_\nat\Y_TNN_1\dots N_k$.
 \end{proof*}

### 2017-03-23 round-corner/round-corner.tex
Rounding off that corner.

@@
 \input{../common/preamble}
+
+\renewcommand{\int}{{\mathtt{int}}}
 
@@
 
+\subsection{The sequoidal exponential}
+
+There are several ways to add exponentials to the basic category of games.  We shall use the definition based on countably many copies of the base game (see \cite{laird02}, for example):
+
+\begin{definition}
+  Let $A$ be a negative game.
+The \emph{exponential} of $A$ is the game $\oc A = (M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A})$, where $M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A}$ are defined as follows:
+  \begin{itemize}
+    \item $M_{\oc A} = M_A \times \omega$
+    \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$
+    \item $b_{\oc A} = O$
+    \item Given a sequence $s\in M_{\oc A}^\omega$, we write $s\vert_n$ for the largest sequence $a_1a_2\dots a_k\in M_A^*$ such that $(a_1,n),(a_2,n),\dots(a_k,n)$ is a subsequence of $s$.
+Then $P_{\oc A}$ is the set of all sequence $s\in M_{\oc A}^\omega$ that are alternating with respect to $\lambda_{\oc A}$, such that $s\vert_n\in P_A$ for all $n$ and such that if $m<n$ and $(a,n)$ occurs in $s$ then $(b,m)$ must occur earlier in $s$ for some move $b$: in other words, player $O$ can start infinitely many copies of the game $A$, but he must start them in order.
+  \end{itemize}
+\end{definition}
+
+This last condition on the order in which games may be opened is very important, as it allows us to define morphisms that give $\oc A$ the semantics of the exponential from linear logic.
+For example, we have a natural morphism $\mu\from\oc A\to\oc A\tensor\oc A$, given by the copycat strategy that starts a new copy of $A$ on the left whenever one is started on the right.
+Because of the condition on the order in which copies of $A$ may be started, there is a unique way to do this.
+
+\begin{proposition}
+  $\mu$ exhibits $\oc A$ as a comonoid in the monoidal category $(\G, \tensor, I)$.  
+\end{proposition}
+\begin{proof}
+  $\mu$ shall be the comultiplication in our comonoid.
+The counit is given by the empty strategy $\eta\from\oc A\to I$.
+We just need to check that $\mu$ is associative and that $\eta$ is a counit for $\mu$.
+
+  For associativity, we need to show that the following diagram commutes:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[rr, "\mu"] \arrow[d, "\mu"']
+        &
+          & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor\mu"] \\
+      \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}"' yshift=-0.4em]
+        & (\oc A \tensor \oc A) \tensor \oc A \arrow[r, "\assoc_{\oc A,\oc A,\oc A}"' yshift=-0.4em]
+          & \oc A \tensor (\oc A \tensor \oc A)
+    \end{tikzcd}
+    \]
+  This is easy to see when we notice that both branches of the square are copycat strategies on $\oc A\implies\oc A\tensor(\oc A\tensor \oc A)$; since copies of $A$ in $\oc A$ must be started in sequence, there is a unique such strategy, and so the square commutes.
+
+  For the counit, we need to show that the follosing two diagrams commute:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[r, "\mu"] \arrow[dr, "\runit_A\inv"']
+        & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \eta"] \\
+      %
+        & \oc A \tensor I
+    \end{tikzcd}
+    \quad\quad\quad
+    \begin{tikzcd}
+      \oc A \arrow[r, "\mu"] \arrow[dr, "\lunit_A\inv"']
+        & \oc A \tensor \oc A \arrow[d, "\eta\tensor\id_{\oc A}"] \\
+      %
+        & I \tensor \oc A
+    \end{tikzcd}
+    \]
+  Once again, these diagrams commute because both branches are copycat strategies for $\oc A\implies\oc A\tensor I$ or $\oc A\implies I\tensor\oc A$ and there is a unique such strategy in each case.
+\end{proof}
+
+We shall later show that $(\oc A, \mu, \eta)$ is in fact the \emph{cofree commutative comonoid} on $A$ in the monoidal category $(\G, \tensor, I)$.
+
+We shall call the exponential $\oc A$ the \emph{sequoidal exponential}.  The following proposition explains the name:
+
+\begin{proposition}
+  Let $A$ be a negative game.  Then we get an endofunctor $A\sequoid\blank$ on $\G$ given by sending $B$ to $A\sequoid B$.
+
+  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.
+In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
+  \[
+    \begin{tikzcd}
+      B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
+        & A \sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
+      \oc A \arrow[r, "\alpha"']
+        & A \sequoid \oc A
+    \end{tikzcd}
+    \]
+\end{proposition}
+\begin{proof}
+  See \cite{martinsthesis}.  We shall shortly give a proof in the more general case.
+\end{proof}
+
+\subsection{Constructing cofree commutative comonoids in sequoidal categories}
+
+We want to deduce the fact that $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ is the cofree commutative comonoid on $A$ from the fact that $\oc A$ is the final coalgebra for $A\sequoid\blank$.
+It turns out that we shall need one more fact about the category of games to prove this.
+
+\begin{definition}
+  Let $A,B$ be objects of an inclusive, Cartesian, distributive sequoidal category with final coalgebras $\oc A\xrightarrow{\alpha_A} A\sequoid\oc A$ for all endofunctors of the form $A\sequoid\blank$.
+Then we have morphisms:
+  \[
+    \begin{tikzcd}
+      \oc A \tensor \oc B \arrow[r, "\alpha_A\tensor\id_{\oc B}"] \arrow[d, "\sym"]
+        & (A \sequoid\oc A)\tensor \oc B \arrow[r, "\wk"]
+          & (A\sequoid\oc A)\sequoid\oc B \arrow[r, "\passoc"]
+            & A \sequoid (\oc A \tensor\oc B)
+              & \\
+      \oc B \tensor \oc A \arrow[r, "\alpha_B\tensor\id_{\oc A}"]
+        & (B\sequoid\oc B)\tensor\oc A \arrow[r, "\wk"]
+          & (B\sequoid\oc B)\sequoid \oc A \arrow[r, "\passoc"]
+            & B \sequoid (\oc B\tensor\oc A) \arrow[r, "\id_B\sequoid\sym"]
+              & B \sequoid (\oc A\tensor\oc B)
+    \end{tikzcd}
+    \]
+inducing a morphism
+\[
+  \oc A\tensor \oc B \to (A \sequoid(\oc A\tensor\oc B)) \times (B \sequoid(\oc A\tensor \oc B)) \xrightarrow{\dist\inv}
+    (A\times B)\sequoid(\oc A\tensor\oc B)
+    \]
+  Remembering that our category has a final coalgebra $\oc(A\times B)$ for the functor $(A\times B)\sequoid\blank$, we write $\int_{A,B}$ for the unique morphism $\oc A\tensor\oc B\to \oc(A\times B)$ making the following diagram commute
+  \[
+    \begin{tikzcd}
+      \oc A\tensor\oc B \arrow[r] \arrow[d, "\int_{A,B}"']
+        & (A\sequoid(\oc A\tensor\oc B))\times(B\sequoid(\oc A\tensor\oc B))\arrow[r,"\dist\inv"]
+          & (A\times B)\sequoid(\oc A\tensor\oc B) \arrow[d, "\id_{A\times B}\sequoid\int_{A,B}"] \\
+      \oc(A\times B) \arrow[rr, "\alpha_{A\times B}"']
+        &
+          & (A\times B)\sequoid\oc(A\times B)
+    \end{tikzcd}
+    \]
+\end{definition}
+
+\begin{proposition}
+  In the category of games, the morphism $\int_{A,B}$ is an isomorphism for all negative games $A,B$.
+\end{proposition}
+\begin{proof}
+  Observe that the morphism $\int_{A,B}$ is the copycat strategy on $\oc A\tensor\oc B\implies \oc (A\times B)$ that starts a copy of $A$ on the left whenever a copy of $A$ is started on the right and starts a copy of $B$ on the left whenever a copy of $B$ is started on the right (indeed, the morphisms in the diagram above are all copycat morphisms, so the copycat strategy we have just described must make that diagram commute.
+Since there are infinitely many copies of both $A$ and $B$ available in $\oc (A\times B)$, and since a new copy of $A$ or $B$ may be started at any time, we may define an inverse copycat strategy on $\oc(A\times B)\implies \oc A\tensor\oc B$.
+\end{proof}
+
+Our main result for this section will be the following:
+\begin{theorem}
+  Let $(\C,\C_s,J)$ be an inclusive, Cartesian, distributive and decomposable sequoidal category with a final coalgebra $\oc A\xrightarrow{\alpha_A}A\sequoid\oc A$ for each endofunctor of the form $A\sequoid\blank$.
+Suppose further that the morphism $\int_{A,B}$ as defined above is an isomorphism for all objects $A,B$.
+Then $\oc A$ is the carrier of a cofree commutative comonoid over $A$ in the monoidal category $(\C,\tensor,I)$.
+\end{theorem}
+
+The first step will be to define the comultiplication and counits for our comonoid over $\oc A$.  For the comultiplication, note that we have a morphism
+\[
+  \oc A \xrightarrow{\alpha_A} A \sequoid \oc A \xrightarrow{\Delta} (A\sequoid\oc A)\times (A\sequoid\oc A)\xrightarrow{\dist\inv} (A\times A)\sequoid\oc A
+  \]
+
 \bibliographystyle{alpha}

### 2017-03-29 round-corner/paper/lipics-v2016-authors/lipics-v2016-sample-article.tex
Added a new paper.

\documentclass[a4paper,UKenglish]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{William John Gowers}
\author[2]{James Laird}
\affil[1]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
  \texttt{W.J.Gowers@bath.ac.uk}}
\affil[2]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
  \texttt{jiml@cs.bath.ac.uk}}
\authorrunning{W.\,J. Gowers and J. Laird} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{William John Gowers and James Laird}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator, Exponentials}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Acces}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. 
 \end{abstract}

\section{Typesetting instructions -- please read carefully}
Please comply with the following instructions when preparing your article for a LIPIcs proceedings volume. 
\begin{itemize}
\item Use pdflatex and an up-to-date LaTeX system.
\item Use further LaTeX packages only if required. Avoid usage of packages like \verb+enumitem+, \verb+enumerate+, \verb+cleverref+. Keep it simple, i.e. use as few additional packages as possible.
\item Add custom made macros carefully and only those which are needed in the article (i.e., do not simply add your convolute of macros collected over the years).
\item Do not use a different main font. For example, the usage of the \verb+times+-package is forbidden.
\item Provide full author names (especially with regard to the first name) in the \verb+\author+ macro and in the \verb+\Copyright+ macro.
\item Fill out the \verb+\subjclass+ and \verb+\keywords+ macros. For the \verb+\subjclass+, please refer to the ACM classification at \url{http://www.acm.org/about/class/ccs98-html}.
\item Take care of suitable linebreaks and pagebreaks. No overfull \verb+\hboxes+ should occur in the warnings log.
\item Provide suitable graphics of at least 300dpi (preferrably in pdf format).
\item Use the provided sectioning macros: \verb+\section+, \verb+\subsection+, \verb+\subsection*+, \verb+\paragraph+, \verb+\subparagraph*+, ... ``Self-made'' sectioning commands (for example, \verb+\noindent{\bf My+ \verb+subparagraph.}+ will be removed and replaced by standard LIPIcs style sectioning commands.
\item Do not alter the spacing of the  \verb+lipics-v2016.cls+ style file. Such modifications will be removed.
\item Do not use conditional structures to include/exclude content. Instead, please provide only the content that should be published -- in one file -- and nothing else.
\item Remove all comments, especially avoid commenting large text blocks and using \verb+\iffalse+ $\ldots$ \verb+\fi+ constructions.
\item Keep the standard style (\verb+plainurl+) for the bibliography as provided by the\linebreak \verb+lipics-v2016.cls+ style file.
\item Use BibTex and provide exactly one BibTex file for your article. The BibTex file should contain only entries that are referenced in the article. Please make sure that there are no errors and warnings with the referenced BibTex entries.
\item Use a spellchecker to get rid of typos.
\item A manual for the LIPIcs style is available at \url{http://drops.dagstuhl.de/styles/lipics-v2016/lipics-v2016-authors/lipics-v2016-manual.pdf}.
\end{itemize}

\section{Lorem ipsum dolor sit amet}

Lorem ipsum dolor sit amet, consectetur adipiscing elit \cite{DBLP:journals/cacm/Knuth74}. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. Donec eget odio et magna ullamcorper vehicula ut vitae libero. Maecenas lectus nulla, auctor nec varius ac, ultricies et turpis. Pellentesque id ante erat. In hac habitasse platea dictumst. Curabitur a scelerisque odio. Pellentesque elit risus, posuere quis elementum at, pellentesque ut diam. Quisque aliquam libero id mi imperdiet quis convallis turpis eleifend.

\begin{lemma}[Lorem ipsum]
\label{lemma:lorem}
Vestibulum sodales dolor et dui cursus iaculis. Nullam ullamcorper purus vel turpis lobortis eu tempus lorem semper. Proin facilisis gravida rutrum. Etiam sed sollicitudin lorem. Proin pellentesque risus at elit hendrerit pharetra. Integer at turpis varius libero rhoncus fermentum vitae vitae metus.
\end{lemma}

\begin{proof}
Cras purus lorem, pulvinar et fermentum sagittis, suscipit quis magna.
\end{proof}

\begin{theorem}[Curabitur pulvinar, \cite{DBLP:books/mk/GrayR93}]
\label{theorem:curabitur}
Nam liber tempor cum soluta nobis eleifend option congue nihil imperdiet doming id quod mazim placerat facer possim assum. Lorem ipsum dolor sit amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod tincidunt ut laoreet dolore magna aliquam erat volutpat.
\end{theorem}

\subsection{Curabitur dictum felis id sapien}

Curabitur dictum felis id sapien mollis ut venenatis tortor feugiat. Curabitur sed velit diam. Integer aliquam, nunc ac egestas lacinia, nibh est vehicula nibh, ac auctor velit tellus non arcu. Vestibulum lacinia ipsum vitae nisi ultrices eget gravida turpis laoreet. Duis rutrum dapibus ornare. Nulla vehicula vulputate iaculis. Proin a consequat neque. Donec ut rutrum urna. Morbi scelerisque turpis sed elit sagittis eu scelerisque quam condimentum. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nec faucibus leo. Cras ut nisl odio, non tincidunt lorem. Integer purus ligula, venenatis et convallis lacinia, scelerisque at erat. Fusce risus libero, convallis at fermentum in, dignissim sed sem. Ut dapibus orci vitae nisl viverra nec adipiscing tortor condimentum \cite{DBLP:journals/cacm/Dijkstra68a}. Donec non suscipit lorem. Nam sit amet enim vitae nisl accumsan pretium.

\begin{lstlisting}[caption={Useless code},label=list:8-6,captionpos=t,float,abovecaptionskip=-\medskipamount]
for i:=maxint to 0 do 
begin 
    j:=square(root(i));
end;
\end{lstlisting}

\subsection{Proin ac fermentum augue}

Proin ac fermentum augue. Nullam bibendum enim sollicitudin tellus egestas lacinia euismod orci mollis. Nulla facilisi. Vivamus volutpat venenatis sapien, vitae feugiat arcu fringilla ac. Mauris sapien tortor, sagittis eget auctor at, vulputate pharetra magna. Sed congue, dui nec vulputate convallis, sem nunc adipiscing dui, vel venenatis mauris sem in dui. Praesent a pretium quam. Mauris non mauris sit amet eros rutrum aliquam id ut sapien. Nulla aliquet fringilla sagittis. Pellentesque eu metus posuere nunc tincidunt dignissim in tempor dolor. Nulla cursus aliquet enim. Cras sapien risus, accumsan eu cursus ut, commodo vel velit. Praesent aliquet consectetur ligula, vitae iaculis ligula interdum vel. Integer faucibus faucibus felis.

\begin{itemize}
\item Ut vitae diam augue. 
\item Integer lacus ante, pellentesque sed sollicitudin et, pulvinar adipiscing sem. 
\item Maecenas facilisis, leo quis tincidunt egestas, magna ipsum condimentum orci, vitae facilisis nibh turpis et elit. 
\end{itemize}

\section{Pellentesque quis tortor}

Nec urna malesuada sollicitudin. Nulla facilisi. Vivamus aliquam tempus ligula eget ornare. Praesent eget magna ut turpis mattis cursus. Aliquam vel condimentum orci. Nunc congue, libero in gravida convallis \cite{DBLP:conf/focs/HopcroftPV75}, orci nibh sodales quam, id egestas felis mi nec nisi. Suspendisse tincidunt, est ac vestibulum posuere, justo odio bibendum urna, rutrum bibendum dolor sem nec tellus.

\begin{lemma} [Quisque blandit tempus nunc]
Sed interdum nisl pretium non. Mauris sodales consequat risus vel consectetur. Aliquam erat volutpat. Nunc sed sapien ligula. Proin faucibus sapien luctus nisl feugiat convallis faucibus elit cursus. Nunc vestibulum nunc ac massa pretium pharetra. Nulla facilisis turpis id augue venenatis blandit. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
\end{lemma}

Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.

\subparagraph*{Acknowledgements.}

I want to thank \dots

\appendix
\section{Morbi eros magna}

Morbi eros magna, vestibulum non posuere non, porta eu quam. Maecenas vitae orci risus, eget imperdiet mauris. Donec massa mauris, pellentesque vel lobortis eu, molestie ac turpis. Sed condimentum convallis dolor, a dignissim est ultrices eu. Donec consectetur volutpat eros, et ornare dui ultricies id. Vivamus eu augue eget dolor euismod ultrices et sit amet nisi. Vivamus malesuada leo ac leo ullamcorper tempor. Donec justo mi, tempor vitae aliquet non, faucibus eu lacus. Donec dictum gravida neque, non porta turpis imperdiet eget. Curabitur quis euismod ligula.

%%
%% Bibliography
%%

%% Either use bibtex (recommended),

\bibliography{lipics-v2016-sample-article}

%% .. or use the thebibliography environment explicitely

\end{document}

### 2017-03-29 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Added a new paper.

\documentclass[a4paper,UKenglish]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{William John Gowers}
\author[2]{James Laird}
\affil[1]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
  \texttt{W.J.Gowers@bath.ac.uk}}
\affil[2]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
  \texttt{jiml@cs.bath.ac.uk}}
\authorrunning{W.\,J. Gowers and J. Laird} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{William John Gowers and James Laird}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator, Exponentials}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Acces}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Author macros and packages
\usepackage{IEEEtrantools} % for \IEEEeqnarray
\usepackage{pbox} % for \pbox
\usepackage{cmll} % Linear logic symbols!
\usepackage{wasysym} % For left and rigth moons
\usepackage{mathtools}

%% Graphics %%
\usepackage{tikz}
\usetikzlibrary{cd}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.pathmorphing}

%% Get the sqsubsetneqq character from the mathabx package
\DeclareFontFamily{U}{mathb}{\hyphenchar\font45}
\DeclareFontShape{U}{mathb}{m}{n}{
      <5> <6> <7> <8> <9> <10> gen * mathb
      <10.95> mathb10 <12> <14.4> <17.28> <20.74> <24.88> mathb12
      }{}
\DeclareSymbolFont{mathb}{U}{mathb}{m}{n}

\DeclareMathSymbol{\sqsubsetneq}    {3}{mathb}{"88}
\DeclareMathSymbol{\varsqsubsetneq} {3}{mathb}{"8A}
\DeclareMathSymbol{\varsqsubsetneqq}{3}{mathb}{"92}
\DeclareMathSymbol{\sqsubsetneqq}   {3}{mathb}{"90}

%% Theorems %%
\theoremstyle{plain}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{notation}[theorem]{Notation}

%% Other macros
\newcommand*\from{\colon}
\def \inv {^{-1}}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\pr}{pr}
\newcommand{\tensor}{\otimes}
\newcommand{\sequoid}{\oslash}
\renewcommand{\implies}{\multimap}
\newcommand{\comp}[2]{#1 \circ #2}
\newcommand{\cprd}{\sqcup}
\newcommand{\bigcprd}{\bigsqcup}
\newcommand{\C}{\mathcal C}
\newcommand{\F}{\mathcal F}
\newcommand{\G}{\mathcal G}
\newcommand{\suchthat}{\;\colon\;}
\newcommand{\varsuchthat}{\;\mid\;}
\newcommand{\OP}{\{O,P\}}
\newcommand{\emptyplay}{\epsilon}
\newcommand{\prefix}{\sqsubseteq}
\newcommand{\pprefix}{\sqsubsetneqq}
\newcommand{\ppprefix}{\sqsubset}
\DeclareMathOperator{\assoc}{assoc}
\DeclareMathOperator{\lunit}{lunit}
\DeclareMathOperator{\runit}{runit}
\DeclareMathOperator{\sym}{sym}
\newcommand{\braid}{\sym}
\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
\newcommand{\der}{{\mathtt{der}}}
\newcommand{\mult}{{\mathtt{mult}}}
\DeclareMathOperator{\wk}{wk}
\newcommand{\toisom}{{\xrightarrow{\cong}}}
\newcommand{\passoc}{{\mathtt{passoc}}}
\newcommand{\pcomm}{{\mathtt{pcomm}}}
\newcommand{\run}{{\mathtt{r}}}
\newcommand{\lun}{{\mathtt{l}}}
\newcommand{\fcoal}[1]{{\leftmoon #1 \rightmoon}}
\renewcommand{\subset}{\subseteq}
\let\oldemptyset\emptyset
\let\emptyset\varnothing
\newcommand{\s}{\mathfrak{s}}
\newcommand{\dist}{{\mathtt{dist}}}
\newcommand{\dec}{{\mathtt{dec}}}
\renewcommand{\int}{{\mathtt{int}}}
\DeclareMathOperator{\CCom}{CCom}

%% Constant width xrightarrows
\newlength{\arrow}
\settowidth{\arrow}{\scriptsize$1000$}
\newcommand*{\constantwidthxrightarrow}[1]{\xrightarrow{\mathmakebox[\arrow]{#1}}}

%% Landscape pages
\usepackage{everypage}
\usepackage{environ}
\usepackage{pdflscape}
\newcounter{abspage}

\makeatletter
\newcommand{\newSFPage}[1]% #1 = \theabspage
  {\global\expandafter\let\csname SFPage@#1\endcsname\null}

\NewEnviron{SidewaysFigure}{\begin{figure}[p]
\protected@write\@auxout{\let\theabspage=\relax}% delays expansion until shipout
  {\string\newSFPage{\theabspage}}%
\ifdim\textwidth=\textheight
  \rotatebox{90}{\parbox[c][\textwidth][c]{\linewidth}{\BODY}}%
\else
  \rotatebox{90}{\parbox[c][\textwidth][c]{\textheight}{\BODY}}%
\fi
\end{figure}}

\AddEverypageHook{% check if sideways figure on this page
  \ifdim\textwidth=\textheight
    \stepcounter{abspage}% already in landscape
  \else
    \@ifundefined{SFPage@\theabspage}{}{\global\pdfpageattr{/Rotate 0}}%
    \stepcounter{abspage}%
    \@ifundefined{SFPage@\theabspage}{}{\global\pdfpageattr{/Rotate 90}}%
  \fi}
\makeatother

\begin{document}

\maketitle

\begin{abstract}
  In \cite{laird02}, Laird introduces the concept of a \emph{sequoidal category} as a formalization of causality in game semantics.  A sequoidal category is like a monoidal category with an extra connective, $\sequoid$, that allows one to construct an exponential object as a final coalgebra \cite{martinsthesis},  Under a further hypothesis, it is possible to show that this final coalgebra allows one to construct cofree commutative comonoids in the category, giving us a model of the exponential connective $\oc$ from linear logic.  In the first part of this note, we review the coalgebraic arguments for constructing the cofree commutative comonoid, which are known but do not yet appear in print.  In the second part, we show that the extra hypotheses are necessary by outlining a definition of \emph{transfinite game}, in which the carriers of the sequoidal coalgebra and the cofree commutative comonoid do not coincide.
\end{abstract}

\section{Sequoidal categories}

\subsection{Game semantics and the sequoidal operator}

We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.  A game will be given by a tuple
\[
  A = (M_A, \lambda_A, b_A, P_A)
  \]
where
\begin{itemize}
  \item $M_A$ is a set of moves.
  \item $\lambda_A\from M_A\to\OP$ is a function designating each move as either an \emph{$O$-move} or a \emph{$P$-move}.
  \item $b_A\in\OP$ is a choice of starting player.
  \item $P_A\subset M_A^*$ is a prefix-closed set of alternating plays (so if $sab\in P_A$ then $\lambda_A(a)=\neg\lambda_A(b)$) such that if $as\in P_A$ then $\lambda_A(a)=b_A$.
\end{itemize}

We call $sa\in P_A$ a \emph{$P$-position} if $a$ is a $P$-move and an \emph{$O$-position} if $a$ is an $O$-move.

A \emph{strategy} for player $P$ for a game $A$ is identified with the set of positions that may arise when playing according to that strategy.  Namely, it is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the two conditions:
\begin{description}
  \item[(sO)] If $s\in\sigma$ is a $P$-position and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.
  \item[(sP)] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
\end{description}

We shall now concentrate on games $A$ for which $b_A=O$, called \emph{negative games}.  We shall informally describe the standard connectives on negative games:

\begin{description}
  \item[Product] If $A$ and $B$ are negative games then the \emph{product} $A\times B$ is the game given by placing the game trees for $A$ and $B$ side by side: that is, player $O$ may play his first move either in $A$ or in $B$.  Thereafter, play continues in the game that player $O$ has chosen.
  \item[Tensor Product] The tensor product $A\tensor B$ is also played by playing the games $A$ and $B$ in parallel, but this time player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
  \item[Linear implication] The implication $A\implies B$ is played by playing the game $B$ in parallel with the \emph{negation} of $A$ - that is, the game formed by switching the roles of players $P$ and $O$ in $A$.  Since play in the negation of $A$ starts with a $P$-move, player $O$ is forced to make his first move in the game $B$.  Thereafter, player $P$ may switch games whenever it is her turn.
\end{description}

If $A,B,C$ are negative games, $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, then we may form a strategy $\comp\tau\sigma$ for $A\implies C$ by setting
\[
  \sigma\|\tau = \{\s\in (M_A\cprd M_B\cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;s\vert_{B,C}\in\tau\}
  \]
and then defining
\[
  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\comp\tau\sigma\}
  \]
It is well known (see, for example, \cite{abramskyjagadeesangames}) that $\comp\tau\sigma$ is indeed a strategy for $A\implies C$ and that this form of composition is associative and has an identity.  It is also well known that the resulting category $\G$ of games and strategies has products given by the operator $\times$ and a symmetric monoidal closed structure given by the operations $\tensor$ and $\implies$.

We turn now to the non-standard \emph{sequoid} connective $\sequoid$.  If $A$ and $B$ are negative games, then the sequoid $A\sequoid B$ is similar to the tensor product $A\tensor B$, but with the restriction that player $O$'s first move must take place in the game $A$.  We observe immediately that we have structural isomorphisms
\begin{gather*}
  \dist\from A\tensor B\toisom (A\sequoid B)\times(B\sequoid A)\\
  \dec\from(A\times B)\sequoid C\toisom (A\sequoid C)\times (B\sequoid C)\\
  \passoc\from (A\sequoid B)\sequoid C\toisom A\sequoid (B\tensor C)
\end{gather*}

One further question to ask is: does the sequoid operator give rise to a functor $\blank\sequoid\blank\from\G\times\G\to\G$, as the tensor operator does?  The answer is no: indeed, let $A,B,C,D$ be negative games, let $\sigma$ be a strategy for $A\implies C$ and let $\tau$ be a strategy for $B\implies D$.  Our aim is to construct a natural strategy $\sigma\sequoid\tau$ for $(A\sequoid B)\implies (C\sequoid D)$.  There is an obvious way to try and do this: player $P$ should play according to the strategy $\sigma$ whenever player $O$'s last move was in $A$ or $C$, and according to $\tau$ whenever player $O$'s last move was in $B$ or $D$.

We show that this does not in general give us a strategy for $(A\sequoid B)\implies (C\sequoid D)$.  Suppose that $\sigma$ is such that player $P$'s response to some opening move in $C$ is another move in $C$ and suppose that $\tau$ is such that player $P$'s response to some opening move in $D$ is a move in $B$ (for example, $\tau$ is a copycat strategy).  Then we end up with the following sequence of events in the game $(A\sequoid B)\implies(C\sequoid D)$  :
\begin{enumerate}
  \item Player $O$ starts with a move in $C$ (as he must).
  \item Player $P$ responds according to $\sigma$ with another move in $C$.
  \item Player $O$ decides to switch games and play a move in $D$.
  \item Player $P$ responds according to $\tau$ with a move in $B$.
\end{enumerate}

But now player $P$'s last move is not a legal move in $(A\sequoid B)\implies(C\sequoid D)$, since no moves have been played in $A$ yet.

We get round this problem by requiring that the strategy $\sigma$ be \emph{strict} -- that is, whatever player $O$'s opening move in $C$ is, player $P$'s reply must be a move in $A$.

\begin{definition}
  Let $N,L$ be negative games and let $\sigma$ be a strategy for $N\implies L$.  We say that $\sigma$ is \emph{strict} if player $P$'s reply to an opening move in $L$ is always a move in $N$.  
\end{definition}

Identity strategies are strict and the composition of two strict strategies is strict, so we get a full-on-objects subcategory $\G_s$ of $\G$ where the morphisms are strict strategies.  Then the sequoid operator gives rise to a functor:
\[
  \blank\sequoid\blank\from \G_s\times\G\to\G_s
  \]

\subsection{Sequoidal categories}

We now have the motivation required to give the definition of a \emph{sequoidal category} from \cite{laird02}.

\begin{definition}
  A \emph{sequoidal category} consists of the following data:
  \begin{itemize}
    \item A symmetric monoidal category $\C$ with monoidal product $\tensor$ and tensor unit $I$, associators $\assoc_{A,B,C}\from(A\tensor B)\tensor C\toisom A\tensor(B\tensor C)$, unitors $\runit_A\from A\tensor I\toisom A$ and $\lunit_A\from I\tensor A\toisom A$ and braiding $\sym_{A,B}\from A\tensor B\to B\tensor A$.
    \item A category $\C_s$
    \item A right monoidal category action of $\C$ on the category $\C_s$.  That is, a functor
      \[
        \blank\sequoid\blank\from\C_s\times\C\to\C_s
        \]
      together natural isomorphisms
      \[
        \passoc_{A,B,C}\from A\sequoid(B\tensor C)\to (A\sequoid B)\sequoid C
        \]
      and
      \[
        \run_A\from A\sequoid I\toisom A
        \]
      subject to the following coherence conditions:
      \begin{equation*}
        \begin{tikzcd}
          A\sequoid(B\tensor(C\tensor D)) \arrow[r, "\passoc_{A,B,C\tensor D}" yshift=0.3em] \arrow[d, "\id_A\sequoid \assoc_{B,C,D}"']
            & (A \sequoid B) \sequoid (C\tensor D) \arrow[r, "\passoc_{A\sequoid B,C,D}" yshift=0.3em]
              & ((A\sequoid B)\sequoid C) \sequoid D \\
          A\sequoid((B\tensor C)\tensor D) \arrow[r, "\passoc_{A,B\tensor C,D}"' yshift=-0.3em]
            & (A\sequoid (B\tensor C)) \sequoid D \arrow[ur, "\passoc_{A,B,C}\sequoid\id_D"']
              &
        \end{tikzcd}
      \end{equation*}
      \begin{equation*}
        \begin{tikzcd}
          A \sequoid (I\tensor B) \arrow[r, "\passoc_{A,I,B}" yshift=0.3em] \arrow[d, "\id_A\sequoid\lunit_B"']
            & (A\sequoid I)\sequoid B \arrow[dl, "\run_A\sequoid\id_B"] \\
          A \sequoid B
            &
        \end{tikzcd}
        \quad
        \begin{tikzcd}
          A \sequoid (B\tensor I) \arrow[r, "\passoc_{A,B,I}" yshift=0.3em] \arrow[d, "\id_A\sequoid\runit_B"']
            & (A\sequoid B) \sequoid I \arrow[dl, "\run_{A\sequoid B}"] \\
          A\sequoid B
            &
        \end{tikzcd}
      \end{equation*}

      \item A functor $J\from \C_s\to\C$ (in the games example, this is the inclusion functor $\G_s\to\G$)

      \item A natural transformation $\wk_{A,B}\from J(A)\tensor B\to J(A\sequoid B)$ satisfying the coherence conditions:
      \begin{equation*}
        \begin{tikzcd}
          A \tensor I \arrow[r, "\runit_A" yshift=0.3em] \arrow[d, "\wk_{A,I}"']
            & A \\
          A \sequoid I \arrow[ur, "J(\run_A)"']
            &
        \end{tikzcd}
        \quad
        \begin{tikzcd}
          (A \tensor B) \tensor C \arrow[r, "\wk_{A,B}\tensor\id_C" yshift=0.3em] \arrow[d, "\assoc_{A,B,C}"']
            & (A \sequoid B) \tensor C \arrow[r, "\wk_{A\sequoid B, C}" yshift=0.3em]
              & (A \sequoid B) \sequoid C\\
          A \tensor (B \tensor C) \arrow[r, "\wk_{A,B\tensor C}"']
            & A \sequoid (B \tensor C) \arrow[ur, "J(\passoc_{A,B,C})"']
              &
        \end{tikzcd}
      \end{equation*}
  \end{itemize}
\end{definition}

Our category of games satisfies further conditions:

\begin{definition}
  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.  We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing the monoidal isomorphisms and the morphisms $\wk_{A,B}$, $J$ is the inclusion functor and $J$ reflects isomorphisms.

  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.  In that case, we say that $\C$ is \emph{decomposable} if the natural transformations
  \begin{gather*}
    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
    \dec^0 \from I \to 1
  \end{gather*}
  are isomorphisms and we say that $\C$ is \emph{distributive} if the natural transformations
  \begin{gather*}
    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
    \dist_{A,0}\from 1\sequoid A\to 1
  \end{gather*}
  are isomorphisms.
\end{definition}

We have one further piece of structure available to us:

\begin{definition}
  Let $\C=(\C,\C_s,J,\wk)$ be an inclusive sequoidal category.  We say that $\C$ is a \emph{sequoidal closed category} if $\C$ is monoidal closed (with internal hom $\implies$ and currying $\Lambda_{A,B,C}\from \C(A\tensor B,C)\toisom \C(A,B\implies C)$) and if the map $f\mapsto\Lambda(\comp{f}{\wk})$ gives rise to a natural transformation
  \[
    \Lambda_{A,B,C,s}\from \C_s(A\sequoid B, C) \to \C_s(A,B\implies C)
    \]
\end{definition}

It can be shown (see for example \cite{martinsthesis}) that our category $\G$ of games has all this structure.

\begin{theorem}
  If $A,B$ are games, let $J$ be the inclusion functor $\G_s\to\G$ and let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
  \[
    (\G,\G_s,J,\wk)
    \]
  is an inclusive, Cartesian, decomposable, distributive sequoidal closed category.
\end{theorem}

\subsection{The sequoidal exponential}

There are several ways to add exponentials to the basic category of games.  We shall use the definition based on countably many copies of the base game (see \cite{laird02}, for example):

\begin{definition}
  Let $A$ be a negative game.  The \emph{exponential} of $A$ is the game $\oc A = (M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A})$, where $M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A}$ are defined as follows:
  \begin{itemize}
    \item $M_{\oc A} = M_A \times \omega$
    \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$
    \item $b_{\oc A} = O$
    \item Given a sequence $s\in M_{\oc A}^\omega$, we write $s\vert_n$ for the largest sequence $a_1a_2\dots a_k\in M_A^*$ such that $(a_1,n),(a_2,n),\dots(a_k,n)$ is a subsequence of $s$.  Then $P_{\oc A}$ is the set of all sequence $s\in M_{\oc A}^\omega$ that are alternating with respect to $\lambda_{\oc A}$, such that $s\vert_n\in P_A$ for all $n$ and such that if $m<n$ and $(a,n)$ occurs in $s$ then $(b,m)$ must occur earlier in $s$ for some move $b$: in other words, player $O$ can start infinitely many copies of the game $A$, but he must start them in order.
  \end{itemize}
\end{definition}

This last condition on the order in which games may be opened is very important, as it allows us to define morphisms that give $\oc A$ the semantics of the exponential from linear logic.  For example, we have a natural morphism $\mu\from\oc A\to\oc A\tensor\oc A$, given by the copycat strategy that starts a new copy of $A$ on the left whenever one is started on the right.  Because of the condition on the order in which copies of $A$ may be started, there is a unique way to do this.

\begin{proposition}
  $\mu$ exhibits $\oc A$ as a comonoid in the monoidal category $(\G, \tensor, I)$.  
\end{proposition}
\begin{proof}
  $\mu$ shall be the comultiplication in our comonoid.  The counit is given by the empty strategy $\eta\from\oc A\to I$.  We just need to check that $\mu$ is associative and that $\eta$ is a counit for $\mu$.

  For associativity, we need to show that the following diagram commutes:
  \[
    \begin{tikzcd}
      \oc A \arrow[rr, "\mu"] \arrow[d, "\mu"']
        &
          & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor\mu"] \\
      \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}" yshift=0.2em]
        & (\oc A \tensor \oc A) \tensor \oc A \arrow[r, "\assoc_{\oc A,\oc A,\oc A}"' yshift=-0.4em]
          & \oc A \tensor (\oc A \tensor \oc A)
    \end{tikzcd}
    \]
  This is easy to see when we notice that both branches of the square are copycat strategies on $\oc A\implies\oc A\tensor(\oc A\tensor \oc A)$; since copies of $A$ in $\oc A$ must be started in sequence, there is a unique such strategy, and so the square commutes.

  For the counit, we need to show that the follosing two diagrams commute:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\mu"] \arrow[dr, "\runit_A\inv"']
        & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \eta"] \\
      %
        & \oc A \tensor I
    \end{tikzcd}
    \quad\quad\quad
    \begin{tikzcd}
      \oc A \arrow[r, "\mu"] \arrow[dr, "\lunit_A\inv"']
        & \oc A \tensor \oc A \arrow[d, "\eta\tensor\id_{\oc A}"] \\
      %
        & I \tensor \oc A
    \end{tikzcd}
    \]
  Once again, these diagrams commute because both branches are copycat strategies for $\oc A\implies\oc A\tensor I$ or $\oc A\implies I\tensor\oc A$ and there is a unique such strategy in each case.
\end{proof}

We shall later show that $(\oc A, \mu, \eta)$ is in fact the \emph{cofree commutative comonoid} on $A$ in the monoidal category $(\G, \tensor, I)$.

We shall call the exponential $\oc A$ the \emph{sequoidal exponential}.  The following proposition explains the name:

\begin{proposition}
  Let $A$ be a negative game.  Then we get an endofunctor $A\sequoid\blank$ on $\G$ given by sending $B$ to $A\sequoid B$.

  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.  In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
  \[
    \begin{tikzcd}
      B \arrow[r, "\sigma"] \arrow[d, "\fcoal{\sigma}"']
        & A \sequoid B \arrow[d, "\id_A\sequoid\fcoal{\sigma}"] \\
      \oc A \arrow[r, "\alpha"']
        & A \sequoid \oc A
    \end{tikzcd}
    \]
\end{proposition}
\begin{proof}
  See \cite{martinsthesis}.  We shall shortly give a proof in the more general case.
\end{proof}

\subsection{Constructing cofree commutative comonoids in sequoidal categories}

We want to deduce the fact that $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ is the cofree commutative comonoid on $A$ from the fact that $\oc A$ is the final coalgebra for $A\sequoid\blank$.  It turns out that we shall need one more fact about the category of games to prove this.

\begin{notation}
  We shall sometimes make the monoidal structure of the Cartesian product explicit by writing $\sigma\times\tau$ for $\langle\comp\sigma{\pr_1},\comp\tau{\pr_2}\rangle$.
\end{notation}

\begin{definition}
  Let $A,B$ be objects of an inclusive, Cartesian, distributive sequoidal category $(\C,\C_s,J,\wk)$ with final coalgebras $\oc A\xrightarrow{\alpha_A} A\sequoid\oc A$ for all endofunctors of the form $A\sequoid\blank$.  Let $A,B$ be objects of $C$.  Then we have a composite $\kappa_{A,B}\from\oc A \tensor\oc B\to(A\times B)\sequoid(\oc A\tensor \oc B)$:
  \settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
  \begin{IEEEeqnarray*}{RCL}
    \kappa_{A,B}=\oc A \tensor \oc B & \constantwidthxrightarrow{\langle\id_{\oc A\tensor\oc B},\; \sym_{\oc A,\oc B}\rangle} & (\oc A \tensor \oc B) \times (\oc B \tensor \oc A) \\
    \cdots & \constantwidthxrightarrow{(\alpha_A\tensor\id_{\oc B})\times(\alpha_B\tensor\id_{\oc A})} & ((A \sequoid \oc A) \tensor \oc B) \times ((B \sequoid \oc B) \tensor \oc A) \\
    \cdots  & \constantwidthxrightarrow{\wk_{A\sequoid\oc A,\oc B}\times\wk_{B\sequoid\oc B,\oc A}} & ((A \sequoid \oc A) \sequoid \oc B) \times ((B \sequoid \oc B) \sequoid \oc A) \\
      \cdots & \constantwidthxrightarrow{\passoc_{A,\oc A,\oc B}\inv\times\passoc_{B,\oc B,\oc A}\inv} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc B \tensor \oc A) \\
      \cdots & \constantwidthxrightarrow{\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc A \tensor \oc B))
  \end{IEEEeqnarray*}
inducing a morphism
\[
  \oc A\tensor \oc B \xrightarrow{\kappa_{A,B}} (A \sequoid(\oc A\tensor\oc B)) \times (B \sequoid(\oc A\tensor \oc B)) \xrightarrow{\dist\inv}
    (A\times B)\sequoid(\oc A\tensor\oc B)
    \]
  Remembering that our category has a final coalgebra $\oc(A\times B)$ for the functor $(A\times B)\sequoid\blank$, we write $\int_{A,B}$ for the unique morphism $\oc A\tensor\oc B\to \oc(A\times B)$ making the following diagram commute
  \begin{equation}\label{definitionOfInt}
    \begin{tikzcd}
      \oc A \tensor \oc B \arrow[r, "\kappa_{A,B}"] \arrow[d, "\int_{A,B}"']
        & (A\sequoid(\oc A \tensor \oc B) \times (B \sequoid (\oc A \tensor \oc B)) \arrow[r, "\dist\inv"]
          & (A \times B) \sequoid (\oc A \tensor \oc B) \arrow[d, "\id_{A\times B}\sequoid\int_{A,B}"] \\
      \oc(A\times B) \arrow[rr, "\alpha_{A\times B}"']
        &
          & (A \times B) \sequoid \oc(A\times B)
    \end{tikzcd}\tag{$\star$}
  \end{equation}
\end{definition}

\begin{proposition}
  In the category of games, the morphism $\int_{A,B}$ is an isomorphism for all negative games $A,B$.
\end{proposition}
\begin{proof}
  Observe that the morphism $\int_{A,B}$ is the copycat strategy on $\oc A\tensor\oc B\implies \oc (A\times B)$ that starts a copy of $A$ on the left whenever a copy of $A$ is started on the right and starts a copy of $B$ on the left whenever a copy of $B$ is started on the right (indeed, the morphisms in the diagram above are all copycat morphisms, so the copycat strategy we have just described must make that diagram commute.  Since there are infinitely many copies of both $A$ and $B$ available in $\oc (A\times B)$, and since a new copy of $A$ or $B$ may be started at any time, we may define an inverse copycat strategy on $\oc(A\times B)\implies \oc A\tensor\oc B$.
\end{proof}

Our first main result for this section will be the following:
\begin{theorem}
  \label{StrongMonoidalFunctor}
  Let $(\C,\C_s,J,\wk)$ be an inclusive, Cartesian, distributive and decomposable sequoidal category with a final coalgebra $\oc A\xrightarrow{\alpha_A}A\sequoid\oc A$ for each endofunctor of the form $A\sequoid\blank$.  Suppose further that the morphism $\int_{A,B}$ as defined above is an isomorphism for all objects $A,B$.  $A\mapsto\oc A$ gives rise to a strong symmetric monoidal functor from the monoidal category $(\C, \times, 1)$ to the monoidal category $(\C, \tensor, I)$.  
\end{theorem}

We start off by defining a morphism $\mu\from\oc A\to\oc A\tensor\oc A$.  This will turn out to be the comultiplication for the cofree commutative comonoid over $A$.  First, we note that we have the following composite:
\[
  \oc A \xrightarrow{\alpha_A} A \sequoid \oc A \xrightarrow{\Delta} (A\sequoid\oc A)\times (A\sequoid\oc A)\xrightarrow{\dist\inv} (A\times A)\sequoid\oc A
  \]
where $\Delta$ is the diagonal map on the product.  There is therefore a unique morphism $\sigma_A=\fcoal{\comp{\dist\inv}{\comp{\Delta}{\alpha_A}}}$ making the following diagram commute:
\begin{equation}\label{definitionOfSigma}
  \begin{tikzcd}
    \oc A \arrow[r, "\alpha_A"] \arrow[d, "\sigma_A"']
      & A \sequoid \oc A \arrow[r, "\Delta"]
        & (A \sequoid \oc A)\times(A \sequoid \oc A) \arrow[r, "\dist\inv"]
          & (A \times A) \sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\sigma_A"] \\
    \oc(A\times A) \arrow[rrr, "\alpha_{A\times A}"]
      &
        &
          & (A \times A) \sequoid \oc(A \times A)
  \end{tikzcd}\tag{\dag}
\end{equation}
and we may set $\mu_A=\comp{\int_{A,A}\inv}{\sigma_A}$.

We also define a morphism $\der_A\from \oc A \to A$.  Note that since $I$ is isomorphic to $1$, we have a unique morphism $*_A\from A\to I$ for each $A$.  We define $\der_A$ to be the composite
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\alpha_A"]
      & A \sequoid \oc A \arrow[r, "\id_A \sequoid *_{\oc A}" yshift=0.3em]
        & A \sequoid I \arrow[r, "\run_A"]
          & A
  \end{tikzcd}
  \]

We define the action of $\oc$ on morphisms as follows: suppose that $\sigma\from A \to B$ is a morphism in $\C$.  Then we have a composite
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\mu"]
      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
        & A \tensor \oc A \arrow[r, "\sigma\tensor\id_{\oc A}"]
          & B \tensor \oc A \arrow[r, "\wk_{B,\oc A}"]
            & B \sequoid \oc A
  \end{tikzcd}
  \]
There is therefore a unique morphism $\oc\sigma\from\oc A \to\oc B$ making the following diagram commute:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\mu"] \arrow[d, "\oc\sigma"']
      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
        & A \tensor \oc A \arrow[r, "\sigma\tensor\id_{\oc A}"]
          & B \tensor \oc A \arrow[r, "\wk_{B,\oc A}"]
            & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
    \oc B \arrow[rrrr, "\alpha_B"]
      &
        &
          &
            & B \sequoid \oc B
  \end{tikzcd}
  \]

\begin{proposition}\label{StrongMonoidalFunctorActual}
  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.  Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
\end{proposition}
\begin{proof}
  See Appendix.
\end{proof}

This completes the proof of Theorem \ref{StrongMonoidalFunctor}.

Since $\oc$ is a strong monoidal functor, it induces a functor $\CCom(\oc)$ from the category $\CCom(\C,\times,1)$ of comonoids over $(\C, \times, 1)$ to the category $\CCom(\C,\tensor,I)$ of comonoids over $(\C, \tensor, I)$ making the following diagram commute:
\[
  \begin{tikzcd}
    \CCom(\C,\times,1) \arrow[r, "\F"] \arrow[d, "\CCom(\oc)"']
      & (\C, \times, 1) \arrow[d, "\oc"] \\
    \CCom(\C, \tensor, I) \arrow[r, "\F"]
      & (\C, \tensor, I)
  \end{tikzcd}
  \]
where $\F$ is the forgetful functor.

Let $A$ be an object of $\C$.  Since $(\C, \times, 1)$ is Cartesian, the diagonal map $\Delta\from A\to A\times A$ is the cofree commutative comonoid over $A$ in $(\C,\times,1)$.

\begin{proposition}
  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right) = \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A$
\end{proposition}
\begin{proof}
  By the (standard) construction of the functor $\CCom(\oc)$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\oc\Delta"]
        & \oc (A\times A) \arrow[r, "\int_{A,A}\inv"]
          & \oc A \tensor \oc A
    \end{tikzcd}
    \]
\end{proof}

In order to show that $\sigma\mapsto\oc\sigma$ respects composition, we need the following lemma:

\begin{lemma}\label{aFormulaForAlpha}
  Let $A$ be an object of $\C$.  Then $\alpha_A\from\oc A\to A\sequoid\oc A$ is equal to the following composite:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\mu_A"]
        & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
          & A \tensor \oc A \arrow[r, "\wk_{A,\oc A}"]
            & A \sequoid \oc A
    \end{tikzcd}
    \]
\end{lemma}

\begin{proof}
  We may paste together diagrams \eqref{definitionOfInt} and \eqref{definitionOfSigma} to form the following diagram (where we shall omit subscripts where there is no ambiguity):
  \begin{equation*}
    \begin{tikzcd}[cramped]
      \oc A \arrow[r, "\alpha"] \arrow[d, "\sigma_A"']
        & A \sequoid \oc A \arrow[r, "\Delta"]
          &[-24pt] (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[r, "\dist\inv"]
            & (A \times A) \sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\sigma_A"] \\
      \oc(A\times A) \arrow[rrr, "\alpha"]
        &
          &
            & (A \times A) \sequoid \oc(A\times A) \\
      \oc A \tensor \oc A \arrow[rr, "\kappa_{A,A}"] \arrow[u, "\int_A"]
        &
          & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "\dist\inv"]
            & (A\times A)\sequoid(\oc A \tensor \oc A) \arrow[u, "\id_{A\times A}\sequoid\int_A"']
    \end{tikzcd}
  \end{equation*}
  where we observe that the composites down the left and right hand sides (after inverting the lower arrows) are $\mu_A$ and $\id_{A\times A}\sequoid\mu_A$.

  Now note that we have the following commutative square:
  \[
    \begin{tikzcd}
      (A \times A) \sequoid \oc A \arrow[r, "\dist"] \arrow[d, "\id_{A\times A}\sequoid\mu_A"']
        & (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[d, "(\id\sequoid\mu)\times(\id\sequoid\mu)"] \\
      (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[r, "\dist"']
        & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)
    \end{tikzcd}
    \]

  (using the definition of $\dist$).  Putting this together with the diagram above, we get the following commutative diagram:
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\alpha"] \arrow[d, "\mu_A"']
        & A \sequoid \oc A \arrow[r, "\Delta"]
          & (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[d, "\id\sequoid\mu_A\times\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[rr, "\kappa_{A,A}"]
        & \cdots \arrow[r]
          & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A))
    \end{tikzcd}
    \]
  We now expand the definition of $\kappa_{A,A}$  and take the projections on to the first and second components, yielding the following two commutative diagrams:
  \[
    \begin{tikzcd}\label{firstProjectionDiagram}
      \oc A \arrow[rrr, "\alpha"] \arrow[d, "\mu_A"']
        &
          &
            & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"]
        & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"]
          & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
            & A \sequoid (\oc A \tensor \oc A)
    \end{tikzcd}\tag{\textbf{1}}
    \]

  \begin{equation*}\label{secondProjectionDiagram}
    \begin{tikzcd}[cramped]
     \oc A \arrow[rrrr, "\alpha"] \arrow[d, "\mu_A"']
        &
          &
            &
              & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[r, "\sym"']
        & \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id" yshift=0.4em]
          & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
            & A \sequoid (\oc A \tensor \oc A) \arrow[r, "\id\sequoid\sym"']
              & A \sequoid (\oc A \tensor \oc A)
    \end{tikzcd}\tag{\textbf{2}}
  \end{equation*}

  From diagram \eqref{firstProjectionDiagram}, we construct the following commutative diagram:
  \[
    \begin{tikzcd}
      \oc A \arrow[rrr, "\alpha"] \arrow[d, rightsquigarrow, "\mu_A"'] \arrow[phantom, drrr, "\textbf{a}" xshift=0.9em]
        &
          &
            & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
      \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"] \arrow[ddr, rightsquigarrow, "\der_A\tensor\id"'] \arrow[phantom, dr, "\textbf{b}" xshift=0.6em]
        & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "(\id\sequoid*)\tensor\id"] \arrow[phantom, dr, "\textbf{c}" xshift=0.3em]
          & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"] \arrow[d, "(\id\sequoid*)\sequoid\id"] \arrow[phantom, dr, "\textbf{e}" xshift=0.3em]
            & A \sequoid (\oc A \sequoid \oc A) \arrow[d, "\id\sequoid(*\tensor\id)"] \\
      %
        & (A \sequoid I) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "\run\tensor\id"] \arrow[phantom, dr, "\textbf{d}" xshift=0.3em]
          & (A \sequoid I) \sequoid \oc A \arrow[r, "\passoc\inv"], \arrow[d, "\run\tensor\id"] \arrow[phantom, r, "\textbf{f}" xshift=-0.6em, yshift=-1.0em]
            & A \sequoid (I \tensor \oc A) \arrow[dl, "\id\sequoid\lunit"] \\
      %
        & A \tensor \oc A \arrow[r, rightsquigarrow, "\wk"]
          & A \sequoid \oc A
            &
    \end{tikzcd}
    \]

  \textbf{a} is diagram \eqref{firstProjectionDiagram}.

  \textbf{b} commutes by the definition of $\der_A$.

  \textbf{c} and \textbf{d} commute because $\wk$ is a natural transformation.

  \textbf{e} commutes because $\passoc$ is a natural transformation.

  \textbf{f} commutes by one of the coherence conditions in the definition of a sequoidal category.

  We now observe that the composite of the three squiggly arrows is the composite we are trying to show is equal to $\alpha$; we have $\alpha$ along the top, so it will suffice to show that the composite
  \[
    \begin{tikzcd}
      \xi_A\;=\;\oc A \arrow[r, "\mu_A"]
        & \oc A \tensor \oc A \arrow[r, "*\tensor\id"]
          & I \tensor \oc A \arrow[r, "\lunit"]
            & \oc A
    \end{tikzcd}
    \]
  is equal to the identity.  We do this using diagram \eqref{secondProjectionDiagram}.  First we construct the diagram shown in Figure \ref{hugeDiagram1}.

  \begin{SidewaysFigure}
    \[
      \begin{tikzcd}[ampersand replacement=\&]
        \oc A \arrow[rrrrr, "\alpha"] \arrow[d, "\mu_A"'] \arrow[phantom, drrrrr, "\textbf{a}"]
          \&
            \&
              \&
                \& 
                  \& A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
        \oc A \tensor \oc A  \arrow[r, "\sym"] \arrow[d, "*\tensor\id"'] \arrow[phantom, dr, "\textbf{b}"]
          \& \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"] \arrow[d, "\id\tensor*"]
            \& (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "\id\sequoid*"] \arrow[phantom, dr, "\textbf{d}"]
              \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"] \arrow[d, "\id\sequoid*"] \arrow[phantom, dr, "\textbf{e}"]
                \& A \sequoid (\oc A \tensor \oc A) \arrow[r, "\id\sequoid\sym"] \arrow[d, "\id\sequoid(\id\sequoid*)"] \arrow[phantom, dr, "\textbf{c}"]
                  \& A \sequoid (\oc A \tensor \oc A) \arrow[d, "\id\sequoid (*\sequoid\id)"] \\
        I \tensor \oc A \arrow[r, "\sym"] \arrow[d, "\lunit"'] \arrow[phantom, dr, "\textbf{g}"]
          \& \oc A \tensor I \arrow[r, "\alpha\tensor\id"] \arrow[d, "\runit"] \arrow[phantom, dr, "\textbf{f}"]
            \& (A \sequoid \oc A) \tensor I \arrow[r, "\wk"] \arrow[d, "\runit"] \arrow[phantom, dr, "\textbf{i}"]
              \& (A \sequoid \oc A) \sequoid I \arrow[r, "\passoc\inv"] \arrow[d, "\run"] \arrow[phantom, dr, "\textbf{j}"]
                \& A \sequoid (\oc A \tensor I) \arrow[r, "\id\sequoid\sym"] \arrow[d, "\id\sequoid\runit"] \arrow[phantom, dr, "\textbf{h}"]
                  \& A \sequoid (I \tensor \oc A) \arrow[d, "\id\sequoid\lunit"] \\
        \oc A \arrow[r, "\id"']
          \& \oc A \arrow[r, "\alpha"]
            \& A \sequoid \oc A \arrow[r, "\id"']
              \& A \sequoid \oc A \arrow[r, "\id"']
                \& A \sequoid \oc A \arrow[r, "\id"']
                  \& A \sequoid \oc A
      \end{tikzcd}
      \]
    \caption{
      \textbf{a} is diagram \eqref{secondProjectionDiagram}. \\[\baselineskip]
      \textbf{b} and \textbf{c} commute because $\sym$ is a natural transformation, \textbf{d} commutes because $\wk$ is a natural transformation and \textbf{e} commutes because $\passoc$ is a natural transformation.  \textbf{f} commutes because $\runit$ is a natural transformation. \\[\baselineskip]
      \textbf{g} and \textbf{h} commute by one of the coherence conditions for a symmetric monoidal category.  \textbf{i} commutes by one of the coherence conditions for $\wk$ in the definition of a sequoidal category and \textbf{j} commutes by one of the coherence conditions for $\passoc$ in the definition of a sequoidal category.
    }\label{hugeDiagram1}
  \end{SidewaysFigure}

  Now observe that the composite $\xi_A$ is running along the left hand side of Figure \ref{hugeDiagram1}, while $\id\sequoid\xi$ is running along the right.  Since we have $\alpha$ along the bottom, it follows by the uniqueness of $\fcoal{\cdot}$ that $\xi=\fcoal{\alpha}=\id_{\oc A}$.  
\end{proof}

Now we are ready to show that $\sigma\mapsto\oc \sigma$ respects composition.  Let $A,B,C$ be objects, let $\sigma$ be a morphism from $A$ to $B$ and let $\tau$ be a morphism from $B$ to $C$.   Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc\sigma$, $\oc\tau$, we may construct a commutative diagram:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\mu"] \arrow[d, "\oc\sigma"']
      & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
        & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
          & B \tensor \oc A \arrow[r, "\wk"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
            & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc \tau"']
      & \oc B \tensor \oc B \arrow[rr, "\der\tensor\id"]
        &
          & B \tensor \oc B \arrow[r, "\wk"] \arrow[d, "\tau\tensor\id"]
            & B \sequoid \oc B \\
    %
      &
        &
          & C \tensor \oc B \arrow[r, "\wk"] \arrow[d, dotted, "\id\tensor\oc\tau"']
            & C \sequoid \oc B \arrow[d, "\id\sequoid\oc\tau"] \\
    \oc C \arrow[r, "\mu"]
      & \oc C \tensor \oc C \arrow[rr, "\der\tensor\id"]
        &
          & C \tensor \oc C \arrow[r, "\wk"]
            & C \sequoid \oc C
  \end{tikzcd}
  \]
Here, the outermost (solid) shapes commute by the definition of $\oc\sigma$, $\oc\tau$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).  The smaller squares on the right hand side commute because $\wk$ is a natural transformation.  Now observe that $\wk_{X,Y}=\comp{\pr_1}{\dec_{X,Y}}$ is the composition of epimorphisms, so is an epimorphism for all $X,Y$.  It follows that the two rectangles on the left commute as well.

Throwing away the right hand squares and adding some new arrows at the right, we arrive at the following commutative diagram:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\comp{(\sigma\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc\sigma"']
      &[72pt] B \tensor \oc A \arrow[r, "\tau\tensor\id"] \arrow[d, "\id\tensor\oc\sigma"']
        & C \tensor \oc A \arrow[d, "\id\tensor\oc\sigma"] \\
    \oc B \arrow[d, "\oc\tau"']
      & B \tensor\oc B \arrow[r, "\tau\tensor\id"] \arrow[d, "\tau\tensor\oc\tau"']
        & C \tensor \oc B \arrow[dl, "\id\tensor\oc\tau"] \\
    \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
      & C \tensor \oc C
        &
  \end{tikzcd}
  \]
We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and re-apply $\wk$ on the right hand side:
\[
  \begin{tikzcd}
    \oc A \arrow[r, "\comp{((\comp\tau\sigma)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc\sigma"']
      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc\sigma"'] \arrow[r, "\wk"]
        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
    \oc B \arrow[d, "\oc\tau"']
      & C \tensor \oc B \arrow[d, "\id\tensor\oc\tau"'] \arrow[r, "\wk"]
        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc\tau"] \\
    \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
      & C \tensor \oc C \arrow[r, "\wk"]
        & C \sequoid\oc C
  \end{tikzcd}
  \]
By Lemma \ref{aFormulaForAlpha}, the composite along the bottom is equal to $\alpha_C$.  Therefore, by uniqueness of $\fcoal{\cdot}$, we have
\[
  \comp{\oc\tau}{\oc\sigma} = \fcoal{\comp{\wk}{\comp{((\comp\tau\sigma)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp\tau\sigma)
  \]
Therefore, $\oc$ is indeed a functor.

We now want to show that $\oc$ has the structure of a strong symmetric monoidal functor from $(\C,\times,1)$ to $(\C,\tensor,I)$.  The relevant morphisms are:
\[
  \int_{A,B}\from \oc A \tensor \oc B \to \oc (A \times B)
  \quad
  \dec^0\from I\to 1
  \]
By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.

\begin{theorem}
  \label{Coalgebra__CoCoCo}
  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.  Let $A$ be an object of $\C$ (equivalently, of $\C_s$).  Then $\oc A$ is the carrier for the cofree commutative comonoid over $A$.
\end{theorem}

%%
%% Bibliography
%%

%% Either use bibtex (recommended),

\bibliography{../../../common/phd_bibliography}

%% .. or use the thebibliography environment explicitely

\end{document}

### 2017-03-29 round-corner/paper/lipics-v2016-authors/sequoidal.tex
More changes

@@
 
-% Author macros and packages
+% Additional packages and macros
 \usepackage{IEEEtrantools} % for \IEEEeqnarray
@@
 \begin{theorem}
-  If $A,B$ are games, let $J$ be the inclusion functor $\G_s\to\G$ and let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
+  Let $J$ be the inclusion functor $\G_s\to\G$.  If $A,B$ are games, let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
   \[
@@
 
-\begin{proposition}
-  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right) = \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A$
+\begin{proposition}\label{itsMu}
+  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ has comultiplication given by $\mu_A\from\oc A \to \oc A\tensor\oc A$ and counit given by the unique morphism $\eta_A\from \oc A \to I$.
 \end{proposition}
 \begin{proof}
-  By the (standard) construction of the functor $\CCom(\oc)$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\oc\Delta"]
-        & \oc (A\times A) \arrow[r, "\int_{A,A}\inv"]
-          & \oc A \tensor \oc A
-    \end{tikzcd}
-    \]
+  See appendix.
 \end{proof}
+
+In particular, this proves that the comultiplication $\mu_A$ is associative and that the counit $\eta_A$ is a valid counit for $\mu_A$.
+
+We can now state our second main result from this section.
+
+\begin{theorem}
+  \label{Coalgebra__CoCoCo}
+  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.
+Let $A$ be an object of $\C$ (equivalently, of $\C_s$).
+Then $\oc A$, together with the comultiplication $\mu_A$ and counit $\eta_A$, is the cofree commutative comonoid over $A$.
+\end{theorem}
+
+\appendix
+
+\section{Proofs}
+
+\subsection{Proof of Proposition \ref{StrongMonoidalFunctorActual}}
+
+\begingroup
+\def\thetheorem{\ref{StrongMonoidalFunctorActual}}
+\begin{proposition}
+  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
+Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
+\end{proposition}
+\addtocounter{theorem}{-1}
+\endgroup
 
@@
 
-\begin{theorem}
-  \label{Coalgebra__CoCoCo}
-  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.
-Let $A$ be an object of $\C$ (equivalently, of $\C_s$).
-Then $\oc A$ is the carrier for the cofree commutative comonoid over $A$.
-\end{theorem}
-
 %%
@@
 
-\bibliography{../../../common/phd_bibliography}
+\bibliography{bibliography}
 

### 2017-03-31 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Added transfinite games section.

@@
 \DeclareMathOperator{\CCom}{CCom}
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
+\newcommand{\Set}{\catname{Set}}
+\newcommand{\Ord}{\catname{Ord}}
+\newcommand\oppcat[1]{#1^{\mathrm{op}}}
 
@@
 
+\begin{proof}
+  See Appendix.
+\end{proof}
+
+\section{Transfinite Games}
+
+Of the conditions that we used to construct the cofree commutative comonoid in sequoidal categories, the requirement that $\int_{A,B}$ be an isomorphism stands out as the least satisfactory.
+All the other conditions are `finitary', and relate directly to the connectives we have introduced, whereas the morphism $\int_{A,B}$ can only be constructed using the final coalgebra property for the exponential connective $\oc$.
+For this reason, we might wonder whether we can do without the condition that $\int_{A,B}$ be an isomorphism.
+In this section, we shall give a negative answer to that question: we shall construct an inclusive, distributive, decomposable sequoidal closed category with final coalgebras $\oc A$ for all functors of the form $A\sequoid\blank$, and shall show that $\oc A$ does not have a natural comonoid structure.
+In doing this, we hope to shed some light upon alternative algebraic or coalgebraic constructions for the cofree commutative comonoid that work in a purely `finitary' manner.
+
+Our sequoidal category will be closely modelled upon the category of games we have just considered: the objects will be games, with the modification that sequences of moves may now have transfinite length.
+This is a natural construction, occurring in the study of determinacy by Mycielski \cite{mycielskiChoice}, Blass \cite{blassChoice} and Weiss \cite{longgamesbook}, and it appears to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
+
+The general idea is as follows: we will show that the definition of the final coalgebra for the sequoid functor in a category of transfinite games is largely unchanged from the definition in the category of games with finite-length plays: $\oc A$ is the game formed from a countably infinite number of copies of $A$, indexed by $\omega$, with the proviso that player $O$ must open them in order.
+We observe that the copycat strategy $\int_{A,B}\from\oc A\tensor\oc B\to \oc(A\times B)$ is not an isomorphism, and that we cannot construct the comultiplication $\oc A \to \oc A \tensor \oc A$ in a sensible way.
+Moreover, we cannot construct the comonad $\oc A \to \oc \oc A$, so $\oc$ does not give us a model of linear logic in even the most general sense.
+In all three cases, the reason why the construction fails is that we might run out of copies of the game $A$ (or $B$) on the left hand side before we have run out of copies on the right hand side.
+In the finite-plays setting, it is impossible to run out of copies of a subgame, because there are infinitely many copies, so it is impossible to play in all of them in a finite-length play.
+In the transfinite setting, however, we cannot guarantee this: consider, for example, a position in $\oc A_0 \implies \oc A_1 \tensor \oc A_2$ (with indices given so we can refer to the different copies of $A$) in which player $O$ has opened all the copies of $A$ in $\oc A_1$.
+Since player $P$ is playing by copycat, she must have opened all of the copies of $A$ in $\oc A_0$.
+If, at time $\omega+1$, player $O$ now plays in $\oc A_2$, player $P$ will have no reply to him.
+
+The `correct' definition of $\oc A$ in the transfinite game category is one in which there is an unlimited number of copies of $A$ to open (rather than $\omega$-many), but this is not the final coalgebra for the functor $A\sequoid\blank$.
+[TODO: discuss ways to construct this object]
+
+\subsection{Transfinite Games}
+
+We give a brief summary of the construction of the category of transfinite games.  Full details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
+
+We shall fix an additively indecomposable ordinal $\alpha = \omega^\beta$ throughout, which will be a bound on the ordinal length of positions in our game.
+So, for example, the original category of games is the case $\alpha=\omega$.
+If $X$ is a set, we write $X^{*<\alpha}$ for the set of transfinite sequences of elements of $X$ of length less than $\alpha$.
+
+\begin{definition}
+  A \emph{game} or a \emph{game over $\alpha$} or an \emph{$\alpha$-game} is a tuple $A=(M_A,\lambda_A,\zeta_A,P_A)$, where:
+  \begin{itemize}
+    \item $M_A$ is a set of moves
+    \item $\lambda_A\from M_A\to\OP$ designates each move as an \emph{$O$-move} or a \emph{$P$-move}
+    \item $P_A\subset M_A^{*<\alpha}$ is a non-empty prefix-closed set of transfinite sequences of moves from $M_A$, called \emph{positions}.
+We say that $s$ is a \emph{successor position} if the length of $s$ is a successor ordinal and we say that $s$ is a \emph{limiting} position if the length of $s$ is a limit ordinal.
+    \item $\zeta_A\from P_A\to\OP$ designates each position as an \emph{$O$-position} or a \emph{$P$-position}.
+  \end{itemize}
+  such that:
+  \begin{description}
+    \item[Consistency] If $sa\in P_A$ is a successor position, then $\zeta_A(sa) = \lambda_A(a)$
+    \item[Alternation] If $s,sa\in P_A$, then $\zeta_A(s) = \neg\zeta_A(sa)$
+    \item[Limit closure] If $s\in M_A^{*<\alpha}$ is a limiting position such that $t\in P_A$ for all proper prefixes $t\pprefix s$, then $s\in P_A$.
+  \end{description}
+
+  We say that a game $A$ is \emph{positive} if $\zeta_A(\emptyplay)=O$ and \emph{negative} if $\zeta_A(\emptyplay) = P$.
+We say that $A$ is \emph{completely negative} if $\zeta_A(s)=P$ for all limiting plays $s$.
+\end{definition}
+
+Apart from the possibly transfinite length of sequences of moves, the only new thing in this definition is the function $\zeta_A$.
+Thanks to the consistency condition, $\zeta_A$ gives us no new information for successor positions; it is necessary in order to tell us which player is to move at limiting positions.
+
+\begin{definition}
+  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the following conditions:
+  \begin{description}
+    \item[Closure under $O$-replies] If $s\in\sigma$ is a $P$-position and $sa\in P_A$, then $sa\in\sigma$.
+    \item[Determinism] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
+  \end{description}
+\end{definition}
+
+Given games $A$ and $B$, we may form their product $A\times B$, tensor product $A\tensor B$, linear implication $A\implies B$ and sequoid $A\sequoid B$ in roughly the same way that we construct these connectives for finite-length games.
+The only point we need to take care of is the behaviour of the $\zeta$-functions at limit ordinals.
+We do this according to the following formulae:
+\begin{gather*}
+  \zeta_{A\times B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
+  \zeta_{A\tensor B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
+  \zeta_{A\implies B}(s) = \zeta_A(s) \Rightarrow \zeta_B(s) \\
+  \zeta_{A\sequoid B}(s) = \zeta_A(s) \wedge \zeta_B(s)
+\end{gather*}
+Here, $\wedge$ and $\Rightarrow$ are the usual propositional connectives on $\{T,F\}$, but with $T$ replaced by $P$ and $F$ replaced by $O$.
+
+Once we have defined our connectives, we may define a \emph{morphism} from $A$ to $B$ to be a strategy for $A\implies B$ and we may define composition of morphisms in the usual way: given games $A$, $B$ and $C$, and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we define
+\[
+  \sigma\|\tau = \{\s\in (M_A \cprd M_B \cprd M_C)^{*<\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
+  \]
+and then we define
+\[
+  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
+  \]
+\begin{remark}
+  Since $\alpha$ is additively decomposable, the interleaving of two sequences of length less than $\alpha$ must itself have length less than $\alpha$.
+This is important: if we allow $\alpha$ to be an additively decomposable ordinal, then it is possible to construct two strategies whose composite is not closed under $O$-replies because a particular reply in the interleaving of two sequences occurs at time later than $\alpha$ and so is not included.
+\end{remark}
+
+We can show that this composition is associative and moreover that we obtain an inclusive, distributive, decomposable sequoidal category.
+We call this category $\G(\alpha)$ and call the corresponding strict subcategory $\G_s(\alpha)$.
+The hardest part of this is showing that the category is monoidal closed, because the linear implication of completely negative games is not necessarily completely negative.
+
+\subsection{The final sequence for the sequoidal exponential}
+
+We now want to show that $\G(\alpha)$ has final coalgebras for the functor $A\sequoid\blank$, given by the transfinite game $\oc A$, which is defined as follows:
+\begin{itemize}
+  \item $M_{\oc A} = M_A \times \omega$
+  \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$
+\end{itemize}
+We define $\oc P_A$ to be the set of all sequences $s\in M_{\oc A}^{*<\alpha}$ such that $s\vert_n\in P_A$ for all $n$.  Then we define $\zeta_{\oc A}\from\oc P_A\to\OP$ by
+\[
+  \zeta_{\oc A}(s) = \bigwedge_{n\in\omega}\zeta_A(s\vert_n)
+  \]
+In other words, $\zeta_{\oc A}(s)=P$ if and only if $\zeta_A(s\vert_n)=P$ for all $n$.
+
+There is a natural copycat strategy $\alpha_A\from \oc A \to A \sequoid \oc A$, just as in the finite plays case.
+We want to show that this is the final coalgebra for $A\sequoid\blank$.
+The proof for the finite case found in \cite{martinsthesis} will not work in this case, since it implicitly uses the fact that $\oc A$ is the limit of the sequence
+\[
+  I \leftarrow A \leftarrow A \sequoid A \leftarrow A \sequoid (A \sequoid A) \leftarrow \cdots
+  \]
+(cf. also \cite{MelliesCofCommCom}).  In the transfinite categories, this is no longer the case.
+
+While it is possible to prove that $\alpha_A\from \oc A\to A\sequoid \oc A$ is the final coalgebra for $A\sequoid\blank$ directly, we shall instead give a proof by extending the sequence given above to an ordinal-indexed sequence.
+This is the \emph{final sequence}, familiar in coalgebra \cite{finalseq}.
+Specifically, we construct a functor $\F\from\oppcat{\Ord}\to\G(\alpha)$, where $\Ord$ is the order category of the ordinals, writing
+\begin{gather*}
+  \F(\gamma)=A^{\sequoid\gamma}\\
+  \F(\gamma\le\delta)=j_\gamma^\delta\from A^{\sequoid\delta}\to A^{\sequoid\gamma}
+\end{gather*}
+according to the following inductive recipe:
+\begin{itemize}
+  \item $A^{\sequoid 0} = 1$
+  \item $A^{\sequoid (\gamma + 1)} = A \sequoid A^{\sequoid\gamma}$
+  \item If $\mu$ is a limit ordinal, then $A^{\sequoid\mu}$ is the limit of the diagram formed by the $A^{\sequoid\gamma}$ for $\gamma<\mu$, together with the morphisms $j_\gamma^\delta$, for $\gamma\le\delta<\mu$.
+  \item $j_0^\gamma=*$
+  \item $j_\gamma^\lambda$ is the morphism in the limiting cone
+  \item $j_\gamma^{\delta+1} = \comp{j_\delta^{\delta+1}}{j_\gamma^\delta}$
+  \item If we write $C_\lambda$ for the limiting cone for $\lambda$ over the $A^{\sequoid\gamma}$ for $\gamma<\mu$, then we may form a cone $A\sequoid C_\lambda$ over the same diagram by applying the functor $A\sequoid\blank$ to $C_\lambda$ and then extending the cone to $1$ in the only possible way.
+Then $j_\lambda^{\lambda+1}$ is the unique morphism from $A^{\sequoid(\lambda+1)}$ to $A^{\sequoid\lambda}$ inducing a morphism of cones from $A\sequoid C_\lambda$ to $C_\lambda$.
+\end{itemize}
+
+It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then $j_\delta^{\delta+1}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
+In this case, we say that the sequence \emph{stabilizes at $\delta$}.
+Our proof strategy is therefore to show that the sequence stabilizes at some $\delta$, and to show that $A^{\sequoid\delta}$ is isomorphic to $\oc A$.
+
+We do this by giving a classification of the games $A^{\sequoid\gamma}$.
+Let $s\in\omega^{*<\alpha}$ be any transfinite sequence of natural numbers.
+We define the \emph{derivative} $\Delta s$ of $s$ to be the sequence given by removing all instances of $0$ from $s$ and subtracting $1$ from all other terms.
+In other words, if $s\from\gamma\to\omega$, for $\gamma<\alpha$, then we have:
+\[
+  \Delta s = s\inv(\omega\setminus\{0\})\xrightarrow{s}\omega\setminus\{0\}\xrightarrow{-1}\omega
+  \]
+(where $s\inv(\omega\setminus\{0\})$ carries the induced order).  We now define predicates $\blank\le\gamma$ on sequences $s\in \omega^{*<\alpha}$ as follows:
+\begin{itemize}
+  \item $\emptyplay\le 0$
+  \item If $\Delta s\le\gamma$, then $s\le\gamma+1$
+  \item If $\mu$ is a limit ordinal and $s\in\omega^{*<\alpha}$ is such that for all successor-length prefixes $t\prefix s$ we have $t\le\gamma$ for some $\gamma<\mu$, then $s\le\mu$.
+In other words, $\{s\in \omega^{*<\alpha}\suchthat s\le\mu\}$ is the limit-closure of the union of the sets $\{s\in\omega^{*<\alpha}\suchthat s\le\gamma\}$ for $\gamma<\mu$.
+\end{itemize}
+
+We can prove some basic results about these predicates:
+\begin{proposition}\label{basicResultsAboutRank}
+  i) If $s\le\gamma$ and $t$ is any subsequence of $s$ (not necessarily an initial prefix), then $t\le\gamma$.
+
+  ii) If $s\le\gamma$, then $\Delta s\le\gamma$
+
+  iii) If $s\le\gamma$ and $\gamma\le\delta$, then $s\le\delta$
+
+  iv) If $s\in\omega^{*<\alpha}$ has length $\mu$, where $\mu$ is a limit ordinal, then $s\le\mu$.
+If $s$ has length $\mu+n$ for some $n\in\omega$, then $s\le\mu+\omega$.
+In particular, $s\le\alpha$ for all $s\in \omega^{*<\alpha}$.
+\end{proposition}
+
+\begin{proof}
+  See Appendix.
+\end{proof}
+
+Our classification result for the final sequence then becomes:
+\begin{theorem}\label{finalseqClassification}
+  Let $A$ be any game.  Then $A^{\sequoid\gamma}\cong(M_{\oc A}, \lambda_{\oc A}, \zeta_{\oc A}, P_{\oc A,\gamma})$, where
+  \[
+    P_{\oc A,\gamma} = \{s\in P_{\oc A}\suchthat \pr_2\circ s\le\gamma\}
+    \]
+  The morphism $j_\gamma^\delta$ is the copycat strategy.
+\end{theorem}
+
+\begin{proof}
+  See Appendix.
+\end{proof}
+
+\begin{corollary}
+  The final sequence for $A\sequoid\blank$ stabilizes at $\alpha$ and we have $A^{\sequoid\alpha}=\oc A$.
+\end{corollary}
+\begin{proof}
+  By Proposition \ref{basicResultsAboutRank}(iv), $\pr_2\circ s\le\alpha$ for all $s\in P_{\oc A}$ and so $\pr_2\circ s\le(\alpha+1)$, by Proposition \ref{basicResultsAboutRank}(iii).
+It follows, by Theorem \ref{finalseqClassification}, that $A^{\sequoid\alpha}=\oc A$ and that the morphism $A^{\sequoid\alpha}\to A^{\sequoid(\alpha+1)}$ is the morphism $\alpha_A$.
+\end{proof}
+
 \appendix

### 2017-04-04 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Continued working.

@@
 
-It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then $j_\delta^{\delta+1}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
+It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then ${j_\delta^{\delta+1}}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
 In this case, we say that the sequence \emph{stabilizes at $\delta$}.
@@
   \]
-By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.
+By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.  That is, for any games $A,B,C$, we need to show that the following diagrams commute:
+\[
+  \begin{tikzcd}
+    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\assoc_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id_{\oc C}"]
+      & \oc A \tensor (\oc B \tensor \oc C) \arrow[d, "\id_{\oc A}\tensor\int_{B,C}"] \\
+    \oc (A \times B) \tensor \oc C \arrow[d, "\int_{A\times B,C}"]
+      & \oc A \tensor \oc(B \times C) \arrow[d, "\int_{A,B\times C}"] \\
+    \oc ((A \times B) \times C) \arrow[r, "\oc\assoc_{\times,A,B,C}"]
+      & \oc (A \times (B \times C))
+  \end{tikzcd}
+  \]
+
+We first prove a small lemma, which gives us a simpler way to compute $\oc \sigma$ in the case that $\sigma$ is a morphism in $\C_s$.
+
+\begin{lemma}\label{ocStrict}
+  Let $A,B$ be objects of $\C_s$ and let $\sigma$ be a morphism from $A$ to $B$ in $\C_s$.  Then the following diagram commutes:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\oc \sigma"']
+        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
+          & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
+      \oc B \arrow[rr, "\alpha_B"]
+        &
+          & B \sequoid \oc B
+    \end{tikzcd}
+    \]
+\end{lemma}
+
+\begin{proof}
+  By the definition of $\oc \sigma$, we have the following commutative diagram:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[r, "\mu_A"] \arrow[d, "\oc \sigma"']
+        & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
+          & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
+            & B \tensor \oc A \arrow[r, "\wk"]
+              & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
+      \oc B \arrow[rrrr, "\alpha_B"]
+        &
+          &
+            &
+              & B \sequoid \oc B
+    \end{tikzcd}
+    \]
+  Therefore, it will suffice to show that the following diagram (solid lines) commutes:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\mu_A"']
+        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
+          & B \sequoid \oc A \\
+      \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
+        & A \tensor \oc A \arrow[u, dotted, "\wk"] \arrow[r, "\sigma\tensor\id"]
+          & B \tensor \oc A \arrow[u, "\wk"]
+    \end{tikzcd}
+    \]
+  The left hand square commutes by Lemma \ref{aFormulaForAlpha}.  The right hand square commutes because $\wk$ is a natural transformation.
+\end{proof}
+
+To show that the first coherence diagram commutes, we define a composite $\eta_{A,B,C}$:
+  \settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
+  \begin{gather*}
+    (\oc A \tensor \oc B) \tensor \oc C \constantwidthxrightarrow{\langle\id,\; \sym\rangle} ((\oc A \tensor \oc B) \tensor \oc C) \times (\oc C \tensor (\oc A \tensor \oc B)) \\
+    \hspace{6pt}\cdots \constantwidthxrightarrow{((\comp{\dist\inv}{\kappa_{A,B}})\tensor\id)\times(\alpha_C\tensor\id)} (((A \times B) \sequoid (\oc A \tensor \oc B)) \tensor \oc C) \times ((C \sequoid \oc C) \tensor (\oc A \tensor \oc B)) \\
+    \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} (((A \times B) \sequoid (\oc A \tensor \oc B)) \sequoid \oc C) \times ((C \sequoid \oc C) \sequoid (\oc A \tensor \oc B)) \\
+    \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid (\oc C \tensor (\oc A \tensor \oc B))) \\
+    \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C))
+  \end{gather*}
+
+  Observe the similarity between the definition of $\eta_{A,B,C}$ and that of $\kappa_{A\times B,C}$.
+Indeed, it may be easily verified that the following diagram commutes, using the definition of $\int_{A,B}$ as the anamorphism for $\comp{\dist\inv}{\kappa_{A,B}}$ and the fact that $\wk$, $\passoc$ and $\sym$ are natural transformations:
+  \[
+    \begin{tikzcd}
+      ((\oc A \tensor \oc B) \tensor \oc C) \arrow[r, "\eta_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id"']
+        & ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \arrow[d, "(\id\sequoid(\int\tensor\id))\times (\id\sequoid(\int\tensor\id))"] \\
+      \oc (A \times B) \tensor \oc C \arrow[r, "\kappa_{A\times B,C}"]
+        & ((A \times B) \sequoid (\oc (A \times B))) \times (C \sequoid (\oc (A \times B) \tensor \oc C))
+    \end{tikzcd}
+    \]
+
+\begin{lemma}\label{assocCoherenceBigCommutes}
+  The diagrams in Figure \ref{assocCoherenceBig} commute.
+\end{lemma}
+\begin{proof}
+  First, observe the diagram in Figure \ref{ThisWorksForA}.  Setting, $X=A$, $Y=B$ and $Z=C$, this gives us diagram \eqref{Aexpansion} immediately.
+\end{proof}
+
+\begin{SidewaysFigure}
+  \begin{equation}\label{Aexpansion}
+    \begin{tikzcd}[ampersand replacement=\&]
+      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "(\alpha_A\tensor\id)\tensor\id" yshift=0.4em] \arrow[d, "\assoc"']
+        \& ((A \sequoid \oc A) \tensor \oc B) \tensor \oc C \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift=0.4em]
+          \& (A \sequoid (\oc A \tensor \oc B)) \tensor \oc C \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
+            \& A \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
+      \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\alpha_A\tensor\id"]
+        \& (A \sequoid \oc A) \tensor (\oc B \tensor \oc C) \arrow[r, "\wk"]
+            \& (A \sequoid \oc A) \sequoid (\oc B \tensor \oc C) \arrow[r, "\passoc\inv"]
+                \& A \sequoid (\oc A \tensor (\oc B \tensor \oc C))
+    \end{tikzcd}\tag{\textbf{A}}
+  \end{equation}\vspace{24pt}
+  \begin{equation}\label{Bexpansion}
+    \begin{tikzcd}[row sep=36pt, column sep=12pt, cramped, ampersand replacement=\&]
+      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\sym" yshift=0.4em] \arrow[d, "\assoc"']
+        \& (\oc B \tensor \oc A) \tensor \oc C \arrow[r, "(\alpha_B\tensor\id)\tensor\id" yshift=0.4em]
+          \& ((B \sequoid \oc B) \tensor \oc A) \tensor \oc C \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift = 0.4em]
+            \& (B \sequoid (\oc B \tensor \oc A)) \tensor \oc C \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
+              \& B \sequoid ((\oc B \tensor \oc A) \tensor \oc C) \arrow[r, "\id\sequoid(\sym\tensor\id)" yshift=0.4em]
+                \& B \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
+      \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\sym" yshift=0.4em]
+        \& (\oc B \tensor \oc C) \tensor \oc A \arrow[r, "(\alpha_B\tensor\id)\tensor\id" yshift=0.4em]
+          \& ((B \sequoid \oc B) \tensor \oc C) \tensor \oc A \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift=0.4em]
+            \& (B \sequoid (\oc B \tensor \oc C)) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
+              \& B \sequoid ((\oc B \tensor \oc C) \tensor \oc A) \arrow[r, "\id\sequoid\sym" yshift=0.4em]
+                \& B \sequoid (\oc A \tensor (\oc B \tensor \oc C))
+    \end{tikzcd}\tag{\textbf{B}}
+  \end{equation}\vspace{36pt}
+  \begin{equation}\label{Cexpansion}
+    \begin{tikzcd}[row sep=36pt, column sep=12pt, cramped, ampersand replacement=\&]
+      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\sym" yshift=0.4em] \arrow[d, "\assoc"']
+        \& \oc C \tensor (\oc A \tensor \oc B) \arrow[r, "\alpha_C\tensor\id" yshift=0.4em]
+          \& (C \sequoid \oc C) \tensor (\oc A \tensor \oc B) \arrow[r, "\wk" yshift=0.4em]
+            \& (C \sequoid \oc C) \sequoid (\oc A \tensor \oc B) \arrow[r, "\passoc\inv" yshift=0.4em]
+              \& C \sequoid (\oc C \tensor (\oc A \tensor \oc B)) \arrow[r, "\id\sequoid\sym" yshift=0.4em]
+                \& C \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
+      \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\comp{(\sym\tensor\id)}{\sym}" yshift=0.4em]
+        \& (\oc C \tensor \oc B) \tensor \oc A \arrow[r, "(\alpha_C\tensor\id)\tensor\id" yshift=0.4em]
+          \& ((C \sequoid \oc C) \tensor \oc B) \tensor \oc A \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift=0.4em]
+            \& (C \sequoid (\oc C \tensor \oc B)) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
+              \& C \sequoid ((\oc C \tensor \oc B) \tensor \oc A) \arrow[r, "\id\sequoid(\comp{(\sym\tensor\id)}{\sym})" yshift=0.4em]
+                \& C \sequoid (\oc A \tensor (\oc B \tensor \oc C))
+    \end{tikzcd}\tag{\textbf{C}}
+  \end{equation}\vspace{24pt}
+  \caption{Lemma \ref{assocCoherenceBigCommutes} asserts that these diagrams commute.}\label{assocCoherenceBig}
+\end{SidewaysFigure}
+
+\begin{SidewaysFigure}
+  \[
+    \begin{tikzcd}[row sep=36pt, cramped, ampersand replacement=\&]
+      (\oc X \tensor \oc Y) \tensor \oc Z \arrow[r, "(\alpha\tensor\id)\tensor\id" yshift=0.4em] \arrow[dd, "\assoc"']
+      \arrow[phantom, ddr, "\textbf{a}"]
+        \& ((X \sequoid \oc X) \tensor \oc Y) \tensor \oc Z \arrow[r, "\wk\tensor\id" yshift=0.4em] \arrow[dd, "\assoc"']
+      \arrow[phantom, ddr, "\textbf{c}"]
+          \& ((X \sequoid \oc X) \sequoid \oc Y) \tensor \oc Z \arrow[r, "\passoc\inv\tensor\id" yshift=0.4em] \arrow[d, "\wk"']
+      \arrow[phantom, dr, "\textbf{b}"]
+            \& (X \sequoid (\oc X \tensor \oc Y)) \tensor \oc Z \arrow[d, "\wk"]
+              \& \\
+      %
+        \&
+          \& ((X \sequoid \oc X) \sequoid \oc Y) \sequoid \oc Z \arrow[r, "\passoc\inv\sequoid\id" yshift=0.4em] \arrow[d, "\passoc\inv"]
+      \arrow[phantom, drr, "\textbf{d}"]
+            \& (X \sequoid (\oc X \tensor \oc Y)) \sequoid \oc Z \arrow[r, "\passoc\inv" yshift=0.4em]
+              \& X \sequoid ((\oc X \tensor \oc Y) \tensor \oc Z) \arrow[d, "\id\sequoid\assoc"] \\
+      \oc X \tensor (\oc Y \tensor \oc Z) \arrow[r, "\alpha_X\tensor\id"]
+        \& (X \sequoid \oc X) \tensor (\oc Y \tensor \oc Z) \arrow[r, "\wk"]
+          \& (X \sequoid \oc X) \sequoid (\oc Y \tensor \oc Z) \arrow[rr, "\passoc\inv"]
+            \& 
+              \& X \sequoid (\oc X \tensor (\oc Y \tensor \oc Z)
+    \end{tikzcd}
+    \]
+  \caption{
+    \textbf{a} commutes because $\assoc$ is a natural transformation.  \textbf{b} commutes because $\wk$ is a natural transformation. \\[\baselineskip]
+    \textbf{c} commutes by the coherence condition for $\wk$.  \textbf{d} commutes by the coherence condition for $\passoc$.
+  }\label{ThisWorksForA}
+\end{SidewaysFigure}
 

### 2017-04-05 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Added material on stateful objects as anamorphisms.

@@
 \newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{exercise}[theorem]{Exercise}
 \theoremstyle{definition}
@@
 \newcommand{\dec}{{\mathtt{dec}}}
-\renewcommand{\int}{{\mathtt{int}}}
+\renewcommand{\int}{{\mathtt{coh}}}
+\renewcommand{\coh}{\int}
 \DeclareMathOperator{\CCom}{CCom}
@@
 \newcommand\oppcat[1]{#1^{\mathrm{op}}}
+\newcommand{\bN}{{\mathbb{N}}}
+\newcommand{\OK}{{\mathtt{OK}}}
+\newcommand{\zero}{{\mathtt{zero}}}
+\renewcommand{\succ}{{\mathtt{succ}}}
+
+%%OUR
 
@@
 
-We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.  A game will be given by a tuple
+To get around the problems caused by the non-commutativity of the comonoid in the sets-and-relations model, we shall consider a game semantics model, in which we will be able to construct cofree commutative comonoids.
+We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.
+A game will be given by a tuple
 \[
@@
     \]
+  We call $\fcoal{\sigma}$ the \emph{anamorphism} of $\sigma$.
 \end{proposition}
@@
 
-\subsection{Constructing cofree commutative comonoids in sequoidal categories}
+\subsection{Imperative programs as anamorphisms}
+
+Let $\Sigma$ be the game
+\[
+  (\{q,a\},\{q\mapsto O,a\mapsto P\},O,\{\emptyplay,q,qa\})
+  \]
+and let $\bN$ be the game
+\[
+  \{q\}\cup\bN,\{q\mapsto O,\;n\mapsto P\},O,\{\emptyplay,q\}\cup\{qn\suchthat n\in\bN\})
+  \]
+That is, $\Sigma$ is the game where player $O$ makes the move $q$ and player $P$ must then reply with the move $a$, while $\bN$ is the game where player $O$ plays the move $q$ and then player $P$ must choose a natural number $n$ to play.
+We model a simple stateful program as a history sensitive strategy on $\oc(\Sigma\times\bN)$: the program interface will consist of a button that can be pressed, and a display that can be activated to display the number of times that the button has been pressed.
+As a strategy on $\oc(\Sigma\times\bN)$, whenever player $O$ plays $q$ in $\Sigma$, player $P$ responds with the move $a$.
+Whenever he plays $q$ in $\bN$, she responds with the number of times we have played in $\Sigma$ so far.
+
+We can construct this strategy using nothing more than the sequoidal structure on $\G$ that we have described and some very basic strategies on the games $\bN$ and $\Sigma$; namely:
+\begin{gather*}
+  \OK \from I \to \Sigma \\
+  \succ \from \bN \to \bN \\
+  \zero \from I \to \bN
+\end{gather*}
+Here, $\OK$ is the strategy that replies $a$ to player $O$'s initial move $q$, $\zero$ is the strategy that replies $0$ to player $O$'s initial move $q$ and $\succ$ is the strategy that queries its argument and then returns the number one greater (so maximal plays in $\succ$ are of the form $qqn(n+1)$ for $n\in\bN$).
+
+We first define a morphism $\mathtt{press}$ from $\oc \bN$ to $\Sigma\sequoid\oc \bN$ as the composite:
+\[
+  \begin{tikzcd}
+    \oc\bN \arrow[r, "\lunit"]
+      & I \tensor \oc \bN \arrow[r, "\OK\tensor\oc\succ"]
+        &[24pt] \Sigma\tensor\oc\bN \arrow[r, "\wk"]
+          & \Sigma \sequoid \oc \bN
+  \end{tikzcd}
+  \]
+In this strategy, the player responds to the initial move $q$ in $\Sigma$ with $a$; from then on, she copies from the $\oc\bN$ to $\oc\bN$, increasing each argument by $1$ before playing it on the right.
+This strategy models the effect of a single button press.
+
+We now define a morphism from $\oc\bN$ to $(\bN\times\Sigma)\sequoid\oc \bN$ by the composite:
+\[
+  \begin{tikzcd}
+    \oc \bN \arrow[r, "\Delta"]
+      & \oc \bN \times \oc \bN \arrow[r, "\alpha\times\mathtt{press}"]
+        &[20pt] \bN \sequoid \oc \bN \;\times\; \Sigma \sequoid \oc \bN \arrow[r, "\dist\inv"]
+          &[12pt] (\bN \times \Sigma) \sequoid \oc \bN
+  \end{tikzcd}
+  \]
+In this strategy, if player $O$ starts with a move in $\bN$, then player $P$ copies plays in $\oc \bN$ on the left and copies over the response.
+From then on, she continues to copy numbers from the left over to the right.
+If player $O$ starts by playing in $\Sigma$, then player $P$ responds with the move $a$.
+From then on, she copies numbers from the left over to the right, but now she increases the numbers by $1$ each time.
+
+This strategy represents a single user interaction (either pressing the button or checking how many times it has been pressed), together with the change of state (represented by the game $\oc \bN$) that takes place after that interaction has taken place.
+We now take the anamorphism of this strategy, giving us a unique morphism $\mathtt{count}$ from $\oc \bN$ to $\oc (\bN\times\Sigma)$ making the following diagram commute:
+\[
+  \begin{tikzcd}
+    \oc \bN \arrow[r, "\Delta"] \arrow[d, "\mathtt{count}"']
+      & \oc \bN \times \oc \bN \arrow[r, "\alpha\times\mathtt{press}"]
+        &[20pt] \bN \sequoid \oc \bN \;\times\; \Sigma \sequoid \oc \bN \arrow[r, "\dist\inv"]
+          &[12pt] (\bN \times \Sigma) \sequoid \oc \bN \arrow[d, "\id\sequoid\mathtt{count}"] \\
+    \oc (\bN\times\Sigma) \arrow[rrr, "\alpha"]
+      &
+        &
+          & (\bN \times \Sigma) \sequoid \oc (\bN \times \Sigma)
+  \end{tikzcd}
+  \]
+In the strategy $\mathtt{count}$, if player $O$ plays $q$ in a copy of $\Sigma$, then player $P$ responds with $a$ and adds $1$ to an (invisible) counter variable.
+If player $O$ plays $q$ in a copy of $\bN$, then player $P$ queries the argument on the left and returns that value, plus her count, on the right.
+If we now substitute in the initial value of the state by forming the composite $\comp{\mathtt{count}}{\oc\zero}$, then we end up with the desired behaviour.
+
+Note that the strategies we started with -- $\OK$, $\succ$ and $\zero$ -- are all history free strategies.  The history-sensitive, stateful behaviour only arose when we passed to the anamorphism.
+
+\begin{exercise}
+  Let $X$ be a set, let $X$ be the game with maximal plays $qx$ for $x\in X$ and let $X_\bot$ be the game with maximal plays $qx$ for $x\in X$ and $q*$, where $*$ is a special error symbol not contained in $X$.
+Consider a history-sensitive strategy on $\oc((X\implies\Sigma)\times X)$ representing a simple stack with $\mathtt{push(x)}$ and $\mathtt{pop()}$ methods.
+The $\mathtt{push(x)}$ method should add the argument of a function $X\implies\Sigma$ on to the stack, while the $\mathtt{pop()}$ method should return the top element of the stack, removing it from the stack in the process, or return $*$ if the stack is empty.
+Show that this strategy may be constructed from the strategy $\OK$ on $\Sigma$, using only the sequoidal structure of $\G$.
+
+  Consider how we might add a $\mathtt{size()}$ method, of type $\bN$, to this stack, returning the number of elements currently on the stack.
+\end{exercise}
+
+\section{Constructing cofree commutative comonoids in Cartesian sequoidal categories}
 

### 2017-04-06 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Added discussion of cell strategy.

@@
 \newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{exercise}[theorem]{Exercise}
+\newtheorem{exercise}{Exercise}
 \theoremstyle{definition}
@@
 \renewcommand{\succ}{{\mathtt{succ}}}
+\newcommand{\cell}{{\mathtt{cell}}}
+\newcommand{\Var}{{\mathtt{Var}}}
+\renewcommand{\read}{{\mathtt{read}}}
+\newcommand{\wwrite}{{\mathtt{write}}}
 
@@
 \begin{description}
-  \item[Product] If $A$ and $B$ are negative games then the \emph{product} $A\times B$ is the game given by placing the game trees for $A$ and $B$ side by side: that is, player $O$ may play his first move either in $A$ or in $B$.
-Thereafter, play continues in the game that player $O$ has chosen.
-  \item[Tensor Product] The tensor product $A\tensor B$ is also played by playing the games $A$ and $B$ in parallel, but this time player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
+  \item[Product] If $(A_i\suchthat i\in I$ is a collection of negative games, then we write $\prod_{i\in I}A_i$ for the game in which player $O$, on his first move, may play in any of the games $A_i$.
+From then on, play continues in $A_i$.
+When we have defined the category of games, $\prod_{i\in I}A_i$ will be the category-theoretic product of the $A_i$.
+If $A_1,A_2$ are games, we write $A_1\times A_2$ for $\prod_{i=1}^2 A_i$.
+  \item[Tensor Product] If $A,B$ are negative games,the tensor product $A\tensor B$ is played by playing the games $A$ and $B$ in parallel, where player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
   \item[Linear implication] The implication $A\implies B$ is played by playing the game $B$ in parallel with the \emph{negation} of $A$ - that is, the game formed by switching the roles of players $P$ and $O$ in $A$.
@@
     \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
+    \dist_{(A_i\colon i\in I),C} = \langle (\pr_i\sequoid\id_C\suchthat i\in I)\rangle \from \left(\prod_{i\in I} A_i\right) \sequoid C \to \prod_{i\in I}(A_i\sequoid C) \\
     \dist_{A,0}\from 1\sequoid A\to 1
@@
 
-Note that the strategies we started with -- $\OK$, $\succ$ and $\zero$ -- are all history free strategies.  The history-sensitive, stateful behaviour only arose when we passed to the anamorphism.
+A more consequential example is the construction of a strategy representing a storage cell.
+This is the strategy $\cell$ for $\oc(\Var[X])$ that is used in \cite{SamsonGuyIAPassive} to construct the denotation of the $\mathtt{new}$ term from Idealized Algol.
+Using this strategy, it is possible to build the model of Idealized Algol from \cite{SamsonGuyIAPassive} and hence construct a wealth of other stateful objects.
+The benefit of constructing $\cell$ in this way, rather than directly, is that we can now reason about it coalgebraically, rather than by direct combinatorial arguments on the strategy.
+
+Let $(X,*)$ be a pointed set and write $X$ for the game with maximal plays $qx$ for $x\in X$.
+Recall that in Idealized Algol we represent $\Var[X]$, the type of variables taking values in $X$, by the game $\Sigma^X\times X$, where $\Sigma$ denotes the command type $\mathtt{com}$ and $\Sigma^X$ is the $X$-fold product of $\Sigma$ with itself.
+Here, $\Sigma^X$ represents the act of writing a value into the storage cell (so playing in $\Sigma_x$ means writing the value $x$), while the copy of $X$ represents reading a value from the storage cell.
+
+We want to construct the strategy $\cell$ for $\oc(\Sigma^X\times X)$ that will remember what value we have written into the cell and will return the value when we request it.
+In the case that we request the value in the cell when nothing has been written to it, we return the default value $*$.
+
+We shall represent the state of the storage cell by the game $X$, and we shall construct a state transformer on $X \implies (\Sigma^X\times X)\sequoid X$ that will allow us to recover the $\cell$ strategy as an anamorphism.
+
+For each $x\in X$, we have a strategy $c_x$ for $I\implies X$ with maximal play $qx$.  Now we construct a morphism $\wwrite(x)$ from $\oc X$ to $\Sigma\sequoid\oc X$ as the composite:
+\[
+  X \xrightarrow{*} 1 \xrightarrow{{(\dec^0)}\inv} I \xrightarrow{\runit_I} I \tensor I \xrightarrow{\OK\tensor c_x} \Sigma \tensor X \xrightarrow{\wk_{\Sigma,X}} \Sigma \sequoid X
+  \]
+This strategy corresponds to filling the cell with the value $x$.
+Consequently, we ignore the previous value from the cell (the copy of $X$ on the left) and we respond in the copy of $X$ on the right with $x$.
+
+We get a strategy:
+\[
+  \wwrite \from \oc X \xrightarrow{\langle \wwrite(x)\suchthat x\in X\rangle} (\Sigma \sequoid \oc X)^X \xrightarrow{\dist_{(\Sigma\colon x\in X),\oc X}\inv} \Sigma^X\sequoid\oc X
+  \]
+
+We also want a strategy $\read$ for $X \implies X \sequoid X$.
+It doesn't appear to be possible to construct this strategy from the sequoidal axioms, but it is easy enough to say what it is: it is the strategy that returns the value of the state while leaving the state unchanged.
+A typical play in $\read$, therefore, might have the following form:
+\[
+  \begin{array}{ccccc}
+    X & \implies & X & \sequoid & X \\
+    && q && \\
+    q &&&& \\
+    x &&&& \\
+    && x && \\
+    &&&& q \\
+    &&&& x
+  \end{array}
+  \]
+Note that the content of the state (the copy of $X$ on the left) is copied into both the output (the first copy of $X$ on the right) and into the new state (the second copy of $X$ on the right).
+
+We put these strategies together to form our state transformer:
+\[
+  \cell'\from \oc X \xrightarrow{\langle\wwrite,\read\rangle} \Sigma^X\sequoid\oc X \;\times\;X\sequoid\oc X \xrightarrow{\dist_{\Sigma^X,X,\oc X}} (\Sigma^X\times X)\sequoid \oc X
+  \]
+When we take the anamorphism $\fcoal{\cell'}$ of this strategy, we get the strategy $\oc X \to \oc (\Sigma^X\times X)$ that, when player $O$ plays in $\Sigma^X$, stores the appropriate element of $X$ into the (invisible) state.
+When player $O$ plays in $X$ on the right, player $P$ responds with the current value held in the state.
+In the case that player $O$ plays in $X$ without having first played in $\Sigma^X$, we return the value of $X$ from the left.
+Therefore, our desired strategy $\cell$ is given by:
+\[
+  \cell = \comp{\fcoal{\cell'}}{c_*}
+  \]
 
 \begin{exercise}
-  Let $X$ be a set, let $X$ be the game with maximal plays $qx$ for $x\in X$ and let $X_\bot$ be the game with maximal plays $qx$ for $x\in X$ and $q*$, where $*$ is a special error symbol not contained in $X$.
-Consider a history-sensitive strategy on $\oc((X\implies\Sigma)\times X)$ representing a simple stack with $\mathtt{push(x)}$ and $\mathtt{pop()}$ methods.
-The $\mathtt{push(x)}$ method should add the argument of a function $X\implies\Sigma$ on to the stack, while the $\mathtt{pop()}$ method should return the top element of the stack, removing it from the stack in the process, or return $*$ if the stack is empty.
-Show that this strategy may be constructed from the strategy $\OK$ on $\Sigma$, using only the sequoidal structure of $\G$.
+  Let $(X,*)$ be a pointed set, where $*$ is a designated error element, and write $X$ for the game with maximal plays $qx$ for $x\in X$.
+Consider a history-sensitive strategy on $\oc(\Sigma^X\times X)$ representing a simple stack with $\mathtt{push(x)}$ and $\mathtt{pop()}$ methods.
+The $\mathtt{push(x)}$ method should add an element $x\in X$ on to the stack, while the $\mathtt{pop()}$ method should return the top element of the stack, removing it from the stack in the process, or return $*$ if the stack is empty.
+Show that this strategy may be constructed from the strategy $\OK$ on $\Sigma$ and the strategies $c_x$ on $X$, using only the sequoidal structure of $\G$.
 
@@
 \section{Constructing cofree commutative comonoids in Cartesian sequoidal categories}
+
+\subsection{The Mellies-Tabareau-Tasson construction}
+
+We observed that the exponential $\oc A$ of a game $A$ arises as the final coalgebra for the functor $A\sequoid\blank$.
+We also observed that $\oc A$ has the structure of a cofree commutative comonoid on $A$.
+In this section, we shall consider various generalizations of this result that hold in sequoidal categories.
+
+The first generalization we will consider is that given by Mellies, Tabareau and Tasson in \cite{MelliesCofCommCom}.
+Their construction is given in a general monoidal category, but we will show how to interpret it sequoidally.
+The first step in their construction is to pass from $A$ to the free pointed object $A_\bullet$ on $A$.
+In our setting, our category is \emph{affine} -- we have an isomorphism $\dec^0$ between the tensor unit $I$ and the terminal object $1$ -- and so there is no need to carry out this step.
+In fact, the affineness assumption is not really necessary to any of our results, though it does greatly simplify them: in the non-affine case, we would need to construct the exponential as the final coalgebra for the functor $(A\sequoid\blank)\times I$, and the construction would become rather more complicated.
+In this paper, we will always use the affineness assumption, so we will leave out the first step in the Mellies-Tabareau-Tasson construction.
+
+The second step in the construction, is to form, for each object $A$, the \emph{symmetrized tensor product} $A^{\le n}$, given as the following equalizer:
+\[
+  \begin{tikzcd}
+    A^{\le n} \arrow[r, dotted]
+      & A^{\tensor n} \arrow[r, yshift=0.3em, "\textrm{symmetry}"] \arrow[phantom, r, "\cdots"] \arrow[r, yshift=-0.3em, "\textrm{symmetry}"']
+        &[24pt] A^{\tensor n}
+  \end{tikzcd}
+  \]
+where $A^{\tensor n} = \underbrace{A\tensor\cdots\tensor A}_n$.  Here, the `$\le$' is because, thanks to our affine structure, we are free to ignore (weaken) any one of the copies of $A$.
+
+---
 
@@
   \label{StrongMonoidalFunctor}
-  Let $(\C,\C_s,J,\wk)$ be an inclusive, Cartesian, distributive and decomposable sequoidal category with a final coalgebra $\oc A\xrightarrow{\alpha_A}A\sequoid\oc A$ for each endofunctor of the form $A\sequoid\blank$.
+  Let $(\C,\C_s,J,\wk)$ be a distributive and decomposable sequoidal category with a final coalgebra $\oc A\xrightarrow{\alpha_A}A\sequoid\oc A$ for each endofunctor of the form $A\sequoid\blank$.
 Suppose further that the morphism $\int_{A,B}$ as defined above is an isomorphism for all objects $A,B$.
@@
 For this reason, we might wonder whether we can do without the condition that $\int_{A,B}$ be an isomorphism.
-In this section, we shall give a negative answer to that question: we shall construct an inclusive, distributive, decomposable sequoidal closed category with final coalgebras $\oc A$ for all functors of the form $A\sequoid\blank$, and shall show that $\oc A$ does not have a natural comonoid structure.
+In this section, we shall give a negative answer to that question: we shall construct a distributive and decomposable sequoidal closed category with final coalgebras $\oc A$ for all functors of the form $A\sequoid\blank$, and shall show that $\oc A$ does not have a natural comonoid structure.
 In doing this, we hope to shed some light upon alternative algebraic or coalgebraic constructions for the cofree commutative comonoid that work in a purely `finitary' manner.
@@
 
-We can show that this composition is associative and moreover that we obtain an inclusive, distributive, decomposable sequoidal category.
+We can show that this composition is associative and moreover that we obtain a distributive and decomposable sequoidal category.
 We call this category $\G(\alpha)$ and call the corresponding strict subcategory $\G_s(\alpha)$.

### 2017-04-06 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Mellies-Tabareau-Tasson things.

@@
 
+We claim that, in a decomposable sequoidal category, the object $A^{\le n}$ always exists and is isomorphic to the game $A^{\sequoid n}$, defined inductively by:
+\begin{gather*}
+  A^{\sequoid 0} = I \\
+  A^{\sequoid (n+1)} = A \sequoid A^{\sequoid n}
+\end{gather*}
+Indeed, by decomposability, the morphisms $\wk,\comp{\wk}{\sym}\from A\tensor A\to A\sequoid A$ exhibit $A\tensor A$ as a product of $A\sequoid A$ with $A\sequoid A$.
+Using the coherence conditions, we may generalize this to higher products: write $\wk^n\from A^{\tensor n}\to A^{\sequoid n}$ for the natural morphism
+\[
+  \wk^n = \comp{\id\sequoid(\cdots\sequoid(\id\sequoid\wk)\cdots)}{\comp{\cdots}{\wk}}
+  \]
+and for $\pi\in S_n$, write $\sym^\pi$ for the corresponding symmetry $A^{\tensor n}\to A^{\tensor n}$.
+We can show that the morphisms $\comp{\wk^n}{\sym^\pi}$ for $\pi\in S_n$ exhibit $A^{\tensor n}$ as the product of $n!$ copies of $A^{\sequoid n}$.
+
+Now the morphism $\langle\id,\dots,\id\rangle\from A^{\sequoid n}\to (A^{\sequoid n})^{n!}$ induces a morphism $e$ from $A^{\sequoid n}$ to $A^{\tensor n}$ that equalizes the morphisms $\comp{\wk^n}{\sym^pi}$ and therefore equalizes the morhpisms $\sym^\pi$ (since $\wk^n$ is an epimorphism).
+We claim that $e$ is the equalizer of the $\sym^\pi$.
+
+Suppose $B$ is an object of the category and that $f\from B\to A^{\tensor n}$ is a morphism equalizing the $\sym^\pi$.
+
 ---

### 2017-04-08 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Draft of paper.

--- 2017-04-06 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
 \newcommand{\G}{\mathcal G}
+\newcommand{\W}{\mathcal W}
 \newcommand{\suchthat}{\;\colon\;}
@@
 \DeclareMathOperator{\CCom}{CCom}
-\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
+\newcommand{\catname}[1]{{\mathsf{#1}}}
 \newcommand{\Set}{\catname{Set}}
@@
 \renewcommand{\succ}{{\mathtt{succ}}}
-\newcommand{\cell}{{\mathtt{cell}}}
 \newcommand{\Var}{{\mathtt{Var}}}
@@
 \newcommand{\wwrite}{{\mathtt{write}}}
+\newcommand{\Rel}{\catname{Rel}}
+\newcommand{\inr}{{\mathsf{inr}}}
+\newcommand{\inl}{{\mathsf{inl}}}
+\newcommand{{\Na}}{\bN}
+\newcommand{{\cell}}{{\mathsf{cell}}}
+\newcommand{\fix}{{\mathsf{fix}}}
+\newcommand{\eq}{{\mathsf{eq}}}
+\newcommand{\co}{{\textrm{\textexclamdown}}}
 
@@
 \begin{abstract}
-  In \cite{laird02}, Laird introduces the concept of a \emph{sequoidal category} as a formalization of causality in game semantics.
-A sequoidal category is like a monoidal category with an extra connective, $\sequoid$, that allows one to construct an exponential object as a final coalgebra \cite{martinsthesis},  Under a further hypothesis, it is possible to show that this final coalgebra allows one to construct cofree commutative comonoids in the category, giving us a model of the exponential connective $\oc$ from linear logic.
-In the first part of this note, we review the coalgebraic arguments for constructing the cofree commutative comonoid, which are known but do not yet appear in print.
-In the second part, we show that the extra hypotheses are necessary by outlining a definition of \emph{transfinite game}, in which the carriers of the sequoidal coalgebra and the cofree commutative comonoid do not coincide.
+The non-commutative sequoid operator $\sequoid$ on games was introduced by one of the authors in order to capture algebraically the presence of state in history-sensitive strategies in game semantics.
+It imposes a causality relation on to the  tensor product of games, so that coalgebras for the  functor  $A\sequoid\blank$  - i.e.
+morphisms from $S$ to $A \sequoid S$ may be viewed as state transformers.
+If $A\sequoid\blank$ has a final coalgebra, $\oc A$, then the anamorphism of such a state transformer encapsulates its explicit state, so that it is shared only between successive invocations.
+
+We shall study  conditions under which such a final coalgebra $\oc A$ for the functor $A\sequoid\blank$ is the carrier of a cofree commutative comonoid on $A$.
+That is, it is a model of the exponential of linear logic, but one in which we can construct imperative objects such as reference cells and stacks coalgebraically, and reason about them coinductively, in a game semantics setting.
+
+We shall review the definition of a sequoidal category, a category-theoretic formalization of the sequoid operator, and the notion of sequoidal decomposition of a symmetric monoidal category.
+We show that given such a decomposition, the final coalgebra !A may be endowed with the structure of the cofree commutative comonoid if it is the bifree algebra for $A\sequoid\blank$, or if it is a limit of sequoidal powers (following the construction  of the cofree commutative comonoid by Melli\'es, Tabareau and Tasson), or if the functor $\oc$ is strong monoidal - for all  $A$ and $B$, the objects $\oc (A \times B)$ and $\oc A \tensor \oc B$ are naturally isomorphic.
+
+We establish necessity of this final condition  by giving an example of a sequoidally decomposable category of games in which plays will be allowed to have transfinite length.
+In this category, the final coalgebra for the functor $A\sequoid\blank$ is not the cofree commutative comonoid over $A$: we illustrate this by explicitly contrasting the final sequence for the functor $A\sequoid\blank$ with the chain of sequoidal powers used in the Melli\'es-Tabareau-Tasson construction.
 \end{abstract}
+
+\section{Introduction}
+
+Games models of pure functional programming languages such as PCF (\cite{ajmPcf} and \cite{hoPcf}, for example) tend to include the requirement that strategies be \emph{history-free}: that is, the response to a particular position may depend only upon the last move played, and not upon what has gone before.
+This makes sense for stateless languages, where the program should have no `memory' to recall what has gone before.
+
+If we include history-sensitive strategies in our models, then we can start to recover some stateful behaviour (see \cite{SamsonGuyIAPassive}, for example), since history-sensitive strategies have a built in state.
+This concept of state is often hard to work with: since the representation as a strategy is so intensional, there is no object representing the state, and the state of the program must be inferred from the behaviour of the strategy.
+
+At the other extreme, we have traditional, domain-theoretic semantics, in which stateful programs are represented as \emph{state transformers} -- that is, functions $W\times X \to W\times Y$, where $W$ is an object representing the state.
+
+State transformers are typically fairly straightforward to reason about, and we would like to have a similar technique available in our games models.
+This gap was bridged by one of the authors in \cite{laird02} with the introduction of the new \emph{sequoid} operator $\blank\sequoid\blank$ on games, which the same as the tensor product $\blank\tensor\blank$, except that play is required to start in the left hand game.
+We interpret a state transformer as a coalgebra for the functor $A\sequoid\blank$ -- that is, a morphism from $S$ to $A\sequoid S$, so that the state $S$ is only modified after the program $A$ has been consulted.
+The benefit of this explicit ordering is that we may model multiple iterations of the state transformer as coalgebras:
+\[
+  S \to A \sequoid (A \sequoid \cdots \sequoid (A \sequoid S)\cdots)
+  \]
+where the copies of $A$ are started in order from left to right.  The state from a previous invocation of $A$ is passed on to the next, until the final modified state finally appears at the right.
+
+Now we introduce the key part of the construction: suppose that the functor $A\sequoid\blank$ has a final coalgebra $\oc A\to A\sequoid \oc A$.
+Then a coalgebra $S\to A\sequoid S$ (i.e., a state transformer) naturally gives rise to a morphism $S \to \oc A$ in which the state is completely encapsulated and we are allowed to invoke the program $A$ as many times as we like.
+We will show that we can construct various history-sensitive strategies denoting stateful programs using precisely this strategy; in particular, we will give a coalgebraic construction of the $\cell$ strategy from \cite{SamsonGuyIAPassive}, which is the key to their model for Idealized Algol.
+
+Even more intriguingly, the game $\oc A$ that arises as the final coalgebra for the functor $A\sequoid\blank$ has the structure of an exponential object in the category of games: it is the cofree commutative comonoid over $A$.
+We will spend the rest of the paper examining why this is, and what general conditions we need in order to show that the final coalgebra for $\oc A$ and the cofree commutative comonoid over $A$ coincide.
+For this, we will need the abstract definition of a \emph{sequoidal category}, which is an extension of a monoidal category in order to accommodate the sequoid operator.
+We will first consider the explicit formula for the cofree commutative comonoid given by Melli\'es, Tabareau and Tasson in \cite{MelliesCofCommCom} and show that it can be given a sequoidal interpretation.
+The Melli\'es-Tabareau-Tasson construction works for finite games, but its hypotheses do not hold in the case of the category of games with infinitary winning conditions and winning strategies, even though the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ still coincide in these categories.
+
+Instead, we will show that if our sequoidal category has all products then the cofree commutative comonoid structure on $\oc A$ may be constructed directly from the sequoidal structure and the definition of $A\sequoid\blank$ as a final coalgebra for $A\sequoid\blank$, provided that we insist on a further hypothesis: that the functor $\oc$ is monoidal from the Cartesian category to the monoidal category: i.e., if we have an isomorphism between $\oc A \tensor \oc B$ and $\oc(A\times B)$ for all $A,B$.
+We show that this hypothesis is automatically satisfied whenever $\oc A$ has the structure of a \emph{bifree algebra} for $A\sequoid\blank$; i.e., when it simultaneously has the structure of final coalgebra and initial algebra.
+However, the exponential in the category of win-games is not an initial algebra for $A\sequoid\blank$ \cite{martinsthesis}.
+
+Lastly, we will provide an illuminating counterexample: a category of games in which the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ do not coincide.
+This is the category of games where plays are allowed to have transfinite length.
+We will show that the Melli\'es-Tabareau-Tasson construction fails badly in this setting, but that we may still construct the final coalgebra for $A\sequoid\blank$ as the limit of its final sequence.
+In this setting, the final coalgebra is the game where we have `only' $\omega$-many copies of the sub-game to play in, whereas in the cofree commutative comonoid we may open transfinite sequences of the subgame.
+
+\section{Defining Higher-order Stateful Objects, Coalgebraically}
+In this section we motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon.
+A \emph{state-transformer} in a symmetric monoidal category is a morphism $f:A \otimes S \rightarrow B \otimes S$ taking an argument together with an input state to a result together with a input state.
+A well-studied \cite{jacobs} technique in semantics is to  use an appropriate final coalgebra to \emph{encapsulate} the state in such a transformer, allowing multiple  successive invocations, each of which passes its output state as an input state to the next invocation.
+
+For example, consider the category $\Rel$ of sets and relations, with symmetric monoidal structure given by the cartesian product (with unit $I$, the singleton set $\{*\}$).
+This has finite (bi)products given by the disjoint union of sets: define the functor $F(A,S) = (A \otimes S) \oplus I$
+
+For any object (set) $A$, let $A^*$ be the set $A^*$ of finite sequences of elements of $A$ (i.e.
+the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$
+\begin{lemma}$(A^*,\alpha_A)$ is a final coalgebra  for $F(A,\_)$.
+\end{lemma}
+\begin{proof}$\Rel$ may be cpo-enriched with the inclusion order: $A^*$ is a \emph{minimal invariant} for $F(A,\_)$ with respect to this order.
+\end{proof}
+Since we have a natural transformation (left injection) $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $f;\inl_{A,B}:S \rightarrow F(A,S)$, --- i.e.
+the unique $F(A,\_)$-coalgebra morphism from $(S,f;\inl)$ into $(A^*,\alpha_{A})$.
+This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ and uses it to update the internal state.
+
+By distributivity of $\oplus$ over  $\otimes$ we have a natural transformation $t: F(A,S) \otimes S' \rightarrow F(A,S \otimes S')$.
+We may use this to encapsulate  state transformers of general form: given $f:A \otimes S \rightarrow B \otimes S$, taking the anamorphism of the $F(B,\_)$-colagebra:
+$$A^* \otimes S  \stackrel{\alpha_A \otimes S}{\longrightarrow} F(A,A^*) \otimes S \stackrel{t}{\longrightarrow} F(A,A^* \otimes S)$$
+
+ Distributivity of $\oplus$ over $\otimes$ also implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
+This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
+i.e.
+given morphisms $f_1:A_1 \otimes S \rightarrow B_1 \otimes S, \ldots , f_n:A_n \otimes S \rightarrow B_n \otimes S$, encapsulating  $\dist;(f_1 \oplus \ldots \oplus f_n);\dist^{-1}$, gives a morphism from $(A_1 \oplus \ldots \oplus A_n)^* \otimes S$ into $(B_1 \oplus \ldots \oplus B_n)^*$.
+
+For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a state consisting of a single integer, representing the contents of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
+Thus (with appropriate tagging) it is the relation $\{(i, (\read(i),i))\ |\ i \in \Na\} \cup \{(i,{\mathtt{write}}(j),j)\}$.
+The anamorphism of the coalgebra $\cell;\inl:\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$ Composition with this morphism is precisely the denotation of new variable declaration in the semantics of  Reynolds \emph{Syntactic Control of Interference} (SCI) in $\Rel$ given in \cite{Mcsci}.
+
+Coalgebraic methods thus give us a recipe for constructing and using categorical definitions of stateful semantic objects, avoiding direct definitions which are rather combinatorial to work with.
+In order to fully exploit these, however, we may endow $A^*$ with the structure of a \emph{comonoid} by defining morphisms $\delta_A:A^* \rightarrow A^* \otimes A^* = \{(u\cdot v,(u,v))\ |\ u,v \in A^*\}$ and $\epsilon:A \rightarrow I = \{(\varepsilon,*)\}$
+
+ In fact, this is the \emph{cofree comonoid} on $A$ --- there is a morphism $\eta_A:A^* \rightarrow A = \{(a,a)\ | \ a \in A\}$ such that for any comonoid $(B,\delta_B,\epsilon_B)$, composition with $\eta_A$ defines an equivalence (natural in $B$)  between the morphisms from $B$ into $A$, and the comonoid morphisms from $(B,\delta_B,\epsilon_B)$ into  $(A^*,\delta_A,\epsilon_A)$.
+\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.
+\end{proposition}
+The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
+$(A^*,\alpha^{-1})$ is an initial algebra for $F(A,\_)$ ($\alpha$ must be an isomorphism by Lambek's lemma).
+We leave this as an exercise.
+
+This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell, the creation of multiple copies of such procedures ($(\_)^*$ is a monoidal comonad)  etc.
+Its main limitation is that we have not defined a \emph{commutative} monoid --- evidently it is not the case that $\delta_A;\sym_{A,A} = \delta_A$ (where $\sym_{A,B}:A \otimes B \rightarrow B \otimes A$ is the symmetry isomorphism for the tensor) for any non-empty set $A$.
+Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is predetermined.
+This is precisely the situation in SCI, where the typing system allows sharing between across sequential composition, but not between functions and their arguments.
+In order to model sharing of state between functions without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a cofree \emph{commutative} comonoid.
+The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra).
+By properly reflecting the interleaving between function calls, game semantics does support a coalgebraic cofree commutative comonoid, leading to models of stateful higher-order languages such as Idealized Algol and core ML.
+As we shall show by example and counterexample, the richer structure of games also means that the relationship between initial and final coalgebras, and cofree objects is more subtle  (note, for example, that any final coalgebra in $\Rel$ must be bifree, by its self-duality).
 
@@
         \]
-      together natural isomorphisms
+      together with natural isomorphisms
       \[
@@
   Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing the monoidal isomorphisms and the morphisms $\wk_{A,B}$, $J$ is the inclusion functor and $J$ reflects isomorphisms.
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing all isomorphisms in $\C$ and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
 
@@
 \end{definition}
-
-We have one further piece of structure available to us:
+\begin{definition}
+  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
+
+%  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
+ We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
+So if $\C$ has all finite products, 
+the natural transformations
+  \begin{gather*}
+    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
+   % \dec^0 \from I \to 1 \\
+    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
+    \dist_{A,0}\from 1\sequoid A\to 1
+  \end{gather*}
+  are isomorphisms.
+\end{definition}
+
+We shall also use the fact that our category of games is \emph{affine} - so the natural transformation $\dec^0\from I \to 1$ is an isomorphism.
+This is not strictly necessary, and techniques are available to obtain similar results in the non-affine case (see \cite{jimNonAffine}, for example), but it will greatly simplify our presentation.
+
+The games model satisfies an analog of monoidal closedness:
 
@@
 
-  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.
+  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha_A\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.
 In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
@@
 
+We shall use the following standard pieces of theory about final coalgebras.  
+\begin{description}
+  \item[Lambek's Lemma] $\alpha_A$ is an isomorphism, with inverse given by the anamorphism of the map $\id\sequoid\alpha_A\from A\sequoid\oc A\to A \sequoid (A \sequoid \oc A)$ \cite{Lambek}.
+In particular, $\alpha_A$ is a morphism in $\G_s$.
+In the general case, we deduce that $\alpha_A$ is a morphism in $\C_s$.
+  \item[Final Sequence] We may construct a transfinite sequence of objects and morphisms between them (in other words, a functor $\Ord\to\G$, where $\Ord$ is the category of ordinals and prefix inclusions:
+    \[
+      \begin{tikzcd}
+        1
+          & A \arrow[l, "*"']
+            & A \sequoid A \arrow[l, "\id\sequoid *"']
+              & A \sequoid (A \sequoid A) \arrow[l, "\id\sequoid(\id\sequoid*)"']
+                & \cdots \arrow[l] \\
+        A^{\sequoid\omega} \arrow[u] \arrow[ur] \arrow[urr] \arrow[urrr] \arrow[phantom, urrrr, "\cdots" xshift=0.6em]
+          & A \sequoid A^{\sequoid\omega} \arrow[l]
+            & A \sequoid (A \sequoid A^{\sequoid\omega}) \arrow[l]
+              & A \sequoid (A \sequoid (A \sequoid A^{\sequoid\omega})) \arrow[l]
+                & \cdots \arrow[l] \\[-24pt]
+        \vdots
+          & \vdots
+            & \vdots
+              & \vdots
+                &
+      \end{tikzcd}
+      \]
+    Here, $A^{\sequoid\omega}$ is the categorical limit of the top line and the morphisms into the top line are the morphisms in the limiting cone.
+The morphism from $A\sequoid A^{\sequoid\omega}$ to $A^{\sequoid\omega}$ is constructed as follows: apply the functor $A\sequoid\blank$ to the limiting cone from $A^{\sequoid\omega}$, giving us a cone from $A\sequoid A^{\sequoid\omega}$ over the top line.
+The desired morphism is now the unique morphism $A\sequoid A^{\sequoid\omega}\to A^{\sequoid\omega}$ that induces a morphism of cones.
+We may continue in this way to build up $A^{\sequoid\gamma}$ for all ordinals $\gamma$, where $A^{\sequoid(\gamma+1)}=A\sequoid A^{\sequoid\gamma}$ and $A^{\sequoid\mu}$ is the limit over the $A^{\sequoid\gamma}$ for $\gamma<\mu$ if $\mu$ is a limit ordinal.
+
+    If the morphism $j_{\gamma}^{\gamma+1}\from A\sequoid A^{\sequoid\gamma}\to A^{\sequoid\gamma}$ is an isomorphism for some $\gamma$, then we say that the final sequence \emph{stabilizes at $\gamma$}.
+In this case, ${j_{\gamma}^{\gamma+1}}\inv\from A^{\sequoid\gamma}\to A\sequoid A^{\sequoid\gamma}$ is the final coalgebra for the functor $A\sequoid\blank$ \cite{finalseq}.
+
+    The same is true for any endofunctor on any category with a terminal object and enough limits.
+\end{description}
+
 \subsection{Imperative programs as anamorphisms}
+
+We may use anamorphisms to construct (history-sensitive) strategies corresponding to stateful programs in an entirely coalgebraic way.
 
@@
 
-\subsection{The Mellies-Tabareau-Tasson construction}
+\subsection{A formula for the sequoidal exponential}
 
@@
 
-The first generalization we will consider is that given by Mellies, Tabareau and Tasson in \cite{MelliesCofCommCom}.
-Their construction is given in a general monoidal category, but we will show how to interpret it sequoidally.
-The first step in their construction is to pass from $A$ to the free pointed object $A_\bullet$ on $A$.
-In our setting, our category is \emph{affine} -- we have an isomorphism $\dec^0$ between the tensor unit $I$ and the terminal object $1$ -- and so there is no need to carry out this step.
-In fact, the affineness assumption is not really necessary to any of our results, though it does greatly simplify them: in the non-affine case, we would need to construct the exponential as the final coalgebra for the functor $(A\sequoid\blank)\times I$, and the construction would become rather more complicated.
-In this paper, we will always use the affineness assumption, so we will leave out the first step in the Mellies-Tabareau-Tasson construction.
-
-The second step in the construction, is to form, for each object $A$, the \emph{symmetrized tensor product} $A^{\le n}$, given as the following equalizer:
-\[
-  \begin{tikzcd}
-    A^{\le n} \arrow[r, dotted]
-      & A^{\tensor n} \arrow[r, yshift=0.3em, "\textrm{symmetry}"] \arrow[phantom, r, "\cdots"] \arrow[r, yshift=-0.3em, "\textrm{symmetry}"']
-        &[24pt] A^{\tensor n}
-  \end{tikzcd}
-  \]
-where $A^{\tensor n} = \underbrace{A\tensor\cdots\tensor A}_n$.  Here, the `$\le$' is because, thanks to our affine structure, we are free to ignore (weaken) any one of the copies of $A$.
-
----
-
-We want to deduce the fact that $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ is the cofree commutative comonoid on $A$ from the fact that $\oc A$ is the final coalgebra for $A\sequoid\blank$.
-It turns out that we shall need one more fact about the category of games to prove this.
+We shall first consider the formula  given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom}, which does not depend on the presence of cartesian products, but obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
+\begin{definition}If $A$ is an object in a symmetric monoidal category, a $n$-fold symmetric tensor power of $A$ is an  \emph{equalizer} $(A^n,\eq)$ for the group $G$ of symmetry automorphisms on $A^{\otimes n}$.
+A tensor power is preserved by the tensor product if $(B\otimes A^n,\eq \otimes B)$ is an equalizer for the automorphisms $\{B \otimes g\ |\ g \in G\}$.
+\end{definition}
+In any affine category\footnote{This is a special case of the situation considered in  \cite{MelliesCofCommCom}: that $A$ is a ``free pointed object''.} with tensor powers of $A$ we may define a diagram $\Delta(A) = $
+$$I \stackrel{p_0}{\leftarrow} A \stackrel{p_1}{\leftarrow} A^2 \ldots A^i \stackrel{p_i}{\leftarrow} A^{i+1} \ldots$$
+where   
+$p_i:A^{i+1} \rightarrow A^i$ is the unique morphism given by the universal property of the symmetric tensor power,  such that $\comp{\eq_i:A^{i+1}}{p_i} \rightarrow A^{\otimes i} = \eq_{i+1};(A^{\otimes i} \otimes t_A)$.
+
+Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} have shown that where the limit $(A^\infty, \{p^\infty_i\from A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e.
+for each object $B$, $B \otimes A^\infty$ is the limit of
+$$B \otimes I \stackrel{B \otimes p_0}{\leftarrow} B \otimes A  \stackrel{B \otimes p_1}{\leftarrow} B\otimes  A^2 \ldots $$
+then a comultiplication $\mu:A^\infty \rightarrow A^\infty \otimes A^\infty$ may be defined making $(A^\infty,\mu,t_{\oc A})$ the cofree commutative comonoid.
+Where these conditions are satisfied, we shall call this a MTT-exponential.
+\begin{proposition}Any sequoidally decomposable category has all symmetric tensor powers, and these are preserved by the tensor.  
+\end{proposition} 
+\begin{proof}
+By sequoidal decomposability, for any $n$, $A^{\otimes (n+1)}$ is the cartesian product $\Pi_{i \leq n} (A \sequoid A^{\otimes n})$ with projections 
+  $\comp{\sym_i}{\wk_{A,A^{\otimes n}}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
+
+  We inductively define the sequoid powers $A^{\sequoid n}$ by $A^{\sequoid 1}=A$ and $A^{\sequoid(n+1)}=A\sequoid A^{\sequoid n}$.
+Given $n$, we inductively define a morphism $\eq_n\from A^{\sequoid n}\to A^{\tensor n}$ as the diagonal $\langle \id_A\sequoid\eq_{n-1}\rangle$ into the product -- so $\comp{\wk}{\comp{\sym_i}{\eq_n}}=\id\sequoid e_{n-1}$ for each $i$.
+
+  If $\pi\in S_n$ is a permutation, we write $\sym^\pi$ for the appropriate symmetry of $A^{\tensor n}$.
+We now claim that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi\in S_n$ -- so $\eq_n$ equalizes the $\sym^\pi$.
+Indeed, let $\pi\in S_n$.
+Then we may write $\sym^\pi = \comp{\id_A\tensor\sym^\rho}{\sym_i}$ for some $i$ and some $\rho\in S_{n-1}$.
+Now we have:
+  \begin{IEEEeqnarray*}{rClC}
+    \comp{\wk}{\comp{\sym^\pi}{\eq_n}} & = & \comp{\wk}{\comp{\comp{(\id\tensor\sym^\rho)}{\sym_i}}{\eq_n}} & \\
+    & = & \comp{(\id\sequoid\sym^\rho)}{\comp{\wk}{\comp{\sym_i}{\eq_n}}} & \hspace{24pt}\textrm{(by naturality of $\wk$)} \\
+    & = & \comp{(\id\sequoid\sym^\rho)}{(\id\sequoid\eq_{n-1})} & \\
+    & = & \id\sequoid\eq_{n-1}
+  \end{IEEEeqnarray*}
+  Since $\pi$ was arbitrary, it follows that $\comp{\wk}{\comp{\comp{\sym_j}{\sym^{\pi}}}{\eq_n}}=\comp{\comp{\wk}{\sym_j}}{\eq_n}$ for all $j$ and therefore that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi$, as desired.
+
+  Now define $\wk^n\from A^{\sequoid n}\to A^{\tensor n}$ inductively by $\wk^n = \comp{\id\sequoid\wk^{n-1}}{\wk}$.
+We may show by induction that $\comp{\wk^n}{\eq_n}=\id_{A^{\sequoid n}}$ for all $n$: indeed, we have
+  \begin{IEEEeqnarray*}{rClC}
+    \comp{\wk^n}{\eq_n} & = & \comp{(\id\sequoid\wk^{n-1})}{\comp{\wk}{\eq_n}} & \\
+    & = & \comp{(\id\sequoid\wk^{n-1})}{(\id\sequoid\eq_{n-1})} & \\
+    & = & \id\sequoid \id = \id & \hspace{24pt}\textrm{(by induction)}
+  \end{IEEEeqnarray*}
+  Now let $f\from C \to B \tensor A^{\tensor n}$ be such that $\comp{(\id\tensor\sym^\pi)}{f}=f$ for all $\pi\in S_n$.
+It follows from what we have just shown that if $f=\comp{(\id\tensor\eq_n)}{g}$, then $g=\comp{\comp{\id\tensor\wk^n}{\id\tensor\eq_n}}{g}=\comp{\id\tensor\wk^n}{f}$.
+So we just need to show that
+  \[
+    f=\comp{(\id\tensor(\comp{\eq_n}{\wk_n}))}{f}
+    \]
+  We first assume that $B=I$, so we have $f\from C\to B\tensor A^{\tensor n}$ and $\comp{\sym^\pi}{f}=f$ for all $\pi\in S_n$ and we are trying to show that $f=\comp{\comp{\eq_n}{\wk^n}}{f}$.
+We do this by showing that $\comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}}=\comp{\comp{\wk}{\sym_i}}{f}$ for all $i$.
+
+  Indeed, we have:
+  \begin{IEEEeqnarray*}{rClC}
+    \comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}} & = & \comp{\comp{(\id\sequoid\eq_{n-1})}{(\id\sequoid\wk^{n-1})}}{\comp{\wk}{f}} & \\
+    & = & \comp{\wk}{\comp{(\id\tensor(\comp{\eq_{n-1}}{\wk^{n-1}}))}{f}} &\hspace{24pt}\textrm{(by naturality of $\wk$)} \\
+    & = & \comp{\wk}{f} &\hspace{2pt}\textrm{(by induction)} \\
+    & = & \comp{\wk}{\comp{\sym_i}{f}}
+  \end{IEEEeqnarray*}
+
+  Now let $B$ be an arbitary object of the category.  [TODO: finish working this out.]
+\end{proof}
+Thus, in any sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit for this diagram exists and is preserved by the sequoid, 
+--- i.e.
+for any $B$, $B \sequoid A^\infty$ is the limit for $B \sequoid \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid.
+Conversely, we may show that any cofree commutative comonoid which arises as a $\otimes$-preserving limit of symmetric tensor powers is a final coalgebra.
+\begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty, \comp{\wk_{A\tensor\oc A}}{\comp{\der_A}{\mu_A}})$ is a final coalgebra for the functor $A \sequoid \_$.
+\end{proposition}
+\begin{proof}
+  Observe that in a sequoidally decomposable category, the morphism $\wk_{A,A^n}:A \sequoid A^n: \rightarrow A^{n+1}$ is a section (we may define the corresponding retraction inductively from the decomposition of the tensor).
+Hence if   the limit $A^\infty$ is preserved by the functor $A \tensor \_$, it is preserved by the sequoid $A \sequoid\_$ --- i.e.
+$A^\infty$ is the limit of the chain $A \sequoid \Delta = \Delta$.
+
+  Thus, for  any  $A \sequoid\_$-coalgebra $f\from B \rightarrow A \sequoid B$, we may define a unique coalgebra morphism $\fcoal{f}\from B \rightarrow \oc A$ as the mediating morphism of the cone $\{f_i\from B \rightarrow A^i\ |\ i \in \omega\}$, where  $f_0 = t_B$ and $f_{i+1} = f;(A \sequoid f_i)$.
+\end{proof}
+
+\subsection{Win-games and winning strategies}
+
+The construction from \cite{MelliesCofCommCom} covers a lot of different cases, but there are some situations in which it does not apply.
+One example is that of \emph{win-games}, or games with a winning condition (\cite{abramskyjagadeesangames}, \cite{martinsthesis}).
+Given a game $A$, we write $\overline{P_A}$ to be the limit-closure of $P_A$ -- that is, $P_A$ together with the set of infinite sequences, all of whose finite prefixes are in $P_A$.
+A \emph{win-game} is a game $A$ together with a function $\zeta_A\from \overline{P_A}\to\OP$ such that:
+\begin{itemize}
+  \item $\zeta_A(\emptyplay) = \neg b_A$
+  \item $\zeta_A(sa) = \lambda_A(a)$
+\end{itemize}
+Thus, $\zeta_A$ is entirely determined on $P_A$, and the only new information is the values that $\zeta_A$ takes on the infinite positions in $\overline{P_A}$.
+The reason we bother to define $\zeta_A$ on finite positions at all is so that we can define it on the connectives:
+\begin{gather*}
+  \zeta_{\prod_{i\in I}A_i}(s) = \bigwedge_{i\in I}\zeta_{A_i}(s\vert_{A_i}) \\
+  \zeta_{A\tensor B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
+  \zeta_{A\sequoid B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
+  \zeta_{A \implies B}(s) = \zeta_A(s) \Rightarrow \zeta_B(s) \\
+  \zeta_{\oc A}(s) = \bigwedge_{i\in I}(\zeta_A(s\vert_i))
+\end{gather*}
+
+Here, $\wedge$ and $\Rightarrow$ are the usual propostional connectives on $\{T,F\}$, where we identify $T$ with $P$ and $F$ with $O$.
+
+We define a \emph{winning strategy} on $(A,\zeta_A)$ to be a total strategy $\sigma$ on $A$ such that $\zeta_A(s)=P$ whenever $s$ is an infinite sequence, all of whose finite prefixes are in $\sigma$.
+It is known (see \cite{abramskyjagadeesangames}) that the composition of winning strategies is winning and that we get a decomposable, distributive sequoidal closed category $\W$ with $\oc A$ as the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ \cite{martinsthesis}.
+
+However, in this case, $\oc A$ is not the sequential limit of the symmetrized tensor powers over $A$.
+Since $\W$ is a decomposable, distributive sequoidal category, the symmetrized tensor powers of $A$ are given by the sequoidal powers $A^{\sequoid n}$.
+But now the limit of these objects is not quite the game $\oc A$; instead, it is the game $A^{\sequoid\omega}=\co A$ in which player $O$ may open an arbitrarily large number of copies of $A$, but not infinitely many.
+In the finite case, there was no way to keep track of infinite positions, so we could not make this distinction, but in the win-games case we can: we set $\zeta_{\co A}(s)=\zeta_{\oc A}(s)$, unless $s$ contains moves in infinitely many games, in which case we set $\zeta_{\co A}(s) = P$.
+
+This limit is not preserved by the functor $A\sequoid\blank$: in the game $A^{\sequoid(\omega+1)}=A\sequoid\co A$, player $O$ wins if he wins either in $A$ or in $\co A$, so he can win even if he plays in infinitely many games, as long as he wins in the first copy of $A$.
+Similarly, in the game $A^{\sequoid(\omega+n)}$, player $O$ can win as long as he wins in one of the first $n$ copies of $A$.
+Therefore, the limit $A^{\sequoid\omega2} \emph{is}$ the game $\oc A$: the final sequence for $A\sequoid\blank$ stabilizes at $\omega2$.
+
+We see that the exponential in $\W$ is not an MTT-exponential.
+
+This example is a special case of our later result on transfinite games.
+For now, we examine a coalgebraic approach that will prove that the final coalgebra $\oc A$ for $A\sequoid \blank$ in the category $\W$ of win-games gives us a cofree commutative comonoid.
+
+\subsection{The coalgebraic construction under the strong monoidal hypothesis}
+
+We will now need to assume that we are in a decomposable, distributive sequoidal category $(\C,\C_s,J,\wk)$ such that $\C_s$ has all products and $J$ preserves them.
+However, we will no longer need the MTT assumption that the exponential should be constructed as a limit of sequoidal powers.
+The main cost is that we will need to make a further assumption: that a certain naturally defined morphism $\oc A \tensor \oc B\to \oc (A\times B)$ is an isomorphism.
+This assumption, broadly corresponding to the demand that the functor $\oc A$ be strong monoidal from the Cartesian category $(\C,\times,1)$ to the monoidal category $(\C,\tensor,I)$, will allow us to construct the comultiplication directly from the Cartesian structure and the definition of $\oc A$ as a final coalgebra.
 
@@
 \begin{definition}
-  Let $A,B$ be objects of an inclusive, Cartesian, distributive sequoidal category $(\C,\C_s,J,\wk)$ with final coalgebras $\oc A\xrightarrow{\alpha_A} A\sequoid\oc A$ for all endofunctors of the form $A\sequoid\blank$.
+  Let $A,B$ be objects of an decomposable, distributive sequoidal category $(\C,\C_s,J,\wk)$ with final coalgebras $\oc A\xrightarrow{\alpha_A} A\sequoid\oc A$ for all endofunctors of the form $A\sequoid\blank$.
 Let $A,B$ be objects of $C$.
@@
   \begin{IEEEeqnarray*}{RCL}
-    \kappa_{A,B}=\oc A \tensor \oc B & \constantwidthxrightarrow{\langle\id_{\oc A\tensor\oc B},\; \sym_{\oc A,\oc B}\rangle} & (\oc A \tensor \oc B) \times (\oc B \tensor \oc A) \\
-    \cdots & \constantwidthxrightarrow{(\alpha_A\tensor\id_{\oc B})\times(\alpha_B\tensor\id_{\oc A})} & ((A \sequoid \oc A) \tensor \oc B) \times ((B \sequoid \oc B) \tensor \oc A) \\
-    \cdots  & \constantwidthxrightarrow{\wk_{A\sequoid\oc A,\oc B}\times\wk_{B\sequoid\oc B,\oc A}} & ((A \sequoid \oc A) \sequoid \oc B) \times ((B \sequoid \oc B) \sequoid \oc A) \\
+    \kappa_{A,B} = \oc A \tensor \oc B & \constantwidthxrightarrow{\langle\wk_{\oc A,\oc B},\;\comp{\sym_{\oc A,\oc B}}{\wk_{\oc A,\oc B}}} & (\oc A \sequoid \oc B) \times (\oc B \sequoid \oc A) \\
+    \cdots & \constantwidthxrightarrow{(\alpha_A\sequoid\id_{\oc B}) \times (\alpha_B\sequoid\id_{\oc A})} & ((A \sequoid \oc A) \sequoid \oc B) \times ((B \sequoid \oc B) \sequoid \oc A) \\
     \cdots & \constantwidthxrightarrow{\passoc_{A,\oc A,\oc B}\inv\times\passoc_{B,\oc B,\oc A}\inv} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc B \tensor \oc A) \\
@@
 \end{proposition}
-\begin{proof}
-  See Appendix.
-\end{proof}
 
@@
 \end{proposition}
-\begin{proof}
-  See appendix.
-\end{proof}
 
@@
 
-\begin{proof}
-  See Appendix.
+We give a broad outline of the proofs of the results in this section in the Appendix.
+
+\subsection{The Sequoidal Exponential as a Bifree Algebra}
+Observe that in our category of games, $(!A,\alpha)$ is in fact a \emph{bifree algebra} for $A\sequoid\blank$ --- the isomorphism $\alpha^{-1}: A \sequoid !A \rightarrow !A$ is an initial algebra for  $A \sequoid \blank$.
+We may show that in such cases, the condition that $!$ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $\oc A$ with the structure of a comonoid by defining:
+$\mu:!A \rightarrow !A  \otimes !A$
+ to be the catamorphism of the $A \sequoid \blank$ algebra:
+$$A \sequoid (!A \otimes !A) %\stackrel{\langle \id, A \sequoid \sym\rangle}{\cong} 
+\cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)$$
+This satisfies the further requirements of a \emph{linear category} in the sense of \cite{Bierman}, although it does not appear to be possible to show that it is the cofree commutative comonoid.} :
+we may define an inverse to $\int:!A \otimes !A \rightarrow ! (A \times B)$  as the \emph{catamorphism} of the  $A \sequoid\blank$-algebra:
+$$(A \times B) \sequoid !A \otimes !B \cong (A \sequoid (!A \otimes !B)) \times  (B \sequoid (!A \otimes !B)) \cong (!A \sequoid !B) \times (!B \sequoid !A)$$
+
+It is not necessary for the final $A \sequoid\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid.
+An example is provided by  the category $\W$ of win-games and winning strategies, which is sequoidal closed and decomposable.
+To show that the  final $A \sequoid\_$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\fix_A(f);f = \fix(f)$.
+\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \sequoid\_$-algebra. Then we may define a fixed point operator on $\C$.  
+\end{proposition}    
+\begin{proof}For any $A$, let  $\Phi_A:!(A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \sequoid\blank \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \sequoid A \rightarrow A$, which is a  $(A \multimap A) \sequoid \blank$-algebra.
+For any morphism $f:A \rightarrow A$ we may define $\fix_A(f) = \Lambda(f)^\dag;\Phi_A$, where $\Lambda(f):I \rightarrow (A \multimap A)$ is the ``name'' of $f$.
 \end{proof}
+As one would expect, it is not possible to define a fixed point operator on the category of games and winning strategies ---  for example, if $\bot$ is the game with a single move then the hom-set $\C(I,\bot)$ is empty and hence there can be no morphism $\fix_\bot(\id_\bot)$.
+So the final  $A \sequoid \_$-coalgebra is not bifree in this case.
 
@@
 The `correct' definition of $\oc A$ in the transfinite game category is one in which there is an unlimited number of copies of $A$ to open (rather than $\omega$-many), but this is not the final coalgebra for the functor $A\sequoid\blank$.
-[TODO: discuss ways to construct this object]
 
@@
 
-We give a brief summary of the construction of the category of transfinite games.  Full details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
+We give a brief summary of the construction of the category of transfinite games.  Some more details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
 
@@
 
-Apart from the possibly transfinite length of sequences of moves, the only new thing in this definition is the function $\zeta_A$.
+Apart from the possibly transfinite length of sequences of moves, the only new thing in this definition is the function $\zeta_A$, which we met briefly when defining win-games.
 Thanks to the consistency condition, $\zeta_A$ gives us no new information for successor positions; it is necessary in order to tell us which player is to move at limiting positions.
@@
 We want to show that this is the final coalgebra for $A\sequoid\blank$.
-The proof for the finite case found in \cite{martinsthesis} will not work in this case, since it implicitly uses the fact that $\oc A$ is the limit of the sequence
-\[
-  I \leftarrow A \leftarrow A \sequoid A \leftarrow A \sequoid (A \sequoid A) \leftarrow \cdots
-  \]
-(cf. also \cite{MelliesCofCommCom}).  In the transfinite categories, this is no longer the case.
-
-While it is possible to prove that $\alpha_A\from \oc A\to A\sequoid \oc A$ is the final coalgebra for $A\sequoid\blank$ directly, we shall instead give a proof by extending the sequence given above to an ordinal-indexed sequence.
-This is the \emph{final sequence}, familiar in coalgebra \cite{finalseq}.
-Specifically, we construct a functor $\F\from\oppcat{\Ord}\to\G(\alpha)$, where $\Ord$ is the order category of the ordinals, writing
-\begin{gather*}
-  \F(\gamma)=A^{\sequoid\gamma}\\
-  \F(\gamma\le\delta)=j_\gamma^\delta\from A^{\sequoid\delta}\to A^{\sequoid\gamma}
-\end{gather*}
-according to the following inductive recipe:
-\begin{itemize}
-  \item $A^{\sequoid 0} = 1$
-  \item $A^{\sequoid (\gamma + 1)} = A \sequoid A^{\sequoid\gamma}$
-  \item If $\mu$ is a limit ordinal, then $A^{\sequoid\mu}$ is the limit of the diagram formed by the $A^{\sequoid\gamma}$ for $\gamma<\mu$, together with the morphisms $j_\gamma^\delta$, for $\gamma\le\delta<\mu$.
-  \item $j_0^\gamma=*$
-  \item $j_\gamma^\lambda$ is the morphism in the limiting cone
-  \item $j_\gamma^{\delta+1} = \comp{j_\delta^{\delta+1}}{j_\gamma^\delta}$
-  \item If we write $C_\lambda$ for the limiting cone for $\lambda$ over the $A^{\sequoid\gamma}$ for $\gamma<\mu$, then we may form a cone $A\sequoid C_\lambda$ over the same diagram by applying the functor $A\sequoid\blank$ to $C_\lambda$ and then extending the cone to $1$ in the only possible way.
-Then $j_\lambda^{\lambda+1}$ is the unique morphism from $A^{\sequoid(\lambda+1)}$ to $A^{\sequoid\lambda}$ inducing a morphism of cones from $A\sequoid C_\lambda$ to $C_\lambda$.
-\end{itemize}
-
-It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then ${j_\delta^{\delta+1}}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
-In this case, we say that the sequence \emph{stabilizes at $\delta$}.
-Our proof strategy is therefore to show that the sequence stabilizes at some $\delta$, and to show that $A^{\sequoid\delta}$ is isomorphic to $\oc A$.
-
-We do this by giving a classification of the games $A^{\sequoid\gamma}$.
+The proof for the finite case found in \cite{martinsthesis} will not work in this case, since it implicitly uses the fact that $\oc A$ is an MTT-exponential.
+In the transfinite categories, this is no longer the case.
+
+While it is possible to prove that $\alpha_A\from \oc A\to A\sequoid \oc A$ is the final coalgebra for $A\sequoid\blank$ directly, we shall instead give a proof by extending the MTT sequence to the full final sequence.
+We shall give a complete classification of the games $A^{\sequoid\gamma}$ and use it to show that the final sequence for $A\sequoid\blank$ must stabilize at $\oc A$.
+
+\begin{definition}
   Let $s\in\omega^{*<\alpha}$ be any transfinite sequence of natural numbers.
@@
   \end{itemize}
-
-We can prove some basic results about these predicates:
+\end{definition}
+
+It is easy to prove some basic results about these predicates:
 \begin{proposition}\label{basicResultsAboutRank}
@@
 
-\begin{proof}
-  See Appendix.
-\end{proof}
-
-Our classification result for the final sequence then becomes:
+We can then classify the terms of the final sequence for $A\sequoid\blank$ as follows:
 \begin{theorem}\label{finalseqClassification}
@@
 \end{theorem}
-
-\begin{proof}
-  See Appendix.
-\end{proof}
 

### 2017-04-09 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Changed direction of composition (...)
Rewrote introduction.

@@
 \renewcommand{\implies}{\multimap}
-\newcommand{\comp}[2]{#1 \circ #2}
+\newcommand{\comp}[2]{#2 ; #1}
 \newcommand{\cprd}{\sqcup}
@@
 
-Games models of pure functional programming languages such as PCF (\cite{ajmPcf} and \cite{hoPcf}, for example) tend to include the requirement that strategies be \emph{history-free}: that is, the response to a particular position may depend only upon the last move played, and not upon what has gone before.
+Games models of pure functional programming languages such as PCF (\cite{ajmPcf} and \cite{hoPcf}, for example) tend to include the requirement that strategies be \emph{history-free}\footnote{In fact, the model in \cite{hoPcf} and other models following the `Hyland-Ong' tradition use \emph{innocent} strategies, rather than history free strategies to model statelessness.
+We will focus on AJM-style Game Semantics in this paper, so we shall focus on history-freeness vs.
+history sensitivity rather than innocence.}: that is, the response to a particular position may depend only upon the last move played, and not upon what has gone before.
 This makes sense for stateless languages, where the program should have no `memory' to recall what has gone before.
 
-If we include history-sensitive strategies in our models, then we can start to recover some stateful behaviour (see \cite{SamsonGuyIAPassive}, for example), since history-sensitive strategies have a built in state.
-This concept of state is often hard to work with: since the representation as a strategy is so intensional, there is no object representing the state, and the state of the program must be inferred from the behaviour of the strategy.
-
-At the other extreme, we have traditional, domain-theoretic semantics, in which stateful programs are represented as \emph{state transformers} -- that is, functions $W\times X \to W\times Y$, where $W$ is an object representing the state.
-
-State transformers are typically fairly straightforward to reason about, and we would like to have a similar technique available in our games models.
-This gap was bridged by one of the authors in \cite{laird02} with the introduction of the new \emph{sequoid} operator $\blank\sequoid\blank$ on games, which the same as the tensor product $\blank\tensor\blank$, except that play is required to start in the left hand game.
-We interpret a state transformer as a coalgebra for the functor $A\sequoid\blank$ -- that is, a morphism from $S$ to $A\sequoid S$, so that the state $S$ is only modified after the program $A$ has been consulted.
-The benefit of this explicit ordering is that we may model multiple iterations of the state transformer as coalgebras:
+If history-free strategies are the game-semantic interpretation of stateless programs, then history-sensitive strategies should be the game-semantic interpretation of stateful programs, and this is indeed how they are used: Abramsky and McCusker's model of Idealized Algol \cite{SamsonGuyIAPassive}, for example, makes use of history-sensitive strategies in order to model stateful programs.
+However, this idea of state can be difficult to work with, because it is completely \emph{implicit} in the strategy.
+Let us, for example, try to model a simple storage cell.
+Let $X$ be a set of values and, as in \cite{SamsonGuyIAPassive}, let $\Var[X]$ be the game with maximal plays $rx$ and $w_x\checkmark$, where $x$ ranges over $X$.
+$rx$ corresponds to a $\read$ method: player $O$ plays $r$ and expects to receive the value $x$ currently in the cell, while $w_x\checkmark$ corresponds to a write method: player $O$ writes $x$ into the cell and then player $P$ confirms that the write has taken place.
+
+It is now clear that we have a strategy $\cell$ on $\oc \Var[X]$ corresponding to a storage cell: whenever player $O$ plays $w_x$, respond with $\checkmark$, and whenever player $O$ plays $r$, respond with the last $x$ such that $w_x$ was played (if the cell is uninitialized -- i.e., if $w_x$ has never been played for any $x$ -- then we return either nothing or some specified initial value, depending on what we are trying to model).
+This strategy is clearly history sensitive and represents a stateful program; however, it is tricky to reason about the statefulness of $\cell$, because there is no object explicitly representing the state: the state in $\cell$ is \emph{implicit}, and it appears that we need to resort to combinatorial arguments in order to reason about it.
+
+Contrast this with the handling of state in traditional domain-theoretic semantics, where we represent a stateful program as a function $W \times X \to W \times Y$, or a \emph{state transformer}, where $W$ is a built-in store of state that can be reasoned about directly.
+In 2002, one of the authors introduced the game-semantic equivalent of a state-transformer by defining a new operation on games -- the \emph{sequoid} $\blank\sequoid\blank$\cite{laird02}.
+The game $A\sequoid B$ is the same as the game $A\tensor B$, except that the first move must take place in $A$.
+We now model a state transformer for a program as a morphism $S \to A \sequoid S$ -- i.e., a \emph{coalgebra} for the functor $A\sequoid\blank$ -- where $A$ is the program and $S$ is the changed state.
+The justification for the order relation on the sequoid operator is that the state should only change in response to some action by the environment.
+
+For example, let $X$ be the game with maximal plays $rx$ for $x\in X$.
+Then we may define a state transformer for $X \implies \Var[X]\sequoid X$ as follows: play must start in the game $\Var[X]$.
+If player $O$ starts with the move $r$, then request a value of $x$ on the left and then copy it into both $\Var[X]$ and $X$ on the right (so if $X$ on the left represents the initial state and $X$ on the right represents the final state, then we have returned the value of the state and left the state unchanged).
+If player $O$ starts with the move $w_y$, return $\checkmark$ and then copy the value $y$ over to $X$ on the right, ignoring the value of $X$ on the left.
+
+Note that we may model multiple iterations of the state transformer as coalgebras:
 \[
@@
 
-Now we introduce the key part of the construction: suppose that the functor $A\sequoid\blank$ has a final coalgebra $\oc A\to A\sequoid \oc A$.
-Then a coalgebra $S\to A\sequoid S$ (i.e., a state transformer) naturally gives rise to a morphism $S \to \oc A$ in which the state is completely encapsulated and we are allowed to invoke the program $A$ as many times as we like.
-We will show that we can construct various history-sensitive strategies denoting stateful programs using precisely this strategy; in particular, we will give a coalgebraic construction of the $\cell$ strategy from \cite{SamsonGuyIAPassive}, which is the key to their model for Idealized Algol.
-
-Even more intriguingly, the game $\oc A$ that arises as the final coalgebra for the functor $A\sequoid\blank$ has the structure of an exponential object in the category of games: it is the cofree commutative comonoid over $A$.
-We will spend the rest of the paper examining why this is, and what general conditions we need in order to show that the final coalgebra for $\oc A$ and the cofree commutative comonoid over $A$ coincide.
-For this, we will need the abstract definition of a \emph{sequoidal category}, which is an extension of a monoidal category in order to accommodate the sequoid operator.
-We will first consider the explicit formula for the cofree commutative comonoid given by Melli\'es, Tabareau and Tasson in \cite{MelliesCofCommCom} and show that it can be given a sequoidal interpretation.
-The Melli\'es-Tabareau-Tasson construction works for finite games, but its hypotheses do not hold in the case of the category of games with infinitary winning conditions and winning strategies, even though the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ still coincide in these categories.
-
-Instead, we will show that if our sequoidal category has all products then the cofree commutative comonoid structure on $\oc A$ may be constructed directly from the sequoidal structure and the definition of $A\sequoid\blank$ as a final coalgebra for $A\sequoid\blank$, provided that we insist on a further hypothesis: that the functor $\oc$ is monoidal from the Cartesian category to the monoidal category: i.e., if we have an isomorphism between $\oc A \tensor \oc B$ and $\oc(A\times B)$ for all $A,B$.
-We show that this hypothesis is automatically satisfied whenever $\oc A$ has the structure of a \emph{bifree algebra} for $A\sequoid\blank$; i.e., when it simultaneously has the structure of final coalgebra and initial algebra.
-However, the exponential in the category of win-games is not an initial algebra for $A\sequoid\blank$ \cite{martinsthesis}.
-
-Lastly, we will provide an illuminating counterexample: a category of games in which the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ do not coincide.
-This is the category of games where plays are allowed to have transfinite length.
-We will show that the Melli\'es-Tabareau-Tasson construction fails badly in this setting, but that we may still construct the final coalgebra for $A\sequoid\blank$ as the limit of its final sequence.
-In this setting, the final coalgebra is the game where we have `only' $\omega$-many copies of the sub-game to play in, whereas in the cofree commutative comonoid we may open transfinite sequences of the subgame.
+Now we come to the key point of the construction: if $A$ is a game, then the Hyland exponential $\oc A$ \cite{hyland1997games} has the structure of the \emph{final coalgebra} for the functor $A \sequoid\blank$.
+Therefore, following \cite{jacobs}, any coalgebra $S\to A\sequoid S$ (i.e., any state transformer) gives rise to a morphism $S\to\oc A$ that encapsulates the explicit state of the state transformer into an implicitly stateful history-sensitive strategy $S\to\oc A$ that corresponds to repeatedly invoking the state transformer, passing the state from one invocation to the next.
+
+Indeed, the state transformer we defined on $X\implies\Var[X]\sequoid X$ gives rise to a morphism $X\to\oc\Var[X]$ that gives us the behaviour of a storage cell with initial value given by the copy of $X$ on the left; composing this with our desired initial value on $X$ gives us the strategy $\cell$.
+The difference now is that, rather than reason directly about the implicit strategy $\cell$, we may reason about the explicit state in our state transformer and then use coalgebraic methods to talk about $\cell$.
+
+It is clear that the key fact in the construction is that the final coalgebra for $A\sequoid\blank$ coincides with the exponential $\oc A$, which has the structure of the \emph{cofree commutative comonoid} on $A$.
+We will begin by introducing the general idea of using coalgebra to define higher-order stateful objects, using a construction on the category $\Rel$ of sets and relations.
+This construction is simple to define, but the final coalgebra in that context does not give us a good model of the exponential: it gives us a cofree comonoid, but not a commutative one.
+This motivates us to study state transformers using game semantics and the sequoid operator.
+
+We review the definition of a \emph{sequoidal category} from \cite{laird02}: a category-theoretic formalization of the sequoid operator akin to the formalization of the tensor product $\tensor$ by the definition of a \emph{monoidal category}.
+We illustrate the definition by showing how the sequoidal structure allows us to model stateful programs as morphisms into the final coalgebra for the functor $A\sequoid\blank$, using the example of the $\cell$ strategy in the category of games.
+
+We spend the rest of the paper discussing the question of what assumptions we need in order to prove that the final coalgebra for $A\sequoid\blank$ coincides with the cofree commutative comonoid on $A$.
+The explicit formula for the cofree commutative comonoid given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} provides a way to link the two constructions that works for the basic category of games; however, it is not powerful enough to prove that the final coalgebra and the cofree commutative comonoid are the same in the category of games with infinitary winning conditions.
+
+We turn instead to a purely sequoidal/coalgebraic proof that the final coalgebra $\oc A$ for $A\sequoid\blank$ is the carrier of the cofree commutative comonoid on $A$.
+In this case, we will need to assume that our category has a Cartesian structure and also assume an additional hypothesis: that if $A$ and $B$ are objects, then a certain natural morphism $\oc A \tensor \oc B \to \oc (A\times B)$ is an isomorphism.
+We will refer to this as the \emph{strong monoidal hypothesis}, since it can be used to show that $\oc\blank$ gives rise to a strong monoidal functor from the category with its Cartesian structure to the category with its monoidal functor.
+
+We show that the strong monoidal hypothesis holds whenever $\oc A$ is a \emph{bifree algebra} for $A\sequoid\blank$: that is, it is simultaneously an initial algebra and a final coalgebra.
+
+We finish with a non-example: the sequoidal category of games with transfinite plays.
+In this setting the final coalgebra for $A\sequoid\blank$ does not carry the structure of the cofree commutative comonoid over $A$.
+By our discussion above, note that the final coalgebra for $A\sequoid\blank$ has the structure of $\omega$-many copies of the game $A$, where we pass the state from $A_i$ to $A_{i+1}$:
+\tikzset{dotsstyle/.style={draw=none}}
+\[
+  \begin{tikzpicture}
+    \matrix[matrix of nodes, column sep=36pt, inner xsep=1ex, name=m, nodes={draw=black}] {
+      $A_0$ & $A_1$ & $A_2$ & |[dotsstyle]| $\cdots$ \\ };
+    \path[commutative diagrams/.cd, every arrow, every label, labels={font size=tiny}]
+      (m-1-1) edge node {state} (m-1-2)
+      (m-1-2) edge node {state} (m-1-3)
+      (m-1-3) edge node {state} (m-1-4);
+  \end{tikzpicture}
+\]
+
+For finite interactions, we can use this to model the exponential, in which repeated access to the resource $A$ is allowed, by passing an empty state in between successive invocations of $A$.
+In the transfinite case, however, there might not be enough copies of $A$ in the final coalgebra to satisfy our needs: consider a program that, over time $\omega$, uses the resource $A$ infinitely many times.
+If we carry on into transfinite time, the program may continue to request access to the resource $A$.
+But this is no longer possible if we are using the final coalgebra for our `exponential', since we are only able to construct a sequence of invocations of $A$ of length $\omega$: there is no predecessor copy of $A$ to receive the (empty) state from.
+
+We shall demonstrate why our earlier approaches fail in this context: the Melli\'es-Tabareau-Tasson construction fails badly in this case, just as it fails for win games and winning strategies (which may be viewed as games of length $\omega+1$).
+Similarly, the strong monoidal hypothesis does not hold, since a transfinite interleaving of two sequences of length $\omega$ may have length greater than $\omega$.
 
@@
 Our sequoidal category will be closely modelled upon the category of games we have just considered: the objects will be games, with the modification that sequences of moves may now have transfinite length.
-This is a natural construction, occurring in the study of determinacy by Mycielski \cite{mycielskiChoice}, Blass \cite{blassChoice} and Weiss \cite{longgamesbook}, and it appears to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
+This is a natural construction, occurring in the study of determinacy by Mycielski \cite{mycielskiChoice}, Blass \cite{blassChoice} and Weiss \cite{longgamesbook}.
+Transfinite games were used by Berardi and de'Liguoro to give a charactarization of total functionsals \cite{BerardiTransfiniteGames}, and they appear to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
 

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Reduced the number of pages.

@@
 We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.
-A game will be given by a tuple
-\[
-  A = (M_A, \lambda_A, b_A, P_A)
-  \]
-where
-\begin{itemize}
-  \item $M_A$ is a set of moves.
-  \item $\lambda_A\from M_A\to\OP$ is a function designating each move as either an \emph{$O$-move} or a \emph{$P$-move}.
-  \item $b_A\in\OP$ is a choice of starting player.
-  \item $P_A\subset M_A^*$ is a prefix-closed set of alternating plays (so if $sab\in P_A$ then $\lambda_A(a)=\neg\lambda_A(b)$) such that if $as\in P_A$ then $\lambda_A(a)=b_A$.
-\end{itemize}
-
-We call $sa\in P_A$ a \emph{$P$-position} if $a$ is a $P$-move and an \emph{$O$-position} if $a$ is an $O$-move.
-
-A \emph{strategy} for player $P$ for a game $A$ is identified with the set of positions that may arise when playing according to that strategy.
-Namely, it is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the two conditions:
-\begin{description}
-  \item[(sO)] If $s\in\sigma$ is a $P$-position and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.
-  \item[(sP)] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
-\end{description}
-
-We shall now concentrate on games $A$ for which $b_A=O$, called \emph{negative games}.  We shall informally describe the standard connectives on negative games:
+A game $A$ is given by a tree $P_A$ of \emph{positions}, which are alternating sequences of $O$-moves and $P$-moves.
+We call a position a \emph{$P$-position} if it ends with a $P$-move and an \emph{$O$-position} if it ends with an $O$-move.
+A \emph{strategy} for a game $A$ is a subtree $\sigma$ of $P_A$ that is closed under $O$-replies to $P$-positions and which satisfies \emph{determinism}: if $sa,sb\in\sigma$, where $s$ is a $P$-position, then $a=b$.
+We will adopt the rule that all positions must start with an $O$-move.
+
+We build connectives on games in the usual way.
 
@@
 From then on, play continues in $A_i$.
-When we have defined the category of games, $\prod_{i\in I}A_i$ will be the category-theoretic product of the $A_i$.
 If $A_1,A_2$ are games, we write $A_1\times A_2$ for $\prod_{i=1}^2 A_i$.
@@
 
-If $A,B,C$ are negative games, $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, then we may form a strategy $\comp\tau\sigma$ for $A\implies C$ by setting
-\[
-  \sigma\|\tau = \{\s\in (M_A\cprd M_B\cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;s\vert_{B,C}\in\tau\}
-  \]
-and then defining
-\[
-  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\comp\tau\sigma\}
-  \]
-It is well known (see, for example, \cite{abramskyjagadeesangames}) that $\comp\tau\sigma$ is indeed a strategy for $A\implies C$ and that this form of composition is associative and has an identity.
-It is also well known that the resulting category $\G$ of games and strategies has products given by the operator $\times$ and a symmetric monoidal closed structure given by the operations $\tensor$ and $\implies$.
+It is well known (see \cite{abramskyjagadeesangames}, for example) that we may compose strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ to get a morphism $\comp\tau\sigma$ for $A\implies C$ and that this structure gives rise to a monoidal category where objects are games, morphisms from $A$ to $B$ are strategies for $A\implies B$ and the tensor product and linear implication are given by $A\tensor B$ and $A\implies B$.
+We call this category $\G$.
+$\G$ has all products, given by $\prod_{i\in I}A_i$ as above.
 
@@
 
-One further question to ask is: does the sequoid operator give rise to a functor $\blank\sequoid\blank\from\G\times\G\to\G$, as the tensor operator does?
-The answer is no: indeed, let $A,B,C,D$ be negative games, let $\sigma$ be a strategy for $A\implies C$ and let $\tau$ be a strategy for $B\implies D$.
-Our aim is to construct a natural strategy $\sigma\sequoid\tau$ for $(A\sequoid B)\implies (C\sequoid D)$.
-There is an obvious way to try and do this: player $P$ should play according to the strategy $\sigma$ whenever player $O$'s last move was in $A$ or $C$, and according to $\tau$ whenever player $O$'s last move was in $B$ or $D$.
-
-We show that this does not in general give us a strategy for $(A\sequoid B)\implies (C\sequoid D)$.
-Suppose that $\sigma$ is such that player $P$'s response to some opening move in $C$ is another move in $C$ and suppose that $\tau$ is such that player $P$'s response to some opening move in $D$ is a move in $B$ (for example, $\tau$ is a copycat strategy).
-Then we end up with the following sequence of events in the game $(A\sequoid B)\implies(C\sequoid D)$  :
-\begin{enumerate}
-  \item Player $O$ starts with a move in $C$ (as he must).
-  \item Player $P$ responds according to $\sigma$ with another move in $C$.
-  \item Player $O$ decides to switch games and play a move in $D$.
-  \item Player $P$ responds according to $\tau$ with a move in $B$.
-\end{enumerate}
-
-But now player $P$'s last move is not a legal move in $(A\sequoid B)\implies(C\sequoid D)$, since no moves have been played in $A$ yet.
-
-We get round this problem by requiring that the strategy $\sigma$ be \emph{strict} -- that is, whatever player $O$'s opening move in $C$ is, player $P$'s reply must be a move in $A$.
-
-\begin{definition}
-  Let $N,L$ be negative games and let $\sigma$ be a strategy for $N\implies L$.  We say that $\sigma$ is \emph{strict} if player $P$'s reply to an opening move in $L$ is always a move in $N$.  
-\end{definition}
-
-Identity strategies are strict and the composition of two strict strategies is strict, so we get a full-on-objects subcategory $\G_s$ of $\G$ where the morphisms are strict strategies.
-Then the sequoid operator gives rise to a functor:
-\[
-  \blank\sequoid\blank\from \G_s\times\G\to\G_s
-  \]
+The sequoid does not give rise to a functor $\G\times\G\to \G$ in the way that the tensor product does: playing strategies $\sigma$ for $A\implies B$ and $\tau$ for $C \implies D$ in parallel does not necessarily give rise to a valid strategy for $(A\sequoid C)\implies (B \sequoid D)$, since player $O$ might end up playing in $C$ before anyone has played in $A$.
+However, if we require that the strategy $\sigma$ is \emph{strict} -- that is, player $P$'s reply to the opening move in $B$ is always a move in $A$ -- then we do get a valid strategy $\sigma\sequoid\tau$ for $(A\sequoid C)\implies (B\sequoid D)$ and, moreover, $\sigma\sequoid\tau$ is strict.
+If we write $\G_s$ for the category of games with \emph{strict} strategies as morphisms, then we see that $\blank\sequoid\blank$ gives us a functor $\G_s\times \G\to\G_s$.
+In fact, the isomorphism $\passoc$ tells us that this functor is a right monoidal category action of $\G$ upon $\G_s$.
 
@@
 
-We now have the motivation required to give the definition of a \emph{sequoidal category} from \cite{laird02}.
+We now formalize this into a category-theoretic definition.
 
@@
     \item A category $\C_s$
-    \item A right monoidal category action of $\C$ on the category $\C_s$.  That is, a functor
-      \[
-        \blank\sequoid\blank\from\C_s\times\C\to\C_s
-        \]
-      together with natural isomorphisms
-      \[
-        \passoc_{A,B,C}\from A\sequoid(B\tensor C)\to (A\sequoid B)\sequoid C
-        \]
-      and
-      \[
-        \run_A\from A\sequoid I\toisom A
-        \]
-      subject to the following coherence conditions:
-      \begin{equation*}
-        \begin{tikzcd}
-          A\sequoid(B\tensor(C\tensor D)) \arrow[r, "\passoc_{A,B,C\tensor D}" yshift=0.3em] \arrow[d, "\id_A\sequoid \assoc_{B,C,D}"']
-            & (A \sequoid B) \sequoid (C\tensor D) \arrow[r, "\passoc_{A\sequoid B,C,D}" yshift=0.3em]
-              & ((A\sequoid B)\sequoid C) \sequoid D \\
-          A\sequoid((B\tensor C)\tensor D) \arrow[r, "\passoc_{A,B\tensor C,D}"' yshift=-0.3em]
-            & (A\sequoid (B\tensor C)) \sequoid D \arrow[ur, "\passoc_{A,B,C}\sequoid\id_D"']
-              &
-        \end{tikzcd}
-      \end{equation*}
-      \begin{equation*}
-        \begin{tikzcd}
-          A \sequoid (I\tensor B) \arrow[r, "\passoc_{A,I,B}" yshift=0.3em] \arrow[d, "\id_A\sequoid\lunit_B"']
-            & (A\sequoid I)\sequoid B \arrow[dl, "\run_A\sequoid\id_B"] \\
-          A \sequoid B
-            &
-        \end{tikzcd}
-        \quad
-        \begin{tikzcd}
-          A \sequoid (B\tensor I) \arrow[r, "\passoc_{A,B,I}" yshift=0.3em] \arrow[d, "\id_A\sequoid\runit_B"']
-            & (A\sequoid B) \sequoid I \arrow[dl, "\run_{A\sequoid B}"] \\
-          A\sequoid B
-            &
-        \end{tikzcd}
-      \end{equation*}
+    \item A right monoidal category action of $\C$ on the category $\C_s$.
+That is, a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ that gives rise to a monoidal functor from $\C$ into the category of endofunctors on $\C_s$.
+We write $\passoc_{A,B,C}\from (A \sequoid B) \sequoid C \to A \sequoid (B\tensor C)$ for the coherence part of the monoidal functor.
 
@@
 
-%  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
  We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
@@
 
-The games model satisfies an analog of monoidal closedness:
-
-\begin{definition}
-  Let $\C=(\C,\C_s,J,\wk)$ be an inclusive sequoidal category.
-We say that $\C$ is a \emph{sequoidal closed category} if $\C$ is monoidal closed (with internal hom $\implies$ and currying $\Lambda_{A,B,C}\from \C(A\tensor B,C)\toisom \C(A,B\implies C)$) and if the map $f\mapsto\Lambda(\comp{f}{\wk})$ gives rise to a natural transformation
-  \[
-    \Lambda_{A,B,C,s}\from \C_s(A\sequoid B, C) \to \C_s(A,B\implies C)
-    \]
-\end{definition}
-
-It can be shown (see for example \cite{martinsthesis}) that our category $\G$ of games has all this structure.
-
-\begin{theorem}
-  Let $J$ be the inclusion functor $\G_s\to\G$.  If $A,B$ are games, let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
-  \[
-    (\G,\G_s,J,\wk)
-    \]
-  is an inclusive, Cartesian, decomposable, distributive sequoidal closed category.
-\end{theorem}
+The games model satisfies an analog of monoidal closedness, but we will not give that here (see \cite{laird02}).
+We see that $\G$ is a prototype example of a distributive, decomposable sequoidal category.
 
@@
 
-There are several ways to add exponentials to the basic category of games.  We shall use the definition based on countably many copies of the base game (see \cite{laird02}, for example):
-
-\begin{definition}
-  Let $A$ be a negative game.
-The \emph{exponential} of $A$ is the game $\oc A = (M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A})$, where $M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A}$ are defined as follows:
-  \begin{itemize}
-    \item $M_{\oc A} = M_A \times \omega$
-    \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$
-    \item $b_{\oc A} = O$
-    \item Given a sequence $s\in M_{\oc A}^\omega$, we write $s\vert_n$ for the largest sequence $a_1a_2\dots a_k\in M_A^*$ such that $(a_1,n),(a_2,n),\dots(a_k,n)$ is a subsequence of $s$.
-Then $P_{\oc A}$ is the set of all sequence $s\in M_{\oc A}^\omega$ that are alternating with respect to $\lambda_{\oc A}$, such that $s\vert_n\in P_A$ for all $n$ and such that if $m<n$ and $(a,n)$ occurs in $s$ then $(b,m)$ must occur earlier in $s$ for some move $b$: in other words, player $O$ can start infinitely many copies of the game $A$, but he must start them in order.
-  \end{itemize}
-\end{definition}
-
-This last condition on the order in which games may be opened is very important, as it allows us to define morphisms that give $\oc A$ the semantics of the exponential from linear logic.
-For example, we have a natural morphism $\mu\from\oc A\to\oc A\tensor\oc A$, given by the copycat strategy that starts a new copy of $A$ on the left whenever one is started on the right.
-Because of the condition on the order in which copies of $A$ may be started, there is a unique way to do this.
-
-\begin{proposition}
-  $\mu$ exhibits $\oc A$ as a comonoid in the monoidal category $(\G, \tensor, I)$.  
-\end{proposition}
-\begin{proof}
-  $\mu$ shall be the comultiplication in our comonoid.
-The counit is given by the empty strategy $\eta\from\oc A\to I$.
-We just need to check that $\mu$ is associative and that $\eta$ is a counit for $\mu$.
-
-  For associativity, we need to show that the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[rr, "\mu"] \arrow[d, "\mu"']
-        &
-          & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor\mu"] \\
-      \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}" yshift=0.2em]
-        & (\oc A \tensor \oc A) \tensor \oc A \arrow[r, "\assoc_{\oc A,\oc A,\oc A}"' yshift=-0.4em]
-          & \oc A \tensor (\oc A \tensor \oc A)
-    \end{tikzcd}
-    \]
-  This is easy to see when we notice that both branches of the square are copycat strategies on $\oc A\implies\oc A\tensor(\oc A\tensor \oc A)$; since copies of $A$ in $\oc A$ must be started in sequence, there is a unique such strategy, and so the square commutes.
-
-  For the counit, we need to show that the follosing two diagrams commute:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\mu"] \arrow[dr, "\runit_A\inv"']
-        & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \eta"] \\
-      %
-        & \oc A \tensor I
-    \end{tikzcd}
-    \quad\quad\quad
-    \begin{tikzcd}
-      \oc A \arrow[r, "\mu"] \arrow[dr, "\lunit_A\inv"']
-        & \oc A \tensor \oc A \arrow[d, "\eta\tensor\id_{\oc A}"] \\
-      %
-        & I \tensor \oc A
-    \end{tikzcd}
-    \]
-  Once again, these diagrams commute because both branches are copycat strategies for $\oc A\implies\oc A\tensor I$ or $\oc A\implies I\tensor\oc A$ and there is a unique such strategy in each case.
-\end{proof}
-
-We shall later show that $(\oc A, \mu, \eta)$ is in fact the \emph{cofree commutative comonoid} on $A$ in the monoidal category $(\G, \tensor, I)$.
-
-We shall call the exponential $\oc A$ the \emph{sequoidal exponential}.  The following proposition explains the name:
-
-\begin{proposition}
-  Let $A$ be a negative game.  Then we get an endofunctor $A\sequoid\blank$ on $\G$ given by sending $B$ to $A\sequoid B$.
-
-  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha_A\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.
-In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
+There are several ways to add exponentials to the basic category of games.
+We shall use the definition based on countably many copies of the base game (see \cite{hyland1997games}, for example): the exponential $\oc A$ of $A$ is the game in which player $O$ may switch between countably many copies of $A$ -- $A_0, A_1, A_2, \dots$, as long as he starts them in order, starting with $A_0$, then opening $A_1$ and so on.
+This condition on the order in which games may be opened is very important, as it allows us to define the exponential morphisms $\oc A \to \oc A \tensor \oc A$ and $\oc A \to \oc \oc A$.
+In the first case, it can be proved \cite{LairdCofCommCom} that the comultiplication $\oc A \to \oc A \tensor \oc A$ exhibits $\oc A$ as the \emph{cofree commutative comonoid} on $A$, which shows that $A$ is a suitable model for the exponential \cite{LafontCofCommCom}.
+
+Even more interestingly, we see that we may characterize $\oc A$ as the \emph{final coalgebra} for the functor $A\sequoid\blank$.
+That is, given a coalgebra from $\sequoid\blank$ -- a game $B$ and a morphism $\sigma\from B \to A \sequoid B$ -- we get a unique morphism $\fcoal{\sigma}$ making the following diagram commute:
 \[
@@
 We call $\fcoal{\sigma}$ the \emph{anamorphism} of $\sigma$.
-\end{proposition}
-\begin{proof}
-  See \cite{martinsthesis}.  We shall shortly give a proof in the more general case.
-\end{proof}
-
-We shall use the following standard pieces of theory about final coalgebras.  
+
+We shall use the following standard pieces of theory about final coalgebras:
 \begin{description}
@@
 In the general case, we deduce that $\alpha_A$ is a morphism in $\C_s$.
-  \item[Final Sequence] We may construct a transfinite sequence of objects and morphisms between them (in other words, a functor $\Ord\to\G$, where $\Ord$ is the category of ordinals and prefix inclusions:
-    \[
-      \begin{tikzcd}
-        1
-          & A \arrow[l, "*"']
-            & A \sequoid A \arrow[l, "\id\sequoid *"']
-              & A \sequoid (A \sequoid A) \arrow[l, "\id\sequoid(\id\sequoid*)"']
-                & \cdots \arrow[l] \\
-        A^{\sequoid\omega} \arrow[u] \arrow[ur] \arrow[urr] \arrow[urrr] \arrow[phantom, urrrr, "\cdots" xshift=0.6em]
-          & A \sequoid A^{\sequoid\omega} \arrow[l]
-            & A \sequoid (A \sequoid A^{\sequoid\omega}) \arrow[l]
-              & A \sequoid (A \sequoid (A \sequoid A^{\sequoid\omega})) \arrow[l]
-                & \cdots \arrow[l] \\[-24pt]
-        \vdots
-          & \vdots
-            & \vdots
-              & \vdots
-                &
-      \end{tikzcd}
-      \]
-    Here, $A^{\sequoid\omega}$ is the categorical limit of the top line and the morphisms into the top line are the morphisms in the limiting cone.
-The morphism from $A\sequoid A^{\sequoid\omega}$ to $A^{\sequoid\omega}$ is constructed as follows: apply the functor $A\sequoid\blank$ to the limiting cone from $A^{\sequoid\omega}$, giving us a cone from $A\sequoid A^{\sequoid\omega}$ over the top line.
-The desired morphism is now the unique morphism $A\sequoid A^{\sequoid\omega}\to A^{\sequoid\omega}$ that induces a morphism of cones.
-We may continue in this way to build up $A^{\sequoid\gamma}$ for all ordinals $\gamma$, where $A^{\sequoid(\gamma+1)}=A\sequoid A^{\sequoid\gamma}$ and $A^{\sequoid\mu}$ is the limit over the $A^{\sequoid\gamma}$ for $\gamma<\mu$ if $\mu$ is a limit ordinal.
-
-    If the morphism $j_{\gamma}^{\gamma+1}\from A\sequoid A^{\sequoid\gamma}\to A^{\sequoid\gamma}$ is an isomorphism for some $\gamma$, then we say that the final sequence \emph{stabilizes at $\gamma$}.
-In this case, ${j_{\gamma}^{\gamma+1}}\inv\from A^{\sequoid\gamma}\to A\sequoid A^{\sequoid\gamma}$ is the final coalgebra for the functor $A\sequoid\blank$ \cite{finalseq}.
-
-    The same is true for any endofunctor on any category with a terminal object and enough limits.
+  \item[Final Sequence] If $\C$ is a category with enough limits and $F$ is an endofunctor on $\C$, we may build up an ordinal indexed sequence of objects and morphisms of $\C$ (that is, a functor $\oppcat{\Ord}\to\C$, where $\Ord$ is the category of ordinals and prefix inclusions:
+    \[
+      1 \leftarrow F(1) \leftarrow F^2(1) \leftarrow \cdots F^\omega(1) \leftarrow F^{\omega+1}(1) \leftarrow \cdots
+      \]
+    (by repeatedly applying $F$ and taking limits).
+If this sequence stabilizes for any $\delta$ (i.e., if the morphism from $F^{\delta+1}(1)\to F^\delta(1)$ is an isomorphism), then $F^\delta(1)$ is the final coalgebra for $F$ \cite{finalseq}.
 \end{description}
@@
 
-We may use anamorphisms to construct (history-sensitive) strategies corresponding to stateful programs in an entirely coalgebraic way.
-
-Let $\Sigma$ be the game
-\[
-  (\{q,a\},\{q\mapsto O,a\mapsto P\},O,\{\emptyplay,q,qa\})
-  \]
-and let $\bN$ be the game
-\[
-  \{q\}\cup\bN,\{q\mapsto O,\;n\mapsto P\},O,\{\emptyplay,q\}\cup\{qn\suchthat n\in\bN\})
-  \]
-That is, $\Sigma$ is the game where player $O$ makes the move $q$ and player $P$ must then reply with the move $a$, while $\bN$ is the game where player $O$ plays the move $q$ and then player $P$ must choose a natural number $n$ to play.
-We model a simple stateful program as a history sensitive strategy on $\oc(\Sigma\times\bN)$: the program interface will consist of a button that can be pressed, and a display that can be activated to display the number of times that the button has been pressed.
-As a strategy on $\oc(\Sigma\times\bN)$, whenever player $O$ plays $q$ in $\Sigma$, player $P$ responds with the move $a$.
-Whenever he plays $q$ in $\bN$, she responds with the number of times we have played in $\Sigma$ so far.
-
-We can construct this strategy using nothing more than the sequoidal structure on $\G$ that we have described and some very basic strategies on the games $\bN$ and $\Sigma$; namely:
-\begin{gather*}
-  \OK \from I \to \Sigma \\
-  \succ \from \bN \to \bN \\
-  \zero \from I \to \bN
-\end{gather*}
-Here, $\OK$ is the strategy that replies $a$ to player $O$'s initial move $q$, $\zero$ is the strategy that replies $0$ to player $O$'s initial move $q$ and $\succ$ is the strategy that queries its argument and then returns the number one greater (so maximal plays in $\succ$ are of the form $qqn(n+1)$ for $n\in\bN$).
-
-We first define a morphism $\mathtt{press}$ from $\oc \bN$ to $\Sigma\sequoid\oc \bN$ as the composite:
-\[
-  \begin{tikzcd}
-    \oc\bN \arrow[r, "\lunit"]
-      & I \tensor \oc \bN \arrow[r, "\OK\tensor\oc\succ"]
-        &[24pt] \Sigma\tensor\oc\bN \arrow[r, "\wk"]
-          & \Sigma \sequoid \oc \bN
-  \end{tikzcd}
-  \]
-In this strategy, the player responds to the initial move $q$ in $\Sigma$ with $a$; from then on, she copies from the $\oc\bN$ to $\oc\bN$, increasing each argument by $1$ before playing it on the right.
-This strategy models the effect of a single button press.
-
-We now define a morphism from $\oc\bN$ to $(\bN\times\Sigma)\sequoid\oc \bN$ by the composite:
-\[
-  \begin{tikzcd}
-    \oc \bN \arrow[r, "\Delta"]
-      & \oc \bN \times \oc \bN \arrow[r, "\alpha\times\mathtt{press}"]
-        &[20pt] \bN \sequoid \oc \bN \;\times\; \Sigma \sequoid \oc \bN \arrow[r, "\dist\inv"]
-          &[12pt] (\bN \times \Sigma) \sequoid \oc \bN
-  \end{tikzcd}
-  \]
-In this strategy, if player $O$ starts with a move in $\bN$, then player $P$ copies plays in $\oc \bN$ on the left and copies over the response.
-From then on, she continues to copy numbers from the left over to the right.
-If player $O$ starts by playing in $\Sigma$, then player $P$ responds with the move $a$.
-From then on, she copies numbers from the left over to the right, but now she increases the numbers by $1$ each time.
-
-This strategy represents a single user interaction (either pressing the button or checking how many times it has been pressed), together with the change of state (represented by the game $\oc \bN$) that takes place after that interaction has taken place.
-We now take the anamorphism of this strategy, giving us a unique morphism $\mathtt{count}$ from $\oc \bN$ to $\oc (\bN\times\Sigma)$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    \oc \bN \arrow[r, "\Delta"] \arrow[d, "\mathtt{count}"']
-      & \oc \bN \times \oc \bN \arrow[r, "\alpha\times\mathtt{press}"]
-        &[20pt] \bN \sequoid \oc \bN \;\times\; \Sigma \sequoid \oc \bN \arrow[r, "\dist\inv"]
-          &[12pt] (\bN \times \Sigma) \sequoid \oc \bN \arrow[d, "\id\sequoid\mathtt{count}"] \\
-    \oc (\bN\times\Sigma) \arrow[rrr, "\alpha"]
-      &
-        &
-          & (\bN \times \Sigma) \sequoid \oc (\bN \times \Sigma)
-  \end{tikzcd}
-  \]
-In the strategy $\mathtt{count}$, if player $O$ plays $q$ in a copy of $\Sigma$, then player $P$ responds with $a$ and adds $1$ to an (invisible) counter variable.
-If player $O$ plays $q$ in a copy of $\bN$, then player $P$ queries the argument on the left and returns that value, plus her count, on the right.
-If we now substitute in the initial value of the state by forming the composite $\comp{\mathtt{count}}{\oc\zero}$, then we end up with the desired behaviour.
-
-A more consequential example is the construction of a strategy representing a storage cell.
+We now show how we can use the characterization of $\oc A$ as a final coalgebra to define a strategy representing a simple storage cell.
 This is the strategy $\cell$ for $\oc(\Var[X])$ that is used in \cite{SamsonGuyIAPassive} to construct the denotation of the $\mathtt{new}$ term from Idealized Algol.
@@
 
+Let $\Sigma$ be the game with maximal play $qa$ and let $\OK$ be the obvious strategy on $\Sigma$.
+$\Sigma$ denotes the type $\texttt{com}$ of commands.
 Let $(X,*)$ be a pointed set and write $X$ for the game with maximal plays $qx$ for $x\in X$.
-Recall that in Idealized Algol we represent $\Var[X]$, the type of variables taking values in $X$, by the game $\Sigma^X\times X$, where $\Sigma$ denotes the command type $\mathtt{com}$ and $\Sigma^X$ is the $X$-fold product of $\Sigma$ with itself.
+Recall that in Idealized Algol we represent $\Var[X]$, the type of variables taking values in $X$, by the game $\Sigma^X\times X$, where $\Sigma^X$ is the $X$-fold product of $\Sigma$ with itself.
 Here, $\Sigma^X$ represents the act of writing a value into the storage cell (so playing in $\Sigma_x$ means writing the value $x$), while the copy of $X$ represents reading a value from the storage cell.
@@
 
-\begin{exercise}
-  Let $(X,*)$ be a pointed set, where $*$ is a designated error element, and write $X$ for the game with maximal plays $qx$ for $x\in X$.
-Consider a history-sensitive strategy on $\oc(\Sigma^X\times X)$ representing a simple stack with $\mathtt{push(x)}$ and $\mathtt{pop()}$ methods.
-The $\mathtt{push(x)}$ method should add an element $x\in X$ on to the stack, while the $\mathtt{pop()}$ method should return the top element of the stack, removing it from the stack in the process, or return $*$ if the stack is empty.
-Show that this strategy may be constructed from the strategy $\OK$ on $\Sigma$ and the strategies $c_x$ on $X$, using only the sequoidal structure of $\G$.
-
-  Consider how we might add a $\mathtt{size()}$ method, of type $\bN$, to this stack, returning the number of elements currently on the stack.
-\end{exercise}
+A similar method may be used to construct a simple stack \cite{martinsthesis}.
 
@@
   $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
-Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
+Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
 \end{proposition}
+\begin{proof}
+  See Appendix.
+\end{proof}
 
@@
 \end{theorem}
-
-We give a broad outline of the proofs of the results in this section in the Appendix.
 
@@
 
-We give a brief summary of the construction of the category of transfinite games.  Some more details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
+We give a brief summary of the construction of the category of transfinite games.  %Some more details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
 
@@
 \end{proposition}
+\begin{proof}
+  Left as an exercise.  
+\end{proof}
 
@@
 
+%%
+%% Bibliography
+%%
+
+%% Either use bibtex (recommended),
+
+\bibliography{bibliography}
+
+%% .. or use the thebibliography environment explicitely
+
+\pagebreak
+
 \appendix
@@
   $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
-Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
+Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
 \end{proposition}
@@
   \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\assoc_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id_{\oc C}"]
-      & \oc A \tensor (\oc B \tensor \oc C) \arrow[d, "\id_{\oc A}\tensor\int_{B,C}"] \\
-    \oc (A \times B) \tensor \oc C \arrow[d, "\int_{A\times B,C}"]
+    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\assoc_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id_{\oc C}"']
+      &[24pt] \oc A \tensor (\oc B \tensor \oc C) \arrow[d, "\id_{\oc A}\tensor\int_{B,C}"] \\
+    \oc (A \times B) \tensor \oc C \arrow[d, "\int_{A\times B,C}"']
       & \oc A \tensor \oc(B \times C) \arrow[d, "\int_{A,B\times C}"] \\
-    \oc ((A \times B) \times C) \arrow[r, "\oc\assoc_{\times,A,B,C}"]
+    \oc ((A \times B) \times C) \arrow[r, "\oc\assoc_{\times,A,B,C}"']
       & \oc (A \times (B \times C))
+  \end{tikzcd}
+\]
+\[
+  \begin{tikzcd}
+    I \tensor \oc A \arrow[r, "\varepsilon\tensor\id"]
+      & \oc 1 \tensor \oc A \arrow[d, "\int_{1,A}"] \\
+    \oc A \arrow[u, "\lunit_{\oc A}"] \arrow[r, "\oc\lunit_A"]
+      & \oc (1 \times A)
+  \end{tikzcd}\quad
+  \begin{tikzcd}
+    \oc A \tensor I \arrow[r, "\id\tensor\varepsilon"]
+      & \oc A \tensor \oc 1 \arrow[d, "\int_{A,1}"] \\
+    \oc A \arrow[r, "\oc\runit_A"] \arrow[u, "\runit_{\oc A}"]
+      & \oc (A \times 1)
+  \end{tikzcd}\quad
+  \begin{tikzcd}
+    \oc A \tensor \oc B \arrow[r, "\sym_{A,B}"] \arrow[d, "\int_{A,B}"']
+      & \oc B \tensor \oc A \arrow[d, "\int_{B,A}"] \\
+    \oc(A\times B) \arrow[r, "\oc\sym_{A,B}"]
+      & \oc(B\times A)
   \end{tikzcd}
@@
 Indeed, it may be easily verified that the following diagram commutes, using the definition of $\int_{A,B}$ as the anamorphism for $\comp{\dist\inv}{\kappa_{A,B}}$ and the fact that $\wk$, $\passoc$ and $\sym$ are natural transformations:
-  \[
-    \begin{tikzcd}
-      ((\oc A \tensor \oc B) \tensor \oc C) \arrow[r, "\eta_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id"']
+\begin{equation}\label{kreuz}
+  \begin{tikzcd}
+    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\eta_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id"']
       & ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \arrow[d, "(\id\sequoid(\int\tensor\id))\times (\id\sequoid(\int\tensor\id))"] \\
     \oc (A \times B) \tensor \oc C \arrow[r, "\kappa_{A\times B,C}"]
-        & ((A \times B) \sequoid (\oc (A \times B))) \times (C \sequoid (\oc (A \times B) \tensor \oc C))
-    \end{tikzcd}
-    \]
-
-\begin{lemma}\label{assocCoherenceBigCommutes}
-  The diagrams in Figure \ref{assocCoherenceBig} commute.
-\end{lemma}
-\begin{proof}
-  First, observe the diagram in Figure \ref{ThisWorksForA}.  Setting, $X=A$, $Y=B$ and $Z=C$, this gives us diagram \eqref{Aexpansion} immediately.
-\end{proof}
+      & ((A \times B) \sequoid (\oc (A \times B) \tensor \oc C)) \times (C \sequoid (\oc (A \times B) \tensor \oc C))
+  \end{tikzcd}\tag{\kreuz}
+\end{equation}
+Then we get the commutative diagram in Figure \ref{CoherenceOneWay}, which tells us that one of the two paths round the coherence diagram is the anamorphism of $\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}$.
+We now show that the other path round the coherence diagram is the anamorphism of the same thing, which will prove that they are equal.
 
 \begin{SidewaysFigure}
-  \begin{equation}\label{Aexpansion}
+  \[
     \begin{tikzcd}[ampersand replacement=\&]
-      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "(\alpha_A\tensor\id)\tensor\id" yshift=0.4em] \arrow[d, "\assoc"']
-        \& ((A \sequoid \oc A) \tensor \oc B) \tensor \oc C \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift=0.4em]
-          \& (A \sequoid (\oc A \tensor \oc B)) \tensor \oc C \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
-            \& A \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
-      \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\alpha_A\tensor\id"]
-        \& (A \sequoid \oc A) \tensor (\oc B \tensor \oc C) \arrow[r, "\wk"]
-            \& (A \sequoid \oc A) \sequoid (\oc B \tensor \oc C) \arrow[r, "\passoc\inv"]
-                \& A \sequoid (\oc A \tensor (\oc B \tensor \oc C))
-    \end{tikzcd}\tag{\textbf{A}}
-  \end{equation}\vspace{24pt}
-  \begin{equation}\label{Bexpansion}
-    \begin{tikzcd}[row sep=36pt, column sep=12pt, cramped, ampersand replacement=\&]
-      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\sym" yshift=0.4em] \arrow[d, "\assoc"']
-        \& (\oc B \tensor \oc A) \tensor \oc C \arrow[r, "(\alpha_B\tensor\id)\tensor\id" yshift=0.4em]
-          \& ((B \sequoid \oc B) \tensor \oc A) \tensor \oc C \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift = 0.4em]
-            \& (B \sequoid (\oc B \tensor \oc A)) \tensor \oc C \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
-              \& B \sequoid ((\oc B \tensor \oc A) \tensor \oc C) \arrow[r, "\id\sequoid(\sym\tensor\id)" yshift=0.4em]
-                \& B \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
-      \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\sym" yshift=0.4em]
-        \& (\oc B \tensor \oc C) \tensor \oc A \arrow[r, "(\alpha_B\tensor\id)\tensor\id" yshift=0.4em]
-          \& ((B \sequoid \oc B) \tensor \oc C) \tensor \oc A \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift=0.4em]
-            \& (B \sequoid (\oc B \tensor \oc C)) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
-              \& B \sequoid ((\oc B \tensor \oc C) \tensor \oc A) \arrow[r, "\id\sequoid\sym" yshift=0.4em]
-                \& B \sequoid (\oc A \tensor (\oc B \tensor \oc C))
-    \end{tikzcd}\tag{\textbf{B}}
-  \end{equation}\vspace{36pt}
-  \begin{equation}\label{Cexpansion}
-    \begin{tikzcd}[row sep=36pt, column sep=12pt, cramped, ampersand replacement=\&]
-      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\sym" yshift=0.4em] \arrow[d, "\assoc"']
-        \& \oc C \tensor (\oc A \tensor \oc B) \arrow[r, "\alpha_C\tensor\id" yshift=0.4em]
-          \& (C \sequoid \oc C) \tensor (\oc A \tensor \oc B) \arrow[r, "\wk" yshift=0.4em]
-            \& (C \sequoid \oc C) \sequoid (\oc A \tensor \oc B) \arrow[r, "\passoc\inv" yshift=0.4em]
-              \& C \sequoid (\oc C \tensor (\oc A \tensor \oc B)) \arrow[r, "\id\sequoid\sym" yshift=0.4em]
-                \& C \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
-      \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\comp{(\sym\tensor\id)}{\sym}" yshift=0.4em]
-        \& (\oc C \tensor \oc B) \tensor \oc A \arrow[r, "(\alpha_C\tensor\id)\tensor\id" yshift=0.4em]
-          \& ((C \sequoid \oc C) \tensor \oc B) \tensor \oc A \arrow[r, "(\comp{\passoc\inv}{\wk})\tensor\id" yshift=0.4em]
-            \& (C \sequoid (\oc C \tensor \oc B)) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
-              \& C \sequoid ((\oc C \tensor \oc B) \tensor \oc A) \arrow[r, "\id\sequoid(\comp{(\sym\tensor\id)}{\sym})" yshift=0.4em]
-                \& C \sequoid (\oc A \tensor (\oc B \tensor \oc C))
-    \end{tikzcd}\tag{\textbf{C}}
-  \end{equation}\vspace{24pt}
-  \caption{Lemma \ref{assocCoherenceBigCommutes} asserts that these diagrams commute.}\label{assocCoherenceBig}
+      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\eta_{A,B,C}}"] \arrow[d, "\int_{A,B}\tensor\id"'] \arrow[phantom, dr, "\textbf{a}"]
+        \&[24pt] ((A \times B) \times C) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid(\int\tensor\id)"] \arrow[phantom, dr, "\textbf{b}"]
+          \&[19pt] (A \times (B\times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid(\int\tensor\id)"] \\
+      \oc (A \times B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\kappa_{A\times B,C}}"] \arrow[d, "\int_{A\times B,C}"'] \arrow[phantom, dr, "\textbf{d}"]
+        \& ((A \times B) \times C) \sequoid (\oc(A\times B)\tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid\int"] \arrow[phantom, dr, "\textbf{c}"]
+          \& (A \times (B\times C)) \sequoid (\oc(A\times B)\tensor\oc C) \arrow[d, "\id\sequoid\int"] \\
+      \oc((A\times B)\times C) \arrow[r, "\alpha_{(A\times B)\times C}"] \arrow[d, "\oc \assoc_\times"'] \arrow[phantom, drr, "\textbf{e}"]
+        \& ((A\times B) \times C) \sequoid \oc ((A\times B)\times C) \arrow[r, "\assoc_\times\sequoid\id"]
+          \& (A \times (B\times C)) \sequoid \oc (A \times(B \times C)) \arrow[d, "\id\sequoid\oc \assoc_\times"] \\
+      \oc(A \times (B\times C)) \arrow[rr, "\alpha_{A\times(B\times C)}"]
+        \&
+          \& (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
+    \end{tikzcd}
+    \]
+  \caption{\textbf{a} commutes by Diagram \eqref{kreuz}, plus the fact that $\dist$ is a natural transformation.  \\[\baselineskip]
+  \textbf{b} and \textbf{c} commute because $\assoc_\times$ is a natural transformation.  \\[\baselineskip]
+  \textbf{d} commutes by the definition of $\int_{A\times B,C}$.  \\[\baselineskip]
+  \textbf{e} commutes by Lemma \ref{ocStrict}.}\label{CoherenceOneWay}
 \end{SidewaysFigure}
 
+For this, we define a composite $\tilde{\eta}_{A,B,C}$:
+\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
+\begin{gather*}
+  \oc A \tensor (\oc B \tensor \oc C) \constantwidthxrightarrow{\langle\sym,\id\rangle} (\oc A \tensor (\oc B \tensor \oc C)) \times ((\oc B \tensor \oc C) \tensor \oc A) \\
+  \hspace{6pt}\cdots \constantwidthxrightarrow{(\alpha_A\tensor\id)\times((\comp{\dist\inv}{\kappa_{B,C}})\tensor\id)} ((A \sequoid \oc A) \tensor (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \tensor \oc A) \\
+  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} ((A \sequoid \oc A) \sequoid (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \sequoid \oc A) \\
+  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid ((\oc B \tensor \oc C) \tensor \oc A)) \\
+  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid (A \tensor (\oc B \tensor \oc C))) \\
+\end{gather*}
+
+We get a commutative diagram:
+\[
+  \begin{tikzcd}
+    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}"] \arrow[d, "\assoc_{A,B,C}"']
+      &[78pt] (A \times (B \times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
+    \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\tilde{\eta}_{A,B,C}}}"] \arrow[d, "\id\tensor\int"']
+      & (A \times (B \times C)) \sequoid (\oc A \tensor (\oc B \tensor \oc C)) \arrow[d, "\id\sequoid(\id\tensor\int)"] \\
+    \oc A \tensor \oc(B \times C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\kappa_{A,B\times C}}}"] \arrow[d, "\int_{A,B\times C}"']
+      & (A \times (B \times C)) \sequoid (\oc A \tensor \oc (B\times C)) \arrow[d, "\id\sequoid\int"] \\
+    \oc (A \times (B \times C)) \arrow[r, "\alpha_{A\times(B\times C)}"]
+      & (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
+  \end{tikzcd}
+  \]
+
+Commutativity of the top square is a long and fairly unenlightening exercise in the coherence conditions for symmetric monoidal categories and for sequoidal categories.
+Commutativity of the middle and bottom squares are by similar arguments to the ones in Figure \ref{CoherenceOneWay}.
+Therefore, the two branches of the coherence diagram are anamorphisms for the same thing, and so they are equal.
+
+The proofs for the other three coherence diagrams are similar.
+
+\subsection{Proof of Proposition \ref{itsMu}}
+
+\begingroup
+\def\thetheorem{\ref{itsMu}}
+\begin{proposition}
+  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ has comultiplication given by $\mu_A\from\oc A \to \oc A\tensor\oc A$ and counit given by the unique morphism $\eta_A\from \oc A \to I$.
+\end{proposition}
+\addtocounter{theorem}{-1}
+\endgroup
+
+By the definition of $\CCom$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite:
+\[
+  \oc A \xrightarrow{\oc\Delta} \oc (A \times A) \xrightarrow{\int_{A,A}\inv} \oc A \times \oc A
+  \]
+By Lemma \ref{ocStrict}, the morphism $\oc\Delta$ is equal to the morphism $\sigma_A$ defined above.  So this composite is equal to $\comp{\int_{A,A}}{\sigma_A}=\mu_A$.
+
+The counit is a morphism $\oc A\to I$, so by uniqueness it must be equal to $\eta_A$.
+
+\subsection{Proof of Theorem \ref{Coalgebra__CoCoCo}}
+
+\begingroup
+\def\thetheorem{\ref{Coalgebra__CoCoCo}}
+\begin{theorem}
+  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.
+Let $A$ be an object of $\C$ (equivalently, of $\C_s$).
+Then $\oc A$, together with the comultiplication $\mu_A$ and counit $\eta_A$, is the cofree commutative comonoid over $A$.
+\end{theorem}
+\addtocounter{theorem}{-1}
+\endgroup
+
+We know from Proposition \ref{itsMu} that the $(\oc A,\mu_A,\eta_A)$ is indeed a commutative comonoid.
+Now let $\delta\from B\to B\tensor B$ be a commutative comonoid in $\C$ and let $f\from B\to A$ be a morphism.
+We need to show that there is a unique morphism $f^\dag\from B \to \oc A$ such that the following diagram commutes:
+\[
+  \begin{tikzcd}
+    %
+      & B \arrow[r, "\delta"] \arrow[d, "f^\dag"] \arrow[dl, "f"']
+        & B \tensor B \arrow[d, "f^\dag\tensor f^\dag"] \\
+    A
+      & \oc A \arrow[l, "\der_A"] \arrow[r, "\mu_A"]
+        & \oc A \tensor \oc A
+  \end{tikzcd}
+  \]
+We define the morphism $f^\dag$ to be the anamorphism of the composite:
+\[
+  B \xrightarrow{\delta} B \tensor B \xrightarrow{f\tensor\id B} A \tensor B \xrightarrow{\wk_{A,B}} A \sequoid B
+  \]
+We first claim that it makes the given diagram commute, starting with the square on the left.
+We show that $\comp{\int_{A,A}}{\comp{\mu_A}{f^\dag}}=\comp{\int_{A,A}}{\comp{(f^\dag\tensor f^\dag)}{\delta}}\from B \to \oc (A\times A)$, by showing that both morphisms are anamorphisms for the composite
+\[
+  B \xrightarrow{\delta} B \tensor B \xrightarrow{f\tensor\id_B} A \tensor B \xrightarrow{\wk_{A,B}} A \sequoid B \xrightarrow{\Delta} (A \sequoid B) \times (A \sequoid B) \xrightarrow{\dist_{A,B}\inv} (A \times A) \sequoid B
+  \]
+Since $\int_{A,A}$ is an isomorphism, this will prove that the square on the right commutes.
+
+For the first case, the diagram in Figure \ref{transferReportDiagram1} proves that $\comp{\int_{A,A}}{\comp{\mu_A}{f^\dag}}=\comp{\sigma_A}{f^\dag}$ is the anamorphisms for that composite.
+For the other case, taking the product of the diagrams in Figure \ref{transferReportDiagram2} gives rise to the diagram in Figure \ref{transferReportDiagram3}, which proves that $\comp{\int_{A,A}}{\comp{(f^\dag\tensor f^\dag)}{\delta}}$ is the anamorphism for the same composite, which completes the proof that the right hand square commutes.
 \begin{SidewaysFigure}
   \[
-    \begin{tikzcd}[row sep=36pt, cramped, ampersand replacement=\&]
-      (\oc X \tensor \oc Y) \tensor \oc Z \arrow[r, "(\alpha\tensor\id)\tensor\id" yshift=0.4em] \arrow[dd, "\assoc"']
-      \arrow[phantom, ddr, "\textbf{a}"]
-        \& ((X \sequoid \oc X) \tensor \oc Y) \tensor \oc Z \arrow[r, "\wk\tensor\id" yshift=0.4em] \arrow[dd, "\assoc"']
-      \arrow[phantom, ddr, "\textbf{c}"]
-          \& ((X \sequoid \oc X) \sequoid \oc Y) \tensor \oc Z \arrow[r, "\passoc\inv\tensor\id" yshift=0.4em] \arrow[d, "\wk"']
-      \arrow[phantom, dr, "\textbf{b}"]
-            \& (X \sequoid (\oc X \tensor \oc Y)) \tensor \oc Z \arrow[d, "\wk"]
+    \begin{tikzcd}[cramped, ampersand replacement=\&]
+      B \arrow[r, "\delta"] \arrow[d, "f^\dag"'] \arrow[phantom, drrr, "\textbf{a}"]
+        \& B \tensor B \arrow[r, "f\tensor\id_B"]
+          \& A \tensor B \arrow[r, "\wk_{A,B}"]
+            \& A \sequoid B \arrow[r, "\Delta"] \arrow[d, "\id\sequoid f^\dag"] \arrow[phantom, dr, "\textbf{b}" xshift=0.6em]
+              \& (A \sequoid B) \times (A \sequoid B) \arrow[r, "\dist_{A,B}\inv"] \arrow[d, "(\id\sequoid f^\dag)\times(\id\sequoid f^\dag)"] \arrow[phantom, dr, "\textbf{c}" xshift=2.0em]
+                \& (A \times A) \sequoid B \arrow[d, "\id\sequoid f^\dag"] \\
+      \oc A \arrow[rrr, "\alpha_A"] \arrow[d, "\sigma_A"'] \arrow[phantom, drrrrr, "\textbf{d}"]
+        \&
+          \&
+            \& A \sequoid \oc A \arrow[r, "\Delta"]
+              \& (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[r, "\dist_{A,\oc A}\inv"]
+                \& (A \times A) \sequoid \oc A \arrow[d, "\id\sequoid\sigma_A"] \\
+      \oc (A\times A) \arrow[rrrrr, "\alpha_{A\times A}"]
+        \&
+          \&
+            \&
+              \&
+                \& (A \times A) \sequoid \oc (A\times A)
+    \end{tikzcd}
+    \]
+  \caption{\textbf{a} commutes by the definition of $f^\dag$.\\[\baselineskip]
+    \textbf{b} commutes because $\Delta$ is a natural transformation.  \textbf{c} commutes because $\dist$ is a natural transformation. \\[\baselineskip]
+    \textbf{d} commutes be the definition of $\sigma_A$.
+  }\label{transferReportDiagram1}
+\end{SidewaysFigure}
+
+\begin{SidewaysFigure}
+  \[
+    \begin{tikzcd}[ampersand replacement=\&]
+      B \arrow[r, "\delta"] \arrow[dd, "\delta"'] \arrow[ddr, phantom, "\textbf{a}"]
+        \& B\tensor B \arrow[r, "f\tensor \id_B"] \arrow[d, "\id_B\tensor\delta"]
+          \& A \tensor B \arrow[rrr, "\wk"] \arrow[d, "\id_A\tensor\delta"] \arrow[drrr, phantom, "\textbf{b}"]
+            \&
+              \&
+                \& A\sequoid B \arrow[d, "\id_A\sequoid\delta"] \\
+      %
+        \& B \tensor(B\tensor B) \arrow[r, "f\tensor\id_{B\tensor B}"] \arrow[d, "{\assoc_{B,B,B}\inv}"] \arrow[phantom, dr, "\textbf{d}" xshift=0.3em]
+          \& A \tensor (B \tensor B) \arrow[rrr, "\wk"] \arrow[drr, phantom, "\textbf{g}"] \arrow[d, "\assoc_{A,B,B}\inv"]
+            \&
+              \&
+                \& A \sequoid (B\tensor B) \arrow[dd, "\id_A\sequoid(f^\dagger \tensor f^\dagger)"] \arrow[dl, "{\passoc_{A,B,B}}"] \arrow[ddl, phantom, "\textbf{e}"] \\
+      B \tensor B \arrow[r, "\delta\tensor \id_B"] \arrow[d, "f^\dagger \tensor f^\dagger"'] \arrow[drrr, phantom, "\textbf{f}" yshift=-0.3em]
+        \& (B \tensor B) \tensor B \arrow[r, "(f\tensor\id_B)\tensor\id_B"' yshift=-0.3em]
+          \& (A \tensor B) \tensor B \arrow[r, "\wk\tensor\id_B"]
+            \& (A \sequoid B) \tensor B \arrow[r, "\wk"] \arrow[d, "(\id\sequoid f^\dagger)\tensor f^\dagger"'] \arrow[dr, phantom, "\textbf{c}"]
+              \& (A\sequoid B)\sequoid B \arrow[d, "(\id\sequoid f^\dagger)\sequoid f^\dagger"]
                 \& \\
+      \oc A \tensor \oc A \arrow[rrr, "\alpha\tensor\id_{\oc A}"']
+        \&
+          \&
+            \& (A \sequoid \oc A)\tensor \oc A \arrow[r, "\wk"]
+              \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
+                \& A \sequoid (\oc A \tensor \oc A)
+    \end{tikzcd}
+  \]
+\[
+  \begin{tikzcd}[ampersand replacement=\&]
     %
-        \&
-          \& ((X \sequoid \oc X) \sequoid \oc Y) \sequoid \oc Z \arrow[r, "\passoc\inv\sequoid\id" yshift=0.4em] \arrow[d, "\passoc\inv"]
-      \arrow[phantom, drr, "\textbf{d}"]
-            \& (X \sequoid (\oc X \tensor \oc Y)) \sequoid \oc Z \arrow[r, "\passoc\inv" yshift=0.4em]
-              \& X \sequoid ((\oc X \tensor \oc Y) \tensor \oc Z) \arrow[d, "\id\sequoid\assoc"] \\
-      \oc X \tensor (\oc Y \tensor \oc Z) \arrow[r, "\alpha_X\tensor\id"]
-        \& (X \sequoid \oc X) \tensor (\oc Y \tensor \oc Z) \arrow[r, "\wk"]
-          \& (X \sequoid \oc X) \sequoid (\oc Y \tensor \oc Z) \arrow[rr, "\passoc\inv"]
-            \& 
-              \& X \sequoid (\oc X \tensor (\oc Y \tensor \oc Z)
-    \end{tikzcd}
-    \]
-  \caption{
-    \textbf{a} commutes because $\assoc$ is a natural transformation.  \textbf{b} commutes because $\wk$ is a natural transformation. \\[\baselineskip]
-    \textbf{c} commutes by the coherence condition for $\wk$.  \textbf{d} commutes by the coherence condition for $\passoc$.
-  }\label{ThisWorksForA}
+    \& B \arrow[r, "\delta"] \arrow[d, "\delta"] \arrow[dl, "\delta"'] \arrow[phantom, ddl, "\textbf{h}" near start] \arrow[phantom, ddrrr, "\textbf{j}"]
+        \& B \tensor B \arrow[r, "f\tensor\id_B"]
+          \& A \tensor B \arrow[r, "\wk"]
+            \& A \sequoid B \arrow[d, "\id\sequoid\delta"] \\
+    B \tensor B \arrow[r, "\sym"] \arrow[d, "f^\dag\tensor f^\dag"'] \arrow[phantom, dr, "\textbf{i}"]
+      \& B \tensor B \arrow[d, "f^\dag\tensor f^\dag"]
+        \&
+          \&
+            \& A \sequoid (B \tensor B) \arrow[d, "\id\sequoid(f^\dag\tensor f^\dag)"] \\
+    \oc A \tensor \oc A \arrow[r, "\sym"]
+      \& \oc A \tensor \oc A \arrow[r, "\alpha_A \tensor \id_A"']
+        \& (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"]
+          \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
+            \& A \sequoid (\oc A \tensor \oc A)
+  \end{tikzcd}
+  \]
+  \caption{\textbf{a} commutes because the comultiplication $\delta$ is associative.\\[\baselineskip]
+    \textbf{b} and \textbf{c} commute because $\wk$ is a natural transformation.  \textbf{d} and \textbf{e} commute because $\assoc$ and $\passoc$ are natural transformations.  \\[\baselineskip]
+    \textbf{f} is the tensor product of two diagrams: one is the definition of $f^\dag$ and the other one obviously commutes.\\[\baselineskip]
+    \textbf{g} is one of the coherence diagrams for $\wk$.\\[\baselineskip]
+    \textbf{h} commutes because the comultiplication $\delta$ is commutative. \\[\baselineskip]
+    \textbf{i} commutes because $\sym$ is a natural transformation.\\[\baselineskip]
+    \textbf{j} commutes by the first diagram.
+  }\label{transferReportDiagram2}
 \end{SidewaysFigure}
 
-%%
-%% Bibliography
-%%
-
-%% Either use bibtex (recommended),
-
-\bibliography{bibliography}
-
-%% .. or use the thebibliography environment explicitely
+\begin{SidewaysFigure}
+  \[
+    \begin{tikzcd}[ampersand replacement=\&]
+      B \arrow[r, "\delta"] \arrow[d, "\delta"'] \arrow[phantom, ddrrrr, "\textbf{a}"]
+        \& B \tensor B \arrow[r, "f\tensor\id_B"]
+          \& A \tensor B \arrow[r, "\wk"]
+            \& A \sequoid B \arrow[r, "\Delta"]
+              \& (A \sequoid B) \times (A \sequoid B) \arrow[r, "\dist_{A,B}\inv"] \arrow[d, "(\id_A\sequoid\delta)\times(\id_A\sequoid\delta)"'] \arrow[phantom, ddr, "\textbf{b}" xshift=1.2em]
+                \& (A \times A) \sequoid B \arrow[d, "\id_{A\times A}\sequoid\delta"] \\
+      B \tensor B \arrow[d, "f^\dag\tensor f^\dag"']
+        \&
+          \&
+            \&
+              \& (A \sequoid (B \tensor B)) \times (A \sequoid (B \tensor B)) \arrow[d, "(\id_A \sequoid (f^\dag\tensor f^\dag))\times(\id_A \sequoid (f^\dag\tensor f^\dag))"']
+                \& (A \times A) \sequoid (B \tensor B) \arrow[d, "\id_{A\times A} \sequoid (f^\dag\tensor f^\dag)"] \\
+      \oc A \tensor \oc A \arrow[rrrr, "\sigma_A"] \arrow[d, "\int_{A,A}"'] \arrow[phantom, drrrrr, "\textbf{c}"]
+        \&
+          \&
+            \&
+              \& (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "\dist_{A,\oc A \tensor \oc A}\inv" yshift=0.3em]
+                \& (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[d, "\id_{A\times A}\sequoid\int_{A,A}"] \\
+      \oc (A\times A) \arrow[rrrrr, "\alpha_{A\times A}"]
+        \&
+          \&
+            \&
+              \&
+                \& (A \times A) \sequoid \oc(A\times A)
+    \end{tikzcd}
+    \]
+  \caption{\textbf{a} is the product of the diagrams in Figure \ref{transferReportDiagram2}.\\[\baselineskip]
+    \textbf{b} commutes because $\dist$ is a natural transformation.\\[\baselineskip]
+    \textbf{c} is the definition of $\int_{A,A}$
+  }\label{transferReportDiagram3}
+\end{SidewaysFigure}
+
+Now the following diagrams show that the triangle on the left commutes:
+\[
+  \begin{tikzcd}
+    B \arrow[r, "\delta"] \arrow[d, "f^\dag"']
+      & B \tensor B \arrow[r, "f\tensor\id_B"]
+        & A \tensor B \arrow[r, "\wk"]
+          & A \sequoid B \arrow[dr, "\id_A\sequoid*"] \arrow[d, "\id_A\sequoid f^\dag"']
+            & 
+              & \\
+    \oc A \arrow[rrr, "\alpha_A"']
+      &
+        &
+          & A \sequoid \oc A \arrow[r, "\id_A\sequoid*"']
+            & A \sequoid I \arrow[r, "\run_A"]
+              & A
+  \end{tikzcd}
+  \]
+\[
+  \begin{tikzcd}
+    B \tensor B \arrow[r, "f\tensor\id"] \arrow[d, "\id_B\tensor*"]
+      & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id\tensor*"]
+        & A \sequoid B \arrow[d, "\id\sequoid*"] \\
+    B \tensor I \arrow[r, "f\tensor\id_I"]
+      & A \tensor I \arrow[r, "\wk"]
+        & A \sequoid I \arrow[dl, "\run_A"] \\
+    B \arrow[uu, bend left=100, "\delta"] \arrow[u, "\runit_B"'] \arrow[r, "f"]
+      & A \arrow[u, "\runit_A"]
+        &
+  \end{tikzcd}
+  \]
+In the first diagram, the morphism along the bottom is $\der_A$, by definition.
+The second diagram shows that the morphism along the top of the first diagram is equal to $f$.
+The triangle at the bottom right of that diagram is one of the coherence conditions for $\wk$, while the semicircle at the left commutes because the comultiplication $\delta$ is unital (with unit $*\from B\to I$).
+
+Lastly, we show uniqueness.  Suppose that $g\from B\to\oc A$ makes the diagram commute:
+\[
+  \begin{tikzcd}
+    %
+      & B \arrow[r, "\delta"] \arrow[d, "g"] \arrow[dl, "f"']
+        & B \tensor B \arrow[d, "g\tensor g"] \\
+    A
+      & \oc A \arrow[l, "\der_A"] \arrow[r, "\mu_A"]
+        & \oc A \tensor \oc A
+  \end{tikzcd}
+  \]
+We may convert this into the following diagram:
+\[
+  \begin{tikzcd}
+    B \arrow[r, "\delta"] \arrow[d, "g"']
+      & B \tensor B \arrow[r, "f\tensor\id_B"] \arrow[d, "g\tensor g"]
+        & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id_A\tensor g"]
+          & A \sequoid B \arrow[d, "\id_A\sequoid g"] \\
+    \oc A \arrow[r, "\mu_A"]
+      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id"]
+        & A \tensor \oc A \arrow[r, "\wk"]
+          & A \sequoid \oc A
+  \end{tikzcd}
+  \]
+Here, the left hand square is taken straight from the previous diagram, while the middle square is the tensor product of the left hand triangle with a diagram that obviously commutes.
+The right hand square commutes because $\wk$ is a natural transformation.
+
+By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.
 

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Fixed Jim's proof.

@@
 Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} have shown that where the limit $(A^\infty, \{p^\infty_i\from A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e.
-for each object $B$, $B \otimes A^\infty$ is the limit of
-$$B \otimes I \stackrel{B \otimes p_0}{\leftarrow} B \otimes A  \stackrel{B \otimes p_1}{\leftarrow} B\otimes  A^2 \ldots $$
-then a comultiplication $\mu:A^\infty \rightarrow A^\infty \otimes A^\infty$ may be defined making $(A^\infty,\mu,t_{\oc A})$ the cofree commutative comonoid.
+for each object $B$, $B \tensor A^\infty$ is the limit of
+$$B \tensor I \stackrel{B \tensor p_0}{\leftarrow} B \tensor A  \stackrel{B \tensor p_1}{\leftarrow} B\tensor  A^2 \ldots $$
+then a comultiplication $\mu:A^\infty \rightarrow A^\infty \tensor A^\infty$ may be defined making $(A^\infty,\mu,t_{\oc A})$ the cofree commutative comonoid.
 Where these conditions are satisfied, we shall call this a MTT-exponential.
-\begin{proposition}Any sequoidally decomposable category has all symmetric tensor powers, and these are preserved by the tensor.  
+
+In the category of games, the morphisms $\id\sequoid\pr_1$ and $\id\sequoid\pr_2 \from A \sequoid (B\times C)\to (A \sequoid B) \times (A \sequoid C)$ are jointly monomorphic.
+If a distributive sequoidal category satisfies the same property, we say that it is \emph{strong distributive}.
+\begin{proposition}Any strong distributive decomposabe sequoidal category has all symmetric tensor powers, and these are preserved by the tensor.  
 \end{proposition} 
 \begin{proof}
-By sequoidal decomposability, for any $n$, $A^{\otimes (n+1)}$ is the cartesian product $\Pi_{i \leq n} (A \sequoid A^{\otimes n})$ with projections 
-  $\comp{\sym_i}{\wk_{A,A^{\otimes n}}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
-
-  We inductively define the sequoid powers $A^{\sequoid n}$ by $A^{\sequoid 1}=A$ and $A^{\sequoid(n+1)}=A\sequoid A^{\sequoid n}$.
-Given $n$, we inductively define a morphism $\eq_n\from A^{\sequoid n}\to A^{\tensor n}$ as the diagonal $\langle \id_A\sequoid\eq_{n-1}\rangle$ into the product -- so $\comp{\wk}{\comp{\sym_i}{\eq_n}}=\id\sequoid e_{n-1}$ for each $i$.
-
-  If $\pi\in S_n$ is a permutation, we write $\sym^\pi$ for the appropriate symmetry of $A^{\tensor n}$.
-We now claim that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi\in S_n$ -- so $\eq_n$ equalizes the $\sym^\pi$.
-Indeed, let $\pi\in S_n$.
-Then we may write $\sym^\pi = \comp{\id_A\tensor\sym^\rho}{\sym_i}$ for some $i$ and some $\rho\in S_{n-1}$.
-Now we have:
-  \begin{IEEEeqnarray*}{rClC}
-    \comp{\wk}{\comp{\sym^\pi}{\eq_n}} & = & \comp{\wk}{\comp{\comp{(\id\tensor\sym^\rho)}{\sym_i}}{\eq_n}} & \\
-    & = & \comp{(\id\sequoid\sym^\rho)}{\comp{\wk}{\comp{\sym_i}{\eq_n}}} & \hspace{24pt}\textrm{(by naturality of $\wk$)} \\
-    & = & \comp{(\id\sequoid\sym^\rho)}{(\id\sequoid\eq_{n-1})} & \\
-    & = & \id\sequoid\eq_{n-1}
-  \end{IEEEeqnarray*}
-  Since $\pi$ was arbitrary, it follows that $\comp{\wk}{\comp{\comp{\sym_j}{\sym^{\pi}}}{\eq_n}}=\comp{\comp{\wk}{\sym_j}}{\eq_n}$ for all $j$ and therefore that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi$, as desired.
-
-  Now define $\wk^n\from A^{\sequoid n}\to A^{\tensor n}$ inductively by $\wk^n = \comp{\id\sequoid\wk^{n-1}}{\wk}$.
-We may show by induction that $\comp{\wk^n}{\eq_n}=\id_{A^{\sequoid n}}$ for all $n$: indeed, we have
-  \begin{IEEEeqnarray*}{rClC}
-    \comp{\wk^n}{\eq_n} & = & \comp{(\id\sequoid\wk^{n-1})}{\comp{\wk}{\eq_n}} & \\
-    & = & \comp{(\id\sequoid\wk^{n-1})}{(\id\sequoid\eq_{n-1})} & \\
-    & = & \id\sequoid \id = \id & \hspace{24pt}\textrm{(by induction)}
-  \end{IEEEeqnarray*}
-  Now let $f\from C \to B \tensor A^{\tensor n}$ be such that $\comp{(\id\tensor\sym^\pi)}{f}=f$ for all $\pi\in S_n$.
-It follows from what we have just shown that if $f=\comp{(\id\tensor\eq_n)}{g}$, then $g=\comp{\comp{\id\tensor\wk^n}{\id\tensor\eq_n}}{g}=\comp{\id\tensor\wk^n}{f}$.
-So we just need to show that
-  \[
-    f=\comp{(\id\tensor(\comp{\eq_n}{\wk_n}))}{f}
-    \]
-  We first assume that $B=I$, so we have $f\from C\to B\tensor A^{\tensor n}$ and $\comp{\sym^\pi}{f}=f$ for all $\pi\in S_n$ and we are trying to show that $f=\comp{\comp{\eq_n}{\wk^n}}{f}$.
-We do this by showing that $\comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}}=\comp{\comp{\wk}{\sym_i}}{f}$ for all $i$.
-
-  Indeed, we have:
-  \begin{IEEEeqnarray*}{rClC}
-    \comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}} & = & \comp{\comp{(\id\sequoid\eq_{n-1})}{(\id\sequoid\wk^{n-1})}}{\comp{\wk}{f}} & \\
-    & = & \comp{\wk}{\comp{(\id\tensor(\comp{\eq_{n-1}}{\wk^{n-1}}))}{f}} &\hspace{24pt}\textrm{(by naturality of $\wk$)} \\
-    & = & \comp{\wk}{f} &\hspace{2pt}\textrm{(by induction)} \\
-    & = & \comp{\wk}{\comp{\sym_i}{f}}
-  \end{IEEEeqnarray*}
-
-  Now let $B$ be an arbitary object of the category.  [TODO: finish working this out.]
+By sequoidal decomposability, for any $n$, $A^{\tensor (n+1)}$ is the cartesian product $\Pi_{i \le n} (A \sequoid A^{\tensor n})$ with projections 
+$\sym_i;\wk_{A,A^{\tensor n}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
+
+  Define  $\wk^n: A^{\tensor n}\rightarrow A^{\sequoid n}$ by $\wk^{n+1} = \wk_{A, A^{\tensor n}}; (A \sequoid \wk^n)$.
+We show (by induction on $n$) that for any $n$, the morphisms $\comp{\wk_n}{\sym^\pi}$ are jointly monomorphic, where $\sym^\pi$ ranges over all of the permutation isomorphisms  on $A^{\tensor n}$.
+
+  The equalizer $\eq_n:A^n \rightarrow A^{\tensor n}$ is defined inductively by $\eq_n=\langle \id\sequoid\eq_{n-1}$, using the identification of $A\sequoid n$ as a product given above.
+We may show inductively that $\comp{\wk^n}{\comp{\sym^\pi}{\eq_n}}=\id$ for all permutations $\pi\in S_n$.
+  Given any $f:C \rightarrow A^{\tensor n} \tensor B$ such that $\comp{(\theta \tensor B)}{f} = f$ for any permutation symmetry $\theta$, taking $\comp{(\wk^n \tensor B)}{f}:C \rightarrow A^{\sequoid n} \tensor B$ gives the unique morphism such that $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$.
+Indeed, for all permutations $\pi\in S_n$ we have $\comp{\wk^n\tensor\id_B}{\comp{\sym^\pi\tensor\id_B}{\comp{\eq_n\tensor\id_B}{\comp{(\wk^n\tensor\id_B}{f}}}}=\comp{(\wk^n\tensor\id_B)}{f}=\comp{(\wk^n\tensor\id_B)}{\comp{\sym^\pi}{f}}$.
+Hence, $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$ (by decomposability and strong distributivity, the joint monomorphism property is preserved by the tensor product).
+For uniqueness, use the fact that $\eq_n$ is a left inverse for $\wk^n$.
 \end{proof}
@@
 for any $B$, $B \sequoid A^\infty$ is the limit for $B \sequoid \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid.
-Conversely, we may show that any cofree commutative comonoid which arises as a $\otimes$-preserving limit of symmetric tensor powers is a final coalgebra.
+Conversely, we may show that any cofree commutative comonoid which arises as a $\tensor$-preserving limit of symmetric tensor powers is a final coalgebra.
 \begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty, \comp{\wk_{A\tensor\oc A}}{\comp{\der_A}{\mu_A}})$ is a final coalgebra for the functor $A \sequoid \_$.

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Made tiny correction.

@@
         & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
-          & B \tensor \oc A \arrow[r, "\wk"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
-            & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
+          & B \tensor \oc A \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
+            & B \sequoid \oc A \;\times\; \oc A \sequoid B \arrow[d, "\id\sequoid\oc\sigma\;\times\;\oc\sigma\sequoid\id"] \\
     \oc B \arrow[r, "\mu"] \arrow[dd, "\oc \tau"']
@@
         &
-          & B \tensor \oc B \arrow[r, "\wk"] \arrow[d, "\tau\tensor\id"]
-            & B \sequoid \oc B \\
+          & B \tensor \oc B \arrow[r, "\dec"] \arrow[d, "\tau\tensor\id"]
+            & B \sequoid \oc B \;\times\; \oc B \sequoid B \\
     %
@@
         &
-          & C \tensor \oc B \arrow[r, "\wk"] \arrow[d, dotted, "\id\tensor\oc\tau"']
-            & C \sequoid \oc B \arrow[d, "\id\sequoid\oc\tau"] \\
+          & C \tensor \oc B \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\tau"']
+            & C \sequoid \oc B \;\times\; \oc B \sequoid C \arrow[d, "\id\sequoid\oc\tau\;\times\oc\tau\sequoid\id"] \\
     \oc C \arrow[r, "\mu"]
@@
         &
-          & C \tensor \oc C \arrow[r, "\wk"]
-            & C \sequoid \oc C
-  \end{tikzcd}
-  \]
-Here, the outermost (solid) shapes commute by the definition of $\oc\sigma$, $\oc\tau$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
-The smaller squares on the right hand side commute because $\wk$ is a natural transformation.
-Now observe that $\wk_{X,Y}=\comp{\pr_1}{\dec_{X,Y}}$ is the composition of epimorphisms, so is an epimorphism for all $X,Y$.
-It follows that the two rectangles on the left commute as well.
+          & C \tensor \oc C \arrow[r, "\dec"]
+            & C \sequoid \oc C \;\times \oc C \sequoid C
+  \end{tikzcd}
+  \]
+Here, the outermost (solid) shapes are the product of shapes that commute by the definition of $\oc\sigma$, $\oc\tau$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
+The smaller squares on the right hand side commute because $\dec$ is a natural transformation.
+Since $\dec$ is an isomorphism, the two rectangles on the left commute as well.
 

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Made it much shorter.

@@
 \begin{abstract}
-The non-commutative sequoid operator $\sequoid$ on games was introduced by one of the authors in order to capture algebraically the presence of state in history-sensitive strategies in game semantics.
-It imposes a causality relation on to the  tensor product of games, so that coalgebras for the  functor  $A\sequoid\blank$  - i.e.
-morphisms from $S$ to $A \sequoid S$ may be viewed as state transformers.
-If $A\sequoid\blank$ has a final coalgebra, $\oc A$, then the anamorphism of such a state transformer encapsulates its explicit state, so that it is shared only between successive invocations.
-
-We shall study  conditions under which such a final coalgebra $\oc A$ for the functor $A\sequoid\blank$ is the carrier of a cofree commutative comonoid on $A$.
-That is, it is a model of the exponential of linear logic, but one in which we can construct imperative objects such as reference cells and stacks coalgebraically, and reason about them coinductively, in a game semantics setting.
-
-We shall review the definition of a sequoidal category, a category-theoretic formalization of the sequoid operator, and the notion of sequoidal decomposition of a symmetric monoidal category.
-We show that given such a decomposition, the final coalgebra !A may be endowed with the structure of the cofree commutative comonoid if it is the bifree algebra for $A\sequoid\blank$, or if it is a limit of sequoidal powers (following the construction  of the cofree commutative comonoid by Melli\'es, Tabareau and Tasson), or if the functor $\oc$ is strong monoidal - for all  $A$ and $B$, the objects $\oc (A \times B)$ and $\oc A \tensor \oc B$ are naturally isomorphic.
-
-We establish necessity of this final condition  by giving an example of a sequoidally decomposable category of games in which plays will be allowed to have transfinite length.
-In this category, the final coalgebra for the functor $A\sequoid\blank$ is not the cofree commutative comonoid over $A$: we illustrate this by explicitly contrasting the final sequence for the functor $A\sequoid\blank$ with the chain of sequoidal powers used in the Melli\'es-Tabareau-Tasson construction.
+The non-commutative sequoid operator $\sequoid$ on games was introduced  to capture algebraically the presence of state in history-sensitive strategies in game semantics, by imposing a causality relation on the  tensor product of games.
+Coalgebras for the  functor  $A\sequoid\blank$  --- i.e.
+morphisms from $S$ to $A \sequoid S$ --- may be viewed as state transformers:  if $A\sequoid\blank$ has a \emph{final coalgebra}, $\oc A$, then the anamorphism of such a state transformer encapsulates its explicit state, so that it is shared only between successive invocations.
+
+We study the  conditions under which a final coalgebra $\oc A$ for  $A\sequoid\blank$ is the carrier of a \emph{cofree commutative comonoid} on $A$.
+That is, it is a model of the exponential of linear logic in which we can construct imperative objects such as reference cells  coalgebraically, in a game semantics setting.
+We show that if the tensor \emph{decomposes} into the sequoid,  the final coalgebra $!A$ may be endowed with the structure of the cofree commutative comonoid if the natural isomorphism $\oc (A \times B) \cong \oc A \tensor \oc B$ holds.
+This condition is always satisfied if $\oc A$ is the \emph{bifree algebra} for $A\sequoid\blank$, but in general it is necessary to impose it, as we establish by giving an example of a sequoidally decomposable category of games in which plays will be allowed to have transfinite length.
+In this category, the final coalgebra for the functor $A\sequoid\blank$ is not the cofree commutative comonoid over $A$: we illustrate this by explicitly contrasting the final sequence for the functor $A\sequoid\blank$ with the chain of symmetric tensor powers used in the construction of the cofree commutative comonoid as a limit by  Melli\'es, Tabareau and Tasson.
+
 \end{abstract}
@@
 \section{Introduction}
-
-Games models of pure functional programming languages such as PCF (\cite{ajmPcf} and \cite{hoPcf}, for example) tend to include the requirement that strategies be \emph{history-free}\footnote{In fact, the model in \cite{hoPcf} and other models following the `Hyland-Ong' tradition use \emph{innocent} strategies, rather than history free strategies to model statelessness.
-We will focus on AJM-style Game Semantics in this paper, so we shall focus on history-freeness vs.
-history sensitivity rather than innocence.}: that is, the response to a particular position may depend only upon the last move played, and not upon what has gone before.
-This makes sense for stateless languages, where the program should have no `memory' to recall what has gone before.
-
-If history-free strategies are the game-semantic interpretation of stateless programs, then history-sensitive strategies should be the game-semantic interpretation of stateful programs, and this is indeed how they are used: Abramsky and McCusker's model of Idealized Algol \cite{SamsonGuyIAPassive}, for example, makes use of history-sensitive strategies in order to model stateful programs.
-However, this idea of state can be difficult to work with, because it is completely \emph{implicit} in the strategy.
-Let us, for example, try to model a simple storage cell.
-Let $X$ be a set of values and, as in \cite{SamsonGuyIAPassive}, let $\Var[X]$ be the game with maximal plays $rx$ and $w_x\checkmark$, where $x$ ranges over $X$.
-$rx$ corresponds to a $\read$ method: player $O$ plays $r$ and expects to receive the value $x$ currently in the cell, while $w_x\checkmark$ corresponds to a write method: player $O$ writes $x$ into the cell and then player $P$ confirms that the write has taken place.
-
-It is now clear that we have a strategy $\cell$ on $\oc \Var[X]$ corresponding to a storage cell: whenever player $O$ plays $w_x$, respond with $\checkmark$, and whenever player $O$ plays $r$, respond with the last $x$ such that $w_x$ was played (if the cell is uninitialized -- i.e., if $w_x$ has never been played for any $x$ -- then we return either nothing or some specified initial value, depending on what we are trying to model).
-This strategy is clearly history sensitive and represents a stateful program; however, it is tricky to reason about the statefulness of $\cell$, because there is no object explicitly representing the state: the state in $\cell$ is \emph{implicit}, and it appears that we need to resort to combinatorial arguments in order to reason about it.
-
-Contrast this with the handling of state in traditional domain-theoretic semantics, where we represent a stateful program as a function $W \times X \to W \times Y$, or a \emph{state transformer}, where $W$ is a built-in store of state that can be reasoned about directly.
-In 2002, one of the authors introduced the game-semantic equivalent of a state-transformer by defining a new operation on games -- the \emph{sequoid} $\blank\sequoid\blank$\cite{laird02}.
-The game $A\sequoid B$ is the same as the game $A\tensor B$, except that the first move must take place in $A$.
-We now model a state transformer for a program as a morphism $S \to A \sequoid S$ -- i.e., a \emph{coalgebra} for the functor $A\sequoid\blank$ -- where $A$ is the program and $S$ is the changed state.
-The justification for the order relation on the sequoid operator is that the state should only change in response to some action by the environment.
-
-For example, let $X$ be the game with maximal plays $rx$ for $x\in X$.
-Then we may define a state transformer for $X \implies \Var[X]\sequoid X$ as follows: play must start in the game $\Var[X]$.
-If player $O$ starts with the move $r$, then request a value of $x$ on the left and then copy it into both $\Var[X]$ and $X$ on the right (so if $X$ on the left represents the initial state and $X$ on the right represents the final state, then we have returned the value of the state and left the state unchanged).
-If player $O$ starts with the move $w_y$, return $\checkmark$ and then copy the value $y$ over to $X$ on the right, ignoring the value of $X$ on the left.
-
-Note that we may model multiple iterations of the state transformer as coalgebras:
-\[
-  S \to A \sequoid (A \sequoid \cdots \sequoid (A \sequoid S)\cdots)
-  \]
-where the copies of $A$ are started in order from left to right.  The state from a previous invocation of $A$ is passed on to the next, until the final modified state finally appears at the right.
-
-Now we come to the key point of the construction: if $A$ is a game, then the Hyland exponential $\oc A$ \cite{hyland1997games} has the structure of the \emph{final coalgebra} for the functor $A \sequoid\blank$.
-Therefore, following \cite{jacobs}, any coalgebra $S\to A\sequoid S$ (i.e., any state transformer) gives rise to a morphism $S\to\oc A$ that encapsulates the explicit state of the state transformer into an implicitly stateful history-sensitive strategy $S\to\oc A$ that corresponds to repeatedly invoking the state transformer, passing the state from one invocation to the next.
-
-Indeed, the state transformer we defined on $X\implies\Var[X]\sequoid X$ gives rise to a morphism $X\to\oc\Var[X]$ that gives us the behaviour of a storage cell with initial value given by the copy of $X$ on the left; composing this with our desired initial value on $X$ gives us the strategy $\cell$.
-The difference now is that, rather than reason directly about the implicit strategy $\cell$, we may reason about the explicit state in our state transformer and then use coalgebraic methods to talk about $\cell$.
-
-It is clear that the key fact in the construction is that the final coalgebra for $A\sequoid\blank$ coincides with the exponential $\oc A$, which has the structure of the \emph{cofree commutative comonoid} on $A$.
-We will begin by introducing the general idea of using coalgebra to define higher-order stateful objects, using a construction on the category $\Rel$ of sets and relations.
-This construction is simple to define, but the final coalgebra in that context does not give us a good model of the exponential: it gives us a cofree comonoid, but not a commutative one.
-This motivates us to study state transformers using game semantics and the sequoid operator.
-
-We review the definition of a \emph{sequoidal category} from \cite{laird02}: a category-theoretic formalization of the sequoid operator akin to the formalization of the tensor product $\tensor$ by the definition of a \emph{monoidal category}.
-We illustrate the definition by showing how the sequoidal structure allows us to model stateful programs as morphisms into the final coalgebra for the functor $A\sequoid\blank$, using the example of the $\cell$ strategy in the category of games.
-
-We spend the rest of the paper discussing the question of what assumptions we need in order to prove that the final coalgebra for $A\sequoid\blank$ coincides with the cofree commutative comonoid on $A$.
-The explicit formula for the cofree commutative comonoid given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} provides a way to link the two constructions that works for the basic category of games; however, it is not powerful enough to prove that the final coalgebra and the cofree commutative comonoid are the same in the category of games with infinitary winning conditions.
-
-We turn instead to a purely sequoidal/coalgebraic proof that the final coalgebra $\oc A$ for $A\sequoid\blank$ is the carrier of the cofree commutative comonoid on $A$.
-In this case, we will need to assume that our category has a Cartesian structure and also assume an additional hypothesis: that if $A$ and $B$ are objects, then a certain natural morphism $\oc A \tensor \oc B \to \oc (A\times B)$ is an isomorphism.
-We will refer to this as the \emph{strong monoidal hypothesis}, since it can be used to show that $\oc\blank$ gives rise to a strong monoidal functor from the category with its Cartesian structure to the category with its monoidal functor.
-
-We show that the strong monoidal hypothesis holds whenever $\oc A$ is a \emph{bifree algebra} for $A\sequoid\blank$: that is, it is simultaneously an initial algebra and a final coalgebra.
-
-We finish with a non-example: the sequoidal category of games with transfinite plays.
-In this setting the final coalgebra for $A\sequoid\blank$ does not carry the structure of the cofree commutative comonoid over $A$.
-By our discussion above, note that the final coalgebra for $A\sequoid\blank$ has the structure of $\omega$-many copies of the game $A$, where we pass the state from $A_i$ to $A_{i+1}$:
-\tikzset{dotsstyle/.style={draw=none}}
-\[
-  \begin{tikzpicture}
-    \matrix[matrix of nodes, column sep=36pt, inner xsep=1ex, name=m, nodes={draw=black}] {
-      $A_0$ & $A_1$ & $A_2$ & |[dotsstyle]| $\cdots$ \\ };
-    \path[commutative diagrams/.cd, every arrow, every label, labels={font size=tiny}]
-      (m-1-1) edge node {state} (m-1-2)
-      (m-1-2) edge node {state} (m-1-3)
-      (m-1-3) edge node {state} (m-1-4);
-  \end{tikzpicture}
-\]
-
-For finite interactions, we can use this to model the exponential, in which repeated access to the resource $A$ is allowed, by passing an empty state in between successive invocations of $A$.
-In the transfinite case, however, there might not be enough copies of $A$ in the final coalgebra to satisfy our needs: consider a program that, over time $\omega$, uses the resource $A$ infinitely many times.
-If we carry on into transfinite time, the program may continue to request access to the resource $A$.
-But this is no longer possible if we are using the final coalgebra for our `exponential', since we are only able to construct a sequence of invocations of $A$ of length $\omega$: there is no predecessor copy of $A$ to receive the (empty) state from.
-
-We shall demonstrate why our earlier approaches fail in this context: the Melli\'es-Tabareau-Tasson construction fails badly in this case, just as it fails for win games and winning strategies (which may be viewed as games of length $\omega+1$).
-Similarly, the strong monoidal hypothesis does not hold, since a transfinite interleaving of two sequences of length $\omega$ may have length greater than $\omega$.
-
-\section{Defining Higher-order Stateful Objects, Coalgebraically}
-In this section we motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon.
-A \emph{state-transformer} in a symmetric monoidal category is a morphism $f:A \otimes S \rightarrow B \otimes S$ taking an argument together with an input state to a result together with a input state.
+Game semantics has been used to define a variety of models of higher-order programming languages with  mutable state, including Idealized Algol  \cite{SamsonGuyIAPassive}, and various fragments of ML \cite{AMV,AHM}.
+Unlike traditional denotational semantics, which typically represent imperative programs as state transformers, the state in these models is completely implicit: local declaration of mutable variables is interpreted as composition with a ``history sensitive'' strategy representing a reference cell.
+This is conceptually simple in principle but leads to some quite combinatorial definitions; a more explicit representation of the current state can be very useful for constructing and reasoning about imperative objects.
+In this paper, we use final coalgebras to forge a link between the explicit and implicit representation of state in game semantics.
+We study the conditions under which the \emph{cofree commutative comonoid} in categories of games may be derived from a final coalgebra, relating their underlying structure as models of linear logic to classical coalgebraic techniques for describing state.
+
+\subsection{Defining Higher-order Stateful Objects, Coalgebraically}
+Let us first motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon. 
+A \emph{state-transformer} in a symmetric monoidal category is a morphism $f:A \otimes S \rightarrow B \otimes S$ taking an argument together with an input state to a result together with an output state.
 A well-studied \cite{jacobs} technique in semantics is to  use an appropriate final coalgebra to \emph{encapsulate} the state in such a transformer, allowing multiple  successive invocations, each of which passes its output state as an input state to the next invocation.
@@
 For example, consider the category $\Rel$ of sets and relations, with symmetric monoidal structure given by the cartesian product (with unit $I$, the singleton set $\{*\}$).
-This has finite (bi)products given by the disjoint union of sets: define the functor $F(A,S) = (A \otimes S) \oplus I$
-
-For any object (set) $A$, let $A^*$ be the set $A^*$ of finite sequences of elements of $A$ (i.e.
-the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$
-\begin{lemma}$(A^*,\alpha_A)$ is a final coalgebra  for $F(A,\_)$.
+This has finite (bi)products (disjoint unions) so we may define the functor $F(A,S) = (A \otimes S) \oplus I$.
+For any object (set) $A$, let $A^*$ be the set of finite sequences of elements of $A$ (i.e.
+the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$.
+It is straightforward to show that:
+% $A^*$ is a \emph{minimal invariant} for $F(A,\_)$ with respect to the inclusion order on $\Rel$ and so:
+\begin{lemma}$(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
 \end{lemma}
-\begin{proof}$\Rel$ may be cpo-enriched with the inclusion order: $A^*$ is a \emph{minimal invariant} for $F(A,\_)$ with respect to this order.
-\end{proof}
-Since we have a natural transformation (left injection) $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $f;\inl_{A,B}:S \rightarrow F(A,S)$, --- i.e.
+Since we have a natural transformation  $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $f;\inl_{A,B}:S \rightarrow F(A,S)$, --- i.e.
 the unique $F(A,\_)$-coalgebra morphism from $(S,f;\inl)$ into $(A^*,\alpha_{A})$.
-This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ and uses it to update the internal state.
-
-By distributivity of $\oplus$ over  $\otimes$ we have a natural transformation $t: F(A,S) \otimes S' \rightarrow F(A,S \otimes S')$.
+This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A^*)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ and together with the encapsulated morphism with updated internal state.
+
+%By distributivity of $\oplus$ over  $\otimes$ we have a natural transformation $t_{A,S}: F(A,S) \otimes S' \rightarrow F(A,S \otimes S')$.
 We may use this to encapsulate  state transformers of general form: given $f:A \otimes S \rightarrow B \otimes S$, taking the anamorphism of the $F(B,\_)$-colagebra:
-$$A^* \otimes S  \stackrel{\alpha_A \otimes S}{\longrightarrow} F(A,A^*) \otimes S \stackrel{t}{\longrightarrow} F(A,A^* \otimes S)$$
-
- Distributivity of $\oplus$ over $\otimes$ also implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
+%$$A^* \otimes S  \stackrel{\alpha_A \otimes S}{\longrightarrow} F(A,A^*) \otimes S \stackrel{t}{\longrightarrow} F(A,A^* \otimes S)$$
+
+ Distributivity of $\oplus$ over $\otimes$ implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
 This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
-i.e.
+%i.e.
 given morphisms $f_1:A_1 \otimes S \rightarrow B_1 \otimes S, \ldots , f_n:A_n \otimes S \rightarrow B_n \otimes S$, encapsulating  $\dist;(f_1 \oplus \ldots \oplus f_n);\dist^{-1}$, gives a morphism from $(A_1 \oplus \ldots \oplus A_n)^* \otimes S$ into $(B_1 \oplus \ldots \oplus B_n)^*$.
-
-For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a state consisting of a single integer, representing the contents of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
+For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contensts of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
 Thus (with appropriate tagging) it is the relation $\{(i, (\read(i),i))\ |\ i \in \Na\} \cup \{(i,{\mathtt{write}}(j),j)\}$.
-The anamorphism of the coalgebra $\cell;\inl:\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$ Composition with this morphism is precisely the denotation of new variable declaration in the semantics of  Reynolds \emph{Syntactic Control of Interference} (SCI) in $\Rel$ given in \cite{Mcsci}.
-
-Coalgebraic methods thus give us a recipe for constructing and using categorical definitions of stateful semantic objects, avoiding direct definitions which are rather combinatorial to work with.
-In order to fully exploit these, however, we may endow $A^*$ with the structure of a \emph{comonoid} by defining morphisms $\delta_A:A^* \rightarrow A^* \otimes A^* = \{(u\cdot v,(u,v))\ |\ u,v \in A^*\}$ and $\epsilon:A \rightarrow I = \{(\varepsilon,*)\}$
-
+The anamorphism of the coalgebra $\cell;\inl:\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$.
+Composition with this morphism is precisely the interpretation of new variable declaration in the semantics  in $\Rel$ of the prototypical functional-imperative language \emph{Syntactic Control of Interference} (SCI) given in \cite{Mcsci}.
+
+Coalgebraic methods thus give us a recipe for constructing and using categorical definitions of stateful semantic objects.
+In order to fully exploit these, however, we endow $A^*$ with the structure of a \emph{comonoid} in our symmetric monoidal category, by defining morphisms $\delta_A:A^* \rightarrow A^* \otimes A^* = \{(u\cdot v,(u,v))\ |\ u,v \in A^*\}$ and $\epsilon:A \rightarrow I = \{(\varepsilon,*)\}$.
 In fact, this is the \emph{cofree comonoid} on $A$ --- there is a morphism $\eta_A:A^* \rightarrow A = \{(a,a)\ | \ a \in A\}$ such that for any comonoid $(B,\delta_B,\epsilon_B)$, composition with $\eta_A$ defines an equivalence (natural in $B$)  between the morphisms from $B$ into $A$, and the comonoid morphisms from $(B,\delta_B,\epsilon_B)$ into  $(A^*,\delta_A,\epsilon_A)$.
-\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.
+\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.\footnote{The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
+$(A^*,\alpha^{-1})$ is an initial algebra for $F(A,\_)$ ($\alpha$ must be an isomorphism by Lambek's lemma).
+We leave this as an exercise.}
 \end{proposition}
-The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
-$(A^*,\alpha^{-1})$ is an initial algebra for $F(A,\_)$ ($\alpha$ must be an isomorphism by Lambek's lemma).
-We leave this as an exercise.
-
-This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell, the creation of multiple copies of such procedures ($(\_)^*$ is a monoidal comonad)  etc.
-Its main limitation is that we have not defined a \emph{commutative} monoid --- evidently it is not the case that $\delta_A;\sym_{A,A} = \delta_A$ (where $\sym_{A,B}:A \otimes B \rightarrow B \otimes A$ is the symmetry isomorphism for the tensor) for any non-empty set $A$.
-Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is predetermined.
-This is precisely the situation in SCI, where the typing system allows sharing between across sequential composition, but not between functions and their arguments.
-In order to model sharing of state between functions without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a cofree \emph{commutative} comonoid.
+This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell.      
+Its main limitation is that we have not defined a \emph{commutative} comonoid  for any non-empty set $A$ (evidently, $\delta$ is not invariant under postcomposition with the symmetry isomorphism of the tensor).
+Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed.
+(This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{Laf}.
 The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra).
-By properly reflecting the interleaving between function calls, game semantics does support a coalgebraic cofree commutative comonoid, leading to models of stateful higher-order languages such as Idealized Algol and core ML.
-As we shall show by example and counterexample, the richer structure of games also means that the relationship between initial and final coalgebras, and cofree objects is more subtle  (note, for example, that any final coalgebra in $\Rel$ must be bifree, by its self-duality).
+Hence, we turn to the richer structures of game semantics.
+%However,  the richer structure of
+%game semantics does support a coalgebraic cofree commutative comonoid. 
+% As we shall show by example and counterexample, the richer structure the relationship between initial and final coalgebras, and cofree objects is more subtle.
+%  (note, for example, that any final coalgebra in $\Rel$ must be bifree, by its self-duality).
+ \subsection{The cofree commutative comonoid as a final colagebra}
+We now outline the remainder of the paper.
+Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.} %Under a simple interpretation, $A\sequoid B$ is the same as the game $A\tensor B$, except that the first move must take place in $A$.
+ In this setting, we  can model a state transformer for a program as a morphism $S \to A \sequoid S$ --- i.e., a coalgebra for the functor $A\sequoid\blank$.
+The final coalgebra for this functor is the exponential game $!A$ introduced by Hyland \cite{hyland1997games}, which corresponds to a $\omega$-fold sequence $A \sequoid (A \sequoid (A \sequoid \ldots ))$; under appropriate conditions, it is the carrier for the  cofree  commutative comonoid on $A$.
+We aim to characterize these conditions using just the categorical structure,  in order to capture a general class of models and to derive formal principles for coinductively proving  program equivalences.
+In a nutshell, we require that a certain natural morphism $\oc A \tensor \oc B \to \oc (A\times B)$ is an isomorphism.
+This can be used to show that $\oc\blank$ gives rise to a strong monoidal functor.
+Perhaps more surprisingly, it is sufficient to show that $\oc A$ is the cofree commutative comonoid.
+
+This \emph{strong monoidal hypothesis} holds whenever $\oc A$ is a bifree algebra for $A\sequoid\blank$.
+But we are also interested in cases where $\oc A$ is not bifree --- for example, in categories of ``win games'' and \emph{winning strategies}  \cite{hyland1997games}, which lack the partial maps which can be shown to arise in the bifree case.
+To show that the strong monoidal hypothesis is necessary in general, we introduce a  sequoidal category of games with \emph{transfinite} plays in which it does not hold: because a transfinite interleaving of two sequences of length $\omega$ may have length greater than $\omega$, the final coalgebra for $A\sequoid\blank$  (corresponding  to only $\omega$-many copies of the game $A$) cannot be the carrier for the cofree commutative comonoid.
+
+We compare the  coalgebraic construction of the cofree exponential to the explicit characterization of the latter given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} as the limit of a chain of symmetric tensor powers.
+This chain exists in any decomposable sequoidal category: where its limit exists and is preserved by the tensor (the conditions required in \cite{MelliesCofCommCom}) it must be the final coalgebra for $A \sequoid\blank$.
+However, in our categories of transfinite games, and win games and winning strategies (which may be viewed as games of length $\omega+1$), the construction fails --- this limit is not the cofree commutative comonoid.
 
@@
 We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.
-A game $A$ is given by a tree $P_A$ of \emph{positions}, which are alternating sequences of $O$-moves and $P$-moves.
+A game $A$ is given by a forest (i.e., a prefix-closed set) $P_A$ of \emph{positions}, which are alternating sequences of $O$-moves and $P$-moves.
 We call a position a \emph{$P$-position} if it ends with a $P$-move and an \emph{$O$-position} if it ends with an $O$-move.
-A \emph{strategy} for a game $A$ is a subtree $\sigma$ of $P_A$ that is closed under $O$-replies to $P$-positions and which satisfies \emph{determinism}: if $sa,sb\in\sigma$, where $s$ is a $P$-position, then $a=b$.
+A \emph{strategy} for a game $A$ is a subforest $\sigma$ of $P_A$ that is closed under $O$-replies to $P$-positions and which satisfies \emph{determinism}: if $sa,sb\in\sigma$, where $s$ is a $P$-position, then $a=b$.
 We will adopt the rule that all positions must start with an $O$-move.
@@
 Thus, $\zeta_A$ is entirely determined on $P_A$, and the only new information is the values that $\zeta_A$ takes on the infinite positions in $\overline{P_A}$.
-The reason we bother to define $\zeta_A$ on finite positions at all is so that we can define it on the connectives:
+The reason we bother to define $\zeta_A$ on finite positions at all is so that we can define it easily on the connectives:
 \begin{gather*}
-  \zeta_{\prod_{i\in I}A_i}(s) = \bigwedge_{i\in I}\zeta_{A_i}(s\vert_{A_i}) \\
-  \zeta_{A\tensor B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
-  \zeta_{A\sequoid B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
-  \zeta_{A \implies B}(s) = \zeta_A(s) \Rightarrow \zeta_B(s) \\
+  \zeta_{A\tensor B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \quad
+  \zeta_{A \implies B}(s) = \zeta_A(s\vert_A) \Rightarrow \zeta_B(s\vert_B) \\
+  \zeta_{\prod_{i\in I}A_i}(s) = \bigwedge_{i\in I}\zeta_{A_i}(s\vert_{A_i}) \quad
+  \zeta_{A\sequoid B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \quad
   \zeta_{\oc A}(s) = \bigwedge_{i\in I}(\zeta_A(s\vert_i))
@@
 However, in this case, $\oc A$ is not the sequential limit of the symmetrized tensor powers over $A$.
-Since $\W$ is a decomposable, distributive sequoidal category, the symmetrized tensor powers of $A$ are given by the sequoidal powers $A^{\sequoid n}$.
+Since $\W$ is a decomposable, strong distributive sequoidal category, the symmetrized tensor powers of $A$ are given by the sequoidal powers $A^{\sequoid n}$.
 But now the limit of these objects is not quite the game $\oc A$; instead, it is the game $A^{\sequoid\omega}=\co A$ in which player $O$ may open an arbitrarily large number of copies of $A$, but not infinitely many.
@@
   \end{IEEEeqnarray*}
-inducing a morphism
-\[
-  \oc A\tensor \oc B \xrightarrow{\kappa_{A,B}} (A \sequoid(\oc A\tensor\oc B)) \times (B \sequoid(\oc A\tensor \oc B)) \xrightarrow{\dist\inv}
-    (A\times B)\sequoid(\oc A\tensor\oc B)
-    \]
-  Remembering that our category has a final coalgebra $\oc(A\times B)$ for the functor $(A\times B)\sequoid\blank$, we write $\int_{A,B}$ for the unique morphism $\oc A\tensor\oc B\to \oc(A\times B)$ making the following diagram commute
-  \begin{equation}\label{definitionOfInt}
-    \begin{tikzcd}
-      \oc A \tensor \oc B \arrow[r, "\kappa_{A,B}"] \arrow[d, "\int_{A,B}"']
-        & (A\sequoid(\oc A \tensor \oc B) \times (B \sequoid (\oc A \tensor \oc B)) \arrow[r, "\dist\inv"]
-          & (A \times B) \sequoid (\oc A \tensor \oc B) \arrow[d, "\id_{A\times B}\sequoid\int_{A,B}"] \\
-      \oc(A\times B) \arrow[rr, "\alpha_{A\times B}"']
-        &
-          & (A \times B) \sequoid \oc(A\times B)
-    \end{tikzcd}\tag{$\star$}
-  \end{equation}
+  We get a morphism $\comp{\dist\inv}{\kappa_A}\from \oc A \tensor \oc B \to (A\times B) \sequoid(\oc A \tensor \oc B)$ and we write $\int_{A,B}=\fcoal{\comp{\dist\inv}{\kappa_A}}\from \oc A \tensor \oc B \to \oc (A\times B)$.
 \end{definition}
@@
 \end{proof}
-
 Our first main result for this section will be the following:
@@
   \]
-where $\Delta$ is the diagonal map on the product.  There is therefore a unique morphism $\sigma_A=\fcoal{\comp{\dist\inv}{\comp{\Delta}{\alpha_A}}}$ making the following diagram commute:
-\begin{equation}\label{definitionOfSigma}
-  \begin{tikzcd}
-    \oc A \arrow[r, "\alpha_A"] \arrow[d, "\sigma_A"']
-      & A \sequoid \oc A \arrow[r, "\Delta"]
-        & (A \sequoid \oc A)\times(A \sequoid \oc A) \arrow[r, "\dist\inv"]
-          & (A \times A) \sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\sigma_A"] \\
-    \oc(A\times A) \arrow[rrr, "\alpha_{A\times A}"]
-      &
-        &
-          & (A \times A) \sequoid \oc(A \times A)
-  \end{tikzcd}\tag{\dag}
-\end{equation}
-and we may set $\mu_A=\comp{\int_{A,A}\inv}{\sigma_A}$.
+where $\Delta$ is the diagonal map on the product.
+We set $\sigma_A=\fcoal{\comp{\dist\inv}{\comp{\Delta}{\alpha_A}}}\from\oc A \to \oc (A\times A)$ and we set $\mu_A=\comp{\int_{A,A}\inv}{\sigma_A}\from \oc A \to \oc A \tensor \oc A$.
 
@@
 
-We define the action of $\oc$ on morphisms as follows: suppose that $\sigma\from A \to B$ is a morphism in $\C$.  Then we have a composite
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"]
+We define the action of $\oc$ on morphisms as follows: suppose that $f\from A \to B$ is a morphism in $\C$.  Then we have a composite
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\mu_A"]
       & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
-        & A \tensor \oc A \arrow[r, "\sigma\tensor\id_{\oc A}"]
+        & A \tensor \oc A \arrow[r, "f\tensor\id_{\oc A}"]
           & B \tensor \oc A \arrow[r, "\wk_{B,\oc A}"]
@@
   \]
-There is therefore a unique morphism $\oc\sigma\from\oc A \to\oc B$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[d, "\oc\sigma"']
-      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
-        & A \tensor \oc A \arrow[r, "\sigma\tensor\id_{\oc A}"]
-          & B \tensor \oc A \arrow[r, "\wk_{B,\oc A}"]
-            & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
-    \oc B \arrow[rrrr, "\alpha_B"]
-      &
-        &
-          &
-            & B \sequoid \oc B
-  \end{tikzcd}
-  \]
+and so we may define $\oc f$ to be the anamorphism $\fcoal{\comp{\wk_{B,\oc A}}{\comp{f\tensor\id_{\oc A}}{\comp{\der_A\tensor\id_{\oc A}}{\mu_A}}}}\from \oc A \to \oc B$.
 
 \begin{proposition}\label{StrongMonoidalFunctorActual}
-  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
+  $f\mapsto\oc f$ respects composition, so $\oc$ is a functor.
 Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
@@
  to be the catamorphism of the $A \sequoid \blank$ algebra:
-$$A \sequoid (!A \otimes !A) %\stackrel{\langle \id, A \sequoid \sym\rangle}{\cong} 
-\cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)$$
+\[
+  A \sequoid (!A \otimes !A) %\stackrel{\langle \id, A \sequoid \sym\rangle}{\cong} 
+\cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)
+\]
 This satisfies the further requirements of a \emph{linear category} in the sense of \cite{Bierman}, although it does not appear to be possible to show that it is the cofree commutative comonoid.} :
@@
 
-We give a brief summary of the construction of the category of transfinite games.  %Some more details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
+We give a brief summary of the construction of the category of transfinite games.
 
@@
 \begin{definition}
-  A \emph{game} or a \emph{game over $\alpha$} or an \emph{$\alpha$-game} is a tuple $A=(M_A,\lambda_A,\zeta_A,P_A)$, where:
-  \begin{itemize}
-    \item $M_A$ is a set of moves
-    \item $\lambda_A\from M_A\to\OP$ designates each move as an \emph{$O$-move} or a \emph{$P$-move}
-    \item $P_A\subset M_A^{*<\alpha}$ is a non-empty prefix-closed set of transfinite sequences of moves from $M_A$, called \emph{positions}.
-We say that $s$ is a \emph{successor position} if the length of $s$ is a successor ordinal and we say that $s$ is a \emph{limiting} position if the length of $s$ is a limit ordinal.
-    \item $\zeta_A\from P_A\to\OP$ designates each position as an \emph{$O$-position} or a \emph{$P$-position}.
-  \end{itemize}
-  such that:
-  \begin{description}
-    \item[Consistency] If $sa\in P_A$ is a successor position, then $\zeta_A(sa) = \lambda_A(a)$
-    \item[Alternation] If $s,sa\in P_A$, then $\zeta_A(s) = \neg\zeta_A(sa)$
-    \item[Limit closure] If $s\in M_A^{*<\alpha}$ is a limiting position such that $t\in P_A$ for all proper prefixes $t\pprefix s$, then $s\in P_A$.
-  \end{description}
-
-  We say that a game $A$ is \emph{positive} if $\zeta_A(\emptyplay)=O$ and \emph{negative} if $\zeta_A(\emptyplay) = P$.
-We say that $A$ is \emph{completely negative} if $\zeta_A(s)=P$ for all limiting plays $s$.
+  A (completely negative) \emph{game} or a \emph{game over $\alpha$} or an \emph{$\alpha$-game} is given by a forest (i.e., a prefix-closed set) $P_A$ of alternating transfinite sequences of $O$-moves and $P$-moves of length less than $\alpha$ and a function $\zeta_A\from P_A\to\OP$ that designates each position as an $O$-position or a $P$-position.
+We require that $sa$ is a $P$-position if $a$ is a $P$-move and and $O$-position if $a$ is an $O$-move, so $\zeta_A$ only gives us information about plays of limiting length.
+
+  $P_A$ is subject to a continuity condition: if $s$ is a sequence of moves whose length is a limit ordinal and $t\in P_A$ for all proper prefixes $t\pprefix s$, then $s\in P_A$.
+
+  We say that a game $A$ is \emph{completely negative} if every position of limiting length is a $P$-position.  
 \end{definition}
 
-Apart from the possibly transfinite length of sequences of moves, the only new thing in this definition is the function $\zeta_A$, which we met briefly when defining win-games.
-Thanks to the consistency condition, $\zeta_A$ gives us no new information for successor positions; it is necessary in order to tell us which player is to move at limiting positions.
-
 \begin{definition}
-  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the following conditions:
-  \begin{description}
-    \item[Closure under $O$-replies] If $s\in\sigma$ is a $P$-position and $sa\in P_A$, then $sa\in\sigma$.
-    \item[Determinism] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
-  \end{description}
+  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty subforest (prefix-closed subset) of $P_A$ that satisfies closure under $O$-replies and the determinism condition, just as for finite strategies.
 \end{definition}
 
-Given games $A$ and $B$, we may form their product $A\times B$, tensor product $A\tensor B$, linear implication $A\implies B$ and sequoid $A\sequoid B$ in roughly the same way that we construct these connectives for finite-length games.
-The only point we need to take care of is the behaviour of the $\zeta$-functions at limit ordinals.
-We do this according to the following formulae:
-\begin{gather*}
-  \zeta_{A\times B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
-  \zeta_{A\tensor B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
-  \zeta_{A\implies B}(s) = \zeta_A(s) \Rightarrow \zeta_B(s) \\
-  \zeta_{A\sequoid B}(s) = \zeta_A(s) \wedge \zeta_B(s)
-\end{gather*}
-Here, $\wedge$ and $\Rightarrow$ are the usual propositional connectives on $\{T,F\}$, but with $T$ replaced by $P$ and $F$ replaced by $O$.
-
-Once we have defined our connectives, we may define a \emph{morphism} from $A$ to $B$ to be a strategy for $A\implies B$ and we may define composition of morphisms in the usual way: given games $A$, $B$ and $C$, and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we define
-\[
-  \sigma\|\tau = \{\s\in (M_A \cprd M_B \cprd M_C)^{*<\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
-  \]
-and then we define
-\[
-  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
-  \]
-\begin{remark}
-  Since $\alpha$ is additively decomposable, the interleaving of two sequences of length less than $\alpha$ must itself have length less than $\alpha$.
-This is important: if we allow $\alpha$ to be an additively decomposable ordinal, then it is possible to construct two strategies whose composite is not closed under $O$-replies because a particular reply in the interleaving of two sequences occurs at time later than $\alpha$ and so is not included.
-\end{remark}
-
-We can show that this composition is associative and moreover that we obtain a distributive and decomposable sequoidal category.
+We can form the product, tensor product, sequoid, exponential and linear implication in the same way that we do for finite games.
+The $\zeta$-functions are extended to connectives according to the propositional formulae given for win-games above.
+If $A$ and $B$ are completely negative, then so are $A\times B$, $A\tensor B$, $A\sequoid B$ and $\oc A$, but $A\implies B$ might not be completely negative.
+
+Given games $A,B,C$, strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we may compose $\sigma$ and $\tau$ in the same way that we compose strategies for finite games (but we have to use the fact that $\alpha$ is additively indecomposable so that we can ensure that the interleaving of sequences of length less than $\alpha$ still has length less than $\alpha$).
+
+We can show that this composition is associative and moreover that we obtain a distributive and decomposable sequoidal category whose objects are completely negative games.
 We call this category $\G(\alpha)$ and call the corresponding strict subcategory $\G_s(\alpha)$.
 The hardest part of this is showing that the category is monoidal closed, because the linear implication of completely negative games is not necessarily completely negative.
+It turns out that there is always a `minimal' completely negative game extending $A\implies B$, which gives us the monoidal closed structure, but we will not discuss this here, since monoidal closedness is not particularly important to any of our constructions.
 
@@
 
-\bibliography{bibliography}
+\bibliography{bibliography}\vfill
 
@@
 \begin{proof}
-  We may paste together diagrams \eqref{definitionOfInt} and \eqref{definitionOfSigma} to form the following diagram (where we shall omit subscripts where there is no ambiguity):
+  We may paste together the anamorphism diagrams for $\int_A$ and $\sigma_A$ to form the following diagram (where we shall omit subscripts where there is no ambiguity):
   \begin{equation*}
@@
 
-Now we are ready to show that $\sigma\mapsto\oc \sigma$ respects composition.
-Let $A,B,C$ be objects, let $\sigma$ be a morphism from $A$ to $B$ and let $\tau$ be a morphism from $B$ to $C$.
-Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc\sigma$, $\oc\tau$, we may construct a commutative diagram:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[d, "\oc\sigma"']
+Now we are ready to show that $f\mapsto\oc f$ respects composition.
+Let $A,B,C$ be objects, let $f$ be a morphism from $A$ to $B$ and let $g$ be a morphism from $B$ to $C$.
+Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc f$, $\oc g$, we may construct a commutative diagram:
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\mu"] \arrow[d, "\oc f"']
       & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-        & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
+        & A \tensor \oc A \arrow[r, "f\tensor\id"]
           & B \tensor \oc A \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
-            & B \sequoid \oc A \;\times\; \oc A \sequoid B \arrow[d, "\id\sequoid\oc\sigma\;\times\;\oc\sigma\sequoid\id"] \\
-    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc \tau"']
+            & B \sequoid \oc A \;\times\; \oc A \sequoid B \arrow[d, "\id\sequoid\oc f\;\times\;\oc f\sequoid\id"] \\
+    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc g"']
       & \oc B \tensor \oc B \arrow[rr, "\der\tensor\id"]
         &
-          & B \tensor \oc B \arrow[r, "\dec"] \arrow[d, "\tau\tensor\id"]
+          & B \tensor \oc B \arrow[r, "\dec"] \arrow[d, "g\tensor\id"]
             & B \sequoid \oc B \;\times\; \oc B \sequoid B \\
@@
         &
-          & C \tensor \oc B \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\tau"']
-            & C \sequoid \oc B \;\times\; \oc B \sequoid C \arrow[d, "\id\sequoid\oc\tau\;\times\oc\tau\sequoid\id"] \\
+          & C \tensor \oc B \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc g"']
+            & C \sequoid \oc B \;\times\; \oc B \sequoid C \arrow[d, "\id\sequoid\oc g\;\times\oc g\sequoid\id"] \\
     \oc C \arrow[r, "\mu"]
@@
   \]
-Here, the outermost (solid) shapes are the product of shapes that commute by the definition of $\oc\sigma$, $\oc\tau$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
+Here, the outermost (solid) shapes are the product of shapes that commute by the definition of $\oc f$, $\oc g$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
 The smaller squares on the right hand side commute because $\dec$ is a natural transformation.
@@
   \begin{tikzcd}
-    \oc A \arrow[r, "\comp{(\sigma\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc\sigma"']
-      &[72pt] B \tensor \oc A \arrow[r, "\tau\tensor\id"] \arrow[d, "\id\tensor\oc\sigma"']
-        & C \tensor \oc A \arrow[d, "\id\tensor\oc\sigma"] \\
-    \oc B \arrow[d, "\oc\tau"']
-      & B \tensor\oc B \arrow[r, "\tau\tensor\id"] \arrow[d, "\tau\tensor\oc\tau"']
-        & C \tensor \oc B \arrow[dl, "\id\tensor\oc\tau"] \\
+    \oc A \arrow[r, "\comp{(f \tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
+      &[72pt] B \tensor \oc A \arrow[r, "g \tensor\id"] \arrow[d, "\id\tensor\oc f"']
+        & C \tensor \oc A \arrow[d, "\id\tensor\oc f"] \\
+    \oc B \arrow[d, "\oc g"']
+      & B \tensor\oc B \arrow[r, "g\tensor\id"] \arrow[d, "g\tensor\oc\tau"']
+        & C \tensor \oc B \arrow[dl, "\id\tensor\oc g"] \\
     \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
@@
   \]
-We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and re-apply $\wk$ on the right hand side:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\comp{((\comp\tau\sigma)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc\sigma"']
-      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc\sigma"'] \arrow[r, "\wk"]
-        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
-    \oc B \arrow[d, "\oc\tau"']
-      & C \tensor \oc B \arrow[d, "\id\tensor\oc\tau"'] \arrow[r, "\wk"]
-        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc\tau"] \\
+We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and apply $\wk$ on the right hand side:
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
+      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc f"'] \arrow[r, "\wk"]
+        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc f"] \\
+    \oc B \arrow[d, "\oc g"']
+      & C \tensor \oc B \arrow[d, "\id\tensor\oc g"'] \arrow[r, "\wk"]
+        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc g"] \\
     \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
@@
 \[
-  \comp{\oc\tau}{\oc\sigma} = \fcoal{\comp{\wk}{\comp{((\comp\tau\sigma)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp\tau\sigma)
+  \comp{\oc g}{\oc f} = \fcoal{\comp{\wk}{\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp g f)
   \]
@@
 
+\section{Notes on the construction of transfinite games}
+
+We expand briefly on the construction of transfinite games.
+
+Fix an additively indecomposable ordinal $\alpha=\omega^\beta$.
+
 \end{document}

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Started writing section on transfinite game construction.

@@
 Fix an additively indecomposable ordinal $\alpha=\omega^\beta$.
+If $X$ is a set, write $X^{*<\alpha}$ for the set of sequences of elements of $X$ of length less than $\alpha$.
+Define a \emph{game over $\alpha$} to be a tuple $(M_A,\lambda_A,\zeta_A,P_A)$, where
+\begin{itemize}
+  \item $M_A$ is a set of moves
+  \item $\lambda_A\from M_A\to\OP$ designates each move as an \emph{$O$-move} or a \emph{$P$-move}
+  \item $P_A\subset M_A^{*<\alpha}$ is a prefix-closed set of positions
+  \item $\zeta_A\from P_A\to\OP$ designates each position as either an \emph{$O$-position} or a \emph{$P$-position}.  
+\end{itemize}
+
+We require that a position ending in a $P$-move be a $P$-position and that a position ending in an $O$-move be an $O$-position.
+We require also that the sequences in $P_A$ be \emph{alternating}: if $sa\in P_A$, then $\zeta_A(s)=\neg\zeta_A(sa)$.
+Lastly, we require that $P_A$ be \emph{limit-closed}: if $s\in M_A^{*<\alpha}$ has length a limit ordinal, and if $t\in P_A$ for all proper prefixes $t\pprefix s$, then $s\in P_A$.
+
+We say that a game $A$ is \emph{completely negative} if all plays of limit-ordinal length are $P$-positions.
+
+A \emph{strategy} for a game $A$ is a non-empty prefix-closed subset of $P_A$ such that if $sa\in P_A$ is an $O$-position and $s\in\sigma$, then $sa\in\sigma$.
+A strategy is \emph{deterministic} if whenever $sa,sb\in\sigma$ are $P$-positions, we have $a=b$.
+
+Let $A,B$ be completely negative games.
+We write $P_A\|P_B$ for the set of interleavings of sequences from $P_A$ with sequences from $P_B$: that is, sequences $s\in (M_A\sqcup M_B)^{*<\alpha}$ such that $s\vert_A\in P_A$ and $s\vert_B\in P_B$.
+We write $\oc P_A$ for the set of interleavings of countably many copies of $A$.
+We may then define functions $\zeta_{A\tensor B},\zeta_{A\implies B},\zeta_{A\sequoid B}\from P_A\|P_B\to\OP$:
+\begin{gather*}
+  \zeta_{A\tensor B}(s) = \zeta_{A\sequoid B}(s) = \zeta_A(s)\wedge\zeta_B(s)\\
+  \zeta_{A\implies B}(s) = \zeta_A(s) \Rightarrow \zeta_B(s)
+\end{gather*}
+and $\zeta_{\oc A}\from \oc P_A\to \OP$:
+\[
+  \zeta_{\oc A}(s) = \bigwedge_{n\in\omega}\zeta_A(s\vert_n)
+  \]
+This allows us to define the connectives:
+\begin{gather*}
+  A \tensor B = (M_A \cprd M_B, \lambda_A \cprd \lambda_B, \zeta_{A\tensor B}, P_{A\tensor B})\\
+  A \sequoid B = (M_A \cprd M_B, \lambda_A \cprd \lambda_B, \zeta_{A\sequoid B}, P_{A\sequoid B})\\
+  A \implies B = (M_A \cprd M_B, (\neg\circ\lambda_A) \cprd \lambda_B, \zeta_{A\implies B}, P_{A\implies B})\\
+  \oc A = (M_A\times \omega, \lambda_A \circ \pr_1, \zeta_{\oc A}, P_{\oc A})
+\end{gather*}
+
+Here, $P_{A\tensor B}$ and $P_{A\implies B}$ are the largest subsets of $P_A\|P_B$ that satisfy the alternating condition with respect to $\zeta_{A\tensor B}$ and $\zeta_{A\implies B}$.
+$P_{A\sequoid B}$ is the subset of $P_{A\tensor B}$ consisting of those positions that start with a move in $A$.
+$P_{\oc A}$ is the largest subset of $\oc A$ that is alternating with respect to $\zeta_{\oc A}$.
+
+We may also define products in the same way we define them for win-games.
+
+The following lemma is important for proving that composition works.
+
+\begin{lemma}\label{signProfileLemma}
+  Let $A$ be a completely negative game and let $B$ be an arbitrary game.  Let $s\in P_{A\implies B}$.  Then $s$ satisfies one of the following \emph{sign profiles}:
+  \[
+    \begin{array}{cc}
+      \zeta_A(s\vert_A) & \zeta_B(s\vert_B)\\
+      \hline
+      O & O \\
+      P & P \\
+      P & O
+    \end{array}
+    \]
+\end{lemma}
+\begin{proof}
+  Induction on the length of $s$.
+Suppose first that $s=s'a$.
+If $a$ is an $O$-move, then $s'a$ is an $O$-position, so $s'a$ must have sign profile $PO$, by the definition of $\zeta_{A\implies B}$.
+Otherwise, $s'$ must be an $O$-position, so it must have sign profile $PO$.
+Since the sign profile of $s'a$ can only differ from that of $s'$ in one place, it must have one of the other two sign profiles in the table.
+
+  Now suppose that $s$ is a limiting-length position.
+If $s\vert_A$ has limiting length, we win immediately, since $A$ is completely negative.
+Otherwise, $s\vert_A$ has successor length.
+Let $t\prefix s$ be the shortest prefix of s containing $s\vert_A$ as a subsequence.
+Then $t$ is has successor length, so is a proper prefix of $s$.
+We therefore have $tb\pprefix s$, where $b$ is a move in $B$.
+By induction, $t$ and $tb$ have distinct sign profiles drawn from the table above; the only possibility is that one has sign profile $PO$ and the other has sign profile $PP$.
+Therefore, $s\vert_A$ is a $P$-position and we win.
+\end{proof}
+
+Let $A,B$ be completely negative games and let $C$ be an arbitrary game.  Let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We define:
+\[
+  \sigma\|\tau = \{\s\in (M_A\cprd M_B \cprd M_C)^{*<\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
+  \]
+and then define
+\[
+  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
+  \]
+We use Lemma \ref{signProfileLemma} to show that $\comp\tau\sigma$ is alternating.  Note first that if $\s\in\sigma\|\tau$, then $\s$ must have one of the following sign profiles:
+\[
+  \begin{array}{ccc}
+    \zeta_A(\s\vert_A) & \zeta_B(\s\vert_B) & \zeta_C(\s\vert_C) \\
+    \hline
+    P & P & P \\
+    P & P & O \\
+    P & O & O \\
+    O & O & O
+  \end{array}
+  \]
+By alternation in $\sigma$ and $\tau$, we may only move between adjacent rows as we step through $\sigma$.
+The sign profile of $\s\vert_{A,C}$ is given by the outer two columns; we see that as we step through $\s\vert_{A,C}$, this sign profile must also be alternating.
+
+Now we show that $\comp\tau\sigma$ is a valid strategy.
+Suppose that $s\in\comp\tau\sigma$ is a $P$-position and that $sa\in P_{A\implies C}$.
+Then we have $s=\s\vert_{A,C}$, where $\s\in\sigma\|\tau$.
+We claim that $\s a\in\sigma\|\tau$.
+Assume that $a$ is a move in $A$.
+Then $\s\vert_{A,C}$ must have sign profile $OO$ and so $\s$ must have sign profile $OOO$.
+It follows that $\s\vert_{A,B}$ has sign profile $OO$ and so $a$ is a legal reply in $A\implies B$.
+Therefore, $\s a\in\sigma\|\tau$ and so
 

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Removed it again.
Fixed up references.

--- 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
 Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed.
-(This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{Laf}.
+(This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{LafontCofCommCom}.
 The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra).
@@
 \end{proof}
+
+In particular, $\oc A$ is the final coalgebra for $A\sequoid\blank$.  But, as we showed above, it is not the cofree commutative coalgebra over $A$.
 
@@
 By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.  
-
-\section{Notes on the construction of transfinite games}
-
-We expand briefly on the construction of transfinite games.
-
-Fix an additively indecomposable ordinal $\alpha=\omega^\beta$.
-
 \end{document}

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Changed title.

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
+\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
 \titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Fixed up a few things.

--- 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
+\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
 \titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column
@@
 It is straightforward to show that:
-% $A^*$ is a \emph{minimal invariant} for $F(A,\_)$ with respect to the inclusion order on $\Rel$ and so:
 \begin{lemma}$(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
@@
 
-%By distributivity of $\oplus$ over  $\otimes$ we have a natural transformation $t_{A,S}: F(A,S) \otimes S' \rightarrow F(A,S \otimes S')$.
-We may use this to encapsulate  state transformers of general form: given $f:A \otimes S \rightarrow B \otimes S$, taking the anamorphism of the $F(B,\_)$-colagebra:
-%$$A^* \otimes S  \stackrel{\alpha_A \otimes S}{\longrightarrow} F(A,A^*) \otimes S \stackrel{t}{\longrightarrow} F(A,A^* \otimes S)$$
-
  Distributivity of $\oplus$ over $\otimes$ implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
 This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
-%i.e.
-given morphisms $f_1:A_1 \otimes S \rightarrow B_1 \otimes S, \ldots , f_n:A_n \otimes S \rightarrow B_n \otimes S$, encapsulating  $\dist;(f_1 \oplus \ldots \oplus f_n);\dist^{-1}$, gives a morphism from $(A_1 \oplus \ldots \oplus A_n)^* \otimes S$ into $(B_1 \oplus \ldots \oplus B_n)^*$.
 For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contensts of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
@@
 Hence, we turn to the richer structures of game semantics.
-%However,  the richer structure of
-%game semantics does support a coalgebraic cofree commutative comonoid. 
-% As we shall show by example and counterexample, the richer structure the relationship between initial and final coalgebras, and cofree objects is more subtle.
-%  (note, for example, that any final coalgebra in $\Rel$ must be bifree, by its self-duality).
  \subsection{The cofree commutative comonoid as a final colagebra}
 We now outline the remainder of the paper.
-Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.} %Under a simple interpretation, $A\sequoid B$ is the same as the game $A\tensor B$, except that the first move must take place in $A$.
+Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.}
  In this setting, we  can model a state transformer for a program as a morphism $S \to A \sequoid S$ --- i.e., a coalgebra for the functor $A\sequoid\blank$.
@@
 \subsection{Game semantics and the sequoidal operator}
-
-To get around the problems caused by the non-commutativity of the comonoid in the sets-and-relations model, we shall consider a game semantics model, in which we will be able to construct cofree commutative comonoids.
 We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.
@@
   Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing all isomorphisms in $\C$ and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
-
-  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
-In that case, we say that $\C$ is \emph{decomposable} if the natural transformations
-  \begin{gather*}
-    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
-    \dec^0 \from I \to 1
-  \end{gather*}
-  are isomorphisms and we say that $\C$ is \emph{distributive} if the natural transformations
-  \begin{gather*}
-    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
-    \dist_{(A_i\colon i\in I),C} = \langle (\pr_i\sequoid\id_C\suchthat i\in I)\rangle \from \left(\prod_{i\in I} A_i\right) \sequoid C \to \prod_{i\in I}(A_i\sequoid C) \\
-    \dist_{A,0}\from 1\sequoid A\to 1
-  \end{gather*}
-  are isomorphisms.
-\end{definition}
-\begin{definition}
-  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
-
- We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
-So if $\C$ has all finite products, 
+We say that $\C$ is \emph{inclusive} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing all isomorphisms in $\C$ and the morphisms $\wk_{A,B}$, and $J$ is the inclusion functor.
+
+ We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \otimes B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \otimes B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \otimes B \rightarrow B \sequoid A$.
+$\C$ is \emph{distributive}  if whenever the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pi_l \sequoid C,\pi_r \sequoid C$.
+So if $\C$ is Cartesian (has all finite products), 
 the natural transformations
@@
     \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
-   % \dec^0 \from I \to 1 \\
     \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
@@
 
+\begin{definition}
+  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
+
+ We say that $\C$ is \emph{decomposable} if $I$ is a terminal object for $\C$ and if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
+So if $\C$ has all finite products, 
+the natural transformations
+  \begin{gather*}
+    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
+    \dec^0 \from I \to 1 \\
+    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
+    \dist_{A,0}\from 1\sequoid A\to 1
+  \end{gather*}
+  are isomorphisms.
+\end{definition}
+
 We shall also use the fact that our category of games is \emph{affine} - so the natural transformation $\dec^0\from I \to 1$ is an isomorphism.
 This is not strictly necessary, and techniques are available to obtain similar results in the non-affine case (see \cite{jimNonAffine}, for example), but it will greatly simplify our presentation.
-
-The games model satisfies an analog of monoidal closedness, but we will not give that here (see \cite{laird02}).
  We see that $\G$ is a prototype example of a distributive, decomposable sequoidal category.
@@
 If a distributive sequoidal category satisfies the same property, we say that it is \emph{strong distributive}.
-\begin{proposition}Any strong distributive decomposabe sequoidal category has all symmetric tensor powers, and these are preserved by the tensor.  
+\begin{proposition}Any strong distributive decomposable sequoidal category has all symmetric tensor powers, and these are preserved by the tensor.  
 \end{proposition} 
@@
 We define a \emph{winning strategy} on $(A,\zeta_A)$ to be a total strategy $\sigma$ on $A$ such that $\zeta_A(s)=P$ whenever $s$ is an infinite sequence, all of whose finite prefixes are in $\sigma$.
-It is known (see \cite{abramskyjagadeesangames}) that the composition of winning strategies is winning and that we get a decomposable, distributive sequoidal closed category $\W$ with $\oc A$ as the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ \cite{martinsthesis}.
+It is known (see \cite{abramskyjagadeesangames}) that the composition of winning strategies is winning and that we get a decomposable, distributive sequoidal category $\W$ with $\oc A$ as the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ \cite{martinsthesis}.
 
@@
 \[
-  A \sequoid (!A \otimes !A) %\stackrel{\langle \id, A \sequoid \sym\rangle}{\cong} 
+  A \sequoid (!A \otimes !A) 
 \cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)
@@
 It is not necessary for the final $A \sequoid\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid.
-An example is provided by  the category $\W$ of win-games and winning strategies, which is sequoidal closed and decomposable.
-To show that the  final $A \sequoid\_$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\fix_A(f);f = \fix(f)$.
+An example is provided by  the category $\W$ of win-games and winning strategies, which is \emph{sequoidal closed} (the restriction of the functor  $A \multimap\blank$ to strict strategies is right adjoint to $\blank \sequoid A$, and inclusion sends this adjunction to the usual monoidal closure).
+To show that the  final $A \sequoid\blank$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\comp{f}{\fix_A(f)} = \fix(f)$.
 \begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \sequoid\_$-algebra. Then we may define a fixed point operator on $\C$.  
@@
 
-In particular, $\oc A$ is the final coalgebra for $A\sequoid\blank$.  But, as we showed above, it is not the cofree commutative coalgebra over $A$.
+In particular, $\oc A$ is the carrier of the final coalgebra for $A\sequoid\blank$.  But, as we saw before, it is not the carrier for the cofree commutative comonoid over $A$.
 
@@
 By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.
+
 \end{document}

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Changed title.

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
+\title{Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
 \titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column

### 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Added missing bracket.

@@
 In the general case, we deduce that $\alpha_A$ is a morphism in $\C_s$.
-  \item[Final Sequence] If $\C$ is a category with enough limits and $F$ is an endofunctor on $\C$, we may build up an ordinal indexed sequence of objects and morphisms of $\C$ (that is, a functor $\oppcat{\Ord}\to\C$, where $\Ord$ is the category of ordinals and prefix inclusions:
+  \item[Final Sequence] If $\C$ is a category with enough limits and $F$ is an endofunctor on $\C$, we may build up an ordinal indexed sequence of objects and morphisms of $\C$ (that is, a functor $\oppcat{\Ord}\to\C$, where $\Ord$ is the category of ordinals and prefix inclusions):
     \[

### 2017-05-08 nondeterminism/nondeterminism.tex
A whole bunch of things.

@@
 \input{../common/preamble}
-
-\newcommand{\stle}{{\;\le_s\;}}
-\newcommand{\exle}{\sqsubseteq}
-\newcommand{\exlub}{\bigsqcup}
-\newcommand{\dv}{{\text{\lightning}}}
-\DeclareMathOperator{\pocl}{pocl}
-\newcommand{\opto}{\longrightarrow}
-\newcommand{\n}{{\mathtt{n}}}
-\newcommand{\IfO}{{\mathtt{If0}\;}}
-\newcommand{\suc}{{\mathtt{suc\;}}}
-\newcommand{\0}{{\mathtt{0}}}
-\newcommand{\plot}{\triangleleft}
 
@@
 
-\subsection{Soundness and adequacy}
+\subsection{Consistency}
 
@@
 \end{theorem}
+
+\subsection{The language OBFPCF}
+
+To prove computational adequacy, our first step is to modify our language.
+We remove the recursion combinator $\Y_T^\alpha$ and replace it with a set of constants $\Y_T^\alpha$ of type $(T\to T)\to T$, where $\alpha$ ranges over the ordinals.
+
+The operational semantics of the operators $\Y_T^\alpha$ is as follows:
+\[
+  \begin{tabular}{cc}
+    $\inferrule*[right=$\alpha<\beta$]{ }{\Y_T^\beta M \opto M(\Y_T^\alpha M)}$
+      & $\inferrule*[right=]{ }{\Y_T^0 M \opto \Omega}$
+  \end{tabular}
+  \]
+Thus, $\Y_T^n$ denotes a recursion that can take at most $n$ steps, $\Y_T^\omega$ denotes a recursion that can take $n$ steps, where $n$ is a number chosen at the start of the evaluation, and so on.
+We call this new language \emph{Ordinal Bounded Fair PCF}, or OBFPCF.
+
+Note, however, that it will not be sufficient to define must-convergence for the new language directly from the operational semantics.
+Take the factorial function $\nat\to\nat$, for instance, which is usually defined as $\Y F$, where $F=\lambda f.\lambda n.\IfO n (\suc \0) (\lambda m.n\times(f m))$.
+The number of recursion steps is unbounded, but is always known at the start of evaluation.
+Thus, we should expect to be able to define the factorial function as $\Y_{\nat\to\nat}^\omega F$.
+However, if we try to evaluate, say, $1!$, we end up with the following possible evaluation sequence:
+\[
+  \Y_{\nat\to\nat}^\omega F 1 \opto F (\Y_{\nat\to\nat}^0 F) \;1 \opto \Y_{\nat\to\nat}^0 F\;0\opto\Omega \to \cdots
+  \]
+which is infinite.  The problem is that we have passed immediately down to $\Y^0$, when we could have completed the evaluation by passing down to $\Y^1$.
+
+\begin{definition}
+  Let $M$ be a term of OBFPCF.  We define the \emph{shadow} $\shad M$ of $M$ to be the FPCF term formed by replacing every instance of $\Y_T^\alpha$ with $\Y_T$ for all $\alpha$.
+
+  If $M$ is a term in some programming language, we define an \emph{evaluation tree} to be a rooted tree $T$ with vertices $v$ labelled by terms $T(v)$ of that language such that:
+  \begin{itemize}
+    \item The root is labelled with $M$
+    \item If $v$ is a vertex with label $N$ and $w$ is a child of $v$ with label $P$ then $N\opto P$
+    \item Distinct children of the same vertex have distinct labels
+  \end{itemize}
+  For any term $M$, there is clearly a unique maximal such tree, which we denote by $\tree_M$.
+
+  If $M$ is a term of FPCF, we define a \emph{decoration} of $\tree_M$ to be an evaluation tree $T$ in OBFPCF together with a (depth-preserving) homomorphism of rooted trees $\phi\from T\to\tree_M$ such that for all vertices $v$ in $T$, the label of $\phi(v)$ is the shadow of the label of $v$:
+  \[
+    \tree_M(\phi(v)) = \shad(T(v))
+    \]
+  If $M$ is a term of OBFPCF, we say that $M$ \emph{must converge}, and write $M\mustconverge$, if:
+  \begin{itemize}
+    \item $\shad M\mustconverge$
+    \item There is a decoration $T$ of $\tree_{\shad M}$ such that the root of $T$ is labelled with $M$.
+  \end{itemize}
+\end{definition}
+
+\begin{lemma}
+  Let $M$ be a term of FPCF such that $M\mustconverge$.
+Then there exists some term $M'$ of OBFPCF such that $M=\shad M'$ and $M'\mustconverge$.
+Moreover, for every instance of a constant $\Y_T^\alpha$ in $M'$, we have $\alpha<\omega_1$.
+  \begin{proof}
+    Since $M\mustconverge$, $\tree_M$ is a well-founded tree.
+We need to define a decoration of $\tree_M$.
+We do this using the standard definition of the ordinal depth of a tree.
+Let $T$ have the same vertices as $\tree_M$.
+Then we recursively tag the vertices of $T$ with ordinals as follows: we tag a vertex $v$ with $\alpha$ if $v$ is a leaf of the tree formed by removing all vertices that have been tagged with $\beta<\alpha$.
+Since $T$ is well-founded, this process must terminate.
+Thus, a vertex $v$ is tagged with the supremum of the successors of the tags of its children.
+Since there are at most countably many children of any vertex, we inductively show that the tag on each vertex is the supremum of countably many countable ordinals, so it is countable.
+
+    We then relabel the vertices $v$ of $T$ inductively as follows: first, we go through the tree and decorate every instance of $\Y$ on a vertex $v$ with the tag of $v$.
+Presently, this is not a valid evaluation tree, since if a term contains an instance of $\Y$ but does not reduce via the rule
+    \[
+      \inferrule{ }{\Y_T M \opto M(\Y_T M)}
+      \]
+    then we are not allowed to decorate the instances of $\Y$ in the child with different ordinals from the instances in the parent.
+In this case, redecorate the instances of $\Y$ in the child to match those in the parent.
+We continue by induction over the depth of the tree and end up with a valid decoration $\tree_M$.
+  \end{proof}
+\end{lemma}
+
+\begin{remark}
+  One way to think of must-convergence in OBFPCF is as follows: given an OBFPCF term $M$, we define a two-player game as follows: if $M$ reduces to a unique term $N$, then replace $M$ with $N$ and start again.
+Otherwise, if $M$ reduces according to the rule:
+  \[
+    \inferrule*[right=$n$]{ }{\wn\opto\n}
+    \]
+  then Player I chooses the value of $n$ to replace $\wn$ with and we go back to the beginning.  If $M$ reduces according to the rule
+  \[
+    \inferrule*[right=$\alpha<\beta$]{ }{\Y_T^\beta M \opto M (\Y_T^\alpha M)}
+    \]
+  then Player II chooses an ordinal $\alpha<\beta$ and applies the rule, and we start again.
+If we converge, then we say that Player II wins.
+Otherwise, we say that Player I wins.
+We say that $M\mustconverge$ if and only if Player II has a winning strategy for this game.
+\end{remark}
+
+\begin{example}
+  We illustrate the capabilities of this new language with a small example.  In FPCF, we have a term of type $\nat\to\nat$ given by:
+  \[
+    \Y_{\nat\to\nat}(\lambda f.\lambda n.\IfO n\;\0\;f)
+    \]
+  that returns $\0$ for all inputs.
+
+  Given a term $M$ of type $T\to T$ and a natural number $n$, we may inductively define $\Y_T^n M$ up to observational equivalence within PCF as:
+  \begin{align*}
+    &\Y_T^0 M = \Omega \\
+    &\Y_T^{n+1} M = M (\Y_T^n M)
+  \end{align*}
+  In this case, we see that $\Y_{\nat\to\nat}^n(\lambda f.\lambda n.\IfO n\;\0\;f)$ evaluates to $\0$ if it is passed a number that is less than $n$ and diverges otherwise.  Thus:
+  \[
+    \Y_{\nat\to\nat}^n(\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn
+    \]
+  may diverge for all $n$, while $\Y_{\nat\to\nat}(\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn$ converges.
+This is reflected in our game semantics: the denotation of $\Y_{\nat\to\nat}^n(\cdots)$ converges for inputs less than $n$ and diverges otherwise; if we pass to the stable least upper bound, then the resulting function converges for all inputs.
+Composing the functions with $\wn$ shows us that composition is not continuous with respect to the stable order $\stle$.
+
+  Now consider the following term of OBFPCF:
+  \[
+    \Y^\omega (\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn
+    \]
+  A typical evaluation of this term might look like this:
+  \begin{align*}
+    & \Y^\omega (\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn \\
+    \opto\quad & (\lambda f.\lambda n.\IfO n\;\0\;f) \Y^m (\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn \\
+    \opto\quad & (\lambda n.\IfO n \;\0 \;\Y^m (\lambda f.\lambda n.\IfO n\;\0\;f))\;\wn \\
+    \opto\quad & \IfO \wn\;\0\;\Y^m(\lambda f.\lambda n.\IfO\;n\;\0\;f) \\
+    \opto\quad & \IfO (m+1)\;\0\;\Y^m(\lambda f.\lambda n.\IfO n\;\0\;f) \\
+    \opto\quad & \Y^m(\lambda f.\lambda n.\IfO n\;\0\;f) \;m
+  \end{align*}
+  which diverges, as we saw above.
+The important point is that whatever value of $m$ we choose to decorate $\Y$ with in the second line, there is a possibility that we will nondeterministically choose a value for $\wn$ that is greater than or equal to $m$ and so causes the program to diverge.
+Therefore:
+  \[
+    \Y^\omega (\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn\not\mustconverge
+    \]
+  Now, if we repace $\omega$ with $\omega+1$, we arrive at the original behaviour: we can replace the $\omega+1$ with $\omega$ in the first line so we arrive at:
+  \begin{align*}
+    & \Y^{\omega+1} (\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn \\
+    \opto\quad & (\lambda f.\lambda n.\IfO n\;\0\;f) \Y^\omega (\lambda f.\lambda n.\IfO n\;\0\;f)\;\wn \\
+    \opto\quad & \cdots \\
+    \opto\quad & \Y^\omega(\lambda f.\lambda n.\IfO n\;\0\;f) \;m \\
+    \opto\quad & (\lambda f.\lambda n.\IfO n\;\0\;f) \Y^{m+1}(\lambda f.\lambda n.\IfO n\;\0\;f) \;m \\
+    \opto\quad & \cdots \\
+    \opto\quad & \0
+  \end{align*}
+
+Here, we are able to choose which natural number to decay to after the value for $\wn$ has been chosen, so this term must converge.
+
+Note that although $\Y^{\omega+1}(\lambda f.\lambda n.\IfO n\;\0\;f)$ is operationally equivalent to $\Y(\lambda f.\lambda n.\IfO n\;\0\;f)$, $\Y^\omega(\lambda f.\lambda n.\IfO n\;\0\;f)$ has no equivalent in FPCF.
+Thus, OBFPCF allows us to discern levels of convergence that are invisible in FPCF.
+
+  Importantly, notice that function application \emph{is} now continuous: $\Y^\omega(\cdots)$ is the limit of the $\Y^n(\cdots)$, and $\Y^\omega(\cdots)\;\wn$ may diverge just as $\Y^n(\cdots)\;\wn$ may.
+
+  At the moment, our game semantics is unable to model terms such as $\Y^\omega(\lambda f.\lambda n.\IfO n\;\0\;f)$.  We will need to modify it.
+\end{example}
+
+\subsection{Game semantics for OBFCPF}
+
+\begin{definition}
+  Let $A$ be a game.  A \emph{multistrategy} for $A$ is a stably directed set $\Sigma$ of strategies for $A$ such that for all $\sigma,\tau\in \Sigma$ we have $T_\sigma=T_\tau$.
+
+  Given a multistrategy $\Sigma$, we write $T_\Sigma$ for the unique value of $T_\sigma$, where $\sigma\in\Sigma$.
+
+  We compose multistrategies in the obvious way: let $A,B,C$ be games, let $\Sigma$ be a multistrategy for $A\iimpl B$ and let $\Tau$ be a multistrategy for $B\iimpl C$.  Then we define:
+  \[
+    \icomp\Tau\Sigma = \{\icomp\tau\sigma\suchthat\sigma\in\Sigma,\;\tau\in\Tau\}
+    \]
+  By Lemmas \ref{compositionMonotonicSO} and \ref{exponentiationMonotonicSO}, this is still stably directed.
+
+  We also extend the stable order to multistrategies.  This time, $\stle$ is a preorder rather than being a full order.
+
+  Let $A$ be a game, and let $\Sigma,\Tau$ be multistrategies for $A$.  We say that $\Sigma\stle\Tau$ if for all $\tau\in\Tau$ there exists $\sigma\in\Sigma$ such that $\sigma\stle\tau$.
+
+  We say that $\Sigma \steq \Tau$ if $\Sigma\stle\Tau$ and $\Tau\stle\Sigma$.
+\end{definition}
+
+\begin{lemma}
+  Let $A$ be a game, let $\sigma$ be a strategy for $A$ and let $\Sigma$ be a multistrategy for $A$ such that $\{\sigma\}\steq\Sigma$.
+Then $\sigma\in\Sigma$ and is a $\stle$-least element of $\Sigma$.
+  \begin{proof}
+    Since $\Sigma\stle\{\sigma\}$, we know that $\tau\stle\sigma$ for all $\tau\in\Sigma$.
+Since $\{\sigma\}\stle\Sigma$, we know that $\sigma\stle\tau$ for some $\tau\in\Tau$ and hence by antisymmetry that $\sigma\in\Sigma$.
+  \end{proof}
+\end{lemma}
+
+Conversely, if $\Sigma$ is a strategy with a $\stle$-greatest element $\sigma$, then $\{\sigma\}\steq\Sigma$.
+
+\begin{definition}
+  Let $A$ be a game and let $F$ be a set of multistrategies for $A$ that is directed with respect to $\stle$.  We define a strategy $\exlub F$ given by
+  \[
+    \exlub F = \left\{\left(\bigcup_{\Sigma\in F} T_\Sigma, D_\sigma\right)\;\middle|\;\textrm{$\sigma\in\Sigma$ for some $\Sigma\in F$}\right\}
+    \]
+\end{definition}
+
+\begin{proposition}
+  $\exlub F$ is a valid multistrategy for $A$.
+  \begin{proof}
+    We need to show that for all $\Sigma\in F$ and for all $\sigma\in\Sigma$, $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)$ satisfies the diverge-or-reply rule.
+Let $\Sigma\in F$ and let $\sigma\in\Sigma$.
+Suppose that $s\in T_\Tau$ for some $\Tau\in F$, that $sa\in P_A$ and that $sa\not\in D_\sigma$.
+Since $F$ is stably directed, there exists some multistrategy $\Upsilon\in F$ such that $\Sigma,\Tau\stle\Upsilon$.
+Let $\tau\in\Tau$.
+Then there are $\upsilon_1,\upsilon_2\in\Upsilon$ such that $\sigma\stle\upsilon_1$ and $\tau\stle\upsilon_2$.
+Then, since $\Upsilon$ is stably directed, there is some $\upsilon\in\Upsilon$ such that $\upsilon_1,\upsilon_2\stle\upsilon$.
+In particular, $s\in T_\upsilon$ and $sa\not\in D_\upsilon$.
+Therefore, $sab\in T_\upsilon$ for some $b$ and so $sab\in\bigcup_{\Sigma\in F}T_\Sigma$.
+  \end{proof}
+\end{proposition}
+
+\begin{proposition}
+  $\exlub F$ is a $\stle$-least upper bound for $F$.
+
+  \begin{proof}
+    Let $\Sigma\in F$ and let $\sigma\in\Sigma$.  Then we have $\sigma\stle\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)\in\exlub F$.  So $\exlub F$ is a $\stle$-upper bound for $F$.
+
+    Now suppose that $\Xi$ is some other $\stle$-upper bound for $F$.
+Then for all $\Sigma\in F$ we must have $T_\Sigma\subset T_\Xi$ and so $\bigcup_{\Sigma\in F}T_\Sigma\subset T_\Xi$.
+Now suppose that $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)$ is some element of $\exlub F$, where $\Sigma\in F$ and $\sigma\in\Sigma$.
+We have $\Sigma\stle\Xi$, so there exists some $\xi\in\Xi$ such that $\sigma\stle\xi$.
+We have $\xi = (T_\Xi, D_\xi)$, where $D_\xi\subset D_\sigma$.
+Therefore, $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)\stle\xi$.
+It follows that $\exlub F\stle\Xi$.
+  \end{proof}
+\end{proposition}
+
+Now let $A$ be a game and let $\Sigma$ be a multistrategy for $A\iimpl A$.  We inductively define an ordinal-indexed sequence of multistrategies $\Sigma^\alpha$ for $A\iimpl A$ as follows:
+\begin{itemize}
+  \item $\Sigma^0 = \{\bot\}$
+  \item $\Sigma^{\alpha+1} = \icomp{\Sigma}{\Sigma^\alpha}$
+  \item $\Sigma^{\lambda} = \exlub_{\alpha<\lambda}\Sigma^\alpha$ if $\lambda$ is a limit ordinal
+\end{itemize}
+
+This chain is increasing and so, by Hartogs' Lemma, it must stabilize: there will be some $\Sigma^\mu$ such that $\Sigma^\mu\steq\icomp\Sigma{\Sigma^\mu}$; this will be a $\stle$-least fixed point of the map $\Tau\mapsto\icomp\Sigma\Tau$ on $\steq$-equivalence classes of multistrategies for $A$.
+
+Now suppose that $\Sigma = \{\sigma\}$, where $\sigma$ is some strategy for $A$.
+
+$\cdots$
 

### 2017-05-08 round-corner/paper/lipics-v2016-authors/jim/sequoidal.tex
A whole bunch of things.

--- 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
+\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
 \titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column
@@
 \newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{exercise}{Exercise}
 \theoremstyle{definition}
@@
 \DeclareMathOperator{\pr}{pr}
+\newcommand{\Rel}{{\mathsf{Rel}}}
+\newcommand{\inr}{{\mathsf{inr}}}
+\newcommand{\inl}{{\mathsf{inl}}}
+\newcommand{{\Na}}{{\mathbb{N}}}
+\newcommand{{\cell}}{{\mathsf{cell}}}
+\newcommand{\tr}{\oslash}
+\newcommand{\fix}{{\mathsf{fix}}}
+\newcommand{\eq}{{\mathsf{eq}}}
+%\\write{{\mathtt{write}}}
+\def\read{{\mathtt{read}}}
+\def\({\ensuremath{( \! [}}
+\def\){\ensuremath{] \! )}}
+\newcommand{\perm}{{\mathsf{perm}}}
 \newcommand{\tensor}{\otimes}
@@
 \renewcommand{\implies}{\multimap}
-\newcommand{\comp}[2]{#2 ; #1}
+\newcommand{\comp}[2]{#1 \circ #2}
 \newcommand{\cprd}{\sqcup}
@@
 \newcommand{\G}{\mathcal G}
-\newcommand{\W}{\mathcal W}
 \newcommand{\suchthat}{\;\colon\;}
@@
 \newcommand{\dec}{{\mathtt{dec}}}
-\renewcommand{\int}{{\mathtt{coh}}}
-\renewcommand{\coh}{\int}
+\renewcommand{\int}{{\mathtt{int}}}
 \DeclareMathOperator{\CCom}{CCom}
-\newcommand{\catname}[1]{{\mathsf{#1}}}
+\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
 \newcommand{\Set}{\catname{Set}}
@@
 \newcommand\oppcat[1]{#1^{\mathrm{op}}}
-\newcommand{\bN}{{\mathbb{N}}}
-\newcommand{\OK}{{\mathtt{OK}}}
-\newcommand{\zero}{{\mathtt{zero}}}
-\renewcommand{\succ}{{\mathtt{succ}}}
-\newcommand{\Var}{{\mathtt{Var}}}
-\renewcommand{\read}{{\mathtt{read}}}
-\newcommand{\wwrite}{{\mathtt{write}}}
-\newcommand{\Rel}{\catname{Rel}}
-\newcommand{\inr}{{\mathsf{inr}}}
-\newcommand{\inl}{{\mathsf{inl}}}
-\newcommand{{\Na}}{\bN}
-\newcommand{{\cell}}{{\mathsf{cell}}}
-\newcommand{\fix}{{\mathsf{fix}}}
-\newcommand{\eq}{{\mathsf{eq}}}
-\newcommand{\co}{{\textrm{\textexclamdown}}}
-
-%%OUR
 
@@
 \begin{abstract}
-The non-commutative sequoid operator $\sequoid$ on games was introduced  to capture algebraically the presence of state in history-sensitive strategies in game semantics, by imposing a causality relation on the  tensor product of games.
-Coalgebras for the  functor  $A\sequoid\blank$  --- i.e.
-morphisms from $S$ to $A \sequoid S$ --- may be viewed as state transformers:  if $A\sequoid\blank$ has a \emph{final coalgebra}, $\oc A$, then the anamorphism of such a state transformer encapsulates its explicit state, so that it is shared only between successive invocations.
-
-We study the  conditions under which a final coalgebra $\oc A$ for  $A\sequoid\blank$ is the carrier of a \emph{cofree commutative comonoid} on $A$.
-That is, it is a model of the exponential of linear logic in which we can construct imperative objects such as reference cells  coalgebraically, in a game semantics setting.
-We show that if the tensor \emph{decomposes} into the sequoid,  the final coalgebra $!A$ may be endowed with the structure of the cofree commutative comonoid if the natural isomorphism $\oc (A \times B) \cong \oc A \tensor \oc B$ holds.
-This condition is always satisfied if $\oc A$ is the \emph{bifree algebra} for $A\sequoid\blank$, but in general it is necessary to impose it, as we establish by giving an example of a sequoidally decomposable category of games in which plays will be allowed to have transfinite length.
-In this category, the final coalgebra for the functor $A\sequoid\blank$ is not the cofree commutative comonoid over $A$: we illustrate this by explicitly contrasting the final sequence for the functor $A\sequoid\blank$ with the chain of symmetric tensor powers used in the construction of the cofree commutative comonoid as a limit by  Melli\'es, Tabareau and Tasson.
-
+  In \cite{laird02}, Laird introduces the concept of a \emph{sequoidal category} as a formalization of causality in game semantics.
+A sequoidal category is like a monoidal category with an extra connective, $\sequoid$, that allows one to construct an exponential object as a final coalgebra \cite{martinsthesis},  Under a further hypothesis, it is possible to show that this final coalgebra allows one to construct cofree commutative comonoids in the category, giving us a model of the exponential connective $\oc$ from linear logic.
+In the first part of this note, we review the coalgebraic arguments for constructing the cofree commutative comonoid, which are known but do not yet appear in print.
+In the second part, we show that the extra hypotheses are necessary by outlining a definition of \emph{transfinite game}, in which the carriers of the sequoidal coalgebra and the cofree commutative comonoid do not coincide.
 \end{abstract}
 
-\section{Introduction}
-Game semantics has been used to define a variety of models of higher-order programming languages with  mutable state, including Idealized Algol  \cite{SamsonGuyIAPassive}, and various fragments of ML \cite{AMV,AHM}.
-Unlike traditional denotational semantics, which typically represent imperative programs as state transformers, the state in these models is completely implicit: local declaration of mutable variables is interpreted as composition with a ``history sensitive'' strategy representing a reference cell.
-This is conceptually simple in principle but leads to some quite combinatorial definitions; a more explicit representation of the current state can be very useful for constructing and reasoning about imperative objects.
-In this paper, we use final coalgebras to forge a link between the explicit and implicit representation of state in game semantics.
-We study the conditions under which the \emph{cofree commutative comonoid} in categories of games may be derived from a final coalgebra, relating their underlying structure as models of linear logic to classical coalgebraic techniques for describing state.
-
-\subsection{Defining Higher-order Stateful Objects, Coalgebraically}
-Let us first motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon. 
-A \emph{state-transformer} in a symmetric monoidal category is a morphism $f:A \otimes S \rightarrow B \otimes S$ taking an argument together with an input state to a result together with an output state.
+\section{Defining Higher-order Stateful Objects, Coalgebraically}
+In this section we motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon.
+A \emph{state-transformer} in a symmetric monoidal category is a morphism $f:A \otimes S \rightarrow B \otimes S$ taking an argument together with an input state to a result together with a input state.
 A well-studied \cite{jacobs} technique in semantics is to  use an appropriate final coalgebra to \emph{encapsulate} the state in such a transformer, allowing multiple  successive invocations, each of which passes its output state as an input state to the next invocation.
@@
 For example, consider the category $\Rel$ of sets and relations, with symmetric monoidal structure given by the cartesian product (with unit $I$, the singleton set $\{*\}$).
-This has finite (bi)products (disjoint unions) so we may define the functor $F(A,S) = (A \otimes S) \oplus I$.
-For any object (set) $A$, let $A^*$ be the set of finite sequences of elements of $A$ (i.e.
-the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$.
-It is straightforward to show that:
-\begin{lemma}$(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
+This has finite (bi)products given by the disjoint union of sets: define the functor $F(A,S) = (A \otimes S) \oplus I$
+
+For any object (set) $A$, let $A^*$ be the set $A^*$ of finite sequences of elements of $A$ (i.e.
+the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$
+\begin{lemma}$(A^*,\alpha_A)$ is a final coalgebra  for $F(A,\_)$.
 \end{lemma}
-Since we have a natural transformation  $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $f;\inl_{A,B}:S \rightarrow F(A,S)$, --- i.e.
+\begin{proof}$\Rel$ may be cpo-enriched with the inclusion order: $A^*$ is a \emph{minimal invariant} for $F(A,\_)$ with respect to this order.
+\end{proof}
+Since we have a natural transformation (left injection) $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $f;\inl_{A,B}:S \rightarrow F(A,S)$, --- i.e.
 the unique $F(A,\_)$-coalgebra morphism from $(S,f;\inl)$ into $(A^*,\alpha_{A})$.
-This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A^*)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ and together with the encapsulated morphism with updated internal state.
-
- Distributivity of $\oplus$ over $\otimes$ implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
+This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ and uses it to update the internal state.
+
+By distributivity of $\oplus$ over  $\otimes$ we have a natural transformation $t: F(A,S) \otimes S' \rightarrow F(A,S \otimes S')$.
+We may use this to encapsulate  state transformers of general form: given $f:A \otimes S \rightarrow B \otimes S$, taking the anamorphism of the $F(B,\_)$-colagebra:
+$$A^* \otimes S  \stackrel{\alpha_A \otimes S}{\longrightarrow} F(A,A^*) \otimes S \stackrel{t}{\longrightarrow} F(A,A^* \otimes S)$$
+
+ Distributivity of $\oplus$ over $\otimes$ also implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
 This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
-For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contensts of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
+i.e.
+given morphisms $f_1:A_1 \otimes S \rightarrow B_1 \otimes S, \ldots , f_n:A_n \otimes S \rightarrow B_n \otimes S$, encapsulating  $\dist;(f_1 \oplus \ldots \oplus f_n);\dist^{-1}$, gives a morphism from $(A_1 \oplus \ldots \oplus A_n)^* \otimes S$ into $(B_1 \oplus \ldots \oplus B_n)^*$.
+
+For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a state consisting of a single integer, representing the contents of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
 Thus (with appropriate tagging) it is the relation $\{(i, (\read(i),i))\ |\ i \in \Na\} \cup \{(i,{\mathtt{write}}(j),j)\}$.
-The anamorphism of the coalgebra $\cell;\inl:\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$.
-Composition with this morphism is precisely the interpretation of new variable declaration in the semantics  in $\Rel$ of the prototypical functional-imperative language \emph{Syntactic Control of Interference} (SCI) given in \cite{Mcsci}.
-
-Coalgebraic methods thus give us a recipe for constructing and using categorical definitions of stateful semantic objects.
-In order to fully exploit these, however, we endow $A^*$ with the structure of a \emph{comonoid} in our symmetric monoidal category, by defining morphisms $\delta_A:A^* \rightarrow A^* \otimes A^* = \{(u\cdot v,(u,v))\ |\ u,v \in A^*\}$ and $\epsilon:A \rightarrow I = \{(\varepsilon,*)\}$.
+The anamorphism of the coalgebra $\cell;\inl:\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$ Composition with this morphism is precisely the denotation of new variable declaration in the semantics of  Reynolds \emph{Syntactic Control of Interference} (SCI) in $\Rel$ given in \cite{Mcsci}.
+
+Coalgebraic methods thus give us a recipe for constructing and using categorical definitions of stateful semantic objects, avoiding direct definitions which are rather combinatorial to work with.
+In order to fully exploit these, however, we may endow $A^*$ with the structure of a \emph{comonoid} by defining morphisms $\delta_A:A^* \rightarrow A^* \otimes A^* = \{(u\cdot v,(u,v))\ |\ u,v \in A^*\}$ and $\epsilon:A \rightarrow I = \{(\varepsilon,*)\}$
+
  In fact, this is the \emph{cofree comonoid} on $A$ --- there is a morphism $\eta_A:A^* \rightarrow A = \{(a,a)\ | \ a \in A\}$ such that for any comonoid $(B,\delta_B,\epsilon_B)$, composition with $\eta_A$ defines an equivalence (natural in $B$)  between the morphisms from $B$ into $A$, and the comonoid morphisms from $(B,\delta_B,\epsilon_B)$ into  $(A^*,\delta_A,\epsilon_A)$.
-\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.\footnote{The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
+\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.
+\end{proposition}
+The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
 $(A^*,\alpha^{-1})$ is an initial algebra for $F(A,\_)$ ($\alpha$ must be an isomorphism by Lambek's lemma).
-We leave this as an exercise.}
-\end{proposition}
-This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell.      
-Its main limitation is that we have not defined a \emph{commutative} comonoid  for any non-empty set $A$ (evidently, $\delta$ is not invariant under postcomposition with the symmetry isomorphism of the tensor).
-Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed.
-(This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{LafontCofCommCom}.
+We leave this as an exercise.
+
+This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell, the creation of multiple copies of such procedures ($(\_)^*$ is a monoidal comonad)  etc.
+Its main limitation is that we have not defined a \emph{commutative} monoid --- evidently it is not the case that $\delta_A;\sym_{A,A} = \delta_A$ (where $\sym_{A,B}:A \otimes B \rightarrow B \otimes A$ is the symmetry isomorphism for the tensor) for any non-empty set $A$.
+Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is predetermined.
+This is precisely the situation in SCI, where the typing system allows sharing between across sequential composition, but not between functions and their arguments.
+In order to model sharing of state between functions without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a cofree \emph{commutative} comonoid.
 The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra).
-Hence, we turn to the richer structures of game semantics.
- \subsection{The cofree commutative comonoid as a final colagebra}
-We now outline the remainder of the paper.
-Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.}
- In this setting, we  can model a state transformer for a program as a morphism $S \to A \sequoid S$ --- i.e., a coalgebra for the functor $A\sequoid\blank$.
-The final coalgebra for this functor is the exponential game $!A$ introduced by Hyland \cite{hyland1997games}, which corresponds to a $\omega$-fold sequence $A \sequoid (A \sequoid (A \sequoid \ldots ))$; under appropriate conditions, it is the carrier for the  cofree  commutative comonoid on $A$.
-We aim to characterize these conditions using just the categorical structure,  in order to capture a general class of models and to derive formal principles for coinductively proving  program equivalences.
-In a nutshell, we require that a certain natural morphism $\oc A \tensor \oc B \to \oc (A\times B)$ is an isomorphism.
-This can be used to show that $\oc\blank$ gives rise to a strong monoidal functor.
-Perhaps more surprisingly, it is sufficient to show that $\oc A$ is the cofree commutative comonoid.
-
-This \emph{strong monoidal hypothesis} holds whenever $\oc A$ is a bifree algebra for $A\sequoid\blank$.
-But we are also interested in cases where $\oc A$ is not bifree --- for example, in categories of ``win games'' and \emph{winning strategies}  \cite{hyland1997games}, which lack the partial maps which can be shown to arise in the bifree case.
-To show that the strong monoidal hypothesis is necessary in general, we introduce a  sequoidal category of games with \emph{transfinite} plays in which it does not hold: because a transfinite interleaving of two sequences of length $\omega$ may have length greater than $\omega$, the final coalgebra for $A\sequoid\blank$  (corresponding  to only $\omega$-many copies of the game $A$) cannot be the carrier for the cofree commutative comonoid.
-
-We compare the  coalgebraic construction of the cofree exponential to the explicit characterization of the latter given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} as the limit of a chain of symmetric tensor powers.
-This chain exists in any decomposable sequoidal category: where its limit exists and is preserved by the tensor (the conditions required in \cite{MelliesCofCommCom}) it must be the final coalgebra for $A \sequoid\blank$.
-However, in our categories of transfinite games, and win games and winning strategies (which may be viewed as games of length $\omega+1$), the construction fails --- this limit is not the cofree commutative comonoid.
+By properly reflecting the interleaving between function calls, game semantics does support a coalgebraic cofree commutative comonoid, leading to models of stateful higher-order languages such as Idealized Algol and core ML.
+As we shall show by example and counterexample, the richer structure of games also means that the relationship between initial and final coalgebras, and cofree objects is more subtle  (note, for example, that any final coalgebra in $\Rel$ must be bifree, by its self-duality).
 
@@
 \subsection{Game semantics and the sequoidal operator}
-We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.
-A game $A$ is given by a forest (i.e., a prefix-closed set) $P_A$ of \emph{positions}, which are alternating sequences of $O$-moves and $P$-moves.
-We call a position a \emph{$P$-position} if it ends with a $P$-move and an \emph{$O$-position} if it ends with an $O$-move.
-A \emph{strategy} for a game $A$ is a subforest $\sigma$ of $P_A$ that is closed under $O$-replies to $P$-positions and which satisfies \emph{determinism}: if $sa,sb\in\sigma$, where $s$ is a $P$-position, then $a=b$.
-We will adopt the rule that all positions must start with an $O$-move.
-
-We build connectives on games in the usual way.
-
+
+We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.  A game will be given by a tuple
+\[
+  A = (M_A, \lambda_A, b_A, P_A)
+  \]
+where
+\begin{itemize}
+  \item $M_A$ is a set of moves.
+  \item $\lambda_A\from M_A\to\OP$ is a function designating each move as either an \emph{$O$-move} or a \emph{$P$-move}.
+  \item $b_A\in\OP$ is a choice of starting player.
+  \item $P_A\subset M_A^*$ is a prefix-closed set of alternating plays (so if $sab\in P_A$ then $\lambda_A(a)=\neg\lambda_A(b)$) such that if $as\in P_A$ then $\lambda_A(a)=b_A$.
+\end{itemize}
+
+We call $sa\in P_A$ a \emph{$P$-position} if $a$ is a $P$-move and an \emph{$O$-position} if $a$ is an $O$-move.
+
+A \emph{strategy} for player $P$ for a game $A$ is identified with the set of positions that may arise when playing according to that strategy.
+Namely, it is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the two conditions:
 \begin{description}
-  \item[Product] If $(A_i\suchthat i\in I$ is a collection of negative games, then we write $\prod_{i\in I}A_i$ for the game in which player $O$, on his first move, may play in any of the games $A_i$.
-From then on, play continues in $A_i$.
-If $A_1,A_2$ are games, we write $A_1\times A_2$ for $\prod_{i=1}^2 A_i$.
-  \item[Tensor Product] If $A,B$ are negative games,the tensor product $A\tensor B$ is played by playing the games $A$ and $B$ in parallel, where player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
+  \item[(sO)] If $s\in\sigma$ is a $P$-position and $a$ is an $O$-move such that $sa\in P_A$, then $sa\in\sigma$.
+  \item[(sP)] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
+\end{description}
+
+We shall now concentrate on games $A$ for which $b_A=O$, called \emph{negative games}.  We shall informally describe the standard connectives on negative games:
+
+\begin{description}
+  \item[Product] If $A$ and $B$ are negative games then the \emph{product} $A\times B$ is the game given by placing the game trees for $A$ and $B$ side by side: that is, player $O$ may play his first move either in $A$ or in $B$.
+Thereafter, play continues in the game that player $O$ has chosen.
+  \item[Tensor Product] The tensor product $A\tensor B$ is also played by playing the games $A$ and $B$ in parallel, but this time player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
   \item[Linear implication] The implication $A\implies B$ is played by playing the game $B$ in parallel with the \emph{negation} of $A$ - that is, the game formed by switching the roles of players $P$ and $O$ in $A$.
@@
 
-It is well known (see \cite{abramskyjagadeesangames}, for example) that we may compose strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ to get a morphism $\comp\tau\sigma$ for $A\implies C$ and that this structure gives rise to a monoidal category where objects are games, morphisms from $A$ to $B$ are strategies for $A\implies B$ and the tensor product and linear implication are given by $A\tensor B$ and $A\implies B$.
-We call this category $\G$.
-$\G$ has all products, given by $\prod_{i\in I}A_i$ as above.
+If $A,B,C$ are negative games, $\sigma$ is a strategy for $A\implies B$ and $\tau$ is a strategy for $B\implies C$, then we may form a strategy $\comp\tau\sigma$ for $A\implies C$ by setting
+\[
+  \sigma\|\tau = \{\s\in (M_A\cprd M_B\cprd M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;s\vert_{B,C}\in\tau\}
+  \]
+and then defining
+\[
+  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\comp\tau\sigma\}
+  \]
+It is well known (see, for example, \cite{abramskyjagadeesangames}) that $\comp\tau\sigma$ is indeed a strategy for $A\implies C$ and that this form of composition is associative and has an identity.
+It is also well known that the resulting category $\G$ of games and strategies has products given by the operator $\times$ and a symmetric monoidal closed structure given by the operations $\tensor$ and $\implies$.
 
@@
 
-The sequoid does not give rise to a functor $\G\times\G\to \G$ in the way that the tensor product does: playing strategies $\sigma$ for $A\implies B$ and $\tau$ for $C \implies D$ in parallel does not necessarily give rise to a valid strategy for $(A\sequoid C)\implies (B \sequoid D)$, since player $O$ might end up playing in $C$ before anyone has played in $A$.
-However, if we require that the strategy $\sigma$ is \emph{strict} -- that is, player $P$'s reply to the opening move in $B$ is always a move in $A$ -- then we do get a valid strategy $\sigma\sequoid\tau$ for $(A\sequoid C)\implies (B\sequoid D)$ and, moreover, $\sigma\sequoid\tau$ is strict.
-If we write $\G_s$ for the category of games with \emph{strict} strategies as morphisms, then we see that $\blank\sequoid\blank$ gives us a functor $\G_s\times \G\to\G_s$.
-In fact, the isomorphism $\passoc$ tells us that this functor is a right monoidal category action of $\G$ upon $\G_s$.
+One further question to ask is: does the sequoid operator give rise to a functor $\blank\sequoid\blank\from\G\times\G\to\G$, as the tensor operator does?
+The answer is no: indeed, let $A,B,C,D$ be negative games, let $\sigma$ be a strategy for $A\implies C$ and let $\tau$ be a strategy for $B\implies D$.
+Our aim is to construct a natural strategy $\sigma\sequoid\tau$ for $(A\sequoid B)\implies (C\sequoid D)$.
+There is an obvious way to try and do this: player $P$ should play according to the strategy $\sigma$ whenever player $O$'s last move was in $A$ or $C$, and according to $\tau$ whenever player $O$'s last move was in $B$ or $D$.
+
+We show that this does not in general give us a strategy for $(A\sequoid B)\implies (C\sequoid D)$.
+Suppose that $\sigma$ is such that player $P$'s response to some opening move in $C$ is another move in $C$ and suppose that $\tau$ is such that player $P$'s response to some opening move in $D$ is a move in $B$ (for example, $\tau$ is a copycat strategy).
+Then we end up with the following sequence of events in the game $(A\sequoid B)\implies(C\sequoid D)$  :
+\begin{enumerate}
+  \item Player $O$ starts with a move in $C$ (as he must).
+  \item Player $P$ responds according to $\sigma$ with another move in $C$.
+  \item Player $O$ decides to switch games and play a move in $D$.
+  \item Player $P$ responds according to $\tau$ with a move in $B$.
+\end{enumerate}
+
+But now player $P$'s last move is not a legal move in $(A\sequoid B)\implies(C\sequoid D)$, since no moves have been played in $A$ yet.
+
+We get round this problem by requiring that the strategy $\sigma$ be \emph{strict} -- that is, whatever player $O$'s opening move in $C$ is, player $P$'s reply must be a move in $A$.
+
+\begin{definition}
+  Let $N,L$ be negative games and let $\sigma$ be a strategy for $N\implies L$.  We say that $\sigma$ is \emph{strict} if player $P$'s reply to an opening move in $L$ is always a move in $N$.  
+\end{definition}
+
+Identity strategies are strict and the composition of two strict strategies is strict, so we get a full-on-objects subcategory $\G_s$ of $\G$ where the morphisms are strict strategies.
+Then the sequoid operator gives rise to a functor:
+\[
+  \blank\sequoid\blank\from \G_s\times\G\to\G_s
+  \]
 
@@
 
-We now formalize this into a category-theoretic definition.
+We now have the motivation required to give the definition of a \emph{sequoidal category} from \cite{laird02}.
 
@@
     \item A category $\C_s$
-    \item A right monoidal category action of $\C$ on the category $\C_s$.
-That is, a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ that gives rise to a monoidal functor from $\C$ into the category of endofunctors on $\C_s$.
-We write $\passoc_{A,B,C}\from (A \sequoid B) \sequoid C \to A \sequoid (B\tensor C)$ for the coherence part of the monoidal functor.
+    \item A right monoidal category action of $\C$ on the category $\C_s$.  That is, a functor
+      \[
+        \blank\sequoid\blank\from\C_s\times\C\to\C_s
+        \]
+      together natural isomorphisms
+      \[
+        \passoc_{A,B,C}\from A\sequoid(B\tensor C)\to (A\sequoid B)\sequoid C
+        \]
+      and
+      \[
+        \run_A\from A\sequoid I\toisom A
+        \]
+      subject to the following coherence conditions:
+      \begin{equation*}
+        \begin{tikzcd}
+          A\sequoid(B\tensor(C\tensor D)) \arrow[r, "\passoc_{A,B,C\tensor D}" yshift=0.3em] \arrow[d, "\id_A\sequoid \assoc_{B,C,D}"']
+            & (A \sequoid B) \sequoid (C\tensor D) \arrow[r, "\passoc_{A\sequoid B,C,D}" yshift=0.3em]
+              & ((A\sequoid B)\sequoid C) \sequoid D \\
+          A\sequoid((B\tensor C)\tensor D) \arrow[r, "\passoc_{A,B\tensor C,D}"' yshift=-0.3em]
+            & (A\sequoid (B\tensor C)) \sequoid D \arrow[ur, "\passoc_{A,B,C}\sequoid\id_D"']
+              &
+        \end{tikzcd}
+      \end{equation*}
+      \begin{equation*}
+        \begin{tikzcd}
+          A \sequoid (I\tensor B) \arrow[r, "\passoc_{A,I,B}" yshift=0.3em] \arrow[d, "\id_A\sequoid\lunit_B"']
+            & (A\sequoid I)\sequoid B \arrow[dl, "\run_A\sequoid\id_B"] \\
+          A \sequoid B
+            &
+        \end{tikzcd}
+        \quad
+        \begin{tikzcd}
+          A \sequoid (B\tensor I) \arrow[r, "\passoc_{A,B,I}" yshift=0.3em] \arrow[d, "\id_A\sequoid\runit_B"']
+            & (A\sequoid B) \sequoid I \arrow[dl, "\run_{A\sequoid B}"] \\
+          A\sequoid B
+            &
+        \end{tikzcd}
+      \end{equation*}
 
@@
   Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is \emph{inclusive} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing all isomorphisms in $\C$ and the morphisms $\wk_{A,B}$, and $J$ is the inclusion functor.
-
- We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \otimes B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \otimes B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \otimes B \rightarrow B \sequoid A$.
-$\C$ is \emph{distributive}  if whenever the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pi_l \sequoid C,\pi_r \sequoid C$.
-So if $\C$ is Cartesian (has all finite products), 
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
+
+%  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
+ We say that $\C$ is \emph{decomposable} if it is affine, and for any $A$ and $B$, the tensor product $A \otimes B$ is a cartesian product of $A \tr B$ and $B \tr A$, with projections $\wk_{A,B}:A \otimes B \rightarrow A \tr B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \otimes B \rightarrow B \tr A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pi_l \sequoid C,\pi_r \sequoid C$.
+So if $\C$ has all finite products, 
 the natural transformations
@@
     \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
+   % \dec^0 \from I \to 1 \\
     \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
@@
 
+We have one further piece of structure available to us:
+
 \begin{definition}
-  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
-
- We say that $\C$ is \emph{decomposable} if $I$ is a terminal object for $\C$ and if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
-So if $\C$ has all finite products, 
-the natural transformations
-  \begin{gather*}
-    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
-    \dec^0 \from I \to 1 \\
-    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
-    \dist_{A,0}\from 1\sequoid A\to 1
-  \end{gather*}
-  are isomorphisms.
+  Let $\C=(\C,\C_s,J,\wk)$ be an inclusive sequoidal category.
+We say that $\C$ is a \emph{sequoidal closed category} if $\C$ is monoidal closed (with internal hom $\implies$ and currying $\Lambda_{A,B,C}\from \C(A\tensor B,C)\toisom \C(A,B\implies C)$) and if the map $f\mapsto\Lambda(\comp{f}{\wk})$ gives rise to a natural transformation
+  \[
+    \Lambda_{A,B,C,s}\from \C_s(A\sequoid B, C) \to \C_s(A,B\implies C)
+    \]
 \end{definition}
 
-We shall also use the fact that our category of games is \emph{affine} - so the natural transformation $\dec^0\from I \to 1$ is an isomorphism.
-This is not strictly necessary, and techniques are available to obtain similar results in the non-affine case (see \cite{jimNonAffine}, for example), but it will greatly simplify our presentation.
- We see that $\G$ is a prototype example of a distributive, decomposable sequoidal category.
+It can be shown (see for example \cite{martinsthesis}) that our category $\G$ of games has all this structure.
+
+\begin{theorem}
+  Let $J$ be the inclusion functor $\G_s\to\G$.  If $A,B$ are games, let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
+  \[
+    (\G,\G_s,J,\wk)
+    \]
+  is an inclusive, Cartesian, decomposable, distributive sequoidal closed category.
+\end{theorem}
 
@@
 
-There are several ways to add exponentials to the basic category of games.
-We shall use the definition based on countably many copies of the base game (see \cite{hyland1997games}, for example): the exponential $\oc A$ of $A$ is the game in which player $O$ may switch between countably many copies of $A$ -- $A_0, A_1, A_2, \dots$, as long as he starts them in order, starting with $A_0$, then opening $A_1$ and so on.
-This condition on the order in which games may be opened is very important, as it allows us to define the exponential morphisms $\oc A \to \oc A \tensor \oc A$ and $\oc A \to \oc \oc A$.
-In the first case, it can be proved \cite{LairdCofCommCom} that the comultiplication $\oc A \to \oc A \tensor \oc A$ exhibits $\oc A$ as the \emph{cofree commutative comonoid} on $A$, which shows that $A$ is a suitable model for the exponential \cite{LafontCofCommCom}.
-
-Even more interestingly, we see that we may characterize $\oc A$ as the \emph{final coalgebra} for the functor $A\sequoid\blank$.
-That is, given a coalgebra from $\sequoid\blank$ -- a game $B$ and a morphism $\sigma\from B \to A \sequoid B$ -- we get a unique morphism $\fcoal{\sigma}$ making the following diagram commute:
+There are several ways to add exponentials to the basic category of games.  We shall use the definition based on countably many copies of the base game (see \cite{laird02}, for example):
+
+\begin{definition}
+  Let $A$ be a negative game.
+The \emph{exponential} of $A$ is the game $\oc A = (M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A})$, where $M_{\oc A}, \lambda_{\oc A}, b_{\oc A}, P_{\oc A}$ are defined as follows:
+  \begin{itemize}
+    \item $M_{\oc A} = M_A \times \omega$
+    \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$
+    \item $b_{\oc A} = O$
+    \item Given a sequence $s\in M_{\oc A}^\omega$, we write $s\vert_n$ for the largest sequence $a_1a_2\dots a_k\in M_A^*$ such that $(a_1,n),(a_2,n),\dots(a_k,n)$ is a subsequence of $s$.
+Then $P_{\oc A}$ is the set of all sequence $s\in M_{\oc A}^\omega$ that are alternating with respect to $\lambda_{\oc A}$, such that $s\vert_n\in P_A$ for all $n$ and such that if $m<n$ and $(a,n)$ occurs in $s$ then $(b,m)$ must occur earlier in $s$ for some move $b$: in other words, player $O$ can start infinitely many copies of the game $A$, but he must start them in order.
+  \end{itemize}
+\end{definition}
+
+This last condition on the order in which games may be opened is very important, as it allows us to define morphisms that give $\oc A$ the semantics of the exponential from linear logic.
+For example, we have a natural morphism $\mu\from\oc A\to\oc A\tensor\oc A$, given by the copycat strategy that starts a new copy of $A$ on the left whenever one is started on the right.
+Because of the condition on the order in which copies of $A$ may be started, there is a unique way to do this.
+
+\begin{proposition}
+  $\mu$ exhibits $\oc A$ as a comonoid in the monoidal category $(\G, \tensor, I)$.  
+\end{proposition}
+\begin{proof}
+  $\mu$ shall be the comultiplication in our comonoid.
+The counit is given by the empty strategy $\eta\from\oc A\to I$.
+We just need to check that $\mu$ is associative and that $\eta$ is a counit for $\mu$.
+
+  For associativity, we need to show that the following diagram commutes:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[rr, "\mu"] \arrow[d, "\mu"']
+        &
+          & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor\mu"] \\
+      \oc A \tensor \oc A \arrow[r, "\mu\tensor\id_{\oc A}" yshift=0.2em]
+        & (\oc A \tensor \oc A) \tensor \oc A \arrow[r, "\assoc_{\oc A,\oc A,\oc A}"' yshift=-0.4em]
+          & \oc A \tensor (\oc A \tensor \oc A)
+    \end{tikzcd}
+    \]
+  This is easy to see when we notice that both branches of the square are copycat strategies on $\oc A\implies\oc A\tensor(\oc A\tensor \oc A)$; since copies of $A$ in $\oc A$ must be started in sequence, there is a unique such strategy, and so the square commutes.
+
+  For the counit, we need to show that the follosing two diagrams commute:
+  \[
+    \begin{tikzcd}
+      \oc A \arrow[r, "\mu"] \arrow[dr, "\runit_A\inv"']
+        & \oc A \tensor \oc A \arrow[d, "\id_{\oc A}\tensor \eta"] \\
+      %
+        & \oc A \tensor I
+    \end{tikzcd}
+    \quad\quad\quad
+    \begin{tikzcd}
+      \oc A \arrow[r, "\mu"] \arrow[dr, "\lunit_A\inv"']
+        & \oc A \tensor \oc A \arrow[d, "\eta\tensor\id_{\oc A}"] \\
+      %
+        & I \tensor \oc A
+    \end{tikzcd}
+    \]
+  Once again, these diagrams commute because both branches are copycat strategies for $\oc A\implies\oc A\tensor I$ or $\oc A\implies I\tensor\oc A$ and there is a unique such strategy in each case.
+\end{proof}
+
+We shall later show that $(\oc A, \mu, \eta)$ is in fact the \emph{cofree commutative comonoid} on $A$ in the monoidal category $(\G, \tensor, I)$.
+
+We shall call the exponential $\oc A$ the \emph{sequoidal exponential}.  The following proposition explains the name:
+
+\begin{proposition}
+  Let $A$ be a negative game.  Then we get an endofunctor $A\sequoid\blank$ on $\G$ given by sending $B$ to $A\sequoid B$.
+
+In any inclusive sequoidal category with a cofree exponential we have  a  $A \tr\_$-coalgebra  $\alpha:!A \rightarrow A \tr !A =  \delta;(\eta \otimes !A);\wk_{A \tr !A}$.
+In our category of games this
+%  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, 
+is the final coalgebra for the endofunctor $A\sequoid\blank$.
+In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
   \[
@@
     \]
-We call $\fcoal{\sigma}$ the \emph{anamorphism} of $\sigma$.
-
-We shall use the following standard pieces of theory about final coalgebras:
-\begin{description}
-  \item[Lambek's Lemma] $\alpha_A$ is an isomorphism, with inverse given by the anamorphism of the map $\id\sequoid\alpha_A\from A\sequoid\oc A\to A \sequoid (A \sequoid \oc A)$ \cite{Lambek}.
-In particular, $\alpha_A$ is a morphism in $\G_s$.
-In the general case, we deduce that $\alpha_A$ is a morphism in $\C_s$.
-  \item[Final Sequence] If $\C$ is a category with enough limits and $F$ is an endofunctor on $\C$, we may build up an ordinal indexed sequence of objects and morphisms of $\C$ (that is, a functor $\oppcat{\Ord}\to\C$, where $\Ord$ is the category of ordinals and prefix inclusions:
-    \[
-      1 \leftarrow F(1) \leftarrow F^2(1) \leftarrow \cdots F^\omega(1) \leftarrow F^{\omega+1}(1) \leftarrow \cdots
-      \]
-    (by repeatedly applying $F$ and taking limits).
-If this sequence stabilizes for any $\delta$ (i.e., if the morphism from $F^{\delta+1}(1)\to F^\delta(1)$ is an isomorphism), then $F^\delta(1)$ is the final coalgebra for $F$ \cite{finalseq}.
-\end{description}
-
-\subsection{Imperative programs as anamorphisms}
-
-We now show how we can use the characterization of $\oc A$ as a final coalgebra to define a strategy representing a simple storage cell.
-This is the strategy $\cell$ for $\oc(\Var[X])$ that is used in \cite{SamsonGuyIAPassive} to construct the denotation of the $\mathtt{new}$ term from Idealized Algol.
-Using this strategy, it is possible to build the model of Idealized Algol from \cite{SamsonGuyIAPassive} and hence construct a wealth of other stateful objects.
-The benefit of constructing $\cell$ in this way, rather than directly, is that we can now reason about it coalgebraically, rather than by direct combinatorial arguments on the strategy.
-
-Let $\Sigma$ be the game with maximal play $qa$ and let $\OK$ be the obvious strategy on $\Sigma$.
-$\Sigma$ denotes the type $\texttt{com}$ of commands.
-Let $(X,*)$ be a pointed set and write $X$ for the game with maximal plays $qx$ for $x\in X$.
-Recall that in Idealized Algol we represent $\Var[X]$, the type of variables taking values in $X$, by the game $\Sigma^X\times X$, where $\Sigma^X$ is the $X$-fold product of $\Sigma$ with itself.
-Here, $\Sigma^X$ represents the act of writing a value into the storage cell (so playing in $\Sigma_x$ means writing the value $x$), while the copy of $X$ represents reading a value from the storage cell.
-
-We want to construct the strategy $\cell$ for $\oc(\Sigma^X\times X)$ that will remember what value we have written into the cell and will return the value when we request it.
-In the case that we request the value in the cell when nothing has been written to it, we return the default value $*$.
-
-We shall represent the state of the storage cell by the game $X$, and we shall construct a state transformer on $X \implies (\Sigma^X\times X)\sequoid X$ that will allow us to recover the $\cell$ strategy as an anamorphism.
-
-For each $x\in X$, we have a strategy $c_x$ for $I\implies X$ with maximal play $qx$.  Now we construct a morphism $\wwrite(x)$ from $\oc X$ to $\Sigma\sequoid\oc X$ as the composite:
-\[
-  X \xrightarrow{*} 1 \xrightarrow{{(\dec^0)}\inv} I \xrightarrow{\runit_I} I \tensor I \xrightarrow{\OK\tensor c_x} \Sigma \tensor X \xrightarrow{\wk_{\Sigma,X}} \Sigma \sequoid X
-  \]
-This strategy corresponds to filling the cell with the value $x$.
-Consequently, we ignore the previous value from the cell (the copy of $X$ on the left) and we respond in the copy of $X$ on the right with $x$.
-
-We get a strategy:
-\[
-  \wwrite \from \oc X \xrightarrow{\langle \wwrite(x)\suchthat x\in X\rangle} (\Sigma \sequoid \oc X)^X \xrightarrow{\dist_{(\Sigma\colon x\in X),\oc X}\inv} \Sigma^X\sequoid\oc X
-  \]
-
-We also want a strategy $\read$ for $X \implies X \sequoid X$.
-It doesn't appear to be possible to construct this strategy from the sequoidal axioms, but it is easy enough to say what it is: it is the strategy that returns the value of the state while leaving the state unchanged.
-A typical play in $\read$, therefore, might have the following form:
-\[
-  \begin{array}{ccccc}
-    X & \implies & X & \sequoid & X \\
-    && q && \\
-    q &&&& \\
-    x &&&& \\
-    && x && \\
-    &&&& q \\
-    &&&& x
-  \end{array}
-  \]
-Note that the content of the state (the copy of $X$ on the left) is copied into both the output (the first copy of $X$ on the right) and into the new state (the second copy of $X$ on the right).
-
-We put these strategies together to form our state transformer:
-\[
-  \cell'\from \oc X \xrightarrow{\langle\wwrite,\read\rangle} \Sigma^X\sequoid\oc X \;\times\;X\sequoid\oc X \xrightarrow{\dist_{\Sigma^X,X,\oc X}} (\Sigma^X\times X)\sequoid \oc X
-  \]
-When we take the anamorphism $\fcoal{\cell'}$ of this strategy, we get the strategy $\oc X \to \oc (\Sigma^X\times X)$ that, when player $O$ plays in $\Sigma^X$, stores the appropriate element of $X$ into the (invisible) state.
-When player $O$ plays in $X$ on the right, player $P$ responds with the current value held in the state.
-In the case that player $O$ plays in $X$ without having first played in $\Sigma^X$, we return the value of $X$ from the left.
-Therefore, our desired strategy $\cell$ is given by:
-\[
-  \cell = \comp{\fcoal{\cell'}}{c_*}
-  \]
-
-A similar method may be used to construct a simple stack \cite{martinsthesis}.
-
-\section{Constructing cofree commutative comonoids in Cartesian sequoidal categories}
-
-\subsection{A formula for the sequoidal exponential}
-
-We observed that the exponential $\oc A$ of a game $A$ arises as the final coalgebra for the functor $A\sequoid\blank$.
-We also observed that $\oc A$ has the structure of a cofree commutative comonoid on $A$.
-In this section, we shall consider various generalizations of this result that hold in sequoidal categories.
-
-We shall first consider the formula  given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom}, which does not depend on the presence of cartesian products, but obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
-\begin{definition}If $A$ is an object in a symmetric monoidal category, a $n$-fold symmetric tensor power of $A$ is an  \emph{equalizer} $(A^n,\eq)$ for the group $G$ of symmetry automorphisms on $A^{\otimes n}$.
-A tensor power is preserved by the tensor product if $(B\otimes A^n,\eq \otimes B)$ is an equalizer for the automorphisms $\{B \otimes g\ |\ g \in G\}$.
-\end{definition}
-In any affine category\footnote{This is a special case of the situation considered in  \cite{MelliesCofCommCom}: that $A$ is a ``free pointed object''.} with tensor powers of $A$ we may define a diagram $\Delta(A) = $
-$$I \stackrel{p_0}{\leftarrow} A \stackrel{p_1}{\leftarrow} A^2 \ldots A^i \stackrel{p_i}{\leftarrow} A^{i+1} \ldots$$
-where   
-$p_i:A^{i+1} \rightarrow A^i$ is the unique morphism given by the universal property of the symmetric tensor power,  such that $\comp{\eq_i:A^{i+1}}{p_i} \rightarrow A^{\otimes i} = \eq_{i+1};(A^{\otimes i} \otimes t_A)$.
-
-Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} have shown that where the limit $(A^\infty, \{p^\infty_i\from A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e.
-for each object $B$, $B \tensor A^\infty$ is the limit of
-$$B \tensor I \stackrel{B \tensor p_0}{\leftarrow} B \tensor A  \stackrel{B \tensor p_1}{\leftarrow} B\tensor  A^2 \ldots $$
-then a comultiplication $\mu:A^\infty \rightarrow A^\infty \tensor A^\infty$ may be defined making $(A^\infty,\mu,t_{\oc A})$ the cofree commutative comonoid.
-Where these conditions are satisfied, we shall call this a MTT-exponential.
-
-In the category of games, the morphisms $\id\sequoid\pr_1$ and $\id\sequoid\pr_2 \from A \sequoid (B\times C)\to (A \sequoid B) \times (A \sequoid C)$ are jointly monomorphic.
-If a distributive sequoidal category satisfies the same property, we say that it is \emph{strong distributive}.
-\begin{proposition}Any strong distributive decomposable sequoidal category has all symmetric tensor powers, and these are preserved by the tensor.  
 \end{proposition}
 \begin{proof}
-By sequoidal decomposability, for any $n$, $A^{\tensor (n+1)}$ is the cartesian product $\Pi_{i \le n} (A \sequoid A^{\tensor n})$ with projections 
-$\sym_i;\wk_{A,A^{\tensor n}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
-
-  Define  $\wk^n: A^{\tensor n}\rightarrow A^{\sequoid n}$ by $\wk^{n+1} = \wk_{A, A^{\tensor n}}; (A \sequoid \wk^n)$.
-We show (by induction on $n$) that for any $n$, the morphisms $\comp{\wk_n}{\sym^\pi}$ are jointly monomorphic, where $\sym^\pi$ ranges over all of the permutation isomorphisms  on $A^{\tensor n}$.
-
-  The equalizer $\eq_n:A^n \rightarrow A^{\tensor n}$ is defined inductively by $\eq_n=\langle \id\sequoid\eq_{n-1}$, using the identification of $A\sequoid n$ as a product given above.
-We may show inductively that $\comp{\wk^n}{\comp{\sym^\pi}{\eq_n}}=\id$ for all permutations $\pi\in S_n$.
-  Given any $f:C \rightarrow A^{\tensor n} \tensor B$ such that $\comp{(\theta \tensor B)}{f} = f$ for any permutation symmetry $\theta$, taking $\comp{(\wk^n \tensor B)}{f}:C \rightarrow A^{\sequoid n} \tensor B$ gives the unique morphism such that $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$.
-Indeed, for all permutations $\pi\in S_n$ we have $\comp{\wk^n\tensor\id_B}{\comp{\sym^\pi\tensor\id_B}{\comp{\eq_n\tensor\id_B}{\comp{(\wk^n\tensor\id_B}{f}}}}=\comp{(\wk^n\tensor\id_B)}{f}=\comp{(\wk^n\tensor\id_B)}{\comp{\sym^\pi}{f}}$.
-Hence, $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$ (by decomposability and strong distributivity, the joint monomorphism property is preserved by the tensor product).
-For uniqueness, use the fact that $\eq_n$ is a left inverse for $\wk^n$.
-\end{proof}
-Thus, in any sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit for this diagram exists and is preserved by the sequoid, 
---- i.e.
-for any $B$, $B \sequoid A^\infty$ is the limit for $B \sequoid \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid.
-Conversely, we may show that any cofree commutative comonoid which arises as a $\tensor$-preserving limit of symmetric tensor powers is a final coalgebra.
-\begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty, \comp{\wk_{A\tensor\oc A}}{\comp{\der_A}{\mu_A}})$ is a final coalgebra for the functor $A \sequoid \_$.
-\end{proposition}
-\begin{proof}
-  Observe that in a sequoidally decomposable category, the morphism $\wk_{A,A^n}:A \sequoid A^n: \rightarrow A^{n+1}$ is a section (we may define the corresponding retraction inductively from the decomposition of the tensor).
-Hence if   the limit $A^\infty$ is preserved by the functor $A \tensor \_$, it is preserved by the sequoid $A \sequoid\_$ --- i.e.
-$A^\infty$ is the limit of the chain $A \sequoid \Delta = \Delta$.
-
-  Thus, for  any  $A \sequoid\_$-coalgebra $f\from B \rightarrow A \sequoid B$, we may define a unique coalgebra morphism $\fcoal{f}\from B \rightarrow \oc A$ as the mediating morphism of the cone $\{f_i\from B \rightarrow A^i\ |\ i \in \omega\}$, where  $f_0 = t_B$ and $f_{i+1} = f;(A \sequoid f_i)$.
-\end{proof}
-
-\subsection{Win-games and winning strategies}
-
-The construction from \cite{MelliesCofCommCom} covers a lot of different cases, but there are some situations in which it does not apply.
-One example is that of \emph{win-games}, or games with a winning condition (\cite{abramskyjagadeesangames}, \cite{martinsthesis}).
-Given a game $A$, we write $\overline{P_A}$ to be the limit-closure of $P_A$ -- that is, $P_A$ together with the set of infinite sequences, all of whose finite prefixes are in $P_A$.
-A \emph{win-game} is a game $A$ together with a function $\zeta_A\from \overline{P_A}\to\OP$ such that:
-\begin{itemize}
-  \item $\zeta_A(\emptyplay) = \neg b_A$
-  \item $\zeta_A(sa) = \lambda_A(a)$
-\end{itemize}
-Thus, $\zeta_A$ is entirely determined on $P_A$, and the only new information is the values that $\zeta_A$ takes on the infinite positions in $\overline{P_A}$.
-The reason we bother to define $\zeta_A$ on finite positions at all is so that we can define it easily on the connectives:
-\begin{gather*}
-  \zeta_{A\tensor B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \quad
-  \zeta_{A \implies B}(s) = \zeta_A(s\vert_A) \Rightarrow \zeta_B(s\vert_B) \\
-  \zeta_{\prod_{i\in I}A_i}(s) = \bigwedge_{i\in I}\zeta_{A_i}(s\vert_{A_i}) \quad
-  \zeta_{A\sequoid B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \quad
-  \zeta_{\oc A}(s) = \bigwedge_{i\in I}(\zeta_A(s\vert_i))
-\end{gather*}
-
-Here, $\wedge$ and $\Rightarrow$ are the usual propostional connectives on $\{T,F\}$, where we identify $T$ with $P$ and $F$ with $O$.
-
-We define a \emph{winning strategy} on $(A,\zeta_A)$ to be a total strategy $\sigma$ on $A$ such that $\zeta_A(s)=P$ whenever $s$ is an infinite sequence, all of whose finite prefixes are in $\sigma$.
-It is known (see \cite{abramskyjagadeesangames}) that the composition of winning strategies is winning and that we get a decomposable, distributive sequoidal category $\W$ with $\oc A$ as the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ \cite{martinsthesis}.
-
-However, in this case, $\oc A$ is not the sequential limit of the symmetrized tensor powers over $A$.
-Since $\W$ is a decomposable, strong distributive sequoidal category, the symmetrized tensor powers of $A$ are given by the sequoidal powers $A^{\sequoid n}$.
-But now the limit of these objects is not quite the game $\oc A$; instead, it is the game $A^{\sequoid\omega}=\co A$ in which player $O$ may open an arbitrarily large number of copies of $A$, but not infinitely many.
-In the finite case, there was no way to keep track of infinite positions, so we could not make this distinction, but in the win-games case we can: we set $\zeta_{\co A}(s)=\zeta_{\oc A}(s)$, unless $s$ contains moves in infinitely many games, in which case we set $\zeta_{\co A}(s) = P$.
-
-This limit is not preserved by the functor $A\sequoid\blank$: in the game $A^{\sequoid(\omega+1)}=A\sequoid\co A$, player $O$ wins if he wins either in $A$ or in $\co A$, so he can win even if he plays in infinitely many games, as long as he wins in the first copy of $A$.
-Similarly, in the game $A^{\sequoid(\omega+n)}$, player $O$ can win as long as he wins in one of the first $n$ copies of $A$.
-Therefore, the limit $A^{\sequoid\omega2} \emph{is}$ the game $\oc A$: the final sequence for $A\sequoid\blank$ stabilizes at $\omega2$.
-
-We see that the exponential in $\W$ is not an MTT-exponential.
-
-This example is a special case of our later result on transfinite games.
-For now, we examine a coalgebraic approach that will prove that the final coalgebra $\oc A$ for $A\sequoid \blank$ in the category $\W$ of win-games gives us a cofree commutative comonoid.
-
-\subsection{The coalgebraic construction under the strong monoidal hypothesis}
-
-We will now need to assume that we are in a decomposable, distributive sequoidal category $(\C,\C_s,J,\wk)$ such that $\C_s$ has all products and $J$ preserves them.
-However, we will no longer need the MTT assumption that the exponential should be constructed as a limit of sequoidal powers.
-The main cost is that we will need to make a further assumption: that a certain naturally defined morphism $\oc A \tensor \oc B\to \oc (A\times B)$ is an isomorphism.
-This assumption, broadly corresponding to the demand that the functor $\oc A$ be strong monoidal from the Cartesian category $(\C,\times,1)$ to the monoidal category $(\C,\tensor,I)$, will allow us to construct the comultiplication directly from the Cartesian structure and the definition of $\oc A$ as a final coalgebra.
+  See \cite{martinsthesis}.  We shall shortly give a proof in the more general case.
+\end{proof}
+
+\subsection{Constructing cofree commutative comonoids in sequoidal categories}
+
+We want to construct  $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ from the final $A\sequoid\blank$-coalgebra, $(\oc A,\alpha)$, and show that it is the cofree commutative comonoid on $A$.
+It turns out that we shall need one more fact about the category of games to prove this.
 
@@
 \begin{definition}
-  Let $A,B$ be objects of an decomposable, distributive sequoidal category $(\C,\C_s,J,\wk)$ with final coalgebras $\oc A\xrightarrow{\alpha_A} A\sequoid\oc A$ for all endofunctors of the form $A\sequoid\blank$.
+  Let $A,B$ be objects of an inclusive, Cartesian, distributive sequoidal category $(\C,\C_s,J,\wk)$ with final coalgebras $\oc A\xrightarrow{\alpha_A} A\sequoid\oc A$ for all endofunctors of the form $A\sequoid\blank$.
 Let $A,B$ be objects of $C$.
@@
   \begin{IEEEeqnarray*}{RCL}
-    \kappa_{A,B} = \oc A \tensor \oc B & \constantwidthxrightarrow{\langle\wk_{\oc A,\oc B},\;\comp{\sym_{\oc A,\oc B}}{\wk_{\oc A,\oc B}}} & (\oc A \sequoid \oc B) \times (\oc B \sequoid \oc A) \\
-    \cdots & \constantwidthxrightarrow{(\alpha_A\sequoid\id_{\oc B}) \times (\alpha_B\sequoid\id_{\oc A})} & ((A \sequoid \oc A) \sequoid \oc B) \times ((B \sequoid \oc B) \sequoid \oc A) \\
+    \kappa_{A,B}=\oc A \tensor \oc B & \constantwidthxrightarrow{\langle\id_{\oc A\tensor\oc B},\; \sym_{\oc A,\oc B}\rangle} & (\oc A \tensor \oc B) \times (\oc B \tensor \oc A) \\
+    \cdots & \constantwidthxrightarrow{(\alpha_A\tensor\id_{\oc B})\times(\alpha_B\tensor\id_{\oc A})} & ((A \sequoid \oc A) \tensor \oc B) \times ((B \sequoid \oc B) \tensor \oc A) \\
+    \cdots  & \constantwidthxrightarrow{\wk_{A\sequoid\oc A,\oc B}\times\wk_{B\sequoid\oc B,\oc A}} & ((A \sequoid \oc A) \sequoid \oc B) \times ((B \sequoid \oc B) \sequoid \oc A) \\
       \cdots & \constantwidthxrightarrow{\passoc_{A,\oc A,\oc B}\inv\times\passoc_{B,\oc B,\oc A}\inv} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc B \tensor \oc A) \\
@@
   \end{IEEEeqnarray*}
-  We get a morphism $\comp{\dist\inv}{\kappa_A}\from \oc A \tensor \oc B \to (A\times B) \sequoid(\oc A \tensor \oc B)$ and we write $\int_{A,B}=\fcoal{\comp{\dist\inv}{\kappa_A}}\from \oc A \tensor \oc B \to \oc (A\times B)$.
+inducing a morphism
+\[
+  \oc A\tensor \oc B \xrightarrow{\kappa_{A,B}} (A \sequoid(\oc A\tensor\oc B)) \times (B \sequoid(\oc A\tensor \oc B)) \xrightarrow{\dist\inv}
+    (A\times B)\sequoid(\oc A\tensor\oc B)
+    \]
+  Remembering that our category has a final coalgebra $\oc(A\times B)$ for the functor $(A\times B)\sequoid\blank$, we write $\int_{A,B}$ for the unique morphism $\oc A\tensor\oc B\to \oc(A\times B)$ making the following diagram commute
+  \begin{equation}\label{definitionOfInt}
+    \begin{tikzcd}
+      \oc A \tensor \oc B \arrow[r, "\kappa_{A,B}"] \arrow[d, "\int_{A,B}"']
+        & (A\sequoid(\oc A \tensor \oc B) \times (B \sequoid (\oc A \tensor \oc B)) \arrow[r, "\dist\inv"]
+          & (A \times B) \sequoid (\oc A \tensor \oc B) \arrow[d, "\id_{A\times B}\sequoid\int_{A,B}"] \\
+      \oc(A\times B) \arrow[rr, "\alpha_{A\times B}"']
+        &
+          & (A \times B) \sequoid \oc(A\times B)
+    \end{tikzcd}\tag{$\star$}
+  \end{equation}
 \end{definition}
@@
 \end{proof}
+
 Our first main result for this section will be the following:
@@
   \label{StrongMonoidalFunctor}
-  Let $(\C,\C_s,J,\wk)$ be a distributive and decomposable sequoidal category with a final coalgebra $\oc A\xrightarrow{\alpha_A}A\sequoid\oc A$ for each endofunctor of the form $A\sequoid\blank$.
+  Let $(\C,\C_s,J,\wk)$ be an inclusive, Cartesian, distributive and decomposable sequoidal category with a final coalgebra $\oc A\xrightarrow{\alpha_A}A\sequoid\oc A$ for each endofunctor of the form $A\sequoid\blank$.
 Suppose further that the morphism $\int_{A,B}$ as defined above is an isomorphism for all objects $A,B$.
@@
   \]
-where $\Delta$ is the diagonal map on the product.
-We set $\sigma_A=\fcoal{\comp{\dist\inv}{\comp{\Delta}{\alpha_A}}}\from\oc A \to \oc (A\times A)$ and we set $\mu_A=\comp{\int_{A,A}\inv}{\sigma_A}\from \oc A \to \oc A \tensor \oc A$.
+where $\Delta$ is the diagonal map on the product.  There is therefore a unique morphism $\sigma_A=\fcoal{\comp{\dist\inv}{\comp{\Delta}{\alpha_A}}}$ making the following diagram commute:
+\begin{equation}\label{definitionOfSigma}
+  \begin{tikzcd}
+    \oc A \arrow[r, "\alpha_A"] \arrow[d, "\sigma_A"']
+      & A \sequoid \oc A \arrow[r, "\Delta"]
+        & (A \sequoid \oc A)\times(A \sequoid \oc A) \arrow[r, "\dist\inv"]
+          & (A \times A) \sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\sigma_A"] \\
+    \oc(A\times A) \arrow[rrr, "\alpha_{A\times A}"]
+      &
+        &
+          & (A \times A) \sequoid \oc(A \times A)
+  \end{tikzcd}\tag{\dag}
+\end{equation}
+and we may set $\mu_A=\comp{\int_{A,A}\inv}{\sigma_A}$.
 
@@
 
-We define the action of $\oc$ on morphisms as follows: suppose that $f\from A \to B$ is a morphism in $\C$.  Then we have a composite
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu_A"]
+We define the action of $\oc$ on morphisms as follows: suppose that $\sigma\from A \to B$ is a morphism in $\C$.  Then we have a composite
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\mu"]
       & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
-        & A \tensor \oc A \arrow[r, "f\tensor\id_{\oc A}"]
+        & A \tensor \oc A \arrow[r, "\sigma\tensor\id_{\oc A}"]
           & B \tensor \oc A \arrow[r, "\wk_{B,\oc A}"]
@@
   \]
-and so we may define $\oc f$ to be the anamorphism $\fcoal{\comp{\wk_{B,\oc A}}{\comp{f\tensor\id_{\oc A}}{\comp{\der_A\tensor\id_{\oc A}}{\mu_A}}}}\from \oc A \to \oc B$.
+There is therefore a unique morphism $\oc\sigma\from\oc A \to\oc B$ making the following diagram commute:
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\mu"] \arrow[d, "\oc\sigma"']
+      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
+        & A \tensor \oc A \arrow[r, "\sigma\tensor\id_{\oc A}"]
+          & B \tensor \oc A \arrow[r, "\wk_{B,\oc A}"]
+            & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
+    \oc B \arrow[rrrr, "\alpha_B"]
+      &
+        &
+          &
+            & B \sequoid \oc B
+  \end{tikzcd}
+  \]
 
 \begin{proposition}\label{StrongMonoidalFunctorActual}
-  $f\mapsto\oc f$ respects composition, so $\oc$ is a functor.
-Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
+  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
+Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
 \end{proposition}
@@
 \end{proposition}
+\begin{proof}
+  See appendix.
+\end{proof}
 
@@
 
+\begin{proof}
+  See Appendix.
+\end{proof}
+
 \subsection{The Sequoidal Exponential as a Bifree Algebra}
-Observe that in our category of games, $(!A,\alpha)$ is in fact a \emph{bifree algebra} for $A\sequoid\blank$ --- the isomorphism $\alpha^{-1}: A \sequoid !A \rightarrow !A$ is an initial algebra for  $A \sequoid \blank$.
-We may show that in such cases, the condition that $!$ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $\oc A$ with the structure of a comonoid by defining:
-$\mu:!A \rightarrow !A  \otimes !A$
- to be the catamorphism of the $A \sequoid \blank$ algebra:
-\[
-  A \sequoid (!A \otimes !A) 
-\cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)
-\]
+Observe that in our category of games, $(!A,\alpha)$ is in fact a \emph{bifree algebra} for $A\tr\_$ --- the isomorphism $\alpha^{-1}: A \tr !A \rightarrow !A$ is an initial algebra for  $A \tr \_$.
+We may show that in such cases, the condition that $!$ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $!A$ with the structure of a comonoid by defining:
+$\delta:!A \rightarrow !A  \otimes !A$
+ to be the catamorphism of the $A \tr \_$ algebra:
+$$A \tr (!A \otimes !A) %\stackrel{\langle \id, A \tr \sym\rangle}{\cong} 
+\cong A \tr (!A \otimes !A) \times  A \tr (!A \otimes !A) \cong (A \tr !A) \tr !A \times  (A \tr !A) \tr !A \cong (!A \tr !A) \cong (!A \tr !A) \cong (!A \otimes !A)$$     
 This satisfies the further requirements of a \emph{linear category} in the sense of \cite{Bierman}, although it does not appear to be possible to show that it is the cofree commutative comonoid.} :
-we may define an inverse to $\int:!A \otimes !A \rightarrow ! (A \times B)$  as the \emph{catamorphism} of the  $A \sequoid\blank$-algebra:
-$$(A \times B) \sequoid !A \otimes !B \cong (A \sequoid (!A \otimes !B)) \times  (B \sequoid (!A \otimes !B)) \cong (!A \sequoid !B) \times (!B \sequoid !A)$$
-
-It is not necessary for the final $A \sequoid\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid.
-An example is provided by  the category $\W$ of win-games and winning strategies, which is \emph{sequoidal closed} (the restriction of the functor  $A \multimap\blank$ to strict strategies is right adjoint to $\blank \sequoid A$, and inclusion sends this adjunction to the usual monoidal closure).
-To show that the  final $A \sequoid\blank$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\comp{f}{\fix_A(f)} = \fix(f)$.
-\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \sequoid\_$-algebra. Then we may define a fixed point operator on $\C$.  
+we may define an inverse to $\int:!A \otimes !A \rightarrow ! (A \times B)$  as the \emph{catamorphism} of the  $A \tr\_$-algebra:
+$$(A \times B) \tr !A \otimes !B \cong (A \tr (!A \otimes !B)) \times  (B \tr (!A \otimes !B)) \cong (!A \tr !B) \times (!B \tr !A)$$
+
+It is not necessary for the final $A \tr\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid.
+An example is provided by  the category of games with winning conditions and winning strategies, which is sequoidal closed and decomposable.
+To show that the  final $A \tr\_$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\fix_A(f);f = \fix(f)$.
+\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \tr\_$-algebra. Then we may define a fixed point operator on $\C$.  
 \end{proposition}    
-\begin{proof}For any $A$, let  $\Phi_A:!(A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \sequoid\blank \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \sequoid A \rightarrow A$, which is a  $(A \multimap A) \sequoid \blank$-algebra.
+\begin{proof}For any $A$, let  $\Phi_A:!(A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \tr\_ \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \tr A \rightarrow A$, which is a  $(A \multimap A) \tr \_$-algebra.
 For any morphism $f:A \rightarrow A$ we may define $\fix_A(f) = \Lambda(f)^\dag;\Phi_A$, where $\Lambda(f):I \rightarrow (A \multimap A)$ is the ``name'' of $f$.
@@
 As one would expect, it is not possible to define a fixed point operator on the category of games and winning strategies ---  for example, if $\bot$ is the game with a single move then the hom-set $\C(I,\bot)$ is empty and hence there can be no morphism $\fix_\bot(\id_\bot)$.
-So the final  $A \sequoid \_$-coalgebra is not bifree in this case.
+So the final  $A \tr \_$-coalgebra is not bifree in this case.
+
+\subsection{A formula for the sequoidal exponential}
+We now consider an alternative construction of the cofree commutative comonoid in a sequoidally decomposable category, which leads to some illuminating comparisons with the coalgebraic approach.
+It is based on the formula  given by
+Melli\'es, Tabareau and Tasson \cite{MTT}, which does not depend on the presence of cartesian products, but obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
+\begin{definition}If $A$ is an object in a symmetric monoidal category, a $n$-fold symmetric tensor power of $A$ is an  \emph{equalizer} $(A^n,\eq)$ for the group $G$ of symmetry automorphisms on $A^{\otimes n}$.
+A tensor power is preserved by the tensor product if $(B\otimes A^n,\eq \otimes B)$ is an equalizer for the automorphisms $\{B \otimes g\ |\ g \in G\}$.
+\end{definition}
+In any affine category\footnote{This is a special case of the situation considered in  \cite{MTT}: that $A$ is a ``free pointed object''.} with tensor powers of $A$ we may define a diagram $\Delta(A) = $
+$$I \stackrel{p_0}{\leftarrow} A \stackrel{p_1}{\leftarrow} A^2 \ldots A^i \stackrel{p_i}{\leftarrow} A^{i+1} \ldots$$
+where   
+$p_i:A^{i+1} \rightarrow A^i$ is the unique morphism given by the universal property of the symmetric tensor power,  such that $p_i;\eq_i:A^{i+1} \rightarrow A^{\otimes i} = \eq_{i+1};(A^{\otimes i} \otimes t_A)$.
+
+Melli\'es, Tabareau and Tasson \cite{MTT} have shown that where the limit $(A^\infty, \{p^\infty_i:A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e.
+for each object $B$, $B \otimes A^\infty$ is the limit of
+$$B \otimes I \stackrel{B \otimes p_0}{\leftarrow} B \otimes A  \stackrel{B \otimes p_1}{\leftarrow} B\otimes  A^2 \ldots $$
+then a comultiplication $\delta:A^\infty \rightarrow A^\infty \otimes A^\infty$ may be defined making $(A^\infty,\delta,t_{!A})$ the cofree commutative comonoid.
+Where these conditions are satisfied, we shall call this a MTT-exponential.
+\begin{proposition}Any sequoidally decomposable category has all symmetric tensor powers, and these are preserved by the tensor.  
+\end{proposition} 
+\begin{proof}
+By sequoidal decomposability, for any $n$, $A^{\otimes (n+1)}$ is the cartesian product $\Pi_{i \leq n} (A \tr A^{\otimes n})$ with projections 
+  $\comp{\sym_i}{\wk_{A,A^{\otimes n}}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
+
+  We inductively define the sequoid powers $A^{\sequoid n}$ by $A^{\sequoid 1}=A$ and $A^{\sequoid(n+1)}=A\sequoid A^{\sequoid n}$.
+Given $n$, we inductively define a morphism $\eq_n\from A^{\sequoid n}\to A^{\tensor n}$ as the diagonal $\langle \id_A\sequoid\eq_{n-1}\rangle$ into the product -- so $\comp{\wk}{\comp{\sym_i}{\eq_n}}=\id\sequoid e_{n-1}$ for each $i$.
+
+  If $\pi\in S_n$ is a permutation, we write $\sym^\pi$ for the appropriate symmetry of $A^{\tensor n}$.
+We now claim that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi\in S_n$ -- so $\eq_n$ equalizes the $\sym^\pi$.
+Indeed, let $\pi\in S_n$.
+Then we may write $\sym^\pi = \comp{\id_A\tensor\sym^\rho}{\sym_i}$ for some $i$ and some $\rho\in S_{n-1}$.
+Now we have:
+  \begin{IEEEeqnarray*}{rClC}
+    \comp{\wk}{\comp{\sym^\pi}{\eq_n}} & = & \comp{\wk}{\comp{\comp{(\id\tensor\sym^\rho)}{\sym_i}}{\eq_n}} & \\
+    & = & \comp{(\id\sequoid\sym^\rho)}{\comp{\wk}{\comp{\sym_i}{\eq_n}}} & \hspace{24pt}\textrm{(by naturality of $\wk$)} \\
+    & = & \comp{(\id\sequoid\sym^\rho)}{(\id\sequoid\eq_{n-1})} & \\
+    & = & \id\sequoid\eq_{n-1}
+  \end{IEEEeqnarray*}
+  Since $\pi$ was arbitrary, it follows that $\comp{\wk}{\comp{\comp{\sym_j}{\sym^{\pi}}}{\eq_n}}=\comp{\comp{\wk}{\sym_j}}{\eq_n}$ for all $j$ and therefore that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi$, as desired.
+
+  Now define $\wk^n\from A^{\sequoid n}\to A^{\tensor n}$ inductively by $\wk^n = \comp{\id\sequoid\wk^{n-1}}{\wk}$.
+We may show by induction that $\comp{\wk^n}{\eq_n}=\id_{A^{\sequoid n}}$ for all $n$: indeed, we have
+  \begin{IEEEeqnarray*}{rClC}
+    \comp{\wk^n}{\eq_n} & = & \comp{(\id\sequoid\wk^{n-1})}{\comp{\wk}{\eq_n}} & \\
+    & = & \comp{(\id\sequoid\wk^{n-1})}{(\id\sequoid\eq_{n-1})} & \\
+    & = & \id\sequoid \id = \id & \hspace{24pt}\textrm{(by induction)}
+  \end{IEEEeqnarray*}
+  Now let $f\from C \to B \tensor A^{\tensor n}$ be such that $\comp{(\id\tensor\sym^\pi)}{f}=f$ for all $\pi\in S_n$.
+It follows from what we have just shown that if $f=\comp{(\id\tensor\eq_n)}{g}$, then $g=\comp{\comp{\id\tensor\wk^n}{\id\tensor\eq_n}}{g}=\comp{\id\tensor\wk^n}{f}$.
+So we just need to show that
+  \[
+    f=\comp{(\id\tensor(\comp{\eq_n}{\wk_n}))}{f}
+    \]
+  We first assume that $B=I$, so we have $f\from C\to B\tensor A^{\tensor n}$ and $\comp{\sym^\pi}{f}=f$ for all $\pi\in S_n$ and we are trying to show that $f=\comp{\comp{\eq_n}{\wk^n}}{f}$.
+We do this by showing that $\comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}}=\comp{\comp{\wk}{\sym_i}}{f}$ for all $i$.
+
+  Indeed, we have:
+  \begin{IEEEeqnarray*}{rClC}
+    \comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}} & = & \comp{\comp{(\id\sequoid\eq_{n-1})}{(\id\sequoid\wk^{n-1})}}{\comp{\wk}{f}} & \\
+    & = & \comp{\wk}{\comp{(\id\tensor(\comp{\eq_{n-1}}{\wk^{n-1}}))}{f}} &\hspace{24pt}\textrm{(by naturality of $\wk$)} \\
+    & = & \comp{\wk}{f} &\hspace{2pt}\textrm{(by induction)} \\
+    & = & \comp{\wk}{\comp{\sym_i}{f}}
+  \end{IEEEeqnarray*}
+
+  Now let $B$ be an arbitary object of the category.  [TODO: finish working this out.]
+\end{proof}
+Thus, in any sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit for this diagram exists and is preserved by the sequoid, 
+--- i.e.
+for any $B$, $B \tr A^\infty$ is the limit for $B \tr \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid.
+Conversely, we may show that any cofree commutative comonoid which arises as a $\otimes$-preserving limit of symmetric tensor powers is a final coalgebra.
+\begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty,\delta;(\eta \otimes !A);\wk_{A \tr !A})$ is a final coalgebra for the functor $A \tr \_$.    
+\end{proposition}
+\begin{proof}
+  Observe that in a sequoidally decomposable category, the morphism $\wk_{A,A^n}:A \tr A^n: \rightarrow A^{n+1}$ is a section (we may define the corresponding retraction inductively from the decomposition of the tensor).
+Hence if   the limit $A^\infty$ is preserved by the functor $A \otimes \_$, it is preserved by the sequoid $A \tr\_$ --- i.e.
+$A^\infty$ is the limit of the chain $A \tr \Delta = \Delta$.
+
+Thus, for  any  $A \tr\_$-coalgebra $f:B \rightarrow A \tr B$, we may define a unique coalgebra morphism $\(f\):B \rightarrow !A$ as the mediating morphism of the cone $\{f_i:B \rightarrow A^i\ |\ i \in \omega\}$, where  $f_0 = t_B$ and $f_{i+1} = f;(A \tr f_i)$.
+\end{proof}
 
@@
 For this reason, we might wonder whether we can do without the condition that $\int_{A,B}$ be an isomorphism.
-In this section, we shall give a negative answer to that question: we shall construct a distributive and decomposable sequoidal closed category with final coalgebras $\oc A$ for all functors of the form $A\sequoid\blank$, and shall show that $\oc A$ does not have a natural comonoid structure.
+In this section, we shall give a negative answer to that question: we shall construct an inclusive, distributive, decomposable sequoidal (closed) category with final coalgebras $\oc A$ for all functors of the form $A\sequoid\blank$, and shall show that $\oc A$ does not have a natural comonoid structure.
 In doing this, we hope to shed some light upon alternative algebraic or coalgebraic constructions for the cofree commutative comonoid that work in a purely `finitary' manner.
@@
 Our sequoidal category will be closely modelled upon the category of games we have just considered: the objects will be games, with the modification that sequences of moves may now have transfinite length.
-This is a natural construction, occurring in the study of determinacy by Mycielski \cite{mycielskiChoice}, Blass \cite{blassChoice} and Weiss \cite{longgamesbook}.
-Transfinite games were used by Berardi and de'Liguoro to give a charactarization of total functionsals \cite{BerardiTransfiniteGames}, and they appear to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
+This is a natural construction, occurring in the study of determinacy by Mycielski \cite{mycielskiChoice}, Blass \cite{blassChoice} and Weiss \cite{longgamesbook}, and it appears to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
 
@@
 The `correct' definition of $\oc A$ in the transfinite game category is one in which there is an unlimited number of copies of $A$ to open (rather than $\omega$-many), but this is not the final coalgebra for the functor $A\sequoid\blank$.
+[TODO: discuss ways to construct this object]
 
@@
 
-We give a brief summary of the construction of the category of transfinite games.
+We give a brief summary of the construction of the category of transfinite games.  Full details may be found in Appendix \ref{TransfiniteGamesConstructionInFull}.
 
@@
 \begin{definition}
-  A (completely negative) \emph{game} or a \emph{game over $\alpha$} or an \emph{$\alpha$-game} is given by a forest (i.e., a prefix-closed set) $P_A$ of alternating transfinite sequences of $O$-moves and $P$-moves of length less than $\alpha$ and a function $\zeta_A\from P_A\to\OP$ that designates each position as an $O$-position or a $P$-position.
-We require that $sa$ is a $P$-position if $a$ is a $P$-move and and $O$-position if $a$ is an $O$-move, so $\zeta_A$ only gives us information about plays of limiting length.
-
-  $P_A$ is subject to a continuity condition: if $s$ is a sequence of moves whose length is a limit ordinal and $t\in P_A$ for all proper prefixes $t\pprefix s$, then $s\in P_A$.
-
-  We say that a game $A$ is \emph{completely negative} if every position of limiting length is a $P$-position.  
+  A \emph{game} or a \emph{game over $\alpha$} or an \emph{$\alpha$-game} is a tuple $A=(M_A,\lambda_A,\zeta_A,P_A)$, where:
+  \begin{itemize}
+    \item $M_A$ is a set of moves
+    \item $\lambda_A\from M_A\to\OP$ designates each move as an \emph{$O$-move} or a \emph{$P$-move}
+    \item $P_A\subset M_A^{*<\alpha}$ is a non-empty prefix-closed set of transfinite sequences of moves from $M_A$, called \emph{positions}.
+We say that $s$ is a \emph{successor position} if the length of $s$ is a successor ordinal and we say that $s$ is a \emph{limiting} position if the length of $s$ is a limit ordinal.
+    \item $\zeta_A\from P_A\to\OP$ designates each position as an \emph{$O$-position} or a \emph{$P$-position}.
+  \end{itemize}
+  such that:
+  \begin{description}
+    \item[Consistency] If $sa\in P_A$ is a successor position, then $\zeta_A(sa) = \lambda_A(a)$
+    \item[Alternation] If $s,sa\in P_A$, then $\zeta_A(s) = \neg\zeta_A(sa)$
+    \item[Limit closure] If $s\in M_A^{*<\alpha}$ is a limiting position such that $t\in P_A$ for all proper prefixes $t\pprefix s$, then $s\in P_A$.
+  \end{description}
+
+  We say that a game $A$ is \emph{positive} if $\zeta_A(\emptyplay)=O$ and \emph{negative} if $\zeta_A(\emptyplay) = P$.
+We say that $A$ is \emph{completely negative} if $\zeta_A(s)=P$ for all limiting plays $s$.
 \end{definition}
 
+Apart from the possibly transfinite length of sequences of moves, the only new thing in this definition is the function $\zeta_A$.
+Thanks to the consistency condition, $\zeta_A$ gives us no new information for successor positions; it is necessary in order to tell us which player is to move at limiting positions.
+
 \begin{definition}
-  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty subforest (prefix-closed subset) of $P_A$ that satisfies closure under $O$-replies and the determinism condition, just as for finite strategies.
+  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty prefix-closed subset $\sigma\subset P_A$ satisfying the following conditions:
+  \begin{description}
+    \item[Closure under $O$-replies] If $s\in\sigma$ is a $P$-position and $sa\in P_A$, then $sa\in\sigma$.
+    \item[Determinism] If $sa,sb\in\sigma$ are $P$-positions, then $a=b$.
+  \end{description}
 \end{definition}
 
-We can form the product, tensor product, sequoid, exponential and linear implication in the same way that we do for finite games.
-The $\zeta$-functions are extended to connectives according to the propositional formulae given for win-games above.
-If $A$ and $B$ are completely negative, then so are $A\times B$, $A\tensor B$, $A\sequoid B$ and $\oc A$, but $A\implies B$ might not be completely negative.
-
-Given games $A,B,C$, strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we may compose $\sigma$ and $\tau$ in the same way that we compose strategies for finite games (but we have to use the fact that $\alpha$ is additively indecomposable so that we can ensure that the interleaving of sequences of length less than $\alpha$ still has length less than $\alpha$).
-
-We can show that this composition is associative and moreover that we obtain a distributive and decomposable sequoidal category whose objects are completely negative games.
+Given games $A$ and $B$, we may form their product $A\times B$, tensor product $A\tensor B$, linear implication $A\implies B$ and sequoid $A\sequoid B$ in roughly the same way that we construct these connectives for finite-length games.
+The only point we need to take care of is the behaviour of the $\zeta$-functions at limit ordinals.
+We do this according to the following formulae:
+\begin{gather*}
+  \zeta_{A\times B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
+  \zeta_{A\tensor B}(s) = \zeta_A(s) \wedge \zeta_B(s) \\
+  \zeta_{A\implies B}(s) = \zeta_A(s) \Rightarrow \zeta_B(s) \\
+  \zeta_{A\sequoid B}(s) = \zeta_A(s) \wedge \zeta_B(s)
+\end{gather*}
+Here, $\wedge$ and $\Rightarrow$ are the usual propositional connectives on $\{T,F\}$, but with $T$ replaced by $P$ and $F$ replaced by $O$.
+
+Once we have defined our connectives, we may define a \emph{morphism} from $A$ to $B$ to be a strategy for $A\implies B$ and we may define composition of morphisms in the usual way: given games $A$, $B$ and $C$, and strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$, we define
+\[
+  \sigma\|\tau = \{\s\in (M_A \cprd M_B \cprd M_C)^{*<\alpha}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}
+  \]
+and then we define
+\[
+  \comp\tau\sigma = \{\s\vert_{A,C}\suchthat\s\in\sigma\|\tau\}
+  \]
+\begin{remark}
+  Since $\alpha$ is additively decomposable, the interleaving of two sequences of length less than $\alpha$ must itself have length less than $\alpha$.
+This is important: if we allow $\alpha$ to be an additively decomposable ordinal, then it is possible to construct two strategies whose composite is not closed under $O$-replies because a particular reply in the interleaving of two sequences occurs at time later than $\alpha$ and so is not included.
+\end{remark}
+
+We can show that this composition is associative and moreover that we obtain an inclusive, distributive, decomposable sequoidal category.
 We call this category $\G(\alpha)$ and call the corresponding strict subcategory $\G_s(\alpha)$.
 The hardest part of this is showing that the category is monoidal closed, because the linear implication of completely negative games is not necessarily completely negative.
-It turns out that there is always a `minimal' completely negative game extending $A\implies B$, which gives us the monoidal closed structure, but we will not discuss this here, since monoidal closedness is not particularly important to any of our constructions.
 
@@
 We want to show that this is the final coalgebra for $A\sequoid\blank$.
-The proof for the finite case found in \cite{martinsthesis} will not work in this case, since it implicitly uses the fact that $\oc A$ is an MTT-exponential.
-In the transfinite categories, this is no longer the case.
-
-While it is possible to prove that $\alpha_A\from \oc A\to A\sequoid \oc A$ is the final coalgebra for $A\sequoid\blank$ directly, we shall instead give a proof by extending the MTT sequence to the full final sequence.
-We shall give a complete classification of the games $A^{\sequoid\gamma}$ and use it to show that the final sequence for $A\sequoid\blank$ must stabilize at $\oc A$.
-
-\begin{definition}
+The proof for the finite case found in \cite{martinsthesis} will not work in this case, since it implicitly uses the fact that $\oc A$ is the limit of the sequence
+\[
+  I \leftarrow A \leftarrow A \sequoid A \leftarrow A \sequoid (A \sequoid A) \leftarrow \cdots
+  \]
+(cf. also \cite{MelliesCofCommCom}).  In the transfinite categories, this is no longer the case.
+
+While it is possible to prove that $\alpha_A\from \oc A\to A\sequoid \oc A$ is the final coalgebra for $A\sequoid\blank$ directly, we shall instead give a proof by extending the sequence given above to an ordinal-indexed sequence.
+This is the \emph{final sequence}, familiar in coalgebra \cite{finalseq}.
+Specifically, we construct a functor $\F\from\oppcat{\Ord}\to\G(\alpha)$, where $\Ord$ is the order category of the ordinals, writing
+\begin{gather*}
+  \F(\gamma)=A^{\sequoid\gamma}\\
+  \F(\gamma\le\delta)=j_\gamma^\delta\from A^{\sequoid\delta}\to A^{\sequoid\gamma}
+\end{gather*}
+according to the following inductive recipe:
+\begin{itemize}
+  \item $A^{\sequoid 0} = 1$
+  \item $A^{\sequoid (\gamma + 1)} = A \sequoid A^{\sequoid\gamma}$
+  \item If $\mu$ is a limit ordinal, then $A^{\sequoid\mu}$ is the limit of the diagram formed by the $A^{\sequoid\gamma}$ for $\gamma<\mu$, together with the morphisms $j_\gamma^\delta$, for $\gamma\le\delta<\mu$.
+  \item $j_0^\gamma=*$
+  \item $j_\gamma^\lambda$ is the morphism in the limiting cone
+  \item $j_\gamma^{\delta+1} = \comp{j_\delta^{\delta+1}}{j_\gamma^\delta}$
+  \item If we write $C_\lambda$ for the limiting cone for $\lambda$ over the $A^{\sequoid\gamma}$ for $\gamma<\mu$, then we may form a cone $A\sequoid C_\lambda$ over the same diagram by applying the functor $A\sequoid\blank$ to $C_\lambda$ and then extending the cone to $1$ in the only possible way.
+Then $j_\lambda^{\lambda+1}$ is the unique morphism from $A^{\sequoid(\lambda+1)}$ to $A^{\sequoid\lambda}$ inducing a morphism of cones from $A\sequoid C_\lambda$ to $C_\lambda$.
+\end{itemize}
+
+It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then ${j_\delta^{\delta+1}}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
+In this case, we say that the sequence \emph{stabilizes at $\delta$}.
+Our proof strategy is therefore to show that the sequence stabilizes at some $\delta$, and to show that $A^{\sequoid\delta}$ is isomorphic to $\oc A$.
+
+We do this by giving a classification of the games $A^{\sequoid\gamma}$.
 Let $s\in\omega^{*<\alpha}$ be any transfinite sequence of natural numbers.
@@
 \end{itemize}
-\end{definition}
-
-It is easy to prove some basic results about these predicates:
+
+We can prove some basic results about these predicates:
 \begin{proposition}\label{basicResultsAboutRank}
@@
 \end{proposition}
+
 \begin{proof}
-  Left as an exercise.  
-\end{proof}
-
-We can then classify the terms of the final sequence for $A\sequoid\blank$ as follows:
+  See Appendix.
+\end{proof}
+
+Our classification result for the final sequence then becomes:
 \begin{theorem}\label{finalseqClassification}
@@
 \end{theorem}
+
+\begin{proof}
+  See Appendix.
+\end{proof}
 
@@
 
-In particular, $\oc A$ is the carrier of the final coalgebra for $A\sequoid\blank$.  But, as we saw before, it is not the carrier for the cofree commutative comonoid over $A$.
-
-%%
-%% Bibliography
-%%
-
-%% Either use bibtex (recommended),
-
-\bibliography{bibliography}\vfill
-
-%% .. or use the thebibliography environment explicitely
-
-\pagebreak
-
 \appendix
@@
   $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
-Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
+Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
 \end{proposition}
@@
 \begin{proof}
-  We may paste together the anamorphism diagrams for $\int_A$ and $\sigma_A$ to form the following diagram (where we shall omit subscripts where there is no ambiguity):
+  We may paste together diagrams \eqref{definitionOfInt} and \eqref{definitionOfSigma} to form the following diagram (where we shall omit subscripts where there is no ambiguity):
   \begin{equation*}
@@
 
-Now we are ready to show that $f\mapsto\oc f$ respects composition.
-Let $A,B,C$ be objects, let $f$ be a morphism from $A$ to $B$ and let $g$ be a morphism from $B$ to $C$.
-Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc f$, $\oc g$, we may construct a commutative diagram:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[d, "\oc f"']
+Now we are ready to show that $\sigma\mapsto\oc \sigma$ respects composition.
+Let $A,B,C$ be objects, let $\sigma$ be a morphism from $A$ to $B$ and let $\tau$ be a morphism from $B$ to $C$.
+Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc\sigma$, $\oc\tau$, we may construct a commutative diagram:
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\mu"] \arrow[d, "\oc\sigma"']
       & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-        & A \tensor \oc A \arrow[r, "f\tensor\id"]
-          & B \tensor \oc A \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
-            & B \sequoid \oc A \;\times\; \oc A \sequoid B \arrow[d, "\id\sequoid\oc f\;\times\;\oc f\sequoid\id"] \\
-    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc g"']
+        & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
+          & B \tensor \oc A \arrow[r, "\wk"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
+            & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
+    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc \tau"']
       & \oc B \tensor \oc B \arrow[rr, "\der\tensor\id"]
         &
-          & B \tensor \oc B \arrow[r, "\dec"] \arrow[d, "g\tensor\id"]
-            & B \sequoid \oc B \;\times\; \oc B \sequoid B \\
+          & B \tensor \oc B \arrow[r, "\wk"] \arrow[d, "\tau\tensor\id"]
+            & B \sequoid \oc B \\
     %
@@
         &
-          & C \tensor \oc B \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc g"']
-            & C \sequoid \oc B \;\times\; \oc B \sequoid C \arrow[d, "\id\sequoid\oc g\;\times\oc g\sequoid\id"] \\
+          & C \tensor \oc B \arrow[r, "\wk"] \arrow[d, dotted, "\id\tensor\oc\tau"']
+            & C \sequoid \oc B \arrow[d, "\id\sequoid\oc\tau"] \\
     \oc C \arrow[r, "\mu"]
@@
         &
-          & C \tensor \oc C \arrow[r, "\dec"]
-            & C \sequoid \oc C \;\times \oc C \sequoid C
-  \end{tikzcd}
-  \]
-Here, the outermost (solid) shapes are the product of shapes that commute by the definition of $\oc f$, $\oc g$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
-The smaller squares on the right hand side commute because $\dec$ is a natural transformation.
-Since $\dec$ is an isomorphism, the two rectangles on the left commute as well.
+          & C \tensor \oc C \arrow[r, "\wk"]
+            & C \sequoid \oc C
+  \end{tikzcd}
+  \]
+Here, the outermost (solid) shapes commute by the definition of $\oc\sigma$, $\oc\tau$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
+The smaller squares on the right hand side commute because $\wk$ is a natural transformation.
+Now observe that $\wk_{X,Y}=\comp{\pr_1}{\dec_{X,Y}}$ is the composition of epimorphisms, so is an epimorphism for all $X,Y$.
+It follows that the two rectangles on the left commute as well.
 
@@
   \begin{tikzcd}
-    \oc A \arrow[r, "\comp{(f \tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
-      &[72pt] B \tensor \oc A \arrow[r, "g \tensor\id"] \arrow[d, "\id\tensor\oc f"']
-        & C \tensor \oc A \arrow[d, "\id\tensor\oc f"] \\
-    \oc B \arrow[d, "\oc g"']
-      & B \tensor\oc B \arrow[r, "g\tensor\id"] \arrow[d, "g\tensor\oc\tau"']
-        & C \tensor \oc B \arrow[dl, "\id\tensor\oc g"] \\
+    \oc A \arrow[r, "\comp{(\sigma\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc\sigma"']
+      &[72pt] B \tensor \oc A \arrow[r, "\tau\tensor\id"] \arrow[d, "\id\tensor\oc\sigma"']
+        & C \tensor \oc A \arrow[d, "\id\tensor\oc\sigma"] \\
+    \oc B \arrow[d, "\oc\tau"']
+      & B \tensor\oc B \arrow[r, "\tau\tensor\id"] \arrow[d, "\tau\tensor\oc\tau"']
+        & C \tensor \oc B \arrow[dl, "\id\tensor\oc\tau"] \\
     \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
@@
   \]
-We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and apply $\wk$ on the right hand side:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
-      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc f"'] \arrow[r, "\wk"]
-        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc f"] \\
-    \oc B \arrow[d, "\oc g"']
-      & C \tensor \oc B \arrow[d, "\id\tensor\oc g"'] \arrow[r, "\wk"]
-        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc g"] \\
+We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and re-apply $\wk$ on the right hand side:
+\[
+  \begin{tikzcd}
+    \oc A \arrow[r, "\comp{((\comp\tau\sigma)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc\sigma"']
+      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc\sigma"'] \arrow[r, "\wk"]
+        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
+    \oc B \arrow[d, "\oc\tau"']
+      & C \tensor \oc B \arrow[d, "\id\tensor\oc\tau"'] \arrow[r, "\wk"]
+        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc\tau"] \\
     \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
@@
 \[
-  \comp{\oc g}{\oc f} = \fcoal{\comp{\wk}{\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp g f)
+  \comp{\oc\tau}{\oc\sigma} = \fcoal{\comp{\wk}{\comp{((\comp\tau\sigma)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp\tau\sigma)
   \]
@@
   \]
-By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.  That is, for any games $A,B,C$, we need to show that the following diagrams commute:
-\[
-  \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\assoc_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id_{\oc C}"']
-      &[24pt] \oc A \tensor (\oc B \tensor \oc C) \arrow[d, "\id_{\oc A}\tensor\int_{B,C}"] \\
-    \oc (A \times B) \tensor \oc C \arrow[d, "\int_{A\times B,C}"']
-      & \oc A \tensor \oc(B \times C) \arrow[d, "\int_{A,B\times C}"] \\
-    \oc ((A \times B) \times C) \arrow[r, "\oc\assoc_{\times,A,B,C}"']
-      & \oc (A \times (B \times C))
-  \end{tikzcd}
-\]
-\[
-  \begin{tikzcd}
-    I \tensor \oc A \arrow[r, "\varepsilon\tensor\id"]
-      & \oc 1 \tensor \oc A \arrow[d, "\int_{1,A}"] \\
-    \oc A \arrow[u, "\lunit_{\oc A}"] \arrow[r, "\oc\lunit_A"]
-      & \oc (1 \times A)
-  \end{tikzcd}\quad
-  \begin{tikzcd}
-    \oc A \tensor I \arrow[r, "\id\tensor\varepsilon"]
-      & \oc A \tensor \oc 1 \arrow[d, "\int_{A,1}"] \\
-    \oc A \arrow[r, "\oc\runit_A"] \arrow[u, "\runit_{\oc A}"]
-      & \oc (A \times 1)
-  \end{tikzcd}\quad
-  \begin{tikzcd}
-    \oc A \tensor \oc B \arrow[r, "\sym_{A,B}"] \arrow[d, "\int_{A,B}"']
-      & \oc B \tensor \oc A \arrow[d, "\int_{B,A}"] \\
-    \oc(A\times B) \arrow[r, "\oc\sym_{A,B}"]
-      & \oc(B\times A)
-  \end{tikzcd}
-  \]
-
-We first prove a small lemma, which gives us a simpler way to compute $\oc \sigma$ in the case that $\sigma$ is a morphism in $\C_s$.
-
-\begin{lemma}\label{ocStrict}
-  Let $A,B$ be objects of $\C_s$ and let $\sigma$ be a morphism from $A$ to $B$ in $\C_s$.  Then the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\oc \sigma"']
-        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
-          & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
-      \oc B \arrow[rr, "\alpha_B"]
-        &
-          & B \sequoid \oc B
-    \end{tikzcd}
-    \]
-\end{lemma}
-
-\begin{proof}
-  By the definition of $\oc \sigma$, we have the following commutative diagram:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\mu_A"] \arrow[d, "\oc \sigma"']
-        & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-          & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
-            & B \tensor \oc A \arrow[r, "\wk"]
-              & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
-      \oc B \arrow[rrrr, "\alpha_B"]
-        &
-          &
-            &
-              & B \sequoid \oc B
-    \end{tikzcd}
-    \]
-  Therefore, it will suffice to show that the following diagram (solid lines) commutes:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\mu_A"']
-        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
-          & B \sequoid \oc A \\
-      \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-        & A \tensor \oc A \arrow[u, dotted, "\wk"] \arrow[r, "\sigma\tensor\id"]
-          & B \tensor \oc A \arrow[u, "\wk"]
-    \end{tikzcd}
-    \]
-  The left hand square commutes by Lemma \ref{aFormulaForAlpha}.  The right hand square commutes because $\wk$ is a natural transformation.
-\end{proof}
-
-To show that the first coherence diagram commutes, we define a composite $\eta_{A,B,C}$:
-\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
-\begin{gather*}
-  (\oc A \tensor \oc B) \tensor \oc C \constantwidthxrightarrow{\langle\id,\; \sym\rangle} ((\oc A \tensor \oc B) \tensor \oc C) \times (\oc C \tensor (\oc A \tensor \oc B)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{((\comp{\dist\inv}{\kappa_{A,B}})\tensor\id)\times(\alpha_C\tensor\id)} (((A \times B) \sequoid (\oc A \tensor \oc B)) \tensor \oc C) \times ((C \sequoid \oc C) \tensor (\oc A \tensor \oc B)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} (((A \times B) \sequoid (\oc A \tensor \oc B)) \sequoid \oc C) \times ((C \sequoid \oc C) \sequoid (\oc A \tensor \oc B)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid (\oc C \tensor (\oc A \tensor \oc B))) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C))
-\end{gather*}
-
-Observe the similarity between the definition of $\eta_{A,B,C}$ and that of $\kappa_{A\times B,C}$.
-Indeed, it may be easily verified that the following diagram commutes, using the definition of $\int_{A,B}$ as the anamorphism for $\comp{\dist\inv}{\kappa_{A,B}}$ and the fact that $\wk$, $\passoc$ and $\sym$ are natural transformations:
-\begin{equation}\label{kreuz}
-  \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\eta_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id"']
-      & ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \arrow[d, "(\id\sequoid(\int\tensor\id))\times (\id\sequoid(\int\tensor\id))"] \\
-    \oc (A \times B) \tensor \oc C \arrow[r, "\kappa_{A\times B,C}"]
-      & ((A \times B) \sequoid (\oc (A \times B) \tensor \oc C)) \times (C \sequoid (\oc (A \times B) \tensor \oc C))
-  \end{tikzcd}\tag{\kreuz}
-\end{equation}
-Then we get the commutative diagram in Figure \ref{CoherenceOneWay}, which tells us that one of the two paths round the coherence diagram is the anamorphism of $\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}$.
-We now show that the other path round the coherence diagram is the anamorphism of the same thing, which will prove that they are equal.
-
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[ampersand replacement=\&]
-      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\eta_{A,B,C}}"] \arrow[d, "\int_{A,B}\tensor\id"'] \arrow[phantom, dr, "\textbf{a}"]
-        \&[24pt] ((A \times B) \times C) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid(\int\tensor\id)"] \arrow[phantom, dr, "\textbf{b}"]
-          \&[19pt] (A \times (B\times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid(\int\tensor\id)"] \\
-      \oc (A \times B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\kappa_{A\times B,C}}"] \arrow[d, "\int_{A\times B,C}"'] \arrow[phantom, dr, "\textbf{d}"]
-        \& ((A \times B) \times C) \sequoid (\oc(A\times B)\tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid\int"] \arrow[phantom, dr, "\textbf{c}"]
-          \& (A \times (B\times C)) \sequoid (\oc(A\times B)\tensor\oc C) \arrow[d, "\id\sequoid\int"] \\
-      \oc((A\times B)\times C) \arrow[r, "\alpha_{(A\times B)\times C}"] \arrow[d, "\oc \assoc_\times"'] \arrow[phantom, drr, "\textbf{e}"]
-        \& ((A\times B) \times C) \sequoid \oc ((A\times B)\times C) \arrow[r, "\assoc_\times\sequoid\id"]
-          \& (A \times (B\times C)) \sequoid \oc (A \times(B \times C)) \arrow[d, "\id\sequoid\oc \assoc_\times"] \\
-      \oc(A \times (B\times C)) \arrow[rr, "\alpha_{A\times(B\times C)}"]
-        \&
-          \& (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
-    \end{tikzcd}
-    \]
-  \caption{\textbf{a} commutes by Diagram \eqref{kreuz}, plus the fact that $\dist$ is a natural transformation.  \\[\baselineskip]
-  \textbf{b} and \textbf{c} commute because $\assoc_\times$ is a natural transformation.  \\[\baselineskip]
-  \textbf{d} commutes by the definition of $\int_{A\times B,C}$.  \\[\baselineskip]
-  \textbf{e} commutes by Lemma \ref{ocStrict}.}\label{CoherenceOneWay}
-\end{SidewaysFigure}
-
-For this, we define a composite $\tilde{\eta}_{A,B,C}$:
-\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
-\begin{gather*}
-  \oc A \tensor (\oc B \tensor \oc C) \constantwidthxrightarrow{\langle\sym,\id\rangle} (\oc A \tensor (\oc B \tensor \oc C)) \times ((\oc B \tensor \oc C) \tensor \oc A) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{(\alpha_A\tensor\id)\times((\comp{\dist\inv}{\kappa_{B,C}})\tensor\id)} ((A \sequoid \oc A) \tensor (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \tensor \oc A) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} ((A \sequoid \oc A) \sequoid (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \sequoid \oc A) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid ((\oc B \tensor \oc C) \tensor \oc A)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid (A \tensor (\oc B \tensor \oc C))) \\
-\end{gather*}
-
-We get a commutative diagram:
-\[
-  \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}"] \arrow[d, "\assoc_{A,B,C}"']
-      &[78pt] (A \times (B \times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
-    \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\tilde{\eta}_{A,B,C}}}"] \arrow[d, "\id\tensor\int"']
-      & (A \times (B \times C)) \sequoid (\oc A \tensor (\oc B \tensor \oc C)) \arrow[d, "\id\sequoid(\id\tensor\int)"] \\
-    \oc A \tensor \oc(B \times C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\kappa_{A,B\times C}}}"] \arrow[d, "\int_{A,B\times C}"']
-      & (A \times (B \times C)) \sequoid (\oc A \tensor \oc (B\times C)) \arrow[d, "\id\sequoid\int"] \\
-    \oc (A \times (B \times C)) \arrow[r, "\alpha_{A\times(B\times C)}"]
-      & (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
-  \end{tikzcd}
-  \]
-
-Commutativity of the top square is a long and fairly unenlightening exercise in the coherence conditions for symmetric monoidal categories and for sequoidal categories.
-Commutativity of the middle and bottom squares are by similar arguments to the ones in Figure \ref{CoherenceOneWay}.
-Therefore, the two branches of the coherence diagram are anamorphisms for the same thing, and so they are equal.
-
-The proofs for the other three coherence diagrams are similar.
-
-\subsection{Proof of Proposition \ref{itsMu}}
-
-\begingroup
-\def\thetheorem{\ref{itsMu}}
-\begin{proposition}
-  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ has comultiplication given by $\mu_A\from\oc A \to \oc A\tensor\oc A$ and counit given by the unique morphism $\eta_A\from \oc A \to I$.
-\end{proposition}
-\addtocounter{theorem}{-1}
-\endgroup
-
-By the definition of $\CCom$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite:
-\[
-  \oc A \xrightarrow{\oc\Delta} \oc (A \times A) \xrightarrow{\int_{A,A}\inv} \oc A \times \oc A
-  \]
-By Lemma \ref{ocStrict}, the morphism $\oc\Delta$ is equal to the morphism $\sigma_A$ defined above.  So this composite is equal to $\comp{\int_{A,A}}{\sigma_A}=\mu_A$.
-
-The counit is a morphism $\oc A\to I$, so by uniqueness it must be equal to $\eta_A$.
-
-\subsection{Proof of Theorem \ref{Coalgebra__CoCoCo}}
-
-\begingroup
-\def\thetheorem{\ref{Coalgebra__CoCoCo}}
-\begin{theorem}
-  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.
-Let $A$ be an object of $\C$ (equivalently, of $\C_s$).
-Then $\oc A$, together with the comultiplication $\mu_A$ and counit $\eta_A$, is the cofree commutative comonoid over $A$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-
-We know from Proposition \ref{itsMu} that the $(\oc A,\mu_A,\eta_A)$ is indeed a commutative comonoid.
-Now let $\delta\from B\to B\tensor B$ be a commutative comonoid in $\C$ and let $f\from B\to A$ be a morphism.
-We need to show that there is a unique morphism $f^\dag\from B \to \oc A$ such that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[r, "\delta"] \arrow[d, "f^\dag"] \arrow[dl, "f"']
-        & B \tensor B \arrow[d, "f^\dag\tensor f^\dag"] \\
-    A
-      & \oc A \arrow[l, "\der_A"] \arrow[r, "\mu_A"]
-        & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-We define the morphism $f^\dag$ to be the anamorphism of the composite:
-\[
-  B \xrightarrow{\delta} B \tensor B \xrightarrow{f\tensor\id B} A \tensor B \xrightarrow{\wk_{A,B}} A \sequoid B
-  \]
-We first claim that it makes the given diagram commute, starting with the square on the left.
-We show that $\comp{\int_{A,A}}{\comp{\mu_A}{f^\dag}}=\comp{\int_{A,A}}{\comp{(f^\dag\tensor f^\dag)}{\delta}}\from B \to \oc (A\times A)$, by showing that both morphisms are anamorphisms for the composite
-\[
-  B \xrightarrow{\delta} B \tensor B \xrightarrow{f\tensor\id_B} A \tensor B \xrightarrow{\wk_{A,B}} A \sequoid B \xrightarrow{\Delta} (A \sequoid B) \times (A \sequoid B) \xrightarrow{\dist_{A,B}\inv} (A \times A) \sequoid B
-  \]
-Since $\int_{A,A}$ is an isomorphism, this will prove that the square on the right commutes.
-
-For the first case, the diagram in Figure \ref{transferReportDiagram1} proves that $\comp{\int_{A,A}}{\comp{\mu_A}{f^\dag}}=\comp{\sigma_A}{f^\dag}$ is the anamorphisms for that composite.
-For the other case, taking the product of the diagrams in Figure \ref{transferReportDiagram2} gives rise to the diagram in Figure \ref{transferReportDiagram3}, which proves that $\comp{\int_{A,A}}{\comp{(f^\dag\tensor f^\dag)}{\delta}}$ is the anamorphism for the same composite, which completes the proof that the right hand square commutes.
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[cramped, ampersand replacement=\&]
-      B \arrow[r, "\delta"] \arrow[d, "f^\dag"'] \arrow[phantom, drrr, "\textbf{a}"]
-        \& B \tensor B \arrow[r, "f\tensor\id_B"]
-          \& A \tensor B \arrow[r, "\wk_{A,B}"]
-            \& A \sequoid B \arrow[r, "\Delta"] \arrow[d, "\id\sequoid f^\dag"] \arrow[phantom, dr, "\textbf{b}" xshift=0.6em]
-              \& (A \sequoid B) \times (A \sequoid B) \arrow[r, "\dist_{A,B}\inv"] \arrow[d, "(\id\sequoid f^\dag)\times(\id\sequoid f^\dag)"] \arrow[phantom, dr, "\textbf{c}" xshift=2.0em]
-                \& (A \times A) \sequoid B \arrow[d, "\id\sequoid f^\dag"] \\
-      \oc A \arrow[rrr, "\alpha_A"] \arrow[d, "\sigma_A"'] \arrow[phantom, drrrrr, "\textbf{d}"]
-        \&
-          \&
-            \& A \sequoid \oc A \arrow[r, "\Delta"]
-              \& (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[r, "\dist_{A,\oc A}\inv"]
-                \& (A \times A) \sequoid \oc A \arrow[d, "\id\sequoid\sigma_A"] \\
-      \oc (A\times A) \arrow[rrrrr, "\alpha_{A\times A}"]
-        \&
-          \&
-            \&
-              \&
-                \& (A \times A) \sequoid \oc (A\times A)
-    \end{tikzcd}
-    \]
-  \caption{\textbf{a} commutes by the definition of $f^\dag$.\\[\baselineskip]
-    \textbf{b} commutes because $\Delta$ is a natural transformation.  \textbf{c} commutes because $\dist$ is a natural transformation. \\[\baselineskip]
-    \textbf{d} commutes be the definition of $\sigma_A$.
-  }\label{transferReportDiagram1}
-\end{SidewaysFigure}
-
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[ampersand replacement=\&]
-      B \arrow[r, "\delta"] \arrow[dd, "\delta"'] \arrow[ddr, phantom, "\textbf{a}"]
-        \& B\tensor B \arrow[r, "f\tensor \id_B"] \arrow[d, "\id_B\tensor\delta"]
-          \& A \tensor B \arrow[rrr, "\wk"] \arrow[d, "\id_A\tensor\delta"] \arrow[drrr, phantom, "\textbf{b}"]
-            \&
-              \&
-                \& A\sequoid B \arrow[d, "\id_A\sequoid\delta"] \\
-      %
-        \& B \tensor(B\tensor B) \arrow[r, "f\tensor\id_{B\tensor B}"] \arrow[d, "{\assoc_{B,B,B}\inv}"] \arrow[phantom, dr, "\textbf{d}" xshift=0.3em]
-          \& A \tensor (B \tensor B) \arrow[rrr, "\wk"] \arrow[drr, phantom, "\textbf{g}"] \arrow[d, "\assoc_{A,B,B}\inv"]
-            \&
-              \&
-                \& A \sequoid (B\tensor B) \arrow[dd, "\id_A\sequoid(f^\dagger \tensor f^\dagger)"] \arrow[dl, "{\passoc_{A,B,B}}"] \arrow[ddl, phantom, "\textbf{e}"] \\
-      B \tensor B \arrow[r, "\delta\tensor \id_B"] \arrow[d, "f^\dagger \tensor f^\dagger"'] \arrow[drrr, phantom, "\textbf{f}" yshift=-0.3em]
-        \& (B \tensor B) \tensor B \arrow[r, "(f\tensor\id_B)\tensor\id_B"' yshift=-0.3em]
-          \& (A \tensor B) \tensor B \arrow[r, "\wk\tensor\id_B"]
-            \& (A \sequoid B) \tensor B \arrow[r, "\wk"] \arrow[d, "(\id\sequoid f^\dagger)\tensor f^\dagger"'] \arrow[dr, phantom, "\textbf{c}"]
-              \& (A\sequoid B)\sequoid B \arrow[d, "(\id\sequoid f^\dagger)\sequoid f^\dagger"]
-                \& \\
-      \oc A \tensor \oc A \arrow[rrr, "\alpha\tensor\id_{\oc A}"']
-        \&
-          \&
-            \& (A \sequoid \oc A)\tensor \oc A \arrow[r, "\wk"]
-              \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-                \& A \sequoid (\oc A \tensor \oc A)
-    \end{tikzcd}
-  \]
-\[
-  \begin{tikzcd}[ampersand replacement=\&]
-    %
-    \& B \arrow[r, "\delta"] \arrow[d, "\delta"] \arrow[dl, "\delta"'] \arrow[phantom, ddl, "\textbf{h}" near start] \arrow[phantom, ddrrr, "\textbf{j}"]
-        \& B \tensor B \arrow[r, "f\tensor\id_B"]
-          \& A \tensor B \arrow[r, "\wk"]
-            \& A \sequoid B \arrow[d, "\id\sequoid\delta"] \\
-    B \tensor B \arrow[r, "\sym"] \arrow[d, "f^\dag\tensor f^\dag"'] \arrow[phantom, dr, "\textbf{i}"]
-      \& B \tensor B \arrow[d, "f^\dag\tensor f^\dag"]
-        \&
-          \&
-            \& A \sequoid (B \tensor B) \arrow[d, "\id\sequoid(f^\dag\tensor f^\dag)"] \\
-    \oc A \tensor \oc A \arrow[r, "\sym"]
-      \& \oc A \tensor \oc A \arrow[r, "\alpha_A \tensor \id_A"']
-        \& (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"]
-          \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            \& A \sequoid (\oc A \tensor \oc A)
-  \end{tikzcd}
-  \]
-  \caption{\textbf{a} commutes because the comultiplication $\delta$ is associative.\\[\baselineskip]
-    \textbf{b} and \textbf{c} commute because $\wk$ is a natural transformation.  \textbf{d} and \textbf{e} commute because $\assoc$ and $\passoc$ are natural transformations.  \\[\baselineskip]
-    \textbf{f} is the tensor product of two diagrams: one is the definition of $f^\dag$ and the other one obviously commutes.\\[\baselineskip]
-    \textbf{g} is one of the coherence diagrams for $\wk$.\\[\baselineskip]
-    \textbf{h} commutes because the comultiplication $\delta$ is commutative. \\[\baselineskip]
-    \textbf{i} commutes because $\sym$ is a natural transformation.\\[\baselineskip]
-    \textbf{j} commutes by the first diagram.
-  }\label{transferReportDiagram2}
-\end{SidewaysFigure}
-
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[ampersand replacement=\&]
-      B \arrow[r, "\delta"] \arrow[d, "\delta"'] \arrow[phantom, ddrrrr, "\textbf{a}"]
-        \& B \tensor B \arrow[r, "f\tensor\id_B"]
-          \& A \tensor B \arrow[r, "\wk"]
-            \& A \sequoid B \arrow[r, "\Delta"]
-              \& (A \sequoid B) \times (A \sequoid B) \arrow[r, "\dist_{A,B}\inv"] \arrow[d, "(\id_A\sequoid\delta)\times(\id_A\sequoid\delta)"'] \arrow[phantom, ddr, "\textbf{b}" xshift=1.2em]
-                \& (A \times A) \sequoid B \arrow[d, "\id_{A\times A}\sequoid\delta"] \\
-      B \tensor B \arrow[d, "f^\dag\tensor f^\dag"']
-        \&
-          \&
-            \&
-              \& (A \sequoid (B \tensor B)) \times (A \sequoid (B \tensor B)) \arrow[d, "(\id_A \sequoid (f^\dag\tensor f^\dag))\times(\id_A \sequoid (f^\dag\tensor f^\dag))"']
-                \& (A \times A) \sequoid (B \tensor B) \arrow[d, "\id_{A\times A} \sequoid (f^\dag\tensor f^\dag)"] \\
-      \oc A \tensor \oc A \arrow[rrrr, "\sigma_A"] \arrow[d, "\int_{A,A}"'] \arrow[phantom, drrrrr, "\textbf{c}"]
-        \&
-          \&
-            \&
-              \& (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "\dist_{A,\oc A \tensor \oc A}\inv" yshift=0.3em]
-                \& (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[d, "\id_{A\times A}\sequoid\int_{A,A}"] \\
-      \oc (A\times A) \arrow[rrrrr, "\alpha_{A\times A}"]
-        \&
-          \&
-            \&
-              \&
-                \& (A \times A) \sequoid \oc(A\times A)
-    \end{tikzcd}
-    \]
-  \caption{\textbf{a} is the product of the diagrams in Figure \ref{transferReportDiagram2}.\\[\baselineskip]
-    \textbf{b} commutes because $\dist$ is a natural transformation.\\[\baselineskip]
-    \textbf{c} is the definition of $\int_{A,A}$
-  }\label{transferReportDiagram3}
-\end{SidewaysFigure}
-
-Now the following diagrams show that the triangle on the left commutes:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\delta"] \arrow[d, "f^\dag"']
-      & B \tensor B \arrow[r, "f\tensor\id_B"]
-        & A \tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[dr, "\id_A\sequoid*"] \arrow[d, "\id_A\sequoid f^\dag"']
-            & 
-              & \\
-    \oc A \arrow[rrr, "\alpha_A"']
-      &
-        &
-          & A \sequoid \oc A \arrow[r, "\id_A\sequoid*"']
-            & A \sequoid I \arrow[r, "\run_A"]
-              & A
-  \end{tikzcd}
-  \]
-\[
-  \begin{tikzcd}
-    B \tensor B \arrow[r, "f\tensor\id"] \arrow[d, "\id_B\tensor*"]
-      & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id\tensor*"]
-        & A \sequoid B \arrow[d, "\id\sequoid*"] \\
-    B \tensor I \arrow[r, "f\tensor\id_I"]
-      & A \tensor I \arrow[r, "\wk"]
-        & A \sequoid I \arrow[dl, "\run_A"] \\
-    B \arrow[uu, bend left=100, "\delta"] \arrow[u, "\runit_B"'] \arrow[r, "f"]
-      & A \arrow[u, "\runit_A"]
-        &
-  \end{tikzcd}
-  \]
-In the first diagram, the morphism along the bottom is $\der_A$, by definition.
-The second diagram shows that the morphism along the top of the first diagram is equal to $f$.
-The triangle at the bottom right of that diagram is one of the coherence conditions for $\wk$, while the semicircle at the left commutes because the comultiplication $\delta$ is unital (with unit $*\from B\to I$).
-
-Lastly, we show uniqueness.  Suppose that $g\from B\to\oc A$ makes the diagram commute:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[r, "\delta"] \arrow[d, "g"] \arrow[dl, "f"']
-        & B \tensor B \arrow[d, "g\tensor g"] \\
-    A
-      & \oc A \arrow[l, "\der_A"] \arrow[r, "\mu_A"]
-        & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-We may convert this into the following diagram:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\delta"] \arrow[d, "g"']
-      & B \tensor B \arrow[r, "f\tensor\id_B"] \arrow[d, "g\tensor g"]
-        & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id_A\tensor g"]
-          & A \sequoid B \arrow[d, "\id_A\sequoid g"] \\
-    \oc A \arrow[r, "\mu_A"]
-      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id"]
-        & A \tensor \oc A \arrow[r, "\wk"]
-          & A \sequoid \oc A
-  \end{tikzcd}
-  \]
-Here, the left hand square is taken straight from the previous diagram, while the middle square is the tensor product of the left hand triangle with a diagram that obviously commutes.
-The right hand square commutes because $\wk$ is a natural transformation.
-
-By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.
+By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.
+
+%%
+%% Bibliography
+%%
+
+%% Either use bibtex (recommended),
+
+\bibliography{bibliography}
+
+%% .. or use the thebibliography environment explicitely
 

### 2017-05-08 round-corner/paper/lipics-v2016-authors/jim1/sequoidal (1).tex
A whole bunch of things.

--- 2017-05-08 round-corner/paper/lipics-v2016-authors/jim/sequoidal.tex
@@
 \newcommand{{\cell}}{{\mathsf{cell}}}
-\newcommand{\tr}{\oslash}
-\newcommand{\fix}{{\mathsf{fix}}}
-\newcommand{\eq}{{\mathsf{eq}}}
+
 %\\write{{\mathtt{write}}}
 \def\read{{\mathtt{read}}}
-\def\({\ensuremath{( \! [}}
-\def\){\ensuremath{] \! )}}
-\newcommand{\perm}{{\mathsf{perm}}}
+
 \newcommand{\tensor}{\otimes}
@@
   Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing the monoidal isomorphisms and the morphisms $\wk_{A,B}$, $J$ is the inclusion functor and $J$ reflects isomorphisms.
+
+S
 
 %  If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
- We say that $\C$ is \emph{decomposable} if it is affine, and for any $A$ and $B$, the tensor product $A \otimes B$ is a cartesian product of $A \tr B$ and $B \tr A$, with projections $\wk_{A,B}:A \otimes B \rightarrow A \tr B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \otimes B \rightarrow B \tr A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pi_l \sequoid C,\pi_r \sequoid C$.
-So if $\C$ has all finite products, 
-the natural transformations
+  In that case, we say that $\C$ is \emph{decomposable} if the natural transformations
   \begin{gather*}
     \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
-   % \dec^0 \from I \to 1 \\
+    \dec^0 \from I \to 1
+  \end{gather*}
+  are isomorphisms and we say that $\C$ is \emph{distributive} if the natural transformations
+  \begin{gather*}
     \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
@@
 
-In any inclusive sequoidal category with a cofree exponential we have  a  $A \tr\_$-coalgebra  $\alpha:!A \rightarrow A \tr !A =  \delta;(\eta \otimes !A);\wk_{A \tr !A}$.
-In our category of games this
-%  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, 
-is the final coalgebra for the endofunctor $A\sequoid\blank$.
+  The sequoidal exponential $\oc A$, together with the obvious copycat strategy $\alpha\from\oc A\to A\sequoid\oc A$, is the final coalgebra for the endofunctor $A\sequoid\blank$.
 In other words, if $B$ is a negative game and $\sigma\from B\to A\sequoid B$ is a morphism then there is a unique morphism $\fcoal{\sigma}\from B\to \oc A$ such that the following diagram commutes:
@@
 
-We want to construct  $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ from the final $A\sequoid\blank$-coalgebra, $(\oc A,\alpha)$, and show that it is the cofree commutative comonoid on $A$.
+We want to deduce the fact that $\oc A\xrightarrow{\mu}\oc A\tensor\oc A$ is the cofree commutative comonoid on $A$ from the fact that $\oc A$ is the final coalgebra for $A\sequoid\blank$.
 It turns out that we shall need one more fact about the category of games to prove this.
@@
   See Appendix.
-\end{proof}
-
-\subsection{The Sequoidal Exponential as a Bifree Algebra}
-Observe that in our category of games, $(!A,\alpha)$ is in fact a \emph{bifree algebra} for $A\tr\_$ --- the isomorphism $\alpha^{-1}: A \tr !A \rightarrow !A$ is an initial algebra for  $A \tr \_$.
-We may show that in such cases, the condition that $!$ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $!A$ with the structure of a comonoid by defining:
-$\delta:!A \rightarrow !A  \otimes !A$
- to be the catamorphism of the $A \tr \_$ algebra:
-$$A \tr (!A \otimes !A) %\stackrel{\langle \id, A \tr \sym\rangle}{\cong} 
-\cong A \tr (!A \otimes !A) \times  A \tr (!A \otimes !A) \cong (A \tr !A) \tr !A \times  (A \tr !A) \tr !A \cong (!A \tr !A) \cong (!A \tr !A) \cong (!A \otimes !A)$$     
-This satisfies the further requirements of a \emph{linear category} in the sense of \cite{Bierman}, although it does not appear to be possible to show that it is the cofree commutative comonoid.} :
-we may define an inverse to $\int:!A \otimes !A \rightarrow ! (A \times B)$  as the \emph{catamorphism} of the  $A \tr\_$-algebra:
-$$(A \times B) \tr !A \otimes !B \cong (A \tr (!A \otimes !B)) \times  (B \tr (!A \otimes !B)) \cong (!A \tr !B) \times (!B \tr !A)$$
-
-It is not necessary for the final $A \tr\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid.
-An example is provided by  the category of games with winning conditions and winning strategies, which is sequoidal closed and decomposable.
-To show that the  final $A \tr\_$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\fix_A(f);f = \fix(f)$.
-\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \tr\_$-algebra. Then we may define a fixed point operator on $\C$.  
-\end{proposition}    
-\begin{proof}For any $A$, let  $\Phi_A:!(A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \tr\_ \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \tr A \rightarrow A$, which is a  $(A \multimap A) \tr \_$-algebra.
-For any morphism $f:A \rightarrow A$ we may define $\fix_A(f) = \Lambda(f)^\dag;\Phi_A$, where $\Lambda(f):I \rightarrow (A \multimap A)$ is the ``name'' of $f$.
-\end{proof}
-As one would expect, it is not possible to define a fixed point operator on the category of games and winning strategies ---  for example, if $\bot$ is the game with a single move then the hom-set $\C(I,\bot)$ is empty and hence there can be no morphism $\fix_\bot(\id_\bot)$.
-So the final  $A \tr \_$-coalgebra is not bifree in this case.
-
-\subsection{A formula for the sequoidal exponential}
-We now consider an alternative construction of the cofree commutative comonoid in a sequoidally decomposable category, which leads to some illuminating comparisons with the coalgebraic approach.
-It is based on the formula  given by
-Melli\'es, Tabareau and Tasson \cite{MTT}, which does not depend on the presence of cartesian products, but obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
-\begin{definition}If $A$ is an object in a symmetric monoidal category, a $n$-fold symmetric tensor power of $A$ is an  \emph{equalizer} $(A^n,\eq)$ for the group $G$ of symmetry automorphisms on $A^{\otimes n}$.
-A tensor power is preserved by the tensor product if $(B\otimes A^n,\eq \otimes B)$ is an equalizer for the automorphisms $\{B \otimes g\ |\ g \in G\}$.
-\end{definition}
-In any affine category\footnote{This is a special case of the situation considered in  \cite{MTT}: that $A$ is a ``free pointed object''.} with tensor powers of $A$ we may define a diagram $\Delta(A) = $
-$$I \stackrel{p_0}{\leftarrow} A \stackrel{p_1}{\leftarrow} A^2 \ldots A^i \stackrel{p_i}{\leftarrow} A^{i+1} \ldots$$
-where   
-$p_i:A^{i+1} \rightarrow A^i$ is the unique morphism given by the universal property of the symmetric tensor power,  such that $p_i;\eq_i:A^{i+1} \rightarrow A^{\otimes i} = \eq_{i+1};(A^{\otimes i} \otimes t_A)$.
-
-Melli\'es, Tabareau and Tasson \cite{MTT} have shown that where the limit $(A^\infty, \{p^\infty_i:A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e.
-for each object $B$, $B \otimes A^\infty$ is the limit of
-$$B \otimes I \stackrel{B \otimes p_0}{\leftarrow} B \otimes A  \stackrel{B \otimes p_1}{\leftarrow} B\otimes  A^2 \ldots $$
-then a comultiplication $\delta:A^\infty \rightarrow A^\infty \otimes A^\infty$ may be defined making $(A^\infty,\delta,t_{!A})$ the cofree commutative comonoid.
-Where these conditions are satisfied, we shall call this a MTT-exponential.
-\begin{proposition}Any sequoidally decomposable category has all symmetric tensor powers, and these are preserved by the tensor.  
-\end{proposition} 
-\begin{proof}
-By sequoidal decomposability, for any $n$, $A^{\otimes (n+1)}$ is the cartesian product $\Pi_{i \leq n} (A \tr A^{\otimes n})$ with projections 
-  $\comp{\sym_i}{\wk_{A,A^{\otimes n}}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
-
-  We inductively define the sequoid powers $A^{\sequoid n}$ by $A^{\sequoid 1}=A$ and $A^{\sequoid(n+1)}=A\sequoid A^{\sequoid n}$.
-Given $n$, we inductively define a morphism $\eq_n\from A^{\sequoid n}\to A^{\tensor n}$ as the diagonal $\langle \id_A\sequoid\eq_{n-1}\rangle$ into the product -- so $\comp{\wk}{\comp{\sym_i}{\eq_n}}=\id\sequoid e_{n-1}$ for each $i$.
-
-  If $\pi\in S_n$ is a permutation, we write $\sym^\pi$ for the appropriate symmetry of $A^{\tensor n}$.
-We now claim that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi\in S_n$ -- so $\eq_n$ equalizes the $\sym^\pi$.
-Indeed, let $\pi\in S_n$.
-Then we may write $\sym^\pi = \comp{\id_A\tensor\sym^\rho}{\sym_i}$ for some $i$ and some $\rho\in S_{n-1}$.
-Now we have:
-  \begin{IEEEeqnarray*}{rClC}
-    \comp{\wk}{\comp{\sym^\pi}{\eq_n}} & = & \comp{\wk}{\comp{\comp{(\id\tensor\sym^\rho)}{\sym_i}}{\eq_n}} & \\
-    & = & \comp{(\id\sequoid\sym^\rho)}{\comp{\wk}{\comp{\sym_i}{\eq_n}}} & \hspace{24pt}\textrm{(by naturality of $\wk$)} \\
-    & = & \comp{(\id\sequoid\sym^\rho)}{(\id\sequoid\eq_{n-1})} & \\
-    & = & \id\sequoid\eq_{n-1}
-  \end{IEEEeqnarray*}
-  Since $\pi$ was arbitrary, it follows that $\comp{\wk}{\comp{\comp{\sym_j}{\sym^{\pi}}}{\eq_n}}=\comp{\comp{\wk}{\sym_j}}{\eq_n}$ for all $j$ and therefore that $\comp{\sym^\pi}{\eq_n}=\eq_n$ for all $\pi$, as desired.
-
-  Now define $\wk^n\from A^{\sequoid n}\to A^{\tensor n}$ inductively by $\wk^n = \comp{\id\sequoid\wk^{n-1}}{\wk}$.
-We may show by induction that $\comp{\wk^n}{\eq_n}=\id_{A^{\sequoid n}}$ for all $n$: indeed, we have
-  \begin{IEEEeqnarray*}{rClC}
-    \comp{\wk^n}{\eq_n} & = & \comp{(\id\sequoid\wk^{n-1})}{\comp{\wk}{\eq_n}} & \\
-    & = & \comp{(\id\sequoid\wk^{n-1})}{(\id\sequoid\eq_{n-1})} & \\
-    & = & \id\sequoid \id = \id & \hspace{24pt}\textrm{(by induction)}
-  \end{IEEEeqnarray*}
-  Now let $f\from C \to B \tensor A^{\tensor n}$ be such that $\comp{(\id\tensor\sym^\pi)}{f}=f$ for all $\pi\in S_n$.
-It follows from what we have just shown that if $f=\comp{(\id\tensor\eq_n)}{g}$, then $g=\comp{\comp{\id\tensor\wk^n}{\id\tensor\eq_n}}{g}=\comp{\id\tensor\wk^n}{f}$.
-So we just need to show that
-  \[
-    f=\comp{(\id\tensor(\comp{\eq_n}{\wk_n}))}{f}
-    \]
-  We first assume that $B=I$, so we have $f\from C\to B\tensor A^{\tensor n}$ and $\comp{\sym^\pi}{f}=f$ for all $\pi\in S_n$ and we are trying to show that $f=\comp{\comp{\eq_n}{\wk^n}}{f}$.
-We do this by showing that $\comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}}=\comp{\comp{\wk}{\sym_i}}{f}$ for all $i$.
-
-  Indeed, we have:
-  \begin{IEEEeqnarray*}{rClC}
-    \comp{\comp{\wk}{\sym_i}}{\comp{\comp{\eq_n}{\wk^n}}{f}} & = & \comp{\comp{(\id\sequoid\eq_{n-1})}{(\id\sequoid\wk^{n-1})}}{\comp{\wk}{f}} & \\
-    & = & \comp{\wk}{\comp{(\id\tensor(\comp{\eq_{n-1}}{\wk^{n-1}}))}{f}} &\hspace{24pt}\textrm{(by naturality of $\wk$)} \\
-    & = & \comp{\wk}{f} &\hspace{2pt}\textrm{(by induction)} \\
-    & = & \comp{\wk}{\comp{\sym_i}{f}}
-  \end{IEEEeqnarray*}
-
-  Now let $B$ be an arbitary object of the category.  [TODO: finish working this out.]
-\end{proof}
-Thus, in any sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit for this diagram exists and is preserved by the sequoid, 
---- i.e.
-for any $B$, $B \tr A^\infty$ is the limit for $B \tr \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid.
-Conversely, we may show that any cofree commutative comonoid which arises as a $\otimes$-preserving limit of symmetric tensor powers is a final coalgebra.
-\begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty,\delta;(\eta \otimes !A);\wk_{A \tr !A})$ is a final coalgebra for the functor $A \tr \_$.    
-\end{proposition}
-\begin{proof}
-  Observe that in a sequoidally decomposable category, the morphism $\wk_{A,A^n}:A \tr A^n: \rightarrow A^{n+1}$ is a section (we may define the corresponding retraction inductively from the decomposition of the tensor).
-Hence if   the limit $A^\infty$ is preserved by the functor $A \otimes \_$, it is preserved by the sequoid $A \tr\_$ --- i.e.
-$A^\infty$ is the limit of the chain $A \tr \Delta = \Delta$.
-
-Thus, for  any  $A \tr\_$-coalgebra $f:B \rightarrow A \tr B$, we may define a unique coalgebra morphism $\(f\):B \rightarrow !A$ as the mediating morphism of the cone $\{f_i:B \rightarrow A^i\ |\ i \in \omega\}$, where  $f_0 = t_B$ and $f_{i+1} = f;(A \tr f_i)$.
 \end{proof}
@@
 
-It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then ${j_\delta^{\delta+1}}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
+It is well known (see \cite{finalseq}, for instance) that if $j_\delta^{\delta+1}$ is an isomorphism for some $\delta$, then $j_\delta^{\delta+1}\inv\from A^{\sequoid\delta}\to A\sequoid A^{\sequoid\delta}$ is the final coalgebra for the functor $A\sequoid\blank$.
 In this case, we say that the sequence \emph{stabilizes at $\delta$}.

### 2017-05-08 round-corner/paper/lipics-v2016-authors/jim3/seq3.tex
A whole bunch of things.

--- 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Acces}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventEditors{}
+\EventNoEds{}
+\EventLongTitle{7th Conference on Algebra and Coalgebra in Computer Science}
+\EventShortTitle{CALCO 2017}
+\EventAcronym{CALCO}
+\EventYear{2017}
+\EventDate{June13 --16, 2017}
+\EventLocation{Ljubljana, Slovenia}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
+\SeriesVolume{}
+\ArticleNo{}
 % Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 It is straightforward to show that:
+% $A^*$ is a \emph{minimal invariant} for $F(A,\_)$ with respect to the inclusion order on $\Rel$ and so:
 \begin{lemma}$(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
@@
 
+%By distributivity of $\oplus$ over  $\otimes$ we have a natural transformation $t_{A,S}: F(A,S) \otimes S' \rightarrow F(A,S \otimes S')$.
+We may use this to encapsulate  state transformers of general form: given $f:A \otimes S \rightarrow B \otimes S$, taking the anamorphism of the $F(B,\_)$-colagebra:
+%$$A^* \otimes S  \stackrel{\alpha_A \otimes S}{\longrightarrow} F(A,A^*) \otimes S \stackrel{t}{\longrightarrow} F(A,A^* \otimes S)$$
+
  Distributivity of $\oplus$ over $\otimes$ implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
 This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
+%i.e.
+given morphisms $f_1:A_1 \otimes S \rightarrow B_1 \otimes S, \ldots , f_n:A_n \otimes S \rightarrow B_n \otimes S$, encapsulating  $\dist;(f_1 \oplus \ldots \oplus f_n);\dist^{-1}$, gives a morphism from $(A_1 \oplus \ldots \oplus A_n)^* \otimes S$ into $(B_1 \oplus \ldots \oplus B_n)^*$.
 For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contensts of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
@@
 Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed.
-(This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{LafontCofCommCom}.
+(This is precisely the situation in SCI, where the typing system allows sharing  across sequential composition, but not between functions and their arguments.) In order to model sharing of state without this constraint (and build a Cartesian closed category), we need to endow our final coalgebra with the structure of a \emph{cofree commutative comonoid}, proposed as the basis of a model of linear logic by Lafont \cite{Laf}.
 The category of sets and relations  does not allow this (the cofree commutative comonoid on an object $A$ in $\Rel$ is given by the set of finite multisets of $A$, which is not a final coalgebra).
 Hence, we turn to the richer structures of game semantics.
+%However,  the richer structure of
+%game semantics does support a coalgebraic cofree commutative comonoid. 
+% As we shall show by example and counterexample, the richer structure the relationship between initial and final coalgebras, and cofree objects is more subtle.
+%  (note, for example, that any final coalgebra in $\Rel$ must be bifree, by its self-duality).
  \subsection{The cofree commutative comonoid as a final colagebra}
 We now outline the remainder of the paper.
-Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.}
+Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.} %Under a simple interpretation, $A\sequoid B$ is the same as the game $A\tensor B$, except that the first move must take place in $A$.
  In this setting, we  can model a state transformer for a program as a morphism $S \to A \sequoid S$ --- i.e., a coalgebra for the functor $A\sequoid\blank$.
@@
 
+  %If $\C$ is an inclusive sequoidal category, we say that $\C$ is \emph{Cartesian} if $\C_s$ has all products and these are preserved by $J$.
+In that case, we say that $\C$ is \emph{decomposable} if the natural transformations
+  %\begin{gather*}
+  %  \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
+   % \dec^0 \from I \to 1
+ % \end{gather*}
+ % are isomorphisms and we say that $\C$ is \emph{distributive} if the natural transformations
+  %\begin{gather*}
+   % \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
+    %\dist_{(A_i\colon i\in I),C} = \langle (\pr_i\sequoid\id_C\suchthat i\in I)\rangle \from \left(\prod_{i\in I} A_i\right) \sequoid C \to \prod_{i\in I}(A_i\sequoid C) \\
+   % \dist_{A,0}\from 1\sequoid A\to 1
+  %\end{gather*}
+ % are isomorphisms.
+%\end{definition}
 \begin{definition}
@@
 
- We say that $\C$ is \emph{decomposable} if $I$ is a terminal object for $\C$ and if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
+ We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
 So if $\C$ has all finite products, 
@@
     \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
-    \dec^0 \from I \to 1 \\
+   % \dec^0 \from I \to 1 \\
     \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
@@
 This is not strictly necessary, and techniques are available to obtain similar results in the non-affine case (see \cite{jimNonAffine}, for example), but it will greatly simplify our presentation.
+%The games model satisfies an analog of monoidal closedness, but we will not give that here (see \cite{laird02}). 
  We see that $\G$ is a prototype example of a distributive, decomposable sequoidal category.
@@
 \[
-  A \sequoid (!A \otimes !A) 
+  A \sequoid (!A \otimes !A) %\stackrel{\langle \id, A \sequoid \sym\rangle}{\cong} 
 \cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)
@@
 It is not necessary for the final $A \sequoid\_$-coalgebra to be bifree for the exponential to be strong monoidal and thus the cofree commutative comonoid.
-An example is provided by  the category $\W$ of win-games and winning strategies, which is \emph{sequoidal closed} (the restriction of the functor  $A \multimap\blank$ to strict strategies is right adjoint to $\blank \sequoid A$, and inclusion sends this adjunction to the usual monoidal closure).
-To show that the  final $A \sequoid\blank$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\comp{f}{\fix_A(f)} = \fix(f)$.
+An example is provided by  the category $\W$ of win-games and winning strategies, which is \emph{sequoidal closed} (the restriction of the functor  $A \multimap\_$ to strict strategies is right adjoint to $\_ \tr A$, and inclusion sends this adjunction to the usual monoidal closure).
+To show that the  final $A \sequoid\_$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\fix_A(f);f = \fix(f)$.
 \begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \sequoid\_$-algebra. Then we may define a fixed point operator on $\C$.  
@@
 \end{proof}
-
-In particular, $\oc A$ is the carrier of the final coalgebra for $A\sequoid\blank$.  But, as we saw before, it is not the carrier for the cofree commutative comonoid over $A$.
 

### 2017-05-30 round-corner/paper/bcss/sequoidal.tex
Updated to final version for publication.

--- 2017-04-11 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
-\documentclass[a4paper,UKenglish]{lipics-v2016}
-%This is a template for producing LIPIcs articles. 
-%See lipics-manual.pdf for further information.
-%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
-%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
-% for section-numbered lemmas etc., use "numberwithinsect"
+\documentclass[a4paper,UKenglish]{article}
+
+\input{../../../common/preamble}
 
 \usepackage{microtype}%if unwanted, comment out or use option "draft"
-
-%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
+\usepackage{hyperref}
+
+\usepackage[margin=0.5in]{geometry}
 
@@
 
-% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
-\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column
-
-%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-\author[1]{William John Gowers}
-\author[2]{James Laird}
-\affil[1]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
-  \texttt{W.J.Gowers@bath.ac.uk}}
-\affil[2]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
-  \texttt{jiml@cs.bath.ac.uk}}
-\authorrunning{W.\,J. Gowers and J. Laird} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
-
-\Copyright{William John Gowers and James Laird}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
-\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator, Exponentials}% mandatory: Please provide 1-5 keywords
-% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Acces}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Additional packages and macros
-\usepackage{IEEEtrantools} % for \IEEEeqnarray
-\usepackage{pbox} % for \pbox
-\usepackage{cmll} % Linear logic symbols!
-\usepackage{wasysym} % For left and rigth moons
-\usepackage{mathtools}
-
-%% Graphics %%
-\usepackage{tikz}
-\usetikzlibrary{cd}
-\usetikzlibrary{patterns}
-\usetikzlibrary{calc}
-\usetikzlibrary{decorations.pathmorphing}
-
-%% Get the sqsubsetneqq character from the mathabx package
-\DeclareFontFamily{U}{mathb}{\hyphenchar\font45}
-\DeclareFontShape{U}{mathb}{m}{n}{
-      <5> <6> <7> <8> <9> <10> gen * mathb
-      <10.95> mathb10 <12> <14.4> <17.28> <20.74> <24.88> mathb12
-      }{}
-\DeclareSymbolFont{mathb}{U}{mathb}{m}{n}
-
-\DeclareMathSymbol{\sqsubsetneq}    {3}{mathb}{"88}
-\DeclareMathSymbol{\varsqsubsetneq} {3}{mathb}{"8A}
-\DeclareMathSymbol{\varsqsubsetneqq}{3}{mathb}{"92}
-\DeclareMathSymbol{\sqsubsetneqq}   {3}{mathb}{"90}
-
-%% Theorems %%
-\theoremstyle{plain}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{exercise}{Exercise}
-\theoremstyle{definition}
-\newtheorem{notation}[theorem]{Notation}
-
-%% Other macros
-\newcommand*\from{\colon}
-\def \inv {^{-1}}
-\DeclareMathOperator{\id}{id}
-\DeclareMathOperator{\pr}{pr}
-\newcommand{\tensor}{\otimes}
-\newcommand{\sequoid}{\oslash}
-\renewcommand{\implies}{\multimap}
-\newcommand{\comp}[2]{#2 ; #1}
-\newcommand{\cprd}{\sqcup}
-\newcommand{\bigcprd}{\bigsqcup}
-\newcommand{\C}{\mathcal C}
-\newcommand{\F}{\mathcal F}
-\newcommand{\G}{\mathcal G}
-\newcommand{\W}{\mathcal W}
-\newcommand{\suchthat}{\;\colon\;}
-\newcommand{\varsuchthat}{\;\mid\;}
-\newcommand{\OP}{\{O,P\}}
-\newcommand{\emptyplay}{\epsilon}
-\newcommand{\prefix}{\sqsubseteq}
-\newcommand{\pprefix}{\sqsubsetneqq}
-\newcommand{\ppprefix}{\sqsubset}
-\DeclareMathOperator{\assoc}{assoc}
-\DeclareMathOperator{\lunit}{lunit}
-\DeclareMathOperator{\runit}{runit}
-\DeclareMathOperator{\sym}{sym}
-\newcommand{\braid}{\sym}
-\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
-\newcommand{\der}{{\mathtt{der}}}
-\newcommand{\mult}{{\mathtt{mult}}}
-\DeclareMathOperator{\wk}{wk}
-\newcommand{\toisom}{{\xrightarrow{\cong}}}
-\newcommand{\passoc}{{\mathtt{passoc}}}
-\newcommand{\pcomm}{{\mathtt{pcomm}}}
-\newcommand{\run}{{\mathtt{r}}}
-\newcommand{\lun}{{\mathtt{l}}}
-\newcommand{\fcoal}[1]{{\leftmoon #1 \rightmoon}}
-\renewcommand{\subset}{\subseteq}
-\let\oldemptyset\emptyset
-\let\emptyset\varnothing
-\newcommand{\s}{\mathfrak{s}}
-\newcommand{\dist}{{\mathtt{dist}}}
-\newcommand{\dec}{{\mathtt{dec}}}
-\renewcommand{\int}{{\mathtt{coh}}}
-\renewcommand{\coh}{\int}
-\DeclareMathOperator{\CCom}{CCom}
-\newcommand{\catname}[1]{{\mathsf{#1}}}
-\newcommand{\Set}{\catname{Set}}
-\newcommand{\Ord}{\catname{Ord}}
-\newcommand\oppcat[1]{#1^{\mathrm{op}}}
-\newcommand{\bN}{{\mathbb{N}}}
 \newcommand{\OK}{{\mathtt{OK}}}
@@
 \renewcommand{\succ}{{\mathtt{succ}}}
-\newcommand{\Var}{{\mathtt{Var}}}
 \renewcommand{\read}{{\mathtt{read}}}
 \newcommand{\wwrite}{{\mathtt{write}}}
-\newcommand{\Rel}{\catname{Rel}}
-\newcommand{\inr}{{\mathsf{inr}}}
-\newcommand{\inl}{{\mathsf{inl}}}
-\newcommand{{\Na}}{\bN}
-\newcommand{{\cell}}{{\mathsf{cell}}}
-\newcommand{\fix}{{\mathsf{fix}}}
-\newcommand{\eq}{{\mathsf{eq}}}
-\newcommand{\co}{{\textrm{\textexclamdown}}}
-
-%%OUR
-
-%% Constant width xrightarrows
-\newlength{\arrow}
-\settowidth{\arrow}{\scriptsize$1000$}
-\newcommand*{\constantwidthxrightarrow}[1]{\xrightarrow{\mathmakebox[\arrow]{#1}}}
-
-%% Landscape pages
-\usepackage{everypage}
-\usepackage{environ}
-\usepackage{pdflscape}
-\newcounter{abspage}
-
-\makeatletter
-\newcommand{\newSFPage}[1]% #1 = \theabspage
-  {\global\expandafter\let\csname SFPage@#1\endcsname\null}
-
-\NewEnviron{SidewaysFigure}{\begin{figure}[p]
-\protected@write\@auxout{\let\theabspage=\relax}% delays expansion until shipout
-  {\string\newSFPage{\theabspage}}%
-\ifdim\textwidth=\textheight
-  \rotatebox{90}{\parbox[c][\textwidth][c]{\linewidth}{\BODY}}%
-\else
-  \rotatebox{90}{\parbox[c][\textwidth][c]{\textheight}{\BODY}}%
-\fi
-\end{figure}}
-
-\AddEverypageHook{% check if sideways figure on this page
-  \ifdim\textwidth=\textheight
-    \stepcounter{abspage}% already in landscape
-  \else
-    \@ifundefined{SFPage@\theabspage}{}{\global\pdfpageattr{/Rotate 0}}%
-    \stepcounter{abspage}%
-    \@ifundefined{SFPage@\theabspage}{}{\global\pdfpageattr{/Rotate 90}}%
-  \fi}
-\makeatother
+
+\title{Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
+
+\author{William John Gowers and James Laird}
 

### 2017-05-30 round-corner/paper/lipics-v2016-authors/sequoidal.tex
Fixed up the section that authors aren't meant to touch.
Updated to final version for publication.

@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: A Coagebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
+\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
 \titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column
@@
 \author[1]{William John Gowers}
-\author[2]{James Laird}
+\author[1]{James Laird}
 \affil[1]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
-  \texttt{W.J.Gowers@bath.ac.uk}}
-\affil[2]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
-  \texttt{jiml@cs.bath.ac.uk}}
+  \texttt{W.J.Gowers@bath.ac.uk} \quad\texttt{jiml@cs.bath.ac.uk}}
 \authorrunning{W.\,J. Gowers and J. Laird} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
@@
 \subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
-\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator, Exponentials}% mandatory: Please provide 1-5 keywords
+\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator}% mandatory: Please provide 1-5 keywords
 % Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Acces}
+\EventEditors{Filippo Bonchi and Barbara K\"onig}
 \EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventLongTitle{7th Conference on Algebra and Coalgebra in Computer
+Science (CALCO 2017)}
+\EventShortTitle{CALCO 2017}
+\EventAcronym{CALCO}
+\EventYear{2017}
+\EventDate{June 12--16, 2017}
+\EventLocation{Ljubljana, Slovenia}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
+\SeriesVolume{72}
+\ArticleNo{13}
 % Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \usepackage{cmll} % Linear logic symbols!
-\usepackage{wasysym} % For left and rigth moons
+\usepackage{wasysym} % For left and right moons
 \usepackage{mathtools}
@@
 \newtheorem{exercise}{Exercise}
+\newtheorem*{warning}{\lightning\ Warning \lightning}
 \theoremstyle{definition}
@@
 \newcommand{\ppprefix}{\sqsubset}
-\DeclareMathOperator{\assoc}{assoc}
-\DeclareMathOperator{\lunit}{lunit}
-\DeclareMathOperator{\runit}{runit}
-\DeclareMathOperator{\sym}{sym}
+\newcommand{\assoc}{{\mathtt{assoc}}}
+\newcommand{\lunit}{{\mathtt{lunit}}}
+\newcommand{\runit}{{\mathtt{runit}}}
+\newcommand{\sym}{{\mathtt{sym}}}
 \newcommand{\braid}{\sym}
-\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
+\newcommand{\blank}{\,\underline{\hspace{1.5ex}}\,}
 \newcommand{\der}{{\mathtt{der}}}
 \newcommand{\mult}{{\mathtt{mult}}}
-\DeclareMathOperator{\wk}{wk}
+\newcommand{\wk}{{\mathtt{wk}}}
 \newcommand{\toisom}{{\xrightarrow{\cong}}}
@@
 \newcommand{\co}{{\textrm{\textexclamdown}}}
+\newcommand{\go}[1]{{\underline{#1}}}
+\newcommand{\com}{{\mathsf{com}}}
+\newcommand{\weak}{{\mathsf{weak}}}
+\newcommand{\cellst}{{\mathsf{cell\_ST}}}
+\newcommand{\cellinit}{{\mathsf{cell\_init}}}
 
@@
 This condition is always satisfied if $\oc A$ is the \emph{bifree algebra} for $A\sequoid\blank$, but in general it is necessary to impose it, as we establish by giving an example of a sequoidally decomposable category of games in which plays will be allowed to have transfinite length.
-In this category, the final coalgebra for the functor $A\sequoid\blank$ is not the cofree commutative comonoid over $A$: we illustrate this by explicitly contrasting the final sequence for the functor $A\sequoid\blank$ with the chain of symmetric tensor powers used in the construction of the cofree commutative comonoid as a limit by  Melli\'es, Tabareau and Tasson.
+In this category, the final coalgebra for the functor $A\sequoid\blank$ is not the cofree commutative comonoid over $A$: we illustrate this by explicitly contrasting the final sequence for the functor $A\sequoid\blank$ with the chain of symmetric tensor powers used in the construction of the cofree commutative comonoid as a limit by  Melli\`es, Tabareau and Tasson.
 
@@
 This is conceptually simple in principle but leads to some quite combinatorial definitions; a more explicit representation of the current state can be very useful for constructing and reasoning about imperative objects.
-In this paper, we use final coalgebras to forge a link between the explicit and implicit representation of state in game semantics.
-We study the conditions under which the \emph{cofree commutative comonoid} in categories of games may be derived from a final coalgebra, relating their underlying structure as models of linear logic to classical coalgebraic techniques for describing state.
-
-\subsection{Defining Higher-order Stateful Objects, Coalgebraically}
+
+\subsection{Defining Higher-order Stateful Objects Coalgebraically}
 Let us first motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon. 
@@
 
-For example, consider the category $\Rel$ of sets and relations, with symmetric monoidal structure given by the cartesian product (with unit $I$, the singleton set $\{*\}$).
-This has finite (bi)products (disjoint unions) so we may define the functor $F(A,S) = (A \otimes S) \oplus I$.
-For any object (set) $A$, let $A^*$ be the set of finite sequences of elements of $A$ (i.e.
-the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$.
+For example, consider the category $\Rel$ of sets and relations, with symmetric monoidal structure given by the Cartesian product (with unit $I$, the singleton set $\{*\}$).
+This has finite (bi)products (disjoint unions), so we may define the functor $F(A,S) = (A \otimes S) \oplus I$.
+For any object (set) $A$, let $A^*$ be the set of finite sequences of elements of $A$, and let $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*))\}\cup  \{(aw,\inl(a,w))\suchthat a \in A,w \in A^*\}$.
 It is straightforward to show that:
-\begin{lemma}$(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
+\begin{lemma}[\cite{Hasuo07generictrace}] $(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
 \end{lemma}
-Since we have a natural transformation  $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $f;\inl_{A,B}:S \rightarrow F(A,S)$, --- i.e.
-the unique $F(A,\_)$-coalgebra morphism from $(S,f;\inl)$ into $(A^*,\alpha_{A})$.
-This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A^*)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ and together with the encapsulated morphism with updated internal state.
-
- Distributivity of $\oplus$ over $\otimes$ implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
-This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
-For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contensts of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
-Thus (with appropriate tagging) it is the relation $\{(i, (\read(i),i))\ |\ i \in \Na\} \cup \{(i,{\mathtt{write}}(j),j)\}$.
-The anamorphism of the coalgebra $\cell;\inl:\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$.
+Since we have a natural transformation $J\from F(A,S) \rightarrow F(A,S\oplus 1)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $\tilde{f}=[f;\inl_{A,S};J, \inr]:S\oplus 1 \rightarrow F(A,S\oplus 1)$, --- i.e.
+the unique $F(A,\_)$-coalgebra morphism from $(S,\tilde{f})$ into $(A^*,\alpha_{A})$.
+This  is  a morphism from $S$ into $A^*$ corresponding to the initial value of the state: by definition, composing it with $\alpha:A^* \rightarrow F(A,A^*)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ together with the encapsulated morphism with updated internal state.
+
+ Distributivity of $\oplus$ over $\otimes$ gives us a morphism $F(A,S) \oplus F(A',S)\to F(A \oplus A',S)$.
+This allows us to construct stateful objects compounded of a series of methods sharing access to a common state.
+For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contents of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
+Thus (with appropriate tagging) it is the relation $\{(i, (\read(i),i))\suchthat i \in \Na\} \cup \{(i,({\mathtt{write}}(j),j))\suchthat i,j\in\Na\}$.
+The anamorphism of the coalgebra $\cell^{\textasciitilde}:\Na\oplus 1 \rightarrow F(\Na \oplus \Na,\Na\oplus 1) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots*)$.
 Composition with this morphism is precisely the interpretation of new variable declaration in the semantics  in $\Rel$ of the prototypical functional-imperative language \emph{Syntactic Control of Interference} (SCI) given in \cite{Mcsci}.
@@
 In fact, this is the \emph{cofree comonoid} on $A$ --- there is a morphism $\eta_A:A^* \rightarrow A = \{(a,a)\ | \ a \in A\}$ such that for any comonoid $(B,\delta_B,\epsilon_B)$, composition with $\eta_A$ defines an equivalence (natural in $B$)  between the morphisms from $B$ into $A$, and the comonoid morphisms from $(B,\delta_B,\epsilon_B)$ into  $(A^*,\delta_A,\epsilon_A)$.
-\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.\footnote{The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
+\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $A$ in $\Rel$.\footnote{The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
 $(A^*,\alpha^{-1})$ is an initial algebra for $F(A,\_)$ ($\alpha$ must be an isomorphism by Lambek's lemma).
@@
 This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell.      
-Its main limitation is that we have not defined a \emph{commutative} comonoid  for any non-empty set $A$ (evidently, $\delta$ is not invariant under postcomposition with the symmetry isomorphism of the tensor).
+Its main limitation is that we have not defined a \emph{commutative} comonoid  for any set $A$ of size at least $2$ (evidently, $\delta$ is not invariant under post-composition with the symmetry isomorphism of the tensor).
 Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed.
@@
 Hence, we turn to the richer structures of game semantics.
- \subsection{The cofree commutative comonoid as a final colagebra}
+ \subsection{The cofree commutative comonoid as a final coalgebra}
 We now outline the remainder of the paper.
-Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games.}
+Our main contribution is an investigation of the circumstances in which the  cofree commutative comonoid on $A$ arises from a final coalgebra for the functor $A\sequoid\blank$, where $\sequoid$ (the sequoid) is a non-commutative operation on games  introduced by one of the authors \cite{laird02}.\footnote{We will focus on a particular category of ``history sensitive'', Abramsky-Jagadeesan style games \cite{abramskyjagadeesangames}, but sequoidal structure is a unifying feature of sequential, history-sensitive games: see \cite{laird02} for a variant of the Hyland-Ong games and \cite{Clairambault08aremark} for Conway games.}
  In this setting, we  can model a state transformer for a program as a morphism $S \to A \sequoid S$ --- i.e., a coalgebra for the functor $A\sequoid\blank$.
@@
 This can be used to show that $\oc\blank$ gives rise to a strong monoidal functor.
-Perhaps more surprisingly, it is sufficient to show that $\oc A$ is the cofree commutative comonoid.
+Perhaps more surprisingly, this is sufficient to show that $\oc A$ is the cofree commutative comonoid.
 
@@
 
-We compare the  coalgebraic construction of the cofree exponential to the explicit characterization of the latter given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} as the limit of a chain of symmetric tensor powers.
+We compare the  coalgebraic construction of the cofree exponential to the explicit characterization of the latter given by Melli\`es, Tabareau and Tasson \cite{MelliesCofCommCom} as the limit of a chain of symmetric tensor powers.
 This chain exists in any decomposable sequoidal category: where its limit exists and is preserved by the tensor (the conditions required in \cite{MelliesCofCommCom}) it must be the final coalgebra for $A \sequoid\blank$.
@@
 We shall present a form of game semantics in the style of \cite{hyland1997games} and \cite{abramskyjagadeesangames}.
-A game $A$ is given by a forest (i.e., a prefix-closed set) $P_A$ of \emph{positions}, which are alternating sequences of $O$-moves and $P$-moves.
-We call a position a \emph{$P$-position} if it ends with a $P$-move and an \emph{$O$-position} if it ends with an $O$-move.
-A \emph{strategy} for a game $A$ is a subforest $\sigma$ of $P_A$ that is closed under $O$-replies to $P$-positions and which satisfies \emph{determinism}: if $sa,sb\in\sigma$, where $s$ is a $P$-position, then $a=b$.
-We will adopt the rule that all positions must start with an $O$-move.
-
-We build connectives on games in the usual way.
+A game $A$ is given by a set $M_A$ of \emph{$P$-moves} and \emph{$O$-moves} and by a non-empty prefix-closed set $P_A\subset M_A^*$ of \emph{positions}, which are alternating sequences of $O$-moves and $P$-moves.
+We shall adopt the rule that all positions must start with an $O$-move.
+We call a position a \emph{$P$-position} if it ends with a $P$-move or is empty and an \emph{$O$-position} if it ends with an $O$-move.
+
+A \emph{strategy} for a game $A$ is a non-empty prefix-closed subset $\sigma$ of $P_A$ that is closed under $O$-replies to $P$-positions and which satisfies \emph{determinism}: if $sa,sb\in\sigma$, where $s$ is an $O$-position, then $a=b$.
+
+We build connectives on games as in \cite{abramskyjagadeesangames}.
+The set of moves for a compound game is given by the disjoint union of the sets of moves for the individual sub-games, and the positions for each game are defined as follows:
 
 \begin{description}
-  \item[Product] If $(A_i\suchthat i\in I$ is a collection of negative games, then we write $\prod_{i\in I}A_i$ for the game in which player $O$, on his first move, may play in any of the games $A_i$.
+  \item[Product] If $(A_i\suchthat i\in I)$ is a collection of games, then we write $\prod_{i\in I}A_i$ for the game in which player $O$, on his first move, may play in any of the games $A_i$.
 From then on, play continues in $A_i$.
 If $A_1,A_2$ are games, we write $A_1\times A_2$ for $\prod_{i=1}^2 A_i$.
-  \item[Tensor Product] If $A,B$ are negative games,the tensor product $A\tensor B$ is played by playing the games $A$ and $B$ in parallel, where player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
+  \item[Tensor Product] If $A,B$ are games,the tensor product $A\tensor B$ is played by playing the games $A$ and $B$ in parallel, where player $O$ may elect to switch games whenever it is his turn and continue play in the game he has switched to.
   \item[Linear implication] The implication $A\implies B$ is played by playing the game $B$ in parallel with the \emph{negation} of $A$ - that is, the game formed by switching the roles of players $P$ and $O$ in $A$.
@@
 
-It is well known (see \cite{abramskyjagadeesangames}, for example) that we may compose strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ to get a morphism $\comp\tau\sigma$ for $A\implies C$ and that this structure gives rise to a monoidal category where objects are games, morphisms from $A$ to $B$ are strategies for $A\implies B$ and the tensor product and linear implication are given by $A\tensor B$ and $A\implies B$.
+It is well known (see \cite{abramskyjagadeesangames}, for example) that we may compose strategies $\sigma$ for $A\implies B$ and $\tau$ for $B\implies C$ to get a morphism $\comp\tau\sigma$ for $A\implies C$ and that this structure gives rise to a monoidal closed category where objects are games, morphisms from $A$ to $B$ are strategies for $A\implies B$ and the tensor product and linear implication are given by $A\tensor B$ and $A\implies B$.
 We call this category $\G$.
@@
 
-We turn now to the non-standard \emph{sequoid} connective $\sequoid$.
-If $A$ and $B$ are negative games, then the sequoid $A\sequoid B$ is similar to the tensor product $A\tensor B$, but with the restriction that player $O$'s first move must take place in the game $A$.
-We observe immediately that we have structural isomorphisms
-\begin{gather*}
-  \dist\from A\tensor B\toisom (A\sequoid B)\times(B\sequoid A)\\
-  \dec\from(A\times B)\sequoid C\toisom (A\sequoid C)\times (B\sequoid C)\\
-  \passoc\from (A\sequoid B)\sequoid C\toisom A\sequoid (B\tensor C)
-\end{gather*}
-
-The sequoid does not give rise to a functor $\G\times\G\to \G$ in the way that the tensor product does: playing strategies $\sigma$ for $A\implies B$ and $\tau$ for $C \implies D$ in parallel does not necessarily give rise to a valid strategy for $(A\sequoid C)\implies (B \sequoid D)$, since player $O$ might end up playing in $C$ before anyone has played in $A$.
-However, if we require that the strategy $\sigma$ is \emph{strict} -- that is, player $P$'s reply to the opening move in $B$ is always a move in $A$ -- then we do get a valid strategy $\sigma\sequoid\tau$ for $(A\sequoid C)\implies (B\sequoid D)$ and, moreover, $\sigma\sequoid\tau$ is strict.
-If we write $\G_s$ for the category of games with \emph{strict} strategies as morphisms, then we see that $\blank\sequoid\blank$ gives us a functor $\G_s\times \G\to\G_s$.
-In fact, the isomorphism $\passoc$ tells us that this functor is a right monoidal category action of $\G$ upon $\G_s$.
+The one non-standard connective we will use is the \emph{sequoid} connective from \cite{laird02}:
+
+\begin{description}
+    \item[Sequoid] If $A$ and $B$ are games, then the positions of $A\sequoid B$ are precisely the positions of $A\tensor B$ that are empty or that start with a move in $A$.
+\end{description}
+
+By inspection, we can verify that we have structural isomorphisms:
+\[
+  \begin{array}{cc}
+    \dist\from A\tensor B\toisom (A\sequoid B)\times(B\sequoid A)
+      & \dist^0 \from I \sequoid C \toisom I \\
+    \dec\from(A\times B)\sequoid C\toisom (A\sequoid C)\times (B\sequoid C)
+      & \run \from A \sequoid I \toisom A \\
+    \passoc\from (A\sequoid B)\sequoid C\toisom A\sequoid (B\tensor C) &
+  \end{array}
+\]
+
+We might expect that the sequoid would give rise to a functor $\G\times\G\to \G$ in the way that the tensor product does, through playing strategies in parallel.
+However, this does not quite work: playing strategies $\sigma$ for $A\implies B$ and $\tau$ for $C \implies D$ in parallel does not necessarily give rise to a valid strategy for $(A\sequoid C)\implies (B \sequoid D)$, since player $P$ might end up playing in $C$ before anyone has played in $A$.
+However, if we require that the strategy $\sigma$ is \emph{strict} --- that is, that player $P$'s reply (if any) to the opening move in $B$ is always a move in $A$ --- then we do get a valid strategy $\sigma\sequoid\tau$ for $(A\sequoid C)\implies (B\sequoid D)$ and, moreover, $\sigma\sequoid\tau$ is strict.
+We shall write $\G_s$ for the category of games with \emph{strict} strategies as morphisms; then $\blank\sequoid\blank$ gives us a functor $\G_s\times \G\to\G_s$.
 
@@
 
-We now formalize this into a category-theoretic definition.
+We now formalize these observations into a category-theoretic definition.
+The purpose of this definition is to formalize precisely what it is about categories of games that makes them suitable for modeling stateful programs, and to give an equational characterization of the combinatorial definitions used in the Abramsky-McCusker model of Idealized Algol \cite{laird02, SamsonGuyIAPassive}.
 
@@
     \item A symmetric monoidal category $\C$ with monoidal product $\tensor$ and tensor unit $I$, associators $\assoc_{A,B,C}\from(A\tensor B)\tensor C\toisom A\tensor(B\tensor C)$, unitors $\runit_A\from A\tensor I\toisom A$ and $\lunit_A\from I\tensor A\toisom A$ and braiding $\sym_{A,B}\from A\tensor B\to B\tensor A$.
-    \item A category $\C_s$
-    \item A right monoidal category action of $\C$ on the category $\C_s$.
+    \item A category $\C_s$.
+    \item A right monoidal category action \cite{Actegory} of $\C$ on the category $\C_s$.
 That is, a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ that gives rise to a monoidal functor from $\C$ into the category of endofunctors on $\C_s$.
-We write $\passoc_{A,B,C}\from (A \sequoid B) \sequoid C \to A \sequoid (B\tensor C)$ for the coherence part of the monoidal functor.
+We write $\passoc_{A,B,C}\from (A \sequoid B) \sequoid C \to A \sequoid (B\tensor C)$ and $\run_A\from A \sequoid I \to A$ for the coherence parts of this monoidal functor.
 
@@
 
-    \item A natural transformation $\wk_{A,B}\from J(A)\tensor B\to J(A\sequoid B)$ satisfying the coherence conditions:
+    \item A natural transformation $\wk_{A,B}\from J(A)\tensor B\to J(A\sequoid B)$ satisfying the coherence conditions\footnote{These coherence conditions say that $(J,\wk)$ is a \emph{lax morphism of right monoidal actions of $\C$} from the sequoidal action $(\C_s, \blank\sequoid\blank)$ to the `right multiplication' action $(\C, \blank\tensor\blank)$.}:
     \begin{equation*}
       \begin{tikzcd}
-        A \tensor I \arrow[r, "\runit_A" yshift=0.3em] \arrow[d, "\wk_{A,I}"']
-          & A \\
-        A \sequoid I \arrow[ur, "J(\run_A)"']
-          &
-      \end{tikzcd}
-      \quad
-      \begin{tikzcd}
-        (A \tensor B) \tensor C \arrow[r, "\wk_{A,B}\tensor\id_C" yshift=0.3em] \arrow[d, "\assoc_{A,B,C}"']
-          & (A \sequoid B) \tensor C \arrow[r, "\wk_{A\sequoid B, C}" yshift=0.3em]
-            & (A \sequoid B) \sequoid C\\
-        A \tensor (B \tensor C) \arrow[r, "\wk_{A,B\tensor C}"']
-          & A \sequoid (B \tensor C) \arrow[ur, "J(\passoc_{A,B,C})"']
+        J(A) \tensor I \arrow[r, "\runit_A" yshift=0.3em] \arrow[d, "\wk_{A,I}"']
+          & J(A) \\
+        J(A \sequoid I) \arrow[ur, "J(\run_A)"']
+          &
+      \end{tikzcd}
+      \,\,\,
+      \begin{tikzcd}
+        (J(A) \tensor B) \tensor C \arrow[r, "\wk_{A,B}\tensor\id_C" yshift=0.3em] \arrow[d, "\assoc_{A,B,C}"']
+          & J(A \sequoid B) \tensor C \arrow[r, "\wk_{A\sequoid B, C}" yshift=0.3em]
+            & J((A \sequoid B) \sequoid C)\\
+        J(A) \tensor (B \tensor C) \arrow[r, "\wk_{A,B\tensor C}"']
+          & J(A \sequoid (B \tensor C)) \arrow[ur, "J(\passoc_{A,B,C})"']
             &
@@
   Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is \emph{inclusive} if $\C_s$ is a full-on-objects subcategoryof $\C$ containing all isomorphisms in $\C$ and the morphisms $\wk_{A,B}$, and $J$ is the inclusion functor.
-
- We say that $\C$ is \emph{decomposable} if for any $A$ and $B$, the tensor product $A \otimes B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \otimes B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \otimes B \rightarrow B \sequoid A$.
-$\C$ is \emph{distributive}  if whenever the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pi_l \sequoid C,\pi_r \sequoid C$.
-So if $\C$ is Cartesian (has all finite products), 
-the natural transformations
+We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
+
+  We say that $\C$ is \emph{decomposable} if $I$ is a terminal object for $\C$ and if for any $A$ and $B$, the tensor product $A \tensor B$ is a Cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$.
+We say that $\C$ is \emph{distributive} if whenever the product $\prod_{i\in I} A_i$ exists, then $\left(\prod_{i\in I}A_i\right)\sequoid B$ is the product of the $A_i\sequoid B$, with projections $\pr_i\sequoid\id_B$, and if it has a terminal object $1$ satisfying $1\sequoid A\cong 1$ for all objects $A$.
+
+Although there are important examples where we do not have products, our examples will all be categories with all products.
+Then we can state the definitions of decomposability and distributivity more succinctly by requiring that the natural transformations
   \begin{gather*}
     \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
+    \dec^0 \from I \to 1 \\
     \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
+    \dist_{(A_i\colon i\in I),B} = \langle \pr_i\sequoid \id_C \suchthat i\in I\rangle \from \left(\prod_{i\in I}A_i\right)\sequoid C \to \prod_{i\in I}(A_i\sequoid C) \\
     \dist_{A,0}\from 1\sequoid A\to 1
@@
 
-\begin{definition}
-  Let $\C=(\C,\C_s,J,\wk)$ be a sequoidal category.
-We say that $\C$ is an \emph{inclusive sequoidal category} if $\C_s$ is a full-on-objects subcategory of $\C$ containing all isomorphisms and finite products of $\C$, and the morphisms $\wk_{A,B}$ and $J$ is the inclusion functor.
-
- We say that $\C$ is \emph{decomposable} if $I$ is a terminal object for $\C$ and if for any $A$ and $B$, the tensor product $A \tensor B$ is a cartesian product of $A \sequoid B$ and $B \sequoid A$, with projections $\wk_{A,B}:A \tensor B \rightarrow A \sequoid B$ and  $\comp{\wk_{A,B}}{\sym_{A,B}}:A \tensor B \rightarrow B \sequoid A$, and if the product $A \times B$ exists, then $(A \times B) \sequoid C$ is the product of $A \sequoid C$ and $B \sequoid C$, with projections $\pr_l \sequoid \id_C,\pr_r \sequoid \id_C$.
-So if $\C$ has all finite products, 
-the natural transformations
-  \begin{gather*}
-    \dec_{A,B} = \langle \wk_{A,B}, \comp{\wk_{A,B}}{\sym_{A,B}}\rangle\from A\tensor B\to (A\sequoid B)\times (B\sequoid A) \\
-    \dec^0 \from I \to 1 \\
-    \dist_{A,B,C} = \langle \pr_1\sequoid \id_C,\pr_2\sequoid\id_C\rangle\from (A\times B)\sequoid C\to (A\sequoid C)\times (B\sequoid C) \\
-    \dist_{A,0}\from 1\sequoid A\to 1
-  \end{gather*}
-  are isomorphisms.
-\end{definition}
-
-We shall also use the fact that our category of games is \emph{affine} - so the natural transformation $\dec^0\from I \to 1$ is an isomorphism.
-This is not strictly necessary, and techniques are available to obtain similar results in the non-affine case (see \cite{jimNonAffine}, for example), but it will greatly simplify our presentation.
- We see that $\G$ is a prototype example of a distributive, decomposable sequoidal category.
+ The category of games $\G$ and categories arising in different traditions of game semantics \cite{Clairambault08aremark,laird02} are the prototype examples of distributive, decomposable sequoidal categories.
+
+ \begin{remark}
+     Churchill, Laird and McCusker give a result in \cite{martinsthesis} that implies that any sequoidal category satisfying these, and other, extra conditions can be used to model a proof calculus for describing games and strategies.
+Nevertheless, they note that examples do exist of sequoidal categories that do not arise as categories of games, such as the category of locally Boolean domains described in \cite{LairdLbd} (see the last paragraph of that paper, and also the citation in \cite{martinsthesis}).
+ \end{remark}
 
@@
 
-There are several ways to add exponentials to the basic category of games.
-We shall use the definition based on countably many copies of the base game (see \cite{hyland1997games}, for example): the exponential $\oc A$ of $A$ is the game in which player $O$ may switch between countably many copies of $A$ -- $A_0, A_1, A_2, \dots$, as long as he starts them in order, starting with $A_0$, then opening $A_1$ and so on.
+There are several ways to add exponentials to the basic category of games, but the definition that fits our purposes is the one based on countably many copies of the base game (see \cite{hyland1997games}, for example): the exponential $\oc A$ of $A$ is the game in which player $O$ may switch between countably many copies of $A$ -- $A_0, A_1, A_2, \dots$, as long as he starts them in order, starting with $A_0$, then opening $A_1$ and so on.
 This condition on the order in which games may be opened is very important, as it allows us to define the exponential morphisms $\oc A \to \oc A \tensor \oc A$ and $\oc A \to \oc \oc A$.
@@
 
-Even more interestingly, we see that we may characterize $\oc A$ as the \emph{final coalgebra} for the functor $A\sequoid\blank$.
-That is, given a coalgebra from $\sequoid\blank$ -- a game $B$ and a morphism $\sigma\from B \to A \sequoid B$ -- we get a unique morphism $\fcoal{\sigma}$ making the following diagram commute:
+Even more interestingly from the point of view of modelling stateful languages, we may characterize $\oc A$ as the \emph{final coalgebra} for the functor $J(A\sequoid\blank)\from \G\to \G$ (henceforth we shall write this functor as $A\sequoid\blank$, eliding the inclusion functor $J$).
+That is, given a coalgebra from $\sequoid\blank$ --- a game $B$ and a morphism $\sigma\from B \to A \sequoid B$ --- we get a unique morphism $\fcoal{\sigma}$ making the following diagram commute:
 \[
@@
 
-We shall use the following standard pieces of theory about final coalgebras:
+We shall use the following standard pieces of coalgebra theory:
 \begin{description}
@@
 If this sequence stabilizes for any $\delta$ (i.e., if the morphism from $F^{\delta+1}(1)\to F^\delta(1)$ is an isomorphism), then $F^\delta(1)$ is the final coalgebra for $F$ \cite{finalseq}.
+In the case $F=A\sequoid\blank$, we shall write $A^{\sequoid\delta}$ for $F^\delta(1)$.
 \end{description}
 
-\subsection{Imperative programs as anamorphisms}
-
-We now show how we can use the characterization of $\oc A$ as a final coalgebra to define a strategy representing a simple storage cell.
-This is the strategy $\cell$ for $\oc(\Var[X])$ that is used in \cite{SamsonGuyIAPassive} to construct the denotation of the $\mathtt{new}$ term from Idealized Algol.
-Using this strategy, it is possible to build the model of Idealized Algol from \cite{SamsonGuyIAPassive} and hence construct a wealth of other stateful objects.
-The benefit of constructing $\cell$ in this way, rather than directly, is that we can now reason about it coalgebraically, rather than by direct combinatorial arguments on the strategy.
-
-Let $\Sigma$ be the game with maximal play $qa$ and let $\OK$ be the obvious strategy on $\Sigma$.
-$\Sigma$ denotes the type $\texttt{com}$ of commands.
-Let $(X,*)$ be a pointed set and write $X$ for the game with maximal plays $qx$ for $x\in X$.
-Recall that in Idealized Algol we represent $\Var[X]$, the type of variables taking values in $X$, by the game $\Sigma^X\times X$, where $\Sigma^X$ is the $X$-fold product of $\Sigma$ with itself.
-Here, $\Sigma^X$ represents the act of writing a value into the storage cell (so playing in $\Sigma_x$ means writing the value $x$), while the copy of $X$ represents reading a value from the storage cell.
-
-We want to construct the strategy $\cell$ for $\oc(\Sigma^X\times X)$ that will remember what value we have written into the cell and will return the value when we request it.
-In the case that we request the value in the cell when nothing has been written to it, we return the default value $*$.
-
-We shall represent the state of the storage cell by the game $X$, and we shall construct a state transformer on $X \implies (\Sigma^X\times X)\sequoid X$ that will allow us to recover the $\cell$ strategy as an anamorphism.
-
-For each $x\in X$, we have a strategy $c_x$ for $I\implies X$ with maximal play $qx$.  Now we construct a morphism $\wwrite(x)$ from $\oc X$ to $\Sigma\sequoid\oc X$ as the composite:
-\[
-  X \xrightarrow{*} 1 \xrightarrow{{(\dec^0)}\inv} I \xrightarrow{\runit_I} I \tensor I \xrightarrow{\OK\tensor c_x} \Sigma \tensor X \xrightarrow{\wk_{\Sigma,X}} \Sigma \sequoid X
-  \]
-This strategy corresponds to filling the cell with the value $x$.
-Consequently, we ignore the previous value from the cell (the copy of $X$ on the left) and we respond in the copy of $X$ on the right with $x$.
-
-We get a strategy:
-\[
-  \wwrite \from \oc X \xrightarrow{\langle \wwrite(x)\suchthat x\in X\rangle} (\Sigma \sequoid \oc X)^X \xrightarrow{\dist_{(\Sigma\colon x\in X),\oc X}\inv} \Sigma^X\sequoid\oc X
-  \]
-
-We also want a strategy $\read$ for $X \implies X \sequoid X$.
-It doesn't appear to be possible to construct this strategy from the sequoidal axioms, but it is easy enough to say what it is: it is the strategy that returns the value of the state while leaving the state unchanged.
-A typical play in $\read$, therefore, might have the following form:
-\[
-  \begin{array}{ccccc}
-    X & \implies & X & \sequoid & X \\
-    && q && \\
-    q &&&& \\
-    x &&&& \\
-    && x && \\
-    &&&& q \\
-    &&&& x
-  \end{array}
-  \]
-Note that the content of the state (the copy of $X$ on the left) is copied into both the output (the first copy of $X$ on the right) and into the new state (the second copy of $X$ on the right).
-
-We put these strategies together to form our state transformer:
-\[
-  \cell'\from \oc X \xrightarrow{\langle\wwrite,\read\rangle} \Sigma^X\sequoid\oc X \;\times\;X\sequoid\oc X \xrightarrow{\dist_{\Sigma^X,X,\oc X}} (\Sigma^X\times X)\sequoid \oc X
-  \]
-When we take the anamorphism $\fcoal{\cell'}$ of this strategy, we get the strategy $\oc X \to \oc (\Sigma^X\times X)$ that, when player $O$ plays in $\Sigma^X$, stores the appropriate element of $X$ into the (invisible) state.
-When player $O$ plays in $X$ on the right, player $P$ responds with the current value held in the state.
-In the case that player $O$ plays in $X$ without having first played in $\Sigma^X$, we return the value of $X$ from the left.
-Therefore, our desired strategy $\cell$ is given by:
-\[
-  \cell = \comp{\fcoal{\cell'}}{c_*}
-  \]
-
-A similar method may be used to construct a simple stack \cite{martinsthesis}.
-
-\section{Constructing cofree commutative comonoids in Cartesian sequoidal categories}
+\subsection{Imperative programs as anamorphisms}\label{Ipaa}
+
+We now illustrate the construction of stateful objects using anamorphisms by constructing the strategy $\cell$ from \cite{SamsonGuyIAPassive} that represents a storage cell.
+If $X$ is a set of values, write $\go{X}$ for the game denoting the corresponding type: that is, $X$ is the game with maximal plays $qx$, where $x$ ranges over the elements of $X$, and $\go{X}$ has canonical strategies $\go{x}$ for $x\in X$, in which player $P$ responds to the opening move $q$ with the move $x$.
+In particular, the game $\go{\{*\}}$ corresponding to a singleton set denotes the void or command type $\com$.
+We shall write $\Sigma = \go{\{*\}}$ for this game, and write $\OK = \go{*}$ for its unique total strategy.
+
+Following \cite{SamsonGuyIAPassive}, we define $\Var[X]$ to be the type $\com^X\times X$; that is, the product of $X$-many copies of the command type with one copy of the type $X$.
+We can think of this with an object that has a method $\wwrite\_x$ for each element $x$, together with a method $\read$.
+The corresponding game is the game
+\[
+    \Var[X]=\Sigma^X \times \go{X}
+  \]
+In order to tell apart the various games, we shall write $\Sigma_x$ for each copy of $\Sigma$, and write the moves of $\Sigma_x$ as $q_x$ and $*_x$.
+Let $d\in X$ be a fixed default value.
+Then it is quite easy to describe what the strategy $\cell$ on $\oc\Var[X]$ should be: it is the strategy that always responds to $q_x$ with $*_x$ (as it is forced to do) and which responds to the move $q$ in $\go X$ with that value $x\in X$ such that $q_x$ has been played most recently (or with $d$ if player $O$ has not yet played in $\Sigma^X$).
+This is more or less how the strategy is defined in \cite{SamsonGuyIAPassive}.
+The problem is that the state (the current most recently written value of $x$) is \emph{implicit}, and it is hard to get a handle on it.
+
+Instead, we try a state-transformer based approach.
+We shall use $\oc \go{X}$ to represent the state of the storage cell (the $\oc$ is there since we will need to refer to the state multiple times).
+We define morphisms $\read\from \oc \go X\to \go X\sequoid \oc \go X$ and $\wwrite\_x\from \oc\go X \to \Sigma\times\oc\go X$ as follows: $\read$ is the canonical morphism $\alpha_{\go X}$, while $\wwrite\_x$ is the following composite, which throws away the previous state and updates it with the value $x$:
+\[
+  \oc X \xrightarrow{\weak} I \xrightarrow{\runit} I \tensor I \xrightarrow{\OK \tensor \oc \go{x}} \Sigma \tensor \oc\go{X} \xrightarrow{\wk} \Sigma\sequoid \oc\go{X}
+  \]
+Taking the product of these morphisms and applying the distributivity of $\times$ over $\sequoid$, we get our state transformer:
+\[
+  \cellst \from \oc \go X \xrightarrow{\langle \wwrite_x\colon x\in X\;,\; \read\rangle} (\Sigma\sequoid\oc \go X)^X \times \go X \sequoid \oc \go X \xrightarrow{\dist\inv} (\Sigma^X \times \go X) \sequoid \oc \go X
+  \]
+By the definition of $\oc\Var[X]$, there is now a unique morphism $\cellinit\from \oc X \to \oc\Var[X]$ making the following diagram commute:
+\[
+  \begin{tikzcd}
+    \oc \go X \arrow[r, "\cellst"] \arrow[d, "\cellinit"']
+      & \Var[X] \sequoid \oc \go X \arrow[d, "\id\sequoid\cellinit"] \\
+    \oc \Var[X] \arrow[r, "\alpha"]
+      & \Var[X] \sequoid \oc \Var[X]
+  \end{tikzcd}
+  \]
+Define a strategy $\sigma\from \oc\go X\to \oc\Var[X]$ combinatorially by saying that $\sigma$ is the strategy that behaves like $\cell$ (as defined above) on $\oc\Var[X]$ but which interrogates its argument in order to establish the default value, rather than using a fixed value.
+By inspection, we can verify that replacing $\cellinit$ with $\sigma$ in the diagram above makes the square commute, and therefore that $\cellinit=\sigma$ by uniqueness.
+It follows that $\cell$ is equal to the following composite:
+\[
+  I=\oc I \xrightarrow{\oc \go{d}} \oc X \xrightarrow{\cellinit} \oc \Var[X]
+  \]
+But now we are able to reason about its state explicitly by using the coalgebraic definition.
+
+\begin{exercise}
+    By modifying the definition of $\wwrite\_x$, show that the same construction may be used to model a stack with $\mathsf{push}$ and $\mathsf{pop}$ methods.
+\end{exercise}
+
+\section{Constructing cofree commutative comonoids in sequoidal categories}
 
@@
 We also observed that $\oc A$ has the structure of a cofree commutative comonoid on $A$.
-In this section, we shall consider various generalizations of this result that hold in sequoidal categories.
-
-We shall first consider the formula  given by Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom}, which does not depend on the presence of cartesian products, but obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
+These two facts are both crucial if we want to use sequoidal categories to model stateful programs.
+In this section, we shall consider conditions under which we may deduce that the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ coincide.
+
+One important result is the formula  given by Melli\`es, Tabareau and Tasson \cite{MelliesCofCommCom}, which does not depend on the presence of Cartesian products but which obtains the cofree commutative comonoid as a limit of \emph{symmetric tensor powers}.
 \begin{definition}If $A$ is an object in a symmetric monoidal category, a $n$-fold symmetric tensor power of $A$ is an  \emph{equalizer} $(A^n,\eq)$ for the group $G$ of symmetry automorphisms on $A^{\otimes n}$.
-A tensor power is preserved by the tensor product if $(B\otimes A^n,\eq \otimes B)$ is an equalizer for the automorphisms $\{B \otimes g\ |\ g \in G\}$.
+A tensor power is preserved by the tensor product if $(B\otimes A^n,\id_B \otimes \eq)$ is an equalizer for the automorphisms $\{\id_B \otimes g\ |\ g \in G\}$.
 \end{definition}
-In any affine category\footnote{This is a special case of the situation considered in  \cite{MelliesCofCommCom}: that $A$ is a ``free pointed object''.} with tensor powers of $A$ we may define a diagram $\Delta(A) = $
-$$I \stackrel{p_0}{\leftarrow} A \stackrel{p_1}{\leftarrow} A^2 \ldots A^i \stackrel{p_i}{\leftarrow} A^{i+1} \ldots$$
+In any affine category\footnote{This is a special case of the situation considered in  \cite{MelliesCofCommCom}: that $A$ is a ``free pointed object''.} with symmetrized tensor powers of $A$ we may define a diagram $\Delta(A) = $
+\[
+  I \xleftarrow{p_0} A \xleftarrow{p_1} A^2 \xleftarrow{p_2}\cdots\xleftarrow{p_{i-1}}A^i\xleftarrow{p_i} \cdots
+  \]
 where   
@@
 
-Melli\'es, Tabareau and Tasson \cite{MelliesCofCommCom} have shown that where the limit $(A^\infty, \{p^\infty_i\from A^\infty \rightarrow A^i\}$ for this diagram exists  and commutes with the tensor,  --- i.e.
+Melli\`es, Tabareau and Tasson \cite{MelliesCofCommCom} have shown that where the limit $(A^\infty, \{p^\infty_i\from A^\infty \rightarrow A^i\})$ for this diagram exists  and commutes with the tensor,  --- i.e.
 for each object $B$, $B \tensor A^\infty$ is the limit of
-$$B \tensor I \stackrel{B \tensor p_0}{\leftarrow} B \tensor A  \stackrel{B \tensor p_1}{\leftarrow} B\tensor  A^2 \ldots $$
+\[
+  B \tensor I \xleftarrow{\id_B\tensor p_0} B\tensor A \xleftarrow{\id_B\tensor p_1} B \tensor A^2 \xleftarrow{\id_B\tensor p_2} \cdots
+  \]
 then a comultiplication $\mu:A^\infty \rightarrow A^\infty \tensor A^\infty$ may be defined making $(A^\infty,\mu,t_{\oc A})$ the cofree commutative comonoid.
@@
 
-In the category of games, the morphisms $\id\sequoid\pr_1$ and $\id\sequoid\pr_2 \from A \sequoid (B\times C)\to (A \sequoid B) \times (A \sequoid C)$ are jointly monomorphic.
+In the category of games, the morphisms $\id\sequoid\pr_1\from A\sequoid(B\times C)\to A\sequoid B$ and $\id\sequoid\pr_2\from A\sequoid(B\times C)\to A\sequoid C$ are jointly monomorphic, and this joint monomorphism is preserved by the tensor product.
 If a distributive sequoidal category satisfies the same property, we say that it is \emph{strong distributive}.
@@
 \begin{proof}
-By sequoidal decomposability, for any $n$, $A^{\tensor (n+1)}$ is the cartesian product $\Pi_{i \le n} (A \sequoid A^{\tensor n})$ with projections 
+By sequoidal decomposability, for any $n\in\mathbb N$, $A^{\tensor (n+1)}$ is the Cartesian product $\prod_{i \le n} (\id_A \sequoid A^{\tensor n})$ with projections 
 $\sym_i;\wk_{A,A^{\tensor n}} $, where  $\sym_i: A^{\tensor (n+1)} \rightarrow A^{\tensor (n+1)}$ is the symmetry isomorphism corresponding to the permutation on $n$ which swaps $1$ and $i$.
 
-  Define  $\wk^n: A^{\tensor n}\rightarrow A^{\sequoid n}$ by $\wk^{n+1} = \wk_{A, A^{\tensor n}}; (A \sequoid \wk^n)$.
-We show (by induction on $n$) that for any $n$, the morphisms $\comp{\wk_n}{\sym^\pi}$ are jointly monomorphic, where $\sym^\pi$ ranges over all of the permutation isomorphisms  on $A^{\tensor n}$.
-
-  The equalizer $\eq_n:A^n \rightarrow A^{\tensor n}$ is defined inductively by $\eq_n=\langle \id\sequoid\eq_{n-1}$, using the identification of $A\sequoid n$ as a product given above.
+  Define  $\wk^n: A^{\tensor n}\rightarrow A^{\sequoid n}$ by $\wk^{n+1} = \wk_{A, A^{\tensor n}}; (\id_A \sequoid \wk^n)$.
+We show (by induction on $n$) that for any $n$, the morphisms $\comp{\wk_n}{\sym^\pi}$ are jointly monomorphic, where $\sym^\pi$ ranges over all of the permutation isomorphisms  on $A^{\tensor n}$, and that this joint monomorphism is preserved by the tensor product.
+
+  We define the equalizer $\eq_n:A^{\sequoid n} \rightarrow A^{\tensor n}$ inductively by setting $\eq_n$ to be the product $\langle \id_A\sequoid\eq_{n-1}, \dots, \id_A\sequoid\eq_{n-1}\rangle$, using the identification of $A^{\sequoid n}$ as a product given above.
 We may show inductively that $\comp{\wk^n}{\comp{\sym^\pi}{\eq_n}}=\id$ for all permutations $\pi\in S_n$.
-  Given any $f:C \rightarrow A^{\tensor n} \tensor B$ such that $\comp{(\theta \tensor B)}{f} = f$ for any permutation symmetry $\theta$, taking $\comp{(\wk^n \tensor B)}{f}:C \rightarrow A^{\sequoid n} \tensor B$ gives the unique morphism such that $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$.
-Indeed, for all permutations $\pi\in S_n$ we have $\comp{\wk^n\tensor\id_B}{\comp{\sym^\pi\tensor\id_B}{\comp{\eq_n\tensor\id_B}{\comp{(\wk^n\tensor\id_B}{f}}}}=\comp{(\wk^n\tensor\id_B)}{f}=\comp{(\wk^n\tensor\id_B)}{\comp{\sym^\pi}{f}}$.
-Hence, $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$ (by decomposability and strong distributivity, the joint monomorphism property is preserved by the tensor product).
+  Given any $f:C \rightarrow A^{\tensor n} \tensor B$ such that $\comp{(\sym^\pi \tensor \id_B)}{f} = f$ for any permutation $\pi$, taking $\comp{(\wk^n \tensor \id_B)}{f}:C \rightarrow A^{\sequoid n} \tensor B$ gives the unique morphism such that $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$.
+Indeed, for all permutations $\pi\in S_n$ we have $\comp{((\comp{\comp{\wk_n}{\sym^\pi}}{\comp{\eq_n}{\wk^n}})\tensor\id_B)}{f} = \comp{(\wk^n\tensor\id_B)}{f}=\comp{((\comp{\wk^n}{\sym^\pi})\tensor\id_B)}{f}$.
+Hence, $\comp{(\eq_n\tensor \id_B)}{\comp{(\wk^n\tensor \id_B)}{f}} = f$.
 For uniqueness, use the fact that $\eq_n$ is a left inverse for $\wk^n$.
 \end{proof}
-Thus, in any sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit for this diagram exists and is preserved by the sequoid, 
---- i.e.
-for any $B$, $B \sequoid A^\infty$ is the limit for $B \sequoid \Delta(A)$ --- then it is preserved by the tensor, and is therefore the cofree commutative comonoid.
-Conversely, we may show that any cofree commutative comonoid which arises as a $\tensor$-preserving limit of symmetric tensor powers is a final coalgebra.
-\begin{proposition}If a sequoidally decomposable category has a MTT-exponential, then $(A^\infty, \comp{\wk_{A\tensor\oc A}}{\comp{\der_A}{\mu_A}})$ is a final coalgebra for the functor $A \sequoid \_$.
-\end{proposition}
-\begin{proof}
-  Observe that in a sequoidally decomposable category, the morphism $\wk_{A,A^n}:A \sequoid A^n: \rightarrow A^{n+1}$ is a section (we may define the corresponding retraction inductively from the decomposition of the tensor).
-Hence if   the limit $A^\infty$ is preserved by the functor $A \tensor \_$, it is preserved by the sequoid $A \sequoid\_$ --- i.e.
-$A^\infty$ is the limit of the chain $A \sequoid \Delta = \Delta$.
-
-  Thus, for  any  $A \sequoid\_$-coalgebra $f\from B \rightarrow A \sequoid B$, we may define a unique coalgebra morphism $\fcoal{f}\from B \rightarrow \oc A$ as the mediating morphism of the cone $\{f_i\from B \rightarrow A^i\ |\ i \in \omega\}$, where  $f_0 = t_B$ and $f_{i+1} = f;(A \sequoid f_i)$.
-\end{proof}
+Thus, in any strong distributive sequoidally decomposable category, the diagram $\Delta(A)$ exists for any $A$. If a limit $A^\infty$ for this diagram exists and is preserved by the tensor 
+--- i.e. for any $B$, $B \tensor A^\infty$ is the limit for $B \tensor \Delta(A)$ --- then it is the cofree commutative comonoid.
+
+Moreover, by distributivity, preservation by the tensor product implies preservation by the sequoid, which tells us that in this case the final sequence for $A\sequoid\blank$ must converge at $\omega$ and that the limit $A^\infty$ must be the carrier for the final coalgebra for $A\sequoid\blank$.
 
@@
 
-The construction from \cite{MelliesCofCommCom} covers a lot of different cases, but there are some situations in which it does not apply.
-One example is that of \emph{win-games}, or games with a winning condition (\cite{abramskyjagadeesangames}, \cite{martinsthesis}).
-Given a game $A$, we write $\overline{P_A}$ to be the limit-closure of $P_A$ -- that is, $P_A$ together with the set of infinite sequences, all of whose finite prefixes are in $P_A$.
+The construction from \cite{MelliesCofCommCom} covers a lot of important cases, but there are some situations in which the right conditions are not satisfied.
+Instead, we shall need the techniques that we shall describe in the following sections.
+One example in which we cannot use the Melli\`es-Tabareau-Tasson formula is that of \emph{win-games}, or games with a winning condition \cite{abramskyjagadeesangames,martinsthesis}.
+Given a game $A$, we write $\overline{P_A}$ to be the limit-closure of $P_A$ --- that is, $P_A$ together with the set of infinite sequences, all of whose finite prefixes are in $P_A$.
 A \emph{win-game} is a game $A$ together with a function $\zeta_A\from \overline{P_A}\to\OP$ such that:
 \begin{itemize}
-  \item $\zeta_A(\emptyplay) = \neg b_A$
+  \item $\zeta_A(\emptyplay) = P$
   \item $\zeta_A(sa) = \lambda_A(a)$
@@
 The reason we bother to define $\zeta_A$ on finite positions at all is so that we can define it easily on the connectives:
-\begin{gather*}
-  \zeta_{A\tensor B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \quad
-  \zeta_{A \implies B}(s) = \zeta_A(s\vert_A) \Rightarrow \zeta_B(s\vert_B) \\
-  \zeta_{\prod_{i\in I}A_i}(s) = \bigwedge_{i\in I}\zeta_{A_i}(s\vert_{A_i}) \quad
-  \zeta_{A\sequoid B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B) \quad
+\[
+  \begin{array}{cccccc}
+    \multicolumn{3}{c}{
+    \zeta_{A\tensor B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B)
+    }
+      & \multicolumn{3}{c}{
+        \zeta_{A \implies B}(s) = \zeta_A(s\vert_A) \Rightarrow \zeta_B(s\vert_B)
+      }\\[8pt]
+    \multicolumn{2}{c}{
+    \zeta_{\prod_{i\in I}A_i}(s) = \bigwedge_{i\in I}\zeta_{A_i}(s\vert_{A_i})
+    }
+      & \multicolumn{2}{c}{
+        \zeta_{A\sequoid B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B)
+      }
+        & \multicolumn{2}{c}{
         \zeta_{\oc A}(s) = \bigwedge_{i\in I}(\zeta_A(s\vert_i))
-\end{gather*}
-
-Here, $\wedge$ and $\Rightarrow$ are the usual propostional connectives on $\{T,F\}$, where we identify $T$ with $P$ and $F$ with $O$.
-
-We define a \emph{winning strategy} on $(A,\zeta_A)$ to be a total strategy $\sigma$ on $A$ such that $\zeta_A(s)=P$ whenever $s$ is an infinite sequence, all of whose finite prefixes are in $\sigma$.
+        }
+  \end{array}
+\]
+
+Here, $\wedge$ and $\Rightarrow$ are the usual propositional connectives on $\{T,F\}$, where we identify $T$ with $P$ and $F$ with $O$.
+The infinite positions $s$ with $\zeta_A(s)=P$ are the \emph{$P$-winning} positions, while the infinite positions $s$ with $\zeta_A(s)=O$ are the \emph{$O$-winning} positions.
+
+We define a \emph{winning strategy} on $(A,\zeta_A)$ to be a total strategy $\sigma$ on $A$ such that every infinite sequence arising as the limit of sequences in $\sigma$ is a $P$-winning position.
 It is known (see \cite{abramskyjagadeesangames}) that the composition of winning strategies is winning and that we get a decomposable, distributive sequoidal category $\W$ with $\oc A$ as the final coalgebra for $A\sequoid\blank$ and the cofree commutative comonoid over $A$ \cite{martinsthesis}.
@@
 Since $\W$ is a decomposable, strong distributive sequoidal category, the symmetrized tensor powers of $A$ are given by the sequoidal powers $A^{\sequoid n}$.
-But now the limit of these objects is not quite the game $\oc A$; instead, it is the game $A^{\sequoid\omega}=\co A$ in which player $O$ may open an arbitrarily large number of copies of $A$, but not infinitely many.
+But now the limit of these objects is not quite the game $\oc A$; instead, it is the game $A^{\sequoid\omega}=\co A$ in which player $O$ may open an arbitrarily large finite number of copies of $A$, but loses if he opens infinitely many.
 In the finite case, there was no way to keep track of infinite positions, so we could not make this distinction, but in the win-games case we can: we set $\zeta_{\co A}(s)=\zeta_{\oc A}(s)$, unless $s$ contains moves in infinitely many games, in which case we set $\zeta_{\co A}(s) = P$.
@@
 This limit is not preserved by the functor $A\sequoid\blank$: in the game $A^{\sequoid(\omega+1)}=A\sequoid\co A$, player $O$ wins if he wins either in $A$ or in $\co A$, so he can win even if he plays in infinitely many games, as long as he wins in the first copy of $A$.
-Similarly, in the game $A^{\sequoid(\omega+n)}$, player $O$ can win as long as he wins in one of the first $n$ copies of $A$.
-Therefore, the limit $A^{\sequoid\omega2} \emph{is}$ the game $\oc A$: the final sequence for $A\sequoid\blank$ stabilizes at $\omega2$.
-
-We see that the exponential in $\W$ is not an MTT-exponential.
+Similarly, in the game $A^{\sequoid(\omega+n)}$, player $O$ wins as long as he wins in one of the first $n$ copies of $A$ or opens finitely many copies.
+Therefore, the limit $A^{\sequoid\omega2}$ \emph{is} the game $\oc A$: the final sequence for $A\sequoid\blank$ in $\W$ stabilizes at $\omega2$ and, consequently, the exponential in $\W$ is not an MTT-exponential.
 
 This example is a special case of our later result on transfinite games.
-For now, we examine a coalgebraic approach that will prove that the final coalgebra $\oc A$ for $A\sequoid \blank$ in the category $\W$ of win-games gives us a cofree commutative comonoid.
+For now, we shall examine a coalgebraic approach that will prove that the final coalgebra $\oc A$ for $A\sequoid \blank$ in the category $\W$ of win-games gives us a cofree commutative comonoid.
 
@@
 
-We will now need to assume that we are in a decomposable, distributive sequoidal category $(\C,\C_s,J,\wk)$ such that $\C_s$ has all products and $J$ preserves them.
-However, we will no longer need the MTT assumption that the exponential should be constructed as a limit of sequoidal powers.
-The main cost is that we will need to make a further assumption: that a certain naturally defined morphism $\oc A \tensor \oc B\to \oc (A\times B)$ is an isomorphism.
+We shall now need to assume that we are in a decomposable, distributive sequoidal category $(\C,\C_s,J,\wk)$ such that $\C_s$ has all products and $J$ preserves them.
+However, we shall no longer need the MTT assumption that the exponential should be constructed as a limit of sequoidal powers.
+The main cost is that we shall need to make a further assumption: that a certain naturally defined morphism $\oc A \tensor \oc B\to \oc (A\times B)$ is an isomorphism.
 This assumption, broadly corresponding to the demand that the functor $\oc A$ be strong monoidal from the Cartesian category $(\C,\times,1)$ to the monoidal category $(\C,\tensor,I)$, will allow us to construct the comultiplication directly from the Cartesian structure and the definition of $\oc A$ as a final coalgebra.
@@
 Let $A,B$ be objects of $C$.
-Then we have a composite $\kappa_{A,B}\from\oc A \tensor\oc B\to(A\times B)\sequoid(\oc A\tensor \oc B)$:
+Then we have a composite $\kappa_{A,B}$:
   \settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
   \begin{IEEEeqnarray*}{RCL}
-    \kappa_{A,B} = \oc A \tensor \oc B & \constantwidthxrightarrow{\langle\wk_{\oc A,\oc B},\;\comp{\sym_{\oc A,\oc B}}{\wk_{\oc A,\oc B}}} & (\oc A \sequoid \oc B) \times (\oc B \sequoid \oc A) \\
+    \kappa_{A,B} = \oc A \tensor \oc B & \constantwidthxrightarrow{\dec_{A,B}} & (\oc A \sequoid \oc B) \times (\oc B \sequoid \oc A) \\
     \cdots & \constantwidthxrightarrow{(\alpha_A\sequoid\id_{\oc B}) \times (\alpha_B\sequoid\id_{\oc A})} & ((A \sequoid \oc A) \sequoid \oc B) \times ((B \sequoid \oc B) \sequoid \oc A) \\
-    \cdots & \constantwidthxrightarrow{\passoc_{A,\oc A,\oc B}\inv\times\passoc_{B,\oc B,\oc A}\inv} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc B \tensor \oc A) \\
+    \cdots & \constantwidthxrightarrow{\passoc_{A,\oc A,\oc B}\inv\times\passoc_{B,\oc B,\oc A}\inv} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc B \tensor \oc A)) \\
       \cdots & \constantwidthxrightarrow{\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})} & (A \sequoid (\oc A \tensor \oc B)) \times (B \sequoid (\oc A \tensor \oc B))
   \end{IEEEeqnarray*}
-  We get a morphism $\comp{\dist\inv}{\kappa_A}\from \oc A \tensor \oc B \to (A\times B) \sequoid(\oc A \tensor \oc B)$ and we write $\int_{A,B}=\fcoal{\comp{\dist\inv}{\kappa_A}}\from \oc A \tensor \oc B \to \oc (A\times B)$.
+  We get a morphism $\comp{\dist\inv}{\kappa_{A,B}}\from \oc A \tensor \oc B \to (A\times B) \sequoid(\oc A \tensor \oc B)$ and we write $\int_{A,B}=\fcoal{\comp{\dist\inv}{\kappa_{A,B}}}\from \oc A \tensor \oc B \to \oc (A\times B)$.
 \end{definition}
@@
 \begin{proposition}
-  In the category of games, the morphism $\int_{A,B}$ is an isomorphism for all negative games $A,B$.
+  In the category of games, the morphism $\int_{A,B}$ is an isomorphism for all games $A,B$.
 \end{proposition}
 \begin{proof}
-  Observe that the morphism $\int_{A,B}$ is the copycat strategy on $\oc A\tensor\oc B\implies \oc (A\times B)$ that starts a copy of $A$ on the left whenever a copy of $A$ is started on the right and starts a copy of $B$ on the left whenever a copy of $B$ is started on the right (indeed, the morphisms in the diagram above are all copycat morphisms, so the copycat strategy we have just described must make that diagram commute.
+  Observe that the morphism $\int_{A,B}$ is the copycat strategy on $\oc A\tensor\oc B\implies \oc (A\times B)$ that starts a copy of $A$ on the left whenever a copy of $A$ is started on the right and starts a copy of $B$ on the left whenever a copy of $B$ is started on the right (indeed, the morphisms in the diagram above are all copycat morphisms, so the copycat strategy we have just described must make that diagram commute).
 Since there are infinitely many copies of both $A$ and $B$ available in $\oc (A\times B)$, and since a new copy of $A$ or $B$ may be started at any time, we may define an inverse copycat strategy on $\oc(A\times B)\implies \oc A\tensor\oc B$.
@@
 Suppose further that the morphism $\int_{A,B}$ as defined above is an isomorphism for all objects $A,B$.
-$A\mapsto\oc A$ gives rise to a strong symmetric monoidal functor from the monoidal category $(\C, \times, 1)$ to the monoidal category $(\C, \tensor, I)$.
+Then $A\mapsto\oc A$ gives rise to a strong symmetric monoidal functor from the monoidal category $(\C, \times, 1)$ to the monoidal category $(\C, \tensor, I)$.
 \end{theorem}
@@
   $f\mapsto\oc f$ respects composition, so $\oc$ is a functor.
-Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
+Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$ (this composite is an isomorphism, so $\epsilon$ is as well).
 \end{proposition}
@@
 \subsection{The Sequoidal Exponential as a Bifree Algebra}
-Observe that in our category of games, $(!A,\alpha)$ is in fact a \emph{bifree algebra} for $A\sequoid\blank$ --- the isomorphism $\alpha^{-1}: A \sequoid !A \rightarrow !A$ is an initial algebra for  $A \sequoid \blank$.
-We may show that in such cases, the condition that $!$ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $\oc A$ with the structure of a comonoid by defining:
-$\mu:!A \rightarrow !A  \otimes !A$
+Observe that in our category of games, $(\oc A,\alpha)$ is in fact a \emph{bifree algebra} for $A\sequoid\blank$ --- the isomorphism $\alpha^{-1}: A \sequoid \oc A \rightarrow \oc A$ is an initial algebra for  $A \sequoid \blank$.
+We may show that in such cases, the condition that $\oc $ is strong monoidal --- and thus the cofree exponential ---  always holds\footnote{Without requiring our sequoidally decomposable category to have finite products  we may equip each object $\oc A$ with the structure of a comonoid by defining:
+$\mu:\oc A \rightarrow \oc A  \otimes \oc A$
  to be the catamorphism of the $A \sequoid \blank$ algebra:
 \[
-  A \sequoid (!A \otimes !A) 
-\cong A \sequoid (!A \otimes !A) \times  A \sequoid (!A \otimes !A) \cong (A \sequoid !A) \sequoid !A \times  (A \sequoid !A) \sequoid !A \cong (!A \sequoid !A) \cong (!A \sequoid !A) \cong (!A \otimes !A)
+  A \sequoid (\oc A \otimes \oc A) 
+\to A \sequoid (\oc A \otimes \oc A) \times  A \sequoid (\oc A \otimes \oc A) \cong (A \sequoid \oc A) \sequoid \oc A \times  (A \sequoid \oc A) \sequoid \oc A \cong (\oc A \sequoid \oc A) \times (\oc A \sequoid \oc A) \cong (\oc A \otimes \oc A)
 \]
 This satisfies the further requirements of a \emph{linear category} in the sense of \cite{Bierman}, although it does not appear to be possible to show that it is the cofree commutative comonoid.} :
-we may define an inverse to $\int:!A \otimes !A \rightarrow ! (A \times B)$  as the \emph{catamorphism} of the  $A \sequoid\blank$-algebra:
-$$(A \times B) \sequoid !A \otimes !B \cong (A \sequoid (!A \otimes !B)) \times  (B \sequoid (!A \otimes !B)) \cong (!A \sequoid !B) \times (!B \sequoid !A)$$
+we may define an inverse to $\int:\oc A \otimes \oc B \rightarrow \oc  (A \times B)$  as the \emph{catamorphism} of the  $A \sequoid\blank$-algebra:
+\[
+  (\comp\dist{\kappa_{A,B}})\inv\from (A\times B) \sequoid (\oc A \tensor \oc B) \to \oc A \tensor \oc B
+  \]
 
@@
 An example is provided by  the category $\W$ of win-games and winning strategies, which is \emph{sequoidal closed} (the restriction of the functor  $A \multimap\blank$ to strict strategies is right adjoint to $\blank \sequoid A$, and inclusion sends this adjunction to the usual monoidal closure).
-To show that the  final $A \sequoid\blank$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\comp{f}{\fix_A(f)} = \fix(f)$.
-\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(!A,\alpha)$ is a bifree $A \sequoid\_$-algebra. Then we may define a fixed point operator on $\C$.  
+To show that the  final $A \sequoid\blank$-coalgebra in this category is not bifree, it suffices to observe that from such an algebra, we may derive a  \emph{fixed point} operator $\fix_A:\C(A,A) \rightarrow \C(I,A)$ for each $A$, such that $\comp{f}{\fix_A(f)} = \fix_A(f)$.
+\begin{proposition}Suppose $\C$ is sequoidal closed and decomposable, and $(\oc A,\alpha)$ is a bifree $A \sequoid\_$-algebra. Then we may define a fixed point operator on $A$.  
 \end{proposition}    
-\begin{proof}For any $A$, let  $\Phi_A:!(A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \sequoid\blank \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \sequoid A \rightarrow A$, which is a  $(A \multimap A) \sequoid \blank$-algebra.
-For any morphism $f:A \rightarrow A$ we may define $\fix_A(f) = \Lambda(f)^\dag;\Phi_A$, where $\Lambda(f):I \rightarrow (A \multimap A)$ is the ``name'' of $f$.
+\begin{proof}For any $A$, let  $\Phi_A:\oc (A \multimap A) \rightarrow A$ be the catamorphism of the counit to the adjunction $A \sequoid\blank \dashv A \multimap$,  $\epsilon_{A,A}: (A \multimap A) \sequoid A \rightarrow A$, which is a  $(A \multimap A) \sequoid \blank$-algebra.
+For any morphism $f:A \rightarrow A$ we may define $\fix_A(f) = \oc\Lambda(f);\Phi_A$, where $\Lambda(f):I \rightarrow (A \multimap A)$ is the ``name'' of $f$.
 \end{proof}
 As one would expect, it is not possible to define a fixed point operator on the category of games and winning strategies ---  for example, if $\bot$ is the game with a single move then the hom-set $\C(I,\bot)$ is empty and hence there can be no morphism $\fix_\bot(\id_\bot)$.
-So the final  $A \sequoid \_$-coalgebra is not bifree in this case.
+So the final  $A \sequoid \blank$-coalgebra is not bifree in this case.
 
@@
 
+\begin{warning}
+    Although we shall refer to the final coalgebra for $A\sequoid\blank$ as $\oc A$ to avoid introducing new notation, this object will not be the carrier for a linear exponential comonad (i.e., a model of the exponential from Linear Logic) in the category.
+\end{warning}
+
 Our sequoidal category will be closely modelled upon the category of games we have just considered: the objects will be games, with the modification that sequences of moves may now have transfinite length.
 This is a natural construction, occurring in the study of determinacy by Mycielski \cite{mycielskiChoice}, Blass \cite{blassChoice} and Weiss \cite{longgamesbook}.
-Transfinite games were used by Berardi and de'Liguoro to give a charactarization of total functionsals \cite{BerardiTransfiniteGames}, and they appear to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
+Transfinite games were used by Berardi and de'Liguoro to give a characterization of total functionals \cite{BerardiTransfiniteGames}, and they appear to the authors to be present in the semantic context in the work of Roscoe \cite{RoscoeCspInfinite}, Levy \cite{LevyGsInfinite} and Laird \cite{LairdOrdinalGames}.
 
@@
   A (completely negative) \emph{game} or a \emph{game over $\alpha$} or an \emph{$\alpha$-game} is given by a forest (i.e., a prefix-closed set) $P_A$ of alternating transfinite sequences of $O$-moves and $P$-moves of length less than $\alpha$ and a function $\zeta_A\from P_A\to\OP$ that designates each position as an $O$-position or a $P$-position.
-We require that $sa$ is a $P$-position if $a$ is a $P$-move and and $O$-position if $a$ is an $O$-move, so $\zeta_A$ only gives us information about plays of limiting length.
+We require that $sa$ is a $P$-position if $a$ is a $P$-move and an $O$-position if $a$ is an $O$-move, so $\zeta_A$ only gives us information about plays of limiting length.
 
@@
 \begin{definition}
-  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty subforest (prefix-closed subset) of $P_A$ that satisfies closure under $O$-replies and the determinism condition, just as for finite strategies.
+  A \emph{strategy} for an $\alpha$-game $A$ is a non-empty prefix-closed subset of $P_A$ that satisfies closure under $O$-replies and the determinism condition, just as for finite strategies.  
 \end{definition}
@@
 
-We now want to show that $\G(\alpha)$ has final coalgebras for the functor $A\sequoid\blank$, given by the transfinite game $\oc A$, which is defined as follows:
+We now want to show that $\G(\alpha)$ has a final coalgebra for each functor $A\sequoid\blank$, given by the transfinite game $\oc A$, which is defined as follows:
 \begin{itemize}
@@
 \end{itemize}
-We define $\oc P_A$ to be the set of all sequences $s\in M_{\oc A}^{*<\alpha}$ such that $s\vert_n\in P_A$ for all $n$.  Then we define $\zeta_{\oc A}\from\oc P_A\to\OP$ by
+We define $\oc P_A$ to be the set of all sequences $s\in M_{\oc A}^{*<\alpha}$ such that $s\vert_n\in P_A$ for all $n$ and such that every move in $A_{n+1}$ occurs later than some move in $A_n$.
+Then we define $\zeta_{\oc A}\from\oc P_A\to\OP$ by
 \[
@@
 In other words, $\zeta_{\oc A}(s)=P$ if and only if $\zeta_A(s\vert_n)=P$ for all $n$.
+We define $P_{\oc A}$ to be the set of all sequences in $\oc P_A$ that are alternating with respect to $\zeta_{\oc A}$.
 
@@
 
-In particular, $\oc A$ is the carrier of the final coalgebra for $A\sequoid\blank$.  But, as we saw before, it is not the carrier for the cofree commutative comonoid over $A$.
+In particular, $\oc A$ is the carrier of the final coalgebra for $A\sequoid\blank$.  But, as we saw before, it is not the carrier for the cofree commutative comonoid over $A$; indeed, more is true:
+
+\begin{proposition}
+  $\oc A$ does not carry the structure of a linear exponential comonad.
+\end{proposition}
+\begin{proof}
+  Indeed, if it did, then \cite{SchalkWhatIs} we would have an isomorphism
+  \[
+    \oc (A\times B) \cong \oc A \tensor \oc B
+    \]
+  But this isomorphism does not hold for suitably long transfinite games.
+For example, if $A$ and $B$ are bounded games (i.e., games such that the lengths of plays are bounded by some finite number $n$) containing at least one play of length $2$ then $\oc A\tensor \oc B$ contains plays of length $\omega2$ (play through all the copies of $A$, then through all the copies of $B$), while the lengths of plays in $\oc (A\times B)$ are bounded by $\omega$, since $A\times B$ is a bounded game.
+\end{proof}
 
@@
 
-%% .. or use the thebibliography environment explicitely
+%% .. or use the thebibliography environment explicitly
 
@@
       (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[r, "\dist"']
-        & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)
+        & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A))
     \end{tikzcd}
@@
   \quad
-  \dec^0\from I\to 1
+  \epsilon\from I \to \oc 1
   \]

### 2017-05-31 round-corner/presentation/presentation.tex
Moved some things around etc.

\documentclass{beamer}

\let\BEAMER=1
\let\NOTARTICLE=1
\let\FEWFONTS=1

\input{../../common/preamble}

\renewcommand{\read}{{\mathsf{read}}}
\newcommand{\wwrite}{{\mathsf{write}}}
\newcommand{\Read}{{\mathsf{Read}}}
\newcommand{\Write}{{\mathsf{Write}}}
\newcommand{\tick}{\checkmark}
\renewcommand{\int}{\texttt{int}}

\title{A Coalgebraic Approach to Stateful Objects in Game Semantics}

\author{John Gowers and James Laird}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Semantics of Stateful Programs}
  In a \emph{purely functional} language, we can represent a function of type $S\to T$ as a function between sets:
  \[
    \deno{f}\from\deno{S}\to\deno{T}
    \]
  \pause
  In a stateful language, we have to take the program \emph{state} into consideration.
  \pause
  We represent a stateful function as a function:
  \[
    \deno{f}\from W \times \deno{S}\to W \times \deno{T}
    \]
  where $W$ denotes the program state.
\end{frame}

\begin{frame}
  \frametitle{Game Semantics}
  In Game Semantics, we denote types by games and we denote elements of types by strategies for those games.  
  \pause
  We start with very simple games and build up more complicated ones using \emph{connectives}
  \pause
  For example, if $X$ is a set of values, we have a game $\Read[X]$ and a game $\Write[X]$:
  \[
    \begin{array}{cc}
      \Read[X]:\ \wn x\ (x\in X)
        & \Write[X]:\  x\tick\ (x\in X)
    \end{array}
    \]
  \pause
  Given games $A,B$, we can form the \emph{compound games} $A\times B$, $A\tensor B$, $A\implies B$, $A\sequoid B$,... in which the games $A$ and $B$ are played in parallel.
\end{frame}

\begin{frame}
  \frametitle{Function types and Exponentials}
  Games of the form $A\implies B$ represent functions from $A$ to $B$.
  \pause
  \[
    \begin{array}{ccc}
      \Read[\bN] & \implies & \Read[\bN] \\
      \pause
      & & \wn \\
      \pause
      \wn & & \\
      \pause
      7 & & \\
      \pause
      & & 49
    \end{array}
    \]
  \pause
  But what if the argument is a function?
  \pause
  For example, take the lambda term
  \[
    \lambda f^{\nat\to\nat}.f(f\ 3)\from (\nat\to\nat)\to\nat
    \]
\end{frame}

\begin{frame}
  \frametitle{Function types and Exponentials}
  \[
    \lambda f^{\nat\to\nat}.f(f\ 3)\from (\nat\to\nat)\to\nat
    \]
  \pause
  \[
    \begin{array}{ccccc}
      (\Read[\bN] & \implies & \Read[\bN]) & \implies & \Read[\bN] \\
      \pause
      & & & & \wn \\
      \pause
      & & \wn & & \\
      \pause
      \wn & & & & \\
      \pause
      3 & & & & \\
      \pause
      & & 9 & & \\
    \end{array}
    \]
  \pause
  ...but now we are stuck.
  \pause
  We introduce the \emph{exponential} $\oc A \approx A \sequoid (A \sequoid (A \sequoid \cdots$
  \pause
  Now we represent the type of functions from $A$ to $B$ using the game
  \[
    \oc A \implies B
    \]
\end{frame}

\begin{frame}[fragile]
  \frametitle{A storage cell}
  Consider the following (Java) class:
  \begin{verbatim}
  public class StorageCell implements AbstractCell {
    private int state;
    public int read() { return state; }
    public void write(int x) { state = x; }
  }
  \end{verbatim}
  \pause
  We represent the \emph{public interface} of the class with the game
  \[
    \oc(\Write[\int] \times \Read[\int])
    \]
  \pause
  The \emph{implementation} now corresponds to a \emph{strategy} for that game:
  \[
    7\ \tick\ \wn\ 7\ \wn\ 7\ 8\ \tick\ 9\ \tick\ \wn\ 9\dots
    \]
\end{frame}

\begin{frame}[fragile]
  \frametitle{A state-transformer based approach}
  \pause
  The strategy is easy to define, but it is hard to study because the state is \emph{implicit} or \emph{encapsulated}.  
  \pause
  We want to return to the classical state-transformer approach
  \pause
  \tikzset{dotsstyle/.style={draw=none}}
  \[
    \begin{tikzpicture}
      \matrix[matrix of nodes, column sep=36pt, inner xsep=1ex, name=m, nodes={draw=black}] {
        & in & in & in & & \\
        $A_0$ & $A_1$ & $A_2$ & $A_3$ & |[dotsstyle]| $\cdots$ \\
        & out & out & out & & \\};
      \path[commutative diagrams/.cd, every arrow, every label, labels={font size=tiny}]
        (m-2-1) edge node {init} (m-2-2)
        (m-2-2) edge node {state} (m-2-3)
        (m-2-3) edge node {state} (m-2-4)
        (m-2-4) edge node {state} (m-2-5);
    \end{tikzpicture}
    \]
  \pause
  We may construct a state transformer (strategy) $\oc X \implies (\Read[X] \times \Write[X]) \sequoid \oc X$ corresponding to a single invocation of the Java class on the previous slide.
  \pause

  Using some category-theoretic magic ($\oc A$ is the \emph{final coalgebra} for the endofunctor $A\sequoid\blank$), we can automatically construct our strategy for $\oc X \implies \oc (\Read[X]\times \Write[X])$ from this state transformer.
\end{frame}

\end{document}

### 2017-06-05 round-corner/presentation2/presentation.tex
Started presentation.

\documentclass{beamer}

\let\NOTARTICLE=1
\let\BEAMER=1
\let\FEWFONTS=1

\newcommand{\tick}{\checkmark}

\newenvironment{theindex}
 {\let\item\par
  %definitions for subitem etc
  }{}
\newcommand\indexspace{}

\input{../../common/preamble}

\newtheorem{proposition}{Proposition}

%%% END Article customizations

\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics}
\subtitle{University of Bath, 2017}

\author{John Gowers and James Laird}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Semantics of Stateful Programs}
  In traditional domain-theoretic semantics, a function without side effects is represented as a map
  \[
    X \to Y
    \]
  \pause
  while a function with side effects is represented as a map
  \[
    S \times X \to S \times Y
    \]
  \pause
  or equivalently an algebra for the monad
  \[
    [S, S \times \blank]
    \]
  \pause
  We can then represent programs with a fixed store $S$ as morphisms in the Kleisli category for this monad.
  \pause
  This is an example of \emph{explicit state}.
\end{frame}

\begin{frame}
  \frametitle{Game Semantics and Implicit State}
  By contrast, the state in Game Semantics is \emph{implicit}.
  \pause

  Consider, for example, the game where player $O$, at any turn, can either say $b$ (button press) or $c$ (count).

  Player $P$ must reply to $b$ with the move $\tick$ and can reply to $c$ by saying any natural number.
  \pause

  There is a strategy for this game corresponding to a simple counter.
  \pause

  An example play in that strategy is:
  \[
    c\ 0\ b\ \tick\ b\ \tick\ b\ \tick\ c\ 3\ c\ 3\ b\ \tick\cdots
    \]
  \pause
  This play has implicit state:
  \[
    \begin{array}{r|cccccccccccccc}
      \text{Moves} & c & 0 & b & \tick & b & \tick & b & \tick & c & 3 & c & 3 & b & \tick \\
      \text{State} & 0 & 0 & 1 & 1 & 2 & 2 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3
    \end{array}
    \]
\end{frame}

\begin{frame}
  \frametitle{Case Study: The Abramsky-McCusker model of Idealized Algol}
  Abramsky and McCusker's model of Idealized Algol (1998) uses a stateful strategy $\cell$, representing the behaviour of a storage cell.
  \pause

  They use a combinatorial definition to define $\cell$ directly.  
  \pause

  Because state is implicit, it is not always easy to keep track of it.
  \pause

  Defining strategies combinatorially doesn't tell us what properties of the category of games make it suitable for modelling stateful programs.  
  \pause

  We want to find a way to \emph{encapsulate} an explicit state in a systematic category-theoretic way.
\end{frame}

\begin{frame}[fragile]
  \frametitle{Encapsulation of State}
  We can think of a state transformer as a box
  \[
    \begin{tikzpicture}
      \matrix[matrix of nodes, column sep=64pt, inner xsep=1ex, name=m, nodes={draw=black}] {
        & in & \\
        $S$ & $A$ & $S$ \\
        & out & \\};
      \path[commutative diagrams/.cd, every arrow, every label, labels={font size=tiny}]
        (m-2-1) edge node {old state} (m-2-2)
        (m-2-2) edge node {new state} (m-2-3);
    \end{tikzpicture}
    \]
  \pause
  Then \emph{encapsulation} means plugging an unbounded number of boxes together:
  \tikzset{dotsstyle/.style={draw=none}}
  \[
    \begin{tikzpicture}
      \matrix[matrix of nodes, column sep=36pt, inner xsep=1ex, name=m, nodes={draw=black}] {
        & in & in & in & & \\
        $S$ & $A_1$ & $A_2$ & $A_3$ & |[dotsstyle]| $\cdots$ \\
        & out & out & out & & \\};
      \path[commutative diagrams/.cd, every arrow, every label, labels={font size=tiny}]
        (m-2-1) edge node {init} (m-2-2)
        (m-2-2) edge node {state} (m-2-3)
        (m-2-3) edge node {state} (m-2-4)
        (m-2-4) edge node {state} (m-2-5);
    \end{tikzpicture}
    \]
\end{frame}

\begin{frame}
  \frametitle{Final coalgebras}
  A well-studied technique in semantics is to use a \emph{final coalgebra} in order to encapsulate state.  
  \pause

  If we have a functor corresponding to `adding  a box':
  \tikzset{bigbox/.style={minimum width=3cm, minimum height=2cm}}
  \[
    \begin{tikzpicture}
      \matrix[matrix of nodes, column sep=64pt, inner xsep=1ex, name=m, nodes={draw=black}] {
        & in & \\
        $S$ & $A$ & $S$ \\
        & out & \\};
      \path[commutative diagrams/.cd, every arrow, every label, labels={font size=tiny}]
        (m-2-1) edge node {old state} (m-2-2)
        (m-2-2) edge node {new state} (m-2-3);
    \end{tikzpicture}
    \]

\end{document}

### 2017-10-07 game_language/gl.tex
A language for writing games.

\documentclass{article}

\input{../common/preamble}

\usepackage[T1]{fontenc}

\newcommand{\game}{\textsc{game}}
\newcommand{\play}{\textsc{play}}
\newcommand{\move}{\textsc{move}}
\newcommand{\team}{\textsc{team}}
\newcommand{\strategy}{\textsc{strategy}}

\begin{document}

\section{A language of games}
\label{sec:game-language}

\subsection{Terms}

In this section, we describe a general framework of the language of games.  
The underlying language we shall normally start with is the simply typed lambda calculus.  
To this, we fix a finite set $\A$ of countable sets and for each $A\in\A$ we add a type $\ul{A}$ to the language.  The types of the form $\ul{A}$ are called the \emph{ground types}.
We then add a set of constants to the language.  These take one of two forms:
\begin{description}
  \item[Value constants] A \emph{value constant} takes the form $\ul{a}\from\ul{A}$, where $A\in\A$ and $a\in A$.  For our purposes, we shall assume that our language includes a value constant for every element of every set $A\in\A$.
  \item[Function constants] Given $A\in\A$ and a type $T$, a \emph{function constant} takes the form $\ul{\phi}$, where $\phi$ is some function sending elements of $A$ to terms of type $T$.
\end{description}

\begin{example}
  In the usual presentation of PCF, we have a type $\nat=\ul{\bN}$.  Then numerals $\n$ are the value constants $\ul{n}$, while the terms $\suc\from\nat\to\nat$ and $\IfO_T\from\nat\to T\to T\to T$ are function constants corresponding to the functions
  \begin{gather*}
    \phi_\suc \from n \mapsto \ul{n + 1} \\
    \phi_{\IfO} \from n \mapsto \begin{cases}
      \lambda x . \lambda y . x & \text{if $n=0$} \\
      \lambda x . \lambda y . y & \text{otherwise}
    \end{cases}
  \end{gather*}
\end{example}

\begin{remark}
  Function constants may refer to other function constants.  To avoid circular definitions, define a directed graph on the set of function constants by drawing an edge from $\ul{\phi}$ to $\ul{\psi}$ if $\phi(n)$ contains an occurrence of $\ul{\psi}$ for some $n$.  We require that this graph be acyclic (in particular, having no loops) and that it be well-founded in the sense that there is no infinite sequence $\ul{\phi_1} \to \ul{\phi_2} \to \cdots$.
\end{remark}

This framework is enough to formalize simple deterministic languages such as PCF.  In order to turn it into a language that can model games, we shall add additional constants to our language:

\begin{definition}
  We fix a finite set $\P$ of \emph{players}.

  \begin{description}
    \item[Move constants] A \emph{move constant} takes the form $S^b\from \ul{A}$, where $S\subset A$ is non-empty and $b\in\mathcal P$.
  \end{description}

  We read $S^b$ as `Player $b$ chooses a value from $S$'.

  Our language will be given by the tuple $(\A,\F, \M)$, where $\F$ the set of function constants and $\M$ the set of move constants.
\end{definition}

\begin{example}
  We can recover the language PCF by setting $\P = \{\RN{1}\}$ and defining numerals by $\n=\ul{n}$, using the function constants $\suc$ and $\IfO$ as defined above.  We can add a nondeterministic oracle to the language by setting $\wn = \bN^\RN{1}$.
\end{example}

\subsection{Operational semantics}

We define a notion of \emph{evaluation context} in the style of Felleisen:

\[
  C ::= \hole \mid C\; M\mid\ul{\phi}\;C
  \]
Here, $M$ ranges over terms in the language and $\ul{\phi}$ ranges over the function constants in $\F$.  We write $M=C[M']$ if the term $M$ is obtained from $C$ by replacing the unique occurrence of $\hole$ in $C$ with the term $M'$.

We call a program of ground type $\ul{A}$ a \emph{game}.  We call a subset $T\subset\P$ a \emph{team} and a subset $t\subset A$ a \emph{target}.

We now define a predicate $\Tct$ on terms as in Figure \ref{fig:big-step}.  
\begin{figure}
  \begin{mathpar}
    \inferrule*{b\in T \\ \exists a\in S\esuchthat C[\ul{a}]\Tct}{C[S^b]\Tct}
      \and \inferrule*{b \not\in T \\ \forall a\in S\esuchthat C[\ul{a}]\Tct}{C[S^b]\Tct}
      \and \inferrule*{C[M[N/x]]\Tct}{C[(\lambda x.M)N]\Tct}
      \and \inferrule*[right=$\ul{\phi}\in\F$]{C[\phi(a)]\Tct}{C[\ul{\phi}\;\ul{a}]\Tct}
  \end{mathpar}
  \caption{Big-step operational semantics for the language $(\A,\F,\M)$}
  \label{fig:big-step}
\end{figure}
To understand this semantics better, let's look at the small-step semantics defined in Figure \ref{fig:small-step}.
\begin{figure}
  \begin{mathpar}
    \inferrule*[left=move,right=$a\in S$]{ }{S^b\opto \ul{a}}
      \and \inferrule*[left=function]{ }{\ul{\phi}\;\ul{a}\opto\phi(a)}
      \and \inferrule*[left=beta-reduction]{ }{(\lambda x.M)N \opto M[N/x]}
      \and \inferrule*[left=context]{M \opto N}{C[M]\opto C[N]}
  \end{mathpar}
  \caption{Small-step operational semantics for the language $(\A,\F,\M)$}
  \label{fig:small-step}
\end{figure}
A term $M\from T$ now defines a game between team $T$ and the opposing team $\P\setminus T$ as follows: we evaluate the term step by step.  At each step, the proof that $M\opto M'$ must terminate with one of the three rules \rulename{move}, \rulename{function} or \rulename{beta-reduction}.  In the last two cases, there is a unique choice of reduction to make.  In the first case, there are multiple possibilities, one for each value $a\in S$.

In such a case, if $b\in T$ then team $T$ are allowed to choose which value $a$ to use.  If $b\not\in T$, then the opposing team $\P\setminus T$ are allowed to choose.  Team $T$ wins if the term eventually converges to a value $\ul{a}$, where $a\in t$ and team $\P\setminus T$ wins if the term converges to $\ul{b}$, where $b\not\in t$.  Then the judgement $M\Tct$ precisely says that team $T$ has a strategy to ensure that the term $M$ ends up in $t$.

\begin{example}
  Coming back to our nondeterministic PCF example, if $M\from\nat$ is a term, then the judgement that $M\teamconverge{\emptyset}{\{n\}}$ says that $M$ \emph{must converge} to $n$.  The judgement that $M\teamconverge{\{I\}}{\{n\}}$ says that $M$ \emph{may converge} to $n$.
\end{example}

We read $M\Tct$ as `Team $T$ can force the term $M$ into the target $t$'.

\begin{definition}[Observational equivalence]
  We define observational equivalence for a specified set $\T\subset\power(\P)$ of `friendly teams' and a specified set $\t \subset \prod_{A\in\A}\power(A)$ of specified targets.

  If $A\in\A$ and $M,M'\from\ul{A}$, we say that $M\equiv_e M'$ ($M$ is \emph{observationally equivalent to $M'$}) if for all teams $T\in\T$ and for all target sets $t\in\t$ we have $M\xrightarrow{T}t(A)$ if and only if $M'\xrightarrow{T}t(A)$.

  For general terms $M,M'$ of the same type, we say that $M\equiv_e M'$ if for all contexts $C$ such that $C[M],C[M']$ have ground type, $C[M]\equiv_e C[M']$.
\end{definition}

\begin{definition}[Observational order]
  Similarly, we say that a term $M$ is \emph{observationally less than or equal to} another term $M'$, and write $M\le_e M'$, if for all $T\in\T$ and for all $t\in\t$, $M\xrightarrow{T}t(A)$ implies $M'\xrightarrow{T}t(A)$.

  For general terms $M,M'$ of the same type, we say that $M\le_e M'$ if for all contexts $C$ such that $C[M],C[M']$ have ground type, $C[M]\le_e C[M']$.
\end{definition}

\begin{example}
  PCF with may equivalence is the case corresponding to the set $\T=\{\{\RN{1}\}\}$ and $\t=\{\bN\}$.

  PCF with must equivalence corresponds to $\T=\{\emptyset\}$ and $\t=\{\bN\}$.

  PCF with may-and-must equivalence corresponds to $\T=\{\emptyset, \{\RN{1}\}\}$ and $\t=\{\bN\}$..
\end{example}

\begin{lemma}
  Let $M,M:S$ be such that $M\le_e M'$, and let $F,F':S\to T$ be such that $F\le_e F'$.  
  Then $F M \le_e F' M'$.
\end{lemma}

\subsection{Recursion}

In order to recover the full language PCF, we need to add recursion combinators $\Y_T$ to our language, corresponding to the following small-step reduction:
\[
  \inferrule*[left=recursion]{ }{\Y_T M \opto M ( \Y_T M )}
  \]
giving us the big-step rule
\[
  \inferrule{C[M (\Y_T M)] \Tct}{C[\Y_T M] \Tct}
  \]
This rule introduces for the first time the possibility of \emph{divergence}, or non-termination.  
We will assume that a team $T$ never wants the program to diverge.  
We do not lose anything by making this assumption; indeed, we can model the predicate $M \xrightarrow{T} t \cup \{\bot\}$ (`Team $T$ has a strategy to force the term $M$ into the target $t$ or to make it diverge') as the negation of the predicate $M \xrightarrow{\P\setminus T}\A \setminus t$ (`The opposition to team $T$ has a strategy to force the term $M$ into the complement of the target $t$'): the games we are considering are all \emph{open} in the sense that they terminate after finitely many moves, so exactly one of the two teams has a strategy by the Gale-Stewart theorem.

It turns out that we can also model PCF -- and other languages we have constructed in this section -- as a subset of a larger language that does not involve any special recursion constants, but uses only the function, value and move constants that we have already introduced.  
The advantage of this is that, since function constants are not self-referential, they are much easier to model in a denotational semantics than recursion, which usually requires some order-theoretic properties of the underlying model.  
The only innovation we will need to make on the semantics side is to give denotational semantics for the move constants; this will be covered in Section \ref{sec:denotational-semantics}.

As an illustration of our technique, we show how PCF itself can be modelled inside another language.
First, we introduce a new function constant, $\iter_T\from \nat \to T \to (T \to T) \to T$, corresponding to iteration (realization of natural numbers as Church numerals).  
$\iter_T$ is defined by $\iter_T=\ul{\iota_T}$, where:
\[
  \iota_T(n) = \lambda z.\lambda s.\underbrace{s (s (s \cdots}_{n\text{ times}}z)\cdots))
    \]
In order to model divergence, we add special divergence constants $\Omega_T$ for each type $T$.  
We include no extra rules for these divergence constants; if we end up with $C[\Omega_T]$ for some context $C$, then we consider the term to be `stuck', and to have converged to no value.

Now let $M$ be a general PCF term (possibly involving instances of $\Y_T$ for some types $T$.  Since PCF is a deterministic language, if $M$ converges then it does so in a bounded number of steps $m$.  If we now replace each instance of $\Y_T$ in $M$ with the function
\[
  \lambda N.\iter_T\;\ul{m}\;\Omega_T N
  \]
then we claim that the term converges to the same value.  Indeed, we observe that $\iter_T\;\ul{m}\;\Omega_T N$ is equivalent to the term
\[
  \underbrace{N (N (N \cdots}_{m\text{ times}}\Omega_T)\cdots))
  \]
and is therefore itself equivalent to
\[
  N(\iter_T (\ul{m-1})\Omega_T N)
  \]
The term $\iter_T\;\ul{m}\;\Omega_T N$ therefore has the same behaviour as the term $\Y_T N$, except that the index $m$ decreases by $1$ each time we use the rule.  
Since the reduction of the term $N$ takes $m$ steps anyway, we will never `run out' of iterations.

However, although this allows us to model \emph{individual programs} in PCF, it does not allow us to model functions that may take an unbounded number of recursion steps depending on their argument.  
In particular, we cannot model $\Y_T$ itself using iteration alone.  
In order to do this, we add a nondeterministic oracle $\wn$ to the language, and using may-equivalence as our equivalence relation on terms.  
In our framework, this corresponds to adding a player so that $\P=\{\RN{1}\}$ and then setting $\wn = \mathbb N^{\RN{1}}$.
Then we can model $\Y_T$ as the term
\[
  \lambda N.\iter_T\;\wn\;\Omega_T N
  \]
Because of the may-equivalence, this now has the same operational semantics (within PCF) as our original $\Y_T$: if a PCF term converges, then it converges after $m$ steps for some $m$, and so there is the \emph{possibility} that the oracle $\wn$ will choose a large enough value such that the term must converge.  
So the term may converge to the same value as the original term with $\Y_T$.  
On the other hand, if a PCF term diverges, then there is no number we could replace the $\wn$ with that would cause the term to converge.  
In that case, for every $m$ that the oracle could choose, the term will eventually `run out' and reach the divergence term $\Omega_T$, at which point it will get stuck.

\begin{theorem}
  There is an embedding of the language
  \[
    \text{PCF} = \lambda + \mathbb N + \Y
    \]
  into the language
  \[
    \text{Nondeterministic iterative PCF} = \lambda + \mathbb N + \iter + \Omega + \wn
    \]
  under may-equivalence.  
  That is to say, there is an structurally-inductive map $r$ from PCF terms/contexts to terms/contexts of nondeterministic iterative PCF such that two PCF programs $M$ and $N$ are observationally equivalent if and only if the corresponding programs in nondeterministic iterative PCF are may-equivalent.
\end{theorem}

\begin{proof}
  The mapping $r$ replaces every instance of $\Y_T$ with $(\lambda N.\iter_T\;\wn\;\Omega_T N$).

  Note the following observational equivalence:
  \[
    \Y_T \equiv_e \lambda N.\iter\;\ul{m}\;(\Y_T N)\;N
    \]
  which holds for any $n$.  
  This is because both terms may converge 
\end{proof}

\section{\game{}s}

In this section, we define the notion of a \game, one of our two alternative formulations of our basic intuition of a `game'.

We fix some set $\P$ of players throughout.

\begin{definition}
  Let $A$ be a set.  
  A \emph{\game{} $\Gamma$ with result set $A$} is given by a tuple $(\M_\Gamma,P_\Gamma,J_\Gamma)$ where
  \begin{itemize}
    \item $\M_\Gamma$ is a set of \move{}s.
    \item $P_\Gamma$ is a prefix-closed set of finite sequences of pairs of the form $p\from m$, where $p\in\P$ is a player and $m\in\M_\Gamma$ is a move.  We define $T_\Gamma$, the set of \emph{terminal \play{}}s in $P_\Gamma$ to be the set of all $s\in P_\Gamma$ such that $sa\not\in P_\Gamma$ for any $a$.  
    \item $J_\Gamma\from T_\Gamma\to A$ is a judgement function that says what the result is after a complete sequence of moves.
  \end{itemize}
  such that
  \begin{itemize}
    \item There is always exactly one player whose turn it is.  
      Explicitly, if $sa,sb\in P_\Gamma$, then the moves $a$ and $b$ are made by the same player.
  \end{itemize}
\end{definition}

\begin{remark}
  $\Gamma$ may contain infinitely long chains of sequences of \move{}s.  
  In that case, there is no result value for the \play{}.
\end{remark}

\begin{remark}
  This construction gives rise to a monad $G$ on the category of (possibly large) sets, where a set $A$ is sent to the set $GA$ of games with result set $A$.  
  The natural transformation $GGA\to GA$ is the one that takes a game whose results are games with result set $A$, and forms a game that plays as follows: the players play through the first game; then, if and when they reach a terminal \play{}, they then play through the resulting game to reach a value in $A$.

  We will not make great use of this monad, but it will be implicit in a lot of what we do.  
  As we can model the powerset monad using nondeterministic strategies, so our game semantics will allow us to model this game monad.
\end{remark}

\begin{definition}
  Let $\Gamma$ be a game with result set $A$.  
  Let $T\subset \P$ be a team of players.  
  Then a $T$-strategy $S$ for $\Gamma$ is a prefix-closed subset of $P_\Gamma$ subject to the following rules:
  \begin{itemize}
    \item If $s\in S$ and $sa\in P_\Gamma$ is such that the move $a$ is made by a player \emph{not} in $T$, then $sa\in S$.
    \item If $sa,sb\in S$, and the moves $a,b$ are made by a player in $T$, then $a=b$.
    \item If $s\in S$ and there exists $sa\in P_\Gamma$ such that the move $a$ is made by a player in $T$, then there exists $b$ such that $sb\in P_\Gamma$.
  \end{itemize}
\end{definition}

\section{Game Semantics}

\subsection{Arenas}

Our basic game semantics will be the one given in \cite{hoPcf}.  
We first present the Hyland-Ong game semantics.  
Then, we shall enrich the semantics by appending \game{}s on to strategies.

\begin{definition}
  An \emph{arena} is a triple $A=(M_A,\lambda_A,\ts_A)$ where
  \begin{itemize}
    \item $M_A$ is a countable set of \emph{moves}.
    \item $\lambda_A\from M_A\to\OP\times\QA$ designates each move as either a \emph{$P$-move} or an \emph{$O$-move} and as either a \emph{question} or an \emph{answer}.  
      We will often split $\lambda_A$ into its two parts
      \begin{gather}
        \lambda_A^{OP} = \pr_1\circ\lambda_A\from M_A\to\OP\\
        \lambda_A^{QA} = \pr_2\circ\lambda_A\from M_A\to\QA
      \end{gather}
    \item $\ts_A$ is an \emph{enabling relation} between $M_A+*$ and $M_A$ satisfying:
      \begin{description}
        \item[Alternation] If $a \ts_A b$ then $\lambda_A^{OP} (a) = \neg(\lambda_A^{OP}(b))$
        \item[Initial moves] If $*\ts_A a$ then $\lambda_A(a) = (O,Q)$ and for all $b\in M_A$, $b\not{\ts_A} a$.
        \item[Answers are enabled by questions] If $a,b\in M_A$ are such that $a \ts_A b$ and $\lambda_A^{QA}(b)=A$ then $\lambda_A^{QA}(a)=Q$.
      \end{description}
      We say that a move $a$ is \emph{initial} if $*\ts_A a$.
  \end{itemize}
\end{definition}

\begin{definition}
  A \emph{justified play} $s$ in an arena $A$ is given by a (finite or infinite) sequence of moves of $A$, together with a \emph{justification pointer} for each non-initial move $a$ occurring in $s$ back to a previous move $b$ such that $b\ts_A a$.  
  In that case, we say that $b$ \emph{justifies} $a$.

  Furthermore, we require that if $s\ne \emptyplay$ then the first move in $s$ is initial.
\end{definition}

\begin{definition}
  We say that a move $a$ \emph{hereditarily justifies} a move $b$ if there is a sequence of justification pointers in $J(s)$ that leads from $b$ to $a$.
\end{definition}

\subsection{Compound arenas}

Let $A,B$ be arenas.  
Then there are two main ways to combine $A$ and $B$ to make a new arena.  
The first forms the \emph{product} $A\times B$ of $A$ and $B$:
\begin{itemize}
  \item $M_{A\times B} = M_A + M_B$.
  \item $\lambda_{A\times B} = [\lambda_A, \lambda_B]$.  
  \item $x\ts_{A\times B} m$ if and only if $x\ts_A m$ or $x\ts_B m$.
\end{itemize}
The second forms the \emph{function space} $A \iimpl B$ from $A$ to $B$:
\begin{itemize}
  \item $M_{A\iimpl B} = M_A + M_B$.
  \item $\lambda_{A\iimpl B} = [(\neg\times\id)\circ\lambda_A,\lambda_B]$.  
  \item $x\ts_{A\iimpl B} m$ if and only if
    \begin{description}
      \item[either] $x\ts_B m$
      \item[or] $x\ne *$ and $x\ts_A m$
      \item[or] $*\ts_B x$ and $*\ts_A m$.
    \end{description}
\end{itemize}

\subsection{Strategies}

In order to capture the possibility of divergence, we follow \cite{mcCHFiniteND} and extend the usual definition of a strategy as a set of traces by adding in an extra set of positions designating which plays may lead to a divergence.

Blah blah blah blah blah.

\subsection{Composition of strategies}

Same as usual.

\section{Strategies as \game{}s}

\subsection{\game{}-plays and \game{}-strategies}

We now enrich the structure of strategies by equipping them with certain classes of \game{}s. We fix a set $\P$ of players throughout.

\begin{definition}
  Let $A$ be an arena and let $\M$ be a set of moves.  
  Then a \game{}-play over $M_A$ is a (possibly infinite) sequence $s$ of moves that are either:
  \begin{itemize}
    \item Moves $a\in M_A$, called \emph{moves} or:
    \item Moves $p\from m\in \P\times\M$, called \emph{\move{}s}
  \end{itemize}
  such that
  \begin{itemize}
    \item The first move in $s$ is an $O$-move in $A$.
    \item If a move of the form $(p\from m)$ is followed by a move $a\in M_A$, then $a$ is a $P$-move.
    \item Every $P$-move in $A$ is followed immediately (if at all) by an $O$-move in $A$.
  \end{itemize}

  The \emph{shadow} of a \game{}-play is the sequence formed by removing all moves of the form $p\from m$.  
  A \emph{justified \game{}-play for $A$} is a \game{}-play $s$ over $A$, together with the structure of a justified play over the shadow of $s$.
\end{definition}

\begin{definition}
  A \emph{\game{}-strategy} for an arena $A$ is a set $\M_\sigma$ of moves and a prefix-closed set of \game{}-plays over $\M$ such that when we forget about the \play{}s $\Sigma_s^t$, the resulting collection of justified sequences is a strategy for $A$, and such that if $s.(p\from m),s.(q\from n)\in S$, then $p=q$.
\end{definition}

\subsection{Composition}

Possibly slightly tricky; the idea is that the process of `hiding' moves concatenates \play{}s together.

\subsection{Ordering strategies}

\begin{definition}
  Let $\sigma$ be a \game{}-strategy and let $T\subset \P$ be a team of players.

  A $T$-\strategy{} for $\sigma$\footnote{Yes, that is a \strategy{} for a strategy.} is a subset $S$ of $\sigma$ subject to the following rules:
  \begin{itemize}
    \item If $s\in S$ and $sa\in\sigma$, where $a$ is either an $O$-move in $M_A$ or a move $(p:m)$, where $m\not\in T$, then $sa\in S$.
    \item If $sa,sb\in S$, where $a,b$ are $P$-moves in $M_A$, then $a=b$.
    \item If $s.(p\from m),s.(p\from n)\in S$, and $p\in T$, then $m=n$.
    \item If $s\in S$ and $sa\in\sigma$, where $a$ is either a $P$-move or a move of the form $(p\from m)$ for $m\in T$, then $sb\in S$ for some $b$.
  \end{itemize}
\end{definition}

\begin{definition}
  Let $\sigma$ be a \game{}-strategy, and let $S$ be a \strategy{} for $\sigma$.  
  Then, if $s$ is an $O$-play in $A$ that is the shadow of some \game{}-play in $\sigma$, we write $R_S^s$ for the set of moves $a$ such that $sa$ is the shadow of some \game{}-play in $S$.

  We write $R_\sigma^s$ for the set
  \[
    \{R_S^s\suchthat \textrm{$S$ is a \strategy{} for $\sigma$ and $s$ is the shadow of a play in $S$}, R_S^s\ne\emptyset\}
    \]
\end{definition}

\begin{definition}
  Let $\sigma,\tau$ be \game{}-strategies.  
  We say that $\sigma \le_T \tau$ if the shadow of $\sigma$ is a subset of the shadow of $\tau$ and if for all $O$-moves $s$ that are the shadow of a play in $\sigma$, we have $R_\sigma^s\subset R_\tau^s$.
\end{definition}

\subsection{Example -- one-player \game{}s}

Suppose that $\P=\{\RN{1}\}$.  
Then there are two possibilities for $T$: $T=\emptyset$ and $T=\{\RN{1}\}$.

We show that these correspond to the may- and must-orderings defined by Harmer and McCusker.

\begin{proposition}
  Suppose $\{P\}=\{\RN{1}\}$.  Let $A$ be an arena and let $\sigma$ be a strategy for $A$.  
  Define
  \begin{itemize}
    \item $T_\sigma$ to be the shadow of $\sigma$
    \item $D_\sigma$ to be the set of all $O$-positions $d$ in $T_\sigma$ such that there is either an infinite position in $\sigma$ having shadow $d$ or such that there is a terminal position in $\sigma$ having shadow $d$ and ending with a \move{}.
  \end{itemize}

  Now let $\sigma,\tau$ be \game{}-strategies for $A$.

  i) $\sigma \le_{\{\RN{1}\}} \tau$ if and only if $T_\sigma \subset T_\tau$.

  ii) $\sigma \le_\emptyset \tau$ if and only if ...
\end{proposition}

\begin{proof}

  (i): \textbf{If. }
  Suppose that $T_\sigma\subset T_\tau$.  
  We want to show that $\sigma\le_{\{\RN{1}\}}$, for which it suffices to show that for all $O$-positions $s\in T_\sigma$ we have $R_\sigma^s\subset R_\tau^s$.  
  Let $s\in T_\sigma$ be an $O$-position and let $S$ be a \strategy{} for $\sigma$ such that $s$ is the shadow of some \game{}-play in $S$ and $R_S^s\ne\emptyset$.  
  Let $a\in R_S^s$.  
  By the definition of a \strategy{} for $\sigma$, we can see that in fact $R_S^s=\{a\}$.

  Since $T_\sigma\subset T_\tau$, we know that there is some \game{}-play in $\tau$ whose shadow is $sa$.  
  Then it is easy to construct a \strategy{} $S'$ for $\tau$ such that $a\in R_{S'}^s$.  
  Moreover, by the same argument, we see that $R_{S'}^s=\{a\}$.  
  Therefore, $R_\sigma^s\subset R_\tau^s$.

  \textbf{Only if. }
  Suppose that $\sigma\le_{\{\RN{1}\}}\tau$.  
  Let $sa\in T_\sigma$ be a non-empty $P$-position.  
  Then $sa$ is the shadow of some position in $\sigma$.  
  We can construct a \strategy{} $S$ for $\sigma$ such that $sa$ is in the shadow of $S$; moreover, we have $R_S^s=\{a\}$.  
  Therefore, $\{a\}=R_{S'}^s$ for some \strategy{} $S'$ for $\tau$.  
  It follows that $sa\in T_\tau$.

  (ii): \textbf{If. }

\end{proof}

\begin{example}
  Fix two players B (black) and W (white) and a set of moves $\M$ consisting of all legal chess moves.  
  Then we can model games played on a chess board using the arena given by
  \[
    (\{q,ww,dr,bw\}, \{q\mapsto(O,Q),\;ww,dr,bw\mapsto(P,A)\},\{q\ts ww,dr,bw\}, \{q\})
    \]
  A justified play over the sequence $q.ww$ is a collection of justification pointers $j$ from $ww$ to $q$, each annotated with a sequence of chess moves carried out by one or other of the two players.  
  The game of chess itself is then described by three particular justified plays:
  \begin{itemize}
    \item One over the sequence $q.ww$, where the labels of the justification pointers from $ww$ to $q$ are precisely those sequences of moves leading to a win for white.
    \item One over the sequence $q.dr$, where the labels of the justification pointers from $dr$ to $q$ are precisely those sequences of moves leading to a draw.
    \item One over the sequence $q.bw$, where the labels of the justification pointers from $bw$ to $q$ are precisely those sequences of moves leading to a win for black.
  \end{itemize}
\end{example}

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2017-10-07 game_language/gl.tex
Cleared it up a bit.

@@
 
-\section{Game Semantics}
+\section{\game{}-Game Semantics}
 
@@
 Our basic game semantics will be the one given in \cite{hoPcf}.  
-We first present the Hyland-Ong game semantics.  
-Then, we shall enrich the semantics by appending \game{}s on to strategies.
+The semantics we present will be an enrichment of the Hyland-Ong semantics obtained by attaching \game{}-moves on to a strategy.
 
@@
   \end{itemize}
-\end{definition}
-
-\begin{definition}
-  A \emph{justified play} $s$ in an arena $A$ is given by a (finite or infinite) sequence of moves of $A$, together with a \emph{justification pointer} for each non-initial move $a$ occurring in $s$ back to a previous move $b$ such that $b\ts_A a$.
-  In that case, we say that $b$ \emph{justifies} $a$.
-
-  Furthermore, we require that if $s\ne \emptyplay$ then the first move in $s$ is initial.
-\end{definition}
-
-\begin{definition}
-  We say that a move $a$ \emph{hereditarily justifies} a move $b$ if there is a sequence of justification pointers in $J(s)$ that leads from $b$ to $a$.
 \end{definition}
@@
 
-In order to capture the possibility of divergence, we follow \cite{mcCHFiniteND} and extend the usual definition of a strategy as a set of traces by adding in an extra set of positions designating which plays may lead to a divergence.
+We now give our notion of a strategy, which will add the \game{}-theoretic data on to the usual definition of a strategy.  
+We fix a set $\P$ of players.
 
-Blah blah blah blah blah.
+\begin{definition}
+  Let $\M$ be a set of \move{}s, and let $\lambda\from\M\to\P$ be a function saying which player makes each move.  We define a function $\lambda\from (M_A+\M)\to\OP\cup \P$ in the obvious way.
+
+  Let $A$ be an arena.  
+  A \emph{\game{}-play} in $A$ is a sequence
+  \[
+    s \in (M_A + \M)^*
+    \]
+  (where we refer to elements of $M_A$ as $A$-moves and elements of $\M$ as \move{}s) together with a justification pointer from each non-initial $A$-move $a$ to an $A$-move $b$ occurring earlier in the sequence than $a$ such that $b\ts_A a$.
+  We refer to the sequence $s\vert_{M_A}$ of all the $A$-moves in $s$ as the \emph{shadow} of $s$.
+  Furthermore, we require that $s$ satisfy the following properties:
+  \begin{enumerate}[a)]
+    \item The first move in $s$ is an initial move in $A$ (and therefore an $O$-question).
+    \item If $tab\prefix s$, where $a$ is a $P$-move in $A$, then $b$ is an $O$-move in $A$.
+    \item If $tab\prefix s$, where $a$ is an $O$-move in $A$, then $b$ is either a $P$-move in $A$ or a \move{}.
+    \item If $tma\prefix s$, where $m$ is a \move{}, then $a$ is either a \move{} or an $O$-move in $A$.
+  \end{enumerate}
+\end{definition}
+
+\begin{definition}
+  A \emph{\game{}-strategy} $\sigma$ for an arena $A$ is a set $M_\sigma$ of moves, a function $\lambda_\sigma\from \M_\sigma\to\P$ and a set $\sigma$ of \game{}-plays in $A$ satisfying the following rules:
+  \begin{enumerate}[a)]
+    \item If $s\in\sigma$ and $sa$ is a \game{}-play in $A$ such that $a$ is either an $O$-move in $A$ or a \move{}, then $sa\in\sigma$.
+  \end{enumerate}
+\end{definition}
+
+  Let $T\subset\P$ be a team of players.  
+  Define a partition of $\OP\cup\P$ into two sets $\F_T$ (`friendly') and $\U_T$ (`unfriendly') by
+  \begin{gather*}
+    \F_T = \{O\} \cup T \\\
+    \U_T = \{P\} \cup (\P \setminus T)
+  \end{gather*}
 

### 2017-10-13 game_language/gl.tex
Made more changes.

@@
 
-\subsection{Strategies}
+\subsection{\game{}-strategies}
 
@@
 \begin{definition}
-  A \emph{\game{}-strategy} $\sigma$ for an arena $A$ is a set $M_\sigma$ of moves, a function $\lambda_\sigma\from \M_\sigma\to\P$ and a set $\sigma$ of \game{}-plays in $A$ satisfying the following rules:
+  A \emph{\game{}-strategy} $\sigma$ for an arena $A$ is a set $M_\sigma$ of moves, a function $\lambda_\sigma\from \M_\sigma\to\P$ and a non-empty prefix-closed set $\sigma$ of \game{}-plays in $A$ satisfying the following rules:
   \begin{enumerate}[a)]
-    \item If $s\in\sigma$ and $sa$ is a \game{}-play in $A$ such that $a$ is either an $O$-move in $A$ or a \move{}, then $sa\in\sigma$.
+    \item If $s\in\sigma$ and $sa$ is a \game{}-play in $A$ such that $a$ is an $O$-move in $A$, then $sa\in\sigma$.
+    \item If $sa,sb\in\sigma$, where $a,b$ are $P$-moves in $A$, then $a=b$.
+    \item If $s\in\sigma$ is non-empty and does not end with a $P$-move then there exists some $a\in M_A+\M_\sigma$ such that $sa\in\sigma$.
+    \item If $sa,sb\in\sigma$, then $\lambda(a)=\lambda(b)$.
   \end{enumerate}
@@
 
-  Let $T\subset\P$ be a team of players.  
-  Define a partition of $\OP\cup\P$ into two sets $\F_T$ (`friendly') and $\U_T$ (`unfriendly') by
-  \begin{gather*}
-    \F_T = \{O\} \cup T \\\
-    \U_T = \{P\} \cup (\P \setminus T)
-  \end{gather*}
+\begin{remark}
+  The axiom (b) for a strategy might make it look as though we can only model deterministic strategies, but we can in fact model nondeterministic strategies by using \move{}s.  
+  For example, the denotation for a nondeterministic oracle $\wn$ might be the strategy with maximal plays
+  \[
+    q\textsc{n}n
+    \]
+  for all $n\in\bN$, where $\textsc{n}$ is a \move{} corresponding to the natural number $n$.
+\end{remark}
 
-\subsection{Composition of strategies}
+\begin{definition}
+  Let $\sigma$ be a strategy for an arena $A$.  
+  We write $T_\sigma$, the \emph{trace-set} or \emph{shadow} of $\sigma$, for the set of all shadows of elements of $\sigma$.  
+  It is easy to see that $T_\sigma$ is a nondeterministic strategy for $A$ in the usual sense.  
+\end{definition}
 
-Same as usual.
+\subsection{Ordering \game{}-strategies}
+
+\begin{definition}
+  Let $T\subset \P$ be a team of players.  
+  Let $A$ be an arena and let $\sigma$ be a \game{}-strategy for $A$.  
+  Then a \emph{$T$-\strategy{} for $\sigma$}\footnote{Yes, that is a \strategy{} for a strategy.} is a non-empty prefix-closed subset $S$ of $\sigma$ satisfying the following rules:
+  \begin{enumerate}[a)]
+    \item If $s\in S$ and $sa\in\sigma$ where $a$ is an $O$-move in $A$ or a \move{} made by a player \emph{not} in $T$, then $sa\in S$.  
+    \item If $sa,sb\in S$, where $a,b$ are $P$-moves in $A$ or \move{}s made by a player in $T$, then $a=b$.  
+    \item If $s\in S$ and there exists some $a\in M_A+\M_\sigma$ such that $sa\in \sigma$ then there exists some $b\in M_A+\M_\sigma$ such that $sb\in S$.
+  \end{enumerate}
+\end{definition}
+
+\begin{definition}
+  As with strategies, if $S$ is a \strategy{} for some \game{}-strategy $\sigma$, we write $T_S$ for the set of all shadows of \game{}-plays in $S$.
+
+  Once again, it is easy to see that $T_S$ is a strategy for $A$ in the usual sense.  
+\end{definition}
+
+We use $T$-\strategy{}s to define an order on \game{}-strategies.
+
+\begin{definition}
+  Let $A$ be an arena, let $\sigma$ be a \game{}-strategy for $A$ and let $T\subset\P$ be a team of players.  
+  Given a $T$-\strategy{} $S$ for $\sigma$ and $s\in T_\sigma$ ending with an $O$-move, define
+  \[
+    R_S^s = \{a\in M_A\suchthat sa\in T_S\}
+    \]
+  If $s\in T_\sigma$ is an $O$-position, we say that the \strategy{} $S$ is \emph{good at $s$} if $s$ is not the shadow of some infinite position in the limit of $\sigma$.
+
+  We define
+  \[
+    R_{\sigma,T}^s = \{R_S^s\suchthat \textrm{$S$ is a $T$-\strategy{} for $\sigma$},\;\textrm{$S$ is good at $s$}\}
+    \]
+
+  Lastly, if $\sigma,\tau$ are \game{}-strategies for $A$, we say that $\sigma\le_T\tau$ if for all $s\in T_\sigma\cap T_\tau$ we have
+  \[
+    R_{\sigma,T}^s\subset R_{\tau,T}^s
+    \]
+  If $\T\subset\power(\P)$ is a set of teams, then we write $\sigma\le_{\T}\tau$ if $\sigma\le_T\tau$ for all $T\in\T$.A
+
+  If $\sigma\le_T\tau$ and $\tau\le_T\sigma$, then we say that $\sigma\equiv_T\tau$.  
+  Similarly, if $\sigma\le_{\T}\tau$ and $\tau\le_{\T}\sigma$, then we say that $\sigma\equiv_{\T}\tau$.  
+\end{definition}
+
+\subsection{Example: one-player games}
+
+In this section we will take $\P=\{\RN{1}\}$, and show that the preorders on strategies correspond to the lower and upper orders defined in \cite{mcCHFiniteND}.
+
+\begin{lemma}
+  \label{lemma:guy}
+  Let $A$ be an arena and let $\sigma$ be a \game{}-strategy for $A$.
+
+  i) Let $S$ be a $\{\RN{1}\}$-\strategy{} for $\sigma$.  
+  Then $T_S$ is a deterministic sub-strategy of $T_\sigma$.
+
+  ii) Let $S$ be an $\emptyset$-\strategy{} for $\sigma$.  
+  Then $S=\sigma$.
+\end{lemma}
+
+\begin{proposition}
+  Let $A$ be an arena.  
+  Given a \game{}-strategy $\sigma$ for $A$, define $D_\sigma$ to be the set of all (finite) sequences in $T_\sigma$ that are the shadow of some infinite sequence $s$ in the limit of $\sigma$.  
+  (A play in $D_\sigma$ necessarily ends with an $O$-move, since an $O$-move is always immediately followed by a $P$-move in a \game{}-play.)
+
+  Now let $\sigma,\tau$ be \game{}-strategies for $A$.
+
+  i) $\sigma \le_{\{\RN{1}\}} \tau$ if and only if $T_\sigma\subset T_\tau$.
+
+  ii) $\sigma \le_{\emptyset} \tau$ if and only if ....
+\end{proposition}
+
+\begin{proof}
+  (i): By Lemma \ref{lemma:guy}, if $S$ is a $\{\RN{1}\}$-\strategy{} for $\sigma$, then $T_S$ is a deterministic sub-strategy of $T_\sigma$.  
+  It follows that if $S$ is good at a position $s$, then $R_S^s$ is a singleton.  
+  Moreover, if $sa\in T_\sigma$ is a $P$-position, then we can construct some $\{\RN{1}\}$-\strategy{} $S$ for $\sigma$ such that $S$ is good at $s$ and $sa\in T_S$.
+
+  Suppose that $\sigma\le_{\{\RN{1}\}}\tau$ and suppose that $s\in T_\sigma\cap T_\tau$ is an $O$-position and that $sa\in T_\sigma$.  
+  Then there is some $\{\RN{1}\}$-\strategy{} $S$ for $\sigma$ such that $S$ is good at $s$ and $sa\in T_S$: so $R_S^s=\{a\}$.  
+  Therefore, there is some $\{\RN{1}\}$-\strategy{} $S'$ for $\tau$ such that $S'$ is good at $s$ and $R_{S'}^s=\{a\}$.  
+  It follows that $sa\in T_\sigma$.  
+  Now, working by induction on the strategy, we can prove that $T_\sigma\subset T_\tau$.
+
+  Conversely, suppose that $T_\sigma\subset T_\tau$.  
+  Let $s\in T_\sigma$ be an $O$-position.  
+  So $s\in T_\tau$.  
+  Let $S$ be a $\{\RN{1}\}$-\strategy{} for $\sigma$ that is good at $s$.  
+  We know that $R_S^s = \{a\}$ for some move $a$ such that $sa\in T_\sigma$.  
+  Then $sa\in T_\tau$, and we can construct $S'$ such that $R_{S'}^s=\{a\}$.  
+  Therefore, $R_{\sigma,\{\RN{1}\}}^s\subset R_{\tau,\{\RN{1}\}}^s$ and it follows that $\sigma \le_{\{\RN{1}\}}\tau$.
+
+  (ii): Suppose that $\sigma,\tau$ are \game{}-strategies for $A$ and that $\sigma\le_{\emptyset}\tau$.  
+  Let $s\in T_\sigma\cap T_\tau$ be an $O$-position and suppose that $s\not\in D_\sigma$.  
+  Then it follows that
+
+\end{proof}
+
+\subsection{Composition of \game{}-strategies}
+
+Let $A,B,C$ be arenas, let $\sigma$ be a \game{}-strategy for $A\iimpl B$ and let $\tau$ be a \game{}-strategy for $B\iimpl C$.  
+We shall construct a strategy $\sigma;\tau$ for $A\iimpl C$, the \emph{composition} of $\sigma$ with $\tau$.
+
+We first define
+\[
+  \M_{\sigma;\tau}=\M_\sigma + \M_\tau
+  \]
 

### 2018-01-21 game_language/gl.tex
Made some structural changes, etc.

@@
   Once again, it is easy to see that $T_S$ is a strategy for $A$ in the usual sense.
+
+  We write $D_S$ for the set of positions $s\in T_\sigma$ where there exists $t\in S$ such that for all $t'\in\sigma$ satisfying $t\prefix t'$, $s$ is the shadow of $t'$.  
 \end{definition}
@@
     \]
-  If $s\in T_\sigma$ is an $O$-position, we say that the \strategy{} $S$ is \emph{good at $s$} if $s$ is not the shadow of some infinite position in the limit of $\sigma$.
 
@@
   \[
-    R_{\sigma,T}^s = \{R_S^s\suchthat \textrm{$S$ is a $T$-\strategy{} for $\sigma$},\;\textrm{$S$ is good at $s$}\}
+    R_{\sigma,T}^s = \{R_S^s\suchthat \textrm{$S$ is a $T$-\strategy{} for $\sigma$},\;\textrm{$t\not\in D_S$ for all $t\prefix s$}\}
     \]
@@
   \[
-    R_{\sigma,T}^s\subset R_{\tau,T}^s
+    R_{\sigma,T}^s\le R_{\tau,T}^s
     \]
+  where we say $R\le R'$ if for all $A\in R$ there exists $B\in R'$ such that $B\subset A$.
+
   If $\T\subset\power(\P)$ is a set of teams, then we write $\sigma\le_{\T}\tau$ if $\sigma\le_T\tau$ for all $T\in\T$.A
@@
   i) Let $S$ be a $\{\RN{1}\}$-\strategy{} for $\sigma$.  
-  Then $T_S$ is a deterministic sub-strategy of $T_\sigma$.
+  Then $T_S$ is a deterministic (possibly partial) sub-strategy of $T_\sigma$.
 
   ii) Let $S$ be an $\emptyset$-\strategy{} for $\sigma$.  
-  Then $S=\sigma$.
+  Then $S=\sigma$ as sets.
 \end{lemma}
@@
   Let $A$ be an arena.  
-  Given a \game{}-strategy $\sigma$ for $A$, define $D_\sigma$ to be the set of all (finite) sequences in $T_\sigma$ that are the shadow of some infinite sequence $s$ in the limit of $\sigma$.  
-  (A play in $D_\sigma$ necessarily ends with an $O$-move, since an $O$-move is always immediately followed by a $P$-move in a \game{}-play.)
+  Given a \game{}-strategy $\sigma$ for $A$, define $D_\sigma$ to be the set of all (finite) $s\in T_\sigma$ where there exists $t\in\sigma$ such that for all $\t'\in\sigma$ satisfying $t\prefix t'$, $s$ is the shadow of $t'$.
 
@@
 \begin{proof}
-  (i): By Lemma \ref{lemma:guy}, if $S$ is a $\{\RN{1}\}$-\strategy{} for $\sigma$, then $T_S$ is a deterministic sub-strategy of $T_\sigma$.  
-  It follows that if $S$ is good at a position $s$, then $R_S^s$ is a singleton.  
-  Moreover, if $sa\in T_\sigma$ is a $P$-position, then we can construct some $\{\RN{1}\}$-\strategy{} $S$ for $\sigma$ such that $S$ is good at $s$ and $sa\in T_S$.
-
-  Suppose that $\sigma\le_{\{\RN{1}\}}\tau$ and suppose that $s\in T_\sigma\cap T_\tau$ is an $O$-position and that $sa\in T_\sigma$.  
-  Then there is some $\{\RN{1}\}$-\strategy{} $S$ for $\sigma$ such that $S$ is good at $s$ and $sa\in T_S$: so $R_S^s=\{a\}$.  
-  Therefore, there is some $\{\RN{1}\}$-\strategy{} $S'$ for $\tau$ such that $S'$ is good at $s$ and $R_{S'}^s=\{a\}$.  
-  It follows that $sa\in T_\sigma$.  
-  Now, working by induction on the strategy, we can prove that $T_\sigma\subset T_\tau$.
+  (i): Suppose that $\sigma\le_{\{\RN{1}\}}\tau$.  
+  Let $s\in T_\sigma$ be a $P$ position.  
+  If $s=\emptyplay$ then $s\in T_\tau$.  
+  Otherwise, $s=s'a$ for some $O$-position $s'$.  
+  We may construct a $\{\RN{1}\}$-\strategy{} $S$ for $\sigma$ by
+  \[
+    S=\{t\in\sigma\suchthat \textrm{for all even-length prefixes $t'\prefix t$, $t'\prefix s$}\}
+    \]
+  Then $S$ contains $s$ and, moreover, $s'\not\in D_S$.  
+  It follows that $\{a\}\in R_{\sigma,\{\RN{1}\}}^{s'}$ and therefore that $\{a\}\in R_{\tau,\{\RN{1}\}}^{s'}$, which means that there is some \strategy{} $S'$ for $\tau$ such that $sa\in T_{S'}$.  
+  It follows that $sa\in T_\tau$.
 
   Conversely, suppose that $T_\sigma\subset T_\tau$.  
-  Let $s\in T_\sigma$ be an $O$-position.  
-  So $s\in T_\tau$.  
-  Let $S$ be a $\{\RN{1}\}$-\strategy{} for $\sigma$ that is good at $s$.  
-  We know that $R_S^s = \{a\}$ for some move $a$ such that $sa\in T_\sigma$.  
-  Then $sa\in T_\tau$, and we can construct $S'$ such that $R_{S'}^s=\{a\}$.  
-  Therefore, $R_{\sigma,\{\RN{1}\}}^s\subset R_{\tau,\{\RN{1}\}}^s$ and it follows that $\sigma \le_{\{\RN{1}\}}\tau$.
+  Let $s\in T_\sigma$ be an $O$-position and let $S$ be a $\{\RN{1}\}$-\strategy{} for $\sigma$ such that $s\not\in D_S$.  
+  Then, by Lemma \ref{lemma:guy}, $T_S$ is a deterministic sub-strategy for $T_\sigma$; since $s\not\in D_S$, we have $sa\in T_\sigma$ for some $a$ and so $R_S^s=\{a\}$.  
+  Since $T_\sigma\subset T_\tau$, we have $sa\in T_\tau$.  
+  As above, we may construct some \strategy{} $S'$ for $\tau$ such that $s\not\in D_{S'}$ and $R_{S'}^s=\{a\}$.  
+  It follows that $\sigma\le_{\{\RN{1}\}}\tau$.
 
-  (ii): Suppose that $\sigma,\tau$ are \game{}-strategies for $A$ and that $\sigma\le_{\emptyset}\tau$.  
-  Let $s\in T_\sigma\cap T_\tau$ be an $O$-position and suppose that $s\not\in D_\sigma$.  
-  Then it follows that
+  (ii): Suppose that $\sigma\le_\emptyset\tau$.  
+  By Lemma \ref{lemma:guy} there are unique $\emptyset$-\strategy{}s $S_\sigma$ for $\sigma$ and $S_\tau$ for $\tau$, given at the level of sets by $S_\sigma=\sigma$ and $S_\tau=\tau$.
 
+  Let $s\in T_\tau$ be a $P$-position, and suppose that $s\not\in T_\sigma$.  
+  Let $d\prefix s$ be the longest prefix contained in $T_\sigma$.  
+  Certainly $d$ is an $O$-position; since $d\ne s$, we have $da\prefix s$ for some $a$.  
+  Now if $R_{\tau,\emptyset}^e$ is inhabited, it must have a single element, $R_{S_\tau, \emptyset}^e$, which contains $a$.  
+  But since $ea\not\in T_\sigma$, no element of $R_{\sigma,\emptyset}^e$ may contain $a$.  
+  The only possibility, then, is that $e'\in D_\sigma$ for some $e'\prefix e\prefix s$.
+
+  Let $d\in D_\tau$; let $d'\prefix d$ be the longest prefix contained in $D_\tau$ and let $e\prefix d'$ be the longest prefix contained in $T_\sigma$.  
+  Then $e$ must be an $O$-position, by the definition of a strategy.
+
+  If $e=d'$, then $R_{\tau,\emptyset}^e=\emptyset$, since $e=d'\in D_\tau = D_{S_\tau}$.  
+  Therefore, $R_{\sigma,\emptyset}^e=\emptyset$, which means that $e'\in D_{S_\sigma}=D_\sigma$ for some $e'\prefix e\prefix d$.
+
+  If instead $e\neq d'$, then $ea\in T_\sigma\setminus T_\tau$, from which it follows that some prefix of $ea$ is contained in $D_\sigma$, as above.
+
+  Conversely, suppose that the conditions on $T_\sigma,D_\sigma,T_\tau,D_\tau$ hold.  
+  Let $s\in T_\sigma\cup T_\tau$ be an $O$-position.  
+  We have $R_{S_\sigma,\emptyset}^s = \{a\suchthat sa\in T_\sigma\}$ and $R_{S_\tau,\emptyset}^s = \{a\suchthat sa\in T_\tau\}$.  
+  Then $R_{\sigma,\emptyset}^s=\{R_{S_\sigma,\emptyset}^s\}$ if $s\in D_\sigma$ and is empty otherwise, and similarly for $\tau$.
+
+  By the first condition, either $e\in D_\sigma$ for some $e\prefix s$ or $R_{S_\tau,\emptyset}^s\prefix R_{S_\sigma,\emptyset}^s$.  
+  In the first case, $R_{\sigma,\emptyset}^s=\emptyset$, and so certainly $R_{\sigma,\emptyset}^s\le R_{\tau,\emptyset}^s$.  
+  In the second case, by the second condition, $d\not\in D_\tau$ for all $d\prefix s$ and therefore we have $R_{\sigma,\emptyset}^s=R_{S_\sigma,\emptyset}$ and similarly for $\tau$.  
+  The claim then follows.
 \end{proof}
@@
 
-\section{Strategies as \game{}s}
+We say that a sequence $\s\in (M_A + M_B + M_C + \M_{\sigma;\tau})^*$ is a \emph{legal interaction} if
+\[
+  \s\vert_{A,B,\M}\in \M_\sigma
+  \]
+and
+\[
+  \s\vert_{B,C,\M}\in M_\tau
+  \]
+and moreover if the justification pointers in the sequences interact nicely in the usual manner.  
+Here, $\s\vert_{A,B,\M}$ is shorthand for $\s\vert_{M_A,M_B,\M_{\sigma;\tau}}$ and similarly for $B,C$.
 
-\subsection{\game{}-plays and \game{}-strategies}
+Write $\sigma\|\tau$ for the set of legal interactions of sequences between $\sigma$ and $\tau$.  
+We then define
+\[
+  \sigma;\tau = \{\s\vert_{A,C,\M}\suchthat \s\in \sigma\|\tau\}
+  \]
 
-We now enrich the structure of strategies by equipping them with certain classes of \game{}s. We fix a set $\P$ of players throughout.
-
-\begin{definition}
-  Let $A$ be an arena and let $\M$ be a set of moves.  
-  Then a \game{}-play over $M_A$ is a (possibly infinite) sequence $s$ of moves that are either:
-  \begin{itemize}
-    \item Moves $a\in M_A$, called \emph{moves} or:
-    \item Moves $p\from m\in \P\times\M$, called \emph{\move{}s}
-  \end{itemize}
-  such that
-  \begin{itemize}
-    \item The first move in $s$ is an $O$-move in $A$.
-    \item If a move of the form $(p\from m)$ is followed by a move $a\in M_A$, then $a$ is a $P$-move.
-    \item Every $P$-move in $A$ is followed immediately (if at all) by an $O$-move in $A$.
-  \end{itemize}
-
-  The \emph{shadow} of a \game{}-play is the sequence formed by removing all moves of the form $p\from m$.  
-  A \emph{justified \game{}-play for $A$} is a \game{}-play $s$ over $A$, together with the structure of a justified play over the shadow of $s$.
-\end{definition}
-
-\begin{definition}
-  A \emph{\game{}-strategy} for an arena $A$ is a set $\M_\sigma$ of moves and a prefix-closed set of \game{}-plays over $\M$ such that when we forget about the \play{}s $\Sigma_s^t$, the resulting collection of justified sequences is a strategy for $A$, and such that if $s.(p\from m),s.(q\from n)\in S$, then $p=q$.
-\end{definition}
-
-\subsection{Composition}
-
-Possibly slightly tricky; the idea is that the process of `hiding' moves concatenates \play{}s together.
-
-\subsection{Ordering strategies}
-
-\begin{definition}
-  Let $\sigma$ be a \game{}-strategy and let $T\subset \P$ be a team of players.
-
-  A $T$-\strategy{} for $\sigma$\footnote{Yes, that is a \strategy{} for a strategy.} is a subset $S$ of $\sigma$ subject to the following rules:
-  \begin{itemize}
-    \item If $s\in S$ and $sa\in\sigma$, where $a$ is either an $O$-move in $M_A$ or a move $(p:m)$, where $m\not\in T$, then $sa\in S$.
-    \item If $sa,sb\in S$, where $a,b$ are $P$-moves in $M_A$, then $a=b$.
-    \item If $s.(p\from m),s.(p\from n)\in S$, and $p\in T$, then $m=n$.
-    \item If $s\in S$ and $sa\in\sigma$, where $a$ is either a $P$-move or a move of the form $(p\from m)$ for $m\in T$, then $sb\in S$ for some $b$.
-  \end{itemize}
-\end{definition}
-
-\begin{definition}
-  Let $\sigma$ be a \game{}-strategy, and let $S$ be a \strategy{} for $\sigma$.  
-  Then, if $s$ is an $O$-play in $A$ that is the shadow of some \game{}-play in $\sigma$, we write $R_S^s$ for the set of moves $a$ such that $sa$ is the shadow of some \game{}-play in $S$.
-
-  We write $R_\sigma^s$ for the set
-  \[
-    \{R_S^s\suchthat \textrm{$S$ is a \strategy{} for $\sigma$ and $s$ is the shadow of a play in $S$}, R_S^s\ne\emptyset\}
-    \]
-\end{definition}
-
-\begin{definition}
-  Let $\sigma,\tau$ be \game{}-strategies.  
-  We say that $\sigma \le_T \tau$ if the shadow of $\sigma$ is a subset of the shadow of $\tau$ and if for all $O$-moves $s$ that are the shadow of a play in $\sigma$, we have $R_\sigma^s\subset R_\tau^s$.
-\end{definition}
-
-\subsection{Example -- one-player \game{}s}
-
-Suppose that $\P=\{\RN{1}\}$.  
-Then there are two possibilities for $T$: $T=\emptyset$ and $T=\{\RN{1}\}$.
-
-We show that these correspond to the may- and must-orderings defined by Harmer and McCusker.
-
-\begin{proposition}
-  Suppose $\{P\}=\{\RN{1}\}$.  Let $A$ be an arena and let $\sigma$ be a strategy for $A$.  
-  Define
-  \begin{itemize}
-    \item $T_\sigma$ to be the shadow of $\sigma$
-    \item $D_\sigma$ to be the set of all $O$-positions $d$ in $T_\sigma$ such that there is either an infinite position in $\sigma$ having shadow $d$ or such that there is a terminal position in $\sigma$ having shadow $d$ and ending with a \move{}.
-  \end{itemize}
-
-  Now let $\sigma,\tau$ be \game{}-strategies for $A$.
-
-  i) $\sigma \le_{\{\RN{1}\}} \tau$ if and only if $T_\sigma \subset T_\tau$.
-
-  ii) $\sigma \le_\emptyset \tau$ if and only if ...
-\end{proposition}
-
-\begin{proof}
-
-  (i): \textbf{If. }
-  Suppose that $T_\sigma\subset T_\tau$.  
-  We want to show that $\sigma\le_{\{\RN{1}\}}$, for which it suffices to show that for all $O$-positions $s\in T_\sigma$ we have $R_\sigma^s\subset R_\tau^s$.  
-  Let $s\in T_\sigma$ be an $O$-position and let $S$ be a \strategy{} for $\sigma$ such that $s$ is the shadow of some \game{}-play in $S$ and $R_S^s\ne\emptyset$.  
-  Let $a\in R_S^s$.  
-  By the definition of a \strategy{} for $\sigma$, we can see that in fact $R_S^s=\{a\}$.
-
-  Since $T_\sigma\subset T_\tau$, we know that there is some \game{}-play in $\tau$ whose shadow is $sa$.  
-  Then it is easy to construct a \strategy{} $S'$ for $\tau$ such that $a\in R_{S'}^s$.  
-  Moreover, by the same argument, we see that $R_{S'}^s=\{a\}$.  
-  Therefore, $R_\sigma^s\subset R_\tau^s$.
-
-  \textbf{Only if. }
-  Suppose that $\sigma\le_{\{\RN{1}\}}\tau$.  
-  Let $sa\in T_\sigma$ be a non-empty $P$-position.  
-  Then $sa$ is the shadow of some position in $\sigma$.  
-  We can construct a \strategy{} $S$ for $\sigma$ such that $sa$ is in the shadow of $S$; moreover, we have $R_S^s=\{a\}$.  
-  Therefore, $\{a\}=R_{S'}^s$ for some \strategy{} $S'$ for $\tau$.  
-  It follows that $sa\in T_\tau$.
-
-  (ii): \textbf{If. }
-
-\end{proof}
+\section{Chess}
 

### 2018-01-21 nondeterminism/nondeterminism.tex
Made some structural changes, etc.

--- 2017-03-06 nondeterminism/nondeterminism.tex
@@
 
-\newcommand{\stle}{{\;\le_s\;}}
-\newcommand{\exle}{\sqsubseteq}
-\newcommand{\exlub}{\bigsqcup}
-\newcommand{\dv}{{\text{\lightning}}}
-\DeclareMathOperator{\pocl}{pocl}
-\newcommand{\opto}{\longrightarrow}
-
-\title{Transfinite Games for Countable Nondeterminism}
-
 \begin{document}
-
-\section{Introduction}
-
-{\it I would like to expand this section and flesh out the examples a bit more to make them clearer.}
-
-The basic idea underpinning the game semantics for nondeterministic programming languages is to remove the constraint of \emph{determinism} from the usual definition of a strategy (see, for example, \cite{abramskyjagadeesangames}) that says that the player may have at most one reply to each move made by the opponent.
-The determinism constraint is of little technical value and its main purpose is to provide a fully abstract denotational semantics for deterministic programming languages; if we remove it in order to study nondeterministic languages, then much of the technical apparatus of game semantics carries over immediately.
-
-One problem that does arise, however, is that the resulting semantics no longer adequately captures the possibility of divergence in the interaction.
-In deterministic game semantics, divergence is represented by the absence of a reply to an opponent's move, but this is not adequate in the nondeterministic case because it gives us no way to capture a \emph{possible} divergence.
-For example, if we represent divergence by the abence of a reply then Program A, which constantly returns the numeral $1$, and Program B, which makes a nondeterministic choice and then either returns $1$ or diverges, have the same semantics, despite exhibiting different behaviour \cite{mcCHFiniteND}.
-
-We therefore need a new way to keep track of divergence.
-This was done by Harmer and McCusker \cite{mcCHFiniteND}, who resolved the problem by adding extra data to the definition of a strategy that records which opponent positions allow the possibility of divergence.
-Using this device, Harmer and McCusker were able to provide a fully abstract game semantics for PCF with finite nondeterminism.
-
-There is, however, a technical subtlety that arises when we try to use the same technique to model PCF with \emph{unbounded} nondeterminism; that is, PCF with the addition of a nondeterministic natural number generator that never diverges.
-Indeed, if we naively relax the Harmer-McCusker model to allow infinite branching then composition of strategies is no longer associative \cite{RusssThesis}.
-
-Ultimately, the reason why unbounded nondeterminism introduces problems is that it makes the language fine-grained enough to distinguish between computation that is \emph{divergent}; i.e., a computation that carries on for infinitely many steps and does not terminate, and computation that is convergent, but may take an unbounded number of steps to do so.
-For example, using recursion, we may define a function that, at each step, makes a nondeterministic choice whether to call its argument or to return.
-If we have access to unbounded nondeterminism then we may write a function that nondeterministically chooses a natural number $n$, calls its argument $n$ times and then returns.
-Observationally, these programs are different: the first may diverge, while the second always converges.
-In the usual model of strategies as sets of positions, the strategies defined by these two programs are the same.
-
-At first glance, it appears that the Harmer-McCusker model is fine-grained enough to distinguish these two strategies, and this is true if we define the strategies directly: the strategy denoting the first program ought to designate the opening move as divergent, whereas the strategy denoting the second program should not designate any positions as divergent.
-However, if we want to define these strategies compositionally, it turns out that both strategies are designated divergent, since the model treats an infinite increasing sequence of positions as a divergence occurring from livelock (the `infinite chattering' in the game semantics).
-This inconsistency between the direct definition of the strategy and the compositional one is what leads to the failure of composition to be associative.
-
-We need, then, some way to distinguish between computation that takes infinitely many steps and computation that takes a finite, but arbitrarily large, number of steps.
-One approach, taken by Tsukada and Ong \cite{TsukadaSheaves} is to represent strategies as trees, rather than sets of positions; here, there is a distinction between a tree of infinite height and an infinite family of trees of finite but arbitrarily large height.
-We take a different approach, one suggested by the work of Roscoe and Levy (\cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}, cited in \cite{TsukadaSheaves}), and by Laird's sequential algorithms model for PCF with unbounded nondeterminism \cite{LairdOrdinalGames}, and enlarge our strategies to include information about the infinite positions that may occur in them.
-
-\subsection{Related Work}
-
-A more detailed overview of previous work, particularly \cite{LairdOrdinalGames}.
-
-\section{PCF with Countable Nondeterminism}
-
-As in \cite{LairdOrdinalGames}.
-
-\subsection{Type Theory}
-
-\subsection{Operational Semantics}
-
-\subsection{Must Testing}
-
-We are interested in soundness and adequacy for the `must-converge' relation, since the `may-converge' relation can be adequately modelled using finite nondeterminism.
 
@@
 
-\subsection{Games}
+Explain the properties of the game semantics that we will be using, \emph{including} the sequoidal-exponential structure.
+
+\section{Harmer-McCusker Game Semantics of Nondeterminism}
+
+Explain about it, and explain the new contribution of considering infinite positions.
+
+\section{Explicit-oracle Game Semantics}
+
+(or better name)
+
+\subsection{Strategies and composition}
+
+We use the usual game semantics of may-equivalence, but with the following change: a \emph{strategy} a game $A$ is now a pair
+\[
+  (X, \sigma)
+  \]
+where $\sigma$ is a strategy (in the usual sense) for $X\implies A$.  
+Where there is no ambiguity, we shall write $\sigma$ for $(X,\sigma)$.
+
+We compose strategies in the following way: if $(X,\sigma)$ is a morphism from $A$ to $B$ and $(Y,\tau)$ is a morphism from $B$ to $C$, then the composition of these morphisms is given by the pair $(X\tensor Y, \sigma;\tau)$, where $\sigma;\tau$ is the following composite in the usual category of games:
+\[
+  \begin{tikzcd}
+    Y \tensor X \arrow[r, "\tau\tensor\sigma"]
+      & (B \implies C) \tensor (A \implies B) \arrow[r]
+        & A \implies C
+  \end{tikzcd}
+  \]
+This composition is not immediately associative for the simple reason that while $Z \tensor (Y\tensor X)$ and $(Z \tensor Y)\tensor X$ are not isomorphic, they are still equal.
+
+We get round this problem by imposing an equivalence relation on these strategies.  
+One possibility would be to say that $\map{\sigma}{X}{A}$ and $\map{\tau}{Y}{A}$ are equivalent if there is an isomorphism $\map{\phi}{X}{Y}$ making the following triangle commute:
+\[
+  \begin{tikzcd}
+    X \arrow[r, "\sigma"] \arrow[d, "\phi"']
+      & A \\
+    Y \arrow[ur, "\tau"']
+      &
+  \end{tikzcd}
+  \]
+However, this is too strong a definition for our purposes.  
+We want to capture the idea that the game $X$ captures the nondeterminism in the strategy and that two strategies are equivalent if they have the same behaviours in $A$ when we play nondeterministically in $X$.
 
 \begin{definition}
-
-  Given a set $X$, we write $\seqs X$ for the set of all (finite and infinite) sequences of elements of $X$ of length $\le \omega$.
-
-  A \emph{game} is given by a tuple
-  \[
-    A = (M_A, \lambda_A, \zeta_A, P_A)
-    \]
-  where
+  Let $(X,\sigma)$, $(Y, \tau)$ be strategies for a game $A$ (so $\sigma$ is a strategy for $X\implies A$ and $\tau$ is a strategy for $Y\implies A$).  
+  Then we say that $(X,\sigma)\le(Y,\tau)$ if there is a morphism $\phi\from Y\implies X$ such that
   \begin{itemize}
-    \item $M_A$ is a set of moves.
-    \item $\lambda_A\from M_A\to\OP$ designates each move as an $O$-move (played by Player $O$) or a $P$-move (played by Player $P$).  
-    \item $P_A\subset \seqs{M_A}$ is a non-empty prefix-closed set of sequences of moves from $M_A$ of length $\le\omega$, called \emph{positions}.
-We call a sequence $s\in P_A$ \emph{infinite} if $\length(s)=\omega$.
-Otherwise, we say that $s$ is \emph{finite}.
-    \item $\zeta_A\from P_A\to\OP$ designates each position in $P_A$ as a $P$-position or an $O$-position.
+    \item $\phi$ is \emph{total with respect to moves in $Y$}: i.e., if $s\in \phi$ is an $O$-position ending with a move in $Y$, then there exists some $sa\in\phi$.  
+    \item The composite (in the usual category of games) $\phi;\sigma\from Y\implies A$ is a subset of the strategy $\tau$.  
   \end{itemize}
 
-  The set $P_A$ and the functions $\lambda_A,\zeta_A$ are required to satisfy certain additional axioms:
-  \begin{description}
-    \item[Compactness] If $s\in M_A^\omega$ is an infinite sequence of moves such that $t\in P_A$ for all finite prefixes $t\ppprefix s$, then $s\in P_A$.
-    \item[Consistency] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(sa)=\lambda_A(a)$.
-    \item[Alternation] If $a\in M_A$ and $sa\in P_A$ then $\zeta_A(s) = \neg \zeta_A(sa)$.
-    \item[Negativity] $\zeta_A(\epsilon)=P$, where $\epsilon$ is the empty position.
-  \end{description}
-
-  Note that the negativity rule and the alternation rule between them imply that all starting moves are made by player $O$.  
+  We say that $\sigma\equiv\tau$ if $\sigma\le\tau$ and $\tau\le\sigma$.
 \end{definition}
 
-We shall write $P_A^P=\zeta_A\inv(\{P\})$ for the set of $P$-positions in $A$ and $P_A^O=\zeta\inv(\{O\})$ for the set of $O$-positions in $A$.
+$\le$ is easily seen to be a preorder on strategies, and it follows that $\equiv$ is an equivalence relation.
 
-\subsection{Strategies}
+An immediate consequence of this definition is that if we have an equivalence in the earlier sense; i.e., an isomorphism between $X$ and $Y$ that commutes with the strategies $\sigma$ and $\tau$, then $\sigma\equiv\tau$.
 
-A nondeterministic \emph{strategy} for a game $A$ will be given by a pair $\sigma=(T_\sigma, D_\sigma)$, where
-\begin{itemize}
-  \item $T_\sigma$ is the set of \emph{traces} of the strategy; i.e., the set of $P$-positions that can occur when player $P$ plays according to the strategy.
-That is, $T_\sigma$ is a non-empty prefix-closed subset of $P_A^P$.
+\begin{proposition}
+  \label{compositionIsAssociative}
+  The composition we have defined is associative, up to the equivalence relation $\equiv$.  
+\end{proposition}
+\begin{proof}
+  The composition map $(\sigma,\tau,\upsilon)\mapsto (\sigma;\tau);\upsilon$ takes strategies $\sigma\from X\implies (A\implies B)$, $\tau\from Y\implies (B\implies C)$ and $\upsilon\implies (C\implies D)$ and gives us a strategy
+  \[
+    (\sigma;\tau);\upsilon\from (Z \tensor (Y\tensor X))\implies (A\implies D)
+    \]
 
-  \item $D_\sigma\subset T_\sigma$ denotes the set of \emph{divergences} in $T_\sigma$; that is, the set of those $O$-positions in $T_\sigma$ for which Player $P$ may elect to diverge rather than respond.
-Accordingly, $\zeta_A(s)=O$ for all $s\in D_\sigma$.
-If a trace has a divergent prefix, then it is divergent, so we shall follow Roscoe and insist that $D_\sigma$ be postfix-closed in $P_A^O$ (\cite{RoscoeCspInfinite}, cited in \cite{mcCHFiniteND}).
-\end{itemize}
+  This mode of composition thus gives rise to a \emph{uniform, history-free winning strategy} (see \cite[3.6]{abramskyjagadeesangames}) for the linear logic term
 
-\begin{definition}
-  Let $A=(M_A,\lambda_A,\zeta_A,P_A)$ be a game.  Then a (nondeterministic) \emph{strategy} for $A$ is a pair $\sigma=(T_\sigma,D_\sigma)$ such that
-  \begin{itemize}
-    \item $T_\sigma\subset P_A^P$.
-    \item $D_\sigma\subset P_A$ is a postfix-closed subset such that all of the minimal positions in $D_\sigma$ are replies to moves in $T_\sigma$ or limits of moves in $T_\sigma$.
-In other words, if $s\in D_\sigma$, then there is some $O$-position $t\prefix s$ such that $t\in D_\sigma$ and all $P$-prefixes of $t$ are contained in $T_\sigma$.
-  \end{itemize}
+  \begin{equation}
+    \label{compositionassociativesequent}
+    \begin{split}
+      &(((X\implies(A\implies B)) \tensor (Y \implies (B \implies C))) \tensor (Z \implies (C \implies D))) \implies\\
+      &\quad((Z \tensor (Y\tensor X)) \implies (A \implies D))
+    \end{split}
+  \end{equation}
 
-  $T_\sigma$ and $D_\sigma$ are required to satisfy the following totality axiom:
-  \begin{description}
-    \item[Diverge-or-reply] If $s\in T_\sigma$ and $sa\in P_A$ then either $sab\in T_\sigma$ for some $P$-move $b$ or $sa\in D_\sigma$.  
-  \end{description}
-
-  The diverge-or-reply rule tells us that a function must either return a value or go into an infinite loop, and corresponds to the absence of an error constant in our language.  
-\end{definition}
-
-We will need one extra condition on the definition of a strategy in order to make sure that the composition of two strategies satisfies the diverge-or-reply rule.
-
-\begin{definition}
-  We say a strategy $\sigma$ is \emph{compact} if $T_\sigma\cup D_\sigma$ satisfies the compactness criterion given above for games: if $s\in M_A^\omega$ is an infinite sequence such that $t\in T_\sigma$ for all finite $P$-prefixes $t\ppprefix s$, then $t\in T_\sigma$ or $t\in D_\sigma$.
-\end{definition}
-
-Compactness is too strong a condition for our purposes: we shall later see that it is not preserved by composition.  We shall use the following local version instead:
-
-\begin{definition}
-  We say a strategy $\sigma$ is \emph{locally compact} if whenever $s\in T_\sigma$ there is some compact strategy $\sigma'$ such that $s\in T_{\sigma'}\subset T_\sigma$ and $D_\sigma\subset D_{\sigma'}$.
-\end{definition}
-
-From now on, we shall use the word \emph{strategy} to mean \emph{locally compact strategy}.
-
-\subsection{Multiplicatives}
-
-Let $A,B$ be games.
-If $s\in \seqs{(M_A\cprd M_B)}$ then we write $s\vert_A$ for the subsequence of $s$ consisting of all moves from $A$ and $s\vert_B$ for the subsequence of $s$ consisting of all moves from $B$.
-We write $P_A\|P_B$ for the set of all such sequences $s$ such that $s\vert_A\in P_A$ and $s\vert_B\in P_B$.
-
-\begin{definition}
-  Let $A,B$ be games.
-Then the \emph{tensor product} of $A$ and $B$ is the game $A\tensor B=(M_{A\tensor B}, \lambda_{A\tensor B}, \zeta_{A\tensor B}, P_{A\tensor B})$ where we define $M_{A\tensor B}$, $\lambda_{A\tensor B}$, $\zeta_{A\tensor B}$, $P_{A\tensor B}$ as follows:
-  \begin{itemize}
-    \item $M_{A\tensor B} = M_A \cprd M_B$
-    \item $\lambda_{A\tensor B} = \lambda_A \cprd \lambda_B$
-    \item For $s\in P_A\|P_B$, $\zeta_{A\tensor B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B)$.
-    \item $P_{A\tensor B}$ is the set of all sequences $s\in P_A\|P_B$ such that $s$ satisfies the alternating condition with respect to $\zeta_{A\tensor B}$: i.e., for all $t,ta\prefix s$, $\zeta_{A\tensor B}(t) = \neg\zeta_{A\tensor B}(ta)$.
-  \end{itemize}
-\end{definition}
-
-\begin{definition}
-  Let $A,B$ be games.
-Then the \emph{linear implication} of $A$ and $B$ is the game $A\implies B=(M_{A\implies B}, \lambda_{A\implies B}, \zeta_{A\implies B}, P_{A\implies B})$ where we define $M_{A\implies B}$, $\lambda_{A\implies B}$, $\zeta_{A\implies B}$, $P_{A\implies B}$ as follows:
-  \begin{itemize}
-    \item $M_{A\implies B} = M_A \cprd M_B$
-    \item $\lambda_{A\implies B} = (\neg\circ\lambda_A) \cprd \lambda_B$
-    \item For $s\in P_A\|P_B$, $\zeta_{A\implies B}(s) = \zeta_A(s\vert_A) \wedge \zeta_B(s\vert_B)$.
-    \item $P_{A\implies B}$ is the set of all sequences $s\in P_A\|P_B$ such that $s$ satisfies the alternating condition with respect to $\zeta_{A\implies B}$.  
-  \end{itemize}
-\end{definition}
-
-We want to prove that these are well formed games.
-
-\begin{proposition}\label{TensorImpliesWellFormed}
-  If $A,B$ are games then $A\tensor B$ and $A\implies B$ are games.
-\end{proposition}
-
-First, we will prove a useful lemma.
-
-\begin{lemma}\label{signProfilesLemma}
-  Let $A,B$ be games.  Given a position $s\in P_A\|P_B$, we define the \emph{sign profile} of $s$ to be given by the signs of its two components:
+  Meanwhile, the composition $(\sigma,\tau,\upsilon)\mapsto\sigma;(\tau;\upsilon)$ returns a strategy
   \[
-    \begin{array}{cc|c}
-      \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \textrm{sign profile} \\
-      \hline
-      P & P & PP \\
-      O & P & OP \\
-      P & O & PO \\
-      O & O & OO
-    \end{array}
+    \sigma;(\tau;\upsilon)\from ((Z\tensor Y) \tensor X)\implies (A\implies D)
     \]
-  If $s\in P_{A\tensor B}$ is a finite position, then $s$ cannot have sign profile $OO$.  If $s\in P_{A\implies B}$ is a finite position then $s$ cannot have sign profile $OP$.  
-  \begin{proof}
-    By negativity, the empty sequence $\epsilon$ always has sign profile $PP$.
-Otherwise, $s=s'a$ for some sequence $s'$ and some move $a$.
-If $s\in P_{A\tensor B}$ and $s$ has sign profile $OO$, then $s$ is an $O$-position in $A\tensor B$.
-Therefore, $s'$ is a $P$-position in $A\tensor B$ and so $s'$ must have sign profile $PP$, by the definition of $\zeta_{A\tensor B}$.
-But this is impossible, as the move $a$ can only change the sign profile in one of the two components.
-
-    The proof for the linear implication is entirely similar.
-  \end{proof}
-\end{lemma}
-
-\begin{proof}[Proof of Proposition \ref{TensorImpliesWellFormed}]
-  Alternation is part of the definition and negativity is implied by the equations $P\wedge P = P$ and $P\Rightarrow P = P$.
-The only tricky part is proving consistency of the $\lambda$ and $\zeta$ functions.
-Since consistency applies only to positions with a last move, we may ignore the infinite plays in $A$ and $B$.
-
-  Suppose $sa\in P_{A\tensor B}$.
-We wish to show that $\zeta_{A}(sa)=\lambda_A(a)$.
-In the presence of alternation, this is equivalent to showing that $\zeta_A(s) = \neg \lambda_A(a)$.
-We show this by cases on the sign profile of $s$.
-By Lemma \ref{signProfilesLemma}, $s$ has sign profile $PP$, $OP$ or $PO$.
-If $s$ has sign profile $PP$ then $s$ is a $P$-position.
-Since $s\vert_A$ and $s\vert_B$ are both $P$-positions, $a$ must be an $O$-move, whether it occurs in $A$ or $B$.
-
-  If instead $s$ has sign profile $OP$ or $PO$, then $s$ is an $O$-position.
-By alternation, $sa$ must be a $P$-position, so it must have sign profile $PP$.
-By consistency and alternation for the games $A,B$, the move $a$ must be a $P$-move.
-
-  For compactness, suppose that $s\in M_{A\tensor B}^\omega$ is an infinite sequence of moves such that $t\in P_{A\tensor B}$ for all finite prefixes $t\ppprefix s$.
-Then $s$ is certainly alternating.
-Moreover, for all finite prefixes $t\ppprefix s\vert_A$, we have $t\in P_A$, and so therefore $s\vert_A\in P_A$ by compactness for $A$.
-Similarly, $s\vert_B\in P_B$, and therefore, $s\in P_{A\tensor B}$.
-
-  The proof for the linear implication is similar.
+  Composing this on the left with the isomorphism $\assoc_{Z,Y,X}$ then gives us a strategy for the game
+  \[
+    (Z \tensor (Y \tensor X))\implies (A\implies D),
+    \]
+  so inducing another uniform history-free winning strategy on the term \eqref{compositionassociativesequent}.  
+  By \cite[Theorem 1]{abramskyjagadeesangames}, any uniform, history-free winning strategy for a term is the denotation of some proof net for that term.  
+  Since the term \eqref{compositionassociativesequent} has exactly two occurrences of each atom, it admits at most one proof net and therefore we deduce that the two uniform, history-free winning strategies on \eqref{compositionassociativesequent} are equal.
+  It follows that we have a commutative triangle in the original category of games:
+  \[
+    \begin{tikzcd}
+      Z \tensor (Y \tensor X) \arrow[r, "(\sigma;\tau);\upsilon"] \arrow[d, "\assoc_{Z,Y,X}"']
+        & A \implies D \\
+      (Z \tensor Y) \tensor X \arrow[ur, "\sigma;(\tau;\upsilon)"']
+        &
+    \end{tikzcd}
+    \]
+  and therefore that $(\sigma;\tau);\upsilon\equiv\sigma;(\tau;\upsilon)$.
 \end{proof}
 
-Looking at the proof above, we may deduce the following important fact:
+As we remarked, two strategies $(X,\sigma)$ and $(Y,\tau)$ for a game $A$ may be equivalent even if the games $X$ and $Y$ are not isomorphic.
 
 \begin{proposition}
-  In the tensor product $A\tensor B$, only player $O$ may switch games.  In the linear implication $A\implies B$, only player $P$ may switch games.
+  Let $X,Y,A$ be games and let $\sigma$ be a strategy for $X\implies A$.  
+  Then the strategies $(X,\sigma)$ and $(X\times Y, \pr_1;\sigma)$ are equivalent.
 \end{proposition}
+\begin{proof}
+  Clearly the following diagram commutes:
+  \[
+    \begin{tikzcd}
+      X \arrow[r, "\sigma"]
+        & A \\
+      X \times Y \arrow[u, "\pr_1"] \arrow[ur, "\pr_1;\sigma"']
+        &
+    \end{tikzcd}
+    \]
+  and so $\sigma\le\pr_1;\sigma$.
 
-\subsection{Composition of Strategies}
-
-Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We shall construct a strategy $\comp\tau\sigma$ for $A\implies C$.
-
-In order to define $T_{\comp\tau\sigma}$, we first define the set $\sigma\|\tau$, given by:
+  In the other direction, we have a retraction $\rho_1\from X\implies X\times Y$ in which the Proponent immediately gives up if the Opponent starts with a move in $Y$.  
+  The strategy $\rho_1$ is total with respect to moves in $X$ on the left.  
+  Moreover, it satisfies $\rho_1;\pr_1=\id_X$ and so the following triangle commutes:
   \[
-  \sigma\|\tau = \left\{\s\in\seqs{(M_A\cprd M_B\cprd M_C)}\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\right\}
+    \begin{tikzcd}
+      X\times Y \arrow[r, "\pr_1;\sigma"]
+        & A \\
+      X \arrow[u, "\rho_1"] \arrow[ur, "\sigma"']
+        &
+    \end{tikzcd}
     \]
-We then define
-\[
-  T_{\comp\tau\sigma} = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}
-  \]
-We need to prove that $T_{\comp\tau\sigma}\subset P_{A\implies B}$.
-$\comp\tau\sigma$ is clearly prefix closed, and transitivity of $\Rightarrow$ proves that all positions in $T_{\comp\tau\sigma}$ are $P$-positions, so we need to show that every finite position in $T_{\comp\tau\sigma}$ has even length.
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Suppose $s\in\comp\tau\sigma$ is finite.  Then $s$ has even length.
-  \begin{proof}
-    Write $s=\s\vert_{A,C}$, where $\s\in\sigma\|\tau$.  Then we have
-    \begin{align*}
-      \length(s) & = \length(\s) - \length(\s\vert_B) \\
-       & = \length(\s\vert_{A,B}) + \length(\s\vert_{B,C} - 2\length(\s\vert_B)
-    \end{align*}
-    $\s\vert_{A,B}$ and $\s\vert_{B,C}$ both have even length, since they are $P$-positions, so the result follows.
+  And therefore $\pr_1;\sigma\le\sigma$.
 \end{proof}
-\end{proposition}
-
-Before we consider the definition of $D_{\comp\tau\sigma}$, we show that composition is associative at the level of trace sets.
-
-\begin{proposition}\label{traceAssociativity}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$, let $\tau$ be a strategy for $B\implies C$ and let $\upsilon$ be a strategy for $C\implies D$.  Then
-  \[
-    T_{\comp{\upsilon}{(\comp\tau\sigma)}} = T_{\comp{(\comp\upsilon\tau)}{\sigma}}
-    \]
-
-  \begin{proof}
-    As in \cite{abramskyjagadeesangames}.  Define
-    \[
-      \sigma\|\tau\|\upsilon = \left\{\s\in\seqs{(M_A \cprd M_B \cprd M_C \cprd M_D)} \suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau,\;\s\vert_{C,D}\in\upsilon\right\}
-      \]
-    We shall show that 
-    \[
-      T_{\comp{\upsilon}{(\comp{\tau}{\sigma})}} = \{\s\vert_{A,D}\suchthat\s\in\sigma\|\tau\|\upsilon\}
-      \]
-    The same claim will follow for $T_{\comp{(\comp{\upsilon}{\tau})}{\sigma}}$ by symmetry, completing the proof.
-
-    Let $\s\in\sigma\|\tau\|\upsilon$.
-Then $\s\vert_{A,B,C}\in\sigma\|\tau$ and so $\s\vert_{A,C}\in\comp\tau\sigma$.
-Now we see that $\s\vert_{A,C,D}\in (\comp\tau\sigma)\|\upsilon$ and so $\s\vert_{A,D}\in\comp{\upsilon}{(\comp\tau\sigma)}$.
-We have shown that
-    \[
-      \{\s\vert_{A,D}\suchthat\s\in\sigma\|\tau\|\upsilon\} \subset T_{\comp{\upsilon}{(\comp{\tau}{\sigma})}}
-      \]
-    To show the reverse inclusion, suppose that $s\in\comp{\upsilon}{(\comp\tau\sigma)}$.
-Let $\s\in(\comp\tau\sigma)\|\upsilon$ be such that $\s\vert_{A,D}=s$ and let $\t\in\sigma\|\tau$ be such that $\t\vert_{A,C}=\s\vert_{A,C}$.
-Our goal is to interleave the sequences $\s$ and $\t$ in order to give rise to a sequence $\u\in\sigma\|\tau\|\upsilon$ such that $\u\vert_{A,D}=s$.
-
-    Note that since $\s\vert_{A,C}=\t\vert_{A,C}$, we may decompose $\s$ and $\t$ into blocks:
-    \begin{gather*}
-      \s = \s_0D_0\s_1D_1\dots\\
-      \t = \s_0B_0\s_1B_1\dots
-    \end{gather*}
-    where $\s_1,\s_2,\dots$ are sequences of moves from either $A$ or $C$, $B_0,B_1\dots$ are (possibly empty) sequences of moves from $B$ and $D_0,D_1,\dots$ are (possibly empty) sequences of moves from $D$.
-
-    We then form the sequence $\u$ as:
-    \[
-      \u = \s_0B_0D_0\s_1B_1D_1\dots
-      \]
-    It might look as if we have made an arbitrary choice in placing the $B_i$ before the $D_i$, but in fact it turns out that there is no choice to make: an examination of sign profiles, for example, will show that $B_i$ is non-empty only if $D_i$ is empty and vice versa: if $\s_i$ can be followed by a move from $B$ then it cannot be followed by a move from $D$.
-
-    In any case, we have
-    \begin{gather*}
-      \u\vert_{A,C,D} = \s_0D_0\s_1D_1\dots = \s \\
-      \u\vert_{A,B,C} = \s_0B_0\s_1B_1\dots = \t
-    \end{gather*}
-    It follows that $\u\in\sigma\|\tau\|\upsilon$: 
-    \begin{gather*}
-      \u\vert_{A,B} = \t\vert_{A,B} \in \sigma \\
-      \u\vert_{B,C} = \t\vert_{B,C} \in \tau \\
-      \u\vert_{C,D} = \s\vert_{C,D} \in \upsilon
-    \end{gather*}
-    Lastly, we have $\u\vert_{A,D} = \s\vert_{A,D} = s$, completing the proof.
-  \end{proof}
-\end{proposition}
-
-At the moment, we have an associative composition at the level of trace sets.  We now define composition at the level of divergences.
-
-Given a game $A$ and a subset $S\subset P_A$, we write $\pocl_A(S)$ for the postfix closure of $S$ in $P_A$; i.e.:
-\[
-  \pocl_A(S) = \{s\in P_A\suchthat t\prefix s\textrm{ for some $t\in S$}\}
-  \]
-We write $\pocl_A^P(S)$ for $\pocl_A(S)\cap P_A^P$ and $\pocl_A^O(S)$ for $\pocl_A(S)\cap P_A^O$.
-
-\begin{definition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  We define the divergences of $\comp\tau\sigma$ as follows: first we define
-  \[
-    \sigma\dv\tau = \left\{\s\in\seqs{(M_A\cprd M_B\cprd M_C)}\;\middle|\; \mbox{\pbox{\textwidth}{\flushRight either $\s\vert_{A,B}\in D_\sigma$ and $s\vert_{B,C}\in T_\tau$ \\ or $\s\vert_{A,B}\in T_\sigma$ and $s\vert_{B,C}\in D_\tau$}}\right\}
-    \]
-  \[
-    D_{\comp\tau\sigma} = \pocl_{A\implies C}^O\left(\{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}\right)
-    \]
-\end{definition}
-
-\begin{proposition}
-  $D_{\comp\tau\sigma}$ is a well-defined divergence set.
-  \begin{proof}
-    $D_{\comp\tau\sigma}$ alternating by the same argument we used for $T_{\comp\tau\sigma}$, and is postfix-closed in $P_{A\implies C}^O$ by definition.
-Now let $s\in D_{\comp\tau\sigma}$ and suppose that $\s\vert_{A,C}\prefix s$, where $\s\in \sigma\dv\tau$.
-We need to show that there is some $O$-position $ta\prefix s$ such that $ta\in D_{\comp\tau\sigma}$ and $t\in T_{\comp\tau\sigma}$.
-
-    Suppose first that $\s\vert_{A,B}\in D_\sigma$ and $\s\vert_{B,C}\in T_\tau$.
-Then there is some $O$-position $r\prefix \s\vert_{A,B}$ such that $r\in D_\sigma$ and $q\in T_\sigma$ for all $P$-prefixes $q\prefix r$.
-Let $\t\prefix\s$ be some prefix such that $\t\vert_{A,B}=r$.
-Then $\t\in\sigma\dv\tau$ and so if we set $t=\t\vert_{A,C}$, we get that $t\in D_{\comp\tau\sigma}$.
-If $u$ is a $P$-prefix of $t$, then there is some prefix $\u$ of $\t$ such that $\u\vert_{A,C}=u$.
-Then $\u\vert_{A,B}$ is a $P$-position by examination of sign profiles and so $\u\vert_{A,B}\in T_\sigma$.
-It follows that $u\in T_{\comp\tau\sigma}$.
-
-    The case where $\s\vert_{A,B}\in T_\sigma$ and $\s\vert_{B,C}\in D_\tau$ is similar.
-  \end{proof}
-\end{proposition}
-
-We need to show that this composition satisfies the diverge-or-reply and local compactness rules.
-
-In order to prove that the composition of locally compact strategies is locally compact, we are going to need some facts about deterministic strategies.
-
-\begin{definition}
-  We say a strategy $\sigma$ is \emph{deterministic} if whenever $s\in\sigma$ is an $O$-position and $a,b$ are moves such that $sa,sb\in\sigma$, then $a=b$.
-\end{definition}
-
-Deterministic strategies have the following nice technical property:
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a deterministic strategy for $A\implies B$ and let $\tau$ be a deterministic strategy for $B\implies C$.
-Then $\comp\tau\sigma$ is a deterministic strategy.
-Moreover, for any $s\in\comp\tau\sigma$, there is a unique minimal $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-  \begin{proof}
-    The idea behind the proof is that determinism of $\sigma$ and $\tau$ mean that the play in the intermediate game $B$ is completely determined (since every move played in $B$ is either a $P$-move in $A\implies B$ or a $P$-move in $B\implies C$.
-For full details, see \cite{abramskyjagadeesangames}.
-  \end{proof}
-\end{proposition}
-
-We can use this to prove the following:
-
-\begin{proposition}
-  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be compact deterministic strategies.  Then $\comp\tau\sigma$ is compact.
-  \begin{proof}
-    Let $s\in M_{A\implies C}^\omega$ be an infinite sequence such that $t\in\comp\tau\sigma$ for all finite prefixes $t\ppprefix s$.
-For each finite prefix $t$ of $s$, there is a unique minimal sequence $\t\in\sigma\|\tau$ such that $\t\vert_{A,C}=t$.
-Writing $s$ as the limit of its finite $P$-prefixes
-    \[
-      t_1 \prefix t_2 \prefix t_3 \prefix \dots
-      \]
-    we build up a sequence
-    \[
-      \t_1 \prefix \t_2 \prefix \t_3 \prefix \dots
-      \]
-    where $\t_i$ is the unique minimal sequence in $\sigma\|\tau$ such that $\t_i\vert_{A,C}=t_i$.
-We have $\t_i\prefix\t_{i+1}$ because if we remove the last move from $\t_{i+1}$ then the resulting sequence $\u_i$ satisfies $\u_i\vert_{A,C}=t_i$ and therefore $\t_i\prefix\u_i\prefix\t_{i+1}$ by minimality of $\t_i$.
-
-    Then the limit of the sequences $\t_i\vert_{A,B}$ must be contained in $T_\sigma\cup D_\sigma$, since $\sigma$ is compact, and similarly the limit of the sequences $\t_i\vert_{B,C}$ must be contained in $T_\tau\cup D_\tau$, since $\tau$ is compact.
-It follows that the limit $\t$ of the sequences $\t_i$ is contained in $\sigma\|\tau\cup\sigma\dv\tau$, and therefore that $\t\vert_{A,C}=s\in T_{\comp\tau\sigma}\cup D_{\comp\tau\sigma}$.
-  \end{proof}
-\end{proposition}
-
-Note that the composition of compact nondeterministic strategies need not be compact.
-
-\begin{example}
-  Let the games $I$ and $\st$ be defined as before, and let the game $\Sigma$ be the game with a unique opponent starting move and a unique player reply:
-  \[
-    \Sigma = (\{q,a\}, \{q\mapsto o, a\mapsto p\}, \{\epsilon\mapsto p,q\mapsto o,qa\mapsto p\}, \{\epsilon, q, qa\}\}
-    \]
-  Let $\bN$ be the game where the opponent asks the player to choose a natural number:
-  \[
-    \bN = \left(\{q\} \cup \bN, \{q\mapsto O, n\mapsto P\}, \{\epsilon\mapsto P,q\mapsto O,qn\mapsto P\}, \{\epsilon, q\} \cup \{qn\suchthat n\in\bN\}\right)
-    \]
-  We have a (deterministic) strategy $\sigma$ for $\bN\implies (\st\implies\Sigma)$ in which the player asks the opponent for a number $n$ and then calls the argument of $\st$ $n$ times before returning.
-For example, a play in $\sigma$ might look like this:
-  \[
-    \begin{array}{ccc}
-      \bN & \st & \Sigma \\
-      & & q \\
-      q & & \\
-      2 & & \\
-      & q & \\
-      & a & \\
-      & q & \\
-      & a & \\
-      & & a
-    \end{array}
-    \]
-  $\sigma$ is compact because there are no infinite chains of positions; indeed, the length of a play in $\sigma$ is already determined by the third move.
-
-  We have a nondeterministic strategy $?$ for $\bN\cong I\implies\bN$ where the player nondeterministically chooses any number - so $?
-= P_{\bN}^P$ as sets of positions.
-$?$ is compact because all plays in $?$ have length at most $2$.
-
-  When we compose these strategies, the resulting strategy $\comp\sigma?$ contains the infinite chain of positions $qq,qqaq,qqaqaq,qqaqaqaq,\dots$, but does not contain any limiting plays.
-So it is not compact.
-It is, however, locally compact, since it is the union of compact strategies $\sigma_n$, where $\sigma_n$ has the unique maximal play
-  \[
-    q\underbrace{qa\dots qa}_{\textrm{$n$ times}}a
-    \]
-\end{example}
-
-\begin{proposition}
-  Let $A,B,C$ be games and let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be (nondeterministic, locally compact) strategies.  Then $\comp\tau\sigma$ is locally compact.
-  \begin{proof}
-    Let $s\in T_{\comp\tau\sigma}$.
-Then there is some sequence $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-We have $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, so, by local compactness for $\sigma$ and $\tau$, there are compact strategies $\sigma'\from A\implies B$ and $\tau'\from B\implies C$ such that $\s\vert_{A,B}\in\sigma'$ and $\s\vert_{B,C}\in\tau'$.
-After removing positions from (and possibly adding divergences to) $\sigma'$ and $\tau'$, we may assume that they are deterministic (and still compact).
-Then $\comp{\tau'}{\sigma'}$ is compact and we have $\s\vert_{A,C}\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$ and $D_{\comp\tau\sigma}\subset D_{\comp{\tau'}{\sigma'}}$.
-  \end{proof}
-\end{proposition}
-
-Unlike \cite{mcCHFiniteND}, we do not need to change the definition of $D_{\comp\tau\sigma}$ to reflect divergence arising from infinite chattering.
-The following example shows that it arises naturally from existing definition of $D_{\comp\tau\sigma}$.
-
-\begin{example}[Infinite chattering]
-  Let $\st$ denote the game where each player has exactly one move available in every position and the resulting infinite position is a $P$-position:
-  \[
-    \st = (\{q, a\}, \{q\mapsto O, a\mapsto P\}, \{\epsilon\mapsto P,sq\mapsto O,sa\mapsto P,qaqa\dots\mapsto P\}, \{s\prefix qaqa\dots\})
-    \]
-  Let $I$ denote the empty game with no moves, and let $\bot$ denote the game with a single opponent move and no player reply:
-  \begin{gather*}
-    I = (\emptyset, \emptyset, \{\epsilon\mapsto P\}, \{\epsilon\}) \\
-    \bot = (\{*\}, \{*\mapsto O\}, \{\epsilon\mapsto P, *\mapsto O\}, \{\epsilon, *\})
-  \end{gather*}
-  There are natural strategies $\sigma$ for $I\implies\st$ and $\tau$ for $\st\implies\bot$ given at the level of traces by:
-  \begin{gather*}
-    \sigma = \{s \prefix^P qaqa\dots\} \\
-    \tau = \{s \prefix^P *qaqa\dots\}
-  \end{gather*}
-  Player $P$ always has a reply to an $O$-position in $\sigma$, and we set $D_\sigma = \emptyset$.
-In $\tau$, the infinite sequence $*qaqa\dots$ satisfies $\zeta_{\st}(*qaqa\dots\vert_{\st}) = \zeta_{\st}(qaqa\dots) = P$ and $\zeta_{\bot}(*qaqa\dots\vert_{\bot}) = \zeta_{\bot}(*) = O$ and so it is an $O$-position.
-We set
-  \[
-    D_\tau = \{*qaqa\dots\}
-    \]
-  Now, when we compose the strategies $\sigma$ and $\tau$, at the level of traces we have
-  \[
-    \comp\tau\sigma = \{\epsilon, *\}
-    \]
-  The sequence $*$ is the restriction to $I,\bot$ of the infinite sequence
-  \[
-    *qaqa\dots \in \sigma\|\tau
-    \]
-  We now have that $*qaqa\dots\vert_{\st,\bot}\in D_\tau$ and therefore the sequence $*\in\comp\tau\sigma$ must be designated divergent.  We have
-  \[
-    D_{\comp\tau\sigma} = \{*\}
-    \]
-  as desired.
-
-  Note that if we modify the definition of $\st$ so that the infinite position is an $O$-position, then we still get a divergence -- this time, because the sequence $*qaqa\dots\vert_{I,\sigma^*}$ must be contained in $D_\sigma$.
-If we leave out the infinite position from $\sigma$ or $\tau$ altogether, then that strategy is no longer locally compact, so it is not a valid strategy according to our definition.
-\end{example}
-
-This example is at the heart of the proof that the composition of strategies satisfies the diverge-or-reply rule.  This is the point at which we need local compactness.
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  Then $T_{\comp\tau\sigma}, D_{\comp\tau\sigma}$ satisfy the diverge-or-reply rule.
-
-  \begin{proof}
-    Suppose that $s\in\comp\tau\sigma$, that $sa\in P_{A\implies C}$ and that $s\not\in D_{\comp\tau\sigma}$.
-Let $\s\in\sigma\|\tau$ be such that $\s\vert_{A,C}=s$.
-By local compactness of $\sigma$ and $\tau$, there must be compact strategies $\sigma'\from A\implies B$ and $\tau'\from B\implies C$ such that $\s\vert_{A,C}\in\sigma'$ and $\s\vert_{B,C}\in\tau'$.
-
-    Let $\s'\in\sigma'\|\tau'$ be maximal such that $\s'a\vert_{A,C}=sa$.
-We know that such a maximal sequence must exist: if $\s_i$ are a chain of sequences from $\sigma'\|\tau'$ such that $\s_ia\vert_{A,C}=sa$ then their limit $\s$ (which is contained in $\sigma'\|\tau'$ by compactness of $\sigma'$ and $\tau'$) must satisfy $\s a\vert_{A,C}=s a$.
-Since $sa\not\in D_{\comp\tau\sigma}$, we must have $\s a\vert_{A,B}\not\in D_\sigma\subset D_{\sigma'}$ and $\s a\vert_{B,C}\not\in D_\tau\subset D_{\tau'}$.
-
-    Since $sa$ is an $O$-position, one of $\s a\vert_{A,B}$ and $\s a\vert_{B,C}$ must be an $O$-position (by transitivity of $\Rightarrow$).
-Suppose without loss of generality that $\s a\vert_{A,B}$ is an $O$-position.
-Since $\s a\vert_{A,B}\not\in D_{\sigma'}$, there must be some move $b$ such that $\s a\vert_{A,B}b\in\sigma'$, since $\sigma'$ satisfies the diverge-or-reply rule.
-Then we have $\s ab\vert_{A,B}\in\sigma'$.
-Moreover, Lemma \ref{signProfilesLemma} tells us that $\s a\vert_{B,C}$ must be a $P$-position, so $\s ab\vert_{B,C}=\s\vert_{B,C}\in\tau'$.
-Therefore, $\s ab\in\sigma'\|\tau'$.
-By maximality of $\s a$, $b$ must be a move in $A$ and therefore we have $sab\in\comp{\tau'}{\sigma'}\subset\comp\tau\sigma$.
-  \end{proof}
-\end{proposition}
-
-We now have a working definition of composition.  It remains to prove that it is associative at the level of divergences:
-
-\begin{proposition}
-  Let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$, let $\tau$ be a strategy for $B\implies C$ and let $\upsilon$ be a strategy for $C\implies D$.  Then 
-  \[
-    D_{\comp\upsilon{(\comp\tau\sigma)}} = D_{\comp{(\comp\upsilon\tau)}\sigma}
-    \]
-  \begin{proof}
-    Let
-    \[
-      D = \left\{\s\in \seqs{(M_A \cprd M_B \cprd M_C \cprd M_D)} \;\middle|\;\mbox{\pbox{\textwidth}{\flushRight
-        either \textbf{1} $\s\vert_{A,B}\in D_\sigma$, $\s\vert_{B,C}\in T_\tau$ and $\s\vert_{C,D}\in T_\upsilon$ \\
-        or \textbf{2} $\s\vert_{A,B}\in T_\sigma$, $\s\vert_{B,C}\in D_\tau$ and $\s\vert_{C,D}\in T_\upsilon$ \\
-        or \textbf{3} $\s\vert_{A,B}\in T_\sigma$, $\s\vert_{B,C}\in T_\tau$ and $\s\vert_{C,D}\in D_\upsilon$
-      }}\right\}
-      \]
-    We claim that $D_{\comp\upsilon{(\comp\tau\sigma)}}=\pocl_{A\implies D}^O\left(\{\s\vert_{A,D}\suchthat\s\in D\}\right)$.
-The same claim will hold for $D_{\comp{(\comp\upsilon\tau)}\sigma}$ by symmetry, completing the proof.
-
-    Let $\s\in D$.
-In cases \textbf{1} and \textbf{2}, we must have $\s\vert_{A,C}\in D_{\comp\tau\sigma}$ and $\s\vert_{C,D}\in T_\upsilon$.
-In case \textbf{3}, we have $\s\vert_{C,D}\in D_\upsilon$ and $\s\vert_{A,C}\in T_{\comp\tau\sigma}$.
-In either case, we must have $\s\vert_{A,D}\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.
-
-    Conversely, suppose that $s\in D_{\comp\upsilon{(\comp\tau\sigma)}}$.  Then there must be some $\t\in \seqs{(M_A\cprd M_C\cprd M_D)}$ such that $\t\vert_{A,D}\prefix s$ and either
-    \[
-      \t\vert_{A,C}\in D_{\comp\tau\sigma}\textrm{ and }\t\vert_{C,D}\in T_\upsilon
-      \]
-    or
-    \[
-      \t\vert_{A,C}\in T_{\comp\tau\sigma}\textrm{ and }\t\vert_{C,D}\in D_\upsilon
-      \]
-    In the first case, we then get a sequence $\u\in \seqs{(M_A\cprd M_B \cprd M_C)}$ such that $\u\vert_{A,C}\prefix\t\vert_{A,C}$ and either
-    \[
-      \u\vert_{A,B}\in D_\sigma\textrm{ and }\u\vert_{B,C}\in T_\tau
-      \]
-    or
-    \[
-      \u\vert_{A,B}\in T_\sigma\textrm{ and }\u\vert_{B,C}\in D_\tau
-      \]
-    By passing to a suitable prefix of $\t$, we may assume that $\u\vert_{A,C}=\t\vert_{A,C}$ (since $T_\upsilon$ is prefix-closed).
-
-    In the second case, we get a sequence $\u\in\sigma\|\tau$ such that $\u\vert_{A,C}=\t\vert_{A,C}$.
-
-    By the argument from Proposition \ref{traceAssociativity}, we may interleave these two sequences $\t$ and $u$ to form a sequence $\s\in\seqs{(M_A\cprd M_B\cprd M_C\cprd M_D)}$ such that $\s\vert_{A,B,C}=\u$ and $\s\vert_{A,C,D}=\t$.
-Then it is clear that $\s\in D$ in all cases and we have $\s\vert_{A,D}=\t\vert_{A,D}\prefix s$.
-  \end{proof}
-\end{proposition}
-
-In order to show that we have a category, it remains to define the identity morphisms.  These are given by the usual copycat strategies:
-\[
-  \id_A = \{s\in P_{A_1\implies A_2}^P\suchthat\textrm{for all even length $t\prefix s$, $t\vert_{A_1}=t\vert_{A_2}$}\}
-  \]
-(Here, we consider infinite positions to have even length).
-
-The divergence set $D_{\id_A}$ is empty: note that infinite positions in $\id_A$ are always $P$-positions.
-
-\begin{theorem}
-  There is a category $\G$ where the objects are games as defined above, morphisms from a game $A$ to a game $B$ are given by nondeterministic strategies $(T_\sigma, D_\sigma)$ for $A\implies B$ and the composition and identity morphisms are as defined above.
-  \begin{proof}
-    All that is left to do is to show that $\id_A$ really is an identity morphism.
-We shall show that if $A$ and $B$ are games and $\sigma$ is a strategy for $A\implies B$ then $\comp\sigma{\id_A}=\sigma$; it will follow by a symmetrical argument that $\comp{\id_B}\sigma = \sigma$.
-
-    We first show that $T_{\comp\sigma{\id_A}}=T_\sigma$.
-If $s\in\comp\sigma{\id_A}$, then there is some sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=s$.
-Since $\s\vert_{A_1,B}$ is a $P$-position, it must have sign profile $PPP$ or $OOO$ by Lemma \ref{signProfilesLemma}, and therefore $\s\vert_{A_1,A_2}$ is a $P$-position, so has even length.
-Therefore, $\s\vert_{A_1}=\s\vert_{A_2}$ and so $s=\s\vert_{A_1,B}=\s\vert_{A_2,B}\in\sigma$.
-
-    Conversely, suppose that $s\in\sigma$.
-There is an obvious sequence $s^2\in\id_A$, given by copying the moves of $s\vert_A$ between copies of $A$, such that $s^2\vert_{A_1}=s^2\vert_{A_2}=s\vert_A$.
-Then $s^2\vert_{A_2}=s\vert_{A_2}$, and so the sequences $s^2$ and $s$ may be interleaved as in the proof of Proposition \ref{traceAssociativity} to yield a sequence $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,B}=\s\vert_{A_2,B}=s$.
-
-    Now we show that $D_{\comp\sigma{\id_A}}=D_\sigma$.
-Suppose $s\in D_{\comp\sigma{\id_A}}$.
-Since $D_{\id_A}=\emptyset$, there is a sequence $\s\in\seqs{(M_{A_1}\cprd M_{A_2}\cprd M_B)}$ such that $\s\vert_{A_1,B}\prefix s$, $\s\vert_{A_1,B_1}\in\id_A$ and $\s\vert_{A_2,B}\in D_\sigma$.
-In particular, $\s\vert_{A_2,B}$ is an $O$-position in $A\implies B$ and so $\s\vert_{A_2}$ is a $P$-position in $A$.
-It follows by Lemma \ref{signProfilesLemma} that $\s\vert_{A_1,A_2}$ is a $P$-position in $A\implies A$; hence, it is even-length and so $\s\vert_{A_1}=\s\vert_{A_2}$.
-Therefore, $\s\vert_{A_1,B}=\s\vert_{A_2,B}\in D_\sigma$, so $s\in D_\sigma$, since $D_\sigma$ is postfix-closed.
-It follows that, $D_{\comp\sigma{\id_A}}\subset D_\sigma$.
-
-    Conversely, suppose that $s\in D_\sigma$.
-We know already that there is some $\s\in\id_A\|\sigma$ such that $\s\vert_{A_1,A_2}\in\id_A$ and $\s\vert_{A_2,B}\in\sigma$.
-Then $\s\vert_{A,C}\in D_{\comp\sigma{\id_A}}$ by definition.
-  \end{proof}
-\end{theorem}
 
@@
 
-We make the category $\G$ into a symmetric monoidal closed category with tensor product given by $\tensor$ and linear implication given by $\implies$.
-At the level of morphisms, the action of $\blank\tensor\blank$ is defined as follows: if $A,B,C,D$ are games, $\sigma$ is a strategy for $A\implies C$ and $\tau$ is a strategy for $B\implies D$, then $\sigma\tensor\tau$ is the strategy for $(A\tensor B)\implies (C\tensor D)$ given by playing the strategy $\sigma$ in $A$ and $C$ and playing the strategy $\tau$ in $B$ and $D$:
+As usual, our category has a monoidal structure induced by the tensor product $\_\tensor\_$.  
+Given strategies $(X,\sigma)$ for $A$ and $(Y,\tau)$ for $B$, we may form the strategy
 \[
-  \sigma\tensor\tau = \left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\suchthat s\vert_{A,C}\in\sigma,\;s\vert_{B,C}\in\tau\right\}
+  (X\tensor Y, \sigma\tensor\tau)
   \]
-The divergences for $\sigma\tensor\tau$ are defined using the divergences for $\sigma$ and $\tau$:
+Functoriality of this construction, up to the equivalence relation $\equiv$, is proved using a similar argument to that used in Proposition \ref{compositionIsAssociative}.
+
+The associators, unitors and braiding are all given by the usual strategies, with the tensor unit $I$ on the left.  
+For example, the associator for games $A,B,C$ is given by the strategy
 \[
-  D_{\sigma\tensor\tau} = \pocl^O\left(\left\{s\in P_{(A\tensor B)\implies (C\tensor D)}\;\middle|\;\mbox{\pbox{\textwidth}{\flushRight
-    either $s\vert_{A,C}\in D_\sigma$ and $s\vert_{B,D}\in T_\tau$ \\
-    or $s\vert_{A,C}\in T_\sigma$ and $s\vert_{B,D}\in D_\tau$
-    }}\right\}\right)
+  \assoc_{A,B,C}\from I \implies (((A\tensor B)\tensor C) \implies (A \tensor(B\tensor C)))
   \]
-\begin{proposition}
-  $\sigma\tensor\tau$ is a valid strategy for $(A\tensor B)\implies (C\tensor D)$
-  \begin{proof}
-    $\sigma\tensor\tau$ is non-empty and prefix-closed, since $\sigma$ and $\tau$ are.
+induced by the usual associator and the monoidal closed structure of the original category.  
+The commutativity of the pentagon diagram, hexagon diagram and so on can all be deduced from the result \cite[Theorem 1]{abramskyjagadeesangames} of Abramsky and Jagadeesan, as above.
 
-    $D_{\sigma\tensor\tau}$ is postfix-closed by definition.
-If $s\in D_{\sigma\tensor\tau}$, we need to find some prefix $t\prefix s$ such that $t\in D_{\sigma\tensor\tau}$ and $u\in T_{\sigma\tensor\tau}$ for all $P$-prefixes $u\prefix t$.
-By definition, we know there is some $s'\prefix s$ such that either $s'\vert_{A,C}\in D_\sigma$ and $s'\vert_{B,D}\in T_\tau$ or $s'\vert_{A,C}\in T_\sigma$ and $s'\vert_{B,D}\in D_\tau$.
-In the first case, we know that there is some $r\prefix s'\vert_{A,C}$ such that $r\in D_\sigma$ and $q\in T_\sigma$ for all $P$-prefixes $q\prefix r$; passing to an appropriate prefix $s''$ of $s'$, we get that $s''\vert_{A,C}=r$ and $s''\vert_{B,D}\in T_\tau$.
-Therefore, $s''\in D_{\sigma\tensor\tau}$ and $t''\in T_{\sigma\tensor\tau}$ for all $P$-positions $t''\prefix s''$.
-Moreover, $s''$ is an $O$-position, since $s''\vert_{A,C}$ is, and the claim follows since $s''\prefix s'\prefix s$.
-The proof in the other case is similar.
+The natural transformation $(C\tensor B)\implies A \cong C\implies (B\implies A)$ gives rise, by composition with the functor $X\implies\_$, to a natural transformation $X\implies ((C\tensor B) \implies A) \cong X\implies (C\implies (B\implies A))$ and thence to a natural transformation between the functors $\G^{eo}(C\tensor B,A)\cong \G^{eo}(C,B\implies A)$, proving that the category $\G^{eo}$ is monoidal closed.
 
-    Now we need to show that $\sigma\tensor\tau$ is locally compact.
-We first show that if $\sigma$ and $\tau$ are compact strategies then $\sigma\tensor\tau$ is compact.
-Indeed, suppose that $s\in\sigma\tensor\tau$ is an infinite sequence such that $t\in T_{\sigma\tensor\tau}\cup D_{\sigma\tensor\tau}$ for all finite prefixes $t\ppprefix s$.
-Then $\sigma$ must contain all finite prefixes of $s\vert_{A,C}$, so one of $T_\sigma$ and $D_\sigma$ must contain $s\vert_{A,C}$, since $\sigma$ is compact.
-Similarly, one of $T_{\tau}$ and $D_\tau$ must contain $s\vert_{B,D}$.
-Therefore, $s\in T_{\sigma\tensor\tau}\cup D_{\sigma\tensor\tau}$.
-Since $s$ was arbitrary, it follows that $\sigma\tensor\tau$ is compact.
+\subsection{Exponential structure}
 
-    Now suppose that $\sigma$ and $\tau$ are locally compact.
-Let $s\in\sigma\tensor\tau$.
-Then there exists a compact strategy $\sigma'$ for $A\implies C$ and $\tau'\from B\implies D$ such that $s\vert_{A,C}\in\sigma'\subset\sigma$ and $D_\sigma\subset D_{\sigma'}$ and a compact strategy $\tau'$ for $B\implies C$ such that $s\vert_{B,C}\in\tau'\subset \tau$ and $D_\tau\subset D_{\tau'}$.
-Then $s\in\sigma'\tensor\tau'$, which is compact, and we have $\sigma'\tensor\tau'\subset\sigma\tensor\tau$ and $D_{\sigma\tensor\tau}\subset D_{\sigma'\tensor\tau'}$.
+Given a strategy
+\[
+  \sigma\from X \implies (A \implies B)
+  \]
+we may uncurry $\sigma$ to give a strategy for
+\[
+  X \tensor A \implies B
+  \]
+which we shall also refer to as $\sigma$.  
+We can now construct a strategy $\oc \sigma$, given in the usual category of games by the composite
+\[
+  \begin{tikzcd}
+    \oc X \tensor \oc A \arrow[r, "m_{X,A}"]
+      & \oc (X \tensor A) \arrow[r, "\oc \sigma"]
+        & \oc B
+  \end{tikzcd}
+  \]
+where $m_{X,A}$ is the natural transformation exhibiting $\oc$ as an endo-monoidal functor on $\G$.
 
-    Lastly, we need to show that $\sigma\tensor\tau$ satisfies diverge-or-reply.
-Indeed, suppose that $s\in\sigma\tensor\tau$, that $sa\in P_{(A\tensor B)\implies (C\tensor D)}$ and that $sa\not\in D_{\sigma\tensor\tau}$.
-Then $sa\vert_{A,C}\not\in D_\sigma$ and $sa\vert_{B,D}\not\in D_\tau$.
-Using Lemma \ref{signProfilesLemma}, we see that $sa$ must have one of the following sign profiles:
-    \[
-      \begin{array}{cccc}
-        \zeta_A(s\vert_A) & \zeta_B(s\vert_B) & \zeta_C(s\vert_C) & \zeta_D(s\vert_D) \\
-        \hline
-        P & P & P & O \\
-        P & P & O & P
-      \end{array}
-      \]
-    It follows that one of $sa\vert_{A,C}$ and $sa\vert_{B,D}$ must be an $O$-position.
-Suppose without loss of generality that $sa\vert_{A,C}$ is an $O$-position.
-Since $sa\vert_{A,C}\not\in D_\sigma$, there must be some move $b$ such that $sab\in\sigma$, since $\sigma$ satisfies diverge-or-reply.
-Then we have $sab\in\sigma\tensor\tau$.
-  \end{proof}
-\end{proposition}
-
-We also need to show that the tensor product respects composition.  This is easy.
+Upon currying $\oc \sigma$, we arrive at a strategy for $\oc X \implies (\oc A \implies \oc B)$, which will give us the exponential functor in our new category.
 
 \begin{proposition}
-  Let $A'',A',A,B'',B',B$ be games and let $\sigma'\from A''\to A'$, $\sigma\from A'\to A$, $\tau'\from B''\to B'$, $\tau\from B'\to B$ be strategies.  Then
+  $\oc$ is an endofunctor on $\G^{eo}$.
+\end{proposition}
+\begin{proof}
+  We prove this in uncurried form.  
+  The curried version will then follow, since currying is a natural isomorphism.
+
+  Let $\sigma\from X\tensor A \to B$ and $\tau\from Y \tensor B\to C$ be strategies.  
+  Then the composition of $\sigma$ with $\tau$ is given, in uncurried form, by the following composite in $\G$:
   \[
-    \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')} = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
+    \begin{tikzcd}
+      (Y\tensor X)\tensor A \arrow[r, "\assoc_{Y,X,A}"]
+        &[24pt] Y \tensor (X \tensor A) \arrow[r, "Y \tensor \sigma"]
+          &[18pt] Y \tensor B \arrow[r, "\tau"]
+            & C
+    \end{tikzcd}
     \]
-  \begin{proof}
-    At the level of trace sets, we have:
-    \begin{gather*}
-      (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'}) = \left\{s\in P_{(A''\tensor B'')\implies(A\tensor B)}\suchthat s\vert_{A'', A}\in\comp\sigma{\sigma'},\;s\vert_{B'', B}\in\comp\tau{\tau'}\right\}
-    \end{gather*}
-    Meanwhile:
-    \begin{align*}
-      (\sigma'\tensor\tau')\|(\sigma\tensor\tau) &= \left\{\s\in \seqs{(M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})}\;\middle|\;{\mbox{\begin{minipage}{120pt}{
-        \setlength{\abovedisplayskip}{-5pt}
-        \setlength{\belowdisplayskip}{-10pt}
-        \begin{IEEEeqnarray*}{cCc}
-          \s\vert_{A''\tensor B'',A'\tensor B'} & \in & \sigma'\tensor\tau' \\
-          \s\vert_{A'\tensor B',A\tensor B} & \in & \sigma\tensor\tau
-        \end{IEEEeqnarray*}}
-        \normalsize
-      \end{minipage}}}\right\} \\[1em]
-      &= \left\{\s\in \seqs{(M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
-        \setlength{\abovedisplayskip}{-5pt}
-        \setlength{\belowdisplayskip}{-10pt}
-        \begin{IEEEeqnarray*}{cCc}
-          \s\vert_{A'', A'} & \in & \sigma' \\
-          \s\vert_{A', A} & \in & \sigma \\
-          \s\vert_{B'', B'} & \in & \tau' \\
-          \s\vert_{B', B} & \in & \tau
-        \end{IEEEeqnarray*}}
-        \normalsize
-      \end{minipage}}}\right\} \\[1em]
-      &= \left\{\s\in \seqs{(M_{A''\tensor B''}\cprd M_{A'\tensor B'}\cprd M_{A\tensor B})}\;\middle|\;{\mbox{\begin{minipage}{80pt}{
-        \setlength{\abovedisplayskip}{-5pt}
-        \setlength{\belowdisplayskip}{-10pt}
-        \begin{IEEEeqnarray*}{cCc}
-          \s\vert_{A'', A', A} & \in & \sigma'\|\sigma \\
-          \s\vert_{B'', B', B} & \in & \tau'\|\tau
-        \end{IEEEeqnarray*}}
-        \normalsize
-      \end{minipage}}}\right\}
-    \end{align*}
+  (We may check this either by inspection or by using \cite[Theorem 1]{abramskyjagadeesangames} again.)
 
-    It follows that
+  Then the exponential of this composition is given by Figure \ref{exponentialFunctorial}(i).  
+  \begin{SidewaysFigure}
+    i)
     \[
-      \comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}
-      = \left\{\s\vert_{A''\tensor B'', A\tensor B}\suchthat\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)\right\}
-      = (\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})
+      \begin{tikzcd}[ampersand replacement=\&]
+        \oc(Y\tensor X) \tensor \oc A \arrow[r, "m_{Y\tensor X,A}"]
+          \&[24pt] \oc((Y\tensor X)\tensor A) \arrow[r, "\oc\assoc_{Y,X,A}"]
+            \&[24pt] \oc (Y \tensor (X \tensor A)) \arrow[r, "\oc(Y\tensor \sigma)"]
+              \&[18pt] \oc (Y\tensor B) \arrow[r, "\oc\tau"]
+                \& \oc C
+      \end{tikzcd}
       \]
 
-    We can show that
+    ii)
     \[
-      D_{\comp{(\sigma\tensor\tau)}{(\sigma'\tensor\tau')}} = D_{(\comp\sigma{\sigma'})\tensor(\comp\tau{\tau'})}
+      \begin{tikzcd}[ampersand replacement=\&]
+        (\oc Y \tensor \oc X) \tensor \oc A \arrow[r, "\assoc_{\oc Y,\oc X,\oc A}"]
+          \&[24pt] \oc Y \tensor (\oc X \tensor \oc A) \arrow[r, "\oc Y \tensor m_{\oc X,\oc A}"]
+            \&[24pt] \oc Y \tensor \oc (X \tensor A) \arrow[r, "\oc Y \tensor \oc \sigma"]
+              \&[18pt] \oc Y \tensor \oc B \arrow[r, "m_{Y,B}"]
+                \&[18pt] \oc (Y \tensor B) \arrow[r, "\oc \tau"]
+                  \& \oc C
+      \end{tikzcd}
       \]
-    using a similar argument.
+
+    iii)
+    \[
+      \begin{tikzcd}[ampersand replacement=\&]
+        \oc(Y\tensor X) \tensor \oc A \arrow[r, "m_{Y\tensor X,A}"]
+          \&[24pt] \oc((Y\tensor X)\tensor A) \arrow[r, "\oc\assoc_{Y,X,A}"]
+            \&[24pt] \oc (Y \tensor (X \tensor A)) \arrow[r, "\oc(Y\tensor \sigma)"]
+              \&[18pt] \oc (Y\tensor B) \arrow[r, "\oc\tau"]
+                \&[18pt] \oc C \\
+        (\oc Y \tensor \oc X) \tensor \oc A \arrow[r, "\assoc_{\oc Y,\oc X,\oc A}"] \arrow[u, "m_{Y,X}\tensor\oc A"]
+          \& \oc Y \tensor (\oc X \tensor \oc A) \arrow[r, "\oc Y \tensor m_{\oc X,\oc A}"]
+            \& \oc Y \tensor \oc (X \tensor A) \arrow[r, "\oc Y \tensor \oc \sigma"] \arrow[u, "m_{Y,X\tensor A}"]
+              \& \oc Y \tensor \oc B \arrow[u, "m_{Y,B}"]
+                \&
+      \end{tikzcd}
+      \]
+    \caption{\\[\baselineskip](i): The composite used to calculate $\oc(\sigma;\tau)$, where $\map{\sigma}{X}{A\implies B}$, $\map{\tau}{Y}{B\implies C}$ are strategies in $\G^{eo}$.
+\\[\baselineskip]
+    (ii): The composite used to calculate $\oc\sigma;\oc\tau$. \\[\baselineskip]
+    (iii): Commutative diagram showing that $\oc(\sigma;\tau)\le\oc\sigma;\oc\tau$.}
+    \label{exponentialFunctorial}
+  \end{SidewaysFigure}
+
+  Alternatively, we may first compute $\oc\sigma$ and $\oc\tau$ and then compose them.  
+  Then we end up with the composition given in Figure \ref{exponentialFunctorial}(ii).
+
+  We can show that $\oc(\sigma;\tau)\le\oc\sigma;\oc\tau$ using the diagram \ref{exponentialFunctorial}(iii), where the left-hand hexagon is the coherence diagram for $m$ and the square at the right commutes because $m$ is a natural transformation.
 \end{proof}
-\end{proposition}
-
-The associators, unitors and braiding for this tensor product are the usual (deterministic, compact, non-divergent) copycat strategies.
-It is straightforward to show that they are natural transformations, using the same argument we used to show that $\id_A$ is an identity, and that the appropriate coherence diagrams are satisfied.
-
-Closedness follows immediately from the structural isomorphism
-\[
-  (A \tensor B) \implies C \cong A \implies (B \implies C)
-  \]
-for all games $A,B,C$, together with the definition of morphisms as strategies on the linear implication.
-
-\subsection{Exponentials}
-
-Let $A$ be a game.  We define a game $\oc A$ in which the opponent may at any point open a new copy of the game $A$:
-\[
-  \oc A = (M_{\oc A}, \lambda_{\oc A}, \zeta_{\oc A}, P_{\oc A})
-  \]
-where
-\begin{itemize}
-  \item $M_{\oc A} = \omega \times M_A$
-  \item $\lambda_{\oc A} = \lambda_A \circ \pr_2$
-\end{itemize}
-
-Given some sequence $s\in \seqs{M_{\oc A}}$, we write $s\vert_n$ for the projection on to the second component of the subsequence of $s$ consisting of those moves of the form $(n, a)$.  We define
-\[
-  \oc P_A = \left\{s\in\seqs{M_{\oc A}} \suchthat s\vert_n\in P_A \textrm{ for all $n\in\omega$}\right\}
-  \]
-We define $\zeta_{\oc A}\from \oc P_A\to\OP$ by
-\[
-  \zeta_{\oc A}(s) = \bigwedge_{n\in\omega}\zeta_A(s\vert_n)
-  \]
-Lastly, we define $P_{\oc A}$ to be the subset of $\oc P_A$ consisting of all those terms that are alternating with respect to $\zeta_{\oc A}$ and that satisfy the following criterion on the order in which copies of $A$ may be opened:
-\begin{description}
-  \item[Ordering criterion] If the move $(n + 1, a)$ occurs in $s$, for $n\ge 0$, then there must be some move $b$ such that $(n, b)$ occurs earlier in the sequence $s$ than $(n + 1, a)$.  
-\end{description}
-
-This criterion says that player $O$ must open the copies of $A$ in sequence: he is not allowed to play in game $n+1$ till he has made a move in game $n$.
 
 \begin{proposition}
-  $\oc A$ is a well formed game.
-  \begin{proof}
-    Exactly the same argument as in Proposition \ref{TensorImpliesWellFormed}.
-We need to prove a version of Lemma \ref{signProfilesLemma} which will tell us that if $s\in P_{\oc A}$ then either $\zeta_A(s\vert_n)=O$ for at most one value of $n$.
-  \end{proof}
+  Let $M$ be a language-term of ground type $T$ and write $\deno{M}$ as $\sigma\from X\to A$.
+  Then for each $OP$-play $S$ over $M$, there is a unique position $s\in\sigma$ such that $S$ is the restriction of $s$ to those answer moves in $X$ and such that the final move in $s$ is the result of the play $S$.
 \end{proposition}
-
-Just like the tensor product, the exponential $\oc A$ has the property that only player $O$ may switch games.
-
-The exponential connective gives rise to a functor $\G\to\G$, where the operation on morphisms $\sigma\from A\implies B$ is given by:
-\[
-  \oc\sigma = \{s\in P_{\oc A\implies \oc B}\suchthat s\vert_{A_n,B_n}\in\sigma\textrm{ for all $n\in\omega$}\}
-  \]
-with divergences
-\[
-  D_{\oc\sigma} = \pocl_{\oc A}^O\left(\left\{s \in \oc\sigma\;\middle|\;\mbox{\pbox{\textwidth}{\Centering
-    there exists $n\in\omega$ such that $s\vert_n\in D_\sigma$ \\
-    and for all $m\ne n$, $s\vert_m\in T_\sigma$
-  }}\right\}\right)
-  \]
-The proof that $\oc(\cdot)$ preserves composition is the same as for the tensor product.
-
-$\oc(\cdot)$ gives rise to a \emph{linear exponential comonad} on $\G$ (see \cite{hyland1997games}, for example).
-The relevant natural transformations, including the comultiplication $\mult\from\oc A\to \oc\oc A$, which opens a copy of $A$ on the left for every copy of $A$ opened on the right, are all deterministic, compact, non-divergent strategies.
-We only have to show that they are natural transformations.
-For illustration, we shall do this in the case of the comultiplication.
-
-\begin{proposition}
-  Let $A,B$ be games, and let $\sigma$ be a strategy for $A\implies B$.  Then the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\mult"] \arrow[d, "\oc \sigma"']
-        & \oc \oc A \arrow[d, "\oc \oc \sigma"] \\
-      \oc B \arrow[r, "\mult"']
-        & \oc \oc B
-    \end{tikzcd}
-    \]
-  \begin{proof}
-    Both branches of the diagram are strategies that play as $\sigma$ in each copy of $B$ in $\oc \oc B$, opening a copy of $A$ in $\oc A$ as required.
-The ordering condition means that there is only one possible order in which to open the copies of $A$ in $\oc A$, so both strategies must behave the same way.
-
-    A divergence occurs in either branch if an only if a divergence arises in $\sigma$ in one of the $A-B$ pairs.  So both branches have the same divergence sets.
-  \end{proof}
-\end{proposition}
-
-We may now form the co-Kleisli category $\G^{\oc}$.  The objects of $\G^{\oc}$ are games $A$ and a morphism from $A$ to $B$ is given by a strategy for
-\[
-  A \iimpl B \coloneqq \oc A \implies B
-  \]
-We compose two morphisms $\sigma\from A\iimpl B$ and $\tau\from B\iimpl C$ by setting:
-\[
-  \icomp{\tau}{\sigma} = \oc A \xrightarrow{\mult} \oc \oc A \xrightarrow{\oc \sigma} \oc B \xrightarrow{\tau} C
-  \]
-where composition on the right is in the category $\G$.
-
-A standard property of the linear exponential comonad is:
-
-\begin{theorem}
-  The category $\G^{\oc}$ is Cartesian closed with $\tensor$ as the Cartesian product and $\iimpl$ as the internal Hom.
-\end{theorem}
-
-\section{Denotational Semantics for Fair PCF}
-
-Our base PCF type $\nat$ will be denoted by the game $\bN$ defined above, while the product and function types will be interpreted by the connectives $\tensor$ and $\iimpl$.
-It remains to give the denotation of each of the terms of Fair PCF as a strategy for the appropriate game.
-
-The numerals $\underline{n}$ will each be interpreted as the strategy for $\bN$ that always returns the value $n$.
-The nondeterministic oracle $?$ will be interpreted as the strategy $?$ given at the level of trace sets by $?=P_{\bN}^P$.
-None of these strategies have any divergent positions.
-
-The other PCF terms all have obvious strategies that they correspond to.  The only difficult one is the combinator $\Y_T$.
-
-As usual, we shall use fixed point theorems from domain theory to define the denotation of $\Y$.  The main ideas come from \cite{LairdOrdinalGames}.
-
-\subsection{The stable order on strategies}
-
-We start by defining some orders on strategies.  Our main ordering, which we shall call the \emph{stable ordering} (following \cite{LairdOrdinalGames}) is the order given in \cite{mcCHFiniteND}.
-
-\begin{definition}[Extensional order]
-  Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\exle\tau$ if:
-
-  \begin{enumerate}[1)]
-    \item $T_\sigma\subset T_\tau$
-    \item $D_\tau\subset D_\sigma$
-  \end{enumerate}
-\end{definition}
-
-The extensional order is simple to define, but it is not preserved by composition (see \cite{mcCHFiniteND} for an example).  Instead, we shall use the stable order, which is preserved by composition:
-
-\begin{definition}[Stable order]
-  Let $A$ be a game and let $\sigma,\tau$ be strategies for $A$.  We say that $\sigma\stle\tau$ if:
-
-  \begin{enumerate}[1)]
-    \item $T_\sigma\subset T_\tau$
-    \item $D_\tau\subset D_\sigma$
-    \item $T_\tau\subset T_\sigma \cup \pocl_A^P(D_\sigma)$
-  \end{enumerate}
-\end{definition}
-
-To show that this is an order, the only non-trivial part is to show that property (3) is transitive.
-Suppose that $\sigma\stle\tau\stle\upsilon$ are strategies and that $s\in T_\upsilon\setminus T_\tau$.
-If $s\in T_\tau$, then there exists $d\in D_\sigma$ such that $d\prefix s$, since $\sigma\stle\tau$ and if $s\not\in T_\tau$, then there exists $d\in D_\tau\subset D_\sigma$ such that $d\prefix s$, since $\tau\stle\upsilon$.
-Therefore, $\sigma\stle\upsilon$.
-
-\begin{proposition}
-  Let $A,B,C$ be games, let $\sigma,\sigma'$ be strategies for $A\implies B$ and let $\tau,\tau'$ be strategies for $B\implies C$.  Suppose that $\sigma\stle\sigma'$ and $\tau\stle\tau'$.  Then:
-  \[
-    \comp\tau\sigma\stle\comp{\tau'}{\sigma'}
-    \]
-  \begin{proof}
-    First suppose that $\tau=\tau'$.
-
-    Since $T_\sigma\subset T_{\sigma'}$, we have $\sigma\|\tau\subset\sigma'\|\tau$ and therefore $T_{\comp\tau\sigma}\subset T_{\comp{\tau}{\sigma'}}$.
-
-    Now let $e\in D_{\comp{\tau}{\sigma'}}$.
-Suppose $\e\vert_{A,C}\prefix e$, where $\e\in\sigma'\dv\tau$, and suppose first that $\e\vert_{A,B}\in D_{\sigma'}$ and $\e\vert_{B,C}\in T_{\tau}$.
-Since $D_{\sigma'}\subset D_\sigma$, we have $\e\vert_{A,B}\in D_\sigma$, so $\e\in\sigma\dv\tau$ and therefore $e$, which is a postfix of $\e\vert_{A,C}$, is contained in $D_{\comp\tau\sigma}$.
-
-    Now suppose that $\e\vert_{A,B}\in T_{\sigma'}$ and $\e\vert_{B,C}\in D_{\tau}$.
-Since $\sigma\stle\sigma'$, we have $\e\vert_{A,B}\in T_\sigma\cup \pocl_A^O(D_\sigma)$.
-If $\e\vert_{B,C}\in T_\sigma$, then we have $\e\in\sigma\dv\tau$ and so $\e\vert_{A,C}\in D_{\comp\tau\sigma}$ and therefore $e\in D_{\comp\tau\sigma}$, since $D_{\comp\tau\sigma}$ is postfix-closed.
-
-    Otherwise, there exists $d\in D_\sigma$ such that $d\prefix\e\vert_{B,C}$.
-Then $\e\vert_{A,B}$ and $\e\vert_{B,C}$ have prefixes $q\prefix\e\vert_{A,B}$, $r\prefix\e\vert_{B,C}$ such that $q\in D_\sigma$, $r\in D_\tau$ and for all $P$-prefixes $q'\prefix q, r'\prefix r$ we have $q'\in T_\sigma$ and $r'\in T_\tau$.
-Passing to an appropriate prefix $\e'$ of $\e$, we have either $\e'\vert_{A,B}=q$ and $r\prefix\e'\vert_{B,C}$ or $q\prefix\e'\vert_{A,B}$ and $\e\vert_{B,C}=r$.
-In either case, $\e'\in \sigma\dv\tau$ and so $\e'\vert_{A,C}\in D_{\comp\tau\sigma}$.
-Then we have $\e'\vert_{A,C}\prefix\e\vert_{A,C}\prefix e$, and so $e\in D_{\comp\tau\sigma}$.
-
-    Lastly, suppose that $s\in T_{\comp{\tau}{\sigma'}}\setminus T_{\comp\tau\sigma}$.
-Write $s=\s$, where $\s\in\sigma'\|\tau$.
-Since $\s\not\in T_{\comp\tau\sigma}$, we must have $\s\vert_{A,B}\in\sigma'\setminus\sigma$.
-It follows that there exists $d\in D_\sigma$ such that $d\prefix\s\vert_{A,B}$ and therefore $\s\in\sigma\dv\tau$.
-Therefore, $d\prefix\s\vert_{A,B} = s$.
-
-    The result follows by a similar argument in the case that $\sigma=\sigma'$.  Therefore, the full result follows from transitivity of $\stle$: if $\sigma\stle\sigma'$ and $\tau\stle\tau'$, then
-    \[
-      \comp\tau\sigma \stle \comp\tau{\sigma'} \stle \comp{\tau'}{\sigma'}
-      \]
-  \end{proof}
-\end{proposition}
-
-We want to get a similar result for composition in the category $\G^{\oc}$.  To do that it will suffice to prove the following result:
-
-\begin{proposition}
-  Let $A,B$ be games and let $\sigma,\tau$ be strategies for $A\implies B$ such that $\sigma\stle\tau$.  Then $\oc\sigma\stle\oc\tau$ as strategies for $\oc A\implies \oc B$.
-  \begin{proof}
-    If $s\in\oc\sigma$, then $s\vert_{A_n,B_n}\in\sigma$ for all $n$ and therefore $s\vert_{A_n,B_n}\in\sigma'$ for all $n$.  It follows that $\oc\sigma\subset\oc\tau$.
-
-    If $e\in D_{\oc\tau}$ then there exists some $e'\prefix e$ and some $n\in\omega$ such that $e'\vert_n\in D_\tau$ and $e'\vert_m\in T_\tau$ for all $m\ne n$.
-
-    Since $\sigma\stle\tau$, we have $D_\tau\subset D_\sigma$ and $T_\tau\subset T_\sigma\cup \pocl_A^P(D_\sigma)$.
-For each $m$, define a subsequence $d_n$ of $e'$ as follows: if $e'\vert_m\in T_\sigma$ then $d_m=e'\vert_m$.
-If $e'\vert_m\in \pocl_A^P(D_\sigma)$, then there is some prefix of $e'\vert_m$ that is an $O$-position in $D_\sigma$, all of whose $P$-prefixes are in $T_\sigma$.
-Let $d_m$ be the shortest such prefix of $e'\vert_m$.
-
-    We know that $e'\vert_n\in D_\tau\subset D_\sigma$, so $d_n\in D_\sigma$.
-Let $d$ be the shortest prefix of $e'$ such that there exists some $m$ such that $d_m\in D_\sigma$ and $d_m\prefix d$.
-Write $d=d'a$.
-We claim that $a$ is the last move in $d_m$ and that $d\vert_k\in T_\sigma$ for all $k\neq m$.
-Certainly, $a$ is a move in $d_m$; otherwise, we could remove it and get a shorter sequence that still contains $d_m$ as a subsequence.
-If $d\vert_k\prefix d_k$, then $d\vert_k\in T_\sigma$, since it is a $P$-position by examination of sign profiles.
-Otherwise, $d_k\pprefix d\vert_k$.
-But this contradicts the minimality of $d$.
-
-    Therefore, we have $d\in D_{\oc\sigma}$.  It follows that $e\in D_{\oc\sigma}$, since $D_{\oc\sigma}$ is postfix-closed.
-
-    Lastly, if $s\in \oc\tau\setminus\oc\sigma$, then there exists some $s'\prefix s$ and some $n\in\omega$ such that $s'\vert_{A_n,B_n}\in\tau\setminus\sigma$.
-Therefore, if we construct the $d_n$ as before, we have $d_n\in D_\sigma$ for at least one $n$ and it follows that we may construct $d\in D_{\oc\sigma}$ as before such that $d\prefix s'$.
-It follows that $s\in D_{\oc\sigma}$.
-  \end{proof}
-\end{proposition}
-
-If $A$ is a game and $S\subset P_A$ is some set, we say that $s\in S$ is \emph{minimal} if $t\not\in S$ for all proper prefixes $t\pprefix s$.
-Let $A$ be a game and let $F$ be a non-empty set of strategies for $A$ that is directed under the extensional order: so if $\sigma,\tau\in F$ then there is some $\upsilon\in F$ such that $\sigma,\tau\exle\upsilon$.
-We define a strategy $\exlub F$ for $F$ by setting
-\begin{gather*}
-  T_{\exlub F} = \bigcup_{\sigma\in F}T_\sigma \\
-  D_{\exlub F} = \bigcap_{\sigma\in F}D_\sigma
-\end{gather*}
-
-\begin{proposition}
-  If $A$ is a game and $F$ is a set of strategies for $A$ that is directed under the extensional order then $\exlub F$ is a strategy for $A$.
-  \begin{proof}
-    $T_{\exlub F}$ is certainly non-empty and prefix-closed in $T_{\exlub F}$.
-Similarly, $D_{\exlub F}$ is certainly postfix-closed.
-Suppose that $s\in D_{\exlub F}$.
-For each $\sigma\in F$, there exists some prefix $t_\sigma\prefix s$ such that $t_\sigma\in D_\sigma$ and $u\in T_\sigma$ for all $P$-prefixes $u\prefix t_\sigma$.
-Let $t$ denote the limit of the $t_\sigma$.
-Then $t$ is an $O$-position, since $s$ and the $t_\sigma$ are $O$-positions, so every $P$-prefix of $t$ is a $P$-prefix of one of the $t_\sigma$ and is therefore contained in $T_\sigma\subset T_{\exlub F}$.
-Moreover, $t\in D_\sigma$ for all $\sigma$ by postfix closure of the $D_\sigma$.
-
-    To show that $\exlub F$ satisfies diverge-or-reply, suppose that $s\in T_{\exlub F}$ and that $sa\in P_A$ is such that $sa\not\in D_{\exlub F}$.
-Then there exist $\sigma,\tau\in F$ such that $s\in T_\sigma$ and $sa\not\in D_\tau$.
-Since $F$ is directed under the extensional order, there exists some strategy $\upsilon\in F$ such that $\sigma,\tau\exle\upsilon$.
-In particular, $s\in T_\upsilon$ and $sa\not\in D_\upsilon$.
-It follows that $sab\in T_\upsilon\subset T_{\exlub F}$ for some $b$.
-Therefore, $\exlub F$ satisfies diverge-or-reply.
-
-    Lastly, we show that $\exlub F$ is locally compact.  Let $s\in T_{\exlub F}$.  Then there is some compact strategy $\sigma'$ such that $s\in T_{\sigma'}$ and $\sigma'\exle\sigma\exle\exlub F$.  
-  \end{proof}
-\end{proposition}
-
-$\exlub F$ is clearly a least upper bound for directed sets of strategies under the extensional ordering.
-More suprisingly, $\exlub F$ is a least upper bound for directed sets of strategies under the stable ordering.
-
-\begin{proposition}
-  Let $A$ be a game, and let $F$ be a set of strategies for $A$ that is directed under the stable ordering -- so if $\sigma,\tau\in F$ then there is some strategy $\upsilon\in F$ such that $\sigma,\tau\stle\upsilon$.
-Then $\exlub F$ is a least upper bound for $F$ under the ordering $\stle$.
-  \begin{proof}
-    First we show that $\exlub F$ is a stable upper bound for $F$.
-Let $\sigma\in F$.
-Certainly $T_\sigma\subset T_{\exlub F}$ and $D_{\exlub F}\subset D_\sigma$, so it remains to show that $T_{\exlub F}\subset T_\sigma\cup \pocl_A^P(D_\sigma)$.
-Suppose $s\in T_{\exlub F}$.
-Then $s\in T_\tau$ for some strategy $\tau$.
-Since $F$ is stably directed, there exists some strategy $\upsilon\in F$ such that $\sigma,\tau\stle\upsilon$.
-In particular:
-    \[
-      s\in T_\upsilon \subset T_\sigma \cup \pocl_A^P(D_\sigma)
-      \]
-
-    Now suppose that $\alpha$ is a stable upper bound for $F$; we need to show that $\exlub F\stle\alpha$.
-Since we have $T_\sigma\subset T_\alpha$ and $D_\alpha\subset D_\sigma$ for all $\sigma\in F$, we have $T_{\exlub F}\subset T_\alpha$ and $D_\alpha\subset D_{\exlub F}$.
-Now suppose that $s\in T_\alpha\setminus\pocl_A^P(D_{\exlub F})$.
-Then there exists some $\sigma\in F$ such that $d\not\prefix s$ for all $d\in D_\sigma$.
-It follows that $s\in T_\alpha\setminus\pocl_A^P(D_\sigma)$; since $D_\sigma\stle D_\alpha$, we must have $s\in T_\sigma\subset T_{\exlub F}$.
-  \end{proof}
-\end{proposition}
-
-\subsection{Soundness}
-
-Our proofs for soundness and adequacy follow \cite{LairdOrdinalGames}.
-
-\begin{lemma}
-  \label{jimsLemma}
-  Let $M$ be a reducible program of type $T$.  If $M\opto N$ then $\deno{N}\exle\deno{M}$.
-  \begin{proof}
-    This is easy to show inductively by analysing the reduction rules.
-  \end{proof}
-\end{lemma}
-
-\begin{theorem}[Soundness]
-  Let $M$ be a program of type $\nat$.  If $M\mustconverge$, then $D_{\deno{M}} = \emptyset$.
-  \begin{proof}
-    By Lemma \ref{jimsLemma}, 
-\end{theorem}
-
-\subsection{Adequacy}
-
-I don't think I'll have a full abstraction result yet, but I could add a section explaining how this model gives us some progress towards full abstraction.
 

### 2018-01-21 cones/cones.tex
Started some new projects.

\documentclass{article}

\input{../common/preamble}

\begin{document}

\subsection{Preliminaries}

\subsubsection{Surjective strategies}

Let $A$, $B$ be games.  
We say that a strategy $\sigma$ for $A\implies B$ is \emph{surjective} if for all positions $b\in P_B$ there exists some $s\in \sigma$ such that $s\vert_B=b$.

The reason we are interested in surjective strategies from the point of view of nondeterminism is that composition with them preserves $\top$: if $\sigma\from A\implies B$ is surjective, then $\top_A;\sigma=\top_B$.

A result of Hyland and Schalk \cite{hylandSchalkGames} sheds some further light on this definition:

\begin{proposition}[Hyland-Schalk functor]
  There is a functor $\G\to\Rel$ given by sending a game $A$ to its set $P_A$ of positions and sending a strategy $\sigma\from A\implies B$ to the set
  \[
    \grel{\sigma} = \{(s\vert_A,s\vert_B)\in P_A\times P_B\suchthat s\in^P\sigma\}
    \]
  This functor is lax monoidal with respect to the Cartesian product on $\Rel$ and the tensor product $\tensor$ on $\G$ and linearly distributive with respect to the finite multisets comonad $W$ on $\Rel$ and the exponential comonad $\oc$ on $\G$.  
  Moreover, the composite $\G_{det}\hookrightarrow\G\to\Rel$ is faithful.  
\end{proposition}

Using this result, we can rephrase our original definition: a strategy $\sigma$ is \emph{surjective} if its image $\grel\sigma$ under the Hyland-Schalk functor is a surjective relation.

We will principally be interested in surjective strategies that are deterministic and total.  
If a deterministic surjective strategy $\sigma\from A\implies B$ is not total, then it introduces the possibility of divergence, and so we will no longer have the equation $\top_A;\sigma=\top_B$, since the composite on the left-hand side will contain divergent positions.  
The problem is that the composition of total strategies is not total in general.  
In order to get around this definition, we place a small restriction on strategies:

\begin{definition}
  \label{def:winning}
  Let $A,B$ be games.  
  Let $\sigma$ be a strategy for $A\implies B$.  
  We write $\bar\sigma$ for the closure of $\sigma$ inside $M_{A\implies B}^{\omega}$; i.e., the set of all possibly infinite sequences of moves, all of whose finite prefixes lie in $\sigma$.

  We say that $\sigma$ is \emph{winning} if $\sigma$ is total and if whenever $s\in\bar\sigma$ is such that $s\vert_A$ is infinite, then $s\vert_B$ is infinite.  
\end{definition}

\begin{remark}
  It is then straightforward to prove that the composition of winning strategies is winning.  
  One way to see this is to observe that our definition says precisely that $\sigma$ is a \emph{winning strategy} in the sense of \cite{abramskyjagadeesangames} in the case that $W_A=P_A$ and $W_B=P_B$.  Then the category of games and winning strategies (in the sense of Definition \ref{def:winning}) is seen to be the full subcategory of the category of games and winning strategies from \cite{abramskyjagadeesangames} consisting of all those games $X$ that satisfy $W_X=P_X$.

  This subcategory is not monoidal \emph{closed}, but neither is the category of games and surjective strategies, so we do not lose anything by adopting this definition.
\end{remark}

\begin{remark}
  Another, perhaps more compact definition of a winning strategy that does not require us to talk about infinite positions is as follows: for every play $s\in\sigma$ ending in an $O$-move from $B$, $s$ is a prefix of some $t\in\sigma$ ending in a $P$-move from $B$.
\end{remark}

\begin{proposition}
  There is a sub-monoidal-exponential category $\G_{sw}$ of $\G$ consisting of all those strategies that are deterministic, surjective and winning.
\end{proposition}

\begin{proof}
  The first step is to show that the composition of deterministic, surjective and winning strategies is deterministic, surjective and winning.

  \begin{itemize}
    \item That the composition of deterministic winning strategies is deterministic and winning is shown in \cite{abramskyjagadeesangames}.
    \item Preservation of surjectivity by composition comes down to the analogous result in $\Rel$, coupled with the functoriality of the Hyland-Schalk construction.
  \end{itemize}

  Therefore, we have a category (the identity is obviously deterministic, surjective and winning).

  We will ignore `deterministic' from here on, because it is well known that the category of games and deterministic strategies has all the structure we are talking about.  We will write `s.w. strategy' for `surjective winning strategy'.

  Let $A,B,C,D$ be games, let $\sigma$ be a s.w. strategy for $A\implies C$ and let $\tau$ be a s.w. strategy for $B\implies D$.  
  It is then easy to see that $\sigma\tensor\tau$ is a winning strategy for $A\tensor B\implies C\tensor D$.

  Next, we need to show that $\sigma\tensor\tau$ is surjective.  
  To do this, we use the monoidality of the Hyland-Schalk functor.  
  Indeed, we have a commutative diagram
  \[
    \begin{tikzcd}
      P_A \times P_B \arrow[r, "\grel{\sigma}\times\grel{\tau}"] \arrow[d, "m_{A,B}"']
        & P_C \times P_D \arrow[d, "m_{C,D}"] \\
      P_{A \tensor B} \arrow[r, "\grel{\sigma\tensor\tau}"]
        & P_{C \tensor D}
    \end{tikzcd}
    \]

  The relation $m_{C,D}$ is the one that relates $(s\vert_C,s\vert_D)$ to $s$ for all $s\in P_{C\tensor D}$.  
  As such, it is certainly surjective.  
  Moreover, since $\grel{\sigma}$ and $\grel{\tau}$ are both surjective relations, then their product is surjective.  
  It follows that $\grel{\sigma\tensor\tau}$ must be surjective, and therefore that $\sigma\tensor\tau$ is a surjective strategy.

  We use an almost identical argument to establish that the bang of a surjective strategy is surjective, this time using the linear distributivity of the Hyland-Schalk functor.  
  In this case, our argument rests on the fact that the coherence $\lambda_A \from W A \to P_{\oc A}$ is surjective; indeed, this is the relation that, for all plays $s\in P_{\oc A}$, relates $s$ with the finite multiset consisting of the restrictions of $s$ to the various subgames.

%  Let $e\in P_{C\tensor D}$.  
%  Then, since $\sigma$, $\tau$ are surjective, there exists some $s\in\sigma$, $t\in\tau$ such that $s\vert_C=e\vert_C$ and $t\vert_D=e\vert_D$.  
%
%  Moreover, since player $O$ switches games in $C\tensor D$, we know that one out of $e\vert_C$, $e\vert_D$ must end in a $P$-move.
%  Assume without loss of generality that $e\vert_C$ ends in a $P$-move, and that the final segment of $e$ consists of moves in $D$.
%  Then we can assume that $s$ ends in a $P$-move.  
%
%  We may now write:
%  \begin{align*}
%    &s' = c_1 a^*_1 C_1 c_2 a^*_2 C_2 \cdots c_m a^*_m C_m \\
%    &t' = d_1 b^*_1 D_1 d_2 b^*_2 D_2 \cdots d_n b^*_n D_n?
%  \end{align*}
%  where each $c_i$ is an $O$-move in $C$, each $C_i$ a $P$-move in $C$, each $d_j$ an $O$-move in $D$, each $D_j$ a $P$-move in $D$, each $a^*_i$ a (possibly empty) sequence of moves in $A$ and each $b^*_j$ a (possibly empty) sequence of moves in $B$.  
%  Lastly, the final move $D_n$ of $t'$ may or may not appear.
%
%  Now we know that $e$ is made up of some sequence of pairs of the form $c_iC_i$ or $d_jD_j$, in some order, and that it ends with either $d_nD_n$ (if $D_n$ is present) or $d_n$ (if not).  
%  If we replace each $c_iC_i$ in $e$ with $c_ia^*_iC_i$ and each $d_jD_j$ with $d_jb^*_jD_j$, then we end up with a valid sequence $e'\in\sigma\tensor\tau$, and we have $e'\vert_{C\tensor D} = e$.  
%  This completes the proof that the tensor product of surjective morphisms is surjective.
%
%  A similar argument shows us that if $\sigma$ is a s. w. strategy then its exponential $\oc\sigma$ is surjective and winning.

  Lastly, we observe that if $A,B$ are games then the comultiplication $\oc A \to \oc\oc A$, dereliction $\oc A \to A$, weakening $\oc A\to I$, contraction $\oc A \to \oc A \tensor \oc A$ and monoidal coherence $\oc A\tensor \oc B \to \oc (A\tensor B)$ are all surjective, winning strategies.
\end{proof}

\subsubsection{The double category \MonCat}

The natural setting for much of the work we will do is the double category \MonCat, introduced in \cite{AdjointsInDoubleCategories}.  
A \emph{double category} is an internal category in $\Cat$, but it is more useful to think of it as a new sort of category made up of the following data:
\begin{itemize}
  \item It has \emph{objects}.
  \item It has two classes of \emph{morphisms}: the \emph{horizontal} morphisms and the \emph{vertical} morphisms, which go between objects.  
    Horizontal morphisms can be composed with other horizontal morphisms, and vertical morphisms with vertical morphisms.
  \item It has \emph{cells} $\alpha$, which are associated to squares of the form
    \[
      \begin{tikzcd}[row sep=large, column sep=large]
        A \arrow[r, "F", ""'{name=F}] \arrow[d, "g"']
          & B \arrow[d, "f"] \\
        C \arrow[r, "G"', ""{name=G}]
          & D
        \arrow[Rightarrow, from=F, to=G, "\alpha"]
      \end{tikzcd}
      \]
    The cell $\alpha$ is associated to the square in the same way that an ordinary morphism is associated to its source and target objects, so there may be more than one cell corrseponding to a particular square.  
    We may compose cells either horizontally or vertically, as long as the squares in question can be pasted together along an edge.  
    For example, horizontal composition is shown in Figure \ref{fig:horizontal-cell-composition}.
\end{itemize}

\begin{figure}
  \begin{mathpar}
    \begin{tikzcd}[row sep=large, column sep=large]
      A' \arrow[r, "F", ""'{name=F}] \arrow[d, "g"']
        & B' \arrow[r, "H", ""'{name=H}] \arrow[d, "f"]
          & C' \arrow[d, "h"] \\
      A \arrow[r, "G"', ""{name=G}]
        & B \arrow[r, "F'"', ""{name=Fprime}]
          & C
      \arrow[Rightarrow, from=F, to=G, "\alpha"]
      \arrow[Rightarrow, from=H, to=Fprime, "\beta"]
    \end{tikzcd}
    \and
    \begin{tikzcd}[row sep=large, column sep=large]
      A' \arrow[r, "F;H", ""'{name=FH}] \arrow[d, "g"']
        & C' \arrow[d, "h"] \\
      A \arrow[r, "G;F'"', ""{name=GFprime}]
        & C
      \arrow[Rightarrow, from=FH, to=GFprime, "(\alpha|\beta)"]
    \end{tikzcd}
  \end{mathpar}
  \caption{We can compose cells between compatible squares horizontally or vertically.  
  Here, we are composing cells horizontally.}
  \label{fig:horizontal-cell-composition}
\end{figure}

The particular double category we are going to be interested in is the double category $\MonCat$ of monoidal categories.  
The objects of $\MonCat$ are monoidal categories, horizontal morphisms are lax monoidal functors and vertical morphisms are oplax monoidal functors.  
The definition of a cell in $\MonCat$ is a bit less familiar, but appears in \cite{AdjointsInDoubleCategories}.  
  Let $\C'$,$C'$,$\D'$,$\D$ be monoidal categories, let $f\from\C'\to\C$, $g\from \D'\to \D$ be oplax monoidal functors and let $F\from\D'\to\C'$, $G\from\D\to\C$ be lax monoidal functors, as in Figure \ref{fig:generalized-monoidal-setup}.

  \begin{figure}
    \[
      \begin{tikzcd}[row sep=large, column sep=large]
        \D' \arrow[r, "F", ""'{name=F}] \arrow[d, "g"']
          & \C' \arrow[d, "f"] \\
        \D \arrow[r, "G"', ""{name=G}]
          & \C
        \arrow[Rightarrow, from=F, to=G, "\phi"]
      \end{tikzcd}
      \]
    \caption{A generalized monoidal natural transformation $\phi$ is a particular sort of natural transformation between composites of lax and oplax monoidal functors.}
    \label{fig:generalized-monoidal-setup}
  \end{figure}

We say that a natural transformation $\phi\from fF\bigto Gg$ is a \emph{generalized monoidal natural transformation} if the following two diagrams commute for all objects $X,Y$ of $\D'$:
\begin{mathpar}
  \begin{tikzcd}
    f F X \tensor f F Y \arrow[r, "\phi_X \tensor \phi_Y"]
      & G g X \tensor G g Y \arrow[d, "m_G"] \\
    f (F X \tensor F Y) \arrow[u, "m_f"] \arrow[d, "f m_F"']
      & G (g X \tensor g Y) \\
    f F (X \tensor Y) \arrow[r, "\phi_{X \tensor Y}"]
      & G g (X \tensor Y) \arrow[u, "G m_g"']
  \end{tikzcd}
  \and
  \begin{tikzcd}[column sep=small, row sep=small]
    %
      & f F I_{\D'} \arrow[rr, "\phi_I"]
        &[-1.2em]
          &[-1.2em] G g I_{\D'} \arrow[dr, "G \epsilon_g"]
            & \\
    f I_{\C'} \arrow[ur, "f \epsilon_F"] \arrow[drr, "\epsilon_f"]
      &
        &
          &
            & G I_{\D} \\
    %
      &
        & I_{\C} \arrow[urr, "\epsilon_G"]
          &
            &
  \end{tikzcd}
\end{mathpar}

We will, in fact, be more interested in the sub-double category $\SymmMonCat$ of $\MonCat$, whose objects are the symmetric monoidal categories, and where the horizontal and vertical morphisms are lax and oplax \emph{symmetric} monoidal functors.  
The definition of a generalized monoidal natural transformation is unchanged in the symmetric case.

\subsubsection{Multiplicative natural transformations}

We observed that if $\sigma$ is a surjective strategy from a game $A$ to a game $B$, then $\top_A;\sigma=\top_B$.  
In other words, $\top_A$ defines a natural transformation from $I$ to the inclusion of $\G_{sw}$ into our model of nondeterministic PCF.  
We shall see that this is in fact a generalized monoidal natural transformation.

Rather than use this natural transformation $I \to j(X)$ directly, however, it will be technically convenient to consider instead the related natural transformation from $A \to j(X) \tensor A$.

\begin{proposition}
  Let $\C',\C,\C''$ be monoidal categories, let $j$ be an oplax monoidal functor from $\C'$ to $\C$ and let $J$ be a lax monoidal functor from $\C$ to $\C''$.  Let $\phi_X\from I \to JjX$ be a generalized monoidal natural transformation and define a natural transformation $\phi_{X,A}^\infty\from JA \to J (jX \tensor A)$ to be given by the following composite:
  \[
    \begin{tikzcd}
      J A \arrow[r, "\lunit"]
        & I \tensor J A \arrow[r, "\phi_X\tensor J A"]
          & J j X \tensor J A \arrow[r, "m_J"]
            & J (j X \tensor A)
    \end{tikzcd}\,.
    \]
  Then $\phi^\infty$ makes the following diagrams commute:
  \begin{mathpar}
    \begin{tikzcd}
      J A \arrow[r, "\phi^\infty_{X,A}"] \arrow[d, "\phi^\infty_{Y\tensor X,A}"']
        & J (j X \tensor A) \arrow[r, "\phi^\infty_{Y,j X \tensor A}"]
          &[24pt] J (jY \tensor (j X \tensor A)) \\
      J (j (Y \tensor X) \tensor A) \arrow[rr, "J (m_j \tensor A)"]
        &
          & J ((j Y \tensor j X) \tensor A) \arrow[u, "J \assoc"']
    \end{tikzcd}
    \and
    \begin{tikzcd}
      JA \arrow[r, "\phi^\infty_{I,A}"] \arrow[dr, "\lunit"']
        & J (j I \tensor A) \arrow[d, "J(\epsilon_j\tensor A)"] \\
      %
        & I \tensor J A
    \end{tikzcd}\,.
  \end{mathpar}
\end{proposition}

We say that $\phi^\infty$ is a \emph{multiplicative natural transformation}.

\begin{definition}
  Let $\C',\C$ be monoidal categories and let $j$ be an oplax monoidal functor from $\C'$ to $\C$.  Let $\C''$ be a category and let $J$ be a functor from $\C$ to $\C''$.  
  Let $\psi_{X,A}\from J A \to J(j X \tensor A)$ be a natural transformation.  
  We say that $\psi$ is \emph{multiplicative} if the following diagrams commute for all objects $X,Y$ of $\C'$ and all objects $A$ of $\C$:
\end{definition}

One reason why we are interested in the rather strange-looking definition of a dimonoidal natural transformation is that they give rise to multiplicative natural transformations.

\begin{proposition}
  Let $\C',\C,\C''$ be monoidal categories, let $j$ be an oplax monoidal functor from $\C'$ to $\C$ and let $J$ be a lax monoidal functor from $\C$ to $\C''$.  
  Let $\phi_X\from I \to J j X$ be a dimonoidal natural transformation:
  \[
    \begin{tikzcd}[row sep=24pt, column sep=36pt]
      \C' \arrow[r, "j"] \arrow[d, "()"']
        & \C \arrow[d, "J"] \\
      I \arrow[r, "I"]
        \arrow[ur,
               Rightarrow,
               start anchor={[xshift=6pt, yshift=4pt]},
               end anchor={[xshift=-6pt, yshift=-4pt]},
               "\phi"]
        & \C''
    \end{tikzcd}\,.
    \]
  Define a natural transformation $\phi^\infty_{X,A}\from J A \to J (j X \tensor A)$ as follows:
  \[
    \phi^\infty_{X,A} =
    \begin{tikzcd}
      J A \arrow[r, "\lunit\inv"]
        & I \tensor J A \arrow[r, "\phi_X\tensor J A"]
          & J j X \tensor J A \arrow[r, "m_J"]
            & J (j X \tensor A)
    \end{tikzcd}
    \]
  Then $\phi^\infty$ is multiplicative.
\end{proposition}

We can also diagonally compose a multiplicative natural transformation with a dimonoidal natural transformation.

\begin{proposition}
  Let $\C'$, $\C$, $\C''$, $\D'$, $\D$ be monoidal categories, let $F'\from \D'\to\C'$, $G \from \D \to \C$ and $J\from \C\to\C''$ be lax monoidal functors and let $g\from D'\to D$ and $j\from \C' \to \C$ be oplax monoidal functors, as in Figure \ref{fig:dimonoidal-multiplicative}.

  \begin{figure}
    \begin{mathpar}
      \begin{tikzcd}[row sep=24pt, column sep=36pt]
        \D' \arrow[r, "g"] \arrow[d, "F"']
          & \D \arrow[d, "G"] \\
        \C' \arrow[r, "j"']
            \arrow[ur,
                   Rightarrow,
                   start anchor={[xshift=6pt, yshift=4pt]},
                   end anchor={[xshift=-6pt, yshift=-4pt]},
                   "\phi"]
          & \C
      \end{tikzcd}
      \and
      \begin{tikzcd}[row sep=24pt, column sep=36pt]
        \C'\times \C \arrow[r, "j\times\id"] \arrow[d, "\pr_2"']
          & \C \times \C \arrow[r, "\_\tensor\_"]
            & \C \arrow[d, "J"] \\
        \C \arrow[rr, "J"']
           \arrow[urr,
                  Rightarrow,
                  start anchor={[xshift=12pt, yshift=8pt]},
                  end anchor={[xshift=-12pt, yshift=-8pt]},
                  "\psi"]
          &
            & \C''
      \end{tikzcd}
    \end{mathpar}
    \caption{We can compose a multiplicative natural transformation $\psi_{X,A}\from J A \bigto J (j X \tensor A)$ with a dimonoidal natural transformation $\phi \from j F \bigto G g$.}
    \label{fig:dimonoidal-multiplicative}
  \end{figure}

  Let $\psi_{X,A}\from J A \bigto J (jX \tensor A)$ be a multiplicative natural transformation and let $\phi\from j F \bigto G g$ be a dimonoidal natural transformation.  
  Then the natural transformation $(\psi\bbslash\phi)_{X,A}\from J G A \bigto J G (g X \tensor A)$ defined by
  \[
    \begin{tikzcd}
      J G A \arrow[r, "\psi_{F X, G A}"]
        &[12pt] J (j F X \tensor G A) \arrow[r, "J (\phi_X \tensor G A)"]
          &[24pt] J (G g X \tensor G A) \arrow[r, "J m_G"]
            & J G (g X \tensor A)
    \end{tikzcd}
    \]
  is multiplicative.
\end{proposition}

\begin{remark}
  In the case that $\psi=(\phi')^\infty$, it is easy to check that 
  \[
    \psi\bbslash\phi = (\phi')^\infty \bbslash \phi = (\phi'\bbslash\phi)^\infty\,.
    \]
\end{remark}

\subsection{Cones}

\subsubsection{Nondeterminism and deterministic factorization}

In this section, we will write $\G_{ND}$ to refer to a putative model of nondeterministic PCF containing the usual game semantics model of PCF as a sub-linear category.

We observed that the important feature of surjective winning strategies is that they preserve the nondeterministic oracle $\top$: if $\sigma\from A\implies B$ is surjective, then $\top_A;\sigma = \top_B$.

Another way of expressing this is that $\top$ is a natural transformation in the following diagram:

\[
  \begin{tikzcd}
    \G_{sw} \arrow[r, hook] \arrow[d, "()"']
      & \G \arrow[d, hook] \\
    I \arrow[r, "I"'] \arrow[ur, "\top", Rightarrow]
      & \G_{ND}
  \end{tikzcd}
  \]

I.e., $\top$ is a natural transformation from the constant $I$ functor from $\G_{sw}$ to $\G_{ND}$ to the inclusion functor.

We will make one more assumption about the category $\G_{ND}$, which will capture the fact that $\G_{ND}$ is the smallest category obtained by adjoining the nondeterministic strategies $\top$ on to our original category $\G$.

\begin{definition}[Factorization]
  Let $\C', \C, \C''$ be monoidal categories, let
  \[
    \begin{tikzcd}
      \C' \arrow[r, "j"]
        & \C \arrow[r, "J"]
          & \C''
    \end{tikzcd}
    \]
  be functors, where $J$ is lax monoidal, and let $\phi$ be a natural transformation from $I$ to $J\circ j$.

  Then we say that $\C''$ satisfies $\phi$-\emph{factorization} if:
  \begin{itemize}
    \item The functor $J$ is essentially surjective.  
    \item If $A$, $B$ are objects of $\C$, then every morphism from $JA$ to $JB$ in $\C''$ is of the form
      \[
        \begin{tikzcd}
          JA \arrow[r, "\lunit\inv"]
            & I \tensor JA \arrow[r, "\phi_X \tensor \id"]
              & JjX \tensor JA \arrow[r, "m_J"]
                & J(jX \tensor A) \arrow[r, "Jf"]
                  & JB
        \end{tikzcd}
        \]
      where $X$ is some object of $\C'$ and $f$ is some morphism in $\G$ from $jX\tensor A$ to $B$.
  \end{itemize}
\end{definition}

\begin{example}
  \begin{enumerate}
    \item In \cite{mcCHFiniteND}, Harmer and McCusker construct a game semantics model $\G_{fnd}$ of finite nondeterminism and prove that if $A$ is any game in that model, then every nondeterministic strategy $\sigma$ for $A$ can be written as the composition of some strategy $Det(\sigma)\from (\bN\to\bN)\to A$ with a fixed strategy $oracle\from I\to(\bN\to\bN)$.

      In our setting, this is the case where $\C'=I$, $\C''$ is the category $\G_{fnd}$ and $\C$ is its subcategory of games and \emph{deterministic} strategies.  
      In this case, the functor $j$ is the (oplax monoidal) functor sending $I$ to $\bN\to\bN$, and the natural transformation $\phi$ has the strategy $oracle$ as its unique component.

    \item For a model of PCF with \emph{countable} nondeterminism, that is, PCF extended by a `deterministic oracle' $\wn\from\bN$, we might expect our category to satisfy a factorization rule such that every strategy might be written as the composition of some deterministic strategy with the denotation $\top_{\bN}$ of $\wn$.

      In this case, we have $\C'=I$ again, $\C''$ is our desired model of PCF with countable nondeterminism and $\C$ is its subcategory of deterministic strategies.  
      The functor $j$ sends $I$ to $\bN$ and the unique component of the natural transformation $\phi$ is the strategy $\top_{\bN}$.

    \item An example not relating to nondeterminism.  
      In the paper \cite{SamsonGuyIAPassive}, Abramsky and McCusker create a model of Idealized Algol based upon a category of games and \emph{visible} strategies.  
      One of the results they prove in the paper is that any visible strategy $\sigma\from I\to A$ may be written as the composition of an \emph{innocent} strategy $\tau\from \oc\Var[X]\implies A$ with the strategy $\cell_{X,x_0}\from I\implies\oc\Var[X]$, where $X$ is some set and $x_0\in X$.

      In this case, $\C'$ is the category of pointed sets, $\C$ is the category of games and innocent strategies and $\C''$ is the category of games and visible strategies.  
      The functor $J$ sends $(X, x_0)$ to the game $\Var[X]$, while the natural transformation $\phi$ is given by $\phi_{(X, x_0)} = \cell_{X,x_0}$.
  \end{enumerate}
\end{example}

We can phrase this factorization definition in terms similar to the ones we used above.

\begin{proposition}
  Let $\C',\C,\C''$ be monoidal categories and let $j\from \C'\to \C$ and $J\from \C\to \C''$ be functors, where $J$ is lax monoidal.

  Let $\phi$ be a dimonoidal natural transformation from $I$ to $J\circ j$ and suppose that $\C''$ satisfies $\phi$-factorization.

  Now suppose that $\D$ is some other category and that we have a lax monoidal functor $\H\from \C \to \D$ and a dimonoidal natural transformation $\psi\from I \to \H\circ J$.  
  Suppose also that we have a lax monoidal functor $\F\from \D\to\C''$ such that $\F\circ I = I$ and $\F\circ\H=J$.

  Then $\F$ is essentially surjective and full.
\end{proposition}

\subsubsection{Cones}

Let $\C'$, $\C$ be monoidal categories and let $j\from \C'\to \C$ be an oplax monoidal functor.

\begin{proposition}
  \label{prop:cone}
  There is a monoidal category $C_j$ together with a lax monoidal functor $J\from\C \to C_j$ and a dimonoidal natural transformation $\Phi$ from $I$ to $J\circ j$.  
  Moreover, $C_j$, $J$ and $\Phi$ are universal in the sense that if $\D$, $\H$ and $\psi$ are a similar triple, then there is a functor $\F\from C_j\to \D$ making ... commute.
\end{proposition}

\begin{proof}
  We first define the category $C_j$.  
  The objects of $C_j$ are the objects of $\C$.
  If $A,B$ are objects of $\C$, then the set of morphisms from $A$ to $B$ is the colimit of the diagram
  \[
    \begin{tikzcd}
      \oppcat{\C'} \arrow[r, "\oppcat j"]
        & \oppcat\C \arrow[r, "{\C[\blank\tensor A, B]}"]
          &[24pt] \Set
    \end{tikzcd}\,.
    \]
  That is, a morphism from $A$ to $B$ is a pair $(X, f)$, where $X$ is an object of $\C'$, $f$ is a morphism from $jX \tensor A \to B$ and $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute:
  \[
    \begin{tikzcd}
      j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
        & B \\
      j X \tensor A \arrow[ur, "f"']
        &
    \end{tikzcd}\,.
    \]
  We define composition as follows: let $A,B,C$ be objects of $\C$, let $X,Y$ be objects of $C'$, and let $f\from X\to A \implies B$, $g\from Y\tensor B\to C$ be morphisms in $\C$, so that $(X,\sigma)$ is a morphism from $A$ to $B$ and $(Y,\tau)$ a morphism from $B$ to $C$ in $C_j$.
  Then the composition of $\sigma$ with $\tau$ is given by the pair $(Y\tensor X,f;g)$, where $f;g$ is the following composite:
  \[
    \begin{tikzcd}[cramped]
      j(Y\tensor X)\tensor A \arrow[r, "m_j\tensor A"]
        & (jY \tensor jX) \tensor A \arrow[r, "\assoc"]
          &[-2pt] jY \tensor (jX \tensor A) \arrow[r, "jY \tensor f"]
            & jY \tensor B \arrow[r, "g"]
              &[-10pt] C
    \end{tikzcd}\,.
    \]
  Well-definedness and associativity of this composition are by standard coherence theorems for monoidal categories and lax monoidal functors.

  We will not define the monoidal structure on $C_j$ yet.  
  Instead, we will first prove its universal property, and then use that to derive the monoidal structure from that of $\C'$ and $\C$.

  First we define the functor $J\from \C\to C_j$ and the natural transformation $\Phi\from I\Rightarrow J\circ j$.  
  Given an object $A$ of $\C$, we set $J(A) = A$.  
  Given a morphism $f\from A \to B$ in $\C$, we set $J(f)$ to be the morphism $(I, \tilde{f})$ in $C_j$, where $\tilde{f}$ is the composite
  \[
    \begin{tikzcd}
      jI\tensor A \arrow[r, "\epsilon_j\tensor A"]
        & I\tensor A \arrow[r, "\lunit_A"]
          & A \arrow[r, "f"]
            & B
    \end{tikzcd}\,.
    \]

  If $X$ is an object of $\C'$, then we define a morphism $\Phi_X\from I \to JjX=jX$ to be given by $\Phi_X = (X, \phi_X)$, where $\phi_X$ is the morphism
  \[
    \begin{tikzcd}
      jX \tensor I \arrow[r, "\runit"]
        & jX
    \end{tikzcd}\,.
    \]

  We need to show that $\Phi$ is indeed a natural transformation.  
  In order to show that, let $X,Y$ be two morphisms and let $f\from X \to Y$ be a morphism.  
  We need to show that the following diagram commutes:
  \[
    \begin{tikzcd}
      I \arrow[r, "\phi_X"] \arrow[dr, "\phi_Y"']
        & J j X \arrow[d, "J j f"] \\
      %
        & J j Y
    \end{tikzcd}
    \]

  Computed inside the category $\C$, the top morphism is equal to the composite
  \[
    \begin{tikzcd}
      j (I \tensor X) \tensor I \arrow[r, "m_j\tensor I"]
        & (j I \tensor j X) \tensor I \arrow[r, "\assoc"]
          & j I \tensor (j X \tensor I) \arrow[r, "j I \tensor \runit"]
            & j I \tensor j X \arrow[r, "\epsilon_j\tensor j X"]
              & I \tensor j X \arrow[r, "\lunit"]
                & j X \arrow[r, "j f"]
                  & j Y
    \end{tikzcd}
    \]

  Suppose that we have a monoidal category $\D$, a monoidal functor $\H\from\C\to\D$ and a monoidal natural transformation $\psi\from I \to \H\circ j$.  
  We define a functor $\F\from C_j\to \D$ as follows: if $A$ is an object of $C_j$ then $A$ is, \emph{a priori}, an object of $\C$.  
  We set $\F(A) = \H(A)$.

  Meanwhile, if $f\from jX \tensor A \to B$ is a morphism from $A$ to $B$ in $C_j$, then we set $\F(f)$ to be the composite
  \[
    \begin{tikzcd}
      \H A \arrow[r, "\lunit\inv"]
        & I \tensor \H A \arrow[r, "\psi_X\tensor \H A"]
          &[18pt] \H j X \tensor \H A \arrow[r, "m_\H"]
            & \H(jX\tensor A) \arrow[r, "Hf"]
              & \H B
    \end{tikzcd}\,.
    \]
  \begin{remark}
    Here we see the connection with factorization results: the functor $\F$ is, in effect, `substituting in' the special morphisms $\psi_X$ to the arbitrary hole $X$ that we have introduced into the formula.
  \end{remark}

  \begin{SidewaysFigure}
    \[
      \begin{tikzcd}[ampersand replacement=\&, row sep=48pt, column sep=36pt, labels={description}]
        HjX \tensor HA \arrow[rrr, "m_H"] \arrow[rrd, "\lunit\inv"]
          \&
            \&
              \& H(jX \tensor A) \arrow[r, "Hf"] \arrow[ddd, "\lunit\inv"]
                \& HB \arrow[ddd, "\lunit\inv"] \\[24pt]
        %
          \& I \tensor (I \tensor HA) \arrow[r, "I\tensor(\psi_X\tensor HA)"' auto] \arrow[d, "\assoc\inv"] \arrow[ddr, "\psi_Y\tensor(\psi_X\tensor HA)"]
            \& I \tensor (HjX \tensor HA) \arrow[dd, "\psi_Y\tensor(HjX\tensor HA)"] \arrow[ddr, "I\tensor m_H"]
              \&
                \& \\
        %
          \& (I \tensor I) \tensor HA \arrow[d, "(\psi_Y\tensor\psi_X)\tensor HA"]
            \&
              \&
                \& \\
        I \tensor HA \arrow[uuu, "\psi_X\tensor HA"] \arrow[uur, "\lunit\inv"] \arrow[ur, "\lunit\inv\tensor H_A" description] \arrow[d, "\psi_{Y\tensor X}\tensor HA"] \arrow[dr, phantom, "\kreuz" yshift=6pt]
          \& (HjY \tensor HjX) \tensor HA \arrow[r, "\assoc"] \arrow[d, "m_H\tensor HA"]
            \& HjY \tensor (HjX \tensor HA) \arrow[d, "HjY\tensor m_H"]
              \& I \tensor H(jX \tensor A) \arrow[dl, "\psi_Y\tensor\id"] \arrow[r, "I\tensor Hf" auto]
                \& I \tensor HB \arrow[dl, "\psi_Y\tensor HB"] \\
        Hj(Y \tensor X) \tensor HA \arrow[r, "H(m_j)\tensor HA" auto] \arrow[d, "m_H"]
          \& H(jY \tensor jX) \tensor HA \arrow[d, "m_H"]
            \& HjY \tensor H(jX \tensor A) \arrow[r, "HjY\tensor Hf" auto] \arrow[d, "m_H"]
              \& HjY \tensor HB \arrow[d, "m_H"]
                \& \\
        H(j(Y \tensor X) \tensor A) \arrow[r, "H(m_j\tensor A)" auto]
          \& H((jY \tensor jX) \tensor A) \arrow[r, "H(\assoc)" auto]
            \& H(jY \tensor (jX \tensor A)) \arrow[r, "H(jY\tensor f)" auto]
              \& H(jY \tensor B)
                \&
      \end{tikzcd}
      \]
    2q~
    2t
    \caption{A diagram showing that the functor $\F$ we defined in the proof of Proposition \ref{prop:cone} preserves composition.  
    The trapezium marked \kreuz{} commutes because $\psi$ is a dimonoidal natural transformation; commutativity of the other cells comes from the standard monoidal theory.}
  \end{SidewaysFigure}

  We need to check that $\F\circ J = \H$.  
  This is certainly the case on objects.  
  For morphisms, let $A,B$ be objects of $\C$ and let $f\from A\to B$ be a morphism.  
  Then $\F J(f)$ is the following composite:
  \[
    \begin{tikzcd}
      \H A \arrow[d, "\lunit\inv"']
        &
          &
            & 
              & \H B \\
      I\tensor \H A \arrow[r, "\psi_I\tensor\H A"]
        & \H j I \tensor \H A \arrow[r, "m_\H"]
          & \H(jI \tensor A) \arrow[r, "\H(jI \tensor A)"]
            & \H(I \tensor A) \arrow[r, "\H\lunit"]
              & \H A \arrow[u, "\H f"']
    \end{tikzcd}\,.
    \]
  In order to show that this is in fact equal to $\H f$, it is sufficient to show that the composition of the middle four morphisms is equal to the left unitor $\lunit_{\H A}$:
  \[
    \begin{tikzcd}
      \H A
        &
          & \H(I\tensor A) \arrow[ll, "\H(\lunit_A)"', squiggly] \\
      I \tensor \H A \arrow[u, "\lunit_{\H A}"] \arrow[r, "\epsilon_\H\tensor\H A"] \arrow[dr, "\psi_I\tensor\H A"', squiggly]
        & \H I \tensor \H A \arrow[ur, "m_\H"]
          & \\
      %
        & \H j I \tensor \H A \arrow[u, "\H\epsilon_j\tensor\H A"'] \arrow[r, "m_\H", squiggly]
          & \H (jI \tensor A) \arrow[uu, "\H(\epsilon_j\tensor A)"', squiggly]
    \end{tikzcd}\,.
    \]
  Here, commutativity of the two trapezia comes from the fact that $\H$ is a monoidal functor and commutativity of the lower-left triangle is because $\psi$ is a dimonoidal natural transformation.

\end{proof}

\section{Denotational Semantics}

Let $\G$ be our game semantics model of PCF and let $\bN_{sw}$ be the one-object subcategory on the object $\oc \bN$ where the morphisms are the surjective winning strategies $\oc\bN\to\oc\bN$ and the tensor product of strategies is given by their composition.

Let $j\from \G_{sw}\to\G$ be the functor induced by the comonoid structure on $\oc \bN$.

Then the natural functor $J\from\G\to C_j$ induces a semantics for PCF on $C_j$.

Now given some term $M\from T$ of nondeterministic PCF, we may write $M$ as $C[\wn]$, where $C$ is a PCF context, where the hole may appear multiple times.  
We define the denotation $\deno{M}=\deno{C[\wn]}$ to be the following composite in $C_j$:
\[
  \deno{C[\wn]} =
  \begin{tikzcd}
    I \arrow[r, "\runit"]
      & I \tensor I \arrow[r, "\Phi_{\oc \bN}\tensor \deno{\lambda n.C[n]}"]
        &[48pt] \oc \bN \tensor (\oc \bN \implies \deno{T}) \arrow[r, "\text{eval}"]
          & \deno{T}
  \end{tikzcd}\,.
  \]
In other words, we have taken the denotation of the term $\lambda n.C[n]$ and substituted in the strategy $\Phi_{\oc \bN}$, which is our representation of the nondeterministic choice $\wn$.

$\deno{C[\wn]}$ is a morphism from $I$ to $\deno{T}$ in $C_j$, but it is an equivalence class of morphisms from $\oc N$ to $\deno{T}$ in $\G$.  
A particular representative of that equivalence class is given by the denotation of the term $\lambda n.C[n]$.  
We call this representative the \emph{canonical presentation} of $\deno{M}$.

\begin{lemma}
  \label{lem:sound-ad-lemma}
  Let $M=C[\wn]$ be a term of nondeterministic PCF of type $\nat$ and let $\pi$ be some evaluation of $M$.  
  Let $\sigma_M$ be the canonical presentation of $\deno{M}$; i.e., the denotation of $\lambda n.C[n]$.

  Then there is some total strategy $\sigma_\pi\from \oc\bN$ such that the composite $\sigma_\pi;\sigma_M$ captures the result of the evaluation $\pi$ as follows:
  \begin{itemize}
    \item If $\pi$ terminates at some value $m$, then $\sigma_\pi;\sigma_M$ is the strategy for $\bN$ that responds with the value $m$.
    \item If $\pi$ is infinite, then $\sigma_\pi;\sigma_M$ is the non-total strategy $\bot$ for $\bN$.
  \end{itemize}
\end{lemma}

\begin{proof}
  We use the fact that our base category $\G$ of games gives rise to a sound model for Idealized Algol.  
  For Hyland-Ong games, this model may be defined so that it is fully abstract \cite{SamsonGuyIAPassive}.  
  However, we will not require full abstraction for the model, so for Abramsky-Jagadeesan games we can use Laird's semantics for a PCF-like language with coroutines \cite{LairdCofCommCom}, since IA may be faithfully modelled within that language.

  Suppose first that $\pi$ is a finite evaluation.  
  Then $\pi$ gives rise to a finite sequence $n_1,\cdots, n_k$ of natural numbers corrseponding to the different choices of nondeterminism made during the evaluation of $\pi$.  
  We can now simulate the behaviour of $\wn$ during this evaluation by creating a (deterministic) device that will return these values in order each time it is called:
  \begin{align*}
    &N_{n_1,\cdots,n_k,d} \from (\nat \to \nat) \to \nat \\
    &N_{n_1,\cdots,n_k,d} = \lambda f . \new (\lambda v.v\coloneqq 0; f(v\coloneqq(\suc\deref v); \case_{k+1}\;\deref v\;\Omega\;n_1\;\cdots\;n_k\;d))\,.
  \end{align*}
  Here, $\case_k\;a\;n_0\;\cdots\;n_k\;d$ evaluates to $n_i$ if $a$ evaluates to $i$ and evaluates to $d$ if $a$ evaluates to a value greater than $k$.  
  This function maintains a new local variable $v$, which it increments each time it is called before looking up the appropriate value in the lookup table.

  By working through the construction of the denotational semantics of $\new$ as in \cite{SamsonGuyIAPassive}, we see that, for any term $F\from\nat\to\nat$, the denotation of $N_{n_1,\cdots,n_k,d}M$ is given by the composite
  \[
    I \xrightarrow{\cell_{\bN,0}}
      \oc \Var[\bN] \xrightarrow{\deno{\lambda v.v\coloneqq (\suc \deref v);\;\case_{k+1}\;\deref v\;\Omega\;n_1\;\cdots\;n_k\;d}}
        \oc \bN \xrightarrow{\deno{F}}
          \bN
    \]

  We write $\sigma_\pi\from I\to \oc\bN$ for the composite of the two arrows on the left.  
  Here, $d$ is some arbitrary natural number.  
  Its value does not affect the the composition $\sigma_\pi;\sigma_M$ and it is only included to satisfy the requirement that $\sigma_\pi$ be a total strategy.  
  Plays in $\sigma_\pi$ take the form
  \[
    q\;n_1\;q\;n_2\;\cdots\;q\;n_k\;q\;d\;q\;d\;\cdots
    \]
  or some subsequence thereof.

  Now $\sigma_\pi;\sigma_M$ is the denotation of the term $N_{n_1,\cdots,n_k}(\lambda n.C[n])$, which corresponds to evaluation of the term-in-context
  \[
    v\from\Var[\bN]\vdash v\coloneqq 0;\;C[v\coloneqq (\suc\deref v); \case_{k+1}\;\deref v\;\Omega\;n_1\;\cdots\;n_k\;d]\,.
    \]
  This term evaluates just as $C[\wn]$ does, except that we use the device we have constructed to simulate the nondeterministic numbers.  
  By following the evaluation of this term in parallel with the evaluation $\pi$ of $C[\wn]$, we can see that both evaluations have the same behaviour: they either both converge to the same number, or they both diverge.  
  By Soundness and Computational Adequacy for the model of Idealized Algol, this means that $\sigma_\pi;\sigma_M$ is the strategy for $\bN$ that captures the eventual behaviour of the evaluation path $\pi$.

  \begin{remark}
    This is the same as the common Software Engineering practice of `mocking' a random number generator for testing purposes by forcing it to always produce the same sequence of numbers.
  \end{remark}

  In the case that $\pi$ evaluates $\wn$ infinitely many times, producing numbers $n_1,n_2,\cdots$, we define approximants $N_{n_1,\cdots,n_k}$, which produce the numbers $n_1$ up to $n_k$ and then diverge the next time they are called.  
  We set $\sigma_\pi^{(k)}$ to be the denotation of $N_{n_1,\cdots,n_k,\Omega}$, considered as a strategy $I \to \oc \bN$ as above.  
  This time, the mocked nondeterminism will answer with $n_k$ each of the first $k$ times it is called, but will diverge on the $(k + 1)$-th time.
  Since $\pi$ evaluates $\wn$ infinitely many times, this means that $\sigma_\pi^{(k)};\sigma_M=\bot$.

  Set $\sigma_\pi$ to be the supremum of the $\sigma_\pi^{(k)}$, under the inclusion order.  
  Then, since composition is continuous with respect to inclusion in deterministic Game Semantics, $\sigma_\pi;\sigma_M$ must also be the divergent strategy $\bot$.

  It remains to show that $\sigma_\pi$ is a total strategy.  
  We can see this combinatorially by observing that each $\sigma_\pi^{(k)}$ has unique maximal play
  \[
    q\;n_1\;\cdots\;q\;n_k\;q\,,
    \]
  after which point the strategy has no reply.  
  This means that the supremum $\sigma_\pi$ has unique maximal play
  \[
    q\;n_1\;q\;n_2\;\cdots\,,
    \]
  which is infinite, and so the strategy is total.
\end{proof}

From this lemma, we may deduce Soundness and Computational Adequacy for our model.

\begin{proposition}[Soundness]
  Let $M=C[\wn]\from \nat$ be a term of nondeterministic PCF and let $\sigma\from\oc \bN \to\bN$ be its denotation.  If $M\mustconverge$ then $\sigma$ is a winning strategy.
\end{proposition}

\begin{proof}
  Suppose that $\sigma$ is not a winning strategy.  
  Then there is some play $qs\in\sigma$ such that $qstn\not\in\sigma$ for any sequence $t$ of moves in $\oc\bN$ and any $n\in\bN$.  
  This sequence $s$ is contained inside some strategy $\sigma_\pi$ for $\oc\bN$, which can be viewed, as in the proof of Lemma \ref{lem:sound-ad-lemma}, as capturing the behaviour of a particular evaluation path $\pi$ of the term $M$.  
  Clearly, we have $\sigma_\pi;\sigma=\bot$, and so Lemma \ref{lem:sound-ad-lemma} tells us that the evaluation path $\pi$ must diverge.  
  So $M\not\mustconverge$.
\end{proof}

\begin{proposition}[Computational Adequacy]
  Let $M\from \nat$ be a term of nondeterministic PCF and let $\sigma\from\oc \bN \to\bN$ be its denotation.  If $\sigma$ is a winning strategy then $M\mustconverge$.
\end{proposition}

\begin{proof}
  Suppose that $\sigma\from\oc \bN\to \bN$ is a winning strategy.  
  Let $\pi$ be an evaluation path for $M$.  
  We claim that $\pi$ converges to some value.  
  Indeed, there is some strategy $\sigma_\pi$ such that $\pi$ converges to a value if and only if $\sigma_\pi;\sigma$ is a winning strategy.  
  But $\sigma_\pi;\sigma$ is the composition of winning strategies, so it is winning.
\end{proof}

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2018-01-21 cones/paper/cones.tex
Started some new projects.

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan,10pt]{acmart}\settopmatter{}

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[LICS'18]{ACM/IEEE Symposium on Logic in Computer Science}{9-12 July, 2018}{Oxford, UK}
\acmYear{2018}
\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from traditional SIGPLAN
%% proceedings format to PACMPL format must update the
%% '\documentclass' and topmatter commands above; see
%% 'acmart-pacmpl-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
%\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
%\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\let\NOTARTICLE=1
\let\FEWFONTS=1
\let\BEAMER=1
\let\G\undefined
\let\C\undefined
\let\W\undefined
\let\U\undefined
\let\E\undefined
\input{../../common/preamble}
\renewcommand{\dv}{{\lightning}}
\newcommand{\oracle}{{\textsf{oracle}}}

\begin{document}

%% Title information
\title[Short Title]{Full Title}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Subtitle}                     %% \subtitle is optional
\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{W. J. Gowers}
\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0002-4513-9618}             %% \orcid is optional
\affiliation{
  \position{PhD Student}
  \department{Department of Computer Science}              %% \department is recommended
  \institution{University of Bath}            %% \institution is required
  \streetaddress{Claverton Down Road}
  \city{Bath}
  \postcode{BA2 7QY}
  \country{United Kingdom}                    %% \country is recommended
}
\email{W.J.Gowers@bath.ac.uk}

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
Text of abstract \ldots.
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10010124.10010131.10010133</concept_id>
<concept_desc>Theory of computation~Denotational semantics</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Theory of computation~Denotational semantics}
%% End of generated code

%% Keywords
%% comma separated list
\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}

Text of paper \ldots

\section{PCF with Countable Nondeterminism}

The language we shall study is similar to that given in \cite{LairdOrdinalGames}.  
It is the language formed by adding an unbounded natural-number choice primitive on to the base language PCF.  
That is, it is the language formed by taking the simply-typed $\lambda$-calculus over the ground type $\nat$, and adding the constants:
\begin{itemize}
  \item Structural constants $\0\from\nat$, $\suc,\pred\from\nat\to\nat$ and $\IfO \from \nat \to \nat \to \nat \to \nat$ for $\nat$
  \item Recursion combinators $\Y_T \from (T \to T) \to T$ for each $T$.
  \item Countable choice $\wn\from\nat$.
\end{itemize}

A small-step operational semantics for this language, taken from \cite{LairdOrdinalGames}, is given in Figure \ref{fig:op-sem}.
\begin{figure}
  \begin{mathpar}
    \inferrule*{ }{(\lambda x.M) N \opto M[N/x]}
    \and
    \inferrule*[right=$n\in\bN$]{ }{\wn\opto\n}
    \and
    \inferrule*{ }{\Y M \opto M (\Y M)}
    \and
    \inferrule*{ }{\IfO \0\;x\;y \opto x}
    \and
    \inferrule*{ }{\IfO (\suc \n)\;x\;y \opto y}
    \and
    \inferrule*{M \opto M'}{M N \opto M' N}
    \and
    \inferrule*{M \opto M'}{\suc M \opto \suc M'}
    \and
    \inferrule*{M \opto M'}{\pred M \opto \pred M'}
    \and
    \inferrule*{M \opto M'}{\IfO M \opto \IfO M'}
  \end{mathpar}
  \caption{Operational Semantics for a PCF-like language with countable nondeterminism.}
  \label{fig:op-sem}
\end{figure}
Our main task will be to give a Denotational Semantics for this language.

Given a term $M$ of ground type $\nat$, we say that $M$ \emph{must converge}, and write $M\mustconverge$, if every evaluation $\pi$ of $M$ (according to the operational semantics given in Figure \ref{fig:op-sem}) terminates at some numeral value.  
We write $M \converges \n$ if there exists some evaluation $\pi$ of $M$ that terminates at $\n$.

Given a type $T$, we define an order on the terms of type $T$, by saying that $M\lmam N$ if for all compatible contexts $C[-]$ of type $\nat$ we have
\begin{gather*}
  C[M]\converges\n\Rightarrow C[N]\converges \n \\
  C[M]\mustconverge\Rightarrow C[N]\mustconverge\,.
\end{gather*}

We say $M\emam N$ if $M\lmam N$ and $N\lmam M$.

One aspect of the language that makes it particularly difficult to model is that function application is not continuous, either with respect to functions or with respect to arguments.

For example, it is easy to write a sequence of functions ${<}\!n \from \nat \to \nat$ that return $0$ if their argument is less than $n$ and diverge otherwise:

\begin{align*}
  &{<}0 = \lambda m.\Omega \\
  &{<}1 = \lambda m.\IfO m\;\0\;\Omega \\
  &{<}2 = \lambda m.\IfO m\;\0\;(\IfO (\pred m)\;\0\;\Omega)\\
  \cdots
\end{align*}
It is easy enough to see (for example, by the denotational semantics) that the least upper bound of these functions is the function $\lambda x.\0$.  
However, it is clear that ${<}n\;\wn\not\mustconverge$ for each $n$, while $\lambda x.\0\;\wn$ must converge to $\0$.  
Thus, $\lambda x.\0\;\wn$ is not the least upper bound of the ${<}n\;\wn$.

This is a bit of a problem, since continuity often plays an important role in full abstraction proofs -- firstly, for proving Computational Adequacy of the recursion combinator, and, secondly, for deducing full abstraction from compact definability.  
Semantically, we shall deal with the first problem by adopting a novel approach to Computational Adequacy, and with the second problem by appealing to the stronger \emph{universality} result: namely, that every \emph{recursive} strategy is definable.

\section{The base model}

We will give a model based on Abramsky, Jagadeesan and Malacaria's Game Semantics for PCF \cite{ajmPcf}.  
We do this partly for the sake of simplicity, and partly to demonstrate the power of our methods -- since AJM games are typically seen as less flexible than the Hyland-Ong games of \cite{hoPcf}.  
However, we stress that our construction can be carried out just as well in Hyland and Ong's model, and we will keep this model in mind throughout, and mention whenever a slightly modified argument is needed for that model.

\subsection{Games}

A \emph{game} is a tuple $A=(M_A,\lambda_A,P_A)$, where
\begin{itemize}
  \item $M_A$ is a set of \emph{moves},
  \item $\lambda_A\from M_A \to \OP\times\QA$ is a function that designates each move as either a \emph{$P$-move} or an \emph{$O$-move}, and as either a \emph{question} or an \emph{answer}.
  \item $P_A$ is a non-empty prefix-closed set of finite sequences of elements of $M_A$ called \emph{positions}, satisfying the following two conditions:
    \begin{description}
      \item[Alternation] any non-empty position in $P_A$ starts with an $O$-move, and if $sab\in P_A$ then $a$ and $b$ have opposite signs - one is a $P$-move and the other an $O$-move.  
      \item[Well-bracketing] If $s\in P_A$, then the corresponding $QA$-sequence of questions and answers is well-bracketed.
    \end{description}
\end{itemize}

\subsection{Strategies}

A (deterministic) \emph{strategy} for a game $A$ is a non-empty, prefix-closed subset $sigma\subset P_A^+$ satisfying \emph{determinism}: if $sa,sb\in \sigma$ are both $P$-positions, then $a=b$.  
Here, $P_A^+$ is the set of $P$-positions in $A$.

We say that a strategy $\sigma$ is \emph{history-free} if whenever $sab,tac\in\sigma$ are both $P$-positions, then $b=c$.  
Such a strategy can be though of as a partial function $M_A^-\pfun M_A^+$, where $M_A^-$ is the set of $O$-moves and $M_A^+$ the set of $P$-moves in $A$.  
If this function can be given as a partial recursive function, we say that the strategy $\sigma$ is \emph{recursive}.

\subsection{Connectives}

Given games $A$ and $B$, we can define games $A\times B$, $A\tensor B$ and $A\implies B$ as follows:
\begin{itemize}
  \item $M_{A\times B}=M_{A\tensor B}=M_{A\implies B}=M_A+M_B$.  
  \item $\lambda_{A\times B}=\lambda_{A\tensor B}=[\lambda_A,\lambda_B]$.  
    $\lambda_{A\implies B}=[\neg\circ\lambda_A,\lambda_B]$, where $\neg\from\OP\times\QA\to\OP\times\QA$ is the function that exchanges $O$ and $P$ and leaves $Q$ and $A$ alone.
  \item $P_{A\times B}$ is the union of $P_A$ and $P_B$.  
    $P_{A\tensor B}$ and $P_{A\implies B}$ are defined by the following formula:
    \[
      \{s\in (M_A + M_B)^* \suchthat s\vert_A\in P_A,\;s\vert_B\in P_B,\;\text{$s$ is alternating}\}\,.
    \]
  Note that this is a different strategy for $P_{A\tensor B}$ and $P_{A\implies B}$, because the definition of an `alternating sequence' depends on the sign function $\lambda$.
\end{itemize}

\subsection{Composition of strategies}

Given strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$, we define a set
\[
  \sigma\|\tau = \{\s\in(M_A+M_B+M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}\,.
  \]
We then define
\[
  \sigma;\tau = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}\,.
  \]
It may be proved \cite{ajmPcf} that this notion of composition is associative and has identities given by the obvious copycat strategy for the game $A\implies A$.  
We therefore end up with a category whose objects are games and where the morphisms from a game $A$ to a game $B$ are the strategies for the game $A\implies B$.

It can also be shown that the composition of two history-free strategies is history free, and that the composition of two recursive strategies is recursive.  
Furthermore, the identity strategy is always history-free and recursive.

We write $\G$ for the category of games and strategies, $\G_{hf}$ for the category of games and history-free strategies, and $\G_{rec}$ for the category of games and recursive strategies.

Lastly, it is well-known that the connectives $\tensor$ and $\implies$ exhibit $\G$ as a monoidal closed category (with tensor unit the empty game $I$ with no moves) and that $\times$ gives products in $\G$.  
All these properties pass on to $\G_{hf}$ and $\G_{rec}$ in the expected way.

\subsection{Exponentials}

Given a game $A$, we define a game $\oc A$ as follows:
\begin{itemize}
  \item $M_{\oc A} = M_A\times\omega$.
  \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$.
  \item $P_{\oc A} = \{s\in M_{\oc_A}^* \suchthat \text{$s$ is alternating},\;s\vert_n\in P_A\forall n\}$.
\end{itemize}

It can be shown \cite{ajmPcf} that this construction gives rise to a \emph{linear exponential comonad} on $\G$, and therefore that the co-Kleisli category $\G^{\oc}$ is a Cartesian closed category.

\subsection{Modelling programming languages}

The results from \cite{ajmPcf} that we will be interested are the following:
\begin{itemize}
  \item $\G_{hf}$ is a fully abstract model of PCF.
  \item $\G_{rec}$ is also a fully abstract model of PCF.  
    Moreover, it is a \emph{universal} model: every morphism between the denotation of types is the denotation of a PCF term.
\end{itemize}

We will also be interested in a result of Laird \cite{LairdCofCommCom}, which tells us about the natural language for $\G$ itself:
\begin{itemize}
  \item $\G$ is a fully abstract model of $\lambda_{\text{co}}$, an extension of PCF with coroutines.
    In particular, $\G$ is a sound and adequate model of a stateful language such as Idealized Algol.
\end{itemize}

This result -- that our model of PCF may be embedded inside a game semantics model of a stateful language -- will be useful when we come to prove Computational Adequacy for our model.  
It is a result specific to AJM games.  
For Hyland-Ong games, the category of games and \emph{innocent} strategies, which is our model of PCF, may be embedded into the category of games and \emph{visible} strategies, which is actually a fully abstract model of Idealized Algol.  
However, we will only need soundness and adequacy, so we can carry out our proof with AJM games as well.

\section{Strategies for Nondeterminism}

The results that we have quoted in the previous section all apply to \emph{deterministic} PCF.  
For nondeterministic PCF, we follow the approach of Harmer and McCusker \cite{mcCHFiniteND}, who modelled nondeterministic programs using \emph{nondeterministic strategies}; i.e., strategies where we have relaxed the nondeterminism condition.  
So, for example, if we model the type $\nat$ by the game $\bN$ with maximal positions $qn$ for $n\in\bN$, where $q$ is a fixed opening move, then we can model the term $\wn$ by the strategy $\top_\nat$ that is the whole of $P_{\bN}$.

However, this model is not yet rich enough to model may-and-must equivalence.  
Consider, for example, the following two of terms of type $\nat$:
\begin{gather*}
  \IfO \wn\;\Omega\;\0 \\
  \0\,.
\end{gather*}
In the first case, there are two possibilities: either the program returns $\0$ or it diverges.
In the second case, the program always returns $\0$.

Since divergence is represented by \emph{partiality} in the strategy, these terms both have the same denotation: the strategy with unique maximal play $q0$.  
However, they are not must-equivalent, since $\0\mustconverge$, while the other term may diverge.  
The point is that in the first case the addition of the play $q0$ into the strategy obscures the partiality present in the denotation of $\Omega$.

Harmer and McCusker's solution to this problem is to augment each strategy by the addition of a set of \emph{divergences}: $O$-positions at which we signify that play may diverge.

Tracking divergences explicitly in this way requires some care when we compose strategies.  
Specifically, we need to be able to add new divergences into strategies when they arise through `infinite chattering' or \emph{livelock}.  
For example, the denotation of the term
\[
  M = \Y_{\nat\to\nat}(\lambda f.\lambda n.n;(f n))\,,
  \]
where $n;P$ is a shorthand for $\IfO n\;P\;P$, is given by a total strategy, without divergences: namely the strategy with plays of the form
\[
  \begin{array}{cc}
    \mathbf{\bN} & \mathbf{\bN} \\
    & q \\
    q & \\
    n_1 & \\
    q & \\
    n_2 & \\
    \vdots &
  \end{array}\,.
  \]
However, when we compose this strategy with any total strategy for $\bN$ on the left, we expect the resulting strategy to contain divergences, since the term $M \n$ diverges for any $\n$.

The approach adopted in \cite{mcCHFiniteND} is to check specifically for infinite chattering between strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ by checking whether the set $\sigma\|\tau$ contains any infinite increasing sequence of plays ending with moves in $B$.  
If there is such a sequence, then it restricts to some $O$-position in $\sigma;\tau$ and we add in a divergence at that position.

This works very satisfactorily for finite nondeterminism, but not at all for countable nondeterminism.  
To see why, consider the term
\[
  N = \Y_{\nat\to\nat\to\nat}(\lambda g.\lambda m n.\IfO m\;\0\;n;(g\;(\pred m)\;n))\wn
  \]
This term first chooses a natural number $m$, and then reads from its input $n$ for a total of $m$ times before eventually returning $\0$.  
Thus, its denotation is the strategy with maximal plays of the form:
\[
  \begin{array}{cc}
    \mathbf{\bN} & \mathbf{\bN} \\
    & q \\
    q & \\
    n_1 & \\
    \vdots & \\
    q & \\
    n_m & \\
    & 0
  \end{array}\,.
  \]
Note that this strategy strictly contains the one we considered before, and therefore that the denotation of
\[
  \IfO \wn M N
  \]
has the same denotation as $N$, even though it has all the divergent evaluations of $M$, while $N\n\mustconverge$ for all $\n$.
Moreover, if we try to compose $\deno{N}$ with the strategy on $\bN$ that always returns $1$, then we end up with an infinite increasing sequence of positions, which triggers the introduction of a divergence into the composite -- even though no divergence occurs in the evaluation of $N$.

Aside from making violating soundness for the model, this example actually leads to composition not being associative if we naively extend the Harmer-McCusker model from finite to infinite nondeterminism (e.g., see \cite[4.4.1]{RusssThesis}).

Somehow, the crucial point is that we need to distinguish between terms like $M$, which contain infinite sequences of moves, and terms like $N$, which contain arbitrarily large finite sequences of oves.  
The way that we do this is by making the infinite sequences of moves explicit in our strategies, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.  
Then the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitarily long finite sequences, but no infinite sequences.

The games in our model will be the same as those that we considered in the last section, but our definition of a strategy will change.

\subsection{Strategies}

Here, we follow \cite{mcCHFiniteND}, but with the addition of infinite positions.
Given a set $X\subset M^*$, we write $\bar{X}$ for the ideal closure of $X$; i.e., $X$ together with the set of all infinite sequences $s\in M^\omega$ all of whose finite prefixes are contained in $X$.

A \emph{strategy} for a game $A=(A,\zeta_A)$ is given by a pair $(T_\sigma, D_\sigma)$, where:
\begin{itemize}
  \item $T_\sigma$ is a prefix-closed subset of $\bar{P_A}$ such that if $s\in T_\sigma$ is a $P$-position and $sa\in P_A$, then $sa\in T_\sigma$.  
    In other words, $T_\sigma$ a nondeterministic strategy in the usual sense (possibly incorporating infinite plays).  
    We consider all infinite positions in $A$ to be $O$-positions.
  \item $D_\sigma\subset T_\sigma$ is a \emph{postfix}-closed set of $O$-positions satifying the following conditions:
    \begin{description}
      \item[All divergences arise from positions] If $d$ is minimal in $D_\sigma$ then either $d\in T_\sigma$ or $d$ is an infinite position that is the limit of positions in $T_\sigma$.
      \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position, then either $s\in D_\sigma$ or there exists $sa\in T_\sigma$.
      \item[Infinite positions are divergences] If $s\in T_\sigma$ is infinite, then $s\in D_\sigma$.
    \end{description}
\end{itemize}

We say that a strategy $\sigma$ is \emph{complete} if $T_\sigma=\bar{T_\sigma}$; i.e., if $s\in T_\sigma$ whenever $s$ is an infinite position, all of whose finite prefixes live in $T_\sigma$.  
For example, the denotation of $M$ above is complete, but the denotation of $N$ is not complete.

We say that $\sigma$ is \emph{locally complete} if $T_\sigma$ can be written as the union of complete strategies.

It is easy to see that the denotation of any term from nondeterministic PCF must be locally complete.  
An example of a strategy that is not locally complete is given by taking the denotation of $M$ above and considering it as a strategy with no infinite positions.  
The difference between this strategy and the denotation of $N$, is that every finite position in $N$ is eventually completed in the copy of $\bN$ on the right, so it is still locally complete.

We will require our strategies to be locally complete from here on.  
The problem with allowing non-locally complete strategies is that their composition does not necessarily satisfy the diverge-or-reply rule.

\subsection{Composition of strategies}

Let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be strategies.  
We define $T_{\sigma;\tau}$ in the usual way.  
In order to define $D_{\sigma;\tau}$, we first define
\[
  \sigma\dv\tau = \pocl\left\{\s\in\seqs{(M_A\cprd M_B\cprd M_C)}\;\middle|\; \mbox{\pbox{\textwidth}{\textbf{either} $\s\vert_{A,B}\in D_\sigma$\\ \hspace*{12pt}and $s\vert_{B,C}\in T_\tau$ \\ \textbf{or} $\s\vert_{A,B}\in T_\sigma$ \\\hspace*{12pt}and $s\vert_{B,C}\in D_\tau$}}\right\}\,,
  \]
where $\pocl X$ denotes the \emph{postfix closure} of $X$; i.e., the set of all $O$-positions in $A\implies C$ that have some prefix in $X$.

Lastly, we define
\[
  D_{\sigma;\tau} = \{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}\,.
  \]

We need to show firstly that composition preserves local completeness.  
This is not completely trivial, since the composition of \emph{complete} strategies need not be complete: for example, we may write $N=N'\;\wn$, where $N'$ is a deterministic strategy.  
Both $N'$ and $\wn$ have complete denotations, but their composite, $N$, has a denotation that is only locally complete.

However, we can show that the composition of \emph{deterministic} complete strategies $\sigma$ and $\tau$ is complete.  
The proof makes use of a lemma from \cite{abramskyjagadeesangames} that says that if $s\in\sigma;\tau$ is some position, where $\sigma$ and $\tau$ are both deterministic, then there is a unique minimal position $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.  
This means that if $s_1\prefix s_2\prefix \cdots$ is an infinite increasing sequence in $\sigma;\tau$, then there is a corresponding infinite increasing sequence $\s_1\prefix\s_2\prefix\cdots$ in $\sigma\|\tau$, whose limit must be contained in $\sigma\|\tau$ by completeness of $\sigma$ and $\tau$.  
It follows that the limit of $s_1,s_2,\dots$ is contained in $\sigma;\tau$.

Now the fact that composition preserves local completeness is an easy consequence of monotonicity of composition with respect to the prefix ordering, together with the fact that if a strategy $\sigma$ is locally complete -- i.e., if it is the union of some collection $(\sigma_\alpha)$ of complete strategies, then the $\sigma_\alpha$ may always be chosen to be deterministic.

We also need to prove that the composition of two strategies satisfies the diverge-or-reply rule.  
Once again, it is sufficient to prove this in the case that the strategies are both deterministic and complete.  
In that case, we can, for example, use the argument from \cite{abramskyjagadeesangames} that shows that a partiality in the composite $\sigma;\tau$ of two strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ (i.e., some $O$-position $s\in\sigma;\tau$ such that $sa\not\in\sigma;\tau$ for any $a$) must arise either from a partiality in one of $\sigma$ or $\tau$ or from an `infinite chattering' between the two strategies.  
A partiality in either of $\sigma$ or $\tau$ gives rise to a divergence in that strategy, by diverge-or-reply, and hence to a divergence at the appropriate place in $\sigma;\tau$.  
In the case that there is some infinite chattering between $\sigma$ and $\tau$; i.e., an infinite sequence $\s\in\bar{\sigma\|\tau}$ such that $\s\vert_{A,C}$ is finite, we must have $\s\in\sigma\|\tau$ by completeness for $\sigma$ and $\tau$.  
Therefore, $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both divergences in their respective strategies, and therefore $\s\vert_{A,C}\in D_{\sigma;\tau}$.

The last thing we need to show -- namely, that composition is associative -- follows in the usual way.  
The important difference between our model and that in \cite{mcCHFiniteND} is that in our model `divergence through infinite chattering' is an organic consequence of the usual definition of composition, not an extra condition that we have imposed upon the model.

To illustrate this, we return to our examples $M$ and $N$ above, and show how the composite $M\;1$ has a non-empty set of divergences, while $N\;1$ is divergence-free.

In order for the strategy denotation of $M$ to satisfy local completeness, it must contain all its infinite positions.  
Infinite positions in $\oc \bN$ are $P$-winning, so the corresponding positions in $\deno{M}\from \oc \bN\implies \bN$ are infinite $O$-positions and are therefore contained in $D_{\deno{M}}$.  
Since the play $q\in \oc\deno{1};\deno{M}$ is the restriction to $\bN$ of the infinite position
\[
  \begin{array}{cc}
    \bN & \bN \\
    & q \\
    q & \\
    1 & \\
    q & \\
    1 & \\
    \vdots &
  \end{array}
  \]
whose right-hand component is contained in $D_{\deno{M}}$, it must therefore be contained in $D_{\oc\deno{1};\deno{M}}$.

We contrast this with the situation with $N$.  
In this case, the strategy-denotation of $N$ contains \emph{no} infinite position, and we have $D_{\deno{N}}=\emptyset$.  
Since a divergence in the composition must arise from a divergence in one of the two component strategies, this means that $D_{\oc\deno{1};\deno{N}}$ is empty too.  
This is in contrast to the Harmer-McCusker model, in which $\sigma;\tau$ may contain a divergence even if neither $\sigma$ nor $\tau$ does.

\subsection{Proving Full Abstraction}

We write $\G_{ND}$ for the category we have defined.  
It may be made into a symmetric monoidal closed category in a straightforward way, following \cite{mcCHFiniteND}.  
Given $\sigma\from A\implies C$ and $\tau\from B\implies D$, $D_{\sigma\tensor\tau}$ is the set of all $s\in P_{(A\tensor B)\implies (C\tensor D)}$ such that either $s\vert_{A,C}\in D_\sigma$ or $s\vert_{B,D}\in D_\tau$.

Similarly, we can define exponentials in our model, where the divergences in $\oc\sigma$ are those positions that are divergent in one of their components.

Although we have solved the problems with associativity of composition, it turns out to be difficult to prove computational adequacy or full abstraction for this model.  
The main problem is a lack of continuity: we can follow \cite{mcCHFiniteND} and define an ordering on strategies, but composition is no longer continuous with respect to this ordering.  
This should not be seen as a defect of our model; indeed, we showed earlier on that the language we are trying to model has a similar lack of continuity, so if our model were continuous it would indicate that it did not model the language faithfully enough.

Our approach to proving full abstraction will be to define a new model $\C$ of our language that is fully abstract for nondeterministic PCF, and to show that $\C$ admits a faithful monoidal functor into $\G_{ND}$, which is enough to show that $\G_{ND}$ is also fully abstract.  
Before we do this, however, we outline an alternative argument that does not go via this supplementary category.  
The argument is suggested in \cite[3.7.2]{RusssThesis} as a means of defining an appropriate notion of `nondeterministic innocent strategy'.

We first define the strategy $\top_\bN$ on $\bN$ by $T_{\top_{\bN}}=P_{\bN}$ and $D_{\top_{\bN}}=\emptyset$.  
Then we say that a strategy $\sigma\from A\implies B$ is \emph{deterministic history free} if it can be written as
\[
  A \xrightarrow{\oracle_A}
    \oc \bN \tensor A \xrightarrow{\sigma'}
      B
  \]
where $\oracle_A=\lunit;\oc\top_\bN\tensor A$ and $\sigma'\from \oc\bN\tensor A \implies B$ is a deterministic, history-free strategy.
It is possible to show that the composition and tensor product of such strategies can again be written in this form, and it is then possible to prove full abstraction using properties of deterministic strategies.  
When we have defined our model $\C$, we will return to this point to show that the two arguments are essentially the same.

\section{Cones on Monoidal Functors}

\subsection{Surjective and winning strategies}

A useful fact about the category $\G$ of games and deterministic strategies, proved in \cite{hylandSchalkGames}, is that it admits a faithful, monoidal and linearly distributive functor into the category $\Rel$ of sets and relations, with monoidal structure given by the Cartesian product and exponentials given by the multiset comonad $W$.  
The functor sends a game $A$ to the set $P_A$ and sends a strategy $\sigma\from A\implies B$ to the relation
\[
  \grel{\sigma}=\{(s\vert_A,s\vert_B)\suchthat s\in\sigma\}\subset P_A\times P_B
  \]

Given a strategy $\sigma\from A\implies B$, we say that $\sigma$ is \emph{surjective} if $\grel{\sigma}$ is a surjective relation; i.e., if for any $b\in P_B$ there exists some $s\in\sigma$ such that $s\vert_B=b$.  
Monoidality and linear distributivity of the Hyland-Schalk functor $\G\to\Rel$ show that the composition of surjective strategies is surjective, as is the tensor product of surjective strategies and the bang of a surjective strategy.

Given a strategy $\sigma\from A\implies B$, we say that $\sigma$ is \emph{winning} if $\sigma$ is total and if for all positions $s\in\sigma$, if $sb\in\sigma$, where $b$ is an $O$-move in $B$, then there is some $t\in\sigma$ such that $sb\prefix t$ and $t$ ends with a move in $B$.

Once again, the composition, tensor product and bang of winning strategies is still winning.  
One way of seeing this is by relating our definition to the definition of a winning strategy given in \cite{abramskyjagadeesangames}, in which a game comes attached with a set of winning infinite positions.  
Then we say that a strategy $\sigma$ is winning if it is total and if every infinite position arising as the limit of plays in $\sigma$ is a winning position.  
If $A$ and $B$ are such that every infinite position is winning, then our notion of a winning strategy coincides with that notion.

The reason we are interested in surjective winning strategies is that they preserve top strategies:

\begin{lemma}
  We say that a game $A$ is \emph{$P$-winning} if for all $O$-positions $s\in P_A$ there exists some $a$ such that $sa\in P_A$.  
  Let $A,B$ be $P$-winning games, and let $\sigma\from A\implies B$ be a surjective winning strategy.  
  Write $\top_A$ for the (nondeterministic) strategy given by $T_{\top_A}=P_A$ and $D_{\top_A}=P_A^\omega$ (i.e., the only divergent plays are the infinite ones), and do the same for $B$.
  Then $\top_A;\sigma=\top_B$.  
\end{lemma}
\begin{proof}
  We can show that $T_{\top_A;\sigma}=T_{\top_B}$ from surjectivity of $\sigma$, using the Hyland-Schalk functor, since the equivalent result clearly holds in $\Rel$.  
  Now suppose that $s$ is some divergent position in $\top_A;\sigma$.  
  Then $s=\s\vert_B$, where $\s$ is a position in $\sigma$ and $\s\vert_A$ is a divergent position in $A$.
  Then $\s\vert_A$ must be infinite; since $\sigma$ is winning, this means that $\s\vert_B$ must be infinite as well, and therefore that $s\in D_{\top_B}$.  
  \label{lem:sw}
\end{proof}

We now define a category $\G_{sw}$ whose objects are $P$-winning games and where the morphisms from a game $A$ to a game $B$ are deterministic surjective winning strategies from $A$ to $B$.  
We write $\G_{sw,rec}$ for the category where the morphisms are \emph{recursive} surjective, winning strategies.

Write $j$ for the inclusion $\G_{sw,rec}\hookrightarrow\G_{rec}$, and write $J$ for the inclusion functor $\G\hookrightarrow\G_{ND}$ that sends a deterministic strategy $\sigma$ to the strategy given by $T=\sigma$ and $D=\pocl\{s\in\sigma^-\suchthat sa\not\in\sigma\forall a\}$
Then the lemma we have just proves means that
\[
  \top \from I \Rightarrow J\circ j
  \]
is a natural transformation, where $I$ is the constant $I$ functor.

Moreover, we would expect Lemma \ref{lem:sw} to hold in \emph{any} sensible game-semantics model of nondeterministic PCF, so the following makes sense as a definition

\begin{definition}
  A \emph{game semantics category for nondeterministic PCF} is a category $\D$ together with a functor $J\from \G_{rec}\to\D$ and a natural transformation $\top\from I\Rightarrow J\circ j\from\G_{sw,rec}\to\D$.  
\end{definition}

\subsection{Generalized monoidal natural transformations}

We will need one more technical definition.

Let $\C'$,$C'$,$\D'$,$\D$ be monoidal categories, let $f\from\C'\to\C$, $g\from \D'\to \D$ be oplax monoidal functors and let $F\from\D'\to\C'$, $G\from\D\to\C$ be lax monoidal functors, as in Figure \ref{fig:generalized-monoidal-setup}.

\begin{figure}
  \[
    \begin{tikzcd}[row sep=large, column sep=large]
      \D' \arrow[r, "F", ""'{name=F}] \arrow[d, "g"']
        & \C' \arrow[d, "f"] \\
      \D \arrow[r, "G"', ""{name=G}]
        & \C
      \arrow[Rightarrow, from=F, to=G, "\phi"]
    \end{tikzcd}
    \]
  \caption{A generalized monoidal natural transformation $\phi$ is a particular sort of natural transformation between composites of lax and oplax monoidal functors.}
  \label{fig:generalized-monoidal-setup}
\end{figure}

We say that a natural transformation $\phi\from fF\bigto Gg$ is a \emph{generalized monoidal natural transformation} if the following two diagrams commute for all objects $X,Y$ of $\D'$:
\begin{mathpar}
  \begin{tikzcd}
    f F X \tensor f F Y \arrow[r, "\phi_X \tensor \phi_Y"]
      & G g X \tensor G g Y \arrow[d, "m_G"] \\
    f (F X \tensor F Y) \arrow[u, "m_f"] \arrow[d, "f m_F"']
      & G (g X \tensor g Y) \\
    f F (X \tensor Y) \arrow[r, "\phi_{X \tensor Y}"]
      & G g (X \tensor Y) \arrow[u, "G m_g"']
  \end{tikzcd}
  \and
  \begin{tikzcd}[column sep=small, row sep=small]
    %
      & f F I_{\D'} \arrow[rr, "\phi_I"]
        &[-1.2em]
          &[-1.2em] G g I_{\D'} \arrow[dr, "G \epsilon_g"]
            & \\
    f I_{\C'} \arrow[ur, "f \epsilon_F"] \arrow[drr, "\epsilon_f"]
      &
        &
          &
            & G I_{\D} \\
    %
      &
        & I_{\C} \arrow[urr, "\epsilon_G"]
          &
            &
  \end{tikzcd}\,.
\end{mathpar}
The particular structure that generalized natural transformations fit into is that of a \emph{double category} (see \cite{LimitsInDoubleCategories} for the definition); in particular, the double category $\SymmMonCat$ introduced in \cite{AdjointsInDoubleCategories}, in which the objects are symmetric monoidal categories, the horizontal morphisms are lax symmetric monoidal functors, the vertical morphisms are oplax symmetric monoidal functors and the $2$-cells are generalized monoidal natural transformations as defined above.

Generalized monoidal natural transformations may thus be composed either horizontally or vertically in the usual way; i.e., given a pair of squares as in Figure \ref{fig:generalized-monoidal-setup} that may be pasted together along an edge, then we may define a generalized monoidal natural transformation across the pasted square.  
We write $\hc{\phi}{\psi}$ for the horizontal composition of natural transformations $\phi,\psi$ pasted together along an oplax monoidal functor and $\vc{\phi}{\psi}$ for the vertical composition of natural transformations $\phi,\psi$ pasted together along a lax monoidal natural functor.

\subsection{The cone of a monoidal functor}

Let $j\from \C'\to \C$ be an oplax monoidal functor.  
We define a \emph{$j$-category} to be a category $\D$ together with a lax monoidal functor $J\from\C\to\D$ and a generalized natural transformation $\phi\from I \to Jj$:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
      & I \arrow[d, "I"] \\
    \C \arrow[r, "J"', ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=J, "\phi"]
  \end{tikzcd}\,.
  \]
\begin{example}
  For example, our previous definition of a game semantics category for nondeterministic PCF can be thought of as a $j$-category, where $j$ is the inclusion functor $\G_{sw,rec}\hookrightarrow\G_{rec}$.  
\end{example}
We define a \emph{morphism of $j$-categories} going from a $j$-category $(\D',J',\phi')$ to a $j$-category $(\D,J,\phi)$ to be a lax monoidal functor $\F\from \D'\to\D$, sending $I$ to $I$, such that $J=\F\circ J'$ and $\phi$ is the vertical composition of $\phi'$ with the `identity transformation' given by this identity; i.e.:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
      & I \arrow[d, "I"] \\
    \C \arrow[r, "J'"'{name=Jprimedown}, ""{name=Jprime}] \arrow[d, "\id"']
      & \D' \arrow[d, "\F"] \\
    \C \arrow[r, "J", ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=Jprime, shift left=1.5ex, "\phi'"]
    \arrow[Rightarrow, from=Jprimedown, to=J, shift left=1.5ex, "\id"]
    \arrow[Rightarrow, from=term, to=J, shift right=3ex, "\phi"' near end]
  \end{tikzcd}\,.
  \]
Our main technical result in this section will be the following:
\begin{proposition}
  The category $j$-$\Cat$ of $j$-categories and $j$-category morphisms has an initial object $C_j$
\end{proposition}
By analogy with homotopy theory, we call this initial object the \emph{mapping cone} or \emph{cone} on $j$.

To see why this is useful, consider another important topic from the theory of semantics.  
We say that a $j$-category $(\D,J,\phi)$ satisfies \emph{$\phi$-factorization} if for any pair of objects $A$ and $B$ of $\C$ and for every morphism $f\from JA \to JB$ in $\D$, we may write $f$ as a composite
\[
  JA \xrightarrow{\lunit;\phi_X\tensor JA}
  Jj X \tensor JA \xrightarrow{m_J}
  J (jX \tensor A) \xrightarrow{J f'}
  JB\,,
  \]
where $X$ is some object of $\C'$ and $f'\from jX \tensor A\to B$ is some morphism in $\C$.
\begin{example}
  In the case that $j$ is the inclusion $\G_{sw,rec}\hookrightarrow\G_{rec}$, and $\phi=\top$, $\phi$-factorization is the same as \emph{deterministic factorization}: the idea that every morphism can be written as the composition of a deterministic recursive strategy with $\top_X$ for some $X$.
\end{example}

Then the following result is easy to prove:
\begin{proposition}
  Let $(\D,J,\phi)$ be a $j$-category satisfying $\phi$-factorization.  
  Suppose $\F\from\D'\to\D$ is a morphism of $j$-categories.  
  Then $\F$ is a full functor.
\end{proposition}
In particular, the unique $j$-category morphism $C_j\to\D$ is a full functor.  
This is useful, because we are viewing game semantic models of nondeterministic PCF as $j$-categories (for a particular $j$), and therefore we can see that $C_j$ admits a full functor into every such model that satisfies deterministic factorization.  
Since we typically require that our models satisfy such a factorization result, we can form any such model by taking $C_j$ and imposing some equivalence relation on the morphisms.  
This suggests that we might consider $C_j$ itself as our model of nondeterministic PCF.

\subsection{Constructing the cone}

We will now define what the cone $C_j$ is and give an outline of why it is initial in the category of $j$-categories.

Recall that we start with an oplax symmetric monoidal functor $j\from \C'\to\C$.  
The objects of $C_j$ are the objects of $\C$.  
Given objects $A,B$ of $\C$, the class of morphisms $A\to B$ is given by the colimit of the functor
\[
  \oppcat{\C'} \xrightarrow{\oppcat{j}}
  \oppcat{\C} \xrightarrow{\C[\blank\tensor A,B]}
  \Set\,.
  \]
That is, a morphism from $A$ to $B$ is a pair $(X,f)$, where $X$ is an object of $\C'$ and $f\from jX \tensor A \to B$ is a morphism in $\C$.  
Furthermore, $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute:
\[
  \begin{tikzcd}
    j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
      & B \\
    j X \tensor A \arrow[ur, "f"']
      &
  \end{tikzcd}\,.
  \]
Given morphisms $(X,f)\from A \to B$, $(Y,g)\from B \to C$, the composite is given by $(Y\tensor X,f;g)$, where $f;g$ is the following composite in $\C$:
\begin{align*}
  j(Y\tensor X)\tensor A & \xrightarrow{m_j\tensor A}
    (jY \tensor jX) \tensor A \\ & \xrightarrow{\assoc}
      jY \tensor (jX \tensor A) \\ & \xrightarrow{jY \tensor f}
        jY \tensor B \xrightarrow{g}
          C\,.
\end{align*}
We can prove that this composition is associative using the usual coherence theorems for monoidal categories.  
Similarly, the symmetric monoidal structure from $\C$ induces a symmetric monoidal structure on $C_j$.

There is a functor $J\from \C\to C_j$ that is the identity on objects and which sends a strategy $f\from A \to B$ to the strategy
\[
  j I \tensor A \xrightarrow{\epsilon_j\tensor A}
  I \tensor A \xrightarrow{\lunit\inv}
  A \xrightarrow{f} B\,.
  \]
This functor is (strong) symmetric monoidal with respect to the monoidal structure on $C_j$.  
Lastly, the natural transformation $\phi\from I \Rightarrow J\circ j$ is given by the composite
\[
  \phi_X = jX \tensor I \xrightarrow{\runit\inv}
  jX\,,
  \]
considered as a morphism from $I$ to $jX$ in $C_j$.  
Proving that this is indeed a natural transformation makes essential use of the equivalence relation on morphisms in $C_j$.  
We can also prove that $\phi$ is a generalized monoidal natural transformation.  
Therefore, $C_j$ is a $j$-category.

Now suppose that $(\D,F,\psi)$ is another $j$-category.  
We define a functor $H\from C_j\to\D$ that sends an object $A=JA$ in $C_j$ to the object $FA$ in $\D$.  
Moreover, we send a morphism $f\from jX\tensor A \to B$ from $JA$ to $JB$ in $C_j$ to the following composite in $\D$:
\begin{align*}
  FA \xrightarrow{\lunit;\psi_X\tensor FA}
  FjX \tensor FA \xrightarrow{m_F}
  F (jX \tensor A) \xrightarrow{F f}
  F B\,.
\end{align*}
Proving that this is indeed a functor is a little tricky, and relies on $\psi$ being a generalized monoidal natural transformation.  
We can then go through and check that $H$ is indeed a morphism of $j$-categories.

In order to prove uniqueness, note that, as a morphism of $j$-categories, $H$ is determined on morphisms of the form $Jf$ by the equation $F = H \circ J$ and on morphisms of the form $\phi_X$ by the equation $\psi=\vc{\phi}{H}$.  
But now, if $f\from jX\tensor A \to B$ is any morphism from $A$ to $B$ in $C_j$, we may write $f$ as the composite
\[
  JA \xrightarrow{\lunit;\phi_X\tensor A}
  JjX \tensor JA \xrightarrow{m_J}
  J (jX \tensor A) \xrightarrow{Jf}
  JB\,;
  \]
i.e., $C_j$ satisfies $\phi$-factorization.  
Since the functor $H$ is required to be monoidal, this implies that it is determined everywhere on $C_j$ by the requirement that it be a morphism of $j$-categories.
Therefore, $C_j$ is initial in the category of $j$-categories.

A consequence of the initiality of the cone construction is that it is \emph{functorial}; that is, given a square of the following form:
\[
  \begin{tikzcd}[row sep=large, column sep=large]
    \C' \arrow[r, "F", ""'{name=term}] \arrow[d, "j"']
      & \D' \arrow[d, "j'"] \\
    \C \arrow[r, "G"', ""{name=J}]
      & \D
    \arrow[Rightarrow, from=term, to=J, "\psi"]
  \end{tikzcd}\,,
  \]
where horizontal arrows correspond to lax monoidal functors and vertical arrows to monoidal functors, we get an induced lax monoidal functor $C_{j}\to C_{j}$, in a way that respects horizontal pasting of squares.

\section{Denotational Semantics}

In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

%% Bibliography
\bibliography{../../common/phd_bibliography}

%% Appendix
\appendix
\section{Appendix}

Text of appendix \ldots

\end{document}

### 2018-01-21 old_nondeterminism/paper/nondeterminism.tex
Started some new projects.

--- 2017-03-10 nondeterminism/paper/nondeterminism.tex
@@
 \begin{definition}
-  Let $A$ be a game.  A \emph{multistrategy} for $A$ is a stably directed set $\Sigma$ of strategies for $A$ such that for all $\sigma,\tau\in \Sigma$ we have $T_\sigma=T_\tau$.
-
-  Given a multistrategy $\Sigma$, we write $T_\Sigma$ for the unique value of $T_\sigma$, where $\sigma\in\Sigma$.
+  Let $A$ be a game.
+A \emph{multistrategy} for $A$ is a stably directed set $\Sigma$ of strategies for $A$.
+(So the set of multistrategies for $A$ is the free directed-completion of the set of strategies for $A$).
 
@@
 \begin{definition}
-  Let $A$ be a game and let $F$ be a set of multistrategies for $A$ that is directed with respect to $\stle$.  We define a strategy $\exlub F$ given by
-  \[
-    \exlub F = \left\{\left(\bigcup_{\Sigma\in F} T_\Sigma, D_\sigma\right)\;\middle|\;\textrm{$\sigma\in\Sigma$ for some $\Sigma\in F$}\right\}
-    \]
-\end{definition}
-
-\begin{proposition}
-  $\exlub F$ is a valid multistrategy for $A$.
-\end{proposition}
-  \begin{proof}
-    We need to show that for all $\Sigma\in F$ and for all $\sigma\in\Sigma$, $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)$ satisfies the diverge-or-reply rule.
-Let $\Sigma\in F$ and let $\sigma\in\Sigma$.
-Suppose that $s\in T_\Tau$ for some $\Tau\in F$, that $sa\in P_A$ and that $sa\not\in D_\sigma$.
-Since $F$ is stably directed, there exists some multistrategy $\Upsilon\in F$ such that $\Sigma,\Tau\stle\Upsilon$.
-Let $\tau\in\Tau$.
-Then there are $\upsilon_1,\upsilon_2\in\Upsilon$ such that $\sigma\stle\upsilon_1$ and $\tau\stle\upsilon_2$.
-Then, since $\Upsilon$ is stably directed, there is some $\upsilon\in\Upsilon$ such that $\upsilon_1,\upsilon_2\stle\upsilon$.
-In particular, $s\in T_\upsilon$ and $sa\not\in D_\upsilon$.
-Therefore, $sab\in T_\upsilon$ for some $b$ and so $sab\in\bigcup_{\Sigma\in F}T_\Sigma$.
-  \end{proof}
+  Let $A$ be a game and let $F$ be a set of multistrategies for $A$ that is directed with respect to $\stle$.
+The least upper bound of $F$ is given by the union of the multistrategies contained in $F$:
+  \[
+    \exlub F = \bigcup_{\Sigma\in F}\Sigma
+    \]
+\end{definition}
 
@@
   \begin{proof}
-    Let $\Sigma\in F$ and let $\sigma\in\Sigma$.  Then we have $\sigma\stle\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)\in\exlub F$.  So $\exlub F$ is a $\stle$-upper bound for $F$.
-
-    Now suppose that $\Xi$ is some other $\stle$-upper bound for $F$.
-Then for all $\Sigma\in F$ we must have $T_\Sigma\subset T_\Xi$ and so $\bigcup_{\Sigma\in F}T_\Sigma\subset T_\Xi$.
-Now suppose that $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)$ is some element of $\exlub F$, where $\Sigma\in F$ and $\sigma\in\Sigma$.
-We have $\Sigma\stle\Xi$, so there exists some $\xi\in\Xi$ such that $\sigma\stle\xi$.
-We have $\xi = (T_\Xi, D_\xi)$, where $D_\xi\subset D_\sigma$.
-Therefore, $\left(\bigcup_{\Sigma\in F}T_\Sigma,D_\sigma\right)\stle\xi$.
-It follows that $\exlub F\stle\Xi$.
+    Let $\Sigma\in F$.
+Then for each $\sigma\in\Sigma$, we have $\sigma\stle\sigma\in \exlub F$.
+So $\Sigma\stle\exlub F$.
+Conversely, suppose that $\Xi$ is some other upper bound for $\Sigma$.
+Let $\sigma\in \exlub F$.
+Then $\sigma\in \Sigma$ for some $\Sigma\in F$.
+Therefore, since $\Sigma\stle\Xi$, there is some $\xi\in \Xi$ such that $\sigma\stle\xi$.
+Therefore, $\exlub F\stle\Xi$.
   \end{proof}
@@
   \[
-    \icomp\Tau\Sigma = \left\{\icomp\tau{\left(\exlub_{\sigma\in\Sigma}\sigma\right)}\;\middle|\;\tau\in\Tau\right\}
+    \icomp\Tau\Sigma = \left\{\exlub_{\sigma\in\Sigma}(\icomp\tau\sigma)\suchthat\tau\in\Tau\right\}
     \]
@@
 The reason for this is the failure of composition of strategies to be continuous.
-It is possible that we could modify the model to make it associative, but we will not need associativity.
-
-What is clear is that composition is monotonic with respect to the stable ordering on multistrategies.  In fact, we it is even continuous with respect to functions (up to $\steq$).
+However, we can show that $\icomp{\{\upsilon\}}{(\icomp\Tau\Sigma)}=\icomp{(\icomp{\{\upsilon\}}\Tau)}\Sigma$ for all multistrategies $\Sigma,\Tau$ and all strategies $\upsilon$.
+Similarly, $\icomp{\{\id\}}{\{\sigma\}}=\{\sigma\}$ and $\icomp{\Sigma}{\{\id\}}=\{\Sigma\}$ for all strategies $\sigma$ and multistrategies $\Sigma$.
+We will not use these facts directly here, but it might be useful for future work to work out what the principles are behind our argument.
+
+What is clear is that composition is monotonic with respect to the stable ordering on multistrategies.  Our main point of interest is that $\comp\Tau\Sigma$ is now continuous with respect to $\Tau$.
 
@@
       \[
-        \icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma \steq \exlub_{\Tau\in F}(\icomp\Tau\Sigma)
+        \icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma = \exlub_{\Tau\in F}(\icomp\Tau\Sigma)
         \]
@@
   (i): We have $\Sigma\stle\Sigma'$ and it follows that $\exlub_{\sigma\in\Sigma}\sigma\stle\exlub_{\sigma\in\Sigma'}\sigma$ by Proposition \ref{exlubIsStlub} and the definition of $\stle$ for multistrategies.
-Then, if $\icomp\tau{\left(\exlub_{\sigma\in\Sigma}\right)}$ is an arbitrary element of $\icomp\Tau\Sigma$, we know that there exists some $\tau'\in \Tau'$ such that $\tau\stle\tau'$.
+Then, if $\exlub_{\sigma\in\Sigma}\icomp\tau\sigma$ is an arbitrary element of $\icomp\Tau\Sigma$, we know that there exists some $\tau'\in \Tau'$ such that $\tau\stle\tau'$.
 Now we have
   \[
-    \icomp\tau{\left(\exlub_{\sigma\in\Sigma}\sigma\right)}\le\icomp{\tau'}{\left(\exlub_{\sigma\in\Sigma'}\sigma\right)}\in\icomp{\Tau'}{\Sigma'}
-    \]
-  by Proposition \ref{compositionMonotonicSO}.
-
-  (ii): By part (i), $\icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma$ is an upper bound for $\{\icomp\Tau\Sigma\suchthat \Tau\in F\}$ and therefore we have
-  \[
-    \exlub_{\Tau\in F}(\icomp\Tau\Sigma)\stle\icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma
-    \]
-  by Proposition \ref{exlubIsStlub}.  For the other direction, we may write:
+    \exlub_{\sigma\in\Sigma}\icomp\tau\sigma\stle\exlub_{\sigma\in\Sigma}\icomp{\tau'}{\sigma}
+    \]
+  by Proposition \ref{compositionMonotonicSO}, together with usual properties of least upper bounds.
+
+  (ii): We have:
   \begin{align*}
-    \icomp{\left(\exlub_{\Tau\in F}\Tau\right)}{\Sigma} & = \left\{\icomp\tau{\exlub_{\sigma\in\Sigma}\sigma}\;\middle|\;\tau\in\exlub_{\Tau\in F}\Tau\right\} \\
-      & = \left\{\icomp{\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)}{\exlub_{\sigma\in\Sigma}\sigma}\;\middle|\;\textrm{$\tau\in\Tau$ for some $\Tau\in F$}\right\}
+    \icomp{\left(\exlub_{\Tau\in F}\Tau\right)}\Sigma & = \left\{\exlub_{\sigma\in\Sigma}(\icomp\tau\sigma)\suchthat\tau\in\bigcup_{\Tau\in F}\Tau\right\} \\
+      & = \bigcup_{\Tau\in F}\left\{\exlub_{\sigma\in \Sigma}(\icomp\tau\sigma)\suchthat\tau\in\Tau\right\} \\
+      & = \exlub_{\Tau\in F}\left(\icomp\Tau\Sigma\right)
   \end{align*}
-  while we have 
-  \begin{align*}
-    \exlub_{\Tau\in F}(\icomp\Tau\Sigma) & = \exlub_{\Tau\in F}\left\{\icomp\tau{\exlub_{\sigma\in\Sigma}\sigma}\;\middle|\;\tau\in\Tau\right\} \\
-      & = \left\{\left(\bigcup_{\Tau\in F}T_{\icomp{\Tau}{\exlub \Sigma}},D_{\icomp\tau{\exlub\Sigma}}\right)\;\middle|\;\textrm{$\tau\in\Tau$ for some $\Tau\in F$}\right\}
-  \end{align*}
-  Write $\tau_*$ for $\icomp{\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)}{\exlub_{\sigma\in\Sigma}\sigma}$ and $\tau^*$ for $\left(\bigcup_{\Tau\in F}T_{\icomp{\Tau}{\exlub \Sigma}},D_{\icomp\tau{\exlub\Sigma}}\right)$.
-We want to show that $\tau_*\stle\tau^*$ for all $\tau$ such that $\tau\in \Tau$ for some $\Tau\in F$, which will complete the proof.
-
-  We first claim that $T_{\tau_*}=T_{\tau^*}$.
-Indeed, if $s\in T_{\tau_*}$ then $s=\s\vert_{A,C}$, where $\s\vert_{A,B}\in\bigcup_{\Tau\in F}T_\Tau$ and $\s\vert_{B,C}\in T_{\exlub\Sigma}$.
-It follows that $s\in\bigcup_{\Tau\in F}T_{\icomp{\Tau}{\exlub\Sigma}}$.
-Conversely, if $s\in\bigcup_{\Tau\in F} T_{\icomp{\Tau}{\exlub\Sigma}}$, then we have $s\in\icomp{\Tau'}\Sigma$ for some $\Tau'\in F$, so $s\in T_{\tau_*}$.
-
-  Now all we need to show is that $D_{\tau^*}\subset D_{\tau_*}$.
-We have $D_{\tau^*}=D_{\icomp{\tau}{\exlub\Sigma}}$.
-So if $d\in D_{\tau^*}$ then there is some $\d\in\left(\exlub_{\sigma\in\Sigma}\sigma\right)\dv\tau$ such that $\d\vert_{A,C}\prefix d$.
-If $\d\vert_{A,B}\in T_{\exlub \Sigma}$ and $\d\vert_{B,C}\in D_\tau$ then certainly $\d\in \left(\exlub_{\sigma\in\Sigma}\sigma\right)\dv\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)$.
-Otherwise, $\d\vert_{A,B}\in D_{\exlub \Sigma}$ and $\d\vert_{B,C}\in T_\tau$.
-But now, since $T_\tau\subset \bigcup_{\Tau\in F}T_\Tau$, we again have $\d\in \left(\exlub_{\sigma\in\Sigma}\sigma\right)\dv\left(\bigcup_{\Tau\in F}T_\Tau,D_\tau\right)$.
-Therefore, $d\in D_{\tau_*}$.
 \end{proof}
@@
 Note that our definition of composition $\icomp\Tau\Sigma$ is not necessarily continuous with respect to $\Sigma$.
+For example, if $\Tau=\{\tau\}$ is a singleton strategy and $F$ is a set of multistrategies composable with $\Tau$, then $\exlub_{\Sigma\in F}(\icomp{\{\tau\}}\Sigma$ may contain multiple elements, but $\icomp{\{\tau\}}{\left(\exlub_{\Sigma\in F}\Sigma\right)}$ is always a singleton.
 
@@
   We have $\Sigma\in S$, so for all $\sigma\in\Sigma$ we have $\comp{\comp\sigma\tau}{\comp{\sigma_1}{\comp{\cdots}{\sigma_k}}}\plot_\nat\Y_TNN_1\dots N_k$.
+By a standard argument, $\chi_A\plot_{((T\to T)\to T)\to(T\to T)\to T}\lambda F.\lambda f.f(F f)$ and so we have
+  \[
+    \icomp{\chi_A}{\icomp{\sigma}{\icomp{\tau}{\icomp{\sigma_1}{\icomp{\dots}{\sigma_k}}}}}\plot_{\nat}(\lambda F.\lambda f.f(F f))\Y_T N N_1\dots N_k
+    \]
+  Therefore:
+  \[
+    \icomp{\chi_A}{\icomp{\sigma}{\icomp{\tau}{\icomp{\sigma_1}{\icomp{\dots}{\sigma_k}}}}}\plot_{\nat}N(\Y_T) N N_1\dots N_k
+    \]
+  Therefore, by part Lemma \ref{jims2ndLemma}, part (i), we have
+  \[
+    \icomp{\chi_A}{\icomp{\sigma}{\icomp{\tau}{\icomp{\sigma_1}{\icomp{\dots}{\sigma_k}}}}}\plot_{\nat}\Y_T N N_1\dots N_k
+    \]
+  Since $N,N_1,\dots,N_k,\tau,\sigma_1,\dots,\sigma_k$ were arbitrary, we see that $\icomp{\chi_A}{\sigma}\plot_{(T\to T)\to T}\Y_T$.
 \end{proof*}

### 2018-01-21 old_nondeterminism/presentation/presentation.tex
Started some new projects.

\documentclass{beamer}

\let\NOTARTICLE=1
\let\BEAMER=1
\let\FEWFONTS=1

\newenvironment{theindex}
 {\let\item\par
  %definitions for subitem etc
  }{}
\newcommand\indexspace{}

\input{../../common/preamble}

\newtheorem{proposition}{Proposition}

%%% END Article customizations

\title{Games for countable nondeterminism}
\subtitle{GaLoP 2017, Uppsala}

\author{John Gowers}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\section*{Outline}
\begin{frame}
  \tableofcontents
\end{frame}

\section{Game Semantics of Nondeterminism}

\renewcommand*{\arraystretch}{3}

\begin{frame}[allowframebreaks]
  \frametitle{Related Work}
  \nocite{mcCHFiniteND, RusssThesis, TsukadaSheaves, RoscoeCspInfinite, LevyGsInfinite, LairdOrdinalGames}
  \bibliographystyle{plain}
  \bibliography{../../common/phd_bibliography}
\end{frame}

\begin{frame}
  \frametitle{Nondeterministic Strategies}

  \pause
  If $A$ is a game with a set $P_A$ of positions, a strategy $\sigma$ for $A$ is a non-empty prefix-closed subset of $P_A^P$ satisfying:
  \begin{description}
    \item[Determinism] If $sa,sb\in\sigma$, then $a=b$
    \item[Totality] If $s\in\sigma$ and $sa\in P_A$, then $sab\in\sigma$ for some $b$
  \end{description}
  \pause
  Relaxing \emph{totality} gives us \emph{partial strategies}.
  \pause

  Relaxing \emph{determinism} gives us \emph{nondeterministic strategies}.
  \pause

  Problem: how can we model divergence in nondeterministic strategies?
\end{frame}

\begin{frame}
  \frametitle{The Harmer-McCusker model}
  \pause

  Harmer and McCusker model nondeterminism by equipping each (nondeterministic) strategy with an explicit set of divergent positions.  
  \pause

  Divergence in a composition of strategies may arise either from a divergence in one of the strategies we are composing, or through \emph{livelock} (infinite chattering).  
  \pause

  This method only works for finite nondeterminism: if we naively relax the finite branching condition, then composition is not associative.  
\end{frame}

\begin{frame}
  \frametitle{Failure of associativity in the presence of infinite branching}
  \begingroup
  \renewcommand*{\arraystretch}{1}
  \[
    \begin{array}{ccccccccc}
      \mathbf{I} & & \mathbf{\Sigma^*} & & \mathbf{\bN} & \tensor & \mathbf{\Sigma^*} & & \mathbf{\Sigma} \\
       & &   & &   & &   & & q \\
       & &   & & q & &   & &   \\
       & &   & & 2 & &   & &   \\
       & &   & &   & & q & &   \\
       & & q & &   & &   & &   \\
       & & a & &   & &   & &   \\
       & &   & &   & & a & &   \\
       & &   & &   & & q & &   \\
       & & q & &   & &   & &   \\
       & & a & &   & &   & &   \\
       & &   & &   & & a & &   \\
       & &   & &   & &   & & a
    \end{array}
    \]
  \endgroup
\end{frame}

\begin{frame}
  \frametitle{Solution: keep track of infinite sequences of moves}
  A game $A$ is now given by a tuple $(M_A, \lambda_A, \zeta_A, P_A)$ where
  \begin{itemize}
    \item $M_A$ is a set of moves
    \item $\lambda_A\from M_A\to \OP$ identifies each move as an $O$-move or a $P$-move
    \item $P_A\subset \seqs{M_A}$ is a set of legal positions
    \item $\zeta_A\from P_A\to\OP$ designates each position as an $O$-position or a $P$-position
  \end{itemize}
  \dots subject to a few rules
\end{frame}

\begin{frame}
  \frametitle{Advantages}
  \pause
  We can distinguish between computations that diverge and computations that converge, but may take an arbitrarily large number of steps to do so.

  \pause
  We do not have to check for infinite chattering explicitly when defining the divergences of a composition of strategies.

  \pause
  Composition is associative.
\end{frame}

\begin{frame}
  \frametitle{Fair PCF}
  \[
    \begin{array}{cc}
      \inferrule*{ }{(\lambda x.M)N\opto M[N/x]} & \inferrule*{ }{\Y_T M\opto M(\Y_T M)} \\
      \inferrule*{ }{\IfO \0 \opto \lambda x.\lambda y.x} & \inferrule*{ }{\IfO (\suc \n) \opto \lambda x.\lambda y.(y \n)} \\
      \inferrule*{M\opto M'}{\suc M\opto\suc M'} & \inferrule*{M\opto M'}{\IfO M\opto \IfO M'} \\
      \inferrule*{M \opto M'}{M N \opto M' N} & \inferrule*[right=$n\in\bN$]{ }{\wn \opto \n} \\
    \end{array}
    \]

\end{frame}

\begin{frame}
  \frametitle{Must-testing for fair PCF}
  If $M$ is a term of Fair PCF of ground type $\nat$, write $M\mustconverge$ if $M$ has no infinite evaluation paths $M\opto M_1\opto M_2\opto\cdots$.

  \pause
  Examples:
  \begin{itemize}
    \item $\Omega_\nat=\Y_\nat(\lambda x.x)\not\mustconverge$
      \pause
    \item $\IfO \wn \;\Omega_\nat \;\0\not\mustconverge$
      \pause
    \item $\Y_{\nat\to\nat} (\lambda f.\lambda x.\IfO x\;\0\;f)\wn\mustconverge$
  \end{itemize}
\end{frame}

\begin{frame}
  \pause
  \frametitle{Denotational Semantics for $\Y_T$}
  Harmer and McCusker define an order $\stle$ on strategies for a game $A$:

  $\sigma\stle\tau$ if
  \begin{enumerate}
    \item $\sigma\subset\tau$
    \item Every divergent position in $\tau$ is divergent in $\sigma$
    \item Every position in $\tau\setminus\sigma$ is divergent in $\sigma$.  
  \end{enumerate}

  \pause
  The order $\stle$ is preserved by composition.

  \pause
  If $F$ is a set of strategies that is directed with respect to $\stle$ then $F$ has a least upper bound given by
  \[
    \left(\bigcup_{\sigma\in F}\sigma\;,\;\bigcap_{\sigma\in F}D_\sigma\right)
    \]
\end{frame}

\begin{frame}
  \frametitle{Denotational semantics for $\Y_T$}

  This means that we can define a strategy $\Y_A$ for $(A\iimpl A) \iimpl A$ to be the least fixed point of the strategy corresponding to the $\lambda$-term
  \[
    \lambda F.\lambda f.f(F f)
    \]
  \pause
  However, $\stle$-limits are not preserved by composition (in either direction), so it is hard to prove computational adequacy for this denotation of $\Y_T$.
\end{frame}

\section{Ordinal-Indexed Recursion}

\begin{frame}
  \frametitle{Introduction to Ordinal-Indexed Recursion}
  \pause
  In languages with no nondeterminism or finite nondeterminism, we can study $\Y_T$ by studying its finite approximants $\Y_T^n$, where:
  \[
    \Y_T^n M = \underbrace{M\cdots M}_{n}\Omega_T
    \]
  \pause
  If $Y_T M M_1\dots M_n\mustconverge$, then $\Y_T^n M M_1\dots M_n\mustconverge$ for some $n$ -- since branching is finite, any well-founded evaluation tree is \emph{bounded}.

  \pause
  However, in the presence of infinite branching, we may have well-founded evaluation trees that are not bounded.

  \pause
  For example, $\Y_{\nat\to\nat}(\lambda f.\lambda x.\IfO x\; \0\; f)\wn\mustconverge$, but $\Y_{\nat\to\nat}^n(\lambda f.\lambda x.\IfO x\; \0\; f)\wn\not\mustconverge$ for all $n$.  
\end{frame}

\begin{frame}
  \frametitle{Introduction to Ordinal-Indexed Recursion}
  We replace $\Y_T$ with a new family of constants $\Y_T^\alpha$, where $\alpha$ ranges over countable ordinals and a formal divergence symbol $\Omega_T$.  $\Y_T^\alpha$ has operational semantics given by:
  \[
    \inferrule*[right=$\beta<\alpha$]{ }{\Y_T^\alpha M\opto M(\Y_T^\beta M)}\hspace{24pt}
    \inferrule*{ }{\Y_T^0M\opto\Omega_{T}}
    \]
  \pause
  If $M\mustconverge$, then the evaluation tree for $M$ is well-founded and hence has complexity given by some countable ordinal $\alpha$.  If we replace $\Y$ with $\Y^\alpha$ in the description of $M$, then we can recover the original evaluation tree.

  \pause
  However, the new term will have additional branches, some of which will diverge.

  \pause
  We want the choice of ordinal $\beta$ to be `friendly', so that it does not affect the behaviour of $\mustconverge$.  
\end{frame}

\begin{frame}
  \frametitle{Big-Step semantics for $\mustconverge$ in Fair PCF}

  We can get round this problem using big step semantics.

  \pause
  We add the following rule for $\wn$ to the usual big-step semantics for $\mustconverge$ in PCF:
  \[
    \inferrule{\forall n\in\omega\esuchthat M n\mustconverge}{M\wn\mustconverge}
    \]
  \pause
  We then give big-step semantics for the constants $\Y_T^\alpha$:
  \[
    \inferrule{\exists \beta<\alpha\esuchthat M(\Y_T^\beta M) M_1\cdots M_n\mustconverge}{\Y_T^\alpha MM_1\cdots M_n\mustconverge}
    \]
\end{frame}

\begin{frame}
  \frametitle{An example}
  \begin{IEEEeqnarray*}{Cl}
    &\Y_{\nat\to\nat}^\omega (\lambda f.\lambda x.\IfO x\;\0\;f)\;\wn\\
    \pause
    \opto &((\lambda f.\lambda x.\IfO x\;\0\;f) \Y_{\nat\to\nat}^n(\lambda f.\lambda x.\IfO x\;\0\;f))\;\wn\\
    \pause
    \opto &\IfO \wn\;\0\;(\Y^n_{\nat\to\nat}(\lambda f.\lambda x.\IfO x\;\0\;f)) \\
    \pause
    \opto &\IfO (n+1)\;\0\;(\Y^n_{\nat\to\nat}(\lambda f.\lambda x.\IfO x\;\0\;f))\\
    \pause
    \opto &\cdots\opto\Omega_{\nat}
    \pause
  \end{IEEEeqnarray*}
  \begin{IEEEeqnarray*}{Cl}
    &\Y_{\nat\to\nat}^{\omega+1}(\lambda f.\lambda x.\IfO x\;\0\;f)\;\wn\\
    \pause
    \opto &((\lambda f.\lambda x.\IfO x\;\0\;f) \Y_{\nat\to\nat}^\omega(\lambda f.\lambda x.\IfO x\;\0\;f))\;\wn\\
    \pause
    \opto &\IfO \wn\;\0\;(\Y^\omega_{\nat\to\nat}(\lambda f.\lambda x.\IfO x\;\0\;f)) \\
    \pause
    \opto &\IfO m\;\0\;(\Y^\omega_{\nat\to\nat}(\lambda f.\lambda x.\IfO x\;\0\;f))\\
    \pause
    \opto &\Y^\omega_{\nat\to\nat}(\lambda f.\lambda x.\IfO x\;\0\;f)\;m\\
    \pause
    \opto &(\lambda f.\lambda x.\IfO x\;\0\;f)\Y_{\nat\to\nat}^{m+1}(\lambda f.\lambda x.\IfO x\;\0\;f)\;m\\
    \pause
    \opto&\cdots\opto\0
  \end{IEEEeqnarray*}
\end{frame}

\begin{frame}
  \frametitle{Can we model $\Y_T^\alpha$ within the language?}
  \pause
  Recall that we could model $\Y_T^n M$ within PCF as
  \[
    \underbrace{M\cdots M}_{n}\Omega_T
    \]
  \pause
  We can do this uniformly if we add a recursion constant $\rec_T\from \nat\to T\to(T\to T)\to T$ to the language.  Then we can model
  \[
    \Y_T^n = \lambda F.\rec_T n\;\Omega_T\;F
    \]
  \pause
  But how would we model $\Y_T^\omega$?  We need to add friendly choice to the language....
\end{frame}

\begin{frame}
  \frametitle{Explicit friendly choice}
  \pause
  We add a new constant to our language:
  \[
    \nw\from\nat
    \]
  \pause
  We give big-step semantics for $\mustconverge$ corresponding to $\nw$:
  \[
    \inferrule{\exists n\in\omega\esuchthat Mn\mustconverge}{M\nw\mustconverge}
    \]
  Then we may model $\Y_T^\omega$ as:
  \[
    \Y_T^\omega = \lambda F.\rec_T \nw\;\Omega_T\;F
    \]
  \pause
  Going further, we may model $\Y_T^{\omega+1}$ as $\lambda F.F(\rec_T\nw\;\Omega_T\;F)$, and so on.

  \pause
  How far can we go?
\end{frame}

\begin{frame}
  \frametitle{Defining recursion principles using friendly choice}
  \pause
  Suppose that we can define an ordinal $\alpha$ in our language as a Church encoding:
  \[
    \alpha_T\from T \to (T \to T) \to ((\nat \to T) \to T) \to T
    \]
  \pause
  Then we can simulate $\Y_T^\alpha$ within our language:
  \[
    \Y_T^\alpha\equiv \lambda F.\alpha_T\;\Omega_T\;F\;(\lambda f.f\nw)
    \]
  \pause
  Using  $\rec_T$, it is possible to define Church encodings $\alpha_T$ for all ordinals $\alpha<\epsilon_0$, so we can simulate $\Y_T^\alpha$ for all $\alpha<\epsilon_0$ in PFC - $\Y$ + $\rec$ + $\nw$.
\end{frame}

\section{Game Semantics for Friendly Choice}

\begin{frame}
  \frametitle{Friendly vs. unfriendly choice: a 2-player game within the language}
  \pause
  Suppose we have a constant
  \begin{gather*}
    \Iflt\from\nat\to\nat\to\nat\to\nat\to\nat
  \end{gather*}
  in our language with the obvious meaning.

  \pause
  Consider the terms
  \begin{gather*}
    \Iflt \wn\;\nw\;\0\;\Omega_\nat\\
    \Iflt \nw\;\wn\;\Omega_\nat\;\0
  \end{gather*}
  \pause
  Because of evaluation order, the first term must converge, but the second may diverge.

  \pause
  With more complicated predicates, we can encode more complicated (bounded) Gale-Stewart games in the language.
\end{frame}

\begin{frame}
  \frametitle{Game Semantics for Friendly Choice}
  \pause
  We need the ability to make all choices at once, but forget about the bad ones (unless all our choices were bad).

  \pause
  If $A$ is a game, then a \emph{flexible strategy} for $A$ is a pair $\Sigma=(\sigma_\Sigma,F_\Sigma)$, where $\sigma_\Sigma$ is a strategy for $A$ and $F_\Sigma\subset\sigma_\Sigma$ is a set of positions in $\sigma_\Sigma$ that are forced.  All other positions in $\sigma$ are optional.

  \pause
  Then a \emph{switching} for $\Sigma$ is a strategy $\sigma'$ for $A$ such that $\sigma'\subset\sigma_\Sigma$ and such that if $s\in\sigma'$ and $sab\in F_{\Sigma}$ then $sab\in\sigma'$.  In this case, we write $\sigma'\sw\Sigma$.

  \pause
  Given flexible strategies $\Sigma\from A\to B$ and $\Tau\from B\to C$, we may form the composite:
  \[
    \comp{\Tau}{\Sigma} = \exlub_{\substack{\sigma'\sw\Sigma\\\tau'\sw\Tau}}\comp{\tau'}{\sigma'}
    \]
\end{frame}

\begin{frame}
  \frametitle{Game semantics for friendly choice}
  \pause
  We embed the original game semantics into the flexible game semantics by sending $\sigma\mapsto|\sigma|\coloneqq(\sigma,\sigma)$.

  \pause
  So $\wn$ inherits its original semantics as $(\wn, \wn)$.

  \pause
  We give $\nw$ an explicitly flexible semantics:
  \[
    \deno{\nw} = (\wn, \{\emptyplay\})
    \]
  \pause
  So all the choices of number in $\nw$ are optional.  
  \pause
  We get a consistency result:
  \begin{proposition}
    If $M$ is a term of PCF - $\Y$ + $\wn$ + $\nw$ of type $\nat$ such that $M\mustconverge$, then there are no divergent positions in $\deno{M}$.  
  \end{proposition}
\end{frame}

\begin{frame}
  \frametitle{Stable ordering for flexible strategies}
  \pause
  We can extend the stable order $\stle$ to flexible strategies.

  \pause
  We say that $\Sigma\stle\Tau$ if $\sigma_\Sigma\stle\sigma_\Tau$ and $\sigma_\Sigma\cap F_\Tau\subset F_\Sigma$.

  \pause
  Then we have least upper bounds for stably-directed sets $X$ of flexible strategies:
  \begin{gather*}
    \sigma_{\exlub_{\Sigma\in X}\Sigma} = \exlub_{\Sigma\in X}\sigma_\Sigma \\
    F_{\exlub_{\Sigma\in X}\Sigma} = \bigcap_{\Sigma\in X}F_\Sigma
  \end{gather*}
  \pause
  $\exlub_{\Sigma\in F}\Sigma$ is a `friendly choice between the $\Sigma\in F$'.

  \pause
  We can then construct the $\Y_T^\alpha$ as the elements of the Bourbaki-Witt chain.

  \pause
  For suitably large $\alpha$ (conjecturally $\alpha=\epsilon_0$), we get a sound and adequate semantics for $\Y_T$.  
\end{frame}

\end{document}

### 2018-01-21 round-corner/paper/lipics-v2016-authors/submission/sequoidal.tex
Started some new projects.

--- 2017-05-30 round-corner/paper/lipics-v2016-authors/sequoidal.tex
@@
 \subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
-\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator}% mandatory: Please provide 1-5 keywords
+\keywords{Game semantics, Stateful languages, Transfinite games, Sequoid operator}% mandatory: Please provide 1-5 keywords
 % Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \newcommand{\W}{\mathcal W}
-\newcommand{\suchthat}{\;\colon\;}
-\newcommand{\varsuchthat}{\;\mid\;}
+\newcommand{\suchthat}{\,\colon\,}
+\newcommand{\varsuchthat}{\,\mid\,}
 \newcommand{\OP}{\{O,P\}}
@@
 The non-commutative sequoid operator $\sequoid$ on games was introduced  to capture algebraically the presence of state in history-sensitive strategies in game semantics, by imposing a causality relation on the  tensor product of games.
-Coalgebras for the  functor  $A\sequoid\blank$  --- i.e.
-morphisms from $S$ to $A \sequoid S$ --- may be viewed as state transformers:  if $A\sequoid\blank$ has a \emph{final coalgebra}, $\oc A$, then the anamorphism of such a state transformer encapsulates its explicit state, so that it is shared only between successive invocations.
+Coalgebras for the  functor  $A\sequoid\blank$  --- i.e., morphisms from $S$ to $A \sequoid S$ --- may be viewed as state transformers:  if $A\sequoid\blank$ has a \emph{final coalgebra}, $\oc A$, then the anamorphism of such a state transformer encapsulates its explicit state, so that it is shared only between successive invocations.
 
@@
 
-\subsection{Defining Higher-order Stateful Objects Coalgebraically}
+\subsection{Defining Higher-order Stateful Objects, Coalgebraically}
 Let us first motivate the study of the coalgebraically derived cofree comonoid in game semantics by considering a similar but simpler and more familiar phenomenon. 
@@
 For example, consider the category $\Rel$ of sets and relations, with symmetric monoidal structure given by the Cartesian product (with unit $I$, the singleton set $\{*\}$).
-This has finite (bi)products (disjoint unions), so we may define the functor $F(A,S) = (A \otimes S) \oplus I$.
-For any object (set) $A$, let $A^*$ be the set of finite sequences of elements of $A$, and let $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*))\}\cup  \{(aw,\inl(a,w))\suchthat a \in A,w \in A^*\}$.
+This has finite (bi)products (disjoint unions) so we may define the functor $F(A,S) = (A \otimes S) \oplus I$.
+For any object (set) $A$, let $A^*$ be the set of finite sequences of elements of $A$ (i.e.
+the carrier of the free monoid on $A$), and $\alpha:A^* \rightarrow F(A,A^*)$ be the morphism $\{(\varepsilon,\inr(*)\}\cup  \{(aw,(\inl(a,w))\ |\ a \in A,w \in A^*\}$.
 It is straightforward to show that:
-\begin{lemma}[\cite{Hasuo07generictrace}] $(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
+\begin{lemma}$(A^*,\alpha_A)$ is the final coalgebra  for $F(A,\_)$.
 \end{lemma}
-Since we have a natural transformation $J\from F(A,S) \rightarrow F(A,S\oplus 1)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $\tilde{f}=[f;\inl_{A,S};J, \inr]:S\oplus 1 \rightarrow F(A,S\oplus 1)$, --- i.e.
+Since we have a natural transformation  $\inl_{A,S}:A \otimes S \rightarrow F(A,S)$, we may encapsulate the state in the  state transformer $f:S \rightarrow A \otimes S$ by taking the \emph{anamorphism} of $\tilde{f} = (f;\inl_{A,S})\cup\{(s,\inr (*))\suchthat s\in S\}\from S \rightarrow F(A,S)$, --- i.e.
 the unique $F(A,\_)$-coalgebra morphism from $(S,\tilde{f})$ into $(A^*,\alpha_{A})$.
-This  is  a morphism from $S$ into $A^*$ corresponding to the initial value of the state: by definition, composing it with $\alpha:A^* \rightarrow F(A,A^*)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ together with the encapsulated morphism with updated internal state.
-
- Distributivity of $\oplus$ over $\otimes$ gives us a morphism $F(A,S) \oplus F(A',S)\to F(A \oplus A',S)$.
-This allows us to construct stateful objects compounded of a series of methods sharing access to a common state.
+This  is  a morphism from an initial state $S$ into $A^*$: by definition, composing it with $\alpha:A \rightarrow F(A,A^*)$ (which we can think of as  \emph{invoking} our stateful object) returns a copy of $f$ together with the encapsulated morphism with updated internal state.
+
+ Distributivity of $\oplus$ over $\otimes$ implies that $F(A \oplus A',S) \cong F(A,S) \oplus F(A',S)$.
+This allows state transformers to be aggregated, to construct stateful objects compounded of a series of methods which share access to a common state.
 For example, we may represent a reference cell storing integer values as a state transformer $\cell:\Na \rightarrow (\Na \oplus \Na) \otimes \Na$, obtained by aggregating two ``methods'' which share access to a value in $\Na$ representing the contents of the cell --- returning a ``read'' of the input state (and leaving it unchanged) or accepting a ``write'' of a new value and using it to update the state.
 Thus (with appropriate tagging) it is the relation $\{(i, (\read(i),i))\suchthat i \in \Na\} \cup \{(i,({\mathtt{write}}(j),j))\suchthat i,j\in\Na\}$.
-The anamorphism of the coalgebra $\cell^{\textasciitilde}:\Na\oplus 1 \rightarrow F(\Na \oplus \Na,\Na\oplus 1) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots*)$.
+The anamorphism of the coalgebra $\cell^{\textasciitilde}\from\Na \rightarrow F(\Na \oplus \Na,\Na) $  is the relation from $\Na$ to $(\Na \oplus \Na)^*$ consisting of pairs of the form $(i_1,\read(i_1)^*{\mathtt{write}}(i_2)\read(i_2)^*\ldots)$.
 Composition with this morphism is precisely the interpretation of new variable declaration in the semantics  in $\Rel$ of the prototypical functional-imperative language \emph{Syntactic Control of Interference} (SCI) given in \cite{Mcsci}.
@@
 In fact, this is the \emph{cofree comonoid} on $A$ --- there is a morphism $\eta_A:A^* \rightarrow A = \{(a,a)\ | \ a \in A\}$ such that for any comonoid $(B,\delta_B,\epsilon_B)$, composition with $\eta_A$ defines an equivalence (natural in $B$)  between the morphisms from $B$ into $A$, and the comonoid morphisms from $(B,\delta_B,\epsilon_B)$ into  $(A^*,\delta_A,\epsilon_A)$.
-\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $A$ in $\Rel$.\footnote{The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
+\begin{proposition}$(A^*,\delta,\epsilon)$ is the cofree comonoid on $\Rel$.\footnote{The definitions of $\delta$ and $\epsilon$, and the proof that this is the cofree comonoid  may be derived from the fact that $(A^*,\alpha_A)$ is a \emph{bifree algebra} for $F(\_, A)$  --- i.e.
 $(A^*,\alpha^{-1})$ is an initial algebra for $F(A,\_)$ ($\alpha$ must be an isomorphism by Lambek's lemma).
@@
 This structure can be used to interpret procedures which share access to a stateful resource such as a reference cell.      
-Its main limitation is that we have not defined a \emph{commutative} comonoid  for any set $A$ of size at least $2$ (evidently, $\delta$ is not invariant under post-composition with the symmetry isomorphism of the tensor).
+Its main limitation is that we have not defined a \emph{commutative} comonoid  for any non-empty set $A$ (evidently, $\delta$ is not invariant under post-composition with the symmetry isomorphism of the tensor).
 Thus we can only model procedures with shared access to the same stateful object if the order in which they are permitted to access it is fixed.
@@
 Hence, we turn to the richer structures of game semantics.
+
  \subsection{The cofree commutative comonoid as a final coalgebra}

### 2018-01-21 round-corner/paper/lipics-v2016-authors/without_appendix/sequoidal.tex
Started some new projects.

--- 2018-01-21 round-corner/paper/lipics-v2016-authors/submission/sequoidal.tex
@@
 % Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1}}
+\title{Sequoidal Categories and Transfinite Games: A Coalgebraic Approach to Stateful Objects in Game Semantics\footnote{This work was partially supported by UK EPSRC Grant EP/K037633/1.
+Full version with appendix available at \cite{RoundCorner}.}}
 \titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column
@@
 \begin{proof}
-  See Appendix.
+    See Appendix to full version \cite{RoundCorner}
 \end{proof}
@@
 
-\appendix
-
-\section{Proofs}
-
-\subsection{Proof of Proposition \ref{StrongMonoidalFunctorActual}}
-
-\begingroup
-\def\thetheorem{\ref{StrongMonoidalFunctorActual}}
-\begin{proposition}
-  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.
-Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\epsilon$, where $\epsilon$ is the anamorphism of the composite $I \xrightarrow{runit} I \tensor I \xrightarrow{*\tensor\id} 1\tensor I\xrightarrow{\wk}1\sequoid I$.
-\end{proposition}
-\addtocounter{theorem}{-1}
-\endgroup
-
-In order to show that $\sigma\mapsto\oc\sigma$ respects composition, we need the following lemma:
-
-\begin{lemma}\label{aFormulaForAlpha}
-  Let $A$ be an object of $\C$.  Then $\alpha_A\from\oc A\to A\sequoid\oc A$ is equal to the following composite:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\mu_A"]
-        & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id_{\oc A}"]
-          & A \tensor \oc A \arrow[r, "\wk_{A,\oc A}"]
-            & A \sequoid \oc A
-    \end{tikzcd}
-    \]
-\end{lemma}
-
-\begin{proof}
-  We may paste together the anamorphism diagrams for $\int_A$ and $\sigma_A$ to form the following diagram (where we shall omit subscripts where there is no ambiguity):
-  \begin{equation*}
-    \begin{tikzcd}[cramped]
-      \oc A \arrow[r, "\alpha"] \arrow[d, "\sigma_A"']
-        & A \sequoid \oc A \arrow[r, "\Delta"]
-          &[-24pt] (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[r, "\dist\inv"]
-            & (A \times A) \sequoid \oc A \arrow[d, "\id_{A\times A}\sequoid\sigma_A"] \\
-      \oc(A\times A) \arrow[rrr, "\alpha"]
-        &
-          &
-            & (A \times A) \sequoid \oc(A\times A) \\
-      \oc A \tensor \oc A \arrow[rr, "\kappa_{A,A}"] \arrow[u, "\int_A"]
-        &
-          & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "\dist\inv"]
-            & (A\times A)\sequoid(\oc A \tensor \oc A) \arrow[u, "\id_{A\times A}\sequoid\int_A"']
-    \end{tikzcd}
-  \end{equation*}
-  where we observe that the composites down the left and right hand sides (after inverting the lower arrows) are $\mu_A$ and $\id_{A\times A}\sequoid\mu_A$.
-
-  Now note that we have the following commutative square:
-  \[
-    \begin{tikzcd}
-      (A \times A) \sequoid \oc A \arrow[r, "\dist"] \arrow[d, "\id_{A\times A}\sequoid\mu_A"']
-        & (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[d, "(\id\sequoid\mu)\times(\id\sequoid\mu)"] \\
-      (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[r, "\dist"']
-        & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A))
-    \end{tikzcd}
-    \]
-
-  (using the definition of $\dist$).  Putting this together with the diagram above, we get the following commutative diagram:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\alpha"] \arrow[d, "\mu_A"']
-        & A \sequoid \oc A \arrow[r, "\Delta"]
-          & (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[d, "\id\sequoid\mu_A\times\id\sequoid\mu_A"] \\
-      \oc A \tensor \oc A \arrow[rr, "\kappa_{A,A}"]
-        & \cdots \arrow[r]
-          & (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A))
-    \end{tikzcd}
-    \]
-  We now expand the definition of $\kappa_{A,A}$  and take the projections on to the first and second components, yielding the following two commutative diagrams:
-  \[
-    \begin{tikzcd}\label{firstProjectionDiagram}
-      \oc A \arrow[rrr, "\alpha"] \arrow[d, "\mu_A"']
-        &
-          &
-            & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
-      \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"]
-        & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"]
-          & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            & A \sequoid (\oc A \tensor \oc A)
-    \end{tikzcd}\tag{\textbf{1}}
-    \]
-
-  \begin{equation*}\label{secondProjectionDiagram}
-    \begin{tikzcd}[cramped]
-     \oc A \arrow[rrrr, "\alpha"] \arrow[d, "\mu_A"']
-        &
-          &
-            &
-              & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
-      \oc A \tensor \oc A \arrow[r, "\sym"']
-        & \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id" yshift=0.4em]
-          & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\comp{\passoc\inv}{\wk}" yshift=0.4em]
-            & A \sequoid (\oc A \tensor \oc A) \arrow[r, "\id\sequoid\sym"']
-              & A \sequoid (\oc A \tensor \oc A)
-    \end{tikzcd}\tag{\textbf{2}}
-  \end{equation*}
-
-  From diagram \eqref{firstProjectionDiagram}, we construct the following commutative diagram:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[rrr, "\alpha"] \arrow[d, rightsquigarrow, "\mu_A"'] \arrow[phantom, drrr, "\textbf{a}" xshift=0.9em]
-        &
-          &
-            & A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
-      \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"] \arrow[ddr, rightsquigarrow, "\der_A\tensor\id"'] \arrow[phantom, dr, "\textbf{b}" xshift=0.6em]
-        & (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "(\id\sequoid*)\tensor\id"] \arrow[phantom, dr, "\textbf{c}" xshift=0.3em]
-          & (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"] \arrow[d, "(\id\sequoid*)\sequoid\id"] \arrow[phantom, dr, "\textbf{e}" xshift=0.3em]
-            & A \sequoid (\oc A \sequoid \oc A) \arrow[d, "\id\sequoid(*\tensor\id)"] \\
-      %
-        & (A \sequoid I) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "\run\tensor\id"] \arrow[phantom, dr, "\textbf{d}" xshift=0.3em]
-          & (A \sequoid I) \sequoid \oc A \arrow[r, "\passoc\inv"], \arrow[d, "\run\tensor\id"] \arrow[phantom, r, "\textbf{f}" xshift=-0.6em, yshift=-1.0em]
-            & A \sequoid (I \tensor \oc A) \arrow[dl, "\id\sequoid\lunit"] \\
-      %
-        & A \tensor \oc A \arrow[r, rightsquigarrow, "\wk"]
-          & A \sequoid \oc A
-            &
-    \end{tikzcd}
-    \]
-
-  \textbf{a} is diagram \eqref{firstProjectionDiagram}.
-
-  \textbf{b} commutes by the definition of $\der_A$.
-
-  \textbf{c} and \textbf{d} commute because $\wk$ is a natural transformation.
-
-  \textbf{e} commutes because $\passoc$ is a natural transformation.
-
-  \textbf{f} commutes by one of the coherence conditions in the definition of a sequoidal category.
-
-  We now observe that the composite of the three squiggly arrows is the composite we are trying to show is equal to $\alpha$; we have $\alpha$ along the top, so it will suffice to show that the composite
-  \[
-    \begin{tikzcd}
-      \xi_A\;=\;\oc A \arrow[r, "\mu_A"]
-        & \oc A \tensor \oc A \arrow[r, "*\tensor\id"]
-          & I \tensor \oc A \arrow[r, "\lunit"]
-            & \oc A
-    \end{tikzcd}
-    \]
-  is equal to the identity.  We do this using diagram \eqref{secondProjectionDiagram}.  First we construct the diagram shown in Figure \ref{hugeDiagram1}.
-
-  \begin{SidewaysFigure}
-    \[
-      \begin{tikzcd}[ampersand replacement=\&]
-        \oc A \arrow[rrrrr, "\alpha"] \arrow[d, "\mu_A"'] \arrow[phantom, drrrrr, "\textbf{a}"]
-          \&
-            \&
-              \&
-                \& 
-                  \& A \sequoid \oc A \arrow[d, "\id\sequoid\mu_A"] \\
-        \oc A \tensor \oc A  \arrow[r, "\sym"] \arrow[d, "*\tensor\id"'] \arrow[phantom, dr, "\textbf{b}"]
-          \& \oc A \tensor \oc A \arrow[r, "\alpha\tensor\id"] \arrow[d, "\id\tensor*"]
-            \& (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"] \arrow[d, "\id\sequoid*"] \arrow[phantom, dr, "\textbf{d}"]
-              \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"] \arrow[d, "\id\sequoid*"] \arrow[phantom, dr, "\textbf{e}"]
-                \& A \sequoid (\oc A \tensor \oc A) \arrow[r, "\id\sequoid\sym"] \arrow[d, "\id\sequoid(\id\sequoid*)"] \arrow[phantom, dr, "\textbf{c}"]
-                  \& A \sequoid (\oc A \tensor \oc A) \arrow[d, "\id\sequoid (*\sequoid\id)"] \\
-        I \tensor \oc A \arrow[r, "\sym"] \arrow[d, "\lunit"'] \arrow[phantom, dr, "\textbf{g}"]
-          \& \oc A \tensor I \arrow[r, "\alpha\tensor\id"] \arrow[d, "\runit"] \arrow[phantom, dr, "\textbf{f}"]
-            \& (A \sequoid \oc A) \tensor I \arrow[r, "\wk"] \arrow[d, "\runit"] \arrow[phantom, dr, "\textbf{i}"]
-              \& (A \sequoid \oc A) \sequoid I \arrow[r, "\passoc\inv"] \arrow[d, "\run"] \arrow[phantom, dr, "\textbf{j}"]
-                \& A \sequoid (\oc A \tensor I) \arrow[r, "\id\sequoid\sym"] \arrow[d, "\id\sequoid\runit"] \arrow[phantom, dr, "\textbf{h}"]
-                  \& A \sequoid (I \tensor \oc A) \arrow[d, "\id\sequoid\lunit"] \\
-        \oc A \arrow[r, "\id"']
-          \& \oc A \arrow[r, "\alpha"]
-            \& A \sequoid \oc A \arrow[r, "\id"']
-              \& A \sequoid \oc A \arrow[r, "\id"']
-                \& A \sequoid \oc A \arrow[r, "\id"']
-                  \& A \sequoid \oc A
-      \end{tikzcd}
-      \]
-    \caption{
-      \textbf{a} is diagram \eqref{secondProjectionDiagram}. \\[\baselineskip]
-      \textbf{b} and \textbf{c} commute because $\sym$ is a natural transformation, \textbf{d} commutes because $\wk$ is a natural transformation and \textbf{e} commutes because $\passoc$ is a natural transformation.
-\textbf{f} commutes because $\runit$ is a natural transformation.
-\\[\baselineskip]
-      \textbf{g} and \textbf{h} commute by one of the coherence conditions for a symmetric monoidal category.
-\textbf{i} commutes by one of the coherence conditions for $\wk$ in the definition of a sequoidal category and \textbf{j} commutes by one of the coherence conditions for $\passoc$ in the definition of a sequoidal category.
-    }\label{hugeDiagram1}
-  \end{SidewaysFigure}
-
-  Now observe that the composite $\xi_A$ is running along the left hand side of Figure \ref{hugeDiagram1}, while $\id\sequoid\xi$ is running along the right.
-Since we have $\alpha$ along the bottom, it follows by the uniqueness of $\fcoal{\cdot}$ that $\xi=\fcoal{\alpha}=\id_{\oc A}$.
-\end{proof}
-
-Now we are ready to show that $f\mapsto\oc f$ respects composition.
-Let $A,B,C$ be objects, let $f$ be a morphism from $A$ to $B$ and let $g$ be a morphism from $B$ to $C$.
-Using Lemma \ref{aFormulaForAlpha} and the definition of $\oc f$, $\oc g$, we may construct a commutative diagram:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\mu"] \arrow[d, "\oc f"']
-      & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-        & A \tensor \oc A \arrow[r, "f\tensor\id"]
-          & B \tensor \oc A \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc\sigma"]
-            & B \sequoid \oc A \;\times\; \oc A \sequoid B \arrow[d, "\id\sequoid\oc f\;\times\;\oc f\sequoid\id"] \\
-    \oc B \arrow[r, "\mu"] \arrow[dd, "\oc g"']
-      & \oc B \tensor \oc B \arrow[rr, "\der\tensor\id"]
-        &
-          & B \tensor \oc B \arrow[r, "\dec"] \arrow[d, "g\tensor\id"]
-            & B \sequoid \oc B \;\times\; \oc B \sequoid B \\
-    %
-      &
-        &
-          & C \tensor \oc B \arrow[r, "\dec"] \arrow[d, dotted, "\id\tensor\oc g"']
-            & C \sequoid \oc B \;\times\; \oc B \sequoid C \arrow[d, "\id\sequoid\oc g\;\times\oc g\sequoid\id"] \\
-    \oc C \arrow[r, "\mu"]
-      & \oc C \tensor \oc C \arrow[rr, "\der\tensor\id"]
-        &
-          & C \tensor \oc C \arrow[r, "\dec"]
-            & C \sequoid \oc C \;\times \oc C \sequoid C
-  \end{tikzcd}
-  \]
-Here, the outermost (solid) shapes are the product of shapes that commute by the definition of $\oc f$, $\oc g$ (after we have replaced $\alpha_B$, $\alpha_C$ with the composite from Lemma \ref{aFormulaForAlpha}).
-The smaller squares on the right hand side commute because $\dec$ is a natural transformation.
-Since $\dec$ is an isomorphism, the two rectangles on the left commute as well.
-
-Throwing away the right hand squares and adding some new arrows at the right, we arrive at the following commutative diagram:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\comp{(f \tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
-      &[72pt] B \tensor \oc A \arrow[r, "g \tensor\id"] \arrow[d, "\id\tensor\oc f"']
-        & C \tensor \oc A \arrow[d, "\id\tensor\oc f"] \\
-    \oc B \arrow[d, "\oc g"']
-      & B \tensor\oc B \arrow[r, "g\tensor\id"] \arrow[d, "g\tensor\oc\tau"']
-        & C \tensor \oc B \arrow[dl, "\id\tensor\oc g"] \\
-    \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
-      & C \tensor \oc C
-        &
-  \end{tikzcd}
-  \]
-We have just shown that the square on the left commutes.  The shapes on the right commute by inspection.  We now throw away the internal arrows and apply $\wk$ on the right hand side:
-\[
-  \begin{tikzcd}
-    \oc A \arrow[r, "\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}"] \arrow[d, "\oc f"']
-      &[72pt] C \tensor \oc A \arrow[d, "\id\tensor\oc f"'] \arrow[r, "\wk"]
-        & C \sequoid \oc A \arrow[d, "\id\sequoid\oc f"] \\
-    \oc B \arrow[d, "\oc g"']
-      & C \tensor \oc B \arrow[d, "\id\tensor\oc g"'] \arrow[r, "\wk"]
-        & \oc C \sequoid \oc B \arrow[d, "\id\sequoid\oc g"] \\
-    \oc C \arrow[r, "\comp{(\der\tensor\id)}{\mu}"]
-      & C \tensor \oc C \arrow[r, "\wk"]
-        & C \sequoid\oc C
-  \end{tikzcd}
-  \]
-By Lemma \ref{aFormulaForAlpha}, the composite along the bottom is equal to $\alpha_C$.  Therefore, by uniqueness of $\fcoal{\cdot}$, we have
-\[
-  \comp{\oc g}{\oc f} = \fcoal{\comp{\wk}{\comp{((\comp g f)\tensor\id)}{\comp{(\der\tensor\id)}\mu}}} = \oc(\comp g f)
-  \]
-Therefore, $\oc$ is indeed a functor.
-
-We now want to show that $\oc$ has the structure of a strong symmetric monoidal functor from $(\C,\times,1)$ to $(\C,\tensor,I)$.  The relevant morphisms are:
-\[
-  \int_{A,B}\from \oc A \tensor \oc B \to \oc (A \times B)
-  \quad
-  \epsilon\from I \to \oc 1
-  \]
-By hypothesis, these are both isomorphisms.  We just need to show that the appropriate coherence diagrams commute.  That is, for any games $A,B,C$, we need to show that the following diagrams commute:
-\[
-  \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\assoc_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id_{\oc C}"']
-      &[24pt] \oc A \tensor (\oc B \tensor \oc C) \arrow[d, "\id_{\oc A}\tensor\int_{B,C}"] \\
-    \oc (A \times B) \tensor \oc C \arrow[d, "\int_{A\times B,C}"']
-      & \oc A \tensor \oc(B \times C) \arrow[d, "\int_{A,B\times C}"] \\
-    \oc ((A \times B) \times C) \arrow[r, "\oc\assoc_{\times,A,B,C}"']
-      & \oc (A \times (B \times C))
-  \end{tikzcd}
-\]
-\[
-  \begin{tikzcd}
-    I \tensor \oc A \arrow[r, "\varepsilon\tensor\id"]
-      & \oc 1 \tensor \oc A \arrow[d, "\int_{1,A}"] \\
-    \oc A \arrow[u, "\lunit_{\oc A}"] \arrow[r, "\oc\lunit_A"]
-      & \oc (1 \times A)
-  \end{tikzcd}\quad
-  \begin{tikzcd}
-    \oc A \tensor I \arrow[r, "\id\tensor\varepsilon"]
-      & \oc A \tensor \oc 1 \arrow[d, "\int_{A,1}"] \\
-    \oc A \arrow[r, "\oc\runit_A"] \arrow[u, "\runit_{\oc A}"]
-      & \oc (A \times 1)
-  \end{tikzcd}\quad
-  \begin{tikzcd}
-    \oc A \tensor \oc B \arrow[r, "\sym_{A,B}"] \arrow[d, "\int_{A,B}"']
-      & \oc B \tensor \oc A \arrow[d, "\int_{B,A}"] \\
-    \oc(A\times B) \arrow[r, "\oc\sym_{A,B}"]
-      & \oc(B\times A)
-  \end{tikzcd}
-  \]
-
-We first prove a small lemma, which gives us a simpler way to compute $\oc \sigma$ in the case that $\sigma$ is a morphism in $\C_s$.
-
-\begin{lemma}\label{ocStrict}
-  Let $A,B$ be objects of $\C_s$ and let $\sigma$ be a morphism from $A$ to $B$ in $\C_s$.  Then the following diagram commutes:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\oc \sigma"']
-        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
-          & B \sequoid \oc A \arrow[d, "\id\sequoid\oc\sigma"] \\
-      \oc B \arrow[rr, "\alpha_B"]
-        &
-          & B \sequoid \oc B
-    \end{tikzcd}
-    \]
-\end{lemma}
-
-\begin{proof}
-  By the definition of $\oc \sigma$, we have the following commutative diagram:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\mu_A"] \arrow[d, "\oc \sigma"']
-        & \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-          & A \tensor \oc A \arrow[r, "\sigma\tensor\id"]
-            & B \tensor \oc A \arrow[r, "\wk"]
-              & B \sequoid \oc A \arrow[d, "\id_B\sequoid\oc\sigma"] \\
-      \oc B \arrow[rrrr, "\alpha_B"]
-        &
-          &
-            &
-              & B \sequoid \oc B
-    \end{tikzcd}
-    \]
-  Therefore, it will suffice to show that the following diagram (solid lines) commutes:
-  \[
-    \begin{tikzcd}
-      \oc A \arrow[r, "\alpha_A"] \arrow[d, "\mu_A"']
-        & A \sequoid \oc A \arrow[r, "\sigma\sequoid\id"]
-          & B \sequoid \oc A \\
-      \oc A \tensor \oc A \arrow[r, "\der\tensor\id"]
-        & A \tensor \oc A \arrow[u, dotted, "\wk"] \arrow[r, "\sigma\tensor\id"]
-          & B \tensor \oc A \arrow[u, "\wk"]
-    \end{tikzcd}
-    \]
-  The left hand square commutes by Lemma \ref{aFormulaForAlpha}.  The right hand square commutes because $\wk$ is a natural transformation.
-\end{proof}
-
-To show that the first coherence diagram commutes, we define a composite $\eta_{A,B,C}$:
-\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
-\begin{gather*}
-  (\oc A \tensor \oc B) \tensor \oc C \constantwidthxrightarrow{\langle\id,\; \sym\rangle} ((\oc A \tensor \oc B) \tensor \oc C) \times (\oc C \tensor (\oc A \tensor \oc B)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{((\comp{\dist\inv}{\kappa_{A,B}})\tensor\id)\times(\alpha_C\tensor\id)} (((A \times B) \sequoid (\oc A \tensor \oc B)) \tensor \oc C) \times ((C \sequoid \oc C) \tensor (\oc A \tensor \oc B)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} (((A \times B) \sequoid (\oc A \tensor \oc B)) \sequoid \oc C) \times ((C \sequoid \oc C) \sequoid (\oc A \tensor \oc B)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid (\oc C \tensor (\oc A \tensor \oc B))) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C))
-\end{gather*}
-
-Observe the similarity between the definition of $\eta_{A,B,C}$ and that of $\kappa_{A\times B,C}$.
-Indeed, it may be easily verified that the following diagram commutes, using the definition of $\int_{A,B}$ as the anamorphism for $\comp{\dist\inv}{\kappa_{A,B}}$ and the fact that $\wk$, $\passoc$ and $\sym$ are natural transformations:
-\begin{equation}\label{kreuz}
-  \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\eta_{A,B,C}"] \arrow[d, "\int_{A,B}\tensor\id"']
-      & ((A \times B) \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \times (C \sequoid ((\oc A \tensor \oc B) \tensor \oc C)) \arrow[d, "(\id\sequoid(\int\tensor\id))\times (\id\sequoid(\int\tensor\id))"] \\
-    \oc (A \times B) \tensor \oc C \arrow[r, "\kappa_{A\times B,C}"]
-      & ((A \times B) \sequoid (\oc (A \times B) \tensor \oc C)) \times (C \sequoid (\oc (A \times B) \tensor \oc C))
-  \end{tikzcd}\tag{\kreuz}
-\end{equation}
-Then we get the commutative diagram in Figure \ref{CoherenceOneWay}, which tells us that one of the two paths round the coherence diagram is the anamorphism of $\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}$.
-We now show that the other path round the coherence diagram is the anamorphism of the same thing, which will prove that they are equal.
-
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[ampersand replacement=\&]
-      (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\eta_{A,B,C}}"] \arrow[d, "\int_{A,B}\tensor\id"'] \arrow[phantom, dr, "\textbf{a}"]
-        \&[24pt] ((A \times B) \times C) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid(\int\tensor\id)"] \arrow[phantom, dr, "\textbf{b}"]
-          \&[19pt] (A \times (B\times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid(\int\tensor\id)"] \\
-      \oc (A \times B) \tensor \oc C \arrow[r, "\comp{\dist\inv}{\kappa_{A\times B,C}}"] \arrow[d, "\int_{A\times B,C}"'] \arrow[phantom, dr, "\textbf{d}"]
-        \& ((A \times B) \times C) \sequoid (\oc(A\times B)\tensor \oc C) \arrow[r, "\assoc_\times\sequoid\id"] \arrow[d, "\id\sequoid\int"] \arrow[phantom, dr, "\textbf{c}"]
-          \& (A \times (B\times C)) \sequoid (\oc(A\times B)\tensor\oc C) \arrow[d, "\id\sequoid\int"] \\
-      \oc((A\times B)\times C) \arrow[r, "\alpha_{(A\times B)\times C}"] \arrow[d, "\oc \assoc_\times"'] \arrow[phantom, drr, "\textbf{e}"]
-        \& ((A\times B) \times C) \sequoid \oc ((A\times B)\times C) \arrow[r, "\assoc_\times\sequoid\id"]
-          \& (A \times (B\times C)) \sequoid \oc (A \times(B \times C)) \arrow[d, "\id\sequoid\oc \assoc_\times"] \\
-      \oc(A \times (B\times C)) \arrow[rr, "\alpha_{A\times(B\times C)}"]
-        \&
-          \& (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
-    \end{tikzcd}
-    \]
-  \caption{\textbf{a} commutes by Diagram \eqref{kreuz}, plus the fact that $\dist$ is a natural transformation.  \\[\baselineskip]
-  \textbf{b} and \textbf{c} commute because $\assoc_\times$ is a natural transformation.  \\[\baselineskip]
-  \textbf{d} commutes by the definition of $\int_{A\times B,C}$.  \\[\baselineskip]
-  \textbf{e} commutes by Lemma \ref{ocStrict}.}\label{CoherenceOneWay}
-\end{SidewaysFigure}
-
-For this, we define a composite $\tilde{\eta}_{A,B,C}$:
-\settowidth{\arrow}{\scriptsize$\id_{A\sequoid(\oc A\tensor\oc B)}\times (\id_B\sequoid\sym_{\oc B,\oc A})$}
-\begin{gather*}
-  \oc A \tensor (\oc B \tensor \oc C) \constantwidthxrightarrow{\langle\sym,\id\rangle} (\oc A \tensor (\oc B \tensor \oc C)) \times ((\oc B \tensor \oc C) \tensor \oc A) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{(\alpha_A\tensor\id)\times((\comp{\dist\inv}{\kappa_{B,C}})\tensor\id)} ((A \sequoid \oc A) \tensor (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \tensor \oc A) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\wk\times\wk} ((A \sequoid \oc A) \sequoid (\oc B \tensor \oc C)) \times (((B \times C) \sequoid (\oc B \tensor \oc C)) \sequoid \oc A) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\passoc\inv\times\passoc\inv} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid ((\oc B \tensor \oc C) \tensor \oc A)) \\
-  \hspace{6pt}\cdots \constantwidthxrightarrow{\id\times(\id\sequoid\sym)} (A \sequoid (\oc A \tensor (\oc B \tensor \oc C))) \times ((B \times C) \sequoid (A \tensor (\oc B \tensor \oc C))) \\
-\end{gather*}
-
-We get a commutative diagram:
-\[
-  \begin{tikzcd}
-    (\oc A \tensor \oc B) \tensor \oc C \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\eta_{A,B,C}}}"] \arrow[d, "\assoc_{A,B,C}"']
-      &[78pt] (A \times (B \times C)) \sequoid ((\oc A \tensor \oc B) \tensor \oc C) \arrow[d, "\id\sequoid\assoc"] \\
-    \oc A \tensor (\oc B \tensor \oc C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\tilde{\eta}_{A,B,C}}}"] \arrow[d, "\id\tensor\int"']
-      & (A \times (B \times C)) \sequoid (\oc A \tensor (\oc B \tensor \oc C)) \arrow[d, "\id\sequoid(\id\tensor\int)"] \\
-    \oc A \tensor \oc(B \times C) \arrow[r, "\comp{\assoc_\times\sequoid\id}{\comp{\dist\inv}{\kappa_{A,B\times C}}}"] \arrow[d, "\int_{A,B\times C}"']
-      & (A \times (B \times C)) \sequoid (\oc A \tensor \oc (B\times C)) \arrow[d, "\id\sequoid\int"] \\
-    \oc (A \times (B \times C)) \arrow[r, "\alpha_{A\times(B\times C)}"]
-      & (A \times (B \times C)) \sequoid \oc (A \times (B \times C))
-  \end{tikzcd}
-  \]
-
-Commutativity of the top square is a long and fairly unenlightening exercise in the coherence conditions for symmetric monoidal categories and for sequoidal categories.
-Commutativity of the middle and bottom squares are by similar arguments to the ones in Figure \ref{CoherenceOneWay}.
-Therefore, the two branches of the coherence diagram are anamorphisms for the same thing, and so they are equal.
-
-The proofs for the other three coherence diagrams are similar.
-
-\subsection{Proof of Proposition \ref{itsMu}}
-
-\begingroup
-\def\thetheorem{\ref{itsMu}}
-\begin{proposition}
-  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ has comultiplication given by $\mu_A\from\oc A \to \oc A\tensor\oc A$ and counit given by the unique morphism $\eta_A\from \oc A \to I$.
-\end{proposition}
-\addtocounter{theorem}{-1}
-\endgroup
-
-By the definition of $\CCom$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite:
-\[
-  \oc A \xrightarrow{\oc\Delta} \oc (A \times A) \xrightarrow{\int_{A,A}\inv} \oc A \times \oc A
-  \]
-By Lemma \ref{ocStrict}, the morphism $\oc\Delta$ is equal to the morphism $\sigma_A$ defined above.  So this composite is equal to $\comp{\int_{A,A}}{\sigma_A}=\mu_A$.
-
-The counit is a morphism $\oc A\to I$, so by uniqueness it must be equal to $\eta_A$.
-
-\subsection{Proof of Theorem \ref{Coalgebra__CoCoCo}}
-
-\begingroup
-\def\thetheorem{\ref{Coalgebra__CoCoCo}}
-\begin{theorem}
-  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.
-Let $A$ be an object of $\C$ (equivalently, of $\C_s$).
-Then $\oc A$, together with the comultiplication $\mu_A$ and counit $\eta_A$, is the cofree commutative comonoid over $A$.
-\end{theorem}
-\addtocounter{theorem}{-1}
-\endgroup
-
-We know from Proposition \ref{itsMu} that the $(\oc A,\mu_A,\eta_A)$ is indeed a commutative comonoid.
-Now let $\delta\from B\to B\tensor B$ be a commutative comonoid in $\C$ and let $f\from B\to A$ be a morphism.
-We need to show that there is a unique morphism $f^\dag\from B \to \oc A$ such that the following diagram commutes:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[r, "\delta"] \arrow[d, "f^\dag"] \arrow[dl, "f"']
-        & B \tensor B \arrow[d, "f^\dag\tensor f^\dag"] \\
-    A
-      & \oc A \arrow[l, "\der_A"] \arrow[r, "\mu_A"]
-        & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-We define the morphism $f^\dag$ to be the anamorphism of the composite:
-\[
-  B \xrightarrow{\delta} B \tensor B \xrightarrow{f\tensor\id B} A \tensor B \xrightarrow{\wk_{A,B}} A \sequoid B
-  \]
-We first claim that it makes the given diagram commute, starting with the square on the left.
-We show that $\comp{\int_{A,A}}{\comp{\mu_A}{f^\dag}}=\comp{\int_{A,A}}{\comp{(f^\dag\tensor f^\dag)}{\delta}}\from B \to \oc (A\times A)$, by showing that both morphisms are anamorphisms for the composite
-\[
-  B \xrightarrow{\delta} B \tensor B \xrightarrow{f\tensor\id_B} A \tensor B \xrightarrow{\wk_{A,B}} A \sequoid B \xrightarrow{\Delta} (A \sequoid B) \times (A \sequoid B) \xrightarrow{\dist_{A,B}\inv} (A \times A) \sequoid B
-  \]
-Since $\int_{A,A}$ is an isomorphism, this will prove that the square on the right commutes.
-
-For the first case, the diagram in Figure \ref{transferReportDiagram1} proves that $\comp{\int_{A,A}}{\comp{\mu_A}{f^\dag}}=\comp{\sigma_A}{f^\dag}$ is the anamorphisms for that composite.
-For the other case, taking the product of the diagrams in Figure \ref{transferReportDiagram2} gives rise to the diagram in Figure \ref{transferReportDiagram3}, which proves that $\comp{\int_{A,A}}{\comp{(f^\dag\tensor f^\dag)}{\delta}}$ is the anamorphism for the same composite, which completes the proof that the right hand square commutes.
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[cramped, ampersand replacement=\&]
-      B \arrow[r, "\delta"] \arrow[d, "f^\dag"'] \arrow[phantom, drrr, "\textbf{a}"]
-        \& B \tensor B \arrow[r, "f\tensor\id_B"]
-          \& A \tensor B \arrow[r, "\wk_{A,B}"]
-            \& A \sequoid B \arrow[r, "\Delta"] \arrow[d, "\id\sequoid f^\dag"] \arrow[phantom, dr, "\textbf{b}" xshift=0.6em]
-              \& (A \sequoid B) \times (A \sequoid B) \arrow[r, "\dist_{A,B}\inv"] \arrow[d, "(\id\sequoid f^\dag)\times(\id\sequoid f^\dag)"] \arrow[phantom, dr, "\textbf{c}" xshift=2.0em]
-                \& (A \times A) \sequoid B \arrow[d, "\id\sequoid f^\dag"] \\
-      \oc A \arrow[rrr, "\alpha_A"] \arrow[d, "\sigma_A"'] \arrow[phantom, drrrrr, "\textbf{d}"]
-        \&
-          \&
-            \& A \sequoid \oc A \arrow[r, "\Delta"]
-              \& (A \sequoid \oc A) \times (A \sequoid \oc A) \arrow[r, "\dist_{A,\oc A}\inv"]
-                \& (A \times A) \sequoid \oc A \arrow[d, "\id\sequoid\sigma_A"] \\
-      \oc (A\times A) \arrow[rrrrr, "\alpha_{A\times A}"]
-        \&
-          \&
-            \&
-              \&
-                \& (A \times A) \sequoid \oc (A\times A)
-    \end{tikzcd}
-    \]
-  \caption{\textbf{a} commutes by the definition of $f^\dag$.\\[\baselineskip]
-    \textbf{b} commutes because $\Delta$ is a natural transformation.  \textbf{c} commutes because $\dist$ is a natural transformation. \\[\baselineskip]
-    \textbf{d} commutes be the definition of $\sigma_A$.
-  }\label{transferReportDiagram1}
-\end{SidewaysFigure}
-
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[ampersand replacement=\&]
-      B \arrow[r, "\delta"] \arrow[dd, "\delta"'] \arrow[ddr, phantom, "\textbf{a}"]
-        \& B\tensor B \arrow[r, "f\tensor \id_B"] \arrow[d, "\id_B\tensor\delta"]
-          \& A \tensor B \arrow[rrr, "\wk"] \arrow[d, "\id_A\tensor\delta"] \arrow[drrr, phantom, "\textbf{b}"]
-            \&
-              \&
-                \& A\sequoid B \arrow[d, "\id_A\sequoid\delta"] \\
-      %
-        \& B \tensor(B\tensor B) \arrow[r, "f\tensor\id_{B\tensor B}"] \arrow[d, "{\assoc_{B,B,B}\inv}"] \arrow[phantom, dr, "\textbf{d}" xshift=0.3em]
-          \& A \tensor (B \tensor B) \arrow[rrr, "\wk"] \arrow[drr, phantom, "\textbf{g}"] \arrow[d, "\assoc_{A,B,B}\inv"]
-            \&
-              \&
-                \& A \sequoid (B\tensor B) \arrow[dd, "\id_A\sequoid(f^\dagger \tensor f^\dagger)"] \arrow[dl, "{\passoc_{A,B,B}}"] \arrow[ddl, phantom, "\textbf{e}"] \\
-      B \tensor B \arrow[r, "\delta\tensor \id_B"] \arrow[d, "f^\dagger \tensor f^\dagger"'] \arrow[drrr, phantom, "\textbf{f}" yshift=-0.3em]
-        \& (B \tensor B) \tensor B \arrow[r, "(f\tensor\id_B)\tensor\id_B"' yshift=-0.3em]
-          \& (A \tensor B) \tensor B \arrow[r, "\wk\tensor\id_B"]
-            \& (A \sequoid B) \tensor B \arrow[r, "\wk"] \arrow[d, "(\id\sequoid f^\dagger)\tensor f^\dagger"'] \arrow[dr, phantom, "\textbf{c}"]
-              \& (A\sequoid B)\sequoid B \arrow[d, "(\id\sequoid f^\dagger)\sequoid f^\dagger"]
-                \& \\
-      \oc A \tensor \oc A \arrow[rrr, "\alpha\tensor\id_{\oc A}"']
-        \&
-          \&
-            \& (A \sequoid \oc A)\tensor \oc A \arrow[r, "\wk"]
-              \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-                \& A \sequoid (\oc A \tensor \oc A)
-    \end{tikzcd}
-  \]
-\[
-  \begin{tikzcd}[ampersand replacement=\&]
-    %
-    \& B \arrow[r, "\delta"] \arrow[d, "\delta"] \arrow[dl, "\delta"'] \arrow[phantom, ddl, "\textbf{h}" near start] \arrow[phantom, ddrrr, "\textbf{j}"]
-        \& B \tensor B \arrow[r, "f\tensor\id_B"]
-          \& A \tensor B \arrow[r, "\wk"]
-            \& A \sequoid B \arrow[d, "\id\sequoid\delta"] \\
-    B \tensor B \arrow[r, "\sym"] \arrow[d, "f^\dag\tensor f^\dag"'] \arrow[phantom, dr, "\textbf{i}"]
-      \& B \tensor B \arrow[d, "f^\dag\tensor f^\dag"]
-        \&
-          \&
-            \& A \sequoid (B \tensor B) \arrow[d, "\id\sequoid(f^\dag\tensor f^\dag)"] \\
-    \oc A \tensor \oc A \arrow[r, "\sym"]
-      \& \oc A \tensor \oc A \arrow[r, "\alpha_A \tensor \id_A"']
-        \& (A \sequoid \oc A) \tensor \oc A \arrow[r, "\wk"]
-          \& (A \sequoid \oc A) \sequoid \oc A \arrow[r, "\passoc\inv"]
-            \& A \sequoid (\oc A \tensor \oc A)
-  \end{tikzcd}
-  \]
-  \caption{\textbf{a} commutes because the comultiplication $\delta$ is associative.\\[\baselineskip]
-    \textbf{b} and \textbf{c} commute because $\wk$ is a natural transformation.  \textbf{d} and \textbf{e} commute because $\assoc$ and $\passoc$ are natural transformations.  \\[\baselineskip]
-    \textbf{f} is the tensor product of two diagrams: one is the definition of $f^\dag$ and the other one obviously commutes.\\[\baselineskip]
-    \textbf{g} is one of the coherence diagrams for $\wk$.\\[\baselineskip]
-    \textbf{h} commutes because the comultiplication $\delta$ is commutative. \\[\baselineskip]
-    \textbf{i} commutes because $\sym$ is a natural transformation.\\[\baselineskip]
-    \textbf{j} commutes by the first diagram.
-  }\label{transferReportDiagram2}
-\end{SidewaysFigure}
-
-\begin{SidewaysFigure}
-  \[
-    \begin{tikzcd}[ampersand replacement=\&]
-      B \arrow[r, "\delta"] \arrow[d, "\delta"'] \arrow[phantom, ddrrrr, "\textbf{a}"]
-        \& B \tensor B \arrow[r, "f\tensor\id_B"]
-          \& A \tensor B \arrow[r, "\wk"]
-            \& A \sequoid B \arrow[r, "\Delta"]
-              \& (A \sequoid B) \times (A \sequoid B) \arrow[r, "\dist_{A,B}\inv"] \arrow[d, "(\id_A\sequoid\delta)\times(\id_A\sequoid\delta)"'] \arrow[phantom, ddr, "\textbf{b}" xshift=1.2em]
-                \& (A \times A) \sequoid B \arrow[d, "\id_{A\times A}\sequoid\delta"] \\
-      B \tensor B \arrow[d, "f^\dag\tensor f^\dag"']
-        \&
-          \&
-            \&
-              \& (A \sequoid (B \tensor B)) \times (A \sequoid (B \tensor B)) \arrow[d, "(\id_A \sequoid (f^\dag\tensor f^\dag))\times(\id_A \sequoid (f^\dag\tensor f^\dag))"']
-                \& (A \times A) \sequoid (B \tensor B) \arrow[d, "\id_{A\times A} \sequoid (f^\dag\tensor f^\dag)"] \\
-      \oc A \tensor \oc A \arrow[rrrr, "\sigma_A"] \arrow[d, "\int_{A,A}"'] \arrow[phantom, drrrrr, "\textbf{c}"]
-        \&
-          \&
-            \&
-              \& (A \sequoid (\oc A \tensor \oc A)) \times (A \sequoid (\oc A \tensor \oc A)) \arrow[r, "\dist_{A,\oc A \tensor \oc A}\inv" yshift=0.3em]
-                \& (A \times A) \sequoid (\oc A \tensor \oc A) \arrow[d, "\id_{A\times A}\sequoid\int_{A,A}"] \\
-      \oc (A\times A) \arrow[rrrrr, "\alpha_{A\times A}"]
-        \&
-          \&
-            \&
-              \&
-                \& (A \times A) \sequoid \oc(A\times A)
-    \end{tikzcd}
-    \]
-  \caption{\textbf{a} is the product of the diagrams in Figure \ref{transferReportDiagram2}.\\[\baselineskip]
-    \textbf{b} commutes because $\dist$ is a natural transformation.\\[\baselineskip]
-    \textbf{c} is the definition of $\int_{A,A}$
-  }\label{transferReportDiagram3}
-\end{SidewaysFigure}
-
-Now the following diagrams show that the triangle on the left commutes:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\delta"] \arrow[d, "f^\dag"']
-      & B \tensor B \arrow[r, "f\tensor\id_B"]
-        & A \tensor B \arrow[r, "\wk"]
-          & A \sequoid B \arrow[dr, "\id_A\sequoid*"] \arrow[d, "\id_A\sequoid f^\dag"']
-            & 
-              & \\
-    \oc A \arrow[rrr, "\alpha_A"']
-      &
-        &
-          & A \sequoid \oc A \arrow[r, "\id_A\sequoid*"']
-            & A \sequoid I \arrow[r, "\run_A"]
-              & A
-  \end{tikzcd}
-  \]
-\[
-  \begin{tikzcd}
-    B \tensor B \arrow[r, "f\tensor\id"] \arrow[d, "\id_B\tensor*"]
-      & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id\tensor*"]
-        & A \sequoid B \arrow[d, "\id\sequoid*"] \\
-    B \tensor I \arrow[r, "f\tensor\id_I"]
-      & A \tensor I \arrow[r, "\wk"]
-        & A \sequoid I \arrow[dl, "\run_A"] \\
-    B \arrow[uu, bend left=100, "\delta"] \arrow[u, "\runit_B"'] \arrow[r, "f"]
-      & A \arrow[u, "\runit_A"]
-        &
-  \end{tikzcd}
-  \]
-In the first diagram, the morphism along the bottom is $\der_A$, by definition.
-The second diagram shows that the morphism along the top of the first diagram is equal to $f$.
-The triangle at the bottom right of that diagram is one of the coherence conditions for $\wk$, while the semicircle at the left commutes because the comultiplication $\delta$ is unital (with unit $*\from B\to I$).
-
-Lastly, we show uniqueness.  Suppose that $g\from B\to\oc A$ makes the diagram commute:
-\[
-  \begin{tikzcd}
-    %
-      & B \arrow[r, "\delta"] \arrow[d, "g"] \arrow[dl, "f"']
-        & B \tensor B \arrow[d, "g\tensor g"] \\
-    A
-      & \oc A \arrow[l, "\der_A"] \arrow[r, "\mu_A"]
-        & \oc A \tensor \oc A
-  \end{tikzcd}
-  \]
-We may convert this into the following diagram:
-\[
-  \begin{tikzcd}
-    B \arrow[r, "\delta"] \arrow[d, "g"']
-      & B \tensor B \arrow[r, "f\tensor\id_B"] \arrow[d, "g\tensor g"]
-        & A \tensor B \arrow[r, "\wk"] \arrow[d, "\id_A\tensor g"]
-          & A \sequoid B \arrow[d, "\id_A\sequoid g"] \\
-    \oc A \arrow[r, "\mu_A"]
-      & \oc A \tensor \oc A \arrow[r, "\der_A\tensor\id"]
-        & A \tensor \oc A \arrow[r, "\wk"]
-          & A \sequoid \oc A
-  \end{tikzcd}
-  \]
-Here, the left hand square is taken straight from the previous diagram, while the middle square is the tensor product of the left hand triangle with a diagram that obviously commutes.
-The right hand square commutes because $\wk$ is a natural transformation.
-
-By Lemma \ref{aFormulaForAlpha}, the morphism along the bottom is equal to $\alpha_A$ and therefore $g$ is the anamorphism for the morphism along the top; i.e., $g=f^\dag$.
-
 \end{document}

### 2018-01-21 cones/paper/cones.tex
More changes.

@@
 Similarly, the symmetric monoidal structure from $\C$ induces a symmetric monoidal structure on $C_j$.  
+If $\C$ is symmetric monoidal \emph{closed}, then so is $C_j$.
 
@@
 where horizontal arrows correspond to lax monoidal functors and vertical arrows to monoidal functors, we get an induced lax monoidal functor $C_{j}\to C_{j}$, in a way that respects horizontal pasting of squares.
+In particular, if $\C$ and $\C'$ have linear structures, compatible with $j$, then $C_j$ inherits a linear structure.
 
@@
 
-In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that
+We now restrict our attention to the inclusion functor $j\from G_{sw,rec}\hookrightarrow \G_{rec}$.  
+Then $C_j$ inherits a linear structure from $\G_{rec}$.
+
+\subsection{Extensional order}
+
+Let $\sigma,\tau\from I \to \bN$ be morphisms in $C_j$, corrseponding to morphisms $\sigma'\from jX \to \bN$, $\tau'\from jY \to \bN$ in $\G_{rec}$.  
+We say that $\sigma\lst\tau$ if the following two conditions hold:
+\begin{itemize}
+  \item If there exists $s\in \sigma'$ such that $s\vert_{\bN}=qn$, then there exists $t\in\tau'$ such that $t\vert_{\bN}=qn$.
+  \item If $\sigma'$ is winning then $\tau'$ is winning.
+\end{itemize}
+In general, given strategies $\sigma,\tau\from I \to A$ in $C_j$, we say that $\sigma\lst\tau$ if for all morphisms $\rho\from A \to \bN$ we have $\sigma;\rho\lst\tau;\rho$.
+
+We can show that this is well-defined; i.e., that it respects the equivalence relation we have already defined on morphisms.  
+This is a good exercise to show the importance of surjective and winning strategies to our model.
+
+\subsection{Countable nondeterminism}
+
+In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that morphisms are strategies for $\oc\bN\tensor A \to B$, rather than $X \tensor A \to B$ for an arbitrary game $X$.
+
+Since $\oc\bN$ has the structure of a comonoid, it gives rise to an oplax monoidal functor
+\[
+  n\from I \to \G_{rec}\,,
+  \]
+where $I$ is the one-object monoidal category.  
+Moreover, this functor is linear distributive from the trivial linear structure on $I$ on to $\G$.
+The cone $C_n$ is therefore a linear category.
+
+Since $\G_{sw,rec}$ is a sub-linear category of $\G_{rec}$, the functor $n$ factors through a functor $n'\from I \to \G_{rec}$.  
+By initiality of the cone construction, this gives rise to a functor $C_n\to C_j$.  
+Our model of nondeterministic PCF will be the category $\C$ that is the image of this functor.
+A morphism in $\C$ from a game $A$ to a game $B$ will be a strategy for $\oc \bN \tensor A \to B$, but the equivalence relation on morphisms is that from $C_j$.  
+For example, two morphisms $f,g\from \oc\bN\to A$ are equivalent in $\C$ if there is a surjective winning strategy $\oc\bN\to \oc\bN$ commuting with $f$ and $g$, but they are not equivalent in $C_n$.
+
+In fact, once we have applied the extensional quotient, there is no difference between working in $\C$ and working in $C_n$.  
+We will use $\C$, because it is closer to being a fully abstract model for nondeterministic PCF before we apply the extensional quotient.
+
+\subsection{The denotation of a term}
+
+Let $M=C[\wn]\from T$ be a term of nondeterministic PCF, where $C[-]$ is a PCF context (i.e., a context not mentioning the constant $\wn$).  
+Then the denotation of $M$ in $\C$ is given by the following composite:
+\[
+  I \xrightarrow{\phi_{\oc\bN}}
+  \oc \bN \xrightarrow{J (\deno{\lambda n. C[n]})}
+  \deno{T}
+  \]
+In other words, when considered as a morphism in $\G_{rec}$, $\deno{M}$ is precisely the denotation of the term $\lambda n.C[n]$ in $\G_{rec}$.
+
+\subsection{Relation to our previous model}
+
+Since our Harmer-McCusker-style model $\G_{ND}$
 

### 2018-01-24 cones/paper/cones.tex
Made changes.

@@
 
-\section{PCF with Countable Nondeterminism}
+\section{Idealized Algol with Countable Nondeterminism}
 
-The language we shall study is similar to that given in \cite{LairdOrdinalGames}.  
-It is the language formed by adding an unbounded natural-number choice primitive on to the base language PCF.  
-That is, it is the language formed by taking the simply-typed $\lambda$-calculus over the ground type $\nat$, and adding the constants:
-\begin{itemize}
-  \item Structural constants $\0\from\nat$, $\suc,\pred\from\nat\to\nat$ and $\IfO \from \nat \to \nat \to \nat \to \nat$ for $\nat$
-  \item Recursion combinators $\Y_T \from (T \to T) \to T$ for each $T$.
-  \item Countable choice $\wn\from\nat$.
-\end{itemize}
+The language that we will be modelling is the language Idealized Algol \cite{SamsonGuyIAPassive}, extended with an additional constant $\wn$ representing countable nondeterminism.  
+This is similar to the approach adopted in \cite{mcCHFiniteND}, which extends Idealized Algol with \emph{finite} nondeterminism.  
+The types of the language are defined inductively as follows:
+\[
+  T \Coloneqq \nat \mid \com \mid \Var \mid T \to T\,.
+  \]
+Meanwhile, the terms are those given in \cite{SamsonGuyIAPassive}, together with the nondeterministic choice:
+\begin{IEEEeqnarray*}{RCL}
+  M & \Coloneqq & x \mid \lambda x . M \mid M\;M \mid \Y_T M \mid \\
+  && \n \mid \skipp \mid \suc M \mid \pred M \mid \\
+  && \IfO M\;M\;M \mid M;M \mid \\
+  && M \coloneqq M \mid \deref M \mid \\
+  && \neww_T\;M \mid \mkvar M\;M \mid \wn\,.
+\end{IEEEeqnarray*}
 
-A small-step operational semantics for this language, taken from \cite{LairdOrdinalGames}, is given in Figure \ref{fig:op-sem}.
-\begin{figure}
+The typing rule for $\wn$ is $\Gamma \vdash \wn\from\nat$.
+We shall use the letter $v$ to range over variables of type $\Var$.
+
+The value forms in the language are given by
+\[
+  V \Coloneqq \skipp \mid \n \mid \lambda x.M \mid v \mid \mkvar
+  \]
+We define predicates $M \converges V$ ($M$ may converge to $V$) and $M\mustconverge$ ($M$ must converge) inductively to give a big-step operational semantics for our language.  
+We give a selection of the appropriate rules in Figure \ref{fig:ia-os}; this presentation is almost identical to that given in \cite{mcCHFiniteND}, with a slightly different rule for the countable nondeterminism.
+In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.
+If $s$ is a store and $v$ a variable, we write $\stup s v n$ for the state formed by updating the value of the variable $v$ to $n$.
+
+\begin{figure*}
   \begin{mathpar}
-    \inferrule*{ }{(\lambda x.M) N \opto M[N/x]}
+    \inferrule*{\ia s N \converges \ia {s'} \n \\ \ia {s'} M \converges \ia {s''} v}
+    {\ia s {M \coloneqq N} \converges \ia {\stup {s''} v n} \skipp}
     \and
-    \inferrule*[right=$n\in\bN$]{ }{\wn\opto\n}
+    \inferrule*[right=${s'(v) = n}$]{\ia s M \converges \ia {s'} v}
+    {\ia s {\deref M} \converges \ia {s'} \n}
     \and
-    \inferrule*{ }{\Y M \opto M (\Y M)}
+    \inferrule*{\ia s M \converges \ia {s'} \skipp \\ \ia {s'} N \converges \ia {s''} V}
+    {\ia s {M;N} \converges \ia {s''} V}
     \and
-    \inferrule*{ }{\IfO \0\;x\;y \opto x}
+    \inferrule*{\ia {\stup s v 0} M \converges \ia {\stup{s'} v n} V}
+    {\ia s {\new_T\;\lambda v.M} \converges \ia {s'} V}
     \and
-    \inferrule*{ }{\IfO (\suc \n)\;x\;y \opto y}
+    \inferrule*[right=$n\in\bN$]{\ia s {M \n} \converges \ia {s'} V}
+    {\ia s {M \wn} \converges \ia {s'} V}
     \and
-    \inferrule*{M \opto M'}{M N \opto M' N}
+    \inferrule*{\forall n\in\bN.\ia s {M \n}\mustconverge}
+    {\ia s {M \wn} \mustconverge}
     \and
-    \inferrule*{M \opto M'}{\suc M \opto \suc M'}
-    \and
-    \inferrule*{M \opto M'}{\pred M \opto \pred M'}
-    \and
-    \inferrule*{M \opto M'}{\IfO M \opto \IfO M'}
+    \inferrule*{\ia s M \mustconverge \\ \forall \ia {s'} {\lambda x.M'}\esuchthat \ia s M \converges \ia {s'} {\lambda x.M'} \Rightarrow \ia {s'}{M'[N/x]}\mustconverge}
+    {\ia s {M\;N}\mustconverge}
   \end{mathpar}
-  \caption{Operational Semantics for a PCF-like language with countable nondeterminism.}
-  \label{fig:op-sem}
-\end{figure}
-Our main task will be to give a Denotational Semantics for this language.
+  \caption{Operational semantics of Idealized Algol with Countable Nondeterminism}
+  \label{fig:ia-os}
+\end{figure*}
 
-Given a term $M$ of ground type $\nat$, we say that $M$ \emph{must converge}, and write $M\mustconverge$, if every evaluation $\pi$ of $M$ (according to the operational semantics given in Figure \ref{fig:op-sem}) terminates at some numeral value.
-We write $M \converges \n$ if there exists some evaluation $\pi$ of $M$ that terminates at $\n$.
+Given a term $M$ of ground type $\com$ or $\nat$, a proof $\pi$ that $\ia s M\converges V$ gives rise to a (possibly infinite) sequence of natural numbers corresponding to a bottom-to-top, left-to-right reading of the natural numbers $n$ used in the first rule for $\wn$.
+We call such a sequence an \emph{evaluation} of the configuration $\ia s M$.  
+It is perhaps easier to view this from the perspective of a small-step reduction: the sequence of numbers is formed by listing the different values that the nondeterminism constant $\wn$ decays to over the course of the evaluation $\pi$.
 
-Given a type $T$, we define an order on the terms of type $T$, by saying that $M\lmam N$ if for all compatible contexts $C[-]$ of type $\nat$ we have
+Let $T$ be an Idealized Algol type, and let $M,N\from T$ be terms.  
+Then we write $M\lmam N$ if for all compatible contexts $C[-]$ of ground type we have
 \begin{gather*}
-  C[M]\converges\n\Rightarrow C[N]\converges \n \\
-  C[M]\mustconverge\Rightarrow C[N]\mustconverge\,.
+  C[M]\converges V \Rightarrow C[N] \converges V\\
+  C[M]\mustconverge \Rightarrow C[N] \mustconverge
 \end{gather*}
 
-We say $M\emam N$ if $M\lmam N$ and $N\lmam M$.
+We write $M\emam N$ if $M\lmam N$ and $N\lmam M$.
 
@@
 
-\section{The base model}
+\section{Game Semantics}
 
-We will give a model based on Abramsky, Jagadeesan and Malacaria's Game Semantics for PCF \cite{ajmPcf}.  
-We do this partly for the sake of simplicity, and partly to demonstrate the power of our methods -- since AJM games are typically seen as less flexible than the Hyland-Ong games of \cite{hoPcf}.  
-However, we stress that our construction can be carried out just as well in Hyland and Ong's model, and we will keep this model in mind throughout, and mention whenever a slightly modified argument is needed for that model.
+We will use the Hyland-Ong version of Game Semantics, as in \cite{SamsonGuyIAPassive}.
 
-\subsection{Games}
+\subsection{Arenas}
 
-A \emph{game} is a tuple $A=(M_A,\lambda_A,P_A)$, where
+An \emph{arena} is given by a triple $A=(M_A,\lambda_A,\ts_A)$, where
 \begin{itemize}
-  \item $M_A$ is a set of \emph{moves},
-  \item $\lambda_A\from M_A \to \OP\times\QA$ is a function that designates each move as either a \emph{$P$-move} or an \emph{$O$-move}, and as either a \emph{question} or an \emph{answer}.
-  \item $P_A$ is a non-empty prefix-closed set of finite sequences of elements of $M_A$ called \emph{positions}, satisfying the following two conditions:
-    \begin{description}
-      \item[Alternation] any non-empty position in $P_A$ starts with an $O$-move, and if $sab\in P_A$ then $a$ and $b$ have opposite signs - one is a $P$-move and the other an $O$-move.  
-      \item[Well-bracketing] If $s\in P_A$, then the corresponding $QA$-sequence of questions and answers is well-bracketed.
-    \end{description}
+  \item $M_A$ is a countable set of moves,
+  \item $\lambda_A\from m_A\to\OP\times\QA$ designates each move as either an \emph{$O$-move} or a \emph{$P$-move}, and as either a \emph{question} or an \emph{answer}.  
+    We define $\lambda_A^{OP}=\pr_1\circ\lambda_A$ and $\lambda_A^{QA}=\pr_2\circ\lambda_A$.  
+    We also define $\neg\from\OP\times\QA\to\OP\times\QA$ to be the function that reverses the values of $O$ and $P$ while leaving $\QA$ unchanged.
+  \item $\ts_A$ is an \emph{enabling relation} between $M_A+\{*\}$ and $M_A$ satisfying the following rules:
+    \begin{itemize}
+      \item If $a\ts_A b$ and $a\ne b$, then $\lambda_A^{OP}(a)\neq\lambda_A^{OP}(b)$.  
+      \item If $*\ts_A a$, then $\lambda_A(a)=OQ$ and $b\nts_A a$ for all $b\in M_A$.
+      \item If $a\ts_A b$ and $b$ is an answer, then $a$ is a question.
+    \end{itemize}
+    We say that a move $a\in M_A$ is \emph{initial} in $A$ if $*\ts_A a$.
 \end{itemize}
 
-\subsection{Strategies}
+Our base arenas will be the \emph{flat arenas} for the types $\nat$ and $\com$.  
+Given a set $X$, the flat arena on $X$ is the arena with a single $O$-question $q$ and a $P$-answer $x$ for each $x\in X$, where $*\ts q$ and $q\ts x$ for each $x$.  
+The denotation of the type $\nat$ will be the flat arena $\bN$ on the set of natural numbers, while the denotation of the type $\com$ will be the flat arena $\bC$ on the singleton set $\{a\}$.
 
-A (deterministic) \emph{strategy} for a game $A$ is a non-empty, prefix-closed subset $sigma\subset P_A^+$ satisfying \emph{determinism}: if $sa,sb\in \sigma$ are both $P$-positions, then $a=b$.  
-Here, $P_A^+$ is the set of $P$-positions in $A$.
+Given an arena $A$, a \emph{justified string} in $A$ is a sequence $s$ of moves in $A$, together with \emph{justification pointers} that go from move to move in the sequence in such a way that every non-initial move $m$ in $s$ has exactly one justification pointer going back to an earlier move $n$ in $s$ such that $n\ts_A m$.
+We say that $n$ \emph{justifies} $m$.  
+It is easy to see that every justified string must begin with an initial move, an hence with an $O$-question.
 
-We say that a strategy $\sigma$ is \emph{history-free} if whenever $sab,tac\in\sigma$ are both $P$-positions, then $b=c$.  
-Such a strategy can be though of as a partial function $M_A^-\pfun M_A^+$, where $M_A^-$ is the set of $O$-moves and $M_A^+$ the set of $P$-moves in $A$.  
-If this function can be given as a partial recursive function, we say that the strategy $\sigma$ is \emph{recursive}.
+A \emph{legal play} $s$ is a justified string in $A$ that strictly alternates between $O$-moves and $P$-moves and is such that the corresponding $QA$-sequence formed by applying $\lambda_A^{QA}$ to terms is well-bracketed.
+We write $L_A$ for the set of legal plays in $A$.
 
-\subsection{Connectives}
+\subsection{Games and strategies}
 
-Given games $A$ and $B$, we can define games $A\times B$, $A\tensor B$ and $A\implies B$ as follows:
-\begin{itemize}
-  \item $M_{A\times B}=M_{A\tensor B}=M_{A\implies B}=M_A+M_B$.  
-  \item $\lambda_{A\times B}=\lambda_{A\tensor B}=[\lambda_A,\lambda_B]$.  
-    $\lambda_{A\implies B}=[\neg\circ\lambda_A,\lambda_B]$, where $\neg\from\OP\times\QA\to\OP\times\QA$ is the function that exchanges $O$ and $P$ and leaves $Q$ and $A$ alone.
-  \item $P_{A\times B}$ is the union of $P_A$ and $P_B$.  
-    $P_{A\tensor B}$ and $P_{A\implies B}$ are defined by the following formula:
-    \[
-      \{s\in (M_A + M_B)^* \suchthat s\vert_A\in P_A,\;s\vert_B\in P_B,\;\text{$s$ is alternating}\}\,.
-    \]
-  Note that this is a different strategy for $P_{A\tensor B}$ and $P_{A\implies B}$, because the definition of an `alternating sequence' depends on the sign function $\lambda$.
-\end{itemize}
+We follow the approach taken by Abramsky and McCusker \cite{SamsonGuyIAPassive} -- a middle road between the \emph{arenas} of Hyland and Ong and the \emph{games} of \cite{ajmPcf} that makes the linear structure more apparent.
 
-\subsection{Composition of strategies}
+Let $s$ be a legal play in some arena $A$.  
+If $m$ and $n$ are moves in $s$ such that there is a chain of justification pointers leading from $m$ back to $n$, we say that $n$ \emph{hereditarily justifies} $m$.  
+Given some set $S$ of initial moves in $s$, we write $s\vert_S$ for the subsequence of $s$ made up of all those moves that are hereditarily justified by some move in $S$.
 
-Given strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$, we define a set
-\[
-  \sigma\|\tau = \{\s\in(M_A+M_B+M_C)^*\suchthat \s\vert_{A,B}\in\sigma,\;\s\vert_{B,C}\in\tau\}\,.
-  \]
-We then define
-\[
-  \sigma;\tau = \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}\,.
-  \]
-It may be proved \cite{ajmPcf} that this notion of composition is associative and has identities given by the obvious copycat strategy for the game $A\implies A$.  
-We therefore end up with a category whose objects are games and where the morphisms from a game $A$ to a game $B$ are the strategies for the game $A\implies B$.
+A \emph{game} is a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$, where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed set of legal plays in that arena such that if $s\in P_A$ and $I$ is a non-empty set of initial moves in $s$, then $s\vert_I\in P_A$.
 
-It can also be shown that the composition of two history-free strategies is history free, and that the composition of two recursive strategies is recursive.  
-Furthermore, the identity strategy is always history-free and recursive.
+\subsubsection{Multiplicatives}
 
-We write $\G$ for the category of games and strategies, $\G_{hf}$ for the category of games and history-free strategies, and $\G_{rec}$ for the category of games and recursive strategies.
+Let $A,B$ be games.  
+We define games $A\tensor B$ and $A\implies B$ as follows.
+\begin{IEEEeqnarray*}{RCL}
+  M_{A\tensor B} & \quad=\quad & M_A + M_B\,. \\
+  \lambda_{A\tensor B} & = & [\lambda_A,\lambda_B]\,.\\
+  *\ts_{A\tensor B} n & \Leftrightarrow & * \ts_A n \text{ or } * \ts_B n\,. \\
+  m \ts_{A\tensor B} n & \Leftrightarrow & m \ts_A n\text{ or } m \ts_B n\,.\\
+  P_{A\tensor B} & = & \{s\in L_{A\tensor B}\suchthat s\vert_A\in P_A\text{ and }s\vert_B\in P_B\}\,.
+\end{IEEEeqnarray*}
+\begin{IEEEeqnarray*}{RCL}
+  M_{A\implies B} & \quad=\quad & M_A + M_B\,. \\
+  \lambda_{A\implies B} & = & [\neg\circ\lambda_A,\lambda_B]\,.\\
+  *\ts_{A\implies B} n & \Leftrightarrow & * \ts_B m\,.\\[1.0ex]
+  m \ts_{A\implies B} n & \Leftrightarrow & \mbox{\pbox\textwidth{$m \ts_A n$ or $m\ts_B n$ \\ or (for $m\neq *$) $ * \ts_B m$ and $* \ts_A n$\,.}} \\[1.0ex]
+  P_{A\implies B} & = & \{s\in L_{A\implies B}\suchthat s\vert_A\in P_A\text{ and }s\vert_B\in P_B\}\,.
+\end{IEEEeqnarray*}
 
-Lastly, it is well-known that the connectives $\tensor$ and $\implies$ exhibit $\G$ as a monoidal closed category (with tensor unit the empty game $I$ with no moves) and that $\times$ gives products in $\G$.
-All these properties pass on to $\G_{hf}$ and $\G_{rec}$ in the expected way.
+\subsubsection{Modelling countable nondeterminism}
 
-\subsection{Exponentials}
+Our definition of a strategy will be modelled upon that given in \cite{mcCHFiniteND}.  
+We model nondeterministic computations by relaxing the determinism constraint on strategies -- so player $P$ may have multiple replies to any given $O$-move.
 
-Given a game $A$, we define a game $\oc A$ as follows:
-\begin{itemize}
-  \item $M_{\oc A} = M_A\times\omega$.
-  \item $\lambda_{\oc A} = \lambda_A \circ \pr_1$.
-  \item $P_{\oc A} = \{s\in M_{\oc_A}^* \suchthat \text{$s$ is alternating},\;s\vert_n\in P_A\forall n\}$.
-\end{itemize}
+In addition, we have to keep track of any possible divergence in the computation; this is so we can distinguish terms such as
+\begin{mathpar}
+  \IfO \wn\;\Omega\;\0 \and \0\,,
+\end{mathpar}
+where the term on the right must converge (to $\0$), while the term on the left has a possible divergence.  
+The traditional way of representing divergences in game semantics is by a partiality in the strategy; i.e., an $O$-move to which $P$ has no reply, but this partiality will be obscured by the alternative behaviour in the denotation of the strategy on the left.
 
-It can be shown \cite{ajmPcf} that this construction gives rise to a \emph{linear exponential comonad} on $\G$, and therefore that the co-Kleisli category $\G^{\oc}$ is a Cartesian closed category.
-
-\subsection{Modelling programming languages}
-
-The results from \cite{ajmPcf} that we will be interested are the following:
-\begin{itemize}
-  \item $\G_{hf}$ is a fully abstract model of PCF.
-  \item $\G_{rec}$ is also a fully abstract model of PCF.  
-    Moreover, it is a \emph{universal} model: every morphism between the denotation of types is the denotation of a PCF term.
-\end{itemize}
-
-We will also be interested in a result of Laird \cite{LairdCofCommCom}, which tells us about the natural language for $\G$ itself:
-\begin{itemize}
-  \item $\G$ is a fully abstract model of $\lambda_{\text{co}}$, an extension of PCF with coroutines.
-    In particular, $\G$ is a sound and adequate model of a stateful language such as Idealized Algol.
-\end{itemize}
-
-This result -- that our model of PCF may be embedded inside a game semantics model of a stateful language -- will be useful when we come to prove Computational Adequacy for our model.  
-It is a result specific to AJM games.  
-For Hyland-Ong games, the category of games and \emph{innocent} strategies, which is our model of PCF, may be embedded into the category of games and \emph{visible} strategies, which is actually a fully abstract model of Idealized Algol.
-However, we will only need soundness and adequacy, so we can carry out our proof with AJM games as well.
-
-\section{Strategies for Nondeterminism}
-
-The results that we have quoted in the previous section all apply to \emph{deterministic} PCF.  
-For nondeterministic PCF, we follow the approach of Harmer and McCusker \cite{mcCHFiniteND}, who modelled nondeterministic programs using \emph{nondeterministic strategies}; i.e., strategies where we have relaxed the nondeterminism condition.
-So, for example, if we model the type $\nat$ by the game $\bN$ with maximal positions $qn$ for $n\in\bN$, where $q$ is a fixed opening move, then we can model the term $\wn$ by the strategy $\top_\nat$ that is the whole of $P_{\bN}$.
-
-However, this model is not yet rich enough to model may-and-must equivalence.  
-Consider, for example, the following two of terms of type $\nat$:
-\begin{gather*}
-  \IfO \wn\;\Omega\;\0 \\
-  \0\,.
-\end{gather*}
-In the first case, there are two possibilities: either the program returns $\0$ or it diverges.
-In the second case, the program always returns $\0$.
-
-Since divergence is represented by \emph{partiality} in the strategy, these terms both have the same denotation: the strategy with unique maximal play $q0$.  
-However, they are not must-equivalent, since $\0\mustconverge$, while the other term may diverge.  
-The point is that in the first case the addition of the play $q0$ into the strategy obscures the partiality present in the denotation of $\Omega$.
-
-Harmer and McCusker's solution to this problem is to augment each strategy by the addition of a set of \emph{divergences}: $O$-positions at which we signify that play may diverge.
+We follow \cite{mcCHFiniteND} by modelling a strategy as a pair $(T_\sigma,D_\sigma)$, where $T_\sigma$ is a nondeterministic strategy in the usual sense and $D_\sigma$ is a set of $O$-plays after which there is a possibility of divergence.
 
@@
   \]
-where $n;P$ is a shorthand for $\IfO n\;P\;P$, is given by a total strategy, without divergences: namely the strategy with plays of the form
+where $n;P$ is a shorthand for $\IfO n\;P\;P$, is given by a total strategy, without divergences: namely the strategy $\mu$ with plays of the form
 \[
@@
 This term first chooses a natural number $m$, and then reads from its input $n$ for a total of $m$ times before eventually returning $\0$.  
-Thus, its denotation is the strategy with maximal plays of the form:
+Thus, its denotation is the strategy $\nu$ with maximal plays of the form:
 \[
@@
 
-\subsection{Strategies}
+\subsubsection{Strategies}
 
-Here, we follow \cite{mcCHFiniteND}, but with the addition of infinite positions.
-Given a set $X\subset M^*$, we write $\bar{X}$ for the ideal closure of $X$; i.e., $X$ together with the set of all infinite sequences $s\in M^\omega$ all of whose finite prefixes are contained in $X$.
+Given an arena $A$, we define an \emph{infinite justified string} in the obvious way.  
+We define $\bar{P_A}$ to be $P_A$ together with the set of all those infinite justified sequences that have all finite prefixes in $P_A$.
 
-A \emph{strategy} for a game $A=(A,\zeta_A)$ is given by a pair $(T_\sigma, D_\sigma)$, where:
+Let $A$ be a game.  
+A \emph{strategy} $\sigma$ for $A$ is a pair $(T_\sigma,D_\sigma)$, where:
 \begin{itemize}
-  \item $T_\sigma$ is a prefix-closed subset of $\bar{P_A}$ such that if $s\in T_\sigma$ is a $P$-position and $sa\in P_A$, then $sa\in T_\sigma$.  
-    In other words, $T_\sigma$ a nondeterministic strategy in the usual sense (possibly incorporating infinite plays).  
-    We consider all infinite positions in $A$ to be $O$-positions.
-  \item $D_\sigma\subset T_\sigma$ is a \emph{postfix}-closed set of $O$-positions satifying the following conditions:
+  \item $T_\sigma$ is a non-empty prefix-closed subset of $\bar{P_A}$ such that if $s\in T_\sigma$ is a $P$-position and $sa\in P_A$ then $sa\in T_\sigma$.
+  \item $D_\sigma\subset \bar{P_A}$ is a postfix-closed set of plays in $\bar{P_A}$ that either end with an $O$-move or are infinite.  
+    We require $D_\sigma$ to obey the following rules:
     \begin{description}
-      \item[All divergences arise from positions] If $d$ is minimal in $D_\sigma$ then either $d\in T_\sigma$ or $d$ is an infinite position that is the limit of positions in $T_\sigma$.
-      \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position, then either $s\in D_\sigma$ or there exists $sa\in T_\sigma$.
-      \item[Infinite positions are divergences] If $s\in T_\sigma$ is infinite, then $s\in D_\sigma$.
+      \item[Divergences come from plays] If $d\in D_\sigma$ then there exists some $s\prefix d$ such that $s\in T_\sigma\cap D_\sigma$.
+      \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position, then either $s\in D_\sigma$ or $sa\in T_\sigma$ for some legal play $sa$.
+      \item[Infinite positions are divergent] If $s\in T_\sigma$ is infinite, then $s\in D_\sigma$.
     \end{description}
@@
 
-We say that a strategy $\sigma$ is \emph{complete} if $T_\sigma=\bar{T_\sigma}$; i.e., if $s\in T_\sigma$ whenever $s$ is an infinite position, all of whose finite prefixes live in $T_\sigma$.  
-For example, the denotation of $M$ above is complete, but the denotation of $N$ is not complete.
+\subsubsection{Composition of strategies}
 
-We say that $\sigma$ is \emph{locally complete} if $T_\sigma$ can be written as the union of complete strategies.
+Given games $A,B,C$, we define a justified string over $A,B,C$ to be a sequence $\s$ of moves with justification pointers from all moves except the initial moves in $C$.  
+Given such a string, we may form the restrictions $\s\vert_{A,B}$ and $\s\vert_{B,C}$ by removing all moves in either $C$ or $A$, together with all justification pointers pointing into these games.  
+We define $\s\vert_{A,C}$ to be the sequence formed by removing all moves from $B$ from $\s$ and all pointers to moves in $B$, \emph{unless} we have a sequence of pointers $a \to b \to c$, in which case we replace them with a pointer $a \to c$.
 
-It is easy to see that the denotation of any term from nondeterministic PCF must be locally complete.  
-An example of a strategy that is not locally complete is given by taking the denotation of $M$ above and considering it as a strategy with no infinite positions.  
-The difference between this strategy and the denotation of $N$, is that every finite position in $N$ is eventually completed in the copy of $\bN$ on the right, so it is still locally complete.
+We call such a sequence $\s$ a \emph{legal interaction} if $\s\vert_{A,B}\in P_{A\implies B}$, $\s\vert_{B,C}\in P_{B\implies C}$ and $\s\vert_{A,C}\in P_{A\implies C}$.  
+We write $\Int_\infty(A,B,C)$ for the set of (possibly infinite) legal interactions between $A$, $B$ and $C$.
 
-We will require our strategies to be locally complete from here on.  
-The problem with allowing non-locally complete strategies is that their composition does not necessarily satisfy the diverge-or-reply rule.
+Now, given strategies $\sigma\from A \implies B$ and $\tau\from B \implies C$, we define
+\[
+  T_\sigma\|T_\tau = \{\s\in\Int_\infty(A,B,C)\suchthat \s\vert_{A,B}\in T_\sigma,\;\s\vert_{B,C}\in T_\tau\}\,,
+  \]
+and then set
+\[
+  T_{\sigma;\tau} = \{\s\vert_{A,C}\suchthat \s\in T_\sigma\|T_\tau\}\,.
+  \]
+As for divergences in $\sigma;\tau$, our approach is actually simpler than that in \cite{mcCHFiniteND}; we set
+\[
+  D_\sigma\dv D_\tau = \left\{\s\in \Int_\infty(A,B,C)\;\middle|\; \mbox{\pbox{\textwidth}{\textbf{either} $\s\vert_{A,B}\in D_\sigma$\\ \hspace*{12pt}and $s\vert_{B,C}\in T_\tau$ \\ \textbf{or} $\s\vert_{A,B}\in T_\sigma$ \\\hspace*{12pt}and $s\vert_{B,C}\in D_\tau$}}\right\}\,.
+  \]
+We then set
+\[
+  D_{\sigma;\tau} = \pocl_{A\implies C}\{\s\vert_{A,C}\suchthat\s\in D_\sigma\dv D_\tau\}\,,
+  \]
+where $\pocl X$ denotes the \emph{postfix closure} of $X$; i.e., the set of all $O$-plays in $P_{A\implies C}$ that have some prefix in $X$.
 
-\subsection{Composition of strategies}
+Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself a legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
 
-Let $\sigma\from A\implies B$ and $\tau\from B\implies C$ be strategies.  
-We define $T_{\sigma;\tau}$ in the usual way.  
-In order to define $D_{\sigma;\tau}$, we first define
+We need to impose one more condition on strategies:
+\begin{definition}
+  Let $\sigma$ be a strategy for a game $A$.  
+  We say that $\sigma$ is \emph{complete} if $T_\sigma=\bar{T_\sigma}$; i.e., $T_\sigma$ contains an infinite position $s$ if it contains every finite prefix of $s$.  
+\end{definition}
+
+Any finite-nondeterminism strategy in the sense of \cite{mcCHFiniteND} may be interpreted as a complete strategy by enlarging it with all its infinite limiting plays.  
+However, when we introduce countable nondeterminism, we introduce the possibility of strategies that are not complete.  
+For example, the strategy $\nu$ that we mentioned above has an infinite increasing sequence of plays $q0\prefix q0q0\prefix \cdots$, but has no infinite play corresponding to its limit.  
+Nonetheless, we do not want to allow arbitrary strategies: for example, the strategy $\mu$ above should include the infinite play $qq0q0\dots$; the strategy $\mu^\circ$ formed by removing this infinite play has no meaning in our language.
+Indeed, if we compose $\mu^\circ$ with the strategy $\0$ for $\bN$ on the left, then the resulting strategy does not satisfy diverge-or-reply.
+
+\begin{definition}
+  Let $\sigma$ be a strategy for a game $A$.  
+  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of complete strategies; i.e., there exist $\sigma_\alpha$ such that $T_\sigma=\bigcup T_{\sigma_\alpha}$ and $D_\sigma=\bigcup D_{\sigma_\alpha}$.
+\end{definition}
+
+From now on, we will use `strategy' to mean \emph{locally complete strategy}.
+
+We need to show that the composition of locally complete strategies is locally complete.  
+Note that this does not hold for \emph{complete} strategies: for example, our term $N$ above can be written as $N'\;\wn$, where $N'$ is a deterministic term with complete denotation $\nu'$.  
+Then we have $\nu=\top_{\bN};\nu'$, but $\nu$ is not complete.
+However, we can show that the composition of \emph{deterministic} complete strategies is complete; since a locally complete strategy may always be written as the union of complete deterministic strategies, this is sufficient to show that the composition of locally complete strategies is locally complete.
+
+\begin{definition}
+  We say that a strategy $\sigma$ for a game $A$ is \emph{deterministic} if
+  \begin{itemize}
+    \item it is complete;
+    \item whenever $sab,sac$ are $P$-plays in $T_\sigma$ we have $b=c$ and the justifier of $b$ is the justifier of $c$;
+    \item If $s\in D_\sigma$ then either $s$ is infinite or there is no $a$ such that $sa\in T_\sigma$.
+  \end{itemize}
+\end{definition}
+
+\begin{lemma}
+  Let $A,B,C$ be games and let $\sigma\from A\implies B$, $\tau\from B\implies C$ be deterministic complete strategies.  
+  Then $\sigma;\tau$ is complete.
+\end{lemma}
+\begin{proof}
+  The proof relies on a lemma from \cite{hoPcf} that states (in our language) that if $\sigma$ and $\tau$ are deterministic strategies and $s\in T_{\sigma;\tau}$ then there is a unique minimal $\s\in T_\sigma\|T_\tau$ such that $\s\vert_{A,C}=s$.
+  That means that if $s_1\prefix s_2\prefix \cdots$ is an infinite increasing sequence of plays in $T_{\sigma;\tau}$, with infinite limit $s$, then there is a corresponding infinite increasing sequence of legal interactions $\s_1 \prefix \s_2 \prefix \cdots$.
+  Then the limit of this sequence is an infinite legal interaction $\s$ and we must have $\s\vert_{A,B}\in\sigma$, $\s\vert_{B,C}\in\tau$ by completeness of $\sigma$ and $\tau$.  
+  Therefore, $s=\s\vert_{A,C}\in T_{\sigma;\tau}$.
+\end{proof}
+
+\begin{corollary}
+  The composition of strategies $\sigma\from A\implies B$ and $\tau\from B \implies C$ is a well-formed strategy for $A\implies C$.
+\end{corollary}
+\begin{proof}
+  The only tricky point is eastablishing that diverge-or-reply holds for $\sigma;\tau$.  
+  Again, it is sufficient to prove this in the case that $\sigma$ and $\tau$ are deterministic and complete.
+  Then it essentially follows from the argument used in \cite{abramskyjagadeesangames} that shows that a partiality at an $O$-position $s\in T_{\sigma;\tau}$ must arise either from a partiality in $T_\sigma$ or $T_\tau$ or from `infinite chattering' between $\sigma$ and $\tau$.
+  In the first case, the diverge-or-reply rule for $\sigma$ and $\tau$ gives us a divergence at $s$ in $\sigma;\tau$.  
+  In the second case, an infinite chattering between $\sigma$ and $\tau$ corresponds to an infinite interaction $\s\in\int(A,B,C)$ ending with infinitely many moves in $B$ such that $\s\vert_{A,C}=s$.
+  Completeness for $\sigma$ and $\tau$ tells us that $\s\vert_{A,B}\in D_\sigma$ and $\s\vert_{B,C}\in D_\tau$ and therefore that $\s\vert_{A,C}\in D_{\sigma;\tau}$.  
+\end{proof}
+
+\subsubsection{Associativity of composition}
+
+In fact, the proof of associativity of composition is pretty much the same in our model as it is in any other model of game semantics.  
+However, it is worth saying a few words about it, since the model obtained by naively extending the Harmer-McCusker model to unbounded nondeterminism does not have an associative composition.  
+The point is that this is not really a problem with associativity, but rather that this naive model gives the wrong result for the composition of strategies.  
+For example, if $\nu$ is the strategy we defined above, and $\0$ is the `constant $0$' strategy on $\bN$, then $\0;\nu$ has a divergence in the naive model, because the strategies $\0$ and $\nu$ appear to be engaged in infinite chattering.
+In our model, we have fixed that problem, because the strategy $\nu$ contains no infinite plays, and so no divergences arise in the composition.
+
+\subsection{A symmetric monoidal closed category}
+
+Given a game $A$, we define a strategy $\id_A$ on $A\implies A$, where $T_{\id_A}$ is given by
 \[
-  \sigma\dv\tau = \pocl\left\{\s\in\seqs{(M_A\cprd M_B\cprd M_C)}\;\middle|\; \mbox{\pbox{\textwidth}{\textbf{either} $\s\vert_{A,B}\in D_\sigma$\\ \hspace*{12pt}and $s\vert_{B,C}\in T_\tau$ \\ \textbf{or} $\s\vert_{A,B}\in T_\sigma$ \\\hspace*{12pt}and $s\vert_{B,C}\in D_\tau$}}\right\}\,,
+  \{s\in P_{A_1\implies A_2}\suchthat\textrm{for all even-length }t\prefix s,\;t\vert_{A_1}=t\vert_{A_2}\}\,,
   \]
-where $\pocl X$ denotes the \emph{postfix closure} of $X$; i.e., the set of all $O$-positions in $A\implies C$ that have some prefix in $X$.
+where we distinguish between the two copies of $A$ by calling them $A_1$ and $A_2$, and where $D_\sigma$ is the set of all infinite plays in $T_\sigma$.
+This is an identity for the composition we have defined, and so we get a category $\G_{ND}$ of games and nondeterministic strategies.
+Moreover, the connectives $\tensor$ and $\implies$ exhibit $\G_{ND}$ as a symmetric monoidal closed category.
 
-Lastly, we define
+$\G_{ND}$ has an important subcategory $\G_D$ of deterministic complete strategies; this category is isomorphic to the category considered in \cite{SamsonGuyIAPassive}.
+
+\subsection{Products and Exponentials}
+
+Let $A, B$ be games
+We define a new game $A \times B$.  
+The arena for $A\times B$ is the same as the arena for $A\tensor B$, but now $P_{A\times B}$ is the disjoint union of $P_A$ and $P_B$ inside that arena:
+\begin{IEEEeqnarray*}{RCL}
+  P_{A \times B} & = & \{s\in L_{A\tensor B}\suchthat s\vert_A \in P_A\text{ and }s\vert_B=\emptyplay\} \\
+  & \cup & \{s\in L_{A\tensor B}\suchthat s\vert_A=\emptyplay\text{ and }s\vert_B\in P_B\}\,.
+\end{IEEEeqnarray*}
+Then $A\times B$ is the category-theoretic product of $A$ and $B$ in $\G_{ND}$.
+
+We define a game $\oc A$ as follows.  
+The arena for $\oc A$ is the same as the arena for $A$, but the set of plays is given by
 \[
-  D_{\sigma;\tau} = \{\s\vert_{A,C}\suchthat\s\in\sigma\dv\tau\}\,.
+  P_{\oc A} = \{s\in L_A\suchthat s\vert_m\in P_A\text{ for each initial move $m$}\}\,.
   \]
+There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\coh\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.
+See \cite{SamsonGuyIAPassive} for full details.
 
-We need to show firstly that composition preserves local completeness.  
-This is not completely trivial, since the composition of \emph{complete} strategies need not be complete: for example, we may write $N=N'\;\wn$, where $N'$ is a deterministic strategy.  
-Both $N'$ and $\wn$ have complete denotations, but their composite, $N$, has a denotation that is only locally complete.
+\subsection{Constraining strategies}
 
-However, we can show that the composition of \emph{deterministic} complete strategies $\sigma$ and $\tau$ is complete.  
-The proof makes use of a lemma from \cite{abramskyjagadeesangames} that says that if $s\in\sigma;\tau$ is some position, where $\sigma$ and $\tau$ are both deterministic, then there is a unique minimal position $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=s$.
-This means that if $s_1\prefix s_2\prefix \cdots$ is an infinite increasing sequence in $\sigma;\tau$, then there is a corresponding infinite increasing sequence $\s_1\prefix\s_2\prefix\cdots$ in $\sigma\|\tau$, whose limit must be contained in $\sigma\|\tau$ by completeness of $\sigma$ and $\tau$.
-It follows that the limit of $s_1,s_2,\dots$ is contained in $\sigma;\tau$.
+Given a non-empty justified string $s$ in an arena $A$, we define the \emph{$P$-view} $\pv s$ of $s$ inductively as follows.
+\begin{IEEEeqnarray*}{rClCR}
+  \pv{sm} & = & m\,, &\qquad& \text{if $m$ is initial;} \\
+  \pv{sntm} & = & \pv s n m\,, && \text{if $m$ is an $O$-move and} \\
+  &&&&\text{$n$ justifies $m$;} \\
+  \pv{sm} & = & \pv s m\,, && \text{if $m$ is a $P$-move.}
+\end{IEEEeqnarray*}
 
-Now the fact that composition preserves local completeness is an easy consequence of monotonicity of composition with respect to the prefix ordering, together with the fact that if a strategy $\sigma$ is locally complete -- i.e., if it is the union of some collection $(\sigma_\alpha)$ of complete strategies, then the $\sigma_\alpha$ may always be chosen to be deterministic.
+We say that a play $sm$ ending in a $P$-move is \emph{$P$-visible} if the justifier of $m$ is contained in $\pv{m}$.  
+We say that a strategy $\sigma$ for a game $A$ is \emph{visible} if every $P$-position $s\in T_\sigma$ is $P$-visible.
+It can be shown that the composition of visible strategies is visible, and that we can build a Cartesian closed category using our exponential.
 
-We also need to prove that the composition of two strategies satisfies the diverge-or-reply rule.  
-Once again, it is sufficient to prove this in the case that the strategies are both deterministic and complete.  
-In that case, we can, for example, use the argument from \cite{abramskyjagadeesangames} that shows that a partiality in the composite $\sigma;\tau$ of two strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ (i.e., some $O$-position $s\in\sigma;\tau$ such that $sa\not\in\sigma;\tau$ for any $a$) must arise either from a partiality in one of $\sigma$ or $\tau$ or from an `infinite chattering' between the two strategies.
-A partiality in either of $\sigma$ or $\tau$ gives rise to a divergence in that strategy, by diverge-or-reply, and hence to a divergence at the appropriate place in $\sigma;\tau$.  
-In the case that there is some infinite chattering between $\sigma$ and $\tau$; i.e., an infinite sequence $\s\in\bar{\sigma\|\tau}$ such that $\s\vert_{A,C}$ is finite, we must have $\s\in\sigma\|\tau$ by completeness for $\sigma$ and $\tau$.
-Therefore, $\s\vert_{A,B}$ and $\s\vert_{B,C}$ are both divergences in their respective strategies, and therefore $\s\vert_{A,C}\in D_{\sigma;\tau}$.
+The resulting category $\G^\oc_{D,vis}$ of games and deterministic visible strategies is a fully abstract model of Idealized Algol \cite{SamsonGuyIAPassive}.
 
-The last thing we need to show -- namely, that composition is associative -- follows in the usual way.  
-The important difference between our model and that in \cite{mcCHFiniteND} is that in our model `divergence through infinite chattering' is an organic consequence of the usual definition of composition, not an extra condition that we have imposed upon the model.
+\subsection{Recursive games and strategies}
 
-To illustrate this, we return to our examples $M$ and $N$ above, and show how the composite $M\;1$ has a non-empty set of divergences, while $N\;1$ is divergence-free.
+Most full abstraction results go via a definability result that says that all \emph{compact} strategies are definable \cite{curienFullAbstraction}.
+However, deducing full abstraction from compact definability makes essential use of continuity properties that are absent when we deal with countable nondeterminism.  
+We will therefore need to appeal to a stronger result -- that of \emph{universality}, which states that \emph{every} strategy is definable.  
+Clearly, universality does not hold for any of our categories of games, since there are many non-computable functions $\bN\to\bN$.  
+However, Hyland and Ong proved in \cite{hoPcf} that every \emph{recursively presentable} innocent strategy is PCF-definable.
 
-In order for the strategy denotation of $M$ to satisfy local completeness, it must contain all its infinite positions.  
-Infinite positions in $\oc \bN$ are $P$-winning, so the corresponding positions in $\deno{M}\from \oc \bN\implies \bN$ are infinite $O$-positions and are therefore contained in $D_{\deno{M}}$.  
-Since the play $q\in \oc\deno{1};\deno{M}$ is the restriction to $\bN$ of the infinite position
-\[
-  \begin{array}{cc}
-    \bN & \bN \\
-    & q \\
-    q & \\
-    1 & \\
-    q & \\
-    1 & \\
-    \vdots &
-  \end{array}
-  \]
-whose right-hand component is contained in $D_{\deno{M}}$, it must therefore be contained in $D_{\oc\deno{1};\deno{M}}$.
+In order to define recursively presentable strategies, we need to work with \emph{enumerated games}; i.e., games where the set of moves comes with an enumeration to the natural numbers.  
+Clearly our base games $\bN$ and $\bC$ can be enumerated, as can the tensor product, linear implication, exponential and product of games.
 
-We contrast this with the situation with $N$.  
-In this case, the strategy-denotation of $N$ contains \emph{no} infinite position, and we have $D_{\deno{N}}=\emptyset$.  
-Since a divergence in the composition must arise from a divergence in one of the two component strategies, this means that $D_{\oc\deno{1};\deno{N}}$ is empty too.  
-This is in contrast to the Harmer-McCusker model, in which $\sigma;\tau$ may contain a divergence even if neither $\sigma$ nor $\tau$ does.
+\begin{proposition}
+  Let $\G_{D,vis,rec}$ be the category of games and \emph{recursive} visible strategies.  
+  Then every morphism in $\G$ is definable in Idealized Algol.
+\end{proposition}
+\begin{proof}
+  This follows from the corresponding results for PCF, together with the \emph{innocent factorization} result of \cite{SamsonGuyIAPassive}.  
+  See also 
+\end{proof}
 
-\subsection{Proving Full Abstraction}
+\subsection{Determinisitic Factorization}
 
-We write $\G_{ND}$ for the category we have defined.  
-It may be made into a symmetric monoidal closed category in a straightforward way, following \cite{mcCHFiniteND}.  
-Given $\sigma\from A\implies C$ and $\tau\from B\implies D$, $D_{\sigma\tensor\tau}$ is the set of all $s\in P_{(A\tensor B)\implies (C\tensor D)}$ such that either $s\vert_{A,C}\in D_\sigma$ or $s\vert_{B,D}\in D_\tau$.
-
-Similarly, we can define exponentials in our model, where the divergences in $\oc\sigma$ are those positions that are divergent in one of their components.
-
-Although we have solved the problems with associativity of composition, it turns out to be difficult to prove computational adequacy or full abstraction for this model.  
-The main problem is a lack of continuity: we can follow \cite{mcCHFiniteND} and define an ordering on strategies, but composition is no longer continuous with respect to this ordering.  
-This should not be seen as a defect of our model; indeed, we showed earlier on that the language we are trying to model has a similar lack of continuity, so if our model were continuous it would indicate that it did not model the language faithfully enough.
-
-Our approach to proving full abstraction will be to define a new model $\C$ of our language that is fully abstract for nondeterministic PCF, and to show that $\C$ admits a faithful monoidal functor into $\G_{ND}$, which is enough to show that $\G_{ND}$ is also fully abstract.
-Before we do this, however, we outline an alternative argument that does not go via this supplementary category.  
-The argument is suggested in \cite[3.7.2]{RusssThesis} as a means of defining an appropriate notion of `nondeterministic innocent strategy'.
-
-We first define the strategy $\top_\bN$ on $\bN$ by $T_{\top_{\bN}}=P_{\bN}$ and $D_{\top_{\bN}}=\emptyset$.  
-Then we say that a strategy $\sigma\from A\implies B$ is \emph{deterministic history free} if it can be written as
-\[
-  A \xrightarrow{\oracle_A}
-    \oc \bN \tensor A \xrightarrow{\sigma'}
-      B
-  \]
-where $\oracle_A=\lunit;\oc\top_\bN\tensor A$ and $\sigma'\from \oc\bN\tensor A \implies B$ is a deterministic, history-free strategy.
-It is possible to show that the composition and tensor product of such strategies can again be written in this form, and it is then possible to prove full abstraction using properties of deterministic strategies.
-When we have defined our model $\C$, we will return to this point to show that the two arguments are essentially the same.
+Our definability results will hinge on a \emph{factorization theorem}, showing that every nondeterministic strategy may be written as the composition of a deterministic strategy with the nondeterministic `oracle' $\top$.
 

### 2018-01-24 cones/paper/cones.tex
Finished universality material.
Got it into a state where I only need to prove the full abstraction things.

@@
   Let $\sigma$ be a strategy for a game $A$.  
-  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of complete strategies; i.e., there exist $\sigma_\alpha$ such that $T_\sigma=\bigcup T_{\sigma_\alpha}$ and $D_\sigma=\bigcup D_{\sigma_\alpha}$.
+  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of countably many complete strategies; i.e., there exist $\sigma_n$ such that $T_\sigma=\bigcup T_{\sigma_n}$ and $D_\sigma=\bigcup D_{\sigma_n}$.
 \end{definition}
@@
 There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\coh\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.
+This construction is essentially the co-Kleisli category on a comonad given by $\oc$, but certain technical issues prevent us from presenting it in this way.
 See \cite{SamsonGuyIAPassive} for full details.
@@
   Let $\G_{D,vis,rec}$ be the category of games and \emph{recursive} visible strategies.  
-  Then every morphism in $\G$ is definable in Idealized Algol.
+  Then $\G_{D,vis,rec}$ is a fully abstract model of Idealized Algol in which every morphism is definable.
 \end{proposition}
@@
   This follows from the corresponding results for PCF, together with the \emph{innocent factorization} result of \cite{SamsonGuyIAPassive}.  
-  See also 
+  See also \cite{MurawskiUniversality}.
 \end{proof}
@@
 
-Our definability results will hinge on a \emph{factorization theorem}, showing that every nondeterministic strategy may be written as the composition of a deterministic strategy with the nondeterministic `oracle' $\top$.
+Our definability results will hinge on a \emph{factorization theorem}, showing that every nondeterministic strategy may be written as the composition of a deterministic strategy with the nondeterministic `oracle' $\top_{\bN}$.
+We can then deduce definability from definability in the model of deterministic Idealized Algol.
 
-\section{Cones on Monoidal Functors}
+Note that our result is a bit simpler than the corresponding result in \cite{mcCHFiniteND}; this is because it is easier to model a countable source of nondeterminism than a `finite but arbitrarily large' source.
 
-\subsection{Surjective and winning strategies}
+\begin{proposition}
+  Let $\sigma\from I \to A$ be a strategy for a game $A$ in $\G_{ND}$.
+  Then we may write $\sigma$ as $\top_{\bN};\Det(\sigma)$, where $\Det(\sigma)\from \oc\bN\to A$ is a deterministic strategy and $\top_{\bN}$ is the strategy for $\oc\bN$ given by
+  \begin{itemize}
+    \item $T_{\top_{\bN}}=P_{\oc\bN}$.
+    \item $D_{\top_{\bN}}$ is the set of infinite positions in $T_{\top_\bN}$.
+  \end{itemize}
+\end{proposition}
 
-A useful fact about the category $\G$ of games and deterministic strategies, proved in \cite{hylandSchalkGames}, is that it admits a faithful, monoidal and linearly distributive functor into the category $\Rel$ of sets and relations, with monoidal structure given by the Cartesian product and exponentials given by the multiset comonad $W$.
-The functor sends a game $A$ to the set $P_A$ and sends a strategy $\sigma\from A\implies B$ to the relation
-\[
-  \grel{\sigma}=\{(s\vert_A,s\vert_B)\suchthat s\in\sigma\}\subset P_A\times P_B
-  \]
+\begin{proof}
+  We begin by fixing an injection $\code_A$ from the set of $P$-moves in $A$ into the natural numbers.  
+  In the enumerated case, this is given to us already.
 
-Given a strategy $\sigma\from A\implies B$, we say that $\sigma$ is \emph{surjective} if $\grel{\sigma}$ is a surjective relation; i.e., if for any $b\in P_B$ there exists some $s\in\sigma$ such that $s\vert_B=b$.
-Monoidality and linear distributivity of the Hyland-Schalk functor $\G\to\Rel$ show that the composition of surjective strategies is surjective, as is the tensor product of surjective strategies and the bang of a surjective strategy.
+  We first assume that the strategy $\sigma$ is complete.
+  Then the strategy $\Det(\sigma)$ is very easy to describe.  
+  For each $O$-position $sa\in T_\sigma$, we have some set $B$ of possible replies to $sa$, which we order as $b_1,b_2,\cdots$, where $\code_A(b_1)<\code_A(b_2)<\cdots$.  
+  We insert a request to the oracle for a natural number; then, depending on her answer $j$, we play the next move as follows:
+  \begin{itemize}
+    \item If $0 < j \le \code_A(b_1)$, then play $b_1$.
+    \item If $\code_A(b_n) < j \le \code_A(b_{n+1})$ then play $b_{n+1}$.
+    \item If $j = 0$ and $sa\in D_\sigma$, then play nothing, and put the resulting play inside $D_{\Det(\sigma)}$.  
+      Otherwise, play $b_1$.
+  \end{itemize}
+  Lastly, we close under limits to make the strategy $\Det(\sigma)$ complete.  
+  $\Det(\sigma)$ is clearly nondeterministic.  
+  Checking that $\top_{\bN};\Det(\sigma)=\sigma$ is easy for finite plays; for infinite plays, it follows by completeness of $\sigma$.
 
-Given a strategy $\sigma\from A\implies B$, we say that $\sigma$ is \emph{winning} if $\sigma$ is total and if for all positions $s\in\sigma$, if $sb\in\sigma$, where $b$ is an $O$-move in $B$, then there is some $t\in\sigma$ such that $sb\prefix t$ and $t$ ends with a move in $B$.
-
-Once again, the composition, tensor product and bang of winning strategies is still winning.  
-One way of seeing this is by relating our definition to the definition of a winning strategy given in \cite{abramskyjagadeesangames}, in which a game comes attached with a set of winning infinite positions.
-Then we say that a strategy $\sigma$ is winning if it is total and if every infinite position arising as the limit of plays in $\sigma$ is a winning position.  
-If $A$ and $B$ are such that every infinite position is winning, then our notion of a winning strategy coincides with that notion.
-
-The reason we are interested in surjective winning strategies is that they preserve top strategies:
-
-\begin{lemma}
-  We say that a game $A$ is \emph{$P$-winning} if for all $O$-positions $s\in P_A$ there exists some $a$ such that $sa\in P_A$.  
-  Let $A,B$ be $P$-winning games, and let $\sigma\from A\implies B$ be a surjective winning strategy.  
-  Write $\top_A$ for the (nondeterministic) strategy given by $T_{\top_A}=P_A$ and $D_{\top_A}=P_A^\omega$ (i.e., the only divergent plays are the infinite ones), and do the same for $B$.
-  Then $\top_A;\sigma=\top_B$.  
-\end{lemma}
-\begin{proof}
-  We can show that $T_{\top_A;\sigma}=T_{\top_B}$ from surjectivity of $\sigma$, using the Hyland-Schalk functor, since the equivalent result clearly holds in $\Rel$.  
-  Now suppose that $s$ is some divergent position in $\top_A;\sigma$.  
-  Then $s=\s\vert_B$, where $\s$ is a position in $\sigma$ and $\s\vert_A$ is a divergent position in $A$.
-  Then $\s\vert_A$ must be infinite; since $\sigma$ is winning, this means that $\s\vert_B$ must be infinite as well, and therefore that $s\in D_{\top_B}$.  
-  \label{lem:sw}
+  Lastly, if $\sigma$ is the union of complete strategies $\sigma_1,\sigma_2,\cdots$, we insert an additional request to the oracle immediately after the very first move by player $O$; after receiving a reply $k$, we play according to $\sigma_k$.
 \end{proof}
 
-We now define a category $\G_{sw}$ whose objects are $P$-winning games and where the morphisms from a game $A$ to a game $B$ are deterministic surjective winning strategies from $A$ to $B$.  
-We write $\G_{sw,rec}$ for the category where the morphisms are \emph{recursive} surjective, winning strategies.
-
-Write $j$ for the inclusion $\G_{sw,rec}\hookrightarrow\G_{rec}$, and write $J$ for the inclusion functor $\G\hookrightarrow\G_{ND}$ that sends a deterministic strategy $\sigma$ to the strategy given by $T=\sigma$ and $D=\pocl\{s\in\sigma^-\suchthat sa\not\in\sigma\forall a\}$
-Then the lemma we have just proves means that
-\[
-  \top \from I \Rightarrow J\circ j
-  \]
-is a natural transformation, where $I$ is the constant $I$ functor.
-
-Moreover, we would expect Lemma \ref{lem:sw} to hold in \emph{any} sensible game-semantics model of nondeterministic PCF, so the following makes sense as a definition
-
-\begin{definition}
-  A \emph{game semantics category for nondeterministic PCF} is a category $\D$ together with a functor $J\from \G_{rec}\to\D$ and a natural transformation $\top\from I\Rightarrow J\circ j\from\G_{sw,rec}\to\D$.
-\end{definition}
-
-\subsection{Generalized monoidal natural transformations}
-
-We will need one more technical definition.
-
-Let $\C'$,$C'$,$\D'$,$\D$ be monoidal categories, let $f\from\C'\to\C$, $g\from \D'\to \D$ be oplax monoidal functors and let $F\from\D'\to\C'$, $G\from\D\to\C$ be lax monoidal functors, as in Figure \ref{fig:generalized-monoidal-setup}.
-
-\begin{figure}
-  \[
-    \begin{tikzcd}[row sep=large, column sep=large]
-      \D' \arrow[r, "F", ""'{name=F}] \arrow[d, "g"']
-        & \C' \arrow[d, "f"] \\
-      \D \arrow[r, "G"', ""{name=G}]
-        & \C
-      \arrow[Rightarrow, from=F, to=G, "\phi"]
-    \end{tikzcd}
-    \]
-  \caption{A generalized monoidal natural transformation $\phi$ is a particular sort of natural transformation between composites of lax and oplax monoidal functors.}
-  \label{fig:generalized-monoidal-setup}
-\end{figure}
-
-We say that a natural transformation $\phi\from fF\bigto Gg$ is a \emph{generalized monoidal natural transformation} if the following two diagrams commute for all objects $X,Y$ of $\D'$:
-\begin{mathpar}
-  \begin{tikzcd}
-    f F X \tensor f F Y \arrow[r, "\phi_X \tensor \phi_Y"]
-      & G g X \tensor G g Y \arrow[d, "m_G"] \\
-    f (F X \tensor F Y) \arrow[u, "m_f"] \arrow[d, "f m_F"']
-      & G (g X \tensor g Y) \\
-    f F (X \tensor Y) \arrow[r, "\phi_{X \tensor Y}"]
-      & G g (X \tensor Y) \arrow[u, "G m_g"']
-  \end{tikzcd}
-  \and
-  \begin{tikzcd}[column sep=small, row sep=small]
-    %
-      & f F I_{\D'} \arrow[rr, "\phi_I"]
-        &[-1.2em]
-          &[-1.2em] G g I_{\D'} \arrow[dr, "G \epsilon_g"]
-            & \\
-    f I_{\C'} \arrow[ur, "f \epsilon_F"] \arrow[drr, "\epsilon_f"]
-      &
-        &
-          &
-            & G I_{\D} \\
-    %
-      &
-        & I_{\C} \arrow[urr, "\epsilon_G"]
-          &
-            &
-  \end{tikzcd}\,.
-\end{mathpar}
-The particular structure that generalized natural transformations fit into is that of a \emph{double category} (see \cite{LimitsInDoubleCategories} for the definition); in particular, the double category $\SymmMonCat$ introduced in \cite{AdjointsInDoubleCategories}, in which the objects are symmetric monoidal categories, the horizontal morphisms are lax symmetric monoidal functors, the vertical morphisms are oplax symmetric monoidal functors and the $2$-cells are generalized monoidal natural transformations as defined above.
-
-Generalized monoidal natural transformations may thus be composed either horizontally or vertically in the usual way; i.e., given a pair of squares as in Figure \ref{fig:generalized-monoidal-setup} that may be pasted together along an edge, then we may define a generalized monoidal natural transformation across the pasted square.
-We write $\hc{\phi}{\psi}$ for the horizontal composition of natural transformations $\phi,\psi$ pasted together along an oplax monoidal functor and $\vc{\phi}{\psi}$ for the vertical composition of natural transformations $\phi,\psi$ pasted together along a lax monoidal natural functor.
-
-\subsection{The cone of a monoidal functor}
-
-Let $j\from \C'\to \C$ be an oplax monoidal functor.  
-We define a \emph{$j$-category} to be a category $\D$ together with a lax monoidal functor $J\from\C\to\D$ and a generalized natural transformation $\phi\from I \to Jj$:
-\[
-  \begin{tikzcd}[row sep=large, column sep=large]
-    \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
-      & I \arrow[d, "I"] \\
-    \C \arrow[r, "J"', ""{name=J}]
-      & \D
-    \arrow[Rightarrow, from=term, to=J, "\phi"]
-  \end{tikzcd}\,.
-  \]
-\begin{example}
-  For example, our previous definition of a game semantics category for nondeterministic PCF can be thought of as a $j$-category, where $j$ is the inclusion functor $\G_{sw,rec}\hookrightarrow\G_{rec}$.
-\end{example}
-We define a \emph{morphism of $j$-categories} going from a $j$-category $(\D',J',\phi')$ to a $j$-category $(\D,J,\phi)$ to be a lax monoidal functor $\F\from \D'\to\D$, sending $I$ to $I$, such that $J=\F\circ J'$ and $\phi$ is the vertical composition of $\phi'$ with the `identity transformation' given by this identity; i.e.:
-\[
-  \begin{tikzcd}[row sep=large, column sep=large]
-    \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
-      & I \arrow[d, "I"] \\
-    \C \arrow[r, "J'"'{name=Jprimedown}, ""{name=Jprime}] \arrow[d, "\id"']
-      & \D' \arrow[d, "\F"] \\
-    \C \arrow[r, "J", ""{name=J}]
-      & \D
-    \arrow[Rightarrow, from=term, to=Jprime, shift left=1.5ex, "\phi'"]
-    \arrow[Rightarrow, from=Jprimedown, to=J, shift left=1.5ex, "\id"]
-    \arrow[Rightarrow, from=term, to=J, shift right=3ex, "\phi"' near end]
-  \end{tikzcd}\,.
-  \]
-Our main technical result in this section will be the following:
-\begin{proposition}
-  The category $j$-$\Cat$ of $j$-categories and $j$-category morphisms has an initial object $C_j$
-\end{proposition}
-By analogy with homotopy theory, we call this initial object the \emph{mapping cone} or \emph{cone} on $j$.
-
-To see why this is useful, consider another important topic from the theory of semantics.  
-We say that a $j$-category $(\D,J,\phi)$ satisfies \emph{$\phi$-factorization} if for any pair of objects $A$ and $B$ of $\C$ and for every morphism $f\from JA \to JB$ in $\D$, we may write $f$ as a composite
-\[
-  JA \xrightarrow{\lunit;\phi_X\tensor JA}
-  Jj X \tensor JA \xrightarrow{m_J}
-  J (jX \tensor A) \xrightarrow{J f'}
-  JB\,,
-  \]
-where $X$ is some object of $\C'$ and $f'\from jX \tensor A\to B$ is some morphism in $\C$.
-\begin{example}
-  In the case that $j$ is the inclusion $\G_{sw,rec}\hookrightarrow\G_{rec}$, and $\phi=\top$, $\phi$-factorization is the same as \emph{deterministic factorization}: the idea that every morphism can be written as the composition of a deterministic recursive strategy with $\top_X$ for some $X$.
-\end{example}
-
-Then the following result is easy to prove:
-\begin{proposition}
-  Let $(\D,J,\phi)$ be a $j$-category satisfying $\phi$-factorization.  
-  Suppose $\F\from\D'\to\D$ is a morphism of $j$-categories.  
-  Then $\F$ is a full functor.
-\end{proposition}
-In particular, the unique $j$-category morphism $C_j\to\D$ is a full functor.  
-This is useful, because we are viewing game semantic models of nondeterministic PCF as $j$-categories (for a particular $j$), and therefore we can see that $C_j$ admits a full functor into every such model that satisfies deterministic factorization.
-Since we typically require that our models satisfy such a factorization result, we can form any such model by taking $C_j$ and imposing some equivalence relation on the morphisms.  
-This suggests that we might consider $C_j$ itself as our model of nondeterministic PCF.
-
-\subsection{Constructing the cone}
-
-We will now define what the cone $C_j$ is and give an outline of why it is initial in the category of $j$-categories.
-
-Recall that we start with an oplax symmetric monoidal functor $j\from \C'\to\C$.  
-The objects of $C_j$ are the objects of $\C$.  
-Given objects $A,B$ of $\C$, the class of morphisms $A\to B$ is given by the colimit of the functor
-\[
-  \oppcat{\C'} \xrightarrow{\oppcat{j}}
-  \oppcat{\C} \xrightarrow{\C[\blank\tensor A,B]}
-  \Set\,.
-  \]
-That is, a morphism from $A$ to $B$ is a pair $(X,f)$, where $X$ is an object of $\C'$ and $f\from jX \tensor A \to B$ is a morphism in $\C$.  
-Furthermore, $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute:
-\[
-  \begin{tikzcd}
-    j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
-      & B \\
-    j X \tensor A \arrow[ur, "f"']
-      &
-  \end{tikzcd}\,.
-  \]
-Given morphisms $(X,f)\from A \to B$, $(Y,g)\from B \to C$, the composite is given by $(Y\tensor X,f;g)$, where $f;g$ is the following composite in $\C$:
-\begin{align*}
-  j(Y\tensor X)\tensor A & \xrightarrow{m_j\tensor A}
-    (jY \tensor jX) \tensor A \\ & \xrightarrow{\assoc}
-      jY \tensor (jX \tensor A) \\ & \xrightarrow{jY \tensor f}
-        jY \tensor B \xrightarrow{g}
-          C\,.
-\end{align*}
-We can prove that this composition is associative using the usual coherence theorems for monoidal categories.  
-Similarly, the symmetric monoidal structure from $\C$ induces a symmetric monoidal structure on $C_j$.  
-If $\C$ is symmetric monoidal \emph{closed}, then so is $C_j$.
-
-There is a functor $J\from \C\to C_j$ that is the identity on objects and which sends a strategy $f\from A \to B$ to the strategy
-\[
-  j I \tensor A \xrightarrow{\epsilon_j\tensor A}
-  I \tensor A \xrightarrow{\lunit\inv}
-  A \xrightarrow{f} B\,.
-  \]
-This functor is (strong) symmetric monoidal with respect to the monoidal structure on $C_j$.  
-Lastly, the natural transformation $\phi\from I \Rightarrow J\circ j$ is given by the composite
-\[
-  \phi_X = jX \tensor I \xrightarrow{\runit\inv}
-  jX\,,
-  \]
-considered as a morphism from $I$ to $jX$ in $C_j$.  
-Proving that this is indeed a natural transformation makes essential use of the equivalence relation on morphisms in $C_j$.  
-We can also prove that $\phi$ is a generalized monoidal natural transformation.  
-Therefore, $C_j$ is a $j$-category.
-
-Now suppose that $(\D,F,\psi)$ is another $j$-category.  
-We define a functor $H\from C_j\to\D$ that sends an object $A=JA$ in $C_j$ to the object $FA$ in $\D$.  
-Moreover, we send a morphism $f\from jX\tensor A \to B$ from $JA$ to $JB$ in $C_j$ to the following composite in $\D$:
-\begin{align*}
-  FA \xrightarrow{\lunit;\psi_X\tensor FA}
-  FjX \tensor FA \xrightarrow{m_F}
-  F (jX \tensor A) \xrightarrow{F f}
-  F B\,.
-\end{align*}
-Proving that this is indeed a functor is a little tricky, and relies on $\psi$ being a generalized monoidal natural transformation.  
-We can then go through and check that $H$ is indeed a morphism of $j$-categories.
-
-In order to prove uniqueness, note that, as a morphism of $j$-categories, $H$ is determined on morphisms of the form $Jf$ by the equation $F = H \circ J$ and on morphisms of the form $\phi_X$ by the equation $\psi=\vc{\phi}{H}$.
-But now, if $f\from jX\tensor A \to B$ is any morphism from $A$ to $B$ in $C_j$, we may write $f$ as the composite
-\[
-  JA \xrightarrow{\lunit;\phi_X\tensor A}
-  JjX \tensor JA \xrightarrow{m_J}
-  J (jX \tensor A) \xrightarrow{Jf}
-  JB\,;
-  \]
-i.e., $C_j$ satisfies $\phi$-factorization.  
-Since the functor $H$ is required to be monoidal, this implies that it is determined everywhere on $C_j$ by the requirement that it be a morphism of $j$-categories.
-Therefore, $C_j$ is initial in the category of $j$-categories.
-
-A consequence of the initiality of the cone construction is that it is \emph{functorial}; that is, given a square of the following form:
-\[
-  \begin{tikzcd}[row sep=large, column sep=large]
-    \C' \arrow[r, "F", ""'{name=term}] \arrow[d, "j"']
-      & \D' \arrow[d, "j'"] \\
-    \C \arrow[r, "G"', ""{name=J}]
-      & \D
-    \arrow[Rightarrow, from=term, to=J, "\psi"]
-  \end{tikzcd}\,,
-  \]
-where horizontal arrows correspond to lax monoidal functors and vertical arrows to monoidal functors, we get an induced lax monoidal functor $C_{j}\to C_{j}$, in a way that respects horizontal pasting of squares.
-In particular, if $\C$ and $\C'$ have linear structures, compatible with $j$, then $C_j$ inherits a linear structure.
-
-\section{Denotational Semantics}
-
-We now restrict our attention to the inclusion functor $j\from G_{sw,rec}\hookrightarrow \G_{rec}$.  
-Then $C_j$ inherits a linear structure from $\G_{rec}$.
-
-\subsection{Extensional order}
-
-Let $\sigma,\tau\from I \to \bN$ be morphisms in $C_j$, corrseponding to morphisms $\sigma'\from jX \to \bN$, $\tau'\from jY \to \bN$ in $\G_{rec}$.  
-We say that $\sigma\lst\tau$ if the following two conditions hold:
-\begin{itemize}
-  \item If there exists $s\in \sigma'$ such that $s\vert_{\bN}=qn$, then there exists $t\in\tau'$ such that $t\vert_{\bN}=qn$.
-  \item If $\sigma'$ is winning then $\tau'$ is winning.
-\end{itemize}
-In general, given strategies $\sigma,\tau\from I \to A$ in $C_j$, we say that $\sigma\lst\tau$ if for all morphisms $\rho\from A \to \bN$ we have $\sigma;\rho\lst\tau;\rho$.
-
-We can show that this is well-defined; i.e., that it respects the equivalence relation we have already defined on morphisms.  
-This is a good exercise to show the importance of surjective and winning strategies to our model.
-
-\subsection{Countable nondeterminism}
-
-In order to model \emph{countable} nondeterminism, rather than arbitrary nondeterminism, we want to constrain our model so that morphisms are strategies for $\oc\bN\tensor A \to B$, rather than $X \tensor A \to B$ for an arbitrary game $X$.
-
-Since $\oc\bN$ has the structure of a comonoid, it gives rise to an oplax monoidal functor
-\[
-  n\from I \to \G_{rec}\,,
-  \]
-where $I$ is the one-object monoidal category.  
-Moreover, this functor is linear distributive from the trivial linear structure on $I$ on to $\G$.
-The cone $C_n$ is therefore a linear category.
-
-Since $\G_{sw,rec}$ is a sub-linear category of $\G_{rec}$, the functor $n$ factors through a functor $n'\from I \to \G_{rec}$.  
-By initiality of the cone construction, this gives rise to a functor $C_n\to C_j$.  
-Our model of nondeterministic PCF will be the category $\C$ that is the image of this functor.
-A morphism in $\C$ from a game $A$ to a game $B$ will be a strategy for $\oc \bN \tensor A \to B$, but the equivalence relation on morphisms is that from $C_j$.  
-For example, two morphisms $f,g\from \oc\bN\to A$ are equivalent in $\C$ if there is a surjective winning strategy $\oc\bN\to \oc\bN$ commuting with $f$ and $g$, but they are not equivalent in $C_n$.
-
-In fact, once we have applied the extensional quotient, there is no difference between working in $\C$ and working in $C_n$.  
-We will use $\C$, because it is closer to being a fully abstract model for nondeterministic PCF before we apply the extensional quotient.
-
-\subsection{The denotation of a term}
-
-Let $M=C[\wn]\from T$ be a term of nondeterministic PCF, where $C[-]$ is a PCF context (i.e., a context not mentioning the constant $\wn$).  
-Then the denotation of $M$ in $\C$ is given by the following composite:
-\[
-  I \xrightarrow{\phi_{\oc\bN}}
-  \oc \bN \xrightarrow{J (\deno{\lambda n. C[n]})}
-  \deno{T}
-  \]
-In other words, when considered as a morphism in $\G_{rec}$, $\deno{M}$ is precisely the denotation of the term $\lambda n.C[n]$ in $\G_{rec}$.
-
-\subsection{Relation to our previous model}
-
-Since our Harmer-McCusker-style model $\G_{ND}$
+Note that in the recursive case, $\Det(\sigma)$ is clearly recursively presentable if $\sigma$ is.  
+Furthermore, if $\sigma$ is visible, then so is $\Det(\sigma)$.
 

### 2018-01-27 cones/paper/cones.tex
Finished full abstraction proof.

@@
 
-Let $T$ be an Idealized Algol type, and let $M,N\from T$ be terms.  
+If $\ia\emptyset M$ is a configuration with empty store, we call $M$ a \emph{closed term}.  
+Let $T$ be an Idealized Algol type, and let $M,N\from T$ be closed terms.
 Then we write $M\lmam N$ if for all compatible contexts $C[-]$ of ground type we have
@@
   Then $\sigma;\tau$ is complete.
+  \label{lem:complete-deterministic-composition}
 \end{lemma}
@@
   The composition of strategies $\sigma\from A\implies B$ and $\tau\from B \implies C$ is a well-formed strategy for $A\implies C$.
+  \label{cor:diverge-or-reply}
 \end{corollary}
@@
 \end{proof}
+
+Our proof for Corollary \ref{cor:diverge-or-reply} really makes use of the fact that a locally complete strategy is \emph{lively} in the sense of \cite{LevyGsInfinite}; i.e., locally deterministic.  
+Our definition is slightly stronger than liveliness, because it insists that the union of complete strategies be \emph{countable}.  
+This will be essential to our definability result.
 
@@
 
+\section{Full abstraction}
+
+\subsection{Denotational Semantics}
+
+The category in which we shall model our language is the category $\G_{ND,vis,rec}^\oc$ -- the Cartesian closed category of (enumerated) games with nondeterministic, recursively presentable visible strategies.
+We have a natural embedding $\G_{D,vis,rec}^\oc\hookrightarrow\G_{ND,vis,rec}^\oc$, and we know that $\G_{D,vis,rec}^\oc$ is a universal and fully abstract model of Idealized Algol.
+
+Any term $M\from T$ of Idealized Algol with countable nondeterminism may be written as $M = C[\wn]$, where $C$ is a context not involving the constant $\wn$.  
+Then the term $\lambda n.C[n]$ is a term of Idealized Algol, and therefore has a denotation $\oc\bN \to \deno{T}$ as in \cite{SamsonGuyIAPassive}.
+We define the denotation of $M$ to be given by the composite
+\[
+  I \xrightarrow{\top_{\bN}}
+  \oc \bN \xrightarrow{\deno{\lambda n.C[n]}}
+  \deno{T}
+  \]
+In other words, we interpret the constant $\wn$ using the strategy $\top_{\bN}$ for $\bN$.
+
+\subsection{Adequacy and soundness}
+
+We prove a \emph{consistency} result for our model.  
+Let $M$ be a closed term of type $\com$.
+
+\begin{lemma}
+  If $M\converges\skipp$ then $qa\in T_{\deno M}$.  
+  If $M\mustconverge$ then $D_{\deno M}=\emptyset$.
+  \label{lem:consistency}
+\end{lemma}
+
+We can also prove the converse, \emph{computational adequacy}.
+
+\begin{proposition}
+  If $qa\in T_{\deno M}$ then $M\converges\skipp$.
+  If $D_{\deno M}=\emptyset$ then $M\mustconverge$.
+  \label{prop:adequacy}
+\end{proposition}
+
+In order to prove these, we come back to the concept of an \emph{evaluation} of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
+
+\begin{lemma}
+  Let $M=C[\wn]$ be a term of type $\com$.  
+  Write $\sigma_M$ for the denotation of the term $\lambda n.C[n]$.  
+  Let $\pi$ be some evaluation of the configuration $\ia s M$, where $s$ is some state.  
+  Then there is a deterministic total strategy $\sigma_\pi\from \oc\bN$ such that
+  \begin{itemize}
+    \item $\pi$ terminates at the value $\skipp$ if and only if then $qa\in T_{\sigma_\pi;\sigma_M}$.
+    \item $\pi$ diverges if and only if $D_{\sigma_\pi;\sigma_M}\ne\emptyset$.
+  \end{itemize}
+  \label{lem:soundness-lemma}
+\end{lemma}
+
+\begin{proof}
+  Let $n_1,\dots,n_k,d$ be a finite sequence of natural numbers.  
+  We define an Idealized Algol term $N_{n_1,\dots,n_k,d}\from (\nat \to \com) \to \com$ to be the following.
+  \[
+    \lambda f.\new_\nat (\lambda v.f(v\coloneqq (suc\;\deref v); \case_{k+1}\;\deref v\;\Omega\;n_1 \cdots n_k d))\,.
+    \]
+  Here, $\case_{k+1}\;a\;n_0\;\cdots\;n_k\;d$ evaluates to $n_i$ if $a$ evaluates to $i$, and evaluates to $d$ if $a$ evaluates to $j> k$.
+  Clearly, it can be built out of $\IfO$s.
+  This term adds an extra variable $v$ to the program; each time $f$ is called, it increments the value of $v$ and maps its value on to one of the $n_i$.
+
+  Now let $\pi$ be a finite evaluation of $\ia s {C[\wn]} \converges\skipp$.  
+  Encode $\pi$ as a sequence $n_1,\dots,n_k$.  
+  Let $d$ be some arbitrary number.
+  Then we can show that the following term also converges to $\skipp$ in the same way:
+  \[
+    N_{n_1,\dots,n_k,d} (\lambda n.C[n])\,.
+    \]
+  The idea here is similar to one used in testing; we want to test the behaviour of a nondeterministic program, and to do so we \emph{mock} the random number generator in order to simulate a particular evaluation path using purely deterministic programs.
+
+  If instead $\pi$ is a finite evaluation of $\ia s {C[\wn]}\not\mustconverge$; i.e., a divergent evaluation (that nevertheless only involves finitely many calls to the nondeterministic oracle), then the term $N_{n_1,\dots,n_k,d} (\lambda n.C[n])$ will diverge according to the same execution path.
+
+  Digging into the construction of $\new$ within Idealized Algol, as given in \cite{SamsonGuyIAPassive}, we see that for any term $F$ of type $\nat\to\com$ the denotation of $N_{n_1,\dots,n_k,d} F$ is given by the composite
+  \[
+    I \xrightarrow{\cell_{0}}
+    \oc \Var \xrightarrow{\deno{\lambda v.v\coloneqq (\suc\;\deref v);\case_{k+1}\;\deref v\;\Omega\;n_1\cdots n_k d}}
+    \oc\bN \xrightarrow{\deno F}
+    \bC\,.
+    \]
+  We set $\sigma_\pi$ to be the composite of the left two arrows.  
+  Observe that $\sigma_\pi$ is the strategy with unique maximal infinite play as follows.
+  \[
+    q\;n_1\;\cdots\;q\;n_k\;q\;d\;q\;d\;\cdots
+    \]
+  Setting $F = \lambda n.C[n]$, we see that $\deno{F}=\sigma_M$.  
+  So, by soundness and adequacy for the Idealized Algol model, we see that $qa\in T_{\sigma_\pi;\sigma_M}$ if and only if $N_{n_1,\dots,n_k,d} (\lambda n.C[n])\converges\skipp$, which is the case if and only if $M\converges\skipp$ along the evaluation $\pi$.
+  Similarly, $D_{\sigma_\pi;\sigma_M}\neq\emptyset$ if and only if $N_{n_1,\dots,n_k,d}(\lambda n.C[n])$ diverges, which is equivalent to saying that $M$ diverges along the evaluation $\pi$.
+
+  Lastly, we need to deal with the case that $\pi$ is an evaluation $n_1,n_2,\dots$ that consults the nondeterministic oracle infinitely often.
+  In this case, $M$ must certainly diverge along the evaluation $\pi$.
+  In that case, we define $\pi_n^{(j)}$ to be the strategy for $\oc N$ corresponding to the term $N_{n_1,\dots,n_j,\Omega}$.  
+  So $\pi_n^{(j)}$ has a unique finite maximal play
+  \[
+    q\;n_1\;q\;n_2\;\cdots\;q\;n_j\;q\,,
+    \]
+  at which point the strategy has a partiality.
+
+  Evaluation of the term $N_{n_1,\dots,n_j,\Omega} (\lambda n.C[n])$ must diverge, since it will proceed according to the evaluation $\pi$ and eventually reach the divergence (since $\pi$ consults the oracle infinitely often).
+  This implies that $D_{\sigma_\pi^{(j)};\sigma_M}\ne\emptyset$ for all $j$.
+
+  We define $\sigma_\pi$ to be the least upper bound of the $\sigma_\pi^{(j)}$ (e.g., in the sense of \cite{mcCHFiniteND}).  
+  Since composition is continuous for deterministic (!) strategies, we deduce that $D_{\sigma_\pi;\sigma_M}\ne\emptyset$.
+
+  $\sigma_\pi$ has plays of the form
+  \[
+    q\;n_1\;q\;n_2\;\cdots\,,
+    \]
+  and so it is total.
+\end{proof}
+
+We can now prove our soundness and adequacy results.
+
+\begin{proof}[Proof of Lemma \ref{lem:consistency}]
+  Suppose that that $M$ is a closed term of type $\com$ and that $M\converges\skipp$.  
+  Let $\pi$ be an evaluation such that $M\converges\skipp$ along $\pi$.  
+  Then $qa\in T_{\sigma_\pi;\sigma_M}$ for some strategy $\sigma_\pi$.  
+  It follows that $qa\in T_{\top_\bN;\sigma_M}$.
+
+  Now suppose that $D_{\deno M}\neq\emptyset$.  
+  Then there is some interaction $\s\in\int_\infty(I,\oc\bN,\bC)$ such that $\s\vert_\bC\in D_{\sigma_M}$.
+  Let $\sigma$ be the minimal deterministic strategy for $\oc\bN$ containing the play $\s\vert_{\oc\bN}$.  
+  By the proof of Lemma \ref{lem:soundness-lemma}, $\sigma\subset\sigma_\pi$ for some evaluation $\pi$ of $M$.  
+  Then we have $D_{\sigma_\pi;\sigma_M}\ne\emptyset$, so $M$ diverges along $\pi$.
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:adequacy}]
+  Suppose that $M$ is a closed term of type $\com$ and that $qa\in T_{\deno M}$.  
+  Then there is some interaction $\s\in\int_\infty(I,\oc\bN,\bC)$ such that $qa\in\s\vert_\bC$.  
+  Let $\sigma$ be the minimal deterministic strategy for $\oc\bN$ containing the play $\s\vert_{\oc\bN}$.  
+  By the proof of Lemma \ref{lem:soundness-lemma}, $\sigma\subset\sigma_\pi$ for some evaluation $\pi$ of the term $M$.
+  Then we have $qa\in T_{\sigma_\pi;\sigma_M}$, so $M\converges\skipp$ along $\pi$.
+
+  Now suppse that $M\not\mustconverge$.  
+  Let $\pi$ be a divergent evaluation of $M$.  
+  Then we have $D_{\sigma_\pi;\sigma_M}\ne\emptyset$.  
+  Moreover, since $\sigma_\pi$ is total, it follows that $D_{\top_{\bN};\sigma_M}\ne\emptyset$.
+\end{proof}
+
+We define \emph{extensional equivalence of strategies} as follows.  
+If $\sigma,\tau$ are two strategies for a game $A$, we say that $\sigma\oes\tau$ if for all test morphisms $\alpha\from A \to \bC$ we have $\sigma;\alpha=\tau;\alpha$.  
+Having defined this equivalence, we may prove \emph{soundness} in the usual way.
+
+\begin{theorem}[Soundness]
+  Let $M,N$ be two closed terms of type $T$.  
+  If $\deno{M}\oes\deno{N}$ then $M\emam N$.  
+\end{theorem}
+
+\subsection{Universality}
+
+Let $S,T$ be Idealized Algol types and let $\sigma\from S\to T$ be a morphism in $\G_{ND,vis,rec}^\oc$.  
+We want to prove that $\sigma$ is the denotation of some term.
+
+By our nondeterministic factorization result, we know that $\sigma=\top_\bN;\Det(\sigma)$, where $\Det(\sigma)$ is a deterministic strategy.  
+By universality for $\G_{D,vis,rec}^\oc$, we know that $\Det(\sigma)=\deno{M}$ for some closed term $M\from S \to T$.  
+Then $\sigma=\top_\bN;\Det(\sigma)=\deno{\wn};\deno M = \deno{M\;\wn}$.
+
+\subsection{Full abstraction}
+
+\begin{theorem}[Full abstraction]
+  Let $M,N$ be two closed terms of type $T$.  
+  If $M\emam N$ then $\deno{M}\oes\deno{N}$.  
+\end{theorem}
+\begin{proof}
+  Let $A=\deno T$.  
+  Suppose that $\deno{M}\not{\oes}\deno{N}$; so there is some strategy $\alpha\from A\to\bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.  
+  By universality, we have $A=\deno{P}$ for some closed term $P$ of type $T\to\com$.  
+  Then we have $\deno{M};\deno{P}\ne\deno{N};\deno{P}$; by consistency and adequacy, it follows that $M\not{\emam} N$.
+\end{proof}
+
 %% Acknowledgments

### 2018-01-28 cones/paper/cones.tex
Wrote section about Tsukada-Ong games.

@@
   In the first case, the diverge-or-reply rule for $\sigma$ and $\tau$ gives us a divergence at $s$ in $\sigma;\tau$.  
-  In the second case, an infinite chattering between $\sigma$ and $\tau$ corresponds to an infinite interaction $\s\in\int(A,B,C)$ ending with infinitely many moves in $B$ such that $\s\vert_{A,C}=s$.
+  In the second case, an infinite chattering between $\sigma$ and $\tau$ corresponds to an infinite interaction $\s\in\Int(A,B,C)$ ending with infinitely many moves in $B$ such that $\s\vert_{A,C}=s$.
   Completeness for $\sigma$ and $\tau$ tells us that $\s\vert_{A,B}\in D_\sigma$ and $\s\vert_{B,C}\in D_\tau$ and therefore that $\s\vert_{A,C}\in D_{\sigma;\tau}$.  
@@
 
-In order to prove these, we come back to the concept of an \emph{evaluation} of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
+Traditional proofs of computational adequacy using logical relations make essential use of the continuity of composition with respect to a natural ordering on strategies (see, for example, \cite{mcCHFiniteND} and \cite{RusssThesis} for the finite nondeterminism case).
+In our case, since composition is not continuous in the language itself, we cannot use this technique.
+In order to prove soundness and adequacy, we use a new technique that involves using a deterministic stateful construction to model the nondeterminism inside a deterministic world in which continuity holds.
+We shall return to the concept of an \emph{evaluation} of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
 
@@
   Write $\sigma_M$ for the denotation of the term $\lambda n.C[n]$.  
-  Let $\pi$ be some evaluation of the configuration $\ia s M$, where $s$ is some state.  
-  Then there is a deterministic total strategy $\sigma_\pi\from \oc\bN$ such that
   \begin{itemize}
-    \item $\pi$ terminates at the value $\skipp$ if and only if then $qa\in T_{\sigma_\pi;\sigma_M}$.
-    \item $\pi$ diverges if and only if $D_{\sigma_\pi;\sigma_M}\ne\emptyset$.
+    \item $M\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$.
+    \item $M\not{\mustconverge}$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$.
   \end{itemize}
@@
 \begin{proof}
+  We prove the forward directions first.
+
   Let $n_1,\dots,n_k,d$ be a finite sequence of natural numbers.  
@@
 
-  Lastly, we need to deal with the case that $\pi$ is an evaluation $n_1,n_2,\dots$ that consults the nondeterministic oracle infinitely often.
+  Lastly, we need to deal with the case that there is an infinite evaluation $\pi = n_1,n_2,\dots$ of $M$ that consults the nondeterministic oracle infinitely often.
   In this case, $M$ must certainly diverge along the evaluation $\pi$.
-  In that case, we define $\pi_n^{(j)}$ to be the strategy for $\oc N$ corresponding to the term $N_{n_1,\dots,n_j,\Omega}$.  
+  For each $j$, we define $\pi_n^{(j)}$ to be the strategy for $\oc N$ corresponding to the term $N_{n_1,\dots,n_j,\Omega}$.  
   So $\pi_n^{(j)}$ has a unique finite maximal play
@@
   and so it is total.
+
+  We now prove the reverse implications.  
+  Let $\sigma\from\bN$ be a total deterministic strategy for $\oc\bN$.
+  Then $\sigma$ must have a maximal infinite play $s_\sigma$ of the form
+  \[
+    q\;m_1\;q\;n_2\;\cdots\,,
+    \]
+  where $m_1,m_2,\dots$ is some infinite sequence of natural numbers.  
+  If the strategy $\sigma_M$ contains some play $\s$ such that $\s\vert_{\oc\bN}=s$, then $\sigma=\sigma_\pi$ for some infinite evaluation $\pi$ of $M$.  
+  Otherwise, let $t$ be the maximal subplay of $s$ such that $\s\vert_{\oc\bN}=t$ for some $\s\in\sigma_M$.  
+  Then, if we replace $\sigma$ with the strategy $\sigma'$ that plays according to $t$ and subsequently plays $q\;d\;q\;d\;\cdots$ for our fixed value $d$, then we will have $\sigma';\sigma_M=\sigma;\sigma_M$.
+  Moreover, $\sigma'=\sigma_\pi$ for some evaluation $\pi$ of $M$.
+
+  Now suppose that there exists $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$.  
+  By the above discussion, we may assume that $\sigma=\sigma_\pi$ for some evaluation $\pi$ of $M$.  
+  Therefore, $qa\in T_{\sigma_\pi;\sigma_M}$, which means that $M\converges\skipp$ along the evaluation $\pi$.  
+  The corresponding statement for must convergence follows in the same way.
 \end{proof}
@@
   Suppose that that $M$ is a closed term of type $\com$ and that $M\converges\skipp$.  
-  Let $\pi$ be an evaluation such that $M\converges\skipp$ along $\pi$.  
-  Then $qa\in T_{\sigma_\pi;\sigma_M}$ for some strategy $\sigma_\pi$.  
+  Then $qa\in T_{\sigma;\sigma_M}$ for some strategy $\sigma$.  
   It follows that $qa\in T_{\top_\bN;\sigma_M}$.
@@
   Now suppose that $D_{\deno M}\neq\emptyset$.  
-  Then there is some interaction $\s\in\int_\infty(I,\oc\bN,\bC)$ such that $\s\vert_\bC\in D_{\sigma_M}$.
-  Let $\sigma$ be the minimal deterministic strategy for $\oc\bN$ containing the play $\s\vert_{\oc\bN}$.  
-  By the proof of Lemma \ref{lem:soundness-lemma}, $\sigma\subset\sigma_\pi$ for some evaluation $\pi$ of $M$.  
-  Then we have $D_{\sigma_\pi;\sigma_M}\ne\emptyset$, so $M$ diverges along $\pi$.
+  Then there is some interaction $\s\in\Int_\infty(I,\oc\bN,\bC)$ such that $\s\vert_\bC\in D_{\sigma_M}$.
+  Let $\sigma$ be a deterministic total strategy containing $\s\vert_{\oc\bN}$.  
+  Then we have $D_{\sigma;\sigma_M}\ne\emptyset$, so $M$ diverges by Lemma \ref{lem:soundness-lemma}.
 \end{proof}
@@
   Suppose that $M$ is a closed term of type $\com$ and that $qa\in T_{\deno M}$.  
-  Then there is some interaction $\s\in\int_\infty(I,\oc\bN,\bC)$ such that $qa\in\s\vert_\bC$.  
-  Let $\sigma$ be the minimal deterministic strategy for $\oc\bN$ containing the play $\s\vert_{\oc\bN}$.  
-  By the proof of Lemma \ref{lem:soundness-lemma}, $\sigma\subset\sigma_\pi$ for some evaluation $\pi$ of the term $M$.
-  Then we have $qa\in T_{\sigma_\pi;\sigma_M}$, so $M\converges\skipp$ along $\pi$.
+  Then there is some interaction $\s\in\Int_\infty(I,\oc\bN,\bC)$ such that $qa\in\s\vert_\bC$.  
+  Let $\sigma$ be a deterministic total strategy for $\oc\bN$ containing the play $\s\vert_{\oc\bN}$.  
+  Then we have $qa\in T_{\sigma;\sigma_M}$, so $M\converges\skipp$ by Lemma \ref{lem:soundness-lemma}.
 
   Now suppse that $M\not\mustconverge$.  
-  Let $\pi$ be a divergent evaluation of $M$.  
-  Then we have $D_{\sigma_\pi;\sigma_M}\ne\emptyset$.  
+  Then we have $D_{\sigma;\sigma_M}\ne\emptyset$ for some strategy $\sigma\from\oc\bN$.
   Moreover, since $\sigma_\pi$ is total, it follows that $D_{\top_{\bN};\sigma_M}\ne\emptyset$.
@@
 
+\section{Nondeterministic PCF}
+
+We conclude by saying a few remarks about the situation when our base deterministic language is PCF rather than Idealized Algol.  
+Tsukada and Ong \cite{TsukadaSheaves} showed that traditional game semantics models are unsuitable for modelling this language: while the definition of \emph{visibility} of strategies can be extended to nondeterministic strategies without difficulty, the corresponding definition for PCF -- that of an \emph{innocent} strategy -- does not.
+Tsukada and Ong instead use a new type of game semantics in which strategies are given not by sets of plays but by justified \emph{trees} whose vertices are moves.  
+The difference is subtle but important: from the point of view of countable nondeterminism it allows us to distinguish between terms that take an arbitrarily large finite number of steps to converge and terms that diverge.
+For example, the denotation of our term $M$ above has an infinite branch in it, while the denotation of $N$ has infinitely many finite branches of arbitrary length.
+
+The main advantage of the tree-based model, however, is that it gives rise to a satisfactory synthetic definition of a \emph{nondeterministic innocent} strategy based on sheaves.  
+In fact, Tsukada and Ong do not prove full abstraction for PCF with countable nondeterminism (even though that language may be interpreted within their category), but for PCF with finite nondeterminism.
+
+Having ourselves given a fully abstract model of Idealized Algol with countable nondeterminism, we shall contribute to the process of `completing the square' by giving a sketch of how we can use our techniques to prove soundness and adequacy for the Tsukada-Ong model of PCF with countable nondeterminism.
+A side-effect of this will be to give an alternative proof of soundness and adequacy for their model of PCF with finite nondeterminism.
+
+The first observation to make is that our Lemma \ref{lem:soundness-lemma} is not really a statement about the category $\G_{ND,vis}$, but one about the deterministic model $\G_{D,vis}$.
+
+For example, the first part of the lemma says that if $C[-]$ is an ordinary deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
+Although we have mentioned a term ($C[\wn]$) living in nondeterministic Idealized Algol, this can be thought of as a statement about $C[-]$ itself, which is part of deterministic Idealized Algol.  
+Moreover, the strategy $\sigma$ and the denotation of $\lambda n.C[n]$ are both deterministic strategies, so we can interpret Lemma \ref{lem:soundness-lemma} as telling us something about Idealized Algol and its game semantics.
+We can therefore forget about our nondeterminism model, with its divergence sets and infinite plays (neither of which are part of the Tsukada-Ong model) and concentrate on the Abramsky-McCusker model of Idealized Algol.
+Note that although Lemma \ref{lem:soundness-lemma} mentions $T_{\sigma;\sigma_M}$ and $D_{\sigma;\sigma_M}$, we can rephrase both of these inside the deterministic model, since the strategies involved are both deterministic.
+
+The second observation is that Lemma \ref{lem:soundness-lemma} can just as easily be applied to PCF contexts and its game semantics model $\G_{inn}$.  
+There really is nothing to this observation: since any PCF context may be interpreted in Idealized Algol, then Lemma \ref{lem:soundness-lemma} applies to it.
+So we have narrowed \ref{lem:soundness-lemma} down to a result about $\G_{inn}$.
+
+Now we have an inclusion functor $\G_{inn}\hookrightarrow\G_{TO}$, where $\G_{TO}$ is the Tsukada-Ong category.  
+Since the nondeterministic oracle $\wn$ may also be interpreted as a tree-strategy $\top_{\bN}$ in $\G_{TO}$, this gives us a model of PCF with countable nondeterminism inside that category.
+
+It is then possible to deduce versions of Lemma \ref{lem:consistency} and Proposition \ref{prop:adequacy} from Lemma \ref{lem:soundness-lemma} as we did above, using the details of the inclusion functor from $\G_{inn}$ and the definition of composition in $\G_{TO}$.
+We can then deduce soundness in the usual way.
+
+\begin{theorem}[Soundness for nondeterministic PCF]
+  Let $M,N\from T$ be two terms of PCF with countable nondeterminism.
+  If $\deno M\oes \deno N$, then $M\emam N$, where the denotation $\deno -$ is taken in the category $\G_{TO}$.  
+\end{theorem}
+
+An alternative line of attack is to first build a copy of our model of Idealized Algol with coutable nondeterminism inside $\G_{TO}$, using our argument to prove soundness and adequacy, and then restrict down to nondeterministic PCF.
+
 %% Acknowledgments

### 2018-01-28 cones/paper/cones.tex
Wrote about the base games N and C.
Ran spell checker.

@@
 
-This is a bit of a problem, since continuity often plays an important role in full abstraction proofs -- firstly, for proving Computational Adequacy of the recursion combinator, and, secondly, for deducing full abstraction from compact definability.
+This is a bit of a problem, since continuity often plays an important role in full abstraction proofs -- firstly, for proving Computational Adequacy of the recursion combinator, and, secondly, for deducing full abstraction from definability of compact elements.
 Semantically, we shall deal with the first problem by adopting a novel approach to Computational Adequacy, and with the second problem by appealing to the stronger \emph{universality} result: namely, that every \emph{recursive} strategy is definable.
@@
 A \emph{game} is a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$, where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed set of legal plays in that arena such that if $s\in P_A$ and $I$ is a non-empty set of initial moves in $s$, then $s\vert_I\in P_A$.
+
+Our base games will be the games $\bN$ and $\bC$ on the arenas of the same names, where $P_{\bN}=\{\emptyplay,q\}\cup\{qn\suchthat n\in\bN\}$ and $\bC = \{\emptyplay,q,qa\}$.
 
@@
 
-Somehow, the crucial point is that we need to distinguish between terms like $M$, which contain infinite sequences of moves, and terms like $N$, which contain arbitrarily large finite sequences of oves.
+Somehow, the crucial point is that we need to distinguish between terms like $M$, which contain infinite sequences of moves, and terms like $N$, which contain arbitrarily large finite sequences of moves.
 The way that we do this is by making the infinite sequences of moves explicit in our strategies, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.  
-Then the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitarily long finite sequences, but no infinite sequences.
+Then the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitrarily long finite sequences, but no infinite sequences.
 
@@
 \begin{proof}
-  The only tricky point is eastablishing that diverge-or-reply holds for $\sigma;\tau$.  
+  The only tricky point is establishing that diverge-or-reply holds for $\sigma;\tau$.  
   Again, it is sufficient to prove this in the case that $\sigma$ and $\tau$ are deterministic and complete.
@@
 
-\subsection{Determinisitic Factorization}
+\subsection{Deterministic Factorization}
 
@@
   If the strategy $\sigma_M$ contains some play $\s$ such that $\s\vert_{\oc\bN}=s$, then $\sigma=\sigma_\pi$ for some infinite evaluation $\pi$ of $M$.  
-  Otherwise, let $t$ be the maximal subplay of $s$ such that $\s\vert_{\oc\bN}=t$ for some $\s\in\sigma_M$.  
+  Otherwise, let $t$ be the maximal sub-play of $s$ such that $\s\vert_{\oc\bN}=t$ for some $\s\in\sigma_M$.  
   Then, if we replace $\sigma$ with the strategy $\sigma'$ that plays according to $t$ and subsequently plays $q\;d\;q\;d\;\cdots$ for our fixed value $d$, then we will have $\sigma';\sigma_M=\sigma;\sigma_M$.
@@
 
-  Now suppse that $M\not\mustconverge$.  
+  Now suppose that $M\not\mustconverge$.  
   Then we have $D_{\sigma;\sigma_M}\ne\emptyset$ for some strategy $\sigma\from\oc\bN$.
@@
 
-An alternative line of attack is to first build a copy of our model of Idealized Algol with coutable nondeterminism inside $\G_{TO}$, using our argument to prove soundness and adequacy, and then restrict down to nondeterministic PCF.
+An alternative line of attack is to first build a copy of our model of Idealized Algol with countable nondeterminism inside $\G_{TO}$, using our argument to prove soundness and adequacy, and then restrict down to nondeterministic PCF.
 

### 2018-01-28 cones/paper/cones.tex
Filled in title, abstract etc.

@@
 %% Title information
-\title[Short Title]{Full Title}         %% [Short Title] is optional;
+\title{A Fully Abstract Game Semantics for Countable Nondeterminism}         %% [Short Title] is optional;
                                         %% when present, will be used in
                                         %% header instead of Full Title.
-\titlenote{with title note}             %% \titlenote is optional;
+%\titlenote{with title note}             %% \titlenote is optional;
                                         %% can be repeated if necessary;
                                         %% contents suppressed with 'anonymous'
-\subtitle{Subtitle}                     %% \subtitle is optional
-\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
+%\subtitle{Subtitle}                     %% \subtitle is optional
+%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                         %% can be repeated if necessary;
@@
 \author{W. J. Gowers}
-\authornote{with author1 note}          %% \authornote is optional;
+%\authornote{with author1 note}          %% \authornote is optional;
                                         %% can be repeated if necessary
@@
 \affiliation{
-  \position{PhD Student}
   \department{Department of Computer Science}              %% \department is recommended
@@
 
+\author{James Laird}
+%\authornote{with author1 note}          %% \authornote is optional;
+                                        %% can be repeated if necessary
+\orcid{0000-0002-4513-9618}             %% \orcid is optional
+\affiliation{
+  \department{Department of Computer Science}              %% \department is recommended
+  \institution{University of Bath}            %% \institution is required
+  \streetaddress{Claverton Down Road}
+  \city{Bath}
+  \postcode{BA2 7QY}
+  \country{United Kingdom}                    %% \country is recommended
+}
+\email{J.D.Laird@bath.ac.uk}
+
 %% Abstract
@@
 \begin{abstract}
-Text of abstract \ldots.
+  The concept of fairness for a concurrent program means that the program must be able to exhibit an unbounded amount of nondeterminism without diverging.
+Game semantics models of nondeterminism show that this is hard to implement; for example, Harmer and McCusker's model only admits infinite nondeterminism if there is also the possibility of divergence.
+  We solve a long standing problem by giving a fully abstract game semantics for a simple stateful language with a countably infinite nondeterminism primitive. 
+  We see that doing so requires us to keep track of infinitary information about strategies, as well as their finite behaviours.
+  The unbounded nondeterminism gives rise to further problems, which can be formalized as a lack of continuity in the language. 
+  In order to prove adequacy for our model (which usually requires continuity), we develop a new technique in which we simulate the nondeterminism using a deterministic stateful construction, and then use combinatorial techniques to transfer the result to the nondeterministic language.
+  Lastly, we prove full abstraction for the model; because of the lack of continuity, we cannot deduce this from definability of compact elements in the usual way, and we have to use a stronger universality result instead.
+  We discuss how our techniques may also be applied to Tsukada and Ong's model of PCF with finite nondeterminism, yielding an alternative proof of computational adequacy.
 \end{abstract}
@@
 %% comma separated list
-\keywords{keyword1, keyword2, keyword3}  %% \keywords are mandatory in final camera-ready submission
+\keywords{semantics, nondeterminism, games and logic}  %% \keywords are mandatory in final camera-ready submission
 

### 2018-01-29 cones/paper/cones.tex
Fixed error in the last section.

@@
 
-The second observation is that Lemma \ref{lem:soundness-lemma} can just as easily be applied to PCF contexts and its game semantics model $\G_{inn}$.  
-There really is nothing to this observation: since any PCF context may be interpreted in Idealized Algol, then Lemma \ref{lem:soundness-lemma} applies to it.
-So we have narrowed \ref{lem:soundness-lemma} down to a result about $\G_{inn}$.
+We want a version of Lemma \ref{lem:soundness-lemma} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
+Clearly, the lemma as currently stated does not hold in $\G_{inn}$, since the strategies $\sigma$ that we define are not innocent in general.
+
+Instead, we need to look at the combinatorial structure of the strategies.  
+We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.
+In addition, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not \emph{winning}; i.e., either $\sigma_M$ is not total or there exists some $\s\in T_{\sigma_M}$ with an infinite tail of moves in $\oc\bN$.
+We recover the following version of Lemma \ref{lem:soundness-lemma} which now applies to the interpretation of PCF in $\G_{inn}$:
+\begin{lemma}
+  Let $M=C[\wn]$ be a term of type $\com$.  
+  Write $\sigma_M\from\oc\bN\to\bC$ for the denotation of the term $\lambda n.C[n]$.  
+  \begin{itemize}
+    \item $M\converges\skipp$ if and only if there exists $\s\in \sigma_M$ such that $\s\vert_{\bC}=qa$.  
+    \item $M\mustconverge$ if and only if $\sigma_M$ is \emph{winning}.
+  \end{itemize}
+  \label{lem:pcf-soundness-lemma}
+\end{lemma}
 
@@
 
-It is then possible to deduce versions of Lemma \ref{lem:consistency} and Proposition \ref{prop:adequacy} from Lemma \ref{lem:soundness-lemma} as we did above, using the details of the inclusion functor from $\G_{inn}$ and the definition of composition in $\G_{TO}$.
+It is then possible to deduce versions of Lemma \ref{lem:consistency} and Proposition \ref{prop:adequacy} from Lemma \ref{lem:pcf-soundness-lemma} as we did above for our model of Idealized Algol, using the details of the inclusion functor from $\G_{inn}$ and the definition of composition in $\G_{TO}$.
 We can then deduce soundness in the usual way.
 
-\begin{theorem}[Soundness for nondeterministic PCF]
-  Let $M,N\from T$ be two terms of PCF with countable nondeterminism.
-  If $\deno M\oes \deno N$, then $M\emam N$, where the denotation $\deno -$ is taken in the category $\G_{TO}$.  
-\end{theorem}
-
-An alternative line of attack is to first build a copy of our model of Idealized Algol with countable nondeterminism inside $\G_{TO}$, using our argument to prove soundness and adequacy, and then restrict down to nondeterministic PCF.
+It is worth noting an alternative line of attack, which is to first build a copy of our model of Idealized Algol with countable nondeterminism inside $\G_{TO}$, using our argument to prove soundness and adequacy, and then restrict down to nondeterministic PCF.
+The approach above is more general, however, since it does not make use of the fact that Idealized Algol may be interpreted in $\G_{TO}$.
 

### 2018-01-29 cones/paper/cones.tex
Fixed incorrect name.

@@
   \]
-There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\coh\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.
+There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\mathsf{coh}\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.
 This construction is essentially the co-Kleisli category on a comonad given by $\oc$, but certain technical issues prevent us from presenting it in this way.

### 2018-01-29 cones/paper/cones.tex
Changed some things.

@@
 
-The language that we will be modelling is the language Idealized Algol \cite{SamsonGuyIAPassive}, extended with an additional constant $\wn$ representing countable nondeterminism.  
+The language that we will be modelling is Idealized Algol \cite{SamsonGuyIAPassive} extended with an additional constant $\wn$ representing countable nondeterminism.  
 This is similar to the approach adopted in \cite{mcCHFiniteND}, which extends Idealized Algol with \emph{finite} nondeterminism.  
@@
 We define predicates $M \converges V$ ($M$ may converge to $V$) and $M\mustconverge$ ($M$ must converge) inductively to give a big-step operational semantics for our language.  
-We give a selection of the appropriate rules in Figure \ref{fig:ia-os}; this presentation is almost identical to that given in \cite{mcCHFiniteND}, with a slightly different rule for the countable nondeterminism.
+We give a selection of the appropriate rules in Figure \ref{fig:ia-os}; this presentation is almost identical to that given in \cite{mcCHFiniteND}, with a rule for countable nondeterminism replacing their rule for finite nondeterminism.
 In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.

### 2018-01-29 cones/paper/cones.tex
Made a small technical point.

@@
 
-Given a term $M$ of ground type $\com$ or $\nat$, a proof $\pi$ that $\ia s M\converges V$ gives rise to a (possibly infinite) sequence of natural numbers corresponding to a bottom-to-top, left-to-right reading of the natural numbers $n$ used in the first rule for $\wn$.
+Given a term $M$ of ground type $\com$ or $\nat$, a proof $\pi$ that $\ia s M\converges V$ or that $\ia S M \not\mustconverge$ gives rise to a (possibly infinite) sequence of natural numbers corresponding to a bottom-to-top, left-to-right reading of the natural numbers $n$ used in the rules for $\wn$.
 We call such a sequence an \emph{evaluation} of the configuration $\ia s M$.  

### 2018-01-29 cones/paper/cones.tex
Did more things.

@@
 
-If $\ia\emptyset M$ is a configuration with empty store, we call $M$ a \emph{closed term}.  
+If $\ia\emptyset M$ is a configuration with empty store, we call $\ia \emptyset M$ a \emph{closed term}.  
+In this case, we shall write $M$ rather than $\ia\emptyset M$.
 Let $T$ be an Idealized Algol type, and let $M,N\from T$ be closed terms.
@@
   \]
-However, when we compose this strategy with any total strategy for $\bN$ on the left, we expect the resulting strategy to contain divergences, since the term $M \n$ diverges for any $\n$.
+However, when we compose this strategy with any total strategy for $\bN$ on the left, we expect the resulting strategy to contain divergences, since $M \n$ diverges for any $\n$.
 
@@
 Given an arena $A$, we define an \emph{infinite justified string} in the obvious way.  
-We define $\bar{P_A}$ to be $P_A$ together with the set of all those infinite justified sequences that have all finite prefixes in $P_A$.
+We define $\overline{P_A}$ to be $P_A$ together with the set of all those infinite justified sequences that have all finite prefixes in $P_A$.
 
@@
 \begin{itemize}
-  \item $T_\sigma$ is a non-empty prefix-closed subset of $\bar{P_A}$ such that if $s\in T_\sigma$ is a $P$-position and $sa\in P_A$ then $sa\in T_\sigma$.
-  \item $D_\sigma\subset \bar{P_A}$ is a postfix-closed set of plays in $\bar{P_A}$ that either end with an $O$-move or are infinite.  
+  \item $T_\sigma$ is a non-empty prefix-closed subset of $\overline{P_A}$ such that if $s\in T_\sigma$ is a $P$-position and $sa\in P_A$ then $sa\in T_\sigma$.
+  \item $D_\sigma\subset \overline{P_A}$ is a postfix-closed set of plays in $\overline{P_A}$ that either end with an $O$-move or are infinite.  
     We require $D_\sigma$ to obey the following rules:
@@
   Let $\sigma$ be a strategy for a game $A$.  
-  We say that $\sigma$ is \emph{complete} if $T_\sigma=\bar{T_\sigma}$; i.e., $T_\sigma$ contains an infinite position $s$ if it contains every finite prefix of $s$.  
+  We say that $\sigma$ is \emph{complete} if $T_\sigma=\overline{T_\sigma}$; i.e., $T_\sigma$ contains an infinite position $s$ if it contains every finite prefix of $s$.  
 \end{definition}
@@
   Let $\sigma\from I \to A$ be a strategy for a game $A$ in $\G_{ND}$.
-  Then we may write $\sigma$ as $\top_{\bN};\Det(\sigma)$, where $\Det(\sigma)\from \oc\bN\to A$ is a deterministic strategy and $\top_{\bN}$ is the strategy for $\oc\bN$ given by
+  Then we may write $\sigma$ as $\top_{\bN};\Det(\sigma)$, where $\Det(\sigma)\from \oc\bN\to A$ is a deterministic strategy and $\top_{\bN}$ is the strategy for $\oc\bN$ that is given by
   \begin{itemize}

### 2018-01-30 cones/paper/cones.tex
Changed some things.

--- 2018-01-29 cones/paper/cones.tex
@@
 
-Text of paper \ldots
+Picture two concurrent processes $P$ and $Q$ with shared access to a variable $v$ that holds natural numbers and is initialized to $0$.  
+The execution of $P$ consists in an infinite loop that increments the value of $v$ at each iteration.  
+Meanwhile, $Q$ performs some computation $A$, and then prints out the current value of $v$ and terminates the whole program.
+Since we cannot predict in advance how may cycles of the loop in $P$ will have elapsed by the time the computation $A$ has completed, the value that ends up printed to the screen may be arbitrarily large.
+Furthermore, under the basic assumption that the task scheduler is \emph{fair}; i.e., any pending task must eventually be executed, we can observe that our program must always terminate by printing out some value to the screen.
+
+We have therefore built an \emph{unbounded nondeterminism} machine, that can print out arbitrarily large natural numbers but which never diverges, as distinct from finitary choice nondeterminism.
+\footnote{Using recursion, we can build a program out of finite nondeterminism that can produce arbitrarily large natural numbers; however, this program also admits the possibility of divergence.}  
+What we have just shown is that if we want to solve the problem of building a fair task scheduler, then we must in particular be able to solve the problem of building an unbounded nondeterminism machine.
+
+This is an important observation to make about concurrent programming, because the task of implementing unbounded nondeterminism is difficult -- indeed, considerably more so than that of implementing bounded nondeterminism.
+Dijkstra argues in \cite[Ch.
+9]{DijkstraBook} that it is impossible to implement unbounded nondeterminism, showing that the natural constructs from which we construct imperative programs satisfy a \emph{continuity} property that unbounded nondeterminism lacks.
+In fact, for semanticists, this lack of continuity is a problem in itself, since the standard proofs of computational adequacy and full abstraction typically make use, implicitly or otherwise, of the fact that composition within the model is continuous with respect to some ordering.
+
+We shall explore some of the problems relating to unbounded nondeterminism, and how they may be solved, using game semantics to give a fully abstract model of a simple stateful language -- Idealized Algol -- enhanced with a countable nondeterminism primitive.
+We begin with a pair of examples that will illustrate the lack of continuity, from a syntactic point of view.  
+Let $\nat$ be our number type and consider a sequence of functions ${<}n\from\nat\to\nat$ where ${<}m\;k$ evaluates to $0$ if $k<n$ and diverges otherwise.
+In that case, the least upper bound of the ${<}n$ is the function that combines all their convergent behaviours; i.e., the function $\lambda k.k;\0$ that evaluates its input and then returns $0$.
+If $\wn\from\nat$ is an unbounded nondeterminism machine, then function application to $\wn$ is not continuous; indeed, ${<}m\;\wn$ always has the possibility of divergence -- since $\wn$ may evaluate to $m+1$, say.
+But $(\lambda k.k;\0);\wn$ always converges to $0$.
+
+Lack of continuity is a problem because fixed-point combinators are typically built using least upper bounds, and proving adequacy of the model requires that these least upper bounds be preserved.  
+In a non-continuous situation, we will need to come up with new techniques in order to prove adequacy without using continuity.
+
+A closely connected problem with unbounded nondeterminism is that it leads to terms that may be distinguished only by their \emph{infinitary} behaviour.  
+A program that flashes a light and unboundedly nondeterministic number of times cannot reliably be distinguished in finite time from a program that flashes that light forever: however long we watch the light flash, there is always a chance that it will stop at some point in the future.
+From a game semantics point of view, this corresponds to the observation that it is not sufficient to consider sets of finite plays in order to define strategies: we must consider infinite sequences of moves as well.
+
+\subsection{Related Work}
+
+Our game semantics model bears closest resemblance to that of Harmer and McCusker \cite{mcCHFiniteND}, which is a fully abstract model of Idealized Algol with \emph{finite} nondeterminism.  
+Indeed, our work can be viewed as an extension of the Harmer-McCusker model with the extra information on infinite plays that we need to model countable nondeterminism.
+
+The idea of adding infinite traces into strategies in order to model unbounded nondeterminism goes back to Roscoe's work on CSP \cite{RoscoeCspInfinite}, and is very similar to work by Levy \cite{LevyGsInfinite} on game semantics for a higher order language.
+In particular, we will need something similar to Levy's \emph{liveliness} condition on strategies, which is a way of saying that a strategy is a union of deterministic strategies -- something that is not automatic when we start tracking infinite plays.
+
+An alternative approach to the game semantics of nondeterminism can be found in Tsukada and Ong's sheaf model of nondeterministic PCF \cite{TsukadaSheaves} and in the more general work on concurrency by Winskel et al.
+(e.g., see \cite{StrategiesAsProfunctors} and \cite{ConcurrentHylandOngGames}), in which there is a very natural interpretation of nondeterminism.
+Although we are able to give a model of Idealized Algol with countable nondeterminism in the more traditional Harmer-McCusker style, it seems necessary to introduce this extra machinery in order to model stateless languages such as PCF (and certainly to model concurrency).
+In the last section of this paper, we will show how our methods can be applied under very general circumstances, and in particular to these models.
+
+Related work by Laird \cite{LairdOrdinalGames,FunctionalProgramsAsCoroutines} discusses a semantics for PCF with unbounded nondeterminism based on sequential algorithms and explores the role played by continuity; however, this semantics is not fully abstract.
+Laird's work is interesting because it shows that we can obtain a traditional adequacy proof for a semantics with one-sided continuity: composition is continuous with respect to functions, but not with respect to arguments.
+We cannot use these techniques here, though, because our composition is not continuous on either side.
+
+\subsection{Contributions}
+
+The main concepts of game semantics and the steps we take to establish full abstraction are well-established, with a few exceptions.  
+The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, has not been carried out in a traditional Hyland-Ong game semantics setting before.
+
+There are two points in the traditional Full Abstraction proof that depend on composition being continuous, and we have had to come up with ways of getting round them.  
+The easier of the two is that continuity is necessary to derive Full Abstraction from definability of compact strategies; in order to get around this, we have had to appeal to the stronger \emph{universality} result of \cite{hoPcf}, that says that every \emph{recursive} strategy is definable.
+
+For the proof of adequacy, we have had to come up with a new technique.  
+This technique can be thought of as a kind of synthesis between the two usual methods of proving adequacy -- one involving logical relations and the other using more hands-on operational techniques.  
+We do this by separating out the deterministic, continuous part of the strategy from the nondeterministic, discontinuous part.  
+Using the stateful language, we can simulate individual evaluation paths of a nondeterministic program using deterministic programs, which allows us to appeal to the adequacy result for deterministic Idealized Algol.
+We then rely on more combinatorial techniques to factor the nondeterminism back in.
+
+This new technique is actually very generally applicable.  
+In the last section of the paper, we show that it may be used to prove adequacy for models of nondeterministic PCF under very mild assumptions.  
+The Tsukada-Ong model, for example, satisfies these assumptions and so we obtain an adequacy result for its semantics.
 
@@
 
-The language that we will be modelling is Idealized Algol \cite{SamsonGuyIAPassive} extended with an additional constant $\wn$ representing countable nondeterminism.  
+We describe a simple type theory and operational semantics for Idealized Algol with countable nondeterminism.
 This is similar to the approach adopted in \cite{mcCHFiniteND}, which extends Idealized Algol with \emph{finite} nondeterminism.  
-The types of the language are defined inductively as follows:
+The types of our language are defined inductively as follows:
 \[
@@
 
-The value forms in the language are given by
-\[
-  V \Coloneqq \skipp \mid \n \mid \lambda x.M \mid v \mid \mkvar
-  \]
-We define predicates $M \converges V$ ($M$ may converge to $V$) and $M\mustconverge$ ($M$ must converge) inductively to give a big-step operational semantics for our language.  
-We give a selection of the appropriate rules in Figure \ref{fig:ia-os}; this presentation is almost identical to that given in \cite{mcCHFiniteND}, with a rule for countable nondeterminism replacing their rule for finite nondeterminism.
+We define a small-step operational semantics for the language; this presentation is equivalent to the big-step semantics given in \cite{mcCHFiniteND}, except with a different rule for the countable rather than finite nondeterminism.
+We give a selection of the appropriate rules in Figure \ref{fig:ia-os}.
 In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.
@@
   \begin{mathpar}
-    \inferrule*{\ia s N \converges \ia {s'} \n \\ \ia {s'} M \converges \ia {s''} v}
-    {\ia s {M \coloneqq N} \converges \ia {\stup {s''} v n} \skipp}
+    \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}
     \and
-    \inferrule*[right=${s'(v) = n}$]{\ia s M \converges \ia {s'} v}
-    {\ia s {\deref M} \converges \ia {s'} \n}
+    \inferrule*[left={$s(v)=n$}]{ }{\ia s {\deref v} \opto \ia s n}
     \and
-    \inferrule*{\ia s M \converges \ia {s'} \skipp \\ \ia {s'} N \converges \ia {s''} V}
-    {\ia s {M;N} \converges \ia {s''} V}
+    \inferrule*{ }{\ia s {\skipp;M} \opto \ia s M}
     \and
-    \inferrule*{\ia {\stup s v 0} M \converges \ia {\stup{s'} v n} V}
-    {\ia s {\new_T\;\lambda v.M} \converges \ia {s'} V}
+    \inferrule*{ }{\ia s {\new_T \lambda v.M}\opto \ia {\stup s v 0} M}
     \and
-    \inferrule*[right=$n\in\bN$]{\ia s {M \n} \converges \ia {s'} V}
-    {\ia s {M \wn} \converges \ia {s'} V}
+    \inferrule*[right=$n\in\bN$]{ }{\wn \opto \n}
     \and
-    \inferrule*{\forall n\in\bN.\ia s {M \n}\mustconverge}
-    {\ia s {M \wn} \mustconverge}
+    \inferrule*{M \opto M'}{M;N\opto M';N}
     \and
-    \inferrule*{\ia s M \mustconverge \\ \forall \ia {s'} {\lambda x.M'}\esuchthat \ia s M \converges \ia {s'} {\lambda x.M'} \Rightarrow \ia {s'}{M'[N/x]}\mustconverge}
-    {\ia s {M\;N}\mustconverge}
+    \inferrule*{M \opto M'}{M N\opto M'N}
   \end{mathpar}
-  \caption{Operational semantics of Idealized Algol with Countable Nondeterminism}
+  \caption{Selected rules in the small-step operational semantics of Idealized Algol with countable nondeterminism}
   \label{fig:ia-os}
@@
 
-Given a term $M$ of ground type $\com$ or $\nat$, a proof $\pi$ that $\ia s M\converges V$ gives rise to a (possibly infinite) sequence of natural numbers corresponding to a bottom-to-top, left-to-right reading of the natural numbers $n$ used in the first rule for $\wn$.
-We call such a sequence an \emph{evaluation} of the configuration $\ia s M$.  
-It is perhaps easier to view this from the perspective of a small-step reduction: the sequence of numbers is formed by listing the different values that the nondeterminism constant $\wn$ decays to over the course of the evaluation $\pi$.
+If $\ia\emptyset M$ is a configuration with empty store, we call $M$ a \emph{closed term}.  
+Given a closed term $M$ of ground type $\com$ or $\nat$, we write that $M\converges x$ (where $x=\skipp$ in the $\com$ case and is a natural number in the $\nat$ case) if there is a finite sequence $M \opto M_1 \opto \cdots \opto M_n = x$.
+If there is no infinite sequence $M \opto M_1 \opto M_2 \opto \cdots$, then we say that $M$ \emph{must converge}, and write $M\mustconverge$.
+In general, we refer to a (finite or infinite) sequence $M \opto M_1 \opto \cdots$ that either terminates at an observable value or continues forever as an \emph{evaluation} $\pi$ of $M$.  
+Since the only case where we have any choice in which rule to use is the application of the rule for $\wn$, $\pi$ may be completely specified by a finite or infinite sequence of natural numbers.
 
-If $\ia\emptyset M$ is a configuration with empty store, we call $M$ a \emph{closed term}.  
 Let $T$ be an Idealized Algol type, and let $M,N\from T$ be closed terms.
@@
 We write $M\emam N$ if $M\lmam N$ and $N\lmam M$.
-
-One aspect of the language that makes it particularly difficult to model is that function application is not continuous, either with respect to functions or with respect to arguments.
-
-For example, it is easy to write a sequence of functions ${<}\!n \from \nat \to \nat$ that return $0$ if their argument is less than $n$ and diverge otherwise:
-
-\begin{align*}
-  &{<}0 = \lambda m.\Omega \\
-  &{<}1 = \lambda m.\IfO m\;\0\;\Omega \\
-  &{<}2 = \lambda m.\IfO m\;\0\;(\IfO (\pred m)\;\0\;\Omega)\\
-  \cdots
-\end{align*}
-It is easy enough to see (for example, by the denotational semantics) that the least upper bound of these functions is the function $\lambda x.\0$.  
-However, it is clear that ${<}n\;\wn\not\mustconverge$ for each $n$, while $\lambda x.\0\;\wn$ must converge to $\0$.  
-Thus, $\lambda x.\0\;\wn$ is not the least upper bound of the ${<}n\;\wn$.
-
-This is a bit of a problem, since continuity often plays an important role in full abstraction proofs -- firstly, for proving Computational Adequacy of the recursion combinator, and, secondly, for deducing full abstraction from definability of compact elements.
-Semantically, we shall deal with the first problem by adopting a novel approach to Computational Adequacy, and with the second problem by appealing to the stronger \emph{universality} result: namely, that every \emph{recursive} strategy is definable.
 
@@
 
-\subsubsection{Multiplicatives}
+\subsubsection{Connectives}
 
 Let $A,B$ be games.  
-We define games $A\tensor B$ and $A\implies B$ as follows.
-\begin{IEEEeqnarray*}{RCL}
-  M_{A\tensor B} & \quad=\quad & M_A + M_B\,. \\
-  \lambda_{A\tensor B} & = & [\lambda_A,\lambda_B]\,.\\
-  *\ts_{A\tensor B} n & \Leftrightarrow & * \ts_A n \text{ or } * \ts_B n\,. \\
-  m \ts_{A\tensor B} n & \Leftrightarrow & m \ts_A n\text{ or } m \ts_B n\,.\\
-  P_{A\tensor B} & = & \{s\in L_{A\tensor B}\suchthat s\vert_A\in P_A\text{ and }s\vert_B\in P_B\}\,.
-\end{IEEEeqnarray*}
+Then we may define games $A\times B$, $A\tensor B$, $A\implies B$ and $\oc A$ as in \cite{SamsonGuyIAPassive}.  
+As an example, we give the definition of $A\implies B$:
 \begin{IEEEeqnarray*}{RCL}
@@
 where the term on the right must converge (to $\0$), while the term on the left has a possible divergence.  
-The traditional way of representing divergences in game semantics is by a partiality in the strategy; i.e., an $O$-move to which $P$ has no reply, but this partiality will be obscured by the alternative behaviour in the denotation of the strategy on the left.
+The traditional way of representing divergences in game semantics is by a partiality in the strategy; i.e., an $O$-move to which $P$ has no reply, but this doesn't work here: $\IfO\wn\;\Omega\;\0$ and $\0$ both denote the strategy with maximal play $q\;0$; the partiality in the former is `hidden' by the move $0$.
 
@@
 \[
-  M = \Y_{\nat\to\nat}(\lambda f.\lambda n.n;(f n))\,,
+  M = \Y_{\nat\to\nat}(\lambda f.\lambda n.n;(f n))
   \]
-where $n;P$ is a shorthand for $\IfO n\;P\;P$, is given by a total strategy, without divergences: namely the strategy $\mu$ with plays of the form
+is given by a total strategy, without divergences: namely the strategy $\mu$ with plays of the form
 \[
-  \begin{array}{cc}
-    \mathbf{\bN} & \mathbf{\bN} \\
-    & q \\
-    q & \\
-    n_1 & \\
-    q & \\
-    n_2 & \\
-    \vdots &
+  \begin{array}{ccccccc}
+    \mathbf{\bN_1} &   & q & n_1 & q & n_2 & \cdots \\
+    \mathbf{\bN_2} & q &   &     &   &     &
   \end{array}\,.
@@
 However, when we compose this strategy with any total strategy for $\bN$ on the left, we expect the resulting strategy to contain divergences, since the term $M \n$ diverges for any $\n$.
+Semantically, this corresponds to the fact that we have a legal interaction $q\;q\;n\;q\;n\;\cdots$ with an infinite tail in $\bN_1$; when we perform `hiding' by restricting the interaction to $\bN$, we have no reply to the initial move $q$.
 
@@
 This term first chooses a natural number $m$, and then reads from its input $n$ for a total of $m$ times before eventually returning $\0$.  
-Thus, its denotation is the strategy $\nu$ with maximal plays of the form:
+Thus, its denotation is the strategy $\nu$ with maximal plays of arbitrary length of the form:
 \[
-  \begin{array}{cc}
-    \mathbf{\bN} & \mathbf{\bN} \\
-    & q \\
-    q & \\
-    n_1 & \\
-    \vdots & \\
-    q & \\
-    n_m & \\
-    & 0
+  \begin{array}{cccccccc}
+    \bN_1 &   & q & n_1 & \cdots & q & n_m & \\
+    \bN_2 & q &   &     &        &   &     & 0
   \end{array}\,.
@@
   \]
-has the same denotation as $N$, even though it has all the divergent evaluations of $M$, while $N\n\mustconverge$ for all $\n$.
+has the same denotation as $N$, even though for any $n$, $M\n\not{\mustconverge}$, while $N\n\mustconverge$.
 Moreover, if we try to compose $\deno{N}$ with the strategy on $\bN$ that always returns $1$, then we end up with an infinite increasing sequence of positions, which triggers the introduction of a divergence into the composite -- even though no divergence occurs in the evaluation of $N$.
@@
 However, it is worth saying a few words about it, since the model obtained by naively extending the Harmer-McCusker model to unbounded nondeterminism does not have an associative composition.  
-The point is that this is not really a problem with associativity, but rather that this naive model gives the wrong result for the composition of strategies.  
+The point is that this is not really a problem with associativity, but rather that this naive model gives the wrong result for the composition of strategies with infinite nondeterminism.
 For example, if $\nu$ is the strategy we defined above, and $\0$ is the `constant $0$' strategy on $\bN$, then $\0;\nu$ has a divergence in the naive model, because the strategies $\0$ and $\nu$ appear to be engaged in infinite chattering.
@@
 
-\subsection{Products and Exponentials}
+\subsection{A Cartesian closed category}
 
-Let $A, B$ be games
-We define a new game $A \times B$.  
-The arena for $A\times B$ is the same as the arena for $A\tensor B$, but now $P_{A\times B}$ is the disjoint union of $P_A$ and $P_B$ inside that arena:
-\begin{IEEEeqnarray*}{RCL}
-  P_{A \times B} & = & \{s\in L_{A\tensor B}\suchthat s\vert_A \in P_A\text{ and }s\vert_B=\emptyplay\} \\
-  & \cup & \{s\in L_{A\tensor B}\suchthat s\vert_A=\emptyplay\text{ and }s\vert_B\in P_B\}\,.
-\end{IEEEeqnarray*}
-Then $A\times B$ is the category-theoretic product of $A$ and $B$ in $\G_{ND}$.
+We follow the construction given in \cite{SamsonGuyIAPassive}, using the connectives $\oc$ and $\times$ to build a Cartesian closed category $\G_{ND}^\oc$ from $\G_{ND}$ whose objects are the well-opened games in $\G_{ND}$ and where a morphism from $A$ to $B$ in $\G_{ND}^\oc$ is a morphism from $\oc A$ to $B$ in $\G_{ND}$.
 
-We define a game $\oc A$ as follows.  
-The arena for $\oc A$ is the same as the arena for $A$, but the set of plays is given by
-\[
-  P_{\oc A} = \{s\in L_A\suchthat s\vert_m\in P_A\text{ for each initial move $m$}\}\,.
-  \]
-There are strategies $\mult_A\from \oc A \to \oc A \tensor \oc A$, $\mathsf{coh}\from \oc (A\times B) \toisom \oc A \tensor \oc B$ and $\der_A\from \oc A \to A$ that can be used to create a Cartesian closed category $\G^\oc_{ND}$, in which morphisms from $A$ to $B$ are strategies for the game $\oc A\implies B$.
-This construction is essentially the co-Kleisli category on a comonad given by $\oc$, but certain technical issues prevent us from presenting it in this way.
-See \cite{SamsonGuyIAPassive} for full details.
+This is very similar to the construction of a co-Kleisli category for a linear exponential comonad, but certain technical issues relating to well-openedness prevent us from displaying it in this way.
 
@@
 Clearly our base games $\bN$ and $\bC$ can be enumerated, as can the tensor product, linear implication, exponential and product of games.  
+We can then define a \emph{recursive} strategy to be one that is recursively presentable with respect to that enumeration of moves.
 
@@
   Let $\G_{D,vis,rec}$ be the category of games and \emph{recursive} visible strategies.  
-  Then $\G_{D,vis,rec}$ is a fully abstract model of Idealized Algol in which every morphism is definable.
+  Then $\G_{D,vis,rec}^\oc$ is a fully abstract model of Idealized Algol in which every morphism is definable.
 \end{proposition}
@@
 
-\subsection{Adequacy and soundness}
+\subsection{Computational Adequacy}
 
-We prove a \emph{consistency} result for our model.  
-Let $M$ be a closed term of type $\com$.
+The \emph{computational adequacy} result for our model can be stated as follows.
 
-\begin{lemma}
-  If $M\converges\skipp$ then $qa\in T_{\deno M}$.  
-  If $M\mustconverge$ then $D_{\deno M}=\emptyset$.
-  \label{lem:consistency}
-\end{lemma}
-
-We can also prove the converse, \emph{computational adequacy}.
-
-\begin{proposition}
-  If $qa\in T_{\deno M}$ then $M\converges\skipp$.
-  If $D_{\deno M}=\emptyset$ then $M\mustconverge$.
+\begin{proposition}[Computational Adequacy]
+  $M\converges\skipp$ if and only if $qa\in T_{\deno M}$.  
+  $M\mustconverge$ if and only if $D_{\deno M}=\emptyset$.
   \label{prop:adequacy}
@@
 \begin{lemma}
-  Let $M=C[\wn]$ be a term of type $\com$.  
+  Let $M=C[\wn]$ be a term of type $\com$, where $C[-]$ is a context of Idealized Algol.
   Write $\sigma_M$ for the denotation of the term $\lambda n.C[n]$.  
   \begin{itemize}
-    \item $M\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$.
-    \item $M\not{\mustconverge}$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$.
+    \item If $M\converges\skipp$ then there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$.
+    \item If $M\not{\mustconverge}$ then there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$.
   \end{itemize}
@@
 \begin{proof}
-  We prove the forward directions first.
-
   Let $n_1,\dots,n_k,d$ be a finite sequence of natural numbers.  
@@
     \]
-  Here, $\case_{k+1}\;a\;n_0\;\cdots\;n_k\;d$ evaluates to $n_i$ if $a$ evaluates to $i$, and evaluates to $d$ if $a$ evaluates to $j> k$.
-  Clearly, it can be built out of $\IfO$s.
+  Here, $\case_{k+1}\;a\;n_0\;\cdots\;n_k\;d$ is a new shorthand that evaluates to $n_i$ if $a$ evaluates to $i$, and evaluates to $d$ if $a$ evaluates to $j> k$.
   This term adds an extra variable $v$ to the program; each time $f$ is called, it increments the value of $v$ and maps its value on to one of the $n_i$.
 
-  Now let $\pi$ be a finite evaluation of $\ia s {C[\wn]} \converges\skipp$.  
+  Now let $\pi$ be a finite evaluation $\ia s {C[\wn]}$ that converges to $\skipp$.  
   Encode $\pi$ as a sequence $n_1,\dots,n_k$.  
@@
 
-  If instead $\pi$ is a finite evaluation of $\ia s {C[\wn]}\not\mustconverge$; i.e., a divergent evaluation (that nevertheless only involves finitely many calls to the nondeterministic oracle), then the term $N_{n_1,\dots,n_k,d} (\lambda n.C[n])$ will diverge according to the same execution path.
+  If instead $\pi$ is a finite evaluation of $\ia s {C[\wn]}$ that diverges (but nevertheless only involves finitely many calls to the nondeterministic oracle), then the term $N_{n_1,\dots,n_k,d} (\lambda n.C[n])$ will diverge according to the same execution path.
 
@@
   and so it is total.
+\end{proof}
 
-  We now prove the reverse implications.  
-  Let $\sigma\from\bN$ be a total deterministic strategy for $\oc\bN$.
-  Then $\sigma$ must have a maximal infinite play $s_\sigma$ of the form
+From this result, we can prove the converse, which we will also need.
+
+\begin{lemma}
+  Let $M=C[\wn]$ be as before.
+  Let $\sigma\from\oc\bN$ be a total deterministic strategy.
+  \begin{itemize}
+    \item If $qa\in T_{\sigma;\sigma_M}$ then $M\converges\skipp$.
+    \item If $D_{\sigma;\sigma_M}\ne\emptyset$ then $M\not\mustconverge$.
+  \end{itemize}
+  \label{lem:soundness-converse}
+\end{lemma}
+
+\begin{proof}
+  Since $\sigma$ is total and deterministic, it must have a maximal infinite play $s_\sigma$ of the form
   \[
@@
   Now suppose that there exists $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$.  
-  By the above discussion, we may assume that $\sigma=\sigma_\pi$ for some evaluation $\pi$ of $M$.  
+  By the proof of Lemma \ref{lem:soundness-lemma}, we may assume that $\sigma=\sigma_\pi$ for some evaluation $\pi$ of $M$.  
   Therefore, $qa\in T_{\sigma_\pi;\sigma_M}$, which means that $M\converges\skipp$ along the evaluation $\pi$.  
@@
 
-We can now prove our soundness and adequacy results.
-
-\begin{proof}[Proof of Lemma \ref{lem:consistency}]
-  Suppose that that $M$ is a closed term of type $\com$ and that $M\converges\skipp$.  
-  Then $qa\in T_{\sigma;\sigma_M}$ for some strategy $\sigma$.  
-  It follows that $qa\in T_{\top_\bN;\sigma_M}$.
-
-  Now suppose that $D_{\deno M}\neq\emptyset$.  
-  Then there is some interaction $\s\in\Int_\infty(I,\oc\bN,\bC)$ such that $\s\vert_\bC\in D_{\sigma_M}$.
-  Let $\sigma$ be a deterministic total strategy containing $\s\vert_{\oc\bN}$.  
-  Then we have $D_{\sigma;\sigma_M}\ne\emptyset$, so $M$ diverges by Lemma \ref{lem:soundness-lemma}.
-\end{proof}
+We can now prove our computational adequacy result.
 
 \begin{proof}[Proof of Proposition \ref{prop:adequacy}]
-  Suppose that $M$ is a closed term of type $\com$ and that $qa\in T_{\deno M}$.  
-  Then there is some interaction $\s\in\Int_\infty(I,\oc\bN,\bC)$ such that $qa\in\s\vert_\bC$.  
-  Let $\sigma$ be a deterministic total strategy for $\oc\bN$ containing the play $\s\vert_{\oc\bN}$.  
-  Then we have $qa\in T_{\sigma;\sigma_M}$, so $M\converges\skipp$ by Lemma \ref{lem:soundness-lemma}.
+  We prove this for must convergence; the corresponding proof for may convergence is very similar.
 
-  Now suppose that $M\not\mustconverge$.  
-  Then we have $D_{\sigma;\sigma_M}\ne\emptyset$ for some strategy $\sigma\from\oc\bN$.
-  Moreover, since $\sigma_\pi$ is total, it follows that $D_{\top_{\bN};\sigma_M}\ne\emptyset$.
+  Let $M=C[\wn]$ be a closed term, where $C$ is a deterministic context.  
+  Then, by Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse}, we see that $M\not\mustconverge$ if and only if there exists some total deterministic $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$.
+  By examining the definition of composition, we see that this is the case if and only if $D_{\deno M}=D_{\top_N;\sigma_M}\ne\emptyset$.
 \end{proof}
@@
 
+Of course, this full abstraction holds just as well for $\G_{ND,vis}^\oc$, where we relax the recursivity condition.
+
 \section{Nondeterministic PCF}
 
-We conclude by saying a few remarks about the situation when our base deterministic language is PCF rather than Idealized Algol.  
-Tsukada and Ong \cite{TsukadaSheaves} showed that traditional game semantics models are unsuitable for modelling this language: while the definition of \emph{visibility} of strategies can be extended to nondeterministic strategies without difficulty, the corresponding definition for PCF -- that of an \emph{innocent} strategy -- does not.
-Tsukada and Ong instead use a new type of game semantics in which strategies are given not by sets of plays but by justified \emph{trees} whose vertices are moves.  
+We conclude by making a few remarks about the situation when our base deterministic language is PCF rather than Idealized Algol.
+
+Hyland and Ong \cite{hoPcf} gave a model of PCF using games and \emph{innocent strategies}.
+If $sab\in P_A$, where $b$ is a $P$-move such that $sab$ is visible at $b$, and if $ta\in P_A$ is such that $\pv{sa}=\pv{ta}$, then it is possible to show that there is a unique way to extend $ta$ by $b$ such that $\pv{sab}=\pv{tab}$.
+We will abuse notation and refer to this play as $tab$, omitting the justification pointer from $b$.
+
+If $\sigma$ is a strategy for $A$ that is deterministic and $P$-visible, we say that $\sigma$ is \emph{innocent} if and only if whenever $sab,ta\in\sigma$ are as above, we have $tab\in\sigma$.
+
+Tsukada and Ong \cite{TsukadaSheaves} showed that traditional game semantics models are unsuitable for modelling \emph{nondeterministic} PCF: while the definition of \emph{visibility} of strategies can be extended to nondeterministic strategies without difficulty, innocence cannot.
+
+Instead, they use a novel type of game semantics in which strategies are given not by sets of plays but by justified \emph{trees} whose vertices are moves.  
 The difference is subtle but important: from the point of view of countable nondeterminism it allows us to distinguish between terms that take an arbitrarily large finite number of steps to converge and terms that diverge.
@@
 
-We want a version of Lemma \ref{lem:soundness-lemma} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
-Clearly, the lemma as currently stated does not hold in $\G_{inn}$, since the strategies $\sigma$ that we define are not innocent in general.
+The second observation is that Lemma \ref{lem:soundness-lemma} can just as easily be applied to PCF contexts and its game semantics model $\G_{inn}$.  
+There really is nothing to this observation: since any PCF context may be interpreted in Idealized Algol, then Lemma \ref{lem:soundness-lemma} applies to it.
+So we have narrowed \ref{lem:soundness-lemma} down to a result about $\G_{inn}$.  
+The only other change we need to make is to switch our base observable type from $\com$ to $\nat$, since PCF has no command type.  
+The version with $\nat$ instead of $\com$ can be proved in exactly the same way.
 
-Instead, we need to look at the combinatorial structure of the strategies.  
-We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.
-In addition, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not \emph{winning}; i.e., either $\sigma_M$ is not total or there exists some $\s\in T_{\sigma_M}$ with an infinite tail of moves in $\oc\bN$.
-We recover the following version of Lemma \ref{lem:soundness-lemma} which now applies to the interpretation of PCF in $\G_{inn}$:
 \begin{lemma}
-  Let $M=C[\wn]$ be a term of type $\com$.  
-  Write $\sigma_M\from\oc\bN\to\bC$ for the denotation of the term $\lambda n.C[n]$.  
-  \begin{itemize}
-    \item $M\converges\skipp$ if and only if there exists $\s\in \sigma_M$ such that $\s\vert_{\bC}=qa$.  
-    \item $M\mustconverge$ if and only if $\sigma_M$ is \emph{winning}.
-  \end{itemize}
-  \label{lem:pcf-soundness-lemma}
+  Let $C[-]\from\nat$ be a PCF context with a hole of type $\nat$.
+  Let $\sigma\from\bN\to\bN$ be the denotation of $\lambda n.C[n]$ in $\G_{inn}^\oc$.  
+  Then $C[\wn]\converges n$ if and only if there exists some $\s\in\sigma$ such that $\s\vert_\bN=qn$.  
+  Moreover, $C[\wn]\mustconverge$ if and only if $\sigma$ is winning.
 \end{lemma}
 
-Now we have an inclusion functor $\G_{inn}\hookrightarrow\G_{TO}$, where $\G_{TO}$ is the Tsukada-Ong category.  
+Now we have an inclusion functor $J:\G_{inn}^\oc\hookrightarrow\G_{TO}$, where $\G_{TO}$ is the Tsukada-Ong category.  
 Since the nondeterministic oracle $\wn$ may also be interpreted as a tree-strategy $\top_{\bN}$ in $\G_{TO}$, this gives us a model of PCF with countable nondeterminism inside that category.
 
-It is then possible to deduce versions of Lemma \ref{lem:consistency} and Proposition \ref{prop:adequacy} from Lemma \ref{lem:pcf-soundness-lemma} as we did above for our model of Idealized Algol, using the details of the inclusion functor from $\G_{inn}$ and the definition of composition in $\G_{TO}$.
-We can then deduce soundness in the usual way.
+In order to prove adequacy for this model, we are only going to use two facts about the category $\G_{TO}$.  
+The first fact is that the inclusion functor $J$ preserves the structure of the model $\G_{inn}$; i.e., it is faithful and strong monoidal.  
+The second fact will capture the properties of the morphism $\top_{\bN}\from I \to \bN$ in $\G_{TO}$.
 
-It is worth noting an alternative line of attack, which is to first build a copy of our model of Idealized Algol with countable nondeterminism inside $\G_{TO}$, using our argument to prove soundness and adequacy, and then restrict down to nondeterministic PCF.
-The approach above is more general, however, since it does not make use of the fact that Idealized Algol may be interpreted in $\G_{TO}$.
+\begin{definition}
+  Let $\sigma,\tau\from\bN_1\to\bN_2$ be morphisms in $\G_{inn}^\oc$.  
+  We say that $\sigma\approx\tau$ if the following two conditions hold.
+  \begin{itemize}
+    \item For all $n\in\omega$, there exists $\s\in\sigma$ such that $\s\vert_{\bN_2}=qn$ if and only if there exists $\t\in\tau$ such that $\t\vert_{\bN_2}=qn$.  
+    \item $\sigma$ is winning if and only if $\tau$ is winning.
+  \end{itemize}
+\end{definition}
+
+\begin{proposition}
+  If $\sigma,\tau\from\bN\to\bN$ are morphisms in $\G_{inn}^\oc$, then $\top_\bN;J(\sigma)=\top_\bN;J(\tau)$ in $\G_{TO}$ if and only if $\sigma\approx\tau$.  
+\end{proposition}
+
+This is evidently true if we replace $\G_{TO}$ with $\G_{ND}$, since a strategy $\rho$ for $\bN$ is determined by the set of $n$ such that $qn\in T_\rho$ and whether or not $D_\rho$ is empty.  
+It is true in $\G_{TO}$, which allows us to prove the following version of adequacy which is sufficient for the purpose of proving full abstraction.
+
+\begin{theorem}[Adequacy for nondeterministic PCF]
+  Let $M,N\from\nat$ be two terms of nondeterministic PCF.  
+  Suppose that for all $n\in\omega$, $M\converges n$ if and only if $N\converges n$ and furthermore that $M\mustconverge$ if and only if $N\mustconverge$.  
+  Then $\deno{M}=\deno{N}$ in $\G_{TO}$.  
+\end{theorem}
 
@@
 
-%% Appendix
-\appendix
-\section{Appendix}
-
-Text of appendix \ldots
-
 \end{document}

### 2018-01-30 cones/paper/cones.tex

@@
 
-The second observation is that Lemma \ref{lem:soundness-lemma} can just as easily be applied to PCF contexts and its game semantics model $\G_{inn}$.  
-There really is nothing to this observation: since any PCF context may be interpreted in Idealized Algol, then Lemma \ref{lem:soundness-lemma} applies to it.
-So we have narrowed \ref{lem:soundness-lemma} down to a result about $\G_{inn}$.  
-The only other change we need to make is to switch our base observable type from $\com$ to $\nat$, since PCF has no command type.  
-The version with $\nat$ instead of $\com$ can be proved in exactly the same way.
+We want a version of Lemma \ref{lem:soundness-lemma} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
+Clearly, the lemma as currently stated does not hold in $\G_{inn}$, since the strategies $\sigma$ that we define are not innocent in general.
 
+Instead, we need to look at the combinatorial structure of the strategies.  
+We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.
+In addition, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not \emph{winning}; i.e., either $\sigma_M$ is not total or there exists some $\s\in T_{\sigma_M}$ with an infinite tail of moves in $\oc\bN$.
+We recover the following version of Lemma \ref{lem:soundness-lemma} which now applies to the interpretation of PCF in $\G_{inn}$:
 \begin{lemma}
-  Let $C[-]\from\nat$ be a PCF context with a hole of type $\nat$.
-  Let $\sigma\from\bN\to\bN$ be the denotation of $\lambda n.C[n]$ in $\G_{inn}^\oc$.  
-  Then $C[\wn]\converges n$ if and only if there exists some $\s\in\sigma$ such that $\s\vert_\bN=qn$.  
-  Moreover, $C[\wn]\mustconverge$ if and only if $\sigma$ is winning.
+  Let $M=C[\wn]$ be a term of type $\com$.  
+  Write $\sigma_M\from\oc\bN\to\bC$ for the denotation of the term $\lambda n.C[n]$.  
+  \begin{itemize}
+    \item $M\converges\skipp$ if and only if there exists $\s\in \sigma_M$ such that $\s\vert_{\bC}=qa$.  
+    \item $M\mustconverge$ if and only if $\sigma_M$ is \emph{winning}.
+  \end{itemize}
+  \label{lem:pcf-soundness-lemma}
 \end{lemma}

### 2018-01-31 cones/paper/cones.tex
Fixed \'soundness and adequacy\' referring to adequacy.

@@
 In our case, since composition is not continuous in the language itself, we cannot use this technique.
-In order to prove soundness and adequacy, we use a new technique that involves using a deterministic stateful construction to model the nondeterminism inside a deterministic world in which continuity holds.
+In order to prove adequacy, we use a new technique that involves using a deterministic stateful construction to model the nondeterminism inside a deterministic world in which continuity holds.  
 We shall return to the concept of an \emph{evaluation} of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
@@
   Setting $F = \lambda n.C[n]$, we see that $\deno{F}=\sigma_M$.  
-  So, by soundness and adequacy for the Idealized Algol model, we see that $qa\in T_{\sigma_\pi;\sigma_M}$ if and only if $N_{n_1,\dots,n_k,d} (\lambda n.C[n])\converges\skipp$, which is the case if and only if $M\converges\skipp$ along the evaluation $\pi$.
+  So, by adequacy for the Idealized Algol model, $qa\in T_{\sigma_\pi;\sigma_M}$ if and only if $N_{n_1,\dots,n_k,d} (\lambda n.C[n])\converges\skipp$, which is the case if and only if $M\converges\skipp$ along the evaluation $\pi$.
   Similarly, $D_{\sigma_\pi;\sigma_M}\neq\emptyset$ if and only if $N_{n_1,\dots,n_k,d}(\lambda n.C[n])$ diverges, which is equivalent to saying that $M$ diverges along the evaluation $\pi$.
@@
   By universality, we have $A=\deno{P}$ for some closed term $P$ of type $T\to\com$.  
-  Then we have $\deno{M};\deno{P}\ne\deno{N};\deno{P}$; by consistency and adequacy, it follows that $M\not{\emam} N$.
+  Then we have $\deno{M};\deno{P}\ne\deno{N};\deno{P}$; by computational adequacy, it follows that $M\not{\emam} N$.
 \end{proof}
@@
 
-Having ourselves given a fully abstract model of Idealized Algol with countable nondeterminism, we shall contribute to the process of `completing the square' by giving a sketch of how we can use our techniques to prove soundness and adequacy for the Tsukada-Ong model of PCF with countable nondeterminism.
-A side-effect of this will be to give an alternative proof of soundness and adequacy for their model of PCF with finite nondeterminism.
+Having ourselves given a fully abstract model of Idealized Algol with countable nondeterminism, we shall contribute to the process of `completing the square' by giving a sketch of how we can use our techniques to prove adequacy for the Tsukada-Ong model of PCF with countable nondeterminism.
+A side-effect of this will be to give an alternative proof of adequacy for their model of PCF with finite nondeterminism.
 
-The first observation to make is that our Lemma \ref{lem:soundness-lemma} is not really a statement about the category $\G_{ND,vis}$, but one about the deterministic model $\G_{D,vis}$.
+The first observation to make is that our Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} are not really statements about the category $\G_{ND,vis}$, but about the deterministic model $\G_{D,vis}$.
 
-For example, the first part of the lemma says that if $C[-]$ is an ordinary deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
+For example, the first part of the lemmas says that if $C[-]$ is an ordinary deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
 Although we have mentioned a term ($C[\wn]$) living in nondeterministic Idealized Algol, this can be thought of as a statement about $C[-]$ itself, which is part of deterministic Idealized Algol.  
-Moreover, the strategy $\sigma$ and the denotation of $\lambda n.C[n]$ are both deterministic strategies, so we can interpret Lemma \ref{lem:soundness-lemma} as telling us something about Idealized Algol and its game semantics.
+Moreover, the strategy $\sigma$ and the denotation of $\lambda n.C[n]$ are both deterministic strategies, so we can interpret Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} as telling us something about Idealized Algol and its game semantics.
 We can therefore forget about our nondeterminism model, with its divergence sets and infinite plays (neither of which are part of the Tsukada-Ong model) and concentrate on the Abramsky-McCusker model of Idealized Algol.
-Note that although Lemma \ref{lem:soundness-lemma} mentions $T_{\sigma;\sigma_M}$ and $D_{\sigma;\sigma_M}$, we can rephrase both of these inside the deterministic model, since the strategies involved are both deterministic.
+Note that although Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} mention $T_{\sigma;\sigma_M}$ and $D_{\sigma;\sigma_M}$, we can rephrase both of these inside the deterministic model, since the strategies involved are both deterministic.
 
-We want a version of Lemma \ref{lem:soundness-lemma} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
+We want a version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
 Clearly, the lemma as currently stated does not hold in $\G_{inn}$, since the strategies $\sigma$ that we define are not innocent in general.
@@
 In addition, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not \emph{winning}; i.e., either $\sigma_M$ is not total or there exists some $\s\in T_{\sigma_M}$ with an infinite tail of moves in $\oc\bN$.
-We recover the following version of Lemma \ref{lem:soundness-lemma} which now applies to the interpretation of PCF in $\G_{inn}$:
+We recover the following version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} which now applies to the interpretation of PCF in $\G_{inn}$:
 \begin{lemma}
@@
   This material is based upon work supported by the
-  \grantsponsor{GS100000001}{National Science
-    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
-  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
-  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
+  \grantsponsor{GS501100000690}{National Science
+    Foundation}{http://dx.doi.org/10.13039/501100000690} under Grant
+  No.~\grantnum{GS501100000690}{EP/K018868/1}. Any opinions, findings, and
   conclusions or recommendations expressed in this material are those
   of the author and do not necessarily reflect the views of the
-  National Science Foundation.
+  EPSRC.
 \end{acks}

### 2018-01-31 cones/paper/cones.tex
Switched from 9pt to 10pt.
Gave more complete account of operational semantics.
Made change to operational semantics.

@@
  %% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+\documentclass[sigplan,9pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
 %% For double-blind review submission, w/ CCS and ACM Reference
@@
 \begin{IEEEeqnarray*}{RCL}
-  M & \Coloneqq & x \mid \lambda x . M \mid M\;M \mid \Y_T M \mid \\
-  && \n \mid \skipp \mid \suc M \mid \pred M \mid \\
-  && \IfO M\;M\;M \mid M;M \mid \\
-  && M \coloneqq M \mid \deref M \mid \\
-  && \neww_T\;M \mid \mkvar M\;M \mid \wn\,.
+  M & \Coloneqq & x \mid \lambda x . M \mid M\;M \mid \Y_T \mid \\
+  && \n \mid \skipp \mid \suc \mid \pred \mid \\
+  && \IfO \mid \blank;\blank \mid \blank \coloneqq \blank \mid \\
+  && \deref \mid \neww_T \mid \mkvar \mid \wn\,.
 \end{IEEEeqnarray*}
@@
 We define a small-step operational semantics for the language; this presentation is equivalent to the big-step semantics given in \cite{mcCHFiniteND}, except with a different rule for the countable rather than finite nondeterminism.
-We give a selection of the appropriate rules in Figure \ref{fig:ia-os}.
+We give the appropriate rules in Figure \ref{fig:ia-os}.
 In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.
@@
   \begin{mathpar}
+    \inferrule*{ }{\ia s {(\lambda x.M)\;N} \opto \ia s {M[N/x]}}
+    \and
+    \inferrule*{ }{\ia s {\Y_T M}\opto \ia s {M (\Y_T M)}}
+    \and
+    \inferrule*{ }{\ia s {\suc \n}\opto\ia s {\n + \mathsf{1}}}
+    \and
+    \inferrule*{ }{\ia s {\pred \n}\opto\ia s {\0 \sqcup (\n - \mathsf{1})}}
+    \and
+    \inferrule*{ }{\ia s {\IfO \0 M N} \opto \ia s M}
+    \and
+    \inferrule*{ }{\ia s {\IfO (\n + \mathsf{1}) M N} \opto \ia s N}
+    \and
+    \inferrule*{ }{\ia s {\deref (\mkvar M N)} \opto \ia s M}
+    \and
+    \inferrule*{ }{\ia s {(\mkvar M N) \coloneqq L} \opto \ia s {N\;L}}
+    \and
     \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}
@@
     \and
-    \inferrule*[right=$n\in\bN$]{ }{\wn \opto \n}
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\IfO M} \opto \ia s {\IfO M'}}
     \and
-    \inferrule*{M \opto M'}{M;N\opto M';N}
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\suc M} \opto \ia s {\suc M'}}
     \and
-    \inferrule*{M \opto M'}{M N\opto M'N}
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\pred M} \opto \ia s {\pred M'}}
+    \and
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {M;\blank} \opto \ia s {M';\blank}}
+    \and
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {M \coloneqq \blank} \opto \ia s {M' \coloneqq \blank}}
+    \and
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\deref M} \opto \ia s {\deref M'}}
+    \and
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\mkvar M} \opto \ia s {\mkvar M'}}
+    \and
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {M N} \opto \ia s {M'N}}
+    \and
+    \inferrule*[right=$n\in\bN$]{ }{\ia s \wn \opto \ia s \n}
   \end{mathpar}
-  \caption{Selected rules in the small-step operational semantics of Idealized Algol with countable nondeterminism}
+  \caption{Small-step operational semantics for Idealized Algol with countable nondeterminism}
   \label{fig:ia-os}
@@
 Indeed, if we compose $\mu^\circ$ with the strategy $\0$ for $\bN$ on the left, then the resulting strategy does not satisfy diverge-or-reply.
+The difference with $\nu$ is that every play $qq0\cdots q0\in T_\nu$ may be completed in $\nu$ by playing the move $0$ on the right.
+In other words, $\nu$ is the union of complete strategies, while $\mu^\circ$ is not.
 

### 2018-01-31 cones/paper/cones.tex
Acknowledgements.

@@
 We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.
-In addition, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not \emph{winning}; i.e., either $\sigma_M$ is not total or there exists some $\s\in T_{\sigma_M}$ with an infinite tail of moves in $\oc\bN$.
+
+We define a deterministic strategy $\sigma\from A \implies B$ to be \emph{winning} if it is divergence-free and if for every $O$-play $s\in T_\sigma$ there exists some $t\in T_\sigma$ such that $s\prefix t$ and $t$ ends with a move in $B$.
+
+Then for any strategy $\sigma_M$, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not winning.
+
 We recover the following version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} which now applies to the interpretation of PCF in $\G_{inn}$:
 \begin{lemma}
-  Let $M=C[\wn]$ be a term of type $\com$.  
-  Write $\sigma_M\from\oc\bN\to\bC$ for the denotation of the term $\lambda n.C[n]$.  
+  Let $C[-]$ be a context of deterministic PCF.
+  Write $\sigma_C\from\oc\bN\to\bN$ for the denotation of the term $\lambda n.C[n]$.  
   \begin{itemize}
-    \item $M\converges\skipp$ if and only if there exists $\s\in \sigma_M$ such that $\s\vert_{\bC}=qa$.  
-    \item $M\mustconverge$ if and only if $\sigma_M$ is \emph{winning}.
+    \item $C[\wn]\converges n$ if and only if there exists $\s\in \sigma_C$ such that $\s\vert_{\bN}=qa$.  
+    \item $C\mustconverge$ if and only if $\sigma_C$ is winning.
   \end{itemize}
@@
   This material is based upon work supported by the
-  \grantsponsor{GS501100000690}{National Science
-    Foundation}{http://dx.doi.org/10.13039/501100000690} under Grant
+  \grantsponsor{GS501100000690}{EPSRC}
+  {http://dx.doi.org/10.13039/501100000690} under Grant
   No.~\grantnum{GS501100000690}{EP/K018868/1}. Any opinions, findings, and
@@
   EPSRC.
+  I am grateful to Martin Hyland for an interesting conversation that helped me develop some of this material.
 \end{acks}

### 2018-01-31 cones/paper/cones.tex
Acknowledgements.

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{balance}
 
@@
 Since we cannot predict in advance how may cycles of the loop in $P$ will have elapsed by the time the computation $A$ has completed, the value that ends up printed to the screen may be arbitrarily large.
-Furthermore, under the basic assumption that the task scheduler is \emph{fair}; i.e., any pending task must eventually be executed, we can observe that our program must always terminate by printing out some value to the screen.
+Furthermore, under the basic assumption that the task scheduler is \emph{fair}; i.e., any pending task must eventually be executed, our program must always terminate by printing out some value to the screen.
 
@@
 Laird's work is interesting because it shows that we can obtain a traditional adequacy proof for a semantics with one-sided continuity: composition is continuous with respect to functions, but not with respect to arguments.
-We cannot use these techniques here, though, because our composition is not continuous on either side.
+
+The idea of using some constrained version of continuity to prove adequacy for countable nondeterminism goes back to Plotkin's work on power-domains \cite{PlotkinApt}.
+A crucial observation in both \cite{PlotkinApt} and \cite{LairdOrdinalGames} is that this sort of proof requires a Hoare logic in which we can reason about all the countable ordinals.
+We cannot use these techniques here, however, because our composition is not continuous on either side.
 
@@
 The main concepts of game semantics and the steps we take to establish full abstraction are well-established, with a few exceptions.  
-The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, has not been carried out in a traditional Hyland-Ong game semantics setting before.
+The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, but this is the first time it has been used to establish a full abstraction result for may and must testing.
 
@@
 
-We define a small-step operational semantics for the language; this presentation is equivalent to the big-step semantics given in \cite{mcCHFiniteND}, except with a different rule for the countable rather than finite nondeterminism.
-We give the appropriate rules in Figure \ref{fig:ia-os}.
-In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.
-If $s$ is a store and $v$ a variable, we write $\stup s v n$ for the state formed by updating the value of the variable $v$ to $n$.
-
 \begin{figure*}
@@
     \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\IfO M} \opto \ia s {\IfO M'}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\suc M} \opto \ia s {\suc M'}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\pred M} \opto \ia s {\pred M'}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {M;\blank} \opto \ia s {M';\blank}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {M \coloneqq \blank} \opto \ia s {M' \coloneqq \blank}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\deref M} \opto \ia s {\deref M'}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {\mkvar M} \opto \ia s {\mkvar M'}}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {M N} \opto \ia s {M'N}}
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {E[M]} \opto \ia s {E[M']}}
     \and
@@
 \end{figure*}
+
+We define a small-step operational semantics for the language; this presentation is equivalent to the big-step semantics given in \cite{mcCHFiniteND}, except with a different rule for the countable rather than finite nondeterminism.
+
+We define a Felleisen-style \emph{evaluation context} $E$ inductively as follows.
+\begin{IEEEeqnarray*}{RCL}
+  E & \Coloneqq & - \mid E M \mid \suc E \mid \pred E \mid \IfO E \mid \\
+  && E;\blank \mid E \coloneqq \blank \mid \deref E \blank \mid \mkvar E \mid \new_T E
+\end{IEEEeqnarray*}
+
+We then give the appropriate small-step rules in Figure \ref{fig:ia-os}.
+In each rule, $\ia{s}{M}$ is a \emph{configuration} of the language, where $M$ is a term, and $s$ is a \emph{store}; i.e., a function from the set of variables free in $M$ to the set of natural numbers.
+If $s$ is a store and $v$ a variable, we write $\stup s v n$ for the state formed by updating the value of the variable $v$ to $n$.
 
@@
 
-\begin{proposition}
-  Let $\G_{D,vis,rec}$ be the category of games and \emph{recursive} visible strategies.  
-  Then $\G_{D,vis,rec}^\oc$ is a fully abstract model of Idealized Algol in which every morphism is definable.
+We shall tacitly assume that the games in our category $\G_{ND}$ come with an enumeration so that we can reason about recursive strategies later.  
+For any game that is the denotation of an Idealized Algol type, this enumeration will be the natural one as described above.
+
+The relevant result pertaining to recursive strategies is as follows.
+
+\begin{proposition}[Recursive Universality for Idealized Algol]
+  Let $S$ be an Idealized Algol type and let $\sigma\from \deno S$ be a recursive strategy.  
+  Then there exists a term $M\from S$ of Idealized Algol such that $\sigma=\deno M$.
 \end{proposition}
@@
 
-The category in which we shall model our language is the category $\G_{ND,vis,rec}^\oc$ -- the Cartesian closed category of (enumerated) games with nondeterministic, recursively presentable visible strategies.
-We have a natural embedding $\G_{D,vis,rec}^\oc\hookrightarrow\G_{ND,vis,rec}^\oc$, and we know that $\G_{D,vis,rec}^\oc$ is a universal and fully abstract model of Idealized Algol.
+The category in which we shall model our language is the category $\G_{ND,vis}^\oc$ -- the Cartesian closed category of (enumerated) games with nondeterministic visible strategies.  
+We have a natural embedding $\G_{D,vis}^\oc\hookrightarrow\G_{ND,vis}^\oc$, and we know that $\G_{D,vis}^\oc$ is a universal and fully abstract model of Idealized Algol.
 
@@
 
-We define \emph{extensional equivalence of strategies} as follows.  
+We define \emph{intrinsic equivalence of strategies} as follows.  
 If $\sigma,\tau$ are two strategies for a game $A$, we say that $\sigma\oes\tau$ if for all test morphisms $\alpha\from A \to \bC$ we have $\sigma;\alpha=\tau;\alpha$.  
@@
 
+For proving full abstraction , it is necessary to take the intrinsic quotient in order to identify, for example, the denotations of $\lambda n.\Omega$ and $\lambda n.\IfO n\;\Omega\;\Omega$ of type $\nat\to\nat$.
+These terms are clearly observationally equivalent, but their denotations are not equal; for example, $q\in D_{\deno{\lambda n.\Omega}}$, but $q\not\in D_{\deno{\lambda n.\IfO n\;\Omega\;\Omega}}$.
+
+The point here is that even though $q$ is not explicitly a divergence in the second case, it is nonetheless impossible to prevent the strategy from eventually reaching a divergence.  
+Given a strategy $\sigma$ for a game $A$, we say that $s\in\sigma$ is \emph{unreliable} if player $P$ has a strategy, starting from $s$ and staying at all times within $T_\sigma$, that ensures that we eventually reach some play in $D_\sigma$.
+We then say that a strategy $\sigma$ is \emph{divergence-complete} if every unreliable point of $\sigma$ is contained in $D_\sigma$.  
+Every strategy $\sigma$ can clearly be extended to a minimal divergence-complete strategy $\text{dc}(\sigma)$; Murawski's explicit characterization of the intrinsic collapse \cite{MurawskiIntrinsic}, which may be applied to our model, essentially says that $\sigma\oes\tau$ if and only if $\text{dc}(\sigma)=\text{dc}(\tau)$.
+
 \subsection{Universality}
 
-Let $S,T$ be Idealized Algol types and let $\sigma\from S\to T$ be a morphism in $\G_{ND,vis,rec}^\oc$.  
+Let $S,T$ be Idealized Algol types and let $\sigma\from S\to T$ be a recursive morphism in $\G_{ND,vis}^\oc$.  
 We want to prove that $\sigma$ is the denotation of some term.
@@
 By our nondeterministic factorization result, we know that $\sigma=\top_\bN;\Det(\sigma)$, where $\Det(\sigma)$ is a deterministic strategy.  
-By universality for $\G_{D,vis,rec}^\oc$, we know that $\Det(\sigma)=\deno{M}$ for some closed term $M\from S \to T$.  
+By universality for $\G_{D,vis}^\oc$, we know that $\Det(\sigma)=\deno{M}$ for some closed term $M\from S \to T$.  
 Then $\sigma=\top_\bN;\Det(\sigma)=\deno{\wn};\deno M = \deno{M\;\wn}$.
@@
   Suppose that $\deno{M}\not{\oes}\deno{N}$; so there is some strategy $\alpha\from A\to\bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.  
-  By universality, we have $A=\deno{P}$ for some closed term $P$ of type $T\to\com$.  
+  We can clearly choose $\alpha$ to be recursively presentable; by universality, we have $\alpha=\deno{P}$ for some closed term $P$ of type $T\to\com$.  
   Then we have $\deno{M};\deno{P}\ne\deno{N};\deno{P}$; by computational adequacy, it follows that $M\not{\emam} N$.
 \end{proof}
-
-Of course, this full abstraction holds just as well for $\G_{ND,vis}^\oc$, where we relax the recursivity condition.
 
@@
 
-\begin{proposition}
-  If $\sigma,\tau\from\bN\to\bN$ are morphisms in $\G_{inn}^\oc$, then $\top_\bN;J(\sigma)=\top_\bN;J(\tau)$ in $\G_{TO}$ if and only if $\sigma\approx\tau$.  
-\end{proposition}
+\begin{definition}
+  We say that a Cartesian closed category $\C$ is a \emph{sensible game semantics of PCF with countable nondeterminism} if there is a strong monoidal functor $J\from\G_{inn}^\oc\to\C$ and a morphism $\top_{\bN}\from 1 \to J(\bN)$ in $\C$ such that for all $\sigma,\tau\from\bN\to\bN$ in $\G_{inn}^\oc$, we have
+  \[
+    \top_\bN;J(\sigma)=\top_\bN;J(\tau)
+    \]
+  if and only if $\sigma\approx\tau$.  
+\end{definition}
 
-This is evidently true if we replace $\G_{TO}$ with $\G_{ND}$, since a strategy $\rho$ for $\bN$ is determined by the set of $n$ such that $qn\in T_\rho$ and whether or not $D_\rho$ is empty.  
-It is true in $\G_{TO}$, which allows us to prove the following version of adequacy which is sufficient for the purpose of proving full abstraction.
+This definition gives a rather minimal condition on the morphism $\top_\bN$ that ensures that it behaves as it should when substituted into functions $\bN \to \bN$.
+For example, our category $\G_{ND}$ is a sensible game semantics of PCF with countable nondeterminism, as is the Tsukada-Ong category $\G_{TO}$.
+
+Using this condition and Lemma \ref{lem:pcf-soundness-lemma}, it is easy to prove the following version of adequacy, which is sufficient for the purpose of proving full abstraction.
 
 \begin{theorem}[Adequacy for nondeterministic PCF]
+  Let $\C$ be a sensible model of nondeterministic PCF, and define $\deno -$ to be given by the functor $J$ and the morphism $\top_\bN$ in the obvious way.
+
   Let $M,N\from\nat$ be two terms of nondeterministic PCF.  
   Suppose that for all $n\in\omega$, $M\converges n$ if and only if $N\converges n$ and furthermore that $M\mustconverge$ if and only if $N\mustconverge$.  
-  Then $\deno{M}=\deno{N}$ in $\G_{TO}$.  
+  Then $\deno{M}=\deno{N}$ in $\C$.
 \end{theorem}
+
+\section{Conclusion}
+
+% Oh ho ho ho ho!!!
+\balance
+Our last result is fairly general, and can be applied to a number of different game semantics models, including the models of concurrent games of \cite{ConcurrentHylandOngGames}.  
+The natural next step is to extend it to give a proof of full abstraction for nondeterministic PCF in the Tsukada-Ong model.  
+The missing ingredient is a universality result for that model.  
+Tsukada and Ong prove compact definability from first principles, rather than using a factorization result, and it is not immediate how one defines a recursive element of their model.  
+Nevertheless, we can have some confidence that such a result is possible, which will allow our results to be carried over to stateless languages.
+
+It would be interesting to see whether our adequacy proof can be applied to effects other than nondeterminism; although most effects do not engender a failure of continuity in the same way, a similar approach could help us use an adequacy result from one language to prove adequacy for another language, rather than proving it from first principles each time.
+
+Lastly, our proof has thrown more light on the important relation between nondeterminism and state.  
+As we have discussed, stateful languages (and visible strategies) pose fewer problems for modelling nondeterminism than do stateless languages (and innocent strategies), but the fact that we needed to use the stateful structure of the language in our proof of Lemma \ref{lem:soundness-lemma} suggests that there is a deeper relationship between the two, which we should explore in future work.
 
@@
   {http://dx.doi.org/10.13039/501100000690} under Grant
-  No.~\grantnum{GS501100000690}{EP/K018868/1}. Any opinions, findings, and
-  conclusions or recommendations expressed in this material are those
-  of the author and do not necessarily reflect the views of the
-  EPSRC.
-  I am grateful to Martin Hyland for an interesting conversation that helped me develop some of this material.
+  No.~\grantnum{GS501100000690}{EP/K018868/1}.   I am grateful to Martin Hyland for an interesting conversation that helped me develop some of this material.
 \end{acks}

### 2018-01-31 cones/paper/cones.tex
Fixed a typo.
Put in changes from Jim.

@@
 
-We have therefore built an \emph{unbounded nondeterminism} machine, that can print out arbitrarily large natural numbers but which never diverges, as distinct from finitary choice nondeterminism.
+We have therefore built an \emph{unbounded nondeterminism} machine, that can print out arbitrarily large natural numbers but which never diverges.  
+This is strictly more powerful than finitary choice nondeterminism.
 \footnote{Using recursion, we can build a program out of finite nondeterminism that can produce arbitrarily large natural numbers; however, this program also admits the possibility of divergence.}  
@@
 9]{DijkstraBook} that it is impossible to implement unbounded nondeterminism, showing that the natural constructs from which we construct imperative programs satisfy a \emph{continuity} property that unbounded nondeterminism lacks.
-In fact, for semanticists, this lack of continuity is a problem in itself, since the standard proofs of computational adequacy and full abstraction typically make use, implicitly or otherwise, of the fact that composition within the model is continuous with respect to some ordering.
+For semanticists, this lack of continuity is a problem in itself, since the standard proofs of computational adequacy and full abstraction typically make use, implicitly or otherwise, of the fact that composition within the model is continuous with respect to some ordering.
 
@@
 We begin with a pair of examples that will illustrate the lack of continuity, from a syntactic point of view.  
-Let $\nat$ be our number type and consider a sequence of functions ${<}n\from\nat\to\nat$ where ${<}m\;k$ evaluates to $0$ if $k<n$ and diverges otherwise.
+Let $\nat$ be our natural number type and consider a sequence of functions ${<}n\from\nat\to\nat$, where ${<}m\;k$ evaluates to $0$ if $k<n$ and diverges otherwise.
 In that case, the least upper bound of the ${<}n$ is the function that combines all their convergent behaviours; i.e., the function $\lambda k.k;\0$ that evaluates its input and then returns $0$.
@@
 
-Lack of continuity is a problem because fixed-point combinators are typically built using least upper bounds, and proving adequacy of the model requires that these least upper bounds be preserved.  
+Lack of continuity is a problem because fixed-point combinators are typically built using least upper bounds, and proving adequacy of the model typically requires that these least upper bounds be preserved.
 In a non-continuous situation, we will need to come up with new techniques in order to prove adequacy without using continuity.
@@
 Although we are able to give a model of Idealized Algol with countable nondeterminism in the more traditional Harmer-McCusker style, it seems necessary to introduce this extra machinery in order to model stateless languages such as PCF (and certainly to model concurrency).
-In the last section of this paper, we will show how our methods can be applied under very general circumstances, and in particular to these models.
+In the last section of this paper, we will show how our methods can be applied under very general circumstances, and in particular to these models of nondeterministic stateless languages.
 
@@
 The main concepts of game semantics and the steps we take to establish full abstraction are well-established, with a few exceptions.  
-The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, but this is the first time it has been used to establish a full abstraction result for may and must testing.
+The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, is the first example of using the technique to establish a full abstraction result for may and must testing.
 
 There are two points in the traditional Full Abstraction proof that depend on composition being continuous, and we have had to come up with ways of getting round them.  
-The easier of the two is that continuity is necessary to derive Full Abstraction from definability of compact strategies; in order to get around this, we have had to appeal to the stronger \emph{universality} result of \cite{hoPcf}, that says that every \emph{recursive} strategy is definable.
+The easier of the two is that continuity is necessary for the usual proof that we can derive Full Abstraction from definability of compact strategies; in order to get around this, we have had to appeal instead to the stronger \emph{universality} result of \cite{hoPcf}, that says that every \emph{recursive} strategy is definable.
 
-For the proof of adequacy, we have had to come up with a new technique.  
-This technique can be thought of as a kind of synthesis between the two usual methods of proving adequacy -- one involving logical relations and the other using more hands-on operational techniques.  
+For the proof of adequacy, we have had to come up with a new technique, which can be thought of as a kind of synthesis between the two usual methods of proving adequacy -- one involving logical relations and the other using more hands-on operational techniques.
 We do this by separating out the deterministic, continuous part of the strategy from the nondeterministic, discontinuous part.  
-Using the stateful language, we can simulate individual evaluation paths of a nondeterministic program using deterministic programs, which allows us to appeal to the adequacy result for deterministic Idealized Algol.
-We then rely on more combinatorial techniques to factor the nondeterminism back in.
+Using the stateful language, we can simulate individual evaluation paths of a nondeterministic program using a deterministic device that corresponds to the idea of `mocking' a random number generator for testing purposes.
+This allows us to appeal to the adequacy result for deterministic Idealized Algol.  
+We then rely on more combinatorial techniques in order to factor the nondeterminism back in.
 
@@
 In the last section of the paper, we show that it may be used to prove adequacy for models of nondeterministic PCF under very mild assumptions.  
-The Tsukada-Ong model, for example, satisfies these assumptions and so we obtain an adequacy result for its semantics.
+The Tsukada-Ong model, for example, satisfies these assumptions, allowing us to obtain an adequacy result for PCF with countable nondeterminism.
 
@@
 
-We define a Felleisen-style \emph{evaluation context} $E$ inductively as follows.
+First, we define a Felleisen-style \emph{evaluation context} $E$ inductively as follows.
 \begin{IEEEeqnarray*}{RCL}
@@
 
-Aside from making violating soundness for the model, this example actually leads to composition not being associative if we naively extend the Harmer-McCusker model from finite to infinite nondeterminism (e.g., see \cite[4.4.1]{RusssThesis}).
+Aside from showing that this model cannot possibly be sound, this example actually leads to composition not being associative if we naively extend the Harmer-McCusker model from finite to infinite nondeterminism (e.g., see \cite[4.4.1]{RusssThesis}).
 
@@
 
-\subsection{Recursive games and strategies}
+\subsection{Enumerated games and recursive strategies}
 
@@
 
-Any term $M\from T$ of Idealized Algol with countable nondeterminism may be written as $M = C[\wn]$, where $C$ is a context not involving the constant $\wn$.  
+Any term $M\from T$ of Idealized Algol with countable nondeterminism may be written as $M = C[\wn]$, where $C$ is a multi-holed context not involving the constant $\wn$.  
 Then the term $\lambda n.C[n]$ is a term of Idealized Algol, and therefore has a denotation $\oc\bN \to \deno{T}$ as in \cite{SamsonGuyIAPassive}.
@@
 \begin{lemma}
-  Let $M=C[\wn]$ be a term of type $\com$, where $C[-]$ is a context of Idealized Algol.
+  Let $M=C[\wn]$ be a term of type $\com$, where $C[-]$ is a multi-holed context of Idealized Algol.
   Write $\sigma_M$ for the denotation of the term $\lambda n.C[n]$.  
@@
   In this case, $M$ must certainly diverge along the evaluation $\pi$.
-  For each $j$, we define $\pi_n^{(j)}$ to be the strategy for $\oc N$ corresponding to the term $N_{n_1,\dots,n_j,\Omega}$.  
+  For each $j$, we define $\pi_n^{(j)}$ to be the strategy for $\oc \bN$ corresponding to the term $N_{n_1,\dots,n_j,\Omega}$.  
   So $\pi_n^{(j)}$ has a unique finite maximal play
@@
 
-  Let $M=C[\wn]$ be a closed term, where $C$ is a deterministic context.  
+  Let $M=C[\wn]$ be a closed term, where $C$ is a deterministic multi-holed context.  
   Then, by Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse}, we see that $M\not\mustconverge$ if and only if there exists some total deterministic $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$.
@@
 
-Tsukada and Ong \cite{TsukadaSheaves} showed that traditional game semantics models are unsuitable for modelling \emph{nondeterministic} PCF: while the definition of \emph{visibility} of strategies can be extended to nondeterministic strategies without difficulty, innocence cannot.
+Tsukada and Ong \cite{TsukadaSheaves}, following Harmer \cite{RusssThesis}, showed that traditional game semantics models are unsuitable for modelling \emph{nondeterministic} PCF: while the definition of \emph{visibility} of strategies can be extended to nondeterministic strategies without difficulty, innocence cannot.
 
@@
 
-For example, the first part of the lemmas says that if $C[-]$ is an ordinary deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
+For example, the first parts of the lemmas says that if $C[-]$ is a deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
 Although we have mentioned a term ($C[\wn]$) living in nondeterministic Idealized Algol, this can be thought of as a statement about $C[-]$ itself, which is part of deterministic Idealized Algol.  
@@
 \begin{lemma}
-  Let $C[-]$ be a context of deterministic PCF.
+  Let $C[-]$ be a multi-holed context of deterministic PCF.
   Write $\sigma_C\from\oc\bN\to\bN$ for the denotation of the term $\lambda n.C[n]$.  
@@
 Tsukada and Ong prove compact definability from first principles, rather than using a factorization result, and it is not immediate how one defines a recursive element of their model.  
-Nevertheless, we can have some confidence that such a result is possible, which will allow our results to be carried over to stateless languages.
+Nevertheless, we can have some confidence that such a result is possible, allowing our results to be carried over to stateless languages.
 

### 2018-01-31 cones/paper/cones.tex
Finished the paper.

@@
   \item $M_A$ is a countable set of moves,
-  \item $\lambda_A\from m_A\to\OP\times\QA$ designates each move as either an \emph{$O$-move} or a \emph{$P$-move}, and as either a \emph{question} or an \emph{answer}.  
+  \item $\lambda_A\from M_A\to\OP\times\QA$ designates each move as either an \emph{$O$-move} or a \emph{$P$-move}, and as either a \emph{question} or an \emph{answer}.  
     We define $\lambda_A^{OP}=\pr_1\circ\lambda_A$ and $\lambda_A^{QA}=\pr_2\circ\lambda_A$.  
@@
 
-Given an arena $A$, a \emph{justified string} in $A$ is a sequence $s$ of moves in $A$, together with \emph{justification pointers} that go from move to move in the sequence in such a way that every non-initial move $m$ in $s$ has exactly one justification pointer going back to an earlier move $n$ in $s$ such that $n\ts_A m$.
+Given an arena $A$, a \emph{justified string} in $A$ is a sequence $s$ of moves in $A$, together with \emph{justification pointers} that go from move to move in the sequence.  
+The justification pointers must be set up in such a way that every non-initial move $m$ in $s$ has exactly one justification pointer going back to an earlier move $n$ in $s$ such that $n\ts_A m$.  
 We say that $n$ \emph{justifies} $m$.  
@@
 
-A \emph{legal play} $s$ is a justified string in $A$ that strictly alternates between $O$-moves and $P$-moves and is such that the corresponding $QA$-sequence formed by applying $\lambda_A^{QA}$ to terms is well-bracketed.
+A \emph{legal play} $s$ is a justified string in $A$ that strictly alternates between $O$-moves and $P$-moves and is such that the corresponding $QA$-sequence formed by applying $\lambda_A^{QA}$ to moves is well-bracketed.
 We write $L_A$ for the set of legal plays in $A$.
@@
 
-Our base games will be the games $\bN$ and $\bC$ on the arenas of the same names, where $P_{\bN}=\{\emptyplay,q\}\cup\{qn\suchthat n\in\bN\}$ and $\bC = \{\emptyplay,q,qa\}$.
+Our base games will be the games $\bN$ and $\bC$ on the arenas of the same names, where $P_{\bN}=\{\emptyplay,q\}\cup\{qn\suchthat n\in\bN\}$ and $P_{\bC} = \{\emptyplay,q,qa\}$.
 
@@
 
-We follow \cite{mcCHFiniteND} by modelling a strategy as a pair $(T_\sigma,D_\sigma)$, where $T_\sigma$ is a nondeterministic strategy in the usual sense and $D_\sigma$ is a set of $O$-plays after which there is a possibility of divergence.
+To fix this problem, we follow \cite{mcCHFiniteND} by modelling a strategy as a pair $(T_\sigma,D_\sigma)$, where $T_\sigma$ is a nondeterministic strategy in the usual sense and $D_\sigma$ is a set of $O$-plays after which there is a possibility of divergence.
 
-Tracking divergences explicitly in this way requires some care when we compose strategies.  
+Tracking divergences explicitly in this way requires some care when we compose strategies using `parallel composition plus hiding'.
 Specifically, we need to be able to add new divergences into strategies when they arise through `infinite chattering' or \emph{livelock}.  
@@
   \]
-is given by a total strategy, without divergences: namely the strategy $\mu$ with plays of the form
-\[
-  \begin{array}{ccccccc}
-    \mathbf{\bN_1} &   & q & n_1 & q & n_2 & \cdots \\
-    \mathbf{\bN_2} & q &   &     &   &     &
-  \end{array}\,.
-  \]
+is given by a total strategy, without divergences: namely the strategy $\mu$ with plays of the form shown in Figure \ref{fig:mn-plays}(a).
+\begin{figure}
+  \begin{mathpar}
+    a) \and
+    \begin{array}{cc}
+      \mathbf{\bN_1} & \mathbf{\bN_2} \\
+                     & q \\
+                  q  &   \\
+                 n_1 &   \\
+                  q  &   \\
+                 n_2 &   \\
+              \vdots &   \\
+              {}     & {}
+    \end{array}
+    \and b) \and
+    \begin{array}{cc}
+      \mathbf{\bN_1} & \mathbf{\bN_2} \\
+                     & q \\
+                  q  &   \\
+                 n_1 &   \\
+              \vdots &   \\
+                  q  &   \\
+                 n_m &   \\
+                     & 0 \\
+    \end{array}
+  \end{mathpar}
+  \caption{Finite plays alone are not sufficient to distinguish between terms of a language with countable nondeterminism.}
+  \label{fig:mn-plays}
+\end{figure}
 However, when we compose this strategy with any total strategy for $\bN$ on the left, we expect the resulting strategy to contain divergences, since the term $M \n$ diverges for any $\n$.
@@
 
-The approach adopted in \cite{mcCHFiniteND} is to check specifically for infinite chattering between strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ by checking whether the set $\sigma\|\tau$ contains any infinite increasing sequence of plays ending with moves in $B$.
+The approach adopted in \cite{mcCHFiniteND} is to check specifically for infinite chattering between strategies $\sigma\from A\implies B$ and $\tau\from B\implies C$ by checking whether there is an infinite increasing sequence of interactions between $\sigma$ and $\tau$ with an infinite tail in $B$.
 If there is such a sequence, then it restricts to some $O$-position in $\sigma;\tau$ and we add in a divergence at that position.
@@
 This term first chooses a natural number $m$, and then reads from its input $n$ for a total of $m$ times before eventually returning $\0$.  
-Thus, its denotation is the strategy $\nu$ with maximal plays of arbitrary length of the form:
-\[
-  \begin{array}{cccccccc}
-    \bN_1 &   & q & n_1 & \cdots & q & n_m & \\
-    \bN_2 & q &   &     &        &   &     & 0
-  \end{array}\,.
-  \]
-Note that this strategy strictly contains the one we considered before, and therefore that the denotation of
+Thus, its denotation is the strategy $\nu$ with maximal plays of arbitrary length of the form shown in Figure \ref{fig:mn-plays}(b).
+Note that this strategy strictly contains the strategy $\mu$ that we considered before, and therefore that the denotation of
 \[
@@
 has the same denotation as $N$, even though for any $n$, $M\n\not{\mustconverge}$, while $N\n\mustconverge$.
-Moreover, if we try to compose $\deno{N}$ with the strategy on $\bN$ that always returns $1$, then we end up with an infinite increasing sequence of positions, which triggers the introduction of a divergence into the composite -- even though no divergence occurs in the evaluation of $N$.
+Moreover, if we try to compose $\deno{N}$ with the strategy on $\bN$ that always returns $1$, then we end up with an infinite increasing sequence of positions, which triggers the introduction of a divergent play into the composite strategy -- even though no divergence occurs in the evaluation of $N$.
 
@@
 The way that we do this is by making the infinite sequences of moves explicit in our strategies, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.  
-Then the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitrarily long finite sequences, but no infinite sequences.
+When we use this technique, the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitrarily long finite sequences, but no infinite sequences.
 
@@
 
-Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself a legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
+Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself an (infinite) legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
 
@@
 Any finite-nondeterminism strategy in the sense of \cite{mcCHFiniteND} may be interpreted as a complete strategy by enlarging it with all its infinite limiting plays.  
-However, when we introduce countable nondeterminism, we introduce the possibility of strategies that are not complete.  
+However, when we introduce countable nondeterminism, we also introduce strategies that are not complete.  
 For example, the strategy $\nu$ that we mentioned above has an infinite increasing sequence of plays $q0\prefix q0q0\prefix \cdots$, but has no infinite play corresponding to its limit.  
@@
 We need to show that the composition of locally complete strategies is locally complete.  
-Note that this does not hold for \emph{complete} strategies: for example, our term $N$ above can be written as $N'\;\wn$, where $N'$ is a deterministic term with complete denotation $\nu'$.  
+Note that the composition of \emph{complete} strategies is not necessarily complete: for example, our term $N$ above can be written as $N'\;\wn$, where $N'$ is a deterministic term with complete denotation $\nu'$.
 Then we have $\nu=\top_{\bN};\nu'$, but $\nu$ is not complete.
@@
 However, it is worth saying a few words about it, since the model obtained by naively extending the Harmer-McCusker model to unbounded nondeterminism does not have an associative composition.  
-The point is that this is not really a problem with associativity, but rather that this naive model gives the wrong result for the composition of strategies with infinite nondeterminism.
+The point is that there is not really a problem with associativity itself, but rather that this naive model gives the wrong result for the composition of strategies with infinite nondeterminism.
 For example, if $\nu$ is the strategy we defined above, and $\0$ is the `constant $0$' strategy on $\bN$, then $\0;\nu$ has a divergence in the naive model, because the strategies $\0$ and $\nu$ appear to be engaged in infinite chattering.
@@
 
-This is very similar to the construction of a co-Kleisli category for a linear exponential comonad, but certain technical issues relating to well-openedness prevent us from displaying it in this way.
+This is very similar to the construction of a co-Kleisli category for a linear exponential comonad, but certain technical issues relating to well-openedness prevent us from presenting it in this way.
 
@@
 We will therefore need to appeal to a stronger result -- that of \emph{universality}, which states that \emph{every} strategy is definable.  
-Clearly, universality does not hold for any of our categories of games, since there are many non-computable functions $\bN\to\bN$.  
+Clearly, universality does not hold for any of our categories of games -- for example, there are many non-computable functions $\bN\to\bN$.  
 However, Hyland and Ong proved in \cite{hoPcf} that every \emph{recursively presentable} innocent strategy is PCF-definable.
@@
 We shall tacitly assume that the games in our category $\G_{ND}$ come with an enumeration so that we can reason about recursive strategies later.  
-For any game that is the denotation of an Idealized Algol type, this enumeration will be the natural one as described above.
+For any game that is the denotation of an Idealized Algol type, this enumeration will be as we have just described.
 
@@
 Our definability results will hinge on a \emph{factorization theorem}, showing that every nondeterministic strategy may be written as the composition of a deterministic strategy with the nondeterministic `oracle' $\top_{\bN}$.
-We can then deduce definability from definability in the model of deterministic Idealized Algol.
+We can then deduce universality from universality in the model of deterministic Idealized Algol.
 
@@
   Lastly, we close under limits to make the strategy $\Det(\sigma)$ complete.  
-  $\Det(\sigma)$ is clearly nondeterministic.  
+  $\Det(\sigma)$ is clearly deterministic.  
   Checking that $\top_{\bN};\Det(\sigma)=\sigma$ is easy for finite plays; for infinite plays, it follows by completeness of $\sigma$.
@@
 \begin{proposition}[Computational Adequacy]
+  Let $M\from\com$ be a closed term of Idealized Algol with countable nondeterminism.
   $M\converges\skipp$ if and only if $qa\in T_{\deno M}$.  
@@
 In order to prove adequacy, we use a new technique that involves using a deterministic stateful construction to model the nondeterminism inside a deterministic world in which continuity holds.  
-We shall return to the concept of an \emph{evaluation} of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
+To do this, we shall return to the concept of an \emph{evaluation} $\pi$ of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
 
@@
   Here, $\case_{k+1}\;a\;n_0\;\cdots\;n_k\;d$ is a new shorthand that evaluates to $n_i$ if $a$ evaluates to $i$, and evaluates to $d$ if $a$ evaluates to $j> k$.
-  This term adds an extra variable $v$ to the program; each time $f$ is called, it increments the value of $v$ and maps its value on to one of the $n_i$.
+  This term adds an extra variable $v$ to the program; each time $f$ is called, it increments the value of $v$ and maps its value to one of the $n_i$.  
+  The result is that when $f$ calls its argument, it will receive $n_1$ the first time, $n_2$ the second and so on.
 
@@
     I \xrightarrow{\cell_{0}}
-    \oc \Var \xrightarrow{\deno{\lambda v.v\coloneqq (\suc\;\deref v);\case_{k+1}\;\deref v\;\Omega\;n_1\cdots n_k d}}
+    \oc \Var \xrightarrow{\oc\deno{\lambda v.v\coloneqq (\suc\;\deref v);\case_{k+1}\;\deref v\;\Omega\;n_1\cdots n_k d}}
     \oc\bN \xrightarrow{\deno F}
@@
   Setting $F = \lambda n.C[n]$, we see that $\deno{F}=\sigma_M$.  
-  So, by adequacy for the Idealized Algol model, $qa\in T_{\sigma_\pi;\sigma_M}$ if and only if $N_{n_1,\dots,n_k,d} (\lambda n.C[n])\converges\skipp$, which is the case if and only if $M\converges\skipp$ along the evaluation $\pi$.
+  So, by adequacy for the Idealized Algol model, $qa\in T_{\sigma_\pi;\sigma_M}$ if and only if we have $N_{n_1,\dots,n_k,d} (\lambda n.C[n])\converges\skipp$, which is the case if and only if $M\converges\skipp$ along the evaluation $\pi$.
   Similarly, $D_{\sigma_\pi;\sigma_M}\neq\emptyset$ if and only if $N_{n_1,\dots,n_k,d}(\lambda n.C[n])$ diverges, which is equivalent to saying that $M$ diverges along the evaluation $\pi$.
@@
   \[
-    q\;m_1\;q\;n_2\;\cdots\,,
+    q\;m_1\;q\;m_2\;\cdots\,,
     \]
@@
   Otherwise, let $t$ be the maximal sub-play of $s$ such that $\s\vert_{\oc\bN}=t$ for some $\s\in\sigma_M$.  
-  Then, if we replace $\sigma$ with the strategy $\sigma'$ that plays according to $t$ and subsequently plays $q\;d\;q\;d\;\cdots$ for our fixed value $d$, then we will have $\sigma';\sigma_M=\sigma;\sigma_M$.
-  Moreover, $\sigma'=\sigma_\pi$ for some evaluation $\pi$ of $M$.
+  Then, if we replace $\sigma$ with the strategy $\sigma'$ that plays according to $t$ and subsequently plays $q\;d\;q\;d\;\cdots$ for our fixed value $d$, we will have $\sigma';\sigma_M=\sigma;\sigma_M$.
+  In either case, $\sigma'=\sigma_\pi$ for some evaluation $\pi$ of the term $M$.
 
   Now suppose that there exists $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$.  
-  By the proof of Lemma \ref{lem:soundness-lemma}, we may assume that $\sigma=\sigma_\pi$ for some evaluation $\pi$ of $M$.  
+  We may assume that $\sigma=\sigma_\pi$ for some evaluation $\pi$ of $M$.  
   Therefore, $qa\in T_{\sigma_\pi;\sigma_M}$, which means that $M\converges\skipp$ along the evaluation $\pi$.  
@@
 The point here is that even though $q$ is not explicitly a divergence in the second case, it is nonetheless impossible to prevent the strategy from eventually reaching a divergence.
-Given a strategy $\sigma$ for a game $A$, we say that $s\in\sigma$ is \emph{unreliable} if player $P$ has a strategy, starting from $s$ and staying at all times within $T_\sigma$, that ensures that we eventually reach some play in $D_\sigma$.
+
+Given a nondeterministic strategy $\sigma$ for a game $A$, we may treat $\sigma$ as a game in its own right (a sub-game of $A$).  
+Moreover, for any $s\in T_\sigma$, we have a particular branch of that game in which play starts at $s$.  
+We say that $s$ is \emph{unreliable} if player $P$ has a strategy for the game starting at $s$ that ensures that play eventually ends up in $D_\sigma$.
+
 We then say that a strategy $\sigma$ is \emph{divergence-complete} if every unreliable point of $\sigma$ is contained in $D_\sigma$.  
@@
 Instead, they use a novel type of game semantics in which strategies are given not by sets of plays but by justified \emph{trees} whose vertices are moves.  
-The difference is subtle but important: from the point of view of countable nondeterminism it allows us to distinguish between terms that take an arbitrarily large finite number of steps to converge and terms that diverge.
+The difference is subtle but important: from the point of view of countable nondeterminism it allows us to distinguish between terms that take an arbitrarily large finite number of steps to converge and terms that diverge, without needing to track infinitary information.
 For example, the denotation of our term $M$ above has an infinite branch in it, while the denotation of $N$ has infinitely many finite branches of arbitrary length.
 
-The main advantage of the tree-based model, however, is that it gives rise to a satisfactory synthetic definition of a \emph{nondeterministic innocent} strategy based on sheaves.  
-In fact, Tsukada and Ong do not prove full abstraction for PCF with countable nondeterminism (even though that language may be interpreted within their category), but for PCF with finite nondeterminism.
+The main advantage of the tree-based model, however, is that it gives rise to a satisfactory synthetic definition of a \emph{nondeterministic innocent} strategy, based on sheaves.  
+The main contribution of their paper is not to prove full abstraction for PCF with countable nondeterminism (even though that language may be interpreted within their category), but for PCF with finite nondeterminism.
 
@@
 For example, the first parts of the lemmas says that if $C[-]$ is a deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
-Although we have mentioned a term ($C[\wn]$) living in nondeterministic Idealized Algol, this can be thought of as a statement about $C[-]$ itself, which is part of deterministic Idealized Algol.  
+Although we have mentioned a term ($C[\wn]$) living in nondeterministic Idealized Algol, this can be thought of as a statement about $C[-]$ itself, and therefore as a statement about the deterministic language.
 Moreover, the strategy $\sigma$ and the denotation of $\lambda n.C[n]$ are both deterministic strategies, so we can interpret Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} as telling us something about Idealized Algol and its game semantics.
+
 We can therefore forget about our nondeterminism model, with its divergence sets and infinite plays (neither of which are part of the Tsukada-Ong model) and concentrate on the Abramsky-McCusker model of Idealized Algol.
@@
 Instead, we need to look at the combinatorial structure of the strategies.  
-We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $\s\in T_{\sigma_M}$ such that $\s\vert_{\bC}=qa$.
+We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $s\in T_{\sigma_M}$ such that $s\vert_{\bC}=qa$.
 
@@
   \begin{itemize}
-    \item $C[\wn]\converges n$ if and only if there exists $\s\in \sigma_C$ such that $\s\vert_{\bN}=qa$.  
+    \item $C[\wn]\converges n$ if and only if there exists $s\in \sigma_C$ such that $s\vert_{\bN}=qa$.  
     \item $C\mustconverge$ if and only if $\sigma_C$ is winning.
@@
   \begin{itemize}
-    \item For all $n\in\omega$, there exists $\s\in\sigma$ such that $\s\vert_{\bN_2}=qn$ if and only if there exists $\t\in\tau$ such that $\t\vert_{\bN_2}=qn$.  
+    \item For all $n\in\omega$, there exists $s\in\sigma$ such that $s\vert_{\bN_2}=qn$ if and only if there exists $t\in\tau$ such that $t\vert_{\bN_2}=qn$.  
     \item $\sigma$ is winning if and only if $\tau$ is winning.
@@
 This definition gives a rather minimal condition on the morphism $\top_\bN$ that ensures that it behaves as it should when substituted into functions $\bN \to \bN$.
-For example, our category $\G_{ND}$ is a sensible game semantics of PCF with countable nondeterminism, as is the Tsukada-Ong category $\G_{TO}$.
+Our category $\G_{ND}$, for example, is a sensible game semantics of PCF with countable nondeterminism, as is the Tsukada-Ong category $\G_{TO}$.
 
-Using this condition and Lemma \ref{lem:pcf-soundness-lemma}, it is easy to prove the following version of adequacy, which is sufficient for the purpose of proving full abstraction.
+Using this condition and Lemma \ref{lem:pcf-soundness-lemma}, it is easy to prove the following version of adequacy, which is sufficient for the purpose of proving full abstraction, for all such models.
 
 \begin{theorem}[Adequacy for nondeterministic PCF]
-  Let $\C$ be a sensible model of nondeterministic PCF, and define $\deno -$ to be given by the functor $J$ and the morphism $\top_\bN$ in the obvious way.
+  Let $\C$ be a sensible model of nondeterministic PCF, and define an interpretation $\deno -$ of nondeterministic PCF in $\C$ to be given by the functor $J$ and the morphism $\top_\bN$ in the obvious way.
 
@@
 The missing ingredient is a universality result for that model.  
-Tsukada and Ong prove compact definability from first principles, rather than using a factorization result, and it is not immediate how one defines a recursive element of their model.  
+Tsukada and Ong prove compact definability from first principles, rather than using a factorization result, and it is not immediately clear how one defines a recursive element of their model.  
 Nevertheless, we can have some confidence that such a result is possible, allowing our results to be carried over to stateless languages.
 
-It would be interesting to see whether our adequacy proof can be applied to effects other than nondeterminism; although most effects do not engender a failure of continuity in the same way, a similar approach could help us use an adequacy result from one language to prove adequacy for another language, rather than proving it from first principles each time.
+It would be interesting to see whether our adequacy proof can be applied to effects other than nondeterminism: although most effects do not engender a failure of continuity in the same way, a similar approach could help us use an adequacy result from one language to prove adequacy for another language, rather than having to prove it from first principles each time.
 
 Lastly, our proof has thrown more light on the important relation between nondeterminism and state.  
-As we have discussed, stateful languages (and visible strategies) pose fewer problems for modelling nondeterminism than do stateless languages (and innocent strategies), but the fact that we needed to use the stateful structure of the language in our proof of Lemma \ref{lem:soundness-lemma} suggests that there is a deeper relationship between the two, which we should explore in future work.
+As we have discussed, stateful languages (and visible strategies) pose fewer problems for modelling nondeterminism than do stateless languages (and innocent strategies).  
+However, the fact that we needed to use the stateful structure of the language in our proof of Lemma \ref{lem:soundness-lemma} suggests that there is a deeper relationship between the two, which we should explore in future work.
 

### 2018-04-07 cones/paper/lipics-v2018-authors/cones.tex
Reworked the paper for CSL.

--- 2018-01-31 cones/paper/cones.tex
@@
- %% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
-\documentclass[sigplan,9pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For double-blind review submission, w/ CCS and ACM Reference
-%\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true}
-%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
-%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-%% For single-blind review submission, w/ CCS and ACM Reference
-%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true}
-%% For final camera-ready submission, w/ required CCS and ACM Reference
-%\documentclass[sigplan,10pt]{acmart}\settopmatter{}
+\documentclass[a4paper,UKenglish]{lipics-v2018}
+%This is a template for producing LIPIcs articles. 
+%See lipics-manual.pdf for further information.
+%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
+%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
+% for section-numbered lemmas etc., use "numberwithinsect"
 
-%% Conference information
-%% Supplied to authors by publisher for camera-ready submission;
-%% use defaults for review submission.
-\acmConference[LICS'18]{ACM/IEEE Symposium on Logic in Computer Science}{9-12 July, 2018}{Oxford, UK}
-\acmYear{2018}
-\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
+\usepackage{microtype}%if unwanted, comment out or use option "draft"
 
-%% Copyright information
-%% Supplied to authors (based on authors' rights management selection;
-%% see authors.acm.org) by publisher for camera-ready submission;
-%% use 'none' for review submission.
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\copyrightyear{2017}           %% If different from \acmYear
+%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
 
-%% Bibliography style
-\bibliographystyle{ACM-Reference-Format}
-%% Citation style
-\citestyle{acmauthoryear}  %% For author/year citations
-%\citestyle{acmnumeric}     %% For numeric citations
-%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
-                            %% sorting of references within a single citation;
-                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
-                            %% rendered as [14,5,2] rather than [2,5,14].
-%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
-                            %% compression of sequential references within a
-                            %% single citation;
-                            %% e.g., \cite{Baker12,Baker14,Baker16}
-                            %% rendered as [2,3,4] rather than [2-4].
+\bibliographystyle{plainurl}% the recommnded bibstyle
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Note: Authors migrating a paper from traditional SIGPLAN
-%% proceedings format to PACMPL format must update the
-%% '\documentclass' and topmatter commands above; see
-%% 'acmart-pacmpl-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{A Fully Abstract Game Semantics for Countable Nondeterminism}
 
-\usepackage{balance}
+\titlerunning{Game Semantics for Countable Nondeterminism}
 
-%% Some recommended packages.
-%\usepackage{booktabs}   %% For formal tables:
-                        %% http://ctan.org/pkg/booktabs
-%\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
-                        %% http://ctan.org/pkg/subcaption
-\let\NOTARTICLE=1
-\let\FEWFONTS=1
-\let\BEAMER=1
-\let\G\undefined
-\let\C\undefined
-\let\W\undefined
-\let\U\undefined
-\let\E\undefined
-\input{../../common/preamble}
-\renewcommand{\dv}{{\lightning}}
-\newcommand{\oracle}{{\textsf{oracle}}}
+\author{W.
+John Gowers}{Computer Science Department, University of Bath\\{Claverton Down Road, Bath.
+BA2 7QY, United Kingdom}}{W.J.Gowers@bath.ac.uk}{https://orcid.org/0000-0002-4513-9618}{funded by EPSRC grant EP/K018868/1}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
+
+\author{James D. Laird}{Department of Computer Science, University of Bath\\{Claverton Down Road, Bath. BA2 7QY, United Kingdom}}{J.D.Laird@bath.ac.uk}{}{}
+
+\authorrunning{W.J. Gowers and J.D. Laird}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+
+\Copyright{W. John Gowers and James D. Laird}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
+E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
+
+\keywords{semantics, nondeterminism, games and logic}%mandatory
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+
+\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{This material is based on work supported by the EPSRC under Grant No.~EP/K018868/1.  
+I am grateful to Martin Hyland for our conversation that helped me to develop some of this material.}%optional
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+%\nolinenumbers %uncomment to disable line numbering
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% AUTHOR MACROS                                      %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{cmll}
+\usepackage{mathtools}
+\usepackage{IEEEtrantools}
+\usepackage{mathpartir}
+\usepackage{pbox}
+\usepackage{stmaryrd}
+
+\theoremstyle{plain}
+\newtheorem{proposition}[theorem]{Proposition}
+
+\newcommand{\nat}{{\mathtt{nat}}}
+\newcommand*\from{\colon}
+\newcommand{\Y}{\mathbf{Y}}
+\newcommand{\opto}{\longrightarrow}
+\newcommand{\n}{{\mathtt{n}}}
+\newcommand{\IfO}{{\mathtt{If0}\;}}
+\newcommand{\suc}{{\mathtt{suc\;}}}
+\newcommand{\pred}{{\mathtt{pred\;}}}
+\newcommand{\0}{{\mathtt{0}}}
+\newcommand{\com}{{\mathtt{com}}}
+\newcommand{\skipp}{{\mathsf{skip}}}
+\newcommand{\neww}{{\mathsf{new}}}
+\newcommand{\mkvar}{{\mathsf{mkvar}\;}}
+\newcommand{\deref}{\texttt{@}}
+\newcommand{\ia}[2]{\langle #1 , #2 \rangle}
+\newcommand{\stup}[3]{\langle #1 \mid #2 \mapsto #3 \rangle}
+\newcommand{\Var}{{\mathtt{Var}}}
+\newcommand{\new}{{\mathtt{new}}}
+\newcommand{\case}{{\mathtt{case}}}
+\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
+\newcommand{\bN}{\mathbb{N}}
+\newcommand{\bC}{\mathbb{C}}
+\newcommand{\deno}[1]{\left\llbracket#1\right\rrbracket}
+\newcommand{\converges}{\Downarrow}
+\newcommand{\mustconverge}{\converges^{\text{must}}}
+\newcommand{\Iflt}{\mathtt{If{<}\;}}
+\newcommand{\Ifgt}{\mathtt{If{>}\;}}
+\newcommand{\inr}{{\mathsf{inr}}}
+\newcommand{\inl}{{\mathsf{inl}}}
+\newcommand{\lmam}{\sqsubseteq_{m\&m}}
+\newcommand{\emam}{\equiv_{m\&m}}
+\newcommand{\lst}{\lesssim}
+\newcommand{\rulename}[1]{\LeftTirNameStyle{#1}}
+\newcommand{\ts}{{\;\vdash}}
+\newcommand{\nts}{{\;\not\vdash}}
+\newcommand{\OP}{\{O,P\}}
+\newcommand{\QA}{\{Q,A\}}
+\DeclareMathOperator{\id}{id}
+\DeclareMathOperator{\pr}{pr}
+\newcommand{\suchthat}{\;\colon\;}
+\newcommand{\varsuchthat}{\;\mid\;}
+\newcommand{\esuchthat}{\;.\;}
+\newcommand{\emptyplay}{\epsilon}
+\newcommand{\tensor}{\otimes}
+\renewcommand{\implies}{\multimap}
+\newcommand{\prefix}{\sqsubseteq}
+\newcommand{\s}{\mathfrak s}
+\newcommand{\C}{{\mathcal{C}}}
+\newcommand{\G}{\mathcal G}
+\DeclareMathOperator{\Int}{int}
+\newcommand{\dv}{{\lightning}}
+\DeclareMathOperator{\pocl}{pocl}
+\newbox\gnBoxA
+\newdimen\gnCornerHgt
+\setbox\gnBoxA=\hbox{$\ulcorner$}
+\global\gnCornerHgt=\ht\gnBoxA
+\newdimen\gnArgHgt
+\def\pv #1{%
+    \setbox\gnBoxA=\hbox{$#1$}%
+    \gnArgHgt=\ht\gnBoxA%
+    \ifnum     \gnArgHgt<\gnCornerHgt \gnArgHgt=0pt%
+    \else \advance \gnArgHgt by -\gnCornerHgt%
+    \fi \raise\gnArgHgt\hbox{$\ulcorner$} \box\gnBoxA %
+    \raise\gnArgHgt\hbox{$\urcorner$}}
+\newcommand{\code}{\mathsf{code}}
+\newcommand{\Det}{\mathsf{Det}}
+\newcommand{{\cell}}{{\mathsf{cell}}}
+\newcommand{\oes}{\sim}
 
@@
 
-%% Title information
-\title{A Fully Abstract Game Semantics for Countable Nondeterminism}         %% [Short Title] is optional;
-                                        %% when present, will be used in
-                                        %% header instead of Full Title.
-%\titlenote{with title note}             %% \titlenote is optional;
-                                        %% can be repeated if necessary;
-                                        %% contents suppressed with 'anonymous'
-%\subtitle{Subtitle}                     %% \subtitle is optional
-%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-                                        %% can be repeated if necessary;
-                                        %% contents suppressed with 'anonymous'
+\maketitle
 
-%% Author information
-%% Contents and number of authors suppressed with 'anonymous'.
-%% Each author should be introduced by \author, followed by
-%% \authornote (optional), \orcid (optional), \affiliation, and
-%% \email.
-%% An author may have multiple affiliations and/or emails; repeat the
-%% appropriate command.
-%% Many elements are not rendered, but should be provided for metadata
-%% extraction tools.
-
-%% Author with single affiliation.
-\author{W. J. Gowers}
-%\authornote{with author1 note}          %% \authornote is optional;
-                                        %% can be repeated if necessary
-\orcid{0000-0002-4513-9618}             %% \orcid is optional
-\affiliation{
-  \department{Department of Computer Science}              %% \department is recommended
-  \institution{University of Bath}            %% \institution is required
-  \streetaddress{Claverton Down Road}
-  \city{Bath}
-  \postcode{BA2 7QY}
-  \country{United Kingdom}                    %% \country is recommended
-}
-\email{W.J.Gowers@bath.ac.uk}
-
-\author{James Laird}
-%\authornote{with author1 note}          %% \authornote is optional;
-                                        %% can be repeated if necessary
-\orcid{0000-0002-4513-9618}             %% \orcid is optional
-\affiliation{
-  \department{Department of Computer Science}              %% \department is recommended
-  \institution{University of Bath}            %% \institution is required
-  \streetaddress{Claverton Down Road}
-  \city{Bath}
-  \postcode{BA2 7QY}
-  \country{United Kingdom}                    %% \country is recommended
-}
-\email{J.D.Laird@bath.ac.uk}
-
-%% Abstract
-%% Note: \begin{abstract}...\end{abstract} environment must come
-%% before \maketitle command
 \begin{abstract}
@@
   Lastly, we prove full abstraction for the model; because of the lack of continuity, we cannot deduce this from definability of compact elements in the usual way, and we have to use a stronger universality result instead.
-  We discuss how our techniques may also be applied to Tsukada and Ong's model of PCF with finite nondeterminism, yielding an alternative proof of computational adequacy.
+  We discuss how our techniques may also be applied to yield a proof of computational adequacy for a model of PCF with unbounded nondeterminism, based on the construction by Hyland and Ong.
 \end{abstract}
-
-%% 2012 ACM Computing Classification System (CSS) concepts
-%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10003752.10010124.10010131.10010133</concept_id>
-<concept_desc>Theory of computation~Denotational semantics</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[300]{Theory of computation~Denotational semantics}
-%% End of generated code
-
-%% Keywords
-%% comma separated list
-\keywords{semantics, nondeterminism, games and logic}  %% \keywords are mandatory in final camera-ready submission
-
-%% \maketitle
-%% Note: \maketitle command must come after title commands, author
-%% commands, abstract environment, Computing Classification System
-%% environment and commands, and keywords command.
-\maketitle
 
@@
 If $\wn\from\nat$ is an unbounded nondeterminism machine, then function application to $\wn$ is not continuous; indeed, ${<}m\;\wn$ always has the possibility of divergence -- since $\wn$ may evaluate to $m+1$, say.
-But $(\lambda k.k;\0);\wn$ always converges to $0$.
+But $(\lambda k.k;\0)\;\wn$ always converges to $0$.
 
@@
 A closely connected problem with unbounded nondeterminism is that it leads to terms that may be distinguished only by their \emph{infinitary} behaviour.  
-A program that flashes a light and unboundedly nondeterministic number of times cannot reliably be distinguished in finite time from a program that flashes that light forever: however long we watch the light flash, there is always a chance that it will stop at some point in the future.
+A program that flashes a light an unboundedly nondeterministic number of times cannot reliably be distinguished in finite time from a program that flashes that light forever: however long we watch the light flash, there is always a chance that it will stop at some point in the future.
 From a game semantics point of view, this corresponds to the observation that it is not sufficient to consider sets of finite plays in order to define strategies: we must consider infinite sequences of moves as well.
@@
   \label{fig:ia-os}
-\end{figure*}
+\end{figure*}/
 
@@
 
-First, we define a Felleisen-style \emph{evaluation context} $E$ inductively as follows.
+First, we define a Felleisen-style notion of \emph{evaluation context} $E$ inductively as follows.
 \begin{IEEEeqnarray*}{RCL}
   E & \Coloneqq & - \mid E M \mid \suc E \mid \pred E \mid \IfO E \mid \\
-  && E;\blank \mid E \coloneqq \blank \mid \deref E \blank \mid \mkvar E \mid \new_T E
+  && E;\blank \mid E \coloneqq \blank \mid \deref E \mid \mkvar E \mid \new_T E
 \end{IEEEeqnarray*}
@@
 
+We shall assume that our arenas are \emph{enumerated}; that is, that the set $M_A$ comes equipped with a partial surjection $\bN\to M_A$. 
+We assume that this enumeration is defined on the flat arenas and extended to the connectives in a natural way.
+
 Given an arena $A$, a \emph{justified string} in $A$ is a sequence $s$ of moves in $A$, together with \emph{justification pointers} that go from move to move in the sequence.  
@@
 If $m$ and $n$ are moves in $s$ such that there is a chain of justification pointers leading from $m$ back to $n$, we say that $n$ \emph{hereditarily justifies} $m$.  
-Given some set $S$ of initial moves in $s$, we write $s\vert_S$ for the subsequence of $s$ made up of all those moves that are hereditarily justified by some move in $S$.
+Given some set $S$ of initial moves in $s$, we write $s\vert_S$ for the subsequence of $s$ made up of all those moves hereditarily justified by some move in $S$.
 
@@
 
-This works very satisfactorily for finite nondeterminism, but not at all for countable nondeterminism.  
+Harmer and McCusker's approach works very satisfactorily for finite nondeterminism, but not at all for countable nondeterminism.  
 To see why, consider the term
 \[
-  N = \Y_{\nat\to\nat\to\nat}(\lambda g.\lambda m n.\IfO m\;\0\;n;(g\;(\pred m)\;n))\wn
+  N = \Y_{\nat\to\nat\to\nat}(\lambda g.\lambda m n.\IfO m\;\0\;n;(g\;(\pred m)\;n))\wn\,.
   \]
@@
 
-The games in our model will be the same as those that we considered in the last section, but our definition of a strategy will change.
+The games in our model are the same as those that we considered in the last section, but our definition of a strategy will change.
 
@@
 Given an arena $A$, we define an \emph{infinite justified string} in the obvious way.  
-We define $\overline{P_A}$ to be $P_A$ together with the set of all those infinite justified sequences that have all finite prefixes in $P_A$.
+We say that such a string is \emph{recursive} if it corresponds, via the enumeration on $M_A$ to a recursive function $\bN\to\bN$.
+
+We define $\overline{P_A}$ to be $P_A$ together with the set of all those recursive infinite justified sequences that have all finite prefixes in $P_A$.
+
+We deliberately ignore any non-recursive infinitary behaviours, since these cannot be detected by computable contexts.
 
@@
 
-We call such a sequence $\s$ a \emph{legal interaction} if $\s\vert_{A,B}\in P_{A\implies B}$, $\s\vert_{B,C}\in P_{B\implies C}$ and $\s\vert_{A,C}\in P_{A\implies C}$.  
+We call the sequence $\s$ a \emph{legal interaction} if $\s\vert_{A,B}\in P_{A\implies B}$, $\s\vert_{B,C}\in P_{B\implies C}$ and $\s\vert_{A,C}\in P_{A\implies C}$.  
 We write $\Int_\infty(A,B,C)$ for the set of (possibly infinite) legal interactions between $A$, $B$ and $C$.
@@
 \[
-  D_\sigma\dv D_\tau = \left\{\s\in \Int_\infty(A,B,C)\;\middle|\; \mbox{\pbox{\textwidth}{\textbf{either} $\s\vert_{A,B}\in D_\sigma$\\ \hspace*{12pt}and $s\vert_{B,C}\in T_\tau$ \\ \textbf{or} $\s\vert_{A,B}\in T_\sigma$ \\\hspace*{12pt}and $s\vert_{B,C}\in D_\tau$}}\right\}\,.
+  D_\sigma\dv D_\tau = \left\{\s\in \Int_\infty(A,B,C)\;\middle|\; \mbox{\pbox{\textwidth}{\textbf{either} $\s\vert_{A,B}\in D_\sigma$ and $s\vert_{B,C}\in T_\tau$ \\ \textbf{or} $\s\vert_{A,B}\in T_\sigma$ and $s\vert_{B,C}\in D_\tau$}}\right\}\,.
   \]
@@
   Let $\sigma$ be a strategy for a game $A$.  
-  We say that $\sigma$ is \emph{complete} if $T_\sigma=\overline{T_\sigma}$; i.e., $T_\sigma$ contains an infinite position $s$ if it contains every finite prefix of $s$.  
+  We say that $\sigma$ is \emph{complete} if $T_\sigma=\overline{T_\sigma}$; i.e., $T_\sigma$ contains an recursive infinite play $s$ if it contains every finite prefix of $s$.  
 \end{definition}
@@
 
-From now on, we will use `strategy' to mean \emph{locally complete strategy}.
+Henceforth, we use `strategy' to mean \emph{locally complete strategy}.
 
@@
 
-In fact, the proof of associativity of composition is pretty much the same in our model as it is in any other model of game semantics.  
-However, it is worth saying a few words about it, since the model obtained by naively extending the Harmer-McCusker model to unbounded nondeterminism does not have an associative composition.  
+In fact, the proof of associativity of composition is pretty much the same in our model as it is in any other model of game semantics if we treat infinite plays the same as finite ones.
+However, it is worth saying a few words about associativity, since the model obtained by naively extending the Harmer-McCusker model to unbounded nondeterminism does not have an associative composition.
 The point is that there is not really a problem with associativity itself, but rather that this naive model gives the wrong result for the composition of strategies with infinite nondeterminism.
@@
 
-\subsection{Enumerated games and recursive strategies}
+\subsection{Recursive strategies}
 
@@
 
-In order to define recursively presentable strategies, we need to work with \emph{enumerated games}; i.e., games where the set of moves comes with an enumeration to the natural numbers.  
-Clearly our base games $\bN$ and $\bC$ can be enumerated, as can the tensor product, linear implication, exponential and product of games.  
-We can then define a \emph{recursive} strategy to be one that is recursively presentable with respect to that enumeration of moves.
+If $\sigma$ is a complete strategy for a game $A$, we say that $\sigma$ is \emph{recursive} if $T_\sigma\cap P_A$ and $D_\sigma\cap P_A$ are recursively enumerable subsets of $\omega^\omega$ (under the enumeration of $M_A$).
+Here, we have thrown away the infinite plays in $T_\sigma$ and $D_\sigma$, but we do not lose any information because $\sigma$ is complete.
 
-We shall tacitly assume that the games in our category $\G_{ND}$ come with an enumeration so that we can reason about recursive strategies later.  
-For any game that is the denotation of an Idealized Algol type, this enumeration will be as we have just described.
+If $\sigma$ is locally complete, we say that $\sigma$ is \emph{recursive} if $\sigma$ is the union of complete strategies $\sigma_1,\sigma_2,\cdots$, where the $\sigma_i$ are recursive and the map $i\mapsto \sigma_i$ is a recursive function $\bN \to (\bN \to \bN) \to 2$.
 
-The relevant result pertaining to recursive strategies is as follows.
+In the case that $\sigma$ is recursive and \emph{deterministic}, we can prove the following result.
 
 \begin{proposition}[Recursive Universality for Idealized Algol]
-  Let $S$ be an Idealized Algol type and let $\sigma\from \deno S$ be a recursive strategy.  
+  \label{prop:ia-universality}
+  Let $S$ be an Idealized Algol type and let $\sigma\from \deno S$ be a recursive deterministic strategy.  
   Then there exists a term $M\from S$ of Idealized Algol such that $\sigma=\deno M$.
@@
 \begin{proof}
-  This follows from the corresponding results for PCF, together with the \emph{innocent factorization} result of \cite{SamsonGuyIAPassive}.  
-  See also \cite{MurawskiUniversality}.
+  We use the `innocent factorization' result of \cite{SamsonGuyIAPassive} to reduce to the innocent case and the proceed in a manner similar to the argument used in \cite{MurawskiUniversality}.
 \end{proof}
+
+Note that Proposition \ref{prop:ia-universality} is sharper than the result in \cite{hoPcf}, which only proves that every recursive strategy may be defined \emph{up to observational equivalence}.  
+Idealized Algol allows us to store variables and then use them multiple times without having to read them again, which allows us to to define all recursive visible strategies exactly.
+Compare with \cite{MurawskiUniversality}, which proves a similar result for \emph{call-by-value} PCF.
 
@@
 \subsection{Denotational Semantics}
+\label{sec:denotational-semantics}
 
@@
   \oc \bN \xrightarrow{\deno{\lambda n.C[n]}}
-  \deno{T}
+  \deno{T}\,.
   \]
@@
 
-  Now let $\pi$ be a finite evaluation $\ia s {C[\wn]}$ that converges to $\skipp$.  
+  Now let $\pi$ be a finite evaluation of $\ia s {C[\wn]}$ that converges to $\skipp$.  
   Encode $\pi$ as a sequence $n_1,\dots,n_k$.  
@@
 
-From this result, we can prove the converse, which we will also need.
+From the proof of this result, we can establish the converse, which we will also need.
 
@@
 
-We can now prove our computational adequacy result.
+Note that these last two lemmas may be cast entirely in the model of Idealized Algol given in \cite{SamsonGuyIAPassive}, since they only refer to the denotations of deterministic terms.  
+We can therefore prove a more general version of Proposition \ref{prop:adequacy}.
 
-\begin{proof}[Proof of Proposition \ref{prop:adequacy}]
-  We prove this for must convergence; the corresponding proof for may convergence is very similar.
+\begin{definition}
+  Let $\sigma\from A\to B$ be a (deterministic) strategy.  
+  We say that $\sigma$ is \emph{winning} if every play in $\sigma$ may be extended to a play that ends with a $P$-move in $B$; i.e., $\sigma$ is total and contains no sequences having an infinite tail in $A$.
+\end{definition}
 
-  Let $M=C[\wn]$ be a closed term, where $C$ is a deterministic multi-holed context.  
-  Then, by Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse}, we see that $M\not\mustconverge$ if and only if there exists some total deterministic $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$.
-  By examining the definition of composition, we see that this is the case if and only if $D_{\deno M}=D_{\top_N;\sigma_M}\ne\emptyset$.
-\end{proof}
+This definition is intimately connected to Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} in the following sense: if $\sigma_M\from\bN\to\bC$ is a strategy, then there exists some $\sigma_M$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma$ is not winning.
+
+The following is now an easy corollary of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse}.
+
+\begin{corollary}
+  \label{cor:adequacy}
+  Let $\C$ be a Cartesian closed category that admits a faithful Cartesian functor $J\from \G_{vis}^\oc\hookrightarrow\C$.
+  Let $\top_{\bN}\from 1 \to J\bN$ be a morphism in $\C$ and use it to extend the semantics of Idealized Algol of $\G_{vis}^\oc$ to a semantics of nondeterministic Idealized Algol, as in Section \ref{sec:denotational-semantics}.
+
+  Suppose we have two predicates $\converges\skipp$ and $\mustconverge$ defined on strategies $1\to J\bC$ in $\C$ satisfying the following rules for all strategies $\sigma\from \bN\to\bC$ in $\G_{vis}^\oc$.
+  \begin{itemize}
+    \item $(\top_{\bN};J\sigma)\converges\skipp$ if and only if there is some $s\in \sigma$ such that $s\vert_{\bC}=qa$.
+    \item $(\top_{\bN};J\sigma)\mustconverge$ if and only if $\sigma$ is winning.
+  \end{itemize}
+  Then the semantics of nondeterministic Idealized Algol inside $\C$ is adequate in the following sense.
+  For all terms $M$ of nondeterministic Idealized Algol of type $\com$:
+  \begin{itemize}
+    \item $M\converges\skipp$ if and only if $\deno{M}\converges\skipp$.
+    \item $M\mustconverge$ if and only if $\deno{M}\mustconverge$.
+  \end{itemize}
+\end{corollary}
+
+We can then deduce Proposition \ref{prop:adequacy} by verifying that the following predicates on strategies $\sigma\from 1 \to \bC$ in the category $\G_{ND,vis}^\oc$ satisfy the conditions of Corollary \ref{cor:adequacy}.
+\begin{itemize}
+  \item $\sigma\converges\skipp$ $\Leftrightarrow$ $qa\in T_\sigma$.
+  \item $\sigma\mustconverge$ $\Leftrightarrow$ $D_\sigma=\emptyset$.
+\end{itemize}
+
+\subsection{Intrinsic Equivalence and Soundness}
 
@@
 We then say that a strategy $\sigma$ is \emph{divergence-complete} if every unreliable point of $\sigma$ is contained in $D_\sigma$.  
-Every strategy $\sigma$ can clearly be extended to a minimal divergence-complete strategy $\text{dc}(\sigma)$; Murawski's explicit characterization of the intrinsic collapse \cite{MurawskiIntrinsic}, which may be applied to our model, essentially says that $\sigma\oes\tau$ if and only if $\text{dc}(\sigma)=\text{dc}(\tau)$.
+Every strategy $\sigma$ can clearly be extended to a minimal divergence-complete strategy $\text{dc}(\sigma)$; Murawski's explicit characterization of the intrinsic collapse \cite{MurawskiIntrinsic}, which may be applied to our model, essentially says that $\sigma\oes\tau$ if and only if $\sigma$ and $\tau$ have the same \emph{complete} plays and $\text{dc}(\sigma)=\text{dc}(\tau)$.
+
+An important fact about intrinsic equivalence is the following Lemma, whose proof makes use of the fact that the infinite plays in our strategies are given by recursive functions.
+
+\begin{lemma}
+  \label{lem:ie-recursive}
+  Let $\sigma,\tau$ be strategies for a game $A$.  
+  Suppose that $\sigma;\alpha=\tau;\alpha$ for all \emph{recursive} strategies $\alpha\from A\to\bC$.  
+  Then $\sigma\oes\tau$.
+\end{lemma}
 
@@
 
-By our nondeterministic factorization result, we know that $\sigma=\top_\bN;\Det(\sigma)$, where $\Det(\sigma)$ is a deterministic strategy.  
+By our nondeterministic factorization result, we know that $\sigma=\top_\bN;\Det(\sigma)$, where $\Det(\sigma)$ is a deterministic recursive strategy.  
 By universality for $\G_{D,vis}^\oc$, we know that $\Det(\sigma)=\deno{M}$ for some closed term $M\from S \to T$.  
@@
   Let $A=\deno T$.  
-  Suppose that $\deno{M}\not{\oes}\deno{N}$; so there is some strategy $\alpha\from A\to\bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.  
-  We can clearly choose $\alpha$ to be recursively presentable; by universality, we have $\alpha=\deno{P}$ for some closed term $P$ of type $T\to\com$.  
+  Suppose that $\deno{M}\not\oes\deno{N}$; so there is some strategy $\alpha\from A\to\bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.  
+  By Lemma \ref{lem:ie-recursive}, we can choose $\alpha$ to be recursively presentable; by universality, we have $\alpha=\deno{P}$ for some closed term $P$ of type $T\to\com$.  
   Then we have $\deno{M};\deno{P}\ne\deno{N};\deno{P}$; by computational adequacy, it follows that $M\not{\emam} N$.
@@
 
-\section{Nondeterministic PCF}
+\section{Conclusion}
 
@@
 
-Hyland and Ong \cite{hoPcf} gave a model of PCF using games and \emph{innocent strategies}.
-If $sab\in P_A$, where $b$ is a $P$-move such that $sab$ is visible at $b$, and if $ta\in P_A$ is such that $\pv{sa}=\pv{ta}$, then it is possible to show that there is a unique way to extend $ta$ by $b$ such that $\pv{sab}=\pv{tab}$.
-We will abuse notation and refer to this play as $tab$, omitting the justification pointer from $b$.
+The principal difficulties in modelling nondeterministic stateless languages were made by Tsukada and Ong in \cite{TsukadaSheaves}, where they discovered how to define an innocent nondeterministic strategy by retaining `branching time information' in strategies.
+An additional benefit of the retention of branching time information is that we no longer need to keep track of infinite plays in order to model unbounded nondeterminism.  
+The model given in \cite{TsukadaSheaves} is not sound for must-equivalence, but the authors make the claim that it their model may be easily modified to yield a model that \emph{is} sound for this type of equivalence, using the same techniques from \cite{mcCHFiniteND} that we have used.
 
-If $\sigma$ is a strategy for $A$ that is deterministic and $P$-visible, we say that $\sigma$ is \emph{innocent} if and only if whenever $sab,ta\in\sigma$ are as above, we have $tab\in\sigma$.
+However, since there is no such model in the literature at the moment, we shall have to be a bit more general in examining how our techniques can be used to model nondeterministic PCF.  
+Our main new contribution is the proof of adequacy, and our methods can be applied to PCF as well.  
+Indeed, Corollary \ref{cor:adequacy} can easily be modified to apply to PCF, even though we have used Idealized Algol terms in the proof.  
+Corollary \ref{cor:adequacy} reduces the proof of adequacy to a combinatorial check on morphisms from $\bN\to\bC$ on strategies in the well-known category $\G_{vis}^\oc$.
 
-Tsukada and Ong \cite{TsukadaSheaves}, following Harmer \cite{RusssThesis}, showed that traditional game semantics models are unsuitable for modelling \emph{nondeterministic} PCF: while the definition of \emph{visibility} of strategies can be extended to nondeterministic strategies without difficulty, innocence cannot.
+%%
+%% Bibliography
+%%
 
-Instead, they use a novel type of game semantics in which strategies are given not by sets of plays but by justified \emph{trees} whose vertices are moves.  
-The difference is subtle but important: from the point of view of countable nondeterminism it allows us to distinguish between terms that take an arbitrarily large finite number of steps to converge and terms that diverge, without needing to track infinitary information.
-For example, the denotation of our term $M$ above has an infinite branch in it, while the denotation of $N$ has infinitely many finite branches of arbitrary length.
+%% Please use bibtex,
 
-The main advantage of the tree-based model, however, is that it gives rise to a satisfactory synthetic definition of a \emph{nondeterministic innocent} strategy, based on sheaves.  
-The main contribution of their paper is not to prove full abstraction for PCF with countable nondeterminism (even though that language may be interpreted within their category), but for PCF with finite nondeterminism.
-
-Having ourselves given a fully abstract model of Idealized Algol with countable nondeterminism, we shall contribute to the process of `completing the square' by giving a sketch of how we can use our techniques to prove adequacy for the Tsukada-Ong model of PCF with countable nondeterminism.
-A side-effect of this will be to give an alternative proof of adequacy for their model of PCF with finite nondeterminism.
-
-The first observation to make is that our Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} are not really statements about the category $\G_{ND,vis}$, but about the deterministic model $\G_{D,vis}$.
-
-For example, the first parts of the lemmas says that if $C[-]$ is a deterministic Idealized Algol context, then $C[\wn]\converges\skipp$ if and only if there exists some total deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\deno{\lambda n.C[n]}}$.
-Although we have mentioned a term ($C[\wn]$) living in nondeterministic Idealized Algol, this can be thought of as a statement about $C[-]$ itself, and therefore as a statement about the deterministic language.
-Moreover, the strategy $\sigma$ and the denotation of $\lambda n.C[n]$ are both deterministic strategies, so we can interpret Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} as telling us something about Idealized Algol and its game semantics.
-
-We can therefore forget about our nondeterminism model, with its divergence sets and infinite plays (neither of which are part of the Tsukada-Ong model) and concentrate on the Abramsky-McCusker model of Idealized Algol.
-Note that although Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} mention $T_{\sigma;\sigma_M}$ and $D_{\sigma;\sigma_M}$, we can rephrase both of these inside the deterministic model, since the strategies involved are both deterministic.
-
-We want a version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
-Clearly, the lemma as currently stated does not hold in $\G_{inn}$, since the strategies $\sigma$ that we define are not innocent in general.
-
-Instead, we need to look at the combinatorial structure of the strategies.  
-We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $s\in T_{\sigma_M}$ such that $s\vert_{\bC}=qa$.
-
-We define a deterministic strategy $\sigma\from A \implies B$ to be \emph{winning} if it is divergence-free and if for every $O$-play $s\in T_\sigma$ there exists some $t\in T_\sigma$ such that $s\prefix t$ and $t$ ends with a move in $B$.
-
-Then for any strategy $\sigma_M$, there exists a deterministic strategy $\sigma\from\oc\bN$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma_M$ is not winning.
-
-We recover the following version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} which now applies to the interpretation of PCF in $\G_{inn}$:
-\begin{lemma}
-  Let $C[-]$ be a multi-holed context of deterministic PCF.
-  Write $\sigma_C\from\oc\bN\to\bN$ for the denotation of the term $\lambda n.C[n]$.  
-  \begin{itemize}
-    \item $C[\wn]\converges n$ if and only if there exists $s\in \sigma_C$ such that $s\vert_{\bN}=qa$.  
-    \item $C\mustconverge$ if and only if $\sigma_C$ is winning.
-  \end{itemize}
-  \label{lem:pcf-soundness-lemma}
-\end{lemma}
-
-Now we have an inclusion functor $J:\G_{inn}^\oc\hookrightarrow\G_{TO}$, where $\G_{TO}$ is the Tsukada-Ong category.  
-Since the nondeterministic oracle $\wn$ may also be interpreted as a tree-strategy $\top_{\bN}$ in $\G_{TO}$, this gives us a model of PCF with countable nondeterminism inside that category.
-
-In order to prove adequacy for this model, we are only going to use two facts about the category $\G_{TO}$.  
-The first fact is that the inclusion functor $J$ preserves the structure of the model $\G_{inn}$; i.e., it is faithful and strong monoidal.  
-The second fact will capture the properties of the morphism $\top_{\bN}\from I \to \bN$ in $\G_{TO}$.
-
-\begin{definition}
-  Let $\sigma,\tau\from\bN_1\to\bN_2$ be morphisms in $\G_{inn}^\oc$.  
-  We say that $\sigma\approx\tau$ if the following two conditions hold.
-  \begin{itemize}
-    \item For all $n\in\omega$, there exists $s\in\sigma$ such that $s\vert_{\bN_2}=qn$ if and only if there exists $t\in\tau$ such that $t\vert_{\bN_2}=qn$.  
-    \item $\sigma$ is winning if and only if $\tau$ is winning.
-  \end{itemize}
-\end{definition}
-
-\begin{definition}
-  We say that a Cartesian closed category $\C$ is a \emph{sensible game semantics of PCF with countable nondeterminism} if there is a strong monoidal functor $J\from\G_{inn}^\oc\to\C$ and a morphism $\top_{\bN}\from 1 \to J(\bN)$ in $\C$ such that for all $\sigma,\tau\from\bN\to\bN$ in $\G_{inn}^\oc$, we have
-  \[
-    \top_\bN;J(\sigma)=\top_\bN;J(\tau)
-    \]
-  if and only if $\sigma\approx\tau$.  
-\end{definition}
-
-This definition gives a rather minimal condition on the morphism $\top_\bN$ that ensures that it behaves as it should when substituted into functions $\bN \to \bN$.
-Our category $\G_{ND}$, for example, is a sensible game semantics of PCF with countable nondeterminism, as is the Tsukada-Ong category $\G_{TO}$.
-
-Using this condition and Lemma \ref{lem:pcf-soundness-lemma}, it is easy to prove the following version of adequacy, which is sufficient for the purpose of proving full abstraction, for all such models.
-
-\begin{theorem}[Adequacy for nondeterministic PCF]
-  Let $\C$ be a sensible model of nondeterministic PCF, and define an interpretation $\deno -$ of nondeterministic PCF in $\C$ to be given by the functor $J$ and the morphism $\top_\bN$ in the obvious way.
-
-  Let $M,N\from\nat$ be two terms of nondeterministic PCF.  
-  Suppose that for all $n\in\omega$, $M\converges n$ if and only if $N\converges n$ and furthermore that $M\mustconverge$ if and only if $N\mustconverge$.  
-  Then $\deno{M}=\deno{N}$ in $\C$.
-\end{theorem}
-
-\section{Conclusion}
-
-% Oh ho ho ho ho!!!
-\balance
-Our last result is fairly general, and can be applied to a number of different game semantics models, including the models of concurrent games of \cite{ConcurrentHylandOngGames}.  
-The natural next step is to extend it to give a proof of full abstraction for nondeterministic PCF in the Tsukada-Ong model.  
-The missing ingredient is a universality result for that model.  
-Tsukada and Ong prove compact definability from first principles, rather than using a factorization result, and it is not immediately clear how one defines a recursive element of their model.  
-Nevertheless, we can have some confidence that such a result is possible, allowing our results to be carried over to stateless languages.
-
-It would be interesting to see whether our adequacy proof can be applied to effects other than nondeterminism: although most effects do not engender a failure of continuity in the same way, a similar approach could help us use an adequacy result from one language to prove adequacy for another language, rather than having to prove it from first principles each time.
-
-Lastly, our proof has thrown more light on the important relation between nondeterminism and state.  
-As we have discussed, stateful languages (and visible strategies) pose fewer problems for modelling nondeterminism than do stateless languages (and innocent strategies).  
-However, the fact that we needed to use the stateful structure of the language in our proof of Lemma \ref{lem:soundness-lemma} suggests that there is a deeper relationship between the two, which we should explore in future work.
-
-%% Acknowledgments
-\begin{acks}                            %% acks environment is optional
-                                        %% contents suppressed with 'anonymous'
-  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
-  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
-  %% acknowledge financial support and will be used by metadata
-  %% extraction tools.
-  This material is based upon work supported by the
-  \grantsponsor{GS501100000690}{EPSRC}
-  {http://dx.doi.org/10.13039/501100000690} under Grant
-  No.~\grantnum{GS501100000690}{EP/K018868/1}.   I am grateful to Martin Hyland for an interesting conversation that helped me develop some of this material.
-\end{acks}
-
-%% Bibliography
-\bibliography{../../common/phd_bibliography}
+\bibliography{cones}
 

### 2018-04-07 cones/paper/lipics-v2018-authors/lipics-v2018-sample-article.tex
Reworked the paper for CSL.

--- 2017-03-29 round-corner/paper/lipics-v2016-authors/lipics-v2016-sample-article.tex
@@
-\documentclass[a4paper,UKenglish]{lipics-v2016}
+\documentclass[a4paper,UKenglish]{lipics-v2018}
 %This is a template for producing LIPIcs articles. 
@@
 
-\bibliographystyle{plainurl}% the recommended bibstyle
+\bibliographystyle{plainurl}% the recommnded bibstyle
 
-% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}}
-\titlerunning{Sequoidal Categories and Transfinite Games} %optional, in case that the title is too long; the running title should fit into the top page column
+\title{Dummy title}
 
-%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
-\author[1]{William John Gowers}
-\author[2]{James Laird}
-\affil[1]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
-  \texttt{W.J.Gowers@bath.ac.uk}}
-\affil[2]{Department of Computer Science, University of Bath, Claverton Down, Bath.  BA2 7AY.  United Kingdom\\
-  \texttt{jiml@cs.bath.ac.uk}}
-\authorrunning{W.\,J. Gowers and J. Laird} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+\titlerunning{Dummy short title}%optional, please use if title is longer than one line
 
-\Copyright{William John Gowers and James Laird}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+\author{John Q.
+Public}{Dummy University Computing Laboratory\\{[Address, Country]}}{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{[funding]}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
 
-\subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
-\keywords{Game semantics, Linear logic, Transfinite games, Sequoid operator, Exponentials}% mandatory: Please provide 1-5 keywords
-% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Joan R. Public}{Department of Informatics, Dummy College\\{[Address, Country]}}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}
+
+\authorrunning{J.Q. Public and J.R. Public}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'
+
+\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
+
+\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
+E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
+
+\keywords{Dummy keyword}%mandatory
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+
+\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{I want to thank \dots}%optional
 
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Acces}
+\EventEditors{John Q. Open and Joan R. Access}
 \EventNoEds{2}
@@
 \ArticleNo{23}
-% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\nolinenumbers %uncomment to disable line numbering
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \item Use pdflatex and an up-to-date LaTeX system.
-\item Use further LaTeX packages only if required. Avoid usage of packages like \verb+enumitem+, \verb+enumerate+, \verb+cleverref+. Keep it simple, i.e. use as few additional packages as possible.
+\item Use further LaTeX packages only if required. Avoid usage of packages like \verb+enumitem+, \verb+paralist+, \verb+cleverref+. Keep it simple, i.e. use as few additional packages as possible.
+\item  The \texttt{enumerate} package is preloaded, so you can use
+ \verb+\begin{enumerate}[(a)]+ or the like.
 \item Add custom made macros carefully and only those which are needed in the article (i.e., do not simply add your convolute of macros collected over the years).
@@
 \item Provide full author names (especially with regard to the first name) in the \verb+\author+ macro and in the \verb+\Copyright+ macro.
-\item Fill out the \verb+\subjclass+ and \verb+\keywords+ macros. For the \verb+\subjclass+, please refer to the ACM classification at \url{http://www.acm.org/about/class/ccs98-html}.
+\item Provide only one author per \verb+\author+ macro, even if two or more authors have the same affiliation.
+\item Fill out the \verb+\subjclass+ and \verb+\keywords+ macros. For the \verb+\subjclass+, please refer to the ACM classification at \url{https://www.acm.org/publications/class-2012}.
+\item If you refer to a longer version of the paper (``full version''), please make sure to provide a persistent URL, e.g., at arXiv.
+Please  mention this full version using the \verb+\relatedversion+ macro.
 \item Take care of suitable linebreaks and pagebreaks. No overfull \verb+\hboxes+ should occur in the warnings log.
@@
 ``Self-made'' sectioning commands (for example, \verb+\noindent{\bf My+ \verb+subparagraph.}+ will be removed and replaced by standard LIPIcs style sectioning commands.
-\item Do not alter the spacing of the  \verb+lipics-v2016.cls+ style file. Such modifications will be removed.
+\item Do not alter the spacing of the  \verb+lipics-v2018.cls+ style file. Such modifications will be removed.
 \item Do not use conditional structures to include/exclude content. Instead, please provide only the content that should be published -- in one file -- and nothing else.
 \item Remove all comments, especially avoid commenting large text blocks and using \verb+\iffalse+ $\ldots$ \verb+\fi+ constructions.
-\item Keep the standard style (\verb+plainurl+) for the bibliography as provided by the\linebreak \verb+lipics-v2016.cls+ style file.
-\item Use BibTex and provide exactly one BibTex file for your article.
-The BibTex file should contain only entries that are referenced in the article.
-Please make sure that there are no errors and warnings with the referenced BibTex entries.
+\item Keep the standard style (\verb+plainurl+) for the bibliography as provided by the\linebreak \verb+lipics-v2018.cls+ style file.
+\item Use BibTex and provide exactly one BibTex file for your article. Please make sure that there are no errors and warnings with the referenced BibTex entries.
 \item Use a spellchecker to get rid of typos.
-\item A manual for the LIPIcs style is available at \url{http://drops.dagstuhl.de/styles/lipics-v2016/lipics-v2016-authors/lipics-v2016-manual.pdf}.
+\item A manual for the LIPIcs style is available at \url{http://drops.dagstuhl.de/styles/lipics-v2018/lipics-v2018-authors/lipics-v2018-manual.pdf}.
 \end{itemize}
@@
 
-\subparagraph*{Acknowledgements.}
-
-I want to thank \dots
-
 \appendix
@@
 
-%% Either use bibtex (recommended),
+%% Please use bibtex,
 
-\bibliography{lipics-v2016-sample-article}
-
-%% .. or use the thebibliography environment explicitely
+\bibliography{lipics-v2018-sample-article}
 

### 2018-04-07 cones/paper/lipics-v2018-authors/cones.tex
Made changes suggested by the seconnd reviewer.

@@
 We begin with a pair of examples that will illustrate the lack of continuity, from a syntactic point of view.  
-Let $\nat$ be our natural number type and consider a sequence of functions ${<}n\from\nat\to\nat$, where ${<}m\;k$ evaluates to $0$ if $k<n$ and diverges otherwise.
+Let $\nat$ be our natural number type and consider a sequence of functions ${<}n\from\nat\to\nat$, where ${<}n\;k$ evaluates to $0$ if $k<n$ and diverges otherwise.
 In that case, the least upper bound of the ${<}n$ is the function that combines all their convergent behaviours; i.e., the function $\lambda k.k;\0$ that evaluates its input and then returns $0$.
@@
   && \IfO \mid \blank;\blank \mid \blank \coloneqq \blank \mid \\
-  && \deref \mid \neww_T \mid \mkvar \mid \wn\,.
+  && \deref\footnote{That is, variable \deref{}ccess.} \mid \neww_T \mid \mkvar \mid \wn\,.
 \end{IEEEeqnarray*}
@@
   \label{fig:ia-os}
-\end{figure*}/
+\end{figure*}
 
@@
   \lambda_{A\implies B} & = & [\neg\circ\lambda_A,\lambda_B]\,.\\
-  *\ts_{A\implies B} n & \Leftrightarrow & * \ts_B m\,.\\[1.0ex]
+  *\ts_{A\implies B} n & \Leftrightarrow & * \ts_B n\,.\\[1.0ex]
   m \ts_{A\implies B} n & \Leftrightarrow & \mbox{\pbox\textwidth{$m \ts_A n$ or $m\ts_B n$ \\ or (for $m\neq *$) $ * \ts_B m$ and $* \ts_A n$\,.}} \\[1.0ex]

### 2018-04-07 cones/paper/lipics-v2018-authors/cones.tex
Modified the abstract.

@@
   Lastly, we prove full abstraction for the model; because of the lack of continuity, we cannot deduce this from definability of compact elements in the usual way, and we have to use a stronger universality result instead.
-  We discuss how our techniques may also be applied to yield a proof of computational adequacy for a model of PCF with unbounded nondeterminism, based on the construction by Hyland and Ong.
+  We discuss how our techniques could be applied to yield proofs of adequacy for models of nondeterministic PCF, such as those given by Tsukada and Ong.
 \end{abstract}

### 2018-04-12 cones/paper/lipics-v2018-authors/cones.tex
Did some shortening.

@@
   Lastly, we prove full abstraction for the model; because of the lack of continuity, we cannot deduce this from definability of compact elements in the usual way, and we have to use a stronger universality result instead.
-  We discuss how our techniques could be applied to yield proofs of adequacy for models of nondeterministic PCF, such as those given by Tsukada and Ong.
+  We discuss how our techniques yield proofs of adequacy for models of nondeterministic PCF, such as those given by Tsukada and Ong.
 \end{abstract}
@@
 9]{DijkstraBook} that it is impossible to implement unbounded nondeterminism, showing that the natural constructs from which we construct imperative programs satisfy a \emph{continuity} property that unbounded nondeterminism lacks.
-For semanticists, this lack of continuity is a problem in itself, since the standard proofs of computational adequacy and full abstraction typically make use, implicitly or otherwise, of the fact that composition within the model is continuous with respect to some ordering.
+This is a problem in itself for semanticists, for whom continuity is often a key ingredient in proofs of computational adequacy and full abstraction.
 
-We shall explore some of the problems relating to unbounded nondeterminism, and how they may be solved, using game semantics to give a fully abstract model of a simple stateful language -- Idealized Algol -- enhanced with a countable nondeterminism primitive.
+We shall explore some of these problems and how they may be solved, using game semantics to give a fully abstract model of a simple stateful language -- Idealized Algol -- enhanced with a countable nondeterminism primitive.
 We begin with a pair of examples that will illustrate the lack of continuity, from a syntactic point of view.  
@@
 In that case, the least upper bound of the ${<}n$ is the function that combines all their convergent behaviours; i.e., the function $\lambda k.k;\0$ that evaluates its input and then returns $0$.
-If $\wn\from\nat$ is an unbounded nondeterminism machine, then function application to $\wn$ is not continuous; indeed, ${<}m\;\wn$ always has the possibility of divergence -- since $\wn$ may evaluate to $m+1$, say.
+If $\wn\from\nat$ is an unbounded nondeterminism machine, then function application to $\wn$ is not continuous; indeed, ${<}m\;\wn$ may diverge -- since $\wn$ may evaluate to $m+1$, say.  
 But $(\lambda k.k;\0)\;\wn$ always converges to $0$.
 
-Lack of continuity is a problem because fixed-point combinators are typically built using least upper bounds, and proving adequacy of the model typically requires that these least upper bounds be preserved.
+Lack of continuity is a problem in denotational semantics because fixed-point combinators are typically built using least upper bounds, and proving adequacy of the model typically requires that these least upper bounds be preserved.
 In a non-continuous situation, we will need to come up with new techniques in order to prove adequacy without using continuity.
@@
 The idea of adding infinite traces into strategies in order to model unbounded nondeterminism goes back to Roscoe's work on CSP \cite{RoscoeCspInfinite}, and is very similar to work by Levy \cite{LevyGsInfinite} on game semantics for a higher order language.
-In particular, we will need something similar to Levy's \emph{liveliness} condition on strategies, which is a way of saying that a strategy is a union of deterministic strategies -- something that is not automatic when we start tracking infinite plays.
+In particular, we will need something similar to Levy's notion of a \emph{lively} strategy -- one that is a union of deterministic strategies -- a property that does not automatically hold when we start tracking infinite plays.
 
@@
 Although we are able to give a model of Idealized Algol with countable nondeterminism in the more traditional Harmer-McCusker style, it seems necessary to introduce this extra machinery in order to model stateless languages such as PCF (and certainly to model concurrency).
-In the last section of this paper, we will show how our methods can be applied under very general circumstances, and in particular to these models of nondeterministic stateless languages.
+In the last section of this paper, we will show how our methods can be applied under very general circumstances, and in particular to some of these models of nondeterministic stateless languages.
 
@@
 The main concepts of game semantics and the steps we take to establish full abstraction are well-established, with a few exceptions.  
-The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, is the first example of using the technique to establish a full abstraction result for may and must testing.
+The idea of including infinitary information in strategies is not new, but this particular presentation, though closely related to that of \cite{LevyGsInfinite}, is the first example of using the technique to establish a compositional full abstraction result for may and must testing.
+
+Levy's work in \cite{LevyGsInfinite} is part of a tradition of techniques used to handle unbounded nondeterminism operationally, normally using Labelled Transition Systems (see, for example, \cite{PitchersThesis}).
+The contribution of this work is to apply the basic idea of including infinitary information to a compositional setting, where the semantics is built using the algebraic structure of higher-order programs.
 
 There are two points in the traditional Full Abstraction proof that depend on composition being continuous, and we have had to come up with ways of getting round them.  
-The easier of the two is that continuity is necessary for the usual proof that we can derive Full Abstraction from definability of compact strategies; in order to get around this, we have had to appeal instead to the stronger \emph{universality} result of \cite{hoPcf}, that says that every \emph{recursive} strategy is definable.
+Firstly, in the absence of continuity, it no longer suffices to show that we can define every \emph{compact} strategy; instead, we need a \emph{universality} result allowing us to define certain infinite strategies -- specifically, the \emph{recursive} ones.
 
@@
 This new technique is actually very generally applicable.  
-In the last section of the paper, we show that it may be used to prove adequacy for models of nondeterministic PCF under very mild assumptions.  
+We shall show that it may be used to prove adequacy for models of nondeterministic PCF under very mild assumptions.  
 The Tsukada-Ong model, for example, satisfies these assumptions, allowing us to obtain an adequacy result for PCF with countable nondeterminism.
@@
 The typing rule for $\wn$ is $\Gamma \vdash \wn\from\nat$.
-We shall use the letter $v$ to range over variables of type $\Var$.
+We shall use $v$ to range over variables of type $\Var$.
 
@@
 
-The principal difficulties in modelling nondeterministic stateless languages were made by Tsukada and Ong in \cite{TsukadaSheaves}, where they discovered how to define an innocent nondeterministic strategy by retaining `branching time information' in strategies.
+The principal difficulties in modelling nondeterministic stateless languages were overcome by Tsukada and Ong in \cite{TsukadaSheaves}, where they outlined how to define an innocent nondeterministic strategy by retaining `branching time information' in strategies.
 An additional benefit of the retention of branching time information is that we no longer need to keep track of infinite plays in order to model unbounded nondeterminism.  
@@
 
-However, since there is no such model in the literature at the moment, we shall have to be a bit more general in examining how our techniques can be used to model nondeterministic PCF.  
-Our main new contribution is the proof of adequacy, and our methods can be applied to PCF as well.  
+We could use our methods to help establish this claim in the case of unbounded nondeterminism; specifically, our proof of adequacy will extend to such a model.  
 Indeed, Corollary \ref{cor:adequacy} can easily be modified to apply to PCF, even though we have used Idealized Algol terms in the proof.  
-Corollary \ref{cor:adequacy} reduces the proof of adequacy to a combinatorial check on morphisms from $\bN\to\bC$ on strategies in the well-known category $\G_{vis}^\oc$.
+Corollary \ref{cor:adequacy} then reduces the proof of adequacy to a combinatorial check on morphisms from $\bN\to\bC$ on strategies in the well-known category $\G_{vis}^\oc$, together with an examination of what happens to those strategies when we compose them with $\top_\bN$.
 

### 2018-04-12 cones/lics-paper/rebuttal.txt
Made some global additions to the repository.

-- Review 1 --

Thank you for this review.  As you point out, the idea of using infinite traces to model unbounded nondeterminism has a long history, and has been encountered in a number of different contexts.  However, I cannot agree that the contribution of our paper is nothing more than a recasting of earlier work with LTS models in the context of game semantics.  Necessarily, our model covers much of the same ground that has been covered in earlier studies of unbounded nondeterminism, going back to Roscoe's work on infinite trace CSP (which we have cited), but we have never claimed this to be an original contribution, and we have been careful to cite Levy's work on LTSs and games as a primary source for this material.

The main contribution lies in our methods for dealing with the lack of continuity in the model, which are different from those employed in CSP and earlier denotational models.  The transfinite induction method used by Roscoe is not suitable in our case, because we do not interpret our operational semantics directly in the model, but use a compositional, algebraic approach to relate the operational to the denotational semantics.  The second author has used transfinite induction to prove a similar result [J. Laird, 2015], but this argument relies on a one-sided continuity property that fails in this case.  The technique in this submission, which uses stateful programs to simulate individual traces within the non-continuous part of the language, is new.

The second review captures the situation well: though our presentation uses techniques that are common in the game semantics community, such as the Harmer-McCusker-style deterministic factorization result, we certainly do not claim novelty for these ideas, and the main technical contribution of the paper is separate both from the earlier game semantics of finite nondeterminism and from the semantics of unbounded nondeterminism using models based on applicative bisimulations.

We chose to illustrate our material with well-known examples demonstrating the difficulty of the problem, which might have contributed to the impression that the only contribution of the paper was to cover well-trodden ground.  I concede that we should perhaps have cited some more of the LTS literature on top of the work on CSP and game semantics in order to make its contribution clear.

We would be interested to study the relationship between game semantic models of nondeterminism and work in LTSs, but we do not feel that the correspondence is yet well enough understood to say that the two strands cover precisely the same ground.  In particular, our semantics is compositional, unlike the model based on LTSs.  This makes it more difficult to navigate the technical issues relating to non-continuity, but also means that our semantics can be extended to give models of non-functional languages that are difficult to study using LTSs and other similar models, and also allows us to study nondeterminism using techniques based on both the algebraic and the combinatorial structure of the model.

-- Review 3 --

Thank you for this detailed review, and for identifying some technical flaws that we missed.

* Definition of recursive strategies:

This is indeed the intended definition of a recursive strategy (in particular, it is required in order for the remark at line 778 to be true).  You are right that this should be spelled out in the paper.

* Theorem 4.5:

Thank you for this clarification.  You are correct that the definition of the intrinsic quotient on strategies needs to be changed so that only recursive 'test morphisms' are allowed.  However, although this is an important adjustment, I am not sure I agree that this makes the result significantly less appealing.  As you are aware, statements of the form 'two programs are indistinguishable by <lang>-contexts if and only if their denotations are indistinguishable by the interpretations of <lang>-contexts' are widespread in full abstraction proofs that use an intrinisic quotient; the only thing we lose here is that we cannot put the word 'compact' in front of 'interpretations', but this is unavoidable.  Indeed, by modifying the \varphi in your example so that the infinite path *is* recursive (but, for example, is very high up in some fast-growing hierarchy), we see that we are unable to impose any boundedness condition on the interpretations of contexts without losing the correspondence with may-must equivalence.

* Tsukada-Ong model:

Your point about the Tsukada-Ong model is technically correct: the model given in that paper is not sound for must-equivalence, and so certainly cannot satisfy the conditions in Definition 5.3 or the conclusion of Theorem 5.4.  However, this is a property of the particular model they choose in order to illustrate their techniques, and is not an essential limitation of those techniques, as they point out in the section titled 'Further considerations'.  Indeed, their techniques are about finding an innocent model of nondeterminism, and are independent of must-equivalence.  It would be worth being clearer that we need to adapt the Tsukada-Ong model using the techniques we have illustrated in the first four sections before it can satisfy the properties in Definition 5.3.  I do not feel, however, that this significantly undermines this section: the conditional result we have shown is still true; it is the motivating example that needs to be adjusted.

I do not agree that the condition in Definition 5.3 is as hard to prove as the result of Theorem 5.4.  In particular, Definition 5.3 does not mention the language at all, so can be proved using only properties of the model (of course, how difficult this is will depend on what the model is).

As an example, take C to be the (Cartesian closed) category of games and (unconstrained) nondeterministic strategies.  Then there is a natural inclusion functor J : G^!_{inn} -> C and a morphism T_\nat : 1 -> J \nat in C given by the top strategy on the game interpretation of the \nat type.  It is then easy to verify that the conditions in Definition 5.3 hold, since the game interpretation of \nat -> \nat is fairly simple.  Of course, this may be more difficult in a semantics that is less explicitly related to games, but, as the name suggests, this result is intended to be used for models that can sensibly be called 'game semantics'.

The gap between Definition 5.3 and Theorem 5.4 is precisely Lemma 5.1, which is the real content of our adequacy result, where we overcome the difficulties relating to the lack of continuity.

We accidentally omitted the converse from Theorem 5.4, which is also true, and which immediately implies Inequational Soundness for the given model.  The given direction can be used to deduce full abstraction as in Theorem 4.5, but only if we have access to a universality result for the model.

* Universality:

Thank you for this small point.  You gave a good example of a strategy whose 'definition' in PCF can in fact be distinguished from it using Idealized Algol terms, which shows that we cannot immediately derive Proposition 3.6 from the Hyland-Ong result, and should instead reprove it in full, following the Hyland-Ong proof.  Murawski and Tzevelekos seem to claim that every recursive innocent strategy is the defnotation of some term of call-by-value PCF (without quotient), which suggests that this result should be true for Idealized Algol by using the stateful structure to mimic the appropriate call-by-value constructs, as you did in your example.

### 2018-04-12 cones/galop_abstract/cones.tex
Made some global additions to the repository.

\documentclass{article}

\input{../../common/preamble}

\begin{document}

We begin with the observation that, in many semantic models of programming languages with effects such as nondeterminism or state, the effects themselves correspond to the presence of certain natural transformations in the categorical semantics.  
If we are careful and make certain qualifications on the morphisms allowed, then game semantic models of nondeterminism contain a natural transformation $\top_A\from I \to A$, while the model of Idealized Algol given by Abramsky and McCusker \cite{SamsonGuyIAPassive} can be thought of as enriching the game semantics of PCF with new morphisms generated by a natural transformation $\cell_X\from I \to \oc \Var[X]$.

We answer the question: if we have a model of an existing language, and an effect that we would like to add to the model expressed as a particular natural transformation we would like to have, is there a systematic way to construct the new model?  It turns out that we can do this in a very abstract category-theoretic way, in such a way that the model we get admits a functor into \emph{any} extension of the original model that has the new effect in it.  
In fact, our construction is \emph{initial} among such extensions, in a way that we can make precise, and so enjoys useful functorial properties.

We show that it is often possible to prove results such as computational adequacy and full abstraction for this category we have constructed, and then lift them on to other models using the induced functor.  
Properties of the model in question correspond to properties of the functor out of our abstract category; for example, if a model satisfies a factorization result such as \emph{innocent factorization} \cite{SamsonGuyIAPassive} or \emph{deterministic factorization} \cite{mcCHFiniteND}, then the induced functor is full.

We can relate this to a number of unsolved problems in Game Semantics.  
For example, it is difficult to give a direct definition of an innocent nondeterministic strategy in Hyland-Ong games, and the Abramsky-Jagadeesan game semantics model has no obvious analogue for the concept of a visible strategy.  
One approach, suggested in Russ Harmer's thesis \cite{RusssThesis}, is to give an \emph{indirect} definition instead; for example, by defining an innocent nondeterministic strategy to be the composition of an innocent \emph{deterministic} strategy with $\top_{\bN}$.  
One way of viewing our work is as an abstract and fully general crystallization of this approach, since our category is in some sense formed by freely adding the effects into the original model.

In the nondeterminism case, we examine similarities with the work of Tsukada and Ong \cite{TsukadaSheaves}, and discuss some examples of effects other than nondeterminism and state.

\bibliographystyle{plain}
\bibliography{../../common/phd_bibliography}
\end{document}

### 2018-04-12 cones/lics-paper/cones.tex
Made some global additions to the repository.

--- 2018-01-31 cones/paper/cones.tex
@@
                                         %% can be repeated if necessary
-\orcid{0000-0002-4513-9618}             %% \orcid is optional
 \affiliation{
@@
 We then say that a strategy $\sigma$ is \emph{divergence-complete} if every unreliable point of $\sigma$ is contained in $D_\sigma$.  
-Every strategy $\sigma$ can clearly be extended to a minimal divergence-complete strategy $\text{dc}(\sigma)$; Murawski's explicit characterization of the intrinsic collapse \cite{MurawskiIntrinsic}, which may be applied to our model, essentially says that $\sigma\oes\tau$ if and only if $\text{dc}(\sigma)=\text{dc}(\tau)$.
+Every strategy $\sigma$ can clearly be extended to a minimal divergence-complete strategy $\text{dc}(\sigma)$; Murawski's explicit characterization of the intrinsic collapse \cite{MurawskiIntrinsic}, which may be applied to our model, essentially says that $\sigma\oes\tau$ if and only if $\sigma$ and $\tau$ have the same \emph{complete} plays and $\text{dc}(\sigma)=\text{dc}(\tau)$.
 
@@
 We want a version of Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} that can be applied to PCF contexts and the game semantics model $\G_{inn}$ of PCF.  
-Clearly, the lemma as currently stated does not hold in $\G_{inn}$, since the strategies $\sigma$ that we define are not innocent in general.
+Clearly, the lemma as currently stated does not hold in $\G_{inn}$, even after switching our observable type from $\com$ to $\nat$, since the strategies $\sigma$ that we define are not innocent in general.
 
 Instead, we need to look at the combinatorial structure of the strategies.  
-We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qa\in T_{\sigma;\sigma_M}$ if and only if there exists some $s\in T_{\sigma_M}$ such that $s\vert_{\bC}=qa$.
+We observe that if $\sigma_M\from\oc\bN\to\bC$ is a strategy, then there exists a deterministic strategy $\sigma\from\oc\bN$ such that $qn\in T_{\sigma;\sigma_M}$ if and only if there exists some $s\in T_{\sigma_M}$ such that $s\vert_{\bC}=qn$.
 
@@
   \begin{itemize}
-    \item $C[\wn]\converges n$ if and only if there exists $s\in \sigma_C$ such that $s\vert_{\bN}=qa$.  
+    \item $C[\wn]\converges n$ if and only if there exists $s\in \sigma_C$ such that $s\vert_{\bN}=qn$.  
     \item $C\mustconverge$ if and only if $\sigma_C$ is winning.
@@
 Now we have an inclusion functor $J:\G_{inn}^\oc\hookrightarrow\G_{TO}$, where $\G_{TO}$ is the Tsukada-Ong category.  
-Since the nondeterministic oracle $\wn$ may also be interpreted as a tree-strategy $\top_{\bN}$ in $\G_{TO}$, this gives us a model of PCF with countable nondeterminism inside that category.
+Since the nondeterministic oracle $\wn$ may also be interpreted as a tree-strategy $\top_{\bN}$ in $\G_{TO}$, this gives us a model of PCF with countable nondeterminism inside $\G_{TO}$.
 
@@
   {http://dx.doi.org/10.13039/501100000690} under Grant
-  No.~\grantnum{GS501100000690}{EP/K018868/1}.   I am grateful to Martin Hyland for an interesting conversation that helped me develop some of this material.
+  No.~\grantnum{GS501100000690}{EP/K018868/1}.   I am grateful to Martin Hyland for our conversation that helped me to develop some of this material.
 \end{acks}

### 2018-04-16 cones/paper/lipics-v2018-authors/cones.tex
Got it under 15 pages.

@@
 
+\let\oldemptyset\emptyset
+\let\emptyset\varnothing
 \newcommand{\nat}{{\mathtt{nat}}}
@@
 
-We describe a simple type theory and operational semantics for Idealized Algol with countable nondeterminism.
-This is similar to the approach adopted in \cite{mcCHFiniteND}, which extends Idealized Algol with \emph{finite} nondeterminism.  
+We describe a type theory and operational semantics for Idealized Algol with countable nondeterminism.
 The types of our language are defined inductively as follows:
@@
 
-We will use the Hyland-Ong version of Game Semantics, as in \cite{SamsonGuyIAPassive}.
-
 \subsection{Arenas}
@@
 Given a set $X$, the flat arena on $X$ is the arena with a single $O$-question $q$ and a $P$-answer $x$ for each $x\in X$, where $*\ts q$ and $q\ts x$ for each $x$.  
-The denotation of the type $\nat$ will be the flat arena $\bN$ on the set of natural numbers, while the denotation of the type $\com$ will be the flat arena $\bC$ on the singleton set $\{a\}$.
+The denotations of the types $\nat$ and $\com$ are the flat arenas $\bN$ and $\bC$ on, respectively, the set of natural numbers and the singleton $\{a\}$.
 
-We shall assume that our arenas are \emph{enumerated}; that is, that the set $M_A$ comes equipped with a partial surjection $\bN\to M_A$. 
-We assume that this enumeration is defined on the flat arenas and extended to the connectives in a natural way.
+We assume that our arenas are \emph{enumerated}; i.e., that the set $M_A$ is equipped with a partial surjection $\bN\to M_A$.  
+The denotation of any IA type has a natural enumeration.
 
 Given an arena $A$, a \emph{justified string} in $A$ is a sequence $s$ of moves in $A$, together with \emph{justification pointers} that go from move to move in the sequence.  
-The justification pointers must be set up in such a way that every non-initial move $m$ in $s$ has exactly one justification pointer going back to an earlier move $n$ in $s$ such that $n\ts_A m$.  
-We say that $n$ \emph{justifies} $m$.  
-It is easy to see that every justified string must begin with an initial move, an hence with an $O$-question.
+The justification pointers must be set up in such a way that every non-initial move $m$ in $s$ has exactly one justification pointer going back to an earlier move $n$ in $s$ such that $n\ts_A m$; we say that $n$ \emph{justifies} $m$.
+In particular, every justified string begins with an initial move, and hence with an $O$-question.
 
@@
 
-We follow the approach taken by Abramsky and McCusker \cite{SamsonGuyIAPassive} -- a middle road between the \emph{arenas} of Hyland and Ong and the \emph{games} of \cite{ajmPcf} that makes the linear structure more apparent.
+We use the approach taken by Abramsky and McCusker \cite{SamsonGuyIAPassive} -- a middle road between the \emph{arenas} of Hyland and Ong and the \emph{games} of \cite{ajmPcf} that makes the linear structure more apparent.
 
@@
 
-Our definition of a strategy will be modelled upon that given in \cite{mcCHFiniteND}.  
-We model nondeterministic computations by relaxing the determinism constraint on strategies -- so player $P$ may have multiple replies to any given $O$-move.
+As in \cite{mcCHFiniteND}, we model nondeterministic computations by relaxing the determinism constraint on strategies -- so player $P$ may have multiple replies to any given $O$-move.
 
-In addition, we have to keep track of any possible divergence in the computation; this is so we can distinguish terms such as
-\begin{mathpar}
-  \IfO \wn\;\Omega\;\0 \and \0\,,
-\end{mathpar}
-where the term on the right must converge (to $\0$), while the term on the left has a possible divergence.  
-The traditional way of representing divergences in game semantics is by a partiality in the strategy; i.e., an $O$-move to which $P$ has no reply, but this doesn't work here: $\IfO\wn\;\Omega\;\0$ and $\0$ both denote the strategy with maximal play $q\;0$; the partiality in the former is `hidden' by the move $0$.
+In addition, we have to keep track of any possible divergence in the computation so we can distinguish terms such as
+$
+  \IfO \wn\;\Omega\;\0$, which may diverge, and $\0$, which must converge.
 
-To fix this problem, we follow \cite{mcCHFiniteND} by modelling a strategy as a pair $(T_\sigma,D_\sigma)$, where $T_\sigma$ is a nondeterministic strategy in the usual sense and $D_\sigma$ is a set of $O$-plays after which there is a possibility of divergence.
+To fix this problem, we follow \cite{mcCHFiniteND} by modelling a strategy as a pair $(T_\sigma,D_\sigma)$, where $T_\sigma$ is a nondeterministic strategy in the usual sense and $D_\sigma$ is the set of those $O$-positions where there is a possibility of divergence.
 
-Tracking divergences explicitly in this way requires some care when we compose strategies using `parallel composition plus hiding'.
+Tracking divergences explicitly in this way requires some care when we compose strategies.
 Specifically, we need to be able to add new divergences into strategies when they arise through `infinite chattering' or \emph{livelock}.  
@@
 Note that this strategy strictly contains the strategy $\mu$ that we considered before, and therefore that the denotation of
-\[
-  \IfO \wn M N
-  \]
-has the same denotation as $N$, even though for any $n$, $M\n\not{\mustconverge}$, while $N\n\mustconverge$.
-Moreover, if we try to compose $\deno{N}$ with the strategy on $\bN$ that always returns $1$, then we end up with an infinite increasing sequence of positions, which triggers the introduction of a divergent play into the composite strategy -- even though no divergence occurs in the evaluation of $N$.
+  $\IfO \wn M N$
+has the same denotation as $N$, even though for any $n$, $M\n\not\mustconverge$, while $N\n\mustconverge$.
+Moreover, if we try to compose $\deno{N}$ with the strategy on $\bN$ that always returns $1$, then we end up with an infinite increasing sequence of positions, which triggers the introduction of a divergent play into the composite strategy -- even though $N$ must converge.
 
-Aside from showing that this model cannot possibly be sound, this example actually leads to composition not being associative if we naively extend the Harmer-McCusker model from finite to infinite nondeterminism (e.g., see \cite[4.4.1]{RusssThesis}).
+Aside from showing that the naive extension of the Harmer-McCusker model cannot be sound, this example actually leads to composition not being associative (e.g., see \cite[4.4.1]{RusssThesis}).
 
-Somehow, the crucial point is that we need to distinguish between terms like $M$, which contain infinite sequences of moves, and terms like $N$, which contain arbitrarily large finite sequences of moves.
-The way that we do this is by making the infinite sequences of moves explicit in our strategies, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.  
+What this illustrates is that we can no longer deduce the infinitary behaviour of a strategy by looking at the limits of its finite plays; instead, we need to keep track of infinite sequences of moves explicitly, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.
 When we use this technique, the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitrarily long finite sequences, but no infinite sequences.
-
-The games in our model are the same as those that we considered in the last section, but our definition of a strategy will change.
 
@@
 
-Given an arena $A$, we define an \emph{infinite justified string} in the obvious way.  
-We say that such a string is \emph{recursive} if it corresponds, via the enumeration on $M_A$ to a recursive function $\bN\to\bN$.
+We define an \emph{infinite justified string} in an arena $A$ in the obvious way.  
+We say such a string is \emph{recursive} if it corresponds, via the enumeration on $M_A$, to a recursive function $\bN\to\bN$.
 
 We define $\overline{P_A}$ to be $P_A$ together with the set of all those recursive infinite justified sequences that have all finite prefixes in $P_A$.
-
-We deliberately ignore any non-recursive infinitary behaviours, since these cannot be detected by computable contexts.
+Note that we deliberately ignore any non-recursive infinitary behaviours, since these cannot be detected by computable contexts.
 
@@
     \begin{description}
-      \item[Divergences come from plays] If $d\in D_\sigma$ then there exists some $s\prefix d$ such that $s\in T_\sigma\cap D_\sigma$.
-      \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position, then either $s\in D_\sigma$ or $sa\in T_\sigma$ for some legal play $sa$.
+      \item[Divergences come from plays] If $d\in D_\sigma$ then there exists $s\prefix d$ such that $s\in T_\sigma\cap D_\sigma$.
+      \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position, then either $s\in D_\sigma$ or $sa\in T_\sigma$ for some $sa$.
       \item[Infinite positions are divergent] If $s\in T_\sigma$ is infinite, then $s\in D_\sigma$.
@@
 
-We call the sequence $\s$ a \emph{legal interaction} if $\s\vert_{A,B}\in P_{A\implies B}$, $\s\vert_{B,C}\in P_{B\implies C}$ and $\s\vert_{A,C}\in P_{A\implies C}$.  
+We call $\s$ a \emph{legal interaction} if $\s\vert_{A,B}\in P_{A\implies B}$, $\s\vert_{B,C}\in P_{B\implies C}$ and $\s\vert_{A,C}\in P_{A\implies C}$.  
 We write $\Int_\infty(A,B,C)$ for the set of (possibly infinite) legal interactions between $A$, $B$ and $C$.
@@
 and then set
-\[
-  T_{\sigma;\tau} = \{\s\vert_{A,C}\suchthat \s\in T_\sigma\|T_\tau\}\,.
-  \]
+  $T_{\sigma;\tau} = \{\s\vert_{A,C}\suchthat \s\in T_\sigma\|T_\tau\}$.
+
 As for divergences in $\sigma;\tau$, our approach is actually simpler than that in \cite{mcCHFiniteND}; we set
@@
 We then set
-\[
-  D_{\sigma;\tau} = \pocl_{A\implies C}\{\s\vert_{A,C}\suchthat\s\in D_\sigma\dv D_\tau\}\,,
-  \]
+  $D_{\sigma;\tau} = \pocl_{A\implies C}\{\s\vert_{A,C}\suchthat\s\in D_\sigma\dv D_\tau\}$,
 where $\pocl X$ denotes the \emph{postfix closure} of $X$; i.e., the set of all $O$-plays in $P_{A\implies C}$ that have some prefix in $X$.
 
-Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself an (infinite) legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
+Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself a legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
 
@@
 
-Any finite-nondeterminism strategy in the sense of \cite{mcCHFiniteND} may be interpreted as a complete strategy by enlarging it with all its infinite limiting plays.  
+Any finite-nondeterminism strategy in the sense of \cite{mcCHFiniteND} may be interpreted as a complete strategy by enlarging it with all its infinite recursive limiting plays.  
 However, when we introduce countable nondeterminism, we also introduce strategies that are not complete.  
@@
     \item it is complete;
-    \item whenever $sab,sac$ are $P$-plays in $T_\sigma$ we have $b=c$ and the justifier of $b$ is the justifier of $c$;
-    \item If $s\in D_\sigma$ then either $s$ is infinite or there is no $a$ such that $sa\in T_\sigma$.
+    \item if $sab,sac$ are $P$-plays in $T_\sigma$ then $b=c$ and the justifier of $b$ is the justifier of $c$;
+    \item if $s\in D_\sigma$ then either $s$ is infinite or there is no $a$ such that $sa\in T_\sigma$.
   \end{itemize}
@@
 \begin{lemma}
-  Let $A,B,C$ be games and let $\sigma\from A\implies B$, $\tau\from B\implies C$ be deterministic complete strategies.  
+  Let $A,B,C$ be games and let $\sigma\from A\implies B$, $\tau\from B\implies C$ be deterministic strategies.  
   Then $\sigma;\tau$ is complete.
@@
   The proof relies on a lemma from \cite{hoPcf} that states (in our language) that if $\sigma$ and $\tau$ are deterministic strategies and $s\in T_{\sigma;\tau}$ then there is a unique minimal $\s\in T_\sigma\|T_\tau$ such that $\s\vert_{A,C}=s$.
-  That means that if $s_1\prefix s_2\prefix \cdots$ is an infinite increasing sequence of plays in $T_{\sigma;\tau}$, with infinite limit $s$, then there is a corresponding infinite increasing sequence of legal interactions $\s_1 \prefix \s_2 \prefix \cdots$.
-  Then the limit of this sequence is an infinite legal interaction $\s$ and we must have $\s\vert_{A,B}\in\sigma$, $\s\vert_{B,C}\in\tau$ by completeness of $\sigma$ and $\tau$.  
+  That means that if $s_1\prefix s_2\prefix \cdots$ is an infinite increasing sequence of plays in $T_{\sigma;\tau}$, with limit $s$, then there is a corresponding infinite increasing sequence of legal interactions $\s_1 \prefix \s_2 \prefix \cdots$.
+  Then the limit of the $\s_i$ is an infinite legal interaction $\s$ and we must have $\s\vert_{A,B}\in\sigma$, $\s\vert_{B,C}\in\tau$ by completeness of $\sigma$ and $\tau$.  
   Therefore, $s=\s\vert_{A,C}\in T_{\sigma;\tau}$.
@@
   In the first case, the diverge-or-reply rule for $\sigma$ and $\tau$ gives us a divergence at $s$ in $\sigma;\tau$.  
-  In the second case, an infinite chattering between $\sigma$ and $\tau$ corresponds to an infinite interaction $\s\in\Int(A,B,C)$ ending with infinitely many moves in $B$ such that $\s\vert_{A,C}=s$.
+  In the second case, an infinite chattering between $\sigma$ and $\tau$ corresponds to an infinite interaction $\s\in\Int_\infty(A,B,C)$ (with a tail in $B$) such that $\s\vert_{A,C}=s$.
 Completeness for $\sigma$ and $\tau$ tells us that $\s\vert_{A,B}\in D_\sigma$ and $\s\vert_{B,C}\in D_\tau$ and therefore that $\s\vert_{A,C}\in D_{\sigma;\tau}$.
@@
 Our proof for Corollary \ref{cor:diverge-or-reply} really makes use of the fact that a locally complete strategy is \emph{lively} in the sense of \cite{LevyGsInfinite}; i.e., locally deterministic.  
-Our definition is slightly stronger than liveliness, because it insists that the union of complete strategies be \emph{countable}.  
+Our definition is slightly stronger than liveliness, because it insists that the union of complete strategies be countable.
 This will be essential to our definability result.
@@
 
-In fact, the proof of associativity of composition is pretty much the same in our model as it is in any other model of game semantics if we treat infinite plays the same as finite ones.
+The proof of associativity of composition is  the same in our model as it is in any other model of game semantics if we treat infinite plays the same as finite ones.
 However, it is worth saying a few words about associativity, since the model obtained by naively extending the Harmer-McCusker model to unbounded nondeterminism does not have an associative composition.
@@
 For example, if $\nu$ is the strategy we defined above, and $\0$ is the `constant $0$' strategy on $\bN$, then $\0;\nu$ has a divergence in the naive model, because the strategies $\0$ and $\nu$ appear to be engaged in infinite chattering.
-In our model, we have fixed that problem, because the strategy $\nu$ contains no infinite plays, and so no divergences arise in the composition.
+In our model, on the other hand, the strategy $\nu$ contains no infinite plays, and so no divergences arise in the composition.
 
@@
 
-This is very similar to the construction of a co-Kleisli category for a linear exponential comonad, but certain technical issues relating to well-openedness prevent us from presenting it in this way.
+This is similar to the construction of a co-Kleisli category for a linear exponential comonad, but technical issues relating to well-openedness prevent us from presenting it in this way.
 
@@
 
-Given a non-empty justified string $s$ in an arena $A$, we define the \emph{$P$-view} $\pv s$ of $s$ inductively as follows.
+Given a non-empty justified string $s$, we define the \emph{$P$-view} $\pv s$ of $s$ inductively as follows.
 \begin{IEEEeqnarray*}{rClCR}
@@
 
-If $\sigma$ is a complete strategy for a game $A$, we say that $\sigma$ is \emph{recursive} if $T_\sigma\cap P_A$ and $D_\sigma\cap P_A$ are recursively enumerable subsets of $\omega^\omega$ (under the enumeration of $M_A$).
-Here, we have thrown away the infinite plays in $T_\sigma$ and $D_\sigma$, but we do not lose any information because $\sigma$ is complete.
+If $\sigma$ is a complete strategy for a game $A$, we say $\sigma$ is \emph{recursive} if $T_\sigma\cap P_A$ and $D_\sigma\cap P_A$ are recursively enumerable subsets of $\omega^\omega$ (under the enumeration of $M_A$).
+Here, we throw away the infinite plays in $T_\sigma$ and $D_\sigma$, but we do not lose any information because $\sigma$ is complete.
 
-If $\sigma$ is locally complete, we say that $\sigma$ is \emph{recursive} if $\sigma$ is the union of complete strategies $\sigma_1,\sigma_2,\cdots$, where the $\sigma_i$ are recursive and the map $i\mapsto \sigma_i$ is a recursive function $\bN \to (\bN \to \bN) \to 2$.
+If $\sigma$ is locally complete, we say that $\sigma$ is \emph{recursive} if $\sigma$ is the union of complete recursive strategies $\sigma_1,\sigma_2,\cdots$, where the map $i\mapsto \sigma_i$ is a recursive function $\bN \to (\bN \to \bN) \to 2$.
 
@@
 
-Note that our result is a bit simpler than the corresponding result in \cite{mcCHFiniteND}; this is because it is easier to model a countable source of nondeterminism than a `finite but arbitrarily large' source.
+Note that our result is a bit simpler than in \cite{mcCHFiniteND} because of the unbounded nondeterminism.
 
@@
   Let $\sigma\from I \to A$ be a strategy for a game $A$ in $\G_{ND}$.
-  Then we may write $\sigma$ as $\top_{\bN};\Det(\sigma)$, where $\Det(\sigma)\from \oc\bN\to A$ is a deterministic strategy and $\top_{\bN}$ is the strategy for $\oc\bN$ that is given by
-  \begin{itemize}
-    \item $T_{\top_{\bN}}=P_{\oc\bN}$.
-    \item $D_{\top_{\bN}}$ is the set of infinite positions in $T_{\top_\bN}$.
-  \end{itemize}
+  Then we may write $\sigma$ as $\top_{\bN};\Det(\sigma)$, where $\Det(\sigma)\from \oc\bN\to A$ is a deterministic strategy and $\top_{\bN}\from\bN$ is the strategy that contains every play in $\oc \bN$ and has no finite divergences.
 \end{proposition}
@@
   \end{itemize}
-  Lastly, we close under limits to make the strategy $\Det(\sigma)$ complete.  
+  We close under limits to make the strategy $\Det(\sigma)$ complete.  
   $\Det(\sigma)$ is clearly deterministic.  
@@
 
-Note that in the recursive case, $\Det(\sigma)$ is clearly recursively presentable if $\sigma$ is.  
-Furthermore, if $\sigma$ is visible, then so is $\Det(\sigma)$.
+Note that $\Det(\sigma)$ is recursive if $\sigma$ is and is visible if $\sigma$ is.
 
@@
 \begin{proposition}[Computational Adequacy]
-  Let $M\from\com$ be a closed term of Idealized Algol with countable nondeterminism.
+  Let $M\from\com$ be a closed term of nondeterministic Idealized Algol.
   $M\converges\skipp$ if and only if $qa\in T_{\deno M}$.  
@@
 In order to prove adequacy, we use a new technique that involves using a deterministic stateful construction to model the nondeterminism inside a deterministic world in which continuity holds.  
-To do this, we shall return to the concept of an \emph{evaluation} $\pi$ of a term as a sequence of natural numbers that we use to replace the constant $\wn$.
+To do this, we shall return to the concept of an \emph{evaluation} $\pi$ of a term as a sequence of natural numbers encoding the nondeterministic choices that we have made.
 
 \begin{lemma}
-  Let $M=C[\wn]$ be a term of type $\com$, where $C[-]$ is a multi-holed context of Idealized Algol.
+  Let $M=C[\wn]$ be a term of type $\com$, where $C[-]$ is a multi-holed context of (deterministic) Idealized Algol.
   Write $\sigma_M$ for the denotation of the term $\lambda n.C[n]$.  
@@
   Here, $\case_{k+1}\;a\;n_0\;\cdots\;n_k\;d$ is a new shorthand that evaluates to $n_i$ if $a$ evaluates to $i$, and evaluates to $d$ if $a$ evaluates to $j> k$.
-  This term adds an extra variable $v$ to the program; each time $f$ is called, it increments the value of $v$ and maps its value to one of the $n_i$.  
-  The result is that when $f$ calls its argument, it will receive $n_1$ the first time, $n_2$ the second and so on.
+  This term calls the function $f$, passing in $n_1$ the first time, $n_2$ the second and so on, passing in $d$ at every call beyond $k+1$.
 
@@
   $\sigma_\pi$ has plays of the form
-  \[
+  $
     q\;n_1\;q\;n_2\;\cdots\,,
-    \]
+    $
   and so it is total.
@@
   Since $\sigma$ is total and deterministic, it must have a maximal infinite play $s_\sigma$ of the form
-  \[
-    q\;m_1\;q\;m_2\;\cdots\,,
-    \]
+  $
+    q\;m_1\;q\;m_2\;\cdots
+    $,
   where $m_1,m_2,\dots$ is some infinite sequence of natural numbers.  
@@
   We may assume that $\sigma=\sigma_\pi$ for some evaluation $\pi$ of $M$.  
-  Therefore, $qa\in T_{\sigma_\pi;\sigma_M}$, which means that $M\converges\skipp$ along the evaluation $\pi$.  
+  Therefore, $qa\in T_{\sigma_\pi;\sigma_M}$, which means that $M\converges\skipp$ along $\pi$.  
   The corresponding statement for must convergence follows in the same way.
@@
 
-Note that these last two lemmas may be cast entirely in the model of Idealized Algol given in \cite{SamsonGuyIAPassive}, since they only refer to the denotations of deterministic terms.  
+Note that these last two lemmas may be cast entirely in the model of \emph{deterministic} Idealized Algol given in \cite{SamsonGuyIAPassive}, since they only refer to the denotations of deterministic terms.
 We can therefore prove a more general version of Proposition \ref{prop:adequacy}.
@@
 
-This definition is intimately connected to Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} in the following sense: if $\sigma_M\from\bN\to\bC$ is a strategy, then there exists some $\sigma_M$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma$ is not winning.
+This definition is motivated by Lemmas \ref{lem:soundness-lemma} and \ref{lem:soundness-converse} in the following sense: if $\sigma_M\from\bN\to\bC$ is a strategy, then there exists some $\sigma_M$ such that $D_{\sigma;\sigma_M}\ne\emptyset$ if and only if $\sigma$ is not winning.
 

### 2018-04-16 cones/paper/lipics-v2018-authors/cones.tex
Made it a bit nicer.
Changed the editor-only section.

@@
 
-\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
-E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
+\subjclass{F3.2.2 Denotational Semantics}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation".
 
@@
 \EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
+\EventLongTitle{Computer Science Logic 2018 (CSL 2018)}
+\EventShortTitle{CSL 2018}
 \EventAcronym{CVIT}
 \EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+\EventDate{September 4 -- 7, 2018}
+\EventLocation{Oxford, United Kingdom}
 \EventLogo{}
@@
 
-Tracking divergences explicitly in this way requires some care when we compose strategies.
+We need to take some care when we compose strategies using `parallel composition plus hiding'.
 Specifically, we need to be able to add new divergences into strategies when they arise through `infinite chattering' or \emph{livelock}.  

### 2018-11-08 cones/galop_presentation/presentation.tex
Haven't made a commit for ages.

\documentclass{beamer}

\let\NOTARTICLE=1
\let\BEAMER=1
\let\FEWFONTS=1

\newenvironment{theindex}
 {\let\item\par
  %definitions for subitem etc
  }{}
\newcommand\indexspace{}

\input{../../common/preamble}

\newtheorem{proposition}{Proposition}

\newcommand{\sign}[1]{\\\hfill -- \parbox[t]{.3\textwidth}{#1}}
\usepackage{wasysym}
\usepackage[absolute,overlay]{textpos}
\DeclareMathOperator{\ding}{ding}

%%% END Article customizations

\title{A unified approach to the semantics of effects}
\subtitle{GaLoP 2018, Thessaloniki}

\author{John Gowers}

\AtBeginSection{\frame{\sectionpage}}
\AtBeginSubsection{\frame{\subsectionpage}}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Outline}
  \tableofcontents
\end{frame}

\section{Some Examples}

\renewcommand*{\arraystretch}{0.5}

%\begin{frame}[allowframebreaks]
  %\frametitle{Related Work}
  %\nocite{mcCHFiniteND, RusssThesis, TsukadaSheaves, RoscoeCspInfinite, LevyGsInfinite, LairdOrdinalGames}
  %\bibliographystyle{plain}
  %\bibliography{../../common/phd_bibliography}
%\end{frame}

\begin{frame}
  \frametitle{Nondeterminism and innocence}

  The game semantics of nondeterminism models nondeterministic programs by \emph{nondeterministic strategies}, where $P$ can have multiple replies to an $O$-position. But there is no satisfactory definition of an \emph{innocent} nondeterministic strategy.
  \pause

  For example, consider the term
  \[
    (\lambda f.f 0) \text{ OR } (\lambda f.f 1)
    \]
  whose denotation is the union of the denotations of the same components.  
  But this strategy is not innocent!
  \pause

  Tsukada and Ong: the problem is missing \emph{branching time information}.
\end{frame}

\begin{frame}
  \frametitle{Is there another approach?}

  Harmer's thesis: a nondeterministic innocent strategy is any strategy of the form
  \[
    1 \xrightarrow{\top_{\bB}}
    \bB \xrightarrow{\sigma}
    A
    \]
  where $\sigma$ is innocent.
  \pause

  \textit{A more “synthetic”, a priori definition
of what it is to be an innocent strategy would be preferable.}
  \sign{Harmer}
  \pause

  \textit{Such
an approach is ultimately unsatisfactory as it provides no new
  insights on nondeterministic stateless computation.}
  \sign{Tsukada, Ong}
  \pause

  \only<4->{
  \begin{textblock}{0.5}(11,4)
    \rotatebox{350}{\Large\#unsatisfactory}
  \end{textblock}
}
\pause

  Tsukada, Ong: We can solve the problem using a sheaf-based model that retains branching-time information.
  \pause

  \only<6->{
  \begin{textblock}{0.5}(11,13)
    \rotatebox{350}{\Large\#satisfactory}
  \end{textblock}
}
\end{frame}

\begin{frame}
  \frametitle{A purely formal treatment of effects}

  Idea: If we use the indirect approach, we can treat $\top_\bB$ as a purely formal symbol and say that a nondeterministic innocent strategy for a game $A$ is a deterministic innocent strategy for $\bB\to A$.
  \pause

  We don't need to mention nondeterministic strategies at all!
  \pause

  Slight drawback: this approach distinguishes strategies that are in fact identical.  
  E.g., $\deno{\lambda b.b}$ and $\deno{\lambda b.\text{not }b}\from\bB$ both denote the term $t\text{ OR }f$.
  \pause

  \begin{minipage}{0pt}
    \includegraphics{circles_2.jpg}
  \end{minipage}
  \hspace{150pt}
  \begin{minipage}{0.01\textwidth}
    \includegraphics{circles_3.jpg}
  \end{minipage}
\end{frame}

\begin{frame}
  \frametitle{The formal treatment and branching-time information}

  Clearly, the strategy $\sigma\from\bB\to A$ contains all the information about branching time that we might need if we were to reason about $\top_\bB;\sigma$.
  \pause

  Since deterministic factorization automatically holds, the problem becomes one of working out the right equivalence relation to impose on strategies for $\bN\to A$ (cutting out the circle).
  \pause

  We can use a semi-indirect approach informed by the operational semantics of the language (e.g., using linear decomposition: $\sigma,\tau\from\bB\to A$ are equivalent if and only if for all $\alpha\from\oc\bB$ there exists some $\beta\from\oc\bB$ such that $\alpha;\sigma=\beta;\tau$ -- and vice versa).
  \pause

  Or we can use more ingenious techniques.  
  For example, we can recover the Tsukada-Ong sheaf-theoretic approach by identifying $\sigma$ with the following sheaf.
  \[
    \sigma(s) = \{t\in\sigma\suchthat t\vert_A=s\}
    \]
\end{frame}

\begin{frame}
  \frametitle{Another example -- bell games}

  We want to model the language PCF${}^{\bell+}$, obtained by enlarging PCF with command types and a constant $\ding\from\com$ with the following operational semantics.
  \[
    \inferrule*[right=\bell]{ }{\ding \opto \skipp}
    \]
  ($\bell$ $=$ `ring the bell every time you evaluate this rule')
  \pause

  Game Semantics (Ghica's `slot games'): insert an additional move $\bell$ (belonging to neither player) into the play whenever we ring the bell (so $\deno{\ding}$ is the strategy with maximal play $q\bell a$).

  The $\bell$s are not hidden during composition:
  \pause
  \begin{mathpar}
    \begin{array}{cccccc}
      {}    &  \com & \to & \com  & \to & \com \\
            &       &     &       &     &   q  \\
            &    q  &     &       &     &      \\
      \bell &       &     &       &     &      \\
            &    a  &     &       &     &      \\
            &       &     &   q   &     &      \\
      \bell &       &     &       &     &      \\
            &       &     &   a   &     &      \\
            &       &     &       &     &   a  \\
    \end{array}
    \and
    \rightsquigarrow
    \and
    \begin{array}{c}
      \\
      q\\
      \\
      \bell
      \\
      \\
      \bell\\
      \\
      a
    \end{array}
  \end{mathpar}
\end{frame}

\begin{frame}
  \frametitle{The formal approach to bell games}
  Suppose instead that we attempt to model $\ding$ as a purely formal morphism $1\to\bC$.  
  In our new model, a strategy for $A$ will be a strategy for $\bC\to A$ in the original model, where we interpret $\sigma\from\bC\to A$ as the strategy $\ding;\sigma\from A$.
  \pause

  For example, the term $\ding;\ding:\com$ is interpreted as the following composite.
  \[
    \bC \xrightarrow{\Delta}
    \bC \times \bC \xrightarrow{\blank;\blank}
    \bC
    \]
  \pause
  \renewcommand*{\arraystretch}{.75}
  As a a strategy:
  \[
    \begin{array}{ccc}
      \bC & \to & \bC \\
          &     &  q  \\
       q  &     &     \\
       a  &     &     \\
       q  &     &     \\
       a  &     &     \\
          &     &  a  \\
    \end{array}
    \]
\pause
$\bell$ $=$ $qa$ on the left.
\end{frame}

\begin{frame}
  \frametitle{A common theme}

  A common theme in both these examples is that formal morphisms expose moves that are normally hidden under composition.
  \pause

  For some computational effects, this is exactly what we want to do. For nondeterminism, the nondeterministic strategy approach hides too much information, and the formal approach reveals too much.
  \pause

  Topics for exploration:
  \pause

  Can we add formal morphisms $A\to A$ for all $A$ in order to make a `revealed game semantics' that is still a Cartesian closed category?
  \pause

  Are these two examples the same?  (E.g., $\ding$ = `unary nondeterminism')
  \pause

  Can we build a model of nondeterministic innocence based on bell games?
\end{frame}

\section{Cones on monoidal functors}

\begin{frame}
  We talked about formally adding morphisms into a category.  
  In this section, we'll look at a slightly more general construction.
  \pause

  The goals of this generalization are twofold:
  \pause
  \begin{itemize}
    \item To allow us to add more than one morphism at a time.
      \pause
    \item To give a more systematic account of the equivalence relation on morphisms.
  \end{itemize}
  \pause

  Previously, we wanted to add a morphism $\phi\from 1\to A$ for some object $A$ or, equivalently, a natural transformation from $I$ to the `constant $A$ functor'.
  \pause

  We replace $I$ with an arbitrary symmetric monoidal category $\C'$ and require that $\phi$ be an oplax monoidal functor.
  \pause

  Note: for every object $A$ of a CCC, the `constant $A$' functor is oplax monoidal with coherence given by the diagonal and projections.
\end{frame}

\begin{frame}
  The setup: we have an oplax monoidal functor $j\from \C'\to\C$, where $\C,\C'$ are symmetric monoidal categories.
  \pause

  We desire a symmetric monoidal category $\D$ that contains $\C$ plus additional morphisms corresponding to the image of $j$.
  \pause

  I.e., this (a \emph{$j$-category}):
  \[
    \begin{tikzcd}[row sep=large, column sep=large, ampersand replacement=\&]
      \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
        \& I \arrow[d, "I"] \\
      \C \arrow[r, "J"', ""{name=J}]
        \& \D
      \arrow[Rightarrow, from=term, to=J, "\phi"]
    \end{tikzcd}\quad,
  \]
where $J$ is a lax monoidal functor and $\phi$ is a `generalized monoidal natural transformation'.
\pause

The more objects there are in $\C'$, the more morphisms there are in $\D$.  
  The more morphisms there are in $\C'$, the \emph{fewer} morphisms there are in $\D$ (or: a finer equivalence relation on morphisms).
\end{frame}

\begin{frame}
  \frametitle{The Cone on $j$}

  We can define a morphism of $j$-categories $(\D',J',\phi')\to(\D,J,\phi)$ to be an oplax monoidal functor $f\from\D'\to\D$ making the following diagram commute.
  \[
    \begin{tikzcd}[row sep=large, column sep=large, ampersand replacement=\&]
      \C' \arrow[r, "()", ""'{name=term}] \arrow[d, "j"']
        \& I \arrow[d, "I"] \\
      \C \arrow[r, "J'"'{name=Jprimedown}, ""{name=Jprime}] \arrow[d, "\id"']
        \& \D' \arrow[d, "f"] \\
      \C \arrow[r, "J", ""{name=J}]
        \& \D
      \arrow[Rightarrow, from=term, to=Jprime, shift left=1.5ex, "\phi'"]
      \arrow[Rightarrow, from=Jprimedown, to=J, shift left=1.5ex, "\id"]
      \arrow[Rightarrow, from=term, to=J, shift right=3ex, "\phi"' near end]
    \end{tikzcd}\,.
    \]
  \pause

  We get a category of $j$-categories.  
  We can show that this category has an initial object $C_j$, called the \emph{cone on $j$}.
  \pause

  $C_j$ is the category obtained from $\C$ by `formally adding morphisms $\psi_X\from I \implies jX$'.
\end{frame}

\begin{frame}
  \frametitle{Construction of $C_j$}

  The construction of $C_j$ is straightforward (and quite familiar in the Cartesian case).
  \pause

  The objects of $C_j$ are the objects of $\C$.

  A morphism $A\to B$ in $C_j$ is a pair $(X,f)$, where $X$ is an object of $\C'$ and $f\from jX \tensor A \to B$ is a morphism in $\C'$.

  Two morphisms $(X, f)$ and $(X', f')$ are considered to be equivalent if there is some morphism $h\from X'\to X$ in $\C'$ making the following diagram commute.
  \[
    \begin{tikzcd}[ampersand replacement=\&]
      j X' \tensor A \arrow[r, "f'"] \arrow[d, "j h \tensor A"']
        \& B \\
      j X \tensor A \arrow[ur, "f"']
        \&
    \end{tikzcd}
    \]
  \pause

  Composition is given by `the only thing you can write down'.
\end{frame}

\begin{frame}
  \frametitle{Constructing models from $C_j$}

  We said that we wanted to model effects by finding a particular $j$-category $\D$ for a suitable $j$ that captures the effect in some way.
  \pause

  Even if we know nothing else about $\D$, we know that there is a functor $C_j\to\D$ that is a morphism of $j$-categories.
  \pause

  If $\D$ satisfies `$j$-factorization', then this functor is full.
  \pause

  In such a case, we can recover $\D$ by imposing a suitable equivalence relation on the morphisms in $C_j$.
  \pause

  The more morphisms we can include in $\C'$, the closer $C_j$ will be to our desired model.
\end{frame}

\section{More examples}

\begin{frame}
  \frametitle{Unbounded nondeterminism}

  Let $\G$ be the category of Hyland-Ong games.  
  \pause

  Now suppose that $\D$ is some extension of $\G$ that somehow models nondeterminism.  
  For each object $A$ of $\D$, there should be a strategy $\top_A\from 1 \to A$ that includes every position in $A$.
  \pause

  $\top_A$ is not a natural transformation $1\to\G$: this would mean that $\top_A;\sigma=\top_B$ for every $\sigma\from A \to B$.
  \pause

  However, if we require that $\sigma$ be \emph{surjective}; i.e., that every position in $B$ is the restriction of some position occurring in $\sigma$, then $\top_A;\sigma=\top_B$.  
  \pause

  If $j_s$ is the inclusion of the category $\G_s$ of games and \emph{surjective strategies} into $\G$, then $\top_A$ is a natural transformation $1\to j_s A$.
  \pause

  Therefore, $\D$ is some quotient of $C_{j_s}$.  
\end{frame}

\begin{frame}
  \frametitle{Unbounded nondeterminism and must-testing}

  $C_j$ models may-testing: in a model of unbounded nondeterminism with must-testing, we may have $\top_A;\sigma\ne \top_B$ even if $\sigma$ is surjective.  
  The reason is that $\sigma$ might have a play ending with infinitely many moves in $A$.
  \pause

  We say that a strategy $\sigma\from A \to B$ is \emph{winning} if it contains no such play.  
  Then if $j_{sw}$ is the inclusion of the category $\G_{sw}$ of games and \emph{surjective winning} strategies, then any model of unbounded nondeterminism with must testing that satisfies deterministic factorization is a quotient of $C_j$.
  \pause

  Notice that $\G_{sw}$ has \emph{fewer} morphisms than $\G_s$ and so the cone $C_{j_{sw}}$ has \emph{more} morphisms than the cone $C_{j_s}$: we no longer identify all strategies that have the same convergent behaviours.
\end{frame}

\begin{frame}
  \frametitle{Finite nondeterminism, revisited}

  We modelled finite nondeterminism in the cone $C_{c_{\bB}}$, where $c_{\bB}\from I \to \G$ is the constant $\bB$ functor.
  \pause

  A problem with this model was that it did not distinguish enough morphisms.
  \pause

  Let us replace $I$ with the one-object category $s_2$ whose morphisms are the surjective functions $\bool\to\bool$.
  Then $c_{\bB}$ extends to a functor $c_{\bB}'\from s_2\to \G$ in an obvious way.
  \pause

  The cone on $c_{\bB}'$ now no longer distinguishes the two terms $\lambda b.b$ and $\lambda b.\text{not }b$.
  \pause

  Alternatively: there is a morphism of oplax monoidal functors from $c_{\bB}\to j_{sw}$, which induces a functor $C_{c_{\bB}}\to C_{j_{sw}}$.  
  If we take the image of $C_{c_{\bB}}$ inside $C_{j_{sw}}$ then we can use the finer equivalence relation with the simpler category.
\end{frame}

\begin{frame}
  \frametitle{Probabilistic game semantics}
  The last example was a category with one object and multiple morphisms.
  \pause

  Now we consider an example with multiple objects and very few morphisms.
  \pause

  We turn the monoid $([0,1],\times)$ into a (strict) monoidal category and then add additional morphisms $\neg_p\from p \to 1-p$.

  Take the functor $c_{\bB}^p\from [0,1]\to \G$ that sends every element of $[0,1]$ to the boolean object $\bB$ and sends each morphism $\neg_p$ to the morphism $\text{not}\from\bB\to\bB$.
  \pause

  Then the cone over $c_{\bB}^p$ interprets probabilistic PCF.
  \pause

  The equivalence relation on morphisms in the cone automatically gives us equations such as the following.
  \begin{gather*}
    \text{if }\psi_{2/3}\text{ then }(\text{if }\psi_{1/2}\text{ then }a\text{ else }b)\text{ else }c=\\
    \text{if }\psi_{1/3}\text{ then }a\text{ else }(\text{if }\psi_{1/2}\text{ then }b\text{ else }c)
  \end{gather*}
\end{frame}

\begin{frame}
  \frametitle{Game semantics of state}
  Let $\Set^{\overset{\rightarrow}{\leftarrow}}$ be the category whose objects are sets and where the morphisms $A\to B$ are pairs of functions $f\from A\to B,g\from B\to A$ such that $f\circ g=\id_B$.

  Then we get an oplax monoidal functor $\Var\from\Set^{\overset{\rightarrow}{\leftarrow}}\to\G$ sending a set $X$ to the game $\Var[X] = \com^X\times \underline X$.
  \pause

  The function $\cell_X\from 1 \to \oc\Var[X]$ that is used to encapsulate state in the Abramsky-McCusker model of Idealized Algol is then a natural transformation from $1$ to $\oc\Var[X]$.
  \pause

  So we can model stateful strategies on a game $A$ as pairs $(X,\sigma)$ where $X$ is a set and $\sigma\from\oc\Var[X]\to A$ is an innocent strategy.
  \pause

  So what?  We can already characterize these as visible strategies.
\end{frame}

\begin{frame}
  \frametitle{Call-by-value state}

  Murawski + Tzevelekos: There is no implicit characterization of the stateful strategies of call-by-value Idealized Algol.
  \pause

  Contrast

  RML $=$ PCF${}^+$ $+$ $\text{ref}\from\Var$

  with

  IA${}_{cbv}$ $=$ PCF${}^+$ $+$ $\new_X\from ((\Var \to X) \to X)$.
  \pause

  Cone models make Idealized Algol's \emph{block structure} explicit:
  \begin{mathpar}
    \text{[RML] }\Var \to A \and \text{[IA${}_{cbv}$] }((\Var \to X) \to X) \to A
  \end{mathpar}
  \pause
  M+T: $S$-strategies for modelling IA${}_{cbv}$ -- make state and block-structure explicit, keeping just enough information to define a notion of \emph{innocence}.
  \pause

  Then discard the explicit state to get the semantics of IA${}_{cbv}$.
\end{frame}

\begin{frame}
  \frametitle{Questions?}
\end{frame}

\end{document}

### 2018-11-08 cones/paper/lipics-v2018-authors/sources/cones.tex
Haven't made a commit for ages.

--- 2018-04-16 cones/paper/lipics-v2018-authors/cones.tex
@@
 \acknowledgements{This material is based on work supported by the EPSRC under Grant No.~EP/K018868/1.  
-I am grateful to Martin Hyland for our conversation that helped me to develop some of this material.}%optional
+I (Gowers) am grateful to Martin Hyland for our conversation that helped me to develop some of this material.
+We are also grateful for the comments made by the anonymous referees for helping to clarify certain points, elaborate on technical difficulties and point to similarities with other parts of the literature.\vspace{24pt}}%optional
 
 %Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
+\EventEditors{Dan Ghica and Achim Jung}
 \EventNoEds{2}
-\EventLongTitle{Computer Science Logic 2018 (CSL 2018)}
+\EventLongTitle{27th EACSL Annual Conference on Computer Science Logic (CSL 2018)}
 \EventShortTitle{CSL 2018}
-\EventAcronym{CVIT}
-\EventYear{2016}
+\EventAcronym{CSL}
+\EventYear{2018}
 \EventDate{September 4 -- 7, 2018}
-\EventLocation{Oxford, United Kingdom}
+\EventLocation{Birmingham, GB}
 \EventLogo{}
-\SeriesVolume{42}
+\SeriesVolume{119}
 \ArticleNo{23}
-%\nolinenumbers %uncomment to disable line numbering
+\nolinenumbers %uncomment to disable line numbering
 %\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
@@
 \newcommand{\oes}{\sim}
+\newcommand{\orr}{\textsf{ or }}
+\newcommand{\lunit}{\textsf{lunit}}
 
@@
 We have therefore built an \emph{unbounded nondeterminism} machine, that can print out arbitrarily large natural numbers but which never diverges.  
-This is strictly more powerful than finitary choice nondeterminism.
-\footnote{Using recursion, we can build a program out of finite nondeterminism that can produce arbitrarily large natural numbers; however, this program also admits the possibility of divergence.}  
+This is strictly more powerful than finitary choice nondeterminism\footnote{Using recursion, we can build a program out of finite nondeterminism that can produce arbitrarily large natural numbers; however, this program also admits the possibility of divergence, unless we are able to insist on fairness.}.
 What we have just shown is that if we want to solve the problem of building a fair task scheduler, then we must in particular be able to solve the problem of building an unbounded nondeterminism machine.
 
-This is an important observation to make about concurrent programming, because the task of implementing unbounded nondeterminism is difficult -- indeed, considerably more so than that of implementing bounded nondeterminism.
+This is an important observation to make about concurrent programming, because the task of modelling unbounded nondeterminism is difficult -- indeed, considerably more so than that of modelling bounded nondeterminism.
 Dijkstra argues in \cite[Ch.
 9]{DijkstraBook} that it is impossible to implement unbounded nondeterminism, showing that the natural constructs from which we construct imperative programs satisfy a \emph{continuity} property that unbounded nondeterminism lacks.
-This is a problem in itself for semanticists, for whom continuity is often a key ingredient in proofs of computational adequacy and full abstraction.
+Park \cite{park1980semantics} shows that these problems can be surmounted if we use a weaker version of continuity (e.g., $\omega_1$- rather than $\omega$-continuity), but the failure of composition to be continuous is a problem in itself for semanticists, for whom continuity is often a key ingredient in proofs of computational adequacy and full abstraction.
 
@@
 Let $T$ be an Idealized Algol type, and let $M,N\from T$ be closed terms.
-Then we write $M\lmam N$ if for all compatible contexts $C[-]$ of ground type we have
+Then we write $M\lmam N$ if for all contexts $C[-]$ of ground type with a hole of type $T$, we have
 \begin{gather*}
@@
     \begin{itemize}
-      \item If $a\ts_A b$ and $a\ne b$, then $\lambda_A^{OP}(a)\neq\lambda_A^{OP}(b)$.  
+      \item If $a\ts_A b$, then $\lambda_A^{OP}(a)\neq\lambda_A^{OP}(b)$.  
       \item If $*\ts_A a$, then $\lambda_A(a)=OQ$ and $b\nts_A a$ for all $b\in M_A$.
@@
 We write $L_A$ for the set of legal plays in $A$.
+
+If $s$ is a justified string, we will write $sa$ for an arbitrary justified string extending $s$ by a single move $a$, itself justified by some move in $s$.
 
@@
 \[
-  N = \Y_{\nat\to\nat\to\nat}(\lambda g.\lambda m n.\IfO m\;\0\;n;(g\;(\pred m)\;n))\wn\,.
+  N = \Y_{\nat\to\nat\to\nat}(\lambda g.\lambda m n.\IfO m\;\0\;(n;(g\;(\pred m)\;n)))\wn\,.
   \]
@@
 
-What this illustrates is that we can no longer deduce the infinitary behaviour of a strategy by looking at the limits of its finite plays; instead, we need to keep track of infinite sequences of moves explicitly, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.
+What this illustrates is the point made by Park in \cite{park1980semantics} and \cite{park1981concurrency}: namely, that we can no longer deduce the infinitary behaviour of a strategy by looking at the limits of its finite plays; instead, we need to keep track of infinite sequences of moves explicitly, in the style of \cite{RoscoeCspInfinite} and \cite{LevyGsInfinite}.
 When we use this technique, the denotation of $M$ will contain an infinite sequence, while the denotation of $N$ will contain arbitrarily long finite sequences, but no infinite sequences.
@@
 We define an \emph{infinite justified string} in an arena $A$ in the obvious way.  
-We say such a string is \emph{recursive} if it corresponds, via the enumeration on $M_A$, to a recursive function $\bN\to\bN$.
+We say such a string is \emph{recursive} if it corresponds, via the enumeration on $M_A$, to a pair of recursive functions $\bN\to\bN$ -- one giving the sequence of moves and the other giving the justification relation.
 
@@
 Note that we deliberately ignore any non-recursive infinitary behaviours, since these cannot be detected by computable contexts.
+
+We shall represent a strategy using two sets: a set $T_\sigma$ of \emph{traces}, which takes the role of the plays that may occur in the strategy (as in the usual definition of a deterministic strategy), and a second set $D_\sigma$ of \emph{divergences}; i.e., $O$-positions at which the strategy may elect to diverge.
+In order to model observational equivalence more closely, we shall require $D_\sigma$ to be postfix-closed, since observable contexts cannot detect divergences that occur after the program might already have diverged: consider, for example, the terms $\Omega_{\nat\to\nat}\orr(\lambda n.n)$ and $\Omega_{\nat\to\nat}\orr(\lambda n.(n\orr\Omega_\nat))$ (where we have defined $M\orr N$ to be $\IfO\;\wn\;M\;N$).
+
+For technical reasons we keep track of infinite plays in both $T_\sigma$ and $D_\sigma$, with the rule that any infinite play in $T_\sigma$ must be contained in $D_\sigma$ (since it clearly corresponds to a divergent evaluation).
+We will require that every divergence arise from a trace; i.e., if every play in $D_\sigma$ must have some prefix that is contained in both $T_\sigma$ and $D_\sigma$.  
+A consequence of this is that if $d\in D_\sigma$ is infinite and has no finite prefixes in $D_\sigma$, then it must also be contained in $T_\sigma$.  
+Not too much importance should be given, however, to the presence or absence of infinite plays in $T_\sigma$: it is quick to show that once we pass to the intrinsic quotient, any such distinction vanishes.
 
@@
     \begin{description}
-      \item[Divergences come from plays] If $d\in D_\sigma$ then there exists $s\prefix d$ such that $s\in T_\sigma\cap D_\sigma$.
+      \item[Divergences come from traces] If $d\in D_\sigma$ then there exists $s\prefix d$ such that $s\in T_\sigma\cap D_\sigma$.
       \item[Diverge-or-reply] If $s\in T_\sigma$ is an $O$-position, then either $s\in D_\sigma$ or $sa\in T_\sigma$ for some $sa$.
@@
 
-Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself a legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
+Note that there is no need to consider separately, as Harmer and McCusker do, divergences that arise through `infinite chattering': in our model, we will see that a case of infinite chattering between strategies $\sigma$ and $\tau$ is itself a legal interaction between the two strategies, which is necessarily divergent (because it is infinite) and therefore gives rise to some divergence in $\sigma;\tau$.
 
@@
   Let $\sigma$ be a strategy for a game $A$.  
-  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of countably many complete strategies; i.e., there exist $\sigma_n$ such that $T_\sigma=\bigcup T_{\sigma_n}$ and $D_\sigma=\bigcup D_{\sigma_n}$.
+  We say that $\sigma$ is \emph{locally complete} if it may be written as the union of complete strategies; i.e., there exist $\sigma_i$ such that $T_\sigma=\bigcup T_{\sigma_i}$ and $D_\sigma=\bigcup D_{\sigma_i}$.
+  Note that since $T_\sigma$ and $D_\sigma$ are countable sets (because there are countably many recursive plays), this union may be taken to be countable.
 \end{definition}
 
-Henceforth, we use `strategy' to mean \emph{locally complete strategy}.
-
-We need to show that the composition of locally complete strategies is locally complete.  
-Note that the composition of \emph{complete} strategies is not necessarily complete: for example, our term $N$ above can be written as $N'\;\wn$, where $N'$ is a deterministic term with complete denotation $\nu'$.
-Then we have $\nu=\top_{\bN};\nu'$, but $\nu$ is not complete.
-However, we can show that the composition of \emph{deterministic} complete strategies is complete; since a locally complete strategy may always be written as the union of complete deterministic strategies, this is sufficient to show that the composition of locally complete strategies is locally complete.
+It will be slightly more convenient to use an equivalent definition, based on unions of \emph{deterministic} strategies, which are a special case of complete strategies.
 
@@
     \item it is complete;
-    \item if $sab,sac$ are $P$-plays in $T_\sigma$ then $b=c$ and the justifier of $b$ is the justifier of $c$;
+    \item if $sa,sb$ are $P$-plays in $T_\sigma$ then $a=b$ and the justifier of $a$ is the justifier of $b$;
     \item if $s\in D_\sigma$ then either $s$ is infinite or there is no $a$ such that $sa\in T_\sigma$.
@@
 \end{definition}
+
+We say that a strategy $\sigma$ is \emph{lively} or \emph{locally deterministic} if there exists a collection of deterministic strategies $\sigma_i$ such that $T_\sigma=\bigcup T_{\sigma_i}$ and $D_\sigma=\bigcup D_{\sigma_i}$.
+It is clear that a strategy is lively if and only if it is locally complete, and that the collection of $\sigma_i$ may again be taken to be countable.
+
+From now on, we will use \emph{strategy} to mean \emph{lively} (or \emph{locally complete}) \emph{strategy}.
+This means that we will need to show that the composition of lively strategies is again lively.
 
@@
 
+It is, of course, true that the composition of deterministic strategies is deterministic, but we do not really need this fact.
+
 \begin{corollary}
@@
 \end{proof}
-
-Our proof for Corollary \ref{cor:diverge-or-reply} really makes use of the fact that a locally complete strategy is \emph{lively} in the sense of \cite{LevyGsInfinite}; i.e., locally deterministic.  
-Our definition is slightly stronger than liveliness, because it insists that the union of complete strategies be countable.
-This will be essential to our definability result.
 
@@
 
-The resulting category $\G^\oc_{D,vis}$ of games and deterministic visible strategies is a fully abstract model of Idealized Algol \cite{SamsonGuyIAPassive}.
+After passing to the intrinsic quotient, the resulting category $\G^\oc_{D,vis}$ of games and deterministic visible strategies is a fully abstract model of Idealized Algol \cite{SamsonGuyIAPassive}.
 
@@
 
-If $\sigma$ is locally complete, we say that $\sigma$ is \emph{recursive} if $\sigma$ is the union of complete recursive strategies $\sigma_1,\sigma_2,\cdots$, where the map $i\mapsto \sigma_i$ is a recursive function $\bN \to (\bN \to \bN) \to 2$.
+If $\sigma$ is lively, we say that $\sigma$ is \emph{recursive}, and if $\sigma$ is the union of complete recursive strategies $\sigma_1,\sigma_2,\cdots$, where the map $i\mapsto \sigma_i$ is a recursive function $\bN \to (\bN \to \bN) \to 2$.
+
+Note that there are plenty of strategies that we want that are not the union of a recursive sequence of \emph{deterministic} strategies -- for example, the strategy on $(\bN\to\bC)\to\bC$ that calls its natural-number argument infinitely many times is complete and has no $O$-branching, but its infinite traces include every recursive sequence of natural numbers.
+
+Using these definitions, it seems to be hard to prove that the composition of recursive strategies is itself a recursive strategy: the tricky point is to show that the decomposition into complete strategies may still be taken to be given by a recursive strategy.
+The example in the previous paragraph shows that we cannot use the same proof as we did in the non-recursive case, which used deterministic strategies.  
+Fortunately, we do not need to be able to show that the composition of recursive strategies is recursive in order to prove our full abstraction result, so we leave this problem for future work.
 
@@
   Then the strategy $\Det(\sigma)$ is very easy to describe.  
-  For each $O$-position $sa\in T_\sigma$, we have some set $B$ of possible replies to $sa$, which we order as $b_1,b_2,\cdots$, where $\code_A(b_1)<\code_A(b_2)<\cdots$.  
+  For each $O$-position $s\in T_\sigma$, we have some set $B$ of possible replies to $s$, which we order as $b_1,b_2,\cdots$, where $\code_A(b_1)<\code_A(b_2)<\cdots$.  
   We insert a request to the oracle for a natural number; then, depending on her answer $j$, we play the next move as follows:
@@
     \item If $\code_A(b_n) < j \le \code_A(b_{n+1})$ then play $b_{n+1}$.
-    \item If $j = 0$ and $sa\in D_\sigma$, then play nothing, and put the resulting play inside $D_{\Det(\sigma)}$.  
+    \item If $j = 0$ and $s\in D_\sigma$, then play nothing, and put the resulting play inside $D_{\Det(\sigma)}$.  
       Otherwise, play $b_1$.
@@
 
+We model the language compositionally, using denotations as in \cite{mcCHFiniteND} for the nondeterministic constants and modelling $\wn$ using the strategy $\top_{\bN}\from \bN$.
+
 Any term $M\from T$ of Idealized Algol with countable nondeterminism may be written as $M = C[\wn]$, where $C$ is a multi-holed context not involving the constant $\wn$.  
 Then the term $\lambda n.C[n]$ is a term of Idealized Algol, and therefore has a denotation $\oc\bN \to \deno{T}$ as in \cite{SamsonGuyIAPassive}.
-We define the denotation of $M$ to be given by the composite
+
+\begin{lemma}
+  The term $C[\wn]$ has the same denotation as the term $(\lambda n.C[n])\wn$.
+\end{lemma}
+
+\begin{proof}
+  This is a straightforward argument by structural induction on $C$, and the constant $\top_\bN$ does not really play a role.  
+  We prove inductively on $T$ that if $\Gamma\ts C[\wn]\from T$ is a term-in-context, then its denotation may be given by the following composite.
   \[
-  I \xrightarrow{\top_{\bN}}
-  \oc \bN \xrightarrow{\deno{\lambda n.C[n]}}
-  \deno{T}\,.
+    \deno{\Gamma}
+    \xrightarrow{\lunit;(\top_{\bN}\times\id)}
+    \bN\times\deno{\Gamma}
+    \xrightarrow{\deno{\Gamma,n\from\nat\ts C[n]\from T}}
+    \deno{T}
     \]
-In other words, we interpret the constant $\wn$ using the strategy $\top_{\bN}$ for $\bN$.
+\end{proof}
 
@@
 
+Corollary \ref{cor:adequacy} is very general, and is intended to be applied in multiple situations.  
+In particular, it may be applied to a game semantics in which we define a `nondeterministic visible strategy' on a game $A$ to be a deterministic visible strategy for $\bN\to A$, up to a suitable equivalence relation.
+This model is an example of a much more general construction that is the subject of ongoing research by the authors.  
+In this sense, our main model based on nondeterministic strategies is not necessary in order to obtain our full abstraction result.  
+Nevertheless, we felt it important to give a model based on nondeterministic strategies, since these are the `natural' game semantic interpretation of nondeterminism.
+
 \subsection{Intrinsic Equivalence and Soundness}
@@
 
-For proving full abstraction , it is necessary to take the intrinsic quotient in order to identify, for example, the denotations of $\lambda n.\Omega$ and $\lambda n.\IfO n\;\Omega\;\Omega$ of type $\nat\to\nat$.
-These terms are clearly observationally equivalent, but their denotations are not equal; for example, $q\in D_{\deno{\lambda n.\Omega}}$, but $q\not\in D_{\deno{\lambda n.\IfO n\;\Omega\;\Omega}}$.
+For full abstraction, we need to take the intrinsic quotient in order to identify, for example, the terms $\lambda n.\Omega$ and $\lambda n.\IfO n\;\Omega\;\Omega \from \nat\to\nat$.  
+These terms are observationally equivalent, but their denotations are not equal; for example, $q\in D_{\deno{\lambda n.\Omega}}$, but $q\not\in D_{\deno{\lambda n.\IfO n\;\Omega\;\Omega}}$.
 
@@
 Moreover, for any $s\in T_\sigma$, we have a particular branch of that game in which play starts at $s$.  
-We say that $s$ is \emph{unreliable} if player $P$ has a strategy for the game starting at $s$ that ensures that play eventually ends up in $D_\sigma$.
+We say that $s$ is \emph{unreliable} if player $P$ has a strategy for the game starting at $s$ that ensures that the (possibly infinite) limiting play is in $D_\sigma$.
 
@@
 An additional benefit of the retention of branching time information is that we no longer need to keep track of infinite plays in order to model unbounded nondeterminism.  
+Tsukada and Ong's primary model was based on sheaves over a site of plays, but they also give a more direct way of characterizing nondeterministic innocence, based on ideas by Levy \cite{levy2014morphisms}.
+
 The model given in \cite{TsukadaSheaves} is not sound for must-equivalence, but the authors make the claim that it their model may be easily modified to yield a model that \emph{is} sound for this type of equivalence, using the same techniques from \cite{mcCHFiniteND} that we have used.

### 2018-11-08 cones/presentation/presentation.tex
Haven't made a commit for ages.

\documentclass{beamer}

\let\NOTARTICLE=1
\let\BEAMER=1
\let\FEWFONTS=1

\newenvironment{theindex}
 {\let\item\par
  %definitions for subitem etc
  }{}
\newcommand\indexspace{}

\usepackage{listings}
\lstset{
  mathescape
}

\input{../../common/preamble}

\title{A Fully Abstract Game Semantics for Countable Nondeterminism}
\subtitle{CSL 2018, Birmingham}

\author{{\ul W. John Gowers} and James Laird}

\begin{document}

\section{Countable nondeterminism}

\begin{frame}
  \frametitle{Countable nondeterminism}

  \pause

  Motivation: if we can build a \emph{fair} task scheduler, then we can use it to construct a countable nondeterminism machine.

  \pause

  But [Dijkstra, ??], countable nondeterminism is \emph{impossible}! \pause{} [Under a continuity assumption]

  \pause

  Failure of continuity / algebraicity.  
  E.g.:
  \begin{align*}
    <_m,<_\infty & \from \nat \to \nat \\
    <_m n & = \text{If } n < m \text{ then } \0 \text{ else }\Omega\\
    <_\infty n & = \0\,,
  \end{align*}
  but
  \begin{align*}
    <_m \wn & \equiv \0\text{ or }\Omega \\
    <_\infty \wn & \equiv \0\,.
  \end{align*}

\end{frame}

\begin{frame}[fragile]
  \frametitle{Must-convergence}

  Nondeterministic languages differ from deterministic ones in that a given term $M$ may admit multiple different small-step reduction rules.

  If $M\from o$ is a term of a nondeterministic language, we say that $M$ \emph{must converge}, and write $M\mustconverge$, if every possible small-step evaluation path of $M$ eventually terminates at some observable value.

  \pause

  \begin{minipage}{0.5\textwidth}
    \begin{lstlisting}
$\lambda$ c . {
  for i = 0 to ? {
    c;
  }
}
    \end{lstlisting}
  \end{minipage}\pause\quad\begin{minipage}{0.3\textwidth}
    \begin{lstlisting}
$\lambda$ c . {
  while (TRUE) {
    c;
  }
}
    \end{lstlisting}
  \end{minipage}

\end{frame}

\begin{frame}
  \frametitle{Must-convergence, continued}
\end{frame}

\end{document}

### 2018-11-08 effects/effects.tex
Haven't made a commit for ages.

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a proceedings volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{svproc}
%
% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{xspace}
\usepackage{IEEEtrantools}
\usetikzlibrary{cd}
\usepackage{mathpartir}
\def\UrlFont{\rmfamily}

\newcommand\C{\mathcal{C}}
\newcommand\D{\mathcal{D}}
\newcommand\F{\mathcal{F}}
\newcommand{\suchthat}{\,\colon\,}
\newcommand{\esuchthat}{\,.\,}
\newcommand\from{\,\colon\,}
\newcommand\object\colon
\DeclareMathOperator{\ac}{ac}
\DeclareMathOperator{\End}{End}
\newcommand{\passoc}{\texttt{passoc}}
\newcommand{\assoc}{\texttt{assoc}}
\newcommand\tensor\otimes
\newcommand\run{\texttt{r}}
\newcommand\lun{\texttt{l}}
\newcommand\lunit{\texttt{lunit}}
\newcommand\runit{\texttt{runit}}
\renewcommand\implies\multimap
\newcommand{\pfc}{\boldsymbol{\cdot}}
\newcommand\Mellies{Melli\`{e}s\xspace}

\newcommand{\catname}[1]{\mathbf{#1}}
\newcommand{\Set}{\catname{Set}}
\newcommand{\Surj}{\catname{Surj}}
\newcommand{\powerset}{\mathcal P}

\DeclareMathOperator{\Prof}{Prof}
\DeclareMathOperator{\Kl}{Kl}

\makeatletter
\newcommand{\colim@}[2]{%
  \vtop{\m@th\ialign{##\cr
    \hfil$#1\operator@font colim$\hfil\cr
    \noalign{\nointerlineskip\kern1.5\ex@}#2\cr
    \noalign{\nointerlineskip\kern-\ex@}\cr}}%
}
\newcommand{\colim}{%
  \mathop{\mathpalette\colim@{\rightarrowfill@\textstyle}}\nmlimits@
}
\makeatother

\begin{document}
\mainmatter              % start of a contribution
%
\title{A Kleisli-like construction for Parametric Monads, with Examples}
%
\titlerunning{Dum-di-dum}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{}
%
\authorrunning{} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{}
%
\institute{University of Bath, Claverton Down Road, Bath.  
BA2 7AY,\\
\email{wjg27@bath.ac.uk},\\ WWW home page:
\texttt{http://people.bath.ac.uk/wjg27}}

\maketitle              % typeset the title of the contribution

\begin{abstract}
\keywords{denotational semantics, category theory, game semantics}
\end{abstract}

\section{Introduction}

\subsection{Monads and Kleisli categories}

This paper is about general frameworks for modelling effects in a categorical semantics.  
The seminal paper in this field is Moggi's \emph{Computational Lambda-Calculus and Monads} \cite{Moggi}, which first put forward the idea that if $\C$ is a categorical model of a programming language, then we can simulate an effect in that language via a suitable \emph{monad} on $\C$.  
Given such a monad, its Kleisli category $Kl_M\C$ is then a model of a language formed by adding the effect to the original language.

Spivey \cite{Spivey} and Wadler \cite{Wadler1,Wadler2} have transferred this theory to the real world by using monads as programming tools, particularly in the Haskell programming language.

Recent progress in the field of game semantics, however, has shown that monads and Kleisli categories are not the be-all and end-all of modelling effects.  
There are perfectly game semantic models of effects such as state and nondeterminism that do not arise as the Kleisli category for a monad on some more basic category of games.  
These models are typically built up using intuition -- for example, by relaxing the determinism condition on strategies to give a model of a nondeterministic language -- and do not readily fit into any category theoretic framework the way Kleisli categories do.  
The goal of this paper is to examine some possible frameworks that will allow us to study these and other models in a systematic way.

A closely related problem is that of using a common technique to model a particular effect in different settings.  
Many of our favourite monads (e.g., the powerset monad on $\Set$ for nondeterminism) live in some particular category and cannot readily be set up in other categories.

Before we start, it is worth mentioning one example of a Kleisli category arising naturally in game semantics.  
If we read Ghica's work on \emph{slot games} \cite{SlotGames}, it is not difficult to show that the category he constructs is in fact isomorphic to the Kleisli category for the \emph{reader monad} $\mathbb{C}\to \_$, where $\mathbb{C}$ is the game corresponding to a singleton set.

Since the reader monad is entirely built out of the Cartesian closed structure of the category, we can perform a similar trick in many different settings, although perhaps not as successfully as in game semantics.

\subsection{Promonads}

It is instructive at this point to see what happens if we generalize from functors to profunctors.  
We define a \emph{promonad} on a category $\C$ to be a monoid in the monoidal category $\Prof[\C,\C]$ of endo-profunctors on $\C$.  
This concept generalizes that of a monad, since an endofunctor $M\from \C\to\C$ may be identified with the profunctor $\C[\_,M(\_)]\from \C^{op}\times\C\to\Set$.

Since the set $\C[A,MB]$ is precisely the set of Kleisli morphisms from $A$ to $B$, it is natural to wonder whether we can perform a Kleisli-type construction on a promonad as well.  
it turns out that we can: if $\D\from \C^{op}\times\C\to\Set$ is a promonad, then we may define a category (also called $\D$) whose objects are the objects of $\C$, and where the morphisms from $A$ to $B$ are the elements of the set $\D(A,B)$.
The promonad action
\[
  (\D\pfc\D)(A,C) = \int^{B}\D(A,B)\times\D(B,C) \to \D(A,C)
  \]
gives us composition in our category and the unit
\[
  1(A,B)=\C[A,B]\to \D[A,B]
  \]
gives us a functor $\C\to\D$ (and, in particular, the identity morphisms).

In fact, the converse is true: if $\C$ and $\D$ are categories with the same objects and $J\from \C\to\D$ is an identity-on-objects functor, then the functor $\D(JA,JB)=\D(A,B)\from\C^{op}\times\C\to\Set$ may be given the structure of a promonad on $\C$.  
Thus, the rather complicated definition of a promonad is in fact equivalent to the much simpler idea of an identity-on-objects functor.
We shall therefore use the word `promonad' to mean both things.

In one sense this is very exciting for us, because we can see that promonads generalize not only monads, but also a very large number of the models developed in Game Semantics.  
For example, the inclusion of the category of games and deterministic strategies into the category of games and nondeterministic strategies is the identity on objects, so it is a promonad.  
So is the inclusion of the category of games and innocent strategies into the category of games and visible strategies.

More generally, this fits in with the idea that effects should not normally create new types, but should instead give us more flexibility when it comes to writing programs -- exactly what is modelled by an identity-on-objects functor.

On the other hand, the sheer generality of promonads means that they don't give us any ways to actually create new models, since the data required to specify one is the entire category that we are trying to build.

One way of describing the purpose of this work, then, is to discover classes intermediate between monads and promonads that are more general than pure monads but can still be specified in a concise way that allows us to transfer them between different settings.

\subsection{Monads on presheaf categories}

We can think of an endo-profunctor $\F\from \C^{op}\times\C\to \Set$ as a functor $\C\to [\C^{op},\Set]$.  
Since the Yoneda embedding exhibits $[\C^{op},\Set]$ as the free cocompletion of $\Set$, this can alternatively be characterized as a colimit-preserving endofunctor on $[\C^{op},\Set]$.  
Similarly, any promonad on $\C$ can alternatively be considered as a monad on $[\C^{op},\Set]$ whose underlying endofunctor preserves colimits.

\subsection{Parametric monads}

\Mellies \cite{ParametricMonads}, following work by Smirnov \cite{Smirnov2008}, has demonstrated that the concept of a lax monoidal category action is a useful generalization of that of a monad.  
A lax action of a monoidal category $\C'$ upon a category $\C$ is a lax monoidal functor $\C'\to \End[\C]$; monads are the special case when $\C'$ is trivial.  
For this reason, \Mellies renames lax monoidal actions to `parametric monads', where we think of the action of $\C'$ as a kind of monad on $\C$ that is parameterized by the objects of $\C'$.

This idea has been further generalized by Katsumata \cite{Katsu}, who has given a definition of a `Kleisli-like resolution' of a parametric monad.  
This particular construction, which takes a parametric monad on a category $\C$ parameterized by a monoidal category $\C'$ and yields a new category, generalizes many important properties of the Kleisli category -- in particular, it gives us an adjunction with the original category -- but it does not fit into our framework, since the objects of the category it creates are not the objects of the original category $\C$, but pairs of an object of $\C$ and an object of $\C'$.

Once again, it is useful to generalize to profunctors.  
First, if $\C$ is a category and $\C'$ a monoidal category, we define a \emph{parametric promonad on $\C$ parameterized by $\C'$} to be a lax monoidal functor $\C'\to\Prof[\C,\C]$.

As with promonads, we can now look at what we have defined and try to recast it as a particular kind of category.  
Suppose that $\D\from \C'\times\C^{op}\times\C$ is a parametric promonad on $\C$ parameterized by $\C'$.  
After some thought, we can see that $\D$ corresponds to a category whose objects are the objects of $\C$ and where the morphisms from $A$ to $B$ are labelled by objects of $\C'$ in such a way that the composition of a morphism labelled with $X$ and a morphism labelled with $Y$ is a morphism labelled with $X\tensor Y$.

One way to state this is as follows.  
Given a parametric promonad $\D\from \C'\times\C^{op}\times\C\to \Set$, we define a bicategory $\D^2$:
\begin{itemize}
  \item whose objects are the objects of $\C$,
  \item where the $1$-morphisms from $A$ to $B$ are pairs $(X,f)$, where $X$ is an object of $\C'$ and $f\in\D(X,A,B)$
  \item and where the $2$-morphisms from $(X,f)$ to $(Y,g)$ are morphisms $h\from X\to Y$ in $\C'$ such that $\D(h,A,B)(f)=g$.
\end{itemize}
This bicategory comes equipped with two important bifunctors:
\begin{itemize}
  \item a bifunctor $J\from \C\to\D^2$ (where we consider $\C$ as a bicategory with only identity $2$-morphisms;
  \item a bifunctor $l\from \D^2\to \C'$ given by the `labelling' (considering $\C'$ as a bicategory with a single object).
\end{itemize}

In order to get a promonad resolution of the parametric promonad, then, we need to convert this bicategory into a $1$-category $\D$, which we do by quotienting out the $1$-morphisms in $\D^2$ by the action of the $2$-morphisms: i.e., the smallest equivalence relation such that two $1$-morphisms are related if there is a $2$-morphism from one to the other.

More explicitly, the set of $1$-morphisms from $A$ to $B$ in our new category will be given by the following colimit.
\[
  \D(A,B) = \colim_{X\object\C'} \D(X,A,B)
  \]
This category $\D$ now admits an identity-on-objects functor from $\C$, meaning that we have found a natural collapse from parametric promonads to ordinary promonads.

In the particular case that the parametric promonad is in fact a parametric \emph{monad}, then we will call the category we obtain $\C/\C'$.  
The morphisms in $\C/\C'$ are given by
\[
  \C/\C'(A,B)=\colim_{X\object\C'} \C(A,X.B)\,,
  \]
with the composition of $f\from A\to X.B$ and $g\from B\to Y.C$ being given by the composite
\[
  A \xrightarrow{f}
  X.B \xrightarrow{X.g}
  X.Y.C \to
  (X\tensor Y).C\,.
  \]
Note that if $\C'$ is the trivial category (so that the action is in fact a monad), then the category $\C/\C'$ is the usual Kleisli category.

\subsection{Effects, monads and colimits}

The colimit that appears in the definition of the category $\C/\C'$ is instructive, because it is linked to the fact that many important monads may be expressed as colimits.  
For example, let $\Surj$ be the category of sets and surjections.  
Then, if $A$ is a set, we have
\[
  \powerset(A) \cong \colim_{X\object\Surj^{op}} [X,A]\,,
  \]
naturally in $A$.

This is useful, because the body of the colimit -- i.e., the function set $[X,A]$ -- has a natural equivalent inside any Cartesian closed category that admits a functor out of $\Set$.  
Moreover, the functor $[X,A]$ is actually an \emph{action} of $\Surj^{op}$ (with the Cartesian product) upon the category of sets.  
So even though we cannot define the powerset \emph{monad} inside arbitrary Cartesian closed categories, we can still define this action of $\Surj^{op}$.

Unfortunately, when we try to apply our construction to this action in the category of sets, we do not get the usual Kleisli category for the powerset monad.  
To see why, note that from the discussion above, we have
\begin{IEEEeqnarray*}{rCl}
  \Set/\Surj^{op}(A,B) & = & \colim_{X\object\Surj^{op}}[A,[X,B]] \\
  & \cong & \colim_{X\object\Surj^{op}}[X,[A,B]] \\
  & \cong & \powerset([A,B])\,,
\end{IEEEeqnarray*}
while the morphisms in the Kleisli category take a different form:
\[
  \Kl_{\powerset}\Set(A,B) = [A,\powerset(B)]\,.
  \]
Nevertheless, there are still a few things we can take from this.  
The sets $\powerset([A,B])$ and $[A,\powerset(B)]$ are not equal, but there is still a natural function
\[
  \powerset([A,B]) \to [A,\powerset(B)]\,,
  \]
that sends a set $\F$ of functions to the function $h$ (the \emph{amalgamation} of $\F$) where
\[
  h(a) = \{f(a)\suchthat f \in \F\}\,.
  \]
This amalgamation function is not \emph{quite} surjective: for example, suppose that $g\from \{0,1\}\to \powerset(\{0\})$ sends $0$ to $\{0\}$ and $1$ to the empty set.  
Then $g$ is not the amalgamation of any set of functions $\{0,1\}\to\{0\}$.  
However, if we use the \emph{nonempty powerset monad} $\powerset^+$ (which corresponds to taking the colimit over the opposite of the category $\Surj^+$ of nonempty sets and surjections), then the amalgamation function gives us a surjection
\[
  \powerset^+([A,B])\twoheadrightarrow [A,\powerset^+(B)]\,.
  \]
This means that we can recover the Kleisli category for the nonempty powerset monad on $\Set$ by taking the quotient by a suitable equivalence relation to the category $\Set/(\Surj^{+\,op}$).

In fact, this surjection has a natural right inverse, formed by sending a function $h\from A\to\powerset^+(B)$ to the \emph{largest} possible set $\F\subseteq[A,B]$ such that for all $f\in \F$ and $a\in A$, $f(a)\in h(a)$.
The composition of these inverses sends a set of functions $A\to B$ to its `amalgamation closure':
\[
  \ac(\F) = \{g\from A \to B\suchthat\forall a\in A\esuchthat g(a)=f(a)\text{ for some $f\in \F$}\}\,.
  \]
By restricting our set of morphisms, then, to those that are fixed points of this operator, we may recover the Kleisli category for $\powerset^+$.

In the next section, we will see how to generalize this idea to other monads, and to other categories.

\subsection{Weakly filtered colimits}

Suppose we have a lax action of a monoidal category $\C'$ upon a cocomplete category $\C$.  
Then we may copy the collapse from parametric promonads to promonads and define a monad on $\C$ given by:
\[
  M A = \colim_{X\object\C'}A.X\,.
  \]
Unfortunately, as in the case of the powerset monad above, this transformation does not commute with the collapse from parametric promonads to promonads.  
Indeed, if we consider our action as a parametric promonad and apply the collapse, then we get a category where the morphisms from $A$ to $B$ are given by the colimit
\[
  \colim_{X\object\C'} \C(A,X.B)\,,
  \]
while the morphisms from $A$ to $B$ in the Kleisli category for the monad $M$ are given by
\[
  \C(A,\colim_{X\object\C'} X.B)\,.
  \]
There is a natural morphism from the first colimit into the second expression, but it is not an isomorphism in general.
If $\C$ is the category of sets, there is a well known result that states that if $\C'$ is a $\kappa$-filtered category and $|A|<\kappa$, then the colimit will commute with the functor $[A,\_]$, but this does not help us, since the category $\C'$ is not filtered in most of the cases we are interested in (e.g., the category $\Surj^{op}$ has not got morphisms coequalizing parallel pairs, since such maps cannot be chosen to be surjective in general).

Instead, we try for the next best thing, which is to show that the natural map $\colim_{X\object\C'}\C(A,X.B)\to\C(A,\colim_{X\object\C'}X.B)$ is a surjection if $\C'$ satisfies some weaker conditions.

We define (see, for example, \cite[Def. 16]{WeaklyFiltered}) a \emph{$\kappa$-weakly filtered category} to be one in which every \emph{discrete} diagram of size $<\kappa$ admits a cocone; i.e., a non-empty category such that whenever $(X_\alpha)_{\alpha<\kappa}$ is a collection of objects we have some object $Y$ and morphisms $X_\alpha\to Y$ for each $\alpha$.

\begin{example}
  The category $\Surj^{+\,op}$ is $\kappa$-weakly filtered for arbitrary $\kappa$, because if $(X_\alpha)_{\alpha<\kappa}$ is a collection of sets, then we can take their Cartesian product, and the projections will be surjective.

  The category $\Surj^{op}$ is not weakly filtered, because if there is a surjection from an object $X$ to the empty set, then there is no surjection from $X$ to any other set.
\end{example}

The importance of $\kappa$-weakly filtered limits is shown by the following result.

\begin{proposition}
  \label{prop:weakly-filtered}
  If $\C'$ is a $\kappa$-weakly filtered category, $D\from \C'\to \Set$ is a functor and $A$ is a set with cardinality less than $\kappa$, then the natural function
  \[
    \colim_{X\object\C'}[A,D(X)]\to [A,\colim_{X\object\C'}D(X)]
    \]
  is a surjection.
\end{proposition}
\begin{proof}
  Given a function $h\from A \to \colim_{X\object\C'}D(X)$, for each $a\in A$, choose some $X_a\object\C'$ such that $h(a)\in D(X_a)$.  
  Since $\C'$ is $\kappa$-weakly filtered, there is some object $Y$ of $\C'$ that admits morphisms out of all of the $X_a$, and therefore $h$ may be considered as a function $A \to D(Y)$. \qed
\end{proof}

By setting $D(X)=X.B$, this means that if we have an action of $\C'$ on $\Set$, where the monoidal category $\C'$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\C'\to\Kl_M\Set$.

Moreover, if the colimit satisfies additional properties, then the $Y$ in the proof of Proposition \ref{prop:weakly-filtered} can be chosen in a functorial manner, so that we get a faithful right inverse to this full functor.

\begin{example}
  If $f\from A \to \colim_{X\object\Surj^{+\,op}}[X,B]$ is a function with $f(a)\in [X_a,B]$ for each $a$, then $f$ is equivalent to a function
  \[
    \tilde{f}\from A \to \left[\prod_{a\in A}X_a,B\right]
    \]
  via the surjections $\prod_{a\in A}X_a\to X_b$ for each $b\in A$.  
  The operator $f\mapsto\tilde{f}$ is well-defined in this case, and gives rise to the amalgamation functor that we considered in the previous section.
\end{example}

The point of these last two sections can be summarized as follows.  
If a monad $M$ on $\Set$ can be expressed as the colimit of an action of a weakly filtered monoidal category $\C'$ on $\Set$, then we do not lose very much by considering the category $\Set/\C'$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.  
More specifically, there is a full functor $\Kl_M\Set\to \Set/\C'$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.

The benefit of reasoning about the action of $\C'$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories.  
For instance, the action of $\Surj^{+\,op}$ on $\Set$ may be replicated inside any monoidal closed category that admits a functor out of the category of sets (for example, most models of PCF or Idealized Algol).

\subsection{Plan for the paper}

The rest of this paper will consist in two sections.  
In the first, we will give a more detailed account of the construction that allows us to build a promonad (i.e., a category) out of a parametric monad.

In the second section, we will give a fully abstract game semantics for the language Probabilistic Algol (PA).  
This is by no means a new result -- the paper \cite{DanosHarmer} that introduced PA also gave it a fully abstract game semantics.  
Instead, the point of this section will be to demonstrate how the ideas we have outlined can be applied systematically to yield fully abstract models of programming languages.

\section{A Kleisli-style construction for parametric monads}

\subsection{Parametric monads}

Let $\C'$ be a monoidal category and let $\C$ be a category.  
Then a \emph{lax left action} of $\C'$ on $\C$ is a functor $\_.\_\from \C'\times\C\to \C$ that gives rise (through currying) to a lax monoidal functor $\C'\to \End[\C,\C]$.  
In other words, we have natural transformations $\passoc_{X,Y,A}\from X.Y.A\to (X\tensor Y).A$ and $\lun_A\from A \to I.A$ making the following diagrams commute for all objects $A$ of $\C$ and $X,Y,Z$ of $\C'$.

\begin{mathpar}
  \begin{tikzcd}[column sep=6em]
    X.Y.Z.A \arrow[dr,"X.\passoc_{Y,Z,A}"'] \arrow[r, "\passoc_{X,Y,Z.A}"]
      & (X \tensor Y).Z.A \arrow[r, "\passoc_{X\tensor Y,Z,A}"]
        & ((X \tensor Y) \tensor Z).A \arrow[d, "\assoc_{X,Y,Z}.A"] \\
    %
      & X.(Y\tensor Z).A \arrow[r, "\passoc_{X,Y\tensor Z,A}"]
        & (X\tensor(Y\tensor Z)).A
  \end{tikzcd}
  \and
  \begin{tikzcd}
    X.A \arrow[r, "\lun_{X.A}"] \arrow[dr, "\lunit_X.A"']
      & I.X.A \arrow[d, "\passoc_{I,X,A}"] \\
    %
      & (I \tensor X) . A
  \end{tikzcd}
  \and
  \begin{tikzcd}
    X.A \arrow[r, "X.\lun_A"] \arrow[dr, "\runit_X.A"']
      & X.I.A \arrow[d, "\passoc_{X,I,A}"] \\
    %
      & (X\tensor I).A
  \end{tikzcd}
\end{mathpar}

\begin{example}
  \begin{itemize}
    \item Any monad $M$ is an action of the trivial category on its underlying category $\C$, regarding $MA$ as the action $I.A$.
      The natural transformation $\passoc_{A,I,I}$ is precisely the monad action on $A$:
      \[
        I.I.A = MMA \to M A = I.A = (I\tensor I).A\,.
        \]
      Dually, any lax action gives rise to a monad on the category being acted upon, by setting $MA = A.I$.
    \item If $\C$ is also a monoidal category and $J\from \C'\to \C$ is a lax monoidal functor with monoidal coherence $\mu$, then there is an action of $\C'^{co}$ (i.e., $\C'$ with the opposite monoidal product) on $\C$ given by
      \[
        A.X = A \tensor JX\,,
        \]
      and
      \[
        \passoc_{X,Y,A}=
        (A \tensor JY) \tensor JX \xrightarrow{\assoc_{A,JX,JY}}
        A \tensor (JY \tensor JX) \xrightarrow{A \tensor \mu_{X,Y}}
        A \tensor J(Y\tensor X)\,.
        \]
      We sometimes refer to a left action of the opposite category $\C'^{co}$ on $\C$ as a \emph{right action} of $\C'$ on $\C$.  
      In that case, we write $X.A$ instead of $A.X$, so that the coherences become
      \begin{gather*}
        \passoc_{A,X,Y}\from A.X.Y \to A.(X\tensor Y)\\
        \run_A\from A \to A.I\,.
      \end{gather*}

    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\C'$ on $\C$ given by
      \[
        A.X = jX \implies A
        \]
      and
      \[
        \passoc_{A,X,Y}=jY \implies (jX \implies A) \to
        (jY \tensor jX) \implies A \xrightarrow{\nu_{Y,X}\implies A}
        j(Y \tensor X) \implies A\,.
        \]
    \item The intersection of the first two examples is the \emph{writer monad} given by $M_WX = X\tensor W$ for any monoid $W$ in $\C$.  
      The intersection of the first and third examples is the \emph{reader monad} given by $M^RX = R \implies X$ for any comonoid $R$ in $\C$ (and, in particular, for any object $R$ if $\C$ if the monoidal product in $\C$ is Cartesian).

      We shall therefore call an action of the form $A \tensor JX$ a \emph{writer-style action} and one of the form $JX \implies A$ a \emph{reader-style action}.
    \item We can define an \emph{oplax action} of $\C'$ on $\C$ to be a lax action of $\C'$ upon the opposite category $\C^{op}$.  
      In this case, the coherence $\passoc$ goes from $A.(X\tensor Y)$ to $A.X.Y$.  
      As monads are lax actions of the trivial category, so are comonads oplax actions of the trivial category.
  \end{itemize}
\end{example}

\bibliographystyle{spbasic}
\bibliography{effects}

\end{document}

### 2018-11-08 exponentials/exponentials.tex
Haven't made a commit for ages.

\documentclass{article}

\usepackage{skull}

\input{../common/preamble}

\newcommand{\ocajm}{\oc_{AJM}}
\newcommand{\ocseq}{\oc_{seq}}

\begin{document}

\section{Games and strategies}

\subsection{Games}

According to \cite{ajmPcf}, a \emph{game} is given by a tuple $(M_A,\lambda_A,P_A,\approx_A)$ where

\begin{itemize}
  \item $M_A$is a set of \emph{moves}.
  \item $\lambda_A\from M_A\to \OP \times \QA$ designates each move as either a $P$-move or and $O$-move, and as either a \emph{question} or an \emph{answer}.
  \item $P_A$ is a non-empty prefix-closed set of finite sequences $s\in M_A^*$ such that each non-empty sequence in $P_A$ starts with an $O$-move and thereafter alternates between $O$-moves and $P$-moves.
  \item $\approx_A$ is an equivalence relation on $P_A$ satisfying the following rules.
    \begin{itemize}
      \item If $s\approx_A t$, then $s$ and $t$ have the same length.
      \item If $s\approx_A t$ and $s'\prefix s$, $t'\prefix t$ have the same length, then $s'\prefix t'$.
      \item If $s\approx_A t$ and $s\prefix s'$, where $s'\in P_A$, then there exists some $t'\in P_A$ such that $t\prefix t'$ and $s'\approx_A t'$.
    \end{itemize}
\end{itemize}

Of these, the only thing that looks slightly odd is the equivalence relation $\approx_A$.  
We will see that it is in fact essential to the model of PCF found in \cite{ajmPcf}.

\subsection{Strategies and multiplicatives}

We shall skip over the definitions of the multiplicative connectives and the composition of strategies; the definitions are all found in \cite{ajmPcf}.

A \emph{strategy} for a game $A$ is defined to be a non-empty prefix-closed set of $P$-positions in $P_A$ subject to the \emph{determinism} condition: if $sab,sac\in \sigma$, then $b=c$.

We define a relation $\approx_A$ on the set of strategies for a game $A$: we say that $\sigma\approx_A\tau$ if whenever $s\in\sigma$, $t\in\tau$ and $s\approx_At$, and whenever $s\prefix s'$, where $s'\in \sigma$, there exists $t'\in \tau$ such that $t\prefix t'$ and $s'\approx_At'$.

We will require in addition that our strategies $\sigma$ satisfy $\sigma\approx_A\sigma$; so if $s,t\in\sigma$ and $s\approx_At$, then for every $s'$ with $s\prefix s'$ there exists $t'\in\sigma$ such that $s'\approx_A t'$ and $t\prefix t'$. This makes $\approx_A$ a reflexive relation on the set of strategies; it is easy to see that it is also symmetric and transitive. We will henceforth consider strategies as being `up to' this equivalence relation.

The condition that $\sigma\approx_A\sigma$ is in fact key to the definability result for PCF.

We say that a strategy $\sigma$ is \emph{well-bracketed} if the sequence of questions and answers in any play of $\sigma$ is a well-bracketed sequence.

We say that $\sigma$ is \emph{history free} if whenever $sab, tac\in\sigma$, we have $b=c$.  
In other words, the choice that we make in $\sigma$ depends only on the last move played, and not on anything that has happened previously (in the `history') of the play.

The properties of well-bracketedness and history-freeness are both preserved by composition of strategies.

\subsection{Exponentials}

The games representing basic data types (e.g., $\nat$, where the game has a single opening $O$-move $q$, that can be replied to by player $P$ with any natural number $n$) are \emph{discrete}; i.e., the equivalence relation $\approx_A$ is the equality relation.  
Moreover, the multiplicative and additive connectives $\tensor$, $\implies$ and $\times$ preserve discreteness: they do not introduce any new equivalent-but-not-equal plays.

Non-discrete equivalence relations are introduced by the exponential connective $\oc$.  
Given a game $A$, $\oc_A$ is defined as follows.

\begin{itemize}
  \item $M_{\oc A} = \bN \times M_A$.
  \item $\lambda_{\oc A} = \lambda_A \circ \pr_2$.
  \item $P_A$ is the set of all alternating sequences $s\in M_{\oc A}^*$ such that $s\vert_i$ (i.e., $(a\vert (i,a)\in s)$) is contained in $P_A$.
\end{itemize}

All that remains is to define the equivalence relation $\approx_{\oc A}$.  
First of all, we ought to take account of the equivalence relation on $A$ itself: we say that $s\sim_At$ if for all $i$ we have $s\vert_i\approx_A t\vert_i$.

Given a function $\phi\from \bN \to \bN$ and $s\in P_{\oc A}$, we define $\phi_*s$ to be the sequence formed by replacing each move $(i,a)$ with $(\phi(i),a)$.

We say that $s\approx_{\oc A}t$ if there exists some injection $\pi\from \bN\to\bN$ such that
\[
  \pi_*s\sim_At\,.
  \]

Any exponential requires coherence morphisms.  
In this case, we need to define strategies on the following games.
\begin{gather*}
  \oc A \implies \oc A \tensor \oc A \\
  \oc A \implies \oc \oc A \\
  \oc A \implies A \\
  \oc A \implies I \\
\end{gather*}

In the first case, the \emph{contraction}, we pick some injection $\bN + \bN \hookrightarrow \bN$. 
Thus, each index on the right hand side corresponds to some index on the left in such a way that there is no overlap, and we can play by copycat.
It is then easy to see that if we choose some different injection $\bN + \bN \hookrightarrow \bN$, then the two strategies we get will be equivalent, so we can drop any mention of the particular function we have used.

Similarly, for the second morphism, the \emph{comultiplication}, we choose some injection $\bN \times \bN \hookrightarrow \bN$, and use it to play copycat between the two copies.

For the third strategy, the \emph{dereliction}, we choose some $i\in \bN$ and copy moves $a$ on the right hand side to moves $(i,a)$ on the left.  
Once again, the choice of $i$ does not change the equivaence class of this strategy.

The \emph{weakening} strategy $\oc A \implies I$ is the empty strategy.

We can see that these strategies obey the appropriate associativity and unitality laws, up to equivalence, and that they form a \emph{linear exponential comonoid}. 
This allows us to form the co-Kleisli category of that comonad, giving us our model of PCF, in which the type $\nat$ corresponds to the game $\bN$ described earlier and the type $S\iimpl T$ corresponds to the game $\oc\deno{S}\implies \deno{T}$.

Moreover, there is an adequate compositional translation from PCF terms $M\from T$ into history-free well-bracketed (equivalence classes of) strategies $\sigma=\deno{M}$ for $\deno{T}$

\subsection{Definability}

The most important result in the proof of full abstraction found in \cite{ajmPcf} is the following.

\begin{theorem}
  Given a PCF term $T$ and a compact history-free well-bracketed strategy $\sigma$ for $\deno{T}$, there exists some PCF term $M\from T$ such that $\sigma=\deno{M}$.
\end{theorem}

\subsection{The sequoidal exponential}

There is an alternative version of the exponential, found in \cite{blassgames} and \cite{hyland1997games}.  
This version is defined as follows.
\begin{itemize}
  \item $M_{\oc A} = \bN\times M_A$.
  \item $\lambda_{\oc A} = \lambda_A \circ \pr_2$.
  \item $P_{\oc A}$ is the set of all $s\in M_{\oc A}^*$ such that $s\vert_i\in P_A$ for all $i$ \textbf{and such that if $(i+1,a)$ occurs in $s$, then $(i,b)$ must occur earlier in the sequence than $s$}.

    In other words, we have to play the indices in strict order: $(q,2)(a,2)(q,1)(a,1)$ would not be a valid play in $\oc A$, but $(q,1)(a,1)(q,2)(a,2)$ would be.  
    This is in contrast to the AJM definition of the exponential, in which these would be two separate but equivalent legal plays in $\oc A$.
  \item $s\approx_{\oc A}t$ if $s\vert_i\approx_A t\vert_i$ for all $i$ (i.e., we do not introduce any additional equivalent-but-not-equal plays).
\end{itemize}

This gives rise to an alternative denotation for PCF types, in which the equivalence relation on the game $\deno{T}$ is discrete for any type $T$.  
This means that we can work in a category of games in which we don't have to mention the equivalence relation at all.  
However, for the purposes of this work, and in order that we can use the definability results from \cite{ajmPcf}, we will work in the full AJM games category.

To avoid confusion, we shall refer to this as the \emph{sequoidal exponential} $\oc_{seq}$ and to the previous version as the \emph{AJM exponential} $\oc_{AJM}$.

This exponential is also a linear exponential comonad: for example, we can define the strategy on $\ocseq A \implies \ocseq A \tensor \ocseq A$ to be the one that opens up a new copy of $A$ on the left for each copy of $A$ that we open on the right, using the order that we are forced to use. Note that this strategy, and the comultiplication $\ocseq A \implies \ocseq \ocseq A$, are not history free.

In fact, we do not have to define these morphisms explicitly, because it turns out that $\ocajm A$ and $\ocseq A$ are isomorphic for any game $A$.

\subsection{The isomorphism $\ocseq A \cong \ocajm A$}

We can define a history-free strategy $w_A$ for $\ocajm A\implies \ocseq A$ that acts as a copycat strategy: we copy the move $(i,a)$ on the right over to $(i,a)$ on the left and vice versa.  
History-freeness of this strategy is easy to see; as for $w_A \approx w_A$, we observe that as long as we play according to this strategy, only player $P$ ever introduces any new indices on the left hand side.

In the other direction, we define a strategy $\skull_A\from \ocseq A \implies \ocajm A$. The macabre symbol for this strategy is meant to indicate that it is not history free.  
In this strategy, every time player $O$ starts a new index on the right-hand side, we start a new index on the left, but instead of choosing the same index, we choose the only index we are allowed to choose, namely the first one that we have not yet used. 
This requires us to remember the index on the right so that we can copy player $O$'s reply back to that index, which is the reason why the strategy is not history free.

It is fairly easy to verify that $\skull_A;w_A$ is the identity strategy on $\ocseq A$, and that while $w_A;\skull_A$ is not the identity on $\ocajm A$, it is nevertheless \emph{equivalent} to the identity.  
It follows that $\ocseq A$ and $\ocajm A$ are isomorphic.  
However, since $\skull_A$ is not history-free, this isomorphism does not preserve history-free strategies in general.  
One consequence of this is one we have mentioned already: namely, that the comultiplication and contraction strategies for the sequoidal exponential are not history free.

In fact, since $w_A$ \emph{is} history-free, we can see that any history free strategy $\sigma$ for $\ocajm A$ will correspond to a history-free strategy $\sigma;w_A$ for $\ocseq A$.

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2018-11-08 old_effects/effects.tex
Haven't made a commit for ages.

\documentclass{article}

\input{../common/preamble}

\begin{document}

\section{Monads and Lawvere Theories}

One of the oldest ideas relating to the treatment of effects in computer science is the idea that an effect should be captured by a suitable monad (or comonad) on our category, and that the effectful category should then be given by the Kleisli category of that monad.  
Typically the base category is taken to be the category of sets, and it is not always obvious how to relate the construction to other categories -- for instance, finite nondeterminism is often regarded as being captured by some finite powerdomain monad on $\Set$.  
However, some particular examples are clearly more general.  
For example, the \emph{state monad} $S_W X = W \implies (X \tensor W)$ exists in any monoidal closed category, while the \emph{reader monad} $R_W X = W \iimpl X$ exists in any Cartesian closed category (and the equivalent \emph{reader comonad} $R^W X = X \times W$ exists in any Cartesian category).

\begin{example}
  Dan Ghica's category of \emph{slot games} is equivalent to the Kleisli category for the reader monad $R_\bC$ on a more traditional category of games, where $\bC$ is the singleton or command-type game.  
  Slot games are used to measure time complexity; we can think of the Kleisli morphism $\text{ask}\from (\bC \iimpl X) \to X$ (given, in the base category, by the identity on $(\bC \iimpl X)$) as being analagous to composing with a term $\text{wait}_T\from \bC$ that pauses for some fixed length of time.
\end{example}

What, then, distinguishes those monads and comonads on $\Set$ that have analogues in arbitrary Cartesian closed categories from those that can't? 
The answer dates back to work by ? and ? in the ?0s: such monads are those corresponding to \emph{Lawvere theories};

\end{document}

### 2018-11-08 quotients/quotients.tex
Haven't made a commit for ages.

--- 2018-11-08 effects/effects.tex
@@
 \usepackage{tikz}
-\usepackage{xspace}
-\usepackage{IEEEtrantools}
 \usetikzlibrary{cd}
@@
 \newcommand\C{\mathcal{C}}
-\newcommand\D{\mathcal{D}}
-\newcommand\F{\mathcal{F}}
-\newcommand{\suchthat}{\,\colon\,}
-\newcommand{\esuchthat}{\,.\,}
 \newcommand\from{\,\colon\,}
-\newcommand\object\colon
-\DeclareMathOperator{\ac}{ac}
 \DeclareMathOperator{\End}{End}
@@
 \newcommand\run{\texttt{r}}
-\newcommand\lun{\texttt{l}}
 \newcommand\lunit{\texttt{lunit}}
@@
 \renewcommand\implies\multimap
-\newcommand{\pfc}{\boldsymbol{\cdot}}
-\newcommand\Mellies{Melli\`{e}s\xspace}
-
-\newcommand{\catname}[1]{\mathbf{#1}}
-\newcommand{\Set}{\catname{Set}}
-\newcommand{\Surj}{\catname{Surj}}
-\newcommand{\powerset}{\mathcal P}
-
-\DeclareMathOperator{\Prof}{Prof}
-\DeclareMathOperator{\Kl}{Kl}
-
-\makeatletter
-\newcommand{\colim@}[2]{%
-  \vtop{\m@th\ialign{##\cr
-    \hfil$#1\operator@font colim$\hfil\cr
-    \noalign{\nointerlineskip\kern1.5\ex@}#2\cr
-    \noalign{\nointerlineskip\kern-\ex@}\cr}}%
-}
-\newcommand{\colim}{%
-  \mathop{\mathpalette\colim@{\rightarrowfill@\textstyle}}\nmlimits@
-}
-\makeatother
 
@@
 
-\subsection{Monads and Kleisli categories}
-
 This paper is about general frameworks for modelling effects in a categorical semantics.  
@@
 
-Recent progress in the field of game semantics, however, has shown that monads and Kleisli categories are not the be-all and end-all of modelling effects.  
-There are perfectly game semantic models of effects such as state and nondeterminism that do not arise as the Kleisli category for a monad on some more basic category of games.  
-These models are typically built up using intuition -- for example, by relaxing the determinism condition on strategies to give a model of a nondeterministic language -- and do not readily fit into any category theoretic framework the way Kleisli categories do.
-The goal of this paper is to examine some possible frameworks that will allow us to study these and other models in a systematic way.
-
-A closely related problem is that of using a common technique to model a particular effect in different settings.  
-Many of our favourite monads (e.g., the powerset monad on $\Set$ for nondeterminism) live in some particular category and cannot readily be set up in other categories.
-
-Before we start, it is worth mentioning one example of a Kleisli category arising naturally in game semantics.  
-If we read Ghica's work on \emph{slot games} \cite{SlotGames}, it is not difficult to show that the category he constructs is in fact isomorphic to the Kleisli category for the \emph{reader monad} $\mathbb{C}\to \_$, where $\mathbb{C}$ is the game corresponding to a singleton set.
-
-Since the reader monad is entirely built out of the Cartesian closed structure of the category, we can perform a similar trick in many different settings, although perhaps not as successfully as in game semantics.
-
-\subsection{Promonads}
-
-It is instructive at this point to see what happens if we generalize from functors to profunctors.  
-We define a \emph{promonad} on a category $\C$ to be a monoid in the monoidal category $\Prof[\C,\C]$ of endo-profunctors on $\C$.  
-This concept generalizes that of a monad, since an endofunctor $M\from \C\to\C$ may be identified with the profunctor $\C[\_,M(\_)]\from \C^{op}\times\C\to\Set$.
-
-Since the set $\C[A,MB]$ is precisely the set of Kleisli morphisms from $A$ to $B$, it is natural to wonder whether we can perform a Kleisli-type construction on a promonad as well.  
-it turns out that we can: if $\D\from \C^{op}\times\C\to\Set$ is a promonad, then we may define a category (also called $\D$) whose objects are the objects of $\C$, and where the morphisms from $A$ to $B$ are the elements of the set $\D(A,B)$.
-The promonad action
-\[
-  (\D\pfc\D)(A,C) = \int^{B}\D(A,B)\times\D(B,C) \to \D(A,C)
-  \]
-gives us composition in our category and the unit
-\[
-  1(A,B)=\C[A,B]\to \D[A,B]
-  \]
-gives us a functor $\C\to\D$ (and, in particular, the identity morphisms).
-
-In fact, the converse is true: if $\C$ and $\D$ are categories with the same objects and $J\from \C\to\D$ is an identity-on-objects functor, then the functor $\D(JA,JB)=\D(A,B)\from\C^{op}\times\C\to\Set$ may be given the structure of a promonad on $\C$.
-Thus, the rather complicated definition of a promonad is in fact equivalent to the much simpler idea of an identity-on-objects functor.
-We shall therefore use the word `promonad' to mean both things.
-
-In one sense this is very exciting for us, because we can see that promonads generalize not only monads, but also a very large number of the models developed in Game Semantics.  
-For example, the inclusion of the category of games and deterministic strategies into the category of games and nondeterministic strategies is the identity on objects, so it is a promonad.  
-So is the inclusion of the category of games and innocent strategies into the category of games and visible strategies.
-
-More generally, this fits in with the idea that effects should not normally create new types, but should instead give us more flexibility when it comes to writing programs -- exactly what is modelled by an identity-on-objects functor.
-
-On the other hand, the sheer generality of promonads means that they don't give us any ways to actually create new models, since the data required to specify one is the entire category that we are trying to build.
-
-One way of describing the purpose of this work, then, is to discover classes intermediate between monads and promonads that are more general than pure monads but can still be specified in a concise way that allows us to transfer them between different settings.
-
-\subsection{Monads on presheaf categories}
-
-We can think of an endo-profunctor $\F\from \C^{op}\times\C\to \Set$ as a functor $\C\to [\C^{op},\Set]$.  
-Since the Yoneda embedding exhibits $[\C^{op},\Set]$ as the free cocompletion of $\Set$, this can alternatively be characterized as a colimit-preserving endofunctor on $[\C^{op},\Set]$.  
-Similarly, any promonad on $\C$ can alternatively be considered as a monad on $[\C^{op},\Set]$ whose underlying endofunctor preserves colimits.
-
-\subsection{Parametric monads}
-
-\Mellies \cite{ParametricMonads}, following work by Smirnov \cite{Smirnov2008}, has demonstrated that the concept of a lax monoidal category action is a useful generalization of that of a monad.  
-A lax action of a monoidal category $\C'$ upon a category $\C$ is a lax monoidal functor $\C'\to \End[\C]$; monads are the special case when $\C'$ is trivial.  
-For this reason, \Mellies renames lax monoidal actions to `parametric monads', where we think of the action of $\C'$ as a kind of monad on $\C$ that is parameterized by the objects of $\C'$.
-
-This idea has been further generalized by Katsumata \cite{Katsu}, who has given a definition of a `Kleisli-like resolution' of a parametric monad.  
-This particular construction, which takes a parametric monad on a category $\C$ parameterized by a monoidal category $\C'$ and yields a new category, generalizes many important properties of the Kleisli category -- in particular, it gives us an adjunction with the original category -- but it does not fit into our framework, since the objects of the category it creates are not the objects of the original category $\C$, but pairs of an object of $\C$ and an object of $\C'$.
-
-Once again, it is useful to generalize to profunctors.  
-First, if $\C$ is a category and $\C'$ a monoidal category, we define a \emph{parametric promonad on $\C$ parameterized by $\C'$} to be a lax monoidal functor $\C'\to\Prof[\C,\C]$.
-
-As with promonads, we can now look at what we have defined and try to recast it as a particular kind of category.  
-Suppose that $\D\from \C'\times\C^{op}\times\C$ is a parametric promonad on $\C$ parameterized by $\C'$.  
-After some thought, we can see that $\D$ corresponds to a category whose objects are the objects of $\C$ and where the morphisms from $A$ to $B$ are labelled by objects of $\C'$ in such a way that the composition of a morphism labelled with $X$ and a morphism labelled with $Y$ is a morphism labelled with $X\tensor Y$.
-
-One way to state this is as follows.  
-Given a parametric promonad $\D\from \C'\times\C^{op}\times\C\to \Set$, we define a bicategory $\D^2$:
-\begin{itemize}
-  \item whose objects are the objects of $\C$,
-  \item where the $1$-morphisms from $A$ to $B$ are pairs $(X,f)$, where $X$ is an object of $\C'$ and $f\in\D(X,A,B)$
-  \item and where the $2$-morphisms from $(X,f)$ to $(Y,g)$ are morphisms $h\from X\to Y$ in $\C'$ such that $\D(h,A,B)(f)=g$.
-\end{itemize}
-This bicategory comes equipped with two important bifunctors:
-\begin{itemize}
-  \item a bifunctor $J\from \C\to\D^2$ (where we consider $\C$ as a bicategory with only identity $2$-morphisms;
-  \item a bifunctor $l\from \D^2\to \C'$ given by the `labelling' (considering $\C'$ as a bicategory with a single object).
-\end{itemize}
-
-In order to get a promonad resolution of the parametric promonad, then, we need to convert this bicategory into a $1$-category $\D$, which we do by quotienting out the $1$-morphisms in $\D^2$ by the action of the $2$-morphisms: i.e., the smallest equivalence relation such that two $1$-morphisms are related if there is a $2$-morphism from one to the other.
-
-More explicitly, the set of $1$-morphisms from $A$ to $B$ in our new category will be given by the following colimit.
-\[
-  \D(A,B) = \colim_{X\object\C'} \D(X,A,B)
-  \]
-This category $\D$ now admits an identity-on-objects functor from $\C$, meaning that we have found a natural collapse from parametric promonads to ordinary promonads.
-
-In the particular case that the parametric promonad is in fact a parametric \emph{monad}, then we will call the category we obtain $\C/\C'$.  
-The morphisms in $\C/\C'$ are given by
-\[
-  \C/\C'(A,B)=\colim_{X\object\C'} \C(A,X.B)\,,
-  \]
-with the composition of $f\from A\to X.B$ and $g\from B\to Y.C$ being given by the composite
-\[
-  A \xrightarrow{f}
-  X.B \xrightarrow{X.g}
-  X.Y.C \to
-  (X\tensor Y).C\,.
-  \]
-Note that if $\C'$ is the trivial category (so that the action is in fact a monad), then the category $\C/\C'$ is the usual Kleisli category.
-
-\subsection{Effects, monads and colimits}
-
-The colimit that appears in the definition of the category $\C/\C'$ is instructive, because it is linked to the fact that many important monads may be expressed as colimits.  
-For example, let $\Surj$ be the category of sets and surjections.  
-Then, if $A$ is a set, we have
-\[
-  \powerset(A) \cong \colim_{X\object\Surj^{op}} [X,A]\,,
-  \]
-naturally in $A$.
-
-This is useful, because the body of the colimit -- i.e., the function set $[X,A]$ -- has a natural equivalent inside any Cartesian closed category that admits a functor out of $\Set$.  
-Moreover, the functor $[X,A]$ is actually an \emph{action} of $\Surj^{op}$ (with the Cartesian product) upon the category of sets.  
-So even though we cannot define the powerset \emph{monad} inside arbitrary Cartesian closed categories, we can still define this action of $\Surj^{op}$.
-
-Unfortunately, when we try to apply our construction to this action in the category of sets, we do not get the usual Kleisli category for the powerset monad.  
-To see why, note that from the discussion above, we have
-\begin{IEEEeqnarray*}{rCl}
-  \Set/\Surj^{op}(A,B) & = & \colim_{X\object\Surj^{op}}[A,[X,B]] \\
-  & \cong & \colim_{X\object\Surj^{op}}[X,[A,B]] \\
-  & \cong & \powerset([A,B])\,,
-\end{IEEEeqnarray*}
-while the morphisms in the Kleisli category take a different form:
-\[
-  \Kl_{\powerset}\Set(A,B) = [A,\powerset(B)]\,.
-  \]
-Nevertheless, there are still a few things we can take from this.  
-The sets $\powerset([A,B])$ and $[A,\powerset(B)]$ are not equal, but there is still a natural function
-\[
-  \powerset([A,B]) \to [A,\powerset(B)]\,,
-  \]
-that sends a set $\F$ of functions to the function $h$ (the \emph{amalgamation} of $\F$) where
-\[
-  h(a) = \{f(a)\suchthat f \in \F\}\,.
-  \]
-This amalgamation function is not \emph{quite} surjective: for example, suppose that $g\from \{0,1\}\to \powerset(\{0\})$ sends $0$ to $\{0\}$ and $1$ to the empty set.  
-Then $g$ is not the amalgamation of any set of functions $\{0,1\}\to\{0\}$.  
-However, if we use the \emph{nonempty powerset monad} $\powerset^+$ (which corresponds to taking the colimit over the opposite of the category $\Surj^+$ of nonempty sets and surjections), then the amalgamation function gives us a surjection
-\[
-  \powerset^+([A,B])\twoheadrightarrow [A,\powerset^+(B)]\,.
-  \]
-This means that we can recover the Kleisli category for the nonempty powerset monad on $\Set$ by taking the quotient by a suitable equivalence relation to the category $\Set/(\Surj^{+\,op}$).
-
-In fact, this surjection has a natural right inverse, formed by sending a function $h\from A\to\powerset^+(B)$ to the \emph{largest} possible set $\F\subseteq[A,B]$ such that for all $f\in \F$ and $a\in A$, $f(a)\in h(a)$.
-The composition of these inverses sends a set of functions $A\to B$ to its `amalgamation closure':
-\[
-  \ac(\F) = \{g\from A \to B\suchthat\forall a\in A\esuchthat g(a)=f(a)\text{ for some $f\in \F$}\}\,.
-  \]
-By restricting our set of morphisms, then, to those that are fixed points of this operator, we may recover the Kleisli category for $\powerset^+$.
-
-In the next section, we will see how to generalize this idea to other monads, and to other categories.
-
-\subsection{Weakly filtered colimits}
-
-Suppose we have a lax action of a monoidal category $\C'$ upon a cocomplete category $\C$.  
-Then we may copy the collapse from parametric promonads to promonads and define a monad on $\C$ given by:
-\[
-  M A = \colim_{X\object\C'}A.X\,.
-  \]
-Unfortunately, as in the case of the powerset monad above, this transformation does not commute with the collapse from parametric promonads to promonads.  
-Indeed, if we consider our action as a parametric promonad and apply the collapse, then we get a category where the morphisms from $A$ to $B$ are given by the colimit
-\[
-  \colim_{X\object\C'} \C(A,X.B)\,,
-  \]
-while the morphisms from $A$ to $B$ in the Kleisli category for the monad $M$ are given by
-\[
-  \C(A,\colim_{X\object\C'} X.B)\,.
-  \]
-There is a natural morphism from the first colimit into the second expression, but it is not an isomorphism in general.
-If $\C$ is the category of sets, there is a well known result that states that if $\C'$ is a $\kappa$-filtered category and $|A|<\kappa$, then the colimit will commute with the functor $[A,\_]$, but this does not help us, since the category $\C'$ is not filtered in most of the cases we are interested in (e.g., the category $\Surj^{op}$ has not got morphisms coequalizing parallel pairs, since such maps cannot be chosen to be surjective in general).
-
-Instead, we try for the next best thing, which is to show that the natural map $\colim_{X\object\C'}\C(A,X.B)\to\C(A,\colim_{X\object\C'}X.B)$ is a surjection if $\C'$ satisfies some weaker conditions.
-
-We define (see, for example, \cite[Def.
-16]{WeaklyFiltered}) a \emph{$\kappa$-weakly filtered category} to be one in which every \emph{discrete} diagram of size $<\kappa$ admits a cocone; i.e., a non-empty category such that whenever $(X_\alpha)_{\alpha<\kappa}$ is a collection of objects we have some object $Y$ and morphisms $X_\alpha\to Y$ for each $\alpha$.
-
-\begin{example}
-  The category $\Surj^{+\,op}$ is $\kappa$-weakly filtered for arbitrary $\kappa$, because if $(X_\alpha)_{\alpha<\kappa}$ is a collection of sets, then we can take their Cartesian product, and the projections will be surjective.
-
-  The category $\Surj^{op}$ is not weakly filtered, because if there is a surjection from an object $X$ to the empty set, then there is no surjection from $X$ to any other set.
-\end{example}
-
-The importance of $\kappa$-weakly filtered limits is shown by the following result.
-
-\begin{proposition}
-  \label{prop:weakly-filtered}
-  If $\C'$ is a $\kappa$-weakly filtered category, $D\from \C'\to \Set$ is a functor and $A$ is a set with cardinality less than $\kappa$, then the natural function
-  \[
-    \colim_{X\object\C'}[A,D(X)]\to [A,\colim_{X\object\C'}D(X)]
-    \]
-  is a surjection.
-\end{proposition}
-\begin{proof}
-  Given a function $h\from A \to \colim_{X\object\C'}D(X)$, for each $a\in A$, choose some $X_a\object\C'$ such that $h(a)\in D(X_a)$.  
-  Since $\C'$ is $\kappa$-weakly filtered, there is some object $Y$ of $\C'$ that admits morphisms out of all of the $X_a$, and therefore $h$ may be considered as a function $A \to D(Y)$. \qed
-\end{proof}
-
-By setting $D(X)=X.B$, this means that if we have an action of $\C'$ on $\Set$, where the monoidal category $\C'$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\C'\to\Kl_M\Set$.
-
-Moreover, if the colimit satisfies additional properties, then the $Y$ in the proof of Proposition \ref{prop:weakly-filtered} can be chosen in a functorial manner, so that we get a faithful right inverse to this full functor.
-
-\begin{example}
-  If $f\from A \to \colim_{X\object\Surj^{+\,op}}[X,B]$ is a function with $f(a)\in [X_a,B]$ for each $a$, then $f$ is equivalent to a function
-  \[
-    \tilde{f}\from A \to \left[\prod_{a\in A}X_a,B\right]
-    \]
-  via the surjections $\prod_{a\in A}X_a\to X_b$ for each $b\in A$.  
-  The operator $f\mapsto\tilde{f}$ is well-defined in this case, and gives rise to the amalgamation functor that we considered in the previous section.
-\end{example}
-
-The point of these last two sections can be summarized as follows.  
-If a monad $M$ on $\Set$ can be expressed as the colimit of an action of a weakly filtered monoidal category $\C'$ on $\Set$, then we do not lose very much by considering the category $\Set/\C'$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
-More specifically, there is a full functor $\Kl_M\Set\to \Set/\C'$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.
-
-The benefit of reasoning about the action of $\C'$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories.  
-For instance, the action of $\Surj^{+\,op}$ on $\Set$ may be replicated inside any monoidal closed category that admits a functor out of the category of sets (for example, most models of PCF or Idealized Algol).
-
-\subsection{Plan for the paper}
-
-The rest of this paper will consist in two sections.  
-In the first, we will give a more detailed account of the construction that allows us to build a promonad (i.e., a category) out of a parametric monad.
-
-In the second section, we will give a fully abstract game semantics for the language Probabilistic Algol (PA).  
-This is by no means a new result -- the paper \cite{DanosHarmer} that introduced PA also gave it a fully abstract game semantics.  
-Instead, the point of this section will be to demonstrate how the ideas we have outlined can be applied systematically to yield fully abstract models of programming languages.
-
-\section{A Kleisli-style construction for parametric monads}
-
-\subsection{Parametric monads}
+\section{Lax quotients of lax actions}
 
 Let $\C'$ be a monoidal category and let $\C$ be a category.  
-Then a \emph{lax left action} of $\C'$ on $\C$ is a functor $\_.\_\from \C'\times\C\to \C$ that gives rise (through currying) to a lax monoidal functor $\C'\to \End[\C,\C]$.  
-In other words, we have natural transformations $\passoc_{X,Y,A}\from X.Y.A\to (X\tensor Y).A$ and $\lun_A\from A \to I.A$ making the following diagrams commute for all objects $A$ of $\C$ and $X,Y,Z$ of $\C'$.
+Then a \emph{lax iright action} of $\C'$ on $\C$ is a functor $\_.\_\from \C\times\C'\to \C$ that gives rise (through currying) to a lax monoidal functor $\C'\to \End[\C,\C]$.  
+In other words, we have natural transformations $\passoc_{A,X,Y}\from A.X.Y\to A.(X\tensor Y)$ and $\run_A\from A \to A.I$ making the following diagrams commute for all objects $A$ of $\C$ and $X,Y,Z$ of $\C'$.
 
@@
   \begin{tikzcd}[column sep=6em]
-    X.Y.Z.A \arrow[dr,"X.\passoc_{Y,Z,A}"'] \arrow[r, "\passoc_{X,Y,Z.A}"]
-      & (X \tensor Y).Z.A \arrow[r, "\passoc_{X\tensor Y,Z,A}"]
-        & ((X \tensor Y) \tensor Z).A \arrow[d, "\assoc_{X,Y,Z}.A"] \\
+    A.X.Y.Z \arrow[dr,"\passoc_{A.X,Y,Z}"'] \arrow[r, "\passoc_{A,X\tensor Y,Z}"]
+      & A.(X \tensor Y).Z \arrow[r, "\passoc_{A,X\tensor Y,Z}"]
+        & A.((X \tensor Y) \tensor Z) \arrow[d, "A.\assoc_{X,Y,Z}"] \\
     %
-      & X.(Y\tensor Z).A \arrow[r, "\passoc_{X,Y\tensor Z,A}"]
-        & (X\tensor(Y\tensor Z)).A
+      & A.X.(Y\tensor Z) \arrow[r, "\passoc_{A,X,Y\tensor Z}"]
+        & A.(X\tensor(Y\tensor Z))
   \end{tikzcd}
@@
   \begin{tikzcd}
-    X.A \arrow[r, "\lun_{X.A}"] \arrow[dr, "\lunit_X.A"']
-      & I.X.A \arrow[d, "\passoc_{I,X,A}"] \\
+    A.X \arrow[r, "\run_A.X"] \arrow[dr, "A.\lunit_X"']
+      & A.I.X \arrow[d, "\passoc_{A,I,X}"] \\
     %
-      & (I \tensor X) . A
+      & A.(I\tensor X)
   \end{tikzcd}
@@
   \begin{tikzcd}
-    X.A \arrow[r, "X.\lun_A"] \arrow[dr, "\runit_X.A"']
-      & X.I.A \arrow[d, "\passoc_{X,I,A}"] \\
+    A.X \arrow[r, "\run_{A.X}"] \arrow[dr, "A.\runit_X"']
+      & A.X.I \arrow[d, "\passoc{A,X,I}"] \\
     %
-      & (X\tensor I).A
+      & A.(X \tensor I)
   \end{tikzcd}
@@
   \begin{itemize}
-    \item Any monad $M$ is an action of the trivial category on its underlying category $\C$, regarding $MA$ as the action $I.A$.
+    \item Any monad $M$ is an action of the trivial category on its underlying category $\C$, regarding $MA$ as the action $A.I$.
       The natural transformation $\passoc_{A,I,I}$ is precisely the monad action on $A$:
       \[
-        I.I.A = MMA \to M A = I.A = (I\tensor I).A\,.
+        A.I.I = MMA \to M A = A.I = A.(I\tensor I)\,.
         \]
       Dually, any lax action gives rise to a monad on the category being acted upon, by setting $MA = A.I$.
-    \item If $\C$ is also a monoidal category and $J\from \C'\to \C$ is a lax monoidal functor with monoidal coherence $\mu$, then there is an action of $\C'^{co}$ (i.e., $\C'$ with the opposite monoidal product) on $\C$ given by
+    \item If $\C$ is also a monoidal category and $J\from \C'\to \C$ is a lax monoidal functor with monoidal coherence $\mu$, then there is an action of $\C'$ on $\C$ given by
       \[
@@
       \[
-        \passoc_{X,Y,A}=
-        (A \tensor JY) \tensor JX \xrightarrow{\assoc_{A,JX,JY}}
-        A \tensor (JY \tensor JX) \xrightarrow{A \tensor \mu_{X,Y}}
-        A \tensor J(Y\tensor X)\,.
+        \passoc_{A,X,Y}=
+        (A \tensor JX) \tensor JY \xrightarrow{\assoc_{A,JX,JY}}
+        A \tensor (JX \tensor JY) \xrightarrow{A \tensor \mu_{X,Y}}
+        A \tensor J(X\tensor Y)\,.
         \]
-      We sometimes refer to a left action of the opposite category $\C'^{co}$ on $\C$ as a \emph{right action} of $\C'$ on $\C$.  
-      In that case, we write $X.A$ instead of $A.X$, so that the coherences become
-      \begin{gather*}
-        \passoc_{A,X,Y}\from A.X.Y \to A.(X\tensor Y)\\
-        \run_A\from A \to A.I\,.
-      \end{gather*}
 
-    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\C'$ on $\C$ given by
+    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\C'^{co}$ (i.e., $\C'$ with the opposite monoidal product) on $\C$ given by
       \[
@@
         \]
+      We sometimes refer to a right action of the opposite category $\C'^{co}$ on $\C$ as a \emph{left action} of $\C'$ on $\C$.  
+      In that case, we write $X.A$ instead of $A.X$, so that the coherence becomes
+      \[
+        \passoc_{Y,X,A}\from Y.X.A \to (Y\tensor X).A\,.
+        \]
     \item The intersection of the first two examples is the \emph{writer monad} given by $M_WX = X\tensor W$ for any monoid $W$ in $\C$.  
@@
 
-      We shall therefore call an action of the form $A \tensor JX$ a \emph{writer-style action} and one of the form $JX \implies A$ a \emph{reader-style action}.
+      We shall therefore call an action of the form $A \tensor JX$ a \emph{writer-type action} and one of the form $JX \implies A$ a \emph{reader-type action}.
     \item We can define an \emph{oplax action} of $\C'$ on $\C$ to be a lax action of $\C'$ upon the opposite category $\C^{op}$.  
       In this case, the coherence $\passoc$ goes from $A.(X\tensor Y)$ to $A.X.Y$.  
-      As monads are lax actions of the trivial category, so are comonads oplax actions of the trivial category.
+      As monads are lax actions of the trivial category, so comonads are oplax actions of the trivial category.
   \end{itemize}
@@
 \bibliographystyle{spbasic}
-\bibliography{effects}
+\bibliography{quotients}
 

### 2018-11-08 effects/effects.tex
Added abstract.

@@
 \begin{abstract}
+  A well-known principle in denotational semantics is that adding an effect to a categorical model should correspond to the Kleisli category construction for some suitable monad.  
+  Our point of departure is the observation that much recent work in semantics, particularly in game semantics, has broken away from this principle by modelling effects using categories that are not Kleisli categories.
+  Such models are usually obtained throuhg a combination of analysis and intuition and therefore, while acknowledging that this program has been very successful, we have set out to provide the beginnings of a theory which could encompass models of effects in a setting like game semantics that is not amenable to the traditional monadic approach.
+
+  An important part of our approach will be to study parametric monads, otherwise known as lax actions, which have been studied recently by \Mellies, Katsumata and others.  
+  We introduce a construction on parametric monads which generalizes the Kleisli construction and also shares one of its most striking features; namely, that it does not change the objects of the category, only the morphisms.
+  We illustrate the importance of this construction by showing that a particular special case gives us a fully abstract game semantics for Probabilistic Algol.
 \keywords{denotational semantics, category theory, game semantics}

### 2018-11-09 effects/effects.tex
Modified abstract.

--- 2018-11-08 effects/effects.tex
@@
 \begin{abstract}
+  A well-known principle in denotational semantics is that adding an effect to a categorical model should correspond to the Kleisli category construction for some suitable monad.  
+  Our point of departure is the observation that much recent work in semantics, particularly in game semantics, has broken away from this principle by modelling effects using categories that are not Kleisli categories.
+  Our aim is to extend the theory of monadic effects to these models in a systematic way.
+
+  An important part of our approach will be to study parametric monads, otherwise known as lax actions of monoidal categories.
+  These generalize monads: a monad is precisely an action of the trivial category.
+  We introduce a construction on parametric monads which takes a parametric monad on a category and gives us back a new category.  
+  As with the Kleisli category, the objects of this category will be the objects of the original category, while the morphisms are obtained from morphisms in the original category in a formal manner brought about by the action.
+  We show that this new construction is closely related to existing models of effects in game semantics, allowing us to reason systematically about adequacy and full abstraction proofs.
+
+  We illustrate the relevance of this construction by showing that a special case gives us a fully abstract game semantics for Probabilistic Algol, which can be related to the existing model given by Danos and Harmer.
 \keywords{denotational semantics, category theory, game semantics}

### 2018-11-09 effects/effects.tex
Modified abstract 2.

@@
   As with the Kleisli category, the objects of this category will be the objects of the original category, while the morphisms are obtained from morphisms in the original category in a formal manner brought about by the action.
+  In the case that the action is actually a monad, we get the usual Kleisli category.
+
   We show that this new construction is closely related to existing models of effects in game semantics, allowing us to reason systematically about adequacy and full abstraction proofs.
-
-  We illustrate the relevance of this construction by showing that a special case gives us a fully abstract game semantics for Probabilistic Algol, which can be related to the existing model given by Danos and Harmer.
+  We illustrate the relevance of the construction by showing that a special case gives us a fully abstract game semantics for Probabilistic Algol, which can be related to the existing model given by Danos and Harmer.
 \keywords{denotational semantics, category theory, game semantics}

### 2018-11-14 effects/effects.tex
Wrote some more of the paper.

@@
 \newcommand\F{\mathcal{F}}
+\newcommand\G{\mathcal{G}}
+\newcommand\M{\mathcal{M}}
+\DeclareMathOperator\pr{pr}
+\DeclareMathOperator\id{id}
 \newcommand{\suchthat}{\,\colon\,}
@@
 \newcommand{\Surj}{\catname{Surj}}
+\newcommand{\Ret}{\catname{Ret}}
+\newcommand{\Cat}{\catname{Cat}}
 \newcommand{\powerset}{\mathcal P}
@@
 \Mellies \cite{ParametricMonads}, following work by Smirnov \cite{Smirnov2008}, has demonstrated that the concept of a lax monoidal category action is a useful generalization of that of a monad.  
-A lax action of a monoidal category $\C'$ upon a category $\C$ is a lax monoidal functor $\C'\to \End[\C]$; monads are the special case when $\C'$ is trivial.  
-For this reason, \Mellies renames lax monoidal actions to `parametric monads', where we think of the action of $\C'$ as a kind of monad on $\C$ that is parameterized by the objects of $\C'$.
+A lax action of a monoidal category $\M$ upon a category $\C$ is a lax monoidal functor $\M\to \End[\C]$; monads are the special case when $\M$ is trivial.  
+For this reason, \Mellies renames lax monoidal actions to `parametric monads', where we think of the action of $\M$ as a kind of monad on $\C$ that is parameterized by the objects of $\M$.
 
 This idea has been further generalized by Katsumata \cite{Katsu}, who has given a definition of a `Kleisli-like resolution' of a parametric monad.  
-This particular construction, which takes a parametric monad on a category $\C$ parameterized by a monoidal category $\C'$ and yields a new category, generalizes many important properties of the Kleisli category -- in particular, it gives us an adjunction with the original category -- but it does not fit into our framework, since the objects of the category it creates are not the objects of the original category $\C$, but pairs of an object of $\C$ and an object of $\C'$.
+This particular construction, which takes a parametric monad on a category $\C$ parameterized by a monoidal category $\M$ and yields a new category, generalizes many important properties of the Kleisli category -- in particular, it gives us an adjunction with the original category -- but it does not fit into our framework, since the objects of the category it creates are not the objects of the original category $\C$, but pairs of an object of $\C$ and an object of $\M$.
 
 Once again, it is useful to generalize to profunctors.  
-First, if $\C$ is a category and $\C'$ a monoidal category, we define a \emph{parametric promonad on $\C$ parameterized by $\C'$} to be a lax monoidal functor $\C'\to\Prof[\C,\C]$.
+First, if $\C$ is a category and $\M$ a monoidal category, we define a \emph{parametric promonad on $\C$ parameterized by $\M$} to be a lax monoidal functor $\M\to\Prof[\C,\C]$.
 
 As with promonads, we can now look at what we have defined and try to recast it as a particular kind of category.  
-Suppose that $\D\from \C'\times\C^{op}\times\C$ is a parametric promonad on $\C$ parameterized by $\C'$.  
-After some thought, we can see that $\D$ corresponds to a category whose objects are the objects of $\C$ and where the morphisms from $A$ to $B$ are labelled by objects of $\C'$ in such a way that the composition of a morphism labelled with $X$ and a morphism labelled with $Y$ is a morphism labelled with $X\tensor Y$.
+Suppose that $\D\from \M\times\C^{op}\times\C$ is a parametric promonad on $\C$ parameterized by $\M$.  
+After some thought, we can see that $\D$ corresponds to a category whose objects are the objects of $\C$ and where the morphisms from $A$ to $B$ are labelled by objects of $\M$ in such a way that the composition of a morphism labelled with $X$ and a morphism labelled with $Y$ is a morphism labelled with $X\tensor Y$.
 
 One way to state this is as follows.  
-Given a parametric promonad $\D\from \C'\times\C^{op}\times\C\to \Set$, we define a bicategory $\D^2$:
+Given a parametric promonad $\D\from \M\times\C^{op}\times\C\to \Set$, we define a bicategory $\D^2$:
 \begin{itemize}
   \item whose objects are the objects of $\C$,
-  \item where the $1$-morphisms from $A$ to $B$ are pairs $(X,f)$, where $X$ is an object of $\C'$ and $f\in\D(X,A,B)$
-  \item and where the $2$-morphisms from $(X,f)$ to $(Y,g)$ are morphisms $h\from X\to Y$ in $\C'$ such that $\D(h,A,B)(f)=g$.
+  \item where the $1$-morphisms from $A$ to $B$ are pairs $(X,f)$, where $X$ is an object of $\M$ and $f\in\D(X,A,B)$
+  \item and where the $2$-morphisms from $(X,f)$ to $(Y,g)$ are morphisms $h\from X\to Y$ in $\M$ such that $\D(h,A,B)(f)=g$.
 \end{itemize}
@@
   \item a bifunctor $J\from \C\to\D^2$ (where we consider $\C$ as a bicategory with only identity $2$-morphisms;
-  \item a bifunctor $l\from \D^2\to \C'$ given by the `labelling' (considering $\C'$ as a bicategory with a single object).
+  \item a bifunctor $l\from \D^2\to \M$ given by the `labelling' (considering $\M$ as a bicategory with a single object).
 \end{itemize}
@@
 \[
-  \D(A,B) = \colim_{X\object\C'} \D(X,A,B)
+  \D(A,B) = \colim_{X\object\M} \D(X,A,B)
   \]
@@
 
-In the particular case that the parametric promonad is in fact a parametric \emph{monad}, then we will call the category we obtain $\C/\C'$.  
-The morphisms in $\C/\C'$ are given by
+In the particular case that the parametric promonad is in fact a parametric \emph{monad}, then we will call the category we obtain $\C/\M$.  
+The morphisms in $\C/\M$ are given by
 \[
-  \C/\C'(A,B)=\colim_{X\object\C'} \C(A,X.B)\,,
+  \C/\M(A,B)=\colim_{X\object\M} \C(A,X.B)\,,
   \]
@@
   \]
-Note that if $\C'$ is the trivial category (so that the action is in fact a monad), then the category $\C/\C'$ is the usual Kleisli category.
+Note that if $\M$ is the trivial category (so that the action is in fact a monad), then the category $\C/\M$ is the usual Kleisli category.
 
@@
 
-The colimit that appears in the definition of the category $\C/\C'$ is instructive, because it is linked to the fact that many important monads may be expressed as colimits.  
+The colimit that appears in the definition of the category $\C/\M$ is instructive, because it is linked to the fact that many important monads may be expressed as colimits.  
 For example, let $\Surj$ be the category of sets and surjections.  
@@
 
-Suppose we have a lax action of a monoidal category $\C'$ upon a cocomplete category $\C$.  
+Suppose we have a lax action of a monoidal category $\M$ upon a cocomplete category $\C$.  
 Then we may copy the collapse from parametric promonads to promonads and define a monad on $\C$ given by:
 \[
-  M A = \colim_{X\object\C'}A.X\,.
+  M A = \colim_{X\object\M}A.X\,.
   \]
@@
 \[
-  \colim_{X\object\C'} \C(A,X.B)\,,
+  \colim_{X\object\M} \C(A,X.B)\,,
   \]
@@
 \[
-  \C(A,\colim_{X\object\C'} X.B)\,.
+  \C(A,\colim_{X\object\M} X.B)\,.
   \]
 There is a natural morphism from the first colimit into the second expression, but it is not an isomorphism in general.
-If $\C$ is the category of sets, there is a well known result that states that if $\C'$ is a $\kappa$-filtered category and $|A|<\kappa$, then the colimit will commute with the functor $[A,\_]$, but this does not help us, since the category $\C'$ is not filtered in most of the cases we are interested in (e.g., the category $\Surj^{op}$ has not got morphisms coequalizing parallel pairs, since such maps cannot be chosen to be surjective in general).
+If $\C$ is the category of sets, there is a well known result that states that if $\M$ is a $\kappa$-filtered category and $|A|<\kappa$, then the colimit will commute with the functor $[A,\_]$, but this does not help us, since the category $\M$ is not filtered in most of the cases we are interested in (e.g., the category $\Surj^{op}$ has not got morphisms coequalizing parallel pairs, since such maps cannot be chosen to be surjective in general).
 
-Instead, we try for the next best thing, which is to show that the natural map $\colim_{X\object\C'}\C(A,X.B)\to\C(A,\colim_{X\object\C'}X.B)$ is a surjection if $\C'$ satisfies some weaker conditions.
+Instead, we try for the next best thing, which is to show that the natural map $\colim_{X\object\M}\C(A,X.B)\to\C(A,\colim_{X\object\M}X.B)$ is a surjection if $\M$ satisfies some weaker conditions.
 
@@
   \label{prop:weakly-filtered}
-  If $\C'$ is a $\kappa$-weakly filtered category, $D\from \C'\to \Set$ is a functor and $A$ is a set with cardinality less than $\kappa$, then the natural function
+  If $\M$ is a $\kappa$-weakly filtered category, $D\from \M\to \Set$ is a functor and $A$ is a set with cardinality less than $\kappa$, then the natural function
   \[
-    \colim_{X\object\C'}[A,D(X)]\to [A,\colim_{X\object\C'}D(X)]
+    \colim_{X\object\M}[A,D(X)]\to [A,\colim_{X\object\M}D(X)]
     \]
@@
 \begin{proof}
-  Given a function $h\from A \to \colim_{X\object\C'}D(X)$, for each $a\in A$, choose some $X_a\object\C'$ such that $h(a)\in D(X_a)$.  
-  Since $\C'$ is $\kappa$-weakly filtered, there is some object $Y$ of $\C'$ that admits morphisms out of all of the $X_a$, and therefore $h$ may be considered as a function $A \to D(Y)$. \qed
+  Given a function $h\from A \to \colim_{X\object\M}D(X)$, for each $a\in A$, choose some $X_a\object\M$ such that $h(a)\in D(X_a)$.  
+  Since $\M$ is $\kappa$-weakly filtered, there is some object $Y$ of $\M$ that admits morphisms out of all of the $X_a$, and therefore $h$ may be considered as a function $A \to D(Y)$. \qed
 \end{proof}
 
-By setting $D(X)=X.B$, this means that if we have an action of $\C'$ on $\Set$, where the monoidal category $\C'$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\C'\to\Kl_M\Set$.
+By setting $D(X)=X.B$, this means that if we have an action of $\M$ on $\Set$, where the monoidal category $\M$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\M\to\Kl_M\Set$.
 
@@
 The point of these last two sections can be summarized as follows.  
-If a monad $M$ on $\Set$ can be expressed as the colimit of an action of a weakly filtered monoidal category $\C'$ on $\Set$, then we do not lose very much by considering the category $\Set/\C'$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
-More specifically, there is a full functor $\Kl_M\Set\to \Set/\C'$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.
+If a monad $M$ on $\Set$ can be expressed as the colimit of an action of a weakly filtered monoidal category $\M$ on $\Set$, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
+More specifically, there is a full functor $\Kl_M\Set\to \Set/\M$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.
 
-The benefit of reasoning about the action of $\C'$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories.  
+The benefit of reasoning about the action of $\M$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories.  
 For instance, the action of $\Surj^{+\,op}$ on $\Set$ may be replicated inside any monoidal closed category that admits a functor out of the category of sets (for example, most models of PCF or Idealized Algol).
@@
 
-Let $\C'$ be a monoidal category and let $\C$ be a category.  
-Then a \emph{lax left action} of $\C'$ on $\C$ is a functor $\_.\_\from \C'\times\C\to \C$ that gives rise (through currying) to a lax monoidal functor $\C'\to \End[\C,\C]$.  
-In other words, we have natural transformations $\passoc_{X,Y,A}\from X.Y.A\to (X\tensor Y).A$ and $\lun_A\from A \to I.A$ making the following diagrams commute for all objects $A$ of $\C$ and $X,Y,Z$ of $\C'$.
+Let $\M$ be a monoidal category and let $\C$ be a category.  
+Then a \emph{lax left action} of $\M$ on $\C$ is a functor $\_.\_\from \M\times\C\to \C$ that gives rise (through currying) to a lax monoidal functor $\M\to \End[\C,\C]$.  
+In other words, we have natural transformations $\passoc_{X,Y,A}\from X.Y.A\to (X\tensor Y).A$ and $\lun_A\from A \to I.A$ making the following diagrams commute for all objects $A$ of $\C$ and $X,Y,Z$ of $\M$.
 
@@
       Dually, any lax action gives rise to a monad on the category being acted upon, by setting $MA = A.I$.
-    \item If $\C$ is also a monoidal category and $J\from \C'\to \C$ is a lax monoidal functor with monoidal coherence $\mu$, then there is an action of $\C'^{co}$ (i.e., $\C'$ with the opposite monoidal product) on $\C$ given by
+    \item If $\C$ is also a monoidal category and $J\from \M\to \C$ is a lax monoidal functor with monoidal coherence $\mu$, then there is an action of $\M^{co}$ (i.e., $\M$ with the opposite monoidal product) on $\C$ given by
       \[
@@
         \]
-      We sometimes refer to a left action of the opposite category $\C'^{co}$ on $\C$ as a \emph{right action} of $\C'$ on $\C$.  
+      We sometimes refer to a left action of the opposite category $\M^{co}$ on $\C$ as a \emph{right action} of $\M$ on $\C$.  
       In that case, we write $X.A$ instead of $A.X$, so that the coherences become
@@
 
-    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\C'$ on $\C$ given by
+    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\M$ on $\C$ given by
       \[
@@
 
-      We shall therefore call an action of the form $A \tensor JX$ a \emph{writer-style action} and one of the form $JX \implies A$ a \emph{reader-style action}.
-    \item We can define an \emph{oplax action} of $\C'$ on $\C$ to be a lax action of $\C'$ upon the opposite category $\C^{op}$.  
+      We shall therefore call an action of the form $A \tensor JX$ a \emph{writer-style action} and one of the form $jX \implies A$ a \emph{reader-style action}.
+    \item We can define an \emph{oplax action} of $\M$ on $\C$ to be a lax action of $\M$ upon the opposite category $\C^{op}$.  
       In this case, the coherence $\passoc$ goes from $A.(X\tensor Y)$ to $A.X.Y$.  
       As monads are lax actions of the trivial category, so are comonads oplax actions of the trivial category.
+
+      Since the functors $\_\tensor U$ and $U\implies \_$ are adjoint, any reader-style lax action $jX \implies A$ may also be regarded as an oplax action $A \tensor jX$.  
+      We shall refer to these oplax actions as \emph{reader-style} too.
   \end{itemize}
 \end{example}
+
+\subsection{The $\C/\M$ construction}
+
+Suppose we have a lax action of a monoidal category $\M$ upon a category $\C$.  
+We define a new category $\C/\M$ as follows.
+The objects of $\C/\M$ are the objects of $\C$, while the morphisms are given by the following formula.
+\[
+  \C/\M(A,B) = \colim_{X\object\M}\C(A,X.B)
+  \]
+That is, if $A$ and $B$ are objects of $\C$, then a morphism from $A$ to $B$ in $\C/\M$ is an equivalence class of pairs $(X,f)$, where $X$ is an object of $\M$ and $f\from A\to X.B$ a morphism in $\C$, and where $(X,f)$ and $(Y,g)$ are said to be equivalent if there is a morphism $h\from X\to Y$ in $\M$ making the following diagram commute.
+\[
+  \begin{tikzcd}
+    A \arrow[r, "f"] \arrow[dr, "g"']
+      & X.B \arrow[d, "h.B"] \\
+    %
+      & Y.B
+  \end{tikzcd}
+  \]
+Note that this does not automatically define an equivalence relation in general, so there may be pairs $(X,f)$ and $(Y,g)$ that are not related by some $h\from X\to Y$ but are nevertheless equivalent because there is some chain of such relations from one to the other.
+
+For the rest of the paper, we will refer to the pair $(X,f)$ using the morphism $f$, since the object $X$ should usually be clear from context.
+
+Let $A,B,C$ be objects of $\C$, and let $f\from A\to X.B,g\from B\to Y.C$ be morphisms $A\to B$ and $B\to C$ in $\C/\M$.  
+We define the composition of $f$ with $g$ to be given by the following composite in $\C$.
+\[
+  A \xrightarrow{f}
+  X.B \xrightarrow{X.g}
+  X.Y.C \xrightarrow{\passoc_{X,Y,C}}
+  (X\tensor Y).C
+  \]
+The identity morphism $A\to A$ is given by the morphism $\lun_A\from A \to I.A$ in $\C$.
+The coherence conditions for the action guarantee that this is an identity and that our composition is associative.
+
+There is a natural functor $J\from \C \to \C/\M$ that is the identity on objects and that sends the morphism $f\from A \to B$ in $\C$ to the composite
+\[
+  A \xrightarrow{f}
+  B \xrightarrow{\lun_B}
+  I.B\,,
+  \]
+considered as a morphism $A\to B$ in $\C/\M$.
+
+\subsection{Universal property of $\C/\M$}
+
+The category $\C/\M$ has one other piece of structure besides the functor out of $\C$.  
+If $X$ is an object of $M$ and $A$ and object of $\C$, then the identity morphism $X.A\to X.A$ may be considered as a morphism $\phi_{X,A}\from J(X.A) \to JA$ in $\C/\M$.  
+$\phi_{X,A}$ is natural in $X$ and $A$ and also makes the following diagram commute.
+\[
+  \begin{tikzcd}
+    J(X.Y.A) \arrow[r, "\phi_{X,Y.A}"] \arrow[d, "J\passoc_{X,Y,A}"']
+      & J(Y.A) \arrow[d, "\phi_{Y,A}"] \\
+    J((X\tensor Y).A) \arrow[r, "\phi_{X\tensor Y,A}"]
+      & JA
+  \end{tikzcd}
+  \]
+We call a natural transformation $\psi_{X,A}\from J(X.A) \to JA$ \emph{multiplicative} if it satisfies the same commutative diagram.
+
+$\C/\M$, $J$ and $\phi_{X,A}$ are universal in the following sense.
+
+\begin{proposition}
+  i) Let $\C/\M$, $J$ and $\phi_{X,A}$ be as above.  
+  Let $\D$ be a category, $F$ a functor $\C\to \D$ and $\psi_{X,A}\from F(X.A) \to FA$ a multiplicative natural transformation in $\D$.  
+  Then there is a unique functor $H\from \C/\M\to \D$ such that $F=H J$ and $\psi=H\phi$.
+
+  ii) Let $\D$ be a category and let $H,K\from \C/\M\to \D$ be two functors.  
+  Let $\alpha\from HJ \to KJ$ be a natural transformation making the following diagram commute.
+  \[
+    \begin{tikzcd}
+      HJ A \arrow[r, "\alpha_A"] \arrow[d, "H\phi_{X,A}"']
+        & KJ A \arrow[d, "K\phi_{X,A}"] \\
+      HJ X.A \arrow[r, "\alpha_{X.A}"]
+        & KJ A
+    \end{tikzcd}
+    \]
+  Then there is a unique natural transformation $\beta\from H\to K$ such that $\alpha=\beta J$.
+  \label{quotient-universal}
+\end{proposition}
+
+\begin{remark}
+  The functor $H$ in Proposition \ref{quotient-universal}(i) sends the object $JA=A$ to the object $FA$.  
+  To define $H$ on morphisms, we use the fact that every morphism $f\from A \to X.B$ from $A$ to $B$ in $\C/\M$ may be factorized as:
+  \[
+    f = A \xrightarrow{Jf}
+    X.B \xrightarrow{\phi_{X,A}}
+    B\,,
+    \]
+  where we have considered $f$ both as a morphism $A\to B$ in $\C/\M$ and as a morphism $A \to X.B$ in $\C$.  
+  It therefore suffices to define $H$ on morphisms of the form $Jf$ (which must be sent to $Ff$, since $F=HJ$) and on morphisms of the form $\phi_{X,A}$ (which must be sent to $\psi_{X,A}$, since $\psi=H\phi$).
+  The proof of part (ii) also follows from this factorization.
+
+  Thus, one way of thinking of the category $\C/\M$ is as a general theory of categories that extend $\C$, and admit a factorization result whereby every morphism is the composition of a morphism from $\C$ with one of the distinguished morphisms $\phi_{X,A}$.
+
+  For example, in \cite{SamsonGuyIAPassive}, it is shown that any morphism $\sigma \from A\to B$ in the category $\G_{vis}$ of games and visible strategies may be factorized as
+  \[
+    \sigma = A \xrightarrow{\text{Inn}(\sigma)}
+    (\text{Var[S]} \to B) \xrightarrow{\textsf{new}_S}
+    B\,,
+    \]
+  where $\text{Inn}(\sigma)$ is a morphism in the category of $\G_{inn}$ of games and innocent strategies, $S$ is a set and $\textsf{new}$ is a special morphism that introduces stateful behaviour.  
+  The $\text{Var}[S]$ construction, which is the game corresponding to a storage cell holding values of the set $S$, may be regarded as an oplax monoidal functor from the category $\Ret$ of sets and retractions into the category of games, and so $\text{Var}[S]\to B$ is a reader-style action.
+  Moreover, it can be shown that $\textsf{new}$ gives rise to a multiplicative natural transformation, inducing a functor $\G_{inn}/\Ret\to \G_{vis}$.  
+  Then the factorization result we have quoted says precisely that this functor is full.
+\end{remark}
+\begin{remark}
+  If $\M$ is the trivial category, so our action is a monad $M$, then this universal property can be used to prove the usual universal property for the Kleisli category; namely, that it is initial among all adjunctions giving rise to $M$.
+  To see this, suppose that $\C \xrightarrow{F} \D \xrightarrow{G} \C$ are functors such that $F$ is left adjoint to $G$ and $M=GF$.  
+  Then we have a natural transformation
+  \[
+    FMA = FGF A \xrightarrow{\epsilon_{F A}} F A\,
+    \]
+  which satisfies the hypotheses of Proposition \ref{quotient-universal}(i).  
+  Therefore, Proposition \ref{quotient-universal} tells us that the Kleisli category is not only initial amongst adjunctions giving rise to $M$, but is initial among all functors $F\from \C \to \D$ that admit a natural transformation $FMA \to FA$.
+  Note that for more general $\M$, we do not in general get an adjunction between $\C$ and $\C/\M$.
+\end{remark}
+\begin{remark}
+  The quotient notation we have used is because the universal property we have outlined exhibits $\C/\M$ as a particular weighted coequalizer of the functors $\pr_2,\_.\_\from \M\times\C \rightrightarrows \C$ in $\Cat$.
+  It may therefore be regarded as a lax $2$-dimensional analogue of the quotient $X/G$ of a set $X$ by a group or monoid action.
+
+  This is a strange idea, since we are not used to thinking of, for example, a Kleisli category as quotient of the original category.  
+  The reason for this is the laxness: we do not identify the objects $A$ and $X.A$ with an isomorphism, but with a morphism in one direction.  
+  One way in which a Kleisli category does act like a quotient is that it allows us to transfer effects that are usually associated with higher types on to lower types.  
+  For example, the type $W\to [A,W]$ encodes a state transformer with state $W$.  
+  Working in the Kleisli category for the state monad allows us to associate this stateful behaviour to the object $A$.
+\end{remark}
+\begin{remark}
+  Suppose we have an oplax right action of a monoidal category $\M$ on a category $\C$.  
+  This may be regarded as a lax left action of $\M^{co}$ upon $\C^{op}$, and therefore we get a category in the same way in which the objects are the objects of $\C$ and the morphisms from $A$ to $B$ are equivalence classes of morphisms $A.X \to B$ in $\C$.
+
+  In the case that the action is an oplax reader-style action given by $A.X = A\tensor jX$ for some oplax monoidal functor $j\from \M \to \C$, then the natural transformation $\phi_{A,X}$ goes from $J(A\tensor jX)$ to $JA$, and may instead be regarded as a natural transformation $I\to jX$ in $\C$.
+  In that case, the category $\C/\M$ that we obtain is what \cite[4.3.11]{lurie2009} calls the \emph{cone} over the functor $j$.  
+  This is because the universal property in that case is a lax version of the property satisfied by the mapping cone in homotopy theory.
+\end{remark}
+
+\subsection{Monoidal and monoidal closed structure of $\C/\M$}
+
+We saw in the last section that the $\C/\M$ construction may be regarded as a kind of lax $2$-coequalizer.  
+In the category of sets, if a pair of morphisms $f,g\from A \rightrightarrows B$ is \emph{reflexive} -- i.e., if there is a morphism $h\from B \to A$ such that $f\circ h = g\circ h = \id_B$, then the coequalizer of $f$ and $g$ commutes with finite products.
+
+In our setting, the two functors $\pr_2$ and $\_.\_$ from $\M\times\C \to \C$ form a reflexive pair, since they have a common section $h\from \C \to \M\times \C$ given by $h(A) = (I, A)$.  
+It turns out that a similar result then applies.
+
+\begin{proposition}
+  Given an action of a monoidal category $\M$ on a category $\C$, there is an obvious way to define an action of $\M\times\M$ on $\C\times\C$.  
+  Then the functor
+  \[
+    (\C\times\C)/(\M\times\M) \to (\C/\M) \times (\C/\M)
+    \]
+  induced as in Proposition \ref{quotient-universal} is an isomorphism.
+  \label{monoidality}
+\end{proposition}
+
+Now suppose that $\C$ is itself a monoidal category.  
+We say that the action of $\M$ on $\C$ is \emph{monoidal} if it is a lax monoidal functor $\M\times\C\to\C$, which means that we need to have a natural transformation 
+\[
+  X.A\tensor Y.B\to (X\tensor Y).(A\tensor B)\,,
+  \]
+together with appropriate coherences.
+
+If the action is reader-style, given by $X.A = jX \implies A$ for an oplax monoidal functor $j\from \M\to \C$, then it is sufficient for $\C$ to be a \emph{symmetric} monoidal category, since then we have a natural transformation
+\[
+  (j X \implies A) \tensor (j Y \implies B)
+  \rightarrow
+  (j X \tensor j Y) \implies (A \tensor B)
+  \rightarrow
+  j (X\tensor Y) \implies (A \tensor B)\,.
+  \]
+Given a monoidal action, we get a natural transformation
+\[
+  (X\tensor Y).(A\tensor B)
+  \rightarrow
+  (X.A)\tensor Y.B
+  \xrightarrow{\phi_{X,A}\tensor \phi_{Y,B}}
+  A\tensor B\,,
+  \]
+which is multiplicative, inducing a functor $(\C\times\C)/(\M\times\M)\to \C/\M$.  
+Composing with the isomorphism from the start of this section, we get a functor $(\C/\M)\times(\C/\M)\to\C/\M$.  
+It turns out that this gives $\C/\M$ the structure of a monoidal category and that in this case the functor $J\from \C\to\C/\M$ is a strict monoidal functor.
+
+This generalizes the case of a monoidal monad, whose the Kleisli category is always a monoidal category.
+
+Now, if $\C$ is monoidal closed and the action of $\M$ on $\C$ is a \emph{reader-type action}, then $\C/\M$ also inherits the monoidal closed structure from $\C$.  
+Note that this may not be true for arbitrary actions, even for monads.  
+For example, the Kleisli category for the power set monad on $\Set$ (which is better known as the category of sets and relations) is monoidal closed, but with inner function space given by the Cartesian product, and not by the function space from $\Set$.
 

### 2018-11-14 cones/paper/lipics-v2018-authors/cones.tex
Made more changes.

@@
 \newcommand{\pred}{{\mathtt{pred\;}}}
-\newcommand{\0}{{\mathtt{0}}}
-\newcommand{\com}{{\mathtt{com}}}
+\newcommand{\0}{{\mathtt{0}}} \newcommand{\com}{{\mathtt{com}}}
 \newcommand{\skipp}{{\mathsf{skip}}}

### 2018-11-14 effects/effects.tex
Made more changes.

@@
 \usepackage{IEEEtrantools}
+\usepackage{mathtools}
 \usetikzlibrary{cd}
@@
 \DeclareMathOperator\id{id}
+\newcommand{\inv}{{}^{-1}}
 \newcommand{\suchthat}{\,\colon\,}
 \newcommand{\esuchthat}{\,.\,}
-\newcommand\from{\,\colon\,}
 \newcommand\object\colon
@@
 
+\let\oldemptyset\emptyset
+\let\emptyset\varnothing
+\newcommand{\nat}{{\mathtt{nat}}}
+\newcommand*\from{\colon}
+\newcommand{\Y}{\mathbf{Y}}
+\newcommand{\opto}{\longrightarrow}
+\newcommand{\n}{{\mathtt{n}}}
+\newcommand{\x}{{\mathtt{x}}}
+\newcommand{\IfO}{{\mathtt{If0}\;}}
+\newcommand{\If}{{\mathtt{If}\;}}
+\newcommand{\suc}{{\mathtt{suc\;}}}
+\newcommand{\pred}{{\mathtt{pred\;}}}
+\newcommand{\0}{{\mathtt{0}}} \newcommand{\com}{{\mathtt{com}}}
+\newcommand{\skipp}{{\mathsf{skip}}}
+\newcommand{\neww}{{\mathsf{new}}}
+\newcommand{\mkvar}{{\mathsf{mkvar}\;}}
+\newcommand{\deref}{\texttt{@}}
+\newcommand{\ia}[2]{\langle #1 , #2 \rangle}
+\newcommand{\stup}[3]{\langle #1 \mid #2 \mapsto #3 \rangle}
+\newcommand{\Var}{{\mathtt{Var}}}
+\newcommand{\new}{{\mathtt{new}}}
+\renewcommand{\case}{{\mathtt{case}}}
+\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
+\newcommand{\converges}{\Downarrow}
+
 \newcommand{\catname}[1]{\mathbf{#1}}
@@
 \newcommand{\Cat}{\catname{Cat}}
+\newcommand{\DProb}{\catname{DProb}}
+\newcommand{\BProb}{\catname{BProb}}
 \newcommand{\powerset}{\mathcal P}
+\usepackage{bbm}
+\newcommand{\true}{\mathbbm{t}}
+\newcommand{\false}{\mathbbm{f}}
+
+\newcommand{\bR}{\mathbb{R}}
+\newcommand{\bN}{\mathbb{N}}
+\newcommand{\bB}{\mathbb{B}}
+\newcommand{\bC}{\mathbb{C}}
+\newcommand{\bP}{\mathbb{P}}
 
@@
 \DeclareMathOperator{\Kl}{Kl}
+
+\newcommand{\coin}{\textsf{coin}}
+\newcommand{\polydie}{\textsf{polydie}}
+\newcommand{\bool}{\textsf{bool}}
+
+\renewcommand{\emptyset}{\varnothing}
 
@@
 
-    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\M$ on $\C$ given by
+    \item If $\C$ is a monoidal closed category, and $j$ an oplax monoidal functor with coherence $\nu$, then there is an action of $\M^{op}$ on $\C$ given by
       \[
@@
     \sigma = A \xrightarrow{\text{Inn}(\sigma)}
-    (\text{Var[S]} \to B) \xrightarrow{\textsf{new}_S}
+    (\text{Var[S]} \to B) \xrightarrow{\new_S}
     B\,,
     \]
-  where $\text{Inn}(\sigma)$ is a morphism in the category of $\G_{inn}$ of games and innocent strategies, $S$ is a set and $\textsf{new}$ is a special morphism that introduces stateful behaviour.  
-  The $\text{Var}[S]$ construction, which is the game corresponding to a storage cell holding values of the set $S$, may be regarded as an oplax monoidal functor from the category $\Ret$ of sets and retractions into the category of games, and so $\text{Var}[S]\to B$ is a reader-style action.
-  Moreover, it can be shown that $\textsf{new}$ gives rise to a multiplicative natural transformation, inducing a functor $\G_{inn}/\Ret\to \G_{vis}$.  
+  where $\text{Inn}(\sigma)$ is a morphism in the category of $\G_{inn}$ of games and innocent strategies, $S$ is a set and $\new$ is a special morphism that introduces stateful behaviour.  
+  The $\Var[S]$ construction, which is the game corresponding to a storage cell holding values of the set $S$, may be regarded as an oplax monoidal functor from the category $\Ret$ of sets and retractions into the category of games, and so $\Var[S]\to B$ is a reader-style action.
+  Moreover, it can be shown that $\new$ gives rise to a multiplicative natural transformation, inducing a functor $\G_{inn}/\Ret\to \G_{vis}$.  
   Then the factorization result we have quoted says precisely that this functor is full.
@@
 \begin{proposition}
-  Given an action of a monoidal category $\M$ on a category $\C$, there is an obvious way to define an action of $\M\times\M$ on $\C\times\C$.  
+  Given an action of a monoidal category $\M$ on a category $\C$, and an action of a monoidal category $\M'$ on a category $\C'$, there is an obvious way to define an action of $\M\times\M'$ on $\C\times\C'$.
   Then the functor
   \[
-    (\C\times\C)/(\M\times\M) \to (\C/\M) \times (\C/\M)
+    (\C\times\C')/(\M\times\M') \to (\C/\M) \times (\C'/\M')
     \]
@@
 
+\section{Game Semantics for Probabilistic Algol}
+
+\subsection{The discrete probability monad}
+
+Given a set $X$, we define a \emph{discrete probability measure} on $X$ to be a function $\bP\from\powerset(X)\to[0,1]$ satisfying the following conditions.
+\begin{description}
+  \item[Empty set] $\bP(\emptyset) = 0$.
+  \item[Countable additivity] If $\{E_i\}_{i=0}^\infty$ is a sequence of pairwise-disjoint subsets of $X$, then
+    \[
+      \bP\left(\bigcup_{i=0}^\infty E_i\right) = \sum_{i=0}^\infty \bP(E_i)\,.
+      \]
+  \item[Whole space] $\bP(X)=1$.
+\end{description}
+
+If instead we have $\bP(X)\le 1$, we say that $\bP$ is a \emph{sub-probability measure}
+
+Note that if $A$ is countable, then $\mu$ may be entirelly specified by its action on singletons: if $A\subseteq X$ is a set, then we have
+\[
+  \bP(A) = \sum_{a\in A}\bP(\{a\})\,.
+  \]
+
+Given a set $X$, we define $P(X)$ to be the set of all discrete probability measures on $X$.  
+Then we have natural maps
+\begin{mathpar}
+  \delta_X\from X \to P(X) \and m_X\from P(P(X)) \to X
+\end{mathpar}
+given by
+\begin{mathpar}
+  \delta_X(x)(A) = \begin{cases}
+    1 & x\in A \\
+    0 & x\not\in A
+  \end{cases} \and
+  \bP_X(\tau)(A) = \sum_{\bP\in P(X)} \tau(\{\bP\})\bP(A)
+\end{mathpar}
+$\delta_X$ and $m_X$ give $P$ the structure of a monad on $\Set$, which we will call the \emph{discrete probability monad}.  
+This is a discrete form of the monad developed in \cite{Giry}.
+
+We want to exhibit this monad as the colimit of an action, as we did for the power set monad earlier.  
+We define a \emph{discrete probability space} to be a pair $(X,\bP_X)$, where $X$ is a set and $\mu$ a discrete probability measure on $X$.  
+We will normally refer to this pair using the set $X$.
+Given discrete probability spaces $X$ and $Y$, we define a \emph{measure-preserving map} from $X$ to $Y$ to be a function $f\from X \to Y$ such that for all $A\subseteq Y$ we have $\bP(X)(f\inv(A)) = \bP_Y(A)$.
+It is clear that discrete probability spaces and measure-preserving maps form a category $\DProb$.
+
+Moreover, $\DProb$ is a monoidal category: given discrete probability spaces $X$ and $Y$, we may define a probability measure on the Cartesian product $X\times Y$ by
+\[
+  \bP_{X\times Y} (A) = \sum_{(x,y)\in A} \bP_X(\{x\})\bP_Y(\{y\})\,.
+  \]
+
+Then we have a natural isomorphism
+\[
+  P(X) \cong \colim_{(Y,\bP_Y)\object\DProb^{op}} [Y,X]\,,
+  \]
+such that the monad structure on $P$ is induced from the reader-style action of $\DProb^{op}$ on $\Set$ given by the monoidal functor $\DProb\to\Set$ that sends $(Y,\bP_Y)$ to its underlying set $Y$.
+
+Moreover, the category $\DProb^{op}$ is weakly filtered, and so, as in our earlier discussion, we feel confident using this action, rather than the monad $P$ we have defined, to model discrete probability.
+
+By cutting down the category $\DProb$ we can obtain slightly different notions of probability.  
+For our purposes, we will be using the full subcategory $\BProb$ where the objects $(X,\bP_X)$ are those that satisfy the following three additional conditions.
+\begin{description}
+  \item[Countability] The set $X$ is countable.
+  \item[Finite support] There is a finite subset $E\subseteq X$ such that $\bP_X(E)=1$.
+  \item[Rational probabilities] $\bP_X(A)\in\mathbb{Q}$ for all $A\subseteq X$.
+\end{description}
+
+The action of $\BProb$ gives rise to a monad on the category of countable sets.
+
+\subsection{Probabilistic Algol}
+
+\cite{DanosHarmer} gives a fully abstract game semantics for the language Probabilistic Algol (PA).  
+The base language for PA is the language Idealized Algol (IA) from \cite{SamsonGuyIAPassive}, and it has been extended with a constant $\coin\from\bool$.  
+We give the language a small-step reduction semantics, as shown in Figure \ref{pa-operational}.
+
+\begin{figure*}
+  \begin{mathpar}
+    \inferrule*{ }{\ia s {(\lambda x.M)\;N} \opto \ia s {M[N/x]}}
+    \and
+    \inferrule*{ }{\ia s {\Y_T M}\opto \ia s {M (\Y_T M)}}
+    \and
+    \inferrule*{ }{\ia s {\suc \n}\opto\ia s {\n + \mathsf{1}}}
+    \and
+    \inferrule*{ }{\ia s {\pred \n}\opto\ia s {\0 \sqcup (\n - \mathsf{1})}}
+    \and
+    \inferrule*{ }{\ia s {\IfO \0 M N} \opto \ia s M}
+    \and
+    \inferrule*{ }{\ia s {\IfO (\n + \mathsf{1}) M N} \opto \ia s N}
+    \and
+    \inferrule*{ }{\ia s {\If \true\;M\;N} \opto M}
+    \and
+    \inferrule*{ }{\ia s {\If \false\;M\;N} \opto N}
+    \and
+    \inferrule*{ }{\ia s {\deref (\mkvar M N)} \opto \ia s M}
+    \and
+    \inferrule*{ }{\ia s {(\mkvar M N) \coloneqq L} \opto \ia s {N\;L}}
+    \and
+    \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}
+    \and
+    \inferrule*[left={$s(v)=n$}]{ }{\ia s {\deref v} \opto \ia s n}
+    \and
+    \inferrule*{ }{\ia s {\skipp;M} \opto \ia s M}
+    \and
+    \inferrule*{ }{\ia s {\new_T \lambda v.M}\opto \ia {\stup s v 0} M}
+    \and
+    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {E[M]} \opto \ia s {E[M']}}
+    \and
+    \inferrule*[left=coin]{ }{\ia s \coin \opto \ia s \true}
+    \and
+    \inferrule*[left=coin]{ }{\ia s \coin \opto \ia s \false}
+  \end{mathpar}
+  \caption{Small-step operational semantics for Probabilistic Algol, where $E$ ranges over suitable evaluation contexts}
+  \label{pa-operational}
+\end{figure*}
+
+All of these rules are deterministic with the exception of the two marked \LeftTirName{coin}.
+Given an evaluation $\pi = M \to M_1 \to \cdots \to \x$ of a term $M$ of ground type $o$, we define the \emph{weight} $w(\pi)$ of $\pi$ to be $\frac{1}{2^k}$, where $k$ is the number of instances of a \LeftTirName{coin} rule occurring in $\pi$.
+
+This defines a discrete sub-probability measure on the set corresponding to the ground type $o$ given by
+\[
+  \bP(\{x\}) = \sum_{\substack{\text{evaluations}\\\pi = M \to\dots \x}}w(\pi)\,.
+  \]
+This is only a subprobability measure, because some evaluations may continue forever.
+
+\cite{DanosHarmer} shows how we can define other probabilistic terms using $\coin$.  
+Specifically, they define a term $\polydie\from\bN\to\bN$, where the behaviour of $\polydie n$ is to return the result of tossing an $n$-sided die (with sides numbered $0$ to $n-1$), with each outcome occurring with probability $1/n$.
+The definition of $\polydie n$ in terms of $\coin$ works as follows.  
+We choose some number $k$ such that $2^k\ge n$ and then toss the coin $n$ times to give one of $2^k$ outcomes.  
+If an outcome corresponds (under some fixed correspondence $n\hookrightarrow 2^k$) to a natural number below $n$, then we return that number; otherwise, we repeat the process until we get such a number.
+
+This process will terminate with probability $1$, and since each $m<n$ occurs with equal probability, they must all occur with probability $1/n$.
+
+\subsection{Extending a semantics for IA to a semantics for PA}
+
+Let $\G$ be a category that admits a fully abstract adequate semantics for Idealized Algol.  
+See \cite{SamsonGuyIAPassive} for a list of the conditions that such a category should satisfy, and also for the best known example, the category of games and visible strategies.
+
+As explained in \cite{SamsonGuyIAPassive}, $\G$ should be Cartesian closed and there should be a lax monoidal functor $\Set\to \G$ that gives the denotation of the ground types $\nat$,$\bool$ and $\com$, together with their structural functions.
+We can therefore get a lax monoidal functor $\BProb \to \G$ by composing this with the forgetful functor $\BProb\to\Set$.
+
+This gives rise to a reader-style action of $\BProb^{op}/\G$, and the resulting category $\G/\BProb^{op}$ is therefore a symmetric monoidal closed category.  
+Unfortunately, the monoidal product on $\G/\BProb^{op}$ is not Cartesian; the problem is that there is no unique way to form the copairing of
+
 \bibliographystyle{spbasic}

### 2018-11-15 effects/effects.tex
Reworked some earlier sections.

@@
 \def\UrlFont{\rmfamily}
+
+\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
+    \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
 
@@
 
-Recent progress in the field of game semantics, however, has shown that monads and Kleisli categories are not the be-all and end-all of modelling effects.  
-There are perfectly game semantic models of effects such as state and nondeterminism that do not arise as the Kleisli category for a monad on some more basic category of games.  
-These models are typically built up using intuition -- for example, by relaxing the determinism condition on strategies to give a model of a nondeterministic language -- and do not readily fit into any category theoretic framework the way Kleisli categories do.
+Monads are certainly not the only formal method of adding effects into categories.  
+For example, \cite{Lawvere} argues that Lawvere theories, a tool used originally in universal algebra (as monads were), also give us a natural way to model effects in categories.  
+Since \cite{FinitaryMonadOnSet} every Lawvere theory may be regarded as a particular monad on the category of sets, this is not surprising.  
+However, Lawvere theories are a lot more flexible than monads when it comes to composing multiple effects together.
+
+More recent work in game semantics, however, has produced models of effects -- such as the well-known game semantics for scoped state \cite{SamsonGuyIAPassive} and nondeterminism \cite{mcCHFiniteND} -- do not arise by applying any systematic procedure to a base category of games that lacks the effect.
+Instead, these models are typically built up using intuition -- for example, by relaxing the determinism condition on strategies to give a model of a nondeterministic language -- and do not readily fit into any category theoretic framework the way Kleisli categories do.
 The goal of this paper is to examine some possible frameworks that will allow us to study these and other models in a systematic way.
@@
 Before we start, it is worth mentioning one example of a Kleisli category arising naturally in game semantics.  
-If we read Ghica's work on \emph{slot games} \cite{SlotGames}, it is not difficult to show that the category he constructs is in fact isomorphic to the Kleisli category for the \emph{reader monad} $\mathbb{C}\to \_$, where $\mathbb{C}$ is the game corresponding to a singleton set.
+The \emph{slot games} defined in \cite{SlotGames} are defined like ordinary games, but their strategies are allowed to contain extra moves, called \emph{tokens}, which are meant to represent a point at which the computation takes up time or resources.
+For example, a strategy for a term of natural number type that returns the value $5$ after two CPU cycles could be represented by the strategy shown on the left of Figure \ref{slot-games}.  
+Now, we can alternatively represent this strategy as being a normal strategy inside the Kleisli category for the reader monad given by the \emph{command} or \emph{singleton} type, as on the right of Figure \ref{slot-games}.
+The translation works by replacing each token $\circled{\$}$ with a request to the argument to the function: since this arguement has singleton type, there is only one possible value that can be passed in, but the game semantics will record that we have made the request.
+What is more, this translation respects composition in the two categories, both the Kleisli composition and the composition defined synthetically for slot games.
+\begin{figure}
+  \begin{mathpar}
+    \begin{array}{c}
+      \mathbf{\bN} \\
+      q \\
+      \circled{\$} \\
+      \circled{\$} \\
+      5 \\
+    \end{array}
+    \and
+    \begin{array}{ccc}
+      \mathbf{\bC} & \mathbf{\implies} & \mathbf{\bN} \\
+      && q \\
+      q && \\
+      a && \\
+      q && \\
+      a && \\
+      && 5
+    \end{array}
+  \end{mathpar}
+  \label{slot-games}
+  \caption{The `slot-games' denotation of a program that uses resources can also be represented in a Kleisli category.}
+\end{figure}
 
@@
 It is instructive at this point to see what happens if we generalize from functors to profunctors.  
-We define a \emph{promonad} on a category $\C$ to be a monoid in the monoidal category $\Prof[\C,\C]$ of endo-profunctors on $\C$.  
+We define a \emph{promonad} on a category $\C$ to be a monoid in the monoidal category $\Prof[\C,\C]$ of endo-profunctors on $\C$, where the monoidal product in $\Prof[\C,\C]$ is given by composition of profunctors.
 This concept generalizes that of a monad, since an endofunctor $M\from \C\to\C$ may be identified with the profunctor $\C[\_,M(\_)]\from \C^{op}\times\C\to\Set$.
@@
 In one sense this is very exciting for us, because we can see that promonads generalize not only monads, but also a very large number of the models developed in Game Semantics.  
-For example, the inclusion of the category of games and deterministic strategies into the category of games and nondeterministic strategies is the identity on objects, so it is a promonad.  
-So is the inclusion of the category of games and innocent strategies into the category of games and visible strategies.
+For example, the inclusion of the category of games and deterministic strategies into the category of games and nondeterministic strategies from \cite{mcCHFiniteND} is the identity on objects, so it is a promonad.
+So is the inclusion of the category of games and innocent strategies (corresponding to stateless programs) into the category of games and visible strategies (corresponding to stateful programs) from \cite{SamsonGuyIAPassive}.
 
-More generally, this fits in with the idea that effects should not normally create new types, but should instead give us more flexibility when it comes to writing programs -- exactly what is modelled by an identity-on-objects functor.
+What these models have in common is that they model effects by changing the morphisms (i.e., the programs) but not the objects (i.e., the types).  
+Though effectful types can be useful [REFERENCE?], the simplest way of adding effects is to give us new ways to create programs between existing types, and this is the formalism that we will adopt in this paper.
 
-On the other hand, the sheer generality of promonads means that they don't give us any ways to actually create new models, since the data required to specify one is the entire category that we are trying to build.
+So promonads give a good general framework for the denotational semantics of effects.
+On the other hand, their sheer generality means that they don't give us any ways to actually create new models, since the data required to specify one is the entire category that we are trying to build.
 
@@
 Then, if $A$ is a set, we have
-\[
-  \powerset(A) \cong \colim_{X\object\Surj^{op}} [X,A]\,,
-  \]
+\begin{IEEEeqnarray*}{CCC}
+  \colim_{X\object\Surj^{op}} [X,A] & \cong & \powerset(A) \\[6pt]
+  \left(X \xrightarrow{f} A\right) & \mapsto & \text{Im}(f)\,,
+\end{IEEEeqnarray*}
 naturally in $A$.
@@
 
-By setting $D(X)=X.B$, this means that if we have an action of $\M$ on $\Set$, where the monoidal category $\M$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\M\to\Kl_M\Set$.
+By setting $D(X)=X.B$, this means that if we have a lax action of $\M$ on $\Set$, where the monoidal category $\M$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\M\to\Kl_M\Set$.
 
@@
 The point of these last two sections can be summarized as follows.  
-If a monad $M$ on $\Set$ can be expressed as the colimit of an action of a weakly filtered monoidal category $\M$ on $\Set$, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
+If a monad $M$ on $\Set$ can be expressed as the colimit of a lax action of a weakly filtered monoidal category $\M$ on $\Set$, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
 More specifically, there is a full functor $\Kl_M\Set\to \Set/\M$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.
+
+For example, since the nonempty power set monad may be expressed as the colimit of the lax action of the weakly filtered category $\Surj^{+\,op}$ on $\Set$, we get an alternative way to model it by using the category $\Set/\Surj^{+\,op}$ rather than the usual Kleisli category.
+Though these two categories are not equal, the colimit representation gives rise to a natural functor from one to the other, which is the same as the amalgamation functor that we defined earlier.
 
@@
 
+If we consider the case that $\M$ is trivial, so the action is a monad $M$ given by $MA = I.A$, then this composition becomes
+\[
+  A \xrightarrow{f}
+  M B \xrightarrow{M g}
+  M M C \xrightarrow{\passoc_{I,I,C}}
+  M C\,,
+  \]
+which is precisely the usual Kleisli composition.
+
 There is a natural functor $J\from \C \to \C/\M$ that is the identity on objects and that sends the morphism $f\from A \to B$ in $\C$ to the composite
@@
 considered as a morphism $A\to B$ in $\C/\M$.
+
+Let us see what that looks like when our action is the action of $\Surj^{+\,op}$ on $\Set$ that we considered earlier.  
+In that case, a morphism $A\to B$ is given by a function $A \to [X,B]$, or equivalently $X \to [A,B]$.
+We may identify this function with its image, which is a subset of $[A,B]$, and this identification corresponds precisely to the equivalence relation that is automatically given by our construction; namely, the smallest equivalence relation such that $X \to [A,B]$ is equivalent to the composite $Y \to X \to [A,B]$ for any surjection $Y \to X$.
+Indeed, if $f\from X \to [A,B]$ and $g \from Y \to [A,B]$ have the same image $\F\subset[A,B]$, then $f$ and $g$ are both equivalent to the inclusion $\F\hookrightarrow [A,B]$, so they are equivalent.
 
@@
 
-\begin{remark}
-  The functor $H$ in Proposition \ref{quotient-universal}(i) sends the object $JA=A$ to the object $FA$.  
-  To define $H$ on morphisms, we use the fact that every morphism $f\from A \to X.B$ from $A$ to $B$ in $\C/\M$ may be factorized as:
+\begin{proof}
+  The proof, which we will not give full details of, comes down to the fact that we can factorize any morphism $f\from A \to X.B$ from $A$ to $B$ in $\C/\M$ as:
   \[
@@
   It therefore suffices to define $H$ on morphisms of the form $Jf$ (which must be sent to $Ff$, since $F=HJ$) and on morphisms of the form $\phi_{X,A}$ (which must be sent to $\psi_{X,A}$, since $\psi=H\phi$).
-  The proof of part (ii) also follows from this factorization.
+  Therefore $H$ is uniquely defined, if it exists, so it suffices to check that the $H$ given by sending the above factorization to the composite
+  \[
+    FA \xrightarrow{Ff}
+    F(X.B) \xrightarrow{\psi_{X,A}}
+    FB
+    \]
+  is indeed a functor satisfying the requirements of the proposition.  
+  Part (ii) is proved in a very similar way.
+\end{proof}
 
-  Thus, one way of thinking of the category $\C/\M$ is as a general theory of categories that extend $\C$, and admit a factorization result whereby every morphism is the composition of a morphism from $\C$ with one of the distinguished morphisms $\phi_{X,A}$.
-
-  For example, in \cite{SamsonGuyIAPassive}, it is shown that any morphism $\sigma \from A\to B$ in the category $\G_{vis}$ of games and visible strategies may be factorized as
-  \[
-    \sigma = A \xrightarrow{\text{Inn}(\sigma)}
-    (\text{Var[S]} \to B) \xrightarrow{\new_S}
-    B\,,
-    \]
-  where $\text{Inn}(\sigma)$ is a morphism in the category of $\G_{inn}$ of games and innocent strategies, $S$ is a set and $\new$ is a special morphism that introduces stateful behaviour.  
-  The $\Var[S]$ construction, which is the game corresponding to a storage cell holding values of the set $S$, may be regarded as an oplax monoidal functor from the category $\Ret$ of sets and retractions into the category of games, and so $\Var[S]\to B$ is a reader-style action.
-  Moreover, it can be shown that $\new$ gives rise to a multiplicative natural transformation, inducing a functor $\G_{inn}/\Ret\to \G_{vis}$.  
-  Then the factorization result we have quoted says precisely that this functor is full.
-\end{remark}
 \begin{remark}
@@
   Note that for more general $\M$, we do not in general get an adjunction between $\C$ and $\C/\M$.
-\end{remark}
-\begin{remark}
+
   The quotient notation we have used is because the universal property we have outlined exhibits $\C/\M$ as a particular weighted coequalizer of the functors $\pr_2,\_.\_\from \M\times\C \rightrightarrows \C$ in $\Cat$.
@@
 
-  This is a strange idea, since we are not used to thinking of, for example, a Kleisli category as quotient of the original category.  
+  When the action is a monad, this is a strange idea, since we are not used to thinking of, for example, a Kleisli category as quotient of the original category.  
   The reason for this is the laxness: we do not identify the objects $A$ and $X.A$ with an isomorphism, but with a morphism in one direction.  
@@
 \begin{remark}
-  Suppose we have an oplax right action of a monoidal category $\M$ on a category $\C$.  
-  This may be regarded as a lax left action of $\M^{co}$ upon $\C^{op}$, and therefore we get a category in the same way in which the objects are the objects of $\C$ and the morphisms from $A$ to $B$ are equivalence classes of morphisms $A.X \to B$ in $\C$.
+  The proof of Proposition \ref{quotient-universal} tells us that one way of thinking of the category $\C/\M$ is as a general theory of categories that extend $\C$, and admit a factorization result whereby every morphism is the composition of a morphism from $\C$ with one of the distinguished morphisms $\phi_{X,A}$.
 
-  In the case that the action is an oplax reader-style action given by $A.X = A\tensor jX$ for some oplax monoidal functor $j\from \M \to \C$, then the natural transformation $\phi_{A,X}$ goes from $J(A\tensor jX)$ to $JA$, and may instead be regarded as a natural transformation $I\to jX$ in $\C$.
-  In that case, the category $\C/\M$ that we obtain is what \cite[4.3.11]{lurie2009} calls the \emph{cone} over the functor $j$.  
-  This is because the universal property in that case is a lax version of the property satisfied by the mapping cone in homotopy theory.
+  Factorization results are very important in the game semantics of effects.  
+  What usually happens is that when we extend a model $\G$ to a new model $\G'$, we wish to show that each morphism in $\G'$ may be written as the composite of a morphism from $\G$ composed with one of a small collection of new morphisms that are readily definable in the language -- for example, nondeterministic oracles, or simple storage cells.
+  This allows us to lift a definability result from the old category to the new one.  
+  If these new morphisms can be cast as the components of some natural transformation $\psi_{X,A}\from X.A \to A$ for some action of some monoidal category $\M$ on $\G$ (and often they can), then Proposition \ref{quotient-universal}(i) gives us a functor from $\G/\M$ to $\G'$.
+  The factorization result then tells us that this functor is full, and so the model $\G'$ can also be defined as a quotient of $\G/\M$.
 \end{remark}
@@
 
+This action is very closely related to the action of $\Surj^{+,op}$ that we defined earlier; indeed, $\Surj^+$ is equivalent to the category of discrete probability spaces taking probabilities in the Boolean semiring $\{0,1\}$ with countable summation given by maximum.
+
 By cutting down the category $\DProb$ we can obtain slightly different notions of probability.  

### 2018-11-16 effects/effects.tex
Finished off the paper.

@@
 \usepackage{mathpartir}
+\usepackage{stmaryrd}
 \def\UrlFont{\rmfamily}
@@
     \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
+\newcommand{\deno}[1]{\left\llbracket#1\right\rrbracket}
+\renewcommand{\ts}{{\;\vdash}}
 
@@
 \newcommand\Mellies{Melli\`{e}s\xspace}
+
+\newcommand{\test}{\texttt{test}}
 
@@
 \newcommand{\polydie}{\textsf{polydie}}
+\newcommand{\multicoin}{\textsf{multicoin}}
 \newcommand{\bool}{\textsf{bool}}
@@
 %
-\title{A Kleisli-like construction for Parametric Monads, with Examples}
+\title{A Kleisli-style construction for Parametric Monads, with Examples}
 %
-\titlerunning{Dum-di-dum}  % abbreviated title (for running head)
+\titlerunning{A Kleisli-Style Construction}  % abbreviated title (for running head)
 %                                     also used for the TOC unless
@@
   \item[Finite support] There is a finite subset $E\subseteq X$ such that $\bP_X(E)=1$.
-  \item[Rational probabilities] $\bP_X(A)\in\mathbb{Q}$ for all $A\subseteq X$.
 \end{description}
 
-The action of $\BProb$ gives rise to a monad on the category of countable sets.
+The action of $\BProb^{op}$ gives rise to a monad on the category of countable sets.
 
@@
 \cite{DanosHarmer} gives a fully abstract game semantics for the language Probabilistic Algol (PA).  
-The base language for PA is the language Idealized Algol (IA) from \cite{SamsonGuyIAPassive}, and it has been extended with a constant $\coin\from\bool$.  
-We give the language a small-step reduction semantics, as shown in Figure \ref{pa-operational}.
+The base language for PA is the language Idealized Algol (IA) from \cite{SamsonGuyIAPassive}, and it has been extended with a constants $\coin\from\bool$.  
+To make things a little more interesting, we will extend this further to incorporate an infinite family of constants $\coin_p\from\bool$, where $p$ ranges over the real interval $[0,1]$.
 
-\begin{figure*}
+We give the language a small-step operational semantics.  
+The rules for the deterministic terms may be derived from the operational semantics given in \cite{SamsonGuyIAPassive}; for example:
+\[
+  \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}
+  \]
+See also \cite{JimGuySmallStep}.
+
+We add two small-step rules for the $\coin_p$ primitives:
+
 \begin{mathpar}
-    \inferrule*{ }{\ia s {(\lambda x.M)\;N} \opto \ia s {M[N/x]}}
+  \inferrule*[left={heads${}_p$}]{ }{\ia s \coin_p \opto \ia s \true}
   \and
-    \inferrule*{ }{\ia s {\Y_T M}\opto \ia s {M (\Y_T M)}}
-    \and
-    \inferrule*{ }{\ia s {\suc \n}\opto\ia s {\n + \mathsf{1}}}
-    \and
-    \inferrule*{ }{\ia s {\pred \n}\opto\ia s {\0 \sqcup (\n - \mathsf{1})}}
-    \and
-    \inferrule*{ }{\ia s {\IfO \0 M N} \opto \ia s M}
-    \and
-    \inferrule*{ }{\ia s {\IfO (\n + \mathsf{1}) M N} \opto \ia s N}
-    \and
-    \inferrule*{ }{\ia s {\If \true\;M\;N} \opto M}
-    \and
-    \inferrule*{ }{\ia s {\If \false\;M\;N} \opto N}
-    \and
-    \inferrule*{ }{\ia s {\deref (\mkvar M N)} \opto \ia s M}
-    \and
-    \inferrule*{ }{\ia s {(\mkvar M N) \coloneqq L} \opto \ia s {N\;L}}
-    \and
-    \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}
-    \and
-    \inferrule*[left={$s(v)=n$}]{ }{\ia s {\deref v} \opto \ia s n}
-    \and
-    \inferrule*{ }{\ia s {\skipp;M} \opto \ia s M}
-    \and
-    \inferrule*{ }{\ia s {\new_T \lambda v.M}\opto \ia {\stup s v 0} M}
-    \and
-    \inferrule*{\ia s M \opto \ia s {M'}}{\ia s {E[M]} \opto \ia s {E[M']}}
-    \and
-    \inferrule*[left=coin]{ }{\ia s \coin \opto \ia s \true}
-    \and
-    \inferrule*[left=coin]{ }{\ia s \coin \opto \ia s \false}
+  \inferrule*[left={tails${}_{1-p}$}]{ }{\ia s \coin_p \opto \ia s \false}\,.
 \end{mathpar}
-  \caption{Small-step operational semantics for Probabilistic Algol, where $E$ ranges over suitable evaluation contexts}
-  \label{pa-operational}
-\end{figure*}
 
-All of these rules are deterministic with the exception of the two marked \LeftTirName{coin}.
-Given an evaluation $\pi = M \to M_1 \to \cdots \to \x$ of a term $M$ of ground type $o$, we define the \emph{weight} $w(\pi)$ of $\pi$ to be $\frac{1}{2^k}$, where $k$ is the number of instances of a \LeftTirName{coin} rule occurring in $\pi$.
+These are the only nondeterministic parts of the operational semantics.
+
+Given a small-step evaluation $\pi = M \to M_1 \to \cdots \to \x$ of a term $M$ of ground type $o$, we define the \emph{probability} $p(\pi)$ of $\pi$ to be the product of all the indices $q$ belonging to \LeftTirName{heads${}_q$} or \LeftTirName{tails${}_q$} rules.
 
@@
 \[
-  \bP(\{x\}) = \sum_{\substack{\text{evaluations}\\\pi = M \to\dots \x}}w(\pi)\,.
+  \bP(\{x\}) = \sum_{\substack{\text{evaluations}\\\pi = M \to\dots \x}}p(\pi)\,.
   \]
@@
 \cite{DanosHarmer} shows how we can define other probabilistic terms using $\coin$.  
-Specifically, they define a term $\polydie\from\bN\to\bN$, where the behaviour of $\polydie n$ is to return the result of tossing an $n$-sided die (with sides numbered $0$ to $n-1$), with each outcome occurring with probability $1/n$.
-The definition of $\polydie n$ in terms of $\coin$ works as follows.  
+Specifically, they define a term $\polydie\from\bN\to\bN$, where the behaviour of $\polydie\,n$ is to return the result of tossing an $n$-sided die (with sides numbered $0$ to $n-1$), with each outcome occurring with probability $1/n$.
+The definition of $\polydie\,n$ in terms of $\coin$ works as follows.  
 We choose some number $k$ such that $2^k\ge n$ and then toss the coin $n$ times to give one of $2^k$ outcomes.  
@@
 This gives rise to a reader-style action of $\BProb^{op}/\G$, and the resulting category $\G/\BProb^{op}$ is therefore a symmetric monoidal closed category.
-Unfortunately, the monoidal product on $\G/\BProb^{op}$ is not Cartesian; the problem is that there is no unique way to form the copairing of
 
-\bibliographystyle{spbasic}
+\subsection{Testing morphisms and plays}
+
+The equivalence relation on morphisms is still too weak for our purposes.  
+For example, if the boolean type $\bB$ carries a Bernoulli distribution with coefficient $p$, then the diagonal map $\Delta\from \bB\to \bB\times\bB$ should be equivalent to the identity $\id\from\bB\times\bB\to\bB\times\bB$ as terms of type $\bB\times\bB$, because the projections on to each component are equivalent.
+However, they are not yet equivalent in our category.
+
+To improve the equivalence relation, we introduce the concept of \emph{testing morphism} for an object $A$ that is the denotation of an Idealized Algol term.
+This is a term of type $(\bN \to A) \to A$ that is the denotation of an Idealized Algol term of the form
+\[
+  \test_{n_1,\cdots,n_k} = \lambda f.\new\;v\coloneqq 0 \text{ in } f(v \coloneqq \deref v + 1; \case\,v\,\_\,n_1\,\cdots\,n_k\,\Omega)\,,
+  \]
+where $n_1,\cdots,n_k$ is a sequence of numbers.  
+The effect of this term is to call $f$, and to pass in the numbers $n_1,\cdots,n_k$ in turn, and diverging if $f$ calls its argument more than $k$ times.
+In game semantics, the sequence $n_1,\cdots,n_k$ is more easily recognized as a sequence of moves occurring in the game $\bN$ on the left.
+
+Given a morphism $\sigma\from \bN \to A$, we say that the sequence $n_1,\cdots,n_k$ is a \emph{play} of $\sigma$ if it is minimal (with respect to the prefix ordering) such that $\test_{n_1,\cdots,n_k}(\sigma)$ represents a non-diverging term.
+In that case, the \emph{result} of the play is the strategy $\test_{n_1,\cdots,n_k}(\sigma)$ for $A$.
+
+Now, if the set $\bN$ carries a probability distribution, then this gives rise to a sub-probability distribution on the set of plays for $\sigma$, where the probability associated to the sequence $n_1,\cdots,n_k$ is the product of the probabilities of the $n_i$.
+This then induces a discrete probability distribution on the set of morphisms $1\to A$.
+
+We say that two morphisms $\sigma,\tau\from \bN\to A$ from $1$ to $A$ in $\G/\BProb$ are equivalent if they give rise to the same probability distribution on the set of strategies for $A$.  
+This equivalence relation refines our earlier one.
+
+\subsection{Single-threaded morphisms}
+
+Our category is symmetric monoidal closed, but not yet Cartesian closed.  
+A trick that is often used in Game Semantics (see, for example, \cite{mcCHFiniteND} and \cite{DanosHarmer}) is to pass to a category of \emph{single-threaded} strategies; this is equivalent to cutting down to those morphisms that are comonoid homomorphisms.
+
+Note that, in our category, every object has a natural commutative comonoid structure that arises from diagonal $\Delta\from A\to A\times A$ in the original category.  
+We say that a morphism $\sigma\from A\to B$ is \emph{single-threaded} if it is a homomorphism of the comonoid structures on $A$ and $B$; i.e., if the following square commutes.
+\[
+  \begin{tikzcd}
+    A \arrow[r, "\sigma"] \arrow[d, "\Delta"']
+      & B \arrow[d, "\Delta"] \\
+    A \times A \arrow[r, "\sigma\times\sigma"]
+      & B \times B
+  \end{tikzcd}
+  \]
+Since the category of commutative comonoids in a symmetric monoidal category is automatically Cartesian closed (see, for example, \cite{Freyd}), this gives us a Cartesian closed category.
+
+The deterministic terms are all comonoid homomorphisms.  
+As long as we have applied the equivalence relation outlined above, the natural morphisms $\phi_{X,A}$ are also comonoid homomorphisms.
+
+\subsection{Denotational semantics and adequacy}
+
+We may now inductively build up a denotational semantics for PA.  
+The deterministic terms may all be defined inside the base category $\G$ and transported into our new category via the natural inclusion.  
+The probabilistic term $\coin_p$ is given by the natural morphism $\phi_{B_p, 1}$, where $B_p$ is a Bernoulli space with coefficient $p$.  
+That is to say, it is given by the pair
+\[
+  ((\{H,T\}, \mu(H)=p, \mu(T)=1-p), 1 \to (\{H,T\} \to \bB))\,
+  \]
+where the function on the right sends $H$ to $\true$ and $T$ to $\false$.
+
+Note now that the denotation of a term $M = C[\coin_{p_1},\cdots,\coin_{p_j}]T$ is given by the following morphism.
+\[
+  \bB^j
+  \xrightarrow{\deno{b_1,\cdots,b_j\ts C[b_1,\cdots,b_j]}}
+  \deno{T}\,,
+  \]
+where the distribution on the product $\bB^j$ is the product of Bernoulli distributions.
+
+Fix an injection $r\from\bB^j\to \bN$ (for instance, the one given by ibinary representation) and suitable projection functions $\pr_i \from \bN \to \bB$ such that $\pr_i(r(v))$ is the $i$-th entry of $v$.
+Let $\multicoin\from\nat$ be the term (depending on the values of the $p_i$) given by
+\[
+  (r\;\coin_{p_1}\,\cdots\,\coin_{p_j})\,.
+  \]
+Now the operational semantics of $\pr_i(\multicoin)$ is the same as the operational semantics of $\coin_{p_i}$, since the projections from the product are probability-preserving.  
+This means that any evaluation $\pi$ of the term $M$ may be pegged to an evaluation of the term formed by replacing each instance of $\coin_{p_i}$ in $M$ with $\pr_i(\multicoin)$.
+
+\begin{proposition}[Computational Adequacy]
+  Let $M = C[\multicoin]\from \com$ be a term of Idealized Algol, where $C$ is a multi-holed deterministic IA context.
+  Let $p$ be the sum of the probabilities of all evaluation sequences of $M$ that terminate at $\skipp$.
+
+  The denotation of $M$ is a morphism $\bN \to \bC$ as outlined above.
+
+  Then we get an induced sub-probability distribution on the set of morphisms $1\to A$.  
+  The adequacy result is that $p$ is the same as the induced probability of the morphism $\deno{\skipp}$.
+\end{proposition}
+\begin{proof}
+  Each terminating evaluation sequence of $M$ corresponds to a finite sequence $n_1,\cdots,n_k$ of the different values that $\multicoin$ takes on over the course of the evaluation of the term.  
+  By inspection, we may peg this evaluation of $M$ exactly to the evaluation of the term $\test_{n_1,\cdots,n_k} (\lambda n.C[n])$ in pure deterministic Idealized Algol, and therefore this IA term must converge.
+  By the Adequacy result for Idealized Algol \cite{SamsonGuyIAPassive}, an IA term converges to $\skipp$ if and only if its denotation is $\deno{\skipp}$.  
+  Therefore, there is bijective matching between terminating evaluation sequences of $M$ and plays of the morphism $\deno{M}$, with each one getting the same probability.  
+  The result follows.
+\end{proof}
+
+\subsection{Full Abstraction}
+
+In order to prove full abstraction for our model, we will define a further equivalence on morphisms.  
+Say that two morphisms $f,g\from A \to B$ are \emph{intrinsically equivalent} if and only if for all morphisms $\alpha\from (A\to B)\to\bC$, $\alpha(f)$ and $\alpha(g)$ are probabilistically equivalent in the sense given above.
+Then our full abstraction result becomes:
+
+\begin{proposition}[Full Abstraction]
+  Let $M,N\from T$ be two PA terms.  
+  Then $M$ and $N$ are observationally equivalent if and only if their denotations $\deno{M}$ and $\deno{N}$ are intrinisically equivalent.
+\end{proposition}
+
+One direction (soundness) follows immediately from our Computational Adequacy result.  
+To prove the other direction, it suffices to show that any compact strategy is definable \cite{CurienFullAbstraction}, where we say that a morphism $\sigma\from A \to (X \to B)$ from $A$ to $B$ is \emph{compact} if it is compact when considered as a morphism in $\G$.
+We prove this using a factorization result:
+\begin{lemma}[Deterministic factorization]
+  Let $\sigma\from A \to B$ be a morphism in $\G/\BProb^{op}$.  
+  Then $\sigma$ may be factorized as $\text{Det}(\sigma)(\multicoin)$, where $\text{Det}(\sigma)\from \bN \to A \to B$ is a strategy in the image of the inclusion functor $J\from \G \to \G/\BProb^{op}$, and $\multicoin$ is defined for some values $p_1,\cdots,p_k$.
+\end{lemma}
+\begin{proof}
+  Treat $\sigma$ as a morphism $A \to X \to B$ in $\G$.  
+  Since $X$ is finitely supported, there is a probability-preserving function $\bN \to X$, for some finitely supported distribution on $\bN$.  
+  So $\sigma$ is equivalent to a morphism $A \to \bN \to B$, and then the factorization is automatic.
+\end{proof}
+
+\bibliographystyle{spphys}
 \bibliography{effects}

### 2018-11-17 effects/effects.tex
Shortened some sections.

@@
 
-It is instructive at this point to see what happens if we generalize from functors to profunctors.  
-We define a \emph{promonad} on a category $\C$ to be a monoid in the monoidal category $\Prof[\C,\C]$ of endo-profunctors on $\C$, where the monoidal product in $\Prof[\C,\C]$ is given by composition of profunctors.
-This concept generalizes that of a monad, since an endofunctor $M\from \C\to\C$ may be identified with the profunctor $\C[\_,M(\_)]\from \C^{op}\times\C\to\Set$.
+One clue comes from generalizing from functors to profunctors.  
+Since a monad is a monoid in the category $\End[\C]$ of endofunctors on $\C$ with monoidal product given by functor composition, we can define a \emph{promonad} to be a monoid in the category $\Prof[\C,\C]$ of endoprofunctors on $\C$ (i.e., functors $\C^{op}\times\C\to \Set$), where the monoidal product is profunctor composition.
+Since a functor $\F\from \C\to \D$ may be identified with the profunctor $\D[F(\blank),\blank]\from\C^{op}\times\D\to\Set$, this certainly generalizes the idea of a monad.
 
-Since the set $\C[A,MB]$ is precisely the set of Kleisli morphisms from $A$ to $B$, it is natural to wonder whether we can perform a Kleisli-type construction on a promonad as well.  
-it turns out that we can: if $\D\from \C^{op}\times\C\to\Set$ is a promonad, then we may define a category (also called $\D$) whose objects are the objects of $\C$, and where the morphisms from $A$ to $B$ are the elements of the set $\D(A,B)$.
-The promonad action
-\[
-  (\D\pfc\D)(A,C) = \int^{B}\D(A,B)\times\D(B,C) \to \D(A,C)
-  \]
-gives us composition in our category and the unit
-\[
-  1(A,B)=\C[A,B]\to \D[A,B]
-  \]
-gives us a functor $\C\to\D$ (and, in particular, the identity morphisms).
+A little thought, however, shows that a promonad is a vast generalization of a monad.  
+Any promonad $\D\from\C^{op}\times\C\to\Set$ on a category $\C$ may be identified \cite{Promonad} with a category (also called $\D$) where the objects are the objects of $\C$ and the morphisms from $A$ to $B$ are elements of the set $\D(A,B)$.
+The promonad structure gives us composition and identities in the category $\D$, and also a functor $J\from \C\to\D$ that is the identity on objects.
 
-In fact, the converse is true: if $\C$ and $\D$ are categories with the same objects and $J\from \C\to\D$ is an identity-on-objects functor, then the functor $\D(JA,JB)=\D(A,B)\from\C^{op}\times\C\to\Set$ may be given the structure of a promonad on $\C$.
-Thus, the rather complicated definition of a promonad is in fact equivalent to the much simpler idea of an identity-on-objects functor.
-We shall therefore use the word `promonad' to mean both things.
+In the other direction, if we have such a $\C\xrightarrow{J}\D$, then the hom functor $\D(J(\blank),J(\blank)$ is a promonad on $\C$.  
+Thus, promonads on $\C$ generalize the Kleisli construction to such an extent that they incorporate, among others, any category formed from $\C$ by keeping the same objects and adding new morphisms, such as the game semantics models of state \cite{SamsonGuyIAPassive} and nondeterminism \cite{mcCHFiniteND}.
 
-In one sense this is very exciting for us, because we can see that promonads generalize not only monads, but also a very large number of the models developed in Game Semantics.  
-For example, the inclusion of the category of games and deterministic strategies into the category of games and nondeterministic strategies from \cite{mcCHFiniteND} is the identity on objects, so it is a promonad.
-So is the inclusion of the category of games and innocent strategies (corresponding to stateless programs) into the category of games and visible strategies (corresponding to stateful programs) from \cite{SamsonGuyIAPassive}.
-
-What these models have in common is that they model effects by changing the morphisms (i.e., the programs) but not the objects (i.e., the types).  
-Though effectful types can be useful [REFERENCE?], the simplest way of adding effects is to give us new ways to create programs between existing types, and this is the formalism that we will adopt in this paper.
-
-So promonads give a good general framework for the denotational semantics of effects.
-On the other hand, their sheer generality means that they don't give us any ways to actually create new models, since the data required to specify one is the entire category that we are trying to build.
-
-One way of describing the purpose of this work, then, is to discover classes intermediate between monads and promonads that are more general than pure monads but can still be specified in a concise way that allows us to transfer them between different settings.
-
-\subsection{Monads on presheaf categories}
-
-We can think of an endo-profunctor $\F\from \C^{op}\times\C\to \Set$ as a functor $\C\to [\C^{op},\Set]$.  
-Since the Yoneda embedding exhibits $[\C^{op},\Set]$ as the free cocompletion of $\Set$, this can alternatively be characterized as a colimit-preserving endofunctor on $[\C^{op},\Set]$.  
-Similarly, any promonad on $\C$ can alternatively be considered as a monad on $[\C^{op},\Set]$ whose underlying endofunctor preserves colimits.
+On the other hand, what promonads capture is quite a natural simple way of modelling effects: keep the same types (objects), but give us new ways to write programs (morphisms).  
+Although effectful types are important (e.g., in work on call-by-push-value \cite{Cbpv}), we shall adopt this paradigm in our paper.  
+So one way to state our goal is that we are looking for systematic ways to construct promonads on a category that are more general than the existing Kleisli construction for monads.
 
@@
 \Mellies \cite{ParametricMonads}, following work by Smirnov \cite{Smirnov2008}, has demonstrated that the concept of a lax monoidal category action is a useful generalization of that of a monad.  
-A lax action of a monoidal category $\M$ upon a category $\C$ is a lax monoidal functor $\M\to \End[\C]$; monads are the special case when $\M$ is trivial.  
+A lax action of a monoidal category $\M$ upon a category $\C$ is a lax monoidal functor $\M\to \End[\C]$ (considered as a functor $\blank.\blank\from\M\times\C\to\C)$; monads are the special case when $\M$ is trivial.
 For this reason, \Mellies renames lax monoidal actions to `parametric monads', where we think of the action of $\M$ as a kind of monad on $\C$ that is parameterized by the objects of $\M$.
@@
 First, if $\C$ is a category and $\M$ a monoidal category, we define a \emph{parametric promonad on $\C$ parameterized by $\M$} to be a lax monoidal functor $\M\to\Prof[\C,\C]$.
+In a similar way to before, if we have a parametric monad $\blank.\blank\from \M\times\C\to\C$ then we may identify it with the parametric promonad given by $\D(X,A,B)=\C(A,X.B)$.
 
-As with promonads, we can now look at what we have defined and try to recast it as a particular kind of category.  
-Suppose that $\D\from \M\times\C^{op}\times\C$ is a parametric promonad on $\C$ parameterized by $\M$.  
-After some thought, we can see that $\D$ corresponds to a category whose objects are the objects of $\C$ and where the morphisms from $A$ to $B$ are labelled by objects of $\M$ in such a way that the composition of a morphism labelled with $X$ and a morphism labelled with $Y$ is a morphism labelled with $X\tensor Y$.
+As with promonads, we can now take a parametric promonad $\D\from \M\times\C^{op}\times\C\to\Set$ and try to recast it as a particular kind of category.  
+There are various ways to do it, but one is to view it as a bicategory whose objects are the objects of $\C$, where the elements of the set $\D(X,A,B)$ are considered as $1$-morphisms from $A$ to $B$ and where morphisms $X\to Y$ in $\M$ give rise to $2$-morphisms between the elements of $\D(X,A,B)$ and the elements of $\D(Y,A,B)$.
 
-One way to state this is as follows.  
-Given a parametric promonad $\D\from \M\times\C^{op}\times\C\to \Set$, we define a bicategory $\D^2$:
-\begin{itemize}
-  \item whose objects are the objects of $\C$,
-  \item where the $1$-morphisms from $A$ to $B$ are pairs $(X,f)$, where $X$ is an object of $\M$ and $f\in\D(X,A,B)$
-  \item and where the $2$-morphisms from $(X,f)$ to $(Y,g)$ are morphisms $h\from X\to Y$ in $\M$ such that $\D(h,A,B)(f)=g$.
-\end{itemize}
-This bicategory comes equipped with two important bifunctors:
-\begin{itemize}
-  \item a bifunctor $J\from \C\to\D^2$ (where we consider $\C$ as a bicategory with only identity $2$-morphisms;
-  \item a bifunctor $l\from \D^2\to \M$ given by the `labelling' (considering $\M$ as a bicategory with a single object).
-\end{itemize}
+A natural idea is to turn this bicategory into a $2$-category by quotienting out by the action of the $2$-morphisms, which gives us the following collapse from parametric promonads to promonads.
+\[
+  \D \mapsto \colim_{X\object\M}\D(X,\blank,\blank)
+  \]
 
-In order to get a promonad resolution of the parametric promonad, then, we need to convert this bicategory into a $1$-category $\D$, which we do by quotienting out the $1$-morphisms in $\D^2$ by the action of the $2$-morphisms: i.e., the smallest equivalence relation such that two $1$-morphisms are related if there is a $2$-morphism from one to the other.
-
-More explicitly, the set of $1$-morphisms from $A$ to $B$ in our new category will be given by the following colimit.
-\[
-  \D(A,B) = \colim_{X\object\M} \D(X,A,B)
-  \]
-This category $\D$ now admits an identity-on-objects functor from $\C$, meaning that we have found a natural collapse from parametric promonads to ordinary promonads.
-
-In the particular case that the parametric promonad is in fact a parametric \emph{monad}, then we will call the category we obtain $\C/\M$.  
+In the particular case that the parametric promonad is in fact a parametric \emph{monad} (so $\D(X,A,B) = \C(A,X.B)$), then we will call the category we obtain $\C/\M$.  
 The morphisms in $\C/\M$ are given by
@@
 The colimit that appears in the definition of the category $\C/\M$ is instructive, because it is linked to the fact that many important monads may be expressed as colimits.  
-For example, let $\Surj$ be the category of sets and surjections.  
+For example, let $\Surj^+$ be the category of non-empty sets and surjections.  
 Then, if $A$ is a set, we have
 \begin{IEEEeqnarray*}{CCC}
-  \colim_{X\object\Surj^{op}} [X,A] & \cong & \powerset(A) \\[6pt]
+  \colim_{X\object\Surj^{+\,op}} [X,A] & \cong & \powerset(A) \\[6pt]
   \left(X \xrightarrow{f} A\right) & \mapsto & \text{Im}(f)\,,
@@
 
-This is useful, because the body of the colimit -- i.e., the function set $[X,A]$ -- has a natural equivalent inside any Cartesian closed category that admits a functor out of $\Set$.  
-Moreover, the functor $[X,A]$ is actually an \emph{action} of $\Surj^{op}$ (with the Cartesian product) upon the category of sets.  
+This is useful, because the body of the colimit -- i.e., the function set $[X,A]$ -- has a natural equivalent inside any Cartesian closed category $\C$ that admits a functor $\F\from\Set\to\C$; i.e., the internal hom $\F(X)\implies A$.
+Moreover, the functor $[X,A]$ is actually a lax action of $\Surj^{+,op}$ (with the Cartesian product) upon the category of sets, and the monad structure of the powerset may be deduced from the structure of this action via the colimit.
 So even though we cannot define the powerset \emph{monad} inside arbitrary Cartesian closed categories, we can still define this action of $\Surj^{op}$.
 
-Unfortunately, when we try to apply our construction to this action in the category of sets, we do not get the usual Kleisli category for the powerset monad.  
-To see why, note that from the discussion above, we have
-\begin{IEEEeqnarray*}{rCl}
-  \Set/\Surj^{op}(A,B) & = & \colim_{X\object\Surj^{op}}[A,[X,B]] \\
-  & \cong & \colim_{X\object\Surj^{op}}[X,[A,B]] \\
-  & \cong & \powerset([A,B])\,,
-\end{IEEEeqnarray*}
-while the morphisms in the Kleisli category take a different form:
+The idea, then, is that we might try to model nondeterminism in other categories (where we might not be able to define the powerset) using this parametric monad.  
+One unfortunate fact is that these two alternatives (powerset monad vs lax action of $\Surj^{+,op}$) do not give rise to the same promonad in the category of sets.  
+Indeed, if we have a general action of a monoidal category $\M$ on $\Set$, then (as long as the possibly large colimits exist) we get a monad on $\Set$ given by
 \[
-  \Kl_{\powerset}\Set(A,B) = [A,\powerset(B)]\,.
+  M A = \colim_{X\object\M} X.A\,
   \]
-Nevertheless, there are still a few things we can take from this.  
-The sets $\powerset([A,B])$ and $[A,\powerset(B)]$ are not equal, but there is still a natural function
+and the morphisms between sets $A$ and $B$ in the Kleisli category are given by
 \[
-  \powerset([A,B]) \to [A,\powerset(B)]\,,
+  [A, \colim_{X\object\M} X.B]\,.
   \]
-that sends a set $\F$ of functions to the function $h$ (the \emph{amalgamation} of $\F$) where
+Meanwhile, the morphisms between $A$ and $B$ in the category $\C/\M$ are given by the set
 \[
-  h(a) = \{f(a)\suchthat f \in \F\}\,.
+  \colim_{X\object\M} [A,X.B]\,,
   \]
-This amalgamation function is not \emph{quite} surjective: for example, suppose that $g\from \{0,1\}\to \powerset(\{0\})$ sends $0$ to $\{0\}$ and $1$ to the empty set.  
-Then $g$ is not the amalgamation of any set of functions $\{0,1\}\to\{0\}$.  
-However, if we use the \emph{nonempty powerset monad} $\powerset^+$ (which corresponds to taking the colimit over the opposite of the category $\Surj^+$ of nonempty sets and surjections), then the amalgamation function gives us a surjection
+and the two sets need not be the same, since the colimit might not commute with the functor $[A,\blank]$.
+
+However, if the category $\M$ satisfies certain additional properties, we can get some relation back.  
+There is always a natural identity-on-objects functor between the two categories, given by the natural map
 \[
-  \powerset^+([A,B])\twoheadrightarrow [A,\powerset^+(B)]\,.
+  \colim_{X\object\M}[A,X.B] \to [A, \colim_{X\object\M} X.B]\,,
   \]
-This means that we can recover the Kleisli category for the nonempty powerset monad on $\Set$ by taking the quotient by a suitable equivalence relation to the category $\Set/(\Surj^{+\,op}$).
+and if the category $\M$ admits a cocone over every discrete diagram (i.e., if whenever $(X_i)$ is a collection of objects of $\M$ there is some $Y$ such that there is a morphism $f_i\from X_i\to Y$ for all $i$), then this function is surjective, meaning that the functor will be full.
+The category $\Surj^{+,op}$ has this property (via the Cartesian product and its projections, which are always surjective for non-empty sets).  
+In the case of the action of $\Surj^{+,op}$ that gives rise to the powerset monad, the natural map given above is the surjection $\powerset[A,B]\to [A,\powerset B]$ that takes a set $\F$ of functions $A\to B$ and forms the function $A\to\powerset B$ that sends an element $a$ to the set
+\[
+  \{f(a)\suchthat f\in\F\}\,.
+  \]
+This means that we may recover the Kleisli category from the category given by the action by taking the quotient by a further equivalence relation on morphisms.
 
-In fact, this surjection has a natural right inverse, formed by sending a function $h\from A\to\powerset^+(B)$ to the \emph{largest} possible set $\F\subseteq[A,B]$ such that for all $f\in \F$ and $a\in A$, $f(a)\in h(a)$.
-The composition of these inverses sends a set of functions $A\to B$ to its `amalgamation closure':
-\[
-  \ac(\F) = \{g\from A \to B\suchthat\forall a\in A\esuchthat g(a)=f(a)\text{ for some $f\in \F$}\}\,.
-  \]
-By restricting our set of morphisms, then, to those that are fixed points of this operator, we may recover the Kleisli category for $\powerset^+$.
-
-In the next section, we will see how to generalize this idea to other monads, and to other categories.
-
-\subsection{Weakly filtered colimits}
-
-Suppose we have a lax action of a monoidal category $\M$ upon a cocomplete category $\C$.  
-Then we may copy the collapse from parametric promonads to promonads and define a monad on $\C$ given by:
-\[
-  M A = \colim_{X\object\M}A.X\,.
-  \]
-Unfortunately, as in the case of the powerset monad above, this transformation does not commute with the collapse from parametric promonads to promonads.  
-Indeed, if we consider our action as a parametric promonad and apply the collapse, then we get a category where the morphisms from $A$ to $B$ are given by the colimit
-\[
-  \colim_{X\object\M} \C(A,X.B)\,,
-  \]
-while the morphisms from $A$ to $B$ in the Kleisli category for the monad $M$ are given by
-\[
-  \C(A,\colim_{X\object\M} X.B)\,.
-  \]
-There is a natural morphism from the first colimit into the second expression, but it is not an isomorphism in general.
-If $\C$ is the category of sets, there is a well known result that states that if $\M$ is a $\kappa$-filtered category and $|A|<\kappa$, then the colimit will commute with the functor $[A,\_]$, but this does not help us, since the category $\M$ is not filtered in most of the cases we are interested in (e.g., the category $\Surj^{op}$ has not got morphisms coequalizing parallel pairs, since such maps cannot be chosen to be surjective in general).
-
-Instead, we try for the next best thing, which is to show that the natural map $\colim_{X\object\M}\C(A,X.B)\to\C(A,\colim_{X\object\M}X.B)$ is a surjection if $\M$ satisfies some weaker conditions.
-
-We define (see, for example, \cite[Def.
-16]{WeaklyFiltered}) a \emph{$\kappa$-weakly filtered category} to be one in which every \emph{discrete} diagram of size $<\kappa$ admits a cocone; i.e., a non-empty category such that whenever $(X_\alpha)_{\alpha<\kappa}$ is a collection of objects we have some object $Y$ and morphisms $X_\alpha\to Y$ for each $\alpha$.
-
-\begin{example}
-  The category $\Surj^{+\,op}$ is $\kappa$-weakly filtered for arbitrary $\kappa$, because if $(X_\alpha)_{\alpha<\kappa}$ is a collection of sets, then we can take their Cartesian product, and the projections will be surjective.
-
-  The category $\Surj^{op}$ is not weakly filtered, because if there is a surjection from an object $X$ to the empty set, then there is no surjection from $X$ to any other set.
-\end{example}
-
-The importance of $\kappa$-weakly filtered limits is shown by the following result.
-
-\begin{proposition}
-  \label{prop:weakly-filtered}
-  If $\M$ is a $\kappa$-weakly filtered category, $D\from \M\to \Set$ is a functor and $A$ is a set with cardinality less than $\kappa$, then the natural function
-  \[
-    \colim_{X\object\M}[A,D(X)]\to [A,\colim_{X\object\M}D(X)]
-    \]
-  is a surjection.
-\end{proposition}
-\begin{proof}
-  Given a function $h\from A \to \colim_{X\object\M}D(X)$, for each $a\in A$, choose some $X_a\object\M$ such that $h(a)\in D(X_a)$.  
-  Since $\M$ is $\kappa$-weakly filtered, there is some object $Y$ of $\M$ that admits morphisms out of all of the $X_a$, and therefore $h$ may be considered as a function $A \to D(Y)$. \qed
-\end{proof}
-
-By setting $D(X)=X.B$, this means that if we have a lax action of $\M$ on $\Set$, where the monoidal category $\M$ is $\kappa$-weakly filtered for any $\kappa$, then we get a full functor $\Set/\M\to\Kl_M\Set$.
-
-Moreover, if the colimit satisfies additional properties, then the $Y$ in the proof of Proposition \ref{prop:weakly-filtered} can be chosen in a functorial manner, so that we get a faithful right inverse to this full functor.
-
-\begin{example}
-  If $f\from A \to \colim_{X\object\Surj^{+\,op}}[X,B]$ is a function with $f(a)\in [X_a,B]$ for each $a$, then $f$ is equivalent to a function
-  \[
-    \tilde{f}\from A \to \left[\prod_{a\in A}X_a,B\right]
-    \]
-  via the surjections $\prod_{a\in A}X_a\to X_b$ for each $b\in A$.  
-  The operator $f\mapsto\tilde{f}$ is well-defined in this case, and gives rise to the amalgamation functor that we considered in the previous section.
-\end{example}
-
-The point of these last two sections can be summarized as follows.  
-If a monad $M$ on $\Set$ can be expressed as the colimit of a lax action of a weakly filtered monoidal category $\M$ on $\Set$, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
+In general, if a monad $M$ on $\Set$ can be expressed as the colimit of a lax action of a monoidal category $\M$ on $\Set$, where $\M$ admits a cocone over every discrete diagram, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
 More specifically, there is a full functor $\Kl_M\Set\to \Set/\M$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.
-
-For example, since the nonempty power set monad may be expressed as the colimit of the lax action of the weakly filtered category $\Surj^{+\,op}$ on $\Set$, we get an alternative way to model it by using the category $\Set/\Surj^{+\,op}$ rather than the usual Kleisli category.
-Though these two categories are not equal, the colimit representation gives rise to a natural functor from one to the other, which is the same as the amalgamation functor that we defined earlier.
-
 The benefit of reasoning about the action of $\M$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories.  
 For instance, the action of $\Surj^{+\,op}$ on $\Set$ may be replicated inside any monoidal closed category that admits a functor out of the category of sets (for example, most models of PCF or Idealized Algol).
+We will see later that the non-empty powerset monad has a probabilistic counterpart, where the set of discrete probability distributions on a set may be obtained as a colimit over the category of probability spaces and probability-preserving maps, which satisfies similar properties, allowing us to model discrete probability in categories other than $\Set$.
 
@@
 Let $\M$ be a monoidal category and let $\C$ be a category.  
-Then a \emph{lax left action} of $\M$ on $\C$ is a functor $\_.\_\from \M\times\C\to \C$ that gives rise (through currying) to a lax monoidal functor $\M\to \End[\C,\C]$.  
+Then a \emph{lax left action} of $\M$ on $\C$ is a functor $\blank.\blank\from \M\times\C\to \C$ that gives rise (through currying) to a lax monoidal functor $\M\to \End[\C,\C]$.  
 In other words, we have natural transformations $\passoc_{X,Y,A}\from X.Y.A\to (X\tensor Y).A$ and $\lun_A\from A \to I.A$ making the following diagrams commute for all objects $A$ of $\C$ and $X,Y,Z$ of $\M$.
@@
 
-      Since the functors $\_\tensor U$ and $U\implies \_$ are adjoint, any reader-style lax action $jX \implies A$ may also be regarded as an oplax action $A \tensor jX$.  
+      Since the functors $\blank\tensor U$ and $U\implies \blank$ are adjoint, any reader-style lax action $jX \implies A$ may also be regarded as an oplax action $A \tensor jX$.  
       We shall refer to these oplax actions as \emph{reader-style} too.
@@
 
-  The quotient notation we have used is because the universal property we have outlined exhibits $\C/\M$ as a particular weighted coequalizer of the functors $\pr_2,\_.\_\from \M\times\C \rightrightarrows \C$ in $\Cat$.
+  The quotient notation we have used is because the universal property we have outlined exhibits $\C/\M$ as a particular weighted coequalizer of the functors $\pr_2,\blank.\blank\from \M\times\C \rightrightarrows \C$ in $\Cat$.
   It may therefore be regarded as a lax $2$-dimensional analogue of the quotient $X/G$ of a set $X$ by a group or monoid action.
@@
 
-In our setting, the two functors $\pr_2$ and $\_.\_$ from $\M\times\C \to \C$ form a reflexive pair, since they have a common section $h\from \C \to \M\times \C$ given by $h(A) = (I, A)$.  
+In our setting, the two functors $\pr_2$ and $\blank.\blank$ from $\M\times\C \to \C$ form a reflexive pair, since they have a common section $h\from \C \to \M\times \C$ given by $h(A) = (I, A)$.  
 It turns out that a similar result then applies.
@@
 Note that this may not be true for arbitrary actions, even for monads.  
-For example, the Kleisli category for the power set monad on $\Set$ (which is better known as the category of sets and relations) is monoidal closed, but with inner function space given by the Cartesian product, and not by the function space from $\Set$.
+For example, the Kleisli category for the powerset monad on $\Set$ (which is better known as the category of sets and relations) is monoidal closed, but with inner function space given by the Cartesian product, and not by the function space from $\Set$.
 
@@
 
-We want to exhibit this monad as the colimit of an action, as we did for the power set monad earlier.  
+We want to exhibit this monad as the colimit of an action, as we did for the powerset monad earlier.  
 We define a \emph{discrete probability space} to be a pair $(X,\bP_X)$, where $X$ is a set and $\mu$ a discrete probability measure on $X$.  
@@
 \[
-  \test_{n_1,\cdots,n_k} = \lambda f.\new\;v\coloneqq 0 \text{ in } f(v \coloneqq \deref v + 1; \case\,v\,\_\,n_1\,\cdots\,n_k\,\Omega)\,,
+  \test_{n_1,\cdots,n_k} = \lambda f.\new\;v\coloneqq 0 \text{ in } f(v \coloneqq \deref v + 1; \case\,v\,\blank\,n_1\,\cdots\,n_k\,\Omega)\,,
   \]

### 2018-11-17 effects/effects.tex
Finished paper for submission.

@@
 \renewcommand{\case}{{\mathtt{case}}}
-\newcommand{\blank}{\;\underline{\hspace{1.5ex}}\;}
+\newcommand{\blank}{\,\underline{\hspace{1.5ex}}\,}
 \newcommand{\converges}{\Downarrow}
@@
 %
-\author{}
+\author{W. John Gowers}
 %
-\authorrunning{} % abbreviated author list (for running head)
+\authorrunning{W. J. Gowers} % abbreviated author list (for running head)
 %
@@
 BA2 7AY,\\
-\email{wjg27@bath.ac.uk},\\ WWW home page:
-\texttt{http://people.bath.ac.uk/wjg27}}
+\email{wjg27@bath.ac.uk}}
 
@@
   As with the Kleisli category, the objects of this category will be the objects of the original category, while the morphisms are obtained from morphisms in the original category in a formal manner brought about by the action.
-  In the case that the action is actually a monad, we get the usual Kleisli category.
+  If the action is actually a monad, we get the usual Kleisli category.
 
@@
 
-\subsection{Monads and Kleisli categories}
-
 This paper is about general frameworks for modelling effects in a categorical semantics.  
 The seminal paper in this field is Moggi's \emph{Computational Lambda-Calculus and Monads} \cite{Moggi}, which first put forward the idea that if $\C$ is a categorical model of a programming language, then we can simulate an effect in that language via a suitable \emph{monad} on $\C$.
-Given such a monad, its Kleisli category $Kl_M\C$ is then a model of a language formed by adding the effect to the original language.
+Given a monad, its Kleisli category $\Kl_M\C$ is then a model of a language formed by adding the effect to the original one.
 
-Spivey \cite{Spivey} and Wadler \cite{Wadler1,Wadler2} have transferred this theory to the real world by using monads as programming tools, particularly in the Haskell programming language.
+Spivey \cite{Spivey} and Wadler \cite{Wadler1,Wadler2} have transferred this theory to the real world by using monads as programming tools, particularly in Haskell.
 
-Monads are certainly not the only formal method of adding effects into categories.  
-For example, \cite{Lawvere} argues that Lawvere theories, a tool used originally in universal algebra (as monads were), also give us a natural way to model effects in categories.  
-Since \cite{FinitaryMonadOnSet} every Lawvere theory may be regarded as a particular monad on the category of sets, this is not surprising.  
-However, Lawvere theories are a lot more flexible than monads when it comes to composing multiple effects together.
-
+There are other systematic treatments of effects -- for example, Lawvere theories \cite{Lawvere}.  
 More recent work in game semantics, however, has produced models of effects -- such as the well-known game semantics for scoped state \cite{SamsonGuyIAPassive} and nondeterminism \cite{mcCHFiniteND} -- do not arise by applying any systematic procedure to a base category of games that lacks the effect.
@@
 The goal of this paper is to examine some possible frameworks that will allow us to study these and other models in a systematic way.
-
-A closely related problem is that of using a common technique to model a particular effect in different settings.  
-Many of our favourite monads (e.g., the powerset monad on $\Set$ for nondeterminism) live in some particular category and cannot readily be set up in other categories.
 
@@
 Now, we can alternatively represent this strategy as being a normal strategy inside the Kleisli category for the reader monad given by the \emph{command} or \emph{singleton} type, as on the right of Figure \ref{slot-games}.
-The translation works by replacing each token $\circled{\$}$ with a request to the argument to the function: since this arguement has singleton type, there is only one possible value that can be passed in, but the game semantics will record that we have made the request.
+The translation works by replacing each token $\circled{\$}$ with a request to the argument to the function: since this argument has singleton type, there is only one possible value that can be passed in, but the game semantics will record that we have made the request.
 What is more, this translation respects composition in the two categories, both the Kleisli composition and the composition defined synthetically for slot games.
@@
 
-Since the reader monad is entirely built out of the Cartesian closed structure of the category, we can perform a similar trick in many different settings, although perhaps not as successfully as in game semantics.
+\section{Promonads and Parametric monads}
 
@@
 One clue comes from generalizing from functors to profunctors.  
-Since a monad is a monoid in the category $\End[\C]$ of endofunctors on $\C$ with monoidal product given by functor composition, we can define a \emph{promonad} to be a monoid in the category $\Prof[\C,\C]$ of endoprofunctors on $\C$ (i.e., functors $\C^{op}\times\C\to \Set$), where the monoidal product is profunctor composition.
-Since a functor $\F\from \C\to \D$ may be identified with the profunctor $\D[F(\blank),\blank]\from\C^{op}\times\D\to\Set$, this certainly generalizes the idea of a monad.
+A monad is a monoid in the category $\End[\C]$ of endofunctors on $\C$, with monoidal product given by composition.
+So we can define a \emph{promonad} to be a monoid in the category $\Prof[\C,\C]$ of endoprofunctors on $\C$ (i.e., functors $\C^{op}\times\C\to \Set$), where the monoidal product is profunctor composition.
+A functor $\F\from \C\to \D$ may be identified with the profunctor $\D[F(\blank),\blank]\from\C^{op}\times\D\to\Set$, so promonads generalize monads.
 
@@
 
-On the other hand, what promonads capture is quite a natural simple way of modelling effects: keep the same types (objects), but give us new ways to write programs (morphisms).  
-Although effectful types are important (e.g., in work on call-by-push-value \cite{Cbpv}), we shall adopt this paradigm in our paper.  
+On the other hand, what promonads capture is quite a natural simple way of modelling effects: keep the same types (objects), but give new ways to write programs (morphisms).  
+Although effectful types are important (e.g., in work on call-by-push-value \cite{Cbpv}), we shall adopt this paradigm here.
 So one way to state our goal is that we are looking for systematic ways to construct promonads on a category that are more general than the existing Kleisli construction for monads.
@@
   \]
-with the composition of $f\from A\to X.B$ and $g\from B\to Y.C$ being given by the composite
+with the composition of $f\from A\to X.B$ and $g\from B\to Y.C$ given by the composite
 \[
@@
 For example, let $\Surj^+$ be the category of non-empty sets and surjections.  
-Then, if $A$ is a set, we have
+Then, if $A$ is a set, we have (naturally in $A$):
 \begin{IEEEeqnarray*}{CCC}
   \colim_{X\object\Surj^{+\,op}} [X,A] & \cong & \powerset(A) \\[6pt]
-  \left(X \xrightarrow{f} A\right) & \mapsto & \text{Im}(f)\,,
+  \left(X \xrightarrow{f} A\right) & \mapsto & \text{Im}(f)\,.
 \end{IEEEeqnarray*}
-naturally in $A$.
 
@@
 Moreover, the functor $[X,A]$ is actually a lax action of $\Surj^{+,op}$ (with the Cartesian product) upon the category of sets, and the monad structure of the powerset may be deduced from the structure of this action via the colimit.
-So even though we cannot define the powerset \emph{monad} inside arbitrary Cartesian closed categories, we can still define this action of $\Surj^{op}$.
+So even though we cannot define the powerset \emph{monad} inside arbitrary CCCs, we can still define this action of $\Surj^{op}$.
 
@@
 One unfortunate fact is that these two alternatives (powerset monad vs lax action of $\Surj^{+,op}$) do not give rise to the same promonad in the category of sets.  
-Indeed, if we have a general action of a monoidal category $\M$ on $\Set$, then (as long as the possibly large colimits exist) we get a monad on $\Set$ given by
+Indeed, if we have a general action of a monoidal category $\M$ on $\Set$, then (as long as the possibly large colimits exist) we get a monad $M$ on $\Set$ given by
 \[
@@
   \]
-Meanwhile, the morphisms between $A$ and $B$ in the category $\C/\M$ are given by the set
+Meanwhile, the morphisms between $A$ and $B$ in the category $\C/\M$ are given by
 \[
@@
 \[
-  \colim_{X\object\M}[A,X.B] \to [A, \colim_{X\object\M} X.B]\,,
+  \colim_{X\object\M}[A,X.B] \to [A, \colim_{X\object\M} X.B]\,.
   \]
-and if the category $\M$ admits a cocone over every discrete diagram (i.e., if whenever $(X_i)$ is a collection of objects of $\M$ there is some $Y$ such that there is a morphism $f_i\from X_i\to Y$ for all $i$), then this function is surjective, meaning that the functor will be full.
+If the category $\M$ admits a cocone over every discrete diagram (i.e., if whenever $(X_i)$ is a collection of objects of $\M$ there is some $Y$ such that there is a morphism $f_i\from X_i\to Y$ for all $i$), then this function is surjective, meaning that the functor will be full.
 The category $\Surj^{+,op}$ has this property (via the Cartesian product and its projections, which are always surjective for non-empty sets).  
-In the case of the action of $\Surj^{+,op}$ that gives rise to the powerset monad, the natural map given above is the surjection $\powerset[A,B]\to [A,\powerset B]$ that takes a set $\F$ of functions $A\to B$ and forms the function $A\to\powerset B$ that sends an element $a$ to the set
-\[
-  \{f(a)\suchthat f\in\F\}\,.
-  \]
-This means that we may recover the Kleisli category from the category given by the action by taking the quotient by a further equivalence relation on morphisms.
+In the case of the action of $\Surj^{+,op}$ that gives rise to the powerset monad, the natural map given above is the surjection $\powerset[A,B]\to [A,\powerset B]$ that takes a set $\F$ of functions $A\to B$ and forms the function $A\to\powerset B$ that sends an element $a$ to the set $\{f(a)\suchthat f\in\F\}$.
+So we may recover the Kleisli category from the category given by the action by applying a further equivalence relation on morphisms.
 
-In general, if a monad $M$ on $\Set$ can be expressed as the colimit of a lax action of a monoidal category $\M$ on $\Set$, where $\M$ admits a cocone over every discrete diagram, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$.
-More specifically, there is a full functor $\Kl_M\Set\to \Set/\M$ that is the identity on objects, so we may recover the Kleisli category by applying a suitable equivalence relation to the set of morphisms.
-The benefit of reasoning about the action of $\M$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories.  
-For instance, the action of $\Surj^{+\,op}$ on $\Set$ may be replicated inside any monoidal closed category that admits a functor out of the category of sets (for example, most models of PCF or Idealized Algol).
+In general, if a monad $M$ on $\Set$ can be expressed as the colimit of a lax action of a monoidal category $\M$ on $\Set$, where $\M$ admits a cocone over every discrete diagram, then we do not lose very much by considering the category $\Set/\M$ obtained from the action rather than the Kleisli category $\Kl_M\Set$, since there is a full functor $\Kl_M\Set\to \Set/\M$ that is the identity on objects, letting us recover the Kleisli category by applying a suitable equivalence relation on morphisms.
+The benefit of reasoning about the action of $\M$ rather than the monad $M$ is that the action might be realizable in a much larger class of categories, as with our action of $\Surj^{+\,op}$.
 We will see later that the non-empty powerset monad has a probabilistic counterpart, where the set of discrete probability distributions on a set may be obtained as a colimit over the category of probability spaces and probability-preserving maps, which satisfies similar properties, allowing us to model discrete probability in categories other than $\Set$.
-
-\subsection{Plan for the paper}
-
-The rest of this paper will consist in two sections.  
-In the first, we will give a more detailed account of the construction that allows us to build a promonad (i.e., a category) out of a parametric monad.
-
-In the second section, we will give a fully abstract game semantics for the language Probabilistic Algol (PA).  
-This is by no means a new result -- the paper \cite{DanosHarmer} that introduced PA also gave it a fully abstract game semantics.  
-Instead, the point of this section will be to demonstrate how the ideas we have outlined can be applied systematically to yield fully abstract models of programming languages.
-
 \section{A Kleisli-style construction for parametric monads}
@@
         \]
-      Dually, any lax action gives rise to a monad on the category being acted upon, by setting $MA = A.I$.
     \item If $\C$ is also a monoidal category and $J\from \M\to \C$ is a lax monoidal functor with monoidal coherence $\mu$, then there is an action of $\M^{co}$ (i.e., $\M$ with the opposite monoidal product) on $\C$ given by
@@
         \]
-      and
+      where $\passoc_{X,Y,A}$ is given by the composite
       \[
-        \passoc_{X,Y,A}=
         (A \tensor JY) \tensor JX \xrightarrow{\assoc_{A,JX,JY}}
@@
         \]
+      and the unit $\lun_A$ similarly.  
       We sometimes refer to a left action of the opposite category $\M^{co}$ on $\C$ as a \emph{right action} of $\M$ on $\C$.  
@@
         \]
-      and
+      where $\passoc_{A,X,Y}$ is given by the composite
       \[
@@
       The intersection of the first and third examples is the \emph{reader monad} given by $M^RX = R \implies X$ for any comonoid $R$ in $\C$ (and, in particular, for any object $R$ if $\C$ if the monoidal product in $\C$ is Cartesian).
-
-      We shall therefore call an action of the form $A \tensor JX$ a \emph{writer-style action} and one of the form $jX \implies A$ a \emph{reader-style action}.
+      We therefore call an action of the form $A \tensor JX$ a \emph{writer-style action} and one of the form $jX \implies A$ a \emph{reader-style action}.
     \item We can define an \emph{oplax action} of $\M$ on $\C$ to be a lax action of $\M$ upon the opposite category $\C^{op}$.  
@@
   \]
-Note that this does not automatically define an equivalence relation in general, so there may be pairs $(X,f)$ and $(Y,g)$ that are not related by some $h\from X\to Y$ but are nevertheless equivalent because there is some chain of such relations from one to the other.
+Note that this does not automatically define an equivalence relation in general, so there may be pairs $(X,f)$ and $(Y,g)$ that are not related by some $h\from X\to Y$ but are nevertheless equivalent because there is some zigzag of such relations from one to the other.
 
@@
 Let $A,B,C$ be objects of $\C$, and let $f\from A\to X.B,g\from B\to Y.C$ be morphisms $A\to B$ and $B\to C$ in $\C/\M$.  
-We define the composition of $f$ with $g$ to be given by the following composite in $\C$.
+The composition of $f$ with $g$ is given in $\C$ by:
 \[
@@
 
-Let us see what that looks like when our action is the action of $\Surj^{+\,op}$ on $\Set$ that we considered earlier.  
-In that case, a morphism $A\to B$ is given by a function $A \to [X,B]$, or equivalently $X \to [A,B]$.
-We may identify this function with its image, which is a subset of $[A,B]$, and this identification corresponds precisely to the equivalence relation that is automatically given by our construction; namely, the smallest equivalence relation such that $X \to [A,B]$ is equivalent to the composite $Y \to X \to [A,B]$ for any surjection $Y \to X$.
-Indeed, if $f\from X \to [A,B]$ and $g \from Y \to [A,B]$ have the same image $\F\subset[A,B]$, then $f$ and $g$ are both equivalent to the inclusion $\F\hookrightarrow [A,B]$, so they are equivalent.
-
 \subsection{Universal property of $\C/\M$}
@@
 
-  ii) Let $\D$ be a category and let $H,K\from \C/\M\to \D$ be two functors.  
-  Let $\alpha\from HJ \to KJ$ be a natural transformation making the following diagram commute.
+  ii) Let $H,K\from \C/\M\to \D$ be two functors.  
+  Let $\alpha\from HJ \to KJ$ be a natural transformation making the following square commute.
   \[
@@
   where we have considered $f$ both as a morphism $A\to B$ in $\C/\M$ and as a morphism $A \to X.B$ in $\C$.  
-  It therefore suffices to define $H$ on morphisms of the form $Jf$ (which must be sent to $Ff$, since $F=HJ$) and on morphisms of the form $\phi_{X,A}$ (which must be sent to $\psi_{X,A}$, since $\psi=H\phi$).
-  Therefore $H$ is uniquely defined, if it exists, so it suffices to check that the $H$ given by sending the above factorization to the composite
+  It therefore suffices to define $H$ on morphisms of the form $Jf$ and on morphisms of the form $\phi_{X,A}$.  
+  The conditions in the statement mean that $H$ must be defined by sending the above factorization to the composite
   \[
@@
     F(X.B) \xrightarrow{\psi_{X,A}}
-    FB
+    FB\,,
     \]
-  is indeed a functor satisfying the requirements of the proposition.  
-  Part (ii) is proved in a very similar way.
+  so it suffices to check that this is indeed a functor.
+  Part (ii) is proved from the factorization in a very similar way.\qed
 \end{proof}
@@
 
-  The quotient notation we have used is because the universal property we have outlined exhibits $\C/\M$ as a particular weighted coequalizer of the functors $\pr_2,\blank.\blank\from \M\times\C \rightrightarrows \C$ in $\Cat$.
-  It may therefore be regarded as a lax $2$-dimensional analogue of the quotient $X/G$ of a set $X$ by a group or monoid action.
+  The `$/$' notation we have used is because the universal property we have outlined exhibits $\C/\M$ as a particular weighted coequalizer of the functors $\pr_2,\blank.\blank\from \M\times\C \rightrightarrows \C$ in $\Cat$.
+  It may therefore be regarded as a lax $2$-dimensional analogue of the quotient $X/G$ of a set $X$ by a monoid action.
 
-  When the action is a monad, this is a strange idea, since we are not used to thinking of, for example, a Kleisli category as quotient of the original category.  
+  When the action is a monad, this is a strange idea, since we are not used to thinking of a Kleisli category as quotient of the original category.  
   The reason for this is the laxness: we do not identify the objects $A$ and $X.A$ with an isomorphism, but with a morphism in one direction.  
@@
   For example, the type $W\to [A,W]$ encodes a state transformer with state $W$.  
-  Working in the Kleisli category for the state monad allows us to associate this stateful behaviour to the object $A$.
+  In the Kleisli category for the state monad, we can associate this stateful behaviour to the object $A$.
 \end{remark}
@@
 Composing with the isomorphism from the start of this section, we get a functor $(\C/\M)\times(\C/\M)\to\C/\M$.  
-It turns out that this gives $\C/\M$ the structure of a monoidal category and that in this case the functor $J\from \C\to\C/\M$ is a strict monoidal functor.
+It turns out that this gives $\C/\M$ the structure of a monoidal category such that the functor $J\from \C\to\C/\M$ is a strict monoidal functor.
 
@@
 
+We will now apply the ideas from the previous section to give a fully abstract game semantics for Probabilistic Algol (PA), where the model will be derived using a parametric monad.
+
 \subsection{The discrete probability monad}
@@
 \begin{description}
-  \item[Empty set] $\bP(\emptyset) = 0$.
-  \item[Countable additivity] If $\{E_i\}_{i=0}^\infty$ is a sequence of pairwise-disjoint subsets of $X$, then
+  \item[Empty set and whole space] $\bP(\emptyset) = 0$ and $\bP(X)=1$.
+  \item[Countable additivity] If $\{E_i\}_{i=0}^\infty$ are pairwise-disjoint subsets of $X$, then
     \[
@@
       \]
-  \item[Whole space] $\bP(X)=1$.
 \end{description}
@@
 If instead we have $\bP(X)\le 1$, we say that $\bP$ is a \emph{sub-probability measure}
-
-Note that if $A$ is countable, then $\mu$ may be entirelly specified by its action on singletons: if $A\subseteq X$ is a set, then we have
-\[
-  \bP(A) = \sum_{a\in A}\bP(\{a\})\,.
-  \]
 
@@
 \end{mathpar}
-given by
 \begin{mathpar}
@@
   \end{cases} \and
-  \bP_X(\tau)(A) = \sum_{\bP\in P(X)} \tau(\{\bP\})\bP(A)
+  m_X(\tau)(A) = \sum_{\bP\in P(X)} \tau(\{\bP\})\bP(A)
 \end{mathpar}
-$\delta_X$ and $m_X$ give $P$ the structure of a monad on $\Set$, which we will call the \emph{discrete probability monad}.  
+$\delta_X$ and $m_X$ give $P$ the structure of a monad on $\Set$, which we call the \emph{discrete probability monad}.  
 This is a discrete form of the monad developed in \cite{Giry}.
@@
 We will normally refer to this pair using the set $X$.
-Given discrete probability spaces $X$ and $Y$, we define a \emph{measure-preserving map} from $X$ to $Y$ to be a function $f\from X \to Y$ such that for all $A\subseteq Y$ we have $\bP(X)(f\inv(A)) = \bP_Y(A)$.
+Given discrete probability spaces $X$ and $Y$, a \emph{measure-preserving map} from $X$ to $Y$ is a function $f\from X \to Y$ such that for all $A\subseteq Y$ we have $\bP(X)(f\inv(A)) = \bP_Y(A)$.
 It is clear that discrete probability spaces and measure-preserving maps form a category $\DProb$.
 
-Moreover, $\DProb$ is a monoidal category: given discrete probability spaces $X$ and $Y$, we may define a probability measure on the Cartesian product $X\times Y$ by
+Moreover, $\DProb$ is a monoidal category: given discrete probability spaces $X$ and $Y$, we define a probability measure on the Cartesian product $X\times Y$ by
 \[
@@
   \]
-such that the monad structure on $P$ is induced from the reader-style action of $\DProb^{op}$ on $\Set$ given by the monoidal functor $\DProb\to\Set$ that sends $(Y,\bP_Y)$ to its underlying set $Y$.
+such that the monad structure on $P$ is induced from this reader-style action of $\DProb$ on $\Set$.
 
-Moreover, the category $\DProb^{op}$ is weakly filtered, and so, as in our earlier discussion, we feel confident using this action, rather than the monad $P$ we have defined, to model discrete probability.
-
-This action is very closely related to the action of $\Surj^{+,op}$ that we defined earlier; indeed, $\Surj^+$ is equivalent to the category of discrete probability spaces taking probabilities in the Boolean semiring $\{0,1\}$ with countable summation given by maximum.
+This action is closely related to the action of $\Surj^{+,op}$ that we defined earlier: $\Surj^+$ is equivalent to the category of discrete probability spaces taking probabilities in the semiring $\{0,1\}$ with countable summation given by maximum.
 
 By cutting down the category $\DProb$ we can obtain slightly different notions of probability.  
-For our purposes, we will be using the full subcategory $\BProb$ where the objects $(X,\bP_X)$ are those that satisfy the following three additional conditions.
+We will be using the full subcategory $\BProb$ where the objects $(X,\bP_X)$ are those that satisfy the following two additional conditions.
 \begin{description}
@@
 
-The action of $\BProb^{op}$ gives rise to a monad on the category of countable sets.
-
 \subsection{Probabilistic Algol}
 
-\cite{DanosHarmer} gives a fully abstract game semantics for the language Probabilistic Algol (PA).  
-The base language for PA is the language Idealized Algol (IA) from \cite{SamsonGuyIAPassive}, and it has been extended with a constants $\coin\from\bool$.  
+PA was introduced in \cite{DanosHarmer}, where it was also given a fully abstract game semantics.
+The base language is the language Idealized Algol (IA) from \cite{SamsonGuyIAPassive}, and it has been extended with a constants $\coin\from\bool$.  
 To make things a little more interesting, we will extend this further to incorporate an infinite family of constants $\coin_p\from\bool$, where $p$ ranges over the real interval $[0,1]$.
@@
 We give the language a small-step operational semantics.  
-The rules for the deterministic terms may be derived from the operational semantics given in \cite{SamsonGuyIAPassive}; for example:
+The rules for the deterministic terms may be derived from the operational semantics given in \cite{SamsonGuyIAPassive} (see also \cite{JimGuySmallStep}); for example:
 \[
-  \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}
+  \inferrule*{ }{\ia s {v \coloneqq n} \opto \ia {\stup s v n} \skipp}\,.
   \]
-See also \cite{JimGuySmallStep}.
 
@@
   \]
-This is only a subprobability measure, because some evaluations may continue forever.
+This is only a subprobability measure, because some evaluations may diverge.
 
@@
 
-Let $\G$ be a category that admits a fully abstract adequate semantics for Idealized Algol.  
-See \cite{SamsonGuyIAPassive} for a list of the conditions that such a category should satisfy, and also for the best known example, the category of games and visible strategies.
+Let $\G$ be a category that admits an adequate semantics for Idealized Algol that satisfies finite definability.
+The reader may assume that we are dealing with the category of games and visible strategies given in \cite{SamsonGuyIAPassive}.
 
-As explained in \cite{SamsonGuyIAPassive}, $\G$ should be Cartesian closed and there should be a lax monoidal functor $\Set\to \G$ that gives the denotation of the ground types $\nat$,$\bool$ and $\com$, together with their structural functions.
-We can therefore get a lax monoidal functor $\BProb \to \G$ by composing this with the forgetful functor $\BProb\to\Set$.
+We assume that $\G$ is symmetric monoidal closed and there is a lax monoidal functor $\Set\to \G$, giving the denotation of the ground types $\nat$,$\bool$ and $\com$ and their structural functions.
+So we get a lax monoidal functor $\BProb \to \G$ by composing this with the forgetful functor $\BProb\to\Set$.
 
 This gives rise to a reader-style action of $\BProb^{op}/\G$, and the resulting category $\G/\BProb^{op}$ is therefore a symmetric monoidal closed category.
-
-\subsection{Testing morphisms and plays}
 
@@
 
-To improve the equivalence relation, we introduce the concept of \emph{testing morphism} for an object $A$ that is the denotation of an Idealized Algol term.
+To improve the equivalence relation, we use the concept of \emph{testing morphism} for an object $A$ that is the denotation of an Idealized Algol term, which the author introduced in \cite{CslPaper}.
 This is a term of type $(\bN \to A) \to A$ that is the denotation of an Idealized Algol term of the form
@@
 Now, if the set $\bN$ carries a probability distribution, then this gives rise to a sub-probability distribution on the set of plays for $\sigma$, where the probability associated to the sequence $n_1,\cdots,n_k$ is the product of the probabilities of the $n_i$.
-This then induces a discrete probability distribution on the set of morphisms $1\to A$.
+This induces a discrete probability distribution on the set of morphisms $1\to A$.
 
-We say that two morphisms $\sigma,\tau\from \bN\to A$ from $1$ to $A$ in $\G/\BProb$ are equivalent if they give rise to the same probability distribution on the set of strategies for $A$.  
+We say that two morphisms $\sigma,\tau\from \bN\to A$ from $1$ to $A$ in $\G/\BProb$ are \emph{probabilistically equivalent} if they give rise to the same probability distribution on the set of strategies for $A$.
 This equivalence relation refines our earlier one.
 
-\subsection{Single-threaded morphisms}
+Our category is symmetric monoidal closed, but not yet Cartesian closed.  
+Since every object of our category has a natural comonoid structure given by the `diagonal' $A\to A\times A$, we may make our category Cartesian closed by cutting the morphisms down to the ones that are comonoid homomorphisms.
+Note that we need to apply this equivalence relation in order to make sure that the natural morphisms $\phi_{X,A}$ are comonoid homomorphisms.
 
-Our category is symmetric monoidal closed, but not yet Cartesian closed.  
-A trick that is often used in Game Semantics (see, for example, \cite{mcCHFiniteND} and \cite{DanosHarmer}) is to pass to a category of \emph{single-threaded} strategies; this is equivalent to cutting down to those morphisms that are comonoid homomorphisms.
-
-Note that, in our category, every object has a natural commutative comonoid structure that arises from diagonal $\Delta\from A\to A\times A$ in the original category.  
-We say that a morphism $\sigma\from A\to B$ is \emph{single-threaded} if it is a homomorphism of the comonoid structures on $A$ and $B$; i.e., if the following square commutes.
-\[
-  \begin{tikzcd}
-    A \arrow[r, "\sigma"] \arrow[d, "\Delta"']
-      & B \arrow[d, "\Delta"] \\
-    A \times A \arrow[r, "\sigma\times\sigma"]
-      & B \times B
-  \end{tikzcd}
-  \]
-Since the category of commutative comonoids in a symmetric monoidal category is automatically Cartesian closed (see, for example, \cite{Freyd}), this gives us a Cartesian closed category.
-
-The deterministic terms are all comonoid homomorphisms.  
-As long as we have applied the equivalence relation outlined above, the natural morphisms $\phi_{X,A}$ are also comonoid homomorphisms.
-
-\subsection{Denotational semantics and adequacy}
+\subsection{Denotational semantics and Full Abstraction}
 
@@
 \[
-  ((\{H,T\}, \mu(H)=p, \mu(T)=1-p), 1 \to (\{H,T\} \to \bB))\,
+  ((\{H,T\}, \mu(H)=p, \mu(T)=1-p), 1 \to (\{H,T\} \to \bB))\,,
   \]
@@
 
-Note now that the denotation of a term $M = C[\coin_{p_1},\cdots,\coin_{p_j}]T$ is given by the following morphism.
+Note now that the denotation of a term $M = C[\coin_{p_1},\cdots,\coin_{p_j}]\from T$ is given by the following morphism.
 \[
@@
   \]
-where the distribution on the product $\bB^j$ is the product of Bernoulli distributions.
+where the distribution on $\bB^j$ is the product of Bernoulli distributions.
 
-Fix an injection $r\from\bB^j\to \bN$ (for instance, the one given by ibinary representation) and suitable projection functions $\pr_i \from \bN \to \bB$ such that $\pr_i(r(v))$ is the $i$-th entry of $v$.
-Let $\multicoin\from\nat$ be the term (depending on the values of the $p_i$) given by
+Fix an injection $r\from\bB^j\to \bN$ (for instance, the one given by binary representation) and projection functions $\pr_i \from \bN \to \bB$ such that $\pr_i(r(v))$ is the $i$-th entry of $v$.
+Let $\multicoin\from\nat$ be the term (depending on the $p_i$) given by
 \[
@@
   \]
-Now the operational semantics of $\pr_i(\multicoin)$ is the same as the operational semantics of $\coin_{p_i}$, since the projections from the product are probability-preserving.  
+Now the operational semantics of $\pr_i(\multicoin)$ is the same as that of $\coin_{p_i}$, since the projections from the product are probability-preserving.  
 This means that any evaluation $\pi$ of the term $M$ may be pegged to an evaluation of the term formed by replacing each instance of $\coin_{p_i}$ in $M$ with $\pr_i(\multicoin)$.
@@
   Let $M = C[\multicoin]\from \com$ be a term of Idealized Algol, where $C$ is a multi-holed deterministic IA context.
-  Let $p$ be the sum of the probabilities of all evaluation sequences of $M$ that terminate at $\skipp$.
+  Let $p$ be the sum of the probabilities of all terminating evaluation sequences of $M$.
 
@@
   Therefore, there is bijective matching between terminating evaluation sequences of $M$ and plays of the morphism $\deno{M}$, with each one getting the same probability.  
-  The result follows.
+  The result follows.\qed
 \end{proof}
 
-\subsection{Full Abstraction}
-
-In order to prove full abstraction for our model, we will define a further equivalence on morphisms.  
+To prove full abstraction for our model, we define a further equivalence on morphisms.  
 Say that two morphisms $f,g\from A \to B$ are \emph{intrinsically equivalent} if and only if for all morphisms $\alpha\from (A\to B)\to\bC$, $\alpha(f)$ and $\alpha(g)$ are probabilistically equivalent in the sense given above.
-Then our full abstraction result becomes:
+Then our full abstraction result is:
 
@@
   Let $M,N\from T$ be two PA terms.  
-  Then $M$ and $N$ are observationally equivalent if and only if their denotations $\deno{M}$ and $\deno{N}$ are intrinisically equivalent.
+  Then $M$ and $N$ are observationally equivalent if and only if their denotations $\deno{M}$ and $\deno{N}$ are intrinsically equivalent.
 \end{proposition}
@@
 \begin{proof}
-  Treat $\sigma$ as a morphism $A \to X \to B$ in $\G$.  
+  Treat $\sigma$ as a morphism $A \to (X \to B)$ in $\G$.  
   Since $X$ is finitely supported, there is a probability-preserving function $\bN \to X$, for some finitely supported distribution on $\bN$.  
-  So $\sigma$ is equivalent to a morphism $A \to \bN \to B$, and then the factorization is automatic.
+  So $\sigma$ is equivalent to a morphism $A \to (\bN \to B)$, and then the factorization is automatic.\qed
 \end{proof}
+The most striking thing about the computational adequacy and deterministic factorization results is that they are proved entirely inside the original category $\G$.  
+This demonstrates what we have been trying to achieve: to model effects using a systematic method that allows us to prove results formulaically.  
+The factorization result, in particular, follows immediately from the way we have set the model up, whereas the corresponding result in traditional game semantics is often intricate and combinatorial.
 

### 2019-01-10 Thesis/thesis.tex
Started writing thesis.

\documentclass{article}

\let\FEWFONTS=1
\let\THESIS=1
\input{../common/preamble}

\begin{document}

\section{Monads and Kleisli categories}

\subsection{Monads}

Let $\C$ be a category.  
Then the category $[\C,\C]$ of functors $\C\to\C$ and natural transformations has a (strict) monoidal structure given by composition.  
A \emph{monad} \cite[\sec VI]{WorkingMathematician} in $\C$ is a monoid in $[\C,\C]$.

In other words, it is a functor $M\from \C\to\C$ together with natural  transformations $m_a \from MMa \to Ma$ and $u_a \from a \to Ma$ such that the following diagrams commute for all objects $a$ of $\C$.

\begin{mathpar}
  \begin{tikzcd}
    MMM a \arrow[r, "Mm_a"] \arrow[d, "m_{Ma}"]
      & MM a \arrow[d, "m_a"] \\
    MM a \arrow[r, "m_a"]
      & M a
  \end{tikzcd}
  \and
  \begin{tikzcd}
    M a \arrow[r, "M u_a"] \arrow[dr, "id"']
      & M M a \arrow[d, "m_a"] \\
    %
      & M a
  \end{tikzcd}
  \and
  \begin{tikzcd}
    M a \arrow[r, "u_{M a}"] \arrow[dr, "id"']
      & M M a \arrow[d, "m_a"] \\
    %
      & M a
  \end{tikzcd}
\end{mathpar}

\begin{example}
  In the category of sets, the \emph{nonempty powerset functor} $\powerset_+$ sends a set $A$ to the set of nonempty subsets of $A$.  
  This has the structure of a monad on $\Set$, since we have a natural transformation (union) from $\powerset_+\powerset_+A \to \powerset_+A$ and a natural transformation (singleton) from $A \to \powerset_+A$ that obey the diagrams given above.
\end{example}
\begin{example}
  Let $\M$ be a monoidal category and let $x$ be a monoid in $\M$.  
  The \emph{writer monoid} $W_x$ on $\M$ is defined by $W_x y = y \tensor x$, with natural transformations
  \begin{mathpar}
    m_y \from y \tensor x \tensor x \to y \tensor x
    \and
    u_y \from y \to y \tensor x
  \end{mathpar}
  given by the monoid structure on $x$.

  Going the other way, if $\M$ is monoidal closed with inner hom $\implies$, and if $z$ is a comonoid in $\M$, then the \emph{reader monoid} $R_z$ is given by $R_z y = z \implies y$.  
  Then the monadic coherences
  \begin{mathpar}
    m_y \from z \implies z \implies y \to z \implies y
    \and
    u_y \from y \to z \implies y
  \end{mathpar}
  are induced from the comonoid structure on $z$.
  This second example is particularly important in Cartesian closed categories, in which every object has the structure of a comonoid.
\end{example}
\begin{example}
  If $\adjunction{\C}{L}{R}{\D}$ is an adjunction with counit $\epsilon\from LR\to 1$ and unit $\eta\from 1 \to RL$, then the composite $RL\from \C \to \C$ has the structure of a monoid on $\C$, where the multiplication and unit are given by
  \begin{mathpar}
    R\epsilon L \from RLRL \to RL
    \and
    \eta \from 1 \to RL\,.
  \end{mathpar}
  We will see in the next section that every monad is induced by an adjunction in this way.

  As an example, if $\M$ is a monoidal closed category and $w$ is an object of $\M$, then the \emph{state monad} $S_w$ on $\M$ is defined by
  \[
    S_w x = w \implies (x \tensor w)\,.
    \]
\end{example}
\begin{example}
  Another example that arises from an adjunction is the \emph{list monad} on $\Set$ that arises from the adjunction between the category of sets and the category of (set-valued) monoids.  
  The underlying set of the free monoid on a set $A$ is the set $A^*$ of finite lists of elements of $A$, and the functor $A\mapsto A^*$ inherits a monoid structure where the multiplication $m_A\from (A^*)^* \to A^*$ concatenates a list of lists into a single list and the unit $u_a \from A \to A^*$ forms a list with a single element.  
\end{example}
\begin{example}
  A monad on $\oppcat\C$ is called a \emph{comonad} on $\C$.  
  The carrier of a comonad is still a functor $M\from \C\to\C$, but now the multiplication and unit are natural transformations $M\Rightarrow MM$ and $M\Rightarrow 1$, rather than the other way round.

  An adjunction $\adjunction\C LR\D$ gives rise to a comonad structure on $LR$ in much the same way as it gives rise to a monad structure on $RL$.  
  So, for example, we have the \emph{store comonad} $S_r'$ for any object $r$ of a monoidal closed category $\M$, given by
  \[
    S_r'x = (r \implies x) \tensor x\,.
    \]
\end{example}

\subsection{Kleisli Categories}

Let $\C$ be a category and let $M$ be a monad on $\C$.  
Then \cite{Kleisli} there is a category $\Kl_M$, called the \emph{Kleisli category} of $M$, whose objects are the objects of $\C$ and where a morphism from an object $a$ to an object $b$ is a morphism $a \to Mb$ in $\C$.

Identity arrows are given by the morphisms $u_c\from c \to M c$ (considered as a morphism $c\to c$ in $\Kl_M$) and the composition of arrows $f\from a \to Mb$ and $g \from b \to Mc$ is given by the following composite in $\C$.
\[
  a \xrightarrow{f}
  Mb \xrightarrow{Mg}
  MMc \xrightarrow{m_c}
  M c
  \]
There is a natural identity-on-objects functor $J\from \C \to \Kl_M$ that sends a morphism $f\from a \to b$ in $\C$ to the composite
\[
  a \xrightarrow{f}
  b \xrightarrow{u_b}
  M b\,,
  \]
considered as a morphism $a\to b$ in $\Kl_M$.

In the other direction, we have a functor $ S \from \Kl_M \to \C$ that sends an object $a$ of $\Kl_M$ to the object $Ma$ of $\C$ and sends a morphism $f\from a \to M b$ from $a$ to $b$ in $\Kl_M$ to the composite
\[
  Ma \xrightarrow{M f}
  MMb \xrightarrow{m_b}
  Mb
  \]
in $\C$.  
Note that $ S J=M$, by one of our coherence conditions on $m$ and $u$.
Meanwhile, $J S $ is the functor $\Kl_M\to\Kl_M$ that sends an object $a$ to $Ma$ and sends a morphism $f\from a \to Mb$ from $a$ to $b$ to the morphism $Mf\from Ma \to MMb$ from $Ma$ to $Mb$.
\begin{proposition}[\cite{Kleisli}]
  $ S $ is a right adjoint to $J$.
  The unit of the adjunction is $u\from \id \Rightarrow M$.  
  The counit $e_a\from J( S  a) \to a$ is given by the identity morphism $Ma \to Ma$ in $\C$, considered as a morphism $Ma \to a$ in $\Kl_M$.
  \label{prop:KleisliHasAdjunction}
\end{proposition}

Given a monad $M$ on a category $\C$ and a functor $F\from \C \to \D$, where $\D$ is another category, we say that a natural transormation $\psi_a \from FMa \to Fa$ is \emph{$M$-multiplicative} if it makes the following diagrams commute.
\begin{mathpar}
  \begin{tikzcd}
    FMMa \arrow[r, "\psi_{Ma}"] \arrow[d, "Fm_a"']
      & FMa \arrow[d, "\psi_a"] \\
    FMa \arrow[r, "\psi_a"]
      & Fa
  \end{tikzcd}
  \and
  \begin{tikzcd}
    Fa \arrow[r, "F u_a"] \arrow[dr, "\id"']
      & FMa \arrow[d, "\psi_a"] \\
    %
      & Fa
  \end{tikzcd}
\end{mathpar}

Given two triples $(\D, F,\psi), (\D', F',\psi')$, where $F\from \C \to \D, F'\from \C'\to\D'$ are functors and $\psi\from FM\Rightarrow F, \psi'\from F'M\Rightarrow F'$ are functors, we define a \emph{morphism} from $(\D', F',\psi')$ to $(\D, F, \psi)$ to be a functor $H\from \D' \to \D$ such that $F=HF'$ and $\psi=H\psi'$.  
This gives us a category.

A defining property of the Kleisli category is that it is initial among such triples $(\D,F,\psi)$:

\begin{proposition}[\cite{StreetMonads}]
  i) Given an object $a$ of $\C$, the identity morphism $Ma \to Ma$ may be considered as a morphism $\phi_a \from JMa \to Ja$ in $\Kl_M$.  
  $\phi_a$ is an $M$-multiplicative natural transformation.

  ii) Let $\D$ be a category, let $F\from \C \to \D$ be a functor and suppose that $\psi_a\from FMa \to Ma$ is an $M$-multiplicative natural transformation.
  Then there is a unique functor $\hat{F}\from \Kl_M \to \D$ such that $F=\hat{F}J$ and $\psi = \hat{F}\phi$.
  \label{pKleisli}
\end{proposition}

Another way to characterize the Kleisli category $\Kl_M$ is to say that the the adjunction we described above is initial among all adjunctions giving rise to the monad $M$.  
This can be deduced from Proposition \ref{pKleisli} using the following result.

\begin{lemma}[\cite{StreetMonads}]
  Let $\C$ be a category and let $M$ be a monad on $\C$.  
  If $\adjunction{\C}{L}{R}{\D}$ is an adjunction (with counit $\epsilon$ and unit $\eta$), we say it \emph{gives rise to $M$} if $M=RL$, $m=R\epsilon L$ and $u=\eta$.

  Any such adjunction gives rise to an $M$-multiplicative natural transformation $\psi\from LM \Rightarrow L$.  
  This gives us a fully faithful functor from the category of adjunctions giving rise to $M$ to the category of triples $(\D,F,\psi)$ where $\psi$ is $M$-multiplicative.
\end{lemma}

The proof of Proposition \ref{pKleisli} essentially comes down to the following factorization result.  
If $f\from a \to b$ is a morphism in $\Kl_M$, then $f$ may be factorized as
\[
  f = a \xrightarrow{Jf}
  Mb \xrightarrow{\phi_b}
  b\,,
  \]
where we use `$f$' to refer both to the morphism $a\to b$ in $\Kl_M$ and to the underlying morphism $a \to Mb$ in $\C$.
Indeed, if we compute this composite inside $\C$, we get
\[
  a \xrightarrow{f}
  Mb \xrightarrow{u_{Mb}}
  MMb \xrightarrow{M\id}
  MMb \xrightarrow{m_b}
  Mb\,,
  \]
which is equal to $f$ by the coherence conditions on $m$ and $u$.
This means that the Kleisli category may be thought of as begin freely generated from the original category $\C$ and a multiplicative natural transformation $\phi$.

\begin{example}
  The morphisms in the Kleisli category for the nonempty powerset monad $\powerset_+$ on $\Set$ are functions $A \to \powerset_+B$, which can be thought of as nondeterministic functions.  
  Given a set $A$, the morphism $\phi_A\from \powerset_+A \to A$ in $\Kl_{\powerset_+}$ can be interpreted as a `nondeterministic choice' function that accepts a nonempty set of elements of $A$ and nondeterministically chooses one of them.
  The factorization then means that the category is freely generated over $\C$ by these nondeterministic choice morphisms.
\end{example}
\begin{example}
  Let $\C$ be a Cartesian closed category and let $z$ be some fixed object of $\C$.  
  Then the Kleisli category for the reader monad $R_z$ on $\C$ is generated over $\C$ by a natural transformation $\phi_y\from (z \to y) \to y$.  
  By the enriched Yoneda lemma, such a natural transformation is always given by precomposition with some fixed morphism $\ask\from 1 \to z$.  
  This means that $\Kl_{R_z}$ is suitable for modelling any situation in which we are generally working in $\C$, but need the ability to request a value of type $z$ (for example, a config file, a piece of user input or something else that isn't being passed into the function in question).
  \label{ExReaderMonadKleisli}
\end{example}

A particularly important fact about the reader monad in Cartesian closed categories is the following.

\begin{theorem}[\cite{FunctionalCompleteness}]
  Let $\C$ be a Cartesian closed category and let $z$ be an object of $\C$.  
  Then the Kleisli category $\Kl_{R_z}$ for the reader monad over $z$ on $\C$ is Cartesian closed.
  \label{FunctionalCompletenessCcc}
\end{theorem}

The \emph{functional completeness} theorem \cite{FunctionalCompleteness} can be thought of as a special case of our remarks above.

\subsection{Extended example: game semantics of time complexity}
This is an extended example of using a reader monad, in the style of Example \ref{ExReaderMonadKleisli}.
Let $\G$ be the category of games and visible single-threaded strategies as in \cite{SamsonGuyIAActive}.  
So $\G$ is a sound and adequate model of Idealized Algol satisfying compact definability.
Let $\bC$ be the denotation of the command type $\com$ of Idealized Algol.  
Then the Kleisli category for the reader monad over $\bC$ is freely generated over $\G$ by a single morphism $1 \to \bC$.

Let us extend Idealized Algol with a single term, $\sleep$, of type $\com$.
This should be thought of as a command to the computer to pause for some fixed interval of time -- let us say a second -- before resuming execution.
By Theorem \ref{FunctionalCompletenessCcc}, our Kleisli category is Cartesian closed.
So it gives us a denotational semantics of IA+$\sleep$, in which the terms of IA are interpreted within $\G$ as in \cite{SamsonGuyIAActive} and the new term $\sleep$ is interpreted by the new morphism $1 \to \bC$.

Let us now give an operational semantics to terms of IA+$\sleep$.  
Let $\Gamma$ be an IA-context.
Then a \emph{store} $s$ over $\Gamma$ is a list of pairs $(v\mapsto x)$, where each $v$ is the name for a $\Var$-type variable occurring in $\Gamma$ and $x$ is a value held in $v$.  
We write $()$ for the empty store, $(s\vert v\mapsto x)$ for the store obtained from $s$ by adding or updating the variable $v$ to hold the value $x$ and $(s\vert v\mapsto \bot)$ for the store obtained by removing the variable $v$ from $s$.
Given disjoint stores $s,t$ (i.e., stores whose sets of variables are disjoint), we write $s+t$ for the store obtained by concatenating together $s$ and $t$.

Given a term $\Gamma\ts M$ in context, stores $s$,$s'$ over $\Gamma$, a value $c$ and a natural number $n$, we define a big-step relation
\[
  \Gamma,s\ts M\converges_n c,s'\,,
  \]
read as `in the context $\Gamma$, $s,M$ converges to $c,s'$ in time $n$'.  
The rule for the constant $\sleep$ is given by
\[
  \inferrule*
  { }
  {\Gamma,s\ts \sleep\converges_1 \skipp,s}\,,
  \]
indicating that execution of the $\sleep$ command takes up an additional time step.  
The other rules are the same as those given in \cite{SamsonGuyIAActive} for the $\converges$ relation, except that we have to modify them in order to take account of the new information we have added to the reduction relation (i.e., the time taken to converge).
For example:
\begin{mathpar}
  \inferrule*
  { }
  {\Gamma,s\ts c \converges_0 c,s}
  \and
  \inferrule*
  {\Gamma,s\ts M\converges_m\skipp,s'\\
  \Gamma,s'\ts N\converges_n\skipp,s''}
  {\Gamma,s\ts M;N\converges_{m+n}\skipp,s''}\,.
\end{mathpar}
If $P$ is a program (i.e., a term of type $\com$) then we write $P\converges_n$ as a shorthand for $,()\ts P \converges_n \skipp,()$.
We say that $P$ \emph{diverges} and write $P\diverges$ if there is no $n$ such that $P\converges_n$.

We now want a way to capture this operational behaviour within the denotational semantics.
First, we note the Computational Adequacy result proved for the game semantics of Idealized Algol.

\begin{proposition}[{\cite[21]{SamsonGuyIAActive}}]
  Let $P$ be a term of type $\com$.  
  Then $P\converges$ if and only if $\deno{P}\ne\bot$.
  \label{SamsonGuyAdequacy}
\end{proposition}

Readers unfamiliar with game semantics should not worry too much about what $\bot$ is; the point of Proposition \ref{SamsonGuyAdequacy} is that the denotation of a command-type term precisely captures the operational behaviourof that term, in the sense that there is some distinguished strategy $\bot\from 1 \to \bC$ that is the denotation of every divergent program, and no convergent one.

Before proceeding further, we prove an important lemma.  
This lemma tells us that the operational semantics of a term of IA+$\sleep$ may be modelled within Idealized Algol; i.e., that IA+$\sleep$ is a conservative extension of the original language.

\begin{lemma}
  Let $P\from T$ be a term of IA+$\sleep$.
  Suppose that
  \[
    \Gamma,s\ts P\converges_n c,s'
    \]
  in IA+$\sleep$.

  Then for all $k\ge 0$, all contexts $\Delta$ disjoint from $\Gamma$, all stores $t$ over $\Gamma,\Delta$ disjoint from $s$ and all variables $v$ not in $\Gamma,\Delta$:
  \[
    \Delta,\Gamma,v,(t{+}s\vert v \mapsto k)\ts P[v \gets \suc !v/\sleep] \converges c,(t{+}s\vert v \mapsto k+n)
    \]
  in Idealized Algol.
  \label{IaSleepsSoundnessLemma}
\end{lemma}
\begin{proof}
  Induction on the derivation that $\Gamma,s\ts P\converges_n c,s'$.
  There are several possibilities for the last step in the derivation.
  \begin{description}
    \item[Structural congruence]
      Suppose that the last step in the derivation is
      \[
        \inferrule*{P\equiv P'\\
        \Gamma,s\ts P' \converges_n \skipp, s'}
        {\Gamma,s\ts P\converges_n \skipp, s'}\,.
        \]
      It is clear then by the definition of structural congruence that $P'[v\gets\suc !v/\sleep]\equiv P[v\gets\suc !v/\sleep]$.  
      So the claim follows by the inductive hypothesis applied to $P'$ and the structural congruence rule for Idealized Algol.
    \item[$\sleep$]
      Suppose that the last step in the derivation is
      \[
        \inferrule*{ }
        {\Gamma,s\ts \sleep \converges_1 \skipp,s}\,.
        \]
      Fix a context $\Delta$ disjoint from $\Gamma$ and a store $t$ over $\Gamma,\Delta$ that is disjoint from $s$.  
      Fix $k\ge n$.  
      Then it suffices to show that the following judgement may be proved within the operational semantics of Idealized Algol.
      \[
        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \gets \suc !v \converges \skipp, (t{+}s\vert v\mapsto k+1)
        \]
      A derivation for this obvious fact is given in Figure \ref{SleepIADerivation}.
      \begin{SidewaysFigure}
        \centering
        \begin{subfigure}{\textheight}
          \[
            \inferrule*
            {
              \inferrule*
              {
                \inferrule*
                {
                  \inferrule*
                  {
                  }
                  {
                    \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \converges v,(t{+}s\vert v\mapsto k)
                  }
                }
                {
                  \Delta,\Gamma,v,(t{+}s\vert v\mapsto k) \ts !v \converges k,(t{+}s\vert v\mapsto k)
                }
              }
              {
                \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts \suc !v \converges k+1,(t{+}s\vert v\mapsto k)
              } \\
              \inferrule*
              {
              }
              {
                \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \converges v,(t{+}s\vert v\mapsto k)
              }
            }
            {
              \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v\gets\suc !v\converges\skipp,(t{+}s\vert v\mapsto k+1)
            }
            \]
          \caption{The crucial part of Lemma \ref{IaSleepsSoundnessLemma} pertaining to the $\sleep$ constant is a routine Idealized Algol derivation.}
          \label{SleepIADerivation}
        \end{subfigure}
        \par\vspace{48pt}
        \begin{subfigure}{\textheight}
          \[
            \inferrule*{\Delta,\Gamma_1,v,(t{+}s\vert v\mapsto k) \ts M_1[v \gets \suc !v/\sleep] \converges c_1,(t{+}s\vert v \mapsto k + n_1) \\
            \cdots \\
            \Delta,\Gamma_p,v,(t{+}s\vert v\mapsto k + n_1 + \cdots + n_{p-1}) \ts M_p[v \gets \suc !v/\sleep] \converges c_1,(t{+}s\vert v \mapsto k+n_1+\cdots+n_p)}
            {\Delta,\Gamma,v,(t{+}s^{(0)}\vert v \mapsto k + n_1 + \cdots + n_p)\ts M[v\gets \suc !v/\sleep] \converges c,(t{+}s^{(p)}\vert v \mapsto k)}
            \]
          \caption{The big-step rules of IA+$\sleep$ give rise to big-step rules of Idealized Algol via our translation.}
          \label{GeneralIADerivation}
        \end{subfigure}
        \caption{The proof of Lemma \ref{IaSleepsSoundnessLemma} works by translating big-step derivations from IA+$\sleep$ into big-step derivations of Idealized Algol.}
        \label{IADerivations}
      \end{SidewaysFigure}
    \item[Canonical forms]
      Suppose that the last step in the derivation is
      \[
        \inferrule*{ }
        {\Gamma,s\ts_0 c\converges c,s}\,.
        \]
      Then, since $\sleep$ is not a canonical form, we have $c[v\gets \suc !v/\sleep]=c$.  
      Then we have the derivation
      \[
        \inferrule*{ }
        {\Delta,\Gamma,(t{+}s\vert v\mapsto k)\ts c \converges c,(t{+}s\vert v\mapsto k)}\,.
        \]
    \item[Sequencing]
      Suppose instead that the last step in the derivation is
      \[
        \inferrule*{\Gamma,s\ts M \converges_m \skipp, s'\\
        \Gamma,s'\ts N \converges_n \skipp, s''}
        {\Gamma,s\ts M;N \converges_{m+n} \skipp, s''}\,.
        \]
      Fix $k\ge 0$.  
      By induction on $M,N$, we have
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts M[v\gets\pred !v/\sleep]\converges \skipp,(t{+}s'\vert  v\mapsto k+m)\,;
        \and
        \Delta,\Gamma,v,(t{+}s'\vert  v\mapsto k+m) \hspace{144pt} \par\vspace{-8pt} \\ \par \hspace{144pt} \ts N[v\gets\pred !v/\sleep]\converges \skipp,(t{+}s''\vert v\mapsto k+m+n)\,.
      \end{mathpar}
      It follows that
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k) \hspace{180pt} \par\vspace{-8pt} \\ \par \hspace{180pt} \ts (M;N)[v\gets\pred !v/\sleep] \converges \skipp, (t{+}s''\vert v\mapsto k+m+n)\,,
      \end{mathpar}
      by the sequencing rule of Idealized Algol.
    \item[Remaining rules]
      Having given the rule for canonical forms and sequencing explicitly, we now give a general technique by which we can deal with all the remaining rules.

      Each rule is of the form
      \[
        \inferrule*{ \Gamma_1,s^{(0)}\ts z_1\converges_{n_1}\gamma_1,s^{(1)} \\
        \cdots \\
        \Gamma_p,s^{(p - 1)}\ts z_p \converges_{n_p} \gamma_p,s^{(p)}}
        { \Gamma,s^{(0)}\ts z \converges_{n_1+\cdots+n_p} \gamma,s^{(p)}}
        \]
      (for $p\in\{0,1,2,3\}$), where
      \[
        \inferrule*{ \Gamma_1,s^{(0)}\ts z_1\converges \gamma_p,s^{(1)} \\
        \cdots \\
        \Gamma_p,s^{(p - 1)}\ts z_p \converges \gamma_1,s^{(p)}}
        { \Gamma,s^{(0)}\ts z \converges \gamma,s^{(p)}}
        \]
      is a rule for Idealized Algol.

      Here, each $z_i,z,\gamma_i,\gamma$ is a term of Idealized Algol (without $\sleep$) that may have free variables that are not included in the $\Gamma_i,\Gamma$.  
      These free variables $(x_\alpha)$ may be shared between the $z_i,z,\gamma_i,\gamma$, introducing a dependence between them.
      For example, in the rule for sequencing, the terms on the top are single-variable terms of IA, where `$M$' and `$N$' are themselves free variables.  
      These variables are bound in the expression `$M;N$' on the bottom of the rule.

      Fix some such rule, and suppose that it is used in the last step of the deduction.  
      So the last step looks like this.
      \[
        \inferrule*{ \Gamma_1,s^{(0)}\ts M_1\converges_{n_1}c_1,s^{(1)} \\
        \cdots \\
        \Gamma_p,s^{(p - 1)}\ts M_p \converges_{n_p} c_p,s^{(p)}}
        { \Gamma,s^{(0)}\ts M \converges_{n_1+\cdots+n_p} c,s^{(p)}}
        \]
      Here, the $M_i,M,c_i,c$ fit the pattern given by the $z_i,z,\gamma_i,\gamma$.  
      By induction, for each $i=1,\cdots,p$, the following judgement may be proved in Idealized Algol.
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s^{(i)}\vert v \mapsto k + n_1 + \cdots + n_{i-1})
        \hspace{144pt} \par\vspace{-20pt} \\ \par \hspace{144pt}
        \ts
        M[v \gets \suc !v] \converges c_i,(t{+}s^{(i)}\vert v \mapsto k + n_1 + \cdots + n_i)
      \end{mathpar}

      Now we know that the $M_i,M,c_i,c$ may be obtained from the $z_i,z,\gamma_i,\gamma$ by substituting in actual terms $N_\alpha$ for the free variables $x_\alpha$ in these expressions.  
      Moreover, since the primitive $\sleep$ is not mentioned anywhere in these rules, it follows that we have
      \begin{IEEEeqnarray*}{rCl}
        M_i[v\gets\suc !v/\sleep] & = & (z_i[N\alpha/x_\alpha])[v\gets \suc !v/\sleep] \\
        & = & z_i[(N[v\gets \suc !v/\sleep])/x_\alpha]\,,
      \end{IEEEeqnarray*}
      and similarly for the $z,\gamma_i,\gamma$.
      Therefore, the $M_i,M,c_i,c$ still fit the pattern given by the $z_i,z,\gamma_i,\gamma$, even after making our substitution.  
      It follows that we may derive
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s^{(0)}\vert v \mapsto k)\hspace{180pt}\par\vspace{-8pt}\\ \par
        \hspace{180pt}\ts M[v\gets \suc !v/\sleep] \converges c,(t{+}s^{(p)}\vert v \mapsto k+n_1+\cdots+n_p)
      \end{mathpar}
      using the derivation shown in Figure \ref{GeneralIADerivation}.
  \end{description}
  This completes the induction.
\end{proof}

In light of this result, we can make a definition relating the denotational and operational semantics of terms of type $\nat$.  
First, observe that since the $\beta$ rule is valid in our semantics, we may write the denotation of a term $M\from\com$ of IA+$\sleep$ as the composite
\[
  1 \xrightarrow{\sleep}
  \bC \xrightarrow{\deno{c\ts M[c/\sleep]}}
  \bC
  \]
in $\Kl_{R_\bC}$.

Working in the original category $\G$, however, we may identify this composite with the morphism
\[
  \deno{c\ts M[c/\sleep]} \from \bC \to \bC\,.
  \]
Now we have morphisms
\begin{mathpar}
  \deno{v\ts v \gets \suc !v} \from \Var \to \bC
  \and
  \deno{v\ts !v} \from \Var \to \bN\,,
\end{mathpar}
which together induce the composite
\[
  \Var \xrightarrow{\langle \deno{v\ts v \gets \suc !v},\deno{v\ts !v}\rangle}
  \bC \times \bN \xrightarrow{\deno{c \ts M[c/\sleep]} \times \id}
  \bC \times \bN \xrightarrow{\deno{\blank;\blank}}
  \bN\,.
  \]
Lastly, we may curry this term to give a morphism $1 \to (\Var\to \bN)$ and compose with the morphism
\[
  \new_\bN \from (\Var \to \bN) \to \bN\,.
  \]
The resulting morphism will be the denotation of the term
\[
  \new\;v=0\text{ in } M[v\gets \suc !v/\sleep];!v\from \nat\,.
  \]
Lemma \ref{IaSleepsSoundnessLemma} tells us that if $M\converges_n\skipp$ then this term converges to $n$ in Idealized Algol.

Before we introduce our adequacy result, we need one more definition in order to take account of the fact that Proposition \ref{SamsonGuyAdequacy} applies to terms of type $\com$, not $\nat$.

\newcommand{\test}{{\mathtt{test}}}
\begin{definition}
  Define terms $\test_n\from\nat\to\com$ inductively by
  \begin{gather*}
    \test_0 = \lambda m.\IfO m\text{ then }\skipp\text{ else }\Omega\,; \\
    \test_{n+1} = \lambda m.\IfO m\text{ then }\Omega\text{ else }\test_n\,. (\pred m)
  \end{gather*}
  So $\test_n$ converges if its input evaluates to $n$ and diverges otherwise.

  Let $t_n\from\bN \to \bC$ be the denotation in $\G$ of $\test_n$.
\end{definition}

\begin{remark}
  In the model $\G$ of Idealized Algol, every morphism $1 \to \bN$ is definable, so if $\sigma\from 1 \to \bN$ is such a morphism, then there must be at most one $n\in\omega$ such that the composite $\sigma;t_n$ is not equal to $\bot$.
\end{remark}

\newcommand{\tit}{\mathrm{tt}}
\begin{definition}
  Let $\sigma\from 1 \to \bC$ be a Kleisli morphism in $\Kl_{R_{\bC}}$, considered as a morphism $\bC \to \bC$ in $\G$.  
  Define:
  \begin{IEEEeqnarray*}{rCl}
    \sigma' & = & \Var \xrightarrow{\langle \deno{v\ts v \gets \suc !v},\deno{v\ts !v}\rangle}
    \bC \times \bN \xrightarrow{\sigma\times\id}
    \bC \times \bN \xrightarrow{\deno{\blank;\blank}}
    \bN\,; \\
    \sigma'' & = & 1 \xrightarrow{\text{curry }\sigma''}
    (\Var \to \bN) \xrightarrow{\new_\bN}
    \bN\,.
  \end{IEEEeqnarray*}

  If there is some (necessarily unique) $n\in\omega$ such that
  \[
    1 \xrightarrow{\sigma''}
    \bN \xrightarrow{t_n}
    \bC
    \]
  is not equal to $\bot$, then we say that $n$ is the \emph{time taken for $\sigma$ to converge}, or $\tit(\sigma)$.
  If there is no such $n$, we say that $\tit(\sigma)=\infty$.
\end{definition}

From our discussion above, we have proved the following result.

\begin{proposition}[Soundness for IA+$\sleep$]
  Let $P\from \com$ be a term of IA+$\sleep$ and let $\sigma\from \bC \to \bC$ be its denotation in $\Kl_{R_\bC}$, considered as a morphism in $\G$.
  If $P\converges_n$ then $\tit(\sigma)=n$.
  \label{IaSleepSoundness}
\end{proposition}

In order to prove the other direction (adequacy), we need to prove a kind of converse to Lemma \ref{IaSleepsSoundnessLemma}.

\begin{lemma}
  Let $\Gamma\ts M\from \com$ be a term of IA+$\sleep$ in context.
  Let $s,s'$ be stores, let $a,b\in\bN$, let $c$ be a canonical form and let $v$ be a variable not included in $\Gamma$.  
  Suppose that
  \[
    \Gamma,v,(s\vert v\mapsto a) \ts M \converges c,(s'\vert v\mapsto b)
    \]
  in Idealized Algol.
  Then there exists $n$ such that
  \[
    \Gamma,s \ts M \converges_n c,s'
    \]
  in IA+$\sleep$.
\end{lemma}
\begin{proof}
  Induction on the derivation that $\Gamma,v,(s\vert v\mapsto a)\ts M\converges c,(s'\vert v\mapsto b)$.  
  Most cases are self-explanatory.  
  For example, suppose that the last step in the derivation is an instance of the sequencing rule:
  \[
    \inferrule{\Gamma,v,(s\vert v \mapsto a) \ts M[v\gets\suc !v/\sleep] \converges \skipp, s' \\
    \Gamma,v,s' \ts N[v\gets\suc !v/\sleep] \converges c, (s''\vert v \mapsto b)}
    {\Gamma,v(s\vert v \mapsto a) \ts (M;N)[v\gets\suc !v/\sleep] \converges c,(s''\vert v \mapsto b)}\,.
    \]
  Since there is no provable sequent of Idealized Algol in which a defined variable on the left ceases to be defined on the right, we may deduce that $s'$ can be written as $(t\vert v \mapsto d)$.  
  Therefore, we may apply the inductive hypothesis to $M$ and $N$, which tells us that there must be $m,n$ such that
  \begin{mathpar}
    \Gamma,s \ts M\converges_m\skipp,t\,;
    \and
    \Gamma,t \ts M\converges_n c,s''\,.
  \end{mathpar}
  From this it follows that
  \[
    \Gamma,s \ts M;N \converges_{m+n} c,s''\,.
    \]
  Crucial to this argument is the fact that
  \[
    (M[v\gets\suc !v/\sleep]);(N[v\gets\suc !v/\sleep]) = (M;N)[v\gets\suc!v/\sleep]\,.
    \]
  For almost all the other rules, a similar equality holds.  
  The only case where there is a problem is the first rule for $\blank\gets\blank$, since this may introduce a new copy of $v\gets\suc!v$ on the bottom that does not arise from copies of $v\gets\suc!v$ on the top.

  The offending term occurs when $M=\sleep$ and so $M[v\gets\suc!v/\sleep]=v\gets\suc!v$.
  In that case, the inference is
  \[
    \inferrule{\Gamma,(s\vert v \mapsto a)\ts \suc ! v \converges b,s'\\
    \Gamma,s'\ts v \converges v,s''}
    {\Gamma,(s\vert v\mapsto a)\ts v \gets\suc!v \converges \skipp,(s''\vert v\mapsto b)}\,.
    \]
  By following the derivation upwards, we may deduce that in fact $s=s'=s''$.
  But in that case the derivation of $\Gamma,s\ts_n M\converges \skipp,s''$ is one of the base rules:
  \[
    \inferrule{ }
    {\Gamma,s \ts \sleep \converges_1 \skipp,s}\,.
    \]
  The other cases are routine.  
  This completes the induction.
  \label{IaSleepAdequacyLemma}
\end{proof}

\begin{theorem}[Computational adequacy for IA+$\sleep$]
  Let $P\from\com$ be a term of IA+$\sleep$ and let $\sigma\from \bC\to \bC$ be its denotation in $\Kl_{R_\bC}$, considered as a morphism in $\G$.
  Then $P\converges_n$ if and only if $\tit(\sigma)=n$.
  \label{IaSleepComputationalAdequacy}
\end{theorem}
\begin{proof}
  The forward direction is Proposition \ref{IaSleepSoundness}.  
  For the reverse direction, note that if $\tit(\sigma)=n$, it means that
  \[
    \deno{\test_n(\new v=0\text{ in }P[v\gets \suc!v/\sleep];!v])} \ne \bot\,,
  \]
  which, by Proposition \ref{SamsonGuyAdequacy}, means that
  \[
    \test_n(\new v=0\text{ in } P[v\gets\suc!v/\sleep];!v])\converges
  \]
  in Idealized Algol, and therefore that
  \[
    v,(v\mapsto 0) \ts P[v\gets\suc!v/\sleep]\converges \skipp,(v\mapsto n)\,.
    \]
  From Lemma \ref{IaSleepAdequacyLemma}, we deduce that we must have
  \[
    ,() \ts P \converges_m \skipp,()
    \]
  in IA+$\sleep$ for some $m$, and by Lemma \ref{IaSleepsSoundnessLemma} we must have $m=n$.  
  Therefore, $P\converges_n$.
\end{proof}

The last definition we need to make is the standard intrinsic equivalence relation.

\begin{definition}
  Let $\sigma,\tau\from A \to B$ be morphisms in $\Kl_{R_\bC}$.  
  By currying, we may consider $\sigma,\tau$ to be morphisms $1 \to (A \to B)$.  
  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$, we have $\tit(\sigma;\alpha)=\tit(\sigma;\beta)$.
\end{definition}

We now have all the tools necessary to prove that $Kl_{R_\bC}$ is fully abstract for IA+$\sleep$.
The technique we use is standard and relies on a factorization result, as with the proofs given in \cite{SamsonGuyIAActive} and \cite{mcCHFiniteND}.  
The difference here is that our factorization result is immediate, and does not rely on any combinatorial arguments.

\begin{theorem}
  Let $M,N\from T$ be two terms of IA+$\sleep$.  
  Then $M$ and $N$ are observationally equivalent if and only if $\deno{M}\sim\deno{N}$.
  \label{IaSleepTimeComplexity}
\end{theorem}
\begin{proof}
  First suppose that $M$ and $N$ are not observationally equivalent.  
  So there is some context $-\from T\ts C[-]\from\com$ such that $C[M]$ and $C[N]$ have different operational behaviours in IA+$\sleep$.
  By Theorem \ref{IaSleepComputationalAdequacy} we know that for any program $P$ we have $P\converges_n$ if and only if $\tit(\deno P)=n$ and $P\diverges$ if and only if $\tit(\deno P)=\infty$.
  Therefore, we must have $\tit(\deno{C[M]})\ne \tit(\deno{C[n]})$.  
  But since $\deno{C[M]}=\deno{M};\deno{C}$ and $\deno{C[N]}=\deno{N};\deno{C}$, we must have $\deno M\not\sim \deno N$.

  Conversely, suppose that $\deno M \not\sim \deno N$.  
  So there is some $\alpha\from \deno{T} \to \bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.

  Let us now work in the category $\G$.  
  So $\deno{M},\deno{N}$ may be regarded as morphisms $\bC \to \deno{T}$ and $\alpha$ may be regarded as a morphism $\deno{T} \to (\bC \to \bC)$, or equivalently as a morphism $\deno{T}\times \bC \to \bC$.
  Then the composites $\deno M;\alpha,\deno N;\alpha$ within $\Kl_{R_\bC}$ are given by the following composites in $\G$.
  \begin{mathpar}
    \bC \xrightarrow{\langle \deno M,\id\rangle}
    \deno T \times \bC \xrightarrow{\alpha}
    \bC
    \and
    \bC \xrightarrow{\langle \deno N,\id\rangle}
    \deno T \times \bC \xrightarrow{\alpha}
    \bC
  \end{mathpar} 
  By assumption, these composites are not equal in $\G$.  
  Then it is sufficient (since this is the case in $\G$) to assume that $\alpha$ is a compact strategy.
  Then, by the compact definability result in \cite{SamsonGuyIAActive}, $\alpha$ must be the denotation (in $\G$) of some term $P\from T \to \com \to \com$, which corresponds to the context
  \[
    C[x] = P\,x\;\sleep
    \]
  in $\Kl_{R_\bC}$.

  It follows that $\deno{C[M]} \ne \deno{C[N]}$.  
  Therefore, by Proposition \ref{IaSleepComputationalAdequacy}, $M$ and $N$ are not observationally equivalent.
\end{proof}

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-01-10 Thesis/thesis.tex
Fixed error.

@@
   Let $\M$ be a monoidal category and let $x$ be a monoid in $\M$.  
-  The \emph{writer monoid} $W_x$ on $\M$ is defined by $W_x y = y \tensor x$, with natural transformations
+  The \emph{writer monad} $W_x$ on $\M$ is defined by $W_x y = y \tensor x$, with natural transformations
   \begin{mathpar}
@@
 
-  Going the other way, if $\M$ is monoidal closed with inner hom $\implies$, and if $z$ is a comonoid in $\M$, then the \emph{reader monoid} $R_z$ is given by $R_z y = z \implies y$.  
+  Going the other way, if $\M$ is monoidal closed with inner hom $\implies$, and if $z$ is a comonoid in $\M$, then the \emph{reader monad} $R_z$ is given by $R_z y = z \implies y$.  
   Then the monadic coherences

### 2019-01-10 Thesis/thesis.tex
Made technical revisions.

@@
 
-Readers unfamiliar with game semantics should not worry too much about what $\bot$ is; the point of Proposition \ref{SamsonGuyAdequacy} is that the denotation of a command-type term precisely captures the operational behaviourof that term, in the sense that there is some distinguished strategy $\bot\from 1 \to \bC$ that is the denotation of every divergent program, and no convergent one.
+To make sense of this strategy, we need to know that $\G$ is enriched in algebraic cpos.  
+Then $\bot$ is the bottom element of $\G(1,\bC)$.
 
@@
 \[
-  \deno{c\ts M[c/\sleep]} \from \bC \to \bC\,.
+  \deno{\lambda c.M[c/\sleep]} \from 1 \to (\bC \to \bC)\,.
   \]
-Now we have morphisms
+Now we have a morphism
 \begin{mathpar}
-  \deno{v\ts v \gets \suc !v} \from \Var \to \bC
-  \and
-  \deno{v\ts !v} \from \Var \to \bN\,,
+  \eta = \deno{f\from \com\to \com \ts \lambda v.f(v\gets \suc!v);!v}\from (\bC \to \bC) \to (\Var \to \bN)\,.
 \end{mathpar}
-which together induce the composite
+If we form the composite
 \[
-  \Var \xrightarrow{\langle \deno{v\ts v \gets \suc !v},\deno{v\ts !v}\rangle}
-  \bC \times \bN \xrightarrow{\deno{c \ts M[c/\sleep]} \times \id}
-  \bC \times \bN \xrightarrow{\deno{\blank;\blank}}
-  \bN\,.
+  1 \xrightarrow{\deno{\lambda c.M[c/\sleep]}}
+  (\bC \to \bC) \xrightarrow{\eta}
+  (\Var \to \bN) \xrightarrow{\new_\bN}
+  \bN
   \]
-Lastly, we may curry this term to give a morphism $1 \to (\Var\to \bN)$ and compose with the morphism
+then the morphism we get will be the denotation in $\G$ of the term
 \[
-  \new_\bN \from (\Var \to \bN) \to \bN\,.
+  \ts \new\;v=0\text{ in } M[v\gets \suc !v/\sleep];!v\from \nat
   \]
-The resulting morphism will be the denotation of the term
-\[
-  \new\;v=0\text{ in } M[v\gets \suc !v/\sleep];!v\from \nat\,.
-  \]
+(since the $\beta$ rule is valid for the semantics in $\G$).
 Lemma \ref{IaSleepsSoundnessLemma} tells us that if $M\converges_n\skipp$ then this term converges to $n$ in Idealized Algol.
@@
 \begin{definition}
-  Let $\sigma\from 1 \to \bC$ be a Kleisli morphism in $\Kl_{R_{\bC}}$, considered as a morphism $\bC \to \bC$ in $\G$.  
-  Define:
-  \begin{IEEEeqnarray*}{rCl}
-    \sigma' & = & \Var \xrightarrow{\langle \deno{v\ts v \gets \suc !v},\deno{v\ts !v}\rangle}
-    \bC \times \bN \xrightarrow{\sigma\times\id}
-    \bC \times \bN \xrightarrow{\deno{\blank;\blank}}
-    \bN\,; \\
-    \sigma'' & = & 1 \xrightarrow{\text{curry }\sigma''}
+  Let $\sigma\from 1 \to \bC$ be a Kleisli morphism in $\Kl_{R_{\bC}}$, considered as a morphism $1 \to (\bC \to \bC)$ in $\G$.
+
+  If there is some (necessarily unique) $n\in\omega$ such that the composite
+  \[
+    1 \xrightarrow{\sigma}
+    (\bC \to \bC) \xrightarrow{\eta}
     (\Var \to \bN) \xrightarrow{\new_\bN}
-    \bN\,.
-  \end{IEEEeqnarray*}
-
-  If there is some (necessarily unique) $n\in\omega$ such that
-  \[
-    1 \xrightarrow{\sigma''}
     \bN \xrightarrow{t_n}
@@
   If there is no such $n$, we say that $\tit(\sigma)=\infty$.
+  \label{DefTimeTaken}
 \end{definition}
@@
   Let us now work in the category $\G$.  
-  So $\deno{M},\deno{N}$ may be regarded as morphisms $\bC \to \deno{T}$ and $\alpha$ may be regarded as a morphism $\deno{T} \to (\bC \to \bC)$, or equivalently as a morphism $\deno{T}\times \bC \to \bC$.
-  Then the composites $\deno M;\alpha,\deno N;\alpha$ within $\Kl_{R_\bC}$ are given by the following composites in $\G$.
+  So $\deno{M},\deno{N}$ may be regarded as morphisms $1 \to (\bC \to \deno{T})$ and $\alpha$ may be regarded as a morphism $\deno{T} \to (\bC \to \bC)$.
+  Then the composites $\deno M;\alpha$ and $\deno N;\alpha$ within $\Kl_{R_\bC}$ are given by the following composites in $\G$.
   \begin{mathpar}
-    \bC \xrightarrow{\langle \deno M,\id\rangle}
-    \deno T \times \bC \xrightarrow{\alpha}
-    \bC
+    1 \xrightarrow{\deno M}
+    (\bC \to \deno T) \xrightarrow{\bC \to \alpha}
+    (\bC \to (\bC \to \bC)) \xrightarrow{\mu}
+    (\bC \to \bC)
     \and
-    \bC \xrightarrow{\langle \deno N,\id\rangle}
-    \deno T \times \bC \xrightarrow{\alpha}
-    \bC
+    1 \xrightarrow{\deno N}
+    (\bC \to \deno T) \xrightarrow{\bC \to \alpha}
+    (\bC \to (\bC \to \bC)) \xrightarrow{\mu}
+    (\bC \to \bC)
   \end{mathpar} 
-  By assumption, these composites are not equal in $\G$.  
-  Then it is sufficient (since this is the case in $\G$) to assume that $\alpha$ is a compact strategy.
-  Then, by the compact definability result in \cite{SamsonGuyIAActive}, $\alpha$ must be the denotation (in $\G$) of some term $P\from T \to \com \to \com$, which corresponds to the context
-  \[
-    C[x] = P\,x\;\sleep
-    \]
-  in $\Kl_{R_\bC}$.
+  Without loss of generality, suppose that there exists some $n$ such that
+  \begin{mathpar}
+    \tit(\deno{M};(\bC \to \alpha);\mu)=n \and \tit(\deno{N};(\bC \to \alpha);\mu)\ne n\,.
+  \end{mathpar}
+  This means that we must have
+  \begin{mathpar}
+    \deno M;(\bC \to \alpha);\mu;\eta;\new_\bC;t_n \ne \bot
+    \and
+    \deno N;(\bC \to \alpha);\mu;\eta;\new_\bC;t_n = \bot
+  \end{mathpar}
+  in $\G$ (where $\eta$ is as defined in Definition \ref{DefTimeTaken}).
 
-  It follows that $\deno{C[M]} \ne \deno{C[N]}$.  
-  Therefore, by Proposition \ref{IaSleepComputationalAdequacy}, $M$ and $N$ are not observationally equivalent.
+  $\G$ is enriched in algebraic cpos, so $\alpha$ is the least upper bound of its compact approximants.  
+  It follows that there is some compact $\alpha'\subset \alpha$ such that
+  \begin{mathpar}
+    \deno M;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n \ne \bot
+    \and
+    \deno N;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n = \bot\,.
+  \end{mathpar}
+  In other words:
+  \begin{mathpar}
+    \tit(\deno M;(\bC \to \alpha');\mu) = n\,;
+    \and
+    \tit(\deno M;(\bC \to \alpha');\mu) \ne n\,.
+  \end{mathpar}
+  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $C[\sleep] \from \com \to \com$ in $\Kl_{R_\bC}$.
+  So we get
+  \begin{mathpar}
+    \tit(\deno{C[\sleep] M}) = n\,;
+    \and
+    \tit(\deno{C[\sleep] N}) \ne n\,.
+  \end{mathpar}
+  By Theorem \ref{IaSleepComputationalAdequacy}, $C[\sleep] M\converges_n$ and $C[\sleep] N\not\converges_n$.  
+  Therefore, $M$ and $N$ are observationally inequivalent in IA+$\sleep$.
 \end{proof}

### 2019-01-10 Thesis/thesis.tex
Correction.

@@
     \and
-    \tit(\deno M;(\bC \to \alpha');\mu) \ne n\,.
+    \tit(\deno N;(\bC \to \alpha');\mu) \ne n\,.
   \end{mathpar}
-  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $C[\sleep] \from \com \to \com$ in $\Kl_{R_\bC}$.
+  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $x\from T \ts C[x]\,\sleep \from \com$ in $\Kl_{R_\bC}$.
   So we get
   \begin{mathpar}
-    \tit(\deno{C[\sleep] M}) = n\,;
+    \tit(\deno{C[M]\,\sleep}) = n\,;
     \and
-    \tit(\deno{C[\sleep] N}) \ne n\,.
+    \tit(\deno{C[N]\,\sleep}) \ne n\,.
   \end{mathpar}
-  By Theorem \ref{IaSleepComputationalAdequacy}, $C[\sleep] M\converges_n$ and $C[\sleep] N\not\converges_n$.  
+  By Theorem \ref{IaSleepComputationalAdequacy}, $C[M]\,\sleep\converges_n$ and $C[N]\,\sleep\not\converges_n$.  
   Therefore, $M$ and $N$ are observationally inequivalent in IA+$\sleep$.

### 2019-03-01 Thesis/bigdiagram.tex
Started writing thesis.

  \begin{SidewaysFigure}
    \[
      \begin{tikzcd}[column sep=1pt, ampersand replacement=\&]
        %
        \&[-126pt] (jx \implies jy \implies a) \tensor (jx' \implies jy' \implies a') \arrow[r] \arrow[d]
            \& (jx \tensor jx') \implies ((jy \implies a)\tensor (jy'\implies a')) \arrow[r] \arrow[d]
              \& j(x\tensor x') \implies ((jy\implies a) \tensor (jy'\implies a')) \arrow[d] \\
        %
          \& ((jx \tensor jy) \implies a) \tensor ((jx' \tensor jy') \implies a') \arrow[ddl, to path= {(\tikztostart.west) -| ([xshift=-50pt] \tikztotarget.north)}] \arrow[d]
            \& (jx \tensor jx') \implies (jy \tensor jy') \implies (a \tensor a') \arrow[d] \arrow[ddr, bend left=10] \arrow[r]
              \& j(x\tensor x') \implies (jy \tensor jy') \implies (a \tensor a') \arrow[dd] \\
        %
          \& ((jx\tensor jy)\tensor (jx'\tensor jy')) \implies (a\tensor a') \arrow[ddl, to path= {([xshift=50pt] \tikztostart.south) |- (\tikztotarget.east)}] \arrow[r]
            \& ((jx \tensor jx') \tensor (jy \tensor jy')) \implies (a\tensor a') \arrow[ddr, to={Z.west}, bend right=10]
              \& \\
        (j(x\tensor y) \implies a) \tensor (j(x'\tensor y') \implies a') \arrow[d]
          \&
            \&
              \& j(x\tensor x') \implies j(y\tensor y') \implies (a \tensor a') \arrow[d] \\
        (j(x\tensor y) \tensor j(x'\tensor y')) \implies (a \tensor a') \arrow[d]
          \&
            \&
              \& |[alias=Z]| (j(x \tensor x') \tensor j(y \tensor y') \implies(a \tensor a')) \arrow[d] \\
        j((x\tensor y)\tensor (x'\tensor y')) \implies (a \tensor a') \arrow[rrr]
          \&
            \&
              \& j((x\tensor x') \tensor (y \tensor y')) \implies (a \tensor a')
      \end{tikzcd}
      \]
    \caption{Proof that the parametric reader monad corresponding to a symmetric monoidal functor is a symmetric monoidal action.  
    The hexagon at the top commutes by the coherence theorems for symmetric monoidal closed categories, while that at the bottom commutes because $j$ is a symmetric monoidal functor.}
    \label{FigReaderMonadIsGoodActionProof}
  \end{SidewaysFigure}

  \begin{figure}
    \[
      \begin{tikzcd}[column sep=60pt]
        \left[B,y.C\right] \times ([A,x.B] \times A) \arrow[r, "{s_{y,B,C}\times(s_{x,A,B} \times A)}" xshift=-3pt, dotted] \arrow[dd, "{[B,y.C]\times\ev_{A,x.B}}"'] \arrow[ddr, "\textbf{1}", phantom]
          & y.[B,C] \times (x.[A,B] \times A) \arrow[d, "{y.[B,C]\times (x.[A,B] \times e_A)}", thick, dashed] \\
        %
          & y.[B,C] \times (x.[A,B]\times I.A) \arrow[d, "{y.[B,C]\times m_{x,I,[A,B],A}}", thick, dashed] \\
        \left[B,y.C\right] \times x.B \arrow[d, "{e_{[B,y.C]}\times x.B}"'] \arrow[dr, "\textbf{2}", phantom]
          & y.[B,C] \times (x\tensor I).([A,B]\times A) \arrow[l, "{s_{y,B,C}\inv\times\runit_x\inv . \ev_{A,B}}"' xshift=3pt, dotted]  \arrow[d, "{e_{y.[B,C]} \times \runit_x\inv.\ev_{A,B}}", thick, dashed] \\
        I.\left[B,y.C\right] \times x.B \arrow[dd, "{m_{I,x,[B,y.C],B}}"'] \arrow[r, "{I.s_{y,B,C} \times x.B}", dotted] \arrow[ddr, "\textbf{3}", phantom]
          & I.y.[B,C] \times x.B  \arrow[d, "{m_{I,x,y,[B,C],B}}", thick, dashed] \\
        %
          & (I \tensor x).(y.[B,C] \times B) \arrow[d, "{(I \tensor x).(y.[B,C] \times e_B)}", thick, dashed] \\
        (I \tensor x).([B,y.C] \times B) \arrow[r, "{(I\tensor x) . (s_{y,B,C} \times e_B)}" xshift=-3pt, dotted] \arrow[d, "{\id.\ev_{B,y.C}}"'] \arrow[dr, "\textbf{4}", phantom]
          & (I \tensor x).(y.[B,C] \times I.B) \arrow[d, "{(I\tensor x).m_{y,I,B,C}}", thick, dashed] \\
        (I \tensor x).y.C \arrow[d, "\lunit_x\inv.y.C"']
          & (I \tensor x).(y \tensor I).([B,C] \times B) \arrow[l, "{(I\tensor x).\lunit_y\inv.\ev_{B,C}}"', dotted] \arrow[dl, "{\lunit_x\inv.\lunit_y\inv.\ev_{B,C}}", thick, dashed] \\
        x.y.C \arrow[d, "{m_{x,y,C}}"'] \arrow[d, thick, dashed]
          & \\
        (x \tensor y).C
          &
      \end{tikzcd}
      \]
      \caption{Commutative diagram relating \Mellies composition with base changed composition for a monoidal lax action.  
      Commutativity of \textbf{1} and \textbf{4} is by the coherence diagram in Definition \ref{DefSymmetricMonoidalClosedAction}. \textbf{2} commutes because $s$ is a natural transformation and \textbf{3} commutes because $m$ is a natural transformation.  
      For the \Mellies composition, we have been fairly free about choosing a representative morphism from each equivalence class; i.e., if $f \from a \to x.b$ is a particular representative for some morphism in $\C/\X$, then we have not }
  \end{figure}

### 2019-03-01 Thesis/pmonads.tex
Started writing thesis.

\documentclass{article}

\input{../common/preamble}
\begin{document}
\section{Parametric monads}

Since a monoid in a monoidal category $\mathcal X$ is the same thing as a lax monoidal functor from the unit category into $\mathcal X$, the definition of a monad on a category $\C$ (i.e., a monoid in $[\C,\C]$) may be generalized to that of a \emph{lax action} \cite{LaxActions} of a monoidal category $\X$ on $\C$; i.e., a lax monoidal functor $\X \to [\C,\C]$ (so that a monoid in $\C$ is a lax action of the unit category on $\C$).

Equivalently, a lax action is given by a functor $\blank.\blank \from \X \times \C \to \C$ together with natural transformations
\begin{mathpar}
  m_{x,y,a}\from x.y.a \to (x\tensor y).a
  \and
  e_a \from a \to I.a
\end{mathpar}
such that the following diagrams commute.
\begin{mathpar}
  \begin{tikzcd}[column sep=36pt]
    x.y.z.a \arrow[r, "x.m_{y,z,a}"] \arrow[d, "m_{x,y,z.a}"']
      & x.(y\tensor z).a \arrow[r, "m_{x,y\tensor z,a}"]
        & (x \tensor (y \tensor z)) . a \\
    (x\tensor y).z.a \arrow[r, "m_{x\tensor y,z,a}"]
      & ((x\tensor y)\tensor z) . a \arrow[ur, "\assoc_{x,y,z}.a"']
        &
  \end{tikzcd}
  \and
  \begin{tikzcd}
    x.a \arrow[r, "e_{x.a}"] \arrow[dr, "\lunit_x.a"']
      & I.x.a \arrow[d, "m_{I,x,a}"] \\
    %
      & (I\tensor x).a
  \end{tikzcd}
  \and
  \begin{tikzcd}
    x.a \arrow[r, "x.e_a"] \arrow[dr, "\runit_x.a"']
      & x.I.a \arrow[d, "m_{x,I,a}"] \\
    %
      & (x\tensor I) . a
  \end{tikzcd}
\end{mathpar}
Since lax actions generalize monads, we shall follow \Mellies \cite{ParametricMonads} and refer to them as \emph{parametric monads}.

\begin{example}
  If $\X$ is a monoidal category, $\C$ is a monoidal closed category and $j\from \X \to \C$ is an oplax monoidal functor, then we have a lax action of $\oppcat\X$ on $\C$ given by
  \[
    x.a = jx \implies a\,,
    \]
  together with the natural coherences
  \begin{mathpar}
    jx\implies jy\implies a \xrightarrow{\makebox[24pt]{}} (jx\tensor jy) \implies a \xrightarrow{m^j_{x,y}\implies a} j(x\tensor y) \implies a
    \and
    a \xrightarrow{\makebox[24pt]{}} I \implies a \xrightarrow{e^j\implies a} jI \implies a\,.
  \end{mathpar}
  This generalizes the \emph{reader monads} that we met earlier, so we shall call a parametric monad of this form a \emph{parametric reader monad} or \emph{lax reader action}.
\end{example}

\begin{definition}
  \label{DefOplaxMorphismOfActions}
  Suppose that a monoidal category $\X$ acts on a category $\C$ and that it also acts on a category $\D$.  
  An \emph{oplax morphism of actions} from one action to the other is given by a functor $F \from \C \to \D$ together with a natural transformation $\mu_{x,a} \from F(x.a) \to x.Fa$ that makes the following diagrams commute for all objects $x,y$ of $\X$ and $a$ of $\C$.
  \begin{mathpar}
    \begin{tikzcd}
      F(x.y.a) \arrow[r, "{\mu_{x,y.a}}"] \arrow[d, "{Fm_{x,y,a}}"']
        & x.F(y.a) \arrow[r, "{x.\mu_{y,a}}"]
          & x.y.Fa \arrow[d, "{m_{x,y,Fa}}"] \\
      F((x\tensor y).a) \arrow[rr, "{\mu_{x\tensor y,a}}"]
        &
          & (x \tensor y).Fa
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Fa \arrow[d, "Fe_a"'] \arrow[dr, "e_{Fa}"]
        & \\
      F(I.a) \arrow[r, "{\mu_{I,a}}" xshift=-3pt]
        & I.Fa
    \end{tikzcd}
  \end{mathpar}
\end{definition}

\subsection{The \Mellies category}

The main thing we want to do with lax actions is to perform a construction analogous to that of the Kleisli category of a monad.  
Fujii, Katsumata and \Mellies give a construction called a `Kleisli resolution' in the paper \cite{KleisliResolution}, but we shall prefer an alternative construction due to \Mellies.

Suppose that a monoidal category $\X$ acts on a category $\C$.
\begin{definition}
  A \emph{\Mellies morphism} from $a$ to $b$ is one of the form
  \[
    a \to x.b\,,
    \]
  for some object $x$ of $\X$.
\end{definition}

\begin{definition}
  Given \Mellies morphisms $f$ from $a$ to $b$ and $g$ from $b$ to $c$ given by
  \begin{mathpar}
    \tilde{f} \from a \to x.b
    \and
    \tilde{g} \from b \to y.c\,,
  \end{mathpar}
  their \emph{\Mellies composition} is given by the composite
  \[
    a \xrightarrow{\tilde f}
    x.b \xrightarrow{x.\tilde g}
    x.y.c \xrightarrow{m_{x,y,c}}
    (x\tensor y).c\,,
    \]
  which is a \Mellies morphism from $a$ to $c$.
  \label{DefMelliesComposition}
\end{definition}
\begin{definition}[\cite{ThesisForDays}]
  Let $\X$ be a monoidal category, and let $F,G\from \X \to \Set$ be functors.  
  Then the \emph{Day convolution} of $F$ and $G$ is a functor
  \[
    F \tensor_{\text{Day}} G \from \X \to \Set
    \]
  given by
  \[
    (F \tensor_{\text{Day}} G)(x) = \int^{y,z\from \X} F(y) \times G(z) \times \X(y\tensor z,x)\,.
    \]
  This makes $[\X,\Set]$ into a monoidal category (the monoidal unit is the functor $\X(I,\blank)\from \X \to \Set$).
  \label{DefDayConvolution}
\end{definition}

\begin{definition}[\cite{MelliesCategory}]
  Given a lax action of a monoidal category $\X$ upon a category $\C$, the \emph{\Mellies category} of the action is an $[\X,\Set]$-enriched category $\Mell_\X\C$ whose objects are the objects of $\C$ and where the hom objects are given by
  \[
    \Mell_\X\C(a,b)(x) = \C(a,x.b)\,.
    \]
  The composition is given by the natural transformation
  \begin{IEEEeqnarray*}{Cl}
    & (\Mell_\X\C(a,b) \tensor_{\text{Day}} \Mell_\X\C(b,c))(x)\\
    = & \int^{y,z\from \X} \C(a,y.b) \times \C(b,z.c) \times \X(y\tensor z,x) \\
    \to & \int^{y,z\from \X} \C(a,(y\tensor z).c) \times \X(y\tensor z,x) \\
    \cong & \C(a,x.c) \\
    = & \Mell_\X\C(a,c)(x)\,,
  \end{IEEEeqnarray*}
  where the arrow is induced by the \Mellies composition $\C(a,y.b) \times \C(b,z.c) \to \C(a,(y\tensor z).c)$.

  The identity transformation
  \[
    \C(I,x) \to \C(a,x.a)
    \]
  is the one sending a morphism $f\from I \to x$ to the composite
  \[
    a \xrightarrow{e_a}
    I.a \xrightarrow{f.a}
    x.a\,.
    \]
\end{definition}

\subsection{The category $\C/\X$}

We will mainly be concerned not with the \Mellies category itself, but with a closely related ordinary category.  
The usual method for turning a $\V$-enriched category into an ordinary category is via base change along a monoidal functor $\V \to \Set$: for example, any $\V$-enriched category has an \emph{underlying ordinary category}, obtained via base change along the functor $\V(I, \blank)$.  
For example, if $a$ and $b$ are objects of the base category $\C$, then the set of morphisms in the underlying ordinary category of the \Mellies category is the set of natural transformations
\[
  \C(I,x) \to \C(a,x.b)\,,
  \]
which by the Yoneda lemma is the same as the set $\C(a,I.b)$.  
In other words, this underlying ordinary category is precisely the Kleisli category for the monad on $\C$ given by the composite
\[
  1 \xrightarrow{I}
  \X \xrightarrow{\blank.\blank}
  \End[\C]\,;
  \]
in other words, the monad on $\C$ given by $Ma = I.a$.

This is not very useful for us, since it ignores most of the action and does not give us any new theory beyond the basic theory of monads and Kleisli categories.  
We want a monoidal functor $[\M,\Set]\to\M$ that will preserve more of the structure.

Let us assume for now that $\X$ is a small category.  
Then we have a functor
\begin{IEEEeqnarray*}{cCc}
  [\X,\Set] & \to & \Set \\
  F & \mapsto & \colim_{x\from \X} F(x)
\end{IEEEeqnarray*}
given by the colimit in $\Set$.

Moreover, this functor is lax monoidal, via the morphisms
\begin{IEEEeqnarray*}{Cl}
  & \left(\int^y F(y)\right)\times \left(\int^z G(z)\right) \\
  \to & \int^{y,z} F(y) \times G(z) \\
  \to & \int^{y,z} F(y) \times G(z) \times \X(y \tensor z,x) \\
  = & \int^x (F\tensor_{\text{Day}} G)(x)
\end{IEEEeqnarray*}
(where the second morphism sends picks out the inhabitant $\inj_{y\tensor z}(\id_{y\tensor z})$ of $\colim_{x\from \X}\X(y\tensor z,x)$)
and
\begin{IEEEeqnarray*}{cCc}
  1 & \to & \colim_{x\from \X} \X(I,x) \\
  () & \mapsto & \inj_I(\id_I)\,.
\end{IEEEeqnarray*}

Rather than pursue this line of argument to its conclusion, though, we choose to define the base-changed category directly.

\begin{definition}
  Let a monoidal category $\X$ act on a category $\C$ via a lax action.  
  Then we define a new category $\C/\X$ where
  \begin{itemize}
    \item the objects are the objects of $\C$,
    \item given objects $a,b$ of $\C$, the set of morphisms $a \to b$ is given by the colimit
      \[
        \colim_{x\from \X} \C(a,x.b)\,;
        \]
      i.e., a morphism in $\C/\X$ from $a$ to $b$ is an equivalence class of \Mellies morphisms
      \[
        a \to x.b
        \]
      in $\C$, where $x$ ranges over the objects of $\X$, and where the equivalence relation on morphisms is generated by identifying two morphisms $f\from a \to x.b$, $g \from a \to y.b$ if there is a morphism $h\from x\to y$ in $\X$ such that the following diagram commutes (we say that $h$ \emph{mediates} between $f$ and $g$);
      \[
        \begin{tikzcd}
          a \arrow[r, "f"] \arrow[dr, "g"']
            & x.b \arrow[d, "h.b"] \\
          %
            & y.b
        \end{tikzcd}
        \]
    \item composition of morphisms is via the \Mellies composition of Definition \ref{DefMelliesComposition} and
    \item the identity $a\to a$ is given by the equivalence class corresponding to the morphism
      \[
        e_a \from a \to I.a
        \]
      in $\C$.
  \end{itemize}
  \label{DefCX}
\end{definition}

\begin{remark}
  We will not in general assume that $\X$ is a small category, as we do above, but we will assume that the colimits in Definition \ref{DefCX} do exist in $\Set$.  
  If $\X$ is a small category, then they are small colimits so they exist automatically.
  If the colimits do not exist, then we get a category that is not locally small.
\end{remark}

\begin{proposition}
  $\C/\X$ is a well defined category.
\end{proposition}
\begin{proof}
  Let us first check that \Mellies composition is well defined with respect to our equivalence relation.  
  Suppose that
  \begin{gather*}
    f \from a \to x.b \\
    f' \from a \to x'.b \\
    g \from b \to y.c \\
    g' \from b \to y'.c
  \end{gather*}
  are \Mellies morphisms, and that there are morphisms $h \from x \to x'$, $k \from y \to y'$ in $\X$ such that the following diagrams commute.
  \begin{mathpar}
    \begin{tikzcd}
      a \arrow[r, "f"] \arrow[dr, "f'"']
        & x.b \arrow[d, "h.b"] \\
      %
        & x'.b
    \end{tikzcd}
    \and
    \begin{tikzcd}
      b \arrow[r, "g"] \arrow[dr, "g'"']
        & y.c \arrow[d, "k.c"] \\
      %
        & y'.c
    \end{tikzcd}
  \end{mathpar}
  Then we have the following commutative diagram, since $m$ is a natural transformation.
  \[
    \begin{tikzcd}
      a \arrow[r, "f"] \arrow[dr, "f'"']
        & x.b \arrow[r, "x.g"] \arrow[dr, "h.g" description] \arrow[d, "h.b" description]
          & x.y.c \arrow[r, "{m_{x,y,c}}"] \arrow[d, "h.y.c" description] \arrow[dd, bend left=50, "h.k.c"]
            & (x \tensor y).c \arrow[dd, "(h\tensor k).c"] \\
      %
        & x'.b \arrow[r, "x'.g" description] \arrow[dr, "x'.g'"']
          & x'.y.c \arrow[d, "x'.k.c" description]
            & \\
      %
        &
          & x'.y'.c \arrow[r, "{m_{x',y',c}}"]
            & (x' \tensor y').c
    \end{tikzcd}
    \]
  This proves that the \Mellies composition of $f$ and $g$ is equivalent to the \Mellies composition of $f'$ and $g'$.

  We should check that \Mellies composition is associative with respect to our equivalence relation.  
  Let $f \from a \to x.b$, $g\from b \to y.c$, $h \from c \to z.d$ be \Mellies morphisms.  
  Then we have the following commutative diagram.
  \[
    \begin{tikzcd}
      a \arrow[d, "f"' yshift=3pt] \arrow[d, dashed, thick]
        &
          &
            & \\
      x.b \arrow[d, "x.g"' yshift=3pt] \arrow[d, dashed, thick]
        &
          &
            & \\
      x.y.c \arrow[r, "x.y.h", thick, dashed] \arrow[d, "{m_{x,y,c}}"']
        & x.y.z.d \arrow[r, "x.m_{y,z,d}", thick, dashed] \arrow[d, "m_{x,y,z.d}"', dotted]
          & x.(y\tensor z).d \arrow[r, "m_{x,y\tensor z,d}", thick, dashed]
            & (x \tensor (y \tensor z)) . a \\
      (x \tensor y).c \arrow[r, "(x\tensor y).h"]
        & (x\tensor y).z.d \arrow[r, "m_{x\tensor y,z,a}"]
          & ((x\tensor y)\tensor z) . a \arrow[ur, "\assoc_{x,y,z}.d"', dotted]
            &
    \end{tikzcd}
    \]
  Here, the pentagon at the right is one of our conditions for a lax action, while the left-hand square commutes because $m$ is a natural transformation.  
  The composite given by the thick dashed lines is the \Mellies composition $f;(g;h)$, while that given by thin lines is the \Mellies composition $(f;g);h$.  
  The arrow $\assoc_{x,y,z}$ in $\X$ then mediates between these morphisms, so they are equivalent.

  Lastly, we need to check that the identity we have defined is indeed an identity for the composition.  
  The following diagrams show us that the morphism $\lunit_x$ in $\X$ mediates between a \Mellies morphism $f\from a \to x.b$ and the \Mellies composite $e_a;f$, and that the morphism $\runit_x$ in $\X$ mediates between $f$ and the \Mellies composite $f;e_b$.
  \begin{mathpar}
    \begin{tikzcd}
      a \arrow[r, "f"] \arrow[d, "e_a"']
        & x.b \arrow[d, "e_{x.b}"'] \arrow[dr, "\lunit_x.b"]
          & \\
      I.a \arrow[r, "I.f"]
        & I.x.b \arrow[r, "{m_{I,x,b}}" xshift=-3pt]
          & (I\tensor x).b
    \end{tikzcd}
    \and
    \begin{tikzcd}
      a \arrow[r, "f"]
        & x.b \arrow[r, "x.e_b"] \arrow[dr, "\runit_x.b"']
          & x.I.b \arrow[d, "{m_{x,I,b}}"] \\
      %
        &
          & (x\tensor I).b
    \end{tikzcd}
    \and
    \qedhere
  \end{mathpar}
\end{proof}

\begin{remark}
  This generalizes the Kleisli category of a monad.  
  Indeed, if $M$ is a monad on $\C$, then we may consider $M$ as a lax action of the unit category on $\C$.
  Then composition of morphisms $f \from a \to I.b$, $g \from b \to I.c$ in the category $\C/1$ is given by
  \[
    a \xrightarrow{f}
    I.b \xrightarrow{I.g}
    I.I.c \xrightarrow{m_{I,I,c}}
    I.c\,.
    \]
  Identifying $I.\blank$ with $M$, we see that this is precisely the definition of composition in the Kleisli category for $M$ (and the identity is the same thing too).  
  Since the unit category has only an identity morphism, the equivalence relation on morphisms in $\C/1$ is discrete, which is why we do not need to mention it in this context.
\end{remark}

There is an identity-on-objects functor $J \from \C \to \C/\X$ given by sending a morphism $f \from a \to b$ to the \Mellies morphism
\[
  a \xrightarrow{f}
  b \xrightarrow{e_b}
  I.b\,.
  \]
It is easy to show that this is a functor, and we will prove this in a more general context in Proposition \ref{PropGrotLaxLimit}.

A special role will be played by the identity morphisms
\[
  \id_{x.a} \from x.a \to x.a\,,
  \]
considered as \Mellies morphisms $x.a \to a$.  
We will see later that these are the components of a natural transformation $\phi_{x,a}\from x.a \to a$ in $\C/\X$, generalizing the natural transformation $\phi_a \from Ma \to a$ in the Kleisli category for a monad $M$ (see Proposition \ref{pKleisli}).

We will be using the following `factorization result'.  
If $f \from a \to x.b$ is a morphism in $\C$ then the corresponding \Mellies morphism $a \to b$ may be written as the following composite in $\C/\X$.
\[
  a \xrightarrow{Jf}
  x.b \xrightarrow{\phi_{x,b}}
  b\,.
  \]
Indeed, if we compute this composite in $\C$, then we get
\[
  a \xrightarrow{f}
  x.b \xrightarrow{e_{x.b}}
  I.x.b \xrightarrow{\id}
  I.x.b \xrightarrow{m_{I,x,b}}
  (I\tensor x).b\,,
  \]
which is equivalent to $f$ in $\C/\X$, because $e_{x.b};m_{I,x,b}=\lunit_x.b$, so $\lunit_x$ mediates between this morphism and $f$.

\subsection{Lax $2$-colimits}

In the previous section, we approached the category $\C/\X$ via the \Mellies category.  
In this section, we will show that $\C/\X$ has important properties in its own right: namely that it is a certain lax $2$-colimit in $\Cat$.  
We will briefly return to the \Mellies category in Section \ref{SecPromonads}, when we will show why it is a natural idea to consider an $[\X,\Set]$-enriched category.

\begin{definition}[\cite{StreetTwoConstructions}]
  Let $\C,\D$ be bicategories.  
  Then a \emph{lax functor} $F\from\C \to \D$ is given by
  \begin{itemize}
    \item a map $F$ from the objects of $\C$ to the objects of $\D$,
    \item for each pair $a,b$ of objects of $\C$, a functor $F$ from $\C(a,b)$ to $\D(F(a),F(b))$,
    \item for each triple $a,b,c$ of objects of $\C$, a transformation $m_{f,g}\from F(f);F(g) \to F(f;g)$ natural in $f\from a \to b$, $g\from b \to c$ and
    \item for each object $a$ of $\C$, a $2$-cell $e_a\from \id_{Fa} \Rightarrow F(\id_a)\from Fa \to Fa$
  \end{itemize}
  such that for all tuples $a,b,c,d$ of objects and all morphisms $f\from a \to b$, $g\from b \to c$, $h \from c \to d$, the following diagrams commute.
  \begin{mathpar}
    \begin{tikzcd}[column sep=60pt]
      (F(f);F(g));F(h) \arrow[r, "{\assoc_{F(f),F(g),F(h)}}"] \arrow[d, "{m_{f,g};F(h)}"']
        & F(f);(F(g);F(h)) \arrow[d, "{F(f);m_{g,h}}"] \\
      F(f;g);F(h) \arrow[d, "{m_{f;g,h}}"']
        & F(f);F(g;h) \arrow[d, "{m_{f,g;h}}"] \\
      F((f;g);h) \arrow[r, "{F(\assoc_{f,g,h})}"]
        & F(f;(g;h))
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ff \arrow[r, "\lunit_{Ff}"] \arrow[d, "F\lunit_f"']
        & \id_{Fa} ; Ff \arrow[d, "e_a;Ff"] \\
      F(\id_a;f)
        & F\id_a;Ff \arrow[l, "{m_{\id_a,f}}"']
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ff \arrow[r, "\runit_{Ff}"] \arrow[d, "F\runit_f"']
        & Ff ; \id_{Fb} \arrow[d, "Ff;e_b"] \\
      F(f;\id_b)
        & Ff;F\id_b \arrow[l, "{m_{f,\id_b}}"']
    \end{tikzcd}
  \end{mathpar}
\end{definition}
\begin{example}
  If $\C = \BB \X$, $\D = \BB \YY$ are the delooping bicategories of monoidal categories $\X, \YY$ -- i.e., $\X$ and $\YY$ considered as bicategories with a single object -- then a lax functor $\C \to \D$ is the same thing as a lax monoidal functor $\X \to \YY$.

  More generally, a lax functor $F\from \BB \X \to \D$ is the same as a lax monoidal functor from $\X$ to the monoidal category of $1$-cells $F(*) \to F(*)$, where $*$ is the unique object of $\BB\X$.  
  In particular, a lax functor $1\to \Cat$ is the same thing as a monad and a lax functor $\BB\X \to \Cat$ is the same thing as a parametric monad parameterized by $\X$.
\end{example}

\begin{definition}
  Let $F \from \C \to \D$ be a lax functor of bicategories.  
  Then an \emph{oplax cocone under $F$} is given by an object $d$ of $\D$, together with $1$-cells
  \[
    l_c \from F(c) \to d
    \]
  for each object $c$ of $\C$ and $2$-cells
  \[
    \mu_h \from F(h);l_{c'} \Rightarrow l_c \from F(c) \to d
    \]
  for each $1$-cell $h\from c \to c'$ in $\C$, such that for all $2$-cells $\phi\from h' \Rightarrow h \from c \to c'$ the diagram
  \[
    \begin{tikzcd}
      F(h');l_{c'} \arrow[r, "\mu_{h'}", Rightarrow] \arrow[d, "F(\phi);l_{c'}"', Rightarrow]
        & l_c \\
      F(h);l_{c'} \arrow[ur, "\mu_h"', Rightarrow]
        &
    \end{tikzcd}
    \]
  commutes, and such that for all $h\from c \to c'$, $h' \from c' \to c''$, the diagrams
  \begin{mathpar}
    \begin{tikzcd}[column sep=60pt]
      (F(h);F(h'));l_{c''} \arrow[r, "{\assoc_{F(h),F(h'),l_{c''}}}", Rightarrow] \arrow[d, "{m_{h,h'};l_{c''}}"', Rightarrow]
        & F(h);(F(h');l_{c''}) \arrow[r, "F(h);\mu_{h'}", Rightarrow] 
          & F(h);l_{c'} \arrow[d, "\mu_h", Rightarrow] \\
      F(h;h');l_{c''} \arrow[rr, "\mu_{h;h'}", Rightarrow]
        &
          & l_c
    \end{tikzcd}
    \and
    \begin{tikzcd}
      l_c \arrow[r, "\lunit_{l_c}", Rightarrow] \arrow[d, "\id_{l_c}"', Rightarrow]
        & \id_c;l_c \arrow[d, "e_c;l_c", Rightarrow] \\
      l_c
        & F(\id_c);l_c \arrow[l, "\mu_{\id}"', Rightarrow]
    \end{tikzcd}
  \end{mathpar}
  commute.
\end{definition}

\begin{definition}[\cite{Gepner}]
  Let $F \from \C \to \D$ be a lax functor of bicategories.  
  Then a \emph{lax colimit} of $F$ is an oplax cocone $(u,k,\nu)$ under $F$ such that if $(d,l,\mu)$ is any other oplax cocone then there is a unique $1$-cell $\hat{l} \from u \to d$ such that $k_c;\hat{l}=l_c$ for each object $c$ of $\C$ and such that $\nu_h\hat{l}=\mu_h$ for any $1$-cell $h\from c \to c'$ in $\C$.
\end{definition}

For the justification of the terminology we have used whereby a \emph{lax} limit is a limiting \emph{oplax} cocone, see \cite{nlab:2-limit}.

\begin{remark}
  The definition of a lax colimit is normally weaker than the one we have given, in that the equations $k_c;\hat l = l_c$ and $\nu_h\hat l = \mu_h$ are not required to hold exactly, but instead up to coherent isomorphism.  
  For the lax functors we are constructing, however, we will be able to construct lax colimits that make these equations hold exactly.
\end{remark}

\subsection{Lax natural transformations and functoriality of lax colimits}

\begin{definition}[\cite{BasicBicategories}]
  Let $F,G \from \C \to \D$ be lax functors of bicategories.  
  A \emph{oplax natural transformation} $\C\to \D$ is given by a family of $1$-cells
  \[
    t_c \from F(c) \to G(c)\,,
    \]
  for each object $c$ of $\C$, together with a family of $2$-cells
  \[
    \mu_h \from F(h);t_{c'} \Rightarrow t_c ; G(h) \from F(c) \to G(c')
    \]
  for each morphism $h\from c \to c'$ in $\C$, such that for all $2$-cells $\phi\from h' \to h\from c \to c'$ the diagram
  \[
    \begin{tikzcd}[arrows=Rightarrow]
      F(h');t_{c'} \arrow[r, "\mu_{h'}"] \arrow[d, "F(\phi);t_{c'}"']
        & t_c;G(h') \arrow[d, "T_c;F(\phi)"] \\
      F(h);t_{c'} \arrow[r, "\mu_h"]
        & t_c;G(h)
    \end{tikzcd}
    \]
  commutes, and such that for all $h\from c\to c'$, $h'\from c' \to c''$, the diagrams
  \begin{mathpar}
    \begin{tikzcd}[column sep=34pt, arrows=Rightarrow]
      (F(h);F(h'));t_{c''} \arrow[r, "\assoc"] \arrow[d, "{m^F_{h,h'};t_{c''}}"']
        & F(h);(F(h');t_{c''}) \arrow[r, "F(h);\mu_{h'}"]
          & F(h);(t_{c'};G(h')) \arrow[d, "\assoc"] \\
      F(h;h');t_{c''} \arrow[d, "\mu_{h;h'}"']
        &
          & (F(h);t_{c'});G(h') \arrow[d, "\mu_h;G(h')"] \\
      t_c;G(h;h')
        & t_c;(G(h);G(h')) \arrow[l, "{t_c;m^G_{h,h'}}"]
          & (t_c;G(h));G(h') \arrow[l, "\assoc"]
    \end{tikzcd}
    \and
    \begin{tikzcd}[arrows=Rightarrow]
      l_c \arrow[r, "\lunit_{l_c}"] \arrow[d, "\runit_{l_c}"']
        & \id_c;l_c \arrow[dd, "e^F_c;l_c"] \\
      l_c;\id_c \arrow[d, "l_c;e^G_c"']
        & \\
      l_c;G(\id_c)
        & F(\id_c);l_c \arrow[l, "\mu_{\id_c}"]
    \end{tikzcd}
  \end{mathpar}
  commute.
\end{definition}

As we would expect, the horizontal/vertical composition of two oplax natural transformations is also an oplax natural transformation, and there is an identity oplax natural transformation $F \Rightarrow F$ for any lax functor $F$ of bicategories.

\begin{example}
  An oplax natural transformation between lax functors $\BB\X \to \Cat$ is the same thing as an oplax morphism between the corresponding actions, as defined in Definition \ref{DefOplaxMorphismOfActions}.
\end{example}
\begin{example}
  If $F\from \C \to \D$ is a lax functor of bicategories, then an oplax cocone under $F$ with tip $d\from \D$ is the same thing as an oplax natural transformation $F \to *_d$, where $*_d$ is the constant functor taking the value $d$.
\end{example}

We can then get a functoriality result similar to the usual one for ordinary colimits.

\begin{proposition}
  Let $F,G \from \C \Rightarrow \D$ be lax functors and let $t \from F \Rightarrow G$ be an oplax natural transformation.  
  Suppose that $F$ and $G$ have lax colimits $\tilde{F}$ and $\tilde{G}$.  
  Then $t$ naturally gives rise to a lax functor $\tilde{F} \to \tilde{G}$ in a way that respects composition and identity of lax natural transformations.
  \label{PropFunctorialityOfLaxColimits}
\end{proposition}
\begin{proof}
  Composing the limiting oplax cocone $k^G\from G \to *_{\tilde{G}}$ with $t$ gives us an oplax natural transformation $F \to *_{\tilde{G}}$ and hence a unique lax functor $(t;k^G)\hat{}\from \tilde{F} \to \tilde{G}$ such that $k^F_c;(t;k^G)\hat{}=t_c;k^G_c$ and $\nu^F_h(t;k^G)\hat{}=\nu^G_h$ for all objects $c$ and morphisms $h$ in $\C$.

  Preservation of composition and identities is via the usual technique: if we have oplax natural transformations $t\from F \Rightarrow G$ and $t' \from G \Rightarrow H$, then the composite of the induced lax functors $\tilde{F} \to \tilde{G}$ and $\tilde{G}\to \tilde{H}$ satisfies the same property that uniquely defines the lax functor $\tilde{F} \to \tilde{H}$ induced from the composite of $t$ and $t'$.
\end{proof}

Another similar functoriality result tells us what happens to lax colimits when we precompose with a lax functor.

\begin{proposition}
  Let $F \from \C \to \D$, $G \from \D \to \E$ be lax functors.  
  Suppose that lax colimits exist for $G$ and for $F;G$.  
  Then we get a natural lax functor $\hat F$ from the lax colimit of $F;G$ to the lax colimit of $G$ such that for all objects $c$ and all morphisms $h$ in $\C$ we have
  \begin{mathpar}
    k^{F;G}_c;\hat{F} = k^g_{Fc}
    \and
    \nu^{F;G}_h \hat{F} = \nu^G_{Fh}\,,
  \end{mathpar}
  where $(k^{F;G},\nu^{F;G})$ is the limiting cocone for the lax colimit of $F;G$ and $(k^G,\nu^G)$ is the limiting cocone for the lax colimit of $G$.
  \label{PropHorizFunctorialityOfLaxColimits}
\end{proposition}
\begin{proof}
  Composing the limiting cocone $(k^G_d,\nu^G_k)$ for the lax colimit of $G$ with $F$ gives us an oplax cocone $(k^G_{Fc},\nu^G_{Fh})$ under $F;G$, inducing a functor from the lax colimit of $F;G$ to the lax colimit of $G$ that satisfies the required properties.
\end{proof}

\subsection{Lax $2$-colimits in $\Cat$}

Let $\C$ be a bicategory, and let $F\from \C \to \Cat$ be a bifunctor.

\begin{definition}[\cite{FibrationsInBicategories}]
  The \emph{Grothendieck construction} associates to the bifunctor $F$ a bicategory $\int F$, where
  \begin{itemize}
    \item the objects are pairs $(a, m)$, where $a$ is an object of $\C$ and $m$ an object of $F(a)$,
    \item the $1$-cells $(a, m) \to (b, n)$ are pairs $(h, f)$, where $h$ is a morphism $b \to a$ and $f$ is a morphism $m \to F(h)(n)$ and
    \item the $2$-cells $(h, f) \Rightarrow (k, g) \from (a,m) \to (b,n)$ are $2$-cells $\phi\from h \Rightarrow k$ in $\C$ that make the following diagram commute.
      \[
        \begin{tikzcd}
          m \arrow[r, "f"] \arrow[dr, "g"']
            & F(h)(n) \arrow[d, "(F\phi)_n"] \\
          %
            & F(k)(n)
        \end{tikzcd}
        \]
  \end{itemize}
  The identity $1$-cell $(a,m)\to(a,m)$ is given by $\left(\id_a,m \xrightarrow{(e_a)_m} F(\id)(m)\right)$.
  The composite of a $1$-cell $(h,f)\from (a,m) \to (b,n)$ with a $1$-cell $(k,g)\from (b,n) \to (c,p)$ is the pair $(k;h,f*g)$, where $f*g$ is the following composite.
  \[
    m \xrightarrow{f}
    F(h)(n) \xrightarrow{F(h)(g)}
    F(h)(F(k)(n)) \xrightarrow{m_{h,k}}
    F(k;h)(n)
    \]
\end{definition}
\begin{remark}
  For the Grothendieck construction see \cite[VI.8]{SGA1} and \cite[B1.3.1]{Elephant} -- in the original formulation, the category $F$ is a pseudofunctor $\C \to \Cat$ (i.e., a lax functor where the coherences $m$ and $e$ are isomorphisms), where $\C$ is an ordinary category -- then $\int F$ is an ordinary category.
  For the version where $\C$ is an arbitrary bicategory (and $\int F$ is a bicategory), see \cite{FibrationsInBicategories}.

  There are many different variations of this construction, where various combinations of arrows are reversed.  
  We have chosen the variation that suits our needs.
\end{remark}

\begin{definition}
  Given a bicategory $\C$, we write $\pi_*\C$ for the ordinary category whose objects are the objects of $\C$ and where the morphisms $a\to b$ are the connected components of the $1$-cells $a\to b$ in $\C$: i.e., equivalence classes of $1$-cells $a\to b$ under the equivalence relation generated by relating $f\from a \to b$ to $g \from a \to b$ if there is a $2$-cell $\phi \from f \to g$.
\end{definition}

\begin{proposition}[{\cite[\sec 3]{nlab:2-limit}}]
  Let $\C$ be a bicategory and let $F\from \C \to \Cat$ be a lax functor.  
  Then $\pi_*\int F$ is the lax colimit of $F$.
  \label{PropGrotLaxLimit}
\end{proposition}
\begin{proof}
  First, we define the lax cocone under $F$ with tip $\pi_*\int F$.
  Given an object $a$ of $\C$, we have a functor $k_a \from F(a) \to \pi_*\int F$ given by
  \begin{mathpar}
    k_a(m) = (a,m)
    \and
    k_a\left(m \xrightarrow{f} n\right) = \left(\id_a,m\xrightarrow{f}n\xrightarrow{(e_a)_n} F(\id)(n)\right)\,.
  \end{mathpar}
  We should check that this is indeed a functor; clearly it preserves the identity, so we need to check that it preserves composition.  
  Let $m\xrightarrow{f}n\xrightarrow{g}p$ be morphisms in $F(a)$.  
  We need to show that $k_a(f);k_a(g) = k_a(f;g)$ in $\pi_*\int F$, for which it suffices to exhibit a $2$-cell in $\int F$ mediating between these two $1$-cells, and indeed such a $2$-cell is given by $\lunit_{\id_a}\from \id_a \to \id_a;\id_a$ (see Figure \ref{FigKaFG=KaFKaG}).
  \begin{figure}
    \[
      \begin{tikzcd}[column sep=45pt]
        m \arrow[r, thick, dashed, "f"] \arrow[r]
          & n \arrow[r, thick, dashed, "(e_a)_n"] \arrow[d, "g"']
            & F(\id_a)(n) \arrow[d, thick, dashed, "F(\id_a)(g)"]
              & \\
        %
          & p \arrow[r, "(e_a)_p"]
            & F(\id_a)(p) \arrow[r, thick, dashed, "F(\id_a)(e_p)" xshift=-3pt] \arrow[dr, dotted, "F(\lunit_{\id_a})_p"']
              & F(\id_a)((F(\id_a)(p))) \arrow[d, thick, dashed, "{m_{\id_a,\id_a}}"] \\
        %
          &
            &
              & F(\id_a,\id_a)(p)
      \end{tikzcd}
      \]
    \caption[The composite $k_a(f);k_a(g)$ is equal to $k_a(f;g)$ in $\pi_*\int F$.]{The square commutes because $(e_a)$ is a natural transformation, while commutativity of the triangle is one of the conditions for a lax functor.  
The composite $k_a(f);k_a(g)$ is given by the pair $\left(\id_a;\id_a, {\begin{tikzcd}[ampersand replacement=\&]m \arrow[r, thick, dashed] \& F(\id_a,\id_a)(p)\end{tikzcd}}\right)$ (thick dashed arrows), while $k_a(f;g)$ is given by $\left(\id_a,m \to F(\id_a)(p)\right)$ (normal arrows). The $2$-cell $\lunit_{\id_a}\from \id_a\to\id_a$ from $\int F$ mediates between them (dotted arrow).}
      \label{FigKaFG=KaFKaG}
  \end{figure}

  Next, if $h\from a \to a'$ is a morphism in $\C$, then we define a natural transformation
  \[
    \nu_h \from F(h);k_{a'} \Rightarrow k_a
    \]
  by
  \[
    (\nu_h)_m = (h, \id_{F(h)(m)}) \from (a',F(h)(m)) \to (a,m)\,.
    \]
  We want to show that this is a natural transformation; i.e., that for any morphism $f \from m \to n$ in $F(a)$, the following diagram commutes.
  \[
    \begin{tikzcd}
      k_{a'}(F(h)(m)) \arrow[r, "(\nu_h)_m"] \arrow[d, "k_{a'}(F(h)(f))"']
        & k_a(m) \arrow[d, "k_a(f)"] \\
      k_{a'}(F(h)(n)) \arrow[r, "(\nu_h)_n"]
        & k_a(n)
    \end{tikzcd}
    \]
  Here, the top right composite is given by
  \[
    F(h)(m) \xrightarrow{F(h)(f)}
    F(h)(n) \xrightarrow{F(h)((e_{a})_n)}
    F(h)(F(\id_a)(n)) \xrightarrow{m_{h,\id_a}}
    F(h;\id_a)(n)\,,
    \]
  which is related to $F(h)(f)$ via $\runit_h$, while the bottom left composite is given by
  \[
    F(h)(m) \xrightarrow{(Fh)f}
    F(h)(n) \xrightarrow{(e_{a'})_{(Fh)f}}
    F(\id_{a'})(F(h)(n)) \xrightarrow{m_{\id_{a'},h}}
    F(\id_{a'};F(h))(n)\,,
    \]
  which is related to $F(h)(f)$ via $\lunit_h$.

  We now need to show that the appropriate diagrams commute to ensure that $\left(\pi_*\int F,k,\nu\right)$ is a lax cocone under $F$.
  For the first diagram, we must show that the following commutes for any $2$-cell $\phi\from h' \Rightarrow h\from a \to a'$ and any object $m$ of $F(a)$.
  \[
    \begin{tikzcd}
      k_{a'}(F(h')(m)) \arrow[r, "(\nu_{h'})_m"] \arrow[d, "k_{a'}((F\phi)_m)"']
        & k_a(m) \\
      k_{a'}(F(h)(m)) \arrow[ur, "(\nu_h)_m"']
        &
    \end{tikzcd}
    \]
  Since the arrow along the top is given by the identity on $F(h')(m)$, it will suffice to show that the arrow along the bottom is of the form $F(\psi)_m$, for some $2$-cell $\psi$ in $\C$, and is therefore equal to the identity in $\pi_*\int F$.
  Indeed, writing this composite out in full, we get
  \[
    F(h')(m) \xrightarrow{(F\phi)_m}
    F(h)(m) \xrightarrow{(e_{a'})_{F(h)(m)}}
    F(\id)(F(h)(n)) \xrightarrow{m_{\id,h}}
    F(\id;h)(n)\,.
    \]
  By the conditions on a lax functor, the composite of the last two morphisms is $F(\lunit_h)_m$, and so the whole thing is equal to $F(\phi;\lunit_h)_m$.

  Lastly, we need to show that the following diagrams commute for any $1$-cells $h\from a \to a'$, $h'\from a' \to a''$ and any object $m$ of $F(a)$.
  \begin{mathpar}
    \begin{tikzcd}[column sep=50pt]
      k_{a''}(F(h')(F(h)(m))) \arrow[r, "(\nu_h)_{F(h)(m)}"] \arrow[d, "{k_{a''}((m_{h,h'})_m)}"']
        & k_{a'}(F(h)(m)) \arrow[d, "(\nu_{h})_m"] \\
      k_{a''}(F(h;h')(m)) \arrow[r, "(\nu_{h;h'})_m"]
        & k_a(m)
    \end{tikzcd}
    \and
    \begin{tikzcd}[column sep=40pt]
      k_a(m) \arrow[r, "k_a((e_a)_m)"] \arrow[dr, "\id_{k_a(m)}"']
        & k_a(F(\id)(m)) \arrow[d, "(\nu_{\id})_m"] \\
      %
        & k_a(m)
    \end{tikzcd}
  \end{mathpar}
  This time, we can compute that both composites in the first diagram are equal to
  \[
    F(h')(F(h)(m)) \xrightarrow{m_{h,h'}} F(h;h')(m)\,,
    \]
  while in the second diagram the top left composite is equal to
  \[
    m \xrightarrow{(e_a)_m}
    F(\id)(m) \xrightarrow{(e_a)_{F(\id)(m)}}
    F(\id)(F(\id)(m)) \xrightarrow{\mu_{\id,\id}}
    F(\id;\id)(m)\,,
    \]
  and the diagonal arrow is given by
  \[
    m \xrightarrow{(\e_a)_m}
    F(\id)(m)\,.
    \]
  These $1$-cells in $\int F$ are related by $F(\lunit_m)$, so they correspond to the same morphism in $\pi_*\int F$.

  This completes the definition of the universal cocone under $\pi_*\int F$.

  Now, suppose that $(\D,l,\mu)$ is another lax cocone under $F$.  
  We define a functor $\hat{l}$ from $\pi_*\int F$ to $\D$ by
  \begin{mathpar}
    \hat{l}(a,m) = l_a(m)
    \and
    \hat{l}\left((a,m) \xrightarrow{(h,f)} (b,n)\right) =
    l_a(m) \xrightarrow{l_a(f)}
    l_a(F(h)(n)) \xrightarrow{(\mu_h)_n}
    l_b(n)\,.
  \end{mathpar}
  We need to show that $\hat{l}$ is a functor.  
  First, observe that it sends the identity on $(a,m)$ to the composite
  \[
    l_a(m) \xrightarrow{l_a((e_a)_m)}
    l_a(F(\id)(m)) \xrightarrow{(\mu_{\id})_m}
    l_a(m)\,,
    \]
  which is equal to the identity on $l_a(m)$ since $l$ is a cocone under $F$.
  Now suppose we have morphisms
  \[
    (a,m) \xrightarrow{(h,f)}
    (b,n) \xrightarrow{(k,g)}
    (c,p)\,.
    \]
  Using the formula above for the composition of morphisms in the Grothendieck construction, we see that $\hat{l}((h,f);(k;g))$ is given by the thick dotted composite in Figure \ref{FigLHatFunctor}, while $\hat{l}(h,f);\hat{l}(k,g)$ is given by the thin composite.  
  Therefore, these two are equal.
  \begin{figure}
    \[
      \begin{tikzcd}[column sep=40pt]
        l_a(m) \arrow[r, "l_a(f)"] \arrow[r, thick, dashed]
          & l_a(F(h)(n)) \arrow[r, "(\mu_h)_n"] \arrow[d, "l_a(F(h)(g))"', thick, dashed]
            & l_b(n) \arrow[d, "l_b(g)"] \\
        %
          & l_a(F(h)(F(k)(p))) \arrow[r, "(\mu_h)_{F(k)(p)}", dotted] \arrow[d, "l_a((m_{k,h})_p)"', thick, dashed]
            & l_b(F(k)(p)) \arrow[d, "(\mu_k)_p"] \\
        %
          & l_a(F(k;h)(p)) \arrow[r, "(\mu_{k;h})_p", thick, dashed]
            & l_c(p)
      \end{tikzcd}
      \]
    \caption{Proof that $\hat{l}$ respects composition.  
    The thick dotted line represents $\hat{l}((h,f);(k,g))$, while the thin solid line represents $\hat{l}(h,f);\hat{l}(k,g)$.  
    The top square commutes because $\mu_h$ is a natural transformation, while the bottom is one of the conditions on a cocone.}
    \label{FigLHatFunctor}
  \end{figure}

  Therefore, $\hat{l}$ is a functor.  
  Moreover, if $a$ is an object of $\C$ and $m$ and object of $F(a)$, we have $\hat{l}(k_a(m))=\hat{l}(a,m)=l_a(m)$, and if $f\from m \to n$ is a morphism in $F(a)$, then $\hat{l}(k_a(f))$ is given by the composite
  \[
    l_a(m) \xrightarrow{l_a(f)}
    l_a(n) \xrightarrow{l_a((e_a)_n)}
    l_a(F(\id)(n)) \xrightarrow{(\mu_{\id})_n}
    l_a(n)\,,
    \]
  which is equal to $l_a(f)$ by the cocone condition on $\mu$.
  Therefore, $k_a;\hat{l}=l_a$ for each object $a$ of $\C$.

  Lastly, if $h\from a \to b$ is a morphism in $\C$, then $\hat{l}((\nu_h)_m)=\hat{l}(h,\id_{F(h)(m)}) = (\mu_h)_m$, and so $\nu_hl = \mu_h$.  
  This completes the existence part of the proof.

  For uniqueness, suppose that $j$ is another functor $\pi_*\int F \to \D$ such that $k_a;j=l_a$ and $\nu_hj=\mu_h$ for each object $a$ of $\C$ and each morphism $h\from a \to b$ in $\C$.

  Let $(a,m)$ be an object of $\pi_*\int F$.  
  Then $j(a,m)=j(k_a(m))=l_a(m)=\hat{l}(a,m)$.

  Now let $(h,f)\from (a,m) \to (b,n)$ be a morphism in $\pi_*\int F$.  
  We claim that we may decompose $(h,f)$ as the composite
  \[
    \begin{tikzcd}
      (a,m) \arrow[d, "k_a(f)"'] \arrow[dr, "{(h,f)}"]
        & \\
      (a,F(h)(n)) \arrow[r, "(\nu_h)_n"']
        & (b,n)
    \end{tikzcd}\,.
    \]
  Indeed, if we work out what that composite is, then we get
  \[
    m \xrightarrow{f}
    F(h)(n) \xrightarrow{(e_a)_n}
    F(\id)(F(h)(n)) \xrightarrow{(m_{\id,h})_n}
    F(\id;h)(n)\,,
    \]
  which is related to $(h,f)$ in $\int F$ by the $2$-cell $\lunit_h$ (since $F$ is a lax functor), and is therefore equal to $(h,f)$ in $\pi_*\int F$.

  We therefore have
  \[
    j(h,f) = j(k_a(f);(\nu_h)_n) = j(k_a(f));j((\nu_h)_n) = l_a(f);(\mu_h)_n = \hat{l}(h, f)\,,
    \]
  and therefore $j=\hat{l}$.  
\end{proof}

\subsection{Examples of lax $2$-colimits in $\Cat$}

Suppose that $M$ is a monad on a category $\C$, considered as a lax functor
\[
  F\from 1\to \Cat
  \]
such that $F(*)=\C$.

If we apply the Grothendieck construction to $F$, then the category we get has pairs $(*,a)$ for objects, where $a$ ranges over the objects of $\C$, and the morphisms from $(*,a)$ to $(*,b)$ are morphisms $a \to F(\id)(b)$ in $\C$, where $F(\id)=M$.  
In other words, $\int F$ is precisely the Kleisli category for $M$.
In this case, Proposition \ref{PropGrotLaxLimit} reduces to Proposition \ref{pKleisli}.

More generally, if $\X$ is a monoidal category and $F\from \BB \X \to \Cat$ is a lax functor, corresponding to a lax action of $\X$ upon $\C = F(*)$, then it is easy to see that $\pi_*\int F$ is isomorphic to the category $\C/\X$ that we defined earlier.  
Indeed, in both cases the objects may be identified with the objects of $\C$, and the morphisms from an object $a$ to an object $b$ may be written as equivalence classes of morphisms $a \to x.b$ in $\C$ under the equivalence relation generated by relating $f\from a \to x.b$ to $g\from a \to y.b$ if there is a morphism $h\from x \to y$ in $\X$ such that $g=f;(h.b)$.

In this case, we can recast Proposition \ref{PropGrotLaxLimit} to get a result about $\C/\X$.

\begin{corollary}
  Let $\blank.\blank$ be an action of a monoidal category $\X$ on a category $\C$.  
  If we identify this action with a lax functor $F \from \BB \X \to \Cat$, then $\C/\X$ is the lax colimit of this functor.

  In other words, there is a functor $J\from \C \to \C/\X$ and a natural transformation
  \[
    \phi_{x,a}\from J(x.a) \to Ja
    \]
  making the following diagrams commute
  \begin{mathpar}
    \begin{tikzcd}
      J(x.y.a) \arrow[r, "{\phi_{x,y.a}}"] \arrow[d, "{J(m_{x,y,a})}"']
        & J(y.a) \arrow[d, "{\phi_{y,a}}"] \\
      J((x\tensor y).a) \arrow[r, "{\phi_{x\tensor y,a}}"]
        & Ja
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Ja \arrow[dr, "\id"] \arrow[d, "J(\lun_a)"']
        & \\
      J(I.a) \arrow[r, "{\phi_{I,a}}" xshift=-4pt]
       & Ja
    \end{tikzcd}\,,
  \end{mathpar}
  such that if $F\from \C \to \D$ is a functor and
  \[
    \psi_{x,a} \from F(x.a) \to Fa
    \]
   is a natural transformation making the following diagrams commute
  \begin{mathpar}
    \begin{tikzcd}
      F(x.y.a) \arrow[r, "{\psi_{x,y.a}}"] \arrow[d, "{F(m_{x,y,a})}"']
        & F(y.a) \arrow[d, "{\psi_{y,a}}"] \\
      F((x\tensor y).a) \arrow[r, "{\psi_{x\tensor y,a}}"]
        & Fa
    \end{tikzcd}
    \and
    \begin{tikzcd}
      Fa \arrow[dr, "\id"] \arrow[d, "F(\lun_a)"']
        & \\
      F(I.a) \arrow[r, "{\psi_{I,a}}" xshift=-4pt]
       & Fa
    \end{tikzcd}\,,
  \end{mathpar}
  then there is a unique functor $\hat{F}\from \C/\X\to \D$ such that $F=\hat{F}J$ and $\psi=\hat{F}\phi$.
  \label{CorTheConstructionUniversalProperty}
\end{corollary}

Corollary \ref{CorTheConstructionUniversalProperty} tells us that $\C/\X$ is generated as a category by the objects and morphisms in $\C$, together with the special morphisms making up the natural transformation $\phi_{x,a}\from x.a \to a$.

This is significant, because it tells us that the category $\C/\X$ always satisfies a `factorization result' akin to those in \cite{SamsonGuyIAActive} and \cite{mcCHFiniteND}: if $f \from a \to b$ is a morphism in $\C/\X$, given by some morphism $\tilde{f}\from a \to x.b$ in $\C$, then we may write $f$ as the composite
\[
  a \xrightarrow{J(\tilde{f})} x.b \xrightarrow{\phi_{x,b}} b
  \]
in $\C$.  
This means that if we have a definability result for the category $\C$ -- for example, that every compact morphism in $\C$ is definable in some language $\L$ -- then we can automatically get a definability result for the category $\C/\X$ -- for example, that every compact morphism in $\C/\X$ (i.e., every morphism $a\to b$ in $\C/\X$ that is given by a compact morphism $a \to x.b$ in $\C$) is definable in the language $\L + \Phi_{x,a}$, where $\Phi_{x,a}$ is a new family of primitives in the language whose denotations are given by the $\phi_{x,a}$.
This is the same purpose that we used Proposition \ref{pKleisli} for when proving Theorem \ref{TheKleisliFullAbstraction}.

\subsection{Finite products distribute over lax colimits in $\Cat$}

The next result mirrors the result for distributivity of finite products over arbitrary colimits in a Cartesian closed category (essentially because the functor $A \times \blank$ is a left adjoint, so preserves colimits).

\begin{proposition}
  Let $F \from \C \to \Cat$ be a lax functor of bicategories.  
  Let $\A$ be a category.
  Then the lax colimit of $\A \times F$ (defined by $(\A \times F)(c) = \A \times F(c)$ and $(\A \times F)(f) = (\id,f)$) is given by the product of $\A$ with the lax colimit of $F$.
  \label{PropGrotCommutesProducts}
\end{proposition}
\begin{proof}
  It is easiest to compute the colimit of $\A \times F$ directly using Proposition \ref{PropGrotLaxLimit}. 
  The objects are tuples $(c,(a,m))$, where $c$ is an object of $\C$, $a$ is an object of $a$ and $m$ is an object of $F(c)$.
  $1$-cells from $(c',(a',m'))$ to $(c,(a,m))$ are given by pairs $(h,(q,f))$, where $h$ is a morphism $c \to c'$ in $\C$, $f$ is a morphism $a' \to F(h)(a)$ in $F(a')$ and $q$ is a morphism $a'\to a$ in $\A$.
  Two $1$-cells $(h,(q,f))$ and $(h',(q',f'))$ from $(c',(a',m'))$ to $(c,(a,m))$ define equivalent morphisms if there is a $2$-cell $\phi\from h \Rightarrow h'$ such that $f;(F\phi)_m=f'$, and if $a'=a$.

  Meanwhile, the product of $\A$ with the lax colimit of $F$ has tuples $(a,(c,m))$ for objects, where $a$ is an object of $\A$, $c$ an object of $\C$ and $m$ an object of $F(c)$.
  $1$-cells $(a',(c',m')) \to (a,(c,m))$ are given by tuples $(q,(h,f))$, where $q$ is a morphism $a' \to a$, $h$ is a morphism $c \to c'$ and $f$ is a morphism $m' \to F(h)(m)$.
  Two $1$-cells $(q,(h,f))$ and $(q',(h',f'))$ from $(a',(c',m'))$ to $(a,(c,m))$ define equivalent morphisms if $a'=a$, and if there is a $2$-cell $\phi\from h\Rightarrow h'$ such that $f;(F\phi)_m=f'$. 
  These two categories are clearly isomorphic.
\end{proof}

\begin{corollary}
  Let $F\from \C\to\Cat$, $G\from \D \to \Cat$ be lax functors of bicategories.  
  Then
  \[
    \laxcolim_{c\from\C,d\from\D} F(c)\times G(d) \cong \laxcolim_{c\from \C} F(c) \times \laxcolim_{d\from\D} G(d)\,.
    \]
  \label{CorGrotBothSidesProductPreservation}
\end{corollary}
\begin{proof}
  By Proposition \ref{PropGrotCommutesProducts}, we have
  \begin{IEEEeqnarray*}{Cl}
    & \laxcolim_{c\from \C} F(c) \times \laxcolim_{d\from\D} G(d) \\
    \cong &
    \laxcolim_{c\from \C} (F(c) \times \laxcolim_{d\from\D} G(d)) \\
    \cong &
    \laxcolim_{c\from \C} \laxcolim_{d\from\D} (F(c)\times G(d)) \\
    \cong  &
    \laxcolim_{c\from\C,d\from\D} (F(c)\times G(d))\,.\qedhere
  \end{IEEEeqnarray*}
\end{proof}

In the particular case of a bifunctor out of $\BB\X$, for $\X$ a monoidal category, we get the following.

\begin{corollary}
  Suppose we have actions of a monoidal category $\X$ on a category $\C$ and of a monoidal category $\YY$ on a category $\D$.
  We get an action of $\X\times\YY$ on $\C\times \D$ by
  \[
    (x,y).(c,d) = (x.c,y.d)\,.
    \]
  Then
  \[
    (\C\times\D)/(\X\times\YY)\cong (\C/\X) \times (\D/\YY)\,.
    \]
  \label{CorQuotProductPreservation}
\end{corollary}
\begin{proof}
  Since the $\C/\X$ construction is a special case of a lax colimit in $\Cat$, this is a direct application of Corollary \ref{CorGrotBothSidesProductPreservation} where we are using the fact that $\BB(\X\times\YY)\cong \BB\X \times \BB\YY$.
\end{proof}

\subsection{Monoidal structure of $\C/\X$}

\begin{definition}
  Suppose that $\X$ is a symmetric monoidal category acting on a monoidal category $\C$, and suppose moreover that the underlying functor $\X\times\C \to \C$ is a lax monoidal functor.

  Then the functor $\X\times\X\times\C\to \C$ that sends $(x,y,a)$ to $x.y.a$ is lax monoidal.  
  Since $\X$ is symmetric monoidal, the tensor product $\blank\tensor\blank\from \X \times\X \to \X$ is a strong monoidal functor and so the functor $\X \times \X \times \C \to \C$ that sends $(x,y,a)$ to $(x\tensor y).a$ is lax monoidal.

  We say that the action of $\X$ on $\C$ is \emph{monoidal} if, in addition to the underlying functor $\X \times \C \to \C$ being monoidal, the natural transformations $m_{x,y,a}$ and $e_a$ are monoidal natural transformations.
  \label{DefMonoidalLaxAction}
\end{definition}

\begin{example}
  If $\X,\C$ are symmetric monoidal categories, where $\C$ is symmetric monoidal closed, and $j\from \X \to \C$ is an oplax symmetric monoidal functor, then the parametric reader monad action
  \[
    x.a = jx\implies a
    \]
  is a symmetric monoidal lax action of $\oppcat\X$ on $\C$.
\end{example}

\begin{remark}
  This generalizes the definition of a monad being \emph{monoidal}; i.e., when the underlying functor $\C \to \C$ is a monoidal functor and the multiplication and unit for the monad are monoidal natural transformations.  
  However, although a monoidal monad can be defined to be a monoid in the category of monoidal functors $\C \to \C$ and monoidal natural transformations between them, a monoidal parametric monad parameterized by a symmetric monoidal category $\X$ cannot be defined as a monoidal functor from $\X$ into this category.  
  Indeed, that would mean we had a natural transformation
  \[
    x.a \tensor x.b \to x.(a\tensor b)\,,
    \]
  whereas we want to specify that there should be a natural transformation
  \[
    x.a \tensor y.b \to (x\tensor y).(a\tensor b)\,.
    \]
\end{remark}

\begin{proposition}
  Suppose that $\X$ is a symmetric monoidal category, and that we have a symmetric monoidal lax action of $\X$ on another monoidal category $\C$.  
  Then $\C/\X$ inherits the structure of a monoidal category and the natural functor $J\from \C \to \C/\X$ is strict monoidal.
\end{proposition}
\begin{proof}
  By taking the product of the action with itself, we get an action of $\X\times\X$ on $\C\times\C$; i.e., the action given by $(x,y).(a,b)=(x.a,y.b)$.  
  Since $\X$ is symmetric monoidal, the tensor product functor $\X\times\X \to \X$ is strong monoidal, so by composing it with the action of $\X$ on $\C$ we get a lax action of $\X\times\X$ on $\C$; i.e., the action given by $(x,y).a = (x\tensor y).a$, with coherence $m_{(x,y),(x',y').a}$ given by
  \[
    (x\tensor y).(x'\tensor y').a \xrightarrow{m_{(x\tensor y),(x'\tensor y'),a}}
    ((x\tensor y)\tensor (x'\tensor y')).a \to
    ((x\tensor x')\tensor (y\tensor y')).a\,,
    \]
  where the last arrow is given by the unique symmetric monoidal isomorphism.

  We claim that the functor $\blank\tensor\blank\from \C\times\C\to\C$ and the monoidal coherence
  \[
    m_{x,y,a,b} \from x.a \tensor y.b \to (x\tensor y).(a\tensor b)
    \]
  of the monoidal functor $\blank.\blank\from \X \times \C \to \C$ give rise to an oplax morphism from the action of $\X\times\X$ on $\C\times\C$ to the action of $\X\times\X$ on $\C$.

  Indeed, the first diagram in Definition \ref{DefOplaxMorphismOfActions} in this case is given by
  \[
    \begin{tikzcd}
      (x.y.a)\tensor(x'.y'.a') \arrow[r, "{m_{x,x',y.a,y'.a'}}"] \arrow[d, "{m_{x,y,a}\tensor m_{x',y',a'}}"']
        & (x\tensor x').(y.a \tensor y'.a') \arrow[d, "{(x\tensor x').m_{y,y',a,a'}}"] \\
      ((x\tensor y).a)\tensor ((x'\tensor y').a') \arrow[d, "{m_{x\tensor y,x'\tensor y',a,a'}}"']
        & (x \tensor x').(y\tensor y').(a \tensor a') \arrow[d, "{m_{x\tensor x',y\tensor y',a\tensor a'}}"] \\
      ((x\tensor y)\tensor (x'\tensor y')).(a\tensor a') \arrow[r]
        & ((x \tensor x')\tensor (y \tensor y')) . (a \tensor a') \\
    \end{tikzcd}\,,
    \]
  which is precisely the diagram saying that $m$ is a monoidal natural transformation.  
  Similarly, the second diagram from Definition \ref{DefOplaxMorphismOfActions} is the same as the diagram saying that $e$ is a monoidal natural transformation.

  Therefore, by Proposition \ref{PropFunctorialityOfLaxColimits}, this lax morphism of actions gives rise to a functor
  \[
    (\C\times\C)/(\X\times\X) \to \C/(\X\times\X)\,.
    \]
  The lax monoidal functor $\X \times \X \to \X$ gives rise by Proposition \ref{PropHorizFunctorialityOfLaxColimits} to a functor $\C/(\X\times\X) \to \C/\X$, which we may compose with the functor above to give us a functor
  \[
    (\C\times\C)/(\X\times\X) \to \C/\X\,.
    \]
  Moreover, Corollary \ref{CorQuotProductPreservation} tells us that $(\C\times\C)/(\X\times\X)$ is isomorphic to $(\C/\X)\times(\C/\X)$, giving us our desired functor
  \[
    \blank\tensor\blank \from (\C/\X)\times(\C/\X) \to (\C/\X)\,.
    \]
  Moreover, the construction of this functor tells us that it commutes with the identity-on-objects functors out of the original categories:
  \[
    \begin{tikzcd}
      \C \times \C \arrow[r, "\blank\tensor\blank"] \arrow[d, "J\times J"]
        & \C \arrow[d, "J"] \\
      (\C/\X)\times (\C/\X) \arrow[r, "\blank\tensor\blank"]
        & \C/\X
    \end{tikzcd}\,,
    \]
  which means that the functor $J$ preserves the tensor product.
  This also means that we may lift the associators and unitors for the tensor product on $\C$ along the functor $J$ morphisms in $\C/\X$, and that these morphisms satisfy the appropriate coherence diagrams.
  It remains to show that they are still natural transformations in $\C/\X$, which we do in Figure \ref{FigAssocUnitorNaturalTransformations}.
  \begin{figure}
    \begin{mathpar}
      \begin{tikzcd}[column sep=100pt]
        (a'\tensor b')\tensor c' \arrow[r, "{\assoc_{a',b',c'}}"] \arrow[d, "(f\tensor g)\tensor h"']
          & a' \tensor (b'\tensor c') \arrow[d, "f\tensor(g\tensor h)"] \\
        (x.a \tensor y.b) \tensor z.c \arrow[r, "{\assoc_{x.a,y.b,z.c}}"] \arrow[d, "{m_{x,y,a,b}\tensor z.c}"']
          & x.a \tensor (y.b \tensor z.c) \arrow[d, "{x.a \tensor m_{y.b,z.c}}"] \\
        ((x\tensor y).(a\tensor b)) \tensor z.c \arrow[d, "{m_{x\tensor y,z,a\tensor b,c}}"']
          & x.a \tensor ((y\tensor z).(b\tensor c)) \arrow[d, "{m_{x,y\tensor z,a,b\tensor c}}"] \\
        ((x\tensor y)\tensor z).((a \tensor b)\tensor c) \arrow[r, "{\assoc_{x,y,z}.\assoc_{a,b,c}}"]
          & (x \tensor (y \tensor z)).(a \tensor (b \tensor c))
      \end{tikzcd}
      \and
      \begin{tikzcd}
        a' \arrow[r, "\lunit_{a'}"] \arrow[d, "f"']
          & I \tensor a \arrow[d, "I\tensor f"] \\
        x.a \arrow[r, "\lunit_{x.a}"] \arrow[d, "\lunit_x.\lunit_a"' description]
          & I\tensor (x.a) \arrow[d, "e\tensor x.a"] \\
        (I\tensor x).(I\tensor a)
          & (I.I) \tensor (x.a) \arrow[l, "{m_{I,x,I,a}}"']
      \end{tikzcd}
      \and
      \begin{tikzcd}
        a' \arrow[r, "\runit_{a'}"] \arrow[d, "f"']
          & a \tensor I \arrow[d, "f\tensor I"] \\
        x.a \arrow[r, "\runit_{x.a}"] \arrow[d, "\runit_x.\runit_a"' description]
          & (x.a)\tensor I \arrow[d, "x.a\tensor e"] \\
        (x\tensor I).(a\tensor I)
          & (x.a) \tensor (I.I) \arrow[l, "{m_{x,I,a,I}}"']
      \end{tikzcd}
    \end{mathpar}
    \caption[Proof that the associators and unitors in $\C/\X$ are indeed natural transformations.]{Proof that the associators and unitors in $\C/\X$ are indeed natural transformations.  
    Here, $f\from a'\to a$, $g\from b' \to b$, $h\from c'\to c$ are morphisms in $\C/\X$, considered as morphisms $a'\to x.a$, $b'\to y.b$, $c'\to z.c$ in $\C$.}
    \label{FigAssocUnitorNaturalTransformations}
  \end{figure}
\end{proof}

Having defined the monoidal structure on $\C/\X$ in a very formal way, let us unpack what it actually is.  
The tensor product on objects is defined exactly as in $\C$, while the tensor product of morphisms $f\from a' \to a$, $g \from b' \to b$ (considered as morphisms $f \from a' \to x.a$, $g\from b'\to y.b$ in $\C$) is given by the composite
\[
  a'\tensor b' \xrightarrow{f\tensor g}
  (x.a) \tensor (y.b) \xrightarrow{m_{x,y,a,b}}
  (x\tensor y).(a\tensor b)\,,
  \]
where the right hand arrow is the multiplicative coherence for the monoidal functor $\blank.\blank\from \X \times \C \to \C$.

The reason we need some kind of symmetry in $\X$ is for this to be a functor: indeed, suppose that we have morphisms $f' \from a'' \to a'$, $f \from a' \to a$, $g' \from b'' \to b'$ and $g \from b' \to b$ in $\C/\X$, considered as morphisms $f' \from a'' \to x'.a'$, $f \from a' \to x.a$, $g' \from b'' \to y'.b'$ and $g \from b' \to y'b$ in $\C$.  
Then $(f'\tensor g');(f\tensor g)$ is given by the composite
\begin{IEEEeqnarray*}{Cl}
  & a'' \tensor b'' \\
  \xrightarrow{\makebox[100pt]{$f'\tensor g'$}}
  & (x'.a') \tensor (y'.b') \\
  \xrightarrow{\makebox[100pt]{$m_{x',y',a',b'}$}}
  & (x'\tensor y').(a'\tensor b') \\
  \xrightarrow{\makebox[100pt]{$(x'\tensor y').(f\tensor g)$}}
  & (x'\tensor y').((x.a)\tensor (y.b)) \\
  \xrightarrow{\makebox[100pt]{$(x'\tensor y').m_{x,y,a,b}$}}
  & (x' \tensor y').(x\tensor y).(a\tensor b) \\
  \xrightarrow{\makebox[100pt]{$m_{x'\tensor y',x\tensor y,a\tensor b}$}}
  & ((x'\tensor y')\tensor (x\tensor y)).(a\tensor b)\,,
\end{IEEEeqnarray*}

while $(f';f)\tensor (g';g)$ is given by
\begin{IEEEeqnarray*}{Cl}
  & a'' \tensor b'' \\
  \xrightarrow{\makebox[100pt]{$f'\tensor g'$}}
  & (x'.a') \tensor (y'.b') \\
  \xrightarrow{\makebox[100pt]{$x'.f \tensor y'.g$}}
  & (x'.x.a) \tensor (y'.y.b) \\
  \xrightarrow{\makebox[100pt]{$m_{x',x,a} \tensor m_{y',y,b}$}}
  & ((x'\tensor x).a) \tensor ((y'\tensor y).b) \\
  \xrightarrow{\makebox[100pt]{$m_{x'\tensor x,y'\tensor y,a,b}$}}
  & ((x' \tensor x) \tensor (y' \tensor y)) \tensor (a \tensor b)\,.
\end{IEEEeqnarray*}

Since $\X$ is symmetric, and since the natural transformation $m_{x,y,a}$ is a monoidal natural transformation with respect to the monoidal functor structure on $x.y.a$ and $(x\tensor y).a$, the natural symmetric monoidal coherence
\[
  ((x'\tensor y')\tensor (x\tensor y)) \toisom ((x' \tensor x) \tensor (y' \tensor y))
  \]
mediates between these two composites, so they give us the same morphism in $\C/\X$.

\subsection{Symmetric monoidal structure of $\C/\X$}

\begin{definition}
  Let a symmetric monoidal category $\X$ act via a monoidal lax action on a monoidal category $\C$.  
  If $\C$ is symmetric monoidal, then we say that the action of $\X$ on $\C$ is \emph{symmetric monoidal} if the underlying functor $\X \times \C \to \C$ is a symmetric monoidal functor.
\end{definition}

\begin{example}
  If $j\from \X \to \C$ is a symmetric oplax monoidal functor, where $\C$ is symmetric monoidal closed, then the reader action of $\oppcat\X$ on $\C$ induced from $j$ is a symmetric monoidal lax action.
\end{example}

\begin{proposition}
  Let a symmetric monoidal category $\X$ act via a symmetric monoidal lax action on a symmetric monoidal category $\C$.  
  Then the category $\C/\X$ is symmetric monoidal.
\end{proposition}
\begin{proof}
  As with the associators and unitors, we can lift the symmetry isomorphisms from $\C$ on to $\C/\X$, and these isomorphisms will satisfy the appropriate coherence diagrams.

  We need only show that they are natural transformations in $\C/\X$.  
  Let $f\from a' \to a$, $g\from b' \to b$ be morphisms in $\C/\X$, considered as morphisms $f\from a' \to x.a$, $g\from b' \to y.b$ in $\C$.  
  Then we need show that the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=80pt]
      a'\tensor b' \arrow[r, "{\sym_{a',b'}}"] \arrow[d, "f\tensor g"']
        & b' \tensor a' \arrow[d, "g\tensor f"] \\
      (x.a)\tensor(y.b) \arrow[r, "{\sym_{x.a,y.b}}", dotted] \arrow[d, "{m_{x,y,a,b}}"']
        & (y.b) \tensor (x.a) \arrow[d, "{m_{y,x,b,a}}"] \\
      (x\tensor y).(a\tensor b) \arrow[r, "{\sym_{x,y}.\sym_{a,b}}"]
        & (y \tensor x).(b\tensor a)
    \end{tikzcd}
    \]
  Indeed, the top square commutes because $\sym$ is a natural transformation in $\C$, and the bottom square commutes because the action is a symmetric monoidal functor.
\end{proof}

\subsection{Symmetric monoidal closed structure of $\C/\X$}

Let a symmetric monoidal category $\X$ act on a symmetric monoidal category $\C$ via a symmetric monoidal action.  
Since any lax monoidal functor between monoidal closed categories is automatically lax monoidal closed, we might expect that in such a situation the category $\C/\X$ would be symmetric monoidal closed.

In fact, this is not the case.  
For example, suppose that $\X$ is the unit monoidal category, and that $\X$ acts on the category of sets via the powerset monad.  
Then the category $\Set/\X$ is the Kleisli category for the powerset monad -- i.e., the category of sets and relations.

Since the powerset functor is lax monoidal, it induces a monoidal structure on the Kleisli category -- i.e., the familiar Cartesian product.  
Indeed, the category of sets and relations \emph{is} monoidal closed under this choice of monoidal product, but the internal hom functor is also given by the Cartesian product, and does not agree with the function space functor on the original category of sets.

In fact, we can obtain a result for monoidal closedness of $\C/\X$, but under different conditions.  
Only $\C$ needs to be monoidal closed, but the action of $\X$ must preserve the internal hom strictly.

\begin{definition}
  Let a symmetric monoidal category $\X$ act on a symmetric monoidal closed category $\C$ via a symmetric monoidal lax action.
  We say that the action is \emph{symmetric monoidal closed} if there is a natural isomorphism
  \[
    s_{x,a,b} \from a\implies (x.b) \toisom x.(a\implies b)
    \]
  that makes the following diagram commute for any object $x$ of $\X$ and any objects $a,b$ of $\C$.
  \[
    \begin{tikzcd}[column sep=50pt]
      (x.(a\implies b)) \tensor (I.a) \arrow[r, "{m_{x,I,a\implies b,a}}"]
        & (x \tensor I).((a\implies b)\tensor a) \arrow[d, "{\runit\inv\tensor \ev_{a,b}}"] \\
      (a \implies x.b)\tensor a \arrow[u, "{s_{x,a,b}\tensor e_a}"] \arrow[r, "{\ev_{a,x.b}}"]
        & x.b
    \end{tikzcd}
    \]
  \label{DefSymmetricMonoidalClosedAction}
\end{definition}

\begin{example}
  If $j$ is an oplax symmetric monoidal functor from a symmetric monoidal category $\X$ to a symmetric monoidal closed category $\C$, then the reader action of $\oppcat X$ on $\C$ induced by $j$ is symmetric monoidal closed, via the isomorphism
  \[
    (jx \implies b) \cong jx \implies (a \implies b)\,.
    \]
\end{example}

\begin{proposition}
  Suppose that a symmetric monoidal category $\X$ acts on a symmetric monoidal closed category $\C$ via a symmetric monoidal closed action.  
  Then the category $\C/\X$ is symmetric monoidal closed.
\end{proposition}
\begin{proof}
  Given objects $a,b$ of $\C$, we define $a\implies b$ in $\C/\X$ to be the same as $a\implies b$ in $\C$, and we define
  \[
    \ev_{a,b} = J(\ev_{a,b}) \from (a\implies b)\tensor a \to b\,,
    \]
  to be given by the same morphism as in $\C$.

  Let $f \from c \tensor a \to b$ be a morphism in $\C/\X$.  
  It is necessary and sufficient to show that there is a unique morphism
  \[
    h \from c \to a \implies b
    \]
  in $\C/\X$ such that $f = (h\tensor a);\ev_{a,b}$.

  Suppose that $f$ is given by a morphism
  \[
    \hat{f} \from c \tensor a \to x.b
    \]
  in $\C$.  
  This then induces a morphism
  \[
    \tilde{f} = W(\hat{f}) \from c \to (a \implies x.b)\,,
    \]
  which we can compose with $s_{x,a,b}\inv$ to give us a morphism
  \[
    \hat{h} = W(\hat{f});s_{x,a,b} \from c \to x.(a\implies b)\,,
    \]
  which we may consider as a morphism $h\from c \to (a\implies b)$ in $\C/\X$.  
  We claim that $(h\tensor a);\ev_{a,b}=f$; indeed, the composite $(h\tensor \id_a);\ev_{a,b}$ is given in $\C$ by the composite
  \[
    \begin{tikzcd}[column sep=50pt]
      %
        & (x.(a\implies b)) \tensor (I.a) \arrow[r, "{m_{x,I,a\implies b,a}}"]
          & (x \tensor I).((a\implies b)\tensor a) \arrow[d, "{\id_{x\tensor I}\tensor \ev_{a,b}}"] \\
      c \tensor a \arrow[r, "\tilde{f}\tensor a"]
        & (a \implies x.b)\tensor a \arrow[u, "{s_{x,a,b}\tensor e_a}"]
          & (x\tensor I).b
    \end{tikzcd}\,.
    \]
  Using the diagram in Definition \ref{DefSymmetricMonoidalClosedAction}, we see that this is equal to the composite
  \[
    c\tensor a \xrightarrow{\tilde{f}\tensor a}
    (a \implies x.b) \tensor a \xrightarrow{\ev_{a,x.b}}
    x.b \xrightarrow{\runit_x.b}
    (x\tensor I).b\,.
    \]
  The composite of the first two morphisms is equal to $\hat{f}$, and so the whole thing defines the same morphism as $f$ in $\C/\X$ (using the equivalence relation on morphisms).

  Now suppose that $h\from c \to a\implies b$ is a morphism in $\C/X$, given by a morphism $\hat{h} \from c \to x.(a\implies b)$ in $\C$.
  Let $f \from c \tensor a \to b$ be given by the morphism
  \[
    \hat{f} = W\inv(\hat{h};s_{x,a,b}\inv)\,.
    \]
  Then $h$ may be recovered from $f$ just as in the first part of this proof, and the equation $f = (h\tensor a);\ev_{a,b}$ determines $f$.  
  It follows that the choice of $h$ is unique.
\end{proof}

\subsection{Cartesianness of the monoidal structure}

Suppose that a symmetric monoidal category $\X$ acts via a symmetric monoidal action on a Cartesian category $\C$.  
In this section we will consider what properties of the action we need in order to ensure that the induced monoidal structure on $\C/\X$ is Cartesian.

Since $\C$ is Cartesian, the diagonal map in $\C$ gives every object a natural comonoid structure:
\[
  a \xrightarrow{\Delta_a} a \times a\,.
  \]
Since the tensor product of objects in $\C/\X$ is given by the same object as in $\C$, we can lift this comonoid structure through the functor $J$ to give us a natural comonoid structure on each object of $\C/\X$:
\[
  a \xrightarrow{J\Delta_a} a \tensor a\,.
  \]
We use the symbol $\tensor$ rather than $\times$ in $\C/\X$, since this is not necessarily a category-theoretic product.

If every morphism $f\from a \to b$ in $\C/\X$ is a comonoid homomorphism with respect to this comonoid structure; i.e., if it makes the diagram
\[
  \begin{tikzcd}
    a \arrow[r, "f"] \arrow[d, "J\Delta_a"']
      & b \arrow[d, "J\Delta_b"] \\
    a \tensor a \arrow[r, "f\tensor f"]
      & b \tensor b
  \end{tikzcd}
  \]
commute, then we may identify $\C/\X$ with a full subcategory of its own category of comonoids, closed under tensor product.  
Since the category of comonoids in a monoidal category is automatically Cartesian, this will tell us that $\C/\X$ is Cartesian.

What does it mean for every morphism in $\C/\X$ to be a comonoid homomorphism?  
Firstly, since $\C$ itself is Cartesian, every morphism in $\C$ is a comonoid homomorphism with respect to the diagonal, and it follows that every morphism of the form $Jf \from a \to b$ (where $f\from a \to b$ is a morphism in $\C$) is a comonoid homomorphism in $\C/\X$.  
Since every morphism in $\C/\X$ may be written as the composite of a morphism of the form $Jf$ with a morphism of the form $\phi_{x,b}$, it will suffice to show that the morphisms of the form $\phi_{x,a}$ are comonoid homomorphisms in $\C/\X$; i.e., that they make the following diagram commute.
\[
  \begin{tikzcd}[column sep=40pt]
    x.a \arrow[r, "{\phi_{x,a}}"] \arrow[d, "J\Delta_{x.a}"']
      & a \arrow[d, "J\Delta_a"] \\
    x.a \tensor x.a \arrow[r, "{\phi_{x,a}\tensor\phi_{x,a}}"]
      & a \tensor a
  \end{tikzcd}
  \]
Let us compute the two arms of this square directly in $\C$.  
The composite along the top right is given in $\C$ by the morphism
\[
  x.a \xrightarrow{x.\Delta_a}
  x.(a\times a)\,,
  \]
while that along the bottom right is given by the composite
\[
  x.a \xrightarrow{\Delta_{x.a}}
  x.a \times x.a \xrightarrow{m_{x,x,a,a}}
  (x\tensor x) . (a \times a)\,.
  \]
Then a sufficient condition for these two morphisms to be equal in $\C/\X$, and therefore for the category $\C/\X$ to be Cartesian, is that for every object $x$ of $\X$ there should be a morphism $f \from x \to x\tensor x$ that makes the following diagram commute.
\[
  \begin{tikzcd}
    x.a \arrow[dr, "f.\Delta_a"] \arrow[d, "\Delta_{x.a}"']
      & \\
    x.a \times x.a \arrow[r, "{m_{x,x,a,a}}"]
      & (x\tensor x). (a\times a)
  \end{tikzcd}
  \]
If $\X$ itself is Cartesian, then we have a natural choice of morphism $x \to x \times x$, but choosing $f$ to be the diagonal map does not automatically make the diagram above commute.  
For example, the Cartesian product is not the category-theoretic product in the category of sets and relations, even though this category is the Kleisli category for the symmetric monoidal monad $\powerset \from \Set \to \Set$, and may be identified with the category $\Set/1$, where $1$ and $\Set$ are both Cartesian.  
In this case, the diagram
\[
  \begin{tikzcd}
    \powerset(A) \arrow[dr, "\powerset(\Delta_A)"] \arrow[d, "\Delta_{\powerset(A)}"']
      & \\
    \powerset(A) \times \powerset(A) \arrow[r, "{m_{A,A}}" xshift=-3pt]
      & \powerset(A \times A)
  \end{tikzcd}
  \]
does not commute, the arrow at the top right sending a set $X\subseteq A$ to the set $\{(x,x) \suchthat x \in X\}$ while the composite at the bottom left sends $X$ to the set $\{(x,y)\suchthat x,y\in X\}$.

An alternative sufficient condition for $\C/\X$ to be Cartesian is for the morphism mediating between the two arms of the square to go in the other direction.  
In this case, we require that for each object $x$ of $\X$ there should be a morphism $g \from x\tensor x \to x$ that makes the following diagram commute.
\[
  \begin{tikzcd}
    x.a \arrow[r, "x.\Delta_a"] \arrow[d, "\Delta_{x.a}"']
      & x.(a\times a) \\
    x.a \times x.a \arrow[r, "{m_{x,x,a,a}}"]
      & (x \tensor x).(a \times a) \arrow[u, "g.(a\times a)"']
  \end{tikzcd}
  \]
This will be particularly useful for reader actions.  
Indeed, suppose that $j\from \X \to \C$ is an oplax symmetric monoidal functor between symmetric monoidal categories, where $\C$ is Cartesian closed.  
The functor $j$ induces a reader action of $\oppcat\X$ on $\C$ (i.e., $x.a = jx \to a$), and we want the category $\C/\oppcat\X$ to be Cartesian.  
For this, it will be sufficient to find, for each object $x$ of $\X$, a morphism $f \from x \to x\tensor x$ such that the following diagram commutes.
\[
  \begin{tikzcd}
    jx \to a \arrow[rr, "jx \to \Delta_a"] \arrow[d, "\Delta_{jx \to a}"']
      &[-10pt]
        &[+10pt] jx \to (a \times a) \\
    (jx \to a) \times (jx \to a) \arrow[r]
      & (jx \times jx) \to (a \times a) \arrow[r, "m^j_x \to (a\times a)"]
        & j(x\tensor x) \to (a \times a) \arrow[u, "jf \to (a \times a)"']
  \end{tikzcd}
  \]
For this to commute, it is sufficient that $jf$ should be equal to the following composite.
\[
  jx \xrightarrow{\Delta_{jx}}
  jx \times jx \xrightarrow{m^j_{x,x}}
  j(x \tensor x)\,.
  \]
We have proved:

\begin{theorem}
  Let $j\from \X \to \C$ be an oplax symmetric monoidal functor between symmetric monoidal categories, where $\C$ is Cartesian closed.  
  Then $j$ induces a reader action of $\oppcat\X$ on $\C$, and the category $\C/\oppcat \X$ is symmetric monoidal closed.

  Suppose that for every object $x$ of $\X$, there is a morphism $f \from x \to x\tensor x$ in $\X$ such that $jf=\Delta_{jx};m^j_{x,x}$.  
  Then $\C/\oppcat \X$ is Cartesian closed.
  \label{TheCartesianClosedCx}
\end{theorem}

In the next section, we will investigate a class of reader actions, and give a more concrete property for the category $\C/\oppcat\X$ to be Cartesian closed.

\section{Reader actions on $\Set$}

\subsection{Colimits of actions are monoidal functors}

\begin{proposition}
  Let $\C$ be a cocomplete monoidal category, and suppose that a symmetric monoidal category $\X$ acts on $\C$ via a symmetric monoidal action in the sense of Definition \ref{DefMonoidalLaxAction}.  
  Define a functor $\C \to \C$ by
  \[
    F a = \colim_{x\from \X} x.a\,.
    \]
  Then $F$ is a lax monoidal functor.
  \label{PropColimitOfActionIsMonoidalFunctor}
\end{proposition}
\begin{proof}
  We have morphisms
  \begin{IEEEeqnarray*}{Cl}
    & \colim_{x \from \X} x.a \tensor \colim_{y\from \X} y.b \\
    \to & \colim_{x,y \from \X} x.a \tensor y.b \\
    \to & \colim_{x,y \from \X} (x\tensor y).(a \tensor b) \\
    \hookrightarrow & \colim_{z \from \X} z.(a\tensor b)\,.
  \end{IEEEeqnarray*}
  and
  \[
    1 \xrightarrow{e}
    I.1 \hookrightarrow
    \colim_{x\from \X} x.1\,.
    \]
  Figures \ref{FigColimMonoidalMultiplicative} and \ref{FigColimMonoidalUnital} show that these satisfy the coherence conditions for a monoidal functor.
  \begin{SidewaysFigure}
    \begin{mathpar}
      \begin{tikzcd}[ampersand replacement=\&]
        %
        \&[-20pt] \left(\colim_{x\from \X}\limits x.a \tensor \colim_{y\from \X}\limits y.b\right) \tensor \colim_{z \from \X}\limits z.c \arrow[r, "\assoc" yshift=5pt] \arrow[d]
            \&[-20pt] \colim_{x \from \X}\limits x.a \tensor \left(\colim_{y\from \X}\limits y.b \tensor \colim_{z \from \X}\limits z.c \right) \arrow[d]
              \&[-20pt] \\
        %
          \& \left(\colim_{x,y\from \X}\limits x.a \tensor y.b\right) \tensor \colim_{z \from \X}\limits z.c \arrow[d]
            \& \colim_{x\from \X}\limits x.a \tensor \left(\colim_{y,z \from \X}\limits (y.b \tensor z.c)\right) \arrow[d]
              \& \\
        %
          \& \colim_{x,y,z \from \X}\limits (x.a \tensor y.b) \tensor z.c \arrow[r, "\Colim\assoc"] \arrow[d, "{\Colim m_{x,y,a,b}\tensor z.c}"']
            \& \colim_{x,y,z \from \X}\limits x.a \tensor (y.b \tensor z.c) \arrow[d, "{\Colim x.a \tensor m_{y,z,b,c}}"]
              \& \\
        \colim_{t,z\from \X}\limits t.(a \tensor b) \tensor z.c \arrow[d, "{\Colim m_{t,z,a\tensor b,c}}"']
          \& \colim_{x,y,z \from \X}\limits (x\tensor y).(a \tensor b) \tensor z.c \arrow[d, "{\Colim m_{x\tensor y,z,a\tensor b,c}}"'] \arrow[l, hookrightarrow]
            \& \colim_{x,y,z \from \X}\limits x.a \tensor (y\tensor z).(b\tensor c) \arrow[d, "{\Colim m_{x,y\tensor z,a,b\tensor c}}"] \arrow[r, hookrightarrow]
              \& \colim_{x,t\from \X}\limits x.a \tensor t.(b\tensor c) \arrow[d, "{\Colim m_{x,t,a,b\tensor c}}"] \\
        \colim_{t,z\from \X}\limits (t\tensor z).((a \tensor b)\tensor c) \arrow[d, hookrightarrow]
          \& \colim_{x,y,z\from\X}\limits ((x\tensor y) \tensor z).((a \tensor b) \tensor c) \arrow[r, "\Colim\assoc.\assoc" yshift=5pt] \arrow[l, hookrightarrow]
            \& \colim_{x,y,z\from\X}\limits (x \tensor (y\tensor z)).(a \tensor (b \tensor c)) \arrow[r, hookrightarrow]
              \& \colim_{x,t\from \X}\limits (x \tensor t).(a \tensor (b \tensor c)) \arrow[d, hookrightarrow] \\
        \colim_{u\from \X}\limits u.((a\tensor b) \tensor c) \arrow[rrr, "\Colim u.\assoc"]
          \&
            \&
              \& \colim_{u\from \X}\limits u.(a \tensor (b\tensor c))
      \end{tikzcd}
    \end{mathpar}
    \caption[Proof that the colimit of a monoidal action satisfies the multiplicative criterion for being a monoidal functor.]
    {Proof that $\colim_{x\from \X} x.a$ satisfies the multiplicative criterion for being a monoidal functor.  
    The bottom hexagon is the multiplicative coherence for $\blank.\blank$ as a monoidal functor, after applying the colimit.}
    \label{FigColimMonoidalMultiplicative}
  \end{SidewaysFigure}
  \begin{figure}
    \begin{mathpar}
      \begin{tikzcd}
        %
          & |[alias=Z]| \colim_{z\from \X}\limits z.(1 \tensor a)
            &[-20pt] \\
        |[alias=Y]| \colim_{y\from \X}\limits y.a \arrow[r, "\Colim\lunit.\lunit" yshift=2pt] \arrow[ur, "\Colim \id.\lunit", from=Y.north, to=Z.west, bend left=20] \arrow[d, "\Colim\lunit" description] \arrow[dd, "\lunit"', bend right=60]
          & \colim_{y\from \X}\limits (I \tensor y).(1\tensor a) \arrow[r, hookrightarrow] \arrow[u, hookrightarrow]
            & |[alias=X]| \colim_{x,y\from \X}\limits (x \tensor y).(1 \tensor a) \arrow[ul, hookrightarrow, from=X.north, to=Z.east, bend right=20] \\
        \colim_{y\from \X}\limits 1 \tensor y.a \arrow[r, "\Colim e \tensor \id"]
          & \colim_{y \from \X}\limits I.1 \tensor y.a \arrow[u, "{\Colim m_{I,y,1,a}}" description] \arrow[r, hookrightarrow]
            & \colim_{x,y\from\X}\limits x.1 \tensor y.a \arrow[u, "{\Colim m_{x,y,1,a}}"'] \\
        1 \tensor \colim_{y \from \X}\limits y.a \arrow[u, Sim] \arrow[r, "e \tensor \id"]
          & I.1 \tensor \colim_{y \from \X}\limits y.a \arrow[u, Sim] \arrow[r, hookrightarrow]
            & \colim_{x\from \X}\limits x.1 \tensor \colim_{y\from 1} y.a \arrow[u]
      \end{tikzcd}
      \and
      \begin{tikzcd}
        %
          & |[alias=Z]| \colim_{z\from \X}\limits z.(a \tensor 1)
            &[-20pt] \\
        |[alias=Y]| \colim_{x\from \X}\limits x.a \arrow[r, "\Colim\runit.\runit" yshift=2pt] \arrow[ur, "\Colim \id.\runit", from=Y.north, to=Z.west, bend left=20] \arrow[d, "\Colim\runit" description] \arrow[dd, "\runit"', bend right=60]
          & \colim_{x\from \X}\limits (x \tensor I).(a\tensor 1) \arrow[r, hookrightarrow] \arrow[u, hookrightarrow]
            & |[alias=X]| \colim_{x,y\from \X}\limits (x \tensor y).(a \tensor 1) \arrow[ul, hookrightarrow, from=X.north, to=Z.east, bend right=20] \\
        \colim_{x\from \X}\limits x.a \tensor 1 \arrow[r, "\Colim \id \tensor e"]
          & \colim_{x \from \X}\limits x.a \tensor I.1 \arrow[u, "{\Colim m_{x,I,a,1}}" description] \arrow[r, hookrightarrow]
            & \colim_{x,y\from\X}\limits x.a \tensor y.1 \arrow[u, "{\Colim m_{x,y,a,1}}"'] \\
        \left(\colim_{x \from \X}\limits x.a\right) \tensor 1 \arrow[u, Sim] \arrow[r, "\id \tensor e"]
          & \left(\colim_{x \from \X}\limits x.a\right)\tensor I.a \arrow[u, Sim] \arrow[r, hookrightarrow]
            & \colim_{x\from \X}\limits x.a \tensor \colim_{y\from 1} y.1 \arrow[u]
      \end{tikzcd}
    \end{mathpar}
    \caption[Proof that the colimit of a monoidal action satisfies the unital criteria for being a monoidal functor.]
    {Proof that $\colim_{x\from \X} x.a$ satisfies the unital criteria for being a monoidal functor.  
    The top-right squares are the unital coherence for $\blank.\blank$ as a monoidal functor, after applying the colimit.}
    \label{FigColimMonoidalUnital}
  \end{figure}
\end{proof}

\begin{proposition}
  If $\C$ is a cocomplete symmetric monoidal category and the action of $\X$ on $\C$ is symmetric monoidal, then
  \[
    \colim_{x\from \X} x.\blank
    \]
  is a symmetric monoidal functor.
\end{proposition}
\begin{proof}
  We have a commutative diagram
  \[
    \begin{tikzcd}
      \colim_{x\from \X}\limits x.a \tensor \colim_{y\from \X} y.b \arrow[r, "\sym"] \arrow[d]
        & \colim_{y\from \X}\limits y.b \tensor \colim_{x\from \X}x.a \arrow[d] \\
      \colim_{x,y\from \X}\limits x.a \tensor y.b \arrow[r, "\Colim\sym"] \arrow[d, "{\Colim m_{x,y,a,b}}"']
        & \colim_{x,y\from \X}\limits y.b \tensor x.a \arrow[d, "{\Colim m_{y,x,b,a}}"] \\
      \colim_{x,y\from \X}\limits (x\tensor y).(a\tensor b) \arrow[r, "\Colim sym.sym"] \arrow[d, hookrightarrow]
        & \colim_{x,y \from \X}\limits (y \tensor x).(b\tensor a) \arrow[d, hookrightarrow] \\
      \colim_{z \from \X}\limits z.(a \tensor b) \arrow[r, "\Colim \id.\sym"]
        & \colim_{z\from \X}\limits z.(b\tensor a)
    \end{tikzcd}\,.
    \]
  Here, commutativity of the middle square is by applying the colimit to the diagram for $\blank.\blank$ to be a symmetric monoidal functor.
\end{proof}

\subsection{Reader actions on $\Set$ vs change of base}

For our next result, we will go via the \Mellies category.  
First, we need a standard result about the Day convolution product.

\begin{proposition}[\cite{Pisani}]
  Let $\X,\YY$ be a monoidal category and let $[\YY,\Set]$ be equipped with the Day convolution product.  
  Then a lax monoidal functor $\X \times \YY \to \Set$ is the same thing (via currying) as a lax monoidal functor $\X \to [\YY,\Set]$.
\end{proposition}

In particular, if $\X$ acts on the category of sets via a monoidal action, then it gives rise to a functor $\Set \to [\X,\Set]$.

\begin{proposition}
  Let $j \from \X \to \Set$ be an oplax symmetric monoidal functor between symmetric monoidal categories.
  Let $\oppcat\X$ act on $\Set$ via the reader action induced by $j$.
  Then the \Mellies category $\Mell_{\oppcat\X}\Set$ is isomorphic to the category obtained via base change along the action regarded as a functor
  \[
    \blank.\blank\from \Set \to [\X,\Set]\,.
    \]
  \label{PropMelliesVsBaseChange}
\end{proposition}
\begin{proof}
  The objects of both categories are sets.  
  The morphism objects in the \Mellies category are given by
  \[
    \Mell_\X\Set(A,B)(x) = [A,[jx,B]]\,,
    \]
  while those in the base-changed category are given by
  \[
    (\blank.\blank)_*\Set(A,B)(x) = [jx, [A,B]]\,,
    \]
  and these may be related by the symmetry isomorphism
  \[
    s_{jx,A,B} \from [A,[jx,B]] \to [jx, [A,B]]\,.
    \]
  We need to show that this preserves composition of morphisms.  
  Recall that composition in the \Mellies category is given by
  \begin{IEEEeqnarray*}{Cl}
    & \int^{y,z} [A,[jy,B]] \times [B,[jz,C]] \times \X(y\tensor z,x) \\
    \to &
    \int^{y,z} [A,[j(y\tensor z),C]]\times \X(y\tensor z,x) \\
    \cong &
    [A,[jx,C]]\,,
  \end{IEEEeqnarray*}
  where the first arrow is induced via the \Mellies composition, while composition in the base changed category is given by
  \begin{IEEEeqnarray*}{Cl}
    &\int^{y,z}[jy,[A,B]] \times [jz,[B,C]] \times \X(y\tensor z,x) \\
    \xrightarrow{\makebox[146pt]{$\int^{y,z} m_{jy,jz,[A,B],[B,C]}\times \X(y\tensor z,x)$}} &
    \int^{y,z}[jy \times jz,[A,B]\times [B,C]] \times \X(y,\tensor z,x) \\
    \xrightarrow{\makebox[146pt]{$\int^{y,z} [m^j_{y,z}, ;] \times \X(y\tensor z,x)$}} &
    \int^{y,z}[j(y \tensor z),[A,C]]\times \X(y\tensor z,x) \\
    \cong & 
    [jx,[A,C]]\,.
  \end{IEEEeqnarray*}
  where $;$ is the internal composition in $\Set$.

  Using the diagram in Figure \ref{FigMelliesVsBaseChange}, we see that the expressions inside the coends are related by the symmetry isomorphisms as follows.
  \[
    \begin{tikzcd}[column sep=30pt]
      {[A,[jy,B]] \times [B,[jz,C]]} \arrow[r, "\text{\Mellies}" xshift=-2pt] \arrow[d, "{s_{jx,A,B}\times s_{jy,B,C}}"']
        & {[A,[j(y\tensor z),C]]} \arrow[d, "{s_{j(x\tensor y)},A,C}"] \\
      {[jy,[A,B]]\times [jz,[B,C]]} \arrow[r, "\text{B.c.}"]
        & {[j(y \tensor z),[A,C]]}
    \end{tikzcd}
    \]
  \begin{SidewaysFigure}
    \[
      \begin{tikzcd}[ampersand replacement=\&, column sep=73pt, row sep=20pt]
        {[A,[jy,B]] \times [B,[jz,C]]} \arrow[d, "{[A,[jy,B]] \times L_{B,[jz,C]}^{jy}}"', thick, dashed] \arrow[r, "{s_{y,A,B}\times s_{z,B,C}}", dotted]
          \& {[jy,[A,B]] \times [jz,[B,C]]} \arrow[d, "{m_{jy,jz,[A,B],[A,C]}}"]
            \& \\
        {[A,[jy,B]] \times [[jy,B],[jy,[jz,C]]]} \arrow[d, "{[A,[jy,B]]\times[[jy,B],W\inv]}"', thick, dashed]
          \& |[alias=Z]| {[jy \times jz,[A,B]\times[B,C]]} \arrow[d, "{[jy\times jz,;]}", dotted] \arrow[dr, "{[m_{y,z},;]}", bend left=17.5, from=Z.east]
            \& \\
        {[A,[jy,B]]} \times [[jy,B],[jy\times jz,C]] \arrow[d, ";"', thick, dashed]
          \& {[jy \times jz,[A,C]]} \arrow[r, "{[m_{y,z},[A,C]]}", dotted]
            \& {[j(y\tensor z),[A,C]]} \\[51pt]
        {[A,[jy \times jz,C]]} \arrow[ur, "{s_{jy\times jz,A,C}}", dotted] \arrow[r, "{[A,[m_{y,z},C]]}", thick, dashed]
          \& {[A,[j(y\tensor z),C]]} \arrow[ur, "{s_{j(y\tensor z),A,C}}", dotted]
            \&
      \end{tikzcd}
      \]
      \caption[Proof that \Mellies composition agrees with base-changed composition in the case of a symmetric reader action on $\Set$.]%
      {Proof that \Mellies composition agrees with base-changed composition in the case of a symmetric reader action on $\Set$.  
      The \Mellies composition is given by the thick dashed arrows, while the composition in the base-changed category is given by the thin arrows.
      The dotted lines at the top and at the bottom right -- given by the symmetry isomorphisms -- mediate between the two.
      We can verify that the main heptagon commutes by directly computing each direction: in each case, a pair $\langle f,g\rangle$ of functions is sent to the function $h \from A \to {[jy\times jz,C]}$ given by
      \[
        h(a)(Y,Z) = g(f(a)(Y))(Z)\,.
        \]}
      \label{FigMelliesVsBaseChange}
  \end{SidewaysFigure}
  It follows that the functor induced by $s$ is an isomorphism of $[\X,\Set]$-enriched categories.
\end{proof}

By applying base change along the colimit functor to both these categories, we get the following.

\begin{corollary}
  Let $j\from \X \to \Set$ be a symmetric monoidal functor.  
  Let $\oppcat\X$ act on $\Set$ via the induced reader action.  
  Then the category $\Set/\oppcat\X$ is isomorphic to the category obtained from $\Set$ by base change along the functor
  \[
    \colim_{x\from \X} x.\blank \from \Set \to \Set\,.
    \]
  \label{CorCxVsBaseChange}
\end{corollary}

Thus, the theory of reader actions on $\Set$ is subsumed into the theory of base change in $\Set$ along monoidal functors $\Set \to \Set$.

\subsection{From monoidal endofunctors on $\Set$ to reader actions}

We can get a result in the other direction; i.e., a kind of converse to Proposition \ref{PropColimitOfActionIsMonoidalFunctor} in the case of reader actions on $\Set$.

\begin{proposition}
  Let $F \from \Set \to \Set$ be a lax symmetric monoidal functor.  
  Then there is a symmetric monoidal category $\X$ and an oplax monoidal functor $j\from \X \to \Set$ such that for all sets $A$, we have
  \[
    FA \cong \colim_{x \from \X} [jx,A]\,,
    \]
  and the monoidal coherences of $F$ arise from the reader action of $\oppcat\X$ on $\Set$ as in Proposition \ref{PropColimitOfActionIsMonoidalFunctor}.
  \label{PropMonoidalFunctorIsColimitOfReaderAction}
\end{proposition}
\begin{proof}
  Consider $F$ as a pseudofunctor $\Set \to \Cat$, and let $\X=\oppcat{\left(\int F\right)}$ be the opposite of its Grothendieck construction.  
  Since $\Set$ is an ordinary category, so is $\X$.

  More concretely, the objects of $\X$ are pairs $(A,m)$, where $A$ is a set and $m\in FA$, and morphisms
  \[
    (A,m) \to (B,n)
    \]
  are given by functions $h\from A \to B$ such that $F(h)(m) = n$.
  $\X$ is normally called the \emph{category of elements of $F$}.

  We define a symmetric monoidal structure on $\X$ by defining
  \begin{mathpar}
    (A,m) \tensor (B,n) = (A \times B, m^F_{A,B}(m,n))
    \and
    I = (1, e^F)\,,
  \end{mathpar}
  using the fact that the monoidal coherences for $F$ are given by functions
  \begin{mathpar}
    m^F_{A,B} \from FA \times FB \to F(A\times B)
    \and
    e^F \from 1 \to F1\,.
  \end{mathpar}
  We now need to show that the monoidal coherences in $\Set$ give rise to morphisms
  \begin{mathpar}
    \assoc_{A,B,C} \from ((A \times B) \times C,m^F_{A\times B,C}(m^F_{A,B}(m,n),p))
    \to
    (A \times (B \times C),m^F_{A,B \times C}(m,m^F_{B,C}(n,p))
    \and
    \lunit_{A} \from (A,m) \to (1\times A,m^F_{1,A}(e^F,m))
    \and
    \runit_{A} \from (A,m) \to (A \times a,m^F_{A,1}(m,e^F))
    \and
    \sym_{A,B} \from (A \times B,m^F_{A,B}(m,n)) \to (B \times A,m^F_{B,A}(n,m))
  \end{mathpar}
  in $\X$.  
  Happily, the diagrams we need for this are precisely the coherence diagrams for $m^F,e^F$ that we get from $F$ being a lax symmetric monoidal functor.

  Since $\assoc,\lunit,\runit,\sym$ satisfy the pentagon, triangle and hexagon identities in $\Set$, so they do in $\X$.
  Therefore, $\X$ is a symmetric monoidal category.

  There is an obvious forgetful functor $\X \to \Set$ that is, in fact, strict monoidal.

  We claim that if $A$ is a set, then we have
  \[
    \colim_{(X,m)\from \oppcat\X} [X,A] \cong FA\,.
    \]
  Indeed, for each object $(X,m)$ of $\X$ we have a function
  \begin{IEEEeqnarray*}{cCc}
    [X,A] & \to & FA \\
    f & \mapsto & F(f)(m)\,.
  \end{IEEEeqnarray*}
  We claim that this defines a cocone under the functor $(X,m) \mapsto [X,A] \from \oppcat\X \to \Set$.  
  Indeed, if we have a morphism $h \from (Y,n) \to (X,m)$ then by definition we have
  \[
    F(h)(n) = m\,,
    \]
  and so we have a commutative triangle
  \[
    \begin{tikzcd}[column sep=50pt]
      {[X,A]} \arrow[r, "{f \mapsto  F(f)(m)}"] \arrow[d, "{f \mapsto h;f}"']
        & FA \\
      {[Y,A]} \arrow[ur, "{g \mapsto F(g)(n)}"']
        &
    \end{tikzcd}\,,
    \]
  since
  \[
    F(h;f)(n) = F(f)(F(h)(n)) = F(f)(m)\,.
    \]
  Therefore, we have an induced map
  \[
    \colim_{(X,m)\from\X}[X,A] \to FA
    \]
  that sends $((X,m),f)$ to $F(f)(m)$.

  Now we define a map in the other direction.
  \begin{IEEEeqnarray*}{cCc}
    FA & \to & \colim_{(X,m)\from \X} [X,A] \\
    m & \mapsto & ((A,m),\id_A)
  \end{IEEEeqnarray*}

  We claim that these two maps are inverses.  
  Indeed, we certainly have
  \[
    F(\id_A)(m) = id_{FA}(m) = m\,.
    \]
  In the other direction, we need to show that
  \[
    ((A,F(f)(m)),\id_A) = ((X,m),f)
    \]
  in the colimit.
  But indeed, we have a morphism $f\from (X,m) \to (A,F(f)(m))$ in $\oppcat\X$, and $f;\id_A=f$.
  Therefore, our map $\colim_{(X,m)\from \X}[X,A] \to FA$ was a bijection.

  Lastly, we need to show that this decomposition as a colimit gives rise to the monoidal structure on the functor $F$; i.e., that the following diagrams commute.
  \begin{mathpar}
    \begin{tikzcd}
      FA \times FB \arrow[r, "{m^F_{A,B}}"] \arrow[d, Isom']
        & F(A\times B) \arrow[d, Isom] \\
      \colim_{(X,m)\from \X}\limits [X,A] \times \colim_{(Y,n)\from\X}\limits [Y,B] \arrow[r]
        & \colim_{(Z,p)\from\X}\limits [Z,A\times B]
    \end{tikzcd}
    \and
    \begin{tikzcd}
      1 \arrow[r, "e^F"] \arrow[dr]
        & F1 \arrow[d, Isom] \\
      %
        & \colim_{(X,m)\from \X}\limits[X,1]
    \end{tikzcd}
  \end{mathpar}
  Here, the arrows marked with the isomorphism symbol $\cong$ are the isomorphisms that we have just defined, while the arrows at the bottom of the first diagram and at the bottom left of the second are as in Proposition \ref{PropColimitOfActionIsMonoidalFunctor}.

  We can check by hand that these diagrams commute: that in the first diagram, both directions send the pair $(m,n)\in FA \times FB$ to
  \[
    ((A\times B,m_{A,B}(m,n)),\id_{A\times B})\in \colim_{(Z,p)\from \X}[Z,A\times B]\,,
    \]
  and that in the second diagram both directions pick out the element
  \[
    ((1,e^F),\id_1)
    \]
  of $\colim_{(X,m)\from \X}[X,1]$.
\end{proof}

\begin{example}
  Let $\powerset_+\from \Set \to \Set$ be the non-empty powerset functor.  
  Then the category $\X$ of elements of $\powerset_+$ has pairs $(A,M)$ as elements, where $A$ is a (necessarily non-empty) set and $M$ is a non-empty subset of $A$.
  Morphisms $(A,M) \to (B,N)$ are functions $f \from A \to B$ such that $f(M)=N$.

  The nonempty powerset functor has a natural monoidal structure:
  \begin{mathpar}
    \powerset_+A \times \powerset_+ B \to \powerset_+(A \times B)
    \and
    1 \to \powerset_+1
  \end{mathpar}
  sending $(M,N)$ to $M\times N\subset A \times B$ and picking out the subset $1 \subset 1$.
  This then gives us a monoidal structure on this category of elements, inducing an action as in Proposition \ref{PropMonoidalFunctorIsColimitOfReaderAction}.
  The colimit of this action then gives us the original functor.  
  Therefore, by Corollary \ref{CorCxVsBaseChange}, the category $\Set/\X$ is isomorphic to the category $(\powerset_+)_*\Set$ obtained by base change along the non-empty powerset functor $\powerset_+\from \Set \to \Set$.
\end{example}

\begin{example}
  Let $\DG \from \Set \to \Set$ be the functor that sends a set $A$ to the set of discrete probability measures on $A$ and sends a function $f\from A \to B$ to the function $\DG(A) \to \DG(B)$ that sends a probability measure $\bP$ on $A$ to the probability measure $f_*\bP$ on $B$ given by
  \[
    f_*\bP(X) = \bP(f\inv(X))\,.
    \]
  Then the category of elements of $\DG$ is the category whose objects are pairs $(A,\bP)$ and where the morphisms $(A,\bP_A) \to (B,\bP_B)$ are functions $f\from A \to B$ such that $\bP_B=f_*\bP_A$.  
  In other words, it is the category of discrete probability spaces and probability-preserving functions.

  The functor $DG$ has a natural monoidal structure: given a discrete probability measure on a set $A$ and a discrete probability measure on a set $B$, we can get a discrete probability measure on the set $A \times B$ by
  \[
    \bP_{A\times B}(\{(a,b)\}) = \bP_A(\{a\})\times\bP_B(\{b\})\,.
    \]
  This then gives us a monoidal structure on the category of discrete probability spaces, where the tensor product of probability spaces $(A,\bP_A)$ and $(B,\bP_B)$ is given by the set $A \times B$, together with the probability measure as described above.
\end{example}

Now suppose that $F\from \Set \to \Set$ is a lax symmetric monoidal endofunctor.  
We have shown that $F$ gives rise to a strict symmetric monoidal functor $j\from \X \to \Set$, for some monoidal category $\X$, and that the induced category $\Set/\oppcat\X$ is isomorphic to the category obtained from $\Set$ by base change along $F$.

Since the action of $\X$ on $\Set$ is the reader action of a symmetric monoidal functor, by Theorem \ref{TheCartesianClosedCx} we know that the category $\Set/\oppcat\X$ must be symmetric monoidal closed.

Now recall that in order to apply the second part of Theorem \ref{TheCartesianClosedCx}, and deduce that $\Set/\oppcat\X$ is Cartesian closed, we must prove that for every object $x$ of $\X$, there is a morphism $f \from x \to x \tensor x$ such that $jf = \Delta_{jx};m^j_x$.  
This is particularly useful in our case, since the functor $\X \to \Set$ is faithful.

In other words, for every set $A$ and every $p\in FA$, the function $\Delta_A$ must define a morphism
\[
  (A,p) \to (A \times A, m^F_{A,A}(p,p))\,;
  \]
i.e., we must have
\[
  F(\Delta_A)(p) = m^F_{A,A}(p,p)\,.
  \]
Let us see what this means in some examples.
\begin{example}
  The finite powerset functor does not satisfy the condition given above; indeed, we have
  \begin{mathpar}
    \powerset_+(\Delta_A)(X) = \{(x,x)\in A \times A \suchthat x \in X\}
    \and
    m^{\powerset_+}_{A,A}(X,X) = X \times X = \{(x,y) \in A \times A \suchthat x \in X\}\,.
  \end{mathpar}
  Similarly, the discrete probability measure functor does not satisfy the condition we have given, since the diagonal map
  \[
    \Delta_A \from (A,\bP_A) \to (A \times A, \bP_{A\times A})
    \]
  does not preserve probability in general.
\end{example}

\begin{example}
  An alternative way of dealing with probability that does satisfy the condition for Cartesianness of the resulting category.
  If $(\Omega,\F,\bP)$ is a fixed probability space, then a \emph{discrete random variable taking values in a set $A$} is a measurable function
  \[
    V\from (\Omega,\F) \to (A,\powerset A)\,.
    \]
  Given $X \subset A$, we define
  \[
    \bP(V \in X) = \bP(V\inv(X))\,.
    \]
  This then gives us a discrete probability measure on $X$.

  Write $\RV_\Omega \from \Set \to \Set$ for the functor that sends a set $A$ to the set of all random variables taking values in the set $A$ and sends a function $f\from A \to B$ to the function
  \[
    \RV_\Omega(A) \to \RV_\Omega(B)
    \]
  given by composing on the right with $f$.

  Moreover, $\RV_\Omega$ is a lax monoidal functor: if $V,W$ are discrete random variables taking values in sets $A,B$, then we have a random variable $\langle V,W \rangle\from X \to A\times B$ given by pairing (and if $(a,b)\in A\times B$, then $(\langle V,W\rangle)\inv(\{(a,b)\}) = V\inv(\{a\})\cap W\inv(\{b\})$, so this is a measurable function).

  Now if we apply the construction from Proposition \ref{PropMonoidalFunctorIsColimitOfReaderAction}, we get the category whose objects are pairs $(A,V)$, where $A$ is a set and $V$ a discrete random variable taking values in $A$ and where the morphisms $(A,V) \to (B,W)$ are functions $f \from A \to B$ such that $W=V;f$.
  This category, which we will call $\Rv_\Omega$, admits a strict monoidal forgetful functor into the category of sets, giving us a lax reader action of $\oppcat{\Rv_\Omega}$ on $\Set$.
  Once again, we can pass to the symmetric monoidal category $\Set/\oppcat{\Rv_\Omega}$, giving us a way of modelling probability that is equivalent to taking base change through the functor $\RV_\Omega$.

  The difference now is that the diagonal map
  \[
    \Delta_A \from (A,V) \to (A\times A, \langle V,V\rangle)
    \]
  \emph{is} probability preserving.  
  In the language of probability, the two copies of the random variable $V$ are \emph{dependent random variables}, so the probability of obtaining the reading $(a,a)$ from $\langle V,V\rangle$ is the same as the probability of obtaining the reading $v$ from $V$.
  Therefore, the category $\Set/\oppcat{\Rv_\Omega}$ will be Cartesian closed.
\end{example}

\subsection{Actions of categories with terminal objects}

The probability example above lends itself to further examination.  
Recall that if a monoidal category $\X$ acts on a category $\C$, and $x$ is a monoid in $\X$ with multiplication $m^x$ and unit $e^x$, then we get a monad on $\C$ given by the composite
\[
  1 \xrightarrow{x} \X \xrightarrow{\blank.\blank} \End[\C]
  \]
of lax monoidal functors.

More explicitly, this monad is given by
\[
  M_xa = x.a\,,
  \]
with the monadic coherences given by
\begin{mathpar}
  M_xM_xa = x.x.a \xrightarrow{m_{x,x}} (x \tensor x).a \xrightarrow{m^x.a} x.a = M_xa
  \and
  a \xrightarrow{e_a} I.a \xrightarrow{e^x.a} x.a = M_x a\,.
\end{mathpar}
In particular, if $j\from \X \to \C$ is an oplax monoidal (in particular, comonoid-preserving) functor, yielding a reader action of $\oppcat\X$ upon $\C$, and $x$ is a monoid in $\oppcat\X$ (i.e., a comonoid in $\X$), then the monad $M_x$ will be the reader monad corresponding to $jx$.

Now suppose that the category $\X$ has a terminal object $1$.  
Then $1$ automatically has the structure of a monoid in $\X$, via the unique morphisms
\begin{mathpar}
  1 \tensor 1 \xrightarrow{()} 1
  \and
  I \xrightarrow{()} 1\,.
\end{mathpar}

\begin{proposition}
  Let a monoidal category $\X$ act on a category $\C$ via a lax action.  
  Suppose that $\X$ has a terminal object $1$.
  Then the category $\C/\X$ is isomorphic to the Kleisli category for the monoid $M_1$.
\end{proposition}
\begin{proof}
  In both cases, the objects are the objects of $\C$.  
  Note also that we have an isomorphism
  \begin{mathpar}
    (\C/\X)(a,b) = \int^x\C(a,x.b) \cong \int^x \C(a,x.b) \times \C(x,1) \cong \C(a,1.b) = \Kl_{M_1}(a,b)\,.
  \end{mathpar}
  More concretely, this isomorphism sends a \Mellies morphism $f\from a \to x.b$ to the Kleisli morphism given by the composite
  \[
    a \xrightarrow{f} x.b \xrightarrow{().b} 1.b\,.
    \]
  By Proposition \ref{PropFunctorialityOfLaxColimits}, this gives us a functor
  \[
    \C/\X \to \Kl_{M_1}\,,
    \]
  which is fully faithful and the identity on objects.
\end{proof}

Now we can get a clearer idea of what is going on in the probability example: the new category $\Rv_\Omega$ \emph{almost} has an initial object (i.e., a terminal object in $\oppcat{\Rv_\Omega}$), given by the pair
\[
  (\Omega,\id_\Omega)\,.
  \]
At least, it does if the $\sigma$-algebra $\F$ on $\Omega$ is discrete.  
But in general, the identity function
\[
  \id_\Omega \from (\Omega,\F) \to (\Omega,\powerset\Omega)
  \]
is not measurable (indeed, it is measurable if and only if $\F=\powerset\Omega$), so $\id_\Omega$ is not a discrete random variable in general.

In the case that $\F=\powerset\Omega$, the category $\Rv_\Omega$ has an initial object, and the category
\[
  \Set/\oppcat{\Rv_\Omega}
  \]
is isomorphic to the Kleisli category for the reader monad for the set $\Omega$ on $\Set$.  
Now, from Theorem \ref{FunctionalCompletenessCcc}, we know that this Kleisli category is automatically Cartesian closed.  
The point here is that the category $\Rv_\Omega$ is just close enough to having an initial object for the category $\Set/\oppcat{\Rv_\Omega}$ to be Cartesian, even though it is not a Kleisli category.

\begin{remark}
  This subtlety with probability spaces is not present in the case of the nonempty powerset functor, which is why we it makes sense to model plain nondeterminism with a Kleisli category, as we did in Section \ref{SecMonads}.
\end{remark}

\subsection{Reader actions and semantics}

Suppose that we have an oplax monoidal functor $j \from \X \to \Set$, giving rise to a lax reader action of $\oppcat\X$ on $\Set$.
Let $\G$ be a (Cartesian closed) model for a programming language $P$, and suppose that there is a functor $D\from \Set \to \G$ that gives us the denotation of the datatypes in $\G$.

For example, if $\G$ is the category of games, then we can define $D(A)$ to be the game given by $M_{D(A)} = \{q\}\cup A$ with $\lambda(q)=O$ and $\lambda(a)=P$ for $a\in A$, where $q$ is initial and justifies the moves $a\in A$ and the legal plays are those of the form $\epsilon$, $q$ or $qa$.

In general, such functions automatically carry an oplax monoidal structure, since the source category $\Set$ and target category $\G$ are Cartesian.  
So we get morphisms
\begin{mathpar}
  m_{A,B} = D(A \times B) \xrightarrow{\langle D(\pr_1),D(\pr_2) \rangle} D(A) \times D(B)
  \and
  e = D(1) \xrightarrow{()} 1\,.
\end{mathpar}

Then we may compose the functors $j$ and $D$ to get a new oplax monoidal functor $\X \to \G$, inducing a reader action of $\oppcat{\X}$ on $\G$.

Now the category $\G/\oppcat\X$ has its universal natural transformation
\[
  \phi_{x,A} \from (Djx \to A) \to A\,,
  \]
which, by the enriched Yoneda lemma, may be equivalently given by the natural transformation
\[
  \omega_x = 1 \xrightarrow{u_{D(jx)}} (D(jx) \to D(jx)) \xrightarrow{\phi_{x,D(jx)}} D(jx)\,.
  \]
We can use this natural transformation to model primitives in the language of the form
\[
  \choose_x \from jx\,,
  \]
for each object $x$ of $\X$, where we use $jx$ to refer to the datatype corresponding to the set $jx$.

The purpose of the final chapter will be to define a language with an operational semantics for which these primitives make sense, and prove a full abstraction result for it.

\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-03-01 Thesis/promonads.tex
Started writing thesis.

\documentclass{article}

\input{../common/preamble}

\begin{document}

\section{Promonads and parametric promonads}
\label{SecPromonads}

The purpose of this section is to shine some light on the definition of the \Mellies category, showing why it is natural to think about $[\X,\Set]$-enriched categories and why the \Mellies category may be considered analogous to the Kleisli category.

As a technical tool to prove the results we want, we shall introduce multicategories, which are a small generalization of monoidal categories.  
The main purpose of this generalization is to allow us to do without coends wherever possible: for example, while we need coends to make $[\X,\Set]$ into a monoidal category, we do not need them to make it into a multicategory.

The first half of this section is, in the interests of completeness, fairly technical, and may be skimmed over on a first reading.  
In section \ref{SecEndoprofunctors}, we introduce the multicategory of endoprofunctors on a category $\C$, which generalizes the monoidal category of endofunctors on $\C$.  
As monoids in $\End(\C)$ are called monads on $\C$, so we will call monoids in $\Endoprof(\C)$ \emph{promonads} on $\C$.  
We will observe that a promonad may be regarded as a sort of category, and that the Kleisli category may be characterized as the embedding of monads on $\C$ into promonads on $\C$.

The main result will then be to show that an $\X$-parametric promonad on a category $\C$ -- i.e., a multifunctor $\X \to \Endoprof(\C)$ -- may be regarded as a sort of $[\X,\Set]$-enriched category, and that the \Mellies category may similarly be regarded as an embedding of $\X$-parametric monads on $\C$ into $\X$-parametric promonads on $\C$.

\subsection{Multicategories}

\begin{definition}[\cite{Multicategories}]
  A \emph{multicategory} $\M$ is given by a set of objects $\text{Ob}(\M)$ whose elements are called \emph{objects} and, for each (possibly empty) list $a_1,\cdots,a_n$ of objects and each object $b$, a set
  \[
    \M_n(x_1,\cdots,x_n;y)
    \]
  whose elements are called the ($n$-ary) \emph{multimorphisms} $a_1,\cdots,a_n\to b$.

  Given collections $(a_{ij} \from i = 1,\cdots, n,j=1, \cdots, k_i), (b_i \from i = 1, \cdots, n), c$ of objects and multimorphisms
  \begin{mathpar}
    f_i \from a_{i1} , \cdots , a_{i,k_{i}} \to b_i
    \and
    g \from b_1, \cdots, b_n \to c\,,
  \end{mathpar}
  there is an operation that forms the \emph{composition}
  \[
    (f_1,\cdots, f_n);g \from a_{11},\cdots,a_{1k_1},\cdots,a_{n1}\cdots,a_{nk_n} \to c\,.
    \]
  Moreover, for each object $a$ of $\M$, there is a distinguished morphism $\id_a \from a \to a$ called the \emph{identity} on $a$.

  The composition and identity are subject to associativity and unitality conditions.
  Namely, let
  \begin{mathpar}
    \left(\mbox{\pbox{24pt}{$a_{pqr}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$ \\ $r=1,\cdots, l_{pq}$}}\right)
    \and
    \left(\mbox{\pbox{24pt}{$b_{pq}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$}}\right)
    \and
    (c_p\from p = 1,\cdots,n)
    \and
    d
  \end{mathpar}
  be collections of objects and let
  \begin{mathpar}
    f_{pq} \from a_{pq1},\cdots,a_{p,q,l_{pq}} \to b_{pq}
    \and
    g_p \from b_{p1},\cdots,b_{p,k_p} \to c_p
    \and
    d \from c_1,\cdots,c_n\to d
  \end{mathpar}
  be multimorphisms.
  Then we require that
  \begin{gather*}
    (((f_{11},\cdots,f_{1k_1});g_1),\cdots,((f_{n1},\cdots,f_{n,k_n});g_n));h\\
    =\\
    (f_{11},\cdots,f_{1k_1},\cdots,f_{n1},\cdots,f_{n,k_n});((g_1,\cdots,g_n);h)\,.
  \end{gather*}
  Furthermore, we require that if $f\from a_1,\cdots,a_n\to b$ is a multimorphism, then
  \begin{mathpar}
    (\id_{a_1},\cdots,\id_{a_n});f = f
    \and
    f = (f);\id_b\,.
  \end{mathpar}
\end{definition}

\begin{example}
  If $\C$ is an ordinary category, then $\C$ may be regarded as a multicategory $\hat{C}$ in which $\hat{C}_1(a;b)=\C(a,b)$ and $\hat{C}_n(a_1,\cdots,a_n;b)=\emptyset$ for $n\ne 1$.  
  At the same time, if $\M$ is a multicategory, then it has an \emph{underlying ordinary category} $\M_1$ whose morphisms are the morphisms in $\M$ with a single source object.
\end{example}
\begin{example}
  If $\M$ is a \emph{monoidal} category, then $\M$ may be regarded as a multicategory $\tilde{\M}$ with
  \begin{mathpar}
    \tilde{\M}_n(a_1,\cdots,a_n;b) = \M(a_1 \tensor \cdots \tensor a_n, b) \quad n\ge 1
    \and
    \tilde{\M}_0(;b) = \M(I, b)
  \end{mathpar}
  Since the tensor product is not necessarily strictly associative, it is not obvious exactly what we mean by $a_1 \tensor \cdots \tensor a_n$.
  In fact, it is enough to choose any one of the possible bracketings (e.g., to make $\blank\tensor\blank$ always associate to the right).

  Composition is then given by
  \begin{IEEEeqnarray*}{CCCCCC}
    & a_{11} \tensor \cdots \tensor a_{1k_1} & \tensor & \mathmakebox[4em]{\cdots} & \tensor & a_{n1} \tensor \cdots \tensor a_{nk_n} \\
    \xrightarrow{\mathmakebox[4em]{}} &
    (a_{11} \tensor \cdots \tensor a_{1k_1}) & \tensor & \mathmakebox[4em]{\cdots} & \tensor & (a_{n1} \tensor \cdots \tensor a_{nk_n}) \\
    \xrightarrow{\mathmakebox[4em]{f_1\tensor \cdots \tensor f_n}} &
    b_1 & \tensor & \mathmakebox[4em]{\cdots} & \tensor & b_n \\
    \xrightarrow{\mathmakebox[4em]{g}} &
    &&c\,,&&
  \end{IEEEeqnarray*}
  where the first arrow is induced from the normal monoidal coherences (exactly which ones depends on how we choose to interpret the iterated tensor product).
\end{example}

\subsection{Representable multicategories}

We call a multicategory \emph{representable} if it isomorphic to a multicategory that arises from a monoidal category in this way.  
The next theorem gives a criterion for a multicategory to be representable.

\begin{theorem}[\cite{RepresentableMulticategories}]
  \label{TheRepresentableMulticategories}
  Let $\M$ be a multicategory and suppose that for each natural number $n$ and each sequence $a_1,\cdots,a_n$ of objects of $\M$ there is an object $\tensor \vec{a}$ and a multimorphism
  \[
    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a
    \]
  that is \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
  \[
    f \from b_1,\cdots,b_k,a_1,\cdots,a_n,c_1,\cdots,c_l \to d
    \]
  factors uniquely through $\pi_{\vec a}$; i.e., there is a unique morphism
  \[
    \hat{f} \from b_1,\cdots,b_k,\tensor\vec{a},c_1,\cdots,c_l \to d
    \]
  such that
  \[
    f=(\id_{b_1},\cdots,\id_{b_k},\pi_{\vec a},\id_{c_1},\cdots,\id_{c_l});\hat{f}\,.
    \]
  Define an operation $\blank\tensor\blank$ that sends objects $a,b$ of $\M$ to $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
  Then $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
  \begin{itemize}
    \item $\blank\tensor\blank$ and $I$ are the monoidal product and unit of a monoidal category on $\M_1$, the underlying category of $\M$.
    \item For any sequence $a_1,\cdots a_n$ of objects of $\M$ there is a canonical isomorphism
      \[
        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a
        \]
      for any bracketing of the left hand side, and the associators and unitors in $\M_1$ are induced from these isomorphisms.
    \item The set of multimorphisms $a_1,\cdots,a_n \to b$ is in bijection with the set of morphisms $a_1\tensor\cdots\tensor a_n \to b$ for $n\ge1$, and the set of multimorphisms $\to b$ is in bijection with the set of morphisms $I \to b$, and these bijections commute with the multicategory composition in $\M$ and the composition in $\M_1$.
  \end{itemize}
\end{theorem}

\begin{definition}
  A \emph{symmetric multicategory} is a multicategory $\M$ together with an action of the symmetric group on the sets $\M_n(a_1,\cdots,a_n;b)$ that respects composition.  
  In other words, for each natural number $n$, each multimorphism $f\from a_1,\cdots,a_n\to b$ and each permutation $\sigma$ of $\{1,\cdots,n\}$ there is a multimorphism
  \[
    \sigma_* f \from a_{\sigma(1))},\cdots,a_{\sigma(n)} \to b
    \]
  such that if $(a_{ij}\from i=1,\cdots,n), (b_i\from i = 1,\cdots,n)$ are objects, 
  \begin{mathpar}
    f_i \from a_{i1},\cdots,a_{i,k_i} \to b_i
    \and
    g \from b_1,\cdots,b_n \to c
  \end{mathpar}
  are multimorphisms, $\sigma_i$ is a permutation of $\{1,\cdots,k_i\}$ and $\tau$ is a permutation of $\{1,\cdots,n\}$, then
  \[
    ({\sigma_1}_* f_q,\cdots,{\sigma_n}_*f_n);(\tau_*g) = (\tau*(\sigma_1,\cdots,\sigma_n))_*((f_1,\cdots,f_n);g)\,,
    \]
  where $\tau*(\sigma_1,\cdots,\sigma_n)$ is the permutation of
  \[
    \{(1,1),\cdots,(1,k_1),\cdots,(n,1),\cdots,(n,k_n)\}
    \]
  that sends $(i,j)$ to $(\tau(i),\sigma_i(j))$.

  Moreover, we require that for any morphism $f\from a_1,\cdots,a_n\to b$ and permutations $\sigma,\tau$ of $\{1,\cdots,n\}$ we have
  \begin{mathpar}
    \sigma_*\tau_*f = (\sigma\circ\tau)_*f
    \and
    \id_* f = f
  \end{mathpar}
\end{definition}

\begin{example}
  Any multicategory arising from an ordinary category is symmetric.
\end{example}
\begin{example}
  A monoidal category is a symmetric multicategory if and only if it is a symmetric monoidal category.  
\end{example}

\subsection{Product and unit multicategories}

\begin{definition}
  Let $\M,\N$ be multicategories.  
  The \emph{product multicategory} $\M\times\N$ has, as objects, pairs $(a,b)$, where $a$ is an object of $\M$ and $b$ an object of $\N$.  
  The multimorphisms are given by
  \[
    (\M\times\N)_n((a_1,b_1),\cdots,(a_n,b_n);(c,d)) = \M_n(a_1,\cdots,a_n;c)\times\N_n(b_1,\cdots,b_n;d),.
    \]
  Composition and the identity are easily defined pointwise.
\end{definition}

\begin{definition}
  The \emph{unit multicategory} $1$ has a single object $I$, and for each $n$, the set
  \[
    1_n(I,\cdots,I;I)
    \]
  is a singleton.

  This is a representable multicategory; indeed, it may be identified with the usual unit monoidal category.
\end{definition}

\subsection{Multifunctors and multinatural transformations}

\begin{definition}
  Let $\M,\N$ be multicategories.  
  A \emph{multifunctor} from $\M$ to $\N$ is a map $F$ from the objects of $\M$ to the objects of $\N$ together with, for each list $a_1,\cdots,a_n,b$ of objects of $\M$, a function
  \[
    \M_n(a_1,\cdots,a_n;b) \to \N_n(F a_1,\cdots,F a_n; F b)
    \]
  that commutes with the composition operator.
\end{definition}

\begin{definition}
  Given multicategories $\M,\N$ and multifunctors $F,G\from \M \to \N$, a \emph{multinatural transformation} $\phi$ is given by morphisms $\phi_a \from F a \to G a$ for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
  \[
    \begin{tikzcd}[column sep=36pt]
      Fa_1,\cdots, Fa_n \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_n}}"] \arrow[d, "Ff"']
        & Ga_1,\cdots, Ga_n \arrow[d, "Gf"] \\
      Fb \arrow[r, "\phi_b"]
        & Gb
    \end{tikzcd}
    \]
\end{definition}

\begin{proposition}
  If $\M,\N$ are monoidal categories, considered as multicategories, then multifunctors $\M\to\N$ are the same thing as lax monoidal functors.  
  Multinatural transformations are the same thing as monoidal natural transformations.
\end{proposition}

\begin{definition}
  Let $\M,\N$ be multicategories, where $\M$ is symmetric.  
  Then the collection of multifunctors $\M\to\N$ forms a multicategory.  
  A multimorphism $F_1,\cdots,F_n\Rightarrow G$, where $F_1,\cdots,F_n,G$ are multifunctors $\M\to \N$, is given by a family
  \[
    \phi_a \from F_1(a),\cdots,F_n(a) \to G(a)
    \]
  such that for any multimorphism $f\from a_1,\cdots,a_m\to b$ in $\M$, the diagram
  \[
    \begin{tikzcd}[column sep=48pt]
      F_1(a_1),\cdots,F_n(a_1),\cdots,F_1(a_m),\cdots,F_n(a_m) \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_m}}"] \arrow[d, "\sigma_*"']
        & G(a_1),\cdots,G(a_m) \arrow[dd, "Gf"] \\
      F_1(a_1),\cdots,F_1(a_m),\cdots,F_n(a_1),\cdots,F_n(a_m) \arrow[d, "{F_1f,\cdots,F_nf}"']
        & \\
      F_1(b),\cdots,F_n(b) \arrow[r, "\phi_b"]
        & G(b)
    \end{tikzcd}
    \]
  commutes, where $\sigma$ is the permutation of
  \[
    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\}
    \]
  that sends $(i,j)$ to $(j,i)$.
\end{definition}

\subsection{Monoids in multicategories}

\begin{definition}
  \label{DefMonoidMulticategory}
Let $\M$ be a multicategory.

  Then a \emph{monoid} in $\M$ is an object $a$ of $\M$ together with multimorphisms
  \begin{mathpar}
    m\from a,a\to a
    \and
    e \from \to a
  \end{mathpar}
  satisfying the following associativity and unitality laws.
  \begin{mathpar}
    \begin{tikzcd}
      a,a,a \arrow[r, "{m,\id_a}"] \arrow[d, "{\id_a,m}"']
        & a,a \arrow[d, "m"] \\
      a,a \arrow[r, "m"]
        & a
    \end{tikzcd}
    \and
    \begin{tikzcd}
      a \arrow[r,"\id_a"] \arrow[d, "{e_a,\id_a}"']
        & a \\
      a,a \arrow[ur, "m"']
        &
    \end{tikzcd}
    \and
    \begin{tikzcd}
      a \arrow[r, "\id_a"] \arrow[d, "{\id_a,e_a}"']
        & a \\
      a,a \arrow[ur, "m"']
        &
    \end{tikzcd}
  \end{mathpar}
\end{definition}

Note that a monoid in a multicategory $\M$ may also be defined to be a multifunctor $1 \to \M$ \cite[2.1.11]{Multicategories}.

\subsection{Categories enriched over multicategories}

\begin{definition}
  \label{DefEnrichedCategoryMulticategory}
  Let $\V$ be a multicategory.  
  Then a \emph{$V$-enriched category} $\C$ is given by a collection $\text{Ob}(\C)$ of objects together with, for each pair $a,b$ of objects, an object
  \[
    \C(a,b)
    \]
  of $\V$ and, for objects $a,b,c$ of $\C$, composition and identity multimorphisms
  \begin{mathpar}
    ;_{a,b,c} \from \C(a,b),\C(b,c) \to \C(a,c)
    \and
    \eta_a \from \to \C(a,a)
  \end{mathpar}
  that satisfy the following associativity and unitality laws for all objects $a,b,c,d$ of $\C$.
  \begin{mathpar}
    \begin{tikzcd}[column sep=12ex]
      \C(a,b),\C(b,c),\C(c,d) \arrow[r, "{;_{a,b,c},\id_{\C(c,d)}}"] \arrow[d, "{\id_{\C(a,b)},;_{b,c,d}}"']
        & \C(a,c),\C(c,d) \arrow[d, "{;_{a,c,d}}"] \\
      \C(a,b),\C(b,d) \arrow[r, "{;_{a,b,d}}"]
        & \C(a,d)
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \C(a,b) \arrow[r, "{\id_{\C(a,b)}}"] \arrow[d, "{\eta_a,\id_{\C(a,b)}}"']
        & \C(a,b) \\
      \C(a,a),\C(a,b) \arrow[ur, "{;_{a,a,b}}"']
        &
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \C(a,b) \arrow[r, "{\id_{\C(a,b)}}"] \arrow[d, "{\id_{\C(a,b)},\eta_b}"']
        & \C(a,b) \\
      \C(a,b),\C(b,b) \arrow[ur, "{;_{a,b,b}}"']
        &
    \end{tikzcd}
  \end{mathpar}
\end{definition}

\begin{remark}
  These definitions clearly generalize the same definitions for categories enriched over a monoidal category.

  In particular, a monoid in a multicategory $\M$ is the same thing as an $\M$-enriched category with a single object.

  Another equivalent definition of a monoid in a multicategory $\M$ is that it is a multifunctor from $1$ to $\M$, where $1$ is the unit monoidal category, considered as a multicategory.
\end{remark}

\begin{remark}
  If $\V$ is a symmetric multicategory and $\C$ is a $\V$-enriched category, then we may define the \emph{opposite category} $\oppcat{\C}$ whose objects are the objects of $\C$ and where
  \[
    \oppcat\C(a,b)=\C(b,a)\,.
    \]
  Composition is defined by
  \[
    \C(b,a),\C(c,b) \xrightarrow{\tau_*}
    \C(c,b),\C(b,a) \xrightarrow{;_{c,b,a}}
    \C(c,a)\,,
    \]
  where $\tau$ is the permutation that transposes the two values.
\end{remark}

\subsection{Multicategory-enriched functors and natural transformations}

\begin{definition}
  Let $\C,\D$ be categories enriched over some multicategory $\V$.  
  An \emph{$\V$-enriched functor} $F \from \C \to \D$ is a map $F$ from the objects of $\C$ to the objects of $\D$ together with, for each, pair $a,b$ of objects of $\C$, a (unary) multimorphism
  \[
    F \from \C(a,b) \to \D(F(a),F(b))
    \]
  such that for all $a, b, c$ the following diagrams commute.
  \begin{mathpar}
    \begin{tikzcd}[column sep=48pt]
      \C(a, b), \C(b, c) \arrow[r, "{;_{a,b,c}}"] \arrow[d, "{F,F}"']
        & \C(a,c) \arrow[d, "F"] \\
      \D(F(a), F(b)), \D(F(b), F(c)) \arrow[r, "{;_{F(a),F(b),F(c)}}"]
        & \D(F(a), F(c))
    \end{tikzcd}
    \and
    \begin{tikzcd}
       \arrow[r, "\eta_a"] \arrow[dr, "\eta_{F(a)}"']
        & \C(a,a) \arrow[d, "F"] \\
      %
        & \D(F(a),F(a))
    \end{tikzcd}
  \end{mathpar}
\end{definition}

\begin{definition}
  Let $\C,\D$ be categories enriched over a multicategory $\V$ and let $F,G\from \C \to \D$ be $\V$-enriched functors.
  An \emph{$\V$-enriched natural transformation} $\phi\from F \Rightarrow G$ is given by a family of $0$-ary multimorphisms
  \[
    \phi_a \from \to \D(F(a),G(a))
    \]
  such that for all objects $a,b$ the following diagram commutes.
  \[
    \begin{tikzcd}
      \C(a,b) \arrow[r, "{F,\phi_b}"] \arrow[d, "{\phi_a,G}"']
        & \D(F(a),F(b)),\D(F(b),G(b)) \arrow[d, "{;_{F(a),F(b),G(b)}}"] \\
      \D(F(a),G(a)),\D(G(a),G(b)) \arrow[r, "{;_{F(a),G(a),G(b)}}"]
        & \D(F(a), G(b))
    \end{tikzcd}
    \]
\end{definition}

\subsection{The categories enriched over a symmetric multicategory form a multicategory}

\begin{definition}
  Let $\V$ be a symmetric multicategory.
  Given $\V$-enriched categories $\C_1,\cdots,\C_n,\D$, a multimorphism
  \[
    F\from \C_1,\cdots,\C_n \to \D
    \]
  is given by a function
  \[
    F \from \text{Ob}(\C_1)\times \cdots \times \text{Ob}(\C_n) \to \text{Ob}(\D)
    \]
  together with, for each $a_i,b_i\in \text{Ob}(\C_i)$, a multimorphism
  \[
    F \from \C_1(a_1,b_1) , \cdots , \C_n(a_n,b_n) \to \D(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n))\,,
    \]
  such that the diagrams in Figure \ref{fig:VEnrichedMulticategoryFunctors} commute.  
  \begin{SidewaysFigure}
    \centering
    \begin{mathpar}
      \begin{tikzcd}[ampersand replacement=\&, column sep=116pt]
        \C_1(a_1,b_1),\C_1(b_1,c_1),\cdots,\C_n(a_n,b_n),\C_n(b_n,c_n) \arrow[r, "{;_{a_1,b_1,c_1},\cdots,;_{a_n,b_n,c_n}}"] \arrow[d, "\sigma_*"']
          \& \C_1(a_1,c_1),\cdots,\C_n(a_n,c_n) \arrow[dd, "F"] \\
        \C_1(a_1,b_1),\cdots,\C_n(a_n,b_n),\C_1(b_1,c_1),\cdots,\C_n(b_n,c_n) \arrow[d, "F"']
          \& \\
        \D(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n)),\D(F(b_1,\cdots,b_n),F(c_1,\cdots,c_n)) \arrow[r, "{;_{F(a_1,\cdots,a_n),F(b_1,\cdots,b_n),F(c_1,\cdots,c_n)}}" yshift=0.3em]
          \& \D(F(a_1,\cdots,a_n),F(c_1,\cdots,c_n))
      \end{tikzcd}
      \\
      \vspace{25pt}
      \\
      \begin{tikzcd}[ampersand replacement=\&]
        { } \arrow[r, "{\eta_{a_1},\cdots,\eta_{a_n}}"] \arrow[dr, "{\eta_{F(a_1,\cdots,a_n)}}"']
          \& \C_1(a_1,a_1),\cdots,\C_n(a_n,a_n) \arrow[d, "F"] \\
        %
          \& \D(F(a_1,\cdots,a_n),F(a_1,\cdots,a_n))
      \end{tikzcd}
    \end{mathpar}
    \caption{The rules for preservation of composition and identity by multimorphisms of $\V$-enriched functors are similar to those for ordinary enriched functors.  
    Note that it is essential for the $\V$ to be a symmetric multicategory.  
    This generalizes the usual construction for categories enriched over a symmetric monoidal category.}
    \label{fig:VEnrichedMulticategoryFunctors}
  \end{SidewaysFigure}

  In the case $n=1$, this is the same thing as a $\V$-enriched functor from $\C_1$ to $\D$.
  We will use the word `functor' to refer to the more general multimorphisms between $\V$-enriched categories in the case that $\V$ is symmetric.
\end{definition}

\subsection{Change of base}

Let $\M,\N$ be multicategories, let $F\from \M \to \N$ be a multifunctor and let $\C$ be an $\M$-enriched category.  
Then we can form an $\N$-enriched category $F_*\C$ whose objects are the objects of $\C$ and where the morphisms are given by the formula
\[
  F_*\C(a,b) = F(\C(a,b))\,.
  \]
We get composition and identities by applying the multifunctor $F$ to the composition and identity multimorphisms in $\C$.
By functoriality of $F$, these composition and identities are associative and unital, meaning that $F_*\C$ is indeed an $\N$-enriched category.

This process is called \emph{base change along $F$}.

\subsection{Closed multicategories}

\begin{definition}[\cite{ClosedMulticategories}]
  We say that a multicategory $\M$ is \emph{closed} if for any pair $a,c$ of objects, there exists an object
  \[
    \underline{\M}(a,c)
    \]
  and a multimorphism
  \[
    \ev_{a,c} \from a,\underline{\M}(a,c) \to c
    \]
  such that for any sequence $b_1,\cdots,b_n$ of objects of $\M$, the function
  \begin{IEEEeqnarray*}{rCcCc}
    \kappa_{a,b_1,\cdots,b_n,c} & \from & \M_n(b_1,\cdots,b_n;\underline{\M}(a,c)) & \to & \M_{n+1}(a,b_1,\cdots,b_n;c) \\
    && f & \mapsto & (\id_a,f);\ev_{a,c}
  \end{IEEEeqnarray*}
  is a bijection.
\end{definition}

\begin{proposition}[\cite{ClosedMulticategories}]
  If $\V$ is a closed multicategory, then $\V$ gives rise to the structure of a $\V$-enriched category on the underlying category $\V_1$ of $\V$.  
  We will also call this category $\V_1$, relying on context to distinguish the two.  
  The objects of $\V_1$ are the objects of $\V$, while the morphisms are given by
  \[
    \V_1(a,b) = \underline{\V}(a,b)\,.
    \]
\end{proposition}

If $\V$ is a closed multicategory and $\C_1,\cdots,\C_n$ are $\V$-enriched categories, then a functor $\C_1,\cdots,\C_n \to \V$ is given by a map $\text{Ob}(\C_1)\times\cdots\times\text{Ob}(\C_n) \to \text{Ob}(\V)$ and, for each $a_i,b_i\in \text{Ob}(\C_i)$, a multimorphism
\[
  \C_1(a_1,b_1),\cdots,\C_n(a_n,b_n) \to \underline{\V}(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n))
  \]
By the definition of a closed multicategory, this is equivalent to providing a multimorphism
\[
  F(a_1,\cdots,a_n),\C_1(a_1,b_1),\cdots,\C_n(a_n,b_n) \to F(b_1,\cdots,b_n)\,.
  \]
We will use the letter $p$ to refer to these multimorphisms and their various permutations.

We have seen so far that multicategories provide us with a rather straightforward generalization of monoidal categories.  
We might ask the question, then: why make this generalization?

To answer this question, we introduce some natural multicategories that are not representable.

\subsection{The multicategory of endoprofunctors}
\label{SecEndoprofunctors}

Let $\C,\D$ be ordinary categories.  
Recall that a \emph{profunctor} $F \from \C \pto \D$ is an ordinary functor $\oppcat\C \times \D\to\Set$.

More generally, if $\C,\D$ are enriched over some symmetric closed multicategory $\V$, then a $\V$-enriched profunctor $F \from \C \pto \D$ is a $\V$-enriched functor $\oppcat\C\times\D\to\V_1$.

Let $F_1,\cdots,F_n,G \from \oppcat \C \times \C \to \V$ be $\V$-enriched profunctors $\C\pto \C$, where $\C$ is a $\V$-enriched category.

We then define a multimorphism $\phi\from F_1,\cdots,F_n \Rightarrow G$ to be given by a family of multimorphisms
\[
  \phi_{a,b_1,\cdots,b_{n-1},c} \from F_1(a,b_1),\cdots,F_n(b_{n-1},c) \to G(a,c)
  \]
that make the diagrams in Figure \ref{FigExtranatural} commute.

A $0$-ary multimorphism $\to G$ is an ordinary enriched natural transformation $\C(a,c) \to G(a,c)$.
\begin{figure}
  \begin{mathpar}
    \begin{tikzcd}[column sep=21pt]
      {\C(a,a'),F_1(a',b_1),\cdots,F_n(b_{n-1},c),\C(c,c')} \arrow[r, "{\id,\phi_{a',\vec{b},c},\id}", xshift=-2ex, shorten=-1.8ex] \arrow[d, "{p,\id,\cdots,\id,p}"']

        & \C(a,a'),G(a',c),G(c,c') \arrow[d, "p"] \\
      F_1(a,b_1),\cdots,F_n(b_{n-1},c') \arrow[r, "{\phi_{a,\vec{b},c'}}"]
        & \G(a,c')
    \end{tikzcd}
    \and
    \begin{tikzcd}[column sep=-120pt]
      & F_1(a,b_1),\C(b_1,b_1'),F_2(b_1',b_2),\cdots,F_{n-1}(b_{n-2}',b_{n-1}),\C(b_{n-1},b_{n-1}'),F_n(b_{n-1}',c)
      \arrow[dr, "{\id,p,\cdots,p}"] \arrow[dl, "{p,\cdots,p,\id}"'] & \\
      F_1(a,b_1'),\cdots,F_n(b_{n-1}',c) \arrow[dr, "{\phi_{a,\vec{b'},c}}"'] & &
      F_1(a,b_1),\cdots,F_n(b_{n-1},c) \arrow[dl, "{\phi_{a,\vec{b},c}}"]  \\
        & G(a,c) &
    \end{tikzcd}
  \end{mathpar}
  \caption{The coherences we require on the multimorphisms between endoprofunctors are essentially the axioms for an extranatural transformation as in \cite{ExtranaturalTransformations}.}
  \label{FigExtranatural}
\end{figure}

We say that $\phi_{a,b_1,\cdots,b_{n-1},c}$ is \emph{natural} in $a$ and $c$ and \emph{extranatural} in the $b_i$.

We will often drop the component objects from $\phi$ and from the profunctors in question where they can be inferred from context.

We compose these multimorphisms pointwise.
The following proposition shows that this is indeed a well-defined composition.

\begin{proposition}
  Let $\V$ be a symmetric closed multicategory and let $\C$ be a $\V$-enriched category.
  Let $F_1,\cdots F_n,G_1,\cdots,G_m,H$ be profunctors $\C \pto \C$, and let $0=k_0,\cdots,k_m=n$ be a (not necessarily strictly) increasing subsequence of $\{0,\cdots,n\}$.  
  Let $\phi^{(i)} \from F_{k_i + 1},\cdots,F_{k_{i+1}} \to \G_i, \psi\from G_1,\cdots,G_m \to G$ be multimorphisms of profunctors.

  Then the family of multimorphisms
  \[
    F_1,\cdots,F_n
    \xrightarrow{\phi^{(1)},\cdots,\phi^{(m)}}
    G_1,\cdots,G_m
    \xrightarrow{\psi}
    H
    \]
  forms a multimorphism $F_1,\cdots,F_n\to H$.
\end{proposition}
\begin{proof}
  For the first condition (naturality), we have
  \[
    \begin{tikzcd}[column sep=60pt]
      \C,F_1,\cdots,F_n,\C \arrow[r, "{\id,\phi^{(1)},\cdots,\phi^{(m)},\id}"] \arrow[d, "{p,\id,\cdots,\id,p}"']
        & \C,\G_1,\cdots,\G_m,\C \arrow[r, "{\id,\psi,\id}"] \arrow[d, "{p,\id,\cdots,\id,p}"]
          & \C,H,\C \arrow[d, "p"] \\
      F_1,\cdots,F_n \arrow[r, "{\phi^{(1)},\cdots,\phi^{(m)}}"]
        & G_1,\cdots,G_m \arrow[r, "\psi"]
          & H
    \end{tikzcd}\,,
    \]
  where commutativity of the left hand square is the naturality condition on $\phi^{(1)}$ and $\phi^{(m)}$, while commutativity of the right hand square is the naturality condition for $\psi$.

  For the second condition (extranaturality), see Figure \ref{FigExtranaturalityComposition}.
\end{proof}

\begin{SidewaysFigure}
  \[
    \begin{tikzcd}[ampersand replacement=\&, row sep=80pt, column sep=30pt]
      %
        \& F_1,\cdots,F_n \arrow[dr, "{\phi^{(1)},\cdots,\phi^{(m)}}"]
          \&
            \& \\
      %
        \& F_1,\cdots,F_{k_1},\C,\cdots,\C,F_{k_{m-1}},\cdots,F_n \arrow[u, "{\id_{F_1},\cdots,\id_{F_{k_1}},p,\cdots,p,\id_{F_{k_{m-1}+1}},\cdots,\id_{F_n}}"' {description, near start, xshift=6ex}] \arrow[dr, "{\phi^{(1)},\id,\cdots,\id,\phi^{(n)}}" description]
          \& G_1,\cdots,G_m \arrow[dr, "\psi"]
            \& \\
      F_1,\C_1,F_2,\cdots,F_{n-1},\C,F_n \arrow[uur, "{\id,p,\cdots,p}"] \arrow[ddr, "{p,\cdots,p,\id}"'] \arrow[ur, "{\id,p,\cdots,p,\id_{\C},\cdots,\id_{\C},\id,\cdots,p}"' {description, xshift=6ex}] \arrow[dr, "{p,\cdots,p,\id,\id_{\C},\cdots,\id_{\C},p,\cdots,p,\id}" {description, xshift=6ex}]
        \&
          \& G_1,\C,G_2,\cdots,G_{m-1},\C,G_m \arrow[u, "{\id,p,\cdots,p}" description] \arrow[d, "{p,\cdots,p,\id}" description]
            \& H \\
      %
        \& F_1,\cdots,F_{k_1},\C,\cdots,\C,F_{k_{m-1}},\cdots,F_n \arrow[d, "{\id_{F_1},\cdots,\id_{F_{k_1}},p,\cdots,p,\id_{F_{k_{m-1}+1}},\cdots,\id_{F_n}}"' {description, near start, xshift=6ex}] \arrow[ur, "{\phi^{(1)},\id,\cdots,\id,\phi^{(n)}}" description]
          \& G_1,\cdots,G_m \arrow[ur, "\psi"']
            \& \\
      %
        \& F_1,\cdots,F_n \arrow[ur, "{\phi^{(1)},\cdots,\phi^{(m)}}"']
          \&
            \& \\
    \end{tikzcd}
    \]
  \caption{Proof that extranaturality is preserved by composition.  
  Commutativity of the central square is by extranaturality of the $\phi^{(i)}$, while that of the four-cornered triangle at the right is by extranaturality of $\psi$.  
  The triangles on the left commute automatically, while the parallelograms at the top and the bottom commute by naturality of the $\phi^{(i)}$.}
  \label{FigExtranaturalityComposition}
\end{SidewaysFigure}

This composition is associative, because it is given pointwise by composition in $\V$, and its unit is given by the identity natural transformation.  
This gives us a multicategory.

Suppose that $\V$ is the category of sets, so that the multimorphisms
\[
  F_1,\cdots,F_n \to G
  \]
are ordinary extranatural transformations
\[
  \phi_{a,\vec{b},c} \from F_1(a,b_1),\cdots,F_n(b_{n-1},c) \to G(a,c)\,.
  \]
Then the definition of the \emph{coend}
\[
  \int_{b_1,\cdots,b_{n-1}\from\C} F_1(a,b_1)\times\cdots\times F_n(b_{n-1},c)
  \]
is that it is universal among all objects admitting such an extranatural transformation out of them.  
It follows that in this case (and more generally, if $\V$ is a cocomplete monoidal category), that the multicategory of endoprofunctors on $\C$ is representable, with monoidal product given by
\[
  F\tensor G(a, c) = \int_{b\from \C} F(a,b) \times G(b,c)\,.
  \]
This is the usual notion of composition for $\Set$-enriched profunctors.  
However, if $\V$ is not cocomplete, then the multicategory of endoprofunctors on $\C$ need not be representable, even if $\V$ is representable.

We have only considered profunctors going from a category into itself.  
We might ask what structure is carried by more general profunctors enriched in a multicategory.
The answer is that they form an \emph{fc-multicategory} \cite{Multicategories}.

\subsection{Functors are a special case of profunctors}

The reason why we refer to a functors $F\from \oppcat\C,\D \to \V$ as a \emph{profunctors} $\C \pto \D$ is that they generalize ordinary functors $\C \to \D$.  
Specifically, if $F \from \C \to \D$ is a functor, then we can identify it with the profunctor
\[
  \tilde{F}(d,c) = \D(d, F(c)) \from \oppcat \D, \C \to \V\,.
  \]
This gives us an embedding of the monoidal category of endofunctors $\C \to \C$ into the multicategory of endoprofunctors $\C \pto \C$:

\begin{proposition}
  Let $\V$ be a closed symmetric multicategory and let $\C$ be a $\V$-enriched category.
  Let $F_1,\cdots,F_n, G\from \C \to \C$ be functors.  
  Then the set of natural transformations $F_1\circ\cdots\circ F_n \to G$ is naturally in bijection with the set of extranatural transformations
  \[
    \hat{F_1},\cdots,\hat{F_n} \to \hat{G}\,.
    \]
  \label{PropFunctorsIntoProfunctors}
\end{proposition}
\begin{proof}
  We have a natural multimorphism
  \begin{IEEEeqnarray*}{RL}
    &\C(a,F_1(b_1)),\cdots,\C(b_{n-1},F_n(c))\\
    \xrightarrow{\mathmakebox[6em]{\id,\cdots,F_1\circ\cdots\circ F_{n-1}}}&
    \C(a,F_1(b_1)),\cdots,\C(F_1\circ\cdots\circ F_{n-1}(b_{n-1}),F_1\circ\cdots\circ F_n(c))\\
    \xrightarrow{\mathmakebox[6em]{;^*}}&
    \C(a,F_1\circ\cdots\circ F_n(c))\,,
  \end{IEEEeqnarray*}
  which is natural in $a,c$ and extranatural in the $b_i$.

  If $\phi\from F_1\circ\cdots\circ F_n\to G$ is a natural transformation, then it gives rise (via postcomposition) to a natural transformation
  \[
    \C(a,F_1(\cdots(F_n(c))\cdots)) \to \C(a,G(c))\,,
    \]
  which we can compose with the multimorphism above to get the required extranatural transformation
  \[
    \C(a,F_1(b_1)),\cdots,\C(b_{n-1},F_n(c)) \to \C(a,G(c))\,.
    \]
  In the other direction, suppose that we have some extranatural transformation
  \[
    \phi_{a,\vec{b},c} \from \C(a,F_1(b_1)),\cdots,\C(b_{n-1},F_n(c)) \to \C(a,G(c))\,.
    \]
  Then we can take components of the form
  \[
    \phi_{a,F_1\circ\cdots\circ F_n(c),\cdots,F_n(c),c}\from \C(a,F_1\circ\cdots\circ F_n(c)),\cdots,\C(F_n(c),F_n(c)) \to \C(a,G(c))
    \]
  and compose with $\id,\eta,\cdots,\eta$ to get our natural transformation
  \[
    \C(a,F_a\circ\cdots\circ F_n(c)) \to \C(a,\G(c))\,.
    \]
  It is easy to check that these two constructions are inverses and that they respect composition of natural transformations.
\end{proof}

\subsection{Promonads are categories}

Since a monad was defined to be a monoid in the category of endofunctors on a category $\C$, we can define a \emph{promonad} to be a monoid in the multicategory of endoprofunctors on $\C$.

\begin{proposition}[See, e.g., \cite{Promonad}]
  \label{PropPromonadsAreCategories}
  Let $\V$ be a symmetric closed multicategory.  
  Let $\C$ be a $\V$-enriched category.  
  Then a promonad $\D\from \C\pto \C$ is the same thing as a $\V$-enriched category $\D$ that admits an identity-on-objects functor $j\from \C \to \D$.
\end{proposition}
\begin{proof}
  This is a matter of unwrapping the definitions.

  Let $\D\from \C \pto \C$ be such a promonad.  
  So $\D$ is given by a functor $\D \from \oppcat \C,\C \to \V$, together with extranatural transformations
  \begin{mathpar}
    m_{a,b,c} \from \D(a,b),\D(b,c) \to \D(a,c)
    \and
    e_{a,b} \from \C(a,b) \to \D(a,b)
  \end{mathpar}
  such that the following diagrams commute (see Definition \ref{DefMonoidMulticategory}).
  \begin{mathpar}
    \begin{tikzcd}[column sep=12ex]
      \D(a,b),\D(b,c),\D(c,d) \arrow[r, "{m_{a,b,c},\id}"] \arrow[d, "{\id,m_{b,c,d}}"']
        & \D(a,c),\D(c,d) \arrow[d, "{m_{a,c,d}}"] \\
      \D(a,b),\D(b,d) \arrow[r, "{m_{a,b,d}}"]
        & \D(a,d)
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \C(a,b),\D(b,c) \arrow[r, "p"] \arrow[d, "{e_{a,b},\id}"']
        & \D(a,c) \\
      \D(a,b),\D(b,c) \arrow[ur, "{m_{a,b,c}}"']
        &
    \end{tikzcd}
    \and
    \begin{tikzcd}
      \D(a,b),\C(b,c) \arrow[r, "p"] \arrow[d, "{\id,e_{a,b}}"']
        & \D(a,c) \\
      \D(a,b),\D(b,c) \arrow[ur, "{m_{a,b,c}}"']
        &
    \end{tikzcd}
  \end{mathpar}
  If we set $a=b$ in the second diagram and $b=c$ in the third, and compose with the identity multimorphisms $\eta$, then these are exactly the diagrams (see Definition \ref{DefEnrichedCategoryMulticategory}) for $\D$ to have the structure of a $\V$-enriched category on the collection of objects of $\C$!
  Moreover, $e_{a,b}$ gives us the enriched functor $\C\to \D$, which is the identity on objects and is the multimorphism $e_{a,b}$ on morphisms.

  We can show that this is indeed a functor using the diagram in Figure \ref{FigPromonadFunctorProof}.
  \begin{figure}[hbt]
    \[
      \begin{tikzcd}
        \C(a,b),\C(b,c) \arrow[rr, "{;_{a,b,c}}"] \arrow[dd, "{e_{a,b},e_{b,c}}"'] \arrow[dr, "{\id_{e_{b,c}}}" description]
          &
            & \C(a,c) \arrow[dd, "{e_{a,c}}"] \\
        %
          & \C(a,b),\D(b,c) \arrow[dl, "{e_{a,b},\id}" description] \arrow[dr, "p" description]
            & \\
        \D(a,b),\D(b,c) \arrow[rr, "{m_{a,b,c}}"]
          &
            & \D(a,c)
      \end{tikzcd}
      \]
    \caption{Proof that the identity-on-objects functor arising from a promonad is indeed a functor.  
    The proof uses naturality of $e_{a,b}$ for commutativity of the large triangle at the top right.}
    \label{FigPromonadFunctorProof}
  \end{figure}
\end{proof}

Consider the case that $\D$ is an actual functor, so that $\D(a,b)=\C(a,F(b))$ for some endofunctor $F\from\C\to\C$.  
Then, by Proposition \ref{PropFunctorsIntoProfunctors}, a promonad structure on $\D$ is the same thing as a monad structure on $F$.  
If we consider $\D$ as a category, then the objects of $\D$ are the objects of $\C$, and morphisms from $a$ to $b$ are morphisms from $a$ to $F(b)$ in $\C$; i.e., Kleisli morphisms for $F$.

If we work the definitions through the proof of Proposition \ref{PropFunctorsIntoProfunctors}, then we see that the composition of morphisms $f\from a \to F(b)$ and $g \from b \to F(c)$ in $\D$ is given by the composite
\[
  a \xrightarrow{f}
  Fb \xrightarrow{Fg}
  FFc \to
  Fc\,,
  \]
where the rightmost arrow arises from the promonad structure on $\D$.  
In other words, $\D$ is precisely the Kleisli category for the monad $F$:

\begin{slogan}
  \label{SlogKleisli}
  The Kleisli category is the category we get by considering functors as profunctors.
\end{slogan}

\subsection{The multicategory of functors}

Let $\X$ be a monoidal category and let $\M$ be a multicategory.
We define a multicategory $[\X,\M]$ where the objects are ordinary functors
\[
  \X \to \M_1
  \]
and where multimorphisms $F_1,\cdots,F_n\to G$ are natural transformations
\[
  \phi_{x_1,\cdots,x_n} \from F_1(x_1),\cdots,F_n(x_n)\to G(x_1\tensor\cdots\tensor x_n)\,.
  \]
\begin{remark}
  Suppose that $\M$ is the category of sets, regarded as a multicategory through its Cartesian structure.  
  Let $x_1,\cdots,x_n,y_1,\cdots,y_p$ be objects of $\X$.  
  Then for any collection of functors
  \[
    F_1,\cdots,F_n,G_1,\cdots,G_p,H \from \X \to \Set\,,
    \]
  the set of natural transformations
  \[
    \phi_{\vec{x},\vec{y}} \from \prod_i F_i(x_i) \times \prod_j G_j(y_j) \to H(x_1\tensor\cdots\tensor x_n\tensor y_1\tensor\cdots\tensor y_p)
    \]
  may be written as the end
  \[
    \int_{\vec{x},\vec{y}} \left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(\Tensor_i x_i \tensor \Tensor_j y_j\right)\right]\,.
    \]
  We may then perform some co/end calculus (See the similar computation in \cite{Pisani}, but note that that version is not quite sufficient to prove representability according to Theorem \ref{TheRepresentableMulticategories}).
  \begin{IEEEeqnarray*}{Cl}
    &\int_{\vec{x},\vec{y}} \left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(\Tensor_i x_i \tensor \Tensor_j y_j\right)\right]\\
    \cong&\int_{\vec{x},z,\vec{y}} \left[\X\left(\Tensor_i x_i,z\right),\left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(z \tensor \Tensor_j y_j\right)\right]\right]\\
    \cong&\int_{\vec{x},z,\vec{y}} \left[\prod_i F_i(x_i) \times \X\left(\Tensor_i x_i,z\right) \times \prod_j G_j(y_j),H\left(z \tensor \Tensor_j y_j\right)\right]\\
    \cong&\int_{z,\vec{y}}\left[\int^{\vec{x}} \left(\prod_i F_i(x_i) \times \X\left(\Tensor_i x_i,z\right)\right)\times\prod_j G_j(y_j),H\left(z\tensor\Tensor_j y_j\right)\right]
  \end{IEEEeqnarray*}
  In other words, this multicategory is representable by the Day convolution that we met in Definition \ref{DefDayConvolution}:
  \[
    (F\tensor_{\text{Day}} G)(z) = \int^{x,y} F(x) \times G(y)\times \X(x\tensor y,z)\,.
    \]
  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, or when the category $\M$ is not the enriching category.
\end{remark}

\subsection{Monoids on functors are multifunctors}
It might seem strange that the objects of the multicategory of functors are ordinary functors, ignoring the monoidal structure of $\X$ and the multicategory structure of $\M$.  
One way to make sense of this fact is to note that an object of a category $\C$ is the same thing as a functor
\[
  1 \to \C\,.
  \]
In the same way, perhaps the correct way to think of an `element' of a multicategory is that it is a \emph{multifunctor}
\[
  1 \to \M\,;
  \]
i.e., a monoid in $\M$.

\begin{proposition}
  Let $\X$ be a monoidal category and let $\M$ be a multicategory.  
  Then a monoid in $[\X,\M]$ is the same thing as a multifunctor $\X \to \M$.
  \label{PropMonoidInXMIsMultifunctorXToM}
\end{proposition}

This can be proved by setting $\N=1$ in the following stronger result.

\begin{proposition}[{\cite[2.8]{Pisani}}]
  Let $\X$ be a monoidal category and let $\M,\N$ be multicategories.  
  \label{PropPisani}
  Then a multifunctor $\N \to [\X,\M]$ is the same thing as a multifunctor $\N\times\X \to \M$.
\end{proposition}

\subsection{Two perspectives on monoids in $\Set$}

We now come to our main result of the section.  
By way of motivation, consider the two ways of generalizing the notion of an internal monoid in $\Set$.

\begin{enumerate}
  \item A monoid in $\Set$ may be regarded as a lax monoidal functor (i.e., a multifunctor) $1 \to \Set$.  
    This generalizes to arbitrary lax monoidal functors $\X \to \Set$, for monoidal categories $\X$.
  \item A monoid in $\Set$ may also be regarded as a category with a single object.  
    This generalizes to arbitrary categories.
\end{enumerate}

The work we have done allows us to unify these into a single definition.  
From Proposition \ref{PropPromonadsAreCategories}, we know that a category with one object is the same thing as a monoid in the category $\Endoprof_\Set(*)$, where $*$ is the category with a single object and only an identity morphism.

We can clearly generalize this to the idea of a monoid in $\Endoprof_\Set(\C)$ for an arbitrary category $\C$.  
This then generalizes to the universal idea of a multifunctor
\[
  \X \to \Endoprof_\Set(\C)\,,
  \]
(which we might call a \emph{parametric promonad on $\C$ parameterized by $\X$}), which generalizes both lax monoidal functors $\X \to \Set$ (when $\C=*$) and $\Set$-enriched categories (when $\X=1$).

However, we can also do things the other way round.  
From Proposition \ref{PropMonoidInXMIsMultifunctorXToM}, a lax monoidal functor $\X \to \Set$ is a monoid in the multicategory $[\X,\Set]$.  
This is the same thing as an $[\X,\Set]$-enriched category with a single object, so another way of generalizing monoids in $\Set$ is to generalize them to monoids in the multicategory
\[
  \Endoprof_{[\X,\Set]}(\C)
  \]
for some monoidal category $\X$ and some $[\X,\Set]$-enriched category $\C$.

This generalizes categories in the case that $\X=1$.  
It generalizes monoidal functors $\X \to \Set$ in the case that $\C$ is the enriched category $*_{[\X,\Set]}$ with a single object $()$, where the morphisms $() \to ()$ are given by the functor $[I,\blank]$, for $I$ the monoidal unit in $\X$, this being the initial object in $[\X,\Set]$.

Our result is that these two ways of unifying the two generalization of a monoid in fact give the same result.  
The only ingredient we are missing is an appropriate change of base to move from ordinary $\Set$-enriched categories to $[\M,\Set]$-enriched categories.

\begin{definition}
  Let $\X$ be a monoidal category.  
  We have a multifunctor
  \[
    \X \to [\Set,\Set]
    \]
  given by
  \[
    x \mapsto \X(I,x) \times \blank\,.
    \]
  By Proposition \ref{PropPisani}, this may equivalently be given as a multifunctor
  \[
    \omega_\X\from\Set \to [\X,\Set]
    \]
  that sends a set $A$ to the functor
  \[
    \X(I,\blank)\times A\,.
    \]
\end{definition}

The important property of this particular multifunctor is as follows.

\begin{proposition}
  If $\C_1,\cdots,\C_n$ are categories, then $[\X,\Set]$-enriched functors ${\omega_\X}_*\C_1,\cdots,{\omega_\X}_*\C_n\to[\X,\Set]$ are the same thing as ordinary functors from $\C_1\times\cdots\times\C_n$ to $[\X,\Set]$.
\end{proposition}
\begin{proof}
  Let $\C_1,\cdots,\C_n$ be categories.  
  An $[\X,\Set]$-enriched functor
  \[
    F \from {\omega_\X}_*\C_1,\cdots,{\omega_\X}_*\C_n \to [\X,\Set]
    \]
  is given by a map
  \[
    F\from \text{Ob}(\C_1)\times\cdots\times\text{Ob}(\C_n) \to \text{Ob}([\X,\Set])\,,
    \]
  together with, for all objects $a_i,b_i$ of $\C_i$, a multimorphism
  \[
    {\omega_X}_*\C_1(a_1,b_1),\cdots,{\omega_X}_*\C_n(a_n,b_n),F(a_1,\cdots,a_n)\to F(b_1,\cdots,b_n)\,;
    \]
  i.e., a natural transformation
  \[
    \left(\prod_i \X(I,x_i)\times\C(a_i,b_i)\right) \times F(a_1,\cdots,a_n)(y) \to F(b_1,\cdots,b_n)(x_1\tensor\cdots\tensor x_n\tensor y)\,.
    \]
  By the Yoneda lemma, such a natural transformation is the same thing as a natural transformation
  \[
    \prod_i \C(a_i,b_i) \times F(a_1,\cdots,a_n)(y) \to F(b_1,\cdots,b_n)(I \tensor \cdots \tensor I \tensor y)\,;
    \]
  i.e., a natural transformation
  \[
    \C(a_1,b_1)\times\cdots\times\C(a_n,b_n) \times F(a_1,\cdots,a_n)(y) \to F(b_1,\cdots,b_n)(y)\,.
    \]
  But this is precisely the data of an ordinary functor $\C_1\times\cdots\times\C_n \to [\X,\Set]$.

  By naturality of the Yoneda transformation (and the left unitor), this process preserves and reflects the property of respecting composition and units.
  \label{PropOmegaProperty}
\end{proof}

\begin{theorem}[`Stokes's Theorem']
  \label{StokessTheorem}
  Let $\X$ be a monoidal category and let $\C$ be a category.  
  Then we have an isomorphism of multicategories
  \[
    [\X,\Endoprof_{\Set}(\C)] \cong \Endoprof_{[X,\Set]}({\omega_\X}_*\C)\,.
    \]
\end{theorem}
\begin{proof}
  Let $F \from \X\times\oppcat\C\times\C \to \Set$ be an ordinary functor.  
  We may view $F$ either as the object
  \[
    F(x, \blank, \blank) \from \X \to \Endoprof_\Set(\C)_1
    \]
  of $[\X,\Endoprof_{\Set}(\C)]$ or, by Proposition \ref{PropOmegaProperty}, as the object
  \[
    F(\blank, a, b) \from \oppcat \C \times \C \to [\X,\Set]
    \]
  of $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$.
  Moreover, every object of each of the two categories arises in such a way.  
  Our aim is to show that the two categories give rise to identical notions of multimorphisms between such $F$.

  Let $F_1,\cdots,F_n,G \from \X \times \oppcat\C\times\C\to \Set$ be functors.  
  Considering the $F_i$ as objects of $[\X,\Endoprof_\Set(\C)]$, a multimorphism $F_1,\cdots,F_n\to G$ is given by a transformation
  \[
    F_1(x_1,\blank,\blank),\cdots, F_n(x_n,\blank,\blank) \to G(x_1\tensor\cdots\tensor x_n,\blank,\blank)\,;
    \]
  natural in the $x_i$ i.e., a transformation
  \[
    F_1(x_1,a,b_1)\times\cdots\times F_n(x_n,b_{n-1},c) \to G(x_1\tensor\cdots\tensor x_n,a,c)\,.
    \]
  natural in the $x_i,a,c$ and extranatural in the $b_i$.

  A multimorphism $\to G$ is given by a multimorphism
  \[
    \to G(I,\blank,\blank)\,;
    \]
  i.e., a morphism
  \[
    \C(a,c) \to G(I,a,c)\,.
    \]

  Now let us consider the $F_i,G$ as objects of $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$.  
  A multimorphism $F_1,\cdots,F_n\to G$ is given by a transformation
  \[
    F_1(\blank,a,b_1),\cdots,F_n(\blank,b_{n-1},c) \to G(\blank,a,c)
    \]
  natural in $a,c$ and extranatural in the $b_i$; i.e., a transformation
  \[
    F_1(x_1,a,b_1)\times\cdots\times F_n(x_n,b_{n-1},c) \to G(x_1\tensor\cdots\tensor x_n,a,c)
    \]
  natural in $a$, $c$ and the $x_i$ and extranatural in the $b_i$.

  A multimorphism $\to G$ is given by an extranatural transformation
  \[
    \omega_\X(\C(a,c)) \to G(\blank,a,c)\,;
    \]
  i.e., a natural transformation
  \[
    \X(I,x)\times\C(a,c) \to \G(x,a,c)\,,
    \]
  which by the Yoneda lemma is the same thing as a natural transformation
  \[
    \C(a,c) \to \G(I,a,c)\,.
    \]
  Thus, the two multicategories are isomorphic.
\end{proof}

Now consider the case that we have a parametric monad $\blank.\blank\from\X \times \C \to \C$ on a category $\C$.  
By considering functors as profunctors, we may identify this with a multifunctor $\X \to \Endoprof_\Set(\C)$; i.e., a monoid in $[\X,\Endoprof_\Set(\C)]$.
Then, by Theorem \ref{StokessTheorem}, we may identify this multifunctor with a monoid in $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$; i.e., an $[\X,\Set]$-enriched promonad on ${\omega_\X}_*\C$.

But now, by Proposition \ref{PropPromonadsAreCategories}, this promonad is the same thing as an $[\X,\Set]$-enriched category with the same objects as $\C$ that admits an identity-on-objects $[\X,\Set]$-enriched functor out of ${\omega_X}_*(\C)$.

The objects of this $[\X,\Set]$-enriched category are the objects of $\C$.
By working the definitions through the proofs of Proposition \ref{PropFunctorsIntoProfunctors} and Theorem \ref{StokessTheorem}, we see that the object of morphisms from $a$ to $b$ is
\[
  x \mapsto \C(a,x.b)\,,
  \]
and that composition of morphisms is the multimorphism
\[
  \C(a,x.b) \times \C(b,y.c) \to \C(a,(x\tensor y).c)
  \]
in $[\X,\Set]$ given by sending morphisms $f\from a \to x.b$, $g\from b \to x.c$ to the composite
\[
  a
  \xrightarrow{f}
  x.b
  \xrightarrow{x.g}
  x.y.c \xrightarrow{m}
  (x\tensor y).c\,,
  \]
which is precisely the definition of composition in the \Mellies category.

We get a new analogue of Slogan \ref{SlogKleisli}.

\begin{slogan}
  The \Mellies category is precisely the $[\X,\Set]$-enriched category that we get by considering functors as profunctors.
\end{slogan}

\bibliographystyle{alpha}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-03-13 Thesis/thesis.tex
Started writing thesis.
Some more progress.

--- 2019-01-10 Thesis/thesis.tex
@@
 
+\usepackage{lua-visual-debug}
+
 \begin{document}
@@
 \section{Monads and Kleisli categories}
+\ref{SecMonads}
 
@@
 which is equal to $f$ by the coherence conditions on $m$ and $u$.
-This means that the Kleisli category may be thought of as begin freely generated from the original category $\C$ and a multiplicative natural transformation $\phi$.
+This means that the Kleisli category may be thought of as being freely generated from the original category $\C$ and a multiplicative natural transformation $\phi$.
 
 \begin{example}
-  The morphisms in the Kleisli category for the nonempty powerset monad $\powerset_+$ on $\Set$ are functions $A \to \powerset_+B$, which can be thought of as nondeterministic functions.  
+  The morphisms in the Kleisli category for the nonempty powerset monad $\powerset_+$ on $\Set$ are functions $A \to \powerset_+B$, which can be thought of as nondeterministic functional programs.  
   Given a set $A$, the morphism $\phi_A\from \powerset_+A \to A$ in $\Kl_{\powerset_+}$ can be interpreted as a `nondeterministic choice' function that accepts a nonempty set of elements of $A$ and nondeterministically chooses one of them.
@@
   Then the Kleisli category for the reader monad $R_z$ on $\C$ is generated over $\C$ by a natural transformation $\phi_y\from (z \to y) \to y$.  
-  By the enriched Yoneda lemma, such a natural transformation is always given by precomposition with some fixed morphism $\ask\from 1 \to z$.  
+  By the enriched Yoneda lemma, such a natural transformation is always given by precomposition with some fixed morphism $\ask_z\from 1 \to z$.  
   This means that $\Kl_{R_z}$ is suitable for modelling any situation in which we are generally working in $\C$, but need the ability to request a value of type $z$ (for example, a config file, a piece of user input or something else that isn't being passed into the function in question).
@@
 
-\subsection{Extended example: game semantics of time complexity}
-This is an extended example of using a reader monad, in the style of Example \ref{ExReaderMonadKleisli}.
-Let $\G$ be the category of games and visible single-threaded strategies as in \cite{SamsonGuyIAActive}.  
-So $\G$ is a sound and adequate model of Idealized Algol satisfying compact definability.
-Let $\bC$ be the denotation of the command type $\com$ of Idealized Algol.  
-Then the Kleisli category for the reader monad over $\bC$ is freely generated over $\G$ by a single morphism $1 \to \bC$.
-
-Let us extend Idealized Algol with a single term, $\sleep$, of type $\com$.
-This should be thought of as a command to the computer to pause for some fixed interval of time -- let us say a second -- before resuming execution.
-By Theorem \ref{FunctionalCompletenessCcc}, our Kleisli category is Cartesian closed.
-So it gives us a denotational semantics of IA+$\sleep$, in which the terms of IA are interpreted within $\G$ as in \cite{SamsonGuyIAActive} and the new term $\sleep$ is interpreted by the new morphism $1 \to \bC$.
-
-Let us now give an operational semantics to terms of IA+$\sleep$.  
-Let $\Gamma$ be an IA-context.
-Then a \emph{store} $s$ over $\Gamma$ is a list of pairs $(v\mapsto x)$, where each $v$ is the name for a $\Var$-type variable occurring in $\Gamma$ and $x$ is a value held in $v$.  
-We write $()$ for the empty store, $(s\vert v\mapsto x)$ for the store obtained from $s$ by adding or updating the variable $v$ to hold the value $x$ and $(s\vert v\mapsto \bot)$ for the store obtained by removing the variable $v$ from $s$.
-Given disjoint stores $s,t$ (i.e., stores whose sets of variables are disjoint), we write $s+t$ for the store obtained by concatenating together $s$ and $t$.
-
-Given a term $\Gamma\ts M$ in context, stores $s$,$s'$ over $\Gamma$, a value $c$ and a natural number $n$, we define a big-step relation
-\[
-  \Gamma,s\ts M\converges_n c,s'\,,
-  \]
-read as `in the context $\Gamma$, $s,M$ converges to $c,s'$ in time $n$'.  
-The rule for the constant $\sleep$ is given by
-\[
-  \inferrule*
-  { }
-  {\Gamma,s\ts \sleep\converges_1 \skipp,s}\,,
-  \]
-indicating that execution of the $\sleep$ command takes up an additional time step.  
-The other rules are the same as those given in \cite{SamsonGuyIAActive} for the $\converges$ relation, except that we have to modify them in order to take account of the new information we have added to the reduction relation (i.e., the time taken to converge).
-For example:
-\begin{mathpar}
-  \inferrule*
-  { }
-  {\Gamma,s\ts c \converges_0 c,s}
-  \and
-  \inferrule*
-  {\Gamma,s\ts M\converges_m\skipp,s'\\
-  \Gamma,s'\ts N\converges_n\skipp,s''}
-  {\Gamma,s\ts M;N\converges_{m+n}\skipp,s''}\,.
-\end{mathpar}
-If $P$ is a program (i.e., a term of type $\com$) then we write $P\converges_n$ as a shorthand for $,()\ts P \converges_n \skipp,()$.
-We say that $P$ \emph{diverges} and write $P\diverges$ if there is no $n$ such that $P\converges_n$.
-
-We now want a way to capture this operational behaviour within the denotational semantics.
-First, we note the Computational Adequacy result proved for the game semantics of Idealized Algol.
-
-\begin{proposition}[{\cite[21]{SamsonGuyIAActive}}]
-  Let $P$ be a term of type $\com$.  
-  Then $P\converges$ if and only if $\deno{P}\ne\bot$.
-  \label{SamsonGuyAdequacy}
+\subsection{Denotational Semantics}
+
+From now till the end of the chapter, we fix an (order-enriched) Cartesian closed category $\G$ that admits a denotational semantics of Idealized Algol satisfying Computational Adequacy and in which every compact element is definable.
+The prototypical example, of course, will be the category of games and visible strategies, but we will not exploit any properties of this model beyond the ones we have already mentioned, mentioning it only in examples where appropriate.
+
+Let $X\in \{\bB,\bN,\bC\}$ be a set that has an interpretation as an Idealized Algol type $X$, and write $X$ also for the corresponding object of $\G$.
+Write $\G_X$ as a shorthand for $\Kl_{R_X}\G$, the Kleisli category for the reader monad on $\G$ corresponding to the object $X$.  
+The purpose of the rest of this chapter will be to define a new language, give it a denotational semantics in $\G_X$, and prove a full abstraction result for this denotational semantics.
+
+\newcommand{\IAX}{{IA${}_X$}\xspace}
+\begin{definition}[{The language \IAX}]
+  The language \IAX is formed by taking Idealized Algol, and adding to it a new constant
+  \[
+    \ask_X
+    \]
+  with typing rule
+  \[
+    \inferrule{ }{\Gamma \ts \ask_X \from X}\,.
+    \]
+\end{definition}
+
+From Proposition \ref{pKleisli}, we know that there is a distinguished natural transformation $\phi_A \from (X \to A) \to A$ in $\G_X$; in particular, we have a morphism
+\[
+  \phi = \phi_X(\id_X) \from 1 \to X\,,
+  \]
+which will be the denotation of the term $\choose_X$.
+Together with the existing denotational semantics of Idealized Algol within $\G$, this gives us an inductively defined denotational semantics of \IAX within $\G_X$.
+
+Clearly any term-in-context of \IAX is of the form
+\[
+  \Gamma \ts M[\ask_X/x]\from T\,,
+  \]
+where
+\[
+  \Gamma,x\from X \ts M \from T
+  \]
+is a judgement of Idealized Algol.
+Given such a term-in-context, we know that the denotation of
+\[
+  \Gamma\ts (\lambda x.M) \ask_X \from T
+  \]
+is given by the composite
+\[
+  1 \xrightarrow{\phi}
+  X \xrightarrow{\deno{\Gamma,x \ts M}}
+  \deno{T}\,.
+  \]
+Now this last term is $\beta$-equivalent to our original term-in-context $\Gamma\ts M$.  
+Since $\G_X$ is Cartesian closed (by Theorem \ref{FunctionalCompletenessCcc}), the $\beta$ rule is valid in $\G_X$, and this means that the composite above is an alternative definition of the denotation of $\Gamma\ts M$.
+
+\subsection{Operational Semantics}
+
+We now define the operational semantics of \IAX and prove a computational adequacy result for our denotational semantics.
+
+\begin{definition}[Operational semantics of \IAX]
+  Let $X^*$ be the free monoid on the set $X$; i.e., the set of all finite strings of elements of $X$.
+  Given $u,v\in X^*$ we shall write $u\cat v$ for their product in $X^*$; i.e., the concatenation of the two strings.
+  We shall write $\epsilon$ for the unit in $X^*$; i.e., the empty string.
+
+  If $u\in X^*$,we write $|u|$ for the length of $u$.
+  If $0\le n < |u|$, then we write $u^{(n)}$ for the corresponding element of $u$, numbering from $0$.
+
+  We inductively define a relation $\Gamma,s\ts M\converges_u c,s'$, where $\Gamma$ is a $\Var$-context, $M,c$ are terms of \IAX with all free variables in $\Gamma$, where $c$ is an IA canonical form, $s,s'$ are $\Gamma$-stores and $u\in X^*$.
+  The definition of this relation is shown in Figure \ref{FigIaxOpSem}.
+
+  \begin{figure}
+    \begin{mathpar}
+      \inferrule*{ }{\Gamma,s\ts c \converges_\epsilon c,s}
+      \and
+      \inferrule*{\Gamma,s \ts M \converges_u \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x] \converges_v c,s''}{\Gamma,s \ts MN \converges_{u\cat v} c,s''}
+      \and
+      \inferrule*{\Gamma,s \ts M(\Y M) \converges_u c,s'}{\Gamma,s \ts \Y M \converges_u c,s'}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u n,s'}{\Gamma,s\ts \suc M \converges_u n+1,s'}
+      \\\and
+      \inferrule*{\Gamma,s\ts M \converges_u n+1,s'}{\Gamma,s\ts \pred M \converges_u n,s'}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u 0,s'}{\Gamma,s\ts \pred M \converges_u 0,s'}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u \skipp,s' \\ \Gamma,s'\ts N \converges_v c,s''}{\Gamma,s \ts M;N \converges_{u\cat v} c,s''}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u \true,s' \\ \Gamma,s' \ts N \converges_v c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges_{u\cat v} c,s''}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u \false,s' \\ \Gamma,s' \ts P \converges_v c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges_{u\cat v} c,s''}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u 0,s' \\ \Gamma,s' \ts N \converges_v c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges_{u\cat v} c,s''}
+      \and
+      \inferrule*{\Gamma,s\ts M \converges_u n+1,s' \\ \Gamma,s' \ts P \converges_v c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges_{u\cat v} c,s''}
+      \and
+      \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges_u n,s' \\ \Gamma,s' \ts V \converges_v x,s''}{\Gamma,s\ts V \gets E \converges_{u\cat v} \skipp,(s''\vert x \mapsto n)}
+      \and
+      \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges_u x,s'}{\Gamma,s\ts !V \converges_u n,s'}
+      \and
+      \inferrule*{\Gamma,x\from\Var,(s\vert x\mapsto 0)\ts M \converges_u c,(s'\vert x\mapsto n)}{\Gamma,s\ts \neww \lambda x.M \converges_u c,s'}
+      \and
+      \inferrule*{\Gamma,s\ts E \converges_u n,s' \\ \Gamma,s'\ts V \converges_v \mkvar W R,s'' \\ \Gamma,s'' \ts Wn \converges_w \skipp,s'''}
+      {\Gamma,s \ts V\gets E \converges_{u\cat v\cat w} \skipp,s'''}
+      \and
+      \inferrule*{\Gamma,s\ts V \converges_u \mkvar W R,s' \\ \Gamma,s'\ts R \converges_v n,s''}{\Gamma,s\ts !V \converges_{u\cat v} n,s''}
+      \\\and
+      \inferrule*[right=$x\in X$]{ }{\Gamma,s\ts \ask_X \converges_x x,s}
+    \end{mathpar}
+    \caption[Operational semantics for \IAX]{Operational semantics for \IAX.  
+    All the rules except the last one are deterministic and may be obtained from the corresponding rules of Idealized Algol by suitably annotating the $\converges$ relation with sequences from $X^*$.}
+    \label{FigIaxOpSem}
+  \end{figure}
+
+  We can define this semantics in an alternative, indirect way.  
+  Note that each rule from ordinary Idealized Algol takes the form
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges c,s^{(n)}}\,,
+    \]
+  Here, we have interpreted each IA rule as an infinite scheme of rules ranging over the different terms $M_i,M$ that the rule can apply to.
+  We first extend this rule to a rule for \IAX, by allowing the $M_i,M$ to range over terms of \IAX.
+  We then replace the rule with the new rule
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1 \converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n \converges_{u_n} c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges_{u_1 \cat \cdots \cat u_n} c,s^{(n)}}\,,
+    \]
+  to give us an operational rule for \IAX (if $n=0$, then we treat the empty string $\epsilon$ as the empty concatenation).
+  Lastly, we add the rule for the new constant $\ask_X$:
+  \[
+    \inferrule*[right=$x\in X$]{ }{\Gamma,s \ts \ask_X \converges_x x,s}\,.
+    \]
+  This rule is the only nondeterministic one in our language, as well as being the only one in which the sequence annotating the $\converges$ symbol at the bottom is not formed from concatenating together the sequences on the top.
+\end{definition}
+
+\begin{example}
+  If $X=\bC$, then, since $X$ has a single element, a sequence $n$ of elements of $X$ may be identified with its length $n$.
+  In this case, the language \IAX gives us a way to model time complexity, and the term $\ask_X$ may be considered as a constant $\sleep\from \com$ whose semantics is to wait for some fixed period of time before continuing.
+  In this case, 
+  \[
+    \Gamma,s\ts M \converges_n c,s'
+    \]
+  is interpreted to say that `$M$ converges to $c$ in time $n$'.
+\end{example}
+\begin{example}
+  If $X\in\{\bB,\bN\}$, then the language \IAX gives us a way to model nondeterminism, where $\ask_X$ behaves as a \emph{nondeterministic oracle}; i.e., a device that nondeterministically returns an element of $X$.
+
+  If $X=\bB$ then we have a model of binary (i.e., finite) nondeterminism, whereas if $X=\bN$ then we have a model of countable nondeterminism.
+
+  We interpret the relation
+  \[
+    \Gamma,s\ts M \converges_u c,s'
+    \]
+  as saying that $M$ converges to $c$ in the case that the sequence of values returned by the nondeterministic oracle is given by the sequence $u$.
+\end{example}
+
+\subsection{Soundness}
+\label{SecSoundness}
+
+To prove our adequacy result for the operational semantics of \IAX, we first give some definitions.
+
+\begin{definition}
+  Fix some constant value $\top \in X$ (the precise value does not matter).
+  We inductively define terms in context $\tr_u\from \nat \to X$ of \emph{ordinary deterministic} Idealized Algol for each $u\in X^*$ as follows.
+  \begin{mathpar}
+    \tr_\epsilon = \lambda n.\top
+    \and
+    \tr_{xu} = \lambda n.\neww (\lambda v.v\gets n;\IfO !v \Then x \Else \tr_u (\pred !v))
+  \end{mathpar}
+\end{definition}
+
+\begin{proposition}
+  Let $u \in X^*$ and let $n<|u|$.  
+  Then it is possible to deduce that
+  \[
+    \inferrule{\Gamma,s \ts M \converges n,s'}{\Gamma,s \ts \tr_u M \converges u^{(n)},s'}
+    \]
+  in Idealized Algol.
+  \label{PropTr}
 \end{proposition}
-
-To make sense of this strategy, we need to know that $\G$ is enriched in algebraic cpos.  
-Then $\bot$ is the bottom element of $\G(1,\bC)$.
-
-Before proceeding further, we prove an important lemma.  
-This lemma tells us that the operational semantics of a term of IA+$\sleep$ may be modelled within Idealized Algol; i.e., that IA+$\sleep$ is a conservative extension of the original language.
+\begin{proof}
+  Induction on $|u|$ and on $n$.
+  Since $n<u$, $u$ must be non-empty, of the form $xu'$.
+
+  Suppose $n=0$.  
+  Then $u^{(n)}=x$, and we have a derivation of $\Gamma,s\ts \tr_{xu} M\converges x,s'$ from $\Gamma,s\ts M\converges n,s'$ as shown in Figure \ref{FigFirstTermOfSequence}.
+
+  Now suppose that $n=m+1$.  
+  Then $(xu)^{(m+1)}=u^{(m)}$.  
+  Then we have a derivation of $\Gamma,s\ts \tr_{xu} M \converges u^{(m)},s'$ from $\Gamma,s\ts M\converges n,s'$ in Figure \ref{FigGeneralTermOOfSequence}, using the inductive hypothesis to tell us that we may derive
+  \[
+    \inferrule*{\Gamma,v,(s'\vert v\mapsto m+1) \ts \pred !v \converges m,(s'\vert v \mapsto m+1)}
+    {\Gamma,v,(s'\vert v \mapsto m+1) \ts \tr_u(\pred !v) \mapsto u^{(m)},(s'\vert v\mapsto m+1)}\,.\qedhere
+    \]
+  \begin{SidewaysFigure}
+    \tiny
+    \begin{subfigure}{\textheight}
+      \centering
+      \[
+        \inferrule*
+        {
+          \inferrule*
+          {
+            \inferrule*
+            {
+              \inferrule*
+              {
+                \Gamma,v,(s\vert v \mapsto 0) \ts M \converges 0,(s'\vert v\mapsto 0)
+                \\
+                \inferrule*
+                {
+                }
+                {
+                  \Gamma,v,(s'\vert v \mapsto 0)\ts v \converges v,(s'\vert v\mapsto 0)
+                }
+              }
+              {
+                \Gamma,v,(s\vert v\mapsto 0) \ts v \gets M \converges \skipp,(s'\vert v\mapsto 0)
+              }
+              \\
+              \inferrule*
+              {
+                \inferrule*
+                {
+                  \inferrule*
+                  {
+                  }
+                  {
+                    \Gamma,v,(s'\vert v\mapsto 0) \ts v \converges v,(s'\vert v\mapsto 0)
+                  }
+                }
+                {
+                  \Gamma,v,(s'\vert v\mapsto 0) \ts !v \converges 0,(s'\vert v\mapsto 0)
+                }
+                \\
+                \inferrule*
+                {
+                }
+                {
+                  \Gamma,v,(s'\vert v\mapsto 0) \ts x \converges x,(s'\vert v\mapsto 0)
+                }
+              }
+              {
+                \Gamma,v,(s'\vert v\mapsto 0) \ts \IfO !v \Then x \Else \tr_u(\pred !v) \converges x,(s'\vert v\mapsto 0)
+              }
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto 0) \ts v\gets M;\IfO !v \Then x \Else \tr_u(\pred !v) \converges x,(s'\vert v\mapsto 0)
+            }
+          }
+          {
+            \Gamma,s\ts \neww (\lambda v.v\gets M;\IfO !v \Then x \Else \tr_u(\pred !v)) \converges x,s'
+          }
+        }
+        {
+          \Gamma,s\ts \lambda n.\neww (\lambda v.v\gets n;\IfO !v \Then x \Else \tr_u(\pred !v)) M \converges x,s'
+        }
+        \]
+      \caption{IA derivation that if $M\converges 0$ then $\tr_u M$ converges to the first element of the sequence $u$.}
+      \label{FigFirstTermOfSequence}
+    \end{subfigure}
+    \par\vspace{24pt}
+    \begin{subfigure}{\textheight}
+    \centering
+      \[
+        \inferrule*
+        {
+          \inferrule*
+          {
+            \inferrule*
+            {
+              \inferrule*
+              {
+                \inferrule*[rightskip=30pt]
+                {
+                }
+                {
+                  \Gamma,v,(s'\vert v\mapsto 0) \ts v \converges v,(s'\vert v\mapsto 0)
+                }
+                \\\\
+                \inferrule*[leftskip=15pt]{}{\Gamma,v,(s\vert v\mapsto 0) \ts M \converges m+1, (s'\vert v\mapsto 0)}
+              }
+              {
+                \Gamma,v,(s\vert v\mapsto 0) \ts v \gets M \converges \skipp,(s'\vert v\mapsto m+1)
+              }
+              \\
+              \inferrule*
+              {
+                \inferrule*
+                {
+                  \inferrule*
+                  {
+                  }
+                  {
+                    \Gamma,v,(s'\vert v\mapsto m+1) \ts v \converges v,(s'\vert v\mapsto m+1)
+                  }
+                }
+                {
+                  \Gamma,v,(s'\vert v\mapsto m+1) \ts !v \converges m+1,(s'\vert v\mapsto m+1)
+                }
+                \\
+                \inferrule*
+                {
+                  \inferrule*
+                  {
+                    \inferrule*
+                    {
+                      \inferrule*
+                      {
+                      }
+                      {
+                        \Gamma,v,(s'\vert v\mapsto m+1) \ts v \converges v,(s'\vert v\mapsto m+1)
+                      }
+                    }
+                    {
+                      \Gamma,v,(s'\vert v\mapsto m+1) \ts !v \converges m+1,(s'\vert v\mapsto m+1)
+                    }
+                  }
+                  {
+                    \Gamma,v,(s'\vert v\mapsto m+1) \ts \pred !v \converges m,(s'\vert v\mapsto m+1)
+                  }
+                }
+                {
+                  \Gamma,v,(s'\vert v\mapsto m+1) \ts \tr_u(\pred !v) \converges u^{(m)}, (s'\vert v \mapsto m+1)
+                }
+              }
+              {
+                \Gamma,v,(s'\vert v\mapsto m+1) \ts \IfO !v \Then x \Else \tr_u(\pred !v) \converges u^{(m)}, (s'\vert v\mapsto m+1)
+              }
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto 0) \ts v \gets M;\IfO !v \Then x \Else \tr_u(\pred !v) \converges u^{(m)}, (s'\vert v \mapsto m+1)
+            }
+          }
+          {
+            \Gamma,s \ts \neww (\lambda v.v\gets M;\IfO !v \Then x \Else \tr_u(\pred !v)) \converges u^{(m)},s'
+          }
+        }
+        {
+          \Gamma,s\ts \lambda n.\new (\lambda v.v\gets n;\IfO !v \Then x \Else \tr_u(\pred !v)) M \converges u^{(m)},s'
+        }
+        \]
+        \caption{IA derivation that if $M\converges m+1$ then $\tr_{u}M$ converges to the $m+1$-th element of the sequence $u$.}
+        \label{FigGeneralTermOOfSequence}
+    \end{subfigure}
+    \par\vspace{24pt}
+    \begin{subfigure}{\textheight}
+      \[
+        \inferrule*
+        {
+          \inferrule*
+          {
+            \inferrule*
+            {
+              \inferrule*
+              {
+                \inferrule*
+                {
+                }
+                {
+                  \Gamma,v,(s\vert v\mapsto k) \ts v \converges v,(s\vert v\mapsto k)
+                }
+              }
+              {
+                \Gamma,v,(s\vert v\mapsto k) \ts !v \converges k,(s\vert v\mapsto k)
+              }
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto k) \ts \suc !v \converges k+1,(s\vert v\mapsto k)
+            }
+            \\
+            \inferrule*
+            {
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto k) \ts v\converges v,(s\vert v\mapsto k)
+            }
+          }
+          {
+            \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v \converges \skipp,(s\vert v\mapsto k+1)
+          }
+          \\
+            \inferrule*[right={Prop. \ref{PropTr}}]
+            {
+              \inferrule*
+              {
+                \inferrule*
+                {
+                }
+                {
+                  \Gamma,v,(s\vert v\mapsto k+1) \ts v\converges v,(s\vert v\mapsto k+1)
+                }
+              }
+              {
+                \Gamma,v,(s\vert v\mapsto k+1) \ts !v \converges k+1,(s\vert v\mapsto k+1)
+              }
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto k+1) \ts \tr_w !v \converges x,(s\vert v\mapsto k+1)
+            }
+          }
+        {
+          \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v;\tr_w !v \converges x,(s\vert v\mapsto k+1)
+        }
+        \]
+      \caption{IA derivation that $(x\mapsto k),v \gets \suc !v;\tr_w !v$ converges to the $k+1$-th term of $w$.}
+      \label{FigTheOneForTheLemma}
+    \end{subfigure}
+    \normalsize
+  \end{SidewaysFigure}
+\end{proof}
+
+We need a small lemma to help us deal with substitution.
 
 \begin{lemma}
-  Let $P\from T$ be a term of IA+$\sleep$.
-  Suppose that
-  \[
-    \Gamma,s\ts P\converges_n c,s'
-    \]
-  in IA+$\sleep$.
-
-  Then for all $k\ge 0$, all contexts $\Delta$ disjoint from $\Gamma$, all stores $t$ over $\Gamma,\Delta$ disjoint from $s$ and all variables $v$ not in $\Gamma,\Delta$:
-  \[
-    \Delta,\Gamma,v,(t{+}s\vert v \mapsto k)\ts P[v \gets \suc !v/\sleep] \converges c,(t{+}s\vert v \mapsto k+n)
-    \]
-  in Idealized Algol.
-  \label{IaSleepsSoundnessLemma}
+  Let
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges c,s^{(n)}}
+    \]
+  be an inference, where the $M_i$,$M$ are terms of \IAX and the whole inference satisfies one of the patterns of the Idealized Algol rules.  
+  Let $Q$ be a fixed term of type $X$.  
+  Then
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1[Q/\ask_X]\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n[Q/\ask_X]\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M[Q/\ask_X] \converges c,s^{(n)}}\,,
+    \]
+  is a valid inference of Idealized Algol.
+  \label{LemFirstSubstitution}
 \end{lemma}
 \begin{proof}
-  Induction on the derivation that $\Gamma,s\ts P\converges_n c,s'$.
-  There are several possibilities for the last step in the derivation.
-  \begin{description}
-    \item[Structural congruence]
-      Suppose that the last step in the derivation is
-      \[
-        \inferrule*{P\equiv P'\\
-        \Gamma,s\ts P' \converges_n \skipp, s'}
-        {\Gamma,s\ts P\converges_n \skipp, s'}\,.
-        \]
-      It is clear then by the definition of structural congruence that $P'[v\gets\suc !v/\sleep]\equiv P[v\gets\suc !v/\sleep]$.  
-      So the claim follows by the inductive hypothesis applied to $P'$ and the structural congruence rule for Idealized Algol.
-    \item[$\sleep$]
-      Suppose that the last step in the derivation is
-      \[
-        \inferrule*{ }
-        {\Gamma,s\ts \sleep \converges_1 \skipp,s}\,.
-        \]
-      Fix a context $\Delta$ disjoint from $\Gamma$ and a store $t$ over $\Gamma,\Delta$ that is disjoint from $s$.  
-      Fix $k\ge n$.  
-      Then it suffices to show that the following judgement may be proved within the operational semantics of Idealized Algol.
-      \[
-        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \gets \suc !v \converges \skipp, (t{+}s\vert v\mapsto k+1)
-        \]
-      A derivation for this obvious fact is given in Figure \ref{SleepIADerivation}.
-      \begin{SidewaysFigure}
-        \centering
-        \begin{subfigure}{\textheight}
-          \[
-            \inferrule*
-            {
-              \inferrule*
-              {
-                \inferrule*
-                {
-                  \inferrule*
-                  {
-                  }
-                  {
-                    \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \converges v,(t{+}s\vert v\mapsto k)
-                  }
-                }
-                {
-                  \Delta,\Gamma,v,(t{+}s\vert v\mapsto k) \ts !v \converges k,(t{+}s\vert v\mapsto k)
-                }
-              }
-              {
-                \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts \suc !v \converges k+1,(t{+}s\vert v\mapsto k)
-              } \\
-              \inferrule*
-              {
-              }
-              {
-                \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \converges v,(t{+}s\vert v\mapsto k)
-              }
-            }
-            {
-              \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v\gets\suc !v\converges\skipp,(t{+}s\vert v\mapsto k+1)
-            }
-            \]
-          \caption{The crucial part of Lemma \ref{IaSleepsSoundnessLemma} pertaining to the $\sleep$ constant is a routine Idealized Algol derivation.}
-          \label{SleepIADerivation}
-        \end{subfigure}
-        \par\vspace{48pt}
-        \begin{subfigure}{\textheight}
-          \[
-            \inferrule*{\Delta,\Gamma_1,v,(t{+}s\vert v\mapsto k) \ts M_1[v \gets \suc !v/\sleep] \converges c_1,(t{+}s\vert v \mapsto k + n_1) \\
-            \cdots \\
-            \Delta,\Gamma_p,v,(t{+}s\vert v\mapsto k + n_1 + \cdots + n_{p-1}) \ts M_p[v \gets \suc !v/\sleep] \converges c_1,(t{+}s\vert v \mapsto k+n_1+\cdots+n_p)}
-            {\Delta,\Gamma,v,(t{+}s^{(0)}\vert v \mapsto k + n_1 + \cdots + n_p)\ts M[v\gets \suc !v/\sleep] \converges c,(t{+}s^{(p)}\vert v \mapsto k)}
-            \]
-          \caption{The big-step rules of IA+$\sleep$ give rise to big-step rules of Idealized Algol via our translation.}
-          \label{GeneralIADerivation}
-        \end{subfigure}
-        \caption{The proof of Lemma \ref{IaSleepsSoundnessLemma} works by translating big-step derivations from IA+$\sleep$ into big-step derivations of Idealized Algol.}
-        \label{IADerivations}
-      \end{SidewaysFigure}
-    \item[Canonical forms]
-      Suppose that the last step in the derivation is
-      \[
-        \inferrule*{ }
-        {\Gamma,s\ts_0 c\converges c,s}\,.
-        \]
-      Then, since $\sleep$ is not a canonical form, we have $c[v\gets \suc !v/\sleep]=c$.  
-      Then we have the derivation
-      \[
-        \inferrule*{ }
-        {\Delta,\Gamma,(t{+}s\vert v\mapsto k)\ts c \converges c,(t{+}s\vert v\mapsto k)}\,.
-        \]
-    \item[Sequencing]
-      Suppose instead that the last step in the derivation is
-      \[
-        \inferrule*{\Gamma,s\ts M \converges_m \skipp, s'\\
-        \Gamma,s'\ts N \converges_n \skipp, s''}
-        {\Gamma,s\ts M;N \converges_{m+n} \skipp, s''}\,.
-        \]
-      Fix $k\ge 0$.  
-      By induction on $M,N$, we have
-      \begin{mathpar}
-        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts M[v\gets\pred !v/\sleep]\converges \skipp,(t{+}s'\vert  v\mapsto k+m)\,;
-        \and
-        \Delta,\Gamma,v,(t{+}s'\vert  v\mapsto k+m) \hspace{144pt} \par\vspace{-8pt} \\ \par \hspace{144pt} \ts N[v\gets\pred !v/\sleep]\converges \skipp,(t{+}s''\vert v\mapsto k+m+n)\,.
-      \end{mathpar}
-      It follows that
-      \begin{mathpar}
-        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k) \hspace{180pt} \par\vspace{-8pt} \\ \par \hspace{180pt} \ts (M;N)[v\gets\pred !v/\sleep] \converges \skipp, (t{+}s''\vert v\mapsto k+m+n)\,,
-      \end{mathpar}
-      by the sequencing rule of Idealized Algol.
-    \item[Remaining rules]
-      Having given the rule for canonical forms and sequencing explicitly, we now give a general technique by which we can deal with all the remaining rules.
-
-      Each rule is of the form
-      \[
-        \inferrule*{ \Gamma_1,s^{(0)}\ts z_1\converges_{n_1}\gamma_1,s^{(1)} \\
-        \cdots \\
-        \Gamma_p,s^{(p - 1)}\ts z_p \converges_{n_p} \gamma_p,s^{(p)}}
-        { \Gamma,s^{(0)}\ts z \converges_{n_1+\cdots+n_p} \gamma,s^{(p)}}
-        \]
-      (for $p\in\{0,1,2,3\}$), where
-      \[
-        \inferrule*{ \Gamma_1,s^{(0)}\ts z_1\converges \gamma_p,s^{(1)} \\
-        \cdots \\
-        \Gamma_p,s^{(p - 1)}\ts z_p \converges \gamma_1,s^{(p)}}
-        { \Gamma,s^{(0)}\ts z \converges \gamma,s^{(p)}}
-        \]
-      is a rule for Idealized Algol.
-
-      Here, each $z_i,z,\gamma_i,\gamma$ is a term of Idealized Algol (without $\sleep$) that may have free variables that are not included in the $\Gamma_i,\Gamma$.  
-      These free variables $(x_\alpha)$ may be shared between the $z_i,z,\gamma_i,\gamma$, introducing a dependence between them.
-      For example, in the rule for sequencing, the terms on the top are single-variable terms of IA, where `$M$' and `$N$' are themselves free variables.  
-      These variables are bound in the expression `$M;N$' on the bottom of the rule.
-
-      Fix some such rule, and suppose that it is used in the last step of the deduction.  
-      So the last step looks like this.
-      \[
-        \inferrule*{ \Gamma_1,s^{(0)}\ts M_1\converges_{n_1}c_1,s^{(1)} \\
-        \cdots \\
-        \Gamma_p,s^{(p - 1)}\ts M_p \converges_{n_p} c_p,s^{(p)}}
-        { \Gamma,s^{(0)}\ts M \converges_{n_1+\cdots+n_p} c,s^{(p)}}
-        \]
-      Here, the $M_i,M,c_i,c$ fit the pattern given by the $z_i,z,\gamma_i,\gamma$.  
-      By induction, for each $i=1,\cdots,p$, the following judgement may be proved in Idealized Algol.
-      \begin{mathpar}
-        \Delta,\Gamma,v,(t{+}s^{(i)}\vert v \mapsto k + n_1 + \cdots + n_{i-1})
-        \hspace{144pt} \par\vspace{-20pt} \\ \par \hspace{144pt}
-        \ts
-        M[v \gets \suc !v] \converges c_i,(t{+}s^{(i)}\vert v \mapsto k + n_1 + \cdots + n_i)
-      \end{mathpar}
-
-      Now we know that the $M_i,M,c_i,c$ may be obtained from the $z_i,z,\gamma_i,\gamma$ by substituting in actual terms $N_\alpha$ for the free variables $x_\alpha$ in these expressions.  
-      Moreover, since the primitive $\sleep$ is not mentioned anywhere in these rules, it follows that we have
-      \begin{IEEEeqnarray*}{rCl}
-        M_i[v\gets\suc !v/\sleep] & = & (z_i[N\alpha/x_\alpha])[v\gets \suc !v/\sleep] \\
-        & = & z_i[(N[v\gets \suc !v/\sleep])/x_\alpha]\,,
-      \end{IEEEeqnarray*}
-      and similarly for the $z,\gamma_i,\gamma$.
-      Therefore, the $M_i,M,c_i,c$ still fit the pattern given by the $z_i,z,\gamma_i,\gamma$, even after making our substitution.  
-      It follows that we may derive
-      \begin{mathpar}
-        \Delta,\Gamma,v,(t{+}s^{(0)}\vert v \mapsto k)\hspace{180pt}\par\vspace{-8pt}\\ \par
-        \hspace{180pt}\ts M[v\gets \suc !v/\sleep] \converges c,(t{+}s^{(p)}\vert v \mapsto k+n_1+\cdots+n_p)
-      \end{mathpar}
-      using the derivation shown in Figure \ref{GeneralIADerivation}.
-  \end{description}
+  The real reason this is true is that the term $\ask_X$ is not mentioned anywhere in the IA rules, so substitution of the term $N$ for $\ask$ could not possibly break the pattern.  
+  Formally, we can show this by inspection on each of the different rules.  
+  For instance, if the original rule is the one for sequencing:
+  \[
+    \inferrule{\Gamma,s\ts M \converges \skipp,s' \\ \Gamma,s'\ts N \converges c,s''}
+    {\Gamma,s \ts M;N \converges c,s''}\,,
+    \]
+  then we have $(M;N)[Q/\ask_X] = M[P/\ask_X];N[P/\ask_X]$ and the inference
+  \[
+    \inferrule{\Gamma,s\ts M[Q/\ask_X] \converges \skipp,s' \\ \Gamma,s'\ts N[Q/\ask_X]\converges c,s''}
+    {\Gamma,s \ts M[Q/\ask_X];N[P/\ask_X] \converges c,s''}
+    \]
+  is still a valid instance of the sequencing rule.
+\end{proof}
+
+We can now state and prove our soundness lemma.
+
+\begin{lemma}
+  Suppose that
+  \[
+    \Gamma,s\ts M\converges_u c,s'
+    \]
+  in \IAX.
+  Fix $k\in\bN$ and let $w\in X^*$ be a sequence such that $u$ is a subsequence of $w$ starting at position $k+1$ (i.e., $u^{(j)}=w^{(k+j+1)}$ for each $j=0,\cdots,|u|-1$).
+  Then
+  \[
+    \Gamma,v\from\Var,(s\vert v\mapsto k) \ts M[v\gets \suc!v;\tr_w !v/\ask_v] \converges c,(s'\vert v\mapsto k + |u|)
+    \]
+  in Idealized Algol.
+  \label{LemSoundness}
+\end{lemma}
+\begin{proof}
+  Structural induction on the derivation.
+
+  Suppose that the last rule we use comes from one of the Idealized Algol rules.
+  That is, there is an inference
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges c,s^{(n)}}\,,
+    \]
+  derived from one of the Idealized Algol schemas, and we have replaced it with the rule
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1 \converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n \converges_{u_n} c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges_{u_1 \cat \cdots \cat u_n} c,s^{(n)}}\,,
+    \]
+  where each of the relations $\Gamma,s^{(i-1)} \ts M_i \converges_{u_i} c_i,s^{(i)}$ is derivable in \IAX.
+
+  Fix $k\in \bN$ and a sequence $w$ such that $u_1\cat \cdots \cat u_n$ is a subsequence of $w$ starting at position $k+1$.  
+  In particular, for each $i=1,\cdots,n$, $u_i$ is a subsequence of $w$ starting at position $k+\sum_{j=1}^{i-1}|u_j|+1$.
+
+  Then by the inductive hypothesis, we know that for each $i=1,\cdots,n$, the relation
+  \small
+  \[
+    \Gamma,v,(s^{(i-1)}\vert v \mapsto k+\sum_{j=1}^{i-1}|u_j|) \ts M_i[v\gets \suc !v;\tr_w !v/\ask_v] \converges c,(s^{(i)}\vert v\mapsto k + \sum_{j=1}^i |u_j|)
+    \]
+  \normalsize
+  is derivable in Idealized Algol.  
+  Then we may apply the Idealized Algol inference and Lemma \ref{LemFirstSubstitution} to deduce that
+  \[
+    \Gamma,v,(s^{(0)}\vert v\mapsto k) \ts M[v\gets \suc !v;\tr_w !v/\ask_v] \converges c, (s^{(n)} \vert v\mapsto k + \sum_{i=1}^{n} |u_n|)\,,
+    \]
+  as desired.
+
+  Now suppose instead that the last rule was the new one for $\ask_X$; i.e., 
+  \[
+    \inferrule{ }{\Gamma,s\ts \ask_X \converges_x x,s}\,,
+    \]
+  where $x\in X$.  
+  Fix some $k\in \bN$ and some $w$ such that the single term $x$ is a subsequence of $w$ starting at position $k+1$; i.e., that $x=w^{(k+1)}$.
+  Then we would like to derive that
+  \[
+    \Gamma,v,(s\vert v\mapsto k) \ts v \gets \suc !v;\tr_w !v \converges x,(s\vert v\mapsto k+1)\,,
+    \]
+  which we can do using the derivation in Figure \ref{FigTheOneForTheLemma}, where we have used Proposition \ref{PropTr} to deal with the $\tr_w$ term.
+
   This completes the induction.
@@
 
-In light of this result, we can make a definition relating the denotational and operational semantics of terms of type $\nat$.  
-First, observe that since the $\beta$ rule is valid in our semantics, we may write the denotation of a term $M\from\com$ of IA+$\sleep$ as the composite
-\[
-  1 \xrightarrow{\sleep}
-  \bC \xrightarrow{\deno{c\ts M[c/\sleep]}}
+In light of Lemma \ref{LemSoundness}, we can state our soundness result.
+
+First recall the statement of Computational Adequacy for $\G$:
+
+\begin{proposition}
+  Let $M\from \com$ be a closed term of Idealized Algol and suppose that
+  \[
+    ,()\ts M\converges \skipp,()\,.
+    \]
+  Then $\deno{M} \ne \bot$.
+\end{proposition}
+
+\begin{definition}
+  Let $u\in X^*$.
+  Let $u^\top$ be the sequence formed by appending some fixed value $\top\in X$ to the start of $u$, so that $u$ is the subsequence of $u^\top$ running from position $1$ up to position $|u|$.
+  Define a morphism
+  \[
+    \eta_u = \deno{f\from X \to \com \ts \lambda v.f(v\gets \suc !v;\tr_{u^\top} !v);!v} \from (X \to \bC) \to (\Var \to \bN)
+    \]
+  in $\G$.
+\end{definition}
+
+\begin{definition}
+  Let $n$ be a natural number.  
+  We define terms $\test_n\from \nat \to \com$ inductively by
+  \begin{mathpar}
+    \test_0 = \lambda m.\IfO m \Then \skipp \Else \Omega
+    \and
+    \test_{n+1} = \lambda m.\IfO m \Then \Omega \Else \test_n (\pred m)\,.
+  \end{mathpar}
+  So $\test_n$ converges if its input evaluates to $n$ and diverges otherwise.
+
+  We then define $t_n\from \bN \to \bC$ to be the denotation of $\test_n$ in $\G$.
+\end{definition}
+
+\begin{proposition}[Soundness]
+  Let $M\from\com$ be a closed term of \IAX, let $u\in X^*$ be a sequence and suppose that
+  \[
+    ,()\ts M\converges_u\skipp,()\,.
+    \]
+  Let the denotation $\deno{M} \from 1 \to \com$ in $\G_X$ be considered as a morphism $1 \to (X \to \bC)$ in $\G$.
+  Then the composite
+  \[
+    1 \xrightarrow{\deno{M}}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
     \bC
     \]
-in $\Kl_{R_\bC}$.
-
-Working in the original category $\G$, however, we may identify this composite with the morphism
-\[
-  \deno{\lambda c.M[c/\sleep]} \from 1 \to (\bC \to \bC)\,.
-  \]
-Now we have a morphism
-\begin{mathpar}
-  \eta = \deno{f\from \com\to \com \ts \lambda v.f(v\gets \suc!v);!v}\from (\bC \to \bC) \to (\Var \to \bN)\,.
-\end{mathpar}
-If we form the composite
-\[
-  1 \xrightarrow{\deno{\lambda c.M[c/\sleep]}}
-  (\bC \to \bC) \xrightarrow{\eta}
-  (\Var \to \bN) \xrightarrow{\new_\bN}
-  \bN
-  \]
-then the morphism we get will be the denotation in $\G$ of the term
-\[
-  \ts \new\;v=0\text{ in } M[v\gets \suc !v/\sleep];!v\from \nat
-  \]
-(since the $\beta$ rule is valid for the semantics in $\G$).
-Lemma \ref{IaSleepsSoundnessLemma} tells us that if $M\converges_n\skipp$ then this term converges to $n$ in Idealized Algol.
-
-Before we introduce our adequacy result, we need one more definition in order to take account of the fact that Proposition \ref{SamsonGuyAdequacy} applies to terms of type $\com$, not $\nat$.
-
-\newcommand{\test}{{\mathtt{test}}}
-\begin{definition}
-  Define terms $\test_n\from\nat\to\com$ inductively by
-  \begin{gather*}
-    \test_0 = \lambda m.\IfO m\text{ then }\skipp\text{ else }\Omega\,; \\
-    \test_{n+1} = \lambda m.\IfO m\text{ then }\Omega\text{ else }\test_n\,. (\pred m)
-  \end{gather*}
-  So $\test_n$ converges if its input evaluates to $n$ and diverges otherwise.
-
-  Let $t_n\from\bN \to \bC$ be the denotation in $\G$ of $\test_n$.
-\end{definition}
-
-\begin{remark}
-  In the model $\G$ of Idealized Algol, every morphism $1 \to \bN$ is definable, so if $\sigma\from 1 \to \bN$ is such a morphism, then there must be at most one $n\in\omega$ such that the composite $\sigma;t_n$ is not equal to $\bot$.
-\end{remark}
-
-\newcommand{\tit}{\mathrm{tt}}
-\begin{definition}
-  Let $\sigma\from 1 \to \bC$ be a Kleisli morphism in $\Kl_{R_{\bC}}$, considered as a morphism $1 \to (\bC \to \bC)$ in $\G$.
-
-  If there is some (necessarily unique) $n\in\omega$ such that the composite
+  is not equal to $\bot$.
+  \label{PropKleisliSoundness}
+\end{proposition}
+\begin{proof}
+  Since the $\beta$ rule is valid in $\G_X$, this composite is equal to the denotation of the term
+  \[
+    \test_{|u|}(\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v))
+    \]
+  in IA.
+  By the adequacy result for Idealized Algol, it suffices to show that this term converges to $\skipp$; i.e., that the term
+  \[
+    \new (\lambda v.M[v\gets\suc !v;\tr_{u^\top} !v/\ask_X];!v)
+    \]
+  converges to $|u|$ in IA.
+
+  We can prove this using the following derivation tree.
+  \tiny
+  \[
+    \inferrule*
+    {
+      \inferrule*
+      {
+        \inferrule*[left={Lem. \ref{LemSoundness}}]
+        {
+        }
+        {
+          v,(v\mapsto 0)\ts M[v\gets\suc!v;\tr_{u^\top} !v/\ask_x]\converges \skipp,(v\mapsto |u|)
+        }
+        \\
+        \inferrule*
+        {
+          \inferrule*
+          {
+          }
+          {
+            v,(v\mapsto |u|) \ts v \converges v,(v\mapsto |u|)
+          }
+        }
+        {
+          v,(v\mapsto |u|)\ts !v \converges |u|,(v\mapsto |u|)
+        }
+      }
+      {
+        v,(v\mapsto 0) \ts M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];v \converges |u|,(v\mapsto |u|)
+      }
+    }
+    {
+      ,()\ts\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v) \converges |u|,()
+    }\qedhere
+    \]
+  \normalsize
+\end{proof}
+
+The statement of Proposition \ref{PropKleisliSoundness} looks a bit strange.  
+This is because the level of generality we are operating at (i.e., $\G$ being a fairly general model for Idealized Algol) does not give us much room to define things other than in terms of the denotations of Idealized Algol terms.
+
+If $\G$ is the category of games and visible strategies, then the statements of Proposition \ref{PropKleisliSoundness} (and our later Adequacy and Full Abstraction results) become clearer.  
+Observe that if $\sigma \from 1 \to (X \to \bC)$ is a strategy in $\G$ (considered as a strategy for $\oc X \implies \bC$, then the maximal plays in the interaction
+\[
+  \sigma || (\eta_u;\deno{\neww})
+  \]
+take the form
+\[
+  \begin{array}{ccc}
+    X         & \bC & \bN \\
+              &     &  q  \\
+              &  q  &     \\
+    q         &     &     \\
+    u^{(0)}   &     &     \\
+    \vdots    &     &     \\
+    q         &     &     \\
+    u^{(k-1)} &     &     \\
+              &  a  &     \\
+              &     &  k  \\
+  \end{array}\,,
+  \]
+for $k\le |u|$ or
+\[
+  \begin{array}{ccc}
+    X         & \bC & \bN \\
+              &     &  q  \\
+              &  q  &     \\
+    q         &     &     \\
+    u^{(0)}   &     &     \\
+    \vdots    &     &     \\
+    q         &     &     \\
+    u^{(|u|-1)}&     &     \\
+    q         &     &     \\
+    \top      &     &     \\
+    \vdots    &     &     \\
+    q         &     &     \\
+    \top      &     &     \\
+              &  a  &     \\
+              &     &  k  \\
+  \end{array}\,,
+  \]
+for $k>|u|$, where the component in $X,\bC$ is a valid play of $\sigma$.
+Moreover, the strategy $t_n$ is the one with maximal plays of the form
+\[
+  \begin{array}{cc}
+    \bN & \bC \\
+        &  q  \\
+    q   &     \\
+    n   &     \\
+        &  a
+  \end{array}
+  \]
+or
+\[
+  \begin{array}{cc}
+    \bN & \bC \\
+        &  q  \\
+    q   &     \\
+    m   &
+  \end{array}
+  \]
+for $m\ne n$.
+
+This means that the composite
 \[
   1 \xrightarrow{\sigma}
-    (\bC \to \bC) \xrightarrow{\eta}
-    (\Var \to \bN) \xrightarrow{\new_\bN}
+  (X \to \bC) \xrightarrow{\eta_u}
+  (\Var \to \bN) \xrightarrow{\deno{\neww}}
   \bN \xrightarrow{t_n}
@@
   \]
-  is not equal to $\bot$, then we say that $n$ is the \emph{time taken for $\sigma$ to converge}, or $\tit(\sigma)$.
-  If there is no such $n$, we say that $\tit(\sigma)=\infty$.
-  \label{DefTimeTaken}
-\end{definition}
-
-From our discussion above, we have proved the following result.
-
-\begin{proposition}[Soundness for IA+$\sleep$]
-  Let $P\from \com$ be a term of IA+$\sleep$ and let $\sigma\from \bC \to \bC$ be its denotation in $\Kl_{R_\bC}$, considered as a morphism in $\G$.
-  If $P\converges_n$ then $\tit(\sigma)=n$.
-  \label{IaSleepSoundness}
-\end{proposition}
-
-In order to prove the other direction (adequacy), we need to prove a kind of converse to Lemma \ref{IaSleepsSoundnessLemma}.
+is not equal to $\bot$ if and only if $\sigma$ contains the sequence
+\[
+  \begin{array}{cc}
+    X         & \bC \\
+              &     \\
+              &  q  \\
+    q         &     \\
+    u^{(0)}   &     \\
+    \vdots    &     \\
+    q         &     \\
+    u^{(|u|-1)}&     \\
+              &  a  \\
+              &     \\
+  \end{array}\,.
+  \]
+Since complete plays in the game $\oc X \implies \bC$ are always of the form $q$, followed by some sequence of pairs of the form $qx_i$ for $x\in X$, followed by $a$, this is a very natural condition to consider when dealing with a strategy $\sigma\from \oc X \implies \bC$.
+
+\subsection{Computational Adequacy}
+
+Now we want to prove Computational Adequacy; i.e., the converse to Proposition \ref{PropKleisliSoundness}.
+To do this, we need to prove a converse to Lemma \ref{LemSoundness}.
+
+First of all, we need to prove a reverse result to Lemma \ref{LemFirstSubstitution} that deals with substitution in the opposite direction; i.e., instead of telling us what happens when we substitute a term for $\ask_X$, we will look at what happens when we substitute a term for $v\gets \suc !v;\tr_u !v$.
+
+In most cases, this will not disrupt the structure of the IA rule.  
+For instance, we always have
+\begin{mathpar}
+  (!V)[Q/v\gets \suc !v;\tr_u !v] = !(V[Q/v\gets \suc !v;\tr_u !v])\,,
+\end{mathpar}
+and so the derivation
+\[
+  \inferrule*[right={$s'(v)=n$}]{\Gamma,s\ts V[Q/v\gets \suc !v;\tr_u !v] \converges v,s'}
+  {\Gamma,s \ts !V[Q/v\gets \suc !v;\tr_u !v] \converges n,s'}
+  \]
+still follows the pattern of the Idealized Algol rule for variable dereference.
+
+There is only one case where this breaks down.  
+Consider the following instance of the sequencing rule.
+\[
+  \inferrule
+  {\Gamma,v,s\ts v\gets \suc !v\converges \skipp,s' \\ \Gamma,v,s'\ts \tr_u !v \converges x,s''}
+  {\Gamma,v,s\ts v\gets \suc !v;\tr_u !v \converges x,s''}
+  \]
+In this case, substituting some term $Q$ for $v\gets \suc !v;\tr_u !v$ in the top two terms will have no effect, whereas it will replace the whole of the bottom with $Q$, invalidating the whole inference.
+
+We have proved the following.
 
 \begin{lemma}
-  Let $\Gamma\ts M\from \com$ be a term of IA+$\sleep$ in context.
-  Let $s,s'$ be stores, let $a,b\in\bN$, let $c$ be a canonical form and let $v$ be a variable not included in $\Gamma$.  
-  Suppose that
-  \[
-    \Gamma,v,(s\vert v\mapsto a) \ts M \converges c,(s'\vert v\mapsto b)
-    \]
-  in Idealized Algol.
-  Then there exists $n$ such that
-  \[
-    \Gamma,s \ts M \converges_n c,s'
-    \]
-  in IA+$\sleep$.
+  Let 
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges c,s^{(n)}}
+    \]
+  be an inference of Idealized Algol.  
+  Let $u\in X^*$ and let $Q\from X$ be a term of \IAX.
+  Fix an unused variable name $v$ and suppose that $M \ne v\gets \suc !v;\tr_u !v$.
+  Then
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1[Q/v\gets \suc!v;\tr_u !v]\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n[Q/v\gets\suc !v;\tr_u !v]\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M[Q/v\gets\suc !v;\tr_u !v] \converges c,s^{(n)}}
+    \]
+  conforms to the same Idealized Algol pattern.
+  In particular, if $w_1,\cdots,w_n\in X^*$, then
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1[Q/v\gets \suc!v;\tr_u !v]\converges_{w_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n[Q/v\gets\suc !v;\tr_u !v]\converges_{w_n} c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M[Q/v\gets\suc !v;\tr_u !v] \converges_{w_1\cat\cdots\cat w_n} c,s^{(n)}}
+    \]
+  is a valid inference of \IAX.
+  \label{LemSecondSubstitution}
+\end{lemma}
+
+We need one more lemma to help us deal with substitution.
+
+\begin{lemma}
+  Suppose that $\Gamma,y\ts M\from T$ is a typing judgement of Idealized Algol, where $\Gamma$ is a $\Var$-context and $y$ is a free variable of type $X$.  
+  Fix $u\in X^*$.  
+  Suppose that $M\ne y$ and that we have some inference
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts N_1\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts N_n\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M[v\gets\suc !v;\tr_u !v/y] \converges c,s^{(n)}}\,.
+    \]
+  of Idealized Algol.
+  Then each $N_i$ may be written as $M_i[v\gets \suc !v;\tr_u !v/y]$ for some $\Gamma,y \ts M_i$.
+  \label{LemThirdSubstitution}
 \end{lemma}
 \begin{proof}
-  Induction on the derivation that $\Gamma,v,(s\vert v\mapsto a)\ts M\converges c,(s'\vert v\mapsto b)$.  
-  Most cases are self-explanatory.  
-  For example, suppose that the last step in the derivation is an instance of the sequencing rule:
-  \[
-    \inferrule{\Gamma,v,(s\vert v \mapsto a) \ts M[v\gets\suc !v/\sleep] \converges \skipp, s' \\
-    \Gamma,v,s' \ts N[v\gets\suc !v/\sleep] \converges c, (s''\vert v \mapsto b)}
-    {\Gamma,v(s\vert v \mapsto a) \ts (M;N)[v\gets\suc !v/\sleep] \converges c,(s''\vert v \mapsto b)}\,.
-    \]
-  Since there is no provable sequent of Idealized Algol in which a defined variable on the left ceases to be defined on the right, we may deduce that $s'$ can be written as $(t\vert v \mapsto d)$.  
-  Therefore, we may apply the inductive hypothesis to $M$ and $N$, which tells us that there must be $m,n$ such that
-  \begin{mathpar}
-    \Gamma,s \ts M\converges_m\skipp,t\,;
-    \and
-    \Gamma,t \ts M\converges_n c,s''\,.
-  \end{mathpar}
-  From this it follows that
-  \[
-    \Gamma,s \ts M;N \converges_{m+n} c,s''\,.
-    \]
-  Crucial to this argument is the fact that
-  \[
-    (M[v\gets\suc !v/\sleep]);(N[v\gets\suc !v/\sleep]) = (M;N)[v\gets\suc!v/\sleep]\,.
-    \]
-  For almost all the other rules, a similar equality holds.  
-  The only case where there is a problem is the first rule for $\blank\gets\blank$, since this may introduce a new copy of $v\gets\suc!v$ on the bottom that does not arise from copies of $v\gets\suc!v$ on the top.
-
-  The offending term occurs when $M=\sleep$ and so $M[v\gets\suc!v/\sleep]=v\gets\suc!v$.
-  In that case, the inference is
-  \[
-    \inferrule{\Gamma,(s\vert v \mapsto a)\ts \suc ! v \converges b,s'\\
-    \Gamma,s'\ts v \converges v,s''}
-    {\Gamma,(s\vert v\mapsto a)\ts v \gets\suc!v \converges \skipp,(s''\vert v\mapsto b)}\,.
-    \]
-  By following the derivation upwards, we may deduce that in fact $s=s'=s''$.
-  But in that case the derivation of $\Gamma,s\ts_n M\converges \skipp,s''$ is one of the base rules:
-  \[
-    \inferrule{ }
-    {\Gamma,s \ts \sleep \converges_1 \skipp,s}\,.
-    \]
-  The other cases are routine.  
+  This can be checked case-by-case.  
+  The most interesting is the case for sequencing: if $M[v\gets \suc !v;\tr_u !v/y] \ne v\gets \suc !v;\tr_u !v$, then we must have
+  \[
+    M[v\gets \suc !v;\tr_u !v/y] = N[v\gets \suc !v;\tr_u !v/y];P[v\gets \suc !v;\tr_u !v/y]\,,
+    \]
+  which is deduced from $N[v\gets \suc !v;\tr_u !v/y]$ and $P[v\gets \suc !v;\tr_u !v/y]$.
+\end{proof}
+
+Now we can state and prove our adequacy lemma.
+
+\begin{lemma}
+  Suppose that $w\in X^*$ is a sequence of length greater than or equal to $k,l$ and that
+  \[
+    \Gamma,v,(s|v\mapsto k) \ts M[v\gets\suc !v;\tr_w !v/y] \converges c,(s'|v\mapsto l)
+    \]
+  is derivable in Idealized Algol, where $v$ is not free in $M$ and $y$ is a variable name of type $X$.
+  Then $l\ge k$ and
+  \[
+    \Gamma,s \ts M[\ask_X/y] \converges_u c,s'
+    \]
+  in \IAX, where $u$ is the subsequence of $w$ consisting of all terms from $k+1$ up to $l$.
+  \label{LemAdequacy}
+\end{lemma}
+\begin{proof}
+  Induction on the derivation.
+
+  Suppose that $M\ne y$.  
+  Then, by Lemma \ref{LemThirdSubstitution}, the last step in the derivation of $M[v\gets \suc !v;\tr_w !v/y]$ must be of the form
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1[v\gets \suc!v;\tr_w !v/y]\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n[v\gets\suc !v;\tr_w !v/y]\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M[v\gets\suc !v;\tr_w !v/y] \converges c,s^{(n)}}\,,
+    \]
+  where each $M_i[v\gets \suc !v;\tr_w !v/y]$ is derivable in Idealized Algol.
+
+  By the inductive hypothesis, $s^{(i-1)}(v) \le s^{(i)}(v)$ for each $i$ and so $s^{(0)}(v) \le s^{(n)}(v)$, as desired (in the case that there are no premises -- i.e., the case of the rule for canonical forms -- we have $s^{(0)}(v)=s^{(0)}(v)$).
+  Moreover, by the inductive hypothesis, it is derivable that
+  \[
+    \Gamma,s^{(i-1)} \ts M_i[\ask_X/y] \converges_{u_i} c_i,s^{(i)}\,,
+    \]
+  where $u_i$ is the subsequence of $w$ going from term $s^{(i-1)}(v)+1$ up to $s^{(i)}(v)$.
+
+  Now for any term $\Gamma,y\ts P$, we have
+  \[
+    P[\ask_X/y] = P[v\gets \suc !v;\tr_u !v/y][\ask_X/v\gets \suc !v;\tr_u !v]\,,
+    \]
+  and so by Lemma \ref{LemSecondSubstitution} we may derive
+  \[
+    \Gamma,s^{(0)} \ts M[\ask_X/y]\converges_{u_1\cat \cdots \cat u_n} c,s^{(n)}\,.
+    \]
+  But $u_1\cat \cdots \cat u_n$ is precisely the subsequence of $w$ going from term $s^{(0)}(v)+1$ up to $s^{(n)}(v)$!
+
+  This completes the first case.  
+  The second case is where $M=y$.  
+  Suppose, then, that
+  \[
+    \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v;\tr_w !v \converges x,(s'\vert v\mapsto l)
+    \]
+  is derivable in Idealized Algol.
+
+  Since IA is a deterministic language (so if $\Gamma,s\ts M\converges c,s'$ and $\Gamma,s\ts M \converges c',s''$ then $c=c'$ and $s'=s''$), then the derivation of this term must agree with the valid IA derivation given in Figure \ref{FigTheOneForTheLemma}.
+  It follows that $l=k+1$ (so, in particular, $l\ge k$) and that $x$ is the $(k+1)$-th term of $w$, so the single-term sequence $x$ is the subsequence of $w$ going from $k+1$ to $l$.
+
+  Then we have the derivation
+  \[
+    \inferrule{ }{\Gamma,s \ts \ask_X \converges_x x,s'}
+    \]
+  in \IAX.
   This completes the induction.
-  \label{IaSleepAdequacyLemma}
 \end{proof}
 
-\begin{theorem}[Computational adequacy for IA+$\sleep$]
-  Let $P\from\com$ be a term of IA+$\sleep$ and let $\sigma\from \bC\to \bC$ be its denotation in $\Kl_{R_\bC}$, considered as a morphism in $\G$.
-  Then $P\converges_n$ if and only if $\tit(\sigma)=n$.
-  \label{IaSleepComputationalAdequacy}
+We can now prove computational adequacy for our model.
+
+\begin{proposition}[Computational adequacy]
+  Let $M\from \com$ be a closed term of \IAX.  
+  Consider the denotation $\deno M\from 1 \to \bC$ in $\G_X$ as a morphism $1 \to (X \to \bC)$ in $\G$.  
+  Let $u\in X^*$ be a sequence and suppose that the composite
+  \[
+    1 \xrightarrow{\deno{M}}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \]
+  is not equal to $\bot$.  
+  Then
+  \[
+    ,()\ts M\converges_u \skipp,()\,.
+    \]
+  \label{PropKleisliAdequacy}
+\end{proposition}
+\begin{proof}
+  As before, the composite given in the statement is the denotation of the term
+  \[
+    \test_{|u|} (\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v))\\,.
+    \]
+  By the adequacy result for Idealized Algol, the fact that this denotation is not equal to $\bot$ means that the term converges to $\skipp$, from which we can deduce that
+  \[
+    \new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v
+    \]
+  converges to $|u|$.
+
+  It is easy to see that this is equivalent to derivability of the following relation in Idealized Algol.
+  \[
+    v,(v\mapsto 0) \ts M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X] \converges \skipp,(v\mapsto |u|)
+    \]
+  Now $u$ is the subsequence of $u^\top$ going from position $1$ to position $|u|$.  
+  So Lemma \ref{LemAdequacy} tells us that we must have
+  \[
+    ,()\ts M \converges_u \skipp,()
+    \]
+  in \IAX.
+\end{proof}
+
+\subsection{Full abstraction}
+
+To prove full abstraction of our semantics for \IAX, we introduce the usual intrinsic equivalence on terms.
+
+\begin{definition}
+  Let $\sigma,\tau\from A \to B$ be morphisms in $\G_X$.  
+  By currying, we may consider $A$ and $B$ as morphisms $1 \to (A \to B)$ in $\G_X$.
+  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$ and for all sequences $u\in X^*$, if we regard the $\alpha;\sigma,\alpha;\tau\from 1 \to \bC$ as morphisms $X \to \bC$ in $\G$, then the composites
+  \begin{mathpar}
+    1 \xrightarrow{\alpha;\sigma}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \and
+    1 \xrightarrow{\alpha;\tau}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+  \end{mathpar}
+  are equal.
+\end{definition}
+
+\begin{theorem}[Full abstraction]
+  Let $M,N\from T$ be closed terms of \IAX.  
+  Then $M,N$ are observationally equivalent -- i.e., for all contexts $C[-]\from\com$ of \IAX with a hole of type $T$ and for all sequences $u\in X^*$, 
+  \[
+    ,()\ts C[M] \converges_u \skipp,() \Longleftrightarrow ,()\ts C[N] \converges_u \skipp,()\,\text{--}
+    \]
+  if and only if $\deno{M}\sim\deno{N}$.
+  \label{TheKleisliFullAbstraction}
 \end{theorem}
 \begin{proof}
-  The forward direction is Proposition \ref{IaSleepSoundness}.  
-  For the reverse direction, note that if $\tit(\sigma)=n$, it means that
-  \[
-    \deno{\test_n(\new v=0\text{ in }P[v\gets \suc!v/\sleep];!v])} \ne \bot\,,
-  \]
-  which, by Proposition \ref{SamsonGuyAdequacy}, means that
-  \[
-    \test_n(\new v=0\text{ in } P[v\gets\suc!v/\sleep];!v])\converges
-  \]
-  in Idealized Algol, and therefore that
-  \[
-    v,(v\mapsto 0) \ts P[v\gets\suc!v/\sleep]\converges \skipp,(v\mapsto n)\,.
-    \]
-  From Lemma \ref{IaSleepAdequacyLemma}, we deduce that we must have
-  \[
-    ,() \ts P \converges_m \skipp,()
-    \]
-  in IA+$\sleep$ for some $m$, and by Lemma \ref{IaSleepsSoundnessLemma} we must have $m=n$.  
-  Therefore, $P\converges_n$.
-\end{proof}
-
-The last definition we need to make is the standard intrinsic equivalence relation.
-
-\begin{definition}
-  Let $\sigma,\tau\from A \to B$ be morphisms in $\Kl_{R_\bC}$.  
-  By currying, we may consider $\sigma,\tau$ to be morphisms $1 \to (A \to B)$.  
-  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$, we have $\tit(\sigma;\alpha)=\tit(\sigma;\beta)$.
-\end{definition}
-
-We now have all the tools necessary to prove that $Kl_{R_\bC}$ is fully abstract for IA+$\sleep$.
-The technique we use is standard and relies on a factorization result, as with the proofs given in \cite{SamsonGuyIAActive} and \cite{mcCHFiniteND}.  
-The difference here is that our factorization result is immediate, and does not rely on any combinatorial arguments.
-
-\begin{theorem}
-  Let $M,N\from T$ be two terms of IA+$\sleep$.  
-  Then $M$ and $N$ are observationally equivalent if and only if $\deno{M}\sim\deno{N}$.
-  \label{IaSleepTimeComplexity}
-\end{theorem}
-\begin{proof}
-  First suppose that $M$ and $N$ are not observationally equivalent.  
-  So there is some context $-\from T\ts C[-]\from\com$ such that $C[M]$ and $C[N]$ have different operational behaviours in IA+$\sleep$.
-  By Theorem \ref{IaSleepComputationalAdequacy} we know that for any program $P$ we have $P\converges_n$ if and only if $\tit(\deno P)=n$ and $P\diverges$ if and only if $\tit(\deno P)=\infty$.
-  Therefore, we must have $\tit(\deno{C[M]})\ne \tit(\deno{C[n]})$.  
-  But since $\deno{C[M]}=\deno{M};\deno{C}$ and $\deno{C[N]}=\deno{N};\deno{C}$, we must have $\deno M\not\sim \deno N$.
-
-  Conversely, suppose that $\deno M \not\sim \deno N$.  
-  So there is some $\alpha\from \deno{T} \to \bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.
-
-  Let us now work in the category $\G$.  
-  So $\deno{M},\deno{N}$ may be regarded as morphisms $1 \to (\bC \to \deno{T})$ and $\alpha$ may be regarded as a morphism $\deno{T} \to (\bC \to \bC)$.
-  Then the composites $\deno M;\alpha$ and $\deno N;\alpha$ within $\Kl_{R_\bC}$ are given by the following composites in $\G$.
+  First, suppose that $\deno{M}\sim\deno{N}$.  
+  Let $C[-]\from\com$ be a context with a hole of type $T$.  
+  Then the denotation of $t\ts C[t]$ is a morphism $\alpha\from \deno{T} \to \bC$.
+  Moreover, the denotation of $C[M]$ is the composite $\alpha;\deno{M}$ and that of $C[N]$ is the composite $\alpha;\deno{N}$, by functional completeness.
+
+  Then the composites
+  \begin{mathpar}
+    1 \xrightarrow{\alpha;\sigma}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \and
+    1 \xrightarrow{\alpha;\tau}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+  \end{mathpar}
+  are equal, so $C[M]\converges_u\skipp$ if and only if $C[N]\converges_u\skipp$ by Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy}.
+
+  Conversely, suppose that $M\not\sim N$.  
+  So there is some $\alpha\from \deno T \to \bC$ in $\G_X$ and some sequence $u$ such that (without loss of generality),
+  \begin{mathpar}
+    (\alpha;\deno M);\eta_u;\deno{\neww};t_{|u|} \ne \bot
+    \and
+    (\alpha;\deno N);\eta_u;\deno{\neww};t_{|u|} = \bot\,.
+  \end{mathpar}
+  Here, we have enclosed $\alpha;\deno M$ and $\alpha;\deno N$ in brackets to indicate that the composition is taken in the Kleisli category $\G_X$, and then the whole thing is considered as a morphism $1 \to (X \to \bC)$ in $\G$.
+
+  More specifically, these composites are given by the composites
   \begin{mathpar}
@@
   \end{mathpar} 
-  Without loss of generality, suppose that there exists some $n$ such that
-  \begin{mathpar}
-    \tit(\deno{M};(\bC \to \alpha);\mu)=n \and \tit(\deno{N};(\bC \to \alpha);\mu)\ne n\,.
-  \end{mathpar}
-  This means that we must have
-  \begin{mathpar}
-    \deno M;(\bC \to \alpha);\mu;\eta;\new_\bC;t_n \ne \bot
-    \and
-    \deno N;(\bC \to \alpha);\mu;\eta;\new_\bC;t_n = \bot
-  \end{mathpar}
-  in $\G$ (where $\eta$ is as defined in Definition \ref{DefTimeTaken}).
-
-  $\G$ is enriched in algebraic cpos, so $\alpha$ is the least upper bound of its compact approximants.  
-  It follows that there is some compact $\alpha'\subset \alpha$ such that
-  \begin{mathpar}
-    \deno M;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n \ne \bot
-    \and
-    \deno N;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n = \bot\,.
-  \end{mathpar}
-  In other words:
-  \begin{mathpar}
-    \tit(\deno M;(\bC \to \alpha');\mu) = n\,;
-    \and
-    \tit(\deno M;(\bC \to \alpha');\mu) \ne n\,.
-  \end{mathpar}
-  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $C[\sleep] \from \com \to \com$ in $\Kl_{R_\bC}$.
+  in $\G$, where $\mu$ indicates precomposition with the diagonal.
+
+  Now $\alpha$ is the least upper bound of its compact approximans, so it follows that there is some compact $\alpha'\subseteq \alpha$ such that
+  \begin{mathpar}
+    \deno M;(\bC \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|} \ne \bot
+    \and
+    \deno N;(\bC \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|} = \bot\,.
+  \end{mathpar}
+  Then, by compact definability in $\G$, $\alpha'$ is the denotation of some IA term $x\from T \ts C[x]\from X \to \com$, which is therefore the denotation of the term $x\from T \ts C[x]\,\ask_X \from \com$ in $\G_X$.
   So we get
   \begin{mathpar}
-    \tit(\deno{C[\sleep] M}) = n\,;
-    \and
-    \tit(\deno{C[\sleep] N}) \ne n\,.
-  \end{mathpar}
-  By Theorem \ref{IaSleepComputationalAdequacy}, $C[\sleep] M\converges_n$ and $C[\sleep] N\not\converges_n$.  
-  Therefore, $M$ and $N$ are observationally inequivalent in IA+$\sleep$.
+    \deno{C[M]};\eta_u;\deno{\neww};t_{|u|} \ne \bot
+    \and
+    \deno{C[N]};\eta_u;\deno{\neww};t_{|u|} = \bot\,,
+  \end{mathpar}
+  and so $C[M]\converges_u\skipp$ by Proposition \ref{PropKleisliAdequacy}, while $C[N] \not\converges_u \skipp$ by Proposition \ref{PropKleisliSoundness}.
+  Therefore, $M$ and $N$ are observationally inequivalent in \IAX.
 \end{proof}
+
+\subsection{Comparison with Ghica's slot games}
+
+Let us suppose now that $\G$ is the category of games and visible strategies, and that $X=\bC$.  
+As we remarked above, this means that \IAX can be interpreted as a language for modelling time complexity.
+
+We compare our approach to a different one, due to Dan Ghica \cite{SlotGames}.  
+Given a game $A$, Ghica defines a \emph{play with costs} in $A$ to be a justified sequence $s\in (M_A + \{\slot\})^*$ such that $s\vert_{M_A}\in P_A$.
+Here, $\slot$ is a special symbol called a \emph{slot} or \emph{token-action}, which can be interleaved throughout the play $s\vert_{M_A}$ from $A$.  
+We shall additionally impose the requirement that an occurrence of the special symbol $\slot$ must take place either after an $O$-move in $A$ or after another instance of $\slot$.
+The token actions do not carry justification pointers.
+
+Following Ghica, we define a \emph{strategy with costs} to be a prefix-closed set $\sigma$ of plays with costs such that the set $\sigma\vert_{M_A} = \{s\vert_{M_A}\suchthat s\in \sigma\}$ is a valid visible strategy for $A$.
+
+The identity strategy with costs is the usual identity strategy, without any token actions.  
+Given an interleaving $\s\in(M_A+M_B+M_C+\{\slot\})^*$ of two justified plays with costs for $A \implies B$ and $B\implies C$, write $\s\vert_{A,B}$ for the subsequence consisting of all those moves in $A$ and $B$, together with all token actions such that the previous move was an $O$-move in $A\implies B$.
+Define $\s\vert_{B,C}$ similarly.  
+Then if $\sigma\from A \implies B$ and $\tau\from B \implies C$ are strategies with costs, we define $\sigma\|\tau$ to be the set of all such sequences $\s$ such that $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$.
+Lastly, we define $\sigma;\tau$ to be the set of all sequences obtained by taking a sequence $\s\in\sigma\|\tau$ and removing all the moves in $B$ (but retaining all the token actions, including those that arise between moves in $B$).
+The usual arguments apply to show that this is indeed a category.
+
+This seems like a purely combinatorial construction, but it can actually be subsumed into our category-theoretic apparatus.
+
+\begin{proposition}
+  Let $A$ be a game.  
+  Then there is a bijection
+  \[
+    c \from \{\text{normal strategies for $\oc\bC \implies A$}\}\leftrightarrow\{\text{strategies with costs for $A$}\}
+    \]
+  Moreover, this bijection respects composition: let $\sigma \from\oc\bC \implies (A \to B)$ and $\tau \from \oc\bC \implies (B \to C)$ be strategies.  
+  Write $\sigma;\tau$ for the Kleisli composition of $\sigma$ and $\tau$ in $\G_{\bC}$; i.e., the composite
+  \[
+    \oc\bC \xrightarrow{\mu}
+    \oc\bC \tensor \oc\bC \xrightarrow{\sigma\tensor\tau}
+    (A \implies B) \tensor (B \implies C) \xrightarrow{;}
+    (A \implies C)\,.
+    \]
+  Then $c(\sigma;\tau)=c(\sigma);c(\tau)$.  
+  Moreover, $c(\id_A)$ is the identity in the category of games and strategies with costs.
+\end{proposition}
+\begin{proof}
+  The map $c$ is the unique functor given by the functional completeness theorem that sends the canonical strategy $\id \from \oc\bC \to \bC$ to the strategy with costs for $\bC$ with maximal play
+  \[
+    q\slot a\,.
+    \]
+  More synthetically, we get from a strategy for $\sigma\from\oc \bC \implies A$ to a strategy with costs for $A$ by replacing each occurrence of the pair $qa$ occurring in the $\bC$ component with the token action $\slot$ in each play of $\sigma$.
+
+  This functor is the identity on objects, and it is fully faithful, since it has an obvious inverse, given by taking a strategy with costs and replacing each occurrence of the token action with a pair of moves $qa$ in $\oc\bC$.
+  Since each token action must always occur after an opponent move or after another token action, and since player $O$ has no reply to the move $q$ other than the move $a$, this always gives us a legal strategy.
+\end{proof}
+
+Therefore, we see that the category of games and strategies with costs is isomorphic to the Kleisli category $\G_\bC$, which we have already shown to be fully abstract for a language with time complexity.
+
+\subsection{Alternative reduction rules - may testing}
+
+We remarked above that if $X\in\{\bB,\bN\}$, then \IAX is a model of nondeterminism, finite in the case of $\bB$ and countable in the case of $\bN$.  
+However, our operational semantics is not the usual one for these languages.
+
+For example, the terms
+\begin{mathpar}
+  \If \ask_\bB \Then \true \Else \false\from \bool
+  \and
+  \If \ask_\bB \Then \false \Else \true\from \bool
+\end{mathpar}
+are not observationally equivalent in our operational semantics; indeed, we have
+\begin{mathpar}
+  \If \ask_\bB \Then \true \Else \false \converges_{\true} \true
+  \and
+  \If \ask_\bB \Then \false \Else \true \converges_{\true} \false\,.
+\end{mathpar}
+
+However, these terms (which both nondeterministically choose either the true or the false value), \emph{should} be observationally equivalent in any sensible nondeterministic semantics.  
+The issue is the labelling on the reduction relations, which is saving too much information about the reduction of the term.
+Indeed, this is sort of the point of nondeterminism: we should be able to make nondeterministic choices without recording which value we used for that choice.
+
+\begin{definition}[\cite{mcCHFiniteND}]
+  If $X\in\{\bB,\bN\}$, we define an operational relation $\converges$ (`may converge') on the language \IAX as follows.  
+  The rules for $\converges$ are identical to the operational rules for Idealized Algol, with the addition of the following rule for the primitive $\ask_X$.
+  \[
+    \inferrule*[right=$x\in X$]{ }{\Gamma,s\ts \ask_X \converges x,s}
+    \]
+\end{definition}
+It is clear that these rules are exactly the same as our original operational semantics for \IAX, but with the sequences $u$ removed.  
+Moreover, if we have a valid derivation of $\Gamma,s\ts M\converges u,s'$, then it is clear (by induction) that we may annotate all the occurrences of $\converges$ with suitable sequences in order to obtain a derivation of $\Gamma,s\ts M\converges_u c,s'$ for some $u\in X^*$.
+So we get the following alternative definition of may convergence.
+\begin{definition}
+  We say that $\Gamma,s\ts M\converges c,s'$ if there is some $u\in X^*$ such that $\Gamma,s\ts M\converges_u c,s'$.
+\end{definition}
+
+We can reflect this operational relation in the semantics by modifying the definition of intrinsic equivalence.
+
+Firstly, an obvious consequence of Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy} is that we have
+
+\begin{corollary}
+  Let $M\from\com$ be a closed term of \IAX.  
+  Consider the denotation $\deno M\from 1 \to \bC$ in $\G_X$ as a morphism $1 \to (X \to \bC)$ in $\G$.  
+  Then there exists some sequence $u\in X^*$ such that the composite
+  \[
+    1 \xrightarrow{\deno M}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \]
+  if and only if
+  \[
+    ,()\ts M \converges \skipp,()\,.
+    \]
+  \label{CorMayAdequacy}
+\end{corollary}
+
+In light of this result, we can define a new intrinsic equivalence on morphisms in $\G_X$:
+
+\begin{definition}
+  Let $\sigma,\tau\from A \to B$ be morphisms in $\G_X$, considered as morphisms $1 \to (A \to B)$ in $\G_X$.  
+  We say that $\sigma \sim_{\may} \tau$ if for all $u\in X^*$ there exists $v\in X^*$ such that the composites
+  \begin{mathpar}
+    1 \xrightarrow{\alpha;\sigma}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \and
+    1 \xrightarrow{\alpha;\tau}
+    (X \to \bC) \xrightarrow{\eta_v}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|v|}}
+    \bC
+  \end{mathpar}
+  are equal, and vice versa.
+  \label{DefMayIntrinsicEquivalence}
+\end{definition}
+
+Then exactly the same argument as before gives us a full abstraction result for may-equivalence.
+
+\begin{theorem}
+  Let $M,N\from T$ be closed terms of \IAX. Then $M,N$ are may-observationally equivalent -- i.e., for all contexts $C[-]\from \com$ of \IAX with a hole of type $T$, \[
+    ,()\ts C[M] \converges \skipp,() \Leftrightarrow ,()\ts C[N] \converges \skipp,()\,\text{--}
+    \]
+  if and only if $\deno M \sim_{\may} \deno N$.
+\end{theorem}
+\begin{proof}
+  Suppose that $\deno M\sim_{\may}\deno N$.  
+  Let $C[-]$ be a context of \IAX, interpreted as a morphism $\alpha \from \deno T \to \bC$.
+
+  Suppose that $,()\ts C[M] \converges \skipp,()$.  
+  So there is some sequence $u\in X^*$ such that $,()\ts C[M] \converges_u \skipp,()$ and therefore the composite
+  \[
+    1 \xrightarrow{\alpha;\deno{M}}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \]
+  is not equal to $\bot$.  
+  Therefore, there exists some $v\in X^*$ such that the composite
+  \[
+    1 \xrightarrow{\alpha;\deno{N}}
+    (X \to \bC) \xrightarrow{\eta_v}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|v|}}
+    \bC
+    \]
+  Therefore, $,()\ts C[N] \converges_v \skipp,()$ and so $,()\ts C[N] \converges \skipp,()$.
+  The reverse direction is identical.
+
+  Conversely, suppose that $M,N$ are may-observationally equivalent.  
+  Then, as before, we can take $\alpha$ to be compact, whence definable, in Definition \ref{DefMayIntrinsicEquivalence}, and the proof continues as in the first part, but in reverse.
+\end{proof}
+
+Let us examine what this means in the category of games.
+If $\sigma\from \oc X \implies \bC$ is a strategy, then, by our discussion at the end of \sec\ref{SecSoundness}, we know that, for any sequence $u$, the composite
+\[
+  1 \xrightarrow{\sigma}
+  (X \to \bC) \xrightarrow{\eta_u}
+  (\Var \to \bN) \xrightarrow{\deno\neww}
+  \bN \xrightarrow{t_{|u|}}
+  \bC
+  \]
+is not equal to $\bot$ if and only if $\sigma$ contains the play
+\[
+  q (q u^{(i)})_{i=0}^{|u|-1} a\,.
+  \]
+Moreover, since any complete play in $\oc X \implies \bC$ must take this form, we can see there exists such a $u$ making the composite above not equal to $\bot$ if and only if
+\[
+  qa \in \{s\vert_\bC \suchthat s\in\sigma\text{ is complete}\}\,.
+  \]
+This suggests a general equivalence relation on Kleisli morphisms in $\G_X$: given a strategy $\sigma\from \oc X \implies A$, we write $\sigma\vert A$ for the set
+\[
+  \{s\vert_A \suchthat s\in \sigma\text{ is complete}\}\,.
+  \]
+We say that two strategies $\sigma,\tau\from \oc X \implies A$ are may-equivalent, and write $\sigma\approx_{\may}\tau$, if
+\[
+  \sigma\vert_A = \tau\vert_A\,.
+  \]
+In this case, Corollary \ref{CorMayAdequacy} tells us that $M\converges \skipp$ if and only if $\sigma\approx_{\may}\tau$.
+
+We need to show that this respects composition, so that we get a category if we take the quotient by this equivalence relation.
+\begin{proposition}
+  Let $\sigma,\sigma' \from A \to B$, $\tau,\tau'\from B \to C$ be morphisms in $\G_X$.
+  Suppose that $\sigma\approx_{\may}\sigma'$ and $\tau\approx_{\may}\tau'$.  
+  Then $\sigma;\tau \approx_{\may} \sigma';\tau'$.
+\end{proposition}
+\begin{proof}
+  A complete play in $\sigma;\tau$ is given by a sequence $\s\vert_{X,A,C}$, where $\s\in (M_X + M_A + M_B + M_C)^*$ that is a legal interaction of a complete play in $\tau$ with a collection of complete plays in $\sigma$, with $B$-components being identified.
+  Then $\s\vert_{A,C}$ can alternatively be characterized as $\t\vert_{A,C}$, where $\t\in (M_A + M_B + M_C)^*$ is a legal interaction of a sequence from $\tau\vert_{B,C}$ with a collection of sequences from $\sigma\vert_{A,B}$.
+
+  It follows that if $\sigma\vert_{A,B}=\sigma'\vert_{A,B}$ and $\tau\vert_{B,C}=\tau'\vert_{B,C}$, then $\sigma;\tau\vert_{A,C} = \sigma';\tau'\vert_{A,C}$.
+\end{proof}
+
+Now we can also see that this equivalence we have just defined is subsumed into the intrinsic equivalence.
+\begin{proposition}
+  Let $\sigma,\tau\from \oc X \implies A$ be strategies.  
+  If $\sigma\approx_{\may}\tau$ then $\sigma\sim_{\may} \tau$.
+\end{proposition}
+\begin{proof}
+  Given strategies $\sigma,\tau\from A$ in $\G_X$, we have $\sigma \sim_{\may} \tau$ if and only if $\alpha;\sigma\approx_{\may}\alpha;\tau$ for any morphism $\alpha\from \oc A \implies \bC$ in $\G_X$.
+  If $\sigma\approx_{\may}\tau$, we have
+  \[
+    \alpha;\sigma\vert_{\bC} = \alpha;(\sigma\vert_{\bC}) = \alpha;(\tau\vert_{\bC}) = \alpha;\tau\vert_{\bC}\,.\qedhere
+    \]
+\end{proof}
+
+Note that it is also the case that if $\alpha\approx_{\may}\alpha'$ and $\sigma\approx_{\may}\tau$ then $\alpha;\sigma \approx_{\may} \alpha';\tau$.  
+Therefore, the Full Abstraction result we have just proved applies to the quotiented category.
+
+The definition of the relation $\approx_{\may}$ suggests that we might forget about the $\oc X$ component of a strategy $\sigma\from\oc X \implies A$ altogether, and consider only the set $\sigma\vert_A$.
+This set is not a strategy, since it does not satisfy the determinism requirement, but it satisfies every other requirement.
+
+\begin{definition}
+  Given a game $A$, a \emph{nondeterministic strategy} is a prefix-closed set of even-length legal plays from $A$.
+\end{definition}
+
+We can compose nondeterministic strategies using `parallel composition plus hiding', just as for deterministic ones, and we get a Cartesian closed category in the same way.  
+We interpret all the Idealized Algol terms in the usual way as deterministic strategies, interpreting the nondeterministic primitive $\ask_X$ as the nondeterministic strategy for $X$ with maximal plays
+\[
+  qx
+  \]
+for every $x\in X$.
+
+It is already known (see \cite{mcCHFiniteND}) that this model is fully abstract for (finitely or countably) nondeterministic Idealized Algol with may-contextual equivalence.
+
+\subsection{Alternative reduction rules - must testing}
+
+A more interesting, and more complicated, reduction rule for nondeterministic IA is the \emph{must-convergence} relation.
+
+We shall define this indirectly via its negation.
+
+\begin{definition}
+  We shall define a relation
+  \[
+    \Gamma,s\ts M\diverges
+    \]
+  between $\Var$-contexts $\Gamma$, $\Gamma$-stores $s$ and terms $\Gamma\ts M\from T$ of Idealized Algol.
+
+  The rules for this relation may be deduced from the rules for Idealized Algol.  
+  If
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges c,s^{(n)}}\,,
+    \]
+  is an IA rule, then
+\end{definition}
 

### 2019-03-17 Thesis/thesis.tex
Some more.

@@
 \section{Monads and Kleisli categories}
-\ref{SecMonads}
+\label{SecMonads}
 
@@
     {
-      \inferrule*
+      \inferrule*[sep=1.7em]
       {
@@
     1 \xrightarrow{\deno M}
-    (\bC \to \deno T) \xrightarrow{\bC \to \alpha}
-    (\bC \to (\bC \to \bC)) \xrightarrow{\mu}
-    (\bC \to \bC)
+    (X \to \deno T) \xrightarrow{X \to \alpha}
+    (X \to (X \to \bC)) \xrightarrow{\mu}
+    (X \to \bC)
     \and
     1 \xrightarrow{\deno N}
-    (\bC \to \deno T) \xrightarrow{\bC \to \alpha}
-    (\bC \to (\bC \to \bC)) \xrightarrow{\mu}
-    (\bC \to \bC)
+    (X \to \deno T) \xrightarrow{X \to \alpha}
+    (X \to (X \to \bC)) \xrightarrow{\mu}
+    (X \to \bC)
   \end{mathpar} 
@@
 
-  Now $\alpha$ is the least upper bound of its compact approximans, so it follows that there is some compact $\alpha'\subseteq \alpha$ such that
+  Now $\alpha$ is the least upper bound of its compact approximants, so it follows that there is some compact $\alpha'\subseteq \alpha$ such that
   \begin{mathpar}
-    \deno M;(\bC \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|} \ne \bot
-    \and
-    \deno N;(\bC \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|} = \bot\,.
+    \deno M;(X \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|} \ne \bot
+    \and
+    \deno N;(X \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|} = \bot\,.
   \end{mathpar}
@@
 
-Firstly, an obvious consequence of Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy} is that we have
+Firstly, an obvious consequence of Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy} is that
 
@@
     \]
-  if and only if
+  is not equal to $\bot$, if and only if
   \[
@@
     \]
-  between $\Var$-contexts $\Gamma$, $\Gamma$-stores $s$ and terms $\Gamma\ts M\from T$ of Idealized Algol.
+  ($M$ `may diverge') between $\Var$-contexts $\Gamma$, $\Gamma$-stores $s$ and terms $\Gamma\ts M\from T$ of Idealized Algol.
 
@@
     \]
-  is an IA rule, then
+  is an IA rule, then for each $j=1,\cdots,n$ we have a rule
+  \[
+    \inferrule*[sep=1.9em]{\Gamma,s^{(0)}\ts M_1 \converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(j-2)} \ts M_{j-1} \converges c_{j-1} \\ \Gamma,s^{(j-1)}\ts M_j\diverges}
+    {\Gamma,s^{(0)} \ts M \diverges}\,.
+    \]
+  In other words, if the evaluation of the term $M$ diverges at any step, then the whole thing diverges.  
+  Note that since the rules for the canonical forms have no premises, there are no rules relating them to the $\diverges$ predicate.
+
+  Crucially, these rules are interpreted not inductively but coinductively; in other words, the derivation trees for $\diverges$ are allowed to have infinite height.
+  Indeed, since every rule for $\diverges$ has at least one premise, any valid tree must be infinitely tall.
+
+  If there is no such derivation tree, then we say that $M$ \emph{must converge}, and write $\Gamma,s\ts M\mustconverge$.
+  \label{DefMayDivergence}
 \end{definition}
+
+\begin{example}
+  If $\Gamma\ts c$ is a canonical form, then $\Gamma\ts c\mustconverge$, since there is no inference that we can apply that will yield the term $\Gamma\ts c\diverges$ on the bottom.
+\end{example}
+
+\begin{example}
+  $,()\ts \Y(\lambda x.x)\diverges$ because it has the following infinite derivation tree.
+  \[
+    \inferrule*
+    {
+      \inferrule*
+      {
+        \inferrule*
+        {
+        }
+        {
+          ,()\ts (\lambda x.x) \converges (\lambda x.x),()
+        }
+        \\
+        \inferrule*
+        {
+          \vdots
+        }
+        {
+          ,() \ts \Y(\lambda x.x)\diverges
+        }
+      }
+      {
+        ,()\ts (\lambda x.x)(\Y(\lambda x.x)) \diverges
+      }
+    }
+    {
+      ,()\ts \Y(\lambda x.x)\diverges
+    }
+    \]
+\end{example}
+
+It is possible to characterize the $\mustconverge$ directly via an inductive relation (see \cite{RusssThesis}, for instance).  
+We will give an alternative definition that will relate it to our existing rules $\converges_u$.
+
+\begin{definition}
+  We say that $\Gamma,s\ts M\mustconverge$ if for every infinite sequence $w\in X^\omega$ there is some finite prefix $u\pprefix w$ such that $\Gamma,s\ts M\converges_u c,s'$ for some canonical form $c$ and some $\Gamma$-store $s'$.
+  \label{DefMustConvergence}
+\end{definition}
+
+Before we show that the two definitions are equivalent, we shall examine why this one makes sense.  
+Recall that we said that the statement $\Gamma,s\ts M\converges_u c,s'$ meant that $M$ will converge to $c$ in the case that the values we obtain by querying the nondeterministic oracle form the sequence $u$.
+Our initial thought, then, might be to say that $\Gamma,s\ts M\mustconverge$ if for all $u\in X^*$, $\Gamma,s\ts M\converges_u c,s'$ for some $c,s'$, but this is not the case.  
+For example, if we have
+\[
+  M = \If \ask_\bB \Then \true \Else \false\,,
+  \]
+then $M\converges_\true \true$ and $M\converges_\false \false$.  
+However, it is not the case that $M\converges_\epsilon c$, nor that $M\converges_{\true\false\false\true\false}c$ for any $c$.
+Instead, we should think of the nondeterministic oracle as a promise to provide us with some infinite sequence of elements of $X$, only some of which we will use to converge.
+
+\begin{proposition}
+  The two definitions of the $\mustconverge$ predicate given in Definitions \ref{DefMayDivergence} and \ref{DefMustConvergence} are equivalent.
+\end{proposition}
+\begin{proof}
+  Suppose that $\Gamma,s\ts M\diverges$.  
+  We coinductively construct a sequence $w\in X^\omega$ such that $\Gamma,s\ts M\not\converges_u c,s'$ for any finite prefix $u\pprefix w$ and any $c,s'$.
+  We shall use the notation $\Gamma,s\ts M\diverges^w$ to indicate this $w$.
+
+  Given any rule
+  \[
+    \inferrule{\Gamma,s^{(0)}\ts M_1 \converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(j-2)} \ts M_{j-1} \converges c_{j-1} \\ \Gamma,s^{(j-1)}\ts M_j\diverges}
+    {\Gamma,s^{(0)} \ts M \diverges}\,,
+    \]
+  by our definition of $\converges$, there are $u_1,\cdots,u_{j-1}\in X^*$ such that $\Gamma,s^{(i-1)}\ts M_i\converges_{u_i}c_i,s^{(i)}$ for each $i=1,\cdots,j-1$.
+
+  The corresponding coinductive rule is then
+  \[
+    \inferrule*[sep=8pt]{\Gamma,s^{(0)}\ts M_1 \converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(j-2)} \ts M_{j-1} \converges_{u_{j-1}} c_{j-1} \\ \Gamma,s^{(j-1)}\ts M_j\diverges^w}
+    {\Gamma,s^{(0)} \ts M \diverges^{u_1\cat \cdots \cat u_{j-1}\cat w}}\,.
+    \]
+  In other words, the sequence $w$ at the bottom of the tree may be characterized as the concatenation of all the sequences $u$ constructed for the $\converges$ relation in the tree, working bottom to top and left to right.
+  If the $w$ so formed is a finite sequence, then pad it with arbitrary values so that it becomes infinite.
+
+  Now suppose that $u\pprefix w$ is some finite prefix such that $\Gamma,s\ts M\converges_u c,s'$ for some $c,s'$.  
+  We claim that $\Gamma,s\ts M\not\diverges$, giving us a contradiction.
+
+  The proof of the claim is via induction on the derivation of $\Gamma,s\ts M\converges_u c,s'$.
+
+  Suppose that the last rule takes the form
+  \[
+    \inferrule*{\Gamma,s^{(0)}\ts M_1\converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges_{u_n} c_n,s^{(n)}}
+    {\Gamma,s^{(0)} \ts M \converges_{u_1\cat \cdots\cat u_n} c,s^{(n)}}\,.
+    \]
+  Then inspection of the IA rules tells us that the last step in our derivation of $\Gamma,s^{(0)} \ts M\diverges$ must look like
+  \[
+    \inferrule*[sep=8pt]{\Gamma,s^{(0)}\ts M_1 \converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(j-2)} \ts M_{j-1} \converges_{u_{j-1}} c_{j-1} \\ \Gamma,s^{(j-1)}\ts M_j\diverges^w}
+    {\Gamma,s^{(0)} \ts M \diverges^{u_1\cat \cdots \cat u_{j-1}\cat w}}
+    \]
+  \emph{for the same $M_i$ and $c_i$}.
+  But we had $\Gamma,s^{(j-1)}\ts M_j\converges_{u_j} c_j,s^{(j)}$.  
+  By hypothesis, $u_1\cat \cdots \cat u_n$ is a finite prefix of $u_1 \cat \cdots \cat u_{j-1} \cat w$, and so $u_j$ is a finite prefix of $w$.  
+  Therefore, by the inductive hypothesis applied to $M_j$, we cannot have $\Gamma,s^{(j-1)}\ts M_j\diverges$, leading to the desired contradiction.
+
+  For the converse, define an \emph{$n$-truncated} derivation tree to be a derivation tree of height $n$ such that the premises of the form $\Gamma,s\ts M\diverges^w$ may occur at the top level without proof.
+  Then we define a family of functions $(F_i \suchthat i \ge 0)$ that take an infinite sequence $w\in X^\omega$ and a triple $\Gamma,s\ts M$ and returns either a proof of height $\le i$ of $\Gamma,s\ts M\converges_u c,s'$ for some $u\pprefix w$, or some $i$-truncated proof of $\Gamma,s\ts M\diverges^v$ for some (possibly infinite) $v\prefix w$.
+
+  For $i=0$, $F(w,\Gamma,s\ts M)$ is the tree of the form
+  \[
+    \Gamma,s\ts M\diverges^w\,,
+    \]
+  where this statement is treated as an unproven (and in many cases untrue) hypothesis.
+
+  Now we define $F_{i+1}(w,\Gamma,s\ts M)$ as follows.  
+  If $M$ is a canonical form, then $F_{i+1}(w,\Gamma,s\ts M)$ is the derivation.
+  \[
+    \inferrule*{ }{\Gamma,s\ts M\converges_\epsilon M,s}\,.
+    \]
+  If $M=\ask_X$, then $F_{i+1}(w,\Gamma,s\ts M)$ is the derivation
+  \[
+    \inferrule*{ }{\Gamma,s\ts M\converges_{w^{(0)}} w^{(0)},s}\,.
+    \]
+  Otherwise, based on the structure of $M$, we choose a first premise $M_1$ for $M$.  
+  In most cases, there is a unique \IAX rule that applies to $M$, but sometimes (i.e., if $M$ is $\pred M'$, $\If M' \Then N' \Else P'$, $\IfO M' \Then N' \Else P'$, $!V$ or $V\gets E$) there may be more than one possible rule.
+  However, in all of these cases, the first premise of each rule is the same.  
+  For instance, if $M=\If M' \Then N' \Else P'$ then the first premise of both the possible IA rules is $M'$, and the value that this converges to then determines which instance of the $\If$ rule we use.
+
+  We evaluate $F_i(w,\Gamma,s\ts M_1)$.  
+  If $F_i(w,\Gamma,s\ts M_1)$ is a complete proof that $\Gamma,s\ts M_1 \converges_{u_1} c_1,s^{(1)}$ for $u\pprefix w$, then write $w=u_1w_2$ and move on to the next premise, computing $F_i(w_2,\Gamma,s\ts M_2)$.
+  Note that now the value of $c_1$ completely determines the \IAX rule we are using; for example, if $M=\If M' \Then N' \Else P'$, and $\Gamma,s\ts M' \converges_{u} c,s'$, then $c$ is either $\true$ or $\false$, and there is a unique \IAX rule that applies in each case.
+
+  We keep going through the premises of $M$ in order.  
+  If we satisfy them all, so that $F_i(w_i,\Gamma,s^{(i-1)} \ts M_i)$ is a proof that $\Gamma,s^{(i-1)} \ts M_i \converges_{u_i} c_i,s^{(i)}$ for each $M_i$, then we can put these together to get a derivation of
+  \[
+    \Gamma,s \ts M\converges_{u_1\cat \cdots \cat u_n} c,s^{(n)}\,,
+    \]
+  of height $\le i+1$, where $u_1\cat \cdots \cat u_n$ is a finite prefix of $w$.
+
+  Otherwise, at some point $F_i(w,\Gamma,s^{(j-1)}\ts M_j)$ must be an $i$-truncated proof that
+  \[
+    \Gamma,s^{(j-1)}\ts M_j\diverges^v
+    \]
+  for some $v\prefix w$.
+  In that case, since we have a proof of height $\le i$ for $\Gamma,s^{(k-1)}\ts M_k \converges_{u_k} c_k,s^{(k)}$ for each $k<j$, we can apply the appropriate rule for $\diverges^v$ to get an $(i+1)$-truncated proof that
+  \[
+    \Gamma,s\ts M\diverges^{u_1\cat \cdots \cat u_{j-1} \cat v}\,,
+    \]
+  where $u_1\cat \cdots \cat u^{j-1} \cat v$ is a prefix of $w$.
+
+  Now, given $w$ and $\Gamma,s\ts M$, either $F_m(\Gamma,s\ts M)$ is a proof that $\Gamma,s\ts M\converges_u c,s'$ for $u\pprefix w$ and $m$ sufficiently large, or the $F_i(w,\Gamma,s\ts M)$ form an infinite sequence of trees of increasing height that all extend one another.
+  In the second case, we can stitch the trees together to form an infinite derivation tree for $\Gamma,s\ts M\diverges$.
+
+  It follows that if there is some $w$ such that $\Gamma,s\ts M\not\converges_u c,s'$ for any finite prefix $u\pprefix w$, then there is an infinite derivation tree for $\Gamma,s\ts M\diverges$.
+\end{proof}
+
+We therefore get an adequacy result for must testing.
+
+\begin{definition}
+  Given a morphism $\sigma\from 1\to\bC$ in $\G_X$, considered as a morphism $X \to \bC$ in $\G$, we write $\sigma\downarrow_{\must}$ if whenever $w\in X^\omega$ is an infinite sequence, then $w$ has a finite prefix $u$ such that the composite
+  \[
+    1 \xrightarrow{\sigma}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \]
+  is not equal to $\bot$.
+\end{definition}
+
+\begin{corollary}
+  Let $M\from \com$ be a closed term of \IAX and consider the denotation $\deno M \from 1 \to \bC$ in $\G_X$ as a morphism $1 \to (X \to \bC)$ in $\G$.
+  Then $,()\ts M\mustconverge$ if and only if $\deno{M}\downarrow_{\must}$.
+  \label{CorAdeqMust}
+\end{corollary}
+
+Once again, this slightly abstruse result becomes much more natural when $\G$ is the category of games, though in this case things are a bit more subtle.  
+Let $\sigma$ be a strategy for $\oc X \implies \bC$.  
+We observed earlier that $\sigma;\eta_u;\deno{\new};t_{|u|}\neq\bot$ if and only if the sequence
+\[
+  q(qu^{(i)})_{i=0}^{|u|-1} a
+  \]
+is contained in $\sigma$, so consider what it means if we say that such a sequence is not contained in $\sigma$ for any $u\pprefix w$.  
+By the definition of a strategy, there are two reasons why this might happen.  
+Either there is a partiality in the strategy, so that for some finite $v\pprefix w$, player $P$ has no reply at all to the $O$-position
+\[
+  q(qv^{(i)})_{i=0}^{|v|-1}\,.
+  \]
+Or, $\sigma$ contains an infinite increasing sequence of plays, whose limit is the infinite sequence
+\[
+  q(qw^{(i)})_{i=0}^\infty\,.
+  \]
+\begin{definition}
+  We say that a strategy $\sigma\from \oc X \implies \bC$ is \emph{winning} if every finite play in $\sigma$ is contained inside some complete play; i.e., if $\sigma$ is total and contains no infinite plays.
+\end{definition}
+
+We have shown the following adequacy result.
+\begin{corollary}
+  Let $M\from \com$ be a closed term of \IAX and consider the denotation $\deno M \from 1 \to \bC$ in $\G_X$ as a morphism $X \to \bC$ in $\G$.
+  Then $,()\ts M\mustconverge$ if and only if this strategy is winning.
+\end{corollary}
+
+\subsection{Full Abstraction for Nondeterminism and Must Testing}
+
+We now extend our earlier definitions using the new $\mustconverge$ rule.
+
+\begin{definition}
+  Given closed terms $M,N\from T$ of \IAX, we write $M\equiv_{\must} N$, if for all contexts $-\from T\ts C[-]\from\com$, $C[M]\mustconverge$ if and only if $C[N]\mustconverge$.
+\end{definition}
+
+We write $M\emam N$ if $M\equiv_{\may} N$ and $M\equiv_{\must} N$.
+
+\begin{definition}
+  Given morphisms $\sigma,\tau\from A \to B$ in $\G_X$, considered as morphisms $1 \to (A \to B)$, we write $\sigma\sim_{\must}\tau$ if whenever $\alpha\from (A \to B) \to \bC$ is a morphism in $\G_X$ and $w\in X^\omega$ is an infinite sequence, then $\alpha;\sigma\downarrow_{\must}$ if and only if $\alpha;\tau\downarrow_{\must}$.
+\end{definition}
+
+We write $\sigma\smam \tau$ if $\sigma\sim_{\may}\tau$ and $\sigma\sim_{\must} \tau$.
+
+\begin{remark}
+  In the category of games we can simplify this to saying that $\alpha;\sigma\approx_{\may}\alpha;\tau$ and that either $\alpha;\sigma$ and $\alpha;\tau$ are both winning, or neither is.
+\end{remark}
+
+Now we might expect to be able to prove a full abstraction result as before, namely that $\deno M\smam \deno N$ if and only if $M\emam N$.  
+In the case of finite nondeterminism, this is possible.
+
+\begin{theorem}
+  Let $M,N\from T$ be closed terms of IA${}_{\bB}$.
+  Then $M\emam N$ if and only if $\deno M\smam \deno N$.
+  \label{FullAbstractionFiniteNondeterminism}
+\end{theorem}
+\begin{proof}
+  We already know that $\deno M\sim_{\may}\deno N$ if and only if $M$ and $N$ are may-contextually equivalent, so it is sufficient to prove that $\deno M\sim_{\must}\deno N$ if and only if $M\equiv_{\must}N$.
+
+  One direction is easy, as usual.  
+  Suppose that $\deno M\sim_{\must} \deno N$, and let $C[-]$ be a context.  
+  Suppose that $C[M]\mustconverge$, and fix $w\in X^\omega$.
+  Then $\deno{C[M]} = \deno{C};\deno{M}$, so there is some finite prefix $u\pprefix w$ such that the composite
+  \[
+    1 \xrightarrow{\deno{C};\deno{M}}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \]
+  is not equal to $\bot$.  
+  Since $M\sim_{\must} N$, there is some finite prefix $v\pprefix w$ such that the composite
+  \[
+    1 \xrightarrow{\deno{C};\deno{N}}
+    (X \to \bC) \xrightarrow{\eta_v}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|v|}}
+    \bC
+    \]
+  is not equal to $\bot$, and therefore $C[N]\mustconverge$.  
+  The other direction is completely symmetric.
+
+  The converse is harder.  
+  Let $\alpha \from \deno{T} \to \bC$ be an arbitrary morphism.
+  Suppose that for all $w\in \bB^\omega$ there is some finite $u\pprefix w$ such that the composite
+  \[
+    \deno{M};(X \to \alpha);\mu;\eta_u;\deno{\neww};t_{|u|}
+    \]
+  is not equal to $\bot$.  
+  Let $V$ be the set of all sequences $v\in \bB^*$ such that $v$ has no prefix $u$ with this property.  
+  Then by hypothesis $V$ is a finitely branching tree with no infinite path so, by K\"{o}nig's Lemma, it is finite.  
+  Therefore, there is some finite set of sequences $U\subset \bB^*$ such that for every sequence $w\in \bB^\omega$, $w$ has some prefix $u\in U$ satisfying the condition above.
+
+  Since $\G$ is enriched in algebraic cpos, for each $u\in U$ there is some compact $\alpha^u\subset\alpha$ such that
+  \[
+    \deno{M};(X \to \alpha^u);\mu;\eta_u;\deno{\neww};t_{|u|}
+    \]
+  is not equal to $\bot$.  
+  Since the set of compact elements below $\alpha$ is directed, there is some compact $\alpha'\subset\alpha$ such that $\alpha^u\subset\alpha'$ for each $u\in U$.
+
+  So we now know that: for any infinite sequence $w\in \bB^\omega$, there is some finite prefix $u\pprefix w$ such that the composite
+  \[
+    \deno{M};(X \to \alpha');\mu;\eta_u;\deno{\neww};t_{|u|}
+    \]
+  is not equal to $\bot$.  
+  Now if $\deno N\not\sim_{\must}\deno M$, then there is some infinite $w\in \bB^\omega$ is such that for every $v\pprefix w$ the composite
+  \[
+    \deno{N};(X \to \alpha);\mu;\eta_v;\deno{\neww};t_{|v|}
+    \]
+  is equal to $\bot$; since $\alpha'\subset \alpha$, the same is true if we replace $\alpha$ with $\alpha'$.
+
+  Now, since $\alpha'$ is compact, it is definable as a term in IA and hence as a term $L$ in IA${}_\bB$.  
+  By Corollary \ref{CorAdeqMust}, this means that $L M \mustconverge$, while $L N\diverges$, so $M\not\equiv_{\must}N$.
+\end{proof}
+
+Now clearly this last result depends on finiteness of $\bB$, since we may have infinite trees with no infinite path if the trees are allowed to be infinitely branching.
+The next result shows that if we replace $\bB$ with $\bN$, then we cannot hope to obtain such a full abstraction result.
+
+\begin{proposition}
+  Let $\C$ be a category that admits a computationally adequate denotational semantics of IA${}_\bN$.  
+  Suppose that the natural number datatype is denoted by an object $\bN$ of $\C$ and that for all functions $f \from \bN \to \bN$ in $\Set$ there is a morphism
+  \[
+    \sigma_f \from \bN \to \bN
+    \]
+  in $\C$ such that for all $n\in \bN$, 
+  \[
+    \deno{n};\sigma_f = \deno{f(n)}\,.
+    \]
+  Then $\C$ is not fully abstract for Idealized Algol with countable nondeterminism.
+  \label{PropNotFullyAbstract}
+\end{proposition}
+\begin{example}
+  In the category $\G$ of games (and hence in its Kleisli categories), we have strategies $\sigma_f$ with maximal plays of the form
+  \[
+    \begin{array}{cc}
+      \bN & \bN \\
+          &  q  \\
+       q  &     \\
+       n  &     \\
+          & f(n)
+    \end{array}\,,
+    \]
+  which have the property stated above.
+\end{example}
+\begin{proof}[Sketch proof of \ref{PropNotFullyAbstract}]
+  We fix an inductive encoding $\encode -$ of IA terms and assume the existence of an \emph{interpreter}
+  \[
+    \Int \from \bN \to \bN\,.
+    \]
+  $\Int n$ first checks whether its argument $n$ is the encoding of a valid IA term of type $\nat$; if it is not, then it returns the value $0$, which will take the place of an error value.
+  If it is, then $\Int n$ evaluates the program corresponding to $n$; if this evaluation terminates, then it adds $1$ to the value returned and returns that.  
+  The reason we add $1$ to the value is primarily to avoid the error value $0$, though it will serve a purpose later too.
+
+  Now consider the term
+  \setlength{\jot}{0pt}%
+  \begin{align*}
+    M=&\lambda f^{\nat \to \nat} .\neww(\lambda p.p\gets\ask_\bN;\\
+      &\hspace{82pt}\new(\lambda v.v\gets f(\oc p);\\
+        &\hspace{116pt}\new(\lambda x.x\gets \Int' \ask_\bN (\app \oc p \encode {\oc p});\\
+          &\hspace{148pt}\IfO \oc x \Then \skipp \Else\\
+            &\hspace{168pt}(\If \oc v = \oc x \Then \skipp \Else \Omega))))
+  \end{align*}
+  of type $(\nat\to \nat) \to \com$.
+  Here, $\app$ is the constructor used in the encoding to apply one term to another: so if $p$ is the encoding of an IA $P\from \nat \to \nat$, then $\app p \encode p$ will be the encoding of the term $P\,p$; i.e., $P$ applied to its own encoding.
+
+  Consider also the term
+  \[
+    N = \lambda f^{\nat \to \nat}.f(\ask_\bN);\IfO \ask_\bN \Then \skipp \Else \Omega\,.
+    \]
+  of type $(\nat \to \nat) \to \com$.  
+  Here, we have used the notation $P;Q$ to mean $\IfO P \Then Q \Else Q$ for $P\from \nat$; i.e., the program that evaluates $P$, forgets the result and then evaluates $Q$.
+
+  We claim that $M$ and $N$ are may-and-must-observationally equivalent.  
+  We will save the formal proof of this until we have a working fully abstract semantics; for now, we shall give an informal argument.
+
+  First, note that $M$ and $N$ have the same behaviour in any applicative context; i.e., if $F\from \nat \to \nat$ is a term, then $MF\converges \skipp$ if and only if $NF\converges\skipp$ and $MF\mustconverge$ if and only if $NF\mustconverge$.
+  Indeed, we certainly have $NF\converges\skipp$ and $NF\diverges$.
+  Moreover, $MF\converges\skipp$, so we need to show that $MF\diverges$.
+
+  Consider the evaluation path of $M$ in which the variable $p$ acquires the value $\encode F$ at the beginning.  
+  If $F (\encode F)$ diverges, then the whole term will diverge.  
+  Otherwise, there is some value $k$ such that $F (\encode F)$ converges to a value $n$ after $k$ steps.
+  Then $v$ acquires the value $n$.  
+  Consider the path where $\ask_\bN$ on the third line acquires the value $k$.  
+  Then $\Int' k (\app F !p \encode{!p})$ will carry out the computation of $F (\encode F)$, returning the value $n$, but will then add $1$ to that value before returning.  
+  The result is that $v$ holds the value $n$ and $x$ holds the value $n+1$.  
+  Therefore, the term diverges.
+
+  The case for a non-applicative context is the same, after we have made the observation that any side-effects that occur when $f$ is evaluated will take place in both terms in the case that they converge, while they will have no effect if the terms diverge.
+
+  After satisfying ourselves that $M$ and $N$ are observationally equivalent, we claim that they are distinguished by the semantics, which proves that the model is not fully abstract.
+
+  Indeed, let $\phi\from \bN \to \bN$ where $\phi(p)$ is $n+1$ if $p$ is the encoding of a term $P\from\nat \to \nat$ and $P\;p\converges n$ and $0$ otherwise (including the case that $P\;p\diverges$.
+
+  We know that $\deno{N};\sigma\not\downarrow_{\must}$ for all $\sigma$, because $N$ essentially discards its argument.
+  We claim that $\deno{M};\sigma_\phi\downarrow_{\must}$, proving that $N\not\sim_{\must} M$.
+
+  Indeed, by compositionality and adequacy of the semantics, we may consider $\sigma_\phi$ to behave as a term $\Phi\from\nat \to \nat$ with the operational behaviour that
+  \[
+    \inferrule*{\Gamma,s\ts N \converges n,s'}{\Gamma,s\ts \Phi N \converges \phi(n),s'}\,.
+    \]
+  Then, whatever the value of $p$, either $\Int' \ask_{\bN} (\app \oc p \encode{\oc p})$ will return $0$ or it will return the value of $\phi(\oc p)$.  
+  In either case, the term will not diverge.
+\end{proof}
+
+\begin{remark}
+  The term $M$ that we have constructed in this proof is an instance of the \emph{Kleene tree} (see, for example, \cite{KleeneTree}), a computable tree with an infinite path but no computable infinite path.
+\end{remark}
+
+The proof of Proposition \ref{PropNotFullyAbstract} makes it clear that the problem is the existence in the semantics of morphisms that behave like certain noncomputable functions.  
+The presence of such morphisms is normally an orthogonal issue to full abstraction, since we can usually assume that the strategy $\alpha$ in the definition of intrinsic equivalence is compact.
+However, in our case, the presence of these noncomputable morphisms is a big problem.
+
+At the extreme, if the category $\G$ satisfies the property (universality) that every morphism between the denotations of IA types is the denotation of an IA term, then we can get the full abstraction result we desire.
+
+\begin{theorem}
+  Let $M,N\from T$ be terms of \IAX and suppose that our base semantics of IA in $\G$ satisfies universality.  
+  Then $M\emam N$ if and only if $\deno M \smam \deno N$.
+\end{theorem}
+\begin{proof}
+  See the proof of Theorem \ref{FullAbstractionFiniteNondeterminism} for the proof that if $\deno M \smam \deno N$ then $M\emam N$.
+
+  Conversely, if $\deno M \not\smam \deno N$, then without loss of generality there is some $\alpha\from\deno T \to \bC$ such that $\alpha;\deno M \downarrow_{\must}$ and $\alpha;\deno N\not\downarrow_{\must}$.
+  But by universality $\alpha;\deno M = \deno{LM}$ and $\alpha;\deno N=\deno{LN}$ for some term $L\from T \to \com$ of IA.  
+  Therefore, the result follows from Corollary \ref{CorAdeqMust}.
+\end{proof}
+
+\begin{example}
+  It was proven in \cite{hoPcf} that every innocent strategy between the denotations of PCF types is innocently intrinsically equivalent to the denotation of some term of PCF.  
+  A sharper result (unpublished, but see \cite[\sec 7.1.5]{LongleyBook}), which allows us to forget the intrinsic equivalence part, is that every innocent strategy between the denotations of PCF terms is the denotation of some term of the language formed by augmenting PCF with a constant called $\lett$ or $\byval$ whose
 

### 2019-03-17 Thesis/thesis.tex
Finished another chapter.

@@
   By currying, we may consider $A$ and $B$ as morphisms $1 \to (A \to B)$ in $\G_X$.
-  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$ and for all sequences $u\in X^*$, if we regard the $\alpha;\sigma,\alpha;\tau\from 1 \to \bC$ as morphisms $X \to \bC$ in $\G$, then the composites
+  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$ and for all sequences $u\in X^*$, if we regard $\sigma;\alpha,\tau;\alpha\from 1 \to \bC$ as morphisms $X \to \bC$ in $\G$, then the composites
   \begin{mathpar}
-    1 \xrightarrow{\alpha;\sigma}
+    1 \xrightarrow{\sigma;\alpha}
     (X \to \bC) \xrightarrow{\eta_u}
@@
     \and
-    1 \xrightarrow{\alpha;\tau}
+    1 \xrightarrow{\tau;\alpha}
     (X \to \bC) \xrightarrow{\eta_u}
@@
   Then the denotation of $t\ts C[t]$ is a morphism $\alpha\from \deno{T} \to \bC$.
-  Moreover, the denotation of $C[M]$ is the composite $\alpha;\deno{M}$ and that of $C[N]$ is the composite $\alpha;\deno{N}$, by functional completeness.
+  Moreover, the denotation of $C[M]$ is the composite $\deno{M};\alpha$ and that of $C[N]$ is the composite $\deno{N};\alpha$ by functional completeness.
 
@@
   \begin{mathpar}
-    1 \xrightarrow{\alpha;\sigma}
+    1 \xrightarrow{\sigma;\alpha}
     (X \to \bC) \xrightarrow{\eta_u}
@@
   \begin{mathpar}
-    (\alpha;\deno M);\eta_u;\deno{\neww};t_{|u|} \ne \bot
-    \and
-    (\alpha;\deno N);\eta_u;\deno{\neww};t_{|u|} = \bot\,.
+    (\deno M;\alpha);\eta_u;\deno{\neww};t_{|u|} \ne \bot
+    \and
+    (\deno N;\alpha);\eta_u;\deno{\neww};t_{|u|} = \bot\,.
   \end{mathpar}
-  Here, we have enclosed $\alpha;\deno M$ and $\alpha;\deno N$ in brackets to indicate that the composition is taken in the Kleisli category $\G_X$, and then the whole thing is considered as a morphism $1 \to (X \to \bC)$ in $\G$.
+  Here, we have enclosed $\deno M;\alpha$ and $\deno N;\alpha$ in brackets to indicate that the composition is taken in the Kleisli category $\G_X$, and then the whole thing is considered as a morphism $1 \to (X \to \bC)$ in $\G$.
 
@@
     \and
-    1 \xrightarrow{\alpha;\tau}
+    1 \xrightarrow{\tau;\alpha}
     (X \to \bC) \xrightarrow{\eta_v}
@@
   \[
-    1 \xrightarrow{\alpha;\deno{M}}
+    1 \xrightarrow{\deno M;\alpha}
     (X \to \bC) \xrightarrow{\eta_u}
@@
   \[
-    1 \xrightarrow{\alpha;\deno{N}}
+    1 \xrightarrow{\deno N;\alpha}
     (X \to \bC) \xrightarrow{\eta_v}
@@
 \begin{proof}
-  Given strategies $\sigma,\tau\from A$ in $\G_X$, we have $\sigma \sim_{\may} \tau$ if and only if $\alpha;\sigma\approx_{\may}\alpha;\tau$ for any morphism $\alpha\from \oc A \implies \bC$ in $\G_X$.
+  Given strategies $\sigma,\tau\from A$ in $\G_X$, we have $\sigma \sim_{\may} \tau$ if and only if $\sigma;\alpha\approx_{\may}\tau;\alpha$ for any morphism $\alpha\from \oc A \implies \bC$ in $\G_X$.
   If $\sigma\approx_{\may}\tau$, we have
   \[
-    \alpha;\sigma\vert_{\bC} = \alpha;(\sigma\vert_{\bC}) = \alpha;(\tau\vert_{\bC}) = \alpha;\tau\vert_{\bC}\,.\qedhere
+    \sigma;\alpha\vert_{\bC} = (\sigma\vert_{\bC});\alpha = (\tau\vert_{\bC});\alpha = \tau;\alpha\vert_{\bC}\,.\qedhere
     \]
@@
 
-Note that it is also the case that if $\alpha\approx_{\may}\alpha'$ and $\sigma\approx_{\may}\tau$ then $\alpha;\sigma \approx_{\may} \alpha';\tau$.  
+Note that it is also the case that if $\alpha\approx_{\may}\alpha'$ and $\sigma\approx_{\may}\tau$ then $\sigma;\alpha \approx_{\may} \tau;\alpha'$.  
 Therefore, the Full Abstraction result we have just proved applies to the quotiented category.
@@
 \begin{definition}
-  Given morphisms $\sigma,\tau\from A \to B$ in $\G_X$, considered as morphisms $1 \to (A \to B)$, we write $\sigma\sim_{\must}\tau$ if whenever $\alpha\from (A \to B) \to \bC$ is a morphism in $\G_X$ and $w\in X^\omega$ is an infinite sequence, then $\alpha;\sigma\downarrow_{\must}$ if and only if $\alpha;\tau\downarrow_{\must}$.
+  Given morphisms $\sigma,\tau \from 1 \to \bC$ in $\G_X$, we write $\sigma\approx_{\must}\tau$ if $\sigma\downarrow_{\must}$ and $\tau\downarrow_{\must}$ or if $\sigma\not\downarrow_{\must}$ and $\tau\not\downarrow_{\must}$.
 \end{definition}
 
+We write $\sigma\amam \tau$ if $\sigma\approx_{\may}\tau$ and $\sigma\approx_{\must}\tau$.
+
+\begin{definition}
+  Given morphisms $\sigma,\tau\from A \to B$ in $\G_X$, considered as morphisms $1 \to (A \to B)$, we write $\sigma\sim_{\must}\tau$ if whenever $\alpha\from (A \to B) \to \bC$ is a morphism in $\G_X$, then $\sigma;\alpha\approx_{\must}\tau;\alpha$.
+\end{definition}
+
 We write $\sigma\smam \tau$ if $\sigma\sim_{\may}\tau$ and $\sigma\sim_{\must} \tau$.
@@
 \begin{remark}
-  In the category of games we can simplify this to saying that $\alpha;\sigma\approx_{\may}\alpha;\tau$ and that either $\alpha;\sigma$ and $\alpha;\tau$ are both winning, or neither is.
+  In the category of games we can simplify this to saying that $\sigma;\alpha\approx_{\may}\tau;\alpha$ and that either $\sigma;\alpha$ and $\tau;\alpha$ are both winning, or neither is.
 \end{remark}
@@
 
-  Conversely, if $\deno M \not\smam \deno N$, then without loss of generality there is some $\alpha\from\deno T \to \bC$ such that $\alpha;\deno M \downarrow_{\must}$ and $\alpha;\deno N\not\downarrow_{\must}$.
-  But by universality $\alpha;\deno M = \deno{LM}$ and $\alpha;\deno N=\deno{LN}$ for some term $L\from T \to \com$ of IA.  
+  Conversely, if $\deno M \not\smam \deno N$, then without loss of generality there is some $\alpha\from\deno T \to \bC$ such that $\deno M;\alpha \downarrow_{\must}$ and $\deno N;\alpha\not\downarrow_{\must}$.
+  But by universality $\deno M;\alpha = \deno{LM}$ and $\deno N;\alpha=\deno{LN}$ for some term $L\from T \to \com$ of IA.  
   Therefore, the result follows from Corollary \ref{CorAdeqMust}.
@@
 
-\begin{example}
-  It was proven in \cite{hoPcf} that every innocent strategy between the denotations of PCF types is innocently intrinsically equivalent to the denotation of some term of PCF.  
-  A sharper result (unpublished, but see \cite[\sec 7.1.5]{LongleyBook}), which allows us to forget the intrinsic equivalence part, is that every innocent strategy between the denotations of PCF terms is the denotation of some term of the language formed by augmenting PCF with a constant called $\lett$ or $\byval$ whose
-
+The next step is to find an example of such a $\G$, which we will do by cutting down the set of strategies in our category of games to those that are in some sense computable.  
+The first step is to fix an enumeration $e_A\from M_A \to \bN$ of the moves of each game $A$.  
+We do this for the ground type games and then extend to the connectives.  
+For example:
+\begin{mathpar}
+  e_{\bC}(q)=0
+  \and
+  e_{\bC}(a)=1
+  \and
+  e_{\bB}(q)=0
+  \and
+  e_{\bB}(\true)=1
+  \and
+  e_{\bB}(\false)=2
+  \\
+  e_{\bN}(q)=0
+  \and
+  e_{\bN}(n)=n+1
+  \and
+  e_{\Var}(q)=0
+  \and
+  e_{\Var}(n)=3n+1
+  \and
+  e_{\Var}(q_n)=3n+2
+  \and
+  e_{\Var}(a_n)=3n+3
+  \\
+  e_{A\tensor B}(\inj_A(a))=2e_A(a)
+  \and
+  e_{A\tensor B}(\inj_B(b))=2e_B(b)+1
+\end{mathpar}
+...and so on.
+
+We can extend the enumeration of moves to an enumeration of (justified) plays in $A$.  
+We then say that a strategy $\sigma$ is \emph{recursive} if it is a recursively enumerable subset of $P_A$.
+Recursive visible strategies give us a Cartesian closed subcategory of the original category of games and visible strategies.
+
+We now appeal to some results about these recursive strategies.  
+For example, the following was proved in \cite{hoPcf}.
+
+\begin{theorem}[Universality for PCF]
+  Let $A$ be the denotation of a PCF type $T$
+  Then every recursive innocent strategy for $A$ is innocently intrinsically equivalent to the denotation of some PCF term $M\from T$.
+\end{theorem}
+
+This result is not quite enough for us, since the innocent intrinsic equivalent is coarser than that for visible strategies.  
+Instead, we appeal to the following result, which gives us definability \emph{on the nose}.  
+For this result, we need to extend PCF with a new constant $\lett$ or $\byval$ where the semantics of $\lett x = M\inn N$ is to evaluate the term $M$ and bind the result to the free variable $x$ in $N$.
+
+\begin{theorem}[{Unpublished, but see \cite[\sec 7.1.5]{LongleyBook}}]
+  Let $A$ be the denotation of a PCF type $T$.
+  Then every recursive innocent strategy for $A$ is the denotation of a term $M\from T$ of PCF+$\lett$.
+\end{theorem}
+
+We can interpret $\lett$ in Idealized Algol by defining
+\[
+  \lett x = M \inn N
+  \]
+to be the term
+\[
+  \neww (\lambda x. x\gets M;N[\oc x/x])\,.
+  \]
+Moreover, these results are all easily extended to the IA ground types that are not present in PCF.  
+So we see that any recursive innocent $\sigma\from \deno T$ is the denotation of some Idealized Algol term $M \from T$.
+
+Lastly, we observe that our innocent factorization result (Proposition \ref{PropInnocentFactorization}) will always produce a recursive innocent strategy if the original strategy is recursive.  
+It follows, then, that any recursive \emph{visible} $\sigma\from \deno T$ is the denotation of some Idealized Algol term $M \from T$.
+Thus, the category $\G^{rec}$ of games and recursive visible strategies is universal for Idealized Algol, and thus its Kleisli category $\G^{rec}_X$ is fully abstract for \IAX.
+
+As an application of this fully abstract semantics, we clear up a loose end from the proof of Propostion \ref{PropNotFullyAbstract}.
+
+\begin{lemma}
+  The terms $M,N\from (\nat \to \nat) \to \com$, as defined in the proof of Propostion \ref{PropNotFullyAbstract}, are observationally equivalent in Idealized Algol with countable nondeterminism.
+\end{lemma}
+\begin{proof}
+  The denotations for $M$ and $N$ both have maximal plays that look like this:
+  \[
+    \begin{array}{cccc}
+      \bN & \bN & \bN & \bC \\
+          &     &     &  q  \\
+       q  &     &     &     \\
+       p  &     &     &     \\
+          &     &  q  &     \\
+          &  q  &     &     \\
+          &  p  &     &     \\
+          &     &  c  &     \\
+       q  &     &     &     \\
+       n  &     &     &     \\
+          &     &     & (a)
+    \end{array}\,.
+    \]
+  Here, the copy of $\bN$ on the left denotes the nondeterministic oracle given by the Kleisli category.  
+  The final move $a$ is in brackets to indicate that it does not always occur, depending on the moves that have gone before.
+
+  More specifically, in $\deno M$, the final move $a$ always occurs unless the number $p$ is the encoding of a term $P\from\nat \to \nat$ of Idealized Algol such that the evaluation $P\;p$ converges in fewer than $n$ steps to a number different from $c+1$.
+
+  Meanwhile, the final move $a$ is present in $\deno N$ if and only if the number $n$ is equal to $0$.
+  Since an evaluation $P\;p$ will never converge in fewer than $0$ steps, this means that $\deno N$ is a subset of $\deno M$.
+
+  Fix some strategy $\alpha\from ((\bN \to \bN)\to\bC) \to \bC$ in $\G_X$ and suppose that
+  \[
+    \deno M;\alpha\not\amam \deno N;\alpha\,.
+    \]
+  To show that $M$ and $N$ are observationally equivalent, it will be sufficient to prove that $\alpha$ is not recursive.
+
+  First note that we always have $\deno M;\alpha\approx_{\may}\deno N;\alpha$ for arbitrary $\alpha$, which we can deduce by ignoring the copy of $\bN$ on the left and considering $\deno M$ and $\deno N$ as nondeterministic strategies.
+  In this setting, $\deno M$ and $\deno N$ are equal, since both have maximal plays of the form
+  \[
+    \begin{array}{ccc}
+      \bN & \bN & \bC \\
+          &     &  q  \\
+          &  q  &     \\
+       q  &     &     \\
+       p  &     &     \\
+          &  c  &     \\
+          &     & a
+    \end{array}\,,
+    \]
+  where $p$ is arbitrary.
+
+  Therefore, we must have $\deno M;\alpha \not\approx_{\must}\deno N;\alpha$.
+
+  Since $\deno N \subseteq \deno M$, it must be the case that $\deno M;\alpha\downarrow_{\must}$ and $\deno N;\alpha\not\downarrow_{\must}$; i.e., that $\deno M;\alpha$ is a winning strategy, when considered as a strategy $\bN \to \bC$ in $\G$, but $\deno N;\alpha$ is not.
+
+  Since $\deno M$ and $\deno N$ do not differ until the very last move, this means that $\alpha$ must respond to the initial move $q$ in the rightmost copy of $\bC$ with the move $q$ in the copy of $\bC$ on the left (otherwise, $\deno N;\alpha$ is winning), and that $\alpha$ must be total (otherwise, $\deno M;\alpha$ is not winning).
+  Then we see that for any value of $p$, $\alpha$ must reply to the move $p$ with the number $\phi(p)$, where $\phi$ is the number defined above.  
+  Otherwise, $\deno M;\alpha$ is not winning.
+
+  But if $\alpha$ is a recursively enumerable subset of $P_{\bN \to ((\bN \to \bN) \to \bC) \to \bC}$, then that would mean that the set of pairs $(p,\phi(p))$ were a recursively enumerable subset of $\bN \times \bN$, and this is not the case, since $\phi$ is not a recursive function.
+  Therefore, $\alpha$ is not recursive.
+
+  It follows that $M$ and $N$ are observationally equivalent in Idealized Algol with countable nondeterminism under may-and-must testing.
+\end{proof}
+
+Note that we certainly have $\sigma_\phi;\deno M\downarrow_{\must}$, while $\sigma_\phi;\deno N\not\downarrow_{\must}$, demonstrating that the recursivity requirement is essential to the full abstraction result in this case.
+
+\subsection{The intrinsic equivalence relation in $\G_X$}
+
+We conclude this section by examining the intrinsic equivalence relation in $\G_X$.
+
+\begin{proposition}
+  Let $\sigma,\tau\from A \to B$ be two morphisms in $\G_X$,
+  If $\sigma\sim\tau$ when considered as morphisms $X \to (A \to B)$ in $\G$, then $\sigma\sim\tau$ in $\G_X$.
+\end{proposition}
+\begin{proof}
+  Suppose that $\alpha$ separates $\sigma$ and $\tau$ in $\G_X$, so without loss of generality, we have
+  \begin{mathpar}
+    1 \xrightarrow{(\sigma;\alpha)}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC = \bot
+    \and
+    1 \xrightarrow{(\tau;\alpha)}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC \ne \bot
+  \end{mathpar}
+  for some $u$.  
+  Expanding the Kleisli compositions $\sigma;\alpha$ and $\tau;\alpha$, we get
+  \begin{mathpar}
+    \sigma;(X \to \alpha);\mu;\eta_u;\deno{\neww};t_{|u|} = \bot
+    \\
+    \tau;(X \to \alpha);\mu;\eta_u;\deno{\neww};t_{|u|} \ne \bot\,,
+  \end{mathpar}
+  and so $(X\to\alpha);\mu;\eta_u;\deno{\neww};t_{|u|}$ distinguishes $\sigma$ and $\tau$, when considered as morphisms $X \to (A \to B)$ in $\G$.
+\end{proof}
+
+As a special case, if $\sigma,\tau\from A \to B$ are morphisms in $\G$, then $\sigma\sim\tau$ in $\G$ if and only if $J\sigma\sim J\tau$ in $\G_X$.  
+Combined with our Full Abstraction results, this tells us that \IAX is a conservative extension of Idealized Algol.
+
+What is more, we have
+\[
+  \sigma \sim \tau \Rightarrow J\sigma \sim J\tau \Rightarrow J\sigma \smam J\tau \Rightarrow \sigma\sim\tau\,.
+  \]
+This proves that the finite and countable nondeterministic variants of Idealized Algol are conservative extensions of Idealized Algol.
 \bibliographystyle{alpha}

### 2019-03-20 Thesis/games.tex
Nightly commit.

\documentclass{article}

\def\FEWFONTS{1}
\input{../common/preamble}

\begin{document}

\section{A Fully Abstract Game Semantics for Idealized Algol}

To introduce our material, we will go back over some old ground, namely the fully abstract game semantics for Idealized Algol developed by Abramsky and McCusker in \cite{SamsonGuyIAActive}.  
In keeping with the spirit of this thesis, we will aim to use category theoretic methods, and so our proofs of soundness and adequacy will depart from those given by Abramsky and McCusker, and will instead involve coalgebraic ideas developed by Laird in \cite{laird02} and \cite{LairdCofCommCom}.

\subsection{Idealized Algol}

The ground types of Idealized Algol are called $\com$, $\bool$, $\nat$ and $\Var$.  
The first three are data types corresponding to the sets $\bC = \{a\}$, $\bB = \{\true,\false\}$ and $\bN = \{0,1,2,\cdots\}$.
$\com$ takes the role of a command or void type; typically, although the return value of a function $T \to \com$ will not convey any information, the function will have useful side effects.

The type $\Var$ is the type of a variable that holds elements of $\bN$.
It is best understood as corresponding to the following pseudo-Java `interface'.

\begin{lstlisting}[language=Java, morekeywords={nat,com}]
public interface Var
{
  nat read();
  com write(nat value);
}
\end{lstlisting}

We now present the typing rules for the language.  
Here, $\Gamma$ will represent a \emph{context}; i.e., a list $x_1\from T_1,\cdots,x_n\from T_n$ of variable names together with their types.

First, we have the usual rules for the simply typed lambda calculus.

\begin{mathpar}
  \inferrule*{ }{\Gamma,x\from T \ts x \from T}
  \and
  \inferrule*{\Gamma\ts M \from S \to T \\ \Gamma \ts N \from S}{\Gamma\ts MN \from T}
  \and
  \inferrule*{\Gamma,x\from S \ts M \from T}{\Gamma \ts \lambda x^S.M \from S \to T}
\end{mathpar}

We then have rules for each of the base types.  
At type $\com$ we have:
\begin{mathpar}
  \inferrule*{ }{\Gamma\ts\skipp\from\com}
  \and
  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma\ts M\from\com \\ \Gamma\ts N \from T}{\Gamma\ts M;N\from T}\,.
\end{mathpar}
Here, $\skipp$ is a generic command with no side-effects that returns the unique element of the singleton set $\bC$.  
$M;N$ represents the sequential composition of $M$ with $N$; i.e., the term that first evaluates $M$, performing any of its side-effects, and then evaluates $N$ and returns the result.

At type $\bool$ we have true/false values and conditionals.
\begin{mathpar}
  \inferrule*{ }{\Gamma\ts\true\from\bool}
  \and
  \inferrule*{ }{\Gamma\ts\false\from\bool}
  \\
  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma\ts M \from \bool \\ \Gamma \ts N \from T \\ \Gamma \ts P \from T}{\Gamma\ts \If M \Then N \Else P \from T}
\end{mathpar}

At type $\nat$ we have numerals, arithmetic operators and a conditional that tests whether a number is equal to $0$ or not.
\begin{mathpar}
  \inferrule*{ }{\Gamma\ts n\from\nat}
  \and
  \inferrule*{\Gamma\ts M \from \nat}{\Gamma\ts \suc M \from \nat}
  \and
  \inferrule*{\Gamma\ts M \from \nat}{\Gamma\ts \pred M\from \nat}
  \\
  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma\ts M \from \nat \\ \Gamma\ts N \from T \\ \Gamma \ts P \from T}{\Gamma \ts \IfO M \Then N \Else P \from T}
\end{mathpar}

At type $\Var$, we have terms that call the read and write `methods' to dereference the variable or to assign a new value to it.
\begin{mathpar}
  \inferrule*{\Gamma\ts V \from \Var}{\Gamma \ts \oc V \from \nat}
  \and
  \inferrule*{\Gamma\ts V \from \Var \\ \Gamma \ts E \from \nat}{\Gamma \ts V\gets E \from \com}
\end{mathpar}

We also have the ability to create a new variable.
\begin{mathpar}
  \inferrule*{\Gamma,x\from \Var \ts M \from T}{\Gamma\ts \neww_T \lambda x.M\from T}
\end{mathpar}
The idea here is that $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).

We have another way of creating variables, using the $\mkvar$ keyword.  
If we think back to our illustration of the $\Var$ type as an interface, this becomes clearer.  
$\mkvar$ creates a new anonymous instance of the $\Var$ interface, using the `methods' supplied through its arguments.
\begin{mathpar}
  \inferrule*{\Gamma \ts M \from \nat \\ \Gamma \ts N \from \nat \to \com}{\Gamma\ts \mkvar M N \from \Var}
\end{mathpar}

Lastly, we have fixpoint combinators at all types that we use to implement recursion.
\begin{mathpar}
  \inferrule*{\Gamma \ts M \from T \to T}{\Gamma \ts \Y_T M \from T}
\end{mathpar}

\subsection{Games and Strategies}

We adopt the game semantics from \cite{SamsonGuyIAActive}; these are based on the game semantics developed in \cite{hoPcf}, with a modification to make them into a linear category.

\begin{definition}
  An \emph{arena} is a tuple $A=(M_A,\lambda_A,\ts_A)$, where
  \begin{itemize}
    \item $M_A$ is a set of \emph{moves},
    \item $\lambda_A \from M_A \to \OP \times \QA$ is a function that identifies each move as either an \emph{$O$-move} or a \emph{$P$-move}, and as either a \emph{question} or an \emph{answer}, and
    \item $\ts_A$ is a relation between $M_A+\{*\}$ and $M_A$ such that
      \begin{itemize}
        \item if $*\ts_A a$, then $\lambda_A(a)=(O,Q)$, and if $b\ts_A a$ then $b=*$,
        \item if $a\ts_A b$ and $a$ is an answer, then $b$ is a question, and
        \item if $a \ts_A b$ and $a\ne *$, then either $a$ is an $O$-move and $b$ a $P$-move, or the other way round.
      \end{itemize}
  \end{itemize}
  If $*\ts_A a$, then we say that $a$ is an \emph{initial move} in $A$.  
  If $a \ts_A b$, the we say that $a$ \emph{enables} $b$.
\end{definition}

As a shorthand, we write $\lambda_A^{OP}\from M_A \to \OP$ for $\pr_1\circ\lambda_A$ and $\lambda_A^{QA}\from M_A \to \QA$ for $\pr_2\circ\lambda_A$.

\begin{definition}
  A \emph{justified sequence} in an arena $A$ is a finite sequence $s$ of moves together with, for each non-initial move $a$ occurring in $s$, a pointer back to some move $b$ occurring earlier in $s$ such that $b\ts_A a$.
  We say that \emph{$b$ justifies $a$} or that $b$ is the \emph{justifier} of $a$.

  Given such a justified sequence, we define the \emph{$P$-view} $\pv s$ and \emph{$O$-view} $\ov s$ of $s$ inductively as follows.
  \begin{IEEEeqnarray*}{RCL"s}
    \pv{\epsilon} & = & \epsilon & \\
    \pv{sa} & = & \pv{s}a & if $a$ is a $P$-move \\
    \pv{sa} & = & a & if $a$ is initial \\
    \pv{sbta} & = & \pv{s}ba & if $a$ is an $O$-move justified by $b$ \\
    & & & \\
    \ov{\epsilon} & = & \epsilon & \\
    \ov{sa} & = & \ov{s}a & if $a$ is an $O$-move \\
    \ov{sbta} & = & \ov{s}ba & if $a$ is a $P$-move justified by $b$
  \end{IEEEeqnarray*}

  A justified sequence $s$ is \emph{well-bracketed} if whenever a question $q$ justifies some answer $a$, then any question $q'$ occurring after $q$ and before $a$ must justify some answer $a'$ occurring between $q'$ and $a$, and moreover $a$ is the only answer justified by $q$.
  We say that a justified sequence $s$ is \emph{alternating} if it alternates between $O$-moves and $P$-moves, and that it is \emph{well-formed} if it is both well-bracketed and alternating.

  We say that a well-formed justified sequence is \emph{visible} if whenever $ta\prefix s$, and $a$ is a $P$-move, then the justifier of $a$ occurs in the $P$-view of $t$, and if whenever $tb\prefix s$, and $b$ is a non-initial $O$-move, then the justifier of $b$ occurs in the $O$-view of $t$.

  We say that a justified sequence $s$ is \emph{legal} if it is well-formed and visible, and write $L_A$ for the set of legal sequences occurring in $A$.
\end{definition}

Note that since every non-initial move in a justified sequence $s$ must be justified by some previous move, then the first move in the sequence must be initial and therefore an $O$-question.  
If $s$ is alternating, this means that $s$ ends with an $O$-move if it has odd length and with a $P$-move if it has even length.

\begin{definition}
  Given a legal sequence $s\in L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.

  We write $s\vert_b$ for the subsequence of $s$ given by all moves in $s$ that are hereditarily justified by $b$.
  Given a set $I$ of initial moves, we write $s\vert_I$ for the subsequence of $s$ given by all moves that are hereditarily justified by some $b\in I$.

  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
\end{definition}

We shall call an odd-length sequence $s\in P_A$ an \emph{$O$-position} and an even-length sequence a \emph{$P$-position}

\begin{example}[Empty game]
  The \emph{empty game} $I$ is given by the tuple
  \[
    (\emptyset,\emptyset,\emptyset,\{\epsilon\})\,,
    \]
  where $\epsilon$ is the empty sequence.
\end{example}

\begin{example}[Data-type games]
  Let $X$ be some set.  
  Then we have a game, which we shall also call $X$, given by:
  \begin{itemize}
    \item $M_X = \{q\} + X$, 
    \item $\lambda_X(q)=(O,Q)$ and $\lambda_X(x)=(P,A)$ for all $x\in X$, 
    \item $q\ts_X x$ for each $x\in X$, and
    \item $P_X = \{\epsilon,q\}\cup\{qx\suchthat x\in X\}$, where the $x$ in $qx$ is justified by $q$.
  \end{itemize}

  In particular, we have games $\bC$, $\bB$ and $\bN$, which we shall use to model the datatypes $\com$, $\bool$ and $\nat$ of Idealized Algol.
\end{example}

\begin{definition}
  Let $A$ be a game.  
  Then a \emph{strategy} for $A$ is a non-empty even-prefix-closed set $\sigma\subset P_A$ of $P$-positions in $A$ such that if $sab,sac\in \sigma$ then $b=c$ and the justifier of $b$ is the justifier of $c$.  
\end{definition}
Here, we have identified a strategy for a game with the set of $P$-positions that can occur when player $P$ plays according to that strategy.  
So the condition we have given is one of \emph{determinism}: in any $O$-position $sa$ that can occur in the strategy, player $P$ must have at most one reply.

Note that there may be $O$-positions for which player $P$ has no reply at all; we use these to model non-terminating computations.

We write $\sigma\from A$ to denote that $\sigma$ is a strategy for the game $A$.

\begin{definition}
  A strategy $\sigma$ for a game $A$ is called \emph{innocent} if player $P$'s moves only depend on the current $P$-view; i.e., if whenever $sab\in\sigma$, $t\in\sigma$ and $ta\in P_A$ such that $\pv{sa}=\pv{ta}$, then we have $tab\in\sigma$.
\end{definition}

\subsection{Connectives on Games}

In the \emph{product} $A\times B$ of games $A$ and $B$, player $O$ chooses either $A$ or $B$ on the first move and subsequent play is that game.

\begin{definition}
  Given games $A$,$B$, define a game $A\times B$ by
  \begin{itemize}
    \item $M_{A\times B} = M_A + M_B$,
    \item $\lambda_{A\times B} = [\lambda_A,\lambda_B]$,
    \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
    \item $P_{A\times B} = \{s\in L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

Here, we have written $s\vert_A$ for the subsequence of $s$ consisting of all moves from $M_A$ and $s\vert_B$ for the subsequence consisting of all moves from $M_B$.

In the \emph{tensor product} $A\tensor B$ of games $A$ and $B$, the games $A$ and $B$ are played in parallel, and player $O$ may switch between games when it is his turn.

\begin{definition}
  Given games $A$,$B$, define a game $A\tensor B$ by
  \begin{itemize}
    \item $M_{A\tensor B} = M_A + M_B$,
    \item $\lambda_{A\tensor B} = [\lambda_A,\lambda_B]$,
    \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
    \item $P_{A\tensor B} = \{s\in L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

In the \emph{linear implication} $A\implies B$, the game $B$ is played in parallel with a version of $A$ in which the two players' roles have been switched around, and player $P$ may switch between the two games when it is her turn.

\begin{definition}
  Given games $A$,$B$, define a game $A\implies B$ by
  \begin{itemize}
    \item $M_{A\implies B} = M_A + M_B$,
    \item $\lambda_{A\implies B} = [\neg\circ\lambda_A,\lambda_B]$,
    \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$, and
    \item $P_{A\implies B} = \{s\in L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
  \end{itemize}
\end{definition}

Here, $\neg\from \OP\times\QA \to \OP\times \QA$ is the function that reverses $O$ and $P$, while leaving $\QA$ unchanged.

In the \emph{exponential} of a game $A$, infinitely many copies of $A$ are played in parallel, and player $O$ may switch between copies whenever it is his move.

\begin{definition}
  Given a game $A$, define a game $\oc A$ by
  \begin{itemize}
    \item $M_{\oc A}=M_A$,
    \item $\lambda_{\oc A} = \lambda_A$,
    \item $\ts_{\oc A} = \ts_A$ and
    \item $P_{\oc A} = \{s\in L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
  \end{itemize}
\end{definition}

Lastly, the \emph{sequoid} $A\sequoid B$ of two games $A$ and $B$ behaves like the tensor product $A\tensor B$, except that the opening move must take place in $A$.

\begin{definition}
  Given games $A,B$, define a game $A\sequoid B$ by
  \begin{itemize}
    \item $M_{A\sequoid B} = M_{A\tensor B}$, 
    \item $\lambda_{A\sequoid B} = \lambda_{A\tensor B}$, 
    \item $\ts_{A\sequoid B} = \ts_{A \tensor B}$ and
    \item $P_{A\sequoid B} = \{s\in P_{A\tensor B}\suchthat\text{$s=\epsilon$ or $s$ begins with a move from $A$}\}$.
  \end{itemize}
\end{definition}

\subsection{Composition of strategies}

\begin{definition}
  Let $A,B,C$ be arenas.  
  An \emph{interaction sequence} between $A,B,C$ is a justified sequence $\s$ of moves drawn from $M_A$, $M_B$ and $M_C$ such that $\s\vert_{A,B}\in L_{A\implies B}$ and $\s\vert_{B,C}\in L_{B\implies C}$.  
  Here, $\s\vert_{A,B}$ is the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$, together with all justification pointers between moves in $A$ and $B$, and $\s\vert_{B,C}$ is defined similarly.

  We write $\Int(A,B,C)$ for the set of all interaction sequences between $A,B,C$.

  Given $\s\in\Int(A,B,C)$, we write $\s\vert_{A,C}$ for the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$.  
  A move $b$ in $\s\vert_{A,C}$ justifies a move $a$ either if $b$ justifies $a$ in either the $A$ or the $C$ components, or if $b$ justifies in $\s$ some initial move $c$ in $B$, which itself justifies $a$.
\end{definition}

\begin{definition}
  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  
  We define $\sigma\|\tau$ to be given by the set
  \[
    \{\s\in\Int(A,B,C)\suchthat \text{$\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$}\}\,.
    \]
  Then we define the \emph{composition} $\sigma;\tau$ of $\sigma$ and $\tau$ to be given by the set
  \[
    \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}\,.
    \]
\end{definition}

We need some small lemmata and definitions to help us show that this is a strategy.

\begin{lemma}
  We extend the function $\lambda_A^{OP}$ to sequences of moves by
  \begin{itemize}
    \item $\lambda_A^{OP}(\epsilon)=P$ and
    \item $\lambda_A^{OP}(sa)=\lambda_A(a)$.
  \end{itemize}

  If $s\in P_{A\implies B}$, then $\lambda_{A\implies B}^{OP}(s)=(\lambda_A^{OP}(s\vert_A)\Rightarrow \lambda_B^{OP}(s\vert_B))$, where $\Rightarrow$ is the binary operation on $\OP$ defined by
  \[
    \begin{array}{cc|c}
      P & Q & P\Rightarrow Q \\
      \hline
      P & P & P \\
      O & P & P \\
      P & O & O \\
      O & O & P
    \end{array}\,.
    \]
  Moreover, if $\lambda_A^{OP}(s\vert_A)=O$ then $\lambda_A^{OP}(s\vert_B)=O$.
  \label{LemCompositionLemma}
\end{lemma}
\begin{proof}
  Induction on the length of $s$.
  If $s=\epsilon$, then $s\vert_A=s\vert_B=\epsilon$, and so $(\lambda_A^{OP}(s\vert_A)\Rightarrow \lambda_B^{OP}(s\vert_B)) = (P\Rightarrow P) = P = \lambda_{A\implies B}^{OP}(s)$.

  Suppose then that $s=ta$, and that $\lambda_{A\implies B}^{OP}(t)=O$.  
  This means that $\lambda_A^{OP}(t\vert_A)=P$ and $\lambda_B^{OP}(t\vert_B)=O$.
  Then, whether $a$ is a move in $A$ or a move in $B$, adding it will flip exactly one of these components -- so $\lambda_{A\implies B}(s\vert_A)=O$ and $\lambda_{A\implies B}^{OP}(s\vert_B)=O$ if $a$ is a move in $A$ and $\lambda_{A\implies B}(s\vert_A)=P$ and $\lambda_{A\implies B}^{OP}(s\vert_B)=P$ if $a$ is a move in $C$.

  Suppose instead that $\lambda_{A\implies B}^{OP}(t)=P$.  
  By induction, this means that either $\lambda_A^{OP}(t\vert_A)=P$ and $\lambda_B^{OP}(t\vert_B)=P$ or that $\lambda_A^{OP}(t\vert_A)=O$ and $\lambda_B^{OP}(t\vert_B)=O$.
  In the first case, this means that either $t\vert_A$ is empty or its last move is a $P$-move in $A$ (and therefore an $O$-move in $A\implies B$), and so the move $a$ must take place in $C$, meaning that $\lambda_A^{OP}(s\vert_A)=P$ and $\lambda_B^{OP}(s\vert_B)=O$.

  Similarly, in the second case, the last move in $t\vert_C$ must be an $O$-move in $B$ (and therefore an $O$-move in $A\implies B$, and so the move $a$ must take place in $A$, meaning that $\lambda_A^{OP}(s\vert_A)=P$ and $\lambda_B^{OP}(s\vert_B)=O$.  
\end{proof}

It follows that

\begin{corollary}[Switching condition]
  Only player $P$ may switch between games in $A\implies B$; i.e., if $tab\in P_{A\implies B}$, and $a$ occurs in $A$ and $b$ in $B$, or if $a$ occurs in $B$ and $b$ in $A$, then $b$ is a $P$-move.
  \label{CorSwitchingCondition}
\end{corollary}
\begin{proof}
  Otherwise, $\lambda_{A\implies B}(t)=O$, so $\lambda_A(t\vert_A)=P$ and $\lambda_B(t\vert_B)=O$.  
  But we must also have $\lambda_{A\implies B}(tab)=O$, so $\lambda_A(tab\vert_A)=P$ and $\lambda_B(tab\vert_B)=O$.  
  But this is a contradiction, since $tab\vert_A$ and $tab\vert_B$ are both one move longer than the plays $t\vert_A$ and $t\vert_B$.
\end{proof}

\begin{definition}[{\cite[\sec 3.1]{Harmer2006InnocentGS}}]
  Given $\s\in \Int(A,B,C)$, we define the \emph{$P$-view} $\pv{\s}$ of $\s$ inductively as follows.
  \begin{IEEEeqnarray*}{RCL?s}
    \pv{\epsilon} & = & \epsilon & \\
    \pv{\s a} & = & \pv{\s}a & if $a$ is a move in $B$, an $O$-move in $A$ or a $P$-move in $C$ \\
    \pv{\s c} & = & c & if $c$ is an initial move of $C$ \\
    \pv{\s b\t a} & = & \pv{\s}ba & if $a$ is a $P$-move of $A$ or an $O$-move of $C$ and is justified by $b$ \\
  \end{IEEEeqnarray*}
\end{definition}

\begin{lemma}
  If $\s\in \Int(A,B,C)$, then $\pv{\s}\vert_{A,C}=\pv{\s\vert_{A,C}}$.
  \label{LemHarmerRestriction}
\end{lemma}
\begin{proof}
  Induction on the length of $\s$.  
  This is clear if $\s=\epsilon$.

  If $a$ is an $O$-move in $A$ or a $P$-move in $C$, then $a$ is a $P$-move in $A\implies C$.  
  We have $\pv{\s a}\vert_{A,C}=\pv{\s}\vert_{A,C}a$, which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}a$, which is the same as $\pv{\s a\vert_{A,C}}$.
  If $b$ is a move in $B$, then $\pv{\s b}\vert_{A,C}=\pv{\s}b\vert_{A,C}=\pv{\s}\vert_{A,C}=\pv{\s\vert_{A,C}}=\pv{\s b\vert_{A,C}}$, by the inductive hypothesis.

  If $c$ is initial in $C$, then $\pv{\s c}\vert_{A,C}=c=\pv{\s c\vert_{A,C}}$.

  Suppose $a$ is a $P$-move of $A$ or an $O$-move of $C$ -- so $a$ is an $O$-move in $A\implies C$ -- and suppose that $a$ is justified by $b$ in the sequence $\s b\t a$.  
  Since $a$ cannot be an initial move in $A$, $b$ must occur in the same game as $a$, and in particular must not occur in $B$.
  Then we have $\pv{\s b\t a}\vert_{A,C}=\pv{\s} ba\vert_{A,C}=\pv{\s}\vert_{A,C}ba$, which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}ba=\pv{\s ba\vert_{A,C}}$.
\end{proof}

\begin{lemma}[{\cite[\sec 3.1]{Harmer2006InnocentGS}}]
  Let $\s a\in \Int(A,B,C)$ (so, in particular, $\s\vert_{A,B}$ and $\s\vert_{B,C}$ satisfy the visibility condition).  
  If $a$ is a move in $B$, an $O$-move in $A$ or a $P$-move in $C$, then $\pv{\s a}\in \Int(A,B,C)$.
  \label{LemHarmersLemma}
\end{lemma}
\begin{proof}
  Induction on the length of $\s$.  
  If $\s=\epsilon$, then this is clear.  
  Otherwise, suppose that $\s$ is non-empty.

  First, we claim that $\pv{\s}\in\Int(A,B,C)$.  
  If $\s$ ends with a move in $B$, an $O$-move in $A$ or a $P$-move in $C$, then this follows immediately from the inductive hypothesis.  
  Otherwise, suppose that $\s$ ends with a $P$-move in $A$ or an $O$-move in $C$.  
  If this last move is initial, then $\pv{\s}$ is a single move, so the claim is trivial.  
  Otherwise, write $\s=\t p\u r$, where $p$ justifies $r$.  
  By the inductive hypothesis, we have $\pv{\t p}\in \Int(A,B,C)$, and then $\pv{s}=\pv{\t p\u r}=\pv{\t}pr=\pv{\t p}r\in \Int(A,B,C)$.

  Now, since $a$ is a $P$-move in $A\implies B$ or in $B\implies C$, its predecessor $b$ is an $O$-move and has some justifier $c$ contained in $\pv{\s\vert_X}$, where $X\in\{A\implies B,B\implies C\}$ is that component in which $a$ is a $P$-move.  
  Then this $c$ is preceded by some other $O$-move $b'$, which is necessarily also contained in $\pv{\s}$, and so has some justifier $c'$, contained in $\pv{\s\vert_X}$ by visibility.  
  Continuing in this way until we reach an initial move, we build up the whole of the sequence $\pv{\s\vert_X}$ as a subsequence of $\pv{\s}$.  
  Therefore, the justifier of $a$ must be contained in $\pv{\s}$, and so $\pv{\s a}=\pv{\s}a\in\Int(A,B,C)$.
\end{proof}

\begin{lemma}[$O$-views in the linear implication, {\cite[4.2,4.3]{hoPcf}}]
  Let $A,B$ be games, and let $bs$ be a non-empty play in $A\implies B$ beginning with an initial move $b$ in $B$.

  i) If $bs$ ends with a $P$-move in $B$, then $\ov{bs}_{A\implies B}=\ov{bs\vert_B}_B$.

  ii) If $bs$ ends with a $P$-move in $A$, then $\ov{bs}_{A\implies B} = b\pv{s\vert_A}^A$.
  \label{LemProjectionLemma}
\end{lemma}
\begin{proof}
  Induction on the length of $s$.
  If $s=\epsilon$, then $bs$ ends with an $O$-move in $B$, and we have $\pv{b}^{A\implies B} = b = \pv{b}^{B}$.

  Otherwise, suppose that $bs$ ends with a $P$-move $c$ in $B$.  
  Let $d$ be the justifier of $c$.  
  Then $d$ must be an $O$-move in $B$.
  Write $bs=tduc$, where $t,u$ are sequences.  
  Then $\ov{tduc}_{A\implies B}=\ov{t}_{A\implies B}dc$ and $\ov{tduc\vert_B}_B=\ov{t\vert_B}_Bdc$.
  By Corollary \ref{CorSwitchingCondition}, $t$ must end with a $P$-move in $B$, or be empty, so by the inductive hypothesis we have $\ov{t}_{A\implies B}=\ov{t\vert_B}_B$.
  Therefore, $\ov{bs}_{A\implies B}=\ov{tduc}_{A\implies B}=\ov{t}_Bdc = \ov{tduc\vert_B}_B=\ov{bs\vert_B}_B$.

  Next, suppose that $bs$ ends with a $P$-move $a$ in $A$.
  Let $c$ be the justifier of $a$.  
  Then $c$ must be an $O$-move in $A$.  
  Write $s=tcua$, where $t,u$ are sequences.  
  Then $\ov{btcua}_{A\implies B}=\ov{bt}_{A\implies B}ca$ and $\pv{tcua\vert_A}^A = \pv{t\vert_A}^Aca$, since the roles are reversed in $A$.
  By Corollary \ref{CorSwitchingCondition}, $t$ must end in a $P$-move in $A$, or be empty, so by the inductive hypothesis we have $\ov{bt}_{A\implies B} = b\pv{t\vert_A}^A$.  
  Therefore, $\ov{bs}_{A\implies B}=\ov{btcua}_{A\implies B}=\ov{bt}_{A\implies B}ca=b\pv{t\vert_A}^Aca=b\pv{tcua\vert_A}^A=b\pv{s\vert_A}^A$.  
\end{proof}

\begin{proposition}
  $\sigma;\tau$ is a strategy for $A\implies C$.  
\end{proposition}
\begin{proof}
  First, we claim that $\s\vert_{A,C}\in P_{A\implies B}$ for any $\s\in \sigma\|\tau$.
  Since we certainly have $\s\vert_{A,C}\vert_A = \s\vert_{A,B}\vert_A\in P_A$ and $\s\vert_{A,C}\vert_C = \s\vert_C = \s\vert_{B,C}\vert_C\in P_C$, it suffices to show that $\s\vert_{A,C}\in L_{A\implies C}$.

  Suppose that $ta\prefix \s\vert_{A,C}$.  We claim that $\lambda_{A\implies C}(t) = \neg\lambda_{A\implies C}(a)$.
  By Lemma \ref{LemCompositionLemma}, we are in one of the following configurations.
  \small
  \[
    \begin{array}{ccc|ccc}
      \lambda_A^{OP}(t\vert_A) & \lambda_B^{OP}(t\vert_B) & \lambda_C^{OP}(t\vert_C) & \lambda_{A\implies B}^{OP}(t\vert_{A,B}) & \lambda_{B\implies C}^{OP}(t\vert_{B,C}) & \lambda_{A\implies C}^{OP}(t\vert_{A,C}) \\
      \hline
      P & P & P & P & P & P \\
      P & P & O & P & O & O \\
      P & O & O & O & P & O \\
      O & O & O & P & P & P 
    \end{array}
    \]
  \normalsize
  In the configuration $PPP$, the move $a$ cannot be a move in $A$, since that would leave $ta\vert_{A\implies B}$ in the configuration $OP$, which is impossible by Lemma \ref{LemCompositionLemma}.  
  Therefore, it must be a move in $C$, and must therefore be an $O$-move in $C$ and hence an $O$-move in $A\implies C$.

  In the configuration $PPO$, once again the move $a$ cannot take place in $A$, since this would leave $ta\vert_{A\implies B}$ in an illegal configuration.  
  Therefore, it must occur in $C$, and must be a $P$-move in $C$ and hence a $P$-move in $A\implies C$.

  In the configuration $POO$, the move $a$ cannot take place in $C$, or it would leave $ta\vert_{B,C}$ in the illegal configuration $OP$, so the move $a$ takes place in $A$.  
  Therefore, it must be an $O$-move in $A$ and hence a $P$-move in $A\implies C$.

  Lastly, in the configuration $OOO$, the move $a$ cannot occur in $C$, or it would leave $ta\vert_{B,C}$ in the configuration $OP$, and so it must take place in $A$.  
  Therefore, it must be a $P$-move in $A$, and hence an $O$-move in $A\implies C$.

  Having established that $\s\vert_{A,C}$ is alternating, we show that it is well-bracketed.
  Suppose that a question move $q$ in $\s\vert_{A,C}$ justifies some answer move $a$.
  $q$ and $a$ must occur in the same component, since the only case in which a move from one of $A$ and $C$ can justify a move in the other is when both moves are initial, and hence questions.
  Suppose first that $q$ and $a$ both occur in the game $C$.  
  Suppose that some other question move $q'$ occurs between $q$ and $a$ in $\s\vert_{A,C}$.  
  If $q'$ occurs in $C$, then it must be answered by some $a'$ occurring between $q'$ and $a$, since $\s\vert_C$ is a well-bracketed sequence.  
  Otherwise, suppose that $q'$ occurs in $A$.

  By examining the table above, we see that there must be some move in $B$ occurring between $q$ and $q'$ in $\s$, since moves in $A$ move between configurations $OOO$ and $POO$, while moves in $C$ move us between configurations $PPP$ and $PPO$.
  Let $b$ be the earliest such move.  
  Then $b$ must be a question; indeed, if it is an answer, then it is non-initial and so can only be justified by questions in $B$.  
  But such a question must occur earlier in $\s\vert_{B,C}$ than $q$, which would mean that $q$ was an unanswered question when the move $b$ was played, contradicting well-bracketedness of $\s\vert_{B,C}$.  
  Since $b$ is a question, it must be answered by some $a''$ occurring between $b$ and $a$.  
  Therefore, since $\s\vert_{A,B}$ is well-bracketed, the move $q'$ must be answered by some $a'$ occurring between $a'$ and $a''$ in $\s\vert_{A,B}$, and therefore between $a'$ and $a$ in $\s\vert_{A,C}$.

  The case when $q$ and $a$ both occur in $A$ is similar.

  Lastly, we need to show that $\s\vert_{A,C}$ satisfies the visibility condition.
  Let $ta\prefix\s\vert_{A,C}$.
  Choose some $\t\prefix\s$ such that $\t\vert_{A,C}=t$.

  Suppose $a$ is a $P$-move.
  Then by Lemma \ref{LemHarmersLemma}, $\pv{\t a}\in\Int(A,B,C)$.  
  By Lemma \ref{LemHarmerRestriction}, $\pv{t}a=\pv{ta}=\pv{\t a}\vert_{A,C}$, and therefore that the justifier of $a$ must be inside $\pv{t}$.

  Secondly, suppose that $a$ is an $O$-move.
  If $a$ is an $O$-move in $C$, then either it is initial or $t$ ends with some $P$-move in $B$, and therefore $\ov{t}_{A\implies C}=\ov{t\vert_B}_B = \ov{\t\vert_{B,C}}_B$.  
  Therefore, since $t\vert_{B,C}$ satisfies visibility, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.  
  If $a$ is an $O$-move in $A$, then write $t=cu$ and $\t=c\u$, where $c$ is the starting move in $C$.
  We have $\ov{cua}_{A\implies C}=c\pv{u\vert_A a}^A = \ov{c\u\vert_{A,B}}_{A\implies B}$.  
  Therefore, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.

  Therefore, $\s\vert_{A,C}\in L_{A\implies C}$, so $\s\vert_{A,C}\in P_{A\implies C}$.

  It is fairly clear that $\sigma;\tau$ is even-prefix closed, since $\sigma$ and $\tau$ are.  
  Indeed, if $\s\vert_{A,C}\in\sigma;\tau$ and $t\prefix\s\vert_{A,C}$, then we may choose some prefix $\t$ of $\s$ such that $t=\t\vert_{A,C}$.  
  Then $\t\vert_{A,B}\prefix\s\vert_{A,B}\in\sigma$ and $\t\vert_{B,C}\prefix\s\vert_{B,C}\in\tau$, so $\t\in\sigma\|\tau$.

  We claim that every sequence in $\sigma;\tau$ has even length.  
  Indeed, if $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, then both $\s\vert_{A,B}$ and $\s\vert_{B,C}$ must have even length, so must be in configuration $OO$ or $PP$.  
  This means that $\s$ as a whole must be in configuration $OOO$ or $PPP$, and so $\s\vert_{A,C}$ must be in configuration $OO$ or $PP$, so must have even length.

  Lastly, we need to show that $\sigma;\tau$ is deterministic.  
  Suppose that $sab,sac\in\sigma;\tau$, and suppose that $b\ne c$.  
  Suppose that $\s\vert_{A,C}=sab$ and $\t\vert_{A,C}=sac$, for $\s,\t\in\sigma\|\tau$, and let $\u$ be the longest common prefix of $\s,\t$.
  $\s$ and $\t$ are certainly incomparable under the prefix ordering, since $\s\vert_{A,C}$ and $\t\vert_{A,C}$ are, so we have $\u p\prefix \s$ and $\u q\prefix \t$, where $p\ne q$.
  Now $p$ and $q$ cannot be $O$-moves in $A$, $P$-moves in $C$ or moves in $B$, or they would have to be equal by determinism of $\sigma$ and $\tau$.  
  Therefore, they are $P$-moves in $A$ or $O$-moves in $C$, but this contradicts $\s\vert_{A,C}=sab$ and $\t\vert_{A,C}=sac$.

  Therefore, the composition $\sigma;\tau$ is a strategy.  
\end{proof}

We also want to show that the composition of innocent strategies is innocent.
We follow the proof given in \cite{Harmer2006InnocentGS}.  
First, we use a lemma.

\begin{lemma}[{\cite[3.3.3]{Harmer2006InnocentGS}}]
  Let $\s a\in\Int(A,B,C)$.

  i) If $a$ is a $P$-move of $A$ or an $O$-move of $B$, then $\pv{\s a\vert_{A,B}}=\pv{\pv{\s a}\vert_{A,B}}$.

  ii) If $a$ is a $P$-move of $B$ or an $O$-move of $C$, then $\pv{\s a\vert_{B,C}}=\pv{\pv{\s a}\vert_{B,C}}$.
  \label{LemHarmerProjection}
\end{lemma}
\begin{proof}
  Induction on the length of $\s$.
  We prove (i); the proof of (ii) is exactly the same.

  If $a$ is a $P$-move of $A$ or an $O$-move of $B$, then it is an $O$-move of $A\implies B$.
  If $a$ is an initial move of $A\implies B$, then we have $\pv{\s\vert_{A,B}a}=a=\pv{a}\vert_{A,B}=\pv{\pv{\s a}}\vert_{A,B}$.  
  Otherwise, write $\s=\t b\u$, where $b$ justifies $a$.  
  Then $\pv{\s a \vert_{A,B}} = \pv{\t\vert_{A,B} b\u\vert_{A,B} a} = \pv{t\vert_{A,B}}ba$, which by the inductive hypothesis is equal to $\pv{\pv{\t}\vert_{A,B}}ba$, which is equal to $\pv{\pv{\t b \u a}\vert_{A,B}} = \pv{\pv{\s a}\vert_{A,B}}$.
\end{proof}

\begin{proposition}
  If $\sigma\from A \implies B$ and $\tau\from B \implies C$ are innocent strategies, then $\sigma;\tau\from A\implies C$ is innocent.
\end{proposition}
\begin{proof}
  Suppose there are $sab,t\in\sigma;\tau$ such that $ta\in P_{A\implies C}$, $\pv{sa}=\pv{ta}$.
  Let $\s' b$ be such that $\s' b\vert_{A,C}=sab$ and choose the minimal prefix $\s\prefix \s'$ such that $\s a\vert_{A,C}=sa$.

  Let $\t a$ be such that $\t a\vert_{A,C}=ta$.
  Since $\pv{sa}=\pv{ta}$, we have $\pv{\s a}\vert_{A,C}=\pv{\s a\vert_{A,C}}=\pv{sa}=\pv{ta}=\pv{\t a\vert_{A,C}}=\pv{\t a}\vert_{A,C}$ by Lemma \ref{LemHarmerRestriction}.  
  Let $\u$ be the longest common prefix of $\pv{\s a}$ and $\pv{\t a}$.  
  If $\s a$ and $\t a$ are not equal, then without loss of generality there is some $\u p\prefix \s$, where $\u p\not\prefix \t$.  
  Then, by determinism of $\sigma$ and $\tau$, this $p$ cannot be a $P$-move in either $A\implies B$ or $B\implies C$, so it must be a $P$-move in $A$ or an $O$-move in $C$, and is therefore preceded by another move in $A$ or $C$, which contradicts $\pv{\s a}\vert_{A,C}=\pv{\t a}\vert_{A,C}$.  
  Therefore, $\pv{\s a}=\pv{\t a}$.

  Now write $\s'=\s a b_1 \cdots b_n b$, where each $b_i$ is a move in $B$.  
  We show by induction that $\t a b_1 \cdots b_j\in\sigma\|\tau$.  
  Indeed, if $\t a b_1 \cdots b_{j-1}\in\sigma\|\tau$, then $b_j$ (or $b$) is a $P$-move in either $A\implies B$ or $B\implies C$, and $b_{j-1}$ is an $O$-move in that same component.  
  Write $X$ for the component ($A\implies B$ or $B\implies C$) in which $b_j$ is a $P$-move.
  Repeating the argument above, we see that $\pv{\t a b_1\cdots b_{j-1}} = \pv{\s a b_1\cdots b_{j-1}}$, and so we have that $\pv{\t a b_1\cdots b_{j-1}\vert_X}=\pv{\s a b_1\cdots b_{j-1}\vert_X}$ by Lemma \ref{LemHarmerProjection}.  
  Therefore, by innocence of $\sigma$ (if $X=A\implies B$) or $\tau$ (if $X=B\implies C$), we see that $\t a b_1 \cdots b_j\in \sigma\|\tau$.  
  It follows that $\t a b_1 \cdots b_n b\in\sigma\|\tau$, and therefore that $t a b\in\sigma;\tau$.
\end{proof}

\subsection{Associativity of composition}

In this section, we will prove that composition is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.  
To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in L_{A\implies B}$, $\u\vert_{B,C}\in L_{B\implies C}$ and $\u\vert_{C,D}\in L_{C \implies D}$.  
Given such a sequence $\u$, we define $\u\vert_{A,D}$ as before; i.e., we take all moves from $\u$ occurring in $A$ and $D$, together with justification pointers within these games, and if an initial move in $A$ is justified by an initial move in $B$, which is justified by an initial move in $C$, which is justified by an initial move in $D$, then we add a justification pointer from that move in $A$ to that move in $D$.

Given strategies $\sigma,\tau,\upsilon$ as above, we define $\sigma\|\tau\|\upsilon$ to be the set of all $\u\in\Int(A,B,C,D)$ such that $\u\vert_{A,B}\in\sigma$, $\u\vert_{B,C}\in\tau$ and $\u\vert_{C,D}\in\upsilon$.
We then claim that:

\begin{lemma}
  \[
    (\sigma;\tau);\upsilon = \{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\} = \sigma;(\tau;\upsilon)\,.
    \]
\end{lemma}
\begin{proof}
  Firstly, if $\u\in\sigma\|\tau\|\upsilon$, then it is clear to see that $\u\vert_{A,B,C}\in\sigma\|\tau$ and that $\u\vert_{B,C,D}\in\tau\|\upsilon$, and therefore that $\{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\}\subset (\sigma;\tau);\upsilon$ and $\{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\}\subset \sigma;(\tau;\upsilon)$.

  Conversely, suppose that $\t\in(\sigma;\tau)\|\upsilon$, so that $\t\vert_{A,C}\in\sigma;\tau$ and $\t\vert_{C,D}\in\upsilon$, and choose some $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=\t\vert_{A,C}$.
  We may write 
  \[
    \s=\ccc_1\bbb_1\aaa_1\cdots \ccc_n\bbb_n\aaa_n
    \]
  for some (possibly empty) sequences of moves $\aaa_i$ from $A$, $\bbb_i$ from $B$ and $\ccc_i$ from $C$.  
  We may then write 
  \[
    \t=\ddd_1\ccc_1\aaa_1\cdots\ddd_n\ccc_n\aaa_n
    \]
  (for the same $\aaa_i$, $\ccc_i$), and we can therefore interleave these sequences into the sequence
  \[
    \u = \ddd_1\ccc_1\bbb_1\aaa_1\cdots\ddd_n\ccc_n\bbb_n\aaa_n\,,
    \]
  which is in $\sigma\|\tau\|\upsilon$.
  Then we have $\u\vert_{A,D}=\t\vert_{A,D}$, and it follows that $(\sigma;\tau);\upsilon\subset\{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\}$, and the case for $\sigma;(\tau;\upsilon)$ is identical.
\end{proof}

\subsection{Copycat strategies}

\begin{definition}
  Let $A,B$ be games.  
  Then a \emph{structural isomorphism} from $A$ to $B$ is a bijection $f\from M_A \to M_B$ such that $a\ts_A b$ if and only if $f(a)\ts_B f(b)$ and $*\ts_A a$ if and only if $*\ts_B f(a)$, and such that the plays of $B$ are precisely the plays of $A$, after applying the function $f$ pointwise to the moves (and keeping the justification indices as they are).

  Given a structural isomorphism $f$ from $A$ to $B$, the \emph{copycat strategy} $\cc_f \from A \to B$ is given by
  \[
    \cc_f = \{s\in P_{A\implies B}^{\textit{even}} \suchthat\text{for all even-length $t\prefix s$, $t\vert_B=f^*(t\vert_A)$}\}\,,
    \]
  where $f^*$ denotes $f$ applied pointwise.
\end{definition}

\begin{proposition}
  $\cc_f$ is an innocent strategy for $A\implies B$.  
  Moreover, if $\sigma\from C\implies A$ is a strategy, then
  \[
    \sigma;\cc_f = \{[\id_{M_C},f]^*(s)\suchthat s\in\sigma\}\,,
    \]
  and if $\tau \from B \implies D$ is a strategy, then
  \[
    \cc_f;\tau = \{[f\inv,\id_{M_D}]^*(s)\suchthat s\in\tau\}\,.
    \]
  \label{PropCopycat}
\end{proposition}
\begin{proof}
  $\cc_f$ is clearly prefix-closed by definition.  
  Suppose that $sab,sac\in\cc_f$; then $s\vert_B=f^*(s\vert_A)$ and $sab\vert_B=f^*(sab\vert_A)=f^*(s\vert_A)f^*(ab\vert_A)=s\vert_Bf^*(ab\vert_A)$.  
  It follows that either $ab\vert_B=f^*(ab\vert_A)$, so either $a$ is a move in $A$ and $b=f(a)$ or $a$ is a move in $b$ and $a=f(b)$.  
  Since the same applies to $c$, we have $b=c$.

  This argument shows that $\cc_f$ is \emph{history-free} -- i.e., that its reply to an $O$-position is entirely determined by the last $O$-move -- and therefore it is certainly innocent.

  Now let $\sigma\from C \implies A$ be a strategy.
  Suppose that $\s\in\sigma\|\cc_f$.  
  Then $\s\vert_{C,A}\in\sigma$ and $\s\vert_B=f^*(\s\vert_A)$.
  It follows that $\s\vert_{C,B}=[\id_{M_C},f]^*(\s\vert_{C,A})$.

  Conversely, given $s\in\sigma$, for each $P$-move $a$ in $s$ occurring in the component $A$, insert the move $f(a)$ immediately after it, and for each $O$-move $b$ in $s$ occurring in the component $A$, insert the move $f(b)$ immediately before it.  
  Let these extra moves in $B$ be justified according to the original moves in $A$.
  Then the resulting sequence $\s$ is contained in $\sigma\|\cc_f$, and $\s\vert_{A,C}=[\id_{M_C},f]^*(s)$.

  The case for composition in the other direction is exactly the same.
\end{proof}

An easy corollary of this fact is that composition of copycat strategies respects composition of the underlying structural isomorphisms.

\begin{corollary}
  Let $f$ be a structural isomorphism from $A$ to $B$ and let $g$ be a structural isomorphism from $B$ to $C$.  
  Then $g\circ f$ is a structural isomorphism from $A$ to $C$ and $\cc_{g\circ f}=\cc_f;\cc_g$.
\end{corollary}

It is also easy to see from Proposition \ref{PropCopycat} that the identity function $\id\from M_A \to M_A$ is a structural isomorphism from $A$ to itself, and that the resulting copycat strategy $\cc_{\id}$ is an identity for composition.  
Combining this with our result for associativity in the previous section, we get that
\begin{theorem}
  The collection of games forms a category $\G$, where the morphisms $A \to B$ are strategies for $A\implies B$, composition is as above and the identity morphisms are the copycat strategies induced from the identity functions on moves.
\end{theorem}

In this setting, Proposition \ref{PropCopycat} tells us that structural isomorphism gives rise to an isomorphism in $\G$.
\begin{proposition}
  Let $f$ be a structural isomorphism from a game $A$ to a game $B$.  
  Then $\cc_f$ is an isomorphim in $\G$ from $A$ to $B$.
\end{proposition}

\subsection{Symmetric Monoidal Closed Structure of $\G$}

We now claim that the tensor product connective $\tensor$ makes $\G$ into a symmetric monoidal closed category, with inner hom given by $\implies$.

\begin{definition}
  Let $\sigma\from A \implies B$ and $\tau\from C \implies D$ be strategies.  
  We define a strategy $\sigma\tensor\tau\from (A\tensor C) \implies (B \tensor D)$ by
  \[
    \sigma\tensor\tau = \{s\in P_{(A\tensor C)\implies (B\tensor D)}\suchthat s\vert_{A,B}\in\sigma\text{ and }s\vert_{C,D}\in\tau\}\,.
    \]
\end{definition}

To prove that this is a strategy, we prove a lemma analogous to our Lemma \ref{LemCompositionLemma}.

\begin{lemma}
  Let $s\in P_{A\tensor B}$.  
  Then $\lambda^{OP}_{A\tensor B}(s)=\lambda^{OP}_A(s\vert_A)\wedge\lambda^{OP}_B(s\vert_B)$, where $\wedge$ is the binary operator on $\OP$ given by
  \[
    \begin{array}{cc|c}
      p & q & p\wedge q \\
      \hline
      P & P & P \\
      O & P & O \\
      P & O & O \\
      O & O & O
    \end{array}\,.
    \]
  Moreover, either $\lambda_A^{OP}(s\vert_A)=P$ or $\lambda_B^{OP}(s\vert_B)=P$.
  \label{LemTensorAnalogue}
\end{lemma}
\begin{proof}
  Mutual induction on the length of $s$.  
  This is obvious if $s$ is empty.  
  Suppose that $sa\in P_{A\tensor B}$, where $a$ is an $O$-move.  
  By induction, since $\lambda_{A\tensor B}(s)=P$, we must have $\lambda_{A\tensor B}(s\vert_A)=P$ and $\lambda_{A\tensor B}(s\vert_B)=P$.  
  Therefore, depending on which game $a$ is played in, either $\lambda_A(sa\vert_A)=O$ and $\lambda_B(sa\vert_B)=P$ or $\lambda_A(sa\vert_A)=P$ and $\lambda_B(sa\vert_B)=O$.

  If $sb\in P_{A\tensor B}$, where $b$ is a $P$-move, then by induction either $\lambda_A(s\vert_A)=O$ and $\lambda_B(s\vert_B)=P$ or $\lambda_A(s\vert_A)=P$ and $\lambda_B(s\vert_B)=O$.  
  In either case, player $P$ must play in whichever game is currently in an $O$-position, returning us to configuration $PP$.
\end{proof}

The above proof gives us the following result analogous to Corollary \ref{CorSwitchingCondition}.

\begin{corollary}[Switching condition for {$\tensor$}]
  Player $O$ switches games in $A\tensor B$; i.e., if $sab\in P_{A\tensor B}$, where $a$ and $b$ take place in different games (i.e., $a$ in $A$ and $b$ in $B$ or $a$ in $B$ and $b$ in $A$), then $b$ is an $O$-move.
\end{corollary}

\begin{proposition}
  $\sigma\tensor\tau$ is a strategy for $(A\tensor C)\implies (B\tensor D)$.
  \label{PropTensorWellDefined}
\end{proposition}
\begin{proof}
  $\sigma\tensor\tau$ is certainly an even-prefix-closed subset of $P_{(A\tensor C)\implies (B\tensor D)}^{\textit{even}}$.

  Let $s$ be a play of $P_{(A\tensor B)\implies (C\tensor D)}$.  
  We consider the possible configurations of $s$; i.e., the tuples $(\lambda_A(s\vert_A),\lambda_B(s\vert_B),\lambda_C(s\vert_C),\lambda_D(s\vert_D))$.

  By Lemma \ref{LemCompositionLemma} we must avoid the overall configuration $OP$ for the linear implication, and by Lemma \ref{LemTensorAnalogue} we must avoid the configuration $OO$ inside either tensor product, so we end up with the following possibilities.
  \scriptsize
  \[
\arraycolsep=4.8pt\def\arraystretch{1.5}
    \begin{array}{cccc|cc|c}
      \lambda_A(s\vert_A) & \lambda_C(s\vert_C) & \lambda_B(s\vert_B) & \lambda_D(s\vert_D) & \lambda_{A\tensor C}(s\vert_{A,C}) & \lambda_{B\tensor D}(s\vert_{B,C}) & \lambda_{(A\tensor C)\implies (B\tensor D)}(s) \\
      \hline
      P & P & P & P & P & P & P \\
      P & P & P & O & P & O & O \\
      P & P & O & P & P & O & O \\
      P & O & P & O & O & O & P \\
      O & P & O & P & O & O & P \\
      P & O & O & P & O & O & P \\
      O & P & P & O & O & O & P \\
    \end{array}
    \]
  \normalsize
  Now, if $s\in\sigma\tensor\tau$, or an odd-length sequence formed by adding an $O$-move to the end of a sequence in $\sigma\tensor\tau$, then we also know that $s\vert_{A,B}\in\sigma\subset P_{A\implies B}$ and that $s\vert_{C,D}\in\tau\subset P_{C\implies D}$.  
  This means that we can discount the last two configurations in the table above, since one contains the illegal configuration $OP$ in $C\implies D$ and the other contains the illegal configuration $OP$ in $A \implies B$.

  Now suppose that $sab,sac\in\sigma\tensor\tau$.  
  Then $sa$ is an $O$-position in $P_{(A\tensor C)\implies (B\tensor D)}$, and is therefore in configuration $PPPO$ or $PPOP$.  
  By inspecting the table above, we see that if $sa$ is in configuration $PPPO$, then $b$ and $c$ must both occur either in $C$ or in $D$, and that if $sa$ is in configuration $PPOP$, then $b$ and $c$ must both occur either in $A$ or in $B$.  
  In either case, we must have $b=c$, by determinism of $\tau$ (in the first case) or of $\sigma$ (in the second case).
\end{proof}

We need a lemma to prove that the tensor product of two innocent strategies is innocent.

\begin{lemma}
  Let $s\in\sigma\tensor\tau$.

  i) If $s$ ends with a move in $A$ or $B$, then $\pv{s}^{(A\tensor C)\implies (B\tensor D)}=\pv{s\vert_{A,B}}^{A\implies B}$.

  ii) If $s$ ends with a move in $C$ or $D$, then $\pv{s}^{(A\tensor C)\implies (B\tensor D)}=\pv{s\vert_{C,D}}^{C\implies D}$.
\end{lemma}
\begin{proof}
  Induction on the length of $s$.  
  We prove (i); (ii) is exactly the same.

  If $a$ is a $P$-move, then we have $\pv{sa}=\pv{s}a$.  
  By our analysis in the proof of Proposition \ref{PropTensorWellDefined}, player $P$ only switches moves between $A$ and $B$, and between $C$ and $D$, so $s$ must end with a move from $A$ or $B$.  
  Therefore, by the inductive hypothesis, $\pv{s}=\pv{s\vert_{A,B}}$.  
  Then $\pv{sa}=\pv{s}a=\pv{s\vert_{A,B}}a=\pv{sa\vert_{A,B}}$.

  If $a$ is an initial move, then $\pv{sa}=a=\pv{sa\vert_{A,B}}$.

  If $a$ is an $O$-move justified by $b$ in $sbta$, then $\pv{sbta}=\pv{s}ba$.  
  Then $b$ is a $P$-move, so $s$ must end with a move in $A$ or $B$, as before.  
  Therefore, by the inductive hypothesis, $\pv{s}=\pv{s\vert_{A,B}}$.  
  Then $\pv{sbta}=\pv{s}ba=\pv{s\vert_{A,B}}ba=\pv{sbta\vert_{A,B}}$.
\end{proof}

\begin{proposition}
  Let $\sigma\from A \to B$, $\tau\from C \to D$ be innocent strategies.  
  Then $\sigma\tensor\tau$ is innocent.
\end{proposition}
\begin{proof}
  Suppose $sab,t\in\sigma\tensor\tau$ such that $ta\in P_{(A\tensor C)\implies (B\tensor D)}$ and $\pv{sa}=\pv{ta}$.  
  Suppose without loss of generality that $a$ is a move in $A$ or $B$.  
  Then $\pv{sa}=\pv{sa\vert_{A,B}}$ and $\pv{ta}=\pv{ta\vert_{A,B}}$, and therefore $tab\vert_{A,B}\in\tau$ by innocence of $\tau$, and so $tab\in\sigma\tensor\tau$.  
\end{proof}

The most important thing we need to prove is that $\tensor$ is a functor.

\begin{proposition}
  Let $\sigma'\from A'' \implies A'$, $\sigma\from A' \implies A$, $\tau'\from B'' \implies B'$ and $\tau \from B' \implies B$ be strategies.  
  Then $(\sigma'\tensor\tau');(\sigma\tensor\tau)=(\sigma';\sigma)\tensor(\tau';\tau)$.

  Moreover, if $A',A,B',B$ are games, $f$ is a structural isomorphism from $A'$ to $A$ and $g$ is a structural isomorphism from $B'$ to $B$, then $\cc_f\tensor\cc_g = \cc_{[f,g]}$.
  In particular, if $A$ and $B$ are games, then $\id_A\tensor \id_B=\id_{A\tensor B}$.
\end{proposition}
\begin{proof}
  First suppose that $s\in(\sigma'\tensor\tau');(\sigma\tensor\tau)$; so $s=\s\vert_{A'',B'',A,B}$, where $\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)$.  
  Then $\s\vert_{A'',A'}\in\sigma'$ and $\s\vert_{A',A}\in\sigma$, so $\s\vert_{A'',A',A}\in\sigma'\|\sigma$ and therefore $s\vert_{A'',A}=\s\vert_{A'',A}\in\sigma';\sigma$.  
  Similarly, $s\vert_{B'',B}\in\tau';\tau$, and therefore $s\in(\sigma';\sigma)\tensor(\tau';\tau)$.

  Conversely, suppose that $s\in(\sigma';\sigma)\tensor (\tau';\tau)$.  
  Choose some $\s\in\sigma'\|\sigma$, $\t\in\tau'\|\tau$ such that $s\vert_{A'',A}=\s\vert_{A'',A}$ and $s\vert_{B'',B}=\s\vert_{B'',B}$.  
  By our analysis, the only time we switch from the $A'',A$-component to the $B'',B$ component in $s$, or \emph{vice versa}, is when player $O$ switches between the games $A$ and $B$.  
  Thus, we may divide $s$ up into blocks, each starting and ending with a move in the outer component $A \tensor B$.  
  This then gives us a way to divide up $\s$ and $\t$ into blocks, such that each block of $\s$ or $\t$ projects on to a block of $s$.  
  Lastly, we can string these blocks together to give us some $\u\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)$ such that $\u\vert_{A'',B'',A,B}=s$.

  For the second part, let $A',A,B',B$ be games, let $f$ be a structural isomorphism from $A'$ to $A$ and let $g$ be a structural isomorphism from $B'$ to $B$.  
  Then we have
  \begin{IEEEeqnarray*}{CCL}
    \cc_f\tensor\cc_g & = & \{s\in P_{(A'\tensor B')\implies (A\tensor B)} \suchthat \text{$s\vert_{A',A}\in\cc_f$ and $s\vert_{B',B}\in \cc_g$}\} \\
    & = & \left\{s\in P_{(A'\tensor B')\implies (A\tensor B)}\,\middle|\, \mbox{\pbox{\textwidth}{for all even $t\prefix s\vert_{A',A}$, $u\prefix s\vert_{B',B}$,\\ $t\vert_A=f^*(t\vert_{A'})$ and $u\vert_B=g^*(u\vert_{B'})$}}\right\}
  \end{IEEEeqnarray*}
\end{proof}

\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-03-20 Thesis/ndgames.tex
Nightly commit.

\subsection{Game semantics for countable nondeterminism with must testing}

In general, it is harder to model terms up to must equivalence than it is up to may equivalence.
For the finite nondeterminism case, the model of Harmer and McCusker \cite{mcCHFiniteND} uses nondeterministic strategies to model terms, as with may-testing, but these are not enough on their own: for instance, the terms $\skipp$ and $\If \ask_\bB \Then \skipp \Else \Omega$ are both denoted by the strategy
\[
  \{\epsilon,qa\}
  \]
for $\bC$, but while these terms are may equivalent, $\skipp \mustconverge$, while $\If \ask_\bB \Then \skipp \Else \Omega\diverges$.
Harmer and McCusker's solution is to augment each strategy $\sigma$ to include a set $D_\sigma$ of $O$-positions after which play may diverge.  
Then the denotation of $\skipp$ is
\[
  (\{\epsilon,qa\},\emptyset)\,,
  \]
while the denotation of $\If \ask_\bB \Then \skipp \Else \Omega$ is
\[
  (\{\epsilon,qa\},\{q\}\}\,,
  \]
where the divergence set $\{q\}$ signifies the fact that there is a possible divergence after the initial question move.

For countable nondeterminism, there is an additional subtlety.  
Consider the term
\[
  c \from\com \ts M = (\Y_{\nat \to \com} \lambda f.\lambda n.\IfO n \Then \skipp \Else c;f(\pred n)) \ask_\bN \from \com\,.
  \]
So $M$ nondeterministically chooses an arbitrarily large number and then calls its argument that many times.
Then consider also the term
\[
  c \from \com \ts N = \IfO \ask_\bN \Then M \Else \Y_{\com} (\lambda f.c;f) \from \com\,,
  \]
which exhibits all the behaviours of $M$, but may also call its argument infinitely many times.

The denotation of $M$ is as the strategy with maximal plays
\[
  q(qa)^na
  \]
for all $n\in\bN$, and no divergences.  
The denotation of $N$ should be the same as that of $M$, except that we must add an extra infinite sequence of increasing plays to capture the divergent behaviour.  
But this infinite sequence of plays is precisely those plays of the form
\[
  q(qa)^mq\,,
  \]
and these are already contained in the denotation of $N$.  
In other words, $M$ and $N$ have the same denotation, because the semantics is not able to distinguish between infinite (divergent) computations, and those that are convergent but may take an arbitrarily long time.
This is a problem, because while $(\lambda c.M)\skipp\mustconverge$, $(\lambda c.N)\skipp\diverges$.

Following Roscoe \cite{RoscoeCspInfinite} and Levy \cite{LevyGsInfinite}, Jim Laird and I published a fully abstract game semantics for IA with countable nondeterminism \cite{CslPaper}, in which a strategy is allowed to contain infinite as well as finite plays.
Our semantics distinguishes between the terms $M$ and $N$ above, in that only $\deno N$ contains the infinite play
\[
  qqaqaqa\cdots\,.
  \]
A problem then arises

### 2019-03-20 Thesis/yold.tex
Nightly commit.

\subsection{Extended example: game semantics of time complexity}
This is an extended example of using a reader monad, in the style of Example \ref{ExReaderMonadKleisli}.
Let $\G$ be the category of games and visible single-threaded strategies as in \cite{SamsonGuyIAActive}.  
So $\G$ is a sound and adequate model of Idealized Algol satisfying compact definability.
Let $\bC$ be the denotation of the command type $\com$ of Idealized Algol.  
Then the Kleisli category for the reader monad over $\bC$ is freely generated over $\G$ by a single morphism $1 \to \bC$.

Let us extend Idealized Algol with a single term, $\sleep$, of type $\com$.
This should be thought of as a command to the computer to pause for some fixed interval of time -- let us say a second -- before resuming execution.
By Theorem \ref{FunctionalCompletenessCcc}, our Kleisli category is Cartesian closed.
So it gives us a denotational semantics of IA+$\sleep$, in which the terms of IA are interpreted within $\G$ as in \cite{SamsonGuyIAActive} and the new term $\sleep$ is interpreted by the new morphism $1 \to \bC$.

Let us now give an operational semantics to terms of IA+$\sleep$.  
Let $\Gamma$ be an IA-context.
Then a \emph{store} $s$ over $\Gamma$ is a list of pairs $(v\mapsto x)$, where each $v$ is the name for a $\Var$-type variable occurring in $\Gamma$ and $x$ is a value held in $v$.  
We write $()$ for the empty store, $(s\vert v\mapsto x)$ for the store obtained from $s$ by adding or updating the variable $v$ to hold the value $x$ and $(s\vert v\mapsto \bot)$ for the store obtained by removing the variable $v$ from $s$.
Given disjoint stores $s,t$ (i.e., stores whose sets of variables are disjoint), we write $s+t$ for the store obtained by concatenating together $s$ and $t$.

Given a term $\Gamma\ts M$ in context, stores $s$,$s'$ over $\Gamma$, a value $c$ and a natural number $n$, we define a big-step relation
\[
  \Gamma,s\ts M\converges_n c,s'\,,
  \]
read as `in the context $\Gamma$, $s,M$ converges to $c,s'$ in time $n$'.  
The rule for the constant $\sleep$ is given by
\[
  \inferrule*
  { }
  {\Gamma,s\ts \sleep\converges_1 \skipp,s}\,,
  \]
indicating that execution of the $\sleep$ command takes up an additional time step.  
The other rules are the same as those given in \cite{SamsonGuyIAActive} for the $\converges$ relation, except that we have to modify them in order to take account of the new information we have added to the reduction relation (i.e., the time taken to converge).
For example:
\begin{mathpar}
  \inferrule*
  { }
  {\Gamma,s\ts c \converges_0 c,s}
  \and
  \inferrule*
  {\Gamma,s\ts M\converges_m\skipp,s'\\
  \Gamma,s'\ts N\converges_n\skipp,s''}
  {\Gamma,s\ts M;N\converges_{m+n}\skipp,s''}\,.
\end{mathpar}
If $P$ is a program (i.e., a term of type $\com$) then we write $P\converges_n$ as a shorthand for $,()\ts P \converges_n \skipp,()$.
We say that $P$ \emph{diverges} and write $P\diverges$ if there is no $n$ such that $P\converges_n$.

We now want a way to capture this operational behaviour within the denotational semantics.
First, we note the Computational Adequacy result proved for the game semantics of Idealized Algol.

\begin{proposition}[{\cite[21]{SamsonGuyIAActive}}]
  Let $P$ be a term of type $\com$.  
  Then $P\converges$ if and only if $\deno{P}\ne\bot$.
  \label{SamsonGuyAdequacy}
\end{proposition}

To make sense of this strategy, we need to know that $\G$ is enriched in algebraic cpos.  
Then $\bot$ is the bottom element of $\G(1,\bC)$.

Before proceeding further, we prove an important lemma.  
This lemma tells us that the operational semantics of a term of IA+$\sleep$ may be modelled within Idealized Algol; i.e., that IA+$\sleep$ is a conservative extension of the original language.

\begin{lemma}
  Let $P\from T$ be a term of IA+$\sleep$.
  Suppose that
  \[
    \Gamma,s\ts P\converges_n c,s'
    \]
  in IA+$\sleep$.

  Then for all $k\ge 0$, all contexts $\Delta$ disjoint from $\Gamma$, all stores $t$ over $\Gamma,\Delta$ disjoint from $s$ and all variables $v$ not in $\Gamma,\Delta$:
  \[
    \Delta,\Gamma,v,(t{+}s\vert v \mapsto k)\ts P[v \gets \suc !v/\sleep] \converges c,(t{+}s\vert v \mapsto k+n)
    \]
  in Idealized Algol.
  \label{IaSleepsSoundnessLemma}
\end{lemma}
\begin{proof}
  Induction on the derivation that $\Gamma,s\ts P\converges_n c,s'$.
  There are several possibilities for the last step in the derivation.
  \begin{description}
    \item[Structural congruence]
      Suppose that the last step in the derivation is
      \[
        \inferrule*{P\equiv P'\\
        \Gamma,s\ts P' \converges_n \skipp, s'}
        {\Gamma,s\ts P\converges_n \skipp, s'}\,.
        \]
      It is clear then by the definition of structural congruence that $P'[v\gets\suc !v/\sleep]\equiv P[v\gets\suc !v/\sleep]$.  
      So the claim follows by the inductive hypothesis applied to $P'$ and the structural congruence rule for Idealized Algol.
    \item[$\sleep$]
      Suppose that the last step in the derivation is
      \[
        \inferrule*{ }
        {\Gamma,s\ts \sleep \converges_1 \skipp,s}\,.
        \]
      Fix a context $\Delta$ disjoint from $\Gamma$ and a store $t$ over $\Gamma,\Delta$ that is disjoint from $s$.  
      Fix $k\ge n$.  
      Then it suffices to show that the following judgement may be proved within the operational semantics of Idealized Algol.
      \[
        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \gets \suc !v \converges \skipp, (t{+}s\vert v\mapsto k+1)
        \]
      A derivation for this obvious fact is given in Figure \ref{SleepIADerivation}.
      \begin{SidewaysFigure}
        \centering
        \begin{subfigure}{\textheight}
          \[
            \inferrule*
            {
              \inferrule*
              {
                \inferrule*
                {
                  \inferrule*
                  {
                  }
                  {
                    \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \converges v,(t{+}s\vert v\mapsto k)
                  }
                }
                {
                  \Delta,\Gamma,v,(t{+}s\vert v\mapsto k) \ts !v \converges k,(t{+}s\vert v\mapsto k)
                }
              }
              {
                \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts \suc !v \converges k+1,(t{+}s\vert v\mapsto k)
              } \\
              \inferrule*
              {
              }
              {
                \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v \converges v,(t{+}s\vert v\mapsto k)
              }
            }
            {
              \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts v\gets\suc !v\converges\skipp,(t{+}s\vert v\mapsto k+1)
            }
            \]
          \caption{The crucial part of Lemma \ref{IaSleepsSoundnessLemma} pertaining to the $\sleep$ constant is a routine Idealized Algol derivation.}
          \label{SleepIADerivation}
        \end{subfigure}
        \par\vspace{48pt}
        \begin{subfigure}{\textheight}
          \[
            \inferrule*{\Delta,\Gamma_1,v,(t{+}s\vert v\mapsto k) \ts M_1[v \gets \suc !v/\sleep] \converges c_1,(t{+}s\vert v \mapsto k + n_1) \\
            \cdots \\
            \Delta,\Gamma_p,v,(t{+}s\vert v\mapsto k + n_1 + \cdots + n_{p-1}) \ts M_p[v \gets \suc !v/\sleep] \converges c_1,(t{+}s\vert v \mapsto k+n_1+\cdots+n_p)}
            {\Delta,\Gamma,v,(t{+}s^{(0)}\vert v \mapsto k + n_1 + \cdots + n_p)\ts M[v\gets \suc !v/\sleep] \converges c,(t{+}s^{(p)}\vert v \mapsto k)}
            \]
          \caption{The big-step rules of IA+$\sleep$ give rise to big-step rules of Idealized Algol via our translation.}
          \label{GeneralIADerivation}
        \end{subfigure}
        \caption{The proof of Lemma \ref{IaSleepsSoundnessLemma} works by translating big-step derivations from IA+$\sleep$ into big-step derivations of Idealized Algol.}
        \label{IADerivations}
      \end{SidewaysFigure}
    \item[Canonical forms]
      Suppose that the last step in the derivation is
      \[
        \inferrule*{ }
        {\Gamma,s\ts_0 c\converges c,s}\,.
        \]
      Then, since $\sleep$ is not a canonical form, we have $c[v\gets \suc !v/\sleep]=c$.  
      Then we have the derivation
      \[
        \inferrule*{ }
        {\Delta,\Gamma,(t{+}s\vert v\mapsto k)\ts c \converges c,(t{+}s\vert v\mapsto k)}\,.
        \]
    \item[Sequencing]
      Suppose instead that the last step in the derivation is
      \[
        \inferrule*{\Gamma,s\ts M \converges_m \skipp, s'\\
        \Gamma,s'\ts N \converges_n \skipp, s''}
        {\Gamma,s\ts M;N \converges_{m+n} \skipp, s''}\,.
        \]
      Fix $k\ge 0$.  
      By induction on $M,N$, we have
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k)\ts M[v\gets\pred !v/\sleep]\converges \skipp,(t{+}s'\vert  v\mapsto k+m)\,;
        \and
        \Delta,\Gamma,v,(t{+}s'\vert  v\mapsto k+m) \hspace{144pt} \par\vspace{-8pt} \\ \par \hspace{144pt} \ts N[v\gets\pred !v/\sleep]\converges \skipp,(t{+}s''\vert v\mapsto k+m+n)\,.
      \end{mathpar}
      It follows that
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s\vert v\mapsto k) \hspace{180pt} \par\vspace{-8pt} \\ \par \hspace{180pt} \ts (M;N)[v\gets\pred !v/\sleep] \converges \skipp, (t{+}s''\vert v\mapsto k+m+n)\,,
      \end{mathpar}
      by the sequencing rule of Idealized Algol.
    \item[Remaining rules]
      Having given the rule for canonical forms and sequencing explicitly, we now give a general technique by which we can deal with all the remaining rules.

      Each rule is of the form
      \[
        \inferrule*{ \Gamma_1,s^{(0)}\ts z_1\converges_{n_1}\gamma_1,s^{(1)} \\
        \cdots \\
        \Gamma_p,s^{(p - 1)}\ts z_p \converges_{n_p} \gamma_p,s^{(p)}}
        { \Gamma,s^{(0)}\ts z \converges_{n_1+\cdots+n_p} \gamma,s^{(p)}}
        \]
      (for $p\in\{0,1,2,3\}$), where
      \[
        \inferrule*{ \Gamma_1,s^{(0)}\ts z_1\converges \gamma_p,s^{(1)} \\
        \cdots \\
        \Gamma_p,s^{(p - 1)}\ts z_p \converges \gamma_1,s^{(p)}}
        { \Gamma,s^{(0)}\ts z \converges \gamma,s^{(p)}}
        \]
      is a rule for Idealized Algol.

      Here, each $z_i,z,\gamma_i,\gamma$ is a term of Idealized Algol (without $\sleep$) that may have free variables that are not included in the $\Gamma_i,\Gamma$.  
      These free variables $(x_\alpha)$ may be shared between the $z_i,z,\gamma_i,\gamma$, introducing a dependence between them.
      For example, in the rule for sequencing, the terms on the top are single-variable terms of IA, where `$M$' and `$N$' are themselves free variables.  
      These variables are bound in the expression `$M;N$' on the bottom of the rule.

      Fix some such rule, and suppose that it is used in the last step of the deduction.  
      So the last step looks like this.
      \[
        \inferrule*{ \Gamma_1,s^{(0)}\ts M_1\converges_{n_1}c_1,s^{(1)} \\
        \cdots \\
        \Gamma_p,s^{(p - 1)}\ts M_p \converges_{n_p} c_p,s^{(p)}}
        { \Gamma,s^{(0)}\ts M \converges_{n_1+\cdots+n_p} c,s^{(p)}}
        \]
      Here, the $M_i,M,c_i,c$ fit the pattern given by the $z_i,z,\gamma_i,\gamma$.  
      By induction, for each $i=1,\cdots,p$, the following judgement may be proved in Idealized Algol.
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s^{(i)}\vert v \mapsto k + n_1 + \cdots + n_{i-1})
        \hspace{144pt} \par\vspace{-20pt} \\ \par \hspace{144pt}
        \ts
        M[v \gets \suc !v] \converges c_i,(t{+}s^{(i)}\vert v \mapsto k + n_1 + \cdots + n_i)
      \end{mathpar}

      Now we know that the $M_i,M,c_i,c$ may be obtained from the $z_i,z,\gamma_i,\gamma$ by substituting in actual terms $N_\alpha$ for the free variables $x_\alpha$ in these expressions.  
      Moreover, since the primitive $\sleep$ is not mentioned anywhere in these rules, it follows that we have
      \begin{IEEEeqnarray*}{rCl}
        M_i[v\gets\suc !v/\sleep] & = & (z_i[N\alpha/x_\alpha])[v\gets \suc !v/\sleep] \\
        & = & z_i[(N[v\gets \suc !v/\sleep])/x_\alpha]\,,
      \end{IEEEeqnarray*}
      and similarly for the $z,\gamma_i,\gamma$.
      Therefore, the $M_i,M,c_i,c$ still fit the pattern given by the $z_i,z,\gamma_i,\gamma$, even after making our substitution.  
      It follows that we may derive
      \begin{mathpar}
        \Delta,\Gamma,v,(t{+}s^{(0)}\vert v \mapsto k)\hspace{180pt}\par\vspace{-8pt}\\ \par
        \hspace{180pt}\ts M[v\gets \suc !v/\sleep] \converges c,(t{+}s^{(p)}\vert v \mapsto k+n_1+\cdots+n_p)
      \end{mathpar}
      using the derivation shown in Figure \ref{GeneralIADerivation}.
  \end{description}
  This completes the induction.
\end{proof}

In light of this result, we can make a definition relating the denotational and operational semantics of terms of type $\nat$.  
First, observe that since the $\beta$ rule is valid in our semantics, we may write the denotation of a term $M\from\com$ of IA+$\sleep$ as the composite
\[
  1 \xrightarrow{\sleep}
  \bC \xrightarrow{\deno{c\ts M[c/\sleep]}}
  \bC
  \]
in $\Kl_{R_\bC}$.

Working in the original category $\G$, however, we may identify this composite with the morphism
\[
  \deno{\lambda c.M[c/\sleep]} \from 1 \to (\bC \to \bC)\,.
  \]
Now we have a morphism
\begin{mathpar}
  \eta = \deno{f\from \com\to \com \ts \lambda v.f(v\gets \suc!v);!v}\from (\bC \to \bC) \to (\Var \to \bN)\,.
\end{mathpar}
If we form the composite
\[
  1 \xrightarrow{\deno{\lambda c.M[c/\sleep]}}
  (\bC \to \bC) \xrightarrow{\eta}
  (\Var \to \bN) \xrightarrow{\new_\bN}
  \bN
  \]
then the morphism we get will be the denotation in $\G$ of the term
\[
  \ts \new\;v=0\text{ in } M[v\gets \suc !v/\sleep];!v\from \nat
  \]
(since the $\beta$ rule is valid for the semantics in $\G$).
Lemma \ref{IaSleepsSoundnessLemma} tells us that if $M\converges_n\skipp$ then this term converges to $n$ in Idealized Algol.

Before we introduce our adequacy result, we need one more definition in order to take account of the fact that Proposition \ref{SamsonGuyAdequacy} applies to terms of type $\com$, not $\nat$.

\newcommand{\test}{{\mathtt{test}}}
\begin{definition}
  Define terms $\test_n\from\nat\to\com$ inductively by
  \begin{gather*}
    \test_0 = \lambda m.\IfO m\text{ then }\skipp\text{ else }\Omega\,; \\
    \test_{n+1} = \lambda m.\IfO m\text{ then }\Omega\text{ else }\test_n\,. (\pred m)
  \end{gather*}
  So $\test_n$ converges if its input evaluates to $n$ and diverges otherwise.

  Let $t_n\from\bN \to \bC$ be the denotation in $\G$ of $\test_n$.
\end{definition}

\begin{remark}
  In the model $\G$ of Idealized Algol, every morphism $1 \to \bN$ is definable, so if $\sigma\from 1 \to \bN$ is such a morphism, then there must be at most one $n\in\omega$ such that the composite $\sigma;t_n$ is not equal to $\bot$.
\end{remark}

\newcommand{\tit}{\mathrm{tt}}
\begin{definition}
  Let $\sigma\from 1 \to \bC$ be a Kleisli morphism in $\Kl_{R_{\bC}}$, considered as a morphism $1 \to (\bC \to \bC)$ in $\G$.

  If there is some (necessarily unique) $n\in\omega$ such that the composite
  \[
    1 \xrightarrow{\sigma}
    (\bC \to \bC) \xrightarrow{\eta}
    (\Var \to \bN) \xrightarrow{\new_\bN}
    \bN \xrightarrow{t_n}
    \bC
    \]
  is not equal to $\bot$, then we say that $n$ is the \emph{time taken for $\sigma$ to converge}, or $\tit(\sigma)$.
  If there is no such $n$, we say that $\tit(\sigma)=\infty$.
  \label{DefTimeTaken}
\end{definition}

From our discussion above, we have proved the following result.

\begin{proposition}[Soundness for IA+$\sleep$]
  Let $P\from \com$ be a term of IA+$\sleep$ and let $\sigma\from \bC \to \bC$ be its denotation in $\Kl_{R_\bC}$, considered as a morphism in $\G$.
  If $P\converges_n$ then $\tit(\sigma)=n$.
  \label{IaSleepSoundness}
\end{proposition}

In order to prove the other direction (adequacy), we need to prove a kind of converse to Lemma \ref{IaSleepsSoundnessLemma}.

\begin{lemma}
  Let $\Gamma\ts M\from \com$ be a term of IA+$\sleep$ in context.
  Let $s,s'$ be stores, let $a,b\in\bN$, let $c$ be a canonical form and let $v$ be a variable not included in $\Gamma$.  
  Suppose that
  \[
    \Gamma,v,(s\vert v\mapsto a) \ts M \converges c,(s'\vert v\mapsto b)
    \]
  in Idealized Algol.
  Then there exists $n$ such that
  \[
    \Gamma,s \ts M \converges_n c,s'
    \]
  in IA+$\sleep$.
\end{lemma}
\begin{proof}
  Induction on the derivation that $\Gamma,v,(s\vert v\mapsto a)\ts M\converges c,(s'\vert v\mapsto b)$.  
  Most cases are self-explanatory.  
  For example, suppose that the last step in the derivation is an instance of the sequencing rule:
  \[
    \inferrule{\Gamma,v,(s\vert v \mapsto a) \ts M[v\gets\suc !v/\sleep] \converges \skipp, s' \\
    \Gamma,v,s' \ts N[v\gets\suc !v/\sleep] \converges c, (s''\vert v \mapsto b)}
    {\Gamma,v(s\vert v \mapsto a) \ts (M;N)[v\gets\suc !v/\sleep] \converges c,(s''\vert v \mapsto b)}\,.
    \]
  Since there is no provable sequent of Idealized Algol in which a defined variable on the left ceases to be defined on the right, we may deduce that $s'$ can be written as $(t\vert v \mapsto d)$.  
  Therefore, we may apply the inductive hypothesis to $M$ and $N$, which tells us that there must be $m,n$ such that
  \begin{mathpar}
    \Gamma,s \ts M\converges_m\skipp,t\,;
    \and
    \Gamma,t \ts M\converges_n c,s''\,.
  \end{mathpar}
  From this it follows that
  \[
    \Gamma,s \ts M;N \converges_{m+n} c,s''\,.
    \]
  Crucial to this argument is the fact that
  \[
    (M[v\gets\suc !v/\sleep]);(N[v\gets\suc !v/\sleep]) = (M;N)[v\gets\suc!v/\sleep]\,.
    \]
  For almost all the other rules, a similar equality holds.  
  The only case where there is a problem is the first rule for $\blank\gets\blank$, since this may introduce a new copy of $v\gets\suc!v$ on the bottom that does not arise from copies of $v\gets\suc!v$ on the top.

  The offending term occurs when $M=\sleep$ and so $M[v\gets\suc!v/\sleep]=v\gets\suc!v$.
  In that case, the inference is
  \[
    \inferrule{\Gamma,(s\vert v \mapsto a)\ts \suc ! v \converges b,s'\\
    \Gamma,s'\ts v \converges v,s''}
    {\Gamma,(s\vert v\mapsto a)\ts v \gets\suc!v \converges \skipp,(s''\vert v\mapsto b)}\,.
    \]
  By following the derivation upwards, we may deduce that in fact $s=s'=s''$.
  But in that case the derivation of $\Gamma,s\ts_n M\converges \skipp,s''$ is one of the base rules:
  \[
    \inferrule{ }
    {\Gamma,s \ts \sleep \converges_1 \skipp,s}\,.
    \]
  The other cases are routine.  
  This completes the induction.
  \label{IaSleepAdequacyLemma}
\end{proof}

\begin{theorem}[Computational adequacy for IA+$\sleep$]
  Let $P\from\com$ be a term of IA+$\sleep$ and let $\sigma\from \bC\to \bC$ be its denotation in $\Kl_{R_\bC}$, considered as a morphism in $\G$.
  Then $P\converges_n$ if and only if $\tit(\sigma)=n$.
  \label{IaSleepComputationalAdequacy}
\end{theorem}
\begin{proof}
  The forward direction is Proposition \ref{IaSleepSoundness}.  
  For the reverse direction, note that if $\tit(\sigma)=n$, it means that
  \[
    \deno{\test_n(\new v=0\text{ in }P[v\gets \suc!v/\sleep];!v])} \ne \bot\,,
  \]
  which, by Proposition \ref{SamsonGuyAdequacy}, means that
  \[
    \test_n(\new v=0\text{ in } P[v\gets\suc!v/\sleep];!v])\converges
  \]
  in Idealized Algol, and therefore that
  \[
    v,(v\mapsto 0) \ts P[v\gets\suc!v/\sleep]\converges \skipp,(v\mapsto n)\,.
    \]
  From Lemma \ref{IaSleepAdequacyLemma}, we deduce that we must have
  \[
    ,() \ts P \converges_m \skipp,()
    \]
  in IA+$\sleep$ for some $m$, and by Lemma \ref{IaSleepsSoundnessLemma} we must have $m=n$.  
  Therefore, $P\converges_n$.
\end{proof}

The last definition we need to make is the standard intrinsic equivalence relation.

\begin{definition}
  Let $\sigma,\tau\from A \to B$ be morphisms in $\Kl_{R_\bC}$.  
  By currying, we may consider $\sigma,\tau$ to be morphisms $1 \to (A \to B)$.  
  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$, we have $\tit(\sigma;\alpha)=\tit(\sigma;\beta)$.
\end{definition}

We now have all the tools necessary to prove that $Kl_{R_\bC}$ is fully abstract for IA+$\sleep$.
The technique we use is standard and relies on a factorization result, as with the proofs given in \cite{SamsonGuyIAActive} and \cite{mcCHFiniteND}.  
The difference here is that our factorization result is immediate, and does not rely on any combinatorial arguments.

\begin{theorem}
  Let $M,N\from T$ be two terms of IA+$\sleep$.  
  Then $M$ and $N$ are observationally equivalent if and only if $\deno{M}\sim\deno{N}$.
  \label{IaSleepTimeComplexity}
\end{theorem}
\begin{proof}
  First suppose that $M$ and $N$ are not observationally equivalent.  
  So there is some context $-\from T\ts C[-]\from\com$ such that $C[M]$ and $C[N]$ have different operational behaviours in IA+$\sleep$.
  By Theorem \ref{IaSleepComputationalAdequacy} we know that for any program $P$ we have $P\converges_n$ if and only if $\tit(\deno P)=n$ and $P\diverges$ if and only if $\tit(\deno P)=\infty$.
  Therefore, we must have $\tit(\deno{C[M]})\ne \tit(\deno{C[n]})$.  
  But since $\deno{C[M]}=\deno{M};\deno{C}$ and $\deno{C[N]}=\deno{N};\deno{C}$, we must have $\deno M\not\sim \deno N$.

  Conversely, suppose that $\deno M \not\sim \deno N$.  
  So there is some $\alpha\from \deno{T} \to \bC$ such that $\deno{M};\alpha\ne\deno{N};\alpha$.

  Let us now work in the category $\G$.  
  So $\deno{M},\deno{N}$ may be regarded as morphisms $1 \to (\bC \to \deno{T})$ and $\alpha$ may be regarded as a morphism $\deno{T} \to (\bC \to \bC)$.
  Then the composites $\deno M;\alpha$ and $\deno N;\alpha$ within $\Kl_{R_\bC}$ are given by the following composites in $\G$.
  \begin{mathpar}
    1 \xrightarrow{\deno M}
    (\bC \to \deno T) \xrightarrow{\bC \to \alpha}
    (\bC \to (\bC \to \bC)) \xrightarrow{\mu}
    (\bC \to \bC)
    \and
    1 \xrightarrow{\deno N}
    (\bC \to \deno T) \xrightarrow{\bC \to \alpha}
    (\bC \to (\bC \to \bC)) \xrightarrow{\mu}
    (\bC \to \bC)
  \end{mathpar} 
  Without loss of generality, suppose that there exists some $n$ such that
  \begin{mathpar}
    \tit(\deno{M};(\bC \to \alpha);\mu)=n \and \tit(\deno{N};(\bC \to \alpha);\mu)\ne n\,.
  \end{mathpar}
  This means that we must have
  \begin{mathpar}
    \deno M;(\bC \to \alpha);\mu;\eta;\new_\bC;t_n \ne \bot
    \and
    \deno N;(\bC \to \alpha);\mu;\eta;\new_\bC;t_n = \bot
  \end{mathpar}
  in $\G$ (where $\eta$ is as defined in Definition \ref{DefTimeTaken}).

  $\G$ is enriched in algebraic cpos, so $\alpha$ is the least upper bound of its compact approximants.  
  It follows that there is some compact $\alpha'\subset \alpha$ such that
  \begin{mathpar}
    \deno M;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n \ne \bot
    \and
    \deno N;(\bC \to \alpha');\mu;\eta;\new_\bC;t_n = \bot\,.
  \end{mathpar}
  In other words:
  \begin{mathpar}
    \tit(\deno M;(\bC \to \alpha');\mu) = n\,;
    \and
    \tit(\deno N;(\bC \to \alpha');\mu) \ne n\,.
  \end{mathpar}
  Now the compact definability result for Idealized Algol \cite[17]{SamsonGuyIAActive} tells us that $\alpha'$ must be the denotation of some IA term $x\from T \ts C[x] \from \com \to \com$, which is therefore the denotation of $x\from T \ts C[x]\,\sleep \from \com$ in $\Kl_{R_\bC}$.
  So we get
  \begin{mathpar}
    \tit(\deno{C[M]\,\sleep}) = n\,;
    \and
    \tit(\deno{C[N]\,\sleep}) \ne n\,.
  \end{mathpar}
  By Theorem \ref{IaSleepComputationalAdequacy}, $C[M]\,\sleep\converges_n$ and $C[N]\,\sleep\not\converges_n$.  
  Therefore, $M$ and $N$ are observationally inequivalent in IA+$\sleep$.
\end{proof}

### 2019-03-27 Thesis/games.tex
Nightly commit.

@@
 \def\FEWFONTS{1}
+\def\THESIS{1}
 \input{../common/preamble}
+\usepackage{lua-visual-debug}
 
@@
 The first three are data types corresponding to the sets $\bC = \{a\}$, $\bB = \{\true,\false\}$ and $\bN = \{0,1,2,\cdots\}$.
-$\com$ takes the role of a command or void type; typically, although the return value of a function $T \to \com$ will not convey any information, the function will have useful side effects.
+$\com$ takes the role of a command or void type; typically, although the return value of a function $T \to \com$ will not convey any information, the function will have side effects that \emph{do} make a difference.
 
@@
   where $\epsilon$ is the empty sequence.
+  \label{ExEmptyGame}
 \end{example}
@@
 \subsection{Connectives on Games}
+\label{SecConnectives}
 
@@
   \end{itemize}
+  We extend this to arbitrary products $\prod_i A_i$ in the obvious way.
+  In particular, the product $1$ of the empty collection is the same as the empty game $I$ defined in Example \ref{ExEmptyGame}.
+  \label{DefProduct}
 \end{definition}
@@
 \subsection{Copycat strategies}
+\label{SecCopycat}
 
@@
   Let $A,B$ be games.  
-  Then a \emph{structural isomorphism} from $A$ to $B$ is a bijection $f\from M_A \to M_B$ such that $a\ts_A b$ if and only if $f(a)\ts_B f(b)$ and $*\ts_A a$ if and only if $*\ts_B f(a)$, and such that the plays of $B$ are precisely the plays of $A$, after applying the function $f$ pointwise to the moves (and keeping the justification indices as they are).
-
-  Given a structural isomorphism $f$ from $A$ to $B$, the \emph{copycat strategy} $\cc_f \from A \to B$ is given by
-  \[
-    \cc_f = \{s\in P_{A\implies B}^{\textit{even}} \suchthat\text{for all even-length $t\prefix s$, $t\vert_B=f^*(t\vert_A)$}\}\,,
-    \]
-  where $f^*$ denotes $f$ applied pointwise.
-\end{definition}
-
-\begin{proposition}
-  $\cc_f$ is an innocent strategy for $A\implies B$.  
-  Moreover, if $\sigma\from C\implies A$ is a strategy, then
-  \[
-    \sigma;\cc_f = \{[\id_{M_C},f]^*(s)\suchthat s\in\sigma\}\,,
-    \]
-  and if $\tau \from B \implies D$ is a strategy, then
-  \[
-    \cc_f;\tau = \{[f\inv,\id_{M_D}]^*(s)\suchthat s\in\tau\}\,.
+  Then a \emph{subset inclusion} of $A$ into $B$ is a partial injection $i\from M_A\hookrightarrow M_B$ such that
+  \begin{itemize}
+    \item if $i$ is defined at $a$ and $b$ then $*\ts_A a$ if and only if $*\ts_B i(a)$, and $a\ts_A b$ if and only if $i(a)\ts_B i(b)$;
+    \item $i(a)$ is defined for every move $a$ occurring in a play in $P_A$; and
+    \item $i_*(s)\in P_B$ for every $s\in P_A$.
+  \end{itemize}
+  Here, $i_*(s)$ means the function $i$ applied pointwise to the elements of the string $s$.
+
+  If $i$ is a subset incusion of $A$ into $B$, then we get an innocent strategy $\subs_i\from B \implies A$ defined by
+  \[
+    \subs_i = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=i_*(t\vert_A)$}\}\,.
+    \]
+  If $P_B=\{i_*(s)\suchthat s\in P_A\}$, then we call it a \emph{structural isomorphism}, and we write $\cc_i$ (`copycat') for $\subs_i$.
+\end{definition}
+
+\begin{proposition}
+  $\subs_i$ is an innocent strategy.
+
+  Moreover, if $\sigma\from C \implies B$ is a strategy, then
+  \[
+    \sigma;\subs_i = \{[\id_{M_C},i\inv]_*(s)\suchthat s\in\sigma,\,s\vert_B\in i_*(P_A)\}\,,
+    \]
+  where $i\inv\from M_B \pfun M_A$ is the canonical partial right-inverse to $i$, and if $\tau \from A \implies D$ is a strategy, then
+  \[
+    \subs_i;\tau = \{[i,\id_{M_D}]_*(s)\suchthat s\in\tau\}\,.
     \]
@@
 \begin{proof}
-  $\cc_f$ is clearly prefix-closed by definition.  
-  Suppose that $sab,sac\in\cc_f$; then $s\vert_B=f^*(s\vert_A)$ and $sab\vert_B=f^*(sab\vert_A)=f^*(s\vert_A)f^*(ab\vert_A)=s\vert_Bf^*(ab\vert_A)$.  
-  It follows that either $ab\vert_B=f^*(ab\vert_A)$, so either $a$ is a move in $A$ and $b=f(a)$ or $a$ is a move in $b$ and $a=f(b)$.  
-  Since the same applies to $c$, we have $b=c$.
-
-  This argument shows that $\cc_f$ is \emph{history-free} -- i.e., that its reply to an $O$-position is entirely determined by the last $O$-move -- and therefore it is certainly innocent.
-
-  Now let $\sigma\from C \implies A$ be a strategy.
-  Suppose that $\s\in\sigma\|\cc_f$.  
-  Then $\s\vert_{C,A}\in\sigma$ and $\s\vert_B=f^*(\s\vert_A)$.
-  It follows that $\s\vert_{C,B}=[\id_{M_C},f]^*(\s\vert_{C,A})$.
-
-  Conversely, given $s\in\sigma$, for each $P$-move $a$ in $s$ occurring in the component $A$, insert the move $f(a)$ immediately after it, and for each $O$-move $b$ in $s$ occurring in the component $A$, insert the move $f(b)$ immediately before it.
-  Let these extra moves in $B$ be justified according to the original moves in $A$.
-  Then the resulting sequence $\s$ is contained in $\sigma\|\cc_f$, and $\s\vert_{A,C}=[\id_{M_C},f]^*(s)$.
-
-  The case for composition in the other direction is exactly the same.
-\end{proof}
-
-An easy corollary of this fact is that composition of copycat strategies respects composition of the underlying structural isomorphisms.
+  $\subs_i$ is clearly prefix-closed by definition.  
+  Suppose that $sab,sac\in\subs_i$; then $s\vert_A=i_*(s\vert_B)$ and $sab\vert_A=i_*(sab\vert_B)$.  
+  It follows that $ab\vert_A=i_*(ab\vert_B)$, so either $a$ is a move in $A$ and $b=i(a)$ or $a$ is a move in $B$ and $a=i(b)$.  
+  Since the same applies to $c$, and since $i$ is injective, we have $b=c$.
+
+  This argument also shows that $\subs_i$ is \emph{history-free} -- i.e., that its reply to an $O$-position is entirely determined by the last $O$-move -- and therefore it is certainly innocent.
+
+  Now let $\sigma \from C \implies B$ be a strategy.  
+  Suppose that $\s\in\sigma\|\subs_i$.  
+  Then $\s\vert_{C,B}\in\sigma$ and $\s\vert_B=i_*(\s\vert_A)$; i.e., $\s\vert_{C,B}=[\id_{M_C},i]_*(\s\vert_{C,A})$, and therefore $\s\vert_{C,A}=[\id_{M_C},i]_*(\s\vert_{C,B})$, where $\s\vert_B\in i_*(P_A)$.
+
+  Conversely, given $s\in\sigma$, where $s\vert_B\in i_*(P_A)$, for each $P$-move $b=i(a)$ in $s$ occurring in the component $B$, insert the move $a$ immediately after it, and for each $O$-move $b'=i(a')$ in $s$ occurring in the component $B$, insert the move $a'$ immediately before it.
+  Let these extra moves in $B$ be justified according to the original moves in $A$, and let all initial moves in $B$ be justified by the initial moves in $A$ that occur immediately before them.
+  Then the resulting sequence $\s$ is contained in $\sigma\|\subs_i$, and $\s\vert_{A,C}=[\id_{M_C},i\inv]_*(s)$.
+
+  The case for composition in the other direction is similar.
+\end{proof}
+
+An easy corollary of this fact is that composition of copycat strategies respects composition of the underlying subset inclusions.
 
 \begin{corollary}
-  Let $f$ be a structural isomorphism from $A$ to $B$ and let $g$ be a structural isomorphism from $B$ to $C$.  
-  Then $g\circ f$ is a structural isomorphism from $A$ to $C$ and $\cc_{g\circ f}=\cc_f;\cc_g$.
+  Let $i$ be a subset inclusion from $A$ to $B$ and let $j$ be a subset inclusion from $B$ to $C$.  
+  Then $j\circ i$ is a subset inclusion from $A$ to $C$ and $\cc_{j\circ i}=\subs_j;\subs_i\from C \implies A$.
 \end{corollary}
@@
 
-In this setting, Proposition \ref{PropCopycat} tells us that structural isomorphism gives rise to an isomorphism in $\G$.
+In this setting, Proposition \ref{PropCopycat} tells us that a structural isomorphism gives rise to an isomorphism in $\G$.
 \begin{proposition}
@@
 \end{proposition}
-
-\subsection{Symmetric Monoidal Closed Structure of $\G$}
-
-We now claim that the tensor product connective $\tensor$ makes $\G$ into a symmetric monoidal closed category, with inner hom given by $\implies$.
+\begin{proof}
+  The underlying partial injection $f\from M_A \hookrightarrow M_B$ has an inverse partial injection $f\inv\from M_B \to M_A$, inducing a structural isomorphism from $B$ to $A$.  
+  Then Proposition \ref{PropCopycat} tells us that $\cc_f$ and $\cc_{f\inv}$ are inverses in $\G$.
+\end{proof}
+
+General subset inclusions are not, of course, isomorphisms, but we can still say something category-theoretic about them.
+
+\begin{proposition}
+  Let $i$ be a subset inclusion from a game $A$ to a game $B$.  
+  Then the strategy $\subs_i$ is an epimorphism from $B$ to $A$.
+  \label{PropSubsetInclusionEpic}
+\end{proposition}
+\begin{proof}
+  In fact, it is a split epimorphism: we can define a retract
+  \[
+    \ret_i = \{s\in P_{A\implies B}\suchthat\text{for all even-length $t\prefix s$, $t\vert_A=i_*(t\vert_B)$}\}\,.
+    \]
+  The same argument as in Proposition \ref{PropCopycat} tells us that this is indeed a strategy for $A\implies B$.
+  Note that although $\subs_i$ is always a total strategy (i.e., if $s\in\subs_i$ and $sa\in P_{B\implies A}$, then there is always $sab\in\subs_i$ for some $b$), the same is not in general true about $\ret_i$.
+
+  In any case, if $\s\in\ret_i\|\subs_i$, then $\s\vert_{A^L} = i_*(\s\vert_B) = \s\vert_{A^R}$, and the same is true of any even-length substring of $\s$, and so $\s\vert_{A,A}\in\id_A$.  
+  Conversely, given any $s\in \id_A$, we can form some $\s\in\ret_i\|\subs_i$ such that $\s\vert_{A,A}=s$ as in Proposition \ref{PropCopycat}.
+
+  We can also prove that $\subs_i$ is an epimorphism directly, which might be useful, for example, in a setting in which non-total strategies such as $\ret_i$ are disallowed.  
+  In this setting, let $\sigma,\tau\from A \implies C$ be strategies such that $\subs_i;\sigma=\subs_i;\tau$.  
+  Then, by Proposition \ref{PropCopycat}, we know that
+  \[
+    \{[i,\id_{M_C}]_*(s)\suchthat s\in\sigma\}
+    =
+    \{[i,\id_{M_C}]_*(s)\suchthat s\in\tau\}\,.
+    \]
+  Then, since the function $[i,\id_{M_D}]_* \from P_{A\implies C} \to P_{B\implies C}$ is an injection, we deduce that $\sigma=\tau$.
+\end{proof}
+
+\subsection{Tree Embeddings}
+
+We can generalize the subset inclusions of the previous section to \emph{tree embeddings}.  
+Tree embeddings are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
+A consequence of this is that while tree embeddings do give rise to strategies, these strategies are not in general innocent.
+
+\begin{definition}
+  Let $A,B$ be games.  
+  A \emph{tree embedding} from $A$ to $B$ is a length-preserving function $\phi\from P_A \hookrightarrow P_B$ such that for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$ and such that if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
+
+  Given a tree embedding $\phi$ from $A$ to $B$, we define a strategy $\tree_\phi\from B \implies A$ by
+  \[
+    \tree_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
+    \]
+\end{definition}
+\begin{example}
+  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree embedding from $A$ to $B$.
+\end{example}
+
+\begin{proposition}
+  $\tree_\phi$ is a strategy.
+
+  If $\phi$ is a tree embedding from $A$ to $B$ and $\psi$ is a tree embedding from $B$ to $C$, then $\psi\circ\phi$ is a tree embedding from $A$ to $C$ and $\tree_{\psi\circ\phi}=\tree_\psi;\tree_\phi$.
+  \label{PropTree}
+\end{proposition}
+\begin{proof}
+  $\tree_\phi$ is a prefix-closed subset of $P_{B\implies A}$ by definition.  
+  If $sab,sac\in\tree_\phi$, then we have $s\vert_B=\phi(s\vert_A)$ and $sab\vert_B=\phi(sab\vert_A)$.
+  Since $\phi$ is length-preserving, $s\vert_A$ and $s\vert_B$ must have the same length, and the same is true of $sab\vert_A$ and $sab\vert_B$.  
+  Therefore, either $a$ is a move in $A$ and $s\vert_Bb=\phi(s\vert_Aa)$ or $a$ is a move in $B$ and $s\vert_Ba=\phi(s\vert_Ab)$.  
+  The same applies to $c$: so either $s\vert_Bb=\phi(s\vert_Aa)=s\vert_Bc$ or $\phi(s\vert_Ab)=s\vert_Ba=\phi(s\vert_Ac)$.  
+  In either case, we have $b=c$.
+
+  Now suppose that $\phi$ is a tree embedding from $A$ to $B$ and that $\psi$ is a tree embedding from $B$ to $C$.  
+  Then $\psi\circ\phi$ certainly preserves length and the prefix relation.  
+  Let $\s\in\tree_\psi\|\tree_\phi$, and let $t\prefix \s\vert_{C,A}$ have even length.  
+  Let $\t$ be a prefix of $\s$ such that $\t\vert_{C,A}=t$.
+  Then, by the argument above, $\t\vert_{C,B}$ and $\t\vert_{B,A}$ have even length, and so $\t\vert_C=\psi(\t\vert_B)$ and $\t\vert_B=\phi(\t\vert_A)$.  
+  Therefore, $t\vert_C=(\psi\circ\phi)(t\vert_A)$.  
+  Since $t$ was arbitrary, this means that $\s\vert_{A,C}\in\tree_{\psi\circ\phi}$.
+
+  Conversely, suppose that $s\in\tree_{\psi\circ\phi}$: so $t\vert_C = \psi(\phi(t\vert_A))$ for all even-length $t\prefix s$.
+  By induction on the length of $s$, we build up a sequence $\s(s)\in\tree_\psi\|\tree_\phi$ such that $\s(s)\vert_{C,A}=s$.
+  \begin{itemize}
+    \item $\s(\epsilon) = \epsilon$.
+    \item Given a sequence $sab\in\tree_{\psi\circ\phi}$, we have $s\vert_C=\psi(\phi(s\vert_A))$.  
+      By our discussion above, we know that $sab\vert_A$ is one move longer than $s\vert_A$, so $\phi(sab\vert_A)=\phi(s\vert_A)c$ for some move $c$ in $B$, justified by some move in $B$.
+      Then we set $\s(sab)=\s(s)acb$, where the justifier of $c$ is as above.
+  \end{itemize}
+  It is clearly true that $\s(s)\vert_{C,A}=s$ for all sequences $s\in\tree_{\psi\circ\phi}$.
+
+  We claim that $\s(s)\in\tree_\psi\|\tree_\phi$ for all $s$.  
+  This is clearly true for the empty sequence; for $sab$, we have $\s(sab)\vert_{B,A} = \s(s)acb\vert_{B,A}$, where $\phi(sab\vert_A)=\phi(s\vert_A)c$.
+
+  By induction, $\s(s)\in\psi(\phi(s\vert_A))$, and so for all even-length $t\prefix \s(s)\vert_{B,A}$ we have $t\vert_B=\phi(t\vert_A)$, and for all even-length $u\prefix\s(s)\vert_{C,B}$ we have $u\vert_C=\psi(u\vert_B)$.
+  All we need to show is that $\s(s)acb\vert_B=\phi(\s(s)acb\vert_A)$ and that $\s(s)acb\vert_C=\psi(\s(s)acb\vert_B)$.  
+  Indeed, $\phi(\s(s)acb\vert_A)=\phi(sab\vert_A)=\phi(s\vert_A)c=\phi(\s(s)\vert_A)c=\s(s)\vert_Bc=\s(s)acb\vert_V$, and, in addition, we have that $\psi(\s(s)acb\vert_B) = \psi(\s(s)\vert_Bc) = \psi(\phi(\s(s)\vert_A)c) = \psi(\phi(sab\vert_A))=sab\vert_C=\s(s)acb\vert_C$.
+\end{proof}
+
+\begin{definition}
+  We say that a tree embedding $\phi$ is a \emph{tree isomorphism} if it is a bijection.
+\end{definition}
+
+\begin{proposition}
+  If $\phi$ is a tree isomorphism from a game $A$ to a game $B$, then $\tree_\phi$ is an isomorphism in $\G$.
+\end{proposition}
+\begin{proof}
+  If $\phi$ is a tree isomorphism, then its inverse $\phi\inv$ is also a tree isomorphism, and Proposition \ref{PropTree} tells us that $\tree_\phi$ and $\tree_{\phi\inv}$ are inverses in $\G$.
+\end{proof}
+
+\subsection{$\G$ as a Symmetric Monoidal Category}
+
+We now claim that the tensor product connective $\tensor$ makes $\G$ into a symmetric monoidal closed category, with internal hom given by $\implies$.
 
@@
   ii) If $s$ ends with a move in $C$ or $D$, then $\pv{s}^{(A\tensor C)\implies (B\tensor D)}=\pv{s\vert_{C,D}}^{C\implies D}$.
+  \label{LemTensorViewLemma}
 \end{lemma}
@@
   Suppose without loss of generality that $a$ is a move in $A$ or $B$.  
-  Then $\pv{sa}=\pv{sa\vert_{A,B}}$ and $\pv{ta}=\pv{ta\vert_{A,B}}$, and therefore $tab\vert_{A,B}\in\tau$ by innocence of $\tau$, and so $tab\in\sigma\tensor\tau$.  
+  Then $\pv{sa}=\pv{sa\vert_{A,B}}$ and $\pv{ta}=\pv{ta\vert_{A,B}}$ by Lemma \ref{LemTensorViewLemma}, and therefore $tab\vert_{A,B}\in\sigma$ by innocence of $\sigma$, and so $tab\in\sigma\tensor\tau$.
 \end{proof}
@@
 
-  Moreover, if $A',A,B',B$ are games, $f$ is a structural isomorphism from $A'$ to $A$ and $g$ is a structural isomorphism from $B'$ to $B$, then $\cc_f\tensor\cc_g = \cc_{[f,g]}$.
+  Moreover, if $A',A,B',B$ are games, $i$ is a subset inclusion from $A$ to $A'$ and $j$ is a structural isomorphism from $B$ to $B'$, then $\subs_i\tensor\subs_j = \subs_{[i,j]}$.
   In particular, if $A$ and $B$ are games, then $\id_A\tensor \id_B=\id_{A\tensor B}$.
+  \label{PropTensorProductIsFunctor}
 \end{proposition}
@@
 
-  For the second part, let $A',A,B',B$ be games, let $f$ be a structural isomorphism from $A'$ to $A$ and let $g$ be a structural isomorphism from $B'$ to $B$.  
+  For the second part, let $A',A,B',B$ be games, let $i$ be a structural isomorphism from $A$ to $A'$ and let $j$ be a structural isomorphism from $B$ to $B'$.  
+  Suppose that $s\in\subs_i\tensor \subs_j$.  
+  Then $s\vert_{A',A}\in\subs_i$ and $s\vert_{B',B}\in\subs_j$ -- so if $u\prefix s\vert_{A,A}$ has even length, then $u\vert_{A'}=i_*(u\vert_A)$, and if $v\prefix s\vert_{B,B}$ has even length, then $v\vert_{B'}=i_*(v\vert_B)$.
+  Suppose that $t\prefix s$ is of even length.  
+  Then, since only player $O$ swtiches between the $A',A$-component and the $B',B$-component, both $t\vert_{A',A}$ and $t\vert_{B',B}$ are of even length, it follows that $t\vert_{A',B'}=[i,j]_*(t\vert_{A,B})$.
+  Since $t$ was arbitrary, this means that $s\in \subs_{[i,j]}$.
+
+  Conversely, suppose that $s\in\subs_{[i,j]}$.  
+  Then for all even-length $t\prefix s$, $t\vert_{A'}=i_*(t\vert_{A})$ and $t\vert_{B'}=j_*(t\vert_{B})$.  
+  Since any play in $\sigma$ or in $\tau$ is itself a play of $\sigma\tensor\tau$, then if $u\prefix s\vert_{A',A}$ has even length, then $u\vert_{A'}=i_*(u\vert_{A})$, and if $v\prefix s\vert_{B',B}$, then $v\vert_{B'}=j_*(v\vert_{B})$.
+  It follows that $s\vert_{A',A}\in \subs_i$ and $s\vert_{B',B}\in\subs_j$, and therefore that $s\in \subs_i\tensor\subs_j$.  
+\end{proof}
+
+Now it is fairly clear that if $A,B,C$ are games, then we have structural isomorphisms
+\begin{mathpar}
+  (A \tensor B) \tensor C \cong A \tensor (B\tensor C)
+  \\
+  A \cong A \tensor I \and A \cong I \tensor A
+  \\
+  A \tensor B \cong B \tensor A\,,
+\end{mathpar}
+induced by the associators, unitors and symmetry of the category of sets with coproduct.
+We claim that these are natural transformations.
+
+\begin{proposition}
+  The families of morphisms
+  \begin{mathpar}
+    \cc_{\assoc_{M_A,M_B,M_C}} \from (A \tensor B) \tensor C \to A \tensor (B \tensor C)
+    \\
+    \cc_{\lunit_{M_A}} \from A \to I \tensor A \and \cc_{\runit_{M_A}} \from A \to A \tensor I
+    \\
+    \cc_{\sym{M_A,M_B}} \from A \tensor B \to B \tensor A
+  \end{mathpar}
+  are natural transformations in $\G$.
+  \label{PropCoherencesAreNatural}
+\end{proposition}
+\begin{proof}
+  We prove this for the associator; the other cases are similar.
+
+  Let $\sigma\from A' \implies A$, $\tau\from B' \implies B$, $\upsilon\from C' \implies C$ be strategies.  
+  By Proposition \ref{PropCopycat}, we have
+  \begin{IEEEeqnarray*}{Cl}
+    & ((\sigma\tensor\tau)\tensor\upsilon);\cc_{\assoc_{M_{A},M_{B},M_{C}}} \\
+    = & \{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s)\suchthat s\in (\sigma\tensor\tau)\tensor\upsilon\} \\
+    = & \left\{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s) \,\middle|\,\mbox{\pbox{\textwidth}{
+      $s\in P_{((A'\tensor B')\tensor C')\implies ((A \tensor B) \tensor C)}$\\
+      $s\vert_{A',A}\in\sigma$, $s\vert_{B',B}\in\tau$, $s\vert_{C',C}\in\upsilon$
+    }}\right\} \\
+    = & \{s\in P_{((A'\tensor B') \tensor C') \implies (A \tensor (B \tensor C))} \suchthat s\vert_{A',A}\in\sigma,s\vert_{B',B}\in\tau,s\vert_{C',C}\in\upsilon\} \\
+    = & \left\{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s) \,\middle|\,\mbox{\pbox{\textwidth}{
+      $s\in P_{(A'\tensor (B'\tensor C'))\implies (A \tensor (B \tensor C))}$\\
+      $s\vert_{A',A}\in\sigma$, $s\vert_{B',B}\in\tau$, $s\vert_{C',C}\in\upsilon$
+    }}\right\} \\
+    = & \{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s)\suchthat s\in \sigma\tensor (\tau\tensor \upsilon)\} \\
+    = & \cc_{\assoc_{M_{A'},M_{B'},M_{C'}}};(\sigma\tensor(\tau\tensor\upsilon))\,.\hspace{1pt plus 1fill} \qedhere
+  \end{IEEEeqnarray*}
+\end{proof}
+
+Then, by Proposition \ref{PropCopycat} again, these natural transformations satisfy the same coherence diagrams (pentagon, triangles, hexagon etc.) satisfied by the original associators, unitors and symmetry in $(\Set,+)$.
+
+It follows that $\tensor$ makes $\G$ into a symmetric monoidal category.
+
+\subsection{$\G$ as a Symmetric Monoidal Closed Category}
+
+\begin{definition}
+  Let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $C\implies D$.  
+  Then we define a strategy $\sigma\implies \tau\from (B\implies C) \implies (A\implies D)$ by
+  \[
+    \sigma\implies \tau = \{s\in P_{(B\implies C) \implies (A \implies D)}\suchthat \text{$s\vert_{A,B}\in\sigma$, $s\vert_{C,D}\in\tau$}\}\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  $\sigma\implies\tau$ is a strategy for $(B\implies C) \implies (A \implies D)$.
+  \label{PropImpliesWellDefined}
+\end{proposition}
+\begin{proof}
+  $\sigma\implies\tau$ is certainly a prefix-closed subset of $P_{(B\implies C)\implies (A \implies D)}^{\textit{even}}$.
+
+  We examine the sign configuration of a play in $(B\implies C)\implies (A\implies D)$, using Lemma \ref{LemCompositionLemma}.  
+  Since we must avoid the configuration $OP$ in either $B\implies C$, $A\implies D$ or in $(B\implies C)\implies (A\implies D)$, we arrive at the following list of possibilities.
+  \scriptsize
+  \[
+\arraycolsep=2.7pt\def\arraystretch{1.5}
+    \begin{array}{cccc|cc|c}
+      \lambda_B^{OP}(s\vert_B) & \lambda_C^{OP}(s\vert_C) & \lambda_A^{OP}(s\vert_A) & \lambda_D^{OP}(s\vert_D) & \lambda_{B\implies C}^{OP}(s\vert_{B,C}) & \lambda_{A\implies D}^{OP}(s\vert_{A,D}) & \lambda_{(B\implies C)\implies (A\implies D)}^{OP}(s) \\
+      \hline
+      P & O & P & O & O & O & P \\
+      P & P & P & O & P & O & O \\
+      O & O & P & O & P & O & O \\
+      P & P & P & P & P & P & P \\
+      O & O & O & O & P & P & P \\
+      P & P & O & O & P & P & P \\
+      O & O & P & P & P & P & P
+    \end{array}
+    \]
+  \normalsize
+  If $s\in\sigma\implies\tau$, then we can immediately discount the last two of these possibilities, since one includes the illegal configuration $OP$ in $A\implies B$, and the other includes the illegal configuration $OP$ in $B\implies D$.
+
+  By examining the remaining possibilities, we arrive at the conclusion that any $O$-position in configuration $PPPO$ constrains player $P$ to play in $C$ (to reach configuration $POPO$) or to play in $D$ (to reach configuration $PPPP$), and that any $O$-position in configuration $OOPO$ constrains player $P$ to play in $A$ (to reach configuration $OOOO$) or to play in $C$ (to reach configuration $POPO$).
+
+  Now suppose that $sab,sac\in\sigma\implies\tau$.  
+  Then, by our above analysis, $b$ and $c$ must either both take place in the $B,A$-component, in which case $b = c$ by determinism of $\sigma$, or both in the $C,D$-component, in which case $b = c$ by determinism of $\tau$.
+\end{proof}
+
+To prove that $\sigma\implies\tau$ is innocent if $\sigma$ and $\tau$ are, we need a lemma analogous to Lemma \ref{LemTensorViewLemma}.
+
+\begin{lemma}
+  Let $s\in \sigma\implies \tau$.
+
+  i) If $s$ ends with a move in $A$ or $B$, then $\pv{s}^{(B\implies C) \implies (A\implies D)} = \pv{s\vert_{A,B}}^{A\implies B}$.
+
+  ii) If $s$ ends with a move in $C$ or $D$, then $\pv{s}^{(B\implies C) \implies (A\implies D)} = \pv{s\vert_{C,D}}^{C\implies D}$.
+  \label{LemImpliesViewLemma}
+\end{lemma}
+\begin{proof}
+  Exactly the same as in Lemma \ref{LemTensorViewLemma}, using the analysis from the proof of Proposition \ref{PropImpliesWellDefined} to show that player $P$ only switches moves between $A$ and $B$, and between $C$ and $D$, in $\sigma\implies\tau$.
+\end{proof}
+
+\begin{proposition}
+  Let $\sigma\from A \implies B$, $\tau\from C\implies D$ be innocent strategies.  
+  Then $\sigma\implies\tau$ is innocent.
+\end{proposition}
+\begin{proof}
+  Suppose $sab,t\in\sigma\implies\tau$ such that $ta\in P_{(B\implies C)\implies (A \implies D)}$ and $\pv{sa}=\pv{ta}$.  
+  Suppose without loss of generality that $a$ is a move in $A$ or $B$.  
+  Then $\pv{sa}=\pv{sa\vert_{A,B}}$ and $\pv{ta}=\pv{ta\vert_{A,B}}$ by Lemma \ref{LemImpliesViewLemma}, and therefore $tab\vert_{A,B}\in\sigma$ by innocence of $\sigma$, and so $tab\in\sigma\implies\tau$.
+\end{proof}
+
+We now need to prove that $\implies$ is a functor $\oppcat\G\times\G\to\G$.
+
+\begin{proposition}
+  Let $\sigma'\from A''\implies A'$, $\sigma\from A'\implies A$, $\tau'\from B'' \implies B'$ and $\tau\from B'\implies B$ be strategies.  
+  Then $(\sigma\implies\tau');(\sigma'\implies\tau) = (\sigma';\sigma)\implies(\tau';\tau)$.
+
+  Moreover, if $A',A,B',B$ are games, $f$ is a structural isomorphism from $A'$ to $A$ and $g$ is a structural isomorphism from $B'$ to $B$, then $\cc_f\implies\cc_g = \cc_{[f\inv,g]}$.
+  In particular, if $A,B$ are games than $\id_A\implies\id_B=\id_{A\implies B}$.
+\end{proposition}
+\begin{proof}
+  As in Proposition \ref{PropTensorProductIsFunctor}.
+\end{proof}
+
+Now it is easy to see that the associator $\assoc_{M_A,M_B,M_C}$ is a structural isomorphism from $(A\tensor B) \implies C$ to $A\implies (B\implies C)$, so it induces a copycat isomorphism $\Lambda_{A,B,C}=\cc_{\assoc_{M_A,M_B,M_C}} \from (A\tensor B) \implies C \to A \implies (B\implies C)$.
+
+\begin{proposition}
+  $\Lambda_{A,B,C}$ is natural in $A,B,C$.
+\end{proposition}
+\begin{proof}
+  The same argument as in Proposition \ref{PropCoherencesAreNatural}.
+\end{proof}
+
+We have proved the following.
+
+\begin{theorem}
+  $\G$ is a symmetric monoidal closed category, with tensor product given by $\tensor$ and internal hom given by $\implies$.
+\end{theorem}
+
+\subsection{Products in $\G$}
+
+\begin{proposition}
+  Given some family $A_i$ of games, the game $\prod_i A_i$, as defined in Definition \ref{DefProduct}, is the category-theoretic product of the $A_i$.
+  \label{PropProductOfGames}
+\end{proposition}
+\begin{proof}
+  We have natural injections $\inj_j \from M_{A_j} \hookrightarrow M_{\prod_i A_i}$ giving rise to subset inclusions.  
+  Then our projections are given by the morphisms 
+  \[
+    \pr_j \coloneqq \subs_{\inj_j}\from \prod_i A_i \to A_j\,.
+    \]
+  Now suppose we have some game $B$, and strategies $\sigma_i \from B \implies A_i$ for each $i$.
+  Define a strategy
+  \[
+    \langle \sigma_i \rangle = \bigcup_i [\id_{M_B},\inj_i]_*(\sigma_i)\,.
+    \]
+  We claim that this is indeed a strategy for $B \implies \prod_i A_i$.
+  Indeed, it is certainly a prefix-closed subset of $P_{C\implies\prod_i A_i}$.
+
+  Moreover, if $sab,sac\in\langle \sigma_i \rangle$, then there is some unique $j$ such that $a$ comes from a move in $A_j$, and therefore $sab,sac$ are both plays in $\sigma_j$, so $b=c$.
+
+  Next, we claim that $\langle\sigma_i\rangle;\pr_j = \sigma_j$.  
+  Indeed, we have
+  \begin{IEEEeqnarray*}{rCl?u}
+    \langle\sigma_i\rangle;\pr_j & = & \langle\sigma_i\rangle;\subs_{\inj_j} \\
+    & = & \{[\id_{M_B},\inj_j\inv]_*(s)\suchthat s\in\langle\sigma_i\rangle,\,s\vert_{\prod_iAi}\in(\inj_j)_*(P_{A_j})\} & \textit{Prop. \ref{PropCopycat}} \\
+    & = & \sigma_j\,.
+  \end{IEEEeqnarray*}
+  Lastly, suppose $\tau\from B\implies\prod_iA_i$ is a strategy such that $\tau;\pr_j=\sigma_j$ for each $j$.
+  We claim that $\tau=\langle\sigma_i\rangle$.
+  Indeed, by the argument above, we must have
+  \[
+    \{[\id_{M_B},\inj_j\inv]_*(s)\suchthat s\in\tau,\,s\vert_{\prod_iA_i}\in(\inj_j)_*(P_{A_j})\} = \sigma_j
+    \]
+  for each $j$.
+  Suppose that $s\in\tau$.  
+  Then $s\vert_{\prod_iA_i}\in(\inj_j)_*(P_{A_j})$ for some $j$, by the definition of $\prod_iA_i$.  
+  Therefore, $s\in[\id_{M_B},\inj_j]_*(\sigma_j)$.
+
+  Conversely, let $t\in \sigma_j$.  
+  By the above equation, we know that there is some $s\in\tau$ such that $s\vert_{\prod_iA_i}\in(\inj_j)_*(P_{A_j})$ and $[\id_{M_B},\inj_j\inv]_*(s)=t$.  
+  It follows that $[\id_{M_B},\inj_j]_*(t)=s\in\tau$.
+\end{proof}
+
+An examination of the definitions tells us that
+\begin{proposition}
+  Let $A_i,B$ be games and let $\phi_i$ be tree embeddings from $A_i$ to $B$.  
+  Then $\langle \tree_{\phi_i} \rangle = \tree_\phi$, where $\phi$ is the tree embeddings from $\prod_iA_i$ to $B$ given by
+  \[
+    \phi(s) = \begin{cases}
+      \epsilon & \text{if $s=\epsilon$} \\
+      \phi_i(s\vert_{A_i}) & \text{if $s$ starts with a move from $A_i$}
+    \end{cases}
+    \]
+  \label{PropProductOfTreeEmbeddings}
+\end{proposition}
+\begin{proof}
+  The only thing we really need to check is that this is indeed a tree embedding.  
+  Let $sb,sc$ be positions in $\prod_iA_i$, where $b,c$ are $P$-moves.
+  Then $sb,sc$ must start with the same move, so if $\phi(sb)=\phi(sc)$ then we have $\phi_i(sb)=\phi_i(sc)$ for some $i$ and therefore $b=c$.
+\end{proof}
+
+Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and there is no version of Proposition \ref{PropProductOfTreeEmbeddings} that works for subset inclusion strategies.
+Of course, since a subset inclusion is a special case of a tree embedding, then $\langle \subs_i\rangle$ is always a tree embedding strategy.
+
+\subsection{Sequoidal categories}
+
+We have now given the category-theoretic properties of all the connectives from Section \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
+
+We would like to say that $\blank\sequoid\blank$ is a functor from $\G \times \G \to \G$, as is the case with the tensor product $\blank\tensor\blank$.  
+However, this does not quite work: given strategies $\sigma\from A \implies B$ and $\tau\from C \implies D$, we may not get a well-formed strategy for $(A \sequoid C) \implies (B \sequoid D)$ by `playing according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $C$ and $D$'.
+The reason is that the constraint that player $O$ plays in $B$ before $D$ is not strong enough to force player $P$ to play in $A$ before $C$; indeed, suppose that $\sigma$ tells player $P$ to respond to an initial move in $B$ with another move in $B$.
+Suppose that player $O$ then decides to make a move in $D$.  
+If $\tau$ tells player $P$ to respond to this move in $D$ with a move in $C$, then she will be stuck, unable to play this move because no move has yet been played in $A$.
+
+We can fix this problem by imposing some constraints on the strategies $\sigma$ and $\tau$.  
+The problem occurs when player $O$'s initial move in $B$ is not reflected by an initial move by player $P$ in $A$; therefore, if $\sigma$ is such that player $P$ always responds to the initial move in $B$ with a move in $A$, then we can form a strategy $\sigma\sequoid\tau$ for $(A\sequoid C)\implies (B\sequoid D)$.
+Moreover, this strategy $\sigma\sequoid\tau$ will inherit this property that the first move on the right is always replied to by a move on the left.
+
+\begin{definition}
+  Let $A,B$ be games.  
+  A \emph{strict morphism} from $A$ to $B$ is a strategy $\sigma$ for $A\implies B$ such that any player $P$ response to an opening move in $B$ is a move in $A$; i.e., such that if $b$ is an initial $O$-move in $B$ and $ba\in\sigma$, then $a$ is a move in $A$.
+\end{definition}
+
+We will call such a $\sigma$ a \emph{strict strategy} for $A\implies B$, although this is a slight abuse of language, since the definition depends on the constituent games $A$ and $B$, which may not be recoverable from $A\implies B$.
+
+It is clear that the composition of strict morphisms is again a strict morphism , as is any morphism of the form $\subs_i$, and so we get a wide subcategory $\G_s$ of $\G$ whose objects are games and where the morphisms are the strict strategies.
+We then have a natural inclusion functor $J\from \G_s\to \G$.
+
+\begin{definition}
+  Given games $A,B,C,D$, a strict morphism $\sigma\from A \implies B$ and a strategy $\tau\from C\implies D$, we define a strict morphism $\sigma\sequoid\tau\from (A \sequoid C)\implies (B \sequoid D)$ by
+  \[
+    \sigma\sequoid\tau = \{s\in P_{(A\sequoid C)\implies (B\sequoid D)}\suchthat s\vert_{A,B}\in\sigma,\,s\vert_{C,D}\in\tau\}\,.
+    \]
+  \label{DefSequoidOfStrategies}
+\end{definition}
+
+\begin{proposition}
+  $\sigma\sequoid\tau$ is a strategy.  
+\end{proposition}
+\begin{proof}
+  $\sigma\sequoid\tau$ is certainly a prefix-closed subset of $P_{(A\sequoid C)\implies (B\sequoid D)}$.  
+  Moreover, if $sab,sac\in\sigma\sequoid\tau$, then $sab,sac\in\sigma\tensor\tau$, so $b=c$.  
+\end{proof}
+
+Of course, $P_{A\sequoid B}$ is a subset of $P_{A\tensor B}$, which means that the identity function $M_A + M_B \to M_A + M_B$ gives us a subset inclusion from $A \sequoid B$ to $A \tensor B$, and hence a strategy $\subs_{\id_{M_A+M_B}}$ for $A\tensor B \implies A \sequoid B$, which we shall refer to as $\wk_{A,B}$.
+
+\begin{proposition}
+  Let $A,B,C,D$ be games, let $\sigma\from A \implies B$ be a strict strategy and let $\tau\from C \implies D$ be a strategy.  
+  Then the following diagram commutes.
+  \[
+    \begin{tikzcd}
+      A \tensor C \arrow[r, "\sigma\tensor\tau"] \arrow[d, "{\wk_{A,C}}"']
+        & B \tensor D \arrow[d, "{\wk_{B,D}}"] \\
+      A \sequoid C \arrow[r, "\sigma\sequoid\tau"]
+        & B \sequoid D
+    \end{tikzcd}
+    \]
+  \label{PropWkCommutativeDiagram}
+\end{proposition}
+\begin{proof}
+  By Proposition \ref{PropCopycat} and the definition of $\wk$, we know that
+  \begin{IEEEeqnarray*}{rCl}
+    \sigma\tensor\tau;\wk_{B,D} & = & \{s\in \sigma\tensor\tau,\,s\vert_{B,D}\in P_{B\sequoid D}\}
+    \\
+    \wk_{A,C};\sigma\sequoid\tau & = & \sigma\sequoid\tau\,,
+  \end{IEEEeqnarray*}
+  as sets of plays.
+
+  Now we know that $\sigma\sequoid\tau = \{s\in\sigma\tensor\tau\suchthat s\in P_{(A\sequoid C)\implies (B\sequoid D)}\}$, so it suffices to show that if $s\in\sigma\tensor\tau$ is such that $s\vert_{B,D}\in P_{B\sequoid D}$ then $s\in P_{(A\sequoid C)\implies (B\sequoid D)}$.
+
+  Indeed, if $s\vert_{B,D}\in P_{B\sequoid D}$ then $s$ begins with an initial $O$-move in $B$.  
+  Then, \emph{since $\sigma$ is strict}, the next move in $s$ must be a move in $A$, and therefore $s\vert_{A,C}$ begins with a move in $A$.
+  Since we also have $s\vert_{A,C}\in P_{A\tensor C}$, we must have that $s\vert_{A,C}\in P_{A\sequoid C}$.
+\end{proof}
+\begin{remark}
+  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definitionk \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.
+  But such a strategy would not satisfy the conclusion of Proposition \ref{PropWkCommutativeDiagram}, since $\sigma\tensor\tau;\wk_{B,D}$ would contain these extra plays where $\wk_{A,C};\sigma\sequoid\tau$ had `given up'.
+\end{remark}
+\begin{remark}
+  Of course, we would \emph{like} to restate Proposition \ref{PropWkCommutativeDiagram} by saying that $\wk$ is some sort of natural transformation, but that doesn't make sense until we've shown that $\blank\sequoid\blank$ is a functor.
+\end{remark}
+
+\begin{proposition}
+  If we have strict strategies $\sigma'\from A'' \implies A'$ and $\sigma\from A' \implies A$, and strategies $\tau' \from B'' \implies B'$ and $\tau \from B' \implies B$, then we have
+  \[
+    (\sigma'\sequoid\tau');(\sigma\sequoid\tau) = (\sigma';\sigma)\sequoid(\tau';\tau)\,.
+    \]
+  If $A',A,B',B$ are games, $i$ is a subset inclusion from $A$ into $A'$ and $j$ is a subset inclusion from $B$ into $B'$, then
+  \[
+    \subs_i\sequoid\subs_j = \subs_{[i,j]}\from A'\sequoid B' \implies A \sequoid B\,.
+    \]
+  In particular, if $A,B$ are games, then $\id_A\sequoid\id_B=\id_{A\sequoid B}$.
+  \label{PropSequoidIsFunctor}
+\end{proposition}
+\begin{proof}
+  Let $A'',A',A,B'',B',B$ and $\sigma',\sigma,\tau',\tau$ be as above.
+
+  We have
+  \begin{IEEEeqnarray*}{rCl?u}
+    \wk_{A'',B''};(\sigma'\sequoid\tau');(\sigma\sequoid\tau) & = & (\sigma'\tensor\tau');\wk_{A',B'};(\sigma\sequoid\tau) & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
+    & = & (\sigma'\tensor\tau');(\sigma\tensor\tau);\wk_{A,B} & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
+    & = & ((\sigma';\sigma)\tensor(\tau';\tau));\wk_{A,B} & \textit{Prop. \ref{PropTensorProductIsFunctor}} \\
+    & = & \wk_{A'',B''};((\sigma';\sigma)\sequoid(\tau';\tau))\,. & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
+  \end{IEEEeqnarray*}
+  By Proposition \ref{PropSubsetInclusionEpic}, $\wk_{A'',B''}$ is an epimorphism, and therefore we have that
+  \[
+    (\sigma'\sequoid\tau');(\sigma\sequoid\tau) = (\sigma';\sigma)\sequoid(\tau';\tau)\,.
+    \]
+
+  Now let $A',A,B',B$ be games, let $i$ be a subset inclusion from $A$ into $A'$ and let $j$ be a subset inclusion from $B$ into $B'$.  
+  Then, since subset inclusion strategies are automatically strict, we have
+  \begin{IEEEeqnarray*}{rCl?u}
+    \wk_{A',B'};(\subs_i\sequoid\subs_j) & = & (\subs_i\tensor\subs_j);\wk_{A,B} & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
+    & = & \subs_{[i,j]};\wk_{A,B} & \textit{Prop. \ref{PropTensorProductIsFunctor}} \\
+    & = & \subs_{[i,j]} & \textit{Prop. \ref{PropCopycat}} \\
+    & = & \wk_{A',B'};\subs_{[i,j]}\,. & \textit{Prop. \ref{PropCopycat}} \\
+  \end{IEEEeqnarray*}
+  As before, we know from Proposition \ref{PropSubsetInclusionEpic} that $\wk_{A',B'}$ is an epimorphism, and so
+  \[
+    \subs_i\sequoid\subs_j = \subs_{[i,j]}\,.\qedhere
+    \]
+\end{proof}
+
+Proposition \ref{PropSequoidIsFunctor} tells us that $\blank\sequoid\blank$ is a functor $\G_s\times\G\to \G$.  
+As before, write $J$ for the inclusion functor $\G_s\hookrightarrow\G$.
+Then we can restate Proposition \ref{PropWkCommutativeDiagram} in a more \emph{natural} way.
+
+\begin{proposition}
+  $\wk_{A,B}$ is a natural transformation $JA \tensor B \to J(A \sequoid B)$.
+  \label{PropWkNatural}
+\end{proposition}
+
+We have some additional structure on the $\tensor$ and $\sequoid$ operators.  
+By inspecting the definitions that if $A,X,Y$ are games then the associator $\assoc_{M_A,M_X,M_Y}$ and unitor $\runit_{M_A}$ in $(\Set,+)$ give rise to structural isomorphisms
+\begin{mathpar}
+  (A \sequoid X) \sequoid Y \cong A \sequoid (X \tensor Y)
+  \and
+  A \cong A \sequoid I\,.
+\end{mathpar}
+Indeed, in the first case, both games are the game in which $A$, $X$ and $Y$ are played in parallel, but where the first move must take place in $A$.  
+In the second case, we have $A\sequoid I=A\tensor I$, because there are no moves in $I$ anyway, and the copycat morphism induced from the right unitor in $(\Set,+)$ is the same strategy as the right unitor $A \toisom A \tensor I$.
+
+We formalize the structure we have uncovered so far in the concept of a \emph{sequoidal category}.
+
+\begin{definition}
+  A \emph{sequoidal category} $\C$ is given by
+  \begin{itemize}
+    \item a monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,\lunit,\runit$);
+    \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
+      \begin{mathpar}
+        \passoc_{a,x,y}\from (a \sequoid x) \sequoid y \toisom a \sequoid (x \tensor y)
+        \and
+        \run_a \from a \toisom a \sequoid I
+      \end{mathpar}
+      that make the diagrams
+      \begin{mathpar}
+        \begin{tikzcd}[column sep=36pt]
+          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}"] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
+            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}"]
+              & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
+          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}"]
+            & a \sequoid (x \tensor (y \tensor z))
+              &
+        \end{tikzcd}
+        \and
+        \begin{tikzcd}
+          a \sequoid x \arrow[r, "{a \sequoid \lunit_x}"] \arrow[d, "\run_a \sequoid x"']
+            & a \sequoid (I \tensor x) \\
+          (a \sequoid I) \sequoid x \arrow[ur, "{\passoc_{a,I,x}}"']
+            &
+        \end{tikzcd}
+        \and
+        \begin{tikzcd}
+          a \sequoid x \arrow[r, "{a \sequoid \runit_x}"] \arrow[d, "\run_{a \sequoid x}"']
+            & a \sequoid (x \tensor I) \\
+          (a \sequoid x) \sequoid I \arrow[ur, "{\passoc_{a,x,I}}"']
+            &
+        \end{tikzcd}
+      \end{mathpar}
+      commute; and
+    \item a lax morphism of actions from $\blank\sequoid\blank$ to the right tensor multiplication action $\blank\tensor\blank$ of $\C$ on itself; i.e., a functor $J\from \C_s \to \C$ and a natural transformation $\wk_{a,x} \from Ja \tensor x \to J(a \sequoid x)$ that makes the following diagrams commute.
+      \begin{mathpar}
+        \begin{tikzcd}[column sep=30pt]
+          (Ja \tensor x) \tensor y \arrow[r, "{\wk_{a,x}\tensor y}"] \arrow[d, "{\assoc_{Ja,x,y}}"'] & J(a \sequoid x) \tensor y \arrow[r, "{\wk_{a\sequoid x,y}}"]
+              & J((a \sequoid x) \sequoid y) \arrow[dl, "{J\passoc_{a,x,y}}"] \\
+          Ja \tensor (x \tensor y) \arrow[r, "{\wk_{a,x\tensor y}}"]
+            & J(a \sequoid (x \tensor y))
+              &
+        \end{tikzcd}
+        \and
+        \begin{tikzcd}
+          Ja \arrow[r, "J\run_a"] \arrow[d, "\runit_{Ja}"']
+            & J(a \sequoid I) \\
+          Ja \tensor I \arrow[ur, "{\wk_{a,I}}"']
+            &
+        \end{tikzcd}
+      \end{mathpar}
+  \end{itemize}
+  \label{DefSequoidalCategory}
+\end{definition}
+\begin{remark}
+  The definitions of \emph{lax action} can be found at the start of Section \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
+  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Section \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.
+  A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
+\end{remark}
+
+\begin{proposition}
+  The monoidal category $\G$, together with the category $\G_s$, the natural transformations
+  \begin{mathpar}
+    \passoc_{A,X,Y} = \cc_{\assoc_{M_A,M_X,M_Y}} \from (A \sequoid X) \sequoid Y \toisom A \sequoid (X \tensor Y)
+    \and
+    \run_A = \cc_{\runit_{M_A}} \from A \toisom A \sequoid I\,,
+  \end{mathpar}
+  the inclusion functor $J\from \G_s \to G$ and the natural transformation
+  \begin{mathpar}
+    \wk_{A,X}=\subs_{j} \from JA \tensor X = A \tensor X \to A \sequoid X = J(A \sequoid X)
+  \end{mathpar}
+  form a sequoidal category.
+\end{proposition}
+\begin{proof}
+  We have shown most of this already; all that remains is to show that $\passoc$ and $\run$ are natural transformations and that the five diagrams in Definition \ref{DefSequoidalCategory} commute.
+
+  Let us start with the diagrams.  
+  By Proposition \ref{PropCopycat}, commutativity of these diagrams follows from commutativity of the diagrams formed from the corresponding subset inclusion functions in $\Set$.  
+  For example, to show that the first diagram commutes in $\G$, we must show that the following diagram commutes in $\Set$.
+  \scriptsize
+  \[
+    \begin{tikzcd}[column sep=19pt, row sep=30pt]
+      ((M_A + M_X) + M_Y) + M_Z \arrow[r, "{[\assoc_{M_A,M_X,M_Y},\id_{M_Z}]}" yshift=3pt] \arrow[d, "{\assoc_{M_A+M_X,M_Y,Z}}" description]
+        & (M_A + (M_X + M_Y)) + M_Z \arrow[r, "{\assoc_{M_A,M_X+M_Y,M_Z}}" yshift=3pt]
+          & M_A + ((M_X + M_Y) + M_Z) \arrow[dl, "{[\id_{M_A},\assoc_{M_X,M_Y,M_Z}]}"] \\
+      (M_A + M_X) + (M_Y + M_Z) \arrow[r, "{\assoc_{M_A,M_X,M_Y+M_Z}}" yshift=3pt]
+        & M_A + (M_X + (M_Y + M_Z))
+          &
+    \end{tikzcd}
+    \]
+  \normalsize
+  This diagram is, of course, none other than the pentagram diagram for the coproduct $+$ in $\Set$.  
+  Similarly, the second and third diagrams in Definition \ref{DefSequoidalCategory} reduce in this case to the triangle diagrams for the coproduct $+$ in $\Set$.
+
+  For the fourth diagram in Definition \ref{DefSequoidalCategory}, since $\wk$ is a subset inclusion strategy induced from an identity map, Proposition \ref{PropCopycat} tells us that both arms of the diagram are the strategy induced by the subset inclusion $\assoc_{M_A,M_X,M_Y}\from (M_A + M_X) + M_Y \to M_A + (M_X + M_Y)$ from $(A \tensor X) \tensor Y$ to $A \sequoid (X \tensor Y)$.
+  Similarly, both arms of the last diagram in Definition \ref{DefSequoidalCategory} are the strategies induced by the subset inclusion $\runit_{M_A} \from M_A \to M_A + \emptyset$ from $A$ to $A \sequoid I$.
+
+  It now remains only to show that $\passoc$ and $\run$ are natural transformations.  
+  For $\passoc$, suppose that $A',X',Y',A,X,Y$ are games, that $\sigma\from A'\implies A$ is a strict strategy and that $\tau\from B'\implies B,\upsilon\from C'\implies C$ are strategies.  
+  Then we need to show that the following diagram commutes.
+  \[
+    \begin{tikzcd}[column sep=50pt]
+      (A' \sequoid X') \sequoid Y' \arrow[r, "{\passoc_{A',X',Y'}}"] \arrow[d, "(\sigma\sequoid\tau)\sequoid\upsilon"']
+        & A' \sequoid (X' \tensor Y') \arrow[d, "\sigma\sequoid (\tau\tensor\upsilon)"] \\
+      (A \sequoid X) \sequoid Y \arrow[r, "{\passoc_{A,X,Y}}"]
+        & A \sequoid (X \tensor Y)
+    \end{tikzcd}
+    \]
+  Indeed, we have
+  \begin{IEEEeqnarray*}{rCl?u}
+    && (\wk_{A',X'}\tensor Y');\wk_{A'\sequoid X',Y'};\passoc_{A',X',Y'};(\sigma\sequoid(\tau\tensor\upsilon)) \\
+    & = & \assoc_{A',X',Y'};\wk_{A',X'\tensor Y'};(\sigma\sequoid(\tau\tensor\upsilon)) & (see above) \\
+    & = & \assoc_{A',X',Y'};(\sigma\tensor(\tau\tensor\upsilon));\wk_{A,X\tensor Y} & \textit{Prop. \ref{PropWkNatural}} \\
+    & = & ((\sigma\tensor\tau)\tensor\upsilon);\assoc_{A,X,Y};\wk_{A,X\tensor Y} & \textit{Prop. \ref{PropCoherencesAreNatural}} \\
+    & = & ((\sigma\tensor\tau)\tensor\upsilon);(\wk_{A,X}\tensor Y);\wk_{A\sequoid X,Y};\passoc_{A,X,Y} & (see above) \\
+    & = & (\wk_{A',X'}\tensor Y');((\sigma\sequoid\tau)\tensor\upsilon);\wk_{A\sequoid X,Y};\passoc_{A,X,Y} & \textit{Prop. \ref{PropWkNatural}} \\
+    & = & (\wk_{A',X'}\tensor Y');\wk_{A'\sequoid X',Y'};((\sigma\sequoid\tau)\sequoid\upsilon);\passoc_{A,X,Y}\,. & \textit{Prop. \ref{PropWkNatural}}
+  \end{IEEEeqnarray*}
+  Now observe that $\wk_{A',X'}\tensor Y=\subs_{[\id_{M_{A'}+M_{X'}},\id_{M_{Y'}}]}$ by Proposition \ref{PropTensorProductIsFunctor}, so it is an epimorphism by Proposition \ref{PropSubsetInclusionEpic}.
+  Proposition \ref{PropSubsetInclusionEpic} also tells us that $\wk_{A'\sequoid X',Y'}$ is an epimorphism.  
+  Therefore, we have
+  \[
+    \passoc_{A',X',Y'};(\sigma\sequoid(\tau\tensor\upsilon)) = ((\sigma\sequoid\tau)\sequoid\upsilon);\passoc_{A,X,Y}
+    \]
+  for any $A',X',Y',A,X,Y,\sigma,\tau,\upsilon$ as above.  
+  It follows that $\passoc$ is a natural transformation.
+
+  The proof that $\run$ is a natural transformation is similar.  
+  Let $A',A$ be games and let $\sigma\from A'\implies A$ be a strict strategy.  
+  We need to show that the following diagram commutes.
+  \[
+    \begin{tikzcd}
+      A' \arrow[r, "\run_{A'}"] \arrow[d, "\sigma"']
+        & A' \sequoid I \arrow[d, "\sigma\sequoid I"] \\
+      A \arrow[r, "\run_A"]
+        & A \sequoid I
+    \end{tikzcd}
+    \]
+  Indeed, we have
+  \begin{IEEEeqnarray*}{rCl?u}
+    \run_{A'};(\sigma\sequoid I) & = & \runit_{A'};\wk_{A',I};(\sigma\tensor I) & (see above) \\
+    & = & \runit_{A'};(\sigma\tensor I);\wk_{A,I} & \textit{Prop. \ref{PropWkNatural}} \\
+    & = & \sigma;\runit_A;\wk_{A,I} & \textit{Prop. \ref{PropCoherencesAreNatural}} \\
+    & = & \sigma;\run_A\,. & (see above)
+  \end{IEEEeqnarray*}
+
+  Therefore, $\run$ is a natural transformation, which completes our check of the criteria required by Definition \ref{DefSequoidalCategory}.
+\end{proof}
+
+\subsection{Sequoidally decomposable categories}
+
+We will now consider some important additional category-theoretic properties of the sequoid operator on games that do not follow from the fact that $\G$ is a sequoidal category.
+
+\begin{definition}[\cite{martinsthesis}]
+  Let $\C$ be a sequoidal category such that $C_s$ has arbitrary products (including a terminal object $1$).
+  We say that $\C$ is \emph{distributive} if whenever $a_i$ is a collection of objects of $\C'$ and $x$ is an object of $\C$, the morphism
+  \[
+    \dec_{(a_i),x} = \langle \pr_i\sequoid x \rangle \from \prod_ia_i \sequoid x \to \prod_i (a_i \sequoid x)
+    \]
+  is an isomorphism.
+\end{definition}
+\begin{remark}
+  In particular, taking $(a_i)$ to be the empty collection, the morphism $\lun_x = () \from 1 \sequoid x \to 1$ is an isomorphism.
+\end{remark}
+
+\begin{proposition}
+  $\G$ is a distributive sequoidal category.
+\end{proposition}
+\begin{proof}
+  Let $(A_i),X$ be games.
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree embedding $\phi\from P_{\prod_iA_i\sequoid X}\to P_{\prod_i(A_i\sequoid X)}$ defined as follows.
+  \[
+    \phi(s) = \begin{cases}
+      \epsilon & \text{if $s=\epsilon$} \\
+      [\inj_{A_j},\inj_{X^j}]_*(s) & \text{if $s$ begins with a move in $A_j$}
+    \end{cases}
+    \]
+  When we say $[\inj_{A_j},\inj_{X^j}]_*(s)$, we have considered $s$ as a sequence in $(M_{A_j} + X)^*$.
+
+  We claim that $\phi$ is a bijection.  
+  Indeed, it is certainly injective.
+  Then, if we have a non-empty sequence $s\in P_{\prod_i(A_i \sequoid X)}$, then $s$ must start with a move in some $A_j$, and must thereafter take place in the games $A_j$ and $X^j$.  
+  Then $s=\phi([\inj_{A_j},\inj_X]_*(s))$, where we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.
+
+  Therefore, $\phi$ is a tree isomorphism, so $\dec_{(A_i),X} = \tree_\phi$ is an isomorphism by Proposition \ref{PropTree}.
+\end{proof}
+
+We can get a distributivity result in the other direction, but this one is not as strong, since the morphism we get is only a monomorphism, not an isomorphism.
+\begin{definition}
+  Let $\C$ be a distributive sequoidal category.  
+  We say that $\C$ is \emph{strongly distributive} if whenever $A,B,C$ are objects of $\C_s$, the morphism
+  \[
+    \langle A \sequoid J(\pr_1),A \sequoid J(\pr_2)\rangle \from A \sequoid J(B \times C) \to (A \sequoid JB) \times (A \sequoid JC)
+    \]
+  is a monomorphism.
+\end{definition}
+
+\begin{proposition}
+  $\G$ is a strongly distributive sequoidal category.
+\end{proposition}
+\begin{proof}
+  Let $\sigma,\tau\from D\implies (A \sequoid (B \times C))$ be strategies and suppose that 
+  \[
+    \sigma;\langle A\sequoid\pr_1,A\sequoid\pr_2\rangle=\tau;\langle A\sequoid \pr_1,A\sequoid \pr_2\rangle\,.
+    \]
+  Let $s\in\sigma$.
+  Without loss of generality, suppose that $s\vert_{B\times C}\in P_B$.  
   Then we have
-  \begin{IEEEeqnarray*}{CCL}
-    \cc_f\tensor\cc_g & = & \{s\in P_{(A'\tensor B')\implies (A\tensor B)} \suchthat \text{$s\vert_{A',A}\in\cc_f$ and $s\vert_{B',B}\in \cc_g$}\} \\
-    & = & \left\{s\in P_{(A'\tensor B')\implies (A\tensor B)}\,\middle|\, \mbox{\pbox{\textwidth}{for all even $t\prefix s\vert_{A',A}$, $u\prefix s\vert_{B',B}$,\\ $t\vert_A=f^*(t\vert_{A'})$ and $u\vert_B=g^*(u\vert_{B'})$}}\right\}
+  \[
+    [\id_{M_D},\inj_{M_{A^L}},\inj_{M_B},\bot]_*(s)\in\sigma;\langle A\sequoid\pr_1,A\sequoid\pr_2\rangle=\tau;\langle A\sequoid \pr_1,A\sequoid \pr_2\rangle\,.
+    \]
+  It follows that $s\in\tau$.  
+  Since $s$ was arbitrary, we get $\sigma\subset\tau$.  
+  By an identical argument, we get that $\tau\subset\sigma$, and therefore that $\sigma=\tau$.
+\end{proof}
+
+\begin{definition}
+  A sequoidal category $\C$ is \emph{inclusive} if $\C_s$ is a full-on-objects subcategory of $\C$ containing $\wk$ and all isomorphisms of $\G$, and the functor $J$ is the inclusion functor.
+\end{definition}
+In such a situation, we will sometimes drop the mention of the functor $J$.
+
+\begin{proposition}
+  $\G$ is an inclusive sequoidal category.
+\end{proposition}
+\begin{proof}
+  The only thing we really need to check is that isomorphisms in $\G$ are always strict strategies.  
+  Indeed, if $\sigma$ is a strategy for $A \implies B$ and $\tau$ a strategy for $B \implies A$ such that $\sigma;\tau=\id_A$, then for any opening move $a$ in $A$ on the right of $\tau$ there is some $\s\in\int(A,B,A)$ such that $\s\vert_{A,A}=aa$, and therefore the reply to $a$ in $\tau$ must take place in $B$.
+\end{proof}
+
+An important fact about the sequoid operator for games is that it gives us a way to decompose the tensor product as
+\[
+  A \tensor B \cong (A \sequoid B) \times (B \sequoid A)\,.
+  \]
+Informally, this is because both sides allow player $O$ to start either in $A$ or in $B$, and thereafter to continue in that game.
+
+\begin{definition}
+  Let $\C$ be a distributive inclusive sequoidal category, where $\C$ is a symmetric monoidal category.
+  We say that $\C$ is \emph{decomposable} if the morphisms
+  \begin{mathpar}
+    \dec_{a,b}=\langle \wk_{a,Jb},\sym_{Ja,Jb};\wk_{b,Ja} \rangle \from Ja \tensor Jb \to (a \sequoid Jb) \times (b \sequoid Ja)
+    \and
+    () \from I \to 1
+  \end{mathpar}
+  are isomorphisms in $\C_s$.
+\end{definition}
+
+\begin{proposition}
+  Let $\C$ be a decomposable sequoidal category and suppose that $a_1,\cdots,a_n$ is a list of objects of $\C_s$.  
+  Then we have an isomorphism
+  \[
+    a_1 \tensor \cdots \tensor a_n \cong \prod_{i=1}^n (a_i \sequoid (a_1 \tensor \cdots \tensor a_{i-1} \tensor a_{i+1} \tensor \cdots \tensor a_n))\,.
+    \]
+  \label{PropDecSeq}
+\end{proposition}
+\begin{proof}
+  Induction on $n$.  
+  If $n=0$, then we have the isomorphism $() \from I \to 1$.  
+  More generally, we have
+  \begin{IEEEeqnarray*}{Cl}
+    & a_1 \tensor \cdots \tensor a_{n+1}\\
+    \cong & (a_1 \tensor \cdots \tensor a_n) \tensor a_{n+1} \\
+    \xrightarrow{\dec} & (a_1 \tensor \cdots \tensor a_n) \sequoid a_{n+1} \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
+    \cong & \left(\prod_{i=1}^n\left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j\right)\right) \sequoid a_{n+1} \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
+    \xrightarrow{\dist\times\id} & \prod_{i=1}^n\left(\left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j \right) \sequoid a_{n+1}\right) \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
+    \xrightarrow{\langle\passoc\rangle\times\id} & \prod_{i=1}^n \left(a_i \sequoid \left(\Tensor_{j\ne i}^{j\le n} a_j \tensor a_{n+1}\right)\right) \times a_{n+1} \sequoid (a_1\tensor \cdots \tensor a_n) \\
+    \cong & \prod_{i=1}^{n+1} \left(a_i \times \Tensor_{j\ne i}^{j\le n+1} a_j\right) \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
+    \cong & \prod_{i=1}^{n+1} (a_i \sequoid (a_1 \tensor \cdots \tensor a_{i-1} \tensor a_{i+1} \tensor \cdots \tensor a_{n+1}))\,,
   \end{IEEEeqnarray*}
-\end{proof}
+  where each of the arrows is an isomorphism.
+\end{proof}
+
+The specific isomorphism in Proposition \ref{PropDecSeq} is rather complicated at the moment, but we can simplify it.
+
+\begin{definition}
+  Given objects $a_1,\cdots,a_n$ of a monoidal category, we write $\sym_i^n$ for the unique symmetric coherence isomorphism
+  \[
+    a_1 \tensor \cdots \tensor a_n \cong a_i \tensor a_1 \cdots \tensor a_{i-1} \tensor a_{i+1} \tensor a_n\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  The isomorphism in the proof of Proposition \ref{PropDecSeq} is given by
+  \[
+    \dec_{(a_i)}^n = \langle \sym_i^{n};\wk_{a_i,a_1\tensor\cdots\tensor a_{i-1}\tensor a_{i+1}\tensor \cdots\tensor a_n}\rangle\,.
+    \]
+  \label{PropDecSeqFormula}
+\end{proposition}
+\begin{proof}
+  Induction on $n$.
+  We will make use of the coherence theorem for symmetric monoidal categories \cite[\sec 11]{WorkingMathematician} to allow us to elide associators.  
+  The base case is obviously true, because $()\from I \to 1$ is the unique morphism between these objects.  
+  Otherwise, we observe that the morphism into $\prod_{i=1}^{n+1} \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n+1} a_j\right)$ is given component-wise by morphisms $a_1 \tensor \cdots \tensor a_{n+1} \to a_i \sequoid \Tensor_{j\ne i}^{j\le n+1}$ for each $i=1,\cdots,n+1$; we need to check that each of these components is equal to $\sym_i^{n+1};\wk_{a_i,\Tensor_{j\ne i}a_j}$.
+
+  If $i\le n$, then the $i$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite thick dashed arrows in Figure \ref{FigDecSeqFormula}, and is therefore equal to the composite of the solid arrows, which is $\sym_i^{n+1};\wk_{a_i,\Tensor_{j\ne i}a_j}$ as desired.
+  The $n+1$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite
+  \small
+  \[
+    \Tensor_{j=1}^{n+1}a_j \to \Tensor_{j=1}^n a_j \tensor a_{n+1} \xrightarrow{\sym_{\Tensor_{j=1}^na_j,a_{n+1}}} a_{n+1} \tensor \Tensor_{j=1}^n a_j \xrightarrow{\wk_{a_{n+1},\Tensor_{j=1}^n a_j}} a_{n+1} \sequoid \Tensor_{j=1}^n a_j\,,
+    \]
+  \normalsize
+  and then we use the fact that the leftmost two morphisms in this composite compose to give us $\sym_{n+1}^{n+1}$.
+  \begin{SidewaysFigure}
+    \[
+      \begin{tikzcd}[ampersand replacement=\&, column sep=10pt, row sep=30pt]
+        \Tensor_{j=1}^{n+1}a_j \arrow[r, thick, dashed] \arrow[dd, "\sym_i^{n+1}"']
+          \& \Tensor_{j=1}^n a_j \tensor a_{n+1} \arrow[r, "{\wk_{\Tensor_{j=1}^na_j,a_{n+1}}}", thick, dashed] \arrow[d, "\sym_i^n\tensor a_{n+1}" description, dotted]
+            \&[45pt] \Tensor_{j=1}^n a_j \sequoid a_{n+1} \arrow[d, "\sym_i^n\sequoid a_{n+1}", thick, dashed]
+              \&[34pt] \\
+        %
+          \& \left(a_i \tensor \Tensor_{j\ne i}^{j\le n} a_j\right)\tensor a_{n+1} \arrow[r, "{\wk_{a_i\tensor\Tensor_{j\ne i}^{j\le n} a_j,a_{n+1}}}" xshift=-10pt, dotted] \arrow[d, "{\assoc_{a_i,\Tensor_{j\ne i}^{j\le n}a_j,a_{n+1}}}" description, dotted] \arrow[dr, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n}a_j}\tensor a_{n+1}}" description, dotted]
+            \& |[alias=Z]| \left(a_i \tensor \Tensor_{j\ne i}^{j\le n} a_j\right)\sequoid a_{n+1} \arrow[dr, from=Z.east, bend left=25, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n}a_j}\sequoid a_{n+1}}", thick, dashed]
+              \& \\
+        a_i \tensor \Tensor_{j\ne i}^{j\le n+1} a_j \arrow[ddrrr, bend right=15, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n+1}a_j}}"']
+          \& a_i \tensor \left(\tensor_{j\ne i}^{j\le n}a_j \tensor a_{n+1}\right) \arrow[l, dotted] \arrow[drr, to=Y.west, bend right=10, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n}a_j\tensor a_{n+1}}}" description, dotted]
+            \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n}\right)\tensor a_{n+1} \arrow[r, "{\wk_{a_i\sequoid \Tensor_{j\ne i}^{j\le n},a_{n+1}}}" xshift=-10pt, dotted]
+              \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j\right) \sequoid a_{n+1} \arrow[d, "{\passoc_{a_i,\Tensor_{j\ne i}^{j\le n}a_j,a_{n+1}}}", thick, dashed] \\
+        %
+          \&
+            \&
+              \& |[alias=Y]| a_i \sequoid \left(\Tensor_{j\ne i}^{j\le n} a_j \tensor a_{n+1}\right) \arrow[d, thick, dashed] \\
+        %
+          \&
+            \&
+              \& a_i \sequoid \Tensor_{j\ne i}^{j\le n+1}a_j
+      \end{tikzcd}
+      \]
+    \caption[Diagram used in the proof of Proposition \ref{PropDecSeqFormula}]{Diagram used in the proof of Proposition \ref{PropDecSeqFormula}.  
+    The pentagon at the heart of the diagram is the coherence diagram for $\passoc$ and $\wk$ from Definition \ref{DefSequoidalCategory}.}
+    \label{FigDecSeqFormula}
+  \end{SidewaysFigure}
+\end{proof}
+
+\begin{proposition}
+  $\G$ is a decomposable sequoidal category.
+\end{proposition}
+\begin{proof}
+  Let $A,B$ be games.  
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the strategy 
+  \[
+    \langle \wk_{A,B},\sym_{A,B};\wk_{A,B}\rangle
+    \]
+  is given by the tree embedding $\phi$ from $(A \sequoid B) \times (B \sequoid A)$ to $A \tensor B)$ given by
+  \[
+    \phi(s) = \begin{cases}
+      \epsilon & \text{if $s=\epsilon$} \\
+      s\vert_{A \sequoid B} & \text{if $s$ takes place entirely within $A\sequoid B$} \\
+      s\vert_{B \sequoid A} & \text{if $s$ takes place entirely within $B\sequoid A$}
+    \end{cases}\,.
+    \]
+  We claim that this tree embedding is a bijection.  
+  Indeed, it is certainly injective.
+  Now let $s\in P_{A\tensor B}$ be a non-empty play.  
+  Then, if $s$ begins with a move in $A$, we have $s=\phi((\inj_{A\sequoid B})_*(s))$, and if $s$ begins with a move in $B$, we have $s=\phi((\inj_{B\sequoid A})_*(s)$.  
+  Therefore, $\phi$ is a tree isomorphism, so $\dec_{A,B}=\tree_\phi$ is an isomorphism in $\G$.
+
+  Lastly, we have $I=1$ in $\G$, and the unique morphism $I\to 1$ is the identity.
+\end{proof}
+
+\subsection{A Formula for the Exponential}
+
+\begin{definition}
+  Let $\C$ be a symmetric monoidal category.  
+  Given objects $A_1,\cdots,A_n$ of $\C$ and a permutation $\pi\in \S_n$, there is a unique canonical symmetry isomorphism
+  \[
+    \sym^\pi \from A_1 \tensor \cdots \tensor A_n \toisom A_{\pi(1)} \tensor \cdots \tensor A_{\pi(n)}\,.
+    \]
+  Given an object $A$ of $\C$, an \emph{$n$-th symmetrized tensor power} of $A$ is an equalizer $(A^n,\eq^n)$ for the diagram given by all morphisms of the form
+  \[
+    \sym_\pi \from A ^{\tensor n} \to A ^{\tensor n}\,.
+    \]
+  We say that the symmetrized tensor power $A^n$ \emph{commutes with the tensor product} if $(B\tensor A^n,B\tensor \eq_n)$ is an equalizer for the diagram given by morphisms of the form
+  \[
+    B\tensor\sym_\pi \from B\tensor A ^{\tensor n} \to B\tensor A ^{\tensor n}\,.
+    \]
+\end{definition}
+
+\begin{proposition}[\cite{CalcoPaper}]
+  Let $\C$ be an inclusive, strongly distributive, decomposable sequoidal category.  
+  Then $\C$ has all symmetrized tensor powers.
+\end{proposition}
+\begin{proof}
+  Let $A$ be an object of $\C$ (equivalently, an object of $\C_s$).  
+  We inductively define objects $A^{\sequoid n}$ by
+  \begin{itemize}
+    \item $A^{\sequoid 0} = I$; and
+    \item $A^{\sequoid (n+1)}=J(A\sequoid A^{\sequoid n})$.
+  \end{itemize}
+  We claim that $A^{\sequoid n}$ is a symmetrized tensor power of $A$.
+
+  Given $n$, we inductively define a morphism $\wk^n\from A^{\tensor n} \to A^{\sequoid n}$, where $\wk^0=\id_I$, and $\wk^{n+1}$ is given by the composite
+  \[
+    A^{\tensor (n+1)} \to A \tensor A^{\tensor n} \xrightarrow{A \tensor \wk^n} A \tensor A^{\sequoid n} \xrightarrow{\wk_{A,A^{\sequoid n}}} A \sequoid A^{\sequoid n}\,.
+    \]
+  We show by induction on $n$ that if $B$ is an object of $\C$ and $k\ge 0$ then the composite
+  \scriptsize
+  \begin{mathpar}
+    B\tensor (A \sequoid\blank)^kA^{\tensor n}
+    \xrightarrow{\langle B\tensor(A \sequoid\blank)^k \sym^\pi \rangle}
+    (B\tensor(A \sequoid\blank)^kA^{\tensor n})^{n!}
+    \xrightarrow{(B\tensor(A\sequoid\blank)^k\wk^n)^{n!}}
+    (B\tensor A^{\sequoid (k+n)})^{n!}
+  \end{mathpar}
+  \normalsize
+  (i.e., the morphism $\langle B\tensor(A\sequoid\blank)^k(\sym^\pi;\wk^n)\rangle$) is a monomorphism.
+  In particular, taking $k=0$, we will have shown that $\langle B\tensor (\sym^\pi;\wk^n)\rangle$ is a monomorphism.
+
+  The hypothesis is clearly true for $n=0$; otherwise, we have a composite
+  \begin{mathpar}
+    B\tensor (A\sequoid\blank)^kA^{\tensor (n+1)}
+    \xrightarrow{B\tensor (A\sequoid\blank)^k\langle \sym^{n+1}_i;\wk_{A,A^{\tensor n}}\rangle}
+    B\tensor (A \sequoid\blank)^k(A\sequoid A^{\tensor n})^{n+1}
+    \xrightarrow{\langle B\tensor (A\sequoid\blank)^k;\pr_i\rangle}
+    (B\tensor(A \sequoid\blank)^{k+1} A^{\tensor n})^{n+1}
+    \to
+    (B\tensor A ^{\sequoid (k + n + 1)})^{(n+1)!}\,,
+  \end{mathpar}
+  where the last arrow is the tensor product of $B$ with the $(n+1)$-th power of the composite given by
+  \footnotesize
+  \[
+    (A \sequoid\blank)^{k+1}A^{\tensor n}
+    \xrightarrow{\langle (A \sequoid \blank)^{k+1}\sym^\sigma\rangle}
+    ((A \sequoid\blank)^{k+1}A^{\tensor n})^{n!}
+    \xrightarrow{((A \sequoid\blank)^{k+1}\wk^n)^{n!}}
+    (A^{\sequoid (k+n+1)})^{n!}\,,
+    \]
+  \normalsize
+  which is a monomorphism by the induction hypothesis.
+  Then the previous composite is the composite of monomorphisms (by our assumptions on $\C$), and is therefore itself a monomorphism.  
+  Now this composite may be written as
+  \[
+    \langle B\tensor(A\sequoid\blank)^k(\sym_i^{n+1};\wk_{A,A^{\tensor n}};(A\sequoid\sym^\sigma);(A\sequoid\wk^n)) \rangle\,,
+    \]
+  which, since $\wk$ is a natural transformation, is equal to
+  \[
+    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A\tensor\sym^\sigma);(A\tensor\wk^n);\wk_{A,A^{\sequoid n}})\rangle\,,
+    \]
+  where $\sigma$ ranges over the permutations in $\S_n$.
+  Moreover, by the definition of $\wk^n$, this is equal to
+  \[
+    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A \tensor \sym^\sigma);\wk^{n+1}\rangle\,.
+    \]
+
+  Now, given $i\in\{1,\cdots n+1\}$ and $\sigma\in\S_n$, there is a unique permutation $\pi\in\S_{n+1}$ such that $\sym_i^{n+1};(A\tensor\sym^\sigma=\sym^\pi)$; moreover, this defines a bijection from $\{1,\cdots,n+1\}\times\S_n \to \S_{n+1}$.
+  Therefore (after choosing an appropriate enumeration of our permutations), we see that this composite is in fact equal to
+  \[
+    \langle B\tensor(A \sequoid\blank)^k (\sym^\pi;\wk^{n+1})\rangle\,.
+    \]
+  Therefore, $\langle B\tensor(A \sequoid\blank)^k(\sym^\pi;\wk^{n+1})\rangle$ is a monomorphism as desired, completing the induction.
+
+  Next, we define morphisms $\eq_n\from A^{\sequoid n} \to A^{\tensor n}$ inductively, where $\eq_0=\id$ and $\eq_{n+1}$ is defined by the following composite
+  \[
+    A^{\sequoid (n+1)} = A\sequoid A^{\sequoid n} \xrightarrow{\langle (A\sequoid \eq_n)_1^n\rangle} (A \sequoid A^{\tensor n})^n \cong A^{\tensor (n+1)}\,,
+    \]
+  where the final isomorphism is as in Propositions \ref{PropDecSeq} and \ref{PropDecSeqFormula}.
+
+  First, we show inductively that $\eq_n;\sym^\pi;\wk^n=\id_{A^{\sequoid n}}$ for all permutations $\pi$ of $S_n$.
+  This is certainly true for $n=0$; otherwise, let $\pi\in \S_{n+1}$ be a permutation.  
+  Let $j=\pi\inv(1)$ be the element sent to $1$ by $\pi$ and let $\sigma$ be the permutation of $1,\cdots,n$ such that applying $\sigma$ to the elements $2,\cdots,n+1$ and composing with $\pi$ gives us the $j$-cycle $(1\,\dots\,j)$.
+  Then we have
+  \[
+    \sym_j^{n+1};(A\tensor\sym^\sigma) = \sym^\pi\,.
+    \]
+  Now we get
+  \begin{IEEEeqnarray*}{Cl}
+    & \eq_{n+1};\sym^\pi;\wk^{n+1} \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym^\pi;(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};(A\tensor\sym^\sigma);(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};\wk_{A,A^{\tensor n}};(A \sequoid \sym^\sigma);(A \sequoid \wk^n) \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\langle \sym_i^{n+1};\wk_{A,A^{\tensor n}}\rangle;\pr_j;(A \sequoid \sym^\sigma);(A \sequoid \wk^n) \\
+    = & A \sequoid (\eq_n;\sym^\sigma;\wk^n)\,,
+  \end{IEEEeqnarray*}
+  which is equal to the identity on $A^{\sequoid (n+1)}$ by the induction hypothesis.
+
+  Now let $\rho$ be a permutation in $\S_n$.  
+  We claim that $\eq_n=\eq_n;\sym^{\rho}$.
+
+  Indeed, we have
+  \begin{IEEEeqnarray*}{rCl}
+    \eq_n;\langle \sym^{\pi} ; \wk^n \rangle
+    & = & \langle \eq_n;\sym^{\pi};\wk^n \rangle \\
+    & = & \langle \id \rangle \\
+    & = & \langle \eq_n;\sym^{\rho\pi};\wk^n \rangle \\
+    & = & \eq_n;\sym^{\rho};\langle \sym^\pi ; \wk^n \rangle\,.
+  \end{IEEEeqnarray*}
+  Since $\langle \sym^\pi;\wk^n\rangle$ is a monomorphism, this means that $\eq_n=\eq_n;\sym^{\rho}$, as desired.
+  Therefore, $\eq_n$ equalizes the morphisms $\eq_n$.  
+  We claim that it is an equalizer, and that this equalizer is preserved by the tensor product.
+
+  Indeed, let $B,C$ be objects of $\C$, and let $f \from C \to B \tensor A^{\tensor n}$ be a morphism such that $f=f;(B\tensor\sym^{\pi})$ for all $\pi\in\S_n$.
+
+  Let $\tilde f = f;(B \tensor \wk^n)\from C \to B \tensor A^{\sequoid n}$.  
+  We claim that $\tilde f;(B\tensor\eq_n)=f$; indeed, we have
+  \begin{IEEEeqnarray*}{rCl}
+    \tilde f;(B \tensor\eq_n);\langle B\tensor(\sym^\pi;\wk^n)\rangle 
+    & = & \langle f;(B \tensor (\wk^n;\eq_n;\sym^\pi;\wk^n)) \rangle \\
+    & = & \langle f;(B\tensor \wk^n)\rangle \\
+    & = & f;\langle B \tensor (\sym^\pi;\wk^n)\rangle\,.
+  \end{IEEEeqnarray*}
+  Therefore, since $\langle B \tensor (\sym^\pi;\wk^n)\rangle$ is a monomorphism, we know that $\tilde f;(B\tensor \eq_n)=f$.
+
+  Now suppose that $h\from C \to B \tensor A^{\sequoid n}$ is such that $h;(B\tensor eq_n)=f$.  
+  We claim that $h=\tilde f$.  
+  Indeed, we have 
+  \[
+    \tilde f = f;(B \tensor \wk^n) = h;(B \tensor \eq_n);(B \tensor \wk^n) = h\,.
+    \]
+  Therefore, $(B\tensor A^{\sequoid n},B\tensor \eq_n)$ is an equalizer of the arrows $B\tensor \sym^\pi\from B \tensor A^{\tensor n} \to B \tensor A^{\tensor n}$, as desired.
+\end{proof}
+
+We are interested in symmetrized tensor powers because of an important result of \Mellies, Tabareau and Tasson.
+Suppose $\C$ is a monoidal category, and that $\C$ has symmetrized tensor powers that commute with the tensor product.  
+Given $n$, we have a morphism
+\[
+  ()\tensor A^{\tensor n} \from A^{\tensor (n+1)} \to A^{\tensor n}\,;
+  \]
+then, if $A^n$ and $A^{n+1}$ are the $n$-th and $n+1$-th symmetrized tensor powers of $A$, and $\eq_{n+1},\eq$ the corresponding equalization, for any $\pi\in\S_n$ we have a commutative diagram
+\[
+  \begin{tikzcd}[column sep=50pt]
+    B \tensor A^{n+1} \arrow[r, "B\tensor\eq_{n+1}"]
+      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor()\tensor A^{\tensor n}"] \arrow[d, "\sym^{\pi'}"']
+        & B \tensor A^{\tensor n} \arrow[d, "\sym^\pi"] \\
+    %
+      & B \tensor A^{\tensor (n+1)} \arrow[r, "B \tensor()\tensor A^{\tensor n}"]
+        & B \tensor A^{\tensor n}
+  \end{tikzcd}\,,
+  \]
+where $\pi'$ is the permutation of $1,\cdots,n+1$ that fixes $1$ and applies $\pi$ to the remaining elements $2,\cdots,n+1$.
+
+This means that for each $\pi\in \S_n$ we have
+\begin{IEEEeqnarray*}{rCl}
+  (B\tensor\eq_{n+1});(B\tensor ()\tensor A^{\tensor n})
+  & = & (B \tensor\eq_{n+1});(B\tensor \sym^{\pi'});(B\tensor ()\tensor A^{\tensor n}) \\
+  & = & (B\tensor\eq_{n+1});(B\tensor()\tensor A^{\tensor n});(B\tensor \sym^\pi)\,,
+\end{IEEEeqnarray*}
+and that there is therefore an induced morphism
+\[
+  B\tensor A^{n+1} \to B \tensor A^n\,,
+  \]
+by the universal property of the equalizer.
+
+\begin{theorem}[\cite{MelliesCofCommCom}]
+  Let $\C$ be a monoidal category in which the monoidal unit is a terminal object.
+  Suppose that $\C$ has symmetrized tensor powers that commute with the tensor product.
+
+  Then, for any objects $A,B$ of $\C$, there is a natural sequence
+  \[
+    B \leftarrow B\tensor A \leftarrow B\tensor A^2 \leftarrow B \tensor A^3 \leftarrow \cdots\,.
+    \]
+  In particular, there is a sequence
+  \[
+    I \leftarrow A \leftarrow A^2 \leftarrow A^3 \leftarrow \cdots\,.
+    \]
+  Suppose that this sequence has a limit $\oc A$, and that $B\tensor \oc A$ is the limit of the first sequence for all $B$.  
+  Then $\oc A$ has the structure of the cofree commutative comonoid on $A$.
+\end{theorem}
 

### 2019-03-28 Thesis/games.tex
N.

@@
 \end{mathpar}
-The idea here is that $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).
+The idea here is that if $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).
 
@@
 
-\subsection{Tree Embeddings}
-
-We can generalize the subset inclusions of the previous section to \emph{tree embeddings}.  
-Tree embeddings are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
-A consequence of this is that while tree embeddings do give rise to strategies, these strategies are not in general innocent.
-
-\begin{definition}
-  Let $A,B$ be games.  
-  A \emph{tree embedding} from $A$ to $B$ is a length-preserving function $\phi\from P_A \hookrightarrow P_B$ such that for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$ and such that if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
-
-  Given a tree embedding $\phi$ from $A$ to $B$, we define a strategy $\tree_\phi\from B \implies A$ by
-  \[
-    \tree_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
-    \]
-\end{definition}
-\begin{example}
-  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree embedding from $A$ to $B$.
-\end{example}
-
-\begin{proposition}
-  $\tree_\phi$ is a strategy.
-
-  If $\phi$ is a tree embedding from $A$ to $B$ and $\psi$ is a tree embedding from $B$ to $C$, then $\psi\circ\phi$ is a tree embedding from $A$ to $C$ and $\tree_{\psi\circ\phi}=\tree_\psi;\tree_\phi$.
-  \label{PropTree}
-\end{proposition}
-\begin{proof}
-  $\tree_\phi$ is a prefix-closed subset of $P_{B\implies A}$ by definition.  
-  If $sab,sac\in\tree_\phi$, then we have $s\vert_B=\phi(s\vert_A)$ and $sab\vert_B=\phi(sab\vert_A)$.
-  Since $\phi$ is length-preserving, $s\vert_A$ and $s\vert_B$ must have the same length, and the same is true of $sab\vert_A$ and $sab\vert_B$.  
-  Therefore, either $a$ is a move in $A$ and $s\vert_Bb=\phi(s\vert_Aa)$ or $a$ is a move in $B$ and $s\vert_Ba=\phi(s\vert_Ab)$.  
-  The same applies to $c$: so either $s\vert_Bb=\phi(s\vert_Aa)=s\vert_Bc$ or $\phi(s\vert_Ab)=s\vert_Ba=\phi(s\vert_Ac)$.  
-  In either case, we have $b=c$.
-
-  Now suppose that $\phi$ is a tree embedding from $A$ to $B$ and that $\psi$ is a tree embedding from $B$ to $C$.  
-  Then $\psi\circ\phi$ certainly preserves length and the prefix relation.  
-  Let $\s\in\tree_\psi\|\tree_\phi$, and let $t\prefix \s\vert_{C,A}$ have even length.  
-  Let $\t$ be a prefix of $\s$ such that $\t\vert_{C,A}=t$.
-  Then, by the argument above, $\t\vert_{C,B}$ and $\t\vert_{B,A}$ have even length, and so $\t\vert_C=\psi(\t\vert_B)$ and $\t\vert_B=\phi(\t\vert_A)$.  
-  Therefore, $t\vert_C=(\psi\circ\phi)(t\vert_A)$.  
-  Since $t$ was arbitrary, this means that $\s\vert_{A,C}\in\tree_{\psi\circ\phi}$.
-
-  Conversely, suppose that $s\in\tree_{\psi\circ\phi}$: so $t\vert_C = \psi(\phi(t\vert_A))$ for all even-length $t\prefix s$.
-  By induction on the length of $s$, we build up a sequence $\s(s)\in\tree_\psi\|\tree_\phi$ such that $\s(s)\vert_{C,A}=s$.
-  \begin{itemize}
-    \item $\s(\epsilon) = \epsilon$.
-    \item Given a sequence $sab\in\tree_{\psi\circ\phi}$, we have $s\vert_C=\psi(\phi(s\vert_A))$.  
-      By our discussion above, we know that $sab\vert_A$ is one move longer than $s\vert_A$, so $\phi(sab\vert_A)=\phi(s\vert_A)c$ for some move $c$ in $B$, justified by some move in $B$.
-      Then we set $\s(sab)=\s(s)acb$, where the justifier of $c$ is as above.
-  \end{itemize}
-  It is clearly true that $\s(s)\vert_{C,A}=s$ for all sequences $s\in\tree_{\psi\circ\phi}$.
-
-  We claim that $\s(s)\in\tree_\psi\|\tree_\phi$ for all $s$.  
-  This is clearly true for the empty sequence; for $sab$, we have $\s(sab)\vert_{B,A} = \s(s)acb\vert_{B,A}$, where $\phi(sab\vert_A)=\phi(s\vert_A)c$.
-
-  By induction, $\s(s)\in\psi(\phi(s\vert_A))$, and so for all even-length $t\prefix \s(s)\vert_{B,A}$ we have $t\vert_B=\phi(t\vert_A)$, and for all even-length $u\prefix\s(s)\vert_{C,B}$ we have $u\vert_C=\psi(u\vert_B)$.
-  All we need to show is that $\s(s)acb\vert_B=\phi(\s(s)acb\vert_A)$ and that $\s(s)acb\vert_C=\psi(\s(s)acb\vert_B)$.  
-  Indeed, $\phi(\s(s)acb\vert_A)=\phi(sab\vert_A)=\phi(s\vert_A)c=\phi(\s(s)\vert_A)c=\s(s)\vert_Bc=\s(s)acb\vert_V$, and, in addition, we have that $\psi(\s(s)acb\vert_B) = \psi(\s(s)\vert_Bc) = \psi(\phi(\s(s)\vert_A)c) = \psi(\phi(sab\vert_A))=sab\vert_C=\s(s)acb\vert_C$.
-\end{proof}
-
-\begin{definition}
-  We say that a tree embedding $\phi$ is a \emph{tree isomorphism} if it is a bijection.
-\end{definition}
-
-\begin{proposition}
-  If $\phi$ is a tree isomorphism from a game $A$ to a game $B$, then $\tree_\phi$ is an isomorphism in $\G$.
-\end{proposition}
-\begin{proof}
-  If $\phi$ is a tree isomorphism, then its inverse $\phi\inv$ is also a tree isomorphism, and Proposition \ref{PropTree} tells us that $\tree_\phi$ and $\tree_{\phi\inv}$ are inverses in $\G$.
-\end{proof}
-
 \subsection{$\G$ as a Symmetric Monoidal Category}
@@
   Then $\sigma\tensor\tau$ is innocent.
+  \label{PropTensorInnocent}
 \end{proposition}
@@
   Let $A_i,B$ be games and let $\phi_i$ be tree embeddings from $A_i$ to $B$.  
-  Then $\langle \tree_{\phi_i} \rangle = \tree_\phi$, where $\phi$ is the tree embeddings from $\prod_iA_i$ to $B$ given by
+  Then $\langle \zz_{\phi_i} \rangle = \zz_\phi$, where $\phi$ is the tree embeddings from $\prod_iA_i$ to $B$ given by
   \[
@@
 
+\subsection{Tree Embeddings and Zigzag Strategies}
+
+So far, the strategies we have been considering have all been innocent.  
+We now start considering some non-innocent strategies.
+
+We can generalize the subset inclusions of the previous section to \emph{tree embeddings}.  
+Tree embeddings are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
+A consequence of this is that while tree embeddings do give rise to strategies, these strategies are not in general innocent.
+
+\begin{definition}
+  Let $A,B$ be games.  
+  A \emph{tree embedding} from $A$ to $B$ is a function $\phi\from P_A \hookrightarrow P_B$ such that
+  \begin{itemize}
+    \item $\phi$ preserves length and justification indices; 
+    \item for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$; and
+    \item if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
+  \end{itemize}
+
+  Given a tree embedding $\phi$ from $A$ to $B$, we define a strategy $\zz_\phi\from B \implies A$ by
+  \[
+    \zz_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
+    \]
+\end{definition}
+\begin{example}
+  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree embedding from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
+\end{example}
+
+\begin{proposition}
+  $\zz_\phi$ is a strategy.  
+\end{proposition}
+\begin{proof}
+  $\zz_\phi$ is a prefix-closed subset of $P_{B\implies A}$ by definition.  
+  If $sab,sac\in\zz_\phi$, then we have $s\vert_B=\phi(s\vert_A)$ and $sab\vert_B=\phi(sab\vert_A)$.
+  Since $\phi$ is length-preserving, $s\vert_A$ and $s\vert_B$ must have the same length, and the same is true of $sab\vert_A$ and $sab\vert_B$.  
+  Therefore, either $a$ is a move in $A$ and $s\vert_Bb=\phi(s\vert_Aa)$ or $a$ is a move in $B$ and $s\vert_Ba=\phi(s\vert_Ab)$.  
+  The same applies to $c$: so either $s\vert_Bb=\phi(s\vert_Aa)=s\vert_Bc$ or $\phi(s\vert_Ab)=s\vert_Ba=\phi(s\vert_Ac)$.  
+  In either case, we have $b=c$.
+\end{proof}
+
+We want an analogue of Proposition \ref{PropCopycat}.
+
+\begin{definition}
+  Given a tree embedding from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
+\end{definition}
+
+\begin{proposition}
+  If $\sigma\from C \implies B$ is a strategy, then $\sigma;\zz_\phi$ is given by
+  \[
+    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\}\,.
+    \]
+
+  In particular, if $\phi$ is a tree embedding from $A$ to $B$ and $\psi$ is a tree embedding from $B$ to $C$, then $\psi\circ\phi$ is a tree embedding from $A$ to $C$ and $\zz_{\psi\circ\phi}=\zz_\psi;\zz_\phi$.
+  \label{PropTree}
+\end{proposition}
+\begin{proof}
+  Suppose that $\s\in\sigma\|\zz_\phi$.  
+  Then $\s\vert_{C,B}\in\sigma$ and $t\vert_B=\phi(t\vert_A)$ for all even-length $t\prefix \s\vert_{B,A}$.  
+  Then it is clear that $(\s\vert_{C,A})^\phi=\s\vert_{C,B}$.
+
+  Conversely, suppose that $s\in P_{C\implies A}$ and that $s^\phi\in\sigma$.  
+  We construct a sequence $\s\in\sigma\|\zz_phi$ such that $\s\vert_{C,B}=s^\phi$ and $\s\vert_{C,A}=s$ by taking the sequence $s$ and inserting, in order, the elements of the sequence $\phi(s\vert_A)$ immediately after each $O$-move in $s\vert_C$ and immediately before each $P$-move in $C$, leaving the rest of $s$ intact.
+  Then $\s\vert_{C,B}=s^\phi\in\sigma$ and $\s\vert_{B,A}\in\zz_\phi$, by construction.  
+  So $s=\s\vert_{C,A}\in \sigma;\zz_\phi$.
+\end{proof}
+
+\begin{definition}
+  We say that a tree embedding $\phi$ is a \emph{tree isomorphism} if it is a bijection.
+\end{definition}
+
+\begin{proposition}
+  If $\phi$ is a tree isomorphism from a game $A$ to a game $B$, then $\zz_\phi$ is an isomorphism in $\G$.
+\end{proposition}
+\begin{proof}
+  If $\phi$ is a tree isomorphism, then its inverse $\phi\inv$ is also a tree isomorphism, and Proposition \ref{PropTree} tells us that $\zz_\phi$ and $\zz_{\phi\inv}$ are inverses in $\G$.
+\end{proof}
+
+More generally:
+
+\begin{proposition}
+  If $\phi$ is a surjection, then $\zz_\phi$ is a monomorphism.
+  \label{PropZigzagMono}
+\end{proposition}
+\begin{proof}
+  Let $\sigma,\tau\from C \implies B$ be strategies.
+  Then, by Proposition \ref{PropTree}, we have
+  \[
+    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\} = \{s\in P_{C\implies A}\suchthat s^\phi\in\tau\}\,.
+    \]
+  Let $t\in\sigma$.  
+  Then, since $\phi$ is surjective, there is some $u\in P_A$ such that $\phi(u)=t\vert_B$.  
+  As before, we may construct some sequence $t'$ such that $t'\vert_A=u$ and $t=(t')^\phi$.  
+  Then, since $(t')^\phi=t\in\sigma$, we must have $(t')^\phi\in\tau$; i.e., that $t\in\tau$.  
+  So $\sigma\subset\tau$.
+
+  Similarly, $\tau\subset\sigma$, and so $\sigma$ and $\tau$ are equal.
+\end{proof}
+
 \subsection{Sequoidally decomposable categories}
@@
   Let $(A_i),X$ be games.
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree embedding $\phi\from P_{\prod_iA_i\sequoid X}\to P_{\prod_i(A_i\sequoid X)}$ defined as follows.
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree embedding $\phi\from P_{\prod_i(A_i\sequoid X)}\to P_{\prod_iA_i\sequoid X}$ defined as follows.
   \[
@@
       \epsilon & \text{if $s=\epsilon$} \\
-      [\inj_{A_j},\inj_{X^j}]_*(s) & \text{if $s$ begins with a move in $A_j$}
+      [\inj_{A_j},\inj_{X}]_*(s) & \text{if $s$ begins with a move in the $j$-th component}
     \end{cases}
     \]
-  When we say $[\inj_{A_j},\inj_{X^j}]_*(s)$, we have considered $s$ as a sequence in $(M_{A_j} + X)^*$.
+  When we say $[\inj_{A_j},\inj_{X^j}]_*(s)$, we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.
 
   We claim that $\phi$ is a bijection.  
-  Indeed, it is certainly injective.
-  Then, if we have a non-empty sequence $s\in P_{\prod_i(A_i \sequoid X)}$, then $s$ must start with a move in some $A_j$, and must thereafter take place in the games $A_j$ and $X^j$.  
-  Then $s=\phi([\inj_{A_j},\inj_X]_*(s))$, where we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.
-
-  Therefore, $\phi$ is a tree isomorphism, so $\dec_{(A_i),X} = \tree_\phi$ is an isomorphism by Proposition \ref{PropTree}.
+  Indeed, it is certainly injective, since if $\phi(s)=\phi(t)$, then the first move of $\phi(s)=\phi(t)$ occurs in one of the $A_j$, which means that $s,t$ must both come from the $j$-th component.
+  Then, if we have a non-empty sequence $s\in P_{\prod_iA_i \sequoid X)}$, then $s$ must start with a move in some $A_j$, and must thereafter take place in the games $A_j$ and $X$.  
+  Then $s=\phi([\inj_{A_j},\inj_{X^j}]_*(s))$, where we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.
+
+  Therefore, $\phi$ is a tree isomorphism, so $\dec_{(A_i),X} = \zz_\phi$ is an isomorphism by Proposition \ref{PropTree}.
 \end{proof}
@@
   Let $\C$ be a distributive sequoidal category.  
-  We say that $\C$ is \emph{strongly distributive} if whenever $A,B,C$ are objects of $\C_s$, the morphism
-  \[
-    \langle A \sequoid J(\pr_1),A \sequoid J(\pr_2)\rangle \from A \sequoid J(B \times C) \to (A \sequoid JB) \times (A \sequoid JC)
+  We say that $\C$ is \emph{strongly distributive} if whenever $(A_i),(B_i)$ are objects of $\C_s$, where $(B_i)$ is a non-empty collection, then the morphism
+  \[
+    \langle A_1 \sequoid(\cdots \sequoid (A_n \sequoid J(\pr_i))\cdots)\rangle
+    \]
+  is a monomorphism
+  \[
+    A_1 \sequoid\left(\cdots\sequoid\left(A_n \sequoid J\left(\prod_iB_i\right)\right)\cdots\right) \to \prod_i (A_1 \sequoid (\cdots \sequoid (A_n \sequoid J(B_i))\cdots))\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  $\G$ is a strongly distributive sequoidal category.
+\end{proposition}
+\begin{proof}
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree embedding $\phi\from P_{\prod_i (A_1 \sequoid(\cdots\sequoid(A_n\sequoid B_i)\cdots))} \to P_{A_1\sequoid(\cdots\sequoid(A_n\sequoid \prod_iB_i))}$ defined as follows.
+  \[
+    \phi(s) = \begin{cases}
+      \epsilon & \text{if $s=\epsilon$} \\
+      [\inj_{A_1,\cdots,A_n},\inj_{B_j}]_*(s) & \text{if $s$ begins with a move in the $j$-th component}
+    \end{cases}
+    \]
+  Note that $\phi$ is not in general injective, since if $s$ occurs entirely inside one of the copies of the $A_i$, then $\phi(s)=\phi(s')$ for any identical sequence $s'$ occurring inside one of the other copies of the $A_i$.
+
+  We claim that $\phi$ is surjective.  
+  Indeed, let $t\in P_{A_1\sequoid(\cdots \sequoid(\prod_i B_i))}$ be a non-empty sequence.  
+  If $t$ contains moves in one of the $B_j$, then we have $t=\phi([\inj_{A_i^j},\inj_{B_j}]_*(t))$, where $A_i^j$ is the copy of $A_i$ in the $j$-th component of the product and we have considered $t$ as a sequence in $(M_{A_1} + \cdots + M_{A_n} + M_{B_j})^*$.
+  If $t$ only contains moves in the $A_i$, then pick some fixed index $0$; then we have $t=\phi([\inj_{A_i^0}]_*(t))$, where we have considered $t$ as a sequence in $(M_{A_1} + \cdots + M_{A_n})^*$.
+
+  Therefore, $\phi$ is a monomorphism by Proposition \ref{PropZigzagMono}.
+\end{proof}
+
+Note that if $\C$ is decomposable, this property of being a monomorphism is automatically preserved by the tensor product; i.e., for any objects $A,(B_i),C$ of $\C_s$ (for $B_i$ a non-empty collection), the morphism
+\[
+  \langle JC \tensor J(A \sequoid J(\pr_i))\rangle \from JC \tensor J\left(A \sequoid J\left(\prod_iB_i\right)\right) \to \prod_i JC \tensor J(A \sequoid J(B_i))
   \]
 is a monomorphism.
-\end{definition}
-
-\begin{proposition}
-  $\G$ is a strongly distributive sequoidal category.
-\end{proposition}
-\begin{proof}
-  Let $\sigma,\tau\from D\implies (A \sequoid (B \times C))$ be strategies and suppose that 
-  \[
-    \sigma;\langle A\sequoid\pr_1,A\sequoid\pr_2\rangle=\tau;\langle A\sequoid \pr_1,A\sequoid \pr_2\rangle\,.
-    \]
-  Let $s\in\sigma$.
-  Without loss of generality, suppose that $s\vert_{B\times C}\in P_B$.  
-  Then we have
-  \[
-    [\id_{M_D},\inj_{M_{A^L}},\inj_{M_B},\bot]_*(s)\in\sigma;\langle A\sequoid\pr_1,A\sequoid\pr_2\rangle=\tau;\langle A\sequoid \pr_1,A\sequoid \pr_2\rangle\,.
-    \]
-  It follows that $s\in\tau$.  
-  Since $s$ was arbitrary, we get $\sigma\subset\tau$.  
-  By an identical argument, we get that $\tau\subset\sigma$, and therefore that $\sigma=\tau$.
-\end{proof}
 
@@
   Then, if $s$ begins with a move in $A$, we have $s=\phi((\inj_{A\sequoid B})_*(s))$, and if $s$ begins with a move in $B$, we have $s=\phi((\inj_{B\sequoid A})_*(s)$.  
-  Therefore, $\phi$ is a tree isomorphism, so $\dec_{A,B}=\tree_\phi$ is an isomorphism in $\G$.
+  Therefore, $\phi$ is a tree isomorphism, so $\dec_{A,B}=\zz_\phi$ is an isomorphism in $\G$.
 
@@
   Then $\C$ has all symmetrized tensor powers.
+  \label{PropSequoidPower}
 \end{proposition}
@@
 
-  The hypothesis is clearly true for $n=0$; otherwise, we have a composite
+  The hypothesis is clearly true for $n=0$; in the general case, we have a composite
   \begin{mathpar}
@@
   First, we show inductively that $\eq_n;\sym^\pi;\wk^n=\id_{A^{\sequoid n}}$ for all permutations $\pi$ of $S_n$.
-  This is certainly true for $n=0$; otherwise, let $\pi\in \S_{n+1}$ be a permutation.  
+  This is certainly true for $n=0$; in the general case, let $\pi\in \S_{n+1}$ be a permutation.  
   Let $j=\pi\inv(1)$ be the element sent to $1$ by $\pi$ and let $\sigma$ be the permutation of $1,\cdots,n$ such that applying $\sigma$ to the elements $2,\cdots,n+1$ and composing with $\pi$ gives us the $j$-cycle $(1\,\dots\,j)$.
@@
 \[
-  ()\tensor A^{\tensor n} \from A^{\tensor (n+1)} \to A^{\tensor n}\,;
-  \]
-then, if $A^n$ and $A^{n+1}$ are the $n$-th and $n+1$-th symmetrized tensor powers of $A$, and $\eq_{n+1},\eq$ the corresponding equalization, for any $\pi\in\S_n$ we have a commutative diagram
+  A^{\tensor n}\tensor() \from A^{\tensor (n+1)} \to A^{\tensor n}\,,
+  \]
+where $()$ is the unique morphism into the terminal object.  
+Then, if $A^n$ and $A^{n+1}$ are the $n$-th and $n+1$-th symmetrized tensor powers of $A$, and $\eq_{n+1},\eq$ the corresponding equalization, for any $\pi\in\S_n$ we have a commutative diagram
 \[
@@
     B \tensor A^{n+1} \arrow[r, "B\tensor\eq_{n+1}"]
-      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor()\tensor A^{\tensor n}"] \arrow[d, "\sym^{\pi'}"']
+      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor A^{\tensor n}\tensor()"] \arrow[d, "\sym^{\pi'}"']
         & B \tensor A^{\tensor n} \arrow[d, "\sym^\pi"] \\
     %
-      & B \tensor A^{\tensor (n+1)} \arrow[r, "B \tensor()\tensor A^{\tensor n}"]
+      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor A^{\tensor n} \tensor()"]
         & B \tensor A^{\tensor n}
@@
 \begin{IEEEeqnarray*}{rCl}
-  (B\tensor\eq_{n+1});(B\tensor ()\tensor A^{\tensor n})
-  & = & (B \tensor\eq_{n+1});(B\tensor \sym^{\pi'});(B\tensor ()\tensor A^{\tensor n}) \\
-  & = & (B\tensor\eq_{n+1});(B\tensor()\tensor A^{\tensor n});(B\tensor \sym^\pi)\,,
+  (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor ())
+  & = & (B \tensor\eq_{n+1});(B\tensor \sym^{\pi'});(B\tensor A^{\tensor n}\tensor ()) \\
+  & = & (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor());(B\tensor \sym^\pi)\,,
 \end{IEEEeqnarray*}
@@
   Then $\oc A$ has the structure of the cofree commutative comonoid on $A$.
+  \label{TheMtt}
 \end{theorem}
+
+We want to show that this theorem applies in $\G$.
+First, we find an explicit formula for the morphisms $B \tensor A^{\sequoid(n+1)}\to B\tensor A^{\sequoid n}$.
+
+\begin{proposition}
+  Let $\C$ be an inclusive, strongly distributive, decomposable sequoidal category -- so $\G$ has symmetrized tensor powers preserved by the tensor product as in Proposition \ref{PropSequoidPower}.
+
+  Then the canonical morphisms $B \tensor A^{\sequoid (n+1)}\to B\tensor A^{\sequoid n}$ are given by
+  \[
+    B \tensor (A \sequoid \blank)^n()\,,
+    \]
+  where $() \from A \to I$ is the unique morphism into the terminal object.
+\end{proposition}
+\begin{proof}
+  First, we show by induction on $n$ that the following diagram commutes.
+  \[
+    \begin{tikzcd}[column sep=40pt]
+      A^{\tensor(n+1)} \arrow[r, "A^{\tensor n}\tensor()"] \arrow[d, "A\tensor\wk^{n+1}"']
+        & A^{\tensor n} \arrow[d, "\wk^n"] \\
+      A^{\sequoid(n+1)} \arrow[r, "(A\sequoid\blank)^n()"]
+        & A^{\sequoid n}
+    \end{tikzcd}
+    \]
+  This is clearly true for $n=0$; in the general case, we have the following commutative diagram --
+  \[
+    \begin{tikzcd}[column sep=42pt]
+      A^{\tensor(n+2)} \arrow[r] \arrow[dd, "\wk^{n+2}"']
+        & A \tensor A^{\tensor (n+1)} \arrow[r, "A \tensor (A^{\tensor n}\tensor ())"] \arrow[d, "A \tensor \wk^{n+1}"']
+          & A \tensor A^{\tensor n} \arrow[r] \arrow[d, "A\tensor \wk^n"]
+            & A^{\tensor(n+1)} \arrow[dd, "\wk^{n+1}"] \\
+      %
+        & A \tensor A^{\sequoid (n+1)} \arrow[r, "A \tensor (A\sequoid\blank)^n()"] \arrow[dl, "{\wk_{A,A^{\sequoid (n+1)}}}" description]
+          & A \tensor A^{\sequoid n} \arrow[dr, "{\wk_{A,A^{\sequoid n}}}" description]
+            & \\
+      A^{\sequoid(n+1)} \arrow[rrr, "(A \sequoid \blank)^{n+1}()"]
+        &
+          &
+            & A^{\sequoid (n+1)}
+    \end{tikzcd}\,\text{--}
+    \]
+  where the middle square is the inductive hypothesis (tensored by $A$), the outer trapezia are the definitions of $\wk^{n+2}$ and $\wk^{n+1}$, and the bottom trapezium commutes because $\wk$ is a natural transformation.
+
+  Now, by the proof of Proposition \ref{PropSequoidPower}, the canonical morphism $B\tensor A^{\sequoid (n+1)} \to B\tensor A^{\sequoid n}$ must be constructed as the composite
+  \[
+    B \tensor (\eq_{n+1};(A^{\tensor n}\tensor ());\wk^n)\,,
+    \]
+  which we have shown is equal to
+  \[
+    B \tensor (\eq_{n+1};\wk^{n+1};(A \sequoid\blank)^n()) = B \tensor (A \sequoid\blank)^n()\,.\qedhere
+    \]
+\end{proof}
+
+\begin{definition}
+  Let $A$ be a game.  
+  We say that $A$ is \emph{well-opened} if initial moves of $A$ can only occur as the very first move in a play.
+\end{definition}
+
+It is immediate from the definitions that:
+\begin{itemize}
+  \item the empty game $I$ and our data-type games $\bC,\bB,\bN$ are well opened;
+  \item if $A_i$ are well-opened games, then so is $\prod_iA_i$; and
+  \item if $B$ is a well-opened game, then so is $A \implies B$;
+\end{itemize}
+but that $A \tensor B$, $A\sequoid B$ and $\oc A$ are not in general well-opened, even if $A$ and $B$ are.
+
+\begin{proposition}
+  Let $A$ be a well-opened game.  
+  Then we have natural morphisms
+  \[
+    \oc A \to A^{\sequoid n}
+    \]
+  for each $n$, and these commute with the natural morphisms $A^{\sequoid(n+1)}\to A^{\sequoid n}$ and make $\oc A$ the limit of the sequence
+  \[
+    I \leftarrow A \leftarrow A^{\sequoid 2} \leftarrow A^{\sequoid 3}\leftarrow\cdots\,.
+    \]
+  Moreover, $B\tensor\oc A$ is the limit of the sequence
+  \[
+    B \leftarrow B \tensor A \leftarrow B \tensor A^{\sequoid 2} \leftarrow B \tensor A^{\sequoid 3}\leftarrow \cdots\,.
+    \]
+\end{proposition}
+\begin{proof}
+  For the sake of notational simplicity, we will only prove the first part of the Proposition, but the second part (the $B\tensor\cdots$ version) goes through in exactly the same way.
+
+  The morphism in question is the (non-innocent) zigzag strategy given by the tree embedding $\phi_n\from P_{A^{\sequoid n}}\to P_{\oc A}$ defined by
+  \[
+    \phi_n(s) = \nabla_*(s)\,,
+    \]
+  where $\nabla\from M_A+\cdots + M_A$ is the co-diagonal.
+
+  We have seen already that the natural morphism $A^{\sequoid (n+1)}\to A^{\sequoid n}$ is the copycat morphism generated by the inclusion $n.(M_A) \to (n+1).(M_A)$, and so it is clear that these commute with $\zz_\phi$ by Proposition \ref{PropTree}.
+
+  Now let $C$ be a game and suppose that there are strategies $\sigma_n \from C \implies A^{\sequoid n}$ that commute with the natural morphisms $A^{\sequoid (n+1)} \to A^{\sequoid n}$.  
+  Then we define a morphism $\sigma\from C \to \oc A$ by
+  \[
+    \sigma = \left\{s\in P_{C\implies \oc A} \,\middle|\, \mbox{\pbox{\textwidth}{
+      for some $n$, $s\vert_{\oc A}$ contains \\
+      at most $n$ initial moves, and \\
+      $[\inj,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\in\sigma_n$.}}\right\}\,.
+    \]
+  Here we have used the fact that $A$ is well-opened to tell us that $s\vert_{\oc A}$ is indeed a valid play in $A^{\sequoid n}$.
+
+  We claim that $\sigma$ is indeed a strategy.
+  First we show that $\sigma$ is prefix closed.  
+  If $s\in \sigma$ and $t\prefix s$, write $n$ for the number of initial moves in $s$.  
+  Then $t$ has at most $n$ initial moves; if $[\id_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\in\sigma_n$, then $[\id_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(t)\in\sigma_n$, and therefore $t\in\sigma$.
+
+  Now note that if $s\in C_{C\implies \oc A}$ is such that $s\vert_{\oc A}$ contains $k$ initial moves, and if $m,n\ge k$, then
+  \[
+    [\inj,\inj_{A_1},\cdots,\inj_{A_m}]_*(s) = [\inj_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\,,
+    \]
+  since the $\sigma_n$ commute with the natural morphisms $A^{\sequoid (n+1)} \to A^{\sequoid n}$.  
+  So, if $sab,sac\in\sigma$, then we can assume that
+  \[
+    [\inj_C,\inj_{A_1},\cdots,\inj_{A_k}]_*(sab),[\inj_C,\inj_{A_1},\cdots,\inj_{A_k}]_*(sac)\in\sigma_k
+  \]
+  for some common $k$, and therefore that $b=c$.
+
+  Now we have $\sigma;\zz_{\phi_n}=\sigma_n$ for each $n$ by Proposition \ref{PropTree}.
+
+  Suppose that $\tau$ is some other strategy for $C\implies \oc A$ such that $\tau;\zz_{\phi_n}=\sigma_n$ for each $n$.  
+  Cy Proposition \ref{PropTree}, we have
+  \[
+    \sigma_n = \tau;\zz_{\phi_n} = \{s\in P_{C\implies A^{\sequoid n}}\suchthat s^{\phi_n}\in\tau\}\,.
+    \]
+  Suppose $s\in\sigma$ and that $s$ contains $n$ initial moves.  
+  Then 
+  \[
+    [\inj_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\in\sigma_n
+    \]
+  for some $n$.  
+  Therefore, $s=([\inj_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s))^{\phi_n}\in\tau$.  
+  So $\sigma\subset\tau$.
+
+  Conversely, suppose that $t\in\tau$.  
+  Suppose that $t\vert_{\oc A}$ contains $n$ initial moves.  
+  Then $t=s^{\phi_n}$ for some sequence $s\in P_{C\implies A^{\sequoid n}}$, and we must have $s\in\sigma_n$.  
+  Therefore, $t\in\sigma$.  
+  So $\tau\subset\sigma$.
+\end{proof}
+
+Therefore, by Theorem \ref{TheMtt}, if $A$ is a well-opened game, then $\oc A$ inherits the structure of a cofree commutative comonoid on $A$.
+
+Let $\G_{wo}$ denote the category of well-opened games and strategies.  
+Let $\CCom(\G)$ denote the category of commutative comonoids with respect to the symmetric monoidal structure on $\G$.
+
+In general, given two commutative comonoids $M,N$ in a symmetric monoidal category $\C$, we can form the \emph{tensor product}
+\begin{mathpar}
+  M \tensor N \to (M \tensor M) \tensor (N \tensor N) \to (M \tensor N) \tensor (M \tensor N)
+  \and
+  M \tensor N \to I \tensor I \to I\,,
+\end{mathpar}
+and this makes $\CCom(\C)$ into a \emph{Cartesian} category.
+
+Now note that we have defined a functor
+\[
+  \G_{wo} \to \CCom(\G)
+  \]
+which is a right adjoint on to its image, and therefore preserves products.  
+So if $A,B$ are well-opened games, then we get a natural isomorphism of comonoids between the tensor product of the comonoids on $\oc A$ and $\oc B$ and the comonoid on $\oc(A\times B)$.
+In particular, we have a natural isomorphism
+\[
+  \oc A \tensor \oc B \cong \oc (A \times B)\,.
+  \]
+We define a category $\G_{wo}^{\oc}$ to be the image of the functor $\G_{wo}\to \CCom(\G)$ inside $\CCom(\G)$.  
+By our discussion above, $\G_{wo}^{\oc}$ is a Cartesian category.
+
+A more convenient description of $\G_{wo}^{\oc}$ is that it is the category where the objects are well-opened games and where the morphisms
+\[
+  A \to B
+  \]
+are morphisms $\oc A \to B$ in the original category $\G$.
+We compose two such morphisms $\sigma \from \oc A \implies B$ and $\tau \from \oc B \implies C$ as
+\[
+  \oc A \xrightarrow{\sigma^\dag} \oc B \xrightarrow{\tau} C\,,
+  \]
+where the \emph{promotion} $\sigma^\dag$ of $\sigma$ comes from the description of $\oc A$ as the cofree commutative comonoid on $A$.
+
+Since the functor $\G_{wo}\to \CCom(\G)$ preserves products, $\G_{wo}^{\oc}$ obtains a Cartesian structure given by the category-theoretic product $\times$.  
+We claim that it is Cartesian closed, with the function object from $A$ to $B$ given by $\oc A \implies B$.  
+Indeed, we have
+\begin{IEEEeqnarray*}{rCl}
+  \G_{wo}^{\oc}(A,\oc B\implies C)
+  & \cong & \G(\oc A,\oc B \implies C) \\
+  & \cong & \G(\oc A \tensor \oc B,C) \\
+  & \cong & \G(\oc(A \times B),C) \\
+  & \cong & \G_{wo}^{\oc}(A\times B,C)\,.
+\end{IEEEeqnarray*}
+
+We have one thing left to prove.
+\begin{proposition}
+  Let $\sigma\from \oc A \implies B$, $\tau\from \oc B \implies C$ be innocent strategies, where $A,B,C$ are well-opened games.  
+  Then the composite of $\sigma$ and $\tau$ in $\G_{wo}^{\oc}$ is an innocent strategy.
+\end{proposition}
+\begin{proof}
+  We may write this composite as
+  \[
+    \oc A \xrightarrow{m}
+    \oc \oc A \xrightarrow{\oc\sigma}
+    \oc B \xrightarrow{\tau}\,,
+    \]
+  where $\oc\sigma$ is the strategy formed by playing $\sigma$ in parallel with itself, whereas $m\from \oc A \to \oc \oc A$ comes from the fact that $\oc A$ is the cofree commutative comonoid on $A$.
+  $\oc \sigma$ is innocent for the same reasons as in Proposition \ref{PropTensorInnocent}, so it suffices to show that $m$ is innocent.
+
+  Indeed, it is clear from our definitions that $\oc\oc A = \oc A$ as games.  
+  Then, $m$ is in fact the identity strategy between these two games, so is innocent.
+\end{proof}
+
+\subsection{The Exponential as a Final Coalgebra}
+
+\begin{definition}
+  Let $F \from \C \to \C$ be a functor.  
+  A \emph{coalgebra for $F$} or \emph{$F$-coalgebra} is an object $a$ of $\C$, together with a morphism $f\from a \to Fa$.
+
+  A \emph{coalgebra homomophism} from $(a,f)$ to $(b,g)$ is a morphism $h\from a \to b$ such that the following diagram commutes.
+  \[
+    \begin{tikzcd}
+      a \arrow[r, "f"] \arrow[d, "h"']
+        & Fa \arrow[d, "Fh"] \\
+      b \arrow[r, "g"]
+        & Fb
+    \end{tikzcd}
+    \]
+
+  Clearly, the coalgebras for a given functor $F$ form a category.  
+  A \emph{final coalgebra} for $F$ is a terminal object for this category; i.e., an $F$-coalgebra $(t,\alpha)$ such that for all $F$-coalgebras $(a,f)$ there is a unique morphism $\fcoal f \from a \to t$ such that the following diagram commutes.
+  \[
+    \begin{tikzcd}
+      a \arrow[r, "f"] \arrow[d, "\fcoal f"']
+        & Fa \arrow[d, "F\fcoal f"] \\
+      t \arrow[r, "\alpha"]
+        & Ft
+    \end{tikzcd}
+    \]
+\end{definition}
+We call $\fcoal f$ the \emph{anamorphism} of $f$.
+
+We use two standard pieces of theory about coalgebras.
+
+\begin{theorem}[Lambek's Theorem, \cite{Lambek}]
+  If $(t,\alpha)$ is a final coalgebra for a functor $F$, then $\alpha\from t \to Ft$ is an isomorphism with inverse given by $\fcoal{F\alpha}$.
+\end{theorem}
+
+\begin{theorem}[Ad{\'{a}}mek's Theorem, {\cite{Adamek}}]
+  Suppose $\C$ has a terminal object $1$.  
+  By repeatedly applying $F$ to the morphism $F1 \to 1$, we build up a sequence
+  \[
+    1 \leftarrow F1 \leftarrow F^2 1 \leftarrow F^31 \leftarrow \cdots\,.
+    \]
+  If this sequence has a limit $F^{\omega}1$, and if the morphism $\beta\from F(F^{\omega}1) \to F^{\omega}1$ induced from the univeral property of the limit is an isomorphism, then $(F^{\omega}1,\beta\inv)$ is a final coalgebra for $F$.
+\end{theorem}
+
+Now we have already shown that if $A$ is well-opened, then $\oc A$ is the limit of the sequence
+\[
+  I \leftarrow A \leftarrow A^{\sequoid 2} \leftarrow A^{\sequoid 3} \leftarrow \cdots\,,
+  \]
+and this sequence is precisely the sequence from Ad{\'a}mek's Theorem, when $F=J(A\sequoid\blank) \from \G \to \G$.
+Moreover, this limit is preserved when taking the sequoid with $A$ on the left, and so we get that
+\begin{corollary}
+  If $A$ is a well-opened game, then $\oc A$ is the final coalgebra for the functor $A \sequoid \blank$.
+\end{corollary}
+In this case, the morphism $\oc A \to A \sequoid \oc A$ is the zigzag strategy that plays copycat between the different copies of $A$; i.e., $\zz_\phi$, where $\phi\from P_{A\sequoid \oc A} \to P_{\oc A}$ is the tree isomorphism given by
+\[
+  \phi(s) = [\inj_{M_A},\id]_*(s)\,.
+  \]
+
+\subsection{Denotational Semantics of Idealized Algol}
+
+We now come to interpret Idealized Algol within our category $\G_{wo}^{\oc}$.  
+The base types $\com$, $\bool$ and $\nat$ are interpreted by the games $\bC$, $\bB$ and $\bN$, while the type $\Var$ is interpreted by the game
+\[
+  \Varr = \bC^{\bN} \times \bN\,,
+  \]
+where $\bC^{\bN}$ is the product of $\bN$-many copies of $\bC$.
+Given types $S,T$, the denotation $\deno{S\to T}$ of the type of functions from $S$ to $T$ is given by
+\[
+  \deno{S}\to\deno{T} \coloneqq \oc\deno{S}\implies\deno{T}\,.
+  \]
+This gives us the denotation of the types of Idealized Algol.
+
+We inductively define a denotation of terms-in-context $\Gamma\ts M$ of IA, where $\deno{x_1\from T_1,\cdots,x_n\from T_n\ts M\from T}$ is a strategy
+\[
+  \deno{T_1} \times \cdots \times \deno{T_n} \to \deno{T}\,.
+  \]
+First note that we have natural innocent strategies $a \from \bC$, $\true,\false\from\bB$ and $n \from \bN$, which give us the denotations of $\Gamma\ts\skipp$, $\Gamma\ts\true$, $\Gamma\ts\false$ and $\Gamma\ts n$.
+
+Moreover, if we have a strategy
+
+\[
+  \deno{\Gamma,x\from S \ts M\from T} \from \deno{\Gamma}\times\deno{S} \to \deno{T}\,,
+  \]
+then, since $\G_{wo}^{\oc}$ is Cartesian closed, we get a strategy
+\[
+  \deno{\Gamma\ts \lambda x^s.M} \from \deno{\Gamma} \to \deno {S} \to \deno{T}\,.
+  \]
+In addition, we have natural morphisms
+\[
+  \deno{\Gamma,x\from T\ts x\from T} = \deno{\Gamma}\times\deno{T} \xrightarrow{\pr_{\deno{T}}} \deno{T}\,.
+  \]
+Lastly, if we have strategies
+\begin{mathpar}
+  \deno{\Gamma\ts M\from S \to T} \from \deno{\Gamma} \to \deno{S} \to \deno{T}
+  \and
+  \deno{\Gamma\ts N \from S} \from \deno{\Gamma} \to \deno{S}\,,
+\end{mathpar}
+then we get a strategy
+\[
+  \deno{\Gamma\ts MN\from T} = \deno \Gamma \xrightarrow{\Delta} \deno\Gamma\times\deno\Gamma \xrightarrow{\deno{\Gamma\ts M}\times\deno{\Gamma\ts N}} (\deno S \to \deno T) \times \deno S \xrightarrow{\ev} \deno{S}\,.
+  \]
+
+In order to form the denotation of the next lot of terms, we need a new definition.
+\begin{definition}
+  Let $X$ be a set, and let $(\sigma_x\suchthat x\in X)$ be a collection of strategies for a game $A$.  
+  Write $X$ for the datatype game corresponding to $X$.  
+  Then we define a strict strategy $(\sigma_x) \from X \to A$ by
+  \[
+    (\sigma_x) = \{\epsilon\}\cup\{*q\suchthat {*}\in P_A\}\cup \{*qys\suchthat {*}s\in\sigma_y\}\,.
+    \]
+  In other words, after the initial move in $A$, $(\sigma_x)$ requests some element $y\in X$, and thereafter plays according to $\sigma_y$ in $A$.
+\end{definition}
+
+\begin{proposition}
+  If the $\sigma_x$ are innocent strategies, then $(\sigma_x)$ is an innocent strategy.
+\end{proposition}
+\begin{proof}
+  If $*s\in\sigma_y$, then $\pv{*qysa}=*qy\pv{sa}$.  
+  Then, if $t\in(\sigma_x)$ and $\pv{ta}=*qy\pv{sa}$, we have $t=*qyt'$ for $t'\in\sigma_y$ and $\pv{*t'a}=\pv{*sa}$.  
+  So if $*sab\in\sigma_y$, then $*t'ab\in\sigma_y$ and therefore $tab\in(\sigma_x)$.
+\end{proof}
+
+Now we define morphisms
+\begin{itemize}
+  \item $\seq_X = (\id_X) \from \bC \to (X \to X)$;
+  \item $\If_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y) \from \bB \to (X \to X \to X)$;
+  \item $\suc = (1, 2, 3, 4,\cdots) \from \bN \to \bN$;
+  \item $\pred = (0,0,1,2,\cdots)\from \bN \to \bN$;
+  \item $\IfO_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y,\lambda x.\lambda y.y,\cdots)\from \bN \to (X \to X \to X)$;
+  \item $\dereff = \pr_\bN \from \Varr \to \bN$;
+  \item $\assign = (\pr_0,\pr_1,\cdots) \from \bN \to (\Varr \to \bC)$; and
+  \item $\mkvar = \lambda w.\lambda r.\langle (w\,n)_{n\in\bN},r\rangle \from (\bN \to \bC) \to \bN \to \Varr$.
+\end{itemize}
+These give us an obvious way to interpret most of the rest of the terms of Idealized Algol.  
+For example, if we have strategies
+\begin{mathpar}
+  \deno{\Gamma\ts V\from \Varr}
+  \and
+  \deno{\Gamma\ts E\from \bN}\,,
+\end{mathpar}
+then we get a strategy
+\[
+  \deno{\Gamma\ts V\gets E \from \bC} = \deno{\Gamma} \xrightarrow{\Delta} \deno{\Gamma}\times\deno{\Gamma} \xrightarrow{\deno{\Gamma\ts E}\times\deno{\Gamma\ts V}} \bN \times \Varr \xrightarrow{\assign} \bC\,.
+  \]
+
+\subsection{Order-Enrichment of $\G$}
+
+The remaining parts of Idealized Algol that we have yet to define are the fixpoint combinator $\Y_T$ and the new variable constructor $\neww$.
+
+To define $\Y_T$, we use order-enriched properties of $\G$.
+
+Note that if $A$ is a game, then we can order the strategies for $A$ by subset inclusion.  
+Then this order is clearly preserved by composition.
+
+\begin{proposition}
+  The partial order of strategies for $A$ is directed-complete.  
+  So is the partial order of innocent strategies for $A$.
+\end{proposition}
+\begin{proof}
+  Let $\Sigma$ be a directed set of strategies for $A$; so if $\sigma,\tau\in\Sigma$ then there is some $\upsilon\in\Sigma$ such that $\sigma\subset\upsilon$ and $\tau\subset\upsilon$.  
+  We claim that $\bigcup\Sigma$ is a strategy for $A$.  
+  Indeed, it is certainly even-prefix-closed, and if $sab,sac\in\Sigma$, then $sab\in\sigma$ and $sac\in\tau$ for $\sigma,\tau\in\Sigma$, and therefore $sab,sac\in\upsilon$ for some $\upsilon\in\Sigma$ and so $b=c$.
+
+  Now suppose that all $\sigma\in\Sigma$ are innocent.
+  Let $sab\in\bigcup\Sigma$ and suppose that $t\in \bigcup\Sigma$ is such that $\pv{ta}=\pv{sa}$.  
+  Then, as before, we have $sab,t\in\upsilon$ for some innocent $\upsilon\in\Sigma$, and therefore $tab\in\upsilon\subset\bigcup\Sigma$.
+\end{proof}
+
+It is clear then that composition of strategies is Scott-continuous with respect to this ordering.
+
+Writing $\bot = \{\epsilon\}$ for the bottom strategy for a game $A$, if we have a strategy $\sigma\from A \to A$, then the Kleene fixed point theorem tells us that we may construct a fixed point for $\sigma$ as the union of the chain
+\[
+  \bot \subset \bot;\sigma \subset \bot;\sigma;\sigma \subset \cdots\,.
+  \]
+Given a game $A$, we define a strategy $\Y_A\from (A \to A) \to A$ as the fixed point of the strategy
+\[
+  \lambda F.\lambda f.f(Ff) \from ((A \to A) \to A) \to (A \to A) \to A\,.
+  \]
+We can then use $\Y_A$ to interpret the term $\Gamma\ts\Y_TM\from T$ for any term $\Gamma\ts M\from T\to T$.
+
+We will later require other order-theoretic properties of the set of strategies for a game $A$.  
+Recall that an element $\sigma$ of a directed-complete partially ordered set is called \emph{compact} if whenever we have $\sigma = \bigcup\Sigma$ for some directed set $\Sigma$, then $\sigma\in\Sigma$.
+
+A little thought convinces us that a strategy $\sigma\from A$ is compact if and only if it is finite as a set of plays; indeed, suppose $\sigma$ is a finite set and $\sigma=\bigcup\Sigma$.  
+For each $s\in\sigma$, we have $s\in\tau_s$ for some $\tau_s\in\Sigma$; since $\Sigma$ is directed, then there is some $\upsilon\in\Sigma$ such that $\tau_s\in\Sigma$ for each $s$, and therefore $\sigma\subset\upsilon\subset\sigma$.
+Conversely, if $\sigma$ is infinite, then by K\"{o}nig's lemma, it either has an infinite branching point (i.e., $s\in\sigma$ such that there are infinitely many plays $sab\in\sigma$) or an infinite branch (i.e., an infinite increasing sequence $s_1\prefix s_2\prefix \cdots$ in $\sigma$).
+In either case, it is easy to construct some directed set $\Sigma$ such that $\sigma=\bigcup\Sigma$ but $\sigma\not\in\Sigma$.
+
+Recall that a directed-complete partial order $P$ is said to be \emph{algebraic} if whenever $p\in P$, the set of compact elements of $P$ lying below $p$ is directed and its supremum is $p$.
+
+\begin{proposition}
+  The set of strategies for a game $A$ is an algebraic directed-complete partial order.
+\end{proposition}
+\begin{proof}
+  Let $\sigma$ be a strategy for a game $A$ and let $\tau_1,\tau_2$ be two finite sub-strategies such that $\tau_1,\tau_2\subset\sigma$.  
+  Then $\tau_1\cup\tau_2\subset\sigma$ and is finite; moreover, if $sab,sac\in\tau_1\cup\tau_2$, then $sab,sac\in\sigma$, so $b=c$.
+
+  Lastly, given any $s\in\sigma$, there is a compact strategy $\sigma_s$ containing $s$; namely
+  \[
+    \sigma_s = \{t\suchthat \text{$t\prefix s$ has even length}\}\,.\qedhere
+    \]
+\end{proof}
+
+\subsection{The Strategy $\cell$}
+
+Now we come to the denotation of $\neww$.  
+For this, we shall define a strategy $\cell\from \oc\bN \implies \oc \Varr$ by using the property of $\oc \Varr$ as a final coalgebra.
+
+Given $n\in\bN$, we define a strategy $\wwrite_n\from \oc\bN \implies \bC \sequoid\oc\bN$ by
+\[
+  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
+  \]
+Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
+Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
+\[
+  \oc\bN \xrightarrow{\langle (\wwrite_n)_{n\in\bN}, \rread\rangle}
+  (\bC \sequoid \oc\bN)^{\bN} \times (\bN \sequoid \oc\bN) \xrightarrow{\dist_{(\bC)_{\bN},\bN,\oc\bN}\inv}
+  (\bC^\bN \times \bN) \sequoid \oc\bN = \Varr \sequoid \oc \bN\,.
+  \]
+We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
+\[
+  \begin{tikzcd}
+    \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
+      & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
+    \oc\Varr \arrow[r, "\alpha_{\Varr}"]
+      & \Varr \sequoid \oc\Varr
+  \end{tikzcd}
+  \]
+Concretely, the strategy $\cell$ behaves as follows.  
+When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
+If he plays the initial move $q_n$ in the $n$-th copy of $\bC$, player $P$ updates the value she has stored in her head to $n$.  
+If he plays the initial move $q$ in $\bN$, then player $P$ replies with this stored value.  
+Lastly, if he plays this initial move $q$ without having played in any of the copies of $\bC$, then player $P$ interrogates the argument in order to find out which value to play.
+
+This strategy $\cell$ now gives us a morphism $\neww_A \from \oc(\oc\Varr \implies A) \implies A$ given by
+\begin{IEEEeqnarray*}{rCl}
+  \oc(\oc\Varr\implies A) & \xrightarrow{\mathmakebox[50pt]{\der}} & (\oc\Varr\implies A) \\
+  & \xrightarrow{\mathmakebox[50pt]{\lunit}} & I \tensor (\oc\Varr\implies A) \\
+  & \xrightarrow{\mathmakebox[50pt]{\oc0\tensor (\oc\Varr\implies A)}} & \oc\bN \tensor (\oc \Varr\implies A) \\
+  & \xrightarrow{\mathmakebox[50pt]{\cell\tensor (\oc\Varr\implies A)}} & \oc\Varr \tensor (\oc \Varr \implies A) \\
+  & \xrightarrow{\mathmakebox[50pt]{\ev}} & A\,.
+\end{IEEEeqnarray*}
+
+We use this to provide the denotation of the term $\neww$.
+
+\subsection{Big-Step Operational Semantics of Idealized Algol}
+
+We now introduce the operational semantics of Idealized Algol, so that we can prove soundness and adequacy of our semantics for it.
+
+We first define a \emph{canonical form} of the language to be
+\begin{itemize}
+  \item at type $\com$, the term $\skipp$;
+  \item at type $\bool$, the terms $\true$ and $\false$;
+  \item at type $\nat$, the numerals $n$; 
+  \item at type $\Var$, variable names $x$ of type $\Var$ and expressions of the form $\mkvar W\,R$; and
+  \item at type $S\to T$, expressions of the form $\lambda x^S.M$.
+\end{itemize}
+
+We define a \emph{$\Var$-context} to be a context $\Gamma$ of the form $x_1\from \Var,\cdots,x_n\from \Var$.
+Given a $\Var$-context $\Gamma$, we define a \emph{$\Gamma$-store} to be a function $s$ from the variable names occurring in $\Gamma$ to the natural numbers.  
+Given such a store $s$, we write $(s\vert x \mapsto n)$ for the store given by
+\[
+  (s\vert x\mapsto n)(y) = \begin{cases}
+    n & \text{if $y = x$} \\
+    s(y) & \text{otherwise}
+  \end{cases}\,.
+  \]
+We now inductively define a relation $\Gamma,s\ts M\converges c,s'$, where
+\begin{itemize}
+  \item $\Gamma$ is a $\Var$-context; 
+  \item $s$ and $s'$ are $\Gamma$-stores;  and
+  \item $\Gamma\ts M$, $\Gamma\ts c$ are Idealized Algol terms-in-context, where $c$ is a canonical form.
+\end{itemize}
+The definition of this relation is shown in Figure \ref{FigIaOpSem}.
+
+\begin{figure}
+  \begin{mathpar}
+    \inferrule*{ }{\Gamma,s\ts c \converges c,s}
+    \and
+    \inferrule*{\Gamma,s \ts M \converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x] \converges c,s''}{\Gamma,s \ts MN \converges c,s''}
+    \and
+    \inferrule*{\Gamma,s \ts M(\Y M) \converges c,s'}{\Gamma,s \ts \Y M \converges c,s'}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges n,s'}{\Gamma,s\ts \suc M \converges n+1,s'}
+    \\\and
+    \inferrule*{\Gamma,s\ts M \converges n+1,s'}{\Gamma,s\ts \pred M \converges n,s'}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges 0,s'}{\Gamma,s\ts \pred M \converges 0,s'}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges \skipp,s' \\ \Gamma,s'\ts N \converges c,s''}{\Gamma,s \ts M;N \converges c,s''}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges \true,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges \false,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges 0,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges n+1,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
+    \and
+    \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges n,s' \\ \Gamma,s' \ts V \converges x,s''}{\Gamma,s\ts V \gets E \converges \skipp,(s''\vert x \mapsto n)}
+    \and
+    \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges x,s'}{\Gamma,s\ts !V \converges n,s'}
+    \and
+    \inferrule*{\Gamma,x\from\Var,(s\vert x\mapsto 0)\ts M \converges c,(s'\vert x\mapsto n)}{\Gamma,s\ts \neww \lambda x.M \converges c,s'}
+    \and
+    \inferrule*{\Gamma,s\ts E \converges n,s' \\ \Gamma,s'\ts V \converges \mkvar W R,s'' \\ \Gamma,s'' \ts Wn \converges \skipp,s'''}
+    {\Gamma,s \ts V\gets E \converges \skipp,s'''}
+    \and
+    \inferrule*{\Gamma,s\ts V \converges \mkvar W R,s' \\ \Gamma,s'\ts R \converges n,s''}{\Gamma,s\ts !V \converges n,s''}
+  \end{mathpar}
+  \caption[Operational semantics for Idealized Algol.]{Operational semantics for Idealized Algol. See \cite{RusssThesis} and \cite{SamsonGuyIAActive}.}
+  \label{FigIaOpSem}
+\end{figure}
+
+\subsection{Small-Step Operational Semantics of Idealized Algol}
+
+We also give a small-step operational semantics for Idealized Algol, which will sometimes be easier to work with.
+
+This time, instead of defining a relation $\Gamma,s\ts M\converges c,s'$, we define a relation $\Gamma,s\ts M\opto \Gamma',s'\ts M'$, where
+\begin{itemize}
+  \item $\Gamma,\Gamma'$ are $\Var$-contexts; 
+  \item $s$ is a $\Gamma$-store and $s'$ a $\Gamma'$-store;  and
+  \item $\Gamma\ts M$, $\Gamma'\ts M'$ are Idealized Algol terms-in-context.
+\end{itemize}
+
+The definition of the relation is in Figure \ref{FigIaSsOpSem}.
+As an auxiliary definition, we need the notion of an \emph{evaluation context} (see \cite{Felleisen}).
+This is a single-holed context defined inductively by the following BNF formula, where $M$ ranges over IA terms.
+\begin{center}
+\parbox{0.7\textwidth}{
+\begin{mathpar}
+  E \Coloneqq - \mid \suc E \mid \pred E \mid E;M \mid \If E\Then M \Else M \mid \IfO E \Then M \Else M \mid !E \mid M \gets E \mid E \gets n
+\end{mathpar}}
+\end{center}
+
+\begin{figure}
+  \begin{mathpar}
+    \inferrule*{\Gamma,s\ts M \opto \Gamma',s',M'}{\Gamma,s\ts E[M] \opto \Gamma',s'\ts E[M']}
+    \\
+    \inferrule*{ }{\Gamma,s\ts (\lambda x.M)N \opto \Gamma,s\ts M[N/x]}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \Y M \opto \Gamma,s\ts M(\Y M)}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \succ n \opto \Gamma,s\ts n+1}
+    \and
+    \inferrule*{ }{\Gamma,s \ts \pred n+1 \opto \Gamma,s\ts n}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \pred 0 \opto \Gamma,s\ts 0}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \skipp;M \opto \Gamma,s\ts M}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \If \true \Then N \Else P \opto \Gamma,s\ts N}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \If \false \Then N \Else P \opto \Gamma,s\ts P}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \IfO 0 \Then N \Else P \opto \Gamma,s\ts N}
+    \and
+    \inferrule*{ }{\Gamma,s\ts \IfO n+1 \Then N \Else P \opto \Gamma,s\ts P}
+    \and
+    \inferrule*{ }{\Gamma,s\ts x \gets n \opto \Gamma,(s\vert x\mapsto n)\ts \skipp}
+    \and
+    \inferrule*[right={$s(x)=n$}]{ }{\Gamma,s\ts \oc x \opto \Gamma,s\ts n}
+    \\
+    \inferrule*{ }{\Gamma,s\ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0)\ts M}
+    \\
+    \inferrule*{ }{\Gamma,s \ts \mkvar W\,R \gets n \opto \Gamma,s\ts Wn}
+    \and
+    \inferrule*{ }{\Gamma,s \ts \oc\mkvar W\,R \opto \Gamma,s\ts R}
+  \end{mathpar}
+  \caption{Felleisen-style small-step operational semantics for Idealized Algol.}
+  \label{FigIaSsOpSem}
+\end{figure}
+
+We need to prove that this is equivalent to our original semantics.
+
+\begin{proposition}
+  Let $\Gamma$ be a $\Var$-context, let $s$ be a $\Gamma$-store, and let $\Gamma\ts M$ be an Idealized Algol term-in-context.  
+  If $s'$ is another $\Gamma$-store and $\Gamma\ts c$ is a canonical form, then $\Gamma,s\ts M\converges c,s'$ if and only if there is some sequence
+  \[
+    \Gamma,s\ts M \opto \Gamma_1,s^{(1)},M_1 \opto \cdots \opto \Gamma_n,s^{(n)},M_n \opto \Gamma'',s'',c\,,
+    \]
+  where $\Gamma_1,\cdots,\Gamma_n,\Gamma''$ are $\Var$-contexts, $s^{(i)}$ is a $\Gamma_i$-store, $s''$ is a $\Gamma''$-store, $\Gamma_i\ts M_i$ are Idealized Algol terms in context, and $s''\vert_\Gamma=s'$.
+\end{proposition}
+\begin{proof}
+  First, suppose that we have some sequence $\Gamma,s\ts M\opto\cdots\opto \Gamma'',s'',c$, where $s''\vert_\Gamma=\s'$.  
+  We construct a derivation of $\Gamma,s\ts M\converges c,s'$ by induction on the length of this sequence.
+
+  If the sequence has length $0$, then we can use the rule for the canonical form; i.e.
+  \[
+    \inferrule*{ }{\Gamma,s\ts c\converges c,\skipp}\,.
+    \]
+  Otherwise, suppose that the sequence starts $\Gamma,s\ts M\converges \Gamma_1,s^{(1)}\ts M_1$, and that we already have a derivation of
+  \[
+    \Gamma_1,s^{(1)} \ts M_1 \opto c,s''\vert_{\Gamma_1}\,.
+    \]
+  We split into cases based on the rule used for $\Gamma,s\ts M\converges \Gamma_1,s^{(1)}$.
+
+\end{proof}
+
+\subsection{Soundness}
 

### 2019-03-28 Thesis/games.tex
Nightly commit.

@@
 
-The definition of the relation is in Figure \ref{FigIaSsOpSem}.
 As an auxiliary definition, we need the notion of an \emph{evaluation context} (see \cite{Felleisen}).
@@
 \begin{center}
-\parbox{0.7\textwidth}{
-\begin{mathpar}
-  E \Coloneqq - \mid \suc E \mid \pred E \mid E;M \mid \If E\Then M \Else M \mid \IfO E \Then M \Else M \mid !E \mid M \gets E \mid E \gets n
+\parbox{0.8\textwidth}{
+\begin{mathpar}
+  \EE \Coloneqq - \mid \EE\,M \mid \suc \EE \mid \pred \EE \mid \EE;M \mid \If \EE\Then M \Else M \mid \IfO \EE \Then M \Else M \mid !\EE \mid M \gets \EE \mid \EE \gets n
 \end{mathpar}}
@@
 
+Next, we define a relation $\Gamma,s,M\oopto\Gamma',s',M'$ as in Figure \ref{FigIaSsOpSem}.
+
+We then define the relation $\opto$ as
+\[
+  \inferrule*{ \Gamma,s\ts M\oopto \Gamma',s'\ts M'}{\Gamma,s\ts \EE[M] \opto \EE[M']}
+  \]
+for each evaluation context $\EE$.
+
 \begin{figure}
   \begin{mathpar}
-    \inferrule*{\Gamma,s\ts M \opto \Gamma',s',M'}{\Gamma,s\ts E[M] \opto \Gamma',s'\ts E[M']}
+    \Gamma,s\ts (\lambda x.M)N \oopto \Gamma,s\ts M[N/x]
+    \and
+    \Gamma,s\ts \Y M \oopto \Gamma,s\ts M(\Y M)
+    \and
+    \Gamma,s\ts \suc n \oopto \Gamma,s\ts n+1
     \\
-    \inferrule*{ }{\Gamma,s\ts (\lambda x.M)N \opto \Gamma,s\ts M[N/x]}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \Y M \opto \Gamma,s\ts M(\Y M)}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \succ n \opto \Gamma,s\ts n+1}
-    \and
-    \inferrule*{ }{\Gamma,s \ts \pred n+1 \opto \Gamma,s\ts n}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \pred 0 \opto \Gamma,s\ts 0}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \skipp;M \opto \Gamma,s\ts M}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \If \true \Then N \Else P \opto \Gamma,s\ts N}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \If \false \Then N \Else P \opto \Gamma,s\ts P}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \IfO 0 \Then N \Else P \opto \Gamma,s\ts N}
-    \and
-    \inferrule*{ }{\Gamma,s\ts \IfO n+1 \Then N \Else P \opto \Gamma,s\ts P}
-    \and
-    \inferrule*{ }{\Gamma,s\ts x \gets n \opto \Gamma,(s\vert x\mapsto n)\ts \skipp}
-    \and
-    \inferrule*[right={$s(x)=n$}]{ }{\Gamma,s\ts \oc x \opto \Gamma,s\ts n}
+    \Gamma,s \ts \pred n+1 \oopto \Gamma,s\ts n
+    \and
+    \Gamma,s\ts \pred 0 \oopto \Gamma,s\ts 0
     \\
-    \inferrule*{ }{\Gamma,s\ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0)\ts M}
+    \Gamma,s\ts \skipp;M \oopto \Gamma,s\ts M
     \\
-    \inferrule*{ }{\Gamma,s \ts \mkvar W\,R \gets n \opto \Gamma,s\ts Wn}
-    \and
-    \inferrule*{ }{\Gamma,s \ts \oc\mkvar W\,R \opto \Gamma,s\ts R}
+    \Gamma,s\ts \If \true \Then N \Else P \oopto \Gamma,s\ts N
+    \and
+    \Gamma,s\ts \If \false \Then N \Else P \oopto \Gamma,s\ts P
+    \and
+    \Gamma,s\ts \IfO 0 \Then N \Else P \oopto \Gamma,s\ts N
+    \and
+    \Gamma,s\ts \IfO n+1 \Then N \Else P \oopto \Gamma,s\ts P
+    \and
+    \Gamma,s\ts x \gets n \oopto \Gamma,(s\vert x\mapsto n)\ts \skipp
+    \and
+    \Gamma,s\ts \oc x \oopto \Gamma,s\ts s(x)
+    \\
+    \Gamma,s\ts \neww \lambda x.M \oopto \Gamma,x,(s\vert x\mapsto 0)\ts M
+    \\
+    \Gamma,s \ts (\mkvar W\,R) \gets n \oopto \Gamma,s\ts Wn
+    \and
+    \Gamma,s \ts \oc(\mkvar W\,R) \oopto \Gamma,s\ts R
   \end{mathpar}
@@
 
-\begin{proposition}
-  Let $\Gamma$ be a $\Var$-context, let $s$ be a $\Gamma$-store, and let $\Gamma\ts M$ be an Idealized Algol term-in-context.  
-  If $s'$ is another $\Gamma$-store and $\Gamma\ts c$ is a canonical form, then $\Gamma,s\ts M\converges c,s'$ if and only if there is some sequence
-  \[
-    \Gamma,s\ts M \opto \Gamma_1,s^{(1)},M_1 \opto \cdots \opto \Gamma_n,s^{(n)},M_n \opto \Gamma'',s'',c\,,
-    \]
-  where $\Gamma_1,\cdots,\Gamma_n,\Gamma''$ are $\Var$-contexts, $s^{(i)}$ is a $\Gamma_i$-store, $s''$ is a $\Gamma''$-store, $\Gamma_i\ts M_i$ are Idealized Algol terms in context, and $s''\vert_\Gamma=s'$.
-\end{proposition}
-\begin{proof}
-  First, suppose that we have some sequence $\Gamma,s\ts M\opto\cdots\opto \Gamma'',s'',c$, where $s''\vert_\Gamma=\s'$.  
-  We construct a derivation of $\Gamma,s\ts M\converges c,s'$ by induction on the length of this sequence.
-
-  If the sequence has length $0$, then we can use the rule for the canonical form; i.e.
-  \[
-    \inferrule*{ }{\Gamma,s\ts c\converges c,\skipp}\,.
-    \]
-  Otherwise, suppose that the sequence starts $\Gamma,s\ts M\converges \Gamma_1,s^{(1)}\ts M_1$, and that we already have a derivation of
-  \[
-    \Gamma_1,s^{(1)} \ts M_1 \opto c,s''\vert_{\Gamma_1}\,.
-    \]
-  We split into cases based on the rule used for $\Gamma,s\ts M\converges \Gamma_1,s^{(1)}$.
-
+\begin{lemma}
+  Suppose that $\Gamma,s\ts M \oopto \Gamma',s'\ts M'$ and that $\Gamma',s'\ts \EE[M'] \converges c,s''$.  
+  Then $\Gamma,s\ts \EE[M]\converges c,s''\vert_\Gamma$.
+  \label{LemSmallToBig}
+\end{lemma}
+\begin{proof}
+  Structural induction on $\EE$.
+  The base case, when $\EE$ is a hole, covers the interesting cases, so we shall leave it to last.
+  The remaining cases are quite similar, so we will show the proof for one of them for illustration.
+
+  If $\EE=\EE'\,N$, for some term $N$, then we have $\Gamma',s'\ts \EE'[M']\,N\converges c,s''$.  
+  By inspection of the rules in Figure \ref{FigIaOpSem}, the derivation of this must end with a rule of the form
+  \[
+    \inferrule*{\Gamma',s'\ts \EE'[M'] \converges \lambda x.M'',t \\ \Gamma',t \ts M''[N/x] \converges c,s''}
+    {\Gamma',s'\ts \EE'[M']\,N \converges c,s''}\,.
+    \]
+  Thus, $\Gamma',s'\ts \EE'[M']\converges \lambda x.M'',t$ must be provable for some $M'',t$.
+  By the induction hypothesis, this means that $\Gamma,s\ts \EE'[M]\converges \lambda x.M'',t$ is provable.
+  Then we have a derivation
+  \[
+    \inferrule*{\Gamma',s\ts \EE'[M] \converges \lambda x.M'',t \\ \Gamma',t \ts M''[N/x] \converges c,s''}
+    {\Gamma',s\ts \EE'[M]\,N\converges c,s''\vert_{\Gamma'}}\,.
+    \]
+  Then, because any extra variables in $\Gamma'$ are not mentioned in $\EE'[M]\,N$ or in $c$, we have
+  \[
+    \Gamma,s\ts \EE'[M]\,N\converges c,s''\vert_\Gamma\,.
+    \]
+  Now, let us suppose that $\EE$ is a hole, so that $\EE[M']=M'$.
+
+  Then there are a number of cases, depending on the particular $\oopto$ rule we are using.  
+  Many of these cases are similar, so we will cover a few of them for the purposes of illustration.
+  \begin{itemize}
+    \item Suppose that $\Gamma,s\ts M[N/x]\converges c,s'$.  
+      Then we have a derivation
+      \[
+        \inferrule*
+        {
+          \inferrule*
+          {
+          }
+          {
+            \Gamma,s \ts \lambda x.M \converges \lambda x.M,s
+          }
+          \\
+          \Gamma,s\ts M[N/x] \converges c,s'
+        }
+        {
+          \Gamma,s\ts (\lambda x.M)N \converges c,s'
+        }\,.
+        \]
+    \item We have a derivation
+      \[
+        \inferrule*
+        {
+          \inferrule*
+          {
+          }
+          {
+            \Gamma,s\ts x\converges x,s
+          }
+          \\
+          \inferrule*
+          {
+          }
+          {
+            \Gamma,s\ts n\converges n,s
+          }
+        }
+        {
+          \Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)
+        }\,.
+        \]
+    \item We have a derivation
+      \[
+        \inferrule*
+        {
+          \inferrule*
+          {
+          }
+          {
+            \Gamma,s\ts x \converges x,s'
+          }
+        }
+        {
+          \Gamma,s\ts \oc x\converges s(x),s
+        }\,.
+        \]
+    \item Suppose that $\Gamma,x,(s\vert x\mapsto 0) \ts M\converges c,s'$.  
+      Then we have a derivation
+      \[
+        \inferrule*
+        {
+          \Gamma,x,(s\vert x\mapsto 0) \ts M \converges c,s'
+        }
+        {
+          \Gamma,s\ts \neww\lambda x.M \converges c,s'\vert_\Gamma
+        }\,,
+        \]
+      since $s'=(s'\vert_\Gamma\vert x\mapsto s'(x))$.\qedhere
+  \end{itemize}
+\end{proof}
+
+We have proved:
+
+\begin{proposition}
+  Suppose that we have a sequence
+  \[
+    \Gamma_1,s^{(1)},M_1\opto\cdots\opto\Gamma_n,s^{(n)},M_n\,,
+    \]
+  where $M_n$ is a canonical form.  
+  Then $\Gamma_1,s^{(1)} \ts M_1\converges M_n,s^{(n)}\vert_{\Gamma_1}$.  
+  \label{PropSmallToBig}
+\end{proposition}
+\begin{proof}
+  Induction on $n$.  
+  The inductive step is Lemma \ref{LemSmallToBig}, while the base case ($n=1$) is given by the derivation
+  \[
+    \inferrule*{ }
+    {\Gamma,s\ts c\converges c,s}\,.\qedhere
+    \]
+\end{proof}
+
+We can also prove the converse.
+
+\begin{proposition}
+  Suppose that $\Gamma,s\ts M\converges c,s'$.  
+  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
+  \[
+    \Gamma_1,s^{(1)}\ts M_1 \opto \cdots \opto \Gamma_n,s^{(n)}\ts M_n\,,
+    \]
+  and $s^{(n)}\vert_{\Gamma}=s'$.
+  \label{PropBigToSmall}
+\end{proposition}
+\begin{proof}
+  Induction on the derivation of $\Gamma,s\ts M\converges c,s'$.  
+  Since most of the cases are similar, we cover a selection for illustration.
+
+  \begin{itemize}
+    \item Suppose that the last step in the derivation is
+      \[
+        \inferrule*{ }
+        {\Gamma,s\ts c\converges c,s}\,.
+        \]
+      Then we have the one-element sequence $\Gamma,s\ts c$.  
+    \item Suppose that the last step in the derivation is
+      \[
+        \inferrule*
+        {
+          \Gamma,s\ts M\converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x]\converges c,s''
+        }
+        {
+          \Gamma,s \ts MN\converges c,s''
+        }\,.
+        \]
+      Then, by the inductive hypothesis, we have small-step derivations
+      \begin{mathpar}
+        \Gamma,s \ts M \opto \cdots \opto \Gamma',t',\lambda x.M'
+        \and
+        \Gamma,s' \ts M'[N/x]\opto \cdots \opto \Gamma'',t'',c\,,
+      \end{mathpar}
+      where $t'\vert_\Gamma=s'$ and $t''\vert_\Gamma=s''$.
+
+      If we apply the evaluation context $-N$ pointwise to the first small-step derivation, then we have another valid small-step derivation.  
+      Then we can join the two together to get the derivation
+      \begin{center}
+        \parbox{0.8\textwidth}{
+        \begin{mathpar}
+          \Gamma,s \ts MN \opto \cdots \opto \Gamma',t',(\lambda x.M')N \opto \Gamma',t',M'[N/x] \opto \cdots \opto \Gamma'\cup\Gamma'',t''\setminus t',c\,,
+        \end{mathpar}}
+      \end{center}
+      where $t''\setminus t'$ is the $\Gamma'\cup\Gamma''$-store that agrees with $t''$ on $\Gamma''$ and with $t'$ on $\Gamma'\setminus\Gamma''$.
+      Then $(t''\setminus t')\vert_{\Gamma}=s''$.
+    \item Suppose that the last step in the derivation is
+      \[
+        \inferrule*
+        {
+          \Gamma,s\ts E\converges n,s' \\ \Gamma,s'\ts V\converges x,s''
+        }
+        {
+          \Gamma,s \ts V \gets E \converges\skipp,(s''\vert x\mapsto n)
+        }\,.
+        \]
+      By the inductive hypothesis, we have small-step derivations
+      \begin{mathpar}
+        \Gamma,s\ts E \opto \cdots \opto \Gamma',t',n
+        \and
+        \Gamma,s'\ts V \opto \cdots \opto \Gamma'',t'',x\,,
+      \end{mathpar}
+      where $t'\vert_{\Gamma}=s'$ and $t''\vert_{\Gamma}=s''$.
+
+      We may apply the evaluation context $V\gets-$ pointwise to the first derivation and the evaluation context $-\gets n$ pointwise to the second, and then string the two together to get
+      \begin{center}
+        \parbox{0.8\textwidth}{
+        \begin{mathpar}
+          \Gamma,s\ts V\gets E \opto \cdots \opto \Gamma',t',V\gets n \opto \cdots \opto \Gamma'\cup\Gamma'',t''\setminus t',x\gets n \opto \Gamma'\cup\Gamma'',(t''\setminus t'\vert x\mapsto n)\,,
+        \end{mathpar}}
+      \end{center}
+      where we have $(t''\setminus t'\vert x\mapsto n)\vert_\Gamma=(s''\vert x\mapsto n)$.
+    \item Suppose that the last step in the derivation is
+      \[
+        \inferrule*
+        {
+          \Gamma,s\ts V \converges x,s'
+        }
+        {
+          \Gamma,s\ts \oc V \converges s'(x),s'
+        }\,.
+        \]
+      Then, by the induction hypothesis, we have a small-step derivation
+      \[
+        \Gamma,s\ts V \opto \cdots \opto \Gamma',t'\ts x\,,
+        \]
+      where $t'\vert_\Gamma=s'$.  
+      Then we may compose this derivation pointwise with the evaluation context $\oc-$, and add an extra term on the end, to arrive at the derivation
+      \[
+        \Gamma,s\ts \oc V \opto \cdots \opto \Gamma',t'\ts \oc x \opto \Gamma',t'\ts t'(x)\,,
+        \]
+      where $t'(x)=s'(x)$.
+    \item Lastly, suppose that the last step in the derivation is
+      \[
+        \inferrule*
+        {
+          \Gamma,x,(s\vert x\mapsto 0) \ts M \converges c,(s'\vert x\mapsto n)
+        }
+        {
+          \Gamma,s \ts \neww \lambda x.M \converges c,s'
+        }\,.
+        \]
+      By the induction hypothesis, we have a small-step derivation
+      \[
+        \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma',x,(t'\vert x\mapsto n),c\,,
+        \]
+      where $t'\vert_\Gamma=s'$.  
+      Then we may add a term at the beginning to give us
+      \[
+        \Gamma,s \ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma',x,(t'\vert x\mapsto n),c\,,
+        \]
+      where $(t'\vert x\mapsto n) \vert_\Gamma=s'$.\qedhere
+  \end{itemize}
 \end{proof}
@@
 \subsection{Soundness}
+
+To prove soundness of our model, we shall use the small-step formulation.  
+Our reason for this is that the most difficult part of the denotational semantics we are using is the part to do with state.  
+In the big-step formulation, nearly every rule involves the state changing in some way, whereas in the small-step formulation, only the rules that specifically pertain to the stateful components of the language do.
+
+\begin{lemma}
+  Suppose that $\Gamma,s\ts M \opto \Gamma',s'\ts N$.
+\end{lemma}
 

### 2019-03-30 Thesis/games.tex
D.

@@
-\documentclass{article}
+\documentclass[11pt]{report}
 
@@
 
-\section{A Fully Abstract Game Semantics for Idealized Algol}
+\chapter{A Fully Abstract Game Semantics for Idealized Algol}
 
@@
 
-\subsection{Idealized Algol}
+\section{Idealized Algol}
 
@@
 
+\begin{minipage}{\linewidth}
 \begin{lstlisting}[language=Java, morekeywords={nat,com}]
@@
 \end{lstlisting}
+\end{minipage}
 
@@
 
-\subsection{Games and Strategies}
+\section{Games and Strategies}
 
@@
 
-\subsection{Connectives on Games}
+\section{Connectives on Games}
 \label{SecConnectives}
@@
     \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
-    \item $P_{A\times B} = \{s\in L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ and $s\vert_B\in P_B$}\}$.
+    \item $P_{A\times B} = \{s\in L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
   \end{itemize}
@@
 
-\subsection{Composition of strategies}
+\section{Composition of strategies}
 
@@
     \pv{\s c} & = & c & if $c$ is an initial move of $C$ \\
-    \pv{\s b\t a} & = & \pv{\s}ba & if $a$ is a $P$-move of $A$ or an $O$-move of $C$ and is justified by $b$ \\
+    \pv{\s b\t a} & = & \pv{\s}ba & \parbox[t][][t]{200pt}{if $a$ is a $P$-move of $A$ or an $O$-move of $C$ and is justified by $b$} \\
   \end{IEEEeqnarray*}
@@
 
-  Having established that $\s\vert_{A,C}$ is alternating, we show that it is well-bracketed.
+  Having established that $\s\vert_{A,C}$ is alternating, we now show that it is well-bracketed.
   Suppose that a question move $q$ in $\s\vert_{A,C}$ justifies some answer move $a$.
@@
 
-\subsection{Associativity of composition}
-
-In this section, we will prove that composition is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.
+\section{Associativity of composition}
+
+In this section, we shall prove that composition of strategies is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.
 To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in L_{A\implies B}$, $\u\vert_{B,C}\in L_{B\implies C}$ and $\u\vert_{C,D}\in L_{C \implies D}$.
@@
 
-\subsection{Copycat strategies}
+\section{Copycat strategies}
 \label{SecCopycat}
@@
 It is also easy to see from Proposition \ref{PropCopycat} that the identity function $\id\from M_A \to M_A$ is a structural isomorphism from $A$ to itself, and that the resulting copycat strategy $\cc_{\id}$ is an identity for composition.
-Combining this with our result for associativity in the previous section, we get that
+Combining this with our result for associativity in the previous chapter, we get that
 \begin{theorem}
@@
 
-\subsection{$\G$ as a Symmetric Monoidal Category}
+\section{$\G$ as a Symmetric Monoidal Category}
 
@@
 
-The above proof gives us the following result analogous to Corollary \ref{CorSwitchingCondition}.
+The above proof gives us the following result, which is analogous to Corollary \ref{CorSwitchingCondition}.
 
@@
   Now suppose that $sab,sac\in\sigma\tensor\tau$.  
-  Then $sa$ is an $O$-position in $P_{(A\tensor C)\implies (B\tensor D)}$, and is therefore in configuration $PPPO$ or $PPOP$.  
+  Then $sa$ is an $O$-position in $(A\tensor C)\implies (B\tensor D)$, and is therefore in configuration $PPPO$ or $PPOP$.  
   By inspecting the table above, we see that if $sa$ is in configuration $PPPO$, then $b$ and $c$ must both occur either in $C$ or in $D$, and that if $sa$ is in configuration $PPOP$, then $b$ and $c$ must both occur either in $A$ or in $B$.
@@
 
-\subsection{$\G$ as a Symmetric Monoidal Closed Category}
+\section{$\G$ as a Symmetric Monoidal Closed Category}
 
@@
   \[
-\arraycolsep=2.7pt\def\arraystretch{1.5}
+\arraycolsep=2.6pt\def\arraystretch{1.5}
     \begin{array}{cccc|cc|c}
@@
 
-\subsection{Products in $\G$}
+\section{Products in $\G$}
 
@@
 
-\subsection{Sequoidal categories}
-
-We have now given the category-theoretic properties of all the connectives from Section \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
+\section{Sequoidal categories}
+
+We have now given the category-theoretic properties of all the connectives from chapter \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
 
@@
 
-\begin{definition}
+\begin{definition}[\cite{laird02}]
   A \emph{sequoidal category} $\C$ is given by
@@
       \begin{mathpar}
-        \begin{tikzcd}[column sep=36pt]
-          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}"] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
-            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}"]
+        \begin{tikzcd}[column sep=31pt]
+          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}" yshift=1pt] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
+            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}" yshift=1pt]
               & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
-          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}"]
+          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}" yshift=1pt]
             & a \sequoid (x \tensor (y \tensor z))
@@
 \begin{remark}
-  The definitions of \emph{lax action} can be found at the start of Section \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
-  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Section \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.
+  The definitions of \emph{lax action} can be found at the start of chapter \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
+  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in chapter \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.
   A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
@@
   \[
-    \begin{tikzcd}[column sep=19pt, row sep=30pt]
+    \begin{tikzcd}[column sep=16pt, row sep=30pt]
       ((M_A + M_X) + M_Y) + M_Z \arrow[r, "{[\assoc_{M_A,M_X,M_Y},\id_{M_Z}]}" yshift=3pt] \arrow[d, "{\assoc_{M_A+M_X,M_Y,Z}}" description]
@@
 
-  For the fourth diagram in Definition \ref{DefSequoidalCategory}, since $\wk$ is a subset inclusion strategy induced from an identity map, Proposition \ref{PropCopycat} tells us that both arms of the diagram are the strategy induced by the subset inclusion $\assoc_{M_A,M_X,M_Y}\from (M_A + M_X) + M_Y \to M_A + (M_X + M_Y)$ from $(A \tensor X) \tensor Y$ to $A \sequoid (X \tensor Y)$.
+  For the fourth diagram in Definition \ref{DefSequoidalCategory}, since $\wk$ is a subset inclusion strategy induced from an identity map, Proposition \ref{PropCopycat} tells us that both arms of the diagram are the strategy induced by the subset inclusion
+  \[
+    \assoc_{M_A,M_X,M_Y}\from (M_A + M_X) + M_Y \to M_A + (M_X + M_Y)
+    \]
+  from $(A \tensor X) \tensor Y$ to $A \sequoid (X \tensor Y)$.
   Similarly, both arms of the last diagram in Definition \ref{DefSequoidalCategory} are the strategies induced by the subset inclusion $\runit_{M_A} \from M_A \to M_A + \emptyset$ from $A$ to $A \sequoid I$.
@@
 
-\subsection{Tree Embeddings and Zigzag Strategies}
+\section{Tree Embeddings and Zigzag Strategies}
 
@@
 
-We can generalize the subset inclusions of the previous section to \emph{tree embeddings}.  
+We can generalize the subset inclusions of the previous chapter to \emph{tree embeddings}.  
 Tree embeddings are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
@@
 
-\subsection{Sequoidally decomposable categories}
+\section{Sequoidally decomposable categories}
 
@@
 \begin{proof}
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree embedding $\phi\from P_{\prod_i (A_1 \sequoid(\cdots\sequoid(A_n\sequoid B_i)\cdots))} \to P_{A_1\sequoid(\cdots\sequoid(A_n\sequoid \prod_iB_i))}$ defined as follows.
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree embedding 
+  \[
+    \phi\from P_{\prod_i (A_1 \sequoid(\cdots\sequoid(A_n\sequoid B_i)\cdots))} \to P_{A_1\sequoid(\cdots\sequoid(A_n\sequoid \prod_iB_i))}
+    \]
+  defined as follows.
   \[
@@
       \epsilon & \text{if $s=\epsilon$} \\
-      [\inj_{A_1,\cdots,A_n},\inj_{B_j}]_*(s) & \text{if $s$ begins with a move in the $j$-th component}
+      [\inj_{A_1,\cdots,A_n},\inj_{B_j}]_*(s) & \parbox[t][][t]{180pt}{if $s$ begins with a move in the $j$-th component}
     \end{cases}
@@
 
-  If $i\le n$, then the $i$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite thick dashed arrows in Figure \ref{FigDecSeqFormula}, and is therefore equal to the composite of the solid arrows, which is $\sym_i^{n+1};\wk_{a_i,\Tensor_{j\ne i}a_j}$ as desired.
+  If $i\le n$, then the $i$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite thick dashed arrows in Figure \ref{FigDecSeqFormula}, and is therefore equal to the composite of the solid arrows, which is equal to $\sym_i^{n+1};\wk_{a_i,\Tensor_{j\ne i}a_j}$ as desired.
   The $n+1$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite
@@
     \[
-      \begin{tikzcd}[ampersand replacement=\&, column sep=10pt, row sep=30pt]
+      \begin{tikzcd}[ampersand replacement=\&, column sep=6pt, row sep=30pt]
         \Tensor_{j=1}^{n+1}a_j \arrow[r, thick, dashed] \arrow[dd, "\sym_i^{n+1}"']
           \& \Tensor_{j=1}^n a_j \tensor a_{n+1} \arrow[r, "{\wk_{\Tensor_{j=1}^na_j,a_{n+1}}}", thick, dashed] \arrow[d, "\sym_i^n\tensor a_{n+1}" description, dotted]
-            \&[45pt] \Tensor_{j=1}^n a_j \sequoid a_{n+1} \arrow[d, "\sym_i^n\sequoid a_{n+1}", thick, dashed]
-              \&[34pt] \\
+            \&[45.5pt] \Tensor_{j=1}^n a_j \sequoid a_{n+1} \arrow[d, "\sym_i^n\sequoid a_{n+1}", thick, dashed]
+              \&[31pt] \\
         %
@@
             \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n}\right)\tensor a_{n+1} \arrow[r, "{\wk_{a_i\sequoid \Tensor_{j\ne i}^{j\le n},a_{n+1}}}" xshift=-10pt, dotted]
-              \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j\right) \sequoid a_{n+1} \arrow[d, "{\passoc_{a_i,\Tensor_{j\ne i}^{j\le n}a_j,a_{n+1}}}", thick, dashed] \\
+              \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j\right) \sequoid a_{n+1} \arrow[d, "{\passoc_{a_i,\Tensor_{j\ne i}^{j\le n}a_j,a_{n+1}}}" {description, yshift=2pt}, thick, dashed] \\
         %
@@
 
-\subsection{A Formula for the Exponential}
+\begin{definition}[\cite{laird02}]
+  A \emph{sequoidal closed category} is an inclusive sequoidal category $\C$ such that $\C$ is a monoidal closed category (with inner hom $\implies$) and such that the map $f\mapsto \Lambda(\wk_{A,B};f)$ defines an isomorphism
+  \[
+    \Lambda_s \from \C_s(A \sequoid B,C) \toisom \C_s(A,B\implies C)\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  $\G$ is a sequoidal closed category.
+\end{proposition}
+\begin{proof}
+  Since $\wk_{A,B}$ is an epimorphism and $\Lambda$ is a bijection, the map is certainly injective.  
+  Showing that it is surjective comes down to proving that uncurrying of a strict strategy for $A\implies (B \implies C)$ is a strict strategy for $(A\sequoid B) \implies C$.
+  Indeed, after the opening move in $C$, in both cases player $P$ must play the next move in $A$.
+\end{proof}
+
+\section{A Formula for the Exponential}
 
@@
 \begin{theorem}[\cite{MelliesCofCommCom}]
-  Let $\C$ be a monoidal category in which the monoidal unit is a terminal object.
+  Let $\C$ be a monoidal category such that the monoidal unit for $\C$ is a terminal object.
   Suppose that $\C$ has symmetrized tensor powers that commute with the tensor product.
@@
   \[
-    \begin{tikzcd}[column sep=40pt]
+    \begin{tikzcd}[column sep=30pt]
       A^{\tensor(n+1)} \arrow[r, "A^{\tensor n}\tensor()"] \arrow[d, "A\tensor\wk^{n+1}"']
@@
   \[
-    \begin{tikzcd}[column sep=42pt]
+    \begin{tikzcd}[column sep=41pt]
       A^{\tensor(n+2)} \arrow[r] \arrow[dd, "\wk^{n+2}"']
@@
 
-\subsection{The Exponential as a Final Coalgebra}
+\section{The Exponential as a Final Coalgebra}
 
@@
 
-\subsection{Denotational Semantics of Idealized Algol}
+\section{Denotational Semantics of Idealized Algol}
 
@@
   \item $\IfO_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y,\lambda x.\lambda y.y,\cdots)\from \bN \to (X \to X \to X)$;
+  \item $\assign = (\pr_0,\pr_1,\cdots) \from \bN \to (\Varr \to \bC)$; and
   \item $\dereff = \pr_\bN \from \Varr \to \bN$;
-  \item $\assign = (\pr_0,\pr_1,\cdots) \from \bN \to (\Varr \to \bC)$; and
   \item $\mkvar = \lambda w.\lambda r.\langle (w\,n)_{n\in\bN},r\rangle \from (\bN \to \bC) \to \bN \to \Varr$.
@@
 
-\subsection{Order-Enrichment of $\G$}
+\section{Order-Enrichment of $\G$}
 
@@
 \begin{proposition}
-  The partial order of strategies for $A$ is directed-complete.  
+  The partial order of strategies for $A$, ordered by inclusion, is directed-complete.  
   So is the partial order of innocent strategies for $A$.
@@
 
-\subsection{The Strategy $\cell$}
+\section{The Strategy $\cell$}
 
@@
 
-\subsection{Big-Step Operational Semantics of Idealized Algol}
+\begin{lemma}
+  $\cell_0;(\pr_n\sequoid\oc\bN) = \wwrite_n$ for each $n$ and $\cell_0;(\pr_\bN\sequoid\oc\bN) = \rread$, where $\pr_n\from \Varr=\bC^\bN \times \bN \implies \bC$ is the projection on to the $n$-th copy of $\bC$ and $\pr_\bN\from \Varr = \bC^\bN \times \bN \implies \bN$ is the projection on to the copy of $\bN$.
+\end{lemma}
+\begin{proof}
+  We have
+  \[
+    \dist_{(\bC)_{\bN},\bN,\oc\bN};\pr_n = \langle(\pr_n\sequoid\oc \bN)_{n\in\bN},\pr_{\bN}\sequoid\oc\bN\rangle;\pr_n = \pr_n\sequoid\oc\bN
+    \]
+  and
+  \[
+    \dist_{(\bC)_{\bN},\bN,\oc\bN};\pr_\bN = \langle(\pr_n\sequoid\oc \bN)_{n\in\bN},\pr_{\bN}\sequoid\oc\bN\rangle;\pr_\bN = \pr_\bN\sequoid\oc\bN\,,
+    \]
+  so
+  \begin{IEEEeqnarray*}{Cl}
+    & \cell_0;(\pr_n\sequoid\oc\bN) \\
+    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv;(\pr_n\sequoid\oc\bN) \\
+    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle ;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv\dist_{(\bC)_\bN,\bN,\oc\bN};\pr_n \\
+    = & \langle (\wwrite_n)_{n\in\bN},\rread\rangle;\pr_n \\
+    = & \wwrite_n
+  \end{IEEEeqnarray*}
+  and
+  \begin{IEEEeqnarray*}{Cl}
+    & \cell_0;(\pr_\bN\sequoid\oc\bN) \\
+    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv;(\pr_\bN\sequoid\oc\bN) \\
+    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle ;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv\dist_{(\bC)_\bN,\bN,\oc\bN};\pr_\bN \\
+    = & \langle (\wwrite_n)_{n\in\bN},\rread\rangle;\pr_\bN \\
+    = & \rread\,.\hspace{1em plus 1fill}\qedhere
+  \end{IEEEeqnarray*}
+\end{proof}
+
+\section{Big-Step Operational Semantics}
 
@@
 
-\subsection{Small-Step Operational Semantics of Idealized Algol}
+\section{Small-Step Operational Semantics}
 
@@
 As an auxiliary definition, we need the notion of an \emph{evaluation context} (see \cite{Felleisen}).
-This is a single-holed context defined inductively by the following BNF formula, where $M$ ranges over IA terms.
+This is a single-holed context defined inductively by the following BNF formula, where $M$ ranges over IA terms (subject to typing rules).
 \begin{center}
@@
 We need to prove that this is equivalent to our original semantics.
+Given a $\Gamma'$-store $s$, and a sub-context $\Gamma$ of $\Gamma'$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.
 
@@
 
-\subsection{Soundness}
+\section{Soundness}
 
@@
 
+Given a $\Var$-context $\Gamma$, we will write $S_\Gamma$ for $\bN \times \cdots \times \bN$ and $\V_\Gamma$ for $\Varr \times \cdots \times \Varr$, where in each case the terms of the tensor product are indexed by the variables in $\Gamma$.
+Then, given some term $\Gamma\ts M$ in context, its denotation will be a morphism $\deno{\Gamma\ts M\from T} \from \oc \V_\Gamma \implies \deno{T}$.
+
+Given $\Gamma$, we have a morphism $\cell^n\from \oc S_\Gamma \implies \oc V_\Gamma$, given by
+\[
+  \oc S_\Gamma \cong \oc \bN \tensor \cdots \tensor \oc \bN \xrightarrow{\cell \tensor \cdots \tensor \cell} \oc \Varr \tensor \cdots \tensor \oc \Varr \cong \oc V_\Gamma\,.
+  \]
 \begin{lemma}
-  Suppose that $\Gamma,s\ts M \opto \Gamma',s'\ts N$.
+  For $j=1,\cdots,n$, the following diagram commutes.
+  \[
+    \begin{tikzcd}
+      \oc S_\Gamma \arrow[r, "\cell^n"] \arrow[d, "\oc\pr_j"']
+        & \oc V_\Gamma \arrow[d, "\oc \pr_j"] \\
+      \oc \bN \arrow[r, "\cell"]
+        & \oc \Varr
+    \end{tikzcd}
+    \]
 \end{lemma}
+\begin{proof}
+  We have a commutative diagram
+  \[
+    \begin{tikzcd}[column sep=40pt, row sep=40pt]
+      \oc S_\Gamma \arrow[r, Isom] \arrow[dr, "\oc \pr_j"']
+        & \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell \tensor \cdots \tensor \cell"] \arrow[d, "() \tensor \cdots \tensor \oc\bN \tensor \cdots \tensor ()"' {description, xshift=10pt}]
+          & \oc \Varr \tensor \cdots \tensor \oc \Varr \arrow[r, Isom] \arrow[d, "() \tensor \cdots \tensor \oc\Varr \tensor \cdots \tensor ()" {description, xshift=-10pt}]
+            & \oc V_\Gamma \arrow[dl, "\oc \pr_j"] \\
+      %
+        & \oc\bN \arrow[r, "\cell"]
+          & \oc\Varr
+            &
+    \end{tikzcd}\,,
+    \]
+  where the outer triangles commute because the vertical arrows are the projections in the tensor product of comonoids.
+\end{proof}
+
+Given a $\Gamma$-store $s$, we will write $\deno{s}$ for the corresponding morphism $I \to S_\Gamma$.
+
+We start our proof of soundness with a result about evaluation contexts.
+This result captures the fact that the term filling the hole of an evaluation context is the first thing to be computed, using the sequoid operator to capture this notion of precedence.
+\begin{lemma}
+  Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context, and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
+  Then there is a game $A$ and strategies $\sigma\from \oc\V_\Gamma \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$ such that $\tau$ is a strict strategy and the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
+  \[
+    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno{T}\tensor A \xrightarrow{\wk_{\deno{T},A}} \deno{T} \sequoid A \xrightarrow{\tau} \deno{U}\,.
+    \]
+  \label{LemEvContexLemma}
+\end{lemma}
+\begin{proof}
+  Structural induction on $\EE$.
+  \begin{itemize}
+    \item If $\EE=-$ is a hole, then we may take $A=I$, $\sigma=()$ and $\tau=\run_{\deno T}$.
+
+    \item If $\EE=\EE' N$ for some term $N$, where $\EE'$ has type $S\to T$, $N$ has type $S$, and $M\from S'$ fits into the hole, then the denotation $\deno{\Gamma \ts \EE[M]} = \deno{\Gamma \ts \EE'[M]\,N}$ is given by the composite
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma \ts \EE'[M]}\tensor \deno{\Gamma \ts N}} (\oc\deno{S} \implies \deno{T}) \tensor \oc\deno{S} \xrightarrow{\ev_{\oc\deno{S},\deno{T}}} \deno{T}.
+        \]
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE' M}$ factors as
+      \small
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{S'}\tensor A' \xrightarrow{\wk_{\deno{S'},A'}} \deno{S'} \sequoid A' \xrightarrow{\tau'} (\oc\deno{S}\implies\deno{T}),
+        \]
+      \normalsize
+      for appropriate $A',\sigma',\tau'$.  
+      Then $\deno{\Gamma\ts\EE[M]} = \deno{\Gamma\ts\EE'[M]\,N}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextApp}.  
+      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form, with
+      \begin{mathpar}
+        A = A' \tensor \oc\deno{S}
+        \and
+        \sigma = \mu_{\V_\Gamma};(\sigma'\tensor\deno{\Gamma\ts N}^\dag)
+        \and
+        \tau = \passoc_{\deno{S'},A',\oc\deno{S}}\inv;(\tau'\sequoid\oc\deno{S});\ev_{s\;\oc\deno{S},\deno{T}}\,.
+      \end{mathpar}
+      \begin{figure}
+        \small
+        \[
+          \begin{tikzcd}[column sep=79pt]
+            \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{\V_\Gamma}"]
+              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\oc\V_\Gamma\tensor\mu_{\V_\Gamma}"] \\
+            \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor \oc\V_\Gamma"' yshift=3pt, thick, dashed]
+              & \oc \V_\Gamma \tensor (\oc \V_\Gamma \tensor \oc \V_\Gamma) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N}^\dag)"] \\
+            (\oc \V_\Gamma \tensor \oc \V_\Gamma) \tensor \oc \V_\Gamma \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}^\dag"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\V_\Gamma,\V_\Gamma,\V_\Gamma}" description, dotted]
+              & \deno{S'} \tensor (A' \tensor \oc\deno{S}) \arrow[d, "{\wk_{\deno{S'},A' \tensor \oc \deno{S}}}"] \\
+            (\deno{S'} \tensor A') \tensor \oc\deno{S} \arrow[d, "{\wk_{\deno{S'},A'}\tensor \oc\deno{S}}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\deno{S'},A',\oc\deno{S}}" description, dotted]
+              & \deno{S'} \sequoid (A' \tensor \oc\deno{S}) \arrow[d, "{\passoc_{\deno{S'},A',\oc\deno{S}}\inv}"] \\
+            (\deno{S'} \sequoid A') \tensor \oc\deno{S} \arrow[d, "\tau' \tensor\oc\deno S"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{\deno{S'}\sequoid A',\oc\deno{S}}}" description, dotted]
+              & (\deno{S'} \sequoid A') \sequoid \oc\deno{S} \arrow[d, "\tau' \sequoid \oc\deno{S}"] \\
+            (\oc \deno{S} \implies \deno{T}) \tensor \oc\deno{S} \arrow[d, "{\ev_{\oc\deno{S},\deno{T}}}"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{\oc\deno S \implies \deno T,\oc\deno S}}" description, dotted]
+              & (\oc\deno{S} \implies \deno{T}) \sequoid \oc\deno{S} \arrow[dl, "{\ev_{s\;\oc\deno{S},\deno{T}}}"] \\
+            \deno{T}
+              &
+          \end{tikzcd}
+          \]
+        \normalsize
+        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by function application.]{The property in Lemma \ref{LemEvContexLemma} is preserved by function application.  
+        Here, $\ev_{s\;\oc\deno{S},\deno{T}} = \Lambda_s\inv(\id_{\oc\deno{S}\implies \deno{T}})$.}
+        \label{FigEvContextApp}
+      \end{figure}
+    \item If $\EE=\suc \EE'$ or $\pred \EE'$, where $\EE'$ is a context of type $\nat$, and $M\from T$ is a term that fits into the hole, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
+      \[
+        \oc \V_\Gamma \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \bN \xrightarrow{\theta} \bN\,,
+        \]
+      where $\theta$ is either $\pred$ or $\suc$.
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \bN\,,
+        \]
+      for appropriate $A',\sigma',\tau'$.  
+      Then we can compose on the right by $\theta$, and we are already in the required form, for
+      \begin{mathpar}
+        A = A' \and \sigma = \sigma' \and \tau = \tau';\theta\,.
+      \end{mathpar}
+    \item Similarly, if $\EE = \oc\EE'$, where $\EE'$ is a context of type $\Var$, and $M\from T$ is a term that fits into the hole, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
+      \[
+        \oc \V_\Gamma \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \Varr \xrightarrow{\dereff} \bN\,.
+        \]
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \Varr\,,
+        \]
+      for appropriate $A',\sigma',\tau'$.  
+      Then we can compose on the right by $\dereff$, and we are already in the required form, for
+      \begin{mathpar}
+        A = A' \and \sigma = \sigma' \and \tau = \tau';\dereff\,.
+      \end{mathpar}
+    \item If $\EE=\EE';N$ for some term $N$ of type $X\in\{\com,\bool,\nat\}$, where $\EE'$ is an evaluation context of type $\com$, and if $M\from T$ fits into the hole in $\EE'$, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bC \times X \xrightarrow{\Lambda\inv(\seq_X)} X\,.
+        \]
+      If $\EE = N\gets\EE'$, for some term $N$ of type $\Var$, where $\EE'$ is an evaluation context of type $\com$, and if $M\from T$ fits into the hole in $\EE'$, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bN \times \Var \xrightarrow{\Lambda\inv(\assign)} \bC\,.
+        \]
+      Write $Y=\bC$, $X'=X$, $Z=X$ and $\upsilon=\seq_X$ in the sequencing case, and $Y=\bN$, $X'=\Var$, $Z=\bC$ and $\upsilon=\assign$ in the variable assignment case.
+      Then, by the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} Y\,,
+        \]
+      for suitable $A',\sigma',\tau'$.
+      Then $\deno{\Gamma\ts\EE[M]}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextSeqAss}.  
+      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form, with
+      \begin{mathpar}
+        A = A' \tensor X'
+        \and
+        \sigma = \mu_{\V_\Gamma};(\sigma'\tensor\deno{\Gamma\ts N})
+        \and
+        \tau = \passoc_{\deno{T},A',X'}\inv;(\tau'\sequoid X');\Lambda_s\inv(\upsilon)\,.
+      \end{mathpar}
+      \begin{figure}
+        \small
+        \[
+          \begin{tikzcd}[column sep=79pt]
+            \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{\V_\Gamma}"]
+              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\oc\V_\Gamma\tensor\mu_{\V_\Gamma}"] \\
+            \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor \oc\V_\Gamma"' yshift=3pt, thick, dashed]
+              & \oc \V_\Gamma \tensor (\oc \V_\Gamma \tensor \oc \V_\Gamma) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N})"] \\
+            (\oc \V_\Gamma \tensor \oc \V_\Gamma) \tensor \oc \V_\Gamma \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\V_\Gamma,\V_\Gamma,\V_\Gamma}" description, dotted]
+              & \deno{T} \tensor (A' \tensor X') \arrow[d, "{\wk_{\deno{T},A' \tensor X'}}"] \\
+            (\deno{T} \tensor A') \tensor X' \arrow[d, "{\wk_{\deno{T},A'}\tensor X'}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\deno{T},A',X'}" description, dotted]
+              & \deno{T} \sequoid (A' \tensor X') \arrow[d, "{\passoc_{\deno{T},A',X'}\inv}"] \\
+            (\deno{T} \sequoid A') \tensor X' \arrow[d, "\tau' \tensor X'"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{\deno{T}\sequoid A',X'}}" description, dotted]
+              & (\deno{T} \sequoid A') \sequoid X' \arrow[d, "\tau' \sequoid X'"] \\
+            Y \tensor X' \arrow[d, "\Lambda\inv(\upsilon)"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{Y,X'}}" description, dotted]
+              & Y \sequoid X' \arrow[dl, "\Lambda_s\inv(\upsilon)"] \\
+            \deno{T}
+              &
+          \end{tikzcd}
+          \]
+        \normalsize
+        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.]{The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.
+        We use the fact that $\upsilon\in\{\seq_X,\assign\}$ is a strict strategy, so that $\Lambda_s\inv(\upsilon)$ is well-defined.}
+        \label{FigEvContextSeqAss}
+      \end{figure}
+    \item If $\EE = \If \EE' \Then N \Else P$ for a context $\EE'$ of type $\bool$, where $N$ and $P$ are terms of type $X\in\{\bool,\com,\nat\}$, then write $Y=\bool$ and $\eta = \If_X$.  
+      If $\EE = \IfO \EE' \Then N \Else P$ for a context $\EE'$ of type $\nat$, where $N$ and $P$ are terms of type $X\in\{\bool,\com,\nat\}$, then write $Y=\nat$ and $\eta=\IfO_X$.  
+      In either case, if $M\from T$ is a term that fits into the hole, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by
+      \begin{mathpar}
+        \oc\V_\Gamma \xrightarrow{\mu_{V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\mu_\Gamma \tensor \V_\Gamma} (\oc \V_\Gamma \tensor \oc \V_\Gamma) \tensor \oc\V_\Gamma \\\xrightarrow{(\deno{\Gamma\ts\EE'[M]} \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma \ts P}} (Y \tensor X) \tensor X \xrightarrow{\Lambda\inv(\Lambda\inv(\eta))} X\,.
+      \end{mathpar}
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} Y\,,
+        \]
+      for appropriate $A',\sigma',\tau'$.  
+      Then $\deno{\Gamma\ts\EE[M]} = \deno{\Gamma\ts\EE'[M]\,N}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextCond}.  
+      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form, with
+      \begin{mathpar}
+        A = (A' \tensor X)\tensor X
+        \and
+        \sigma = \mu_{\V_\Gamma};(\mu_{\V_\Gamma}\tensor\oc\V_\Gamma);((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})
+        \and
+        \tau = \passoc_{\deno T,A'\tensor X,X}\inv;(\passoc_{\deno T,A',X}\inv\sequoid X);((\tau'\sequoid X)\sequoid X);\Lambda_s\inv(\Lambda_s\inv(\eta))\,.
+      \end{mathpar}
+      \begin{SidewaysFigure}
+        \small
+        \[
+          \begin{tikzcd}[ampersand replacement=\&, column sep=78pt, row sep=20pt]
+            \oc \V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}"] \arrow[d, "\mu_{\V_\Gamma}"', thick, dashed]
+              \&
+                \& \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\oc\V_\Gamma \tensor\mu_{\V_\Gamma}"] \\
+            \oc \V_\Gamma \tensor \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}\tensor \oc\V_\Gamma", dotted] \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"', thick, dashed]
+              \& (\oc \V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma \arrow[r, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}}", dotted] \arrow[d, "(\oc\V_\Gamma \tensor \mu_{\V_\Gamma}) \tensor \oc\V_\Gamma" description, dotted]
+                \& \oc \V_\Gamma \tensor (\oc \V_\Gamma \tensor \oc\V_\Gamma) \arrow[d, "\oc\V_\Gamma \tensor (\mu_{\V_\Gamma}\tensor \oc\V_\Gamma)"] \\
+            (\oc \V_\Gamma \tensor \oc\V_\Gamma)\tensor \oc\V_\Gamma \arrow[d, "(\mu_{\V_\Gamma}\tensor\oc\V_\Gamma)\tensor \oc\V_\Gamma"', thick, dashed]
+              \& |[alias=Z]| (\oc \V_\Gamma \tensor(\oc\V_\Gamma\tensor \oc\V_\Gamma)) \tensor \oc\V_\Gamma \arrow[r, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma\tensor\oc\V_\Gamma,\oc\V_\Gamma}}", dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor (\sigma'\tensor\deno{\Gamma\ts N})) \tensor \deno{\Gamma\ts P}" description, dotted]
+                \& \oc\V_\Gamma \tensor ((\oc\V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma) \arrow[d, "\deno{\Gamma\ts M} \tensor ((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})" description] \\
+            ((\oc\V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma \arrow[d, "((\deno{\Gamma\ts M} \tensor \sigma') \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma\ts P}" {description, xshift=-20pt}, thick, dashed] \arrow[ur, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}\tensor\oc\V_\Gamma}" description, to=Z.west, dotted]
+              \& |[alias=Y]| (\deno T \tensor (A' \tensor X)) \tensor X \arrow[r, "{\assoc_{\deno T,A'\tensor X,X}}" description, dotted] \arrow[d, "{\wk_{T,A'\tensor X}\tensor X}" description, dotted]
+                \& \deno T \tensor ((A' \tensor X) \tensor X) \arrow[d, "{\wk_{\deno T,(A'\tensor X)\tensor X}}"] \\
+            ((\deno T\tensor A') \tensor X)\tensor X \arrow[ur, "{\assoc_{\deno T,A',X}\tensor X}" description, to=Y.west, dotted] \arrow[d, "{(\wk_{\deno T,A'}\tensor X)\tensor X}"', thick, dashed]
+              \& (\deno T \sequoid (A' \tensor X))\tensor X \arrow[dr, "{\wk_{\deno T\sequoid (A'\tensor X),X}}" description, dotted] \arrow[d, "{\passoc_{\deno T,A',X}\tensor X}" description, dotted]
+                \& \deno T \sequoid ((A' \tensor X)\tensor X) \arrow[d, "{\passoc_{\deno T,A'\tensor X,X}\inv}"] \\
+            ((\deno T\sequoid A') \tensor X) \tensor X \arrow[r, "{\wk_{\deno T \sequoid A',X}\tensor X}", dotted] \arrow[d, "(\tau'\tensor X)\tensor X)"', thick, dashed]
+              \& ((\deno T \sequoid A') \sequoid X) \tensor X \arrow[dr, "{\wk_{(\deno T\sequoid A') \sequoid X,X}}" description, dotted] \arrow[d, "(\tau'\sequoid X)\tensor X" description, dotted]
+                \& (\deno T \sequoid (A' \tensor X)) \sequoid X \arrow[d, "{\passoc_{\deno T,A',X}\inv\sequoid X}"] \\
+            (Y \tensor X) \tensor X \arrow[r, "{\wk_{Y,X}\tensor X}", dotted] \arrow[d, "\Lambda\inv(\Lambda\inv(\eta))"', thick, dashed]
+              \& (Y \sequoid X) \tensor X \arrow[dr, "{\wk_{Y\sequoid X,X}}" description, dotted] \arrow[dl, "\Lambda\inv(\Lambda_s\inv(\eta))" description, dotted]
+                \& ((\deno T \sequoid A') \sequoid X) \sequoid X \arrow[d, "(\tau'\sequoid X) \sequoid X"] \\
+            X
+              \&
+                \& (Y \sequoid X)\sequoid X \arrow[ll, "\Lambda_s\inv(\Lambda_s\inv(\eta))"']
+          \end{tikzcd}
+          \]
+          \normalsize
+        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.
+        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\eta)$ is well-defined.}
+        \label{FigEvContextCond}
+      \end{SidewaysFigure}
+    \item Lastly, suppose that $\EE = \EE' \gets n$ for some numeral $n$, where $\EE'$ is a context of type $\Var$, and suppose that $M\from T$ fits into the hole.  
+      The denotation $\deno{\Gamma\ts \EE[M]}$ is given by
+      \[
+        \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts \EE'[M]}} \Varr \xrightarrow{\lunit_{\Varr}} I \tensor \Varr \xrightarrow{n\tensor\Varr} \bN \tensor \Varr \xrightarrow{\assign} \bC\,.
+        \]
+      By the induction hypothesis, $\deno{\Gamma\ts\EE'[M]}$ takes the form
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}}
+        \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'}
+        \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}}
+        \deno T\sequoid A' \xrightarrow{\tau'}
+        \Varr\,,
+        \]
+      for suitable $A',\sigma',\tau'$.  
+      Then, if we compose on the right by the morphism $\lunit_{\Varr};(n\tensor\Varr);\assign$, in order to give us the denotation $\deno{\Gamma\ts \EE'[M]\gets n} = \deno{\Gamma\ts\EE[M]}$, then we are already in the required form, with
+      \begin{mathpar}
+        A = A' \and \sigma = \sigma' \and \tau = \tau';\lunit_{\Varr};(n\tensor\Varr);\assign\,.\hspace{1em plus 1fill}\qedhere
+      \end{mathpar}
+  \end{itemize}
+\end{proof}
+
+Our next lemma will help us deal with the base $\oopto$ rules.  
+We will then use Lemma \ref{LemEvContexLemma} to extend this to the $\opto$ relation.
+
+\begin{lemma}
+  Suppose that $\Gamma,s\ts M \oopto \Gamma',s'\ts N$, where $M,N$ have type $T$.
+  Then the following diagram commutes.
+  \[
+    \begin{tikzcd}[column sep=40pt]
+      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
+        & \oc S_\Gamma \arrow[r, "\cell^n"]
+          & \oc V_\Gamma \arrow[r, "\mu_{V_\Gamma}"]
+            & \oc V_\Gamma \tensor \oc V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
+      \oc \bN \arrow[d, "\cell^n"']
+        &
+          &
+            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc V_\Gamma}}"] \\
+      \oc V_\Gamma \arrow[r, "\mu_{V_\Gamma}"]
+        & \oc V_\Gamma \tensor \oc V_\Gamma \arrow[r, "\deno{\Gamma\ts N} \tensor \oc V_\Gamma"]
+          & \deno T \tensor \oc V_\Gamma \arrow[r, "{\wk_{\deno T,\oc V_\Gamma}}"]
+            & \deno T \sequoid \oc V_\Gamma
+    \end{tikzcd}
+    \]
+\end{lemma}
+\begin{proof}
+  \begin{itemize}
+    \item For most of the rules, 
+  \end{itemize}
+\end{proof}
 

### 2019-03-31 Thesis/games.tex
Daily commit.

@@
 
+The most important feature of strategies of the form $(\sigma_x)$ is the most obvious one: given $X$, and $y\in X$, we have a strategy $y$ for the game $X$ with maximal play $qx$.  
+Then $y;(\sigma_x) = \sigma_y$.
+
 Now we define morphisms
@@
 
-This time, instead of defining a relation $\Gamma,s\ts M\converges c,s'$, we define a relation $\Gamma,s\ts M\opto \Gamma',s'\ts M'$, where
+This time, instead of defining a relation $\Gamma,s\ts M\converges c,s'$, we define a relation $\Gamma,s\ts M\opto \Gamma,\Delta,s'\ts M'$, where
 \begin{itemize}
-  \item $\Gamma,\Gamma'$ are $\Var$-contexts; 
-  \item $s$ is a $\Gamma$-store and $s'$ a $\Gamma'$-store;  and
-  \item $\Gamma\ts M$, $\Gamma'\ts M'$ are Idealized Algol terms-in-context.
+  \item $\Gamma,\Delta$ are disjoint $\Var$-contexts; 
+  \item $s$ is a $\Gamma$-store and $s'$ a $\Gamma,\Delta$-store;  and
+  \item $\Gamma\ts M$, $\Gamma,\Delta\ts M'$ are Idealized Algol terms-in-context.
 \end{itemize}
@@
 
-Next, we define a relation $\Gamma,s,M\oopto\Gamma',s',M'$ as in Figure \ref{FigIaSsOpSem}.
+Next, we define a relation $\Gamma,s,M\oopto\Gamma,\Delta,s',M'$ as in Figure \ref{FigIaSsOpSem}.
 
@@
 \[
-  \inferrule*{ \Gamma,s\ts M\oopto \Gamma',s'\ts M'}{\Gamma,s\ts \EE[M] \opto \EE[M']}
+  \inferrule*{ \Gamma,s\ts M\oopto \Gamma,\Delta,s'\ts M'}{\Gamma,s\ts \EE[M] \opto \Gamma,\Delta,s'\ts\EE[M']}
   \]
@@
     \\
-    \Gamma,s \ts \pred n+1 \oopto \Gamma,s\ts n
+    \Gamma,s \ts \pred (n+1) \oopto \Gamma,s\ts n
     \and
@@
     \and
-    \Gamma,s\ts \IfO n+1 \Then N \Else P \oopto \Gamma,s\ts P
+    \Gamma,s\ts \IfO (n+1) \Then N \Else P \oopto \Gamma,s\ts P
     \and
@@
 We need to prove that this is equivalent to our original semantics.
-Given a $\Gamma'$-store $s$, and a sub-context $\Gamma$ of $\Gamma'$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.
+Given a $\Gamma,\Delta$-store $s$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.
 
 \begin{lemma}
-  Suppose that $\Gamma,s\ts M \oopto \Gamma',s'\ts M'$ and that $\Gamma',s'\ts \EE[M'] \converges c,s''$.  
+  Suppose that $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts M'$ and that $\Gamma,\Delta,s'\ts \EE[M'] \converges c,s''$.  
   Then $\Gamma,s\ts \EE[M]\converges c,s''\vert_\Gamma$.
@@
 
-  If $\EE=\EE'\,N$, for some term $N$, then we have $\Gamma',s'\ts \EE'[M']\,N\converges c,s''$.  
+  If $\EE=\EE'\,N$, for some term $N$, then we have $\Gamma,\Delta,s'\ts \EE'[M']\,N\converges c,s''$.  
   By inspection of the rules in Figure \ref{FigIaOpSem}, the derivation of this must end with a rule of the form
   \[
-    \inferrule*{\Gamma',s'\ts \EE'[M'] \converges \lambda x.M'',t \\ \Gamma',t \ts M''[N/x] \converges c,s''}
-    {\Gamma',s'\ts \EE'[M']\,N \converges c,s''}\,.
-    \]
-  Thus, $\Gamma',s'\ts \EE'[M']\converges \lambda x.M'',t$ must be provable for some $M'',t$.
+    \inferrule*{\Gamma,\Delta,s'\ts \EE'[M'] \converges \lambda x.M'',t \\ \Gamma,\Delta,t \ts M''[N/x] \converges c,s''}
+    {\Gamma,\Delta,s'\ts \EE'[M']\,N \converges c,s''}\,.
+    \]
+  Thus, $\Gamma,\Delta,s'\ts \EE'[M']\converges \lambda x.M'',t$ and $\Gamma,\Delta\ts M''[N/x]\converges c,s''$ must be provable for some $M'',t$.
   By the induction hypothesis, this means that $\Gamma,s\ts \EE'[M]\converges \lambda x.M'',t$ is provable.
@@
   \[
-    \inferrule*{\Gamma',s\ts \EE'[M] \converges \lambda x.M'',t \\ \Gamma',t \ts M''[N/x] \converges c,s''}
-    {\Gamma',s\ts \EE'[M]\,N\converges c,s''\vert_{\Gamma'}}\,.
-    \]
-  Then, because any extra variables in $\Gamma'$ are not mentioned in $\EE'[M]\,N$ or in $c$, we have
+    \inferrule*{\Gamma,\Delta,s\ts \EE'[M] \converges \lambda x.M'',t \\ \Gamma,\Delta,t \ts M''[N/x] \converges c,s''}
+    {\Gamma,\Delta,s\ts \EE'[M]\,N\converges c,s''\vert_{\Gamma,\Delta}}\,.
+    \]
+  Then, because any variables in $\Delta$ are not mentioned in $\EE'[M]\,N$ or in $c$, we have
   \[
@@
       \begin{mathpar}
-        \Gamma,s \ts M \opto \cdots \opto \Gamma',t',\lambda x.M'
-        \and
-        \Gamma,s' \ts M'[N/x]\opto \cdots \opto \Gamma'',t'',c\,,
+        \Gamma,s \ts M \opto \cdots \opto \Gamma,\Delta,t',\lambda x.M'
+        \and
+        \Gamma,s' \ts M'[N/x]\opto \cdots \opto \Gamma,\Delta',t'',c\,,
       \end{mathpar}
@@
         \begin{mathpar}
-          \Gamma,s \ts MN \opto \cdots \opto \Gamma',t',(\lambda x.M')N \opto \Gamma',t',M'[N/x] \opto \cdots \opto \Gamma'\cup\Gamma'',t''\setminus t',c\,,
+          \Gamma,s \ts MN \opto \cdots \opto \Gamma,\Delta,t',(\lambda x.M')N \opto \Gamma,\Delta,t',M'[N/x] \opto \cdots \opto \Gamma,\Delta\cup\Delta',t''\setminus t',c\,,
         \end{mathpar}}
       \end{center}
-      where $t''\setminus t'$ is the $\Gamma'\cup\Gamma''$-store that agrees with $t''$ on $\Gamma''$ and with $t'$ on $\Gamma'\setminus\Gamma''$.
+      where $t''\setminus t'$ is the $\Gamma,\Delta\cup\Delta'$-store that agrees with $t''$ on $\Gamma,\Delta'$ and with $t'$ on $\Delta\setminus\Delta'$.
       Then $(t''\setminus t')\vert_{\Gamma}=s''$.
@@
       \begin{mathpar}
-        \Gamma,s\ts E \opto \cdots \opto \Gamma',t',n
-        \and
-        \Gamma,s'\ts V \opto \cdots \opto \Gamma'',t'',x\,,
+        \Gamma,s\ts E \opto \cdots \opto \Gamma,\Delta,t',n
+        \and
+        \Gamma,s'\ts V \opto \cdots \opto \Gamma,\Delta',t'',x\,,
       \end{mathpar}
@@
         \begin{mathpar}
-          \Gamma,s\ts V\gets E \opto \cdots \opto \Gamma',t',V\gets n \opto \cdots \opto \Gamma'\cup\Gamma'',t''\setminus t',x\gets n \opto \Gamma'\cup\Gamma'',(t''\setminus t'\vert x\mapsto n)\,,
+          \Gamma,s\ts V\gets E \opto \cdots \opto \Gamma,\Delta,t',V\gets n \opto \cdots \opto \Gamma,\Delta\cup\Delta',t''\setminus t',x\gets n \opto \Gamma,\Delta\cup\Delta',(t''\setminus t'\vert x\mapsto n)\,,
         \end{mathpar}}
@@
       \[
-        \Gamma,s\ts V \opto \cdots \opto \Gamma',t'\ts x\,,
+        \Gamma,s\ts V \opto \cdots \opto \Gamma,\Delta,t'\ts x\,,
         \]
@@
       \[
-        \Gamma,s\ts \oc V \opto \cdots \opto \Gamma',t'\ts \oc x \opto \Gamma',t'\ts t'(x)\,,
+        \Gamma,s\ts \oc V \opto \cdots \opto \Gamma,\Delta,t'\ts \oc x \opto \Gamma,\Delta,t'\ts t'(x)\,,
         \]
@@
       \[
-        \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma',x,(t'\vert x\mapsto n),c\,,
+        \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma,\Delta,x,(t'\vert x\mapsto n),c\,,
         \]
@@
       Then we may add a term at the beginning to give us
-      \[
-        \Gamma,s \ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma',x,(t'\vert x\mapsto n),c\,,
-        \]
+      \begin{center}
+        \parbox{0.6\textwidth}{
+        \begin{mathpar}
+          \Gamma,s \ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma,\Delta,x,(t'\vert x\mapsto n),c\,,
+        \end{mathpar}}
+      \end{center}
       where $(t'\vert x\mapsto n) \vert_\Gamma=s'$.\qedhere
@@
 
-Given $\Gamma$, we have a morphism $\cell^n\from \oc S_\Gamma \implies \oc V_\Gamma$, given by
+Given $\Gamma$, we have a morphism $\cell^\Gamma\from \oc S_\Gamma \implies \oc V_\Gamma$, given by
 \[
@@
 \begin{lemma}
-  For $j=1,\cdots,n$, the following diagram commutes.
+  For $j=1,\cdots,|\Gamma|$, the following diagram commutes.
   \[
     \begin{tikzcd}
-      \oc S_\Gamma \arrow[r, "\cell^n"] \arrow[d, "\oc\pr_j"']
+      \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "\oc\pr_j"']
         & \oc V_\Gamma \arrow[d, "\oc \pr_j"] \\
@@
   Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context, and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
-  Then there is a game $A$ and strategies $\sigma\from \oc\V_\Gamma \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$ such that $\tau$ is a strict strategy and the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
+  Then there is a game $A$ and strategies $\sigma\from \oc\V_\Gamma \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$, where $\tau$ is a strict strategy, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
   \[
@@
         \[
-          \begin{tikzcd}[ampersand replacement=\&, column sep=78pt, row sep=20pt]
+          \begin{tikzcd}[ampersand replacement=\&, column sep=78pt, row sep=30pt]
             \oc \V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}"] \arrow[d, "\mu_{\V_\Gamma}"', thick, dashed]
@@
           \normalsize
-        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.
-        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\eta)$ is well-defined.}
+        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.
+        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\Lambda_s\inv(\eta))$ is well-defined.}
         \label{FigEvContextCond}
@@
 \begin{lemma}
-  Suppose that $\Gamma,s\ts M \oopto \Gamma',s'\ts N$, where $M,N$ have type $T$.
+  Suppose that $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$.
   Then the following diagram commutes.
   \[
-    \begin{tikzcd}[column sep=40pt]
+    \begin{tikzcd}[column sep=28pt]
       I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
-        & \oc S_\Gamma \arrow[r, "\cell^n"]
-          & \oc V_\Gamma \arrow[r, "\mu_{V_\Gamma}"]
-            & \oc V_\Gamma \tensor \oc V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
-      \oc \bN \arrow[d, "\cell^n"']
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
+            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
+      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
         &
           &
-            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc V_\Gamma}}"] \\
-      \oc V_\Gamma \arrow[r, "\mu_{V_\Gamma}"]
-        & \oc V_\Gamma \tensor \oc V_\Gamma \arrow[r, "\deno{\Gamma\ts N} \tensor \oc V_\Gamma"]
-          & \deno T \tensor \oc V_\Gamma \arrow[r, "{\wk_{\deno T,\oc V_\Gamma}}"]
-            & \deno T \sequoid \oc V_\Gamma
+            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"] \\
+      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
+        &
+          &
+            &  \deno{T}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{T} \sequoid (\Gamma+0_\Delta)}"] \\
+      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts N} \tensor \oc \V_{\Gamma,\Delta}}"]
+        &
+          & {\deno T \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"]
+            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,,}
     \end{tikzcd}
     \]
+  where $\Gamma+0_\Delta\from \oc \V_\Gamma \to \oc \V_{\Gamma,\Delta}$ is the composite
+  \[
+    \oc \V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc \V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor \oc0} \oc\V_\Gamma \tensor \oc S_\Delta \xrightarrow{\oc\V_\Gamma\tensor \cell^\Delta} \oc \V_\Gamma \tensor \oc \V_\Delta \to \oc \V_{\Gamma,\Delta}\,;
+    \]
+  i.e., the morphism given by initializing new storage cells to $0$ for all the new variables in $\Delta$.
+  \label{LemSoundnessOopto}
 \end{lemma}
 \begin{proof}
+  We prove this on a case-by-case basis.
   \begin{itemize}
-    \item For most of the rules, 
+    \item For most of the rules, $\Delta=\_$ and $s=s'$; i.e., the rule is of the form
+      \[
+        \Gamma,s\ts M \oopto \Gamma,s \ts N
+        \]
+      for some $M,N$.
+      In such a case, it suffices to show that $\deno{\Gamma\ts M}=\deno{\Gamma\ts N}$.
+      Indeed, we have
+      \begin{itemize}
+        \item $\deno{\Gamma\ts(\lambda x.M)N} = \deno{\Gamma\ts M[N/x]}$ (by a usual substitution-lemma argument);
+        \item $\deno{\Gamma\ts\Y M} = \deno{\Gamma\ts (\lambda F.\lambda f.f(F f)) \Y M} = \deno{\Gamma\ts M(\Y M)}$;
+        \item $\deno{\Gamma\ts \suc n} = \deno{\Gamma \ts n+1}$;
+        \item $\deno{\Gamma\ts \pred (n+1)} = \deno{\Gamma\ts n}$;
+        \item $\deno{\Gamma\ts \pred 0} = \deno{\Gamma\ts 0}$;
+        \item $\deno{\Gamma\ts\skipp;M} = \deno{\Gamma\ts M}$;
+        \item $\deno{\Gamma\ts\If \true \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.x)NP} = \deno{\Gamma\ts N}$;
+        \item $\deno{\Gamma\ts\If \false \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
+        \item $\deno{\Gamma\ts\IfO 0 \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.x)NP} = \deno{\Gamma\ts N}$;
+        \item $\deno{\Gamma\ts\IfO (n+1) \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
+        \item \parbox[t][][t]{0.8\textwidth}{$\deno{\Gamma\ts(\mkvar W\,R)\gets n} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_n = \deno{\Gamma\ts Wn}$; and}
+        \item $\deno{\Gamma\ts\oc(\mkvar W\,R)} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_{\bN} = \deno{\Gamma\ts R}$.
+      \end{itemize}
+    \item Now consider the rule
+      \[
+        \Gamma,s\ts\neww \lambda x.M\oopto \Gamma,x,(s\vert x\mapsto 0)\ts M\,,
+        \]
+      where $\Gamma\ts M\from T$.
+      The first observation to make is that the denotation $\deno{\Gamma\ts \neww \lambda x.M}$ may be written as
+      \[
+        \oc\V_\Gamma \xrightarrow{\Gamma + 0_x} \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,
+        \]
+      where $\Gamma+0_x$ is as defined in the statement of this Lemma.
+      Of course, $\Lambda\inv(\deno{\Gamma\ts \lambda x.M})=\deno{\Gamma,x\ts M}$.
+
+      Next, we claim that we have a commutative diagram
+      \[
+        \begin{tikzcd}
+          \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "{\oc\langle S_\Gamma,0\rangle}"']
+            & \oc \V_\Gamma \arrow[d, "\Gamma+0_x"] \\
+          {\oc S_{\Gamma,x}} \arrow[r, "{\cell^{\Gamma,x}}"]
+            & {\oc \V_{\Gamma,x}\,.}
+        \end{tikzcd}
+        \]
+      Indeed, we have the diagram
+      \[
+        \begin{tikzcd}[column sep=2pt, row sep=20pt]
+          \oc S_\Gamma \arrow[r] \arrow[dddd, "{\oc\langle S_\Gamma,0\rangle}"' description]
+            &[5pt] \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell\tensor \cdots \tensor \cell"] \arrow[d, "\runit" description]
+              &[10pt] \oc\Varr \tensor \cdots \tensor \oc\Varr \arrow[r] \arrow[d, "\runit" description]
+                & \oc\V_\Gamma \arrow[d, "\runit" description] \\
+          %
+            & \oc \bN \tensor \cdots \tensor \oc\bN \tensor I \arrow[r, "\cell \tensor \cdots \tensor \cell \tensor I" yshift=6pt] \arrow[ddd, "\oc\bN \tensor \cdots \tensor \oc\bN \tensor \oc0" description]
+              & \oc \Varr \tensor \cdots \tensor \oc\Varr\tensor I \arrow[d, "\oc\Varr \tensor \cdots \tensor \oc\Varr \tensor I" description] \arrow[r]
+                & \oc\V_\Gamma \tensor I \arrow[d, "\oc\V_\Gamma\tensor\oc0" description] \\
+          %
+            &
+              & \oc\Varr \tensor \cdots \tensor \oc\Varr\tensor \oc\bN \arrow[r] \arrow[dd, "\oc\Varr\tensor\cdots\tensor\oc\Varr\tensor\cell" description]
+                & \oc\V_\Gamma \tensor \oc\bN \arrow[d, "\oc\V_\Gamma\tensor\cell" description] \\
+          %
+            &
+              &
+                & \oc\V_\Gamma\tensor\oc\Varr \arrow[d] \\
+          {\oc S_{\Gamma,x}} \arrow[r]
+            & \oc\bN \tensor\cdots \tensor\oc\bN \tensor\oc\bN \arrow[uur, "\cell\tensor\cdots\tensor\cell\tensor\oc\bN" {description, near start}] \arrow[r, "\cell\tensor\cdots\tensor\cell\tensor\cell"' yshift=-3pt]
+              & \oc\Varr \tensor \cdots\tensor\oc\Varr \tensor \oc\Varr \arrow[ur] \arrow[r]
+                & {\oc\V_{\Gamma,x}\,.}
+        \end{tikzcd}
+        \]
+      Now the diagram in Figure \ref{FigSoundnessOoptoNew} shows us that the conclusion of the lemma is satisfied for this rule.
+      \begin{SidewaysFigure}
+        \[
+          \begin{tikzcd}[ampersand replacement=\&, column sep=50pt, row sep=40pt]
+            I \arrow[r, "\oc\deno s"] \arrow[d, "\oc(\deno s\times 0)"']
+              \& \oc S_\Gamma \arrow[dl, "{\oc\langle S_\Gamma,0\rangle}" description] \arrow[dr, "\mu_{S_\Gamma}" description] \arrow[r, "\cell^\Gamma" description]
+                \& \oc \V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}"]
+                  \&
+                    \& \oc \V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "(\Gamma + 0_x)\tensor\oc\V_\Gamma"] \arrow[ddddllll, "(\Gamma+0_x)\tensor(\Gamma+0_x)" description, bend left=12] \\
+            {\oc S_{\Gamma,x}} \arrow[dr, "\mu_{S_\Gamma}" description] \arrow[d, "{\cell^{\Gamma,x}}"']
+              \&
+                \& \oc S_\Gamma \tensor \oc S_\Gamma \arrow[urr, "\cell^{\Gamma} \tensor \cell^{\Gamma}" {description, near start}, bend left=10] \arrow[dl, "{\oc\langle S_\Gamma,0\rangle\tensor\oc\langle S_\Gamma,0\rangle}" description]
+                  \& 
+                    \& {\oc\V_{\Gamma,x}\tensor\oc\V_\Gamma} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\V_\Gamma}"] \\
+            {\oc\V_{\Gamma,x}} \arrow[dd, "{\mu_{\V_{\Gamma,x}}}"']
+              \& {\oc S_{\Gamma,x}\tensor\oc S_{\Gamma,x}} \arrow[ddl, "{\cell^{\Gamma,x}\tensor\cell^{\Gamma,x}}"' {description, near start}, bend right=10]
+                \&
+                  \&
+                    \& \deno T \tensor \oc\V_{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \arrow[ddll, "\deno T \tensor (\Gamma + 0_x)" description, bend left=8] \\
+            %
+              \&
+                \&
+                  \&
+                    \& \deno T \sequoid \oc\V_\Gamma\arrow[d, "{\deno T \sequoid (\Gamma + 0)}"] \\
+            {\oc \V_{\Gamma,x} \tensor \oc \V_{\Gamma,x}} \arrow[rr, "{\deno{\Gamma,x\ts M}\tensor \oc\V_{\Gamma,x}}"]
+              \&
+                \& {\deno T \tensor \oc\V_{\Gamma,x}} \arrow[rr, "{\wk_{\deno T,\oc\V_{\Gamma,x}}}"]
+                  \&
+                    \& {\deno T\sequoid\oc\V_{\Gamma,x}}
+          \end{tikzcd}
+          \]
+        \caption{The reduction $\Gamma,s\ts\neww\lambda x.M\oopto\Gamma,x,(s\vert x\mapsto 0)\ts M$ satisfies the conclusion of Lemma \ref{LemSoundnessOopto}.}
+        \label{FigSoundnessOoptoNew}
+      \end{SidewaysFigure}
+    \item Now consider the rule
+      \[
+        \Gamma,s\ts x\gets n \oopto \Gamma,(s\vert x\mapsto n) \ts \skipp\,.
+        \]
   \end{itemize}

### 2019-04-01 Thesis/games.tex
D.

@@
     \and
-    \Gamma,s\ts x \gets n \oopto \Gamma,(s\vert x\mapsto n)\ts \skipp
-    \and
-    \Gamma,s\ts \oc x \oopto \Gamma,s\ts s(x)
+    x,\Gamma,s\ts x \gets n \oopto x,\Gamma,(s\vert x\mapsto n)\ts \skipp
+    \and
+    x,\Gamma,s\ts \oc x \oopto x,\Gamma,s\ts s(x)
     \\
@@
 \begin{lemma}
-  Suppose that $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$.
-  Then the following diagram commutes.
+  The relation $\oopto$ betwen triples $\Gamma,s\ts M$ preserves the composite
+  \[
+    \oc\deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_{\Gamma}}\,.
+    \]
+  In other words, if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, then the following diagram commutes.
   \[
@@
           &
-            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"] \\
+            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma}}}"] \\
       {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
@@
       \end{SidewaysFigure}
-    \item Now consider the rule
-      \[
-        \Gamma,s\ts x\gets n \oopto \Gamma,(s\vert x\mapsto n) \ts \skipp\,.
-        \]
+    \item Now consider the rules
+      \begin{mathpar}
+        x,\Gamma,s\ts x\gets n \oopto x,\Gamma,(s\vert x\mapsto n) \ts \skipp
+        \and
+        x,\Gamma,s\ts \oc x\oopto x,\Gamma,s\ts s(x)\,.
+      \end{mathpar}
+      In each of these cases, the outer context $\Gamma$ is unchanged by the rule; moreover, each term ignores the variables in $\Gamma$.
+      So the denotations terms-in-context $x,\Gamma\ts M\from T$ on either side of each rule are of the form
+      \[
+        \oc\V_{x,\Gamma} \xrightarrow{\oc\pr_1} \oc \Varr \xrightarrow{\deno{x\ts M}} \deno{T}\,.
+        \]
+      Now the diagram in Figure \ref{FigSoundnessOoptoContext} tells us that each
+      \[
+        \oc\deno{s};\cell^{x,\Gamma};\mu_{\V_{x,\Gamma}};(\deno{x,\Gamma\ts M}\tensor\oc\V_{x,\Gamma});\wk_{\deno T,\oc\V_{x,\Gamma}}\,\text{--}
+        \]
+      i.e., the composites we are trying to show are preserved by the $\oopto$ relation -- may be written as
+      \begin{mathpar}
+        \oc\deno{s\vert_\Gamma};\cell^\Gamma;\lunit_{\oc\V_\Gamma};\\((\oc\deno{s\vert_x};\cell;\mu_{\Varr};(\deno{x\ts M}\tensor\oc\Varr);\wk_{\deno T,\oc\Varr})\tensor\oc\V_\Gamma);\\\wk_{\deno T\sequoid \oc\Varr,\oc\V_\Gamma};\passoc_{\deno T,\oc\Varr,\oc\V_\Gamma};\cong
+      \end{mathpar}
+      (where $\cong$ represents the natural isomorpism between $\deno T\sequoid(\oc\Varr\tensor\oc\V_\Gamma)$ and $\deno T \sequoid\oc\V_{x,\Gamma}$),
+      and so is determined by the composite
+      \[
+        \oc\deno{s\vert_x};\cell;\mu_{\Varr};(\deno{x\ts M}\tensor\oc\Varr);\wk_{\deno T,\oc\Varr}\,;
+        \]
+      i.e., the composite that we would get if $\Gamma$ were empty.
+      This tells us that we can assume that $\Gamma$ is the empty context when we want to deal with these two cases.
+      \begin{SidewaysFigure}
+        \[
+          \begin{tikzcd}[ampersand replacement=\&, column sep=5pt]
+            I \arrow[r, "\oc\deno{s\vert_\Gamma}"] \arrow[d, "\oc\deno s"' {description, yshift=2pt}, thick, dashed]
+              \& \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[dr, "\lunit_{\oc S_\Gamma}" description, dotted]
+                \&[18pt] \oc \V_\Gamma \arrow[r, "\lunit_{\oc\V_\Gamma}"] 
+                  \&[18pt] I \tensor \oc\V_\Gamma \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\V_\Gamma" description, thick] \\
+            {\oc S_{x,\Gamma}} \arrow[drr, Isom, dotted] \arrow[dd, "{\cell^{x,\Gamma}}"' description, thick, dashed]
+              \&
+                \& I \tensor \oc S_\Gamma \arrow[ur, "I \tensor\cell^\Gamma" description, dotted] \arrow[d, "\oc\deno{s\vert_x}\tensor\oc S_\Gamma" description, dotted]
+                  \& \\
+            %
+              \&
+                \& \oc\bN\tensor\oc S_\Gamma \arrow[r, "\oc\bN\tensor\cell^\Gamma" description, dotted] \arrow[dr, "\cell\tensor\cell^\Gamma" description, dotted]
+                  \& \oc\bN \tensor\oc\V_\Gamma \arrow[d, "\cell\tensor\oc\V_\Gamma" description, thick] \\
+            {\oc\V_{x,\Gamma}} \arrow[rrr, Isom, dotted] \arrow[d, "{\mu_{\V_{x,\Gamma}}}"' description, thick, dashed]
+              \&
+                \&
+                  \& \oc\Varr \tensor \oc\V_\Gamma \arrow[d, "\mu_{\Varr}\tensor\oc\V_\Gamma" description, thick] \arrow[dl, "\mu_{\Varr}\tensor\mu_{\V_\Gamma}" description, bend right=15, dotted] \\[10pt]
+            {\oc\V_{x,\Gamma}\tensor\oc\V_{x,\Gamma}} \arrow[r, dotted] \arrow[d, "{\oc\pr_1\tensor\oc\V_{x,\Gamma}}" description, dotted] \arrow[dd, "{\deno{x,\Gamma\ts M}\tensor\oc\V_{x,\Gamma}}" description, bend right=68, thick, dashed, end anchor={[xshift=-3pt]}]
+              \& (\oc\Varr \tensor \oc\V_\Gamma) \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[r, dotted] \arrow[d, "(\oc\Varr\tensor())\tensor(\oc\Varr\tensor\oc\V_{\Gamma})" description, dotted]
+                \& (\oc\Varr \tensor \oc\Varr) \tensor (\oc\V_\Gamma \tensor\oc\V_\Gamma) \arrow[r, "(\oc\Varr\tensor\oc\Varr)\tensor(()\tensor\oc\V_\Gamma)" yshift=5pt, dotted]
+                  \& (\oc\Varr \tensor \oc\Varr) \tensor\oc\V_\Gamma \arrow[d, "(\deno{x\ts M}\tensor \oc\Varr) \tensor \oc\V_\Gamma" description, thick] \\[30pt]
+            {\oc\Varr \tensor \oc\V_{x,\Gamma}} \arrow[r, Isom, dotted] \arrow[d, "{\deno{x\ts M} \tensor \oc\V_{x,\Gamma}}"' {description, yshift=1pt}, dotted]
+              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt, dotted]}, bend left=5] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
+                \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma}}" description, dotted]
+                  \& (\deno T \tensor \oc\Varr) \tensor \oc\V_\Gamma\arrow[d, "{\wk_{\deno T,\oc\Varr}\tensor\oc\V_\Gamma}" {description, yshift=1pt}, thick] \\
+            {\deno T \tensor \oc\V_{x,\Gamma}} \arrow[d, "{\wk_{\deno T,\oc\V_{x,\Gamma}}}"' {description, yshift=2pt}, thick, dashed] \arrow[urr, Isom, dotted]
+              \&
+                \&
+                  \& (\deno T \sequoid \oc\Varr) \tensor \oc\V_\Gamma \arrow[d, "{\wk_{(\deno T\sequoid\oc\Varr),\oc\V_\Gamma}}" {description, yshift=2pt}] \\[5pt]
+            {\deno T \sequoid \oc\V_{x,\Gamma}} \arrow[r, Isom]
+              \& \deno T \sequoid (\oc\Varr \tensor\oc\V_\Gamma)
+                \&
+                  \& (\deno T \sequoid \oc\Varr) \sequoid\oc\V_\Gamma \arrow[ll, "{\passoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}"]
+          \end{tikzcd}
+          \]
+          \caption{Diagram proving that if we want to prove the conclusion of Lemma \ref{LemSoundnessOopto} for a small-step rule that does not change the context and only mentions one variable, then it suffices to assume that that variable is the only variable in the context.}
+          \label{FigSoundnessOoptoContext}
+      \end{SidewaysFigure}
   \end{itemize}

### 2019-04-01 Thesis/games.tex
Nightly commit.

@@
 
+Note also that if $m,n$ are integers, then any permutations $\sigma$ of $1,\cdots,m$ and $\pi$ of $1,\cdots,n$ induce a permutation $[\sigma,\pi]$ of $1,\cdots,m+n$.  
+Then we get morphisms
+\[
+  A^{m+n} \to A^{\tensor (m+n)} \to A^{\tensor m} \tensor A^{\tensor n}\,,
+  \]
+which are equalized by all symmetries on $A^{\tensor m}$ and $A^{\tensor n}$ individually.  
+Since the equalizers $A^m$ and $A^n$ are preserved by the tensor product, then we get an induced morphisms
+\[
+  A^{m+n}\to A^m\tensor A^n\,.
+  \]
+
 \begin{theorem}[\cite{MelliesCofCommCom}]
@@
   Suppose that this sequence has a limit $\oc A$, and that $B\tensor \oc A$ is the limit of the first sequence for all $B$.
-  Then $\oc A$ has the structure of the cofree commutative comonoid on $A$.
+
+  For each $m$, we can define morphisms
+  \[
+    \oc A \to A^{m+n} \to A^m \tensor A^n
+    \]
+  for each $n$, which commute with the morphisms $A^{n+1}\to A^n$ and hence induce a morphism $\oc A \to A^m \tensor \oc A$.  
+  Then these morphisms themselves commute with the morphisms $A^{m+1}\tensor \oc A \to A^m \tensor \oc A$, and so we get a morphism $\mu_A\from \oc A \to \oc A \tensor \oc A$.
+
+  The morphisms $\mu_A\from \oc A \to \oc A \tensor \oc A$ and $()\from A \to I$ give $\oc A$ the structure of a commutative comonoid in $\C$.  
+  In fact, this is the \emph{cofree commutative comonoid} over $A$ in $\C$.  
+  The counit $\der_A\from \oc A \to A$ of the adjunction is the map in the limiting cone.
   \label{TheMtt}
@@
   \]
+
+One small thing we need to do is to relate the two structures on the exponential.
+
+\begin{proposition}
+  The final coalgebra
+  \[
+    \alpha\from \oc A \to A \sequoid \oc A
+    \]
+  is given by the composite
+  \[
+    \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A \xrightarrow{\der_A\tensor \oc A} A \tensor \oc A \xrightarrow{\wk_A,\oc A} A \sequoid \oc A\,.
+    \]
+  \label{PropFormulaForAlpha}
+\end{proposition}
+\begin{proof}
+  By Theorem \ref{TheMtt}, we can tell that this composite is a copycat strategy between $\oc A$ and $A \sequoid \oc A$, as is $\alpha$.  
+  Since $A$ is well-opened, there is a unique such strategy.
+\end{proof}
 
@@
                 \&[18pt] \oc \V_\Gamma \arrow[r, "\lunit_{\oc\V_\Gamma}"] 
-                  \&[18pt] I \tensor \oc\V_\Gamma \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\V_\Gamma" description, thick] \\
+                  \&[17pt] I \tensor \oc\V_\Gamma \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\V_\Gamma" description, thick] \\
             {\oc S_{x,\Gamma}} \arrow[drr, Isom, dotted] \arrow[dd, "{\cell^{x,\Gamma}}"' description, thick, dashed]
@@
       \end{SidewaysFigure}
+
+      Now we have a commutative diagram
+      \begin{figure}[htbp]
+        \[
+          \begin{tikzcd}[column sep=41pt, row sep=30pt]
+            I \arrow[r, "\oc s(x)"] \arrow[d, "\oc n" description] \arrow[dr, Rightarrow, no head]
+              & \oc \bN \arrow[r, "\cell"] \arrow[d, "()" description] \arrow[dr, "\cell_0" description]
+                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}]
+                  & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" description]  \\
+            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}]
+              & I \arrow[l, "\oc n" description]
+                & \Varr \sequoid \oc\bN \arrow[d, "\Varr\sequoid\cell" description] \arrow[dd, "\pr_n\sequoid\oc\bN" {description, pos=0.44}, controls={+(-2.5,-0.2) and (-0.5,0.5)}]
+                  & \Varr \tensor \oc\Varr \arrow[dl, "{\wk_{\Varr,\oc\Varr}}" description] \arrow[dd, "\pr_n\tensor\oc\Varr" description] \\
+            %
+              & \bC \tensor \oc\bN \arrow[dr, "{\wk_{\bC,\oc\bN}}" description] \arrow[ddr, "\bC \tensor \cell" description]
+                & \Varr \sequoid\oc\Varr \arrow[ddr, "\pr_n\sequoid\oc\Varr" description]
+                  & \\
+            \oc\Varr \arrow[d, "\mu_{\Varr}" description] \arrow[dr, "\lunit_{\oc\Varr}" description]
+              & I \tensor \oc\bN \arrow[u, "\skipp\tensor\oc\bN" {description, pos=0.44}] \arrow[d, "I\tensor \cell" description]
+                & \bC \sequoid \oc\bN \arrow[dr, "\bC \sequoid \cell" description]
+                  & \bC \tensor \oc\Varr \arrow[d, "{\wk_{\bC,\oc\Varr}}" {description, pos=0.44}] \\
+            \oc\Varr \tensor \oc\Varr \arrow[r, "()\tensor\oc\Varr"']
+              & I \tensor \oc\Varr \arrow[r, "\skipp \tensor \oc\Varr"']
+                & \oc\bC \tensor \oc\Varr \arrow[r, "{\wk_{\bC,\oc\Varr}}"']
+                  & \bC \sequoid \oc\Varr
+          \end{tikzcd}
+          \]
+      \end{figure}
   \end{itemize}

### 2019-04-02 Thesis/games.tex
Did another big fuck-off diagram.

@@
 Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
+In other words, by Proposition \ref{PropFormulaForAlpha}, $\rread$ is the composite
+\[
+  \rread = \oc\bN \xrightarrow{\mu_\bN} \oc\bN \tensor \oc\bN \xrightarrow{\der_\bN\tensor\oc\bN} \bN \tensor \oc\bN \xrightarrow{\wk_{\bN,\oc\bN}} \bN \sequoid\oc\bN\,.
+  \]
 Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
@@
       \begin{figure}[htbp]
-        \[
+        \begin{mathpar}
           \begin{tikzcd}[column sep=41pt, row sep=30pt]
@@
           \end{tikzcd}
-          \]
+          \and
+          \begin{tikzcd}[row sep=30pt]
+            I \arrow[r, "\oc s(x)"] \arrow[d, "\oc s(x)" description] \arrow[dr]
+              &[-31pt] \oc\bN \arrow[r, "\cell"] \arrow[dr, "\mu_\bN" description] \arrow[ddr, "\cell_0" {description, near end}, bend left=50]
+                &[-100pt] \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[ddd, "\alpha_{\Varr}" description]
+                  &[-21pt] \oc\Varr \tensor \oc\Varr \arrow[d, "\der_{\Varr}\tensor\oc\Varr" description] \\
+            |[alias=Z]| \oc\bN \arrow[d, "\lunit_{\oc\bN}" description] \arrow[dd, "\cell" description]
+              & |[left=40pt of Z.east]| I \tensor I \arrow[dl, "I \tensor \oc s(x)" description] \arrow[r, "\oc s(x) \tensor \oc s(x)"] \arrow[d, "s(x)\tensor \oc s(x)" description]
+                & |[left=50pt of Z.west]| \oc \bN \tensor \oc\bN \arrow[dl, "\der_\bN \tensor \oc\bN" description]
+                  & \Varr \tensor \oc\Varr \arrow[ddl, "{\wk_{\Varr,\oc\Varr}}" {description, pos=0.65}] \arrow[dd, "\pr_{\bN}\tensor\oc\Varr" description] \\
+            |[right=of Z.west]| I \tensor \oc\bN \arrow[r, "s(x)\tensor\oc\bN"'] \arrow[ddr, "I \tensor \cell" description]
+              & \bN \tensor \oc\bN \arrow[d, "{\wk_{\bN,\oc\bN}}" description] \arrow[ddr, "\bN \tensor\cell" {description, pos=0.4, xshift=-5pt}, bend right=30]
+                & |[left=of Z]| \Varr \sequoid \oc\bN \arrow[dl, "\pr_\bN \sequoid \oc\bN" {description, pos=0.65}, bend left=30] \arrow[d, "\Varr\sequoid\cell" {description, xshift=-5pt}, bend left=30]
+                  & \\
+            \oc\Varr \arrow[d, "\mu_{\Varr}" description] \arrow[dr, "\lunit_{\Varr}" description]
+              & |[right=of Z]| \bN \sequoid \oc\bN \arrow[drr, "\bN \sequoid \cell" {description, pos=0.4}, controls={+(0.2,-1.2) and +(-0.3,0.2)}, to=Y.north west, end anchor={[yshift=-2pt]}]
+                & \Varr \sequoid\oc\Varr \arrow[dr, "\pr_\bN \sequoid \oc\Varr" {description, pos=0.35}]
+                  & \bN \tensor \oc\Varr \arrow[d, "{\wk_{\bN},\oc\Varr}" description] \\
+            \oc\Varr \tensor \oc\Varr \arrow[r, "()\tensor\oc\Varr"']
+              & I \tensor \oc\Varr \arrow[r, "s(x)\tensor\oc\Varr"']
+                & \bN \tensor \oc\Varr \arrow[r, "{\wk_{\bN,\oc\Varr}}"']
+                  & |[alias=Y]| \bN \sequoid \oc\Varr
+          \end{tikzcd}
+        \end{mathpar}
       \end{figure}

### 2019-04-02 Thesis/games.tex
Tweaked the big diagrams a bit.

@@
   $\cell_0;(\pr_n\sequoid\oc\bN) = \wwrite_n$ for each $n$ and $\cell_0;(\pr_\bN\sequoid\oc\bN) = \rread$, where $\pr_n\from \Varr=\bC^\bN \times \bN \implies \bC$ is the projection on to the $n$-th copy of $\bC$ and $\pr_\bN\from \Varr = \bC^\bN \times \bN \implies \bN$ is the projection on to the copy of $\bN$.
+  \label{LemCellProjections}
 \end{lemma}
@@
               & \oc \bN \arrow[r, "\cell"] \arrow[d, "()" description] \arrow[dr, "\cell_0" description]
-                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}]
-                  & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" description]  \\
-            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}]
+                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}] \arrow[dr, phantom, "\text{P.
+\ref{PropFormulaForAlpha}}" {xshift=20pt, yshift=-7pt}]
+                  & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" {description, near start}]  \\
+            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}] \arrow[ddrr, phantom, "\text{L.
+\ref{LemCellProjections}}" {xshift=2pt, yshift=20pt}]
               & I \arrow[l, "\oc n" description]
@@
             I \arrow[r, "\oc s(x)"] \arrow[d, "\oc s(x)" description] \arrow[dr]
-              &[-31pt] \oc\bN \arrow[r, "\cell"] \arrow[dr, "\mu_\bN" description] \arrow[ddr, "\cell_0" {description, near end}, bend left=50]
-                &[-100pt] \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[ddd, "\alpha_{\Varr}" description]
-                  &[-21pt] \oc\Varr \tensor \oc\Varr \arrow[d, "\der_{\Varr}\tensor\oc\Varr" description] \\
+              &[-31pt] \oc\bN \arrow[r, "\cell"] \arrow[dr, "\mu_\bN" description] \arrow[ddr, "\cell_0" {description, near end}, bend left=50, end anchor={[xshift=4pt]}] \arrow[ddd, phantom, "\text{L.\ref{LemCellProjections}}" {xshift=3pt,yshift=-7pt}]
+                &[-100pt] \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[ddd, "\alpha_{\Varr}" description] \arrow[dr, phantom, "\text{P.\ref{PropFormulaForAlpha}}", {yshift=-5pt}]
+                  &[-21pt] \oc\Varr \tensor \oc\Varr \arrow[d, "\der_{\Varr}\tensor\oc\Varr" {description, near start}] \\
             |[alias=Z]| \oc\bN \arrow[d, "\lunit_{\oc\bN}" description] \arrow[dd, "\cell" description]
               & |[left=40pt of Z.east]| I \tensor I \arrow[dl, "I \tensor \oc s(x)" description] \arrow[r, "\oc s(x) \tensor \oc s(x)"] \arrow[d, "s(x)\tensor \oc s(x)" description]
-                & |[left=50pt of Z.west]| \oc \bN \tensor \oc\bN \arrow[dl, "\der_\bN \tensor \oc\bN" description]
+                & |[left=50pt of Z.west]| \oc \bN \tensor \oc\bN \arrow[dl, "\der_\bN \tensor \oc\bN" {description, near start}, bend right=10]
                   & \Varr \tensor \oc\Varr \arrow[ddl, "{\wk_{\Varr,\oc\Varr}}" {description, pos=0.65}] \arrow[dd, "\pr_{\bN}\tensor\oc\Varr" description] \\

### 2019-04-02 Thesis/games.tex
Nightly commit (not in a compiling state rn).

@@
 \section{The Strategy $\cell$}
+\label{SecCell}
 
@@
       i.e., the composite that we would get if $\Gamma$ were empty.
-      This tells us that we can assume that $\Gamma$ is the empty context when we want to deal with these two cases.
+      This tells us that we can assume that $\Gamma$ is the empty context, so that the rules take on the form
+      \begin{mathpar}
+        x,s\ts x\gets n \oopto x,(x\mapsto n)\ts \skipp
+        \and
+        x,s \ts \oc x \oopto x,s\ts s(x)\,.
+      \end{mathpar}
       \begin{SidewaysFigure}
@@
             {\oc\Varr \tensor \oc\V_{x,\Gamma}} \arrow[r, Isom, dotted] \arrow[d, "{\deno{x\ts M} \tensor \oc\V_{x,\Gamma}}"' {description, yshift=1pt}, dotted]
-              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt, dotted]}, bend left=5] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
+              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
                 \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma}}" description, dotted]
@@
 
-      Now we have a commutative diagram
+      Now the commutative diagrams in Figure \ref{FigSoundnessOoptoStorage} deal with these last two cases.\qedhere
       \begin{figure}[htbp]
@@
         \end{mathpar}
+        \caption[Diagrams to prove that the conclusion of Lemma \ref{LemSoundnessOopto} holds for the storage cell rules.]{Diagrams to prove that the conclusion of Lemma \ref{LemSoundnessOopto} holds for the storage cell rules.
+        References in the middle of a shape refer to Lemma \ref{LemCellProjections} and Proposition \ref{PropFormulaForAlpha} above.  
+        Note the prominent role played in both diagrams by the anamorphism square for $\cell$ as in Section \ref{SecCell}.}
+        \label{FigSoundnessOoptoStorage}
       \end{figure}
@@
 
+Now that we have dealt with the base rules, we can move on to the full relation $\opto$.
+
+\begin{lemma}
+  The relation $\opto$ between triples $\Gamma,s\ts M$ preserves the composite
+  \[
+    \oc\deno s;\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,.
+    \]
+  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, and $\EE$ is a context of type $U$ with a hole of type $T$, then the following diagram commutes.
+  \[
+    \begin{tikzcd}[column sep=24pt]
+      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
+            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts \EE[M]}\tensor \oc V_\Gamma"] \\
+      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
+        &
+          &
+            & \deno U \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno U,\oc \V_{\Gamma}}}"] \\
+      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
+        &
+          &
+            &  \deno{U}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{U} \sequoid (\Gamma+0_\Delta)}"] \\
+      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts \EE[N]} \tensor \oc \V_{\Gamma,\Delta}}"]
+        &
+          & {\deno U \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno U,\oc \V_{\Gamma,\Delta}}}"]
+            & {{\deno U \sequoid \oc \V_{\Gamma,\Delta}}\,,}
+    \end{tikzcd}
+    \]
+\end{lemma}
+\begin{proof}
+  We use Lemma
+  \[
+    \begin{tikzcd}
+      I \arrow[r, "\deno s"] \arrow[d, "\deno s"']
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "\lunit_{S_\Gamma}" description]
+          & \oc \V_\Gamma \arrow[d, "\lunit_{\oc\V_\Gamma}"'] \\
+      \oc S_\Gamma \arrow[d, "\cell"'] \arrow[dr, "\mu_{S_\Gamma}" description]
+        & I \tensor \oc S_\Gamma \arrow[r, "I\tensor \cell" description] \arrow[d, "\deno s \tensor \oc S_\Gamma" description]
+          & I \tensor \oc\V_\Gamma \arrow[d, "\deno s \tensor \oc\V_\Gamma"] \\
+      \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"'] \arrow[dr, "\mu_{\V_\Gamma}" description]
+        & \oc S_\Gamma \tensor \oc S_\Gamma \arrow[d, "\cell\tensor\cell" description] \arrow[r, "\oc S_\Gamma\tensor \cell" description]
+          & \oc S_\Gamma \tensor \oc\V_\Gamma \arrow[dl, "\cell\tensor\oc \V_\Gamma"] \\
+      \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"']
+        & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"]
+          & \\
+      (\oc\V_\Gamma\tensor\oc\V_\Gamma) \tensor\oc\V_\Gamma \arrow[r, "{\sym^{(23)}_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}}" description] \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma"']
+        & (\oc\V_\Gamma\tensor\oc\V_\Gamma) \tensor\oc\V_\Gamma \arrow[r, "(\deno{\Gamma\ts M}\tensor\sigma)\tensor\oc\V_\Gamma"] \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma" description]
+          & (\deno T\tensor A)\tensor\oc\V_\Gamma \arrow[d, "{\wk_{\deno T,A}\tensor\oc\V_\Gamma}"] \\
+      (\deno T \tensor \oc\V_\Gamma)\tensor\oc\V_\Gamma \arrow[r, "{\sym^{(23)}_{\deno T,\oc\V_\Gamma,\oc\V_\Gamma}}" description] \arrow[d, "{
+\end{proof}
+
 \bibliographystyle{alpha2}

### 2019-04-08 Thesis/games.tex
Heidelberg library.

--- 2019-04-02 Thesis/games.tex
@@
 \begin{mathpar}
-  \inferrule*{\Gamma,x\from \Var \ts M \from T}{\Gamma\ts \neww_T \lambda x.M\from T}
+  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma,x\from \Var \ts M \from T}{\Gamma\ts \neww_T \lambda x.M\from T}
 \end{mathpar}
@@
 \begin{remark}
-  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definitionk \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.
+  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definition \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.
   But such a strategy would not satisfy the conclusion of Proposition \ref{PropWkCommutativeDiagram}, since $\sigma\tensor\tau;\wk_{B,D}$ would contain these extra plays where $\wk_{A,C};\sigma\sequoid\tau$ had `given up'.
@@
   \begin{itemize}
-    \item a monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,\lunit,\runit$);
+    \item a symmetric monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,$ $\lunit$, $\runit$, $\sym$);
     \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
@@
 \begin{figure}
+  \vspace{-27pt}
   \begin{mathpar}
@@
   Suppose that $\Gamma,s\ts M\converges c,s'$.  
-  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
+  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
   \[
@@
 
+\begin{definition}
+  Let $\Gamma,s\ts M\from T$ be a term with store.  
+  Then the \emph{sequoidal denotation} $\seqdeno{\Gamma,s\ts M}$ is the composite
+  \[
+    I \xrightarrow{\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\oc\V_\Gamma} \deno T \tensor\oc\V_\Gamma \xrightarrow{\wk_{\deno T,\oc\V_\Gamma}} \deno T \sequoid \oc\V_\Gamma\,.
+    \]
+\end{definition}
+
 \begin{lemma}
-  The relation $\oopto$ betwen triples $\Gamma,s\ts M$ preserves the composite
-  \[
-    \oc\deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_{\Gamma}}\,.
-    \]
+  The relation $\oopto$ betwen triples $\Gamma,s\ts M$ preserves the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.
+
   In other words, if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, then the following diagram commutes.
@@
           &
-            &  \deno{T}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{T} \sequoid (\Gamma+0_\Delta)}"] \\
+            &  \deno{T}\sequoid \oc\V_\Gamma \\
       {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts N} \tensor \oc \V_{\Gamma,\Delta}}"]
@@
           & {\deno T \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"]
-            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,,}
+            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,.} \arrow[u, "\deno{T}\sequoid\oc\pr_\Gamma"']
     \end{tikzcd}
     \]
-  where $\Gamma+0_\Delta\from \oc \V_\Gamma \to \oc \V_{\Gamma,\Delta}$ is the composite
-  \[
-    \oc \V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc \V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor \oc0} \oc\V_\Gamma \tensor \oc S_\Delta \xrightarrow{\oc\V_\Gamma\tensor \cell^\Delta} \oc \V_\Gamma \tensor \oc \V_\Delta \to \oc \V_{\Gamma,\Delta}\,;
-    \]
-  i.e., the morphism given by initializing new storage cells to $0$ for all the new variables in $\Delta$.
+  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, then $\seqdeno{\Gamma,s\ts M} = \seqdeno{\Gamma,\Delta,s'\ts N};\oc\pr_\Gamma$.
   \label{LemSoundnessOopto}
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\Gamma + 0_x} \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,
-        \]
-      where $\Gamma+0_x$ is as defined in the statement of this Lemma.
-      Of course, $\Lambda\inv(\deno{\Gamma\ts \lambda x.M})=\deno{\Gamma,x\ts M}$.
-
-      Next, we claim that we have a commutative diagram
-      \[
-        \begin{tikzcd}
-          \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "{\oc\langle S_\Gamma,0\rangle}"']
-            & \oc \V_\Gamma \arrow[d, "\Gamma+0_x"] \\
-          {\oc S_{\Gamma,x}} \arrow[r, "{\cell^{\Gamma,x}}"]
-            & {\oc \V_{\Gamma,x}\,.}
+        \oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor (0;\cell)} \oc\V_\Gamma \tensor \oc\Varr \to \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,
+        \]
+      where, of course $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc\V_{\Gamma,x}$ is a right inverse for the composite $\runit_{\oc\V_\Gamma};(\oc\V_{\Gamma}\tensor(0;\cell));\cong$, since we have a commutative diagram
+      \[
+        \begin{tikzcd}[column sep=50pt]
+          \oc\V_\Gamma \arrow[r, "\runit_{\oc\V_\Gamma}"] \arrow[d, Rightarrow, no head]
+            & \oc\V_\Gamma \tensor I \arrow[r, "\oc\V_\Gamma\tensor(0;\cell)"] \arrow[d, "\id_{\oc\V_\Gamma\tensor I}" description]
+              & \oc\V_\Gamma \tensor \oc\Varr \arrow[d] \arrow[dl, "\oc\V_\Gamma\tensor()" description] \\
+          \oc\V_\Gamma
+            & \oc\V_\Gamma \tensor I \arrow[l, "\runit\inv"']
+              & {\oc\V_{\Gamma,x}\,.} \arrow[ll, "\oc\pr_\Gamma", bend left=20]
         \end{tikzcd}
         \]
-      Indeed, we have the diagram
-      \[
-        \begin{tikzcd}[column sep=2pt, row sep=20pt]
-          \oc S_\Gamma \arrow[r] \arrow[dddd, "{\oc\langle S_\Gamma,0\rangle}"' description]
-            &[5pt] \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell\tensor \cdots \tensor \cell"] \arrow[d, "\runit" description]
-              &[10pt] \oc\Varr \tensor \cdots \tensor \oc\Varr \arrow[r] \arrow[d, "\runit" description]
-                & \oc\V_\Gamma \arrow[d, "\runit" description] \\
-          %
-            & \oc \bN \tensor \cdots \tensor \oc\bN \tensor I \arrow[r, "\cell \tensor \cdots \tensor \cell \tensor I" yshift=6pt] \arrow[ddd, "\oc\bN \tensor \cdots \tensor \oc\bN \tensor \oc0" description]
-              & \oc \Varr \tensor \cdots \tensor \oc\Varr\tensor I \arrow[d, "\oc\Varr \tensor \cdots \tensor \oc\Varr \tensor I" description] \arrow[r]
-                & \oc\V_\Gamma \tensor I \arrow[d, "\oc\V_\Gamma\tensor\oc0" description] \\
-          %
-            &
-              & \oc\Varr \tensor \cdots \tensor \oc\Varr\tensor \oc\bN \arrow[r] \arrow[dd, "\oc\Varr\tensor\cdots\tensor\oc\Varr\tensor\cell" description]
-                & \oc\V_\Gamma \tensor \oc\bN \arrow[d, "\oc\V_\Gamma\tensor\cell" description] \\
-          %
-            &
-              &
-                & \oc\V_\Gamma\tensor\oc\Varr \arrow[d] \\
-          {\oc S_{\Gamma,x}} \arrow[r]
-            & \oc\bN \tensor\cdots \tensor\oc\bN \tensor\oc\bN \arrow[uur, "\cell\tensor\cdots\tensor\cell\tensor\oc\bN" {description, near start}] \arrow[r, "\cell\tensor\cdots\tensor\cell\tensor\cell"' yshift=-3pt]
-              & \oc\Varr \tensor \cdots\tensor\oc\Varr \tensor \oc\Varr \arrow[ur] \arrow[r]
-                & {\oc\V_{\Gamma,x}\,.}
+      Then we may prove this case using the commutative diagram in Figure \ref{FigSoundnessOoptoNew}.
+      \begin{figure}[htbp]
+        \[
+          \begin{tikzcd}[column sep=34pt, row sep=30pt]
+            I \arrow[r, "\oc\deno s"] \arrow[d, "{\oc\langle\deno s,0\rangle}" description]
+              &[5pt] \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+                &[-5pt] \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"] \arrow[d, "\mu_{\V_\Gamma}" description]
+                  & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\runit_{\oc\V_\Gamma};(\oc\V_\Gamma\tensor (0;\cell));\cong" {description, xshift=-16pt}] \\
+            {\oc S_{\Gamma,x}} \arrow[ur, "\oc\pr_\Gamma" description] \arrow[d, "{\cell^{\Gamma,x}}" description]
+              &
+                & \oc\V_\Gamma\tensor\oc\V_\Gamma
+                  & {\oc\V_{\Gamma,x}\tensor\oc\V_\Gamma} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\V_\Gamma}" description] \arrow[l, "\pr_\Gamma\tensor\oc\V_\Gamma"'] \\
+            {\oc\V_{\Gamma,x}} \arrow[uurr, "\oc\pr_\Gamma" description] \arrow[d, "{\mu_{\V_{\Gamma,x}}}"]
+              &
+                &
+                  & \deno T \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}" description] \\
+            {\oc\V_{\Gamma,x}\tensor\oc\V_{\Gamma,x}} \arrow[uurr, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma" {description, pos=0.7}] \arrow[uurrr, "{\V_{\Gamma,x}\tensor\pr_\Gamma}" {description, pos=0.7}] \arrow[r, "{\deno{\Gamma,x\ts M}\tensor\oc\V_{\Gamma,x}}"' yshift=-3pt]
+              & {\deno T \tensor \oc\V_{\Gamma,x}} \arrow[r, "{\wk_{\deno T,\oc\V_{\Gamma,x}}}"' yshift=-3pt]
+                & {\deno T \sequoid \oc\V_{\Gamma,x}} \arrow[r, "\deno T \sequoid\pr_\Gamma"' yshift=-3pt]
+                  & \deno T \sequoid\oc\V_\Gamma
           \end{tikzcd}
           \]
-      Now the diagram in Figure \ref{FigSoundnessOoptoNew} shows us that the conclusion of the lemma is satisfied for this rule.
-      \begin{SidewaysFigure}
-        \[
-          \begin{tikzcd}[ampersand replacement=\&, column sep=50pt, row sep=40pt]
-            I \arrow[r, "\oc\deno s"] \arrow[d, "\oc(\deno s\times 0)"']
-              \& \oc S_\Gamma \arrow[dl, "{\oc\langle S_\Gamma,0\rangle}" description] \arrow[dr, "\mu_{S_\Gamma}" description] \arrow[r, "\cell^\Gamma" description]
-                \& \oc \V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}"]
-                  \&
-                    \& \oc \V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "(\Gamma + 0_x)\tensor\oc\V_\Gamma"] \arrow[ddddllll, "(\Gamma+0_x)\tensor(\Gamma+0_x)" description, bend left=12] \\
-            {\oc S_{\Gamma,x}} \arrow[dr, "\mu_{S_\Gamma}" description] \arrow[d, "{\cell^{\Gamma,x}}"']
-              \&
-                \& \oc S_\Gamma \tensor \oc S_\Gamma \arrow[urr, "\cell^{\Gamma} \tensor \cell^{\Gamma}" {description, near start}, bend left=10] \arrow[dl, "{\oc\langle S_\Gamma,0\rangle\tensor\oc\langle S_\Gamma,0\rangle}" description]
-                  \& 
-                    \& {\oc\V_{\Gamma,x}\tensor\oc\V_\Gamma} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\V_\Gamma}"] \\
-            {\oc\V_{\Gamma,x}} \arrow[dd, "{\mu_{\V_{\Gamma,x}}}"']
-              \& {\oc S_{\Gamma,x}\tensor\oc S_{\Gamma,x}} \arrow[ddl, "{\cell^{\Gamma,x}\tensor\cell^{\Gamma,x}}"' {description, near start}, bend right=10]
-                \&
-                  \&
-                    \& \deno T \tensor \oc\V_{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \arrow[ddll, "\deno T \tensor (\Gamma + 0_x)" description, bend left=8] \\
-            %
-              \&
-                \&
-                  \&
-                    \& \deno T \sequoid \oc\V_\Gamma\arrow[d, "{\deno T \sequoid (\Gamma + 0)}"] \\
-            {\oc \V_{\Gamma,x} \tensor \oc \V_{\Gamma,x}} \arrow[rr, "{\deno{\Gamma,x\ts M}\tensor \oc\V_{\Gamma,x}}"]
-              \&
-                \& {\deno T \tensor \oc\V_{\Gamma,x}} \arrow[rr, "{\wk_{\deno T,\oc\V_{\Gamma,x}}}"]
-                  \&
-                    \& {\deno T\sequoid\oc\V_{\Gamma,x}}
-          \end{tikzcd}
-          \]
-        \caption{The reduction $\Gamma,s\ts\neww\lambda x.M\oopto\Gamma,x,(s\vert x\mapsto 0)\ts M$ satisfies the conclusion of Lemma \ref{LemSoundnessOopto}.}
+        \caption{The conclusion of Lemma \ref{LemSoundnessOopto} holds for the $\neww$ rule.}
         \label{FigSoundnessOoptoNew}
-      \end{SidewaysFigure}
+      \end{figure}
     \item Now consider the rules
@@
         \]
-      Now the diagram in Figure \ref{FigSoundnessOoptoContext} tells us that each
-      \[
-        \oc\deno{s};\cell^{x,\Gamma};\mu_{\V_{x,\Gamma}};(\deno{x,\Gamma\ts M}\tensor\oc\V_{x,\Gamma});\wk_{\deno T,\oc\V_{x,\Gamma}}\,\text{--}
-        \]
-      i.e., the composites we are trying to show are preserved by the $\oopto$ relation -- may be written as
+      Now the diagram in Figure \ref{FigSoundnessOoptoContext} tells us that each $\seqdeno{\Gamma,x,s\ts M}$ may be written as the composite
       \begin{mathpar}
@@
       (where $\cong$ represents the natural isomorpism between $\deno T\sequoid(\oc\Varr\tensor\oc\V_\Gamma)$ and $\deno T \sequoid\oc\V_{x,\Gamma}$),
-      and so is determined by the composite
+      and so is completely determined by the value of the composite
       \[
@@
         \]
-      i.e., the composite that we would get if $\Gamma$ were empty.
-      This tells us that we can assume that $\Gamma$ is the empty context when we want to deal with these two cases.
+      i.e., the sequoidal denotation $\seqdeno{x,s\vert_x\ts M}$.
+
+      This tells us that we can assume that $\Gamma$ is the empty context, so that the rules take on the form
+      \begin{mathpar}
+        x,s\ts x\gets n \oopto x,(x\mapsto n)\ts \skipp
+        \and
+        x,s \ts \oc x \oopto x,s\ts s(x)\,.
+      \end{mathpar}
       \begin{SidewaysFigure}
@@
             {\oc\Varr \tensor \oc\V_{x,\Gamma}} \arrow[r, Isom, dotted] \arrow[d, "{\deno{x\ts M} \tensor \oc\V_{x,\Gamma}}"' {description, yshift=1pt}, dotted]
-              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt, dotted]}, bend left=5] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
-                \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma}}" description, dotted]
+              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
+                \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma)}}" description, dotted]
                   \& (\deno T \tensor \oc\Varr) \tensor \oc\V_\Gamma\arrow[d, "{\wk_{\deno T,\oc\Varr}\tensor\oc\V_\Gamma}" {description, yshift=1pt}, thick] \\
@@
 
-      Now we have a commutative diagram
+      Now the commutative diagrams in Figure \ref{FigSoundnessOoptoStorage} prove that
+      \[
+        \seqdeno{x,s\vert_x\ts x\gets n} = \seqdeno{x,(x\mapsto n)\ts \skipp}
+        \]
+      and that
+      \[
+        \seqdeno{x,s\vert_x\ts \oc x} = \seqdeno{x,s\vert_x\ts s(x)}\,,
+        \]
+      completing the proof.\qedhere
       \begin{figure}[htbp]
@@
 
+Now that we have dealt with the base rules, we can move on to the full relation $\opto$.
+
+\begin{lemma}
+  The relation $\opto$ between triples $\Gamma,s\ts M$ preserves the composite
+  \[
+    \oc\deno s;\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,.
+    \]
+  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, and $\EE$ is a context of type $U$ with a hole of type $T$, then the following diagram commutes.
+  \[
+    \begin{tikzcd}[column sep=24pt]
+      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno {s'}"']
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
+            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts \EE[M]}\tensor \oc V_\Gamma"] \\
+      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
+        &
+          &
+            & \deno U \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno U,\oc \V_{\Gamma}}}"] \\
+      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
+        &
+          &
+            &  \deno{U}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{U} \sequoid (\Gamma+0_\Delta)}"] \\
+      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts \EE[N]} \tensor \oc \V_{\Gamma,\Delta}}"]
+        &
+          & {\deno U \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno U,\oc \V_{\Gamma,\Delta}}}"]
+            & {{\deno U \sequoid \oc \V_{\Gamma,\Delta}}\,,}
+    \end{tikzcd}
+    \]
+  \label{LemSoundnessOpto}
+\end{lemma}
+\begin{proof}
+  We use Lemma \ref{LemEvContexLemma} to reduce this to Lemma \ref{LemSoundnessOpto}.  
+  Indeed, Lemma \ref{LemEvContexLemma} tells us that for any $\Gamma,s\ts M$, $\deno{\Gamma\ts \EE[M]}$ may be written as
+  \[
+    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno T \tensor A \xrightarrow{\wk_{\deno T,A}} \deno T \sequoid A \xrightarrow{\tau} \deno U
+    \]
+  for suitably chosen $A,\sigma,\tau$.
+
+  Let us write $\seqdeno{\Gamma,s\ts M}$ for the composite
+  \[
+    \oc\deno s;\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma};(\deno T \sequoid (\Gamma+0_\Delta))\,.
+    \]
+  So we are trying to show that $\seqdeno{\Gamma,s\ts \EE[M]}=\seqdeno{\Gamma,\Delta,s'\ts \EE[N]};(\deno U \sequoid \oc\pr_\Gamma)$.
+
+  Now the diagram in Figure \ref{FigSoundnessOpto} shows us that for any $\Gamma,s\ts M$ we may write
+  \[
+    \seqdeno{\Gamma,s\ts \EE[M]} = \seqdeno{\Gamma,s\ts M};(\deno T \sequoid (\mu_{\V_\Gamma};(\sigma\tensor\oc\V_\Gamma));\passoc_{\deno T,A,\oc\V_\Gamma}\inv;(\tau\sequoid\oc\V_\Gamma)\,.
+    \]
+
+  \begin{SidewaysFigure}
+    \[
+      \begin{tikzcd}[column sep=45pt, row sep=30pt, ampersand replacement=\&]
+        \oc S_\Gamma \arrow[d, "\cell^\Gamma"', thick]
+          \& I \arrow[l, "\oc\deno s"', thick]
+            \&
+              \& \\
+        \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}", thick] \arrow[d, "\mu_{\V_\Gamma}"', thick, dashed]
+          \& \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[r, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma", thick] \arrow[dd, "\oc\V_\Gamma\tensor\mu_{\V_\Gamma}" description, dotted]
+            \& \deno T \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno T,\oc\V_\Gamma}}", thick] \arrow[dd, "\deno T \tensor \mu_{\V_\Gamma}" description, dotted]
+              \& \deno T \sequoid \oc\V_\Gamma \arrow[dd, "\deno T \sequoid \mu_{\V_\Gamma}"] \\
+        \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"', thick, dashed]
+          \&
+            \&
+              \& \\
+        (\oc\V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma \arrow[r, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}}" yshift=3pt, dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor \sigma) \tensor\oc\V_\Gamma"', thick, dashed]
+          \& \oc\V_\Gamma \tensor (\oc\V_\Gamma \tensor \oc\V_\Gamma) \arrow[r, "\deno{\Gamma\ts M} \tensor (\oc\V_\Gamma\tensor \oc\V_\Gamma)" yshift=3pt, dotted] \arrow[d, "\deno{\Gamma\ts M}\tensor (\sigma\tensor\oc\V_\Gamma)" description, dotted]
+            \& \deno T \tensor (\oc\V_\Gamma\ \tensor \oc\V_\Gamma) \arrow[r, "{\wk_{\deno T,\oc\V_\Gamma\tensor\oc\V_\Gamma}}" yshift=3pt, dotted] \arrow[dl, "\deno T \tensor (\sigma \tensor\oc\V_\Gamma)" description, dotted]
+              \& \deno T \sequoid (\oc\V_\Gamma \tensor \oc\V_\Gamma) \arrow[d, "\deno T \sequoid (\sigma \tensor \oc\V_\Gamma)"] \\
+        (\deno T \tensor A) \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,A}\tensor\oc\V_\Gamma}"', thick, dashed] \arrow[r, "{\assoc_{\deno T,A,\oc\V_\Gamma}}", dotted]
+          \& \deno T \tensor (A \tensor \oc\V_\Gamma) \arrow[rr, "{\wk_{\deno T,A\tensor\oc\V_\Gamma}}", dotted]
+            \&
+              \& \deno T \sequoid (A \tensor \oc\V_\Gamma) \\
+        (\deno T \sequoid A) \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno T\sequoid A,\oc\V_\Gamma}}", dotted] \arrow[d, "\tau\tensor\oc\V_\Gamma", thick, dashed]
+          \& (\deno T \sequoid A) \sequoid \oc\V_\Gamma \arrow[d, "\tau\sequoid\oc\V_\Gamma"] \arrow[urr, "{\passoc_{\deno T,A,\oc\V_\Gamma}}"']
+            \&
+              \& \\
+        \deno U \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno U,\oc\V_\Gamma}}", thick, dashed]
+          \& \deno U \sequoid \oc\V_\Gamma
+            \&
+              \&
+      \end{tikzcd}
+      \]
+      \caption{Diagram proving that the conclusion of Lemma \ref{LemSoundnessOopto} can be lifted to the $\opto$ relation.}
+      \label{FigSoundnessOpto}
+  \end{SidewaysFigure}
+
+  Therefore, Lemma \ref{LemSoundnessOopto} tells us that if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, then we have
+  \begin{IEEEeqnarray*}{Cl}
+    & \seqdeno{\Gamma,s\ts \EE[M]} \\
+    = & \seqdeno{\Gamma,s\ts M};(\deno T\sequoid(\mu_{\V_\Gamma};(\sigma\tensor\oc\V_\Gamma));\passoc\inv;(\tau\sequoid\oc\V_\Gamma) \\
+    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid \oc\pr_\Gamma);(\deno T\sequoid(\mu_{\V_\Gamma};(\sigma\tensor\oc\V_\Gamma));\passoc\inv;(\tau\sequoid\oc\V_\Gamma) \\
+    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid (\mu_{\V_{\Gamma,\Delta}};((\pr_\Gamma;\sigma)\tensor\oc\V_{\Gamma,\Delta})));\passoc\inv; \\
+    &\qquad(\tau\sequoid\oc\V_\Gamma);(\deno U\sequoid\oc\pr_\Gamma) \\
+    = & \seqdeno{\Gamma,s\ts \EE[N]};(\deno U\sequoid\oc\pr_\Gamma)\,,
+  \end{IEEEeqnarray*}
+  as desired.
+\end{proof}
+
+It is now a simple induction to show that we can extend this to the $\converges$ relation.
+
+\begin{lemma}
+  Suppose that $\Gamma,s\ts M \converges c,s'$, where $M,c\from T$.
+  Then the following diagram commutes.
+  \[
+    \begin{tikzcd}[column sep=40pt]
+      I \arrow[r, "\oc\deno s"] \arrow[d, "\oc\deno{s'}"']
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+          & \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
+            & \oc\V_\Gamma\tensor\oc\V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma"] \\
+      \oc S_\Gamma \arrow[d, "\cell^\Gamma"']
+        &
+          &
+             & \deno{T} \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \\
+      \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
+        & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[r, "\deno{\Gamma\ts c}\tensor\oc\V_\Gamma"]
+          & \deno T \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno T,\oc\V_\Gamma}}"]
+            & \deno T \sequoid \oc\V_\Gamma
+    \end{tikzcd}
+    \]
+  \label{LemSoundness}
+\end{lemma}
+\begin{proof}
+  By Proposition \ref{PropBigToSmall}, there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
+  \[
+    \Gamma_1,s^{(1)}\ts M_1 \opto \cdots \opto \Gamma_n,s^{(n)} \ts M_n\,,
+    \]
+  and $s^{(n)}\vert_\Gamma = s'$.
+
+  By inductively applying Lemma \ref{LemSoundnessOpto}, we see that we have a commutative diagram
+  \[
+    \begin{tikzcd}[column sep=28pt]
+      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno {s^{(n)}}"']
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
+            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
+      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
+        &
+          &
+            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma}}}"] \\
+      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
+        &
+          &
+            &  \deno{T}\sequoid \oc\V_\Gamma \\
+      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts c} \tensor \oc \V_{\Gamma,\Delta}}"]
+        &
+          & {\deno T \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"]
+            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,,} \arrow[u, "\deno T \sequoid \oc\pr_\Gamma"]
+    \end{tikzcd}
+    \]
+  Now, since $s^{(n)}\vert_\Gamma = s'$, we have a commutative diagram
+  \[
+    \begin{tikzcd}[column sep=50pt]
+      I \arrow[r, "\deno {s'}"] \arrow[d, "\deno{s^{(n)}}"']
+        & \oc S_\Gamma \arrow[dd, "\cell^\Gamma"] \\
+      {\oc S_{\Gamma,\Delta}} \arrow[ur, "\oc\pr_\Gamma" description] \arrow[d, "{\cell^{\Gamma,\Delta}}"']
+        & \\
+      {\oc\V_{\Gamma,\Delta}} \arrow[r, "\oc\pr_\Gamma"] \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
+        & \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"] \\
+      {\oc\V_{\Gamma,\Delta}\tensor\oc\V_{\Gamma,\Delta}} \arrow[d, "{\deno{\Gamma,\Delta\ts c}\tensor\oc\V_{\Gamma,\Delta}}"'] \arrow[r, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma"]
+        & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\deno{\Gamma\ts c}\tensor\oc\V_\Gamma"]  \\
+      {\deno T \tensor \oc\V_{\Gamma,\Delta}} \arrow[r, "\deno T \tensor \oc\pr_\Gamma"] \arrow[d, "{\wk_{\deno T,\oc\V_{\Gamma,\Delta}}}"']
+        & \deno T \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \\
+      {\deno T \sequoid \oc\V_{\Gamma,\Delta}} \arrow[r, "\deno T \sequoid \oc\pr_\Gamma"]
+        & \deno T \sequoid \oc\V_\Gamma \\
+    \end{tikzcd}
+    \]
+  which, together with the diagram above, gives us the commutative diagram in the statement.
+\end{proof}
+
+It is then an easy corollary to show the sense in which our semantics is sound.
+
+\begin{proposition}[\cite{SamsonGuyIAActive}]
+  Suppose that $\Gamma,s\ts M\converges c,s'$.  
+  Then
+  \[
+    \deno s;\cell^\Gamma;\deno{\Gamma\ts M} = \deno{s'};\cell^\Gamma;\deno{\Gamma\ts c}\,.
+    \]
+\end{proposition}
+\begin{proof}
+  Lemma \ref{LemSoundness}, plus the fact that if $\Gamma,s\ts P\from T$, then we have a commutative diagram
+  \[
+    \begin{tikzcd}[column sep=14.5pt]
+      I \arrow[r, "\deno{s}", thick]
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma", thick]
+          & \oc\V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\V_\Gamma}" description, dotted]
+            &
+              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[rr, "\deno{\Gamma\ts P}\tensor\oc\V_\Gamma", thick, dashed] \arrow[d, "\oc\V_\Gamma\tensor()" description, dotted]
+                &
+                  & \deno T \tensor\oc\V_\Gamma \arrow[ddd, "{\wk_{\deno T,\oc\V_\Gamma}}" description, thick, dashed] \arrow[ddl, "\deno T \tensor ()" description, dotted] \\
+      %
+        &
+          &
+            &
+              & \oc\V_\Gamma \tensor I \arrow[dr, "\deno{\Gamma\ts P}\tensor I" description, dotted] \arrow[dl, "{\wk_{\oc\V_\Gamma,I}}" description, dotted]
+                &
+                  & \\
+      %
+        &
+          &
+            & \oc\V_\Gamma \sequoid I \arrow[dr, "\deno{\Gamma\ts P}\sequoid I" description, dotted] \arrow[uul, "\run_{\oc\V_\Gamma}" description, dotted]
+              &
+                & \deno T \tensor I \arrow[dl, "{\wk_{\deno T,I}}" description, dotted]
+                  & \\
+      %
+        &
+          & \deno T
+            &
+              & \deno T \sequoid I \arrow[ll, "{\run_{\deno T}}"']
+                &
+                  & \deno T \sequoid \oc\V_\Gamma \arrow[ll, "\deno T \sequoid()"']\,,
+    \end{tikzcd}
+    \]
+  allowing us to recover $\deno{s};\cell^\Gamma;\deno{\Gamma\ts P}$ from 
+  \[
+    \seqdeno{\Gamma,s\ts P} = \deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts P}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,,
+    \]
+  for $P=M,c$.
+\end{proof}
+
+\section{Computational Adequacy}
+
+Our proof of computational adequacy is based on that from \cite{SamsonGuyIAActive}, but modified to make use of the coalgebraic definition of the $\cell$ strategy.  
+As is usual in proofs of computational adequacy, our proof relies on logical relations.
+
+First, we note some additional order-theoretic properties of our model.  
+For any game $A$, we have a strategy $\bot_A\from A$, given by $\bot_A=\{\epsilon\}$; i.e., the strategy that has no reply even for the very first move.  
+It is clear that $\bot$ is the bottom element of the set of strategies for $A$, ordered by inclusion.
+
+It is then easy to see the following.
+\begin{proposition}
+  \begin{itemize}
+    \item Given $\sigma\from A \implies B$, $\sigma;\bot_{B\implies C}=\bot_{A\implies C}$.
+    \item Given a strict strategy $\tau\from B\implies C$, $\bot_{A\implies B};\tau=\bot_{A\implies C}$.
+    \item Given a zigzag (copycat) strategy $\zz_\phi\from B \implies C$ and a strategy $\sigma\from A\implies B$, if $\sigma;\zz_\phi=\bot_{A\implies C}$ then $\sigma=\bot_{A\implies B}$.
+  \end{itemize}
+\end{proposition}
+
+\begin{definition}
+  Given a $\Var$-store $\Gamma$, a strategy $\sigma\from\oc\V_\Gamma \implies A$ and a $\Gamma$-store $s$, we write
+  \[
+    \seqdeno{s,\sigma}
+    \]
+  for the composite
+  \[
+    I \xrightarrow{\oc\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\oc\V_\Gamma} A \tensor \oc\V_\Gamma \xrightarrow{\wk_{A,\oc\V_\Gamma}} A \sequoid \oc\V_\Gamma\,.
+    \]
+  In particular, if $\Gamma\ts M\from T$ is a term in context, then $\seqdeno{s,\deno{\Gamma\ts M}}$ is equal to the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.
+\end{definition}
+
+\begin{definition}
+  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies for $\oc\V_\Gamma \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
+  \begin{itemize}
+    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\V_\Gamma\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,\sigma}=\seqdeno{s',u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
+
+    \item If $\sigma\from \oc\V_\Gamma \implies \Varr$ and $\Gamma\ts M\from \Var$, we say that $\sigma\plot_{\Var}^\Gamma M$ if
+      \[
+        \sigma;\pr_n\plot_{\com}^\Gamma M\gets n
+        \]
+      for all $n$, and if
+      \[
+        \sigma;\pr_{\bN}\plot_{\nat}^\Gamma \oc M\,.
+        \]
+
+    \item If $\sigma \from \oc\V_\Gamma \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\V_\Gamma \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
+      \[
+        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
+        \]
+      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, then
+      \small
+      \[
+        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor \cell} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right) \plot_X^\Gamma \neww_X (\lambda x.M\,x)\,.
+        \]
+      \normalsize
+  \end{itemize}
+\end{definition}
+
+\begin{lemma}
+  Let $\Gamma\ts M,N\from T$ be terms in context of Idealized Algol such that
+  \[
+    \Gamma,s\ts M\opto \Gamma,s\ts N
+    \]
+  for all $\Gamma$-stores $s$.  
+  Suppose $\sigma\from\oc\V_\Gamma\implies\deno T$ is a strategy such that $\sigma\plot_T^\Gamma N$.  
+  Then $\sigma\plot_T^\Gamma M$.
+\end{lemma}
+\begin{proof}
+  Induction on $T$.
+
+  Suppose that $\Gamma,s\ts M,N\ts X$, where $X$ is some datatype, and that $\Gamma,s\ts M\opto \Gamma,s\ts N$ for all $\Gamma$-stores $s$.  
+  Fix some $\Gamma$-store $s$ and some strategy $\sigma\from \oc\V_\Gamma\implies \deno T$, and suppose that $\sigma\plot_T^\Gamma N$.
+
+  If $\seqdeno{s,\sigma}\ne\bot_{\oc\V_\Gamma\implies X}$, then by hypothesis it is equal to $\seqdeno{s',u}$ for some $u$ such that $\Gamma,s\ts N\converges u,s'$.  
+  Then, by Lemma \ref{LemSmallToBig}, $\Gamma,s\ts M\converges u,s'$.
+
+  If $\Gamma,s\ts M,N\from \Var$ and $\sigma\plot_\Var^\Gamma N$, then we have $\sigma;\pr_n\plot_\com^\Gamma N\gets n$ for each $n$ and $\sigma;\pr_\bN\plot_\nat^\Gamma \oc N$.  
+  If $\Gamma,s\ts M\opto \Gamma,s\ts N$, then $\Gamma,s\ts M\gets n\opto\Gamma,s\ts N\gets n$ for each $n$ and $\Gamma,s\ts \oc M\opto\Gamma,s\ts \oc N$.  
+  Then, by the previous paragraph, we must have $\sigma;\pr_n\plot_{\com}^\Gamma M\gets n$ for each $n$ and $\sigma;\pr_\bN\plot_{\nat}^\Gamma \oc M$, and therefore $\sigma\plot_{\Var}^\Gamma M$.
+
+  Lastly, suppose that 
+\end{proof}
+
+\begin{lemma}
+  Let $\Gamma$ be a $\Var$-context, let $\Delta$ be an arbitrary context and let $T$ be an Idealized Algol type.
+  Write $\Delta=x_1\from T_1,\cdots,x_n\from T_n$.  
+  Suppose that $\sigma_i\from \oc\V_\Gamma \implies \deno{T_i}$ are strategies and $\Gamma\ts N_i\from T_i$ are terms-in-context such that $\sigma_i\plot_{T_i}^\Gamma N_i$ for each $i$.
+
+  Given a strategy $\sigma\from \oc\V_{\Gamma,\Delta}\implies \deno{T}$, we write
+  \[
+    (\sigma_i)\semicom \sigma
+    \]
+  for the composite
+  \[
+    \oc\V_\Gamma \xrightarrow{\langle \oc\V_\Gamma,\sigma_1^\dag,\cdots,\sigma_n^\dag\rangle} \oc\V_{\Gamma,\Delta} \xrightarrow{\sigma} \deno{T}\,.
+    \]
+
+  Then for any term-in-context $\Gamma,\Delta \ts M\from T$, we have
+  \[
+    (\sigma_i)\semicom\deno{\Gamma\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
+    \]
+\end{lemma}
+
 \bibliographystyle{alpha2}

### 2019-04-11 Thesis/games.tex
old.

@@
 \begin{mathpar}
+  \inferrule*{\Gamma\ts V \from \Var \\ \Gamma \ts E \from \nat}{\Gamma \ts V\gets E \from \com}
+  \and
   \inferrule*{\Gamma\ts V \from \Var}{\Gamma \ts \oc V \from \nat}
-  \and
-  \inferrule*{\Gamma\ts V \from \Var \\ \Gamma \ts E \from \nat}{\Gamma \ts V\gets E \from \com}
 \end{mathpar}
@@
     \]
+  \label{PropSoundness}
 \end{proposition}
@@
     \item Given a strict strategy $\tau\from B\implies C$, $\bot_{A\implies B};\tau=\bot_{A\implies C}$.
+    \item $\bot_{A\implies B}$ is a strict strategy and $\bot_{A\implies B}\sequoid\sigma=\bot_{(A\sequoid C)\implies (B\sequoid D)}$ for any $\sigma\from C\implies D$.
+    \item $\Lambda(\bot_{A\tensor B\implies C})=\bot_{A\implies(B\implies C)}$.
     \item Given a zigzag (copycat) strategy $\zz_\phi\from B \implies C$ and a strategy $\sigma\from A\implies B$, if $\sigma;\zz_\phi=\bot_{A\implies C}$ then $\sigma=\bot_{A\implies B}$.
@@
   \begin{itemize}
-    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\V_\Gamma\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,\sigma}=\seqdeno{s',u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
+    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\V_\Gamma\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
 
@@
         \]
-      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, then
-      \small
-      \[
-        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor \cell} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right) \plot_X^\Gamma \neww_X (\lambda x.M\,x)\,.
-        \]
-      \normalsize
+      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, where $M=\lambda x.M'$, then
+      \begin{align*}
+        \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
+        \plot_X^\Gamma \neww_X M\,.
+      \end{align*}
   \end{itemize}
@@
   Then $\sigma\plot_T^\Gamma M$.
+  \label{LemAdequacyOpto}
 \end{lemma}
@@
 
-  Lastly, suppose that 
+  Lastly, suppose that $\Gamma,s\ts M,N\from S \to T$ and suppose that $\Gamma,s\ts M \opto \Gamma,s\ts N$.
+  Let $\sigma\from \oc\V_\Gamma \implies (\oc\deno S \implies \deno T)$ be a strategy and suppose that $\sigma \plot_{S\to T} N$.  
+  We claim that $\sigma \plot_{S\to T} M$.  
+  Indeed, let $\tau\from\oc\V_\Gamma\implies\deno S$ be a strategy and let $\Gamma \ts P\from S$ be a term in context such that $\tau\plot_S^\Gamma P$.  
+  Then, since $\sigma\plot_{S\to T} N$, we must have that $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev \plot_T^\Gamma N\,P$.  
+  Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.
+
+  In the case that $S=\Var$ and $T=X$ is a datatype, we also need to show that $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev\plot_X^\Gamma\neww_X(\lambda x.M\,x)$.  
+  Writing $\sigma'$ for the composite $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev$, we know already that $\sigma'\plot_X^\Gamma \neww_X(\lambda x.N\,x)$.
+  Let $s$ be a $\Gamma$-store.  
+  Then we know that if $\seqdeno{s,\sigma'}\ne\bot_{\oc\V_\Gamma\implies X}$, then $\seqdeno{s,\sigma'}=\seqdeno{s',u}$ for some $s'$, $u$ such that $\Gamma,\neww_X \lambda x.N\,x\converges u,s'$.
+  It follows that $\Gamma,x,(s\vert x\mapsto 0)\ts N\,x\converges u,s'$; then, since $\Gamma,x,(s\vert x\mapsto 0)\ts M\,x\opto \Gamma,x(s\vert_x\mapsto 0)\ts N\,x$, we have $\Gamma,x\ts M\,x\converges u,s'$ by Lemma \ref{LemSoundnessOpto}.
+  Therefore, $\Gamma,s\ts \neww_X \lambda x.M\,x \ts u,s'$.  
+  Since $s$ was arbitrary, it follows that $\sigma'\plot_X^\Gamma \new_X(\lambda x.M\,x)$.
+\end{proof}
+
+\begin{lemma}
+  Let $T$ be a type of Idealized Algol, and let $\Gamma$ be a $\Var$-context.  
+  Then $\bot_{\oc\V_\Gamma\implies \deno T}\plot_T^\Gamma M$ for any term-in-context $\Gamma\ts M\from T$.
+  \label{LemAdequacyBot}
+\end{lemma}
+\begin{proof}
+  Induction on $T$.  
+  If $T$ is a datatype and $s$ a store, then for any $\sigma\from \oc\V_\Gamma\implies \deno T$ we have
+  \[
+    \oc\deno s;\cell^\Gamma;\sigma = \seqdeno{s,\sigma};(\deno T\sequoid ());\run_{\deno T}\,,
+    \]
+  as in the proof of Proposition \ref{PropSoundness}; since $(\deno T\sequoid());\run_{\deno T}$ is a zigzag strategy, if $\sigma=\bot_{\oc\V_\Gamma\implies\deno T}$, then $\oc\deno s;\cell^\Gamma;\sigma=\bot_{\deno T}$, and therefore $\seqdeno{s,\sigma}=\bot_{T\sequoid\oc\V_\Gamma}$.
+
+  Suppose $\Gamma\ts M\from\Var$.  
+  Since the projections are strict strategies, we have $\bot_{\oc\V_\Gamma\implies\Varr};\pr_n=\bot_{\oc\V_\Gamma\implies\bC}\plot_{\Var}^\Gamma M$ and $\bot_{\oc\V_\Gamma\implies\Varr};\pr_{\bC}=\bot_{\oc\V_\Gamma\implies\bN}\plot_{\bN}^\Gamma M$, and therefore $\bot_{\oc\V_\Gamma\implies\Varr}\plot_{\Var}^\Gamma M$.
+
+  Suppose that $\Gamma\ts M\from S\to T$.  
+  Fix some $N\from S$ and $\tau\from \oc\V_\Gamma\implies \deno S$ such that $\tau\plot_S^\Gamma N$.
+
+  We are required to show that
+  \[
+    \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\bot\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
+    \]
+  which, by induction, we can do by showing that it is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
+  Indeed, we may write this composite as
+  \[
+    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\oc\V_\Gamma \tensor \tau^\dag} \oc\V_\Gamma\tensor\oc\deno S \xrightarrow{\Lambda\inv(\bot_{\oc\V_\Gamma \implies (\oc\deno S \implies \deno T))}} \deno T\,,
+    \]
+  which is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
+
+  Lastly, in the special case that $S=\Var$ and $T=X$ is a datatype, we need to show that
+  \begin{align*}
+    \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
+    \plot_X^\Gamma \neww_X M\,.
+  \end{align*}
+  Indeed, this composite is equal to $\bot_{\oc\V_\Gamma\implies X}$ by an identical argument.
+\end{proof}
+
+\begin{lemma}
+  Let $T$ be an idealized Algol type, and let $\Gamma\ts M\from T$ be a typing judgement, where $\Gamma$ is a $\Var$-context.
+  Suppose that $\sigma_1\subset\sigma_2\subset\cdots$ is a nested sequence of strategies for $\oc\V_\Gamma$ such that $\sigma_i\plot_T^\Gamma M$ for all $i$.  
+  Let $\sigma=\bigcup_i \sigma_i$.  
+  Then $\sigma\plot_T^\Gamma M$.
+  \label{LemAdequacyLimits}
+\end{lemma}
+\begin{proof}
+  If $X$ is a datatype, $\Gamma$ is a $\Var$-context, $s$ is a $\Gamma$-store and $\Gamma\ts M\from X$ is a typing judgement, then if $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\V_\Gamma}$ for all $i$, then we must have $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\V_\Gamma} = \bot_{X\sequoid\oc\V_\Gamma}$ by continuity of composition.
+  Otherwise, $\seqdeno{s,\sigma_i}=\seqdeno{\Gamma,s'\ts u}$ for some $i$, some $\Gamma$-store $s'$ and some $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
+  In that case, since $\seqdeno{\Gamma,s'\ts u}$ is a maximal strategy for $X\sequoid\oc\V_\Gamma$, we must have $\seqdeno{s,\sigma_j}=\seqdeno{\Gamma,s'\ts u}$ for all $j\ge i$, and therefore that $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$.
+
+  By induction on $T$, this extends to higher types by continuity of composition.
 \end{proof}
@@
   \[
-    \oc\V_\Gamma \xrightarrow{\langle \oc\V_\Gamma,\sigma_1^\dag,\cdots,\sigma_n^\dag\rangle} \oc\V_{\Gamma,\Delta} \xrightarrow{\sigma} \deno{T}\,.
+    \oc\V_\Gamma \xrightarrow{\langle \der,\sigma_1,\cdots,\sigma_n^\dag\rangle^\dag} \oc\V_{\Gamma,\Delta} \xrightarrow{\sigma} \deno{T}\,.
     \]
@@
   \[
-    (\sigma_i)\semicom\deno{\Gamma\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
-    \]
+    (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
+    \]
+  \label{LemAdequacy}
 \end{lemma}
+\begin{proof}
+  Induction on the typing derivation $\Gamma,\Delta \ts M\from T$.
+
+  \begin{itemize}
+    \item Let $x_j\from T_j$ be a variable occurring in $\Delta$.  
+      Then $x_j[N_i/x_i]=N_j$.  
+      Moreover, it is clear that $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts x_j} = \sigma_j$.
+      And we have $\sigma_j\plot_{T_j}^\Gamma N_j$ by hypothesis.
+
+    \item Next, suppose that $x\from\Var$ is a variable occurring in $\Gamma$.
+      Then we have $x[N_i/x_i]=x$, and it is easy to see that we have
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts x} = \deno{\Gamma\ts x}\,.
+        \]
+      Now we have $\deno{\Gamma\ts x};\pr_n = \deno{\Gamma\ts x\gets n}$ and $\deno{\Gamma\ts x};\pr_{\bN} = \deno{\Gamma \ts \oc\bN}$.  
+      From Lemma \ref{LemSoundnessOpto} (in particular, Figures \ref{FigSoundnessOoptoContext} and \ref{FigSoundnessOoptoStorage}), we know that if $s$ is a $\Gamma$-store, then
+      \[
+        \seqdeno{s,\deno{\Gamma\ts x\gets n}} = \seqdeno{\Gamma,s\ts x\gets n} = \seqdeno{\Gamma, (s\vert x\mapsto n)\ts \skipp}\,,
+        \]
+      where we have that $\Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)$, and that
+      \[
+        \seqdeno{s,\deno{\Gamma\ts \oc x}} = \seqdeno{\Gamma,s\ts \oc x} = \seqdeno{\Gamma,s\ts s(x)}\,,
+        \]
+      where we have that $\Gamma,s\ts \oc x \converges s(x),s$.
+
+    \item Next, suppose that $\Gamma,\Delta\ts M\from S\to T$ and $\Gamma,\Delta\ts N\from S$, where we already know that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{S\to T}^\Gamma M[N_i/x_i]
+        \]
+      and that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts N}\plot_S^\Gamma N[N_i/x_i]\,.
+        \]
+      Then it easy to see that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N}
+        \]
+      is given by the composite
+      \small
+      \[
+        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}) \tensor ((\sigma_i)\semicom\deno{\Gamma,\Delta\ts N})} (\oc\deno S \implies \deno T) \tensor \oc\deno {S} \xrightarrow{\ev} \deno T.
+        \]
+      \normalsize
+      Therefore, by the definition of $\plot_{S\to T}^\Gamma$, it must be the case that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N} \plot_{T}^\Gamma M[N_i/x_i]\,N[N_i/x_i] = (M\,N)[N_i/x_i],.
+        \]
+    \item Next, suppose that $\Gamma,\Delta,x\from S \ts M\from T$.  
+      We claim that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta,\lambda x.M} \plot_{S\to T}^\Gamma (\lambda x.M)[N_i/x_i]\,.
+        \]
+      Let $\sigma'\from \oc\V_\Gamma \implies \deno S$ be a strategy and let $\Gamma\ts N\from S$ be a term in context such that $\sigma\plot_S^\Gamma N$.  
+      Then, by the inductive hypothesis (with $x$ lying in the `$\Delta$-part', we know that
+      \[
+        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}\plot_T^\Gamma M[N_i/x_i,N'/x]\,.
+        \]
+      Then, since $\Gamma,s\ts (\lambda x.M[N_i/x_i])\,N'\opto \Gamma,s\ts M[N_i/x_i,N'/x]$ for any $\Gamma$-store $s$, by Lemma \ref{LemAdequacyOpto} we know that
+      \[
+        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M} \plot_T^\Gamma ((\lambda x.M)[N_i/x_i])\,N'\,.
+        \]
+      Finally, observe that $(\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}$ is the composite
+      \[
+        \oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n,\sigma'\rangle^\dag} \oc\V_{\Gamma,\Delta,x} \xrightarrow{\deno{\Gamma,\Delta,x\from S\ts M}} \deno T\,,
+        \]
+      which can alternatively be written as
+      \begin{mathpar}
+        \oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag} \oc\V_{\Gamma,\Delta} \xrightarrow{\mu_{\V_{\Gamma,\Delta}}} \oc\V_{\Gamma,\Delta}\tensor\oc\V_{\Gamma,\Delta}\\ \xrightarrow{\deno{\Gamma,\Delta\ts \lambda x.M} \tensor (\sigma')^\dag} (\oc\deno S\implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\,.
+      \end{mathpar}
+
+      In the special case that $S=\Var$ and $T=X$ is a datatype, we need to show that we also have
+      \begin{mathpar}
+        \bigg(\oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag}
+        \oc\V_{\Gamma,\Delta} \xrightarrow{\runit_{\oc\V_{\Gamma,\Delta}}}
+        \oc\V_{\Gamma,\Delta}\tensor I \xrightarrow{\oc\V_{\Gamma,\Delta} \tensor \oc0}
+        \oc\V_{\Gamma,\Delta}\tensor\oc\bN \xrightarrow{\oc\V_{\Gamma,\Delta}\tensor\cell}
+        \oc\V_{\Gamma,\Delta}\tensor\oc\Var \xrightarrow{\deno{\Gamma,\Delta\ts\lambda x.M}\tensor \oc\Var}\\
+        (\oc\Var \implies X) \tensor \oc\Var \xrightarrow{\ev}
+        X\bigg)
+        \plot_X^\Gamma \neww_X \lambda x.M[N_i/x_i]\,.
+      \end{mathpar}
+      Call this composite (in brackets) $\zeta$.
+
+      By induction (taking $x$ to be in the `$\Gamma$-component'), we know already that
+      \begin{mathpar}
+        \left(
+        \oc\V_{\Gamma,x} \xrightarrow{\langle\pr_\Gamma,\sigma_1,\cdots,\sigma_n,\pr_x\rangle^\dag}
+        \oc\V_{\Gamma,\Delta,x} \xrightarrow{\deno{\Gamma,\Delta,x\ts M}}
+        X
+        \right)
+        \plot_X^{\Gamma,x} M[N_i/x_i]\,.
+      \end{mathpar}
+      Call this composite $\xi$.  
+      Then we can write the first composite $\zeta$ as
+      \begin{mathpar}
+        \oc\V_\Gamma \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag}
+        \oc\V_{\Gamma,\Delta} \xrightarrow{\runit_{\oc\V_{\Gamma,\Delta}}}
+        \oc\V_{\Gamma,\Delta}\tensor I \xrightarrow{\oc\V_{\Gamma,\Delta} \tensor \oc0}
+        \oc\V_{\Gamma,\Delta}\tensor\oc\bN \xrightarrow{\oc\V_{\Gamma,\Delta}\tensor\cell}
+        \oc\V_{\Gamma,\Delta}\tensor\oc\Var \xrightarrow{\xi}
+        X\,.
+      \end{mathpar}
+      Therefore, for any $\Gamma$-store $s$, either $\seqdeno{s,\xi}=\bot$, in which case $\seqdeno{s,\zeta}=\bot$, or $\seqdeno{(s\vert x\mapsto 0),\xi}=\seqdeno{s',u}$ for some $u$ in $X$ and some $\Gamma,x$-store $s'$ such that $\Gamma,x,(s\vert x\mapsto 0) \ts M \converges u,s'$.
+      In the second case, we have $\seqdeno{s,\zeta} = \seqdeno{s'\vert_\Gamma,u}$, and $\Gamma,s\ts M \converges u,s'\vert_\Gamma$.
+  \end{itemize}
+
+  Now we move on to the structural constants for the datatypes.  
+  We deal with the case of the type $\nat$ (i.e., the terms $n$, $\suc M$, $\pred M$ and $\IfO M\Then N \Else P$, and it should be clear how our ideas translate to the corresponding rules at the types $\com$ and $\bool$.
+
+  \begin{itemize}
+    \item Given a numeral $n$ and a $\Gamma$-store $s$, we have $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts n} = \deno{\Gamma\ts n}$ and $\seqdeno{s,\deno{\Gamma\ts n}} = \seqdeno{\Gamma,s\ts n}$, where $\Gamma,s\ts n\converges n,s$.
+
+    \item Suppose $\Gamma,\Delta\ts M\from \nat$, and that we already know that 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{\nat}^\Gamma M[N_i/x_i]\,.
+        \]
+      So for all $\Gamma$-stores $s$, either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \bot_{\bN\sequoid\oc\V_\Gamma}$ or it is equal to $\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$.
+
+      Now we have 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M};(\suc\tensor\oc\V_\Gamma)\,;
+        \]
+      since $\suc\from\bN \implies \bN$ is a strict strategy, we know that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \suc M})} = \bot_{\bN\sequoid\oc\V_\Gamma}$ or it is equal to $\seqdeno{\Gamma,s'\ts n};(\suc\tensor\oc\V_\Gamma) = \seqdeno{\Gamma,s'\ts n+1}$, and we have $\Gamma,s\ts \suc M[N_i/x_i]\converges n+1$.
+      Therefore, 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} \plot_{\nat}^\Gamma \suc M[N_o/x_i]\,.
+        \]
+
+      A similar argument proves that 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\pred M} \plot_{\nat}^\Gamma \pred M[N_i/x_i]\,.
+        \]
+
+    \item Now we move on to the conditional.  
+      Suppose that we have $\Gamma,\Delta\ts M\from \nat$ and $\Gamma,\Delta\ts N,P\from X$ for some datatype $X$.  
+      Let $s$ be a $\Gamma$-store.  
+      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\oc\V_\Gamma\ts \bN}$, then
+      \[
+        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{\oc\V_\Gamma \ts X}\,.
+        \]
+      Otherwise, by induction we know that $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}}=\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$ such that $\Gamma,s\ts M[N_i/x_i]\converges n,s'$.
+      Without loss of generality, suppose that $n=0$.  
+      Then we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma\,\Delta\ts \IfO M \Then N \Else P})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO 0 \Then N \Else P})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta \ts N})}\,. \\
+      \end{IEEEeqnarray*}
+      Then, by induction, this last term is either equal to $\bot_{X\sequoid\V_\Gamma}$,or is equal to $\seqdeno{\Gamma,s''\ts u}$ for some $u\in X$ such that $\Gamma,s'\ts N[N_i/x_i]\converges u,s''$.
+      In this second case, we have $\Gamma,s\ts \IfO M[N_i/x_i] \Then N[N_i/x_i] \Else P[N_i/x_i] \converges u,s''$.
+  \end{itemize}
+  Next, we deal with the rules for variables.
+  \begin{itemize}
+    \item Suppose $\Gamma,\Delta\ts V\from\Var$, and suppose we already know that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var} V[N_i/x_i]\,.
+        \]
+      Then by definition we have
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \oc V} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_{\bN} \plot_{\bN}^\Gamma \oc\V[N_i/x_i]\,.
+        \]
+      Suppose $\Gamma,\Delta\ts E\from \nat$, and suppose we know already that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E} \plot_{\bN} E[N_i/x_i]$.  
+      Then, for all $s$, either $\seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E}}=\bot_{\bN \sequoid\oc\V_\Gamma}$ -- in which case
+      \[
+        \seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets E}} = \bot_{\bC \sequoid \oc\V_\Gamma}
+        \]
+      (since $\assign$ is a strict strategy) -- or it is equal to $\seqdeno{s',n}$ for some $n\in \bN$ such that $\Gamma,s\ts E[N_i/x_i]\converges n,s'$.
+      In the second case, we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V \gets E})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets n}} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)} \\
+        \plot_{\Var}^\Gamma & V[N_i/x_i]\gets n\,.
+      \end{IEEEeqnarray*}
+      Then, since we have $\Gamma,s,V[N_i/x_i]\gets E[N_i/x_i] \opto \cdots \opto \Gamma,s',V[N_i/x_i]\gets n$, the claim follows by Lemma \ref{LemAdequacyOpto}.
+    \item Suppose that $\Gamma,\Delta\ts W \from \nat \to \com$ and that $\Gamma,\Delta \ts R \from \nat$.
+      We claim that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts\mkvar\,W\,R};\pr_n\plot_\com^\Gamma (\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\gets n$ for each $n$ and that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN\plot_\nat^\Gamma \oc(\mkvar\,W[N_i/x_i]\,R[N_i/x_i])$.
+
+      For the first of these, let $s$ be a $\Gamma$-store.  
+      We have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_n)} \\
+        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts W\,n})} \\
+        \plot_{\com}^\Gamma & W[N_i/x_i]\,n\,.
+      \end{IEEEeqnarray*}
+      Since we have $\Gamma,s\ts (\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\gets n \opto \Gamma,s,W[N_i/x_i]\,n$, the claim follows by Lemma \ref{LemAdequacyOpto}.
+
+      For the second, we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN)} \\
+        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts R})} \\
+        \plot_{\com}^\Gamma & R[N_i/x_i]\,.
+      \end{IEEEeqnarray*}
+      Since we have $\Gamma,s\ts\oc(\mkvar\,W\,R)\opto\Gamma,s\ts R$, the claim follows by Lemma \ref{LemAdequacyOpto}.
+
+    \item We have already proved that if $\Gamma,x\from \Var,\Delta\ts M\from X$, and $(\sigma_i)\semicom\deno{\Gamma,x\from \Var,\Delta\ts M}\plot_X^\Gamma M$ then $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts \neww_X\lambda x.M}\plot_X^\Gamma \neww_X\lambda x.M$.
+  \end{itemize}
+  It remains to deal with the case of the recursion combinator $\Y_T$.  
+  First recall that if $h\from ((\deno T \to \deno T) \to \deno T) \to (\deno T\to \deno T) \to T$ (where we write $A \to B$ for $\oc A \implies B$) is the morphism corresponding to $\lambda F^{(T\to T) \to T}.\lambda f^{T\to T}.f(F\,f)$, then $\Y_T$ is constructed as the limit of the chain
+  \[
+    \bot_{(T\to T)\to T} \subset \bot_{(T\to T) \to T};h \subset \bot_{(T\to T)\to T};h;h \subset \cdots\,.
+    \]
+  By Lemma \ref{LemAdequacyLimits}, then, it suffices to show that if $\Gamma,\Delta \ts M\from T \to T$ then $(\sigma_i)\semicom \deno {\Gamma,\Delta\ts M};\left(\bot_{(T\to T)\to T}\right);h^n\plot_{T}^{\Gamma} \Y_T M[N_i/x_i]$ for each $n$.
+
+  We do this by induction on $n$.  
+  Lemma \ref{LemAdequacyBot} takes care of the initial case, and it will therefore suffice to prove that if $\sigma\plot_T^\Gamma \Y_T M$ then $\sigma;h\plot_T^\Gamma \Y_T M$.
+
+  Suppose first that $T=X$ is a datatype.  
+  We know from above that $\sigma;h\plot_X^\Gamma (\lambda F.\lambda f.f(F\,f))\Y_T M$.
+  Let $s$ be a $\Gamma$-store.  
+  Then either $\seqdeno{s,(\sigma;h)} = \bot_{X\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,(\sigma;h)} = \seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ and some $u\in X$ such that $\Gamma,s\ts (\lambda F.\lambda f.f(F\,f))\Y_t M\converges s',u$.
+\end{proof}
 

### 2019-04-11 Thesis/games.tex
new.

@@
       \[
-        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
-        \]
-      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, where $M=\lambda x.M'$, then
-      \begin{align*}
-        \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
-        \plot_X^\Gamma \neww_X M\,.
-      \end{align*}
+        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,.
+        \]
   \end{itemize}
@@
   Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\V_\Gamma};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.
-
-  In the case that $S=\Var$ and $T=X$ is a datatype, we also need to show that $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev\plot_X^\Gamma\neww_X(\lambda x.M\,x)$.  
-  Writing $\sigma'$ for the composite $\runit_{\oc\V_\Gamma};(\sigma\tensor(\oc 0;\cell));\ev$, we know already that $\sigma'\plot_X^\Gamma \neww_X(\lambda x.N\,x)$.
-  Let $s$ be a $\Gamma$-store.  
-  Then we know that if $\seqdeno{s,\sigma'}\ne\bot_{\oc\V_\Gamma\implies X}$, then $\seqdeno{s,\sigma'}=\seqdeno{s',u}$ for some $s'$, $u$ such that $\Gamma,\neww_X \lambda x.N\,x\converges u,s'$.
-  It follows that $\Gamma,x,(s\vert x\mapsto 0)\ts N\,x\converges u,s'$; then, since $\Gamma,x,(s\vert x\mapsto 0)\ts M\,x\opto \Gamma,x(s\vert_x\mapsto 0)\ts N\,x$, we have $\Gamma,x\ts M\,x\converges u,s'$ by Lemma \ref{LemSoundnessOpto}.
-  Therefore, $\Gamma,s\ts \neww_X \lambda x.M\,x \ts u,s'$.  
-  Since $s$ was arbitrary, it follows that $\sigma'\plot_X^\Gamma \new_X(\lambda x.M\,x)$.
 \end{proof}
@@
   which is equal to $\bot_{\oc\V_\Gamma\implies\deno T}$.
-
-  Lastly, in the special case that $S=\Var$ and $T=X$ is a datatype, we need to show that
-  \begin{align*}
-    \left(\oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\sigma\tensor (\oc 0;\cell)} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right)\qquad\\
-    \plot_X^\Gamma \neww_X M\,.
-  \end{align*}
-  Indeed, this composite is equal to $\bot_{\oc\V_\Gamma\implies X}$ by an identical argument.
 \end{proof}
@@
       \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var} V[N_i/x_i]\,.
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var}^\Gamma V[N_i/x_i]\,.
         \]
@@
         = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets n}} \\
-        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)} \\
-        \plot_{\Var}^\Gamma & V[N_i/x_i]\gets n\,.
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)}\,.
       \end{IEEEeqnarray*}
+      Now we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n\plot_{\Var}^\Gamma V[N_i/x_i]$ by induction, so this composite is either equal to 
       Then, since we have $\Gamma,s,V[N_i/x_i]\gets E[N_i/x_i] \opto \cdots \opto \Gamma,s',V[N_i/x_i]\gets n$, the claim follows by Lemma \ref{LemAdequacyOpto}.

### 2019-04-16 Thesis/games.tex
Finished chapter.

--- 2019-04-08 Thesis/games.tex
@@
 
-  We say that a justified sequence $s$ is \emph{legal} if it is well-formed and visible, and write $L_A$ for the set of legal sequences occurring in $A$.
+  We say that a justified sequence $s$ is \emph{legal} if it is well-formed and visible, and write $\L_A$ for the set of legal sequences occurring in $A$.
 \end{definition}
@@
 \begin{definition}
-  Given a legal sequence $s\in L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.
+  Given a legal sequence $s\in \L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.
 
@@
 
-  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
+  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
 \end{definition}
@@
     \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
-    \item $P_{A\times B} = \{s\in L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
+    \item $P_{A\times B} = \{s\in \L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
   \end{itemize}
@@
     \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
-    \item $P_{A\tensor B} = \{s\in L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
+    \item $P_{A\tensor B} = \{s\in \L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
   \end{itemize}
@@
     \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$, and
-    \item $P_{A\implies B} = \{s\in L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
+    \item $P_{A\implies B} = \{s\in \L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
   \end{itemize}
@@
     \item $\ts_{\oc A} = \ts_A$ and
-    \item $P_{\oc A} = \{s\in L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
+    \item $P_{\oc A} = \{s\in \L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
   \end{itemize}
@@
   Let $A,B,C$ be arenas.  
-  An \emph{interaction sequence} between $A,B,C$ is a justified sequence $\s$ of moves drawn from $M_A$, $M_B$ and $M_C$ such that $\s\vert_{A,B}\in L_{A\implies B}$ and $\s\vert_{B,C}\in L_{B\implies C}$.
+  An \emph{interaction sequence} between $A,B,C$ is a justified sequence $\s$ of moves drawn from $M_A$, $M_B$ and $M_C$ such that $\s\vert_{A,B}\in \L_{A\implies B}$ and $\s\vert_{B,C}\in \L_{B\implies C}$.
   Here, $\s\vert_{A,B}$ is the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$, together with all justification pointers between moves in $A$ and $B$, and $\s\vert_{B,C}$ is defined similarly.
@@
   Induction on the length of $s$.
-  If $s=\epsilon$, then $bs$ ends with an $O$-move in $B$, and we have $\pv{b}^{A\implies B} = b = \pv{b}^{B}$.
+  If $s=\epsilon$, then $bs$ ends with an $O$-move in $B$, and we have $\ov{b}^{A\implies B} = b = \ov{b}^{B}$.
 
@@
   $\sigma;\tau$ is a strategy for $A\implies C$.  
+  \label{PropComposition}
 \end{proposition}
@@
   First, we claim that $\s\vert_{A,C}\in P_{A\implies B}$ for any $\s\in \sigma\|\tau$.
-  Since we certainly have $\s\vert_{A,C}\vert_A = \s\vert_{A,B}\vert_A\in P_A$ and $\s\vert_{A,C}\vert_C = \s\vert_C = \s\vert_{B,C}\vert_C\in P_C$, it suffices to show that $\s\vert_{A,C}\in L_{A\implies C}$.
+  Since we certainly have $\s\vert_{A,C}\vert_A = \s\vert_{A,B}\vert_A\in P_A$ and $\s\vert_{A,C}\vert_C = \s\vert_C = \s\vert_{B,C}\vert_C\in P_C$, it suffices to show that $\s\vert_{A,C}\in \L_{A\implies C}$.
 
@@
   Let $ta\prefix\s\vert_{A,C}$.
-  Choose some $\t\prefix\s$ such that $\t\vert_{A,C}=t$.
+  Choose some $\t a\prefix\s$ such that $\t a\vert_{A,C}=ta$.
 
@@
   Then by Lemma \ref{LemHarmersLemma}, $\pv{\t a}\in\Int(A,B,C)$.  
-  By Lemma \ref{LemHarmerRestriction}, $\pv{t}a=\pv{ta}=\pv{\t a}\vert_{A,C}$, and therefore that the justifier of $a$ must be inside $\pv{t}$.
+  By Lemma \ref{LemHarmerRestriction}, we know that $\pv{t}a=\pv{ta}=\pv{\t a}\vert_{A,C}$, and therefore that the justifier of $a$ must be inside $\pv{t}$.
 
   Secondly, suppose that $a$ is an $O$-move.
-  If $a$ is an $O$-move in $C$, then either it is initial or $t$ ends with some $P$-move in $B$, and therefore $\ov{t}_{A\implies C}=\ov{t\vert_B}_B = \ov{\t\vert_{B,C}}_B$.  
-  Therefore, since $t\vert_{B,C}$ satisfies visibility, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.  
+  If $a$ is an $O$-move in $C$, then either it is initial or $\t$ ends with some $P$-move in $C$, and therefore $\ov{t}_{A\implies C} = \ov{t\vert_C}_C = \ov{\t\vert_{B,C}}_C$ by Lemma \ref{LemProjectionLemma}.
+  Therefore, since $\t\vert_{B,C}$ satisfies visibility, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.  
   If $a$ is an $O$-move in $A$, then write $t=cu$ and $\t=c\u$, where $c$ is the starting move in $C$.
@@
 
-  Therefore, $\s\vert_{A,C}\in L_{A\implies C}$, so $\s\vert_{A,C}\in P_{A\implies C}$.
+  Therefore, $\s\vert_{A,C}\in \L_{A\implies C}$, so $\s\vert_{A,C}\in P_{A\implies C}$.
 
@@
 In this section, we shall prove that composition of strategies is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.
-To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in L_{A\implies B}$, $\u\vert_{B,C}\in L_{B\implies C}$ and $\u\vert_{C,D}\in L_{C \implies D}$.
+To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in \L_{A\implies B}$, $\u\vert_{B,C}\in \L_{B\implies C}$ and $\u\vert_{C,D}\in \L_{C \implies D}$.
 Given such a sequence $\u$, we define $\u\vert_{A,D}$ as before; i.e., we take all moves from $\u$ occurring in $A$ and $D$, together with justification pointers within these games, and if an initial move in $A$ is justified by an initial move in $B$, which is justified by an initial move in $C$, which is justified by an initial move in $D$, then we add a justification pointer from that move in $A$ to that move in $D$.
@@
 \begin{remark}
-  The definitions of \emph{lax action} can be found at the start of chapter \ref{SecParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
-  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in chapter \ref{SecParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.
+  The definitions of \emph{lax action} can be found at the start of Chapter \ref{ChapParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
+  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.
   A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
@@
   \]
-Concretely, the strategy $\cell$ behaves as follows.  
+Concretely, the strategy $\cell$ behaves as follows, as we shall prove in Proposition \ref{PropCellComb}.
 When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
@@
   \end{IEEEeqnarray*}
+\end{proof}
+
+This coalgebraic definition of the $\cell$ strategy will be sufficient for most of our purposes, it will also be convenient to have a more direct definition.
+
+\begin{proposition}
+  The strategy $\cell$ is the strategy on $\oc\bN \implies \oc\Varr$ that behaves as follows.  
+  It replies to a move $q_n$ (i.e., the initial move in the $n$-th component of $\bC$ in $\Varr$) with the unique answer $a$, and replies to the move $q$ in the $\bN$ component of $\Varr$ with that number $n$ such that $q_n$ was the most recently played $O$-move in the $\bC^\bN$ component, or, if no such move has been played, it interrogates $\oc\bN$ on the left and copies the value back on to the right.
+  \label{PropCellComb}
+\end{proposition}
+\begin{proof}
+  It will suffice to show that the strategy $\cell$ as described in the statement makes the diagram
+  \[
+    \begin{tikzcd}
+      \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
+        & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
+      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
+        & \Varr \sequoid \oc\Varr
+    \end{tikzcd}
+    \]
+  commute.
+  Since $\dist_{(\bC)_\bN,\bN}$ is an isomorphism, it will suffice to show commutativity of the diagram formed by composing by it on the right; i.e.:
+  \[
+    \begin{tikzcd}[column sep=60pt]
+      \oc\bN \arrow[rr, "{\langle (\wwrite_n)_{n\in\bN},\rread \rangle}"] \arrow[d, "\cell"']
+        &
+          & (\bC \sequoid\oc\bN)^\bN \times (\oc\bN \sequoid \oc\bN) \arrow[d, "(\bC \sequoid \cell)^\bN \times (\bN \sequoid \cell)"] \\
+      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
+        & \Varr\sequoid\oc\Varr \arrow[r, "{\dist_{(\bC)_{\bN},\bN}}"]
+          & {(\bC \sequoid \oc\Varr)^{\bN} \times (\bN \sequoid \oc\Varr)\,.}
+    \end{tikzcd}
+    \]
+  That is, we need to show that the following diagrams commute, where $n$ in the first diagram ranges over the natural numbers.
+  \begin{mathpar}
+    \begin{tikzcd}[column sep=40pt]
+      \oc\bN \arrow[rr, "\wwrite_n"] \arrow[d, "\cell"']
+        &
+          & \bC \sequoid \oc\bN \arrow[d, "\bC \sequoid \cell"] \\
+      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
+        & \Varr \sequoid \oc\Varr \arrow[r, "\pr_n \sequoid \oc\Varr"]
+          & \bC \sequoid \oc\Varr
+    \end{tikzcd}
+    \and
+    \begin{tikzcd}[column sep=40pt]
+      \oc\bN \arrow[rr, "\rread"] \arrow[d, "\cell"']
+        &
+          & \bN \sequoid \oc\bN \arrow[d, "\bN \sequoid \cell"] \\
+      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
+        & \Varr \sequoid \oc\Varr \arrow[r, "\pr_\bN \sequoid \oc\Varr"]
+          & \bN \sequoid \oc\Varr
+    \end{tikzcd}
+  \end{mathpar}
+  Consider the first diagram.  
+  We may identify plays of $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$ with those plays in $\cell$ that begin with the initial move $q_n$ in $\Varr$ (i.e., the initial move $q$ in the $n$-th copy of $\bC$).
+  We need to show that plays in $\wwrite_n;(\bC\sequoid\cell)$ take the same form.  
+  Indeed, the response to the initial move in $\bC$ in $\wwrite_n;(\bC\sequoid\cell)$ is the unique response $a$, by the definition of $\wwrite_n$; thereafter, play continues in $\oc\Varr$ according to $\cell$ -- so the response to a move $q_m$ will be $a$, while the response to $q$, if some $q_m$ has been played already in $\oc\Varr$, will be the most recently occurring value of $m$.
+
+  If no $q_m$ has been played in $\oc\Varr$, then the behaviour of $\cell$ tells us that we must interrogate the $\oc\bN$ in $\bC\sequoid\oc\bN$ in order to get the value.  
+  By the definition of $\wwrite_n$, the value returned will be $n$, mirroring the behaviour in $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$.
+
+  Now consider the second diagram.  
+  We may identify plays of the strategy $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$ with those plays in $\cell$ that begin with the initial move $q$ in $\Varr$ (i.e., the initial move $q$ in the copy of $\bN$).
+  We need to show that plays in $\rread;(\bN\sequoid\cell)$ take the same form.  
+  Indeed, the response to the initial move will be to interrogate $\oc\bN$ on the left to get the value.  
+  Thereafter, play will continue between $\oc\bN$ and $\oc\Varr$ according to the $\cell$ strategy -- so once again the response to a move $q_m$ will be $a$, while the response to $q$, if some $q_m$ has been played, will be the most recently occurring value $m$.
+
+  If no $q_m$ has been played in $\oc\Varr$, then, by the definition of $\rread$, the strategy will interrogate $\oc\bN$ in order to get its response, just as in the strategy $\cell;\alpha_{\Varr};(\pr_\bN\sequoid\oc\Varr)$.
 \end{proof}
@@
 
-Given a $\Var$-context $\Gamma$, we will write $S_\Gamma$ for $\bN \times \cdots \times \bN$ and $\V_\Gamma$ for $\Varr \times \cdots \times \Varr$, where in each case the terms of the tensor product are indexed by the variables in $\Gamma$.
-Then, given some term $\Gamma\ts M$ in context, its denotation will be a morphism $\deno{\Gamma\ts M\from T} \from \oc \V_\Gamma \implies \deno{T}$.
-
-Given $\Gamma$, we have a morphism $\cell^\Gamma\from \oc S_\Gamma \implies \oc V_\Gamma$, given by
-\[
-  \oc S_\Gamma \cong \oc \bN \tensor \cdots \tensor \oc \bN \xrightarrow{\cell \tensor \cdots \tensor \cell} \oc \Varr \tensor \cdots \tensor \oc \Varr \cong \oc V_\Gamma\,.
+Given a $\Var$-context $\Gamma$, we will write $S_\Gamma$ for $\bN \times \cdots \times \bN$.
+
+Given $\Gamma$, we have a morphism $\cell^\Gamma\from \oc S_\Gamma \implies \oc \deno{\Gamma}$, given by
+\[
+  \oc S_\Gamma \cong \oc \bN \tensor \cdots \tensor \oc \bN \xrightarrow{\cell \tensor \cdots \tensor \cell} \oc \Varr \tensor \cdots \tensor \oc \Varr \cong \oc \deno{\Gamma}\,.
   \]
@@
 \begin{lemma}
-  Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context, and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
-  Then there is a game $A$ and strategies $\sigma\from \oc\V_\Gamma \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$, where $\tau$ is a strict strategy, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
-  \[
-    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno{T}\tensor A \xrightarrow{\wk_{\deno{T},A}} \deno{T} \sequoid A \xrightarrow{\tau} \deno{U}\,.
+  Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context (where $\Gamma$ is an arbitrary context), and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
+  Then there is a game $A$ and strategies $\sigma\from \oc{\deno{\Gamma}} \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$, where $\tau$ is a strict strategy, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
+  \[
+    \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno{T}\tensor A \xrightarrow{\wk_{\deno{T},A}} \deno{T} \sequoid A \xrightarrow{\tau} \deno{U}\,.
     \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma \ts \EE'[M]}\tensor \deno{\Gamma \ts N}} (\oc\deno{S} \implies \deno{T}) \tensor \oc\deno{S} \xrightarrow{\ev_{\oc\deno{S},\deno{T}}} \deno{T}.
+        \oc{\deno{\Gamma}} \xrightarrow{\mathmakebox[9pt]{\mu_{{\deno{\Gamma}}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma \ts \EE'[M]}\tensor \deno{\Gamma \ts N}} (\oc\deno{S} \implies \deno{T}) \tensor \oc\deno{S} \xrightarrow{\mathmakebox[-4pt]{}\ev_{\oc\deno{S},\deno{T}}} \deno{T}.
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{S'}\tensor A' \xrightarrow{\wk_{\deno{S'},A'}} \deno{S'} \sequoid A' \xrightarrow{\tau'} (\oc\deno{S}\implies\deno{T}),
+        \oc{\deno{\Gamma}} \xrightarrow{\mathmakebox[-1pt]{}\mu_{{\deno{\Gamma}}}\mathmakebox[-1pt]{}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{S'}\tensor A' \xrightarrow{\mathmakebox[-1pt]{}\wk_{\deno{S'},A'}} \deno{S'} \sequoid A' \xrightarrow{\mathmakebox[-1pt]{}\tau'\mathmakebox[-1pt]{}} (\oc\deno{S}\implies\deno{T}),
         \]
@@
         \and
-        \sigma = \mu_{\V_\Gamma};(\sigma'\tensor\deno{\Gamma\ts N}^\dag)
+        \sigma = \mu_{{\deno{\Gamma}}};(\sigma'\tensor\deno{\Gamma\ts N}^\dag)
         \and
@@
           \begin{tikzcd}[column sep=79pt]
-            \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{\V_\Gamma}"]
-              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\oc\V_\Gamma\tensor\mu_{\V_\Gamma}"] \\
-            \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor \oc\V_\Gamma"' yshift=3pt, thick, dashed]
-              & \oc \V_\Gamma \tensor (\oc \V_\Gamma \tensor \oc \V_\Gamma) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N}^\dag)"] \\
-            (\oc \V_\Gamma \tensor \oc \V_\Gamma) \tensor \oc \V_\Gamma \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}^\dag"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\V_\Gamma,\V_\Gamma,\V_\Gamma}" description, dotted]
+            \oc{\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{{\deno{\Gamma}}}"]
+              & \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[d, "\oc{\deno{\Gamma}}\tensor\mu_{{\deno{\Gamma}}}"] \\
+            \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}}"' yshift=3pt, thick, dashed]
+              & \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N}^\dag)"] \\
+            (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc {\deno{\Gamma}} \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}^\dag"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{{\deno{\Gamma}},{\deno{\Gamma}},{\deno{\Gamma}}}" description, dotted]
               & \deno{S'} \tensor (A' \tensor \oc\deno{S}) \arrow[d, "{\wk_{\deno{S'},A' \tensor \oc \deno{S}}}"] \\
@@
       \[
-        \oc \V_\Gamma \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \bN \xrightarrow{\theta} \bN\,,
+        \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \bN \xrightarrow{\theta} \bN\,,
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \bN\,,
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \bN\,,
         \]
@@
       \[
-        \oc \V_\Gamma \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \Varr \xrightarrow{\dereff} \bN\,.
+        \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \Varr \xrightarrow{\dereff} \bN\,.
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \Varr\,,
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \Varr\,,
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bC \times X \xrightarrow{\Lambda\inv(\seq_X)} X\,.
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bC \times X \xrightarrow{\Lambda\inv(\seq_X)} X\,.
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bN \times \Var \xrightarrow{\Lambda\inv(\assign)} \bC\,.
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bN \times \Var \xrightarrow{\Lambda\inv(\assign)} \bC\,.
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc \V_\Gamma \tensor \oc \V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} Y\,,
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} Y\,,
         \]
@@
         \and
-        \sigma = \mu_{\V_\Gamma};(\sigma'\tensor\deno{\Gamma\ts N})
+        \sigma = \mu_{{\deno{\Gamma}}};(\sigma'\tensor\deno{\Gamma\ts N})
         \and
@@
           \begin{tikzcd}[column sep=79pt]
-            \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{\V_\Gamma}"]
-              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\oc\V_\Gamma\tensor\mu_{\V_\Gamma}"] \\
-            \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor \oc\V_\Gamma"' yshift=3pt, thick, dashed]
-              & \oc \V_\Gamma \tensor (\oc \V_\Gamma \tensor \oc \V_\Gamma) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N})"] \\
-            (\oc \V_\Gamma \tensor \oc \V_\Gamma) \tensor \oc \V_\Gamma \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\V_\Gamma,\V_\Gamma,\V_\Gamma}" description, dotted]
+            \oc{\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{{\deno{\Gamma}}}"]
+              & \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[d, "\oc{\deno{\Gamma}}\tensor\mu_{{\deno{\Gamma}}}"] \\
+            \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}}"' yshift=3pt, thick, dashed]
+              & \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N})"] \\
+            (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc {\deno{\Gamma}} \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{{\deno{\Gamma}},{\deno{\Gamma}},{\deno{\Gamma}}}" description, dotted]
               & \deno{T} \tensor (A' \tensor X') \arrow[d, "{\wk_{\deno{T},A' \tensor X'}}"] \\
@@
       \begin{mathpar}
-        \oc\V_\Gamma \xrightarrow{\mu_{V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\mu_\Gamma \tensor \V_\Gamma} (\oc \V_\Gamma \tensor \oc \V_\Gamma) \tensor \oc\V_\Gamma \\\xrightarrow{(\deno{\Gamma\ts\EE'[M]} \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma \ts P}} (Y \tensor X) \tensor X \xrightarrow{\Lambda\inv(\Lambda\inv(\eta))} X\,.
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{V_\Gamma}} \oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}} \xrightarrow{\mu_\Gamma \tensor {\deno{\Gamma}}} (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \\\xrightarrow{(\deno{\Gamma\ts\EE'[M]} \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma \ts P}} (Y \tensor X) \tensor X \xrightarrow{\Lambda\inv(\Lambda\inv(\eta))} X\,.
       \end{mathpar}
@@
         \and
-        \sigma = \mu_{\V_\Gamma};(\mu_{\V_\Gamma}\tensor\oc\V_\Gamma);((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})
+        \sigma = \mu_{{\deno{\Gamma}}};(\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}});((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})
         \and
@@
         \[
-          \begin{tikzcd}[ampersand replacement=\&, column sep=78pt, row sep=30pt]
-            \oc \V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}"] \arrow[d, "\mu_{\V_\Gamma}"', thick, dashed]
+          \begin{tikzcd}[ampersand replacement=\&, column sep=68pt, row sep=30pt]
+            \oc {\deno{\Gamma}} \arrow[rr, "\mu_{{\deno{\Gamma}}}"] \arrow[d, "\mu_{{\deno{\Gamma}}}"', thick, dashed]
               \&
-                \& \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\oc\V_\Gamma \tensor\mu_{\V_\Gamma}"] \\
-            \oc \V_\Gamma \tensor \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}\tensor \oc\V_\Gamma", dotted] \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"', thick, dashed]
-              \& (\oc \V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma \arrow[r, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}}", dotted] \arrow[d, "(\oc\V_\Gamma \tensor \mu_{\V_\Gamma}) \tensor \oc\V_\Gamma" description, dotted]
-                \& \oc \V_\Gamma \tensor (\oc \V_\Gamma \tensor \oc\V_\Gamma) \arrow[d, "\oc\V_\Gamma \tensor (\mu_{\V_\Gamma}\tensor \oc\V_\Gamma)"] \\
-            (\oc \V_\Gamma \tensor \oc\V_\Gamma)\tensor \oc\V_\Gamma \arrow[d, "(\mu_{\V_\Gamma}\tensor\oc\V_\Gamma)\tensor \oc\V_\Gamma"', thick, dashed]
-              \& |[alias=Z]| (\oc \V_\Gamma \tensor(\oc\V_\Gamma\tensor \oc\V_\Gamma)) \tensor \oc\V_\Gamma \arrow[r, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma\tensor\oc\V_\Gamma,\oc\V_\Gamma}}", dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor (\sigma'\tensor\deno{\Gamma\ts N})) \tensor \deno{\Gamma\ts P}" description, dotted]
-                \& \oc\V_\Gamma \tensor ((\oc\V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma) \arrow[d, "\deno{\Gamma\ts M} \tensor ((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})" description] \\
-            ((\oc\V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma \arrow[d, "((\deno{\Gamma\ts M} \tensor \sigma') \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma\ts P}" {description, xshift=-20pt}, thick, dashed] \arrow[ur, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}\tensor\oc\V_\Gamma}" description, to=Z.west, dotted]
+                \& \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \arrow[d, "\oc{\deno{\Gamma}} \tensor\mu_{{\deno{\Gamma}}}"] \\
+            \oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[r, "\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}}", dotted] \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}}"', thick, dashed]
+              \& (\oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}}", dotted] \arrow[d, "(\oc{\deno{\Gamma}} \tensor \mu_{{\deno{\Gamma}}}) \tensor \oc{\deno{\Gamma}}" description, dotted]
+                \& \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \arrow[d, "\oc{\deno{\Gamma}} \tensor (\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}})"] \\
+            (\oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}})\tensor \oc{\deno{\Gamma}} \arrow[d, "(\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}})\tensor \oc{\deno{\Gamma}}"', thick, dashed]
+              \& |[alias=Z]| (\oc {\deno{\Gamma}} \tensor(\oc{\deno{\Gamma}}\tensor \oc{\deno{\Gamma}})) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}}", dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor (\sigma'\tensor\deno{\Gamma\ts N})) \tensor \deno{\Gamma\ts P}" description, dotted]
+                \& \oc{\deno{\Gamma}} \tensor ((\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}}) \arrow[d, "\deno{\Gamma\ts M} \tensor ((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})" description] \\
+            ((\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \arrow[d, "((\deno{\Gamma\ts M} \tensor \sigma') \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma\ts P}" {description, xshift=-20pt}, thick, dashed] \arrow[ur, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}}}" description, to=Z.west, dotted]
               \& |[alias=Y]| (\deno T \tensor (A' \tensor X)) \tensor X \arrow[r, "{\assoc_{\deno T,A'\tensor X,X}}" description, dotted] \arrow[d, "{\wk_{T,A'\tensor X}\tensor X}" description, dotted]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts \EE'[M]}} \Varr \xrightarrow{\lunit_{\Varr}} I \tensor \Varr \xrightarrow{n\tensor\Varr} \bN \tensor \Varr \xrightarrow{\assign} \bC\,.
+        \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts \EE'[M]}} \Varr \xrightarrow{\lunit_{\Varr}} I \tensor \Varr \xrightarrow{n\tensor\Varr} \bN \tensor \Varr \xrightarrow{\assign} \bC\,.
         \]
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}}
-        \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'}
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}}
+        \oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'}
         \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}}
@@
   \[
-    I \xrightarrow{\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\oc\V_\Gamma} \deno T \tensor\oc\V_\Gamma \xrightarrow{\wk_{\deno T,\oc\V_\Gamma}} \deno T \sequoid \oc\V_\Gamma\,.
+    I \xrightarrow{\ms\ms\ms\oc\deno s\ms\ms} \oc S_\Gamma \xrightarrow{\ms\ms\ms\cell^\Gamma\ms\ms} \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\mu_{\deno{\Gamma}}\ms\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\ms\ms\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma}\ms\ms} \deno T \tensor\oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\ms\ms\wk_{\deno T,\oc\deno{\Gamma}}\ms\ms} \deno T \sequoid \oc\deno{\Gamma}.
     \]
@@
   \[
-    \begin{tikzcd}[column sep=28pt]
+    \begin{tikzcd}[column sep=25pt, row sep=25pt]
       I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
         & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
-            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
+          & \oc \deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
+            &[22pt] \oc \deno{\Gamma} \tensor \oc \deno{\Gamma} \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma" description] \\
       {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
@@
           &
-            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma}}}"] \\
-      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
-        &
-          &
-            &  \deno{T}\sequoid \oc\V_\Gamma \\
-      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts N} \tensor \oc \V_{\Gamma,\Delta}}"]
-        &
-          & {\deno T \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"]
-            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,.} \arrow[u, "\deno{T}\sequoid\oc\pr_\Gamma"']
+            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc {\deno{\Gamma}}}}" description] \\
+      {\oc {\deno{\Gamma,\Delta}}} \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
+        &
+          &
+            &  \deno{T}\sequoid \oc\deno{\Gamma} \\
+      {\oc {\deno{\Gamma,\Delta}} \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[rr, "{\deno{\Gamma,\Delta\ts N} \tensor \oc {\deno{\Gamma,\Delta}}}"]
+        &
+          & {\deno T \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[r, "{\wk_{\deno T,\oc {\deno{\Gamma,\Delta}}}}"]
+            & {{\deno T \sequoid \oc {\deno{\Gamma,\Delta}}}\,.} \arrow[u, "\deno{T}\sequoid\oc\pr_\Gamma"' description]
     \end{tikzcd}
@@
       \[
-        \oc\V_\Gamma \xrightarrow{\runit_{\oc\V_\Gamma}} \oc\V_\Gamma \tensor I \xrightarrow{\oc\V_\Gamma\tensor (0;\cell)} \oc\V_\Gamma \tensor \oc\Varr \to \oc\V_{\Gamma,x} \xrightarrow{\Lambda\inv(\deno{\Gamma \ts \lambda x.M})} \deno{T}\,,
-        \]
-      where, of course $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc\V_{\Gamma,x}$ is a right inverse for the composite $\runit_{\oc\V_\Gamma};(\oc\V_{\Gamma}\tensor(0;\cell));\cong$, since we have a commutative diagram
+        \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\ms\runit_{\oc\deno{\Gamma}}\ms\ms\ms} \oc\deno{\Gamma} \tensor I \xrightarrow{\ms\ms\ms\ms\oc\deno{\Gamma}\tensor (0;\cell)\ms\ms\ms\ms} \oc\deno{\Gamma} \tensor \oc\Varr \to \oc{\deno{\Gamma,x}} \xrightarrow{\ms\ms\ms\ms\Lambda\inv(\deno{\Gamma \ts \lambda x.M})\ms\ms\ms} \deno{T},
+        \]
+      where, of course $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc{\deno{\Gamma,x}}$ is a right inverse for the composite $\runit_{\oc\deno{\Gamma}};(\oc{\deno{\Gamma}}\tensor(0;\cell));\cong$, since we have a commutative diagram
       \[
         \begin{tikzcd}[column sep=50pt]
-          \oc\V_\Gamma \arrow[r, "\runit_{\oc\V_\Gamma}"] \arrow[d, Rightarrow, no head]
-            & \oc\V_\Gamma \tensor I \arrow[r, "\oc\V_\Gamma\tensor(0;\cell)"] \arrow[d, "\id_{\oc\V_\Gamma\tensor I}" description]
-              & \oc\V_\Gamma \tensor \oc\Varr \arrow[d] \arrow[dl, "\oc\V_\Gamma\tensor()" description] \\
-          \oc\V_\Gamma
-            & \oc\V_\Gamma \tensor I \arrow[l, "\runit\inv"']
-              & {\oc\V_{\Gamma,x}\,.} \arrow[ll, "\oc\pr_\Gamma", bend left=20]
+          \oc\deno{\Gamma} \arrow[r, "\runit_{\oc\deno{\Gamma}}"] \arrow[d, Rightarrow, no head]
+            & \oc\deno{\Gamma} \tensor I \arrow[r, "\oc\deno{\Gamma}\tensor(0;\cell)"] \arrow[d, "\id_{\oc\deno{\Gamma}\tensor I}" description]
+              & \oc\deno{\Gamma} \tensor \oc\Varr \arrow[d] \arrow[dl, "\oc\deno{\Gamma}\tensor()" description] \\
+          \oc\deno{\Gamma}
+            & \oc\deno{\Gamma} \tensor I \arrow[l, "\runit\inv"']
+              & {\oc{\deno{\Gamma,x}}\,.} \arrow[ll, "\oc\pr_\Gamma", bend left=20]
         \end{tikzcd}
@@
       Then we may prove this case using the commutative diagram in Figure \ref{FigSoundnessOoptoNew}.
-      \begin{figure}[htbp]
-        \[
-          \begin{tikzcd}[column sep=34pt, row sep=30pt]
+      \begin{SidewaysFigure}
+        \[
+          \begin{tikzcd}[ampersand replacement=\&, column sep=50pt, row sep=50pt]
             I \arrow[r, "\oc\deno s"] \arrow[d, "{\oc\langle\deno s,0\rangle}" description]
-              &[5pt] \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-                &[-5pt] \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"] \arrow[d, "\mu_{\V_\Gamma}" description]
-                  & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\runit_{\oc\V_\Gamma};(\oc\V_\Gamma\tensor (0;\cell));\cong" {description, xshift=-16pt}] \\
+              \&[5pt] \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
+                \&[-5pt] \oc\deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"] \arrow[d, "\mu_{\deno{\Gamma}}" description]
+                  \& \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[d, "\runit_{\oc\deno{\Gamma}};(\oc\deno{\Gamma}\tensor (0;\cell));\cong" {description, xshift=-16pt}] \\
             {\oc S_{\Gamma,x}} \arrow[ur, "\oc\pr_\Gamma" description] \arrow[d, "{\cell^{\Gamma,x}}" description]
-              &
-                & \oc\V_\Gamma\tensor\oc\V_\Gamma
-                  & {\oc\V_{\Gamma,x}\tensor\oc\V_\Gamma} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\V_\Gamma}" description] \arrow[l, "\pr_\Gamma\tensor\oc\V_\Gamma"'] \\
-            {\oc\V_{\Gamma,x}} \arrow[uurr, "\oc\pr_\Gamma" description] \arrow[d, "{\mu_{\V_{\Gamma,x}}}"]
-              &
-                &
-                  & \deno T \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}" description] \\
-            {\oc\V_{\Gamma,x}\tensor\oc\V_{\Gamma,x}} \arrow[uurr, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma" {description, pos=0.7}] \arrow[uurrr, "{\V_{\Gamma,x}\tensor\pr_\Gamma}" {description, pos=0.7}] \arrow[r, "{\deno{\Gamma,x\ts M}\tensor\oc\V_{\Gamma,x}}"' yshift=-3pt]
-              & {\deno T \tensor \oc\V_{\Gamma,x}} \arrow[r, "{\wk_{\deno T,\oc\V_{\Gamma,x}}}"' yshift=-3pt]
-                & {\deno T \sequoid \oc\V_{\Gamma,x}} \arrow[r, "\deno T \sequoid\pr_\Gamma"' yshift=-3pt]
-                  & \deno T \sequoid\oc\V_\Gamma
+              \&
+                \& \oc\deno{\Gamma}\tensor\oc\deno{\Gamma}
+                  \& {\oc{\deno{\Gamma,x}}\tensor\oc\deno{\Gamma}} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\deno{\Gamma}}" description] \arrow[l, "\pr_\Gamma\tensor\oc\deno{\Gamma}"'] \\
+            {\oc{\deno{\Gamma,x}}} \arrow[uurr, "\oc\pr_\Gamma" description] \arrow[d, "{\mu_{{\deno{\Gamma,x}}}}"']
+              \&
+                \&
+                  \& \deno T \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\deno{\Gamma}}}" description] \\
+            {\oc{\deno{\Gamma,x}}\tensor\oc{\deno{\Gamma,x}}} \arrow[uurr, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma" {description, pos=0.7}] \arrow[uurrr, "{{\deno{\Gamma,x}}\tensor\pr_\Gamma}" {description, pos=0.7}] \arrow[r, "{\deno{\Gamma,x\ts M}\tensor\oc{\deno{\Gamma,x}}}"' yshift=-3pt]
+              \& {\deno T \tensor \oc{\deno{\Gamma,x}}} \arrow[r, "{\wk_{\deno T,\oc{\deno{\Gamma,x}}}}"' yshift=-3pt]
+                \& {\deno T \sequoid \oc{\deno{\Gamma,x}}} \arrow[r, "\deno T \sequoid\pr_\Gamma"' yshift=-3pt]
+                  \& \deno T \sequoid\oc\deno{\Gamma}
           \end{tikzcd}
@@
         \label{FigSoundnessOoptoNew}
-      \end{figure}
+      \end{SidewaysFigure}
     \item Now consider the rules
@@
       \[
-        \oc\V_{x,\Gamma} \xrightarrow{\oc\pr_1} \oc \Varr \xrightarrow{\deno{x\ts M}} \deno{T}\,.
+        \oc{\deno{x,\Gamma}} \xrightarrow{\oc\pr_1} \oc \Varr \xrightarrow{\deno{x\ts M}} \deno{T}\,.
         \]
@@
       \begin{mathpar}
-        \oc\deno{s\vert_\Gamma};\cell^\Gamma;\lunit_{\oc\V_\Gamma};\\((\oc\deno{s\vert_x};\cell;\mu_{\Varr};(\deno{x\ts M}\tensor\oc\Varr);\wk_{\deno T,\oc\Varr})\tensor\oc\V_\Gamma);\\\wk_{\deno T\sequoid \oc\Varr,\oc\V_\Gamma};\passoc_{\deno T,\oc\Varr,\oc\V_\Gamma};\cong
+        \oc\deno{s\vert_\Gamma};\cell^\Gamma;\lunit_{\oc\deno{\Gamma}};\\((\oc\deno{s\vert_x};\cell;\mu_{\Varr};(\deno{x\ts M}\tensor\oc\Varr);\wk_{\deno T,\oc\Varr})\tensor\oc\deno{\Gamma});\\\wk_{\deno T\sequoid \oc\Varr,\oc\deno{\Gamma}};\passoc_{\deno T,\oc\Varr,\oc\deno{\Gamma}};\cong
       \end{mathpar}
-      (where $\cong$ represents the natural isomorpism between $\deno T\sequoid(\oc\Varr\tensor\oc\V_\Gamma)$ and $\deno T \sequoid\oc\V_{x,\Gamma}$),
+      (where $\cong$ represents the natural isomorpism between the games $\deno T\sequoid(\oc\Varr\tensor\oc\deno{\Gamma})$ and $\deno T \sequoid\oc{\deno{x,\Gamma}}$),
       and so is completely determined by the value of the composite
@@
       \begin{SidewaysFigure}
+        \small
         \[
@@
               \& \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[dr, "\lunit_{\oc S_\Gamma}" description, dotted]
-                \&[18pt] \oc \V_\Gamma \arrow[r, "\lunit_{\oc\V_\Gamma}"] 
-                  \&[17pt] I \tensor \oc\V_\Gamma \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\V_\Gamma" description, thick] \\
+                \&[18pt] \oc \deno{\Gamma} \arrow[r, "\lunit_{\oc\deno{\Gamma}}"] 
+                  \&[17pt] I \tensor \oc\deno{\Gamma} \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\deno{\Gamma}" description, thick] \\
             {\oc S_{x,\Gamma}} \arrow[drr, Isom, dotted] \arrow[dd, "{\cell^{x,\Gamma}}"' description, thick, dashed]
@@
                 \& \oc\bN\tensor\oc S_\Gamma \arrow[r, "\oc\bN\tensor\cell^\Gamma" description, dotted] \arrow[dr, "\cell\tensor\cell^\Gamma" description, dotted]
-                  \& \oc\bN \tensor\oc\V_\Gamma \arrow[d, "\cell\tensor\oc\V_\Gamma" description, thick] \\
-            {\oc\V_{x,\Gamma}} \arrow[rrr, Isom, dotted] \arrow[d, "{\mu_{\V_{x,\Gamma}}}"' description, thick, dashed]
+                  \& \oc\bN \tensor\oc\deno{\Gamma} \arrow[d, "\cell\tensor\oc\deno{\Gamma}" description, thick] \\
+            {\oc{\deno{x,\Gamma}}} \arrow[rrr, Isom, dotted] \arrow[d, "{\mu_{{\deno{x,\Gamma}}}}"' description, thick, dashed]
               \&
                 \&
-                  \& \oc\Varr \tensor \oc\V_\Gamma \arrow[d, "\mu_{\Varr}\tensor\oc\V_\Gamma" description, thick] \arrow[dl, "\mu_{\Varr}\tensor\mu_{\V_\Gamma}" description, bend right=15, dotted] \\[10pt]
-            {\oc\V_{x,\Gamma}\tensor\oc\V_{x,\Gamma}} \arrow[r, dotted] \arrow[d, "{\oc\pr_1\tensor\oc\V_{x,\Gamma}}" description, dotted] \arrow[dd, "{\deno{x,\Gamma\ts M}\tensor\oc\V_{x,\Gamma}}" description, bend right=68, thick, dashed, end anchor={[xshift=-3pt]}]
-              \& (\oc\Varr \tensor \oc\V_\Gamma) \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[r, dotted] \arrow[d, "(\oc\Varr\tensor())\tensor(\oc\Varr\tensor\oc\V_{\Gamma})" description, dotted]
-                \& (\oc\Varr \tensor \oc\Varr) \tensor (\oc\V_\Gamma \tensor\oc\V_\Gamma) \arrow[r, "(\oc\Varr\tensor\oc\Varr)\tensor(()\tensor\oc\V_\Gamma)" yshift=5pt, dotted]
-                  \& (\oc\Varr \tensor \oc\Varr) \tensor\oc\V_\Gamma \arrow[d, "(\deno{x\ts M}\tensor \oc\Varr) \tensor \oc\V_\Gamma" description, thick] \\[30pt]
-            {\oc\Varr \tensor \oc\V_{x,\Gamma}} \arrow[r, Isom, dotted] \arrow[d, "{\deno{x\ts M} \tensor \oc\V_{x,\Gamma}}"' {description, yshift=1pt}, dotted]
-              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\V_\Gamma) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\V_\Gamma}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\V_\Gamma)" yshift=2pt, dotted]
-                \& \deno{T} \tensor (\oc\Varr \tensor \oc\V_\Gamma) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\V_\Gamma)}}" description, dotted]
-                  \& (\deno T \tensor \oc\Varr) \tensor \oc\V_\Gamma\arrow[d, "{\wk_{\deno T,\oc\Varr}\tensor\oc\V_\Gamma}" {description, yshift=1pt}, thick] \\
-            {\deno T \tensor \oc\V_{x,\Gamma}} \arrow[d, "{\wk_{\deno T,\oc\V_{x,\Gamma}}}"' {description, yshift=2pt}, thick, dashed] \arrow[urr, Isom, dotted]
+                  \& \oc\Varr \tensor \oc\deno{\Gamma} \arrow[d, "\mu_{\Varr}\tensor\oc\deno{\Gamma}" description, thick] \arrow[dl, "\mu_{\Varr}\tensor\mu_{\deno{\Gamma}}" description, bend right=15, dotted] \\[10pt]
+            {\oc{\deno{x,\Gamma}}\tensor\oc{\deno{x,\Gamma}}} \arrow[r, dotted] \arrow[d, "{\oc\pr_1\tensor\oc{\deno{x,\Gamma}}}" description, dotted] \arrow[dd, "{\deno{x,\Gamma\ts M}\tensor\oc{\deno{x,\Gamma}}}" description, bend right=68, thick, dashed, end anchor={[xshift=-3pt]}]
+              \& (\oc\Varr \tensor \oc\deno{\Gamma}) \tensor (\oc\Varr \tensor\oc\deno{\Gamma}) \arrow[r, dotted] \arrow[d, "(\oc\Varr\tensor())\tensor(\oc\Varr\tensor\oc{\deno{\Gamma}})" description, dotted]
+                \& (\oc\Varr \tensor \oc\Varr) \tensor (\oc\deno{\Gamma} \tensor\oc\deno{\Gamma}) \arrow[r, "(\oc\Varr\tensor\oc\Varr)\tensor(()\tensor\oc\deno{\Gamma})" yshift=5pt, dotted]
+                  \& (\oc\Varr \tensor \oc\Varr) \tensor\oc\deno{\Gamma} \arrow[d, "(\deno{x\ts M}\tensor \oc\Varr) \tensor \oc\deno{\Gamma}" description, thick] \\[30pt]
+            {\oc\Varr \tensor \oc{\deno{x,\Gamma}}} \arrow[r, Isom, dotted] \arrow[d, "{\deno{x\ts M} \tensor \oc{\deno{x,\Gamma}}}"' {description, yshift=1pt}, dotted]
+              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\deno{\Gamma}) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\deno{\Gamma}}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\deno{\Gamma})" yshift=2pt, dotted]
+                \& \deno{T} \tensor (\oc\Varr \tensor \oc\deno{\Gamma}) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\deno{\Gamma}}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\deno{\Gamma})}}" description, dotted]
+                  \& (\deno T \tensor \oc\Varr) \tensor \oc\deno{\Gamma}\arrow[d, "{\wk_{\deno T,\oc\Varr}\tensor\oc\deno{\Gamma}}" {description, yshift=1pt}, thick] \\
+            {\deno T \tensor \oc{\deno{x,\Gamma}}} \arrow[d, "{\wk_{\deno T,\oc{\deno{x,\Gamma}}}}"' {description, yshift=2pt}, thick, dashed] \arrow[urr, Isom, dotted]
               \&
                 \&
-                  \& (\deno T \sequoid \oc\Varr) \tensor \oc\V_\Gamma \arrow[d, "{\wk_{(\deno T\sequoid\oc\Varr),\oc\V_\Gamma}}" {description, yshift=2pt}] \\[5pt]
-            {\deno T \sequoid \oc\V_{x,\Gamma}} \arrow[r, Isom]
-              \& \deno T \sequoid (\oc\Varr \tensor\oc\V_\Gamma)
+                  \& (\deno T \sequoid \oc\Varr) \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{(\deno T\sequoid\oc\Varr),\oc\deno{\Gamma}}}" {description, yshift=2pt}] \\[5pt]
+            {\deno T \sequoid \oc{\deno{x,\Gamma}}} \arrow[r, Isom]
+              \& \deno T \sequoid (\oc\Varr \tensor\oc\deno{\Gamma})
                 \&
-                  \& (\deno T \sequoid \oc\Varr) \sequoid\oc\V_\Gamma \arrow[ll, "{\passoc_{\deno T,\oc\Varr,\oc\V_\Gamma}}"]
+                  \& (\deno T \sequoid \oc\Varr) \sequoid\oc\deno{\Gamma} \arrow[ll, "{\passoc_{\deno T,\oc\Varr,\oc\deno{\Gamma}}}"]
           \end{tikzcd}
           \]
+          \normalsize
           \caption{Diagram proving that if we want to prove the conclusion of Lemma \ref{LemSoundnessOopto} for a small-step rule that does not change the context and only mentions one variable, then it suffices to assume that that variable is the only variable in the context.}
@@
   \[
-    \oc\deno s;\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,.
+    \oc\deno s;\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}}\,.
     \]
@@
         & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
-            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts \EE[M]}\tensor \oc V_\Gamma"] \\
+          & \oc \deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
+            &[22pt] \oc \deno{\Gamma} \tensor \oc \deno{\Gamma} \arrow[d, "\deno{\Gamma\ts \EE[M]}\tensor \oc V_\Gamma" description] \\
       {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
@@
           &
-            & \deno U \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno U,\oc \V_{\Gamma}}}"] \\
-      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
-        &
-          &
-            &  \deno{U}\sequoid \oc\V_\Gamma \arrow[d, "{\deno{U} \sequoid (\Gamma+0_\Delta)}"] \\
-      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts \EE[N]} \tensor \oc \V_{\Gamma,\Delta}}"]
-        &
-          & {\deno U \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno U,\oc \V_{\Gamma,\Delta}}}"]
-            & {{\deno U \sequoid \oc \V_{\Gamma,\Delta}}\,,}
+            & \deno U \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno U,\oc {\deno{\Gamma}}}}" description] \\
+      {\oc {\deno{\Gamma,\Delta}}} \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
+        &
+          &
+            &  \deno{U}\sequoid \oc\deno{\Gamma} \\
+      {\oc {\deno{\Gamma,\Delta}} \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[rr, "{\deno{\Gamma,\Delta\ts \EE[N]} \tensor \oc {\deno{\Gamma,\Delta}}}"]
+        &
+          & {\deno U \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[r, "{\wk_{\deno U,\oc {\deno{\Gamma,\Delta}}}}"]
+            & {{\deno U \sequoid \oc {\deno{\Gamma,\Delta}}}\,,} \arrow[u, "\deno U \sequoid \oc\pr_\Gamma" description]
     \end{tikzcd}
@@
   \[
-    \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma\tensor\oc\V_\Gamma \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno T \tensor A \xrightarrow{\wk_{\deno T,A}} \deno T \sequoid A \xrightarrow{\tau} \deno U
+    \oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma}\tensor\oc\deno{\Gamma} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno T \tensor A \xrightarrow{\wk_{\deno T,A}} \deno T \sequoid A \xrightarrow{\tau} \deno U
     \]
@@
   \[
-    \oc\deno s;\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts M}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma};(\deno T \sequoid (\Gamma+0_\Delta))\,.
+    \oc\deno s;\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}};(\deno T \sequoid (\Gamma+0_\Delta))\,.
     \]
@@
   \[
-    \seqdeno{\Gamma,s\ts \EE[M]} = \seqdeno{\Gamma,s\ts M};(\deno T \sequoid (\mu_{\V_\Gamma};(\sigma\tensor\oc\V_\Gamma));\passoc_{\deno T,A,\oc\V_\Gamma}\inv;(\tau\sequoid\oc\V_\Gamma)\,.
+    \seqdeno{\Gamma,s\ts \EE[M]} = \seqdeno{\Gamma,s\ts M};(\deno T \sequoid (\mu_{\deno{\Gamma}};(\sigma\tensor\oc\deno{\Gamma}));\passoc_{\deno T,A,\oc\deno{\Gamma}}\inv;(\tau\sequoid\oc\deno{\Gamma})\,.
     \]
@@
     \[
-      \begin{tikzcd}[column sep=45pt, row sep=30pt, ampersand replacement=\&]
-        \oc S_\Gamma \arrow[d, "\cell^\Gamma"', thick]
-          \& I \arrow[l, "\oc\deno s"', thick]
-            \&
-              \& \\
-        \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}", thick] \arrow[d, "\mu_{\V_\Gamma}"', thick, dashed]
-          \& \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[r, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma", thick] \arrow[dd, "\oc\V_\Gamma\tensor\mu_{\V_\Gamma}" description, dotted]
-            \& \deno T \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno T,\oc\V_\Gamma}}", thick] \arrow[dd, "\deno T \tensor \mu_{\V_\Gamma}" description, dotted]
-              \& \deno T \sequoid \oc\V_\Gamma \arrow[dd, "\deno T \sequoid \mu_{\V_\Gamma}"] \\
-        \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}\tensor\oc\V_\Gamma"', thick, dashed]
+      \begin{tikzcd}[column sep=46pt, row sep=30pt, ampersand replacement=\&]
+        \oc{\deno{\Gamma}} \arrow[r, "\mu_{{\deno{\Gamma}}}", thick] \arrow[d, "\mu_{{\deno{\Gamma}}}"' description, thick, dashed]
+          \& \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[r, "\deno{\Gamma\ts M}\tensor\oc{\deno{\Gamma}}", thick] \arrow[dd, "\oc{\deno{\Gamma}}\tensor\mu_{{\deno{\Gamma}}}" description, dotted]
+            \& \deno T \tensor \oc{\deno{\Gamma}} \arrow[r, "{\wk_{\deno T,\oc{\deno{\Gamma}}}}", thick] \arrow[dd, "\deno T \tensor \mu_{{\deno{\Gamma}}}" description, dotted]
+              \& \deno T \sequoid \oc{\deno{\Gamma}} \arrow[dd, "\deno T \sequoid \mu_{{\deno{\Gamma}}}" description] \\
+        \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}}"' description, thick, dashed]
           \&
@@
               \& \\
-        (\oc\V_\Gamma \tensor \oc\V_\Gamma) \tensor \oc\V_\Gamma \arrow[r, "{\assoc_{\oc\V_\Gamma,\oc\V_\Gamma,\oc\V_\Gamma}}" yshift=3pt, dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor \sigma) \tensor\oc\V_\Gamma"', thick, dashed]
-          \& \oc\V_\Gamma \tensor (\oc\V_\Gamma \tensor \oc\V_\Gamma) \arrow[r, "\deno{\Gamma\ts M} \tensor (\oc\V_\Gamma\tensor \oc\V_\Gamma)" yshift=3pt, dotted] \arrow[d, "\deno{\Gamma\ts M}\tensor (\sigma\tensor\oc\V_\Gamma)" description, dotted]
-            \& \deno T \tensor (\oc\V_\Gamma\ \tensor \oc\V_\Gamma) \arrow[r, "{\wk_{\deno T,\oc\V_\Gamma\tensor\oc\V_\Gamma}}" yshift=3pt, dotted] \arrow[dl, "\deno T \tensor (\sigma \tensor\oc\V_\Gamma)" description, dotted]
-              \& \deno T \sequoid (\oc\V_\Gamma \tensor \oc\V_\Gamma) \arrow[d, "\deno T \sequoid (\sigma \tensor \oc\V_\Gamma)"] \\
-        (\deno T \tensor A) \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,A}\tensor\oc\V_\Gamma}"', thick, dashed] \arrow[r, "{\assoc_{\deno T,A,\oc\V_\Gamma}}", dotted]
-          \& \deno T \tensor (A \tensor \oc\V_\Gamma) \arrow[rr, "{\wk_{\deno T,A\tensor\oc\V_\Gamma}}", dotted]
+        (\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}}" yshift=3pt, dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor \sigma) \tensor\oc{\deno{\Gamma}}"' description, thick, dashed]
+          \& \oc{\deno{\Gamma}} \tensor (\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \arrow[r, "\deno{\Gamma\ts M} \tensor (\oc{\deno{\Gamma}}\tensor \oc{\deno{\Gamma}})" yshift=3pt, dotted] \arrow[d, "\deno{\Gamma\ts M}\tensor (\sigma\tensor\oc{\deno{\Gamma}})" description, dotted]
+            \& \deno T \tensor (\oc{\deno{\Gamma}}\ \tensor \oc{\deno{\Gamma}}) \arrow[r, "{\wk_{\deno T,\oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}}}}" yshift=3pt, dotted] \arrow[dl, "\deno T \tensor (\sigma \tensor\oc{\deno{\Gamma}})" description, dotted]
+              \& \deno T \sequoid (\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \arrow[d, "\deno T \sequoid (\sigma \tensor \oc{\deno{\Gamma}})" description] \\
+        (\deno T \tensor A) \tensor \oc{\deno{\Gamma}} \arrow[d, "{\wk_{\deno T,A}\tensor\oc{\deno{\Gamma}}}"' description, thick, dashed] \arrow[r, "{\assoc_{\deno T,A,\oc{\deno{\Gamma}}}}", dotted]
+          \& \deno T \tensor (A \tensor \oc{\deno{\Gamma}}) \arrow[rr, "{\wk_{\deno T,A\tensor\oc{\deno{\Gamma}}}}", dotted]
             \&
-              \& \deno T \sequoid (A \tensor \oc\V_\Gamma) \\
-        (\deno T \sequoid A) \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno T\sequoid A,\oc\V_\Gamma}}", dotted] \arrow[d, "\tau\tensor\oc\V_\Gamma", thick, dashed]
-          \& (\deno T \sequoid A) \sequoid \oc\V_\Gamma \arrow[d, "\tau\sequoid\oc\V_\Gamma"] \arrow[urr, "{\passoc_{\deno T,A,\oc\V_\Gamma}}"']
+              \& \deno T \sequoid (A \tensor \oc{\deno{\Gamma}}) \\
+        (\deno T \sequoid A) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\wk_{\deno T\sequoid A,\oc{\deno{\Gamma}}}}", dotted] \arrow[d, "\tau\tensor\oc{\deno{\Gamma}}" description, thick, dashed]
+          \& (\deno T \sequoid A) \sequoid \oc{\deno{\Gamma}} \arrow[d, "\tau\sequoid\oc{\deno{\Gamma}}"] \arrow[urr, "{\passoc_{\deno T,A,\oc{\deno{\Gamma}}}}"']
             \&
               \& \\
-        \deno U \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno U,\oc\V_\Gamma}}", thick, dashed]
-          \& \deno U \sequoid \oc\V_\Gamma
+        \deno U \tensor \oc{\deno{\Gamma}} \arrow[r, "{\wk_{\deno U,\oc{\deno{\Gamma}}}}", thick, dashed]
+          \& \deno U \sequoid \oc{\deno{\Gamma}}
             \&
@@
     & \seqdeno{\Gamma,s\ts \EE[M]} \\
-    = & \seqdeno{\Gamma,s\ts M};(\deno T\sequoid(\mu_{\V_\Gamma};(\sigma\tensor\oc\V_\Gamma));\passoc\inv;(\tau\sequoid\oc\V_\Gamma) \\
-    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid \oc\pr_\Gamma);(\deno T\sequoid(\mu_{\V_\Gamma};(\sigma\tensor\oc\V_\Gamma));\passoc\inv;(\tau\sequoid\oc\V_\Gamma) \\
-    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid (\mu_{\V_{\Gamma,\Delta}};((\pr_\Gamma;\sigma)\tensor\oc\V_{\Gamma,\Delta})));\passoc\inv; \\
-    &\qquad(\tau\sequoid\oc\V_\Gamma);(\deno U\sequoid\oc\pr_\Gamma) \\
+    = & \seqdeno{\Gamma,s\ts M};(\deno T\sequoid(\mu_{\deno{\Gamma}};(\sigma\tensor\oc\deno{\Gamma}));\passoc\inv;(\tau\sequoid\oc\deno{\Gamma}) \\
+    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid \oc\pr_\Gamma);(\deno T\sequoid(\mu_{\deno{\Gamma}};(\sigma\tensor\oc\deno{\Gamma}));\passoc\inv;(\tau\sequoid\oc\deno{\Gamma}) \\
+    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid (\mu_{{\deno{\Gamma,\Delta}}};((\pr_\Gamma;\sigma)\tensor\oc{\deno{\Gamma,\Delta}})));\passoc\inv; \\
+    &\qquad(\tau\sequoid\oc\deno{\Gamma});(\deno U\sequoid\oc\pr_\Gamma) \\
     = & \seqdeno{\Gamma,s\ts \EE[N]};(\deno U\sequoid\oc\pr_\Gamma)\,,
@@
   \[
-    \begin{tikzcd}[column sep=40pt]
-      I \arrow[r, "\oc\deno s"] \arrow[d, "\oc\deno{s'}"']
+    \begin{tikzcd}[column sep=47pt]
+      I \arrow[r, "\oc\deno s"] \arrow[d, "\oc\deno{s'}" description]
         & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
-            & \oc\V_\Gamma\tensor\oc\V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\V_\Gamma"] \\
-      \oc S_\Gamma \arrow[d, "\cell^\Gamma"']
-        &
-          &
-             & \deno{T} \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \\
-      \oc\V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
-        & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[r, "\deno{\Gamma\ts c}\tensor\oc\V_\Gamma"]
-          & \deno T \tensor \oc\V_\Gamma \arrow[r, "{\wk_{\deno T,\oc\V_\Gamma}}"]
-            & \deno T \sequoid \oc\V_\Gamma
+          & \oc\deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
+            & \oc\deno{\Gamma}\tensor\oc\deno{\Gamma} \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma}" description] \\
+      \oc S_\Gamma \arrow[d, "\cell^\Gamma"' description]
+        &
+          &
+             & \deno{T} \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\deno{\Gamma}}}" description] \\
+      \oc\deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
+        & \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[r, "\deno{\Gamma\ts c}\tensor\oc\deno{\Gamma}"]
+          & \deno T \tensor \oc\deno{\Gamma} \arrow[r, "{\wk_{\deno T,\oc\deno{\Gamma}}}"]
+            & \deno T \sequoid \oc\deno{\Gamma}
     \end{tikzcd}
@@
   \[
-    \begin{tikzcd}[column sep=28pt]
+    \begin{tikzcd}[column sep=25pt]
       I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno {s^{(n)}}"']
         & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc \V_\Gamma \arrow[r, "\mu_{\V_\Gamma}"]
-            &[22pt] \oc \V_\Gamma \tensor \oc \V_\Gamma \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma"] \\
+          & \oc \deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
+            &[22pt] \oc \deno{\Gamma} \tensor \oc \deno{\Gamma} \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma" description] \\
       {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
@@
           &
-            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc \V_{\Gamma}}}"] \\
-      {\oc \V_{\Gamma,\Delta}} \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
-        &
-          &
-            &  \deno{T}\sequoid \oc\V_\Gamma \\
-      {\oc \V_{\Gamma,\Delta} \tensor \oc \V_{\Gamma,\Delta}} \arrow[rr, "{\deno{\Gamma,\Delta\ts c} \tensor \oc \V_{\Gamma,\Delta}}"]
-        &
-          & {\deno T \tensor \oc \V_{\Gamma,\Delta}} \arrow[r, "{\wk_{\deno T,\oc \V_{\Gamma,\Delta}}}"]
-            & {{\deno T \sequoid \oc \V_{\Gamma,\Delta}}\,,} \arrow[u, "\deno T \sequoid \oc\pr_\Gamma"]
+            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc {\deno{\Gamma}}}}" description] \\
+      {\oc {\deno{\Gamma,\Delta}}} \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
+        &
+          &
+            &  \deno{T}\sequoid \oc\deno{\Gamma} \\
+      {\oc {\deno{\Gamma,\Delta}} \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[rr, "{\deno{\Gamma,\Delta\ts c} \tensor \oc {\deno{\Gamma,\Delta}}}"]
+        &
+          & {\deno T \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[r, "{\wk_{\deno T,\oc {\deno{\Gamma,\Delta}}}}"]
+            & {{\deno T \sequoid \oc {\deno{\Gamma,\Delta}}}\,,} \arrow[u, "\deno T \sequoid \oc\pr_\Gamma" description]
     \end{tikzcd}
@@
         & \\
-      {\oc\V_{\Gamma,\Delta}} \arrow[r, "\oc\pr_\Gamma"] \arrow[d, "{\mu_{\V_{\Gamma,\Delta}}}"']
-        & \oc\V_\Gamma \arrow[d, "\mu_{\V_\Gamma}"] \\
-      {\oc\V_{\Gamma,\Delta}\tensor\oc\V_{\Gamma,\Delta}} \arrow[d, "{\deno{\Gamma,\Delta\ts c}\tensor\oc\V_{\Gamma,\Delta}}"'] \arrow[r, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma"]
-        & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[d, "\deno{\Gamma\ts c}\tensor\oc\V_\Gamma"]  \\
-      {\deno T \tensor \oc\V_{\Gamma,\Delta}} \arrow[r, "\deno T \tensor \oc\pr_\Gamma"] \arrow[d, "{\wk_{\deno T,\oc\V_{\Gamma,\Delta}}}"']
-        & \deno T \tensor \oc\V_\Gamma \arrow[d, "{\wk_{\deno T,\oc\V_\Gamma}}"] \\
-      {\deno T \sequoid \oc\V_{\Gamma,\Delta}} \arrow[r, "\deno T \sequoid \oc\pr_\Gamma"]
-        & \deno T \sequoid \oc\V_\Gamma \\
+      {\oc{\deno{\Gamma,\Delta}}} \arrow[r, "\oc\pr_\Gamma"] \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
+        & \oc\deno{\Gamma} \arrow[d, "\mu_{\deno{\Gamma}}"] \\
+      {\oc{\deno{\Gamma,\Delta}}\tensor\oc{\deno{\Gamma,\Delta}}} \arrow[d, "{\deno{\Gamma,\Delta\ts c}\tensor\oc{\deno{\Gamma,\Delta}}}"'] \arrow[r, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma"]
+        & \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[d, "\deno{\Gamma\ts c}\tensor\oc\deno{\Gamma}"]  \\
+      {\deno T \tensor \oc{\deno{\Gamma,\Delta}}} \arrow[r, "\deno T \tensor \oc\pr_\Gamma"] \arrow[d, "{\wk_{\deno T,\oc{\deno{\Gamma,\Delta}}}}"']
+        & \deno T \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\deno{\Gamma}}}"] \\
+      {\deno T \sequoid \oc{\deno{\Gamma,\Delta}}} \arrow[r, "\deno T \sequoid \oc\pr_\Gamma"]
+        & \deno T \sequoid \oc\deno{\Gamma} \\
     \end{tikzcd}
@@
   \[
-    \begin{tikzcd}[column sep=14.5pt]
+    \begin{tikzcd}[column sep=10.8pt]
       I \arrow[r, "\deno{s}", thick]
         & \oc S_\Gamma \arrow[r, "\cell^\Gamma", thick]
-          & \oc\V_\Gamma \arrow[rr, "\mu_{\V_\Gamma}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\V_\Gamma}" description, dotted]
-            &
-              & \oc\V_\Gamma \tensor \oc\V_\Gamma \arrow[rr, "\deno{\Gamma\ts P}\tensor\oc\V_\Gamma", thick, dashed] \arrow[d, "\oc\V_\Gamma\tensor()" description, dotted]
-                &
-                  & \deno T \tensor\oc\V_\Gamma \arrow[ddd, "{\wk_{\deno T,\oc\V_\Gamma}}" description, thick, dashed] \arrow[ddl, "\deno T \tensor ()" description, dotted] \\
+          & \oc\deno{\Gamma} \arrow[rr, "\mu_{\deno{\Gamma}}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\deno{\Gamma}}" description, dotted]
+            &
+              & \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[rr, "\deno{\Gamma\ts P}\tensor\oc\deno{\Gamma}", thick, dashed] \arrow[d, "\oc\deno{\Gamma}\tensor()" description, dotted]
+                &
+                  & \deno T \tensor\oc\deno{\Gamma} \arrow[ddd, "{\wk_{\deno T,\oc\deno{\Gamma}}}" description, thick, dashed] \arrow[ddl, "\deno T \tensor ()" description, dotted] \\
       %
@@
             &
-              & \oc\V_\Gamma \tensor I \arrow[dr, "\deno{\Gamma\ts P}\tensor I" description, dotted] \arrow[dl, "{\wk_{\oc\V_\Gamma,I}}" description, dotted]
+              & \oc\deno{\Gamma} \tensor I \arrow[dr, "\deno{\Gamma\ts P}\tensor I" description, dotted] \arrow[dl, "{\wk_{\oc\deno{\Gamma},I}}" description, dotted]
                 &
@@
           &
-            & \oc\V_\Gamma \sequoid I \arrow[dr, "\deno{\Gamma\ts P}\sequoid I" description, dotted] \arrow[uul, "\run_{\oc\V_\Gamma}" description, dotted]
+            & \oc\deno{\Gamma} \sequoid I \arrow[dr, "\deno{\Gamma\ts P}\sequoid I" description, dotted] \arrow[uul, "\run_{\oc\deno{\Gamma}}" description, dotted]
               &
@@
                 &
-                  & \deno T \sequoid \oc\V_\Gamma \arrow[ll, "\deno T \sequoid()"']\,,
+                  & \deno T \sequoid \oc\deno{\Gamma} \arrow[ll, "\deno T \sequoid()"']\,,
     \end{tikzcd}
@@
   \[
-    \seqdeno{\Gamma,s\ts P} = \deno{s};\cell^\Gamma;\mu_{\V_\Gamma};(\deno{\Gamma\ts P}\tensor\oc\V_\Gamma);\wk_{\deno T,\oc\V_\Gamma}\,,
+    \seqdeno{\Gamma,s\ts P} = \deno{s};\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts P}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}}\,,
     \]
@@
 \begin{definition}
-  Given a $\Var$-store $\Gamma$, a strategy $\sigma\from\oc\V_\Gamma \implies A$ and a $\Gamma$-store $s$, we write
+  Given a $\Var$-store $\Gamma$, a strategy $\sigma\from\oc\deno{\Gamma} \implies A$ and a $\Gamma$-store $s$, we write
   \[
@@
   \[
-    I \xrightarrow{\oc\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\oc\V_\Gamma} A \tensor \oc\V_\Gamma \xrightarrow{\wk_{A,\oc\V_\Gamma}} A \sequoid \oc\V_\Gamma\,.
+    I \xrightarrow{\oc\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma\tensor\oc\deno{\Gamma}} A \tensor \oc\deno{\Gamma} \xrightarrow{\wk_{A,\oc\deno{\Gamma}}} A \sequoid \oc\deno{\Gamma}\,.
     \]
@@
 \begin{definition}
-  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies for $\oc\V_\Gamma \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
+  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies for $\oc\deno{\Gamma} \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
   \begin{itemize}
-    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\V_\Gamma\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\V_\Gamma}$ or $\seqdeno{s,\sigma}=\seqdeno{s',u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
-
-    \item If $\sigma\from \oc\V_\Gamma \implies \Varr$ and $\Gamma\ts M\from \Var$, we say that $\sigma\plot_{\Var}^\Gamma M$ if
+    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\deno{\Gamma}\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\deno{\Gamma}}$ or $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
+
+    \item If $\sigma\from \oc\deno{\Gamma} \implies \Varr$ and $\Gamma\ts M\from \Var$, we say that $\sigma\plot_{\Var}^\Gamma M$ if
       \[
@@
 
-    \item If $\sigma \from \oc\V_\Gamma \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\V_\Gamma \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
-      \[
-        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
-        \]
-      and in addition if $S=\Var$ and $T=X$ for some datatype $X$, then
-      \small
-      \[
-        \left(\oc\V_\Gamma \xrightarrow{\mu_{\V_\Gamma}} \oc\V_\Gamma \tensor \oc\V_\Gamma \xrightarrow{\sigma\tensor \cell} (\oc\Varr \implies X) \tensor \oc\Varr \xrightarrow{\ev} X\right) \plot_X^\Gamma \neww_X (\lambda x.M\,x)\,.
-        \]
-      \normalsize
+    \item If $\sigma \from \oc\deno{\Gamma} \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\deno{\Gamma} \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
+      \[
+        \left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N.
+        \]
   \end{itemize}
@@
   for all $\Gamma$-stores $s$.  
-  Suppose $\sigma\from\oc\V_\Gamma\implies\deno T$ is a strategy such that $\sigma\plot_T^\Gamma N$.  
+  Suppose $\sigma\from\oc\deno{\Gamma}\implies\deno T$ is a strategy such that $\sigma\plot_T^\Gamma N$.  
   Then $\sigma\plot_T^\Gamma M$.
+  \label{LemAdequacyOpto}
 \end{lemma}
@@
   Suppose that $\Gamma,s\ts M,N\ts X$, where $X$ is some datatype, and that $\Gamma,s\ts M\opto \Gamma,s\ts N$ for all $\Gamma$-stores $s$.  
-  Fix some $\Gamma$-store $s$ and some strategy $\sigma\from \oc\V_\Gamma\implies \deno T$, and suppose that $\sigma\plot_T^\Gamma N$.
-
-  If $\seqdeno{s,\sigma}\ne\bot_{\oc\V_\Gamma\implies X}$, then by hypothesis it is equal to $\seqdeno{s',u}$ for some $u$ such that $\Gamma,s\ts N\converges u,s'$.  
+  Fix some $\Gamma$-store $s$ and some strategy $\sigma\from \oc\deno{\Gamma}\implies \deno T$, and suppose that $\sigma\plot_T^\Gamma N$.
+
+  If $\seqdeno{s,\sigma}\ne\bot_{\oc\deno{\Gamma}\implies X}$, then by hypothesis it is equal to $\seqdeno{s',u}$ for some $u$ such that $\Gamma,s\ts N\converges u,s'$.  
   Then, by Lemma \ref{LemSmallToBig}, $\Gamma,s\ts M\converges u,s'$.
@@
 
-  Lastly, suppose that 
+  Lastly, suppose that $\Gamma,s\ts M,N\from S \to T$ and suppose that $\Gamma,s\ts M \opto \Gamma,s\ts N$.
+  Let $\sigma\from \oc\deno{\Gamma} \implies (\oc\deno S \implies \deno T)$ be a strategy and suppose that $\sigma \plot_{S\to T} N$.  
+  We claim that $\sigma \plot_{S\to T} M$.  
+  Indeed, let $\tau\from\oc\deno{\Gamma}\implies\deno S$ be a strategy and let $\Gamma \ts P\from S$ be a term in context such that $\tau\plot_S^\Gamma P$.  
+  Then, since $\sigma\plot_{S\to T} N$, we must have that $\mu_{\deno{\Gamma}};(\sigma\tensor\tau^\dag);\ev \plot_T^\Gamma N\,P$.  
+  Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\deno{\Gamma}};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.
+\end{proof}
+
+\begin{lemma}
+  Let $T$ be a type of Idealized Algol, and let $\Gamma$ be a $\Var$-context.  
+  Then $\bot_{\oc\deno{\Gamma}\implies \deno T}\plot_T^\Gamma M$ for any term-in-context $\Gamma\ts M\from T$.
+  \label{LemAdequacyBot}
+\end{lemma}
+\begin{proof}
+  Induction on $T$.  
+  If $T$ is a datatype and $s$ a store, then for any $\sigma\from \oc\deno{\Gamma}\implies \deno T$ we have
+  \[
+    \oc\deno s;\cell^\Gamma;\sigma = \seqdeno{s,\sigma};(\deno T\sequoid ());\run_{\deno T}\,,
+    \]
+  as in the proof of Proposition \ref{PropSoundness}; since $(\deno T\sequoid());\run_{\deno T}$ is a zigzag strategy, if $\sigma=\bot_{\oc\deno{\Gamma}\implies\deno T}$, then $\oc\deno s;\cell^\Gamma;\sigma=\bot_{\deno T}$, and therefore $\seqdeno{s,\sigma}=\bot_{T\sequoid\oc\deno{\Gamma}}$.
+
+  Suppose $\Gamma\ts M\from\Var$.  
+  Since the projections are strict strategies, we have $\bot_{\oc\deno{\Gamma}\implies\Varr};\pr_n=\bot_{\oc\deno{\Gamma}\implies\bC}\plot_{\Var}^\Gamma M$ and $\bot_{\oc\deno{\Gamma}\implies\Varr};\pr_{\bC}=\bot_{\oc\deno{\Gamma}\implies\bN}\plot_{\bN}^\Gamma M$, and therefore $\bot_{\oc\deno{\Gamma}\implies\Varr}\plot_{\Var}^\Gamma M$.
+
+  Suppose that $\Gamma\ts M\from S\to T$.  
+  Fix some $N\from S$ and $\tau\from \oc\deno{\Gamma}\implies \deno S$ such that $\tau\plot_S^\Gamma N$.
+
+  We are required to show that
+  \[
+    \left(\oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\bot\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
+    \]
+  which, by induction, we can do by showing that it is equal to $\bot_{\oc\deno{\Gamma}\implies\deno T}$.
+  Indeed, we may write this composite as
+  \[
+    \oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma}\tensor\oc\deno{\Gamma} \xrightarrow{\oc\deno{\Gamma} \tensor \tau^\dag} \oc\deno{\Gamma}\tensor\oc\deno S \xrightarrow{\Lambda\inv(\bot_{\oc\deno{\Gamma} \implies (\oc\deno S \implies \deno T))}} \deno T\,,
+    \]
+  which is equal to $\bot_{\oc\deno{\Gamma}\implies\deno T}$.
+\end{proof}
+
+\begin{lemma}
+  Let $T$ be an idealized Algol type, and let $\Gamma\ts M\from T$ be a typing judgement, where $\Gamma$ is a $\Var$-context.
+  Suppose that $\sigma_1\subset\sigma_2\subset\cdots$ is a nested sequence of strategies for $\oc\deno{\Gamma}$ such that $\sigma_i\plot_T^\Gamma M$ for all $i$.  
+  Let $\sigma=\bigcup_i \sigma_i$.  
+  Then $\sigma\plot_T^\Gamma M$.
+  \label{LemAdequacyLimits}
+\end{lemma}
+\begin{proof}
+  If $X$ is a datatype, $\Gamma$ is a $\Var$-context, $s$ is a $\Gamma$-store and $\Gamma\ts M\from X$ is a typing judgement, then if $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\deno{\Gamma}}$ for all $i$, then we must have $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\deno{\Gamma}} = \bot_{X\sequoid\oc\deno{\Gamma}}$ by continuity of composition.
+  Otherwise, $\seqdeno{s,\sigma_i}=\seqdeno{\Gamma,s'\ts u}$ for some $i$, some $\Gamma$-store $s'$ and some $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
+  In that case, since $\seqdeno{\Gamma,s'\ts u}$ is a maximal strategy for $X\sequoid\oc\deno{\Gamma}$, we must have $\seqdeno{s,\sigma_j}=\seqdeno{\Gamma,s'\ts u}$ for all $j\ge i$, and therefore that $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$.
+
+  By induction on $T$, this extends to higher types by continuity of composition.
 \end{proof}
@@
   Write $\Delta=x_1\from T_1,\cdots,x_n\from T_n$.  
-  Suppose that $\sigma_i\from \oc\V_\Gamma \implies \deno{T_i}$ are strategies and $\Gamma\ts N_i\from T_i$ are terms-in-context such that $\sigma_i\plot_{T_i}^\Gamma N_i$ for each $i$.
-
-  Given a strategy $\sigma\from \oc\V_{\Gamma,\Delta}\implies \deno{T}$, we write
+  Suppose that $\sigma_i\from \oc\deno{\Gamma} \implies \deno{T_i}$ are strategies and $\Gamma\ts N_i\from T_i$ are terms-in-context such that $\sigma_i\plot_{T_i}^\Gamma N_i$ for each $i$.
+
+  Given a strategy $\sigma\from \oc{\deno{\Gamma,\Delta}}\implies \deno{T}$, we write
   \[
@@
   \[
-    \oc\V_\Gamma \xrightarrow{\langle \oc\V_\Gamma,\sigma_1^\dag,\cdots,\sigma_n^\dag\rangle} \oc\V_{\Gamma,\Delta} \xrightarrow{\sigma} \deno{T}\,.
+    \oc\deno{\Gamma} \xrightarrow{\langle \der,\sigma_1,\cdots,\sigma_n^\dag\rangle^\dag} \oc{\deno{\Gamma,\Delta}} \xrightarrow{\sigma} \deno{T}\,.
     \]
@@
   \[
-    (\sigma_i)\semicom\deno{\Gamma\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
-    \]
+    (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
+    \]
+  \label{LemAdequacy}
 \end{lemma}
+\begin{proof}
+  Induction on the typing derivation $\Gamma,\Delta \ts M\from T$.
+
+  \begin{itemize}
+    \item Let $x_j\from T_j$ be a variable occurring in $\Delta$.  
+      Then $x_j[N_i/x_i]=N_j$.  
+      Moreover, it is clear that $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts x_j} = \sigma_j$.
+      And we have $\sigma_j\plot_{T_j}^\Gamma N_j$ by hypothesis.
+
+    \item Next, suppose that $x\from\Var$ is a variable occurring in $\Gamma$.
+      Then we have $x[N_i/x_i]=x$, and it is easy to see that we have
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts x} = \deno{\Gamma\ts x}\,.
+        \]
+      Now we have $\deno{\Gamma\ts x};\pr_n = \deno{\Gamma\ts x\gets n}$ and $\deno{\Gamma\ts x};\pr_{\bN} = \deno{\Gamma \ts \oc\bN}$.  
+      From Lemma \ref{LemSoundnessOpto} (in particular, Figures \ref{FigSoundnessOoptoContext} and \ref{FigSoundnessOoptoStorage}), we know that if $s$ is a $\Gamma$-store, then
+      \[
+        \seqdeno{s,\deno{\Gamma\ts x\gets n}} = \seqdeno{\Gamma,s\ts x\gets n} = \seqdeno{\Gamma, (s\vert x\mapsto n)\ts \skipp}\,,
+        \]
+      where we have that $\Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)$, and that
+      \[
+        \seqdeno{s,\deno{\Gamma\ts \oc x}} = \seqdeno{\Gamma,s\ts \oc x} = \seqdeno{\Gamma,s\ts s(x)}\,,
+        \]
+      where we have that $\Gamma,s\ts \oc x \converges s(x),s$.
+
+    \item Next, suppose that $\Gamma,\Delta\ts M\from S\to T$ and $\Gamma,\Delta\ts N\from S$, where we already know that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{S\to T}^\Gamma M[N_i/x_i]
+        \]
+      and that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts N}\plot_S^\Gamma N[N_i/x_i]\,.
+        \]
+      Then it easy to see that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N}
+        \]
+      is given by the composite
+      \small
+      \[
+        \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\mu_{\deno{\Gamma}}\ms\ms\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}) \tensor ((\sigma_i)\semicom\deno{\Gamma,\Delta\ts N})\ms\ms\ms} (\oc\deno S \implies \deno T) \tensor \oc\deno {S} \xrightarrow{\ms\ms\ms\ev\ms\ms\ms} \deno T.
+        \]
+      \normalsize
+      Therefore, by the definition of $\plot_{S\to T}^\Gamma$, it must be the case that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N} \plot_{T}^\Gamma M[N_i/x_i]\,N[N_i/x_i] = (M\,N)[N_i/x_i]\,.
+        \]
+    \item Next, suppose that $\Gamma,\Delta,x\from S \ts M\from T$.  
+      We claim that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta,\lambda x.M} \plot_{S\to T}^\Gamma (\lambda x.M)[N_i/x_i]\,.
+        \]
+      Let $\sigma'\from \oc\deno{\Gamma} \implies \deno S$ be a strategy and let $\Gamma\ts N\from S$ be a term in context such that $\sigma\plot_S^\Gamma N$.  
+      Then, by the inductive hypothesis (with $x$ lying in the `$\Delta$-part', we know that
+      \[
+        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}\plot_T^\Gamma M[N_i/x_i,N'/x]\,.
+        \]
+      Then, since $\Gamma,s\ts (\lambda x.M[N_i/x_i])\,N'\opto \Gamma,s\ts M[N_i/x_i,N'/x]$ for any $\Gamma$-store $s$, by Lemma \ref{LemAdequacyOpto} we know that
+      \[
+        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M} \plot_T^\Gamma ((\lambda x.M)[N_i/x_i])\,N'\,.
+        \]
+      Finally, observe that $(\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}$ is the composite
+      \[
+        \oc\deno{\Gamma} \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n,\sigma'\rangle^\dag} \oc{\deno{\Gamma,\Delta,x}} \xrightarrow{\deno{\Gamma,\Delta,x\from S\ts M}} \deno T\,,
+        \]
+      which can alternatively be written as
+      \begin{mathpar}
+        \oc\deno{\Gamma} \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag} \oc{\deno{\Gamma,\Delta}} \xrightarrow{\mu_{{\deno{\Gamma,\Delta}}}} \oc{\deno{\Gamma,\Delta}}\tensor\oc{\deno{\Gamma,\Delta}}\\ \xrightarrow{\deno{\Gamma,\Delta\ts \lambda x.M} \tensor (\sigma')^\dag} (\oc\deno S\implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\,.
+      \end{mathpar}
+  \end{itemize}
+
+  Now we move on to the structural constants for the datatypes.  
+  We deal with the case of the type $\nat$ (i.e., the terms $n$, $\suc M$, $\pred M$ and $\IfO M\Then N \Else P$), and it should be clear how our ideas translate to the corresponding rules at the types $\com$ and $\bool$ (i.e., $\skipp$, $\true$/$\false$, sequencing and the boolean conditional).
+
+  Before we cover these cases, we make an important observation.  
+  Suppose that $\Gamma,\Delta\ts M,N\from T$, and that
+  \[
+    \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts N}}\,.
+    \]
+  Let $\EE$ be an evaluation context of type $U$ with a hole of type $T$.  
+  Then
+  \[
+    \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \EE[M]})} = \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \EE[N]}}\,.
+    \]
+  We can see this by precomposing both directions of the diagram in Figure \ref{FigSoundnessOpto} (with $\Gamma$ in that diagram standing for $\Gamma,\Delta$) with the composite
+  \[
+    I \xrightarrow{\oc\deno{s}}
+    \oc S_\Gamma \xrightarrow{\cell^\Gamma}
+    \oc\deno{\Gamma} \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag}
+    \oc\deno{\Gamma,\Delta}\,,
+    \]
+  in order to prove that the value of $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts\EE[M]}}$ depends only on the value of $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}$ and $\EE$.
+
+  \begin{itemize}
+    \item Given a numeral $n$ and a $\Gamma$-store $s$, we have $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts n} = \deno{\Gamma\ts n}$ and $\seqdeno{s,\deno{\Gamma\ts n}} = \seqdeno{\Gamma,s\ts n}$, where $\Gamma,s\ts n\converges n,s$.
+
+    \item Suppose $\Gamma,\Delta\ts M\from \nat$, and that we already know that 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{\nat}^\Gamma M[N_i/x_i]\,.
+        \]
+      So for all $\Gamma$-stores $s$, either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \bot_{\bN\sequoid\oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$.
+
+      Now we have 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M};(\suc\tensor\oc\deno{\Gamma})\,;
+        \]
+      since $\suc\from\bN \implies \bN$ is a strict strategy, we know that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \suc M})} = \bot_{\bN\sequoid\oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,s'\ts n};(\suc\tensor\oc\deno{\Gamma}) = \seqdeno{\Gamma,s'\ts n+1}$, and we have $\Gamma,s\ts \suc M[N_i/x_i]\converges n+1$.
+      Therefore, 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} \plot_{\nat}^\Gamma \suc M[N_o/x_i]\,.
+        \]
+
+      A similar argument proves that 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\pred M} \plot_{\nat}^\Gamma \pred M[N_i/x_i]\,.
+        \]
+
+    \item Now we move on to the conditional.  
+      Suppose that we have $\Gamma,\Delta\ts M\from \nat$ and $\Gamma,\Delta\ts N,P\from X$ for some datatype $X$.  
+      Let $s$ be a $\Gamma$-store.  
+      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\oc\deno{\Gamma}\ts \bN}$, then
+      \[
+        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{\oc\deno{\Gamma} \ts X}\,.
+        \]
+      Otherwise, by induction we know that $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}}=\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$ such that $\Gamma,s\ts M[N_i/x_i]\converges n,s'$.
+      Without loss of generality, suppose that $n=0$.  
+      Then we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO 0 \Then N \Else P})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta \ts N})}\,, \\
+      \end{IEEEeqnarray*}
+      where the first equality is by our observation above (since $\IfO - \Then N \Else P$ is an evaluation context), and the second is by the definition of $\IfO$.
+      Then, by induction, this last term is either equal to $\bot_{X\sequoid\deno{\Gamma}}$,or is equal to $\seqdeno{\Gamma,s''\ts u}$ for some $u\in X$ such that $\Gamma,s'\ts N[N_i/x_i]\converges u,s''$.
+      In this second case, we have $\Gamma,s\ts \IfO M[N_i/x_i] \Then N[N_i/x_i] \Else P[N_i/x_i] \converges u,s''$.
+  \end{itemize}
+  Next, we deal with the rules for variables.
+  \begin{itemize}
+    \item Suppose $\Gamma,\Delta\ts V\from\Var$, and suppose we already know that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var}^\Gamma V[N_i/x_i]\,.
+        \]
+      Then by definition we have
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \oc V} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_{\bN} \plot_{\bN}^\Gamma \oc\V[N_i/x_i]\,.
+        \]
+      Suppose $\Gamma,\Delta\ts E\from \nat$, and suppose we know already that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E} \plot_{\bN} E[N_i/x_i]$.  
+      Then, for all $s$, either $\seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E}}=\bot_{\bN \sequoid\oc\deno{\Gamma}}$ -- in which case
+      \[
+        \seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets E}} = \bot_{\bC \sequoid \oc\deno{\Gamma}}
+        \]
+      (since $\assign$ is a strict strategy) -- or it is equal to $\seqdeno{s',n}$ for some $n\in \bN$ such that $\Gamma,s\ts E[N_i/x_i]\converges n,s'$.
+      In the second case, we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V \gets E})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets n}} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)}\,.
+      \end{IEEEeqnarray*}
+      Now we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n\plot_{\com}^\Gamma V[N_i/x_i]\gets n$ by induction, so this composite is either equal to $\bot_{\bC\sequoid\oc\deno\Gamma}$ or it is equal to $\seqdeno{\Gamma,s''\ts \skipp}$ for $s''$ such that $\Gamma,s'\ts V[N_i/x_i]\gets n\converges \skipp,s''$.
+      In this second case, we have $\Gamma,s\ts V[N_i/x_i]\gets E[N_i/x_i]\converges \skipp,s''$.
+
+    \item Suppose that $\Gamma,\Delta\ts W \from \nat \to \com$ and that $\Gamma,\Delta \ts R \from \nat$.
+      We claim that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\mkvar\,W\,R};\pr_n\plot_\com^\Gamma (\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\gets n
+        \]
+      for each $n$ and that 
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN\plot_\nat^\Gamma \oc(\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\,.
+        \]
+
+      For the first of these, let $s$ be a $\Gamma$-store.  
+      We have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_n)} \\
+        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts W\,n})}\,. \\
+      \end{IEEEeqnarray*}
+      By induction, we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts W\,n} \plot_{\com}^\Gamma W[N_i/x_i]\,n$.  
+      Therefore, this last composite is either equal to $\bot_{\bC\sequoid\oc\deno{\Gamma}}$, or it is equal to $\seqdeno{\Gamma,s',\skipp}$ for some $s'$ such that $\Gamma,s\ts W\,n\converges \skipp,s'$.
+      In this second case, we have $\Gamma,s\ts (\mkvar W\,R)\gets n\converges \skipp,s'$.
+
+      For the second, we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN)} \\
+        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts R})}\,.
+      \end{IEEEeqnarray*}
+      By induction, we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts R} \plot_{\nat}^\Gamma R[N_i/x_i]$.  
+      Therefore, this last composite is either equal to $\bot_{\bC\sequoid\oc\deno{\Gamma}}$, or it is equal to $\seqdeno{\Gamma,s',n}$ for some $s',n$ such that $\Gamma,s,R \converges n,s'$.  
+      In this second case, we have $\Gamma,s\ts \oc(\mkvar W\,R) \converges n,s'$.
+
+    \item Suppose that $\Gamma,x\from\Var,\Delta\ts M\from X$, where $X$ is a datatype, and suppose we already know that
+      \[
+        (\sigma_i)\semicom\deno{\Gamma,x\from\Var,\Delta\ts M} \plot_X^{\Gamma,x} M\,,
+        \]
+      where $x$ is considered as belonging to the `$Gamma$-component'.
+      Let $s$ be a $\Gamma$-store -- then we get a $\Gamma,x$-store $(s\vert x\mapsto 0)$.
+      So either $\seqdeno{(s\vert x\mapsto 0),((\sigma_i)\semicom\deno{\Gamma,x,\Delta\ts M})}=\bot_{X\sequoid\oc\deno\Gamma}$, or it is equal to $\seqdeno{\Gamma,x,(s'\vert x\mapsto n),u}$ for some $s',n,u$ such that $\Gamma,(s\vert x\mapsto 0)\ts M[N_i/x_i] \converges u,(s'\vert x\mapsto n)$.
+
+      But by the definition of $\new$, we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{(s\vert x\mapsto 0),((\sigma_i)\semicom\deno{\Gamma,x,\Delta\ts M})};(X\sequoid\oc\pr_\Gamma) \\
+        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \neww\lambda x.M})}\,.
+      \end{IEEEeqnarray*}
+      It follows that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts\neww\lambda x.M})}=\bot_{X\sequoid \oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,x,(s'\vert x\mapsto n),u};(X\sequoid\oc\pr_\Gamma) = \seqdeno{\Gamma,s',u}$ for some $u$ such that $\Gamma,(s\vert x\mapsto 0)\ts M[N_i/x_i]\converges u,(s'\vert x\mapsto n)$.
+      In this case, $\Gamma,s\ts\neww \lambda x.M\converges u,s'$.
+  \end{itemize}
+  It remains to deal with the case of the recursion combinator $\Y_T$.  
+  First recall that if $h\from ((\deno T \to \deno T) \to \deno T) \to (\deno T\to \deno T) \to T$ (where we write $A \to B$ for $\oc A \implies B$) is the morphism corresponding to the $\lambda$-term
+  \[
+    \lambda F^{(T\to T) \to T}.\lambda f^{T\to T}.f(F\,f)\,,
+    \]
+  then $\Y_T$ is constructed as the limit of the chain
+  \[
+    \bot_{(T\to T)\to T} \subset \bot_{(T\to T) \to T};h \subset \bot_{(T\to T)\to T};h;h \subset \cdots\,.
+    \]
+  By Lemma \ref{LemAdequacyLimits}, then, it suffices to show that if $\Gamma,\Delta \ts M\from T \to T$ then $(\sigma_i)\semicom \deno {\Gamma,\Delta\ts M};\left(\bot_{(T\to T)\to T}\right);h^n\plot_{T}^{\Gamma} \Y_T M[N_i/x_i]$ for each $n$.
+
+  We do this by induction on $n$.  
+  Lemma \ref{LemAdequacyBot} takes care of the initial case, and it will therefore suffice to prove that if $\sigma\plot_T^\Gamma \Y_T M$ then $\sigma;h\plot_T^\Gamma \Y_T M$.
+
+  Suppose $T=T_1\to \cdots\to T_n \to X$, where $X$ is a datatype.
+  Fix terms $M_i\from T_i$ and strategies $\tau_i\from \deno{\Gamma}\to \deno{T_i}$ such that $\tau_i\plot_{T_i}^\Gamma M_i$ for each $i$.
+
+  Since $\sigma\plot_T^\Gamma \Y_T M$, we know that $\langle \tau_1,\cdots,\tau_n\rangle;\sigma \plot_X^\Gamma \Y_T M\,M_1\,\cdots\,M_n$.
+  It follows that $\langle \tau_1,\cdots,\tau_n\rangle;\sigma;h \plot_X^\Gamma M(\Y_T M)\,M_1,\cdots\,M_n$.  
+  Then, since
+  \[
+    \Gamma,s,\Y_T M\,M_1,\cdots\,M_n\opto\Gamma,s,M(\Y_T M)\,M_1\,\cdots\,\M_n
+    \]
+  for any $\Gamma$-store $s$, by Lemma \ref{LemAdequacyOpto} we have that
+  \[
+    \langle\tau_1,\cdots,\tau_n\rangle;\sigma;h \plot_X^\Gamma \Y_T M\,M_1,\cdots,M_n\,,
+    \]
+  and therefore that $\sigma;h\plot_X^\Gamma \Y_T M$, since the $M_i,\tau_i$ were arbitrary.
+\end{proof}
+
+This is now enough to prove a \emph{computational adequacy result} for our denotational semantics.
+
+\begin{definition}[Computational Adequacy Result]
+  Suppose we have a programming language $\L$ and a denotational semantics $\deno{-}$ of $\L$ in some category $\C$.  
+  Let $o$ be a ground type of $\L$ and let $\converges$ be some operational predicate on closed terms of $\L$ of type $o$.  
+  Let $\downarrow$ be a predicate on morphisms $1 \to \deno{L}$ in $\C$.  
+  Then a \emph{computational adequacy} result for the semantics is a result that says that for all terms $M\from o$ in $\L$, 
+  \[
+    M\converges \text{ if and only if } \deno{M}\downarrow\,.
+    \]
+\end{definition}
+
+We will prove a computational adequacy result for our semantics of IA, taking $o=\com$.  
+If $M\from\com$ is a term of IA, we say that $M\converges$ if $\blank,()\ts M\converges \skipp,()$.
+If $\sigma\from 1 \implies \bC$ is a strategy, we say that $\sigma\downarrow$ if $\sigma\ne\bot_{\com}$.
+
+\begin{theorem}[Computational Adequacy]
+  Let $M\from\com$ be a closed term of Idealized Algol.
+  Then $M\converges$ if and only if $\deno{M}\ne\bot_{\com}$.
+  \label{TheComputationalAdequacyIA}
+\end{theorem}
+\begin{proof}
+  First suppose that $M\converges$.  
+  Then Proposition \ref{PropSoundness} tells us that $\deno{M} = \deno{\skipp}\ne\bot_{\com}$.
+
+  Conversely, suppose that $\deno{M}\ne\bot_{\com}$.  
+  Lemma \ref{LemAdequacy} tells us that $\deno{M}\plot_{\com} M$.  
+  Since $\deno{M}\ne\bot_{\com}$, the only possibility is that $\blank,()\ts M\converges\skipp,()$.
+\end{proof}
+
+We can then prove an \emph{equational soundness} result.
+First, we recall the definition of \emph{observational equivalence} of terms.
+
+\begin{definition}[Observational Equivalence]
+  Suppose we have a language $\L$, together with a distinguished ground type $o$ and operational predicate $\converges$ as above.  
+  Given two closed terms $M,N\from T$ in $\L$, we say that $M$ and $N$ are \emph{observationally equivalent} if for all contexts $C[-]\from o$ in $\L$ with a hole of type $T$, $C[M]\converges$ if and only if $C[N] \converges$.
+\end{definition}
+
+Next, we create a definition that mirrors this one within the denotational semantics.
+
+\begin{definition}[Intrinsic Equivalence]
+  Suppose we have a language $\L$, together with a denotational semantics $\deno{-}$ in a Cartesian closed category $\C$, a distinguished ground type $o$ and a predicate $\downarrow$ on morphisms $1 \to \deno{o}$ as above.
+
+  Given objects $A,B$ of $\C$, and morphisms $\sigma,\tau\from A \to B$, we say that $\sigma,\tau$ are \emph{intrinisically equivalent}, and write $\sigma\sim\tau$, if for all $\alpha\from (A \to B) \to \deno{o}$, $\Lambda(\sigma);\alpha\downarrow$ if and only if $\Lambda(\tau);\alpha\downarrow$.
+\end{definition}
+
+\begin{definition}[Equational Soundness Result]
+  An \emph{inequational soundness result} for a semantics as above is a result that says that if $M,N\from T$ are such that $\deno{M}\sim\deno{N}$, then $M$ and $N$ are observationally equivalent.
+\end{definition}
+
+\begin{proposition}
+  Any semantics satisfying Computational Adequacy satisfies Inequational Soundness.
+\end{proposition}
+\begin{proof}
+  Suppose that $\deno{M}\sim\deno{N}$.  
+  Let $C[-]\from o$ be a context with a hole of type $T$.
+  Then, since $\C$ is Cartesian closed, the $\beta$-rule is valid in $\C$, and therefore we have
+  \[
+    \deno{C[M]} = 1 \xrightarrow{\deno{M}} \deno{T} \xrightarrow{\deno{x\from T\ts C[x]}} \deno{o}\,,
+    \]
+  and similarly for $C[N]$.  
+  Therefore, taking $\alpha=\deno{x\ts C[x]}$ in the definition of $\sim$, we get that $\deno{C[M]}\downarrow$ if and only if $\deno{C[N]}\downarrow$.  
+  By Computational Adequacy, this means that $C[M]\converges$ if and only if $C[N]\converges$.  
+  Since $C$ was arbitrary, it follows that $M$ and $N$ are observationally equivalent.
+\end{proof}
+
+This proof relies on the fact that the context $C$ gives rise to a morphism $\alpha = \deno{x\ts C[x]}$.  
+To go in the other direction (full abstraction), we need a \emph{definability} result, to allow us to transform a morphism in $\G$ into an Idealized Algol context.  
+This will be the subject of the next section.
+
+\section{Innocent Factorization}
+
+The aim of this section will be to show that any strategy between the denotations of Idealized Algol types may be factorized as the composite of some innocent strategy with the strategy $\cell$.  
+This will reduce the problem to showing that certain innocent strategies are definable, for which we can use known results.
+
+Again, we follow the proof from \cite{SamsonGuyIAActive} very closely.
+
+\begin{proposition}[Innocent Factorization, {\cite[14]{SamsonGuyIAActive}}]
+  Let $A$ be a game, and suppose $A$ has the property that whenever $sb\in P_A$ is an $O$-position and $tbc\in P_A$ is a $P$-position such that $\pv{sb}=\pv{tb}$, then $sbc\in P_A$.
+  Suppose also that $M_A$ is a countable set.
+  Let $\sigma$ be a strategy for $A$.  
+  Then there is an innocent strategy $\hat\sigma$ for $\oc\Varr \implies A$ such that $\sigma$ factorizes as the composite
+  \[
+    I \xrightarrow{\oc 0} \oc\bN \xrightarrow{\cell} \oc\Varr \xrightarrow{\hat\sigma} A\,.
+    \]
+  \label{PropInnocentFactorization}
+\end{proposition}
+\begin{proof}
+  Fix some injection $\L_A \hookrightarrow \bN$, thought of as giving a `code' to each legal sequence, such that the code of the empty sequence is $0$.
+  $\hat{\sigma}$ proceeds as follows.  
+  At each position $sb$ ending with an $O$-move $a$ in $A$, player $P$ first plays the move $q$ in $\oc\Varr$, after which player $O$ returns some natural number $n$.  
+  If $n$ is not the code of a sequence in $P_A$, or if it encodes some sequence $t$ such that $\pv{tb}\ne\pv{s\vert_Ab}$, then player $P$ has no reply.  
+  Otherwise, let $c$ be the reply to $t a$ that player $P$ would have made under $\sigma$.  
+  Player $P$ computes the code $k$ of the sequence $tbc$ and plays $q_k$ in $\oc\Varr$.  
+  After the $O$-reply $a$, player $P$ then plays the move $b$ in $\oc\Varr$.
+
+  Since $tbc\in P_A$ and $\pv{tb}=\pv{tc}$, we have $s\vert_Abc\in P_A$ by our hypothesis on $A$, which implies that this is a valid strategy.
+  We claim that it is innocent.  
+  Moreover, since player $P$'s moves depend only on the number $n$ returned and on the current $P$-view within $A$, this strategy is innocent.
+
+  Lastly, if we compose with $\oc0;\cell$, then we ensure that this number $n$ that is returned is always the code of the current sequence in $A$, and therefore that $\oc 0;\cell;\hat{\sigma}=\sigma$ by the explicit description of the $\cell$ strategy given in Proposition \ref{PropCellComb}.
+\end{proof}
+
+We want to apply this result in the case that $A$ is the denotation of an IA type, so we need to show that for any IA type $T$, the game $\deno T$ satisfies the hypotheses of Proposition \ref{PropInnocentFactorization}.
+In fact, we show something stronger.
+
+\begin{lemma}
+  Let $T$ be a type of Idealized Algol.  
+  Then $P_{\deno T}$ is the set of all sequences in $\L_{\deno T}$ that contain at most a single initial move.
+  \label{LemTypeCharacterization}
+\end{lemma}
+\begin{proof}
+  This is obvious for the dataypes and for $\Var$.  
+  Let $S,T$ be types -- so $\deno{S \to T} = \oc\deno S \implies \deno T$ -- and let $s\in P_{\oc\deno S\implies \deno T}$.  
+  An initial move in $\oc\deno S \implies \deno T$ is an initial move in $\deno T$; by induction, $s\vert_{\deno T}\in P_{\deno T}$ contains at most one initial move, and so $s$ contains at most one initial move.
+
+  Conversely, suppose that $s\in \L_{\oc\deno S \implies \deno T}$ contains at most one initial move.
+  We show by induction on the length of $s$ that $s\in P_{\oc\deno S \implies \deno T}$.  
+  This is obvious if $s=\epsilon$; if $s=ta$ for some $t$, then by induction we have $t\in P_{\oc\deno S \implies \deno T}$, so $t\vert_{\oc\deno S}\in P_{\oc\deno S}$ and $t\vert_{\deno T}\in P_{\deno T}$.
+  We need to show that $ta\in P_{\oc\deno S}$, for which it suffices by induction to show that $ta\vert_{\oc\deno S}$ and $ta\vert_{\deno T}$ are both legal positions, $ta\vert_{\oc\deno S}\vert_n$ has a unique initial move in $\deno S$ for each initial move $n$ of $\deno S$, and $ta\vert_{\deno T}$ has a unique initial move in $\deno T$.
+  Indeed, we can show that they are alternating using the same arguments we used in Proposition \ref{PropComposition}, and they are clearly well-bracketed sequences.  
+  Visibility then follows from Lemma \ref{LemProjectionLemma}, and from Proposition 4.3 from \cite{hoPcf}, which states that if $s$ is a play in $A\implies B$, then $\pv{s}^{A\implies B}\vert_A$ is a subsequence of $\pv{s\vert_A}^A$ and $\pv{s}^{A\implies B}\vert_B$ is a subsequence of $\pv{s\vert_B}^B$.
+  This means that the justifier of the move $a$ must occur within the appropriate $O$- or $P$-view, since we know that $t\vert_{\oc\deno S}$ and $t\vert_{\deno T}$ are both visible sequences.
+\end{proof}
+
+\begin{proposition}
+  Let $T$ be a type of Idealized Algol.  
+  Then $\deno T$ satisfies the hypotheses of Proposition \ref{PropInnocentFactorization}.
+\end{proposition}
+\begin{proof}
+  Suppose that $sb,tbc\in P_{\deno T}$, where $c$ is a $P$-move, are such that $\pv{sb}=\pv{tb}$.  
+  It is clear that $sbc$ is an alternating and visible sequence; moreover, it is well-bracketed, since the most recently unanswered question in $sb$ is the same as in $tb$.  
+  Therefore, $sbc$ is a legal sequence with a unique initial move, and so it is contained in $P_{\deno T}$ by Lemma \ref{LemTypeCharacterization}.
+\end{proof}
+
+\section{Arena-only Semantics}
+
+Before we complete our Full Abstraction result, we take a detour to consider a variation of our game semantics in which we do away with the sets of plays $P_A$.  
+We call this an \emph{arena-only semantics}, since the objects of our category are plain arenas.
+Since the semantics given in \cite{hoPcf} are of this form, and since we want to quote definability results from this work, it makes sense to cast our own work in this form.
+
+\begin{definition}
+  Let $A$ be a game.  
+  We say that $A$ is \emph{full} if $P_A=\L_A$.
+\end{definition}
+
+Let $A$ be a game.  
+Since the underlying arena of $\oc A$ is the same as that of $A$, and since we have $P_A \subset P_{\oc A}$, we have the following result.
+
+\begin{proposition}
+  If $A$ is full, then we have $A=\oc A$.
+\end{proposition}
+
+Note that the definition of the $\oc$ connective, together with Lemma \ref{LemTypeCharacterization}, implies the following.
+
+\begin{proposition}
+  Let $T$ be an Idealized Algol type.  
+  Then $\oc\deno{T}$ is full.
+\end{proposition}
+
+This Proposition on its own does not seem to be much use, since we want to consider the game $\deno T$ without the $\oc$ in front of it.  
+But recall that the `co-Kleisli'-style morphisms in our category, which are strategies for $\oc A \implies B$, may alternatively be regarded as comonoid homomorphisms from the comonoid on $\oc A$ to the comonoid on $\oc B$.
+Thus, if $S,T$ are Idealized Algol types, then the set of morphisms $\oc\deno S \implies \deno T$ in our original category is precisely the same as the set of morphisms $\oc\deno S \implies \oc\deno T$ that are comonoid homomorphisms.
+
+\begin{definition}
+  Let $A$ be a game and let $sa$ be a play in $A$.  
+  Then the \emph{current thread} $\ct{sa}$ of $sa$ is $sa\vert_n$, where $n$ is the unique initial move that hereditarily justifies $a$.
+
+  Let $\sigma$ be a strategy for $A$.
+  We say that $\sigma$ is \emph{single-threaded} if player $P$'s moves only depend on the current thread; i.e., if whenever $sab\in\sigma$, $t\in\sigma$ and $ta\in P_A$ such that $\ct{sa}=\ct{ta}$, then we have $tab\in\sigma$.
+\end{definition}
+
+Note the similarity with the definition of innocence, where the only difference is that we use the $P$-views $\pv{sa}$ and $\pv{ta}$ rather than the current threads $\ct{sa}$ and $\ct{ta}$.
+Since $\pv{s}$ is a subsequence of $\ct{s}$ for any sequence $s$, we get:
+\begin{proposition}
+  Any innocent strategy is single-threaded.
+\end{proposition}
+
+\begin{lemma}[{\cite[3.5.1]{RusssThesis}}]
+  Let $\sigma \from A$ be a single-threaded strategy.  
+  Suppose $s\in \sigma$, and let $I$ be a set of occurrences of initial moves in $s$.  
+  Then $s\vert_I\in\sigma$.
+  \label{LemRuss1}
+\end{lemma}
+\begin{proof}
+  Induction on the length of $s$.
+  Suppose that $sab\in\sigma$.  
+  Since $sab$ is a visible sequence, we know that the justifier of $b$ occurs in $\pv{sa}$, and in particular in $\ct{sa}$.
+  Now $a$ must be hereditarily justified by that initial move that hereditarily justifies $b$; if this initial move is not contained in $I$, then we have $sab\vert_I=s\vert_I\in\sigma$ by induction.  
+  Otherwise, we have $sab\vert_I=s\vert_Iab$.  
+  Then, since we have $\ct{sa}=\ct{s\vert_I a}$, we must have $s\vert_Iab\in\sigma$ by single-threadedness of $\sigma$.
+\end{proof}
+
+We now link the combinatorial definition of single-threadedness to a definition about comonoid homomorphisms.
+
+\begin{proposition}
+  Let $A,B$ be well-opened games.
+  Given a strategy $\sigma\from \oc A \implies \oc B$, $\sigma$ is single-threaded if and only if it is a comonoid homomorphism with respect to the natural comonoid structures on $\oc A$ and $\oc B$; i.e., it makes the following diagrams commute.
+  \begin{mathpar}
+    \begin{tikzcd}
+      \oc A \arrow[r, "\sigma"] \arrow[d, "\mu_A"']
+        & \oc B \arrow[d, "\mu_B"] \\
+      \oc A \tensor \oc A \arrow[r, "\sigma \tensor \sigma"]
+        & \oc B \tensor \oc B
+    \end{tikzcd}
+    \and
+    \begin{tikzcd}
+      \oc A \arrow[r, "\sigma"] \arrow[d, "()"']
+        & \oc B \arrow[dl, "()"] \\
+      I
+        &
+    \end{tikzcd}
+  \end{mathpar}
+\end{proposition}
+\begin{proof}
+  Of course, the second diagram is automatically satisfied by any strategy $\sigma$, since $I$ is a terminal object.
+
+  Since $A,B$ are well-opened, $\oc A$ and $\oc B$ are the cofree commutative comonoids on $A,B$, and therefore the comonoid homomorphisms $\sigma\from \oc A \implies \oc B$ are precisely the strategies of the form $\tau^\dag$, where $\tau\from\oc A \implies B$ is an arbitrary morphism.
+  It is easy to check that such a strategy is single-threaded; indeed, the plays of $\tau^\dag$ are precisely those plays $s\in P_{\oc A \implies \oc B}$ such that $s\vert_n\in\tau$ for any occurrence $n$ of an initial move in $s$.
+
+  Conversely, let $\sigma\from \oc A \implies \oc B$ be single-threaded.  
+  Let $\tau=\sigma\cap P_{\oc A \implies B}$ -- so $\tau$ consists of all sequences in $\sigma$ that have at most one initial move.  
+  Then $\tau$ is clearly a strategy, since it is a prefix-closed subset of $\sigma$.
+  We claim that $\sigma=\tau^\dag$.  
+  Indeed, suppose that $s\in\sigma$.  
+  ket $n$ be an occurrence of an initial move in $s$.  
+  Then, by Lemma \ref{LemRuss1}, $s\vert_n\in\sigma$ and has a unique initial move, and is therefore contained in $\tau$.  
+  Therefore, $\sigma=\tau^\dag$.
+\end{proof}
+
+Now consider the category whose objects are arenas and where the morphisms from $A$ to $B$ are single-threaded strategies for $A\implies B$, where we identify $A$ and $B$ with their corresponding full games.
+Then, if $T$ is any Idealized Algol type, there is some corresponding arena such that the full game on that arena is isomorphic to $\oc\deno T$.  
+We will call this arena $\deno T$ as well, relying on context to distinguish them.
+This means that our semantics of Idealized Algol lives within the new category, since a single-threaded strategy for $\deno S \to \deno T$ is the same thing as a strategy for $\oc \deno S \implies \deno T$ in the original semantics.
+
+This semantics is much closer to the game semantics of PCF developed by Hyland and Ong in \cite{hoPcf}; the difference there is that they use innocent rather than single-threaded strategies.
+
+Note that it is impossible to define the tensor product of games, let alone the sequoid, in the arena-only semantics, so our Computational Adequacy proof would not have worked had we adopted this approach from the start.
+
+\section{Full Abstraction}
+
+We now quote a definability result from \cite{hoPcf}.
+
+\begin{theorem}[{\cite[7.1]{hoPcf}}]
+  Let $T$ be a PCF type, and let $\sigma$ be a compact innocent strategy for $\deno T$ (within the arena-only semantics).  
+  Then there is some closed PCF term $M\from T$ such that $\deno M=\sigma$.
+  \label{ThePcfDefinability}
+\end{theorem}
+
+Here, PCF is the sub-language of PCF generated by the types $\nat$ and $\bool$, together with their structural constants.  
+We will take it as read that this result may be extended to the types $\com$ and $\Varr$, so that we can say that if $T$ is an Idealized Algol type, then any compact innocent strategy for $\deno T$ is the denotation of some IA term.
+Then our factorization result (Proposition \ref{PropInnocentFactorization}) gives us the following definability result.
+
+\begin{proposition}
+  Let $T$ be an Idealized Algol type, and let $\sigma\from \deno T$ be a compact strategy.
+  Then there is some closed IA term $M\from T$ such that $\deno M=\sigma$.
+  \label{PropIaDefinability}
+\end{proposition}
+\begin{proof}
+  We work in the arena-only semantics so that we can apply Theorem \ref{ThePcfDefinability}.  
+  By Proposition \ref{PropInnocentFactorization}, we know that $\sigma=\oc 0;\cell;\hat{\sigma}$ for some innocent strategy $\hat\sigma \from \Varr \to \deno T$.
+  By looking at the proof of Proposition \ref{PropInnocentFactorization}, we can see that $\hat\sigma$ is compact if $\sigma$ is.
+  Then, by Theorem \ref{ThePcfDefinability}, we know that there is some IA term $\lambda x.M\from \Var \to T$ such that $\deno{\lambda x.M}=\hat\sigma$.  
+  It follows that $\sigma$ is the denotation of the term $\new(\lambda x.M)\from T$.
+\end{proof}
+
+\begin{definition}[Full Abstraction result]
+  A \emph{full abstraction result} encompasses both an equational soundness result and its converse, asserting that two programs are observationally equivalent if and only if their denotations are intrinsically equivalent.
+\end{definition}
+
+\begin{theorem}[Full Abstraction]
+  Let $M,N\from T$ be closed terms of Idealized Algol.  
+  Then $M$ and $N$ are observationally equivalent if and only if $\deno M\sim\deno N$.
+\end{theorem}
+\begin{proof}
+  We have already proved that our semantics is computationally adequate, and therefore that the reverse direction (equational soundness) holds.  
+  Now suppose instead that $\deno M\not\sim\deno N$.
+  Without loss of generality, suppose there is $\alpha\from \deno T\to \bC$ such that $\deno{M}^\dag;\alpha\ne\bot_{\bC}$ and $\deno{N}^\dag;\alpha=\bot_{\bC}$.
+
+  Since $\deno{M}^\dag$ is the supremum of all its compact sub-strategies, if $\deno{M}^\dag;\alpha'=\bot_{\bC}$ for all compact $\alpha'\subset \alpha$, then $\deno{M}^\dag;\alpha=\bot_{\bC}$ by continuity of composition.
+  Therefore, there is some compact $\alpha'\subset\alpha$ such that $\deno M^\dag;\alpha\ne\bot_{\bC}$; moreover, we have that $\deno{N}^\dag;\alpha'=\bot_{\bC}$ by monotonicity of composition.
+
+  Then $\alpha'$ is the denotation of some term $P\from T \to \com$, and we have $P\,M\converges$ and $P\,N\not\converges$ by Computational Adequacy.  
+  Therefore, $M$ and $N$ are not observationally equivalent.
+\end{proof}
+
+\section{The Intrinsic Equivalence Relation}
+
+We conclude by giving a more concrete description of the intrinsic equivalence relation on strategies.
+
+\begin{definition}
+  We say that a justified sequence $s$ is \emph{complete} if every question move $q$ occurring in $s$ has some answer move $a$ justified by $q$.
+\end{definition}
+
+\begin{proposition}[{\cite[25]{SamsonGuyIAActive}}]
+  Let $\sigma,\tau\from \oc A \implies B$ be strategies, where $A,B$ are well-opened games.  
+  Then $\sigma\sim\tau$ if and only if $\sigma$ and $\tau$ contain the same complete plays.
+\end{proposition}
+\begin{proof}
+  Suppose first that $\sigma$ and $\tau$ do not contain the same complete plays.  
+  So, without loss of generality, there is some complete $s\in\sigma\setminus\tau$.
+  Then we may define a strategy $\alpha \from \oc(\oc A \implies B) \implies \bC$ that behaves as follows.  
+  After the opening move $q$ in $\bC$, player $P$ plays precisely those moves in $\oc A \implies B$ that make up the sequence $s$.  
+  If player $O$ deviates from the sequence $s$ at any point, then player $P$ has no response under $\alpha$; if player $P$ succeeds in building up the entire sequence $s$, then she finishes by playing $a$ in $\bC$.
+  Note that $\alpha$ is not innocent in general.
+  It is clear then that $\sigma^\dag;\alpha=\skipp$ and $\tau^\dag;\alpha=\bot_{\bC}$.
+
+  Conversely, suppose that $\sigma\not\sim\tau$.  
+  Then, without loss of generality, there is some $\alpha \from \oc(\oc A\implies B) \implies \bC$ such that $\sigma^\dag;\alpha=\skipp$ and $\tau^\dag;\alpha=\bot_{\bC}$.  
+  Then we have some $\s\in\sigma^\dag\|\alpha$ such that $\s\vert_{\bC}=qa$, and $\s\vert_{\oc A \implies B}$ decomposes into `threads' which are plays of $\oc A \implies B$, one for each initial move occurring in that sequence.
+  By the well bracketing condition, every one of these threads is itself a complete play in $\oc A \implies B$.  
+  Every one of these sequences is contained in $\sigma$; if they were all contained in $\tau$, then we would have $\s\in\\tau^\dag\|\alpha$, which would be a contradiction, so we end up with a complete sequence contained in $\sigma\setminus\tau$.
+\end{proof}
 

### 2019-04-16 Thesis/pmonads.tex
Nightly commit.
Finished chapter.

@@
 \section{Parametric monads}
+\label{ChapParametricMonads}
 
@@
 \begin{remark}
-  This subtlety with probability spaces is not present in the case of the nonempty powerset functor, which is why we it makes sense to model plain nondeterminism with a Kleisli category, as we did in Section \ref{SecMonads}.
+  This subtlety with probability spaces is not present in the case of the nonempty powerset functor, which is why we it makes sense to model plain nondeterminism with a Kleisli category, as we did in Chapter \ref{ChapMonads}.
 \end{remark}

### 2019-04-16 Thesis/thesis.tex
Nightly commit.
Finished chapter.

@@
 
-\section{Monads and Kleisli categories}
-\label{SecMonads}
-
-\subsection{Monads}
+\tableofcontents
+\newpage
+
+\chapter{Monads and Kleisli categories}
+\label{ChapMonads}
+
+\section{Monads}
 
@@
   \end{mathpar}
-  We will see in the next section that every monad is induced by an adjunction in this way.
+  We will see in the next chapter that every monad is induced by an adjunction in this way.
 
@@
 
-\subsection{Kleisli Categories}
+\section{Kleisli Categories}
 
@@
 
-\subsection{Denotational Semantics}
-
-From now till the end of the chapter, we fix an (order-enriched) Cartesian closed category $\G$ that admits a denotational semantics of Idealized Algol satisfying Computational Adequacy and in which every compact element is definable.
+\section{Denotational Semantics}
+
+Having given an overview of the general theory of monads and Kleisli categories, we now examine the relationship between Kleisli categories and Full Abstraction.
+From now till the end of the chapter, we fix an base Cartesian closed category $\G$ that admits a denotational semantics of Idealized Algol satisfying Computational Adequacy.
+In addition, we require that $\G$ can be interpreted as being enriched in directed-complete partial orders, in such a way that any compact morphism between the denotation of IA types is the denotation of some IA term.
 The prototypical example, of course, will be the category of games and visible strategies, but we will not exploit any properties of this model beyond the ones we have already mentioned, mentioning it only in examples where appropriate.
+
+In addition, we will specialize to reader monads.  
+The rationale behind this is twofold: firstly, we do not wish to assume too much about the underlying category $\G$ beyond the fact that it gives us a good model of Idealized Algol.  
+Secondly, in order to get a compositional semantics for the $\lambda$-calculus, it is important that the Kleisli categories we consider are themselves Cartesian closed.
 
@@
 
-\subsection{Operational Semantics}
+\section{Operational Semantics}
 
@@
 
-\subsection{Soundness}
+\section{Soundness}
 \label{SecSoundness}
@@
   Let $n$ be a natural number.  
-  We define terms $\test_n\from \nat \to \com$ inductively by
+  We inductively define terms $\test_n\from \nat \to \com$ by
   \begin{mathpar}
@@
   We can prove this using the following derivation tree.
-  \tiny
   \[
@@
     \]
-  \normalsize
 \end{proof}
@@
 
-\subsection{Computational Adequacy}
+\section{Computational Adequacy}
 
@@
 
-\subsection{Full abstraction}
+\section{Full Abstraction}
 
@@
 
-\subsection{Comparison with Ghica's slot games}
+\section{Comparison with Ghica's slot games}
 
@@
 
-\subsection{Alternative reduction rules - may testing}
+\section{Alternative Reduction Rules - May Testing}
 
@@
 
-\subsection{Alternative reduction rules - must testing}
+\section{Alternative Reduction Rules - Must Testing}
 
@@
 
-\subsection{Full Abstraction for Nondeterminism and Must Testing}
+\section{Full Abstraction for Nondeterminism Under Must Testing}
 
@@
 
-\subsection{The intrinsic equivalence relation in $\G_X$}
-
-We conclude this section by examining the intrinsic equivalence relation in $\G_X$.
+\section{The Intrinsic Equivalence Relation}
+
+We conclude this chapter by examining the intrinsic equivalence relation in $\G_X$.
 

### 2019-04-27 Thesis/games.tex
Monthly commit.

@@
 \begin{definition}[Equational Soundness Result]
-  An \emph{inequational soundness result} for a semantics as above is a result that says that if $M,N\from T$ are such that $\deno{M}\sim\deno{N}$, then $M$ and $N$ are observationally equivalent.
+  An \emph{equational soundness result} for a semantics as above is a result that says that if $M,N\from T$ are such that $\deno{M}\sim\deno{N}$, then $M$ and $N$ are observationally equivalent.
 \end{definition}
@@
 \begin{proposition}
-  Any semantics satisfying Computational Adequacy satisfies Inequational Soundness.
+  Any semantics satisfying Computational Adequacy satisfies Equational Soundness.
+  \label{PropEquationalSoundness}
 \end{proposition}

### 2019-04-27 Thesis/pmonads.tex
Monthly commit.

@@
-\documentclass{article}
+\documentclass{report}[11pt]
 
 \input{../common/preamble}
+\usepackage{lua-visual-debug}
 \begin{document}
-\section{Parametric monads}
+\chapter{Parametric monads}
 \label{ChapParametricMonads}
@@
 
-\subsection{The \Mellies category}
+\section{The \Mellies category}
 
@@
 
-\subsection{The category $\C/\X$}
+\section{The category $\C/\X$}
 
@@
 
-\subsection{Lax $2$-colimits}
-
-In the previous section, we approached the category $\C/\X$ via the \Mellies category.  
-In this section, we will show that $\C/\X$ has important properties in its own right: namely that it is a certain lax $2$-colimit in $\Cat$.  
-We will briefly return to the \Mellies category in Section \ref{SecPromonads}, when we will show why it is a natural idea to consider an $[\X,\Set]$-enriched category.
+\section{Lax $2$-colimits}
+
+In the previous chapter, we approached the category $\C/\X$ via the \Mellies category.  
+In this chapter, we will show that $\C/\X$ has important properties in its own right: namely that it is a certain lax $2$-colimit in $\Cat$.  
+We will briefly return to the \Mellies category in chapter \ref{SecPromonads}, when we will show why it is a natural idea to consider an $[\X,\Set]$-enriched category.
 
@@
   Let $\C,\D$ be bicategories.  
-  Then a \emph{lax functor} $F\from\C \to \D$ is given by
+  A \emph{lax functor} $F\from\C \to \D$ is given by
   \begin{itemize}
@@
 
-\subsection{Lax natural transformations and functoriality of lax colimits}
+\section{Lax natural transformations and functoriality of lax colimits}
 
@@
 
-\subsection{Lax $2$-colimits in $\Cat$}
+\section{Lax $2$-colimits in $\Cat$}
 
@@
 
-\subsection{Examples of lax $2$-colimits in $\Cat$}
+\section{Examples of lax $2$-colimits in $\Cat$}
 
@@
 
-This is significant, because it tells us that the category $\C/\X$ always satisfies a `factorization result' akin to those in \cite{SamsonGuyIAActive} and \cite{mcCHFiniteND}: if $f \from a \to b$ is a morphism in $\C/\X$, given by some morphism $\tilde{f}\from a \to x.b$ in $\C$, then we may write $f$ as the composite
+This is significant, because it tells us that the category $\C/\X$ always satisfies a `factorization result' akin to those in \cite{SamsonGuyIAActive} (our Proposition \ref{PropInnocentFactorization}) and \cite{mcCHFiniteND}: if $f \from a \to b$ is a morphism in $\C/\X$, given by some morphism $\tilde{f}\from a \to x.b$ in $\C$, then we may write $f$ as the composite
 \[
@@
 
-\subsection{Finite products distribute over lax colimits in $\Cat$}
+\section{Finite products distribute over lax colimits in $\Cat$}
 
@@
 
-\subsection{Monoidal structure of $\C/\X$}
+\section{Monoidal structure of $\C/\X$}
 
@@
 
-\subsection{Symmetric monoidal structure of $\C/\X$}
+\section{Symmetric monoidal structure of $\C/\X$}
 
@@
 
-\subsection{Symmetric monoidal closed structure of $\C/\X$}
+\section{Monoidal closed structure of $\C/\X$}
 
@@
 
-\subsection{Cartesianness of the monoidal structure}
+\section{Cartesianness of the monoidal structure}
 
 Suppose that a symmetric monoidal category $\X$ acts via a symmetric monoidal action on a Cartesian category $\C$.  
-In this section we will consider what properties of the action we need in order to ensure that the induced monoidal structure on $\C/\X$ is Cartesian.
-
-Since $\C$ is Cartesian, the diagonal map in $\C$ gives every object a natural comonoid structure:
-\[
-  a \xrightarrow{\Delta_a} a \times a\,.
-  \]
+In this chapter we will consider what properties of the action we need in order to ensure that the induced monoidal structure on $\C/\X$ is Cartesian.
+
+Since $\C$ is Cartesian, the diagonal and terminal maps in $\C$ gives every object a natural comonoid structure:
+\begin{mathpar}
+  a \xrightarrow{\Delta_a} a \times a
+  \and
+  a \xrightarrow{()} 1\,.
+\end{mathpar}
 Since the tensor product of objects in $\C/\X$ is given by the same object as in $\C$, we can lift this comonoid structure through the functor $J$ to give us a natural comonoid structure on each object of $\C/\X$:
-\[
-  a \xrightarrow{J\Delta_a} a \tensor a\,.
-  \]
-We use the symbol $\tensor$ rather than $\times$ in $\C/\X$, since this is not necessarily a category-theoretic product.
-
-If every morphism $f\from a \to b$ in $\C/\X$ is a comonoid homomorphism with respect to this comonoid structure; i.e., if it makes the diagram
-\[
+\begin{mathpar}
+  a \xrightarrow{J\Delta_a} a \tensor a
+  \and
+  a \xrightarrow{J()} I\,.
+\end{mathpar}
+We use the symbols $\tensor$ and $I$ rather than $\times$ and $1$ in $\C/\X$, since this tensor product is not necessarily Cartesian.
+
+If every morphism $f\from a \to b$ in $\C/\X$ is a comonoid homomorphism with respect to this comonoid structure; i.e., if it makes the diagrams
+\begin{mathpar}
   \begin{tikzcd}
@@
   \end{tikzcd}
-  \]
+  \and
+  \begin{tikzcd}
+    a \arrow[r, "f"] \arrow[d, "J()"']
+      & b \arrow[dl, "J()"] \\
+    I
+  \end{tikzcd}
+\end{mathpar}
 commute, then we may identify $\C/\X$ with a full subcategory of its own category of comonoids, closed under tensor product.  
@@
 Firstly, since $\C$ itself is Cartesian, every morphism in $\C$ is a comonoid homomorphism with respect to the diagonal, and it follows that every morphism of the form $Jf \from a \to b$ (where $f\from a \to b$ is a morphism in $\C$) is a comonoid homomorphism in $\C/\X$.
-Since every morphism in $\C/\X$ may be written as the composite of a morphism of the form $Jf$ with a morphism of the form $\phi_{x,b}$, it will suffice to show that the morphisms of the form $\phi_{x,a}$ are comonoid homomorphisms in $\C/\X$; i.e., that they make the following diagram commute.
-\[
+Since every morphism in $\C/\X$ may be written as the composite of a morphism of the form $Jf$ with a morphism of the form $\phi_{x,b}$, it will suffice to show that the morphisms of the form $\phi_{x,a}$ are comonoid homomorphisms in $\C/\X$; i.e., that they make the following diagrams commute.
+\begin{mathpar}
   \begin{tikzcd}[column sep=40pt]
@@
   \end{tikzcd}
-  \]
-Let us compute the two arms of this square directly in $\C$.  
+  \and
+  \begin{tikzcd}
+    x.a \arrow[r, "{\phi_{x,a}}"] \arrow[d, "J()"']
+      & a \arrow[dl, "J()"] \\
+    I
+  \end{tikzcd}
+\end{mathpar}
+Let us compute the two arms of the first square directly in $\C$.  
 The composite along the top right is given in $\C$ by the morphism
@@
   \]
-Then a sufficient condition for these two morphisms to be equal in $\C/\X$, and therefore for the category $\C/\X$ to be Cartesian, is that for every object $x$ of $\X$ there should be a morphism $f \from x \to x\tensor x$ that makes the following diagram commute.
+Then a sufficient condition for these two morphisms to be equal in $\C/\X$ is that for every object $x$ of $\X$ there should be a morphism $f \from x \to x\tensor x$ that makes the following diagram commute.
 \[
@@
   \]
-If $\X$ itself is Cartesian, then we have a natural choice of morphism $x \to x \times x$, but choosing $f$ to be the diagonal map does not automatically make the diagram above commute.  
+Similarly, we can calculate the two arms of the second diagram directly in $\C$.  
+The downwards arrow $J()$ is given by the composite
+\[
+  x.a \xrightarrow{()} 1 \xrightarrow{e_1} I.1\,,
+  \]
+while the composite $\phi_{x,a};J()$ is given by the composite
+\[
+  x.a \xrightarrow{x.()} x.1\,.
+  \]
+Thus, a sufficient condition for these two morphisms to be equal in $\C/\X$ is that for every object $x$ of $\X$ there should be a morphism $f_0 \from x \to I$ that makes the following diagram commute.
+\[
+  \begin{tikzcd}
+    x.a \arrow[d, "()"] \arrow[dr, "f_0.()"']
+      & \\
+    1 \arrow[r, "e"]
+      & I.1
+  \end{tikzcd}
+  \]
+
+If $\X$ itself is Cartesian, then we have a natural choice of morphisms $x \to x \times x$ and $x \to 1$, but choosing $f$ to be the diagonal map and $g$ to be the terminal map does not automatically make the diagram above commute.
 For example, the Cartesian product is not the category-theoretic product in the category of sets and relations, even though this category is the Kleisli category for the symmetric monoidal monad $\powerset \from \Set \to \Set$, and may be identified with the category $\Set/1$, where $1$ and $\Set$ are both Cartesian.
@@
 
-An alternative sufficient condition for $\C/\X$ to be Cartesian is for the morphism mediating between the two arms of the square to go in the other direction.  
-In this case, we require that for each object $x$ of $\X$ there should be a morphism $g \from x\tensor x \to x$ that makes the following diagram commute.
-\[
+An alternative sufficient condition for $\C/\X$ to be Cartesian is for the morphisms mediating between the two arms of the squares to go in the other direction.  
+In this case, we require that for each object $x$ of $\X$ there should be morphisms $g \from x\tensor x \to x$ and $g_0\from I \to x$ that make the following diagram commute.
+\begin{mathpar}
   \begin{tikzcd}
@@
   \end{tikzcd}
-  \]
-This will be particularly useful for reader actions.  
+  \and
+  \begin{tikzcd}
+    x.a \arrow[r, "x.()"] \arrow[d, "()"']
+      & x.1 \\
+    1 \arrow[r, "e"]
+      & I.1 \arrow[u, "g_0.1"']
+  \end{tikzcd}
+\end{mathpar}
+This will be particularly useful for reader actions, where an oplax monoidal functor $\X\to \C$ gives rise to an action of $\oppcat \X$ on $\C$.  
 Indeed, suppose that $j\from \X \to \C$ is an oplax symmetric monoidal functor between symmetric monoidal categories, where $\C$ is Cartesian closed.  
 The functor $j$ induces a reader action of $\oppcat\X$ on $\C$ (i.e., $x.a = jx \to a$), and we want the category $\C/\oppcat\X$ to be Cartesian.  
-For this, it will be sufficient to find, for each object $x$ of $\X$, a morphism $f \from x \to x\tensor x$ such that the following diagram commutes.
-\[
+For this, it will be sufficient to find, for each object $x$ of $\X$, morphisms $f \from x \to x\tensor x$ and $f_0 \from x \to I$ such that the following diagrams commute.
+\begin{mathpar}
   \begin{tikzcd}
@@
   \end{tikzcd}
-  \]
-For this to commute, it is sufficient that $jf$ should be equal to the following composite.
-\[
-  jx \xrightarrow{\Delta_{jx}}
-  jx \times jx \xrightarrow{m^j_{x,x}}
-  j(x \tensor x)\,.
-  \]
+  \and
+  \begin{tikzcd}
+    jx \to a \arrow[rr, "jx \to ()"] \arrow[d, "()"']
+      &
+        & jx \to 1 \\
+    1 \arrow[r]
+      & 1 \to 1 \arrow[r, "e^j \to 1"]
+        & jI \to 1 \arrow[u, "jf_0 \to 1"']
+  \end{tikzcd}
+\end{mathpar}
+For these to commute, it is sufficient that the composite
+\[
+  jx \xrightarrow{jf} j(x \tensor x) \xrightarrow{m^j_{x,x}} jx \times jx
+  \]
+should be equal to the diagonal on $jx$, and that the composite
+\[
+  jx \xrightarrow{jf_0} jI \xrightarrow{e^j} 1
+  \]
+should be equal to the terminal morphism $jx \to 1$.  
+Of course, this second condition is automatically satisfied by the definition of a terminal object, so all we require is that some morphism $f_0 \from x \to I$ should exist.
+
 We have proved:
@@
 
-  Suppose that for every object $x$ of $\X$, there is a morphism $f \from x \to x\tensor x$ in $\X$ such that $jf=\Delta_{jx};m^j_{x,x}$.  
+  Suppose that for every object $x$ of $\X$, there are morphisms $f \from x \to x\tensor x$ and $f_0 \from x \to I$ in $\X$ such that $jf;m^j_{x,x}=\Delta_{jx}$.
   Then $\C/\oppcat \X$ is Cartesian closed.
@@
 
-In the next section, we will investigate a class of reader actions, and give a more concrete property for the category $\C/\oppcat\X$ to be Cartesian closed.
-
-\section{Reader actions on $\Set$}
-
-\subsection{Colimits of actions are monoidal functors}
+In the next chapter, we will investigate a class of reader actions, and give a more concrete property for the category $\C/\oppcat\X$ to be Cartesian closed.
+
+\chapter{Reader actions on $\Set$}
+
+\section{Colimits of actions are monoidal functors}
 
@@
               \& \\
-        \colim_{t,z\from \X}\limits t.(a \tensor b) \tensor z.c \arrow[d, "{\Colim m_{t,z,a\tensor b,c}}"']
+        \colim_{t,z\from \X}\limits t.(a \tensor b) \tensor z.c \arrow[ddr, "{\Colim m_{t,z,a\tensor b,c}}" description, to=L.west, bend right=30]
           \& \colim_{x,y,z \from \X}\limits (x\tensor y).(a \tensor b) \tensor z.c \arrow[d, "{\Colim m_{x\tensor y,z,a\tensor b,c}}"'] \arrow[l, hookrightarrow]
             \& \colim_{x,y,z \from \X}\limits x.a \tensor (y\tensor z).(b\tensor c) \arrow[d, "{\Colim m_{x,y\tensor z,a,b\tensor c}}"] \arrow[r, hookrightarrow]
-              \& \colim_{x,t\from \X}\limits x.a \tensor t.(b\tensor c) \arrow[d, "{\Colim m_{x,t,a,b\tensor c}}"] \\
-        \colim_{t,z\from \X}\limits (t\tensor z).((a \tensor b)\tensor c) \arrow[d, hookrightarrow]
-          \& \colim_{x,y,z\from\X}\limits ((x\tensor y) \tensor z).((a \tensor b) \tensor c) \arrow[r, "\Colim\assoc.\assoc" yshift=5pt] \arrow[l, hookrightarrow]
-            \& \colim_{x,y,z\from\X}\limits (x \tensor (y\tensor z)).(a \tensor (b \tensor c)) \arrow[r, hookrightarrow]
-              \& \colim_{x,t\from \X}\limits (x \tensor t).(a \tensor (b \tensor c)) \arrow[d, hookrightarrow] \\
-        \colim_{u\from \X}\limits u.((a\tensor b) \tensor c) \arrow[rrr, "\Colim u.\assoc"]
+              \& \colim_{x,t\from \X}\limits x.a \tensor t.(b\tensor c) \arrow[ddl, "{\Colim m_{x,t,a,b\tensor c}}" description, to=R.east, bend left=30] \\
+        %
+          \& \colim_{x,y,z\from\X}\limits ((x\tensor y) \tensor z).((a \tensor b) \tensor c) \arrow[r, "\Colim\assoc.\assoc" yshift=5pt] \arrow[d, hookrightarrow]
+            \& \colim_{x,y,z\from\X}\limits (x \tensor (y\tensor z)).(a \tensor (b \tensor c)) \arrow[d, hookrightarrow]
+              \& \\
+        %
+          \& |[alias=L]| \colim_{t,z\from \X}\limits (t\tensor z).((a \tensor b)\tensor c) \arrow[d, hookrightarrow]
+            \& |[alias=R]| \colim_{x,t\from \X}\limits (x \tensor t).(a \tensor (b \tensor c)) \arrow[d, hookrightarrow]
+              \& \\
+        %
+          \& \colim_{u\from \X}\limits u.((a\tensor b) \tensor c) \arrow[r, "\Colim u.\assoc"]
+            \& \colim_{u\from \X}\limits u.(a \tensor (b\tensor c))
               \&
-            \&
-              \& \colim_{u\from \X}\limits u.(a \tensor (b\tensor c))
       \end{tikzcd}
@@
 
-\subsection{Reader actions on $\Set$ vs change of base}
+\section{Reader actions on $\Set$ vs change of base}
 
@@
     &\int^{y,z}[jy,[A,B]] \times [jz,[B,C]] \times \X(y\tensor z,x) \\
-    \xrightarrow{\makebox[146pt]{$\int^{y,z} m_{jy,jz,[A,B],[B,C]}\times \X(y\tensor z,x)$}} &
+    \xrightarrow{\makebox[144pt]{$\int^{y,z} m_{jy,jz,[A,B],[B,C]}\times \X(y\tensor z,x)$}} &
     \int^{y,z}[jy \times jz,[A,B]\times [B,C]] \times \X(y,\tensor z,x) \\
-    \xrightarrow{\makebox[146pt]{$\int^{y,z} [m^j_{y,z}, ;] \times \X(y\tensor z,x)$}} &
+    \xrightarrow{\makebox[144pt]{$\int^{y,z} [m^j_{y,z}, ;] \times \X(y\tensor z,x)$}} &
     \int^{y,z}[j(y \tensor z),[A,C]]\times \X(y\tensor z,x) \\
@@
 
-\subsection{From monoidal endofunctors on $\Set$ to reader actions}
+\section{From monoidal endofunctors to reader actions}
 
@@
 
-Now recall that in order to apply the second part of Theorem \ref{TheCartesianClosedCx}, and deduce that $\Set/\oppcat\X$ is Cartesian closed, we must prove that for every object $x$ of $\X$, there is a morphism $f \from x \to x \tensor x$ such that $jf = \Delta_{jx};m^j_x$.
-This is particularly useful in our case, since the functor $\X \to \Set$ is faithful.
+Now recall that in order to apply the second part of Theorem \ref{TheCartesianClosedCx}, and deduce that $\Set/\oppcat\X$ is Cartesian closed, we must prove that for every object $x$ of $\X$, there are morphisms $f \from x \to x \tensor x$ and $f_0 \from x \to I$ such that $jf = \Delta_{jx};m^j_x$ and $jf_0 = ();e^j$.
+This is particularly useful in our case, since the functor $\X \to \Set$ is faithful, making $\X$ into a concrete category.  
+Then the morphisms between two objects in $\X$ may be thought of as `structure-preserving functions' between the corresponding sets.  
+The criterion from Theorem \ref{TheCartesianClosedCx} then says that the composites $\Delta_{jx};m^j_x$ and $();e^j$ are structure-preserving.
 
@@
 \[
-  (A,p) \to (A \times A, m^F_{A,A}(p,p))\,;
+  (A,p) \to (A \times A, m^F_{A,A}(p,p))\,\text{--}
   \]
@@
 \[
-  F(\Delta_A)(p) = m^F_{A,A}(p,p)\,.
+  F(\Delta_A)(p) = m^F_{A,A}(p,p)\,\text{--}
+  \]
+and the function $()$ must define a morphism
+\[
+  (A,p) \to (1, e^F)\,\text{--}
+  \]
+i.e., we must have
+\[
+  F(())(p) = e^F\,.
   \]
@@
   In the language of probability, the two copies of the random variable $V$ are \emph{dependent random variables}, so the probability of obtaining the reading $(a,a)$ from $\langle V,V\rangle$ is the same as the probability of obtaining the reading $v$ from $V$.
-  Therefore, the category $\Set/\oppcat{\Rv_\Omega}$ will be Cartesian closed.
+  Since the terminal morphism from $(A,V)$ to $(1,())$ is also probability preserving, the category $\Set/\oppcat{\Rv_\Omega}$ will be Cartesian closed.
 \end{example}
 
-\subsection{Actions of categories with terminal objects}
+\section{Actions of categories with terminal objects}
 
@@
 At least, it does if the $\sigma$-algebra $\F$ on $\Omega$ is discrete.  
-But in general, the identity function
+But if $\Omega$ is not itself a discrete probability space, then the function
 \[
@@
   \]
-is not measurable (indeed, it is measurable if and only if $\F=\powerset\Omega$), so $\id_\Omega$ is not a discrete random variable in general.
+will not be measurable, and so $\id_\Omega$ will not be a discrete random variable.
 
@@
 Now, from Theorem \ref{FunctionalCompletenessCcc}, we know that this Kleisli category is automatically Cartesian closed.
-The point here is that the category $\Rv_\Omega$ is just close enough to having an initial object for the category $\Set/\oppcat{\Rv_\Omega}$ to be Cartesian, even though it is not a Kleisli category.
+
+What is going on in the general case is that the category $\Rv_\Omega$ is just close enough to having an initial object for the category $\Set/\oppcat{\Rv_\Omega}$ to be Cartesian, even though it is not a Kleisli category.
 
@@
 
-\subsection{Reader actions and semantics}
+\section{Reader actions and denotational semantics}
 
@@
 
+\Urlmuskip=0mu plus 9mu\relax
 \bibliographystyle{alpha2}

### 2019-04-27 Thesis/pmonads2.tex
Monthly commit.

\documentclass{report}[11pt]
\let\FEWFONTS=1

\input{../common/preamble}
\usepackage{lua-visual-debug}

\begin{document}

\chapter{Parametric Monads and Full Abstraction}

Let a monoidal category $\X$ act on a category $\G$, where $\G$ is a suitable model of some programming language.  
In this chapter we will investigate the adequacy and full abstraction properties of the resulting category $\G/\X$, as we did with Kleisli categories in Chapter \ref{ChapMonads}.  
Once again, we will pass to a special case of the general theory.  
As in Chapter \ref{ChapMonads}, we will require $\G$ to be a Cartesian closed category that admits a computationally adequate denotational semantics of Idealized Algol, and we shall require that $\G$ may be regarded as being enriched in algebraic directed-complete partial orders in such a way that every compact morphism between the denotations of types is the denotation of some term.
As hinted at in Chapter \ref{ChapParametricMonads}, we shall require the action of $\X$ on $\G$ to be a reader action corresponding to an oplax symmetric monoidal functor that satisfies the condition in Theorem \ref{TheCartesianClosedCx}, so that the category $\G/\X$ is Cartesian closed.

We fix a symmetric monoidal category $\X$ and an oplax monoidal functor $j\from \X \to \Set$ such that for any object $p$ of $\X$ there are morphisms $h\from p \to p \tensor p$ and $h_0 \from p \to I$ such that the composite
\[
  j(p) \xrightarrow{jh} j(p\tensor p) \xrightarrow{m^j_{p,p}} j(p) \times j(p)
  \]
is equal to the diagonal on $j(p)$.

We fix a model $\G$ of Idealized Algol as above, and suppose that the datatypes in $\G$ are interpreted via an oplax monoidal functor $\Set \to \G$.  
Then we get an oplax monoidal functor $\X \to \G$, inducing a reader action of $\oppcat\X$ on $\G$ such that the category $\G/\oppcat\X$ is Cartesian closed.  
We will define a language and an interpretation of this language in the category $\G/\oppcat\X$.

\newcommand{\IAX}{{IA${}_{X}$}\xspace}
\newcommand{\IAXX}{{IA${}_{\X}$}\xspace}
\section{The language \IAXX}

\begin{definition}[{The language \IAXX}]
  The language \IAXX is formed by taking Idealized Algol, and adding to it new constants
  \[
    \choose_p
    \]
  for each object $p$ of $\X$ such that $j(p)\in\{\bC,\bB,\bN\}$, with typing rule
  \[
    \inferrule{ }{\Gamma \ts \choose_p \from j(p)}\,.
    \]
\end{definition}

The interpretation of $\choose_p$ is that it requests an element $a$ of the set $j(p)$.

Let $\G$ be a model of Idealized Algol as described above, and suppose that there is an oplax monoidal functor $\Set \to \G$ that is used to interpret datatypes.  
We will use an underline to indicate thies functor; so, for example, the object of $\G$ that is used to denote the natural number type is written $\ul\bN$.

By our description of $\G/\oppcat \X$ as a lax colimit in $\Cat$ (i.e., Corollary \ref{CorTheConstructionUniversalProperty}), we have a natual functor $J\from \G\to\G/\oppcat \X$ and a natural transformation $\phi_{p,a}\from J(jp\to a) \to Ja$.  
Our denotational semantics of \IAXX is then given in the category $\G/\oppcat X$ as follows.  
The denotation of any type $T$ of Idealized Algol is given by $J(\deno{T}_\G)$, where $\deno{T}_\G$ is the original denotation in $\G$.
The denotation of any sequent $\Gamma\ts M$ is given by $\deno{\Gamma\ts M} = J(\deno{\Gamma\ts M}_\G)$, where $\deno{-}_\G$ is the original denotation in $\G$.
The denotation of $\choose_p$ is given by the morphism $\omega_p \from 1 \to j(p)$ given by the composite
\[
  I \xrightarrow{\Lambda(\id_{Jjp})} (Jjp \to Jjp)  \to J(jp \to jp) \xrightarrow{\phi_{p,jp}} Jjp\,.
  \]

This denotation may alternatively be defined in a non-compositional way: given a term $\Gamma\ts M\from T$ in context of \IAXX, we can write
\[
  M = N[\choose_p/x_p]\,,
  \]
where $(x_p)$ is a finite collection of free variables in $M$.

Since the categories $\G$ and $\G/\X$ are Cartesian closed, the $\beta$-rule is valid in the semantics, and so if $N$ is a term of \IAXX that refers to $(\choose_p)_{p\in\P}$ for some finite collection $\P$ of objects of $\X$, then we may write the denotation of $\Gamma \ts N$ as the composite
\[
  \deno{\Gamma} \xrightarrow{\langle \id,(\omega_p)\rangle} \deno{\Gamma,(x_p)} \xrightarrow{\deno{\Gamma,(x_p)\ts N[x_p/\choose_p}} \deno{T}\,,
  \]
where the denotation at the right is that of ordinary Idealized Algol.

This is a morphism in $\G/\oppcat\X$.  
If we consider it as a morphism in $\G$, we see that it is given by the curried form of the composite
\[
  \deno{\Gamma}\times j\left(\Tensor_p p\right) \xrightarrow{\deno{\Gamma}\times m^j} \deno \Gamma \times \prod_p j(p) \xrightarrow{\deno{\Gamma,(x_p)\ts N[x_p/\choose_p]}} \deno T\,.
  \]

The example to have in mind is that of probability; here, the objects of our category $\X$ are discrete random variables, with $j(p)$ giving the codomain of the random variable, and the term $\choose_p\from j(p)$ can be thought of as choosing an element of that set.

\section{Operational Semantics}

We inductively define a relation
\[
  \Gamma,s\ts M\converges_U c,s'\,,
  \]
where $\Gamma$ is a $\Var$-context, $s,s'$ are $\Gamma$-stores, $\Gamma\ts M,\Gamma\ts c$ are \IAXX terms-in-context such that $c$ is an IA canonical form, and $U$ is a sequence of pairs of the form $(p:a)$, where $p$ is an object of $\X$ and $a\in j(p)$.
The definition of this rule is shown in Figure \ref{FigIaxxOpSem}.

\begin{figure}
  \begin{mathpar}
    \inferrule*{ }{\Gamma,s\ts c \converges_\epsilon c,s}
    \and
    \inferrule*{\Gamma,s \ts M \converges_U \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x] \converges_V c,s''}{\Gamma,s \ts MN \converges_{U\cat V} c,s''}
    \and
    \inferrule*{\Gamma,s \ts M(\Y M) \converges_U c,s'}{\Gamma,s \ts \Y M \converges_U c,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U n,s'}{\Gamma,s\ts \suc M \converges_U n+1,s'}
    \\\and
    \inferrule*{\Gamma,s\ts M \converges_U n+1,s'}{\Gamma,s\ts \pred M \converges_U n,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U 0,s'}{\Gamma,s\ts \pred M \converges_U 0,s'}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U \skipp,s' \\ \Gamma,s'\ts N \converges_V c,s''}{\Gamma,s \ts M;N \converges_{U\cat V} c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U \true,s' \\ \Gamma,s' \ts N \converges_V c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges_{U\cat V} c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U \false,s' \\ \Gamma,s' \ts P \converges_V c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges_{U\cat V} c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U 0,s' \\ \Gamma,s' \ts N \converges_V c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges_{U\cat V} c,s''}
    \and
    \inferrule*{\Gamma,s\ts M \converges_U n+1,s' \\ \Gamma,s' \ts P \converges_V c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges_{U \cat V} c,s''}
    \and
    \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges_U n,s' \\ \Gamma,s' \ts V \converges_V x,s''}{\Gamma,s\ts V \gets E \converges_{U \cat V} \skipp,(s''\vert x \mapsto n)}
    \and
    \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges_U x,s'}{\Gamma,s\ts !V \converges_U n,s'}
    \and
    \inferrule*{\Gamma,x\from\Var,(s\vert x\mapsto 0)\ts M \converges_U c,(s'\vert x\mapsto n)}{\Gamma,s\ts \neww \lambda x.M \converges_U c,s'}
    \and
    \inferrule*{\Gamma,s\ts E \converges_U n,s' \\ \Gamma,s'\ts V \converges_V \mkvar W R,s'' \\ \Gamma,s'' \ts Wn \converges_W \skipp,s'''}
    {\Gamma,s \ts V\gets E \converges_{U \cat V \cat W} \skipp,s'''}
    \and
    \inferrule*{\Gamma,s\ts V \converges_U \mkvar W R,s' \\ \Gamma,s'\ts R \converges_V n,s''}{\Gamma,s\ts !V \converges_{U \cat V} n,s''}
    \\\and
    \inferrule*[right=$a\in j(p)$]{ }{\Gamma,s\ts \choose_p \converges_{(p:a)} a,s}
  \end{mathpar}
  \caption[Operational semantics for \IAXX]{Operational semantics for \IAXX.}
  \label{FigIaxxOpSem}
\end{figure}

We notice immediately that all but one of these rules are exactly the same as the corresponding rules from \IAX, the only difference being the form the form that the associated sequence takes.  
The one difference is the rule for $\choose_p$.

\section{Translation into \IAX}

We make the connection between the languages \IAX and \IAXX more explicit in the following series of lemmas.
In this section, we will make use of an encoding between an object of the form $jp$ and an Idealized Algol datatype $N$.  
The case we have in mind is when $jp$ is some finite set and $N$ is the natural number object, so that we can choose some way of representing elements of $jp$ as elements of $N$.

\begin{definition}
  Let $p_1,\cdots,p_n$ be a sequence of objects of $\X$ and let $N$ be an object of $\X$ such that $j(N)$ is a datatype of Idealized Algol (i.e., $j(N)\in\{\bC,\bB,\bN\}$).  
  Suppose we have a morphism
  \[
    f \from N \to p_1 \tensor \cdots \tensor p_n
    \]
  in $\X$ such that $jf$ is a surjection.  
  Define functions $\pi_i\from j(N) \to j(p_i)$ to be given by the composites
  \[
    j(N) \xrightarrow{jf} j(p_1 \tensor \cdots \tensor p_n) \xrightarrow{m^j} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\pr_i} j(p_i)\,.
    \]

  Let $u\in j(N)^*$ be a sequence of elements of $j(N)$, and let $U$ be a sequence of pairs $(p:a)$, where each $p$ is one of the $p_i$.  
  We say that $u$ \emph{covers $U$ with respect to $f$} if $U$ and $u$ have the same length and if whenever $U^{(k)}=(p_i:a)$, we have $a = \pi_i(u^{(k)})$.
  \label{DefCovers}
\end{definition}

Recall that, in the definition of the category $\G/\oppcat\X$, the \Mellies morphisms are left unchanged by precomposing with a morphism in the image of the functor $j$; therefore, if $M\from T$ is a closed term of \IAXX referring to $\choose_{p_1},\cdots,\choose_{p_n}$, then we may write the denotation of $M$ as the composite
\[
  j(N) \xrightarrow{jf} j(p_1 \tensor \cdots \tensor p_n) \xrightarrow{m^j} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \deno T\,;
  \]
i.e., as
\[
  j(N) \xrightarrow{\langle \pi_1,\cdots,\pi_n\rangle} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \deno T\,.
  \]

\begin{lemma}
  Let $\Gamma \ts M$ be an \IAXX term-in-context, where $M$ refers to terms $\choose_{p_1},\cdots,\choose_{p_n}$, and no other $\choose$ terms.
  Let $N$ be an object of $\X$ such that $j(N)$ is an IA datatype and let $f\from N \to p_1\tensor \cdots \tensor p_n$ be a morphism, as in Definition \ref{DefCovers}.  
  Suppose that the functions $\pi_i$ are all definable in Idealized Algol; that is, that there are terms $\Pi_i\from j(N) \to j(p_i)$ of IA such that the following inference is valid.
  \[
    \inferrule{ \Gamma,s\ts M \converges m,s'}{\Gamma,s\ts \Pi_i M\converges \pi_i(m),s'}
    \]

  Let $s,s'$ be $\Gamma$-stores, and let $\Gamma\ts c$ be a canonical form.  
  Suppose $U$ is a sequence such that we have
  \[
    \Gamma,s\ts M\converges_U c,s'\,.
    \]
  Then
  \[
    \Gamma,s\ts M[\neww (\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/\choose_{p_i}] \converges_u c,s'
    \]
  in IA${}_{j(N)}$ for all sequences $u\in j(N)^*$ that cover $U$.
  \label{LemSoundnessIaxx}
\end{lemma}
\begin{proof}
  Induction on the derivation of $\Gamma,s\ts M\converges_U c,s'$.  
  Suppose that the last rule in the derivation takes the following form.
  \[
    \inferrule{\Gamma_1,s^{(0)}\ts M_1\converges_{U_1} c_1,s^{(1)} \\ \cdots \\ \Gamma_n,s^{(n-1)}\ts M \converges_{U_n} c_n,s^{(n)}}
    {\Gamma,s^{(0)} \ts M \converges_{U_1 \cat \cdots \cat U_n} c,s^{(n)}}
    \]
  Suppose a sequence $u$ covers $U_1\cat \cdots \cat U_n$.  
  Then we may write $u = u_1 \cat \cdots \cat u_n$, where $u_i$ covers $U_i$.

  By induction, then, we may derive that
  \[
    \Gamma_k,s^{(k)}\ts M_k[\neww (\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/\choose_{p_i}]  \converges_{u_k} c_k,s^{(k)}
    \]
  for $k=1,\cdots,n$.
  Now note that Lemma \ref{LemFirstSubstitution} still holds if we use the terms $\choose_{p_i}$ instead of the $\ask_X$; this means that we have a valid IA${}_j(N)$ inference given by
  \[
    \inferrule*{\Gamma_1,s^{(0)}\ts M_1[\new(\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/\choose_{p_i}] \converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma_n,s^{(n-1)}\ts M_n[\new(\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/\choose_{p_i}] \converges_{u_n} c_n,s^{(n)}}
    {\Gamma,s^{(0)}\ts M[(\lambda z.\Pi_i) \ask_{j(N)}.\choose_{p_i}] \converges_u c,s^{(n)}}\,,
    \]
  from which we can deduce that
  \[
    \Gamma,s^{(0)}\ts M[\new(\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/\choose_{p_i}] \converges_i c,s^{(n)}\,,
    \]
  as desired.

  The other possibility is that the final step in the derivation takes the form
  \[
    \inferrule*{ }{\Gamma,s \ts \choose_{p_j} \converges_{(p_j:a)} a,s}\,.
    \]
  Let $U$ be a (length $1$) sequence covering $(p_j:a)$.  
  So $U=t$, where $t\in j(P)$ is such that $\pi_j(t)=a$.

  Then 
  \[
    \choose_{p_j}[\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/\choose_{p_i}] = \neww(\lambda v.v\gets \ask_{j(N)};\Pi_j \oc v)\,,
    \]
  and we may derive
  \[
    \Gamma,s\ts \new(\lambda v.v\gets \ask_{j(N)};\Pi_j\oc v) \converges_t a,s\,.\qedhere
    \]
\end{proof}

To prove the converse, we prove a lemma about substitution analogous to  Lemma \ref{LemSecondSubstitution}.

\begin{lemma}
  Let
  \[
    \inferrule{\Gamma,s^{(0)}\ts M_1\converges_{u_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n\converges_{u_n} c_n,s^{(n)}}
    {\Gamma,s^{(0)} \ts M \converges_{u_1\cat \cdots \cat u_n} c,s^{(n)}}
    \]
  be an inference of IA${}_{j(N)}$, where every instance of $\ask_{j(N)}$ occurs as part of some term $\neww (\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)$, and suppose that $M\ne \neww(\lambda v.v\gets\ask_{j(N)};\Pi_j\oc v)$ for any $j$.  
  Suppose we have sequences $U_1,\cdots,U_n$ such that $u_k$ covers $U_k$ for $k=1,\cdots,n$.
  Then
  \[
    \inferrule{\Gamma,s^{(0)}\ts M_1[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges_{U_1} c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges_{U_n} c_n,s^{(n)}}
    {\Gamma,s^{(0)} \ts M[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges_{U_1\cat \cdots \cat U_n} c,s^{(n)}}
    \]
  is a valid inference of \IAXX.
  \label{LemThirdSubstitution}
\end{lemma}
\begin{proof}
  As in Lemma \ref{LemSecondSubstitution}, we can prove this by looking at cases.  
  For example, consider the sequencing rule
  \[
    \inferrule{\Gamma,s\ts M\converges_u \skipp,s' \\ \Gamma,s' \ts N \converges_v c,s''}{\Gamma,s\ts M;N \converges c,s''}\,.
    \]
  We have
  \begin{IEEEeqnarray*}{Cl}
    &(M;N)[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \\
    = &M[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)];\\&N[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)]\,,
  \end{IEEEeqnarray*}
  and so we certainly get a rule
  \[
    \inferrule*{\Gamma,s\ts M[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)]\converges_U \skipp,s' \\ \Gamma,s' \ts N[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges_V c,s''}{\Gamma,s\ts (M;N)[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges c,s''}\,.
    \]
  The only case where we need to be careful is for the $\neww$ rule:
  \[
    \inferrule*{\Gamma,x,(s\vert x\mapsto 0)\ts M\converges_u c,(s'\vert x\mapsto n)}
    {\Gamma,s\ts \neww \lambda x.M \converges_u c,s'}\,.
    \]
  If $\neww\lambda x.M \ne \neww(\lambda v.v\gets \ask_{j(N)};\Pi_j \oc v)$, then we have
  \begin{IEEEeqnarray*}{Cl}
    &(\neww \lambda x.M)[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \\
    = & \neww \lambda x. (M[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)])\,.
  \end{IEEEeqnarray*}
  Then we can apply the rule
  \[
    \inferrule*{\Gamma,x,(s\vert x\mapsto 0)\ts M[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges_U c,(s'\vert x\mapsto n)}
    {\Gamma,s\ts (\neww\lambda x.M)[\choose_{p_i}/\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)] \converges U c,s'}.\qedhere
    \]
\end{proof}

We now prove the converse to Lemma \ref{LemSoundnessIaxx}.

\begin{lemma}
  Let $\Gamma,y_1\from j(p_1),\cdots,y_n\from j(p_n) \ts M \from T$ be a term-in-context of ordinary Idealized Algol, where $\Gamma$ is a $\Var$-context.  
  Let $U$ be a sequence and let $N,\pi_i,\Pi_i$ be as above.
  Suppose that there exists some sequence $u\in j(N)^*$ such that $u$ covers $U$ and such that
  \[
    \Gamma,s\ts M[\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)/y_i]\converges_u c,s'\,.
    \]
  Then
  \[
    \Gamma,s\ts M[\choose_{p_i}/y_i] \converges_U c,s'\,.
    \]
  \label{LemAdequacyIaxx}
\end{lemma}
\begin{proof}
  Induction on the derivation.
  Suppose that $M$ is not one of the $y_i$; then $M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)/y_i]$ is not equal to $\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)$.
  Moreover, every instance of $\ask_{j(N)}$ in $M$ occurs as part of an expression of the form $\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)$, and so we win by Lemma \ref{LemThirdSubstitution} and the inductive hypothesis.

  Otherwise, $M=\new\lambda v.v\gets \ask_{j(N)};\Pi_j\oc v)$ for some $j$.  
  Now, if we have
  \[
    \Gamma,s\ts \neww(\lambda v.v\gets\ask_{j(N)};\Pi_j\oc v)\converges_u c,s'\,,
    \]
  then a simple examination of the reduction tells us that we must have $s'=s$, and that $u$ must have length $1$ -- say $u=m$ -- where the single element $n$ of $u$ satisfies $\pi_j(m)=c$.

  But now we certainly have
  \[
    \Gamma,s\ts \choose_{p_j} \converges_{(p_j:c)} c,s\,,
    \]
  and the sequence $m$ covers the sequence $(p_j:c)$.
\end{proof}

Lemmas \ref{LemSoundnessIaxx} and \ref{LemAdequacyIaxx} together prove the following.

\begin{lemma}
  Let $\Gamma,x_1,\cdots,x_n\ts M$ be a term-in-context of Idealized Algol, where $\Gamma$ is a $\Var$-context.
  Then the following are equivalent.

  i) $\Gamma,s\ts M[\choose_{p_i/x_i}]\converges_U c,s'$.

  ii) $\Gamma,s\ts M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v/x_i]\converges_u c,s'$ for all $u$ covering $U$.

  iii) $\Gamma,s\ts M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v/x_i]\converges_u c,s'$ for some $u$ covering $U$.
  \label{LemComputationalAdequacyIaxx}
\end{lemma}
\begin{proof}
  (i) $\Rightarrow$ (ii): Lemma \ref{LemSoundnessIaxx}.

  (ii) $\Rightarrow$ (iii): By assumption, the function $j(f) \from N \to j(\Tensor_i p_i)$ is surjective, so for any $U$ there is some $u\in j(N)^*$ covering $U$.

  (iii) $\Rightarrow$ (i): Lemma \ref{LemAdequacyIaxx}.
\end{proof}

\section{Computational Adequacy}

We are now ready to make the definitions we need to state our Computational Adequacy result.

Recall that if $\sigma$ was a Kleisli morphism $1 \to \bC$ (i.e., a morphism $1 \to (X \to \bC)$ in the original category, where $X$ was an Idealized Algol datatype), then we wrote $\sigma\downarrow_u$ if the composite
\[
  1 \xrightarrow{\sigma} (X \to \bC) \xrightarrow{\eta_u} (\Varr \to \bN) \xrightarrow{\neww} \bN \xrightarrow{t_{|u|}} \bC
  \]
was not equal to $\bot$, where $\eta_u$ was the denotation of the Idealized Algol term-in-context
\[
  f \from X \to \com \ts \lambda v.v\gets 0;f(v\gets\suc\oc v;\tr_u \oc v);\oc v \from \Var \to \nat\,.
  \]

We want to extend this definition to morphisms in the category $\G/\oppcat \X$.  
There are a couple of problems here.

Firstly, the morphisms in $\G/\oppcat \X$ are equivalence classes of \Mellies morphisms, and the equivalence relation does not respect this predicate $\downarrow_u$ -- especially since the $X$ in the above formula could change when we choose a different representative of the equivalence class.

Secondly, a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an (equivalence class of) morphisms $1 \to (j(p) \to \bC)$ in $\G$, and the object $j(p)$ need not be an Idealized Algol datatype.

To solve the second problem, we make an additional small assumption on our category $\G$.  
We require that there exist morphisms
\[
  \xi_u \from (X \to \bC) \to \bC
  \]
for any set $X$ and any finite sequence $u\in X^*$ such that for any function $f \from X \to Y$, we have $(f\to \bC);\xi_u = \xi_{f_*u}$, where $f_*u$ is the sequence formed by applying $f$ pointwise to $u$, and such that if $X$ is an IA datatype, then
\[
  \xi_u = (X \to \bC) \xrightarrow{\eta_u} (\Varr \to \bN) \xrightarrow{\neww} \bN \xrightarrow{t_{|u|}} \bC\,.
  \]

\begin{example}
  In the category of games, the morphisms $\xi_u$ are the strategies containing the plays $\epsilon$, $qq$ and plays of the form
  \begin{mathpar}
    \begin{array}{ccc}
      X           & \bC & \bC \\
                  &     &  q  \\
                  &  q  &     \\
      q           &     &     \\
      u^{(0)}     &     &     \\
      \vdots      &     &     \\
      q           &     &     \\
      u^{(k)}       &     &    
    \end{array}
    \and
    \begin{array}{ccc}
      X           & \bC & \bC \\
                  &     &  q  \\
                  &  q  &     \\
      q           &     &     \\
      u^{(0)}     &     &     \\
      \vdots      &     &     \\
      q           &     &     \\
      u^{(|u|-1)} &     &     \\
                  &  a  &     \\
                  &     &  a  
    \end{array}
  \end{mathpar}
  (so the strategy has no reply if player $O$ asks the question in $X$ fewer than $|u|$ times, or tries to ask it more than $|u|$ times).
\end{example}

\begin{definition}
  Given a set $X$ and a \Mellies morphism $\sigma \from 1 \to (X \to \bC)$, we say that $\sigma$ \emph{accepts} a sequence $u\in X^*$ if $\sigma;\xi_u\ne\bot$.
  We write $\Acc(\sigma)$ for the set of all sequences accepted by $\sigma$.
\end{definition}

Recall that a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an equivalence class of \Mellies morphisms $1 \to (j(p) \to \bC)$ in $\G$, where $p$ ranges over the objects of $\X$, and where the equivalence relation is generated by identifying all pairs of morphisms $\sigma \from 1 \to (j(p) \to \bC)$ and $\tau \from 1 \to (j(q) \to \bC)$ such that there is a morphism $f \from p \to q$ such that $\tau;(j(f)\to\bC)=\sigma$.

\begin{definition}
  We define an equivalence relation on pairs $(p,\U)$, where $p$ is an object of $\X$ and $\U\subset j(p)^*$ is a set of finite sequences drawn from $j(p)$ to be the equivalence relation generated by identifying $(p,\U)$ and $(q,\V)$ whenever there is a morphism $f\from p \to q$ in $\X$ such that for all $u\in j(p)^*$, we have $u\in\U$ if and only if $j(f)_*u\in\V$.
  \label{DefEquivalenceOfPairs}
\end{definition}

It is instructive to consider the equivalence relation on pairs $(p,\U)$ in the case that $\X = \Rv_\Omega$ is the category of random variables on some probability space $\Omega$.
Given a random variable $V$ on a set $X$, we get an induced random variable taking values in $X^*$.  
If we have a random variable $W$ on a set $Y$ and a function $f\from X \to Y$ such that $W=f\circ X$, and if $\U\subset X^*$ and $\V\subset Y^*$ are such that $u\in\U$ if and only if $f_*u\in\V$, then the induced probabilities of the sets $\U$ and $\V$ are the same.  
So, in this case, the equivalence relation on sets of sequences is subsumed into the very natural equivalence relation of having the same probability.

\begin{proposition}
  Let $\sigma\from 1 \to (j(p) \to \bC)$, $\tau\from 1 \to (j(q) \to \bC)$ be two representatives of the same morphism $1 \to \bC$ in $\G/\oppcat\X$.  
  Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
  \label{PropAccEquivalent}
\end{proposition}
\begin{proof}
  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\tau$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \tau;(j(f)\to \bC)$.

  Let $u\in j(p)^*$.  
  Then we have
  \begin{IEEEeqnarray*}{rCl}
    u\in\Acc(\sigma) & \Leftrightarrow & \sigma;\xi_u\ne\bot \\
    & \Leftrightarrow & \tau;(j(f)\to\bC);\xi_u\ne\bot \\
    & \Leftrightarrow & \tau;\xi_{j(f)_*u}\ne\bot \\
    & \Leftrightarrow & j(f)_*u \in \Acc(\tau)\,.
  \end{IEEEeqnarray*}
  Therefore, $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
\end{proof}

We can now state and prove our Computational Adequacy result.
For this result, given a term $M\from \com$ mentioning objects $p_1,\cdots,p_n$, we shall assume the existence of some IA datatype $N$ admitting a morphism $f \from N \to p_1 \tensor \cdots \tensor p_n$ such that the definable projections $\pi_i$ on to the objects $j(p_i)$ are IA-definable.

\begin{definition}
  Let $M$ be a closed term of \IAXX of type $\com$ mentioning $p_1,\cdots,p_n$.
  Let $S(M)$ be the set of all sequences $U$ such that $M\converges_U\skipp$.

  We define $B(M)$, the \emph{behaviours of $M$}, to be the equivalence class corresponding to the pair
  \[
    (p_1\tensor \cdots \tensor p_n, \U)\,,
    \]
  where $\U$ is the set of all sequences $u\in j(p_1\tensor \cdots \tensor p_n)^*$ that cover some sequence $U\in S(M)$, via the projections
  \[
    j(p_1\tensor \cdots \tensor p_n) \xrightarrow{m^j} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\pr_i} j(p_i)\,.
    \]
\end{definition}

\begin{theorem}[Computational Adequacy for \IAXX]
  Let $M \from \com$ be a closed term of \IAXX referring to $p_1,\cdots,p_n$.  
  Suppose the denotation of $M$ is given by a morphism $1 \to (j(p) \to \bC)$ in $\G/\oppcat\X$.

  Then $(p,\Acc(\deno M))$ is equivalent to $B(M)$.
  \label{TheComputationalAdequacyIAXX}
\end{theorem}
\begin{proof}
  By Proposition \ref{PropAccEquivalent}, we may assume that the denotation of $M$ is in a particular form, namely the (curried form of) the composite
  \[
    j(N) \xrightarrow{\langle\pi_1,\cdots,\pi_n\rangle} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \bC\,.
    \]
  But if we consider this as a Kleisli morphism in the category $\Kl_{R_{j(N)}}\G$, then this is the denotation of the IA${}_{j(N)}$ term
  \[
    M[\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)/\choose_{p_i}]\,.
    \]
  By Lemma \ref{LemComputationalAdequacyIaxx}, if $u\in j(N)^*$ is a sequence, then
  \[
    M[\neww(\lambda v.v\gets \ask_{j(N)};\Pi_i\oc v)/\choose_{p_i}]\converges_u \skipp
    \]
  if and only if $u$ covers a sequence $U$ such that $M\converges_U\skipp$.
  By our Computational Adequacy result for \IAX (Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy}), this means that for all $u\in j(N)^*$, $u\in \Acc(\deno M)$ (for this particular form of $\deno M$) if and only if $u\in \U$.
  Therefore, $(N,\Acc(\deno M)) = (N,\U')$, where $\U'\subset j(N)^*$ is the set of all sequences $u$ that cover some $U$ such that $M\converges_U\skipp$ via the projections $\pi_i$.
  Lastly, we note that $(N,\U')$ is equivalent to $B(M)$, through the morphism $f\from N \to p_1\tensor\cdots\tensor p_n$.
\end{proof}

\section{Equational Soundness}

We transfer to an Equational Soundness result in our standard way.
First, we make a definition of observational equivalence of \IAXX terms.

\begin{definition}
  Let $M$ be a closed term of \IAXX of type $\com$ mentioning $p_1,\cdots,p_n$.
  Let $S(M)$ be the set of all sequences $U$ such that $M\converges_U\skipp$.

  We define $B(M)$, the \emph{behaviours of $M$}, to be the equivalence class corresponding to the pair
  \[
    (p_1\tensor \cdots \tensor p_n, \U)\,,
    \]
  where $\U$ is the set of all sequences $u\in j(p_1\tensor \cdots \tensor p_n)^*$ that cover some sequence $U\in S(M)$, via the projections
  \[
    j(p_1\tensor \cdots \tensor p_n) \xrightarrow{m^j} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\pr_i} j(p_i)\,.
    \]
\end{definition}

\begin{definition}[Observational Equivalence]
  Let $M,M'\from T$ be closed terms of \IAXX.  
  We say that $M$ and $M'$ are \emph{observationally equivalent} if $B(C[M])$ and $B(C[M'])$ are equivalent for all contexts $C\from \com$ with a hole of type $T$.
\end{definition}

We then make definitions that will mirror this equivalence in the denotational semantics.

\begin{definition}[Equivalence of morphisms $1 \to \bC$]
  Let $\sigma,\tau\from 1 \to \bC$ be morphisms in $\G/\oppcat\X$, considered as morphisms $\sigma\from j(p) \to \bC$ and $\tau \from j(q) \to \bC$ in $\G$.  
  We say that $\sigma\approx\tau$ if $(p,\Acc(\sigma))$ is equivalent to $(q,\Acc(\tau))$.
\end{definition}

\begin{definition}[Intrinsic Equivalence]
  Let $\sigma,\tau\from A \to B$ be morphisms in $\G/\oppcat\X$.  
  Then we say that $\sigma\sim\tau$ if for all $\alpha\from (A\to B) \to \bC$, we have $\Lambda(\sigma);\alpha \approx \Lambda(\tau);\alpha$.
\end{definition}

Now we can prove Equational Soundness as we did in Proposition \ref{PropEquationalSoundness}.

\begin{theorem}[Equational Soundness for \IAXX]
  Let $M,M'\from T$ be closed terms of \IAXX such that $\deno{M}\sim\deno{N}$.
  Then $M$ and $M'$ are observationally equivalent.
\end{theorem}
\begin{proof}
  First suppose that $M$ and $M'$ are not observationally equivalent -- so there is some context $C$ such that $B(C[M])$ and $B(C[M'])$ are inequivalent.
  Now $B(C[M])$ is equivalent to $(N,\U)$ and $B(C[M'])$ is equivalent to $(N,\U')$, where $\U\subset j(N)^*$ is the set of sequences that cover some $U\in S(C[M])$ and $\U'$ the set of sequences that cover some $U\in S(C[M'])$ via the projections $\pi_i$.

  Let $\alpha$ be the denotation of the term-in-context $f\from T \ts C[f]$.  
  Then $\Lambda(\deno{M});\alpha$ is the denotation of $C[M]$ and $\Lambda(\deno{M'});\alpha$ the denotation of $C[M']$.  
  By Theorem \ref{TheComputationalAdequacyIAXX}, the sets $(N,\Acc(\Lambda(\deno{M});\alpha))$ and $(N,\Acc(\Lambda(\deno{M'})))$ are inequivalent, and so $\deno M \not\sim\deno{M'}$.
\end{proof}

Our setup is too general for us to prove Full Abstraction, but we will be able to prove a Full Abstraction result in an important special case: that of Probabilistic Algol.

\section{Probability}

We now specialize to the case where $\X$ is a category of random variables on some fixed probability space $(\Omega,\F,\bP)$, in order to model a probabilistic language.
For our purposes, it will suffice to take $\Omega$ to be the real interval $(0,1)$ with its Borel $\sigma$-algebra and measure.
A \emph{random variable} on $\Omega$ is a measurable function $V \from \Omega \to X$.  
Given such a random variable, and $A\subset X$, we write $\bP(V \in A)$ for $\bP(V\inv(A))$, and $\bP(V = x)$ for $\bP(V \in \{x\})$.

The category $\X = \Rv_\Omega^{FS}$ will then be the category whose objects are random variables of \emph{finite support}; that is, measurable functions $V\from\Omega \to X$, where $X$ is a discrete space, such that there is some finite subset $Y\subset X$ such that $\bP(V\in Y) = 1$.

The morphisms in $\Rv_\Omega^{FS}$ from $V\from \Omega \to X$ to $W \from \Omega \to Y$ are probability-preserving functions $X \to Y$; i.e., functions $X \to Y$ such that for all $A \subset Y$, we have $\bP(f(V) \in A) = \bP(W \in A)$.

Recall that the tensor product of two random variables $V\from \Omega \to X$ and $W \from \Omega \to Y$ is their pairing $V \tensor W = \langle V,W\rangle \from \Omega \to X \times Y$.

We define a language Probabilistic Algol (PA) to be the sublanguage of IA${}_{\Rv_\Omega^{FS}}$ generated by the terms of Idealized Algol and the terms
\[
  \choose_{V_p}\,,
  \]
where $p\in [0,1]$, and where we have identified $V_p$ is the Bernoulli random variable
\[
  \Omega \to \bB
  \]
that returns $\true$ if its input is less than $p$ and $\false$ if it is greater than or equal to $p$.

The denotation of any term of PA, then, will be an (equivalence class of) morphisms
\[
  \ul{\bB^n} \xrightarrow{m} \ul{\bB}^n \to \deno{T}\,,
  \]
together with some random variable taking values in $\bB^n$.
We have used an underline to distinguish between the object $\ul{\bB^n}$ of $\G$ corresponding to the set $\bB^n$ of $n$-tuples of booleans and the $n$-fold Cartesian power $\ul{\bB}^n$ in $\G$ of the object $\bB$ corresponding to the set of booleans.

Lastly, given such a random variable $V\from\Omega \to \bB^n$, there is a random variable $\tilde{V} \from \Omega \to \bN$ such that for each $\vec{v}\in\bB^n$, we have
\[
  \bP\left(\tilde{V} = \sum_{i=1}^n 2^{i-1}\vec{v}_i\right) = \bP(V = \vec{v})
  \]
and such that $\bP(\tilde{V}=k)=0$ for any $k\ge 2^n$.
Then we have a function $f \from \bN \to \bB^n$ that sends $\sum_{i=1}^n 2^{i-1}a_i$ to $(a_1,\cdots,a_n)$ and sends $k\ge 2^n$ to some fixed value (say, $(\false,\cdots,\false)$), and then we have
\[
  f\circ\tilde{V}=V\,.
  \]
Moreover, $\tilde{V}$ has finite support.

Now suppose that $X$ is a finite discrete probability space.  
Then the set $X^\omega$ of all infinite sequences of elements of $X$ may be given the product topology, and equipped with the resulting Borel $\sigma$-algebra.  
A basic open subset of $X^\omega$ is a set $\S\subset X^\omega$ for which there exists some $n$ such that if $s\in \S$ and $t$ is a sequence such that $s$ and $t$ are identical on the first $n$ terms, then $t\in\S$.
We can define a pre-probability measure on these basic open sets by setting
\[
  \bP(\S) = \sum_{u\in \S\vert_n} \prod_{i=0}^{n-1} \bP(u^{(i)})\,,
  \]
where $\S\vert_n$ is the set of all length-$n$ prefixes of elements of $\S$.

Then the Carath\'{e}odory Extension Theorem tells us that there is a unique extension of this to a probability measure on the whole space (see, for example, \cite[1.1.4]{StochasticCalculusII}).

If $V \from \Omega \to Z$ is a finitely-supported random variable, then $V$ induces a probability measure on its support $\im(V)\subset Z$.
This gives us a probability measure on $\im(V)^*$, which we can extend to a probability measure on $Z^*$ by setting
\[
  \bP(A) = \bP(A \cap \im(V)^*)
  \]
for any $A \subset Z^*$.

\begin{definition}
  Let $V\from \Omega \to X$ be a finitely supported random variable and let $\U\subset X^*$ be a set of sequences.  
  Then we define
  \[
    \bP(V,\U) = \bP(\U^\omega)\,,
    \]
  where $\U^\omega\subset X^\omega$ is the set of all infinite sequences having some prefix in $\U$.
  Note that $\U^\omega$ is an open subset of $X^\omega$, so is in particular measurable.

  An easier way to define $\bP(V,\U)$ is that it is the sum of the probabilities of all the sequences in $\U$; i.e.:
  \[
    \bP(V,\U) = \sum_{u\in \U} \prod_{i=0}^{|u|-1} \bP(u^{(i)})\,,
    \]
  where the infinite sum refers to the supremum of the sums of all finite subsets of $\U$.
\end{definition}

\begin{proposition}
  Suppose that $(V,\U)$ and $(W,\V)$ are equivalent pairs, in the sense of Definition \ref{DefEquivalenceOfPairs}, where $V \from \Omega \to X$, $W \from \Omega \to Y$ are finitely-supported random variables, and $\U\subset X^*$, $\V\subset Y^*$ are sets of sequences.
  Then $\bP(V,\U) = \bP(W, \V)$.
  \label{PropProbabilityWellDefined}
\end{proposition}
\begin{proof}
  Without loss of generality, we may assume that there is a probability-preserving function $f \from X \to Y$; i.e., a function such that for any $A \subset Y$ we have $\bP(W \in A) = \bP(f(V) \in A)$ and such that $\U = f_*\inv(\V)$.
  Then we have
  \begin{IEEEeqnarray*}{rCl}
    \bP(V,\U) & = & \bP(V,f_*\inv(\V)) \\
    & = & \sum_{\stackrel{u\in X^*}{f_*u\in\V}} \prod_{i=0}^{|u|-1} \bP(V = u^{(i)}) \\
    & = & \sum_{v\in \V}\sum_{\stackrel{u\in X^*}{f_*u = v}} \prod_{i=0}^{|u|-1} \bP(V = u^{(i)}) \\
    & = & \sum_{v\in \V}\prod_{i=0}^{|v|-1} \sum_{\stackrel{x\in X }{ f(x) = v}} \bP(V = x) \\
    & = & \sum_{v\in \V} \prod_{i=0}^{|v|-1} \bP(f(V) = v^{(i)}) \\
    & = & \sum_{v\in \V} \prod_{i=0}^{|v|-1} \bP(W = v^{(i)}) \\
    & = & \bP(W,\V)\,.\hspace{1em plus 1fill}\qedhere
  \end{IEEEeqnarray*}
\end{proof}

We now make a definition relating the operational behaviour we have defined for \IAXX to probability.

\begin{definition}
  Let $M\from \com$ be a closed term of PA mentioning probabilities $p_1,\cdots,p_n$.
  We define $\bP(M\converges)$ to be $\bP(B(M))$; i.e.,
  \[
    \bP(V_{p_1}\tensor \cdots \tensor V_{p_n},\U)\,,
    \]
  where $\U$ is the set of all sequences $u\in j(V_{p_1}\tensor \cdots \tensor V_{p_n})^*$ that cover some sequence $U$ such that $M\converges_U\skipp$.
  \label{DefProbConverges}
\end{definition}

We can define a corresponding notion for morphisms in the denotational semantics.

\begin{definition}
  Let $\sigma \from 1 \to \bC$ be a morphism in $\G/\oppcat{(\Rv_\Omega^{FS})}$, considered as a morphism $\sigma \from 1 \to (X \to \bC)$ in $\G$, together with a finitely-supported random variable $V \from \Omega \to X$.

  Then we define $\bP(\sigma\downarrow)$ to be
  \[
    \bP(V, \Acc(\sigma)\,.
    \]
  \label{DefProbNonBot}
\end{definition}

\begin{remark}
  By Propositions \ref{PropProbabilityWellDefined} and \ref{PropAccEquivalent}, Definitions \ref{DefProbConverges} and \ref{DefProbNonBot} are well defined.
\end{remark}

Now we are ready to prove computational adequacy.

\begin{proposition}[Computational Adequacy for PA]
  Let $M\from \com$ be a closed term of PA.  
  Then $\bP(M\converges) = \bP(\deno M \downarrow)$.
  \label{PropComputationalAdequacyPa}
\end{proposition}
\begin{proof}
  By Theorem \ref{TheComputationalAdequacyIAXX}, $B(M)$ is equivalent to $(p,\Acc(\deno M))$.  
  Therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(M\converges) = \bP(B(M)) = \bP(V,\Acc(\deno M)) = \bP(\deno M\downarrow)$.
\end{proof}

We can define observational equivalence for terms.

\begin{definition}
  Let $M,N\from T$ be closed terms of PA.  
  Then we say that $M$ and $N$ are (probabilistically) \emph{observationally equivalent} if for all contexts $C\from \com$ with a hole of type $T$, we have
  \[
    \bP(C[M]\converges) = \bP(C[N]\converges)\,.
    \]
\end{definition}

We then have the usual corresponding definition in the denotational semantics.

\begin{definition}
  Let $\sigma,\tau\from A \to B$ be morphisms in $\G/\oppcat{(\Rv_\Omega^{FS})}$.  
  We write $\sigma\sim_{\bP}\tau$ if for all morphisms $\alpha \from (A \to B) \to \bC$ in $\G/\oppcat{(\Rv_\Omega^{FS})}$ we have
  \[
    \bP(\Lambda(\sigma);\alpha\downarrow) = \bP(\Lambda(\tau);\alpha\downarrow)\,.
    \]
\end{definition}

Then, by our standard argument, we may derive Equational Soundness from Computational Adequacy.

\begin{proposition}
  Let $M,N\from T$ be closed terms of PA such that $\deno M \sim_{\bP} \deno N$.  
  Then $M$ and $N$ are probabilistically observationally equivalent.
\end{proposition}

Our next goal will be to prove the converse to this result: Full Abstraction.

\section{Full Abstraction for Probabilistic Algol}

\begin{proposition}
  Let $V\from \Omega \to X$ be a finitely supported random variable.  
  Then there exist $p_1,\cdots,p_n$ and a function
  \[
    f \from \bB^n \to X
    \]
  such that for all $x\in X$ we have $\bP(V = x) = \bP(f(V_{p_1},\cdots,V_{p_n}) = x)$.
  \label{PropFiniteSupport}
\end{proposition}
\begin{proof}
  Recall that the $V_p$ are not independent in our formulation; indeed, if $p<q$, then $V_p = \true \Rightarrow V_q = \true$.

  Enumerate those elements $x\in X$ such that $\bP(V = x) \ne 0$ as $x_1,\cdots,x_n$, and for each $k = 1,\cdots,n$, define
  \[
    p_k = \sum_{i=1}^n \bP(X = x_i)\,.
    \]
  Note that we must have $p_n = 1$.  
  Then we define
  \[
    f(\vec{b}) = \begin{cases}
      x_1 & \text{if $\vec{b} = \vec{\false}$} \\
      \min\{k \suchthat b_k = \true\} & \text{otherwise}\,.
    \end{cases}
    \]
  Fix $x\in X$.  
  If $x$ is not one of the $x_i$, then we have $\bP(f(V_{p_1},\cdots,V_{p_n}) = x) = 0 = \bP(V = x)$.  
  Otherwise, suppose $x = x_k$.  
  If $\omega\in\Omega$ and $p_{k-1}\le\omega<p_k$, then $V_{p_k}(\omega) = \true$, and $V_{p_i}(\omega) = \false$ for all $i \le k$.  
  So $f((V_{p_1}\tensor\cdots\tensor V_{p_n})(\omega)) = x_k$.
  If $\omega<p_{k-1}$, then $V_{p_{k-1}}(\omega) = \true$, so $f((V_{p_1}\tensor\cdots\tensor V_{p_n})(\omega)) \ne x_k$.
  If $\omega\ge p_k$, then $V_{p_k}(\omega) = \false$, so $f((V_{p_1}\tensor\cdots\tensor V_{p_n})(\omega)) \ne x_k$.  
  Therefore, 
  \[
    \bP(f(V_{p_1},\cdots,V_{p_k}) = x_k) = \bP([p_{k-1},p_k)) = p_k - p_{k-1} = \bP(X = x_k)\,.
    \]
  It follows that $f$ is probability preserving in the sense required.
\end{proof}

The most important consequence of Proposition \ref{PropFiniteSupport} is that it tells us that any morphism $A\to B$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ may be considered as a pair 
\[
  (V_{p_1}\tensor\cdots\tensor V_{p_n},f \from A \to (\bB^n \to B))
  \]
for appropriately chosen $p_1,\cdots,p_n$.

\begin{definition}
  Let $\sigma\from A \to B$ be a morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
  We say that $\sigma$ is \emph{compact} if it is compact when considered as a morphism in $\G$.
\end{definition}

\begin{remark}
  When we say `considered as a morphism in $\G$' in the above definition, we mean `in at least one of its possible interpretations as a morphism in $\G$'.  
  Note, however, that the continuous image of a compact element is compact, and so if we pass to a new representative of $\sigma$ by composing on the left by the image of some morphism in $\Rv_{\Omega}^{FS}$, then the resulting representative of $\sigma$ will also be compact.

  Note that if $\G$ is the category of games, this compactness property is invariant under the choice of representative for $\sigma$.
\end{remark}

\begin{proposition}[Compact definability]
  Let $T$ be an Idealized Algol type and let $\sigma \from 1 \to \deno{T}$ be a compact morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
  Then there is some closed term $M\from T$ such that $\sigma = \deno{M}$.
  \label{PropProbabilityCompactDefinability}
\end{proposition}
\begin{proof}
  Let $(V, \sigma \from 1 \to (X \to \deno{T})$ be a compact representative of $\sigma$, where $X$ is a set and $V$ is a finitely-supported random variable taking values in $X$.  
  By Proposition \ref{PropFiniteSupport}, we may choose $p_1,\cdots,p_n$ such that there is a probability-preserving function
  \[
    f \from V_{p_1} \tensor \cdots \tensor V_{p_n} \to \deno{T}\,.
    \]
  After composing on the right by $(\sigma \to \deno{T})$, we may assume that $\sigma$ is of the form
  \[
    (V_{p_1}\tensor\cdots\tensor V_{p_n}, \sigma \from 1 \to (\ul{\bB^n} \to \deno{T}))\,.
    \]

  Now this $\sigma$ necessarily factors as
  \[
    1 \xrightarrow{\hat{\sigma}}
    (\ul{\bB}^n \to \deno T) \xrightarrow{(m \to \deno T)}
    (\ul{\bB^n} \to \deno T)\,,
    \]
  where $\hat{\sigma}$ is compact.  
  Then, by compact definability in $\G$, $\hat\sigma$ is the denotation of some term $N \from \bool \to \cdots \to \bool \to T$, and it follows that our original morphism $\sigma$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ is the denotation of
  \[
    N\,\choose_{p_1}\,\cdots\,\choose_{p_n}\,.\qedhere
    \]
\end{proof}

\begin{theorem}[Full Abstraction for PA]
  Let $M,N \from T$ be observationally equivalent terms of PA.  
  Then $\deno M \sim_{\bP} \deno N$.
  \label{TheFullAbstractionPa}
\end{theorem}
\begin{proof}
  Suppose that $\deno M \not\sim_{\bP} \deno N$.
  So there is some $\alpha \from \deno T \to \bC$ such that $\bP(\deno{M};\alpha\downarrow) \ne \bP(\deno{N};\alpha\downarrow)$.

  Let $\bP(\deno M;\alpha\downarrow) = p$ and $\bP(\deno N;\alpha\downarrow) = q$, and suppose without loss of generality that $p>q$.
  Now there must be some finite subset $\V$ of $\Acc(\deno M;\alpha\downarrow)$ such that the combined probability of the sequences in $\V$ is still greater than $q$.  
  For each $u\in \V$, we can choose some compact $\alpha_u\subset \alpha$ such that $u$ is still accepted by $\deno M;\alpha_u$, by algebraicity.
  Since the set of compact elements below $\alpha$ is directed, there is some $\alpha'\subset \alpha$ such that $\alpha_u\subset \alpha'$ for each $u\in \V$.  
  Then we have
  \begin{mathpar}
    \bP(\deno{M};\alpha'\downarrow) > q
    \and
    \bP(\deno{N};\alpha'\downarrow) \le q\,,
  \end{mathpar}
  and therefore $\bP(\deno{M};\alpha'\downarrow) \ne \bP(\deno{N};\alpha'\downarrow)$.

  By Proposition \ref{PropProbabilityCompactDefinability}, $\alpha'$ is the denotation of some term $L\from T \to \com$, and our Computational Adequacy result (Proposition \ref{PropComputationalAdequacyPa}) then tells us that 
  \[
    \bP(L\,M\converges)=\bP(\deno M;\alpha'\downarrow)\ne\bP(\deno N;\alpha'\downarrow) = \bP(L\,N\converges)\,.
    \]
  Therefore, $M$ and $N$ are not observationally equivalent.
\end{proof}

\section{Comparison with a Kleisli Category Model}

An alternative way to model probability is using the Kleisli category construction that we considered in Chapter \ref{ChapMonads}.  
Specifically, we can consider the language IA${}_\bB$ as a probabilistic Algol variant, by treating the term $\ask_\bB$ as a coin flip that returns $\true$ or $\false$ each with probability $\frac12$.

Given a closed term $M\from\com$ of IA${}_\bB$, we define
\[
  \bP(M\converges) = \sum_{u\in\bB^*\colon M\converges_u\skipp} 2^{-|u|}\,,
  \]
since $2^{-|u|}$ is the probability of a particular sequence $u$ of $\true$ and $\false$ values occurring.
Here, the infinite sum means the supremum over all sums of finite subsets.
Similarly, given a Kleisli morphism $\sigma\from 1 \to \bC$ -- i.e., a morphism $\sigma\from 1 \to (\bB \to \bC)$ in $\G$, we can define
\[
  \bP(\sigma\downarrow) = \sum_{u\in\Acc(\sigma)} 2^{-|u|}\,.
  \]
Our Computational Adequacy result for IAX (Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy}) then gives us a Computational adequacy result for this model.

\begin{proposition}
  Let $M\from \com$ be a closed term of IA${}_\bB$.  
  Then $\bP(M\converges) = \bP(\deno M\downarrow)$.
\end{proposition}
\begin{proof}
  Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy} tell us that the set of sequences $u$ such that $M\converges_u\skipp$ is the same as the set $\Acc(\deno{M})$.
\end{proof}

We can define probabilistic observational equivalence and the probabilistic intrinsic equivalence $\sim_{\bP}$ in exactly the same way as we did for PA.  
Then the same argument we used in Theorem \ref{TheFullAbstractionPa} proves Full Abstraction for this model.

\begin{theorem}
  Let $M,N\from T$ be closed terms of IA${}_\bB$.  
  Then $M$ and $N$ are probabilistically observationally equivalent if and only if $\deno{M}\sim_{\bP}\deno{N}$.
\end{theorem}

This model is much easier to realize.  
What do we gain, then, from our more complicated model?

The most obvious answer is that our original model allowed us to work with arbitrary probabilities, rather than using a fixed coin with probability $\frac12$.  
This is not such a great advantage as it might seem, since if $p\in[0,1]$ is any real number whose binary expansion is computable as a function $\bN \to \bB$, then we can simulate $\choose_p$ within the probabilistic version of IA${}_\bB$\footnote{Idea: build up a sequence of intervals $I_n$ of width $2^n$ by repeatedly flipping the coin and using the result to choose either the lower or the upper half of $I_{n-1}$.  
If at any point the upper bound of $I_n$ is less than or equal to $p$ (which can be checked by computing the first $n$ terms of the binary expansion of $p$, then return $\true$.  
If at any point the lower bound of $I_n$ is greater than or equal to $p$, return $\false$.}.

\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-04-27 Thesis/promonads.tex
Monthly commit.

@@
-\documentclass{article}
+\documentclass{report}[11pt]
 
@@
 
-\section{Promonads and parametric promonads}
+\chapter{Promonads and parametric promonads}
 \label{SecPromonads}
 
-The purpose of this section is to shine some light on the definition of the \Mellies category, showing why it is natural to think about $[\X,\Set]$-enriched categories and why the \Mellies category may be considered analogous to the Kleisli category.
+The purpose of this chapter is to shine some light on the definition of the \Mellies category, showing why it is natural to think about $[\X,\Set]$-enriched categories and why the \Mellies category may be considered analogous to the Kleisli category.
 
@@
 
-The first half of this section is, in the interests of completeness, fairly technical, and may be skimmed over on a first reading.  
-In section \ref{SecEndoprofunctors}, we introduce the multicategory of endoprofunctors on a category $\C$, which generalizes the monoidal category of endofunctors on $\C$.  
+The first half of this chapter is, in the interests of completeness, fairly technical, and may be skimmed over on a first reading.  
+In chapter \ref{SecEndoprofunctors}, we introduce the multicategory of endoprofunctors on a category $\C$, which generalizes the monoidal category of endofunctors on $\C$.  
 As monoids in $\End(\C)$ are called monads on $\C$, so we will call monoids in $\Endoprof(\C)$ \emph{promonads} on $\C$.  
@@
 
-\subsection{Multicategories}
+\section{Multicategories}
 
@@
 
-\subsection{Representable multicategories}
+\section{Representable multicategories}
 
@@
 
-\subsection{Product and unit multicategories}
+\section{Product and unit multicategories}
 
@@
 
-\subsection{Multifunctors and multinatural transformations}
+\section{Multifunctors and multinatural transformations}
 
@@
 
-\subsection{Monoids in multicategories}
+\section{Monoids in multicategories}
 
@@
 
-\subsection{Categories enriched over multicategories}
+\section{Categories enriched over multicategories}
 
@@
 
-\subsection{Multicategory-enriched functors and natural transformations}
+\section{Multicategory-enriched functors and natural transformations}
 
@@
 
-\subsection{The categories enriched over a symmetric multicategory form a multicategory}
+\section{The categories enriched over a symmetric multicategory form a multicategory}
 
@@
 
-\subsection{Change of base}
+\section{Change of base}
 
@@
 
-\subsection{Closed multicategories}
+\section{Closed multicategories}
 
@@
 
-\subsection{The multicategory of endoprofunctors}
+\section{The multicategory of endoprofunctors}
 \label{SecEndoprofunctors}
@@
           \&
-            \& \\
+            \&
     \end{tikzcd}
@@
 
-\subsection{Functors are a special case of profunctors}
+\section{Functors are a special case of profunctors}
 
@@
 
-\subsection{Promonads are categories}
+\section{Promonads are categories}
 
@@
 
-\subsection{The multicategory of functors}
+\section{The multicategory of functors}
 
@@
 
-\subsection{Monoids on functors are multifunctors}
+\section{Monoids on functors are multifunctors}
 It might seem strange that the objects of the multicategory of functors are ordinary functors, ignoring the monoidal structure of $\X$ and the multicategory structure of $\M$.  
@@
 
-\subsection{Two perspectives on monoids in $\Set$}
-
-We now come to our main result of the section.  
+\section{Two perspectives on monoids in $\Set$}
+
+We now come to our main result of the chapter.  
 By way of motivation, consider the two ways of generalizing the notion of an internal monoid in $\Set$.

### 2019-04-27 Thesis/thesis.tex
Monthly commit.

@@
 The rationale behind this is twofold: firstly, we do not wish to assume too much about the underlying category $\G$ beyond the fact that it gives us a good model of Idealized Algol.  
+Reader monads can be constructed for any object inside any Cartesian closed category.
 Secondly, in order to get a compositional semantics for the $\lambda$-calculus, it is important that the Kleisli categories we consider are themselves Cartesian closed.  
+Theorem \ref{FunctionalCompletenessCcc} tells us that this is the case for the Kleisli categories of reader monads on categories that are themselves Cartesian closed, but this may not be the case for other monads we can build from the Cartesian closed structure on our base category, such as state monads.
 
@@
 \begin{definition}
-  Fix some constant value $\top \in X$ (the precise value does not matter).
   We inductively define terms in context $\tr_u\from \nat \to X$ of \emph{ordinary deterministic} Idealized Algol for each $u\in X^*$ as follows.
   \begin{mathpar}
-    \tr_\epsilon = \lambda n.\top
+    \tr_\epsilon = \lambda n.\Omega
     \and
@@
           {
-            \inferrule*
+            \inferrule*[sep=5pt]
             {
@@
               \\
-              \inferrule*
+              \inferrule*[sep=5pt]
               {
@@
 
-First recall the statement of Computational Adequacy for $\G$:
-
-\begin{proposition}
-  Let $M\from \com$ be a closed term of Idealized Algol and suppose that
-  \[
-    ,()\ts M\converges \skipp,()\,.
-    \]
-  Then $\deno{M} \ne \bot$.
-\end{proposition}
+First recall the statement of Computational Adequacy for $\G$ (Theorem \ref{TheComputationalAdequacyIA} if $\G$ is the category of games):
+
+\begin{theorem}
+  Let $M\from \com$ be a closed term of Idealized Algol.  
+  Then
+  \[
+    \blank,()\ts M\converges \skipp,()\,.
+    \]
+  if and only if $\deno{M} \ne \bot$.
+\end{theorem}
 
@@
 
-\begin{proposition}[Soundness]
+\begin{definition}
+  Let $\sigma \from 1 \to \bC$ be a morphism in $\G_X$, considered as a morphism $(X \to \bC)$ in $\G$.  
+  We say that $\sigma\downarrow_u$ if the composite
+  \[
+    1 \xrightarrow{\sigma}
+    (X \to \bC) \xrightarrow{\eta_u}
+    (\Var \to \bN) \xrightarrow{\deno{\neww}}
+    \bN \xrightarrow{t_{|u|}}
+    \bC
+    \]
+  is not equal to $\bot$.
+\end{definition}
+
+\begin{proposition}
   Let $M\from\com$ be a closed term of \IAX, let $u\in X^*$ be a sequence and suppose that
   \[
-    ,()\ts M\converges_u\skipp,()\,.
+    \blank,()\ts M\converges_u\skipp,()\,.
     \]
   Let the denotation $\deno{M} \from 1 \to \com$ in $\G_X$ be considered as a morphism $1 \to (X \to \bC)$ in $\G$.
-  Then the composite
+  Then $\deno{M}\downarrow_u$; i.e., the composite
   \[
@@
   We can prove this using the following derivation tree.
-  \[
-    \inferrule*
-    {
-      \inferrule*[sep=1.7em]
+  \tiny
+  \[
+    \inferrule*
+    {
+      \inferrule*[sep=0em]
       {
@@
     {
-      ,()\ts\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v) \converges |u|,()
+      \blank,()\ts\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v) \converges |u|,()
     }\qedhere
     \]
+  \normalsize
 \end{proof}
@@
   \]
-for $k\le |u|$ or
-\[
-  \begin{array}{ccc}
-    X         & \bC & \bN \\
-              &     &  q  \\
-              &  q  &     \\
-    q         &     &     \\
-    u^{(0)}   &     &     \\
-    \vdots    &     &     \\
-    q         &     &     \\
-    u^{(|u|-1)}&     &     \\
-    q         &     &     \\
-    \top      &     &     \\
-    \vdots    &     &     \\
-    q         &     &     \\
-    \top      &     &     \\
-              &  a  &     \\
-              &     &  k  \\
-  \end{array}\,,
-  \]
-for $k>|u|$, where the component in $X,\bC$ is a valid play of $\sigma$.
+for $k\le |u|$, where the component in $X,\bC$ is a valid play of $\sigma$.
 Moreover, the strategy $t_n$ is the one with maximal plays of the form
@@
 We can now prove computational adequacy for our model.
+We have proved one direction already in Proposition \ref{PropKleisliSoundness}, so it suffices to prove the other direction.
 
@@
   \[
-    ,()\ts M\converges_u \skipp,()\,.
+    \blank,()\ts M\converges_u \skipp,()\,.
     \]
@@
   \[
-    ,()\ts M \converges_u \skipp,()
+    \blank,()\ts M \converges_u \skipp,()
     \]
@@
   \[
-    ,()\ts C[M] \converges_u \skipp,() \Longleftrightarrow ,()\ts C[N] \converges_u \skipp,()\,\text{--}
+    \blank,()\ts C[M] \converges_u \skipp,() \Longleftrightarrow \blank,()\ts C[N] \converges_u \skipp,()\,\text{--}
     \]
@@
   \[
-    ,()\ts M \converges \skipp,()\,.
+    \blank,()\ts M \converges \skipp,()\,.
     \]
@@
   Let $M,N\from T$ be closed terms of \IAX. Then $M,N$ are may-observationally equivalent -- i.e., for all contexts $C[-]\from \com$ of \IAX with a hole of type $T$, \[
-    ,()\ts C[M] \converges \skipp,() \Leftrightarrow ,()\ts C[N] \converges \skipp,()\,\text{--}
+    \blank,()\ts C[M] \converges \skipp,() \Leftrightarrow \blank,()\ts C[N] \converges \skipp,()\,\text{--}
     \]
@@
 
-  Suppose that $,()\ts C[M] \converges \skipp,()$.  
-  So there is some sequence $u\in X^*$ such that $,()\ts C[M] \converges_u \skipp,()$ and therefore the composite
+  Suppose that $\blank,()\ts C[M] \converges \skipp,()$.  
+  So there is some sequence $u\in X^*$ such that $\blank,()\ts C[M] \converges_u \skipp,()$ and therefore the composite
   \[
@@
     \]
-  Therefore, $,()\ts C[N] \converges_v \skipp,()$ and so $,()\ts C[N] \converges \skipp,()$.
+  Therefore, $\blank,()\ts C[N] \converges_v \skipp,()$ and so $\blank,()\ts C[N] \converges \skipp,()$.
   The reverse direction is identical.
@@
 \begin{example}
-  $,()\ts \Y(\lambda x.x)\diverges$ because it has the following infinite derivation tree.
-  \[
-    \inferrule*
-    {
-      \inferrule*
-      {
-        \inferrule*
-        {
-        }
-        {
-          ,()\ts (\lambda x.x) \converges (\lambda x.x),()
+  $\blank,()\ts \Y(\lambda x.x)\diverges$ because it has the following infinite derivation tree.
+  \[
+    \inferrule*
+    {
+      \inferrule*
+      {
+        \inferrule*
+        {
+        }
+        {
+          \blank,()\ts (\lambda x.x) \converges (\lambda x.x),()
         }
@@
         {
-          ,() \ts \Y(\lambda x.x)\diverges
-        }
-      }
-      {
-        ,()\ts (\lambda x.x)(\Y(\lambda x.x)) \diverges
-      }
-    }
-    {
-      ,()\ts \Y(\lambda x.x)\diverges
+          \blank,() \ts \Y(\lambda x.x)\diverges
+        }
+      }
+      {
+        \blank,()\ts (\lambda x.x)(\Y(\lambda x.x)) \diverges
+      }
+    }
+    {
+      \blank,()\ts \Y(\lambda x.x)\diverges
     }
@@
   Let $M\from \com$ be a closed term of \IAX and consider the denotation $\deno M \from 1 \to \bC$ in $\G_X$ as a morphism $1 \to (X \to \bC)$ in $\G$.
-  Then $,()\ts M\mustconverge$ if and only if $\deno{M}\downarrow_{\must}$.
+  Then $\blank,()\ts M\mustconverge$ if and only if $\deno{M}\downarrow_{\must}$.
   \label{CorAdeqMust}
@@
   Let $M\from \com$ be a closed term of \IAX and consider the denotation $\deno M \from 1 \to \bC$ in $\G_X$ as a morphism $X \to \bC$ in $\G$.
-  Then $,()\ts M\mustconverge$ if and only if this strategy is winning.
+  Then $\blank,()\ts M\mustconverge$ if and only if this strategy is winning.
 \end{corollary}

### 2019-05-06 Thesis/games.tex
Did some things.

@@
 
+\section{Tree Immersions and Zigzag Strategies}
+
+So far, the strategies we have been considering have all been innocent.  
+We now start considering some non-innocent strategies.
+
+We can generalize the subset inclusions of the previous chapter to \emph{tree immersions}.  
+Tree immersions are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
+A consequence of this is that while tree immersions do give rise to strategies, these strategies are not in general innocent.
+
+\begin{definition}
+  Let $A,B$ be games.  
+  A \emph{tree immersion} from $A$ to $B$ is a function $\phi\from P_A \hookrightarrow P_B$ such that
+  \begin{itemize}
+    \item $\phi$ preserves length and justification indices; 
+    \item for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$; and
+    \item if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
+  \end{itemize}
+
+  Given a tree immersion $\phi$ from $A$ to $B$, we define a strategy $\zz_\phi\from B \implies A$ by
+  \[
+    \zz_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
+    \]
+\end{definition}
+\begin{example}
+  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree immersion from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
+\end{example}
+
+\begin{proposition}
+  $\zz_\phi$ is a strategy.  
+\end{proposition}
+\begin{proof}
+  $\zz_\phi$ is a prefix-closed subset of $P_{B\implies A}$ by definition.  
+  If $sab,sac\in\zz_\phi$, then we have $s\vert_B=\phi(s\vert_A)$ and $sab\vert_B=\phi(sab\vert_A)$.
+  Since $\phi$ is length-preserving, $s\vert_A$ and $s\vert_B$ must have the same length, and the same is true of $sab\vert_A$ and $sab\vert_B$.  
+  Therefore, either $a$ is a move in $A$ and $s\vert_Bb=\phi(s\vert_Aa)$ or $a$ is a move in $B$ and $s\vert_Ba=\phi(s\vert_Ab)$.  
+  The same applies to $c$: so either $s\vert_Bb=\phi(s\vert_Aa)=s\vert_Bc$ or $\phi(s\vert_Ab)=s\vert_Ba=\phi(s\vert_Ac)$.  
+  In either case, we have $b=c$.
+\end{proof}
+
+We want an analogue of Proposition \ref{PropCopycat}.
+
+\begin{definition}
+  Given a tree immersion from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
+\end{definition}
+
+\begin{proposition}
+  If $\sigma\from C \implies B$ is a strategy, then $\sigma;\zz_\phi$ is given by
+  \[
+    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\}\,.
+    \]
+
+  In particular, if $\phi$ is a tree immersion from $A$ to $B$ and $\psi$ is a tree immersion from $B$ to $C$, then $\psi\circ\phi$ is a tree immersion from $A$ to $C$ and $\zz_{\psi\circ\phi}=\zz_\psi;\zz_\phi$.
+  \label{PropTree}
+\end{proposition}
+\begin{proof}
+  Suppose that $\s\in\sigma\|\zz_\phi$.  
+  Then $\s\vert_{C,B}\in\sigma$ and $t\vert_B=\phi(t\vert_A)$ for all even-length $t\prefix \s\vert_{B,A}$.  
+  Then it is clear that $(\s\vert_{C,A})^\phi=\s\vert_{C,B}$.
+
+  Conversely, suppose that $s\in P_{C\implies A}$ and that $s^\phi\in\sigma$.  
+  We construct a sequence $\s\in\sigma\|\zz_phi$ such that $\s\vert_{C,B}=s^\phi$ and $\s\vert_{C,A}=s$ by taking the sequence $s$ and inserting, in order, the elements of the sequence $\phi(s\vert_A)$ immediately after each $O$-move in $s\vert_C$ and immediately before each $P$-move in $C$, leaving the rest of $s$ intact.
+  Then $\s\vert_{C,B}=s^\phi\in\sigma$ and $\s\vert_{B,A}\in\zz_\phi$, by construction.  
+  So $s=\s\vert_{C,A}\in \sigma;\zz_\phi$.
+\end{proof}
+
+\begin{definition}
+  We say that a tree immersion $\phi$ is a \emph{tree isomorphism} if it is a bijection.
+\end{definition}
+
+\begin{proposition}
+  If $\phi$ is a tree isomorphism from a game $A$ to a game $B$, then $\zz_\phi$ is an isomorphism in $\G$.
+\end{proposition}
+\begin{proof}
+  If $\phi$ is a tree isomorphism, then its inverse $\phi\inv$ is also a tree isomorphism, and Proposition \ref{PropTree} tells us that $\zz_\phi$ and $\zz_{\phi\inv}$ are inverses in $\G$.
+\end{proof}
+
+More generally:
+
+\begin{proposition}
+  If $\phi$ is a surjection, then $\zz_\phi$ is a monomorphism.
+  \label{PropZigzagMono}
+\end{proposition}
+\begin{proof}
+  Let $\sigma,\tau\from C \implies B$ be strategies.
+  Then, by Proposition \ref{PropTree}, we have
+  \[
+    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\} = \{s\in P_{C\implies A}\suchthat s^\phi\in\tau\}\,.
+    \]
+  Let $t\in\sigma$.  
+  Then, since $\phi$ is surjective, there is some $u\in P_A$ such that $\phi(u)=t\vert_B$.  
+  As before, we may construct some sequence $t'$ such that $t'\vert_A=u$ and $t=(t')^\phi$.  
+  Then, since $(t')^\phi=t\in\sigma$, we must have $(t')^\phi\in\tau$; i.e., that $t\in\tau$.  
+  So $\sigma\subset\tau$.
+
+  Similarly, $\tau\subset\sigma$, and so $\sigma$ and $\tau$ are equal.
+\end{proof}
+
 \section{Products in $\G$}
@@
 \begin{proposition}
-  Let $A_i,B$ be games and let $\phi_i$ be tree embeddings from $A_i$ to $B$.  
-  Then $\langle \zz_{\phi_i} \rangle = \zz_\phi$, where $\phi$ is the tree embeddings from $\prod_iA_i$ to $B$ given by
+  Let $A_i,B$ be games and let $\phi_i$ be tree immersions from $A_i$ to $B$.  
+  Then $\langle \zz_{\phi_i} \rangle = \zz_\phi$, where $\phi$ is the tree immersion from $\prod_iA_i$ to $B$ given by
   \[
@@
 \begin{proof}
-  The only thing we really need to check is that this is indeed a tree embedding.  
+  The only thing we really need to check is that this is indeed a tree immersion.  
   Let $sb,sc$ be positions in $\prod_iA_i$, where $b,c$ are $P$-moves.
@@
 Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and there is no version of Proposition \ref{PropProductOfTreeEmbeddings} that works for subset inclusion strategies.
-Of course, since a subset inclusion is a special case of a tree embedding, then $\langle \subs_i\rangle$ is always a tree embedding strategy.
+Of course, since a subset inclusion is a special case of a tree immersion, then $\langle \subs_i\rangle$ is always a tree immersion strategy.
 
@@
 
-\section{Tree Embeddings and Zigzag Strategies}
-
-So far, the strategies we have been considering have all been innocent.  
-We now start considering some non-innocent strategies.
-
-We can generalize the subset inclusions of the previous chapter to \emph{tree embeddings}.  
-Tree embeddings are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
-A consequence of this is that while tree embeddings do give rise to strategies, these strategies are not in general innocent.
-
-\begin{definition}
-  Let $A,B$ be games.  
-  A \emph{tree embedding} from $A$ to $B$ is a function $\phi\from P_A \hookrightarrow P_B$ such that
-  \begin{itemize}
-    \item $\phi$ preserves length and justification indices; 
-    \item for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$; and
-    \item if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
-  \end{itemize}
-
-  Given a tree embedding $\phi$ from $A$ to $B$, we define a strategy $\zz_\phi\from B \implies A$ by
-  \[
-    \zz_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
-    \]
-\end{definition}
-\begin{example}
-  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree embedding from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
-\end{example}
-
-\begin{proposition}
-  $\zz_\phi$ is a strategy.  
-\end{proposition}
-\begin{proof}
-  $\zz_\phi$ is a prefix-closed subset of $P_{B\implies A}$ by definition.  
-  If $sab,sac\in\zz_\phi$, then we have $s\vert_B=\phi(s\vert_A)$ and $sab\vert_B=\phi(sab\vert_A)$.
-  Since $\phi$ is length-preserving, $s\vert_A$ and $s\vert_B$ must have the same length, and the same is true of $sab\vert_A$ and $sab\vert_B$.  
-  Therefore, either $a$ is a move in $A$ and $s\vert_Bb=\phi(s\vert_Aa)$ or $a$ is a move in $B$ and $s\vert_Ba=\phi(s\vert_Ab)$.  
-  The same applies to $c$: so either $s\vert_Bb=\phi(s\vert_Aa)=s\vert_Bc$ or $\phi(s\vert_Ab)=s\vert_Ba=\phi(s\vert_Ac)$.  
-  In either case, we have $b=c$.
-\end{proof}
-
-We want an analogue of Proposition \ref{PropCopycat}.
-
-\begin{definition}
-  Given a tree embedding from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
-\end{definition}
-
-\begin{proposition}
-  If $\sigma\from C \implies B$ is a strategy, then $\sigma;\zz_\phi$ is given by
-  \[
-    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\}\,.
-    \]
-
-  In particular, if $\phi$ is a tree embedding from $A$ to $B$ and $\psi$ is a tree embedding from $B$ to $C$, then $\psi\circ\phi$ is a tree embedding from $A$ to $C$ and $\zz_{\psi\circ\phi}=\zz_\psi;\zz_\phi$.
-  \label{PropTree}
-\end{proposition}
-\begin{proof}
-  Suppose that $\s\in\sigma\|\zz_\phi$.  
-  Then $\s\vert_{C,B}\in\sigma$ and $t\vert_B=\phi(t\vert_A)$ for all even-length $t\prefix \s\vert_{B,A}$.  
-  Then it is clear that $(\s\vert_{C,A})^\phi=\s\vert_{C,B}$.
-
-  Conversely, suppose that $s\in P_{C\implies A}$ and that $s^\phi\in\sigma$.  
-  We construct a sequence $\s\in\sigma\|\zz_phi$ such that $\s\vert_{C,B}=s^\phi$ and $\s\vert_{C,A}=s$ by taking the sequence $s$ and inserting, in order, the elements of the sequence $\phi(s\vert_A)$ immediately after each $O$-move in $s\vert_C$ and immediately before each $P$-move in $C$, leaving the rest of $s$ intact.
-  Then $\s\vert_{C,B}=s^\phi\in\sigma$ and $\s\vert_{B,A}\in\zz_\phi$, by construction.  
-  So $s=\s\vert_{C,A}\in \sigma;\zz_\phi$.
-\end{proof}
-
-\begin{definition}
-  We say that a tree embedding $\phi$ is a \emph{tree isomorphism} if it is a bijection.
-\end{definition}
-
-\begin{proposition}
-  If $\phi$ is a tree isomorphism from a game $A$ to a game $B$, then $\zz_\phi$ is an isomorphism in $\G$.
-\end{proposition}
-\begin{proof}
-  If $\phi$ is a tree isomorphism, then its inverse $\phi\inv$ is also a tree isomorphism, and Proposition \ref{PropTree} tells us that $\zz_\phi$ and $\zz_{\phi\inv}$ are inverses in $\G$.
-\end{proof}
-
-More generally:
-
-\begin{proposition}
-  If $\phi$ is a surjection, then $\zz_\phi$ is a monomorphism.
-  \label{PropZigzagMono}
-\end{proposition}
-\begin{proof}
-  Let $\sigma,\tau\from C \implies B$ be strategies.
-  Then, by Proposition \ref{PropTree}, we have
-  \[
-    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\} = \{s\in P_{C\implies A}\suchthat s^\phi\in\tau\}\,.
-    \]
-  Let $t\in\sigma$.  
-  Then, since $\phi$ is surjective, there is some $u\in P_A$ such that $\phi(u)=t\vert_B$.  
-  As before, we may construct some sequence $t'$ such that $t'\vert_A=u$ and $t=(t')^\phi$.  
-  Then, since $(t')^\phi=t\in\sigma$, we must have $(t')^\phi\in\tau$; i.e., that $t\in\tau$.  
-  So $\sigma\subset\tau$.
-
-  Similarly, $\tau\subset\sigma$, and so $\sigma$ and $\tau$ are equal.
-\end{proof}
-
 \section{Sequoidally decomposable categories}
@@
   Let $(A_i),X$ be games.
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree embedding $\phi\from P_{\prod_i(A_i\sequoid X)}\to P_{\prod_iA_i\sequoid X}$ defined as follows.
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree immersion $\phi\from P_{\prod_i(A_i\sequoid X)}\to P_{\prod_iA_i\sequoid X}$ defined as follows.
   \[
@@
 \begin{proof}
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree embedding 
+  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree immersion 
   \[
@@
     \]
-  is given by the tree embedding $\phi$ from $(A \sequoid B) \times (B \sequoid A)$ to $A \tensor B)$ given by
+  is given by the tree immersion $\phi$ from $(A \sequoid B) \times (B \sequoid A)$ to $A \tensor B)$ given by
   \[
@@
     \]
-  We claim that this tree embedding is a bijection.  
+  We claim that this tree immersion is a bijection.  
   Indeed, it is certainly injective.
@@
 
-  The morphism in question is the (non-innocent) zigzag strategy given by the tree embedding $\phi_n\from P_{A^{\sequoid n}}\to P_{\oc A}$ defined by
+  The morphism in question is the (non-innocent) zigzag strategy given by the tree immersion $\phi_n\from P_{A^{\sequoid n}}\to P_{\oc A}$ defined by
   \[
@@
 \section{Arena-only Semantics}
+\label{SecArenaOnly}
 

### 2019-05-06 Thesis/pmonads2.tex
Did some things.

@@
   We write $\Acc(\sigma)$ for the set of all sequences accepted by $\sigma$.
+
+  More generally, if $\sigma\from 1 \to (X \to A)$ is a \Mellies morphism and $\tau\from 1 \to A$ is an ordinary morphism in $\G$, we write
+  \[
+    \Acc_\tau(\sigma) = \{u\in X^*\suchthat \sigma;\xi_u = \tau\}\,.
+    \]
+  When $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$.
+  \label{DefAcc}
 \end{definition}
@@
 \begin{proposition}
-  Let $\sigma\from 1 \to (j(p) \to \bC)$, $\tau\from 1 \to (j(q) \to \bC)$ be two representatives of the same morphism $1 \to \bC$ in $\G/\oppcat\X$.  
-  Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
+  Let $\sigma\from 1 \to (j(p) \to A)$, $\sigma'\from 1 \to (j(q) \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
+  Let $\tau\from 1 \to A$ be an ordinary morphism in $\G$.
+  Then $(p,\Acc_\tau(\sigma))$ and $(q,\Acc_\tau(\sigma'))$ are equivalent.
+  In particular, if $A=\bC$, then $(p,\Acc(\sigma))$ and $(q,\Acc(\sigma')$ are equivalent.
   \label{PropAccEquivalent}
@@
 \begin{proof}
-  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\tau$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \tau;(j(f)\to \bC)$.
+  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\sigma'$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \sigma';(j(f)\to \bC)$.
 
@@
   \begin{IEEEeqnarray*}{rCl}
-    u\in\Acc(\sigma) & \Leftrightarrow & \sigma;\xi_u\ne\bot \\
-    & \Leftrightarrow & \tau;(j(f)\to\bC);\xi_u\ne\bot \\
-    & \Leftrightarrow & \tau;\xi_{j(f)_*u}\ne\bot \\
-    & \Leftrightarrow & j(f)_*u \in \Acc(\tau)\,.
+    u\in\Acc_\tau(\sigma) & \Leftrightarrow & \sigma;\xi_u=\tau \\
+    & \Leftrightarrow & \sigma';(j(f)\to A);\xi_u=\tau \\
+    & \Leftrightarrow & \sigma';\xi_{j(f)_*u}=\tau \\
+    & \Leftrightarrow & j(f)_*u \in \Acc_\tau(\sigma')\,.
   \end{IEEEeqnarray*}
-  Therefore, $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
+  Therefore, $(p,\Acc_\tau(\sigma))$ and $(q,\Acc_\tau(\sigma'))$ are equivalent.
 \end{proof}
@@
   \[
-    \bP(V, \Acc(\sigma)\,.
+    \bP(V, \Acc(\sigma))\,.
     \]
@@
 
+Perhaps a better way of thinking about the difference between the two models, then, is to consider what the denotation of a term actually looks like.  
+In the language IA${}_\bB$, we can define a term that converges to $\true$ with probability $\frac23$ and to $\false$ with probability $\frac13$ by
+\[
+  \Y_\bool(\lambda b.\If \choose_{\frac12} \Then \true \Else (\If \choose_{\frac12} \Then b \Else \false))\,.
+  \]
+Here, we have renamed $\ask_{\bB}$ to $\choose_{\frac12}$ to give a better idea of what the term does in the probabilistic setup.
+
+Now the denotation of this term in $\Kl_{R_{\bB}}\G$ is given by the denotation of the term-in-context
+\[
+  c\from\bool\ts\Y_{\bool}(\lambda b.\If c \Then \true \Else (\If c \Then b \Else \false))
+  \]
+in $\G$.
+If $\G$ is the category of games, then this morphism is the strategy with maximal plays taking one of the following two forms.
+\begin{mathpar}
+  q(q\false q\true)^nq\true \true
+  \and
+  q(q\false q\true)^nq\false q\false\false
+\end{mathpar}
+In other words, it is not at all clear from the denotation that the term should give $\true$ with probability $\frac23$ and $\false$ with probability $\frac13$.
+
+In $\G/\Rv_{\Omega}^{FS}$, however, we can model a term that has the same behaviour using the morphism
+\[
+  \left(V_{\frac23}, \id_\bB\right)\,,
+  \]
+which makes it much clearer what the probabilistic behaviour is.
+
+\section{The Probabilistic Equivalence Relation on Morphisms}
+
+\begin{definition}
+  Let $A$ be an object of $\G$.  
+  Let $(V\from\Omega \to X,\sigma\from X \to A)$ be a morphim $1\to A$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, and let $\tau \from 1 \to A$ be a morphism in $\G$.  
+  Recall from \ref{DefAcc} the definition
+  \[
+    \Acc_\tau(\sigma) = \{u\in X^* \suchthat \sigma;\xi_u = \tau\}\,.
+    \]
+  Now we define
+  \[
+    \bP(\sigma = \tau)
+    \]
+  to be
+  \[
+    \bP(V,\Acc_\tau(\sigma))\,.
+    \]
+  Given Kleisli morphisms $\sigma,\tau\from 1 \to A$, we say that $\sigma\approx_{\bP}\sigma'$ if for all $\tau\from 1 \to A$, we have
+  \[
+    \bP(\sigma = \tau) = \bP(\sigma' = \tau)\,.
+    \]
+  \label{DefProbEquiv}
+\end{definition}
+\begin{remark}
+  In the case that $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$ and
+  \[
+    \bP(\sigma\converges) = \bP(\sigma = \deno{\skipp}) = 1 - \bP(\sigma = \bot)\,.
+    \]
+  Then $\sigma\approx_{\bP}\sigma'$ if and only if $\bP(\sigma\converges)=\bP(\sigma'\converges)$.
+\end{remark}
+
+\begin{proposition}
+  i) Definition \ref{DefProbEquiv} is well defined.  
+  I.e., let
+  \begin{mathpar}
+    (V\from\Omega \to X,\sigma\from 1 \to (X \to A))
+    \and
+    (W\from\Omega \to Y,\sigma'\from 1 \to (Y \to A))
+  \end{mathpar}
+  be representatives for the same morphism in $\G/\Rv_{\Omega}^{FS}$, and let $\tau \from 1 \to A$ be an ordinary morphism in $\G$.  
+  Then $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.  
+\end{proposition}
+\begin{proof}
+  By Proposition \ref{PropAccEquivalent}, $(V,\Acc_\tau(\sigma))$ and $(W,\Acc_\tau(\sigma'))$ are equivalent pairs, and therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.
+\end{proof}
+
+\section{Danos-Harmer Probabilistic Game Semantics}
+
+We really want to show that the equivalence relation $\approx_{\bP}$ respects composition of morphisms, but this does not seem to be possible in the general setting.  
+Accordingly, we pass now to the special case when $\G$ is the category of games and strategies.  
+More specifically, we shall use the arena-only semantics which we developed in \sec\ref{SecArenaOnly} -- so the objects of our category $\G$ will be arenas and the morphisms will be single-threaded strategies between arenas.
+
+\begin{definition}
+  Let $\sigma,\sigma'$ be strategies $A \to B$.  
+  We say that $\sigma\approx_\bP\sigma'$ if $\Lambda(\sigma)\approx_{\bP}\Lambda(\sigma')$ as strategies $1 \to (A \to B)$.
+\end{definition}
+
+\begin{definition}
+  Let $X$ be a set and let $u\in X^*$ be a sequence.  
+  Consider $X$ as an arena $\ul X$.  
+  Then we write $qu$ for the play in $\ul X$ given by
+  \[
+    q\,u^{(1)}\,\cdots\,q\,u^{(|u|-1)}\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  Let $X$ be a set, considered as an arena, and let $\sigma \from X \to A$ be a single-threaded strategy.
+  Let $\tau$ be a single-threaded strategy for $A$.  
+  Then, if $u\in X^*$ is a sequence, we have $u\in\Acc_\tau(\sigma)$ if and only if
+  \[
+    \{s\vert_A \suchthat s\in\sigma;\,s\vert_{\ul X} = qu\} = \tau\,.
+    \]
+\end{proposition}
+\begin{proof}
+  Immediate from the definition of composition and from our description of the strategy $\xi_u$.
+\end{proof}
+
+\begin{definition}
+  Recall that we have written $s\vert_A$ for the restriction of a sequence in a compound game to the moves occurring in some constituent part $A$, and similarly for a list $s\vert_{A_1,\cdots,A_n}$.
+  If $s$ is a sequence in an arena of the form $\ul{X\times Y}$; i.e., the arena in which player $O$ has an initial move $q$ to which player $P$ replies with some pair $(x,y)\in X\times Y$, the we write $s\vert_X$ for the play formed by projecting every such pair $(x,y)$ on to its first component $x$.
+\end{definition}
+
+\begin{lemma}
+  Let $\sigma\from A \to (\ul{X} \to B)$, $\tau \from B \to (\ul{Y} \to C)$ be strategies, where $X,Y$ are sets.
+  Write $\sigma\semicom_{\text{Mell}}\tau \from A \to (\ul{X\times Y} \to C)$ for the \Mellies composition of $\sigma$ and $\tau$.
+
+  Let $s\in\sigma\semicom_{\text{Mell}}\tau$.  
+  Then there exist four sequence $s_X,s_Y,\s_X,\s_Y$ such that
+  \begin{itemize}
+    \item $s$ is an interleaving of the sequences $s_X$ and $s_Y$;
+    \item $\s_X\in\sigma$ and $\s_Y\in\tau$;
+    \item $s_X\vert_{A,X} = \s_X\vert_{A,X}$; and
+    \item $s_Y\vert_{C,Y} = \s_Y\vert_{C,Y}$.
+  \end{itemize}
+  \label{LemMelliesDecomposition}
+\end{lemma}
+\begin{proof}
+  Recall that $\sigma\semicom_{\text{Mell}}\tau$ is given by the following composite in $\G$, where $\mu$ is the composite $\langle\ul{\pr_X},\ul{\pr_Y}\rangle$.
+  \[
+    A \xrightarrow{\sigma}
+    (\ul{X} \to B) \xrightarrow{\ul{X} \to \tau}
+    (\ul X \to (\ul Y \to C)) \to
+    ((\ul X \times \ul Y) \to C) \xrightarrow{\mu\to C}
+    (\ul{X\times Y} \to C)
+    \]
+  We consider the composite of the first two morphisms.  
+  We know that a play $t\in \sigma;(\X\to \tau)$ is given by $\s\vert_{A,X,Y,C}$, where $\s\vert_{A,X,B}\in\sigma$ and $\s\vert_{B,Y,C}\in\tau$.
+  Write $\s_X$ for $\s\vert_{A,X,B}$ and $\s_Y$ for $\s\vert_{B,Y,C}$.
+
+  Now suppose that $s$ is a sequence in the whole composition, and let
+  \[
+    \t\in ((A\times\mu);\cong)\|((\sigma\times \ul Y);\tau)
+    \]
+  be such that $\t\vert_{A,\ul{X \times Y}\to C}=s$.
+  Write $t=\t\vert_{A,\ul X \to (\ul Y \to C)}\in\sigma;(\ul X \to \tau)$ and let $\s$ cover $t$ as above.
+  Then $\t$ is formed from $t$ by inserting between every pair $q\,x$ of moves in $\ul X$ a pair $q\,(x,y_0)$ in $\ul{X\times Y}$ for some $y_0$, and between every pair $q\,y$ of moves in $\ul Y$ a pair $q\,(x_0,y)$ in $\ul{X \times Y}$ for some $x_0$.
+  This gives a partitition of $s\vert_{\ul {X \times Y}}$ into moves that occur before a move in $\ul X$ and moves that occur before a move in $\ul Y$ in the sequence $\t$.
+  We then define $s_X$ to be the sequence formed from $\s_X\vert_A$, together with those moves in $\ul{X \times Y}$ that occur before a move in $\ul X$ in $\t$, and $s_Y$ fto be formed from $\s_Y\vert_C$, together with those moves in $\ul{X\times Y}$ that occur before a move in $\ul Y$ in $\t$.
+
+  Then we have $s_X\vert_{A,X}=\s_X\vert_{A,X}$ and $s_Y\vert_{C,Y} = \s_Y\vert_{C,Y}$ as desired.
+\end{proof}
+
+\begin{proposition}
+  Let $\sigma,\sigma'\from A \to B$ and $\tau,\tau'\from B \to C$ be morphisms in $\G/\Rv_{\Omega}^{FS}$, where $\G$ is the category of games and single-threaded strategies.
+  If $\sigma\approx_{\bP}\sigma'$ and $\tau\approx_\bP\tau'$, then $\sigma;\tau\approx_\bP\sigma';\tau'$.
+\end{proposition}
+\begin{proof}
+  Suppose that $\sigma$ is given by a single-threaded strategy $A \to (\ul X \to B)$ and $\tau$ by a single-threaded strategy $B \to (\ul Y \to C)$.
+
+  Suppose $s\in\sigma;\tau$ satisfies $s\vert_{\ul{X\times Y}}=qu$, for some sequence $u\in(X\times Y)^*$.
+  By Lemma \ref{LemMelliesDecomposition}, $s$ can be decomposed into sequences $s_X$ and $s_Y$ such that there are $\s_X\in\sigma$ and $\s_Y\in\tau$ with $\s_X\vert_{X,A}=s\vert_{X,A}$ and $\s_Y\vert_{Y,C}=s_Y\vert_{Y,C}$.
+  We have $\s_X\vert_X=qv$ and $\s_Y\vert_Y=qw$ for sequences $v\in X^*$ and $w\in Y^*$, and $s_X\vert_{X\times Y} = qV$ and $s_Y\vert_{X\times Y}=qW$ for sequences $V\in (X\times Y)^*,W\in (X\times Y)^*$ such that $(\pr_X)_*V = v$ and $(\pr_Y)_*W = w$, and such that $u$ is an interleaving of $V$ and $W$.
+
+  Now write $\hat\sigma$ for $\sigma;\xi_v$ and $\hat\tau$ for $\tau;\xi_w$.
+  We claim that $(\sigma;\tau);\xi_u = \hat{\sigma};\hat{\tau}$.
+
+  Thus, $\sigma$ and $\tau$ give rise to maps
+  \begin{mathpar}
+    \phi_{\sigma,\tau}\from (X\times Y)^* \to X^* \times Y^*
+    \and
+    \Phi_{\sigma,\tau}\from (X\times Y)^* \to (X\times Y)^* \times (X \times Y)^*
+  \end{mathpar}
+  (sending $u$ to $(v,w)$ and to $(V,W)$ respectively), such that the components of $\Phi(u)$ form a decomposition of $u$, and such that $\phi(u) = ((\pr_X)_*\times(\pr_Y)_*)(\Phi(u))$.
+\end{proof}
+
 \bibliographystyle{alpha2}

### 2019-05-06 Thesis/pmonads2.tex
Nightly build.

@@
   We write $\Acc(\sigma)$ for the set of all sequences accepted by $\sigma$.
-
-  More generally, if $\sigma\from 1 \to (X \to A)$ is a \Mellies morphism and $\tau\from 1 \to A$ is an ordinary morphism in $\G$, we write
-  \[
-    \Acc_\tau(\sigma) = \{u\in X^*\suchthat \sigma;\xi_u = \tau\}\,.
-    \]
-  When $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$.
   \label{DefAcc}
@@
 \begin{proposition}
-  Let $\sigma\from 1 \to (j(p) \to A)$, $\sigma'\from 1 \to (j(q) \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
-  Let $\tau\from 1 \to A$ be an ordinary morphism in $\G$.
-  Then $(p,\Acc_\tau(\sigma))$ and $(q,\Acc_\tau(\sigma'))$ are equivalent.
-  In particular, if $A=\bC$, then $(p,\Acc(\sigma))$ and $(q,\Acc(\sigma')$ are equivalent.
+  Let $\sigma\from 1 \to (j(p) \to A)$, $\tau\from 1 \to (j(q) \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
+  Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau)$ are equivalent.
   \label{PropAccEquivalent}
@@
 \begin{proof}
-  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\sigma'$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \sigma';(j(f)\to \bC)$.
+  Since the relation on pairs $(p,\U)$ is an equivalence relation, it suffices to assume that $\sigma$ and $\sigma'$ are related by the relation that generates the equivalence relation on \Mellies morphisms; i.e., that there is a morphism $f\from p \to q$ such that $\sigma = \tau;(j(f)\to \bC)$.
 
@@
   \begin{IEEEeqnarray*}{rCl}
-    u\in\Acc_\tau(\sigma) & \Leftrightarrow & \sigma;\xi_u=\tau \\
-    & \Leftrightarrow & \sigma';(j(f)\to A);\xi_u=\tau \\
-    & \Leftrightarrow & \sigma';\xi_{j(f)_*u}=\tau \\
-    & \Leftrightarrow & j(f)_*u \in \Acc_\tau(\sigma')\,.
+    u\in\Acc(\sigma) & \Leftrightarrow & \sigma;\xi_u\ne\bot \\
+    & \Leftrightarrow & \tau;(j(f)\to A);\xi_u\ne\bot \\
+    & \Leftrightarrow & \tau\xi_{j(f)_*u}\ne\bot \\
+    & \Leftrightarrow & j(f)_*u \in \Acc(\tau)\,.
   \end{IEEEeqnarray*}
-  Therefore, $(p,\Acc_\tau(\sigma))$ and $(q,\Acc_\tau(\sigma'))$ are equivalent.
+  Therefore, $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
 \end{proof}
@@
 
-\section{The Probabilistic Equivalence Relation on Morphisms}
-
-\begin{definition}
-  Let $A$ be an object of $\G$.  
-  Let $(V\from\Omega \to X,\sigma\from X \to A)$ be a morphim $1\to A$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, and let $\tau \from 1 \to A$ be a morphism in $\G$.  
-  Recall from \ref{DefAcc} the definition
-  \[
-    \Acc_\tau(\sigma) = \{u\in X^* \suchthat \sigma;\xi_u = \tau\}\,.
-    \]
-  Now we define
-  \[
-    \bP(\sigma = \tau)
-    \]
-  to be
-  \[
-    \bP(V,\Acc_\tau(\sigma))\,.
-    \]
-  Given Kleisli morphisms $\sigma,\tau\from 1 \to A$, we say that $\sigma\approx_{\bP}\sigma'$ if for all $\tau\from 1 \to A$, we have
-  \[
-    \bP(\sigma = \tau) = \bP(\sigma' = \tau)\,.
-    \]
-  \label{DefProbEquiv}
-\end{definition}
-\begin{remark}
-  In the case that $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$ and
-  \[
-    \bP(\sigma\converges) = \bP(\sigma = \deno{\skipp}) = 1 - \bP(\sigma = \bot)\,.
-    \]
-  Then $\sigma\approx_{\bP}\sigma'$ if and only if $\bP(\sigma\converges)=\bP(\sigma'\converges)$.
-\end{remark}
-
-\begin{proposition}
-  i) Definition \ref{DefProbEquiv} is well defined.  
-  I.e., let
-  \begin{mathpar}
-    (V\from\Omega \to X,\sigma\from 1 \to (X \to A))
-    \and
-    (W\from\Omega \to Y,\sigma'\from 1 \to (Y \to A))
-  \end{mathpar}
-  be representatives for the same morphism in $\G/\Rv_{\Omega}^{FS}$, and let $\tau \from 1 \to A$ be an ordinary morphism in $\G$.  
-  Then $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.  
-\end{proposition}
-\begin{proof}
-  By Proposition \ref{PropAccEquivalent}, $(V,\Acc_\tau(\sigma))$ and $(W,\Acc_\tau(\sigma'))$ are equivalent pairs, and therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.
-\end{proof}
-
-\section{Danos-Harmer Probabilistic Game Semantics}
-
-We really want to show that the equivalence relation $\approx_{\bP}$ respects composition of morphisms, but this does not seem to be possible in the general setting.  
-Accordingly, we pass now to the special case when $\G$ is the category of games and strategies.  
-More specifically, we shall use the arena-only semantics which we developed in \sec\ref{SecArenaOnly} -- so the objects of our category $\G$ will be arenas and the morphisms will be single-threaded strategies between arenas.
-
-\begin{definition}
-  Let $\sigma,\sigma'$ be strategies $A \to B$.  
-  We say that $\sigma\approx_\bP\sigma'$ if $\Lambda(\sigma)\approx_{\bP}\Lambda(\sigma')$ as strategies $1 \to (A \to B)$.
-\end{definition}
+\section{Game Semantics and Probability}
+
+We now specialize to the case that $\G$ is the category of arenas and single-threaded strategies that we developed in Chapters \ref{ChapGames} and \ref{ChapFullAbstraction}.
+This will allow us to capture the close relationship between the sequences $u$ that we have been considering and the plays in a strategy.
 
@@
     \]
-\end{definition}
+  Note that any $P$-position in $\ul X$ is of the form $qu$ for some sequence $u$.  
+\end{definition}
+
+\begin{definition}
+  Let $A$ be an arena, let $V$ be a random variable taking values in a set $X$, and let $\sigma \from X \to A$ be a single-threaded strategy.  
+  We may consider $X$ as a game $\ul X$.  
+  Let $s$ be a legal play of $A$.  
+  If $t\in\sigma$, we write $t/s$ if $t\vert_A = s$ and if the last move of $t$ is the last move of $s$ (this implies in particular that $t\vert_{\ul X}$ is a $P$-position in $\ul X$).
+  Then we define
+  \[
+    \Acc_s(\sigma) = \{u\in X^*\suchthat \exists t\in\sigma\esuchthat t/s,\,t\vert_{\ul X} = qu\}\,.
+    \]
+  We define
+  \[
+    \bP_V(s\in\sigma) = \bP(V, \Acc_s(\sigma))\,.
+    \]
+\end{definition}
+
+We would like use this definition to define $\bP(s\in\sigma)$ for $\sigma$ a morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, but we first need to check that this is well-defined with respect to the equivalence relation on \Mellies morphisms.
 
 \begin{proposition}
-  Let $X$ be a set, considered as an arena, and let $\sigma \from X \to A$ be a single-threaded strategy.
-  Let $\tau$ be a single-threaded strategy for $A$.  
-  Then, if $u\in X^*$ is a sequence, we have $u\in\Acc_\tau(\sigma)$ if and only if
-  \[
-    \{s\vert_A \suchthat s\in\sigma;\,s\vert_{\ul X} = qu\} = \tau\,.
-    \]
+  Let
+  \begin{mathpar}
+    (V\from \Omega \to X, \sigma \from \ul X \to A)
+    \and
+    (W\from \Omega \to Y, \sigma \from \ul Y \to A)
+  \end{mathpar}
+  be representatives of the same morphism $A \to B$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, where $X$ and $Y$ are sets.  
+  Let $s$ be a legal play of $A$.
+  Then $(V,\Acc_s(\sigma))$ and $(W,\Acc_s(\sigma'))$ are equivalent as pairs in the sense of Definition \ref{DefEquivalenceOfPairs}.
 \end{proposition}
 \begin{proof}
-  Immediate from the definition of composition and from our description of the strategy $\xi_u$.
-\end{proof}
-
-\begin{definition}
-  Recall that we have written $s\vert_A$ for the restriction of a sequence in a compound game to the moves occurring in some constituent part $A$, and similarly for a list $s\vert_{A_1,\cdots,A_n}$.
-  If $s$ is a sequence in an arena of the form $\ul{X\times Y}$; i.e., the arena in which player $O$ has an initial move $q$ to which player $P$ replies with some pair $(x,y)\in X\times Y$, the we write $s\vert_X$ for the play formed by projecting every such pair $(x,y)$ on to its first component $x$.
-\end{definition}
+  It suffices by induction to prove this in the case that the two representatives are related by the relation that generates the equivalence relation on morphisms; i.e., that there is a probability-preserving function $f\from X \to Y$ such that $\sigma=\sigma';(j(f) \to A)$.
+
+  Let $u\in X^*$.  
+  Then we have
+  \begin{IEEEeqnarray*}{rCl}
+    u \in \Acc_s(\sigma) & \Leftrightarrow & \exists t\in \sigma \esuchthat t/s,\,t\vert_{\ul X}=qu \\
+    & \Leftrightarrow & \exists t \in \sigma';(j(f) \to A) \esuchthat t/s,\,t\vert_{\ul X}=qu \\
+    & \Leftrightarrow & \exists t' \in \sigma' \esuchthat t/s,\,t\vert_{\ul Y} = q(f_*u) \\
+    & \Leftrightarrow & f_*u \in \Acc_s(\sigma')\,.
+  \end{IEEEeqnarray*}
+  Therefore, $(V,\Acc_s(\sigma))$ and $(W,\Acc_s(\sigma'))$ are equivalent.
+\end{proof}
+
+It follows by Proposition \ref{PropProbabilityWellDefined} that $\bP_V(s\in\sigma)=\bP_W(s\in\sigma')$ for all $s$.  
+Therefore, the following is well-defined.
+
+\begin{definition}
+  Let $\sigma \from A \to B$ be a morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, where $\G$ is the category of arenas and single-threaded strategies, and suppose that $\sigma$ is given (after currying) by a morphism
+  \[
+    \tilde\sigma \from \ul X \to (A \to B)
+    \]
+  in $\G$, together with a random variable $V$ taking values in $X$.
+  Then we define
+  \[
+    \bP(s\in\sigma) = \bP_V(s\in\tilde\sigma)\,.
+    \]
+\end{definition}
+
+\begin{definition}
+  Let $\sigma,\sigma'\from A \to B$ be morphisms in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, where $\G$ is the category of arenas and single-threaded strategies.  
+  We say that $\sigma\approx_{\bP}\sigma'$ if for all legal plays $s$ of $A \to B$ we have
+  \[
+    \bP(s\in\sigma) = \bP(s\in\sigma')\,.
+    \]
+\end{definition}
+
+We now relate this definition to \Mellies composition of strategies.
+
+\begin{definition}
+  Let $A,B,C$ be arenas and let $s$ be a play in $A\to C$.  
+  We write
+  \[
+    \wit_B(s) = \{\s\in\Int(A,B,C)\suchthat \s\vert_{A,C}=s\}\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  Let $\sigma\from A \to B$, $\tau\from B \to C$ be morphisms in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
+  Let $s$ be a legal play in $A \to C$.
+  Then
+  \[
+    \bP(s\in\sigma;\tau) = \sum_{\s\in\wit_B(s)}\bP(\s\vert_{A,B}\in\sigma)\bP(\s\vert_{B,C}\in\tau)\,.
+    \]
+\end{proposition}
+\begin{proof}
+  Suppose that $\sigma$ and $\tau$ are given by (equivalence classes of) pairs
+  \begin{mathpar}
+    (V\from\Omega\to X, \tilde \sigma \from A \to (\ul X \to B))
+    \and
+    (W\from\Omega\to Y, \tilde \tau \from B \to (\ul Y \to C))\,,
+  \end{mathpar}
+  where $V$ and $W$ are random variables and $\tilde \sigma,\tilde\tau$ are strategies in $\G$.
+  Then the composition $\sigma;\tau$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ is given by $V\tensor W\from\Omega \to X\times Y$, together with the \Mellies composition
+  \[
+    A \xrightarrow{\tilde\sigma}
+    (\ul{X} \to B) \xrightarrow{\ul{X} \to \tilde\tau}
+    (\ul X \to (\ul Y \to C)) \to
+    ((\ul X \times \ul Y) \to C) \xrightarrow{\mu\to C}
+    (\ul{X\times Y} \to C)\,,
+    \]
+  where $\mu$ is $\langle\ul{\pr_X},\ul{\pr_Y}\rangle$.
+
+  First suppose that $s$ is a sequence in $A \to C$, and let $\s\in\wit_B(s)$.  
+  Let $\t$ be a sequence in $\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\s$.  
+  Then $\t\vert_{A,\ul X \to B}\in\sigma$ and $\t\vert_{B,\ul Y,C}\in\tau$.
+\end{proof}
+
+We want to prove that this is preserved by composition of strategies.  
+First, we prove a lemma.
 
@@
   We consider the composite of the first two morphisms.  
-  We know that a play $t\in \sigma;(\X\to \tau)$ is given by $\s\vert_{A,X,Y,C}$, where $\s\vert_{A,X,B}\in\sigma$ and $\s\vert_{B,Y,C}\in\tau$.
+  We know that a play $t\in \sigma;(\ul X\to \tau)$ is given by $\s\vert_{A,X,Y,C}$, where $\s\vert_{A,X,B}\in\sigma$ and $\s\vert_{B,Y,C}\in\tau$.
   Write $\s_X$ for $\s\vert_{A,X,B}$ and $\s_Y$ for $\s\vert_{B,Y,C}$.
@@
 
+\section{The Probabilistic Equivalence Relation on Morphisms}
+
+\begin{definition}
+  Let $A$ be an object of $\G$.  
+  Let $(V\from\Omega \to X,\sigma\from X \to A)$ be a morphim $1\to A$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, and let $\tau \from 1 \to A$ be a morphism in $\G$.  
+  Recall from \ref{DefAcc} the definition
+  \[
+    \Acc_\tau(\sigma) = \{u\in X^* \suchthat \sigma;\xi_u = \tau\}\,.
+    \]
+  Now we define
+  \[
+    \bP(\sigma = \tau)
+    \]
+  to be
+  \[
+    \bP(V,\Acc_\tau(\sigma))\,.
+    \]
+  Given Kleisli morphisms $\sigma,\tau\from 1 \to A$, we say that $\sigma\approx_{\bP}\sigma'$ if for all $\tau\from 1 \to A$, we have
+  \[
+    \bP(\sigma = \tau) = \bP(\sigma' = \tau)\,.
+    \]
+  \label{DefProbEquiv}
+\end{definition}
+\begin{remark}
+  In the case that $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$ and
+  \[
+    \bP(\sigma\converges) = \bP(\sigma = \deno{\skipp}) = 1 - \bP(\sigma = \bot)\,.
+    \]
+  Then $\sigma\approx_{\bP}\sigma'$ if and only if $\bP(\sigma\converges)=\bP(\sigma'\converges)$.
+\end{remark}
+
+\begin{proposition}
+  i) Definition \ref{DefProbEquiv} is well defined.  
+  I.e., let
+  \begin{mathpar}
+    (V\from\Omega \to X,\sigma\from 1 \to (X \to A))
+    \and
+    (W\from\Omega \to Y,\sigma'\from 1 \to (Y \to A))
+  \end{mathpar}
+  be representatives for the same morphism in $\G/\Rv_{\Omega}^{FS}$, and let $\tau \from 1 \to A$ be an ordinary morphism in $\G$.  
+  Then $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.  
+\end{proposition}
+\begin{proof}
+  By Proposition \ref{PropAccEquivalent}, $(V,\Acc_\tau(\sigma))$ and $(W,\Acc_\tau(\sigma'))$ are equivalent pairs, and therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.
+\end{proof}
+
+\section{Danos-Harmer Probabilistic Game Semantics}
+
+We really want to show that the equivalence relation $\approx_{\bP}$ respects composition of morphisms, but this does not seem to be possible in the general setting.  
+Accordingly, we pass now to the special case when $\G$ is the category of games and strategies.  
+More specifically, we shall use the arena-only semantics which we developed in \sec\ref{SecArenaOnly} -- so the objects of our category $\G$ will be arenas and the morphisms will be single-threaded strategies between arenas.
+
+\begin{definition}
+  Let $\sigma,\sigma'$ be strategies $A \to B$.  
+  We say that $\sigma\approx_\bP\sigma'$ if $\Lambda(\sigma)\approx_{\bP}\Lambda(\sigma')$ as strategies $1 \to (A \to B)$.
+\end{definition}
+
+\begin{definition}
+  Let $X$ be a set and let $u\in X^*$ be a sequence.  
+  Consider $X$ as an arena $\ul X$.  
+  Then we write $qu$ for the play in $\ul X$ given by
+  \[
+    q\,u^{(1)}\,\cdots\,q\,u^{(|u|-1)}\,.
+    \]
+\end{definition}
+
+\begin{proposition}
+  Let $X$ be a set, considered as an arena, and let $\sigma \from X \to A$ be a single-threaded strategy.
+  Let $\tau$ be a single-threaded strategy for $A$.  
+  Then, if $u\in X^*$ is a sequence, we have $u\in\Acc_\tau(\sigma)$ if and only if
+  \[
+    \{s\vert_A \suchthat s\in\sigma;\,s\vert_{\ul X} = qu\} = \tau\,.
+    \]
+\end{proposition}
+\begin{proof}
+  Immediate from the definition of composition and from our description of the strategy $\xi_u$.
+\end{proof}
+
+\begin{definition}
+  Recall that we have written $s\vert_A$ for the restriction of a sequence in a compound game to the moves occurring in some constituent part $A$, and similarly for a list $s\vert_{A_1,\cdots,A_n}$.
+  If $s$ is a sequence in an arena of the form $\ul{X\times Y}$; i.e., the arena in which player $O$ has an initial move $q$ to which player $P$ replies with some pair $(x,y)\in X\times Y$, the we write $s\vert_X$ for the play formed by projecting every such pair $(x,y)$ on to its first component $x$.
+\end{definition}
+
 \begin{proposition}

### 2019-05-12 Thesis/pmonads2.tex
Commit just so I have it.

@@
   Then $\t\vert_{A,\ul X \to B}\in\sigma$ and $\t\vert_{B,\ul Y,C}\in\tau$.
+
+  Moreover, since we have $\t\vert_{A,B}=\s\vert_{A,B}$ and $\t\vert_{B,C}=\s\vert_{B,C}$, we must have
+  \begin{mathpar}
+    \t\vert_{\ul X} \in \Acc_{\s\vert_{A,B}}(\sigma)
+    \and
+    \t\vert_{\ul Y} \in \Acc_{\s\vert_{B,C}}(\tau)\,,
+  \end{mathpar}
+  where we have identified a play $qu$ occurring in the arena $\ul X$ with its underlying sequence $u$ of elements of $X$, and likewise for $Y$.
+
+  This gives us a function
+  \[
+    \{\t\in\sigma\|(\ul X \to \tau)\suchthat \t\vert_{A,B,C}=\s\} \to \Acc_{\s\vert_{A,B}}(\sigma)\times\Acc_{\s\vert_{B,C}}(\tau)\,.
+    \]
+  We claim that this function is a bijection.
+
+  Indeed, suppose that $\t,\t'$ are two interactions in $\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}=\s$, $\t\vert_{\ul X} = \t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$.
+  We claim that $\t = \t'$.
+
+  Indeed, suppose for a contradiction that $\t\ne\t'$: then there are prefixes $\r p\prefix \t$ and $\r q \prefix \t'$, where $\r$ is the longest common subsequence of $\t$ and $\t'$ and $p\ne q$ are moves.
+
+  By our earlier analysis (see, for example, the proof of \ref{PropComposition}), we know that $p$ and $q$ must either both occur in the $A \to (\ul X \to B)$-component, or both in the $(\ul X \to B) \to (\ul X \to (\ul Y \to C))$-component.
+  But since $\t,\t'\in\sigma\|(\ul X \to \tau)$ are both interactions of deterministic strategies, we also know that they must both be $O$-moves in that component -- otherwise, they would have to be equal.
+  In particular, neither $p$ nor $q$ may be a move in the middle component $\ul X \to B$, since then it would be a $P$-move in one of the two components.
+
+  Therefore, $p$ and $q$ are both $O$-moves in one of the outer components $A$ and $\ul X \to (\ul Y \to C)$.  
+  By Corollary \ref{CorSwitchingCondition}, we know that only Player $P$ may switch between games in $\ul X \to (\ul Y \to C)$, and therefore $p$ and $q$ must occur in the same component game -- i.e., both in $A$, both in $\ul X$, both in $\ul Y$ or both in $C$.
+  But now the conditions that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}$, $\t\vert_{\ul X}=\t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$ mean that we must have $p=q$, which is the desired contradiction.
+
+  For surjectivity, let $u\in\Acc_{\s\vert_{A,B}}(\sigma)$ and $v\in\Acc_{\s\vert_{B,C}}(\tau)$.  
+  We seek a sequence $\t\in\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\s$, $\t\vert_{\ul X}=qu$ and $\t\vert_{\ul Y}=qv$.
 \end{proof}

### 2019-05-12 Thesis/pmonads2.tex
Deleted some cruft.

@@
 
-We want to prove that this is preserved by composition of strategies.  
-First, we prove a lemma.
-
-\begin{lemma}
-  Let $\sigma\from A \to (\ul{X} \to B)$, $\tau \from B \to (\ul{Y} \to C)$ be strategies, where $X,Y$ are sets.
-  Write $\sigma\semicom_{\text{Mell}}\tau \from A \to (\ul{X\times Y} \to C)$ for the \Mellies composition of $\sigma$ and $\tau$.
-
-  Let $s\in\sigma\semicom_{\text{Mell}}\tau$.  
-  Then there exist four sequence $s_X,s_Y,\s_X,\s_Y$ such that
-  \begin{itemize}
-    \item $s$ is an interleaving of the sequences $s_X$ and $s_Y$;
-    \item $\s_X\in\sigma$ and $\s_Y\in\tau$;
-    \item $s_X\vert_{A,X} = \s_X\vert_{A,X}$; and
-    \item $s_Y\vert_{C,Y} = \s_Y\vert_{C,Y}$.
-  \end{itemize}
-  \label{LemMelliesDecomposition}
-\end{lemma}
-\begin{proof}
-  Recall that $\sigma\semicom_{\text{Mell}}\tau$ is given by the following composite in $\G$, where $\mu$ is the composite $\langle\ul{\pr_X},\ul{\pr_Y}\rangle$.
-  \[
-    A \xrightarrow{\sigma}
-    (\ul{X} \to B) \xrightarrow{\ul{X} \to \tau}
-    (\ul X \to (\ul Y \to C)) \to
-    ((\ul X \times \ul Y) \to C) \xrightarrow{\mu\to C}
-    (\ul{X\times Y} \to C)
-    \]
-  We consider the composite of the first two morphisms.  
-  We know that a play $t\in \sigma;(\ul X\to \tau)$ is given by $\s\vert_{A,X,Y,C}$, where $\s\vert_{A,X,B}\in\sigma$ and $\s\vert_{B,Y,C}\in\tau$.
-  Write $\s_X$ for $\s\vert_{A,X,B}$ and $\s_Y$ for $\s\vert_{B,Y,C}$.
-
-  Now suppose that $s$ is a sequence in the whole composition, and let
-  \[
-    \t\in ((A\times\mu);\cong)\|((\sigma\times \ul Y);\tau)
-    \]
-  be such that $\t\vert_{A,\ul{X \times Y}\to C}=s$.
-  Write $t=\t\vert_{A,\ul X \to (\ul Y \to C)}\in\sigma;(\ul X \to \tau)$ and let $\s$ cover $t$ as above.
-  Then $\t$ is formed from $t$ by inserting between every pair $q\,x$ of moves in $\ul X$ a pair $q\,(x,y_0)$ in $\ul{X\times Y}$ for some $y_0$, and between every pair $q\,y$ of moves in $\ul Y$ a pair $q\,(x_0,y)$ in $\ul{X \times Y}$ for some $x_0$.
-  This gives a partitition of $s\vert_{\ul {X \times Y}}$ into moves that occur before a move in $\ul X$ and moves that occur before a move in $\ul Y$ in the sequence $\t$.
-  We then define $s_X$ to be the sequence formed from $\s_X\vert_A$, together with those moves in $\ul{X \times Y}$ that occur before a move in $\ul X$ in $\t$, and $s_Y$ fto be formed from $\s_Y\vert_C$, together with those moves in $\ul{X\times Y}$ that occur before a move in $\ul Y$ in $\t$.
-
-  Then we have $s_X\vert_{A,X}=\s_X\vert_{A,X}$ and $s_Y\vert_{C,Y} = \s_Y\vert_{C,Y}$ as desired.
-\end{proof}
-
-\section{The Probabilistic Equivalence Relation on Morphisms}
-
-\begin{definition}
-  Let $A$ be an object of $\G$.  
-  Let $(V\from\Omega \to X,\sigma\from X \to A)$ be a morphim $1\to A$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, and let $\tau \from 1 \to A$ be a morphism in $\G$.  
-  Recall from \ref{DefAcc} the definition
-  \[
-    \Acc_\tau(\sigma) = \{u\in X^* \suchthat \sigma;\xi_u = \tau\}\,.
-    \]
-  Now we define
-  \[
-    \bP(\sigma = \tau)
-    \]
-  to be
-  \[
-    \bP(V,\Acc_\tau(\sigma))\,.
-    \]
-  Given Kleisli morphisms $\sigma,\tau\from 1 \to A$, we say that $\sigma\approx_{\bP}\sigma'$ if for all $\tau\from 1 \to A$, we have
-  \[
-    \bP(\sigma = \tau) = \bP(\sigma' = \tau)\,.
-    \]
-  \label{DefProbEquiv}
-\end{definition}
-\begin{remark}
-  In the case that $A=\bC$, we have $\Acc(\sigma) = \Acc_{\deno{\skipp}}(\sigma)$ and
-  \[
-    \bP(\sigma\converges) = \bP(\sigma = \deno{\skipp}) = 1 - \bP(\sigma = \bot)\,.
-    \]
-  Then $\sigma\approx_{\bP}\sigma'$ if and only if $\bP(\sigma\converges)=\bP(\sigma'\converges)$.
-\end{remark}
-
-\begin{proposition}
-  i) Definition \ref{DefProbEquiv} is well defined.  
-  I.e., let
-  \begin{mathpar}
-    (V\from\Omega \to X,\sigma\from 1 \to (X \to A))
-    \and
-    (W\from\Omega \to Y,\sigma'\from 1 \to (Y \to A))
-  \end{mathpar}
-  be representatives for the same morphism in $\G/\Rv_{\Omega}^{FS}$, and let $\tau \from 1 \to A$ be an ordinary morphism in $\G$.  
-  Then $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.  
-\end{proposition}
-\begin{proof}
-  By Proposition \ref{PropAccEquivalent}, $(V,\Acc_\tau(\sigma))$ and $(W,\Acc_\tau(\sigma'))$ are equivalent pairs, and therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(\sigma = \tau) = \bP(\sigma' = \tau)$.
-\end{proof}
-
 \section{Danos-Harmer Probabilistic Game Semantics}
-
-We really want to show that the equivalence relation $\approx_{\bP}$ respects composition of morphisms, but this does not seem to be possible in the general setting.  
-Accordingly, we pass now to the special case when $\G$ is the category of games and strategies.  
-More specifically, we shall use the arena-only semantics which we developed in \sec\ref{SecArenaOnly} -- so the objects of our category $\G$ will be arenas and the morphisms will be single-threaded strategies between arenas.
-
-\begin{definition}
-  Let $\sigma,\sigma'$ be strategies $A \to B$.  
-  We say that $\sigma\approx_\bP\sigma'$ if $\Lambda(\sigma)\approx_{\bP}\Lambda(\sigma')$ as strategies $1 \to (A \to B)$.
-\end{definition}
-
-\begin{definition}
-  Let $X$ be a set and let $u\in X^*$ be a sequence.  
-  Consider $X$ as an arena $\ul X$.  
-  Then we write $qu$ for the play in $\ul X$ given by
-  \[
-    q\,u^{(1)}\,\cdots\,q\,u^{(|u|-1)}\,.
-    \]
-\end{definition}
-
-\begin{proposition}
-  Let $X$ be a set, considered as an arena, and let $\sigma \from X \to A$ be a single-threaded strategy.
-  Let $\tau$ be a single-threaded strategy for $A$.  
-  Then, if $u\in X^*$ is a sequence, we have $u\in\Acc_\tau(\sigma)$ if and only if
-  \[
-    \{s\vert_A \suchthat s\in\sigma;\,s\vert_{\ul X} = qu\} = \tau\,.
-    \]
-\end{proposition}
-\begin{proof}
-  Immediate from the definition of composition and from our description of the strategy $\xi_u$.
-\end{proof}
-
-\begin{definition}
-  Recall that we have written $s\vert_A$ for the restriction of a sequence in a compound game to the moves occurring in some constituent part $A$, and similarly for a list $s\vert_{A_1,\cdots,A_n}$.
-  If $s$ is a sequence in an arena of the form $\ul{X\times Y}$; i.e., the arena in which player $O$ has an initial move $q$ to which player $P$ replies with some pair $(x,y)\in X\times Y$, the we write $s\vert_X$ for the play formed by projecting every such pair $(x,y)$ on to its first component $x$.
-\end{definition}
-
-\begin{proposition}
-  Let $\sigma,\sigma'\from A \to B$ and $\tau,\tau'\from B \to C$ be morphisms in $\G/\Rv_{\Omega}^{FS}$, where $\G$ is the category of games and single-threaded strategies.
-  If $\sigma\approx_{\bP}\sigma'$ and $\tau\approx_\bP\tau'$, then $\sigma;\tau\approx_\bP\sigma';\tau'$.
-\end{proposition}
-\begin{proof}
-  Suppose that $\sigma$ is given by a single-threaded strategy $A \to (\ul X \to B)$ and $\tau$ by a single-threaded strategy $B \to (\ul Y \to C)$.
-
-  Suppose $s\in\sigma;\tau$ satisfies $s\vert_{\ul{X\times Y}}=qu$, for some sequence $u\in(X\times Y)^*$.
-  By Lemma \ref{LemMelliesDecomposition}, $s$ can be decomposed into sequences $s_X$ and $s_Y$ such that there are $\s_X\in\sigma$ and $\s_Y\in\tau$ with $\s_X\vert_{X,A}=s\vert_{X,A}$ and $\s_Y\vert_{Y,C}=s_Y\vert_{Y,C}$.
-  We have $\s_X\vert_X=qv$ and $\s_Y\vert_Y=qw$ for sequences $v\in X^*$ and $w\in Y^*$, and $s_X\vert_{X\times Y} = qV$ and $s_Y\vert_{X\times Y}=qW$ for sequences $V\in (X\times Y)^*,W\in (X\times Y)^*$ such that $(\pr_X)_*V = v$ and $(\pr_Y)_*W = w$, and such that $u$ is an interleaving of $V$ and $W$.
-
-  Now write $\hat\sigma$ for $\sigma;\xi_v$ and $\hat\tau$ for $\tau;\xi_w$.
-  We claim that $(\sigma;\tau);\xi_u = \hat{\sigma};\hat{\tau}$.
-
-  Thus, $\sigma$ and $\tau$ give rise to maps
-  \begin{mathpar}
-    \phi_{\sigma,\tau}\from (X\times Y)^* \to X^* \times Y^*
-    \and
-    \Phi_{\sigma,\tau}\from (X\times Y)^* \to (X\times Y)^* \times (X \times Y)^*
-  \end{mathpar}
-  (sending $u$ to $(v,w)$ and to $(V,W)$ respectively), such that the components of $\Phi(u)$ form a decomposition of $u$, and such that $\phi(u) = ((\pr_X)_*\times(\pr_Y)_*)(\Phi(u))$.
-\end{proof}
 

### 2019-05-27 Thesis/conc.tex
Monthly commit.

\documentclass[11pt]{report}

\let\FEWFONTS=1
\input{../common/preamble}

\begin{document}

\chapter{Further Directions}

\section{Stateless Languages}
\label{SecStatelessLanguages}

In this thesis, the base language we have used has been the stateful language Idealized Algol.  
One area to explore is whether the techniques we have developed allow us to build models of effectful versions of stateless languages such as PCF.

One immediate problem we face is that the addition of nondeterministic effects to PCF allows us to distinguish terms that cannot be distinguished within PCF itself.  
Consider, for instance, the PCF term
\[
  M = \lambda x^{\bool}.\If x \Then \Omega \Else (\If x \Then \true \Else \Omega)
  \]
is observationally equivalent (in PCF) to $\Omega$ -- informally, because the term $x$ must have the same `value' both time it is called, so if it is false the first time, then it must be false the second time.
However, the same term inside PCF with finite nondeterminism is not observationally equivalent to $\Omega$: if we substitute nondeterministic choice in for $x$, then it could be false the first time and true the second, causing the term to converge to $\true$.

This means that if $\G$ is a `truly fully abstract' model of PCF -- i.e., one in which observational equivalence of terms corresponds to equality of morphisms rather than intrinsic equivalence\footnote{As an example, take any model that is full abstract in our sense, and take the quotient by the intrinsic equivalence relation.} -- then there can be no natural inclusion functor from $\G$ into a model of PCF with finite nondeterminism.  
Indeed, in such a model $\deno{M}$ and $\deno{\Omega}$ are the same morphism, so they would have to be sent to the same morphism in the model of nondeterministic PCF.

This is a problem for us, since both our techniques -- the Kleisli category and the $\G/\X$ construction -- have a natural functor coming out of the original category $\G$.

All is not lost, however, since we can still try and impose some condition on the original model $\G$ of PCF to say that it is still fine-grained enough to distinguish between certain morphisms that are denotations of observationally equivalent PCF terms.  
One convenient way to do this is to ask that $\G$ should embed into some model $\G^{IA}$ of Idealized Algol.  
An obvious case when this holds is when $\G$ is the (unquotiented) Hyland-Ong category of arenas and innocent strategies, and $\G^{IA}$ is the category of arenas and single-threaded strategies.

For example, fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the langauge PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  
I.e., it is the language with types given by the following inductive grammar.
\[
  T \Coloneqq \bool \mid \nat \mid T \to T
  \]
And with a type theory as shown in Figure \ref{FigNDPcfTypeTheory}.
\begin{figure}
  \begin{mathpar}
    \inferrule*{ }{\Gamma,x\from T \ts x \from T}
    \and
    \inferrule*{\Gamma\ts M \from S \to T \\ \Gamma \ts N \from S}{\Gamma\ts MN \from T}
    \and
    \inferrule*{\Gamma,x\from S \ts M \from T}{\Gamma \ts \lambda x^S.M \from S \to T}
    \and
    \inferrule*{ }{\Gamma\ts\true\from\bool}
    \and
    \inferrule*{ }{\Gamma\ts\false\from\bool}
    \\
    \inferrule*[right={$T\in\{\bool,\nat\}$}]{\Gamma\ts M \from \bool \\ \Gamma \ts N \from T \\ \Gamma \ts P \from T}{\Gamma\ts \If M \Then N \Else P \from T}
    \\
    \inferrule*{ }{\Gamma\ts n\from\nat}
    \and
    \inferrule*{\Gamma\ts M \from \nat}{\Gamma\ts \suc M \from \nat}
    \and
    \inferrule*{\Gamma\ts M \from \nat}{\Gamma\ts \pred M\from \nat}
    \\
    \inferrule*[right={$T\in\{\bool,\nat\}$}]{\Gamma\ts M \from \nat \\ \Gamma\ts N \from T \\ \Gamma \ts P \from T}{\Gamma \ts \IfO M \Then N \Else P \from T}
    \and
    \inferrule*{\Gamma \ts M \from T \to T}{\Gamma \ts \Y_T M \from T}
    \and
    \inferrule*{ }
    {\ask_X \from\bool}
  \end{mathpar}
  \caption[Type theory for a variant of PCF with nondeterminism.]
  {Type theory for a variant of PCF with nondeterminism.
  Note that if the nondeterminism is infinite (i.e., $X=\bN$), then it is common (see \cite{LairdOrdinalGames} for nondeterminism and \cite{ProbabilisicPcf} for the probabilistic case) to modify the conditional construct $\IfO M\Then N \Else P$ so that the value of $M$ is passed into $P$ (so that the typing rule for $\IfO$ becomes
  \[
    \inferrule*[right={$T\in\{\bool,\nat\}$}]{\Gamma\ts M \from \nat \\ \Gamma \ts N \from T \\ \Gamma \ts P \from \nat \to T}
    {\Gamma \ts \IfO M \Then N \Else P \from T}\,.
    \]
  The idea behind this is that if $M$ evaluates to $0$ then $N$ will be evaluated, and if it evaluates to $n+1$ then $P\,n$ will be evaluated.
  In ordinary deterministic PCF, this does not change the expressive power of the language, since we could always write
  \[
    \IfO M \Then N \Else (P\,M)\,.
    \]
  However, this does not work if $M$ may exhibit nondeterministic behaviour, since it may evaluate to two different values the two times it is called.
  We will stick with the variant shown above for the sake of simplicity, but nothing changes in our proofs if we choose the other version.}
  \label{FigNDPcfTypeTheory}
\end{figure}
We endow this language with an operational semantics of may testing.  
Define a \emph{canonical form} of the language to be a term taking one of the following forms.
\begin{itemize}
  \item At type $\bool$, the constants $\true$ and $\false$;
  \item at type $\nat$, the numerals $n$; and
  \item at type $S \to T$, terms of the form $\lambda x^S.M$.
\end{itemize}
We then define a relation $M \converges c$ (read `$M$ \emph{may converge to} $c$'), for $M$ a term of Nondeterministic PCF and $c$ a canonical form, inductively as in Figure \ref{FigNDPCFOpSem}.
\begin{figure}
  \begin{mathpar}
    \inferrule*{ }{c\converges c}
    \and
    \inferrule*{M\converges\lambda x.M' \\ M'[N/x] \converges c}{M\,N\converges c}
    \\
    \inferrule*{M\converges \true \\ N \converges c}{\If M \Then N \Else P \converges c}
    \and
    \inferrule*{M\converges \false \\ P \converges c}{\If M \Then N \Else P \converges c}
    \\
    \inferrule*{M \converges n}{\suc M \converges n+1}
    \and
    \inferrule*{M \converges n+1}{\pred M \converges n}
    \and
    \inferrule*{M \converges 0}{\pred M \converges 0}
    \\
    \inferrule*{M \converges 0 \\ N \converges c}{\IfO M \Then N \Else P \converges c}
    \and
    \inferrule*{M \converges n+1 \\ P \converges c}{\IfO M \Then N \Else P \converges c}
    \\
    \inferrule*{M(\Y M) \converges c}{\Y M \converges c}
    \and
    \inferrule*{ }{\ask_X \converges \true}
    \and
    \inferrule*{ }{\ask_X \converges \false}
  \end{mathpar}
  \caption{Big-step operational semantics for Nondeterministic PCF with may testing}
  \label{FigNDPCFOpSem}
\end{figure}

It is a quick check to see that every term of Nondeterministic PCF may be regarded as a term of IA${}_X$, giving us a denotational semantics of the language within $\Kl_{R_X}\G$, where $\G$ is the category of arenas and single-threaded strategies.
But we can be more precise than this: we know from \cite{hoPcf} that the denotation of any term of ordinary PCF is an innocent strategy, so that the denotational semantics of PCF within $\G$ factors through the inclusion $\G_{inn}\hookrightarrow\G$, where $\G_{inn}$ is the category of arenas and innocent strategies.
In particular, the denotation within $\Kl_{R_X}\G$ of any term of ordinary PCF lives within $\Kl_{R_X}\G_{inn}$.
Moreover, the denotation of the new term $\ask_X$, being given by the identity morphism in $\G$, also lives in $\Kl_{R_X}\G_{inn}$, meaning that the whole of Nondeterministic PCF is interpreted within this category.

It is also quick to check that our operational semantics in Figure \ref{FigNDPCFOpSem} may be regarded as a subset of the rules for IA${}_X$ with May Testing, as we studied in \sec \ref{SecMayTesting}.
Specifically, if $M$ is a term of PCF and $c$ a canonical form, then $M\converges c$ if and only if
\[
  \blank,()\ts M\converges c,()
  \]
in IA${}_X$.

We want to use our Computational Adequacy result for IA${}_X$ with May Testing (Corollary \ref{CorMayAdequacy}) to get a Computational Adequacy result for Nondeterministic PCF.
The only slight problem is that Corollary \ref{CorMayAdequacy} is stated for terms of type $\com$, whereas our language has no such type.  
We get around this by using $\nat$ as our main ground type rather than $\com$, and by using the following easy lemma.

\begin{lemma}
  Let $M\from\nat$ be a term of IA${}_X$.  
  Then there exists $n$ such that $\Gamma,s\ts M\converges n,s'$ if and only if
  \[
    \Gamma,s\ts \IfO M \Then \skipp \Else \skipp \converges \skipp, s'\,.
    \]
\end{lemma}

We will write $\delta\from \bN \to \bC$ for the denotation of the term-in-context 
\[
  x\from\nat \ts \IfO x \Then \skipp \Else \skipp \from \com\,.
  \]
Then we immediately get the following result as a special case of Corollary \ref{CorMayAdequacy}.

\begin{corollary}[Computational Adequacy for Nondeterministic PCF]
  Let $M\from\nat$ be a closed term of Nondeterministic PCF.
  Consider the denotation $\deno M \from 1 \to \bN$ in $\Kl_{R_X}\G_{inn}$ as a morphism $1 \to (X \to \bN)$ in $\G_{inn}$, and thence as a morphism $1 \to (X \to \bN)$ in $\G$.

  Then there exists some sequence $u\in X^*$ such that the composite
  \[
    1 \xrightarrow{\deno M}
    (X \to \bN) \xrightarrow{X \to \delta}
    (X \to \bC) \xrightarrow{\eta_u}
    (\Varr \to \bN) \xrightarrow{\deno{\neww}}
    \bN \xrightarrow{t_{|u|}}
    \bC
    \]
  is not equal to $\bot$, if and only if $M\converges n$ for some $n$.
  \label{CorMayAdequacyPCF}
\end{corollary}

Note that Corollary \ref{CorMayAdequacyPCF}, which does not depend on any specific details of the models $\G_{inn}$ and $\G$ beyond the fact that they are computationally adequate for ordinary PCF and Idealized Algol, uses morphisms $\delta$, $\eta_u$, $\deno{\neww}$ and $\t_{|u|}$ that do not occur in the category $\G_{inn}$.

In the case that $\G$ is the category of arenas and single-threaded strategies, and $\G_{inn}$ the category of arenas and innocent strategies, we can restate Corollary \ref{CorMayAdequacyPCF} in a way that does not refer to Idealized Algol terms at all.

\begin{corollary}
  Let $M\from\nat$ be a closed term of Nondeterministic PCF and consider the denotation $\deno M \from 1 \to \bN$ in $\Kl_{R_X}\G_{inn}$ as a morphism $1 \to (X \to \bN)$ in $\G_{inn}$.

  Then, for all $n\in\bN$, there exists some sequence $s\in\deno M$ such that $s\vert_{\bN} = qn$ if and only if $M\converges n$.
  \label{CorMayAdequacyPcfComb}
\end{corollary}
\begin{proof}
  Corollary \ref{CorMayAdequacyPCF}, together with our earlier analysis, immediately tells us that we have
  \[
    \exists s\in \deno M \esuchthat s\vert_\bN = qn\text{ for some $n$} \Leftrightarrow \exists n\esuchthat M\converges n\,.
    \]
  The problem is that the two $n$'s might be different.  
  However, we can obtain the desired result for a given $n$ from this one by composing with an appropriate term $\nat \to \nat$ that converges if and only if its input is equal to $n$.
\end{proof}

The passage to full abstraction, via innocent definability for PCF is essentially the same as for Idealized Algol (though if $X=\bN$, then we need to cut down to a category of \emph{recursive} strategies).

If we so desire, we can continue with the programme from \sec\ref{SecMayTesting}, declaring two Kleisli strategies $A \to (X \to B)$ to be equivalent if they contain the same plays after restriction to $A \to B$.
We can then do away with the plays in $X$ altogether and give a model that involves only nondeterministic strategies.

At this point, we run into a well-known problem: under what circumstances should a nondeterministic strategy be described as \emph{innocent}? 
The answer that we get from our model is that it is innocent if and only if it takes the form
\[
  A \xrightarrow{\sigma} (X \to B) \xrightarrow{\deno{\ask_X} \to B} B\,,
  \]
where $\sigma$ is an innocent deterministic strategy.  
This is the definition considered -- and ultimately rejected for being too indirect -- by Harmer in his thesis \cite[\sec 3.7]{RusssThesis}.  
This definition is correct, but, perhaps surprisingly, does not coincide with the same definition that we would get by naively applying the usual definition of innocence to nondeterministic strategies.

Consider, for example, the denotation of the term 
\[
  \If \ask_\bB \Then (\lambda f.f\true) \Else (\lambda f.f\false)\,,
  \]
which has maximal plays taking one of the following two forms.
\begin{mathpar}
  \begin{tikzcd}[row sep=5pt]
    %
      &
        & q \\
    %
      & q \arrow[ur, bend left=10]
        & \\
    |[alias=A]| q \arrow[ur, bend left=10]
      &
        & \\
    |[alias=B]| \true \arrow[u, bend left=45, from=B.west, to=A.west]
      &
        & \\
    \vdots
      &
        & \\
    |[alias=C]| q  \arrow[uuuur, from=C.east, bend right=10]
      & 
        & \\
    |[alias=D]| \true \arrow[u, bend left=45, from=D.west, to=C.west]
      &
        & \\
    %
      & a \arrow[uuuuuu, bend right=10]
        & \\
    %
      &
        & a \arrow[uuuuuuuu, bend right=10]
  \end{tikzcd}
  \and
  \begin{tikzcd}[row sep=5pt]
    %
      &
        & q \\
    %
      & q \arrow[ur, bend left=10]
        & \\
    |[alias=A]| q \arrow[ur, bend left=10]
      &
        & \\
    |[alias=B]| \false \arrow[u, bend left=45, from=B.west, to=A.west]
      &
        & \\
    \vdots
      &
        & \\
    |[alias=C]| q  \arrow[uuuur, from=C.east, bend right=10]
      & 
        & \\
    |[alias=D]| \false \arrow[u, bend left=45, from=D.west, to=C.west]
      &
        & \\
    %
      & a \arrow[uuuuuu, bend right=10]
        & \\
    %
      &
        & a \arrow[uuuuuuuu, bend right=10]
  \end{tikzcd}
\end{mathpar}
Note that this strategy displays typically non-innocent behaviour: if player $P$ has played $\true$ on the left, then she must play $\true$ again whenever player $O$ asks, even though the original move $\true$ occurs outside the current $P$-view.

In the Kleisli category, the innocence of this strategy becomes clear: plays are either of the form
\[
  \begin{tikzcd}[row sep=5pt]
    %
      &
        &
          & q \\
    |[alias=Y]| q  \arrow[urrr, bend left=10] \\
    |[alias=Z]| \true \arrow[u, bend left=45, from=Z.west, to=Y.west] \\
    %
      &
        & q \arrow[uuur, bend left=10]
          & \\
    %
      & |[alias=A]| q \arrow[ur, bend left=10]
        &
          & \\
    %
      & |[alias=B]| \true \arrow[u, bend left=45, from=B.west, to=A.west]
        &
          & \\
    %
      & \vdots
        &
          & \\
    %
      & |[alias=C]| q  \arrow[uuuur, from=C.east, bend right=10]
        & 
          & \\
    %
      & |[alias=D]| \true \arrow[u, bend left=45, from=D.west, to=C.west]
        &
          & \\
    %
      &
        & a \arrow[uuuuuu, bend right=10]
          & \\
    %
      &
        &
          & a \arrow[uuuuuuuuuu, bend right=10]
  \end{tikzcd}
  \]
or of the form
\[
  \begin{tikzcd}[row sep=5pt]
    %
      &
        &
          & q \\
    |[alias=Y]| q  \arrow[urrr, bend left=10] \\
    |[alias=Z]| \false \arrow[u, bend left=45, from=Z.west, to=Y.west] \\
    %
      &
        & q \arrow[uuur, bend left=10]
          & \\
    %
      & |[alias=A]| q \arrow[ur, bend left=10]
        &
          & \\
    %
      & |[alias=B]| \false \arrow[u, bend left=45, from=B.west, to=A.west]
        &
          & \\
    %
      & \vdots
        &
          & \\
    %
      & |[alias=C]| q  \arrow[uuuur, from=C.east, bend right=10]
        & 
          & \\
    %
      & |[alias=D]| \false \arrow[u, bend left=45, from=D.west, to=C.west]
        &
          & \\
    %
      &
        & a \arrow[uuuuuu, bend right=10]
          & \\
    %
      &
        &
          & {a\,,} \arrow[uuuuuuuuuu, bend right=10]
  \end{tikzcd}
  \]
where now the move $\true$ or $\false$ in the nondeterministic oracle game (on the very left) locks the `branching-time information' into the $P$-view.

There is a surprising and elegant definition of nondeterministic innocence (see Levy \cite{levy2014morphisms}, with the correction given by Tsukada and Ong in \cite[Proposition 46]{TsukadaSheaves}), which we shall not detail here.
Tsukada and Ong have also demonstrated that it is instructive to consider strategies as presheaves over plays, where we assign to each individual play a set of possible branches that lead us to that play.  
In this formalism, the innocent nondeterministic strategies are preciesly those presheaves that are sheaves with respect to a certain natural Grothendieck topology.

What, then, can our Kleisli category model do for us?
One answer is that it provides a general setting in which we can prove results such as adequacy without worrying about the specific details of a nondeterministic construction.  
For example, we can prove a computational adequacy result for Tsukada and Ong's model $\G_{TO}$ from Corollary \ref{CorMayAdequacyPcfComb} by noting that the denotational semantics in that category factors through the natural functor $\Kl_{R_\bB}\G \to \G_{TO}$.  
Of course, Tsukada and Ong have provided their own proof of Computational Adequacy in the finite nondeterminism case, but this method could be useful if, for example, we wanted to extend their model to deal with countable nondeterminism.

\section{Stateful Effects}

In Chapters \ref{ChapGames} and \ref{ChapFullAbstraction}, we presented a categorical algebra of scoped state via sequoidal categories.  
A natural question to ask is whether we could use the techniques we have developed in the remainder of this thesis in the stateful case.  
Indeed, the state monad
\[
  A \mapsto (W \to (A \times W))
  \]
can be constructed in categories of games.  
More ambitiously, we might hope to capture a parametric notion of local state, via the action
\[
  (R,W).A = R \to (A \times W)\,.
  \]
of $\oppcat \G \times \G$ on $\G$.

In this section, we will present some of the problems involved in this case.

One issue, which we have touched on already, is that the state monad is not a monoidal functor, which was the condition we needed in order to ensure that its Kleisli category inherited a monoidal structure.  
Indeed, there is not obvious natural morphism
\[
  (W \to (A \times W)) \times (W \to (B \times W)) \to (W \to ((A \times B) \times W)\,.
  \]

The parametric version suffers from a different problem.  
Suppose we have two \Mellies morphisms
\begin{mathpar}
  f \from A \to (R \to (B \times W))
  \and
  g \from B \to (R' \to (C \times W'))\,.
\end{mathpar}
Then their composition will be given by a \Mellies morphism
\[
  f;g \from A \to ((R \times R') \to (C \times (W \times W')))\,:
  \]
in other words, we will have combined the two inputs $R$ and $R'$ and the two outputs $W$ and $W'$, without any way of specifying that the output state $W$ from $f$ should be used as the input state $R'$ from $g$.

The difficulty is that we might want $W$ and $R'$ to represent different variables, in which case this is the right thing to do, but we might want them to represent the same storage cell, in which case, the output from $W$ should be fed into $R'$.  
It's not clear how to deal with this in a category-theoretic way.

Linear type theory provides a perspective on this problem.  
Note that the state monad and the parametric action above can both be defined inside an arbitrary monoidal category.  
However, if we want our language to exhibit any typically stateful behaviour, then we need to be able to refer to the same variable more than once: there is little point writing a value into a cell if we are not able to read from it later.  
This is not a problem in a monolithic stateful system -- such as we have with the state monad -- but if we want to refer to individual storage cells using variables in the language, then we need our category to admit diagonals, to allow us to refer to a storage cell twice.
Since the state action above does not interact in any way with the Cartesian structure of the category (i.e., the diagonals and terminal morphisms), it cannot hope to capture local state in this way.

One avenue that could shed some light on this issue is the sequoidal semantics which we developed for game semantics, in which the stateful behaviour is intimately connected to the Cartesian structure of the category, via the exponential.

There is also a \emph{local state monad}, due to Plotkin and Power \cite{PlotkinPower} and based on a construction by Levy \cite{PaulsThesis}, which is defined on the category $[\Inj,\Set]$ of functors from $\Inj$, the category of natural numbers and injections, into the category of sets.  
It is given by the following formula, where $V$ denotes a fixes set of values.
\[
  (TA)(n) = V^n \to \left( \int^{p\from\Inj} V^p \times A(p) \times \Inj(n, p) \right)
  \]
Here, if $A \from \Inj \to \Set$ is a functor, then we think of $A(n)$ as the set of all values that $A$ takes on in the presence of $n$ local variables taking values in $V$.

We cannot construct this coend in the category of games, but there is a clear link with our constructions with probabilistic monads.  
Note that the `state action'
\[
  (W, A) \mapsto W \to (A \times W)
  \]
has mixed variance in $W$, suggesting a modification of our $\C/\X$ construction that uses a coend rather than an ordinary colimit.

\section{Relational Models}

The archetypal Cartesian closed category is the category $\Set$ of sets and functions.  
Most of the work in this thesis has been to do with reader actions (including reader monads as a special case), and we have already provided a classification of the reader actions on $\Set$ -- up to the equivalence relation that identifies actions of monoidal categories $\X$ and $\YY$ if the resulting categories $\Set/\oppcat\X$ and $\Set/\oppcat\YY$ are isomorphic -- in Propositions \ref{PropColimitOfActionIsMonoidalFunctor} and \ref{PropMonoidalFunctorIsColimitOfReaderAction}: namely, they are classified by lax monoidal functors $F\from\Set \to \Set$, in such a way that if a reader action given by an oplax monoidal functor $j\from\X \to \Set$ corresponds to the functor $F \from \Set \to \Set$, then $\Set/\oppcat\X$ is isomorphic to the category $F_*\Set$ formed from $\Set$ by base change along $F$.
Thus, the theory in the case of $\Set$ reduces to the theory of $\Set$-enriched base change.

There are, however, many more examples in the literature of models of programming languages that ultimately derive from Kleisli categories for monads not of the reader kind.  
The problem with this, from our point of view, is that the resulting Kleisli categories will not be automatically Cartesian.  
This means that we need different methods to ensure that we end up with a category suitable for modelling a compositional semantics.

For example, the Kleisli category for the powerset monad on $\Set$ is the category $\Rel$ of sets and relations.  
This is a monoidal closed category, so can be used to model multiplicative linear type theory.
By using a linear exponential comonad based on finite multisets, we can transform it into a Cartesian closed category.

An important category derived from the category of sets and relations is the category $\Coh$ of coherence spaces.  
A coherence space is a set with some additional structure on it -- namely, the structure of an undirected graph -- and a morphism between coherence spaces is a relation between sets that respects this structure in a particular way (see \cite{MelliesCoherence} for details).

Danos and Ehrhard in \cite{ProbabilisticCoherenceSpaces} develop a probabilistic version of coherence spaces, which is still monoidal closed.  
By using the finite multiset comonad, we can transform it into a Cartesian closed category.  
A striking result of Ehrhard, Pagani and Tasson \cite{ProbabilisicPcf} is that this category is already fully abstract for a probabilistic variant of PCF.

This suggests an alternative way to get round the Cartesianness hurdle when adding effects: start with a model of the base language that is constructed by applying a linear exponential comonad to a monoidal closed category, and then delay application of the linear exponential comonad until after we have added the effect.

Unfortunately, there is no real guarantee that a linear exponential comonad on the base category will give us a linear exponential comonad on a Kleisli category or one of the other effectful categories we have considered.  
Some work is required to investigate the conditions in which we can lift an exponential construction in this way, given the functorial results from Chapter \ref{ChapParametricMonads}.  
This will pave the way for us to understand the relational and coherence-space models using the ideas developed in this thesis.

\section{Adequacy Proofs}

In Chapters \ref{ChapMonads} and \ref{ChapParametricMonadsFullAbstraction} we proved Computational Adequacy via a factorization and operational techniques.  
This is good, because it allows us to assume very little about the underlying model, other than that it is itself computationally adequate.  
Nevertheless, our techniques rely very heavily on the fact that our base language is Idealized Algol.  
Although we outlined ways to get around this in Section \ref{SecStatelessLanguages}, it would also be useful to have a conventional logical relations-based proof of Computational Adequacy.

Assume that $\G$ is a Cartesian closed category enriched in directed-complete partial orders (dcpos).
If $M\from\G \to \G$ is a monoidal monad, then the Kleisli category associated to $M$ inherits an order, whereby $\sigma\le\tau\from A \to B$ in $\Kl_M\G$ if $\sigma\le\tau\from A \to MB$ in $\G$.
Moreover, since composition in the Kleisli category is given by a composition in the base category, this partial order will be respected by composition, as will be limits of directed sets.

Suppose again that $\G$ is a dcpo-enriched category, and that a monoidal category $\X$ acts on $\G$ via a lax action.  
Then the construction of \Mellies yields an $[\X,\Dcpo]$-enriched category $\Mell_\X\G$.
Since $\Dcpo$ is cocomplete \cite{CocompleteDcpo}, we can construct the coends we need to define the Day convolution product in $[\X,\Dcpo]$.

If $\X$ is small, or if the required colimits exist for other reasons, then we may take the change of base with respect to the colimit functor $[\X,\Dcpo] \to \Dcpo$ to $\Mell_\X\G$ to give us a $\Dcpo$-enriched category $\G/\X$.

\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-05-27 Thesis/games.tex
Nightly build.
Monthly commit.

@@
 
-\chapter{A Fully Abstract Game Semantics for Idealized Algol}
+\chapter{A Sequoidal Game Semantics for Idealized Algol}
+\label{ChapGames}
 
@@
 \end{minipage}
+
+The types of Idealized Algol are then defined by the following inductive grammar.
+
+\[
+  T \Coloneqq \com \mid \bool \mid \nat \mid \Var \mid T \to T\,.
+  \]
 
@@
 It is also easy to see from Proposition \ref{PropCopycat} that the identity function $\id\from M_A \to M_A$ is a structural isomorphism from $A$ to itself, and that the resulting copycat strategy $\cc_{\id}$ is an identity for composition.
-Combining this with our result for associativity in the previous chapter, we get that
+Combining this with our result for associativity in the previous section, we get that
 \begin{theorem}
@@
 
-We can generalize the subset inclusions of the previous chapter to \emph{tree immersions}.  
+We can generalize the subset inclusions of the previous section to \emph{tree immersions}.  
 Tree immersions are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
@@
 
-We have now given the category-theoretic properties of all the connectives from chapter \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
+We have now given the category-theoretic properties of all the connectives from section \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
 
@@
 \end{proof}
+
+\chapter{Operational Semantics, Computational Adequacy and Full Abstraction}
+\label{ChapFullAbstraction}
 

### 2019-05-27 Thesis/pmonads2.tex
Monthly commit.

@@
 \chapter{Parametric Monads and Full Abstraction}
+\label{ChapParametricMonadsFullAbstraction}
 
@@
     \]
+  \label{DefProbabilisticEquivalenceRelation}
 \end{definition}
@@
     \]
+  \label{PropCompositionProb}
 \end{proposition}
@@
   First suppose that $s$ is a sequence in $A \to C$, and let $\s\in\wit_B(s)$.  
-  Let $\t$ be a sequence in $\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\s$.  
-  Then $\t\vert_{A,\ul X \to B}\in\sigma$ and $\t\vert_{B,\ul Y,C}\in\tau$.
+  Let $\t$ be a sequence in $\tilde\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\s$.  
+  Then $\t\vert_{A,\ul X \to B}\in\tilde\sigma$ and $\t\vert_{B,\ul Y,C}\in\tilde\tau$.
 
@@
   \begin{mathpar}
-    \t\vert_{\ul X} \in \Acc_{\s\vert_{A,B}}(\sigma)
-    \and
-    \t\vert_{\ul Y} \in \Acc_{\s\vert_{B,C}}(\tau)\,,
+    \t\vert_{\ul X} \in \Acc_{\s\vert_{A,B}}(\tilde\sigma)
+    \and
+    \t\vert_{\ul Y} \in \Acc_{\s\vert_{B,C}}(\tilde\tau)\,,
   \end{mathpar}
@@
   \[
-    \{\t\in\sigma\|(\ul X \to \tau)\suchthat \t\vert_{A,B,C}=\s\} \to \Acc_{\s\vert_{A,B}}(\sigma)\times\Acc_{\s\vert_{B,C}}(\tau)\,.
+    \{\t\in\tilde\sigma\|(\ul X \to \tilde\tau)\suchthat \t\vert_{A,B,C}=\s\} \to \Acc_{\s\vert_{A,B}}(\tilde\sigma)\times\Acc_{\s\vert_{B,C}}(\tilde\tau)\,.
     \]
@@
 
-  Indeed, suppose that $\t,\t'$ are two interactions in $\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}=\s$, $\t\vert_{\ul X} = \t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$.
+  Indeed, suppose that $\t,\t'$ are two interactions in $\tilde\sigma\|(\ul X \to \tilde\tau)$ such that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}=\s$, $\t\vert_{\ul X} = \t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$.
   We claim that $\t = \t'$.
@@
   By our earlier analysis (see, for example, the proof of \ref{PropComposition}), we know that $p$ and $q$ must either both occur in the $A \to (\ul X \to B)$-component, or both in the $(\ul X \to B) \to (\ul X \to (\ul Y \to C))$-component.
-  But since $\t,\t'\in\sigma\|(\ul X \to \tau)$ are both interactions of deterministic strategies, we also know that they must both be $O$-moves in that component -- otherwise, they would have to be equal.
+  But since $\t,\t'\in\tilde\sigma\|(\ul X \to \tilde\tau)$ are both interactions of deterministic strategies, we also know that they must both be $O$-moves in that component -- otherwise, they would have to be equal.
   In particular, neither $p$ nor $q$ may be a move in the middle component $\ul X \to B$, since then it would be a $P$-move in one of the two components.
@@
   By Corollary \ref{CorSwitchingCondition}, we know that only Player $P$ may switch between games in $\ul X \to (\ul Y \to C)$, and therefore $p$ and $q$ must occur in the same component game -- i.e., both in $A$, both in $\ul X$, both in $\ul Y$ or both in $C$.
-  But now the conditions that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}$, $\t\vert_{\ul X}=\t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$ mean that we must have $p=q$, which is the desired contradiction.
+  But now the conditions that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}$, $\t\vert_{\ul X}=\t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$ mean that we must have $p=q$.  
+  For example, if $p$ and $q$ are both moves in $C$, then we have $\r\vert_Cp\prefix\t\vert_C$ and $\r\vert_Cq\prefix \t'\vert_C$; since $\t\vert_C=\t'\vert_C$, we must have $p=q$.  
+  This is the desired contradiction.
 
   For surjectivity, let $u\in\Acc_{\s\vert_{A,B}}(\sigma)$ and $v\in\Acc_{\s\vert_{B,C}}(\tau)$.  
-  We seek a sequence $\t\in\sigma\|(\ul X \to \tau)$ such that $\t\vert_{A,B,C}=\s$, $\t\vert_{\ul X}=qu$ and $\t\vert_{\ul Y}=qv$.
-\end{proof}
-
-\section{Danos-Harmer Probabilistic Game Semantics}
+  We seek a sequence $\t\in\tilde\sigma\|(\ul X \to \tilde\tau)$ such that $\t\vert_{A,B,C}=\s$, $\t\vert_{\ul X}=qu$ and $\t\vert_{\ul Y}=qv$.
+
+  Since $u\in\Acc_{\s\vert_{A,B}}(\sigma)$, there is some sequence $s\in\sigma$ such that $s\vert_{A,B}=\s\vert_{A,B}$ and $s\vert_{\ul X}=qu$.  
+  Similarly, since $v\in\Acc_{\s\vert_{B,C}}(\tau)$, there is some sequence $t\in\tau$ such that $t\vert_{B,C}=\s\vert_{B,C}$ and $t\vert_{\ul Y}=qv$.
+  We form the sequence $\t$ as a suitable interleaving of $s$ and $t$, noting that they have the same $B$-components: we start with the sequence $\s$, and then insert the appropriate moves from (the left-hand copy of) $\ul X$ and $\ul Y$ between the corresponding moves from $A$, $B$ and $C$.
+  Lastly, we insert moves from the right-hand copy of $\ul X$ adjacent to the corresponding moves in the right-hand copy, inserting an $O$-move $q$ in the right-hand copy of $\ul X$ immediately after each $O$-move $q$ in the left-hand copy, and a $P$-move $x$ in the right-hand copy immediately before each $P$-move $x$ in the left-hand copy.
+
+  This tells us that we have
+{\setlength{\IEEEnormaljot}{20pt}%
+  \begin{IEEEeqnarray*}{Cl}
+    &  \bP(\s\vert_{A,B}\in\sigma)\bP(\s\vert_{B,C}\in\tau) \\
+    = & \left( \sum_{u\in\Acc_{\tilde\sigma}(\s\vert_{A,B})} \prod_{i=0}^{|u|-1} \bP(V = u^{(i)}) \right)
+        \left( \sum_{v\in\Acc_{\tilde\tau}  (\s\vert_{A,B})} \prod_{i=0}^{|v|-1} \bP(W = v^{(i)}) \right) \\
+    = & \sum_{(u,v)\in\Acc_{\tilde\sigma}(\s\vert_{A,B}) \times \Acc_{\tilde\tau}(\s\vert_{B,C})} \prod_{i=0}^{|u|-1} \bP(V=u^{(i)}) \prod_{i=1}^{|v|-1} \bP(W=v^{(i)}) \\
+    = & \sum_{\stackrel{\t\in\tilde\sigma\|(\ul X \to \tilde\tau)}{\t\vert_{A,B,C}=\s}}
+      \left[ \prod_{i=1}^{|u|-1} \bP(V = u^{(i)}) \prod_{i=0}^{|v|-1} \bP(W = v^{(i)}) \;\middle|\; \mbox{\pbox{\textwidth}{where\\$\t\vert_{\ul X} = qu$ \\ $\t\vert_{\ul Y} = qv$}} \right]\,.
+  \end{IEEEeqnarray*}
+}
+  Now let $s\in \L_{A \to C}$ and let $t\in\sigma;\tau$ be such that $t/s$.
+  By the argument in Proposition \ref{PropComposition}, there is a unique interaction sequence $S\in\sigma\|(\ul X\to\tau)\|(\Lambda\inv;\mu)$ such that $S\vert_{A,\ul{X\times Y} \to C}=t$.
+  Define $\t = S\vert_{A,\ul X \to B,\ul X \to (\ul Y \to C)}$, and $\s=\t\vert_{A,B,C}$.
+  Now we must have $\s\vert_{A,C}=t\vert_{A,C}=s$, so $\s\in\wit_B(s)$.
+
+  Now consider $\t\vert_{\ul X,\ul Y}$, which has the same length as $S\vert_{\ul{X\times Y}}=t\vert_{\ul{X\times Y}}$.
+  This sequence is made up of pairs of moves $qx$ for $x\in X$ or $qy$ for $y\in Y$.
+
+  By the definition of $\mu$, we know that if the $i$-th pair of moves in $\t\vert_{\ul X,\ul Y}$ is $qx$ for $x\in X$, then the $i$-th pair of moves in $t\vert_{\ul{X\times Y}}$ is $q(x,y_0)$ for some $y_0$, and if the $i$-th pair of moves in $\t\vert_{\ul X,\ul Y}$ is $qy$ for $y\in Y$, then the $i$-th pair of mvoes in $t\vert_{\ul{X\times Y}}$ is $q(x_0,y)$ for some $x_0\in X$.
+  Moreover, if $t'$ is some other sequence such that $t'/s$ and such that $t'$ differs only from $t$ in the choice of the `irrelevant' moves $x_0,y_0$, then there is some $S'\in\sigma\|(\ul X \to \tau)\|(\Lambda\inv;\mu)$ such that $S\vert_{A,\ul{X\times Y}\to C}=t'$ and $S\vert_{A,\ul X \to (\ul Y \to C)}=\t$.
+  Then the combined probability of all such sequences is given by
+  \[
+    \left[ \prod_{i=1}^{|u|-1} \bP(V = u^{(i)}) \prod_{i=0}^{|v|-1} \bP(W = v^{(i)}) \;\middle|\; \mbox{\pbox{\textwidth}{where\\$\t\vert_{\ul X} = qu$ \\ $\t\vert_{\ul Y} = qv$}} \right]\,,
+    \]
+  and we can combine this with our calculations above to get the desired result.
+\end{proof}
+
+A consequence of Proposition \ref{PropCompositionProb} is that the probabilistic equivalence relation defined in \ref{DefProbabilisticEquivalenceRelation} is respected by composition of strategies.
+We may therefore take the quotient of this category by the probabilistic equivalence relation to form a new category
+\[
+  (\G/\oppcat{(\Rv_{\Omega}^{FS})})\char`\\\approx_\bP\,.
+  \]
+Then next proposition shows that we do not lose anything by doing this, since the probabilistic equivalence relation gets subsumed into our intrinsic equivalence.
+
+\begin{proposition}
+  Suppose that $[\sigma],[\tau]\from A \to B$ are morphisms in the quotiented category, given by equivalence classes of strategies in $\G/\oppcat{(\Rv_\Omega^{FS})}$.
+  Then $[\sigma]$ and $[\tau]$ are probabilistically intrinsically equivalent in the quotiented category if and only if $\sigma$ and $\tau$ are probabilistically intrinsically equivalent in the original category.
+\end{proposition}
+\begin{proof}
+  If $\sigma,\tau$ are not intrinisically equivalent, then there is some $\alpha\from(A \to B) \to \bC$ such that $\bP(\Lambda\inv(\sigma);\alpha\downarrow)\ne\bP(\Lambda\inv(\tau);\alpha;\downarrow)$.
+  Then we have $\bP(qa\in\Lambda\inv(\sigma);\alpha) \ne \bP(qa\in\Lambda\inv(\tau);\alpha)$, and therefore $\Lambda\inv(\sigma);\alpha\not\approx_{\bP}\Lambda\inv(\tau);\alpha$.
+
+  Conversely, if $[\sigma],[\tau]$ are not intrinsically equivalent in the quotiented category, then there is some $[\alpha]\from (A \to B) \to \bC$ such that
+  \[
+    [\Lambda\inv(\sigma);\alpha] \not\approx_\bP [\Lambda\inv(\tau);\alpha]\,.
+    \]
+  It follows that
+  \[
+    \bP(qa\in\Lambda\inv(\sigma);\alpha) \ne \bP(qa\in\Lambda\inv(\tau);\alpha)\,;
+    \]
+  i.e., that
+  \[
+    \bP(\Lambda\inv(\sigma);\alpha\downarrow) \ne \bP(\Lambda\inv(\tau);\alpha\downarrow)\,,
+    \]
+  and so $\sigma$ and $\tau$ are not intrinsically equivalent in the original category.
+\end{proof}
+
+\section{The Probabilistic Game Semantics of Danos and Harmer}
+
+The work in the previous section shows that it suffices to consider equivalence classes of strategies under the relation $\approx_\bP$, which suggests that we may take the quantities $\bP(s\in\sigma)$ as primitives, rather than defining them indirectly.
+
+This is the approach taken by Danos and Harmer in \cite{DanosHarmer} -- the original game semantics for a probabilistic variant of Algol.  
+Danos and Harmer define an arena as we do, but define a probabilistic strategy on an arena $A$ to be given by a function
+\[
+  \sigma \from \L_A^{\text{even}} \to [0,1]
+  \]
+such that for any even-length $s$, and any extension $sa$, we have
+\[
+  \sigma(s) \ge \sum_{sab\in\L_A} \sigma(sab)\,.
+  \]for any even-length $s$, and any extension $sa$, we have
+\[
+  \sigma(s) \ge \sum_{sab\in\L_A} \sigma(sab)\,.
+  \]
+These quantites $\sigma(s)$ take the role of our $\bP(s\in\sigma)$, but now they are part of the \emph{definition} of the strategy $\sigma$, rather than being a calculated quantity.
+
+\begin{proposition}
+  For any \Mellies strategy $\sigma\from A \to B$ given by a random variable $V$ taking values in a set $X$ and a strategy $\tilde\sigma \from A \to (\ul X \to B)$, we get a probabilistic strategy in the sense of Danos and Harmer by setting
+  \[
+    \sigma(s)=\bP(s\in\sigma)\,.
+    \]
+\end{proposition}
+\begin{proof}
+  We need to check that for any odd-length legal play $sa\in \L_A$ we have
+  \[
+    \bP(s\in\sigma) \ge \sum_{sab\in \L_A} \bP(sab\in\sigma)\,.
+    \]
+  But for any $u\in\Acc_{sab}(\sigma)$, there must be some prefix $v$ of $u$ such that $v\in\Acc_s(\sigma)$.
+  Then all the sequences $u$ arising in this way that have $v$ as a prefix are pairwise incomparable (since $\tilde\sigma$ is a deterministic strategy), and so their combined probability is at most the probability of $v$.
+\end{proof}
+Clearly, two morphisms in $\G/\oppcat{(\Rv_\Omega^{FS})}$ give rise to the same probabilistic strategy in this way if and only if they are probabilistically equivalent.
+
+Danos and Harmer then \emph{define} the composition of two probabilistic strategies using the formula that we derived in Proposition \ref{PropCompositionProb}:
+
+\begin{definition}
+  Let $\sigma\from A \to B$, $\tau \from B \to C$ be probabilistic strategies.  
+  Then their composition $\sigma;\tau$ is given by
+  \[
+    (\sigma;\tau)(s) = \sum_{\s\in\wit_B(s)} \sigma(\s\vert_{A,B})\tau(\s\vert_{B,C})\,.
+    \]
+\end{definition}
+By Proposition \ref{PropCompositionProb}, the composition of strategies in the quotiented category agrees with this composition of Danos and Harmer.
+Our proof above then gives an alternative proof of Full Abstraction for Danos and Harmer's probabilistic game semantics.
 

### 2019-05-28 Thesis/conc.tex
Nightly commit.

@@
 
+Concretely, the morphisms in $\G/\X$ are the same as usual, while the order structure is given by a transfinite construction as in \cite[2.17]{Fiech}.  
+In particular, if $\sigma,\tau\from A \to B$ in $\G/\X$ are given by morphisms
+\begin{mathpar}
+  \tilde{\sigma}\from A \to X.B
+  \and
+  \tilde{\tau} \from A \to Y.B
+\end{mathpar}
+in $\G$, and if there are morphisms $h\from X \to Z$, $k\from Y \to Z$ in $\X$ such that
+\[
+  \sigma;(h.B)\le\tau;(k.B)\,,
+  \]
+then $\sigma\le\tau$ in $\G/\X$.
+
+In either case, we now define the interpretation of the fixpoint combinator $\Y$ using the properties of this new order, which will be enough to prove adequacy along the lines of Theorem \ref{TheComputationalAdequacyIA}.
+
+It is worth mentioning that although we can prove computational adequacy for our various Kleisli categories (and categories of the form $\G/\X$), it does not automatically follow that we can prove adequacy in the same way for the various quotiented categories.
+An important example is our model of countable nondeterminism with must testing.  
+It is well known (see, e.g., \cite{Apt,PlotkinApt}) that countable nondeterminism is inextricably linked to dicontinuity of composition, which robs us of an important ingredient in the standard order-theoretic proof of adequacy.
+
+The solution is to prove adequacy in the normal way for the semantics of IA${}_\bN$ in $\G_\bN$, and then to apply the argument from Corollary \ref{CorAdeqMust} to reduce this to a Computational Adequacy result for the semantics of Idealized Algol with countable nondeterminism and must testing.
+Here, we are using an idea due to Levy \cite{LevyGsInfinite}: that if we want to prove adequacy for countable nondeterminism, then we need a form of \emph{explicit forcing}, in which we uncover some information about the points at which we have made an infinite nondeterministic branch.
+In our case, the explicit forcing is done through the language IA${}_\bN$, which creates a complete record of the nondeterministic values we have chosen along the way.  
+We have then applied the second part of Levy's technique -- \emph{hiding} -- to remove the explicit information and yield a pure, computationally adequate model of countable nondeterminism.
+
 \bibliographystyle{alpha2}

### 2019-07-01 Thesis/conc.tex
Stoke Ferry commit.

@@
 
-Concretely, the morphisms in $\G/\X$ are the same as usual, while the order structure is given by a transfinite construction as in \cite[2.17]{Fiech}.  
+Concretely, the underling set of morphisms in $\G/\X$ contains all the usual morphisms from the $\Set$-enriched case, while the order structure is given by a transfinite construction as in \cite[2.17]{Fiech}.
 In particular, if $\sigma,\tau\from A \to B$ in $\G/\X$ are given by morphisms
@@
 
-In either case, we now define the interpretation of the fixpoint combinator $\Y$ using the properties of this new order, which will be enough to prove adequacy along the lines of Theorem \ref{TheComputationalAdequacyIA}.
+A slight problem is that it is not true in general that the colimit of cpos with bottom elements has itself a bottom element.  
+For example, let $-[n]$ be the partial order $\{-n<\cdots<0\}$.  
+Then, $-[n]$ is a dcpo with a bottom element for each $n$, but the colimit of the chain
+\[
+  -[0] \hookrightarrow -[1] \hookrightarrow -[2] \hookrightarrow \cdots
+  \]
+is the partial order of non-positive integers.
+
+However, if all the morphisms in a diagram of dcpos are such that they preserve bottom elements, then the colimit of that diagram will have a bottom element.
+
+In particular, if the action of $\X$ on $\G$ is a reader-style action that factors through the category of sets (as in all our examples), then every arrow in the colimit diagram that defines $\G/\X(A,B)$ will be of the form
+\[
+  \G(A, \ul Y \to B) \xrightarrow{\G(A,\ul f.B)} \G(A, \ul X \to B)
+  \]
+for some sets $X,Y$, considered as objects $\ul X,\ul Y$ of $\G$, and some function $f \from X \to B$ considered as a morphism $\ul f \from \ul A \to \ul B$ such that composition with $\ul f$ preserves bottom elements.
+Therefore, the map $\G(A,\ul f.B)$ of dcpos will also preserve bottom elements.
+
+A second problem is that the setwise colimit of the $\G(A,X.B)$, with the order from \cite{Fiech}, is not necessarily itself a dcpo.  
+In fact, to get the correct colimit of the diagram, we need to perform an extra step of \emph{completion}.  
+However, with a little more care, we can show that if the action is a reader action that factors through the category of sets, then the colimit is already directed complete under the order, at least in the category of games.
+
+Having given the definition of the order-enriched structure of $\G$, we may define the interpretation of the fixpoint combinator $\Y$ using the properties of this new order, which will be enough to prove adequacy along the lines of Theorem \ref{TheComputationalAdequacyIA}.
 

### 2019-07-01 Thesis/intro.tex
Adding introduction.

\documentclass[11pt]{report}

\input{../common/preamble}

\begin{document}

\chapter{Introduction}

\section{Denotational Semantics and Program Equivalence}

Given two pieces of computer code, in what circumstances can we say that they are interchangeable?
Clearly, the two pieces of code should return the same output for any choice of input values. 
But -- depending on the expressive power of the language -- this might not be enough.

For example, the following two Haskell functions appear to do the same thing.

\begin{lstlisting}[language=haskell]
f :: Int -> Int
f n = if (n == 0) then 0 else 0

g :: Int -> Int
g n = 0
\end{lstlisting}

However, if we introduce a non-terminating function
\begin{lstlisting}[language=haskell]
diverge :: Int -> Int
diverge x = diverge x
\end{lstlisting}
then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: since \lstinline[language=haskell]{f} always evaluates its argument \lstinline[language=haskell]{n}, \lstinline[language=haskell]{f (diverge 0)} will fail to terminate, whereas \lstinline[language=haskell]{g (diverge 0)} will give us \lstinline[language=haskell]{0}, since inputs to functions are evaluated lazily in Haskell.

We can have another go at answering our original question, then, by adding the requirement that the two programs should behave in the same way if they are passed non-terminating inputs.
Thus, we add to each datatype an extra distinguished value $\bot$ representing non-termination (so, for example, the type of integers is represented by the set $\bZ_\bot = \bZ + \{\bot\}$), and then function types are interpreted as functions between these sets -- so a term of type \lstinline[language=haskell]{Int -> Int} is reprepresented by a function $\bZ_\bot \to \bZ_\bot$.

We need to be careful, though, since not every such function arises from a program in this way.
For example, we cannot write a program corresponding to the function $\chi\from\bZ_\bot \to \bZ_\bot$ that sends $\bot$ to $0$ and all other values to $1$since $\chi$ is not constant, such a program would have to evaluate its argument, and would consequently fail to terminate if that argument did not terminate.

If our language admits higher types, then it becomes especially important to exclude such `impossible' functions from our model.
For example, if $F$ and $G$ are two programs of type \lstinline[language=haskell]{(Int -> Int) -> Int} -- i.e., functions that take in a function from integers to integers and return an integer -- then we do not want to declare that $F$ and $G$ are different on the basis that $F(\chi)\ne G(\chi)$.

In order to rule out these `impossible' functions, we define a partial order on the sets $T_\bot$ corresponding to types, defined by setting $x\le x$ and $\bot\le x$ for all $x$.
We then require that functions should be monotonic and continuous with respect to this order. 
For example, a monotonic function $\bZ_\bot \to \bZ_\bot$ is either constant (correponding to a function that does not evaluate its argument at all) or sends $\bot$ to $\bot$ and is otherwise unconstrained (corresponding to a function that evaluates its argument).
It turns out that if we order functions pointwise, then we get the correct constraints at higher types as well.

Even if we get round the problems with divergence, there are other language features that we may need to consider if we want to determine whether two pieces of code are equivalent. 
If our functions have access to global variables, then we need to check that these variables end up taking the same final value, whatever their initial values were.
If we have IO calls in our language, then we need to check that the functions print out the same text, whatever the user input was.
If we have a random number generator, then we need to check that our functions return the same \emph{set} of values, whatever the input.

What we have been doing in all these examples is \emph{denotational semantics}: the art of using mathematical objects to study logic and programming languages.  
In the first case, our denotational semantics was expressed through the mathematics of sets and functions, whereby we captured the behaviour of a (programming language) function via a (mathematical) function.

Then, following Scott \cite{ScottDomains}, we refind this model to one based on partially-ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.

In our other examples, we need to come up with further refinements to our model in order to incorporate the new computational effects. 
For example, to handle nondeterminism, we might want to switch to using nondeterministic functions, or \emph{relations}, instead of ordinary functions.

The advantages in all of these cases is that the mathematical objects we use are often fairly simple, whereas computer programs, even in simple `toy' languages, are very complicated to study. 
A program is, at its heart, a string of symbols governed by a collection of operational rules that govern how such strings should behave. 
Such an object is very fiddly to reason with directly; indeed, the only way to think about it is as some kind of `function' from input to outputs.
Denotational takes this basic intuition further, and aims to capture features of programming languages through a diverse collection of different mathematical models.

A word of warning: the principal mode of denotational semantics which we shall be studying in this thesis is game semantics, which is much more complicated than the semantics of sets and functions. 
However, it is still a very valuable tool for determining equivalence of programs.

\section{Computational Adequacy and Full Abstraction}

In order for a denotational semantics to tell us anything, we first need to prove some results that relate it to the language we are studying. 
For example, if we are hoping to model a programming language with sets and functions, then we need to define a mapping $\deno{-}$ (the \emph{denotation}) that takes program types to sets and program functions to functions between those sets, and we also need to prove that this denotation respects the operational rules of the language: for example, we might want to prove that if $f \from \Int \to \Int$ is a function and $M \from \Int$ is a term that evaluates to the integer $n$, then the term $f M$ will evaluate to the integer $\deno{f}(n)$.
This type of result is called \emph{Computational Adequacy}, and relates to programs of a ground or observable type (e.g., a program that returns an integer has ground type, and we can observe that it either returns an integer or fails to teminate, whereas a program that takes in an integer and returns an integer has a function type: it is not possible to `observe' its behaviour without substituting in values).

Briefly speaking, a Computational Adequacy result tells us that the behaviour of a program of ground type may be deduced exactly from its denotation.
For example, in a domain-theoretic semantics, we might want to say that a program $M$ evaluates to a value $v$ if and only if $\deno M=v$ and that $M$ fails to terminate if and only if $\deno M = \bot$.

Such a computational adequacy result extends readily to terms not of ground type.  
Given two programs $M$ and $N$ of the same type, we say that $M$ and $N$ are \emph{observationally equivalent} if $C[M]$ and $C[N]$ have the same behaviour for any one-holed context $C[-]$ of ground type.
If our semantics is \emph{compositional} -- so that the denotation of $C[M]$ is obtained by `applying' the denotation of $C[-]$ to the denotation of $M$ -- and computationally adequate, then it follows that the semantics is \emph{equationally sound}: if two terms $M$ and $N$ have the same denotation, then they are observationally equivalent.

If we have an effective way of computing denotations, then this can give us an easy way to prove observational equivalence of terms.  
However, there is no guarantee that we are able to use such a trick: the terms $M$ and $N$ might be observationally equivalent despite having distinct denotations.  
The gold standard of denotational semantics -- \emph{Full Abstraction} -- asserts in addition that the converse of equational soundness holds, so that the denotational semantics completely captures the observational equivalence relation.

An important early success in this direction came with Plotkin's introduction of the stateless sequential programming language PCF \cite{PlotkinPcf}.  
Plotkin was unable to provide a fully abstract denotational semantics for PCF itself, but he showed that if we add a simple parallel construct\footnote{Specifically, `parallel or', which evaluates its two boolean arguments in parallel, and is thus able to return true if either the left or the right argument returns true, even if the other fails to terminate.} to PCF, then a denotational semantics based on Scott domains is fully abstract.  
This astounding result presents us with a world in which we can practically and systematically check observational equivalence (for terms of this extended version of PCF) by computing denotations.  
This vision is a little rosey-eyed -- deciding observational equivalence is stronger than the halting problem and is hence undecidable in general -- but if the programs in question are finitely presentable in some sense, then we really can use the denotational semantics to check observational equivalence.

Unfortunately, this stop working for PCF itself.  
PCF is a sub-language of the parallelized version, but this also means that the observational equivalence relation is coarser: there may be terms that can be distinguished by a context including the parallel construct that cannot be distinguished inside any purely sequential context.  
The enterprise was brought down to earth by Ralph Loader's 2001 theorem that observational equivalence for PCF is undecidable, even if we restrict ourselves to a finitary version of the language with no infinite datatypes or recursion beyond a simple non-termination primitive $\bot$.
This in particular tells us that no concretely presentable denotational semantics for PCF can possibly be fully abstract, or it would give us an algorithm for deciding observational equivalence in this finite version.

Nevertheless there were, roughly contemporaneous with Loader's result, several fully abstract models of PCF published, in a watershed moment for the subject.
The models published by Nickau \cite{NickauPcf} and O'Hearn and Riecke \cite{OHearnRieckePcf} were more or less along domain-theoretic lines, while those of Abramsky, Jagadeesan and Malacaria \cite{ajmPcf} and Hyland and Ong \cite{hoPcf} used the relatively new Game Semantics.

These models took a slightly oblique approach to Full Abstraction.  
First, they defined the notion of \emph{intrinsic equivalence} of terms of the same type $T$ in a denotational model, where two elements $\sigma$ and $\tau$ of the denotation of $T$ are intrinsically equivalent if $\alpha(\sigma)=\alpha(\tau)$ for all functions $\alpha\from\deno{T}\to\deno{o}$ from the denotation of $T$ to the denotation of some fixed ground type $o$.
This definition is very closely linked to that of observational equivalence; indeed, if two terms $M$ and $N$ are observationally equivalent, and we are working in a computationally adequate and compositional denotational semantics, then the denotations of $M$ and $N$ will be intrinsically equivalent, since for any ground-type context $C[-]$, we can take $\alpha$ to be the denotation of $C[-]$ in the above definition.

Proving the converse -- that intrinsic equivalence of denotations implies observational equivalence -- entails going in the opposite direction; i.e., starting with some element $\alpha$ in the model and coming up with a context $C[-]$ in the language whose denotation is $\alpha$.  
Thus, proving this direction normally reduces to some kind of \emph{definability} result.  
Typically, we only need to prove definability for a restricted class of elements $\alpha$ of the denotational model -- the \emph{compact} elements.

If we can prove, for some denotational model of a language, that observational equivalence of terms is equivalent to intrinsic equivalence of their denotations, then we can form a fully abstract model by passing to equivalence classes under the intrinsic equivalence relation.  
This is the approach taken by the fully abstract semantics that have been given for PCF; there is no contradiction of Loader's theorem, because the intrinsic equivalence relation is itself undecidable.

In this thesis, we shall skip the final step of passing to equivalence classes and declare a denotational semantics to be fully abstract for a language if we can prove that observational equivalence of terms is equivalent to intrinsic equivalence of their denotations.  
Thus, the Full Abstraction results that we prove will have three main ingredients: compositionality, computational adequacy and definability.

\section{Categorical Semantics}

There is a close link between (typed) programming langauges and categories.
Programming languages have things called \emph{types}, and they have \emph{functions} that go from one type to another. 
Typically, it will be possible to compose two functions together in the language in an associative way, giving us a category.
It should come as no surprise, then, that a very important branch of denotational semantics is \emph{categorical semantics}, in which we take some existing category from mathematics, and use its objects and morphisms to represent the types and terms of a programming language.

We can then use concepts from category theory to inform our denotational semantics. 
The most important of these is that if the category we choose is Cartesian closed, then we can automatically interpret terms of the simply typed lambda calculus as morphisms.
This is particularly useful, since many of the languages that we are most interested in studying from a mathematical point of view -- in particular, PCF and Idealized Algol -- are based upon the simply typed lambda calculus.
Thus, if we make sure that our base category is Cartesian closed, then we get a denotational semantics for the lambda calculus-part of the language for free, allowing us to concentrate on the other parts of the language.

Category-theoretic topics have taken on a new importance within functional programminging.
In 1991, Eugenio Moggi observed that \emph{monads} on categories provide a way to study computational effects. 
For example, we have already alluded to the fact that a stateful function $A \to B$ may be identified with an ordinary stateless function
\[
	A \times W \to B \times W\,,
	\]
where $W$ is some fixed set (the \emph{state}). 
Such a function may alternatively be written as a function
\[
	A \to (W \to (B \times W))\,;
	\]
thus, a morphism $A \to B$ in the Kleisli category for the \emph{state monad}
\[
	B \mapsto W \to (B \times W)\,.
	\]
Similarly, a nondeterministic function $A\to B$ may be thought of as a function from elements of $A$ to subsets of $B$, and thus as a morphism in the Kleisli category for the \emph{powerset monad} $\powerset-$.

The link between monads and computational effects has not been confined to the theoretical domain; indeed, monads quickly became the main way of expressing effectful programming in languages such as Haskell \cite{Haskell}.

In 2001, Plotkin and Power \cite{PlotkinPower} made this idea more precise by demonstrating that if a computational effect can be given by algebraic operations and equations, then it determines a monad.

More specifically, a \emph{signature} $\Sigma$ is made up of a set of \emph{operations} $\sigma$ with (possibly infinite) \emph{arities} $\text{ar}(\sigma)$ and \emph{equations} that encode the rules that hese operations must follow.
An \emph{interpretation} of a signature $\Sigma$ in a category $\C$ with products is given by an object $A$ of $\C$, together with morphisms
\[
	A^\text{ar}(\sigma) \to A
	\]
for each operation $\sigma$ in $\Sigma$, such that the equations all hold when interpreted as equalities of morphisms in $\C$.

A \emph{homomorphism} between $\Sigma$-algebras $A$ and $B$ is a morphism $A \to B$ that respects the $\Sigma$-algebra structure on $A$ and $B$ in a natural way. 
Thus, we get a category of $\Sigma$-algebras.
Moreover, the natural forgetful functor from this category into $\C$ admits a left adjoint, inducing a monad on $\C$.
This monad sends a set $A$ to the underlying set of the \emph{free $\Sigma$-algebra} on $A$, given by taking the set of all terms that can be formed from the operations in $\Sigma$, with the elements of $A$ as variables, and quotienting by the equivalence generated by the equations in $\Sigma$.

For example (see \cite{Powerset}, for instance), the powerset monad for countable sets is induced from the signature $\Sigma_\powerset$ consisting of a single infinitary operator $\sum$ (i.e., nondeterministic choice between the infinite collection of values), together with equations for infinitary commutativity (reordering the $a_i$ should not change the observed behaviour), associativity ($\sum_i \sum_j a_{ij} = \sum_{i,j} a_{ij}$) and idempotence (repeat entries do not change the behaviour).

If $A$ is a set, then we may identify an element $\phi$ of the free $\Sigma_\powerset$-algebra on $A$ with the subset of $A$ consisting of all elements $a\in A$ that appear in the term-description of $\phi$.
For example, if $A=\bN$, then we can identify
\[
	\sum_i 2i
	\]
with the set of even natural numbers, and
\[
	\sum_i \sum_j \pi(i)^j
	\]
with the set of all prime powers.
The axioms for commutativity, associativity and idempotence mean that this is a well-defined operation, giving us an equivalence between the free $\Sigma_\powerset$-algebra monad and the powerset monad $\powerset$.

\newcommand{\lku}{\operatorname{lookup}}
\newcommand{\upd}{\operatorname{update}}

The state monad with state given by a set $W$ is induced from the signature given by a $W$-ary operation $\lku$, corresponding to choosing between $W$-many options based on the value of the state; and $W$-many nullary operations $\upd_w$, each corresponding to updating the state to a particular value $w$.
There are four axioms relating these two operations, which we adapt from \cite{PlotkinPower}.
\begin{description}
	\item[Update with current value] 
          \[
            \lku(\upd_w(x)\suchthat w\in W) = x\,.
            \]
          Looking up the current value and rewriting it is a no-op.
	\item[Idempotence of lookup]
          \[
            \lku(\lku(x_{vw}\suchthat v\in W)\suchthat w\in W)=\lku(x_{ww}\suchthat w\in W)\,.
            \]
          If we look up the state twice in succession, then we will get the same value both times.
	\item[Double update] 
          \[
            \upd_v(\upd_w(x))=\upd_w(x)\,.
            \]
          If we update the value twice in succession, then the first update has no effect.
	\item[Lookup] 
          \[
            \upd_w(\lku(x_v\suchthat v\in W)) = \upd_w(x_w)\,.
            \]
          If we update the value to $w$ and then look up the state, we get $w$ back.
\end{description}

Plotkin and Power prove in \cite{PlotkinPower} that the free algebra monad for this signature is isomorphic to the usual state monad $(W \times -)^W$.
We therefore get a strong connection between some very concrete syntactic concepts about what state should look like and the abstract category-theoretic concept of a monad.

\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-07-15 Thesis/intro.tex
Daily commit.

@@
 
-We can then use concepts from category theory to inform our denotational semantics. 
-The most important of these is that if the category we choose is Cartesian closed, then we can automatically interpret terms of the simply typed lambda calculus as morphisms.
-This is particularly useful, since many of the languages that we are most interested in studying from a mathematical point of view -- in particular, PCF and Idealized Algol -- are based upon the simply typed lambda calculus.
-Thus, if we make sure that our base category is Cartesian closed, then we get a denotational semantics for the lambda calculus-part of the language for free, allowing us to concentrate on the other parts of the language.
+Typically, each type $T$ of the language will correspond to some object $\deno T$ of the category, while a term of type $T$ will correspond to a morphism $1 \to \deno T$, where $1$ is some fixed object in the category (usually a terminal object).
 
-Category-theoretic topics have taken on a new importance within functional programminging.
-In 1991, Eugenio Moggi observed that \emph{monads} on categories provide a way to study computational effects. 
-For example, we have already alluded to the fact that a stateful function $A \to B$ may be identified with an ordinary stateless function
+Particularly important \cite{Lambek} are the Cartesian closed categories, which have a number of properties making them suitable for denotational semantics:
+\begin{description}
+  \item[Product and function spaces] Given types $S$ and $T$, we can define the denotations of the product type $S \times T$ and the function type $S \to T$ to be given by $\deno S \times \deno T$ and ${\deno T}^{\deno S}$.
+  \item[Compositionality] Given types $S$ and $T$, and corresponding objects $\deno S$ and $\deno T$ of the category, we can define the denotation of the function type $S \to T$ to be given by the exponentiation ${\deno T}^{\deno S}$ as above.
+    Then we automatically have a recipe for substituting a term of type $S$ into a function of type $S\to T$ via the canonical morphism
     \[
-	A \times W \to B \times W\,,
+      {\deno T}^{\deno S} \times \deno S \to \deno T\,.
       \]
-where $W$ is some fixed set (the \emph{state}). 
-Such a function may alternatively be written as a function
+  \item[Abstraction] Given a morphism $\sigma \from A \times B \to C$, we may form a morphism $\Lambda(\sigma) \from A \to C^B$.
+    This gives us the semantics for $\lambda$-abstraction, whereby we pass from a term-in-context
     \[
-	A \to (W \to (B \times W))\,;
+      \Gamma,x\from S \ts M \from T
       \]
-thus, a morphism $A \to B$ in the Kleisli category for the \emph{state monad}
+    to the term-in-context
     \[
-	B \mapsto W \to (B \times W)\,.
+      \Gamma \ts \lambda x.M\from S \to T\,.
       \]
-Similarly, a nondeterministic function $A\to B$ may be thought of as a function from elements of $A$ to subsets of $B$, and thus as a morphism in the Kleisli category for the \emph{powerset monad} $\powerset-$.
+\end{description}
+These rules allow us to build up a model of the simply-typed $\lambda$-calculus within any Cartesian closed category, which means we get a large part of the denotation (and the subsequent proof of Computational Adequacy) for free.
 
-The link between monads and computational effects has not been confined to the theoretical domain; indeed, monads quickly became the main way of expressing effectful programming in languages such as Haskell \cite{Haskell}.
+This alone would be a good justification for using category theory in denotational semantics, but the benefits go further.  
+The development of programming languages such as Haskell has been strongly influenced by category-theoretic concepts.  
+For example, Moggi's 19xx observation \cite{Moggi} that monads on categories provide us with a way of modelling computational effects influenced work that led directly to the introduction of support for monads in Haskell \cite{Haskell}, where they have become the primary tool for abstracting out effectful computation.
 
-In 2001, Plotkin and Power \cite{PlotkinPower} made this idea more precise by demonstrating that if a computational effect can be given by algebraic operations and equations, then it determines a monad.
+Monads will be particularly important in this thesis, so it is worth dwelling on them a little further.  
+A \emph{monad} on a category $\C$ is given by a functor $M\from \C \to \C$, together with natural transformations
+\begin{mathpar}
+  e\from\id_\C \Rightarrow M \and m\from M\circ M\Rightarrow M
+\end{mathpar}
+that endow $M$ with an algebraic structure.
+One example is the non-empty powerset functor on the category of sets, together with the natural transformations given by
+\begin{mathpar}
+  \begin{IEEEeqnarraybox*}{rCcCl}
+    e & \from & A & \to & \powerset(A) \\
+    && a & \mapsto & \{a\}
+  \end{IEEEeqnarraybox*}
+  \and
+  \begin{IEEEeqnarraybox*}{rCcCl}
+    m & \from & \powerset(\powerset(A)) & \to & \powerset(A) \\
+    && \mathcal A & \mapsto & \bigcup_{A \in \mathcal A} A\,.
+  \end{IEEEeqnarraybox*}
+\end{mathpar}
+This powerset monad indicates some kind of nondeterministic choice between elements of $A$, particularly if we modify the construction to the \emph{non-empty powerset} functor $\powerset_+$.
 
-More specifically, a \emph{signature} $\Sigma$ is made up of a set of \emph{operations} $\sigma$ with (possibly infinite) \emph{arities} $\text{ar}(\sigma)$ and \emph{equations} that encode the rules that hese operations must follow.
-An \emph{interpretation} of a signature $\Sigma$ in a category $\C$ with products is given by an object $A$ of $\C$, together with morphisms
+Another example in the category of sets is the functor $A \mapsto A + \{\bot\}$, that appends an additional element on to a set.  
+We have natural functions $A \to A + \{\bot\}$ and $A + \{\bot\} + \{\bot\} \to A + \{\bot\}$ that make this into a monad as well.
+In the study of programming languages, this is often called the \emph{maybe monad}, because $A + \{\bot\}$ indicates an element of $A$ that may or may not be present (with the distinguished value $\bot$ indicating no value).
+
+Given a monad $M$ on a category $\C$, we can form a new category $\Kl_M\C$ -- the \emph{Kleisli category} of $M$ -- whose objects are the objects of $\C$ and where a morphism from $A$ to $B$ is given by a morphism $A \to MB$ in $\C$.
+The monadic coherence gives us the correct notion of composition: given Kleisli morphisms $\sigma \from A \to MB$ and $\tau\from B \to MC$, we may compose them to give a morphism $A \to MC$ via the following formula.
 \[
-	A^\text{ar}(\sigma) \to A
+  A \xrightarrow{\sigma} MB \xrightarrow{M\tau} M M C \xrightarrow{m} MC
   \]
-for each operation $\sigma$ in $\Sigma$, such that the equations all hold when interpreted as equalities of morphisms in $\C$.
+The Kleisli category of the powerset monad is the category of sets and relations, while the Kleisli category of the maybe monad is the category of sets and partial functions.
 
-A \emph{homomorphism} between $\Sigma$-algebras $A$ and $B$ is a morphism $A \to B$ that respects the $\Sigma$-algebra structure on $A$ and $B$ in a natural way. 
-Thus, we get a category of $\Sigma$-algebras.
-Moreover, the natural forgetful functor from this category into $\C$ admits a left adjoint, inducing a monad on $\C$.
-This monad sends a set $A$ to the underlying set of the \emph{free $\Sigma$-algebra} on $A$, given by taking the set of all terms that can be formed from the operations in $\Sigma$, with the elements of $A$ as variables, and quotienting by the equivalence generated by the equations in $\Sigma$.
+There are numerous other monads that can be used to model computational effects, such as the state monad and the exception monad.  
+Work by Plotkin and Power \cite{PlotkinPower} makes this more precise, by studying monads that can be built up via algebraic operations and equations.  
+For example, we might want to model nondeterministic choice on a set $A$ via an operation $\sum$ that takes in infinitely many elements of $A$ -- so $\sum a_i$ gives us a choice between the $a_i$.  
+We then impose some axioms on this operation.
+\begin{description}
+  \item[Idempotence] If $a_i=a$ for all $i$, then $\sum a_i=a$;
+  \item[Commutativity] $\sum a_i = \sum_{a_{\pi(i)}}$ for any permutation $\pi$; and
+  \item[Associativity] $\sum_i (\sum_j a_{ij}) = \sum_{i,j} a_{ij}$.
+\end{description}
+This is an algebraic theory akin to the theory of groups, and its category of free algebras is isomorphic to the Kleisli category of the powerset monad.
 
-For example (see \cite{Powerset}, for instance), the powerset monad for countable sets is induced from the signature $\Sigma_\powerset$ consisting of a single infinitary operator $\sum$ (i.e., nondeterministic choice between the infinite collection of values), together with equations for infinitary commutativity (reordering the $a_i$ should not change the observed behaviour), associativity ($\sum_i \sum_j a_{ij} = \sum_{i,j} a_{ij}$) and idempotence (repeat entries do not change the behaviour).
+\section{Game Semantics}
 
-If $A$ is a set, then we may identify an element $\phi$ of the free $\Sigma_\powerset$-algebra on $A$ with the subset of $A$ consisting of all elements $a\in A$ that appear in the term-description of $\phi$.
-For example, if $A=\bN$, then we can identify
-\[
-	\sum_i 2i
-	\]
-with the set of even natural numbers, and
-\[
-	\sum_i \sum_j \pi(i)^j
-	\]
-with the set of all prime powers.
-The axioms for commutativity, associativity and idempotence mean that this is a well-defined operation, giving us an equivalence between the free $\Sigma_\powerset$-algebra monad and the powerset monad $\powerset$.
+Game Semantics gives us a particularly fruitful categorical semantics for programming languages.  
+The underlying idea is that a computer program behaves like a strategy for a two-player game, in that it needs to respond to arbitrary inputs (opponent moves) with its own behaviours (proponent moves).
+Thus, we represent a programming language type by an idealized two-player game and represent a term of that type by a strategy for that game.
 
-\newcommand{\lku}{\operatorname{lookup}}
-\newcommand{\upd}{\operatorname{update}}
+The precise definition of a strategy that we use depends on the language that we are trying to model -- a language with less expressive power can realize fewer strategies.  
+For example, the denotations of terms in a stateless langauge such as PCF are \emph{history-free} or \emph{innocent}, in which the proponent's moves can only depend on a particular subsequence of the current sequence of moves -- the $P$-view -- rather than on the whole sequence.
+So for a lot of computational effects, particularly ones that have something to do with state, adding that effect corresponds to a \emph{relaxing} of conditions on strategies.
 
-The state monad with state given by a set $W$ is induced from the signature given by a $W$-ary operation $\lku$, corresponding to choosing between $W$-many options based on the value of the state; and $W$-many nullary operations $\upd_w$, each corresponding to updating the state to a particular value $w$.
-There are four axioms relating these two operations, which we adapt from \cite{PlotkinPower}.
-\begin{description}
-	\item[Update with current value] 
-          \[
-            \lku(\upd_w(x)\suchthat w\in W) = x\,.
-            \]
-          Looking up the current value and rewriting it is a no-op.
-	\item[Idempotence of lookup]
-          \[
-            \lku(\lku(x_{vw}\suchthat v\in W)\suchthat w\in W)=\lku(x_{ww}\suchthat w\in W)\,.
-            \]
-          If we look up the state twice in succession, then we will get the same value both times.
-	\item[Double update] 
-          \[
-            \upd_v(\upd_w(x))=\upd_w(x)\,.
-            \]
-          If we update the value twice in succession, then the first update has no effect.
-	\item[Lookup] 
-          \[
-            \upd_w(\lku(x_v\suchthat v\in W)) = \upd_w(x_w)\,.
-            \]
-          If we update the value to $w$ and then look up the state, we get $w$ back.
-\end{description}
+We model other types of effects by extending the definition of a strategy.  
+For example, if we want to provide a semantics for a language with nondeterminism, then we modify the definition of a strategy so that the propoonent can have multiple replies to each opponent move, as in the work of Harmer and McCusker \cite{mcCHFiniteND}.
+If we want to model a probabilistic language, then we decorate these different moves with probabilities, as in the work of Danos and Harmer \cite{DanosHarmer}.
 
-Plotkin and Power prove in \cite{PlotkinPower} that the free algebra monad for this signature is isomorphic to the usual state monad $(W \times -)^W$.
-We therefore get a strong connection between some very concrete syntactic concepts about what state should look like and the abstract category-theoretic concept of a monad.
+When choosing a definition of a strategy, the aim is to prove a definability result, so that we can prove Full Abstraction.  
+The original proofs of definability of compact innocent strategies in PCF from \cite{ajmPcf} and \cite{hoPcf} were intricate and technical.  
+Subsequent work on languages that extend PCF tends to try to prove definability via a \emph{factorization result}, in which we show that every strategy in an extended category of games may be written as the composition of a strategy in an original category of games with some fixed strategy in the new category.
+Then, if we have a definability result for the original semantics, we can extend it to a definability result in the new category.
+
+For example, the language Idealized Algol is an extended version of PCF that adds some stateful primitives.
+For example, Abramsky and McCusker's proof of compact definability for Idealized Algol in \cite{SamsonGuyIAActive} first proves that each compact strategy in their model may be written as the composite of a compact innocent strategy with the (non-innocent) denotation of one of the new stateful constants.
+Thus, they can deduce compact definability for Idealized Algol from Hyland and Ong's result that every compact innocent strategy is the denotation of a term of PCF.
+
+Harmer and McCusker develop in \cite{mcCHFiniteND} a model of game semantics in which strategies can be nondeterministic.  
+They show that every such strategy can be written as the composite of a deterministic strategy with some particular fixed nondeterministic strategy.  
+Then, to prove compact definability for nondeterministic Idealized Algol, it suffices for them to exhibit a nondeterministic term whose denotation is that fixed strategy.
 

### 2019-07-21 Thesis/intro.tex
Regular commit.

@@
 The underlying idea is that a computer program behaves like a strategy for a two-player game, in that it needs to respond to arbitrary inputs (opponent moves) with its own behaviours (proponent moves).
-Thus, we represent a programming language type by an idealized two-player game and represent a term of that type by a strategy for that game.
+Thus, we represent a programming language type by an idealized game between two players $O$ and $P$\footnote{Another convention is to refer to player $O$ as $\forall{}$belard and player $P$ as $\exists{}$lo\"{i}se, so I will refer to player $O$ as `he' and player $P$ as `she' throughout.}, and represent a term of that type by a strategy for that game.
+
+The power of game semantics comes from the fact, first noted in \cite{blassgames} by Blass, that certain natural operations on games correspond to some of the connectives of linear logic.  
+For example, if $A$ and $B$ are two-player games, then we may form their \emph{tensor product} $A\tensor B$, which is played by running the games $A$ and $B$ together in parallel, with the opposing player $O$ allowed to switch between games when it is his turn.
+
+A closely related construction takes games $A$ and $B$ and forms their \emph{linear implication} $A\implies B$, in which $B$ is played in parallel with the \emph{dual} of $A$, in which the roles of players $P$ and $O$ are swapped round.
+This time, player $P$ can choose to switch game when it is her turn.
+
+The remarkable thing about the $\implies$ construction, first pointed out by Joyal in \cite{joyalgames}, is that if $A$, $B$ and $C$ are games, then we may compose a $P$-strategy for $A\implies B$ with a $P$-strategy for $B\implies C$ to get a $P$-strategy for $A\implies C$.
+
+In order to form her strategy, player $P$ sets up a `scratchpad' consisting of the games $A\implies B$ and $B\implies C$ side by side.
+Now suppose that player $O$ makes a move in $A\implies C$ that originally came from the game $C$.  
+Then player $P$ treats this move as a move in $B\implies C$, and uses her strategy for that game to come up with a reply.  
+If that reply is a move in $C$, then she plays it as her response.
+Otherwise, if it is a move in $B$, she treats that move as an $O$-move in $A\implies B$, and therefore has a reply in $A\implies B$ according to her strategy for that game.  
+Eventually, if she plays a move in $A$ or $C$, then that will be her reply in the composite strategy.
+See Figure \ref{FigComposition} for an illustration.
+\begin{figure}
+  \[
+    \begin{tikzcd}[arrows={no head, dotted, shorten=-1mm}, row sep=0pt]
+      A
+        & B
+          &[-20pt] B
+            & C \\
+      %
+        & 
+          &
+            & \circ \arrow[d] \\
+      %
+        & 
+          & 
+            & \bullet \\
+      %
+        & 
+          & 
+            & \circ \arrow[dl] \\
+      %
+        & \circ \arrow[d]
+          & \bullet
+            & \\
+      %
+        & \bullet
+          & \circ \arrow[d]
+            & \\
+      %
+        & \circ \arrow[dl]
+          & \bullet
+            & \\
+      \bullet
+        &
+          &
+            & \\
+      \circ \arrow[dr]
+        &
+          &
+            & \\
+      %
+        & \bullet
+          & \circ \arrow[dr]
+            & \\
+      %
+        &
+          &
+            & \bullet
+    \end{tikzcd}
+    \]
+  \caption[Illustration of the composition of strategies in Game Semantics.]{Illustration of the composition of strategies in Game Semantics.  
+  Working top-to-bottom, the symbol $\circ$ denotes a move by $O$ and the symbol $\bullet$ a move by $P$.  
+  A dotted line indicates that a move is determined by one of the strategies for the games $A\implies B$ and $B\implies C$.  
+  Note that the moves in $B$ are duplicated, so that they may always be considered as an $O$-move in either $A\implies B$ or $B\implies C$.  
+  Moves from $B$ are hidden in the composite strategy: in this case, player $P$'s first `real' move is in $C$, her second in $A$ and her third in $C$.}
+  \label{FigComposition}
+\end{figure}
+
+It is possible instead that player $P$ flips between her two strategies for ever, always playing moves in $B$ and never coming out into $A$ or $C$.  
+Computationally, this represents `livelock': a computation that does not terminate because two subroutines are continually deferring to each other without returning values of their own.
+
+This composition of strategies gives us a category $\G$ in which the objects are games and a morphism from a game $A$ to a game $B$ is a strategy for the game $A\implies B$.  
+In this category, the identity morphism on a game $A$ is the \emph{copycat strategy} for $A\implies A$, which responds to an $O$-move in either copy of $A$ with the identical move in the other copy.
+
+What is more, the connectives $\tensor$ and $\implies$ make this into a symmetric monoidal closed category.  
+We typically apply some category-theoretic construction to $\G$ to get a Cartesian closed category, by passing either to the Kleisli category for a linear exponential comonad on $\G$ (as in \cite{ajmPcf}; see \cite{SchalkWhatIs}), or to a subcategory of the category of commutative comonoids in $\G$ (as in \cite{hoPcf,SamsonGuyIAActive}; see \cite[\sec 3.5.2]{RusssThesis}).
+
+\section{Game Semantics for Programming Languages}
+
+The first triumph of Game Semantics was to solve the Full Abstraction problem for PCF, but a more lasting application of the discipline has been to model more general programming languages with effects such as state.
+By making changes to the definitions of game and strategy, Game Semantics has proved to be applicable to a wide variety of programming language effects, including exceptions \cite{Lli}, coroutines and continuations \cite{FunctionalProgramsAsCoroutines}, nondeterminism \cite{mcCHFiniteND}, probability \cite{DanosHarmer}, and general references \cite{HondaMcCusker}.
 

### 2019-07-28 Thesis/intro.tex
Added some more pages to the introduction.

@@
 \section{Computational Adequacy and Full Abstraction}
+\label{SecCAnFA}
 
@@
 \section{Categorical Semantics}
+\label{SecCatSem}
 
@@
   Working top-to-bottom, the symbol $\circ$ denotes a move by $O$ and the symbol $\bullet$ a move by $P$.  
-  A dotted line indicates that a move is determined by one of the strategies for the games $A\implies B$ and $B\implies C$.  
+  A dotted line indicates that a move is determined by one of player $P$'s strategies for the games $A\implies B$ and $B\implies C$.  
   Note that the moves in $B$ are duplicated, so that they may always be considered as an $O$-move in either $A\implies B$ or $B\implies C$.  
@@
 
-What is more, the connectives $\tensor$ and $\implies$ make this into a symmetric monoidal closed category.  
-We typically apply some category-theoretic construction to $\G$ to get a Cartesian closed category, by passing either to the Kleisli category for a linear exponential comonad on $\G$ (as in \cite{ajmPcf}; see \cite{SchalkWhatIs}), or to a subcategory of the category of commutative comonoids in $\G$ (as in \cite{hoPcf,SamsonGuyIAActive}; see \cite[\sec 3.5.2]{RusssThesis}).
+What is more, the connectives $\tensor$ and $\implies$ make $\G$ into a symmetric monoidal closed category.  
+We typically apply some category-theoretic construction to $\G$ to get a Cartesian closed category, by passing either to the Kleisli category for a linear exponential comonad on $\G$ (as in \cite{ajmPcf}; see \cite{SchalkWhatIs}), or to a subcategory of the category of cocommutative comonoids in $\G$ (as in \cite{hoPcf,SamsonGuyIAActive}; see \cite[\sec 3.5.2]{RusssThesis}).
+Once we have a Cartesian closed category, we automatically have a way to interpret the simply-typed lambda calculus.
 
@@
 The first triumph of Game Semantics was to solve the Full Abstraction problem for PCF, but a more lasting application of the discipline has been to model more general programming languages with effects such as state.
-By making changes to the definitions of game and strategy, Game Semantics has proved to be applicable to a wide variety of programming language effects, including exceptions \cite{Lli}, coroutines and continuations \cite{FunctionalProgramsAsCoroutines}, nondeterminism \cite{mcCHFiniteND}, probability \cite{DanosHarmer}, and general references \cite{HondaMcCusker}.
+By making changes to the definitions of game and strategy, Game Semantics has proved to be applicable to a wide variety of programming language effects, including exceptions \cite{LLi}, coroutines and continuations \cite{FunctionalProgramsAsCoroutines}, nondeterminism \cite{mcCHFiniteND}, probability \cite{DanosHarmer}, and general references \cite{HondaMcCusker}.
 
@@
 
+We can now summarize the typical process of proving a Full Abstraction language for a language $\L'$ that extends a language $\L$ as follows.
+\begin{itemize}
+  \item Starting with an existing computationally adequate model $\C$ of $\L$ that satisfies compact definability, define a categorical model $\C'$ that admits an identity-on-objects functor $J\from \C \to \C'$.
+    For example, if $\C$ is a category of games and strategies, $\C'$ might be a category whose objects are the same games as $\C$, but where the strategies are less rigidly constrained.
+  \item Prove that the model $\C'$ is a Cartesian closed category and is computationally adequate for $\L'$.
+  \item Prove a factorization result that exhibits every morphism $g$ in $\C'$ as the composition of some morphism $Jf$ in the image of $J$ with one of some fixed collection of morphisms that are known to be definable in $\L'$ (for example, single terms from $\L'\setminus\L$.
+    In addition, if $g$ is compact, then $f$ should be compact in $\C$.
+\end{itemize}
+The third bullet point allows us to deduce a compact definability result for $\L'$ in $\C'$ from the compact definability result of $\L$ in $\C$, and then Full Abstraction follows as we have outlined in Section \ref{SecCAnFA}.
+
+Aside from the proofs of Full Abstraction for stateful and nondeterministic languages that we have mentioned \cite{SamsonGuyIAActive,mcCHFiniteND}, other important Full Abstraction results in Game Semantics that follow this pattern include Danos and Harmer's result for a probabilistic variant of Idealized Algol \cite{DanosHarmer}, the Full Abstraction result for general references of Abramsky, Honda and McCusker \cite{HondaMcCusker}, Laird's result for local exceptions \cite{LLi}, Murawski and Tzevelekos's Nominal Game Semantics \cite{NGS} and the result for countable nondeterminism by Laird and the present author \cite{CslPaper}.
+
+It is also worth mentioning several papers that prove Full Abstraction directly, rather than through a factorization result, usually because they depart more radically from traditional game semantics.
+Such papers include Tsukada and Ong's sheaf-based models for nondeterministic PCF \cite{TsukadaSheaves,Sheaves}, Laird's categorical semantics for coroutines \cite{FunctionalProgramsAsCoroutines} and the results for probabilistic PCF by Castellan, Clairambault, Paquet and Winskel using concurrent games \cite{PPCF}.
+
+\section{Full Abstraction for Kleisli Categories}
+
+One thing which these Full Abstraction results have in common is that they rely on some degree of human intuition to build the original model.  
+This process can often be very difficult.  
+For instance, it seems obvious that if we want to model a nondeterminstic programming language, then we need to relax the determinism constraint on strategies.  
+However, this turns out not to be enough on its own: recall that we model a nonterminating computation in game semantics by a strategy that has no $P$-reply to a particular $O$-move.  
+How then do we model a term which chooses between terminating at a value $v$ and not terminating, and how do we distinguish it from a term which always terminates at $v$?  
+In both cases, player $P$ has the reply $v$ to player $O$'s initial move, but now there is nothing to indicate the possibility of non-termination.
+
+Harmer and McCusker are able to solve this problem, in the finite nondeterminism case, by separately keeping track of divergences in the strategy, but further problems arise when we start to consider countable nondeterminism.
+Since Game Semantics usually keeps track of finite sequences of moves, nondeterministic strategies are unable to distinguish between a program that nondeterministically chooses a number $n$ and prints ``Hello, world'' $n$ times, and a program that either does the same thing, or prints out the message infinitely many times.
+So now we have to add extra information in about infinite sequences of moves (see Levy's work on infinite trace equivalence \cite{LevyGsInfinite} and the work of Laird and the present author on nondeterministic Idealized Algol \cite{CslPaper}).
+
+Things get even more difficult when we consider nondeterministic versions of stateless languages such as PCF.  
+Naively relaxing the determinism constraint on the usual definition of an innocent strategy does not give the right notion of a nondeterministic innocent strategy \cite{TsukadaSheaves}.  
+There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, and to Tsukada and Ong \cite{TsukadaSheaves} that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper on deterministic innocence.
+Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we add nondeterminism to innocence.
+
+Meanwhile, there is plenty of well-known theory that deals with computational effects in a purely systematic way.  
+We have already met two such techniques in section \ref{SecCatSem}: monads (and Kleisli categories) and Lawvere theories.
+Put simply, the purpose of this thesis is to investigate what happens when we try to use these systematic techniques to prove Full Abstraction results for effectful languages.
+
+Let us start by looking at Kleisli categories for monads.  
+Recall that a monad $M$ on a category $\C$ is a functor $M \from \C \to \C$ that satisfies certain conditions, and that the Kleisli category $\Kl_M\C$ of $M$ has the objects of $\C$ as its objects, and that a morphism $a \to b$ in $\Kl_M\C$ is given by a morphism $a \to Mb$ in $\C$.
+There is a natural identity-on-objects functor $J\from \C \to \Kl_M\C$.
+
+In particular, if $a$ is any object of $\C$, then we have a distinguished Kleisli morphism $\phi_A\from Ma \to a$ in $\Kl_M\C$ given by the identity morphism $Ma \to Ma$ in $\C$.
+Now let $f\from a \to b$ be an arbitrary morphism in $\Kl_M\C$, given by a morphism $\hat f\from a \to Mb$ in $\C$.
+Then we can write $f$ as the following composite in $\Kl_M\C$.
+\[
+  a \xrightarrow{J\hat{f}} Mb \xrightarrow{\phi_b} b
+  \]
+In other words, the Kleisli category $\Kl_M\C$ automatically satisfies a factorization result of the type we have been talking about.  
+So if $\C$ is a model of a language $\L$ that satisfies compact definability, then $\Kl_M\C$ will automatically satisfy compact definability for any denotational semantics for a language language $\L'$ that includes (via the functor $J$) the existing denotational semantics for $\L$ and in which the morphisms $\phi_a$ are all definable.
+
+Proving computational adequacy is not so automatic.  
+One approach is to treat $\Kl_M\C$ like any other model and to apply the usual arguments for proving adequacy.  
+Most computational adequacy arguments rely on order-enriched properties of the underlying categories, particularly for dealing with recursion, and the Kleisli category $\Kl_M\C$ automatically inherits order-enriched structure from $\C$, by saying that $f\le g\from a \to b$ in $\Kl_M\C$ if $f\le g$ when considered as morphisms $a \to Mb$ in $\C$.
+
+An alternative approach, which we shall use in this thesis, is to try and deduce computational adequacy for $\Kl_M\C$ from a computational adequacy result for the original language $\L$ in $\C$.  
+In this approach, we take a term $N$ of the extended language $\L'$ and note that its denotation $\deno{N} \from a \to b$ in $\Kl_M\C$ is given by some morphism $f \from a \to Mb$ in $\C$.  
+Typically, it is easy to construct a term $P$ of $\L$ whose denotation in $\C$ is $f$.
+We then prove results to peg the operational behaviour of $N$ in $\L'$ to that of $P$ in $\L$, allowing us to deduce a computational adequacy result for our model of $\L'$ from the corresponding result for $\L$.
+
+The last ingredient that we need is to prove that $\Kl_M\C$ is a Cartesian closed category.  
+This is not immediate either: $\Kl_M\C$ need not be Cartesian, even if $\C$ is.  
+For the purposes of this thesis, we will be considering only monads of a very special form -- the \emph{reader monads} $R_z$ on Cartesian closed categories, given by $R_za = z \to a$.
+The Kleisli category for a reader monad on a Cartesian closed category is always Cartesian closed \cite{FunctionalCompleteness}.
+
+\section{Plan for this Thesis}
+
+This thesis will develop the theory of Full Abstraction from the point of view of techniques of categorical algebra such as Kleisli categories.
+
+\begin{description}
+  \item[Chapters \ref{ChapGames} and \ref{ChapFullAbstraction}] give a fairly traditional presentation of a Fully Abstract game semantics model for Idealized Algol.  
+    All subsequent results will be for extended versions of Idealized Algol, so this model can serve as the foundation for the rest of our work.  
+    Although these chapters form by some distance the longest part of the thesis, they also contain the smallest amount of new material, and owe much to Abramsky and McCusker's Fully Abstract game semantics for Idealized Algol \cite{SamsonGuyIAActive}.
+    The main difference, which ties in with the general theme of the thesis, is that we prove Computational Adequacy using techniques of categorical algebra rather than via the ad hoc combinatorial arguments found in \cite{SamsonGuyIAActive}.
+    Specifically, we use Laird's concept of a \emph{sequoidal category} and of the exponential as a final coalgebra, used to prove Full Abstraction for a language with general references \cite{laird02}.
+    We present the first application of this technique to a language with purely local state of ground type.
+    The remainder of the Full Abstraction result is largely as in \cite{SamsonGuyIAActive}.
+  \item[Chapter \ref{ChapMonads}] presents the general theory of monads and Kleisli categories.  
+    It then presents a technique which can be used to prove Full Abstraction for several nondeterministic effects, along the lines we outlined in the previous section.
+\end{description}
+For the remainder of the thesis, we deal with a generalization of monads -- \emph{parametric monads}, in which the action of the monad is parameterized by an object of some monoidal category $\X$ (so that we deal with a functor $\X \times \C \to \C$ rather than a functor $\C \to \C$).
+\begin{description}
+  \item[Chapter \ref{ChapParametricMonads}] introduces and defines parametric monads (also known as \emph{lax actions}), and proves a number of technical results which we need.
+    It also introduces the \emph{\Mellies category} and the oplax $2$-limit $\C/\X$, which give us two related analogues of the Kleisli category in the parametric case.
+    The \Mellies category is an enriched category, while $\C/\X$ is an ordinary category obtained from it by change of base.
+    As with monads, we need to specialize to a small class of parametric monads -- the \emph{reader actions} -- in order to ensure that $\C/\X$ is a Cartesian closed category.
+  \item[Chapter \ref{ChapReaderActions}] uncovers a large source of these reader actions, proving that reader actions on the category $\Set$ of sets are equivalent to lax monoidal functors $\Set \to \Set$.
+  \item[Chapter \ref{ChapPromonads}] takes a small detour away from the main narrative to study the \Mellies category from the point of view of profunctors.
+  \item[Chapter \ref{ChapParametricMonadsFullAbstraction}] completes our study of parametric monads by proving a Full Abstraction result for a probabilistic language for a category derived from a particular parametric monad, using similar techniques to Chapter \ref{ChapMonads}.
+\end{description}
+Lastly, our conclusion in {\bf Chapter \ref{ChapFurtherDirections}} provides a glimpse into several further directions that are left unexplored by the rest of the thesis.
+
 \bibliographystyle{alpha2}

### 2019-07-28 Thesis/pmonads.tex
Monthly commit.
Added some more pages to the introduction.

@@
 In this chapter, we will show that $\C/\X$ has important properties in its own right: namely that it is a certain lax $2$-colimit in $\Cat$.  
-We will briefly return to the \Mellies category in chapter \ref{SecPromonads}, when we will show why it is a natural idea to consider an $[\X,\Set]$-enriched category.
+We will briefly return to the \Mellies category in chapter \ref{ChapPromonads}, when we will show why it is a natural idea to consider an $[\X,\Set]$-enriched category.
 
@@
 \chapter{Reader actions on $\Set$}
+\label{ChapReaderActions}
 
@@
   Consider $F$ as a pseudofunctor $\Set \to \Cat$, and let $\X=\oppcat{\left(\int F\right)}$ be the opposite of its Grothendieck construction.  
-  Since $\Set$ is an ordinary category, so is $\X$.
+  Since $\Set$ is an ordinary category (as opposed to a proper bicategory), so is $\X$.
 

### 2019-08-04 Thesis/complete_thesis.tex
Put everything into one document, added title page, did spell check etc.

\documentclass[11pt]{report}

\def\FEWFONTS{1}
\def\THESIS{1}
\input{../common/preamble}
\usepackage{lua-visual-debug}

\begin{document}
\begin{titlepage}
  \begin{center}
    \Huge
    \textbf{The Crossroads of Categorical Algebra and Game Semantics}

    \vspace{0.2cm}
    \LARGE
    An investigation into the application of Kleisli categories and related constructions to the study of Full Abstraction for nondeterministic effects in Algol-like languages

    \vspace{0.3cm}

    \textbf{William John Gowers}

    A thesis submitted for the degree of\\
    Doctor of Philosophy

    \vspace{0.1cm}

    \Large
    Department of Computer Science\\
    University of Bath\\
    United Kingdom\\
    August 2019

    \textbf{COPYRIGHT}
    Attention is drawn to the fact that copyright of this thesis rests with the author. A copy of this thesis has
    been supplied on condition that anyone who consults it is understood to recognise that its copyright rests
    with the author and that they must not copy it or use material from it except as permitted by law or with
    the consent of the author.

    This thesis may be made available for consultation within
    the University Library and may be photocopied or lent to other libraries
    for the purposes of consultation. \ul{\hspace{64pt}}

  \end{center}
\end{titlepage}

\let\OldClearpage\clearpage
\let\clearpage\relax

\tableofcontents
\listoffigures

\let\clearpage\OldClearpage
\newpage

\input{intro}
\input{games}
\input{thesis}
\input{pmonads}
\input{promonads}
\input{pmonads2}
\input{conc}

\Urlmuskip=0mu plus 9mu\relax
\bibliographystyle{alpha2}
\bibliography{../common/phd_bibliography}

\end{document}

### 2019-08-04 Thesis/conc.tex
Added some more pages to the introduction.
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass[11pt]{report}
-
-\let\FEWFONTS=1
-\input{../common/preamble}
-
-\begin{document}
-
 \chapter{Further Directions}
+\label{ChapFurtherDirections}
 
@@
 
-For example, fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the langauge PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  
+For example, fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the language PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  
 I.e., it is the language with types given by the following inductive grammar.
@@
   \end{mathpar}
-  \caption{Big-step operational semantics for Nondeterministic PCF with may testing}
+  \caption{Big-step operational semantics for Nondeterministic PCF and may testing}
   \label{FigNDPCFOpSem}
@@
 Tsukada and Ong have also demonstrated that it is instructive to consider strategies as presheaves over plays, where we assign to each individual play a set of possible branches that lead us to that play.
-In this formalism, the innocent nondeterministic strategies are preciesly those presheaves that are sheaves with respect to a certain natural Grothendieck topology.
+In this formalism, the innocent nondeterministic strategies are precisely those presheaves that are sheaves with respect to a certain natural Grothendieck topology.
 
@@
 An important example is our model of countable nondeterminism with must testing.  
-It is well known (see, e.g., \cite{Apt,PlotkinApt}) that countable nondeterminism is inextricably linked to dicontinuity of composition, which robs us of an important ingredient in the standard order-theoretic proof of adequacy.
+It is well known (see, e.g., \cite{Apt,PlotkinApt}) that countable nondeterminism is inextricably linked to discontinuity of composition, which robs us of an important ingredient in the standard order-theoretic proof of adequacy.
 
@@
 We have then applied the second part of Levy's technique -- \emph{hiding} -- to remove the explicit information and yield a pure, computationally adequate model of countable nondeterminism.
-
-\bibliographystyle{alpha2}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-04 Thesis/games.tex
Daily commit.
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass[11pt]{report}
-
-\def\FEWFONTS{1}
-\def\THESIS{1}
-\input{../common/preamble}
-\usepackage{lua-visual-debug}
-
-\begin{document}
-
 \chapter{A Sequoidal Game Semantics for Idealized Algol}
@@
 We now present the typing rules for the language.  
-Here, $\Gamma$ will represent a \emph{context}; i.e., a list $x_1\from T_1,\cdots,x_n\from T_n$ of variable names together with their types.
+Here, $\Gamma$ will stand for a \emph{context}; i.e., a list $x_1\from T_1,\cdots,x_n\from T_n$ of variable names together with their types.
 
@@
 
-  If $i$ is a subset incusion of $A$ into $B$, then we get an innocent strategy $\subs_i\from B \implies A$ defined by
+  If $i$ is a subset inclusion of $A$ into $B$, then we get an innocent strategy $\subs_i\from B \implies A$ defined by
   \[
@@
   Let $f$ be a structural isomorphism from a game $A$ to a game $B$.  
-  Then $\cc_f$ is an isomorphim in $\G$ from $A$ to $B$.
+  Then $\cc_f$ is an isomorphism in $\G$ from $A$ to $B$.
 \end{proposition}
@@
   Suppose that $t\prefix s$ is of even length.  
-  Then, since only player $O$ swtiches between the $A',A$-component and the $B',B$-component, both $t\vert_{A',A}$ and $t\vert_{B',B}$ are of even length, it follows that $t\vert_{A',B'}=[i,j]_*(t\vert_{A,B})$.
+  Then, since only player $O$ switches between the $A',A$-component and the $B',B$-component, both $t\vert_{A',A}$ and $t\vert_{B',B}$ are of even length, it follows that $t\vert_{A',B'}=[i,j]_*(t\vert_{A,B})$.
   Since $t$ was arbitrary, this means that $s\in \subs_{[i,j]}$.
@@
   Indeed, we have
-  \begin{IEEEeqnarray*}{rCl?u}
+  \begin{IEEEeqnarray*}{rCl/u}
     \langle\sigma_i\rangle;\pr_j & = & \langle\sigma_i\rangle;\subs_{\inj_j} \\
-    & = & \{[\id_{M_B},\inj_j\inv]_*(s)\suchthat s\in\langle\sigma_i\rangle,\,s\vert_{\prod_iAi}\in(\inj_j)_*(P_{A_j})\} & \textit{Prop. \ref{PropCopycat}} \\
+    & = & \{[\id_{M_B},\inj_j\inv]_*(s)\suchthat s\in\langle\sigma_i\rangle,\,s\vert_{\prod_iAi}\in(\inj_j)_*(P_{A_j})\} & \textit{Prop.~\ref{PropCopycat}} \\
     & = & \sigma_j\,.
@@
 \begin{remark}
-  The definitions of \emph{lax action} can be found at the start of Chapter \ref{ChapParametricMonads}, whie that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
-  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphims.
+  The definitions of \emph{lax action} can be found at the start of Chapter \ref{ChapParametricMonads}, while that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
+  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphisms.
   A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
@@
   Suppose that $\tau$ is some other strategy for $C\implies \oc A$ such that $\tau;\zz_{\phi_n}=\sigma_n$ for each $n$.  
-  Cy Proposition \ref{PropTree}, we have
+  By Proposition \ref{PropTree}, we have
   \[
@@
 
-  A \emph{coalgebra homomophism} from $(a,f)$ to $(b,g)$ is a morphism $h\from a \to b$ such that the following diagram commutes.
+  A \emph{coalgebra homomorphism} from $(a,f)$ to $(b,g)$ is a morphism $h\from a \to b$ such that the following diagram commutes.
   \[
@@
     \]
-  If this sequence has a limit $F^{\omega}1$, and if the morphism $\beta\from F(F^{\omega}1) \to F^{\omega}1$ induced from the univeral property of the limit is an isomorphism, then $(F^{\omega}1,\beta\inv)$ is a final coalgebra for $F$.
+  If this sequence has a limit $F^{\omega}1$, and if the morphism $\beta\from F(F^{\omega}1) \to F^{\omega}1$ induced from the universal property of the limit is an isomorphism, then $(F^{\omega}1,\beta\inv)$ is a final coalgebra for $F$.
 \end{theorem}
@@
       \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mathmakebox[-1pt]{}\mu_{{\deno{\Gamma}}}\mathmakebox[-1pt]{}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{S'}\tensor A' \xrightarrow{\mathmakebox[-1pt]{}\wk_{\deno{S'},A'}} \deno{S'} \sequoid A' \xrightarrow{\mathmakebox[-1pt]{}\tau'\mathmakebox[-1pt]{}} (\oc\deno{S}\implies\deno{T}),
+        \oc{\deno{\Gamma}} \xrightarrow{\mathmakebox[-1pt]{}\mu_{{\deno{\Gamma}}}\mathmakebox[-1pt]{}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{S'}\tensor A' \xrightarrow{\mathmakebox[-1.2pt]{}\wk_{\deno{S'},A'}} \deno{S'} \sequoid A' \xrightarrow{\mathmakebox[-1.2pt]{}\tau'\mathmakebox[-1.4pt]{}} (\oc\deno{S}\implies\deno{T}),
         \]
@@
 \begin{lemma}
-  The relation $\oopto$ betwen triples $\Gamma,s\ts M$ preserves the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.
+  The relation $\oopto$ between triples $\Gamma,s\ts M$ preserves the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.
 
@@
       \end{mathpar}
-      (where $\cong$ represents the natural isomorpism between the games $\deno T\sequoid(\oc\Varr\tensor\oc\deno{\Gamma})$ and $\deno T \sequoid\oc{\deno{x,\Gamma}}$),
+      (where $\cong$ represents the natural isomorphism between the games $\deno T\sequoid(\oc\Varr\tensor\oc\deno{\Gamma})$ and $\deno T \sequoid\oc{\deno{x,\Gamma}}$),
       and so is completely determined by the value of the composite
@@
 \begin{definition}
-  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies for $\oc\deno{\Gamma} \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
+  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies $\sigma\from\oc\deno{\Gamma} \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
   \begin{itemize}
@@
   Let $T$ be an idealized Algol type, and let $\Gamma\ts M\from T$ be a typing judgement, where $\Gamma$ is a $\Var$-context.
-  Suppose that $\sigma_1\subset\sigma_2\subset\cdots$ is a nested sequence of strategies for $\oc\deno{\Gamma}$ such that $\sigma_i\plot_T^\Gamma M$ for all $i$.  
+  Suppose that $\sigma_1\subset\sigma_2\subset\cdots$ is a nested sequence of strategies for $\oc\deno{\Gamma}\implies \deno{T}$ such that $\sigma_i\plot_T^\Gamma M$ for all $i$.  
   Let $\sigma=\bigcup_i \sigma_i$.  
@@
   By induction on $T$, this extends to higher types by continuity of composition.
+  For example, suppose that we have $\Gamma\ts M \from S \to T$, and that the $\sigma_i$ are strategies $\oc\deno{\Gamma} \implies (\oc\deno S \implies \deno T)$ such that $\sigma_i \plot_{S\to T}^\Gamma M$ for all $i$.
+  We claim that $\bigcup_i\sigma_i \plot_{S \to T}^\Gamma M$.
+
+  Indeed, suppose that $\tau\from \oc \deno \Gamma \implies \deno S$ is a strategy and $N \from S$ a term such that $\tau\plot_S^\Gamma N$.  
+  Then, by hypothesis, we have
+  \[
+    \left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma_i\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N
+    \]
+  for each $i$, and so, by the inductive hypothesis applied to $T$, we know that we have
+  \[
+    \bigcup_i\left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma_i\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,.
+    \]
+  But continuity of composition tells us that this composite is equal to
+  \[
+    \left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\bigcup_i\sigma_i\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
+    \]
+  and so the result follows.
 \end{proof}
@@
 \begin{proof}
-  This is obvious for the dataypes and for $\Var$.  
+  This is obvious for the datatypes and for $\Var$.  
   Let $S,T$ be types -- so $\deno{S \to T} = \oc\deno S \implies \deno T$ -- and let $s\in P_{\oc\deno S\implies \deno T}$.  
@@
   Let $A,B$ be well-opened games.
-  Given a strategy $\sigma\from \oc A \implies \oc B$, $\sigma$ is single-threaded if and only if it is a comonoid homomorphism with respect to the natural comonoid structures on $\oc A$ and $\oc B$; i.e., it makes the following diagrams commute.
+  Given a strategy
+  \[
+    \sigma\from \oc A \implies \oc B\,,
+    \]
+  $\sigma$ is single-threaded if and only if it is a comonoid homomorphism with respect to the natural comonoid structures on $\oc A$ and $\oc B$; i.e., it makes the following diagrams commute.
   \begin{mathpar}
@@
   Indeed, suppose that $s\in\sigma$.  
-  ket $n$ be an occurrence of an initial move in $s$.  
+  Let $n$ be an occurrence of an initial move in $s$.  
   Then, by Lemma \ref{LemRuss1}, $s\vert_n\in\sigma$ and has a unique initial move, and is therefore contained in $\tau$.  
@@
 \section{The Intrinsic Equivalence Relation}
+\label{SecIntrinsicEquivalence}
 
@@
 \end{proof}
-
-\bibliographystyle{alpha2}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-04 Thesis/intro.tex
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass[11pt]{report}
-
-\input{../common/preamble}
-
-\begin{document}
-
 \chapter{Introduction}
@@
 \end{lstlisting}
-then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: since \lstinline[language=haskell]{f} always evaluates its argument \lstinline[language=haskell]{n}, \lstinline[language=haskell]{f (diverge 0)} will fail to terminate, whereas \lstinline[language=haskell]{g (diverge 0)} will give us \lstinline[language=haskell]{0}, since inputs to functions are evaluated lazily in Haskell.
+then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: indeed, since \lstinline[language=haskell]{f} always evaluates its argument \lstinline[language=haskell]{n}, \lstinline[language=haskell]{f (diverge 0)} will fail to terminate, whereas \lstinline[language=haskell]{g (diverge 0)} will give us \lstinline[language=haskell]{0}, since inputs to functions are evaluated lazily in Haskell.
 
-We can have another go at answering our original question, then, by adding the requirement that the two programs should behave in the same way if they are passed non-terminating inputs.
-Thus, we add to each datatype an extra distinguished value $\bot$ representing non-termination (so, for example, the type of integers is represented by the set $\bZ_\bot = \bZ + \{\bot\}$), and then function types are interpreted as functions between these sets -- so a term of type \lstinline[language=haskell]{Int -> Int} is reprepresented by a function $\bZ_\bot \to \bZ_\bot$.
+We can have another go at answering our original question, then, by adding the requirement that the two programs should behave in the same way when they are passed non-terminating inputs.
+Thus, we add to each datatype an extra distinguished value $\bot$ representing non-termination (so, for example, the type of integers is represented by the set $\bZ_\bot = \bZ + \{\bot\}$), and then function types are interpreted as functions between these sets -- so a term of type \lstinline[language=haskell]{Int -> Int} is represented by a function $\bZ_\bot \to \bZ_\bot$.
 
 We need to be careful, though, since not every such function arises from a program in this way.
-For example, we cannot write a program corresponding to the function $\chi\from\bZ_\bot \to \bZ_\bot$ that sends $\bot$ to $0$ and all other values to $1$since $\chi$ is not constant, such a program would have to evaluate its argument, and would consequently fail to terminate if that argument did not terminate.
+For example, we cannot write a program corresponding to the function $\chi\from\bZ_\bot \to \bZ_\bot$ that sends $\bot$ to $0$ and all other values to $1$: since $\chi$ is not constant, such a program would have to evaluate its argument, and would consequently fail to terminate if that argument did not terminate.
 
@@
 We then require that functions should be monotonic and continuous with respect to this order. 
-For example, a monotonic function $\bZ_\bot \to \bZ_\bot$ is either constant (correponding to a function that does not evaluate its argument at all) or sends $\bot$ to $\bot$ and is otherwise unconstrained (corresponding to a function that evaluates its argument).
+For example, a monotonic function $\bZ_\bot \to \bZ_\bot$ is either constant (corresponding to a function that does not evaluate its argument at all) or sends $\bot$ to $\bot$ and is otherwise unconstrained (corresponding to a function that evaluates its argument).
 It turns out that if we order functions pointwise, then we get the correct constraints at higher types as well.
@@
 
-Then, following Scott \cite{ScottDomains}, we refind this model to one based on partially-ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.
+Then, following Scott \cite{ScottDomains}, we refine this model to one based on partially-ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.
 
@@
 
-\section{Computational Adequacy and Full Abstraction}
+\section{Computational Adequacy \& Full Abstraction}
 \label{SecCAnFA}
@@
 For example, if we are hoping to model a programming language with sets and functions, then we need to define a mapping $\deno{-}$ (the \emph{denotation}) that takes program types to sets and program functions to functions between those sets, and we also need to prove that this denotation respects the operational rules of the language: for example, we might want to prove that if $f \from \Int \to \Int$ is a function and $M \from \Int$ is a term that evaluates to the integer $n$, then the term $f M$ will evaluate to the integer $\deno{f}(n)$.
-This type of result is called \emph{Computational Adequacy}, and relates to programs of a ground or observable type (e.g., a program that returns an integer has ground type, and we can observe that it either returns an integer or fails to teminate, whereas a program that takes in an integer and returns an integer has a function type: it is not possible to `observe' its behaviour without substituting in values).
+This type of result is called \emph{Computational Adequacy}, and relates to programs of a ground or observable type (e.g., a program that returns an integer has ground type, and we can observe that it either returns an integer or fails to terminate, whereas a program that takes in an integer and returns an integer has a function type: it is not possible to `observe' its behaviour without substituting in values).
 
@@
 This astounding result presents us with a world in which we can practically and systematically check observational equivalence (for terms of this extended version of PCF) by computing denotations.  
-This vision is a little rosey-eyed -- deciding observational equivalence is stronger than the halting problem and is hence undecidable in general -- but if the programs in question are finitely presentable in some sense, then we really can use the denotational semantics to check observational equivalence.
+This vision is a little rosy-eyed -- deciding observational equivalence is stronger than the halting problem and is hence undecidable in general -- but if the programs in question are finitely presentable in some sense, then we really can use the denotational semantics to check observational equivalence.
 
@@
 
+Lastly, we note that the conclusion of Loader's theorem does not necessarily hold for other languages.  
+For example, in Section \ref{SecIntrinsicEquivalence}, we shall demonstrate a denotational characterization of observational equivalence in Idealized Algol, due to Abramsky and McCusker \cite{SamsonGuyIAActive}, which can be adapted to give us an algorithm for deciding observational equivalence for a finitary version of Idealized Algol.
+
 \section{Categorical Semantics}
@@
 
-There is a close link between (typed) programming langauges and categories.
+There is a close link between (typed) programming languages and categories.
 Programming languages have things called \emph{types}, and they have \emph{functions} that go from one type to another. 
@@
 The development of programming languages such as Haskell has been strongly influenced by category-theoretic concepts.  
-For example, Moggi's 19xx observation \cite{Moggi} that monads on categories provide us with a way of modelling computational effects influenced work that led directly to the introduction of support for monads in Haskell \cite{Haskell}, where they have become the primary tool for abstracting out effectful computation.
+For example, Moggi's 1991 observation \cite{Moggi} that monads on categories provide us with a way of modelling computational effects influenced work that led directly to the introduction of support for monads in Haskell \cite{Haskell}, where they have become the primary tool for abstracting out effectful computation.
 
@@
   \[
-    \begin{tikzcd}[arrows={no head, dotted, shorten=-1mm}, row sep=0pt]
+    \begin{tikzcd}[arrows={no head, dotted, shorten=-1.5mm}, row sep=-1pt]
       A
@@
 The precise definition of a strategy that we use depends on the language that we are trying to model -- a language with less expressive power can realize fewer strategies.  
-For example, the denotations of terms in a stateless langauge such as PCF are \emph{history-free} or \emph{innocent}, in which the proponent's moves can only depend on a particular subsequence of the current sequence of moves -- the $P$-view -- rather than on the whole sequence.
+For example, the denotations of terms in a stateless language such as PCF are \emph{history-free} or \emph{innocent}, in which the proponent's moves can only depend on a particular subsequence of the current sequence of moves -- the $P$-view -- rather than on the whole sequence.
 So for a lot of computational effects, particularly ones that have something to do with state, adding that effect corresponds to a \emph{relaxing} of conditions on strategies.
@@
 We model other types of effects by extending the definition of a strategy.  
-For example, if we want to provide a semantics for a language with nondeterminism, then we modify the definition of a strategy so that the propoonent can have multiple replies to each opponent move, as in the work of Harmer and McCusker \cite{mcCHFiniteND}.
+For example, if we want to provide a semantics for a language with nondeterminism, then we modify the definition of a strategy so that the proponent can have multiple replies to each opponent move, as in the work of Harmer and McCusker \cite{mcCHFiniteND}.
 If we want to model a probabilistic language, then we decorate these different moves with probabilities, as in the work of Danos and Harmer \cite{DanosHarmer}.
@@
 This process can often be very difficult.  
-For instance, it seems obvious that if we want to model a nondeterminstic programming language, then we need to relax the determinism constraint on strategies.  
+For instance, it seems obvious that if we want to model a nondeterministic programming language, then we need to relax the determinism constraint on strategies.  
 However, this turns out not to be enough on its own: recall that we model a nonterminating computation in game semantics by a strategy that has no $P$-reply to a particular $O$-move.  
@@
 
+\section{Difficulties with Countable Nondeterminism}
+
+This thesis will focus on nondeterministic effects.  
+Of these, perhaps the trickiest to work with is countable nondeterminism, in which a program can nondeterministically choose between a possibly infinite number of different options, without the possibility of non-termination\footnote{If we have a source of finite nondeterminism, then we can get infinite branching if we accept the possibility that our program might never terminate -- for example, count the number of coin tosses it takes before we get the first head.}
+
+There are three main difficulties when dealing with countable nondeterminism in game semantics.  
+The first we have covered in the previous section: we cannot tell everything about a program's behaviour by looking at its possible finite traces, even when the traces are allowed to be arbitrarily long, as in the example where a program nondeterministically chooses a number $n$ and prints out a message $n$ times vs the program which may print out the message infinitely many times.
+
+The fact that finite nondeterminism avoids this behaviour comes down to K\"{o}nig's Lemma, which asserts that any finitely branching tree without an infinite branch has bounded height.
+
+This is related to the second problem, which is the failure of continuity of composition, as noticed by Dijkstra in \cite[Ch.~9]{DijkstraBook} and later studied by Plotkin and Apt in \cite{PlotkinApt}.
+In order to talk about continuity, we define the \emph{observational preorder} on terms of a language.  
+If $M,N\from T$, we write $M\lesssim N$ if for all ground-type contexts $C[-]$ with a hole of type $T$ we have
+\[
+  C[M]\text{ always terminates} \Rightarrow C[N]\text{ always terminates.}
+  \]
+In particular, $M$ and $N$ are observationally equivalent if and only if $M\lesssim N$ and $N \lesssim M$.
+
+Continuity of composition says that least upper bounds with respect to this order are preserved by function application.  
+Consider, for example, the terms $\le_m \from \bN \to \bN$ for $m=0,1,\dots$ that return $0$ if their argument is less than or equal to $m$ and go into an infinite loop otherwise.
+It is fairly clear (with a straightforward rigorous proof once we have introduced the denotational semantics) that a least upper bound for the $\le_m$ is the term $\le_\infty$ that evaluates its argument and then returns $0$ regardless of what value it finds\footnote{$\le_\infty$ differs slightly from $\lambda n.0$ -- also an upper bound for the $\le_m$, but not the least upper bound -- in that it will fail to terminate if its argument fails to terminate}.
+
+But now notice what happens if we have a countable nondeterminism primitive $?$ in our language which when evaluated returns an arbitrarily large natural number.
+Then the terms $\le_m ?$ are all observationally equivalent: they either return $0$ (when $?$ returns a number less than or equal to $m$), or fail to terminate (when $?$ returns a number greater than $m$).
+Therefore, $\le_m?$ is a constant sequence and its least upper bound is that constant value, which we can write as
+\[
+  0+\Omega\,.
+  \]
+Meanwhile, $\le_\infty?$ always returns $0$.  
+So application to $?$ does not preserve least upper bounds.
+
+The reason that this is a problem is that a typical strategy for proving computational adequacy is via an order-enriched category in which the observational preorder at a type matches up with the ordering of morphisms into the denotation of that type.
+The standard adequacy proof uses continuity of composition in the model in an essential way -- see Lemma \ref{LemAdequacyLimits} for an example of such an argument being used to prove computational adequacy for a deterministic language.
+But if the ordering of morphisms in a denotational model of a language with countable nondeterminism faithfully respects the observational ordering of terms, then it will not have the continuity properties that we need for this proof.
+
+Our strategy for getting around this problem goes back to Levy's paper \emph{Infinite Trace Equivalence} \cite{LevyGsInfinite}, and essentially involves going via an auxiliary language, in which the nondeterministic oracle $?$, when it chooses a value, must print that value to a log.
+Given a term $P$ of ground type, we write $P\converges_u$ if $P$ terminates whenever it prints the sequence $u$ to the log.  
+Then, if we modify our definition of observational equivalence to say that $M\lesssim N$ if for all suitable contexts $C[-]$ we have
+\[
+  C[M] \converges_u \mathrel{\Rightarrow C[N]} \converges_u\,,
+  \]
+then this ordering will be continuous.  
+For example, this extra requirement wrecks our previous example of failure of continuity of composition.  
+Indeed, the sequence $\le_m ?$ is no longer constant, since, for example, $\le_5 ?$ does not terminate if it prints $6$ to the log, whereas $\le_{1000} ?$ does.
+The least upper bound of the $\le_m?$ is then the term that terminates whenever it prints a single number to the log; i.e., $\le_\infty ?$.
+
+Having proved computational adequacy for this new language, we then use operational methods to find a way to identify terms that should be observationally equivalent in the original sense.  
+We form a model for the language with countable nondeterminism by taking our model for the new language and taking the quotient by an appropriate equivalence relation on morphisms.
+
+In order to introduce the last problem that we face with countable nondeterminism, we note that there are two different reasons why an element of a denotational model (e.g., a strategy) might not be definable in a particular reason.
+One reason is structural: for example, a stateless language such as PCF cannot define a strategy whose behaviour depends on its entire history, since that would indicate stateful behaviour.  
+The other reason is purely computational.  
+Given a non-computable function $f\from \bN \to \bN$ (for example, the function that returns $0$ if its argument is source code for a terminating program an $1$ otherwise), we have a perfectly well-behaved history free strategy that represents $f$, but it is nevertheless still not definable in most programming languages.
+Historically, the study of Full Abstraction has not been too concerned with non-definable elements of the second kind: the reason is that they are do not usually play a role in determining the intrinsic equivalence relation, since such a strategy is necessarily not compact.
+However, in the presence of countable nondeterminism, there exist terms that can be distinguished in the model that cannot be distinguished by compact elements; indeed, we can use a diagonal argument to define two functions $(\bN \to \bN) \to \bN$ that are distinguished only by non-computable functions $\bN \to \bN$.
+An example of such a function is found in Proposition \ref{PropNotFullyAbstract}; the general idea is due to Kleene and can be found in \cite{KleeneTree}.
+
+What this means is that if we want to model countable nondeterminism then, in addition to the usual structural constraints on strategies relating to the effectful behaviour available in our language, we also need to impose computability constraints that say that our strategies can in some sense be defined using a computable function.
+Happily, such notions are well studied already, even appearing in the original Hyland-Ong and AJM papers \cite{hoPcf,ajmPcf}, in which the authors give a complete characterization of those strategies definable in PCF -- a \emph{universality} result for the model.
+Similar results can also be found in earlier work on Full Abstraction, such as Plotkin's original PCF paper \cite{PlotkinPcf}.
+
+The difficulties with countable nondeterminism that we have outlined are essentially domain-theoretic; indeed, the reason that compact strategies suffice to distinguish morphisms in models of finite nondeterminism is that the sets of morphisms in that case form \emph{algebraic domains}, in which every element is the least upper bound of the set of compact elements below it.
+Algebraicity fails for models of countable nondeterminism.
+
 \section{Plan for this Thesis}
@@
     As with monads, we need to specialize to a small class of parametric monads -- the \emph{reader actions} -- in order to ensure that $\C/\X$ is a Cartesian closed category.
-  \item[Chapter \ref{ChapReaderActions}] uncovers a large source of these reader actions, proving that reader actions on the category $\Set$ of sets are equivalent to lax monoidal functors $\Set \to \Set$.
+  \item[Chapter \ref{ChapReaderActions}] uncovers a large source of these reader actions; in this chapter, we prove that reader actions on the category $\Set$ of sets are equivalent to lax monoidal functors $\Set \to \Set$.
   \item[Chapter \ref{ChapPromonads}] takes a small detour away from the main narrative to study the \Mellies category from the point of view of profunctors.
@@
 Lastly, our conclusion in {\bf Chapter \ref{ChapFurtherDirections}} provides a glimpse into several further directions that are left unexplored by the rest of the thesis.
-
-\bibliographystyle{alpha2}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-04 Thesis/pmonads.tex
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass{report}[11pt]
-
-\input{../common/preamble}
-\usepackage{lua-visual-debug}
-\begin{document}
 \chapter{Parametric monads}
@@
 \begin{definition}[\cite{ThesisForDays}]
-  Let $\X$ be a monoidal category, and let $F,G\from \X \to \Set$ be functors.  
+  Let $\X$ be a monoidal category and let 
+  \[
+    F,G\from \X \to \Set
+    \]
+  be functors.  
   Then the \emph{Day convolution} of $F$ and $G$ is a functor
@@
   \begin{itemize}
-    \item a map $F$ from the objects of $\C$ to the objects of $\D$,
-    \item for each pair $a,b$ of objects of $\C$, a functor $F$ from $\C(a,b)$ to $\D(F(a),F(b))$,
-    \item for each triple $a,b,c$ of objects of $\C$, a transformation $m_{f,g}\from F(f);F(g) \to F(f;g)$ natural in $f\from a \to b$, $g\from b \to c$ and
-    \item for each object $a$ of $\C$, a $2$-cell $e_a\from \id_{Fa} \Rightarrow F(\id_a)\from Fa \to Fa$
+    \item a map $F$ from the objects of $\C$ to the objects of $\D$;
+    \item for each pair $a,b$ of objects of $\C$, a functor
+      \[
+        F \from \C(a,b) \to \D(F(a),F(b))\,;
+        \]
+    \item for each triple $a,b,c$ of objects of $\C$, a transformation 
+      \[
+        m_{f,g}\from F(f);F(g) \to F(f;g)
+        \]
+      natural in $f\from a \to b$, $g\from b \to c$; and
+    \item for each object $a$ of $\C$, a $2$-cell 
+      \[
+        e_a\from \id_{Fa} \Rightarrow F(\id_a)\from Fa \to Fa\,;
+        \]
   \end{itemize}
@@
 \begin{example}
-  An oplax natural transformation between lax functors $\BB\X \to \Cat$ is the same thing as an oplax morphism between the corresponding actions, as defined in Definition \ref{DefOplaxMorphismOfActions}.
+  An oplax natural transformation between two lax functors $\BB\X \to \Cat$ is the same thing as an oplax morphism between the corresponding actions, as defined in Definition \ref{DefOplaxMorphismOfActions}.
 \end{example}
@@
   \[
-    F(h)(m) \xrightarrow{(Fh)f}
-    F(h)(n) \xrightarrow{(e_{a'})_{(Fh)f}}
-    F(\id_{a'})(F(h)(n)) \xrightarrow{m_{\id_{a'},h}}
+    F(h)(m) \xrightarrow{\ms\ms(Fh)f\ms\ms}
+    F(h)(n) \xrightarrow{\ms\ms(e_{a'})_{(Fh)f}\ms\ms}
+    F(\id_{a'})(F(h)(n)) \xrightarrow{\ms\ms m_{\id_{a'},h}\ms\ms}
     F(\id_{a'};F(h))(n)\,,
@@
     \]
-  Using the formula above for the composition of morphisms in the Grothendieck construction, we see that $\hat{l}((h,f);(k;g))$ is given by the thick dotted composite in Figure \ref{FigLHatFunctor}, while $\hat{l}(h,f);\hat{l}(k,g)$ is given by the thin composite.
+  Using the formula for the composition of morphisms in the Grothendieck construction, we see that $\hat{l}((h,f);(k;g))$ is given by the thick dotted composite in Figure \ref{FigLHatFunctor}, while $\hat{l}(h,f);\hat{l}(k,g)$ is given by the thin composite.
   Therefore, these two are equal.
@@
       \]
-    \caption{Proof that $\hat{l}$ respects composition.  
+    \caption[Proof that $\hat{l}$ respects composition.]
+    {Proof that $\hat{l}$ respects composition.  
     The thick dotted line represents $\hat{l}((h,f);(k,g))$, while the thin solid line represents $\hat{l}(h,f);\hat{l}(k,g)$.  
@@
     \begin{mathpar}
-      \begin{tikzcd}[column sep=100pt]
+      \begin{tikzcd}[column sep=94pt]
         (a'\tensor b')\tensor c' \arrow[r, "{\assoc_{a',b',c'}}"] \arrow[d, "(f\tensor g)\tensor h"']
@@
 \end{IEEEeqnarray*}
-
 while $(f';f)\tensor (g';g)$ is given by
@@
 
-Suppose that a symmetric monoidal category $\X$ acts via a symmetric monoidal action on a Cartesian category $\C$.  
+Suppose that a symmetric monoidal category $\X$ acts on a Cartesian category $\C$ via a symmetric monoidal lax action.
 In this chapter we will consider what properties of the action we need in order to ensure that the induced monoidal structure on $\C/\X$ is Cartesian.
@@
     jx \to a \arrow[rr, "jx \to \Delta_a"] \arrow[d, "\Delta_{jx \to a}"']
-      &[-10pt]
+      &[-15pt]
         &[+10pt] jx \to (a \times a) \\
@@
         %
-        \&[-20pt] \left(\colim_{x\from \X}\limits x.a \tensor \colim_{y\from \X}\limits y.b\right) \tensor \colim_{z \from \X}\limits z.c \arrow[r, "\assoc" yshift=5pt] \arrow[d]
-            \&[-20pt] \colim_{x \from \X}\limits x.a \tensor \left(\colim_{y\from \X}\limits y.b \tensor \colim_{z \from \X}\limits z.c \right) \arrow[d]
-              \&[-20pt] \\
+        \&[-37pt] \left(\colim_{x\from \X}\limits x.a \tensor \colim_{y\from \X}\limits y.b\right) \tensor \colim_{z \from \X}\limits z.c \arrow[r, bend left=15, yshift=-1em, "\assoc"] \arrow[d]
+            \&[-26pt] \colim_{x \from \X}\limits x.a \tensor \left(\colim_{y\from \X}\limits y.b \tensor \colim_{z \from \X}\limits z.c \right) \arrow[d]
+              \&[-37pt] \\
         %
@@
         %
-          & |[alias=Z]| \colim_{z\from \X}\limits z.(a \tensor 1)
+          &[-18pt] |[alias=Z]| \colim_{z\from \X}\limits z.(a \tensor 1)
             &[-20pt] \\
-        |[alias=Y]| \colim_{x\from \X}\limits x.a \arrow[r, "\Colim\runit.\runit" yshift=2pt] \arrow[ur, "\Colim \id.\runit", from=Y.north, to=Z.west, bend left=20] \arrow[d, "\Colim\runit" description] \arrow[dd, "\runit"', bend right=60]
+        |[alias=Y]| \colim_{x\from \X}\limits x.a \arrow[r, "\Colim\runit.\runit" yshift=4pt] \arrow[ur, "\Colim \id.\runit", from=Y.north, to=Z.west, bend left=20] \arrow[d, "\Colim\runit" description] \arrow[dd, "\runit"', bend right=60]
           & \colim_{x\from \X}\limits (x \tensor I).(a\tensor 1) \arrow[r, hookrightarrow] \arrow[u, hookrightarrow]
             & |[alias=X]| \colim_{x,y\from \X}\limits (x \tensor y).(a \tensor 1) \arrow[ul, hookrightarrow, from=X.north, to=Z.east, bend right=20] \\
-        \colim_{x\from \X}\limits x.a \tensor 1 \arrow[r, "\Colim \id \tensor e"]
+        \colim_{x\from \X}\limits x.a \tensor 1 \arrow[r, "\Colim \id \tensor e" yshift=2pt]
           & \colim_{x \from \X}\limits x.a \tensor I.1 \arrow[u, "{\Colim m_{x,I,a,1}}" description] \arrow[r, hookrightarrow]
             & \colim_{x,y\from\X}\limits x.a \tensor y.1 \arrow[u, "{\Colim m_{x,y,a,1}}"'] \\
-        \left(\colim_{x \from \X}\limits x.a\right) \tensor 1 \arrow[u, Sim] \arrow[r, "\id \tensor e"]
+        \left(\colim_{x \from \X}\limits x.a\right) \tensor 1 \arrow[u, Sim] \arrow[r, "\id \tensor e" yshift=2pt]
           & \left(\colim_{x \from \X}\limits x.a\right)\tensor I.a \arrow[u, Sim] \arrow[r, hookrightarrow]
@@
 \begin{proposition}[\cite{Pisani}]
-  Let $\X,\YY$ be a monoidal category and let $[\YY,\Set]$ be equipped with the Day convolution product.  
+  Let $\X,\YY$ be a monoidal category and let the functor category $[\YY,\Set]$ be equipped with the Day convolution product.  
   Then a lax monoidal functor $\X \times \YY \to \Set$ is the same thing (via currying) as a lax monoidal functor $\X \to [\YY,\Set]$.
@@
     &\int^{y,z}[jy,[A,B]] \times [jz,[B,C]] \times \X(y\tensor z,x) \\
-    \xrightarrow{\makebox[144pt]{$\int^{y,z} m_{jy,jz,[A,B],[B,C]}\times \X(y\tensor z,x)$}} &
+    \xrightarrow{\makebox[141pt]{$\int^{y,z} m_{jy,jz,[A,B],[B,C]}\times \X(y\tensor z,x)$}} &
     \int^{y,z}[jy \times jz,[A,B]\times [B,C]] \times \X(y,\tensor z,x) \\
-    \xrightarrow{\makebox[144pt]{$\int^{y,z} [m^j_{y,z}, ;] \times \X(y\tensor z,x)$}} &
+    \xrightarrow{\makebox[141pt]{$\int^{y,z} [m^j_{y,z}, ;] \times \X(y\tensor z,x)$}} &
     \int^{y,z}[j(y \tensor z),[A,C]]\times \X(y\tensor z,x) \\
@@
       \]
-      \caption[Proof that \Mellies composition agrees with base-changed composition in the case of a symmetric reader action on $\Set$.]%
+      \caption[\Mellies composition and base-changed composition agree for symmetric reader actions on $\Set$.]%
       {Proof that \Mellies composition agrees with base-changed composition in the case of a symmetric reader action on $\Set$.  
@@
   \end{IEEEeqnarray*}
-  We claim that this defines a cocone under the functor $(X,m) \mapsto [X,A] \from \oppcat\X \to \Set$.  
+  We claim that this defines a cocone under the functor 
+  \[
+    (X,m) \mapsto [X,A] \from \oppcat\X \to \Set\,.
+    \]
   Indeed, if we have a morphism $h \from (Y,n) \to (X,m)$ then by definition we have
@@
 
-  Moreover, $\RV_\Omega$ is a lax monoidal functor: if $V,W$ are discrete random variables taking values in sets $A,B$, then we have a random variable $\langle V,W \rangle\from X \to A\times B$ given by pairing (and if $(a,b)\in A\times B$, then $(\langle V,W\rangle)\inv(\{(a,b)\}) = V\inv(\{a\})\cap W\inv(\{b\})$, so this is a measurable function).
+  Moreover, $\RV_\Omega$ is a lax monoidal functor: if $V,W$ are discrete random variables taking values in sets $A,B$, then we have a random variable 
+  \[
+    \langle V,W \rangle\from X \to A\times B
+    \]
+  given by pairing (and if $(a,b)\in A\times B$, then 
+  \[
+    (\langle V,W\rangle)\inv(\{(a,b)\}) = V\inv(\{a\})\cap W\inv(\{b\})\,,
+    \]
+  so this is a measurable function).
 
@@
 The purpose of the final chapter will be to define a language with an operational semantics for which these primitives make sense, and prove a full abstraction result for it.
-
-\Urlmuskip=0mu plus 9mu\relax
-\bibliographystyle{alpha2}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-04 Thesis/pmonads2.tex
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass{report}[11pt]
-\let\FEWFONTS=1
-
-\input{../common/preamble}
-\usepackage{lua-visual-debug}
-
-\begin{document}
-
 \chapter{Parametric Monads and Full Abstraction}
@@
 
-\newcommand{\IAX}{{IA${}_{X}$}\xspace}
 \newcommand{\IAXX}{{IA${}_{\X}$}\xspace}
@@
 Let $\G$ be a model of Idealized Algol as described above, and suppose that there is an oplax monoidal functor $\Set \to \G$ that is used to interpret datatypes.  
-We will use an underline to indicate thies functor; so, for example, the object of $\G$ that is used to denote the natural number type is written $\ul\bN$.
-
-By our description of $\G/\oppcat \X$ as a lax colimit in $\Cat$ (i.e., Corollary \ref{CorTheConstructionUniversalProperty}), we have a natual functor $J\from \G\to\G/\oppcat \X$ and a natural transformation $\phi_{p,a}\from J(jp\to a) \to Ja$.
+We will use an underline to indicate this functor; so, for example, the object of $\G$ that is used to denote the natural number type is written $\ul\bN$.
+
+By our description of $\G/\oppcat \X$ as a lax colimit in $\Cat$ (i.e., Corollary \ref{CorTheConstructionUniversalProperty}), we have a natural functor $J\from \G\to\G/\oppcat \X$ and a natural transformation $\phi_{p,a}\from J(jp\to a) \to Ja$.
 Our denotational semantics of \IAXX is then given in the category $\G/\oppcat X$ as follows.  
@@
 
-Recall that, in the definition of the category $\G/\oppcat\X$, the \Mellies morphisms are left unchanged by precomposing with a morphism in the image of the functor $j$; therefore, if $M\from T$ is a closed term of \IAXX referring to $\choose_{p_1},\cdots,\choose_{p_n}$, then we may write the denotation of $M$ as the composite
+Recall that, in the definition of the category $\G/\oppcat\X$, the \Mellies morphisms are left unchanged by precomposing with a morphism in the image of the functor $j$; therefore, if $M\from T$ is a closed term of \IAXX referring to $\choose_{p_1}$, $\cdots$, $\choose_{p_n}$, then we may write the denotation of $M$ as the composite
 \[
@@
   is a valid inference of \IAXX.
-  \label{LemThirdSubstitution}
+  \label{LemFourthSubstitution}
 \end{lemma}
@@
   Suppose that $M$ is not one of the $y_i$; then $M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)/y_i]$ is not equal to $\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)$.
-  Moreover, every instance of $\ask_{j(N)}$ in $M$ occurs as part of an expression of the form $\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)$, and so we win by Lemma \ref{LemThirdSubstitution} and the inductive hypothesis.
+  Moreover, every instance of $\ask_{j(N)}$ in $M$ occurs as part of an expression of the form $\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v)$, and so we win by Lemma \ref{LemFourthSubstitution} and the inductive hypothesis.
 
@@
   \]
-Our Computational Adequacy result for IAX (Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy}) then gives us a Computational adequacy result for this model.
+Our Computational Adequacy result for \IAX (Propositions \ref{PropKleisliSoundness} and \ref{PropKleisliAdequacy}) then gives us a Computational adequacy result for this model.
 
@@
 This model is much easier to realize.  
-What do we gain, then, from our more complicated model?
+What do we gain, then, from our more complicated original model?
 
@@
 This is not such a great advantage as it might seem, since if $p\in[0,1]$ is any real number whose binary expansion is computable as a function $\bN \to \bB$, then we can simulate $\choose_p$ within the probabilistic version of IA${}_\bB$\footnote{Idea: build up a sequence of intervals $I_n$ of width $2^n$ by repeatedly flipping the coin and using the result to choose either the lower or the upper half of $I_{n-1}$.
-If at any point the upper bound of $I_n$ is less than or equal to $p$ (which can be checked by computing the first $n$ terms of the binary expansion of $p$, then return $\true$.  
+If at any point the upper bound of $I_n$ is less than or equal to $p$ (which can be checked by computing the first $n$ terms of the binary expansion of $p$), then return $\true$.  
 If at any point the lower bound of $I_n$ is greater than or equal to $p$, return $\false$.}.
@@
 \begin{proposition}
-  Let $\sigma\from A \to B$, $\tau\from B \to C$ be morphisms in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
+  Let $\sigma\from A \to B$, $\tau\from B \to C$ be morphisms in the category $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
   Let $s$ be a legal play in $A \to C$.
@@
   Then the composition $\sigma;\tau$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ is given by $V\tensor W\from\Omega \to X\times Y$, together with the \Mellies composition
-  \[
+  \begin{mathpar}
     A \xrightarrow{\tilde\sigma}
@@
     (\ul{X\times Y} \to C)\,,
-    \]
+  \end{mathpar}
   where $\mu$ is $\langle\ul{\pr_X},\ul{\pr_Y}\rangle$.
@@
 
-  By the definition of $\mu$, we know that if the $i$-th pair of moves in $\t\vert_{\ul X,\ul Y}$ is $qx$ for $x\in X$, then the $i$-th pair of moves in $t\vert_{\ul{X\times Y}}$ is $q(x,y_0)$ for some $y_0$, and if the $i$-th pair of moves in $\t\vert_{\ul X,\ul Y}$ is $qy$ for $y\in Y$, then the $i$-th pair of mvoes in $t\vert_{\ul{X\times Y}}$ is $q(x_0,y)$ for some $x_0\in X$.
+  By the definition of $\mu$, we know that if the $i$-th pair of moves in $\t\vert_{\ul X,\ul Y}$ is $qx$ for $x\in X$, then the $i$-th pair of moves in $t\vert_{\ul{X\times Y}}$ is $q(x,y_0)$ for some $y_0$, and if the $i$-th pair of moves in $\t\vert_{\ul X,\ul Y}$ is $qy$ for $y\in Y$, then the $i$-th pair of moves in $t\vert_{\ul{X\times Y}}$ is $q(x_0,y)$ for some $x_0\in X$.
   Moreover, if $t'$ is some other sequence such that $t'/s$ and such that $t'$ differs only from $t$ in the choice of the `irrelevant' moves $x_0,y_0$, then there is some $S'\in\sigma\|(\ul X \to \tau)\|(\Lambda\inv;\mu)$ such that $S\vert_{A,\ul{X\times Y}\to C}=t'$ and $S\vert_{A,\ul X \to (\ul Y \to C)}=\t$.
@@
   \]
-These quantites $\sigma(s)$ take the role of our $\bP(s\in\sigma)$, but now they are part of the \emph{definition} of the strategy $\sigma$, rather than being a calculated quantity.
+These quantities $\sigma(s)$ take the role of our $\bP(s\in\sigma)$, but now they are part of the \emph{definition} of the strategy $\sigma$, rather than being a calculated quantity.
 
@@
 Our proof above then gives an alternative proof of Full Abstraction for Danos and Harmer's probabilistic game semantics.
-
-\bibliographystyle{alpha2}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-04 Thesis/promonads.tex
Added some more pages to the introduction.
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass{report}[11pt]
-
-\input{../common/preamble}
-
-\begin{document}
-
 \chapter{Promonads and parametric promonads}
-\label{SecPromonads}
+\label{ChapPromonads}
 
@@
     \]
-  Moreover, for each object $a$ of $\M$, there is a distinguished morphism $\id_a \from a \to a$ called the \emph{identity} on $a$.
+  Moreover, for each object $a$ of $\M$, there is a distinguished multimorphism $\id_a \from a \to a$ called the \emph{identity} on $a$.
 
@@
   The multimorphisms are given by
-  \[
-    (\M\times\N)_n((a_1,b_1),\cdots,(a_n,b_n);(c,d)) = \M_n(a_1,\cdots,a_n;c)\times\N_n(b_1,\cdots,b_n;d),.
-    \]
+  \begin{mathpar}
+    (\M\times\N)_n((a_1,b_1),\cdots,(a_n,b_n);(c,d)) = \M_n(a_1,\cdots,a_n;c)\times\N_n(b_1,\cdots,b_n;d)\,.
+  \end{mathpar}
   Composition and the identity are easily defined pointwise.
@@
 
-\section{Multifunctors and multinatural transformations}
+\section{Multifunctors \& multinatural transformations}
 
@@
 \begin{definition}
-  Given multicategories $\M,\N$ and multifunctors $F,G\from \M \to \N$, a \emph{multinatural transformation} $\phi$ is given by morphisms $\phi_a \from F a \to G a$ for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
+  Given multicategories $\M,\N$ and multifunctors 
+  \[
+    F,G\from \M \to \N\,,
+    \]
+  a \emph{multinatural transformation} $\phi\from F \Rightarrow G$ is given by morphisms $\phi_a \from F a \to G a$ for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
   \[
@@
   \[
-    \begin{tikzcd}[column sep=48pt]
+    \begin{tikzcd}[column sep=46pt]
       F_1(a_1),\cdots,F_n(a_1),\cdots,F_1(a_m),\cdots,F_n(a_m) \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_m}}"] \arrow[d, "\sigma_*"']
@@
     \begin{mathpar}
-      \begin{tikzcd}[ampersand replacement=\&, column sep=116pt]
+      \begin{tikzcd}[ampersand replacement=\&, column sep=68pt]
         \C_1(a_1,b_1),\C_1(b_1,c_1),\cdots,\C_n(a_n,b_n),\C_n(b_n,c_n) \arrow[r, "{;_{a_1,b_1,c_1},\cdots,;_{a_n,b_n,c_n}}"] \arrow[d, "\sigma_*"']
@@
           \& \\
-        \D(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n)),\D(F(b_1,\cdots,b_n),F(c_1,\cdots,c_n)) \arrow[r, "{;_{F(a_1,\cdots,a_n),F(b_1,\cdots,b_n),F(c_1,\cdots,c_n)}}" yshift=0.3em]
+        \D(F(a_1,\cdots,a_n),F(b_1,\cdots,b_n)),\D(F(b_1,\cdots,b_n),F(c_1,\cdots,c_n)) \arrow[r, "{;_{F(a_1,\cdots,a_n),F(b_1,\cdots,b_n),F(c_1,\cdots,c_n)}}" yshift=0.5em]
           \& \D(F(a_1,\cdots,a_n),F(c_1,\cdots,c_n))
@@
     \end{mathpar}
-    \caption{The rules for preservation of composition and identity by multimorphisms of $\V$-enriched functors are similar to those for ordinary enriched functors.  
+    \caption[Definition of multimorphisms between categories enriched in multicategories.]
+    {The rules for preservation of composition and identity by multimorphisms of $\V$-enriched functors are similar to those for ordinary enriched functors.  
     Note that it is essential for the $\V$ to be a symmetric multicategory.  
@@
   \begin{mathpar}
-    \begin{tikzcd}[column sep=21pt]
-      {\C(a,a'),F_1(a',b_1),\cdots,F_n(b_{n-1},c),\C(c,c')} \arrow[r, "{\id,\phi_{a',\vec{b},c},\id}", xshift=-2ex, shorten=-1.8ex] \arrow[d, "{p,\id,\cdots,\id,p}"']
+    \begin{tikzcd}[column sep=8pt]
+      {\C(a,a'),F_1(a',b_1),\cdots,F_n(b_{n-1},c),\C(c,c')} \arrow[r, "{\id,\phi_{a',\vec{b},c},\id}", xshift=-2ex, yshift=1pt, shorten=-1.8ex] \arrow[d, "{p,\id,\cdots,\id,p}"']
 
@@
     \and
-    \begin{tikzcd}[column sep=-120pt]
+    \begin{tikzcd}[column sep=-134pt]
       & F_1(a,b_1),\C(b_1,b_1'),F_2(b_1',b_2),\cdots,F_{n-1}(b_{n-2}',b_{n-1}),\C(b_{n-1},b_{n-1}'),F_n(b_{n-1}',c)
@@
   \end{mathpar}
-  \caption{The coherences we require on the multimorphisms between endoprofunctors are essentially the axioms for an extranatural transformation as in \cite{ExtranaturalTransformations}.}
+  \caption[Extranatural transformations between endoprofunctors.]
+  {Extranatural transformations between endoprofunctors.
+  The coherences we require on the multimorphisms between endoprofunctors are essentially the axioms for an extranatural transformation as in \cite{ExtranaturalTransformations}.}
   \label{FigExtranatural}
@@
   \[
-    \begin{tikzcd}[ampersand replacement=\&, row sep=80pt, column sep=30pt]
+    \begin{tikzcd}[ampersand replacement=\&, row sep=80pt, column sep=23pt]
       %
@@
             \& \\
-      F_1,\C_1,F_2,\cdots,F_{n-1},\C,F_n \arrow[uur, "{\id,p,\cdots,p}"] \arrow[ddr, "{p,\cdots,p,\id}"'] \arrow[ur, "{\id,p,\cdots,p,\id_{\C},\cdots,\id_{\C},\id,\cdots,p}"' {description, xshift=6ex}] \arrow[dr, "{p,\cdots,p,\id,\id_{\C},\cdots,\id_{\C},p,\cdots,p,\id}" {description, xshift=6ex}]
+      F_1,\C_1,F_2,\cdots,F_{n-1},\C,F_n \arrow[uur, "{\id,p,\cdots,p}", bend left=5] \arrow[ddr, "{p,\cdots,p,\id}"', bend right=5] \arrow[ur, "{\id,p,\cdots,p,\id_{\C},\cdots,\id_{\C},\id,\cdots,p}"' {description, xshift=6ex}] \arrow[dr, "{p,\cdots,p,\id,\id_{\C},\cdots,\id_{\C},p,\cdots,p,\id}" {description, xshift=6ex}]
         \&
@@
     \]
-  \caption{Proof that extranaturality is preserved by composition.  
+  \caption[Proof that extranaturality is preserved by composition.]
+  {Proof that extranaturality is preserved by composition.  
   Commutativity of the central square is by extranaturality of the $\phi^{(i)}$, while that of the four-cornered triangle at the right is by extranaturality of $\psi$.  
@@
       \]
-    \caption{Proof that the identity-on-objects functor arising from a promonad is indeed a functor.  
+    \caption[Promonads are identity-on-objects functors.]
+    {Proof that the identity-on-objects functor arising from a promonad is indeed a functor.  
     The proof uses naturality of $e_{a,b}$ for commutativity of the large triangle at the top right.}
@@
   i.e., a natural transformation
-  \[
+  \begin{mathpar}
     \left(\prod_i \X(I,x_i)\times\C(a_i,b_i)\right) \times F(a_1,\cdots,a_n)(y) \to F(b_1,\cdots,b_n)(x_1\tensor\cdots\tensor x_n\tensor y)\,.
-    \]
+  \end{mathpar}
   By the Yoneda lemma, such a natural transformation is the same thing as a natural transformation
@@
 Now consider the case that we have a parametric monad $\blank.\blank\from\X \times \C \to \C$ on a category $\C$.  
-By considering functors as profunctors, we may identify this with a multifunctor $\X \to \Endoprof_\Set(\C)$; i.e., a monoid in $[\X,\Endoprof_\Set(\C)]$.
+By considering functors as profunctors, we may identify this with a multifunctor $\X \to \Endoprof_\Set(\C)$, which is the same thing as a monoid in $[\X,\Endoprof_\Set(\C)]$.
 Then, by Theorem \ref{StokessTheorem}, we may identify this multifunctor with a monoid in $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$; i.e., an $[\X,\Set]$-enriched promonad on ${\omega_\X}_*\C$.
 
-But now, by Proposition \ref{PropPromonadsAreCategories}, this promonad is the same thing as an $[\X,\Set]$-enriched category with the same objects as $\C$ that admits an identity-on-objects $[\X,\Set]$-enriched functor out of ${\omega_X}_*(\C)$.
+But now, by Proposition \ref{PropPromonadsAreCategories}, this promonad is the same thing as an $[\X,\Set]$-enriched category that has the same objects as $\C$ and admits an identity-on-objects $[\X,\Set]$-enriched functor out of ${\omega_X}_*(\C)$.
 
@@
 \end{slogan}
-
-\bibliographystyle{alpha}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-04 Thesis/thesis.tex
Monthly commit.
Put everything into one document, added title page, did spell check etc.

@@
-\documentclass[11pt]{report}
-
-\let\FEWFONTS=1
-\let\THESIS=1
-\input{../common/preamble}
-
-\usepackage{lua-visual-debug}
-
-\begin{document}
-
-\tableofcontents
-\newpage
-
 \chapter{Monads and Kleisli categories}
@@
 
-Given a monad $M$ on a category $\C$ and a functor $F\from \C \to \D$, where $\D$ is another category, we say that a natural transormation $\psi_a \from FMa \to Fa$ is \emph{$M$-multiplicative} if it makes the following diagrams commute.
+Given a monad $M$ on a category $\C$ and a functor $F\from \C \to \D$, where $\D$ is another category, we say that a natural transformation $\psi_a \from FMa \to Fa$ is \emph{$M$-multiplicative} if it makes the following diagrams commute.
 \begin{mathpar}
@@
 
-Another way to characterize the Kleisli category $\Kl_M$ is to say that the the adjunction we described above is initial among all adjunctions giving rise to the monad $M$.  
+Another way to characterize the Kleisli category $\Kl_M$ is to say that the adjunction we described above is initial among all adjunctions giving rise to the monad $M$.  
 This can be deduced from Proposition \ref{pKleisli} using the following result.
@@
     \normalsize
+    \caption{Some useful IA derivations}
   \end{SidewaysFigure}
@@
   in Idealized Algol.
-  \label{LemSoundness}
+  \label{LemSoundnessMonads}
 \end{lemma}
@@
 
-In light of Lemma \ref{LemSoundness}, we can state our soundness result.
+In light of Lemma \ref{LemSoundnessMonads}, we can state our soundness result.
 
@@
       {
-        \inferrule*[left={Lem. \ref{LemSoundness}}]
+        \inferrule*[left={Lem. \ref{LemSoundnessMonads}}]
         {
@@
 Now we want to prove Computational Adequacy; i.e., the converse to Proposition \ref{PropKleisliSoundness}.
-To do this, we need to prove a converse to Lemma \ref{LemSoundness}.
+To do this, we need to prove a converse to Lemma \ref{LemSoundnessMonads}.
 
@@
   in \IAX, where $u$ is the subsequence of $w$ consisting of all terms from $k+1$ up to $l$.
-  \label{LemAdequacy}
+  \label{LemAdequacyMonads}
 \end{lemma}
@@
   Now $u$ is the subsequence of $u^\top$ going from position $1$ to position $|u|$.  
-  So Lemma \ref{LemAdequacy} tells us that we must have
+  So Lemma \ref{LemAdequacyMonads} tells us that we must have
   \[
@@
 \section{Alternative Reduction Rules - May Testing}
+\label{SecMayTesting}
 
@@
 
-\begin{corollary}
+\begin{corollary}[Computational Adequacy for May Testing]
   Let $M\from\com$ be a closed term of \IAX.  
@@
 
-As an application of this fully abstract semantics, we clear up a loose end from the proof of Propostion \ref{PropNotFullyAbstract}.
+As an application of this fully abstract semantics, we clear up a loose end from the proof of Proposition \ref{PropNotFullyAbstract}.
 
 \begin{lemma}
-  The terms $M,N\from (\nat \to \nat) \to \com$, as defined in the proof of Propostion \ref{PropNotFullyAbstract}, are observationally equivalent in Idealized Algol with countable nondeterminism.
+  The terms $M,N\from (\nat \to \nat) \to \com$, as defined in the proof of Proposition \ref{PropNotFullyAbstract}, are observationally equivalent in Idealized Algol with countable nondeterminism.
 \end{lemma}
@@
 This proves that the finite and countable nondeterministic variants of Idealized Algol are conservative extensions of Idealized Algol.
-\bibliographystyle{alpha}
-\bibliography{../common/phd_bibliography}
-
-\end{document}

### 2019-08-23 Thesis/intro.tex
Made some corrections

@@
 For example, if we are hoping to model a programming language with sets and functions, then we need to define a mapping $\deno{-}$ (the \emph{denotation}) that takes program types to sets and program functions to functions between those sets, and we also need to prove that this denotation respects the operational rules of the language: for example, we might want to prove that if $f \from \Int \to \Int$ is a function and $M \from \Int$ is a term that evaluates to the integer $n$, then the term $f M$ will evaluate to the integer $\deno{f}(n)$.
-This type of result is called \emph{Computational Adequacy}, and relates to programs of a ground or observable type (e.g., a program that returns an integer has ground type, and we can observe that it either returns an integer or fails to terminate, whereas a program that takes in an integer and returns an integer has a function type: it is not possible to `observe' its behaviour without substituting in values).
+This type of result is called \emph{Computational Adequacy}, and relates to a program's \emph{observable behaviour}.  
+Some programs have an automatic notion of observable behaviour: if we run them, then they will return a concrete value or fail to terminate.  
+In a typed setting, these are the programs of ground type.
+Others -- for example, programs of function type -- require input before they can return a value.  
+These programs have no observable behaviour of their own, but if we insert them into a hole in a larger context, then they may influence the observable behaviour of the complete program.
 
-Briefly speaking, a Computational Adequacy result tells us that the behaviour of a program of ground type may be deduced exactly from its denotation.
+Briefly speaking, a Computational Adequacy result tells us that the observable behaviour of a program of ground type may be deduced exactly from its denotation.
 For example, in a domain-theoretic semantics, we might want to say that a program $M$ evaluates to a value $v$ if and only if $\deno M=v$ and that $M$ fails to terminate if and only if $\deno M = \bot$.
@@
 If we have an effective way of computing denotations, then this can give us an easy way to prove observational equivalence of terms.  
-However, there is no guarantee that we are able to use such a trick: the terms $M$ and $N$ might be observationally equivalent despite having distinct denotations.  
+However, there is no guarantee that we are able to prove observational equivalence this way: the terms $M$ and $N$ might be observationally equivalent despite having distinct denotations.  
 The gold standard of denotational semantics -- \emph{Full Abstraction} -- asserts in addition that the converse of equational soundness holds, so that the denotational semantics completely captures the observational equivalence relation.
+This means that if two terms are observationally equivalent, then we can always prove that they are by showing that they have the same denotation.
 
@@
 
-Unfortunately, this stop working for PCF itself.  
+Unfortunately, this stops working for PCF itself.  
 PCF is a sub-language of the parallelized version, but this also means that the observational equivalence relation is coarser: there may be terms that can be distinguished by a context including the parallel construct that cannot be distinguished inside any purely sequential context.
@@
 Nevertheless there were, roughly contemporaneous with Loader's result, several fully abstract models of PCF published, in a watershed moment for the subject.
-The models published by Nickau \cite{NickauPcf} and O'Hearn and Riecke \cite{OHearnRieckePcf} were more or less along domain-theoretic lines, while those of Abramsky, Jagadeesan and Malacaria \cite{ajmPcf} and Hyland and Ong \cite{hoPcf} used the relatively new Game Semantics.
+The model published by O'Hearn and Riecke \cite{OHearnRieckePcf} was more or less along domain-theoretic lines, while those of Abramsky, Jagadeesan and Malacaria \cite{ajmPcf}, Hyland and Ong \cite{hoPcf}, and Nickau \cite{NickauPcf} used the relatively new Game Semantics.
 
@@
 Thus, proving this direction normally reduces to some kind of \emph{definability} result.  
-Typically, we only need to prove definability for a restricted class of elements $\alpha$ of the denotational model -- the \emph{compact} elements.
+Typically, we do not actually need to prove that every $\alpha$ is definable within the language -- and, indeed, this is often not the case.  
+Instead, we try to show that each element $\alpha$ in the language can be written as the least upper bound of elements $\alpha'$ living in some more restricted class whose members can all be defined in the language.
+This class usually consists of those elements which are \emph{compact} or finitary in some sense, though McCusker's Fully Abstract relational semantics for SCI \cite{GuySci} is an important exception.
+Under mild continuity assumptions, this suffices to prove Full Abstraction, for we can then deduce that if $\alpha(\sigma)\ne \alpha(\tau)$ for some $\alpha$, then there is some definable $\alpha'$ such that $\alpha'(\sigma)\ne\alpha'(\tau)$.
 
@@
 There is a close link between (typed) programming languages and categories.
-Programming languages have things called \emph{types}, and they have \emph{functions} that go from one type to another. 
+Most programming languages have things called \emph{types}, and many have \emph{functions} that go from one type to another. 
 Typically, it will be possible to compose two functions together in the language in an associative way, giving us a category.
@@
 For example, the language Idealized Algol is an extended version of PCF that adds some stateful primitives.
-For example, Abramsky and McCusker's proof of compact definability for Idealized Algol in \cite{SamsonGuyIAActive} first proves that each compact strategy in their model may be written as the composite of a compact innocent strategy with the (non-innocent) denotation of one of the new stateful constants.
+Abramsky and McCusker's proof of compact definability for Idealized Algol in \cite{SamsonGuyIAActive} first proves that each compact strategy in their model may be written as the composite of a compact innocent strategy with the (non-innocent) denotation of one of the new stateful constants.
 Thus, they can deduce compact definability for Idealized Algol from Hyland and Ong's result that every compact innocent strategy is the denotation of a term of PCF.
@@
   \item Prove that the model $\C'$ is a Cartesian closed category and is computationally adequate for $\L'$.
-  \item Prove a factorization result that exhibits every morphism $g$ in $\C'$ as the composition of some morphism $Jf$ in the image of $J$ with one of some fixed collection of morphisms that are known to be definable in $\L'$ (for example, single terms from $\L'\setminus\L$.
+  \item Prove a factorization result that exhibits every morphism $g$ in $\C'$ as the composition of some morphism $Jf$ in the image of $J$ with one of some fixed collection of morphisms that are known to be definable in $\L'$ (for example, single terms from $\L'\setminus\L$).
     In addition, if $g$ is compact, then $f$ should be compact in $\C$.
@@
 Naively relaxing the determinism constraint on the usual definition of an innocent strategy does not give the right notion of a nondeterministic innocent strategy \cite{TsukadaSheaves}.  
-There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, and to Tsukada and Ong \cite{TsukadaSheaves} that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper on deterministic innocence.
+There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, toTsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper on deterministic innocence.
 Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we add nondeterminism to innocence.
@@
 
-In order to introduce the last problem that we face with countable nondeterminism, we note that there are two different reasons why an element of a denotational model (e.g., a strategy) might not be definable in a particular reason.
+In order to introduce the last problem that we face with countable nondeterminism, we note that there are two different reasons why an element of a denotational model (e.g., a strategy) might not be definable in a particular language.
 One reason is structural: for example, a stateless language such as PCF cannot define a strategy whose behaviour depends on its entire history, since that would indicate stateful behaviour.  
@@
 Given a non-computable function $f\from \bN \to \bN$ (for example, the function that returns $0$ if its argument is source code for a terminating program an $1$ otherwise), we have a perfectly well-behaved history free strategy that represents $f$, but it is nevertheless still not definable in most programming languages.
-Historically, the study of Full Abstraction has not been too concerned with non-definable elements of the second kind: the reason is that they are do not usually play a role in determining the intrinsic equivalence relation, since such a strategy is necessarily not compact.
+Historically, the study of Full Abstraction has not been too concerned with non-definable elements of the second kind: the reason is that they do not usually play a role in determining the intrinsic equivalence relation, since such a strategy is necessarily not compact.
 However, in the presence of countable nondeterminism, there exist terms that can be distinguished in the model that cannot be distinguished by compact elements; indeed, we can use a diagonal argument to define two functions $(\bN \to \bN) \to \bN$ that are distinguished only by non-computable functions $\bN \to \bN$.
@@
 
-The difficulties with countable nondeterminism that we have outlined are essentially domain-theoretic; indeed, the reason that compact strategies suffice to distinguish morphisms in models of finite nondeterminism is that the sets of morphisms in that case form \emph{algebraic domains}, in which every element is the least upper bound of the set of compact elements below it.
-Algebraicity fails for models of countable nondeterminism.
+The difficulties with countable nondeterminism that we have outlined are essentially domain-theoretic, and can be summed up by saying that composition of countably nondeterministic functions is not continuous -- i.e., does not preserve least upper bounds -- with respect to the natural orderings on terms.
 

### 2019-08-23 Thesis/thesis.tex
Made some corrections

@@
 \begin{proposition}
-  Let $\C$ be a category that admits a computationally adequate denotational semantics of IA${}_\bN$.  
+  Let $\C$ be a category and suppose we have a computationally adequate denotational semantics of IA with countable nondeterminism in $\C$.
   Suppose that the natural number datatype is denoted by an object $\bN$ of $\C$ and that for all functions $f \from \bN \to \bN$ in $\Set$ there is a morphism
@@
     \]
-  Then $\C$ is not fully abstract for Idealized Algol with countable nondeterminism.
+  Then the denotational semantics in $\C$ is not fully abstract.
   \label{PropNotFullyAbstract}
@@
 
-  Indeed, let $\phi\from \bN \to \bN$ where $\phi(p)$ is $n+1$ if $p$ is the encoding of a term $P\from\nat \to \nat$ and $P\;p\converges n$ and $0$ otherwise (including the case that $P\;p\diverges$.
+  Indeed, let $\phi\from \bN \to \bN$ where $\phi(p)$ is $n+1$ if $p$ is the encoding of a term $P\from\nat \to \nat$ and $P\;p\converges n$ and $0$ otherwise (including the case that $P\;p\diverges$).
 

### 2019-09-17 Thesis/conc.tex
Made some corrections
Random commit.

@@
 \label{ChapFurtherDirections}
+
+We conclude by examining a few avenues that we are left unexplored in this thesis.
 
@@
 
-In this thesis, the base language we have used has been the stateful language Idealized Algol.  
-One area to explore is whether the techniques we have developed allow us to build models of effectful versions of stateless languages such as PCF.
+So far, the base language we have used has been the stateful language Idealized Algol.  
+One further question to ask is whether the techniques we have developed allow us to build models of effectful versions of stateless languages such as PCF.
 
 One immediate problem we face is that the addition of nondeterministic effects to PCF allows us to distinguish terms that cannot be distinguished within PCF itself.  
-Consider, for instance, the PCF term
+For instance, the PCF term
 \[
@@
 is observationally equivalent (in PCF) to $\Omega$ -- informally, because the term $x$ must have the same `value' both time it is called, so if it is false the first time, then it must be false the second time.
-However, the same term inside PCF with finite nondeterminism is not observationally equivalent to $\Omega$: if we substitute nondeterministic choice in for $x$, then it could be false the first time and true the second, causing the term to converge to $\true$.
+However, the same term inside PCF with finite nondeterminism is not observationally equivalent to $\Omega$: if we substitute a nondeterministic oracle in for $x$, then the nondeterministic oracle could return false the first time and true the second, causing the term to converge to $\true$.
+Note that this problem does not arise in Idealized Algol: nondeterminism does not allow us to distinguish terms that were indistinguishable in the deterministic language, as we proved in Section \ref{SecIntrinsicEquivalenceRelationKleisli}.
 
-This means that if $\G$ is a `truly fully abstract' model of PCF -- i.e., one in which observational equivalence of terms corresponds to equality of morphisms rather than intrinsic equivalence\footnote{As an example, take any model that is full abstract in our sense, and take the quotient by the intrinsic equivalence relation.} -- then there can be no natural inclusion functor from $\G$ into a model of PCF with finite nondeterminism.
+This means that if $\G$ is a `truly Fully Abstract' model of PCF -- i.e., one in which observational equivalence of terms corresponds to equality of morphisms rather than intrinsic equivalence\footnote{As an example, take any model that is full abstract in our sense, and take the quotient by the intrinsic equivalence relation.} -- then there can be no natural inclusion functor from $\G$ into a model of PCF with finite nondeterminism.
 Indeed, in such a model $\deno{M}$ and $\deno{\Omega}$ are the same morphism, so they would have to be sent to the same morphism in the model of nondeterministic PCF.
 
-This is a problem for us, since both our techniques -- the Kleisli category and the $\G/\X$ construction -- have a natural functor coming out of the original category $\G$.
+This is a problem for us, since it means that our model of PCF cannot be the Kleisli category for a monad on $\G$ (or a category of the form $\G/\X$), since then we \emph{do} have a functor coming out of $\G$.
 
-All is not lost, however, since we can still try and impose some condition on the original model $\G$ of PCF to say that it is still fine-grained enough to distinguish between certain morphisms that are denotations of observationally equivalent PCF terms.
-One convenient way to do this is to ask that $\G$ should embed into some model $\G^{IA}$ of Idealized Algol.  
-An obvious case when this holds is when $\G$ is the (unquotiented) Hyland-Ong category of arenas and innocent strategies, and $\G^{IA}$ is the category of arenas and single-threaded strategies.
+A way to get around this program is to insist that our category $\G$ is not `truly Fully Abstract', but is still fine-grained enough to distinguish between terms that will eventually be distinguished when we add in the nondeterminism.
+A convenient requirement to make is that $\G$ should be embeddable into some model $\G^{IA}$ of Idealized Algol (as is the case for Hyland and Ong's game semantics).  
+The idea is that since $\G^{IA}$ must necessarily distinguish between observationally inequivalent terms of nondeterministic PCF, then $\G$ must distinguish between them too.
 
-For example, fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the language PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  
-I.e., it is the language with types given by the following inductive grammar.
+The other advantage of going via an Idealized Algol model is that we can automatically apply many of the results that we have already obtained.
+
+Let us try this out with an example.  
+Fix $X\in\{\bB,\bN\}$ and let \emph{Nondeterministic PCF} be the language PCF, together with a constant $\ask_X \from \bool$ that plays the role of a nondeterministic oracle.  
+It is the language with types given by
 \[
-  T \Coloneqq \bool \mid \nat \mid T \to T
+  T \Coloneqq \bool \mid \nat \mid T \to T\,,
   \]
-And with a type theory as shown in Figure \ref{FigNDPcfTypeTheory}.
+and with a type theory as shown in Figure \ref{FigNDPcfTypeTheory}.
 \begin{figure}
@@
     \]
-  However, this does not work if $M$ may exhibit nondeterministic behaviour, since it may evaluate to two different values the two times it is called.
+  However, this does not work if $M$ may exhibit nondeterministic behaviour, since $M$ may evaluate to two different values the two times it is called.
   We will stick with the variant shown above for the sake of simplicity, but nothing changes in our proofs if we choose the other version.}
@@
 We then define a relation $M \converges c$ (read `$M$ \emph{may converge to} $c$'), for $M$ a term of Nondeterministic PCF and $c$ a canonical form, inductively as in Figure \ref{FigNDPCFOpSem}.
+This rule is the restriction of the $\converges$ rule from Nondeterministic Idealized Algol to the set of those terms that are terms of Nondeterministic PCF.
 \begin{figure}
@@
 
-It is a quick check to see that every term of Nondeterministic PCF may be regarded as a term of IA${}_X$, giving us a denotational semantics of the language within $\Kl_{R_X}\G$, where $\G$ is the category of arenas and single-threaded strategies.
+It is a quick check to see that every term of Nondeterministic PCF may be regarded as a term of IA${}_X$, giving us a denotational semantics of the Nondeterministic PCF within $\Kl_{R_X}\G$, where $\G$ is the category of arenas and single-threaded strategies.
 But we can be more precise than this: we know from \cite{hoPcf} that the denotation of any term of ordinary PCF is an innocent strategy, so that the denotational semantics of PCF within $\G$ factors through the inclusion $\G_{inn}\hookrightarrow\G$, where $\G_{inn}$ is the category of arenas and innocent strategies.
 In particular, the denotation within $\Kl_{R_X}\G$ of any term of ordinary PCF lives within $\Kl_{R_X}\G_{inn}$.
-Moreover, the denotation of the new term $\ask_X$, being given by the identity morphism in $\G$, also lives in $\Kl_{R_X}\G_{inn}$, meaning that the whole of Nondeterministic PCF is interpreted within this category.
+Moreover, the denotation of the new term $\ask_X$, being given by the identity morphism in $\G$, also lives in the category
+\[
+  \G_{inn,X} \coloneqq \Kl_{R_X}\G_{inn}\,,
+  \]
+giving us a denotational semantics of Nondeterministic PCF within $\G_{inn,X}$.
 
@@
 
-The passage to full abstraction, via innocent definability for PCF is essentially the same as for Idealized Algol (though if $X=\bN$, then we need to cut down to a category of \emph{recursive} strategies).
+The passage to full abstraction, via innocent definability for PCF is essentially the same as for Idealized Algol (though, as before, if $X=\bN$, then we need to cut down to a category of \emph{recursive} strategies).
 
@@
 This is the definition considered -- and ultimately rejected for being too indirect -- by Harmer in his thesis \cite[\sec 3.7]{RusssThesis}.  
-This definition is correct, but, perhaps surprisingly, does not coincide with the same definition that we would get by naively applying the usual definition of innocence to nondeterministic strategies.
+This definition is correct, but, perhaps surprisingly, does not coincide with what we would get by naively applying the usual definition of innocence to nondeterministic strategies.
 
@@
 
-In the Kleisli category, the innocence of this strategy becomes clear: plays are either of the form
+In the Kleisli category model, the innocence of this strategy becomes clear: plays are either of the form
 \[
@@
 
-There is a surprising and elegant definition of nondeterministic innocence (see Levy \cite{levy2014morphisms}, with the correction given by Tsukada and Ong in \cite[Proposition 46]{TsukadaSheaves}), which we shall not detail here.
+Moving away from our Kleisli-category model, there is a surprising and elegant definition of nondeterministic innocence within the usual category of games (see Levy \cite{levy2014morphisms}, with the correction given by Tsukada and Ong in \cite[Proposition 46]{TsukadaSheaves}), which we shall not detail here.
 Tsukada and Ong have also demonstrated that it is instructive to consider strategies as presheaves over plays, where we assign to each individual play a set of possible branches that lead us to that play.
@@
 
-What, then, can our Kleisli category model do for us?
-One answer is that it provides a general setting in which we can prove results such as adequacy without worrying about the specific details of a nondeterministic construction.  
+Even given this theory, however, our Kleisli category model is still worthwhile, since it provides a general setting in which we can prove results such as adequacy without worrying about the specific details of a nondeterministic construction.
 For example, we can prove a computational adequacy result for Tsukada and Ong's model $\G_{TO}$ from Corollary \ref{CorMayAdequacyPcfComb} by noting that the denotational semantics in that category factors through the natural functor $\Kl_{R_\bB}\G \to \G_{TO}$.
-Of course, Tsukada and Ong have provided their own proof of Computational Adequacy in the finite nondeterminism case, but this method could be useful if, for example, we wanted to extend their model to deal with countable nondeterminism.
+Tsukada and Ong have provided their own proof of Computational Adequacy in the finite nondeterminism case, but this method could be useful if, for example, we wanted to extend their model to deal with countable nondeterminism.
 
@@
 In Chapters \ref{ChapGames} and \ref{ChapFullAbstraction}, we presented a categorical algebra of scoped state via sequoidal categories.  
-A natural question to ask is whether we could use the techniques we have developed in the remainder of this thesis in the stateful case.  
-Indeed, the state monad
+The category theory that we used in those chapters is fairly non-standard, and a natural question to ask is whether we can come up with a treatment of state from the point of view of monads or lax actions.
+
+Indeed, there is a well known \emph{state monad}
 \[
-  A \mapsto (W \to (A \times W))
+  A \mapsto (W \to (A \times W))\,,
   \]
-can be constructed in categories of games.  
+which can be constructed in categories of games.  
 More ambitiously, we might hope to capture a parametric notion of local state, via the action
@@
 One issue, which we have touched on already, is that the state monad is not a monoidal functor, which was the condition we needed in order to ensure that its Kleisli category inherited a monoidal structure.
-Indeed, there is not obvious natural morphism
+Indeed, there is no obvious natural morphism
 \[
-  (W \to (A \times W)) \times (W \to (B \times W)) \to (W \to ((A \times B) \times W)\,.
+  (W \to (A \times W)) \times (W \to (B \times W)) \to (W \to ((A \times B) \times W))\,.
   \]
@@
   \]
-in other words, we will have combined the two inputs $R$ and $R'$ and the two outputs $W$ and $W'$, without any way of specifying that the output state $W$ from $f$ should be used as the input state $R'$ from $g$.
+in other words, we will have combined the two inputs $R$ and $R'$ and the two outputs $W$ and $W'$.
 
-The difficulty is that we might want $W$ and $R'$ to represent different variables, in which case this is the right thing to do, but we might want them to represent the same storage cell, in which case, the output from $W$ should be fed into $R'$.
-It's not clear how to deal with this in a category-theoretic way.
+This works well up to a point, but the main point of state is that we want to be able to write to a variable once and then read from it later.  
+So we'd need some way of wiring up the output on the right to the input on the left, and it's not clear how to deal with this in a category-theoretic way.
 
@@
 There is also a \emph{local state monad}, due to Plotkin and Power \cite{PlotkinPower} and based on a construction by Levy \cite{PaulsThesis}, which is defined on the category $[\Inj,\Set]$ of functors from $\Inj$, the category of natural numbers and injections, into the category of sets.
-It is given by the following formula, where $V$ denotes a fixes set of values.
+It is given by the following formula, where $V$ denotes a fixed set of values.
 \[
@@
 The archetypal Cartesian closed category is the category $\Set$ of sets and functions.  
-Most of the work in this thesis has been to do with reader actions (including reader monads as a special case), and we have already provided a classification of the reader actions on $\Set$ -- up to the equivalence relation that identifies actions of monoidal categories $\X$ and $\YY$ if the resulting categories $\Set/\oppcat\X$ and $\Set/\oppcat\YY$ are isomorphic -- in Propositions \ref{PropColimitOfActionIsMonoidalFunctor} and \ref{PropMonoidalFunctorIsColimitOfReaderAction}: namely, they are classified by lax monoidal functors $F\from\Set \to \Set$, in such a way that if a reader action given by an oplax monoidal functor $j\from\X \to \Set$ corresponds to the functor $F \from \Set \to \Set$, then $\Set/\oppcat\X$ is isomorphic to the category $F_*\Set$ formed from $\Set$ by base change along $F$.
+Most of the work in this thesis has been to do with reader actions (including reader monads as a special case), and we have already provided a classification of the reader actions on $\Set$ in Propositions \ref{PropColimitOfActionIsMonoidalFunctor} and \ref{PropMonoidalFunctorIsColimitOfReaderAction}: namely, they are classified by lax monoidal functors $F\from\Set \to \Set$, in such a way that if a reader action given by an oplax monoidal functor $j\from\X \to \Set$ corresponds to the functor $F \from \Set \to \Set$, then $\Set/\oppcat\X$ is isomorphic to the category $F_*\Set$ formed from $\Set$ by base change along $F$.
 Thus, the theory in the case of $\Set$ reduces to the theory of $\Set$-enriched base change.

### 2019-09-17 Thesis/games.tex
Random commit.

@@
 The first three are data types corresponding to the sets $\bC = \{a\}$, $\bB = \{\true,\false\}$ and $\bN = \{0,1,2,\cdots\}$.
-$\com$ takes the role of a command or void type; typically, although the return value of a function $T \to \com$ will not convey any information, the function will have side effects that \emph{do} make a difference.
-
-The type $\Var$ is the type of a variable that holds elements of $\bN$.
+$\com$ takes the role of a command or void type; typically, although the return value of a function $T \to \com$ does not convey any information, the function will have side effects that \emph{do} make a difference.
+
+The type $\Var$ is the type of a variable holding elements of $\bN$.
 It is best understood as corresponding to the following pseudo-Java `interface'.
@@
 
+In other words, a given a term $M$ of type $\Var$, we can either insert a natural number into $M$ or we can request a natural number from $M$.  
+An example is when $M$ acts like a storage cell, returning the last number that was inserted into it, but $M$ could act in a different way.
+
 The types of Idealized Algol are then defined by the following inductive grammar.
@@
 
-We now present the typing rules for the language.  
+Next, we present the typing rules for the language.  
 Here, $\Gamma$ will stand for a \emph{context}; i.e., a list $x_1\from T_1,\cdots,x_n\from T_n$ of variable names together with their types.
@@
 \end{mathpar}
-Here, $\skipp$ is a generic command with no side-effects that returns the unique element of the singleton set $\bC$.  
+Here, $\skipp$ is a generic command with no side-effects that returns the unique element $a$ of the singleton set $\bC$.  
 $M;N$ represents the sequential composition of $M$ with $N$; i.e., the term that first evaluates $M$, performing any of its side-effects, and then evaluates $N$ and returns the result.
@@
 
-At type $\Var$, we have terms that call the read and write `methods' to dereference the variable or to assign a new value to it.
+At type $\Var$, we have terms that call the read and write `methods' to assign a new value to the variable or to get its current value.
 \begin{mathpar}
@@
 
-We also have the ability to create a new variable.
+We have two ways to create tems of type $\Var$.  
+The first gives us the storage-cell behaviour.
 \begin{mathpar}
@@
 
-We have another way of creating variables, using the $\mkvar$ keyword.  
-If we think back to our illustration of the $\Var$ type as an interface, this becomes clearer.  
+The second way of creating terms of type $\Var$ is using the $\mkvar$ keyword.  
+$\mkvar$ can be used to create `bad variables': arbitrary pairs of read and write methods that do not necessarily actually behave like actual storage cells.
+If we think back to our earlier illustration of the $\Var$ type as an interface, this becomes clearer.  
 $\mkvar$ creates a new anonymous instance of the $\Var$ interface, using the `methods' supplied through its arguments.
@@
 
-We adopt the game semantics from \cite{SamsonGuyIAActive}; these are based on the game semantics developed in \cite{hoPcf}, with a modification to make them into a linear category.
+We adopt the game semantics from \cite{SamsonGuyIAActive}.  
+For the most part, these are very similar to the \emph{arenas} defined by Hyland and Ong in \cite{hoPcf}; however, they are slightly modified (through the prescription of a set of \emph{legal plays}) in order to give us access to the substructural logic (in particular, linear logic) that we will use as the basis of the model of local state.
 
@@
 \begin{definition}
-  A \emph{justified sequence} in an arena $A$ is a finite sequence $s$ of moves together with, for each non-initial move $a$ occurring in $s$, a pointer back to some move $b$ occurring earlier in $s$ such that $b\ts_A a$.
+  A \emph{justified sequence} in an arena $A$ is a finite sequence $s$ of moves together with, for each non-initial move $a$ occurring in $s$, a pointer from $a$ back to some move $b$ occurring earlier in $s$ such that $b\ts_A a$.
   We say that \emph{$b$ justifies $a$} or that $b$ is the \emph{justifier} of $a$.
@@
 
-  A justified sequence $s$ is \emph{well-bracketed} if whenever a question $q$ justifies some answer $a$, then any question $q'$ occurring after $q$ and before $a$ must justify some answer $a'$ occurring between $q'$ and $a$, and moreover $a$ is the only answer justified by $q$.
+  A justified sequence $s$ is \emph{well-bracketed} if whenever a question $q$ justifies some answer $a$, then any question $q'$ occurring after $q$ and before $a$ must justify some answer $a'$ occurring between $q'$ and $a$, and if $a$ is, moreover, the only answer justified by $q$:
+  \[
+    \begin{tikzcd}[row sep=0pt]
+      q \arrow[dddddd, bend right] \\
+      \vdots \\
+      q' \arrow[dd, bend right] \\
+      \vdots \\
+      a' \\
+      \vdots \\
+      a
+    \end{tikzcd}
+    \]
   We say that a justified sequence $s$ is \emph{alternating} if it alternates between $O$-moves and $P$-moves, and that it is \emph{well-formed} if it is both well-bracketed and alternating.
@@
 
-  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
+  A \emph{game} is a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
 \end{definition}
 
-We shall call an odd-length sequence $s\in P_A$ an \emph{$O$-position} and an even-length sequence a \emph{$P$-position}
+We shall call an odd-length sequence $s\in P_A$ an \emph{$O$-position} and an even-length sequence a \emph{$P$-position}.
 
@@
   \begin{itemize}
-    \item $M_X = \{q\} + X$, 
-    \item $\lambda_X(q)=(O,Q)$ and $\lambda_X(x)=(P,A)$ for all $x\in X$, 
-    \item $q\ts_X x$ for each $x\in X$, and
+    \item $M_X = \{q\} + X$;
+    \item $\lambda_X(q)=(O,Q)$ and $\lambda_X(x)=(P,A)$ for all $x\in X$;
+    \item $q\ts_X x$ for each $x\in X$; and
     \item $P_X = \{\epsilon,q\}\cup\{qx\suchthat x\in X\}$, where the $x$ in $qx$ is justified by $q$.
@@
 \end{example}
+
+Given a game $A$, there are several ways to capture the natural notion of a strategy for $A$ for player $P$.  
+The most convenient way is to identify a strategy with the set of $P$-positions that may occur if $P$ plays according to that strategy.
 
@@
 \begin{definition}
-  Given games $A$,$B$, define a game $A\times B$ by
+  Given games $A,B$, define a game $A\times B$ by
   \begin{itemize}
-    \item $M_{A\times B} = M_A + M_B$,
-    \item $\lambda_{A\times B} = [\lambda_A,\lambda_B]$,
-    \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
+    \item $M_{A\times B} = M_A + M_B$;
+    \item $\lambda_{A\times B} = [\lambda_A,\lambda_B]$;
+    \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$; and
     \item $P_{A\times B} = \{s\in \L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
   \end{itemize}
+  Here, we have written $s\vert_A$ for the subsequence of $s$ consisting of all moves from $M_A$ and $s\vert_B$ for the subsequence consisting of all moves from $M_B$.
+
   We extend this to arbitrary products $\prod_i A_i$ in the obvious way.
@@
 
-Here, we have written $s\vert_A$ for the subsequence of $s$ consisting of all moves from $M_A$ and $s\vert_B$ for the subsequence consisting of all moves from $M_B$.
+Our interpretation of the type $\Var$ will be given by a particular infinite product; namely, the product of countably many copies of the game $\bC$, each one corresponding to the action of writing a particular natural number into the variable, together with a copy of the game $\bN$, corresponding to requesting the current value of the variable.
 
@@
   \begin{itemize}
-    \item $M_{A\tensor B} = M_A + M_B$,
-    \item $\lambda_{A\tensor B} = [\lambda_A,\lambda_B]$,
-    \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
+    \item $M_{A\tensor B} = M_A + M_B$;
+    \item $\lambda_{A\tensor B} = [\lambda_A,\lambda_B]$;
+    \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$; and
     \item $P_{A\tensor B} = \{s\in \L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
@@
   \begin{itemize}
-    \item $M_{A\implies B} = M_A + M_B$,
-    \item $\lambda_{A\implies B} = [\neg\circ\lambda_A,\lambda_B]$,
-    \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$, and
+    \item $M_{A\implies B} = M_A + M_B$;
+    \item $\lambda_{A\implies B} = [\neg\circ\lambda_A,\lambda_B]$;
+    \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$; and
     \item $P_{A\implies B} = \{s\in \L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
@@
   \begin{itemize}
-    \item $M_{\oc A}=M_A$,
-    \item $\lambda_{\oc A} = \lambda_A$,
-    \item $\ts_{\oc A} = \ts_A$ and
+    \item $M_{\oc A}=M_A$;
+    \item $\lambda_{\oc A} = \lambda_A$;
+    \item $\ts_{\oc A} = \ts_A$; and
     \item $P_{\oc A} = \{s\in \L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
@@
   \begin{itemize}
-    \item $M_{A\sequoid B} = M_{A\tensor B}$, 
-    \item $\lambda_{A\sequoid B} = \lambda_{A\tensor B}$, 
-    \item $\ts_{A\sequoid B} = \ts_{A \tensor B}$ and
+    \item $M_{A\sequoid B} = M_{A\tensor B}$;
+    \item $\lambda_{A\sequoid B} = \lambda_{A\tensor B}$;
+    \item $\ts_{A\sequoid B} = \ts_{A \tensor B}$; and
     \item $P_{A\sequoid B} = \{s\in P_{A\tensor B}\suchthat\text{$s=\epsilon$ or $s$ begins with a move from $A$}\}$.
@@
 
-  Given $\s\in\Int(A,B,C)$, we write $\s\vert_{A,C}$ for the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$.  
+  Given $\s\in\Int(A,B,C)$, we write $\s\vert_{A,C}$ for the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $C$.  
   A move $b$ in $\s\vert_{A,C}$ justifies a move $a$ either if $b$ justifies $a$ in either the $A$ or the $C$ components, or if $b$ justifies in $\s$ some initial move $c$ in $B$, which itself justifies $a$.
@@
 
-We need some small lemmata and definitions to help us show that this is a strategy.
+We have not yet shown that this is indeed a well-formed strategy; the proof of this fact will take us a few pages.  
+We start by proving some lemmata and making some definitions.
 
@@
   Moreover, if $\lambda_A^{OP}(s\vert_A)=O$ then $\lambda_A^{OP}(s\vert_B)=O$.
+  In other words, the second row of the table above never occurs.
   \label{LemCompositionLemma}
@@
   Induction on the length of $s$.
-  If $s=\epsilon$, then $s\vert_A=s\vert_B=\epsilon$, and so $(\lambda_A^{OP}(s\vert_A)\Rightarrow \lambda_B^{OP}(s\vert_B)) = (P\Rightarrow P) = P = \lambda_{A\implies B}^{OP}(s)$.
+  If $s=\epsilon$, then $s\vert_A=s\vert_B=\epsilon$, and so 
+  \[
+    (\lambda_A^{OP}(s\vert_A)\Rightarrow \lambda_B^{OP}(s\vert_B)) = (P\Rightarrow P) = P = \lambda_{A\implies B}^{OP}(s)\,.
+    \]
 
   Suppose then that $s=ta$, and that $\lambda_{A\implies B}^{OP}(t)=O$.  
-  This means that $\lambda_A^{OP}(t\vert_A)=P$ and $\lambda_B^{OP}(t\vert_B)=O$.
-  Then, whether $a$ is a move in $A$ or a move in $B$, adding it will flip exactly one of these components -- so $\lambda_{A\implies B}(s\vert_A)=O$ and $\lambda_{A\implies B}^{OP}(s\vert_B)=O$ if $a$ is a move in $A$ and $\lambda_{A\implies B}(s\vert_A)=P$ and $\lambda_{A\implies B}^{OP}(s\vert_B)=P$ if $a$ is a move in $C$.
+  This means that
+  \begin{mathpar}
+    \lambda_A^{OP}(t\vert_A)=P \and \lambda_B^{OP}(t\vert_B)=O\,.
+  \end{mathpar}
+  Then, whether $a$ is a move in $A$ or a move in $B$, adding it will flip exactly one of these components -- so 
+  \begin{mathpar}
+    \lambda_{A\implies B}(s\vert_A)=O \and \lambda_{A\implies B}^{OP}(s\vert_B)=O
+  \end{mathpar}
+  if $a$ is a move in $A$, and 
+  \begin{mathpar}
+    \lambda_{A\implies B}(s\vert_A)=P \and \lambda_{A\implies B}^{OP}(s\vert_B)=P
+  \end{mathpar}
+  if $a$ is a move in $C$.
 
   Suppose instead that $\lambda_{A\implies B}^{OP}(t)=P$.  
-  By induction, this means that either $\lambda_A^{OP}(t\vert_A)=P$ and $\lambda_B^{OP}(t\vert_B)=P$ or that $\lambda_A^{OP}(t\vert_A)=O$ and $\lambda_B^{OP}(t\vert_B)=O$.
+  By induction, this means that either 
+  \begin{mathpar}
+    \lambda_A^{OP}(t\vert_A)=P \and \lambda_B^{OP}(t\vert_B)=P
+  \end{mathpar}
+  or that 
+  \begin{mathpar}
+    \lambda_A^{OP}(t\vert_A)=O \and \lambda_B^{OP}(t\vert_B)=O\,.
+  \end{mathpar}
   In the first case, this means that either $t\vert_A$ is empty or its last move is a $P$-move in $A$ (and therefore an $O$-move in $A\implies B$), and so the move $a$ must take place in $C$, meaning that $\lambda_A^{OP}(s\vert_A)=P$ and $\lambda_B^{OP}(s\vert_B)=O$.
@@
   But we must also have $\lambda_{A\implies B}(tab)=O$, so $\lambda_A(tab\vert_A)=P$ and $\lambda_B(tab\vert_B)=O$.  
-  But this is a contradiction, since $tab\vert_A$ and $tab\vert_B$ are both one move longer than the plays $t\vert_A$ and $t\vert_B$.
+  But this is a contradiction, since $tab\vert_A$ and $tab\vert_B$ are both one move longer than the plays $t\vert_A$ and $t\vert_B$, so $\lambda_A(tab\vert_A) \ne \lambda_A(t\vert_A)$ and $\lambda_B(tab\vert_B)\ne \lambda_B(t\vert_B)$.
 \end{proof}
@@
   We have $\pv{\s a}\vert_{A,C}=\pv{\s}\vert_{A,C}a$, which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}a$, which is the same as $\pv{\s a\vert_{A,C}}$.
-  If $b$ is a move in $B$, then $\pv{\s b}\vert_{A,C}=\pv{\s}b\vert_{A,C}=\pv{\s}\vert_{A,C}=\pv{\s\vert_{A,C}}=\pv{\s b\vert_{A,C}}$, by the inductive hypothesis.
+  If $b$ is a move in $B$, then 
+  \[
+    \pv{\s b}\vert_{A,C}=\pv{\s}b\vert_{A,C}=\pv{\s}\vert_{A,C}=\pv{\s\vert_{A,C}}=\pv{\s b\vert_{A,C}}\,,
+    \]
+  by the inductive hypothesis.
 
@@
   Since $a$ cannot be an initial move in $A$, $b$ must occur in the same game as $a$, and in particular must not occur in $B$.
-  Then we have $\pv{\s b\t a}\vert_{A,C}=\pv{\s} ba\vert_{A,C}=\pv{\s}\vert_{A,C}ba$, which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}ba=\pv{\s ba\vert_{A,C}}$.
+  Then we have 
+  \[
+    \pv{\s b\t a}\vert_{A,C}=\pv{\s} ba\vert_{A,C}=\pv{\s}\vert_{A,C}ba\,,
+    \]
+  which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}ba=\pv{\s ba\vert_{A,C}}$.
 \end{proof}
@@
 
-  In the configuration $PPO$, once again the move $a$ cannot take place in $A$, since this would leave $ta\vert_{A\implies B}$ in an illegal configuration.  
+  In the configuration $PPO$, once again the move $a$ cannot take place in $A$, since this would leave $ta\vert_{A\implies B}$ in the illegal configuration $OP$.
   Therefore, it must occur in $C$, and must be a $P$-move in $C$ and hence a $P$-move in $A\implies C$.
@@
 
-\begin{lemma}
+\begin{proposition}
   \[
@@
     \]
-\end{lemma}
+  \label{PropAssociativityOfComposition}
+\end{proposition}
 \begin{proof}
@@
   \end{itemize}
-  Here, $i_*(s)$ means the function $i$ applied pointwise to the elements of the string $s$.
+  Here, $i_*(s)$ means the function $i$ applied pointwise to the elements of the string $s$, leaving justification indices as they are in $s$.
 
@@
     \]
-  If $P_B=\{i_*(s)\suchthat s\in P_A\}$, then we call it a \emph{structural isomorphism}, and we write $\cc_i$ (`copycat') for $\subs_i$.
+  If $P_B=\{i_*(s)\suchthat s\in P_A\}$, then we call it a \emph{structural isomorphism}, and we write $\cc_i$ (`copycat') instead of $\subs_i$.
 \end{definition}
@@
   Suppose that $\s\in\sigma\|\subs_i$.  
-  Then $\s\vert_{C,B}\in\sigma$ and $\s\vert_B=i_*(\s\vert_A)$; i.e., $\s\vert_{C,B}=[\id_{M_C},i]_*(\s\vert_{C,A})$, and therefore $\s\vert_{C,A}=[\id_{M_C},i]_*(\s\vert_{C,B})$, where $\s\vert_B\in i_*(P_A)$.
+  Then $\s\vert_{C,B}\in\sigma$ and $\s\vert_B=i_*(\s\vert_A)$; i.e., 
+  \[
+    \s\vert_{C,B}=[\id_{M_C},i]_*(\s\vert_{C,A})\,,
+    \]
+  and therefore 
+  \[
+    \s\vert_{C,A}=[\id_{M_C},i]_*(\s\vert_{C,B})\,,
+    \]
+  where $\s\vert_B\in i_*(P_A)$.
 
@@
 It is also easy to see from Proposition \ref{PropCopycat} that the identity function $\id\from M_A \to M_A$ is a structural isomorphism from $A$ to itself, and that the resulting copycat strategy $\cc_{\id}$ is an identity for composition.
-Combining this with our result for associativity in the previous section, we get that
+Combining this with our result for associativity in the previous section (Proposition \ref{PropAssociativityOfComposition}), we get that
 \begin{theorem}
@@
 We now claim that the tensor product connective $\tensor$ makes $\G$ into a symmetric monoidal closed category, with internal hom given by $\implies$.  
+We shall prove this result over the next two sections.
 
@@
   \normalsize
-  Now, if $s\in\sigma\tensor\tau$, or an odd-length sequence formed by adding an $O$-move to the end of a sequence in $\sigma\tensor\tau$, then we also know that $s\vert_{A,B}\in\sigma\subset P_{A\implies B}$ and that $s\vert_{C,D}\in\tau\subset P_{C\implies D}$.
+  If $s\in\sigma\tensor\tau$, or an odd-length sequence formed by adding an $O$-move to the end of a sequence in $\sigma\tensor\tau$, then we also know that $s\vert_{A,B}\in\sigma\subset P_{A\implies B}$ and that $s\vert_{C,D}\in\tau\subset P_{C\implies D}$.
   This means that we can discount the last two configurations in the table above, since one contains the illegal configuration $OP$ in $C\implies D$ and the other contains the illegal configuration $OP$ in $A \implies B$.
@@
   \begin{IEEEeqnarray*}{Cl}
-    & ((\sigma\tensor\tau)\tensor\upsilon);\cc_{\assoc_{M_{A},M_{B},M_{C}}} \\
-    = & \{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s)\suchthat s\in (\sigma\tensor\tau)\tensor\upsilon\} \\
+    & ((\sigma\tensor\tau)\tensor\upsilon);\cc_{\assoc_{M_{A},M_{B},M_{C}}} \\[10pt]
+    = & \{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s)\suchthat s\in (\sigma\tensor\tau)\tensor\upsilon\} \\[10pt]
     = & \left\{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s) \,\middle|\,\mbox{\pbox{\textwidth}{
@@
       $s\vert_{A',A}\in\sigma$, $s\vert_{B',B}\in\tau$, $s\vert_{C',C}\in\upsilon$
-    }}\right\} \\
-    = & \{s\in P_{((A'\tensor B') \tensor C') \implies (A \tensor (B \tensor C))} \suchthat s\vert_{A',A}\in\sigma,s\vert_{B',B}\in\tau,s\vert_{C',C}\in\upsilon\} \\
+    }}\right\} \\[10pt]
+    = & \{s\in P_{((A'\tensor B') \tensor C') \implies (A \tensor (B \tensor C))} \suchthat s\vert_{A',A}\in\sigma,s\vert_{B',B}\in\tau,s\vert_{C',C}\in\upsilon\} \\[10pt]
     = & \left\{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s) \,\middle|\,\mbox{\pbox{\textwidth}{
@@
       $s\vert_{A',A}\in\sigma$, $s\vert_{B',B}\in\tau$, $s\vert_{C',C}\in\upsilon$
-    }}\right\} \\
-    = & \{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s)\suchthat s\in \sigma\tensor (\tau\tensor \upsilon)\} \\
+    }}\right\} \\[10pt]
+    = & \{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s)\suchthat s\in \sigma\tensor (\tau\tensor \upsilon)\} \\[10pt]
     = & \cc_{\assoc_{M_{A'},M_{B'},M_{C'}}};(\sigma\tensor(\tau\tensor\upsilon))\,.\hspace{1pt plus 1fill} \qedhere
@@
 
-Then, by Proposition \ref{PropCopycat} again, these natural transformations satisfy the same coherence diagrams (pentagon, triangles, hexagon etc.) satisfied by the original associators, unitors and symmetry in $(\Set,+)$.
+This proves that the coherences we have defined are natural transformations.  
+By Proposition \ref{PropCopycat} again, these natural transformations satisfy the same coherence diagrams (pentagon, triangles, hexagon etc.) satisfied by the original associators, unitors and symmetry in $(\Set,+)$.
 
@@
   Let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $C\implies D$.  
-  Then we define a strategy $\sigma\implies \tau\from (B\implies C) \implies (A\implies D)$ by
+  Then we define a strategy 
+  \[
+    \sigma\implies \tau\from (B\implies C) \implies (A\implies D)
+    \]
+  by
   \[
@@
 So far, the strategies we have been considering have all been innocent.  
-We now start considering some non-innocent strategies.
-
-We can generalize the subset inclusions of the previous section to \emph{tree immersions}.  
+For our model of state, we are going to need to start using some non-innocent strategies as well.  
+We begin with a generalization of the idea of a subset inclusion to that of a \emph{tree immersion}, which gives us a similar recipe for constructing strategies.  
 Tree immersions are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
@@
 \begin{definition}
-  Given a tree immersion from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
+  Given a tree immersion from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$.
+  Since $\phi$ preserves length and justification indices, the resulting play is a legal play of $C\implies A$.
 \end{definition}
@@
 
-Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and there is no version of Proposition \ref{PropProductOfTreeEmbeddings} that works for subset inclusion strategies.
-Of course, since a subset inclusion is a special case of a tree immersion, then $\langle \subs_i\rangle$ is always a tree immersion strategy.
+Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and Proposition \ref{PropProductOfTreeEmbeddings} cannot be adapted to use subset inclusions rather than tree immersions.
+Of course, since a subset inclusion is a special case of a tree immersion, then $\langle \subs_i\suchthat i \in \mathcal I\rangle$ is always a tree immersion strategy for any set $\mathcal I$ of subset inclusions.
 
@@
 
-We have now given the category-theoretic properties of all the connectives from section \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
-
-We would like to say that $\blank\sequoid\blank$ is a functor from $\G \times \G \to \G$, as is the case with the tensor product $\blank\tensor\blank$.  
+We have given the category-theoretic properties of all the connectives from section \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
+In this section, we will introduce the categorical semantics of the sequoid operator $\blank\sequoid\blank$.  
+The sequoid is a non-standard operator and does not fall into any of the established patterns of categorical algebra; rather, it gives rise to the new notion of a \emph{sequoidal category} introduced by Laird in \cite{laird02}.
+
+To start with, we would like to be able to say that $\blank\sequoid\blank$ is a functor from $\G \times \G \to \G$, as is the case with the tensor product $\blank\tensor\blank$.  
 However, this does not quite work: given strategies $\sigma\from A \implies B$ and $\tau\from C \implies D$, we may not get a well-formed strategy for $(A \sequoid C) \implies (B \sequoid D)$ by `playing according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $C$ and $D$'.
@@
 
-It is clear that the composition of strict morphisms is again a strict morphism , as is any morphism of the form $\subs_i$, and so we get a wide subcategory $\G_s$ of $\G$ whose objects are games and where the morphisms are the strict strategies.
+It is clear that the composition of strict morphisms is again a strict morphism, and that any morphism of the form $\subs_i$ is a strict morphism, and so we get a wide subcategory $\G_s$ of $\G$ whose objects are games and where the morphisms are the strict strategies.
 We then have a natural inclusion functor $J\from \G_s\to \G$.
@@
 \begin{remark}
-  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definition \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.
-  But such a strategy would not satisfy the conclusion of Proposition \ref{PropWkCommutativeDiagram}, since $\sigma\tensor\tau;\wk_{B,D}$ would contain these extra plays where $\wk_{A,C};\sigma\sequoid\tau$ had `given up'.
+  If $\sigma$ is not a strict strategy, then the set 
+  \[
+    \{s\in\sigma\tensor\tau \suchthat s\in P_{(A\sequoid C)\implies (B\sequoid D)}\}
+    \]
+  is still a valid strategy for $P_{(A\sequoid C)\implies (B \sequoid D)}$, but now the conclusion of Proposition \ref{PropWkCommutativeDiagram} no longer holds.
 \end{remark}
 \begin{remark}
-  Of course, we would \emph{like} to restate Proposition \ref{PropWkCommutativeDiagram} by saying that $\wk$ is some sort of natural transformation, but that doesn't make sense until we've shown that $\blank\sequoid\blank$ is a functor.
+  Of course, we would \emph{like} to restate Proposition \ref{PropWkCommutativeDiagram} by saying that $\wk$ is a natural transformation, but it doesn't make sense to do so, because we don't yet know that $\blank\sequoid\blank$ is a functor.
 \end{remark}
@@
 \begin{proposition}
-  $\wk_{A,B}$ is a natural transformation $JA \tensor B \to J(A \sequoid B)$.
+  $\wk_{A,B}$ is a natural transformation
+  \[
+    JA \tensor B \to J(A \sequoid B)\,.
+    \]
   \label{PropWkNatural}
@@
 We have some additional structure on the $\tensor$ and $\sequoid$ operators.  
-By inspecting the definitions that if $A,X,Y$ are games then the associator $\assoc_{M_A,M_X,M_Y}$ and unitor $\runit_{M_A}$ in $(\Set,+)$ give rise to structural isomorphisms
+By inspecting the definitions, we can see that if $A,X,Y$ are games then the associator $\assoc_{M_A,M_X,M_Y}$ and unitor $\runit_{M_A}$ in $(\Set,+)$ give rise to structural isomorphisms
 \begin{mathpar}
@@
   The definitions of \emph{lax action} can be found at the start of Chapter \ref{ChapParametricMonads}, while that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
-  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphisms.
+  The definitions we have used here are not quite the same as the ones from Chapter \ref{ChapParametricMonads}, but they are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphisms.
   A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
@@
     \]
-  Indeed, we have
+  We have
   \begin{IEEEeqnarray*}{rCl?u}
@@
 
-We will now consider some important additional category-theoretic properties of the sequoid operator on games that do not follow from the fact that $\G$ is a sequoidal category.
+The definition of a sequoidal category captures some of the important properties of the sequoid operator $\sequoid$ in the category of games, but not all of them.  
+In this section, we will consider some further category-theoretic properties of the sequoid operator.
 
@@
   \[
-    \dec_{(a_i),x} = \langle \pr_i\sequoid x \rangle \from \prod_ia_i \sequoid x \to \prod_i (a_i \sequoid x)
+    \dec_{(a_i),x} = \langle \pr_i\sequoid x \rangle \from \left(\prod_ia_i\right) \sequoid x \to \prod_i (a_i \sequoid x)
     \]
@@
   Let $\C$ be a distributive sequoidal category.  
-  We say that $\C$ is \emph{strongly distributive} if whenever $(A_i),(B_i)$ are objects of $\C_s$, where $(B_i)$ is a non-empty collection, then the morphism
-  \[
-    \langle A_1 \sequoid(\cdots \sequoid (A_n \sequoid J(\pr_i))\cdots)\rangle
+  We say that $\C$ is \emph{strongly distributive} if whenever $(A_i),(B_i),C$ are objects of $\C_s$, where $(B_i)$ is a non-empty collection, then the morphism
+  \[
+    \langle JC \tensor J(A_1 \sequoid(\cdots \sequoid (A_n \sequoid J(\pr_i))\cdots))\rangle
     \]
   is a monomorphism
-  \[
-    A_1 \sequoid\left(\cdots\sequoid\left(A_n \sequoid J\left(\prod_iB_i\right)\right)\cdots\right) \to \prod_i (A_1 \sequoid (\cdots \sequoid (A_n \sequoid J(B_i))\cdots))\,.
-    \]
+  \begin{mathpar}
+    JC \tensor J\left(A_1 \sequoid\left(\cdots\sequoid\left(A_n \sequoid J\left(\prod_iB_i\right)\right)\cdots\right)\right) \to \prod_i (JC \tensor J(A_1 \sequoid (\cdots \sequoid (A_n \sequoid J(B_i))\cdots)))\,.
+  \end{mathpar}
 \end{definition}
@@
 \begin{proof}
+  We first ignore the $JC \tensor \blank$ part.
+
   By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree immersion 
@@
   Therefore, $\phi$ is a monomorphism by Proposition \ref{PropZigzagMono}.
-\end{proof}
-
-Note that if $\C$ is decomposable, this property of being a monomorphism is automatically preserved by the tensor product; i.e., for any objects $A,(B_i),C$ of $\C_s$ (for $B_i$ a non-empty collection), the morphism
-\[
-  \langle JC \tensor J(A \sequoid J(\pr_i))\rangle \from JC \tensor J\left(A \sequoid J\left(\prod_iB_i\right)\right) \to \prod_i JC \tensor J(A \sequoid J(B_i))
-  \]
-is a monomorphism.
+
+  Now, if we take the tensor product on the left by $JC$, we still get a surjective tree immersion and hence a monomorphism.
+\end{proof}
 
@@
   The only thing we really need to check is that isomorphisms in $\G$ are always strict strategies.  
-  Indeed, if $\sigma$ is a strategy for $A \implies B$ and $\tau$ a strategy for $B \implies A$ such that $\sigma;\tau=\id_A$, then for any opening move $a$ in $A$ on the right of $\tau$ there is some $\s\in\int(A,B,A)$ such that $\s\vert_{A,A}=aa$, and therefore the reply to $a$ in $\tau$ must take place in $B$.
+  Indeed, if $\sigma$ is a strategy for $A \implies B$ and $\tau$ a strategy for $B \implies A$ such that $\sigma;\tau=\id_A$, then for any opening move $a$ in $A$ on the right of $\tau$ there is some $\s\in\Int(A,B,A)$ such that $\s\vert_{A,A}=aa$, and therefore the reply to $a$ in $\tau$ must take place in $B$.
 \end{proof}
@@
   \]
-Informally, this is because both sides allow player $O$ to start either in $A$ or in $B$, and thereafter to continue in that game.
+Informally, this is because both sides allow player $O$ to start either in $A$ or in $B$ on the first move, and thereafter switch between $A$ and $B$ as he chooses.
 
@@
 
-The specific isomorphism in Proposition \ref{PropDecSeq} is rather complicated at the moment, but we can simplify it.
+The formula for the isomorphism given in the proof of Proposition \ref{PropDecSeq} is rather complicated.  
+Our next task will be to give an equivalent formulation that will be simpler to work with later.
 
@@
     \]
-  Suppose that this sequence has a limit $\oc A$, and that $B\tensor \oc A$ is the limit of the first sequence for all $B$.
+  Suppose that this sequence has a limit $\oc A$, and suppose moreover that tensoring this limiting cone with $B$ exhibits $B\tensor \oc A$ as the limit of
+  \[
+    B \leftarrow B\tensor A \leftarrow B\tensor A^2 \leftarrow B \tensor A^3 \leftarrow \cdots\,.
+    \]
+  for any $B$.
 
@@
   In fact, this is the \emph{cofree commutative comonoid} over $A$ in $\C$.  
-  The counit $\der_A\from \oc A \to A$ of the adjunction is the map in the limiting cone.
+  The counit $\der_A\from \oc A \to A$ of the adjunction is the morphism in the limiting cone.
   \label{TheMtt}
@@
 \end{itemize}
-but that $A \tensor B$, $A\sequoid B$ and $\oc A$ are not in general well-opened, even if $A$ and $B$ are.
+but that $A \tensor B$, $A\sequoid B$ and $\oc A$ are not in general well-opened, even if both $A$ and $B$ are.
 
@@
   \]
-We define a category $\G_{wo}^{\oc}$ to be the image of the functor $\G_{wo}\to \CCom(\G)$ inside $\CCom(\G)$.  
+We define a category $\G_{wo}^{\oc}$ to be the span of the functor $\G_{wo}\to \CCom(\G)$ inside $\CCom(\G)$.  
 By our discussion above, $\G_{wo}^{\oc}$ is a Cartesian category.
 
-A more convenient description of $\G_{wo}^{\oc}$ is that it is the category where the objects are well-opened games and where the morphisms
+This gives us a category in which the objects are commutative comonoids over well-opened games.
+A more convenient description of this category is that it is the category where the objects are well-opened games and where the morphisms
 \[
@@
   \]
-where the \emph{promotion} $\sigma^\dag$ of $\sigma$ comes from the description of $\oc A$ as the cofree commutative comonoid on $A$.
+where the \emph{promotion} operator $blank^\dag$ from strategies $\sigma\from \oc A \to B$ to strategies $\sigma^\dag\from \oc A \to \oc B$ is the right half of the adjunction between $\G$ and $\CCom(\G)$.
 
@@
   Indeed, it is clear from our definitions that $\oc\oc A = \oc A$ as games.  
-  Then, $m$ is in fact the identity strategy between these two games, so is innocent.
+  Then, $m$ is in fact the identity strategy between these two games.
 \end{proof}
@@
 \begin{corollary}
-  If $A$ is a well-opened game, then $\oc A$ is the final coalgebra for the functor $A \sequoid \blank$.
+  If $A$ is a well-opened game, then $\oc A$ is a final coalgebra for the functor $A \sequoid \blank$.
 \end{corollary}
@@
   \[
-    \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A \xrightarrow{\der_A\tensor \oc A} A \tensor \oc A \xrightarrow{\wk_A,\oc A} A \sequoid \oc A\,.
+    \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A \xrightarrow{\der_A\tensor \oc A} A \tensor \oc A \xrightarrow{\wk_{A,\oc A}} A \sequoid \oc A\,.
     \]
@@
 
-We now come to interpret Idealized Algol within our category $\G_{wo}^{\oc}$.  
+At last we are in a position to interpret Idealized Algol within our category $\G_{wo}^{\oc}$.  
 The base types $\com$, $\bool$ and $\nat$ are interpreted by the games $\bC$, $\bB$ and $\bN$, while the type $\Var$ is interpreted by the game
@@
   \]
-where $\bC^{\bN}$ is the product of $\bN$-many copies of $\bC$.
+where $\bC^{\bN}$ is the product of countably many copies of $\bC$ (so we have used the symbol $\bN$ to denote both the set $\bN$ and the game $\bN$ in the same formula).
 Given types $S,T$, the denotation $\deno{S\to T}$ of the type of functions from $S$ to $T$ is given by
@@
 
-The most important feature of strategies of the form $(\sigma_x)$ is the most obvious one: given $X$, and $y\in X$, we have a strategy $y$ for the game $X$ with maximal play $qx$.  
+The most important feature of strategies of the form $(\sigma_x)$ is the most obvious one: given $X$, and $y\in X$, we have a strategy $y$ for the game $X$ with maximal play $qy$.  
 Then $y;(\sigma_x) = \sigma_y$.
@@
 \end{itemize}
-These give us an obvious way to interpret most of the rest of the terms of Idealized Algol.  
+Here, $\pr_n$ and $\pr_\bN$ are the natural projections on to $\bC$ and $\bN$ from $\Var = (\bC)^n \times \bN$.
+
+These morphisms give us an obvious way to interpret most of the rest of the terms of Idealized Algol.  
 For example, if we have strategies
@@
 \[
-  \deno{\Gamma\ts V\gets E \from \bC} = \deno{\Gamma} \xrightarrow{\Delta} \deno{\Gamma}\times\deno{\Gamma} \xrightarrow{\deno{\Gamma\ts E}\times\deno{\Gamma\ts V}} \bN \times \Varr \xrightarrow{\assign} \bC\,.
-  \]
+  \deno{\Gamma\ts V\gets E \from \bC} = \deno{\Gamma} \xrightarrow{\Delta} \deno{\Gamma}\times\deno{\Gamma} \xrightarrow{\deno{\Gamma\ts E}\times\deno{\Gamma\ts V}} \bN \times \Varr \xrightarrow{\assign} \bC
+  \]
+that we can use as the denotation of the term $\Gamma \ts V \gets E$.
+
+We use $\seq_X$ for the denotation of $M;N$ and $\deref$ for the denotation of $\oc V$.  
+The role played by the remaining morphisms can easily be deduced from their names.
 
@@
 Note that if $A$ is a game, then we can order the strategies for $A$ by subset inclusion.  
-Then this order is clearly preserved by composition.
+This order is clearly preserved by composition.
 
@@
   We claim that $\bigcup\Sigma$ is a strategy for $A$.  
-  Indeed, it is certainly even-prefix-closed, and if $sab,sac\in\Sigma$, then $sab\in\sigma$ and $sac\in\tau$ for $\sigma,\tau\in\Sigma$, and therefore $sab,sac\in\upsilon$ for some $\upsilon\in\Sigma$ and so $b=c$.
+  Indeed, it is certainly even-prefix-closed, and if $sab,sac\in\bigcup\Sigma$, then $sab\in\sigma$ and $sac\in\tau$ for $\sigma,\tau\in\Sigma$, and therefore $sab,sac\in\upsilon$ for some $\upsilon\in\Sigma$ and so $b=c$.
 
@@
 
+It is possible to prove an innocent version of this (see \cite{hoPcf}), but we will not need this to prove Full Abstraction for Idealized Algol.
+
 \section{The Strategy $\cell$}
@@
 Now we come to the denotation of $\neww$.  
-For this, we shall define a strategy $\cell\from \oc\bN \implies \oc \Varr$ by using the property of $\oc \Varr$ as a final coalgebra.
+For this, we shall define a strategy $\cell\from \oc\bN \implies \oc \Varr$ by using the universal property of $\oc \Varr$ that arises from the fact that it is a final coalgebra for $\Var \sequoid\blank$.
 
@@
   \]
-We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
+We then define the strategy $\cell$ to be the anamorphism $\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
 \[
@@
 
-This coalgebraic definition of the $\cell$ strategy will be sufficient for most of our purposes, it will also be convenient to have a more direct definition.
+While this coalgebraic definition of the $\cell$ strategy will be sufficient for most of our purposes, it will also be convenient to have a more direct definition.
 
@@
   commute.
-  Since $\dist_{(\bC)_\bN,\bN}$ is an isomorphism, it will suffice to show commutativity of the diagram formed by composing by it on the right; i.e.:
+  Since $\dist_{(\bC)_\bN,\bN}$ is a natural isomorphism, it will suffice to show commutativity of the diagram formed by composing by $\dist_{(\bC)_\bN,\bN}$ on the right to give us the diagram
+  \[
+    \begin{tikzcd}[column sep=60pt]
+      \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
+        & \Varr \sequoid \oc\bN \arrow[r, "\dist_{(\bC)_\bN,\bN}"]
+          & (\bC \sequoid \oc\bN)^\bN \times (\oc\bN \sequoid \oc\bN) \arrow[d, "(\bC \sequoid \cell)^\bN \times (\bN \sequoid \cell)"] \\
+      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
+        & \Varr \sequoid \oc\Varr \arrow[r, "\dist_{(\bC)_\bN,\bN}"]
+          & {(\bC \sequoid \oc\Varr)^\bN \times (\bN \sequoid \oc\Varr)\,,}
+    \end{tikzcd}
+    \]
+  which, by the definition of $\cell_0$, is the same as the diagram
   \[
@@
 
-We now introduce the operational semantics of Idealized Algol, so that we can prove soundness and adequacy of our semantics for it.
+We now introduce the operational semantics of Idealized Algol.  
+When we have done so, we will link it to our denotational semantics by proving Computational Adequacy and Full Abstraction.
 
@@
   \item at type $\nat$, the numerals $n$; 
-  \item at type $\Var$, variable names $x$ of type $\Var$ and expressions of the form $\mkvar W\,R$; and
+  \item at type $\Var$, variable names $x\from\Var$ and expressions taking the form $\mkvar W\,R$; and
   \item at type $S\to T$, expressions of the form $\lambda x^S.M$.
 \end{itemize}
+These are the terms that cannot be evaluated any further.
 
 We define a \emph{$\Var$-context} to be a context $\Gamma$ of the form $x_1\from \Var,\cdots,x_n\from \Var$.
-Given a $\Var$-context $\Gamma$, we define a \emph{$\Gamma$-store} to be a function $s$ from the variable names occurring in $\Gamma$ to the natural numbers.  
+Given a $\Var$-context $\Gamma$, we define a \emph{$\Gamma$-store} to be a function $s$ from the set of variable names occurring in $\Gamma$ to the set of natural numbers.  
 Given such a store $s$, we write $(s\vert x \mapsto n)$ for the store given by
@@
 The definition of this relation is shown in Figure \ref{FigIaOpSem}.
+The idea behind it is that the predicate $\Gamma,s\ts M\converges c,s'$ should represent the assertion that, given initial state $s$, the term $M$ will evaluate to the canonical form $c$, leaving the state $s'$.
 
@@
 
-We also give a small-step operational semantics for Idealized Algol, which will sometimes be easier to work with.
+We also give an equivalent small-step operational semantics for Idealized Algol.  
+For a lot of our purposes, the small-step semantics will be easier to work with.
 
@@
 
-As an auxiliary definition, we need the notion of an \emph{evaluation context} (see \cite{Felleisen}).
-This is a single-holed context defined inductively by the following BNF formula, where $M$ ranges over IA terms (subject to typing rules).
+As an auxiliary definition, we need the notion of an \emph{evaluation context}, as introduced by Felleisen in \cite{Felleisen}.
+An evaluation context is a single-holed context defined inductively by the following BNF formula, where $M$ ranges over IA terms (subject to typing rules).
 \begin{center}
@@
 
-Next, we define a relation $\Gamma,s,M\oopto\Gamma,\Delta,s',M'$ as in Figure \ref{FigIaSsOpSem}.
-
-We then define the relation $\opto$ as
+The idea behind the evaluation contexts is that they tell us about the order of evaluation of a term: if we want to evaluate the term $\EE[M]$ for one step, then we first evaluate $M$ for one step, yielding another term $M'$, and then replace $\EE[M]$ with $\EE[M']$.
+
+Next, we define a relation $\Gamma,s,M\oopto\Gamma,\Delta,s',M'$.  
+The definition of this relation is in Figure \ref{FigIaSsOpSem}; we interpret the judgement $\Gamma,s,M \oopto \Gamma,\Delta,s',M'$ as saying that if we start in state $s$ and evaluate the term $M$ for a single step, then we get the term $M'$ in the state $s'$, possibly adding some new free variables through the $\Var$-context $\Delta$.
+
+Lastly, we define the relation $\opto$ as
 \[
@@
 for each evaluation context $\EE$.
+Note that $\EE$ may itself contain free variables of type $\Var$: we assume that these are all contained in the $\Var$-context $\Gamma$.
 
@@
 We need to prove that this is equivalent to our original semantics.
+
 Given a $\Gamma,\Delta$-store $s$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.
-
 \begin{lemma}
@@
   Structural induction on $\EE$.
-  The base case, when $\EE$ is a hole, covers the interesting cases, so we shall leave it to last.
-  The remaining cases are quite similar, so we will show the proof for one of them for illustration.
+  The base case, when $\EE=-$e, covers the interesting cases, so we shall leave it to last.
+  The remaining cases are quite similar, so we will show the proof for the case where $\EE = \EE'\,N$ for illustration.
 
@@
     \]
-  Now, let us suppose that $\EE$ is a hole, so that $\EE[M']=M'$.
+  The remaining cases when $\EE\ne-$ are quite similar.
+  Now, let us suppose that $\EE=-$, so that $\EE[M']=M'$.
 
@@
   \begin{itemize}
-    \item Suppose that $\Gamma,s\ts M[N/x]\converges c,s'$.  
+    \item For function application, suppose that $\Gamma,s\ts M[N/x]\converges c,s'$.  
       Then we have a derivation
@@
         \]
-    \item We have a derivation
+    \item For variable assignment, we have a derivation
       \[
@@
         \]
-    \item We have a derivation
+    \item For variable dereference, we have a derivation
       \[
@@
         \]
-    \item Suppose that $\Gamma,x,(s\vert x\mapsto 0) \ts M\converges c,s'$.  
+    \item For $\neww$, suppose that $\Gamma,x,(s\vert x\mapsto 0) \ts M\converges c,s'$.  
       Then we have a derivation
@@
   Suppose that $\Gamma,s\ts M\converges c,s'$.  
-  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
+  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$ of $\Var$-contexts, $s=s^{(1)},\cdots,s^{(n)}$ of $\Gamma_n$-stores and $M=M_1,\cdots,M_n=c$ of terms such that
   \[
@@
       where $t'\vert_\Gamma=s'$ and $t''\vert_\Gamma=s''$.
-
-      If we apply the evaluation context $-N$ pointwise to the first small-step derivation, then we have another valid small-step derivation.  
+      Note that we can easily enlarge $\Gamma$ to make sure that it contains all the free variables in $N$.
+
+      If we apply the evaluation context $-N$ pointwise to the first small-step derivation, then we have another valid small-step derivation
+      \[
+        \Gamma,s \ts M\,N \opto \cdots \opto \Gamma,\Delta,t',\lambda x.M'\,N\,.
+        \]
       Then we can join the two together to get the derivation
@@
       where $t'(x)=s'(x)$.
-    \item Lastly, suppose that the last step in the derivation is
+    \item Suppose that the last step in the derivation is
       \[
@@
 
-We start our proof of soundness with a result about evaluation contexts.
-This result captures the fact that the term filling the hole of an evaluation context is the first thing to be computed, using the sequoid operator to capture this notion of precedence.
+We start our proof of soundness with a structural result about evaluation contexts.
+Recall that the most important property of an evaluation context $\EE$ is that if a term $M$ fits into the hole in $\EE$, then $M$ is the first part of $\EE[M]$ to be evaluated.
+Using the sequoid operator, we can capture in category-theoretic terms an analogous property for the denotation of $\EE$.
 \begin{lemma}
   Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context (where $\Gamma$ is an arbitrary context), and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
-  Then there is a game $A$ and strategies $\sigma\from \oc{\deno{\Gamma}} \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$, where $\tau$ is a strict strategy, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
+  Then there are (independent of $M$) a game $A$, a strategy $\sigma\from \oc{\deno{\Gamma}} \implies A$ and a strict strategy $\tau\from\deno{T}\sequoid A \implies \deno{S}$, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
   \[
@@
       for appropriate $A',\sigma',\tau'$.  
-      Then we can compose on the right by $\theta$, and we are already in the required form, for
+      When we compose on the right by $\theta$, we are already in the required form, for
       \begin{mathpar}
@@
       for appropriate $A',\sigma',\tau'$.  
-      Then we can compose on the right by $\dereff$, and we are already in the required form, for
+      When we compose on the right by $\dereff$, we are already in the required form, for
       \begin{mathpar}
@@
       Write $Y=\bC$, $X'=X$, $Z=X$ and $\upsilon=\seq_X$ in the sequencing case, and $Y=\bN$, $X'=\Var$, $Z=\bC$ and $\upsilon=\assign$ in the variable assignment case.
-      Then, by the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
       \[
@@
         \sigma = \mu_{{\deno{\Gamma}}};(\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}});((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})
-        \and
+        \\
         \tau = \passoc_{\deno T,A'\tensor X,X}\inv;(\passoc_{\deno T,A',X}\inv\sequoid X);((\tau'\sequoid X)\sequoid X);\Lambda_s\inv(\Lambda_s\inv(\eta))\,.
@@
       for suitable $A',\sigma',\tau'$.  
-      Then, if we compose on the right by the morphism $\lunit_{\Varr};(n\tensor\Varr);\assign$, in order to give us the denotation $\deno{\Gamma\ts \EE'[M]\gets n} = \deno{\Gamma\ts\EE[M]}$, then we are already in the required form, with
+      When we compose on the right by the morphism $\lunit_{\Varr};(n\tensor\Varr);\assign$, in order to give us the denotation $\deno{\Gamma\ts \EE'[M]\gets n} = \deno{\Gamma\ts\EE[M]}$, then we are already in the required form, with
       \begin{mathpar}
@@
 
+First, note that the denotation $\deno{\Gamma\ts M}\from \oc\deno{\Gamma} \implies \deno{M}$ tells us what result we get out if we substitute in some initial $\Gamma$-store $s$ to $M$, but it does not tell us what state we are left in at the end.
+The next definition will give us an alternative version of the denotation that will convey this information.
+
 \begin{definition}
   Let $\Gamma,s\ts M\from T$ be a term with store.  
-  Then the \emph{sequoidal denotation} $\seqdeno{\Gamma,s\ts M}$ is the composite
+  Then we define the \emph{sequoidal denotation} $\seqdeno{\Gamma,s\ts M}$ to be the composite
   \[
@@
   \begin{itemize}
-    \item For most of the rules, $\Delta=\_$ and $s=s'$; i.e., the rule is of the form
+    \item For most of the rules, $\Delta=\blank$ and $s=s'$; i.e., the rule is of the form
       \[
@@
         \]
-      where, of course $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc{\deno{\Gamma,x}}$ is a right inverse for the composite $\runit_{\oc\deno{\Gamma}};(\oc{\deno{\Gamma}}\tensor(0;\cell));\cong$, since we have a commutative diagram
+      where, of course, $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc{\deno{\Gamma,x}}$ is a right inverse for the composite $\runit_{\oc\deno{\Gamma}};(\oc{\deno{\Gamma}}\tensor(0;\cell));\cong$, since we have a commutative diagram
       \[
@@
       In each of these cases, the outer context $\Gamma$ is unchanged by the rule; moreover, each term ignores the variables in $\Gamma$.
-      So the denotations terms-in-context $x,\Gamma\ts M\from T$ on either side of each rule are of the form
+      So the denotations of the terms-in-context $x,\Gamma\ts M\from T$ on either side of each rule are of the form
       \[
@@
         References in the middle of a shape refer to Lemma \ref{LemCellProjections} and Proposition \ref{PropFormulaForAlpha} above.  
-        Note the prominent role played in both diagrams by the anamorphism square for $\cell$ as in Section \ref{SecCell}.}
+        Note the prominent role played in both diagrams by the anamorphism square for $\cell$ given in Section \ref{SecCell}.}
         \label{FigSoundnessOoptoStorage}
@@
 \begin{lemma}
-  The relation $\opto$ between triples $\Gamma,s\ts M$ preserves the composite
-  \[
-    \oc\deno s;\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}}\,.
+  The relation $\opto$ between triples $\Gamma,s\ts M$ preserves the sequoidal denotation
+  \[
+    \seqdeno{\Gamma,s\ts M} = \oc\deno s;\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}}\,.
     \]
@@
 \begin{proof}
-  We use Lemma \ref{LemEvContexLemma} to reduce this to Lemma \ref{LemSoundnessOpto}.  
-  Indeed, Lemma \ref{LemEvContexLemma} tells us that for any $\Gamma,s\ts M$, $\deno{\Gamma\ts \EE[M]}$ may be written as
+  We use Lemma \ref{LemEvContexLemma} and Lemma \ref{LemSoundnessOpto}.  
+  Lemma \ref{LemEvContexLemma} tells us that for any $\Gamma,s\ts M$, $\deno{\Gamma\ts \EE[M]}$ may be written as
   \[
@@
 
-It is now a simple induction to show that we can extend this to the $\converges$ relation.
+It is now a simple induction to lift this result from the small-step $\opto$ relation to the big-step $\converges$ relation.
 
@@
 \end{proof}
+So we have now proved that if $\Gamma,s\ts M \converges c,s'$, then the sequoidal denotations
+\begin{mathpar}
+  \seqdeno{\Gamma,s\ts M}
+  \and
+  \seqdeno{\Gamma,s'\ts c}
+\end{mathpar}
+are equal.
 
@@
     \begin{tikzcd}[column sep=10.8pt]
-      I \arrow[r, "\deno{s}", thick]
-        & \oc S_\Gamma \arrow[r, "\cell^\Gamma", thick]
+      I \arrow[r, "\deno{s}" yshift=3pt, thick]
+        & \oc S_\Gamma \arrow[r, "\cell^\Gamma" yshift=3pt, thick]
           & \oc\deno{\Gamma} \arrow[rr, "\mu_{\deno{\Gamma}}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\deno{\Gamma}}" description, dotted]
@@
   \begin{itemize}
-    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\deno{\Gamma}\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\deno{\Gamma}}$ or $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
+    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$, $u\in X$ and $\sigma\from \oc\deno{\Gamma}\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\deno{\Gamma}}$ or $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ such that $\Gamma,s\ts M \converges u,s'$.
 
@@
 \end{definition}
+
+We now prove some lemmata about this new relation.
 
@@
 
+Now we are ready to prove our main adequacy Lemma.
+
 \begin{lemma}
@@
       Now we have $\deno{\Gamma\ts x};\pr_n = \deno{\Gamma\ts x\gets n}$ and $\deno{\Gamma\ts x};\pr_{\bN} = \deno{\Gamma \ts \oc\bN}$.  
-      From Lemma \ref{LemSoundnessOpto} (in particular, Figures \ref{FigSoundnessOoptoContext} and \ref{FigSoundnessOoptoStorage}), we know that if $s$ is a $\Gamma$-store, then
+      From the proof of Lemma \ref{LemSoundnessOpto} (in particular, Figures \ref{FigSoundnessOoptoContext} and \ref{FigSoundnessOoptoStorage}), we know that if $s$ is a $\Gamma$-store, then
       \[
@@
         \]
-      where we have that $\Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)$, and that
+      where $\Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)$, and that
       \[
@@
         \]
-      where we have that $\Gamma,s\ts \oc x \converges s(x),s$.
+      where $\Gamma,s\ts \oc x \converges s(x),s$.
 
@@
     \]
-  We can see this by precomposing both directions of the diagram in Figure \ref{FigSoundnessOpto} (with $\Gamma$ in that diagram standing for $\Gamma,\Delta$) with the composite
+  We can prove this by precomposing both directions of the diagram in Figure \ref{FigSoundnessOpto} (with $\Gamma$ in that diagram standing for $\Gamma,\Delta$) with the composite
   \[
@@
         \]
-      since $\suc\from\bN \implies \bN$ is a strict strategy, we know that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \suc M})} = \bot_{\bN\sequoid\oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,s'\ts n};(\suc\tensor\oc\deno{\Gamma}) = \seqdeno{\Gamma,s'\ts n+1}$, and we have $\Gamma,s\ts \suc M[N_i/x_i]\converges n+1$.
+      since $\suc\from\bN \implies \bN$ is a strict strategy, we know that either 
+      \[
+        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \suc M})} = \bot_{\bN\sequoid\oc\deno{\Gamma}}
+        \]
+      or
+      \[
+        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M})} = \seqdeno{\Gamma,s'\ts n};(\suc\tensor\oc\deno{\Gamma}) = \seqdeno{\Gamma,s'\ts n+1}\,,
+        \]
+      and we have $\Gamma,s\ts \suc M[N_i/x_i]\converges n+1$.
       Therefore, 
@@
         \]
-      where $x$ is considered as belonging to the `$Gamma$-component'.
+      where $x$ is considered as belonging to the `$\Gamma$-component'.
       Let $s$ be a $\Gamma$-store -- then we get a $\Gamma,x$-store $(s\vert x\mapsto 0)$.
@@
 
-We can then prove an \emph{equational soundness} result.
+We can now prove an \emph{equational soundness} result.
 First, we recall the definition of \emph{observational equivalence} of terms.
@@
 \begin{proposition}
-  Any semantics satisfying Computational Adequacy satisfies Equational Soundness.
+  Any compositional semantics satisfying Computational Adequacy satisfies Equational Soundness.
   \label{PropEquationalSoundness}
@@
 
-\begin{lemma}
+\begin{lemma}[{\cite[Lemma 15]{SamsonGuyIAActive}}]
   Let $T$ be a type of Idealized Algol.  
@@
 
-Before we complete our Full Abstraction result, we take a detour to consider a variation of our game semantics in which we do away with the sets of plays $P_A$.  
+Before we complete our definability proof, and hence our proof of Full Abstraction, we take a detour to consider a variation of our game semantics in which we do away with the sets of plays $P_A$.  
 We call this an \emph{arena-only semantics}, since the objects of our category are plain arenas.
@@
 \begin{proposition}
-  If $A$ is full, then we have $A=\oc A$.
+  If $A$ is full, then $A=\oc A$.
 \end{proposition}
@@
 
-This Proposition on its own does not seem to be much use, since we want to consider the game $\deno T$ without the $\oc$ in front of it.  
+This Proposition on its own does not seem to be much use, since it relates to the exponential of the denotation of $T$, while all our results have been proved about the denotation $\deno T$ itself.
 But recall that the `co-Kleisli'-style morphisms in our category, which are strategies for $\oc A \implies B$, may alternatively be regarded as comonoid homomorphisms from the comonoid on $\oc A$ to the comonoid on $\oc B$.
 Thus, if $S,T$ are Idealized Algol types, then the set of morphisms $\oc\deno S \implies \deno T$ in our original category is precisely the same as the set of morphisms $\oc\deno S \implies \oc\deno T$ that are comonoid homomorphisms.
+We will take up the rest of this section giving a combinatorial characterization of these morphisms.
 
@@
 
-Note the similarity with the definition of innocence, where the only difference is that we use the $P$-views $\pv{sa}$ and $\pv{ta}$ rather than the current threads $\ct{sa}$ and $\ct{ta}$.
+Note that this definition is identical to the definition of an innocent strategy, except with the current thread $\ct{-}$ taking the role of the $P$-view $\pv{-}$.
 Since $\pv{s}$ is a subsequence of $\ct{s}$ for any sequence $s$, we get:
@@
 
-We now link the combinatorial definition of single-threadedness to a definition about comonoid homomorphisms.
+We now link this definition to the idea of a comonoid homomorphism.
 
@@
 Then, if $T$ is any Idealized Algol type, there is some corresponding arena such that the full game on that arena is isomorphic to $\oc\deno T$.  
-We will call this arena $\deno T$ as well, relying on context to distinguish them.
+We shall write $\deno T$ for this arena, relying on context to distinguish the two notions of denotation.
 This means that our semantics of Idealized Algol lives within the new category, since a single-threaded strategy for $\deno S \to \deno T$ is the same thing as a strategy for $\oc \deno S \implies \deno T$ in the original semantics.
 
+We end up with a game semantics entirely based around arenas, without having to talk about distinguished sets of legal plays.
 This semantics is much closer to the game semantics of PCF developed by Hyland and Ong in \cite{hoPcf}; the difference there is that they use innocent rather than single-threaded strategies.
@@
 
-  Since $\deno{M}^\dag$ is the supremum of all its compact sub-strategies, if $\deno{M}^\dag;\alpha'=\bot_{\bC}$ for all compact $\alpha'\subset \alpha$, then $\deno{M}^\dag;\alpha=\bot_{\bC}$ by continuity of composition.
+  Since $\alpha$ is the supremum of all its compact sub-strategies, if $\deno{M}^\dag;\alpha'=\bot_{\bC}$ for all compact $\alpha'\subset \alpha$, then $\deno{M}^\dag;\alpha=\bot_{\bC}$ by continuity of composition.
   Therefore, there is some compact $\alpha'\subset\alpha$ such that $\deno M^\dag;\alpha\ne\bot_{\bC}$; moreover, we have that $\deno{N}^\dag;\alpha'=\bot_{\bC}$ by monotonicity of composition.
@@
 We conclude by giving a more concrete description of the intrinsic equivalence relation on strategies.
+This will give us a concrete representation of a morphism in the quotiented category, and hence an algorithm for deciding observational equivalence of (finitary) terms of Idealized Algol.
 
@@
   Then, without loss of generality, there is some $\alpha \from \oc(\oc A\implies B) \implies \bC$ such that $\sigma^\dag;\alpha=\skipp$ and $\tau^\dag;\alpha=\bot_{\bC}$.  
-  Then we have some $\s\in\sigma^\dag\|\alpha$ such that $\s\vert_{\bC}=qa$, and $\s\vert_{\oc A \implies B}$ decomposes into `threads' which are plays of $\oc A \implies B$, one for each initial move occurring in that sequence.
+  Therefore we must have some $\s\in\sigma^\dag\|\alpha$ such that $\s\vert_{\bC}=qa$, and $\s\vert_{\oc A \implies B}$ decomposes into `threads' which are plays of $\oc A \implies B$, one for each initial move occurring in that sequence.
   By the well bracketing condition, every one of these threads is itself a complete play in $\oc A \implies B$.  
-  Every one of these sequences is contained in $\sigma$; if they were all contained in $\tau$, then we would have $\s\in\\tau^\dag\|\alpha$, which would be a contradiction, so we end up with a complete sequence contained in $\sigma\setminus\tau$.
-\end{proof}
+  Every one of these sequences is contained in $\sigma$; if they were all contained in $\tau$, then we would have $\s\in\tau^\dag\|\alpha$, which would be a contradiction, so we end up with a complete sequence contained in $\sigma\setminus\tau$.
+\end{proof}
+
+The significance of this result is that it gives us an algorithm for deciding whether two IA terms are observationally equivalent, at least if we pass to a finitary version of IA with only finite datatypes and no recursion other than a primitive for divergence).
+Recall from Section \ref{SecCAnFA} that this was impossible for PCF.

### 2019-09-17 Thesis/intro.tex
Random commit.

@@
 Given two pieces of computer code, in what circumstances can we say that they are interchangeable?
-Clearly, the two pieces of code should return the same output for any choice of input values. 
-But -- depending on the expressive power of the language -- this might not be enough.
+I.e., when can we be absolutely sure that we can replace one with the other and know that the behaviour of the program will not change?
+This is a simple question with a complicated answer.
 
-For example, the following two Haskell functions appear to do the same thing.
+A starting point is to require that the two pieces of code should return the same output for any choice of input values. 
+But that is not necessarily enough.
+For example, the following two Haskell functions appear to do the same thing: indeed, both return $0$, whatever input is passed in.
 
@@
 \end{lstlisting}
-then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: indeed, since \lstinline[language=haskell]{f} always evaluates its argument \lstinline[language=haskell]{n}, \lstinline[language=haskell]{f (diverge 0)} will fail to terminate, whereas \lstinline[language=haskell]{g (diverge 0)} will give us \lstinline[language=haskell]{0}, since inputs to functions are evaluated lazily in Haskell.
+then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: indeed, since Haskell evaluates inputs to functions lazily, evaluating \lstinline[language=haskell]{g (diverge 0)} will not evaluate the non-terminating term \lstinline[language=haskell]{(diverge 0)} and will terminate at the value \listinline[language=haskell]{0}, while \lstinline[language=haskell]{f (diverge 0)} \emph{will} evaluate \lstinline[language=haskell]{(diverge 0)} and will itself fail to converge.
 
-We can have another go at answering our original question, then, by adding the requirement that the two programs should behave in the same way when they are passed non-terminating inputs.
+This is not itself a difficult problem to get around: all we have to do is treat non-termination as a separate input value in itself.
 Thus, we add to each datatype an extra distinguished value $\bot$ representing non-termination (so, for example, the type of integers is represented by the set $\bZ_\bot = \bZ + \{\bot\}$), and then function types are interpreted as functions between these sets -- so a term of type \lstinline[language=haskell]{Int -> Int} is represented by a function $\bZ_\bot \to \bZ_\bot$.
+We can then tell that our functions \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are different, since \lstinline[language=haskell]{g} corresponds to the constant $0$ function $\bZ_\bot \to \bZ_\bot$, while \lstinline[language=haskell]{f} corresponds to the function that sends $n\in \bZ$ to $0$ but sends $\bot$ to $\bot$.
 
-We need to be careful, though, since not every such function arises from a program in this way.
-For example, we cannot write a program corresponding to the function $\chi\from\bZ_\bot \to \bZ_\bot$ that sends $\bot$ to $0$ and all other values to $1$: since $\chi$ is not constant, such a program would have to evaluate its argument, and would consequently fail to terminate if that argument did not terminate.
+Every program gives rise to a function in this way, but not every such function arises from a program.
+For example, we cannot write a program corresponding to the function $\chi\from\bZ_\bot \to \bZ_\bot$ that sends $\bot$ to $0$ and all other values to $1$: since $\chi$ is not constant, such a program would have to evaluate its argument, and would consequently fail to terminate if that argument did not terminate, so it would have to send $\bot$ to $\bot$.
 
@@
 What we have been doing in all these examples is \emph{denotational semantics}: the art of using mathematical objects to study logic and programming languages.  
-In the first case, our denotational semantics was expressed through the mathematics of sets and functions, whereby we captured the behaviour of a (programming language) function via a (mathematical) function.
+In the first case, our denotational semantics was expressed through the mathematics of sets and functions, where we captured the behaviour of a (programming language) function via a (mathematical) function.
 
-Then, following Scott \cite{ScottDomains}, we refine this model to one based on partially-ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.
+Then, following Scott \cite{ScottDomains}, we refined this model to one based on partially-ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.
 
@@
 A word of warning: the principal mode of denotational semantics which we shall be studying in this thesis is game semantics, which is much more complicated than the semantics of sets and functions.
-However, it is still a very valuable tool for determining equivalence of programs.
 
@@
 In order for a denotational semantics to tell us anything, we first need to prove some results that relate it to the language we are studying. 
-For example, if we are hoping to model a programming language with sets and functions, then we need to define a mapping $\deno{-}$ (the \emph{denotation}) that takes program types to sets and program functions to functions between those sets, and we also need to prove that this denotation respects the operational rules of the language: for example, we might want to prove that if $f \from \Int \to \Int$ is a function and $M \from \Int$ is a term that evaluates to the integer $n$, then the term $f M$ will evaluate to the integer $\deno{f}(n)$.
+For example, if we are hoping to model a programming language using sets and functions, then we need to define a mapping $\deno{-}$ (the \emph{denotation}) that takes program types to sets and program functions to functions between those sets, and we also need to prove that this denotation respects the operational rules of the language.
+For example, we might want to prove that if $f \from \Int \to \Int$ is a function and $M \from \Int$ is a term that evaluates to the integer $n$, then the term $f M$ will evaluate to the integer $\deno{f}(n)$.
+
 This type of result is called \emph{Computational Adequacy}, and relates to a program's \emph{observable behaviour}.  
@@
 If we have an effective way of computing denotations, then this can give us an easy way to prove observational equivalence of terms.  
-However, there is no guarantee that we are able to prove observational equivalence this way: the terms $M$ and $N$ might be observationally equivalent despite having distinct denotations.  
+However, it gives no guarantee that this technique is always going to work: the terms $M$ and $N$ might be observationally equivalent despite having distinct denotations.  
 The gold standard of denotational semantics -- \emph{Full Abstraction} -- asserts in addition that the converse of equational soundness holds, so that the denotational semantics completely captures the observational equivalence relation.
-This means that if two terms are observationally equivalent, then we can always prove that they are by showing that they have the same denotation.
+This means that if two terms are observationally equivalent, then we can always prove that they are observationally equivalent by showing that they have the same denotation.
 
@@
 Plotkin was unable to provide a fully abstract denotational semantics for PCF itself, but he showed that if we add a simple parallel construct\footnote{Specifically, `parallel or', which evaluates its two boolean arguments in parallel, and is thus able to return true if either the left or the right argument returns true, even if the other fails to terminate.} to PCF, then a denotational semantics based on Scott domains is fully abstract.
-This astounding result presents us with a world in which we can practically and systematically check observational equivalence (for terms of this extended version of PCF) by computing denotations.  
-This vision is a little rosy-eyed -- deciding observational equivalence is stronger than the halting problem and is hence undecidable in general -- but if the programs in question are finitely presentable in some sense, then we really can use the denotational semantics to check observational equivalence.
+This result presents us with a world in which we can practically and systematically check observational equivalence (for terms of this extended version of PCF) by computing denotations.  
+If two term displays infinitary behaviour, then it is not necessarily possible to check whether their denotations are equal, but if they are finitely presentable in some sense, so that their denotations as functions between Scott domains can be computed and compared, then the Full Abstraction result gives us, at least in principle, a systematic recipe for checking observational equivalence.
 
-Unfortunately, this stops working for PCF itself.  
-PCF is a sub-language of the parallelized version, but this also means that the observational equivalence relation is coarser: there may be terms that can be distinguished by a context including the parallel construct that cannot be distinguished inside any purely sequential context.
-The enterprise was brought down to earth by Ralph Loader's 2001 theorem that observational equivalence for PCF is undecidable, even if we restrict ourselves to a finitary version of the language with no infinite datatypes or recursion beyond a simple non-termination primitive $\bot$.
-This in particular tells us that no concretely presentable denotational semantics for PCF can possibly be fully abstract, or it would give us an algorithm for deciding observational equivalence in this finite version.
+Unfortunately, this stops working once we remove the extra parallel construct.
+PCF is a sub-language of the parallelized version, and therefore can also be given a denotational semantics via Scott domains, but the absence of parallelism also means that the observational equivalence relation is coarser: there may be terms that can be distinguished by a context including the parallel construct that cannot be distinguished inside any purely sequential context.
+This means that the Full Abstraction result does not automatically pass over to sequential PCF.
 
-Nevertheless there were, roughly contemporaneous with Loader's result, several fully abstract models of PCF published, in a watershed moment for the subject.
+Any hope of solving the problem with a tweaked model was brought down to earth by Ralph Loader's 2001 theorem that observational equivalence for PCF is undecidable, even if we restrict ourselves to a finitary version of the language with no infinite datatypes or recursion beyond a simple non-termination primitive $\bot$.
+This in particular tells us that no concretely presentable denotational semantics for PCF can possibly be fully abstract, or it would in principle give us an algorithm for deciding observational equivalence in this finite version.
+
+Despite this fact, there were, roughly contemporaneous with Loader's result, several fully abstract models of PCF published, in a watershed moment for the subject.
 The model published by O'Hearn and Riecke \cite{OHearnRieckePcf} was more or less along domain-theoretic lines, while those of Abramsky, Jagadeesan and Malacaria \cite{ajmPcf}, Hyland and Ong \cite{hoPcf}, and Nickau \cite{NickauPcf} used the relatively new Game Semantics.
 
-These models took a slightly oblique approach to Full Abstraction.  
+These models took a slightly oblique approach to Full Abstraction, which is how they reconcile themselves with Loader's Theorem.
 First, they defined the notion of \emph{intrinsic equivalence} of terms of the same type $T$ in a denotational model, where two elements $\sigma$ and $\tau$ of the denotation of $T$ are intrinsically equivalent if $\alpha(\sigma)=\alpha(\tau)$ for all functions $\alpha\from\deno{T}\to\deno{o}$ from the denotation of $T$ to the denotation of some fixed ground type $o$.
@@
 Under mild continuity assumptions, this suffices to prove Full Abstraction, for we can then deduce that if $\alpha(\sigma)\ne \alpha(\tau)$ for some $\alpha$, then there is some definable $\alpha'$ such that $\alpha'(\sigma)\ne\alpha'(\tau)$.
+This is the approach taken by the fully abstract semantics that have been given for PCF; there is no contradiction of Loader's theorem, because the intrinsic equivalence relation is itself undecidable, even for finitary terms.
 
 If we can prove, for some denotational model of a language, that observational equivalence of terms is equivalent to intrinsic equivalence of their denotations, then we can form a fully abstract model by passing to equivalence classes under the intrinsic equivalence relation.
-This is the approach taken by the fully abstract semantics that have been given for PCF; there is no contradiction of Loader's theorem, because the intrinsic equivalence relation is itself undecidable.
-
 In this thesis, we shall skip the final step of passing to equivalence classes and declare a denotational semantics to be fully abstract for a language if we can prove that observational equivalence of terms is equivalent to intrinsic equivalence of their denotations.
@@
 
-The power of game semantics comes from the fact, first noted in \cite{blassgames} by Blass, that certain natural operations on games correspond to some of the connectives of linear logic.  
+The power of game semantics comes from the fact, first noted by Blass in \cite{blassgames}, that certain natural operations on games correspond to some of the connectives of linear logic.  
 For example, if $A$ and $B$ are two-player games, then we may form their \emph{tensor product} $A\tensor B$, which is played by running the games $A$ and $B$ together in parallel, with the opposing player $O$ allowed to switch between games when it is his turn.
@@
 
-Harmer and McCusker develop in \cite{mcCHFiniteND} a model of game semantics in which strategies can be nondeterministic.  
+Similarly, Harmer and McCusker develop in \cite{mcCHFiniteND} a model of game semantics in which strategies can be nondeterministic.  
 They show that every such strategy can be written as the composite of a deterministic strategy with some particular fixed nondeterministic strategy.  
@@
 
-Aside from the proofs of Full Abstraction for stateful and nondeterministic languages that we have mentioned \cite{SamsonGuyIAActive,mcCHFiniteND}, other important Full Abstraction results in Game Semantics that follow this pattern include Danos and Harmer's result for a probabilistic variant of Idealized Algol \cite{DanosHarmer}, the Full Abstraction result for general references of Abramsky, Honda and McCusker \cite{HondaMcCusker}, Laird's result for local exceptions \cite{LLi}, Murawski and Tzevelekos's Nominal Game Semantics \cite{NGS} and the result for countable nondeterminism by Laird and the present author \cite{CslPaper}.
+The proofs of Full Abstraction for stateful and nondeterministic languages that we have mentioned \cite{SamsonGuyIAActive,mcCHFiniteND} prove Full Abstraction in this way.  
+Other important Full Abstraction results in Game Semantics that follow this pattern include Danos and Harmer's result for a probabilistic variant of Idealized Algol \cite{DanosHarmer}, the Full Abstraction result for general references of Abramsky, Honda and McCusker \cite{HondaMcCusker}, Laird's result for local exceptions \cite{LLi}, Murawski and Tzevelekos's Nominal Game Semantics \cite{NGS} and the result for countable nondeterminism by Laird and the present author \cite{CslPaper}.
 
-It is also worth mentioning several papers that prove Full Abstraction directly, rather than through a factorization result, usually because they depart more radically from traditional game semantics.
+Lastly, it is worth mentioning several papers that prove Full Abstraction without going through a factorization result.  
+This is usually because they depart more radically from traditional game semantics.  
 Such papers include Tsukada and Ong's sheaf-based models for nondeterministic PCF \cite{TsukadaSheaves,Sheaves}, Laird's categorical semantics for coroutines \cite{FunctionalProgramsAsCoroutines} and the results for probabilistic PCF by Castellan, Clairambault, Paquet and Winskel using concurrent games \cite{PPCF}.
@@
 For instance, it seems obvious that if we want to model a nondeterministic programming language, then we need to relax the determinism constraint on strategies.  
-However, this turns out not to be enough on its own: recall that we model a nonterminating computation in game semantics by a strategy that has no $P$-reply to a particular $O$-move.  
+However, relaxing the determinism constraint turns out not to be enough on its own: recall that we model a nonterminating computation in game semantics by a strategy that has no $P$-reply to a particular $O$-move.
 How then do we model a term which chooses between terminating at a value $v$ and not terminating, and how do we distinguish it from a term which always terminates at $v$?  
@@
 Naively relaxing the determinism constraint on the usual definition of an innocent strategy does not give the right notion of a nondeterministic innocent strategy \cite{TsukadaSheaves}.  
-There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, toTsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper on deterministic innocence.
-Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we add nondeterminism to innocence.
+There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, toTsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper that introduced deterministic innocent strategies.
+Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we try to mix nondeterminism and innocence.
 
+This is just one example that shows that the process of adding different computational effects into a game semantics can be very hard and can require some ingenuity.
 Meanwhile, there is plenty of well-known theory that deals with computational effects in a purely systematic way.  
@@
 This thesis will focus on nondeterministic effects.  
-Of these, perhaps the trickiest to work with is countable nondeterminism, in which a program can nondeterministically choose between a possibly infinite number of different options, without the possibility of non-termination\footnote{If we have a source of finite nondeterminism, then we can get infinite branching if we accept the possibility that our program might never terminate -- for example, count the number of coin tosses it takes before we get the first head.}
+Of these, perhaps the trickiest to work with is countable nondeterminism, in which a program can nondeterministically choose between a possibly infinite number of different options, without the possibility of non-termination\footnote{If we have a source of finite nondeterminism, then we can get infinite branching if we accept the possibility that our program might never terminate -- for example, count the number of coin tosses it takes before we get the first head.}.
 
 There are three main difficulties when dealing with countable nondeterminism in game semantics.  
-The first we have covered in the previous section: we cannot tell everything about a program's behaviour by looking at its possible finite traces, even when the traces are allowed to be arbitrarily long, as in the example where a program nondeterministically chooses a number $n$ and prints out a message $n$ times vs the program which may print out the message infinitely many times.
+We have covered the first in the previous section: we cannot tell everything about a program's behaviour by looking at its possible finite traces, even when the traces are allowed to be arbitrarily long, as in the example where a program nondeterministically chooses a number $n$ and prints out a message $n$ times vs the program which may print out the message infinitely many times.
 
@@
 
-This is related to the second problem, which is the failure of continuity of composition, as noticed by Dijkstra in \cite[Ch.~9]{DijkstraBook} and later studied by Plotkin and Apt in \cite{PlotkinApt}.
-In order to talk about continuity, we define the \emph{observational preorder} on terms of a language.  
+Related is second problem, which is the failure of continuity of composition.  
+This was noticed by Dijkstra in \cite[Ch.~9]{DijkstraBook} and later studied by Plotkin and Apt in \cite{PlotkinApt}.
+
+In order to explain what we mean by continuity, we define the \emph{observational preorder} on terms of a language.  
 If $M,N\from T$, we write $M\lesssim N$ if for all ground-type contexts $C[-]$ with a hole of type $T$ we have
@@
 
-Continuity of composition says that least upper bounds with respect to this order are preserved by function application.  
-Consider, for example, the terms $\le_m \from \bN \to \bN$ for $m=0,1,\dots$ that return $0$ if their argument is less than or equal to $m$ and go into an infinite loop otherwise.
-It is fairly clear (with a straightforward rigorous proof once we have introduced the denotational semantics) that a least upper bound for the $\le_m$ is the term $\le_\infty$ that evaluates its argument and then returns $0$ regardless of what value it finds\footnote{$\le_\infty$ differs slightly from $\lambda n.0$ -- also an upper bound for the $\le_m$, but not the least upper bound -- in that it will fail to terminate if its argument fails to terminate}.
+Continuity of composition means that least upper bounds with respect to this order are preserved by function application.  
+Consider, for example, the infinite sequence of terms $\le_m \from \bN \to \bN$ for $m=0,1,\dots$ that return $0$ if their argument is less than or equal to $m$ and go into an infinite loop otherwise.
+It is fairly clear (with a straightforward rigorous proof once we have introduced the denotational semantics) that a least upper bound for the $\le_m$ is the term $\le_\infty$ that evaluates its argument and then returns $0$ regardless of what value it finds\footnote{$\le_\infty$ differs slightly from $\lambda n.0$ -- also an upper bound for the $\le_m$, but not the least upper bound -- in that it evaluates its argument before returning $0$.
+This means that it will fail to terminate if its argument fails to terminate.}.
 
@@
 Then the terms $\le_m ?$ are all observationally equivalent: they either return $0$ (when $?$ returns a number less than or equal to $m$), or fail to terminate (when $?$ returns a number greater than $m$).
-Therefore, $\le_m?$ is a constant sequence and its least upper bound is that constant value, which we can write as
+We might write
 \[
-  0+\Omega\,.
+  \le_m ? = 0 + \Omega\,.
   \]
+Therefore, the sequence $\le_m?$ is a constant sequence and its least upper bound is that constant value $0+\Omega$.
+
 Meanwhile, $\le_\infty?$ always returns $0$.  
-So application to $?$ does not preserve least upper bounds.
+Therefore, application to $?$ does not preserve least upper bounds.
 
@@
 The standard adequacy proof uses continuity of composition in the model in an essential way -- see Lemma \ref{LemAdequacyLimits} for an example of such an argument being used to prove computational adequacy for a deterministic language.
-But if the ordering of morphisms in a denotational model of a language with countable nondeterminism faithfully respects the observational ordering of terms, then it will not have the continuity properties that we need for this proof.
+But if the ordering of morphisms in a denotational model of a language with countable nondeterminism faithfully respects the observational ordering of terms, then composition of morphisms is necessarily not continuous -- since it is not continuous in the language itself.
 
@@
 Given a term $P$ of ground type, we write $P\converges_u$ if $P$ terminates whenever it prints the sequence $u$ to the log.  
-Then, if we modify our definition of observational equivalence to say that $M\lesssim N$ if for all suitable contexts $C[-]$ we have
+We then replace our earlier definition of the observational preorder with a stronger one: we write that $M\lesssim N$ if for all suitable contexts $C[-]$ we have
 \[
-  C[M] \converges_u \mathrel{\Rightarrow C[N]} \converges_u\,,
+  C[M] \converges_u \mathrel{\Rightarrow C[N]} \converges_u\,.
   \]
-then this ordering will be continuous.  
-For example, this extra requirement wrecks our previous example of failure of continuity of composition.  
+This ordering on terms is continuous.
+For example, the extra requirement wrecks our previous example of failure of continuity of composition.  
 Indeed, the sequence $\le_m ?$ is no longer constant, since, for example, $\le_5 ?$ does not terminate if it prints $6$ to the log, whereas $\le_{1000} ?$ does.
@@
 
-Having proved computational adequacy for this new language, we then use operational methods to find a way to identify terms that should be observationally equivalent in the original sense.  
-We form a model for the language with countable nondeterminism by taking our model for the new language and taking the quotient by an appropriate equivalence relation on morphisms.
+We can prove continuoity of composition in general for the new language, which allows us to prove computational adequacy in the usual way.
+Having done this, we then use operational methods to find a way to identify terms that should be observationally equivalent in the original sense.  
+This allows us to quotient out our model for the new language to get one that is computationally adequate for the ordinary nondeterministic version.
 
-In order to introduce the last problem that we face with countable nondeterminism, we note that there are two different reasons why an element of a denotational model (e.g., a strategy) might not be definable in a particular language.
+The last problem is to do with definability.
+First note that there are two different reasons why an element of a denotational model (e.g., a strategy) might not be definable in a particular language.  
 One reason is structural: for example, a stateless language such as PCF cannot define a strategy whose behaviour depends on its entire history, since that would indicate stateful behaviour.  
 The other reason is purely computational.  
-Given a non-computable function $f\from \bN \to \bN$ (for example, the function that returns $0$ if its argument is source code for a terminating program an $1$ otherwise), we have a perfectly well-behaved history free strategy that represents $f$, but it is nevertheless still not definable in most programming languages.
-Historically, the study of Full Abstraction has not been too concerned with non-definable elements of the second kind: the reason is that they do not usually play a role in determining the intrinsic equivalence relation, since such a strategy is necessarily not compact.
-However, in the presence of countable nondeterminism, there exist terms that can be distinguished in the model that cannot be distinguished by compact elements; indeed, we can use a diagonal argument to define two functions $(\bN \to \bN) \to \bN$ that are distinguished only by non-computable functions $\bN \to \bN$.
+Given a non-computable function $f\from \bN \to \bN$ (for example, the function that returns $0$ if its argument is source code for a terminating program and $1$ otherwise), we have a perfectly well-behaved history free strategy that represents $f$, but $f$ is nevertheless still not definable in most programming languages.
+Historically, the study of Full Abstraction has not been too concerned with non-definable elements of the second kind: the reason is that they do not usually play a role in determining the intrinsic equivalence relation.
+However, in the presence of countable nondeterminism, there exist definable terms that can be distinguished in the model that cannot be distinguished by definable elements, but can be distinguished by non-computable functions.
 An example of such a function is found in Proposition \ref{PropNotFullyAbstract}; the general idea is due to Kleene and can be found in \cite{KleeneTree}.
 
-What this means is that if we want to model countable nondeterminism then, in addition to the usual structural constraints on strategies relating to the effectful behaviour available in our language, we also need to impose computability constraints that say that our strategies can in some sense be defined using a computable function.
+What this means is that if we want to model countable nondeterminism then structural constraints are not enough: we need to impose computability constraints on strategies as well.
 Happily, such notions are well studied already, even appearing in the original Hyland-Ong and AJM papers \cite{hoPcf,ajmPcf}, in which the authors give a complete characterization of those strategies definable in PCF -- a \emph{universality} result for the model.
@@
     All subsequent results will be for extended versions of Idealized Algol, so this model can serve as the foundation for the rest of our work.  
-    Although these chapters form by some distance the longest part of the thesis, they also contain the smallest amount of new material, and owe much to Abramsky and McCusker's Fully Abstract game semantics for Idealized Algol \cite{SamsonGuyIAActive}.
+    Although these chapters form by some distance the longest part of the thesis, they also contain the smallest amount of new material, and essentially cover the same material as Abramsky and McCusker's Fully Abstract game semantics for Idealized Algol \cite{SamsonGuyIAActive}.
     The main difference, which ties in with the general theme of the thesis, is that we prove Computational Adequacy using techniques of categorical algebra rather than via the ad hoc combinatorial arguments found in \cite{SamsonGuyIAActive}.
-    Specifically, we use Laird's concept of a \emph{sequoidal category} and of the exponential as a final coalgebra, used to prove Full Abstraction for a language with general references \cite{laird02}.
+    Specifically, we use the concept of a \emph{sequoidal category} and of the exponential as a final coalgebra, introduced by Laird in \cite{laird02} to prove Full Abstraction for a language with general references.
     We present the first application of this technique to a language with purely local state of ground type.
@@
   \item[Chapter \ref{ChapPromonads}] takes a small detour away from the main narrative to study the \Mellies category from the point of view of profunctors.
-  \item[Chapter \ref{ChapParametricMonadsFullAbstraction}] completes our study of parametric monads by proving a Full Abstraction result for a probabilistic language for a category derived from a particular parametric monad, using similar techniques to Chapter \ref{ChapMonads}.
+  \item[Chapter \ref{ChapParametricMonadsFullAbstraction}] completes our study of parametric monads by proving a Full Abstraction result for categories derived from \Mellies categories, using similar techniques to Chapter \ref{ChapMonads}.
+    As an example, we give a semantics for a probabilistic language for a category derived from a particular parametric monad, and show that it is Fully Abstract.
 \end{description}

### 2019-09-17 Thesis/pmonads.tex
Random commit.

@@
 \end{mathpar}
-Since lax actions generalize monads, we shall follow \Mellies \cite{ParametricMonads} and refer to them as \emph{parametric monads}.
+Since lax actions generalize monads, we shall sometimes follow \Mellies \cite{ParametricMonads} and refer to them as \emph{parametric monads}.
+We shall not be considering strong actions (for which $m,e$ are required to be isomorphisms), so we shall sometimes say `action' to mean `lax action'.
 
@@
     \]
-  given by
+  given by the coend
   \[
@@
   \end{IEEEeqnarray*}
-  where the arrow is induced by the \Mellies composition $\C(a,y.b) \times \C(b,z.c) \to \C(a,(y\tensor z).c)$.
+  where the arrow on the third line is induced by the \Mellies composition $\C(a,y.b) \times \C(b,z.c) \to \C(a,(y\tensor z).c)$.
 
@@
 We will mainly be concerned not with the \Mellies category itself, but with a closely related ordinary category.  
-The usual method for turning a $\V$-enriched category into an ordinary category is via base change along a monoidal functor $\V \to \Set$: for example, any $\V$-enriched category has an \emph{underlying ordinary category}, obtained via base change along the functor $\V(I, \blank)$.
-For example, if $a$ and $b$ are objects of the base category $\C$, then the set of morphisms in the underlying ordinary category of the \Mellies category is the set of natural transformations
+The usual method for turning a $\V$-enriched category into an ordinary category is via base change along a monoidal functor $\V \to \Set$.
+
+For example, any $\V$-enriched category has an \emph{underlying ordinary category}, obtained via base change along the functor $\V(I, \blank)$.  
+If $a$ and $b$ are objects of the base category $\C$, then the set of morphisms in the underlying ordinary category of the \Mellies category is the set of natural transformations
 \[
@@
 
-This is not very useful for us, since it ignores most of the action and does not give us any new theory beyond the basic theory of monads and Kleisli categories.  
-We want a monoidal functor $[\M,\Set]\to\M$ that will preserve more of the structure.
-
+More generally, if $m\tensor m\to m$ is a monoid in $\X$, then we can construct a lax monoidal functor $[\X,\Set] \to \Set$ that sends $F$ to $F(m)$.  
+If we change base through this functor, then the morphisms $a \to b$ in the resulting ordinary category will be elements of $\C(a,m.b)$; i.e., morphisms $a \to m.b$ in $\C$, and the category turns out to be the Kleisli category corresponding to the monad on $\C$ given by $Ma = m.a$.
+So the \Mellies category can be thought of as classifying all the Kleisli categories that arise from the action $\blank.\blank$ through the monoids in $\M$.
+
+For our purposes, however, we will want to use a single ordinary category that captures as much as possible of the structure of the \Mellies category.
 Let us assume for now that $\X$ is a small category.  
@@
 
-Moreover, this functor is lax monoidal, via the morphisms
+Moreover, this functor is lax monoidal, via the multiplicative
 \begin{IEEEeqnarray*}{Cl}
@@
 \end{IEEEeqnarray*}
-(where the second morphism sends picks out the inhabitant $\inj_{y\tensor z}(\id_{y\tensor z})$ of $\colim_{x\from \X}\X(y\tensor z,x)$)
-and
+(where the second morphism sends picks out the inhabitant $\inj_{y\tensor z}(\id_{y\tensor z})$ of $\colim_{x\from \X}\X(y\tensor z,x)$),
+and via the unital
 \begin{IEEEeqnarray*}{cCc}
@@
 
-Rather than pursue this line of argument to its conclusion, though, we choose to define the base-changed category directly.
+We then conclude by changing base through this colimit functor.  
+It turns out to be fairly easy to describe the resulting category directly.
 
@@
   \begin{itemize}
-    \item the objects are the objects of $\C$,
+    \item the objects are the objects of $\C$;
     \item given objects $a,b$ of $\C$, the set of morphisms $a \to b$ is given by the colimit
@@
         \]
-    \item composition of morphisms is via the \Mellies composition of Definition \ref{DefMelliesComposition} and
+    \item composition of morphisms is via the \Mellies composition of Definition \ref{DefMelliesComposition}; and
     \item the identity $a\to a$ is given by the equivalence class corresponding to the morphism
@@
   \end{gather*}
-  are \Mellies morphisms, and that there are morphisms $h \from x \to x'$, $k \from y \to y'$ in $\X$ such that the following diagrams commute.
+  are \Mellies morphisms, and that $f$ is equivalent to $f'$ and $g$ is equivalent to $g'$.  
+  By induction, we can assume that $f,f'$ and $g,g'$ are related by the relation that generates the equivalence relation on \Mellies morphisms, so that there are morphisms $h \from x \to x'$, $k \from y \to y'$ in $\X$ such that the following diagrams commute.
   \begin{mathpar}
@@
     \]
-  Here, the pentagon at the right is one of our conditions for a lax action, while the left-hand square commutes because $m$ is a natural transformation.  
+  Here, the pentagon at the right is one of the coherence diagrams for a lax action, while the left-hand square commutes because $m$ is a natural transformation.  
   The composite given by the thick dashed lines is the \Mellies composition $f;(g;h)$, while that given by thin lines is the \Mellies composition $(f;g);h$.  
-  The arrow $\assoc_{x,y,z}$ in $\X$ then mediates between these morphisms, so they are equivalent.
+  The arrow $\assoc_{x,y,z}$ in $\X$ then mediates between these morphisms, so they are equivalent, and therefore correspond to the same morphism in $\C/\X$.
 
@@
   This generalizes the Kleisli category of a monad.  
-  Indeed, if $M$ is a monad on $\C$, then we may consider $M$ as a lax action of the unit category on $\C$.
+  Indeed, if $M$ is a monad on $\C$, then we may consider $M$ as a lax action of the unit category $1$ on $\C$.
   Then composition of morphisms $f \from a \to I.b$, $g \from b \to I.c$ in the category $\C/1$ is given by
@@
     \]
-  Identifying $I.\blank$ with $M$, we see that this is precisely the definition of composition in the Kleisli category for $M$ (and the identity is the same thing too).  
-  Since the unit category has only an identity morphism, the equivalence relation on morphisms in $\C/1$ is discrete, which is why we do not need to mention it in this context.
+  Writing $M$ for $I.\blank$, we see that this is precisely the definition of composition in the Kleisli category for $M$ (and the identity is the same thing too).  
+  Note that since the unit category has only an identity morphism, the equivalence relation on morphisms in $\C/1$ is discrete, so $\C/1$ \emph{is} the Kleisli category for $M$.
 \end{remark}
@@
   \]
-It is easy to show that this is a functor, and we will prove this in a more general context in Proposition \ref{PropGrotLaxLimit}.
+It is easy to show that this is a functor, and we will prove that it is in a more general context in Proposition \ref{PropGrotLaxLimit}.
 
@@
 considered as \Mellies morphisms $x.a \to a$.  
-We will see later that these are the components of a natural transformation $\phi_{x,a}\from x.a \to a$ in $\C/\X$, generalizing the natural transformation $\phi_a \from Ma \to a$ in the Kleisli category for a monad $M$ (see Proposition \ref{pKleisli}).
-
-We will be using the following `factorization result'.  
+We will see later that these are the components of a natural transformation $\phi_{x,a}\from x.a \to a$ in $\C/\X$, generalizing the natural transformation $\phi_a \from Ma \to a$ in the Kleisli category for a monad $M$ that we met in Proposition \ref{pKleisli}.
+
+We will be meeting the following `factorization result', analogous to the corresponding result for Kleisli categories that we met in the previous section.
 If $f \from a \to x.b$ is a morphism in $\C$ then the corresponding \Mellies morphism $a \to b$ may be written as the following composite in $\C/\X$.
@@
 In this chapter, we will show that $\C/\X$ has important properties in its own right: namely that it is a certain lax $2$-colimit in $\Cat$.  
-We will briefly return to the \Mellies category in chapter \ref{ChapPromonads}, when we will show why it is a natural idea to consider an $[\X,\Set]$-enriched category.
+We will briefly return to the \Mellies category in chapter \ref{ChapPromonads}, when we will approach it from the point of view of profunctors.
 
@@
   If $\C = \BB \X$, $\D = \BB \YY$ are the delooping bicategories of monoidal categories $\X, \YY$ -- i.e., $\X$ and $\YY$ considered as bicategories with a single object -- then a lax functor $\C \to \D$ is the same thing as a lax monoidal functor $\X \to \YY$.
-
+\end{example}
+
+\begin{example}
   More generally, a lax functor $F\from \BB \X \to \D$ is the same as a lax monoidal functor from $\X$ to the monoidal category of $1$-cells $F(*) \to F(*)$, where $*$ is the unique object of $\BB\X$.
@@
   The definition of a lax colimit is normally weaker than the one we have given, in that the equations $k_c;\hat l = l_c$ and $\nu_h\hat l = \mu_h$ are not required to hold exactly, but instead up to coherent isomorphism.
-  For the lax functors we are constructing, however, we will be able to construct lax colimits that make these equations hold exactly.
+  The distinction is not important for our purposes, since the lax colimits we will be considering will all satisfy our stronger definition.
 \end{remark}
+
+We shall sometimes write
+\[
+  \laxcolim_{c \from \C}F(c)
+  \]
+for the lax colimit of the functor $F$.
 
@@
 
-  Preservation of composition and identities is via the usual technique: if we have oplax natural transformations $t\from F \Rightarrow G$ and $t' \from G \Rightarrow H$, then the composite of the induced lax functors $\tilde{F} \to \tilde{G}$ and $\tilde{G}\to \tilde{H}$ satisfies the same property that uniquely defines the lax functor $\tilde{F} \to \tilde{H}$ induced from the composite of $t$ and $t'$.
+  We can prove that this procedure preserves composition and identities via the usual technique: if we have oplax natural transformations $t\from F \Rightarrow G$ and $t' \from G \Rightarrow H$, then the composite of the induced lax functors $\tilde{F} \to \tilde{G}$ and $\tilde{G}\to \tilde{H}$ satisfies the same property that uniquely defines the lax functor $\tilde{F} \to \tilde{H}$ induced from the composite of $t$ and $t'$.
 \end{proof}
@@
   \begin{itemize}
-    \item the objects are pairs $(a, m)$, where $a$ is an object of $\C$ and $m$ an object of $F(a)$,
-    \item the $1$-cells $(a, m) \to (b, n)$ are pairs $(h, f)$, where $h$ is a morphism $b \to a$ and $f$ is a morphism $m \to F(h)(n)$ and
+    \item the objects of $\int F$ are pairs $(a, m)$, where $a$ is an object of $\C$ and $m$ an object of $F(a)$;
+    \item the $1$-cells $(a, m) \to (b, n)$ are pairs $(h, f)$, where $h$ is a morphism $b \to a$ and $f$ is a morphism $m \to F(h)(n)$; and
     \item the $2$-cells $(h, f) \Rightarrow (k, g) \from (a,m) \to (b,n)$ are $2$-cells $\phi\from h \Rightarrow k$ in $\C$ that make the following diagram commute.
@@
 \begin{remark}
-  For the Grothendieck construction see \cite[VI.8]{SGA1} and \cite[B1.3.1]{Elephant} -- in the original formulation, the category $F$ is a pseudofunctor $\C \to \Cat$ (i.e., a lax functor where the coherences $m$ and $e$ are isomorphisms), where $\C$ is an ordinary category -- then $\int F$ is an ordinary category.
+  For the Grothendieck construction see \cite[VI.8]{SGA1} and \cite[B1.3.1]{Elephant} -- in the original formulation, the category $F$ is a pseudofunctor $\C \to \Cat$ (i.e., a lax functor where the coherences $m$ and $e$ are isomorphisms), where $\C$ is an ordinary category -- then $\int F$ contains only identity $2$-cells, so we can consider it as an ordinary category as well.
   For the version where $\C$ is an arbitrary bicategory (and $\int F$ is a bicategory), see \cite{FibrationsInBicategories}.
@@
   First, we define the lax cocone under $F$ with tip $\pi_*\int F$.
-  Given an object $a$ of $\C$, we have a functor $k_a \from F(a) \to \pi_*\int F$ given by
+  Given an object $a$ of $\C$, the arrow from $F(a)$ to $\pi_*F\int F$ is the functor $k$ defined by
   \begin{mathpar}
@@
   Let $m\xrightarrow{f}n\xrightarrow{g}p$ be morphisms in $F(a)$.  
-  We need to show that $k_a(f);k_a(g) = k_a(f;g)$ in $\pi_*\int F$, for which it suffices to exhibit a $2$-cell in $\int F$ mediating between these two $1$-cells, and indeed such a $2$-cell is given by $\lunit_{\id_a}\from \id_a \to \id_a;\id_a$ (see Figure \ref{FigKaFG=KaFKaG}).
+  We need to show that $k_a(f);k_a(g) = k_a(f;g)$ in $\pi_*\int F$, for which it suffices to exhibit a $2$-cell in $\int F$ mediating between these two $1$-cells.  
+  Indeed, such a $2$-cell is given by $\lunit_{\id_a}\from \id_a \to \id_a;\id_a$ (see Figure \ref{FigKaFG=KaFKaG}).
   \begin{figure}
@@
     \]
-  Since the arrow along the top is given by the identity on $F(h')(m)$, it will suffice to show that the arrow along the bottom is of the form $F(\psi)_m$, for some $2$-cell $\psi$ in $\C$, and is therefore equal to the identity in $\pi_*\int F$.
+  Since the arrow along the top is given by the identity on $F(h')(m)$, it will suffice to show that the arrow along the bottom is of the form $F(\psi)_m$, for some $2$-cell $\psi$ in $\C$, and that it is therefore equal to the identity in $\pi_*\int F$.
   Indeed, writing this composite out in full, we get
@@
   Now, suppose that $(\D,l,\mu)$ is another lax cocone under $F$.  
-  We define a functor $\hat{l}$ from $\pi_*\int F$ to $\D$ by
+  We define
   \begin{mathpar}
@@
   \end{mathpar}
-  We need to show that $\hat{l}$ is a functor.  
+  We need to show that $\hat{l}$ is a functor $\pi_*\int F \to \D$.
   First, observe that it sends the identity on $(a,m)$ to the composite
@@
   Using the formula for the composition of morphisms in the Grothendieck construction, we see that $\hat{l}((h,f);(k;g))$ is given by the thick dotted composite in Figure \ref{FigLHatFunctor}, while $\hat{l}(h,f);\hat{l}(k,g)$ is given by the thin composite.
-  Therefore, these two are equal.
+  We can deal with the identity in a similar way.
+  Therefore, $\hat{l}$ is a functor.  
   \begin{figure}
@@
 
-  Therefore, $\hat{l}$ is a functor.  
   Moreover, if $a$ is an object of $\C$ and $m$ and object of $F(a)$, we have $\hat{l}(k_a(m))=\hat{l}(a,m)=l_a(m)$, and if $f\from m \to n$ is a morphism in $F(a)$, then $\hat{l}(k_a(f))$ is given by the composite
@@
 
-  Lastly, if $h\from a \to b$ is a morphism in $\C$, then $\hat{l}((\nu_h)_m)=\hat{l}(h,\id_{F(h)(m)}) = (\mu_h)_m$, and so $\nu_hl = \mu_h$.  
+  Lastly, if $h\from a \to b$ is a morphism in $\C$, then 
+  \[
+    \hat{l}((\nu_h)_m)=\hat{l}(h,\id_{F(h)(m)}) = (\mu_h)_m\,,
+    \]
+  and so $\nu_hl = \mu_h$.  
   This completes the existence part of the proof.
@@
 
-If we apply the Grothendieck construction to $F$, then the category we get has pairs $(*,a)$ for objects, where $a$ ranges over the objects of $\C$, and the morphisms from $(*,a)$ to $(*,b)$ are morphisms $a \to F(\id)(b)$ in $\C$, where $F(\id)=M$.
+If we apply the Grothendieck construction to $F$, then the category we get has pairs $(*,a)$ for objects, where $a$ ranges over the objects of $\C$; and the morphisms from $(*,a)$ to $(*,b)$ are morphisms $a \to F(\id)(b)$ in $\C$, where $F(\id)=M$.
 In other words, $\int F$ is precisely the Kleisli category for $M$.
@@
 
-This is significant, because it tells us that the category $\C/\X$ always satisfies a `factorization result' akin to those in \cite{SamsonGuyIAActive} (our Proposition \ref{PropInnocentFactorization}) and \cite{mcCHFiniteND}: if $f \from a \to b$ is a morphism in $\C/\X$, given by some morphism $\tilde{f}\from a \to x.b$ in $\C$, then we may write $f$ as the composite
+In this special case, the proof of Proposition \ref{PropGrotLaxLimit} tells us that $\C/\X$ always satisfies a `factorization result' akin to those in \cite{SamsonGuyIAActive} (our Proposition \ref{PropInnocentFactorization}) and \cite{mcCHFiniteND}: if $f \from a \to b$ is a morphism in $\C/\X$, given by some morphism $\tilde{f}\from a \to x.b$ in $\C$, then we may write $f$ as the composite
 \[
@@
 This means that if we have a definability result for the category $\C$ -- for example, that every compact morphism in $\C$ is definable in some language $\L$ -- then we can automatically get a definability result for the category $\C/\X$ -- for example, that every compact morphism in $\C/\X$ (i.e., every morphism $a\to b$ in $\C/\X$ that is given by a compact morphism $a \to x.b$ in $\C$) is definable in the language $\L + \Phi_{x,a}$, where $\Phi_{x,a}$ is a new family of primitives in the language whose denotations are given by the $\phi_{x,a}$.
-This is the same purpose that we used Proposition \ref{pKleisli} for when proving Theorem \ref{TheKleisliFullAbstraction}.
+
+In the case that $\X=1$ and the action is a monad, this factorization result is Proposition \ref{pKleisli}, which played an important role in our main Full Abstraction result (Theorem \ref{TheKleisliFullAbstraction}).
+We shall use our new factorization result to prove a Full Abstraction result in a similar way.
 
@@
 
-The next result mirrors the result for distributivity of finite products over arbitrary colimits in a Cartesian closed category (essentially because the functor $A \times \blank$ is a left adjoint, so preserves colimits).
+The next result mirrors the result for distributivity of finite products over arbitrary colimits in a Cartesian closed category (which is essentially because the functor $A \times \blank$ is a left adjoint, so preserves colimits).
 
@@
 
-  We say that the action of $\X$ on $\C$ is \emph{monoidal} if, in addition to the underlying functor $\X \times \C \to \C$ being monoidal, the natural transformations $m_{x,y,a}$ and $e_a$ are monoidal natural transformations.
+  We say that the action of $\X$ on $\C$ is \emph{monoidal} if the underlying functor $\X \times \C \to \C$ is a lax monoidal functor and the natural transformations $m_{x,y,a}$ and $e_a$ are monoidal natural transformations.
   \label{DefMonoidalLaxAction}
@@
   However, although a monoidal monad can be defined to be a monoid in the category of monoidal functors $\C \to \C$ and monoidal natural transformations between them, a monoidal parametric monad parameterized by a symmetric monoidal category $\X$ cannot be defined as a monoidal functor from $\X$ into this category.
-  Indeed, that would mean we had a natural transformation
+  Indeed, that would mean we had, \emph{inter alia}, a natural transformation
   \[
@@
   By taking the product of the action with itself, we get an action of $\X\times\X$ on $\C\times\C$; i.e., the action given by $(x,y).(a,b)=(x.a,y.b)$.  
-  Since $\X$ is symmetric monoidal, the tensor product functor $\X\times\X \to \X$ is strong monoidal, so by composing it with the action of $\X$ on $\C$ we get a lax action of $\X\times\X$ on $\C$; i.e., the action given by $(x,y).a = (x\tensor y).a$, with coherence $m_{(x,y),(x',y').a}$ given by
+  Since $\X$ is symmetric monoidal, the tensor product functor $\X\times\X \to \X$ is strong monoidal, so by composing it with the action of $\X$ on $\C$ we get a lax action of $\X\times\X$ on $\C$; i.e., the action given by $(x,y).a = (x\tensor y).a$, with multiplicative coherence $m_{(x,y),(x',y').a}$ given by
   \[
@@
     \]
-  where the last arrow is given by the unique symmetric monoidal isomorphism.
+  where the last arrow is given by the unique symmetric monoidal isomorphism, and with unital coherence $e_a$ given by
+  \[
+    a \xrightarrow{e_a}
+    I.a \to
+    (I \tensor I).a\,.
+    \]
 
@@
     \]
-  Moreover, the construction of this functor tells us that it commutes with the identity-on-objects functors out of the original categories:
+  The construction of this functor tells us that it commutes with the identity-on-objects functors out of the original categories:
   \[
@@
         & \C/\X
-    \end{tikzcd}\,,
-    \]
-  which means that the functor $J$ preserves the tensor product.
-  This also means that we may lift the associators and unitors for the tensor product on $\C$ along the functor $J$ morphisms in $\C/\X$, and that these morphisms satisfy the appropriate coherence diagrams.
-  It remains to show that they are still natural transformations in $\C/\X$, which we do in Figure \ref{FigAssocUnitorNaturalTransformations}.
+    \end{tikzcd}\,.
+    \]
+  This means that the functor $J$ preserves the tensor product.
+  It also means that we may lift the associators and unitors for the tensor product on $\C$ along the functor $J$ morphisms in $\C/\X$, and that these morphisms satisfy the appropriate coherence diagrams.
+  It remains to show that they are still natural transformations in $\C/\X$, and we do this in Figure \ref{FigAssocUnitorNaturalTransformations}.
   \begin{figure}
@@
 
-Since $\X$ is symmetric, and since the natural transformation $m_{x,y,a}$ is a monoidal natural transformation with respect to the monoidal functor structure on $x.y.a$ and $(x\tensor y).a$, the natural symmetric monoidal coherence
+Since $\X$ is symmetric, and since  $m_{x,y,a}$ is a monoidal natural transformation, the natural symmetric monoidal coherence
 \[
@@
   We need only show that they are natural transformations in $\C/\X$.  
-  Let $f\from a' \to a$, $g\from b' \to b$ be morphisms in $\C/\X$, considered as morphisms $f\from a' \to x.a$, $g\from b' \to y.b$ in $\C$.  
+  Let $f\from a' \to a$, $g\from b' \to b$ be morphisms in $\C/\X$, considered as morphisms 
+  \begin{mathpar}
+    f\from a' \to x.a
+    \and
+    g\from b' \to y.b
+  \end{mathpar}
+  in $\C$.  
   Then we need show that the following diagram commutes.
@@
 Since the powerset functor is lax monoidal, it induces a monoidal structure on the Kleisli category -- i.e., the familiar Cartesian product.  
-Indeed, the category of sets and relations \emph{is} monoidal closed under this choice of monoidal product, but the internal hom functor is also given by the Cartesian product, and does not agree with the function space functor on the original category of sets.
-
-In fact, we can obtain a result for monoidal closedness of $\C/\X$, but under different conditions.  
-Only $\C$ needs to be monoidal closed, but the action of $\X$ must preserve the internal hom strictly.
+In fact, the category of sets and relations \emph{is} monoidal closed with respect to this choice of product, but this is a bit of a coincidence: in particular, the internal hom functor this category (which is also given by Cartesian product) does not agree with the function-space construction in the category of sets.
+
+We are going to need to impose some stricter constraints on our action, then, in order to ensure that $\C/\X$ is monoidal closed.  
+It turns out that we only need $\C$ to be monoidal closed, but that we need the action of $\X$ on $\C$ to preserve the internal hom \emph{strictly}.
 
@@
     \]
-  which we can compose with $s_{x,a,b}\inv$ to give us a morphism
+  which we can compose with $s_{x,a,b}$ to give us a morphism
   \[
@@
     \]
-  The composite of the first two morphisms is equal to $\hat{f}$, and so the whole thing defines the same morphism as $f$ in $\C/\X$ (using the equivalence relation on morphisms).
+  The composite of the first two morphisms is equal to $\hat{f}$, and so the whole thing defines the same morphism as $f$ in $\C/\X$, with $\runit_x$ mediating between the two.
 
@@
 In this chapter we will consider what properties of the action we need in order to ensure that the induced monoidal structure on $\C/\X$ is Cartesian.
+Remember that the category of sets and relations is not Cartesian, even though it arises from an action of the unit category on the category of sets.
 
@@
 \end{mathpar}
-Since the tensor product of objects in $\C/\X$ is given by the same object as in $\C$, we can lift this comonoid structure through the functor $J$ to give us a natural comonoid structure on each object of $\C/\X$:
+The tensor product of objects $A,B$ in $\C/\X$ is the same object $A\times B$ that defines the Cartesian product $\C$, so we can lift this comonoid structure through the functor $J$ to give us a natural comonoid structure on each object of $\C/\X$:
 \begin{mathpar}
@@
 \end{mathpar}
-We use the symbols $\tensor$ and $I$ rather than $\times$ and $1$ in $\C/\X$, since this tensor product is not necessarily Cartesian.
+We have replaced the symbol $\times$ with the symbol $\tensor$ when we are working in $\C/\X$, since we do not know whether this tensor product is still Cartesian in $\C/\X$.
 
@@
 commute, then we may identify $\C/\X$ with a full subcategory of its own category of comonoids, closed under tensor product.  
-Since the category of comonoids in a monoidal category is automatically Cartesian, this will tell us that $\C/\X$ is Cartesian.
+Since the category of comonoids in a monoidal category is always Cartesian, this will tell us that $\C/\X$ is Cartesian.
 
@@
   \]
-Then a sufficient condition for these two morphisms to be equal in $\C/\X$ is that for every object $x$ of $\X$ there should be a morphism $f \from x \to x\tensor x$ that makes the following diagram commute.
-\[
+
+\begin{proposition}
+  Let a symmetric monoidal category $\X$ act on a Cartesian category $\C$ via a symmetric monoidal lax action.  
+  Suppose that \textbf{either}
+  \begin{itemize}
+    \item for every object $x$ of $\X$ there are morphisms $f\from x \to x\tensor x$ and $f_0 \from x \to I$ that make the following diagrams commute;
+      \begin{mathpar}
         \begin{tikzcd}
@@
         \end{tikzcd}
-  \]
-Similarly, we can calculate the two arms of the second diagram directly in $\C$.  
-The downwards arrow $J()$ is given by the composite
-\[
-  x.a \xrightarrow{()} 1 \xrightarrow{e_1} I.1\,,
-  \]
-while the composite $\phi_{x,a};J()$ is given by the composite
-\[
-  x.a \xrightarrow{x.()} x.1\,.
-  \]
-Thus, a sufficient condition for these two morphisms to be equal in $\C/\X$ is that for every object $x$ of $\X$ there should be a morphism $f_0 \from x \to I$ that makes the following diagram commute.
-\[
-  \begin{tikzcd}
-    x.a \arrow[d, "()"] \arrow[dr, "f_0.()"']
+        \and
+        \begin{tikzcd}
+          x.a \arrow[d, "()"'] \arrow[dr, "f_0.()"]
             & \\
@@
         \end{tikzcd}
-  \]
-
-If $\X$ itself is Cartesian, then we have a natural choice of morphisms $x \to x \times x$ and $x \to 1$, but choosing $f$ to be the diagonal map and $g$ to be the terminal map does not automatically make the diagram above commute.
-For example, the Cartesian product is not the category-theoretic product in the category of sets and relations, even though this category is the Kleisli category for the symmetric monoidal monad $\powerset \from \Set \to \Set$, and may be identified with the category $\Set/1$, where $1$ and $\Set$ are both Cartesian.
-In this case, the diagram
-\[
-  \begin{tikzcd}
-    \powerset(A) \arrow[dr, "\powerset(\Delta_A)"] \arrow[d, "\Delta_{\powerset(A)}"']
-      & \\
-    \powerset(A) \times \powerset(A) \arrow[r, "{m_{A,A}}" xshift=-3pt]
-      & \powerset(A \times A)
-  \end{tikzcd}
-  \]
-does not commute, the arrow at the top right sending a set $X\subseteq A$ to the set $\{(x,x) \suchthat x \in X\}$ while the composite at the bottom left sends $X$ to the set $\{(x,y)\suchthat x,y\in X\}$.
-
-An alternative sufficient condition for $\C/\X$ to be Cartesian is for the morphisms mediating between the two arms of the squares to go in the other direction.  
-In this case, we require that for each object $x$ of $\X$ there should be morphisms $g \from x\tensor x \to x$ and $g_0\from I \to x$ that make the following diagram commute.
+      \end{mathpar}
+    \textbf{or}
+  \item for every object $x$ of $\X$ there is are morphisms $g \from x \tensor x \to x$ and $g_0 \from I \to x$ that make the following diagrams commute.
     \begin{mathpar}
@@
     \end{mathpar}
-This will be particularly useful for reader actions, where an oplax monoidal functor $\X\to \C$ gives rise to an action of $\oppcat \X$ on $\C$.  
-Indeed, suppose that $j\from \X \to \C$ is an oplax symmetric monoidal functor between symmetric monoidal categories, where $\C$ is Cartesian closed.  
-The functor $j$ induces a reader action of $\oppcat\X$ on $\C$ (i.e., $x.a = jx \to a$), and we want the category $\C/\oppcat\X$ to be Cartesian.  
-For this, it will be sufficient to find, for each object $x$ of $\X$, morphisms $f \from x \to x\tensor x$ and $f_0 \from x \to I$ such that the following diagrams commute.
+  \end{itemize}
+  Then the monoidal structure on $\C/\X$ is Cartesian.
+  \label{PropCartesianness}
+\end{proposition}
+\begin{proof}
+  In either case, the morphisms $f,f_0$ or $g,g_0$ mediate between the composites from our earlier discussion.
+\end{proof}
+
+Note that this result is not the sharpest possible, since they do not consider the case that there may be more complicated zigzags mediating between the morphisms.
+Nevertheless, they are sufficient for our purposes.
+
+An obvious idea for constructing the morphisms $f,f_0$ is to look at the case that $\X$ is itself Cartesian, taking $f$ to be the diagonal and $f_0$ the terminal morphism.
+Note, however, that this does not automatically mean that the diagrams in Proposition \ref{PropCartesianness} commute: for example, the trivial category and the category of sets are both presheaf categories and hence Cartesian closed, but if $1$ acts on the category of sets via the powerset monad then the resulting monoidal category $\Set/1$ (i.e., the category of sets and relations) is not Cartesian.
+
+If $\X$ is Cartesian and $\oppcat{\X}$ acts on $\C$, then we can try taking $g$ and $g_0$ to be (the opposites of) the diagonal and terminal morphism in $\X$.
+This will be particularly useful for reader actions, where an oplax monoidal functor $j\from \X \to \C$ gives rise to an action of the opposite category $\oppcat\X$ of $\X$ on $\C$.  
+If $\C$ is Cartesian and we want to show that $\C/\X$ is Cartesian, then it will be sufficient to find, for each object $x$ of $\X$, morphisms $f \from x \to x\tensor x$ and $f_0 \from x \to I$ such that the following diagrams commute.
 \begin{mathpar}
@@
 In the next chapter, we will investigate a class of reader actions, and give a more concrete property for the category $\C/\oppcat\X$ to be Cartesian closed.
+We will start to see how we can come up with reader actions to model different computational effects and come closer to our eventual Computational Adequacy and Full Abstraction results.
 
@@
   Let $\X,\YY$ be a monoidal category and let the functor category $[\YY,\Set]$ be equipped with the Day convolution product.  
-  Then a lax monoidal functor $\X \times \YY \to \Set$ is the same thing (via currying) as a lax monoidal functor $\X \to [\YY,\Set]$.
+  Given a functor $F \from \X \times \YY \to \Set$, we have an associated functor $\Lambda(F) \from \X \to [\YY,\Set]$.
+  Then $F$ is lax monoidal if and only if $\Lambda(F)$ is lax monoidal.
 \end{proposition}
 
-In particular, if $\X$ acts on the category of sets via a monoidal action, then it gives rise to a functor $\Set \to [\X,\Set]$.
+In particular, if $\X$ acts on the category of sets via a monoidal action, then it gives rise to a monoidal functor $\Set \to [\X,\Set]$.
 
@@
   Let $\oppcat\X$ act on $\Set$ via the reader action induced by $j$.
-  Then the \Mellies category $\Mell_{\oppcat\X}\Set$ is isomorphic to the category obtained via base change along the action regarded as a functor
-  \[
-    \blank.\blank\from \Set \to [\X,\Set]\,.
-    \]
+  Then the \Mellies category $\Mell_{\oppcat\X}\Set$ is isomorphic to the category obtained via base change along the functor $\Set \to [\X,\Set]$ obtained from the action $\blank.\blank$.
   \label{PropMelliesVsBaseChange}
@@
     \cong & 
-    [jx,[A,C]]\,.
+    [jx,[A,C]]\,,
   \end{IEEEeqnarray*}
@@
 \begin{proof}
-  Consider $F$ as a pseudofunctor $\Set \to \Cat$, and let $\X=\oppcat{\left(\int F\right)}$ be the opposite of its Grothendieck construction.  
-  Since $\Set$ is an ordinary category (as opposed to a proper bicategory), so is $\X$.
+  By considering each set $F(A)$ as a category with only identity morphisms, we can imagine $F$ as a $2$-functor $\Set \to \Cat$.  
+  Let $\X=\oppcat{\left(\int F\right)}$ be the opposite of its Grothendieck construction.  
+  Since $\Set$ is an ordinary category (as opposed to a proper bicategory), $\X$ has only identity $2$-morphisms, so may be considered as an ordinary category.
 
@@
 
-  We define a symmetric monoidal structure on $\X$ by defining
+  We define a symmetric monoidal structure on $\X$ by setting
   \begin{mathpar}
@@
     \]
-  Indeed, for each object $(X,m)$ of $\X$ we have a function
+  To see this, note that for each object $(X,m)$ of $\X$ there is a function
   \begin{IEEEeqnarray*}{cCc}
@@
     \]
-  Indeed, if we have a morphism $h \from (Y,n) \to (X,m)$ then by definition we have
+  Indeed, if $h \from (Y,n) \to (X,m)$ is a morphism then by definition we have
   \[
@@
     \]
-  and so we have a commutative triangle
+  and so we get a commutative triangle
   \[
@@
     \]
-  Therefore, we have an induced map
+  Therefore, there is an induced map
   \[
@@
   in the colimit.
-  But indeed, we have a morphism $f\from (X,m) \to (A,F(f)(m))$ in $\oppcat\X$, and $f;\id_A=f$.
+  But we have a morphism $f\from (X,m) \to (A,F(f)(m))$ in $\oppcat\X$, and $f;\id_A=f$.
   Therefore, our map $\colim_{(X,m)\from \X}[X,A] \to FA$ was a bijection.
@@
   Let $\powerset_+\from \Set \to \Set$ be the non-empty powerset functor.  
-  Then the category $\X$ of elements of $\powerset_+$ has pairs $(A,M)$ as elements, where $A$ is a (necessarily non-empty) set and $M$ is a non-empty subset of $A$.
+  Then the category $\X$ of elements of $\powerset_+$ has pairs $(A,M)$ as elements, where $A$ is a (necessarily non-empty) set and $M$ a non-empty subset of $A$.
   Morphisms $(A,M) \to (B,N)$ are functions $f \from A \to B$ such that $f(M)=N$.
@@
   sending $(M,N)$ to $M\times N\subset A \times B$ and picking out the subset $1 \subset 1$.
-  This then gives us a monoidal structure on this category of elements, inducing an action as in Proposition \ref{PropMonoidalFunctorIsColimitOfReaderAction}.
+  Therefore this category of elements is a monoidal category, and has a natural induced action as in Proposition \ref{PropMonoidalFunctorIsColimitOfReaderAction}.
   The colimit of this action then gives us the original functor.  
@@
   \emph{is} probability preserving.  
-  In the language of probability, the two copies of the random variable $V$ are \emph{dependent random variables}, so the probability of obtaining the reading $(a,a)$ from $\langle V,V\rangle$ is the same as the probability of obtaining the reading $v$ from $V$.
+  In the language of probability, the two copies of the random variable $V$ are \emph{dependent random variables}, so the probability of obtaining the reading $(v,v)$ from $\langle V,V\rangle$ is the same as the probability of obtaining the reading $v$ from $V$.
   Since the terminal morphism from $(A,V)$ to $(1,())$ is also probability preserving, the category $\Set/\oppcat{\Rv_\Omega}$ will be Cartesian closed.
@@
 \end{mathpar}
-In particular, if $j\from \X \to \C$ is an oplax monoidal (in particular, comonoid-preserving) functor, yielding a reader action of $\oppcat\X$ upon $\C$, and $x$ is a monoid in $\oppcat\X$ (i.e., a comonoid in $\X$), then the monad $M_x$ will be the reader monad corresponding to $jx$.
+If $j\from \X \to \C$ is an oplax monoidal (in particular, comonoid-preserving) functor, yielding a reader action of $\oppcat\X$ upon $\C$, and $x$ is a monoid in $\oppcat\X$ (i.e., a comonoid in $\X$), then the monad $M_x$ will be the reader monad corresponding to $jx$.
 
@@
   Suppose that $\X$ has a terminal object $1$.
-  Then the category $\C/\X$ is isomorphic to the Kleisli category for the monoid $M_1$.
+  Then the category $\C/\X$ is isomorphic to the Kleisli category for the monad $M_1$.
 \end{proposition}
@@
   \]
-At least, it does if the $\sigma$-algebra $\F$ on $\Omega$ is discrete.  
-But if $\Omega$ is not itself a discrete probability space, then the function
+In fact, if $\F=\powerset(\Omega)$ then this is indeed an initial object.
+However, if $\F\ne\powerset(\Omega)$, then the function
 \[
@@
   \]
-will not be measurable, and so $\id_\Omega$ will not be a discrete random variable.
-
-In the case that $\F=\powerset\Omega$, the category $\Rv_\Omega$ has an initial object, and the category
+is not measurable, and so $\id_\Omega$ is not a discrete random variable.
+
+If $\Rv_\Omega$ has an initial object $(\Omega,\id_\Omega)$, then the category
 \[
@@
 \begin{remark}
-  This subtlety with probability spaces is not present in the case of the nonempty powerset functor, which is why we it makes sense to model plain nondeterminism with a Kleisli category, as we did in Chapter \ref{ChapMonads}.
+  We could redo this whole probability example using the nonempty powerset functor, in an effort to model nondeterminism. 
+  To do that, we'd construct a new category whose objects were pairs $(A,f)$, where $f\from \Omega \to A$ is a function out of some fixed set $\Omega$.
+  However, in that case the resulting monoidal category would always have an initial object (namely, $(\Omega, \id_\Omega)$), and our resulting action would collapse to an ordinary monad, taking us back to Chapter \ref{ChapMonads}.
 \end{remark}
@@
 
-In general, such functions automatically carry an oplax monoidal structure, since the source category $\Set$ and target category $\G$ are Cartesian.  
-So we get morphisms
+In general, since the source category $\Set$ and target category $\G$ are Cartesian, such functors automatically carry an oplax monoidal structure, given by
 \begin{mathpar}
@@
 The purpose of the final chapter will be to define a language with an operational semantics for which these primitives make sense, and prove a full abstraction result for it.
+
+But first, an interlude.

### 2019-09-17 Thesis/pmonads2.tex
Random commit.

@@
 In this chapter we will investigate the adequacy and full abstraction properties of the resulting category $\G/\X$, as we did with Kleisli categories in Chapter \ref{ChapMonads}.
-Once again, we will pass to a special case of the general theory.  
-As in Chapter \ref{ChapMonads}, we will require $\G$ to be a Cartesian closed category that admits a computationally adequate denotational semantics of Idealized Algol, and we shall require that $\G$ may be regarded as being enriched in algebraic directed-complete partial orders in such a way that every compact morphism between the denotations of types is the denotation of some term.
-As hinted at in Chapter \ref{ChapParametricMonads}, we shall require the action of $\X$ on $\G$ to be a reader action corresponding to an oplax symmetric monoidal functor that satisfies the condition in Theorem \ref{TheCartesianClosedCx}, so that the category $\G/\X$ is Cartesian closed.
+
+As in Chapter \ref{ChapMonads}, we shall generally require $\G$ to be a Cartesian closed category that admits a computationally adequate denotational semantics of Idealized Algol, and we shall require that $\G$ may be regarded as being enriched in algebraic directed-complete partial orders in such a way that every compact morphism between the denotations of types is the denotation of some term.
+
+As hinted at in Chapter \ref{ChapParametricMonads}, we shall also require the action of $\X$ on $\G$ to be a reader action corresponding to an oplax symmetric monoidal functor that satisfies the condition in Theorem \ref{TheCartesianClosedCx}, so that the category $\G/\X$ is Cartesian closed.
 
@@
 By our description of $\G/\oppcat \X$ as a lax colimit in $\Cat$ (i.e., Corollary \ref{CorTheConstructionUniversalProperty}), we have a natural functor $J\from \G\to\G/\oppcat \X$ and a natural transformation $\phi_{p,a}\from J(jp\to a) \to Ja$.
-Our denotational semantics of \IAXX is then given in the category $\G/\oppcat X$ as follows.  
-The denotation of any type $T$ of Idealized Algol is given by $J(\deno{T}_\G)$, where $\deno{T}_\G$ is the original denotation in $\G$.
-The denotation of any sequent $\Gamma\ts M$ is given by $\deno{\Gamma\ts M} = J(\deno{\Gamma\ts M}_\G)$, where $\deno{-}_\G$ is the original denotation in $\G$.
-The denotation of $\choose_p$ is given by the morphism $\omega_p \from 1 \to j(p)$ given by the composite
+We define our denotational semantics of \IAXX in the category $\G/\oppcat X$ as follows.  
+The denotation of any type $T$ of Idealized Algol is the object $J(\deno{T}_\G)$, where $\deno{T}_\G$ is the original denotation in $\G$.
+The denotation of any sequent $\Gamma\ts M$ the morphism $\deno{\Gamma\ts M} = J(\deno{\Gamma\ts M}_\G)$, where $\deno{-}_\G$ is the original denotation in $\G$.
+The denotation of $\choose_p$ is the morphism $\omega_p \from 1 \to j(p)$ given by the composite
 \[
@@
 
-The example to have in mind is that of probability; here, the objects of our category $\X$ are discrete random variables, with $j(p)$ giving the codomain of the random variable, and the term $\choose_p\from j(p)$ can be thought of as choosing an element of that set.
+The example to have in mind is that of probability; here, the objects $p$ of our category $\X$ are discrete random variables, with $j(p)$ giving the codomain of the random variable, and the term $\choose_p\from j(p)$ can be thought of as randomly sampling a single element of that set with the probability distribution coming from that random variable.
 
@@
 \begin{figure}
+  \small
   \begin{mathpar}
@@
     \inferrule*{\Gamma,s\ts M \converges_U n,s'}{\Gamma,s\ts \suc M \converges_U n+1,s'}
-    \\\and
+    \and
     \inferrule*{\Gamma,s\ts M \converges_U n+1,s'}{\Gamma,s\ts \pred M \converges_U n,s'}
@@
     \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges_U n,s' \\ \Gamma,s' \ts V \converges_V x,s''}{\Gamma,s\ts V \gets E \converges_{U \cat V} \skipp,(s''\vert x \mapsto n)}
-    \and
+    \\
     \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges_U x,s'}{\Gamma,s\ts !V \converges_U n,s'}
@@
     \inferrule*{\Gamma,s\ts V \converges_U \mkvar W R,s' \\ \Gamma,s'\ts R \converges_V n,s''}{\Gamma,s\ts !V \converges_{U \cat V} n,s''}
-    \\\and
+    \and
     \inferrule*[right=$a\in j(p)$]{ }{\Gamma,s\ts \choose_p \converges_{(p:a)} a,s}
@@
   \label{FigIaxxOpSem}
+  \normalsize
 \end{figure}
 
-We notice immediately that all but one of these rules are exactly the same as the corresponding rules from \IAX, the only difference being the form the form that the associated sequence takes.  
-The one difference is the rule for $\choose_p$.
+We notice immediately that all but one of these rules are exactly the same as the corresponding rules from \IAX, except that the symbol $\converges$ is now decorated with a sequence of pairs rather than a simple sequence.
+The one major difference is the rule for $\choose_p$.
 
@@
   in $\X$ such that $jf$ is a surjection.  
-  Define functions $\pi_i\from j(N) \to j(p_i)$ to be given by the composites
+  Define functions $\pi_i\from j(N) \to j(p_i)$ (depending on $f$) to be given by the composites
   \[
@@
   for $k=1,\cdots,n$.
-  Now note that Lemma \ref{LemFirstSubstitution} still holds if we use the terms $\choose_{p_i}$ instead of the $\ask_X$; this means that we have a valid IA${}_j(N)$ inference given by
+  Now note that Lemma \ref{LemFirstSubstitution} still holds if we use the terms $\choose_{p_i}$ instead of the $\ask_X$; this means that we have a valid IA${}_{j(N)}$ inference given by
   \[
@@
 
-  Otherwise, $M=\new\lambda v.v\gets \ask_{j(N)};\Pi_j\oc v)$ for some $j$.  
+  Otherwise, $M=\new\lambda v.v\gets \ask_{j(N)};\Pi_j\oc v$ for some $j$.  
   Now, if we have
@@
     \]
-  then a simple examination of the reduction tells us that we must have $s'=s$, and that $u$ must have length $1$ -- say $u=m$ -- where the single element $n$ of $u$ satisfies $\pi_j(m)=c$.
+  then a simple examination of the reduction tells us that we must have $s'=s$, and that $u$ must have length $1$ -- say $u=m$ -- where the single element $m$ of $u$ satisfies $\pi_j(m)=c$.
 
@@
 It is instructive to consider the equivalence relation on pairs $(p,\U)$ in the case that $\X = \Rv_\Omega$ is the category of random variables on some probability space $\Omega$.
-Given a random variable $V$ on a set $X$, we get an induced random variable taking values in $X^*$.  
+Given a random variable $V$ taking values in a set $X$, we get an induced notion of probability for the elements of $X^*$: given a sequence $u$ of elements of $x$, we write
+\[
+  \bP(u) = \prod_{i=0}^{|u|-1} \bP(V = u^{(i)})\,.
+  \]
 If we have a random variable $W$ on a set $Y$ and a function $f\from X \to Y$ such that $W=f\circ X$, and if $\U\subset X^*$ and $\V\subset Y^*$ are such that $u\in\U$ if and only if $f_*u\in\V$, then the induced probabilities of the sets $\U$ and $\V$ are the same.
@@
   Let $\sigma\from 1 \to (j(p) \to A)$, $\tau\from 1 \to (j(q) \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
-  Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau)$ are equivalent.
+  Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
   \label{PropAccEquivalent}
@@
 We can now state and prove our Computational Adequacy result.
-For this result, given a term $M\from \com$ mentioning objects $p_1,\cdots,p_n$, we shall assume the existence of some IA datatype $N$ admitting a morphism $f \from N \to p_1 \tensor \cdots \tensor p_n$ such that the definable projections $\pi_i$ on to the objects $j(p_i)$ are IA-definable.
+For this result, given a term $M\from \com$ mentioning objects $p_1,\cdots,p_n$, we shall assume the existence of some IA datatype $N$ admitting a morphism $f \from N \to p_1 \tensor \cdots \tensor p_n$ such that the corresponding projections $\pi_i$ on to the objects $j(p_i)$ are IA-definable.
 
@@
 
-\begin{definition}
-  Let $M$ be a closed term of \IAXX of type $\com$ mentioning $p_1,\cdots,p_n$.
-  Let $S(M)$ be the set of all sequences $U$ such that $M\converges_U\skipp$.
-
-  We define $B(M)$, the \emph{behaviours of $M$}, to be the equivalence class corresponding to the pair
-  \[
-    (p_1\tensor \cdots \tensor p_n, \U)\,,
-    \]
-  where $\U$ is the set of all sequences $u\in j(p_1\tensor \cdots \tensor p_n)^*$ that cover some sequence $U\in S(M)$, via the projections
-  \[
-    j(p_1\tensor \cdots \tensor p_n) \xrightarrow{m^j} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\pr_i} j(p_i)\,.
-    \]
-\end{definition}
-
 \begin{definition}[Observational Equivalence]
@@
 
-Our setup is too general for us to prove Full Abstraction, but we will be able to prove a Full Abstraction result in an important special case: that of Probabilistic Algol.
+Unfortunately, compact definability does not hold for this setup in general.  
+In the next section we will develop an important special case -- a semantics of Probabilistic Algol -- for which we will be able to prove Full Abstraction.
 
@@
 
-The category $\X = \Rv_\Omega^{FS}$ will then be the category whose objects are random variables of \emph{finite support}; that is, measurable functions $V\from\Omega \to X$, where $X$ is a discrete space, such that there is some finite subset $Y\subset X$ such that $\bP(V\in Y) = 1$.
+The category $\X = \Rv_\Omega^{FS}$ will then be the category whose objects are random variables of \emph{finite support}; that is, measurable functions $V\from\Omega \to X$, where $X$ is a discrete space, such that there is some finite subset $Y\subset X$ satisfying $\bP(V\in Y) = 1$.
 
@@
 
+There is a natural strict monoidal functor $\Rv_{\Omega}^{FS} \to \Set$ (sending $V \from \Omega \to X$ to the set $X$), which gives us an oplax monoidal functor $\Rv_{\Omega}^{FS} \to \G$ and hence a lax reader action of $\Rv_{\Omega}^{FS}$ on $\G$.
+By our discussion in Chapter \ref{ChapReaderActions}, this action satisfies all of the requirements we imposed in the previous section.
+
 Recall that the tensor product of two random variables $V\from \Omega \to X$ and $W \from \Omega \to Y$ is their pairing $V \tensor W = \langle V,W\rangle \from \Omega \to X \times Y$.
@@
 \[
-  \Omega \to \bB
+  B_p \from \Omega \to \bB
   \]
@@
 and such that $\bP(\tilde{V}=k)=0$ for any $k\ge 2^n$.
-Then we have a function $f \from \bN \to \bB^n$ that sends $\sum_{i=1}^n 2^{i-1}a_i$ to $(a_1,\cdots,a_n)$ and sends $k\ge 2^n$ to some fixed value (say, $(\false,\cdots,\false)$), and then we have
+Then there is a function $f \from \bN \to \bB^n$ that sends $\sum_{i=1}^n 2^{i-1}a_i$ to $(a_1,\cdots,a_n)$ and sends $k\ge 2^n$ to some fixed value (say, $(\false,\cdots,\false)$).  
+This function $f$ satisfies
 \[
@@
     \]
-  where the infinite sum refers to the supremum of the sums of all finite subsets of $\U$.
+  where the infinite sum refers to the supremum of the sums over all finite subsets of $\U$.
 \end{definition}
@@
 
-We now make a definition relating the operational behaviour we have defined for \IAXX to probability.
+We now define the operational semantics for Probabilistic Algol.
 
@@
   By Theorem \ref{TheComputationalAdequacyIAXX}, $B(M)$ is equivalent to $(p,\Acc(\deno M))$.  
-  Therefore, by Proposition \ref{PropProbabilityWellDefined}, $\bP(M\converges) = \bP(B(M)) = \bP(V,\Acc(\deno M)) = \bP(\deno M\downarrow)$.
+  Therefore, by Proposition \ref{PropProbabilityWellDefined}, 
+  \[
+    \bP(M\converges) = \bP(B(M)) = \bP(V,\Acc(\deno M)) = \bP(\deno M\downarrow)\,.\qedhere
+    \]
 \end{proof}
@@
 \section{Full Abstraction for Probabilistic Algol}
+
+In order to prove a definability result, we would like to know that any morphism $A\to B$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ may be considered as a pair 
+\[
+  (V_{p_1}\tensor\cdots\tensor V_{p_n},f \from A \to (\bB^n \to B))
+  \]
+for appropriately chosen $p_1,\cdots,p_n$.
+
+This is because every morphism definable in PA takes this form.
+It will suffice to prove the following.
 
@@
 
-The most important consequence of Proposition \ref{PropFiniteSupport} is that it tells us that any morphism $A\to B$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ may be considered as a pair 
-\[
-  (V_{p_1}\tensor\cdots\tensor V_{p_n},f \from A \to (\bB^n \to B))
-  \]
-for appropriately chosen $p_1,\cdots,p_n$.
+Then if we have an arbitrary morphism $\sigma \from A \to B$ (given by a morphism $\tilde\sigma \from A \to (j(X) \to B)$ in the base category), Proposition \ref{PropFiniteSupport} gives us the morphism $f$ mediating between $\tilde\sigma$ and a morphism of the form specified at the start of this section.
 
@@
 
-  Note that if $\G$ is the category of games, this compactness property is invariant under the choice of representative for $\sigma$.
+  If $\G$ is the category of games, this compactness property is invariant under the choice of representative for $\sigma$.
 \end{remark}
+
+We can now prove our compact definability result.
 
@@
 \begin{proof}
-  Let $(V, \sigma \from 1 \to (X \to \deno{T})$ be a compact representative of $\sigma$, where $X$ is a set and $V$ is a finitely-supported random variable taking values in $X$.  
+  Let $(V, \sigma \from 1 \to (X \to \deno{T}))$ be a compact representative of $\sigma$, where $X$ is a set and $V$ is a finitely-supported random variable taking values in $X$.  
   By Proposition \ref{PropFiniteSupport}, we may choose $p_1,\cdots,p_n$ such that there is a probability-preserving function
   \[
-    f \from V_{p_1} \tensor \cdots \tensor V_{p_n} \to \deno{T}\,.
-    \]
-  After composing on the right by $(\sigma \to \deno{T})$, we may assume that $\sigma$ is of the form
+    f \from V_{p_1} \tensor \cdots \tensor V_{p_n} \to V\,.
+    \]
+  After composing on the right by $(f \to \deno{T})$, we may assume that $\sigma$ is of the form
   \[
@@
 
-An alternative way to model probability is using the Kleisli category construction that we considered in Chapter \ref{ChapMonads}.  
+The probabilistic language is our main example of an application of the theory of parametric monads that we have developed.
+However, it is worth noting that it is possible to model a probabilistic language within the langauge IA${}_\bB$ from Chapter \ref{ChapMonads}.
 Specifically, we can consider the language IA${}_\bB$ as a probabilistic Algol variant, by treating the term $\ask_\bB$ as a coin flip that returns $\true$ or $\false$ each with probability $\frac12$.
@@
 since $2^{-|u|}$ is the probability of a particular sequence $u$ of $\true$ and $\false$ values occurring.
-Here, the infinite sum means the supremum over all sums of finite subsets.
+Here, the infinite sum means the supremum over all sums over finite subsets.
 Similarly, given a Kleisli morphism $\sigma\from 1 \to \bC$ -- i.e., a morphism $\sigma\from 1 \to (\bB \to \bC)$ in $\G$, we can define
@@
 
-This model is much easier to realize.  
-What do we gain, then, from our more complicated original model?
+Since this model relies on a lot less theory, it is worth spending a bit of time thinking about what our existing parametric monad model gives us that this one doesn't.
 
 The most obvious answer is that our original model allowed us to work with arbitrary probabilities, rather than using a fixed coin with probability $\frac12$.  
-This is not such a great advantage as it might seem, since if $p\in[0,1]$ is any real number whose binary expansion is computable as a function $\bN \to \bB$, then we can simulate $\choose_p$ within the probabilistic version of IA${}_\bB$\footnote{Idea: build up a sequence of intervals $I_n$ of width $2^n$ by repeatedly flipping the coin and using the result to choose either the lower or the upper half of $I_{n-1}$.
+However, this is not such a great advantage as it might seem, since if $p\in[0,1]$ is any real number whose binary expansion is computable as a function $\bN \to \bB$, then we can simulate $\choose_p$ within the probabilistic version of IA${}_\bB$\footnote{Idea: build up a sequence of intervals $I_n$ of width $2^n$ by repeatedly flipping the coin and using the result to choose either the lower or the upper half of $I_{n-1}$.
 If at any point the upper bound of $I_n$ is less than or equal to $p$ (which can be checked by computing the first $n$ terms of the binary expansion of $p$), then return $\true$.  
@@
 Perhaps a better way of thinking about the difference between the two models, then, is to consider what the denotation of a term actually looks like.  
+For comparison, we look at the denotations of the term $\choose_{\frac23}$ in the two different semantics.
+
 In the language IA${}_\bB$, we can define a term that converges to $\true$ with probability $\frac23$ and to $\false$ with probability $\frac13$ by
@@
     (\ul X \to (\ul Y \to C)) \to
-    ((\ul X \times \ul Y) \to C) \xrightarrow{\mu\to C}
+    ((\ul X \times \ul Y) \to C) \\ \xrightarrow{\mu\to C}
     (\ul{X\times Y} \to C)\,,
@@
   Indeed, suppose that $\t,\t'$ are two interactions in $\tilde\sigma\|(\ul X \to \tilde\tau)$ such that $\t\vert_{A,B,C}=\t'\vert_{A,B,C}=\s$, $\t\vert_{\ul X} = \t'\vert_{\ul X}$ and $\t\vert_{\ul Y}=\t'\vert_{\ul Y}$.
-  We claim that $\t = \t'$.
-
-  Indeed, suppose for a contradiction that $\t\ne\t'$: then there are prefixes $\r p\prefix \t$ and $\r q \prefix \t'$, where $\r$ is the longest common subsequence of $\t$ and $\t'$ and $p\ne q$ are moves.
+  Next we claim that $\t = \t'$.
+
+  To see why, suppose for a contradiction that $\t\ne\t'$: then there are prefixes $\r p\prefix \t$ and $\r q \prefix \t'$, where $\r$ is the longest common subsequence of $\t$ and $\t'$ and $p\ne q$ are moves.
 
@@
   Now let $s\in \L_{A \to C}$ and let $t\in\sigma;\tau$ be such that $t/s$.
-  By the argument in Proposition \ref{PropComposition}, there is a unique interaction sequence $S\in\sigma\|(\ul X\to\tau)\|(\Lambda\inv;\mu)$ such that $S\vert_{A,\ul{X\times Y} \to C}=t$.
+  By the argument in Proposition \ref{PropComposition}, there is a unique interaction sequence 
+  \[
+    S\in\sigma\|(\ul X\to\tau)\|(\Lambda\inv;\mu)
+    \]
+  such that $S\vert_{A,\ul{X\times Y} \to C}=t$.
   Define $\t = S\vert_{A,\ul X \to B,\ul X \to (\ul Y \to C)}$, and $\s=\t\vert_{A,B,C}$.
@@
 
-  Now consider $\t\vert_{\ul X,\ul Y}$, which has the same length as $S\vert_{\ul{X\times Y}}=t\vert_{\ul{X\times Y}}$.
+  Consider the sequence $\t\vert_{\ul X,\ul Y}$, which has the same length as $S\vert_{\ul{X\times Y}}=t\vert_{\ul{X\times Y}}$.
   This sequence is made up of pairs of moves $qx$ for $x\in X$ or $qy$ for $y\in Y$.
@@
   \[
+    \sum_{\stackrel{\t\in\tilde\sigma\|(\ul X \to \tilde\tau)}{\t\vert_{A,B,C}=\s}}
     \left[ \prod_{i=1}^{|u|-1} \bP(V = u^{(i)}) \prod_{i=0}^{|v|-1} \bP(W = v^{(i)}) \;\middle|\; \mbox{\pbox{\textwidth}{where\\$\t\vert_{\ul X} = qu$ \\ $\t\vert_{\ul Y} = qv$}} \right]\,,
@@
 
-The work in the previous section shows that it suffices to consider equivalence classes of strategies under the relation $\approx_\bP$, which suggests that we may take the quantities $\bP(s\in\sigma)$ as primitives, rather than defining them indirectly.
-
-This is the approach taken by Danos and Harmer in \cite{DanosHarmer} -- the original game semantics for a probabilistic variant of Algol.  
+The work in the previous section shows that two strategies that are related by the probabilistic equivalence relation $\approx_\bP$ are automatically observationally equivalent.  
+This suggests that the realy content of a probabilistic strategy consists in the quantities $\bP(s\in\sigma)$.  
+An idea, then, is to take the quantities $\bP(s\in\sigma)$ as primitives, rather than defining them indirectly.
+
+That is the approach taken by Danos and Harmer in \cite{DanosHarmer} -- the original game semantics for a probabilistic variant of Algol.  
 Danos and Harmer define an arena as we do, but define a probabilistic strategy on an arena $A$ to be given by a function

### 2019-09-17 Thesis/promonads.tex
Random commit.

@@
 
-The purpose of this chapter is to shine some light on the definition of the \Mellies category, showing why it is natural to think about $[\X,\Set]$-enriched categories and why the \Mellies category may be considered analogous to the Kleisli category.
+The purpose of this short chapter is to shine some light on the definition of the \Mellies category for a parametric monad, showing why it is natural to think of it as being an analogue for the Kleisli category on a monad.
 
@@
   \[
-    \M_n(x_1,\cdots,x_n;y)
+    \M_n(a_1,\cdots,a_n;b)
     \]
@@
     \left(\mbox{\pbox{24pt}{$b_{pq}$}} \suchthat \mbox{\pbox{80pt}{$p=1,\cdots,n$ \\ $q=1,\cdots,k_p$}}\right)
-    \and
+    \\
     (c_p\from p = 1,\cdots,n)
@@
     \and
-    d \from c_1,\cdots,c_n\to d
+    h \from c_1,\cdots,c_n\to d
   \end{mathpar}
@@
 
+\begin{remark}
+  We will use a slightly different form of commutative diagrams for multicategories, which should be fairly straightforward to understand.
+  If, for example, we say that the following diagram commutes,
+  \[
+    \begin{tikzcd}[column sep=40pt]
+      {a_1,\cdots,a_n} \arrow[r, "{f_1,\cdots,f_j}"] \arrow[d, "{g_1,\cdots,g_k}"']
+        & {b_1,\cdots,b_j} \arrow[d, "h"] \\
+      {c_1,\cdots,c_k} \arrow[r, "i"]
+        & d
+    \end{tikzcd}
+    \]
+  where the arities of $f_1,\cdots,f_j$ sum to $n$, as do the arities of $g_1,\cdots,g_k$, then we mean that the composite $(f_1,\cdots,f_k);h$ is equal to the composite $(g_1,\cdots,g_k);i$.
+  We leave it to the reader to extend this to more complicated diagrams.
+\end{remark}
+
 \begin{example}
@@
   \end{mathpar}
+  If we're being careful, then we should note that the expression $a_1 \tensor \cdots \tensor a_n$ does not define a single object of $\M$, since the tensor product is not in general strictly associative.
   Since the tensor product is not necessarily strictly associative, it is not obvious exactly what we mean by $a_1 \tensor \cdots \tensor a_n$.
-  In fact, it is enough to choose any one of the possible bracketings (e.g., to make $\blank\tensor\blank$ always associate to the right).
+  It is enough to fix any one of the possible bracketings (e.g., to make $\blank\tensor\blank$ always associate to the right).
 
@@
   where the first arrow is induced from the normal monoidal coherences (exactly which ones depends on how we choose to interpret the iterated tensor product).
+  \label{ExMonoidalCategoryAsMulticategory}
 \end{example}
@@
 
-We call a multicategory \emph{representable} if it isomorphic to a multicategory that arises from a monoidal category in this way.  
+We call a multicategory \emph{representable} if it isomorphic to a multicategory that arises from a monoidal category as in Example \ref{ExMonoidalCategoryAsMulticategory}.
 The next theorem gives a criterion for a multicategory to be representable.
@@
   \[
-    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a
-    \]
-  that is \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
+    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a\,.
+    \]
+  Suppose that the $\pi_{\vec a}$ are \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
   \[
@@
     \]
-  Define an operation $\blank\tensor\blank$ that sends objects $a,b$ of $\M$ to $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
-  Then $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
+  Given objects $a,b$ of $\M$, define $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
+  Then the operation $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
   \begin{itemize}
@@
       \[
-        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a
+        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a\,,
         \]
@@
   \end{mathpar}
-  are multimorphisms, $\sigma_i$ is a permutation of $\{1,\cdots,k_i\}$ and $\tau$ is a permutation of $\{1,\cdots,n\}$, then
+  are multimorphisms, $\sigma_i$ is a permutation of $\{1,\cdots,k_i\}$, and $\tau$ is a permutation of $\{1,\cdots,n\}$, then
   \[
@@
   \end{mathpar}
-  Composition and the identity are easily defined pointwise.
+  Composition and the identity are similarly defined pointwise.
 \end{definition}
@@
     \]
-  a \emph{multinatural transformation} $\phi\from F \Rightarrow G$ is given by morphisms $\phi_a \from F a \to G a$ for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
+  a \emph{multinatural transformation} $\phi\from F \Rightarrow G$ is given by morphisms 
+  \[
+    \phi_a \from F a \to G a
+    \]
+  for each object $a$ of $\M$, such that if $f\from a_1,\cdots a_n\to b$ is any morphism in $\M$, then the following diagram commutes.
   \[
@@
     \]
-  commutes, where $\sigma$ is the permutation of
-  \[
-    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\}
-    \]
-  that sends $(i,j)$ to $(j,i)$.
+  commutes, where $\sigma$ is the map
+  \begin{mathpar}
+    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\} \to \{(1,1),\cdots,(1,m),\cdots,(n,1),\cdots,(n,m)\}
+  \end{mathpar}
+  that sends $(i,j)$ to $(j,i)$, considered as a permutation of $\{1,\cdots,mn\}$.
 \end{definition}
@@
 
-Note that a monoid in a multicategory $\M$ may also be defined to be a multifunctor $1 \to \M$ \cite[2.1.11]{Multicategories}.
+Note that a monoid in a multicategory $\M$ may equivalently be defined as a multifunctor $1 \to \M$ \cite[2.1.11]{Multicategories}.
 
@@
   In particular, a monoid in a multicategory $\M$ is the same thing as an $\M$-enriched category with a single object.
-
-  Another equivalent definition of a monoid in a multicategory $\M$ is that it is a multifunctor from $1$ to $\M$, where $1$ is the unit monoidal category, considered as a multicategory.
 \end{remark}
@@
   In the case $n=1$, this is the same thing as a $\V$-enriched functor from $\C_1$ to $\D$.
-  We will use the word `functor' to refer to the more general multimorphisms between $\V$-enriched categories in the case that $\V$ is symmetric.
 \end{definition}
@@
   \]
-We will use the letter $p$ to refer to these multimorphisms and their various permutations.
+In what follows, we will denote these multimorphisms (and their various permutations) with the letter $p$.
 
@@
 
-Let $F_1,\cdots,F_n,G \from \oppcat \C \times \C \to \V$ be $\V$-enriched profunctors $\C\pto \C$, where $\C$ is a $\V$-enriched category.
+Let $F_1,\cdots,F_n,G \from \oppcat \C \times \C \to \V_1$ be $\V$-enriched profunctors $\C\pto \C$, where $\C$ is a $\V$-enriched category.
 
@@
 We have only considered profunctors going from a category into itself.  
-We might ask what structure is carried by more general profunctors enriched in a multicategory.
-The answer is that they form an \emph{fc-multicategory} \cite{Multicategories}.
+Profunctors in general form a structure called an \emph{fc-multicategory} \cite{Multicategories}, though we shall not be using this notion.
 
@@
   Let $\C$ be a $\V$-enriched category.  
-  Then a promonad $\D\from \C\pto \C$ is the same thing as a $\V$-enriched category $\D$ that admits an identity-on-objects functor $j\from \C \to \D$.
+  Then a promonad $\D\from \C\pto \C$ is the same thing as a $\V$-enriched category $\D$ together with an identity-on-objects functor $j\from \C \to \D$.
 \end{proposition}
@@
   Let $\D\from \C \pto \C$ be such a promonad.  
-  So $\D$ is given by a functor $\D \from \oppcat \C,\C \to \V$, together with extranatural transformations
+  So $\D$ is given by a $\V$-enriched functor $\D \from \oppcat \C,\C \to \V_1$, together with extranatural transformations
   \begin{mathpar}
@@
   If we set $a=b$ in the second diagram and $b=c$ in the third, and compose with the identity multimorphisms $\eta$, then these are exactly the diagrams (see Definition \ref{DefEnrichedCategoryMulticategory}) for $\D$ to have the structure of a $\V$-enriched category on the collection of objects of $\C$!
-  Moreover, $e_{a,b}$ gives us the enriched functor $\C\to \D$, which is the identity on objects and is the multimorphism $e_{a,b}$ on morphisms.
+
+  Then the full versions of the second and third diagrams give us our desired enriched functor $\C\to \D$.  
+  It is the identity on objects and is the multimorphism $e_{a,b}$ on morphisms.
 
@@
 \section{Monoids on functors are multifunctors}
-It might seem strange that the objects of the multicategory of functors are ordinary functors, ignoring the monoidal structure of $\X$ and the multicategory structure of $\M$.  
+It might seem strange that the objects of the multicategory of functors are ordinary functors rather than multifunctors.  
+We appear to have ignored the monoidal structure of $\X$ and the multicategory structure of $\M$.
+
 One way to make sense of this fact is to note that an object of a category $\C$ is the same thing as a functor
@@
 i.e., a monoid in $\M$.
+
+Then the following proposition tells us that the `elements' of $\X \to \M$ in this sense are the multifunctors.
 
@@
 We now come to our main result of the chapter.  
-By way of motivation, consider the two ways of generalizing the notion of an internal monoid in $\Set$.
+We will approach it from an oblique perspective.  
+First note the following two rather different generalizations of the notion of an internal monoid in $\Set$.
 
@@
 
-The work we have done allows us to unify these into a single definition.  
+We shall now attempt to unify these into a single grand unifying generalization of a monoid.
 From Proposition \ref{PropPromonadsAreCategories}, we know that a category with one object is the same thing as a monoid in the category $\Endoprof_\Set(*)$, where $*$ is the category with a single object and only an identity morphism.
@@
 
-Our result is that these two ways of unifying the two generalization of a monoid in fact give the same result.  
+Our main result will tell us that it doesn't actually matter which way round we choose: these two ways of unifying the two generalization of a monoid in fact give the same result.  
 The only ingredient we are missing is an appropriate change of base to move from ordinary $\Set$-enriched categories to $[\M,\Set]$-enriched categories.
@@
   \[
-    \omega_\X\from\Set \to [\X,\Set]
+    \partial_\X\from\Set \to [\X,\Set]
     \]
@@
 \begin{proposition}
-  If $\C_1,\cdots,\C_n$ are categories, then $[\X,\Set]$-enriched functors ${\omega_\X}_*\C_1,\cdots,{\omega_\X}_*\C_n\to[\X,\Set]$ are the same thing as ordinary functors from $\C_1\times\cdots\times\C_n$ to $[\X,\Set]$.
+  If $\C_1,\cdots,\C_n$ are categories, then $[\X,\Set]$-enriched functors ${\partial_\X}_*\C_1,\cdots,{\partial_\X}_*\C_n\to[\X,\Set]$ are the same thing as ordinary functors from $\C_1\times\cdots\times\C_n$ to $[\X,\Set]$.
 \end{proposition}
@@
   \[
-    F \from {\omega_\X}_*\C_1,\cdots,{\omega_\X}_*\C_n \to [\X,\Set]
+    F \from {\partial_\X}_*\C_1,\cdots,{\partial_\X}_*\C_n \to [\X,\Set]
     \]
@@
   \[
-    {\omega_X}_*\C_1(a_1,b_1),\cdots,{\omega_X}_*\C_n(a_n,b_n),F(a_1,\cdots,a_n)\to F(b_1,\cdots,b_n)\,;
+    {\partial_X}_*\C_1(a_1,b_1),\cdots,{\partial_X}_*\C_n(a_n,b_n),F(a_1,\cdots,a_n)\to F(b_1,\cdots,b_n)\,;
     \]
@@
   By naturality of the Yoneda transformation (and the left unitor), this process preserves and reflects the property of respecting composition and units.
-  \label{PropOmegaProperty}
+  \label{ProppartialProperty}
 \end{proof}
@@
   \[
-    [\X,\Endoprof_{\Set}(\C)] \cong \Endoprof_{[X,\Set]}({\omega_\X}_*\C)\,.
+    [\X,\Endoprof_{\Set}(\C)] \cong \Endoprof_{[X,\Set]}({\partial_\X}_*\C)\,.
     \]
@@
     \]
-  of $[\X,\Endoprof_{\Set}(\C)]$ or, by Proposition \ref{PropOmegaProperty}, as the object
+  of $[\X,\Endoprof_{\Set}(\C)]$ or, by Proposition \ref{ProppartialProperty}, as the object
   \[
@@
     \]
-  of $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$.
+  of $\Endoprof_{[\X,\Set]}({\partial_\X}_*\C)$.
   Moreover, every object of each of the two categories arises in such a way.  
@@
 
-  Now let us consider the $F_i,G$ as objects of $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$.  
+  Now let us consider the $F_i,G$ as objects of $\Endoprof_{[\X,\Set]}({\partial_\X}_*\C)$.  
   A multimorphism $F_1,\cdots,F_n\to G$ is given by a transformation
@@
   \[
-    \omega_\X(\C(a,c)) \to G(\blank,a,c)\,;
+    \partial_\X(\C(a,c)) \to G(\blank,a,c)\,;
     \]
@@
 By considering functors as profunctors, we may identify this with a multifunctor $\X \to \Endoprof_\Set(\C)$, which is the same thing as a monoid in $[\X,\Endoprof_\Set(\C)]$.
-Then, by Theorem \ref{StokessTheorem}, we may identify this multifunctor with a monoid in $\Endoprof_{[\X,\Set]}({\omega_\X}_*\C)$; i.e., an $[\X,\Set]$-enriched promonad on ${\omega_\X}_*\C$.
-
-But now, by Proposition \ref{PropPromonadsAreCategories}, this promonad is the same thing as an $[\X,\Set]$-enriched category that has the same objects as $\C$ and admits an identity-on-objects $[\X,\Set]$-enriched functor out of ${\omega_X}_*(\C)$.
+Then, by Theorem \ref{StokessTheorem}, we may identify this multifunctor with a monoid in $\Endoprof_{[\X,\Set]}({\partial_\X}_*\C)$; i.e., an $[\X,\Set]$-enriched promonad on ${\partial_\X}_*\C$.
+
+But now, by Proposition \ref{PropPromonadsAreCategories}, this promonad is the same thing as an $[\X,\Set]$-enriched category that has the same objects as $\C$ and admits an identity-on-objects $[\X,\Set]$-enriched functor out of ${\partial_X}_*(\C)$.
 

### 2019-09-17 Thesis/thesis.tex
Random commit.

@@
 
-In other words, it is a functor $M\from \C\to\C$ together with natural  transformations $m_a \from MMa \to Ma$ and $u_a \from a \to Ma$ such that the following diagrams commute for all objects $a$ of $\C$.
+In other words, a monad is a functor $M\from \C\to\C$ together with natural  transformations $m_a \from MMa \to Ma$ and $u_a \from a \to Ma$ such that the following diagrams commute for all objects $a$ of $\C$.
 
@@
   In the category of sets, the \emph{nonempty powerset functor} $\powerset_+$ sends a set $A$ to the set of nonempty subsets of $A$.  
-  This has the structure of a monad on $\Set$, since we have a natural transformation (union) from $\powerset_+\powerset_+A \to \powerset_+A$ and a natural transformation (singleton) from $A \to \powerset_+A$ that obey the diagrams given above.
+  This functor has the structure of a monad on $\Set$, since we have a natural transformation (union) from $\powerset_+\powerset_+A$ to $powerset_+A$ and a natural transformation (singleton) from $A$ to$ \powerset_+A$ that obey the diagrams given above.
 \end{example}
@@
   are induced from the comonoid structure on $z$.
-  This second example is particularly important in Cartesian closed categories, in which every object has the structure of a comonoid.
+
+  If the monoidal structure on $\M$ is Cartesian, then a comonoid in $\M$ is the same thing as an object $a$ of $\M$ (with the diagonal $a \to a \times a$ and terminal $a \to 1$ morphisms).  
+  In such a case, every object $a$ of $\M$ gives rise to a reader monad on $\M$.
 \end{example}
@@
 
-  As an example, if $\M$ is a monoidal closed category and $w$ is an object of $\M$, then the \emph{state monad} $S_w$ on $\M$ is defined by
-  \[
-    S_w x = w \implies (x \tensor w)\,.
-    \]
+  As an example, the definition of a monoidal closed category $\M$ is that it admits an adjunction between functors $\blank\tensor w$ and $w\implies\blank$ for any object $w$ of $M$.  
+  if $\M$ is a monoidal closed category and $w$ is an object of $\M$, then the functor $S_w$ on $\M$ defined by
+  \[
+    S_w x = w \implies (x \tensor w)
+    \]
+  is the composition of these adjoint functors and therefore inherits the structure of a monad, known as the \emph{state monad}.
 \end{example}
 \begin{example}
-  Another example that arises from an adjunction is the \emph{list monad} on $\Set$ that arises from the adjunction between the category of sets and the category of (set-valued) monoids.  
+  Another example that arises from an adjunction is the \emph{list monad} on $\Set$ that arises from the adjunction between the $\Set$ and the category of monoids.
   The underlying set of the free monoid on a set $A$ is the set $A^*$ of finite lists of elements of $A$, and the functor $A\mapsto A^*$ inherits a monoid structure where the multiplication $m_A\from (A^*)^* \to A^*$ concatenates a list of lists into a single list and the unit $u_a \from A \to A^*$ forms a list with a single element.
@@
 
-Identity arrows are given by the morphisms $u_c\from c \to M c$ (considered as a morphism $c\to c$ in $\Kl_M$) and the composition of arrows $f\from a \to Mb$ and $g \from b \to Mc$ is given by the following composite in $\C$.
+Identity arrows are given by the morphisms $u_c\from c \to M c$ (considered as morphisms $c\to c$ in $\Kl_M$) and the composition of arrows $f\from a \to Mb$ and $g \from b \to Mc$ is given by the following composite in $\C$.
 \[
@@
 Note that $ S J=M$, by one of our coherence conditions on $m$ and $u$.
-Meanwhile, $J S $ is the functor $\Kl_M\to\Kl_M$ that sends an object $a$ to $Ma$ and sends a morphism $f\from a \to Mb$ from $a$ to $b$ to the morphism $Mf\from Ma \to MMb$ from $Ma$ to $Mb$.
+Meanwhile, $J S $ is the functor $\Kl_M\to\Kl_M$ that sends an object $a$ to $Ma$ and sends a morphism $a\to b$ given by a morphism $f\from a \to Mb$ in $\C$ to the morphism $Mf\from Ma \to MMb$, considered as a morphism $Ma \to Mb$ in $\Kl_M$.
 \begin{proposition}[\cite{Kleisli}]
@@
 \end{proposition}
+
+\subsection{Multiplicative natural transformations}
 
@@
 
-A defining property of the Kleisli category is that it is initial among such triples $(\D,F,\psi)$:
+A defining property of the Kleisli category is that it is an initial object in the category of such triples $(\D,F,\psi)$:
 
 \begin{proposition}[\cite{StreetMonads}]
-  i) Given an object $a$ of $\C$, the identity morphism $Ma \to Ma$ may be considered as a morphism $\phi_a \from JMa \to Ja$ in $\Kl_M$.  
-  $\phi_a$ is an $M$-multiplicative natural transformation.
+  i) Given an object $a$ of $\C$, consider the identity morphism $Ma \to Ma$ as a morphism $\phi_a \from JMa \to Ja$ in $\Kl_M$.  
+  Then $\phi_a$ is an $M$-multiplicative natural transformation.
 
@@
   By the enriched Yoneda lemma, such a natural transformation is always given by precomposition with some fixed morphism $\ask_z\from 1 \to z$.  
-  This means that $\Kl_{R_z}$ is suitable for modelling any situation in which we are generally working in $\C$, but need the ability to request a value of type $z$ (for example, a config file, a piece of user input or something else that isn't being passed into the function in question).
+  This means that $\Kl_{R_z}$ is suitable for modelling any situation in which we are generally working in $\C$, but need the ability to request a value of type $z$ (for example, a config file, a piece of user input, a random number or something else that isn't being passed into the function in question).
   \label{ExReaderMonadKleisli}
@@
 From now till the end of the chapter, we fix an base Cartesian closed category $\G$ that admits a denotational semantics of Idealized Algol satisfying Computational Adequacy.
-In addition, we require that $\G$ can be interpreted as being enriched in directed-complete partial orders, in such a way that any compact morphism between the denotation of IA types is the denotation of some IA term.
+In addition, we require that $\G$ can be interpreted as being enriched in algebraic partial orders, in such a way that any compact morphism between the denotation of IA types is the denotation of some IA term.
 The prototypical example, of course, will be the category of games and visible strategies, but we will not exploit any properties of this model beyond the ones we have already mentioned, mentioning it only in examples where appropriate.
@@
 Let $X\in \{\bB,\bN,\bC\}$ be a set that has an interpretation as an Idealized Algol type $X$, and write $X$ also for the corresponding object of $\G$.
-Write $\G_X$ as a shorthand for $\Kl_{R_X}\G$, the Kleisli category for the reader monad on $\G$ corresponding to the object $X$.  
+We shall write $\G_X$ as a shorthand for $\Kl_{R_X}\G$, the Kleisli category for the reader monad on $\G$ that corresponds to the object $X$.  
 The purpose of the rest of this chapter will be to define a new language, give it a denotational semantics in $\G_X$, and prove a full abstraction result for this denotational semantics.
@@
 \[
-  \phi = \phi_X(\id_X) \from 1 \to X\,,
-  \]
-which will be the denotation of the term $\choose_X$.
+  \phi = \Lambda(\lunit_X;\id_X);\phi_X
+  \]
+(where $\Lambda(\lunit_X;\id_X)\from 1 \to (X \to X)$ is the interpretation of the $\lambda$-term $\lambda x.x$), which will be the denotation of the term $\choose_X$.
 Together with the existing denotational semantics of Idealized Algol within $\G$, this gives us an inductively defined denotational semantics of \IAX within $\G_X$.
@@
 
-  We can define this semantics in an alternative, indirect way.  
+  Closer examination of the rules in Figure \ref{FigIaxOpSem} reveals an alternative, indirect definition of the operational semantics of \IAX.
   Note that each rule from ordinary Idealized Algol takes the form
@@
 \begin{example}
-  If $X=\bC$, then, since $X$ has a single element, a sequence $n$ of elements of $X$ may be identified with its length $n$.
-  In this case, the language \IAX gives us a way to model time complexity, and the term $\ask_X$ may be considered as a constant $\sleep\from \com$ whose semantics is to wait for some fixed period of time before continuing.
+  If $X=\bC$, then, since $X$ has a single element $a$, a sequence $u=\underbrace{a\cdots a}_n$ of elements of $X$ may be identified with its length $n$.
+  In this case, the language \IAX gives us a way to model time complexity, and the term $\ask_X$ may be considered as a subroutine $\sleep\from \com$ whose semantics is to wait for some fixed period of time before continuing.
   In this case, 
@@
     \]
-  is interpreted to say that `$M$ converges to $c$ in time $n$'.
+  is interpreted to say that `starting with the store $s$, $M$ converges to $c$ in time $n$, leaving store $s'$'.
+\end{example}
+\begin{example}
+  If $X=\bN$, we can interpret the language \IAX as giving us a way to model user input.  
+  When we call $\ask_\bN$, we are asking the user to provide us as a string of text (which we interpret as a binary string and hence as a natural number).  
+  Then we interpret the judgement
+  \[
+    \Gamma,s\ts M \converges_u c,s'
+    \]
+  as saying that `starting with the store $s$, and the sequence $u$ of user input, $M$ converges to $c$, leaving store $s'$'.
 \end{example}
@@
 
-  We interpret the relation
+  In these cases, we interpret the relation
   \[
@@
 \end{definition}
+In other words, $\tr_u$ is the function that will return the $i$-th term of the sequence $u$ when given $i$ as an input, or will fail to terminate if passed some index $k\ge|u|$.
 
@@
 
-We need a small lemma to help us deal with substitution.
+We start with a small lemma to help us deal with substitution.
 
@@
     \inferrule{\Gamma,s^{(0)}\ts M_1[Q/\ask_X]\converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(n-1)}\ts M_n[Q/\ask_X]\converges c_n,s^{(n)}}
-    {\Gamma,s^{(0)} \ts M[Q/\ask_X] \converges c,s^{(n)}}\,,
+    {\Gamma,s^{(0)} \ts M[Q/\ask_X] \converges c,s^{(n)}}
     \]
@@
 \begin{proof}
-  The real reason this is true is that the term $\ask_X$ is not mentioned anywhere in the IA rules, so substitution of the term $N$ for $\ask$ could not possibly break the pattern.  
+  Informally, this is true because the term $\ask_X$ is not mentioned anywhere in the IA rules, so substitution of the term $Q$ for $\ask_X$ could not possibly break the pattern.  
   Formally, we can show this by inspection on each of the different rules.  
@@
     \]
-  then we have $(M;N)[Q/\ask_X] = M[P/\ask_X];N[P/\ask_X]$ and the inference
+  then we have $(M;N)[Q/\ask_X] = M[Q/\ask_X];N[Q/\ask_X]$ and the inference
   \[
@@
     \]
-  in \IAX.
+  is derivable in \IAX.
   Fix $k\in\bN$ and let $w\in X^*$ be a sequence such that $u$ is a subsequence of $w$ starting at position $k+1$ (i.e., $u^{(j)}=w^{(k+j+1)}$ for each $j=0,\cdots,|u|-1$).
@@
     \and
-    \test_{n+1} = \lambda m.\IfO m \Then \Omega \Else \test_n (\pred m)\,.
+    \test_{n+1} = \lambda m.\neww \lambda x.(x\gets m;\IfO \oc x \Then \Omega \Else \test_n (\pred \oc x))\,.
   \end{mathpar}
@@
   is not equal to $\bot$.
+  \label{DefDenotationalUConvergence}
 \end{definition}
@@
 
-  We can prove this using the following derivation tree.
-  \tiny
+  We can prove this using the derivation tree in Figure \ref{FigKleisliSoundnessDerivation}.\qedhere
+  \begin{SidewaysFigure}
     \[
@@
       \]
-  \normalsize
+    \caption{IA derivation used in the proof of Proposition \ref{PropKleisliSoundness}.}
+    \label{FigKleisliSoundnessDerivation}
+  \end{SidewaysFigure}
 \end{proof}
 
-The statement of Proposition \ref{PropKleisliSoundness} looks a bit strange.  
-This is because the level of generality we are operating at (i.e., $\G$ being a fairly general model for Idealized Algol) does not give us much room to define things other than in terms of the denotations of Idealized Algol terms.
+Definition \ref{DefDenotationalUConvergence} looks a bit odd.  
+This is a result of working at such a high level of generality: since we have not assumed much about $\G$ beyond the fact that it is a suitable model of Idealized Algol, then we have to define everything in terms of Idealized Algol denotations.
 
@@
               &  a  &     \\
-              &     &  k  \\
-  \end{array}\,,
+              &     &  {k\,,}  \\
+  \end{array}
   \]
@@
   (\Var \to \bN) \xrightarrow{\deno{\neww}}
-  \bN \xrightarrow{t_n}
+  \bN \xrightarrow{t_|u|}
   \bC
@@
   \]
-Since complete plays in the game $\oc X \implies \bC$ are always of the form $q$, followed by some sequence of pairs of the form $qx_i$ for $x\in X$, followed by $a$, this is a very natural condition to consider when dealing with a strategy $\sigma\from \oc X \implies \bC$.
+Since complete plays in the game $\oc X \implies \bC$ are always of the form $q$, followed by some sequence of pairs of the form $qx_i$ for $x_i\in X$, followed by $a$, it is very natural to consider conditions on those $x_i$ when dealing with a strategy $\sigma\from \oc X \implies \bC$.
 
@@
 
-First of all, we need to prove a reverse result to Lemma \ref{LemFirstSubstitution} that deals with substitution in the opposite direction; i.e., instead of telling us what happens when we substitute a term for $\ask_X$, we will look at what happens when we substitute a term for $v\gets \suc !v;\tr_u !v$.
+First of all, we need to prove a reverse result to Lemma \ref{LemFirstSubstitution} that deals with substitution in the opposite direction.  
+That is, instead of telling us what happens when we substitute a term for $\ask_X$, we will look at what happens when we substitute a term for $v\gets \suc !v;\tr_u !v$.
 
@@
   Since IA is a deterministic language (so if $\Gamma,s\ts M\converges c,s'$ and $\Gamma,s\ts M \converges c',s''$ then $c=c'$ and $s'=s''$), then the derivation of this term must agree with the valid IA derivation given in Figure \ref{FigTheOneForTheLemma}.
-  It follows that $l=k+1$ (so, in particular, $l\ge k$) and that $x$ is the $(k+1)$-th term of $w$, so the single-term sequence $x$ is the subsequence of $w$ going from $k+1$ to $l$.
+  It follows that $l=k+1$ and that $x$ is the $(k+1)$-th term of $w$, so the single-term sequence $x$ is the subsequence of $w$ going from $k+1$ to $l$.
 
@@
   Consider the denotation $\deno M\from 1 \to \bC$ in $\G_X$ as a morphism $1 \to (X \to \bC)$ in $\G$.  
-  Let $u\in X^*$ be a sequence and suppose that the composite
+  Let $u\in X^*$ be a sequence and suppose that $\deno M \downarrow_u$; i.e., that the composite
   \[
@@
   \[
-    \test_{|u|} (\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v))\\,.
+    \test_{|u|} (\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v))\,.
     \]
@@
 
-  It is easy to see that this is equivalent to derivability of the following relation in Idealized Algol.
+  It is easy to see that this is equivalent to asking whether we can derive the following relation in Idealized Algol.
   \[
@@
 \end{proof}
+
+\begin{remark}
+  Recall that if $\G$ is the category of games, then we have $\sigma\downarrow_u$ if and only if $\sigma$ contains the play 
+  \[
+    \begin{array}{cc}
+      X         & \bC \\
+                &     \\
+                &  q  \\
+      q         &     \\
+      u^{(0)}   &     \\
+      \vdots    &     \\
+      q         &     \\
+      u^{(|u|-1)}&     \\
+                &  a  \\
+                &     \\
+    \end{array}\,.
+    \]
+  Therefore, we have now proved that we have $\blank,() \ts M \converges_u \skipp,()$ if and only if $\deno{M}$ contains that sequence.
+\end{remark}
 
@@
   By currying, we may consider $A$ and $B$ as morphisms $1 \to (A \to B)$ in $\G_X$.
-  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$ and for all sequences $u\in X^*$, if we regard $\sigma;\alpha,\tau;\alpha\from 1 \to \bC$ as morphisms $X \to \bC$ in $\G$, then the composites
+  We say that $\sigma\sim\tau$ if for all morphisms $\alpha\from (A \to B) \to \bC$ and for all sequences $u\in X^*$, if we regard $\sigma;\alpha,\tau;\alpha\from 1 \to \bC$ as morphisms $1 \to (X \to \bC)$ in $\G$, then the composites
   \begin{mathpar}
@@
   Then the denotation of $t\ts C[t]$ is a morphism $\alpha\from \deno{T} \to \bC$.
-  Moreover, the denotation of $C[M]$ is the composite $\deno{M};\alpha$ and that of $C[N]$ is the composite $\deno{N};\alpha$ by functional completeness.
+  Moreover, the denotation of $C[M]$ is the composite $\deno{M};\alpha$ and that of $C[N]$ is the composite $\deno{N};\alpha$ since we are working in a Cartesian closed category.
 
@@
 
-Let us suppose now that $\G$ is the category of games and visible strategies, and that $X=\bC$.  
+For this section, let us suppose that $\G$ is the category of games and visible strategies, and that $X=\bC$.  
 As we remarked above, this means that \IAX can be interpreted as a language for modelling time complexity.
@@
 Here, $\slot$ is a special symbol called a \emph{slot} or \emph{token-action}, which can be interleaved throughout the play $s\vert_{M_A}$ from $A$.  
-We shall additionally impose the requirement that an occurrence of the special symbol $\slot$ must take place either after an $O$-move in $A$ or after another instance of $\slot$.
+We shall also impose the requirement (not found in \cite{SlotGames}) that an occurrence of the special symbol $\slot$ must take place either after an $O$-move in $A$ or after another instance of $\slot$.
 The token actions do not carry justification pointers.
@@
 The identity strategy with costs is the usual identity strategy, without any token actions.  
-Given an interleaving $\s\in(M_A+M_B+M_C+\{\slot\})^*$ of two justified plays with costs for $A \implies B$ and $B\implies C$, write $\s\vert_{A,B}$ for the subsequence consisting of all those moves in $A$ and $B$, together with all token actions such that the previous move was an $O$-move in $A\implies B$.
+We can similarly define an \emph{interaction sequence with costs} to be a sequence $\s\in(M_A+M_B+M_C+\{\slot\})^*$ such that $\s\vert_{A,B,C}$ is an interaction sequence for $A,B,C$ and such that each occurrence of the token action $*$ occurs after a move that could be considered as an $O$-move in either $A\implies B$ or $B\implies C$.
+
+Given such an interaction sequence $\s\in(M_A+M_B+M_C+\{\slot\})^*$ between the games $A$, $B$ and $C$, write $\s\vert_{A,B}$ for the subsequence consisting of all those moves in $A$ and $B$, together with all token actions such that the previous move was an $O$-move in $A\implies B$.
 Define $\s\vert_{B,C}$ similarly.  
@@
 \begin{proof}
-  The map $c$ is the unique functor given by the functional completeness theorem that sends the canonical strategy $\id \from \oc\bC \to \bC$ to the strategy with costs for $\bC$ with maximal play
+  The map $c$ is the unique functor given by the functional completeness theorem (Proposition \ref{pKleisli}) that sends the canonical strategy $\phi \from 1 \to \bC$ to the strategy with costs for $\bC$ with maximal play
   \[
@@
 
-  This functor is the identity on objects, and it is fully faithful, since it has an obvious inverse, given by taking a strategy with costs and replacing each occurrence of the token action with a pair of moves $qa$ in $\oc\bC$.
+  This functor is the identity on objects, and it is fully faithful, since it has an obvious inverse, given by taking a strategy with costs and replacing each occurrence of the token action with a pair of moves $qa$ in $\oc\bC$, where $q$ justifies $a$ and is itself justified by the most recently occurring $O$-move in $A$.
   Since each token action must always occur after an opponent move or after another token action, and since player $O$ has no reply to the move $q$ other than the move $a$, this always gives us a legal strategy.
@@
 We remarked above that if $X\in\{\bB,\bN\}$, then \IAX is a model of nondeterminism, finite in the case of $\bB$ and countable in the case of $\bN$.  
-However, our operational semantics is not the usual one for these languages.
+However, we have given a rather strange operational semantics for these languages (the relation $\converges_u$) that does not accurately reflect how they are normally used.
 
@@
 \end{definition}
-It is clear that these rules are exactly the same as our original operational semantics for \IAX, but with the sequences $u$ removed.  
+These rules are exactly the same as our original operational semantics for \IAX, but with the sequences $u$ removed.  
 Moreover, if we have a valid derivation of $\Gamma,s\ts M\converges u,s'$, then it is clear (by induction) that we may annotate all the occurrences of $\converges$ with suitable sequences in order to obtain a derivation of $\Gamma,s\ts M\converges_u c,s'$ for some $u\in X^*$.
@@
     \]
-  Therefore, $\blank,()\ts C[N] \converges_v \skipp,()$ and so $\blank,()\ts C[N] \converges \skipp,()$.
+  Therefore, $\blank,()\ts C[N] \converges_v \skipp,()$, and so $\blank,()\ts C[N] \converges \skipp,()$.
   The reverse direction is identical.
@@
 \[
-  q (q u^{(i)})_{i=0}^{|u|-1} a\,.
+  \begin{array}{cc}
+    X         & \bC \\
+              &     \\
+              &  q  \\
+    q         &     \\
+    u^{(0)}   &     \\
+    \vdots    &     \\
+    q         &     \\
+    u^{(|u|-1)}&     \\
+              &  a  \\
+              &     \\
+  \end{array}\,.
   \]
@@
 \begin{proof}
-  A complete play in $\sigma;\tau$ is given by a sequence $\s\vert_{X,A,C}$, where $\s\in (M_X + M_A + M_B + M_C)^*$ that is a legal interaction of a complete play in $\tau$ with a collection of complete plays in $\sigma$, with $B$-components being identified.
+  A complete play in $\sigma;\tau$ is given by a sequence $\s\vert_{X,A,C}$, where $\s\in (M_X + M_A + M_B + M_C)^*$ is a legal interaction of a complete play in $\tau$ with a collection of complete plays in $\sigma$, with $B$-components being identified.
   Then $\s\vert_{A,C}$ can alternatively be characterized as $\t\vert_{A,C}$, where $\t\in (M_A + M_B + M_C)^*$ is a legal interaction of a sequence from $\tau\vert_{B,C}$ with a collection of sequences from $\sigma\vert_{A,B}$.
@@
 It is already known (see \cite{mcCHFiniteND}) that this model is fully abstract for (finitely or countably) nondeterministic Idealized Algol with may-contextual equivalence.
+We have just provided an alternative proof of this fact.
 
@@
 \begin{definition}
-  We shall define a relation
+  We define a relation
   \[
@@
   \[
-    \inferrule*[sep=1.9em]{\Gamma,s^{(0)}\ts M_1 \converges c_1,s^{(1)} \\ \cdots \\ \Gamma,s^{(j-2)} \ts M_{j-1} \converges c_{j-1} \\ \Gamma,s^{(j-1)}\ts M_j\diverges}
+    \inferrule*[sep=1.9em]{\Gamma,s^{(0)}\ts M_1 \converges c_1,s^{(1)} \and \cdots \\ \Gamma,s^{(j-2)} \ts M_{j-1} \converges c_{j-1},s^{(j-1)} \\ \Gamma,s^{(j-1)}\ts M_j\diverges}
     {\Gamma,s^{(0)} \ts M \diverges}\,.
@@
 
-It is possible to characterize the $\mustconverge$ directly via an inductive relation (see \cite{RusssThesis}, for instance).  
-We will give an alternative definition that will relate it to our existing rules $\converges_u$.
+\begin{remark}
+It is possible to characterize the $\mustconverge$ predicate directly via an inductive relation (see \cite{RusssThesis}, for instance).  
+\end{remark}
+
+We will give an alternative definition of $\mustconverge$ that will relate it to our existing rules $\converges_u$.
 
@@
 Before we show that the two definitions are equivalent, we shall examine why this one makes sense.  
-Recall that we said that the statement $\Gamma,s\ts M\converges_u c,s'$ meant that $M$ will converge to $c$ in the case that the values we obtain by querying the nondeterministic oracle form the sequence $u$.
-Our initial thought, then, might be to say that $\Gamma,s\ts M\mustconverge$ if for all $u\in X^*$, $\Gamma,s\ts M\converges_u c,s'$ for some $c,s'$, but this is not the case.  
+Recall that we said that the statement $\Gamma,s\ts M\converges_u c,s'$ meant `$M$ will converge to $c$ in the case that the values we obtain by querying the nondeterministic oracle form the sequence $u$'.
+Our initial thought, then, might be to declare that $\Gamma,s\ts M\mustconverge$ if for all $u\in X^*$, $\Gamma,s\ts M\converges_u c,s'$ for some $c,s'$.  
+However, this is not the case even for terms that clearly have to converge.
 For example, if we have
@@
   \]
-then $M\converges_\true \true$ and $M\converges_\false \false$.  
-However, it is not the case that $M\converges_\epsilon c$, nor that $M\converges_{\true\false\false\true\false}c$ for any $c$.
-Instead, we should think of the nondeterministic oracle as a promise to provide us with some infinite sequence of elements of $X$, only some of which we will use to converge.
+then $M\converges_\true \true$ and $M\converges_\false \false$, and it is certainly true that $M\mustconverge$.
+However, it is not the case that, for example, $M\converges_\epsilon c$; nor is it the case that $M\converges_{\false\false\true\false\true}c$ for any $c$.
+In the first case, the sequence is too short: we can extend it to the sequence $\true$ and then we get convergence.  
+In the second case, the sequence is too long: we have already converged after the first term $\false$, so we never get the chance to read any other terms.
+
+We could define $M\mustconverge$ by saying that any sequence $u$ is either a subsequence or a supersequence of some $v$ such that $M\converges_v$; our equivalent definition above is a little neater.  
+The idea is that if we fix beforehand an infinite sequence made up of all the values that the nondeterministic oracle could possibly give, then we know that the term will always end up reading some finite sequence of values from the beginning of the sequence and then terminating at a value.
 
@@
 
-  For the converse, define an \emph{$n$-truncated} derivation tree to be a derivation tree of height $n$ such that the premises of the form $\Gamma,s\ts M\diverges^w$ may occur at the top level without proof.
-  Then we define a family of functions $(F_i \suchthat i \ge 0)$ that take an infinite sequence $w\in X^\omega$ and a triple $\Gamma,s\ts M$ and returns either a proof of height $\le i$ of $\Gamma,s\ts M\converges_u c,s'$ for some $u\pprefix w$, or some $i$-truncated proof of $\Gamma,s\ts M\diverges^v$ for some (possibly infinite) $v\prefix w$.
-
-  For $i=0$, $F(w,\Gamma,s\ts M)$ is the tree of the form
+  For the converse, define an \emph{$n$-truncated} derivation tree to be a derivation tree of height $n$ such that premises of the form $\Gamma,s\ts M\diverges^w$ may occur at the top level without proof.
+  We now define, for any infinite sequence $w\in X^\omega$, any triple $\Gamma,s\ts M$ and any $i\ge 0$, either
+  \begin{itemize}
+    \item a proof of height $\le i$ that $\Gamma,s\ts M\converges_u c,s'$ for some $u\pprefix w$ (and some $c,s'$); or
+    \item an $i$-truncated proof $F_i(w,\Gamma,s\ts M)$ of $\Gamma,s\ts M\diverges^v$ for some (possibly infinite) $v\prefix w$.
+  \end{itemize}
+  Moreover, the $F_i(w,\Gamma,s\ts M)$ will form an infinite sequence, so that if $i<j$ then $F_i(w,\Gamma,s\ts M)$ is the result of truncating $F_j(w,\Gamma,s\ts M)$ at the $i$-th level.
+
+  For $i=0$, $F_i(w,\Gamma,s\ts M)$ is the tree of the form
   \[
@@
 
-We therefore get an adequacy result for must testing.
+We can now get an adequacy result for must testing.
 
@@
   is not equal to $\bot$.
+  \label{DefDenoMust}
 \end{definition}
@@
 
-Once again, this slightly abstruse result becomes much more natural when $\G$ is the category of games, though in this case things are a bit more subtle.  
+Once again, this slightly abstruse Definition \ref{DefDenoMust} becomes much more natural when $\G$ is the category of games, though in this case things are a bit more subtle.  
 Let $\sigma$ be a strategy for $\oc X \implies \bC$.  
@@
   Let $M\from \com$ be a closed term of \IAX and consider the denotation $\deno M \from 1 \to \bC$ in $\G_X$ as a morphism $X \to \bC$ in $\G$.
-  Then $\blank,()\ts M\mustconverge$ if and only if this strategy is winning.
+  Then 
+  \[
+    \blank,()\ts M\mustconverge
+    \]
+  if and only if this strategy is winning.
 \end{corollary}
 
-\section{Full Abstraction for Nondeterminism Under Must Testing}
+\section{Full Abstraction for Finite Nondeterminism Under Must Testing}
 
@@
 \begin{definition}
-  Given closed terms $M,N\from T$ of \IAX, we write $M\equiv_{\must} N$, if for all contexts $-\from T\ts C[-]\from\com$, $C[M]\mustconverge$ if and only if $C[N]\mustconverge$.
+  Given closed terms $M,N\from T$ of \IAX, we write 
+  \[
+    M\equiv_{\must} N
+    \]
+  if for all contexts $-\from T\ts C[-]\from\com$, $C[M]\mustconverge$ if and only if $C[N]\mustconverge$.
 \end{definition}
@@
 \begin{remark}
-  In the category of games we can simplify this to saying that $\sigma;\alpha\approx_{\may}\tau;\alpha$ and that either $\sigma;\alpha$ and $\tau;\alpha$ are both winning, or neither is.
+  In the category of games we can simplify the definition of $\smam$ to saying that $\sigma\smam \tau$ if for all $\alpha\from (A \to B) \to \bC$, $\sigma;\alpha\approx_{\may}\tau;\alpha$ and either $\sigma;\alpha$ and $\tau;\alpha$ are both winning, or neither is.
 \end{remark}
@@
   is not equal to $\bot$.  
-  Since $M\sim_{\must} N$, there is some finite prefix $v\pprefix w$ such that the composite
+  Since $M\sim_{\must} N$, there is some finite prefix $v\pprefix w$ and some compact $\alpha'\from \deno{T}\to\bC$ such that the composite
   \[
@@
   Let $V$ be the set of all sequences $v\in \bB^*$ such that $v$ has no prefix $u$ with this property.  
-  Then by hypothesis $V$ is a finitely branching tree with no infinite path so, by K\"{o}nig's Lemma, it is finite.  
-  Therefore, there is some finite set of sequences $U\subset \bB^*$ such that for every sequence $w\in \bB^\omega$, $w$ has some prefix $u\in U$ satisfying the condition above.
+  Then $V$ is a finitely branching tree with no infinite path so, by K\"{o}nig's Lemma, it is finite.  
+  Therefore, there is some finite set of sequences $U\subset \bB^*$ such that for every sequence $w\in \bB^\omega$, $w$ has some prefix $u\in U$ such that $\deno{M};(X \to \alpha);\mu;\eta_u;\deno{\neww};t_{|u|}\ne\bot$.
 
@@
 
-Now clearly this last result depends on finiteness of $\bB$, since we may have infinite trees with no infinite path if the trees are allowed to be infinitely branching.
-The next result shows that if we replace $\bB$ with $\bN$, then we cannot hope to obtain such a full abstraction result.
+This last result makes crucial use of the finiteness of $\bB$ in order to apply K\"{o}nig's lemma.  
+In the case of IA${}_\bN$, the argument we have just used does not apply, since we can certainly have infinite bounded-height trees if we allow infinite branching.
+
+In fact, this point is essential: not only does this specific argument not work for our model of IA${}_\bN$, the model is not necessarily Fully Abstract at all! 
+In particular, if $\G$ is the category of games, then the semantics of must testing in $\G_{\bN}$ is not Fully Abstract.
+The next result will show that no model of countable nondeterminism can be Fully Abstract, subject to some rather mild assumptions.  
+We will then explore how we can come up with a model for which these assumptions do not hold, and eventually prove a Full Abstraction result.
+
+\subsection{Full Abstraction for Countable Nondeterminism under Must Testing}
 
@@
   $\Int n$ first checks whether its argument $n$ is the encoding of a valid IA term of type $\nat$; if it is not, then it returns the value $0$, which will take the place of an error value.
-  If it is, then $\Int n$ evaluates the program corresponding to $n$; if this evaluation terminates, then it adds $1$ to the value returned and returns that.  
+  If it is -- say, $n=\encode{P}$, then $\Int n$ evaluates the program $P$; if this evaluation terminates, then it adds $1$ to the value returned and returns that.  
   The reason we add $1$ to the value is primarily to avoid the error value $0$, though it will serve a purpose later too.
+
+  We now consider a slight variation $\Int'$ of the term $\Int$, which takes in an additional parameter called a \emph{timeout}.  
+  $\Int' n \encode{P}$ will evaluate the term $P$ for $n$ steps, returning $m+1$ as before if $P$ converges to $m$ in that time, and otherwise returning $0$ if $P$ has not yet terminated after $n$ steps.
 
@@
   First, note that $M$ and $N$ have the same behaviour in any applicative context; i.e., if $F\from \nat \to \nat$ is a term, then $MF\converges \skipp$ if and only if $NF\converges\skipp$ and $MF\mustconverge$ if and only if $NF\mustconverge$.
-  Indeed, we certainly have $NF\converges\skipp$ and $NF\diverges$.
-  Moreover, $MF\converges\skipp$, so we need to show that $MF\diverges$.
-
-  Consider the evaluation path of $M$ in which the variable $p$ acquires the value $\encode F$ at the beginning.  
-  If $F (\encode F)$ diverges, then the whole term will diverge.  
-  Otherwise, there is some value $k$ such that $F (\encode F)$ converges to a value $n$ after $k$ steps.
+  Indeed, we certainly have $MF\converges\skipp$ and $NF\converges\skipp$.
+  Moreover, $NF\diverges$, so we need to show that $MF\diverges$.
+
+  Consider the following evaluation path of $MF$.
+  \begin{enumerate}
+    \item The variable $p$ acquires the value $\encode F$.  
+      At this point, we apply $F$ to $\encode F$.  
+      If this computation diverges, then we win.  
+      Otherwise, suppose that $F\encode F$ converges to some value $n$.  
       Then $v$ acquires the value $n$.
-  Consider the path where $\ask_\bN$ on the third line acquires the value $k$.  
-  Then $\Int' k (\app F !p \encode{!p})$ will carry out the computation of $F (\encode F)$, returning the value $n$, but will then add $1$ to that value before returning.  
-  The result is that $v$ holds the value $n$ and $x$ holds the value $n+1$.  
-  Therefore, the term diverges.
+      Let $k$ be the number of steps taken for $P$ to converge to $n$.
+    \item Now suppose that the next instance of $\ask_\bN$ acquires the value $k$.  
+      We already know that $\Int' k (\app \oc p \encode{\oc p})$ will converge to $n+1$, so $x$ acquires the value $n+1$.
+    \item Now $n+1 \ne n$, so the term diverges.
+  \end{enumerate}
+  Therefore, $MF\diverges$.
 
@@
 
-  Indeed, let $\phi\from \bN \to \bN$ where $\phi(p)$ is $n+1$ if $p$ is the encoding of a term $P\from\nat \to \nat$ and $P\;p\converges n$ and $0$ otherwise (including the case that $P\;p\diverges$).
+  Indeed, let $\phi\from \bN \to \bN$ where $\phi(p)$ is $n+1$ if $p$ is the encoding of a term $P\from\nat \to \nat$ and $P\;p\converges n$ and $\phi(p)=0$ otherwise (including the case that $P\;p\diverges$).
 
@@
 
-At the extreme, if the category $\G$ satisfies the property (universality) that every morphism between the denotations of IA types is the denotation of an IA term, then we can get the full abstraction result we desire.
+In order to get around this problem, then, we will clearly need to disallow noncomputable functions $\bN\to\bN$, which quickly entails that we should disallow all morphisms that are not computable.
+
+Such models were considered by Hyland and Ong \cite{hoPcf} and by Abramsky, Jagadeesan and Malacaria \cite{ajmPcf} in their original proofs of Full Abstraction for PCF.
+In these models, a game (or arena) $A$ comes equipped with an encoding function $M_A \to \bN$; a strategy is said to be \emph{recursive} if it can be defined by a recursive function $\bN \to \bN$.
+The remarkable thing about these models is that they satisfy a property called \emph{universality}: \emph{every} morphism into the denotation of one of the types of the language is definable.
+
+Suppose our model $\G$ of Idealized Algol satisfies universality.  
+Then it is relatively easy to pass from Computational Adequacy to Full Abstraction.
 
@@
 
-The next step is to find an example of such a $\G$, which we will do by cutting down the set of strategies in our category of games to those that are in some sense computable.  
+The next step is to find an example of such a $\G$.
+As we said earlier, we will do this by cutting our game semantics down so that it only contains \emph{computable} strategies.
 The first step is to fix an enumeration $e_A\from M_A \to \bN$ of the moves of each game $A$.  
@@
 It follows, then, that any recursive \emph{visible} $\sigma\from \deno T$ is the denotation of some Idealized Algol term $M \from T$.
-Thus, the category $\G^{rec}$ of games and recursive visible strategies is universal for Idealized Algol, and thus its Kleisli category $\G^{rec}_X$ is fully abstract for \IAX.
+Thus, the category $\G^{rec}$ of games and recursive visible strategies is universal for Idealized Algol, and therefore its Kleisli category $\G^{rec}_X$ is fully abstract for \IAX.
 
@@
   Since $\deno M$ and $\deno N$ do not differ until the very last move, this means that $\alpha$ must respond to the initial move $q$ in the rightmost copy of $\bC$ with the move $q$ in the copy of $\bC$ on the left (otherwise, $\deno N;\alpha$ is winning), and that $\alpha$ must be total (otherwise, $\deno M;\alpha$ is not winning).
-  Then we see that for any value of $p$, $\alpha$ must reply to the move $p$ with the number $\phi(p)$, where $\phi$ is the number defined above.  
+  Then we see that for any value of $p$, $\alpha$ must reply to the move $p$ with the number $\phi(p)$, where $\phi$ is the function defined above.  
   Otherwise, $\deno M;\alpha$ is not winning.
@@
 \section{The Intrinsic Equivalence Relation}
+\label{SecIntrinsicEquivalenceRelationKleisli}
 

### 2019-09-17 Thesis/complete_thesis.tex
Random commit.
The final commit?

@@
 
+\section*{Acknowledgements}
+
+There are many people and organizations to whom I owe a debt of gratitude, and without whom this thesis would not have been written.  
+My first thanks go to EPSRC research grant EP/K018868/1 for funding my PhD, keeping me fed and housed for three and a half years, and sponsoring several trips to conferences and schools at home and abroad.
+I am also indebted to the organizers of those conferences and schools, including but not limited to 
+\begin{itemize}
+  \item Paul Blain Levy, Juha Kontinen, Marina Lenisa, Ugo dal Lago and Gabriel Sandu, chairs of various iterations of GaLoP (and, in Paul's case, organizer of the Midlands Graduate School 2016);
+  \item Filippo Bonchi and Barbara K\"{o}nig, organizers of CALCO 2017;
+  \item Matthias Felleisen, Robby Findler, Matthew Flatt, Shriram Krishnamurthi, Jay McCarthy, and Justin Pombrio, teachers at the Racket Summer School 2017;
+  \item Moshe Vardi, Daniel Kroening and Marta Kwiatkowska, co-chairs of FloC 2018; and
+  \item Dan Ghica and Achim Jung, co-chairs of CSL 2018.
+\end{itemize}
+I would also like to express gratitude to those people whom I have had productive discussions with at conferences and during departmental visits: in particular, Martin Hyland, Paul-Andr\'{e} \Mellies, Paul Levy and Pierre Clairambault.
+
+Thank you to the anonymous reviewers from CALCO 2017, LICS 2018, CSL 2018 and FoSSaCS 2019 for your careful comments, all of which have shaped this thesis in some way.
+
+Thank you to the whole Computer Science Department at the University of Bath, particularly the Mathematical Foundations team, for all your help over the years.  
+Congratulations to John Power on the conclusion of a momentous career, and thanks for helping me with my category theory.  
+Thank you too to Ben, David and Alessio for organizing the Departmental Seminar at Bath and for being such good colleagues.
+
+Thank you to my family for all your support during my PhD.  
+Thank you to Ellie for your patience and love, and for enduring a three-year long-distance relationship while I was in Bath.  
+This thesis is dedicated to you.
+
+Lastly, there would be no thesis at all without my PhD supervisor, Jim Laird, who took me on when I had little to no knowledge of the subject and has carefully guided me throughout.  
+That I am able to submit this now is testament to Jim's compendious knowledge of the subject and his patience in imparting some of it to me.  
+At all stages of my PhD, I have been able to rely on our weekly meetings for insight when I was stuck or unsure about the correct direction to investigate.  
+In addition, Jim often encouraged me to submit papers to workshops and conferences, even in the early stages of my PhD, and the experience of doing so has shaped the direction of my research, and helped me form valuable relationships with other researchers.
+
+\begin{abstract}
+  Starting with a Fully Abstract denotational semantics for an Algol-like programming language, we investigate how we can use techniques of categorical algebra to adapt the semantics when the original language is extended with various nondeterministic effects.
+  Our running example for the base denotational semantics is Abramsky and McCusker's game semantics for Idealized Algol \cite{SamsonGuyIAActive}.  
+  We give a full presentation of this game semantics, including an alternative proof of Computational Adequacy that uses Laird's concept of a sequoidal category \cite{laird02} rather than the combinatorial proof from Abramsky and McCusker's original paper.
+
+  We introduce the familiar concepts of monads and Kleisli categories, and prove a Full Abstraction result that shows how the process of passing to certain Kleisli categories corresponds to particular language extensions.
+  We link these language extensions to may- and must-testing for finite and countable nondeterminism, showing how we can construct Fully Abstract models of these effects using Kleisli categories.
+
+  We introduce a generalization of monads: lax actions, also known as parametric monads.
+  We investigate various corresponding generalizations of Kleisli categories, and prove a Full Abstraction result for one such generalization, showing how it too can be used to construct a model of an extended version of our original Algol-like language.
+  We show how a special case of this construction can be adapted to model a probabilistic language.
+\end{abstract}
+
 \input{intro}

### 2019-09-17 Thesis/conc.tex
The final commit?

@@
 We have then applied the second part of Levy's technique -- \emph{hiding} -- to remove the explicit information and yield a pure, computationally adequate model of countable nondeterminism.
+
+\section{Afterword}
+
+The aim of this thesis was to demonstrate how techniques of categorical algebra can be applied to the study of Full Abstraction for programming languages.
+I can think of two main benefits of this combination.
+The first is a technical one: the results that we have proved are very generally applicable, and it would not be unreasonable to hope that they could be applied in the future to help construct new Fully Abstract models of programming languages.
+The second reason is less precise, but equally important: throughout this thesis, we have endeavoured to clear up some of the mystery surrounding Full Abstraction, particularly in Game Semantics.  
+The idea of using monads and Kleisli categories to model computational effects has a long history, but work in Full Abstraction, though it sometimes uses category-theoretic techniques, has often seemed fairly \emph{ad hoc}.
+My hope is that the work presented here -- including both the sequoidal-exponential semantics for Idealized Algol and the work on Kleisli categories and parametric monads -- has gone some way towards explaining where some of the constructions used in Game Semantics come from.
+
+One of the themes in this thesis has been an attempt to push results as far as they can go: thus, we have tried as far as possible to use, for example, Computational Adequacy results for a base language in order to prove Computational Adequacy for an extended language, rather than writing on a stand-alone proof.
+To an extent, we have been forced to do this by the level of generality we have been working at, but I hope that our focus on syntactic rather than semantic results has helped shift the focus away from the properties of any particular model.

### 2019-09-17 Thesis/intro.tex
The final commit?

@@
 \end{lstlisting}
-then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: indeed, since Haskell evaluates inputs to functions lazily, evaluating \lstinline[language=haskell]{g (diverge 0)} will not evaluate the non-terminating term \lstinline[language=haskell]{(diverge 0)} and will terminate at the value \listinline[language=haskell]{0}, while \lstinline[language=haskell]{f (diverge 0)} \emph{will} evaluate \lstinline[language=haskell]{(diverge 0)} and will itself fail to converge.
+then it becomes clear that \lstinline[language=haskell]{f} and \lstinline[language=haskell]{g} are not interchangeable: indeed, since Haskell evaluates inputs to functions lazily, evaluating \lstinline[language=haskell]{g (diverge 0)} will not evaluate the non-terminating term \lstinline[language=haskell]{(diverge 0)} and will terminate at the value \lstinline[language=haskell]{0}, while \lstinline[language=haskell]{f (diverge 0)} \emph{will} evaluate \lstinline[language=haskell]{(diverge 0)} and will itself fail to converge.
 
@@
 
-Then, following Scott \cite{ScottDomains}, we refined this model to one based on partially-ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.
+Then, following Scott \cite{ScottDomains}, we refined this model to one based on partially ordered sets -- more specifically, \emph{Scott domains} -- in which we modelled the behaviour or a program via an associated Scott-continuous functions between domains.
 

### 2019-09-17 Thesis/pmonads.tex
The final commit?

@@
 \end{mathpar}
-Since lax actions generalize monads, we shall sometimes follow \Mellies \cite{ParametricMonads} and refer to them as \emph{parametric monads}.
+Since lax actions are a generalization of monads, we shall sometimes follow \Mellies \cite{ParametricMonads} and refer to them as \emph{parametric monads}.
 We shall not be considering strong actions (for which $m,e$ are required to be isomorphisms), so we shall sometimes say `action' to mean `lax action'.
@@
   Let $\X,\YY$ be a monoidal category and let the functor category $[\YY,\Set]$ be equipped with the Day convolution product.
+
   Given a functor $F \from \X \times \YY \to \Set$, we have an associated functor $\Lambda(F) \from \X \to [\YY,\Set]$.

### 2019-09-17 Thesis/pmonads2.tex
The final commit?

@@
 
-We fix a model $\G$ of Idealized Algol as above, and suppose that the datatypes in $\G$ are interpreted via an oplax monoidal functor $\Set \to \G$.  
+Having fix a model $\G$ of Idealized Algol as above, suppose that the datatypes in $\G$ are interpreted via an oplax monoidal functor $\Set \to \G$.  
 Then we get an oplax monoidal functor $\X \to \G$, inducing a reader action of $\oppcat\X$ on $\G$ such that the category $\G/\oppcat\X$ is Cartesian closed.  
@@
 
-We make the connection between the languages \IAX and \IAXX more explicit in the following series of lemmas.
-In this section, we will make use of an encoding between an object of the form $jp$ and an Idealized Algol datatype $N$.  
-The case we have in mind is when $jp$ is some finite set and $N$ is the natural number object, so that we can choose some way of representing elements of $jp$ as elements of $N$.
+Having noted the connection between the operational semantics of \IAX and \IAXX, we now link the denotational semantics of the two languages.  
+Recall that a morphism $A \to B$ in our model of \IAX was a Kleisli morphism; i.e., a morphism of the form
+\[
+  A \to (X \to B)
+  \]
+in the original category, while a morphism $A \to B$ in the category $\G/\oppcat\X$ is a \Mellies morphism; i.e., a morphism
+\[
+  A \to (j(x) \to B)
+  \]
+for some object $x$ of $\X$.  
+Now, if we can ensure that $j(x)$ is a set corresponding to an IA datatype, then we can treat this \Mellies morphism as a Kleisli morphism and start to pull results from Chapter \ref{ChapMonads} over to the parametric monad case.
+
+We have already required that the terms $\choose_{p}$ are such that $j(p)$ is always an IA datatype.  
+However, when we compose two \Mellies morphisms together, we take the tensor product of the corresponding objects of $\X$.  
+Therefore, we need to ensure that we can represent $j(p_1 \tensor \cdots \tensor p_n)$ using an IA datatype, for any finite collection $p_i$ of objects of $\X$ such that $j(p_i)$ is an IA datatype for all $i$.
+
+We shall therefore assume that, whenever $p_1,\cdots,p_n$ is a finite collection of objects of $\X$ such that the set $j(p_i)$ is an IA datatype for all $i$.
+
+The case we have in mind is when the $j(p_i)=\bB$ for all $i$ and $N$ is the natural number object, so that we can choose some way of representing elements of $jp$ as elements of $N$.
 
@@
     \]
-  be an inference of IA${}_{j(N)}$, where every instance of $\ask_{j(N)}$ occurs as part of some term $\neww (\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)$, and suppose that $M\ne \neww(\lambda v.v\gets\ask_{j(N)};\Pi_j\oc v)$ for any $j$.
+  be an inference of IA${}_{j(N)}$, where every instance of $\ask_{j(N)}$ occurs as part of some term of the form $\neww (\lambda v.v\gets \ask_{j(N)};\Pi_i \oc v)$, and suppose that $M\ne \neww(\lambda v.v\gets\ask_{j(N)};\Pi_j\oc v)$ for any $j$.
   Suppose we have sequences $U_1,\cdots,U_n$ such that $u_k$ covers $U_k$ for $k=1,\cdots,n$.
@@
 
-  i) $\Gamma,s\ts M[\choose_{p_i/x_i}]\converges_U c,s'$.
-
-  ii) $\Gamma,s\ts M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v/x_i]\converges_u c,s'$ for all $u$ covering $U$.
-
-  iii) $\Gamma,s\ts M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v/x_i]\converges_u c,s'$ for some $u$ covering $U$.
+  i) $\Gamma,s\ts M[\choose_{p_i/x_i}]\converges_U c,s'$ in \IAXX.
+
+  ii) $\Gamma,s\ts M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v/x_i]\converges_u c,s'$ in IA${}_N$ for all $u$ covering $U$.
+
+  iii) $\Gamma,s\ts M[\neww(\lambda v.v\gets\ask_{j(N)};\Pi_i \oc v/x_i]\converges_u c,s'$ in IA${}_N$ for some $u$ covering $U$.
   \label{LemComputationalAdequacyIaxx}
@@
 To solve the second problem, we make an additional small assumption on our category $\G$.  
-We require that there exist morphisms
+We require that our category $\G$ contains morphisms
 \[
@@
   \]
-for any set $X$ and any finite sequence $u\in X^*$ such that for any function $f \from X \to Y$, we have $(f\to \bC);\xi_u = \xi_{f_*u}$, where $f_*u$ is the sequence formed by applying $f$ pointwise to $u$, and such that if $X$ is an IA datatype, then
+for any set $X$ and any finite sequence $u\in X^*$ such that for any function $f \from X \to Y$, we have $(f\to \bC);\xi_u = \xi_{f_*u}$ (where $f_*u$ is the sequence formed by applying $f$ pointwise to $u$), and such that if $X$ is an IA datatype, then
 \[
@@
 \begin{example}
-  In the category of games, the morphisms $\xi_u$ are the strategies containing the plays $\epsilon$, $qq$ and plays of the form
+  In the category of games, the morphisms $\xi_u$ can be taken to be the strategies containing the plays $\epsilon$, $qq$ and plays of the form
   \begin{mathpar}
@@
   \end{mathpar}
-  (so the strategy has no reply if player $O$ asks the question in $X$ fewer than $|u|$ times, or tries to ask it more than $|u|$ times).
+  (so the strategy has no reply if player $O$ asks the question in $X$ fewer than $|u|$ times before returning, or tries to ask it more than $|u|$ times).
 \end{example}
@@
 
-Recall that a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an equivalence class of \Mellies morphisms $1 \to (j(p) \to \bC)$ in $\G$, where $p$ ranges over the objects of $\X$, and where the equivalence relation is generated by identifying all pairs of morphisms $\sigma \from 1 \to (j(p) \to \bC)$ and $\tau \from 1 \to (j(q) \to \bC)$ such that there is a morphism $f \from p \to q$ such that $\tau;(j(f)\to\bC)=\sigma$.
+Recall that a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an equivalence class of \Mellies morphisms $1 \to (j(p) \to \bC)$ in $\G$, where $p$ ranges over the objects of $\X$, and where the equivalence relation is generated by identifying all pairs of morphisms $\sigma \from 1 \to (j(p) \to \bC)$ and $\tau \from 1 \to (j(q) \to \bC)$ such that there is a morphism $f \from p \to q$ such that $\tau;(j(f)\to A)=\sigma$.
 
@@
 
+For example, if $j(p_i) = \bB$ for all $i$, then we can take $N=\bN$ and use the binary encoding.
+
 \begin{definition}
@@
 \begin{theorem}[Equational Soundness for \IAXX]
-  Let $M,M'\from T$ be closed terms of \IAXX such that $\deno{M}\sim\deno{N}$.
+  Let $M,M'\from T$ be closed terms of \IAXX such that $\deno{M}\sim\deno{M'}$.
   Then $M$ and $M'$ are observationally equivalent.
+  \label{TheEquationalSoundnessIAXX}
 \end{theorem}
@@
   Then $\Lambda(\deno{M});\alpha$ is the denotation of $C[M]$ and $\Lambda(\deno{M'});\alpha$ the denotation of $C[M']$.  
-  By Theorem \ref{TheComputationalAdequacyIAXX}, the sets $(N,\Acc(\Lambda(\deno{M});\alpha))$ and $(N,\Acc(\Lambda(\deno{M'})))$ are inequivalent, and so $\deno M \not\sim\deno{M'}$.
-\end{proof}
-
-Unfortunately, compact definability does not hold for this setup in general.  
-In the next section we will develop an important special case -- a semantics of Probabilistic Algol -- for which we will be able to prove Full Abstraction.
+  By Theorem \ref{TheComputationalAdequacyIAXX}, the sets $(N,\Acc(\Lambda(\deno{M});\alpha))$ and $(N,\Acc(\Lambda(\deno{M'};\alpha)))$ are inequivalent, and so $\deno M \not\sim\deno{M'}$.
+\end{proof}
+
+\subsection{Full Abstraction for \IAXX}
+
+In order to prove Full Abstraction, we first prove a compact definability result.
+
+\begin{definition}
+  Let $\sigma\from A \to B$ be a morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
+  We say that $\sigma$ is \emph{compact} if it is compact when considered as a morphism in $\G$.
+\end{definition}
+
+\begin{remark}
+  When we say `considered as a morphism in $\G$' in the above definition, we mean `in at least one of its possible interpretations as a morphism in $\G$'.  
+  Note, however, that the continuous image of a compact element is compact, and so if we pass to a new representative of $\sigma$ by composing on the left by the image of some morphism in $\Rv_{\Omega}^{FS}$, then the resulting representative of $\sigma$ will also be compact.
+
+  Lastly, if $\G$ is the category of games, this compactness property is invariant under the choice of representative for $\sigma$.
+\end{remark}
+
+In order to prove compact definability, we need to make a further assumption.
+
+\begin{proposition}[{Compact Definability for \IAXX}]
+  Suppose the functor $j \from \X \to \Set$ is strong monoidal and that for any object $x$ of $\X$ there is a finite collection $p_1,\cdots,p_n$ such that $j(p_i)$ is an IA datatype for each $i$ and such that there is a morphism
+  \[
+    h \from j(p_1) \times \cdots \times j(p_n) \to x\,.
+    \]
+  Then any compact morphism in $\G/\oppcat \X$ between denotations of IA types is definable.
+  \label{PropIAXXCompactDefinability}
+\end{proposition}
+\begin{proof}
+  Let $\sigma \from \deno S \to \deno T$ be a morphism in $\G/\oppcat \X$, where $S$ and $T$ are IA types.  
+  After composing with some suitable $h$ as above, we may assume that $\sigma$ is given by a compact morphism
+  \[
+    \deno S \to j(p_1 \tensor \cdots \tensor p_n) \to \deno T
+    \]
+  in $\G$.  
+  After precomposing with the multiplicative coherence for $j$ on the $p_i$, we get a compact morphism
+  \[
+    \deno S \to (j(p_1) \times \cdots \times j(p_n) \to \deno T)\,,
+    \]
+  which is the denotation of some term-in-context
+  \[
+    x \from S,a_1 \from p_1,\cdots,a_n\from p_n \ts M \from T
+    \]
+  by compact definability for $\G$.
+  Then, by our earlier work, we know that $\sigma$ itself is the denotation of the term
+  \[
+    x\from S \ts M[\choose_{p_i}/a_i] \from T\,.\qedhere
+    \]
+\end{proof}
+
+We can now prove Full Abstraction.
+
+\begin{theorem}[{Full Abstraction for \IAXX}]
+  Suppose that our action satisfies the conditions of Proposition \ref{PropIAXXCompactDefinability}.
+  Let $M,M'\from T$ be closed terms of \IAXX.  
+  Then $M$ and $M'$ are observationally equivalent if and only if $\deno M\sim \deno M'$.
+\end{theorem}
+\begin{proof}
+  The right-to-left direction is Theorem \ref{TheEquationalSoundnessIAXX}.  
+  For the other direction, suppose that $\deno M \not\sim \deno M'$.  
+  Then, without loss of generality there is some $\alpha$ such that the sets $(N,\Acc(\Lambda(\deno M);\alpha))$ and $(N,\Acc(\Lambda(\deno{M'};\alpha))$ are inequivalent.  
+  Since $\G$ is enriched in algebraic domains, $\alpha$ may be taken to be compact, and is therefore the denotation of some term-in-context $L \from T \to \com$.
+  Then, by our Computational Adequacy result, we have that $B(L M)$ and $B(L M')$ are inequivalent; i.e., that $M$ is not observationally equivalent to $N$.
+\end{proof}
 
@@
 
-\begin{definition}
-  Let $\sigma\from A \to B$ be a morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
-  We say that $\sigma$ is \emph{compact} if it is compact when considered as a morphism in $\G$.
-\end{definition}
-
-\begin{remark}
-  When we say `considered as a morphism in $\G$' in the above definition, we mean `in at least one of its possible interpretations as a morphism in $\G$'.  
-  Note, however, that the continuous image of a compact element is compact, and so if we pass to a new representative of $\sigma$ by composing on the left by the image of some morphism in $\Rv_{\Omega}^{FS}$, then the resulting representative of $\sigma$ will also be compact.
-
-  If $\G$ is the category of games, this compactness property is invariant under the choice of representative for $\sigma$.
-\end{remark}
-
 We can now prove our compact definability result.
 
-\begin{proposition}[Compact definability]
+\begin{proposition}[Compact definability for PA]
   Let $T$ be an Idealized Algol type and let $\sigma \from 1 \to \deno{T}$ be a compact morphism in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$.  
@@
 The work in the previous section shows that two strategies that are related by the probabilistic equivalence relation $\approx_\bP$ are automatically observationally equivalent.  
-This suggests that the realy content of a probabilistic strategy consists in the quantities $\bP(s\in\sigma)$.  
+This suggests that the real content of a probabilistic strategy consists in the quantities $\bP(s\in\sigma)$.  
 An idea, then, is to take the quantities $\bP(s\in\sigma)$ as primitives, rather than defining them indirectly.

### 2019-09-17 Thesis/promonads.tex
The final commit?

@@
     \]
-  Suppose that the $\pi_{\vec a}$ are \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
+  Suppose that the $\pi_{\vec a}$ are \emph{strongly universal} in the sense that if 
+  \begin{mathpar}
+    b_1,\cdots b_k, c_1
+    \and
+    \cdots,c_l
+  \end{mathpar}
+  are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
   \[
@@
   Given objects $a,b$ of $\M$, define $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
-  Then the operation $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
+  Then the operation $\blank\tensor\blank$ and $I$ make $\M$ into a monoidal category $\overline{\M}$ such that $\tilde{\overline{\M}}$ and $\M$ are isomorphic multicategories.
   \begin{itemize}
@@
   \begin{mathpar}
-    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\} \to \{(1,1),\cdots,(1,m),\cdots,(n,1),\cdots,(n,m)\}
-  \end{mathpar}
-  that sends $(i,j)$ to $(j,i)$, considered as a permutation of $\{1,\cdots,mn\}$.
+    (1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m) \to (1,1),\cdots,(1,m),\cdots,(n,1),\cdots,(n,m)
+  \end{mathpar}
+  sending $(i,j)$ to $(i,j)$, considered as a permutation of $\{1,\cdots,mn\}$.
 \end{definition}
@@
 This is the usual notion of composition for $\Set$-enriched profunctors.  
-However, if $\V$ is not cocomplete, then the multicategory of endoprofunctors on $\C$ need not be representable, even if $\V$ is representable.
+However, it relies on the appropriate coends existing in $\Set$; for more generally $\V$-enriched profunctors, the multicategory of endoprofunctors on $\C$ need not be representable, even if $\V$ is a monoidal category.
 
 We have only considered profunctors going from a category into itself.  
-Profunctors in general form a structure called an \emph{fc-multicategory} \cite{Multicategories}, though we shall not be using this notion.
+Profunctors in general form a structure called an \emph{fc-multicategory} \cite{Multicategories}, but we shall not be using this notion.
 
@@
     \]
-  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, or when the category $\M$ is not the enriching category.
+  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, or when the category $\M$ is not the enriching multicategory.
 \end{remark}
@@
 This generalizes categories in the case that $\X=1$.  
-It generalizes monoidal functors $\X \to \Set$ in the case that $\C$ is the enriched category $*_{[\X,\Set]}$ with a single object $()$, where the morphisms $() \to ()$ are given by the functor $[I,\blank]$, for $I$ the monoidal unit in $\X$, this being the initial object in $[\X,\Set]$.
+It generalizes monoidal functors $\X \to \Set$ in the case that $\C$ is the $[\X,\Set]$-enriched category $*_{[\X,\Set]}$ with a single object $()$, where the morphisms $() \to ()$ are given by the functor $[I,\blank]$, for $I$ the monoidal unit in $\X$, this being the initial object in $[\X,\Set]$.
 
@@
 The objects of this $[\X,\Set]$-enriched category are the objects of $\C$.
-By working the definitions through the proofs of Proposition \ref{PropFunctorsIntoProfunctors} and Theorem \ref{StokessTheorem}, we see that the object of morphisms from $a$ to $b$ is
-\[
-  x \mapsto \C(a,x.b)\,,
+By working the definitions through the proofs of Proposition \ref{PropFunctorsIntoProfunctors} and Theorem \ref{StokessTheorem}, we see that the object of morphisms from $a$ to $b$ is the functor
+\[
+  x \mapsto \C(a,x.b)\from \X \to \Set\,,
   \]

### 2020-04-04 Thesis/conc.tex
Corrections.
Formatting/spell changes

@@
     \and
+    \inferrule*[right={$S,T\in\{\bool,\nat\}$}]{\Gamma\ts M \from S \\ \Gamma,x\from S\ts N \from T}{\Gamma\ts \lett x=M\inn N\from T}
+    \and
     \inferrule*{\Gamma \ts M \from T \to T}{\Gamma \ts \Y_T M \from T}
@@
   {Type theory for a variant of PCF with nondeterminism.
-  Note that if the nondeterminism is infinite (i.e., $X=\bN$), then it is common (see \cite{LairdOrdinalGames} for nondeterminism and \cite{ProbabilisicPcf} for the probabilistic case) to modify the conditional construct $\IfO M\Then N \Else P$ so that the value of $M$ is passed into $P$ (so that the typing rule for $\IfO$ becomes
-  \[
-    \inferrule*[right={$T\in\{\bool,\nat\}$}]{\Gamma\ts M \from \nat \\ \Gamma \ts N \from T \\ \Gamma \ts P \from \nat \to T}
-    {\Gamma \ts \IfO M \Then N \Else P \from T}\,.
-    \]
-  The idea behind this is that if $M$ evaluates to $0$ then $N$ will be evaluated, and if it evaluates to $n+1$ then $P\,n$ will be evaluated.
-  In ordinary deterministic PCF, this does not change the expressive power of the language, since we could always write
-  \[
-    \IfO M \Then N \Else (P\,M)\,.
-    \]
-  However, this does not work if $M$ may exhibit nondeterministic behaviour, since $M$ may evaluate to two different values the two times it is called.
-  We will stick with the variant shown above for the sake of simplicity, but nothing changes in our proofs if we choose the other version.}
+  Note that although ordinary deterministic PCF does not include the $\lett$ construct, it has to be included in the nondeterministic (see \cite{LairdOrdinalGames}) and probabilistic (see \cite{ProbabilisicPcf}) versions.
+
+  In ordinary PCF, we may simulate the term $\lett x=M \inn N$ by the term $(\lambda x.N) M$, which is less efficient than the version with $\lett$ (If $N$ contains multiple occurrences of the variable $x$, then we end up compute $M$ multiple times), but which still gives the same result.
+
+  In nondeterministic variants of PCF, however, evaluating $M$ multiple times may give a different answer each time, in contrast to the version with $\lett$, in which we get a single answer and use it multiple times.}
   \label{FigNDPcfTypeTheory}

### 2020-04-04 Thesis/pmonads2.tex
Corrections.
Formatting/spell changes

@@
 
-Let a monoidal category $\X$ act on a category $\G$, where $\G$ is a suitable model of some programming language.  
+Let a monoidal category $\YY$ with a small descendent set act on a category $\G$, where $\G$ is a suitable model of some programming language.  
 In this chapter we will investigate the adequacy and full abstraction properties of the resulting category $\G/\X$, as we did with Kleisli categories in Chapter \ref{ChapMonads}.
@@
 
-As hinted at in Chapter \ref{ChapParametricMonads}, we shall also require the action of $\X$ on $\G$ to be a reader action corresponding to an oplax symmetric monoidal functor that satisfies the condition in Theorem \ref{TheCartesianClosedCx}, so that the category $\G/\X$ is Cartesian closed.
-
-We fix a symmetric monoidal category $\X$ and an oplax monoidal functor $j\from \X \to \Set$ such that for any object $p$ of $\X$ there are morphisms $h\from p \to p \tensor p$ and $h_0 \from p \to I$ such that the composite
+As hinted at in Chapter \ref{ChapParametricMonads}, we shall also require the action of $\YY$ on $\G$ to be a reader action corresponding to an oplax symmetric monoidal functor $\oppcat Y \to \G$ that satisfies the condition in Theorem \ref{TheCartesianClosedCx}, so that the category $\G/\X$ is Cartesian closed.
+
+We fix a symmetric monoidal category $\X$ (corresponding to $\oppcat \YY$ above) with a small ancestral set and an oplax monoidal functor $j\from \X \to \Set$ such that for any object $p$ of $\X$ there are morphisms $h\from p \to p \tensor p$ and $h_0 \from p \to I$ such that the composite
 \[
@@
 
-Having fix a model $\G$ of Idealized Algol as above, suppose that the datatypes in $\G$ are interpreted via an oplax monoidal functor $\Set \to \G$.  
+Fix a model $\G$ of Idealized Algol as above and suppose that the datatypes in $\G$ are interpreted via an oplax monoidal functor $\Set \to \G$.  
 Then we get an oplax monoidal functor $\X \to \G$, inducing a reader action of $\oppcat\X$ on $\G$ such that the category $\G/\oppcat\X$ is Cartesian closed.  
@@
 
-By our description of $\G/\oppcat \X$ as a lax colimit in $\Cat$ (i.e., Corollary \ref{CorTheConstructionUniversalProperty}), we have a natural functor $J\from \G\to\G/\oppcat \X$ and a natural transformation $\phi_{p,a}\from J(jp\to a) \to Ja$.
+By our description of $\G/\oppcat \X$ as a lax colimit in $\Cat$ (i.e., Corollary \ref{CorTheConstructionUniversalProperty}), we have a natural functor $J\from \G\to\G/\oppcat \X$ and a natural transformation $\phi_{p,a}\from J(\ul{jp}\to a) \to Ja$.
 We define our denotational semantics of \IAXX in the category $\G/\oppcat X$ as follows.  
@@
 The denotation of any sequent $\Gamma\ts M$ the morphism $\deno{\Gamma\ts M} = J(\deno{\Gamma\ts M}_\G)$, where $\deno{-}_\G$ is the original denotation in $\G$.
-The denotation of $\choose_p$ is the morphism $\omega_p \from 1 \to j(p)$ given by the composite
-\[
-  I \xrightarrow{\Lambda(\id_{Jjp})} (Jjp \to Jjp)  \to J(jp \to jp) \xrightarrow{\phi_{p,jp}} Jjp\,.
+The denotation of $\choose_p$ is the morphism $\omega_p \from 1 \to \ul{j(p)}$ given by the composite
+\[
+  1 \xrightarrow{\Lambda(\id_{J\ul{jp}})} (J\ul{jp} \to J\ul{jp})  \to J(\ul{jp} \to \ul{jp}) \xrightarrow{\phi_{p,\ul{jp}}} J\ul{jp}\,.
   \]
@@
 \[
-  \deno{\Gamma}\times j\left(\Tensor_p p\right) \xrightarrow{\deno{\Gamma}\times m^j} \deno \Gamma \times \prod_p j(p) \xrightarrow{\deno{\Gamma,(x_p)\ts N[x_p/\choose_p]}} \deno T\,.
+  \deno{\Gamma}\times \ul{j\left(\Tensor_p p\right)} \xrightarrow{\deno{\Gamma}\times m^j} \deno \Gamma \times \prod_p \ul{j(p)} \xrightarrow{\deno{\Gamma,(x_p)\ts N[x_p/\choose_p]}} \deno T\,.
   \]
@@
     \inferrule*{\Gamma,s\ts M \converges_U n+1,s' \\ \Gamma,s' \ts P \converges_V c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges_{U \cat V} c,s''}
+    \and
+    \inferrule*{\Gamma,s\ts M \converges c',s' \\ \Gamma,s' \ts N[c'/x] \converges c,s''}{\Gamma,s\ts \lett x=M \inn N \converges c,s''}
     \and
@@
 \[
-  A \to (j(x) \to B)
+  A \to (\ul{j(x)} \to B)
   \]
@@
 \[
-  j(N) \xrightarrow{jf} j(p_1 \tensor \cdots \tensor p_n) \xrightarrow{m^j} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \deno T\,;
+  \ul{jN} \xrightarrow{\ul{jf}} \ul{j(p_1 \tensor \cdots \tensor p_n)} \xrightarrow{m^j} \ul{jp_1} \times \cdots \times \ul{jp_n} \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \deno T\,;
   \]
@@
 \[
-  j(N) \xrightarrow{\langle \pi_1,\cdots,\pi_n\rangle} j(p_1) \times \cdots \times j(p_n) \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \deno T\,.
+  \ul{jN} \xrightarrow{\langle \pi_1,\cdots,\pi_n\rangle} \ul{jp_1} \times \cdots \times \ul{jp_n} \xrightarrow{\deno{x_1,\cdots,x_n\ts M[x_i/\choose_{p_i}]}_\G} \deno T\,.
   \]
@@
 
-Secondly, a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an (equivalence class of) morphisms $1 \to (j(p) \to \bC)$ in $\G$, and the object $j(p)$ need not be an Idealized Algol datatype.
+Secondly, a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an (equivalence class of) morphisms $1 \to (\ul{j(p)} \to \bC)$ in $\G$, and the object $\ul{j(p)}$ need not be an Idealized Algol datatype.
 
@@
   \]
-for any set $X$ and any finite sequence $u\in X^*$ such that for any function $f \from X \to Y$, we have $(f\to \bC);\xi_u = \xi_{f_*u}$ (where $f_*u$ is the sequence formed by applying $f$ pointwise to $u$), and such that if $X$ is an IA datatype, then
+for any set $X$ and any finite sequence $u\in X^*$ such that for any function $f \from X \to Y$, we have $(\ul{f}\to \bC);\xi_u = \xi_{f_*u}$ (where $f_*u$ is the sequence formed by applying $f$ pointwise to $u$), and such that if $X$ is an IA datatype, then
 \[
@@
 \begin{definition}
-  Given a set $X$ and a \Mellies morphism $\sigma \from 1 \to (X \to \bC)$, we say that $\sigma$ \emph{accepts} a sequence $u\in X^*$ if $\sigma;\xi_u\ne\bot$.
+  Given a set $X$ and a morphism $\sigma \from 1 \to (X \to \bC)$, we say that $\sigma$ \emph{accepts} a sequence $u\in X^*$ if $\sigma;\xi_u\ne\bot$.
   We write $\Acc(\sigma)$ for the set of all sequences accepted by $\sigma$.
@@
 
-Recall that a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an equivalence class of \Mellies morphisms $1 \to (j(p) \to \bC)$ in $\G$, where $p$ ranges over the objects of $\X$, and where the equivalence relation is generated by identifying all pairs of morphisms $\sigma \from 1 \to (j(p) \to \bC)$ and $\tau \from 1 \to (j(q) \to \bC)$ such that there is a morphism $f \from p \to q$ such that $\tau;(j(f)\to A)=\sigma$.
+Recall that a morphism $1 \to \bC$ in $\G/\oppcat\X$ is given by an equivalence class of \Mellies morphisms $1 \to (\ul{j(p)} \to \bC)$ in $\G$, where $p$ ranges over the objects of $\X$, and where the equivalence relation is generated by identifying all pairs of morphisms $\sigma \from 1 \to (\ul{j(p)} \to \bC)$ and $\tau \from 1 \to (\ul{j(q)} \to \bC)$ such that there is a morphism $f \from p \to q$ such that $\tau;(\ul{j(f)}\to A)=\sigma$.
 
@@
 \begin{proposition}
-  Let $\sigma\from 1 \to (j(p) \to A)$, $\tau\from 1 \to (j(q) \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
+  Let $\sigma\from 1 \to (\ul{j(p)} \to A)$, $\tau\from 1 \to (\ul{j(q)} \to A)$ be two representatives of the same morphism $1 \to A$ in $\G/\oppcat\X$.  
   Then $(p,\Acc(\sigma))$ and $(q,\Acc(\tau))$ are equivalent.
@@
 \begin{definition}[Equivalence of morphisms $1 \to \bC$]
-  Let $\sigma,\tau\from 1 \to \bC$ be morphisms in $\G/\oppcat\X$, considered as morphisms $\sigma\from j(p) \to \bC$ and $\tau \from j(q) \to \bC$ in $\G$.  
+  Let $\sigma,\tau\from 1 \to \bC$ be morphisms in $\G/\oppcat\X$, considered as morphisms $\sigma\from \ul{j(p)} \to \bC$ and $\tau \from \ul{j(q)} \to \bC$ in $\G$.  
   We say that $\sigma\approx\tau$ if $(p,\Acc(\sigma))$ is equivalent to $(q,\Acc(\tau))$.
@@
   \[
-    h \from j(p_1) \times \cdots \times j(p_n) \to x\,.
+    h \from p_1 \tensor \cdots \tensor p_n \to x\,.
     \]
@@
   \[
-    \deno S \to j(p_1 \tensor \cdots \tensor p_n) \to \deno T
+    \deno S \to \ul{j(p_1 \tensor \cdots \tensor p_n)} \to \deno T
     \]
@@
   \[
-    \deno S \to (j(p_1) \times \cdots \times j(p_n) \to \deno T)\,,
+    \deno S \to (\ul{j(p_1) \times \cdots \times j(p_n)} \to \deno T)\,,
     \]
@@
   \[
-    x \from S,a_1 \from p_1,\cdots,a_n\from p_n \ts M \from T
+    v \from S,a_1 \from p_1,\cdots,a_n\from p_n \ts M \from T
     \]
@@
   \[
-    x\from S \ts M[\choose_{p_i}/a_i] \from T\,.\qedhere
+    v\from S \ts M[\choose_{p_i}/a_i] \from T\,.\qedhere
     \]
@@
 We now specialize to the case where $\X$ is a category of random variables on some fixed probability space $(\Omega,\F,\bP)$, in order to model a probabilistic language.
-For our purposes, it will suffice to take $\Omega$ to be the real interval $(0,1)$ with its Borel $\sigma$-algebra and measure.
+For our purposes, it will suffice to take $\Omega$ to be the real interval $(0,1)$ with its Lebesgue $\sigma$-algebra and measure.
+Note that the Lebesgue measure satisfies the conditions from Example \ref{ExRandomVariable} and Proposition \ref{PropRandomVariablePairing} -- every countable set is measurable and every subset of a measure-zero set is measurable.
+
 A \emph{random variable} on $\Omega$ is a measurable function $V \from \Omega \to X$.  
@@
 
-The category $\X = \Rv_\Omega^{FS}$ will then be the category whose objects are random variables of \emph{finite support}; that is, measurable functions $V\from\Omega \to X$, where $X$ is a discrete space, such that there is some finite subset $Y\subset X$ satisfying $\bP(V\in Y) = 1$.
+The category $\X = \Rv_\Omega^{FS}$ will then be the category whose objects are random variables of \emph{finite support}; that is, discrete spaces $X$ together with measurable functions $V\from\Omega \to X$, such that there is some finite subset $Y\subset X$ satisfying $\bP(V\in Y) = 1$.
 
@@
 
-The denotation of any term of PA, then, will be an (equivalence class of) morphisms
+The denotation of a base term of PA of type $S$ is a \Mellies morphism taking the form
+\[
+  \ul(1) \to \deno{S}
+  \]
+(for the IA terms) or the form
+\[
+  \ul(\bB) \to \deno{S}
+  \]
+for the term $\choose_p$.  
+When we compose or tensor these together, we take the tensor products of the objects on the left in $\X$, which corresponds, after application of the oplax monoidal functor $j$, to taking Cartesian products in $\Set$, and thence to taking Cartesian products in $\G$.
+
+The denotation of any term of PA of type $T$, then, will be an (equivalence class of) morphisms
 \[
@@
   \]
-together with some random variable taking values in $\bB^n$.
-We have used an underline to distinguish between the object $\ul{\bB^n}$ of $\G$ corresponding to the set $\bB^n$ of $n$-tuples of booleans and the $n$-fold Cartesian power $\ul{\bB}^n$ in $\G$ of the object $\bB$ corresponding to the set of booleans.
+together with some random variable taking values in $\bB^n$ (formed by taking the tensor product of Bernoulli random variables).
 
@@
 This is because every morphism definable in PA takes this form.
-It will suffice to prove the following.
+By Proposition \ref{PropIAXXCompactDefinability}, it will suffice to prove the following.
 
@@
 
+\begin{remark}
+  This also proves that $\Rv_{\Omega}^{FS}$ has a small ancestral set.
+\end{remark}
+
 Then if we have an arbitrary morphism $\sigma \from A \to B$ (given by a morphism $\tilde\sigma \from A \to (j(X) \to B)$ in the base category), Proposition \ref{PropFiniteSupport} gives us the morphism $f$ mediating between $\tilde\sigma$ and a morphism of the form specified at the start of this section.
@@
 The probabilistic language is our main example of an application of the theory of parametric monads that we have developed.
-However, it is worth noting that it is possible to model a probabilistic language within the langauge IA${}_\bB$ from Chapter \ref{ChapMonads}.
+However, it is worth noting that it is possible to model a probabilistic language within the language IA${}_\bB$ from Chapter \ref{ChapMonads}.
 Specifically, we can consider the language IA${}_\bB$ as a probabilistic Algol variant, by treating the term $\ask_\bB$ as a coin flip that returns $\true$ or $\false$ each with probability $\frac12$.
@@
 
-In $\G/\Rv_{\Omega}^{FS}$, however, we can model a term that has the same behaviour using the morphism
+In $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, however, we can model a term that has the same behaviour using the morphism
 \[
@@
 
+Let us now examine two more models based on Kleisli categories.
+
+One idea we might have is to use the datatype game $(0,1)$ (corresponding to the open unit interval of reals) as our reader object.  
+That way, we could model the term $\choose_p$ as the morphism
+\[
+  (0,1) \to \bB
+  \]
+that returns $\true$ if its input is less than $p$ and $\false$ if its input is greater than or equal to $p$.  
+Unfortunately, however, this model allows us to construct too many strategies, including some that have no probabilistic interpretation.  
+If $X \subset (0,1)$ is a non-measurable set, for instance, then there is a perfectly valid morphism\footnote{At least, in the category of games and any other model satisfying the condition from Definition \ref{DefBrackets}.}
+\[
+  \chi_X \from (0,1) \to \bB
+  \]
+corresponding to the indicator function of $X$, but there is now no sensible answer to the question `What is the probability that $\chi_X$ returns $\true$?'\footnote{Recall also from Section \ref{SecActionsOfCategoriesWithTerminalObjects} that this Kleisli category is precisely what we end up with if we relax the discreteness condition on random variables -- so we are left trying to model continuous probability distributions (such as the uniform distribution on $(0,1)$) with games that are very much discrete.}
+Fixing this problem would require us to impose further measurability conditions on strategies, taking us away from our core idea of sticking to the category-theoretic constructions as closely as possible.
+
+A more successful approach is to replace the datatype $(0,1)$ with the (game-theoretic) product of a countably infinite collection of copies of $\bB$, indexed by $(0,1)$, each corresponding to one of the $\choose_p$.
+Computationally, this corresponds to `encapsulating' the chosen value in $(0,1)$ behind a countably infinite family of `methods', each of which will only tell you whether the value is less than some fixed number.
+Since any program can call only finitely many of these `methods', we avoid introducing any non-measurable behaviour.
+
+There is then, at least in the category of games, some clear idea about how to define the probability of a particular play occurring in a strategy.  
+Since any play must make at most countably many appeals to the product-of-booleans oracle, and since each such appeal has an associated probability, we can associate a probability to each such play by multiplying these probabilities together.
+
+It is less clear, however, how to prove Adequacy and Full Abstraction for this model.  
+The approach that we have adopted in this chapter -- a translation into \IAX -- does not work for a strategy of the form
+\[
+  \sigma\from\prod_{p\in (0,1)} \bB \to A\,,
+  \]
+where the left-hand side is an uncountable product of booleans and certainly cannot be embedded inside any IA datatype game.
+
+We could reason about such a strategy by asking whether it factored through any finite product of booleans; i.e., whether there was any $\hat\sigma$ such that $\sigma$ factors as
+\[
+  \prod_{p\in(0,1)} \bB \xrightarrow{\langle \pr_{p_1},\cdots,\pr_{p_n}\rangle} \bB^n \xrightarrow{\hat\sigma} A\,,
+  \]
+for some finite collection $p_1,\cdots,p_n$ of probabilities.  
+We could then reason about the strategy $\hat\sigma$.  
+But if we are doing that, then why not reason about the strategy $\hat\sigma$ from the start?
+And if we have two possible choices for this $\hat\sigma$, why not make it explicit in the model that they are equal?
+This is exactly what our $\G/\oppcat{(\Rv_{\Omega}^{FS})}$ model is doing.
+Rather than try and rely on some global probabilistic oracle, our strategies can form their own mini (i.e., finite/countable) oracles that give them what they need.  
+Composition of morphisms automatically groups these mini oracles together into one, and the equivalence relation on morphisms ensures that we can always enlarge our mini oracle if we need to (for example, by converting from a product of finitely many booleans to a natural number to help the translation into \IAX).
+
 \section{Game Semantics and Probability}
 
+So far, we have considered things in the abstract.
 We now specialize to the case that $\G$ is the category of arenas and single-threaded strategies that we developed in Chapters \ref{ChapGames} and \ref{ChapFullAbstraction}.
@@
   \begin{mathpar}
-    (V\from \Omega \to X, \sigma \from \ul X \to A)
-    \and
-    (W\from \Omega \to Y, \sigma \from \ul Y \to A)
+    (V\from \Omega \to X, \sigma \from \ul X \to (A\to B))
+    \and
+    (W\from \Omega \to Y, \sigma \from \ul Y \to (A\to B))
   \end{mathpar}
   be representatives of the same morphism $A \to B$ in $\G/\oppcat{(\Rv_{\Omega}^{FS})}$, where $X$ and $Y$ are sets.  
-  Let $s$ be a legal play of $A$.
+  Let $s$ be a legal play of $A\to B$.
   Then $(V,\Acc_s(\sigma))$ and $(W,\Acc_s(\sigma'))$ are equivalent as pairs in the sense of Definition \ref{DefEquivalenceOfPairs}.
@@
 \begin{proof}
-  It suffices by induction to prove this in the case that the two representatives are related by the relation that generates the equivalence relation on morphisms; i.e., that there is a probability-preserving function $f\from X \to Y$ such that $\sigma=\sigma';(j(f) \to A)$.
+  It suffices by induction to prove this in the case that the two representatives are related by the relation that generates the equivalence relation on morphisms; i.e., that there is a probability-preserving function $f\from X \to Y$ such that $\sigma=\sigma';(\ul{j(f)} \to A)$.
 
@@
     u \in \Acc_s(\sigma) & \Leftrightarrow & \exists t\in \sigma \esuchthat t/s,\,t\vert_{\ul X}=qu \\
-    & \Leftrightarrow & \exists t \in \sigma';(j(f) \to A) \esuchthat t/s,\,t\vert_{\ul X}=qu \\
+    & \Leftrightarrow & \exists t \in \sigma';(\ul{j(f)} \to A) \esuchthat t/s,\,t\vert_{\ul X}=qu \\
     & \Leftrightarrow & \exists t' \in \sigma' \esuchthat t/s,\,t\vert_{\ul Y} = q(f_*u) \\

### 2020-04-04 Thesis/thesis.tex
Corrections.
Formatting/spell changes

@@
   In the category of sets, the \emph{nonempty powerset functor} $\powerset_+$ sends a set $A$ to the set of nonempty subsets of $A$.  
-  This functor has the structure of a monad on $\Set$, since we have a natural transformation (union) from $\powerset_+\powerset_+A$ to $powerset_+A$ and a natural transformation (singleton) from $A$ to$ \powerset_+A$ that obey the diagrams given above.
+  This functor has the structure of a monad on $\Set$, since we have a natural transformation (union) from $\powerset_+\powerset_+A$ to $\powerset_+A$ and a natural transformation (singleton) from $A$ to$ \powerset_+A$ that obey the diagrams given above.
 \end{example}
@@
 
-  As an example, the definition of a monoidal closed category $\M$ is that it admits an adjunction between functors $\blank\tensor w$ and $w\implies\blank$ for any object $w$ of $M$.  
-  if $\M$ is a monoidal closed category and $w$ is an object of $\M$, then the functor $S_w$ on $\M$ defined by
+  Let us look at an example of a monad that arises from an adjunction in this way.  
+  Recall that the definition of a monoidal closed category $\M$ is that it admits an adjunction between functors $\blank\tensor w$ and $w\implies\blank$ for any object $w$ of $M$.  
+  If $\M$ is a monoidal closed category and $w$ is an object of $\M$, then the functor $S_w$ on $\M$ defined by
   \[
@@
 \begin{example}
-  Another example that arises from an adjunction is the \emph{list monad} on $\Set$ that arises from the adjunction between the $\Set$ and the category of monoids.
+  Another example that arises from an adjunction is the \emph{list monad} on $\Set$ that arises from the adjunction between the category $\Set$ of sets and the category of monoids.
   The underlying set of the free monoid on a set $A$ is the set $A^*$ of finite lists of elements of $A$, and the functor $A\mapsto A^*$ inherits a monoid structure where the multiplication $m_A\from (A^*)^* \to A^*$ concatenates a list of lists into a single list and the unit $u_a \from A \to A^*$ forms a list with a single element.
@@
   \[
-    S_r'x = (r \implies x) \tensor x\,.
+    S_r'x = (r \implies x) \tensor r\,.
     \]
@@
 
-\subsection{Multiplicative natural transformations}
+\section{Multiplicative natural transformations}
 
@@
 which is equal to $f$ by the coherence conditions on $m$ and $u$.
-This means that the Kleisli category may be thought of as being freely generated from the original category $\C$ and a multiplicative natural transformation $\phi$.
+This means that the Kleisli category may be thought of as being freely generated from the original category $\C$ and an $M$-multiplicative natural transformation $\phi$.
 
@@
   Then the Kleisli category for the reader monad $R_z$ on $\C$ is generated over $\C$ by a natural transformation $\phi_y\from (z \to y) \to y$.  
-  By the enriched Yoneda lemma, such a natural transformation is always given by precomposition with some fixed morphism $\ask_z\from 1 \to z$.  
+  As a Cartesian closed category, $\C$ may be regarded as being enriched over itself.
+  By the enriched Yoneda lemma, then, such a natural transformation is always given by precomposition with some fixed morphism $\ask_z\from 1 \to z$.  
   This means that $\Kl_{R_z}$ is suitable for modelling any situation in which we are generally working in $\C$, but need the ability to request a value of type $z$ (for example, a config file, a piece of user input, a random number or something else that isn't being passed into the function in question).
@@
 In addition, we require that $\G$ can be interpreted as being enriched in algebraic partial orders, in such a way that any compact morphism between the denotation of IA types is the denotation of some IA term.
-The prototypical example, of course, will be the category of games and visible strategies, but we will not exploit any properties of this model beyond the ones we have already mentioned, mentioning it only in examples where appropriate.
+The prototypical example, of course, will be the category of games and visible strategies that we met in Chapter \ref{ChapGames}, but we will not exploit any properties of this model beyond the ones we have already mentioned, mentioning it only in examples where appropriate.
 
@@
   \]
-(where $\Lambda(\lunit_X;\id_X)\from 1 \to (X \to X)$ is the interpretation of the $\lambda$-term $\lambda x.x$), which will be the denotation of the term $\choose_X$.
+(where $\Lambda(\lunit_X;\id_X)\from 1 \to (X \to X)$ is the interpretation of the $\lambda$-term $\lambda x.x$), which will be the denotation of the term $\ask_X$.
 Together with the existing denotational semantics of Idealized Algol within $\G$, this gives us an inductively defined denotational semantics of \IAX within $\G_X$.
@@
   \begin{figure}
+    \small
     \begin{mathpar}
@@
       \inferrule*{\Gamma,s\ts M \converges_u n+1,s' \\ \Gamma,s' \ts P \converges_v c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges_{u\cat v} c,s''}
-      \and
+      \\
+      \inferrule{\Gamma,s\ts M\converges c',s' \\ \Gamma,s' \ts N[c'/x]\converges c,s''}{\Gamma,s\ts \lett x=M \inn N \converges c,s''}
+      \\
       \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges_u n,s' \\ \Gamma,s' \ts V \converges_v x,s''}{\Gamma,s\ts V \gets E \converges_{u\cat v} \skipp,(s''\vert x \mapsto n)}
@@
   Here, we have interpreted each IA rule as an infinite scheme of rules ranging over the different terms $M_i,M$ that the rule can apply to.
-  We first extend this rule to a rule for \IAX, by allowing the $M_i,M$ to range over terms of \IAX.
+  We first extend this scheme of rules to a scheme of rules for \IAX, by allowing the $M_i,M$ to range over terms of \IAX.
   We then replace the rule with the new rule
@@
     \]
-  as saying that `starting with the store $s$, and the sequence $u$ of user input, $M$ converges to $c$, leaving store $s'$'.
+  as saying that `starting with the store $s$, and the sequence $u$ of pieces of user input, $M$ converges to $c$, leaving store $s'$'.
 \end{example}
@@
     \and
-    \tr_{xu} = \lambda n.\neww (\lambda v.v\gets n;\IfO !v \Then x \Else \tr_u (\pred !v))
+    \tr_{xu} = \lambda n.\lett y=n \inn \IfO y \Then x \Else \tr_u(\pred y)
   \end{mathpar}
@@
 \end{proposition}
-\begin{proof}
-  Induction on $|u|$ and on $n$.
-  Since $n<u$, $u$ must be non-empty, of the form $xu'$.
-
-  Suppose $n=0$.  
-  Then $u^{(n)}=x$, and we have a derivation of $\Gamma,s\ts \tr_{xu} M\converges x,s'$ from $\Gamma,s\ts M\converges n,s'$ as shown in Figure \ref{FigFirstTermOfSequence}.
-
-  Now suppose that $n=m+1$.  
-  Then $(xu)^{(m+1)}=u^{(m)}$.  
-  Then we have a derivation of $\Gamma,s\ts \tr_{xu} M \converges u^{(m)},s'$ from $\Gamma,s\ts M\converges n,s'$ in Figure \ref{FigGeneralTermOOfSequence}, using the inductive hypothesis to tell us that we may derive
-  \[
-    \inferrule*{\Gamma,v,(s'\vert v\mapsto m+1) \ts \pred !v \converges m,(s'\vert v \mapsto m+1)}
-    {\Gamma,v,(s'\vert v \mapsto m+1) \ts \tr_u(\pred !v) \mapsto u^{(m)},(s'\vert v\mapsto m+1)}\,.\qedhere
-    \]
-  \begin{SidewaysFigure}
-    \tiny
-    \begin{subfigure}{\textheight}
-      \centering
-      \[
-        \inferrule*
-        {
-          \inferrule*
-          {
-            \inferrule*
-            {
-              \inferrule*
-              {
-                \Gamma,v,(s\vert v \mapsto 0) \ts M \converges 0,(s'\vert v\mapsto 0)
-                \\
-                \inferrule*
-                {
-                }
-                {
-                  \Gamma,v,(s'\vert v \mapsto 0)\ts v \converges v,(s'\vert v\mapsto 0)
-                }
-              }
-              {
-                \Gamma,v,(s\vert v\mapsto 0) \ts v \gets M \converges \skipp,(s'\vert v\mapsto 0)
-              }
-              \\
-              \inferrule*
-              {
-                \inferrule*
-                {
-                  \inferrule*
-                  {
-                  }
-                  {
-                    \Gamma,v,(s'\vert v\mapsto 0) \ts v \converges v,(s'\vert v\mapsto 0)
-                  }
-                }
-                {
-                  \Gamma,v,(s'\vert v\mapsto 0) \ts !v \converges 0,(s'\vert v\mapsto 0)
-                }
-                \\
-                \inferrule*
-                {
-                }
-                {
-                  \Gamma,v,(s'\vert v\mapsto 0) \ts x \converges x,(s'\vert v\mapsto 0)
-                }
-              }
-              {
-                \Gamma,v,(s'\vert v\mapsto 0) \ts \IfO !v \Then x \Else \tr_u(\pred !v) \converges x,(s'\vert v\mapsto 0)
-              }
-            }
-            {
-              \Gamma,v,(s\vert v\mapsto 0) \ts v\gets M;\IfO !v \Then x \Else \tr_u(\pred !v) \converges x,(s'\vert v\mapsto 0)
-            }
-          }
-          {
-            \Gamma,s\ts \neww (\lambda v.v\gets M;\IfO !v \Then x \Else \tr_u(\pred !v)) \converges x,s'
-          }
-        }
-        {
-          \Gamma,s\ts \lambda n.\neww (\lambda v.v\gets n;\IfO !v \Then x \Else \tr_u(\pred !v)) M \converges x,s'
-        }
-        \]
-      \caption{IA derivation that if $M\converges 0$ then $\tr_u M$ converges to the first element of the sequence $u$.}
-      \label{FigFirstTermOfSequence}
-    \end{subfigure}
-    \par\vspace{24pt}
-    \begin{subfigure}{\textheight}
-    \centering
-      \[
-        \inferrule*
-        {
-          \inferrule*
-          {
-            \inferrule*[sep=5pt]
-            {
-              \inferrule*
-              {
-                \inferrule*[rightskip=30pt]
-                {
-                }
-                {
-                  \Gamma,v,(s'\vert v\mapsto 0) \ts v \converges v,(s'\vert v\mapsto 0)
-                }
-                \\\\
-                \inferrule*[leftskip=15pt]{}{\Gamma,v,(s\vert v\mapsto 0) \ts M \converges m+1, (s'\vert v\mapsto 0)}
-              }
-              {
-                \Gamma,v,(s\vert v\mapsto 0) \ts v \gets M \converges \skipp,(s'\vert v\mapsto m+1)
-              }
-              \\
-              \inferrule*[sep=5pt]
-              {
-                \inferrule*
-                {
-                  \inferrule*
-                  {
-                  }
-                  {
-                    \Gamma,v,(s'\vert v\mapsto m+1) \ts v \converges v,(s'\vert v\mapsto m+1)
-                  }
-                }
-                {
-                  \Gamma,v,(s'\vert v\mapsto m+1) \ts !v \converges m+1,(s'\vert v\mapsto m+1)
-                }
-                \\
-                \inferrule*
-                {
-                  \inferrule*
-                  {
-                    \inferrule*
-                    {
-                      \inferrule*
-                      {
-                      }
-                      {
-                        \Gamma,v,(s'\vert v\mapsto m+1) \ts v \converges v,(s'\vert v\mapsto m+1)
-                      }
-                    }
-                    {
-                      \Gamma,v,(s'\vert v\mapsto m+1) \ts !v \converges m+1,(s'\vert v\mapsto m+1)
-                    }
-                  }
-                  {
-                    \Gamma,v,(s'\vert v\mapsto m+1) \ts \pred !v \converges m,(s'\vert v\mapsto m+1)
-                  }
-                }
-                {
-                  \Gamma,v,(s'\vert v\mapsto m+1) \ts \tr_u(\pred !v) \converges u^{(m)}, (s'\vert v \mapsto m+1)
-                }
-              }
-              {
-                \Gamma,v,(s'\vert v\mapsto m+1) \ts \IfO !v \Then x \Else \tr_u(\pred !v) \converges u^{(m)}, (s'\vert v\mapsto m+1)
-              }
-            }
-            {
-              \Gamma,v,(s\vert v\mapsto 0) \ts v \gets M;\IfO !v \Then x \Else \tr_u(\pred !v) \converges u^{(m)}, (s'\vert v \mapsto m+1)
-            }
-          }
-          {
-            \Gamma,s \ts \neww (\lambda v.v\gets M;\IfO !v \Then x \Else \tr_u(\pred !v)) \converges u^{(m)},s'
-          }
-        }
-        {
-          \Gamma,s\ts \lambda n.\new (\lambda v.v\gets n;\IfO !v \Then x \Else \tr_u(\pred !v)) M \converges u^{(m)},s'
-        }
-        \]
-        \caption{IA derivation that if $M\converges m+1$ then $\tr_{u}M$ converges to the $m+1$-th element of the sequence $u$.}
-        \label{FigGeneralTermOOfSequence}
-    \end{subfigure}
-    \par\vspace{24pt}
-    \begin{subfigure}{\textheight}
-      \[
-        \inferrule*
-        {
-          \inferrule*
-          {
-            \inferrule*
-            {
-              \inferrule*
-              {
-                \inferrule*
-                {
-                }
-                {
-                  \Gamma,v,(s\vert v\mapsto k) \ts v \converges v,(s\vert v\mapsto k)
-                }
-              }
-              {
-                \Gamma,v,(s\vert v\mapsto k) \ts !v \converges k,(s\vert v\mapsto k)
-              }
-            }
-            {
-              \Gamma,v,(s\vert v\mapsto k) \ts \suc !v \converges k+1,(s\vert v\mapsto k)
-            }
-            \\
-            \inferrule*
-            {
-            }
-            {
-              \Gamma,v,(s\vert v\mapsto k) \ts v\converges v,(s\vert v\mapsto k)
-            }
-          }
-          {
-            \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v \converges \skipp,(s\vert v\mapsto k+1)
-          }
-          \\
-            \inferrule*[right={Prop. \ref{PropTr}}]
-            {
-              \inferrule*
-              {
-                \inferrule*
-                {
-                }
-                {
-                  \Gamma,v,(s\vert v\mapsto k+1) \ts v\converges v,(s\vert v\mapsto k+1)
-                }
-              }
-              {
-                \Gamma,v,(s\vert v\mapsto k+1) \ts !v \converges k+1,(s\vert v\mapsto k+1)
-              }
-            }
-            {
-              \Gamma,v,(s\vert v\mapsto k+1) \ts \tr_w !v \converges x,(s\vert v\mapsto k+1)
-            }
-          }
-        {
-          \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v;\tr_w !v \converges x,(s\vert v\mapsto k+1)
-        }
-        \]
-      \caption{IA derivation that $(x\mapsto k),v \gets \suc !v;\tr_w !v$ converges to the $k+1$-th term of $w$.}
-      \label{FigTheOneForTheLemma}
-    \end{subfigure}
-    \normalsize
-    \caption{Some useful IA derivations}
-  \end{SidewaysFigure}
-\end{proof}
-
-We start with a small lemma to help us deal with substitution.
+
+We start our soundness proof with a small lemma to help us deal with substitution.
 
@@
 We can now state and prove our soundness lemma.
+As suggested by the substitution lemmas we have just proved, we will be taking a term $M$ of nondeterministic IA and replacing all instances of $\ask_X$ in $M$ with some particular term $Q$.  
+The $Q$ that we will use is
+\[
+  \Gamma,v\from\Var \ts v \gets \succ \oc v;\tr_w \oc v\from X\,,
+  \]
+where $w$ is some sequence of elements of $X$.  
+The idea is that this term will trace the effect of a particular evaluation path of $\ask_X$, similarly to how we sometimes `mock' a random number generator when writing unit tests.
+
+Each time we call the term above, we increment the value of $v$, and successive invocations will end up spelling out a particular substring $u$ of $w$ -- depending on the initial value of $v$ and assuming that $w$ is long enough.
+This will allow us to study one particular evaluation path of the original term $M$ -- namely, the one where the successive values returned by $\ask_X$ spell out the sequence $u$.
 
@@
   is derivable in \IAX.
-  Fix $k\in\bN$ and let $w\in X^*$ be a sequence such that $u$ is a subsequence of $w$ starting at position $k+1$ (i.e., $u^{(j)}=w^{(k+j+1)}$ for each $j=0,\cdots,|u|-1$).
+  Fix $k\in\bN$ and let $w\in X^*$ be a sequence such that $u$ is the substring of $w$ starting at position $k+1$ (i.e., $u^{(j)}=w^{(k+j+1)}$ for each $j=0,\cdots,|u|-1$).
   Then
@@
 
+\begin{SidewaysFigure}
+  \small
+  \begin{subfigure}{\textheight}
+    \[
+      \inferrule*
+      {
+        \inferrule*
+        {
+          \inferrule*
+          {
+            \inferrule*
+            {
+              \inferrule*
+              {
+              }
+              {
+                \Gamma,v,(s\vert v\mapsto k) \ts v \converges v,(s\vert v\mapsto k)
+              }
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto k) \ts !v \converges k,(s\vert v\mapsto k)
+            }
+          }
+          {
+            \Gamma,v,(s\vert v\mapsto k) \ts \suc !v \converges k+1,(s\vert v\mapsto k)
+          }
+          \\
+          \inferrule*
+          {
+          }
+          {
+            \Gamma,v,(s\vert v\mapsto k) \ts v\converges v,(s\vert v\mapsto k)
+          }
+        }
+        {
+          \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v \converges \skipp,(s\vert v\mapsto k+1)
+        }
+        \\
+          \inferrule*
+          {
+            \inferrule*
+            {
+              \inferrule*
+              {
+              }
+              {
+                \Gamma,v,(s\vert v\mapsto k+1) \ts v\converges v,(s\vert v\mapsto k+1)
+              }
+            }
+            {
+              \Gamma,v,(s\vert v\mapsto k+1) \ts !v \converges k+1,(s\vert v\mapsto k+1)
+            }
+          }
+          {
+            \Gamma,v,(s\vert v\mapsto k+1) \ts \tr_w !v \converges x,(s\vert v\mapsto k+1)
+          }
+        }
+      {
+        \Gamma,v,(s\vert v\mapsto k) \ts v\gets \suc !v;\tr_w !v \converges x,(s\vert v\mapsto k+1)
+      }
+      \]
+    \normalsize
+    \caption{IA derivation that if $s(v)=k$, then $\Gamma,s\ts v \gets \suc !v;\tr_w !v$ converges to the $k+1$-th term of $w$, leaving state $v\mapsto k+1$.}
+    \label{FigTheOneForTheLemma}
+  \end{subfigure}
+  \vspace{48pt}\\
+  \begin{subfigure}{\textheight}
+    \[
+      \inferrule*
+      {
+        \inferrule*[sep=0em]
+        {
+          \inferrule*[left={Lem. \ref{LemSoundnessMonads}}]
+          {
+          }
+          {
+            v,(v\mapsto 0)\ts M[v\gets\suc!v;\tr_{u^\top} !v/\ask_x]\converges \skipp,(v\mapsto |u|)
+          }
+          \\
+          \inferrule*
+          {
+            \inferrule*
+            {
+            }
+            {
+              v,(v\mapsto |u|) \ts v \converges v,(v\mapsto |u|)
+            }
+          }
+          {
+            v,(v\mapsto |u|)\ts !v \converges |u|,(v\mapsto |u|)
+          }
+        }
+        {
+          v,(v\mapsto 0) \ts M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];v \converges |u|,(v\mapsto |u|)
+        }
+      }
+      {
+        \blank,()\ts\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v) \converges |u|,()
+      }\qedhere
+      \]
+    \caption{IA derivation used in the proof of Proposition \ref{PropKleisliSoundness}.}
+    \label{FigKleisliSoundnessDerivation}
+  \end{subfigure}
+  \caption{Some useful IA derivations}
+\end{SidewaysFigure}
+
 In light of Lemma \ref{LemSoundnessMonads}, we can state our soundness result.
@@
     \and
-    \test_{n+1} = \lambda m.\neww \lambda x.(x\gets m;\IfO \oc x \Then \Omega \Else \test_n (\pred \oc x))\,.
+    \test_{n+1} = \lambda m.\lett x=m \inn \IfO x \Then \Omega \Else \test_n(\pred x)
   \end{mathpar}
@@
   \begin{SidewaysFigure}
-    \[
-      \inferrule*
-      {
-        \inferrule*[sep=0em]
-        {
-          \inferrule*[left={Lem. \ref{LemSoundnessMonads}}]
-          {
-          }
-          {
-            v,(v\mapsto 0)\ts M[v\gets\suc!v;\tr_{u^\top} !v/\ask_x]\converges \skipp,(v\mapsto |u|)
-          }
-          \\
-          \inferrule*
-          {
-            \inferrule*
-            {
-            }
-            {
-              v,(v\mapsto |u|) \ts v \converges v,(v\mapsto |u|)
-            }
-          }
-          {
-            v,(v\mapsto |u|)\ts !v \converges |u|,(v\mapsto |u|)
-          }
-        }
-        {
-          v,(v\mapsto 0) \ts M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];v \converges |u|,(v\mapsto |u|)
-        }
-      }
-      {
-        \blank,()\ts\new (\lambda v.M[v\gets \suc !v;\tr_{u^\top} !v/\ask_X];!v) \converges |u|,()
-      }\qedhere
-      \]
-    \caption{IA derivation used in the proof of Proposition \ref{PropKleisliSoundness}.}
-    \label{FigKleisliSoundnessDerivation}
   \end{SidewaysFigure}
@@
 
+\begin{remark}
   Definition \ref{DefDenotationalUConvergence} looks a bit odd.  
@@
   Since complete plays in the game $\oc X \implies \bC$ are always of the form $q$, followed by some sequence of pairs of the form $qx_i$ for $x_i\in X$, followed by $a$, it is very natural to consider conditions on those $x_i$ when dealing with a strategy $\sigma\from \oc X \implies \bC$.
+\end{remark}
 
@@
 
-Following Ghica, we define a \emph{strategy with costs} to be a prefix-closed set $\sigma$ of plays with costs such that the set $\sigma\vert_{M_A} = \{s\vert_{M_A}\suchthat s\in \sigma\}$ is a valid visible strategy for $A$.
+Following Ghica, we define a \emph{strategy with costs} to be a prefix-closed set $\sigma$ of plays with costs such that the set $\sigma\vert_{M_A} = \{s\vert_{M_A}\suchthat s\in \sigma\}$ is a valid visible strategy for $A$ and such that determinism applies to token actions as well as ordinary moves -- i.e., if $s$ is an $O$-play with costs in $A$ such that $s\slot a\in\sigma$ for some ordinary move $a$, then $sb\not\in\sigma$ for all ordinary moves $b$.
 
@@
     \]
-  Moreover, this bijection respects composition: let $\sigma \from\oc\bC \implies (A \to B)$ and $\tau \from \oc\bC \implies (B \to C)$ be strategies.  
+  Moreover, this bijection respects composition and identity in the Kleisli category: let $\sigma \from\oc\bC \implies (A \to B)$ and $\tau \from \oc\bC \implies (B \to C)$ be strategies.  
   Write $\sigma;\tau$ for the Kleisli composition of $\sigma$ and $\tau$ in $\G_{\bC}$; i.e., the composite
@@
   is not equal to $\bot$.  
-  Therefore, there exists some $v\in X^*$ such that the composite
+  This means that there exists some $v\in X^*$ such that the composite
   \[
@@
   \]
-This suggests a general equivalence relation on Kleisli morphisms in $\G_X$: given a strategy $\sigma\from \oc X \implies A$, we write $\sigma\vert A$ for the set
+This suggests a general equivalence relation on Kleisli morphisms in $\G_X$: given a strategy $\sigma\from \oc X \implies A$, we write $\sigma\vert_A$ for the set
 \[
@@
 \begin{proof}
-  A complete play in $\sigma;\tau$ is given by a sequence $\s\vert_{X,A,C}$, where $\s\in (M_X + M_A + M_B + M_C)^*$ is a legal interaction of a complete play in $\tau$ with a collection of complete plays in $\sigma$, with $B$-components being identified.
+  A complete play in $\sigma;\tau$ is given by a sequence $\s\vert_{X,A,C}$, where $\s\in (M_X + M_A + M_B + M_C)^*$ is a legal interaction of a complete play in $\tau$ with a collection of complete plays in $\sigma$, $B$-components being identified.
   Then $\s\vert_{A,C}$ can alternatively be characterized as $\t\vert_{A,C}$, where $\t\in (M_A + M_B + M_C)^*$ is a legal interaction of a sequence from $\tau\vert_{B,C}$ with a collection of sequences from $\sigma\vert_{A,B}$.
@@
 
+Now, if we have a Kleisli morphism $\sigma\from \oc X \implies A$, then $\sigma\vert_A$ is a nondeterministic strategy for $A$.  
+The composition of nondeterministic strategies respects the composition and identity in the Kleisli category; moreover, any two Kleisli morphisms that give rise to the same nondeterministic strategy are intrinsically equivalent.
+
 It is already known (see \cite{mcCHFiniteND}) that this model is fully abstract for (finitely or countably) nondeterministic Idealized Algol with may-contextual equivalence.
@@
 
-We will give an alternative definition of $\mustconverge$ that will relate it to our existing rules $\converges_u$.
+We will next give an alternative definition of $\mustconverge$ that will relate it to our existing rules $\converges_u$.
 
@@
 
-We could define $M\mustconverge$ by saying that any sequence $u$ is either a subsequence or a supersequence of some $v$ such that $M\converges_v$; our equivalent definition above is a little neater.  
 The idea is that if we fix beforehand an infinite sequence made up of all the values that the nondeterministic oracle could possibly give, then we know that the term will always end up reading some finite sequence of values from the beginning of the sequence and then terminating at a value.
@@
 \[
-  q(qu^{(i)})_{i=0}^{|u|-1} a
-  \]
-is contained in $\sigma$, so consider what it means if we say that such a sequence is not contained in $\sigma$ for any $u\pprefix w$.  
+  \begin{array}{ccc}
+    \oc X       & \implies & \bC \\
+                &          &  q  \\
+      q         &          &     \\
+    u^{(0)}     &          &     \\
+    \vdots      &          &     \\
+      q         &          &     \\
+   u^{(|u|-1}   &          &     \\
+                &          &  a
+  \end{array}
+  \]
+is contained in $\sigma$.  
+Now fix some infinite sequence $w\in X^\omega$ and consider what it means if we say that such a sequence is not contained in $\sigma$ for any $u\pprefix w$.  
 By the definition of a strategy, there are two reasons why this might happen.  
@@
 \[
-  q(qv^{(i)})_{i=0}^{|v|-1}\,.
+  \begin{array}{ccc}
+    \oc X       & \implies & \bC \\
+                &          &  q  \\
+      q         &          &     \\
+    v^{(0)}     &          &     \\
+    \vdots      &          &     \\
+      q         &          &     \\
+   v^{(|v|-1}   &          &     \\
+                &          & {a\,.}
+  \end{array}
   \]
@@
 \[
-  q(qw^{(i)})_{i=0}^\infty\,.
+  \begin{array}{ccc}
+    \oc X       & \implies & \bC \\
+                &          &  q  \\
+      q         &          &     \\
+    v^{(0)}     &          &     \\
+      q         &          &     \\
+    v^{(1)}     &          &     \\
+    \vdots      &          &     
+  \end{array}
   \]
 \begin{definition}
-  We say that a strategy $\sigma\from \oc X \implies \bC$ is \emph{winning} if every finite play in $\sigma$ is contained inside some complete play; i.e., if $\sigma$ is total and contains no infinite plays.
+  We say that a strategy $\sigma\from \oc X \implies \bC$ is \emph{winning} if $\sigma$ is total and contains no infinite plays.
 \end{definition}
@@
 
-\subsection{Full Abstraction for Countable Nondeterminism under Must Testing}
+\section{The Kleene Tree}
+\label{SecKleene}
+
+In order to show that our model is not Fully Abstract, we start by introducing the Kleene tree.
+
+We define a \emph{binary tree} to be a prefix-closed subset of $\bB^*$.  
+Using the binary representation, we can identify $\bB^*$ with $\bN$, meaning that every such tree can be specified by its characteristic function $\chi \from \bN \to \bB$.
+
+We say that the tree is \emph{computable} if there is some IA term $M\from \nat \to \bool$ such that $M n$ converges to $\chi(n)$ for all $n\in\bN$.
+
+In this section, we will show the construction of the \emph{Kleene tree} (see \cite[4.5]{Joshua} and \cite{KleeneTree}).  
+This is a tree $K$ that has the following seemingly paradoxical properties.
+\begin{itemize}
+  \item It is computable.
+  \item It has an infinite path; that is, there are $b_0,b_1,\cdots\in\bB$ such that for all $k$, the string $b_0\cdots b_{k-1}$ is contained in $K$.
+  \item It has no computable infinite path.  
+    I.e., if $M \from \bool \to \nat$ is a term of IA such that $M i$ converges to some $a_i\in \bB$ for each $i\in \bN$, then there is some $k$ such that the string $a_0 \cdots a_{k-1}$ is not contained in $K$.
+\end{itemize}
+
+In order to construct $K$, we are first going to assume that we have fixed some sensible encoding of IA terms as binary strings and hence as natural numbers.  
+We shall further assume the existence of an \emph{interpreter} for IA terms of type $\bool$; that is, a term $\Int \from \nat \to \nat$ such that:
+\begin{itemize}
+  \item if $n$ is the encoding of some $M \from \bool$ such that $M \converges \true$, then $\Int n \converges 0$;
+  \item if $n$ is the encoding of some $M \from \bool$ such that $M \converges \false$, then $\Int n \converges 1$; 
+  \item if $n$ is the encoding of some $M \from \bool$ such that $M$ diverges, then $\Int n$ diverges; and
+  \item if $n$ is not the encoding of a term of type $\bool$, then $\Int n\converges 255$.
+\end{itemize}
+
+The construction of $\Int$ is more a matter of software engineering than anything else.  
+The idea is to use pattern matching and recursion to implement the small-step semantics of Idealized Algol within the encoding we have fixed.
+
+In fact, we shall need a slightly modified version of $\Int$ that accepts an extra \emph{timeout} parameter.  
+That is, we require some $\Int'\from \nat \to \nat \to \nat$ such that
+\begin{itemize}
+  \item if $n$ is the encoding of some $M \from \bool$ such that $M\converges\true$ in under $k$ steps, then $\Int' k\,n \converges 0$;
+  \item if $n$ is the encoding of some $M \from \bool$ such that $M\converges\false$ in under $k$ steps, then $\Int' k\,n \converges 1$; and
+  \item if $n$ is the encoding of some $M \from \bool$ such that $M$ does not converge after $k$ steps, or if $n$ is not the encoding of a term of type $\bool$, then $\Int' k\,n \converges 255$.
+\end{itemize}
+
+This modification to the original $\Int$ is not too hard to make, but now we can be assured that $\Int'$ will always converge, even if fed the encoding of a divergent program.  
+This will be important later.
+
+\begin{definition}[Kleene tree]
+  We construct the tree $K$ as follows.  
+  Suppose $b=b_0,\cdots,b_{k-1}$ is a finite sequence of binary digits.  
+  Then $b$ is contained in $K$ if and only if for all $n=0,\cdots,k-1$, if $n$ is the encoding of a program $M\from \nat \to \bool$ such that $M n$ converges in under $k$ steps, then $M n$ converges to a value different from $b_n$.
+\end{definition}
+
+\begin{remark}
+  We can use $\Int'$ to construct an IA term $\nat \to \bool$ that computes the characteristic function of $K$.  
+  Since the syntax of IA is not very transparent, we shall describe the operation of the term informally.  
+  Given an input $n$, treated as a sequence $b_0 \cdots \b_{k-1}$, we iterate from $0$ up to $k-1$.  
+  For each number $p$, if $p$ is the encoding of a term $M \from \nat \to \bool$, we pass the encoding of $M p$ to $\Int'$, giving $k$ as the timeout parameter.  
+  If we get $0$ (true) or $1$ (false) back, then we compare against $b_p$, returning $\false$ if the values are equal and $\true$ if they are different.  
+  If we get the error value $255$ back, then we return $\true$.
+
+  Lastly, if we have got $\true$ back for each $p$, we return $\true$; otherwise, we return $\false$.
+\end{remark}
 
 \begin{proposition}
-  Let $\C$ be a category and suppose we have a computationally adequate denotational semantics of IA with countable nondeterminism in $\C$.
-  Suppose that the natural number datatype is denoted by an object $\bN$ of $\C$ and that for all functions $f \from \bN \to \bN$ in $\Set$ there is a morphism
-  \[
-    \sigma_f \from \bN \to \bN
-    \]
-  in $\C$ such that for all $n\in \bN$, 
-  \[
-    \deno{n};\sigma_f = \deno{f(n)}\,.
-    \]
-  Then the denotational semantics in $\C$ is not fully abstract.
-  \label{PropNotFullyAbstract}
+  i) $K$ has an infinite path.
+
+  ii) $K$ has no computable infinite path.
 \end{proposition}
-\begin{example}
-  In the category $\G$ of games (and hence in its Kleisli categories), we have strategies $\sigma_f$ with maximal plays of the form
+\begin{proof}
+  (i): For each $p$ such that $p$ is the encoding of some $M \from \nat \to \bool$ such that $M p$ converges, let $a_p$ be $\true$ if $M p \converges \false$ and $\false$ if $M p \converges \true$.  
+  Otherwise -- i.e., if $M p$ does not converge or if $p$ is not the encoding of a term $\nat \to \bool$ -- then return any value -- $\false$, say.
+  Then any sequence $a_0 \cdots a_{k-1}$ must be contained in $K$.
+
+  (ii): Let $M \from \nat \to \bool$ be such that there are $b_i\in\bB$ for which $M i \converges b_i$ for all $i$, let $p$ be the encoding of $M$ and suppose that $M p$ converges in $k$ steps.  
+  Let $N=\max\{k-1,p\}$.
+  We claim that $b_0\cdots b_{N}$ is not contained in $K$.  
+  Indeed, $p$ is the encoding of $M$ and $M p$ converges to $b_p$ in under $N$ steps.
+\end{proof}
+
+\section{Non-computable functions and Observational Equivalence}
+\label{SecNonComputable}
+
+The presence of non-computable functions in the semantics for a language does not normally present a problem for Full Abstraction.  
+In previous sections, we have been able to appeal to continuity results that tell us that the intrinsic equivalence relation in our model is determined entirely by some collection of \emph{compact} (and hence computable) morphisms.
+In the presence of countable nondeterminism, these continuity results no longer hold, and the intrinsic equivalence becomes sensitive to noncomputable elements in the semantics.
+
+To investigate this, we define a language IA+Functions by extending IA with, for each (set-theoretic) function $f\from \bN \to \bB$, a primitive $\Phi_f \from \nat \to \bool$ with the following operational semantics.
+\[
+  \inferrule*{\Gamma,s\ts N \converges n,s'}{\Gamma,s \ts \mathop{\Phi_f}N \converges f(n),s'}
+  \]
+
+We make some new claims.
+
+\begin{proposition}
+  i) The Game Semantics model from Sections \ref{ChapGames} and \ref{ChapFullAbstraction} is Computationally Adequate and Fully Abstract for IA+Functions.
+
+  ii) Two terms of IA are observationally equivalent within IA if and only if they are observationally equivalent when we consider them as terms of IA+Functions.
+\end{proposition}
+\begin{proof}
+  (i): The denotation of $\Phi_f$ is the strategy with maximal plays of the form
   \[
@@
     \]
-  which have the property stated above.
-\end{example}
-\begin{proof}[Sketch proof of \ref{PropNotFullyAbstract}]
-  We fix an inductive encoding $\encode -$ of IA terms and assume the existence of an \emph{interpreter}
-  \[
-    \Int \from \bN \to \bN\,.
-    \]
-  $\Int n$ first checks whether its argument $n$ is the encoding of a valid IA term of type $\nat$; if it is not, then it returns the value $0$, which will take the place of an error value.
-  If it is -- say, $n=\encode{P}$, then $\Int n$ evaluates the program $P$; if this evaluation terminates, then it adds $1$ to the value returned and returns that.  
-  The reason we add $1$ to the value is primarily to avoid the error value $0$, though it will serve a purpose later too.
-
-  We now consider a slight variation $\Int'$ of the term $\Int$, which takes in an additional parameter called a \emph{timeout}.  
-  $\Int' n \encode{P}$ will evaluate the term $P$ for $n$ steps, returning $m+1$ as before if $P$ converges to $m$ in that time, and otherwise returning $0$ if $P$ has not yet terminated after $n$ steps.
-
-  Now consider the term
-  \setlength{\jot}{0pt}%
+  for $n\in \bN$.  
+  In the notation of Section \ref{DenotationalSemanticsOfIdealizedAlgol}, this is the strategy given by the formula
+  \[
+    ( f(0), f(1), f(2), \cdots )\,.
+    \]
+  Computational adequacy for this function follows by exactly the same arguments as for the functions $\suc$ and $\pred$; note that we used no special properties of the successor or predecessor functions in Chapter \ref{ChapFullAbstraction}, so exactly the same arguments go through for any function $\bN \to \bN$.
+  Full Abstraction also goes through without modification.
+
+  (ii): This follows from (i), since the two languages share a Fully Abstract model.
+  \label{PropPlusFunctions}
+\end{proof}
+
+In the presence of countable nondeterminism, however, we shall show that the equivalent of (ii) does not hold; i.e., that there are observationally equivalent terms of nondeterministic IA that are observationally distinguishable within IA+Functions+Countable nondeterminism.
+
+This will then give the reason why our proposed semantics cannot be fully abstract: our starting model is fully abstract for both IA and IA+Functions and we have already proved that the nondeterministic version is Equationally Sound for nondeterministic IA (and, by a similar argument, for IA+Functions+Countable nondeterminism).
+Equational Soundness tells us that any observationally distinguishable terms of IA+Functions+Countable nondeterminism must therefore be distinguished by the model, proving that it cannot be fully abstract for IA+Countable nondeterminism.
+
+Let us now examine the two terms that we shall be considering.  
+First, we define $M \from (\nat \to \bool) \to \com$ by the formula
 \begin{align*}
-    M=&\lambda f^{\nat \to \nat} .\neww(\lambda p.p\gets\ask_\bN;\\
-      &\hspace{82pt}\new(\lambda v.v\gets f(\oc p);\\
-        &\hspace{116pt}\new(\lambda x.x\gets \Int' \ask_\bN (\app \oc p \encode {\oc p});\\
-          &\hspace{148pt}\IfO \oc x \Then \skipp \Else\\
-            &\hspace{168pt}(\If \oc v = \oc x \Then \skipp \Else \Omega))))
+  M=& \lambda f.\Let k=?\In \\
+  & \hspace{10pt} \If K((f\,0)\cdots(f\,(k-1))) \Then (\skipp\Or\skipp) \Else (\skipp \Or \Omega)\,,
 \end{align*}
-  of type $(\nat\to \nat) \to \com$.
-  Here, $\app$ is the constructor used in the encoding to apply one term to another: so if $p$ is the encoding of an IA $P\from \nat \to \nat$, then $\app p \encode p$ will be the encoding of the term $P\,p$; i.e., $P$ applied to its own encoding.
-
-  Consider also the term
-  \[
-    N = \lambda f^{\nat \to \nat}.f(\ask_\bN);\IfO \ask_\bN \Then \skipp \Else \Omega\,.
-    \]
-  of type $(\nat \to \nat) \to \com$.  
-  Here, we have used the notation $P;Q$ to mean $\IfO P \Then Q \Else Q$ for $P\from \nat$; i.e., the program that evaluates $P$, forgets the result and then evaluates $Q$.
-
-  We claim that $M$ and $N$ are may-and-must-observationally equivalent.  
-  We will save the formal proof of this until we have a working fully abstract semantics; for now, we shall give an informal argument.
-
-  First, note that $M$ and $N$ have the same behaviour in any applicative context; i.e., if $F\from \nat \to \nat$ is a term, then $MF\converges \skipp$ if and only if $NF\converges\skipp$ and $MF\mustconverge$ if and only if $NF\mustconverge$.
-  Indeed, we certainly have $MF\converges\skipp$ and $NF\converges\skipp$.
-  Moreover, $NF\diverges$, so we need to show that $MF\diverges$.
-
-  Consider the following evaluation path of $MF$.
-  \begin{enumerate}
-    \item The variable $p$ acquires the value $\encode F$.  
-      At this point, we apply $F$ to $\encode F$.  
-      If this computation diverges, then we win.  
-      Otherwise, suppose that $F\encode F$ converges to some value $n$.  
-      Then $v$ acquires the value $n$.
-      Let $k$ be the number of steps taken for $P$ to converge to $n$.
-    \item Now suppose that the next instance of $\ask_\bN$ acquires the value $k$.  
-      We already know that $\Int' k (\app \oc p \encode{\oc p})$ will converge to $n+1$, so $x$ acquires the value $n+1$.
-    \item Now $n+1 \ne n$, so the term diverges.
-  \end{enumerate}
-  Therefore, $MF\diverges$.
-
-  The case for a non-applicative context is the same, after we have made the observation that any side-effects that occur when $f$ is evaluated will take place in both terms in the case that they converge, while they will have no effect if the terms diverge.
-
-  After satisfying ourselves that $M$ and $N$ are observationally equivalent, we claim that they are distinguished by the semantics, which proves that the model is not fully abstract.
-
-  Indeed, let $\phi\from \bN \to \bN$ where $\phi(p)$ is $n+1$ if $p$ is the encoding of a term $P\from\nat \to \nat$ and $P\;p\converges n$ and $\phi(p)=0$ otherwise (including the case that $P\;p\diverges$).
-
-  We know that $\deno{N};\sigma\not\downarrow_{\must}$ for all $\sigma$, because $N$ essentially discards its argument.
-  We claim that $\deno{M};\sigma_\phi\downarrow_{\must}$, proving that $N\not\sim_{\must} M$.
-
-  Indeed, by compositionality and adequacy of the semantics, we may consider $\sigma_\phi$ to behave as a term $\Phi\from\nat \to \nat$ with the operational behaviour that
-  \[
-    \inferrule*{\Gamma,s\ts N \converges n,s'}{\Gamma,s\ts \Phi N \converges \phi(n),s'}\,.
-    \]
-  Then, whatever the value of $p$, either $\Int' \ask_{\bN} (\app \oc p \encode{\oc p})$ will return $0$ or it will return the value of $\phi(\oc p)$.  
-  In either case, the term will not diverge.
-\end{proof}
-
-\begin{remark}
-  The term $M$ that we have constructed in this proof is an instance of the \emph{Kleene tree} (see, for example, \cite{KleeneTree}), a computable tree with an infinite path but no computable infinite path.
-\end{remark}
-
-The proof of Proposition \ref{PropNotFullyAbstract} makes it clear that the problem is the existence in the semantics of morphisms that behave like certain noncomputable functions.  
+where
+\[
+  ((f\,0)\cdots(f\,(k-1)))
+  \]
+is shorthand for the natural number corresponding to the binary sequence given by $(f\,0)$ up to $(f\,(k-1))$, $\Or$ is binary choice and $K$ is the Kleene tree from the previous section.
+Now define $N \from (\nat \to \bool) \to \com$ by the formula
+\begin{align*}
+  N=& \lambda f.\Let k=?\In (f\,0);\cdots;(f\,(k-1));\\
+  &\hspace{10pt}\skipp \Or \Omega\,,
+\end{align*}
+where we have used the notation $P;Q$ (for $P \from \nat$) as a shorthand for
+\[
+  \IfO P \Then Q \Else Q\,;
+  \]
+i.e., the program that evaluates $P$, forgets the result and then evaluates $Q$.
+The reason for evaluating $(f\,0), \cdots, (f\,(k-1))$ before either returning or diverging is to make sure that any side effects of the evaluation of $f$ are the same for both programs (we shall assume that $K$ operates in such a way that it evaluates each of the $(f\,i)$ exactly once).
+
+We now claim that $M$ and $N$ are observationally equivalent in nondeterministic IA.  
+We will postpone the formal proof of this fact until we have a working Fully Abstract semantics for that language, but a rough argument is as follows.  
+$M$ and $N$ can only be distinguished by an $f$ such that
+\[
+  K((f\,0)\cdots(f\,(k-1)))
+  \]
+evaluates to $\true$ for all $k$.  
+Otherwise, both terms may diverge.  
+But we have shown in the previous section that there is no computable $f$ with this property.
+
+Meanwhile, $M$ and $N$ are not observationally equivalent in nondeterministic IA+Functions; indeed, if $\kappa\from \bN \to \bB$ is an infinite path in the Kleene tree, then $M$ and $N$ are distinguished by $\Phi_\kappa$.
+
+\section{Full Abstraction for Countable Nondeterminism under Must Testing}
+
+The previous two sections make it clear that the problem is the existence in the semantics of morphisms that behave like certain noncomputable functions.  
 The presence of such morphisms is normally an orthogonal issue to full abstraction, since we can usually assume that the strategy $\alpha$ in the definition of intrinsic equivalence is compact.
@@
 This result is not quite enough for us, since the innocent intrinsic equivalent is coarser than that for visible strategies.  
-Instead, we appeal to the following result, which gives us definability \emph{on the nose}.  
-For this result, we need to extend PCF with a new constant $\lett$ or $\byval$ where the semantics of $\lett x = M\inn N$ is to evaluate the term $M$ and bind the result to the free variable $x$ in $N$.
+However, if we add the constant $\lett$ to PCF, then we can get a stronger result that gives us definability \emph{on the nose}.
 
@@
 
-We can interpret $\lett$ in Idealized Algol by defining
-\[
-  \lett x = M \inn N
-  \]
-to be the term
-\[
-  \neww (\lambda x. x\gets M;N[\oc x/x])\,.
-  \]
 Moreover, these results are all easily extended to the IA ground types that are not present in PCF.  
@@
 
-As an application of this fully abstract semantics, we clear up a loose end from the proof of Proposition \ref{PropNotFullyAbstract}.
+As an application of this fully abstract semantics, we clear up a loose end from Section \ref{SecNonComputable}.
 
 \begin{lemma}
-  The terms $M,N\from (\nat \to \nat) \to \com$, as defined in the proof of Proposition \ref{PropNotFullyAbstract}, are observationally equivalent in Idealized Algol with countable nondeterminism.
+  The terms $M,N\from (\nat \to \bool) \to \com$, as defined in Section \ref{SecNonComputable}, are observationally equivalent in Idealized Algol with countable nondeterminism.
 \end{lemma}
@@
     \begin{array}{cccc}
-      \bN & \bN & \bN & \bC \\
+      \bN & \bN & \bB & \bC \\
           &     &     &  q  \\
        q  &     &     &     \\
-       p  &     &     &     \\
+       k  &     &     &     \\
           &     &  q  &     \\
           &  q  &     &     \\
-          &  p  &     &     \\
-          &     &  c  &     \\
+          &  0  &     &     \\
+          &     & a_0 &     \\
+          &\vdots&    &     \\
+          &     &  q  &     \\
+          &  q  &     &     \\
+          &(k-1)&     &     \\
+          &     &a_{k-1}&   \\
        q  &     &     &     \\
@@
 
-  More specifically, in $\deno M$, the final move $a$ always occurs unless the number $p$ is the encoding of a term $P\from\nat \to \nat$ of Idealized Algol such that the evaluation $P\;p$ converges in fewer than $n$ steps to a number different from $c+1$.
+  More specifically, in $\deno M$, the final move $a$ always occurs if $a_0\cdots a_{k-1}$ is a finite path in the Kleene tree; otherwise, it may or may not occur, depending on whether $n$ is $0$ or not.
 
   Meanwhile, the final move $a$ is present in $\deno N$ if and only if the number $n$ is equal to $0$.
-  Since an evaluation $P\;p$ will never converge in fewer than $0$ steps, this means that $\deno N$ is a subset of $\deno M$.
-
-  Fix some strategy $\alpha\from ((\bN \to \bN)\to\bC) \to \bC$ in $\G_X$ and suppose that
+  This means that $\deno N$ is a subset of $\deno M$.
+
+  Fix some strategy $\alpha\from ((\bN \to \bC)\to\bC) \to \bC$ in $\G_X$ and suppose that
   \[
@@
     \]
-  To show that $M$ and $N$ are observationally equivalent, it will be sufficient to prove that $\alpha$ is not recursive.
-
   First note that we always have $\deno M;\alpha\approx_{\may}\deno N;\alpha$ for arbitrary $\alpha$, which we can deduce by ignoring the copy of $\bN$ on the left and considering $\deno M$ and $\deno N$ as nondeterministic strategies.
@@
     \begin{array}{ccc}
-      \bN & \bN & \bC \\
+       \bN & \bB & \bC \\
            &     &  q  \\
+           &     &     \\
+           &     &     \\
            &  q  &     \\
         q  &     &     \\
-       p  &     &     \\
-          &  c  &     \\
-          &     & a
+        0  &     &     \\
+           & a_0 &     \\
+     \vdots&\vdots&   \\
+           &  q  &     \\
+        q  &     &     \\
+      (k-1)&     &     \\
+           &a_{k-1}&   \\
+           &     &     \\
+           &     &     \\
+           &     & (a)
     \end{array}\,,
     \]
-  where $p$ is arbitrary.
+  where $k$ is arbitrary.
 
@@
   Since $\deno M$ and $\deno N$ do not differ until the very last move, this means that $\alpha$ must respond to the initial move $q$ in the rightmost copy of $\bC$ with the move $q$ in the copy of $\bC$ on the left (otherwise, $\deno N;\alpha$ is winning), and that $\alpha$ must be total (otherwise, $\deno M;\alpha$ is not winning).
-  Then we see that for any value of $p$, $\alpha$ must reply to the move $p$ with the number $\phi(p)$, where $\phi$ is the function defined above.  
-  Otherwise, $\deno M;\alpha$ is not winning.
-
-  But if $\alpha$ is a recursively enumerable subset of $P_{\bN \to ((\bN \to \bN) \to \bC) \to \bC}$, then that would mean that the set of pairs $(p,\phi(p))$ were a recursively enumerable subset of $\bN \times \bN$, and this is not the case, since $\phi$ is not a recursive function.
+  $\alpha$ replies to each move $i$ in $\bN$ with some move in $\bB$, and this defines a function $\bN \to \bB$.  
+  Since $\alpha$ is total, this function must trace out an infinite path in the Kleene tree.
+
+  But if $\alpha$ were recursive, then we would be able to recover this infinite path from $\alpha$ via a recursive algorithm, and we know that this is not possible
   Therefore, $\alpha$ is not recursive.
@@
 \begin{proof}
-  Suppose that $\alpha$ separates $\sigma$ and $\tau$ in $\G_X$, so without loss of generality, we have
+  Suppose that $\alpha \from (A \to B) \to \bC$ separates $\sigma$ and $\tau$ in $\G_X$, so without loss of generality, we have
   \begin{mathpar}

### 2020-04-04 Thesis/games.tex
The final commit?
Corrections.

@@
 
-In other words, a given a term $M$ of type $\Var$, we can either insert a natural number into $M$ or we can request a natural number from $M$.  
-An example is when $M$ acts like a storage cell, returning the last number that was inserted into it, but $M$ could act in a different way.
+In other words, any term $M$ of type $\Var$ supports two operations: one `read' operation that returns a natural number and one `write' operation that accepts a natural number.
+The most natural case to consider is when $M$ actually corresponds to a storage cell, with `write' updating the value and `read' returning it, but our language will permit any other implementation of the $\Var$ interface, including, for example, a term of type $\Var$ that ignores any values `written' to it and always returns $0$ when read: such terms, which fulfil the type-theoretic contract of a storage cell without replicating its behaviour, are sometimes called `bad variables' (e.g., in \cite[\sec 2]{SamsonGuyIAPassive}).
 
@@
 
-We have two ways to create tems of type $\Var$.  
+We have the $\lett$ keyword that allows us to evaluate an expression and bind the result to a variable name.
+\begin{mathpar}
+  \inferrule*[right={$S\in\{\bool,\nat\}$; $T\in\{\com,\bool,\nat\}$}]{\Gamma \ts M \from S \\ \Gamma,x\from S \ts N \from T}{\Gamma \ts \lett_{S,T} x = M \inn N \from T}
+\end{mathpar}
+
+We have two ways to create terms of type $\Var$.  
 The first gives us the storage-cell behaviour.
@@
 \end{mathpar}
-The idea here is that if $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).
+The idea here is that if $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual (zero-initialized) storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).
 
@@
 
+We shall call an odd-length sequence $s\in P_A$ an \emph{$O$-position} and an even-length sequence a \emph{$P$-position}.
+
 \begin{definition}
-  Given a legal sequence $s\in \L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.
-
-  We write $s\vert_b$ for the subsequence of $s$ given by all moves in $s$ that are hereditarily justified by $b$.
-  Given a set $I$ of initial moves, we write $s\vert_I$ for the subsequence of $s$ given by all moves that are hereditarily justified by some $b\in I$.
-
-  A \emph{game} is a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
+  A \emph{game} is a tuple
+  \[
+    A=(M_A,\lambda_A,\ts_A,P_A)
+    \]
+  where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$.
 \end{definition}
-
-We shall call an odd-length sequence $s\in P_A$ an \emph{$O$-position} and an even-length sequence a \emph{$P$-position}.
 
@@
 \begin{definition}
-  Given games $A,B$, define a game $A\times B$ by
+  Given games $A,B$, define the \emph{product} of $A$ and $B$ to be the game $A\times B$ given by
   \begin{itemize}
@@
 \begin{lemma}
-  We extend the function $\lambda_A^{OP}$ to sequences of moves by
+  We extend the function $\lambda_A^{OP}$ to alternating sequences of moves by
   \begin{itemize}
@@
     \]
-  If $P_B=\{i_*(s)\suchthat s\in P_A\}$, then we call it a \emph{structural isomorphism}, and we write $\cc_i$ (`copycat') instead of $\subs_i$.
+  If $P_B=\{i_*(s)\suchthat s\in P_A\}$, then we call $i$ a \emph{structural isomorphism}, and we write $\cc_i$ (`copycat') instead of $\subs_i$.
 \end{definition}
+
+\begin{example}
+  If, in particular, $A = B$ and $i$ is the identity, then the resulting strategy is sometimes called \emph{the} copycat strategy on $A \implies A$.  
+  It will take the role of the identity in our categorical semantics.
+\end{example}
+
+\begin{example}
+  If $A$ and $B$ are games, then the set of plays of $A \sequoid B$ is a subset of the set of plays of $A \tensor B$.  
+  This will give us a subset inclusion morphism $A \tensor B \implies A \sequoid B$.
+\end{example}
+
+\begin{example}
+  If $(A_i)$ is a collection of games, then there is a natural injection from the set of plays for $A_j$ into the set of plays for $\prod_i A_i$.  
+  This gives us projection morphisms $\prod_i A_i \implies A_j$ for each $j$.
+\end{example}
 
@@
 
-  This argument also shows that $\subs_i$ is \emph{history-free} -- i.e., that its reply to an $O$-position is entirely determined by the last $O$-move -- and therefore it is certainly innocent.
+  This argument also shows that $\subs_i$ is \emph{history-free} -- i.e., that its reply to an $O$-position is entirely determined by the last $O$-move -- and therefore that it is certainly innocent.
 
@@
   Let $i$ be a subset inclusion from $A$ to $B$ and let $j$ be a subset inclusion from $B$ to $C$.  
-  Then $j\circ i$ is a subset inclusion from $A$ to $C$ and $\cc_{j\circ i}=\subs_j;\subs_i\from C \implies A$.
+  Then $j\circ i$ is a subset inclusion from $A$ to $C$ and $\subs_{j\circ i}=\subs_j;\subs_i\from C \implies A$.
 \end{corollary}
@@
     \]
-  Moreover, either $\lambda_A^{OP}(s\vert_A)=P$ or $\lambda_B^{OP}(s\vert_B)=P$.
+  Moreover, either $\lambda_A^{OP}(s\vert_A)=P$ or $\lambda_B^{OP}(s\vert_B)=P$; i.e., the bottom row of the table above does not occur.
   \label{LemTensorAnalogue}
@@
     \]
+  We shall refer to strategies of the form $\zz_\phi$ as \emph{zigzag strategies}.
 \end{definition}
@@
   If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree immersion from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
+\end{example}
+\begin{example}
+  If $A,B,C$ are games, then we have a natural morphism
+  \[
+    (A \sequoid C) \times (B \sequoid C) \implies (A \times B) \sequoid C\,,
+    \]
+  given by a tree immersion from the set of plays of $(A \times B) \sequoid C$ to the set of plays of $(A \sequoid C) \times (B \sequoid C)$.  
+  Note that this is not a subset inclusion: if $s$ is a play  of $(A \times B) \sequoid C$ ending in a move in $C$, then the copy of $C$ that that move ends up in is determined by whether $s$ begins with a move in $A$ or in $B$.
 \end{example}
@@
   Conversely, suppose that $s\in P_{C\implies A}$ and that $s^\phi\in\sigma$.  
-  We construct a sequence $\s\in\sigma\|\zz_phi$ such that $\s\vert_{C,B}=s^\phi$ and $\s\vert_{C,A}=s$ by taking the sequence $s$ and inserting, in order, the elements of the sequence $\phi(s\vert_A)$ immediately after each $O$-move in $s\vert_C$ and immediately before each $P$-move in $C$, leaving the rest of $s$ intact.
+  We construct a sequence $\s\in\sigma\|\zz_\phi$ such that $\s\vert_{C,B}=s^\phi$ and $\s\vert_{C,A}=s$ by taking the sequence $s$ and inserting, in order, the elements of the sequence $\phi(s\vert_A)$ immediately after each $O$-move in $s\vert_C$ and immediately before each $P$-move in $C$, leaving the rest of $s$ intact.
   Then $\s\vert_{C,B}=s^\phi\in\sigma$ and $\s\vert_{B,A}\in\zz_\phi$, by construction.  
@@
 \end{proof}
+
+Applying this to subset inclusions using Proposition \ref{PropSubsetInclusionEpic}, we see that a surjective subset inclusion is both a monomorphism and a split epimorphism, and hence an isomorphism.
 
@@
 To start with, we would like to be able to say that $\blank\sequoid\blank$ is a functor from $\G \times \G \to \G$, as is the case with the tensor product $\blank\tensor\blank$.  
-However, this does not quite work: given strategies $\sigma\from A \implies B$ and $\tau\from C \implies D$, we may not get a well-formed strategy for $(A \sequoid C) \implies (B \sequoid D)$ by `playing according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $C$ and $D$'.
-The reason is that the constraint that player $O$ plays in $B$ before $D$ is not strong enough to force player $P$ to play in $A$ before $C$; indeed, suppose that $\sigma$ tells player $P$ to respond to an initial move in $B$ with another move in $B$.
-Suppose that player $O$ then decides to make a move in $D$.  
-If $\tau$ tells player $P$ to respond to this move in $D$ with a move in $C$, then she will be stuck, unable to play this move because no move has yet been played in $A$.
+However, this does not quite work: given strategies $\sigma\from A \implies B$ and $\tau\from C \implies D$, we would \emph{like} to say that we get a strategy $\sigma\sequoid\tau \from A \sequoid C \implies B \sequoid D$.
+However, this does not quite work as we might expect: suppose player $O$ begins (as he must) with some move $b$ in $B$, and suppose that $\sigma$'s reply to $b$ is another move $b'$ in $B$.  
+Suppose then that player $O$ switches and plays a move $d$ in $D$, and suppose that $\tau$'s reply to $d$ is a move $c$ in $C$.  
+Then player $P$ is unable to play according to $\tau$, because $d$ is not yet a legal move in $(A\sequoid C) \implies (B \sequoid D)$ since no move has yet been played in $A$.
 
@@
   \begin{mathpar}
-    \wk_{A,X}=\subs_{j} \from JA \tensor X = A \tensor X \to A \sequoid X = J(A \sequoid X)
+    \wk_{A,X}\from JA \tensor X = A \tensor X \to A \sequoid X = J(A \sequoid X)
   \end{mathpar}
@@
   For example, to show that the first diagram commutes in $\G$, we must show that the following diagram commutes in $\Set$.
-  \scriptsize
   \[
     \begin{tikzcd}[column sep=16pt, row sep=30pt]
-      ((M_A + M_X) + M_Y) + M_Z \arrow[r, "{[\assoc_{M_A,M_X,M_Y},\id_{M_Z}]}" yshift=3pt] \arrow[d, "{\assoc_{M_A+M_X,M_Y,Z}}" description]
-        & (M_A + (M_X + M_Y)) + M_Z \arrow[r, "{\assoc_{M_A,M_X+M_Y,M_Z}}" yshift=3pt]
-          & M_A + ((M_X + M_Y) + M_Z) \arrow[dl, "{[\id_{M_A},\assoc_{M_X,M_Y,M_Z}]}"] \\
-      (M_A + M_X) + (M_Y + M_Z) \arrow[r, "{\assoc_{M_A,M_X,M_Y+M_Z}}" yshift=3pt]
+      ((M_A + M_X) + M_Y) + M_Z \arrow[r, "{[\assoc_{M_A,M_X,M_Y},\id_{M_Z}]}" yshift=6pt] \arrow[d, "{\assoc_{M_A+M_X,M_Y,Z}}"']
+        & (M_A + (M_X + M_Y)) + M_Z \arrow[d, "{\assoc_{M_A,M_X+M_Y,M_Z}}" yshift=3pt] \\
+      (M_A + M_X) + (M_Y + M_Z) \arrow[dr, "{\assoc_{M_A,M_X,M_Y+M_Z}}"' yshift=3pt]
+        & M_A + ((M_X + M_Y) + M_Z) \arrow[d, "{[\id_{M_A},\assoc_{M_X,M_Y,M_Z}]}"] \\
         & M_A + (M_X + (M_Y + M_Z))
-          &
     \end{tikzcd}
     \]
-  \normalsize
-  This diagram is, of course, none other than the pentagram diagram for the coproduct $+$ in $\Set$.  
+  This diagram is, of course, none other than the pentagon diagram for the coproduct $+$ in $\Set$.  
   Similarly, the second and third diagrams in Definition \ref{DefSequoidalCategory} reduce in this case to the triangle diagrams for the coproduct $+$ in $\Set$.
@@
   \[
-    \dec_{(a_i),x} = \langle \pr_i\sequoid x \rangle \from \left(\prod_ia_i\right) \sequoid x \to \prod_i (a_i \sequoid x)
+    \dist_{(a_i),x} = \langle \pr_i\sequoid x \rangle \from \left(\prod_ia_i\right) \sequoid x \to \prod_i (a_i \sequoid x)
     \]
@@
 
-  Therefore, $\phi$ is a tree isomorphism, so $\dec_{(A_i),X} = \zz_\phi$ is an isomorphism by Proposition \ref{PropTree}.
+  Therefore, $\phi$ is a tree isomorphism, so $\dist_{(A_i),X} = \zz_\phi$ is an isomorphism by Proposition \ref{PropTree}.
 \end{proof}
@@
 
+We now move on to the categorical semantics of the exponential operator $\oc\blank$.  
+As the name suggests, this operator gives us a way to model the exponential connective from linear logic.  
+More specifically, we shall show that, for a certain class of games $A$ (the \emph{well-opened games}), $\oc A$ is the carrier for a \emph{cofree commutative comonoid} over $A$.  
+We use a result of \Mellies, Tabareau and Tasson to show why this is the case.
+
 \begin{definition}
@@
   \[
-    \sym^\pi \from A_1 \tensor \cdots \tensor A_n \toisom A_{\pi(1)} \tensor \cdots \tensor A_{\pi(n)}\,.
+    \sym_\pi \from A_1 \tensor \cdots \tensor A_n \toisom A_{\pi(1)} \tensor \cdots \tensor A_{\pi(n)}\,.
     \]
@@
   Let $\C$ be an inclusive, strongly distributive, decomposable sequoidal category.  
-  Then $\C$ has all symmetrized tensor powers.
+  Then $\C$ has all symmetrized tensor powers and they commute with the tensor product.
   \label{PropSequoidPower}
@@
     B\tensor (A \sequoid\blank)^kA^{\tensor n}
-    \xrightarrow{\langle B\tensor(A \sequoid\blank)^k \sym^\pi \rangle}
+    \xrightarrow{\langle B\tensor(A \sequoid\blank)^k \sym_\pi \rangle}
     (B\tensor(A \sequoid\blank)^kA^{\tensor n})^{n!}
@@
   \normalsize
-  (i.e., the morphism $\langle B\tensor(A\sequoid\blank)^k(\sym^\pi;\wk^n)\rangle$) is a monomorphism.
-  In particular, taking $k=0$, we will have shown that $\langle B\tensor (\sym^\pi;\wk^n)\rangle$ is a monomorphism.
+  (i.e., the morphism $\langle B\tensor(A\sequoid\blank)^k(\sym_\pi;\wk^n)\rangle$) is a monomorphism.
+  In particular, taking $k=0$, we will have shown that $\langle B\tensor (\sym_\pi;\wk^n)\rangle$ is a monomorphism.
 
   The hypothesis is clearly true for $n=0$; in the general case, we have a composite
-  \begin{mathpar}
-    B\tensor (A\sequoid\blank)^kA^{\tensor (n+1)}
-    \xrightarrow{B\tensor (A\sequoid\blank)^k\langle \sym^{n+1}_i;\wk_{A,A^{\tensor n}}\rangle}
-    B\tensor (A \sequoid\blank)^k(A\sequoid A^{\tensor n})^{n+1}
-    \xrightarrow{\langle B\tensor (A\sequoid\blank)^k;\pr_i\rangle}
-    (B\tensor(A \sequoid\blank)^{k+1} A^{\tensor n})^{n+1}
-    \to
-    (B\tensor A ^{\sequoid (k + n + 1)})^{(n+1)!}\,,
+  \begin{IEEEeqnarray*}{Cl}
+    &B\tensor (A\sequoid\blank)^kA^{\tensor (n+1)}\\
+    \xrightarrow{\mathmakebox[120pt]{B\tensor (A\sequoid\blank)^k\langle \sym^{n+1}_i;\wk_{A,A^{\tensor n}}\rangle}}
+    &B\tensor (A \sequoid\blank)^k(A\sequoid A^{\tensor n})^{n+1}\\
+    \xrightarrow{\mathmakebox[120pt]{\langle B\tensor (A\sequoid\blank)^k;\pr_i\rangle}}
+    &(B\tensor(A \sequoid\blank)^{k+1} A^{\tensor n})^{n+1}\\
+    \xrightarrow{\mathmakebox[120pt]{}}
+    &(B\tensor A ^{\sequoid (k + n + 1)})^{(n+1)!}\,,
+  \end{IEEEeqnarray*}
+  \begin{mathpar}
   \end{mathpar}
@@
     (A \sequoid\blank)^{k+1}A^{\tensor n}
-    \xrightarrow{\langle (A \sequoid \blank)^{k+1}\sym^\sigma\rangle}
+    \xrightarrow{\langle (A \sequoid \blank)^{k+1}\sym_\sigma\rangle}
     ((A \sequoid\blank)^{k+1}A^{\tensor n})^{n!}
@@
   \[
-    \langle B\tensor(A\sequoid\blank)^k(\sym_i^{n+1};\wk_{A,A^{\tensor n}};(A\sequoid\sym^\sigma);(A\sequoid\wk^n)) \rangle\,,
+    \langle B\tensor(A\sequoid\blank)^k(\sym_i^{n+1};\wk_{A,A^{\tensor n}};(A\sequoid\sym_\sigma);(A\sequoid\wk^n)) \rangle\,,
     \]
@@
   \[
-    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A\tensor\sym^\sigma);(A\tensor\wk^n);\wk_{A,A^{\sequoid n}})\rangle\,,
+    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A\tensor\sym_\sigma);(A\tensor\wk^n);\wk_{A,A^{\sequoid n}})\rangle\,,
     \]
@@
   \[
-    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A \tensor \sym^\sigma);\wk^{n+1}\rangle\,.
-    \]
-
-  Now, given $i\in\{1,\cdots n+1\}$ and $\sigma\in\S_n$, there is a unique permutation $\pi\in\S_{n+1}$ such that $\sym_i^{n+1};(A\tensor\sym^\sigma=\sym^\pi)$; moreover, this defines a bijection from $\{1,\cdots,n+1\}\times\S_n \to \S_{n+1}$.
+    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A \tensor \sym_\sigma);\wk^{n+1}\rangle\,.
+    \]
+
+  Now, given $i\in\{1,\cdots n+1\}$ and $\sigma\in\S_n$, there is a unique permutation $\pi\in\S_{n+1}$ such that $\sym_i^{n+1};(A\tensor\sym_\sigma=\sym_\pi)$; moreover, the map $(i,\sigma)\mapsto\pi$ defines a bijection from $\{1,\cdots,n+1\}\times\S_n \to \S_{n+1}$.
   Therefore (after choosing an appropriate enumeration of our permutations), we see that this composite is in fact equal to
   \[
-    \langle B\tensor(A \sequoid\blank)^k (\sym^\pi;\wk^{n+1})\rangle\,.
-    \]
-  Therefore, $\langle B\tensor(A \sequoid\blank)^k(\sym^\pi;\wk^{n+1})\rangle$ is a monomorphism as desired, completing the induction.
+    \langle B\tensor(A \sequoid\blank)^k (\sym_\pi;\wk^{n+1})\rangle\,.
+    \]
+  Therefore, $\langle B\tensor(A \sequoid\blank)^k(\sym_\pi;\wk^{n+1})\rangle$ is a monomorphism as desired, completing the induction.
 
@@
 
-  First, we show inductively that $\eq_n;\sym^\pi;\wk^n=\id_{A^{\sequoid n}}$ for all permutations $\pi$ of $S_n$.
+  First, we show inductively that $\eq_n;\sym_\pi;\wk^n=\id_{A^{\sequoid n}}$ for all permutations $\pi$ of $S_n$.
   This is certainly true for $n=0$; in the general case, let $\pi\in \S_{n+1}$ be a permutation.  
@@
   \[
-    \sym_j^{n+1};(A\tensor\sym^\sigma) = \sym^\pi\,.
+    \sym_j^{n+1};(A\tensor\sym_\sigma) = \sym_\pi\,.
     \]
@@
   \begin{IEEEeqnarray*}{Cl}
-    & \eq_{n+1};\sym^\pi;\wk^{n+1} \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym^\pi;(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};(A\tensor\sym^\sigma);(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};\wk_{A,A^{\tensor n}};(A \sequoid \sym^\sigma);(A \sequoid \wk^n) \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\langle \sym_i^{n+1};\wk_{A,A^{\tensor n}}\rangle;\pr_j;(A \sequoid \sym^\sigma);(A \sequoid \wk^n) \\
-    = & A \sequoid (\eq_n;\sym^\sigma;\wk^n)\,,
+    & \eq_{n+1};\sym_\pi;\wk^{n+1} \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_\pi;(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};(A\tensor\sym_\sigma);(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};\wk_{A,A^{\tensor n}};(A \sequoid \sym_\sigma);(A \sequoid \wk^n) \\
+    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\langle \sym_i^{n+1};\wk_{A,A^{\tensor n}}\rangle;\pr_j;(A \sequoid \sym_\sigma);(A \sequoid \wk^n) \\
+    = & A \sequoid (\eq_n;\sym_\sigma;\wk^n)\,,
   \end{IEEEeqnarray*}
@@
   Now let $\rho$ be a permutation in $\S_n$.  
-  We claim that $\eq_n=\eq_n;\sym^{\rho}$.
+  We claim that $\eq_n=\eq_n;\sym_{\rho}$.
 
@@
   \begin{IEEEeqnarray*}{rCl}
-    \eq_n;\langle \sym^{\pi} ; \wk^n \rangle
-    & = & \langle \eq_n;\sym^{\pi};\wk^n \rangle \\
+    \eq_n;\langle \sym_{\pi} ; \wk^n \rangle
+    & = & \langle \eq_n;\sym_{\pi};\wk^n \rangle \\
     & = & \langle \id \rangle \\
-    & = & \langle \eq_n;\sym^{\rho\pi};\wk^n \rangle \\
-    & = & \eq_n;\sym^{\rho};\langle \sym^\pi ; \wk^n \rangle\,.
+    & = & \langle \eq_n;\sym_{\rho\pi};\wk^n \rangle \\
+    & = & \eq_n;\sym_{\rho};\langle \sym_\pi ; \wk^n \rangle\,.
   \end{IEEEeqnarray*}
-  Since $\langle \sym^\pi;\wk^n\rangle$ is a monomorphism, this means that $\eq_n=\eq_n;\sym^{\rho}$, as desired.
+  Since $\langle \sym_\pi;\wk^n\rangle$ is a monomorphism, this means that $\eq_n=\eq_n;\sym_{\rho}$, as desired.
   Therefore, $\eq_n$ equalizes the morphisms $\eq_n$.  
@@
 
-  Indeed, let $B,C$ be objects of $\C$, and let $f \from C \to B \tensor A^{\tensor n}$ be a morphism such that $f=f;(B\tensor\sym^{\pi})$ for all $\pi\in\S_n$.
+  Indeed, let $B,C$ be objects of $\C$, and let $f \from C \to B \tensor A^{\tensor n}$ be a morphism such that $f=f;(B\tensor\sym_{\pi})$ for all $\pi\in\S_n$.
 
@@
   \begin{IEEEeqnarray*}{rCl}
-    \tilde f;(B \tensor\eq_n);\langle B\tensor(\sym^\pi;\wk^n)\rangle 
-    & = & \langle f;(B \tensor (\wk^n;\eq_n;\sym^\pi;\wk^n)) \rangle \\
+    \tilde f;(B \tensor\eq_n);\langle B\tensor(\sym_\pi;\wk^n)\rangle 
+    & = & \langle f;(B \tensor (\wk^n;\eq_n;\sym_\pi;\wk^n)) \rangle \\
     & = & \langle f;(B\tensor \wk^n)\rangle \\
-    & = & f;\langle B \tensor (\sym^\pi;\wk^n)\rangle\,.
+    & = & f;\langle B \tensor (\sym_\pi;\wk^n)\rangle\,.
   \end{IEEEeqnarray*}
-  Therefore, since $\langle B \tensor (\sym^\pi;\wk^n)\rangle$ is a monomorphism, we know that $\tilde f;(B\tensor \eq_n)=f$.
+  Therefore, since $\langle B \tensor (\sym_\pi;\wk^n)\rangle$ is a monomorphism, we know that $\tilde f;(B\tensor \eq_n)=f$.
 
@@
     \]
-  Therefore, $(B\tensor A^{\sequoid n},B\tensor \eq_n)$ is an equalizer of the arrows $B\tensor \sym^\pi\from B \tensor A^{\tensor n} \to B \tensor A^{\tensor n}$, as desired.
+  Therefore, $(B\tensor A^{\sequoid n},B\tensor \eq_n)$ is an equalizer of the arrows $B\tensor \sym_\pi\from B \tensor A^{\tensor n} \to B \tensor A^{\tensor n}$, as desired.
 \end{proof}
@@
 We are interested in symmetrized tensor powers because of an important result of \Mellies, Tabareau and Tasson.
-Suppose $\C$ is a monoidal category, and that $\C$ has symmetrized tensor powers that commute with the tensor product.  
+Suppose $\C$ is a monoidal category with a terminal unit object, and that $\C$ has symmetrized tensor powers that commute with the tensor product.  
 Given $n$, we have a morphism
@@
     B \tensor A^{n+1} \arrow[r, "B\tensor\eq_{n+1}"]
-      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor A^{\tensor n}\tensor()"] \arrow[d, "\sym^{\pi'}"']
-        & B \tensor A^{\tensor n} \arrow[d, "\sym^\pi"] \\
+      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor A^{\tensor n}\tensor()"] \arrow[d, "\sym_{\pi'}"']
+        & B \tensor A^{\tensor n} \arrow[d, "\sym_\pi"] \\
     %
@@
   (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor ())
-  & = & (B \tensor\eq_{n+1});(B\tensor \sym^{\pi'});(B\tensor A^{\tensor n}\tensor ()) \\
-  & = & (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor());(B\tensor \sym^\pi)\,,
+  & = & (B \tensor\eq_{n+1});(B\tensor \sym_{\pi'});(B\tensor A^{\tensor n}\tensor ()) \\
+  & = & (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor());(B\tensor \sym_\pi)\,,
 \end{IEEEeqnarray*}
@@
   In fact, this is the \emph{cofree commutative comonoid} over $A$ in $\C$.  
-  The counit $\der_A\from \oc A \to A$ of the adjunction is the morphism in the limiting cone.
+  The corresponding counit $\der_A\from \oc A \to A$ is the morphism in the limiting cone.
   \label{TheMtt}
@@
     \]
-  Moreover, $B\tensor\oc A$ is the limit of the sequence
+  Moreover, if $B$ is any game, then $B\tensor\oc A$ is the limit of the sequence
   \[
@@
   \]
-which is a right adjoint on to its image, and therefore preserves products.  
+We define a category $\G_{wo}^{\oc}$ to be the span of this functor inside $\CCom(\G)$.  
+Then the corresponding functor
+\[
+  \G_{wo} \to \G_{wo}^{\oc}
+  \]
+is a right adjoint, and therefore preserves products.  
 So if $A,B$ are well-opened games, then we get a natural isomorphism of comonoids between the tensor product of the comonoids on $\oc A$ and $\oc B$ and the comonoid on $\oc(A\times B)$.
@@
   \]
-We define a category $\G_{wo}^{\oc}$ to be the span of the functor $\G_{wo}\to \CCom(\G)$ inside $\CCom(\G)$.  
-By our discussion above, $\G_{wo}^{\oc}$ is a Cartesian category.
+$\G_{wo}^{\oc}$ therefore inherits the structure of a Cartesian category.
 
@@
   \]
-where the \emph{promotion} operator $blank^\dag$ from strategies $\sigma\from \oc A \to B$ to strategies $\sigma^\dag\from \oc A \to \oc B$ is the right half of the adjunction between $\G$ and $\CCom(\G)$.
+where the \emph{promotion} operator $\blank^\dag$ from strategies $\sigma\from \oc A \to B$ to strategies $\sigma^\dag\from \oc A \to \oc B$ is the right half of the adjunction between $\G_{wo}$ and $\G_{wo}^{\oc}$.
 
@@
 \begin{proof}
-  We may write this composite as
-  \[
-    \oc A \xrightarrow{m}
-    \oc \oc A \xrightarrow{\oc\sigma}
-    \oc B \xrightarrow{\tau}\,,
-    \]
-  where $\oc\sigma$ is the strategy formed by playing $\sigma$ in parallel with itself, whereas $m\from \oc A \to \oc \oc A$ comes from the fact that $\oc A$ is the cofree commutative comonoid on $A$.
-  $\oc \sigma$ is innocent for the same reasons as in Proposition \ref{PropTensorInnocent}, so it suffices to show that $m$ is innocent.
-
-  Indeed, it is clear from our definitions that $\oc\oc A = \oc A$ as games.  
-  Then, $m$ is in fact the identity strategy between these two games.
+  It suffices to show that $\sigma^\dag$ is innocent, which follows by an argument similar to that in Proposition \ref{PropTensorInnocent}.
 \end{proof}
@@
 \section{The Exponential as a Final Coalgebra}
+
+Our proof in the previous section that $\oc A$ is the cofree commutative comonoid over $A$ (if $A$ is well-opened) leads us towards another category-theoretic property enjoyed by $\oc A$, one that is more closely tied to the sequoid operator.
+This property will be key to our treatment of the semantics of state.
 
@@
 \begin{corollary}
-  If $A$ is a well-opened game, then $\oc A$ is a final coalgebra for the functor $A \sequoid \blank$.
+  If $A$ is a well-opened game, then $\oc A$ is a final coalgebra for the functor $J(A \sequoid \blank) \from \G \to \G$.
 \end{corollary}
@@
 \section{Denotational Semantics of Idealized Algol}
+\label{DenotationalSemanticsOfIdealizedAlgol}
 
@@
   In other words, after the initial move in $A$, $(\sigma_x)$ requests some element $y\in X$, and thereafter plays according to $\sigma_y$ in $A$.
+  \label{DefBrackets}
 \end{definition}
@@
 \begin{itemize}
-  \item $\seq_X = (\id_X) \from \bC \to (X \to X)$;
-  \item $\If_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y) \from \bB \to (X \to X \to X)$;
-  \item $\suc = (1, 2, 3, 4,\cdots) \from \bN \to \bN$;
-  \item $\pred = (0,0,1,2,\cdots)\from \bN \to \bN$;
-  \item $\IfO_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y,\lambda x.\lambda y.y,\cdots)\from \bN \to (X \to X \to X)$;
-  \item $\assign = (\pr_0,\pr_1,\cdots) \from \bN \to (\Varr \to \bC)$; and
-  \item $\dereff = \pr_\bN \from \Varr \to \bN$;
-  \item $\mkvar = \lambda w.\lambda r.\langle (w\,n)_{n\in\bN},r\rangle \from (\bN \to \bC) \to \bN \to \Varr$.
+  \item $\seq_X = (\id_X) \from \bC \implies (X \to X)$;
+  \item $\If_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y) \from \bB \implies (X \to X \to X)$;
+  \item $\suc = (1, 2, 3, 4,\cdots) \from \bN \implies \bN$;
+  \item $\pred = (0,0,1,2,\cdots)\from \bN \implies \bN$;
+  \item $\IfO_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y,\lambda x.\lambda y.y,\cdots)\from \bN \implies (X \to X \to X)$;
+  \item $\assign = (\pr_0,\pr_1,\cdots) \from \bN \implies (\Varr \to \bC)$;
+  \item $\dereff = \pr_\bN \from \Varr \implies \bN$;
+  \item $\lett_{\bB,X} = (\lambda f. f\true,\lambda f.f\false) \from \bB \implies (\bB \to X) \to X$;
+  \item $\lett_{\bN,X} = (\lambda f.f0,\lambda f.f1,\cdots) \from \bN \implies (\bN \to X) \to X$; and
+  \item $\mkvar = \lambda w.\lambda r.\langle (w\,n)_{n\in\bN},r\rangle \from (\bN \to \bC) \to \bN \implies \Varr$.
 \end{itemize}
@@
 
-We use $\seq_X$ for the denotation of $M;N$ and $\deref$ for the denotation of $\oc V$.  
+We use $\seq_X$ for the denotation of $M;N$ and $\dereff$ for the denotation of $\oc V$.  
 The role played by the remaining morphisms can easily be deduced from their names.
@@
 \[
-  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
+  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\oc n} \oc\bN \xrightarrow{\lunit_{\oc\bN}} I \tensor \oc \bN \xrightarrow{\skipp \tensor \oc\bN} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
   \]
@@
 
-This strategy $\cell$ now gives us a morphism $\neww_A \from \oc(\oc\Varr \implies A) \implies A$ given by
+This strategy $\cell$ now gives us a morphism $\neww_A \from \oc(\oc\Varr \implies A) \implies A$ (for $A$ well-opened), given by
 \begin{IEEEeqnarray*}{rCl}
@@
 We define a \emph{$\Var$-context} to be a context $\Gamma$ of the form $x_1\from \Var,\cdots,x_n\from \Var$.
-Given a $\Var$-context $\Gamma$, we define a \emph{$\Gamma$-store} to be a function $s$ from the set of variable names occurring in $\Gamma$ to the set of natural numbers.  
+Given a $\Var$-context $\Gamma$, we define a \emph{$\Gamma$-store} to be a function $s$ from the set of variable names occurring in $\Gamma$ (i.e., the $x_i$) to the set of natural numbers.  
 Given such a store $s$, we write $(s\vert x \mapsto n)$ for the store given by
@@
     \and
+    \inferrule*{\Gamma,s \ts M \converges c,s' \\ \Gamma,s' \ts N[c/x] \converges c',s''}{\Gamma,s\ts \lett x = M \inn N \converges c',s''}
+    \and
     \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges n,s' \\ \Gamma,s' \ts V \converges x,s''}{\Gamma,s\ts V \gets E \converges \skipp,(s''\vert x \mapsto n)}
@@
 \begin{mathpar}
-  \EE \Coloneqq - \mid \EE\,M \mid \suc \EE \mid \pred \EE \mid \EE;M \mid \If \EE\Then M \Else M \mid \IfO \EE \Then M \Else M \mid !\EE \mid M \gets \EE \mid \EE \gets n
+  \EE \Coloneqq - \mid \EE\,M \mid \suc \EE \mid \pred \EE \mid \EE;M \mid \If \EE\Then M \Else M \mid \IfO \EE \Then M \Else M \mid !\EE \mid M \gets \EE \mid \EE \gets n \mid \lett x = \EE \inn M
 \end{mathpar}}
@@
   \]
-for each evaluation context $\EE$.
-Note that $\EE$ may itself contain free variables of type $\Var$: we assume that these are all contained in the $\Var$-context $\Gamma$.
+for each evaluation context $\EE$ whose free variables lie in $\Gamma$.
 
@@
     \Gamma,s \ts \oc(\mkvar W\,R) \oopto \Gamma,s\ts R
+    \\
+    \Gamma,s \ts \lett x = \true \inn M \oopto \Gamma,s\ts M[\true/x]
+    \and
+    \Gamma,s\ts \lett x = \false \inn M \oopto \Gamma,s\ts M[\false/x]
+    \and
+    \Gamma,s\ts \lett x = n \inn M \oopto \Gamma,s\ts M[n/x]
   \end{mathpar}
@@
   Structural induction on $\EE$.
-  The base case, when $\EE=-$e, covers the interesting cases, so we shall leave it to last.
+  The base case, when $\EE=-$, covers the interesting cases, so we shall leave it to last.
   The remaining cases are quite similar, so we will show the proof for the case where $\EE = \EE'\,N$ for illustration.
@@
         \]
-      By the inductive hypothesis, $\deno{\Gamma\ts\EE' M}$ factors as
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE' [M]}$ factors as
       \small
@@
               & \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N}^\dag)"] \\
-            (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc {\deno{\Gamma}} \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}^\dag"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{{\deno{\Gamma}},{\deno{\Gamma}},{\deno{\Gamma}}}" description, dotted]
+            (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc {\deno{\Gamma}} \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}^\dag"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}" description, dotted]
               & \deno{S'} \tensor (A' \tensor \oc\deno{S}) \arrow[d, "{\wk_{\deno{S'},A' \tensor \oc \deno{S}}}"] \\
@@
       \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bC \times X \xrightarrow{\Lambda\inv(\seq_X)} X\,.
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bC \tensor X \xrightarrow{\Lambda\inv(\seq_X)} X\,.
         \]
@@
       \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bN \times \Var \xrightarrow{\Lambda\inv(\assign)} \bC\,.
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bN \tensor \Var \xrightarrow{\Lambda\inv(\assign)} \bC\,.
         \]
@@
         \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.
-        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\Lambda_s\inv(\eta))$ is well-defined.}
+        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\Lambda_s\inv(\eta))$ is well-defined and strict.}
         \label{FigEvContextCond}
       \end{SidewaysFigure}
+    \item If $\EE = \lett_{Y,X} x = \EE' \inn N$, for $X\in\{\bC,\bB,\bN\}$ and $Y\in\{\bB,\bN\}$, then the denotation $\deno{\Gamma\ts \EE[M]}$ is given by
+      \[
+        \oc {\deno{\Gamma}} \xrightarrow{\mu_{V_\Gamma}} \oc \deno \Gamma \tensor \oc \deno \Gamma \xrightarrow{\deno{\Gamma\ts \EE'[M]}\tensor \deno{\Gamma\ts \lambda x.N}} Y \tensor (\oc Y \implies X) \xrightarrow{\Lambda\inv(\lett)} X\,.
+        \]
+      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ can be written as
+      \[
+        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}}
+        \oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'}
+        \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}}
+        \deno T\sequoid A' \xrightarrow{\tau'}
+        Y\,,
+        \]
+      for suitable $A,\sigma,\tau$.
+      This means that $\deno{\Gamma\ts \EE[M]}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextLet}.  
+      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form with
+      \begin{mathpar}
+        A = A' \tensor (\oc Y \implies X)
+        \and
+        \sigma = \mu_{\deno{\Gamma}};(\sigma'\tensor\deno{\Gamma\ts \lambda x.N})
+        \and
+        \tau = \passoc_{\deno{T},A',(\oc Y\implies X)}\inv;(\tau'\sequoid(\oc Y\implies \deno{T}));\Lambda_s\inv(\lett)\,.
+      \end{mathpar}
+      \begin{figure}
+        \[
+          \begin{tikzcd}[column sep=49pt, row sep=30pt]
+            \oc\deno{\Gamma} \arrow[d, "\mu_{\deno \Gamma}"', thick, dashed] \arrow[r, "\mu_{\deno\Gamma}"]
+              & \oc \deno \Gamma \tensor \oc \deno \Gamma \arrow[d, "\oc \deno \Gamma \tensor \mu_{\deno \Gamma}"] \\
+            \oc \deno \Gamma \tensor \oc \deno \Gamma \arrow[d, "{\mu_{\deno \Gamma} \tensor \oc \deno \Gamma}"', thick, dashed]
+              & \oc \deno \Gamma \tensor ( \oc \deno \Gamma \tensor \oc \deno \Gamma ) \arrow[d, "\deno{\Gamma \ts M} \tensor (\sigma' \tensor \deno{\Gamma\ts \lambda x.N})"] \\
+            ( \oc \deno \Gamma \tensor \oc \deno \Gamma ) \tensor \oc \deno \Gamma \arrow[ur, "{\assoc_{\oc\deno\Gamma,\oc\deno\Gamma,\oc\deno\Gamma}}" description, dotted] \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma) \tensor \deno{\Gamma \ts \lambda x.N}"', thick, dashed]
+              & \deno T \tensor ( A' \tensor ( \oc Y \implies X ) ) \arrow[d, "{\wk_{\deno T,A' \tensor (\oc Y \implies X)}}"] \\
+            (\deno T \tensor A') \tensor (\oc Y \implies X) \arrow[ur, "{\assoc_{\deno T,A',\oc Y \implies X}}" description, dotted] \arrow[d, "{\wk_{\deno T\tensor A',\oc Y\implies X}}"', thick, dashed]
+              & \deno T \sequoid (A' \tensor (\oc Y \implies X) \arrow[d, "{\passoc_{\deno T,A,\oc Y \implies X}\inv}"] \\
+            (\deno T \sequoid A') \tensor (\oc Y \implies X) \arrow[r, "{\wk_{\deno T \sequoid A',\oc Y \implies X}}", dotted] \arrow[d, "\tau' \tensor (\oc Y \implies X)"', thick, dashed]
+              & (\deno T \sequoid A) \sequoid (\oc Y \implies X) \arrow[d, "\tau' \sequoid (\oc Y \implies X)"] \\
+            Y \tensor (\oc Y \implies X) \arrow[r, "{\wk_{Y, \oc Y \implies X}}" description, dotted] \arrow[d, "{\Lambda\inv(\lett)}"', thick, dashed]
+              & Y \sequoid (\oc Y \implies X) \arrow[dl, "\Lambda_s\inv(\lett)"] \\
+            X
+          \end{tikzcd}
+          \]
+        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by the $\lett$ keyword.]{The property in Lemma \ref{LemEvContexLemma} is preserved by the $\lett$ keyword.
+        We use the fact that $\lett_{Y,X}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies.}
+        \label{FigEvContextLet}
+      \end{figure}
     \item Lastly, suppose that $\EE = \EE' \gets n$ for some numeral $n$, where $\EE'$ is a context of type $\Var$, and suppose that $M\from T$ fits into the hole.  
@@
 
-Our next lemma will help us deal with the base $\oopto$ rules.  
-We will then use Lemma \ref{LemEvContexLemma} to extend this to the $\opto$ relation.
-
-First, note that the denotation $\deno{\Gamma\ts M}\from \oc\deno{\Gamma} \implies \deno{M}$ tells us what result we get out if we substitute in some initial $\Gamma$-store $s$ to $M$, but it does not tell us what state we are left in at the end.
-The next definition will give us an alternative version of the denotation that will convey this information.
+Having proved this result about evaluation contexts, we now give an outline of the general soundness proof.
+We would like to represent a term-with-store $\Gamma,s\ts M\from T$ by its denotation
+\[
+  I \xrightarrow{\oc\deno{s}} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc \deno{\Gamma} \xrightarrow{\deno{\Gamma \ts M}} \deno{T} \,.
+  \]
+This composite tells us what the behaviour of $M$ is when we evaluate it with state $s$.  
+However, it tells us nothing about the state that $M$ leaves after it has evaluated, and is therefore inadequate for inductive proofs along a derivation.
+
+Instead, we want to capture information about the state that $M$ leaves, which we do using the following derivation.  
+\begin{itemize}
+  \item We use the comonoid structure of $\oc\deno{\Gamma}$ to create two separate references to the storage cells -- one for the use of $M$ and one for the use of any code that will run after $M$ has finished.
+  \item We then use the sequoid operator to indicate the temporal relationship -- namely, that $M$ runs first and all other accesses to the storage cells will receive the state that $M$ left behind.
+\end{itemize}
 
@@
 \end{definition}
+
+Our next lemma will help us deal with the base $\oopto$ rules.  
+We will then use Lemma \ref{LemEvContexLemma} to extend this to the $\opto$ relation.
 
@@
         \item $\deno{\Gamma\ts\IfO (n+1) \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
+        \item $\deno{\Gamma\ts\lett x = \true \inn M} = \deno{(\lambda x.M) \true} = \deno{M[\true/x]}$;
+        \item $\deno{\Gamma\ts\lett x = \false \inn M} = \deno{(\lambda x.M) \false} = \deno{M[\false/x]}$;
+        \item $\deno{\Gamma\ts\lett x = n \inn M} = \deno{(\lambda x.M) n} = \deno{M[n/x]}$;
         \item \parbox[t][][t]{0.8\textwidth}{$\deno{\Gamma\ts(\mkvar W\,R)\gets n} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_n = \deno{\Gamma\ts Wn}$; and}
@@
       Let $s$ be a $\Gamma$-store.  
-      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\oc\deno{\Gamma}\ts \bN}$, then
-      \[
-        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{\oc\deno{\Gamma} \ts X}\,.
+      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\bN\sequoid\oc\deno{\Gamma}}$, then
+      \[
+        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{X\sequoid\oc\deno{\Gamma}}\,.
         \]
@@
   \end{itemize}
+  The argument for $\lett$ is similar.
+  \begin{itemize}
+    \item Suppose that $\Gamma,\Delta\ts M \from Y$ and $\Gamma,\Delta,x\from Y \ts N\from X$, where $Y$ is either $\bool$ or $\nat$ and $X$ is either $\bool$, $\nat$ or $\com$.  
+      Let $s$ be a $\Gamma$-store.  
+      Since $\lett\from Y \implies ((Y \to X) \to X)$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \bot_{Y\sequoid\oc\deno\Gamma}$, then
+      \[
+        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts \lett x=M \inn N}} = \bot_{X\sequoid \oc\deno\Gamma}\,.
+        \]
+      Otherwise, by induction we must have $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}} = \seqdeno{\Gamma,s'\ts y}$ for some $y\in Y$ such that $\Gamma,s\ts M[N_i/x_i]\ts y,s'$.  
+      Then we have
+      \begin{IEEEeqnarray*}{Cl}
+        & \seqdeno{s,((\sigma_i)\semicom \deno{\Gamma,\Delta\ts \lett x=M \inn N})} \\
+        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \lett x=y \inn N}} \\
+        = & \seqdeno{s',((\sigma_i)\semicom \deno{\Gamma,\Delta\ts (\lambda x.N)y}}\,, \\
+        = & \seqdeno{s',((\sigma_i)\semicom \deno{\Gamma,\Delta\ts N[y/x]}}\,, \\
+      \end{IEEEeqnarray*}
+      where the first inequality holds because $\lett x=- \inn N$ is an evaluation context, and the second holds by the definition of $\lett$.  
+      Then, by induction, this last term is either equal to $\bot_{X\sequoid\oc\deno\Gamma}$ or it is equal to $\seqdeno{\Gamma,s''\ts u}$ for some $u\in X$ such that 
+      \[
+        \Gamma,s'\ts N[y/x,N_i/x_i]\ts u,s''\,.
+        \]
+      In this second case, we have
+      \[
+        \Gamma,s\ts \lett x=M[N_i/x_i] \inn N[N_i/x_i] \converges u,s''\,.
+        \]
+  \end{itemize}
   Next, we deal with the rules for variables.
@@
 \begin{proposition}
-  Any compositional semantics satisfying Computational Adequacy satisfies Equational Soundness.
+  Any compositional semantics that satisfies Computational Adequacy satisfies Equational Soundness.
   \label{PropEquationalSoundness}
@@
 
-This Proposition on its own does not seem to be much use, since it relates to the exponential of the denotation of $T$, while all our results have been proved about the denotation $\deno T$ itself.
-But recall that the `co-Kleisli'-style morphisms in our category, which are strategies for $\oc A \implies B$, may alternatively be regarded as comonoid homomorphisms from the comonoid on $\oc A$ to the comonoid on $\oc B$.
+This does not immediately seem very useful: $\oc\deno{T}$ may be full, but $\deno T$ itself is not, and $\deno T$ is the game that we are using to model the type $T$ in our semantics.
+Recall, however, that the `co-Kleisli'-style morphisms in our category, which are strategies for $\oc A \implies B$, may alternatively be regarded as comonoid homomorphisms from the comonoid on $\oc A$ to the comonoid on $\oc B$.
 Thus, if $S,T$ are Idealized Algol types, then the set of morphisms $\oc\deno S \implies \deno T$ in our original category is precisely the same as the set of morphisms $\oc\deno S \implies \oc\deno T$ that are comonoid homomorphisms.
@@
 
+We now make a new definition.
+
+\begin{definition}
+  Given a legal sequence $s\in \L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.
+
+  We write $s\vert_b$ for the subsequence of $s$ given by all moves in $s$ that are hereditarily justified by $b$.
+  Given a set $I$ of initial moves, we write $s\vert_I$ for the subsequence of $s$ given by all moves that are hereditarily justified by some $b\in I$.
+
+  We say that a game $A$ is \emph{thread-closed} if $s\vert_I\in P_A$ whenever $s\in P_A$ and $I$ is some collection of occurrences of initial moves in $s$.
+\end{definition}
+
+If $A$ and $B$ are non-empty games, then the sequoid $A \sequoid B$ is never thread-closed: if we take some play $s$ with moves in both $A$ and $B$, then $s\vert_B$ is not a play of $A \sequoid B$.
+
+However, if $A$ is a well-opened game, then $\oc A$ is always thread-closed.
+
 \begin{lemma}[{\cite[3.5.1]{RusssThesis}}]
-  Let $\sigma \from A$ be a single-threaded strategy.  
+  Let $A$ be a thread-closed game and let $\sigma \from A$ be a single-threaded strategy.  
   Suppose $s\in \sigma$, and let $I$ be a set of occurrences of initial moves in $s$.  
@@
 
-We now link this definition to the idea of a comonoid homomorphism.
+We now link the concept of single-threadedness to the idea of a comonoid homomorphism.
 
@@
 
-Note that it is impossible to define the tensor product of games, let alone the sequoid, in the arena-only semantics, so our Computational Adequacy proof would not have worked had we adopted this approach from the start.
+We might ask why we did not try to work with this arena-only semantics from the start (as has been done in other work -- see \cite{RusssThesis} and \cite{Harmer2006InnocentGS}, for example).  
+The reason is that this semantics is unable to accommodate the tensor and sequoid operators, which -- although not involved in the denotation of any Idealized Algol type -- have been essential to our proof of Computational Adequacy.
 
@@
 
-Here, PCF is the sub-language of PCF generated by the types $\nat$ and $\bool$, together with their structural constants.  
+Here, PCF is the sub-language of Idealized Algol generated by the types $\nat$ and $\bool$, together with their structural constants.  
+Notably, it does not contain $\lett$ or any of the explicit stateful structure of Idealized Algol.
+
 We will take it as read that this result may be extended to the types $\com$ and $\Varr$, so that we can say that if $T$ is an Idealized Algol type, then any compact innocent strategy for $\deno T$ is the denotation of some IA term.
@@
 \end{proof}
-
-The significance of this result is that it gives us an algorithm for deciding whether two IA terms are observationally equivalent, at least if we pass to a finitary version of IA with only finite datatypes and no recursion other than a primitive for divergence).
-Recall from Section \ref{SecCAnFA} that this was impossible for PCF.

### 2020-04-04 Thesis/intro.tex
Corrections.

@@
 Naively relaxing the determinism constraint on the usual definition of an innocent strategy does not give the right notion of a nondeterministic innocent strategy \cite{TsukadaSheaves}.  
-There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, toTsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper that introduced deterministic innocent strategies.
+There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, to Tsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper that introduced deterministic innocent strategies.
 Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we try to mix nondeterminism and innocence.
@@
 
-We can prove continuoity of composition in general for the new language, which allows us to prove computational adequacy in the usual way.
+We can prove continuity of composition in general for the new language, which allows us to prove computational adequacy in the usual way.
 Having done this, we then use operational methods to find a way to identify terms that should be observationally equivalent in the original sense.  

### 2020-04-04 Thesis/pictures.tex
Corrections.

--- 2019-08-04 Thesis/games.tex
@@
-\chapter{A Sequoidal Game Semantics for Idealized Algol}
-\label{ChapGames}
-
-To introduce our material, we will go back over some old ground, namely the fully abstract game semantics for Idealized Algol developed by Abramsky and McCusker in \cite{SamsonGuyIAActive}.  
-In keeping with the spirit of this thesis, we will aim to use category theoretic methods, and so our proofs of soundness and adequacy will depart from those given by Abramsky and McCusker, and will instead involve coalgebraic ideas developed by Laird in \cite{laird02} and \cite{LairdCofCommCom}.
-
-\section{Idealized Algol}
-
-The ground types of Idealized Algol are called $\com$, $\bool$, $\nat$ and $\Var$.  
-The first three are data types corresponding to the sets $\bC = \{a\}$, $\bB = \{\true,\false\}$ and $\bN = \{0,1,2,\cdots\}$.
-$\com$ takes the role of a command or void type; typically, although the return value of a function $T \to \com$ will not convey any information, the function will have side effects that \emph{do} make a difference.
-
-The type $\Var$ is the type of a variable that holds elements of $\bN$.
-It is best understood as corresponding to the following pseudo-Java `interface'.
-
-\begin{minipage}{\linewidth}
-\begin{lstlisting}[language=Java, morekeywords={nat,com}]
-public interface Var
-{
-  nat read();
-  com write(nat value);
-}
-\end{lstlisting}
-\end{minipage}
-
-The types of Idealized Algol are then defined by the following inductive grammar.
-
-\[
-  T \Coloneqq \com \mid \bool \mid \nat \mid \Var \mid T \to T\,.
-  \]
-
-We now present the typing rules for the language.  
-Here, $\Gamma$ will stand for a \emph{context}; i.e., a list $x_1\from T_1,\cdots,x_n\from T_n$ of variable names together with their types.
-
-First, we have the usual rules for the simply typed lambda calculus.
-
-\begin{mathpar}
-  \inferrule*{ }{\Gamma,x\from T \ts x \from T}
-  \and
-  \inferrule*{\Gamma\ts M \from S \to T \\ \Gamma \ts N \from S}{\Gamma\ts MN \from T}
-  \and
-  \inferrule*{\Gamma,x\from S \ts M \from T}{\Gamma \ts \lambda x^S.M \from S \to T}
-\end{mathpar}
-
-We then have rules for each of the base types.  
-At type $\com$ we have:
-\begin{mathpar}
-  \inferrule*{ }{\Gamma\ts\skipp\from\com}
-  \and
-  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma\ts M\from\com \\ \Gamma\ts N \from T}{\Gamma\ts M;N\from T}\,.
-\end{mathpar}
-Here, $\skipp$ is a generic command with no side-effects that returns the unique element of the singleton set $\bC$.  
-$M;N$ represents the sequential composition of $M$ with $N$; i.e., the term that first evaluates $M$, performing any of its side-effects, and then evaluates $N$ and returns the result.
-
-At type $\bool$ we have true/false values and conditionals.
-\begin{mathpar}
-  \inferrule*{ }{\Gamma\ts\true\from\bool}
-  \and
-  \inferrule*{ }{\Gamma\ts\false\from\bool}
-  \\
-  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma\ts M \from \bool \\ \Gamma \ts N \from T \\ \Gamma \ts P \from T}{\Gamma\ts \If M \Then N \Else P \from T}
-\end{mathpar}
-
-At type $\nat$ we have numerals, arithmetic operators and a conditional that tests whether a number is equal to $0$ or not.
-\begin{mathpar}
-  \inferrule*{ }{\Gamma\ts n\from\nat}
-  \and
-  \inferrule*{\Gamma\ts M \from \nat}{\Gamma\ts \suc M \from \nat}
-  \and
-  \inferrule*{\Gamma\ts M \from \nat}{\Gamma\ts \pred M\from \nat}
-  \\
-  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma\ts M \from \nat \\ \Gamma\ts N \from T \\ \Gamma \ts P \from T}{\Gamma \ts \IfO M \Then N \Else P \from T}
-\end{mathpar}
-
-At type $\Var$, we have terms that call the read and write `methods' to dereference the variable or to assign a new value to it.
-\begin{mathpar}
-  \inferrule*{\Gamma\ts V \from \Var \\ \Gamma \ts E \from \nat}{\Gamma \ts V\gets E \from \com}
-  \and
-  \inferrule*{\Gamma\ts V \from \Var}{\Gamma \ts \oc V \from \nat}
-\end{mathpar}
-
-We also have the ability to create a new variable.
-\begin{mathpar}
-  \inferrule*[right={$T\in\{\com,\bool,\nat\}$}]{\Gamma,x\from \Var \ts M \from T}{\Gamma\ts \neww_T \lambda x.M\from T}
-\end{mathpar}
-The idea here is that if $M$ is a term that refers to some free variable $x$ of type $\Var$; then $\neww \lambda x.M$ makes $x$ behave like an actual storage cell (so, for instance, the result of the computation $\neww_\nat \lambda x.(x\gets 5);!x$ will be $5$).
-
-We have another way of creating variables, using the $\mkvar$ keyword.  
-If we think back to our illustration of the $\Var$ type as an interface, this becomes clearer.  
-$\mkvar$ creates a new anonymous instance of the $\Var$ interface, using the `methods' supplied through its arguments.
-\begin{mathpar}
-  \inferrule*{\Gamma \ts M \from \nat \\ \Gamma \ts N \from \nat \to \com}{\Gamma\ts \mkvar M N \from \Var}
-\end{mathpar}
-
-Lastly, we have fixpoint combinators at all types that we use to implement recursion.
-\begin{mathpar}
-  \inferrule*{\Gamma \ts M \from T \to T}{\Gamma \ts \Y_T M \from T}
-\end{mathpar}
-
-\section{Games and Strategies}
-
-We adopt the game semantics from \cite{SamsonGuyIAActive}; these are based on the game semantics developed in \cite{hoPcf}, with a modification to make them into a linear category.
-
-\begin{definition}
-  An \emph{arena} is a tuple $A=(M_A,\lambda_A,\ts_A)$, where
-  \begin{itemize}
-    \item $M_A$ is a set of \emph{moves},
-    \item $\lambda_A \from M_A \to \OP \times \QA$ is a function that identifies each move as either an \emph{$O$-move} or a \emph{$P$-move}, and as either a \emph{question} or an \emph{answer}, and
-    \item $\ts_A$ is a relation between $M_A+\{*\}$ and $M_A$ such that
-      \begin{itemize}
-        \item if $*\ts_A a$, then $\lambda_A(a)=(O,Q)$, and if $b\ts_A a$ then $b=*$,
-        \item if $a\ts_A b$ and $a$ is an answer, then $b$ is a question, and
-        \item if $a \ts_A b$ and $a\ne *$, then either $a$ is an $O$-move and $b$ a $P$-move, or the other way round.
-      \end{itemize}
-  \end{itemize}
-  If $*\ts_A a$, then we say that $a$ is an \emph{initial move} in $A$.  
-  If $a \ts_A b$, the we say that $a$ \emph{enables} $b$.
-\end{definition}
-
-As a shorthand, we write $\lambda_A^{OP}\from M_A \to \OP$ for $\pr_1\circ\lambda_A$ and $\lambda_A^{QA}\from M_A \to \QA$ for $\pr_2\circ\lambda_A$.
-
-\begin{definition}
-  A \emph{justified sequence} in an arena $A$ is a finite sequence $s$ of moves together with, for each non-initial move $a$ occurring in $s$, a pointer back to some move $b$ occurring earlier in $s$ such that $b\ts_A a$.
-  We say that \emph{$b$ justifies $a$} or that $b$ is the \emph{justifier} of $a$.
-
-  Given such a justified sequence, we define the \emph{$P$-view} $\pv s$ and \emph{$O$-view} $\ov s$ of $s$ inductively as follows.
-  \begin{IEEEeqnarray*}{RCL"s}
-    \pv{\epsilon} & = & \epsilon & \\
-    \pv{sa} & = & \pv{s}a & if $a$ is a $P$-move \\
-    \pv{sa} & = & a & if $a$ is initial \\
-    \pv{sbta} & = & \pv{s}ba & if $a$ is an $O$-move justified by $b$ \\
-    & & & \\
-    \ov{\epsilon} & = & \epsilon & \\
-    \ov{sa} & = & \ov{s}a & if $a$ is an $O$-move \\
-    \ov{sbta} & = & \ov{s}ba & if $a$ is a $P$-move justified by $b$
-  \end{IEEEeqnarray*}
-
-  A justified sequence $s$ is \emph{well-bracketed} if whenever a question $q$ justifies some answer $a$, then any question $q'$ occurring after $q$ and before $a$ must justify some answer $a'$ occurring between $q'$ and $a$, and moreover $a$ is the only answer justified by $q$.
-  We say that a justified sequence $s$ is \emph{alternating} if it alternates between $O$-moves and $P$-moves, and that it is \emph{well-formed} if it is both well-bracketed and alternating.
-
-  We say that a well-formed justified sequence is \emph{visible} if whenever $ta\prefix s$, and $a$ is a $P$-move, then the justifier of $a$ occurs in the $P$-view of $t$, and if whenever $tb\prefix s$, and $b$ is a non-initial $O$-move, then the justifier of $b$ occurs in the $O$-view of $t$.
-
-  We say that a justified sequence $s$ is \emph{legal} if it is well-formed and visible, and write $\L_A$ for the set of legal sequences occurring in $A$.
-\end{definition}
-
-Note that since every non-initial move in a justified sequence $s$ must be justified by some previous move, then the first move in the sequence must be initial and therefore an $O$-question.  
-If $s$ is alternating, this means that $s$ ends with an $O$-move if it has odd length and with a $P$-move if it has even length.
-
-\begin{definition}
-  Given a legal sequence $s\in \L_A$, and a move $b$ in $s$, we say that a move $a$ in $s$ is \emph{hereditarily justified by $b$} if there is a chain of justification pointers going back from $a$ to $b$.
-
-  We write $s\vert_b$ for the subsequence of $s$ given by all moves in $s$ that are hereditarily justified by $b$.
-  Given a set $I$ of initial moves, we write $s\vert_I$ for the subsequence of $s$ given by all moves that are hereditarily justified by some $b\in I$.
-
-  A \emph{game} is given by a tuple $A=(M_A,\lambda_A,\ts_A,P_A)$ where $(M_A,\lambda_A,\ts_A)$ is an arena and $P_A$ is a non-empty prefix-closed subset of $\L_A$ such that if $s\in P_A$ and $I$ is a set of initial moves, then $s\vert_I\in P_A$.
-\end{definition}
-
-We shall call an odd-length sequence $s\in P_A$ an \emph{$O$-position} and an even-length sequence a \emph{$P$-position}
-
-\begin{example}[Empty game]
-  The \emph{empty game} $I$ is given by the tuple
-  \[
-    (\emptyset,\emptyset,\emptyset,\{\epsilon\})\,,
-    \]
-  where $\epsilon$ is the empty sequence.
-  \label{ExEmptyGame}
-\end{example}
-
-\begin{example}[Data-type games]
-  Let $X$ be some set.  
-  Then we have a game, which we shall also call $X$, given by:
-  \begin{itemize}
-    \item $M_X = \{q\} + X$, 
-    \item $\lambda_X(q)=(O,Q)$ and $\lambda_X(x)=(P,A)$ for all $x\in X$, 
-    \item $q\ts_X x$ for each $x\in X$, and
-    \item $P_X = \{\epsilon,q\}\cup\{qx\suchthat x\in X\}$, where the $x$ in $qx$ is justified by $q$.
-  \end{itemize}
-
-  In particular, we have games $\bC$, $\bB$ and $\bN$, which we shall use to model the datatypes $\com$, $\bool$ and $\nat$ of Idealized Algol.
-\end{example}
-
-\begin{definition}
-  Let $A$ be a game.  
-  Then a \emph{strategy} for $A$ is a non-empty even-prefix-closed set $\sigma\subset P_A$ of $P$-positions in $A$ such that if $sab,sac\in \sigma$ then $b=c$ and the justifier of $b$ is the justifier of $c$.
-\end{definition}
-Here, we have identified a strategy for a game with the set of $P$-positions that can occur when player $P$ plays according to that strategy.  
-So the condition we have given is one of \emph{determinism}: in any $O$-position $sa$ that can occur in the strategy, player $P$ must have at most one reply.
-
-Note that there may be $O$-positions for which player $P$ has no reply at all; we use these to model non-terminating computations.
-
-We write $\sigma\from A$ to denote that $\sigma$ is a strategy for the game $A$.
-
-\begin{definition}
-  A strategy $\sigma$ for a game $A$ is called \emph{innocent} if player $P$'s moves only depend on the current $P$-view; i.e., if whenever $sab\in\sigma$, $t\in\sigma$ and $ta\in P_A$ such that $\pv{sa}=\pv{ta}$, then we have $tab\in\sigma$.
-\end{definition}
-
-\section{Connectives on Games}
-\label{SecConnectives}
-
-In the \emph{product} $A\times B$ of games $A$ and $B$, player $O$ chooses either $A$ or $B$ on the first move and subsequent play is that game.
-
-\begin{definition}
-  Given games $A$,$B$, define a game $A\times B$ by
-  \begin{itemize}
-    \item $M_{A\times B} = M_A + M_B$,
-    \item $\lambda_{A\times B} = [\lambda_A,\lambda_B]$,
-    \item $* \ts_{A\times B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\times B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
-    \item $P_{A\times B} = \{s\in \L_{A\times B} \suchthat \text{$s\vert_A\in P_A$ \& $s\vert_B=\epsilon$ or $s\vert_A=\epsilon$ \& $s\vert_B\in P_B$}\}$.
-  \end{itemize}
-  We extend this to arbitrary products $\prod_i A_i$ in the obvious way.
-  In particular, the product $1$ of the empty collection is the same as the empty game $I$ defined in Example \ref{ExEmptyGame}.
-  \label{DefProduct}
-\end{definition}
-
-Here, we have written $s\vert_A$ for the subsequence of $s$ consisting of all moves from $M_A$ and $s\vert_B$ for the subsequence consisting of all moves from $M_B$.
-
-In the \emph{tensor product} $A\tensor B$ of games $A$ and $B$, the games $A$ and $B$ are played in parallel, and player $O$ may switch between games when it is his turn.
-
-\begin{definition}
-  Given games $A$,$B$, define a game $A\tensor B$ by
-  \begin{itemize}
-    \item $M_{A\tensor B} = M_A + M_B$,
-    \item $\lambda_{A\tensor B} = [\lambda_A,\lambda_B]$,
-    \item $* \ts_{A\tensor B} a$ if and only if $*\ts_A a$ or $*\ts_B a$ and $a \ts_{A\tensor B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, and
-    \item $P_{A\tensor B} = \{s\in \L_{A\tensor B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
-  \end{itemize}
-\end{definition}
-
-In the \emph{linear implication} $A\implies B$, the game $B$ is played in parallel with a version of $A$ in which the two players' roles have been switched around, and player $P$ may switch between the two games when it is her turn.
-
-\begin{definition}
-  Given games $A$,$B$, define a game $A\implies B$ by
-  \begin{itemize}
-    \item $M_{A\implies B} = M_A + M_B$,
-    \item $\lambda_{A\implies B} = [\neg\circ\lambda_A,\lambda_B]$,
-    \item $* \ts_{A\implies B} a$ if and only if $*\ts_B a$, and $a \ts_{A\implies B} b$ if and only if $a \ts_A b$ or $a\ts_B b$, or if $a$ is initial in $B$ and $b$ is initial in $a$, and
-    \item $P_{A\implies B} = \{s\in \L_{A\implies B} \suchthat \text{$s\vert_A\in P_A$ and $s\vert_B\in P_B$}\}$.
-  \end{itemize}
-\end{definition}
-
-Here, $\neg\from \OP\times\QA \to \OP\times \QA$ is the function that reverses $O$ and $P$, while leaving $\QA$ unchanged.
-
-In the \emph{exponential} of a game $A$, infinitely many copies of $A$ are played in parallel, and player $O$ may switch between copies whenever it is his move.
-
-\begin{definition}
-  Given a game $A$, define a game $\oc A$ by
-  \begin{itemize}
-    \item $M_{\oc A}=M_A$,
-    \item $\lambda_{\oc A} = \lambda_A$,
-    \item $\ts_{\oc A} = \ts_A$ and
-    \item $P_{\oc A} = \{s\in \L_{\oc A} \suchthat \text{$s\vert_b\in P_A$ for each initial move $b$ occurring in $s$}\}$.
-  \end{itemize}
-\end{definition}
-
-Lastly, the \emph{sequoid} $A\sequoid B$ of two games $A$ and $B$ behaves like the tensor product $A\tensor B$, except that the opening move must take place in $A$.
-
-\begin{definition}
-  Given games $A,B$, define a game $A\sequoid B$ by
-  \begin{itemize}
-    \item $M_{A\sequoid B} = M_{A\tensor B}$, 
-    \item $\lambda_{A\sequoid B} = \lambda_{A\tensor B}$, 
-    \item $\ts_{A\sequoid B} = \ts_{A \tensor B}$ and
-    \item $P_{A\sequoid B} = \{s\in P_{A\tensor B}\suchthat\text{$s=\epsilon$ or $s$ begins with a move from $A$}\}$.
-  \end{itemize}
-\end{definition}
-
-\section{Composition of strategies}
-
-\begin{definition}
-  Let $A,B,C$ be arenas.  
-  An \emph{interaction sequence} between $A,B,C$ is a justified sequence $\s$ of moves drawn from $M_A$, $M_B$ and $M_C$ such that $\s\vert_{A,B}\in \L_{A\implies B}$ and $\s\vert_{B,C}\in \L_{B\implies C}$.
-  Here, $\s\vert_{A,B}$ is the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$, together with all justification pointers between moves in $A$ and $B$, and $\s\vert_{B,C}$ is defined similarly.
-
-  We write $\Int(A,B,C)$ for the set of all interaction sequences between $A,B,C$.
-
-  Given $\s\in\Int(A,B,C)$, we write $\s\vert_{A,C}$ for the subsequence of $\s$ consisting of those moves from $\s$ that occur in $A$ or $B$.  
-  A move $b$ in $\s\vert_{A,C}$ justifies a move $a$ either if $b$ justifies $a$ in either the $A$ or the $C$ components, or if $b$ justifies in $\s$ some initial move $c$ in $B$, which itself justifies $a$.
-\end{definition}
-
-\begin{definition}
-  Let $A,B,C$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $B\implies C$.  
-  We define $\sigma\|\tau$ to be given by the set
-  \[
-    \{\s\in\Int(A,B,C)\suchthat \text{$\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$}\}\,.
-    \]
-  Then we define the \emph{composition} $\sigma;\tau$ of $\sigma$ and $\tau$ to be given by the set
-  \[
-    \{\s\vert_{A,C}\suchthat \s\in\sigma\|\tau\}\,.
-    \]
-\end{definition}
-
-We need some small lemmata and definitions to help us show that this is a strategy.
-
-\begin{lemma}
-  We extend the function $\lambda_A^{OP}$ to sequences of moves by
-  \begin{itemize}
-    \item $\lambda_A^{OP}(\epsilon)=P$ and
-    \item $\lambda_A^{OP}(sa)=\lambda_A(a)$.
-  \end{itemize}
-
-  If $s\in P_{A\implies B}$, then $\lambda_{A\implies B}^{OP}(s)=(\lambda_A^{OP}(s\vert_A)\Rightarrow \lambda_B^{OP}(s\vert_B))$, where $\Rightarrow$ is the binary operation on $\OP$ defined by
-  \[
-    \begin{array}{cc|c}
-      P & Q & P\Rightarrow Q \\
-      \hline
-      P & P & P \\
-      O & P & P \\
-      P & O & O \\
-      O & O & P
-    \end{array}\,.
-    \]
-  Moreover, if $\lambda_A^{OP}(s\vert_A)=O$ then $\lambda_A^{OP}(s\vert_B)=O$.
-  \label{LemCompositionLemma}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $s$.
-  If $s=\epsilon$, then $s\vert_A=s\vert_B=\epsilon$, and so $(\lambda_A^{OP}(s\vert_A)\Rightarrow \lambda_B^{OP}(s\vert_B)) = (P\Rightarrow P) = P = \lambda_{A\implies B}^{OP}(s)$.
-
-  Suppose then that $s=ta$, and that $\lambda_{A\implies B}^{OP}(t)=O$.  
-  This means that $\lambda_A^{OP}(t\vert_A)=P$ and $\lambda_B^{OP}(t\vert_B)=O$.
-  Then, whether $a$ is a move in $A$ or a move in $B$, adding it will flip exactly one of these components -- so $\lambda_{A\implies B}(s\vert_A)=O$ and $\lambda_{A\implies B}^{OP}(s\vert_B)=O$ if $a$ is a move in $A$ and $\lambda_{A\implies B}(s\vert_A)=P$ and $\lambda_{A\implies B}^{OP}(s\vert_B)=P$ if $a$ is a move in $C$.
-
-  Suppose instead that $\lambda_{A\implies B}^{OP}(t)=P$.  
-  By induction, this means that either $\lambda_A^{OP}(t\vert_A)=P$ and $\lambda_B^{OP}(t\vert_B)=P$ or that $\lambda_A^{OP}(t\vert_A)=O$ and $\lambda_B^{OP}(t\vert_B)=O$.
-  In the first case, this means that either $t\vert_A$ is empty or its last move is a $P$-move in $A$ (and therefore an $O$-move in $A\implies B$), and so the move $a$ must take place in $C$, meaning that $\lambda_A^{OP}(s\vert_A)=P$ and $\lambda_B^{OP}(s\vert_B)=O$.
-
-  Similarly, in the second case, the last move in $t\vert_C$ must be an $O$-move in $B$ (and therefore an $O$-move in $A\implies B$, and so the move $a$ must take place in $A$, meaning that $\lambda_A^{OP}(s\vert_A)=P$ and $\lambda_B^{OP}(s\vert_B)=O$.
-\end{proof}
-
-It follows that
-
-\begin{corollary}[Switching condition]
-  Only player $P$ may switch between games in $A\implies B$; i.e., if $tab\in P_{A\implies B}$, and $a$ occurs in $A$ and $b$ in $B$, or if $a$ occurs in $B$ and $b$ in $A$, then $b$ is a $P$-move.
-  \label{CorSwitchingCondition}
-\end{corollary}
-\begin{proof}
-  Otherwise, $\lambda_{A\implies B}(t)=O$, so $\lambda_A(t\vert_A)=P$ and $\lambda_B(t\vert_B)=O$.  
-  But we must also have $\lambda_{A\implies B}(tab)=O$, so $\lambda_A(tab\vert_A)=P$ and $\lambda_B(tab\vert_B)=O$.  
-  But this is a contradiction, since $tab\vert_A$ and $tab\vert_B$ are both one move longer than the plays $t\vert_A$ and $t\vert_B$.
-\end{proof}
-
-\begin{definition}[{\cite[\sec 3.1]{Harmer2006InnocentGS}}]
-  Given $\s\in \Int(A,B,C)$, we define the \emph{$P$-view} $\pv{\s}$ of $\s$ inductively as follows.
-  \begin{IEEEeqnarray*}{RCL?s}
-    \pv{\epsilon} & = & \epsilon & \\
-    \pv{\s a} & = & \pv{\s}a & if $a$ is a move in $B$, an $O$-move in $A$ or a $P$-move in $C$ \\
-    \pv{\s c} & = & c & if $c$ is an initial move of $C$ \\
-    \pv{\s b\t a} & = & \pv{\s}ba & \parbox[t][][t]{200pt}{if $a$ is a $P$-move of $A$ or an $O$-move of $C$ and is justified by $b$} \\
-  \end{IEEEeqnarray*}
-\end{definition}
-
-\begin{lemma}
-  If $\s\in \Int(A,B,C)$, then $\pv{\s}\vert_{A,C}=\pv{\s\vert_{A,C}}$.
-  \label{LemHarmerRestriction}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $\s$.  
-  This is clear if $\s=\epsilon$.
-
-  If $a$ is an $O$-move in $A$ or a $P$-move in $C$, then $a$ is a $P$-move in $A\implies C$.  
-  We have $\pv{\s a}\vert_{A,C}=\pv{\s}\vert_{A,C}a$, which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}a$, which is the same as $\pv{\s a\vert_{A,C}}$.
-  If $b$ is a move in $B$, then $\pv{\s b}\vert_{A,C}=\pv{\s}b\vert_{A,C}=\pv{\s}\vert_{A,C}=\pv{\s\vert_{A,C}}=\pv{\s b\vert_{A,C}}$, by the inductive hypothesis.
-
-  If $c$ is initial in $C$, then $\pv{\s c}\vert_{A,C}=c=\pv{\s c\vert_{A,C}}$.
-
-  Suppose $a$ is a $P$-move of $A$ or an $O$-move of $C$ -- so $a$ is an $O$-move in $A\implies C$ -- and suppose that $a$ is justified by $b$ in the sequence $\s b\t a$.  
-  Since $a$ cannot be an initial move in $A$, $b$ must occur in the same game as $a$, and in particular must not occur in $B$.
-  Then we have $\pv{\s b\t a}\vert_{A,C}=\pv{\s} ba\vert_{A,C}=\pv{\s}\vert_{A,C}ba$, which by the inductive hypothesis is equal to $\pv{\s\vert_{A,C}}ba=\pv{\s ba\vert_{A,C}}$.
-\end{proof}
-
-\begin{lemma}[{\cite[\sec 3.1]{Harmer2006InnocentGS}}]
-  Let $\s a\in \Int(A,B,C)$ (so, in particular, $\s\vert_{A,B}$ and $\s\vert_{B,C}$ satisfy the visibility condition).  
-  If $a$ is a move in $B$, an $O$-move in $A$ or a $P$-move in $C$, then $\pv{\s a}\in \Int(A,B,C)$.
-  \label{LemHarmersLemma}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $\s$.  
-  If $\s=\epsilon$, then this is clear.  
-  Otherwise, suppose that $\s$ is non-empty.
-
-  First, we claim that $\pv{\s}\in\Int(A,B,C)$.  
-  If $\s$ ends with a move in $B$, an $O$-move in $A$ or a $P$-move in $C$, then this follows immediately from the inductive hypothesis.  
-  Otherwise, suppose that $\s$ ends with a $P$-move in $A$ or an $O$-move in $C$.  
-  If this last move is initial, then $\pv{\s}$ is a single move, so the claim is trivial.  
-  Otherwise, write $\s=\t p\u r$, where $p$ justifies $r$.  
-  By the inductive hypothesis, we have $\pv{\t p}\in \Int(A,B,C)$, and then $\pv{s}=\pv{\t p\u r}=\pv{\t}pr=\pv{\t p}r\in \Int(A,B,C)$.
-
-  Now, since $a$ is a $P$-move in $A\implies B$ or in $B\implies C$, its predecessor $b$ is an $O$-move and has some justifier $c$ contained in $\pv{\s\vert_X}$, where $X\in\{A\implies B,B\implies C\}$ is that component in which $a$ is a $P$-move.
-  Then this $c$ is preceded by some other $O$-move $b'$, which is necessarily also contained in $\pv{\s}$, and so has some justifier $c'$, contained in $\pv{\s\vert_X}$ by visibility.  
-  Continuing in this way until we reach an initial move, we build up the whole of the sequence $\pv{\s\vert_X}$ as a subsequence of $\pv{\s}$.  
-  Therefore, the justifier of $a$ must be contained in $\pv{\s}$, and so $\pv{\s a}=\pv{\s}a\in\Int(A,B,C)$.
-\end{proof}
-
-\begin{lemma}[$O$-views in the linear implication, {\cite[4.2,4.3]{hoPcf}}]
-  Let $A,B$ be games, and let $bs$ be a non-empty play in $A\implies B$ beginning with an initial move $b$ in $B$.
-
-  i) If $bs$ ends with a $P$-move in $B$, then $\ov{bs}_{A\implies B}=\ov{bs\vert_B}_B$.
-
-  ii) If $bs$ ends with a $P$-move in $A$, then $\ov{bs}_{A\implies B} = b\pv{s\vert_A}^A$.
-  \label{LemProjectionLemma}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $s$.
-  If $s=\epsilon$, then $bs$ ends with an $O$-move in $B$, and we have $\ov{b}^{A\implies B} = b = \ov{b}^{B}$.
-
-  Otherwise, suppose that $bs$ ends with a $P$-move $c$ in $B$.  
-  Let $d$ be the justifier of $c$.  
-  Then $d$ must be an $O$-move in $B$.
-  Write $bs=tduc$, where $t,u$ are sequences.  
-  Then $\ov{tduc}_{A\implies B}=\ov{t}_{A\implies B}dc$ and $\ov{tduc\vert_B}_B=\ov{t\vert_B}_Bdc$.
-  By Corollary \ref{CorSwitchingCondition}, $t$ must end with a $P$-move in $B$, or be empty, so by the inductive hypothesis we have $\ov{t}_{A\implies B}=\ov{t\vert_B}_B$.
-  Therefore, $\ov{bs}_{A\implies B}=\ov{tduc}_{A\implies B}=\ov{t}_Bdc = \ov{tduc\vert_B}_B=\ov{bs\vert_B}_B$.
-
-  Next, suppose that $bs$ ends with a $P$-move $a$ in $A$.
-  Let $c$ be the justifier of $a$.  
-  Then $c$ must be an $O$-move in $A$.  
-  Write $s=tcua$, where $t,u$ are sequences.  
-  Then $\ov{btcua}_{A\implies B}=\ov{bt}_{A\implies B}ca$ and $\pv{tcua\vert_A}^A = \pv{t\vert_A}^Aca$, since the roles are reversed in $A$.
-  By Corollary \ref{CorSwitchingCondition}, $t$ must end in a $P$-move in $A$, or be empty, so by the inductive hypothesis we have $\ov{bt}_{A\implies B} = b\pv{t\vert_A}^A$.  
-  Therefore, $\ov{bs}_{A\implies B}=\ov{btcua}_{A\implies B}=\ov{bt}_{A\implies B}ca=b\pv{t\vert_A}^Aca=b\pv{tcua\vert_A}^A=b\pv{s\vert_A}^A$.  
-\end{proof}
-
-\begin{proposition}
-  $\sigma;\tau$ is a strategy for $A\implies C$.  
-  \label{PropComposition}
-\end{proposition}
-\begin{proof}
-  First, we claim that $\s\vert_{A,C}\in P_{A\implies B}$ for any $\s\in \sigma\|\tau$.
-  Since we certainly have $\s\vert_{A,C}\vert_A = \s\vert_{A,B}\vert_A\in P_A$ and $\s\vert_{A,C}\vert_C = \s\vert_C = \s\vert_{B,C}\vert_C\in P_C$, it suffices to show that $\s\vert_{A,C}\in \L_{A\implies C}$.
-
-  Suppose that $ta\prefix \s\vert_{A,C}$.  We claim that $\lambda_{A\implies C}(t) = \neg\lambda_{A\implies C}(a)$.
-  By Lemma \ref{LemCompositionLemma}, we are in one of the following configurations.
-  \small
-  \[
-    \begin{array}{ccc|ccc}
-      \lambda_A^{OP}(t\vert_A) & \lambda_B^{OP}(t\vert_B) & \lambda_C^{OP}(t\vert_C) & \lambda_{A\implies B}^{OP}(t\vert_{A,B}) & \lambda_{B\implies C}^{OP}(t\vert_{B,C}) & \lambda_{A\implies C}^{OP}(t\vert_{A,C}) \\
-      \hline
-      P & P & P & P & P & P \\
-      P & P & O & P & O & O \\
-      P & O & O & O & P & O \\
-      O & O & O & P & P & P 
-    \end{array}
-    \]
-  \normalsize
-  In the configuration $PPP$, the move $a$ cannot be a move in $A$, since that would leave $ta\vert_{A\implies B}$ in the configuration $OP$, which is impossible by Lemma \ref{LemCompositionLemma}.  
-  Therefore, it must be a move in $C$, and must therefore be an $O$-move in $C$ and hence an $O$-move in $A\implies C$.
-
-  In the configuration $PPO$, once again the move $a$ cannot take place in $A$, since this would leave $ta\vert_{A\implies B}$ in an illegal configuration.  
-  Therefore, it must occur in $C$, and must be a $P$-move in $C$ and hence a $P$-move in $A\implies C$.
-
-  In the configuration $POO$, the move $a$ cannot take place in $C$, or it would leave $ta\vert_{B,C}$ in the illegal configuration $OP$, so the move $a$ takes place in $A$.  
-  Therefore, it must be an $O$-move in $A$ and hence a $P$-move in $A\implies C$.
-
-  Lastly, in the configuration $OOO$, the move $a$ cannot occur in $C$, or it would leave $ta\vert_{B,C}$ in the configuration $OP$, and so it must take place in $A$.  
-  Therefore, it must be a $P$-move in $A$, and hence an $O$-move in $A\implies C$.
-
-  Having established that $\s\vert_{A,C}$ is alternating, we now show that it is well-bracketed.
-  Suppose that a question move $q$ in $\s\vert_{A,C}$ justifies some answer move $a$.
-  $q$ and $a$ must occur in the same component, since the only case in which a move from one of $A$ and $C$ can justify a move in the other is when both moves are initial, and hence questions.
-  Suppose first that $q$ and $a$ both occur in the game $C$.  
-  Suppose that some other question move $q'$ occurs between $q$ and $a$ in $\s\vert_{A,C}$.  
-  If $q'$ occurs in $C$, then it must be answered by some $a'$ occurring between $q'$ and $a$, since $\s\vert_C$ is a well-bracketed sequence.  
-  Otherwise, suppose that $q'$ occurs in $A$.
-
-  By examining the table above, we see that there must be some move in $B$ occurring between $q$ and $q'$ in $\s$, since moves in $A$ move between configurations $OOO$ and $POO$, while moves in $C$ move us between configurations $PPP$ and $PPO$.
-  Let $b$ be the earliest such move.  
-  Then $b$ must be a question; indeed, if it is an answer, then it is non-initial and so can only be justified by questions in $B$.  
-  But such a question must occur earlier in $\s\vert_{B,C}$ than $q$, which would mean that $q$ was an unanswered question when the move $b$ was played, contradicting well-bracketedness of $\s\vert_{B,C}$.
-  Since $b$ is a question, it must be answered by some $a''$ occurring between $b$ and $a$.  
-  Therefore, since $\s\vert_{A,B}$ is well-bracketed, the move $q'$ must be answered by some $a'$ occurring between $a'$ and $a''$ in $\s\vert_{A,B}$, and therefore between $a'$ and $a$ in $\s\vert_{A,C}$.
-
-  The case when $q$ and $a$ both occur in $A$ is similar.
-
-  Lastly, we need to show that $\s\vert_{A,C}$ satisfies the visibility condition.
-  Let $ta\prefix\s\vert_{A,C}$.
-  Choose some $\t a\prefix\s$ such that $\t a\vert_{A,C}=ta$.
-
-  Suppose $a$ is a $P$-move.
-  Then by Lemma \ref{LemHarmersLemma}, $\pv{\t a}\in\Int(A,B,C)$.  
-  By Lemma \ref{LemHarmerRestriction}, we know that $\pv{t}a=\pv{ta}=\pv{\t a}\vert_{A,C}$, and therefore that the justifier of $a$ must be inside $\pv{t}$.
-
-  Secondly, suppose that $a$ is an $O$-move.
-  If $a$ is an $O$-move in $C$, then either it is initial or $\t$ ends with some $P$-move in $C$, and therefore $\ov{t}_{A\implies C} = \ov{t\vert_C}_C = \ov{\t\vert_{B,C}}_C$ by Lemma \ref{LemProjectionLemma}.
-  Therefore, since $\t\vert_{B,C}$ satisfies visibility, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.  
-  If $a$ is an $O$-move in $A$, then write $t=cu$ and $\t=c\u$, where $c$ is the starting move in $C$.
-  We have $\ov{cua}_{A\implies C}=c\pv{u\vert_A a}^A = \ov{c\u\vert_{A,B}}_{A\implies B}$.  
-  Therefore, the justifier of $a$ must lie in $\ov{t}_{A\implies C}$.
-
-  Therefore, $\s\vert_{A,C}\in \L_{A\implies C}$, so $\s\vert_{A,C}\in P_{A\implies C}$.
-
-  It is fairly clear that $\sigma;\tau$ is even-prefix closed, since $\sigma$ and $\tau$ are.  
-  Indeed, if $\s\vert_{A,C}\in\sigma;\tau$ and $t\prefix\s\vert_{A,C}$, then we may choose some prefix $\t$ of $\s$ such that $t=\t\vert_{A,C}$.  
-  Then $\t\vert_{A,B}\prefix\s\vert_{A,B}\in\sigma$ and $\t\vert_{B,C}\prefix\s\vert_{B,C}\in\tau$, so $\t\in\sigma\|\tau$.
-
-  We claim that every sequence in $\sigma;\tau$ has even length.  
-  Indeed, if $\s\vert_{A,B}\in\sigma$ and $\s\vert_{B,C}\in\tau$, then both $\s\vert_{A,B}$ and $\s\vert_{B,C}$ must have even length, so must be in configuration $OO$ or $PP$.  
-  This means that $\s$ as a whole must be in configuration $OOO$ or $PPP$, and so $\s\vert_{A,C}$ must be in configuration $OO$ or $PP$, so must have even length.
-
-  Lastly, we need to show that $\sigma;\tau$ is deterministic.  
-  Suppose that $sab,sac\in\sigma;\tau$, and suppose that $b\ne c$.  
-  Suppose that $\s\vert_{A,C}=sab$ and $\t\vert_{A,C}=sac$, for $\s,\t\in\sigma\|\tau$, and let $\u$ be the longest common prefix of $\s,\t$.
-  $\s$ and $\t$ are certainly incomparable under the prefix ordering, since $\s\vert_{A,C}$ and $\t\vert_{A,C}$ are, so we have $\u p\prefix \s$ and $\u q\prefix \t$, where $p\ne q$.
-  Now $p$ and $q$ cannot be $O$-moves in $A$, $P$-moves in $C$ or moves in $B$, or they would have to be equal by determinism of $\sigma$ and $\tau$.  
-  Therefore, they are $P$-moves in $A$ or $O$-moves in $C$, but this contradicts $\s\vert_{A,C}=sab$ and $\t\vert_{A,C}=sac$.
-
-  Therefore, the composition $\sigma;\tau$ is a strategy.  
-\end{proof}
-
-We also want to show that the composition of innocent strategies is innocent.
-We follow the proof given in \cite{Harmer2006InnocentGS}.  
-First, we use a lemma.
-
-\begin{lemma}[{\cite[3.3.3]{Harmer2006InnocentGS}}]
-  Let $\s a\in\Int(A,B,C)$.
-
-  i) If $a$ is a $P$-move of $A$ or an $O$-move of $B$, then $\pv{\s a\vert_{A,B}}=\pv{\pv{\s a}\vert_{A,B}}$.
-
-  ii) If $a$ is a $P$-move of $B$ or an $O$-move of $C$, then $\pv{\s a\vert_{B,C}}=\pv{\pv{\s a}\vert_{B,C}}$.
-  \label{LemHarmerProjection}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $\s$.
-  We prove (i); the proof of (ii) is exactly the same.
-
-  If $a$ is a $P$-move of $A$ or an $O$-move of $B$, then it is an $O$-move of $A\implies B$.
-  If $a$ is an initial move of $A\implies B$, then we have $\pv{\s\vert_{A,B}a}=a=\pv{a}\vert_{A,B}=\pv{\pv{\s a}}\vert_{A,B}$.  
-  Otherwise, write $\s=\t b\u$, where $b$ justifies $a$.  
-  Then $\pv{\s a \vert_{A,B}} = \pv{\t\vert_{A,B} b\u\vert_{A,B} a} = \pv{t\vert_{A,B}}ba$, which by the inductive hypothesis is equal to $\pv{\pv{\t}\vert_{A,B}}ba$, which is equal to $\pv{\pv{\t b \u a}\vert_{A,B}} = \pv{\pv{\s a}\vert_{A,B}}$.
-\end{proof}
-
-\begin{proposition}
-  If $\sigma\from A \implies B$ and $\tau\from B \implies C$ are innocent strategies, then $\sigma;\tau\from A\implies C$ is innocent.
-\end{proposition}
-\begin{proof}
-  Suppose there are $sab,t\in\sigma;\tau$ such that $ta\in P_{A\implies C}$, $\pv{sa}=\pv{ta}$.
-  Let $\s' b$ be such that $\s' b\vert_{A,C}=sab$ and choose the minimal prefix $\s\prefix \s'$ such that $\s a\vert_{A,C}=sa$.
-
-  Let $\t a$ be such that $\t a\vert_{A,C}=ta$.
-  Since $\pv{sa}=\pv{ta}$, we have $\pv{\s a}\vert_{A,C}=\pv{\s a\vert_{A,C}}=\pv{sa}=\pv{ta}=\pv{\t a\vert_{A,C}}=\pv{\t a}\vert_{A,C}$ by Lemma \ref{LemHarmerRestriction}.  
-  Let $\u$ be the longest common prefix of $\pv{\s a}$ and $\pv{\t a}$.  
-  If $\s a$ and $\t a$ are not equal, then without loss of generality there is some $\u p\prefix \s$, where $\u p\not\prefix \t$.  
-  Then, by determinism of $\sigma$ and $\tau$, this $p$ cannot be a $P$-move in either $A\implies B$ or $B\implies C$, so it must be a $P$-move in $A$ or an $O$-move in $C$, and is therefore preceded by another move in $A$ or $C$, which contradicts $\pv{\s a}\vert_{A,C}=\pv{\t a}\vert_{A,C}$.
-  Therefore, $\pv{\s a}=\pv{\t a}$.
-
-  Now write $\s'=\s a b_1 \cdots b_n b$, where each $b_i$ is a move in $B$.  
-  We show by induction that $\t a b_1 \cdots b_j\in\sigma\|\tau$.  
-  Indeed, if $\t a b_1 \cdots b_{j-1}\in\sigma\|\tau$, then $b_j$ (or $b$) is a $P$-move in either $A\implies B$ or $B\implies C$, and $b_{j-1}$ is an $O$-move in that same component.  
-  Write $X$ for the component ($A\implies B$ or $B\implies C$) in which $b_j$ is a $P$-move.
-  Repeating the argument above, we see that $\pv{\t a b_1\cdots b_{j-1}} = \pv{\s a b_1\cdots b_{j-1}}$, and so we have that $\pv{\t a b_1\cdots b_{j-1}\vert_X}=\pv{\s a b_1\cdots b_{j-1}\vert_X}$ by Lemma \ref{LemHarmerProjection}.
-  Therefore, by innocence of $\sigma$ (if $X=A\implies B$) or $\tau$ (if $X=B\implies C$), we see that $\t a b_1 \cdots b_j\in \sigma\|\tau$.  
-  It follows that $\t a b_1 \cdots b_n b\in\sigma\|\tau$, and therefore that $t a b\in\sigma;\tau$.
-\end{proof}
-
-\section{Associativity of composition}
-
-In this section, we shall prove that composition of strategies is associative; i.e., that if $\sigma\from A \implies B$, $\tau\from B\implies C$ and $\upsilon \from C \implies D$ are strategies, then $(\sigma;\tau);\upsilon=\sigma;(\tau;\upsilon)$.
-To do this, if $A,B,C,D$ are arenas, we define the set $\Int(A,B,C,D)$ to be the set of all sequences $\u$ of moves such that $\u\vert_{A,B}\in \L_{A\implies B}$, $\u\vert_{B,C}\in \L_{B\implies C}$ and $\u\vert_{C,D}\in \L_{C \implies D}$.
-Given such a sequence $\u$, we define $\u\vert_{A,D}$ as before; i.e., we take all moves from $\u$ occurring in $A$ and $D$, together with justification pointers within these games, and if an initial move in $A$ is justified by an initial move in $B$, which is justified by an initial move in $C$, which is justified by an initial move in $D$, then we add a justification pointer from that move in $A$ to that move in $D$.
-
-Given strategies $\sigma,\tau,\upsilon$ as above, we define $\sigma\|\tau\|\upsilon$ to be the set of all $\u\in\Int(A,B,C,D)$ such that $\u\vert_{A,B}\in\sigma$, $\u\vert_{B,C}\in\tau$ and $\u\vert_{C,D}\in\upsilon$.
-We then claim that:
-
-\begin{lemma}
-  \[
-    (\sigma;\tau);\upsilon = \{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\} = \sigma;(\tau;\upsilon)\,.
-    \]
-\end{lemma}
-\begin{proof}
-  Firstly, if $\u\in\sigma\|\tau\|\upsilon$, then it is clear to see that $\u\vert_{A,B,C}\in\sigma\|\tau$ and that $\u\vert_{B,C,D}\in\tau\|\upsilon$, and therefore that $\{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\}\subset (\sigma;\tau);\upsilon$ and $\{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\}\subset \sigma;(\tau;\upsilon)$.
-
-  Conversely, suppose that $\t\in(\sigma;\tau)\|\upsilon$, so that $\t\vert_{A,C}\in\sigma;\tau$ and $\t\vert_{C,D}\in\upsilon$, and choose some $\s\in\sigma\|\tau$ such that $\s\vert_{A,C}=\t\vert_{A,C}$.
-  We may write 
-  \[
-    \s=\ccc_1\bbb_1\aaa_1\cdots \ccc_n\bbb_n\aaa_n
-    \]
-  for some (possibly empty) sequences of moves $\aaa_i$ from $A$, $\bbb_i$ from $B$ and $\ccc_i$ from $C$.  
-  We may then write 
-  \[
-    \t=\ddd_1\ccc_1\aaa_1\cdots\ddd_n\ccc_n\aaa_n
-    \]
-  (for the same $\aaa_i$, $\ccc_i$), and we can therefore interleave these sequences into the sequence
-  \[
-    \u = \ddd_1\ccc_1\bbb_1\aaa_1\cdots\ddd_n\ccc_n\bbb_n\aaa_n\,,
-    \]
-  which is in $\sigma\|\tau\|\upsilon$.
-  Then we have $\u\vert_{A,D}=\t\vert_{A,D}$, and it follows that $(\sigma;\tau);\upsilon\subset\{\u\vert_{A,C}\suchthat \u\in\sigma\|\tau\|\upsilon\}$, and the case for $\sigma;(\tau;\upsilon)$ is identical.
-\end{proof}
-
-\section{Copycat strategies}
-\label{SecCopycat}
-
-\begin{definition}
-  Let $A,B$ be games.  
-  Then a \emph{subset inclusion} of $A$ into $B$ is a partial injection $i\from M_A\hookrightarrow M_B$ such that
-  \begin{itemize}
-    \item if $i$ is defined at $a$ and $b$ then $*\ts_A a$ if and only if $*\ts_B i(a)$, and $a\ts_A b$ if and only if $i(a)\ts_B i(b)$;
-    \item $i(a)$ is defined for every move $a$ occurring in a play in $P_A$; and
-    \item $i_*(s)\in P_B$ for every $s\in P_A$.
-  \end{itemize}
-  Here, $i_*(s)$ means the function $i$ applied pointwise to the elements of the string $s$.
-
-  If $i$ is a subset inclusion of $A$ into $B$, then we get an innocent strategy $\subs_i\from B \implies A$ defined by
-  \[
-    \subs_i = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=i_*(t\vert_A)$}\}\,.
-    \]
-  If $P_B=\{i_*(s)\suchthat s\in P_A\}$, then we call it a \emph{structural isomorphism}, and we write $\cc_i$ (`copycat') for $\subs_i$.
-\end{definition}
-
-\begin{proposition}
-  $\subs_i$ is an innocent strategy.
-
-  Moreover, if $\sigma\from C \implies B$ is a strategy, then
-  \[
-    \sigma;\subs_i = \{[\id_{M_C},i\inv]_*(s)\suchthat s\in\sigma,\,s\vert_B\in i_*(P_A)\}\,,
-    \]
-  where $i\inv\from M_B \pfun M_A$ is the canonical partial right-inverse to $i$, and if $\tau \from A \implies D$ is a strategy, then
-  \[
-    \subs_i;\tau = \{[i,\id_{M_D}]_*(s)\suchthat s\in\tau\}\,.
-    \]
-  \label{PropCopycat}
-\end{proposition}
-\begin{proof}
-  $\subs_i$ is clearly prefix-closed by definition.  
-  Suppose that $sab,sac\in\subs_i$; then $s\vert_A=i_*(s\vert_B)$ and $sab\vert_A=i_*(sab\vert_B)$.  
-  It follows that $ab\vert_A=i_*(ab\vert_B)$, so either $a$ is a move in $A$ and $b=i(a)$ or $a$ is a move in $B$ and $a=i(b)$.  
-  Since the same applies to $c$, and since $i$ is injective, we have $b=c$.
-
-  This argument also shows that $\subs_i$ is \emph{history-free} -- i.e., that its reply to an $O$-position is entirely determined by the last $O$-move -- and therefore it is certainly innocent.
-
-  Now let $\sigma \from C \implies B$ be a strategy.  
-  Suppose that $\s\in\sigma\|\subs_i$.  
-  Then $\s\vert_{C,B}\in\sigma$ and $\s\vert_B=i_*(\s\vert_A)$; i.e., $\s\vert_{C,B}=[\id_{M_C},i]_*(\s\vert_{C,A})$, and therefore $\s\vert_{C,A}=[\id_{M_C},i]_*(\s\vert_{C,B})$, where $\s\vert_B\in i_*(P_A)$.
-
-  Conversely, given $s\in\sigma$, where $s\vert_B\in i_*(P_A)$, for each $P$-move $b=i(a)$ in $s$ occurring in the component $B$, insert the move $a$ immediately after it, and for each $O$-move $b'=i(a')$ in $s$ occurring in the component $B$, insert the move $a'$ immediately before it.
-  Let these extra moves in $B$ be justified according to the original moves in $A$, and let all initial moves in $B$ be justified by the initial moves in $A$ that occur immediately before them.
-  Then the resulting sequence $\s$ is contained in $\sigma\|\subs_i$, and $\s\vert_{A,C}=[\id_{M_C},i\inv]_*(s)$.
-
-  The case for composition in the other direction is similar.
-\end{proof}
-
-An easy corollary of this fact is that composition of copycat strategies respects composition of the underlying subset inclusions.
-
-\begin{corollary}
-  Let $i$ be a subset inclusion from $A$ to $B$ and let $j$ be a subset inclusion from $B$ to $C$.  
-  Then $j\circ i$ is a subset inclusion from $A$ to $C$ and $\cc_{j\circ i}=\subs_j;\subs_i\from C \implies A$.
-\end{corollary}
-
-It is also easy to see from Proposition \ref{PropCopycat} that the identity function $\id\from M_A \to M_A$ is a structural isomorphism from $A$ to itself, and that the resulting copycat strategy $\cc_{\id}$ is an identity for composition.
-Combining this with our result for associativity in the previous section, we get that
-\begin{theorem}
-  The collection of games forms a category $\G$, where the morphisms $A \to B$ are strategies for $A\implies B$, composition is as above and the identity morphisms are the copycat strategies induced from the identity functions on moves.
-\end{theorem}
-
-In this setting, Proposition \ref{PropCopycat} tells us that a structural isomorphism gives rise to an isomorphism in $\G$.
-\begin{proposition}
-  Let $f$ be a structural isomorphism from a game $A$ to a game $B$.  
-  Then $\cc_f$ is an isomorphism in $\G$ from $A$ to $B$.
-\end{proposition}
-\begin{proof}
-  The underlying partial injection $f\from M_A \hookrightarrow M_B$ has an inverse partial injection $f\inv\from M_B \to M_A$, inducing a structural isomorphism from $B$ to $A$.  
-  Then Proposition \ref{PropCopycat} tells us that $\cc_f$ and $\cc_{f\inv}$ are inverses in $\G$.
-\end{proof}
-
-General subset inclusions are not, of course, isomorphisms, but we can still say something category-theoretic about them.
-
-\begin{proposition}
-  Let $i$ be a subset inclusion from a game $A$ to a game $B$.  
-  Then the strategy $\subs_i$ is an epimorphism from $B$ to $A$.
-  \label{PropSubsetInclusionEpic}
-\end{proposition}
-\begin{proof}
-  In fact, it is a split epimorphism: we can define a retract
-  \[
-    \ret_i = \{s\in P_{A\implies B}\suchthat\text{for all even-length $t\prefix s$, $t\vert_A=i_*(t\vert_B)$}\}\,.
-    \]
-  The same argument as in Proposition \ref{PropCopycat} tells us that this is indeed a strategy for $A\implies B$.
-  Note that although $\subs_i$ is always a total strategy (i.e., if $s\in\subs_i$ and $sa\in P_{B\implies A}$, then there is always $sab\in\subs_i$ for some $b$), the same is not in general true about $\ret_i$.
-
-  In any case, if $\s\in\ret_i\|\subs_i$, then $\s\vert_{A^L} = i_*(\s\vert_B) = \s\vert_{A^R}$, and the same is true of any even-length substring of $\s$, and so $\s\vert_{A,A}\in\id_A$.  
-  Conversely, given any $s\in \id_A$, we can form some $\s\in\ret_i\|\subs_i$ such that $\s\vert_{A,A}=s$ as in Proposition \ref{PropCopycat}.
-
-  We can also prove that $\subs_i$ is an epimorphism directly, which might be useful, for example, in a setting in which non-total strategies such as $\ret_i$ are disallowed.  
-  In this setting, let $\sigma,\tau\from A \implies C$ be strategies such that $\subs_i;\sigma=\subs_i;\tau$.  
-  Then, by Proposition \ref{PropCopycat}, we know that
-  \[
-    \{[i,\id_{M_C}]_*(s)\suchthat s\in\sigma\}
-    =
-    \{[i,\id_{M_C}]_*(s)\suchthat s\in\tau\}\,.
-    \]
-  Then, since the function $[i,\id_{M_D}]_* \from P_{A\implies C} \to P_{B\implies C}$ is an injection, we deduce that $\sigma=\tau$.
-\end{proof}
-
-\section{$\G$ as a Symmetric Monoidal Category}
-
-We now claim that the tensor product connective $\tensor$ makes $\G$ into a symmetric monoidal closed category, with internal hom given by $\implies$.
-
-\begin{definition}
-  Let $\sigma\from A \implies B$ and $\tau\from C \implies D$ be strategies.  
-  We define a strategy $\sigma\tensor\tau\from (A\tensor C) \implies (B \tensor D)$ by
-  \[
-    \sigma\tensor\tau = \{s\in P_{(A\tensor C)\implies (B\tensor D)}\suchthat s\vert_{A,B}\in\sigma\text{ and }s\vert_{C,D}\in\tau\}\,.
-    \]
-\end{definition}
-
-To prove that this is a strategy, we prove a lemma analogous to our Lemma \ref{LemCompositionLemma}.
-
-\begin{lemma}
-  Let $s\in P_{A\tensor B}$.  
-  Then $\lambda^{OP}_{A\tensor B}(s)=\lambda^{OP}_A(s\vert_A)\wedge\lambda^{OP}_B(s\vert_B)$, where $\wedge$ is the binary operator on $\OP$ given by
-  \[
-    \begin{array}{cc|c}
-      p & q & p\wedge q \\
-      \hline
-      P & P & P \\
-      O & P & O \\
-      P & O & O \\
-      O & O & O
-    \end{array}\,.
-    \]
-  Moreover, either $\lambda_A^{OP}(s\vert_A)=P$ or $\lambda_B^{OP}(s\vert_B)=P$.
-  \label{LemTensorAnalogue}
-\end{lemma}
-\begin{proof}
-  Mutual induction on the length of $s$.  
-  This is obvious if $s$ is empty.  
-  Suppose that $sa\in P_{A\tensor B}$, where $a$ is an $O$-move.  
-  By induction, since $\lambda_{A\tensor B}(s)=P$, we must have $\lambda_{A\tensor B}(s\vert_A)=P$ and $\lambda_{A\tensor B}(s\vert_B)=P$.  
-  Therefore, depending on which game $a$ is played in, either $\lambda_A(sa\vert_A)=O$ and $\lambda_B(sa\vert_B)=P$ or $\lambda_A(sa\vert_A)=P$ and $\lambda_B(sa\vert_B)=O$.
-
-  If $sb\in P_{A\tensor B}$, where $b$ is a $P$-move, then by induction either $\lambda_A(s\vert_A)=O$ and $\lambda_B(s\vert_B)=P$ or $\lambda_A(s\vert_A)=P$ and $\lambda_B(s\vert_B)=O$.  
-  In either case, player $P$ must play in whichever game is currently in an $O$-position, returning us to configuration $PP$.
-\end{proof}
-
-The above proof gives us the following result, which is analogous to Corollary \ref{CorSwitchingCondition}.
-
-\begin{corollary}[Switching condition for {$\tensor$}]
-  Player $O$ switches games in $A\tensor B$; i.e., if $sab\in P_{A\tensor B}$, where $a$ and $b$ take place in different games (i.e., $a$ in $A$ and $b$ in $B$ or $a$ in $B$ and $b$ in $A$), then $b$ is an $O$-move.
-\end{corollary}
-
-\begin{proposition}
-  $\sigma\tensor\tau$ is a strategy for $(A\tensor C)\implies (B\tensor D)$.
-  \label{PropTensorWellDefined}
-\end{proposition}
-\begin{proof}
-  $\sigma\tensor\tau$ is certainly an even-prefix-closed subset of $P_{(A\tensor C)\implies (B\tensor D)}^{\textit{even}}$.
-
-  Let $s$ be a play of $P_{(A\tensor B)\implies (C\tensor D)}$.  
-  We consider the possible configurations of $s$; i.e., the tuples $(\lambda_A(s\vert_A),\lambda_B(s\vert_B),\lambda_C(s\vert_C),\lambda_D(s\vert_D))$.
-
-  By Lemma \ref{LemCompositionLemma} we must avoid the overall configuration $OP$ for the linear implication, and by Lemma \ref{LemTensorAnalogue} we must avoid the configuration $OO$ inside either tensor product, so we end up with the following possibilities.
-  \scriptsize
-  \[
-\arraycolsep=4.8pt\def\arraystretch{1.5}
-    \begin{array}{cccc|cc|c}
-      \lambda_A(s\vert_A) & \lambda_C(s\vert_C) & \lambda_B(s\vert_B) & \lambda_D(s\vert_D) & \lambda_{A\tensor C}(s\vert_{A,C}) & \lambda_{B\tensor D}(s\vert_{B,C}) & \lambda_{(A\tensor C)\implies (B\tensor D)}(s) \\
-      \hline
-      P & P & P & P & P & P & P \\
-      P & P & P & O & P & O & O \\
-      P & P & O & P & P & O & O \\
-      P & O & P & O & O & O & P \\
-      O & P & O & P & O & O & P \\
-      P & O & O & P & O & O & P \\
-      O & P & P & O & O & O & P \\
-    \end{array}
-    \]
-  \normalsize
-  Now, if $s\in\sigma\tensor\tau$, or an odd-length sequence formed by adding an $O$-move to the end of a sequence in $\sigma\tensor\tau$, then we also know that $s\vert_{A,B}\in\sigma\subset P_{A\implies B}$ and that $s\vert_{C,D}\in\tau\subset P_{C\implies D}$.
-  This means that we can discount the last two configurations in the table above, since one contains the illegal configuration $OP$ in $C\implies D$ and the other contains the illegal configuration $OP$ in $A \implies B$.
-
-  Now suppose that $sab,sac\in\sigma\tensor\tau$.  
-  Then $sa$ is an $O$-position in $(A\tensor C)\implies (B\tensor D)$, and is therefore in configuration $PPPO$ or $PPOP$.  
-  By inspecting the table above, we see that if $sa$ is in configuration $PPPO$, then $b$ and $c$ must both occur either in $C$ or in $D$, and that if $sa$ is in configuration $PPOP$, then $b$ and $c$ must both occur either in $A$ or in $B$.
-  In either case, we must have $b=c$, by determinism of $\tau$ (in the first case) or of $\sigma$ (in the second case).
-\end{proof}
-
-We need a lemma to prove that the tensor product of two innocent strategies is innocent.
-
-\begin{lemma}
-  Let $s\in\sigma\tensor\tau$.
-
-  i) If $s$ ends with a move in $A$ or $B$, then $\pv{s}^{(A\tensor C)\implies (B\tensor D)}=\pv{s\vert_{A,B}}^{A\implies B}$.
-
-  ii) If $s$ ends with a move in $C$ or $D$, then $\pv{s}^{(A\tensor C)\implies (B\tensor D)}=\pv{s\vert_{C,D}}^{C\implies D}$.
-  \label{LemTensorViewLemma}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $s$.  
-  We prove (i); (ii) is exactly the same.
-
-  If $a$ is a $P$-move, then we have $\pv{sa}=\pv{s}a$.  
-  By our analysis in the proof of Proposition \ref{PropTensorWellDefined}, player $P$ only switches moves between $A$ and $B$, and between $C$ and $D$, so $s$ must end with a move from $A$ or $B$.  
-  Therefore, by the inductive hypothesis, $\pv{s}=\pv{s\vert_{A,B}}$.  
-  Then $\pv{sa}=\pv{s}a=\pv{s\vert_{A,B}}a=\pv{sa\vert_{A,B}}$.
-
-  If $a$ is an initial move, then $\pv{sa}=a=\pv{sa\vert_{A,B}}$.
-
-  If $a$ is an $O$-move justified by $b$ in $sbta$, then $\pv{sbta}=\pv{s}ba$.  
-  Then $b$ is a $P$-move, so $s$ must end with a move in $A$ or $B$, as before.  
-  Therefore, by the inductive hypothesis, $\pv{s}=\pv{s\vert_{A,B}}$.  
-  Then $\pv{sbta}=\pv{s}ba=\pv{s\vert_{A,B}}ba=\pv{sbta\vert_{A,B}}$.
-\end{proof}
-
-\begin{proposition}
-  Let $\sigma\from A \to B$, $\tau\from C \to D$ be innocent strategies.  
-  Then $\sigma\tensor\tau$ is innocent.
-  \label{PropTensorInnocent}
-\end{proposition}
-\begin{proof}
-  Suppose $sab,t\in\sigma\tensor\tau$ such that $ta\in P_{(A\tensor C)\implies (B\tensor D)}$ and $\pv{sa}=\pv{ta}$.  
-  Suppose without loss of generality that $a$ is a move in $A$ or $B$.  
-  Then $\pv{sa}=\pv{sa\vert_{A,B}}$ and $\pv{ta}=\pv{ta\vert_{A,B}}$ by Lemma \ref{LemTensorViewLemma}, and therefore $tab\vert_{A,B}\in\sigma$ by innocence of $\sigma$, and so $tab\in\sigma\tensor\tau$.
-\end{proof}
-
-The most important thing we need to prove is that $\tensor$ is a functor.
-
-\begin{proposition}
-  Let $\sigma'\from A'' \implies A'$, $\sigma\from A' \implies A$, $\tau'\from B'' \implies B'$ and $\tau \from B' \implies B$ be strategies.  
-  Then $(\sigma'\tensor\tau');(\sigma\tensor\tau)=(\sigma';\sigma)\tensor(\tau';\tau)$.
-
-  Moreover, if $A',A,B',B$ are games, $i$ is a subset inclusion from $A$ to $A'$ and $j$ is a structural isomorphism from $B$ to $B'$, then $\subs_i\tensor\subs_j = \subs_{[i,j]}$.
-  In particular, if $A$ and $B$ are games, then $\id_A\tensor \id_B=\id_{A\tensor B}$.
-  \label{PropTensorProductIsFunctor}
-\end{proposition}
-\begin{proof}
-  First suppose that $s\in(\sigma'\tensor\tau');(\sigma\tensor\tau)$; so $s=\s\vert_{A'',B'',A,B}$, where $\s\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)$.  
-  Then $\s\vert_{A'',A'}\in\sigma'$ and $\s\vert_{A',A}\in\sigma$, so $\s\vert_{A'',A',A}\in\sigma'\|\sigma$ and therefore $s\vert_{A'',A}=\s\vert_{A'',A}\in\sigma';\sigma$.  
-  Similarly, $s\vert_{B'',B}\in\tau';\tau$, and therefore $s\in(\sigma';\sigma)\tensor(\tau';\tau)$.
-
-  Conversely, suppose that $s\in(\sigma';\sigma)\tensor (\tau';\tau)$.  
-  Choose some $\s\in\sigma'\|\sigma$, $\t\in\tau'\|\tau$ such that $s\vert_{A'',A}=\s\vert_{A'',A}$ and $s\vert_{B'',B}=\s\vert_{B'',B}$.  
-  By our analysis, the only time we switch from the $A'',A$-component to the $B'',B$ component in $s$, or \emph{vice versa}, is when player $O$ switches between the games $A$ and $B$.  
-  Thus, we may divide $s$ up into blocks, each starting and ending with a move in the outer component $A \tensor B$.  
-  This then gives us a way to divide up $\s$ and $\t$ into blocks, such that each block of $\s$ or $\t$ projects on to a block of $s$.  
-  Lastly, we can string these blocks together to give us some $\u\in(\sigma'\tensor\tau')\|(\sigma\tensor\tau)$ such that $\u\vert_{A'',B'',A,B}=s$.
-
-  For the second part, let $A',A,B',B$ be games, let $i$ be a structural isomorphism from $A$ to $A'$ and let $j$ be a structural isomorphism from $B$ to $B'$.  
-  Suppose that $s\in\subs_i\tensor \subs_j$.  
-  Then $s\vert_{A',A}\in\subs_i$ and $s\vert_{B',B}\in\subs_j$ -- so if $u\prefix s\vert_{A,A}$ has even length, then $u\vert_{A'}=i_*(u\vert_A)$, and if $v\prefix s\vert_{B,B}$ has even length, then $v\vert_{B'}=i_*(v\vert_B)$.
-  Suppose that $t\prefix s$ is of even length.  
-  Then, since only player $O$ switches between the $A',A$-component and the $B',B$-component, both $t\vert_{A',A}$ and $t\vert_{B',B}$ are of even length, it follows that $t\vert_{A',B'}=[i,j]_*(t\vert_{A,B})$.
-  Since $t$ was arbitrary, this means that $s\in \subs_{[i,j]}$.
-
-  Conversely, suppose that $s\in\subs_{[i,j]}$.  
-  Then for all even-length $t\prefix s$, $t\vert_{A'}=i_*(t\vert_{A})$ and $t\vert_{B'}=j_*(t\vert_{B})$.  
-  Since any play in $\sigma$ or in $\tau$ is itself a play of $\sigma\tensor\tau$, then if $u\prefix s\vert_{A',A}$ has even length, then $u\vert_{A'}=i_*(u\vert_{A})$, and if $v\prefix s\vert_{B',B}$, then $v\vert_{B'}=j_*(v\vert_{B})$.
-  It follows that $s\vert_{A',A}\in \subs_i$ and $s\vert_{B',B}\in\subs_j$, and therefore that $s\in \subs_i\tensor\subs_j$.  
-\end{proof}
-
-Now it is fairly clear that if $A,B,C$ are games, then we have structural isomorphisms
-\begin{mathpar}
-  (A \tensor B) \tensor C \cong A \tensor (B\tensor C)
-  \\
-  A \cong A \tensor I \and A \cong I \tensor A
-  \\
-  A \tensor B \cong B \tensor A\,,
-\end{mathpar}
-induced by the associators, unitors and symmetry of the category of sets with coproduct.
-We claim that these are natural transformations.
-
-\begin{proposition}
-  The families of morphisms
-  \begin{mathpar}
-    \cc_{\assoc_{M_A,M_B,M_C}} \from (A \tensor B) \tensor C \to A \tensor (B \tensor C)
-    \\
-    \cc_{\lunit_{M_A}} \from A \to I \tensor A \and \cc_{\runit_{M_A}} \from A \to A \tensor I
-    \\
-    \cc_{\sym{M_A,M_B}} \from A \tensor B \to B \tensor A
-  \end{mathpar}
-  are natural transformations in $\G$.
-  \label{PropCoherencesAreNatural}
-\end{proposition}
-\begin{proof}
-  We prove this for the associator; the other cases are similar.
-
-  Let $\sigma\from A' \implies A$, $\tau\from B' \implies B$, $\upsilon\from C' \implies C$ be strategies.  
-  By Proposition \ref{PropCopycat}, we have
-  \begin{IEEEeqnarray*}{Cl}
-    & ((\sigma\tensor\tau)\tensor\upsilon);\cc_{\assoc_{M_{A},M_{B},M_{C}}} \\
-    = & \{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s)\suchthat s\in (\sigma\tensor\tau)\tensor\upsilon\} \\
-    = & \left\{[\id_{M_{(A'\tensor B')\tensor C'}},\assoc_{M_A,M_B,M_C}]_*(s) \,\middle|\,\mbox{\pbox{\textwidth}{
-      $s\in P_{((A'\tensor B')\tensor C')\implies ((A \tensor B) \tensor C)}$\\
-      $s\vert_{A',A}\in\sigma$, $s\vert_{B',B}\in\tau$, $s\vert_{C',C}\in\upsilon$
-    }}\right\} \\
-    = & \{s\in P_{((A'\tensor B') \tensor C') \implies (A \tensor (B \tensor C))} \suchthat s\vert_{A',A}\in\sigma,s\vert_{B',B}\in\tau,s\vert_{C',C}\in\upsilon\} \\
-    = & \left\{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s) \,\middle|\,\mbox{\pbox{\textwidth}{
-      $s\in P_{(A'\tensor (B'\tensor C'))\implies (A \tensor (B \tensor C))}$\\
-      $s\vert_{A',A}\in\sigma$, $s\vert_{B',B}\in\tau$, $s\vert_{C',C}\in\upsilon$
-    }}\right\} \\
-    = & \{[\assoc_{M_{A'},M_{B'},M_{C'}},\id_{M_{A\tensor (B\tensor C)}}]_*(s)\suchthat s\in \sigma\tensor (\tau\tensor \upsilon)\} \\
-    = & \cc_{\assoc_{M_{A'},M_{B'},M_{C'}}};(\sigma\tensor(\tau\tensor\upsilon))\,.\hspace{1pt plus 1fill} \qedhere
-  \end{IEEEeqnarray*}
-\end{proof}
-
-Then, by Proposition \ref{PropCopycat} again, these natural transformations satisfy the same coherence diagrams (pentagon, triangles, hexagon etc.) satisfied by the original associators, unitors and symmetry in $(\Set,+)$.
-
-It follows that $\tensor$ makes $\G$ into a symmetric monoidal category.
-
-\section{$\G$ as a Symmetric Monoidal Closed Category}
-
-\begin{definition}
-  Let $A,B,C,D$ be games, let $\sigma$ be a strategy for $A\implies B$ and let $\tau$ be a strategy for $C\implies D$.  
-  Then we define a strategy $\sigma\implies \tau\from (B\implies C) \implies (A\implies D)$ by
-  \[
-    \sigma\implies \tau = \{s\in P_{(B\implies C) \implies (A \implies D)}\suchthat \text{$s\vert_{A,B}\in\sigma$, $s\vert_{C,D}\in\tau$}\}\,.
-    \]
-\end{definition}
-
-\begin{proposition}
-  $\sigma\implies\tau$ is a strategy for $(B\implies C) \implies (A \implies D)$.
-  \label{PropImpliesWellDefined}
-\end{proposition}
-\begin{proof}
-  $\sigma\implies\tau$ is certainly a prefix-closed subset of $P_{(B\implies C)\implies (A \implies D)}^{\textit{even}}$.
-
-  We examine the sign configuration of a play in $(B\implies C)\implies (A\implies D)$, using Lemma \ref{LemCompositionLemma}.  
-  Since we must avoid the configuration $OP$ in either $B\implies C$, $A\implies D$ or in $(B\implies C)\implies (A\implies D)$, we arrive at the following list of possibilities.
-  \scriptsize
-  \[
-\arraycolsep=2.6pt\def\arraystretch{1.5}
-    \begin{array}{cccc|cc|c}
-      \lambda_B^{OP}(s\vert_B) & \lambda_C^{OP}(s\vert_C) & \lambda_A^{OP}(s\vert_A) & \lambda_D^{OP}(s\vert_D) & \lambda_{B\implies C}^{OP}(s\vert_{B,C}) & \lambda_{A\implies D}^{OP}(s\vert_{A,D}) & \lambda_{(B\implies C)\implies (A\implies D)}^{OP}(s) \\
-      \hline
-      P & O & P & O & O & O & P \\
-      P & P & P & O & P & O & O \\
-      O & O & P & O & P & O & O \\
-      P & P & P & P & P & P & P \\
-      O & O & O & O & P & P & P \\
-      P & P & O & O & P & P & P \\
-      O & O & P & P & P & P & P
-    \end{array}
-    \]
-  \normalsize
-  If $s\in\sigma\implies\tau$, then we can immediately discount the last two of these possibilities, since one includes the illegal configuration $OP$ in $A\implies B$, and the other includes the illegal configuration $OP$ in $B\implies D$.
-
-  By examining the remaining possibilities, we arrive at the conclusion that any $O$-position in configuration $PPPO$ constrains player $P$ to play in $C$ (to reach configuration $POPO$) or to play in $D$ (to reach configuration $PPPP$), and that any $O$-position in configuration $OOPO$ constrains player $P$ to play in $A$ (to reach configuration $OOOO$) or to play in $C$ (to reach configuration $POPO$).
-
-  Now suppose that $sab,sac\in\sigma\implies\tau$.  
-  Then, by our above analysis, $b$ and $c$ must either both take place in the $B,A$-component, in which case $b = c$ by determinism of $\sigma$, or both in the $C,D$-component, in which case $b = c$ by determinism of $\tau$.
-\end{proof}
-
-To prove that $\sigma\implies\tau$ is innocent if $\sigma$ and $\tau$ are, we need a lemma analogous to Lemma \ref{LemTensorViewLemma}.
-
-\begin{lemma}
-  Let $s\in \sigma\implies \tau$.
-
-  i) If $s$ ends with a move in $A$ or $B$, then $\pv{s}^{(B\implies C) \implies (A\implies D)} = \pv{s\vert_{A,B}}^{A\implies B}$.
-
-  ii) If $s$ ends with a move in $C$ or $D$, then $\pv{s}^{(B\implies C) \implies (A\implies D)} = \pv{s\vert_{C,D}}^{C\implies D}$.
-  \label{LemImpliesViewLemma}
-\end{lemma}
-\begin{proof}
-  Exactly the same as in Lemma \ref{LemTensorViewLemma}, using the analysis from the proof of Proposition \ref{PropImpliesWellDefined} to show that player $P$ only switches moves between $A$ and $B$, and between $C$ and $D$, in $\sigma\implies\tau$.
-\end{proof}
-
-\begin{proposition}
-  Let $\sigma\from A \implies B$, $\tau\from C\implies D$ be innocent strategies.  
-  Then $\sigma\implies\tau$ is innocent.
-\end{proposition}
-\begin{proof}
-  Suppose $sab,t\in\sigma\implies\tau$ such that $ta\in P_{(B\implies C)\implies (A \implies D)}$ and $\pv{sa}=\pv{ta}$.  
-  Suppose without loss of generality that $a$ is a move in $A$ or $B$.  
-  Then $\pv{sa}=\pv{sa\vert_{A,B}}$ and $\pv{ta}=\pv{ta\vert_{A,B}}$ by Lemma \ref{LemImpliesViewLemma}, and therefore $tab\vert_{A,B}\in\sigma$ by innocence of $\sigma$, and so $tab\in\sigma\implies\tau$.
-\end{proof}
-
-We now need to prove that $\implies$ is a functor $\oppcat\G\times\G\to\G$.
-
-\begin{proposition}
-  Let $\sigma'\from A''\implies A'$, $\sigma\from A'\implies A$, $\tau'\from B'' \implies B'$ and $\tau\from B'\implies B$ be strategies.  
-  Then $(\sigma\implies\tau');(\sigma'\implies\tau) = (\sigma';\sigma)\implies(\tau';\tau)$.
-
-  Moreover, if $A',A,B',B$ are games, $f$ is a structural isomorphism from $A'$ to $A$ and $g$ is a structural isomorphism from $B'$ to $B$, then $\cc_f\implies\cc_g = \cc_{[f\inv,g]}$.
-  In particular, if $A,B$ are games than $\id_A\implies\id_B=\id_{A\implies B}$.
-\end{proposition}
-\begin{proof}
-  As in Proposition \ref{PropTensorProductIsFunctor}.
-\end{proof}
-
-Now it is easy to see that the associator $\assoc_{M_A,M_B,M_C}$ is a structural isomorphism from $(A\tensor B) \implies C$ to $A\implies (B\implies C)$, so it induces a copycat isomorphism $\Lambda_{A,B,C}=\cc_{\assoc_{M_A,M_B,M_C}} \from (A\tensor B) \implies C \to A \implies (B\implies C)$.
-
-\begin{proposition}
-  $\Lambda_{A,B,C}$ is natural in $A,B,C$.
-\end{proposition}
-\begin{proof}
-  The same argument as in Proposition \ref{PropCoherencesAreNatural}.
-\end{proof}
-
-We have proved the following.
-
-\begin{theorem}
-  $\G$ is a symmetric monoidal closed category, with tensor product given by $\tensor$ and internal hom given by $\implies$.
-\end{theorem}
-
-\section{Tree Immersions and Zigzag Strategies}
-
-So far, the strategies we have been considering have all been innocent.  
-We now start considering some non-innocent strategies.
-
-We can generalize the subset inclusions of the previous section to \emph{tree immersions}.  
-Tree immersions are similar to subset inclusions, but generated by a function between plays, rather than between moves.  
-A consequence of this is that while tree immersions do give rise to strategies, these strategies are not in general innocent.
-
-\begin{definition}
-  Let $A,B$ be games.  
-  A \emph{tree immersion} from $A$ to $B$ is a function $\phi\from P_A \hookrightarrow P_B$ such that
-  \begin{itemize}
-    \item $\phi$ preserves length and justification indices; 
-    \item for all sequences $s,t\in P_A$, if $t\prefix s$ then $\phi(t)\prefix\phi(s)$; and
-    \item if $\phi(sb)=\phi(sc)$, where $b,c$ are $P$-moves in $A$, then $b=c$.
-  \end{itemize}
-
-  Given a tree immersion $\phi$ from $A$ to $B$, we define a strategy $\zz_\phi\from B \implies A$ by
-  \[
-    \zz_\phi = \{s\in P_{B\implies A}\suchthat\text{for all even-length $t\prefix s$, $t\vert_B=\phi(t\vert_A)$}\}\,.
-    \]
-\end{definition}
-\begin{example}
-  If $i$ is a subset inclusion from $A$ to $B$, then $i_*$ is a tree immersion from $A$ to $B$ and $\zz_{i_*}=\subs_i$.
-\end{example}
-
-\begin{proposition}
-  $\zz_\phi$ is a strategy.  
-\end{proposition}
-\begin{proof}
-  $\zz_\phi$ is a prefix-closed subset of $P_{B\implies A}$ by definition.  
-  If $sab,sac\in\zz_\phi$, then we have $s\vert_B=\phi(s\vert_A)$ and $sab\vert_B=\phi(sab\vert_A)$.
-  Since $\phi$ is length-preserving, $s\vert_A$ and $s\vert_B$ must have the same length, and the same is true of $sab\vert_A$ and $sab\vert_B$.  
-  Therefore, either $a$ is a move in $A$ and $s\vert_Bb=\phi(s\vert_Aa)$ or $a$ is a move in $B$ and $s\vert_Ba=\phi(s\vert_Ab)$.  
-  The same applies to $c$: so either $s\vert_Bb=\phi(s\vert_Aa)=s\vert_Bc$ or $\phi(s\vert_Ab)=s\vert_Ba=\phi(s\vert_Ac)$.  
-  In either case, we have $b=c$.
-\end{proof}
-
-We want an analogue of Proposition \ref{PropCopycat}.
-
-\begin{definition}
-  Given a tree immersion from $A$ to $B$, and a play $s\in P_{C\implies A}$ for some $C$, we write $s^\phi$ for the play obtained by replacing the moves of $s\vert_A$ wholesale with the moves of $\phi(s\vert_A)$ (using the fact that $\phi$ preserves length and justification indices).
-\end{definition}
-
-\begin{proposition}
-  If $\sigma\from C \implies B$ is a strategy, then $\sigma;\zz_\phi$ is given by
-  \[
-    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\}\,.
-    \]
-
-  In particular, if $\phi$ is a tree immersion from $A$ to $B$ and $\psi$ is a tree immersion from $B$ to $C$, then $\psi\circ\phi$ is a tree immersion from $A$ to $C$ and $\zz_{\psi\circ\phi}=\zz_\psi;\zz_\phi$.
-  \label{PropTree}
-\end{proposition}
-\begin{proof}
-  Suppose that $\s\in\sigma\|\zz_\phi$.  
-  Then $\s\vert_{C,B}\in\sigma$ and $t\vert_B=\phi(t\vert_A)$ for all even-length $t\prefix \s\vert_{B,A}$.  
-  Then it is clear that $(\s\vert_{C,A})^\phi=\s\vert_{C,B}$.
-
-  Conversely, suppose that $s\in P_{C\implies A}$ and that $s^\phi\in\sigma$.  
-  We construct a sequence $\s\in\sigma\|\zz_phi$ such that $\s\vert_{C,B}=s^\phi$ and $\s\vert_{C,A}=s$ by taking the sequence $s$ and inserting, in order, the elements of the sequence $\phi(s\vert_A)$ immediately after each $O$-move in $s\vert_C$ and immediately before each $P$-move in $C$, leaving the rest of $s$ intact.
-  Then $\s\vert_{C,B}=s^\phi\in\sigma$ and $\s\vert_{B,A}\in\zz_\phi$, by construction.  
-  So $s=\s\vert_{C,A}\in \sigma;\zz_\phi$.
-\end{proof}
-
-\begin{definition}
-  We say that a tree immersion $\phi$ is a \emph{tree isomorphism} if it is a bijection.
-\end{definition}
-
-\begin{proposition}
-  If $\phi$ is a tree isomorphism from a game $A$ to a game $B$, then $\zz_\phi$ is an isomorphism in $\G$.
-\end{proposition}
-\begin{proof}
-  If $\phi$ is a tree isomorphism, then its inverse $\phi\inv$ is also a tree isomorphism, and Proposition \ref{PropTree} tells us that $\zz_\phi$ and $\zz_{\phi\inv}$ are inverses in $\G$.
-\end{proof}
-
-More generally:
-
-\begin{proposition}
-  If $\phi$ is a surjection, then $\zz_\phi$ is a monomorphism.
-  \label{PropZigzagMono}
-\end{proposition}
-\begin{proof}
-  Let $\sigma,\tau\from C \implies B$ be strategies.
-  Then, by Proposition \ref{PropTree}, we have
-  \[
-    \{s\in P_{C\implies A}\suchthat s^\phi\in\sigma\} = \{s\in P_{C\implies A}\suchthat s^\phi\in\tau\}\,.
-    \]
-  Let $t\in\sigma$.  
-  Then, since $\phi$ is surjective, there is some $u\in P_A$ such that $\phi(u)=t\vert_B$.  
-  As before, we may construct some sequence $t'$ such that $t'\vert_A=u$ and $t=(t')^\phi$.  
-  Then, since $(t')^\phi=t\in\sigma$, we must have $(t')^\phi\in\tau$; i.e., that $t\in\tau$.  
-  So $\sigma\subset\tau$.
-
-  Similarly, $\tau\subset\sigma$, and so $\sigma$ and $\tau$ are equal.
-\end{proof}
-
-\section{Products in $\G$}
-
-\begin{proposition}
-  Given some family $A_i$ of games, the game $\prod_i A_i$, as defined in Definition \ref{DefProduct}, is the category-theoretic product of the $A_i$.
-  \label{PropProductOfGames}
-\end{proposition}
-\begin{proof}
-  We have natural injections $\inj_j \from M_{A_j} \hookrightarrow M_{\prod_i A_i}$ giving rise to subset inclusions.  
-  Then our projections are given by the morphisms 
-  \[
-    \pr_j \coloneqq \subs_{\inj_j}\from \prod_i A_i \to A_j\,.
-    \]
-  Now suppose we have some game $B$, and strategies $\sigma_i \from B \implies A_i$ for each $i$.
-  Define a strategy
-  \[
-    \langle \sigma_i \rangle = \bigcup_i [\id_{M_B},\inj_i]_*(\sigma_i)\,.
-    \]
-  We claim that this is indeed a strategy for $B \implies \prod_i A_i$.
-  Indeed, it is certainly a prefix-closed subset of $P_{C\implies\prod_i A_i}$.
-
-  Moreover, if $sab,sac\in\langle \sigma_i \rangle$, then there is some unique $j$ such that $a$ comes from a move in $A_j$, and therefore $sab,sac$ are both plays in $\sigma_j$, so $b=c$.
-
-  Next, we claim that $\langle\sigma_i\rangle;\pr_j = \sigma_j$.  
-  Indeed, we have
-  \begin{IEEEeqnarray*}{rCl/u}
-    \langle\sigma_i\rangle;\pr_j & = & \langle\sigma_i\rangle;\subs_{\inj_j} \\
-    & = & \{[\id_{M_B},\inj_j\inv]_*(s)\suchthat s\in\langle\sigma_i\rangle,\,s\vert_{\prod_iAi}\in(\inj_j)_*(P_{A_j})\} & \textit{Prop.~\ref{PropCopycat}} \\
-    & = & \sigma_j\,.
-  \end{IEEEeqnarray*}
-  Lastly, suppose $\tau\from B\implies\prod_iA_i$ is a strategy such that $\tau;\pr_j=\sigma_j$ for each $j$.
-  We claim that $\tau=\langle\sigma_i\rangle$.
-  Indeed, by the argument above, we must have
-  \[
-    \{[\id_{M_B},\inj_j\inv]_*(s)\suchthat s\in\tau,\,s\vert_{\prod_iA_i}\in(\inj_j)_*(P_{A_j})\} = \sigma_j
-    \]
-  for each $j$.
-  Suppose that $s\in\tau$.  
-  Then $s\vert_{\prod_iA_i}\in(\inj_j)_*(P_{A_j})$ for some $j$, by the definition of $\prod_iA_i$.  
-  Therefore, $s\in[\id_{M_B},\inj_j]_*(\sigma_j)$.
-
-  Conversely, let $t\in \sigma_j$.  
-  By the above equation, we know that there is some $s\in\tau$ such that $s\vert_{\prod_iA_i}\in(\inj_j)_*(P_{A_j})$ and $[\id_{M_B},\inj_j\inv]_*(s)=t$.  
-  It follows that $[\id_{M_B},\inj_j]_*(t)=s\in\tau$.
-\end{proof}
-
-An examination of the definitions tells us that
-\begin{proposition}
-  Let $A_i,B$ be games and let $\phi_i$ be tree immersions from $A_i$ to $B$.  
-  Then $\langle \zz_{\phi_i} \rangle = \zz_\phi$, where $\phi$ is the tree immersion from $\prod_iA_i$ to $B$ given by
-  \[
-    \phi(s) = \begin{cases}
-      \epsilon & \text{if $s=\epsilon$} \\
-      \phi_i(s\vert_{A_i}) & \text{if $s$ starts with a move from $A_i$}
-    \end{cases}
-    \]
-  \label{PropProductOfTreeEmbeddings}
-\end{proposition}
-\begin{proof}
-  The only thing we really need to check is that this is indeed a tree immersion.  
-  Let $sb,sc$ be positions in $\prod_iA_i$, where $b,c$ are $P$-moves.
-  Then $sb,sc$ must start with the same move, so if $\phi(sb)=\phi(sc)$ then we have $\phi_i(sb)=\phi_i(sc)$ for some $i$ and therefore $b=c$.
-\end{proof}
-
-Note that $\langle\sigma_i\rangle$ is not in general innocent, even if all the $\sigma_i$ are, and there is no version of Proposition \ref{PropProductOfTreeEmbeddings} that works for subset inclusion strategies.
-Of course, since a subset inclusion is a special case of a tree immersion, then $\langle \subs_i\rangle$ is always a tree immersion strategy.
-
-\section{Sequoidal categories}
-
-We have now given the category-theoretic properties of all the connectives from section \ref{SecConnectives}, with the exception of the sequoid $\sequoid$ and the exponential $\oc$.
-
-We would like to say that $\blank\sequoid\blank$ is a functor from $\G \times \G \to \G$, as is the case with the tensor product $\blank\tensor\blank$.  
-However, this does not quite work: given strategies $\sigma\from A \implies B$ and $\tau\from C \implies D$, we may not get a well-formed strategy for $(A \sequoid C) \implies (B \sequoid D)$ by `playing according to $\sigma$ in $A$ and $B$ and according to $\tau$ in $C$ and $D$'.
-The reason is that the constraint that player $O$ plays in $B$ before $D$ is not strong enough to force player $P$ to play in $A$ before $C$; indeed, suppose that $\sigma$ tells player $P$ to respond to an initial move in $B$ with another move in $B$.
-Suppose that player $O$ then decides to make a move in $D$.  
-If $\tau$ tells player $P$ to respond to this move in $D$ with a move in $C$, then she will be stuck, unable to play this move because no move has yet been played in $A$.
-
-We can fix this problem by imposing some constraints on the strategies $\sigma$ and $\tau$.  
-The problem occurs when player $O$'s initial move in $B$ is not reflected by an initial move by player $P$ in $A$; therefore, if $\sigma$ is such that player $P$ always responds to the initial move in $B$ with a move in $A$, then we can form a strategy $\sigma\sequoid\tau$ for $(A\sequoid C)\implies (B\sequoid D)$.
-Moreover, this strategy $\sigma\sequoid\tau$ will inherit this property that the first move on the right is always replied to by a move on the left.
-
-\begin{definition}
-  Let $A,B$ be games.  
-  A \emph{strict morphism} from $A$ to $B$ is a strategy $\sigma$ for $A\implies B$ such that any player $P$ response to an opening move in $B$ is a move in $A$; i.e., such that if $b$ is an initial $O$-move in $B$ and $ba\in\sigma$, then $a$ is a move in $A$.
-\end{definition}
-
-We will call such a $\sigma$ a \emph{strict strategy} for $A\implies B$, although this is a slight abuse of language, since the definition depends on the constituent games $A$ and $B$, which may not be recoverable from $A\implies B$.
-
-It is clear that the composition of strict morphisms is again a strict morphism , as is any morphism of the form $\subs_i$, and so we get a wide subcategory $\G_s$ of $\G$ whose objects are games and where the morphisms are the strict strategies.
-We then have a natural inclusion functor $J\from \G_s\to \G$.
-
-\begin{definition}
-  Given games $A,B,C,D$, a strict morphism $\sigma\from A \implies B$ and a strategy $\tau\from C\implies D$, we define a strict morphism $\sigma\sequoid\tau\from (A \sequoid C)\implies (B \sequoid D)$ by
-  \[
-    \sigma\sequoid\tau = \{s\in P_{(A\sequoid C)\implies (B\sequoid D)}\suchthat s\vert_{A,B}\in\sigma,\,s\vert_{C,D}\in\tau\}\,.
-    \]
-  \label{DefSequoidOfStrategies}
-\end{definition}
-
-\begin{proposition}
-  $\sigma\sequoid\tau$ is a strategy.  
-\end{proposition}
-\begin{proof}
-  $\sigma\sequoid\tau$ is certainly a prefix-closed subset of $P_{(A\sequoid C)\implies (B\sequoid D)}$.  
-  Moreover, if $sab,sac\in\sigma\sequoid\tau$, then $sab,sac\in\sigma\tensor\tau$, so $b=c$.  
-\end{proof}
-
-Of course, $P_{A\sequoid B}$ is a subset of $P_{A\tensor B}$, which means that the identity function $M_A + M_B \to M_A + M_B$ gives us a subset inclusion from $A \sequoid B$ to $A \tensor B$, and hence a strategy $\subs_{\id_{M_A+M_B}}$ for $A\tensor B \implies A \sequoid B$, which we shall refer to as $\wk_{A,B}$.
-
-\begin{proposition}
-  Let $A,B,C,D$ be games, let $\sigma\from A \implies B$ be a strict strategy and let $\tau\from C \implies D$ be a strategy.  
-  Then the following diagram commutes.
-  \[
-    \begin{tikzcd}
-      A \tensor C \arrow[r, "\sigma\tensor\tau"] \arrow[d, "{\wk_{A,C}}"']
-        & B \tensor D \arrow[d, "{\wk_{B,D}}"] \\
-      A \sequoid C \arrow[r, "\sigma\sequoid\tau"]
-        & B \sequoid D
-    \end{tikzcd}
-    \]
-  \label{PropWkCommutativeDiagram}
-\end{proposition}
-\begin{proof}
-  By Proposition \ref{PropCopycat} and the definition of $\wk$, we know that
-  \begin{IEEEeqnarray*}{rCl}
-    \sigma\tensor\tau;\wk_{B,D} & = & \{s\in \sigma\tensor\tau,\,s\vert_{B,D}\in P_{B\sequoid D}\}
-    \\
-    \wk_{A,C};\sigma\sequoid\tau & = & \sigma\sequoid\tau\,,
-  \end{IEEEeqnarray*}
-  as sets of plays.
-
-  Now we know that $\sigma\sequoid\tau = \{s\in\sigma\tensor\tau\suchthat s\in P_{(A\sequoid C)\implies (B\sequoid D)}\}$, so it suffices to show that if $s\in\sigma\tensor\tau$ is such that $s\vert_{B,D}\in P_{B\sequoid D}$ then $s\in P_{(A\sequoid C)\implies (B\sequoid D)}$.
-
-  Indeed, if $s\vert_{B,D}\in P_{B\sequoid D}$ then $s$ begins with an initial $O$-move in $B$.  
-  Then, \emph{since $\sigma$ is strict}, the next move in $s$ must be a move in $A$, and therefore $s\vert_{A,C}$ begins with a move in $A$.
-  Since we also have $s\vert_{A,C}\in P_{A\tensor C}$, we must have that $s\vert_{A,C}\in P_{A\sequoid C}$.
-\end{proof}
-\begin{remark}
-  This is the main place where we have used the assumption that $\sigma$ is a strict strategy: if we drop the strictness requirement from Definition \ref{DefSequoidOfStrategies}, then we get a valid (if nonsensical) strategy that has a partiality (`gives up') if playing according to $\sigma$ and $\tau$ would lead to it creating an invalid play.
-  But such a strategy would not satisfy the conclusion of Proposition \ref{PropWkCommutativeDiagram}, since $\sigma\tensor\tau;\wk_{B,D}$ would contain these extra plays where $\wk_{A,C};\sigma\sequoid\tau$ had `given up'.
-\end{remark}
-\begin{remark}
-  Of course, we would \emph{like} to restate Proposition \ref{PropWkCommutativeDiagram} by saying that $\wk$ is some sort of natural transformation, but that doesn't make sense until we've shown that $\blank\sequoid\blank$ is a functor.
-\end{remark}
-
-\begin{proposition}
-  If we have strict strategies $\sigma'\from A'' \implies A'$ and $\sigma\from A' \implies A$, and strategies $\tau' \from B'' \implies B'$ and $\tau \from B' \implies B$, then we have
-  \[
-    (\sigma'\sequoid\tau');(\sigma\sequoid\tau) = (\sigma';\sigma)\sequoid(\tau';\tau)\,.
-    \]
-  If $A',A,B',B$ are games, $i$ is a subset inclusion from $A$ into $A'$ and $j$ is a subset inclusion from $B$ into $B'$, then
-  \[
-    \subs_i\sequoid\subs_j = \subs_{[i,j]}\from A'\sequoid B' \implies A \sequoid B\,.
-    \]
-  In particular, if $A,B$ are games, then $\id_A\sequoid\id_B=\id_{A\sequoid B}$.
-  \label{PropSequoidIsFunctor}
-\end{proposition}
-\begin{proof}
-  Let $A'',A',A,B'',B',B$ and $\sigma',\sigma,\tau',\tau$ be as above.
-
-  We have
-  \begin{IEEEeqnarray*}{rCl?u}
-    \wk_{A'',B''};(\sigma'\sequoid\tau');(\sigma\sequoid\tau) & = & (\sigma'\tensor\tau');\wk_{A',B'};(\sigma\sequoid\tau) & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
-    & = & (\sigma'\tensor\tau');(\sigma\tensor\tau);\wk_{A,B} & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
-    & = & ((\sigma';\sigma)\tensor(\tau';\tau));\wk_{A,B} & \textit{Prop. \ref{PropTensorProductIsFunctor}} \\
-    & = & \wk_{A'',B''};((\sigma';\sigma)\sequoid(\tau';\tau))\,. & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
-  \end{IEEEeqnarray*}
-  By Proposition \ref{PropSubsetInclusionEpic}, $\wk_{A'',B''}$ is an epimorphism, and therefore we have that
-  \[
-    (\sigma'\sequoid\tau');(\sigma\sequoid\tau) = (\sigma';\sigma)\sequoid(\tau';\tau)\,.
-    \]
-
-  Now let $A',A,B',B$ be games, let $i$ be a subset inclusion from $A$ into $A'$ and let $j$ be a subset inclusion from $B$ into $B'$.  
-  Then, since subset inclusion strategies are automatically strict, we have
-  \begin{IEEEeqnarray*}{rCl?u}
-    \wk_{A',B'};(\subs_i\sequoid\subs_j) & = & (\subs_i\tensor\subs_j);\wk_{A,B} & \textit{Prop. \ref{PropWkCommutativeDiagram}} \\
-    & = & \subs_{[i,j]};\wk_{A,B} & \textit{Prop. \ref{PropTensorProductIsFunctor}} \\
-    & = & \subs_{[i,j]} & \textit{Prop. \ref{PropCopycat}} \\
-    & = & \wk_{A',B'};\subs_{[i,j]}\,. & \textit{Prop. \ref{PropCopycat}} \\
-  \end{IEEEeqnarray*}
-  As before, we know from Proposition \ref{PropSubsetInclusionEpic} that $\wk_{A',B'}$ is an epimorphism, and so
-  \[
-    \subs_i\sequoid\subs_j = \subs_{[i,j]}\,.\qedhere
-    \]
-\end{proof}
-
-Proposition \ref{PropSequoidIsFunctor} tells us that $\blank\sequoid\blank$ is a functor $\G_s\times\G\to \G$.  
-As before, write $J$ for the inclusion functor $\G_s\hookrightarrow\G$.
-Then we can restate Proposition \ref{PropWkCommutativeDiagram} in a more \emph{natural} way.
-
-\begin{proposition}
-  $\wk_{A,B}$ is a natural transformation $JA \tensor B \to J(A \sequoid B)$.
-  \label{PropWkNatural}
-\end{proposition}
-
-We have some additional structure on the $\tensor$ and $\sequoid$ operators.  
-By inspecting the definitions that if $A,X,Y$ are games then the associator $\assoc_{M_A,M_X,M_Y}$ and unitor $\runit_{M_A}$ in $(\Set,+)$ give rise to structural isomorphisms
-\begin{mathpar}
-  (A \sequoid X) \sequoid Y \cong A \sequoid (X \tensor Y)
-  \and
-  A \cong A \sequoid I\,.
-\end{mathpar}
-Indeed, in the first case, both games are the game in which $A$, $X$ and $Y$ are played in parallel, but where the first move must take place in $A$.  
-In the second case, we have $A\sequoid I=A\tensor I$, because there are no moves in $I$ anyway, and the copycat morphism induced from the right unitor in $(\Set,+)$ is the same strategy as the right unitor $A \toisom A \tensor I$.
-
-We formalize the structure we have uncovered so far in the concept of a \emph{sequoidal category}.
-
-\begin{definition}[\cite{laird02}]
-  A \emph{sequoidal category} $\C$ is given by
-  \begin{itemize}
-    \item a symmetric monoidal category $(\C,\tensor, I)$ (with coherences $\assoc,$ $\lunit$, $\runit$, $\sym$);
-    \item a (strong) right action of $\C$ on a category $\C_s$; i.e., a functor $\blank\sequoid\blank\from\C_s\times\C\to\C_s$ together with natural isomorphisms
-      \begin{mathpar}
-        \passoc_{a,x,y}\from (a \sequoid x) \sequoid y \toisom a \sequoid (x \tensor y)
-        \and
-        \run_a \from a \toisom a \sequoid I
-      \end{mathpar}
-      that make the diagrams
-      \begin{mathpar}
-        \begin{tikzcd}[column sep=31pt]
-          ((a \sequoid x) \sequoid y) \sequoid z \arrow[r, "{\passoc_{a,x,y}\sequoid z}" yshift=1pt] \arrow[d, "{\passoc_{a\sequoid x,y,z}}"' description]
-            & (a \sequoid (x \tensor y)) \sequoid z \arrow[r, "{\passoc_{a,x\tensor y,z}}" yshift=1pt]
-              & a \sequoid ((x\tensor y) \tensor z)  \arrow[dl, "{a \sequoid \assoc_{x,y,z}}"] \\
-          (a \sequoid x) \sequoid (y \tensor z) \arrow[r, "{\passoc_{a,x,(y\tensor z)}}" yshift=1pt]
-            & a \sequoid (x \tensor (y \tensor z))
-              &
-        \end{tikzcd}
-        \and
-        \begin{tikzcd}
-          a \sequoid x \arrow[r, "{a \sequoid \lunit_x}"] \arrow[d, "\run_a \sequoid x"']
-            & a \sequoid (I \tensor x) \\
-          (a \sequoid I) \sequoid x \arrow[ur, "{\passoc_{a,I,x}}"']
-            &
-        \end{tikzcd}
-        \and
-        \begin{tikzcd}
-          a \sequoid x \arrow[r, "{a \sequoid \runit_x}"] \arrow[d, "\run_{a \sequoid x}"']
-            & a \sequoid (x \tensor I) \\
-          (a \sequoid x) \sequoid I \arrow[ur, "{\passoc_{a,x,I}}"']
-            &
-        \end{tikzcd}
-      \end{mathpar}
-      commute; and
-    \item a lax morphism of actions from $\blank\sequoid\blank$ to the right tensor multiplication action $\blank\tensor\blank$ of $\C$ on itself; i.e., a functor $J\from \C_s \to \C$ and a natural transformation $\wk_{a,x} \from Ja \tensor x \to J(a \sequoid x)$ that makes the following diagrams commute.
-      \begin{mathpar}
-        \begin{tikzcd}[column sep=30pt]
-          (Ja \tensor x) \tensor y \arrow[r, "{\wk_{a,x}\tensor y}"] \arrow[d, "{\assoc_{Ja,x,y}}"'] & J(a \sequoid x) \tensor y \arrow[r, "{\wk_{a\sequoid x,y}}"]
-              & J((a \sequoid x) \sequoid y) \arrow[dl, "{J\passoc_{a,x,y}}"] \\
-          Ja \tensor (x \tensor y) \arrow[r, "{\wk_{a,x\tensor y}}"]
-            & J(a \sequoid (x \tensor y))
-              &
-        \end{tikzcd}
-        \and
-        \begin{tikzcd}
-          Ja \arrow[r, "J\run_a"] \arrow[d, "\runit_{Ja}"']
-            & J(a \sequoid I) \\
-          Ja \tensor I \arrow[ur, "{\wk_{a,I}}"']
-            &
-        \end{tikzcd}
-      \end{mathpar}
-  \end{itemize}
-  \label{DefSequoidalCategory}
-\end{definition}
-\begin{remark}
-  The definitions of \emph{lax action} can be found at the start of Chapter \ref{ChapParametricMonads}, while that of an \emph{oplax morphism of actions} is found at Definition \ref{DefOplaxMorphismOfActions}.
-  The definitions we have used are similar: a \emph{strong action} is a lax action in which the coherences (called $m$ and $e$ in Chapter \ref{ChapParametricMonads} and $\passoc$ and $\run$ here) are isomorphisms.
-  A \emph{lax morphism of actions} is defined in the same way as an oplax morphism, except that the coherence (called $\mu$ in Definition \ref{DefOplaxMorphismOfActions} and $\wk$ here) goes in the opposite direction.
-\end{remark}
-
-\begin{proposition}
-  The monoidal category $\G$, together with the category $\G_s$, the natural transformations
-  \begin{mathpar}
-    \passoc_{A,X,Y} = \cc_{\assoc_{M_A,M_X,M_Y}} \from (A \sequoid X) \sequoid Y \toisom A \sequoid (X \tensor Y)
-    \and
-    \run_A = \cc_{\runit_{M_A}} \from A \toisom A \sequoid I\,,
-  \end{mathpar}
-  the inclusion functor $J\from \G_s \to G$ and the natural transformation
-  \begin{mathpar}
-    \wk_{A,X}=\subs_{j} \from JA \tensor X = A \tensor X \to A \sequoid X = J(A \sequoid X)
-  \end{mathpar}
-  form a sequoidal category.
-\end{proposition}
-\begin{proof}
-  We have shown most of this already; all that remains is to show that $\passoc$ and $\run$ are natural transformations and that the five diagrams in Definition \ref{DefSequoidalCategory} commute.
-
-  Let us start with the diagrams.  
-  By Proposition \ref{PropCopycat}, commutativity of these diagrams follows from commutativity of the diagrams formed from the corresponding subset inclusion functions in $\Set$.  
-  For example, to show that the first diagram commutes in $\G$, we must show that the following diagram commutes in $\Set$.
-  \scriptsize
-  \[
-    \begin{tikzcd}[column sep=16pt, row sep=30pt]
-      ((M_A + M_X) + M_Y) + M_Z \arrow[r, "{[\assoc_{M_A,M_X,M_Y},\id_{M_Z}]}" yshift=3pt] \arrow[d, "{\assoc_{M_A+M_X,M_Y,Z}}" description]
-        & (M_A + (M_X + M_Y)) + M_Z \arrow[r, "{\assoc_{M_A,M_X+M_Y,M_Z}}" yshift=3pt]
-          & M_A + ((M_X + M_Y) + M_Z) \arrow[dl, "{[\id_{M_A},\assoc_{M_X,M_Y,M_Z}]}"] \\
-      (M_A + M_X) + (M_Y + M_Z) \arrow[r, "{\assoc_{M_A,M_X,M_Y+M_Z}}" yshift=3pt]
-        & M_A + (M_X + (M_Y + M_Z))
-          &
-    \end{tikzcd}
-    \]
-  \normalsize
-  This diagram is, of course, none other than the pentagram diagram for the coproduct $+$ in $\Set$.  
-  Similarly, the second and third diagrams in Definition \ref{DefSequoidalCategory} reduce in this case to the triangle diagrams for the coproduct $+$ in $\Set$.
-
-  For the fourth diagram in Definition \ref{DefSequoidalCategory}, since $\wk$ is a subset inclusion strategy induced from an identity map, Proposition \ref{PropCopycat} tells us that both arms of the diagram are the strategy induced by the subset inclusion
-  \[
-    \assoc_{M_A,M_X,M_Y}\from (M_A + M_X) + M_Y \to M_A + (M_X + M_Y)
-    \]
-  from $(A \tensor X) \tensor Y$ to $A \sequoid (X \tensor Y)$.
-  Similarly, both arms of the last diagram in Definition \ref{DefSequoidalCategory} are the strategies induced by the subset inclusion $\runit_{M_A} \from M_A \to M_A + \emptyset$ from $A$ to $A \sequoid I$.
-
-  It now remains only to show that $\passoc$ and $\run$ are natural transformations.  
-  For $\passoc$, suppose that $A',X',Y',A,X,Y$ are games, that $\sigma\from A'\implies A$ is a strict strategy and that $\tau\from B'\implies B,\upsilon\from C'\implies C$ are strategies.  
-  Then we need to show that the following diagram commutes.
-  \[
-    \begin{tikzcd}[column sep=50pt]
-      (A' \sequoid X') \sequoid Y' \arrow[r, "{\passoc_{A',X',Y'}}"] \arrow[d, "(\sigma\sequoid\tau)\sequoid\upsilon"']
-        & A' \sequoid (X' \tensor Y') \arrow[d, "\sigma\sequoid (\tau\tensor\upsilon)"] \\
-      (A \sequoid X) \sequoid Y \arrow[r, "{\passoc_{A,X,Y}}"]
-        & A \sequoid (X \tensor Y)
-    \end{tikzcd}
-    \]
-  Indeed, we have
-  \begin{IEEEeqnarray*}{rCl?u}
-    && (\wk_{A',X'}\tensor Y');\wk_{A'\sequoid X',Y'};\passoc_{A',X',Y'};(\sigma\sequoid(\tau\tensor\upsilon)) \\
-    & = & \assoc_{A',X',Y'};\wk_{A',X'\tensor Y'};(\sigma\sequoid(\tau\tensor\upsilon)) & (see above) \\
-    & = & \assoc_{A',X',Y'};(\sigma\tensor(\tau\tensor\upsilon));\wk_{A,X\tensor Y} & \textit{Prop. \ref{PropWkNatural}} \\
-    & = & ((\sigma\tensor\tau)\tensor\upsilon);\assoc_{A,X,Y};\wk_{A,X\tensor Y} & \textit{Prop. \ref{PropCoherencesAreNatural}} \\
-    & = & ((\sigma\tensor\tau)\tensor\upsilon);(\wk_{A,X}\tensor Y);\wk_{A\sequoid X,Y};\passoc_{A,X,Y} & (see above) \\
-    & = & (\wk_{A',X'}\tensor Y');((\sigma\sequoid\tau)\tensor\upsilon);\wk_{A\sequoid X,Y};\passoc_{A,X,Y} & \textit{Prop. \ref{PropWkNatural}} \\
-    & = & (\wk_{A',X'}\tensor Y');\wk_{A'\sequoid X',Y'};((\sigma\sequoid\tau)\sequoid\upsilon);\passoc_{A,X,Y}\,. & \textit{Prop. \ref{PropWkNatural}}
-  \end{IEEEeqnarray*}
-  Now observe that $\wk_{A',X'}\tensor Y=\subs_{[\id_{M_{A'}+M_{X'}},\id_{M_{Y'}}]}$ by Proposition \ref{PropTensorProductIsFunctor}, so it is an epimorphism by Proposition \ref{PropSubsetInclusionEpic}.
-  Proposition \ref{PropSubsetInclusionEpic} also tells us that $\wk_{A'\sequoid X',Y'}$ is an epimorphism.  
-  Therefore, we have
-  \[
-    \passoc_{A',X',Y'};(\sigma\sequoid(\tau\tensor\upsilon)) = ((\sigma\sequoid\tau)\sequoid\upsilon);\passoc_{A,X,Y}
-    \]
-  for any $A',X',Y',A,X,Y,\sigma,\tau,\upsilon$ as above.  
-  It follows that $\passoc$ is a natural transformation.
-
-  The proof that $\run$ is a natural transformation is similar.  
-  Let $A',A$ be games and let $\sigma\from A'\implies A$ be a strict strategy.  
-  We need to show that the following diagram commutes.
-  \[
-    \begin{tikzcd}
-      A' \arrow[r, "\run_{A'}"] \arrow[d, "\sigma"']
-        & A' \sequoid I \arrow[d, "\sigma\sequoid I"] \\
-      A \arrow[r, "\run_A"]
-        & A \sequoid I
-    \end{tikzcd}
-    \]
-  Indeed, we have
-  \begin{IEEEeqnarray*}{rCl?u}
-    \run_{A'};(\sigma\sequoid I) & = & \runit_{A'};\wk_{A',I};(\sigma\tensor I) & (see above) \\
-    & = & \runit_{A'};(\sigma\tensor I);\wk_{A,I} & \textit{Prop. \ref{PropWkNatural}} \\
-    & = & \sigma;\runit_A;\wk_{A,I} & \textit{Prop. \ref{PropCoherencesAreNatural}} \\
-    & = & \sigma;\run_A\,. & (see above)
-  \end{IEEEeqnarray*}
-
-  Therefore, $\run$ is a natural transformation, which completes our check of the criteria required by Definition \ref{DefSequoidalCategory}.
-\end{proof}
-
-\section{Sequoidally decomposable categories}
-
-We will now consider some important additional category-theoretic properties of the sequoid operator on games that do not follow from the fact that $\G$ is a sequoidal category.
-
-\begin{definition}[\cite{martinsthesis}]
-  Let $\C$ be a sequoidal category such that $C_s$ has arbitrary products (including a terminal object $1$).
-  We say that $\C$ is \emph{distributive} if whenever $a_i$ is a collection of objects of $\C'$ and $x$ is an object of $\C$, the morphism
-  \[
-    \dec_{(a_i),x} = \langle \pr_i\sequoid x \rangle \from \prod_ia_i \sequoid x \to \prod_i (a_i \sequoid x)
-    \]
-  is an isomorphism.
-\end{definition}
-\begin{remark}
-  In particular, taking $(a_i)$ to be the empty collection, the morphism $\lun_x = () \from 1 \sequoid x \to 1$ is an isomorphism.
-\end{remark}
-
-\begin{proposition}
-  $\G$ is a distributive sequoidal category.
-\end{proposition}
-\begin{proof}
-  Let $(A_i),X$ be games.
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle \pr_i\sequoid X\rangle$ is given by the tree immersion $\phi\from P_{\prod_i(A_i\sequoid X)}\to P_{\prod_iA_i\sequoid X}$ defined as follows.
-  \[
-    \phi(s) = \begin{cases}
-      \epsilon & \text{if $s=\epsilon$} \\
-      [\inj_{A_j},\inj_{X}]_*(s) & \text{if $s$ begins with a move in the $j$-th component}
-    \end{cases}
-    \]
-  When we say $[\inj_{A_j},\inj_{X^j}]_*(s)$, we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.
-
-  We claim that $\phi$ is a bijection.  
-  Indeed, it is certainly injective, since if $\phi(s)=\phi(t)$, then the first move of $\phi(s)=\phi(t)$ occurs in one of the $A_j$, which means that $s,t$ must both come from the $j$-th component.
-  Then, if we have a non-empty sequence $s\in P_{\prod_iA_i \sequoid X)}$, then $s$ must start with a move in some $A_j$, and must thereafter take place in the games $A_j$ and $X$.  
-  Then $s=\phi([\inj_{A_j},\inj_{X^j}]_*(s))$, where we have considered $s$ as a sequence in $(M_{A_j} + M_{X^j})^*$.
-
-  Therefore, $\phi$ is a tree isomorphism, so $\dec_{(A_i),X} = \zz_\phi$ is an isomorphism by Proposition \ref{PropTree}.
-\end{proof}
-
-We can get a distributivity result in the other direction, but this one is not as strong, since the morphism we get is only a monomorphism, not an isomorphism.
-\begin{definition}
-  Let $\C$ be a distributive sequoidal category.  
-  We say that $\C$ is \emph{strongly distributive} if whenever $(A_i),(B_i)$ are objects of $\C_s$, where $(B_i)$ is a non-empty collection, then the morphism
-  \[
-    \langle A_1 \sequoid(\cdots \sequoid (A_n \sequoid J(\pr_i))\cdots)\rangle
-    \]
-  is a monomorphism
-  \[
-    A_1 \sequoid\left(\cdots\sequoid\left(A_n \sequoid J\left(\prod_iB_i\right)\right)\cdots\right) \to \prod_i (A_1 \sequoid (\cdots \sequoid (A_n \sequoid J(B_i))\cdots))\,.
-    \]
-\end{definition}
-
-\begin{proposition}
-  $\G$ is a strongly distributive sequoidal category.
-\end{proposition}
-\begin{proof}
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the morphism $\langle (A_1\sequoid(\cdots\sequoid(A_n \sequoid\pr_i)\cdots))\rangle$ is given by the tree immersion 
-  \[
-    \phi\from P_{\prod_i (A_1 \sequoid(\cdots\sequoid(A_n\sequoid B_i)\cdots))} \to P_{A_1\sequoid(\cdots\sequoid(A_n\sequoid \prod_iB_i))}
-    \]
-  defined as follows.
-  \[
-    \phi(s) = \begin{cases}
-      \epsilon & \text{if $s=\epsilon$} \\
-      [\inj_{A_1,\cdots,A_n},\inj_{B_j}]_*(s) & \parbox[t][][t]{180pt}{if $s$ begins with a move in the $j$-th component}
-    \end{cases}
-    \]
-  Note that $\phi$ is not in general injective, since if $s$ occurs entirely inside one of the copies of the $A_i$, then $\phi(s)=\phi(s')$ for any identical sequence $s'$ occurring inside one of the other copies of the $A_i$.
-
-  We claim that $\phi$ is surjective.  
-  Indeed, let $t\in P_{A_1\sequoid(\cdots \sequoid(\prod_i B_i))}$ be a non-empty sequence.  
-  If $t$ contains moves in one of the $B_j$, then we have $t=\phi([\inj_{A_i^j},\inj_{B_j}]_*(t))$, where $A_i^j$ is the copy of $A_i$ in the $j$-th component of the product and we have considered $t$ as a sequence in $(M_{A_1} + \cdots + M_{A_n} + M_{B_j})^*$.
-  If $t$ only contains moves in the $A_i$, then pick some fixed index $0$; then we have $t=\phi([\inj_{A_i^0}]_*(t))$, where we have considered $t$ as a sequence in $(M_{A_1} + \cdots + M_{A_n})^*$.
-
-  Therefore, $\phi$ is a monomorphism by Proposition \ref{PropZigzagMono}.
-\end{proof}
-
-Note that if $\C$ is decomposable, this property of being a monomorphism is automatically preserved by the tensor product; i.e., for any objects $A,(B_i),C$ of $\C_s$ (for $B_i$ a non-empty collection), the morphism
-\[
-  \langle JC \tensor J(A \sequoid J(\pr_i))\rangle \from JC \tensor J\left(A \sequoid J\left(\prod_iB_i\right)\right) \to \prod_i JC \tensor J(A \sequoid J(B_i))
-  \]
-is a monomorphism.
-
-\begin{definition}
-  A sequoidal category $\C$ is \emph{inclusive} if $\C_s$ is a full-on-objects subcategory of $\C$ containing $\wk$ and all isomorphisms of $\G$, and the functor $J$ is the inclusion functor.
-\end{definition}
-In such a situation, we will sometimes drop the mention of the functor $J$.
-
-\begin{proposition}
-  $\G$ is an inclusive sequoidal category.
-\end{proposition}
-\begin{proof}
-  The only thing we really need to check is that isomorphisms in $\G$ are always strict strategies.  
-  Indeed, if $\sigma$ is a strategy for $A \implies B$ and $\tau$ a strategy for $B \implies A$ such that $\sigma;\tau=\id_A$, then for any opening move $a$ in $A$ on the right of $\tau$ there is some $\s\in\int(A,B,A)$ such that $\s\vert_{A,A}=aa$, and therefore the reply to $a$ in $\tau$ must take place in $B$.
-\end{proof}
-
-An important fact about the sequoid operator for games is that it gives us a way to decompose the tensor product as
-\[
-  A \tensor B \cong (A \sequoid B) \times (B \sequoid A)\,.
-  \]
-Informally, this is because both sides allow player $O$ to start either in $A$ or in $B$, and thereafter to continue in that game.
-
-\begin{definition}
-  Let $\C$ be a distributive inclusive sequoidal category, where $\C$ is a symmetric monoidal category.
-  We say that $\C$ is \emph{decomposable} if the morphisms
-  \begin{mathpar}
-    \dec_{a,b}=\langle \wk_{a,Jb},\sym_{Ja,Jb};\wk_{b,Ja} \rangle \from Ja \tensor Jb \to (a \sequoid Jb) \times (b \sequoid Ja)
-    \and
-    () \from I \to 1
-  \end{mathpar}
-  are isomorphisms in $\C_s$.
-\end{definition}
-
-\begin{proposition}
-  Let $\C$ be a decomposable sequoidal category and suppose that $a_1,\cdots,a_n$ is a list of objects of $\C_s$.  
-  Then we have an isomorphism
-  \[
-    a_1 \tensor \cdots \tensor a_n \cong \prod_{i=1}^n (a_i \sequoid (a_1 \tensor \cdots \tensor a_{i-1} \tensor a_{i+1} \tensor \cdots \tensor a_n))\,.
-    \]
-  \label{PropDecSeq}
-\end{proposition}
-\begin{proof}
-  Induction on $n$.  
-  If $n=0$, then we have the isomorphism $() \from I \to 1$.  
-  More generally, we have
-  \begin{IEEEeqnarray*}{Cl}
-    & a_1 \tensor \cdots \tensor a_{n+1}\\
-    \cong & (a_1 \tensor \cdots \tensor a_n) \tensor a_{n+1} \\
-    \xrightarrow{\dec} & (a_1 \tensor \cdots \tensor a_n) \sequoid a_{n+1} \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
-    \cong & \left(\prod_{i=1}^n\left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j\right)\right) \sequoid a_{n+1} \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
-    \xrightarrow{\dist\times\id} & \prod_{i=1}^n\left(\left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j \right) \sequoid a_{n+1}\right) \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
-    \xrightarrow{\langle\passoc\rangle\times\id} & \prod_{i=1}^n \left(a_i \sequoid \left(\Tensor_{j\ne i}^{j\le n} a_j \tensor a_{n+1}\right)\right) \times a_{n+1} \sequoid (a_1\tensor \cdots \tensor a_n) \\
-    \cong & \prod_{i=1}^{n+1} \left(a_i \times \Tensor_{j\ne i}^{j\le n+1} a_j\right) \times a_{n+1} \sequoid (a_1 \tensor \cdots \tensor a_n) \\
-    \cong & \prod_{i=1}^{n+1} (a_i \sequoid (a_1 \tensor \cdots \tensor a_{i-1} \tensor a_{i+1} \tensor \cdots \tensor a_{n+1}))\,,
-  \end{IEEEeqnarray*}
-  where each of the arrows is an isomorphism.
-\end{proof}
-
-The specific isomorphism in Proposition \ref{PropDecSeq} is rather complicated at the moment, but we can simplify it.
-
-\begin{definition}
-  Given objects $a_1,\cdots,a_n$ of a monoidal category, we write $\sym_i^n$ for the unique symmetric coherence isomorphism
-  \[
-    a_1 \tensor \cdots \tensor a_n \cong a_i \tensor a_1 \cdots \tensor a_{i-1} \tensor a_{i+1} \tensor a_n\,.
-    \]
-\end{definition}
-
-\begin{proposition}
-  The isomorphism in the proof of Proposition \ref{PropDecSeq} is given by
-  \[
-    \dec_{(a_i)}^n = \langle \sym_i^{n};\wk_{a_i,a_1\tensor\cdots\tensor a_{i-1}\tensor a_{i+1}\tensor \cdots\tensor a_n}\rangle\,.
-    \]
-  \label{PropDecSeqFormula}
-\end{proposition}
-\begin{proof}
-  Induction on $n$.
-  We will make use of the coherence theorem for symmetric monoidal categories \cite[\sec 11]{WorkingMathematician} to allow us to elide associators.  
-  The base case is obviously true, because $()\from I \to 1$ is the unique morphism between these objects.  
-  Otherwise, we observe that the morphism into $\prod_{i=1}^{n+1} \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n+1} a_j\right)$ is given component-wise by morphisms $a_1 \tensor \cdots \tensor a_{n+1} \to a_i \sequoid \Tensor_{j\ne i}^{j\le n+1}$ for each $i=1,\cdots,n+1$; we need to check that each of these components is equal to $\sym_i^{n+1};\wk_{a_i,\Tensor_{j\ne i}a_j}$.
-
-  If $i\le n$, then the $i$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite thick dashed arrows in Figure \ref{FigDecSeqFormula}, and is therefore equal to the composite of the solid arrows, which is equal to $\sym_i^{n+1};\wk_{a_i,\Tensor_{j\ne i}a_j}$ as desired.
-  The $n+1$-th component of the morphism in the proof of Proposition \ref{PropDecSeq} is given by the composite
-  \small
-  \[
-    \Tensor_{j=1}^{n+1}a_j \to \Tensor_{j=1}^n a_j \tensor a_{n+1} \xrightarrow{\sym_{\Tensor_{j=1}^na_j,a_{n+1}}} a_{n+1} \tensor \Tensor_{j=1}^n a_j \xrightarrow{\wk_{a_{n+1},\Tensor_{j=1}^n a_j}} a_{n+1} \sequoid \Tensor_{j=1}^n a_j\,,
-    \]
-  \normalsize
-  and then we use the fact that the leftmost two morphisms in this composite compose to give us $\sym_{n+1}^{n+1}$.
-  \begin{SidewaysFigure}
-    \[
-      \begin{tikzcd}[ampersand replacement=\&, column sep=6pt, row sep=30pt]
-        \Tensor_{j=1}^{n+1}a_j \arrow[r, thick, dashed] \arrow[dd, "\sym_i^{n+1}"']
-          \& \Tensor_{j=1}^n a_j \tensor a_{n+1} \arrow[r, "{\wk_{\Tensor_{j=1}^na_j,a_{n+1}}}", thick, dashed] \arrow[d, "\sym_i^n\tensor a_{n+1}" description, dotted]
-            \&[45.5pt] \Tensor_{j=1}^n a_j \sequoid a_{n+1} \arrow[d, "\sym_i^n\sequoid a_{n+1}", thick, dashed]
-              \&[31pt] \\
-        %
-          \& \left(a_i \tensor \Tensor_{j\ne i}^{j\le n} a_j\right)\tensor a_{n+1} \arrow[r, "{\wk_{a_i\tensor\Tensor_{j\ne i}^{j\le n} a_j,a_{n+1}}}" xshift=-10pt, dotted] \arrow[d, "{\assoc_{a_i,\Tensor_{j\ne i}^{j\le n}a_j,a_{n+1}}}" description, dotted] \arrow[dr, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n}a_j}\tensor a_{n+1}}" description, dotted]
-            \& |[alias=Z]| \left(a_i \tensor \Tensor_{j\ne i}^{j\le n} a_j\right)\sequoid a_{n+1} \arrow[dr, from=Z.east, bend left=25, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n}a_j}\sequoid a_{n+1}}", thick, dashed]
-              \& \\
-        a_i \tensor \Tensor_{j\ne i}^{j\le n+1} a_j \arrow[ddrrr, bend right=15, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n+1}a_j}}"']
-          \& a_i \tensor \left(\tensor_{j\ne i}^{j\le n}a_j \tensor a_{n+1}\right) \arrow[l, dotted] \arrow[drr, to=Y.west, bend right=10, "{\wk_{a_i,\Tensor_{j\ne i}^{j\le n}a_j\tensor a_{n+1}}}" description, dotted]
-            \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n}\right)\tensor a_{n+1} \arrow[r, "{\wk_{a_i\sequoid \Tensor_{j\ne i}^{j\le n},a_{n+1}}}" xshift=-10pt, dotted]
-              \& \left(a_i \sequoid \Tensor_{j\ne i}^{j\le n} a_j\right) \sequoid a_{n+1} \arrow[d, "{\passoc_{a_i,\Tensor_{j\ne i}^{j\le n}a_j,a_{n+1}}}" {description, yshift=2pt}, thick, dashed] \\
-        %
-          \&
-            \&
-              \& |[alias=Y]| a_i \sequoid \left(\Tensor_{j\ne i}^{j\le n} a_j \tensor a_{n+1}\right) \arrow[d, thick, dashed] \\
-        %
-          \&
-            \&
-              \& a_i \sequoid \Tensor_{j\ne i}^{j\le n+1}a_j
-      \end{tikzcd}
-      \]
-    \caption[Diagram used in the proof of Proposition \ref{PropDecSeqFormula}]{Diagram used in the proof of Proposition \ref{PropDecSeqFormula}.  
-    The pentagon at the heart of the diagram is the coherence diagram for $\passoc$ and $\wk$ from Definition \ref{DefSequoidalCategory}.}
-    \label{FigDecSeqFormula}
-  \end{SidewaysFigure}
-\end{proof}
-
-\begin{proposition}
-  $\G$ is a decomposable sequoidal category.
-\end{proposition}
-\begin{proof}
-  Let $A,B$ be games.  
-  By Proposition \ref{PropProductOfTreeEmbeddings}, the strategy 
-  \[
-    \langle \wk_{A,B},\sym_{A,B};\wk_{A,B}\rangle
-    \]
-  is given by the tree immersion $\phi$ from $(A \sequoid B) \times (B \sequoid A)$ to $A \tensor B)$ given by
-  \[
-    \phi(s) = \begin{cases}
-      \epsilon & \text{if $s=\epsilon$} \\
-      s\vert_{A \sequoid B} & \text{if $s$ takes place entirely within $A\sequoid B$} \\
-      s\vert_{B \sequoid A} & \text{if $s$ takes place entirely within $B\sequoid A$}
-    \end{cases}\,.
-    \]
-  We claim that this tree immersion is a bijection.  
-  Indeed, it is certainly injective.
-  Now let $s\in P_{A\tensor B}$ be a non-empty play.  
-  Then, if $s$ begins with a move in $A$, we have $s=\phi((\inj_{A\sequoid B})_*(s))$, and if $s$ begins with a move in $B$, we have $s=\phi((\inj_{B\sequoid A})_*(s)$.  
-  Therefore, $\phi$ is a tree isomorphism, so $\dec_{A,B}=\zz_\phi$ is an isomorphism in $\G$.
-
-  Lastly, we have $I=1$ in $\G$, and the unique morphism $I\to 1$ is the identity.
-\end{proof}
-
-\begin{definition}[\cite{laird02}]
-  A \emph{sequoidal closed category} is an inclusive sequoidal category $\C$ such that $\C$ is a monoidal closed category (with inner hom $\implies$) and such that the map $f\mapsto \Lambda(\wk_{A,B};f)$ defines an isomorphism
-  \[
-    \Lambda_s \from \C_s(A \sequoid B,C) \toisom \C_s(A,B\implies C)\,.
-    \]
-\end{definition}
-
-\begin{proposition}
-  $\G$ is a sequoidal closed category.
-\end{proposition}
-\begin{proof}
-  Since $\wk_{A,B}$ is an epimorphism and $\Lambda$ is a bijection, the map is certainly injective.  
-  Showing that it is surjective comes down to proving that uncurrying of a strict strategy for $A\implies (B \implies C)$ is a strict strategy for $(A\sequoid B) \implies C$.
-  Indeed, after the opening move in $C$, in both cases player $P$ must play the next move in $A$.
-\end{proof}
-
-\section{A Formula for the Exponential}
-
-\begin{definition}
-  Let $\C$ be a symmetric monoidal category.  
-  Given objects $A_1,\cdots,A_n$ of $\C$ and a permutation $\pi\in \S_n$, there is a unique canonical symmetry isomorphism
-  \[
-    \sym^\pi \from A_1 \tensor \cdots \tensor A_n \toisom A_{\pi(1)} \tensor \cdots \tensor A_{\pi(n)}\,.
-    \]
-  Given an object $A$ of $\C$, an \emph{$n$-th symmetrized tensor power} of $A$ is an equalizer $(A^n,\eq^n)$ for the diagram given by all morphisms of the form
-  \[
-    \sym_\pi \from A ^{\tensor n} \to A ^{\tensor n}\,.
-    \]
-  We say that the symmetrized tensor power $A^n$ \emph{commutes with the tensor product} if $(B\tensor A^n,B\tensor \eq_n)$ is an equalizer for the diagram given by morphisms of the form
-  \[
-    B\tensor\sym_\pi \from B\tensor A ^{\tensor n} \to B\tensor A ^{\tensor n}\,.
-    \]
-\end{definition}
-
-\begin{proposition}[\cite{CalcoPaper}]
-  Let $\C$ be an inclusive, strongly distributive, decomposable sequoidal category.  
-  Then $\C$ has all symmetrized tensor powers.
-  \label{PropSequoidPower}
-\end{proposition}
-\begin{proof}
-  Let $A$ be an object of $\C$ (equivalently, an object of $\C_s$).  
-  We inductively define objects $A^{\sequoid n}$ by
-  \begin{itemize}
-    \item $A^{\sequoid 0} = I$; and
-    \item $A^{\sequoid (n+1)}=J(A\sequoid A^{\sequoid n})$.
-  \end{itemize}
-  We claim that $A^{\sequoid n}$ is a symmetrized tensor power of $A$.
-
-  Given $n$, we inductively define a morphism $\wk^n\from A^{\tensor n} \to A^{\sequoid n}$, where $\wk^0=\id_I$, and $\wk^{n+1}$ is given by the composite
-  \[
-    A^{\tensor (n+1)} \to A \tensor A^{\tensor n} \xrightarrow{A \tensor \wk^n} A \tensor A^{\sequoid n} \xrightarrow{\wk_{A,A^{\sequoid n}}} A \sequoid A^{\sequoid n}\,.
-    \]
-  We show by induction on $n$ that if $B$ is an object of $\C$ and $k\ge 0$ then the composite
-  \scriptsize
-  \begin{mathpar}
-    B\tensor (A \sequoid\blank)^kA^{\tensor n}
-    \xrightarrow{\langle B\tensor(A \sequoid\blank)^k \sym^\pi \rangle}
-    (B\tensor(A \sequoid\blank)^kA^{\tensor n})^{n!}
-    \xrightarrow{(B\tensor(A\sequoid\blank)^k\wk^n)^{n!}}
-    (B\tensor A^{\sequoid (k+n)})^{n!}
-  \end{mathpar}
-  \normalsize
-  (i.e., the morphism $\langle B\tensor(A\sequoid\blank)^k(\sym^\pi;\wk^n)\rangle$) is a monomorphism.
-  In particular, taking $k=0$, we will have shown that $\langle B\tensor (\sym^\pi;\wk^n)\rangle$ is a monomorphism.
-
-  The hypothesis is clearly true for $n=0$; in the general case, we have a composite
-  \begin{mathpar}
-    B\tensor (A\sequoid\blank)^kA^{\tensor (n+1)}
-    \xrightarrow{B\tensor (A\sequoid\blank)^k\langle \sym^{n+1}_i;\wk_{A,A^{\tensor n}}\rangle}
-    B\tensor (A \sequoid\blank)^k(A\sequoid A^{\tensor n})^{n+1}
-    \xrightarrow{\langle B\tensor (A\sequoid\blank)^k;\pr_i\rangle}
-    (B\tensor(A \sequoid\blank)^{k+1} A^{\tensor n})^{n+1}
-    \to
-    (B\tensor A ^{\sequoid (k + n + 1)})^{(n+1)!}\,,
-  \end{mathpar}
-  where the last arrow is the tensor product of $B$ with the $(n+1)$-th power of the composite given by
-  \footnotesize
-  \[
-    (A \sequoid\blank)^{k+1}A^{\tensor n}
-    \xrightarrow{\langle (A \sequoid \blank)^{k+1}\sym^\sigma\rangle}
-    ((A \sequoid\blank)^{k+1}A^{\tensor n})^{n!}
-    \xrightarrow{((A \sequoid\blank)^{k+1}\wk^n)^{n!}}
-    (A^{\sequoid (k+n+1)})^{n!}\,,
-    \]
-  \normalsize
-  which is a monomorphism by the induction hypothesis.
-  Then the previous composite is the composite of monomorphisms (by our assumptions on $\C$), and is therefore itself a monomorphism.  
-  Now this composite may be written as
-  \[
-    \langle B\tensor(A\sequoid\blank)^k(\sym_i^{n+1};\wk_{A,A^{\tensor n}};(A\sequoid\sym^\sigma);(A\sequoid\wk^n)) \rangle\,,
-    \]
-  which, since $\wk$ is a natural transformation, is equal to
-  \[
-    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A\tensor\sym^\sigma);(A\tensor\wk^n);\wk_{A,A^{\sequoid n}})\rangle\,,
-    \]
-  where $\sigma$ ranges over the permutations in $\S_n$.
-  Moreover, by the definition of $\wk^n$, this is equal to
-  \[
-    \langle B\tensor(A \sequoid\blank)^k(\sym_i^{n+1};(A \tensor \sym^\sigma);\wk^{n+1}\rangle\,.
-    \]
-
-  Now, given $i\in\{1,\cdots n+1\}$ and $\sigma\in\S_n$, there is a unique permutation $\pi\in\S_{n+1}$ such that $\sym_i^{n+1};(A\tensor\sym^\sigma=\sym^\pi)$; moreover, this defines a bijection from $\{1,\cdots,n+1\}\times\S_n \to \S_{n+1}$.
-  Therefore (after choosing an appropriate enumeration of our permutations), we see that this composite is in fact equal to
-  \[
-    \langle B\tensor(A \sequoid\blank)^k (\sym^\pi;\wk^{n+1})\rangle\,.
-    \]
-  Therefore, $\langle B\tensor(A \sequoid\blank)^k(\sym^\pi;\wk^{n+1})\rangle$ is a monomorphism as desired, completing the induction.
-
-  Next, we define morphisms $\eq_n\from A^{\sequoid n} \to A^{\tensor n}$ inductively, where $\eq_0=\id$ and $\eq_{n+1}$ is defined by the following composite
-  \[
-    A^{\sequoid (n+1)} = A\sequoid A^{\sequoid n} \xrightarrow{\langle (A\sequoid \eq_n)_1^n\rangle} (A \sequoid A^{\tensor n})^n \cong A^{\tensor (n+1)}\,,
-    \]
-  where the final isomorphism is as in Propositions \ref{PropDecSeq} and \ref{PropDecSeqFormula}.
-
-  First, we show inductively that $\eq_n;\sym^\pi;\wk^n=\id_{A^{\sequoid n}}$ for all permutations $\pi$ of $S_n$.
-  This is certainly true for $n=0$; in the general case, let $\pi\in \S_{n+1}$ be a permutation.  
-  Let $j=\pi\inv(1)$ be the element sent to $1$ by $\pi$ and let $\sigma$ be the permutation of $1,\cdots,n$ such that applying $\sigma$ to the elements $2,\cdots,n+1$ and composing with $\pi$ gives us the $j$-cycle $(1\,\dots\,j)$.
-  Then we have
-  \[
-    \sym_j^{n+1};(A\tensor\sym^\sigma) = \sym^\pi\,.
-    \]
-  Now we get
-  \begin{IEEEeqnarray*}{Cl}
-    & \eq_{n+1};\sym^\pi;\wk^{n+1} \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym^\pi;(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};(A\tensor\sym^\sigma);(A \tensor \wk^n);\wk_{A,A^{\sequoid n}} \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\sym_j^{n+1};\wk_{A,A^{\tensor n}};(A \sequoid \sym^\sigma);(A \sequoid \wk^n) \\
-    = & \langle (A \sequoid \eq_n)_1^n\rangle;(\dec_{\vec A}^{n+1})\inv;\langle \sym_i^{n+1};\wk_{A,A^{\tensor n}}\rangle;\pr_j;(A \sequoid \sym^\sigma);(A \sequoid \wk^n) \\
-    = & A \sequoid (\eq_n;\sym^\sigma;\wk^n)\,,
-  \end{IEEEeqnarray*}
-  which is equal to the identity on $A^{\sequoid (n+1)}$ by the induction hypothesis.
-
-  Now let $\rho$ be a permutation in $\S_n$.  
-  We claim that $\eq_n=\eq_n;\sym^{\rho}$.
-
-  Indeed, we have
-  \begin{IEEEeqnarray*}{rCl}
-    \eq_n;\langle \sym^{\pi} ; \wk^n \rangle
-    & = & \langle \eq_n;\sym^{\pi};\wk^n \rangle \\
-    & = & \langle \id \rangle \\
-    & = & \langle \eq_n;\sym^{\rho\pi};\wk^n \rangle \\
-    & = & \eq_n;\sym^{\rho};\langle \sym^\pi ; \wk^n \rangle\,.
-  \end{IEEEeqnarray*}
-  Since $\langle \sym^\pi;\wk^n\rangle$ is a monomorphism, this means that $\eq_n=\eq_n;\sym^{\rho}$, as desired.
-  Therefore, $\eq_n$ equalizes the morphisms $\eq_n$.  
-  We claim that it is an equalizer, and that this equalizer is preserved by the tensor product.
-
-  Indeed, let $B,C$ be objects of $\C$, and let $f \from C \to B \tensor A^{\tensor n}$ be a morphism such that $f=f;(B\tensor\sym^{\pi})$ for all $\pi\in\S_n$.
-
-  Let $\tilde f = f;(B \tensor \wk^n)\from C \to B \tensor A^{\sequoid n}$.  
-  We claim that $\tilde f;(B\tensor\eq_n)=f$; indeed, we have
-  \begin{IEEEeqnarray*}{rCl}
-    \tilde f;(B \tensor\eq_n);\langle B\tensor(\sym^\pi;\wk^n)\rangle 
-    & = & \langle f;(B \tensor (\wk^n;\eq_n;\sym^\pi;\wk^n)) \rangle \\
-    & = & \langle f;(B\tensor \wk^n)\rangle \\
-    & = & f;\langle B \tensor (\sym^\pi;\wk^n)\rangle\,.
-  \end{IEEEeqnarray*}
-  Therefore, since $\langle B \tensor (\sym^\pi;\wk^n)\rangle$ is a monomorphism, we know that $\tilde f;(B\tensor \eq_n)=f$.
-
-  Now suppose that $h\from C \to B \tensor A^{\sequoid n}$ is such that $h;(B\tensor eq_n)=f$.  
-  We claim that $h=\tilde f$.  
-  Indeed, we have 
-  \[
-    \tilde f = f;(B \tensor \wk^n) = h;(B \tensor \eq_n);(B \tensor \wk^n) = h\,.
-    \]
-  Therefore, $(B\tensor A^{\sequoid n},B\tensor \eq_n)$ is an equalizer of the arrows $B\tensor \sym^\pi\from B \tensor A^{\tensor n} \to B \tensor A^{\tensor n}$, as desired.
-\end{proof}
-
-We are interested in symmetrized tensor powers because of an important result of \Mellies, Tabareau and Tasson.
-Suppose $\C$ is a monoidal category, and that $\C$ has symmetrized tensor powers that commute with the tensor product.  
-Given $n$, we have a morphism
-\[
-  A^{\tensor n}\tensor() \from A^{\tensor (n+1)} \to A^{\tensor n}\,,
-  \]
-where $()$ is the unique morphism into the terminal object.  
-Then, if $A^n$ and $A^{n+1}$ are the $n$-th and $n+1$-th symmetrized tensor powers of $A$, and $\eq_{n+1},\eq$ the corresponding equalization, for any $\pi\in\S_n$ we have a commutative diagram
-\[
-  \begin{tikzcd}[column sep=50pt]
-    B \tensor A^{n+1} \arrow[r, "B\tensor\eq_{n+1}"]
-      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor A^{\tensor n}\tensor()"] \arrow[d, "\sym^{\pi'}"']
-        & B \tensor A^{\tensor n} \arrow[d, "\sym^\pi"] \\
-    %
-      & B \tensor A^{\tensor (n+1)} \arrow[r, "B\tensor A^{\tensor n} \tensor()"]
-        & B \tensor A^{\tensor n}
-  \end{tikzcd}\,,
-  \]
-where $\pi'$ is the permutation of $1,\cdots,n+1$ that fixes $1$ and applies $\pi$ to the remaining elements $2,\cdots,n+1$.
-
-This means that for each $\pi\in \S_n$ we have
-\begin{IEEEeqnarray*}{rCl}
-  (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor ())
-  & = & (B \tensor\eq_{n+1});(B\tensor \sym^{\pi'});(B\tensor A^{\tensor n}\tensor ()) \\
-  & = & (B\tensor\eq_{n+1});(B\tensor A^{\tensor n}\tensor());(B\tensor \sym^\pi)\,,
-\end{IEEEeqnarray*}
-and that there is therefore an induced morphism
-\[
-  B\tensor A^{n+1} \to B \tensor A^n\,,
-  \]
-by the universal property of the equalizer.
-
-Note also that if $m,n$ are integers, then any permutations $\sigma$ of $1,\cdots,m$ and $\pi$ of $1,\cdots,n$ induce a permutation $[\sigma,\pi]$ of $1,\cdots,m+n$.  
-Then we get morphisms
-\[
-  A^{m+n} \to A^{\tensor (m+n)} \to A^{\tensor m} \tensor A^{\tensor n}\,,
-  \]
-which are equalized by all symmetries on $A^{\tensor m}$ and $A^{\tensor n}$ individually.  
-Since the equalizers $A^m$ and $A^n$ are preserved by the tensor product, then we get an induced morphisms
-\[
-  A^{m+n}\to A^m\tensor A^n\,.
-  \]
-
-\begin{theorem}[\cite{MelliesCofCommCom}]
-  Let $\C$ be a monoidal category such that the monoidal unit for $\C$ is a terminal object.
-  Suppose that $\C$ has symmetrized tensor powers that commute with the tensor product.
-
-  Then, for any objects $A,B$ of $\C$, there is a natural sequence
-  \[
-    B \leftarrow B\tensor A \leftarrow B\tensor A^2 \leftarrow B \tensor A^3 \leftarrow \cdots\,.
-    \]
-  In particular, there is a sequence
-  \[
-    I \leftarrow A \leftarrow A^2 \leftarrow A^3 \leftarrow \cdots\,.
-    \]
-  Suppose that this sequence has a limit $\oc A$, and that $B\tensor \oc A$ is the limit of the first sequence for all $B$.
-
-  For each $m$, we can define morphisms
-  \[
-    \oc A \to A^{m+n} \to A^m \tensor A^n
-    \]
-  for each $n$, which commute with the morphisms $A^{n+1}\to A^n$ and hence induce a morphism $\oc A \to A^m \tensor \oc A$.  
-  Then these morphisms themselves commute with the morphisms $A^{m+1}\tensor \oc A \to A^m \tensor \oc A$, and so we get a morphism $\mu_A\from \oc A \to \oc A \tensor \oc A$.
-
-  The morphisms $\mu_A\from \oc A \to \oc A \tensor \oc A$ and $()\from A \to I$ give $\oc A$ the structure of a commutative comonoid in $\C$.  
-  In fact, this is the \emph{cofree commutative comonoid} over $A$ in $\C$.  
-  The counit $\der_A\from \oc A \to A$ of the adjunction is the map in the limiting cone.
-  \label{TheMtt}
-\end{theorem}
-
-We want to show that this theorem applies in $\G$.
-First, we find an explicit formula for the morphisms $B \tensor A^{\sequoid(n+1)}\to B\tensor A^{\sequoid n}$.
-
-\begin{proposition}
-  Let $\C$ be an inclusive, strongly distributive, decomposable sequoidal category -- so $\G$ has symmetrized tensor powers preserved by the tensor product as in Proposition \ref{PropSequoidPower}.
-
-  Then the canonical morphisms $B \tensor A^{\sequoid (n+1)}\to B\tensor A^{\sequoid n}$ are given by
-  \[
-    B \tensor (A \sequoid \blank)^n()\,,
-    \]
-  where $() \from A \to I$ is the unique morphism into the terminal object.
-\end{proposition}
-\begin{proof}
-  First, we show by induction on $n$ that the following diagram commutes.
-  \[
-    \begin{tikzcd}[column sep=30pt]
-      A^{\tensor(n+1)} \arrow[r, "A^{\tensor n}\tensor()"] \arrow[d, "A\tensor\wk^{n+1}"']
-        & A^{\tensor n} \arrow[d, "\wk^n"] \\
-      A^{\sequoid(n+1)} \arrow[r, "(A\sequoid\blank)^n()"]
-        & A^{\sequoid n}
-    \end{tikzcd}
-    \]
-  This is clearly true for $n=0$; in the general case, we have the following commutative diagram --
-  \[
-    \begin{tikzcd}[column sep=41pt]
-      A^{\tensor(n+2)} \arrow[r] \arrow[dd, "\wk^{n+2}"']
-        & A \tensor A^{\tensor (n+1)} \arrow[r, "A \tensor (A^{\tensor n}\tensor ())"] \arrow[d, "A \tensor \wk^{n+1}"']
-          & A \tensor A^{\tensor n} \arrow[r] \arrow[d, "A\tensor \wk^n"]
-            & A^{\tensor(n+1)} \arrow[dd, "\wk^{n+1}"] \\
-      %
-        & A \tensor A^{\sequoid (n+1)} \arrow[r, "A \tensor (A\sequoid\blank)^n()"] \arrow[dl, "{\wk_{A,A^{\sequoid (n+1)}}}" description]
-          & A \tensor A^{\sequoid n} \arrow[dr, "{\wk_{A,A^{\sequoid n}}}" description]
-            & \\
-      A^{\sequoid(n+1)} \arrow[rrr, "(A \sequoid \blank)^{n+1}()"]
-        &
-          &
-            & A^{\sequoid (n+1)}
-    \end{tikzcd}\,\text{--}
-    \]
-  where the middle square is the inductive hypothesis (tensored by $A$), the outer trapezia are the definitions of $\wk^{n+2}$ and $\wk^{n+1}$, and the bottom trapezium commutes because $\wk$ is a natural transformation.
-
-  Now, by the proof of Proposition \ref{PropSequoidPower}, the canonical morphism $B\tensor A^{\sequoid (n+1)} \to B\tensor A^{\sequoid n}$ must be constructed as the composite
-  \[
-    B \tensor (\eq_{n+1};(A^{\tensor n}\tensor ());\wk^n)\,,
-    \]
-  which we have shown is equal to
-  \[
-    B \tensor (\eq_{n+1};\wk^{n+1};(A \sequoid\blank)^n()) = B \tensor (A \sequoid\blank)^n()\,.\qedhere
-    \]
-\end{proof}
-
-\begin{definition}
-  Let $A$ be a game.  
-  We say that $A$ is \emph{well-opened} if initial moves of $A$ can only occur as the very first move in a play.
-\end{definition}
-
-It is immediate from the definitions that:
-\begin{itemize}
-  \item the empty game $I$ and our data-type games $\bC,\bB,\bN$ are well opened;
-  \item if $A_i$ are well-opened games, then so is $\prod_iA_i$; and
-  \item if $B$ is a well-opened game, then so is $A \implies B$;
-\end{itemize}
-but that $A \tensor B$, $A\sequoid B$ and $\oc A$ are not in general well-opened, even if $A$ and $B$ are.
-
-\begin{proposition}
-  Let $A$ be a well-opened game.  
-  Then we have natural morphisms
-  \[
-    \oc A \to A^{\sequoid n}
-    \]
-  for each $n$, and these commute with the natural morphisms $A^{\sequoid(n+1)}\to A^{\sequoid n}$ and make $\oc A$ the limit of the sequence
-  \[
-    I \leftarrow A \leftarrow A^{\sequoid 2} \leftarrow A^{\sequoid 3}\leftarrow\cdots\,.
-    \]
-  Moreover, $B\tensor\oc A$ is the limit of the sequence
-  \[
-    B \leftarrow B \tensor A \leftarrow B \tensor A^{\sequoid 2} \leftarrow B \tensor A^{\sequoid 3}\leftarrow \cdots\,.
-    \]
-\end{proposition}
-\begin{proof}
-  For the sake of notational simplicity, we will only prove the first part of the Proposition, but the second part (the $B\tensor\cdots$ version) goes through in exactly the same way.
-
-  The morphism in question is the (non-innocent) zigzag strategy given by the tree immersion $\phi_n\from P_{A^{\sequoid n}}\to P_{\oc A}$ defined by
-  \[
-    \phi_n(s) = \nabla_*(s)\,,
-    \]
-  where $\nabla\from M_A+\cdots + M_A$ is the co-diagonal.
-
-  We have seen already that the natural morphism $A^{\sequoid (n+1)}\to A^{\sequoid n}$ is the copycat morphism generated by the inclusion $n.(M_A) \to (n+1).(M_A)$, and so it is clear that these commute with $\zz_\phi$ by Proposition \ref{PropTree}.
-
-  Now let $C$ be a game and suppose that there are strategies $\sigma_n \from C \implies A^{\sequoid n}$ that commute with the natural morphisms $A^{\sequoid (n+1)} \to A^{\sequoid n}$.  
-  Then we define a morphism $\sigma\from C \to \oc A$ by
-  \[
-    \sigma = \left\{s\in P_{C\implies \oc A} \,\middle|\, \mbox{\pbox{\textwidth}{
-      for some $n$, $s\vert_{\oc A}$ contains \\
-      at most $n$ initial moves, and \\
-      $[\inj,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\in\sigma_n$.}}\right\}\,.
-    \]
-  Here we have used the fact that $A$ is well-opened to tell us that $s\vert_{\oc A}$ is indeed a valid play in $A^{\sequoid n}$.
-
-  We claim that $\sigma$ is indeed a strategy.
-  First we show that $\sigma$ is prefix closed.  
-  If $s\in \sigma$ and $t\prefix s$, write $n$ for the number of initial moves in $s$.  
-  Then $t$ has at most $n$ initial moves; if $[\id_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\in\sigma_n$, then $[\id_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(t)\in\sigma_n$, and therefore $t\in\sigma$.
-
-  Now note that if $s\in C_{C\implies \oc A}$ is such that $s\vert_{\oc A}$ contains $k$ initial moves, and if $m,n\ge k$, then
-  \[
-    [\inj,\inj_{A_1},\cdots,\inj_{A_m}]_*(s) = [\inj_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\,,
-    \]
-  since the $\sigma_n$ commute with the natural morphisms $A^{\sequoid (n+1)} \to A^{\sequoid n}$.  
-  So, if $sab,sac\in\sigma$, then we can assume that
-  \[
-    [\inj_C,\inj_{A_1},\cdots,\inj_{A_k}]_*(sab),[\inj_C,\inj_{A_1},\cdots,\inj_{A_k}]_*(sac)\in\sigma_k
-  \]
-  for some common $k$, and therefore that $b=c$.
-
-  Now we have $\sigma;\zz_{\phi_n}=\sigma_n$ for each $n$ by Proposition \ref{PropTree}.
-
-  Suppose that $\tau$ is some other strategy for $C\implies \oc A$ such that $\tau;\zz_{\phi_n}=\sigma_n$ for each $n$.  
-  By Proposition \ref{PropTree}, we have
-  \[
-    \sigma_n = \tau;\zz_{\phi_n} = \{s\in P_{C\implies A^{\sequoid n}}\suchthat s^{\phi_n}\in\tau\}\,.
-    \]
-  Suppose $s\in\sigma$ and that $s$ contains $n$ initial moves.  
-  Then 
-  \[
-    [\inj_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s)\in\sigma_n
-    \]
-  for some $n$.  
-  Therefore, $s=([\inj_C,\inj_{A_1},\cdots,\inj_{A_n}]_*(s))^{\phi_n}\in\tau$.  
-  So $\sigma\subset\tau$.
-
-  Conversely, suppose that $t\in\tau$.  
-  Suppose that $t\vert_{\oc A}$ contains $n$ initial moves.  
-  Then $t=s^{\phi_n}$ for some sequence $s\in P_{C\implies A^{\sequoid n}}$, and we must have $s\in\sigma_n$.  
-  Therefore, $t\in\sigma$.  
-  So $\tau\subset\sigma$.
-\end{proof}
-
-Therefore, by Theorem \ref{TheMtt}, if $A$ is a well-opened game, then $\oc A$ inherits the structure of a cofree commutative comonoid on $A$.
-
-Let $\G_{wo}$ denote the category of well-opened games and strategies.  
-Let $\CCom(\G)$ denote the category of commutative comonoids with respect to the symmetric monoidal structure on $\G$.
-
-In general, given two commutative comonoids $M,N$ in a symmetric monoidal category $\C$, we can form the \emph{tensor product}
-\begin{mathpar}
-  M \tensor N \to (M \tensor M) \tensor (N \tensor N) \to (M \tensor N) \tensor (M \tensor N)
-  \and
-  M \tensor N \to I \tensor I \to I\,,
-\end{mathpar}
-and this makes $\CCom(\C)$ into a \emph{Cartesian} category.
-
-Now note that we have defined a functor
-\[
-  \G_{wo} \to \CCom(\G)
-  \]
-which is a right adjoint on to its image, and therefore preserves products.  
-So if $A,B$ are well-opened games, then we get a natural isomorphism of comonoids between the tensor product of the comonoids on $\oc A$ and $\oc B$ and the comonoid on $\oc(A\times B)$.
-In particular, we have a natural isomorphism
-\[
-  \oc A \tensor \oc B \cong \oc (A \times B)\,.
-  \]
-We define a category $\G_{wo}^{\oc}$ to be the image of the functor $\G_{wo}\to \CCom(\G)$ inside $\CCom(\G)$.  
-By our discussion above, $\G_{wo}^{\oc}$ is a Cartesian category.
-
-A more convenient description of $\G_{wo}^{\oc}$ is that it is the category where the objects are well-opened games and where the morphisms
-\[
-  A \to B
-  \]
-are morphisms $\oc A \to B$ in the original category $\G$.
-We compose two such morphisms $\sigma \from \oc A \implies B$ and $\tau \from \oc B \implies C$ as
-\[
-  \oc A \xrightarrow{\sigma^\dag} \oc B \xrightarrow{\tau} C\,,
-  \]
-where the \emph{promotion} $\sigma^\dag$ of $\sigma$ comes from the description of $\oc A$ as the cofree commutative comonoid on $A$.
-
-Since the functor $\G_{wo}\to \CCom(\G)$ preserves products, $\G_{wo}^{\oc}$ obtains a Cartesian structure given by the category-theoretic product $\times$.  
-We claim that it is Cartesian closed, with the function object from $A$ to $B$ given by $\oc A \implies B$.  
-Indeed, we have
-\begin{IEEEeqnarray*}{rCl}
-  \G_{wo}^{\oc}(A,\oc B\implies C)
-  & \cong & \G(\oc A,\oc B \implies C) \\
-  & \cong & \G(\oc A \tensor \oc B,C) \\
-  & \cong & \G(\oc(A \times B),C) \\
-  & \cong & \G_{wo}^{\oc}(A\times B,C)\,.
-\end{IEEEeqnarray*}
-
-We have one thing left to prove.
-\begin{proposition}
-  Let $\sigma\from \oc A \implies B$, $\tau\from \oc B \implies C$ be innocent strategies, where $A,B,C$ are well-opened games.  
-  Then the composite of $\sigma$ and $\tau$ in $\G_{wo}^{\oc}$ is an innocent strategy.
-\end{proposition}
-\begin{proof}
-  We may write this composite as
-  \[
-    \oc A \xrightarrow{m}
-    \oc \oc A \xrightarrow{\oc\sigma}
-    \oc B \xrightarrow{\tau}\,,
-    \]
-  where $\oc\sigma$ is the strategy formed by playing $\sigma$ in parallel with itself, whereas $m\from \oc A \to \oc \oc A$ comes from the fact that $\oc A$ is the cofree commutative comonoid on $A$.
-  $\oc \sigma$ is innocent for the same reasons as in Proposition \ref{PropTensorInnocent}, so it suffices to show that $m$ is innocent.
-
-  Indeed, it is clear from our definitions that $\oc\oc A = \oc A$ as games.  
-  Then, $m$ is in fact the identity strategy between these two games, so is innocent.
-\end{proof}
-
-\section{The Exponential as a Final Coalgebra}
-
-\begin{definition}
-  Let $F \from \C \to \C$ be a functor.  
-  A \emph{coalgebra for $F$} or \emph{$F$-coalgebra} is an object $a$ of $\C$, together with a morphism $f\from a \to Fa$.
-
-  A \emph{coalgebra homomorphism} from $(a,f)$ to $(b,g)$ is a morphism $h\from a \to b$ such that the following diagram commutes.
-  \[
-    \begin{tikzcd}
-      a \arrow[r, "f"] \arrow[d, "h"']
-        & Fa \arrow[d, "Fh"] \\
-      b \arrow[r, "g"]
-        & Fb
-    \end{tikzcd}
-    \]
-
-  Clearly, the coalgebras for a given functor $F$ form a category.  
-  A \emph{final coalgebra} for $F$ is a terminal object for this category; i.e., an $F$-coalgebra $(t,\alpha)$ such that for all $F$-coalgebras $(a,f)$ there is a unique morphism $\fcoal f \from a \to t$ such that the following diagram commutes.
-  \[
-    \begin{tikzcd}
-      a \arrow[r, "f"] \arrow[d, "\fcoal f"']
-        & Fa \arrow[d, "F\fcoal f"] \\
-      t \arrow[r, "\alpha"]
-        & Ft
-    \end{tikzcd}
-    \]
-\end{definition}
-We call $\fcoal f$ the \emph{anamorphism} of $f$.
-
-We use two standard pieces of theory about coalgebras.
-
-\begin{theorem}[Lambek's Theorem, \cite{Lambek}]
-  If $(t,\alpha)$ is a final coalgebra for a functor $F$, then $\alpha\from t \to Ft$ is an isomorphism with inverse given by $\fcoal{F\alpha}$.
-\end{theorem}
-
-\begin{theorem}[Ad{\'{a}}mek's Theorem, {\cite{Adamek}}]
-  Suppose $\C$ has a terminal object $1$.  
-  By repeatedly applying $F$ to the morphism $F1 \to 1$, we build up a sequence
-  \[
-    1 \leftarrow F1 \leftarrow F^2 1 \leftarrow F^31 \leftarrow \cdots\,.
-    \]
-  If this sequence has a limit $F^{\omega}1$, and if the morphism $\beta\from F(F^{\omega}1) \to F^{\omega}1$ induced from the universal property of the limit is an isomorphism, then $(F^{\omega}1,\beta\inv)$ is a final coalgebra for $F$.
-\end{theorem}
-
-Now we have already shown that if $A$ is well-opened, then $\oc A$ is the limit of the sequence
-\[
-  I \leftarrow A \leftarrow A^{\sequoid 2} \leftarrow A^{\sequoid 3} \leftarrow \cdots\,,
-  \]
-and this sequence is precisely the sequence from Ad{\'a}mek's Theorem, when $F=J(A\sequoid\blank) \from \G \to \G$.
-Moreover, this limit is preserved when taking the sequoid with $A$ on the left, and so we get that
-\begin{corollary}
-  If $A$ is a well-opened game, then $\oc A$ is the final coalgebra for the functor $A \sequoid \blank$.
-\end{corollary}
-In this case, the morphism $\oc A \to A \sequoid \oc A$ is the zigzag strategy that plays copycat between the different copies of $A$; i.e., $\zz_\phi$, where $\phi\from P_{A\sequoid \oc A} \to P_{\oc A}$ is the tree isomorphism given by
-\[
-  \phi(s) = [\inj_{M_A},\id]_*(s)\,.
-  \]
-
-One small thing we need to do is to relate the two structures on the exponential.
-
-\begin{proposition}
-  The final coalgebra
-  \[
-    \alpha\from \oc A \to A \sequoid \oc A
-    \]
-  is given by the composite
-  \[
-    \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A \xrightarrow{\der_A\tensor \oc A} A \tensor \oc A \xrightarrow{\wk_A,\oc A} A \sequoid \oc A\,.
-    \]
-  \label{PropFormulaForAlpha}
-\end{proposition}
-\begin{proof}
-  By Theorem \ref{TheMtt}, we can tell that this composite is a copycat strategy between $\oc A$ and $A \sequoid \oc A$, as is $\alpha$.  
-  Since $A$ is well-opened, there is a unique such strategy.
-\end{proof}
-
-\section{Denotational Semantics of Idealized Algol}
-
-We now come to interpret Idealized Algol within our category $\G_{wo}^{\oc}$.  
-The base types $\com$, $\bool$ and $\nat$ are interpreted by the games $\bC$, $\bB$ and $\bN$, while the type $\Var$ is interpreted by the game
-\[
-  \Varr = \bC^{\bN} \times \bN\,,
-  \]
-where $\bC^{\bN}$ is the product of $\bN$-many copies of $\bC$.
-Given types $S,T$, the denotation $\deno{S\to T}$ of the type of functions from $S$ to $T$ is given by
-\[
-  \deno{S}\to\deno{T} \coloneqq \oc\deno{S}\implies\deno{T}\,.
-  \]
-This gives us the denotation of the types of Idealized Algol.
-
-We inductively define a denotation of terms-in-context $\Gamma\ts M$ of IA, where $\deno{x_1\from T_1,\cdots,x_n\from T_n\ts M\from T}$ is a strategy
-\[
-  \deno{T_1} \times \cdots \times \deno{T_n} \to \deno{T}\,.
-  \]
-First note that we have natural innocent strategies $a \from \bC$, $\true,\false\from\bB$ and $n \from \bN$, which give us the denotations of $\Gamma\ts\skipp$, $\Gamma\ts\true$, $\Gamma\ts\false$ and $\Gamma\ts n$.
-
-Moreover, if we have a strategy
-
-\[
-  \deno{\Gamma,x\from S \ts M\from T} \from \deno{\Gamma}\times\deno{S} \to \deno{T}\,,
-  \]
-then, since $\G_{wo}^{\oc}$ is Cartesian closed, we get a strategy
-\[
-  \deno{\Gamma\ts \lambda x^s.M} \from \deno{\Gamma} \to \deno {S} \to \deno{T}\,.
-  \]
-In addition, we have natural morphisms
-\[
-  \deno{\Gamma,x\from T\ts x\from T} = \deno{\Gamma}\times\deno{T} \xrightarrow{\pr_{\deno{T}}} \deno{T}\,.
-  \]
-Lastly, if we have strategies
-\begin{mathpar}
-  \deno{\Gamma\ts M\from S \to T} \from \deno{\Gamma} \to \deno{S} \to \deno{T}
-  \and
-  \deno{\Gamma\ts N \from S} \from \deno{\Gamma} \to \deno{S}\,,
-\end{mathpar}
-then we get a strategy
-\[
-  \deno{\Gamma\ts MN\from T} = \deno \Gamma \xrightarrow{\Delta} \deno\Gamma\times\deno\Gamma \xrightarrow{\deno{\Gamma\ts M}\times\deno{\Gamma\ts N}} (\deno S \to \deno T) \times \deno S \xrightarrow{\ev} \deno{S}\,.
-  \]
-
-In order to form the denotation of the next lot of terms, we need a new definition.
-\begin{definition}
-  Let $X$ be a set, and let $(\sigma_x\suchthat x\in X)$ be a collection of strategies for a game $A$.  
-  Write $X$ for the datatype game corresponding to $X$.  
-  Then we define a strict strategy $(\sigma_x) \from X \to A$ by
-  \[
-    (\sigma_x) = \{\epsilon\}\cup\{*q\suchthat {*}\in P_A\}\cup \{*qys\suchthat {*}s\in\sigma_y\}\,.
-    \]
-  In other words, after the initial move in $A$, $(\sigma_x)$ requests some element $y\in X$, and thereafter plays according to $\sigma_y$ in $A$.
-\end{definition}
-
-\begin{proposition}
-  If the $\sigma_x$ are innocent strategies, then $(\sigma_x)$ is an innocent strategy.
-\end{proposition}
-\begin{proof}
-  If $*s\in\sigma_y$, then $\pv{*qysa}=*qy\pv{sa}$.  
-  Then, if $t\in(\sigma_x)$ and $\pv{ta}=*qy\pv{sa}$, we have $t=*qyt'$ for $t'\in\sigma_y$ and $\pv{*t'a}=\pv{*sa}$.  
-  So if $*sab\in\sigma_y$, then $*t'ab\in\sigma_y$ and therefore $tab\in(\sigma_x)$.
-\end{proof}
-
-The most important feature of strategies of the form $(\sigma_x)$ is the most obvious one: given $X$, and $y\in X$, we have a strategy $y$ for the game $X$ with maximal play $qx$.  
-Then $y;(\sigma_x) = \sigma_y$.
-
-Now we define morphisms
-\begin{itemize}
-  \item $\seq_X = (\id_X) \from \bC \to (X \to X)$;
-  \item $\If_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y) \from \bB \to (X \to X \to X)$;
-  \item $\suc = (1, 2, 3, 4,\cdots) \from \bN \to \bN$;
-  \item $\pred = (0,0,1,2,\cdots)\from \bN \to \bN$;
-  \item $\IfO_X = (\lambda x.\lambda y.x,\lambda x.\lambda y.y,\lambda x.\lambda y.y,\cdots)\from \bN \to (X \to X \to X)$;
-  \item $\assign = (\pr_0,\pr_1,\cdots) \from \bN \to (\Varr \to \bC)$; and
-  \item $\dereff = \pr_\bN \from \Varr \to \bN$;
-  \item $\mkvar = \lambda w.\lambda r.\langle (w\,n)_{n\in\bN},r\rangle \from (\bN \to \bC) \to \bN \to \Varr$.
-\end{itemize}
-These give us an obvious way to interpret most of the rest of the terms of Idealized Algol.  
-For example, if we have strategies
-\begin{mathpar}
-  \deno{\Gamma\ts V\from \Varr}
-  \and
-  \deno{\Gamma\ts E\from \bN}\,,
-\end{mathpar}
-then we get a strategy
-\[
-  \deno{\Gamma\ts V\gets E \from \bC} = \deno{\Gamma} \xrightarrow{\Delta} \deno{\Gamma}\times\deno{\Gamma} \xrightarrow{\deno{\Gamma\ts E}\times\deno{\Gamma\ts V}} \bN \times \Varr \xrightarrow{\assign} \bC\,.
-  \]
-
-\section{Order-Enrichment of $\G$}
-
-The remaining parts of Idealized Algol that we have yet to define are the fixpoint combinator $\Y_T$ and the new variable constructor $\neww$.
-
-To define $\Y_T$, we use order-enriched properties of $\G$.
-
-Note that if $A$ is a game, then we can order the strategies for $A$ by subset inclusion.  
-Then this order is clearly preserved by composition.
-
-\begin{proposition}
-  The partial order of strategies for $A$, ordered by inclusion, is directed-complete.  
-  So is the partial order of innocent strategies for $A$.
-\end{proposition}
-\begin{proof}
-  Let $\Sigma$ be a directed set of strategies for $A$; so if $\sigma,\tau\in\Sigma$ then there is some $\upsilon\in\Sigma$ such that $\sigma\subset\upsilon$ and $\tau\subset\upsilon$.  
-  We claim that $\bigcup\Sigma$ is a strategy for $A$.  
-  Indeed, it is certainly even-prefix-closed, and if $sab,sac\in\Sigma$, then $sab\in\sigma$ and $sac\in\tau$ for $\sigma,\tau\in\Sigma$, and therefore $sab,sac\in\upsilon$ for some $\upsilon\in\Sigma$ and so $b=c$.
-
-  Now suppose that all $\sigma\in\Sigma$ are innocent.
-  Let $sab\in\bigcup\Sigma$ and suppose that $t\in \bigcup\Sigma$ is such that $\pv{ta}=\pv{sa}$.  
-  Then, as before, we have $sab,t\in\upsilon$ for some innocent $\upsilon\in\Sigma$, and therefore $tab\in\upsilon\subset\bigcup\Sigma$.
-\end{proof}
-
-It is clear then that composition of strategies is Scott-continuous with respect to this ordering.
-
-Writing $\bot = \{\epsilon\}$ for the bottom strategy for a game $A$, if we have a strategy $\sigma\from A \to A$, then the Kleene fixed point theorem tells us that we may construct a fixed point for $\sigma$ as the union of the chain
-\[
-  \bot \subset \bot;\sigma \subset \bot;\sigma;\sigma \subset \cdots\,.
-  \]
-Given a game $A$, we define a strategy $\Y_A\from (A \to A) \to A$ as the fixed point of the strategy
-\[
-  \lambda F.\lambda f.f(Ff) \from ((A \to A) \to A) \to (A \to A) \to A\,.
-  \]
-We can then use $\Y_A$ to interpret the term $\Gamma\ts\Y_TM\from T$ for any term $\Gamma\ts M\from T\to T$.
-
-We will later require other order-theoretic properties of the set of strategies for a game $A$.  
-Recall that an element $\sigma$ of a directed-complete partially ordered set is called \emph{compact} if whenever we have $\sigma = \bigcup\Sigma$ for some directed set $\Sigma$, then $\sigma\in\Sigma$.
-
-A little thought convinces us that a strategy $\sigma\from A$ is compact if and only if it is finite as a set of plays; indeed, suppose $\sigma$ is a finite set and $\sigma=\bigcup\Sigma$.  
-For each $s\in\sigma$, we have $s\in\tau_s$ for some $\tau_s\in\Sigma$; since $\Sigma$ is directed, then there is some $\upsilon\in\Sigma$ such that $\tau_s\in\Sigma$ for each $s$, and therefore $\sigma\subset\upsilon\subset\sigma$.
-Conversely, if $\sigma$ is infinite, then by K\"{o}nig's lemma, it either has an infinite branching point (i.e., $s\in\sigma$ such that there are infinitely many plays $sab\in\sigma$) or an infinite branch (i.e., an infinite increasing sequence $s_1\prefix s_2\prefix \cdots$ in $\sigma$).
-In either case, it is easy to construct some directed set $\Sigma$ such that $\sigma=\bigcup\Sigma$ but $\sigma\not\in\Sigma$.
-
-Recall that a directed-complete partial order $P$ is said to be \emph{algebraic} if whenever $p\in P$, the set of compact elements of $P$ lying below $p$ is directed and its supremum is $p$.
-
-\begin{proposition}
-  The set of strategies for a game $A$ is an algebraic directed-complete partial order.
-\end{proposition}
-\begin{proof}
-  Let $\sigma$ be a strategy for a game $A$ and let $\tau_1,\tau_2$ be two finite sub-strategies such that $\tau_1,\tau_2\subset\sigma$.  
-  Then $\tau_1\cup\tau_2\subset\sigma$ and is finite; moreover, if $sab,sac\in\tau_1\cup\tau_2$, then $sab,sac\in\sigma$, so $b=c$.
-
-  Lastly, given any $s\in\sigma$, there is a compact strategy $\sigma_s$ containing $s$; namely
-  \[
-    \sigma_s = \{t\suchthat \text{$t\prefix s$ has even length}\}\,.\qedhere
-    \]
-\end{proof}
-
-\section{The Strategy $\cell$}
-\label{SecCell}
-
-Now we come to the denotation of $\neww$.  
-For this, we shall define a strategy $\cell\from \oc\bN \implies \oc \Varr$ by using the property of $\oc \Varr$ as a final coalgebra.
-
-Given $n\in\bN$, we define a strategy $\wwrite_n\from \oc\bN \implies \bC \sequoid\oc\bN$ by
-\[
-  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
-  \]
-Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
-In other words, by Proposition \ref{PropFormulaForAlpha}, $\rread$ is the composite
-\[
-  \rread = \oc\bN \xrightarrow{\mu_\bN} \oc\bN \tensor \oc\bN \xrightarrow{\der_\bN\tensor\oc\bN} \bN \tensor \oc\bN \xrightarrow{\wk_{\bN,\oc\bN}} \bN \sequoid\oc\bN\,.
-  \]
-Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
-\[
-  \oc\bN \xrightarrow{\langle (\wwrite_n)_{n\in\bN}, \rread\rangle}
-  (\bC \sequoid \oc\bN)^{\bN} \times (\bN \sequoid \oc\bN) \xrightarrow{\dist_{(\bC)_{\bN},\bN,\oc\bN}\inv}
-  (\bC^\bN \times \bN) \sequoid \oc\bN = \Varr \sequoid \oc \bN\,.
-  \]
-We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
-\[
-  \begin{tikzcd}
-    \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
-      & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
-    \oc\Varr \arrow[r, "\alpha_{\Varr}"]
-      & \Varr \sequoid \oc\Varr
-  \end{tikzcd}
-  \]
-Concretely, the strategy $\cell$ behaves as follows, as we shall prove in Proposition \ref{PropCellComb}.
-When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
-If he plays the initial move $q_n$ in the $n$-th copy of $\bC$, player $P$ updates the value she has stored in her head to $n$.  
-If he plays the initial move $q$ in $\bN$, then player $P$ replies with this stored value.  
-Lastly, if he plays this initial move $q$ without having played in any of the copies of $\bC$, then player $P$ interrogates the argument in order to find out which value to play.
-
-This strategy $\cell$ now gives us a morphism $\neww_A \from \oc(\oc\Varr \implies A) \implies A$ given by
-\begin{IEEEeqnarray*}{rCl}
-  \oc(\oc\Varr\implies A) & \xrightarrow{\mathmakebox[50pt]{\der}} & (\oc\Varr\implies A) \\
-  & \xrightarrow{\mathmakebox[50pt]{\lunit}} & I \tensor (\oc\Varr\implies A) \\
-  & \xrightarrow{\mathmakebox[50pt]{\oc0\tensor (\oc\Varr\implies A)}} & \oc\bN \tensor (\oc \Varr\implies A) \\
-  & \xrightarrow{\mathmakebox[50pt]{\cell\tensor (\oc\Varr\implies A)}} & \oc\Varr \tensor (\oc \Varr \implies A) \\
-  & \xrightarrow{\mathmakebox[50pt]{\ev}} & A\,.
-\end{IEEEeqnarray*}
-
-We use this to provide the denotation of the term $\neww$.
-
-\begin{lemma}
-  $\cell_0;(\pr_n\sequoid\oc\bN) = \wwrite_n$ for each $n$ and $\cell_0;(\pr_\bN\sequoid\oc\bN) = \rread$, where $\pr_n\from \Varr=\bC^\bN \times \bN \implies \bC$ is the projection on to the $n$-th copy of $\bC$ and $\pr_\bN\from \Varr = \bC^\bN \times \bN \implies \bN$ is the projection on to the copy of $\bN$.
-  \label{LemCellProjections}
-\end{lemma}
-\begin{proof}
-  We have
-  \[
-    \dist_{(\bC)_{\bN},\bN,\oc\bN};\pr_n = \langle(\pr_n\sequoid\oc \bN)_{n\in\bN},\pr_{\bN}\sequoid\oc\bN\rangle;\pr_n = \pr_n\sequoid\oc\bN
-    \]
-  and
-  \[
-    \dist_{(\bC)_{\bN},\bN,\oc\bN};\pr_\bN = \langle(\pr_n\sequoid\oc \bN)_{n\in\bN},\pr_{\bN}\sequoid\oc\bN\rangle;\pr_\bN = \pr_\bN\sequoid\oc\bN\,,
-    \]
-  so
-  \begin{IEEEeqnarray*}{Cl}
-    & \cell_0;(\pr_n\sequoid\oc\bN) \\
-    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv;(\pr_n\sequoid\oc\bN) \\
-    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle ;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv\dist_{(\bC)_\bN,\bN,\oc\bN};\pr_n \\
-    = & \langle (\wwrite_n)_{n\in\bN},\rread\rangle;\pr_n \\
-    = & \wwrite_n
-  \end{IEEEeqnarray*}
-  and
-  \begin{IEEEeqnarray*}{Cl}
-    & \cell_0;(\pr_\bN\sequoid\oc\bN) \\
-    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv;(\pr_\bN\sequoid\oc\bN) \\
-    = & \langle (\wwrite_n)_{n\in\bN},\rread \rangle ;\dist_{(\bC)_\bN,\bN,\oc\bN}\inv\dist_{(\bC)_\bN,\bN,\oc\bN};\pr_\bN \\
-    = & \langle (\wwrite_n)_{n\in\bN},\rread\rangle;\pr_\bN \\
-    = & \rread\,.\hspace{1em plus 1fill}\qedhere
-  \end{IEEEeqnarray*}
-\end{proof}
-
-This coalgebraic definition of the $\cell$ strategy will be sufficient for most of our purposes, it will also be convenient to have a more direct definition.
-
-\begin{proposition}
-  The strategy $\cell$ is the strategy on $\oc\bN \implies \oc\Varr$ that behaves as follows.  
-  It replies to a move $q_n$ (i.e., the initial move in the $n$-th component of $\bC$ in $\Varr$) with the unique answer $a$, and replies to the move $q$ in the $\bN$ component of $\Varr$ with that number $n$ such that $q_n$ was the most recently played $O$-move in the $\bC^\bN$ component, or, if no such move has been played, it interrogates $\oc\bN$ on the left and copies the value back on to the right.
-  \label{PropCellComb}
-\end{proposition}
-\begin{proof}
-  It will suffice to show that the strategy $\cell$ as described in the statement makes the diagram
-  \[
-    \begin{tikzcd}
-      \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
-        & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
-      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
-        & \Varr \sequoid \oc\Varr
-    \end{tikzcd}
-    \]
-  commute.
-  Since $\dist_{(\bC)_\bN,\bN}$ is an isomorphism, it will suffice to show commutativity of the diagram formed by composing by it on the right; i.e.:
-  \[
-    \begin{tikzcd}[column sep=60pt]
-      \oc\bN \arrow[rr, "{\langle (\wwrite_n)_{n\in\bN},\rread \rangle}"] \arrow[d, "\cell"']
-        &
-          & (\bC \sequoid\oc\bN)^\bN \times (\oc\bN \sequoid \oc\bN) \arrow[d, "(\bC \sequoid \cell)^\bN \times (\bN \sequoid \cell)"] \\
-      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
-        & \Varr\sequoid\oc\Varr \arrow[r, "{\dist_{(\bC)_{\bN},\bN}}"]
-          & {(\bC \sequoid \oc\Varr)^{\bN} \times (\bN \sequoid \oc\Varr)\,.}
-    \end{tikzcd}
-    \]
-  That is, we need to show that the following diagrams commute, where $n$ in the first diagram ranges over the natural numbers.
-  \begin{mathpar}
-    \begin{tikzcd}[column sep=40pt]
-      \oc\bN \arrow[rr, "\wwrite_n"] \arrow[d, "\cell"']
-        &
-          & \bC \sequoid \oc\bN \arrow[d, "\bC \sequoid \cell"] \\
-      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
-        & \Varr \sequoid \oc\Varr \arrow[r, "\pr_n \sequoid \oc\Varr"]
-          & \bC \sequoid \oc\Varr
-    \end{tikzcd}
-    \and
-    \begin{tikzcd}[column sep=40pt]
-      \oc\bN \arrow[rr, "\rread"] \arrow[d, "\cell"']
-        &
-          & \bN \sequoid \oc\bN \arrow[d, "\bN \sequoid \cell"] \\
-      \oc\Varr \arrow[r, "\alpha_{\Varr}"]
-        & \Varr \sequoid \oc\Varr \arrow[r, "\pr_\bN \sequoid \oc\Varr"]
-          & \bN \sequoid \oc\Varr
-    \end{tikzcd}
-  \end{mathpar}
-  Consider the first diagram.  
-  We may identify plays of $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$ with those plays in $\cell$ that begin with the initial move $q_n$ in $\Varr$ (i.e., the initial move $q$ in the $n$-th copy of $\bC$).
-  We need to show that plays in $\wwrite_n;(\bC\sequoid\cell)$ take the same form.  
-  Indeed, the response to the initial move in $\bC$ in $\wwrite_n;(\bC\sequoid\cell)$ is the unique response $a$, by the definition of $\wwrite_n$; thereafter, play continues in $\oc\Varr$ according to $\cell$ -- so the response to a move $q_m$ will be $a$, while the response to $q$, if some $q_m$ has been played already in $\oc\Varr$, will be the most recently occurring value of $m$.
-
-  If no $q_m$ has been played in $\oc\Varr$, then the behaviour of $\cell$ tells us that we must interrogate the $\oc\bN$ in $\bC\sequoid\oc\bN$ in order to get the value.  
-  By the definition of $\wwrite_n$, the value returned will be $n$, mirroring the behaviour in $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$.
-
-  Now consider the second diagram.  
-  We may identify plays of the strategy $\cell;\alpha_{\Varr};(\pr_n\sequoid\oc\Varr)$ with those plays in $\cell$ that begin with the initial move $q$ in $\Varr$ (i.e., the initial move $q$ in the copy of $\bN$).
-  We need to show that plays in $\rread;(\bN\sequoid\cell)$ take the same form.  
-  Indeed, the response to the initial move will be to interrogate $\oc\bN$ on the left to get the value.  
-  Thereafter, play will continue between $\oc\bN$ and $\oc\Varr$ according to the $\cell$ strategy -- so once again the response to a move $q_m$ will be $a$, while the response to $q$, if some $q_m$ has been played, will be the most recently occurring value $m$.
-
-  If no $q_m$ has been played in $\oc\Varr$, then, by the definition of $\rread$, the strategy will interrogate $\oc\bN$ in order to get its response, just as in the strategy $\cell;\alpha_{\Varr};(\pr_\bN\sequoid\oc\Varr)$.
-\end{proof}
-
-\chapter{Operational Semantics, Computational Adequacy and Full Abstraction}
-\label{ChapFullAbstraction}
-
-\section{Big-Step Operational Semantics}
-
-We now introduce the operational semantics of Idealized Algol, so that we can prove soundness and adequacy of our semantics for it.
-
-We first define a \emph{canonical form} of the language to be
-\begin{itemize}
-  \item at type $\com$, the term $\skipp$;
-  \item at type $\bool$, the terms $\true$ and $\false$;
-  \item at type $\nat$, the numerals $n$; 
-  \item at type $\Var$, variable names $x$ of type $\Var$ and expressions of the form $\mkvar W\,R$; and
-  \item at type $S\to T$, expressions of the form $\lambda x^S.M$.
-\end{itemize}
-
-We define a \emph{$\Var$-context} to be a context $\Gamma$ of the form $x_1\from \Var,\cdots,x_n\from \Var$.
-Given a $\Var$-context $\Gamma$, we define a \emph{$\Gamma$-store} to be a function $s$ from the variable names occurring in $\Gamma$ to the natural numbers.  
-Given such a store $s$, we write $(s\vert x \mapsto n)$ for the store given by
-\[
-  (s\vert x\mapsto n)(y) = \begin{cases}
-    n & \text{if $y = x$} \\
-    s(y) & \text{otherwise}
-  \end{cases}\,.
-  \]
-We now inductively define a relation $\Gamma,s\ts M\converges c,s'$, where
-\begin{itemize}
-  \item $\Gamma$ is a $\Var$-context; 
-  \item $s$ and $s'$ are $\Gamma$-stores;  and
-  \item $\Gamma\ts M$, $\Gamma\ts c$ are Idealized Algol terms-in-context, where $c$ is a canonical form.
-\end{itemize}
-The definition of this relation is shown in Figure \ref{FigIaOpSem}.
-
-\begin{figure}
-  \vspace{-27pt}
-  \begin{mathpar}
-    \inferrule*{ }{\Gamma,s\ts c \converges c,s}
-    \and
-    \inferrule*{\Gamma,s \ts M \converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x] \converges c,s''}{\Gamma,s \ts MN \converges c,s''}
-    \and
-    \inferrule*{\Gamma,s \ts M(\Y M) \converges c,s'}{\Gamma,s \ts \Y M \converges c,s'}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges n,s'}{\Gamma,s\ts \suc M \converges n+1,s'}
-    \\\and
-    \inferrule*{\Gamma,s\ts M \converges n+1,s'}{\Gamma,s\ts \pred M \converges n,s'}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges 0,s'}{\Gamma,s\ts \pred M \converges 0,s'}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges \skipp,s' \\ \Gamma,s'\ts N \converges c,s''}{\Gamma,s \ts M;N \converges c,s''}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges \true,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges \false,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \If M \Then N \Else P \converges c,s''}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges 0,s' \\ \Gamma,s' \ts N \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
-    \and
-    \inferrule*{\Gamma,s\ts M \converges n+1,s' \\ \Gamma,s' \ts P \converges c,s''}{\Gamma,s \ts \IfO M \Then N \Else P \converges c,s''}
-    \and
-    \inferrule*[right=$x\in\Gamma$]{\Gamma,s\ts E \converges n,s' \\ \Gamma,s' \ts V \converges x,s''}{\Gamma,s\ts V \gets E \converges \skipp,(s''\vert x \mapsto n)}
-    \and
-    \inferrule*[right={$s'(x)=n$}]{\Gamma,s\ts V \converges x,s'}{\Gamma,s\ts !V \converges n,s'}
-    \and
-    \inferrule*{\Gamma,x\from\Var,(s\vert x\mapsto 0)\ts M \converges c,(s'\vert x\mapsto n)}{\Gamma,s\ts \neww \lambda x.M \converges c,s'}
-    \and
-    \inferrule*{\Gamma,s\ts E \converges n,s' \\ \Gamma,s'\ts V \converges \mkvar W R,s'' \\ \Gamma,s'' \ts Wn \converges \skipp,s'''}
-    {\Gamma,s \ts V\gets E \converges \skipp,s'''}
-    \and
-    \inferrule*{\Gamma,s\ts V \converges \mkvar W R,s' \\ \Gamma,s'\ts R \converges n,s''}{\Gamma,s\ts !V \converges n,s''}
-  \end{mathpar}
-  \caption[Operational semantics for Idealized Algol.]{Operational semantics for Idealized Algol. See \cite{RusssThesis} and \cite{SamsonGuyIAActive}.}
-  \label{FigIaOpSem}
-\end{figure}
-
-\section{Small-Step Operational Semantics}
-
-We also give a small-step operational semantics for Idealized Algol, which will sometimes be easier to work with.
-
-This time, instead of defining a relation $\Gamma,s\ts M\converges c,s'$, we define a relation $\Gamma,s\ts M\opto \Gamma,\Delta,s'\ts M'$, where
-\begin{itemize}
-  \item $\Gamma,\Delta$ are disjoint $\Var$-contexts; 
-  \item $s$ is a $\Gamma$-store and $s'$ a $\Gamma,\Delta$-store;  and
-  \item $\Gamma\ts M$, $\Gamma,\Delta\ts M'$ are Idealized Algol terms-in-context.
-\end{itemize}
-
-As an auxiliary definition, we need the notion of an \emph{evaluation context} (see \cite{Felleisen}).
-This is a single-holed context defined inductively by the following BNF formula, where $M$ ranges over IA terms (subject to typing rules).
-\begin{center}
-\parbox{0.8\textwidth}{
-\begin{mathpar}
-  \EE \Coloneqq - \mid \EE\,M \mid \suc \EE \mid \pred \EE \mid \EE;M \mid \If \EE\Then M \Else M \mid \IfO \EE \Then M \Else M \mid !\EE \mid M \gets \EE \mid \EE \gets n
-\end{mathpar}}
-\end{center}
-
-Next, we define a relation $\Gamma,s,M\oopto\Gamma,\Delta,s',M'$ as in Figure \ref{FigIaSsOpSem}.
-
-We then define the relation $\opto$ as
-\[
-  \inferrule*{ \Gamma,s\ts M\oopto \Gamma,\Delta,s'\ts M'}{\Gamma,s\ts \EE[M] \opto \Gamma,\Delta,s'\ts\EE[M']}
-  \]
-for each evaluation context $\EE$.
-
-\begin{figure}
-  \begin{mathpar}
-    \Gamma,s\ts (\lambda x.M)N \oopto \Gamma,s\ts M[N/x]
-    \and
-    \Gamma,s\ts \Y M \oopto \Gamma,s\ts M(\Y M)
-    \and
-    \Gamma,s\ts \suc n \oopto \Gamma,s\ts n+1
-    \\
-    \Gamma,s \ts \pred (n+1) \oopto \Gamma,s\ts n
-    \and
-    \Gamma,s\ts \pred 0 \oopto \Gamma,s\ts 0
-    \\
-    \Gamma,s\ts \skipp;M \oopto \Gamma,s\ts M
-    \\
-    \Gamma,s\ts \If \true \Then N \Else P \oopto \Gamma,s\ts N
-    \and
-    \Gamma,s\ts \If \false \Then N \Else P \oopto \Gamma,s\ts P
-    \and
-    \Gamma,s\ts \IfO 0 \Then N \Else P \oopto \Gamma,s\ts N
-    \and
-    \Gamma,s\ts \IfO (n+1) \Then N \Else P \oopto \Gamma,s\ts P
-    \and
-    x,\Gamma,s\ts x \gets n \oopto x,\Gamma,(s\vert x\mapsto n)\ts \skipp
-    \and
-    x,\Gamma,s\ts \oc x \oopto x,\Gamma,s\ts s(x)
-    \\
-    \Gamma,s\ts \neww \lambda x.M \oopto \Gamma,x,(s\vert x\mapsto 0)\ts M
-    \\
-    \Gamma,s \ts (\mkvar W\,R) \gets n \oopto \Gamma,s\ts Wn
-    \and
-    \Gamma,s \ts \oc(\mkvar W\,R) \oopto \Gamma,s\ts R
-  \end{mathpar}
-  \caption{Felleisen-style small-step operational semantics for Idealized Algol.}
-  \label{FigIaSsOpSem}
-\end{figure}
-
-We need to prove that this is equivalent to our original semantics.
-Given a $\Gamma,\Delta$-store $s$, write $s\vert_{\Gamma}$ for the restriction of $s$ to $\Gamma$.
-
-\begin{lemma}
-  Suppose that $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts M'$ and that $\Gamma,\Delta,s'\ts \EE[M'] \converges c,s''$.  
-  Then $\Gamma,s\ts \EE[M]\converges c,s''\vert_\Gamma$.
-  \label{LemSmallToBig}
-\end{lemma}
-\begin{proof}
-  Structural induction on $\EE$.
-  The base case, when $\EE$ is a hole, covers the interesting cases, so we shall leave it to last.
-  The remaining cases are quite similar, so we will show the proof for one of them for illustration.
-
-  If $\EE=\EE'\,N$, for some term $N$, then we have $\Gamma,\Delta,s'\ts \EE'[M']\,N\converges c,s''$.  
-  By inspection of the rules in Figure \ref{FigIaOpSem}, the derivation of this must end with a rule of the form
-  \[
-    \inferrule*{\Gamma,\Delta,s'\ts \EE'[M'] \converges \lambda x.M'',t \\ \Gamma,\Delta,t \ts M''[N/x] \converges c,s''}
-    {\Gamma,\Delta,s'\ts \EE'[M']\,N \converges c,s''}\,.
-    \]
-  Thus, $\Gamma,\Delta,s'\ts \EE'[M']\converges \lambda x.M'',t$ and $\Gamma,\Delta\ts M''[N/x]\converges c,s''$ must be provable for some $M'',t$.
-  By the induction hypothesis, this means that $\Gamma,s\ts \EE'[M]\converges \lambda x.M'',t$ is provable.
-  Then we have a derivation
-  \[
-    \inferrule*{\Gamma,\Delta,s\ts \EE'[M] \converges \lambda x.M'',t \\ \Gamma,\Delta,t \ts M''[N/x] \converges c,s''}
-    {\Gamma,\Delta,s\ts \EE'[M]\,N\converges c,s''\vert_{\Gamma,\Delta}}\,.
-    \]
-  Then, because any variables in $\Delta$ are not mentioned in $\EE'[M]\,N$ or in $c$, we have
-  \[
-    \Gamma,s\ts \EE'[M]\,N\converges c,s''\vert_\Gamma\,.
-    \]
-  Now, let us suppose that $\EE$ is a hole, so that $\EE[M']=M'$.
-
-  Then there are a number of cases, depending on the particular $\oopto$ rule we are using.  
-  Many of these cases are similar, so we will cover a few of them for the purposes of illustration.
-  \begin{itemize}
-    \item Suppose that $\Gamma,s\ts M[N/x]\converges c,s'$.  
-      Then we have a derivation
-      \[
-        \inferrule*
-        {
-          \inferrule*
-          {
-          }
-          {
-            \Gamma,s \ts \lambda x.M \converges \lambda x.M,s
-          }
-          \\
-          \Gamma,s\ts M[N/x] \converges c,s'
-        }
-        {
-          \Gamma,s\ts (\lambda x.M)N \converges c,s'
-        }\,.
-        \]
-    \item We have a derivation
-      \[
-        \inferrule*
-        {
-          \inferrule*
-          {
-          }
-          {
-            \Gamma,s\ts x\converges x,s
-          }
-          \\
-          \inferrule*
-          {
-          }
-          {
-            \Gamma,s\ts n\converges n,s
-          }
-        }
-        {
-          \Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)
-        }\,.
-        \]
-    \item We have a derivation
-      \[
-        \inferrule*
-        {
-          \inferrule*
-          {
-          }
-          {
-            \Gamma,s\ts x \converges x,s'
-          }
-        }
-        {
-          \Gamma,s\ts \oc x\converges s(x),s
-        }\,.
-        \]
-    \item Suppose that $\Gamma,x,(s\vert x\mapsto 0) \ts M\converges c,s'$.  
-      Then we have a derivation
-      \[
-        \inferrule*
-        {
-          \Gamma,x,(s\vert x\mapsto 0) \ts M \converges c,s'
-        }
-        {
-          \Gamma,s\ts \neww\lambda x.M \converges c,s'\vert_\Gamma
-        }\,,
-        \]
-      since $s'=(s'\vert_\Gamma\vert x\mapsto s'(x))$.\qedhere
-  \end{itemize}
-\end{proof}
-
-We have proved:
-
-\begin{proposition}
-  Suppose that we have a sequence
-  \[
-    \Gamma_1,s^{(1)},M_1\opto\cdots\opto\Gamma_n,s^{(n)},M_n\,,
-    \]
-  where $M_n$ is a canonical form.  
-  Then $\Gamma_1,s^{(1)} \ts M_1\converges M_n,s^{(n)}\vert_{\Gamma_1}$.  
-  \label{PropSmallToBig}
-\end{proposition}
-\begin{proof}
-  Induction on $n$.  
-  The inductive step is Lemma \ref{LemSmallToBig}, while the base case ($n=1$) is given by the derivation
-  \[
-    \inferrule*{ }
-    {\Gamma,s\ts c\converges c,s}\,.\qedhere
-    \]
-\end{proof}
-
-We can also prove the converse.
-
-\begin{proposition}
-  Suppose that $\Gamma,s\ts M\converges c,s'$.  
-  Then there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
-  \[
-    \Gamma_1,s^{(1)}\ts M_1 \opto \cdots \opto \Gamma_n,s^{(n)}\ts M_n\,,
-    \]
-  and $s^{(n)}\vert_{\Gamma}=s'$.
-  \label{PropBigToSmall}
-\end{proposition}
-\begin{proof}
-  Induction on the derivation of $\Gamma,s\ts M\converges c,s'$.  
-  Since most of the cases are similar, we cover a selection for illustration.
-
-  \begin{itemize}
-    \item Suppose that the last step in the derivation is
-      \[
-        \inferrule*{ }
-        {\Gamma,s\ts c\converges c,s}\,.
-        \]
-      Then we have the one-element sequence $\Gamma,s\ts c$.  
-    \item Suppose that the last step in the derivation is
-      \[
-        \inferrule*
-        {
-          \Gamma,s\ts M\converges \lambda x.M',s' \\ \Gamma,s' \ts M'[N/x]\converges c,s''
-        }
-        {
-          \Gamma,s \ts MN\converges c,s''
-        }\,.
-        \]
-      Then, by the inductive hypothesis, we have small-step derivations
-      \begin{mathpar}
-        \Gamma,s \ts M \opto \cdots \opto \Gamma,\Delta,t',\lambda x.M'
-        \and
-        \Gamma,s' \ts M'[N/x]\opto \cdots \opto \Gamma,\Delta',t'',c\,,
-      \end{mathpar}
-      where $t'\vert_\Gamma=s'$ and $t''\vert_\Gamma=s''$.
-
-      If we apply the evaluation context $-N$ pointwise to the first small-step derivation, then we have another valid small-step derivation.  
-      Then we can join the two together to get the derivation
-      \begin{center}
-        \parbox{0.8\textwidth}{
-        \begin{mathpar}
-          \Gamma,s \ts MN \opto \cdots \opto \Gamma,\Delta,t',(\lambda x.M')N \opto \Gamma,\Delta,t',M'[N/x] \opto \cdots \opto \Gamma,\Delta\cup\Delta',t''\setminus t',c\,,
-        \end{mathpar}}
-      \end{center}
-      where $t''\setminus t'$ is the $\Gamma,\Delta\cup\Delta'$-store that agrees with $t''$ on $\Gamma,\Delta'$ and with $t'$ on $\Delta\setminus\Delta'$.
-      Then $(t''\setminus t')\vert_{\Gamma}=s''$.
-    \item Suppose that the last step in the derivation is
-      \[
-        \inferrule*
-        {
-          \Gamma,s\ts E\converges n,s' \\ \Gamma,s'\ts V\converges x,s''
-        }
-        {
-          \Gamma,s \ts V \gets E \converges\skipp,(s''\vert x\mapsto n)
-        }\,.
-        \]
-      By the inductive hypothesis, we have small-step derivations
-      \begin{mathpar}
-        \Gamma,s\ts E \opto \cdots \opto \Gamma,\Delta,t',n
-        \and
-        \Gamma,s'\ts V \opto \cdots \opto \Gamma,\Delta',t'',x\,,
-      \end{mathpar}
-      where $t'\vert_{\Gamma}=s'$ and $t''\vert_{\Gamma}=s''$.
-
-      We may apply the evaluation context $V\gets-$ pointwise to the first derivation and the evaluation context $-\gets n$ pointwise to the second, and then string the two together to get
-      \begin{center}
-        \parbox{0.8\textwidth}{
-        \begin{mathpar}
-          \Gamma,s\ts V\gets E \opto \cdots \opto \Gamma,\Delta,t',V\gets n \opto \cdots \opto \Gamma,\Delta\cup\Delta',t''\setminus t',x\gets n \opto \Gamma,\Delta\cup\Delta',(t''\setminus t'\vert x\mapsto n)\,,
-        \end{mathpar}}
-      \end{center}
-      where we have $(t''\setminus t'\vert x\mapsto n)\vert_\Gamma=(s''\vert x\mapsto n)$.
-    \item Suppose that the last step in the derivation is
-      \[
-        \inferrule*
-        {
-          \Gamma,s\ts V \converges x,s'
-        }
-        {
-          \Gamma,s\ts \oc V \converges s'(x),s'
-        }\,.
-        \]
-      Then, by the induction hypothesis, we have a small-step derivation
-      \[
-        \Gamma,s\ts V \opto \cdots \opto \Gamma,\Delta,t'\ts x\,,
-        \]
-      where $t'\vert_\Gamma=s'$.  
-      Then we may compose this derivation pointwise with the evaluation context $\oc-$, and add an extra term on the end, to arrive at the derivation
-      \[
-        \Gamma,s\ts \oc V \opto \cdots \opto \Gamma,\Delta,t'\ts \oc x \opto \Gamma,\Delta,t'\ts t'(x)\,,
-        \]
-      where $t'(x)=s'(x)$.
-    \item Lastly, suppose that the last step in the derivation is
-      \[
-        \inferrule*
-        {
-          \Gamma,x,(s\vert x\mapsto 0) \ts M \converges c,(s'\vert x\mapsto n)
-        }
-        {
-          \Gamma,s \ts \neww \lambda x.M \converges c,s'
-        }\,.
-        \]
-      By the induction hypothesis, we have a small-step derivation
-      \[
-        \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma,\Delta,x,(t'\vert x\mapsto n),c\,,
-        \]
-      where $t'\vert_\Gamma=s'$.  
-      Then we may add a term at the beginning to give us
-      \begin{center}
-        \parbox{0.6\textwidth}{
-        \begin{mathpar}
-          \Gamma,s \ts \neww \lambda x.M \opto \Gamma,x,(s\vert x\mapsto 0) \ts M \opto \cdots \opto \Gamma,\Delta,x,(t'\vert x\mapsto n),c\,,
-        \end{mathpar}}
-      \end{center}
-      where $(t'\vert x\mapsto n) \vert_\Gamma=s'$.\qedhere
-  \end{itemize}
-\end{proof}
-
-\section{Soundness}
-
-To prove soundness of our model, we shall use the small-step formulation.  
-Our reason for this is that the most difficult part of the denotational semantics we are using is the part to do with state.  
-In the big-step formulation, nearly every rule involves the state changing in some way, whereas in the small-step formulation, only the rules that specifically pertain to the stateful components of the language do.
-
-Given a $\Var$-context $\Gamma$, we will write $S_\Gamma$ for $\bN \times \cdots \times \bN$.
-
-Given $\Gamma$, we have a morphism $\cell^\Gamma\from \oc S_\Gamma \implies \oc \deno{\Gamma}$, given by
-\[
-  \oc S_\Gamma \cong \oc \bN \tensor \cdots \tensor \oc \bN \xrightarrow{\cell \tensor \cdots \tensor \cell} \oc \Varr \tensor \cdots \tensor \oc \Varr \cong \oc \deno{\Gamma}\,.
-  \]
-\begin{lemma}
-  For $j=1,\cdots,|\Gamma|$, the following diagram commutes.
-  \[
-    \begin{tikzcd}
-      \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[d, "\oc\pr_j"']
-        & \oc V_\Gamma \arrow[d, "\oc \pr_j"] \\
-      \oc \bN \arrow[r, "\cell"]
-        & \oc \Varr
-    \end{tikzcd}
-    \]
-\end{lemma}
-\begin{proof}
-  We have a commutative diagram
-  \[
-    \begin{tikzcd}[column sep=40pt, row sep=40pt]
-      \oc S_\Gamma \arrow[r, Isom] \arrow[dr, "\oc \pr_j"']
-        & \oc \bN \tensor \cdots \tensor \oc \bN \arrow[r, "\cell \tensor \cdots \tensor \cell"] \arrow[d, "() \tensor \cdots \tensor \oc\bN \tensor \cdots \tensor ()"' {description, xshift=10pt}]
-          & \oc \Varr \tensor \cdots \tensor \oc \Varr \arrow[r, Isom] \arrow[d, "() \tensor \cdots \tensor \oc\Varr \tensor \cdots \tensor ()" {description, xshift=-10pt}]
-            & \oc V_\Gamma \arrow[dl, "\oc \pr_j"] \\
-      %
-        & \oc\bN \arrow[r, "\cell"]
-          & \oc\Varr
-            &
-    \end{tikzcd}\,,
-    \]
-  where the outer triangles commute because the vertical arrows are the projections in the tensor product of comonoids.
-\end{proof}
-
-Given a $\Gamma$-store $s$, we will write $\deno{s}$ for the corresponding morphism $I \to S_\Gamma$.
-
-We start our proof of soundness with a result about evaluation contexts.
-This result captures the fact that the term filling the hole of an evaluation context is the first thing to be computed, using the sequoid operator to capture this notion of precedence.
-\begin{lemma}
-  Let $\Gamma\ts M\from T$ be an Idealized Algol term-in-context (where $\Gamma$ is an arbitrary context), and let $\EE$ be an evaluation context with a hole of type $T$, where $\EE[M]\from U$.  
-  Then there is a game $A$ and strategies $\sigma\from \oc{\deno{\Gamma}} \implies A$, $\tau\from\deno{T}\sequoid A \implies \deno{S}$, where $\tau$ is a strict strategy, such that the denotation $\deno{\Gamma\ts\EE[M]}$ factors as
-  \[
-    \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno{T}\tensor A \xrightarrow{\wk_{\deno{T},A}} \deno{T} \sequoid A \xrightarrow{\tau} \deno{U}\,.
-    \]
-  \label{LemEvContexLemma}
-\end{lemma}
-\begin{proof}
-  Structural induction on $\EE$.
-  \begin{itemize}
-    \item If $\EE=-$ is a hole, then we may take $A=I$, $\sigma=()$ and $\tau=\run_{\deno T}$.
-
-    \item If $\EE=\EE' N$ for some term $N$, where $\EE'$ has type $S\to T$, $N$ has type $S$, and $M\from S'$ fits into the hole, then the denotation $\deno{\Gamma \ts \EE[M]} = \deno{\Gamma \ts \EE'[M]\,N}$ is given by the composite
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mathmakebox[9pt]{\mu_{{\deno{\Gamma}}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma \ts \EE'[M]}\tensor \deno{\Gamma \ts N}} (\oc\deno{S} \implies \deno{T}) \tensor \oc\deno{S} \xrightarrow{\mathmakebox[-4pt]{}\ev_{\oc\deno{S},\deno{T}}} \deno{T}.
-        \]
-      By the inductive hypothesis, $\deno{\Gamma\ts\EE' M}$ factors as
-      \small
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mathmakebox[-1pt]{}\mu_{{\deno{\Gamma}}}\mathmakebox[-1pt]{}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{S'}\tensor A' \xrightarrow{\mathmakebox[-1.2pt]{}\wk_{\deno{S'},A'}} \deno{S'} \sequoid A' \xrightarrow{\mathmakebox[-1.2pt]{}\tau'\mathmakebox[-1.4pt]{}} (\oc\deno{S}\implies\deno{T}),
-        \]
-      \normalsize
-      for appropriate $A',\sigma',\tau'$.  
-      Then $\deno{\Gamma\ts\EE[M]} = \deno{\Gamma\ts\EE'[M]\,N}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextApp}.  
-      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form, with
-      \begin{mathpar}
-        A = A' \tensor \oc\deno{S}
-        \and
-        \sigma = \mu_{{\deno{\Gamma}}};(\sigma'\tensor\deno{\Gamma\ts N}^\dag)
-        \and
-        \tau = \passoc_{\deno{S'},A',\oc\deno{S}}\inv;(\tau'\sequoid\oc\deno{S});\ev_{s\;\oc\deno{S},\deno{T}}\,.
-      \end{mathpar}
-      \begin{figure}
-        \small
-        \[
-          \begin{tikzcd}[column sep=79pt]
-            \oc{\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{{\deno{\Gamma}}}"]
-              & \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[d, "\oc{\deno{\Gamma}}\tensor\mu_{{\deno{\Gamma}}}"] \\
-            \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}}"' yshift=3pt, thick, dashed]
-              & \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N}^\dag)"] \\
-            (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc {\deno{\Gamma}} \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}^\dag"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{{\deno{\Gamma}},{\deno{\Gamma}},{\deno{\Gamma}}}" description, dotted]
-              & \deno{S'} \tensor (A' \tensor \oc\deno{S}) \arrow[d, "{\wk_{\deno{S'},A' \tensor \oc \deno{S}}}"] \\
-            (\deno{S'} \tensor A') \tensor \oc\deno{S} \arrow[d, "{\wk_{\deno{S'},A'}\tensor \oc\deno{S}}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\deno{S'},A',\oc\deno{S}}" description, dotted]
-              & \deno{S'} \sequoid (A' \tensor \oc\deno{S}) \arrow[d, "{\passoc_{\deno{S'},A',\oc\deno{S}}\inv}"] \\
-            (\deno{S'} \sequoid A') \tensor \oc\deno{S} \arrow[d, "\tau' \tensor\oc\deno S"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{\deno{S'}\sequoid A',\oc\deno{S}}}" description, dotted]
-              & (\deno{S'} \sequoid A') \sequoid \oc\deno{S} \arrow[d, "\tau' \sequoid \oc\deno{S}"] \\
-            (\oc \deno{S} \implies \deno{T}) \tensor \oc\deno{S} \arrow[d, "{\ev_{\oc\deno{S},\deno{T}}}"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{\oc\deno S \implies \deno T,\oc\deno S}}" description, dotted]
-              & (\oc\deno{S} \implies \deno{T}) \sequoid \oc\deno{S} \arrow[dl, "{\ev_{s\;\oc\deno{S},\deno{T}}}"] \\
-            \deno{T}
-              &
-          \end{tikzcd}
-          \]
-        \normalsize
-        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by function application.]{The property in Lemma \ref{LemEvContexLemma} is preserved by function application.  
-        Here, $\ev_{s\;\oc\deno{S},\deno{T}} = \Lambda_s\inv(\id_{\oc\deno{S}\implies \deno{T}})$.}
-        \label{FigEvContextApp}
-      \end{figure}
-    \item If $\EE=\suc \EE'$ or $\pred \EE'$, where $\EE'$ is a context of type $\nat$, and $M\from T$ is a term that fits into the hole, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
-      \[
-        \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \bN \xrightarrow{\theta} \bN\,,
-        \]
-      where $\theta$ is either $\pred$ or $\suc$.
-      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \bN\,,
-        \]
-      for appropriate $A',\sigma',\tau'$.  
-      Then we can compose on the right by $\theta$, and we are already in the required form, for
-      \begin{mathpar}
-        A = A' \and \sigma = \sigma' \and \tau = \tau';\theta\,.
-      \end{mathpar}
-    \item Similarly, if $\EE = \oc\EE'$, where $\EE'$ is a context of type $\Var$, and $M\from T$ is a term that fits into the hole, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
-      \[
-        \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma \ts \EE'[M]}} \Varr \xrightarrow{\dereff} \bN\,.
-        \]
-      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} \Varr\,,
-        \]
-      for appropriate $A',\sigma',\tau'$.  
-      Then we can compose on the right by $\dereff$, and we are already in the required form, for
-      \begin{mathpar}
-        A = A' \and \sigma = \sigma' \and \tau = \tau';\dereff\,.
-      \end{mathpar}
-    \item If $\EE=\EE';N$ for some term $N$ of type $X\in\{\com,\bool,\nat\}$, where $\EE'$ is an evaluation context of type $\com$, and if $M\from T$ fits into the hole in $\EE'$, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bC \times X \xrightarrow{\Lambda\inv(\seq_X)} X\,.
-        \]
-      If $\EE = N\gets\EE'$, for some term $N$ of type $\Var$, where $\EE'$ is an evaluation context of type $\com$, and if $M\from T$ fits into the hole in $\EE'$, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by the composite
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts\EE'[M]}\tensor\deno{\Gamma\tensor N}} \bN \times \Var \xrightarrow{\Lambda\inv(\assign)} \bC\,.
-        \]
-      Write $Y=\bC$, $X'=X$, $Z=X$ and $\upsilon=\seq_X$ in the sequencing case, and $Y=\bN$, $X'=\Var$, $Z=\bC$ and $\upsilon=\assign$ in the variable assignment case.
-      Then, by the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} Y\,,
-        \]
-      for suitable $A',\sigma',\tau'$.
-      Then $\deno{\Gamma\ts\EE[M]}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextSeqAss}.  
-      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form, with
-      \begin{mathpar}
-        A = A' \tensor X'
-        \and
-        \sigma = \mu_{{\deno{\Gamma}}};(\sigma'\tensor\deno{\Gamma\ts N})
-        \and
-        \tau = \passoc_{\deno{T},A',X'}\inv;(\tau'\sequoid X');\Lambda_s\inv(\upsilon)\,.
-      \end{mathpar}
-      \begin{figure}
-        \small
-        \[
-          \begin{tikzcd}[column sep=79pt]
-            \oc{\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}"' yshift=3pt, thick, dashed] \arrow[r, "\mu_{{\deno{\Gamma}}}"]
-              & \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[d, "\oc{\deno{\Gamma}}\tensor\mu_{{\deno{\Gamma}}}"] \\
-            \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}}"' yshift=3pt, thick, dashed]
-              & \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \arrow[d, "\deno{\Gamma \ts M}\tensor (\sigma' \tensor \deno{\Gamma\ts N})"] \\
-            (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc {\deno{\Gamma}} \arrow[d, "(\deno{\Gamma\ts M} \tensor \sigma')\tensor\deno{\Gamma\ts N}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{{\deno{\Gamma}},{\deno{\Gamma}},{\deno{\Gamma}}}" description, dotted]
-              & \deno{T} \tensor (A' \tensor X') \arrow[d, "{\wk_{\deno{T},A' \tensor X'}}"] \\
-            (\deno{T} \tensor A') \tensor X' \arrow[d, "{\wk_{\deno{T},A'}\tensor X'}"' yshift=3pt, thick, dashed] \arrow[ur, "\assoc_{\deno{T},A',X'}" description, dotted]
-              & \deno{T} \sequoid (A' \tensor X') \arrow[d, "{\passoc_{\deno{T},A',X'}\inv}"] \\
-            (\deno{T} \sequoid A') \tensor X' \arrow[d, "\tau' \tensor X'"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{\deno{T}\sequoid A',X'}}" description, dotted]
-              & (\deno{T} \sequoid A') \sequoid X' \arrow[d, "\tau' \sequoid X'"] \\
-            Y \tensor X' \arrow[d, "\Lambda\inv(\upsilon)"' yshift=3pt, thick, dashed] \arrow[r, "{\wk_{Y,X'}}" description, dotted]
-              & Y \sequoid X' \arrow[dl, "\Lambda_s\inv(\upsilon)"] \\
-            \deno{T}
-              &
-          \end{tikzcd}
-          \]
-        \normalsize
-        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.]{The property in Lemma \ref{LemEvContexLemma} is preserved by sequencing and variable assignment.
-        We use the fact that $\upsilon\in\{\seq_X,\assign\}$ is a strict strategy, so that $\Lambda_s\inv(\upsilon)$ is well-defined.}
-        \label{FigEvContextSeqAss}
-      \end{figure}
-    \item If $\EE = \If \EE' \Then N \Else P$ for a context $\EE'$ of type $\bool$, where $N$ and $P$ are terms of type $X\in\{\bool,\com,\nat\}$, then write $Y=\bool$ and $\eta = \If_X$.  
-      If $\EE = \IfO \EE' \Then N \Else P$ for a context $\EE'$ of type $\nat$, where $N$ and $P$ are terms of type $X\in\{\bool,\com,\nat\}$, then write $Y=\nat$ and $\eta=\IfO_X$.  
-      In either case, if $M\from T$ is a term that fits into the hole, then the denotation $\deno{\Gamma\ts\EE[M]}$ is given by
-      \begin{mathpar}
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{V_\Gamma}} \oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}} \xrightarrow{\mu_\Gamma \tensor {\deno{\Gamma}}} (\oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \\\xrightarrow{(\deno{\Gamma\ts\EE'[M]} \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma \ts P}} (Y \tensor X) \tensor X \xrightarrow{\Lambda\inv(\Lambda\inv(\eta))} X\,.
-      \end{mathpar}
-      By the inductive hypothesis, $\deno{\Gamma\ts\EE'[M]}$ factors as
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}} \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'} \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}} \deno{T} \sequoid A' \xrightarrow{\tau'} Y\,,
-        \]
-      for appropriate $A',\sigma',\tau'$.  
-      Then $\deno{\Gamma\ts\EE[M]} = \deno{\Gamma\ts\EE'[M]\,N}$ is given by the thick dashed arrows in the diagram in Figure \ref{FigEvContextCond}.  
-      But this composite is equal to that given by the thin solid arrows in the diagram, which is of the required form, with
-      \begin{mathpar}
-        A = (A' \tensor X)\tensor X
-        \and
-        \sigma = \mu_{{\deno{\Gamma}}};(\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}});((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})
-        \and
-        \tau = \passoc_{\deno T,A'\tensor X,X}\inv;(\passoc_{\deno T,A',X}\inv\sequoid X);((\tau'\sequoid X)\sequoid X);\Lambda_s\inv(\Lambda_s\inv(\eta))\,.
-      \end{mathpar}
-      \begin{SidewaysFigure}
-        \small
-        \[
-          \begin{tikzcd}[ampersand replacement=\&, column sep=68pt, row sep=30pt]
-            \oc {\deno{\Gamma}} \arrow[rr, "\mu_{{\deno{\Gamma}}}"] \arrow[d, "\mu_{{\deno{\Gamma}}}"', thick, dashed]
-              \&
-                \& \oc {\deno{\Gamma}} \tensor \oc {\deno{\Gamma}} \arrow[d, "\oc{\deno{\Gamma}} \tensor\mu_{{\deno{\Gamma}}}"] \\
-            \oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[r, "\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}}", dotted] \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}}"', thick, dashed]
-              \& (\oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}}", dotted] \arrow[d, "(\oc{\deno{\Gamma}} \tensor \mu_{{\deno{\Gamma}}}) \tensor \oc{\deno{\Gamma}}" description, dotted]
-                \& \oc {\deno{\Gamma}} \tensor (\oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \arrow[d, "\oc{\deno{\Gamma}} \tensor (\mu_{{\deno{\Gamma}}}\tensor \oc{\deno{\Gamma}})"] \\
-            (\oc {\deno{\Gamma}} \tensor \oc{\deno{\Gamma}})\tensor \oc{\deno{\Gamma}} \arrow[d, "(\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}})\tensor \oc{\deno{\Gamma}}"', thick, dashed]
-              \& |[alias=Z]| (\oc {\deno{\Gamma}} \tensor(\oc{\deno{\Gamma}}\tensor \oc{\deno{\Gamma}})) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}}", dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor (\sigma'\tensor\deno{\Gamma\ts N})) \tensor \deno{\Gamma\ts P}" description, dotted]
-                \& \oc{\deno{\Gamma}} \tensor ((\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}}) \arrow[d, "\deno{\Gamma\ts M} \tensor ((\sigma'\tensor\deno{\Gamma\ts N})\tensor \deno{\Gamma\ts P})" description] \\
-            ((\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \arrow[d, "((\deno{\Gamma\ts M} \tensor \sigma') \tensor \deno{\Gamma\ts N}) \tensor \deno{\Gamma\ts P}" {description, xshift=-20pt}, thick, dashed] \arrow[ur, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}}}" description, to=Z.west, dotted]
-              \& |[alias=Y]| (\deno T \tensor (A' \tensor X)) \tensor X \arrow[r, "{\assoc_{\deno T,A'\tensor X,X}}" description, dotted] \arrow[d, "{\wk_{T,A'\tensor X}\tensor X}" description, dotted]
-                \& \deno T \tensor ((A' \tensor X) \tensor X) \arrow[d, "{\wk_{\deno T,(A'\tensor X)\tensor X}}"] \\
-            ((\deno T\tensor A') \tensor X)\tensor X \arrow[ur, "{\assoc_{\deno T,A',X}\tensor X}" description, to=Y.west, dotted] \arrow[d, "{(\wk_{\deno T,A'}\tensor X)\tensor X}"', thick, dashed]
-              \& (\deno T \sequoid (A' \tensor X))\tensor X \arrow[dr, "{\wk_{\deno T\sequoid (A'\tensor X),X}}" description, dotted] \arrow[d, "{\passoc_{\deno T,A',X}\tensor X}" description, dotted]
-                \& \deno T \sequoid ((A' \tensor X)\tensor X) \arrow[d, "{\passoc_{\deno T,A'\tensor X,X}\inv}"] \\
-            ((\deno T\sequoid A') \tensor X) \tensor X \arrow[r, "{\wk_{\deno T \sequoid A',X}\tensor X}", dotted] \arrow[d, "(\tau'\tensor X)\tensor X)"', thick, dashed]
-              \& ((\deno T \sequoid A') \sequoid X) \tensor X \arrow[dr, "{\wk_{(\deno T\sequoid A') \sequoid X,X}}" description, dotted] \arrow[d, "(\tau'\sequoid X)\tensor X" description, dotted]
-                \& (\deno T \sequoid (A' \tensor X)) \sequoid X \arrow[d, "{\passoc_{\deno T,A',X}\inv\sequoid X}"] \\
-            (Y \tensor X) \tensor X \arrow[r, "{\wk_{Y,X}\tensor X}", dotted] \arrow[d, "\Lambda\inv(\Lambda\inv(\eta))"', thick, dashed]
-              \& (Y \sequoid X) \tensor X \arrow[dr, "{\wk_{Y\sequoid X,X}}" description, dotted] \arrow[dl, "\Lambda\inv(\Lambda_s\inv(\eta))" description, dotted]
-                \& ((\deno T \sequoid A') \sequoid X) \sequoid X \arrow[d, "(\tau'\sequoid X) \sequoid X"] \\
-            X
-              \&
-                \& (Y \sequoid X)\sequoid X \arrow[ll, "\Lambda_s\inv(\Lambda_s\inv(\eta))"']
-          \end{tikzcd}
-          \]
-          \normalsize
-        \caption[The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.]{The property in Lemma \ref{LemEvContexLemma} is preserved by conditionals.
-        We use the fact that $\eta\in\{\If_X,\IfO_X\}$ is a strict strategy, and that the $\Lambda_s\inv$ is a function from strict strategies to strict strategies, so that $\Lambda_s\inv(\Lambda_s\inv(\eta))$ is well-defined.}
-        \label{FigEvContextCond}
-      \end{SidewaysFigure}
-    \item Lastly, suppose that $\EE = \EE' \gets n$ for some numeral $n$, where $\EE'$ is a context of type $\Var$, and suppose that $M\from T$ fits into the hole.  
-      The denotation $\deno{\Gamma\ts \EE[M]}$ is given by
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts \EE'[M]}} \Varr \xrightarrow{\lunit_{\Varr}} I \tensor \Varr \xrightarrow{n\tensor\Varr} \bN \tensor \Varr \xrightarrow{\assign} \bC\,.
-        \]
-      By the induction hypothesis, $\deno{\Gamma\ts\EE'[M]}$ takes the form
-      \[
-        \oc{\deno{\Gamma}} \xrightarrow{\mu_{{\deno{\Gamma}}}}
-        \oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma'}
-        \deno{T}\tensor A' \xrightarrow{\wk_{\deno{T},A'}}
-        \deno T\sequoid A' \xrightarrow{\tau'}
-        \Varr\,,
-        \]
-      for suitable $A',\sigma',\tau'$.  
-      Then, if we compose on the right by the morphism $\lunit_{\Varr};(n\tensor\Varr);\assign$, in order to give us the denotation $\deno{\Gamma\ts \EE'[M]\gets n} = \deno{\Gamma\ts\EE[M]}$, then we are already in the required form, with
-      \begin{mathpar}
-        A = A' \and \sigma = \sigma' \and \tau = \tau';\lunit_{\Varr};(n\tensor\Varr);\assign\,.\hspace{1em plus 1fill}\qedhere
-      \end{mathpar}
-  \end{itemize}
-\end{proof}
-
-Our next lemma will help us deal with the base $\oopto$ rules.  
-We will then use Lemma \ref{LemEvContexLemma} to extend this to the $\opto$ relation.
-
-\begin{definition}
-  Let $\Gamma,s\ts M\from T$ be a term with store.  
-  Then the \emph{sequoidal denotation} $\seqdeno{\Gamma,s\ts M}$ is the composite
-  \[
-    I \xrightarrow{\ms\ms\ms\oc\deno s\ms\ms} \oc S_\Gamma \xrightarrow{\ms\ms\ms\cell^\Gamma\ms\ms} \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\mu_{\deno{\Gamma}}\ms\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\ms\ms\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma}\ms\ms} \deno T \tensor\oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\ms\ms\wk_{\deno T,\oc\deno{\Gamma}}\ms\ms} \deno T \sequoid \oc\deno{\Gamma}.
-    \]
-\end{definition}
-
-\begin{lemma}
-  The relation $\oopto$ between triples $\Gamma,s\ts M$ preserves the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.
-
-  In other words, if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, then the following diagram commutes.
-  \[
-    \begin{tikzcd}[column sep=25pt, row sep=25pt]
-      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno s'"']
-        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc \deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
-            &[22pt] \oc \deno{\Gamma} \tensor \oc \deno{\Gamma} \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma" description] \\
-      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
-        &
-          &
-            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc {\deno{\Gamma}}}}" description] \\
-      {\oc {\deno{\Gamma,\Delta}}} \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
-        &
-          &
-            &  \deno{T}\sequoid \oc\deno{\Gamma} \\
-      {\oc {\deno{\Gamma,\Delta}} \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[rr, "{\deno{\Gamma,\Delta\ts N} \tensor \oc {\deno{\Gamma,\Delta}}}"]
-        &
-          & {\deno T \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[r, "{\wk_{\deno T,\oc {\deno{\Gamma,\Delta}}}}"]
-            & {{\deno T \sequoid \oc {\deno{\Gamma,\Delta}}}\,.} \arrow[u, "\deno{T}\sequoid\oc\pr_\Gamma"' description]
-    \end{tikzcd}
-    \]
-  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, then $\seqdeno{\Gamma,s\ts M} = \seqdeno{\Gamma,\Delta,s'\ts N};\oc\pr_\Gamma$.
-  \label{LemSoundnessOopto}
-\end{lemma}
-\begin{proof}
-  We prove this on a case-by-case basis.
-  \begin{itemize}
-    \item For most of the rules, $\Delta=\_$ and $s=s'$; i.e., the rule is of the form
-      \[
-        \Gamma,s\ts M \oopto \Gamma,s \ts N
-        \]
-      for some $M,N$.
-      In such a case, it suffices to show that $\deno{\Gamma\ts M}=\deno{\Gamma\ts N}$.
-      Indeed, we have
-      \begin{itemize}
-        \item $\deno{\Gamma\ts(\lambda x.M)N} = \deno{\Gamma\ts M[N/x]}$ (by a usual substitution-lemma argument);
-        \item $\deno{\Gamma\ts\Y M} = \deno{\Gamma\ts (\lambda F.\lambda f.f(F f)) \Y M} = \deno{\Gamma\ts M(\Y M)}$;
-        \item $\deno{\Gamma\ts \suc n} = \deno{\Gamma \ts n+1}$;
-        \item $\deno{\Gamma\ts \pred (n+1)} = \deno{\Gamma\ts n}$;
-        \item $\deno{\Gamma\ts \pred 0} = \deno{\Gamma\ts 0}$;
-        \item $\deno{\Gamma\ts\skipp;M} = \deno{\Gamma\ts M}$;
-        \item $\deno{\Gamma\ts\If \true \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.x)NP} = \deno{\Gamma\ts N}$;
-        \item $\deno{\Gamma\ts\If \false \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
-        \item $\deno{\Gamma\ts\IfO 0 \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.x)NP} = \deno{\Gamma\ts N}$;
-        \item $\deno{\Gamma\ts\IfO (n+1) \Then N \Else P} = \deno{\Gamma\ts (\lambda x.\lambda y.y)NP} = \deno{\Gamma\ts P}$;
-        \item \parbox[t][][t]{0.8\textwidth}{$\deno{\Gamma\ts(\mkvar W\,R)\gets n} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_n = \deno{\Gamma\ts Wn}$; and}
-        \item $\deno{\Gamma\ts\oc(\mkvar W\,R)} = \langle \deno{\Gamma\ts Wn}_{n\in\bN},\deno{\Gamma\ts R}\rangle;\pr_{\bN} = \deno{\Gamma\ts R}$.
-      \end{itemize}
-    \item Now consider the rule
-      \[
-        \Gamma,s\ts\neww \lambda x.M\oopto \Gamma,x,(s\vert x\mapsto 0)\ts M\,,
-        \]
-      where $\Gamma\ts M\from T$.
-      The first observation to make is that the denotation $\deno{\Gamma\ts \neww \lambda x.M}$ may be written as
-      \[
-        \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\ms\runit_{\oc\deno{\Gamma}}\ms\ms\ms} \oc\deno{\Gamma} \tensor I \xrightarrow{\ms\ms\ms\ms\oc\deno{\Gamma}\tensor (0;\cell)\ms\ms\ms\ms} \oc\deno{\Gamma} \tensor \oc\Varr \to \oc{\deno{\Gamma,x}} \xrightarrow{\ms\ms\ms\ms\Lambda\inv(\deno{\Gamma \ts \lambda x.M})\ms\ms\ms} \deno{T},
-        \]
-      where, of course $\Lambda\inv(\deno{\Gamma\ts\lambda x.M})=\deno{\Gamma,x\ts M}$, and that the projection $\pr_\Gamma \from \oc{\deno{\Gamma,x}}$ is a right inverse for the composite $\runit_{\oc\deno{\Gamma}};(\oc{\deno{\Gamma}}\tensor(0;\cell));\cong$, since we have a commutative diagram
-      \[
-        \begin{tikzcd}[column sep=50pt]
-          \oc\deno{\Gamma} \arrow[r, "\runit_{\oc\deno{\Gamma}}"] \arrow[d, Rightarrow, no head]
-            & \oc\deno{\Gamma} \tensor I \arrow[r, "\oc\deno{\Gamma}\tensor(0;\cell)"] \arrow[d, "\id_{\oc\deno{\Gamma}\tensor I}" description]
-              & \oc\deno{\Gamma} \tensor \oc\Varr \arrow[d] \arrow[dl, "\oc\deno{\Gamma}\tensor()" description] \\
-          \oc\deno{\Gamma}
-            & \oc\deno{\Gamma} \tensor I \arrow[l, "\runit\inv"']
-              & {\oc{\deno{\Gamma,x}}\,.} \arrow[ll, "\oc\pr_\Gamma", bend left=20]
-        \end{tikzcd}
-        \]
-      Then we may prove this case using the commutative diagram in Figure \ref{FigSoundnessOoptoNew}.
-      \begin{SidewaysFigure}
-        \[
-          \begin{tikzcd}[ampersand replacement=\&, column sep=50pt, row sep=50pt]
-            I \arrow[r, "\oc\deno s"] \arrow[d, "{\oc\langle\deno s,0\rangle}" description]
-              \&[5pt] \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-                \&[-5pt] \oc\deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"] \arrow[d, "\mu_{\deno{\Gamma}}" description]
-                  \& \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[d, "\runit_{\oc\deno{\Gamma}};(\oc\deno{\Gamma}\tensor (0;\cell));\cong" {description, xshift=-16pt}] \\
-            {\oc S_{\Gamma,x}} \arrow[ur, "\oc\pr_\Gamma" description] \arrow[d, "{\cell^{\Gamma,x}}" description]
-              \&
-                \& \oc\deno{\Gamma}\tensor\oc\deno{\Gamma}
-                  \& {\oc{\deno{\Gamma,x}}\tensor\oc\deno{\Gamma}} \arrow[d, "{\deno{\Gamma,x\ts M}\tensor\oc\deno{\Gamma}}" description] \arrow[l, "\pr_\Gamma\tensor\oc\deno{\Gamma}"'] \\
-            {\oc{\deno{\Gamma,x}}} \arrow[uurr, "\oc\pr_\Gamma" description] \arrow[d, "{\mu_{{\deno{\Gamma,x}}}}"']
-              \&
-                \&
-                  \& \deno T \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\deno{\Gamma}}}" description] \\
-            {\oc{\deno{\Gamma,x}}\tensor\oc{\deno{\Gamma,x}}} \arrow[uurr, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma" {description, pos=0.7}] \arrow[uurrr, "{{\deno{\Gamma,x}}\tensor\pr_\Gamma}" {description, pos=0.7}] \arrow[r, "{\deno{\Gamma,x\ts M}\tensor\oc{\deno{\Gamma,x}}}"' yshift=-3pt]
-              \& {\deno T \tensor \oc{\deno{\Gamma,x}}} \arrow[r, "{\wk_{\deno T,\oc{\deno{\Gamma,x}}}}"' yshift=-3pt]
-                \& {\deno T \sequoid \oc{\deno{\Gamma,x}}} \arrow[r, "\deno T \sequoid\pr_\Gamma"' yshift=-3pt]
-                  \& \deno T \sequoid\oc\deno{\Gamma}
-          \end{tikzcd}
-          \]
-        \caption{The conclusion of Lemma \ref{LemSoundnessOopto} holds for the $\neww$ rule.}
-        \label{FigSoundnessOoptoNew}
-      \end{SidewaysFigure}
-    \item Now consider the rules
-      \begin{mathpar}
-        x,\Gamma,s\ts x\gets n \oopto x,\Gamma,(s\vert x\mapsto n) \ts \skipp
-        \and
-        x,\Gamma,s\ts \oc x\oopto x,\Gamma,s\ts s(x)\,.
-      \end{mathpar}
-      In each of these cases, the outer context $\Gamma$ is unchanged by the rule; moreover, each term ignores the variables in $\Gamma$.
-      So the denotations terms-in-context $x,\Gamma\ts M\from T$ on either side of each rule are of the form
-      \[
-        \oc{\deno{x,\Gamma}} \xrightarrow{\oc\pr_1} \oc \Varr \xrightarrow{\deno{x\ts M}} \deno{T}\,.
-        \]
-      Now the diagram in Figure \ref{FigSoundnessOoptoContext} tells us that each $\seqdeno{\Gamma,x,s\ts M}$ may be written as the composite
-      \begin{mathpar}
-        \oc\deno{s\vert_\Gamma};\cell^\Gamma;\lunit_{\oc\deno{\Gamma}};\\((\oc\deno{s\vert_x};\cell;\mu_{\Varr};(\deno{x\ts M}\tensor\oc\Varr);\wk_{\deno T,\oc\Varr})\tensor\oc\deno{\Gamma});\\\wk_{\deno T\sequoid \oc\Varr,\oc\deno{\Gamma}};\passoc_{\deno T,\oc\Varr,\oc\deno{\Gamma}};\cong
-      \end{mathpar}
-      (where $\cong$ represents the natural isomorphism between the games $\deno T\sequoid(\oc\Varr\tensor\oc\deno{\Gamma})$ and $\deno T \sequoid\oc{\deno{x,\Gamma}}$),
-      and so is completely determined by the value of the composite
-      \[
-        \oc\deno{s\vert_x};\cell;\mu_{\Varr};(\deno{x\ts M}\tensor\oc\Varr);\wk_{\deno T,\oc\Varr}\,;
-        \]
-      i.e., the sequoidal denotation $\seqdeno{x,s\vert_x\ts M}$.
-
-      This tells us that we can assume that $\Gamma$ is the empty context, so that the rules take on the form
-      \begin{mathpar}
-        x,s\ts x\gets n \oopto x,(x\mapsto n)\ts \skipp
-        \and
-        x,s \ts \oc x \oopto x,s\ts s(x)\,.
-      \end{mathpar}
-      \begin{SidewaysFigure}
-        \small
-        \[
-          \begin{tikzcd}[ampersand replacement=\&, column sep=5pt]
-            I \arrow[r, "\oc\deno{s\vert_\Gamma}"] \arrow[d, "\oc\deno s"' {description, yshift=2pt}, thick, dashed]
-              \& \oc S_\Gamma \arrow[r, "\cell^\Gamma"] \arrow[dr, "\lunit_{\oc S_\Gamma}" description, dotted]
-                \&[18pt] \oc \deno{\Gamma} \arrow[r, "\lunit_{\oc\deno{\Gamma}}"] 
-                  \&[17pt] I \tensor \oc\deno{\Gamma} \arrow[dd, "\oc\deno{s\vert_x}\tensor\oc\deno{\Gamma}" description, thick] \\
-            {\oc S_{x,\Gamma}} \arrow[drr, Isom, dotted] \arrow[dd, "{\cell^{x,\Gamma}}"' description, thick, dashed]
-              \&
-                \& I \tensor \oc S_\Gamma \arrow[ur, "I \tensor\cell^\Gamma" description, dotted] \arrow[d, "\oc\deno{s\vert_x}\tensor\oc S_\Gamma" description, dotted]
-                  \& \\
-            %
-              \&
-                \& \oc\bN\tensor\oc S_\Gamma \arrow[r, "\oc\bN\tensor\cell^\Gamma" description, dotted] \arrow[dr, "\cell\tensor\cell^\Gamma" description, dotted]
-                  \& \oc\bN \tensor\oc\deno{\Gamma} \arrow[d, "\cell\tensor\oc\deno{\Gamma}" description, thick] \\
-            {\oc{\deno{x,\Gamma}}} \arrow[rrr, Isom, dotted] \arrow[d, "{\mu_{{\deno{x,\Gamma}}}}"' description, thick, dashed]
-              \&
-                \&
-                  \& \oc\Varr \tensor \oc\deno{\Gamma} \arrow[d, "\mu_{\Varr}\tensor\oc\deno{\Gamma}" description, thick] \arrow[dl, "\mu_{\Varr}\tensor\mu_{\deno{\Gamma}}" description, bend right=15, dotted] \\[10pt]
-            {\oc{\deno{x,\Gamma}}\tensor\oc{\deno{x,\Gamma}}} \arrow[r, dotted] \arrow[d, "{\oc\pr_1\tensor\oc{\deno{x,\Gamma}}}" description, dotted] \arrow[dd, "{\deno{x,\Gamma\ts M}\tensor\oc{\deno{x,\Gamma}}}" description, bend right=68, thick, dashed, end anchor={[xshift=-3pt]}]
-              \& (\oc\Varr \tensor \oc\deno{\Gamma}) \tensor (\oc\Varr \tensor\oc\deno{\Gamma}) \arrow[r, dotted] \arrow[d, "(\oc\Varr\tensor())\tensor(\oc\Varr\tensor\oc{\deno{\Gamma}})" description, dotted]
-                \& (\oc\Varr \tensor \oc\Varr) \tensor (\oc\deno{\Gamma} \tensor\oc\deno{\Gamma}) \arrow[r, "(\oc\Varr\tensor\oc\Varr)\tensor(()\tensor\oc\deno{\Gamma})" yshift=5pt, dotted]
-                  \& (\oc\Varr \tensor \oc\Varr) \tensor\oc\deno{\Gamma} \arrow[d, "(\deno{x\ts M}\tensor \oc\Varr) \tensor \oc\deno{\Gamma}" description, thick] \\[30pt]
-            {\oc\Varr \tensor \oc{\deno{x,\Gamma}}} \arrow[r, Isom, dotted] \arrow[d, "{\deno{x\ts M} \tensor \oc{\deno{x,\Gamma}}}"' {description, yshift=1pt}, dotted]
-              \& \oc\Varr \tensor (\oc\Varr \tensor\oc\deno{\Gamma}) \arrow[urr, "{\assoc_{\oc\Varr,\oc\Varr,\oc\deno{\Gamma}}\inv}" {description, xshift=-5pt, yshift=5pt}, start anchor={[xshift=-25pt]}, bend left=5, dotted] \arrow[r, "\deno{x\ts M} \tensor (\oc\Varr\tensor\oc\deno{\Gamma})" yshift=2pt, dotted]
-                \& \deno{T} \tensor (\oc\Varr \tensor \oc\deno{\Gamma}) \arrow[r, "{\assoc_{\deno T,\oc\Varr,\oc\deno{\Gamma}}}" yshift=2pt, dotted] \arrow[ddl, "{\wk_{\deno T,(\oc\Varr\tensor\oc\deno{\Gamma})}}" description, dotted]
-                  \& (\deno T \tensor \oc\Varr) \tensor \oc\deno{\Gamma}\arrow[d, "{\wk_{\deno T,\oc\Varr}\tensor\oc\deno{\Gamma}}" {description, yshift=1pt}, thick] \\
-            {\deno T \tensor \oc{\deno{x,\Gamma}}} \arrow[d, "{\wk_{\deno T,\oc{\deno{x,\Gamma}}}}"' {description, yshift=2pt}, thick, dashed] \arrow[urr, Isom, dotted]
-              \&
-                \&
-                  \& (\deno T \sequoid \oc\Varr) \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{(\deno T\sequoid\oc\Varr),\oc\deno{\Gamma}}}" {description, yshift=2pt}] \\[5pt]
-            {\deno T \sequoid \oc{\deno{x,\Gamma}}} \arrow[r, Isom]
-              \& \deno T \sequoid (\oc\Varr \tensor\oc\deno{\Gamma})
-                \&
-                  \& (\deno T \sequoid \oc\Varr) \sequoid\oc\deno{\Gamma} \arrow[ll, "{\passoc_{\deno T,\oc\Varr,\oc\deno{\Gamma}}}"]
-          \end{tikzcd}
-          \]
-          \normalsize
-          \caption{Diagram proving that if we want to prove the conclusion of Lemma \ref{LemSoundnessOopto} for a small-step rule that does not change the context and only mentions one variable, then it suffices to assume that that variable is the only variable in the context.}
-          \label{FigSoundnessOoptoContext}
-      \end{SidewaysFigure}
-
-      Now the commutative diagrams in Figure \ref{FigSoundnessOoptoStorage} prove that
-      \[
-        \seqdeno{x,s\vert_x\ts x\gets n} = \seqdeno{x,(x\mapsto n)\ts \skipp}
-        \]
-      and that
-      \[
-        \seqdeno{x,s\vert_x\ts \oc x} = \seqdeno{x,s\vert_x\ts s(x)}\,,
-        \]
-      completing the proof.\qedhere
-      \begin{figure}[htbp]
+\begin{figure}[p]
   \begin{mathpar}
@@
         & \oc \bN \arrow[r, "\cell"] \arrow[d, "()" description] \arrow[dr, "\cell_0" description]
-                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}] \arrow[dr, phantom, "\text{P.
-\ref{PropFormulaForAlpha}}" {xshift=20pt, yshift=-7pt}]
+          & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}]
             & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" {description, near start}]  \\
-            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}] \arrow[ddrr, phantom, "\text{L.
-\ref{LemCellProjections}}" {xshift=2pt, yshift=20pt}]
+      \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}]
         & I \arrow[l, "\oc n" description]
@@
     \end{tikzcd}
-          \and
+    \vspace{48pt}\and
     \begin{tikzcd}[row sep=30pt]
       I \arrow[r, "\oc s(x)"] \arrow[d, "\oc s(x)" description] \arrow[dr]
-              &[-31pt] \oc\bN \arrow[r, "\cell"] \arrow[dr, "\mu_\bN" description] \arrow[ddr, "\cell_0" {description, near end}, bend left=50, end anchor={[xshift=4pt]}] \arrow[ddd, phantom, "\text{L.\ref{LemCellProjections}}" {xshift=3pt,yshift=-7pt}]
-                &[-100pt] \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[ddd, "\alpha_{\Varr}" description] \arrow[dr, phantom, "\text{P.\ref{PropFormulaForAlpha}}", {yshift=-5pt}]
+        &[-31pt] \oc\bN \arrow[r, "\cell"] \arrow[dr, "\mu_\bN" description] \arrow[ddr, "\cell_0" {description, near end}, bend left=50, end anchor={[xshift=4pt]}]
+          &[-100pt] \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[ddd, "\alpha_{\Varr}" description]
             &[-21pt] \oc\Varr \tensor \oc\Varr \arrow[d, "\der_{\Varr}\tensor\oc\Varr" {description, near start}] \\
@@
   \end{mathpar}
-        \caption[Diagrams to prove that the conclusion of Lemma \ref{LemSoundnessOopto} holds for the storage cell rules.]{Diagrams to prove that the conclusion of Lemma \ref{LemSoundnessOopto} holds for the storage cell rules.
-        References in the middle of a shape refer to Lemma \ref{LemCellProjections} and Proposition \ref{PropFormulaForAlpha} above.  
-        Note the prominent role played in both diagrams by the anamorphism square for $\cell$ as in Section \ref{SecCell}.}
-        \label{FigSoundnessOoptoStorage}
 \end{figure}
-  \end{itemize}
-\end{proof}
-
-Now that we have dealt with the base rules, we can move on to the full relation $\opto$.
-
-\begin{lemma}
-  The relation $\opto$ between triples $\Gamma,s\ts M$ preserves the composite
-  \[
-    \oc\deno s;\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}}\,.
-    \]
-  I.e., if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, where $M,N$ have type $T$, and $\EE$ is a context of type $U$ with a hole of type $T$, then the following diagram commutes.
-  \[
-    \begin{tikzcd}[column sep=24pt]
-      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno {s'}"']
-        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc \deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
-            &[22pt] \oc \deno{\Gamma} \tensor \oc \deno{\Gamma} \arrow[d, "\deno{\Gamma\ts \EE[M]}\tensor \oc V_\Gamma" description] \\
-      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
-        &
-          &
-            & \deno U \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno U,\oc {\deno{\Gamma}}}}" description] \\
-      {\oc {\deno{\Gamma,\Delta}}} \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
-        &
-          &
-            &  \deno{U}\sequoid \oc\deno{\Gamma} \\
-      {\oc {\deno{\Gamma,\Delta}} \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[rr, "{\deno{\Gamma,\Delta\ts \EE[N]} \tensor \oc {\deno{\Gamma,\Delta}}}"]
-        &
-          & {\deno U \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[r, "{\wk_{\deno U,\oc {\deno{\Gamma,\Delta}}}}"]
-            & {{\deno U \sequoid \oc {\deno{\Gamma,\Delta}}}\,,} \arrow[u, "\deno U \sequoid \oc\pr_\Gamma" description]
-    \end{tikzcd}
-    \]
-  \label{LemSoundnessOpto}
-\end{lemma}
-\begin{proof}
-  We use Lemma \ref{LemEvContexLemma} to reduce this to Lemma \ref{LemSoundnessOpto}.  
-  Indeed, Lemma \ref{LemEvContexLemma} tells us that for any $\Gamma,s\ts M$, $\deno{\Gamma\ts \EE[M]}$ may be written as
-  \[
-    \oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma}\tensor\oc\deno{\Gamma} \xrightarrow{\deno{\Gamma\ts M}\tensor\sigma} \deno T \tensor A \xrightarrow{\wk_{\deno T,A}} \deno T \sequoid A \xrightarrow{\tau} \deno U
-    \]
-  for suitably chosen $A,\sigma,\tau$.
-
-  Let us write $\seqdeno{\Gamma,s\ts M}$ for the composite
-  \[
-    \oc\deno s;\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}};(\deno T \sequoid (\Gamma+0_\Delta))\,.
-    \]
-  So we are trying to show that $\seqdeno{\Gamma,s\ts \EE[M]}=\seqdeno{\Gamma,\Delta,s'\ts \EE[N]};(\deno U \sequoid \oc\pr_\Gamma)$.
-
-  Now the diagram in Figure \ref{FigSoundnessOpto} shows us that for any $\Gamma,s\ts M$ we may write
-  \[
-    \seqdeno{\Gamma,s\ts \EE[M]} = \seqdeno{\Gamma,s\ts M};(\deno T \sequoid (\mu_{\deno{\Gamma}};(\sigma\tensor\oc\deno{\Gamma}));\passoc_{\deno T,A,\oc\deno{\Gamma}}\inv;(\tau\sequoid\oc\deno{\Gamma})\,.
-    \]
-
-  \begin{SidewaysFigure}
-    \[
-      \begin{tikzcd}[column sep=46pt, row sep=30pt, ampersand replacement=\&]
-        \oc{\deno{\Gamma}} \arrow[r, "\mu_{{\deno{\Gamma}}}", thick] \arrow[d, "\mu_{{\deno{\Gamma}}}"' description, thick, dashed]
-          \& \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[r, "\deno{\Gamma\ts M}\tensor\oc{\deno{\Gamma}}", thick] \arrow[dd, "\oc{\deno{\Gamma}}\tensor\mu_{{\deno{\Gamma}}}" description, dotted]
-            \& \deno T \tensor \oc{\deno{\Gamma}} \arrow[r, "{\wk_{\deno T,\oc{\deno{\Gamma}}}}", thick] \arrow[dd, "\deno T \tensor \mu_{{\deno{\Gamma}}}" description, dotted]
-              \& \deno T \sequoid \oc{\deno{\Gamma}} \arrow[dd, "\deno T \sequoid \mu_{{\deno{\Gamma}}}" description] \\
-        \oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}} \arrow[d, "\mu_{{\deno{\Gamma}}}\tensor\oc{\deno{\Gamma}}"' description, thick, dashed]
-          \&
-            \&
-              \& \\
-        (\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\assoc_{\oc{\deno{\Gamma}},\oc{\deno{\Gamma}},\oc{\deno{\Gamma}}}}" yshift=3pt, dotted] \arrow[d, "(\deno{\Gamma\ts M}\tensor \sigma) \tensor\oc{\deno{\Gamma}}"' description, thick, dashed]
-          \& \oc{\deno{\Gamma}} \tensor (\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \arrow[r, "\deno{\Gamma\ts M} \tensor (\oc{\deno{\Gamma}}\tensor \oc{\deno{\Gamma}})" yshift=3pt, dotted] \arrow[d, "\deno{\Gamma\ts M}\tensor (\sigma\tensor\oc{\deno{\Gamma}})" description, dotted]
-            \& \deno T \tensor (\oc{\deno{\Gamma}}\ \tensor \oc{\deno{\Gamma}}) \arrow[r, "{\wk_{\deno T,\oc{\deno{\Gamma}}\tensor\oc{\deno{\Gamma}}}}" yshift=3pt, dotted] \arrow[dl, "\deno T \tensor (\sigma \tensor\oc{\deno{\Gamma}})" description, dotted]
-              \& \deno T \sequoid (\oc{\deno{\Gamma}} \tensor \oc{\deno{\Gamma}}) \arrow[d, "\deno T \sequoid (\sigma \tensor \oc{\deno{\Gamma}})" description] \\
-        (\deno T \tensor A) \tensor \oc{\deno{\Gamma}} \arrow[d, "{\wk_{\deno T,A}\tensor\oc{\deno{\Gamma}}}"' description, thick, dashed] \arrow[r, "{\assoc_{\deno T,A,\oc{\deno{\Gamma}}}}", dotted]
-          \& \deno T \tensor (A \tensor \oc{\deno{\Gamma}}) \arrow[rr, "{\wk_{\deno T,A\tensor\oc{\deno{\Gamma}}}}", dotted]
-            \&
-              \& \deno T \sequoid (A \tensor \oc{\deno{\Gamma}}) \\
-        (\deno T \sequoid A) \tensor \oc{\deno{\Gamma}} \arrow[r, "{\wk_{\deno T\sequoid A,\oc{\deno{\Gamma}}}}", dotted] \arrow[d, "\tau\tensor\oc{\deno{\Gamma}}" description, thick, dashed]
-          \& (\deno T \sequoid A) \sequoid \oc{\deno{\Gamma}} \arrow[d, "\tau\sequoid\oc{\deno{\Gamma}}"] \arrow[urr, "{\passoc_{\deno T,A,\oc{\deno{\Gamma}}}}"']
-            \&
-              \& \\
-        \deno U \tensor \oc{\deno{\Gamma}} \arrow[r, "{\wk_{\deno U,\oc{\deno{\Gamma}}}}", thick, dashed]
-          \& \deno U \sequoid \oc{\deno{\Gamma}}
-            \&
-              \&
-      \end{tikzcd}
-      \]
-      \caption{Diagram proving that the conclusion of Lemma \ref{LemSoundnessOopto} can be lifted to the $\opto$ relation.}
-      \label{FigSoundnessOpto}
-  \end{SidewaysFigure}
-
-  Therefore, Lemma \ref{LemSoundnessOopto} tells us that if $\Gamma,s\ts M \oopto \Gamma,\Delta,s'\ts N$, then we have
-  \begin{IEEEeqnarray*}{Cl}
-    & \seqdeno{\Gamma,s\ts \EE[M]} \\
-    = & \seqdeno{\Gamma,s\ts M};(\deno T\sequoid(\mu_{\deno{\Gamma}};(\sigma\tensor\oc\deno{\Gamma}));\passoc\inv;(\tau\sequoid\oc\deno{\Gamma}) \\
-    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid \oc\pr_\Gamma);(\deno T\sequoid(\mu_{\deno{\Gamma}};(\sigma\tensor\oc\deno{\Gamma}));\passoc\inv;(\tau\sequoid\oc\deno{\Gamma}) \\
-    = & \seqdeno{\Gamma,s\ts N};(\deno T \sequoid (\mu_{{\deno{\Gamma,\Delta}}};((\pr_\Gamma;\sigma)\tensor\oc{\deno{\Gamma,\Delta}})));\passoc\inv; \\
-    &\qquad(\tau\sequoid\oc\deno{\Gamma});(\deno U\sequoid\oc\pr_\Gamma) \\
-    = & \seqdeno{\Gamma,s\ts \EE[N]};(\deno U\sequoid\oc\pr_\Gamma)\,,
-  \end{IEEEeqnarray*}
-  as desired.
-\end{proof}
-
-It is now a simple induction to show that we can extend this to the $\converges$ relation.
-
-\begin{lemma}
-  Suppose that $\Gamma,s\ts M \converges c,s'$, where $M,c\from T$.
-  Then the following diagram commutes.
-  \[
-    \begin{tikzcd}[column sep=47pt]
-      I \arrow[r, "\oc\deno s"] \arrow[d, "\oc\deno{s'}" description]
-        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc\deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
-            & \oc\deno{\Gamma}\tensor\oc\deno{\Gamma} \arrow[d, "\deno{\Gamma\ts M}\tensor\oc\deno{\Gamma}" description] \\
-      \oc S_\Gamma \arrow[d, "\cell^\Gamma"' description]
-        &
-          &
-             & \deno{T} \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\deno{\Gamma}}}" description] \\
-      \oc\deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
-        & \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[r, "\deno{\Gamma\ts c}\tensor\oc\deno{\Gamma}"]
-          & \deno T \tensor \oc\deno{\Gamma} \arrow[r, "{\wk_{\deno T,\oc\deno{\Gamma}}}"]
-            & \deno T \sequoid \oc\deno{\Gamma}
-    \end{tikzcd}
-    \]
-  \label{LemSoundness}
-\end{lemma}
-\begin{proof}
-  By Proposition \ref{PropBigToSmall}, there are sequences $\Gamma=\Gamma_1,\cdots,\Gamma_n=\Gamma,\Delta$, $s=s^{(1)},\cdots,s^{(n)}$, $M=M_1,\cdots,M_n=c$ such that
-  \[
-    \Gamma_1,s^{(1)}\ts M_1 \opto \cdots \opto \Gamma_n,s^{(n)} \ts M_n\,,
-    \]
-  and $s^{(n)}\vert_\Gamma = s'$.
-
-  By inductively applying Lemma \ref{LemSoundnessOpto}, we see that we have a commutative diagram
-  \[
-    \begin{tikzcd}[column sep=25pt]
-      I \arrow[r, "\oc \deno s"] \arrow[d, "\oc \deno {s^{(n)}}"']
-        & \oc S_\Gamma \arrow[r, "\cell^\Gamma"]
-          & \oc \deno{\Gamma} \arrow[r, "\mu_{\deno{\Gamma}}"]
-            &[22pt] \oc \deno{\Gamma} \tensor \oc \deno{\Gamma} \arrow[d, "\deno{\Gamma\ts M}\tensor \oc V_\Gamma" description] \\
-      {\oc S_{\Gamma,\Delta}} \arrow[d, "{\cell^{\Gamma,\Delta}}"']
-        &
-          &
-            & \deno T \tensor \oc V_\Gamma \arrow[d, "{\wk_{\deno T,\oc {\deno{\Gamma}}}}" description] \\
-      {\oc {\deno{\Gamma,\Delta}}} \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
-        &
-          &
-            &  \deno{T}\sequoid \oc\deno{\Gamma} \\
-      {\oc {\deno{\Gamma,\Delta}} \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[rr, "{\deno{\Gamma,\Delta\ts c} \tensor \oc {\deno{\Gamma,\Delta}}}"]
-        &
-          & {\deno T \tensor \oc {\deno{\Gamma,\Delta}}} \arrow[r, "{\wk_{\deno T,\oc {\deno{\Gamma,\Delta}}}}"]
-            & {{\deno T \sequoid \oc {\deno{\Gamma,\Delta}}}\,,} \arrow[u, "\deno T \sequoid \oc\pr_\Gamma" description]
-    \end{tikzcd}
-    \]
-  Now, since $s^{(n)}\vert_\Gamma = s'$, we have a commutative diagram
-  \[
-    \begin{tikzcd}[column sep=50pt]
-      I \arrow[r, "\deno {s'}"] \arrow[d, "\deno{s^{(n)}}"']
-        & \oc S_\Gamma \arrow[dd, "\cell^\Gamma"] \\
-      {\oc S_{\Gamma,\Delta}} \arrow[ur, "\oc\pr_\Gamma" description] \arrow[d, "{\cell^{\Gamma,\Delta}}"']
-        & \\
-      {\oc{\deno{\Gamma,\Delta}}} \arrow[r, "\oc\pr_\Gamma"] \arrow[d, "{\mu_{{\deno{\Gamma,\Delta}}}}"']
-        & \oc\deno{\Gamma} \arrow[d, "\mu_{\deno{\Gamma}}"] \\
-      {\oc{\deno{\Gamma,\Delta}}\tensor\oc{\deno{\Gamma,\Delta}}} \arrow[d, "{\deno{\Gamma,\Delta\ts c}\tensor\oc{\deno{\Gamma,\Delta}}}"'] \arrow[r, "\oc\pr_\Gamma\tensor\oc\pr_\Gamma"]
-        & \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[d, "\deno{\Gamma\ts c}\tensor\oc\deno{\Gamma}"]  \\
-      {\deno T \tensor \oc{\deno{\Gamma,\Delta}}} \arrow[r, "\deno T \tensor \oc\pr_\Gamma"] \arrow[d, "{\wk_{\deno T,\oc{\deno{\Gamma,\Delta}}}}"']
-        & \deno T \tensor \oc\deno{\Gamma} \arrow[d, "{\wk_{\deno T,\oc\deno{\Gamma}}}"] \\
-      {\deno T \sequoid \oc{\deno{\Gamma,\Delta}}} \arrow[r, "\deno T \sequoid \oc\pr_\Gamma"]
-        & \deno T \sequoid \oc\deno{\Gamma} \\
-    \end{tikzcd}
-    \]
-  which, together with the diagram above, gives us the commutative diagram in the statement.
-\end{proof}
-
-It is then an easy corollary to show the sense in which our semantics is sound.
-
-\begin{proposition}[\cite{SamsonGuyIAActive}]
-  Suppose that $\Gamma,s\ts M\converges c,s'$.  
-  Then
-  \[
-    \deno s;\cell^\Gamma;\deno{\Gamma\ts M} = \deno{s'};\cell^\Gamma;\deno{\Gamma\ts c}\,.
-    \]
-  \label{PropSoundness}
-\end{proposition}
-\begin{proof}
-  Lemma \ref{LemSoundness}, plus the fact that if $\Gamma,s\ts P\from T$, then we have a commutative diagram
-  \[
-    \begin{tikzcd}[column sep=10.8pt]
-      I \arrow[r, "\deno{s}", thick]
-        & \oc S_\Gamma \arrow[r, "\cell^\Gamma", thick]
-          & \oc\deno{\Gamma} \arrow[rr, "\mu_{\deno{\Gamma}}", thick, dashed] \arrow[ddd, "\deno{\Gamma\ts P}"', thick] \arrow[drr, "\runit_{\oc\deno{\Gamma}}" description, dotted]
-            &
-              & \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \arrow[rr, "\deno{\Gamma\ts P}\tensor\oc\deno{\Gamma}", thick, dashed] \arrow[d, "\oc\deno{\Gamma}\tensor()" description, dotted]
-                &
-                  & \deno T \tensor\oc\deno{\Gamma} \arrow[ddd, "{\wk_{\deno T,\oc\deno{\Gamma}}}" description, thick, dashed] \arrow[ddl, "\deno T \tensor ()" description, dotted] \\
-      %
-        &
-          &
-            &
-              & \oc\deno{\Gamma} \tensor I \arrow[dr, "\deno{\Gamma\ts P}\tensor I" description, dotted] \arrow[dl, "{\wk_{\oc\deno{\Gamma},I}}" description, dotted]
-                &
-                  & \\
-      %
-        &
-          &
-            & \oc\deno{\Gamma} \sequoid I \arrow[dr, "\deno{\Gamma\ts P}\sequoid I" description, dotted] \arrow[uul, "\run_{\oc\deno{\Gamma}}" description, dotted]
-              &
-                & \deno T \tensor I \arrow[dl, "{\wk_{\deno T,I}}" description, dotted]
-                  & \\
-      %
-        &
-          & \deno T
-            &
-              & \deno T \sequoid I \arrow[ll, "{\run_{\deno T}}"']
-                &
-                  & \deno T \sequoid \oc\deno{\Gamma} \arrow[ll, "\deno T \sequoid()"']\,,
-    \end{tikzcd}
-    \]
-  allowing us to recover $\deno{s};\cell^\Gamma;\deno{\Gamma\ts P}$ from 
-  \[
-    \seqdeno{\Gamma,s\ts P} = \deno{s};\cell^\Gamma;\mu_{\deno{\Gamma}};(\deno{\Gamma\ts P}\tensor\oc\deno{\Gamma});\wk_{\deno T,\oc\deno{\Gamma}}\,,
-    \]
-  for $P=M,c$.
-\end{proof}
-
-\section{Computational Adequacy}
-
-Our proof of computational adequacy is based on that from \cite{SamsonGuyIAActive}, but modified to make use of the coalgebraic definition of the $\cell$ strategy.  
-As is usual in proofs of computational adequacy, our proof relies on logical relations.
-
-First, we note some additional order-theoretic properties of our model.  
-For any game $A$, we have a strategy $\bot_A\from A$, given by $\bot_A=\{\epsilon\}$; i.e., the strategy that has no reply even for the very first move.  
-It is clear that $\bot$ is the bottom element of the set of strategies for $A$, ordered by inclusion.
-
-It is then easy to see the following.
-\begin{proposition}
-  \begin{itemize}
-    \item Given $\sigma\from A \implies B$, $\sigma;\bot_{B\implies C}=\bot_{A\implies C}$.
-    \item Given a strict strategy $\tau\from B\implies C$, $\bot_{A\implies B};\tau=\bot_{A\implies C}$.
-    \item $\bot_{A\implies B}$ is a strict strategy and $\bot_{A\implies B}\sequoid\sigma=\bot_{(A\sequoid C)\implies (B\sequoid D)}$ for any $\sigma\from C\implies D$.
-    \item $\Lambda(\bot_{A\tensor B\implies C})=\bot_{A\implies(B\implies C)}$.
-    \item Given a zigzag (copycat) strategy $\zz_\phi\from B \implies C$ and a strategy $\sigma\from A\implies B$, if $\sigma;\zz_\phi=\bot_{A\implies C}$ then $\sigma=\bot_{A\implies B}$.
-  \end{itemize}
-\end{proposition}
-
-\begin{definition}
-  Given a $\Var$-store $\Gamma$, a strategy $\sigma\from\oc\deno{\Gamma} \implies A$ and a $\Gamma$-store $s$, we write
-  \[
-    \seqdeno{s,\sigma}
-    \]
-  for the composite
-  \[
-    I \xrightarrow{\oc\deno s} \oc S_\Gamma \xrightarrow{\cell^\Gamma} \oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma\tensor\oc\deno{\Gamma}} A \tensor \oc\deno{\Gamma} \xrightarrow{\wk_{A,\oc\deno{\Gamma}}} A \sequoid \oc\deno{\Gamma}\,.
-    \]
-  In particular, if $\Gamma\ts M\from T$ is a term in context, then $\seqdeno{s,\deno{\Gamma\ts M}}$ is equal to the sequoidal denotation $\seqdeno{\Gamma,s\ts M}$.
-\end{definition}
-
-\begin{definition}
-  We inductively define a relation $\plot_T^\Gamma$, where $\Gamma$ is a $\Var$-store and $T$ a type, between strategies $\sigma\from\oc\deno{\Gamma} \implies \deno T$ and terms $\Gamma\ts M\from T$ in context as follows.
-  \begin{itemize}
-    \item If $X\in\{\bC,\bB,\bN\}$ is a datatype, $M\from X$ and $\sigma\from \oc\deno{\Gamma}\implies X$, then we say that $\sigma \plot_X^\Gamma u$ if for all $\Gamma$-stores $s$, either $\seqdeno{s,\sigma}=\bot_{A\sequoid\oc\deno{\Gamma}}$ or $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$ for some $\Gamma$-store $s'$ and some canonical form $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
-
-    \item If $\sigma\from \oc\deno{\Gamma} \implies \Varr$ and $\Gamma\ts M\from \Var$, we say that $\sigma\plot_{\Var}^\Gamma M$ if
-      \[
-        \sigma;\pr_n\plot_{\com}^\Gamma M\gets n
-        \]
-      for all $n$, and if
-      \[
-        \sigma;\pr_{\bN}\plot_{\nat}^\Gamma \oc M\,.
-        \]
-
-    \item If $\sigma \from \oc\deno{\Gamma} \implies (\oc\deno{S} \implies \deno T)$ and $M\from S \to T$, we say that $\sigma\plot_{S\to T}^\Gamma M$ if whenever $\tau\from \oc\deno{\Gamma} \implies \deno S$ is a strategy and $N\from S$ is a term such that $\tau\plot_S^\Gamma N$, then
-      \[
-        \left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N.
-        \]
-  \end{itemize}
-\end{definition}
-
-\begin{lemma}
-  Let $\Gamma\ts M,N\from T$ be terms in context of Idealized Algol such that
-  \[
-    \Gamma,s\ts M\opto \Gamma,s\ts N
-    \]
-  for all $\Gamma$-stores $s$.  
-  Suppose $\sigma\from\oc\deno{\Gamma}\implies\deno T$ is a strategy such that $\sigma\plot_T^\Gamma N$.  
-  Then $\sigma\plot_T^\Gamma M$.
-  \label{LemAdequacyOpto}
-\end{lemma}
-\begin{proof}
-  Induction on $T$.
-
-  Suppose that $\Gamma,s\ts M,N\ts X$, where $X$ is some datatype, and that $\Gamma,s\ts M\opto \Gamma,s\ts N$ for all $\Gamma$-stores $s$.  
-  Fix some $\Gamma$-store $s$ and some strategy $\sigma\from \oc\deno{\Gamma}\implies \deno T$, and suppose that $\sigma\plot_T^\Gamma N$.
-
-  If $\seqdeno{s,\sigma}\ne\bot_{\oc\deno{\Gamma}\implies X}$, then by hypothesis it is equal to $\seqdeno{s',u}$ for some $u$ such that $\Gamma,s\ts N\converges u,s'$.  
-  Then, by Lemma \ref{LemSmallToBig}, $\Gamma,s\ts M\converges u,s'$.
-
-  If $\Gamma,s\ts M,N\from \Var$ and $\sigma\plot_\Var^\Gamma N$, then we have $\sigma;\pr_n\plot_\com^\Gamma N\gets n$ for each $n$ and $\sigma;\pr_\bN\plot_\nat^\Gamma \oc N$.  
-  If $\Gamma,s\ts M\opto \Gamma,s\ts N$, then $\Gamma,s\ts M\gets n\opto\Gamma,s\ts N\gets n$ for each $n$ and $\Gamma,s\ts \oc M\opto\Gamma,s\ts \oc N$.  
-  Then, by the previous paragraph, we must have $\sigma;\pr_n\plot_{\com}^\Gamma M\gets n$ for each $n$ and $\sigma;\pr_\bN\plot_{\nat}^\Gamma \oc M$, and therefore $\sigma\plot_{\Var}^\Gamma M$.
-
-  Lastly, suppose that $\Gamma,s\ts M,N\from S \to T$ and suppose that $\Gamma,s\ts M \opto \Gamma,s\ts N$.
-  Let $\sigma\from \oc\deno{\Gamma} \implies (\oc\deno S \implies \deno T)$ be a strategy and suppose that $\sigma \plot_{S\to T} N$.  
-  We claim that $\sigma \plot_{S\to T} M$.  
-  Indeed, let $\tau\from\oc\deno{\Gamma}\implies\deno S$ be a strategy and let $\Gamma \ts P\from S$ be a term in context such that $\tau\plot_S^\Gamma P$.  
-  Then, since $\sigma\plot_{S\to T} N$, we must have that $\mu_{\deno{\Gamma}};(\sigma\tensor\tau^\dag);\ev \plot_T^\Gamma N\,P$.  
-  Since $\Gamma,s\ts M\opto\Gamma,s\ts N$, we must have $\Gamma,s\ts M\,P\opto\Gamma,s\ts N\,P$, and therefore $\mu_{\deno{\Gamma}};(\sigma\tensor\tau^\dag);\ev\plot_T^\Gamma M\,P$ by induction.
-\end{proof}
-
-\begin{lemma}
-  Let $T$ be a type of Idealized Algol, and let $\Gamma$ be a $\Var$-context.  
-  Then $\bot_{\oc\deno{\Gamma}\implies \deno T}\plot_T^\Gamma M$ for any term-in-context $\Gamma\ts M\from T$.
-  \label{LemAdequacyBot}
-\end{lemma}
-\begin{proof}
-  Induction on $T$.  
-  If $T$ is a datatype and $s$ a store, then for any $\sigma\from \oc\deno{\Gamma}\implies \deno T$ we have
-  \[
-    \oc\deno s;\cell^\Gamma;\sigma = \seqdeno{s,\sigma};(\deno T\sequoid ());\run_{\deno T}\,,
-    \]
-  as in the proof of Proposition \ref{PropSoundness}; since $(\deno T\sequoid());\run_{\deno T}$ is a zigzag strategy, if $\sigma=\bot_{\oc\deno{\Gamma}\implies\deno T}$, then $\oc\deno s;\cell^\Gamma;\sigma=\bot_{\deno T}$, and therefore $\seqdeno{s,\sigma}=\bot_{T\sequoid\oc\deno{\Gamma}}$.
-
-  Suppose $\Gamma\ts M\from\Var$.  
-  Since the projections are strict strategies, we have $\bot_{\oc\deno{\Gamma}\implies\Varr};\pr_n=\bot_{\oc\deno{\Gamma}\implies\bC}\plot_{\Var}^\Gamma M$ and $\bot_{\oc\deno{\Gamma}\implies\Varr};\pr_{\bC}=\bot_{\oc\deno{\Gamma}\implies\bN}\plot_{\bN}^\Gamma M$, and therefore $\bot_{\oc\deno{\Gamma}\implies\Varr}\plot_{\Var}^\Gamma M$.
-
-  Suppose that $\Gamma\ts M\from S\to T$.  
-  Fix some $N\from S$ and $\tau\from \oc\deno{\Gamma}\implies \deno S$ such that $\tau\plot_S^\Gamma N$.
-
-  We are required to show that
-  \[
-    \left(\oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\bot\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
-    \]
-  which, by induction, we can do by showing that it is equal to $\bot_{\oc\deno{\Gamma}\implies\deno T}$.
-  Indeed, we may write this composite as
-  \[
-    \oc\deno{\Gamma} \xrightarrow{\mu_{\deno{\Gamma}}} \oc\deno{\Gamma}\tensor\oc\deno{\Gamma} \xrightarrow{\oc\deno{\Gamma} \tensor \tau^\dag} \oc\deno{\Gamma}\tensor\oc\deno S \xrightarrow{\Lambda\inv(\bot_{\oc\deno{\Gamma} \implies (\oc\deno S \implies \deno T))}} \deno T\,,
-    \]
-  which is equal to $\bot_{\oc\deno{\Gamma}\implies\deno T}$.
-\end{proof}
-
-\begin{lemma}
-  Let $T$ be an idealized Algol type, and let $\Gamma\ts M\from T$ be a typing judgement, where $\Gamma$ is a $\Var$-context.
-  Suppose that $\sigma_1\subset\sigma_2\subset\cdots$ is a nested sequence of strategies for $\oc\deno{\Gamma}\implies \deno{T}$ such that $\sigma_i\plot_T^\Gamma M$ for all $i$.  
-  Let $\sigma=\bigcup_i \sigma_i$.  
-  Then $\sigma\plot_T^\Gamma M$.
-  \label{LemAdequacyLimits}
-\end{lemma}
-\begin{proof}
-  If $X$ is a datatype, $\Gamma$ is a $\Var$-context, $s$ is a $\Gamma$-store and $\Gamma\ts M\from X$ is a typing judgement, then if $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\deno{\Gamma}}$ for all $i$, then we must have $\seqdeno{s,\sigma_i}=\bot_{X\sequoid\oc\deno{\Gamma}} = \bot_{X\sequoid\oc\deno{\Gamma}}$ by continuity of composition.
-  Otherwise, $\seqdeno{s,\sigma_i}=\seqdeno{\Gamma,s'\ts u}$ for some $i$, some $\Gamma$-store $s'$ and some $u\in X$ such that $\Gamma,s\ts M \converges u,s'$.
-  In that case, since $\seqdeno{\Gamma,s'\ts u}$ is a maximal strategy for $X\sequoid\oc\deno{\Gamma}$, we must have $\seqdeno{s,\sigma_j}=\seqdeno{\Gamma,s'\ts u}$ for all $j\ge i$, and therefore that $\seqdeno{s,\sigma}=\seqdeno{\Gamma,s'\ts u}$.
-
-  By induction on $T$, this extends to higher types by continuity of composition.
-  For example, suppose that we have $\Gamma\ts M \from S \to T$, and that the $\sigma_i$ are strategies $\oc\deno{\Gamma} \implies (\oc\deno S \implies \deno T)$ such that $\sigma_i \plot_{S\to T}^\Gamma M$ for all $i$.
-  We claim that $\bigcup_i\sigma_i \plot_{S \to T}^\Gamma M$.
-
-  Indeed, suppose that $\tau\from \oc \deno \Gamma \implies \deno S$ is a strategy and $N \from S$ a term such that $\tau\plot_S^\Gamma N$.  
-  Then, by hypothesis, we have
-  \[
-    \left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma_i\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N
-    \]
-  for each $i$, and so, by the inductive hypothesis applied to $T$, we know that we have
-  \[
-    \bigcup_i\left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\sigma_i\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,.
-    \]
-  But continuity of composition tells us that this composite is equal to
-  \[
-    \left(\oc\deno{\Gamma} \xrightarrow{\ms\mu_{\deno{\Gamma}}\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\bigcup_i\sigma_i\tensor\tau^\dag} (\oc\deno S \implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\right) \plot_T^\Gamma M\,N\,,
-    \]
-  and so the result follows.
-\end{proof}
-
-\begin{lemma}
-  Let $\Gamma$ be a $\Var$-context, let $\Delta$ be an arbitrary context and let $T$ be an Idealized Algol type.
-  Write $\Delta=x_1\from T_1,\cdots,x_n\from T_n$.  
-  Suppose that $\sigma_i\from \oc\deno{\Gamma} \implies \deno{T_i}$ are strategies and $\Gamma\ts N_i\from T_i$ are terms-in-context such that $\sigma_i\plot_{T_i}^\Gamma N_i$ for each $i$.
-
-  Given a strategy $\sigma\from \oc{\deno{\Gamma,\Delta}}\implies \deno{T}$, we write
-  \[
-    (\sigma_i)\semicom \sigma
-    \]
-  for the composite
-  \[
-    \oc\deno{\Gamma} \xrightarrow{\langle \der,\sigma_1,\cdots,\sigma_n^\dag\rangle^\dag} \oc{\deno{\Gamma,\Delta}} \xrightarrow{\sigma} \deno{T}\,.
-    \]
-
-  Then for any term-in-context $\Gamma,\Delta \ts M\from T$, we have
-  \[
-    (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M} \plot_T^{\Gamma} M[N_i/x_i]\,.
-    \]
-  \label{LemAdequacy}
-\end{lemma}
-\begin{proof}
-  Induction on the typing derivation $\Gamma,\Delta \ts M\from T$.
-
-  \begin{itemize}
-    \item Let $x_j\from T_j$ be a variable occurring in $\Delta$.  
-      Then $x_j[N_i/x_i]=N_j$.  
-      Moreover, it is clear that $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts x_j} = \sigma_j$.
-      And we have $\sigma_j\plot_{T_j}^\Gamma N_j$ by hypothesis.
-
-    \item Next, suppose that $x\from\Var$ is a variable occurring in $\Gamma$.
-      Then we have $x[N_i/x_i]=x$, and it is easy to see that we have
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts x} = \deno{\Gamma\ts x}\,.
-        \]
-      Now we have $\deno{\Gamma\ts x};\pr_n = \deno{\Gamma\ts x\gets n}$ and $\deno{\Gamma\ts x};\pr_{\bN} = \deno{\Gamma \ts \oc\bN}$.  
-      From Lemma \ref{LemSoundnessOpto} (in particular, Figures \ref{FigSoundnessOoptoContext} and \ref{FigSoundnessOoptoStorage}), we know that if $s$ is a $\Gamma$-store, then
-      \[
-        \seqdeno{s,\deno{\Gamma\ts x\gets n}} = \seqdeno{\Gamma,s\ts x\gets n} = \seqdeno{\Gamma, (s\vert x\mapsto n)\ts \skipp}\,,
-        \]
-      where we have that $\Gamma,s\ts x\gets n\converges \skipp,(s\vert x\mapsto n)$, and that
-      \[
-        \seqdeno{s,\deno{\Gamma\ts \oc x}} = \seqdeno{\Gamma,s\ts \oc x} = \seqdeno{\Gamma,s\ts s(x)}\,,
-        \]
-      where we have that $\Gamma,s\ts \oc x \converges s(x),s$.
-
-    \item Next, suppose that $\Gamma,\Delta\ts M\from S\to T$ and $\Gamma,\Delta\ts N\from S$, where we already know that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{S\to T}^\Gamma M[N_i/x_i]
-        \]
-      and that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts N}\plot_S^\Gamma N[N_i/x_i]\,.
-        \]
-      Then it easy to see that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N}
-        \]
-      is given by the composite
-      \small
-      \[
-        \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms\mu_{\deno{\Gamma}}\ms\ms\ms} \oc\deno{\Gamma} \tensor \oc\deno{\Gamma} \xrightarrow{\ms\ms\ms((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}) \tensor ((\sigma_i)\semicom\deno{\Gamma,\Delta\ts N})\ms\ms\ms} (\oc\deno S \implies \deno T) \tensor \oc\deno {S} \xrightarrow{\ms\ms\ms\ev\ms\ms\ms} \deno T.
-        \]
-      \normalsize
-      Therefore, by the definition of $\plot_{S\to T}^\Gamma$, it must be the case that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M\,N} \plot_{T}^\Gamma M[N_i/x_i]\,N[N_i/x_i] = (M\,N)[N_i/x_i]\,.
-        \]
-    \item Next, suppose that $\Gamma,\Delta,x\from S \ts M\from T$.  
-      We claim that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta,\lambda x.M} \plot_{S\to T}^\Gamma (\lambda x.M)[N_i/x_i]\,.
-        \]
-      Let $\sigma'\from \oc\deno{\Gamma} \implies \deno S$ be a strategy and let $\Gamma\ts N\from S$ be a term in context such that $\sigma\plot_S^\Gamma N$.  
-      Then, by the inductive hypothesis (with $x$ lying in the `$\Delta$-part', we know that
-      \[
-        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}\plot_T^\Gamma M[N_i/x_i,N'/x]\,.
-        \]
-      Then, since $\Gamma,s\ts (\lambda x.M[N_i/x_i])\,N'\opto \Gamma,s\ts M[N_i/x_i,N'/x]$ for any $\Gamma$-store $s$, by Lemma \ref{LemAdequacyOpto} we know that
-      \[
-        (\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M} \plot_T^\Gamma ((\lambda x.M)[N_i/x_i])\,N'\,.
-        \]
-      Finally, observe that $(\sigma_i,\sigma')\semicom\deno{\Gamma,\Delta,x\from S\ts M\from T}$ is the composite
-      \[
-        \oc\deno{\Gamma} \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n,\sigma'\rangle^\dag} \oc{\deno{\Gamma,\Delta,x}} \xrightarrow{\deno{\Gamma,\Delta,x\from S\ts M}} \deno T\,,
-        \]
-      which can alternatively be written as
-      \begin{mathpar}
-        \oc\deno{\Gamma} \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag} \oc{\deno{\Gamma,\Delta}} \xrightarrow{\mu_{{\deno{\Gamma,\Delta}}}} \oc{\deno{\Gamma,\Delta}}\tensor\oc{\deno{\Gamma,\Delta}}\\ \xrightarrow{\deno{\Gamma,\Delta\ts \lambda x.M} \tensor (\sigma')^\dag} (\oc\deno S\implies \deno T) \tensor \oc\deno S \xrightarrow{\ev} \deno T\,.
-      \end{mathpar}
-  \end{itemize}
-
-  Now we move on to the structural constants for the datatypes.  
-  We deal with the case of the type $\nat$ (i.e., the terms $n$, $\suc M$, $\pred M$ and $\IfO M\Then N \Else P$), and it should be clear how our ideas translate to the corresponding rules at the types $\com$ and $\bool$ (i.e., $\skipp$, $\true$/$\false$, sequencing and the boolean conditional).
-
-  Before we cover these cases, we make an important observation.  
-  Suppose that $\Gamma,\Delta\ts M,N\from T$, and that
-  \[
-    \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts N}}\,.
-    \]
-  Let $\EE$ be an evaluation context of type $U$ with a hole of type $T$.  
-  Then
-  \[
-    \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \EE[M]})} = \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \EE[N]}}\,.
-    \]
-  We can see this by precomposing both directions of the diagram in Figure \ref{FigSoundnessOpto} (with $\Gamma$ in that diagram standing for $\Gamma,\Delta$) with the composite
-  \[
-    I \xrightarrow{\oc\deno{s}}
-    \oc S_\Gamma \xrightarrow{\cell^\Gamma}
-    \oc\deno{\Gamma} \xrightarrow{\langle\der,\sigma_1,\cdots,\sigma_n\rangle^\dag}
-    \oc\deno{\Gamma,\Delta}\,,
-    \]
-  in order to prove that the value of $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts\EE[M]}}$ depends only on the value of $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}$ and $\EE$.
-
-  \begin{itemize}
-    \item Given a numeral $n$ and a $\Gamma$-store $s$, we have $(\sigma_i)\semicom \deno{\Gamma,\Delta\ts n} = \deno{\Gamma\ts n}$ and $\seqdeno{s,\deno{\Gamma\ts n}} = \seqdeno{\Gamma,s\ts n}$, where $\Gamma,s\ts n\converges n,s$.
-
-    \item Suppose $\Gamma,\Delta\ts M\from \nat$, and that we already know that 
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}\plot_{\nat}^\Gamma M[N_i/x_i]\,.
-        \]
-      So for all $\Gamma$-stores $s$, either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})} = \bot_{\bN\sequoid\oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$.
-
-      Now we have 
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts M};(\suc\tensor\oc\deno{\Gamma})\,;
-        \]
-      since $\suc\from\bN \implies \bN$ is a strict strategy, we know that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \suc M})} = \bot_{\bN\sequoid\oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,s'\ts n};(\suc\tensor\oc\deno{\Gamma}) = \seqdeno{\Gamma,s'\ts n+1}$, and we have $\Gamma,s\ts \suc M[N_i/x_i]\converges n+1$.
-      Therefore, 
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\suc M} \plot_{\nat}^\Gamma \suc M[N_o/x_i]\,.
-        \]
-
-      A similar argument proves that 
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\pred M} \plot_{\nat}^\Gamma \pred M[N_i/x_i]\,.
-        \]
-
-    \item Now we move on to the conditional.  
-      Suppose that we have $\Gamma,\Delta\ts M\from \nat$ and $\Gamma,\Delta\ts N,P\from X$ for some datatype $X$.  
-      Let $s$ be a $\Gamma$-store.  
-      Since $\IfO$ is a strict strategy, if $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M})}=\bot_{\oc\deno{\Gamma}\ts \bN}$, then
-      \[
-        \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P}} = \bot_{\oc\deno{\Gamma} \ts X}\,.
-        \]
-      Otherwise, by induction we know that $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts M}}=\seqdeno{\Gamma,s'\ts n}$ for some numeral $n$ such that $\Gamma,s\ts M[N_i/x_i]\converges n,s'$.
-      Without loss of generality, suppose that $n=0$.  
-      Then we have
-      \begin{IEEEeqnarray*}{Cl}
-        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO M \Then N \Else P})} \\
-        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \IfO 0 \Then N \Else P})} \\
-        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta \ts N})}\,, \\
-      \end{IEEEeqnarray*}
-      where the first equality is by our observation above (since $\IfO - \Then N \Else P$ is an evaluation context), and the second is by the definition of $\IfO$.
-      Then, by induction, this last term is either equal to $\bot_{X\sequoid\deno{\Gamma}}$,or is equal to $\seqdeno{\Gamma,s''\ts u}$ for some $u\in X$ such that $\Gamma,s'\ts N[N_i/x_i]\converges u,s''$.
-      In this second case, we have $\Gamma,s\ts \IfO M[N_i/x_i] \Then N[N_i/x_i] \Else P[N_i/x_i] \converges u,s''$.
-  \end{itemize}
-  Next, we deal with the rules for variables.
-  \begin{itemize}
-    \item Suppose $\Gamma,\Delta\ts V\from\Var$, and suppose we already know that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V} \plot_{\Var}^\Gamma V[N_i/x_i]\,.
-        \]
-      Then by definition we have
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \oc V} = (\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_{\bN} \plot_{\bN}^\Gamma \oc\V[N_i/x_i]\,.
-        \]
-      Suppose $\Gamma,\Delta\ts E\from \nat$, and suppose we know already that $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E} \plot_{\bN} E[N_i/x_i]$.  
-      Then, for all $s$, either $\seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts E}}=\bot_{\bN \sequoid\oc\deno{\Gamma}}$ -- in which case
-      \[
-        \seqdeno{s,(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets E}} = \bot_{\bC \sequoid \oc\deno{\Gamma}}
-        \]
-      (since $\assign$ is a strict strategy) -- or it is equal to $\seqdeno{s',n}$ for some $n\in \bN$ such that $\Gamma,s\ts E[N_i/x_i]\converges n,s'$.
-      In the second case, we have
-      \begin{IEEEeqnarray*}{Cl}
-        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V \gets E})} \\
-        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V\gets n}} \\
-        = & \seqdeno{s',((\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n)}\,.
-      \end{IEEEeqnarray*}
-      Now we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts V};\pr_n\plot_{\com}^\Gamma V[N_i/x_i]\gets n$ by induction, so this composite is either equal to $\bot_{\bC\sequoid\oc\deno\Gamma}$ or it is equal to $\seqdeno{\Gamma,s''\ts \skipp}$ for $s''$ such that $\Gamma,s'\ts V[N_i/x_i]\gets n\converges \skipp,s''$.
-      In this second case, we have $\Gamma,s\ts V[N_i/x_i]\gets E[N_i/x_i]\converges \skipp,s''$.
-
-    \item Suppose that $\Gamma,\Delta\ts W \from \nat \to \com$ and that $\Gamma,\Delta \ts R \from \nat$.
-      We claim that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts\mkvar\,W\,R};\pr_n\plot_\com^\Gamma (\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\gets n
-        \]
-      for each $n$ and that 
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN\plot_\nat^\Gamma \oc(\mkvar\,W[N_i/x_i]\,R[N_i/x_i])\,.
-        \]
-
-      For the first of these, let $s$ be a $\Gamma$-store.  
-      We have
-      \begin{IEEEeqnarray*}{Cl}
-        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_n)} \\
-        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts W\,n})}\,. \\
-      \end{IEEEeqnarray*}
-      By induction, we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts W\,n} \plot_{\com}^\Gamma W[N_i/x_i]\,n$.  
-      Therefore, this last composite is either equal to $\bot_{\bC\sequoid\oc\deno{\Gamma}}$, or it is equal to $\seqdeno{\Gamma,s',\skipp}$ for some $s'$ such that $\Gamma,s\ts W\,n\converges \skipp,s'$.
-      In this second case, we have $\Gamma,s\ts (\mkvar W\,R)\gets n\converges \skipp,s'$.
-
-      For the second, we have
-      \begin{IEEEeqnarray*}{Cl}
-        & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \mkvar\,W\,R};\pr_\bN)} \\
-        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta \ts R})}\,.
-      \end{IEEEeqnarray*}
-      By induction, we have $(\sigma_i)\semicom\deno{\Gamma,\Delta\ts R} \plot_{\nat}^\Gamma R[N_i/x_i]$.  
-      Therefore, this last composite is either equal to $\bot_{\bC\sequoid\oc\deno{\Gamma}}$, or it is equal to $\seqdeno{\Gamma,s',n}$ for some $s',n$ such that $\Gamma,s,R \converges n,s'$.  
-      In this second case, we have $\Gamma,s\ts \oc(\mkvar W\,R) \converges n,s'$.
-
-    \item Suppose that $\Gamma,x\from\Var,\Delta\ts M\from X$, where $X$ is a datatype, and suppose we already know that
-      \[
-        (\sigma_i)\semicom\deno{\Gamma,x\from\Var,\Delta\ts M} \plot_X^{\Gamma,x} M\,,
-        \]
-      where $x$ is considered as belonging to the `$Gamma$-component'.
-      Let $s$ be a $\Gamma$-store -- then we get a $\Gamma,x$-store $(s\vert x\mapsto 0)$.
-      So either $\seqdeno{(s\vert x\mapsto 0),((\sigma_i)\semicom\deno{\Gamma,x,\Delta\ts M})}=\bot_{X\sequoid\oc\deno\Gamma}$, or it is equal to $\seqdeno{\Gamma,x,(s'\vert x\mapsto n),u}$ for some $s',n,u$ such that $\Gamma,(s\vert x\mapsto 0)\ts M[N_i/x_i] \converges u,(s'\vert x\mapsto n)$.
-
-      But by the definition of $\new$, we have
-      \begin{IEEEeqnarray*}{Cl}
-        & \seqdeno{(s\vert x\mapsto 0),((\sigma_i)\semicom\deno{\Gamma,x,\Delta\ts M})};(X\sequoid\oc\pr_\Gamma) \\
-        = & \seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts \neww\lambda x.M})}\,.
-      \end{IEEEeqnarray*}
-      It follows that either $\seqdeno{s,((\sigma_i)\semicom\deno{\Gamma,\Delta\ts\neww\lambda x.M})}=\bot_{X\sequoid \oc\deno{\Gamma}}$ or it is equal to $\seqdeno{\Gamma,x,(s'\vert x\mapsto n),u};(X\sequoid\oc\pr_\Gamma) = \seqdeno{\Gamma,s',u}$ for some $u$ such that $\Gamma,(s\vert x\mapsto 0)\ts M[N_i/x_i]\converges u,(s'\vert x\mapsto n)$.
-      In this case, $\Gamma,s\ts\neww \lambda x.M\converges u,s'$.
-  \end{itemize}
-  It remains to deal with the case of the recursion combinator $\Y_T$.  
-  First recall that if $h\from ((\deno T \to \deno T) \to \deno T) \to (\deno T\to \deno T) \to T$ (where we write $A \to B$ for $\oc A \implies B$) is the morphism corresponding to the $\lambda$-term
-  \[
-    \lambda F^{(T\to T) \to T}.\lambda f^{T\to T}.f(F\,f)\,,
-    \]
-  then $\Y_T$ is constructed as the limit of the chain
-  \[
-    \bot_{(T\to T)\to T} \subset \bot_{(T\to T) \to T};h \subset \bot_{(T\to T)\to T};h;h \subset \cdots\,.
-    \]
-  By Lemma \ref{LemAdequacyLimits}, then, it suffices to show that if $\Gamma,\Delta \ts M\from T \to T$ then $(\sigma_i)\semicom \deno {\Gamma,\Delta\ts M};\left(\bot_{(T\to T)\to T}\right);h^n\plot_{T}^{\Gamma} \Y_T M[N_i/x_i]$ for each $n$.
-
-  We do this by induction on $n$.  
-  Lemma \ref{LemAdequacyBot} takes care of the initial case, and it will therefore suffice to prove that if $\sigma\plot_T^\Gamma \Y_T M$ then $\sigma;h\plot_T^\Gamma \Y_T M$.
-
-  Suppose $T=T_1\to \cdots\to T_n \to X$, where $X$ is a datatype.
-  Fix terms $M_i\from T_i$ and strategies $\tau_i\from \deno{\Gamma}\to \deno{T_i}$ such that $\tau_i\plot_{T_i}^\Gamma M_i$ for each $i$.
-
-  Since $\sigma\plot_T^\Gamma \Y_T M$, we know that $\langle \tau_1,\cdots,\tau_n\rangle;\sigma \plot_X^\Gamma \Y_T M\,M_1\,\cdots\,M_n$.
-  It follows that $\langle \tau_1,\cdots,\tau_n\rangle;\sigma;h \plot_X^\Gamma M(\Y_T M)\,M_1,\cdots\,M_n$.  
-  Then, since
-  \[
-    \Gamma,s,\Y_T M\,M_1,\cdots\,M_n\opto\Gamma,s,M(\Y_T M)\,M_1\,\cdots\,\M_n
-    \]
-  for any $\Gamma$-store $s$, by Lemma \ref{LemAdequacyOpto} we have that
-  \[
-    \langle\tau_1,\cdots,\tau_n\rangle;\sigma;h \plot_X^\Gamma \Y_T M\,M_1,\cdots,M_n\,,
-    \]
-  and therefore that $\sigma;h\plot_X^\Gamma \Y_T M$, since the $M_i,\tau_i$ were arbitrary.
-\end{proof}
-
-This is now enough to prove a \emph{computational adequacy result} for our denotational semantics.
-
-\begin{definition}[Computational Adequacy Result]
-  Suppose we have a programming language $\L$ and a denotational semantics $\deno{-}$ of $\L$ in some category $\C$.  
-  Let $o$ be a ground type of $\L$ and let $\converges$ be some operational predicate on closed terms of $\L$ of type $o$.  
-  Let $\downarrow$ be a predicate on morphisms $1 \to \deno{L}$ in $\C$.  
-  Then a \emph{computational adequacy} result for the semantics is a result that says that for all terms $M\from o$ in $\L$, 
-  \[
-    M\converges \text{ if and only if } \deno{M}\downarrow\,.
-    \]
-\end{definition}
-
-We will prove a computational adequacy result for our semantics of IA, taking $o=\com$.  
-If $M\from\com$ is a term of IA, we say that $M\converges$ if $\blank,()\ts M\converges \skipp,()$.
-If $\sigma\from 1 \implies \bC$ is a strategy, we say that $\sigma\downarrow$ if $\sigma\ne\bot_{\com}$.
-
-\begin{theorem}[Computational Adequacy]
-  Let $M\from\com$ be a closed term of Idealized Algol.
-  Then $M\converges$ if and only if $\deno{M}\ne\bot_{\com}$.
-  \label{TheComputationalAdequacyIA}
-\end{theorem}
-\begin{proof}
-  First suppose that $M\converges$.  
-  Then Proposition \ref{PropSoundness} tells us that $\deno{M} = \deno{\skipp}\ne\bot_{\com}$.
-
-  Conversely, suppose that $\deno{M}\ne\bot_{\com}$.  
-  Lemma \ref{LemAdequacy} tells us that $\deno{M}\plot_{\com} M$.  
-  Since $\deno{M}\ne\bot_{\com}$, the only possibility is that $\blank,()\ts M\converges\skipp,()$.
-\end{proof}
-
-We can then prove an \emph{equational soundness} result.
-First, we recall the definition of \emph{observational equivalence} of terms.
-
-\begin{definition}[Observational Equivalence]
-  Suppose we have a language $\L$, together with a distinguished ground type $o$ and operational predicate $\converges$ as above.  
-  Given two closed terms $M,N\from T$ in $\L$, we say that $M$ and $N$ are \emph{observationally equivalent} if for all contexts $C[-]\from o$ in $\L$ with a hole of type $T$, $C[M]\converges$ if and only if $C[N] \converges$.
-\end{definition}
-
-Next, we create a definition that mirrors this one within the denotational semantics.
-
-\begin{definition}[Intrinsic Equivalence]
-  Suppose we have a language $\L$, together with a denotational semantics $\deno{-}$ in a Cartesian closed category $\C$, a distinguished ground type $o$ and a predicate $\downarrow$ on morphisms $1 \to \deno{o}$ as above.
-
-  Given objects $A,B$ of $\C$, and morphisms $\sigma,\tau\from A \to B$, we say that $\sigma,\tau$ are \emph{intrinisically equivalent}, and write $\sigma\sim\tau$, if for all $\alpha\from (A \to B) \to \deno{o}$, $\Lambda(\sigma);\alpha\downarrow$ if and only if $\Lambda(\tau);\alpha\downarrow$.
-\end{definition}
-
-\begin{definition}[Equational Soundness Result]
-  An \emph{equational soundness result} for a semantics as above is a result that says that if $M,N\from T$ are such that $\deno{M}\sim\deno{N}$, then $M$ and $N$ are observationally equivalent.
-\end{definition}
-
-\begin{proposition}
-  Any semantics satisfying Computational Adequacy satisfies Equational Soundness.
-  \label{PropEquationalSoundness}
-\end{proposition}
-\begin{proof}
-  Suppose that $\deno{M}\sim\deno{N}$.  
-  Let $C[-]\from o$ be a context with a hole of type $T$.
-  Then, since $\C$ is Cartesian closed, the $\beta$-rule is valid in $\C$, and therefore we have
-  \[
-    \deno{C[M]} = 1 \xrightarrow{\deno{M}} \deno{T} \xrightarrow{\deno{x\from T\ts C[x]}} \deno{o}\,,
-    \]
-  and similarly for $C[N]$.  
-  Therefore, taking $\alpha=\deno{x\ts C[x]}$ in the definition of $\sim$, we get that $\deno{C[M]}\downarrow$ if and only if $\deno{C[N]}\downarrow$.  
-  By Computational Adequacy, this means that $C[M]\converges$ if and only if $C[N]\converges$.  
-  Since $C$ was arbitrary, it follows that $M$ and $N$ are observationally equivalent.
-\end{proof}
-
-This proof relies on the fact that the context $C$ gives rise to a morphism $\alpha = \deno{x\ts C[x]}$.  
-To go in the other direction (full abstraction), we need a \emph{definability} result, to allow us to transform a morphism in $\G$ into an Idealized Algol context.  
-This will be the subject of the next section.
-
-\section{Innocent Factorization}
-
-The aim of this section will be to show that any strategy between the denotations of Idealized Algol types may be factorized as the composite of some innocent strategy with the strategy $\cell$.  
-This will reduce the problem to showing that certain innocent strategies are definable, for which we can use known results.
-
-Again, we follow the proof from \cite{SamsonGuyIAActive} very closely.
-
-\begin{proposition}[Innocent Factorization, {\cite[14]{SamsonGuyIAActive}}]
-  Let $A$ be a game, and suppose $A$ has the property that whenever $sb\in P_A$ is an $O$-position and $tbc\in P_A$ is a $P$-position such that $\pv{sb}=\pv{tb}$, then $sbc\in P_A$.
-  Suppose also that $M_A$ is a countable set.
-  Let $\sigma$ be a strategy for $A$.  
-  Then there is an innocent strategy $\hat\sigma$ for $\oc\Varr \implies A$ such that $\sigma$ factorizes as the composite
-  \[
-    I \xrightarrow{\oc 0} \oc\bN \xrightarrow{\cell} \oc\Varr \xrightarrow{\hat\sigma} A\,.
-    \]
-  \label{PropInnocentFactorization}
-\end{proposition}
-\begin{proof}
-  Fix some injection $\L_A \hookrightarrow \bN$, thought of as giving a `code' to each legal sequence, such that the code of the empty sequence is $0$.
-  $\hat{\sigma}$ proceeds as follows.  
-  At each position $sb$ ending with an $O$-move $a$ in $A$, player $P$ first plays the move $q$ in $\oc\Varr$, after which player $O$ returns some natural number $n$.  
-  If $n$ is not the code of a sequence in $P_A$, or if it encodes some sequence $t$ such that $\pv{tb}\ne\pv{s\vert_Ab}$, then player $P$ has no reply.  
-  Otherwise, let $c$ be the reply to $t a$ that player $P$ would have made under $\sigma$.  
-  Player $P$ computes the code $k$ of the sequence $tbc$ and plays $q_k$ in $\oc\Varr$.  
-  After the $O$-reply $a$, player $P$ then plays the move $b$ in $\oc\Varr$.
-
-  Since $tbc\in P_A$ and $\pv{tb}=\pv{tc}$, we have $s\vert_Abc\in P_A$ by our hypothesis on $A$, which implies that this is a valid strategy.
-  We claim that it is innocent.  
-  Moreover, since player $P$'s moves depend only on the number $n$ returned and on the current $P$-view within $A$, this strategy is innocent.
-
-  Lastly, if we compose with $\oc0;\cell$, then we ensure that this number $n$ that is returned is always the code of the current sequence in $A$, and therefore that $\oc 0;\cell;\hat{\sigma}=\sigma$ by the explicit description of the $\cell$ strategy given in Proposition \ref{PropCellComb}.
-\end{proof}
-
-We want to apply this result in the case that $A$ is the denotation of an IA type, so we need to show that for any IA type $T$, the game $\deno T$ satisfies the hypotheses of Proposition \ref{PropInnocentFactorization}.
-In fact, we show something stronger.
-
-\begin{lemma}
-  Let $T$ be a type of Idealized Algol.  
-  Then $P_{\deno T}$ is the set of all sequences in $\L_{\deno T}$ that contain at most a single initial move.
-  \label{LemTypeCharacterization}
-\end{lemma}
-\begin{proof}
-  This is obvious for the datatypes and for $\Var$.  
-  Let $S,T$ be types -- so $\deno{S \to T} = \oc\deno S \implies \deno T$ -- and let $s\in P_{\oc\deno S\implies \deno T}$.  
-  An initial move in $\oc\deno S \implies \deno T$ is an initial move in $\deno T$; by induction, $s\vert_{\deno T}\in P_{\deno T}$ contains at most one initial move, and so $s$ contains at most one initial move.
-
-  Conversely, suppose that $s\in \L_{\oc\deno S \implies \deno T}$ contains at most one initial move.
-  We show by induction on the length of $s$ that $s\in P_{\oc\deno S \implies \deno T}$.  
-  This is obvious if $s=\epsilon$; if $s=ta$ for some $t$, then by induction we have $t\in P_{\oc\deno S \implies \deno T}$, so $t\vert_{\oc\deno S}\in P_{\oc\deno S}$ and $t\vert_{\deno T}\in P_{\deno T}$.
-  We need to show that $ta\in P_{\oc\deno S}$, for which it suffices by induction to show that $ta\vert_{\oc\deno S}$ and $ta\vert_{\deno T}$ are both legal positions, $ta\vert_{\oc\deno S}\vert_n$ has a unique initial move in $\deno S$ for each initial move $n$ of $\deno S$, and $ta\vert_{\deno T}$ has a unique initial move in $\deno T$.
-  Indeed, we can show that they are alternating using the same arguments we used in Proposition \ref{PropComposition}, and they are clearly well-bracketed sequences.  
-  Visibility then follows from Lemma \ref{LemProjectionLemma}, and from Proposition 4.3 from \cite{hoPcf}, which states that if $s$ is a play in $A\implies B$, then $\pv{s}^{A\implies B}\vert_A$ is a subsequence of $\pv{s\vert_A}^A$ and $\pv{s}^{A\implies B}\vert_B$ is a subsequence of $\pv{s\vert_B}^B$.
-  This means that the justifier of the move $a$ must occur within the appropriate $O$- or $P$-view, since we know that $t\vert_{\oc\deno S}$ and $t\vert_{\deno T}$ are both visible sequences.
-\end{proof}
-
-\begin{proposition}
-  Let $T$ be a type of Idealized Algol.  
-  Then $\deno T$ satisfies the hypotheses of Proposition \ref{PropInnocentFactorization}.
-\end{proposition}
-\begin{proof}
-  Suppose that $sb,tbc\in P_{\deno T}$, where $c$ is a $P$-move, are such that $\pv{sb}=\pv{tb}$.  
-  It is clear that $sbc$ is an alternating and visible sequence; moreover, it is well-bracketed, since the most recently unanswered question in $sb$ is the same as in $tb$.  
-  Therefore, $sbc$ is a legal sequence with a unique initial move, and so it is contained in $P_{\deno T}$ by Lemma \ref{LemTypeCharacterization}.
-\end{proof}
-
-\section{Arena-only Semantics}
-\label{SecArenaOnly}
-
-Before we complete our Full Abstraction result, we take a detour to consider a variation of our game semantics in which we do away with the sets of plays $P_A$.  
-We call this an \emph{arena-only semantics}, since the objects of our category are plain arenas.
-Since the semantics given in \cite{hoPcf} are of this form, and since we want to quote definability results from this work, it makes sense to cast our own work in this form.
-
-\begin{definition}
-  Let $A$ be a game.  
-  We say that $A$ is \emph{full} if $P_A=\L_A$.
-\end{definition}
-
-Let $A$ be a game.  
-Since the underlying arena of $\oc A$ is the same as that of $A$, and since we have $P_A \subset P_{\oc A}$, we have the following result.
-
-\begin{proposition}
-  If $A$ is full, then we have $A=\oc A$.
-\end{proposition}
-
-Note that the definition of the $\oc$ connective, together with Lemma \ref{LemTypeCharacterization}, implies the following.
-
-\begin{proposition}
-  Let $T$ be an Idealized Algol type.  
-  Then $\oc\deno{T}$ is full.
-\end{proposition}
-
-This Proposition on its own does not seem to be much use, since we want to consider the game $\deno T$ without the $\oc$ in front of it.  
-But recall that the `co-Kleisli'-style morphisms in our category, which are strategies for $\oc A \implies B$, may alternatively be regarded as comonoid homomorphisms from the comonoid on $\oc A$ to the comonoid on $\oc B$.
-Thus, if $S,T$ are Idealized Algol types, then the set of morphisms $\oc\deno S \implies \deno T$ in our original category is precisely the same as the set of morphisms $\oc\deno S \implies \oc\deno T$ that are comonoid homomorphisms.
-
-\begin{definition}
-  Let $A$ be a game and let $sa$ be a play in $A$.  
-  Then the \emph{current thread} $\ct{sa}$ of $sa$ is $sa\vert_n$, where $n$ is the unique initial move that hereditarily justifies $a$.
-
-  Let $\sigma$ be a strategy for $A$.
-  We say that $\sigma$ is \emph{single-threaded} if player $P$'s moves only depend on the current thread; i.e., if whenever $sab\in\sigma$, $t\in\sigma$ and $ta\in P_A$ such that $\ct{sa}=\ct{ta}$, then we have $tab\in\sigma$.
-\end{definition}
-
-Note the similarity with the definition of innocence, where the only difference is that we use the $P$-views $\pv{sa}$ and $\pv{ta}$ rather than the current threads $\ct{sa}$ and $\ct{ta}$.
-Since $\pv{s}$ is a subsequence of $\ct{s}$ for any sequence $s$, we get:
-\begin{proposition}
-  Any innocent strategy is single-threaded.
-\end{proposition}
-
-\begin{lemma}[{\cite[3.5.1]{RusssThesis}}]
-  Let $\sigma \from A$ be a single-threaded strategy.  
-  Suppose $s\in \sigma$, and let $I$ be a set of occurrences of initial moves in $s$.  
-  Then $s\vert_I\in\sigma$.
-  \label{LemRuss1}
-\end{lemma}
-\begin{proof}
-  Induction on the length of $s$.
-  Suppose that $sab\in\sigma$.  
-  Since $sab$ is a visible sequence, we know that the justifier of $b$ occurs in $\pv{sa}$, and in particular in $\ct{sa}$.
-  Now $a$ must be hereditarily justified by that initial move that hereditarily justifies $b$; if this initial move is not contained in $I$, then we have $sab\vert_I=s\vert_I\in\sigma$ by induction.  
-  Otherwise, we have $sab\vert_I=s\vert_Iab$.  
-  Then, since we have $\ct{sa}=\ct{s\vert_I a}$, we must have $s\vert_Iab\in\sigma$ by single-threadedness of $\sigma$.
-\end{proof}
-
-We now link the combinatorial definition of single-threadedness to a definition about comonoid homomorphisms.
-
-\begin{proposition}
-  Let $A,B$ be well-opened games.
-  Given a strategy
-  \[
-    \sigma\from \oc A \implies \oc B\,,
-    \]
-  $\sigma$ is single-threaded if and only if it is a comonoid homomorphism with respect to the natural comonoid structures on $\oc A$ and $\oc B$; i.e., it makes the following diagrams commute.
-  \begin{mathpar}
-    \begin{tikzcd}
-      \oc A \arrow[r, "\sigma"] \arrow[d, "\mu_A"']
-        & \oc B \arrow[d, "\mu_B"] \\
-      \oc A \tensor \oc A \arrow[r, "\sigma \tensor \sigma"]
-        & \oc B \tensor \oc B
-    \end{tikzcd}
-    \and
-    \begin{tikzcd}
-      \oc A \arrow[r, "\sigma"] \arrow[d, "()"']
-        & \oc B \arrow[dl, "()"] \\
-      I
-        &
-    \end{tikzcd}
-  \end{mathpar}
-\end{proposition}
-\begin{proof}
-  Of course, the second diagram is automatically satisfied by any strategy $\sigma$, since $I$ is a terminal object.
-
-  Since $A,B$ are well-opened, $\oc A$ and $\oc B$ are the cofree commutative comonoids on $A,B$, and therefore the comonoid homomorphisms $\sigma\from \oc A \implies \oc B$ are precisely the strategies of the form $\tau^\dag$, where $\tau\from\oc A \implies B$ is an arbitrary morphism.
-  It is easy to check that such a strategy is single-threaded; indeed, the plays of $\tau^\dag$ are precisely those plays $s\in P_{\oc A \implies \oc B}$ such that $s\vert_n\in\tau$ for any occurrence $n$ of an initial move in $s$.
-
-  Conversely, let $\sigma\from \oc A \implies \oc B$ be single-threaded.  
-  Let $\tau=\sigma\cap P_{\oc A \implies B}$ -- so $\tau$ consists of all sequences in $\sigma$ that have at most one initial move.  
-  Then $\tau$ is clearly a strategy, since it is a prefix-closed subset of $\sigma$.
-  We claim that $\sigma=\tau^\dag$.  
-  Indeed, suppose that $s\in\sigma$.  
-  Let $n$ be an occurrence of an initial move in $s$.  
-  Then, by Lemma \ref{LemRuss1}, $s\vert_n\in\sigma$ and has a unique initial move, and is therefore contained in $\tau$.  
-  Therefore, $\sigma=\tau^\dag$.
-\end{proof}
-
-Now consider the category whose objects are arenas and where the morphisms from $A$ to $B$ are single-threaded strategies for $A\implies B$, where we identify $A$ and $B$ with their corresponding full games.
-Then, if $T$ is any Idealized Algol type, there is some corresponding arena such that the full game on that arena is isomorphic to $\oc\deno T$.  
-We will call this arena $\deno T$ as well, relying on context to distinguish them.
-This means that our semantics of Idealized Algol lives within the new category, since a single-threaded strategy for $\deno S \to \deno T$ is the same thing as a strategy for $\oc \deno S \implies \deno T$ in the original semantics.
-
-This semantics is much closer to the game semantics of PCF developed by Hyland and Ong in \cite{hoPcf}; the difference there is that they use innocent rather than single-threaded strategies.
-
-Note that it is impossible to define the tensor product of games, let alone the sequoid, in the arena-only semantics, so our Computational Adequacy proof would not have worked had we adopted this approach from the start.
-
-\section{Full Abstraction}
-
-We now quote a definability result from \cite{hoPcf}.
-
-\begin{theorem}[{\cite[7.1]{hoPcf}}]
-  Let $T$ be a PCF type, and let $\sigma$ be a compact innocent strategy for $\deno T$ (within the arena-only semantics).  
-  Then there is some closed PCF term $M\from T$ such that $\deno M=\sigma$.
-  \label{ThePcfDefinability}
-\end{theorem}
-
-Here, PCF is the sub-language of PCF generated by the types $\nat$ and $\bool$, together with their structural constants.  
-We will take it as read that this result may be extended to the types $\com$ and $\Varr$, so that we can say that if $T$ is an Idealized Algol type, then any compact innocent strategy for $\deno T$ is the denotation of some IA term.
-Then our factorization result (Proposition \ref{PropInnocentFactorization}) gives us the following definability result.
-
-\begin{proposition}
-  Let $T$ be an Idealized Algol type, and let $\sigma\from \deno T$ be a compact strategy.
-  Then there is some closed IA term $M\from T$ such that $\deno M=\sigma$.
-  \label{PropIaDefinability}
-\end{proposition}
-\begin{proof}
-  We work in the arena-only semantics so that we can apply Theorem \ref{ThePcfDefinability}.  
-  By Proposition \ref{PropInnocentFactorization}, we know that $\sigma=\oc 0;\cell;\hat{\sigma}$ for some innocent strategy $\hat\sigma \from \Varr \to \deno T$.
-  By looking at the proof of Proposition \ref{PropInnocentFactorization}, we can see that $\hat\sigma$ is compact if $\sigma$ is.
-  Then, by Theorem \ref{ThePcfDefinability}, we know that there is some IA term $\lambda x.M\from \Var \to T$ such that $\deno{\lambda x.M}=\hat\sigma$.  
-  It follows that $\sigma$ is the denotation of the term $\new(\lambda x.M)\from T$.
-\end{proof}
-
-\begin{definition}[Full Abstraction result]
-  A \emph{full abstraction result} encompasses both an equational soundness result and its converse, asserting that two programs are observationally equivalent if and only if their denotations are intrinsically equivalent.
-\end{definition}
-
-\begin{theorem}[Full Abstraction]
-  Let $M,N\from T$ be closed terms of Idealized Algol.  
-  Then $M$ and $N$ are observationally equivalent if and only if $\deno M\sim\deno N$.
-\end{theorem}
-\begin{proof}
-  We have already proved that our semantics is computationally adequate, and therefore that the reverse direction (equational soundness) holds.  
-  Now suppose instead that $\deno M\not\sim\deno N$.
-  Without loss of generality, suppose there is $\alpha\from \deno T\to \bC$ such that $\deno{M}^\dag;\alpha\ne\bot_{\bC}$ and $\deno{N}^\dag;\alpha=\bot_{\bC}$.
-
-  Since $\deno{M}^\dag$ is the supremum of all its compact sub-strategies, if $\deno{M}^\dag;\alpha'=\bot_{\bC}$ for all compact $\alpha'\subset \alpha$, then $\deno{M}^\dag;\alpha=\bot_{\bC}$ by continuity of composition.
-  Therefore, there is some compact $\alpha'\subset\alpha$ such that $\deno M^\dag;\alpha\ne\bot_{\bC}$; moreover, we have that $\deno{N}^\dag;\alpha'=\bot_{\bC}$ by monotonicity of composition.
-
-  Then $\alpha'$ is the denotation of some term $P\from T \to \com$, and we have $P\,M\converges$ and $P\,N\not\converges$ by Computational Adequacy.  
-  Therefore, $M$ and $N$ are not observationally equivalent.
-\end{proof}
-
-\section{The Intrinsic Equivalence Relation}
-\label{SecIntrinsicEquivalence}
-
-We conclude by giving a more concrete description of the intrinsic equivalence relation on strategies.
-
-\begin{definition}
-  We say that a justified sequence $s$ is \emph{complete} if every question move $q$ occurring in $s$ has some answer move $a$ justified by $q$.
-\end{definition}
-
-\begin{proposition}[{\cite[25]{SamsonGuyIAActive}}]
-  Let $\sigma,\tau\from \oc A \implies B$ be strategies, where $A,B$ are well-opened games.  
-  Then $\sigma\sim\tau$ if and only if $\sigma$ and $\tau$ contain the same complete plays.
-\end{proposition}
-\begin{proof}
-  Suppose first that $\sigma$ and $\tau$ do not contain the same complete plays.  
-  So, without loss of generality, there is some complete $s\in\sigma\setminus\tau$.
-  Then we may define a strategy $\alpha \from \oc(\oc A \implies B) \implies \bC$ that behaves as follows.  
-  After the opening move $q$ in $\bC$, player $P$ plays precisely those moves in $\oc A \implies B$ that make up the sequence $s$.  
-  If player $O$ deviates from the sequence $s$ at any point, then player $P$ has no response under $\alpha$; if player $P$ succeeds in building up the entire sequence $s$, then she finishes by playing $a$ in $\bC$.
-  Note that $\alpha$ is not innocent in general.
-  It is clear then that $\sigma^\dag;\alpha=\skipp$ and $\tau^\dag;\alpha=\bot_{\bC}$.
-
-  Conversely, suppose that $\sigma\not\sim\tau$.  
-  Then, without loss of generality, there is some $\alpha \from \oc(\oc A\implies B) \implies \bC$ such that $\sigma^\dag;\alpha=\skipp$ and $\tau^\dag;\alpha=\bot_{\bC}$.  
-  Then we have some $\s\in\sigma^\dag\|\alpha$ such that $\s\vert_{\bC}=qa$, and $\s\vert_{\oc A \implies B}$ decomposes into `threads' which are plays of $\oc A \implies B$, one for each initial move occurring in that sequence.
-  By the well bracketing condition, every one of these threads is itself a complete play in $\oc A \implies B$.  
-  Every one of these sequences is contained in $\sigma$; if they were all contained in $\tau$, then we would have $\s\in\\tau^\dag\|\alpha$, which would be a contradiction, so we end up with a complete sequence contained in $\sigma\setminus\tau$.
-\end{proof}

### 2020-04-04 Thesis/pmonads.tex
Corrections.

@@
 
-Since a monoid in a monoidal category $\mathcal X$ is the same thing as a lax monoidal functor from the unit category into $\mathcal X$, the definition of a monad on a category $\C$ (i.e., a monoid in $[\C,\C]$) may be generalized to that of a \emph{lax action} \cite{LaxActions} of a monoidal category $\X$ on $\C$; i.e., a lax monoidal functor $\X \to [\C,\C]$ (so that a monoid in $\C$ is a lax action of the unit category on $\C$).
+Since a monoid in a monoidal category $\mathcal X$ is the same thing as a lax monoidal functor from the unit category into $\mathcal X$, the definition of a monad on a category $\C$ (i.e., a monoid in $[\C,\C]$) may be generalized to that of a \emph{lax action} \cite{LaxActions} of a monoidal category $\X$ on $\C$; i.e., a lax monoidal functor $\X \to [\C,\C]$ (so that a monad on $\C$ is a lax action of the unit category on $\C$).
 
@@
 \begin{definition}
-  A \emph{\Mellies morphism} from $a$ to $b$ is one of the form
+  A \emph{\Mellies morphism} from $a$ to $b$ is a morphism of the form
   \[
@@
 \end{definition}
+
+\begin{remark}
+  In what follows, the object $x$ will be part of the data of the \Mellies morphism, so a \Mellies morphism from $a$ to $b$ is a pair $(x,f)$, where $f\from a \to x.b$ is an ordinary morphism.  
+  We will omit the $x$ when it is clear from the context.
+\end{remark}
 
@@
 \end{definition}
+
+Having defined our basic notion of composition, we can move on to our main constructions.
+We start with some definitions that will help us navigate size issues.
+
+\begin{definition}
+  Let $\C$ be a category.  
+  An \emph{ancestral set} (see \cite{AllGoodCategories}) for $\C$ is a set $\A$ of objects of $\C$ such that for any object $a$ of $\C$, there is an object $a'\in\A$ and a morphism $f \from a' \to a$.
+  A \emph{descendent\footnote{This is not a typo -- \emph{descendent} is the adjectival form of the noun \emph{descendant}.} set} for $\C$ is an ancestral set for $\oppcat\C$; i.e., a set $\D$ of objects of $\C$ such that for any object $a$ of $\C$, there is an object $a'\in\D$ and a morphism $f \from a \to a'$.
+\end{definition}
+
+We are interested in (small) ancestral and descendent sets, because they help guarantee the existence of certain large limits and colimits in $\Set$.
+
+\begin{proposition}[\cite{AllGoodCategories}]
+  i) Let $J \from \X \to \Set$ be a diagram, where $\X$ has a small ancestral set $\A$.
+  Then $J$ has a limit in $\Set$.
+
+  ii) Let $J\from \YY \to \Set$ be a diagram, where $\YY$ has a small descendent set $\D$.
+  Then $J$ has a colimit in $\Set$.
+  \label{PropAllGoodCategories}
+\end{proposition}
+\begin{proof}
+  (i): The limit is given by the set
+  \[
+    l = \left\{(\xi_a) \in \prod_{a\in A}J(a) \suchthat \forall f \from a \to x, g \from b \to x,\,J(f)(\xi_a)=J(g)(\xi_b)\right\}\,,
+    \]
+  where $f$ and $g$ range over all morphisms from objects in $\A$ to general objects of $\X$.
+
+  (ii): The colimit is given by the set
+  \[
+    c = \sum_{d \in \D} J(d) / \sim\,,
+    \]
+  where $\sim$ is the equivalence relation on pairs $(d, \eta_d)$ (for $d\in \D$ and $\eta_d\in J(d)$), generated by
+  \[
+    \left(\exists y\from \YY, f\from d \to y,g\from e \to y \esuchthat J(f)(\eta_d) = J(g)(\eta_{e})\right) \mathrel{\Rightarrow} (d,\eta_d) \sim (e,\eta_e)\,.
+    \]
+  The proofs that these are indeed a limit and a colimit for the corresponding diagrams are very similar to the proofs for ordinary small limits and colimits in $\Set$.  
+  However, the constructions we have made above rely on more than the fact that $\Set$ is complete and cocomplete.  
+  We also need to be able to perform universal and existential quantification over large collections of objects; this corresponds to the category-theoretic fact that if we have any (possibly large) collection of monomorphisms
+  \[
+    A_i \to B
+    \]
+  in $\Set$ (for fixed $B$), then we can form their intersection (i.e., a category-theoretic pullback for the collection), and similarly that we can form the pushout of any (possibly large) collection of epimorphisms out of a set.
+  See \ref{AllGoodCategories} for full details.
+\end{proof}
+
+\begin{definition}
+  Let $\X$ be a monoidal category.  
+  Given an object $x$ of $\X$, a \emph{tensor-descendent set for $x$} is an ancestral set for the category of elements\footnote{See the proof of Proposition \ref{PropMonoidalFunctorIsColimitOfReaderAction}.} of the functor $\X(\blank\tensor\blank,x) \from \oppcat\X \times \oppcat\X \to \Set$; i.e., a set $\D_x$ of objects of $\X$ such that for any morphism
+  \[
+    f \from y \tensor z \to x
+    \]
+  there exist $y',z'\in \D_x$ and morphisms $h \from y \to y'$, $k \from z \to z'$, $\tilde f \from y'\tensor z' \to x$ such that the following diagram commutes.
+  \[
+    \begin{tikzcd}
+      y \tensor z \arrow[r, "h \tensor k"] \arrow[dr, "f"']
+        & y' \tensor z' \arrow[d, "\tilde f"] \\
+      %
+        & x
+    \end{tikzcd}
+    \]
+  We say that $\X$ is \emph{well-tensored} if every object $x$ of $\X$ has a small tensor-descendent set.
+  \label{DefWellTensored}
+\end{definition}
+
 \begin{definition}[\cite{ThesisForDays}]
-  Let $\X$ be a monoidal category and let 
+  Let $\X$ be a well-tensored monoidal category and let 
   \[
@@
 
+\begin{remark}
+  The reason that we need well-tensoredness of $\X$ is to ensure that the coend above is a small set.  
+  Indeed, let
+  \[
+    [y, z, a, b, f]
+    \]
+  be an arbitrary element of the coend (for $y,z\from \X$, $a\in F(y)$, $b\in G(z)$ and $f \from y\tensor z \to x$).  
+  Given a small tensor-descendent set $\D_x$, we can find $y',z'\in \D_x$ and morphisms $h \from y \to y'$, $k \from z \to z'$ and $\tilde{f} \from y'\tensor z' \to x$ as in Definition \ref{DefWellTensored}.
+  Then we have
+  \[
+    [y, z, a, b, f] = [y', z', F(h)(a), F(k)(b), \tilde{f}]\,.
+    \]
+  It follows that the coend is a subset of the small set
+  \[
+    \sum_{y',z'\in \D_x} F(y') \times G(z') \times \X(y'\tensor z',x)\,,
+    \]
+  and is therefore itself small.
+
+  We could alternatively have deduced this from Proposition \ref{PropAllGoodCategories}, using the fact that the coend above may be recast as a colimit indexed by the opposite of the category of elements of $\X(\blank\tensor\blank,x)$.
+\end{remark}
+
 \begin{definition}[\cite{MelliesCategory}]
-  Given a lax action of a monoidal category $\X$ upon a category $\C$, the \emph{\Mellies category} of the action is an $[\X,\Set]$-enriched category $\Mell_\X\C$ whose objects are the objects of $\C$ and where the hom objects are given by
+  Given a lax action of a well-tensored monoidal category $\X$ upon a category $\C$, the \emph{\Mellies category} of the action is an $[\X,\Set]$-enriched category $\Mell_\X\C$ whose objects are the objects of $\C$ and where the hom objects are given by
   \[
@@
 For our purposes, however, we will want to use a single ordinary category that captures as much as possible of the structure of the \Mellies category.
-Let us assume for now that $\X$ is a small category.  
+Suppose that $\X$ has, in addition, a small descendent set.
 Then we have a functor
@@
 We then conclude by changing base through this colimit functor.  
-It turns out to be fairly easy to describe the resulting category directly.
+It turns out to be fairly easy to describe the resulting category directly, and we can drop the well-tensoredness condition.
 
 \begin{definition}
-  Let a monoidal category $\X$ act on a category $\C$ via a lax action.  
+  Let a monoidal category $\X$ with a small descendent set act on a category $\C$ via a lax action.  
   Then we define a new category $\C/\X$ where
@@
 \begin{remark}
-  We will not in general assume that $\X$ is a small category, as we do above, but we will assume that the colimits in Definition \ref{DefCX} do exist in $\Set$.  
-  If $\X$ is a small category, then they are small colimits so they exist automatically.
-  If the colimits do not exist, then we get a category that is not locally small.
+  If we follow Proposition \ref{PropAllGoodCategories} exactly, then the object $x$ in the \Mellies morphism $a \to x.b$ has to be contained in the small descendent set of $\X$.  
+  Instead, we shall stick to the traditional formulation of the colimit, as for small diagrams, only using Proposition \ref{PropAllGoodCategories} so that we can be sure that the colimit is a small set.
 \end{remark}
@@
     \end{tikzcd}
-    \and
     \qedhere
@@
 We will see later that these are the components of a natural transformation $\phi_{x,a}\from x.a \to a$ in $\C/\X$, generalizing the natural transformation $\phi_a \from Ma \to a$ in the Kleisli category for a monad $M$ that we met in Proposition \ref{pKleisli}.
-
-We will be meeting the following `factorization result', analogous to the corresponding result for Kleisli categories that we met in the previous section.
-If $f \from a \to x.b$ is a morphism in $\C$ then the corresponding \Mellies morphism $a \to b$ may be written as the following composite in $\C/\X$.
-\[
-  a \xrightarrow{Jf}
-  x.b \xrightarrow{\phi_{x,b}}
-  b\,.
-  \]
-Indeed, if we compute this composite in $\C$, then we get
-\[
-  a \xrightarrow{f}
-  x.b \xrightarrow{e_{x.b}}
-  I.x.b \xrightarrow{\id}
-  I.x.b \xrightarrow{m_{I,x,b}}
-  (I\tensor x).b\,,
-  \]
-which is equivalent to $f$ in $\C/\X$, because $e_{x.b};m_{I,x,b}=\lunit_x.b$, so $\lunit_x$ mediates between this morphism and $f$.
 
@@
 \begin{example}
-  If $\C = \BB \X$, $\D = \BB \YY$ are the delooping bicategories of monoidal categories $\X, \YY$ -- i.e., $\X$ and $\YY$ considered as bicategories with a single object -- then a lax functor $\C \to \D$ is the same thing as a lax monoidal functor $\X \to \YY$.
+  Given a monoidal category $\X$, write $\BB \X$ for the bicategory having a single object $*$, where $\BB\X(*,*)$ is the category $\X$ and composition of $1$-cells $x,y \from * \to *$ is given by
+  \[
+    x;y = x \tensor y\,.
+    \]
+  If $\C = \BB \X$, $\D = \BB \YY$ are the delooping bicategories of monoidal categories $\X, \YY$, then a lax functor $\C \to \D$ is the same thing as a lax monoidal functor $\X \to \YY$.  
 \end{example}
@@
 \begin{example}
-  More generally, a lax functor $F\from \BB \X \to \D$ is the same as a lax monoidal functor from $\X$ to the monoidal category of $1$-cells $F(*) \to F(*)$, where $*$ is the unique object of $\BB\X$.
+  More generally, a lax functor $F\from \BB \X \to \D$ is the same as a lax monoidal functor from $\X$ to the monoidal category of $1$-cells $F(*) \to F(*)$.
   In particular, a lax functor $1\to \Cat$ is the same thing as a monad and a lax functor $\BB\X \to \Cat$ is the same thing as a parametric monad parameterized by $\X$.
@@
   Let $F \from \C \to \D$ be a lax functor of bicategories.  
-  Then an \emph{oplax cocone under $F$} is given by an object $d$ of $\D$, together with $1$-cells
+  Then an \emph{oplax cocone under $F$} is given by an object $d$ of $\D$ (called the \emph{tip} of the cocone), together with $1$-cells
   \[
@@
 
+\begin{definition}[\cite{BasicBicategories}]
+  Let $(d, l, \mu)$, $(d', l', \mu')$ be oplax cocones for a lax functor $F \from \C \to \D$.  
+  Then a \emph{modification of oplax cocones} $l \to l'$ is given by a collection of $2$-cells
+  \[
+    \delta_c \from l_c \Rightarrow l_c'
+    \]
+  for each object $c$ of $\C$, such that the following diagram commutes for any $1$-cell $h \from c \to c'$ in $\C$.
+  \[
+    \begin{tikzcd}[arrows=Rightarrow]
+      F(h);l_{c'} \arrow[r, "\mu_h"] \arrow[d, "F(h);\delta_{c'}"']
+        & l_c \arrow[d, "\delta_c"] \\
+      F(h);l_{c'}' \arrow[r, "\mu_h'"]
+        & l_c'
+    \end{tikzcd}
+    \]
+\end{definition}
+
 \begin{definition}[\cite{Gepner}]
   Let $F \from \C \to \D$ be a lax functor of bicategories.  
-  Then a \emph{lax colimit} of $F$ is an oplax cocone $(u,k,\nu)$ under $F$ such that if $(d,l,\mu)$ is any other oplax cocone then there is a unique $1$-cell $\hat{l} \from u \to d$ such that $k_c;\hat{l}=l_c$ for each object $c$ of $\C$ and such that $\nu_h\hat{l}=\mu_h$ for any $1$-cell $h\from c \to c'$ in $\C$.
+  Then a \emph{lax colimit} of $F$ is an oplax cocone $(u,k,\nu)$ under $F$ such that 
+  \begin{itemize}
+    \item if $(d,l,\mu)$ is any other oplax cocone under $F$ then there is a unique $1$-cell $\hat{l} \from u \to d$ such that $k_c;\hat{l}=l_c$ for each object $c$ of $\C$ and such that $\nu_h\hat{l}=\mu_h$ for any $1$-cell $h\from c \to c'$ in $\C$; and
+    \item if $(d,l',\mu')$ is another oplax cocone under $F$ with tip $d$ and $\delta \from l \Rightarrow l'$ is a modification of oplax cocones, then there is a unique $2$-cell $\hat{\delta} \from \hat{l} \Rightarrow \hat{l'}$ such that $h_c;\hat{\delta}=\delta_c$ for all objects $c$ of $\C$.
+  \end{itemize}
 \end{definition}
@@
 \begin{remark}
-  The definition of a lax colimit is normally weaker than the one we have given, in that the equations $k_c;\hat l = l_c$ and $\nu_h\hat l = \mu_h$ are not required to hold exactly, but instead up to coherent isomorphism.
+  Our definition of a lax colimit $(u,k,\nu)$ tells us that if $d$ is an object of $\C$, then there is an isomorphism of categories from the category $\C(u, d)$ to the category of oplax cocones under $F$ with tip $d$, with morphisms given by modifications of oplax cocones.
+  As a consequence, any two lax colimits for the same diagram are uniquely isomorphic as cocones.
+
+  There is a more usual definition of an oplax cocone, in which this isomorphism of categories is weakened to an equivalence.
   The distinction is not important for our purposes, since the lax colimits we will be considering will all satisfy our stronger definition.
@@
   Let $F,G \from \C \Rightarrow \D$ be lax functors and let $t \from F \Rightarrow G$ be an oplax natural transformation.  
-  Suppose that $F$ and $G$ have lax colimits $\tilde{F}$ and $\tilde{G}$.  
+  Suppose that $F$ and $G$ have lax colimits with tips $\tilde{F}$ and $\tilde{G}$.  
   Then $t$ naturally gives rise to a lax functor $\tilde{F} \to \tilde{G}$ in a way that respects composition and identity of lax natural transformations.
@@
     \item the objects of $\int F$ are pairs $(a, m)$, where $a$ is an object of $\C$ and $m$ an object of $F(a)$;
-    \item the $1$-cells $(a, m) \to (b, n)$ are pairs $(h, f)$, where $h$ is a morphism $b \to a$ and $f$ is a morphism $m \to F(h)(n)$; and
+    \item the $1$-cells $(a, m) \to (b, n)$ are pairs $(h, f)$, where $h$ is a $1$-cell $b \to a$ and $f$ is a morphism $m \to F(h)(n)$ in $F(a)$; and
     \item the $2$-cells $(h, f) \Rightarrow (k, g) \from (a,m) \to (b,n)$ are $2$-cells $\phi\from h \Rightarrow k$ in $\C$ that make the following diagram commute.
@@
 \begin{definition}
-  Given a bicategory $\C$, we write $\pi_*\C$ for the ordinary category whose objects are the objects of $\C$ and where the morphisms $a\to b$ are the connected components of the $1$-cells $a\to b$ in $\C$: i.e., equivalence classes of $1$-cells $a\to b$ under the equivalence relation generated by relating $f\from a \to b$ to $g \from a \to b$ if there is a $2$-cell $\phi \from f \to g$.
+  Let $\C$ be a bicategory, and suppose that whenever $a,b$ are objects of $\C$, the category $\C(a,b)$ of $1$-cells has a small descendent set.
+  Then we write $\pi_*\C$ for the ordinary category whose objects are the objects of $\C$ and where the morphisms $a\to b$ are the connected components of the $1$-cells $a\to b$ in $\C$: i.e., equivalence classes of $1$-cells $a\to b$ under the equivalence relation generated by relating $f\from a \to b$ to $g \from a \to b$ if there is a $2$-cell $\phi \from f \to g$.
 \end{definition}
@@
 \begin{proposition}[{\cite[\sec 3]{nlab:2-limit}}]
-  Let $\C$ be a bicategory and let $F\from \C \to \Cat$ be a lax functor.  
-  Then $\pi_*\int F$ is the lax colimit of $F$.
+  Let $\C$ be a bicategory such that $\C(a,b)$ has a small descendent set for every pair $(a,b)$ of objects of $\C$, and let $F\from \C \to \Cat$ be a lax functor.  
+  Then $\pi_*\int F$ is a lax colimit for $F$.
   \label{PropGrotLaxLimit}
@@
 \begin{proof}
-  First, we define the lax cocone under $F$ with tip $\pi_*\int F$.
-  Given an object $a$ of $\C$, the arrow from $F(a)$ to $\pi_*F\int F$ is the functor $k$ defined by
+  First, we need to show that $\pi_*\int F$ is well defined; i.e., that each category $\int F((a,m), (b,n))$ of morphisms in $\int F$ has a small descendent set.  
+  Suppose that $\D$ is a small descendent set for $\C(b, a)$.
+  We claim that
+  \[
+    \{(h', f')\suchthat h'\in \D\,,f \from m \to F(h)(n)\}
+    \]
+  is a descendent set for $\int F((a,m), (b,n))$.
+
+  Indeed, let $(h,f) \from (a, m) \to (b, n)$ be a morphism in $\int F$ -- so $h \from b \to a$ is a $1$-cell in $\C$ and $f$ is a morphism $m \to F(h)(n)$ in $F(a)$.
+  Let $h'\in \D$ be such that there exists a $2$-cell $\phi \from h \Rightarrow h'$ and let $f'\from m \to F(h')(n)$ be given by the composite
+  \[
+    m \xrightarrow{f} F(h)(n) \xrightarrow{(F\phi)_n} F(h')(n)\,.
+    \]
+  Then $\phi$ is a $2$-cell from $(h,f)$ to $(h',f')$ in $\int F((a,m),(b,n))$.
+
+  Now we have assured ourselves that there are no size problems, we define the oplax cocone under $F$ with tip $\pi_*\int F$.
+  Given an object $a$ of $\C$, the arrow from $F(a)$ to $\pi_*\int F$ is the functor $k$ defined by
   \begin{mathpar}
@@
 
-  We now need to show that the appropriate diagrams commute to ensure that $\left(\pi_*\int F,k,\nu\right)$ is a lax cocone under $F$.
+  We now need to show that the appropriate diagrams commute to ensure that $\left(\pi_*\int F,k,\nu\right)$ is a oplax cocone under $F$.
   For the first diagram, we must show that the following commutes for any $2$-cell $\phi\from h' \Rightarrow h\from a \to a'$ and any object $m$ of $F(a)$.
@@
 
-  Now, suppose that $(\D,l,\mu)$ is another lax cocone under $F$.  
+  Now, suppose that $(\D,l,\mu)$ is another oplax cocone under $F$.  
   We define
@@
   and therefore $j=\hat{l}$.
+
+  Lastly, suppose that $(l',\mu')$ is another oplax cocone with tip $\D$ under $F$, and let $\delta \from l \Rightarrow l'$ be a modification of oplax cocones.  
+  Then, for each object $a$ of $\C$ and each object $m$ of $F(a)$, we have a morphism
+  \[
+    \delta_{a,m} \from l_a(m) \to l_a'(m)\,.
+    \]
+  We claim that these $\delta_{a,m}$ form the components of a natural transformation $\hat{\delta} \from \hat{l} \Rightarrow \hat{l'}$.  
+  Indeed, if $(h, f) \from (a, m) \to (b, n)$ is a morphism in $\int F$, then we have the following commutative diagram.
+  \[
+    \begin{tikzcd}[column sep=30pt]
+      l_a(m) \arrow[r, "{\delta_{a,m}}"] \arrow[d, "l_a(f)"']
+        & l_a'(m) \arrow[d, "l_a'(f)"] \\
+      l_a(F(h)(n)) \arrow[r, "{\delta_{a, F(h)(n)}}"] \arrow[d, "(\mu_h)_n"']
+        & l_a'(F(h)(n)) \arrow[d, "(\mu_h')_n"] \\
+      l_b(n) \arrow[r, "{\delta_{b,n}}"]
+        & l_b'(n)
+    \end{tikzcd}
+    \]
+  Here, the top square commutes because $\delta_a$ is a natural transformation, while the bottom commutes because $\delta$ is a modification of oplax cocones.
+
+  Now we have
+  \[
+    (k_a;\hat{\delta})_m = \hat{\delta}_{k_a(m)} = \delta_{a,m}\,,
+    \]
+  as desired.
 \end{proof}
@@
 
-More generally, if $\X$ is a monoidal category and $F\from \BB \X \to \Cat$ is a lax functor, corresponding to a lax action of $\X$ upon $\C = F(*)$, then it is easy to see that $\pi_*\int F$ is isomorphic to the category $\C/\X$ that we defined earlier.
+More generally, if $\X$ is a monoidal category with a small descendent set, then $\BB\X$ satisfies our smallness condition (all categories of $1$-cells have a small descendent set).  
+If $F\from \BB \X \to \Cat$ is a lax functor, corresponding to a lax action of $\X$ upon $\C = F(*)$, then it is easy to see that $\pi_*\int F$ is isomorphic to the category $\C/\X$ that we defined earlier.
 Indeed, in both cases the objects may be identified with the objects of $\C$, and the morphisms from an object $a$ to an object $b$ may be written as equivalence classes of morphisms $a \to x.b$ in $\C$ under the equivalence relation generated by relating $f\from a \to x.b$ to $g\from a \to y.b$ if there is a morphism $h\from x \to y$ in $\X$ such that $g=f;(h.b)$.
@@
 
-  In other words, there is a functor $J\from \C \to \C/\X$ and a natural transformation
+  In particular, there is a functor $J\from \C \to \C/\X$ and a natural transformation
   \[
@@
 
+\begin{remark}
+  Here, $J\from \C \to \C/\X$ is the identity on objects and sends a morphism $f \from a \to b$ in $\C$ to the \Mellies morphism
+  \[
+    a \xrightarrow{f} b \xrightarrow{e_b} I.b\,,
+    \]
+  while the component $\phi_{x,a}$ of $\phi$ is the identity
+  \[
+    x.a \to x.a\,,
+    \]
+  considered as a \Mellies morphism $x.a \to a$.
+\end{remark}
+
 Corollary \ref{CorTheConstructionUniversalProperty} tells us that $\C/\X$ is generated as a category by the objects and morphisms in $\C$, together with the special morphisms making up the natural transformation $\phi_{x,a}\from x.a \to a$.
@@
 \begin{proposition}
-  Let $F \from \C \to \Cat$ be a lax functor of bicategories.  
+  Let $F \from \C \to \Cat$ be a lax functor of bicategories, where $\C(a,b)$ has a small descendent set for any pair $(a,b)$ of objects of $\C$.
   Let $\A$ be a category.
@@
   \[
-    \laxcolim_{c\from\C,d\from\D} F(c)\times G(d) \cong \laxcolim_{c\from \C} F(c) \times \laxcolim_{d\from\D} G(d)\,.
+    \laxcolim_{c\from\C,d\from\D} (F(c)\times G(d)) \cong \laxcolim_{c\from \C} F(c) \times \laxcolim_{d\from\D} G(d)\,.
     \]
@@
 
+We shall now consider the $\C/\X$ construction in more depth, looking at the properties that $\C/\X$ has when $\C$ is also a monoidal category.  
+Until the end of the chapter, we assume that the monoidal category $\X$ has a small descendent set.
+
 \begin{definition}
@@
   Then the functor $\X\times\X\times\C\to \C$ that sends $(x,y,a)$ to $x.y.a$ is lax monoidal.  
-  Since $\X$ is symmetric monoidal, the tensor product $\blank\tensor\blank\from \X \times\X \to \X$ is a strong monoidal functor and so the functor $\X \times \X \times \C \to \C$ that sends $(x,y,a)$ to $(x\tensor y).a$ is lax monoidal.
-
-  We say that the action of $\X$ on $\C$ is \emph{monoidal} if the underlying functor $\X \times \C \to \C$ is a lax monoidal functor and the natural transformations $m_{x,y,a}$ and $e_a$ are monoidal natural transformations.
+  Since $\X$ is symmetric monoidal, the tensor product $\blank\tensor\blank\from \X \times\X \to \X$ is a strong monoidal functor and so the functor $\X \times \X \times \C \to \C$ that sends $(x,y,a)$ to $(x\tensor y).a$ is also lax monoidal.
+
+  We say that the action of $\X$ on $\C$ is \emph{monoidal} if the underlying functor $\X \times \C \to \C$ is a lax monoidal functor and the natural transformations
+  \begin{mathpar}
+    m_{x,y,a} \from x.y.a \Rightarrow (x\tensor y).a \from \X \times \X \times \C \to \C
+    \and
+    e_a \from a \Rightarrow I.a \from \C \to \C
+  \end{mathpar}
+  are monoidal natural transformations.
   \label{DefMonoidalLaxAction}
@@
 \begin{proposition}
-  Suppose that $\X$ is a symmetric monoidal category, and that we have a symmetric monoidal lax action of $\X$ on another monoidal category $\C$.  
+  Suppose that $\X$ is a symmetric monoidal category, and that we have a monoidal lax action of $\X$ on another monoidal category $\C$.  
   Then $\C/\X$ inherits the structure of a monoidal category and the natural functor $J\from \C \to \C/\X$ is strict monoidal.
@@
     \]
-  where the last arrow is given by the unique symmetric monoidal isomorphism, and with unital coherence $e_a$ given by
+  where the last arrow is given by the unique symmetric monoidal isomorphism; and with unital coherence $e_a$ given by
   \[
@@
 
-Note that this result is not the sharpest possible, since they do not consider the case that there may be more complicated zigzags mediating between the morphisms.
+Note that these results is not the sharpest possible: there may well be more complicated zigzags mediating between the morphisms.
 Nevertheless, they are sufficient for our purposes.
@@
 An obvious idea for constructing the morphisms $f,f_0$ is to look at the case that $\X$ is itself Cartesian, taking $f$ to be the diagonal and $f_0$ the terminal morphism.
-Note, however, that this does not automatically mean that the diagrams in Proposition \ref{PropCartesianness} commute: for example, the trivial category and the category of sets are both presheaf categories and hence Cartesian closed, but if $1$ acts on the category of sets via the powerset monad then the resulting monoidal category $\Set/1$ (i.e., the category of sets and relations) is not Cartesian.
+Note, however, that this does not automatically mean that the diagrams in Proposition \ref{PropCartesianness} commute: for example, the trivial category and the category of sets are both presheaf categories and hence Cartesian closed, but if $1$ acts on the category of sets via the powerset monad then the resulting monoidal category $\Set/1$ (i.e., the category of sets and relations with the set-theoretic product) is not Cartesian.
 
@@
 \begin{proposition}
-  Let $\C$ be a cocomplete monoidal category, and suppose that a symmetric monoidal category $\X$ acts on $\C$ via a symmetric monoidal action in the sense of Definition \ref{DefMonoidalLaxAction}.  
+  Let $\C$ be a cocomplete monoidal category, and suppose that a symmetric monoidal category $\X$ with a small descendent set acts on $\C$ via a symmetric monoidal action in the sense of Definition \ref{DefMonoidalLaxAction}.
   Define a functor $\C \to \C$ by
@@
 \begin{proposition}[\cite{Pisani}]
-  Let $\X,\YY$ be a monoidal category and let the functor category $[\YY,\Set]$ be equipped with the Day convolution product.
-
-  Given a functor $F \from \X \times \YY \to \Set$, we have an associated functor $\Lambda(F) \from \X \to [\YY,\Set]$.
+  Let $\X,\YY$ be monoidal categories, where $\X$ is well-tensored, and let the functor category $[\X,\Set]$ be equipped with the Day convolution product.
+
+  Given a functor $F \from \YY \times \X \to \Set$, we have an associated functor $\Lambda(F) \from \YY \to [\X,\Set]$.
   Then $F$ is lax monoidal if and only if $\Lambda(F)$ is lax monoidal.
@@
 \begin{proposition}
-  Let $j \from \X \to \Set$ be an oplax symmetric monoidal functor between symmetric monoidal categories.
+  Let $j \from \X \to \Set$ be an oplax symmetric monoidal functor between symmetric monoidal categories, where $\X$ is well-tensored.
   Let $\oppcat\X$ act on $\Set$ via the reader action induced by $j$.
@@
 \begin{corollary}
-  Let $j\from \X \to \Set$ be a symmetric monoidal functor.  
+  Let $j\from \X \to \Set$ be a symmetric monoidal functor, where $\X$ has a small ancestral set (so $\oppcat \X$ has a small descendent set).
   Let $\oppcat\X$ act on $\Set$ via the induced reader action.  
@@
 
+\begin{remark}
+  If the category $\X$ that we have constructed has a small ancestral set, this means that $\Set/\oppcat \X$ is isomorphic to the category obtained from $\Set$ via base change through $F$.
+
+  If $\X$ has not got a small ancestral set, then this is still true, except that now $\Set/\oppcat \X$ is not technically defined.
+  This is not really important: we only need $\oppcat \X$ to have a small descendent set so that we can prove that $\colim_{x\from\X}[jx,A]$ is a small set, but in this case we know that anyway -- $\colim_{x\from \X}[jx,A] \cong F(A)$!
+
+  In any case, our main examples will satisfy the smallness conditions on $\X$ that we have been working with up to this point.
+\end{remark}
+
 \begin{example}
@@
 
+  Suppose that $(\Omega,\F,\bP)$ is such that $\F$ contains all singleton sets (and hence all countable sets) and that if $Y\in\F$ has measure $0$ (i.e., $\bP(Y)=0$) and $Z\subset Y$, then $Z\in \F$.
   Write $\RV_\Omega \from \Set \to \Set$ for the functor that sends a set $A$ to the set of all random variables taking values in the set $A$ and sends a function $f\from A \to B$ to the function
@@
 
-  Moreover, $\RV_\Omega$ is a lax monoidal functor: if $V,W$ are discrete random variables taking values in sets $A,B$, then we have a random variable 
-  \[
-    \langle V,W \rangle\from X \to A\times B
-    \]
-  given by pairing (and if $(a,b)\in A\times B$, then 
-  \[
-    (\langle V,W\rangle)\inv(\{(a,b)\}) = V\inv(\{a\})\cap W\inv(\{b\})\,,
-    \]
-  so this is a measurable function).
+  Moreover, $\RV_\Omega$ is a lax monoidal functor: if $V,W$ are discrete random variables taking values in sets $A,B$, then we can define
+  \[
+    \langle V,W \rangle\from \Omega \to A\times B
+    \]
+  given by pairing.
+
+  \begin{proposition}
+    $\langle V,W \rangle$ is a measurable function, so this is a random variable.
+    \label{PropRandomVariablePairing}
+  \end{proposition}
+  \begin{proof}
+    Any discrete random variable is countably supported.  
+    This means that there are countable $\hat A \subset A$, $\hat B\subset B$ such that $V\inv(\hat A)$ and $W\inv(\hat B)$ are measurable and have measure $1$.
+    Now let $U\subset A \times B$.  
+    Write $\hat U = U \cap (\hat A \times \hat B)$.  
+    Then
+    \begin{IEEEeqnarray*}{rCl}
+      \langle V,W \rangle\inv(\hat U) & = & \langle V,W \rangle \inv(U) \cap \langle V,W \rangle \inv (\hat A \times \hat B) \\
+      & = & \langle V,W \rangle\inv (U) \cap V\inv(\hat A) \cap W\inv(\hat B)\,,
+    \end{IEEEeqnarray*}
+    which is countable and therefore measurable, while
+    \[
+      \langle V,W \rangle\inv(U \setminus \hat U) \subset (\Omega \setminus \hat A) \cup (\Omega \setminus \hat B)\,,
+      \]
+    which is measurable of measure $0$, meaning that $\langle V,W \rangle\inv (U \setminus \hat U)$ is measurable and has measure $0$, by hypothesis.
+    Therefore, $\langle V,W \rangle \inv(U)$ is the union of two measurable sets and is therefore measurable.
+  \end{proof}
 
@@
   Since the terminal morphism from $(A,V)$ to $(1,())$ is also probability preserving, the category $\Set/\oppcat{\Rv_\Omega}$ will be Cartesian closed.
+  \label{ExRandomVariables}
 \end{example}
@@
 \section{Actions of categories with terminal objects}
+\label{SecActionsOfCategoriesWithTerminalObjects}
 

### 2020-04-04 Thesis/promonads.tex
Corrections.

@@
 The first half of this chapter is, in the interests of completeness, fairly technical, and may be skimmed over on a first reading.  
-In chapter \ref{SecEndoprofunctors}, we introduce the multicategory of endoprofunctors on a category $\C$, which generalizes the monoidal category of endofunctors on $\C$.  
+In Section \ref{SecEndoprofunctors}, we introduce the multicategory of endoprofunctors on a category $\C$, which generalizes the monoidal category of endofunctors on $\C$.  
 As monoids in $\End(\C)$ are called monads on $\C$, so we will call monoids in $\Endoprof(\C)$ \emph{promonads} on $\C$.  
-We will observe that a promonad may be regarded as a sort of category, and that the Kleisli category may be characterized as the embedding of monads on $\C$ into promonads on $\C$.
-
-The main result will then be to show that an $\X$-parametric promonad on a category $\C$ -- i.e., a multifunctor $\X \to \Endoprof(\C)$ -- may be regarded as a sort of $[\X,\Set]$-enriched category, and that the \Mellies category may similarly be regarded as an embedding of $\X$-parametric monads on $\C$ into $\X$-parametric promonads on $\C$.
+We will observe that a promonad may be regarded as a sort of category, and that the Kleisli category for a monad $M$ is precisely the category we get by considering $M$ as a promonad.
+
+The main result will then be to show that an $\X$-parametric promonad on a category $\C$ -- i.e., a multifunctor $\X \to \Endoprof(\C)$ -- may be regarded as a sort of $[\X,\Set]$-enriched category, and that the \Mellies category for a parametric monad may similarly be regarded as the $[\X,\Set]$-enriched category that we get by regarding that parametric monad as a parametric promonad.
 
@@
   \end{mathpar}
-  If we're being careful, then we should note that the expression $a_1 \tensor \cdots \tensor a_n$ does not define a single object of $\M$, since the tensor product is not in general strictly associative.
-  Since the tensor product is not necessarily strictly associative, it is not obvious exactly what we mean by $a_1 \tensor \cdots \tensor a_n$.
+  If we're being careful, then we should note that the expression $a_1 \tensor \cdots \tensor a_n$ does not define a single object of $\M$.
+  Since the tensor product is not necessarily strictly associative, the choice of bracketing in the expression $a_1 \tensor \cdots \tensor a_n$ affects which object we end up with.
   It is enough to fix any one of the possible bracketings (e.g., to make $\blank\tensor\blank$ always associate to the right).
@@
 
-The reason why we refer to a functors $F\from \oppcat\C,\D \to \V$ as a \emph{profunctors} $\C \pto \D$ is that they generalize ordinary functors $\C \to \D$.  
-Specifically, if $F \from \C \to \D$ is a functor, then we can identify it with the profunctor
-\[
-  \tilde{F}(d,c) = \D(d, F(c)) \from \oppcat \D, \C \to \V\,.
+The reason why we refer to a functors $F\from \oppcat\C,\D \to \V$ as a \emph{profunctors} $\C \pto \D$ is that they generalize ordinary functors.
+Specifically, if $F \from \D \to \C$ is a functor, then we can identify it with the profunctor
+\[
+  \tilde{F}(c,d) = \C(c, F(d)) \from \oppcat \C, \D \to \V\,.
   \]
@@
   \[
-    \hat{F_1},\cdots,\hat{F_n} \to \hat{G}\,.
+    \tilde{F_1},\cdots,\tilde{F_n} \to \tilde{G}\,.
     \]
@@
 \begin{remark}
-  Suppose that $\M$ is the category of sets, regarded as a multicategory through its Cartesian structure.  
+  Suppose that $\X$ is small and suppose that $\M$ is the category of sets, regarded as a multicategory through its Cartesian structure.  
   Let $x_1,\cdots,x_n,y_1,\cdots,y_p$ be objects of $\X$.  
@@
     \]
-  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, or when the category $\M$ is not the enriching multicategory.
+  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, if $\X$ is large, or when the category $\M$ is not the enriching multicategory.
 \end{remark}
@@
 \begin{definition}
-  Let $\X$ be a monoidal category.  
+  Let $\X$ be a small monoidal category.  
   We have a multifunctor
@@
   \label{StokessTheorem}
-  Let $\X$ be a monoidal category and let $\C$ be a category.  
+  Let $\X$ be a small monoidal category and let $\C$ be a category.  
   Then we have an isomorphism of multicategories

### 2020-06-14 Thesis/games.tex
Update references; one typo; fix broken links.

@@
 To introduce our material, we will go back over some old ground, namely the fully abstract game semantics for Idealized Algol developed by Abramsky and McCusker in \cite{SamsonGuyIAActive}.  
-In keeping with the spirit of this thesis, we will aim to use category theoretic methods, and so our proofs of soundness and adequacy will depart from those given by Abramsky and McCusker, and will instead involve coalgebraic ideas developed by Laird in \cite{laird02} and \cite{LairdCofCommCom}.
+In keeping with the spirit of this thesis, we will aim to use category theoretic methods, and so our proofs of soundness and adequacy will depart from those given by Abramsky and McCusker, and will instead involve coalgebraic ideas developed by Laird in \cite{laird02} and \cite{FunctionalProgramsAsCoroutines}.
 

### 2020-06-14 Thesis/intro.tex
Update references; one typo; fix broken links.

@@
 However, in the presence of countable nondeterminism, there exist definable terms that can be distinguished in the model that cannot be distinguished by definable elements, but can be distinguished by non-computable functions.
-An example of such a function is found in Proposition \ref{PropNotFullyAbstract}; the general idea is due to Kleene and can be found in \cite{KleeneTree}.
+An example of such a function is found in Section \ref{SecNonComputable}; the general idea is due to Kleene and can be found in \cite{KleeneTree}.
 

### 2020-06-14 Thesis/pmonads.tex
Update references; one typo; fix broken links.

@@
   in $\Set$ (for fixed $B$), then we can form their intersection (i.e., a category-theoretic pullback for the collection), and similarly that we can form the pushout of any (possibly large) collection of epimorphisms out of a set.
-  See \ref{AllGoodCategories} for full details.
+  See \cite{AllGoodCategories} for full details.
 \end{proof}
@@
 
-Note that these results is not the sharpest possible: there may well be more complicated zigzags mediating between the morphisms.
+Note that these results are not the sharpest possible: there may well be more complicated zigzags mediating between the morphisms.
 Nevertheless, they are sufficient for our purposes.
@@
 \begin{example}
+  \label{ExRandomVariable}
   An alternative way of dealing with probability that does satisfy the condition for Cartesianness of the resulting category.
